### 2021-07-02 prism-backend/docs/protocol/tex/article.tex
Add clean protocol description (#2254)
This commit adds the protocol description in a compact document

\documentclass[10pt,a4paper]{article}

\title{PRISM protocol v0.3}

\author{Atala PRISM team - IOG}

\date{}

\begin{document}

\maketitle

\begin{abstract} 
This document describes the current state of the protocol that supports PRISM. PRISM is a framework for the management of decentralized identifiers and verifiable credentials. 
\end{abstract}

\setcounter{tocdepth}{3}

\tableofcontents 
\newpage

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\section{Introduction and protocol description}

In this section we will informally describe a protocol to create and manage DIDs (\textbf{D}ecentralized textbf{Id}entifiers), that also allows to manage the creation, revocation and presentation of verifiable credentials.

\subsection{DIDs management}

For simplicity, we will define a DID as a string identifier of the form

\begin{center}
	\emph{did:prism:<identifier>}
\end{center}

Each DID is associated to a list of public keys. The list can be updated over time by adding and revoking keys. Each key has an assigned role during its lifetime. The three possible roles we describe are:

\begin{description}
\item[issuing keys] used to issue credentials on behalf of the DID.
\item[revocation keys] used to revoke credentials on behalf of the DID.
\item[master keys] used to add or revoke other keys associated to the DID.
\end{description}

Our construction for DID management relies on an underlying blockchain. The blockchain allows us to publish transactions with sufficiently large metadata. We use the blockchain for both; data distribution along parties, and for consensus related to the order of relevant events in our protocol. All the parties participating in our protocol are running a full node that reads the metadata of the blockchain transactions. When they find a protocol event, they process it to construct their view of the system.

In the following sub-sections we describe the events in our protocol related to DID management.

\subsubsection{DID creation}

In order to create a DID, a user will follow the steps below:

\begin{itemize}
\item The user generates a desired list of public keys. He will associate each key to a key identifier and a role.
      There must be at least one key with the master role in this initial list.
\item The resulting list is encoded and hashed producing an encoded \emph{initial\_state} and a \emph{hash}.
\item The \emph{hash} is encoded in hexadecimal form producing an \emph{encoded\_hash}.
\item The user DID is constructed as \emph{did:prism:encoded\_hash}.
\item The user will send in the metadata of a blockchain transaction a signed \emph{CreateDID} event. 
      The event contains the list of public keys with their identifiers and roles.
      The signature will be performed using the private key associated to any of the master keys in the initial list of keys.
\end{itemize}

Once the transaction is added to the blockchain with a sufficient number of confirmations $d$ (i.e. the block containing the transaction has $d$ blocks appended after it on the underlying chain), all the participants following our protocol will validate the signature of the CreateDID event. After verification, they will register the DID as \emph{published} along with all the keys posted in the initial list. The keys will be considered valid since the time associated to the event carrier transaction. This is a timestamp generated by the blockchain.

Optionally, while waiting for blockchain confirmation, the user can also use the associated DID

\begin{center}
\emph{did:prism:encoded\_hash:initial\_state}
\end{center}

This DID, called \emph{long form} or \emph{unpublished} DID will not be recognised as \emph{published} by other parties in the protocol. However, other users would be able to verify that the list of keys encoded in \emph{initial\_state} corresponds to the DID \emph{did:prism:encoded\_hash}. The recipient of an unpublished DID needs to query the state of the \emph{short form} of the DID (the prefix before "\emph{:initial\_state}") to check for changes in the list of keys.

\subsubsection{DID update}

Updating a DID means that the user controlling a master key associated to it, will add new or revoke existing keys to the list associated to the DID. In order to update the list of keys, the user will:
\begin{itemize}
\item Create the list of key identifiers that the user wants to revoke from the current state of his DID.
\item Create a list of keys he wants to add to the list of keys associated to his identifier. 
      This keys must be associated to a role and a fresh key identifier.
\item Create an \emph{UpdateDID} event that contains the two previously generated lists.
\item Sign the even with one of the \emph{currently associated} master keys of the DID, and publish the event inside the metadata of a transaction.
\end{itemize}

When the event added to the blockchain with enough confirmations, all parties will process the event. This is, they will validate the signature, and update their internal knowledge of the updated DID. The newly added keys and the revoked keys will be timestamped using the time of the carrier transaction.

With these two events we have shown how to create and update DIDs.

\subsubsection{Obtain the list of keys associated to a DID}

Now, we can define the process that a protocol participant must follow to obtain the keys associated to a list. 
We mentioned that a DID can be presented in long form (or as an unpublished DID), or in its short form. Hence, we will describe the process in the two cases.

In order to obtain the keys associated to a DID in short form, we simply read the state we have constructed so far by processing the CreateDID and UpdateDID events we read from the blockchain. The list of DIDs associated to the DID is the list of keys we see in our internal state. If we do not find the DID as a published one in our state, we return a \emph{DID unknown} response.

Now, if the DID we receive is in long form, we first verify that $hash(initial\_state) = initial\_hash$. If that check fails we reply with an \emph{Invalid DID} response. If the check passes, we extract the short form of this DID (the prefix that ends right before the last \emph{":"}), and we check the list of keys as described in the previous paragraph. If the result of this process is a \emph{DID unknown} response, then we decode the list from the \emph{initial\_state} suffix and return this list as a result.

With this process we complete the events and operations related to DIDs. 
Lets now move into the events related to issue and revoke credentials.

\subsection{Verifiable credentials}

Now that we have DIDs, we can proceed to the creation and revocation of credentials. A \emph{credential} to us is a set of \emph{claims}. Each claim is represented by a property-value pair, e.g. $(name, John)$. Credentials are created by \emph{issuers} to \emph{subjects}. Both issuers and subjects are represented with their corresponding DIDs.

For practical reasons, we assume that issuers want to issue credentials in batches. This is, an issuer would like to create multiple credentials at once. Below we describe the steps to issue a batch of credentials.

\subsubsection{Credentials batch issuance}

In the following steps, we assume the issuer and subjects have already established a secure communication channel.
In order to issue a batch of an arbitrary number $N$ of credentials, the issuer will:
\begin{itemize}
\item Ask to each subject the DID they would like to use for the credential they will receive.
\item The issuer creates the credentials (sets of claims) for each subject. One of the claims is the subject DID.
      The issuer DID is also attached in the claims.
\item The issuer signs each individual credential with an \emph{issuing key} associated to his publicly known DID. 
      The signing key id is also attached to the credentials' claims.
\item The issuer computes a merkle root based on the list of signed credentials.
\item The issuer creates an \emph{IssueBatch} event that contains the merkle root, and signs the event with an \emph{issuing key} associated to his publicly known DID. 
      \textbf{Note}: Today we use the same issuing key for the event signature and the individual credentials signature, but those could be different keys.
\item The issuer attaches the signed event to the metadata of a transaction and sends it to the blockchain.
\item The issuer gives to each user their corresponding signed credential along with their associated merkle inclusion proof.
\end{itemize}

Likewise previous protocol events, all parties will process the transaction once confirmed, validate the event signature and timestamp the merkle root with the time associated to the carrier transaction.

Note that, to issue credential batches, the issuer DID \emph{must be published} already. However, users' DIDs can remain unpublished.

\subsubsection{Credentials revocation}

In order to revoke a credentials, issuers have two alternatives:
\begin{enumerate}
\item They revoke all the credentials in a batch.
      This is done by signing a \emph{RevokeBath} event with a \emph{revocation} key associated to the issuer DID.
      The signed event contains the merkle root to revoke.
\item They revoke specific credentials associated to a batch.
      This is done by signing a \emph{RevokeCredentials} event with a \emph{revocation} key associated to the issuer DID. 
      The signed event contains both the merkle root associated to the credentials to revoke, and the hashes of the specific credentials to revoke.
\end{enumerate}

In both variants, the event is published on-chain and processed by all the participants. The participants will timestamp the new information with the carrier transaction time.

\subsection{Credential presentation and verification}

Once they receive credentials from issuers, subjects will present them to interested parties, called \emph{verifiers}. For example, a student may receive a verifiable credential from a university, and would like to present his credential to a potential employer. In our setting, the verifier will be a party following our protocol events from the blockchain. The steps to present and verify a credential are the following:
\begin{itemize}
\item We assume a safe communication channel between the subject and verifier. 
      We also assume that the verifier has a DID $DID_{V}$ known by the subject.
\item The subject shares his credential and merkle inclusion proof to the verifier.
\item The verifier computes the merkle root from the inclusion proof and the credential hash; extracts the issuer DID and signing key id from the credential claims. Then, it retrieves from the state he computed from the blockchain, the timestamps associated to the merkle root, the issuing key, he also extracts the signing key and checks if the merkle root or credential hash has been revoked. With all that data, he validates the issuer signature and is able to determine if it was signed at a time when the issuer key was valid.
\item At this point, the verifier knows that the credential was properly signed. Now, he shares a nonce to the subject and asks him to sign it with a key associated to his DID.
\item The subject signs the hash of $nonce || DID_{V}$ and returns the signature to the verifier.
\item The verifier now checks the signature and concludes that the credential subject is indeed the person presenting it.
\end{itemize}

%----------------------------------------------------------------------------------------
%	PROPERTIES
%----------------------------------------------------------------------------------------

\section{Properties we believe we have}

\paragraph{Unforgeability.} A user cannot forge issuer-generated credentials.
\paragraph{Privacy against issuers.} An issuer does not learn whether a user (who acquired a credential from the issuer) has interacted with a given verifier (assuming no cooperation between issuer and verifiers).
\paragraph{Revocability.} An issuer can revoke a previously-issued credential without users’ cooperation.
\paragraph{Protection against credential reuse.} A verifier can ensure no credential is used by different DIDs. 
\paragraph{Deferred and offline verification checks.} A verifier can verify the revocation status of a credential asynchronously without users’ participation. A verifier can also verify a credential without contacting the internet, in which case the verification result is with respect to the last time the verifier synchronized with blockchain events.
\paragraph{Resistance to key rotation.} If an issuer's issuing key is revoked, credentials already issued by that key remain valid. This means that the issuer does not need to re-issue the credentials signed by a compromised issuing key. This is possible due to the fact that key revocation and credential issuances are timestamped. Hence, if an issuing key is revoked, credentials already issued remain valid unless they are explicitly revoked.
\paragraph{Independence of issuers and verifiers.} Verifiers only need to know which issuer DIDs they trust. They do not need to contact issuers to query issuance nor revocation lists.
\paragraph{Past preservation.} Any party that verifies a credential has non-reputable information of when the credential was valid even if it has been revoked.

\section{Properties we are not offering}

\paragraph{Unlinkability.} A coalition of verifiers cannot link activities of users across verifiers.
\paragraph{Minimal disclosure.} A user only reveals what is necessary to establish a relationship with a verifier.

%----------------------------------------------------------------------------------------
%	PROPOSED IDEAS
%----------------------------------------------------------------------------------------

% \section{Ideas to add missing properties}

\end{document}

### 2021-08-12 prism-backend/research/article.tex
nits

--- 2021-07-02 prism-backend/docs/protocol/tex/article.tex
@@
 \documentclass[10pt,a4paper]{article}
+\usepackage[margin=1in]{geometry}
 
@@
 \begin{center}
-	\emph{did:prism:<identifier>}
+	\emph{did:prism:$\langle$identifier$\rangle$}
 \end{center}
@@
 
+Lets us define first what a credential is in the context of this document
+
+\begin{description}
+\item[Credential] a credential is a JSON document that contains three key-value maps.
+ \begin{itemize}
+ \item the "issuer" key represents the issuer DID.
+ \item the "keyId" key represents the key identifier associated to the issuer DID that was used to sign the credential.
+ \item the "claims" key represents claims that the issuer makes about the subject. The claims are grouped in a JSON object.
+       There is a key for each claim asserted by the issuer. One particular claim is the subject DID, that represents a DID
+       controlled by the subject of the credential.
+ \end{itemize}
+\end{description}
+
 In the following steps, we assume the issuer and subjects have already established a secure communication channel.
@@
 \item Ask to each subject the DID they would like to use for the credential they will receive.
-\item The issuer creates the credentials (sets of claims) for each subject. One of the claims is the subject DID.
-      The issuer DID is also attached in the claims.
-\item The issuer signs each individual credential with an \emph{issuing key} associated to his publicly known DID. 
-      The signing key id is also attached to the credentials' claims.
-\item The issuer computes a merkle root based on the list of signed credentials.
+\item The issuer creates the credentials for each subject. It uses his DID and the key id of an \emph{issuing key} to populate
+      the credential corresponding fields. On each credential, it adds the corresponding subject DID as one of the claims.
+\item The issuer encodes each individual credential using a base64URL encoding.
+\item The issuer signs each individual encoded credential with an \emph{issuing key} associated to his publicly known DID. 
+      The signing key corresponds to the key id in the credentials' claims.
+\item The issuer encodes each signature, and concatenate them to their corresponding credentials using a dot (".") as separator.
+      This produces strings of the form $\langle{}encoded\_credentials\rangle{}.\langle{}encoded\_signature\rangle{}$. We call these strings as \emph{signed credentials}.
+\item Now, the issuer takes all the signed credentials, and computes a merkle root from them.
 \item The issuer creates an \emph{IssueBatch} event that contains the merkle root, and signs the event with an \emph{issuing key} associated to his publicly known DID. 
@@
 \item We assume a safe communication channel between the subject and verifier.
-      We also assume that the verifier has a DID $DID_{V}$ known by the subject.
+      We also assume that the channel can be identified by an identifier $ch$.
 \item The subject shares his credential and merkle inclusion proof to the verifier.
-\item The verifier computes the merkle root from the inclusion proof and the credential hash; extracts the issuer DID and signing key id from the credential claims.
-Then, it retrieves from the state he computed from the blockchain, the timestamps associated to the merkle root, the issuing key, he also extracts the signing key and checks if the merkle root or credential hash has been revoked.
-With all that data, he validates the issuer signature and is able to determine if it was signed at a time when the issuer key was valid.
+\item The verifier then: 
+	\begin{itemize}
+	\item computes the merkle root from the inclusion proof and the credential hash;
+	\item extracts the issuer DID and signing key id from the credential claims,
+	\item retrieves from the state he computed from the blockchain, the timestamps associated to the merkle root and the issuing key, 
+	\item checks if the merkle root or credential hash has been revoked
+	\item validates the issuer signature on the credential, and determines if it was signed at a time when the issuer key was valid.
+	\end{itemize}
+  \textbf{Note:} The signature of the IssueBatch event has already been verified by the protocol participants at the time of batch publication. 
 \item At this point, the verifier knows that the credential was properly signed. Now, he shares a nonce to the subject and asks him to sign it with a key associated to his DID.
-\item The subject signs the hash of $nonce || DID_{V}$ and returns the signature to the verifier.
+\item The subject signs the hash of $nonce || ch$ and returns the signature to the verifier.
 \item The verifier now checks the signature and concludes that the credential subject is indeed the person presenting it.

### 2021-09-23 prism-backend/research/article.tex
ATA-4755: add section addressing scalability (#150)
This commit adds a section exploring scalability proposals for our
protocol

@@
 % \section{Ideas to add missing properties}
+\section{Further thoughts}
 
+\subsection{Scaling}
+
+In the previous sections we described a protocol that allows transparent management of decentralized identifiers and credentials.
+The protocol usage of a blockchain facilitates the solution to three points:
+\begin{itemize}
+\item Events ordering: All participants can agree on the order in which any pair of events occurred 
+\item Fork protection (safety): There is no point in time where a valid sequence of processed protocol events could become invalid, nor replaced by 
+      another sequence
+\item Data transmission: All participants receive the same sequence of protocol events as they are transmitted through the blockchain
+\end{itemize}
+
+The second point has particular relevance to guarantee that the history of events can be trusted. For instance, imagine Alice controls a DID (its 
+associated master keys) that represents a real world object, like a car. If Alice's wants to sell the car and transfer the corresponding DID, she 
+would perform a DID update that revokes all the master keys controlled by her, and adds a new master key controlled by the new car owner. If Alice 
+could later "undo" this update, the DID ownership transfer could not be trusted.
+
+The properties brought by the blockchain come at a cost. Namely, the protocol throughput (number of events that participants can attach in 
+transactions per unit of time) is bounded to the blockchain throughput. In order to scale the throughput, we have reviewed Sidetree's approach. The 
+idea behind Sidetree is to not publish individual events attached to blockchain transactions, but to publish a hash-link to an off-chain content 
+addressable storage (CAS), like IPFS. The CAS will contain the file referenced by the hash-link, which contains a batch of many protocol events 
+(allowing to transcend the size limits imposed by blockchain transactions).
+
+We identify a non-ideal drawback about this approach, which is a loss of the safety property. In the setting defined by Sidetree, participants can 
+control changes to the past of their identifiers. This is, if Alice desires, she could create a DID by posting a file, $F_{1}$ on the CAS, and its 
+hash on-chain, $F_{1}$ would contain Alice $CreateDID$ event. Later, Alice can create a file $F_{2}$, containing an $UpdateDID$ event, post the hash 
+of $F_{2}$ on-chain, but intentionally not posting $F_{2}$ on the CAS. Then, Alice can create a third file $F_{3}$ which contains an new $UpdateDID$
+event that would be invalid if $F_{2}$ were revealed in the CAS (e.g. $F_{2}$ event could revoke the key that signs the update in $F_{3}$). However, 
+Alice can post both $F_{3}$ in the CAS and the hash of $F_{3}$ on-chain. In Sidetree, this sequence of actions would lead all protocol participants 
+to believe that Alice's DID is in certain state, produced by the $CreateDID$ of $F_{1}$ and the $UpdateDID$ from $F_{3}$.
+
+Alice has the power to reveal at any point $F_{2}$, making the update from $F_{3}$ as invalid, and forcing all participants to update Alice's
+DID to the state reflected by $F_{2}$. This is known as \textbf{late publish attack}, and makes technically impossible to trust the past history 
+history of events in Sidetree implementations. As an example consequence, it is not possible to transfer ownership of a DID when using Sidetree.
+
+In order to avoid introducing this issue, we considered two options.
+
+The first one is to add a permissioned actor (or a federation of them) that are allowed to batch protocol events and publish both on-chain hash-links,
+and files in corresponding CAS. The special actor introduces a trust model that assumes that it will always reveal files. If the actor fails to 
+reveal a file, the protocol participants stop processing further batches until the missing file is revealed. This is not possible in Sidetree because
+any participant would be able to freeze the system by not revealing a file. The protocol would still allow users to publish events on-chain directly, 
+leaving space for some decentralization for those participants that do not want to depend on the centralized batcher.
+
+In order to use the batcher to publish the $UpdateDID$ events associated to a DID $D$, the owner of $D$ will have to declare on-chain that future 
+updates for $D$ will be found on the off-chain batches. This public declaration is needed to avoid race conditions when a hash is on-chain but
+a file is not revealed.
+
+A second option consist of a more decentralized variation of the previous approach. Namely, allow any participant to propose itself as an event 
+batcher. The proposal is performed by submitting an on-chain event declaring the batcher DID. Every user that would like to batch its events 
+off-chain should publicly notify the batcher they will use. Only one batcher can be assigned to each DID, this is, the $UpdateDID$ events associated 
+to a DID will be published by at most one batcher. The objective is once again, to be able to identify missing files in a sequence, allowing 
+participants to stop processing files out of order.
+
+In any of the approaches, if the associated batcher stops publishing files, the DID registered to the batcher is "frozen" until the file is revealed.
+We could re-introduce some liveness protection to DID owners by requesting batches from a same batcher to be separated at least $N$ underlying 
+blockchain blocks, in order to provide that time for users to send a $Contention$ event that invalidates the events associated to a DID published in
+the previous batch. During the processing of batches, participants will wait the contention period (the $N$ blocks) before applying events from a 
+batch in order to not apply the updates to contended DIDs.
+
+Notes:
+\begin{itemize}
+\item we could change the $CreateDID$ event to incorporate an optional batcher DID from start, the batcher DID would be part of the initial state, 
+      bounding the batcher to the DID suffix. 
+\item we could support events to de-register from a batcher, and to switch batcher too.
+\item a user is free to batch his own DIDs' related events. This could be useful for a case like a car manufacturer that would like to batch all DIDs
+      associated to their cars, allowing car owners to de-register from a batcher at will.
+\item a priori, we do not see a need to batch credential issuance/revocation events
+\end{itemize}
 \end{document}

### 2021-10-05 prism-backend/research/article.tex
Updated ECIES and Connector models to meet more closely standard ECIES.

@@
 \usepackage[margin=1in]{geometry}
+
+\newcommand{\todo}[1]{{\colorbox{red}{\bf TODO:}\textcolor{red}{#1}}}
 
@@
 
+\subsection{Specific Sub-Protocols}
+\label{ssec:subproto}
+
+\subsubsection{End-to-End Encrypted Data Exchange via the Connector}
+\label{sssec:e2eeconnector}
+
+Assuming each participant of the system owns a (set of) DIDs, we want to let
+holders receive new credentials from issuers, in a secure -- yet convenient --
+manner. We describe a protocol for this purpose.  At the moment, we require
+that issuer and prospective holder can perform a one-time physical interaction
+with each other or, alternatively, that they have a secure channel at their
+avail (although possibly cumbersome to use, hence we only require to use it
+once).
+
+In a nutshell, the proposed protocol is composed essentially of two phases. In
+the first phase, the issuer shares a QR code with the holder. This QR code
+contains the issuer's public key (or, maybe, its DID), a random value, and a
+session identifier. This exchange takes place through a secure (i.e.,
+confidential and authenticated) channel, such as physical exchange. Probably
+immediately, although also possibly at a later point in time, the prospective
+holder sends back her own public key (or, alternatively, her DID) and the
+session identifier, all authenticated with a MAC, where we use the random value
+in the QR code as secret key. The issuer uses the session identifier to locate
+the corresponding session and, now that it received in an authenticated manner
+the public key of the holder, can leverage hybrid encryption techniques to
+establish an end-to-end encrypted session, e.g., using ECIES \cite{abr01}.
+Ensuring end-to-end encryption and authentication is important at this point, as
+all the information exchanged between issuer and holder is routed through the
+connector: an entity or set of entities who ensure that asynchronous
+communication can take place between issuer and holder. Thus, ECIES is crucial
+to ensure the secrecy and authenticity of the information, end-to-end.
+
+We have modelled this protocol using Tamarin%
+\footnote{https://tamarin-prover.github.io/ (Last access, October 5th, 2021.)}
+
 %----------------------------------------------------------------------------------------
@@
 \end{itemize}
+
+\bibliographystyle{plain}
+\bibliography{article}
+
 \end{document}

### 2021-10-12 prism-backend/research/article.tex
Updated description of the connector protocol and its security properties.

@@
 \usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\usepackage{xcolor}
+\usepackage{graphicx}
 
+\newcommand{\figref}[1]{Fig. \ref{#1}}
+\newcommand{\tabref}[1]{Table \ref{#1}}
+\newcommand{\lstref}[1]{Listing \ref{#1}}
+\newcommand{\secref}[1]{Section \ref{#1}}
+\newcommand{\appref}[1]{Appendix \ref{#1}}
 \newcommand{\todo}[1]{{\colorbox{red}{\bf TODO:}\textcolor{red}{#1}}}
@@
 communication can take place between issuer and holder. Thus, ECIES is crucial
-to ensure the secrecy and authenticity of the information, end-to-end.
+to ensure the secrecy of the information, end-to-end. Since the holder needs to
+have certainty that the data it receives comes from the issuer (and ECIES does
+not authenticate the sender), we have the issuer digitally sign the data it
+sends through the ECIES-secured channel. Note that we could involve the random
+value shared via the QR code for this. But that would force us to re-execute the
+first phase of the protocol even when the QR code is compromised after having
+completed the first phase of the protocol. Digital signatures using the issuer's
+DID prevent this.
 
-We have modelled this protocol using Tamarin%
+While the protocol is simple, and is based on common cryptographic constructions,
+it is easy to get such protocols wrong, as pointed out in numerous occasions
+\cite{davi01, kraw01}. Hence, we have used Tamarin%
 \footnote{https://tamarin-prover.github.io/ (Last access, October 5th, 2021.)}
+to model our protocol\footnote{Source code for the model available here
+  \url{https://github.com/input-output-hk/atala-prism/blob/research-tamarin-connector/prism-backend/research/formalizations/connector.spthy}
+  \todo{Update to final URL.}}, which is schematized in \figref{fig:e2econnector}
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[scale=0.4]{figures/connector.png}
+  \caption{Sequence diagram for the E2EE protocol through the connector.}
+  \label{fig:e2econnector}%
+\end{figure}
+
+The security properties that we prove are as follows (we refer to the actual
+model for the formal definition):
+
+\begin{description}
+\item[Code secrecy.] Codes exchanged via a QR code are always confidential.
+  Note that this is trivial, as it is exchanged via a secure channel, and
+  the holder never sends it back in the clear.
+\item[Code injectivity.] Every QR code that is received by a holder, allegedly
+  sent by an issuer, was sent before by that issuer. Again, this is trivial due
+  to the secure channel used to exchange the QR code.
+\item[Holder's public key authenticity.] Every message received by an issuer
+  in step 3, containing a public key for key-exchange usage, that was
+  allegedly sent by a holder, was indeed previously sent by that holder.
+  This is ensured through the message authentication code (MAC) that
+  leverages the random QR code exchanged via the secure channel, which is
+  only known to the issuer and the holder.
+\item[Holder's public key injectivity.] For every session in which an
+  issuer receives in step 3 a message, allegedly sent by a holder in
+  step 2, containing the holder's public key, it was that holder, in
+  the same session, who sent the public key in step 2.  
+\item[Credential secrecy.] This property has two variants: it ensures
+  secrecy for credentials sent by an honest issuer to a holder that was honest
+  at the moment of sending the credential, and is not compromised afterwards;
+  and it also ensures secrecy for credentials received by an honest holder,
+  allegedly from an honest issuer, if both holder and issuer were honest when
+  the credential is received, and they are not corrupted afterwards. Altogether
+  with the credential authenticity property shown next, it ensures that only
+  (honest) holder and issuer learn the contents of a credential.
+\item[Credential authenticity.] All messages containing a credential, received
+  by a holder at step 5, where indeed sent by an issuer and addressed to that
+  same holder, as long as both issuer and holder keys are not compromised.
+\item[Credential non-injectivity.] All messages containing a credential, received
+  by a holder at step 5, were sent by an issuer and addressed to that holder
+  at step 4. Note, however, that both messages in steps 4 and 5 dont necessarily
+  pertain to the  same ``session'' (in instantiations where parallel sessions
+  may occur). However, this does not pose a risk, as in any case, the messaged
+  is sent by the issuer, and received by the intended holder.
+\end{description}
+
+Concerning the technical details of the protocol, note that we are combining
+signature and encryption (plus, the MAC-based authentication natively provided
+by ECIES). This places us in the context put forward in \cite{davi01}, that
+discusses some good practices when combining such primitives. In a nutshell,
+we follow the sign-then-encrypt approach\footnote{What we call here ``sign-then-
+  encrypt'' is called ``Sign \& Encrypt'' in \cite{davi01}. However, we find
+  more explicit the naming convention of \cite{kraw01}, which is more consistent
+  when referring to the order in which the primitives are used -- order that, in
+  these cases, is crucial.}, combined with including the public
+keys of both holder and issuer into the signed (and then encrypted) data.
+This intertwines the inner layer (the signature) with the outer layer (the
+encryption), ensuring that any alteration on any of them will be detected.
+We note that there are other options that, a priori, are equally secure -- e.g.,
+encrypt-then-sign, including also the sender's public key in the encrypted data
+(but that would require separately signing a (hash of) the data, to ensure
+non-repudiation). It is worth noting that ECIES follows the
+encrypt-then-authenticate approach, which is proven to realize secure channels
+in \cite{kraw01}, as long as the underlying encryption scheme is IND-CPA secure,
+and the underlying MAC function is secure.
 

### 2021-10-12 prism-backend/research/article.tex
Completed section on connector e2ee protocol.

@@
   by a holder at step 5, were sent by an issuer and addressed to that holder
-  at step 4. Note, however, that both messages in steps 4 and 5 dont necessarily
+  at step 4. Note, however, that both messages in steps 4 and 5 don't necessarily
   pertain to the  same ``session'' (in instantiations where parallel sessions

### 2021-10-15 prism-backend/research/article.tex
Some rewriting. Added section on non-injective 'attack'.

@@
 
-In a nutshell, the proposed protocol is composed essentially of two phases. In
-the first phase, the issuer shares a QR code with the holder. This QR code
-contains the issuer's public key (or, maybe, its DID), a random value, and a
-session identifier. This exchange takes place through a secure (i.e.,
+In a nutshell, the proposed protocol (see \figref{fig:e2econnector}) is composed
+of two phases. In the first phase, the issuer shares a QR code with the holder.
+This QR code contains the issuer's public key (or, maybe, its DID), a random
+value ($code$, in \figref{fig:e2econnector}), and a session identifier ($token$,
+in \figref{fig:e2econnector}). This exchange takes place through a secure (i.e.,
 confidential and authenticated) channel, such as physical exchange. Probably
@@
 DID prevent this.
+
+Note that we are combining signature and encryption (plus, the MAC-based
+authentication natively provided by ECIES). This places us in the context put
+forward in \cite{davi01}, that discusses some good practices when combining such
+primitives. In a nutshell, we follow the sign-then-encrypt approach%
+\footnote{What we call here ``sign-then-encrypt'' is called ``Sign \& Encrypt''
+  in \cite{davi01}. However, we find
+  more explicit the naming convention of \cite{kraw01}, which is more consistent
+  when referring to the order in which the primitives are used -- order that, in
+  these cases, is crucial.}, combined with including the public
+keys of both holder and issuer into the signed (and then encrypted) data.
+This intertwines the inner layer (the signature) with the outer layer (the
+encryption), ensuring that any alteration on any of them will be detected.
+We note that there are other options that, a priori, are equally secure -- e.g.,
+encrypt-then-sign, including also the sender's public key in the encrypted data
+(but that would require separately signing a (hash of) the data, to ensure
+non-repudiation). Finally, it is worth noting that ECIES follows the
+encrypt-then-authenticate approach, which is proven to realize secure channels
+in \cite{kraw01}, as long as the underlying encryption scheme is IND-CPA secure,
+and the underlying MAC function is secure -- but this is independent of the
+sign-then-encrypt approach.
 
@@
   pertain to the  same ``session'' (in instantiations where parallel sessions
-  may occur). However, this does not pose a risk, as in any case, the messaged
-  is sent by the issuer, and received by the intended holder.
+  may occur). However, our current understanding is that this does not pose a
+  risk, as in any case, the messaged is sent by the issuer, and received by the
+  intended holder. For the sake of future reference, we give an illustrative
+  flow of this ``non-injective'' execution, in \appref{app:non-inj-e2ee}.
 \end{description}
-
-Concerning the technical details of the protocol, note that we are combining
-signature and encryption (plus, the MAC-based authentication natively provided
-by ECIES). This places us in the context put forward in \cite{davi01}, that
-discusses some good practices when combining such primitives. In a nutshell,
-we follow the sign-then-encrypt approach\footnote{What we call here ``sign-then-
-  encrypt'' is called ``Sign \& Encrypt'' in \cite{davi01}. However, we find
-  more explicit the naming convention of \cite{kraw01}, which is more consistent
-  when referring to the order in which the primitives are used -- order that, in
-  these cases, is crucial.}, combined with including the public
-keys of both holder and issuer into the signed (and then encrypted) data.
-This intertwines the inner layer (the signature) with the outer layer (the
-encryption), ensuring that any alteration on any of them will be detected.
-We note that there are other options that, a priori, are equally secure -- e.g.,
-encrypt-then-sign, including also the sender's public key in the encrypted data
-(but that would require separately signing a (hash of) the data, to ensure
-non-repudiation). It is worth noting that ECIES follows the
-encrypt-then-authenticate approach, which is proven to realize secure channels
-in \cite{kraw01}, as long as the underlying encryption scheme is IND-CPA secure,
-and the underlying MAC function is secure.
 
@@
 
+\appendix
+
+\section{Example of Non-Injective Execution of Connector E2EE Protocol}
+\label{app:non-inj-e2ee}
+
+The diagram in \figref{fig:e2econnector-noninj} depicts an scenario in which a
+non-injective execution between the issuer and the holder takes place.
+
+First, we have to take into account that such execution requires a somehow
+extended setting than what we considered in \secref{sssec:e2eeconnector}. Namely,
+here we assume a (certainly realistic) scenario in which any prospective holder
+has several computing devices -- e.g., a laptop and a smartphone. Similarly,
+the issuer instantiates several concurrent services -- depicted as
+\emph{Instance 1} and \emph{Instance 2} in \figref{fig:e2econnector-noninj}.
+Still, the same user operates both computing devices, which share the same
+private values; and all issuer instances have access to the same database with
+holders' information, and the issuer's private keys.
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[scale=0.32]{figures/connector-noninjective.png}
+  \caption{Sequence diagram of a sample non-injective execution of the E2EE
+    connector protocol}
+  \label{fig:e2econnector-noninj}%
+\end{figure}
+
+In the diagram, the holder requests a QR code once with each device -- for this,
+we envision an extended setting in which the holder can request QR codes
+securely (e.g., through signed email). The smartphone communicates with Instance
+2 of the issuer, while the laptop communicates with Instance 1. Eventually, the
+holder decides to complete the process from her laptop. The connector forwards
+the request to Instance 1, which stores it in the database. Then, it might
+happen that it is Instance 2 the one that takes care of finalizing the request:
+it fetches the necessary data from the shared database, and sends the result to
+the holder's phone (which is the computing device that communicated with
+Instance 2). This lack of correspondence between who initiated a request, and
+who responds it, is what is formally referred to as non-injectivity.
+Theoretically, that might perfectly happen in our proposed protocol, as there is
+nothing preventing such behaviour in a cryptographic manner, as our model shows.
+However, two observations are relevant:
+
+\begin{itemize}
+\item The authenticity and secrecy properties still ensure that only the holder
+  and issuer have access to the data that is sent by the issuer, and that it
+  indeed originates from the issuer.
+\item Such behaviour, if deemed unwanted, could be easily prevented through a
+  proper session handling, at the implementation level.
+\end{itemize}
+
 \bibliographystyle{plain}

### 2021-10-27 prism-backend/research/soa_review/ac.tex
Migrating research log content from former personal repository.

\section{Anonymous Credentials}
\label{sec:ac}

First proposed in \cite{chau85}.
CL signatures (idemix) \cite{cl01,cl04}.
UC formalisation in \cite{cdhk15}.
Brands works (U-prove).
Coconut paper, referenced in \cite[Section 1]{cdl+20}: anonymous credentials with
threshold opening.

\begin{enumerate}
\item Main intuition.
\item Evolution of main security models.
\item Variations concerning functionality.
\item Evolution in efficiency.
\item Main issues.
\item Approx. number of related works in main crypto+security venues: IACR,
  Esorics, CCS, AsiaCCS, SP, EuroSP, Usenix Sec and Privacy, PETs...
\end{enumerate}

\subsection{Approaches, Models, and Variations}

\paragraph{Main approaches.}

\paragraph{Main security models.}

\paragraph{Variations in functionality.}

\paragraph{Efficiency.}

\paragraph{Main challenges.}

\subsection{Related Primitives}

\subsubsection{Pseudonym Systems}
\label{sssec:pseudonyms}

\doubt{Not sure if this fits here.}

\subsection{Applications}
\label{ssec:acapplication}

\subsubsection{Theory}
\label{sssec:actheoryapp}

Main approaches to build ACs (from ToPS paper I reviewed):

\begin{itemize}
\item Re-randomizable signatures on commitments (also as in DAA):
  \cite{cl02,cl04,lmpy16,ps16}.
\item Equivalence class signatures: \cite{fhs19,hs14}.
\item Redactable signatures \cite{cdhk15,sand20} and malleable signatures
  \cite{ckl14}.
\item Predicate encryption: \cite{dmm+18}.
\end{itemize}

PS: Tokenization.

\subsubsection{Real World Deployments}
\label{sssec:acrwdeploy}

PS: Tokenization.
U-Prove.
Idemix.
Signal's AC \cite{}

\subsection{TODO}

\cite{cl04,ckl+15}.

Look also for the non-bilinear-based approach of \cite{cl04}.

[ToPS paper I reviewed] refers to a strategy to do threshold issuing in \cite{bbh06}.

Mental note: some of the early CL papers mentioned something about ACs
containing some secret key/value of the credential holder (I think, to avoid
sharing or something like that). Check which paper was it, and what happened
with this concept in subsequent refinements. If this has been removed, this may
be one key difference with respect to group signatures: i.e., without some
holder-specific secret value in the show-verify protocols, it is just not
possible to ensure traceability and/or non-frameability.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "sok-privsig"
%%% End:

### 2021-10-27 prism-backend/research/soa_review/daa.tex
Migrating research log content from former personal repository.

\section{Direct Anonymous Attestation}
\label{sec:daa}

% \begin{enumerate}
% \item Main intuition.
% \item Evolution of main security models.
% \item Variations concerning functionality.
% \item Evolution in efficiency.
% \item Main issues.
% \item Approx. number of related works in main crypto+security venues: IACR,
%   Esorics, CCS, AsiaCCS, SP, EuroSP, Usenix Sec and Privacy, PETs...
% \end{enumerate}

\paragraph{Main intuition.}
%
Direct Anonymous Attestation \cite{bcc04} was initially proposed to address a
need in the Trusted Computing Group
\footnote{\url{https://trustedcomputinggroup.org/}. Last access on October 29th,
  2020.}. Take a computing platform equipped with a trusted hardware element
(referred to as TPM, from Trusted Platform Module, in the TCG jargon). A TPM
is trusted to securely store secrets and perform some cryptographic operations,
but is otherwise not able to communicate directly with the outside world. To
do that, it has to leverage other components of the larger computing platform,
which are not fully trusted. Then, the challenge is to come up with a way for
third parties (verifiers) to check that they are indeed communicating with a
computing platform that is equipped with a valid TPM. Moreover, in order to
preserve privacy, a requirement is not to reveal which specific TPM the
verifier is communicating with. Initially, several proposals were made
\needcite\footnote{\cite{bcc04} references works by Boneh et al, and Brickel,
  but no academic reference seems to exist.}, but it was \cite{bcc04} the one
that was finally adopted.

\subsection{Approaches, Models, and Variations}
\label{ssec:daaapproach}

\note{For now, just write down notes on the DAA papers. Then, unify.}
\note{Remember: talk about the properties that security models aim to achieve
  in DAA.}

DAA has many similarities with group signatures, but also important differences.
While in group signatures the user joining the group is an ``indivisible''
entity, in DAA this role is divided among the TPM and the larger platform
containing the TPM (usually referred to as the Host). This undoubtedly
complicates the modelling, as different trust assumptions have to be made for
each of them. Also, security in DAA is modelled in the UC paradigm \todo{why?}
\todo{(not true. Some works use game-based definitions, as \cite{bfg+13} -- see
  also the discussion and references therein)},
whereas group signatures are modelled with game-based definitions. From a
functionality perspective, DAA does not allow opening and, also, uses pseudonyms
that can be leveraged to provide linkability%
\footnote{We note that, recently, group signature schemes have been proposed
  that do not implement opening either \cite{dl21}, and also leverage pseudonyms
  to introduce some kind of linkability \cite{gl19,kss19,dl21} -- and, indeed,
  these schemes draw techniques from DAA.}.

Besides these differences, the typical approach is similar: a new TPM runs an
interactive $\langle Join,Issue \rangle$ protocol with an issuer whereby the
TPM receives a membership credential. Then, to produce attestations, the TPM
creates SPKs of a valid credential, over a message including information about
the status of the Host. However, since there is no opening, DAA employs the
\emph{Sign-Randomize-Prove} strategy from group signatures, which produces more
efficient attestations (in group signatures, at the cost of more inefficient
opening). In addition, the pseudonyms added in DAA are built from \emph{scopes}
(also called \emph{basenames}) and cryptographic hash functions \todo{more
  insight on this}.

In \cite{bl07}, an extension of the DAA approach in \cite{bcc04} is made so
that it is possible to revoke TPMs not only based on leaked private keys (which
is a restricted approach), but also based on signatures and on requests by the
issuer. To do so, the membership proving protocol (roughly, signing) is extended
so that the prover demonstrates that its membership credential is different to
the ones who have been included in revocation lists by a revocation authority.
This, however, incurs in extra costs of the signing and verification protocols,
which grow linearly with the number of revoked users. During signing, \cite{bl07}
also remove the basename concept, which in \cite{bcc04} is used to derive
linkable pseudonyms when needed. Instead, they employ random bases. Finally, in
their model, \cite{bl07} do not differentiate between TPM and host. While the
authors give some insight into how to separate them, extending the formalization
(and proofs) has been shown to be problematic \todo{Bernhard work and later
  criticism?}

\cite{cms08} points out a flaw in the reduction of \cite{bcc04} and fixes it.
Interesting definition of DAA (maybe useful for giving a high-level overview).
It also provides a security proof (simulation/UC-based model) for the
scheme in \cite{cms08b}. In \cite{cms08b}, the authors present a pairing-based
DAA system using asymmetric pairings, achieving improved efficiency.
However, as pointed out in \cite{bfg+13} linking is still not correctly modelled,
being possible to link different authentications from a same TPM \todo{no detail
  is given. Try to see how/why.}
\note{\cite{cms08b} contains some nice (albeit now old) cost comparison.}

\cite{bcl09} proposes an alternative model using games, rather than the
simulation paradigm. They show that security in the UC model by \cite{bcc04}
implies security in their game-based model, but the converse is left as an
open question. However, as pointed out in \cite{bfg+13}, the model in
\cite{bcc04} has a flaw concerning linkability, which is thus inherited by
\cite{bcl09}. \todo{Cross-check this with subsequent Camensich-Lehmann works.}
Construction-wise, they propose an instantiation based on bilinear pairings,
which greatly improves costs.

In \cite{bfg+13}, flaws are pointed out in previous schemes (notably in the
one adopted by the TCG, \cite{bcc04}) that affect unforgeability and linkability
of the produced signatures. They argue that proving security in the UC model is
hard and error-prone in for DAA. Thus, they to game-based approach. In this
context, they propose a black box approach for building DAA systems from
\emph{weakly blind signatures} and \emph{Linkable Indistinguishable Tag} systems.
Moreover, they first capture security for scenarios in which TPM and host are
the same entity; then, they provide an approach to generalise to the case
in which they are different entities (with the different trust assumptions).
However, in their model, they make some odd requirements in the way they
capture identity \todo{delve more into this, and reference the other paper
  that points this out.}

\subsection{Related Primitives}

\begin{itemize}
\item Anonymous Credentials. \cite{bcc04} builds on Camenisch-Lysyanskaya
  signatures.
\item \cite{cms08b} mentions two schemes that are based on two different
  variants of CL signatures (one uses pairings, one does not).
\end{itemize}

\subsection{Applications}
\label{ssec:daaapplication}

\subsubsection{Theory}
\label{sssec:daatheoryapp}

\subsubsection{Real World Deployments}
\label{sssec:daarwdeploy}

\subsection{TODO}

\cite{cdl16,cdl16b,ccd+17,cdl17,cu15}.

Pairing-based DAA: see references in page 2 of \cite{bfg+11}.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "sok-privsig"
%%% End:

### 2021-10-27 prism-backend/research/soa_review/discussion.tex
Migrating research log content from former personal repository.

--- 2021-10-27 prism-backend/research/soa_review/daa.tex
@@
-\section{Direct Anonymous Attestation}
-\label{sec:daa}
-
-% \begin{enumerate}
-% \item Main intuition.
-% \item Evolution of main security models.
-% \item Variations concerning functionality.
-% \item Evolution in efficiency.
-% \item Main issues.
-% \item Approx. number of related works in main crypto+security venues: IACR,
-%   Esorics, CCS, AsiaCCS, SP, EuroSP, Usenix Sec and Privacy, PETs...
-% \end{enumerate}
-
-\paragraph{Main intuition.}
-%
-Direct Anonymous Attestation \cite{bcc04} was initially proposed to address a
-need in the Trusted Computing Group
-\footnote{\url{https://trustedcomputinggroup.org/}. Last access on October 29th,
-  2020.}. Take a computing platform equipped with a trusted hardware element
-(referred to as TPM, from Trusted Platform Module, in the TCG jargon). A TPM
-is trusted to securely store secrets and perform some cryptographic operations,
-but is otherwise not able to communicate directly with the outside world. To
-do that, it has to leverage other components of the larger computing platform,
-which are not fully trusted. Then, the challenge is to come up with a way for
-third parties (verifiers) to check that they are indeed communicating with a
-computing platform that is equipped with a valid TPM. Moreover, in order to
-preserve privacy, a requirement is not to reveal which specific TPM the
-verifier is communicating with. Initially, several proposals were made
-\needcite\footnote{\cite{bcc04} references works by Boneh et al, and Brickel,
-  but no academic reference seems to exist.}, but it was \cite{bcc04} the one
-that was finally adopted.
-
-\subsection{Approaches, Models, and Variations}
-\label{ssec:daaapproach}
-
-\note{For now, just write down notes on the DAA papers. Then, unify.}
-\note{Remember: talk about the properties that security models aim to achieve
-  in DAA.}
-
-DAA has many similarities with group signatures, but also important differences.
-While in group signatures the user joining the group is an ``indivisible''
-entity, in DAA this role is divided among the TPM and the larger platform
-containing the TPM (usually referred to as the Host). This undoubtedly
-complicates the modelling, as different trust assumptions have to be made for
-each of them. Also, security in DAA is modelled in the UC paradigm \todo{why?}
-\todo{(not true. Some works use game-based definitions, as \cite{bfg+13} -- see
-  also the discussion and references therein)},
-whereas group signatures are modelled with game-based definitions. From a
-functionality perspective, DAA does not allow opening and, also, uses pseudonyms
-that can be leveraged to provide linkability%
-\footnote{We note that, recently, group signature schemes have been proposed
-  that do not implement opening either \cite{dl21}, and also leverage pseudonyms
-  to introduce some kind of linkability \cite{gl19,kss19,dl21} -- and, indeed,
-  these schemes draw techniques from DAA.}.
-
-Besides these differences, the typical approach is similar: a new TPM runs an
-interactive $\langle Join,Issue \rangle$ protocol with an issuer whereby the
-TPM receives a membership credential. Then, to produce attestations, the TPM
-creates SPKs of a valid credential, over a message including information about
-the status of the Host. However, since there is no opening, DAA employs the
-\emph{Sign-Randomize-Prove} strategy from group signatures, which produces more
-efficient attestations (in group signatures, at the cost of more inefficient
-opening). In addition, the pseudonyms added in DAA are built from \emph{scopes}
-(also called \emph{basenames}) and cryptographic hash functions \todo{more
-  insight on this}.
-
-In \cite{bl07}, an extension of the DAA approach in \cite{bcc04} is made so
-that it is possible to revoke TPMs not only based on leaked private keys (which
-is a restricted approach), but also based on signatures and on requests by the
-issuer. To do so, the membership proving protocol (roughly, signing) is extended
-so that the prover demonstrates that its membership credential is different to
-the ones who have been included in revocation lists by a revocation authority.
-This, however, incurs in extra costs of the signing and verification protocols,
-which grow linearly with the number of revoked users. During signing, \cite{bl07}
-also remove the basename concept, which in \cite{bcc04} is used to derive
-linkable pseudonyms when needed. Instead, they employ random bases. Finally, in
-their model, \cite{bl07} do not differentiate between TPM and host. While the
-authors give some insight into how to separate them, extending the formalization
-(and proofs) has been shown to be problematic \todo{Bernhard work and later
-  criticism?}
-
-\cite{cms08} points out a flaw in the reduction of \cite{bcc04} and fixes it.
-Interesting definition of DAA (maybe useful for giving a high-level overview).
-It also provides a security proof (simulation/UC-based model) for the
-scheme in \cite{cms08b}. In \cite{cms08b}, the authors present a pairing-based
-DAA system using asymmetric pairings, achieving improved efficiency.
-However, as pointed out in \cite{bfg+13} linking is still not correctly modelled,
-being possible to link different authentications from a same TPM \todo{no detail
-  is given. Try to see how/why.}
-\note{\cite{cms08b} contains some nice (albeit now old) cost comparison.}
-
-\cite{bcl09} proposes an alternative model using games, rather than the
-simulation paradigm. They show that security in the UC model by \cite{bcc04}
-implies security in their game-based model, but the converse is left as an
-open question. However, as pointed out in \cite{bfg+13}, the model in
-\cite{bcc04} has a flaw concerning linkability, which is thus inherited by
-\cite{bcl09}. \todo{Cross-check this with subsequent Camensich-Lehmann works.}
-Construction-wise, they propose an instantiation based on bilinear pairings,
-which greatly improves costs.
-
-In \cite{bfg+13}, flaws are pointed out in previous schemes (notably in the
-one adopted by the TCG, \cite{bcc04}) that affect unforgeability and linkability
-of the produced signatures. They argue that proving security in the UC model is
-hard and error-prone in for DAA. Thus, they to game-based approach. In this
-context, they propose a black box approach for building DAA systems from
-\emph{weakly blind signatures} and \emph{Linkable Indistinguishable Tag} systems.
-Moreover, they first capture security for scenarios in which TPM and host are
-the same entity; then, they provide an approach to generalise to the case
-in which they are different entities (with the different trust assumptions).
-However, in their model, they make some odd requirements in the way they
-capture identity \todo{delve more into this, and reference the other paper
-  that points this out.}
-
-\subsection{Related Primitives}
-
-\begin{itemize}
-\item Anonymous Credentials. \cite{bcc04} builds on Camenisch-Lysyanskaya
-  signatures.
-\item \cite{cms08b} mentions two schemes that are based on two different
-  variants of CL signatures (one uses pairings, one does not).
-\end{itemize}
-
-\subsection{Applications}
-\label{ssec:daaapplication}
-
-\subsubsection{Theory}
-\label{sssec:daatheoryapp}
-
-\subsubsection{Real World Deployments}
-\label{sssec:daarwdeploy}
-
-\subsection{TODO}
-
-\cite{cdl16,cdl16b,ccd+17,cdl17,cu15}.
-
-Pairing-based DAA: see references in page 2 of \cite{bfg+11}.
+\section{Discussion}
+\label{sec:discussion}
 

### 2021-10-27 prism-backend/research/soa_review/gs.tex
Migrating research log content from former personal repository.

\section{Group Signatures}
\label{sec:gs}

\paragraph{Main intuition.}
%
Group signatures were first proposed by Chaum and van Heyst in 1991 \cite{ch91}
as a privacy-respectful extension to conventional digital signatures.
The intuition is simple: in order to avoid revealing the identity of the signer,
we make her signatures look indistinguishable to the signatures of all other
members of a group. Then, any entity with access to the group public key can
verify that a group signature comes from a member of the group, but cannot
tell which specific one actually created it.
%
Beyond this, group signature schemes have one main feature: a (set of) group
manager(s) control who can become a member of the group. Also, most frequently,
a (set of) group manager(s) decide when to expell a member from the group, or
when to re-identify the creator of a specific signature.
%
The initial idea put forward in \cite{ch91} had, as is to be expected, a number
of limitations. In the following years, the seminal work was extended, both
formally, functionally and efficiency-wise.

\subsection{Approaches, Models, and Variations}
\label{ssec:gsapproach}

\subsubsection{Main approaches.}
%
There are two main ways that are recurrently used to instantiate group signature
schemes: \emph{Sign-Encrypt-Prove} and \emph{Sign-Randomize-Prove}. In both
variants, when new members of the group join, they receive a credential (i.e.,
a signature by the issuer) derived from a secret they choose. Then, when
creating a group signature, they prove control a valid credential and the
associated secret. The difference lies on how this credential is kept hidden
from the verifier.
%
In the sign-encrypt-prove variant, proposed in \cite{bmw03}, signers
encrypt their credential with a \doubt{IND-CCA2? what type?} scheme and then
create a NIZK \needcite proof of knowledge of such a valid credential
over their secret (plus the message they want to sign). This typically results
in schemes with more efficient openings, as the opening authority just has
to decrypt the encrypted credential. However, group signatures require more
space.
%
In the sign-randomize-prove variant, proposed in \needcite \todo{Get Shorty?},
credentials are actually randomizable signatures by the issuer. Signers then
randomize the signature (credential), and create a NIZK proof of knowledge that
this credential is issued for a secret they know (again, plus the message
they want to sign). This usually results in schemes with less efficient openings,
as the opening authority needs to iterate over the registered credentials until
finding the one from which the randomized credential was derived. However, the
produced group signatures are also shorter.

When a new user wants to become a group member, a common habit is also to have
her prove ownership of a conventional digital identity. This identity is then
added to the de-identifying information leveraged by the opening authority, in
order to be able to associate (anonymous) group signatures to a real-world
identity. These conventional digital identities can be any type of PKI-based
(e.g. X.509 or equivalent) certificate. \todo{This is important for
  non-frameability! Check \cite[Section 3.2]{cdl+20} and re-state this.}
\todo{This is indeed necessary for non-repudiation (mentioned in
  \cite[Section 4]{lpy12}).}
\todo{Typically used in schemes with verifiable openings. See
  \cite[Section 1.3.3]{bsi12}.}

\subsubsection{Main security models.}
%
Security for group signatures is given in the form of game-based definitions
\needcite.
The first formal security model appeared in \cite{bmw03}. It captured security
for groups with a prefixed set of members, added by the group manager upon the
creation of the group. This static requirement was too restrictive to be
realistic, and was quickly extended in \cite{bsz05} and \cite{kty04,ky06}, to
model that new users can join the group after it has been created. The models
in \cite{bsz05,kty04,ky06} are usually referred to as dynamic or partially
dynamic. \cite{bcc+16} generalizes the (partially) dynamic setting into a fully
dynamic model, which considers extra desirable security properties when users
can be revoked (i.e., removed from the group).

Up to some subtleties, the main security properties in most works that appeared
after \cite{bmw03,bsz05,kty04,ky06} are as follows:

\begin{itemize}
\item {\bf Anonymity}. This is the core property concerning privacy. It
  ensures that given a signature produced by one out of two honest (challenge)
  users picked at random from the set of honest group members, it should be
  unfeasible to determine which one actually created it.

\item {\bf Traceability}. This property (covered by the misidentification attack
  in \cite{kty04,ky06}, and spaning also non-frameability in \cite{bmw03})
  captures that it must be possible (by the proper authority) to unambiguously
  recover the identity of the signer of any valid group signature.

\item {\bf Non-frameability}. This property (considered in the framing attacks
  in \cite{kty04,ky06}) requires that no adversary should be able to create
  valid signatures that can be used to incriminate honest users by having them
  open to an honest user who did not create them.

\end{itemize}

\cite{bcc+16} also includes a trace soundness property, ensuring that signatures
can be associated (via opening proofs) to only one user \todo{why does this not
  appear in the other models? Maybe because they don't support verifiable
  openings? Check \cite{kss19} and, if so, move this to the variations in
  functionality.}

\subsubsection{Variations in functionality.}
%
Note that, while the security properties just described roughly have the same
purpose across models, there are still differences making some models stronger
or more general than others in some respects. This includes subtleties like who
generates the keys of the authorities (the environment vs the adversary), how
many queries can be made to the challenge oracles and whether or not the
signatures are fixed, etc. However, while important, there are usually generic
techniques that allow to migrate from one variant to another \todo{\needcite,
  ellaborate more, or rewrite}. Now we are interested in revisiting some of
the variations that have impact into the functionality that schemes
following each model can provide, or variations that are specific to group
signatures schemes and do not appear in other cryptosystems.

\paragraph{Separating issuer and opener.}
In some schemes \cite{bmw03,kty04} one single authority concentrates the
power to add new members to the group, and open signatures. This endows such authority with great
power -- and trust -- and is therefore one of the main concerns for privacy
advocates: not only this authority can prevent users from joining (in the case
of dynamic groups), but it can also reidentify group members. In order to reduce
this trust, and since it is a clear distinction between both functionalities
(issuing and opening), many schemes separate both roles into an issuer and an
opener. While both authorities need to be trusted for their respective tasks,
one can now make independent assumptions and even ensure certain properties
if only one of the two authorities is compromised or malicious. For instance,
non-frameability can be achieved even when both authorities are malicious;
traceability can be achieved with malicious openers; and anonymity can be
kept as long as the opener is honest. This is the case in \cite{bsz05} and
\cite{ky06} (which, although starts from a single authority, also considers
and formalises the case of separate authorities).

\paragraph{Protecting against corrupt authorities.}
Even when the issuance and opening functionalities are separated, as mentioned,
each entity can unilaterally break crucial properties in a group signature scheme.
While placing such kind of trust may be reasonable in some use cases, it may not
be so for others. Thus, a natural extension is to reduce this trust as much as
possible. In this direction, there have been works that have applied threshold
and similar techniques \needcite to require that a set of openers (as opposed
to a single opener) need to cooperate in order to open any group signature
\cite{bcly08} \needcite.
Recently, the role of the issuer was also subject to these techniques
\cite{cdl+20}, and it is now known how to produce group signatures such that no
single entity can prevent users from joining nor reidentify them.

\paragraph{Forward security.}
Forward security aims at restricting the impact of security compromises (e.g.,
key leakage) to the future: i.e., if an attacker gains control of a user's
private key, only signatures produced after the compromise should be considered
invalid. In schemes that do not ensure forward secrecy, such a compromise also
renders invalid signatures produced before the compromise. Note that, for
conventional signatures, only the compromised users is (directly) affected by
such event. However,  in group signatures, all group members are directly
affected, as the signer's identity is not revealed by the signature. Thus,
in order to learn whether or not a past signature was issued by a compromised
user, it is necessary to resort to the opener -- therefore, reidentifying
\emph{all} users in the system.
%
Forward security has been introduced in group signatures in works like
\cite{song01,ly12} \needcite.
%
Interestingly (but logically), the approach to incorporate this property
holds similarities with the functionality to implement fully dynamic group
signatures: for forward security, users are usually required to apply an
update procedure to their private keys \cite{ly12}; in fully dynamic group
signatures, it is the group manager (or the opener) who has to update some
key material \cite{bcc+16}. In both cases, time has to be discretized in epochs,
and conditions are introduced into the security properties that prevent an
adversary being able to deanonymize (produce) a valid signature generated
(using) a key in an epoch in which such key was not supposed to be active
(either because the user updated it -- in a forward secure scheme -- or the
group manager revoked it -- in a fully dynamic scheme).

\paragraph{Revocation mechanisms.}
Verifier Local Revocation \cite{bs04}, accumulators approach.

\paragraph{Opening controls.}
Even when separating the roles of the authorities or distributing them, the
fact that some entity (or set of entities) can open group signatures is still
a delicate matter that creates friction. A minimal control is to enable the
opener to prove that the opening process has been performed honestly. This is
precisely what is done by schemes that support \emph{verifiable opening}
\needcite. To further aleviate this issue, some schemes
introduce mechanisms to even prevent opening as long as some condition is
met. For instance, in \cite{seh+12,ehk+19}, the condition is determined by
the message (e.g., only signatures over offending messages can be opened).
To implement this, the authors introduce an extra authority, the
\emph{admitter}, such that the opener needs to get some information from the
admitter in order to be able to open signatures over some specific message.
In \cite{sbm10}, the authors propose \emph{contractual} anonymity: before a user
is able to anonymously access some service, both user and service sign a
contract defining the conditions upon which anonymity can be revoked. This
contract can only be enforced by a trusted entity, the \emph{accountability
  service} who runs a trusted execution environment (such as today's Intel
SGX \needcite) ensuring that the conditions are checked in a trustworthy manner.

\paragraph{Alternatives to opening.}
%
Even with separated authorities, with distributed openers, or with more generic
opening controls such as message-dependent opening, opening may not even be
the type of reduction of privacy that is necessary. In this vein, alternative
schemes have been proposed that do not include any kind of
opening at all.
%
In the schemes proposed in \cite{kty04,cpy06,bcly08}, there is an extra
authority that can produce \emph{tracing} trapdoors on a per-user basis.
Once the tracing trapdoor for a specific user is given to some entity, this
entity can link (or trace) all group signatures produced by that user.
These trapdoors are also an effective mechanism for implementing verifier-local
revocation.
%
In \cite{gl19}, the opener is replaced by a \emph{converter} who, rather than
opening any given group signature, can link sets of signatures. More
specifically, when queried with a set of signatures, the converter transforms
them so that every signature coming from the same user gets assigned a same
randomized pseudonym. Furthermore, to prevent the converter from gradually
relinking all the signatures, these conversions are non-transitive: i.e.,
signatures produced by user $A$ will receive a different randomized pseudonym in
different queries.
%
In \cite{dl21}, there is directly no trusted entity that can open or link group
signatures. Instead, every user can create proofs of several signatures having
been issued by herself. In this case, the authors also propose a scheme whereby
a user can prove sequentiality of a set of signatures: i.e., that all signatures
were produced by herself, and no signature has been omitted or inserted into the
sequence, which is also given in the order in which the original signatures were
produced.

\subsubsection{Efficiency.}

\begin{itemize}
\item Size of (group) keys.
\item Size of signatures.
\item Verification time (batching, including revocation checks...)
\item Accumulators.
\end{itemize}

\subsubsection{Main challenges.}

Efficiency is possibly good for many real-world cases. Still: utility
and unavailability of implementations.

\note{Concurrent joins -- avoid extraction \cite{ky05,klap20}.}

\subsection{Related Primitives}

\subsubsection{Ring Signatures}
\label{sssec:rs}

\cite{rst06}

\cite{bcc+15} uses ring signatures to build a fully dynamic group signature
scheme.

\subsection{Applications}
\label{ssec:gsapplication}

See \cite[Section 1.2.3]{bsi12}: it seems mostly theoretical applications.

\subsubsection{Theory}
\label{sssec:gstheoryapp}

GS-MDO imply IBE \cite{ehk+19}.
GS are implied (shouldn't his by imply?) by trapdoor permutations \cite{bmw03}.
GS imply one-way functions \cite{romp90}.
GS imply public key encryption \cite{aw04}.
Commitments from group signatures (group signatures imply commitments?)
(ref. 25 in \cite{bfg+11}).

\subsubsection{Real World Deployments}
\label{sssec:gsrwdeploy}

\cite{ehk+19} mentions anonymous auctions, anonymous bulletin boards and
anomaly detection systems.

Maybe make some comments on how to deploy gs schemes, or what aspects may be
relevant. For instnace, some schemes/models (e.g. \cite{ly12}) assume a
trusted party who generates the keys for the authorities. While this has
a big impact in security/trust model, in the real world it would probably
be circumventable with audited processes for most use cases. Also, the
issue with concurrent issuance and the approach we took for implementing
\cite{gl19} in ICT4Cart, or the limitation to logarithmic numbers of users, etc.

\subsection{Further Notes}
\note{Integrate this section or delete it.}

\todo{CCA2 type of anonymity is defined in \cite{bbs04}. Schemes with CPA type
  of anonymity are (according to \cite{ehk+19}): \cite{bw06,bw07}.}

\cite{ehk+19} has a nice related work mentioning the assumptions that are
typically used.

Signature highjacking attacks (referenced in \cite{ehk+19}).

If we want to have traceability, the issuer needs to be honest. See what
implications this has in practice (e.g., what architectures are compatible
with this?) This probably makes schemes with separate issuing and opening
authorities more attractive in practice.

Other minor variants: group blind signatures, democratic group signatures,
mediated group signatures. All referenced in \cite[Section 1.3.5]{bsi12}.

Backward linkability property of group signatures with Timed Verifier-Local
Revocation, proposed in \cite{nf05}. Mentioned in \cite[Section 8.1.2]{bsi12}.

Relation of forward security with proactive security \cite{oy91}?

References 1, 24, 32 and, probably, 35 in \cite{bfg+11} seem to be (traceable)
group signatures that use the nym approach (or similar) for linking. Check.

\paragraph{Academic indicators.}
IACR, Esorics, CCS, AsiaCCS, SP, EuroSP, Usenix Sec and Privacy, PETs... Not
sure where to fit this.

Main cryptographic building blocks:

\begin{itemize}
\item BB signatures \cite{bb04}.
  \begin{itemize}
  \item Used in: \cite{ky05}.
  \item Paillier encryption of discrete-logarithms? Used in \cite{ky05} and,
    I think, \cite{gl19}.    
  \end{itemize}
\item Model for reduction: list of group signature schemes based on RO and
  non-RO are given in \cite{bcc+16}.
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "sok-privsig"
%%% End:

### 2021-10-27 prism-backend/research/soa_review/introduction.tex
Migrating research log content from former personal repository.

\section{Introduction}
\label{sec:introduction}

Privacy is a human right \needcite. It is also one of the most threatened ones
as a consequence of digitalization and hyperconnectivity \needcite. Maybe one
of the reasons behind this is that, on many occasions, it conflicts with another
human right: security \needcite. The most representative occasion in which this
happens is when we, as individuals%
\footnote{This, of course, also happens when authenticating machines -- as they
  carry to some extent information of some individual(s).}%
, want to gain access to some (possibly
digital) good or service. In that context, one has to prove having the legitimate
rights to access that good or service. However, in the process of doing so, the
entity verifying that we have the rights, typically learns something about us,
like our real name. This has been traditionally fine in physical systems, as the
impact was mostly local. However, with the advent of digitalization and
hyperconnectivity, this usually means that something related to our identity is
being logged in some server, who knows where and with what security controls,
and probably vulnerable to a number of criminal activities \needcite.

Of course, the cryptographic community has not been stranger to the need of
providing satisfactory solutions that enable both privacy and security. We
refer to all works trying to address to this need as \emph{privacy-preserving
  authentication} mechanisms. For decades, a huge amount of research, with many
variations, has been produced in the field. Sadly, still with limited impact in
the real world. Within this context, the goal of this review is manyfold: from a
practical perspective, serve
as a hub to security and privacy professionals that may find themselves in need
to balance privacy and security in some real world application; from a more
academic one, provide a (somehow detailed) overview of the vast amount of
literature in the field, which is already overwhelming enough to make it hard
to find the most appropriate variant of some property we may find ourselves
in need to provide; and finally, attempt to throw some insight into why such a
vast academic work has so far failed to gain more real world adoption.

In order to achieve this, %
we go over the main cryptographic primitives used to build privacy-preserving
authentication mechanisms. For all of them, we first provide a high-level
intuition of the approach to protect users' privacy. Then, we overview the
most prominent security models since their inception, and complement this
with some relevant variations concerning the provided functionality. We also
summarise the main results from an efficiency standpoint, and the main
challenges found so far both in theory and practice. To gain some initial
insight into the academic impact of each primitive, we provide (approximate)
numbers on publications in the main cryptography, security and privacy venues.
Finally, with a more practical mindset, we overview the applications that each
primitive has ``in theory'', and the extent to which they have been deployed
in the real world.

\note{Argue/mention that focus is on primitives that can be used for signing.
  This therefore excludes protocols that can only be used for anonymous
  authentication, but not anonymous singing per se (e.g., PAKE, PASTA, PESTO...
  and probably also Nymble, PEREA, BLAC...)}

\note{Create a graph of relationships between basic primitives and their
  applications. E.g., much of
  the work in SRP group signatures and DAA seems to be derived from randomizable
  signatures (which, afaik, are also a foundation for anonymous credentials).}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "sok-privsig"
%%% End:

### 2021-10-27 prism-backend/research/soa_review/soa-review.tex
Migrating research log content from former personal repository.

\documentclass{llncs}%[10pt]{llncs}
\pagestyle{plain}

\usepackage[n,advantage,operators,sets,adversary,landau,probability,notions,
logic,ff,mm,primitives,events,complexity,asymptotics,keys]{cryptocode}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage[normalem]{ulem}
\usepackage{hyperref}

\title{State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication}
\author{}

% Custom shorthands for this paper
\input{symbols.tex}

\begin{document}
\maketitle

\begin{abstract}
	\textbf{DISCLAIMER}: Please, keep in mind that, as of now, this document
	basically contains a research log in the shape of personal notes. Do not take 
	anything written here as ground truth.
\end{abstract}

\input{introduction.tex}
\input{gs.tex}
\input{abs.tex}
\input{ac.tex}
\input{daa.tex}
\input{other.tex}
\input{discussion.tex}
\input{conclusion.tex}

\bibliographystyle{splncs04}
\bibliography{soa-review}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: ucl.tex
%%% End:

### 2021-10-28 prism-backend/research/soa_review/ac.tex
Added summary of CL01.

@@
 
+Anonymous Credentials (ACs) were first proposed by Chaum \cite{chau85}, and
+later formally treated and optimized in a series of papers by Camenisch and
+Lysyanskaya \cite{cl01,cl02,cl04}. Roughly speaking, users receive credentials
+from an issuing organization, which can then use to authenticate against some
+verifier. The main property is that this authentication process can be done
+in a privacy-preserving way. This typically means that the verifier cannot
+link different authentication processes by that same user. And, usually, in
+credentials composed by multiple attributes, that the verifier only learns
+the attributes that the user is willing to share (or a function of them).
+
 \subsection{Approaches, Models, and Variations}
 
-\paragraph{Main approaches.}
+\paragraph{Main approaches.} %
+
+\begin{enumerate}
+\item[\cite{cl01}:]
+  \begin{itemize}
+  \item Functionality: FormNym, GrantCred, VerifyCred, VerifyCredOnNym.
+  \item Approach: Users create a pseudonym with each organization. For this,
+    users have to register first with the organization (associating a key to
+    a user name). Whenever the user wants to get a credential from a organization
+    in which he registered, he has to authenticate, and then the organization
+    decides whether or not to grant the credential. Users can show their
+    credentials to organizations in two ways: (1) just proving that they own a
+    credential issued by some organization; or (2), proving that they own a
+    credential issued by some organization \emph{and} this credential is over
+    the same pseudonym that the user holds with the verifying organization.
+    Essentially, pseudonyms are the concatenation of two random numbers (one
+    provided by the user, and the other by the organization). They get
+    associated an authenticating tag, which is a statistically hiding commitment
+    to the user secret (computed using randomness provided by both user and
+    organization). Organizations keep a database of the generated pseudonyms.
+    To get a credential from an organization where the user registered
+    previously, the user proves knowledge of the secret involved in the
+    pseudonym. The organization then creates a ``random signature'' (by using a
+    the inverse of random exponent, with the help of the factorization of an RSA
+    modulus chosen by the organization at setup time) over the pseudonym, and
+    gives that to the user. Users can show the credentials (in any of the
+    previously stated two ways) by creating non-interactive zero-knowledge
+    proofs of knowledge of the appropriate secret. Note that, in case (2),
+    this means that the proof is over two pseudonyms, which must share the
+    same secret.    
+  \end{itemize}
+\item[\cite{cl02}:] 
+\item[\cite{cl04}:]
+\item[\cite{cdhk15}:]
+\end{enumerate}
 
@@
 
+\begin{enumerate}
+\item[\cite{cl01}:] Security in \cite{cl01} is proven in an ad-hoc way,
+  using the ideal-world/real-world paradigm. The authors describe a
+  simulator for the operations supported by the system (Setup, FormNym,
+  GrantCred, VerifyCred and VerifyCredOnNym), and prove that the output of this
+  simulator is indistinguishable from that of the real protocol, under the
+  strong RSA and Diffie-Hellman assumptions.  
+\item[\cite{cl02}:] 
+\item[\cite{cl04}:]
+\item[\cite{cdhk15}:]
+\end{enumerate}
+
 \paragraph{Variations in functionality.}
+
+\begin{enumerate}
+\item[\cite{cl01}:] Extensions provided to the main functionality are:
+  \begin{itemize}
+  \item PKI-based and all-or-nothing non-transferability: Both options
+    involve sharing a verifiable encryption of the user secrets. In the
+    case of PKI-based non-transferability, the CA receives a verifiable
+    encryption, using as key the user's master secret, of some valuable
+    piece of information belonging to the user (e.g., the user's secret
+    key associated to his public key with that CA). In the all-or-nothing
+    case, the user shares with each organization (with which it has a
+    pseudonym), a verifiable encryption of his pseudonym secret data, encrypted
+    with his master secret. In both cases, if the user shares his master
+    secret with someone else, then he automatically gives access to
+    other relevant pieces of information (as the verifiable encryptions are
+    made public by the corresponding entity).    
+  \item One-show credentials: The validating tags over pseudonyms are extended
+    to include an extra value in their commitment. Then, users have to reveal
+    that value (or, rather, a value deterministically derived from that) in the
+    zero-knowledge proofs they create at show time. Since the value is always
+    the same, verifiers can check whether they have seen it before, or not.
+  \item Revocation: Both local (i.e., within an organization) and global (i.e.,
+    referring to an identity of the user in an external CA) is possible by
+    extending the pseudonyms of the user, and the credential showing protocols,
+    with values that allow subsequent decryption by a trusted party of their
+    pseudonym or external identity, given a transcript of the credential
+    showing.    
+  \item Attributes: The paper also succinctly describes how multiple attributes
+    per credential could be included. This would be done by dividing the inverval
+    within the exponent used to compute the pseudonym in sub-intervals, and then
+    proving that the exponent lies within a sub-interval.
+  \end{itemize}
+\item[\cite{cl02}:] 
+\item[\cite{cl04}:]
+\item[\cite{cdhk15}:]
+\end{enumerate}
 

### 2021-10-29 prism-backend/research/article.tex

@@
 with each other or, alternatively, that they have a secure channel at their
-avail (although possibly cumbersome to use, hence we only require to use it
-once).
+availability (although possibly cumbersome to use, hence we only require to use
+it once).
 
@@
 immediately, although also possibly at a later point in time, the prospective
-holder sends back her own public key (or, alternatively, her DID) and the
-session identifier, all authenticated with a MAC, where we use the random value
+holder sends back her own public key (or, alternatively, her DID) authenticated
+with a MAC, where we use the random value
 in the QR code as secret key. The issuer uses the session identifier to locate
@@
 completed the first phase of the protocol. Digital signatures using the issuer's
-DID prevent this.
+keypair prevent this.
 

### 2021-10-29 prism-backend/research/soa_review/ac.tex
Added small summary of CL02 and CL04.

@@
   \item Approach: Users create a pseudonym with each organization. For this,
-    users have to register first with the organization (associating a key to
+    they have to register first with the organization (associating a key to
     a user name). Whenever the user wants to get a credential from a organization
@@
 \item[\cite{cl02}:]
-\item[\cite{cl04}:]
+  \begin{itemize}
+  \item Functionality:
+  \item Approach: Te paper aims at improving efficiency of AC systems, as
+    well as still ensuring that the user can retrieve their credentials in
+    a privacy-preserving manner. For this purpose, the core of the paper
+    describes a signature scheme that allows signing blocks of messages,
+    and later prove, in zero-knowledge, knowledge of such a signature. To
+    enable private retrieval of credentials, the authors describe a protocol
+    for their signature scheme, whereby the user specifices a commitment to
+    a message (or a block of messages, although this is not actually
+    formalized), and get a signature of the message in return. While the
+    authors do not strictly define an AC system, the application of their
+    signature system and related protocols to the AC domain seems direct.
+    Indeed, the same functionality as in \cite{cl01} seems straight
+    forward given the cryptosystems in \cite{cl02}.
+  \end{itemize}
+\item[\cite{cl04}:] Follows a similar approach to \cite{cl02}, although
+  changing the security assumptions to be based only on problems related
+  to the discrete logarithm, and on bilinear maps. Basically, defines a
+  signature scheme suitable for signing multiple messages, a protocol to
+  obtain a signature con a committed value, and a protocol to prove knowledge
+  of a signature. Concerning commitments, they rely on Pedersen commitment
+  scheme, for which protocols are known to prove knowledge and equality of
+  committed values. This lets them follow the same approach to \cite{cl02},
+  which is in turn the one in \cite{cl01}.
 \item[\cite{cdhk15}:]
@@
   strong RSA and Diffie-Hellman assumptions.  
-\item[\cite{cl02}:] 
-\item[\cite{cl04}:]
+\item[\cite{cl02}:] No security model is given for the anonymous credential
+  application of the signature scheme (reasonably, as it is not the main focus
+  of the paper). The signature scheme is proven secure (no specific mention
+  to a security model, although I suppose it would be quite straight forward)
+  based on the Strong RSA and Diffie-Hellman assumptions.
+\item[\cite{cl04}:] Same as in \cite{cl02} (no actual security model for the
+  AC system). The custom proofs are based on the DDH and LRSW assumptions.
 \item[\cite{cdhk15}:]
@@
   \end{itemize}
-\item[\cite{cl02}:] 
-\item[\cite{cl04}:]
 \item[\cite{cdhk15}:]

### 2021-11-01 prism-backend/research/soa_review/ac.tex
Added comments on chdk15.

--- 2021-10-28 prism-backend/research/soa_review/ac.tex
@@
 \item[\cite{cl02}:]
-\item[\cite{cl04}:]
-\item[\cite{cdhk15}:]
+  \begin{itemize}
+  \item Approach: Te paper aims at improving efficiency of AC systems, as
+    well as still ensuring that the user can retrieve their credentials in
+    a privacy-preserving manner. For this purpose, the core of the paper
+    describes a signature scheme that allows signing blocks of messages,
+    and later prove, in zero-knowledge, knowledge of such a signature. To
+    enable private retrieval of credentials, the authors describe a protocol
+    for their signature scheme, whereby the user specifices a commitment to
+    a message (or a block of messages, although this is not actually
+    formalized), and get a signature of the message in return. While the
+    authors do not strictly define an AC system, the application of their
+    signature system and related protocols to the AC domain seems direct.
+    Indeed, the same functionality as in \cite{cl01} seems straight
+    forward given the cryptosystems in \cite{cl02}.
+  \end{itemize}
+\item[\cite{cl04}:] Follows a similar approach to \cite{cl02}, although
+  changing the security assumptions to be based only on problems related
+  to the discrete logarithm, and on bilinear maps. Basically, defines a
+  signature scheme suitable for signing multiple messages, a protocol to
+  obtain a signature on a committed value, and a protocol to prove knowledge
+  of a signature. Concerning commitments, they rely on Pedersen commitment
+  scheme, for which protocols are known to prove knowledge and equality of
+  committed values. This lets them follow the same approach to \cite{cl02},
+  which is in turn the one in \cite{cl01}.
+\item[\cite{cdhk15}:] The approach to build anonymous credentials is roughly
+  the same as in the previous works \cite{cl01,cl02,cl04}, although with
+  relevant differences that make it more efficient. Basically, users create
+  pseudonyms derived from a common secret. Then, any user can request a
+  credential. For this, the user needs to prove knowledge of the pseudonym's
+  secret. In return, the issuer produces an ``unlinkable redactable signature''
+  on a set of attributes, for that pseudonym. A redactable signature is
+  essentially a signature over a set (block) of messages, that enables
+  subsequent verification that a subset of those messages was signed. This
+  is essentially the same as in \cite{cl02,cl04}. However, to achieve
+  unlinkability, \cite{cdhk15} incorporates efficient zero-knowledge proofs
+  to prove correctness of the subset of the messages that a user wants to
+  ``show'' in a credential showing process. This ensures unlinkability (hence,
+  privacy). The internal scheme used for this is a vector commitment scheme
+  that uses Lagrange interpolation to allow checking that a subset of the
+  committed messages are indeed contained within the commitment. Moreover,
+  both the vector commitment scheme, and the vector signing scheme, are
+  structure preserving. This means that, since all the produced messages,
+  commitments, and signatures, are elements of the group (rather than of the
+  field), proving knowledge is much more efficient (e.g., it prevents costly
+  extraction required for security proofs).
 \end{enumerate}
@@
   strong RSA and Diffie-Hellman assumptions.  
-\item[\cite{cl02}:] 
-\item[\cite{cl04}:]
-\item[\cite{cdhk15}:]
+\item[\cite{cl02}:] No security model is given for the anonymous credential
+  application of the signature scheme (reasonably, as it is not the main focus
+  of the paper). The signature scheme is proven secure (no specific mention
+  to a security model, although I suppose it would be quite straight forward)
+  based on the Strong RSA and Diffie-Hellman assumptions.
+\item[\cite{cl04}:] Same as in \cite{cl02} (no actual security model for the
+  AC system). The custom proofs are based on the DDH and LRSW assumptions.
+\item[\cite{cdhk15}:] The model (and associated proofs) presented in this paper
+  is very comprehensive, and detailed. Specifically, for the main building block
+  (Unlinkable Redactable Signatures), the authors give both game-based
+  definitions as well as an ideal functionality. This ideal functionality models
+  security in a single-issuer setting. However, as it is done in the UC
+  framework, it can be composed with itself, so that a scenario with multiple
+  issuers, in which users can combine credentials obtained by different users
+  into a single showing process (``presentation'') is directly achievable by
+  composing multiple instances of the ideal functionality (one per ``proof
+  part'').
 \end{enumerate}
@@
   \end{itemize}
-\item[\cite{cl02}:] 
-\item[\cite{cl04}:]
-\item[\cite{cdhk15}:]
+\item[\cite{cdhk15}:] The same as in the previous works (\cite{cl01,cl02,cl04}).
 \end{enumerate}

### 2021-11-03 prism-backend/research/soa_review/ac.tex
Mention to Coconut.

@@
   extraction required for security proofs).
+\item[sms+19:] The Coconut system follows a similar approach than the previous
+  works with respect to the representation and showing protocol for credentials.
+  Namely, credentials are randomizable signatures issued blindly. In this case,
+  the authors rely on Pointcheval Sanders signatures \cite{ps16} as main
+  building block, to which they incorporate techniques from other schemes to
+  support threshold issuance.
 \end{enumerate}
@@
   part'').
+\item[\cite{sms+19}:] No security model is given nor adopted.
 \end{enumerate}
@@
 \item[\cite{cdhk15}:] The same as in the previous works (\cite{cl01,cl02,cl04}).
+\item[\cite{sms+19}:] It is essentially the same as previous works, although it
+  supports threshold issuance. Interestingly, \cite{sms+19} does not make use
+  of pseudonyms. I.e., credentials are just signed (blocks of) attributes. This
+  probably lets them achieve better efficiency. \doubt{This makes the scheme
+    to be practically like a group signature scheme (without revocation...)}
 \end{enumerate}
@@
 
+\cite{sms+19} seems to be the most efficient one (note: relies on the
+Fiat-Shamir heuristic). Credentials are only composed by two G1 elements,
+independently on the number of attributes.
+
 \paragraph{Main challenges.}
@@
 \subsection{Related Primitives}
+
+Most schemes \cite{cl01,cl02,cl04,cdhk15,sms+19} are based on randomizable
+signatures, with the possibility of signing committed values, that also support
+efficient proofs of knowledge.
+
+The most recurrent signature schemes are Camenisch-Lysyanskaya \cite{cl02,cl04},
+BBS/BBS+ \cite{asm06,cdl16b}, and Pointcheval Sanders \cite{ps16}, with the
+exception of \cite{cdhk15} that leverages their own signature scheme, called
+Unlinkable Randomizable Signatures.
 

### 2021-11-04 prism-backend/research/soa_review/ac.tex
Review of MAC-based ACs.

@@
   which is in turn the one in \cite{cl01}.
+\item[\cite{cmz14}:] This work differs from the rest in that they use
+  secret key cryptography rather than public key. Namely, they assume a
+  setting in which the issuer will also be the verifier (e.g., a
+  transportation organization that issues tickets for its travelers). In
+  this setting, it is reasonable to assume that both issuer and verifier
+  will have access to the same secret. Therefore, they replace signatures
+  with (algebraic) MACs. They do not create pseudonyms for end users (like
+  \cite{sms+19}). Other than that, the supported functionality is similar
+  to the rest: Setup and KeyGen to initialize the cryptographic parameters,
+  and produce the issuer's keys, respectively; an interactive protocol for
+  end users to blindly receive credentials (MACs) on their attributes; and
+  an interactive protocol for showing and verifying a credential. In case
+  that issuance does not need to be blinded, it becomes a non-interactive
+  protocol (i.e., the issuer just produces the credential and sends it to
+  the user). Otherwise, the user has to encrypt the attributes and prove
+  they are correct. Presentation only requires one message from the user
+  to the verifier.
 \item[\cite{cdhk15}:] The approach to build anonymous credentials is roughly
@@
   AC system). The custom proofs are based on the DDH and LRSW assumptions.
+\item[\cite{cmz14}:] The security properties proven in this work are:
+  \begin{itemize}
+  \item \emph{Unforgeability}: The adversary cannot produce a valid proof for a
+    statement, if none of the attribute sets for which it has received a
+    credential meets that statement.
+  \item \emph{Anonymity}: The proofs produced in a presentation do not leak
+    more information than the statement being proved.
+  \item \emph{Blind issuance}: The issuance protocol is a secure two-party
+    protocol for generating credentials on th euser's attributes.
+  \item \emph{Key-parameter consistency}: no issuer can use different parameters
+    to produce credentials of different users such that their anonymity can
+    be compromised afterwards. \doubt{This somehow remembers non-frameability in
+      group signatures.}
+  \end{itemize}
 \item[\cite{cdhk15}:] The model (and associated proofs) presented in this paper
@@
   \end{itemize}
+\item[\cite{cmz14}:] The paper mentions ``Credential translation'', which
+  basically means being able to prove that two attributes in different
+  credentials are actually the same. This is not formalized or detailed,
+  though.
 \item[\cite{cdhk15}:] The same as in the previous works (\cite{cl01,cl02,cl04}).
@@
 Idemix.
-Signal's AC \cite{}
+Signal's AC \needcite
 
@@
 
-\cite{cl04,ckl+15}.
-
-Look also for the non-bilinear-based approach of \cite{cl04}.
+\cite{bcc+09}: Delegation.
+\cite{dmm+18}: Functional credentials.
+\cite{fhs19}: Structure-preserving signatures for AC.
 
@@
 
-Mental note: some of the early CL papers mentioned something about ACs
-containing some secret key/value of the credential holder (I think, to avoid
-sharing or something like that). Check which paper was it, and what happened
-with this concept in subsequent refinements. If this has been removed, this may
-be one key difference with respect to group signatures: i.e., without some
-holder-specific secret value in the show-verify protocols, it is just not
-possible to ensure traceability and/or non-frameability.
+\cite{cmz14} says: Idemix is efficient in that credentials are constant-size,
+although very expensive to present.
 

### 2021-11-05 prism-backend/research/soa_review/ac.tex
Added summary on Functional Credentials paper.

@@
   extraction required for security proofs).
-\item[sms+19:] The Coconut system follows a similar approach than the previous
+\item[\cite{dmm+18}:] Follows a completely different approach to (most) other
+  works. Instead of using randomizable signatures (over committed values) or
+  some equivalent building block, it relies on predicate encryption.
+  Essentially, a user with attributes $A$ is given a decryption key for a
+  predicate $f_A(g)$ which, given a predicate $g$, returns $g(A)$. When
+  a verifier wants to check if a user has a set of attributes that meet
+  certain policy $h$, challenges the user to decrypt a ciphertext over
+  a random message that has been associated to predicate $h$. Then, only
+  if the attribute set $A$ of the user meets policy $h$, the user will be
+  able to decrypt the random message (since $f_A(h) = h(A) = 1$). This
+  protocol is actually augmented with some commitments, to prevent
+  misbehaviour from user and from verifier, but the approach is the same.
+  \doubt{There is something weird here, or that I do not understand --
+    predicate encryption requires a
+    set of attributes for encryption, rather than another predicate. I have
+    reached out to the authors to see if they can help me clarify this.}
+\item[\cite{sms+19}:] The Coconut system follows a similar approach than the previous
   works with respect to the representation and showing protocol for credentials.
@@
   part'').
+\item[\cite{dmm+18}:] The authors give a game-based security model, covering
+  properties of unforgeability, anonymity, and policy-hiding. The latter
+  means that, for delegated verification, the verifier is oblivious to the
+  policy being verified.
 \item[\cite{sms+19}:] No security model is given nor adopted.
@@
 \item[\cite{cdhk15}:] The same as in the previous works (\cite{cl01,cl02,cl04}).
+\item[\cite{dmm+18}:] The scheme supports delegated verification. Basically,
+  to implement delegated verification, the delegatee receives an encryption of
+  the policy it has to verify, plus a signature of the encryption. If the
+  signature is valid, it re-randomizes the ciphertext for the policy, and
+  sends it to the user, who follows the same protocol as in the normal case.
+  The paper also mentions how to add more functionality, like delegation of
+  credentials and revocation, but they are not modelled. Also interestingly,
+  they claim somewhat informally (in Section 2.3) that no scheme satisfying
+  anonymity in the presence of an untrustworthy issuer can support delegation
+  of verification with policy hiding.
 \item[\cite{sms+19}:] It is essentially the same as previous works, although it
@@
 
-\cite{bcc+09}: Delegation.
-\cite{dmm+18}: Functional credentials.
-\cite{fhs19}: Structure-preserving signatures for AC.
+\begin{itemize}
+\item \cite{bcc+09}: Delegation.
+\item \cite{dmm+18}: Functional credentials.
+\item \cite{fhs19}: Structure-preserving signatures for AC.
+\item \cite{cks10,aks12}: ACs with revocation.
+\item \cite{ckl+15}: Formal treatment of privacy-preserving credentials.
+\end{itemize}
 
 [ToPS paper I reviewed] refers to a strategy to do threshold issuing in \cite{bbh06}.
-
-\cite{cmz14} says: Idemix is efficient in that credentials are constant-size,
-although very expensive to present.
 

### 2021-11-09 prism-backend/research/soa_review/ac.tex
Added comment on CKS10.

@@
   which is in turn the one in \cite{cl01}.
+\item[\cite{cks10}:] The system proposed here follows the conventional
+  approach to anonymous credentials based on randomizable signatures (with
+  the possibility to sign committed values) over vectors of messages.
+  It however enables issuers to produce updates on already signed messages.
+  This updates can be leveraged to incorporate revocation. Essentially,
+  time is divided in epochs, and credentials include an attribute which
+  represents the expiration date/epoch of the credential. Users have to
+  prove that their credential is valid for the current epoch. Similarly,
+  to add new attributes, the issuer leverages the internal structure of
+  the signatures over vectors of messages, to basically add new messages
+  (attributes). In both cases, it is responsibility of the user to update
+  her credential given the latest update by the issuer. An example
+  instantiation is given using BBS signatures.
 \item[\cite{cmz14}:] This work differs from the rest in that they use
@@
   extraction required for security proofs).
+\item[\cite{ckl+15}:] Follows the conventional approach: a secure commitment
+  scheme with proofs of knowledge, and a signature scheme that allows to
+  sign vectors of messages, including commitments.
 \item[\cite{dmm+18}:] Follows a completely different approach to (most) other
@@
   AC system). The custom proofs are based on the DDH and LRSW assumptions.
+\item[\cite{cks10}:] Signer privacy and user privacy properties are required
+  for the underlying signature scheme (thus, inherited by the credential system,
+  although I have not found explicit model). Signer privacy captures that the
+  adversary (including corrupt users) doesn't learn any information about the
+  signer from signatures and updates of signatures. User privacy captures that
+  the adversary (including a corrupt issuer) does not learn any information
+  about the blindly signed messages. \doubt{Not sure I get the utility of
+    signer privacy. The original property seems to come from \cite{bckl08}.}
 \item[\cite{cmz14}:] The security properties proven in this work are:
@@
 \item \cite{bcc+09}: Delegation.
-\item \cite{dmm+18}: Functional credentials.
 \item \cite{fhs19}: Structure-preserving signatures for AC.
-\item \cite{cks10,aks12}: ACs with revocation.
+\item \cite{aks12}: ACs with revocation.
 \item \cite{ckl+15}: Formal treatment of privacy-preserving credentials.

### 2021-11-09 prism-backend/research/soa_review/discussion.tex
Added comment on CKS10.

@@
 \label{sec:discussion}
+
+Interesting topic for discussion, which applies mostly for ACs, but probably
+to most other equivalent tools: we have tools that provide a (reasonably
+complete and) secure way to authenticate in a privacy-preserving manner.
+However, what do we do after such authentication takes place? E.g., it is of
+little use to employ an AC to log into an online service, if that service
+will learn all about us after we have anonymously authenticated. How does
+privacy-preserving authentication improve the situation even in that case?
+Is there some way in which we can help avoid that?
 

### 2021-11-09 prism-backend/research/soa_review/soa-review.tex
Added comment on CKS10.

@@
 
+\section{TODOs}
+
+General/pending doubts and tasks:
+
+\begin{itemize}
+\item Many constructions of ACs and GSs seem to be built using the same
+  approach: an issuer and a user interact so that the latter receives a signature
+  from the former; then the user employs that signature to do something else (in
+  ACs, prove attributes; in GSs, produce further signatures). Still, the typical
+  security models are different. Concretely, GSs have a very well established
+  model, but ACs don't. It also ``bothers'' me that none of the AC models I've
+  seen cover something similar to non-frameability, nor traceability, but just
+  include conventional unforgeability properties. Why is this?
+\end{itemize}
+
 \bibliographystyle{splncs04}

### 2021-11-09 prism-backend/research/soa_review/soa-review.tex
Thought on lack of non-frameability in ACs.

@@
   include conventional unforgeability properties. Why is this?
+  \begin{itemize}
+  \item Concerning non-frameability, this probably is because the de-anonymizing
+    functionality that ACs include (if any) is revocation, which is essentially
+    a blacklisting. On the other hand, GSs usually allow opening, which extracts
+    the actual identity. Opening is ``stronger'' than blacklisting, in the sense
+    that it can be used to build blacklisting, but it is also more threatening
+    to privacy and may have further implications. Among these, unequivocable
+    framing of users. This, in general, does not seem possible with conventional
+    blacklisting (or, at least, not in an unequivocable way).
+  \item Concerning traceability.
+  \end{itemize}
 \end{itemize}

### 2021-11-09 prism-backend/research/soa_review/ac.tex
Summary of CKL+15. Nice.

@@
   scheme with proofs of knowledge, and a signature scheme that allows to
-  sign vectors of messages, including commitments.
+  sign vectors of messages, including commitments. Here, as in the seminal
+  works by Camenisch and Lysyanskaya \cite{cl01,cl02,cl04}, pseudonyms are
+  used as explicit building blocks. \todo{Not sure yet of how they are
+    made explicit in the generic construction. Clarify.}
+  A ``syntactic'' variation: they introduce
+  the concept of tokens both for credential issuance and presentation. To
+  request issuance of a credential, users have to produce an issuance token
+  from the set of attributes they want to reveal to the issuer, and the set
+  of attributes they want to hide (potentially coming from another credential
+  already owned by the user). An equivalent description applies for presentation
+  of a credential to a verifier. In both cases, the issuer/verifier has to
+  check the received token prior to issuing a credential or granting access.
+  They also add revocation functionality. For this, a revocation authority
+  (not necessarily the issuer) keeps a revocation information list, which is
+  basically a list containing no longer valid attributes. In order to prove
+  that their credentials are valid w.r.t. some attribute, users have to generate
+  a (non) revocation token, which proves that the attribute has not been
+  included in the revocation information list.
 \item[\cite{dmm+18}:] Follows a completely different approach to (most) other
@@
   \item \emph{Blind issuance}: The issuance protocol is a secure two-party
-    protocol for generating credentials on th euser's attributes.
+    protocol for generating credentials on the user's attributes.
   \item \emph{Key-parameter consistency}: no issuer can use different parameters
@@
   part'').
+\item[\cite{ckl+15}:] The main security and privacy properties required are
+  pseudonym collision-resistance (two different user secret keys cannot produce
+  the same nym for the same scope), unforgeability (the adversary cannot forge
+  issuance tokens or presentation tokens), and privacy (no two presentations by
+  the same user can be linked) or weak privacy (presentations by the same user
+  can be linked, but not traced to an issuance session). Privacy is modelled
+  in the simulation paradigm, the difference in the modelling between privacy
+  and weak privacy being a filter that removes some information \note{(I find
+    this kind of weird; probably I'm wrong. Would be nice to study further)}.
+  The unforgeability and privacy properties are essentially inherited from the
+  main building block, privacy-enhancing attribute-based signatures. Although
+  there, the authors begin by defining a blind issuance experiment (ensuring
+  that the issuer does not learn anything more than what it should during
+  isusance), and then define two variants for user privacy: presentation privacy
+  and untraceability, which basically match the strong and weak notions for
+  PABCs (in untraceability, two presentations by the same user can be linked,
+  but not trace to a specific credential issuance). [Strong] user privacy has
+  to satisfy both blind issuance and presentation privacy; weak user privacy
+  has to satisfy both blind issuance and untraceability. I find this model
+  somehow interesting, as it is one of the few (maybe along with \cite{cmz14})
+  that includes some notion related to tracing back to issuance of credentials,
+  as in group signatures). In both cases (PABC and PABS), [strong] privacy
+  implies weak privacy.
+  Essentially, the security properties required by the PABC scheme, are
+  ensured by the building blocks. Namely: the pseudonym system (requiring
+  key extractability, collision resistance and pseudonym unlinkability); the
+  revocation scheme (requiring soundness and revocation privacy); the
+  PABs (requiring unforgeability, and [weak] privacy); and the commitment
+  scheme (requiring blinding and hiding, and opening extractability).
 \item[\cite{dmm+18}:] The authors give a game-based security model, covering
@@
 \item \cite{aks12}: ACs with revocation.
-\item \cite{ckl+15}: Formal treatment of privacy-preserving credentials.
 \end{itemize}

### 2021-11-11 prism-backend/research/soa_review/ac.tex
Review of FHS19.

@@
     reached out to the authors to see if they can help me clarify this.}
+\item[\cite{fhs19}:] Based on Structure Preserving Signatures from equivalence
+  classes (SPS-EQ). The approach resembles that of \cite{ckl+15} in that it
+  uses a structure preserving primitive, and signs (commitments of) sets of
+  messages. However, they aim to avoid (as they claim) costly zero-knowledge
+  proofs. Basically, upon setup, a set commitment scheme is set up. Each user
+  generates a keypair. To obtain a credential on a set of attributes $A$, the
+  user proves knowledge of the user secret key, which is used as randomness
+  for a set commitment over $A$. The issuer (proves knowledge of the secret
+  key and) returns a SPS-EQ signature over $A$. To show the credential, the
+  user randomizes the commitment set and the signature, reveals the required
+  subset $D$ of $A$, and computes a witness that indeed $D \subset A$, as well
+  as a proof knowledge of the randomness used to randomize the credential (to
+  prevent replays). 
 \item[\cite{sms+19}:] The Coconut system follows a similar approach than the previous
@@
   policy being verified.
+\item[\cite{fhs19}:] Gives a game-based security model, with anonymity and
+  unforgeability being the main security properties (besides correctness).
+  Unforgeability resembles the traceability property of group signatures,
+  which are recognised as an influence in their modelling -- more specifically,
+  \cite{bmw03} (the model -- and the oracles therein -- definitely resembles
+  the BMW model for GSs). The authors claim to be the firsts to give a well defined and
+  formal model for ACs, besides \cite{ckl+15} (which gives game-based properties
+  in the simulation paradigm) and \cite{cdhk15} (which follows the UC framework).
+  However, \cite{fhs19} claims that adopting non-simulation based definitions
+  allows them to reach a more efficient construction. They also support malicious
+  issuer key generation, as issuers have to prove knowledge of their secret keys
+  (which allows extraction in the games).
+  An interesting aspect of their model is that all attributes in their
+  credentials are learned by the issuer -- i.e., there are no blindly signed
+  attributes. This implies that it is not possible to sign secret keys owned
+  by the users (as in the conventional CL credentials). Then, for showing a
+  credential, all the user has to do is reveal the attributes s/he is required
+  to show. This has the disadvantage that, depending on the use case, this may
+  be trivial to attack. For instance, assume a COVID-like pandemic situation,
+  in which citizens have to prove being vaccinated. An AC system for this use
+  could be naively defined as: { Type of vaccine, Date of vaccination }. But
+  this is very susceptible to dictionary attacks, and leaves much to the
+  engineering/implementation level. E.g., if it is easy for an eavesdroper
+  to get hold of a credential (not even the plaintext attributes), s/he can
+  just iterate through the small list of possible values, and then take
+  advantage of the ``stolen'' credential. This is certainly secure under the
+  model defined in \cite{fhs19}, but it is definitely easy for implementations
+  following this model to go wrong...
+  They also model only interactive show processes. Furthermore, to prevent
+  replay attacks, the user has to prove knowledge of some randomness included
+  in the credential. However (\textbf{cross-check this!}), since signatures
+  are randomizable without knowledge of any secret value, any adversary that
+  learns a credential (not necessarily any plaintext attribute associated to
+  it), would be capable of authenticating through a dictionary attack in case
+  of small attribute ranges.
+  Note: this may just be a modelling issue (or not even that, cross-check later
+  in case I misunderstood something). In their construction, they include
+  a secret key of the user in the credentials, of which the user has to prove
+  knowledge during the issue protocol. They do this by ``reusing'' the user
+  secret key as the randomness employed for the set commitment scheme, and
+  requiring the user to prove knowledge of the corresponding public key.
+  However, I am not sure of whether or not this somehow thwarts the previously
+  mentioned ``attack'', which affects the show protocol (\todo{i.e., the user does
+    not need to prove knowledge of the usk during show, no?} \note{Actually, it
+    should not, as it would probably prevent anonymity}) In any case, even if
+  the specific construction and instantiation thwarts this attack, I think their
+  model allows it.
 \item[\cite{sms+19}:] No security model is given nor adopted.
@@
 Fiat-Shamir heuristic). Credentials are only composed by two G1 elements,
-independently on the number of attributes.
+independently on the number of attributes. \todo{Cross-check this after
+  review.}
+
+\cite{cdhk15} and \cite{fhs19} achieve credential showings of size independent
+of the number of attributes.
 
@@
 \begin{itemize}
-\item \cite{bcc+09}: Delegation.
-\item \cite{fhs19}: Structure-preserving signatures for AC.
+\item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
 \item \cite{aks12}: ACs with revocation.
+\item \cite{asm06}: This seems to be the origin of the BBS+ branch of ACs (also,
+  probably \cite{aks12} is in this family).
+\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
+  such as ECDSA) signatures.
+\item \cite{cl11}: ACs from aggregate signatures.
 \end{itemize}
@@
 [ToPS paper I reviewed] refers to a strategy to do threshold issuing in \cite{bbh06}.
+
+Concepts in ACs: multishow, one-show (Brands et al); interactive vs non-interactive
+showings (differentiation made in \cite[p.6]{fhs19} but, why would one want interactive,
+in the real world?)
+
+Which schemes support comibning credentials from multiple issuers? I think this
+is directly obtained in the schemes following the CL approach; but others?
+
+A recurrent claim in schemes avoiding using zero-knowledge proofs of knowledge
+of some attributes being included in a credential is that these proofs are costly
+(like, linear in the number of attributes). Yet, they resort to other primitives
+that may also be costly (e.g., predicate encryption \cite{dmm+18}) or somehow move
+the cost to some other place (e.g., \cite{fhs19} uses a vector commitment scheme
+that requires a public key with size that grows with the number of attributes
+that \emph{can} be committed). It would be nice to have a detailed and complete
+(e.g., not skipping the data that makes one scheme look bad, like the size of
+the public keys) comparison. And, ideally, with concrete instantiations (not only
+theoretical analysis)?
 

### 2021-11-12 prism-backend/research/soa_review/ac.tex
Comment.
Added summary of ASM06 into related work section (not realy an AC system).

@@
 
+The ``family'' of AC systems known in the industry as BBS+ originates from
+\cite{asm06} (or, probably, from the BBS+ variant in \cite{cdl16b}, which
+introduces several improvements). \cite{asm06} presents a GS-like system that
+lets users obtain a credential from a Group Manager. This credential is a
+BBS+ signature. BBS+ signatures are a digital signature scheme, based on
+\cite{bbs04} and following the modification guidelines put forward in
+\cite{cl04}\footnote{Essentially, the authors of \cite{asm06} acknowledge
+  \cite{cl04} as those who proposed the BBS+ scheme -- but without security
+  proofs, which are provided in (the full version of) \cite{asm06}.}. On top
+of the signature scheme, they add efficient protocols for obtaining a signature
+over a set of committed messages, and proving -- in zero knowledge -- knowledge
+of a signature. Users can then be authorized by Application Providers (APs) to
+access their services: for this, APs maintain a list of the users they have
+granted/revoked access to, using a dynamic accumulator. APs also allow users to
+authenticate anonymously up to $k$ times. In order to access the services of APs,
+users have to derive a value using a VRF, and further prove that the value used
+to seed the VRF is a number within $[1,k]$ -- in addition to, of course, proving
+knowledge of a valid BBS+ signature (their credential). APs keep a record of the
+accesses. Thus, if a user accesses more than $k$ times a given AP, anyone with
+access to the record will be able to learn that a user has accessed more than
+$k$ times, as there will be more than one matching VRF-derived values.
+Furthermore, these two (or more) values let anyone extract a ``pseudonymous''
+identity of the user. The model (only informally presented, formal definitions
+appear in \cite{ts06} and proofs are deferred to a full version) seems to be
+used in $k$-TAA systems ($k$ Times Anonymous Authentication), and defines
+properties for:
+
+\begin{itemize}
+\item D-Detectability: Adversaries authenticating more than $k$ times are
+  detected.  
+\item D-Anonymity: Honest users authenticating less than $k$ times remain
+  anonymous.
+\item D-Exculpability: No honest user can be framed as having authenticated
+  more than $k$ times. The GM cannot be framed as dishonest if that is not
+  the case.
+\end{itemize}
+
 \subsubsection{Pseudonym Systems}
@@
 \item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
-\item \cite{aks12}: ACs with revocation.
-\item \cite{asm06}: This seems to be the origin of the BBS+ branch of ACs (also,
-  probably \cite{aks12} is in this family).
+\item \cite{aks12}: BBS+-based ACs with revocation.
 \item \cite{cgm16} An AC system that builds ACs from existing (conventional,
@@
 
+\cite{fhs19} has a nice comparison table.
+
 %%% Local Variables:

### 2021-11-13 prism-backend/research/soa_review/ac.tex
Added review of AKS12. Not really an AC system.

@@
 The most recurrent signature schemes are Camenisch-Lysyanskaya \cite{cl02,cl04},
-BBS/BBS+ \cite{asm06,cdl16b}, and Pointcheval Sanders \cite{ps16}, with the
-exception of \cite{cdhk15} that leverages their own signature scheme, called
-Unlinkable Randomizable Signatures.
+BBS/BBS+ \cite{asm06,cdl16b}, and Pointcheval Sanders \cite{ps16}.
+\cite{cdhk15} leverages their own signature scheme, called Unlinkable
+Randomizable Signatures, which lets users obtain a signature on a set of
+(committed) messages and then prove knowledge of (a subset of) these
+messages, introducing rerandomization to prevent linking. \cite{fhs19}
+follows a similar approach, using vector commitments. Both schemes
+\cite{cdhk15,fhs19} seem to be the most efficient AC instantiations to date.
+\cite{cdhk15} follows the UC framework; \cite{fhs19} a game-based definition.
 
@@
 
+The system in \cite{aks12} also uses BBS+ signatures as a main building block
+to design a system with accountable anonymity, although it is not ``strictly''
+an anonymous credentials system: users receive a credential that lets them
+authenticate anonymously against service providers, but this credential does
+not include attributes, which seems to be the common case in ACs (however,
+with BBS+ it is trivial to add attributes, although this should be modelled).
+The main contribution of \cite{aks12} is the design and incorporation of
+protocols to block misbehaving users depending on their behaviour, without
+relying on trusted third parties. This is based on ``reputation lists'',
+maintained by each service provider. Uses that have previously registered
+with a Group Manager can authenticate against service providers by proving
+knowledge of a valid credential. Depending on how these users behave during
+the session with the service provider, the latter adds the interaction to
+either a \emph{good behaviour} list, or a \emph{misbehaviour list}. For
+subsequent authentications, users prove (in an ``almost unlinkable'' way
+w.r.t. previous authentications) that they have a certain reputation,
+computed as a weighted sum of their presence in the good/bad behaviour
+lists. Moreover, each service provider can maintain multiple thematic lists,
+and then require users to satisfy arbitrary boolean policies based on these
+lists (e.g., reputation $\gt X_1$ on $list_1$ and reputation $\lt X_2$ on
+$list_2$ or reputation $\eq X_3$ on $list_3$) so that only users meeting
+the defined policy can access their system. These proves have though a linear
+dependency on the number of authentications that each user has done in
+the past. To reduce the impact of this, the authors create epochs. When a
+user authenticates successfully against a service provider, at a given epoch
+$i$, the service provider gives the user a token that authenticates the
+reputation that the user had at epoch $i$. Then, when this user tries to
+authenticate again, he only needs to give that token, and prove his reputation
+since epoch $i$ (this is why authentication is ``almost unlinkable'', as
+service providers may learn when the user authenticated for the last time).
+Note that no trusted party is involved in the blacklisting process, as
+correctness of all tokens exchanged between users and service providers to prove
+meeting certain policy, is ensured via the corresponing proof protocols.
+Concerning security, the system is proven secure in the simulation paradigm,
+claiming to meet (informally defined) properties of:
+
+\begin{itemize}
+\item Anonymity: All the SPs can infer from authenticating users is that they
+  meet the predefined policy, and that they authenticated at a certain epoch.
+\item Authenticity: Only users meeting the defined policies can authenticate.
+\item Mis-authentication resistance: Un-registered users cannot authenticate
+  successfully.
+\item Non-frameability: No coalition of users can cause that another user
+  meeting the required policy, cannot authenticate successfully.
+\end{itemize}
+
+Somehow, these properties resemble those in the group signatures model in
+\cite{kty04}. Probably, the addition of non-frameability is a consequence
+of adding a variant of revocation.
+
 \subsubsection{Pseudonym Systems}
@@
 \item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
-\item \cite{aks12}: BBS+-based ACs with revocation.
 \item \cite{cgm16} An AC system that builds ACs from existing (conventional,

### 2021-11-13 prism-backend/research/soa_review/ac.tex
Added review of CL11. AC based on aggregate signatures.

@@
   to the verifier.
+\item[\cite{cl11}:] The approach differs from the conventional ones. In this
+  case, the focus is on settings where users may want to combine multiple
+  credentials from different issuers. Thus, interest is on reducing the size
+  of the resulting credentials, and the efficiency of associated processes.
+  The approach is based on aggregate signatures. As usual, each credential
+  may contain several attributes. Each attribute is independently signed
+  by the issuer. Then, users can combine an arbitrary number of signed
+  attributes (by the same or different issuers) into a single aggregate
+  signature. Verification only needs the aggregated signature and the set
+  of public keys of all the involved issuers. To prevent different users
+  from aggregating their credentials, the authors resort to \emph{indexed}
+  aggregate signatures: an index is added to each signature, such that only
+  signatures that have the same index can be aggregated. In their instantiation,
+  the signature is a BGLS signature \cite{bgls03}, and the index is a BB
+  signature \cite{bb04}. The actual instantiation seems impractical (too many
+  linear costs, see the table in the paper).
 \item[\cite{cdhk15}:] The approach to build anonymous credentials is roughly
@@
     signer privacy. The original property seems to come from \cite{bckl08}.}
+\item[\cite{cl11}:] The security properties in this work are unforgeability
+  and anonymity, for which the authors give game-based definitions.
 \item[\cite{cmz14}:] The security properties proven in this work are:
@@
 and then require users to satisfy arbitrary boolean policies based on these
-lists (e.g., reputation $\gt X_1$ on $list_1$ and reputation $\lt X_2$ on
-$list_2$ or reputation $\eq X_3$ on $list_3$) so that only users meeting
+lists (e.g., reputation $\ge X_1$ on $list_1$ and reputation $\le X_2$ on
+$list_2$ or reputation $= X_3$ on $list_3$) so that only users meeting
 the defined policy can access their system. These proves have though a linear
@@
   such as ECDSA) signatures.
-\item \cite{cl11}: ACs from aggregate signatures.
 \end{itemize}
@@
 
+How to compare efficiency of AC systems?
+
 %%% Local Variables:

### 2021-11-15 prism-backend/research/soa_review/ac.tex
Added note on CGM16 (primitives for ACs with generic policies.)

@@
 
+\paragraph{Primitives for credentials with generic policies.} \cite{cgm16}
+describes techniques to be able to create efficient proofs that combine both
+algebraic and non-algebraic relations. For instance, proving knowledge of an
+ECDSA or RSA-FDH signature (both of which include computation of a hash
+function); but also being able to prove any arbitrary (non-algebraic) funcion
+$f$. This may be very useful to achieve compatibility with traditional
+credentials/signature schemes, that mostly do not follow the algorithms
+used in anonymous credentials systems. In fact, that is one of the main
+motivations in the paper. The approach in \cite{cgm16} builds on committing
+Oblivious Transfer and Garbled Circuits (not necessarily with privacy).
+A closely related work seems to be \cite{dfkp16},
+which achieves the same goal but using SNARKS, which results in different
+tradeoffs -- hence, it may be interesting, as the SNARK domain has improved
+significantly since 2016. \cite{kkl+16} also allows building anonymous
+credentials for arbitrary policies, but using a different approach too.
+
 \subsubsection{Pseudonym Systems}
@@
 
+Also:
+
+\begin{itemize}
+  \item ACs based on aggregate signatures: \cite{cl11}.
+\end{itemize}
+
 PS: Tokenization.
@@
 \item \cite{cgm16} An AC system that builds ACs from existing (conventional,
-  such as ECDSA) signatures.
+  such as ECDSA) signatures. \cite{kkl+16} achieves similar results with a
+  different approach?
 \end{itemize}

### 2021-11-17 prism-backend/research/soa_review/ac.tex
Review of BCC+09.

@@
   which is in turn the one in \cite{cl01}.
+\item[\cite{bcc+09}:] This is mostly a theoretical work, which is relevant
+  since it is (one of) the first to propose a delegatable anonymous
+  credentials systems. The building blocks are randomizable proofs of
+  knowledge that randomize both the proof and the statement (which the authors
+  build on top of Groth-Sahai proofs), and message authenticators (a variant
+  of signatures that require a special notion of unforgeability). Each user
+  can create pseudonyms, which are commitments to his secret key, and use
+  these commitments to prove ownership of and delegate credentials. These
+  pseudonyms are essentially as in the CL line of work (user with pseudonym
+  $N^A_U$ w.r.t. organization $A$ and $^B_U$ w.r.t. orgainzation $B$, can
+  prove to $B$ (resp. $A$) that $N^A_U$ and $N^B_U$ are related to the
+  same secret key). Delegations here follow a sequential order: i.e., if
+  a credential has level $L$, then its owner can further delegate this
+  credential, and the result would be a credential with level $L+1$. To
+  delegate, essentially, the delegator (with pseudonym $N_I$) and delegatee
+  (with pseudonym $N_D$) perform an interactive protocol
+  through which the delegatee receives a randomizable NIZKP that lets him
+  prove knowledge of an authenticator over $N_D$, issued by $N_I$. Since
+  both the proof and the statement can be randomized, verifiers do not
+  learn the chain of delegation.  Although this is informally mentioned,
+  ``attributes'' can be added to the delegation process too (besides to the
+  credentials themselves). This is suggested by adding the attributes -- which
+  would be visible to the verifier -- to the application of a hash function
+  used to derive the authenticator). 
 \item[\cite{cks10}:] The system proposed here follows the conventional
@@
   AC system). The custom proofs are based on the DDH and LRSW assumptions.
+\item[\cite{bcc+09}:] The article follows a game-based definition approach,
+  with two security properties (besides correctness): anonymity and
+  unforgeability, which are the usual, but extended to the scenario with
+  delegation. Basically, the anonymity (in the ideal/real world paradigm)
+  property requires that the adversary should not distinguish real credentials
+  from simulated ones. Moreover, the adversary should not learn the delegation
+  chain of an honest credential (even if it was issued by himself). For
+  unforgeability, the requirement is that the adversary should not create
+  a delegation chain that includes a delegation by an honest user, if the
+  user did not actually perform that delegation.
 \item[\cite{cks10}:] Signer privacy and user privacy properties are required

### 2021-11-22 prism-backend/research/soa_review/ac.tex
Added review of CKLM14.

@@
   linear costs, see the table in the paper).
+\item[\cite{cklm14}:] This work is, in essence, a generalization of \cite{bcc+09}.
+  The main novel building block are controlled-malleability NIZKs. Basically,
+  these are NIZKs that can be re-randomized, but only for a pre-defined set of
+  (NP) transformations. From this cm-NIZKs, malleable signatures are built.
+  From malleable signatures and commitments, delegatable credentials are built
+  as follows. Credentials are basically a tuple $(nym, l, flag)$, where $nym$
+  is a commitment to the user's private key, $l$ is the length of the credential
+  in the delegation chain, and $flag$ is either $cred$ or $proof$. Credentials
+  are accompanied with a malleable signature (which, for level 1 credentials,
+  it is a signature by the issuer). To create ``proofs'' or to delegate, the
+  credential owner has to apply one of the two allowed transformations. For
+  ``proofs'', basically the transformation that has to be applied to the original
+  proof (malleable signature) converts it to a proof showing that the prover
+  knows the secret in the ``source'' pseudonym and ``target'' pseudonym, and
+  both are the same. In the case of delegations, flag is set to ``cred'', and
+  the transformation converts the cm-NIZK proof into one that lets the prover
+  prove knowledge of the secret key in the ``source'' pseudonym, and allows
+  only to produce a new credential with structure $(nym', l+1, cred)$ -- i.e.,
+  from a credential of level $l$, only a credential of level $l+1$ can be
+  derived. On the delegation topic, the type of delegation this work ``supports'',
+  at least by default, is the simple one of hierarchical delegation.
 \item[\cite{cdhk15}:] The approach to build anonymous credentials is roughly
@@
   and anonymity, for which the authors give game-based definitions.
+\item[\cite{cklm14}:] Defines security of the DAC scheme using simulation-based
+  notions of anonymity and unforgeability.
 \item[\cite{cmz14}:] The security properties proven in this work are:
@@
 \begin{itemize}
-\item \cite{bcc+09,cklm14}: Delegation (\cite{cklm14} relies on \cite{cklm12}).
+\item : Delegation (\cite{cklm14} relies on \cite{cklm12}).
 \item \cite{cgm16} An AC system that builds ACs from existing (conventional,

### 2021-11-22 prism-backend/research/soa_review/ac.tex
Added note on Nym Credentials.

@@
   support threshold issuance.
+\item[\cite{halp20}:] Builds on Coconut credentials and a blockchain -- in theory,
+  any blockchain with smart-contract capability, although it seems they are building
+  their own blockchain. This paper is in the frontier of academic and industry
+  work. On the cryptographic side, the credentials they build are essentially an
+  extension of Coconut credentials (although the extension is not described, nor
+  formalized). Users can combine multiple Coconut credentials into one Nym
+  Credential. In order to control Sybil attacks, Nym Credentials are obtained
+  in exchange of Nym Tokens (how users get hold of these, is not described).
+  Service Providers receive Nym Tokens in exchange of offering their services
+  through the network.
 \end{enumerate}
@@
 \item[\cite{sms+19}:] No security model is given nor adopted.
+\item[\cite{halp20}:] No formal definition is given. The following properties
+  are claimed: undetectability (this seems similar to traceability in group sigs),
+  unlinkability, selective attributes disclosure, unforgeability, persistent
+  accounts, sybil resistance, extensibility, availability, decentralization.
 \end{enumerate}

### 2021-11-22 prism-backend/public-docs/article.tex
ATA-5717: Add protocol description
This commit adds a compact description of the protocol we use in PRISM

--- 2021-10-12 prism-backend/research/article.tex
@@
 \usepackage{graphicx}
-
-\newcommand{\figref}[1]{Fig. \ref{#1}}
-\newcommand{\tabref}[1]{Table \ref{#1}}
-\newcommand{\lstref}[1]{Listing \ref{#1}}
-\newcommand{\secref}[1]{Section \ref{#1}}
-\newcommand{\appref}[1]{Appendix \ref{#1}}
-\newcommand{\todo}[1]{{\colorbox{red}{\bf TODO:}\textcolor{red}{#1}}}
 
@@
 We use the blockchain for both; data distribution along parties, and for consensus related to the order of relevant events in our protocol.
-All the parties participating in our protocol are running a full node that reads the metadata of the blockchain transactions.
+All the parties participating in our protocol are running a blockchain node that reads the metadata of the blockchain transactions.
 When they find a protocol event, they process it to construct their view of the system.
@@
 Once the transaction is added to the blockchain with a sufficient number of confirmations $d$ (i.e.
-the block containing the transaction has $d$ blocks appended after it on the underlying chain), all the participants following our protocol will validate the signature of the CreateDID event.
+the block containing the transaction has $d$ blocks appended after it on the underlying chain), all the participants following our protocol will validate the signature of the \emph{CreateDID} event.
 After verification, they will register the DID as \emph{published} along with all the keys posted in the initial list.
@@
 \item Create an \emph{UpdateDID} event that contains the two previously generated lists.
-\item Sign the even with one of the \emph{currently associated} master keys of the DID, and publish the event inside the metadata of a transaction.
+      The event also carries a hash of the last \emph{UpdateDID} performed over the DID (or the hash of the \emph{CreateDID} if this is the first 
+      update)
+\item Sign the event with one of the \emph{currently associated} master keys of the DID, and publish the event inside the metadata of a transaction.
 \end{itemize}
@@
 
-In order to obtain the keys associated to a DID in short form, we simply read the state we have constructed so far by processing the CreateDID and UpdateDID events we read from the blockchain.
-The list of DIDs associated to the DID is the list of keys we see in our internal state.
+In order to obtain the keys associated to a DID in short form, we simply read the state we have constructed so far by processing the \emph{CreateDID} and \emph{UpdateDID} events we read from the blockchain.
+The list of keys associated to the DID, is the one we see in our internal state.
 If we do not find the DID as a published one in our state, we return a \emph{DID unknown} response.
@@
 
-Lets us define first what a credential is in the context of this document
+Lets us refine first what a credential is in the context of this document
 
@@
 
-In the following steps, we assume the issuer and subjects have already established a secure communication channel.
+In the following steps, we assume the issuer and subjects have already established a secure communication channel. We also assume that the issuer has
+a published DID that will be used to represent him in credentials.
 In order to issue a batch of an arbitrary number $N$ of credentials, the issuer will:
@@
 \item Ask to each subject the DID they would like to use for the credential they will receive.
-\item The issuer creates the credentials for each subject. It uses his DID and the key id of an \emph{issuing key} to populate
+\item The issuer creates the credentials for each subject. It uses his published DID and the key id of an \emph{issuing key} to populate
       the credential corresponding fields. On each credential, it adds the corresponding subject DID as one of the claims.
@@
 \item The issuer encodes each signature, and concatenate them to their corresponding credentials using a dot (".") as separator.
-      This produces strings of the form $\langle{}encoded\_credentials\rangle{}.\langle{}encoded\_signature\rangle{}$. We call these strings as \emph{signed credentials}.
+      This produces strings of the form $\langle{}encoded\_credentials\rangle{}.\langle{}encoded\_signature\rangle{}$. We call these strings asa
+      \emph{signed credentials}.
 \item Now, the issuer takes all the signed credentials, and computes a merkle root from them.
-\item The issuer creates an \emph{IssueBatch} event that contains the merkle root, and signs the event with an \emph{issuing key} associated to his publicly known DID. 
+\item The issuer creates an \emph{IssueBatch} event that contains the merkle root and issuer DID, and signs the event with an \emph{issuing key} associated to this DID. 
 \textbf{Note}: Today we use the same issuing key for the event signature and the individual credentials signature, but those could be different keys.
 \item The issuer attaches the signed event to the metadata of a transaction and sends it to the blockchain.
-\item The issuer gives to each user their corresponding signed credential along with their associated merkle inclusion proof.
+\item The issuer gives to each subject their corresponding signed credential along with their associated merkle inclusion proof.
 \end{itemize}
@@
 
-Note that, to issue credential batches, the issuer DID \emph{must be published} already. However, users' DIDs can remain unpublished.
+Note that, even though the issuer DID \emph{must be published}, subjects' DIDs can remain unpublished.
 
@@
 
-\subsection{Specific Sub-Protocols}
-\label{ssec:subproto}
-
-\subsubsection{End-to-End Encrypted Data Exchange via the Connector}
-\label{sssec:e2eeconnector}
-
-Assuming each participant of the system owns a (set of) DIDs, we want to let
-holders receive new credentials from issuers, in a secure -- yet convenient --
-manner. We describe a protocol for this purpose.  At the moment, we require
-that issuer and prospective holder can perform a one-time physical interaction
-with each other or, alternatively, that they have a secure channel at their
-avail (although possibly cumbersome to use, hence we only require to use it
-once).
-
-In a nutshell, the proposed protocol is composed essentially of two phases. In
-the first phase, the issuer shares a QR code with the holder. This QR code
-contains the issuer's public key (or, maybe, its DID), a random value, and a
-session identifier. This exchange takes place through a secure (i.e.,
-confidential and authenticated) channel, such as physical exchange. Probably
-immediately, although also possibly at a later point in time, the prospective
-holder sends back her own public key (or, alternatively, her DID) and the
-session identifier, all authenticated with a MAC, where we use the random value
-in the QR code as secret key. The issuer uses the session identifier to locate
-the corresponding session and, now that it received in an authenticated manner
-the public key of the holder, can leverage hybrid encryption techniques to
-establish an end-to-end encrypted session, e.g., using ECIES \cite{abr01}.
-Ensuring end-to-end encryption and authentication is important at this point, as
-all the information exchanged between issuer and holder is routed through the
-connector: an entity or set of entities who ensure that asynchronous
-communication can take place between issuer and holder. Thus, ECIES is crucial
-to ensure the secrecy of the information, end-to-end. Since the holder needs to
-have certainty that the data it receives comes from the issuer (and ECIES does
-not authenticate the sender), we have the issuer digitally sign the data it
-sends through the ECIES-secured channel. Note that we could involve the random
-value shared via the QR code for this. But that would force us to re-execute the
-first phase of the protocol even when the QR code is compromised after having
-completed the first phase of the protocol. Digital signatures using the issuer's
-DID prevent this.
-
-While the protocol is simple, and is based on common cryptographic constructions,
-it is easy to get such protocols wrong, as pointed out in numerous occasions
-\cite{davi01, kraw01}. Hence, we have used Tamarin%
-\footnote{https://tamarin-prover.github.io/ (Last access, October 5th, 2021.)}
-to model our protocol\footnote{Source code for the model available here
-  \url{https://github.com/input-output-hk/atala-prism/blob/research-tamarin-connector/prism-backend/research/formalizations/connector.spthy}
-  \todo{Update to final URL.}}, which is schematized in \figref{fig:e2econnector}
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[scale=0.4]{figures/connector.png}
-  \caption{Sequence diagram for the E2EE protocol through the connector.}
-  \label{fig:e2econnector}%
-\end{figure}
-
-The security properties that we prove are as follows (we refer to the actual
-model for the formal definition):
-
-\begin{description}
-\item[Code secrecy.] Codes exchanged via a QR code are always confidential.
-  Note that this is trivial, as it is exchanged via a secure channel, and
-  the holder never sends it back in the clear.
-\item[Code injectivity.] Every QR code that is received by a holder, allegedly
-  sent by an issuer, was sent before by that issuer. Again, this is trivial due
-  to the secure channel used to exchange the QR code.
-\item[Holder's public key authenticity.] Every message received by an issuer
-  in step 3, containing a public key for key-exchange usage, that was
-  allegedly sent by a holder, was indeed previously sent by that holder.
-  This is ensured through the message authentication code (MAC) that
-  leverages the random QR code exchanged via the secure channel, which is
-  only known to the issuer and the holder.
-\item[Holder's public key injectivity.] For every session in which an
-  issuer receives in step 3 a message, allegedly sent by a holder in
-  step 2, containing the holder's public key, it was that holder, in
-  the same session, who sent the public key in step 2.  
-\item[Credential secrecy.] This property has two variants: it ensures
-  secrecy for credentials sent by an honest issuer to a holder that was honest
-  at the moment of sending the credential, and is not compromised afterwards;
-  and it also ensures secrecy for credentials received by an honest holder,
-  allegedly from an honest issuer, if both holder and issuer were honest when
-  the credential is received, and they are not corrupted afterwards. Altogether
-  with the credential authenticity property shown next, it ensures that only
-  (honest) holder and issuer learn the contents of a credential.
-\item[Credential authenticity.] All messages containing a credential, received
-  by a holder at step 5, where indeed sent by an issuer and addressed to that
-  same holder, as long as both issuer and holder keys are not compromised.
-\item[Credential non-injectivity.] All messages containing a credential, received
-  by a holder at step 5, were sent by an issuer and addressed to that holder
-  at step 4. Note, however, that both messages in steps 4 and 5 don't necessarily
-  pertain to the  same ``session'' (in instantiations where parallel sessions
-  may occur). However, this does not pose a risk, as in any case, the messaged
-  is sent by the issuer, and received by the intended holder.
-\end{description}
-
-Concerning the technical details of the protocol, note that we are combining
-signature and encryption (plus, the MAC-based authentication natively provided
-by ECIES). This places us in the context put forward in \cite{davi01}, that
-discusses some good practices when combining such primitives. In a nutshell,
-we follow the sign-then-encrypt approach\footnote{What we call here ``sign-then-
-  encrypt'' is called ``Sign \& Encrypt'' in \cite{davi01}. However, we find
-  more explicit the naming convention of \cite{kraw01}, which is more consistent
-  when referring to the order in which the primitives are used -- order that, in
-  these cases, is crucial.}, combined with including the public
-keys of both holder and issuer into the signed (and then encrypted) data.
-This intertwines the inner layer (the signature) with the outer layer (the
-encryption), ensuring that any alteration on any of them will be detected.
-We note that there are other options that, a priori, are equally secure -- e.g.,
-encrypt-then-sign, including also the sender's public key in the encrypted data
-(but that would require separately signing a (hash of) the data, to ensure
-non-repudiation). It is worth noting that ECIES follows the
-encrypt-then-authenticate approach, which is proven to realize secure channels
-in \cite{kraw01}, as long as the underlying encryption scheme is IND-CPA secure,
-and the underlying MAC function is secure.
-
-%----------------------------------------------------------------------------------------
-%	PROPERTIES
-%----------------------------------------------------------------------------------------
-
-\section{Properties we believe we have}
-
-\paragraph{Unforgeability.} A user cannot forge issuer-generated credentials.
-\paragraph{Privacy against issuers.} An issuer does not learn whether a user (who acquired a credential from the issuer) has interacted with a given verifier (assuming no cooperation between issuer and verifiers).
-\paragraph{Revocability.} An issuer can revoke a previously-issued credential without users’ cooperation.
-\paragraph{Protection against credential reuse.} A verifier can ensure no credential is used by different DIDs. 
-\paragraph{Deferred and offline verification checks.} A verifier can verify the revocation status of a credential asynchronously without users’ participation.
-A verifier can also verify a credential without contacting the internet, in which case the verification result is with respect to the last time the verifier synchronized with blockchain events.
-\paragraph{Resistance to key rotation.} If an issuer's issuing key is revoked, credentials already issued by that key remain valid.
-This means that the issuer does not need to re-issue the credentials signed by a compromised issuing key.
-This is possible due to the fact that key revocation and credential issuances are timestamped.
-Hence, if an issuing key is revoked, credentials already issued remain valid unless they are explicitly revoked.
-\paragraph{Independence of issuers and verifiers.} Verifiers only need to know which issuer DIDs they trust. They do not need to contact issuers to query issuance nor revocation lists.
-\paragraph{Past preservation.} Any party that verifies a credential has non-reputable information of when the credential was valid even if it has been revoked.
-
-\section{Properties we are not offering}
-
-\paragraph{Unlinkability.} A coalition of verifiers cannot link activities of users across verifiers.
-\paragraph{Minimal disclosure.} A user only reveals what is necessary to establish a relationship with a verifier.
-
 %----------------------------------------------------------------------------------------
@@
 
-\subsection{Scaling}
+\subsection{Increasing scalability}
 
@@
 The properties brought by the blockchain come at a cost. Namely, the protocol throughput (number of events that participants can attach in 
-transactions per unit of time) is bounded to the blockchain throughput. In order to scale the throughput, we have reviewed Sidetree's approach. The 
-idea behind Sidetree is to not publish individual events attached to blockchain transactions, but to publish a hash-link to an off-chain content 
-addressable storage (CAS), like IPFS. The CAS will contain the file referenced by the hash-link, which contains a batch of many protocol events 
-(allowing to transcend the size limits imposed by blockchain transactions).
+transactions per unit of time) is bounded to the blockchain throughput.
+In order to scale the throughput, we have reviewed Sidetree's  \footnote{https://identity.foundation/sidetree/spec/} approach.
+The high level idea behind Sidetree is to not publish individual events attached to blockchain
+transactions, but to publish a hash-link to an off-chain content addressable storage (CAS), like IPFS. The CAS will contain the file referenced by 
+the hash-link, which contains a batch of many protocol events (allowing to transcend the size limits imposed by blockchain transactions).
 
@@
 reveal a file, the protocol participants stop processing further batches until the missing file is revealed. This is not possible in Sidetree because
-any participant would be able to freeze the system by not revealing a file. The protocol would still allow users to publish events on-chain directly, 
-leaving space for some decentralization for those participants that do not want to depend on the centralized batcher.
+any participant would be able to freeze the system by not revealing a file.
+
+This protocol variation would still allow users to publish events on-chain directly, leaving space for some decentralization for those participants that do not want to depend on the centralized batcher.
 
@@
 
-\bibliographystyle{plain}
-\bibliography{article}
+At the time of this writing, we haven't implemented any of the above approaches.
+We had, however, implemented on-chain batching, which allows to submit multiple events in a single transaction.
+The events are processed in order per transaction.
+This has been helpful in use cases where a multiple events coming from different entities, are submitted to the same PRISM node to publish them.
 

### 2021-11-23 prism-backend/research/soa_review/ac.tex
Added review of HS21.

@@
   through the network.
+\item[\cite{hs21}:] This work merges AC approaches based on SPS-EQ and aggregate
+  signatures, and also introduces the separation between a trusted but restricted
+  device, and a less trusted but powerful device typical in DAA systems. The
+  former is referred to as \emph{core}, and the latter as \emph{helper}, hence
+  the Core-Helper AC (CHAC) acronym. In addition to the previous basic building
+  blocks, the system uses a Signature with Flexible Public Keys (SFPK) scheme.
+  Roughly, these are signature schemes where the public keys can be randomized,
+  but in a manner that no adversary can decide whether two public keys are
+  related or not (i.e., if one is a randomization of the other). Users identities
+  are SFPK keypairs, where the public part gets signed by the issuer, using an
+  AAEQ scheme (Aggregatable Attribute-based Signature Scheme on Equivalence Classes).
+  Roughly, an AAEQ scheme is a combination of attribute-based signatures on
+  equivalence classes (which the authors combine with Tag-based Signatures on
+  Equivalence Classes), and aggregate signatures. In the proposed AAEQ scheme,
+  a tag is derived from an attribute an a nonce, which is then ``signed'' (note:
+  this tag resembles much the concept of nyms based on scopes). Since signatures
+  (and tags) are group elements sharing the same discrete log (the signer's key),
+  they can be aggregated easily via multiplication. Hence, for each attribute that
+  the issuer wants to grant to the user, it creates an independent signature where
+  the tag depends on the attribute to grant. Then, the user can just aggregate
+  all of them into one credential. In addition to this, the authors split the
+  operations (which are in the bilinear setting), in a way that requires the
+  core to perform only a few operations in $G_1$. The result seems to be quite
+  efficient. However, it only supports selective disclosure (no advanced
+  privacy-preserving policies), and even revocation is not considered from scratch,
+  although the authors sketch an approach to integrate it -- which probably
+  would require a more formal analysis and would incur in (possibly bad?)
+  added costs.
 \end{enumerate}
@@
   accounts, sybil resistance, extensibility, availability, decentralization.
+\item[\cite{hs21}:] Security is given through game-based definitions of
+  unforgeability, anonymity, and dependability. The first two are the usual ones,
+  while the latter roughly requires that an adversarial helper cannot produce
+  successful showings without cooperation from the core. It would be interesting
+  to make a detailed comparison with security models of DAA (usually in the UC
+  framework, although some game-based (seemingly flawed) definitions exist).
+  The main argument that the authors give when comparing to DAA, is that the
+  latter does not support attributes, and it is essentially a group signature
+  scheme without revocation and optional linkability (this frontier is also
+  blurry, see \cite{dl21}).
 \end{enumerate}
@@
     to be practically like a group signature scheme (without revocation...)}
+\item[\cite{hs21}:] The main variation here is the application of the core-helper
+  division (typical of DAA) to the AC domain.
 \end{enumerate}
@@
 PS: Tokenization.
-U-Prove.
-Idemix.
-Signal's AC \needcite
+Signal's AC \cite{cpz20}.
+
+\begin{itemize}
+\item U-Prove (see ref. 65 in \cite{hs21}):  This is largely based on Brands
+  thesis. There was a deployment by Microsoft, mostly concurrent to Idemix.
+  They are one-show credentials, but seemingly there is recent real-world
+  deployments based on them (references in p.1 of \cite{hs21}):
+
+  \begin{itemize}
+  \item Privacy-Pass by Cloudflare.
+  \item Trust Tokens API by Google.
+  \item PrivateStats proposal by Facebook.
+  \end{itemize}
+
+\item Idemix \cite{ch02}: This is largely based on CL signatures. It has been
+  deployed (or is being deployed) in Hyperledger Fabric, and I think there is
+  some of it in Indy too.
+\end{itemize}
+
+\cite{hs21} contains also many references to ``practical'' applications of
+ACs. However, these are mostly references to papers in cryptographic venues,
+so I suspect that they are more academic than real-world systems.
 

### 2021-11-24 prism-backend/research/soa_review/ac.tex
Some synthesis effort in the AC part.

@@
 
-First proposed in \cite{chau85}.
-CL signatures (idemix) \cite{cl01,cl04}.
-UC formalisation in \cite{cdhk15}.
-Brands works (U-prove).
-Coconut paper, referenced in \cite[Section 1]{cdl+20}: anonymous credentials with
-threshold opening.
+\todo{Big: Brands's line of works (U-prove).}
 
@@
 Anonymous Credentials (ACs) were first proposed by Chaum \cite{chau85}, and
-later formally treated and optimized in a series of papers by Camenisch and
-Lysyanskaya \cite{cl01,cl02,cl04}. Roughly speaking, users receive credentials
-from an issuing organization, which can then use to authenticate against some
-verifier. The main property is that this authentication process can be done
-in a privacy-preserving way. This typically means that the verifier cannot
-link different authentication processes by that same user. And, usually, in
-credentials composed by multiple attributes, that the verifier only learns
-the attributes that the user is willing to share (or a function of them).
+further studied, formally treated, and optimized, in a series of papers by
+Camenisch and Lysyanskaya \cite{cl01,cl02,cl04} and, independently, by Brands
+\needcite\footnote{Camenisch and Lysyanskaya line of work is well known for
+  IBM's Idemix system, and Brands's work for Microsoft's U-Prove. More detail
+  appears in the sequel.}. In an AC system, roughly speaking, users receive
+credentials from an issuing organization, which they can then use to
+authenticate against some verifier. The main property is that this
+authentication process can be done in a privacy-preserving way. This typically
+means that the verifier cannot link different authentication processes by that
+same user. Usually, credentials are composed by multiple attributes, such that
+the verifier only learns the attributes that the user is willing to share (or a
+function of them).
 
@@
 \paragraph{Main approaches.} %
+The more fruitful line of work within the AC domain is the one initiated by
+Camenisch and Lysyanskaya \cite{cl01,cl02,cl04} (henceforth, CL credentials or,
+when referring to the underlying signature schemes defined in \cite{cl02,cl04},
+CL signatures). The core idea is simple: in order to build a (basic) AC
+system, all that is needed are a commitment scheme, and a signature scheme
+with efficient protocols for signing committed values, and proving knowledge
+of a signature. From this, a basic AC system can be derived as in \figref{XXX}.
+Essentially:
+
+\begin{itemize}
+\item User $A$ randomly produces a secret value $s_A$, and commits to it,
+  producing $c_A$.
+\item User $A$ interacts with issuer $I$ to get a signature on $s_A$. To
+  avoid leaking the secret to $I$, $A$ uses $c_A$, proving knowledge of the
+  associated secret. The produced signature $\sigma_A$, is $A$'s anonymous
+  credential.
+\item When $A$ needs to convince a verifier $B$ that she owns a valid credential
+  issued by $I$, she just has to create a zero-knowledge proof of knowledge
+  of $\sigma_A$.
+\end{itemize}
+
+Usually, the commitment to the user's secret key is known as a pseudonym, or
+in short form, \emph{nym}. These nyms have proven to be a useful component to
+ensure security and privacy properties -- and are also leveraged in many group
+signature and DAA works.
+
+A large part of the academic works in the AC domain follow this approach, which
+is then extended to support enhanced functionality. For instance, in order to
+support multiple issuers (and, in some sense, multiple attributes)
+\cite{cl01,cl02,cl04} \todo{check if the references are correct} require an
+extra protocol for proving, in zero-knowledge, equality of two committed and signed values.
+This allows user $A$, with credential $\sigma_A^I$ obtained from issuer $I$ and
+credential $\sigma_A^J$ obtained from issuer $J$, to prove $J$ that she has a
+valid credential from $I$, by issuing a zero-knowledge proof of equality for
+both credentials. Now, if each credential is associated with a different set of
+attributes, this also lets to ``naively'' build multi-attribute AC systems.
+
+For multi-attribute ACs, though, much more efficient variants are possible. To
+begin with, CL signatures allow signing blocks of messages (and commitments),
+which can be seen as attributes signed by the issuer. BBS+ signatures
+\cite{am06,cdl16b}, and PS16 signatures \cite{ps16} also support similar
+functionality, and have been leveraged to build multi-attribute AC systems
+too (e.g., \cite{cks10} gives a construction with BBS+ credentials, and
+\cite{sms+19,halp20} are based on PS16). These family of signatures on blocks
+of messages have yet another very useful property: signatures are easily
+randomizable, which can be used (along with the previously mentioned
+zero-knowledge proofs) to make unlinkable showings of the same credential.
+AC systems achieving the latter property of unlinkable showings are said
+to offer \emph{multi-show} credentials.
+
+Most of these systems also have in common that, being based on building blocks
+leveraging discrete logarithm structures, they are easily extended to prove
+arbitrary statements on the credentials attributes -- such as the usual ``Over
+18'' claim. However, while it is certainly doable, the approach does not scale
+for complex statements involving multiple attributes \todo{some concrete
+  figures?}
+
+Restricting the expressiveness, and focusing on letting the credential holder
+reveal only a subset of the attributes in a credential, more efficient schemes
+have been proposed, leveraging algebraic tricks such as structure-preserving
+signatures on equivalence classes (SPS-EQ), along with vector commitment schemes
+\cite{cdhk15}, or set commitment schemes \cite{fhs19}. The former uses Lagrange
+interpolation to allow revealing only a subset of the committed messages;
+\todo{what was the specific technique of \cite{fhs19}?}. \cite{fhs19}, is more
+efficient, as avoids complex zero-knowledge proofs; however it does not support
+blind issuance of credentials, as opposed to \cite{cdhk15} \todo{confirm this
+  last part, and refine}.
+
+\todo{Mention the subline of delegatable credentials, with controlled
+  malleability.}
+
+All AC systems mentioned up to this point follow, up to small variations, the
+same approach: randomizable signatures on sets of (committed) messages, with
+(somehow) efficient proofs. \todo{Move to the ones based on predicate
+  encryption.}
+
+\todo{End with the MAC-based approach.}
 
@@
   added costs.
+  \note{The concept of aggregation here is different than the one in \cite{cl11}.
+    In the latter, users can aggregate credentials from different issuers. Here,
+    this is not possible, as aggregation won't work for different signing keys
+    (i.e., issuer keys). Hence, aggregation rather refers to receiving multiple,
+    independently signed, attributes by the same issuer, and then combining them
+    into a single credential by that same issuer.}
 \end{enumerate}
@@
 \begin{itemize}
-\item : Delegation (\cite{cklm14} relies on \cite{cklm12}).
-\item \cite{cgm16} An AC system that builds ACs from existing (conventional,
-  such as ECDSA) signatures. \cite{kkl+16} achieves similar results with a
-  different approach?
+\item \cite{bckl08}.
+\item \cite{sand20}.
+\item \cite{kkl+16}: achieves similar results to \cite{cgm16} with a different approach?
 \end{itemize}

### 2021-11-25 prism-backend/node-technical-report/article.tex
ATA-5719: Add node technical report
This commit adds the first draft of the node technical report

\documentclass[10pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{graphicx}

\title{PRISM node technical notes}

\author{Atala PRISM team - IOG}

\date{}

\begin{document}

\maketitle

%\begin{abstract} 
%This document describes implementation details about the PRISM node. 
%\end{abstract}

\setcounter{tocdepth}{3}

\tableofcontents 
\newpage

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\section{High level overview}

This document provides a technical description of how the PRISM protocol has been implemented.

We assume the reader has familiarity with the PRISM protocol, and understands some high level aspects about Cardano. The document makes focus on closing the gap between the PRISM protocol, and a practical implementation.

At a very high level, the PRISM protocol establishes that each protocol participant will manage his own keys, publish their own events, and read the full underlying blockchain to be aware of the state of the system. The state of the system consists of:
\begin{itemize}
  \item An association of DIDs to their list of keys (and respective timestamps)
  \item A set of merkle roots associated to their corresponding issuer, and the timestamp in which they where added on-chain
  \item A set of revoked roots (or credentials hashes) associated with the timestamp in which they were added on-chain
\end{itemize}

Throughout this document we will use the term \emph{operation} to refer to protocol events.

The PRISM node is in charge of:
\begin{itemize}
  \item Receiving the user's signed operations (\emph{CreateDID, UpdateDID, IssueBatch, RevokeCredentials}), accom
  \item Construct transactions to submit users' operations
  \item Track the confirmation of submitted transactions
  \item Read protocol operations from the blockchain, validate them and apply them
  \item Reply to users' queries about the status of submitted operations
  \item Reply to users' queries about the state of DIDs, batches and credentials
\end{itemize}

In the following sub-sections, we will describe how the node is structured, the trade-offs taken in order to provide a practical implementation, and the API plus core models that are related to the node.

\subsection{Node sub-components}

The PRISM node implementation is based upon Cardano. Our implementation is hence dependent on some Cardano components, namely, the Cardano wallet and db-sync. We use the Cardano wallet as part of the submission flow, the wallet exposes an HTTP API that the PRISM node uses to construct transactions with metadata and submit them to the blockchain. On the other side, we use db-sync, a component in the Cardano stack that indexes the blockchain information in a database. We use db-sync to obtain information of new blocks confirmed by the Cardano network, which allow us to process new events we retrieve from the blockchain.

Outside of Cardano dependencies, the node structurally consists of two main sub-components. One could be described as an operations queue that contains the operations that the user has submitted along with some status representing whether the operation has been submitted, is waiting confirmation, has been applied, or other status we will describe later in this document. The operations queue is crucial to orchestrate the submission flow for operations. This queue also represents state that is local to the node instance, and is not known by other nodes in the PRISM network.

The other core component that builds-up the node is an operations' processing service. This component is the one responsible of processing the operations retrieved from db-sync, validate them apply their effect to the system state. This component is crucial in the operations' processing flow. The state updated by this component is what we consider to be the global state that all PRISM nodes that are up-to-date with the network will share.

Putting all pieces together, the high level interaction between these component can be broken between two flows that we will describe in depth in future sections.
\begin{itemize}
  \item Submission flow: The user calls the PRISM node with an operation. The node adds it to a queue. A timeout triggers to gather operations in the queue and submit them. The submission mechanism calls the Cardano wallet, which actually submits the transaction carrying the operations. A separate node timeout periodically controls the status of the transactions submitted, and handles retries when needed.
  \item Processing flow: The node receives a notification from db-sync announcing that a new block has reached a determined depth. The processing service is called with this new block, inspects every transaction in search of PRISM events, validates them and apply their effect on the node state.
\end{itemize}

\subsection{Practical challenges and trade-offs selection}

Now that we have a basic description of what the node does, and a high level intuition of how it is accomplishing it, we should expose some points to contrast the idealised protocol description with an actual implementation.

During the development process and based on some interactions with users of the node, we observed the following:
\begin{enumerate}
  \item Many participants may share a single node instance
  \item The underlying blockchain fees may be costly for some use cases if each event is submitted in a separate transaction
  \item The underlying blockchain wallet may not be available (UTxOs may be insufficient at times of high demand)
  \item The underlying blockchain may suffer congestions
  \item Blockchains may produce temporal forks. This is, a network may temporarily be split between two (or more) competing candidate chains. These 
	forks are usually short-lasting, their frequency and extension is dependent on the consensus protocol of the underlying network
\end{enumerate}

In order to address part of these observations, we took some initial design directions:
\begin{itemize}
  \item The node optimizes fees by batching many operations in the metadata of a single transaction (on-chain batching)
  \item The node provides a configurable timer for basic accumulation of operations
  \item The node limits the requests made to the Cardano wallet to avoid overloading it
  \item The node manages transaction retries
  \item The node waits for enough depth to make fork-based rollbacks improbable
\end{itemize}

The above points allow for a relative efficient management of fees, time delays, submission complexity.

The implications of sharing a node instance is dependent on use case. If the common node instance is used to submit operations on behalf of many (related) entities, then some coordinator is needed to handle the transaction costs, and submission rules. For instance, a company may use a single node to allow multiple employees issue credentials or manage DIDs on behalf of the company. It is responsibility of the company to administrate any limit on the number of operations that the node will accept/submit to balance fee costs. If unrelated parties aim to share a node, e.g. a third party decides to provide an operations' submission service, then this third party would be responsible of managing submission limits and/or a cost model per user.

The node itself does not provide an authentication mechanism. In the same way a system does not expose openly a database server IP/Port, or a blockchain node nor wallet, we extend the recommendation to hide the PRISM node from public access from the internet.

\subsection{API and core models}

\section{Operations submission flow}

\section{Operations procesing flow}

\end{document}

### 2021-11-25 prism-backend/research/soa_review/ac.tex
Some writeup on ACs main approaches, security models, and functionality. Doc reorg.

@@
 
-\todo{Big: Brands's line of works (U-prove).}
-
-\begin{enumerate}
-\item Main intuition.
-\item Evolution of main security models.
-\item Variations concerning functionality.
-\item Evolution in efficiency.
-\item Main issues.
-\item Approx. number of related works in main crypto+security venues: IACR,
-  Esorics, CCS, AsiaCCS, SP, EuroSP, Usenix Sec and Privacy, PETs...
-\end{enumerate}
-
+\paragraph{Main intuition.}
+%
 Anonymous Credentials (ACs) were first proposed by Chaum \cite{chau85}, and
@@
 \subsection{Approaches, Models, and Variations}
+\label{ssec:acapproach}
 
-\paragraph{Main approaches.} %
+\subsubsection{Main approaches.}
+%
 The more fruitful line of work within the AC domain is the one initiated by
@@
 with efficient protocols for signing committed values, and proving knowledge
-of a signature. From this, a basic AC system can be derived as in \figref{XXX}.
-Essentially:
+of a signature. From this, a basic AC system can be derived essentially as
+follows:
 
-\begin{itemize}
-\item User $A$ randomly produces a secret value $s_A$, and commits to it,
-  producing $c_A$.
+\begin{enumerate}
+\item User $A$, with secret value $s_A$, commits to it into $c_A$.
 \item User $A$ interacts with issuer $I$ to get a signature on $s_A$. To
@@
   of $\sigma_A$.
-\end{itemize}
+\end{enumerate}
 
@@
   last part, and refine}.
+%
+Also improving efficiency, but restricting to the scenario in which the issuer
+is the same entity as the verifier (as in ticketing systems for public transport),
+\cite{cmz14}, replaces signatures with algebraic MACs.
 
-\todo{Mention the subline of delegatable credentials, with controlled
-  malleability.}
+Somewhat similar is the approach to (delegatable) credentials that builds on
+signatures with controlled malleability \cite{bcc+09,cklm14}, where \cite{cklm14}
+is a generalization of \cite{bcc+09}. Roughly, credentials are signatures, built
+from non-interactive zero-knowledge proofs of knowledge, on commitments to the
+user key, that support \emph{controlled malleability}. This malleability means
+that both the proof and the statements can be randomized and transformed, but
+only for allowed transformatoins. The specific transformation considered for
+delegation requires that a credential with depth $L$, can only produce a credential
+with level $L+1$. Credential showings are also represented through transformations,
+through which the holder proves knowledge, and equality, of the secret in the
+``source'' and ``target'' nyms. Although the credentials in these works do not
+include multiple attributes (some hint on how to support public attributes is
+given in \cite{bcc+09}), it is certainly possible to do so through a proper
+transformation -- although, probably, the result won't be very efficient if
+done naively \todo{specific figures?} The notion of transformations is interesting,
+though, as the authors prove that it is similar (or even more generic) than those
+used to achieve expresiveness in related digital singature schemes (such as
+policy-based signatures \needcite and delegatable functional signatures \needcite).
+Thus, it is reasonable to expect that very expressive AC systems could be built
+with this approach.
 
@@
 same approach: randomizable signatures on sets of (committed) messages, with
-(somehow) efficient proofs. \todo{Move to the ones based on predicate
-  encryption.}
+(somehow) efficient proofs. A completely different approach is described in
+\cite{dmm+18}, based on predicate encryption. In predicate encryption, given
+a master key pair, decryption keys associated with specific predicates can be
+derived. Messages, and attribute sets, are encrypted with the master public key,
+such that the resulting ciphertext can only be decrypted with a decryption key
+associated with a predicate that is satisfied by the attributes in the
+ciphertext. Assume an attribute space that can be represented by binary strings
+$\Sigma$. On one hand, policies defined by verifiers in \cite{dmm+18} are encoded
+as binary circuits through strings in $\Sigma$ too\footnote{\todo{This seems
+    like an abuse of predicate encryption, as encryption receives a predicate,
+    rather than an attribute set.}}, which can thus be associated to
+ciphertexts through the predicate encryption process. On the other hand,
+credentials received by users are decryption keys on a generic policy $f$, with
+a hardcoded set of attributes (the attributes that the user is granted), that
+can evaluate circuits. Then, intuitively, in order for a verifier to check
+whether a user owns a attribute-based credential meeting certain policy $g$, it
+creates a ciphertext with encoding a circuit for $g$. If the user can decrypt
+this ciphertext, the verifier accepts. This only supports public attributes
+(i.e., known to the issuer), though. A negative part of this approach is that
+credential showings can only be interactive, whereas in the randomizable proofs
+approach, they can be made non-interactive too.
 
-\todo{End with the MAC-based approach.}
+\subsubsection{Main Security Models.}
+%
+All AC systems include \emph{anonymity} and \emph{unforgeability} as main
+security properties. Up to minor variations depending on extra functionality,
+anonymity typically captures that, concerning a user's credential, nothing
+should be learnt by third parties that the user does not explicitly reveal.
+E.g., for ACs that support multiple attributes and selectively disclosing
+subsets of them, anonymity captures that the information leaked during a showing
+of such credential is limited to the subset of attributes voluntarily revealed
+by the user. Since multi-show credentials are also the most common type,
+anonymity also captures that two different showings must be unlinkable.
+As mentioned, further variations in the functionality affect anonymity --
+e.g., in systems supporting delegation, the delegation chain may be required
+to be kept private.
+% 
+Concerning unforgeability, it basically captures that no adversary can make
+a verifier accept a credential that has not been honestly produced by an
+issuer of the system. Again, there are variations to this. For instance, when
+credentials are composed of attributes that can further be selectively
+disclosed. In this case, the adversary should not be able to prove ownership
+of a set of attributes not contained within the set of attributes that have
+been leaked.a showing that include attributes not contained in credentials leaked to the
+adversary.
 
-\begin{enumerate}
-\item[\cite{cl01}:]
-  \begin{itemize}
-  \item Functionality: FormNym, GrantCred, VerifyCred, VerifyCredOnNym.
-  \item Approach: Users create a pseudonym with each organization. For this,
-    they have to register first with the organization (associating a key to
-    a user name). Whenever the user wants to get a credential from a organization
-    in which he registered, he has to authenticate, and then the organization
-    decides whether or not to grant the credential. Users can show their
-    credentials to organizations in two ways: (1) just proving that they own a
-    credential issued by some organization; or (2), proving that they own a
-    credential issued by some organization \emph{and} this credential is over
-    the same pseudonym that the user holds with the verifying organization.
-    Essentially, pseudonyms are the concatenation of two random numbers (one
-    provided by the user, and the other by the organization). They get
-    associated an authenticating tag, which is a statistically hiding commitment
-    to the user secret (computed using randomness provided by both user and
-    organization). Organizations keep a database of the generated pseudonyms.
-    To get a credential from an organization where the user registered
-    previously, the user proves knowledge of the secret involved in the
-    pseudonym. The organization then creates a ``random signature'' (by using a
-    the inverse of random exponent, with the help of the factorization of an RSA
-    modulus chosen by the organization at setup time) over the pseudonym, and
-    gives that to the user. Users can show the credentials (in any of the
-    previously stated two ways) by creating non-interactive zero-knowledge
-    proofs of knowledge of the appropriate secret. Note that, in case (2),
-    this means that the proof is over two pseudonyms, which must share the
-    same secret.    
-  \end{itemize}
-\item[\cite{cl02}:]
-  \begin{itemize}
-  \item Approach: Te paper aims at improving efficiency of AC systems, as
-    well as still ensuring that the user can retrieve their credentials in
-    a privacy-preserving manner. For this purpose, the core of the paper
-    describes a signature scheme that allows signing blocks of messages,
-    and later prove, in zero-knowledge, knowledge of such a signature. To
-    enable private retrieval of credentials, the authors describe a protocol
-    for their signature scheme, whereby the user specifices a commitment to
-    a message (or a block of messages, although this is not actually
-    formalized), and get a signature of the message in return. While the
-    authors do not strictly define an AC system, the application of their
-    signature system and related protocols to the AC domain seems direct.
-    Indeed, the same functionality as in \cite{cl01} seems straight
-    forward given the cryptosystems in \cite{cl02}.
-  \end{itemize}
-\item[\cite{cl04}:] Follows a similar approach to \cite{cl02}, although
-  changing the security assumptions to be based only on problems related
-  to the discrete logarithm, and on bilinear maps. Basically, defines a
-  signature scheme suitable for signing multiple messages, a protocol to
-  obtain a signature on a committed value, and a protocol to prove knowledge
-  of a signature. Concerning commitments, they rely on Pedersen commitment
-  scheme, for which protocols are known to prove knowledge and equality of
-  committed values. This lets them follow the same approach to \cite{cl02},
-  which is in turn the one in \cite{cl01}.
-\item[\cite{bcc+09}:] This is mostly a theoretical work, which is relevant
-  since it is (one of) the first to propose a delegatable anonymous
-  credentials systems. The building blocks are randomizable proofs of
-  knowledge that randomize both the proof and the statement (which the authors
-  build on top of Groth-Sahai proofs), and message authenticators (a variant
-  of signatures that require a special notion of unforgeability). Each user
-  can create pseudonyms, which are commitments to his secret key, and use
-  these commitments to prove ownership of and delegate credentials. These
-  pseudonyms are essentially as in the CL line of work (user with pseudonym
-  $N^A_U$ w.r.t. organization $A$ and $^B_U$ w.r.t. orgainzation $B$, can
-  prove to $B$ (resp. $A$) that $N^A_U$ and $N^B_U$ are related to the
-  same secret key). Delegations here follow a sequential order: i.e., if
-  a credential has level $L$, then its owner can further delegate this
-  credential, and the result would be a credential with level $L+1$. To
-  delegate, essentially, the delegator (with pseudonym $N_I$) and delegatee
-  (with pseudonym $N_D$) perform an interactive protocol
-  through which the delegatee receives a randomizable NIZKP that lets him
-  prove knowledge of an authenticator over $N_D$, issued by $N_I$. Since
-  both the proof and the statement can be randomized, verifiers do not
-  learn the chain of delegation.  Although this is informally mentioned,
-  ``attributes'' can be added to the delegation process too (besides to the
-  credentials themselves). This is suggested by adding the attributes -- which
-  would be visible to the verifier -- to the application of a hash function
-  used to derive the authenticator). 
-\item[\cite{cks10}:] The system proposed here follows the conventional
-  approach to anonymous credentials based on randomizable signatures (with
-  the possibility to sign committed values) over vectors of messages.
-  It however enables issuers to produce updates on already signed messages.
-  This updates can be leveraged to incorporate revocation. Essentially,
-  time is divided in epochs, and credentials include an attribute which
-  represents the expiration date/epoch of the credential. Users have to
-  prove that their credential is valid for the current epoch. Similarly,
-  to add new attributes, the issuer leverages the internal structure of
-  the signatures over vectors of messages, to basically add new messages
-  (attributes). In both cases, it is responsibility of the user to update
-  her credential given the latest update by the issuer. An example
-  instantiation is given using BBS signatures.
-\item[\cite{cmz14}:] This work differs from the rest in that they use
-  secret key cryptography rather than public key. Namely, they assume a
-  setting in which the issuer will also be the verifier (e.g., a
-  transportation organization that issues tickets for its travelers). In
-  this setting, it is reasonable to assume that both issuer and verifier
-  will have access to the same secret. Therefore, they replace signatures
-  with (algebraic) MACs. They do not create pseudonyms for end users (like
-  \cite{sms+19}). Other than that, the supported functionality is similar
-  to the rest: Setup and KeyGen to initialize the cryptographic parameters,
-  and produce the issuer's keys, respectively; an interactive protocol for
-  end users to blindly receive credentials (MACs) on their attributes; and
-  an interactive protocol for showing and verifying a credential. In case
-  that issuance does not need to be blinded, it becomes a non-interactive
-  protocol (i.e., the issuer just produces the credential and sends it to
-  the user). Otherwise, the user has to encrypt the attributes and prove
-  they are correct. Presentation only requires one message from the user
-  to the verifier.
-\item[\cite{cl11}:] The approach differs from the conventional ones. In this
-  case, the focus is on settings where users may want to combine multiple
-  credentials from different issuers. Thus, interest is on reducing the size
-  of the resulting credentials, and the efficiency of associated processes.
-  The approach is based on aggregate signatures. As usual, each credential
-  may contain several attributes. Each attribute is independently signed
-  by the issuer. Then, users can combine an arbitrary number of signed
-  attributes (by the same or different issuers) into a single aggregate
-  signature. Verification only needs the aggregated signature and the set
-  of public keys of all the involved issuers. To prevent different users
-  from aggregating their credentials, the authors resort to \emph{indexed}
-  aggregate signatures: an index is added to each signature, such that only
-  signatures that have the same index can be aggregated. In their instantiation,
-  the signature is a BGLS signature \cite{bgls03}, and the index is a BB
-  signature \cite{bb04}. The actual instantiation seems impractical (too many
-  linear costs, see the table in the paper).
-\item[\cite{cklm14}:] This work is, in essence, a generalization of \cite{bcc+09}.
-  The main novel building block are controlled-malleability NIZKs. Basically,
-  these are NIZKs that can be re-randomized, but only for a pre-defined set of
-  (NP) transformations. From this cm-NIZKs, malleable signatures are built.
-  From malleable signatures and commitments, delegatable credentials are built
-  as follows. Credentials are basically a tuple $(nym, l, flag)$, where $nym$
-  is a commitment to the user's private key, $l$ is the length of the credential
-  in the delegation chain, and $flag$ is either $cred$ or $proof$. Credentials
-  are accompanied with a malleable signature (which, for level 1 credentials,
-  it is a signature by the issuer). To create ``proofs'' or to delegate, the
-  credential owner has to apply one of the two allowed transformations. For
-  ``proofs'', basically the transformation that has to be applied to the original
-  proof (malleable signature) converts it to a proof showing that the prover
-  knows the secret in the ``source'' pseudonym and ``target'' pseudonym, and
-  both are the same. In the case of delegations, flag is set to ``cred'', and
-  the transformation converts the cm-NIZK proof into one that lets the prover
-  prove knowledge of the secret key in the ``source'' pseudonym, and allows
-  only to produce a new credential with structure $(nym', l+1, cred)$ -- i.e.,
-  from a credential of level $l$, only a credential of level $l+1$ can be
-  derived. On the delegation topic, the type of delegation this work ``supports'',
-  at least by default, is the simple one of hierarchical delegation.
-\item[\cite{cdhk15}:] The approach to build anonymous credentials is roughly
-  the same as in the previous works \cite{cl01,cl02,cl04}, although with
-  relevant differences that make it more efficient. Basically, users create
-  pseudonyms derived from a common secret. Then, any user can request a
-  credential. For this, the user needs to prove knowledge of the pseudonym's
-  secret. In return, the issuer produces an ``unlinkable redactable signature''
-  on a set of attributes, for that pseudonym. A redactable signature is
-  essentially a signature over a set (block) of messages, that enables
-  subsequent verification that a subset of those messages was signed. This
-  is essentially the same as in \cite{cl02,cl04}. However, to achieve
-  unlinkability, \cite{cdhk15} incorporates efficient zero-knowledge proofs
-  to prove correctness of the subset of the messages that a user wants to
-  ``show'' in a credential showing process. This ensures unlinkability (hence,
-  privacy). The internal scheme used for this is a vector commitment scheme
-  that uses Lagrange interpolation to allow checking that a subset of the
-  committed messages are indeed contained within the commitment. Moreover,
-  both the vector commitment scheme, and the vector signing scheme, are
-  structure preserving. This means that, since all the produced messages,
-  commitments, and signatures, are elements of the group (rather than of the
-  field), proving knowledge is much more efficient (e.g., it prevents costly
-  extraction required for security proofs).
-\item[\cite{ckl+15}:] Follows the conventional approach: a secure commitment
-  scheme with proofs of knowledge, and a signature scheme that allows to
-  sign vectors of messages, including commitments. Here, as in the seminal
-  works by Camenisch and Lysyanskaya \cite{cl01,cl02,cl04}, pseudonyms are
-  used as explicit building blocks. \todo{Not sure yet of how they are
-    made explicit in the generic construction. Clarify.}
-  A ``syntactic'' variation: they introduce
-  the concept of tokens both for credential issuance and presentation. To
-  request issuance of a credential, users have to produce an issuance token
-  from the set of attributes they want to reveal to the issuer, and the set
-  of attributes they want to hide (potentially coming from another credential
-  already owned by the user). An equivalent description applies for presentation
-  of a credential to a verifier. In both cases, the issuer/verifier has to
-  check the received token prior to issuing a credential or granting access.
-  They also add revocation functionality. For this, a revocation authority
-  (not necessarily the issuer) keeps a revocation information list, which is
-  basically a list containing no longer valid attributes. In order to prove
-  that their credentials are valid w.r.t. some attribute, users have to generate
-  a (non) revocation token, which proves that the attribute has not been
-  included in the revocation information list.
-\item[\cite{dmm+18}:] Follows a completely different approach to (most) other
-  works. Instead of using randomizable signatures (over committed values) or
-  some equivalent building block, it relies on predicate encryption.
-  Essentially, a user with attributes $A$ is given a decryption key for a
-  predicate $f_A(g)$ which, given a predicate $g$, returns $g(A)$. When
-  a verifier wants to check if a user has a set of attributes that meet
-  certain policy $h$, challenges the user to decrypt a ciphertext over
-  a random message that has been associated to predicate $h$. Then, only
-  if the attribute set $A$ of the user meets policy $h$, the user will be
-  able to decrypt the random message (since $f_A(h) = h(A) = 1$). This
-  protocol is actually augmented with some commitments, to prevent
-  misbehaviour from user and from verifier, but the approach is the same.
-  \doubt{There is something weird here, or that I do not understand --
-    predicate encryption requires a
-    set of attributes for encryption, rather than another predicate. I have
-    reached out to the authors to see if they can help me clarify this.}
-\item[\cite{fhs19}:] Based on Structure Preserving Signatures from equivalence
-  classes (SPS-EQ). The approach resembles that of \cite{ckl+15} in that it
-  uses a structure preserving primitive, and signs (commitments of) sets of
-  messages. However, they aim to avoid (as they claim) costly zero-knowledge
-  proofs. Basically, upon setup, a set commitment scheme is set up. Each user
-  generates a keypair. To obtain a credential on a set of attributes $A$, the
-  user proves knowledge of the user secret key, which is used as randomness
-  for a set commitment over $A$. The issuer (proves knowledge of the secret
-  key and) returns a SPS-EQ signature over $A$. To show the credential, the
-  user randomizes the commitment set and the signature, reveals the required
-  subset $D$ of $A$, and computes a witness that indeed $D \subset A$, as well
-  as a proof knowledge of the randomness used to randomize the credential (to
-  prevent replays). 
-\item[\cite{sms+19}:] The Coconut system follows a similar approach than the previous
-  works with respect to the representation and showing protocol for credentials.
-  Namely, credentials are randomizable signatures issued blindly. In this case,
-  the authors rely on Pointcheval Sanders signatures \cite{ps16} as main
-  building block, to which they incorporate techniques from other schemes to
-  support threshold issuance.
-\item[\cite{halp20}:] Builds on Coconut credentials and a blockchain -- in theory,
-  any blockchain with smart-contract capability, although it seems they are building
-  their own blockchain. This paper is in the frontier of academic and industry
-  work. On the cryptographic side, the credentials they build are essentially an
-  extension of Coconut credentials (although the extension is not described, nor
-  formalized). Users can combine multiple Coconut credentials into one Nym
-  Credential. In order to control Sybil attacks, Nym Credentials are obtained
-  in exchange of Nym Tokens (how users get hold of these, is not described).
-  Service Providers receive Nym Tokens in exchange of offering their services
-  through the network.
-\item[\cite{hs21}:] This work merges AC approaches based on SPS-EQ and aggregate
-  signatures, and also introduces the separation between a trusted but restricted
-  device, and a less trusted but powerful device typical in DAA systems. The
-  former is referred to as \emph{core}, and the latter as \emph{helper}, hence
-  the Core-Helper AC (CHAC) acronym. In addition to the previous basic building
-  blocks, the system uses a Signature with Flexible Public Keys (SFPK) scheme.
-  Roughly, these are signature schemes where the public keys can be randomized,
-  but in a manner that no adversary can decide whether two public keys are
-  related or not (i.e., if one is a randomization of the other). Users identities
-  are SFPK keypairs, where the public part gets signed by the issuer, using an
-  AAEQ scheme (Aggregatable Attribute-based Signature Scheme on Equivalence Classes).
-  Roughly, an AAEQ scheme is a combination of attribute-based signatures on
-  equivalence classes (which the authors combine with Tag-based Signatures on
-  Equivalence Classes), and aggregate signatures. In the proposed AAEQ scheme,
-  a tag is derived from an attribute an a nonce, which is then ``signed'' (note:
-  this tag resembles much the concept of nyms based on scopes). Since signatures
-  (and tags) are group elements sharing the same discrete log (the signer's key),
-  they can be aggregated easily via multiplication. Hence, for each attribute that
-  the issuer wants to grant to the user, it creates an independent signature where
-  the tag depends on the attribute to grant. Then, the user can just aggregate
-  all of them into one credential. In addition to this, the authors split the
-  operations (which are in the bilinear setting), in a way that requires the
-  core to perform only a few operations in $G_1$. The result seems to be quite
-  efficient. However, it only supports selective disclosure (no advanced
-  privacy-preserving policies), and even revocation is not considered from scratch,
-  although the authors sketch an approach to integrate it -- which probably
-  would require a more formal analysis and would incur in (possibly bad?)
-  added costs.
-  \note{The concept of aggregation here is different than the one in \cite{cl11}.
-    In the latter, users can aggregate credentials from different issuers. Here,
-    this is not possible, as aggregation won't work for different signing keys
-    (i.e., issuer keys). Hence, aggregation rather refers to receiving multiple,
-    independently signed, attributes by the same issuer, and then combining them
-    into a single credential by that same issuer.}
-\end{enumerate}
+Special mention is worth to the model variation in \cite{hs20}, which divides
+the user into two entities: core and helper, thus taking anonymous credentials
+closer to DAA. This is reflected into the model by adding a property named
+\emph{dependability}, which requires that no adversary should be capable to
+show an honestly generated credential withouth compromising the core entity.
 
-\paragraph{Main security models.}
+On the approach to formalize AC security notions, game-based definitions tend
+to be more frequent \needcite, also including definitions in the simulation
+paradigm. The UC framework has also been used \needcite, even in combination
+with game-based definitions \needcite.
 
-\begin{enumerate}
-\item[\cite{cl01}:] Security in \cite{cl01} is proven in an ad-hoc way,
-  using the ideal-world/real-world paradigm. The authors describe a
-  simulator for the operations supported by the system (Setup, FormNym,
-  GrantCred, VerifyCred and VerifyCredOnNym), and prove that the output of this
-  simulator is indistinguishable from that of the real protocol, under the
-  strong RSA and Diffie-Hellman assumptions.  
-\item[\cite{cl02}:] No security model is given for the anonymous credential
-  application of the signature scheme (reasonably, as it is not the main focus
-  of the paper). The signature scheme is proven secure (no specific mention
-  to a security model, although I suppose it would be quite straight forward)
-  based on the Strong RSA and Diffie-Hellman assumptions.
-\item[\cite{cl04}:] Same as in \cite{cl02} (no actual security model for the
-  AC system). The custom proofs are based on the DDH and LRSW assumptions.
-\item[\cite{bcc+09}:] The article follows a game-based definition approach,
-  with two security properties (besides correctness): anonymity and
-  unforgeability, which are the usual, but extended to the scenario with
-  delegation. Basically, the anonymity (in the ideal/real world paradigm)
-  property requires that the adversary should not distinguish real credentials
-  from simulated ones. Moreover, the adversary should not learn the delegation
-  chain of an honest credential (even if it was issued by himself). For
-  unforgeability, the requirement is that the adversary should not create
-  a delegation chain that includes a delegation by an honest user, if the
-  user did not actually perform that delegation.
-\item[\cite{cks10}:] Signer privacy and user privacy properties are required
-  for the underlying signature scheme (thus, inherited by the credential system,
-  although I have not found explicit model). Signer privacy captures that the
-  adversary (including corrupt users) doesn't learn any information about the
-  signer from signatures and updates of signatures. User privacy captures that
-  the adversary (including a corrupt issuer) does not learn any information
-  about the blindly signed messages. \doubt{Not sure I get the utility of
-    signer privacy. The original property seems to come from \cite{bckl08}.}
-\item[\cite{cl11}:] The security properties in this work are unforgeability
-  and anonymity, for which the authors give game-based definitions.
-\item[\cite{cklm14}:] Defines security of the DAC scheme using simulation-based
-  notions of anonymity and unforgeability.
-\item[\cite{cmz14}:] The security properties proven in this work are:
-  \begin{itemize}
-  \item \emph{Unforgeability}: The adversary cannot produce a valid proof for a
-    statement, if none of the attribute sets for which it has received a
-    credential meets that statement.
-  \item \emph{Anonymity}: The proofs produced in a presentation do not leak
-    more information than the statement being proved.
-  \item \emph{Blind issuance}: The issuance protocol is a secure two-party
-    protocol for generating credentials on the user's attributes.
-  \item \emph{Key-parameter consistency}: no issuer can use different parameters
-    to produce credentials of different users such that their anonymity can
-    be compromised afterwards. \doubt{This somehow remembers non-frameability in
-      group signatures.}
-  \end{itemize}
-\item[\cite{cdhk15}:] The model (and associated proofs) presented in this paper
-  is very comprehensive, and detailed. Specifically, for the main building block
-  (Unlinkable Redactable Signatures), the authors give both game-based
-  definitions as well as an ideal functionality. This ideal functionality models
-  security in a single-issuer setting. However, as it is done in the UC
-  framework, it can be composed with itself, so that a scenario with multiple
-  issuers, in which users can combine credentials obtained by different users
-  into a single showing process (``presentation'') is directly achievable by
-  composing multiple instances of the ideal functionality (one per ``proof
-  part'').
-\item[\cite{ckl+15}:] The main security and privacy properties required are
-  pseudonym collision-resistance (two different user secret keys cannot produce
-  the same nym for the same scope), unforgeability (the adversary cannot forge
-  issuance tokens or presentation tokens), and privacy (no two presentations by
-  the same user can be linked) or weak privacy (presentations by the same user
-  can be linked, but not traced to an issuance session). Privacy is modelled
-  in the simulation paradigm, the difference in the modelling between privacy
-  and weak privacy being a filter that removes some information \note{(I find
-    this kind of weird; probably I'm wrong. Would be nice to study further)}.
-  The unforgeability and privacy properties are essentially inherited from the
-  main building block, privacy-enhancing attribute-based signatures. Although
-  there, the authors begin by defining a blind issuance experiment (ensuring
-  that the issuer does not learn anything more than what it should during
-  isusance), and then define two variants for user privacy: presentation privacy
-  and untraceability, which basically match the strong and weak notions for
-  PABCs (in untraceability, two presentations by the same user can be linked,
-  but not trace to a specific credential issuance). [Strong] user privacy has
-  to satisfy both blind issuance and presentation privacy; weak user privacy
-  has to satisfy both blind issuance and untraceability. I find this model
-  somehow interesting, as it is one of the few (maybe along with \cite{cmz14})
-  that includes some notion related to tracing back to issuance of credentials,
-  as in group signatures). In both cases (PABC and PABS), [strong] privacy
-  implies weak privacy.
-  Essentially, the security properties required by the PABC scheme, are
-  ensured by the building blocks. Namely: the pseudonym system (requiring
-  key extractability, collision resistance and pseudonym unlinkability); the
-  revocation scheme (requiring soundness and revocation privacy); the
-  PABs (requiring unforgeability, and [weak] privacy); and the commitment
-  scheme (requiring blinding and hiding, and opening extractability).
-\item[\cite{dmm+18}:] The authors give a game-based security model, covering
-  properties of unforgeability, anonymity, and policy-hiding. The latter
-  means that, for delegated verification, the verifier is oblivious to the
-  policy being verified.
-\item[\cite{fhs19}:] Gives a game-based security model, with anonymity and
-  unforgeability being the main security properties (besides correctness).
-  Unforgeability resembles the traceability property of group signatures,
-  which are recognised as an influence in their modelling -- more specifically,
-  \cite{bmw03} (the model -- and the oracles therein -- definitely resembles
-  the BMW model for GSs). The authors claim to be the firsts to give a well defined and
-  formal model for ACs, besides \cite{ckl+15} (which gives game-based properties
-  in the simulation paradigm) and \cite{cdhk15} (which follows the UC framework).
-  However, \cite{fhs19} claims that adopting non-simulation based definitions
-  allows them to reach a more efficient construction. They also support malicious
-  issuer key generation, as issuers have to prove knowledge of their secret keys
-  (which allows extraction in the games).
-  An interesting aspect of their model is that all attributes in their
-  credentials are learned by the issuer -- i.e., there are no blindly signed
-  attributes. This implies that it is not possible to sign secret keys owned
-  by the users (as in the conventional CL credentials). Then, for showing a
-  credential, all the user has to do is reveal the attributes s/he is required
-  to show. This has the disadvantage that, depending on the use case, this may
-  be trivial to attack. For instance, assume a COVID-like pandemic situation,
-  in which citizens have to prove being vaccinated. An AC system for this use
-  could be naively defined as: { Type of vaccine, Date of vaccination }. But
-  this is very susceptible to dictionary attacks, and leaves much to the
-  engineering/implementation level. E.g., if it is easy for an eavesdroper
-  to get hold of a credential (not even the plaintext attributes), s/he can
-  just iterate through the small list of possible values, and then take
-  advantage of the ``stolen'' credential. This is certainly secure under the
-  model defined in \cite{fhs19}, but it is definitely easy for implementations
-  following this model to go wrong...
-  They also model only interactive show processes. Furthermore, to prevent
-  replay attacks, the user has to prove knowledge of some randomness included
-  in the credential. However (\textbf{cross-check this!}), since signatures
-  are randomizable without knowledge of any secret value, any adversary that
-  learns a credential (not necessarily any plaintext attribute associated to
-  it), would be capable of authenticating through a dictionary attack in case
-  of small attribute ranges.
-  Note: this may just be a modelling issue (or not even that, cross-check later
-  in case I misunderstood something). In their construction, they include
-  a secret key of the user in the credentials, of which the user has to prove
-  knowledge during the issue protocol. They do this by ``reusing'' the user
-  secret key as the randomness employed for the set commitment scheme, and
-  requiring the user to prove knowledge of the corresponding public key.
-  However, I am not sure of whether or not this somehow thwarts the previously
-  mentioned ``attack'', which affects the show protocol (\todo{i.e., the user does
-    not need to prove knowledge of the usk during show, no?} \note{Actually, it
-    should not, as it would probably prevent anonymity}) In any case, even if
-  the specific construction and instantiation thwarts this attack, I think their
-  model allows it.
-\item[\cite{sms+19}:] No security model is given nor adopted.
-\item[\cite{halp20}:] No formal definition is given. The following properties
-  are claimed: undetectability (this seems similar to traceability in group sigs),
-  unlinkability, selective attributes disclosure, unforgeability, persistent
-  accounts, sybil resistance, extensibility, availability, decentralization.
-\item[\cite{hs21}:] Security is given through game-based definitions of
-  unforgeability, anonymity, and dependability. The first two are the usual ones,
-  while the latter roughly requires that an adversarial helper cannot produce
-  successful showings without cooperation from the core. It would be interesting
-  to make a detailed comparison with security models of DAA (usually in the UC
-  framework, although some game-based (seemingly flawed) definitions exist).
-  The main argument that the authors give when comparing to DAA, is that the
-  latter does not support attributes, and it is essentially a group signature
-  scheme without revocation and optional linkability (this frontier is also
-  blurry, see \cite{dl21}).
-\end{enumerate}
+\subsubsection{Variations in functionality.}
+%
+Multi-attribute and multi-show credentials, with selective disclosure, are
+the most frequent \needcite.  Blind issuance, i.e., letting users include in
+their credentials attributes that are kept hidden from issuers, is also frequent
+(and certainly useful to, e.g., include secret keys) \needcite. Delegation has
+gained attention in the last decade \needcite, as well as supporting more
+expressive proofs. While the latter is indeed possible in the early works
+(one can use general zero-knowledge proofs on discrete logarithms given a
+CL-, BBS- or PS16- based credential) it is worth noting that the costs are
+probably too high, and it also needs to be considered in the model.
+%
+Perhaps surprisingly, revocation is not a common functionality, although it is
+certainly considered by several works \needcite.
+%
+Threshold issuance is also interesting for decentralized scenarios, but it
+was only considered in \cite{sms+19} and, consequently, in \cite{halp20}
+(which builds on \cite{sms+19}).
+%
+And, finally, an interesting variation that only one work seems to target,
+is that of efficient aggregation of credentials created by different issuers
+\cite{cl11}. As in the topic of expressiveness, this is easily doable with the
+conventional approaches: e.g., if the owner of credential A and credential B
+wants to use both credentials in the same showing, she just has to prove that
+they share the same secret key (although this is only possible in schemes that
+embed a user secret within the credential). Still, even if possible and even
+supported, this process is inefficient. \cite{cl11} leverages aggregatable
+signatures, which target precisely that setting.
 
-\paragraph{Variations in functionality.}
+\subsubsection{Efficiency.}
+%
 
-\begin{enumerate}
-\item[\cite{cl01}:] Extensions provided to the main functionality are:
-  \begin{itemize}
-  \item PKI-based and all-or-nothing non-transferability: Both options
-    involve sharing a verifiable encryption of the user secrets. In the
-    case of PKI-based non-transferability, the CA receives a verifiable
-    encryption, using as key the user's master secret, of some valuable
-    piece of information belonging to the user (e.g., the user's secret
-    key associated to his public key with that CA). In the all-or-nothing
-    case, the user shares with each organization (with which it has a
-    pseudonym), a verifiable encryption of his pseudonym secret data, encrypted
-    with his master secret. In both cases, if the user shares his master
-    secret with someone else, then he automatically gives access to
-    other relevant pieces of information (as the verifiable encryptions are
-    made public by the corresponding entity).    
-  \item One-show credentials: The validating tags over pseudonyms are extended
-    to include an extra value in their commitment. Then, users have to reveal
-    that value (or, rather, a value deterministically derived from that) in the
-    zero-knowledge proofs they create at show time. Since the value is always
-    the same, verifiers can check whether they have seen it before, or not.
-  \item Revocation: Both local (i.e., within an organization) and global (i.e.,
-    referring to an identity of the user in an external CA) is possible by
-    extending the pseudonyms of the user, and the credential showing protocols,
-    with values that allow subsequent decryption by a trusted party of their
-    pseudonym or external identity, given a transcript of the credential
-    showing.    
-  \item Attributes: The paper also succinctly describes how multiple attributes
-    per credential could be included. This would be done by dividing the inverval
-    within the exponent used to compute the pseudonym in sub-intervals, and then
-    proving that the exponent lies within a sub-interval.
-  \end{itemize}
-\item[\cite{cmz14}:] The paper mentions ``Credential translation'', which
-  basically means being able to prove that two attributes in different
-  credentials are actually the same. This is not formalized or detailed,
-  though.
-\item[\cite{cdhk15}:] The same as in the previous works (\cite{cl01,cl02,cl04}).
-\item[\cite{dmm+18}:] The scheme supports delegated verification. Basically,
-  to implement delegated verification, the delegatee receives an encryption of
-  the policy it has to verify, plus a signature of the encryption. If the
-  signature is valid, it re-randomizes the ciphertext for the policy, and
-  sends it to the user, who follows the same protocol as in the normal case.
-  The paper also mentions how to add more functionality, like delegation of
-  credentials and revocation, but they are not modelled. Also interestingly,
-  they claim somewhat informally (in Section 2.3) that no scheme satisfying
-  anonymity in the presence of an untrustworthy issuer can support delegation
-  of verification with policy hiding.
-\item[\cite{sms+19}:] It is essentially the same as previous works, although it
-  supports threshold issuance. Interestingly, \cite{sms+19} does not make use
-  of pseudonyms. I.e., credentials are just signed (blocks of) attributes. This
-  probably lets them achieve better efficiency. \doubt{This makes the scheme
-    to be practically like a group signature scheme (without revocation...)}
-\item[\cite{hs21}:] The main variation here is the application of the core-helper
-  division (typical of DAA) to the AC domain.
-\end{enumerate}
-
-\paragraph{Efficiency.}
-
-\cite{sms+19} seems to be the most efficient one (note: relies on the
-Fiat-Shamir heuristic). Credentials are only composed by two G1 elements,
-independently on the number of attributes. \todo{Cross-check this after
-  review.}
-
-\cite{cdhk15} and \cite{fhs19} achieve credential showings of size independent
-of the number of attributes.
-
-\paragraph{Main challenges.}
+\subsubsection{Main challenges.}
+%
 
 \subsection{Related Primitives}
-
-Most schemes \cite{cl01,cl02,cl04,cdhk15,sms+19} are based on randomizable
-signatures, with the possibility of signing committed values, that also support
-efficient proofs of knowledge.
-
-The most recurrent signature schemes are Camenisch-Lysyanskaya \cite{cl02,cl04},
-BBS/BBS+ \cite{asm06,cdl16b}, and Pointcheval Sanders \cite{ps16}.
-\cite{cdhk15} leverages their own signature scheme, called Unlinkable
-Randomizable Signatures, which lets users obtain a signature on a set of
-(committed) messages and then prove knowledge of (a subset of) these
-messages, introducing rerandomization to prevent linking. \cite{fhs19}
-follows a similar approach, using vector commitments. Both schemes
-\cite{cdhk15,fhs19} seem to be the most efficient AC instantiations to date.
-\cite{cdhk15} follows the UC framework; \cite{fhs19} a game-based definition.
-
-The ``family'' of AC systems known in the industry as BBS+ originates from
-\cite{asm06} (or, probably, from the BBS+ variant in \cite{cdl16b}, which
-introduces several improvements). \cite{asm06} presents a GS-like system that
-lets users obtain a credential from a Group Manager. This credential is a
-BBS+ signature. BBS+ signatures are a digital signature scheme, based on
-\cite{bbs04} and following the modification guidelines put forward in
-\cite{cl04}\footnote{Essentially, the authors of \cite{asm06} acknowledge
-  \cite{cl04} as those who proposed the BBS+ scheme -- but without security
-  proofs, which are provided in (the full version of) \cite{asm06}.}. On top
-of the signature scheme, they add efficient protocols for obtaining a signature
-over a set of committed messages, and proving -- in zero knowledge -- knowledge
-of a signature. Users can then be authorized by Application Providers (APs) to
-access their services: for this, APs maintain a list of the users they have
-granted/revoked access to, using a dynamic accumulator. APs also allow users to
-authenticate anonymously up to $k$ times. In order to access the services of APs,
-users have to derive a value using a VRF, and further prove that the value used
-to seed the VRF is a number within $[1,k]$ -- in addition to, of course, proving
-knowledge of a valid BBS+ signature (their credential). APs keep a record of the
-accesses. Thus, if a user accesses more than $k$ times a given AP, anyone with
-access to the record will be able to learn that a user has accessed more than
-$k$ times, as there will be more than one matching VRF-derived values.
-Furthermore, these two (or more) values let anyone extract a ``pseudonymous''
-identity of the user. The model (only informally presented, formal definitions
-appear in \cite{ts06} and proofs are deferred to a full version) seems to be
-used in $k$-TAA systems ($k$ Times Anonymous Authentication), and defines
-properties for:
+\label{ssec:acrelated}
 
 \begin{itemize}
-\item D-Detectability: Adversaries authenticating more than $k$ times are
-  detected.  
-\item D-Anonymity: Honest users authenticating less than $k$ times remain
-  anonymous.
-\item D-Exculpability: No honest user can be framed as having authenticated
-  more than $k$ times. The GM cannot be framed as dishonest if that is not
-  the case.
+\item Anonymous Authentication systems in the line of Nymble, BLACR, PEREA...
 \end{itemize}
 
-The system in \cite{aks12} also uses BBS+ signatures as a main building block
-to design a system with accountable anonymity, although it is not ``strictly''
-an anonymous credentials system: users receive a credential that lets them
-authenticate anonymously against service providers, but this credential does
-not include attributes, which seems to be the common case in ACs (however,
-with BBS+ it is trivial to add attributes, although this should be modelled).
-The main contribution of \cite{aks12} is the design and incorporation of
-protocols to block misbehaving users depending on their behaviour, without
-relying on trusted third parties. This is based on ``reputation lists'',
-maintained by each service provider. Uses that have previously registered
-with a Group Manager can authenticate against service providers by proving
-knowledge of a valid credential. Depending on how these users behave during
-the session with the service provider, the latter adds the interaction to
-either a \emph{good behaviour} list, or a \emph{misbehaviour list}. For
-subsequent authentications, users prove (in an ``almost unlinkable'' way
-w.r.t. previous authentications) that they have a certain reputation,
-computed as a weighted sum of their presence in the good/bad behaviour
-lists. Moreover, each service provider can maintain multiple thematic lists,
-and then require users to satisfy arbitrary boolean policies based on these
-lists (e.g., reputation $\ge X_1$ on $list_1$ and reputation $\le X_2$ on
-$list_2$ or reputation $= X_3$ on $list_3$) so that only users meeting
-the defined policy can access their system. These proves have though a linear
-dependency on the number of authentications that each user has done in
-the past. To reduce the impact of this, the authors create epochs. When a
-user authenticates successfully against a service provider, at a given epoch
-$i$, the service provider gives the user a token that authenticates the
-reputation that the user had at epoch $i$. Then, when this user tries to
-authenticate again, he only needs to give that token, and prove his reputation
-since epoch $i$ (this is why authentication is ``almost unlinkable'', as
-service providers may learn when the user authenticated for the last time).
-Note that no trusted party is involved in the blacklisting process, as
-correctness of all tokens exchanged between users and service providers to prove
-meeting certain policy, is ensured via the corresponing proof protocols.
-Concerning security, the system is proven secure in the simulation paradigm,
-claiming to meet (informally defined) properties of:
+\subsection{Real World Deployments}
+\label{ssec:acrealworld}
 
-\begin{itemize}
-\item Anonymity: All the SPs can infer from authenticating users is that they
-  meet the predefined policy, and that they authenticated at a certain epoch.
-\item Authenticity: Only users meeting the defined policies can authenticate.
-\item Mis-authentication resistance: Un-registered users cannot authenticate
-  successfully.
-\item Non-frameability: No coalition of users can cause that another user
-  meeting the required policy, cannot authenticate successfully.
-\end{itemize}
-
-Somehow, these properties resemble those in the group signatures model in
-\cite{kty04}. Probably, the addition of non-frameability is a consequence
-of adding a variant of revocation.
-
-\paragraph{Primitives for credentials with generic policies.} \cite{cgm16}
-describes techniques to be able to create efficient proofs that combine both
-algebraic and non-algebraic relations. For instance, proving knowledge of an
-ECDSA or RSA-FDH signature (both of which include computation of a hash
-function); but also being able to prove any arbitrary (non-algebraic) funcion
-$f$. This may be very useful to achieve compatibility with traditional
-credentials/signature schemes, that mostly do not follow the algorithms
-used in anonymous credentials systems. In fact, that is one of the main
-motivations in the paper. The approach in \cite{cgm16} builds on committing
-Oblivious Transfer and Garbled Circuits (not necessarily with privacy).
-A closely related work seems to be \cite{dfkp16},
-which achieves the same goal but using SNARKS, which results in different
-tradeoffs -- hence, it may be interesting, as the SNARK domain has improved
-significantly since 2016. \cite{kkl+16} also allows building anonymous
-credentials for arbitrary policies, but using a different approach too.
-
-\subsubsection{Pseudonym Systems}
-\label{sssec:pseudonyms}
-
-\doubt{Not sure if this fits here.}
-
-\subsection{Applications}
-\label{ssec:acapplication}
-
-\subsubsection{Theory}
-\label{sssec:actheoryapp}
-
-Main approaches to build ACs (from ToPS paper I reviewed):
-
-\begin{itemize}
-\item Re-randomizable signatures on commitments (also as in DAA):
-  \cite{cl02,cl04,lmpy16,ps16}.
-\item Equivalence class signatures: \cite{fhs19,hs14}.
-\item Redactable signatures \cite{cdhk15,sand20} and malleable signatures
-  \cite{ckl14}.
-\item Predicate encryption: \cite{dmm+18}.
-\end{itemize}
-
-Also:
-
-\begin{itemize}
-  \item ACs based on aggregate signatures: \cite{cl11}.
-\end{itemize}
-
-PS: Tokenization.
-
-\subsubsection{Real World Deployments}
-\label{sssec:acrwdeploy}
-
-PS: Tokenization.
-Signal's AC \cite{cpz20}.
-
-\begin{itemize}
-\item U-Prove (see ref. 65 in \cite{hs21}):  This is largely based on Brands
-  thesis. There was a deployment by Microsoft, mostly concurrent to Idemix.
-  They are one-show credentials, but seemingly there is recent real-world
-  deployments based on them (references in p.1 of \cite{hs21}):
-
-  \begin{itemize}
-  \item Privacy-Pass by Cloudflare.
-  \item Trust Tokens API by Google.
-  \item PrivateStats proposal by Facebook.
-  \end{itemize}
-
-\item Idemix \cite{ch02}: This is largely based on CL signatures. It has been
-  deployed (or is being deployed) in Hyperledger Fabric, and I think there is
-  some of it in Indy too.
-\end{itemize}
-
-\cite{hs21} contains also many references to ``practical'' applications of
-ACs. However, these are mostly references to papers in cryptographic venues,
-so I suspect that they are more academic than real-world systems.
-
-\subsection{TODO}
+\subsection{TODOs}
 
@@
 
-How to compare efficiency of AC systems?
-
 %%% Local Variables:

### 2021-11-26 prism-backend/research/soa_review/ac.tex
Polished version. Still early draft, but at least readable (excluding DAA section, which is not a priority for now).

@@
 Camenisch and Lysyanskaya \cite{cl01,cl02,cl04} and, independently, by Brands
-\needcite\footnote{Camenisch and Lysyanskaya line of work is well known for
+\cite{bran00}\footnote{Camenisch and Lysyanskaya line of work is well known for
   IBM's Idemix system, and Brands's work for Microsoft's U-Prove. More detail
@@
 means that the verifier cannot link different authentication processes by that
-same user. Usually, credentials are composed by multiple attributes, such that
-the verifier only learns the attributes that the user is willing to share (or a
-function of them).
+same user. Also, usually, credentials are composed by multiple attributes, such
+that the verifier only learns the attributes that the user is willing to share
+(or a function of them).
 
@@
 ensure security and privacy properties -- and are also leveraged in many group
-signature and DAA works.
+signature and DAA works. Not all anonymous credentials systems use pseudonyms,
+though.
 
@@
 is then extended to support enhanced functionality. For instance, in order to
-support multiple issuers (and, in some sense, multiple attributes)
-\cite{cl01,cl02,cl04} \todo{check if the references are correct} require an
-extra protocol for proving, in zero-knowledge, equality of two committed and signed values.
+let a user with two different credentials prove being the owner of both of
+them, \cite{cl01,cl02,cl04} require an extra protocol for proving, in
+zero-knowledge, equality of two committed and signed values.
 This allows user $A$, with credential $\sigma_A^I$ obtained from issuer $I$ and
@@
 valid credential from $I$, by issuing a zero-knowledge proof of equality for
-both credentials. Now, if each credential is associated with a different set of
-attributes, this also lets to ``naively'' build multi-attribute AC systems.
+both credentials. Furthermore, if each credential is associated with a different
+(set of) attribute(s), this also leads to ``naive'' constructions of
+multi-attribute AC systems.
 
@@
 which can be seen as attributes signed by the issuer. BBS+ signatures
-\cite{am06,cdl16b}, and PS16 signatures \cite{ps16} also support similar
+\cite{asm06,cdl16b}, and PS16 signatures \cite{ps16} also support similar
 functionality, and have been leveraged to build multi-attribute AC systems
@@
 interpolation to allow revealing only a subset of the committed messages;
-\todo{what was the specific technique of \cite{fhs19}?}. \cite{fhs19}, is more
-efficient, as avoids complex zero-knowledge proofs; however it does not support
-blind issuance of credentials, as opposed to \cite{cdhk15} \todo{confirm this
-  last part, and refine}.
+while \cite{fhs19} employs set commitment schemes, mapping the attributes to
+be committed to roots of a polynomial, so that opening a specific subset of the
+commmitted elements just requires revealing a subset of the roots of the
+polynomial.
 %
@@
 
-Somewhat similar is the approach to (delegatable) credentials that builds on
-signatures with controlled malleability \cite{bcc+09,cklm14}, where \cite{cklm14}
-is a generalization of \cite{bcc+09}. Roughly, credentials are signatures, built
-from non-interactive zero-knowledge proofs of knowledge, on commitments to the
-user key, that support \emph{controlled malleability}. This malleability means
+Within this line of credentials from randomizable signatures, we can also find
+systems that can achieve high expressiveness, like the (delegatable) credentials
+building on signatures with controlled malleability \cite{bcc+09,cklm14},
+where \cite{cklm14} is a generalization of \cite{bcc+09}. Here, at a high level,
+credentials are signatures, built from non-interactive zero-knowledge proofs of
+knowledge, on commitments to the user key, that support \emph{controlled
+  malleability}. This malleability means
 that both the proof and the statements can be randomized and transformed, but
@@
 though, as the authors prove that it is similar (or even more generic) than those
-used to achieve expresiveness in related digital singature schemes (such as
-policy-based signatures \needcite and delegatable functional signatures \needcite).
+used to achieve expressiveness in related digital singature schemes (such as
+policy-based signatures \cite{bf14} and delegatable functional signatures \cite{bms16}).
 Thus, it is reasonable to expect that very expressive AC systems could be built
@@
 
-All AC systems mentioned up to this point follow, up to small variations, the
-same approach: randomizable signatures on sets of (committed) messages, with
+All AC systems mentioned up to this point follow, up to ``small'' variations,
+the same approach: randomizable signatures on sets of (committed) messages, with
 (somehow) efficient proofs. A completely different approach is described in
@@
 ciphertext. Assume an attribute space that can be represented by binary strings
-$\Sigma$. On one hand, policies defined by verifiers in \cite{dmm+18} are encoded
+in a set $\Sigma$. On one hand, policies defined by verifiers in \cite{dmm+18}
+are encoded
 as binary circuits through strings in $\Sigma$ too\footnote{\todo{This seems
@@
 can evaluate circuits. Then, intuitively, in order for a verifier to check
-whether a user owns a attribute-based credential meeting certain policy $g$, it
-creates a ciphertext with encoding a circuit for $g$. If the user can decrypt
-this ciphertext, the verifier accepts. This only supports public attributes
+whether a user owns an attribute-based credential meeting certain policy $g$, it
+creates a ciphertext, associating as attribute an encoding a circuit for $g$
+(that belongs to $\Sigma$). If the user can decrypt this ciphertext, the
+verifier accepts, as this means that the decryption key in the user's credential
+has a hardcoded set of attributes that makes $g$ evaluate to true. This only
+supports public attributes
 (i.e., known to the issuer), though. A negative part of this approach is that
@@
 of such credential is limited to the subset of attributes voluntarily revealed
-by the user. Since multi-show credentials are also the most common type,
-anonymity also captures that two different showings must be unlinkable.
+by the user. In multi-show credentials, anonymity also captures that two
+different showings must be unlinkable.
 As mentioned, further variations in the functionality affect anonymity --
@@
 of a set of attributes not contained within the set of attributes that have
-been leaked.a showing that include attributes not contained in credentials leaked to the
-adversary.
+been obtained by the adversary or leaked to it.
 
-Special mention is worth to the model variation in \cite{hs20}, which divides
+Special mention is worth to the model variation in \cite{hs21}, which divides
 the user into two entities: core and helper, thus taking anonymous credentials
@@
 
-On the approach to formalize AC security notions, game-based definitions tend
-to be more frequent \needcite, also including definitions in the simulation
-paradigm. The UC framework has also been used \needcite, even in combination
-with game-based definitions \needcite.
+On the approach to formalize AC security notions, game-based definitions tend to
+be more frequent \cite{bcc+09,cks10,cl11,cklm14,cmz14,ckl+15,dmm+18,fhs19,hs21},
+also including definitions in the simulation paradigm. The UC framework
+has also been used \cite{cdhk15}.
 
@@
 %
-Multi-attribute and multi-show credentials, with selective disclosure, are
-the most frequent \needcite.  Blind issuance, i.e., letting users include in
-their credentials attributes that are kept hidden from issuers, is also frequent
-(and certainly useful to, e.g., include secret keys) \needcite. Delegation has
-gained attention in the last decade \needcite, as well as supporting more
-expressive proofs. While the latter is indeed possible in the early works
-(one can use general zero-knowledge proofs on discrete logarithms given a
-CL-, BBS- or PS16- based credential) it is worth noting that the costs are
-probably too high, and it also needs to be considered in the model.
+\paragraph{Attributes, selective disclosure, and expressiveness.} %
+Multi-attribute and multi-show credentials are the most frequent
+\cite{cks10,cl11,cdhk15,ckl+15,fhs19,sms+19,halp20,hs21}, although one-show
+credentials have also been studied \cite{bran00}.
+Similarly, selective disclosure has also been more studied
+\cite{cks10,cl11,cdhk15,sms+19,halp20,hs21}, when compared to 
+more expressive AC systems \cite{bcc+09,cklm14,dmm+18}, while \cite{fhs19}
+supports selective disclosure and restricted policies (specifically,
+conjunctions), for the sake of efficiency. Probably, the higher attention to
+selective disclosure so far is due to the fact that the building blocks enabling
+efficient constructions with high expressiveness (such as SNARKs and functional
+encryption) are recent in the cryptographic literature.
+
+\paragraph{Security and privacy against issuers.} %
+Blind issuance, i.e., letting users include in their credentials attributes that
+are kept hidden from issuers, is also frequent (and certainly useful to, e.g.,
+include secret keys; or support private attributes in general)
+\cite{cklm14,ckl+15}, although it is also frequent to assume (even implicitly)
+that the issuer \emph{needs} to learn the attributes it signs, and thus private
+attributes are not considered, e.g. as in \cite{dmm+18,fhs19,sms+19}.
 %
+Threshold issuance is also interesting for decentralized scenarios, as it
+protects against misbehaving issuers, but it was only considered recently in
+\cite{sms+19} and, consequently, in \cite{halp20} (which actually builds on
+\cite{sms+19}).
+
+\paragraph{Delegation.} %
+Delegation has gained attention in the last decade \cite{bcc+09,cklm14},
+including delegated verification \cite{dmm+18}, as well as supporting more
+expressive proofs \cite{cklm14,dmm+18}. While the latter is indeed possible in
+the early works (one can use general zero-knowledge proofs on discrete
+logarithms given a CL-, BBS- or PS16- based credential) it is worth noting that
+the costs are probably too high. An interesting learning, that can be extracted
+from \cite{cklm14}, is that we can see delegation as a sort of policy that can
+be checked with expressive policies.
+
+\paragraph{Revocation.} %
 Perhaps surprisingly, revocation is not a common functionality, although it is
-certainly considered by several works \needcite.
-%
-Threshold issuance is also interesting for decentralized scenarios, but it
-was only considered in \cite{sms+19} and, consequently, in \cite{halp20}
-(which builds on \cite{sms+19}).
-%
+certainly considered by several works, e.g. \cite{cl01,cks10,ckl+15}, and for
+some it is just sketched \cite{hs21}.
+
+\paragraph{Credential aggregation.} %
 And, finally, an interesting variation that only one work seems to target,
 is that of efficient aggregation of credentials created by different issuers
-\cite{cl11}. As in the topic of expressiveness, this is easily doable with the
-conventional approaches: e.g., if the owner of credential A and credential B
-wants to use both credentials in the same showing, she just has to prove that
-they share the same secret key (although this is only possible in schemes that
-embed a user secret within the credential). Still, even if possible and even
-supported, this process is inefficient. \cite{cl11} leverages aggregatable
+\cite{cl11}. As in the topic of expressiveness, the conventional approach
+can easily be extended to support this: e.g., if the owner of credential A and
+credential B wants to use both credentials in the same showing, she just has to
+prove that they share the same secret key (although this is only possible in
+schemes that embed a user secret within the credential). Still, even if
+possible, this process is inefficient. \cite{cl11} leverages aggregatable
 signatures, which target precisely that setting.
@@
 
-\subsubsection{Main challenges.}
+\subsubsection{Main challenges and interesting lines of work.}
 %
+\note{I find interesting that, given that ACs and group signatures are
+  essentially the same thing, there is no work (or I have not come across it)
+  trying to connect both. Specifically, the following questions:}
 
-\subsection{Related Primitives}
+\begin{itemize}
+\item Anonymity properties in ACs and GSs are roughly similar. However, concerning
+  unforgeability-related properties:
+  \begin{itemize}
+  \item The notion of traceability in GSs seems incompatible in AC systems that
+    do not include a user secret key in the credentials. Even for AC systems that
+    do include it, unforgeability in AC is different than traceability, as there
+    is no guarantee that a credential can be traced to a ``join'' process. Or
+    there is?
+  \item The notion of non-frameability of GSs does not seem to have an equivalent
+    in ACs. I find this kind of surprising from a practical point of view, as an
+    adversary in AC systems can very well aim at impersonating an honest user,
+    which may then carry consequences (e.g., legal actions) for the honest user.
+  \item Maybe I'm wrong in the two previous points, and we can draw a connection
+    between (some basic notion of) unforgeability in ACs, and the usual notions
+    of traceability and non-frameability in GSs. If I recall correctly, the
+    \cite{bmw03} paper merged non-frameability and traceability into
+    unforgeability, and this was later divided again in \cite{bsz05}. Check the
+    reasoning again...
+  \end{itemize}  
+\item I find very surprising that essentially all the body of work in ACs is
+  based on what seems to be the sign-randomize-proof approach of GSs, yet there
+  is nothing (or I have not seen it) similar to the encrypt-then-prove approach.
+  Can we do it? This may be due to the fact that revocation has not been
+  considered as a main requirement in ACs (which, IMHO, is a drawback if we want
+  systems applicable in the real world).
+  \begin{itemize}
+  \item Can we come up with a black-box construction of ACs from GSs, or vice
+    versa? It should not be hard, and this may open a completely new breed of
+    ACs (i.e., those based on the encrypt-then-prove approach).
+  \end{itemize}
+\end{itemize}
+
+\subsection{Related Primitives and Systems}
 \label{ssec:acrelated}
@@
 
-\subsection{TODOs}
-
 \begin{itemize}
-\item \cite{bckl08}.
-\item \cite{sand20}.
-\item \cite{kkl+16}: achieves similar results to \cite{cgm16} with a different approach?
+\item Idemix.
+\item Hyperledger Indy.
+\item U-Prove.
 \end{itemize}
-
-[ToPS paper I reviewed] refers to a strategy to do threshold issuing in \cite{bbh06}.
-
-Concepts in ACs: multishow, one-show (Brands et al); interactive vs non-interactive
-showings (differentiation made in \cite[p.6]{fhs19} but, why would one want interactive,
-in the real world?)
-
-Which schemes support comibning credentials from multiple issuers? I think this
-is directly obtained in the schemes following the CL approach; but others?
-
-A recurrent claim in schemes avoiding using zero-knowledge proofs of knowledge
-of some attributes being included in a credential is that these proofs are costly
-(like, linear in the number of attributes). Yet, they resort to other primitives
-that may also be costly (e.g., predicate encryption \cite{dmm+18}) or somehow move
-the cost to some other place (e.g., \cite{fhs19} uses a vector commitment scheme
-that requires a public key with size that grows with the number of attributes
-that \emph{can} be committed). It would be nice to have a detailed and complete
-(e.g., not skipping the data that makes one scheme look bad, like the size of
-the public keys) comparison. And, ideally, with concrete instantiations (not only
-theoretical analysis)?
-
-\cite{fhs19} has a nice comparison table.
 

### 2021-11-26 prism-backend/research/soa_review/app-ac.tex
Polished version. Still early draft, but at least readable (excluding DAA section, which is not a priority for now).

\section{Log on Review of Anonymous Credentials Systems}
\label{app:ac}

\subsection{TODOs}

\begin{itemize}
\item \cite{bckl08}.
\item \cite{sand20}.
\item \cite{kkl+16}: achieves similar results to \cite{cgm16} with a different
  approach?
\end{itemize}

A recurrent claim in schemes avoiding using zero-knowledge proofs of knowledge
of some attributes being included in a credential is that these proofs are costly
(like, linear in the number of attributes). Yet, they resort to other primitives
that may also be costly (e.g., predicate encryption \cite{dmm+18}) or somehow move
the cost to some other place (e.g., \cite{fhs19} uses a vector commitment scheme
that requires a public key with size that grows with the number of attributes
that \emph{can} be committed). It would be nice to have a detailed and complete
(e.g., not skipping the data that makes one scheme look bad, like the size of
the public keys) comparison. And, ideally, with concrete instantiations (not only
theoretical analysis)?

\subsection{Approaches, Models, and Variations}

\paragraph{Main approaches.} %

\begin{enumerate}
\item[\cite{cl01}:]
  \begin{itemize}
  \item Functionality: FormNym, GrantCred, VerifyCred, VerifyCredOnNym.
  \item Approach: Users create a pseudonym with each organization. For this,
    they have to register first with the organization (associating a key to
    a user name). Whenever the user wants to get a credential from a organization
    in which he registered, he has to authenticate, and then the organization
    decides whether or not to grant the credential. Users can show their
    credentials to organizations in two ways: (1) just proving that they own a
    credential issued by some organization; or (2), proving that they own a
    credential issued by some organization \emph{and} this credential is over
    the same pseudonym that the user holds with the verifying organization.
    Essentially, pseudonyms are the concatenation of two random numbers (one
    provided by the user, and the other by the organization). They get
    associated an authenticating tag, which is a statistically hiding commitment
    to the user secret (computed using randomness provided by both user and
    organization). Organizations keep a database of the generated pseudonyms.
    To get a credential from an organization where the user registered
    previously, the user proves knowledge of the secret involved in the
    pseudonym. The organization then creates a ``random signature'' (by using a
    the inverse of random exponent, with the help of the factorization of an RSA
    modulus chosen by the organization at setup time) over the pseudonym, and
    gives that to the user. Users can show the credentials (in any of the
    previously stated two ways) by creating non-interactive zero-knowledge
    proofs of knowledge of the appropriate secret. Note that, in case (2),
    this means that the proof is over two pseudonyms, which must share the
    same secret.    
  \end{itemize}
\item[\cite{cl02}:]
  \begin{itemize}
  \item Approach: Te paper aims at improving efficiency of AC systems, as
    well as still ensuring that the user can retrieve their credentials in
    a privacy-preserving manner. For this purpose, the core of the paper
    describes a signature scheme that allows signing blocks of messages,
    and later prove, in zero-knowledge, knowledge of such a signature. To
    enable private retrieval of credentials, the authors describe a protocol
    for their signature scheme, whereby the user specifices a commitment to
    a message (or a block of messages, although this is not actually
    formalized), and get a signature of the message in return. While the
    authors do not strictly define an AC system, the application of their
    signature system and related protocols to the AC domain seems direct.
    Indeed, the same functionality as in \cite{cl01} seems straight
    forward given the cryptosystems in \cite{cl02}.
  \end{itemize}
\item[\cite{cl04}:] Follows a similar approach to \cite{cl02}, although
  changing the security assumptions to be based only on problems related
  to the discrete logarithm, and on bilinear maps. Basically, defines a
  signature scheme suitable for signing multiple messages, a protocol to
  obtain a signature on a committed value, and a protocol to prove knowledge
  of a signature. Concerning commitments, they rely on Pedersen commitment
  scheme, for which protocols are known to prove knowledge and equality of
  committed values. This lets them follow the same approach to \cite{cl02},
  which is in turn the one in \cite{cl01}.
\item[\cite{bcc+09}:] This is mostly a theoretical work, which is relevant
  since it is (one of) the first to propose a delegatable anonymous
  credentials systems. The building blocks are randomizable proofs of
  knowledge that randomize both the proof and the statement (which the authors
  build on top of Groth-Sahai proofs), and message authenticators (a variant
  of signatures that require a special notion of unforgeability). Each user
  can create pseudonyms, which are commitments to his secret key, and use
  these commitments to prove ownership of and delegate credentials. These
  pseudonyms are essentially as in the CL line of work (user with pseudonym
  $N^A_U$ w.r.t. organization $A$ and $^B_U$ w.r.t. orgainzation $B$, can
  prove to $B$ (resp. $A$) that $N^A_U$ and $N^B_U$ are related to the
  same secret key). Delegations here follow a sequential order: i.e., if
  a credential has level $L$, then its owner can further delegate this
  credential, and the result would be a credential with level $L+1$. To
  delegate, essentially, the delegator (with pseudonym $N_I$) and delegatee
  (with pseudonym $N_D$) perform an interactive protocol
  through which the delegatee receives a randomizable NIZKP that lets him
  prove knowledge of an authenticator over $N_D$, issued by $N_I$. Since
  both the proof and the statement can be randomized, verifiers do not
  learn the chain of delegation.  Although this is informally mentioned,
  ``attributes'' can be added to the delegation process too (besides to the
  credentials themselves). This is suggested by adding the attributes -- which
  would be visible to the verifier -- to the application of a hash function
  used to derive the authenticator). 
\item[\cite{cks10}:] The system proposed here follows the conventional
  approach to anonymous credentials based on randomizable signatures (with
  the possibility to sign committed values) over vectors of messages.
  It however enables issuers to produce updates on already signed messages.
  This updates can be leveraged to incorporate revocation. Essentially,
  time is divided in epochs, and credentials include an attribute which
  represents the expiration date/epoch of the credential. Users have to
  prove that their credential is valid for the current epoch. Similarly,
  to add new attributes, the issuer leverages the internal structure of
  the signatures over vectors of messages, to basically add new messages
  (attributes). In both cases, it is responsibility of the user to update
  her credential given the latest update by the issuer. An example
  instantiation is given using BBS signatures.
\item[\cite{cmz14}:] This work differs from the rest in that they use
  secret key cryptography rather than public key. Namely, they assume a
  setting in which the issuer will also be the verifier (e.g., a
  transportation organization that issues tickets for its travelers). In
  this setting, it is reasonable to assume that both issuer and verifier
  will have access to the same secret. Therefore, they replace signatures
  with (algebraic) MACs. They do not create pseudonyms for end users (like
  \cite{sms+19}). Other than that, the supported functionality is similar
  to the rest: Setup and KeyGen to initialize the cryptographic parameters,
  and produce the issuer's keys, respectively; an interactive protocol for
  end users to blindly receive credentials (MACs) on their attributes; and
  an interactive protocol for showing and verifying a credential. In case
  that issuance does not need to be blinded, it becomes a non-interactive
  protocol (i.e., the issuer just produces the credential and sends it to
  the user). Otherwise, the user has to encrypt the attributes and prove
  they are correct. Presentation only requires one message from the user
  to the verifier.
\item[\cite{cl11}:] The approach differs from the conventional ones. In this
  case, the focus is on settings where users may want to combine multiple
  credentials from different issuers. Thus, interest is on reducing the size
  of the resulting credentials, and the efficiency of associated processes.
  The approach is based on aggregate signatures. As usual, each credential
  may contain several attributes. Each attribute is independently signed
  by the issuer. Then, users can combine an arbitrary number of signed
  attributes (by the same or different issuers) into a single aggregate
  signature. Verification only needs the aggregated signature and the set
  of public keys of all the involved issuers. To prevent different users
  from aggregating their credentials, the authors resort to \emph{indexed}
  aggregate signatures: an index is added to each signature, such that only
  signatures that have the same index can be aggregated. In their instantiation,
  the signature is a BGLS signature \cite{bgls03}, and the index is a BB
  signature \cite{bb04}. The actual instantiation seems impractical (too many
  linear costs, see the table in the paper).
\item[\cite{cklm14}:] This work is, in essence, a generalization of \cite{bcc+09}.
  The main novel building block are controlled-malleability NIZKs. Basically,
  these are NIZKs that can be re-randomized, but only for a pre-defined set of
  (NP) transformations. From this cm-NIZKs, malleable signatures are built.
  From malleable signatures and commitments, delegatable credentials are built
  as follows. Credentials are basically a tuple $(nym, l, flag)$, where $nym$
  is a commitment to the user's private key, $l$ is the length of the credential
  in the delegation chain, and $flag$ is either $cred$ or $proof$. Credentials
  are accompanied with a malleable signature (which, for level 1 credentials,
  it is a signature by the issuer). To create ``proofs'' or to delegate, the
  credential owner has to apply one of the two allowed transformations. For
  ``proofs'', basically the transformation that has to be applied to the original
  proof (malleable signature) converts it to a proof showing that the prover
  knows the secret in the ``source'' pseudonym and ``target'' pseudonym, and
  both are the same. In the case of delegations, flag is set to ``cred'', and
  the transformation converts the cm-NIZK proof into one that lets the prover
  prove knowledge of the secret key in the ``source'' pseudonym, and allows
  only to produce a new credential with structure $(nym', l+1, cred)$ -- i.e.,
  from a credential of level $l$, only a credential of level $l+1$ can be
  derived. On the delegation topic, the type of delegation this work ``supports'',
  at least by default, is the simple one of hierarchical delegation.
\item[\cite{cdhk15}:] The approach to build anonymous credentials is roughly
  the same as in the previous works \cite{cl01,cl02,cl04}, although with
  relevant differences that make it more efficient. Basically, users create
  pseudonyms derived from a common secret. Then, any user can request a
  credential. For this, the user needs to prove knowledge of the pseudonym's
  secret. In return, the issuer produces an ``unlinkable redactable signature''
  on a set of attributes, for that pseudonym. A redactable signature is
  essentially a signature over a set (block) of messages, that enables
  subsequent verification that a subset of those messages was signed. This
  is essentially the same as in \cite{cl02,cl04}. However, to achieve
  unlinkability, \cite{cdhk15} incorporates efficient zero-knowledge proofs
  to prove correctness of the subset of the messages that a user wants to
  ``show'' in a credential showing process. This ensures unlinkability (hence,
  privacy). The internal scheme used for this is a vector commitment scheme
  that uses Lagrange interpolation to allow checking that a subset of the
  committed messages are indeed contained within the commitment. Moreover,
  both the vector commitment scheme, and the vector signing scheme, are
  structure preserving. This means that, since all the produced messages,
  commitments, and signatures, are elements of the group (rather than of the
  field), proving knowledge is much more efficient (e.g., it prevents costly
  extraction required for security proofs).
\item[\cite{ckl+15}:] Follows the conventional approach: a secure commitment
  scheme with proofs of knowledge, and a signature scheme that allows to
  sign vectors of messages, including commitments. Here, as in the seminal
  works by Camenisch and Lysyanskaya \cite{cl01,cl02,cl04}, pseudonyms are
  used as explicit building blocks. \todo{Not sure yet of how they are
    made explicit in the generic construction. Clarify.}
  A ``syntactic'' variation: they introduce
  the concept of tokens both for credential issuance and presentation. To
  request issuance of a credential, users have to produce an issuance token
  from the set of attributes they want to reveal to the issuer, and the set
  of attributes they want to hide (potentially coming from another credential
  already owned by the user). An equivalent description applies for presentation
  of a credential to a verifier. In both cases, the issuer/verifier has to
  check the received token prior to issuing a credential or granting access.
  They also add revocation functionality. For this, a revocation authority
  (not necessarily the issuer) keeps a revocation information list, which is
  basically a list containing no longer valid attributes. In order to prove
  that their credentials are valid w.r.t. some attribute, users have to generate
  a (non) revocation token, which proves that the attribute has not been
  included in the revocation information list.
\item[\cite{dmm+18}:] Follows a completely different approach to (most) other
  works. Instead of using randomizable signatures (over committed values) or
  some equivalent building block, it relies on predicate encryption.
  Essentially, a user with attributes $A$ is given a decryption key for a
  predicate $f_A(g)$ which, given a predicate $g$, returns $g(A)$. When
  a verifier wants to check if a user has a set of attributes that meet
  certain policy $h$, challenges the user to decrypt a ciphertext over
  a random message that has been associated to predicate $h$. Then, only
  if the attribute set $A$ of the user meets policy $h$, the user will be
  able to decrypt the random message (since $f_A(h) = h(A) = 1$). This
  protocol is actually augmented with some commitments, to prevent
  misbehaviour from user and from verifier, but the approach is the same.
  \doubt{There is something weird here, or that I do not understand --
    predicate encryption requires a
    set of attributes for encryption, rather than another predicate. I have
    reached out to the authors to see if they can help me clarify this.}
\item[\cite{fhs19}:] Based on Structure Preserving Signatures from equivalence
  classes (SPS-EQ). The approach resembles that of \cite{ckl+15} in that it
  uses a structure preserving primitive, and signs (commitments of) sets of
  messages. However, they aim to avoid (as they claim) costly zero-knowledge
  proofs. Basically, upon setup, a set commitment scheme is set up. Each user
  generates a keypair. To obtain a credential on a set of attributes $A$, the
  user proves knowledge of the user secret key, which is used as randomness
  for a set commitment over $A$. The issuer (proves knowledge of the secret
  key and) returns a SPS-EQ signature over $A$. To show the credential, the
  user randomizes the commitment set and the signature, reveals the required
  subset $D$ of $A$, and computes a witness that indeed $D \subset A$, as well
  as a proof knowledge of the randomness used to randomize the credential (to
  prevent replays). 
\item[\cite{sms+19}:] The Coconut system follows a similar approach than the previous
  works with respect to the representation and showing protocol for credentials.
  Namely, credentials are randomizable signatures issued blindly. In this case,
  the authors rely on Pointcheval Sanders signatures \cite{ps16} as main
  building block, to which they incorporate techniques from other schemes to
  support threshold issuance.
\item[\cite{halp20}:] Builds on Coconut credentials and a blockchain -- in theory,
  any blockchain with smart-contract capability, although it seems they are building
  their own blockchain. This paper is in the frontier of academic and industry
  work. On the cryptographic side, the credentials they build are essentially an
  extension of Coconut credentials (although the extension is not described, nor
  formalized). Users can combine multiple Coconut credentials into one Nym
  Credential. In order to control Sybil attacks, Nym Credentials are obtained
  in exchange of Nym Tokens (how users get hold of these, is not described).
  Service Providers receive Nym Tokens in exchange of offering their services
  through the network.
\item[\cite{hs21}:] This work merges AC approaches based on SPS-EQ and aggregate
  signatures, and also introduces the separation between a trusted but restricted
  device, and a less trusted but powerful device typical in DAA systems. The
  former is referred to as \emph{core}, and the latter as \emph{helper}, hence
  the Core-Helper AC (CHAC) acronym. In addition to the previous basic building
  blocks, the system uses a Signature with Flexible Public Keys (SFPK) scheme.
  Roughly, these are signature schemes where the public keys can be randomized,
  but in a manner that no adversary can decide whether two public keys are
  related or not (i.e., if one is a randomization of the other). Users identities
  are SFPK keypairs, where the public part gets signed by the issuer, using an
  AAEQ scheme (Aggregatable Attribute-based Signature Scheme on Equivalence Classes).
  Roughly, an AAEQ scheme is a combination of attribute-based signatures on
  equivalence classes (which the authors combine with Tag-based Signatures on
  Equivalence Classes), and aggregate signatures. In the proposed AAEQ scheme,
  a tag is derived from an attribute an a nonce, which is then ``signed'' (note:
  this tag resembles much the concept of nyms based on scopes). Since signatures
  (and tags) are group elements sharing the same discrete log (the signer's key),
  they can be aggregated easily via multiplication. Hence, for each attribute that
  the issuer wants to grant to the user, it creates an independent signature where
  the tag depends on the attribute to grant. Then, the user can just aggregate
  all of them into one credential. In addition to this, the authors split the
  operations (which are in the bilinear setting), in a way that requires the
  core to perform only a few operations in $G_1$. The result seems to be quite
  efficient. However, it only supports selective disclosure (no advanced
  privacy-preserving policies), and even revocation is not considered from scratch,
  although the authors sketch an approach to integrate it -- which probably
  would require a more formal analysis and would incur in (possibly bad?)
  added costs.
  \note{The concept of aggregation here is different than the one in \cite{cl11}.
    In the latter, users can aggregate credentials from different issuers. Here,
    this is not possible, as aggregation won't work for different signing keys
    (i.e., issuer keys). Hence, aggregation rather refers to receiving multiple,
    independently signed, attributes by the same issuer, and then combining them
    into a single credential by that same issuer.}
\end{enumerate}

\paragraph{Main security models.}

\begin{enumerate}
\item[\cite{cl01}:] Security in \cite{cl01} is proven in an ad-hoc way,
  using the ideal-world/real-world paradigm. The authors describe a
  simulator for the operations supported by the system (Setup, FormNym,
  GrantCred, VerifyCred and VerifyCredOnNym), and prove that the output of this
  simulator is indistinguishable from that of the real protocol, under the
  strong RSA and Diffie-Hellman assumptions.  
\item[\cite{cl02}:] No security model is given for the anonymous credential
  application of the signature scheme (reasonably, as it is not the main focus
  of the paper). The signature scheme is proven secure (no specific mention
  to a security model, although I suppose it would be quite straight forward)
  based on the Strong RSA and Diffie-Hellman assumptions.
\item[\cite{cl04}:] Same as in \cite{cl02} (no actual security model for the
  AC system). The custom proofs are based on the DDH and LRSW assumptions.
\item[\cite{bcc+09}:] The article follows a game-based definition approach,
  with two security properties (besides correctness): anonymity and
  unforgeability, which are the usual, but extended to the scenario with
  delegation. Basically, the anonymity (in the ideal/real world paradigm)
  property requires that the adversary should not distinguish real credentials
  from simulated ones. Moreover, the adversary should not learn the delegation
  chain of an honest credential (even if it was issued by himself). For
  unforgeability, the requirement is that the adversary should not create
  a delegation chain that includes a delegation by an honest user, if the
  user did not actually perform that delegation.
\item[\cite{cks10}:] Signer privacy and user privacy properties are required
  for the underlying signature scheme (thus, inherited by the credential system,
  although I have not found explicit model). Signer privacy captures that the
  adversary (including corrupt users) doesn't learn any information about the
  signer from signatures and updates of signatures. User privacy captures that
  the adversary (including a corrupt issuer) does not learn any information
  about the blindly signed messages. \doubt{Not sure I get the utility of
    signer privacy. The original property seems to come from \cite{bckl08}.}
\item[\cite{cl11}:] The security properties in this work are unforgeability
  and anonymity, for which the authors give game-based definitions.
\item[\cite{cklm14}:] Defines security of the DAC scheme using simulation-based
  notions of anonymity and unforgeability.
\item[\cite{cmz14}:] The security properties proven in this work are:
  \begin{itemize}
  \item \emph{Unforgeability}: The adversary cannot produce a valid proof for a
    statement, if none of the attribute sets for which it has received a
    credential meets that statement.
  \item \emph{Anonymity}: The proofs produced in a presentation do not leak
    more information than the statement being proved.
  \item \emph{Blind issuance}: The issuance protocol is a secure two-party
    protocol for generating credentials on the user's attributes.
  \item \emph{Key-parameter consistency}: no issuer can use different parameters
    to produce credentials of different users such that their anonymity can
    be compromised afterwards. \doubt{This somehow remembers non-frameability in
      group signatures.}
  \end{itemize}
\item[\cite{cdhk15}:] The model (and associated proofs) presented in this paper
  is very comprehensive, and detailed. Specifically, for the main building block
  (Unlinkable Redactable Signatures), the authors give both game-based
  definitions as well as an ideal functionality. This ideal functionality models
  security in a single-issuer setting. However, as it is done in the UC
  framework, it can be composed with itself, so that a scenario with multiple
  issuers, in which users can combine credentials obtained by different users
  into a single showing process (``presentation'') is directly achievable by
  composing multiple instances of the ideal functionality (one per ``proof
  part'').
\item[\cite{ckl+15}:] The main security and privacy properties required are
  pseudonym collision-resistance (two different user secret keys cannot produce
  the same nym for the same scope), unforgeability (the adversary cannot forge
  issuance tokens or presentation tokens), and privacy (no two presentations by
  the same user can be linked) or weak privacy (presentations by the same user
  can be linked, but not traced to an issuance session). Privacy is modelled
  in the simulation paradigm, the difference in the modelling between privacy
  and weak privacy being a filter that removes some information \note{(I find
    this kind of weird; probably I'm wrong. Would be nice to study further)}.
  The unforgeability and privacy properties are essentially inherited from the
  main building block, privacy-enhancing attribute-based signatures. Although
  there, the authors begin by defining a blind issuance experiment (ensuring
  that the issuer does not learn anything more than what it should during
  isusance), and then define two variants for user privacy: presentation privacy
  and untraceability, which basically match the strong and weak notions for
  PABCs (in untraceability, two presentations by the same user can be linked,
  but not trace to a specific credential issuance). [Strong] user privacy has
  to satisfy both blind issuance and presentation privacy; weak user privacy
  has to satisfy both blind issuance and untraceability. I find this model
  somehow interesting, as it is one of the few (maybe along with \cite{cmz14})
  that includes some notion related to tracing back to issuance of credentials,
  as in group signatures). In both cases (PABC and PABS), [strong] privacy
  implies weak privacy.
  Essentially, the security properties required by the PABC scheme, are
  ensured by the building blocks. Namely: the pseudonym system (requiring
  key extractability, collision resistance and pseudonym unlinkability); the
  revocation scheme (requiring soundness and revocation privacy); the
  PABs (requiring unforgeability, and [weak] privacy); and the commitment
  scheme (requiring blinding and hiding, and opening extractability).
\item[\cite{dmm+18}:] The authors give a game-based security model, covering
  properties of unforgeability, anonymity, and policy-hiding. The latter
  means that, for delegated verification, the verifier is oblivious to the
  policy being verified.
\item[\cite{fhs19}:] Gives a game-based security model, with anonymity and
  unforgeability being the main security properties (besides correctness).
  Unforgeability resembles the traceability property of group signatures,
  which are recognised as an influence in their modelling -- more specifically,
  \cite{bmw03} (the model -- and the oracles therein -- definitely resembles
  the BMW model for GSs). The authors claim to be the firsts to give a well defined and
  formal model for ACs, besides \cite{ckl+15} (which gives game-based properties
  in the simulation paradigm) and \cite{cdhk15} (which follows the UC framework).
  However, \cite{fhs19} claims that adopting non-simulation based definitions
  allows them to reach a more efficient construction. They also support malicious
  issuer key generation, as issuers have to prove knowledge of their secret keys
  (which allows extraction in the games).
  An interesting aspect of their model is that all attributes in their
  credentials are learned by the issuer -- i.e., there are no blindly signed
  attributes. This implies that it is not possible to sign secret keys owned
  by the users (as in the conventional CL credentials). Then, for showing a
  credential, all the user has to do is reveal the attributes s/he is required
  to show. This has the disadvantage that, depending on the use case, this may
  be trivial to attack. For instance, assume a COVID-like pandemic situation,
  in which citizens have to prove being vaccinated. An AC system for this use
  could be naively defined as: { Type of vaccine, Date of vaccination }. But
  this is very susceptible to dictionary attacks, and leaves much to the
  engineering/implementation level. E.g., if it is easy for an eavesdroper
  to get hold of a credential (not even the plaintext attributes), s/he can
  just iterate through the small list of possible values, and then take
  advantage of the ``stolen'' credential. This is certainly secure under the
  model defined in \cite{fhs19}, but it is definitely easy for implementations
  following this model to go wrong...
  They also model only interactive show processes. Furthermore, to prevent
  replay attacks, the user has to prove knowledge of some randomness included
  in the credential. However (\textbf{cross-check this!}), since signatures
  are randomizable without knowledge of any secret value, any adversary that
  learns a credential (not necessarily any plaintext attribute associated to
  it), would be capable of authenticating through a dictionary attack in case
  of small attribute ranges.
  Note: this may just be a modelling issue (or not even that, cross-check later
  in case I misunderstood something). In their construction, they include
  a secret key of the user in the credentials, of which the user has to prove
  knowledge during the issue protocol. They do this by ``reusing'' the user
  secret key as the randomness employed for the set commitment scheme, and
  requiring the user to prove knowledge of the corresponding public key.
  However, I am not sure of whether or not this somehow thwarts the previously
  mentioned ``attack'', which affects the show protocol (\todo{i.e., the user does
    not need to prove knowledge of the usk during show, no?} \note{Actually, it
    should not, as it would probably prevent anonymity}) In any case, even if
  the specific construction and instantiation thwarts this attack, I think their
  model allows it.
\item[\cite{sms+19}:] No security model is given nor adopted.
\item[\cite{halp20}:] No formal definition is given. The following properties
  are claimed: undetectability (this seems similar to traceability in group sigs),
  unlinkability, selective attributes disclosure, unforgeability, persistent
  accounts, sybil resistance, extensibility, availability, decentralization.
\item[\cite{hs21}:] Security is given through game-based definitions of
  unforgeability, anonymity, and dependability. The first two are the usual ones,
  while the latter roughly requires that an adversarial helper cannot produce
  successful showings without cooperation from the core. It would be interesting
  to make a detailed comparison with security models of DAA (usually in the UC
  framework, although some game-based (seemingly flawed) definitions exist).
  The main argument that the authors give when comparing to DAA, is that the
  latter does not support attributes, and it is essentially a group signature
  scheme without revocation and optional linkability (this frontier is also
  blurry, see \cite{dl21}).
\end{enumerate}

\paragraph{Variations in functionality.}

\begin{enumerate}
\item[\cite{cl01}:] Extensions provided to the main functionality are:
  \begin{itemize}
  \item PKI-based and all-or-nothing non-transferability: Both options
    involve sharing a verifiable encryption of the user secrets. In the
    case of PKI-based non-transferability, the CA receives a verifiable
    encryption, using as key the user's master secret, of some valuable
    piece of information belonging to the user (e.g., the user's secret
    key associated to his public key with that CA). In the all-or-nothing
    case, the user shares with each organization (with which it has a
    pseudonym), a verifiable encryption of his pseudonym secret data, encrypted
    with his master secret. In both cases, if the user shares his master
    secret with someone else, then he automatically gives access to
    other relevant pieces of information (as the verifiable encryptions are
    made public by the corresponding entity).    
  \item One-show credentials: The validating tags over pseudonyms are extended
    to include an extra value in their commitment. Then, users have to reveal
    that value (or, rather, a value deterministically derived from that) in the
    zero-knowledge proofs they create at show time. Since the value is always
    the same, verifiers can check whether they have seen it before, or not.
  \item Revocation: Both local (i.e., within an organization) and global (i.e.,
    referring to an identity of the user in an external CA) is possible by
    extending the pseudonyms of the user, and the credential showing protocols,
    with values that allow subsequent decryption by a trusted party of their
    pseudonym or external identity, given a transcript of the credential
    showing.    
  \item Attributes: The paper also succinctly describes how multiple attributes
    per credential could be included. This would be done by dividing the inverval
    within the exponent used to compute the pseudonym in sub-intervals, and then
    proving that the exponent lies within a sub-interval.
  \end{itemize}
\item[\cite{cmz14}:] The paper mentions ``Credential translation'', which
  basically means being able to prove that two attributes in different
  credentials are actually the same. This is not formalized or detailed,
  though.
\item[\cite{cdhk15}:] The same as in the previous works (\cite{cl01,cl02,cl04}).
\item[\cite{dmm+18}:] The scheme supports delegated verification. Basically,
  to implement delegated verification, the delegatee receives an encryption of
  the policy it has to verify, plus a signature of the encryption. If the
  signature is valid, it re-randomizes the ciphertext for the policy, and
  sends it to the user, who follows the same protocol as in the normal case.
  The paper also mentions how to add more functionality, like delegation of
  credentials and revocation, but they are not modelled. Also interestingly,
  they claim somewhat informally (in Section 2.3) that no scheme satisfying
  anonymity in the presence of an untrustworthy issuer can support delegation
  of verification with policy hiding.
\item[\cite{sms+19}:] It is essentially the same as previous works, although it
  supports threshold issuance. Interestingly, \cite{sms+19} does not make use
  of pseudonyms. I.e., credentials are just signed (blocks of) attributes. This
  probably lets them achieve better efficiency. \doubt{This makes the scheme
    to be practically like a group signature scheme (without revocation...)}
\item[\cite{hs21}:] The main variation here is the application of the core-helper
  division (typical of DAA) to the AC domain.
\end{enumerate}

\paragraph{Efficiency.}

\cite{sms+19} seems to be the most efficient one (note: relies on the
Fiat-Shamir heuristic). Credentials are only composed by two G1 elements,
independently on the number of attributes. \todo{Cross-check this after
  review.}

\cite{cdhk15} and \cite{fhs19} achieve credential showings of size independent
of the number of attributes.

\paragraph{Main challenges.}

\subsection{Related Primitives}

Most schemes \cite{cl01,cl02,cl04,cdhk15,sms+19} are based on randomizable
signatures, with the possibility of signing committed values, that also support
efficient proofs of knowledge.

The most recurrent signature schemes are Camenisch-Lysyanskaya \cite{cl02,cl04},
BBS/BBS+ \cite{asm06,cdl16b}, and Pointcheval Sanders \cite{ps16}.
\cite{cdhk15} leverages their own signature scheme, called Unlinkable
Randomizable Signatures, which lets users obtain a signature on a set of
(committed) messages and then prove knowledge of (a subset of) these
messages, introducing rerandomization to prevent linking. \cite{fhs19}
follows a similar approach, using vector commitments. Both schemes
\cite{cdhk15,fhs19} seem to be the most efficient AC instantiations to date.
\cite{cdhk15} follows the UC framework; \cite{fhs19} a game-based definition.

The ``family'' of AC systems known in the industry as BBS+ originates from
\cite{asm06} (or, probably, from the BBS+ variant in \cite{cdl16b}, which
introduces several improvements). \cite{asm06} presents a GS-like system that
lets users obtain a credential from a Group Manager. This credential is a
BBS+ signature. BBS+ signatures are a digital signature scheme, based on
\cite{bbs04} and following the modification guidelines put forward in
\cite{cl04}\footnote{Essentially, the authors of \cite{asm06} acknowledge
  \cite{cl04} as those who proposed the BBS+ scheme -- but without security
  proofs, which are provided in (the full version of) \cite{asm06}.}. On top
of the signature scheme, they add efficient protocols for obtaining a signature
over a set of committed messages, and proving -- in zero knowledge -- knowledge
of a signature. Users can then be authorized by Application Providers (APs) to
access their services: for this, APs maintain a list of the users they have
granted/revoked access to, using a dynamic accumulator. APs also allow users to
authenticate anonymously up to $k$ times. In order to access the services of APs,
users have to derive a value using a VRF, and further prove that the value used
to seed the VRF is a number within $[1,k]$ -- in addition to, of course, proving
knowledge of a valid BBS+ signature (their credential). APs keep a record of the
accesses. Thus, if a user accesses more than $k$ times a given AP, anyone with
access to the record will be able to learn that a user has accessed more than
$k$ times, as there will be more than one matching VRF-derived values.
Furthermore, these two (or more) values let anyone extract a ``pseudonymous''
identity of the user. The model (only informally presented, formal definitions
appear in \cite{ts06} and proofs are deferred to a full version) seems to be
used in $k$-TAA systems ($k$ Times Anonymous Authentication), and defines
properties for:

\begin{itemize}
\item D-Detectability: Adversaries authenticating more than $k$ times are
  detected.  
\item D-Anonymity: Honest users authenticating less than $k$ times remain
  anonymous.
\item D-Exculpability: No honest user can be framed as having authenticated
  more than $k$ times. The GM cannot be framed as dishonest if that is not
  the case.
\end{itemize}

The system in \cite{aks12} also uses BBS+ signatures as a main building block
to design a system with accountable anonymity, although it is not ``strictly''
an anonymous credentials system: users receive a credential that lets them
authenticate anonymously against service providers, but this credential does
not include attributes, which seems to be the common case in ACs (however,
with BBS+ it is trivial to add attributes, although this should be modelled).
The main contribution of \cite{aks12} is the design and incorporation of
protocols to block misbehaving users depending on their behaviour, without
relying on trusted third parties. This is based on ``reputation lists'',
maintained by each service provider. Uses that have previously registered
with a Group Manager can authenticate against service providers by proving
knowledge of a valid credential. Depending on how these users behave during
the session with the service provider, the latter adds the interaction to
either a \emph{good behaviour} list, or a \emph{misbehaviour list}. For
subsequent authentications, users prove (in an ``almost unlinkable'' way
w.r.t. previous authentications) that they have a certain reputation,
computed as a weighted sum of their presence in the good/bad behaviour
lists. Moreover, each service provider can maintain multiple thematic lists,
and then require users to satisfy arbitrary boolean policies based on these
lists (e.g., reputation $\ge X_1$ on $list_1$ and reputation $\le X_2$ on
$list_2$ or reputation $= X_3$ on $list_3$) so that only users meeting
the defined policy can access their system. These proves have though a linear
dependency on the number of authentications that each user has done in
the past. To reduce the impact of this, the authors create epochs. When a
user authenticates successfully against a service provider, at a given epoch
$i$, the service provider gives the user a token that authenticates the
reputation that the user had at epoch $i$. Then, when this user tries to
authenticate again, he only needs to give that token, and prove his reputation
since epoch $i$ (this is why authentication is ``almost unlinkable'', as
service providers may learn when the user authenticated for the last time).
Note that no trusted party is involved in the blacklisting process, as
correctness of all tokens exchanged between users and service providers to prove
meeting certain policy, is ensured via the corresponing proof protocols.
Concerning security, the system is proven secure in the simulation paradigm,
claiming to meet (informally defined) properties of:

\begin{itemize}
\item Anonymity: All the SPs can infer from authenticating users is that they
  meet the predefined policy, and that they authenticated at a certain epoch.
\item Authenticity: Only users meeting the defined policies can authenticate.
\item Mis-authentication resistance: Un-registered users cannot authenticate
  successfully.
\item Non-frameability: No coalition of users can cause that another user
  meeting the required policy, cannot authenticate successfully.
\end{itemize}

Somehow, these properties resemble those in the group signatures model in
\cite{kty04}. Probably, the addition of non-frameability is a consequence
of adding a variant of revocation.

\paragraph{Primitives for credentials with generic policies.} \cite{cgm16}
describes techniques to be able to create efficient proofs that combine both
algebraic and non-algebraic relations. For instance, proving knowledge of an
ECDSA or RSA-FDH signature (both of which include computation of a hash
function); but also being able to prove any arbitrary (non-algebraic) funcion
$f$. This may be very useful to achieve compatibility with traditional
credentials/signature schemes, that mostly do not follow the algorithms
used in anonymous credentials systems. In fact, that is one of the main
motivations in the paper. The approach in \cite{cgm16} builds on committing
Oblivious Transfer and Garbled Circuits (not necessarily with privacy).
A closely related work seems to be \cite{dfkp16},
which achieves the same goal but using SNARKS, which results in different
tradeoffs -- hence, it may be interesting, as the SNARK domain has improved
significantly since 2016. \cite{kkl+16} also allows building anonymous
credentials for arbitrary policies, but using a different approach too.

\subsubsection{Pseudonym Systems}
\label{sssec:pseudonyms}

\doubt{Not sure if this fits here.}

\subsection{Applications}
\label{ssec:acapplication}

\subsubsection{Theory}
\label{sssec:actheoryapp}

Main approaches to build ACs (from ToPS paper I reviewed):

\begin{itemize}
\item Re-randomizable signatures on commitments (also as in DAA):
  \cite{cl02,cl04,lmpy16,ps16}.
\item Equivalence class signatures: \cite{fhs19,hs14}.
\item Redactable signatures \cite{cdhk15,sand20} and malleable signatures
  \cite{ckl14}.
\item Predicate encryption: \cite{dmm+18}.
\end{itemize}

Also:

\begin{itemize}
  \item ACs based on aggregate signatures: \cite{cl11}.
\end{itemize}

PS: Tokenization.

\subsubsection{Real World Deployments}
\label{sssec:acrwdeploy}

PS: Tokenization.
Signal's AC \cite{cpz20}.

\begin{itemize}
\item U-Prove (see ref. 65 in \cite{hs21}):  This is largely based on Brands
  thesis. There was a deployment by Microsoft, mostly concurrent to Idemix.
  They are one-show credentials, but seemingly there is recent real-world
  deployments based on them (references in p.1 of \cite{hs21}):

  \begin{itemize}
  \item Privacy-Pass by Cloudflare.
  \item Trust Tokens API by Google.
  \item PrivateStats proposal by Facebook.
  \end{itemize}

\item Idemix \cite{ch02}: This is largely based on CL signatures. It has been
  deployed (or is being deployed) in Hyperledger Fabric, and I think there is
  some of it in Indy too.
\end{itemize}

\cite{hs21} contains also many references to ``practical'' applications of
ACs. However, these are mostly references to papers in cryptographic venues,
so I suspect that they are more academic than real-world systems.

\subsection{TODO}

\begin{itemize}
\item \cite{bckl08}.
\item \cite{sand20}.
\item \cite{kkl+16}: achieves similar results to \cite{cgm16} with a different approach?
\end{itemize}

[ToPS paper I reviewed] refers to a strategy to do threshold issuing in \cite{bbh06}.

Concepts in ACs: multishow, one-show (Brands et al); interactive vs non-interactive
showings (differentiation made in \cite[p.6]{fhs19} but, why would one want interactive,
in the real world?)

Which schemes support comibning credentials from multiple issuers? I think this
is directly obtained in the schemes following the CL approach; but others?

A recurrent claim in schemes avoiding using zero-knowledge proofs of knowledge
of some attributes being included in a credential is that these proofs are costly
(like, linear in the number of attributes). Yet, they resort to other primitives
that may also be costly (e.g., predicate encryption \cite{dmm+18}) or somehow move
the cost to some other place (e.g., \cite{fhs19} uses a vector commitment scheme
that requires a public key with size that grows with the number of attributes
that \emph{can} be committed). It would be nice to have a detailed and complete
(e.g., not skipping the data that makes one scheme look bad, like the size of
the public keys) comparison. And, ideally, with concrete instantiations (not only
theoretical analysis)?

\cite{fhs19} has a nice comparison table.

How to compare efficiency of AC systems?

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "sok-privsig"
%%% End:

### 2021-11-26 prism-backend/research/soa_review/app-gs.tex
Polished version. Still early draft, but at least readable (excluding DAA section, which is not a priority for now).

--- 2021-10-27 prism-backend/research/soa_review/gs.tex
@@
-\section{Group Signatures}
-\label{sec:gs}
+\section{Log on Review of Group Signatures schemes}
+\label{app:ac}
 
-\paragraph{Main intuition.}
-%
-Group signatures were first proposed by Chaum and van Heyst in 1991 \cite{ch91}
-as a privacy-respectful extension to conventional digital signatures.
-The intuition is simple: in order to avoid revealing the identity of the signer,
-we make her signatures look indistinguishable to the signatures of all other
-members of a group. Then, any entity with access to the group public key can
-verify that a group signature comes from a member of the group, but cannot
-tell which specific one actually created it.
-%
-Beyond this, group signature schemes have one main feature: a (set of) group
-manager(s) control who can become a member of the group. Also, most frequently,
-a (set of) group manager(s) decide when to expell a member from the group, or
-when to re-identify the creator of a specific signature.
-%
-The initial idea put forward in \cite{ch91} had, as is to be expected, a number
-of limitations. In the following years, the seminal work was extended, both
-formally, functionally and efficiency-wise.
-
-\subsection{Approaches, Models, and Variations}
-\label{ssec:gsapproach}
-
-\subsubsection{Main approaches.}
-%
-There are two main ways that are recurrently used to instantiate group signature
-schemes: \emph{Sign-Encrypt-Prove} and \emph{Sign-Randomize-Prove}. In both
-variants, when new members of the group join, they receive a credential (i.e.,
-a signature by the issuer) derived from a secret they choose. Then, when
-creating a group signature, they prove control a valid credential and the
-associated secret. The difference lies on how this credential is kept hidden
-from the verifier.
-%
-In the sign-encrypt-prove variant, proposed in \cite{bmw03}, signers
-encrypt their credential with a \doubt{IND-CCA2? what type?} scheme and then
-create a NIZK \needcite proof of knowledge of such a valid credential
-over their secret (plus the message they want to sign). This typically results
-in schemes with more efficient openings, as the opening authority just has
-to decrypt the encrypted credential. However, group signatures require more
-space.
-%
-In the sign-randomize-prove variant, proposed in \needcite \todo{Get Shorty?},
-credentials are actually randomizable signatures by the issuer. Signers then
-randomize the signature (credential), and create a NIZK proof of knowledge that
-this credential is issued for a secret they know (again, plus the message
-they want to sign). This usually results in schemes with less efficient openings,
-as the opening authority needs to iterate over the registered credentials until
-finding the one from which the randomized credential was derived. However, the
-produced group signatures are also shorter.
-
-When a new user wants to become a group member, a common habit is also to have
-her prove ownership of a conventional digital identity. This identity is then
-added to the de-identifying information leveraged by the opening authority, in
-order to be able to associate (anonymous) group signatures to a real-world
-identity. These conventional digital identities can be any type of PKI-based
-(e.g. X.509 or equivalent) certificate. \todo{This is important for
-  non-frameability! Check \cite[Section 3.2]{cdl+20} and re-state this.}
-\todo{This is indeed necessary for non-repudiation (mentioned in
-  \cite[Section 4]{lpy12}).}
-\todo{Typically used in schemes with verifiable openings. See
-  \cite[Section 1.3.3]{bsi12}.}
-
-\subsubsection{Main security models.}
-%
-Security for group signatures is given in the form of game-based definitions
-\needcite.
-The first formal security model appeared in \cite{bmw03}. It captured security
-for groups with a prefixed set of members, added by the group manager upon the
-creation of the group. This static requirement was too restrictive to be
-realistic, and was quickly extended in \cite{bsz05} and \cite{kty04,ky06}, to
-model that new users can join the group after it has been created. The models
-in \cite{bsz05,kty04,ky06} are usually referred to as dynamic or partially
-dynamic. \cite{bcc+16} generalizes the (partially) dynamic setting into a fully
-dynamic model, which considers extra desirable security properties when users
-can be revoked (i.e., removed from the group).
-
-Up to some subtleties, the main security properties in most works that appeared
-after \cite{bmw03,bsz05,kty04,ky06} are as follows:
+\subsection{TODOs}
 
 \begin{itemize}
-\item {\bf Anonymity}. This is the core property concerning privacy. It
-  ensures that given a signature produced by one out of two honest (challenge)
-  users picked at random from the set of honest group members, it should be
-  unfeasible to determine which one actually created it.
-
-\item {\bf Traceability}. This property (covered by the misidentification attack
-  in \cite{kty04,ky06}, and spaning also non-frameability in \cite{bmw03})
-  captures that it must be possible (by the proper authority) to unambiguously
-  recover the identity of the signer of any valid group signature.
-
-\item {\bf Non-frameability}. This property (considered in the framing attacks
-  in \cite{kty04,ky06}) requires that no adversary should be able to create
-  valid signatures that can be used to incriminate honest users by having them
-  open to an honest user who did not create them.
-
+\item Fully anonymous dynamic GS from SPS-EQ \cite{ds16}
+\item Multi-group group signature schemes. Compare with ACs with multiple
+  issuers.
 \end{itemize}
 
-\cite{bcc+16} also includes a trace soundness property, ensuring that signatures
-can be associated (via opening proofs) to only one user \todo{why does this not
-  appear in the other models? Maybe because they don't support verifiable
-  openings? Check \cite{kss19} and, if so, move this to the variations in
-  functionality.}
-
-\subsubsection{Variations in functionality.}
-%
-Note that, while the security properties just described roughly have the same
-purpose across models, there are still differences making some models stronger
-or more general than others in some respects. This includes subtleties like who
-generates the keys of the authorities (the environment vs the adversary), how
-many queries can be made to the challenge oracles and whether or not the
-signatures are fixed, etc. However, while important, there are usually generic
-techniques that allow to migrate from one variant to another \todo{\needcite,
-  ellaborate more, or rewrite}. Now we are interested in revisiting some of
-the variations that have impact into the functionality that schemes
-following each model can provide, or variations that are specific to group
-signatures schemes and do not appear in other cryptosystems.
-
-\paragraph{Separating issuer and opener.}
-In some schemes \cite{bmw03,kty04} one single authority concentrates the
-power to add new members to the group, and open signatures. This endows such authority with great
-power -- and trust -- and is therefore one of the main concerns for privacy
-advocates: not only this authority can prevent users from joining (in the case
-of dynamic groups), but it can also reidentify group members. In order to reduce
-this trust, and since it is a clear distinction between both functionalities
-(issuing and opening), many schemes separate both roles into an issuer and an
-opener. While both authorities need to be trusted for their respective tasks,
-one can now make independent assumptions and even ensure certain properties
-if only one of the two authorities is compromised or malicious. For instance,
-non-frameability can be achieved even when both authorities are malicious;
-traceability can be achieved with malicious openers; and anonymity can be
-kept as long as the opener is honest. This is the case in \cite{bsz05} and
-\cite{ky06} (which, although starts from a single authority, also considers
-and formalises the case of separate authorities).
-
-\paragraph{Protecting against corrupt authorities.}
-Even when the issuance and opening functionalities are separated, as mentioned,
-each entity can unilaterally break crucial properties in a group signature scheme.
-While placing such kind of trust may be reasonable in some use cases, it may not
-be so for others. Thus, a natural extension is to reduce this trust as much as
-possible. In this direction, there have been works that have applied threshold
-and similar techniques \needcite to require that a set of openers (as opposed
-to a single opener) need to cooperate in order to open any group signature
-\cite{bcly08} \needcite.
-Recently, the role of the issuer was also subject to these techniques
-\cite{cdl+20}, and it is now known how to produce group signatures such that no
-single entity can prevent users from joining nor reidentify them.
-
-\paragraph{Forward security.}
-Forward security aims at restricting the impact of security compromises (e.g.,
-key leakage) to the future: i.e., if an attacker gains control of a user's
-private key, only signatures produced after the compromise should be considered
-invalid. In schemes that do not ensure forward secrecy, such a compromise also
-renders invalid signatures produced before the compromise. Note that, for
-conventional signatures, only the compromised users is (directly) affected by
-such event. However,  in group signatures, all group members are directly
-affected, as the signer's identity is not revealed by the signature. Thus,
-in order to learn whether or not a past signature was issued by a compromised
-user, it is necessary to resort to the opener -- therefore, reidentifying
-\emph{all} users in the system.
-%
-Forward security has been introduced in group signatures in works like
-\cite{song01,ly12} \needcite.
-%
-Interestingly (but logically), the approach to incorporate this property
-holds similarities with the functionality to implement fully dynamic group
-signatures: for forward security, users are usually required to apply an
-update procedure to their private keys \cite{ly12}; in fully dynamic group
-signatures, it is the group manager (or the opener) who has to update some
-key material \cite{bcc+16}. In both cases, time has to be discretized in epochs,
-and conditions are introduced into the security properties that prevent an
-adversary being able to deanonymize (produce) a valid signature generated
-(using) a key in an epoch in which such key was not supposed to be active
-(either because the user updated it -- in a forward secure scheme -- or the
-group manager revoked it -- in a fully dynamic scheme).
-
-\paragraph{Revocation mechanisms.}
-Verifier Local Revocation \cite{bs04}, accumulators approach.
-
-\paragraph{Opening controls.}
-Even when separating the roles of the authorities or distributing them, the
-fact that some entity (or set of entities) can open group signatures is still
-a delicate matter that creates friction. A minimal control is to enable the
-opener to prove that the opening process has been performed honestly. This is
-precisely what is done by schemes that support \emph{verifiable opening}
-\needcite. To further aleviate this issue, some schemes
-introduce mechanisms to even prevent opening as long as some condition is
-met. For instance, in \cite{seh+12,ehk+19}, the condition is determined by
-the message (e.g., only signatures over offending messages can be opened).
-To implement this, the authors introduce an extra authority, the
-\emph{admitter}, such that the opener needs to get some information from the
-admitter in order to be able to open signatures over some specific message.
-In \cite{sbm10}, the authors propose \emph{contractual} anonymity: before a user
-is able to anonymously access some service, both user and service sign a
-contract defining the conditions upon which anonymity can be revoked. This
-contract can only be enforced by a trusted entity, the \emph{accountability
-  service} who runs a trusted execution environment (such as today's Intel
-SGX \needcite) ensuring that the conditions are checked in a trustworthy manner.
-
-\paragraph{Alternatives to opening.}
-%
-Even with separated authorities, with distributed openers, or with more generic
-opening controls such as message-dependent opening, opening may not even be
-the type of reduction of privacy that is necessary. In this vein, alternative
-schemes have been proposed that do not include any kind of
-opening at all.
-%
-In the schemes proposed in \cite{kty04,cpy06,bcly08}, there is an extra
-authority that can produce \emph{tracing} trapdoors on a per-user basis.
-Once the tracing trapdoor for a specific user is given to some entity, this
-entity can link (or trace) all group signatures produced by that user.
-These trapdoors are also an effective mechanism for implementing verifier-local
-revocation.
-%
-In \cite{gl19}, the opener is replaced by a \emph{converter} who, rather than
-opening any given group signature, can link sets of signatures. More
-specifically, when queried with a set of signatures, the converter transforms
-them so that every signature coming from the same user gets assigned a same
-randomized pseudonym. Furthermore, to prevent the converter from gradually
-relinking all the signatures, these conversions are non-transitive: i.e.,
-signatures produced by user $A$ will receive a different randomized pseudonym in
-different queries.
-%
-In \cite{dl21}, there is directly no trusted entity that can open or link group
-signatures. Instead, every user can create proofs of several signatures having
-been issued by herself. In this case, the authors also propose a scheme whereby
-a user can prove sequentiality of a set of signatures: i.e., that all signatures
-were produced by herself, and no signature has been omitted or inserted into the
-sequence, which is also given in the order in which the original signatures were
-produced.
-
-\subsubsection{Efficiency.}
-
-\begin{itemize}
-\item Size of (group) keys.
-\item Size of signatures.
-\item Verification time (batching, including revocation checks...)
-\item Accumulators.
-\end{itemize}
-
-\subsubsection{Main challenges.}
-
-Efficiency is possibly good for many real-world cases. Still: utility
-and unavailability of implementations.
-
-\note{Concurrent joins -- avoid extraction \cite{ky05,klap20}.}
-
-\subsection{Related Primitives}
-
-\subsubsection{Ring Signatures}
-\label{sssec:rs}
-
-\cite{rst06}
-
-\cite{bcc+15} uses ring signatures to build a fully dynamic group signature
-scheme.
-
-\subsection{Applications}
-\label{ssec:gsapplication}
-
-See \cite[Section 1.2.3]{bsi12}: it seems mostly theoretical applications.
-
-\subsubsection{Theory}
-\label{sssec:gstheoryapp}
-
-GS-MDO imply IBE \cite{ehk+19}.
-GS are implied (shouldn't his by imply?) by trapdoor permutations \cite{bmw03}.
-GS imply one-way functions \cite{romp90}.
-GS imply public key encryption \cite{aw04}.
-Commitments from group signatures (group signatures imply commitments?)
-(ref. 25 in \cite{bfg+11}).
-
-\subsubsection{Real World Deployments}
-\label{sssec:gsrwdeploy}
-
-\cite{ehk+19} mentions anonymous auctions, anonymous bulletin boards and
-anomaly detection systems.
-
-Maybe make some comments on how to deploy gs schemes, or what aspects may be
-relevant. For instnace, some schemes/models (e.g. \cite{ly12}) assume a
-trusted party who generates the keys for the authorities. While this has
-a big impact in security/trust model, in the real world it would probably
-be circumventable with audited processes for most use cases. Also, the
-issue with concurrent issuance and the approach we took for implementing
-\cite{gl19} in ICT4Cart, or the limitation to logarithmic numbers of users, etc.
-
-\subsection{Further Notes}
+\subsubsection{Further Notes}
 \note{Integrate this section or delete it.}
@@
 \end{itemize}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "sok-privsig"
-%%% End:

### 2021-11-26 prism-backend/research/soa_review/gs.tex
Review of FHS19.
Some writeup on ACs main approaches, security models, and functionality. Doc reorg.
Polished version. Still early draft, but at least readable (excluding DAA section, which is not a priority for now).

@@
 of limitations. In the following years, the seminal work was extended, both
-formally, functionally and efficiency-wise.
+formally, functionally, and efficiency-wise.
 
@@
 In the sign-encrypt-prove variant, proposed in \cite{bmw03}, signers
-encrypt their credential with a \doubt{IND-CCA2? what type?} scheme and then
+encrypt their credential and then
 create a NIZK \needcite proof of knowledge of such a valid credential
@@
 %
-Security for group signatures is given in the form of game-based definitions
-\needcite.
+Security for group signatures is given in the form of game-based definitions.
 The first formal security model appeared in \cite{bmw03}. It captured security
@@
 renders invalid signatures produced before the compromise. Note that, for
-conventional signatures, only the compromised users is (directly) affected by
+conventional signatures, only the compromised user is (directly) affected by
 such event. However,  in group signatures, all group members are directly
@@
 Forward security has been introduced in group signatures in works like
-\cite{song01,ly12} \needcite.
+\cite{song01,ly12}.
 %
@@
 update procedure to their private keys \cite{ly12}; in fully dynamic group
-signatures, it is the group manager (or the opener) who has to update some
+signatures \todo{fully dynamic gs have not been introduced yet!}, it is the
+group manager (or the opener) who has to update some
 key material \cite{bcc+16}. In both cases, time has to be discretized in epochs,
@@
 
-\paragraph{Revocation mechanisms.}
+\paragraph{\todo{Revocation mechanisms}.}
 Verifier Local Revocation \cite{bs04}, accumulators approach.
@@
 \item Verification time (batching, including revocation checks...)
-\item Accumulators.
 \end{itemize}
 
-\subsubsection{Main challenges.}
+\subsubsection{Main challenges and interesting lines of work.}
 
@@
 
-GS-MDO imply IBE \cite{ehk+19}.
-GS are implied (shouldn't his by imply?) by trapdoor permutations \cite{bmw03}.
-GS imply one-way functions \cite{romp90}.
-GS imply public key encryption \cite{aw04}.
-Commitments from group signatures (group signatures imply commitments?)
-(ref. 25 in \cite{bfg+11}).
+\begin{itemize}
+\item GS-MDO imply IBE \cite{ehk+19}.
+\item GS are implied by trapdoor permutations \cite{bmw03}.
+\item GS imply one-way functions \cite{romp90}.
+\item GS imply public key encryption \cite{aw04}.
+\item Commitments from GS (ref. 25 in \cite{bfg+11}).
+\end{itemize}
 
@@
 
-\subsection{Further Notes}
-\note{Integrate this section or delete it.}
-
-\todo{CCA2 type of anonymity is defined in \cite{bbs04}. Schemes with CPA type
-  of anonymity are (according to \cite{ehk+19}): \cite{bw06,bw07}.}
-
-\cite{ehk+19} has a nice related work mentioning the assumptions that are
-typically used.
-
-Signature highjacking attacks (referenced in \cite{ehk+19}).
-
-If we want to have traceability, the issuer needs to be honest. See what
-implications this has in practice (e.g., what architectures are compatible
-with this?) This probably makes schemes with separate issuing and opening
-authorities more attractive in practice.
-
-Other minor variants: group blind signatures, democratic group signatures,
-mediated group signatures. All referenced in \cite[Section 1.3.5]{bsi12}.
-
-Backward linkability property of group signatures with Timed Verifier-Local
-Revocation, proposed in \cite{nf05}. Mentioned in \cite[Section 8.1.2]{bsi12}.
-
-Relation of forward security with proactive security \cite{oy91}?
-
-References 1, 24, 32 and, probably, 35 in \cite{bfg+11} seem to be (traceable)
-group signatures that use the nym approach (or similar) for linking. Check.
-
-\paragraph{Academic indicators.}
-IACR, Esorics, CCS, AsiaCCS, SP, EuroSP, Usenix Sec and Privacy, PETs... Not
-sure where to fit this.
-
-Main cryptographic building blocks:
-
-\begin{itemize}
-\item BB signatures \cite{bb04}.
-  \begin{itemize}
-  \item Used in: \cite{ky05}.
-  \item Paillier encryption of discrete-logarithms? Used in \cite{ky05} and,
-    I think, \cite{gl19}.    
-  \end{itemize}
-\item Model for reduction: list of group signature schemes based on RO and
-  non-RO are given in \cite{bcc+16}.
-\end{itemize}
-
 %%% Local Variables:

### 2021-11-29 prism-backend/research/soa_review/ac.tex
Pass to improve readability.

@@
 is the same entity as the verifier (as in ticketing systems for public transport),
-\cite{cmz14}, replaces signatures with algebraic MACs.
+\cite{cmz14} replaces signatures with algebraic MACs.
 
@@
 %
+\comment{This section is just a placeholder for now...}
 
@@
 %
-\note{I find interesting that, given that ACs and group signatures are
+\comment{This section is just a placeholder for now...}
+
+I find interesting that, given that ACs and group signatures are
 essentially the same thing, there is no work (or I have not come across it)
-  trying to connect both. Specifically, the following questions:}
+trying to connect both. Specifically, the following questions:
 
@@
     which may then carry consequences (e.g., legal actions) for the honest user.
+    Probably, this is related to ACs not having opening, although it has been
+    shown in the GS literature that schemes without opening, but with linking
+    can still have a notion of non-frameability \cite{dl21} (and, certainly,
+    blacklisting/revocation allows linking, and this has already been done in
+    the AC domain.)
   \item Maybe I'm wrong in the two previous points, and we can draw a connection
@@
   \end{itemize}
+\item Also, forward security does not seem to have been explored in the AC
+  domain (again, I may just overlooked works on it). But it has been studied in
+  GSs. Can we leverage that?
 \end{itemize}
@@
 \label{ssec:acrelated}
+
+\comment{This section is just a placeholder for now...}
 
@@
 \label{ssec:acrealworld}
+
+\comment{This section is just a placeholder for now...}
 

### 2021-11-29 prism-backend/research/soa_review/gs.tex
Pass to improve readability.

@@
 signatures are fixed, etc. However, while important, there are usually generic
-techniques that allow to migrate from one variant to another \todo{\needcite,
-  ellaborate more, or rewrite}. Now we are interested in revisiting some of
+techniques that allow to migrate from one variant to another \needcite. Now we
+are interested in revisiting some of
 the variations that have impact into the functionality that schemes
@@
 
+\comment{This section is just a placeholder for now...}
+
 \begin{itemize}
@@
 
+\comment{This section is just a placeholder for now...}
+
 Efficiency is possibly good for many real-world cases. Still: utility
@@
 
-\note{Concurrent joins -- avoid extraction \cite{ky05,klap20}.}
+Concurrent joins -- avoid extraction \cite{ky05,klap20}.
 
 \subsection{Related Primitives}
+
+\comment{This section is just a placeholder for now...}
 
@@
 
+\comment{This section is just a placeholder for now...}
+
 See \cite[Section 1.2.3]{bsi12}: it seems mostly theoretical applications.
@@
 \label{sssec:gstheoryapp}
+
+\comment{This section is just a placeholder for now...}
 
@@
 \label{sssec:gsrwdeploy}
+
+\comment{This section is just a placeholder for now...}
 

### 2021-11-29 prism-backend/research/soa_review/soa-review.tex
Review of FHS19.
Some writeup on ACs main approaches, security models, and functionality. Doc reorg.
Polished version. Still early draft, but at least readable (excluding DAA section, which is not a priority for now).
Pass to improve readability.

@@
 
-\title{State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication}
+\title{State of the Art Review on Privacy-Preserving Authentication}
 \author{}
@@
 \begin{abstract}
-	\textbf{DISCLAIMER}: Please, keep in mind that, as of now, this document
-	basically contains a research log in the shape of personal notes. Do not take 
-	anything written here as ground truth.
+  \comment{\textbf{DISCLAIMER}: Please, keep in mind that this is a working
+    draft. Its main use in its current state is to foster debate on the topics
+    it deals with. Do not take anything written here as ground truth.}
+
+  This document explores three closely related cryptographic systems in the area
+  of privacy-enhanced and, more concretely, in the domain of authentication.
+  Namely, we study advances in group signatures (GS), anonymous credentials
+  (AC), and direct anonymous attestation (DAA). All three have somehow similar
+  purpose, have followed similar approaches, and have received much attention in
+  the the academic literature for the last (almost) four decades but, in some
+  sense, independently on one another.
+
+  Our goal is to extract common insight from all of them. Firstly, from a
+  theoretical perspective, with the aim to identify the advantages and
+  disadvantages of existing models and approaches, and develop intuition as to
+  whether we can (or cannot) combine ideas and fill gaps, and what may be the
+  most suitable path to follow for new projects, depending on their needs.
+  Secondly, from a practical perspective, DAA and ACs have already been deployed
+  in the real world, and analysing the difficulties they have come across will
+  certainly be of use.
+
 \end{abstract}
 
+\iffalse
 \input{introduction.tex}
+\fi
 \input{gs.tex}
-\input{abs.tex}
+%\input{abs.tex}
 \input{ac.tex}
@@
 \input{conclusion.tex}
+
+\bibliographystyle{splncs04}
+\bibliography{soa-review}
+
+\appendix
 
@@
     blacklisting (or, at least, not in an unequivocable way).
-  \item Concerning traceability.
+  \item Concerning traceability. \cite{fhs19} definition of unforgeability
+    resembles traceability. I guess this would be the case in most AC works.
   \end{itemize}
@@
 
-\bibliographystyle{splncs04}
-\bibliography{soa-review}
+\input{app-gs}
+\input{app-ac}
 

### 2021-11-30 prism-backend/research/soa_review/app-ac.tex
Added review of Evernym.

@@
 
-\subsection{TODOs}
+\subsection{Academic Literature Review}
 
-\begin{itemize}
-\item \cite{bckl08}.
-\item \cite{sand20}.
-\item \cite{kkl+16}: achieves similar results to \cite{cgm16} with a different
-  approach?
-\end{itemize}
-
-A recurrent claim in schemes avoiding using zero-knowledge proofs of knowledge
-of some attributes being included in a credential is that these proofs are costly
-(like, linear in the number of attributes). Yet, they resort to other primitives
-that may also be costly (e.g., predicate encryption \cite{dmm+18}) or somehow move
-the cost to some other place (e.g., \cite{fhs19} uses a vector commitment scheme
-that requires a public key with size that grows with the number of attributes
-that \emph{can} be committed). It would be nice to have a detailed and complete
-(e.g., not skipping the data that makes one scheme look bad, like the size of
-the public keys) comparison. And, ideally, with concrete instantiations (not only
-theoretical analysis)?
-
-\subsection{Approaches, Models, and Variations}
+\subsubsection{Approaches, Models, and Variations}
 
@@
 
-\paragraph{Efficiency.}
+\subsubsection{Efficiency.}
 
@@
 
-\paragraph{Main challenges.}
+\subsubsection{Main challenges.}
 
-\subsection{Related Primitives}
+\subsubsection{Related Primitives}
 
@@
 
-\subsection{Applications}
+\subsubsection{Applications}
 \label{ssec:acapplication}
@@
 
-\subsection{TODO}
+\subsubsection{TODO}
 
@@
 \end{itemize}
+
+A recurrent claim in schemes avoiding using zero-knowledge proofs of knowledge
+of some attributes being included in a credential is that these proofs are costly
+(like, linear in the number of attributes). Yet, they resort to other primitives
+that may also be costly (e.g., predicate encryption \cite{dmm+18}) or somehow move
+the cost to some other place (e.g., \cite{fhs19} uses a vector commitment scheme
+that requires a public key with size that grows with the number of attributes
+that \emph{can} be committed). It would be nice to have a detailed and complete
+(e.g., not skipping the data that makes one scheme look bad, like the size of
+the public keys) comparison. And, ideally, with concrete instantiations (not only
+theoretical analysis)?
 
@@
 
+\subsection{Industry Systems Review}
+
+\begin{itemize}
+\item Evernym. \url{https://www.evernym.com/}
+  \begin{itemize}
+  \item {\bf Introduction}. Evernym is a software company that is some kind of
+    relative of Sovrin. Their solution builds completely on the Sovrin system.
+  \item \emph{``How Sovrin Works''}%
+    \footnote{\url{https://www.evernym.com/wp-content/uploads/2017/07/How-Sovrin-Works.pdf}}.
+    Describes from a high-level perspective what information the Sovrin system
+    manages, how it does it, and the main actors. Basically, it is a public and
+    permissioned blockchain, that stores DIDs and VC schemas.
+    %
+    Some interesting properties (\textbf{Note: the following is based on
+      whitepapers from 2016!}):
+    \begin{itemize}
+    \item Credentials/claims are multi-show.
+    \item The keys used by issuers to produce claims can be rotated. To ensure
+      that verifiers will be able to check credentials that have been issued
+      with a rotated key, old keys are saved. This ``backward compatibility''
+      is an interesting feature for real-world systems to consider.      
+    \item Relationships between users and verifiers are not private:
+      \emph{``Jane has a relationship with a retailer (we can tell since they
+        have her verification key)''}
+    \item Consent receipts: A kind of ``policy'' that is stored in the ledger,
+      which contains the agreements reached between users and service providers
+      (e.g., SP can use Alice's data to do X or Y, only during 30 days). The
+      user can resort to the ledger to track past agreements.      
+    \item Support for public and private attributes. Public attributes are/can
+      be stored in the Sovrin ledger. Private attributes are stored in each
+      user's private ledger: \emph{``One important purpose of the private ledger
+        is to track the time and order that things are written. Hashes of the
+        private ledger can be written to Sovrin's public ledger periodically to
+        provide evidence of Jane's holdings. These are called anchors. Jane can
+        thus generate audit proofs that any particular interaction happened at a
+        particular time without disclosing the details of the interaction.''}
+      Private ledgers can be managed by agencies, but they should be easily
+      exportable to avoid lock-in.
+    \end{itemize}
+  \item \emph{``The Technical Foundations of Sovrin.''}%
+    \footnote{\url{https://www.evernym.com/wp-content/uploads/2017/07/The-Technical-Foundations-of-Sovrin.pdf}}.
+    Describes from a high-level perspective the architecture of the system,
+    mostly focusing on the blockchain network, and related components (like
+    agents and clients). Some identity-related stuff:
+    \begin{itemize}
+    \item To create a new identity from scratch, users have to rely on ``trust
+      anchors'' (i.e., participants of the network that have somehow acquired
+      trust). The new user perform a kind of issuance protocol with this trust
+      anchor, who endorses the new user by registering some information in the
+      ledger. The user can check the trustworthiness of the anchor, and result
+      of the registration, via the ledger. The described process (page 14)
+      resembles the join-issue protocols in GSs and ACs.      
+    \item Brief mention is made to public and private attributes (in page 20),
+      which again are differentiated depending on whether they are: stored in
+      the ledger (public), no matter if they are encrypted/obfuscated or not;
+      or in a private ledger (private). %
+      The document also mentions five types of claims: cleartext claims,
+      encrypted claims, hash signature claims, proof of existence claims, and
+      anonymous credentials. See page 21, although it barely gives an
+      intuition.      
+    \end{itemize}
+  \item \emph{``Why the Verifiable Credentials Community Should Converge on BBS+''}%
+    \footnote{\url{https://www.evernym.com/blog/bbs-verifiable-credentials/}}.
+    This is a blog post by a cryptographer in Evernym, that describes the
+    evolution of Evernym's approach. They initially targetted CL credentials,
+    which they implemented for Sovrin/Indy. Then, they decided to migrate to
+    BBS+, supporting predicates for proofs, and revocation. They seemed to fail.
+    Later, MATTR restricted the approach to selective disclosure (not sure if
+    revocation is included). This is useful to understand the confusion between
+    the terms ZKP-CL vs JSON-LD BBS+. They are just historical: the former is the
+    approach Indy adopted, and they have their own user base and formats;
+    JSON-LD BBS+ is the approach of MATTR, which Evernym (the descendant of
+    Sovrin/Indy) seems to be adopting too.
+  \end{itemize}
+\end{itemize}
+
 %%% Local Variables:

### 2021-12-13 prism-backend/research/single-mnemonic/bip32-etal.tex
Initial content on the single mnemonic research spike. Summarizing BIP32.

\section{An Overview of BIP32-based HD Wallets}
\label{sec:bip32}

Hierarchical Deterministic Wallets (HD wallets, for short) in the cryptocurrency
domain derive from the BIP32 specification%
\footnote{\url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}.
  Last access, December 13th, 2021.}
The motivation behind creating this type of wallets is clear if one thinks about
how typical cryptocurrency systems work: each address is associated with a key
pair and, in order to achieve high security and privacy levels, it is best to
limit the reusage of addresses (thus, key pairs). Therefore, a too high number
of needed key pairs is quickly reached. If each key is generated independently
at random, management becomes too complex -- especially, if several devices
are expected to be synchronised. As a solution to this challenge, a hierachical
tree-based data structure was proposed, in which each parent node can be used to
derive multiple child nodes, deterministically. This approach seems also useful
to foster some sort of separation -- i.e., create sub-trees that are
(computationally) independent from one another, in the sense that a compromise
in one does not lead to a compromise in the other. Typically, the root node
of the tree is derived from a seed encoded as a mnemonic. BIP39%
\footnote{\url{https://github.com/bitcoin/bips/blob/master/bip-0039.mediawiki}.
  Last access, December 13th, 2021.} is the main specification for this purpose.

In this section, we give a brief overview of the BIP32 specification, and
provide a ``full path'' from mnemonic to key pair. To avoid repeating already
well documented processes, the overview will refer to the specifications when
appropriate.
%
In a final subsection, we will also overview how does all this apply to the
Cardano Lightwallet and Atala Prism cases.

\subsection{Main Specifications}

While the main specification is BIP32, it essentially gives the main guidelines
to create HD wallets. To avoid ambiguity leading to incompatible
implementations, BIP43%
\footnote{\url{https://github.com/bitcoin/bips/blob/master/bip-0043.mediawiki}.
  Last access, December 13th, 2021.} and BIP44%
\footnote{\url{https://github.com/bitcoin/bips/blob/master/bip-0044.mediawiki}.
  Last access, December 13th, 2021.} specify how to organize HD wallets so
that the resulting tree structure enables the most common use cases (which, at
least initially, focus on the cryptocurrency scenario). In addition, the
specification that defines how to encode (pseudo-)random bitstrings as
mnemonic is given in BIP39.

\subsection{Main Concepts}

\begin{description}
\item[HD wallet tree structure.] HD wallets are organised as trees, where the
  root node is directly derived from the main seed (typically, a mnemonic-encoded
  random string). We denote the root level with level $0$, and all descendants
  with increasing numbers. A level other than the root level can have an
  arbitrary number of nodes.
\item[(Child) Index.] The child index just identifies how many childs can be (or
  have been) created before the current child, at the current depth of the tree.
  We assume $0$ to be the first index.
\item[Chaincode.] To introduce extra ``non-determinism'' in the way child keys
  are derived from parent keys, part of the pseudo-randomly derived data is
  used as key for pseudo-random derivations of lower levels. This part of the
  derived data is referred to as chaincode. We will denote the chaincode of the
  $j$-th node at level $i$ of the tree with $c_{i,j}$.
\item[Extended keys.] An extended public (resp. private) key is composed by the
  public (resp. private) key and the chaincode.  
\item[Hardened child keys.] A hardened child key can only be derived from the
  parent private key, and the parent key chaincode. 
\item[Non-hardened child keys.] A non-hardened child key can be derived both
  from the parent private and parent public key, and the parent key chaincode.
\end{description}

\paragraph{Hardened vs non-hardened child derivation.}

\paragraph{Isolation of HD partitions.} In the following section, we use
the concept of isolated and non-isolated partitions. This is something that is
only indirectly mentioned in the BIPs and other related works, but which is of
crucial importance in order to limit the impact of compromised keys. Namely,
assume that a child key is derived in non-hardened mode. Then, if the extended
parent public key is leaked, as well as the private (non-extended) child key, it
is possible to extract the parent private key -- and, therefore, all the keys
(private and public; hardened or not) that derive from it. If child keys are
derived in hardened mode, this does not apply. For the sake of clarity, we
illustrate the difference through the diagram in \figref{fig:isolation}.

\begin{figure}[ht!]
  \includegraphics[width=\textwidth]{figures/child_derivation.png}
  \caption{Partition isolation through hardened child derivation. $G$ is the
    base point of the underlying elliptic curve, and $n$ is the order of
    the associated group.}
  \label{fig:isolation}
\end{figure}

Assume that the extended public key $(K_{i,j}, c_{i,j})$ is compromised, along
with its child private non-hardened key $k^{nh}_{(i+1),t}$. Then, it is
straightforward  to recompute the \emph{parent} private key $k_{i,j}$
(indedpendently on whether it was derived in hardened mode or not) as:
$k_{i,j} \leftarrow (K_{(i+1),t}^{nh} - Left(I_{(i+1),t}^{nh})) \bmod n$.
Obviously, given the parent private key $k_{i,j}$, it is straightforward to
derive all its descendants (hardened or not), as well as recursively apply the
same strategy, should any ancestor be also compromised.

\subsection{From Mnemonic to Key Pairs: High-level Overview}

The following description is based on BIP39 for the processing of mnemonics,
and BIP44 (which is a restriction to BIP43 and BIP32) for the structure of
an HD wallet.

\paragraph{From (pseudo-)random bitstrings to mnemonics, and back.}

\paragraph{Layer 1: \emph{isolated} partitions per \texttt{purpose}}

\paragraph{Layer 2: \emph{isolated} partitions per \texttt{coin type}}

\paragraph{Layer 3: \emph{isolated} partitions per \texttt{account}}

\paragraph{Layer 4: \emph{non-isolated} partitions per \texttt{visibility}}

\paragraph{Layer 5: Final key pairs}

\subsection{Comments on a Recent Security Evaluation}

\cite{def+21}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "single-mnemonic"
%%% End:

### 2021-12-13 prism-backend/research/single-mnemonic/introduction.tex
Initial content on the single mnemonic research spike. Summarizing BIP32.

--- 2021-10-27 prism-backend/research/soa_review/introduction.tex
@@
 
-Privacy is a human right \needcite. It is also one of the most threatened ones
-as a consequence of digitalization and hyperconnectivity \needcite. Maybe one
-of the reasons behind this is that, on many occasions, it conflicts with another
-human right: security \needcite. The most representative occasion in which this
-happens is when we, as individuals%
-\footnote{This, of course, also happens when authenticating machines -- as they
-  carry to some extent information of some individual(s).}%
-, want to gain access to some (possibly
-digital) good or service. In that context, one has to prove having the legitimate
-rights to access that good or service. However, in the process of doing so, the
-entity verifying that we have the rights, typically learns something about us,
-like our real name. This has been traditionally fine in physical systems, as the
-impact was mostly local. However, with the advent of digitalization and
-hyperconnectivity, this usually means that something related to our identity is
-being logged in some server, who knows where and with what security controls,
-and probably vulnerable to a number of criminal activities \needcite.
-
-Of course, the cryptographic community has not been stranger to the need of
-providing satisfactory solutions that enable both privacy and security. We
-refer to all works trying to address to this need as \emph{privacy-preserving
-  authentication} mechanisms. For decades, a huge amount of research, with many
-variations, has been produced in the field. Sadly, still with limited impact in
-the real world. Within this context, the goal of this review is manyfold: from a
-practical perspective, serve
-as a hub to security and privacy professionals that may find themselves in need
-to balance privacy and security in some real world application; from a more
-academic one, provide a (somehow detailed) overview of the vast amount of
-literature in the field, which is already overwhelming enough to make it hard
-to find the most appropriate variant of some property we may find ourselves
-in need to provide; and finally, attempt to throw some insight into why such a
-vast academic work has so far failed to gain more real world adoption.
-
-In order to achieve this, %
-we go over the main cryptographic primitives used to build privacy-preserving
-authentication mechanisms. For all of them, we first provide a high-level
-intuition of the approach to protect users' privacy. Then, we overview the
-most prominent security models since their inception, and complement this
-with some relevant variations concerning the provided functionality. We also
-summarise the main results from an efficiency standpoint, and the main
-challenges found so far both in theory and practice. To gain some initial
-insight into the academic impact of each primitive, we provide (approximate)
-numbers on publications in the main cryptography, security and privacy venues.
-Finally, with a more practical mindset, we overview the applications that each
-primitive has ``in theory'', and the extent to which they have been deployed
-in the real world.
-
-\note{Argue/mention that focus is on primitives that can be used for signing.
-  This therefore excludes protocols that can only be used for anonymous
-  authentication, but not anonymous singing per se (e.g., PAKE, PASTA, PESTO...
-  and probably also Nymble, PEREA, BLAC...)}
-
-\note{Create a graph of relationships between basic primitives and their
-  applications. E.g., much of
-  the work in SRP group signatures and DAA seems to be derived from randomizable
-  signatures (which, afaik, are also a foundation for anonymous credentials).}
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "sok-privsig"
+%%% TeX-master: "single-mnemonic"
 %%% End:

### 2021-12-13 prism-backend/research/single-mnemonic/single-mnemonic.tex
Initial content on the single mnemonic research spike. Summarizing BIP32.

--- 2021-11-09 prism-backend/research/soa_review/soa-review.tex
@@
-\documentclass{llncs}%[10pt]{llncs}
+\documentclass{llncs}
 \pagestyle{plain}
@@
 logic,ff,mm,primitives,events,complexity,asymptotics,keys]{cryptocode}
-\usepackage{amssymb}
+%\usepackage{amssymb}
 \usepackage{xspace}
-\usepackage[normalem]{ulem}
+%\usepackage[normalem]{ulem}
 \usepackage{hyperref}
 
-\title{State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication}
+\title{Research Spike: Evaluation of Using a Single Mnemonic both
+  for Cryptocurrency and Identity Wallets}
 \author{}
@@
 \begin{abstract}
-	\textbf{DISCLAIMER}: Please, keep in mind that, as of now, this document
-	basically contains a research log in the shape of personal notes. Do not take 
-	anything written here as ground truth.
+  \comment{\textbf{DISCLAIMER}: Please, keep in mind that this is a working
+    draft. Its main use in its current state is to foster debate on the topics
+    it deals with. Do not take anything written here as ground truth.}  
 \end{abstract}
@@
 \input{introduction.tex}
-\input{gs.tex}
-\input{abs.tex}
-\input{ac.tex}
-\input{daa.tex}
-\input{other.tex}
+\input{bip32-etal.tex}
+\input{idwal.tex}
 \input{discussion.tex}
@@
 
-\section{TODOs}
-
-General/pending doubts and tasks:
-
-\begin{itemize}
-\item Many constructions of ACs and GSs seem to be built using the same
-  approach: an issuer and a user interact so that the latter receives a signature
-  from the former; then the user employs that signature to do something else (in
-  ACs, prove attributes; in GSs, produce further signatures). Still, the typical
-  security models are different. Concretely, GSs have a very well established
-  model, but ACs don't. It also ``bothers'' me that none of the AC models I've
-  seen cover something similar to non-frameability, nor traceability, but just
-  include conventional unforgeability properties. Why is this?
-\end{itemize}
-
 \bibliographystyle{splncs04}
-\bibliography{soa-review}
+\bibliography{single-mnemonic}
 

### 2021-12-14 prism-backend/research/single-mnemonic/bip32-etal.tex
Completed section on overview of BIP32 et al.

@@
 
-While the main specification is BIP32, it essentially gives the main guidelines
+While the main specification is BIP32, it essentially gives the basic guidelines
 to create HD wallets. To avoid ambiguity leading to incompatible
@@
   derived data is referred to as chaincode. We will denote the chaincode of the
-  $j$-th node at level $i$ of the tree with $c_{i,j}$.
+  $j$-th node at level $i$ of the tree with $c_{i,j}$. This data should be kept
+  secret; otherwise, entire subtrees can be compromised.
 \item[Extended keys.] An extended public (resp. private) key is composed by the
@@
 
-\paragraph{Hardened vs non-hardened child derivation.}
+\paragraph{Hardened vs non-hardened child derivation.} Basically, child nodes
+are derived as rerandomizations of their parent node private key. The
+pseudo-random data used for rerandomization can be derived from the parent
+private extended key, or from the parent public extended key. The former case is
+referred to as hardened derivation, and the latter as non-hardened derivation.
+In a nutshell, this means that hardened child keys (private or public) can only
+be derived from their parent private key, but not from their parent public key.
+Naturally, child private keys can only be derived from parent private keys.
 
-\paragraph{Isolation of HD partitions.} In the following section, we use
-the concept of isolated and non-isolated partitions. This is something that is
+For self-containedness, \figref{fig:childderivation} shows the different
+algorithms to derive child keys from a parent keys, excluding some details. For
+the full algorithms, we refer to BIP32.
+
+\begin{figure}[ht!]
+  \begin{minipage}[t]{0.55\textwidth}
+    \procedure{$prv2HardChild$ \pccomment{Parent private key $\rightarrow$ $i$-th Child hardened key pair}}{
+      \pcind I \gets HMAC(c_{par}, k_{par}, i) \\
+      \pcind k^h \gets (k_{par} + Left(I)) \bmod n; K^h \gets k^hG; c^h \gets Right(I) \\
+      \pcind \pcreturn (k^h,K^h,c^h) \\
+    }
+    \procedure{$prv2NonHardChild$ \pccomment{Parent private key $\rightarrow$ $i$-th Child non-hardened key pair}}{    
+      \pcind I \gets HMAC(c_{par}, K_{par}, i) \\
+      \pcind k^{nh} \gets (k_{par} + Left(I)) \bmod n; K^{nh} \gets k^{nh}G; c^{nh} \gets Right(I) \\
+      \pcind \pcreturn (k^{nh},K^{nh},c^{nh}) \\      
+    }
+    \procedure{$pub2NonhardPubChild$ \pccomment{Parent public key $\rightarrow$ $i$-th Child non-hardened public key}}{      
+      \pcind I \gets HMAC(c_{par}, K_{par}, i) \\
+      \pcind K^{nh} \gets Left(I)G + K_{par}; c^{nh} \gets Right(I) \\
+      \pcind \pcreturn (K^{nh},c^{nh}) 
+    }    
+  \end{minipage}
+  \caption{Algorithms for child derivation. $k_{par},K_{par},c_{par}$ denote the
+    parent's public key, private key, and chaincode, respectively. $k,K,c$
+    denote the resulting child's private key, public key, and chaincode. $h$ or
+    $nh$ superscripts denote hardened or non-hardened derivation. $Left$
+    (resp. $Right$) divides a bitstring in two equal parts, and takes the left
+    (resp. right) half. The result of both $Left$ and $Right$ can be interpreted
+    as a scalar, and thus multipled by points in the elliptic curve, such as $G$,
+    which is the base point, or public keys, which also are points in the
+    curve.}
+  \label{fig:childderivation}
+\end{figure}
+
+\paragraph{Isolation of HD wallet subtrees.} In the following section, we use
+the concept of isolated and non-isolated subtrees. This is something that is
 only indirectly mentioned in the BIPs and other related works, but which is of
@@
 assume that a child key is derived in non-hardened mode. Then, if the extended
-parent public key is leaked, as well as the private (non-extended) child key, it
-is possible to extract the parent private key -- and, therefore, all the keys
-(private and public; hardened or not) that derive from it. If child keys are
-derived in hardened mode, this does not apply. For the sake of clarity, we
-illustrate the difference through the diagram in \figref{fig:isolation}.
+parent public key is leaked, as well as the private (non-extended) non-hardened
+child key, it is possible to extract the parent private key -- and, therefore,
+all the keys (private and public; hardened or not) that derive from it. If child
+keys are derived in hardened mode, this does not apply. For the sake of clarity,
+we illustrate the difference through the diagram in \figref{fig:isolation}.
 
@@
   \includegraphics[width=\textwidth]{figures/child_derivation.png}
-  \caption{Partition isolation through hardened child derivation. $G$ is the
+  \caption{Sub-tree isolation through hardened child derivation. $G$ is the
     base point of the underlying elliptic curve, and $n$ is the order of
@@
 
-Assume that the extended public key $(K_{i,j}, c_{i,j})$ is compromised, along
-with its child private non-hardened key $k^{nh}_{(i+1),t}$. Then, it is
-straightforward  to recompute the \emph{parent} private key $k_{i,j}$
-(indedpendently on whether it was derived in hardened mode or not) as:
+For instance, assume that the extended public key $(K_{i,j}, c_{i,j})$ is
+compromised, along with its child private non-hardened key $k^{nh}_{(i+1),t}$.
+Then, it is straightforward  to recompute the \emph{parent} private key
+$k_{i,j}$ (independently on whether it was derived in hardened mode or not) as:
 $k_{i,j} \leftarrow (K_{(i+1),t}^{nh} - Left(I_{(i+1),t}^{nh})) \bmod n$.
 Obviously, given the parent private key $k_{i,j}$, it is straightforward to
-derive all its descendants (hardened or not), as well as recursively apply the
-same strategy, should any ancestor be also compromised.
+derive all its descendants (hardened or not), as well as possibly and
+recursively apply the same strategy, if the just recovered parent key was
+derived in non-hardened mode.
 
@@
 The following description is based on BIP39 for the processing of mnemonics,
-and BIP44 (which is a restriction to BIP43 and BIP32) for the structure of
-an HD wallet.
+and BIP44 (which is a restriction of BIP43 and BIP32) for general structure of
+an HD wallet, which we depict in \figref{fig:bip44-tree}.
 
-\paragraph{From (pseudo-)random bitstrings to mnemonics, and back.}
+\begin{figure}[ht!]
+  \includegraphics[width=\textwidth]{figures/bip44_tree.png}
+  \caption{Basic tree structure of a BIP44-based HD wallet.}
+  \label{fig:bip44-tree}
+\end{figure}
 
-\paragraph{Layer 1: \emph{isolated} partitions per \texttt{purpose}}
+\paragraph{From (pseudo-)random bitstrings to mnemonics, and back.} %
+Mnemonics encode randomness in human-readable form. BIP39 is the main
+specification for this. Roughly, between 128 and 256 random bits (in multiples
+of 32) are generated, a checksum (the first few bits of a hash of these random
+bits) is concatenated, and the result is divided in chunks of 11 bits. Each of
+these chunks is used as index to a predefined dictionary of words. The result
+is a mnemonic of 12 to 24 words. To convert from mnemonic to random bits, just
+the inverse process has to be followed (verifying the checksum).
 
-\paragraph{Layer 2: \emph{isolated} partitions per \texttt{coin type}}
+Given the mnemonic, it is converted back into a bitstring as just described.
+Then, this bitstring is processed with an HMAC function, using the string
+``Bitcoin seed'' as key \needcite~based on SHA512 -- hence producing 512 bits of
+output. The first 256 bits are set as master secret key, and the last 256 bits
+as master chaincode (i.e., $k_{0,0}$ and $c_{0,0}$, in our previous notation).
 
-\paragraph{Layer 3: \emph{isolated} partitions per \texttt{account}}
+\paragraph{Layer 1: \emph{isolated} subtrees per \texttt{purpose}} %
+The first layer of a BIP44-compatible HD wallet is composed of up to $2^{31}$
+nodes of hardened childs: i.e., layer 1 is composed of childs $(1,2^{31})$
+to $(1,2^{62}-1)$, where the second element in the pair is the $i$ value used
+in the child derivation processes, and denotes for what ``purpose'' the
+descendant keys will be used -- this roughly translates to the system (e.g.,
+Bitcoin, Cardano... or even non-blockchain systems, in theory).
 
-\paragraph{Layer 4: \emph{non-isolated} partitions per \texttt{visibility}}
+Note that, being layer 1 computed in hardened mode, a private key compromise
+of one node in layer 1 does not affect the master node, nor other layer 1
+siblings. Hence, this is an ``isolated'' subtree, according to our terminology.
 
-\paragraph{Layer 5: Final key pairs}
+For BIP44-compatible wallets, the expected index is $44$. Cardano, since
+the Shelley era, uses $1852$%
+\footnote{\url{https://cips.cardano.org/cips/cip1852/}. Last access, December
+  14th, 2021.}. Note that, since these are hardened indexes, the encoding
+rules translate this into $1852+2^{31}$ (resp. $44+2^{31}$ for BIP44); see
+BIP44 for more details.
+
+\paragraph{Layer 2: \emph{isolated} subtrees per \texttt{coin type}} %
+The second layer is again composed of up to $2^{31}$ nodes of hardened childs:
+i.e., layer 2 is composed of childs $(2,2^{31})$ to $(2,2^{62}-1)$ per each child
+node of layer 1. In theory, up to $2^{31}*2^{31}=2^{62}$ second-level nodes can
+coexist in the same HD wallet. The aim of the second level is for any HD wallet
+to be able to support multiple types of coins. E.g., so that the same mnemonic
+can be used to derive key pairs for Bitcoin, Cardano, etc.
+
+Note that, being layer 2 computed in hardened mode, a private key compromise
+of one node in layer 2 does not affect its parent in layer 1, nor other layer 2
+siblings. Hence, this is an ``isolated'' subtree, according to our terminology.
+
+Although not mandatory, each coin is expected to have an assigned coin type
+index. The complete list of reserved indexes is available in SLIP44%
+\footnote{\url{https://github.com/satoshilabs/slips/blob/master/slip-0044.md}.
+  Last access, December 14th, 2021.}.
+
+\paragraph{Layer 3: \emph{isolated} subtrees per \texttt{account}} %
+The third layer is again composed of up to $2^{31}$ nodes of hardened childs:
+i.e., layer 3 is composed of childs $(3,2^{31})$ to $(3,2^{62}-1)$ per each child
+node of layer 2. In theory, up to $2^{3*31}=2^{93}$ third-level nodes can
+coexist in the same HD wallet. The aim of the third level is to allow the HD
+wallet user to maintain many accounts per coin type. E.g., the same mnemonic
+seed could be used for up to $2^{31}$ key pairs for Cardano addresses.
+
+Again, note that being layer 3 computed in hardened mode, a private key compromise
+of one node in layer 3 does not affect its parent in layer 2, nor other layer 3
+siblings. Hence, this is an ``isolated'' subtree, according to our terminology.
+
+\paragraph{Layer 4: \emph{non-isolated} subtrees per \texttt{change}}
+According to BIP32, the fourth layer can be composed of up to  $2^{31}$ nodes of
+non-hardened childs: i.e., layer 4 can be composed of childs $(4,0)$ to
+$(4,2^{31}-1)$ per each child node of layer 3. However, in BIP44, only
+non-hardened childs 0 and 1 are used: i.e., each node of layer 3 will only have
+non-hardened childs $(4,0)$ and $(4,1)$. This layer is used to differentiate
+whether the descendant nodes will be used as a change addresses, or not. I.e.,
+child $(4,0)$ will \emph{not} be used for receiving change in payments, and
+therefore is expected to be associated to an address that may be published
+outside of the wallet; while child $(4,1)$ is expected to be used for receiving
+change in payments.
+
+Note that, since the 4th layer is not derived in hardened mode, if the private
+key of the $(4,0)$ child of some layer 3 node is compromised along with the
+extended public key of the node at layer 3, then the entire subtree of that
+layer 3 node will be compromised (but not the subtrees of other layer 3 nodes,
+as layer 3 is derived in hardened mode). That is, all the addresses (change or
+not) of an specific account of some cryptocurrency, will be compromised.
+
+\paragraph{Layer 5: \emph{non-isolated} final key pairs (\texttt{index})} %
+The fifth and last layer is used to derive final key pairs. It can be composed
+of up to $2^{31}$ non-hardened nodes: i.e., every change (and non-change) node
+of level 4 may have level 5 childs from $(5,0)$ to $(5,2^{31}-1)$.
+
+Note that, since layer 4 nodes are derived in non-hardened mode, if a layer 5
+private key is compromised, as well as its parent extended public key of layer
+4, then the whole layer 4 subtree will be compromised. Furthermore, if the
+layer 3 extended public key from which the layer 4 parent derives is also
+compromised, the entire account will be compromised too, as layer 4 is also
+derived in non-hardened mode.
+
+\subsection{Variations in the Cardano Ecosystem}
+
+\paragraph{Lightwallet.}
+
+\paragraph{Atala.}
 

### 2021-12-16 prism-backend/research/single-mnemonic/bip32-etal.tex
Added some extra descriptions on BIP44 and Cardano & Atala variations.

@@
 
-\paragraph{Lightwallet.}
+\paragraph{Lightwallet.} HD wallets in Cardano are mostly BIP44-compatible
+wallets, with the exception that the used elliptic curve is Ed25519 \needcite,
+instead of Secp256k1 \needcite, like Bitcoin's BIP32 (and thus, BIP44). This
+difference is marked by using index 1852 for hardened child derivation at
+layer 1 (purpose level), as specified in CIP1852%
+\footnote{\url{https://cips.cardano.org/cips/cip1852/}. Last access, December
+  15th, 2021.}.
 
-\paragraph{Atala.}
+\paragraph{Atala.} HD wallets in Atala follow a slightly different tree
+organisation, layer-wise. Namely, it defines 4 layers: root, DID number, key
+type, and index. All child derivations are done in hardened mode. The elliptic
+curve is Secp256k1, as BIP44. See the key derivation document for details%
+\footnote{\url{https://github.com/input-output-hk/atala-prism/blob/master/prism-backend/docs/protocol/key-derivation.md}. Last access December 15th, 2021. \textbf{WARNING!
+    Internal link!}}.
 

### 2021-12-18 prism-backend/research/single-mnemonic/bip32-etal.tex
Added content on PoS wallets, and some conclusions on security and privacy considerations.

--- 2021-12-14 prism-backend/research/single-mnemonic/bip32-etal.tex
@@
 Then, this bitstring is processed with an HMAC function, using the string
-``Bitcoin seed'' as key \needcite~based on SHA512 -- hence producing 512 bits of
+``Bitcoin seed'' as key based on SHA512 -- hence producing 512 bits of
 output. The first 256 bits are set as master secret key, and the last 256 bits
@@
 
-\subsection{Variations in the Cardano Ecosystem}
+\subsection{Comments on a Recent Security Evaluation of BIP32 Wallets}
 
-\paragraph{Lightwallet.}
+Very recently, \cite{def+21} was published in CCS'21, a major applied
+cryptography and security conference. The paper builds on prior work from
+2019 \cite{dfl19}, and analyses the security of BIP32-like wallets. For this purpose,
+the authors first model and analyse (additively) re-randomizable signatures
+built on ECDSA. They prove security, as long as every message is signed at
+most once, at the cost of a security loss proportional to the number of
+signature re-randomizations performed by the adversary\footnote{They also prove
+  this security loss to be unavoidable with additive re-randomization, although
+  I have not checked that proof.}. Then, they build a model for HD wallets,
+and provide a generic construction using additively re-randomizable signatures.
+The properties considered in this HD wallet model are unlinkability and
+unforgeability (restricted to only one signature per message). The unlinkability
+property expects that an adversary cannot distinguish (uncompromised) keys
+derived from a non-hardened node, from keys derived from keys derived from an
+independent master key. The unforgeability property is the usual one, excluding
+the one message restriction (which seems reasonable, as long as new randomness
+is included in every signed message); namely, the adversary should not be able
+to create a valid signature under a hardened key that has not been compromised,
+or a non-hardened key.
 
-\paragraph{Atala.}
+An interesting extension is mentioned, to achieve forward unlinkability in case
+of compromise of non-hardened node public key and chaincode. Namely, if that
+happens, the adversary will be able to derive the public extended keys for
+all the subtree, which breaks unlinkability for the subtree. The proposal is to
+keep a state along with every node. On every child derivation in the tree, the
+state of the existing nodes is refreshed. Then, in case of compromise of a
+node, the keys previously derived in subtrees of it are not affected (assuming
+that previous states are securely erased).
 
-\subsection{Comments on a Recent Security Evaluation}
+Building on the proven security of the additively re-randomizable ECDSA, they
+prove security of their generic construction, which now also depends on the
+number of leaked hardened keys. Assuming that roughly $1\%$ of the total number
+of (additively re-randomized) hardened keys are compromised, the estimated
+security level for ECDSA of 256-bit keys (hence, 128-bit security) is 91-bit
+security.
 
-\cite{def+21}
+\paragraph{Discussion.} %
+The model does seem to follow BIP32, but \textbf{assuming a hot/cold approach}.
+Concretely, they assume that non-hardened secret keys are always kept in a cold
+wallet, and therefore cannot be compromised. On the other hand, hardened secret
+keys are assumed \emph{not} to be stored in cold wallets, and therefore can be
+compromised (this is reflected in the model with corresponding oracles or lack
+thereof). The underlying reasoning being that hardened derivation is used to
+share keys with not fully trusted entities (e.g., employees in a company). Also,
+hardened keys are assumed to be leafs (i.e., keys used directly for signing); or,
+alternatively, roots of independent subtrees. Under this modelling, if the
+partially trusted entity leaks the hardened key, this would only affect the
+security of its subtree (if it exists), but certainly not siblings or ancestors.
+However, this may not be fit for BIP44 wallets, where hardened derivation is
+expected to be used directly for the first 3 layers, and the leaves are actually
+computed with non-hardened derivation.
+
+The property of forward unlinkability is interesting for identity-related
+wallets.
 

### 2021-12-18 prism-backend/research/single-mnemonic/discussion.tex
Initial content on the single mnemonic research spike. Summarizing BIP32.
Added content on PoS wallets, and some conclusions on security and privacy considerations.

--- 2021-10-27 prism-backend/research/soa_review/discussion.tex
@@
 
+From a theoretical point of view, it seems very reasonable to derive all
+keys, even for different purposes (payments, staking, or identities) from
+the same mnemonic. However, there are some aspects that may need careful
+consideration, as they may have impact in the overall security and privacy
+properties of the wallet (and related systems).
+
+\paragraph{Domain separation when different cryptosystems are
+  necessary.} %
+As mentioned, Cardano uses EdDSA (i.e., it is based on Ed25519 curve),
+while Atala uses ECDSA with Secp256k1. It is \emph{not} a good idea%
+\footnote{I have not been able to find a concrete paper that describes
+  some concrete related attack or gives some impossibility result for
+  proving security under this circumstance but, at the least, it seems to
+  be folklore knowledge. See Lindell's answer at
+  \url{https://crypto.stackexchange.com/a/54666/52362} for instance.
+  \cite{dlp12+,thorm21} seem good references to study this topic further, if
+  needed.} to use the same key for different cryptosystems, nor for different
+curves, even though ``structurally'' it may be possible (e.g., in EdDSA and
+ECDSA, private keys are 32-byte random numbers). However, this is easily
+avoidable by ensuring domain separation in the key derivation functions that
+are applied on the common seed. Since this would be handled by the
+
+\paragraph{Ensure a correct hierarchical key derivation strategy.} %
+We need to take into account what specific usage we expect from the wallets
+and, from there, define hierarchical derivation rules that ensure a correct
+separation. For instance, related to the previous paragraph, we should make
+sure that keys that are aimed to be used in different cryptosystems, are
+derived in tree branches that ensure domain separation (just using a
+different \texttt{purpose} branch, or \texttt{coin type} branch, would probably
+be enough). Similarly, one needs to consider if specific subtrees are expected
+to be used in an standalone manner, even probably by different (but related)
+entities. For instance, different faculties of a university may need to maintain
+their own subrees for the sake of efficiency (i.e., each one independently
+deriving keys as needed). But then, compromises to one of them should not
+affect the other. Again, this can be easily achieved using hardened
+derivation in BIP44 slang (e.g., at the \texttt{account} level). From this
+point of view, a formalization along the lines of \cite{def+21} would be
+desirable, but the one given there is probably too strict (as, for instance,
+it assumes that hardened nodes are leaves of the tree, and secret key
+compromise of non-hardened nodes, is not possible.)
+
+\paragraph{Malleability considerations when combining multiple
+  attributes into one address.} %
+Are the keys for the different purposes going to be used \emph{only} in a
+standalone manner? Or, rather, it can be expected that they are somehow
+encoded and distributed jointly? The latter seems to be the case for PoS
+wallets, which are expected to be used in the Cardano ecosystem. As pointed
+out by \cite{kkl20}, naive encoding of keys with different purposes, into
+a single address, may enable certain (malleability) attacks.
+
+\paragraph{Careful consideration of extra security properties.} %
+The main related work analysed so far\footnote{BIP32, BIP44, \cite{def+21}
+  and, partially, \cite{kkl20}.} analyses the security of either BIP44
+wallets, or PoS wallets. The introduction of identity-related (frequently
+associated to actual people) data may require additional properties, only
+mentioned in these works (or not considered, as in the BIPs). For instance,
+some sort of forward security will be very desirable. While, for the case of
+payments or staking, the impact of a compromise (either of a leaf node --
+i.e., a key -- or a complete subtree) can be mitigated by prompt detection
+and transfer of funds to an uncompromised address, this may be harder for
+keys representing in some way real world identities. Most probably, the
+latter will frequently be long-lived keys, that also can, in turn, be used
+to issue further identities (e.g., as in the case of identity providers).
+Thus, the consequences of a compromise may be more cumbersome to address
+(re-issuing credentials, distributing revocation lists, etc.) and,
+consequently, it seems desirable to look for constructions that give some
+sort of guarantee about the security of keys produced at time $t' < t$, if a
+compromise happens at time $t$.
+
+Also, it cannot be discarded that further desirable privacy or security
+properties arise, as we get more familiar with the targetted use cases.
+
+\subsection{Further related work}
+
+There seems to be a large body of related research, which is specially
+growing lately (probably, due to the rise of cryptocurrencies). Here,
+I just include some of the main references I've come across for
+self-bookkeeping (besides \cite{kkl20} and \cite{def+21}, already
+mentioned in earlier sections). Note that they, in turn, include references
+to further related work.
+
+\begin{itemize}
+\item ``Arcula: A Secure Hierarchical Deterministic Wallet for Multi-asset
+  Blockchains'', \cite{lfa20}.
+\item ``Simple, Efficient and Strongly KI-Secure Hierarchical Key Assignment
+  Schemes'', \cite{fpp13}.
+\item ``A Formal Treatment of Deterministic Wallets'', \cite{dfl19}.
+\end{itemize}
+
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "sok-privsig"
+%%% TeX-master: "single-mnemonic"
 %%% End:

### 2021-12-18 prism-backend/research/single-mnemonic/iowal.tex
Added content on PoS wallets, and some conclusions on security and privacy considerations.

\section{IO Ecosystem Specifics}
\label{sec:io}

\paragraph{Lightwallet.} HD wallets in Cardano are mostly BIP44-compatible
wallets, with the exception that the used elliptic curve is Ed25519,
instead of Secp256k1, like Bitcoin's BIP32 (and thus, BIP44). This
difference is marked by using index 1852 for hardened child derivation at
layer 1 (purpose level), as specified in CIP1852%
\footnote{\url{https://cips.cardano.org/cips/cip1852/}. Last access, December
  15th, 2021.}.

\paragraph{Atala.} HD wallets in Atala follow a slightly different tree
organisation, layer-wise. Namely, it defines 4 layers: root, DID number, key
type, and index. All child derivations are done in hardened mode. The elliptic
curve is Secp256k1, as BIP44. See the key derivation document for details%
\footnote{\url{https://github.com/input-output-hk/atala-prism/blob/master/prism-backend/docs/protocol/key-derivation.md}. Last access December 15th, 2021. \textbf{WARNING!
    Internal link!}}.

\paragraph{Related effots.} There seems to be an effort to analyse the security
of wallets that manage addresses combining payment and staking keys \cite{kkl20}.
These wallets are referred to as PoS wallets. The paper identifies a series of
malleability attacks, depending on how the addresses are derived from the
associated staking and payment keys. A core wallet functionality is proposed,
and a base protocol realizing that functionality is given. While the proposal
seems to be somehow compatible with BIP44 wallets, the proposal seems to be
somehow orthogonal to the way keys are derived -- instead, they focus on how
to generate addresses, and check that produced/received addresses are correct.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "single-mnemonic"
%%% End:

### 2021-12-21 prism-backend/research/single-mnemonic/discussion.tex
Fixed typo.
Added comments on diffs w/ sec. model of CCS'21 paper, and interoperability.

@@
 avoidable by ensuring domain separation in the key derivation functions that
-are applied on the common seed. Since this would be handled by the
+are applied on the common seed. This is an important concern on its own; yet,
+it should be addressed natively through the considerations in the next
+paragraph.
 
@@
 
+\paragraph{Concrete differences in prior security analysis} %
+The security analysis in \cite{def+21} is on BIP32, not BIP44. While BIP44
+is actually a subset of BIP32, it further specifies it in concrete ways
+that may alter the result of the analysis. For instance, \cite{def+21}
+assumes that non-hardened nodes are leaves of the tree (which, alternatively,
+can be seen as roots in new trees). However, in BIP44 the leaves are
+non-hardened nodes, and intermediate nodes are mostly hardened. Yet another
+possible source of discrepancy is that the analysis assumes that non-hardened
+nodes are maintained in a hot/cold wallet setting and, thus, the private keys
+cannot be compromised. This assumption may not hold for all use cases, and
+that would change completely the security reasoning. If we want to determine
+the concrete security level we want/need in some specific use cases that differ
+from the analysis of \cite{def+21} as mentioned above, a new model might be
+necessary.
+
 \paragraph{Careful consideration of extra security properties.} %
 The main related work analysed so far\footnote{BIP32, BIP44, \cite{def+21}
-  and, partially, \cite{kkl20}.} analyses the security of either BIP44
-wallets, or PoS wallets. The introduction of identity-related (frequently
-associated to actual people) data may require additional properties, only
-mentioned in these works (or not considered, as in the BIPs). For instance,
+  and, partially, \cite{kkl20}.} study the security of either BIP32
+wallets for payments, or PoS wallets. The introduction of identity-related
+(frequently associated to actual people) data may require additional properties,
+only mentioned in these works (or not considered, as in the BIPs). For instance,
 some sort of forward security will be very desirable. While, for the case of
@@
 properties arise, as we get more familiar with the targetted use cases.
+
+\paragraph{On ``generic'' interoperability issues.} %
+Interoperability can mean many things. Hence, in this discussion, we restrict
+to the structure of the (hierarchically and deterministically) produced tree,
+and on the mnemonic length, which are two differing aspects in Atala and
+Cardano (lightwallet). On the length of the mnemonic, Atala uses 12-word
+mnemonics, while Cardano uses 24 words. According to BIP39, 12 words encode
+128 bits of entropy, and 24 words encode 256. Taking into account that ECDSA
+(in the case of Atala) provides a security level of roughly half of the size
+of the key, and that the deterministic approach to derive keys from the seed
+(HMAC-SHA512) does not amplify entropy \cite{rfc5869}, it is advisable to move
+to 24-word mnemonics. Even more, considering the analysis of \cite{def+21},
+that concludes that the construction of HD wallets based on additively
+re-randomized ECDSA results in a security loss of 31 bits.
+
+Related to the structure of the tree, it is worth mentioning that the Cardano
+light wallet uses the conventional BIP44 hierarchy, composed of a 6-levels tree
+(including the master seed), where the first four levels are derived in
+hardened mode, and the last one in non-hardened mode; on the other hand, Atala
+uses a 4-levels tree (again, including the master seed), all of them derived
+in hardened mode. Essentially, the Atala wallet ``prunes'' the last two levels.
+While the format of the produced keys is of course the same (they are just
+random bitstrings), this discrepancy may lead to issues implementation-wise,
+that should be further evaluated.
 

### 2021-12-22 prism-backend/research/single-mnemonic/bip32-etal.tex
Added comments and refinements based on yesterday's sync.

@@
 
+\paragraph{Notation.} It is frequent that the values used to derive keys in
+the different layers are written in a short form like \texttt{m/a'/b'/c'/d'/e/f},
+where \texttt{m} denotes the master seed (mnemonic); and each value between
+bars is the number used to derive the key for the node at the corresponding
+layer, where a tilded value denotes hardened derivation, and a non-tilded value
+denotes non-hardened derivation. For instance, in the previous path, \texttt{a'}
+denotes that the value \texttt{a} is used to derive, in hardened mode, the second
+level of the path; or the value \texttt{f}  is used to derive, in non-hardened
+mode, the last node in the path.
+
 \subsection{Comments on a Recent Security Evaluation of BIP32 Wallets}

### 2021-12-22 prism-backend/research/single-mnemonic/discussion.tex
Added comments and refinements based on yesterday's sync.

--- 2021-11-09 prism-backend/research/soa_review/discussion.tex
@@
 
-Interesting topic for discussion, which applies mostly for ACs, but probably
-to most other equivalent tools: we have tools that provide a (reasonably
-complete and) secure way to authenticate in a privacy-preserving manner.
-However, what do we do after such authentication takes place? E.g., it is of
-little use to employ an AC to log into an online service, if that service
-will learn all about us after we have anonymously authenticated. How does
-privacy-preserving authentication improve the situation even in that case?
-Is there some way in which we can help avoid that?
+From a theoretical point of view, it seems very reasonable to derive all
+keys, even for different purposes (payments, staking, or identities) from
+the same mnemonic. \secref{ssec:unification}, listed a series of topics
+that should be taken into account prior to unifying Cardano and Atala
+wallets under the same mnemonic, to avoid security pitfalls. In addition to
+those,  there are also some aspects that may need careful consideration, as they
+may have impact in the overall security and privacy properties of the wallet
+(and related systems).
+
+\paragraph{Malleability considerations when combining multiple
+  attributes into one address.} %
+Are the keys for the different purposes going to be used \emph{only} in a
+standalone manner? Or, rather, it can be expected that they are somehow
+encoded and distributed jointly? The latter seems to be the case for PoS
+wallets, which are expected to be used in the Cardano ecosystem. As pointed
+out by \cite{kkl20}, naive encoding of keys with different purposes, into
+a single address, may enable certain (malleability) attacks.
+
+\paragraph{Concrete differences in prior security analysis.} %
+The security analysis in \cite{def+21} (which is one of the main references
+used in this research spike) is on BIP32, not BIP44. While BIP44
+is actually a subset of BIP32, it further specifies it in concrete ways
+that may alter the result of the analysis. For instance, \cite{def+21}
+assumes that non-hardened nodes are leaves of the tree (which, alternatively,
+can be seen as roots in new trees). However, in BIP44 the leaves are
+non-hardened nodes, and intermediate nodes are mostly hardened. Yet another
+possible source of discrepancy is that the analysis assumes that non-hardened
+nodes are maintained in a hot/cold wallet setting and, thus, the private keys
+cannot be compromised. This assumption may not hold for all use cases, and
+that would change completely the security reasoning. If we want to determine
+the concrete security level we want/need in some specific use cases that differ
+from the analysis of \cite{def+21} as mentioned above, a new model might be
+necessary.
+
+\paragraph{Careful consideration of extra security properties.} %
+The main related work analysed so far\footnote{BIP32, BIP44, \cite{def+21}
+  and, partially, \cite{kkl20}.} study the security of either BIP32
+wallets for payments, or PoS wallets. The introduction of identity-related
+(frequently associated to actual people) data may require additional properties,
+only mentioned in these works (or not considered, as in the BIPs). For instance,
+some sort of forward security will be very desirable. While, for the case of
+payments or staking, the impact of a compromise (either of a leaf node --
+i.e., a key -- or a complete subtree) can be mitigated by prompt detection
+and transfer of funds to an uncompromised address, this may be harder for
+keys representing in some way real world identities. Most probably, the
+latter will frequently be long-lived keys, that also can, in turn, be used
+to issue further identities (e.g., as in the case of identity providers).
+Thus, the consequences of a compromise may be more cumbersome to address
+(re-issuing credentials, distributing revocation lists, etc.) and,
+consequently, it seems desirable to look for constructions that give some
+sort of guarantee about the security of keys produced at time $t' < t$, if a
+compromise happens at time $t$.
+
+Also, it cannot be discarded that further desirable privacy or security
+properties arise, as we get more familiar with the targetted use cases.
+
+\subsection{Further related work}
+
+There seems to be a growing body of related research, which is specially
+growing lately (probably, due to the rise of cryptocurrencies). The following
+just includes some of the main references for self-bookkeeping (besides
+\cite{kkl20} and \cite{def+21}, already mentioned in earlier sections). Note
+that they, in turn, include references to further related work.
+
+\begin{itemize}
+\item ``Arcula: A Secure Hierarchical Deterministic Wallet for Multi-asset
+  Blockchains'', \cite{lfa20}.
+\item ``Simple, Efficient and Strongly KI-Secure Hierarchical Key Assignment
+  Schemes'', \cite{fpp13}.
+\item ``A Formal Treatment of Deterministic Wallets'', \cite{dfl19}.
+\end{itemize}
 
@@
 %%% mode: latex
-%%% TeX-master: "sok-privsig"
+%%% TeX-master: "single-mnemonic"
 %%% End:

### 2021-12-22 prism-backend/research/single-mnemonic/iowal.tex
Added comments and refinements based on yesterday's sync.

@@
 \footnote{\url{https://cips.cardano.org/cips/cip1852/}. Last access, December
-  15th, 2021.}.
+  15th, 2021.}. Mnemonics in Cardano are composed by 24 words, and hence
+encode 256-bit random bitstrings.
 
-\paragraph{Atala.} HD wallets in Atala follow a slightly different tree
-organisation, layer-wise. Namely, it defines 4 layers: root, DID number, key
-type, and index. All child derivations are done in hardened mode. The elliptic
-curve is Secp256k1, as BIP44. See the key derivation document for details%
+\paragraph{Atala.} HD wallets in Atala follow the same overall rules as in
+BIP32. Specifically, the same distinction between hardened and non-hardened
+child derivation rules are applied, as well as Secp256k1 as the elliptic curve,
+wich ECDSA as digital signature scheme. However, Atala defines a different
+tree structure, with the following layers, depicted also in \figref{fig:atalatree}:
+
+\begin{description}
+\item[Layer 0: Root.] Encoded as/derived from a 12-word mnemonic.
+\item[Layer 1: DID Number.] Obtained by hardened child derivation from the root.
+  Each node in this level corresponds to a different DID.
+\item[Layer 2: Key Type.]  Obtained by hardened child derivation from a layer 1
+  node. Currently, the Atala specification defines four types of keys: master
+  keys, issuing keys, communication keys, and authentication keys.
+\item[Layer 3: Index.] Obtained by hardened child derivation from a layer 2 node.
+  Each layer 2 node may have up to $2^{31}$ child nodes, which are the leaves of
+  the tree.
+\end{description}
+
+See the key derivation document for details%
 \footnote{\url{https://github.com/input-output-hk/atala-prism/blob/master/prism-backend/docs/protocol/key-derivation.md}. Last access December 15th, 2021. \textbf{WARNING!
-    Internal link!}}.
+    Internal link!}}. Mnemonics in Atala are composed by 12 words, and hence
+encode 256-bit random bitstrings.
+
+\begin{figure}[ht]
+  \includegraphics[width=\textwidth]{figures/atala_tree.png}
+  \caption{Atala tree derivation structure.}
+  \label{fig:atalatree}
+\end{figure}
 
@@
 
+\subsection{Aspects to consider before unification}
+\label{ssec:unification}
+
+Next, we emphasize some concrete topics that would need to be considered
+from an implementation/software-design point of view, prior to making
+Atala and Cardano keys to be derived from a single mnemonic.
+
+\paragraph{Domain separation when different cryptosystems is
+  necessary.} %
+As mentioned, Cardano uses EdDSA (which is based on Ed25519 curve),
+while Atala uses ECDSA with Secp256k1. It is \emph{not} a good idea%
+\footnote{I have not been able to find a paper that describes
+  some concrete related attack or gives some impossibility result for
+  proving security under this circumstance but, at the least, it seems to
+  be folklore knowledge. See Lindell's answer at
+  \url{https://crypto.stackexchange.com/a/54666/52362} for instance.
+  \cite{dlp12+,thorm21} seem good references to study this topic further, if
+  needed.} to use the same key in different cryptosystems, nor for different
+curves, even though ``structurally'' it may be possible (e.g., in EdDSA and
+ECDSA, private keys are 32-byte random numbers). However, this is easily
+avoidable by ensuring domain separation in the key derivation functions that
+are applied on the common seed. This is an important concern on its own; yet,
+it should be addressed natively through the considerations in the next
+paragraph.
+
+\paragraph{Ensure a correct hierarchical key derivation strategy.} %
+We need to take into account what specific usage we expect from the wallets
+and, from there, define hierarchical derivation rules that ensure security
+without disabling current utility. Related to the previous paragraph, we should
+make sure that keys that are aimed to be used in different
+cryptosystems, are derived in separate tree branches that ensure domain
+separation. Or, since the Atala derivation path is shorter, than no Atala
+derivation path can be a prefix of a Cardano derivation path. For instance,
+according to the current specification, the derivation path
+\texttt{m/1852'/1815'/0'} corresponds to account \texttt{0'} for Ada coins in
+CIP1852-compliant Cardano wallets. In Atala, \texttt{1852'} could be a valid
+DID number and, while \texttt{1815'} is currently not a valid key type, if,
+in the future it becomes so, then \texttt{m/1852'/1815'/0'} would be a valid
+derivation path in both Atala and Cardano -- which could open an attack vector.
+An easy fix would be to concatenate the master seed with some value \texttt{C}
+in Cardano, and some distinct value \texttt{A} in Atala. The derivation paths would
+become \texttt{Cm'/1852'/1815'/...} in Cardano, and \texttt{Am'/...} in Atala
+-- hence, domain separation would be ensured. Probably, many other alternatives
+exist, more suitable from an engineering perspective (e.g., assigning Atala its
+own \texttt{purpose} level in BIP44 wallets). But, whatever option is followed,
+domain separation should be ensured.
+
+\paragraph{On the mnemonic length.} %
+Atala uses 12-word mnemonics to encode the master seed from which all keys are
+derived, while Cardano uses 24 words. According to BIP39, 12 words encode 128-bits
+seeds, and 24 words encode 256-bit seeds. These entropy bits are then subject to
+the extract-and-expand approach of the HKDF used in BIP32 to produce pseudoranom
+bits that are computationally indistinguishable from true random numbers%
+\footnote{Note: only 256 of these bits are used to produce the final keys.}.
+The keys used by both Atala (for ECDSA), and Cardano (for EdDSA), are thus
+securely derived pseudorandom keys of 256 bits. For keys of 256 bits, both ECDSA
+and EdDSA are expected to provide 128 bits of security against unforgeability
+attacks. Given this, and assuming (like \cite{def+21} does) that some keys
+will be compromised, there are two ways to attack a wallet: by breaking
+security of the HKDF used to derive the keys; or by breaking security of
+the wallet construction itself. Given this, on the one hand, in \cite{def+21}%
+\footnote{Important! Note that \cite{def+21} is defined for ECDSA-based BIP32
+  wallets with a structure slightly different from BIP44 wallets. Hence, its
+  results may not translate to our setting -- and of course, neither to
+  EdDSA-based BIP44 wallets.}, security of BIP32 wallets against unforgeability
+is estimated to have a security loss of 37 bits over the underlying digital
+signature scheme (under somewhat arbitrary estimations for
+a typical setting, like leaking about $1\%$ of roughly $2^{20}$ produced
+keys). For 256-bit ECDSA keys, this translates to 91 bits of security.
+On the other hand, even for 128-bit seeds (thus, with entropy at most
+128), breaking the security of the HMAC-based HKDF construction (that would
+seem to affect the unlinkability property of BIP32 wallets, rather than their
+unforgeability) would be harder than breaking the unforgeability property of
+the BIP32 wallet, as per the results in \cite{kraw10}\footnote{According to the
+  analysis in \cite{kraw10}, the outputs of HMAC-based HKDFs are roughly
+  $q2^{-m}$-close to uniform, where $q$ in our setting would be $2^{20}$ as per
+  \cite{def+21}, and $m$ is the min-entropy of the randomness source (our
+  mnemonic). Hence, for seeds (mnemonics) of 128 bits of entropy, we can still
+  expect the outputs to be $\sim 2^{-100}$-close to uniform.}. Given this, and
+lacking a more detailed analysis, seeds of 12 words would appear to be enough
+for security, strictly speaking. However, taking into account that we are
+aiming to combine two wallets into one, it does not seem logical to reduce the
+overall security of the wallet that uses 24-word mnemonics, as the unified
+wallet will use the same mnemonic to produce even more keys than what it
+was producing before. Therefore, it seems advisable to increase the mnemonic
+length of Atala to 24 words, rather than reducing the length of Cardano to
+12 words.
+
 %%% Local Variables:

### 2021-12-30 prism-backend/research/soa_review/app-ac.tex
Added comments of PrivacyPass and Whatsapp's DIT.

@@
 \item \cite{kkl+16}: achieves similar results to \cite{cgm16} with a different approach?
+\item \cite{hkrw21}: multi-party revocation in Sovrin.
 \end{itemize}
@@
 \begin{itemize}
-\item Evernym. \url{https://www.evernym.com/}
+\item Evernym and Sovrin. \url{https://www.evernym.com/}
   \begin{itemize}
-  \item {\bf Introduction}. Evernym is a software company that is some kind of
-    relative of Sovrin. Their solution builds completely on the Sovrin system.
+  \item {\bf Introduction}. Evernym is a software company that produced Sovrin.
   \item \emph{``How Sovrin Works''}%
@@
   \end{itemize}
+\item Hyperledger Fabric \& Idemix: \url{https://hyperledger-fabric.readthedocs.io/en/release-2.2/idemix.html}.
+  \begin{itemize}
+  \item Hyperledger Fabric is the private and permissioned blockchain, initially
+    created by IBM, and then used to seed the Hyperledger framework. Fabric's
+    participants are authenticated via certificates issued by a Membership
+    Service Provider (MSP) entity. In Fabric's first versions, the MSP was a
+    conventional Certificate Authority (or a set of them, forming a traditional
+    PKI system).
+  \item Since v1.3, Fabric has included support for Idemix-based credentials
+    \url{https://idemix.wordpress.com/}. Idemix credentials were initially based
+    on CL signatures, but the current implementation seems to build on BBS+
+    signatures\footnote{See \url{https://hyperledger-fabric.readthedocs.io/en/release-2.2/idemix.html\#underlying-cryptographic-protocols}.}.    
+    With Idemix-based credentials, users (including transactors of the system)
+    can restrict the attributes that they share with verifiers, and their
+    operations are anonymous and unlinkable (up to the revealed attributes). Not
+    even the MSP can link them.
+  \item An interesting practical aspect: the documentation advises to use at
+    most one Idemix-based MSP per channel (or, per network). This is because
+    the MDP identity is always revealed when showing a credential (as it is
+    needed for verification). Therefore, the more MSPs, the easier it is to
+    deanonymize users. They mention that it may be possible in the future to
+    extend Idemix to support hierarchies of Idemix issuers and, therefore,
+    provide more flexibility.
+  \end{itemize}
+\item Hyperledger Indy, Aries, and Ursa:
+  \begin{itemize}
+  \item \url{https://hyperledger-indy.readthedocs.io/projects/sdk/en/latest/docs/getting-started/indy-walkthrough.html}
+  \item \url{https://www.hyperledger.org/use/aries}
+  \item \url{https://github.com/hyperledger/ursa}
+  \end{itemize}
+\item Indy is Hyperledger's project for digital identity. It was originated by
+  the donation of the Sovrin codebase by Evernym, so the essentials explained
+  for Sovrin mostly apply here too. It is therefore also based on CL anonymous
+  credentials -- although, according to the online documentation%
+  \footnote{\url{https://hyperledger-indy.readthedocs.io/projects/hipe/en/latest/text/0109-anoncreds-protocol/README.html}.}%
+  , it uses actual CL signatures (the original ones from 2002, based on RSA), as
+  opposed to Evernym/Sovrin, that have migrated to the BBS+ equivalent.
+\item In a nutshell, Indy covers layer 1 of the ToIP stack%
+  \footnote{\url{https://trustoverip.org/}}, and Aries
+  covers layers 2 and 3\footnote{According to this:
+    \url{https://www.youtube.com/watch?v=FfuhlF9ZYPM}.}. This means that Indy
+  manages DIDs \doubt{Does Indy also take care of writing credential schemas,
+    etc. into the blockchain?}, and Aries uses the DIDs from Indy to establish
+  secure connections and exchange verifiable credentials. Ursa is the
+  cryptographic library that both projects use.
+\item PrivacyPass \cite{dgs+18}.
+  \begin{itemize}
+  \item PrivacyPass is not an anonymous credential system per se, although
+    probably some techniques can be leveraged. It is actually closer to
+    Nymble, PEREA... and the line of anonymous blacklisting systems. Each
+    time a user proves ``being human'', e.g., through a CAPTCHA, it gets
+    $N$ blindly signed messages from a user, along with a batched
+    zero-knowledge proof of knowledge of all of them being signed with the
+    same secret key. To access a resource, the user then derives a MAC
+    from the blindly signed value, and sends the result along with a tag
+    that allows the server to reproduce the calculations and compare with
+    the received MAC. If the comparison succeeds, the user is granted access.
+    The server needs to keep a list of all used tags. Cryptographically, this
+    is simple (and thus, it should be efficient). A main advantage seems to
+    be that it is easily integrated in current web infrastructure. There is an
+    open source implementation, avaliable in
+    \url{https://privacypass.github.io/} that has been integrated in the
+    Trust Token API \url{https://github.com/WICG/trust-token-api}.
+  \end{itemize}
+\item Whatsapp's DIT (formerly known as Private Stats) \cite{hij+21}.
+  Note: the report seems to have been taken offline. I managed to find a copy
+  (I did not take note of the URL). The only available information seems
+  to be this URL: \url{https://engineering.fb.com/2021/04/16/security/dit/}.
+  \begin{itemize}
+  \item This system is inspired by PrivacyPass, focusing on authentication of
+    clients that need to log data in the context of Whatsapp -- hence,
+    efficiency is very relevant. It indeed follows a similar execution flow to
+    PrivacyPass: clients first authenticate against an authentication server,
+    who requests to an anonymous credential server, on their behalf, a sort of
+    anonymous credential using a blinded value received from the client. The
+    received blinded credential is then unblinded, and can be used to authenticate
+    subsequent ``anonymous connections''. Roughly, the anonymous credential is
+    build from an attribute-based VOPRF inspired by Naor and Reingold
+    \cite{nr04}. To authenticate a connection, similarly to PrivacyPass, the
+    server recomputes a MAC, using as key a value reproduced through the VOPRF,
+    using a tag that determines the attributes contained in the ``anonymous
+    credential''. While the system seems very practical -- and indeed, its
+    greatest merit is that it seems to be very well integrated in Whatsapp's
+    infrastructure --, its relation to anonymous credentials is barely
+    justifiable, despite it is mentioned several times in the paper. Its only
+    common point is the support for different attributes. However multiple
+    authentications with the same credential are linkable and, even though
+    multiple attributes are supported, the client cannot choose which subset
+    of the credentials are revealed. Moreover, security is defined for the
+    VRF component, but no model or formalization whatsoever is given that
+    resembles the usual ones for Anonymous Credentiasl (e.g., there is no
+    property for unforgeability or anonymity of credentials).
+  \end{itemize}
 \end{itemize}

### 2022-01-10 prism-backend/research/single-mnemonic/bip32-etal.tex
Changes based on Tony's comments.

--- 2021-12-18 prism-backend/research/single-mnemonic/bip32-etal.tex
@@
 \label{sec:bip32}
-
-Hierarchical Deterministic Wallets (HD wallets, for short) in the cryptocurrency
-domain derive from the BIP32 specification%
-\footnote{\url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}.
-  Last access, December 13th, 2021.}
-The motivation behind creating this type of wallets is clear if one thinks about
-how typical cryptocurrency systems work: each address is associated with a key
-pair and, in order to achieve high security and privacy levels, it is best to
-limit the reusage of addresses (thus, key pairs). Therefore, a too high number
-of needed key pairs is quickly reached. If each key is generated independently
-at random, management becomes too complex -- especially, if several devices
-are expected to be synchronised. As a solution to this challenge, a hierachical
-tree-based data structure was proposed, in which each parent node can be used to
-derive multiple child nodes, deterministically. This approach seems also useful
-to foster some sort of separation -- i.e., create sub-trees that are
-(computationally) independent from one another, in the sense that a compromise
-in one does not lead to a compromise in the other. Typically, the root node
-of the tree is derived from a seed encoded as a mnemonic. BIP39%
-\footnote{\url{https://github.com/bitcoin/bips/blob/master/bip-0039.mediawiki}.
-  Last access, December 13th, 2021.} is the main specification for this purpose.
 
@@
 
-\subsection{Main Specifications}
+\subsection{Main Specifications: A Brief History of BIPs for Wallets}
 
-While the main specification is BIP32, it essentially gives the basic guidelines
-to create HD wallets. To avoid ambiguity leading to incompatible
-implementations, BIP43%
+BIPs, or Bitcoin Improvement Proposals, are ``standards'' in the Bitcoin domain
+that specify how concrete components of the ecosystem work and/or should be
+implemented. Being Bitcoin the first blockchain, many others import these
+standards.
+
+In 2013, BIP32 was published. It defines an approach to HD wallets
+using a tree structure in which each node can be associated to a key pair. It
+also defines two ways to derive child nodes from parent nodes: one that allows,
+given a public key of a node, to derive the public and private keys of all its
+descendants; and another one that requires the private key for derivation of
+its child nodes. Based on this child derivation processes, it also specifies a
+basic strategy for building HD structures for payments.
+
+However, although BIP32 does specify a basic structure, it does not mandate that
+it has to be followed. According to BIP43%
 \footnote{\url{https://github.com/bitcoin/bips/blob/master/bip-0043.mediawiki}.
-  Last access, December 13th, 2021.} and BIP44%
+  Last access, December 13th, 2021.}, published in 2014, this led to a set of
+self-claimed BIP32-compliant wallets not to be compliant between themselves.
+BIP43 requires that the first level of child derivation (directly from the
+root) be dedicated to define a ``purpose''. BIP44%
 \footnote{\url{https://github.com/bitcoin/bips/blob/master/bip-0044.mediawiki}.
-  Last access, December 13th, 2021.} specify how to organize HD wallets so
-that the resulting tree structure enables the most common use cases (which, at
-least initially, focus on the cryptocurrency scenario). In addition, the
-specification that defines how to encode (pseudo-)random bitstrings as
-mnemonic is given in BIP39.
+  Last access, December 13th, 2021.}, published simultaneously to BIP43, further
+refines this, by establishing 6 different levels (which we introduce in
+subsequent sections). Thus, BIP44 is an specialization of BIP43, which is itself
+an specialization of BIP32.
+
+Somehow orthoghonally to these, BIP39 defines how to encode random binary seeds
+into mnemonic sentences, and back. In this manner, the root node of a BIP44
+wallet is decoded into a bitstring, from a mnemonic, using BIP39. Then, this
+root node and its child nodes are computed as defined in BIP44. \tabref{tab:bips}
+summarizes the mentioned standards.
+
+\begin{table}[ht!]
+  \centering
+  \scalebox{0.95}{
+    \begin{tabular}{|c|c|l|}
+      \hline
+      \bf BIP & \bf Year & \bf Description \\
+      \hline
+      BIP32 & 2013 & Basic structure and derivation rules for HD wallets. \\
+      BIP43 & 2014 & Definition of ``purpose'' level. \\
+      BIP44 & 2014 & Definition of 6-level structure (root, purpose, coin type,
+                     account, change, address.) \\
+      BIP32 & 2013 & Encoding/decoding of bitstrings to/from mnemonic sentences. \\
+      \hline
+    \end{tabular}
+  }
+  \caption{Summary of BIPs for HD wallets.}
+  \label{tab:bips}
+\end{table}
+
+HD wallets that follow the BIP44 specification have to define a value of 44
+(with hardened derivation; see next) at the ``purpose'' layer. Wallets following
+a different structure, but still compatible with BIP32, can (should?) define
+their own code, for the sake of ensuring compatibility across implementations.
+For instance, Cardano defines the code 1852 (again, hardened derivation), as
+it has some minor variations with respect to BIP44. There are several well-known
+wallets that follow this specification. For instance, Trezor%
+\footnote{\url{https://docs.trezor.io/trezor-firmware/misc/coins-bip44-paths.html}.
+  Last access, January 10th, 2022.}, or Ledger%
+\footnote{\url{https://support.ledger.com/hc/en-us/articles/4404388633489-Export-your-accounts?docs=true}.
+Last access, January 10th, 2022.}.
+
+Additionally, Satoshi Labs SLIP44 maintains a registry of the different
+cryptocurrencies that have ``registered'' codes for wallet specifications
+that follow BIP44. That is, this registry contains codes for the ``coin type''
+level of BIP44. Examples of registered coins include Bitcoin mainnet and testnet,
+Litecoin, Cardano, Ether, and many others (currently, there are several
+hundreds).
+
+% While the main specification is BIP32, it essentially gives the basic guidelines
+% to create HD wallets. To avoid ambiguity leading to incompatible
+% implementations, BIP43 and BIP44 specify how to organize HD wallets so
+% that the resulting tree structure enables the most common use cases (which, at
+% least initially, focus on the cryptocurrency scenario). In addition, the
+% specification that defines how to encode (pseudo-)random bitstrings as
+% mnemonic is given in BIP39.
 
 \subsection{Main Concepts}
+\label{ssec:mainhdconcepts}
 
@@
 
+\paragraph{Path notation.} As can be seen in \figref{fig:bip44-tree}, the
+hierarchical structure of an HD wallet is defined in layers (or levels), where
+different indexes are used to derive the cryptographic values associated to
+different nodes in a same layer, with the exception of the root node (at layer
+0), which is frequently just denoted with an \texttt{m}, after master seed.
+Thus, for instance, paths  \texttt{m/1} and \texttt{m/2} denote a tree with two
+layer 1 nodes computed with index \texttt{1} and index \texttt{2},
+respectively. If a child node index is \emph{primed}, it means that hardened
+derivation is used (whereas the absence of a prime means non-hardened
+derivation). More specifically, since BIP44 wallets have up to layer 6, paths
+look like \texttt{m/a'/b'/c'/d'/e/f}. Note that layers 1 to 3 are derived in
+hardened mode, and layers 4 and 5 are derived in non-hardened mode.
+
 \begin{figure}[ht!]
@@
 nodes of hardened childs: i.e., layer 1 is composed of childs $(1,2^{31})$
-to $(1,2^{62}-1)$, where the second element in the pair is the $i$ value used
-in the child derivation processes, and denotes for what ``purpose'' the
-descendant keys will be used -- this roughly translates to the system (e.g.,
-Bitcoin, Cardano... or even non-blockchain systems, in theory).
+to $(1,2^{62}-1)$, where the second element in the pair is the index $i$,
+whose value is used in the child derivation processes, and denotes for what
+``purpose'' the descendant keys will be used -- this roughly translates to the
+system (e.g., Bitcoin, Cardano... or even non-blockchain systems, in theory).
 
@@
 
-For BIP44-compatible wallets, the expected index is $44$. Cardano, since
-the Shelley era, uses $1852$%
+For BIP44-compatible wallets, the expected value for the $i$ index is $44$, so
+all paths begin with \texttt{m/44'}. Cardano, since the Shelley era, uses index
+$1852$ (and thus, Cardano paths begin with \texttt{m/1852'}%
 \footnote{\url{https://cips.cardano.org/cips/cip1852/}. Last access, December
@@
 \footnote{\url{https://github.com/satoshilabs/slips/blob/master/slip-0044.md}.
-  Last access, December 14th, 2021.}.
+  Last access, December 14th, 2021.}. For instance, Cardano's ADA has an index
+of 1815 in hardened mode -- thus, its path prefix is \texttt{m/1852'/1815'}.
 
@@
 non-hardened childs $(4,0)$ and $(4,1)$. This layer is used to differentiate
-whether the descendant nodes will be used as a change addresses, or not. I.e.,
+whether the descendant nodes will be used as change addresses, or not. I.e.,
 child $(4,0)$ will \emph{not} be used for receiving change in payments, and
@@
 outside of the wallet; while child $(4,1)$ is expected to be used for receiving
-change in payments.
+change in payments, and will typically not be published outside of the
+transaction.
 
-Note that, since the 4th layer is not derived in hardened mode, if the private
-key of the $(4,0)$ child of some layer 3 node is compromised along with the
-extended public key of the node at layer 3, then the entire subtree of that
-layer 3 node will be compromised (but not the subtrees of other layer 3 nodes,
-as layer 3 is derived in hardened mode). That is, all the addresses (change or
-not) of an specific account of some cryptocurrency, will be compromised.
+Note that, since nodes in layer 4 are not derived in hardened mode, if the private
+key of a layer 4 node is compromised, along with the extended public key of its
+layer 3 parent, then the entire subtree of that layer 3 node will be compromised
+(but not the subtrees of other layer 3 nodes, as layer 3 is derived in hardened
+mode). For example, take the derivation path of a layer 4 node to be
+\texttt{m/x'/y'/z'/0}. If the private key of \texttt{m/x'/y'/z'/0} is leaked to
+an attacker, who also gains access to the \emph{extended public} key (i.e.,
+the public key and chaincode) of \texttt{m/x'/y'/z'}, then the attacker will
+be able to compute the extended private (and public) keys of the sibling node
+\texttt{m/x'/y'/z'/1}. This is precisely the attack explained in the last
+paragraph of \secref{ssec:mainhdconcepts}.
 

### 2022-01-10 prism-backend/research/single-mnemonic/introduction.tex
Changes based on Tony's comments.

@@
 \label{sec:introduction}
+
+Hierarchical Deterministic Wallets (HD wallets, for short) in the cryptocurrency
+domain derive from the BIP32 specification%
+\footnote{\url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}.
+  Last access, December 13th, 2021.}
+The motivation behind creating this type of wallets is clear if one thinks about
+how typical cryptocurrency systems work: each address is associated with a key
+pair and, in order to achieve high security and privacy levels, it is best to
+limit the reusage of addresses (thus, key pairs). Therefore, a too high number
+of needed key pairs is quickly reached. If each key is generated independently
+at random, management becomes too complex -- especially, if several devices
+are expected to be synchronised. As a solution to this challenge, a hierachical
+tree-based data structure was proposed, in which each parent node can be used to
+derive multiple child nodes, deterministically. This approach seems also useful
+to foster some sort of separation -- i.e., create sub-trees that are
+(computationally) independent from one another, in the sense that a compromise
+in one does not lead to a compromise in the other. Typically, the root node
+of the tree is derived from a seed encoded as a mnemonic. BIP39%
+\footnote{\url{https://github.com/bitcoin/bips/blob/master/bip-0039.mediawiki}.
+  Last access, December 13th, 2021.} is the main specification for this latter
+purpose.
+
+\subsection{Preliminaries}
+
+In the sequel, the processes that compose an (BIP44-compliant) HD wallet are
+described, including high-level cryptographic algorithms. For the sake of
+readability of non-cryptography savvy audience, we give informal descriptions of
+the cryptographic concepts and schemes mentioned next.
+
+\paragraph{Signature schemes.} A signature scheme uses an asymmetric key pair,
+composed of a public key and a private key (also frequently referred to as
+verification key and signing key, respectively). Intuitively, the owner of the
+signing key can produce a digital signature over arbitrary messages, which can
+be verified by anyone with the verification key, which is frequently somehow
+made publicly accessible. Secure signature schemes ensure that only the owner
+of the signing key can produce signatures verifiable with the corresponding
+verifying key. In the HD wallets studied next, typical signing algorithms are
+ECDSA and EdDSA.
+
+\paragraph{HMACs and HKDFs.} A Hash-based Message Authentication Code scheme is
+a concrete approach to build MAC functions, using cryptographic hashes as main
+building block. A MAC function is a kind of symmetric equivalent to digital
+signature -- i.e., it relies on a shared secret rather than on an asymmetric key
+pair. HMACs have been proved to be secure pseudo random number
+generators \cite{bck96}, which is a useful building block to build secure HKDFs
+\cite{kraw10}, or Hash-based Key Derivation Functions. Specifically, an HKDF, as
+defined in \cite{kraw10}, can be applied to produce secure cryptographic keys
+from low entropy sources, by applying a two-phase process of randomness
+extraction and expansion (the extract-expand approach). In summary, given a
+(possibly low-entropy) bitstring, an HKDF produces an arbitrarily long pseudo
+random bitstring that is fit for cryptographic purposes.
 

### 2022-01-15 prism-backend/research/soa_review/ac.tex
Added section on real-world deployments of ACs.

@@
 Perhaps surprisingly, revocation is not a common functionality, although it is
-certainly considered by several works, e.g. \cite{cl01,cks10,ckl+15}, and for
-some it is just sketched \cite{hs21}.
+certainly considered by several works, e.g. \cite{cl01,cks10,ckl+15,bran00}, and
+for some it is just sketched \cite{hs21}.
 
@@
 
-\comment{This section is just a placeholder for now...}
+Anonymous credential systems saw a first phase of real world deployment during
+the first years of the 2010s, mostly through IBM's Idemix%
+\footnote{\url{https://idemix.wordpress.com/} (last access, January 15th, 2022).}
+and Microsoft's U-Prove%
+\footnote{\url{https://www.microsoft.com/en-us/research/project/u-prove/} (last
+access, January 15th, 2022).}. Idemix is based on the CL line of works, and
+thus inherits their security and privacy properties (multi-show, selective
+disclosure). U-Prove is based on on Brands's work, and thus it features
+one-show credentials with selective disclosure. Both approaches also support
+proving, in zero-knowledge, arbitrary predicates on the credentials' attributes
+(albeit with linear costs). \todo{Verify the last claim -- they do, but I'm not
+  sure if this is specified in their corresponding papers.}
 
-\begin{itemize}
-\item Idemix.
-\item Hyperledger Indy.
-\item U-Prove.
-\end{itemize}
+In the late 2010s, anonymous credential systems started receiving increased
+attention by the industry, as a consequence of the W3C's Decentralised
+Identities%
+\footnote{\url{https://www.w3.org/TR/did-core/} (last access, January 15th, 2022).}
+and Verifiable Credentials%
+\footnote{\url{https://www.w3.org/TR/vc-data-model/} (last access, January 15th,
+  2022).} initiatives, associated to the blockchain world. Idemix made its way
+into Hyperldedger Fabric%
+\footnote{See \url{https://hyperledger-fabric.readthedocs.io/en/release-2.2/idemix.html} (last access, January 15th, 2022).}
+, which since version 1.3 allows the distribution of Idemix credentials
+(although they have migrated from CL-based credentials to BBS+-based ones).
+Also within the umbrella of the Hyperledger consortium, we can find Indy
+\needcite, which directly focuses on digital identity (as opposed to Fabric,
+which is a general-purpose permissioned blockchain system). Indy is, in turn,
+the evolution of Sovrin%
+\footnote{\url{https://sovrin.org/} (last access, January 15th, 2022).}, one of
+the main proponents of verifiable credentials, building on CL anonymous credentials%
+\footnote{Note, as opposed to Idemix, which migrated to BBS+ credentials,
+  Indy/Sovrin seems to stick to CL credentials, according to online
+  documentation \url{https://hyperledger-indy.readthedocs.io/projects/hipe/en/latest/text/0109-anoncreds-protocol/README.html} (last access, January 15th, 2022).}
+Indy has related subprojects Aries%
+\footnote{\url{https://www.hyperledger.org/use/aries} (last access, January
+  15th, 2022.)} and Ursa%
+\footnote{\url{https://www.hyperledger.org/use/ursa} (last access, January 15th,
+  2022).}; Aries deals
+with other layers of the approach to credential systems defined by the W3C's
+VC initiative, and Ursa is the library implementing the underlying cryptographic
+primitives (e.g., CL signatures). With respect to W3C's DID and VC initiatives,
+the one that is closely related to anonymous credentials is VC. Basically, this
+is a set of specifications that define how to represent digital credentials and
+their associated processes. Having been heavily influenced by the literature
+on anonymous credentials, the specifications include (or are working on)
+definitions for CL and BBS+ credentials. Within this community, there seems to
+be some controversy as to the appropriate type of credentials to support.
+According to a blog post%
+\footnote{``Why the Verifiable Credentials Community Should Converge on BBS+'',
+  \url{https://www.evernym.com/blog/bbs-verifiable-credentials/} (last
+  access, January 15th, 2022).} by a cryptographer in Evernym (the company
+that created Sovrin, which led to Indy) the complexity, engineering-wise, of a
+verifiable credentials system with support to prove arbitrary claims on the
+attributes of the credentials, makes it more desirable to restrict to
+credentials supporting only selective disclosure%
+\footnote{Interestingly, and confusingly, (parts of) this community equate BBS+
+  credentials to selective disclosure, even though using BBS+ credentials does
+  not (in theory) restrict the expressiveness of the claims that one can prove.
+  This confusion seems to derive from the solution offered by the company MATTR,
+  which has become one of the most popular proponents of BBS+ credentials
+  restricted to selective disclosure.}
+. Note that, related to the Verifiable Credentials effort, there are tens (maybe
+even hundreds) of different initiatives that build credential systems claiming
+to take into account privacy requirements (e.g., for healthcare use-cases, as a
+consequence of the popular health passports originated from the COVID-19
+pandemic). However, most of these initiatives lack formal, or even technical,
+publicly accessible documentation, or have some public documentation but, as
+of the moment of this writing, we are not aware of actual implementations
+(like Microsoft's zero-knoweldge credentials%
+\footnote{``Zero-knowledge credentials with deferred revocation checks'' white
+  paper, available at \url{url{https://github.com/decentralized-identity/snark-credentials/blob/master/whitepaper.pdf}}
+  (last access, January 15th, 2022.)}). Hence, we do not cover them here.
+
+Finally, there are also related works that have seen real world deployments
+which, although do not implement an anonymous credential systems, are somehow
+influenced by them. Among these, we can find Cloudflare's PrivacyPass \cite{dgs+18},
+which uses blind issuance of tokens associated to a secret key, through which
+service providers can implement privacy-preserving blacklisting (in this sense,
+they are closer to works like PEREA \cite{atk11} or Nymble \cite{tkcs11}, than
+to anonymous credentials). A similar approach is followed by Whatsapp's DIT
+system \cite{hij+21} (formerly known as PrivateStats), which further supports
+the inclusion of attributes in the produced tokens. In this case, DIT is
+designed to support privacy-preserving logging. Both in PrivacyPass and DIT, the
+produced tokens are one-use, meaning that multiple uses of the same token are
+linkable.
 

### 2022-01-15 prism-backend/research/soa_review/app-ac.tex
Added section on real-world deployments of ACs.

@@
     subsequent ``anonymous connections''. Roughly, the anonymous credential is
-    build from an attribute-based VOPRF inspired by Naor and Reingold
+    built from an attribute-based VOPRF inspired by Naor and Reingold
     \cite{nr04}. To authenticate a connection, similarly to PrivacyPass, the
@@
     VRF component, but no model or formalization whatsoever is given that
-    resembles the usual ones for Anonymous Credentiasl (e.g., there is no
+    resembles the usual ones for Anonymous Credentials (e.g., there is no
     property for unforgeability or anonymity of credentials).
+  \end{itemize}
+\item Microsoft's zero-knowledge credentials \url{https://github.com/decentralized-identity/snark-credentials/blob/master/whitepaper.pdf}.
+  \begin{itemize}
+  \item The system presented by Microsoft is something that approximates
+    anonymous credentials, but is not strictly an AC system. Note: this may just
+    be because the authors do not properly model their proposal. It indeed
+    follows an approach that resembles much the framework defined in \cite{cl01},
+    where users have to establish pseudonyms with issuers and each RP, and can
+    run presentations in which they prove that they have pseudonyms with both
+    some issuer and the verifiying RP, such that the credential attributes
+    associated to the issuer's pseudonym meet some claim. They further require
+    some practical properties related to revocation: namely, deferred revocation
+    and deferred revocation status check -- which are not very formally defined,
+    though. They also make some informal claims about inherent limitations of
+    these type of systems. Also, it is noteworthy that their proposal is one-show,
+    although they sketch how to make it multi-show by relying on anonymous
+    credentials. For expressiveness, they rely on ZK-SNARKS, and make some
+    preliminary analysis based on popular choices of cryptographic algorithms.
+  \end{itemize}
+\item Microsoft U-Prove \url{https://www.microsoft.com/en-us/research/publication/u-prove-technology-overview-v1-1-revision-2/}.
+  \begin{itemize}
+  \item Along with Idemix, U-Prove is probably the most mature application of
+    ACs to date. It has both a solid scientific background, and seems that it
+    reached a reasonably mature level implementation-wise.
+  \item According to the technology overview report linked above, it supports
+    the main functionalities for one-use ACs. Namely, it allows selective
+    disclosure and blind issuance of attributes; as well as some of the also
+    frequent variations, including several approaches for revocation, measures
+    to desincentivize transferability, reuse-prevention, and scope-exclusive
+    pseudonyms (note: most of these are natively provided by the system, and
+    are even somehow related between themselves, like the reuse-prevention and
+    the scope-exclusive pseudonyms). Integration with smartcards or similar
+    trusted execution environments is also considered as a way to reach higher
+    security in certain scenarios. However, this is an aspect that is not very
+    formally treated even in \cite{bran00}, and is certainly a well-known source
+    of complications, as learned from related works on DAA.
   \end{itemize}

### 2022-01-17 prism-backend/research/single-mnemonic/iowal.tex
Added comments on cryptographic choices by Atala and Cardano.

@@
 \end{figure}
+
+\paragraph{Note on the different cryptographic choices.} As stated, Cardano's
+Lightwallet CIP1852 follows a variation of BIP44 where the chosen singing
+algorithm is EdDSA, which uses Ed25519 as elliptic curve; whereas Atala builds
+from BIP32, thus employs ECDSA with a secp256k1 curve. The reason behind this
+difference seems just circumstancial, and due to the fact that Atala started to
+build from a different specification. From a cryptographic point of view, it is
+possible to unify under the same curve, or to stick to different ones. In the
+latter case, however, we must make sure that domain separation is correctly
+done: i.e., even if having a sort of unified wallet derived from the same
+mnemonic, it should not be possible to generate the same key to be used for
+payment purposes and identity purposes. More detail on this is given in
+\secref{ssec:unification}.
+
+Other than the previous, either choice seems to have its pros and cons. On the
+one hand, having both Cardano and Atala use the same curve would make it
+possible to benefit from joint development efforts. Also, it would avoid
+pitfalls such as using the same key in different curves, which can lead to
+security issues as described next (however, this can also be avoided with proper
+domain separation). Also, Edwards curves (such as Ed25519) are, at least in
+theory, more efficient. On the other hand, Secp256k1 is an standardized curve,
+which has seen more implementation and optimization effort. This means that the
+better theoretical efficiency of Ed25519 may somehow ``mitigated'' by more
+efficient implementations in Secp256k1. Also, Secp256k1 probably has more
+availability of implementations in different programming languages. In any case,
+this is something that needs to be considered by the development/engineering
+teams.
 

### 2022-01-17 prism-backend/research/single-mnemonic/discussion.tex
Changes based on Tony's comments.
Added some [non-final] notes on trust registries and secure storage.

@@
 may have impact in the overall security and privacy properties of the wallet
-(and related systems).
+and related systems.
 
@@
 
+\paragraph{Secure wallet storage.} %
+Currently, Atala has some basic support for encrypted storage%
+\footnote{\url{https://github.com/input-output-hk/atala-prism/tree/53f3414a34c88a4a8e54b6d2128d4b14ce2ee8b9/prism-backend/docs/data-vault}
+  {\bf WARNING! Internal link.}}, that basically allows storing and
+fetching data encrypted with a public key owned by a user. Some secure
+storage proposals for cryptocurrency wallets already exist, like Aries's
+RFC0050%
+\footnote{\url{https://github.com/hyperledger/aries-rfcs/blob/main/concepts/0050-wallets/README.md}
+  (last access January 18th, 2022).} or, in a more generic sense,
+Identity Foundation's Confidential Storage%
+\footnote{\url{https://identity.foundation/confidential-storage} (last access
+  January 18th, 2022).}. However, a careful analysis would be needed depending
+on the features we want to support (e.g., some sort of generic search on
+encrypted data vs just specific types of search), and also the expected
+infrastructure (e.g., an oblivious centralized secure storage service vs
+multiple user-owned devices that synchronize ``automagically'').
+%
+Although initially, these may be highly orthogonal topics to the hierarchical
+derivation of cryptographic keys, decissions in one domain may affect the other
+-- e.g., if we are to implement some sort of forward security mechanism in
+an identity wallet, how can we ensure that proper re-encryption is done in
+a centralized oblivious secure storage system?
+
+\paragraph{Trust registries.} %
+A core component of a decentralized identity system will be one that lets
+parties, a priori unknown to each other, derive some sort of trust based on the
+system itself. It is reasonable to expect that cryptographic keys (in the
+shape of DIDs, or related notions) are used to identify parties in the system,
+and assign them some sort of trust metric. As in the topic of secure storage,
+this would initially seem an orthogonal issue. But some properties (like, again,
+some notion of forward security), may require ad hoc updates of trust registries
+in a coordinated manner with an identity wallet -- which might have some
+implications into the security analysis.
+
+\paragraph{Are you aware of further challenges that may be worth
+  looking into? Have some feedback?} Please, reach out to us:
+
+\begin{itemize}
+\item Jesus Diaz Vico (Atala Semantics team).
+\item Christos KK Loverdos (Atala Technical Director).
+\item Ezequiel Postan (Atala Semantics team).
+\item Tony Rose (Atala Head of Product).
+\end{itemize}
+
 \subsection{Further related work}

### 2022-01-18 prism-backend/research/single-mnemonic/appendix.tex
Final pass based on Tony's feedback.

--- 2021-12-22 prism-backend/research/single-mnemonic/discussion.tex
@@
-\section{Discussion}
-\label{sec:discussion}
+\section{Appendix}
 
-From a theoretical point of view, it seems very reasonable to derive all
-keys, even for different purposes (payments, staking, or identities) from
-the same mnemonic. \secref{ssec:unification}, listed a series of topics
-that should be taken into account prior to unifying Cardano and Atala
-wallets under the same mnemonic, to avoid security pitfalls. In addition to
-those,  there are also some aspects that may need careful consideration, as they
-may have impact in the overall security and privacy properties of the wallet
-(and related systems).
+\subsection{Feedback Welcome}
 
-\paragraph{Malleability considerations when combining multiple
-  attributes into one address.} %
-Are the keys for the different purposes going to be used \emph{only} in a
-standalone manner? Or, rather, it can be expected that they are somehow
-encoded and distributed jointly? The latter seems to be the case for PoS
-wallets, which are expected to be used in the Cardano ecosystem. As pointed
-out by \cite{kkl20}, naive encoding of keys with different purposes, into
-a single address, may enable certain (malleability) attacks.
+Are you aware of further challenges that may be worth looking into? Have some
+feedback? Please, reach out to us:
 
-\paragraph{Concrete differences in prior security analysis.} %
-The security analysis in \cite{def+21} (which is one of the main references
-used in this research spike) is on BIP32, not BIP44. While BIP44
-is actually a subset of BIP32, it further specifies it in concrete ways
-that may alter the result of the analysis. For instance, \cite{def+21}
-assumes that non-hardened nodes are leaves of the tree (which, alternatively,
-can be seen as roots in new trees). However, in BIP44 the leaves are
-non-hardened nodes, and intermediate nodes are mostly hardened. Yet another
-possible source of discrepancy is that the analysis assumes that non-hardened
-nodes are maintained in a hot/cold wallet setting and, thus, the private keys
-cannot be compromised. This assumption may not hold for all use cases, and
-that would change completely the security reasoning. If we want to determine
-the concrete security level we want/need in some specific use cases that differ
-from the analysis of \cite{def+21} as mentioned above, a new model might be
-necessary.
-
-\paragraph{Careful consideration of extra security properties.} %
-The main related work analysed so far\footnote{BIP32, BIP44, \cite{def+21}
-  and, partially, \cite{kkl20}.} study the security of either BIP32
-wallets for payments, or PoS wallets. The introduction of identity-related
-(frequently associated to actual people) data may require additional properties,
-only mentioned in these works (or not considered, as in the BIPs). For instance,
-some sort of forward security will be very desirable. While, for the case of
-payments or staking, the impact of a compromise (either of a leaf node --
-i.e., a key -- or a complete subtree) can be mitigated by prompt detection
-and transfer of funds to an uncompromised address, this may be harder for
-keys representing in some way real world identities. Most probably, the
-latter will frequently be long-lived keys, that also can, in turn, be used
-to issue further identities (e.g., as in the case of identity providers).
-Thus, the consequences of a compromise may be more cumbersome to address
-(re-issuing credentials, distributing revocation lists, etc.) and,
-consequently, it seems desirable to look for constructions that give some
-sort of guarantee about the security of keys produced at time $t' < t$, if a
-compromise happens at time $t$.
-
-Also, it cannot be discarded that further desirable privacy or security
-properties arise, as we get more familiar with the targetted use cases.
+\begin{itemize}
+\item Jesus Diaz Vico (Atala Semantics team).
+\item Christos KK Loverdos (Atala Technical Director).
+\item Ezequiel Postan (Atala Semantics team).
+\item Tony Rose (Atala Head of Product).
+\end{itemize}
 

### 2022-01-18 prism-backend/research/single-mnemonic/discussion.tex
Final pass based on Tony's feedback.

@@
 
-\paragraph{Are you aware of further challenges that may be worth
-  looking into? Have some feedback?} Please, reach out to us:
-
-\begin{itemize}
-\item Jesus Diaz Vico (Atala Semantics team).
-\item Christos KK Loverdos (Atala Technical Director).
-\item Ezequiel Postan (Atala Semantics team).
-\item Tony Rose (Atala Head of Product).
-\end{itemize}
-
-\subsection{Further related work}
-
-There seems to be a growing body of related research, which is specially
-growing lately (probably, due to the rise of cryptocurrencies). The following
-just includes some of the main references for self-bookkeeping (besides
-\cite{kkl20} and \cite{def+21}, already mentioned in earlier sections). Note
-that they, in turn, include references to further related work.
-
-\begin{itemize}
-\item ``Arcula: A Secure Hierarchical Deterministic Wallet for Multi-asset
-  Blockchains'', \cite{lfa20}.
-\item ``Simple, Efficient and Strongly KI-Secure Hierarchical Key Assignment
-  Schemes'', \cite{fpp13}.
-\item ``A Formal Treatment of Deterministic Wallets'', \cite{dfl19}.
-\end{itemize}
-
 %%% Local Variables:

### 2022-02-01 prism-backend/research/soa_review/relationships.tex
Working on relationships between GS and AC.

\section{Relationships Between Primitives}
\label{sec:relationships}

In this section, we explore relationships between Group Signatures and Anonymous
Crednetials. Naturally, the wide range of constructions in both fields (of which
we have given some account in \secref{sec:gs} and \secref{sec:ac}) makes it
hardly possible to give relationships that hold in a universal sense. Therefore,
we begin from what we (possibly arbitrarily) consider the reference scheme of
each type. It is between these reference schemes from which we will then
establish connections.

\subsection{Reference GS Model}
\label{ssec:refgs}

\subsubsection{Partially Dynamic GS.} %
Partially dynamic group signatures where first formally studied in \cite{bsz05}.
There, the authors express a scheme where users can join the group at any point
in time, although some subtle aspects of revocation are not considered. However,
this is a mature enough model, in the sense that it captures the main security
and privacy properties (to the point that most subsequent models build on it);
and also it offers a functionality probably enough for many scenarios.

\paragraph{Syntax.} %
A partially dynamic group signature scheme, PDGS for short, meets the following
syntax:

\begin{description}
\item[$\PDGSparam \leftarrow \PDGSSetup(1^\PDGSsec)$]
\item[$(\PDGSisk, \PDGSipk) \leftarrow \PDGSIKeyGen(\PDGSparam)$]
\item[$(\PDGSosk, \PDGSopk) \leftarrow \PDGSOKeyGen(\PDGSparam)$]
\item[$(\PDGSusk, \PDGSupk) \leftarrow \PDGSUKeyGen(\PDGSparam)$]
\item[$\langle \PDGSucred, \PDGSutrans \rangle \leftarrow
  \langle \PDGSJoin(\PDGSparam, \PDGSusk, \PDGSipk),
  \PDGSIssue(\PDGSparam, \PDGSisk, \PDGSupk) \rangle$]
\item[$\PDGSsig \leftarrow \PDGSSign((\PDGSusk, \PDGSucred),
  (\PDGSparam, \PDGSipk, \PDGSopk), \PDGSmsg)$]
\item[$1/0 \leftarrow \PDGSVerify((\PDGSparam, \PDGSipk, \PDGSopk), \PDGSsig, \PDGSmsg)$]
\item[$(\PDGSupk, \PDGSoproof) \leftarrow \PDGSOpen(\PDGSparam, \PDGSosk, \PDGSalltrans, \PDGSsig, \PDGSmsg)$]
\item[$1/0 \leftarrow \PDGSJudge((\PDGSparam, \PDGSipk, \PDGSopk),
  \PDGSsig, \PDGSmsg, \PDGSupk, \PDGSoproof)$]
\end{description}

\doubt{We may need Link and LinkVerify, which is not in BSZ05 (nor BCC+16)...}

For brevity, we henceforth use \PDGSgpk to denote the pair $(\PDGSipk,\PDGSopk)$,
and assume that it includes the parameters created in \PDGSSetup, which are also
assumed to be included in the issuer's and opener's secret kyes.
Also, since the user credential has to be kept secret, we abuse the previous
notation to include it as part of the user secret key; i.e., we can see the
\PDGSJoin as ``expanding'' the previous user secret key to include the
membership credential. Note that, up to renaming, this is the syntax put forth
in \cite{bsz05} except for two differences: the open algorithm does not return
the index of the user, as what actually carries the identifying information is
the opening proof and the user public key, which we return directly. Also, we
divide the initial configuration (which in \cite{bsz05} is run in one single
setup process) into three steps: one for the creation of the global parameters
(e.g., picking algebraic groups, etc.); and two for creating the issuer and
opener key pairs. This makes notation a bit more verbose, but it is actually
closer to real world requirements. Furthermore, it does not affect the modelling
beyond the necessary syntactic adjustments, as described next.

Correctness of a PDGS scheme basically requires that, the \PDGSVerify algorithm
returns 1 when it is given a signature generated by an honest group member; and,
similarly, that \PDGSJudge accepts an honestly generated opening proof computed
over a valid group signature. More formally, a PDGS scheme is correct if
\PDGSExpCorrect returns 0 with negligible probability.

\begin{figure}[ht!]
  \begin{center}
    \scalebox{0.9}{
      \procedure{$\PDGSExpCorrect(1^\PDGSsec)$}{%
        \PDGSparam \gets \PDGSSetup(1^\PDGSsec) \\
        (\PDGSisk,\PDGSipk) \gets \PDGSIKeyGen(\PDGSparam) \\
        (\PDGSosk,\PDGSopk) \gets \PDGSOKeyGen(\PDGSparam) \\
        \PDGSgpk \gets (\PDGSipk, \PDGSopk) \\
        (\uid, \PDGSmsg) \gets \Adv^{\ADDU}(\PDGSgpk) \\
        \PDGSsig \gets \PDGSSign(\PDGSvusk\lbrack\uid\rbrack,\PDGSgpk,\PDGSmsg) \\
        (\PDGSupk,\PDGSoproof) \gets
        \PDGSOpen(\PDGSosk, \PDGSalltrans, \PDGSsig, \PDGSmsg) \\
        \pcif
        \PDGSVerify(\PDGSgpk,\PDGSsig,\PDGSmsg) = 0 \textrm{~or~}
        \PDGSJudge(\PDGSgpk,\PDGSsig,\PDGSmsg,\PDGSupk,\PDGSoproof) = 0:
        \pcreturn 0 \\
        \pcelse \pcreturn 1
      }
    }
  \end{center}
  \caption{Correctness definition for PDGS schemes.
    \todo{Define oracles and other variables!}}
  \label{fig:pdgscorr}
\end{figure}

\paragraph{Security.} %

The security properties required from a partially dynamic group signature scheme
are anonymity, traceability and non-frameability. Anonymity captures that no
third party observer should be able to distinguish signatures issued by two
honest members. Traceability ensures that, in the presence of an honest issuer
(but possibly corrupt opener), every valid group signature originates from a
member that completed successfully the join process. Finally, non-frameability
requires that, even in the presence of dishonest issuer and opener, no member
can be blamed as having been generated a group signature she did not produce.
Formal definitions follow, adapted from \cite{bsz05} up to the minor variations
due to our slightly different syntax.

\begin{figure}[ht!]
  \begin{center}
    \scalebox{0.9}{
      \procedure{$\PDGSExpAnonb(1^\PDGSsec)$}{%
        \PDGSparam \gets \PDGSSetup(1^\PDGSsec) \\
        (\PDGSisk,\PDGSipk) \gets \PDGSIKeyGen(\PDGSparam) \\
        (\PDGSosk,\PDGSopk) \gets \PDGSOKeyGen(\PDGSparam) \\
        \PDGSgpk \gets (\PDGSipk, \PDGSopk) \\
        (\uid, \PDGSmsg) \gets \Adv^{\ADDU}(\PDGSgpk,\PDGSisk)\\
      }

      \procedure{$\PDGSExpTrace(1^\PDGSsec)$}{%
        \PDGSparam \gets \PDGSSetup(1^\PDGSsec) \\
        (\PDGSisk,\PDGSipk) \gets \PDGSIKeyGen(\PDGSparam) \\
        (\PDGSosk,\PDGSopk) \gets \PDGSOKeyGen(\PDGSparam) \\
        \PDGSgpk \gets (\PDGSipk, \PDGSopk) \\
        (\uid, \PDGSmsg) \gets \Adv^{\ADDU}(\PDGSgpk,\PDGSosk)\\
      }

      \procedure{$\PDGSExpNonframe(1^\PDGSsec)$}{%
        \PDGSparam \gets \PDGSSetup(1^\PDGSsec) \\
        (\PDGSisk,\PDGSipk) \gets \PDGSIKeyGen(\PDGSparam) \\
        (\PDGSosk,\PDGSopk) \gets \PDGSOKeyGen(\PDGSparam) \\
        \PDGSgpk \gets (\PDGSipk, \PDGSopk) \\
        (\uid, \PDGSmsg) \gets \Adv^{\ADDU}(\PDGSgpk,\PDGSisk,\PDGSosk)\\
      }      
    }
  \end{center}
  \caption{Anonymity, traceability, and non-frameability definitions for PDGS
    schemes. \todo{Unfinished!}}
  \label{fig:pdgssec}
\end{figure}

\subsubsection{Fully Dynamic GS.} %
\todo{Can we do this?} \cite{bcc+16}

\subsection{Reference AC Model}
\label{ssec:refac}

As stated in \secref{sec:ac}, multi-show, multi-attribute anonymous credential
schemes are the most frequent ones in the AC domain. While there are variations
in the offered functionality (like those improving expressiveness of the
supported claims) we assume selective disclosure as the base scheme. Also,
we begin by modelling one-show schemes, which will ease our analysis.
\doubt{Not $100\%$ sure of the latter yet, but take it as running hypothesis.}

\subsubsection{One-Show Multi-Attribute AC with Selective Disclosure.} %
We recall that, in an One-Show Multi-Attribute AC Scheme with Selective
Disclosure (OMACSD), if a user shows the same credential more than once, these
multiple showings are linkable across themselves.

\paragraph{Syntax.} %
An OMACSD scheme offers the following syntax.

\begin{description}
\item[$\OMACSDparam \leftarrow \OMACSDSetup(1^\OMACSDsec,1^\OMACSDnattr)$.]
\item[$(\OMACSDisk,\OMACSDipk) \leftarrow \OMACSDIKeyGen(\OMACSDparam)$.]
\item[$(\OMACSDusk,\OMACSDupk) \leftarrow \OMACSDUKeyGen(\OMACSDparam)$.]
\item[$\langle \OMACSDcred/0, 1/0 \rangle \leftarrow
  \langle \OMACSDObtain(\OMACSDusk,\OMACSDipk,\OMACSDattr),
  \OMACSDIssue(\OMACSDisk,\OMACSDupk,\OMACSDattr) \rangle$.]
\item[$1/0 \leftarrow
  \langle \OMACSDShow(\OMACSDipk,\OMACSDattr,\OMACSDdattr,\OMACSDcred),
  \OMACSDVerify(\OMACSDipk,\OMACSDdattr) \rangle$.]
\end{description}

We note that this syntax is, up to some renaming for consistency with previous
sections, and the addition of the setup process, the one in \cite{fhs19} for
multi-show multi-attribute AC schemes with selective disclosure.

Correctness of an OMACSD scheme ensures that \OMACSDVerify accepts when
presented a credential that has been honestly obtained from a valid issuer, as
long as the subset of revealed attributes \OMACSDdattr is contained in the set
of attributes \OMACSDattr that were included in the credential. This is formally
captured in the \OMACSDExpCorrect game, which must return 1 except with
negligible probatility.

\begin{figure}[ht!]
    \begin{center}
    \scalebox{0.9}{
      \procedure{$\OMACSDExpCorrect(1^\OMACSDsec,1^\OMACSDnattr)$}{%
        \OMACSDparam \gets \OMACSDSetup(1^\OMACSDsec,1^\OMACSDnattr) \\
        (\OMACSDisk,\OMACSDipk) \gets \OMACSDIKeyGen(\OMACSDparam) \\
        (\OMACSDcred,\OMACSDdattr) \gets \Adv^{\ADDU}(\OMACSDipk) \\
        \pcif \OMACSDdattr \subseteq \OMACSDattr: \pcreturn \bot \\
        b \gets \langle \OMACSDShow(\OMACSDipk,\OMACSDattr,\OMACSDdattr, \OMACSDcred),
        \OMACSDVerify(\OMACSDipk,\OMACSDdattr) \rangle \\
        \pcreturn b
      }
    }
  \end{center}
  \caption{Correctness definition in OMACSD schemes.
    \todo{Unfinished!}}
  \label{fig:omacsdcorr}
\end{figure}

\paragraph{Security.} %
In an OMACSD scheme, security is formulated through anonymity and unforgeability
properties, which we define formally as experiments in \figref{fig:omacsdsec}.
Roughly, anonymity ensures that given two users with corresponding credentials,
each revealing the same subset of matching attributes in their respective
show processes, no third party should be able to distinguish which credential
belongs to which user. \doubt{Something like that -- make sure that it fits
  the formal definition.} Unforgeability captures that no adversary should be
able to successfully prove possession of a set of attributes that have not been
included by a legitimate issuer in a credential issued (or leaked) to the
adversary.

\begin{figure}[ht!]
  \begin{center}
    \scalebox{0.9}{
      \procedure{$\OMACSDExpAnonb(1^\OMACSDsec,1^\OMACSDnattr)$}{%
        \OMACSDparam \gets \OMACSDSetup(1^\OMACSDsec,1^\OMACSDnattr) \\
        (\OMACSDisk,\OMACSDipk) \gets \OMACSDIKeyGen(\OMACSDparam) \\
        \OMACSDcred \gets \Adv^{\ADDU}(\OMACSDisk) \\
      }

      \procedure{$\OMACSDExpUnfor(1^\OMACSDsec,1^\OMACSDnattr)$}{%
        \OMACSDparam \gets \OMACSDSetup(1^\OMACSDsec,1^\OMACSDnattr) \\
        (\OMACSDisk,\OMACSDipk) \gets \OMACSDIKeyGen(\OMACSDparam) \\
        \OMACSDcred \gets \Adv^{\ADDU}(\OMACSDipk) \\
      }

    }
  \end{center}
  \caption{Anonymity and unforgeability definitions for OMACSD schemes.
    \todo{Unfinished!}}
  \label{fig:omacsdsec}
\end{figure}

\subsubsection{Multi-Show Multi-Attribute AC with Selective Disclosure.} %
The syntax met by Multi-Show Multi-Attribute AC Systems with Selective
Disclosure (MMACSD) is exactly the same as that of OMACSD systems. Correctness
and unforgeability properties are also the same. The only difference lies on
the anonymity property.

\subsection{From GS to AC schemes; or Not}
\label{ssec:gs2ac}

Next, we describe black-box implications of separations when trying to build
anonymous credential schemes from group signature ones. \todo{Currently, I think
  it is possible to build \OMACSD from \PDGS, but not \MMACSD from \PDGS
  (although it should be possible to build \MMACSD from multi-group
  signatures...)}.

\subsubsection{Black-Box Construction of \OMACSD from \PDGS.} %
\doubt{I guess it is ok to have a black-box construction in which obatin/issue
  requires much more interaction... is it?}

\begin{figure}[ht!]
  \begin{center}
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure{$\OMACSDSetup(1^\OMACSDsec,1^\OMACSDnattr)$} {
          \PDGSparam \gets \PDGSSetup(1^\OMACSDsec) \\
          \pcreturn (1^\OMACSDsec,1^\OMACSDnattr,\PDGSparam) \\
        }

        \procedure{$\OMACSDUKeyGen(\OMACSDparam)$}{
          \textrm{Parse \OMACSDparam as $(1^\OMACSDsec,1^\OMACSDnattr,\PDGSparam)$} \\
          (\PDGSusk,\PDGSupk) \gets \PDGSUKeyGen(\PDGSparam) \\          
          \pcreturn \PDGSusk \\
        }

        \procedure{$\OMACSDShow(\OMACSDipk,\OMACSDattr,\OMACSDdattr,\OMACSDcred),$\\
          $\OMACSDVerify(\OMACSDipk,\OMACSDdattr)$}{
          \textrm{- \underline{Verifier}: Send random nonce $c$ to User} \\
          \textrm{- \underline{User}: } \\
          \pcind \textrm{Parse \OMACSDcred as
            $(\PDGSusk,n,\PDGSsig_n,\lbrace \PDGSsig_i \rbrace_{i \in [\OMACSDattr}])$} \\
          \pcind \PDGSsig_c \gets \PDGSSign(\PDGSusk,\PDGSgpk^u,c) \\
          \pcind \textrm{Send $(\PDGSsig_c,n,
            \PDGSsig_n,\lbrace \PDGSsig_i \rbrace_{i \in [\OMACSDdattr}])$ to Verifier} \\
          \textrm{- \underline{Verifier}:} \pccomment{If any check fails, abort} \\
          \pcind \PDGSVerify(\PDGSgpk^u,\PDGSsig_c,c) \\
          \pcind \pcfor i \in [\OMACSDdattr]: \\
          \pcind \pcind \PDGSVerify(\PDGSgpk^a,) \\
        }

      \end{minipage}
    }
    ~
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure{$\OMACSDIKeyGen(\OMACSDparam)$}{
          \textrm{Parse \OMACSDparam as $(1^\OMACSDsec,1^\OMACSDnattr,\PDGSparam)$} \\
          (\PDGSisk^a,\PDGSipk^a) \gets \PDGSIKeyGen(\PDGSparam)
          ~\pccomment{Attributes group} \\
          (\PDGSosk^a,\PDGSopk^a) \gets \PDGSOKeyGen(\PDGSparam) \\
          (\PDGSisk^u,\PDGSipk^u) \gets \PDGSIKeyGen(\PDGSparam) 
          ~\pccomment{Users group} \\
          (\PDGSosk^u,\PDGSopk^u) \gets \PDGSOKeyGen(\PDGSparam) \\
          \PDGSgpk^a \gets (\PDGSipk^a,\PDGSopk^a);
          \PDGSgpk^u \gets (\PDGSipk^u,\PDGSopk^u); \\
          \pcfor i \in [\OMACSDnattr]:
          ~\pccomment{Add one member per attribute} \\
          \pcind (\PDGSusk^a_i,\PDGSupk^a_i) \gets \PDGSUKeyGen(\PDGSparam) \\
          \pcind
          \PDGSucred^a_i \gets \langle \PDGSJoin(\PDGSgpk^a,\PDGSusk^a_i),
          \PDGSIssue(\PDGSgpk^a, \PDGSisk^a, \PDGSupk^a_i) \rangle \\
          \pcind \PDGSusk^a_i \gets (\PDGSusk^a_i, \PDGSucred^a_i) \\
          \pcreturn ((\PDGSisk_a,\PDGSisk_u,\PDGSosk_u,
          \lbrace \PDGSusk^a_i, \PDGSupk^a_i \rbrace_{i \in [\OMACSDnattr]}),
                     (\PDGSgpk_a,\PDGSosk_a,\PDGSgpk_u)) \\
        }

        \procedure{$\OMACSDObtain(\OMACSDusk,\OMACSDipk,\OMACSDattr),
          \OMACSDIssue(\OMACSDisk,\OMACSDupk,\OMACSDattr)$}{
          \pccomment{User and Issuer run the PDGS join/issue protocol}  \\
          \langle \PDGSucred,\PDGSutrans \rangle \gets
          \langle \PDGSJoin(\PDGSgpk^u,\PDGSusk),
          \PDGSIssue(\PDGSgpk^u, \PDGSisk^u, \PDGSupk) \rangle \\
          \PDGSusk \gets (\PDGSusk, \PDGSucred) \\
          \pccomment{User requests an OMAC} \\
          \textrm{- \underline{Issuer}: Send random nonce $n$ to User} \\
          \textrm{- \underline{User}: } \PDGSsig_n \gets \PDGSSign(\PDGSusk,\PDGSgpk,n);
          \textrm{Send $\PDGSsig_n$ to Issuer} \\
          \textrm{- \underline{Issuer}: } \\
          \pcind \pcif \PDGSVerify(\PDGSgpk,\PDGSsig_n,n) = 1~\textrm{and}\\
          \pcind \pcind \PDGSOpen(\PDGSgpk^u,\PDGSosk^u,\PDGSalltrans,\PDGSsig_n,n) = (\PDGSupk, \cdot): \\
          \pcind \pcind \pcfor i \in [\OMACSDattr]:
          \PDGSsig_i \gets \PDGSSign(\PDGSusk^a_i,\PDGSgpk^a,\PDGSsig_n) \\
          \pcind \textrm{Send $\lbrace \PDGSsig_i \rbrace_{i \in [\OMACSDnattr]}$ to User }
          \textrm{and \pcreturn 1} \\
          \textrm{- \underline{User}: } \\
          \pcind \pcfor i \in [\OMACSDattr]:
          \pcif \PDGSVerify(\PDGSgpk^a,\PDGSsig_i,\PDGSsig_n) = 0: \textrm{abort} \\
          \pcind \pcreturn (\PDGSusk, n,\PDGSsig_n,\lbrace \PDGSsig_i \rbrace_{i \in [\OMACSDattr}]) \\
        }

      \end{minipage}
    }
  \end{center}
  \caption{Black-box constrction of \OMACSD from \PDGS.
    \todo{In Show/Verify, user/issuer need to get \PDGSgpk from somewhere!}}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "soa-review"
%%% End:

### 2022-02-06 prism-backend/research/gsac/conclusion.tex
Creating branch for work on GSAC schemes.

--- 2021-11-29 prism-backend/research/soa_review/gs.tex
@@
-\section{Group Signatures}
-\label{sec:gs}
-
-\paragraph{Main intuition.}
-%
-Group signatures were first proposed by Chaum and van Heyst in 1991 \cite{ch91}
-as a privacy-respectful extension to conventional digital signatures.
-The intuition is simple: in order to avoid revealing the identity of the signer,
-we make her signatures look indistinguishable to the signatures of all other
-members of a group. Then, any entity with access to the group public key can
-verify that a group signature comes from a member of the group, but cannot
-tell which specific one actually created it.
-%
-Beyond this, group signature schemes have one main feature: a (set of) group
-manager(s) control who can become a member of the group. Also, most frequently,
-a (set of) group manager(s) decide when to expell a member from the group, or
-when to re-identify the creator of a specific signature.
-%
-The initial idea put forward in \cite{ch91} had, as is to be expected, a number
-of limitations. In the following years, the seminal work was extended, both
-formally, functionally, and efficiency-wise.
-
-\subsection{Approaches, Models, and Variations}
-\label{ssec:gsapproach}
-
-\subsubsection{Main approaches.}
-%
-There are two main ways that are recurrently used to instantiate group signature
-schemes: \emph{Sign-Encrypt-Prove} and \emph{Sign-Randomize-Prove}. In both
-variants, when new members of the group join, they receive a credential (i.e.,
-a signature by the issuer) derived from a secret they choose. Then, when
-creating a group signature, they prove control a valid credential and the
-associated secret. The difference lies on how this credential is kept hidden
-from the verifier.
-%
-In the sign-encrypt-prove variant, proposed in \cite{bmw03}, signers
-encrypt their credential and then
-create a NIZK \needcite proof of knowledge of such a valid credential
-over their secret (plus the message they want to sign). This typically results
-in schemes with more efficient openings, as the opening authority just has
-to decrypt the encrypted credential. However, group signatures require more
-space.
-%
-In the sign-randomize-prove variant, proposed in \needcite \todo{Get Shorty?},
-credentials are actually randomizable signatures by the issuer. Signers then
-randomize the signature (credential), and create a NIZK proof of knowledge that
-this credential is issued for a secret they know (again, plus the message
-they want to sign). This usually results in schemes with less efficient openings,
-as the opening authority needs to iterate over the registered credentials until
-finding the one from which the randomized credential was derived. However, the
-produced group signatures are also shorter.
-
-When a new user wants to become a group member, a common habit is also to have
-her prove ownership of a conventional digital identity. This identity is then
-added to the de-identifying information leveraged by the opening authority, in
-order to be able to associate (anonymous) group signatures to a real-world
-identity. These conventional digital identities can be any type of PKI-based
-(e.g. X.509 or equivalent) certificate. \todo{This is important for
-  non-frameability! Check \cite[Section 3.2]{cdl+20} and re-state this.}
-\todo{This is indeed necessary for non-repudiation (mentioned in
-  \cite[Section 4]{lpy12}).}
-\todo{Typically used in schemes with verifiable openings. See
-  \cite[Section 1.3.3]{bsi12}.}
-
-\subsubsection{Main security models.}
-%
-Security for group signatures is given in the form of game-based definitions.
-The first formal security model appeared in \cite{bmw03}. It captured security
-for groups with a prefixed set of members, added by the group manager upon the
-creation of the group. This static requirement was too restrictive to be
-realistic, and was quickly extended in \cite{bsz05} and \cite{kty04,ky06}, to
-model that new users can join the group after it has been created. The models
-in \cite{bsz05,kty04,ky06} are usually referred to as dynamic or partially
-dynamic. \cite{bcc+16} generalizes the (partially) dynamic setting into a fully
-dynamic model, which considers extra desirable security properties when users
-can be revoked (i.e., removed from the group).
-
-Up to some subtleties, the main security properties in most works that appeared
-after \cite{bmw03,bsz05,kty04,ky06} are as follows:
-
-\begin{itemize}
-\item {\bf Anonymity}. This is the core property concerning privacy. It
-  ensures that given a signature produced by one out of two honest (challenge)
-  users picked at random from the set of honest group members, it should be
-  unfeasible to determine which one actually created it.
-
-\item {\bf Traceability}. This property (covered by the misidentification attack
-  in \cite{kty04,ky06}, and spaning also non-frameability in \cite{bmw03})
-  captures that it must be possible (by the proper authority) to unambiguously
-  recover the identity of the signer of any valid group signature.
-
-\item {\bf Non-frameability}. This property (considered in the framing attacks
-  in \cite{kty04,ky06}) requires that no adversary should be able to create
-  valid signatures that can be used to incriminate honest users by having them
-  open to an honest user who did not create them.
-
-\end{itemize}
-
-\cite{bcc+16} also includes a trace soundness property, ensuring that signatures
-can be associated (via opening proofs) to only one user \todo{why does this not
-  appear in the other models? Maybe because they don't support verifiable
-  openings? Check \cite{kss19} and, if so, move this to the variations in
-  functionality.}
-
-\subsubsection{Variations in functionality.}
-%
-Note that, while the security properties just described roughly have the same
-purpose across models, there are still differences making some models stronger
-or more general than others in some respects. This includes subtleties like who
-generates the keys of the authorities (the environment vs the adversary), how
-many queries can be made to the challenge oracles and whether or not the
-signatures are fixed, etc. However, while important, there are usually generic
-techniques that allow to migrate from one variant to another \needcite. Now we
-are interested in revisiting some of
-the variations that have impact into the functionality that schemes
-following each model can provide, or variations that are specific to group
-signatures schemes and do not appear in other cryptosystems.
-
-\paragraph{Separating issuer and opener.}
-In some schemes \cite{bmw03,kty04} one single authority concentrates the
-power to add new members to the group, and open signatures. This endows such authority with great
-power -- and trust -- and is therefore one of the main concerns for privacy
-advocates: not only this authority can prevent users from joining (in the case
-of dynamic groups), but it can also reidentify group members. In order to reduce
-this trust, and since it is a clear distinction between both functionalities
-(issuing and opening), many schemes separate both roles into an issuer and an
-opener. While both authorities need to be trusted for their respective tasks,
-one can now make independent assumptions and even ensure certain properties
-if only one of the two authorities is compromised or malicious. For instance,
-non-frameability can be achieved even when both authorities are malicious;
-traceability can be achieved with malicious openers; and anonymity can be
-kept as long as the opener is honest. This is the case in \cite{bsz05} and
-\cite{ky06} (which, although starts from a single authority, also considers
-and formalises the case of separate authorities).
-
-\paragraph{Protecting against corrupt authorities.}
-Even when the issuance and opening functionalities are separated, as mentioned,
-each entity can unilaterally break crucial properties in a group signature scheme.
-While placing such kind of trust may be reasonable in some use cases, it may not
-be so for others. Thus, a natural extension is to reduce this trust as much as
-possible. In this direction, there have been works that have applied threshold
-and similar techniques \needcite to require that a set of openers (as opposed
-to a single opener) need to cooperate in order to open any group signature
-\cite{bcly08} \needcite.
-Recently, the role of the issuer was also subject to these techniques
-\cite{cdl+20}, and it is now known how to produce group signatures such that no
-single entity can prevent users from joining nor reidentify them.
-
-\paragraph{Forward security.}
-Forward security aims at restricting the impact of security compromises (e.g.,
-key leakage) to the future: i.e., if an attacker gains control of a user's
-private key, only signatures produced after the compromise should be considered
-invalid. In schemes that do not ensure forward secrecy, such a compromise also
-renders invalid signatures produced before the compromise. Note that, for
-conventional signatures, only the compromised user is (directly) affected by
-such event. However,  in group signatures, all group members are directly
-affected, as the signer's identity is not revealed by the signature. Thus,
-in order to learn whether or not a past signature was issued by a compromised
-user, it is necessary to resort to the opener -- therefore, reidentifying
-\emph{all} users in the system.
-%
-Forward security has been introduced in group signatures in works like
-\cite{song01,ly12}.
-%
-Interestingly (but logically), the approach to incorporate this property
-holds similarities with the functionality to implement fully dynamic group
-signatures: for forward security, users are usually required to apply an
-update procedure to their private keys \cite{ly12}; in fully dynamic group
-signatures \todo{fully dynamic gs have not been introduced yet!}, it is the
-group manager (or the opener) who has to update some
-key material \cite{bcc+16}. In both cases, time has to be discretized in epochs,
-and conditions are introduced into the security properties that prevent an
-adversary being able to deanonymize (produce) a valid signature generated
-(using) a key in an epoch in which such key was not supposed to be active
-(either because the user updated it -- in a forward secure scheme -- or the
-group manager revoked it -- in a fully dynamic scheme).
-
-\paragraph{\todo{Revocation mechanisms}.}
-Verifier Local Revocation \cite{bs04}, accumulators approach.
-
-\paragraph{Opening controls.}
-Even when separating the roles of the authorities or distributing them, the
-fact that some entity (or set of entities) can open group signatures is still
-a delicate matter that creates friction. A minimal control is to enable the
-opener to prove that the opening process has been performed honestly. This is
-precisely what is done by schemes that support \emph{verifiable opening}
-\needcite. To further aleviate this issue, some schemes
-introduce mechanisms to even prevent opening as long as some condition is
-met. For instance, in \cite{seh+12,ehk+19}, the condition is determined by
-the message (e.g., only signatures over offending messages can be opened).
-To implement this, the authors introduce an extra authority, the
-\emph{admitter}, such that the opener needs to get some information from the
-admitter in order to be able to open signatures over some specific message.
-In \cite{sbm10}, the authors propose \emph{contractual} anonymity: before a user
-is able to anonymously access some service, both user and service sign a
-contract defining the conditions upon which anonymity can be revoked. This
-contract can only be enforced by a trusted entity, the \emph{accountability
-  service} who runs a trusted execution environment (such as today's Intel
-SGX \needcite) ensuring that the conditions are checked in a trustworthy manner.
-
-\paragraph{Alternatives to opening.}
-%
-Even with separated authorities, with distributed openers, or with more generic
-opening controls such as message-dependent opening, opening may not even be
-the type of reduction of privacy that is necessary. In this vein, alternative
-schemes have been proposed that do not include any kind of
-opening at all.
-%
-In the schemes proposed in \cite{kty04,cpy06,bcly08}, there is an extra
-authority that can produce \emph{tracing} trapdoors on a per-user basis.
-Once the tracing trapdoor for a specific user is given to some entity, this
-entity can link (or trace) all group signatures produced by that user.
-These trapdoors are also an effective mechanism for implementing verifier-local
-revocation.
-%
-In \cite{gl19}, the opener is replaced by a \emph{converter} who, rather than
-opening any given group signature, can link sets of signatures. More
-specifically, when queried with a set of signatures, the converter transforms
-them so that every signature coming from the same user gets assigned a same
-randomized pseudonym. Furthermore, to prevent the converter from gradually
-relinking all the signatures, these conversions are non-transitive: i.e.,
-signatures produced by user $A$ will receive a different randomized pseudonym in
-different queries.
-%
-In \cite{dl21}, there is directly no trusted entity that can open or link group
-signatures. Instead, every user can create proofs of several signatures having
-been issued by herself. In this case, the authors also propose a scheme whereby
-a user can prove sequentiality of a set of signatures: i.e., that all signatures
-were produced by herself, and no signature has been omitted or inserted into the
-sequence, which is also given in the order in which the original signatures were
-produced.
-
-\subsubsection{Efficiency.}
+\section{Conclusion}
+\label{sec:conclusion}
 
 \comment{This section is just a placeholder for now...}
-
-\begin{itemize}
-\item Size of (group) keys.
-\item Size of signatures.
-\item Verification time (batching, including revocation checks...)
-\end{itemize}
-
-\subsubsection{Main challenges and interesting lines of work.}
-
-\comment{This section is just a placeholder for now...}
-
-Efficiency is possibly good for many real-world cases. Still: utility
-and unavailability of implementations.
-
-Concurrent joins -- avoid extraction \cite{ky05,klap20}.
-
-\subsection{Related Primitives}
-
-\comment{This section is just a placeholder for now...}
-
-\subsubsection{Ring Signatures}
-\label{sssec:rs}
-
-\cite{rst06}
-
-\cite{bcc+15} uses ring signatures to build a fully dynamic group signature
-scheme.
-
-\subsection{Applications}
-\label{ssec:gsapplication}
-
-\comment{This section is just a placeholder for now...}
-
-See \cite[Section 1.2.3]{bsi12}: it seems mostly theoretical applications.
-
-\subsubsection{Theory}
-\label{sssec:gstheoryapp}
-
-\comment{This section is just a placeholder for now...}
-
-\begin{itemize}
-\item GS-MDO imply IBE \cite{ehk+19}.
-\item GS are implied by trapdoor permutations \cite{bmw03}.
-\item GS imply one-way functions \cite{romp90}.
-\item GS imply public key encryption \cite{aw04}.
-\item Commitments from GS (ref. 25 in \cite{bfg+11}).
-\end{itemize}
-
-\subsubsection{Real World Deployments}
-\label{sssec:gsrwdeploy}
-
-\comment{This section is just a placeholder for now...}
-
-\cite{ehk+19} mentions anonymous auctions, anonymous bulletin boards and
-anomaly detection systems.
-
-Maybe make some comments on how to deploy gs schemes, or what aspects may be
-relevant. For instnace, some schemes/models (e.g. \cite{ly12}) assume a
-trusted party who generates the keys for the authorities. While this has
-a big impact in security/trust model, in the real world it would probably
-be circumventable with audited processes for most use cases. Also, the
-issue with concurrent issuance and the approach we took for implementing
-\cite{gl19} in ICT4Cart, or the limitation to logarithmic numbers of users, etc.
 

### 2022-02-06 prism-backend/research/gsac/gsac.tex
Creating branch for work on GSAC schemes.

--- 2021-11-09 prism-backend/research/soa_review/soa-review.tex
@@
 
-\title{State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication}
+\title{Group Signatures Meet Anonymous Credentials: Or, How to Build
+  Privacy Preserving Identities with Accountability}
 \author{}
@@
 \input{introduction.tex}
-\input{gs.tex}
-\input{abs.tex}
-\input{ac.tex}
-\input{daa.tex}
-\input{other.tex}
-\input{discussion.tex}
+\input{preliminaries.tex}
+\input{model.tex}
+\input{construction.tex}
+%\input{benchmarks.tex}
 \input{conclusion.tex}
 
-\section{TODOs}
+\bibliographystyle{splncs04}
+\bibliography{gsac}
 
-General/pending doubts and tasks:
-
-\begin{itemize}
-\item Many constructions of ACs and GSs seem to be built using the same
-  approach: an issuer and a user interact so that the latter receives a signature
-  from the former; then the user employs that signature to do something else (in
-  ACs, prove attributes; in GSs, produce further signatures). Still, the typical
-  security models are different. Concretely, GSs have a very well established
-  model, but ACs don't. It also ``bothers'' me that none of the AC models I've
-  seen cover something similar to non-frameability, nor traceability, but just
-  include conventional unforgeability properties. Why is this?
-\end{itemize}
-
-\bibliographystyle{splncs04}
-\bibliography{soa-review}
+% \appendix
 

### 2022-02-06 prism-backend/research/gsac/introduction.tex
Creating branch for work on GSAC schemes.

\section{Introduction}
\label{sec:introduction}

In this work, we combine two closely related schemes -- group signatures (GS)
and anonymous credentials (AC) -- which, for some reason, have followed a
separate path up to now, beyond individual constructions from both fields
drawing inspiration (and techniques) from one another. This combination is in
some sense a natural evolution, which we do believe may have relevant impact in
practical settings. On the one hand, anonymous credentials enable a richer
functionality in regards to what one can prove about his own identity, in a
privacy-preserving way. Academic proof of this is the fact that AC systems have
naturally evolved to enabling arbitrary claims that only reveal the minimally
possible 1-bit of information \needcite. Also, AC systems have been proposed to
go even beyond what one can prove about his identity, covering also orthogonal
functionality such as delegation \needcite, or aggregation of multiple
credentials into one \needcite. Even outside academia, prominent
technical workgroups \needcite, startups \needcite, and big techs \needcite are
promoting and adopting solutions which are directly inspired by AC systems. On
the other hand, GS 
schemes have inspection functionality (e.g., opening and linking of signatures)
at their core, which is reflected formally through non-frameability properties.
This has originated a large body of research focusing on the construction and
formalisation of variants of these notions \needcite. Consequently, group
signatures tend to be proposed for scenarios that require some sort of
de-anonymization \needcite. Indeed, this is not possible in ACs, which at most
support revocation of issued credentials, which essentially can compare to
linking, but not to opening-related notions.

Our goal is to get the best of both worlds: leverage the richer functionality
of ACs in what respects to proving, in a privacy-preserving manner, useful
claims on one's identity; and, at the same time support, through inspection
capabilities, use cases that may require some sort of de-anonymiztion. We
could target the ideal case of allowing to create proofs of arbitrary predicates
on one's identity (as some AC systems do), as well as provide flexible or several
notions of non-frameability. However, this being -- as far as we know -- the
first work that explores this intersection, we opt for keeping things simple
for the sake of facilitating technical precission and readability, and fostering
discussion. Therefore, we focus on the case of selective attribute disclosure
for ACs, and conventional opening for GSs, building a GSAC scheme that supports
both.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "sok-privsig"
%%% End:

### 2022-02-06 prism-backend/research/gsac/model.tex
Creating branch for work on GSAC schemes.

\section{Model for GSAC Systems}
\label{sec:model}

While group signatures and anonymous credentials share quite common syntax and
security properties, which are even frequently formalised in a similar way,
there are aspects that need to be considered with care.

The first choice that has to be made is whether to make sign/show and
verification a non-interactive or an interactive process -- in group signatures,
we are in the former case, whereas in anonymous credentials, we are in the
latter. While both options are of course valid, this has direct impact in the
modelling. We choose the non-interactive approach, and then prove how to
generically translate it into an interactive process. The reason is that this
results in a more flexible building block, suitable for a wider set of
scenarios. And, syntactically, it seems more natural to combine two
non-interactive processes into an interactive one, than the other way around.

We also need to take into account that, in group signature schemes, users only
get one membership credential -- typically bound to their personal secret
key --, which they then use to create as many group signatures as they want. On
the other hand, in anonymous credentials, users can get as many credentials as
they desire, which can (typically) then be showed also arbitrarily many times.
In this regard, we follow a somehow intermediate approach: users own a single
personal secret key, which they can use to get as many credentials as they wish.
Subsequently, they can use any of those credentials to create GSAC signatures.
This has, as expected, some nuanced impact in the modelling. For instance, in
group signatures, tracing and non-frameability are frequently dependent on the
open function, which (among other things) returns an index pointing to the join
transcript associated with the user who produced the signature given by the
adversary as a response to the game's challenge. In our approach, though, each
user may have many such transcripts -- one per credential that the user
obtains. However, note that what actually provides meaning to these notions
is not the index; but the associated user key pair, which is moreover necessary
to prove that the opening has been performed honestly. Thus, with some
restructuring of the corresponding games, we can still capture the main
meaning of these traceability and non-frameability notions from group
signatures. This also impacts anonymity, since in group signatures, this is
modelled by challenging the adversary to guess which user (which implicitly
translates to ``which user credential'') out of two challenge users was
leveraged to produce the challenge signature. But again, in our case, users may
have multiple credentials. However, it seems sufficient to adopt a similar
anonymity flavour to that of anonymous credentials, where the adversary has to
distinguish between presentations (signatures) produced from two arbitrary
credentials, independently on whether these credentials were obtained by the
same user, or not.

Getting closer to the anonymity definition of anonymous credentials also has the
side effect to introduce the notions of attributes for free into the domain of
group signatures -- which, up to now, had considered membership credentials
\emph{without} attributes. Yet another side effect of introducing multiple
attributes (if we think from a group signature perspective) is that, in order
to avoid trivial wins, the anonymity game has to enforce that both challenge
credentials reveal the same predicate on their attributes.

In the model described below, we follow closely the definitions from
\cite{bsz05} for group signatures, and \cite{fhs19} for anonymous credentials
(which are in turn influenced by \cite{bsz05}).

\subsection{Syntax}
\label{ssec:syntax}

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm)$.] Given global system parameters
  \parm, returns the issuer's key pair. Hereafter, we assume that the public
  part \ipk is added to the group public key \gpk.
\item[$(\opk,\osk) \gets \OKeyGen(\parm)$.] Given global system parameters
  \parm, returns an opener's key pair. Hereafter, we assume that the public part
  \opk is added to the group public key \gpk.
\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's key pair.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle \Obtain(\gpk,\usk,\Attrs),\Issue(\gpk,\isk,\upk,\Attrs) \rangle$.]
  This interactive protocol lets a user with key pair (\upk,\usk) running the
  \Obtain process, obtain a credential \cred with attributes \Attrs, by
  communicating with an issuer, with private key \isk, running the \Issue
  counterpart. The user outputs the produced credential \cred, while the issuer
  outputs the protocol transcript \utrans for the produced credential.
\item[$\sig \gets \Sign(\gpk,\usk,\cred,\Attrs,\DAttrs,\msg)$.] The user with
  with secret key \usk, who obtained a credential \cred for attributes \Attrs,
  produces a signature over message \msg, revealing subset \DAttrs of \Attrs.
\item[$1/0 \gets \Verify(\gpk,\sig,\DAttrs,\msg)$.] Checks whether \sig is a
  valid signature revealing the attribute set \DAttrs of its signing credential,
  over message \msg.
\item[$(\upk,\oproof) \gets \Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg)$.]
  Given a signature \sig over message \msg, produced by a credential with
  attributes containing the set \DAttrs, associated to transcript \utrans,
  returns the user public key that was used to obtain the credential, and a
  proof of opening correctness \oproof.  
\item[$1/0 \gets \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg)$.] Checks if
  \oproof is a valid opening correctness proof stating that the user with public
  key \upk generated the signature \sig over message \msg, by using a credential
  with attributes containing the set \DAttrs. 
\end{description}

The correctness and security properties are defined with the help of the
following sets of oracles, and global variables that help oracles and games
keep consistent state.

\paragraph{Global Variables.} %
All the honestly generated users (i.e., all honestly generated user key pairs,
since we assume a one-to-one relationship between user and user key pair), as
well as all honestly generated credentials, are assigned identifiers. That we
typically write as \uid for users, and \cid for credentials. The adversary can
refer to any individual user or credential using the corresponding identifier --
even though he may not know the actual contents of the key pairs or credentials.
In games that involve challenge user or credential identifiers, we use \cuid and
\ccid to refer to these challenge user/credential.
%
The games, usually through the oracles, keep track of the users (through
set \USK) and credentials (through table \CRED) that are created as a result of
oracle calls by the adversary, as well as the attributes that each credential
is associated (through table \ATTR), and the user to which each credential has
been issued to (through table \OWNR). We use the user and credential identifiers
to reference specific user key pairs, credentials, and credential attributes.
For instance, $\USK[\uid]$ refers to the user key pair corresponding to user
with identifier \uid, $\PUBUSK[\uid]$ refers to the public key of that key pair,
and $\PRVUSK[\uid]$ to the private key; credential $\CRED[\cid]$ refers to the
credential data associated to the credential with identifier \cid; $\ATTR[\cid]$
is the set of attributes that was assigned to the credential with identifier
\cid; and $\OWNR[\cid]$ is set to the \uid corresponding to the user that
credential \cid was issued to.
%
Additionally, the games keep track of all honest and corrupt users that have
been generated, through sets \HU and \CU, respectively. They also keep track of
the signatures that have been honestly produced, through the \SIG table. Since
signatures are produced through credentials, the \SIG table is indexed with
{\cid}s.
%
All global variables are initially set by the games to undefined values (denoted
with $\bot$, and all tables/sets are initialized as empty tables/sets, denoted
with $\empty$. Also, for readability, we abuse the syntax as follows: we write
$\CRED[\uid]$ to mean $\CRED[\cid]$ for all $\cid$ such that
$\OWNR[\cid] = \uid$; \todo{Something else?}

\paragraph{Oracles.} %
Oracles are the interface of the adversary with the corresponding games. In
other words: through these oracles, the game enviroment exposes to the adversary
functionality that could otherwise be executed only by honest parties with
private knowledge -- knowledge that would make the adversary capable of
trivially breaking the security properties formalized in the experiments.
In the game-based definitions of our GSAC model, we leverage the following
oracles, which are formally defined in \figref{fig:oracles}

\begin{description}
\item[$\HUGEN$.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[$\CUGEN$.] If the specified user identifier is not already in the game,
  sets the user public key to a value given by the adversary. If it already
  exists, and is associated to an honest user, then it reveals to the adversary
  the user's secret key.
\item[$\OBTISS$.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[$\OBTAIN$.] Enables the adversary to play the role of a dishonest issuer
  in games that support it, by letting it interact with honest users who want to
  receive credentials.
\item[$\ISSUE$.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials fo them.
\item[$\SIGN$.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[$\OPEN$.] Given an honestly produced signature, lets the adversary learn
  which credential was used to produce it.
\item[$\CHALb$.] Upon receiving two challenge credentials, a common intersecting
  set of attributes, and a message, returns a signature produced by one of these
  two credentials, defined by the bit $b$, which is established in the anonymity
  game.
\end{description}

{%\setlength\intextsep{\sep}
  \begin{figure*}[htp!]
    \centering
    \scalebox{0.9}{

      \begin{minipage}[t]{0.55\textwidth}

        \procedure{$\HUGEN(\uid)$}{%
          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
          (\upk,\usk) \gets \UKeyGen(\parm) \\
          \USK[\uid] \gets (\upk,\usk);
          \HU \gets \HU \cup \lbrace  \uid \rbrace \\
          \pcreturn \top \\
        }

        \procedure{$\CUGEN(\uid,\upk)$}{%
          \pcif \uid \in \CU: \pcreturn \bot \\
          \CU \gets \CU \cup \lbrace \uid \rbrace \\          
          \pcif \uid \in \HU: \\
          \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
          \pcind \pcreturn (\USK[\uid],\CRED[\uid]) \\
          \pcelse: \USK[\uid] = (\upk,\bot) \\          
          \pcreturn \top \\
        }

        \procedure{$\OBTISS(\uid,\cid,\Attrs)$}{%
          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\gpk,\PRVUSK[\uid],\Attrs), \\
          \pcind \pcind \pcind \pcind \pcind \pcind
          \Issue(\gpk,\isk,\PUBUSK[\uid],\Attrs) \rangle \\
          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
          \pcreturn \top \\
        }

        \procedure{$\OBTAIN(\uid,\cid,\Attrs)$}{%
          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\gpk,\PRVUSK[\uid],\Attrs),\Adv \rangle \\
          \CRED[\cid] \gets \cred \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
          \pcreturn \top \\
        }

      \end{minipage}
    }
    \scalebox{0.9}{

      \begin{minipage}[t]{.5\textwidth}

        \procedure{$\ISSUE(\uid,\cid,\Attrs)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \Adv, \Issue(\gpk,\isk,\PUBUSK[\uid],\Attrs) \rangle \\
          \trans[\cid] \gets \utrans \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
          \pcreturn \top \\          
        }

        \procedure{$\SIGN(\cid,\DAttrs,\msg)$}{%
          \uid \gets \OWNR[\cid] \\
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \cred \gets \CRED[\cid] \\
          \sig \gets \Sign(\gpk,\PRVUSK[\uid],\cred,\ATTR[\cid],\DAttrs,\msg) \\
          \SIG[\cid] \gets \SIG[\cid] \cup \lbrace (\sig,\DAttrs,\msg) \rbrace \\
          \pcreturn \sig \\
        }

        \procedure{$\OPEN(\sig)$}{%
          \textrm{Let}~\cid~\textrm{be s.t.}~(\sig,\DAttrs,\msg) \in \SIG[\cid] \\
          \pcif \textrm{no such \cid exists, or there is more than one}:
          \pcreturn \bot \\
          \pcif \trans[\cid] = \bot: \pcreturn \bot \\
          (\upk,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
          \pcreturn (\upk,\oproof) \\
        }

        \procedure{$\CHALb(\ccid_0,\ccid_1,\DAttrs,\msg)$}{%
          \pcif \ATTR[\ccid_0] \cap \ATTR[\ccid_1] \nsubseteq \DAttrs:
          \pcreturn \bot \\
          \pcif \cuid_0 \neq \bot \lor \cuid_1 \neq \bot: \pcreturn \bot \\
          \cuid_0 = \OWNR[\ccid_0];~\cuid_1 = \OWNR[\ccid_1] \\
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \csig \gets \Sign(\gpk,\USK[\cuid_b],\CRED[\ccid_b],
          \ATTR[\ccid_b],\DAttrs,\msg) \\
          \pcreturn \csig
        }

      \end{minipage}

    }

    \caption{Detailed oracles available in our model.}
    \label{fig:oracles}
  \end{figure*}
}

\paragraph{Correctness.} %
Correctness of GSAC schemes is formalized through the experiment in
\figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
revealing attributes \DAttrs, which was honestly produced though a credential
that was obtained by an honest user interacting with an honest issuer, with a
set of attributes \Attrs such that $\DAttrs \subseteq \Attrs$, must be accepted
by \Verify. Moreover, an honestly produced correctness proof of opening for such
signature, revealing the public key pair of the user, must also be accepted by
\Judge.

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
     \gpk \gets (\ipk,\opk) \\
    (\cid,\Attrs,\DAttrs,\msg) \gets \adv^{\HUGEN,\OBTISS}(\gpk) \\
    \pcif \DAttrs \nsubseteq \Attrs \lor \Attrs \nsubseteq \ATTR[\cid] :
    \pcreturn \bot \\
    \sig \gets \Sign(\gpk,\USK[\OWNR[\cid]],\CRED[\cid],\Attrs,\DAttrs,\msg) \\
    (\upk,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
    \pcif \Verify(\gpk, \sig, \DAttrs,\msg) = 0 \lor
    \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0:
    \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Correctness experiment for GSAC schemes.}
  \label{fig:exp-gsac-corr}
  \end{figure}

\subsection{Security Properties}
\label{ssec:security}

\subsection{Tranformation to Interactive Presentations}
\label{ssec:interactivetransform}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "gsac"
%%% End:

### 2022-02-06 prism-backend/research/gsac/preliminaries.tex
Creating branch for work on GSAC schemes.

\section{Preliminaries}
\label{sec:preliminaries}

\subsection{Related Work}
\label{ssec:related}

\todo{\textbf{IMPORTANT!} There actually seems to be closely related work
  on Attribute-Based Group Signatures (ABGS): \cite{khad07,emo09,aa14}.}

\subsection{Building Blocks}
\label{ssec:bblocks}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "gsac"
%%% End:

### 2022-02-06 prism-backend/research/soa_review/relationships.tex
Creating branch for work on GSAC schemes.

@@
 \label{sec:relationships}
+
+\todo{DISCLAIMER: This section contains a line of work we've put on hold for
+  now. Leaving it here just for archival purposes -- the reference definitions
+  for GS and AC may be of use (if we refine them!), at least for informational
+  purposes..}
 
@@
 
-As stated in \secref{sec:ac}, multi-show, multi-attribute anonymous credential
-schemes are the most frequent ones in the AC domain. While there are variations
-in the offered functionality (like those improving expressiveness of the
-supported claims) we assume selective disclosure as the base scheme. Also,
-we begin by modelling one-show schemes, which will ease our analysis.
-\doubt{Not $100\%$ sure of the latter yet, but take it as running hypothesis.}
-
 \subsubsection{One-Show Multi-Attribute AC with Selective Disclosure.} %
@@
 
-\subsection{From GS to AC schemes; or Not}
-\label{ssec:gs2ac}
-
-Next, we describe black-box implications of separations when trying to build
-anonymous credential schemes from group signature ones. \todo{Currently, I think
-  it is possible to build \OMACSD from \PDGS, but not \MMACSD from \PDGS
-  (although it should be possible to build \MMACSD from multi-group
-  signatures...)}.
-
-\subsubsection{Black-Box Construction of \OMACSD from \PDGS.} %
-\doubt{I guess it is ok to have a black-box construction in which obatin/issue
-  requires much more interaction... is it?}
-
-\begin{figure}[ht!]
-  \begin{center}
-    \scalebox{0.9}{
-      \begin{minipage}[t]{0.5\textwidth}
-        \procedure{$\OMACSDSetup(1^\OMACSDsec,1^\OMACSDnattr)$} {
-          \PDGSparam \gets \PDGSSetup(1^\OMACSDsec) \\
-          \pcreturn (1^\OMACSDsec,1^\OMACSDnattr,\PDGSparam) \\
-        }
-
-        \procedure{$\OMACSDUKeyGen(\OMACSDparam)$}{
-          \textrm{Parse \OMACSDparam as $(1^\OMACSDsec,1^\OMACSDnattr,\PDGSparam)$} \\
-          (\PDGSusk,\PDGSupk) \gets \PDGSUKeyGen(\PDGSparam) \\          
-          \pcreturn \PDGSusk \\
-        }
-
-        \procedure{$\OMACSDShow(\OMACSDipk,\OMACSDattr,\OMACSDdattr,\OMACSDcred),$\\
-          $\OMACSDVerify(\OMACSDipk,\OMACSDdattr)$}{
-          \textrm{- \underline{Verifier}: Send random nonce $c$ to User} \\
-          \textrm{- \underline{User}: } \\
-          \pcind \textrm{Parse \OMACSDcred as
-            $(\PDGSusk,n,\PDGSsig_n,\lbrace \PDGSsig_i \rbrace_{i \in [\OMACSDattr}])$} \\
-          \pcind \PDGSsig_c \gets \PDGSSign(\PDGSusk,\PDGSgpk^u,c) \\
-          \pcind \textrm{Send $(\PDGSsig_c,n,
-            \PDGSsig_n,\lbrace \PDGSsig_i \rbrace_{i \in [\OMACSDdattr}])$ to Verifier} \\
-          \textrm{- \underline{Verifier}:} \pccomment{If any check fails, abort} \\
-          \pcind \PDGSVerify(\PDGSgpk^u,\PDGSsig_c,c) \\
-          \pcind \pcfor i \in [\OMACSDdattr]: \\
-          \pcind \pcind \PDGSVerify(\PDGSgpk^a,) \\
-        }
-
-      \end{minipage}
-    }
-    ~
-    \scalebox{0.9}{
-      \begin{minipage}[t]{0.5\textwidth}
-        \procedure{$\OMACSDIKeyGen(\OMACSDparam)$}{
-          \textrm{Parse \OMACSDparam as $(1^\OMACSDsec,1^\OMACSDnattr,\PDGSparam)$} \\
-          (\PDGSisk^a,\PDGSipk^a) \gets \PDGSIKeyGen(\PDGSparam)
-          ~\pccomment{Attributes group} \\
-          (\PDGSosk^a,\PDGSopk^a) \gets \PDGSOKeyGen(\PDGSparam) \\
-          (\PDGSisk^u,\PDGSipk^u) \gets \PDGSIKeyGen(\PDGSparam) 
-          ~\pccomment{Users group} \\
-          (\PDGSosk^u,\PDGSopk^u) \gets \PDGSOKeyGen(\PDGSparam) \\
-          \PDGSgpk^a \gets (\PDGSipk^a,\PDGSopk^a);
-          \PDGSgpk^u \gets (\PDGSipk^u,\PDGSopk^u); \\
-          \pcfor i \in [\OMACSDnattr]:
-          ~\pccomment{Add one member per attribute} \\
-          \pcind (\PDGSusk^a_i,\PDGSupk^a_i) \gets \PDGSUKeyGen(\PDGSparam) \\
-          \pcind
-          \PDGSucred^a_i \gets \langle \PDGSJoin(\PDGSgpk^a,\PDGSusk^a_i),
-          \PDGSIssue(\PDGSgpk^a, \PDGSisk^a, \PDGSupk^a_i) \rangle \\
-          \pcind \PDGSusk^a_i \gets (\PDGSusk^a_i, \PDGSucred^a_i) \\
-          \pcreturn ((\PDGSisk_a,\PDGSisk_u,\PDGSosk_u,
-          \lbrace \PDGSusk^a_i, \PDGSupk^a_i \rbrace_{i \in [\OMACSDnattr]}),
-                     (\PDGSgpk_a,\PDGSosk_a,\PDGSgpk_u)) \\
-        }
-
-        \procedure{$\OMACSDObtain(\OMACSDusk,\OMACSDipk,\OMACSDattr),
-          \OMACSDIssue(\OMACSDisk,\OMACSDupk,\OMACSDattr)$}{
-          \pccomment{User and Issuer run the PDGS join/issue protocol}  \\
-          \langle \PDGSucred,\PDGSutrans \rangle \gets
-          \langle \PDGSJoin(\PDGSgpk^u,\PDGSusk),
-          \PDGSIssue(\PDGSgpk^u, \PDGSisk^u, \PDGSupk) \rangle \\
-          \PDGSusk \gets (\PDGSusk, \PDGSucred) \\
-          \pccomment{User requests an OMAC} \\
-          \textrm{- \underline{Issuer}: Send random nonce $n$ to User} \\
-          \textrm{- \underline{User}: } \PDGSsig_n \gets \PDGSSign(\PDGSusk,\PDGSgpk,n);
-          \textrm{Send $\PDGSsig_n$ to Issuer} \\
-          \textrm{- \underline{Issuer}: } \\
-          \pcind \pcif \PDGSVerify(\PDGSgpk,\PDGSsig_n,n) = 1~\textrm{and}\\
-          \pcind \pcind \PDGSOpen(\PDGSgpk^u,\PDGSosk^u,\PDGSalltrans,\PDGSsig_n,n) = (\PDGSupk, \cdot): \\
-          \pcind \pcind \pcfor i \in [\OMACSDattr]:
-          \PDGSsig_i \gets \PDGSSign(\PDGSusk^a_i,\PDGSgpk^a,\PDGSsig_n) \\
-          \pcind \textrm{Send $\lbrace \PDGSsig_i \rbrace_{i \in [\OMACSDnattr]}$ to User }
-          \textrm{and \pcreturn 1} \\
-          \textrm{- \underline{User}: } \\
-          \pcind \pcfor i \in [\OMACSDattr]:
-          \pcif \PDGSVerify(\PDGSgpk^a,\PDGSsig_i,\PDGSsig_n) = 0: \textrm{abort} \\
-          \pcind \pcreturn (\PDGSusk, n,\PDGSsig_n,\lbrace \PDGSsig_i \rbrace_{i \in [\OMACSDattr}]) \\
-        }
-
-      \end{minipage}
-    }
-  \end{center}
-  \caption{Black-box constrction of \OMACSD from \PDGS.
-    \todo{In Show/Verify, user/issuer need to get \PDGSgpk from somewhere!}}
-\end{figure}
-
 %%% Local Variables:

### 2022-02-08 prism-backend/research/gsac/model.tex
First complete version of the model.

@@
-\section{Model for GSAC Systems}
+\section{Model for \GSAC Schemes}
 \label{sec:model}
+
+\todo{Big doubt in this model. Currently, \Open (and \OPEN) return the public
+  key and credential of the signer along with the correctness proof. This is
+  as opposed to conventional practice, in which just an index and the proof
+  are returned. It is also intentional, as in the future I'd
+  like to extend \Open to a sort of functional version, where instead we return
+  a function of the user (secret or public) key, the credential, and the
+  signed message. However, I am not sure yet if this will be too strong to be
+  realized. If it is possible, though, our model would be stronger in this
+  sense. And also, I like this better, as by outputing an index, but then
+  requiring \Judge to use the public key (as in \cite{bsz05}) you impose the
+  need to create ad hoc protocols so that the \Judge learns the actual public
+  key, which in the real world can lead to very bad practices... (Such as
+  integrating the Judge inside the Opener, and not making the correctness
+  proof public -- hence, full trust in the Opener+Judge; or implementations
+  of \Open that directly output the public key instead of the index for
+  convenience, but in that case, deviating from the model and thus without
+  security guarantees.)}
 
@@
 personal secret key, which they can use to get as many credentials as they wish.
-Subsequently, they can use any of those credentials to create GSAC signatures.
+Subsequently, they can use any of those credentials to create \GSAC signatures.
 This has, as expected, some nuanced impact in the modelling. For instance, in
@@
   outputs the protocol transcript \utrans for the produced credential.
-\item[$\sig \gets \Sign(\gpk,\usk,\cred,\Attrs,\DAttrs,\msg)$.] The user with
-  with secret key \usk, who obtained a credential \cred for attributes \Attrs,
-  produces a signature over message \msg, revealing subset \DAttrs of \Attrs.
+\item[$\sig \gets \Sign(\gpk,\usk,\cred,\DAttrs,\msg)$.] The user with
+  with secret key \usk, who obtained a credential \cred, produces a signature
+  \sig over message \msg, revealing subset of attributes \DAttrs in \cred.
 \item[$1/0 \gets \Verify(\gpk,\sig,\DAttrs,\msg)$.] Checks whether \sig is a
@@
   over message \msg.
-\item[$(\upk,\oproof) \gets \Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg)$.]
+\item[$(\upk,\cred,\oproof)/\bot \gets
+  \Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg)$.]
   Given a signature \sig over message \msg, produced by a credential with
   attributes containing the set \DAttrs, associated to transcript \utrans,
-  returns the user public key that was used to obtain the credential, and a
-  proof of opening correctness \oproof.  
-\item[$1/0 \gets \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg)$.] Checks if
+  returns the user public key that was used to obtain the credential used for
+  producing \sig, the credential, and a proof of opening correctness \oproof; or
+  $\bot$ if the opening process fails.  
+\item[$1/0 \gets \Judge(\gpk,\upk,\cred,\oproof,\sig,\DAttrs,\msg)$.] Checks if
   \oproof is a valid opening correctness proof stating that the user with public
-  key \upk generated the signature \sig over message \msg, by using a credential
-  with attributes containing the set \DAttrs. 
+  key \upk generated the signature \sig over message \msg, by using credential
+  \cred with attributes containing the set \DAttrs. 
 \end{description}
@@
 signatures are produced through credentials, the \SIG table is indexed with
-{\cid}s.
+{\cid}s. For the anonymity game, we also need to keep track of the challenge
+signatures that the adversary has obtained, in order to prevent trivial wins
+by allowing any of them to be opened. 
 %
@@
 trivially breaking the security properties formalized in the experiments.
-In the game-based definitions of our GSAC model, we leverage the following
+In the game-based definitions of our \GSAC model, we leverage the following
 oracles, which are formally defined in \figref{fig:oracles}
@@
           \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\gpk,\PRVUSK[\uid],\Attrs),\Adv \rangle \\
+          \langle \Obtain(\gpk,\PRVUSK[\uid],\Attrs),\adv \rangle \\
           \CRED[\cid] \gets \cred \\
@@
           \langle \cdot, \utrans \rangle \gets
-          \langle \Adv, \Issue(\gpk,\isk,\PUBUSK[\uid],\Attrs) \rangle \\
+          \langle \adv, \Issue(\gpk,\isk,\PUBUSK[\uid],\Attrs) \rangle \\
           \trans[\cid] \gets \utrans \\
@@
           \cred \gets \CRED[\cid] \\
-          \sig \gets \Sign(\gpk,\PRVUSK[\uid],\cred,\ATTR[\cid],\DAttrs,\msg) \\
+          \sig \gets \Sign(\gpk,\PRVUSK[\uid],\cred,\DAttrs,\msg) \\
           \SIG[\cid] \gets \SIG[\cid] \cup \lbrace (\sig,\DAttrs,\msg) \rbrace \\
@@
           \textrm{Let}~\cid~\textrm{be s.t.}~(\sig,\DAttrs,\msg) \in \SIG[\cid] \\
-          \pcif \textrm{no such \cid exists, or there is more than one}:
-          \pcreturn \bot \\
-          \pcif \trans[\cid] = \bot: \pcreturn \bot \\
-          (\upk,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
-          \pcreturn (\upk,\oproof) \\
+          \pcif \textrm{no such \cid exists, or there is more than one}: \\
+          \pcind \pcreturn \bot \\
+          \pcif \sig \in \CSIG: \pcreturn \bot \\
+          (\upk,\cred,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
+%          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
+%          \CCRED \gets \CCRED \cup \lbrace \cid \rbrace \\
+          \pcreturn (\upk,\cred,\oproof) \\
         }
@@
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
-          \csig \gets \Sign(\gpk,\USK[\cuid_b],\CRED[\ccid_b],
-          \ATTR[\ccid_b],\DAttrs,\msg) \\
+ %         \pcif \ccid_0 \in \CCRED \lor \ccid_1 \in \CCRED: \pcreturn \bot \\
+          \csig \gets \Sign(\gpk,\PRVUSK[\cuid_b],\CRED[\ccid_b],
+          \DAttrs,\msg) \\
+          \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
           \pcreturn \csig
@@
 \paragraph{Correctness.} %
-Correctness of GSAC schemes is formalized through the experiment in
+Correctness of \GSAC schemes is formalized through the experiment in
 \figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
@@
      \gpk \gets (\ipk,\opk) \\
-    (\cid,\Attrs,\DAttrs,\msg) \gets \adv^{\HUGEN,\OBTISS}(\gpk) \\
-    \pcif \DAttrs \nsubseteq \Attrs \lor \Attrs \nsubseteq \ATTR[\cid] :
+    (\cid,\DAttrs,\msg) \gets \adv^{\HUGEN,\OBTISS}(\gpk) \\
+    \pcif \DAttrs \nsubseteq \ATTR[\cid] :
     \pcreturn \bot \\
-    \sig \gets \Sign(\gpk,\USK[\OWNR[\cid]],\CRED[\cid],\Attrs,\DAttrs,\msg) \\
+    \sig \gets \Sign(\gpk,\PRVUSK[\OWNR[\cid]],\CRED[\cid],\DAttrs,\msg) \\
     (\upk,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
@@
   }
-  \caption{Correctness experiment for GSAC schemes.}
+  \caption{Correctness experiment for \GSAC schemes.}
   \label{fig:exp-gsac-corr}
@@
 
+\paragraph{Anonymity.} %
+In group signatures, anonymity captures that no adversary must be able to learn,
+from any group signature, anything about its signer. In anonymous credentials,
+it requires that no adversary should learn anything about the holder of a
+credential that has been successfully shown, beyond that he owns a credential
+containing the revealed attributes. In both GS and AC, it is also typically
+required that
+multiple signatures/presentations by the users are unlinkable. The approach to
+formally state this property is in both cases frequently the same: the adversary
+picks two (honest) users (or credentials in the AC case), the game randomly
+chooses one of them, and lets the adversary request challenge
+signatures/presentations from it. The adversary wins if it succeeds in guessing
+which was the chosen user/credential better than guessing at random. In group
+signatures, the game must also restrict the adversary from opening challenge
+signatures. In anonymous credentials, the game must further constraint the
+adversary to output credentials that have some common subset of attributes, and
+to use that common subset to request the challenge presentations. Here, we need
+to take into account both. Furthermore, a key difference with group signatures
+is that the game requires the adversary to output credential identifiers, rather
+than user identifiers. Specifically, this means that the adversary may actually
+output two credentials that belong to the same user. Therefore, in some sense,
+the anonymity we get is more general than that of group signatures. The formal
+specification of the anonymity game is given in \figref{fig:exp-gsac-anonb}.
+%
+Similarly, this notion of anonymity is also stronger than the notion of
+anonymity in both group signatures and anonymous credentials, in the sense
+that calls to the \OPEN oracle reveal the public key and credential of the users
+that (via the \SIGN and \CHALb oracles) create the signatures that the adversary
+sees. Therefore, all security relies \emph{only} on the user secret key.
+
+\begin{figure}[htp!]
+  \procedure{$\ExpAnonb(1^\secpar)$}{%
+     \parm \gets \Setup(1^\secpar) \\
+     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
+     \gpk \gets (\ipk,\opk) \\
+     (\cid_0,\cid_1,\status) \gets
+     \adv^{\HUGEN,\CUGEN,\OBTAIN,\SIGN,\OPEN}(\choose,\gpk,\isk) \\
+     b^* \gets
+     \adv^{\HUGEN,\CUGEN,\OBTAIN,\SIGN,\OPEN,\CHALb}(\guess,\gpk,\isk,\status) \\
+     \pcreturn b^*
+  }
+  \caption{Anonymity experiment for \GSAC schemes.}
+  \label{fig:exp-gsac-anonb}
+\end{figure}
+
+\begin{definition}{(Anonymity of \GSAC)}
+  We define the advantage \AdvAnon of $\adv$ against \ExpAnonb as
+  $\AdvAnon=|\Pr\lbrack\ExpAnono(1^\secpar)=1\rbrack-
+  \Pr\lbrack\ExpAnonz(1^\secpar)=1\rbrack|$.
+  %
+  A \GSAC scheme satisfies anonymity if, for any p.p.t. adversary $\adv$,
+  \AdvAnon is a negligible function of $1^\secpar$.
+\end{definition}
+
+\paragraph{Traceability.} %
+Traceability is one of the unforgeability-related properties in group
+signatures. It captures that any signature accepted by \Verify needs to open
+to one of the users that joined the group. While there is no traceability notion
+in anonymous credentials, it is natural to map it to their unforgeability
+property; if only because both require the issuer to be honest. Unforgeability
+in anonymous credentials typically ensures that no adversary can get a verifier
+to accept a credential presentation requiring a set of attributes that is not
+contained in one of the credentials controlled by the adversary.
+%
+Our notion of traceability for \GSAC combines both requirements. It assumes an
+honest issuer, as otherwise the adversary can create untraceable credentials at
+will. The game then lets the adversary add honest and corrupt users, create
+honest signatures, and open them. The adversary wins if, after this interaction,
+is able to produce a $(\sig,\DAttrs,\msg)$ tuple that is accepted by \Verify,
+but either cannot be opened, it can be opened by the proof is rejected by
+\Judge, or even though it is accepted by \Judge, there was no issued credential
+(honest or not) that contained the set of attributes \DAttrs. We formally
+define traceability in the \ExpTrace experiment in \figref{fig:exp-gsac-trace}.
+
+\begin{figure}[htp!]
+  \procedure{$\ExpTrace(1^\secpar)$}{%
+     \parm \gets \Setup(1^\secpar) \\
+     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
+     \gpk \gets (\ipk,\opk) \\
+     (\sig,\DAttrs,\msg) \gets
+     \adv^{\HUGEN,\CUGEN,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
+     \pcreturn 1~\pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 1~\land~( \\
+     \pcind \pccomment{All \Obtain transcripts fail to open \sig} \\
+     \pcind \forall \utrans \in \trans:
+     \Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg) = \bot~\lor \\
+     \pcind \pccomment{Such transcript exists, but ...} \\
+     \pcind \exists~\utrans~\st~\Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg) =
+     (\upk,\cred,\oproof)~\land (\\
+     \pcind \pcind \pccomment{... the opening proof is rejected by \Judge ...} \\
+     \pcind \pcind \Judge(\gpk,\upk,\cred,\oproof,\sig,\DAttrs,\msg) = 0~\lor \\
+     \pcind \pcind \pccomment{... or \Judge accepts the proof, but \DAttrs was
+       not issued to any credential} \\
+     \pcind \pcind \DAttrs \nsubseteq \ATTR[\cred] \\
+     \pcind ) \\
+     ) \\
+     \pcreturn 0
+  }
+  \caption{Traceability experiment for \GSAC schemes.}
+  \label{fig:exp-gsac-trace}
+\end{figure}
+
+\begin{definition}{(Traceability of \GSAC)}
+  We define the advantage \AdvTrace of $\adv$ against \ExpTrace as
+  $\AdvTrace=\Pr\lbrack\ExpTrace(1^\secpar)=1\rbrack$.
+  %
+  A \GSAC scheme satisfies traceability if, for any p.p.t. adversary $\adv$,
+  \AdvTrace is a negligible function of $1^\secpar$.
+\end{definition}
+
+\paragraph{Non-frameability.} %
+Non-frameability variants are a core unforgeability-type property in group
+signatures. However, no
+similar property is modelled for anonymous credentials (\todo{see the discussion
+  in \secref{sec:introduction} for further detail}). It is a quite strong
+property, as it must be ensured even in the presence of dishonest issuer and
+opener. Intuitively, it prevents the adversary from creating a signature that
+frames an honest user. Depending on the inspection capabilities of the scheme,
+this framing could be done in different ways; i.e., by convincing third parties
+that signatures by different (possibly corrupt) users are linked, or directly
+by having open proofs output the identity of a user who did not create the
+signature being opened.
+%
+In \GSAC schemes, in order for a user to be framed, the adversary first needs to
+create a $(\sig,\DAttrs,\msg,\upk,\cred,\oproof)$ such that the signature,
+attributes, and message are accepted by \Verify, and which, along with the user
+public key, credential, and open correctness proof, are accepted by \Judge.
+Then, the adversary wins the game if the owner of the credential is honest, but
+the signature was not produced via the \SIGN oracle, or if the public key output
+by the adversary does not match the public key associated to the credential
+owner.
+%
+Note that, as in anonymity, this notion of non-frameability is even stronger
+to that of group signatures, since our \Open function returns both the public
+key and the credential that were used to create the signature.
+
+\begin{figure}[htp!]
+  \procedure{$\ExpNonframe(1^\secpar)$}{%
+    \parm \gets \Setup(1^\secpar) \\
+     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
+     \gpk \gets (\ipk,\opk) \\
+     (\sig,\DAttrs,\msg,\upk,\cred,\oproof) \gets
+     \adv^{\HUGEN,\CUGEN,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
+     \pcreturn 1~\pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 1 \land
+     \OWNR[\cred] \in \HU \\%\land \cred \notin \CCRED~\land\\
+     \pcind \Judge(\gpk,\upk,\cred,\oproof,\sig,\DAttrs,\msg) = 1~\land \\
+     \pcind \pccomment{\sig was not produced by \SIGN, or \upk and \cred do not match} \\
+     \pcind (\sig \notin \SIG[\OWNR[\cred]] \lor \PUBUSK[\OWNR[\cred]] \neq \upk) \\
+     \pcreturn 0
+  }
+  \caption{Non-frameability experiment for \GSAC schemes.}
+  \label{fig:exp-gsac-frame}
+\end{figure}
+
+\begin{definition}{(Non-frameability of \GSAC)}
+  We define the advantage \AdvNonframe of $\adv$ against \ExpNonframe as
+  $\AdvNonframe=\Pr\lbrack\ExpNonframe(1^\secpar)=1\rbrack$.
+  %
+  A \GSAC scheme satisfies non-frameability if, for any p.p.t. adversary $\adv$,
+  \AdvNonframe is a negligible function of $1^\secpar$.
+\end{definition}
+
+\paragraph{Discussion.} %
+\todo{Argue that our properties cover (and augment) a direct combination
+  (even if possible) of their GS and AC counterparts. Specifically, anonymity
+  of \GSAC is stronger than anonymity in GS and AC, and the same for trace and
+  non-frame.}
+
 \subsection{Tranformation to Interactive Presentations}
 \label{ssec:interactivetransform}
+
+\todo{Is it possible to give it in some generic sense?}
 

### 2022-02-08 prism-backend/research/gsac/preliminaries.tex
First complete version of the model.

@@
 \todo{\textbf{IMPORTANT!} There actually seems to be closely related work
-  on Attribute-Based Group Signatures (ABGS): \cite{khad07,emo09,aa14}.}
+  on Attribute-Based Group Signatures (ABGS): \cite{khad07a,khad07b,emo09,aa14}.}
+
+One difference between our current approach to GSAC, and the existing ABGS
+works, is that in ABGS each group member can only get one credential. On the
+other hand, we are trying to let any group member obtain as many credentials
+as he wishes, possibly with different attributes, albeit all of them related to
+the same user key pair (if a different user key pair is employed, then this is
+considered as a different user).
 

### 2022-02-09 prism-backend/research/gsac/introduction.tex
First complete version of the model.
Some minor edits.

@@
 In this work, we combine two closely related schemes -- group signatures (GS)
-and anonymous credentials (AC) -- which, for some reason, have followed a
+and anonymous credentials (AC) -- which have followed a
 separate path up to now, beyond individual constructions from both fields
@@
 for ACs, and conventional opening for GSs, building a GSAC scheme that supports
-both.
+both. \commentwho{Jesus}{This being the first work in this direction is not (at
+  least in part) true. See the related work section. Then update this
+  accordingly.}
 

### 2022-02-09 prism-backend/research/gsac/model.tex
Some minor edits.

@@
 modelling. We choose the non-interactive approach, and then prove how to
-generically translate it into an interactive process. The reason is that this
-results in a more flexible building block, suitable for a wider set of
-scenarios. And, syntactically, it seems more natural to combine two
+generically translate it into an interactive process \todo{do we?}. The reason
+is that this results in a more flexible building block, suitable for a wider set
+of scenarios. And, syntactically, it seems more natural to combine two
 non-interactive processes into an interactive one, than the other way around.
@@
 credentials reveal the same predicate on their attributes.
+\commentwho{Jesus}{Again, taking into account ABGS, this is no longer true.
+  Cross-check and re-write.}
 
@@
 since we assume a one-to-one relationship between user and user key pair), as
-well as all honestly generated credentials, are assigned identifiers. That we
-typically write as \uid for users, and \cid for credentials. The adversary can
+well as all honestly generated credentials, are assigned identifiers. Wex
+typically write as \uid for users' identifiers, and \cid for credentials'. The
+adversary can
 refer to any individual user or credential using the corresponding identifier --
@@
 %
-All global variables are initially set by the games to undefined values (denoted
-with $\bot$, and all tables/sets are initialized as empty tables/sets, denoted
-with $\empty$. Also, for readability, we abuse the syntax as follows: we write
-$\CRED[\uid]$ to mean $\CRED[\cid]$ for all $\cid$ such that
+All global variables are initially set by the games to empty values (denoted
+with $\bot$), and all tables/sets are initialized as empty tables/sets, denoted
+with $\emptyset$. Also, for readability, we abuse the syntax as follows: we
+write $\CRED[\uid]$ to mean $\CRED[\cid]$ for all $\cid$ such that
 $\OWNR[\cid] = \uid$; \todo{Something else?}
@@
 
+\todo{It would be nice to prove that a \GSAC scheme to which we remove the
+  \Open/\Judge functions becomes an AC scheme. And conversely, a \GSAC scheme
+  where all credentials have no attributes, and where we restrict to only
+  one credential per user, becomes a conventional GS scheme.}
+
 \subsection{Tranformation to Interactive Presentations}

### 2022-02-13 prism-backend/research/gsac/introduction.tex
Added review of ABGS.

@@
 \label{sec:introduction}
+
+\commentwho{Jesus}{The following will most probably change completely if we
+  are to submit this for publication. However, this should capture tha main
+  ideas.}
 
@@
 claims on one's identity; and, at the same time support, through inspection
-capabilities, use cases that may require some sort of de-anonymiztion. We
-could target the ideal case of allowing to create proofs of arbitrary predicates
-on one's identity (as some AC systems do), as well as provide flexible or several
-notions of non-frameability. However, this being -- as far as we know -- the
-first work that explores this intersection, we opt for keeping things simple
-for the sake of facilitating technical precission and readability, and fostering
-discussion. Therefore, we focus on the case of selective attribute disclosure
-for ACs, and conventional opening for GSs, building a GSAC scheme that supports
-both. \commentwho{Jesus}{This being the first work in this direction is not (at
-  least in part) true. See the related work section. Then update this
-  accordingly.}
+capabilities, use cases that may require some sort of de-anonymization. This is
+not the first work that somehow follows this direction, though --
+Attribute-Based Group Signatures, covered in \secref{ssec:related}, propose
+group signatures with attributes (although mentions to AC works from the ABGS
+papers are non-existent, so the resemblance seems circumstancial). However, we
+believe that ABGS lack the flexibility that has made AC schemes gain popularity
+recently. Hence, we propose a different approach that directly integrates GS
+features and properties with those of AC, as closely as possible to their
+original notions.
 

### 2022-02-13 prism-backend/research/gsac/preliminaries.tex
Added review of ABGS.

--- 2022-02-06 prism-backend/research/gsac/preliminaries.tex
@@
 
-\todo{\textbf{IMPORTANT!} There actually seems to be closely related work
-  on Attribute-Based Group Signatures (ABGS): \cite{khad07,emo09,aa14}.}
+\paragraph{Group Signatures and Anonymous Credentials.} %
+\todo{Brief summary of GS and AC here. Maybe split them in different
+  paragraphs.}
+
+\paragraph{Attribute-Based Group Signatures.} %
+The closest related works to our \GSAC are the series of Attribute-Based Group
+Signature schemes (ABGS) published between 2007 and 2014. The initial proposals
+\cite{khad07a,khad07b} defined a variant of group signatures in which membership
+credentials contained attributes. Yet, there are some
+crucial differences that make ABGS too rigid for practice. Ignoring that the
+first works \cite{khad07a,khad07b} are modelled as static group signatures
+(i.e., they do not allow dynamic joins of new members), each group has a static
+``attribute access tree'' associated to it. This tree defines what combinations
+of attributes make a signature valid. For instance, an example given in
+\cite{khad07b} requires group signatures to originate from an employee who is
+``a member of the IT department, and either at least a junior manager from the
+cryptography group, or a senior manager from the biometrics team''. If,
+eventually, a different attribute access tree is needed, a new group needs to
+be created. Additionally, only revocation is considered in \cite{khad07b},
+which is a subset of the accountability flavours that can be reached through
+the open function of conventional GS schemes. These schemes also lack formalism
+in their definitions. For instance, correctness does not cover correctness of
+revocation, and the anonymity definition does not seem to consider trivial wins
+by the adversary in which the adversary can revoke one of the two challenge
+users.
+%
+\cite{emo09} follows the attribute access tree aproach, but generalizes it so
+that attributes can be removed from the access tree, or the required conditions
+can be modified -- e.g., in \cite{emo09}, we could remove the ``or a senior
+manager from the biometrics team'' condition in the previous example. It also
+allows dynamic joins, and models open rather than just revocation. However,
+it does not
+allow adding new attributes; in that case, a new group has to be created. It
+also deviates from the conventional group signatures model, by introducing a
+\emph{collision-resistance} property that prevents different users from
+combining their membership credentials. While this is just a modelling choice
+with no impact in the actual functionality, it seems that this could be
+integrated within the existing traceability property, leading to a cleaner
+model. \todo{How does removing attributes or changing the access rules affect
+  anonymity? Is this considered?}
+%
+Finally, and as far as we know, \cite{aa14} is the last work in this ABGS line.
+They support dynamic joins, open and verifier-local revocation (hence, their
+variant is named VLR-ABGS). Furthermore, they include backwards unlinkability,
+meaning that a compromise of a user key at epoch $t$ does not affect anonymity
+of signatures on previous epochs by that same user. This scheme is still based
+on attribute access trees -- concretely, those in \cite{emo09}, and thus
+inherits its constraints. It also resorts to many properties, deviating from the
+cleaner approaches of GS schemes. Specifically, it defines security of VLR-ABGS
+by means of attribute anonymity (which is not formally defined),
+backwards-unlinkability user anonymity, traceability, non-frameability,
+attribute unforgeability, and collision resistance of attributes. Again, this
+are just modelling choices, but it would seem that several of these properties
+could be collapsed, hence leading to a cleaner model, much easier to evaluate
+(e.g., traceability, attribute unforgeability and collision resistance of
+attributes all seem similar).
+
+In summary, the previous line of ABGS seems to lack the flexibility of AC
+schemes in regards to what can be proven with attribute-based credentials.
+Restricting to AC with selective disclosure, one can get essentially the same
+functionality as with ABGS, but with flexible policies. That is, just let
+the verifier specify the policy that users need to meet depending on the
+situation, and only users revealing a matching subset of attributes will be
+accepted. In this respect, anonymity and unforgeability of ACs are equivalent to
+anonymity and traceability/unforgeability properties of ABGS. Still, an ABGS
+group is tied up to one concrete policy, while a single AC scheme spans
+arbitrarily many.
+%
+On the other hand, what ABGS (or, rather, some of its variants) adds with
+respect to AC schemes is the non-frameability property of group signatures,
+which opens the possibility to easily incorporate accountability notions.
+%
+In addition to what we have already mentioned, none of the ABGS works allows
+a group member to obtain multiple credentials -- not even from the same issuer.
+While obtaining multiple credentials in the setting of GS is not useful, it is
+if we include attributes and realize that the same user may have multiple
+attributes. This is certainly the case in multiple real life scenarios. For
+instance, the same person may obtain two different degrees within the same
+university; or an employee of a bank can also be a client. Both situations
+require attribute credentials issued by the same entity (the university, or
+the bank), none of them being a proper subset of the other, but still being
+associated to the same person.
+
+% One difference between our current approach to GSAC, and the existing ABGS
+% works, is that in ABGS each group member can only get one credential. On the
+% other hand, we are trying to let any group member obtain as many credentials
+% as he wishes, possibly with different attributes, albeit all of them related to
+% the same user key pair (if a different user key pair is employed, then this is
+% considered as a different user).
 

### 2022-02-15 prism-backend/research/gsac/uas-model.tex
Refined model of UAS. Working on properties.

--- 2022-02-09 prism-backend/research/gsac/model.tex
@@
-\section{Model for \GSAC Schemes}
-\label{sec:model}
+\section{Model for \UAS Schemes}
+\label{sec:model-uas}
 
-\todo{Big doubt in this model. Currently, \Open (and \OPEN) return the public
-  key and credential of the signer along with the correctness proof. This is
-  as opposed to conventional practice, in which just an index and the proof
-  are returned. It is also intentional, as in the future I'd
-  like to extend \Open to a sort of functional version, where instead we return
-  a function of the user (secret or public) key, the credential, and the
-  signed message. However, I am not sure yet if this will be too strong to be
-  realized. If it is possible, though, our model would be stronger in this
-  sense. And also, I like this better, as by outputing an index, but then
-  requiring \Judge to use the public key (as in \cite{bsz05}) you impose the
-  need to create ad hoc protocols so that the \Judge learns the actual public
-  key, which in the real world can lead to very bad practices... (Such as
-  integrating the Judge inside the Opener, and not making the correctness
-  proof public -- hence, full trust in the Opener+Judge; or implementations
-  of \Open that directly output the public key instead of the index for
-  convenience, but in that case, deviating from the model and thus without
-  security guarantees.)}
-
-While group signatures and anonymous credentials share quite common syntax and
-security properties, which are even frequently formalised in a similar way,
-there are aspects that need to be considered with care.
-
-The first choice that has to be made is whether to make sign/show and
-verification a non-interactive or an interactive process -- in group signatures,
-we are in the former case, whereas in anonymous credentials, we are in the
-latter. While both options are of course valid, this has direct impact in the
-modelling. We choose the non-interactive approach, and then prove how to
-generically translate it into an interactive process \todo{do we?}. The reason
-is that this results in a more flexible building block, suitable for a wider set
-of scenarios. And, syntactically, it seems more natural to combine two
-non-interactive processes into an interactive one, than the other way around.
-
-We also need to take into account that, in group signature schemes, users only
-get one membership credential -- typically bound to their personal secret
-key --, which they then use to create as many group signatures as they want. On
-the other hand, in anonymous credentials, users can get as many credentials as
-they desire, which can (typically) then be showed also arbitrarily many times.
-In this regard, we follow a somehow intermediate approach: users own a single
-personal secret key, which they can use to get as many credentials as they wish.
-Subsequently, they can use any of those credentials to create \GSAC signatures.
-This has, as expected, some nuanced impact in the modelling. For instance, in
-group signatures, tracing and non-frameability are frequently dependent on the
-open function, which (among other things) returns an index pointing to the join
-transcript associated with the user who produced the signature given by the
-adversary as a response to the game's challenge. In our approach, though, each
-user may have many such transcripts -- one per credential that the user
-obtains. However, note that what actually provides meaning to these notions
-is not the index; but the associated user key pair, which is moreover necessary
-to prove that the opening has been performed honestly. Thus, with some
-restructuring of the corresponding games, we can still capture the main
-meaning of these traceability and non-frameability notions from group
-signatures. This also impacts anonymity, since in group signatures, this is
-modelled by challenging the adversary to guess which user (which implicitly
-translates to ``which user credential'') out of two challenge users was
-leveraged to produce the challenge signature. But again, in our case, users may
-have multiple credentials. However, it seems sufficient to adopt a similar
-anonymity flavour to that of anonymous credentials, where the adversary has to
-distinguish between presentations (signatures) produced from two arbitrary
-credentials, independently on whether these credentials were obtained by the
-same user, or not.
-
-Getting closer to the anonymity definition of anonymous credentials also has the
-side effect to introduce the notions of attributes for free into the domain of
-group signatures -- which, up to now, had considered membership credentials
-\emph{without} attributes. Yet another side effect of introducing multiple
-attributes (if we think from a group signature perspective) is that, in order
-to avoid trivial wins, the anonymity game has to enforce that both challenge
-credentials reveal the same predicate on their attributes.
-\commentwho{Jesus}{Again, taking into account ABGS, this is no longer true.
-  Cross-check and re-write.}
-
-In the model described below, we follow closely the definitions from
-\cite{bsz05} for group signatures, and \cite{fhs19} for anonymous credentials
-(which are in turn influenced by \cite{bsz05}).
+Universal Anonymous Signatures.
 
@@
 
+In the following, we assume a setting with multiple groups. For simplicity,
+we assume that each has its own issuer and inspector.
+
+\todo{Are generalizations where different groups can share issuer or inspector
+  straight forward?} \\
+\todo{The notation for multisets is not strictly correct. Still, leaving it as
+  is for now.} \\
+\commentwho{Jesus}{I'm trying to define \Sign, \Verify, \Inspect and \Judge such
+  that multiple credentials can be used to produce a single signature, proving
+  claims over arbitrary subsets of all the credentials owned by a user. \Verify
+  and, consequently, \Inspect and \Judge need to receive all the \gpk's.
+  \Inspect only requires one inspector's secret key, though, and will thus only
+  produce that inspector's
+  function of the signature and message (this is to avoid complex interactive
+  protocols between many inspectors). This, however, creates a quite annoying
+  syntax. It may just be easier to restrict signatures to claims over the
+  attributes contained in \emph{one} credential.}
+
 \begin{description}
@@
   returns a global system parameter variable \parm.
-\item[$(\ipk,\isk) \gets \IKeyGen(\parm)$.] Given global system parameters
-  \parm, returns the issuer's key pair. Hereafter, we assume that the public
-  part \ipk is added to the group public key \gpk.
-\item[$(\opk,\osk) \gets \OKeyGen(\parm)$.] Given global system parameters
-  \parm, returns an opener's key pair. Hereafter, we assume that the public part
-  \opk is added to the group public key \gpk.
+\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\LangIss)$.] Given global system
+  parameters \parm, and the language \LangIss defining the NP relation for
+  issuance, an issuer runs this function to generate its issuing key pair.
+  Hereafter, we assume that the public part \ipk is added to the group public
+  key \gpk.
+\item[$(\opk,\osk) \gets \OKeyGen(\parm,\LangIns)$.] Given global system
+  parameters \parm, and the language \LangIns defining the NP relaton for
+  inspection, an inspector runs this function to generate its inspecting key
+  pair. It returns the inspector's key pair. Hereafter, we assume that the
+  public part \opk is added to the group public key \gpk.
 \item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
@@
 \item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle \Obtain(\gpk,\usk,\Attrs),\Issue(\gpk,\isk,\upk,\Attrs) \rangle$.]
+  \langle
+  \Obtain(\usk,\UAttrs,\DAttrs,\ldblbrace (gpk_i,\cred_i,\UAttrs_i,\DAttrs_i)\rdblbrace_{i \in \Issuers}),
+  \Issue(\isk,\DAttrs,\upk,\ldblbrace (\gpk_i,\DAttrs_i)\rdblbrace_{i \in \Issuers})
+  \rangle$.] %
   This interactive protocol lets a user with key pair (\upk,\usk) running the
-  \Obtain process, obtain a credential \cred with attributes \Attrs, by
-  communicating with an issuer, with private key \isk, running the \Issue
-  counterpart. The user outputs the produced credential \cred, while the issuer
-  outputs the protocol transcript \utrans for the produced credential.
-\item[$\sig \gets \Sign(\gpk,\usk,\cred,\DAttrs,\msg)$.] The user with
-  with secret key \usk, who obtained a credential \cred, produces a signature
-  \sig over message \msg, revealing subset of attributes \DAttrs in \cred.
-\item[$1/0 \gets \Verify(\gpk,\sig,\DAttrs,\msg)$.] Checks whether \sig is a
-  valid signature revealing the attribute set \DAttrs of its signing credential,
-  over message \msg.
-\item[$(\upk,\cred,\oproof)/\bot \gets
-  \Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg)$.]
-  Given a signature \sig over message \msg, produced by a credential with
-  attributes containing the set \DAttrs, associated to transcript \utrans,
-  returns the user public key that was used to obtain the credential used for
-  producing \sig, the credential, and a proof of opening correctness \oproof; or
-  $\bot$ if the opening process fails.  
-\item[$1/0 \gets \Judge(\gpk,\upk,\cred,\oproof,\sig,\DAttrs,\msg)$.] Checks if
-  \oproof is a valid opening correctness proof stating that the user with public
-  key \upk generated the signature \sig over message \msg, by using credential
-  \cred with attributes containing the set \DAttrs. 
+  \Obtain process, obtain a credential \cred from an issuer in the system, on
+  attribute set $\UAttrs \cup \DAttrs$, where the attributes in $\UAttrs$ are
+  kept hidden from the issuer, while those in \DAttrs are revealed. In order
+  to get the credential, the user may leverage previously obtained credentials
+  $\cred_i$ from a multiset of other issuers (including the one to whom a new
+  credential is being requested) with public keys $\gpk_i$. Moreover, each
+  credential $\cred_i$ can be used to prove claims over undisclosed attributes
+  $\UAttrs_i$ that the user wishes to include in the new credential. The user
+  outputs the produced credential \cred, while the issuer outputs the protocol
+  transcript \utrans for the produced credential.
+\item[$\sig \gets \Sign(\usk,\ldblbrace (\gpk_i,\cred_i,\UAttrs_i,\DAttrs_i)
+  \rdblbrace_{i \in \Issuers},\msg)$.] %
+  The user with with secret key \usk, who obtained credentials $\cred_i$ from a
+  multiset of issuers in the system, produces a signature \sig over message
+  \msg. The produced signature proves arbitrary claims over the set of
+  disclosed attributes $\bigcup_i \DAttrs_i$ and undisclosed attributes
+  $\bigcup_i \UAttrs_i$.
+\item[$1/0 \gets
+  \Verify(\sig,\msg,\ldblbrace (\gpk_i,\DAttrs_i) \rdblbrace_{i \in \Issuers})$.]
+  Checks whether \sig is a valid signature, over message \msg, satisfying
+  arbitrary claims over disclosed attributes $\bigcup_i \DAttrs_i$, as well as
+  potentially other undisclosed attributes endorsed by issuers in the systsem
+  with public keys $\bigcup_i \gpk_i$.
+\item[$(\y,\iproof)/\bot \gets
+  \Inspect(\osk,\utrans,\sig,\msg,
+  \ldblbrace (\gpk_i,\DAttrs_i) \rdblbrace_{i \in \Issuers})$.] %
+  \commentwho{Jesus}{I do not like this definition. It's complicated. This needs
+    to be rephrased from scratch.}
+  Executed by the inspector with opening key \osk. Receives a signature \sig
+  over message \msg, produced by a set of credentials satisfying claims on
+  disclosed attributes $\bigcup_i \DAttrs_i$, as well as potentially undisclosed
+  attributes, all endorsed by a multiset of issuers with public keys $\gpk_i$. 
+  If \utrans is a valid transcript of the execution of a
+  $\langle\Obtain,\Issue\rangle$ interactive protocol where the signer obtained
+  the credential associated to the inspector's group, then the function outputs
+  a value $\y$ derived from the signer's credential and public key, and the
+  signed message, as well as a proof of correct inspection.
+\item[$1/0 \gets \Judge(\y,\iproof,\sig,\msg,
+  \ldblbrace (\gpk_i,\DAttrs_i)\rdblbrace_{i \in \Issuers})$.] %
+  Checks if \iproof is a valid inspection correctness proof for the value \y,
+  obtained by applying \Inspect to the the pair signature \sig over \msg. 
 \end{description}
@@
 since we assume a one-to-one relationship between user and user key pair), as
-well as all honestly generated credentials, are assigned identifiers. Wex
+well as all honestly generated credentials, are assigned identifiers. Week's
 typically write as \uid for users' identifiers, and \cid for credentials'. The
@@
 Oracles are the interface of the adversary with the corresponding games. In
-other words: through these oracles, the game enviroment exposes to the adversary
+other words: through these oracles, the game environment exposes to the adversary
 functionality that could otherwise be executed only by honest parties with
@@
 \item[$\ISSUE$.] Allows the adversary to play the role of dishonest users,
-  requesting an honest issuer to produce credentials fo them.
+  requesting an honest issuer to produce credentials for them.
 \item[$\SIGN$.] Lets the adversary get signatures from credentials belonging
@@
 signatures. However, no
-similar property is modelled for anonymous credentials (\todo{see the discussion
+similar property is modeled for anonymous credentials (\todo{see the discussion
   in \secref{sec:introduction} for further detail}). It is a quite strong
@@
 
-\subsection{Tranformation to Interactive Presentations}
+\subsection{Transformation to Interactive Presentations}
 \label{ssec:interactivetransform}

### 2022-02-16 prism-backend/research/gsac/uas-model.tex
Still refining model of UAS: oracle definitions.

@@
   \langle
-  \Obtain(\usk,\UAttrs,\DAttrs,\ldblbrace (gpk_i,\cred_i,\UAttrs_i,\DAttrs_i)\rdblbrace_{i \in \Issuers}),
-  \Issue(\isk,\DAttrs,\upk,\ldblbrace (\gpk_i,\DAttrs_i)\rdblbrace_{i \in \Issuers})
+  \Obtain(\usk,\uattrs,\dattrs,\ldblbrace (gpk_i,\cred_i,\uattrs_i,\dattrs_i)\rdblbrace_{i \in \Issuers}),
+  \Issue(\isk,\upk,\ldblbrace (\gpk_i,\dattrs_i)\rdblbrace_{i \in \Issuers})
   \rangle$.] %
@@
   \Obtain process, obtain a credential \cred from an issuer in the system, on
-  attribute set $\UAttrs \cup \DAttrs$, where the attributes in $\UAttrs$ are
-  kept hidden from the issuer, while those in \DAttrs are revealed. In order
-  to get the credential, the user may leverage previously obtained credentials
-  $\cred_i$ from a multiset of other issuers (including the one to whom a new
-  credential is being requested) with public keys $\gpk_i$. Moreover, each
-  credential $\cred_i$ can be used to prove claims over undisclosed attributes
-  $\UAttrs_i$ that the user wishes to include in the new credential. The user
+  attribute set $\uattrs \cup \dattrs$, where the attributes in $\uattrs$ (and
+  the ones in the $\uattrs_i$'s) are kept hidden from the issuer, while those in
+  \dattrs (as well as those in the $\dattrs_i$'s) are revealed. Moreover,
+  $\uattrs \cup \dattrs$ must be a subset of $\bigcup_i (\uattrs_i \cup
+  \dattrs_i)$. In order to get the credential, the user may leverage previously
+  obtained credentials $\cred_i$ from a multiset of other issuers (including the
+  one to whom a new credential is being requested) with public keys $\gpk_i$.
+  Moreover, each credential $\cred_i$ can be used to prove claims over
+  undisclosed attributes $\uattrs_i$. The user
   outputs the produced credential \cred, while the issuer outputs the protocol
   transcript \utrans for the produced credential.
-\item[$\sig \gets \Sign(\usk,\ldblbrace (\gpk_i,\cred_i,\UAttrs_i,\DAttrs_i)
+\item[$\sig \gets \Sign(\usk,\ldblbrace (\gpk_i,\cred_i,\uattrs_i,\dattrs_i)
   \rdblbrace_{i \in \Issuers},\msg)$.] %
@@
   \msg. The produced signature proves arbitrary claims over the set of
-  disclosed attributes $\bigcup_i \DAttrs_i$ and undisclosed attributes
-  $\bigcup_i \UAttrs_i$.
+  disclosed attributes $\bigcup_i \dattrs_i$ and undisclosed attributes
+  $\bigcup_i \uattrs_i$.
 \item[$1/0 \gets
-  \Verify(\sig,\msg,\ldblbrace (\gpk_i,\DAttrs_i) \rdblbrace_{i \in \Issuers})$.]
+  \Verify(\sig,\msg,\ldblbrace (\gpk_i,\dattrs_i) \rdblbrace_{i \in \Issuers})$.]
   Checks whether \sig is a valid signature, over message \msg, satisfying
-  arbitrary claims over disclosed attributes $\bigcup_i \DAttrs_i$, as well as
+  arbitrary claims over disclosed attributes $\bigcup_i \dattrs_i$, as well as
   potentially other undisclosed attributes endorsed by issuers in the systsem
@@
   \Inspect(\osk,\utrans,\sig,\msg,
-  \ldblbrace (\gpk_i,\DAttrs_i) \rdblbrace_{i \in \Issuers})$.] %
+  \ldblbrace (\gpk_i,\dattrs_i) \rdblbrace_{i \in \Issuers})$.] %
   \commentwho{Jesus}{I do not like this definition. It's complicated. This needs
@@
   over message \msg, produced by a set of credentials satisfying claims on
-  disclosed attributes $\bigcup_i \DAttrs_i$, as well as potentially undisclosed
+  disclosed attributes $\bigcup_i \dattrs_i$, as well as potentially undisclosed
   attributes, all endorsed by a multiset of issuers with public keys $\gpk_i$. 
@@
 \item[$1/0 \gets \Judge(\y,\iproof,\sig,\msg,
-  \ldblbrace (\gpk_i,\DAttrs_i)\rdblbrace_{i \in \Issuers})$.] %
+  \ldblbrace (\gpk_i,\dattrs_i)\rdblbrace_{i \in \Issuers})$.] %
   Checks if \iproof is a valid inspection correctness proof for the value \y,
@@
 The games, usually through the oracles, keep track of the users (through
-set \USK) and credentials (through table \CRED) that are created as a result of
+set \UK) and credentials (through table \CRED) that are created as a result of
 oracle calls by the adversary, as well as the attributes that each credential
@@
 to reference specific user key pairs, credentials, and credential attributes.
-For instance, $\USK[\uid]$ refers to the user key pair corresponding to user
-with identifier \uid, $\PUBUSK[\uid]$ refers to the public key of that key pair,
-and $\PRVUSK[\uid]$ to the private key; credential $\CRED[\cid]$ refers to the
+For instance, $\UK[\uid]$ refers to the user key pair corresponding to user
+with identifier \uid, $\PUBUK[\uid]$ refers to the public key of that key pair,
+and $\PRVUK[\uid]$ to the private key; credential $\CRED[\cid]$ refers to the
 credential data associated to the credential with identifier \cid; $\ATTR[\cid]$
@@
 In the game-based definitions of our \GSAC model, we leverage the following
-oracles, which are formally defined in \figref{fig:oracles}
+oracles, which are formally defined in \figref{fig:oracles}. Note that we
+identify issuers and inspectors by the group identifier.
 
 \begin{description}
-\item[$\HUGEN$.] Adds a new honest user to the game, by honestly generating
+\item[\HIGEN.] Adds a new honest issuer to the game, by honestly generating
+  its key pair.
+\item[\CIGEN.] Adds a new corrupt issuer to the game or, if the specified issuer
+  already exists and is honest, corrupts it.
+\item[\HOGEN.] Adds a new honest inspector to the game, by honestly generating
+  its key pair.
+\item[\COGEN.] Adds a new corrupt inspector to the game or, if the specified
+  inspector already exists and is honest, corrupts it. 
+\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
   the user's key pair.
-\item[$\CUGEN$.] If the specified user identifier is not already in the game,
-  sets the user public key to a value given by the adversary. If it already
-  exists, and is associated to an honest user, then it reveals to the adversary
-  the user's secret key.
-\item[$\OBTISS$.] Lets the adversary add a new honestly generated credential to
+\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
+  user already exists and is honest, corrupts it.
+\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
   the game, on behalf of an honest user.
-\item[$\OBTAIN$.] Enables the adversary to play the role of a dishonest issuer
+\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
   in games that support it, by letting it interact with honest users who want to
   receive credentials.
-\item[$\ISSUE$.] Allows the adversary to play the role of dishonest users,
+\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
   requesting an honest issuer to produce credentials for them.
-\item[$\SIGN$.] Lets the adversary get signatures from credentials belonging
+\item[\SIGN.] Lets the adversary get signatures from credentials belonging
   to honest users.
-\item[$\OPEN$.] Given an honestly produced signature, lets the adversary learn
+\item[\OPEN.] Given an honestly produced signature, lets the adversary learn
   which credential was used to produce it.
-\item[$\CHALb$.] Upon receiving two challenge credentials, a common intersecting
+\item[\CHALb.] Upon receiving two challenge credentials, a common intersecting
   set of attributes, and a message, returns a signature produced by one of these
@@
 
+        \procedure{$\HIGEN(\gid,\fissue)$}{%
+          \pcif \gid \in \HI \lor \gid \in \CI: \pcreturn \bot \\
+          (\ipk,\isk) \gets \IKeyGen(\parm) \\
+          \IK[\gid] \gets (\ipk,\isk,\fissue);
+          \HI \gets \HI \cup \lbrace \gid \rbrace \\
+          \pcreturn \ipk \\
+        }
+
+        \procedure{$\CIGEN(\gid,\ipk,\fissue)$}{%
+          \pcif \gid \in \CI: \pcreturn \bot \\
+          \CI \gets \CI \cup \lbrace \gid \rbrace \\          
+          \pcif \gid \in \HI: \\
+          \pcind \HI \gets \HI \setminus \lbrace \gid \rbrace; \\
+          \pcind \pcreturn \IK[\gid] \\
+          \pcelse: \IK[\gid] = (\ipk,\bot,\fissue) \\          
+          \pcreturn \top \\
+        }
+
         \procedure{$\HUGEN(\uid)$}{%
@@
           (\upk,\usk) \gets \UKeyGen(\parm) \\
-          \USK[\uid] \gets (\upk,\usk);
+          \UK[\uid] \gets (\upk,\usk);
           \HU \gets \HU \cup \lbrace  \uid \rbrace \\
@@
 
-        \procedure{$\CUGEN(\uid,\upk)$}{%
-          \pcif \uid \in \CU: \pcreturn \bot \\
-          \CU \gets \CU \cup \lbrace \uid \rbrace \\          
-          \pcif \uid \in \HU: \\
-          \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
-          \pcind \pcreturn (\USK[\uid],\CRED[\uid]) \\
-          \pcelse: \USK[\uid] = (\upk,\bot) \\          
+        \procedure{$\ISSUE(\cid,\uid,\gid,
+          \lbrace (\sgid,\scid,\dattrs) \rbrace)$}{%
+          \pcif \uid \notin \CU: \pcreturn \bot \\
+          \pcif \gid \notin \HI: \pcreturn \bot \\
+          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
+          \pcif \exists \cid \in \scid~\st~\CRED[\cid] \neq \bot: \pcreturn \bot \\
+          \langle \cdot, \utrans \rangle \gets
+          \langle \adv, %
+          \Issue(\PRVIK[\gid],\PUBUK[\uid],(\GK[\gid],\dattrs)) \rangle \\
+          \trans[\cid] \gets \utrans \\
+          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \bot, \dattrs) \\
           \pcreturn \top \\          
@@
 
-        \procedure{$\OBTISS(\uid,\cid,\Attrs)$}{%
-          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
+        \procedure{$\OBTISS(\cid,\uid,\gid,
+          \lbrace (\sgpk,\scid,\uattrs,\dattrs) \rbrace)$}{%
+          \pcif \uid \notin \HU: \pcreturn \bot \\
+          \pcif \gid \notin \HI: \pcreturn \bot \\          
+          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
+          \pcif \exists \cid \in \scid~\st~\CRED[\cid] \neq \bot: \pcreturn \bot \\
           \langle \cred, \utrans \rangle \gets
-          \langle \Obtain(\gpk,\PRVUSK[\uid],\Attrs), \\
+          \langle \Obtain(\gpk,\PRVUK[\uid],\attrs), \\
           \pcind \pcind \pcind \pcind \pcind \pcind
-          \Issue(\gpk,\isk,\PUBUSK[\uid],\Attrs) \rangle \\
+          \Issue(\gpk,\isk,\PUBUK[\uid],\attrs) \rangle \\
           \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
+          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \attrs \\
           \pcreturn \top \\
@@
 
-        \procedure{$\OBTAIN(\uid,\cid,\Attrs)$}{%
+        \procedure{$\OBTAIN(\cid,\uid,\gid,
+          \lbrace (\sgpk,\scid,\uattrs,\dattrs) \rbrace)$}{%
           \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
@@
           \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\gpk,\PRVUSK[\uid],\Attrs),\adv \rangle \\
+          \langle \Obtain(\gpk,\PRVUK[\uid],\attrs),\adv \rangle \\
           \CRED[\cid] \gets \cred \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
+          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \attrs \\
           \pcreturn \top \\
@@
 
-        \procedure{$\ISSUE(\uid,\cid,\Attrs)$}{%
-          \pcif \uid \notin \CU: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
-          \langle \cdot, \utrans \rangle \gets
-          \langle \adv, \Issue(\gpk,\isk,\PUBUSK[\uid],\Attrs) \rangle \\
-          \trans[\cid] \gets \utrans \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
+        \procedure{$\HOGEN(\gid,\feval,\finsp)$}{%
+          \pcif \gid \in \HO \lor \gid \in \CO: \pcreturn \bot \\
+          (\opk,\osk) \gets \OKeyGen(\parm) \\
+          \OK[\gid] \gets (\opk,\osk,\feval,\finsp);
+          \HO \gets \HO \cup \lbrace  \gid \rbrace \\
+          \pcreturn \opk \\
+        }
+
+        \procedure{$\COGEN(\gid,\opk,\feval,\finsp)$}{%
+          \pcif \gid \in \CO: \pcreturn \bot \\
+          \CO \gets \CO \cup \lbrace \gid \rbrace \\          
+          \pcif \gid \in \HO: \\
+          \pcind \HO \gets \HO \setminus \lbrace \gid \rbrace; \\
+          \pcind \pcreturn \OK[\gid]) \\
+          \pcelse: \OK[\gid] = (\opk,\bot,\feval,\finsp) \\
           \pcreturn \top \\
@@
 
-        \procedure{$\SIGN(\cid,\DAttrs,\msg)$}{%
+        \procedure{$\CUGEN(\uid,\upk)$}{%
+          \pcif \uid \in \CU: \pcreturn \bot \\
+          \CU \gets \CU \cup \lbrace \uid \rbrace \\          
+          \pcif \uid \in \HU: \\
+          \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
+          \pcind \pcreturn (\UK[\uid],\CRED[\uid]) \\
+          \pcelse: \UK[\uid] = (\upk,\bot) \\          
+          \pcreturn \top \\
+        }
+
+        \procedure{$\SIGN(\msg,
+          \lbrace (\scid,\uattrs,\dattrs) \rbrace )$}{%
           \uid \gets \OWNR[\cid] \\
@@
           \cred \gets \CRED[\cid] \\
-          \sig \gets \Sign(\gpk,\PRVUSK[\uid],\cred,\DAttrs,\msg) \\
-          \SIG[\cid] \gets \SIG[\cid] \cup \lbrace (\sig,\DAttrs,\msg) \rbrace \\
+          \sig \gets \Sign(\gpk,\PRVUK[\uid],\cred,\dattrs,\msg) \\
+          \SIG[\cid] \gets \SIG[\cid] \cup \lbrace (\sig,\dattrs,\msg) \rbrace \\
           \pcreturn \sig \\
@@
         \procedure{$\OPEN(\sig)$}{%
-          \textrm{Let}~\cid~\textrm{be s.t.}~(\sig,\DAttrs,\msg) \in \SIG[\cid] \\
+          \textrm{Let}~\cid~\textrm{be s.t.}~(\sig,\dattrs,\msg) \in \SIG[\cid] \\
           \pcif \textrm{no such \cid exists, or there is more than one}: \\
@@
           \pcif \sig \in \CSIG: \pcreturn \bot \\
-          (\upk,\cred,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
+          (\upk,\cred,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\dattrs,\msg) \\
 %          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
@@
 
-        \procedure{$\CHALb(\ccid_0,\ccid_1,\DAttrs,\msg)$}{%
-          \pcif \ATTR[\ccid_0] \cap \ATTR[\ccid_1] \nsubseteq \DAttrs:
+        \procedure{$\CHALb(\msg,
+          \lbrace (\cscid_0,\cscid_1,\uattrs,\dattrs) \rbrace )$}{%
+          \pcif \ATTR[\cscid_0] \cap \ATTR[\cscid_1] \nsubseteq \dattrs:
           \pcreturn \bot \\
@@
  %         \pcif \ccid_0 \in \CCRED \lor \ccid_1 \in \CCRED: \pcreturn \bot \\
-          \csig \gets \Sign(\gpk,\PRVUSK[\cuid_b],\CRED[\ccid_b],
-          \DAttrs,\msg) \\
+          \csig \gets \Sign(\gpk,\PRVUK[\cuid_b],\CRED[\ccid_b],
+          \dattrs,\msg) \\
           \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
@@
 \figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
-revealing attributes \DAttrs, which was honestly produced though a credential
+revealing attributes \dattrs, which was honestly produced though a credential
 that was obtained by an honest user interacting with an honest issuer, with a
-set of attributes \Attrs such that $\DAttrs \subseteq \Attrs$, must be accepted
+set of attributes \attrs such that $\dattrs \subseteq \attrs$, must be accepted
 by \Verify. Moreover, an honestly produced correctness proof of opening for such
@@
      \gpk \gets (\ipk,\opk) \\
-    (\cid,\DAttrs,\msg) \gets \adv^{\HUGEN,\OBTISS}(\gpk) \\
-    \pcif \DAttrs \nsubseteq \ATTR[\cid] :
+    (\cid,\dattrs,\msg) \gets \adv^{\HUGEN,\OBTISS}(\gpk) \\
+    \pcif \dattrs \nsubseteq \ATTR[\cid] :
     \pcreturn \bot \\
-    \sig \gets \Sign(\gpk,\PRVUSK[\OWNR[\cid]],\CRED[\cid],\DAttrs,\msg) \\
-    (\upk,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
-    \pcif \Verify(\gpk, \sig, \DAttrs,\msg) = 0 \lor
-    \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0:
+    \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\dattrs,\msg) \\
+    (\upk,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\dattrs,\msg) \\
+    \pcif \Verify(\gpk, \sig, \dattrs,\msg) = 0 \lor
+    \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 0:
     \pcreturn 1 \\
@@
 honest signatures, and open them. The adversary wins if, after this interaction,
-is able to produce a $(\sig,\DAttrs,\msg)$ tuple that is accepted by \Verify,
+is able to produce a $(\sig,\dattrs,\msg)$ tuple that is accepted by \Verify,
 but either cannot be opened, it can be opened by the proof is rejected by
 \Judge, or even though it is accepted by \Judge, there was no issued credential
-(honest or not) that contained the set of attributes \DAttrs. We formally
+(honest or not) that contained the set of attributes \dattrs. We formally
 define traceability in the \ExpTrace experiment in \figref{fig:exp-gsac-trace}.
@@
      \gpk \gets (\ipk,\opk) \\
-     (\sig,\DAttrs,\msg) \gets
+     (\sig,\dattrs,\msg) \gets
      \adv^{\HUGEN,\CUGEN,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
-     \pcreturn 1~\pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 1~\land~( \\
+     \pcreturn 1~\pcif \Verify(\gpk,\sig,\dattrs,\msg) = 1~\land~( \\
      \pcind \pccomment{All \Obtain transcripts fail to open \sig} \\
      \pcind \forall \utrans \in \trans:
-     \Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg) = \bot~\lor \\
+     \Open(\gpk,\osk,\utrans,\sig,\dattrs,\msg) = \bot~\lor \\
      \pcind \pccomment{Such transcript exists, but ...} \\
-     \pcind \exists~\utrans~\st~\Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg) =
+     \pcind \exists~\utrans~\st~\Open(\gpk,\osk,\utrans,\sig,\dattrs,\msg) =
      (\upk,\cred,\oproof)~\land (\\
      \pcind \pcind \pccomment{... the opening proof is rejected by \Judge ...} \\
-     \pcind \pcind \Judge(\gpk,\upk,\cred,\oproof,\sig,\DAttrs,\msg) = 0~\lor \\
-     \pcind \pcind \pccomment{... or \Judge accepts the proof, but \DAttrs was
+     \pcind \pcind \Judge(\gpk,\upk,\cred,\oproof,\sig,\dattrs,\msg) = 0~\lor \\
+     \pcind \pcind \pccomment{... or \Judge accepts the proof, but \dattrs was
        not issued to any credential} \\
-     \pcind \pcind \DAttrs \nsubseteq \ATTR[\cred] \\
+     \pcind \pcind \dattrs \nsubseteq \ATTR[\cred] \\
      \pcind ) \\
@@
 In \GSAC schemes, in order for a user to be framed, the adversary first needs to
-create a $(\sig,\DAttrs,\msg,\upk,\cred,\oproof)$ such that the signature,
+create a $(\sig,\dattrs,\msg,\upk,\cred,\oproof)$ such that the signature,
 attributes, and message are accepted by \Verify, and which, along with the user
@@
      \gpk \gets (\ipk,\opk) \\
-     (\sig,\DAttrs,\msg,\upk,\cred,\oproof) \gets
+     (\sig,\dattrs,\msg,\upk,\cred,\oproof) \gets
      \adv^{\HUGEN,\CUGEN,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
-     \pcreturn 1~\pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 1 \land
+     \pcreturn 1~\pcif \Verify(\gpk,\sig,\dattrs,\msg) = 1 \land
      \OWNR[\cred] \in \HU \\%\land \cred \notin \CCRED~\land\\
-     \pcind \Judge(\gpk,\upk,\cred,\oproof,\sig,\DAttrs,\msg) = 1~\land \\
+     \pcind \Judge(\gpk,\upk,\cred,\oproof,\sig,\dattrs,\msg) = 1~\land \\
      \pcind \pccomment{\sig was not produced by \SIGN, or \upk and \cred do not match} \\
-     \pcind (\sig \notin \SIG[\OWNR[\cred]] \lor \PUBUSK[\OWNR[\cred]] \neq \upk) \\
+     \pcind (\sig \notin \SIG[\OWNR[\cred]] \lor \PUBUK[\OWNR[\cred]] \neq \upk) \\
      \pcreturn 0

### 2022-02-17 prism-backend/research/gsac/uas-model.tex
Refining oracles. Some doubts remain; should be solved while specifying games.

@@
   \langle
-  \Obtain(\usk,\uattrs,\dattrs,\ldblbrace (gpk_i,\cred_i,\uattrs_i,\dattrs_i)\rdblbrace_{i \in \Issuers}),
-  \Issue(\isk,\upk,\ldblbrace (\gpk_i,\dattrs_i)\rdblbrace_{i \in \Issuers})
+  \Obtain(\usk,\uattrs,\dattrs,\ldblbrace (gpk_i,\cred_i,\tuattrs_i,\tdattrs_i)\rdblbrace_{i \in \Issuers}),
+  \Issue(\isk,\upk,\dattrs,\ldblbrace (\gpk_i,\tdattrs_i)\rdblbrace_{i \in \Issuers})
   \rangle$.] %
@@
   attribute set $\uattrs \cup \dattrs$, where the attributes in $\uattrs$ (and
-  the ones in the $\uattrs_i$'s) are kept hidden from the issuer, while those in
-  \dattrs (as well as those in the $\dattrs_i$'s) are revealed. Moreover,
-  $\uattrs \cup \dattrs$ must be a subset of $\bigcup_i (\uattrs_i \cup
-  \dattrs_i)$. In order to get the credential, the user may leverage previously
+  the ones in the $\tuattrs_i$'s) are kept hidden from the issuer, while those
+  in \dattrs (as well as those in the $\tdattrs_i$'s) are revealed. Moreover,
+  $\uattrs \cup \dattrs$ must be a subset of $\bigcup_i (\tuattrs_i \cup
+  \tdattrs_i)$. In order to get the credential, the user may leverage previously
   obtained credentials $\cred_i$ from a multiset of other issuers (including the
@@
   Moreover, each credential $\cred_i$ can be used to prove claims over
-  undisclosed attributes $\uattrs_i$. The user
-  outputs the produced credential \cred, while the issuer outputs the protocol
-  transcript \utrans for the produced credential.
-\item[$\sig \gets \Sign(\usk,\ldblbrace (\gpk_i,\cred_i,\uattrs_i,\dattrs_i)
-  \rdblbrace_{i \in \Issuers},\msg)$.] %
+  undisclosed attributes $\tuattrs_i$. The user outputs the produced credential
+  \cred, while the issuer outputs the protocol transcript \utrans for the
+  produced credential.
+\item[$\sig \gets \Sign(\usk,\msg,\uattrs,\dattrs,
+  \ldblbrace (\gpk_i,\cred_i,\tuattrs_i,\tdattrs_i)\rdblbrace_{i \in \Issuers})$.]
   The user with with secret key \usk, who obtained credentials $\cred_i$ from a
@@
   disclosed attributes $\bigcup_i \dattrs_i$ and undisclosed attributes
-  $\bigcup_i \uattrs_i$.
+  $\bigcup_i \uattrs_i$, which must be a subset of the corresponding disclosed
+  (resp. undisclosed) attributes \tdattrs (resp. \tuattrs) in the credentials
+  used to generate the signature.
 \item[$1/0 \gets
-  \Verify(\sig,\msg,\ldblbrace (\gpk_i,\dattrs_i) \rdblbrace_{i \in \Issuers})$.]
+  \Verify(\sig,\msg,\dattrs, \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.]
   Checks whether \sig is a valid signature, over message \msg, satisfying
-  arbitrary claims over disclosed attributes $\bigcup_i \dattrs_i$, as well as
+  arbitrary claims over disclosed attributes $\dattrs$, as well as
   potentially other undisclosed attributes endorsed by issuers in the systsem
@@
 \item[$(\y,\iproof)/\bot \gets
-  \Inspect(\osk,\utrans,\sig,\msg,
-  \ldblbrace (\gpk_i,\dattrs_i) \rdblbrace_{i \in \Issuers})$.] %
-  \commentwho{Jesus}{I do not like this definition. It's complicated. This needs
+  \Inspect(\osk,\trans,\sig,\msg,\dattrs,
+  \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.] %
+  \commentwho{Jesus}{I do not like this description. It's complicated. This needs
     to be rephrased from scratch.}
@@
   over message \msg, produced by a set of credentials satisfying claims on
-  disclosed attributes $\bigcup_i \dattrs_i$, as well as potentially undisclosed
+  disclosed attributes $\dattrs$, as well as potentially undisclosed
   attributes, all endorsed by a multiset of issuers with public keys $\gpk_i$. 
-  If \utrans is a valid transcript of the execution of a
+  If \trans is a valid set of transcripts of the execution of a
   $\langle\Obtain,\Issue\rangle$ interactive protocol where the signer obtained
-  the credential associated to the inspector's group, then the function outputs
+  the credential associated to the inspector's group%
+  \footnote{Note: we are not constraining that the group to which the inspector
+    with key \osk belongs to, issued only one of the credentials used to
+    generate the signature being inspected.}, then the function outputs
   a value $\y$ derived from the signer's credential and public key, and the
   signed message, as well as a proof of correct inspection.
-\item[$1/0 \gets \Judge(\y,\iproof,\sig,\msg,
-  \ldblbrace (\gpk_i,\dattrs_i)\rdblbrace_{i \in \Issuers})$.] %
+\item[$1/0 \gets \Judge(\y,\iproof,\sig,\msg,\dattrs,
+  \ldblbrace \gpk_i\rdblbrace_{i \in \Issuers})$.] %
   Checks if \iproof is a valid inspection correctness proof for the value \y,
@@
 In the game-based definitions of our \GSAC model, we leverage the following
-oracles, which are formally defined in \figref{fig:oracles}. Note that we
-identify issuers and inspectors by the group identifier.
+oracles, which are formally defined in \figref{fig:oracles1} and
+\figref{fig:oracles2}. Note that we identify issuers and inspectors by the group
+identifier.
 
@@
           (\ipk,\isk) \gets \IKeyGen(\parm) \\
-          \IK[\gid] \gets (\ipk,\isk,\fissue);
+          \IK[\gid] \gets (\ipk,\isk,\fissue) \\
           \HI \gets \HI \cup \lbrace \gid \rbrace \\
+          \GK[\gid] \gets (\ipk,\fissue,\cdot,\cdot,\cdot) \\
           \pcreturn \ipk \\
@@
           \pcelse: \IK[\gid] = (\ipk,\bot,\fissue) \\ 
+          \GK[\gid] \gets (\ipk,\fissue,\cdot,\cdot,\cdot) \\         
           \pcreturn \top \\
@@
           \HU \gets \HU \cup \lbrace  \uid \rbrace \\
-          \pcreturn \top \\
-        }
-
-        \procedure{$\ISSUE(\cid,\uid,\gid,
-          \lbrace (\sgid,\scid,\dattrs) \rbrace)$}{%
-          \pcif \uid \notin \CU: \pcreturn \bot \\
-          \pcif \gid \notin \HI: \pcreturn \bot \\
-          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
-          \pcif \exists \cid \in \scid~\st~\CRED[\cid] \neq \bot: \pcreturn \bot \\
-          \langle \cdot, \utrans \rangle \gets
-          \langle \adv, %
-          \Issue(\PRVIK[\gid],\PUBUK[\uid],(\GK[\gid],\dattrs)) \rangle \\
-          \trans[\cid] \gets \utrans \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \bot, \dattrs) \\
-          \pcreturn \top \\          
-        }
-
-        \procedure{$\OBTISS(\cid,\uid,\gid,
-          \lbrace (\sgpk,\scid,\uattrs,\dattrs) \rbrace)$}{%
-          \pcif \uid \notin \HU: \pcreturn \bot \\
-          \pcif \gid \notin \HI: \pcreturn \bot \\          
-          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
-          \pcif \exists \cid \in \scid~\st~\CRED[\cid] \neq \bot: \pcreturn \bot \\
-          \langle \cred, \utrans \rangle \gets
-          \langle \Obtain(\gpk,\PRVUK[\uid],\attrs), \\
-          \pcind \pcind \pcind \pcind \pcind \pcind
-          \Issue(\gpk,\isk,\PUBUK[\uid],\attrs) \rangle \\
-          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \attrs \\
-          \pcreturn \top \\
-        }
-
-        \procedure{$\OBTAIN(\cid,\uid,\gid,
-          \lbrace (\sgpk,\scid,\uattrs,\dattrs) \rbrace)$}{%
-          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
-          \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\gpk,\PRVUK[\uid],\attrs),\adv \rangle \\
-          \CRED[\cid] \gets \cred \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \attrs \\
-          \pcreturn \top \\
+          \pcreturn \top
         }
@@
           (\opk,\osk) \gets \OKeyGen(\parm) \\
-          \OK[\gid] \gets (\opk,\osk,\feval,\finsp);
+          \OK[\gid] \gets (\opk,\osk,\feval,\finsp) \\
           \HO \gets \HO \cup \lbrace  \gid \rbrace \\
+          \GK[\gid] \gets (\cdot,\cdot,\opk,\feval,\finsp) \\          
           \pcreturn \opk \\
@@
           \pcelse: \OK[\gid] = (\opk,\bot,\feval,\finsp) \\
+          \GK[\gid] \gets (\cdot,\cdot,\opk,\feval,\finsp) \\
           \pcreturn \top \\
@@
           \pcelse: \UK[\uid] = (\upk,\bot) \\          
+          \pcreturn \top
+        }
+
+      \end{minipage}
+
+    }
+
+    \caption{Detailed oracles available in our model (1/2). Oracles for
+      generating users, issuers, and inspectors.\\
+      \doubt{Do we need to specify the functions in the GEN Oracles? They do
+        not seem necessary in \SIGN/\CHALb/\INSPECT. Should they? Maybe there
+        is something wrong here... Maybe they are needed in the games...}}
+    \label{fig:oracles1}
+  \end{figure*}
+}
+
+{%\setlength\intextsep{\sep}
+  \begin{figure*}[htp!]
+    \centering
+    \scalebox{0.9}{
+
+      \begin{minipage}[t]{0.55\textwidth}
+
+        \procedure{$\ISSUE(\cid,\uid,\gid,\dattrs,
+          \ldblbrace (\sgid,\scid,\tdattrs) \rdblbrace)$}{%
+          \pcif \uid \notin \CU: \pcreturn \bot \\
+          \pcif \gid \notin \HI: \pcreturn \bot \\
+%          \pcif \exists \cid
+          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
+          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
+          \langle \cdot, \utrans \rangle \gets
+          \langle \adv, \\
+          \pcind \pcind
+          \Issue(\PRVIK[\gid],\PUBUK[\uid],
+          \ldblbrace (\GK[\sgid],\tdattrs)\rdblbrace) \rangle \\
+          \trans[\cid] \gets \utrans \\
+          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \bot, \dattrs) \\
           \pcreturn \top \\          
@@
 
-        \procedure{$\SIGN(\msg,
-          \lbrace (\scid,\uattrs,\dattrs) \rbrace )$}{%
-          \uid \gets \OWNR[\cid] \\
+        \procedure{$\OBTAIN(\cid,\uid,\gid,\uattrs,\dattrs,
+          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)$}{%
+          \pcif \uid \notin \HU: \pcreturn \bot \\
+          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
+          \langle \cred, \cdot \rangle \gets
+          \langle \Obtain(\PRVUK[\uid],\uattrs,\dattrs, \\
+          \hspace*{65pt}
+          \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace), \\
+          \hspace*{50pt} \adv \rangle \\
+          \CRED[\cid] \gets \cred \\
+          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \uattrs, \dattrs) \\
+          \pcreturn \top \\
+        }
+
+        \procedure{$\INSPECT(\gid,\sig,\msg)$}{%
+          \textrm{Let}~\uid~\textrm{be s.t.}~(\sig,\msg,\scid,\uattrs,\dattrs,\sgid)
+          \in \SIG[\uid] \\
+          \pcif \sig \in \CSIG: \pcreturn \bot \\
+          (\y,\oproof) \gets
+          \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\GK[\sgid]) \\
+          \pcreturn (\y,\oproof)
+        }
+
+      \end{minipage}
+    }
+    \scalebox{0.9}{
+
+      \begin{minipage}[t]{.5\textwidth}
+
+        \procedure{$\OBTISS(\cid,\uid,\gid,\uattrs,\dattrs,
+          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)$}{%
+          \pcif \uid \notin \HU: \pcreturn \bot \\
+          \pcif \gid \notin \HI: \pcreturn \bot \\          
+          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
+          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot:
+          \pcreturn \bot \\
+          \langle \cred, \utrans \rangle \gets
+          \langle \Obtain(\PRVUK[\uid],\uattrs,\dattrs,\ldblbrace (\GK[\sgid],
+          \CRED[\scid],\tuattrs,\tdattrs) \rdblbrace), \\
+          \pcind \pcind \pcind \pcind \pcind \pcind
+          \Issue(\PRVIK[\gid],\PUBUK[\uid],\ldblbrace (\GK[\sgid],\tdattrs)
+          \rdblbrace ) \rangle \\
+          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
+          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid,\uattrs,\dattrs) \\
+          \pcreturn \top \\
+        }
+
+        \procedure{$\SIGN(\msg,\uid,\uattrs,\dattrs,
+          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace )$}{%
           \pcif \uid \notin \HU: \pcreturn \bot \\
           \cred \gets \CRED[\cid] \\
-          \sig \gets \Sign(\gpk,\PRVUK[\uid],\cred,\dattrs,\msg) \\
-          \SIG[\cid] \gets \SIG[\cid] \cup \lbrace (\sig,\dattrs,\msg) \rbrace \\
+          \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs,
+          \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace) \\
+          \SIG[\uid] \gets \SIG[\uid] \cup
+          \lbrace (\sig,\msg,\scid,\uattrs,\dattrs,\sgid) \rbrace \\
           \pcreturn \sig \\
@@
 
-        \procedure{$\OPEN(\sig)$}{%
-          \textrm{Let}~\cid~\textrm{be s.t.}~(\sig,\dattrs,\msg) \in \SIG[\cid] \\
-          \pcif \textrm{no such \cid exists, or there is more than one}: \\
-          \pcind \pcreturn \bot \\
-          \pcif \sig \in \CSIG: \pcreturn \bot \\
-          (\upk,\cred,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\dattrs,\msg) \\
-%          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
-%          \CCRED \gets \CCRED \cup \lbrace \cid \rbrace \\
-          \pcreturn (\upk,\cred,\oproof) \\
-        }
-
         \procedure{$\CHALb(\msg,
-          \lbrace (\cscid_0,\cscid_1,\uattrs,\dattrs) \rbrace )$}{%
-          \pcif \ATTR[\cscid_0] \cap \ATTR[\cscid_1] \nsubseteq \dattrs:
+          (\uid_{0,1},\uattrs_{0,1},\dattrs_{0,1},\ldblbrace (\sgid,\cscid_{0,1},\tuattrs_{0,1},\tdattrs_{0,1}) \rdblbrace))$}{%
+          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
+          \pccomment{Note: since both \uid's need to be honest, we must have
+            all the}\\
+          \pccomment{undisclosed attributes in the \ATTR lists.} \\
+          \dattrs' \gets \DATTR[\cscid_0] \cap \DATTR[\cscid_1] \\
+          \uattrs' \gets \UATTR[\cscid_0] \cap \UATTR[\cscid_1] \\
+          \pcif (\dattrs_0 \cap \dattrs_1) \nsubseteq \dattrs':
           \pcreturn \bot \\
-          \pcif \cuid_0 \neq \bot \lor \cuid_1 \neq \bot: \pcreturn \bot \\
-          \cuid_0 = \OWNR[\ccid_0];~\cuid_1 = \OWNR[\ccid_1] \\
-          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
- %         \pcif \ccid_0 \in \CCRED \lor \ccid_1 \in \CCRED: \pcreturn \bot \\
-          \csig \gets \Sign(\gpk,\PRVUK[\cuid_b],\CRED[\ccid_b],
-          \dattrs,\msg) \\
-          \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
+          \pcif (\uattrs_0 \cap \uattrs_1) \nsubseteq \uattrs':          
+          \pcreturn \bot \\
+          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\uattrs_b,\dattrs_b,
+          \ldblbrace (\GK[\sgid],\CRED[\scid_b],\tuattrs_b,\tdattrs_b) \rdblbrace) \\
+          \CSIG \gets \CSIG \cup
+          \lbrace (\csig,\msg,\scid_b,\uattrs_b,\dattrs_b,\sgid) \rbrace \\
           \pcreturn \csig
@@
 
-    \caption{Detailed oracles available in our model.}
+    \caption{Detailed oracles available in our model (2/2). Oracles for
+      obtaining credentials, signatures, and processing them.}
     \label{fig:oracles}

### 2022-02-19 prism-backend/research/gsac/uas-model.tex
Refined oracles. Completed correctness definition (v1). Working on anoymity.

@@
   returns a global system parameter variable \parm.
-\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\LangIss)$.] Given global system
-  parameters \parm, and the language \LangIss defining the NP relation for
-  issuance, an issuer runs this function to generate its issuing key pair.
-  Hereafter, we assume that the public part \ipk is added to the group public
-  key \gpk.
-\item[$(\opk,\osk) \gets \OKeyGen(\parm,\LangIns)$.] Given global system
-  parameters \parm, and the language \LangIns defining the NP relaton for
-  inspection, an inspector runs this function to generate its inspecting key
-  pair. It returns the inspector's key pair. Hereafter, we assume that the
-  public part \opk is added to the group public key \gpk.
+\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
+  parameters \parm, and the function \fissue to be used to check that credential
+  requestors meet the conditions to be issued a credential, an issuer runs
+  \IKeyGen to generate its issuing key pair. Hereafter, we assume that the
+  public part \ipk is added to the group public key \gpk, as well as \fissue.
+\item[$(\opk,\osk) \gets \OKeyGen(\parm,\feval,\finsp)$.] Given global system
+  parameters \parm, and two functions \feval and \finsp, an inspector runs
+  \OKeyGen to generate its inspecting key pair. The function \feval defines
+  requirements that signed message-signature pairs must meet. The function
+  \finsp defines the type of utility that will be extractable from those pairs
+  that do not meet \feval. Hereafter, we assume that the public part \opk is
+  added to the group public key \gpk, along with \feval and \finsp.
 \item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
@@
   \langle
-  \Obtain(\usk,\uattrs,\dattrs,\ldblbrace (gpk_i,\cred_i,\tuattrs_i,\tdattrs_i)\rdblbrace_{i \in \Issuers}),
-  \Issue(\isk,\upk,\dattrs,\ldblbrace (\gpk_i,\tdattrs_i)\rdblbrace_{i \in \Issuers})
+  \Obtain(\usk,\uattrs,\dattrs,
+  \ldblbrace (gpk_i,\cred_i,\tuattrs_i,\tdattrs_i)\rdblbrace_{i \in \Issuers}),
+  \Issue(\isk,\upk,\dattrs,
+  \ldblbrace (\gpk_i,\tdattrs_i)\rdblbrace_{i \in \Issuers})
   \rangle$.] %
@@
 keep consistent state.
+
+\paragraph{Issuance, evaluation, and inspection private functions.} %
+We emphasize that, both in our syntax definition, as well as on the following
+modelling, we make use of three different and abstract functions: \fissue,
+\feval and \finsp. The three functions are run by users (maybe, on user-private
+data) as part of different algorithms in an \UAS scheme. In all cases, the
+user has to prove correctness of their computation. We introduce them next,
+\todo{and will give concrete examples in \secref{sec:uac-instantiation}.}
+
+\todo{Domains (attributes, messages, etc.) are not correctly defined here. But
+  for now, just leave it as is to at least convey the idea. Also, this needs
+  refinement in general: what properties (if any) do these functions need to
+  meet in order to be meaningful?}
+\begin{description}
+\item[$\fissue: (\uattrs,\dattrs) \rightarrow 0/1$.] Governs what customized
+  conditions an issuer requires in order to issue credentials, when receiving
+  a request from a user with a set of disclosed attributes \dattrs, and
+  undisclosed attributes \uattrs (which need to be kept private from the
+  issuer). \fissue returns 1 to accept a request, 0 to reject it.  
+\item[$\feval: (\msg,\sig) \rightarrow 0/1$.] Governs customized conditions upon
+  which a verifier should accept (1) or reject (0) a given message-signature
+  pair.
+\item[$\finsp: (\upk,\scred) \rightarrow \bin^*$.] Defines what utility value,
+  derived from the user's public key and credentials, should be extractable by
+  the group inspector.
+\end{description}
 
@@
     \caption{Detailed oracles available in our model (1/2). Oracles for
-      generating users, issuers, and inspectors.\\
+      generating key material for users, issuers, and inspectors.\\
       \doubt{Do we need to specify the functions in the GEN Oracles? They do
@@
           \langle \cred, \utrans \rangle \gets
-          \langle \Obtain(\PRVUK[\uid],\uattrs,\dattrs,\ldblbrace (\GK[\sgid],
+          \langle \Obtain(\PRVUK[\uid],\uattrs,\dattrs,\\
+          \hspace*{75pt} \ldblbrace (\GK[\sgid],
           \CRED[\scid],\tuattrs,\tdattrs) \rdblbrace), \\
-          \pcind \pcind \pcind \pcind \pcind \pcind
-          \Issue(\PRVIK[\gid],\PUBUK[\uid],\ldblbrace (\GK[\sgid],\tdattrs)
+          \hspace*{60pt} \Issue(\PRVIK[\gid],\PUBUK[\uid],
+          \ldblbrace (\GK[\sgid],\tdattrs)
           \rdblbrace ) \rangle \\
@@
           \cred \gets \CRED[\cid] \\
-          \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs,
+          \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs, \\
+          \hspace*{42pt}
           \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace) \\
@@
           \pcreturn \bot \\
-          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\uattrs_b,\dattrs_b,
+          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\uattrs_b,\dattrs_b, \\
+          \hspace*{42pt}
           \ldblbrace (\GK[\sgid],\CRED[\scid_b],\tuattrs_b,\tdattrs_b) \rdblbrace) \\
@@
 \paragraph{Correctness.} %
-Correctness of \GSAC schemes is formalized through the experiment in
-\figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
+Correctness of \UAS schemes is formalized through the experiment in
+\figref{fig:exp-uas-corr}. It states that a signature for some message \msg,
 revealing attributes \dattrs, which was honestly produced though a credential
@@
     \parm \gets \Setup(1^\secpar) \\
-     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
-     \gpk \gets (\ipk,\opk) \\
-    (\cid,\dattrs,\msg) \gets \adv^{\HUGEN,\OBTISS}(\gpk) \\
-    \pcif \dattrs \nsubseteq \ATTR[\cid] :
-    \pcreturn \bot \\
-    \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\dattrs,\msg) \\
-    (\upk,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\dattrs,\msg) \\
-    \pcif \Verify(\gpk, \sig, \dattrs,\msg) = 0 \lor
-    \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 0:
-    \pcreturn 1 \\
-    \pcreturn 0
+    (\uid,\msg,\uattrs,\dattrs,
+    \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)
+    \gets \adv^{\HIGEN,\HOGEN,\HUGEN,\OBTISS}(\parm) \\
+    \pcif \dattrs \nsubseteq \bigcup_{\cid \in \scid} \DATTR[\cid] \lor
+    \bigcup \tdattrs \nsubseteq \dattrs: \pcreturn \bot \\
+    \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs,
+    \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace ) \\
+    \pccomment{Signature fails to verify} \\
+    \pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 0: \pcreturn 0 \\
+    \pccomment{An inspector among those involved in credentials used to produce
+      \sig cannot inspect it} \\
+    \pcif \exists \gid \in \sgid~\st~
+    \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,
+    \ldblbrace \GK[\sgid] \rdblbrace) = \bot: \pcreturn 0 \\
+    \pccomment{Some of the produced $(\y,\iproof)$ pairs is rejected by
+      \Judge \todo{This must be conditioned on \feval = 0!}} \\
+    \pcif \exists \gid \in \sgid~\st~
+    (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,
+    \ldblbrace \GK[\sgid] \rdblbrace) \land \\
+    \pcind
+    \Judge(\y,\iproof,\sig,\msg,\dattrs,\ldblbrace \GK[\sgid] \rdblbrace) = 0):
+    \pcreturn 0 \\
+    \textrm{Let}~(\fissue^\gid,\feval^\gid,\finsp^\gid)~\textrm{denote the
+      issue, evaluation and inspection functions defined} \\
+    \textrm{by each $\gid \in \sgid$} \pccomment{\todo{Come up with some
+        notation for this}} \\
+    \pccomment{\fissue rejects some issued credential} \\
+    \pcif \exists \gid \in \sgid~\st~\fissue^\gid(\tuattrs,\tdattrs) = 0:
+    \pcreturn 0 \\
+    \pccomment{\feval rejects the signature-message pair} \\
+    \pcif \exists \gid \in \sgid~\st~\feval^\gid(\msg,\sig) = 0: \pcreturn 0 \\
+    \pccomment{\y is the wrong value according to \finsp} \\
+    \pcif \exists \gid \in \sgid~\st~
+    \y \neq \finsp^\gid(\PUBUK[\uid],\CRED[\scid])): \pcreturn 0 \\
+    \pcreturn 1
   }
-  \caption{Correctness experiment for \GSAC schemes.}
-  \label{fig:exp-gsac-corr}
+  \caption{Correctness experiment for \UAS schemes. \todo{Reorganize this.}}
+  \label{fig:exp-uas-corr}
 \end{figure}
@@
 it requires that no adversary should learn anything about the holder of a
-credential that has been successfully shown, beyond that he owns a credential
-containing the revealed attributes. In both GS and AC, it is also typically
-required that
+successfully shown credential, beyond that he owns a credential attesting for
+the claimed function of attributes it contains. In both GS and AC, it is also
+typically required that
 multiple signatures/presentations by the users are unlinkable. The approach to
@@
 signatures. In anonymous credentials, the game must further constraint the
-adversary to output credentials that have some common subset of attributes, and
-to use that common subset to request the challenge presentations. Here, we need
-to take into account both. Furthermore, a key difference with group signatures
-is that the game requires the adversary to output credential identifiers, rather
-than user identifiers. Specifically, this means that the adversary may actually
-output two credentials that belong to the same user. Therefore, in some sense,
-the anonymity we get is more general than that of group signatures. The formal
-specification of the anonymity game is given in \figref{fig:exp-gsac-anonb}.
-%
-Similarly, this notion of anonymity is also stronger than the notion of
-anonymity in both group signatures and anonymous credentials, in the sense
-that calls to the \OPEN oracle reveal the public key and credential of the users
-that (via the \SIGN and \CHALb oracles) create the signatures that the adversary
-sees. Therefore, all security relies \emph{only} on the user secret key.
+adversary to output credentials that have some common function of (a subset of)
+its attributes.
+
+In our notion of anonymity for \UAS, we need to merge the previous constraints.
+Furthermore, a key difference with group signatures is that the game requires
+the adversary to output credential identifiers, rather than user identifiers.
+Specifically, this means that the adversary may actually output two credentials
+that belong to the same user. Therefore, in some sense, the anonymity we get is
+more general than that of group signatures. Moreover, in order to prevent
+trivial wins by the adversary, we have to restrict that the challenge signatures
+belong to a group that has been ``programmed'' with the same evaluation and
+inspection functions. The formal specification of the anonymity game is given in
+\figref{fig:exp-uas-anonb}.
 
@@
      \parm \gets \Setup(1^\secpar) \\
-     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
-     \gpk \gets (\ipk,\opk) \\
-     (\cid_0,\cid_1,\status) \gets
-     \adv^{\HUGEN,\CUGEN,\OBTAIN,\SIGN,\OPEN}(\choose,\gpk,\isk) \\
+     (\cscid_0,\cscid_1,\status) \gets
+     \adv^{\lbrace\HI,\CI,\HO,\CO,\HU,\CU\rbrace\GEN,\OBTAIN,\SIGN,\INSPECT}
+     (\choose,\parm) \\
      b^* \gets
-     \adv^{\HUGEN,\CUGEN,\OBTAIN,\SIGN,\OPEN,\CHALb}(\guess,\gpk,\isk,\status) \\
+     \adv^{\lbrace\HI,\CI,\HO,\CO,\HU,\CU\rbrace,\GEN,\OBTAIN,\SIGN,\INSPECT,\CHALb}
+     (\guess,\status) \\
      \pcreturn b^*
   }
-  \caption{Anonymity experiment for \GSAC schemes.}
-  \label{fig:exp-gsac-anonb}
+  \caption{Anonymity experiment for \UAS schemes.}
+  \label{fig:exp-uas-anonb}
 \end{figure}
@@
 
+\paragraph{Discussion on the generic anonymity of \UAS schemes.} %
+This notion of anonymity is also more general in the sense that calls to
+the \INSPECT oracle reveal an arbitrary function of the identity of the user
+-- which can certainly be the identity itself, as in group signatures, ore any
+other function computable from the \textcolor{red}{user public key and all of
+  its credentials}. Of course, this requires to restrict the adversary to
+programming equivalent inspection functions in the challenge signatures it
+gets (or, more precisely, into the groups they belong to). While this could
+appear as having a more restricted type of anonymity -- and indeed it could be
+for some subset of inspection functions -- we point out that it is just a
+generalization, as the concrete inspection function depends on the needs of
+the use case where a \UAS scheme is to be integrated.
+
 \paragraph{Traceability.} %
@@
 %
-Our notion of traceability for \GSAC combines both requirements. It assumes an
-honest issuer, as otherwise the adversary can create untraceable credentials at
-will. The game then lets the adversary add honest and corrupt users, create
-honest signatures, and open them. The adversary wins if, after this interaction,
-is able to produce a $(\sig,\dattrs,\msg)$ tuple that is accepted by \Verify,
-but either cannot be opened, it can be opened by the proof is rejected by
-\Judge, or even though it is accepted by \Judge, there was no issued credential
-(honest or not) that contained the set of attributes \dattrs. We formally
-define traceability in the \ExpTrace experiment in \figref{fig:exp-gsac-trace}.
+Our notion of traceability for \UAS...
 
@@
 %
-In \GSAC schemes, in order for a user to be framed, the adversary first needs to
-create a $(\sig,\dattrs,\msg,\upk,\cred,\oproof)$ such that the signature,
-attributes, and message are accepted by \Verify, and which, along with the user
-public key, credential, and open correctness proof, are accepted by \Judge.
-Then, the adversary wins the game if the owner of the credential is honest, but
-the signature was not produced via the \SIGN oracle, or if the public key output
-by the adversary does not match the public key associated to the credential
-owner.
-%
-Note that, as in anonymity, this notion of non-frameability is even stronger
-to that of group signatures, since our \Open function returns both the public
-key and the credential that were used to create the signature.
+In \UAS schemes, in order for a user to be framed...
 

### 2022-02-20 prism-backend/research/gsac/uas-model.tex
Working on non-frameability. Realized there are issues in the current definition of traceability.

@@
 \todo{Are generalizations where different groups can share issuer or inspector
-  straight forward?} \\
+  straight forward?}
+
 \todo{The notation for multisets is not strictly correct. Still, leaving it as
-  is for now.} \\
+  is for now.}
+
 \commentwho{Jesus}{I'm trying to define \Sign, \Verify, \Inspect and \Judge such
@@
   attributes contained in \emph{one} credential.}
+
+\commentwho{Jesus}{Maybe we could remove the attribute sets \uattrs, \dattrs,
+  \tuattrs, \tdattrs, from the syntax, and assume that they are part of the
+  signatures and/or credentials. This would certainly lead to a cleaner syntax,
+  but, what impact would that have in other definitions, etc? Specifically, can
+  we support selective disclosure credentials without them? (if so, \fissue,
+  \feval and \finsp would be essential in doing so.); Right now, I am more in
+  favour of tryint to remove the attribute sets from the definitions, as much
+  as possible (and see if we can still support plain selective disclosure).}
 
@@
   issuer). \fissue returns 1 to accept a request, 0 to reject it.  
-\item[$\feval: (\msg,\sig) \rightarrow 0/1$.] Governs customized conditions upon
-  which a verifier should accept (1) or reject (0) a given message-signature
-  pair.
-\item[$\finsp: (\upk,\scred) \rightarrow \bin^*$.] Defines what utility value,
-  derived from the user's public key and credentials, should be extractable by
-  the group inspector.
+\item[$\feval: (\msg,\scred) \rightarrow 0/1$.] Governs customized conditions
+  to define whether the owner of a set of credentials -- or, more specifically,
+  credentials encoding certain attributes -- should be able to sign certain
+  messages.
+\item[$\finsp: (\upk,\scred,\sig) \rightarrow \bin^*$.] Defines what utility
+  value, derived from the user's public key, credentials, and produced signature
+  (or a subset thereof), should be extractable by the group inspector.
 \end{description}
@@
     \caption{Detailed oracles available in our model (1/2). Oracles for
-      generating key material for users, issuers, and inspectors.\\
-      \doubt{Do we need to specify the functions in the GEN Oracles? They do
-        not seem necessary in \SIGN/\CHALb/\INSPECT. Should they? Maybe there
-        is something wrong here... Maybe they are needed in the games...}}
+      generating key material for users, issuers, and inspectors.}
     \label{fig:oracles1}
@@
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
-          \pccomment{Note: since both \uid's need to be honest, we must have
-            all the}\\
-          \pccomment{undisclosed attributes in the \ATTR lists.} \\
-          \dattrs' \gets \DATTR[\cscid_0] \cap \DATTR[\cscid_1] \\
-          \uattrs' \gets \UATTR[\cscid_0] \cap \UATTR[\cscid_1] \\
-          \pcif (\dattrs_0 \cap \dattrs_1) \nsubseteq \dattrs':
-          \pcreturn \bot \\
-          \pcif (\uattrs_0 \cap \uattrs_1) \nsubseteq \uattrs':          
+          \pcif \feval(\msg,\CRED[\scid_0]) \neq \feval(\msg,\CRED[\scid_1]):
           \pcreturn \bot \\
@@
           \CSIG \gets \CSIG \cup
-          \lbrace (\csig,\msg,\scid_b,\uattrs_b,\dattrs_b,\sgid) \rbrace \\
+          \lbrace (\csig,\msg,\cscid_b,\uattrs_b,\dattrs_b,\sgid) \rbrace \\
           \pcreturn \csig
@@
 In group signatures, anonymity captures that no adversary must be able to learn,
-from any group signature, anything about its signer. In anonymous credentials,
-it requires that no adversary should learn anything about the holder of a
-successfully shown credential, beyond that he owns a credential attesting for
-the claimed function of attributes it contains. In both GS and AC, it is also
-typically required that
+from any group signature, the identity (e.g., member index) of its signer. In 
+anonymous credentials, it requires that no adversary should learn anything about
+the holder of a successfully shown credential, beyond that he owns a credential
+attesting for the claimed function of the attributes it contains. In both GS and
+AC, it is also typically required that
 multiple signatures/presentations by the users are unlinkable. The approach to
@@
 belong to a group that has been ``programmed'' with the same evaluation and
-inspection functions. The formal specification of the anonymity game is given in
-\figref{fig:exp-uas-anonb}.
+inspection functions, which is again a generalization over group signatures,
+as discussed in the sequel. The formal specification of the anonymity game is
+given in \figref{fig:exp-uas-anonb}.
 
@@
 
-\begin{definition}{(Anonymity of \GSAC)}
+\begin{definition}{(Anonymity of \UAS)}
   We define the advantage \AdvAnon of $\adv$ against \ExpAnonb as
@@
   %
-  A \GSAC scheme satisfies anonymity if, for any p.p.t. adversary $\adv$,
+  An \UAS scheme satisfies anonymity if, for any p.p.t. adversary $\adv$,
   \AdvAnon is a negligible function of $1^\secpar$.
@@
 
-\paragraph{Discussion on the generic anonymity of \UAS schemes.} %
-This notion of anonymity is also more general in the sense that calls to
-the \INSPECT oracle reveal an arbitrary function of the identity of the user
--- which can certainly be the identity itself, as in group signatures, ore any
-other function computable from the \textcolor{red}{user public key and all of
-  its credentials}. Of course, this requires to restrict the adversary to
-programming equivalent inspection functions in the challenge signatures it
-gets (or, more precisely, into the groups they belong to). While this could
-appear as having a more restricted type of anonymity -- and indeed it could be
-for some subset of inspection functions -- we point out that it is just a
-generalization, as the concrete inspection function depends on the needs of
-the use case where a \UAS scheme is to be integrated.
+\paragraph{Discussion on the generality of anonymity in \UAS schemes.} %
+This notion of anonymity is more general than that of group signatures in the
+sense that calls to the \INSPECT oracle reveal an arbitrary function of the
+identity of the user -- which can certainly be the member index itself, as it
+is frequent in group signatures, ore any other function computable from the
+user public key, its credentials, and produced signature. \todo{Delve more in
+  this.}
 
@@
 contained in one of the credentials controlled by the adversary.
-%
-Our notion of traceability for \UAS...
+
+Our notion of traceability for \UAS is inspired by both. First, we restrict to
+signatures that are accepted by \Verify. For any such signature, \Inspect has to
+create a valid output (i.e., must not abort). The output of \Inspect has to be
+accepted by \Judge too. Moreover, there must exist one user (either honest or
+corrupt) who used his public key to obtain one or more credentials that allowed
+him to produce a signature which, once inspected, returns \y.
 
@@
     \parm \gets \Setup(1^\secpar) \\
-     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
-     \gpk \gets (\ipk,\opk) \\
+    \pccomment{\todo{Right now, in \COGEN we may not know \osk! Then, the checks
+        in the last part of the game may not be executable!}} \\
      (\sig,\dattrs,\msg) \gets
-     \adv^{\HUGEN,\CUGEN,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
-     \pcreturn 1~\pcif \Verify(\gpk,\sig,\dattrs,\msg) = 1~\land~( \\
+     \adv^{\lbrace \HI,\CO,\HU,\CU \rbrace \GEN,\OBTISS,\ISSUE,\SIGN,\INSPECT}
+     (\parm) \\
+     \pcreturn 1~\pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 1~\land~( \\
      \pcind \pccomment{All \Obtain transcripts fail to open \sig} \\
-     \pcind \forall \utrans \in \trans:
-     \Open(\gpk,\osk,\utrans,\sig,\dattrs,\msg) = \bot~\lor \\
+     \pcind \nexists \gid \in \sgid:
+     \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\sgid) = \bot~\lor \\
      \pcind \pccomment{Such transcript exists, but ...} \\
-     \pcind \exists~\utrans~\st~\Open(\gpk,\osk,\utrans,\sig,\dattrs,\msg) =
-     (\upk,\cred,\oproof)~\land (\\
-     \pcind \pcind \pccomment{... the opening proof is rejected by \Judge ...} \\
-     \pcind \pcind \Judge(\gpk,\upk,\cred,\oproof,\sig,\dattrs,\msg) = 0~\lor \\
-     \pcind \pcind \pccomment{... or \Judge accepts the proof, but \dattrs was
-       not issued to any credential} \\
-     \pcind \pcind \dattrs \nsubseteq \ATTR[\cred] \\
+     \pcind \exists\gid \in \sgid~\st~
+     \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs) =
+     (\y,\iproof)~\land (\\
+     \pcind \pcind \pccomment{... the proof is rejected by \Judge ...} \\
+     \pcind \pcind \Judge(\y,\iproof,\sig,\msg,\dattrs,\GK[\sgid]) = 0~\lor \\
+     \pcind \pcind \pccomment{... or \Judge accepts the proof, but inspect
+       returns an invalid value} \\
+     \pcind \pcind \nexists \uid \in \CU \cup \HU~\st~
+     \y = \finsp(\PUBUK[\uid],\CRED[\uid],\sig) \\
      \pcind ) \\
@@
   }
-  \caption{Traceability experiment for \GSAC schemes.}
-  \label{fig:exp-gsac-trace}
+  \caption{Traceability experiment for \UAS schemes.}
+  \label{fig:exp-uas-trace}
 \end{figure}
 
-\begin{definition}{(Traceability of \GSAC)}
+\begin{definition}{(Traceability of \UAS)}
   We define the advantage \AdvTrace of $\adv$ against \ExpTrace as
@@
   %
-  A \GSAC scheme satisfies traceability if, for any p.p.t. adversary $\adv$,
+  A \UAS scheme satisfies traceability if, for any p.p.t. adversary $\adv$,
   \AdvTrace is a negligible function of $1^\secpar$.
 \end{definition}
+
+\paragraph{Discussion on the generality of traceability in \UAS schemes.} %
+Note that this notion of traceability is, again, strictly more general than
+both group signatures and anonymous credentials. On the group signatures side,
+it all depends on the \Inspect function. If we set it to the traditional
+inspection function, where it returns the identity (index) of the signer, then
+our notion of traceability becomes exactly that of conventional group
+signatures. On the other hand, \Inspect may be set to a non-injective function,
+meaning that it can be possible that different user public keys, credentials and
+signature tuples, may produce the same output. In that case, though, our notion
+of traceability ensures that there must exist \emph{at least one} user capable
+of issuing that signature.
+%
+On the anonymous credentials side, note that our definition allows that users
+combine multiple credentials in a ``presentation''. However, in anonymous
+credentials, it is frequent to require that all the attributes proven in a
+presentation must be contained in a single credential. Note though that our
+definition requires all credentials to be tied to the same user identity.
+Therefore, it is a natural extension as (in the real life), it is very frequent
+to combine multiple identifying documents to prove that you are entitled to
+something. Moreover, any specific instantiation that restricts signatures
+to be associated to just one credential directly leads to the previously
+mentioned ``one credential per presentation'' rule.
 
@@
     \parm \gets \Setup(1^\secpar) \\
-     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
-     \gpk \gets (\ipk,\opk) \\
      (\sig,\dattrs,\msg,\upk,\cred,\oproof) \gets
-     \adv^{\HUGEN,\CUGEN,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
+     \adv^{\lbrace\CI,\CO,\HU,\CU\rbrace\GEN,\OBTAIN,\SIGN}(\parm) \\
      \pcreturn 1~\pcif \Verify(\gpk,\sig,\dattrs,\msg) = 1 \land

### 2022-02-22 prism-backend/research/gsac/uas-model.tex
Still working on non-frameability property of UAS.
Potentially correct non-frameability definition. Fixed issue in traceability too.

@@
   \feval and \finsp would be essential in doing so.); Right now, I am more in
-  favour of tryint to remove the attribute sets from the definitions, as much
+  favour of trying to remove the attribute sets from the definitions, as much
   as possible (and see if we can still support plain selective disclosure).}
@@
   issuer). \fissue returns 1 to accept a request, 0 to reject it.  
-\item[$\feval: (\msg,\scred) \rightarrow 0/1$.] Governs customized conditions
-  to define whether the owner of a set of credentials -- or, more specifically,
-  credentials encoding certain attributes -- should be able to sign certain
-  messages.
-\item[$\finsp: (\upk,\scred,\sig) \rightarrow \bin^*$.] Defines what utility
-  value, derived from the user's public key, credentials, and produced signature
-  (or a subset thereof), should be extractable by the group inspector.
+\item[$\feval: (\upk,\scred,\msg) \rightarrow 0/1$.] Governs customized
+  conditions to define whether the owner of a user key and set of credentials --
+  or, more specifically, credentials encoding certain attributes -- should be
+  able to sign certain messages.
+\item[$\finsp: (\upk,\scred,\msg,\sig) \rightarrow \bin^*$.] Defines what
+  utility value, derived from the user's public key, credentials, signed
+  message, and produced signature (or a subset thereof), should be extractable
+  by the group inspector.
 \end{description}
@@
 \begin{description}
-\item[\HIGEN.] Adds a new honest issuer to the game, by honestly generating
-  its key pair.
-\item[\CIGEN.] Adds a new corrupt issuer to the game or, if the specified issuer
-  already exists and is honest, corrupts it.
-\item[\HOGEN.] Adds a new honest inspector to the game, by honestly generating
-  its key pair.
-\item[\COGEN.] Adds a new corrupt inspector to the game or, if the specified
-  inspector already exists and is honest, corrupts it. 
+\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
+  the associated issuance function.
+\item[\OGEN.] Adds a new inspector to the game, generating its key pair and
+  setting the associated evaluation and inspection functions.
 \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
@@
 
-        \procedure{$\HIGEN(\gid,\fissue)$}{%
+        \procedure{$\IGEN(\gid,\fissue)$}{%
           \pcif \gid \in \HI \lor \gid \in \CI: \pcreturn \bot \\
@@
 
-        \procedure{$\CIGEN(\gid,\ipk,\fissue)$}{%
-          \pcif \gid \in \CI: \pcreturn \bot \\
+        \procedure{$\ICORR(\gid)$}{%
+          \pcif \gid \in \CI \lor \gid \notin \HI: \pcreturn \bot \\
+          \HI \gets \HI \setminus \lbrace \gid \rbrace \\
           \CI \gets \CI \cup \lbrace \gid \rbrace \\
-          \pcif \gid \in \HI: \\
-          \pcind \HI \gets \HI \setminus \lbrace \gid \rbrace; \\
-          \pcind \pcreturn \IK[\gid] \\
-          \pcelse: \IK[\gid] = (\ipk,\bot,\fissue) \\ 
-          \GK[\gid] \gets (\ipk,\fissue,\cdot,\cdot,\cdot) \\         
-          \pcreturn \top \\
+          \pcreturn \isk \\
         }
@@
 
-        \procedure{$\HOGEN(\gid,\feval,\finsp)$}{%
+        \procedure{$\OGEN(\gid,\feval,\finsp)$}{%
           \pcif \gid \in \HO \lor \gid \in \CO: \pcreturn \bot \\
@@
 
-        \procedure{$\COGEN(\gid,\opk,\feval,\finsp)$}{%
-          \pcif \gid \in \CO: \pcreturn \bot \\
+        \procedure{$\OCORR(\gid)$}{%
+          \pcif \gid \in \CO \lor \gid \notin \HO: \pcreturn \bot \\
+          \HO \gets \HO \setminus \lbrace \gid \rbrace \\
           \CO \gets \CO \cup \lbrace \gid \rbrace \\
-          \pcif \gid \in \HO: \\
-          \pcind \HO \gets \HO \setminus \lbrace \gid \rbrace; \\
-          \pcind \pcreturn \OK[\gid]) \\
-          \pcelse: \OK[\gid] = (\opk,\bot,\feval,\finsp) \\
-          \GK[\gid] \gets (\cdot,\cdot,\opk,\feval,\finsp) \\
-          \pcreturn \top \\
+          \pcreturn \osk \\
         }
@@
           \pcif \gid \notin \HI: \pcreturn \bot \\
-%          \pcif \exists \cid
           \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
@@
         \procedure{$\CHALb(\msg,
-          (\uid_{0,1},\uattrs_{0,1},\dattrs_{0,1},\ldblbrace (\sgid,\cscid_{0,1},\tuattrs_{0,1},\tdattrs_{0,1}) \rdblbrace))$}{%
+          (\uid_{0,1},\uattrs_{0,1},\dattrs_{0,1},\ldblbrace (\sgid,\cscid_{0,1},
+          \tuattrs_{0,1},\tdattrs_{0,1}) \rdblbrace))$}{%          
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
+          \pcif \exists \gid \in \sgid~\st~\gid \in \CO: \pcreturn \bot \\
           \pcif \feval(\msg,\CRED[\scid_0]) \neq \feval(\msg,\CRED[\scid_1]):
@@
     \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)
-    \gets \adv^{\HIGEN,\HOGEN,\HUGEN,\OBTISS}(\parm) \\
+    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS}(\parm) \\
     \pcif \dattrs \nsubseteq \bigcup_{\cid \in \scid} \DATTR[\cid] \lor
@@
 as discussed in the sequel. The formal specification of the anonymity game is
-given in \figref{fig:exp-uas-anonb}.
+given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,\CU\rbrace
+\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN,
+\INSPECT)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace
+\GEN,\lbrace\II,\OO\rbrace,\CORR,\OBTAIN,\SIGN,\INSPECT,\CHALb)$
 
@@
      \parm \gets \Setup(1^\secpar) \\
-     (\cscid_0,\cscid_1,\status) \gets
-     \adv^{\lbrace\HI,\CI,\HO,\CO,\HU,\CU\rbrace\GEN,\OBTAIN,\SIGN,\INSPECT}
-     (\choose,\parm) \\
-     b^* \gets
-     \adv^{\lbrace\HI,\CI,\HO,\CO,\HU,\CU\rbrace,\GEN,\OBTAIN,\SIGN,\INSPECT,\CHALb}
-     (\guess,\status) \\
+     (\cscid_0,\cscid_1,\status) \gets \adv^{\Oanonc}(\choose,\parm) \\
+     b^* \gets \adv^{\Oanong} (\guess,\status) \\
      \pcreturn b^*
@@
 corrupt) who used his public key to obtain one or more credentials that allowed
-him to produce a signature which, once inspected, returns \y.
+him to produce a signature which, once inspected, returns \y. The formal
+definition of the traceability experiment is given in \figref{fig:exp-uas-trace},
+where $\Otrace \gets \lbrace\HU,\CU\rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,
+\ISSUE,\SIGN,\INSPECT$.
 
@@
     \parm \gets \Setup(1^\secpar) \\
-    \pccomment{\todo{Right now, in \COGEN we may not know \osk! Then, the checks
-        in the last part of the game may not be executable!}} \\
      (\sig,\dattrs,\msg) \gets
-     \adv^{\lbrace \HI,\CO,\HU,\CU \rbrace \GEN,\OBTISS,\ISSUE,\SIGN,\INSPECT}
-     (\parm) \\
+     \adv^{\Otrace}(\parm) \\
      \pcreturn 1~\pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 1~\land~( \\
@@
 
+Finally, note that we can only ensure consistency of the value returned by
+\finsp, for all users, as long as the issuer is honest. This follows from the
+fact that \finsp depends on the user key pair and the credentials that are
+issued to each user. Therefore, a dishonest issuer could create untraceable
+credentials (i.e., issue credentials without updating the \trans table), so that
+the \finsp function outputs whatever desired value, yet it cannot be traced to
+any registered user. That is, this minimality argument is just a generalization
+of the one described in \cite[Section 4.3]{bsz05}. This is also consistent with
+the unforgeability requirement of anonymous credentials systems, as a corrupt
+issuer can grant arbitrary credentials to any user, and therefore honest
+issuers are required.
+
 \paragraph{Non-frameability.} %
@@
 %
-In \UAS schemes, in order for a user to be framed...
+In \UAS schemes, in order for a user to be framed \todo{...}. The
+non-frameability property for \UAS schemes is formally defined in
+\figref{fig:exp-uas-frame}, where $\Oframe \gets \lbrace\HU,\CU\rbrace\GEN,
+\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN$
 
@@
     \parm \gets \Setup(1^\secpar) \\
-     (\sig,\dattrs,\msg,\upk,\cred,\oproof) \gets
-     \adv^{\lbrace\CI,\CO,\HU,\CU\rbrace\GEN,\OBTAIN,\SIGN}(\parm) \\
-     \pcreturn 1~\pcif \Verify(\gpk,\sig,\dattrs,\msg) = 1 \land
-     \OWNR[\cred] \in \HU \\%\land \cred \notin \CCRED~\land\\
-     \pcind \Judge(\gpk,\upk,\cred,\oproof,\sig,\dattrs,\msg) = 1~\land \\
-     \pcind \pccomment{\sig was not produced by \SIGN, or \upk and \cred do not match} \\
-     \pcind (\sig \notin \SIG[\OWNR[\cred]] \lor \PUBUK[\OWNR[\cred]] \neq \upk) \\
+     (\sig,\dattrs,\msg,\sgid,\y,\iproof) \gets
+     \adv^{\Oframe}(\parm) \\
+     \pcreturn 1~\pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 1 \land
+     \Judge(\y,\iproof,\sig,\msg,\dattrs,\GK[\sgid]) = 1~\land \\
+     \pcind \exists \uid \in \HU~\st~\Identify(\PRVUK[\uid],\sig) = 1 \land
+     \sig \notin \SIG[\uid] \\
      \pcreturn 0
   }
-  \caption{Non-frameability experiment for \GSAC schemes.}
-  \label{fig:exp-gsac-frame}
+  \caption{Non-frameability experiment for \UAS schemes.}
+  \label{fig:exp-uas-frame}
 \end{figure}

### 2022-02-22 prism-backend/research/gsac/uas-model.tex
Security of fiss, feval and finsp was ignored. Should go on trace.

@@
 
-\todo{Domains (attributes, messages, etc.) are not correctly defined here. But
-  for now, just leave it as is to at least convey the idea. Also, this needs
-  refinement in general: what properties (if any) do these functions need to
-  meet in order to be meaningful?}
 \begin{description}
@@
 \end{description}
+
+\todo{\fissue and \feval are not covered in the security definitions! Probably,
+  they should go into traceability -- which may need to be generalized into
+  unforgeability or something like that.}
+
+\paragraph{Helper Function \Identify.} In addition, we make use of a helper
+function \Identify for our non-frameability definition. This function receives
+a signature and a user secret key, and determines whether the latter was used
+to produce the former. This is in line with previous works on DAA
+\cite{bfg+11,cdl16} and group signatures without traditional open functions
+\cite{dl21,fgl21,gl19}. More concreltely \Identify function, defined as $1/0
+\gets \Identify(\usk,\sig)$, conveys meaning to our non-frameability definition
+conditioned on the fact that, given a signature \sig accepted by \Verify,
+\Identify returns $1$ for exactly one \usk.
 
@@
   setting the associated evaluation and inspection functions.
+\item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
+  key to the adversary.
+\item[\OCORR.] Corrupts an existing (and honest) inspector, by giving its secret
+  key to the adversary.  
 \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
@@
           \pcif \exists \gid \in \sgid~\st~\gid \in \CO: \pcreturn \bot \\
-          \pcif \feval(\msg,\CRED[\scid_0]) \neq \feval(\msg,\CRED[\scid_1]):
+          \pcif \feval(\PUBUK[\uid_0],\CRED[\scid_0],\msg) \neq \\
+          \pcind \feval(\PUBUK[\uid_1],\CRED[\scid_1],\msg):
           \pcreturn \bot \\
@@
 \begin{figure}[htp!]
+%  \begin{minipage}[t]{\textwidth}
     \procedure{$\ExpTrace(1^\secpar)$}{%
       \parm \gets \Setup(1^\secpar) \\
-     (\sig,\dattrs,\msg) \gets
+      (\sig,\dattrs,\msg,\sgid) \gets
       \adv^{\Otrace}(\parm) \\
-     \pcreturn 1~\pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 1~\land~( \\
-     \pcind \pccomment{All \Obtain transcripts fail to open \sig} \\
+      \pcreturn 1~\pcif: \\
+      \pcind \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 1~\land~(
+      \IssueForge(\sig,\msg,\dattrs,\sgid) = 1~\lor \\
+      \pcind \pcind \EvalForge(\sig,\msg,\dattrs,\sgid) = 1~\lor~
+      \InspectForge(\sig,\msg,\dattrs,\sgid) = 1) \\
+      \pcreturn 0 \\
+    }
+
+  % \end{minipage}
+  % \begin{minipage}[t]{0.5\textwidth}
+    \procedure{$\IssueForge(\sig,\msg,\dattrs,\sgid)$}{%
+      \pcreturn 0 \\
+    }
+
+    \procedure{$\EvalForge(\sig,\msg,\dattrs,\sgid)$}{%
+      \feval(\PUBUK[\uid],\CRED[\uid],\msg) = 0 \\
+      \pcreturn 0 \\
+    }
+
+    \procedure{$\InspectForge(\sig,\msg,\dattrs,\sgid)$}{%
+      \pcreturn 1~\pcif: \\
+      \pcind \pccomment{All \Obtain transcripts fail to inspect \sig} \\
       \pcind \nexists \gid \in \sgid:
       \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\sgid) = \bot~\lor \\
-     \pcind \pccomment{Such transcript exists, but ...} \\
+      \pcind \pccomment{A valid transcript exists, but ...} \\
       \pcind \exists\gid \in \sgid~\st~
@@
       \pcind \pcind \Judge(\y,\iproof,\sig,\msg,\dattrs,\GK[\sgid]) = 0~\lor \\
-     \pcind \pcind \pccomment{... or \Judge accepts the proof, but inspect
-       returns an invalid value} \\
+      \pcind \pcind \pccomment{... or \Judge accepts the proof, but \Inspect
+      returns an invalid value \y} \\
       \pcind \pcind \nexists \uid \in \CU \cup \HU~\st~
@@
       \pcind ) \\      
-     ) \\
       \pcreturn 0
     }
+%  \end{minipage}      
   \caption{Traceability experiment for \UAS schemes.}

### 2022-02-23 prism-backend/research/gsac/uas-model.tex
Just one issue seems to remain in traceability.

@@
   \Inspect only requires one inspector's secret key, though, and will thus only
-  produce that inspector's
-  function of the signature and message (this is to avoid complex interactive
-  protocols between many inspectors). This, however, creates a quite annoying
-  syntax. It may just be easier to restrict signatures to claims over the
-  attributes contained in \emph{one} credential.}
+  produce that inspector's function of the signature and message (this is to
+  avoid complex interactive protocols between many inspectors). This, however,
+  creates a quite annoying syntax. If this becomes unmanageable, it may just be
+  easier to restrict signatures to claims over the attributes contained in
+  \emph{one} credential.}
 
-\commentwho{Jesus}{Maybe we could remove the attribute sets \uattrs, \dattrs,
-  \tuattrs, \tdattrs, from the syntax, and assume that they are part of the
-  signatures and/or credentials. This would certainly lead to a cleaner syntax,
-  but, what impact would that have in other definitions, etc? Specifically, can
-  we support selective disclosure credentials without them? (if so, \fissue,
-  \feval and \finsp would be essential in doing so.); Right now, I am more in
-  favour of trying to remove the attribute sets from the definitions, as much
-  as possible (and see if we can still support plain selective disclosure).}
+\commentwho{Jesus}{I'm moving to a syntax that applies arbitrary functions over
+  the credentials, at different points (issuance, evaluation, and inspection).
+  Concretely, I'm moving away from the selective disclosure type of syntax.
+  However, it is my intention that selective disclosure becomes an especial case
+  of this. That is, the syntax should support both credentials with plain
+  selective attribute disclosure, and ``functional'' credentials.}
 
@@
   public part \ipk is added to the group public key \gpk, as well as \fissue.
-\item[$(\opk,\osk) \gets \OKeyGen(\parm,\feval,\finsp)$.] Given global system
-  parameters \parm, and two functions \feval and \finsp, an inspector runs
-  \OKeyGen to generate its inspecting key pair. The function \feval defines
-  requirements that signed message-signature pairs must meet. The function
-  \finsp defines the type of utility that will be extractable from those pairs
-  that do not meet \feval. Hereafter, we assume that the public part \opk is
-  added to the group public key \gpk, along with \feval and \finsp.
+\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
+  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
+  its inspecting key pair. The function \finsp defines the type of utility that
+  will be extractable from those pairs that do not meet conditions defined
+  at signing time (typically, by verifiers). Hereafter, we assume that the
+  public part \opk is added to the group public key \gpk, along with \finsp.
 \item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
@@
   \langle
-  \Obtain(\usk,\uattrs,\dattrs,
-  \ldblbrace (gpk_i,\cred_i,\tuattrs_i,\tdattrs_i)\rdblbrace_{i \in \Issuers}),
-  \Issue(\isk,\upk,\dattrs,
-  \ldblbrace (\gpk_i,\tdattrs_i)\rdblbrace_{i \in \Issuers})
+  \Obtain(\usk,\attrs,\ldblbrace (gpk_i,\cred_i)\rdblbrace_{i \in \Issuers}),
+  \Issue(\isk,\upk,\attrs,\ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})
   \rangle$.] %
@@
   \Obtain process, obtain a credential \cred from an issuer in the system, on
-  attribute set $\uattrs \cup \dattrs$, where the attributes in $\uattrs$ (and
-  the ones in the $\tuattrs_i$'s) are kept hidden from the issuer, while those
-  in \dattrs (as well as those in the $\tdattrs_i$'s) are revealed. Moreover,
-  $\uattrs \cup \dattrs$ must be a subset of $\bigcup_i (\tuattrs_i \cup
-  \tdattrs_i)$. In order to get the credential, the user may leverage previously
-  obtained credentials $\cred_i$ from a multiset of other issuers (including the
-  one to whom a new credential is being requested) with public keys $\gpk_i$.
-  Moreover, each credential $\cred_i$ can be used to prove claims over
-  undisclosed attributes $\tuattrs_i$. The user outputs the produced credential
-  \cred, while the issuer outputs the protocol transcript \utrans for the
-  produced credential.
-\item[$\sig \gets \Sign(\usk,\msg,\uattrs,\dattrs,
-  \ldblbrace (\gpk_i,\cred_i,\tuattrs_i,\tdattrs_i)\rdblbrace_{i \in \Issuers})$.]
+  attribute set $\attrs$ plus, possibly, blinded attributes attested by
+  previously obtained credentials $\cred_i$, from a multiset of other issuers
+  (which may include the one to whom a new credential is being requested) with
+  public keys $\gpk_i$. The user outputs the produced credential \cred, while
+  the issuer outputs the protocol transcript \utrans for the produced
+  credential. To ease notation, we assume that the group to which each
+  credential belongs is available from the credential itself, and therefore
+  omit the $\gpk_i$ values from the syntax, unless necessary to avoid ambiguity.
+\item[$\sig \gets \Sign(\usk,\msg,\feval,
+  \ldblbrace (\gpk_i,\cred_i)\rdblbrace_{i \in \Issuers})$.]
   The user with with secret key \usk, who obtained credentials $\cred_i$ from a
   multiset of issuers in the system, produces a signature \sig over message
-  \msg. The produced signature proves arbitrary claims over the set of
-  disclosed attributes $\bigcup_i \dattrs_i$ and undisclosed attributes
-  $\bigcup_i \uattrs_i$, which must be a subset of the corresponding disclosed
-  (resp. undisclosed) attributes \tdattrs (resp. \tuattrs) in the credentials
-  used to generate the signature.
+  \msg, meeting the conditions defined by \feval. As in \Obtain and \Issue, we
+  omit the credentials' group public keys when possible.
 \item[$1/0 \gets
-  \Verify(\sig,\msg,\dattrs, \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.]
-  Checks whether \sig is a valid signature, over message \msg, satisfying
-  arbitrary claims over disclosed attributes $\dattrs$, as well as
-  potentially other undisclosed attributes endorsed by issuers in the systsem
-  with public keys $\bigcup_i \gpk_i$.
-\item[$(\y,\iproof)/\bot \gets
-  \Inspect(\osk,\trans,\sig,\msg,\dattrs,
+  \Verify(\sig,\msg,\ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.]
+  Checks whether \sig is a valid signature, over message \msg.
+\item[$(\y,\iproof)/\bot \gets \Inspect(\osk,\trans,\sig,\msg,
   \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.] %
-  \commentwho{Jesus}{I do not like this description. It's complicated. This needs
-    to be rephrased from scratch.}
-  Executed by the inspector with opening key \osk. Receives a signature \sig
-  over message \msg, produced by a set of credentials satisfying claims on
-  disclosed attributes $\dattrs$, as well as potentially undisclosed
-  attributes, all endorsed by a multiset of issuers with public keys $\gpk_i$. 
-  If \trans is a valid set of transcripts of the execution of a
-  $\langle\Obtain,\Issue\rangle$ interactive protocol where the signer obtained
-  the credential associated to the inspector's group%
-  \footnote{Note: we are not constraining that the group to which the inspector
-    with key \osk belongs to, issued only one of the credentials used to
-    generate the signature being inspected.}, then the function outputs
-  a value $\y$ derived from the signer's credential and public key, and the
-  signed message, as well as a proof of correct inspection.
-\item[$1/0 \gets \Judge(\y,\iproof,\sig,\msg,\dattrs,
+  Executed by the inspector with private key \osk. Receives a signature \sig
+  over message \msg, produced by a set of credentials endorsed by a multiset of
+  issuers with public keys $\gpk_i$. If \trans contains a set of valid
+  transcripts corresponding to the $\langle\Obtain,\Issue\rangle$ interactive
+  protocol executions that issued one or more credentials used to produced \sig,
+  the function outputs a value $\y$ derived from the signer's public key,
+  credentials, message, and signature, as well as a proof of correct inspection.
+  We sometimes abuse notation, and write $\trans[\uid]$ to mean that the \Inspect
+  function is operating only for the obtain transcripts related to user \uid. 
+\item[$1/0 \gets \Judge(\y,\iproof,\sig,\msg,
   \ldblbrace \gpk_i\rdblbrace_{i \in \Issuers})$.] %
   Checks if \iproof is a valid inspection correctness proof for the value \y,
-  obtained by applying \Inspect to the the pair signature \sig over \msg. 
+  obtained by applying \Inspect to the the signature \sig over message \msg. 
 \end{description}
@@
 
-\paragraph{Issuance, evaluation, and inspection private functions.} %
+\paragraph{Issuance, evaluation, and inspection functions.} %
 We emphasize that, both in our syntax definition, as well as on the following
 modelling, we make use of three different and abstract functions: \fissue,
-\feval and \finsp. The three functions are run by users (maybe, on user-private
-data) as part of different algorithms in an \UAS scheme. In all cases, the
-user has to prove correctness of their computation. We introduce them next,
-\todo{and will give concrete examples in \secref{sec:uac-instantiation}.}
+\feval and \finsp. The three functions are introduced to allow customized
+governance of the resulting instantiation of an \UAS scheme. They will be
+defined by different parties, but in all cases, they are run by users (maybe,
+on user-private data). Also, in all cases, the user has to prove correctness of
+their computation. We introduce them next, \todo{and will give concrete examples
+  in \secref{sec:uac-instantiation}.}
 
 \begin{description}
-\item[$\fissue: (\uattrs,\dattrs) \rightarrow 0/1$.] Governs what customized
-  conditions an issuer requires in order to issue credentials, when receiving
-  a request from a user with a set of disclosed attributes \dattrs, and
-  undisclosed attributes \uattrs (which need to be kept private from the
-  issuer). \fissue returns 1 to accept a request, 0 to reject it.  
-\item[$\feval: (\upk,\scred,\msg) \rightarrow 0/1$.] Governs customized
-  conditions to define whether the owner of a user key and set of credentials --
-  or, more specifically, credentials encoding certain attributes -- should be
-  able to sign certain messages.
+\item[$\fissue: (\upk, \attrs,\scred) \rightarrow 0/1$.] Defined by issuers,
+  governs what customized conditions an issuer requires in order to issue
+  credentials, when receiving a request from user with public key \upk, for
+  attributes \attrs. \fissue may run checks on a (possibly empty) set of
+  additional credentials \scred, which may further be used for blind issuance
+  \commentwho{Jesus}{can it?}. \fissue returns $1$ to accept a request, $0$ to
+  reject it.  
+\item[$\feval: (\upk,\scred,\msg) \rightarrow 0/1$.] Can be defined by any party,
+  although we anticipate that this will typically be done by either singers,
+  verifiers, or some governance organization. It defines customized conditions
+  to be met by the owner of a user key \upk and set of credentials \scred, in
+  order to sign a concrete message \msg. Returns $1$ to allow the signing,
+  or $0$ to disallow it.
 \item[$\finsp: (\upk,\scred,\msg,\sig) \rightarrow \bin^*$.] Defines what
@@
 
-\todo{\fissue and \feval are not covered in the security definitions! Probably,
-  they should go into traceability -- which may need to be generalized into
-  unforgeability or something like that.}
-
 \paragraph{Helper Function \Identify.} In addition, we make use of a helper
-function \Identify for our non-frameability definition. This function receives
+function \Identify for some of our definitions. This function receives
 a signature and a user secret key, and determines whether the latter was used
@@
 \cite{bfg+11,cdl16} and group signatures without traditional open functions
-\cite{dl21,fgl21,gl19}. More concreltely \Identify function, defined as $1/0
+\cite{dl21,fgl21,gl19}. More concretely, the \Identify function, defined as $1/0
 \gets \Identify(\usk,\sig)$, conveys meaning to our non-frameability definition
@@
 \paragraph{Global Variables.} %
-All the honestly generated users (i.e., all honestly generated user key pairs,
-since we assume a one-to-one relationship between user and user key pair), as
-well as all honestly generated credentials, are assigned identifiers. Week's
-typically write as \uid for users' identifiers, and \cid for credentials'. The
-adversary can
-refer to any individual user or credential using the corresponding identifier --
-even though he may not know the actual contents of the key pairs or credentials.
-In games that involve challenge user or credential identifiers, we use \cuid and
-\ccid to refer to these challenge user/credential.
-%
-The games, usually through the oracles, keep track of the users (through
-set \UK) and credentials (through table \CRED) that are created as a result of
-oracle calls by the adversary, as well as the attributes that each credential
-is associated (through table \ATTR), and the user to which each credential has
-been issued to (through table \OWNR). We use the user and credential identifiers
-to reference specific user key pairs, credentials, and credential attributes.
-For instance, $\UK[\uid]$ refers to the user key pair corresponding to user
-with identifier \uid, $\PUBUK[\uid]$ refers to the public key of that key pair,
-and $\PRVUK[\uid]$ to the private key; credential $\CRED[\cid]$ refers to the
-credential data associated to the credential with identifier \cid; $\ATTR[\cid]$
-is the set of attributes that was assigned to the credential with identifier
-\cid; and $\OWNR[\cid]$ is set to the \uid corresponding to the user that
-credential \cid was issued to.
-%
-Additionally, the games keep track of all honest and corrupt users that have
-been generated, through sets \HU and \CU, respectively. They also keep track of
-the signatures that have been honestly produced, through the \SIG table. Since
-signatures are produced through credentials, the \SIG table is indexed with
-{\cid}s. For the anonymity game, we also need to keep track of the challenge
-signatures that the adversary has obtained, in order to prevent trivial wins
-by allowing any of them to be opened. 
-%
-All global variables are initially set by the games to empty values (denoted
-with $\bot$), and all tables/sets are initialized as empty tables/sets, denoted
-with $\emptyset$. Also, for readability, we abuse the syntax as follows: we
-write $\CRED[\uid]$ to mean $\CRED[\cid]$ for all $\cid$ such that
-$\OWNR[\cid] = \uid$; \todo{Something else?}
+The environment manages several global variables in the games posed to the
+adversary. Users are referred to with user identifiers, \uid; for credentials,
+we use \cid; for groups, \gid. For credentials and groups, we use bold font to
+denote sets: i.e., \scid and \sgid denot sets of credential and group
+identifiers. All tables/sets are initialized as empty tables/sets, denoted
+with $\emptyset$.
+
+\begin{description}
+\item[Tables for parties]:
+  \begin{description}
+  \item[\HU and \CU.] Keep track of honest (\HU) and corrupted (\CU) users;
+    i.e., they are sets of {\uid}s.
+  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers.
+    Since we assume only one issuer per group, they are sets of {\gid}s.
+  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) inspectors.
+    Since we assume only one inspector per group, they are sets of {\gid}s.
+  \end{description}
+\item[Tables for keys]:
+  \begin{description}
+  \item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$.
+    To refer to the key pair of a specific user, we use $\UK[\uid]$. \PUBUK
+    is a shorthand to refer to the public part, and \PRVUK refers to the
+    private part -- we may also index both by \uid.
+  \item[\IK, \PUBIK and \PRVIK.] Same as \UK, but for issuer key pairs. In
+    addition, \IK also includes the \fissue function, which is part of the
+    public key.
+  \item[\OK, \PUBOK, \PRVOK.] Same as \UK, but for inspector key pairs. In
+    addition, \OK also includes the \finsp function, which is part of the
+    public key.
+  \item[\GK.] We bundle public keys for issuers and inspectors into a common
+    public key for each group. We use the table \GK for that purpose which,
+    consequently, can also be indexed by \gid.
+  \end{description}
+\item[Tables for credentials-related data]:
+  \begin{description}
+  \item[\CRED.] Stores credentials obtained by honest users. Thus, it is
+    indexable by \cid. However, we slightly abuse notation and also use
+    $\CRED[\uid]$ as a shorthand for all credentials obtained by honest user
+    \uid, or $\CRED[\scid]$ to refer to a set of credentials with the
+    identifiers in set \scid.
+  \item[\OWNR.] Keeps track of which \uid is the owner of credentials obtained
+    by honest users; i.e., $\OWNR[\cid]$ returns the \uid that obtained
+    credential with identifier \cid.
+  \item[\ATTR.] Keeps track of the attributes assigned to a credential, as well
+    as the credential identifiers used to attest for any arbitrary claims
+    required for issuance. This table can be indexed by credential identifier
+    \cid.
+  \item[\GRP.] Keeps track of the group to which a credential belongs to; i.e.,
+    the group of the issuer who issued the credential. This table can be indexed
+    by credential identifier \cid.
+  \end{description}
+\item[STables for signatures]:
+  \begin{description}
+  \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
+    of honest users.
+  \item[\CSIG.] Maintains challenge signatures, generated via the \CHALb oracle,
+    by one of the challenge users in the anonymity game.
+  \end{description}
+\end{description}
 
@@
 trivially breaking the security properties formalized in the experiments.
-In the game-based definitions of our \GSAC model, we leverage the following
+In the game-based definitions of our \UAS model, we leverage the following
 oracles, which are formally defined in \figref{fig:oracles1} and
-\figref{fig:oracles2}. Note that we identify issuers and inspectors by the group
-identifier.
+\figref{fig:oracles2}.
 
@@
           (\ipk,\isk) \gets \IKeyGen(\parm) \\
-          \IK[\gid] \gets (\ipk,\isk,\fissue) \\
+          \IK[\gid] \gets ((\ipk,\fissue),\isk) \\
           \HI \gets \HI \cup \lbrace \gid \rbrace \\
-          \GK[\gid] \gets (\ipk,\fissue,\cdot,\cdot,\cdot) \\
+          \GK[\gid] \gets ((\ipk,\fissue),\cdot) \\
           \pcreturn \ipk \\
@@
           (\opk,\osk) \gets \OKeyGen(\parm) \\
-          \OK[\gid] \gets (\opk,\osk,\feval,\finsp) \\
+          \OK[\gid] \gets ((\opk,\finsp),\osk) \\
           \HO \gets \HO \cup \lbrace \gid \rbrace \\
-          \GK[\gid] \gets (\cdot,\cdot,\opk,\feval,\finsp) \\
+          \GK[\gid] \gets (\cdot,(\opk,\finsp)) \\
           \pcreturn \opk \\
@@
 
-        \procedure{$\ISSUE(\cid,\uid,\gid,\dattrs,
-          \ldblbrace (\sgid,\scid,\tdattrs) \rdblbrace)$}{%
+        \procedure{$\ISSUE(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
           \pcif \uid \notin \CU: \pcreturn \bot \\
@@
           \langle \adv, \\
-          \pcind \pcind
-          \Issue(\PRVIK[\gid],\PUBUK[\uid],
-          \ldblbrace (\GK[\sgid],\tdattrs)\rdblbrace) \rangle \\
-          \trans[\cid] \gets \utrans \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \bot, \dattrs) \\
+          \hspace*{45pt}
+          \Issue(\PRVIK[\gid],\PUBUK[\uid], \attrs,
+          \ldblbrace \GK[\sgid] \rdblbrace) \rangle \\
+          \trans[\cid] \gets \utrans;~\GRP[\cid] \gets \gid \\
+          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \attrs) \\
           \pcreturn \top \\          
@@
 
-        \procedure{$\OBTAIN(\cid,\uid,\gid,\uattrs,\dattrs,
-          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)$}{%
+        \procedure{$\OBTAIN(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
           \pcif \uid \notin \HU: \pcreturn \bot \\
@@
           \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\PRVUK[\uid],\uattrs,\dattrs, \\
-          \hspace*{65pt}
-          \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace), \\
+          \langle \Obtain(\PRVUK[\uid],\attrs, 
+          \ldblbrace \CRED[\scid] \rdblbrace), \\
           \hspace*{50pt} \adv \rangle \\
-          \CRED[\cid] \gets \cred \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \uattrs, \dattrs) \\
+          \CRED[\cid] \gets \cred;~\GRP[\cid] \gets \gid \\
+          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \attrs) \\
           \pcreturn \top \\
@@
 
-        \procedure{$\OBTISS(\cid,\uid,\gid,\uattrs,\dattrs,
-          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)$}{%
+        \procedure{$\OBTISS(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
           \pcif \uid \notin \HU: \pcreturn \bot \\
@@
           \langle \cred, \utrans \rangle \gets
-          \langle \Obtain(\PRVUK[\uid],\uattrs,\dattrs,\\
-          \hspace*{75pt} \ldblbrace (\GK[\sgid],
-          \CRED[\scid],\tuattrs,\tdattrs) \rdblbrace), \\
-          \hspace*{60pt} \Issue(\PRVIK[\gid],\PUBUK[\uid],
-          \ldblbrace (\GK[\sgid],\tdattrs)
-          \rdblbrace ) \rangle \\
+          \langle \Obtain(\PRVUK[\uid],\attrs,
+          \ldblbrace \CRED[\scid] \rdblbrace), \\
+          \hspace*{60pt} \Issue(\PRVIK[\gid],\PUBUK[\uid],\attrs,
+          \ldblbrace \GK[\sgid] \rdblbrace ) \rangle \\
           \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid,\uattrs,\dattrs) \\
+          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid,\attrs) \\
+          \GRP[\cid] \gets \gid \\
           \pcreturn \top \\
@@
 
-        \procedure{$\SIGN(\msg,\uid,\uattrs,\dattrs,
-          \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace )$}{%
+        \procedure{$\SIGN(\uid,\msg,\feval,\ldblbrace\scid\rdblbrace )$}{%
           \pcif \uid \notin \HU: \pcreturn \bot \\
           \cred \gets \CRED[\cid] \\
-          \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs, \\
-          \hspace*{42pt}
-          \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace) \\
+          \sig \gets \Sign(\PRVUK[\uid],\msg,\ldblbrace\CRED[\scid]\rdblbrace) \\
           \SIG[\uid] \gets \SIG[\uid] \cup
-          \lbrace (\sig,\msg,\scid,\uattrs,\dattrs,\sgid) \rbrace \\
+          \lbrace (\sig,\msg,\feval,\scid) \rbrace \\
           \pcreturn \sig \\
@@
 
-        \procedure{$\CHALb(\msg,
-          (\uid_{0,1},\uattrs_{0,1},\dattrs_{0,1},\ldblbrace (\sgid,\cscid_{0,1},
-          \tuattrs_{0,1},\tdattrs_{0,1}) \rdblbrace))$}{%          
+        \procedure{$\CHALb(\uid_{0,1},\msg,\feval,
+          \ldblbrace (\cscid_{0,1},\sgid) \rdblbrace))$}{%          
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
@@
           \pcreturn \bot \\
-          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\uattrs_b,\dattrs_b, \\
+          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\feval, \\
           \hspace*{42pt}
-          \ldblbrace (\GK[\sgid],\CRED[\scid_b],\tuattrs_b,\tdattrs_b) \rdblbrace) \\
+          \ldblbrace (\GK[\sgid],\CRED[\scid_b]) \rdblbrace) \\
           \CSIG \gets \CSIG \cup
-          \lbrace (\csig,\msg,\cscid_b,\uattrs_b,\dattrs_b,\sgid) \rbrace \\
+          \lbrace (\csig,\msg,\feval,\cscid_b,\sgid) \rbrace \\
           \pcreturn \csig
@@
       obtaining credentials, signatures, and processing them.}
-    \label{fig:oracles}
+    \label{fig:oracles2}
   \end{figure*}
@@
 \figref{fig:exp-uas-corr}. It states that a signature for some message \msg,
-revealing attributes \dattrs, which was honestly produced though a credential
-that was obtained by an honest user interacting with an honest issuer, with a
+revealing attributes \dattrs, which was honestly produced through a (set of)
+credentials obtained by an honest user interacting with honest issuer(s), with a
 set of attributes \attrs such that $\dattrs \subseteq \attrs$, must be accepted
@@
     \parm \gets \Setup(1^\secpar) \\
-    (\uid,\msg,\uattrs,\dattrs,
-    \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)
+    (\uid,\msg,\feval,\ldblbrace \scid \rdblbrace)
     \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS}(\parm) \\
-    \pcif \dattrs \nsubseteq \bigcup_{\cid \in \scid} \DATTR[\cid] \lor
-    \bigcup \tdattrs \nsubseteq \dattrs: \pcreturn \bot \\
-    \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs,
-    \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace ) \\
-    \pccomment{Signature fails to verify} \\
-    \pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 0: \pcreturn 0 \\
-    \pccomment{An inspector among those involved in credentials used to produce
-      \sig cannot inspect it} \\
+    \sig \gets \Sign(\PRVUK[\uid],\msg,\feval,
+    \ldblbrace \CRED[\scid] \rdblbrace ) \\
+    \pcif \Verify(\sig,\msg,\GK[\sgid]) = 0: \pcreturn 1~
+    \pccomment{\sig fails to verify} \\
+    \pcif \CorrectIssue(\uid,\ldblbrace \scid \rdblbrace)
+    = 0: \pcreturn 1~
+    \pccomment{Some \cid should not have been issued} \\
+    \pcif \CorrectEval(\uid,\msg,\feval,\ldblbrace \scid \rdblbrace)
+    = 0: \pcreturn 1~
+    \pccomment{\msg should not have been signed}\\
+    \pcif \CorrectInspect(\uid,\msg,\ldblbrace \scid \rdblbrace,
+    \sig) = 0: \pcreturn 1~
+    \pccomment{Some inspection of \sig is invalid}\\
+    \pcreturn 0 \\
+  }
+
+  \procedure{$\CorrectIssue(\uid,\ldblbrace \scid \rdblbrace)$}{
+    \forall \cid \in \scid~\textrm{parse}~\ATTR[\cid]~\textrm{as}~
+    (\scid^\cid,\attrs^\cid) \\
+    \forall \gid \in \GRP[\scid]~\textrm{parse}~\GK[\gid]~\textrm{as}~
+    ((\cdot,\fissue^\gid),\cdot) \\        
+    \pcif \exists \cid \in \scid, \gid \in \GRP[\scid]~\st~
+    \fissue^\gid(\PUBUK[\uid],\attrs^\cid,\CRED[\scid]^\cid) = 0: 
+    \pcreturn 0 \\
+    \pcreturn 1 \\   
+  }
+
+  \procedure{$\CorrectEval(\uid,\msg,\feval,\ldblbrace \scid \rdblbrace)$}{
+    \pcif \feval(\PUBUK[\uid],\CRED[\scid],\msg) = 0: \pcreturn 0 \\
+    \pcreturn 1 \\
+  }
+
+  \procedure{$\CorrectInspect(\uid,\msg,\ldblbrace \scid \rdblbrace, \sig)$}{
+    \textrm{Let}~\sgid \gets \GRP[\scid];~
+    \forall \gid \in \sgid~\textrm{parse}~\GK[\sgid]~\textrm{as}~
+    (\cdot,(\cdot,\finsp^\gid)) \\
+    \pccomment{\sig cannot be inspected by a suitable inspector} \\
     \pcif \exists \gid \in \sgid~\st~
-    \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,
-    \ldblbrace \GK[\sgid] \rdblbrace) = \bot: \pcreturn 0 \\
-    \pccomment{Some of the produced $(\y,\iproof)$ pairs is rejected by
-      \Judge \todo{This must be conditioned on \feval = 0!}} \\
+    \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\GK[\sgid]) = \bot: \pcreturn 0 \\
+    \pccomment{An $(\y,\iproof)$ pair is rejected by \Judge
+      % \todo{This must be conditioned on \feval = 0!}
+    } \\
     \pcif \exists \gid \in \sgid~\st~
-    (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,
-    \ldblbrace \GK[\sgid] \rdblbrace) \land \\
+    (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\GK[\sgid]) \land \\
     \pcind
-    \Judge(\y,\iproof,\sig,\msg,\dattrs,\ldblbrace \GK[\sgid] \rdblbrace) = 0):
+    \Judge(\y,\iproof,\sig,\msg,\GK[\sgid]) = 0):
     \pcreturn 0 \\
-    \textrm{Let}~(\fissue^\gid,\feval^\gid,\finsp^\gid)~\textrm{denote the
-      issue, evaluation and inspection functions defined} \\
-    \textrm{by each $\gid \in \sgid$} \pccomment{\todo{Come up with some
-        notation for this}} \\
-    \pccomment{\fissue rejects some issued credential} \\
-    \pcif \exists \gid \in \sgid~\st~\fissue^\gid(\tuattrs,\tdattrs) = 0:
-    \pcreturn 0 \\
-    \pccomment{\feval rejects the signature-message pair} \\
-    \pcif \exists \gid \in \sgid~\st~\feval^\gid(\msg,\sig) = 0: \pcreturn 0 \\
-    \pccomment{\y is the wrong value according to \finsp} \\
+    \pccomment{\y is the wrong value for some $\finsp^\gid$} \\
     \pcif \exists \gid \in \sgid~\st~
-    \y \neq \finsp^\gid(\PUBUK[\uid],\CRED[\scid])): \pcreturn 0 \\
-    \pcreturn 1
+    \y \neq \finsp^\gid(\PUBUK[\uid],\CRED[\scid],\msg,\sig)): \pcreturn 0 \\
   }
-  \caption{Correctness experiment for \UAS schemes. \todo{Reorganize this.}}
+
+  \caption{Correctness experiment for \UAS schemes.}
   \label{fig:exp-uas-corr}
@@
     \procedure{$\IssueForge(\sig,\msg,\dattrs,\sgid)$}{%
-      \pcreturn 0 \\
+      \pcif \exists \uid~\st~\Identify(\uid,\sig) = 1 \land
+      \fissue(\PUBUK[\uid],\attrs,\CRED[\uid]) = 0 \\
+      \pcind \pcreturn 1 \\
+      \pcelse \pcreturn 0 \\
     }
@@
     \procedure{$\EvalForge(\sig,\msg,\dattrs,\sgid)$}{%
+      \pccomment{\todo{This assumes that there is no $\cred \in \CRED[\uid]$ \st~
+          $\feval(\PUBUK[\uid],\CRED[\uid],\msg) = 0$, but}} \\
+      \pccomment{\todo{$\feval(\PUBUK[\uid],\CRED[\uid]\setminus \cred,\msg) = 1$}} \\
+      \pcif \exists \uid~\st~\Identify(\uid,\sig) = 1 \land
       \feval(\PUBUK[\uid],\CRED[\uid],\msg) = 0 \\
-      \pcreturn 0 \\
+      \pcind \pcreturn 1 \\
+      \pcelse \pcreturn 0 \\
     }
@@
       \pcind \nexists \gid \in \sgid:
-      \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\sgid) = \bot~\lor \\
+      \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\sgid) \neq \bot~\lor \\
       \pcind \pccomment{A valid transcript exists, but ...} \\
-      \pcind \exists\gid \in \sgid~\st~
-      \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs) =
+      \pcind \exists\gid \in \sgid, \exists \uid~\st~
+      \Inspect(\PRVOK[\gid],\trans[\uid],\sig,\msg,\dattrs) =
       (\y,\iproof)~\land (\\
@@
       returns an invalid value \y} \\
-      \pcind \pcind \nexists \uid \in \CU \cup \HU~\st~
-      \y = \finsp(\PUBUK[\uid],\CRED[\uid],\sig) \\
+      \pcind \pcind \y = \finsp(\PUBUK[\uid],\CRED[\uid],\msg,\sig) \\
       \pcind ) \\      

### 2022-02-26 prism-backend/research/gsac/uas-model.tex
Seemingly complete definition! Working on textual descriptions.

@@
 \label{sec:model-uas}
+
+\textcolor{red}{\textbf{WARNING:} The syntax and oracles below should be close
+  to what we want. The game definitions should may be farther (especially
+  traceability and non-frameability), but I'm having trouble with this level
+  of abstraction without having some concrete scheme to consult on. Therefore,
+  I'll start with a generic construction and then iterate the model again.
+  Thus, note that the current modelling is, essentially, wrong.}
 
@@
   is for now.}
-
-\commentwho{Jesus}{I'm trying to define \Sign, \Verify, \Inspect and \Judge such
-  that multiple credentials can be used to produce a single signature, proving
-  claims over arbitrary subsets of all the credentials owned by a user. \Verify
-  and, consequently, \Inspect and \Judge need to receive all the \gpk's.
-  \Inspect only requires one inspector's secret key, though, and will thus only
-  produce that inspector's function of the signature and message (this is to
-  avoid complex interactive protocols between many inspectors). This, however,
-  creates a quite annoying syntax. If this becomes unmanageable, it may just be
-  easier to restrict signatures to claims over the attributes contained in
-  \emph{one} credential.}
 
@@
   \Obtain(\usk,\attrs,\ldblbrace (gpk_i,\cred_i)\rdblbrace_{i \in \Issuers}),
-  \Issue(\isk,\upk,\attrs,\ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})
+  \Issue(\isk,\upk,\attrs,\ldblbrace (\gpk_i,\cred_i) \rdblbrace_{i \in \Issuers})
   \rangle$.] %
@@
   omit the $\gpk_i$ values from the syntax, unless necessary to avoid ambiguity.
-\item[$\sig \gets \Sign(\usk,\msg,\feval,
-  \ldblbrace (\gpk_i,\cred_i)\rdblbrace_{i \in \Issuers})$.]
-  The user with with secret key \usk, who obtained credentials $\cred_i$ from a
-  multiset of issuers in the system, produces a signature \sig over message
-  \msg, meeting the conditions defined by \feval. As in \Obtain and \Issue, we
-  omit the credentials' group public keys when possible.
-\item[$1/0 \gets
-  \Verify(\sig,\msg,\ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.]
-  Checks whether \sig is a valid signature, over message \msg.
-\item[$(\y,\iproof)/\bot \gets \Inspect(\osk,\trans,\sig,\msg,
-  \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})$.] %
+\item[$\sig \gets \Sign(\gpk,\usk,\cred,\msg,\feval)$.]
+  The user with with secret key \usk and credential \cred, produces a signature
+  \sig over message \msg, meeting the conditions defined by \feval.
+\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Checks whether \sig is a valid
+  signature, over message \msg, from a user in the group with public key \gpk.
+\item[$(\y,\iproof)/\bot \gets \Inspect(\gpk,\osk,\trans,\sig,\msg)$.] %
   Executed by the inspector with private key \osk. Receives a signature \sig
-  over message \msg, produced by a set of credentials endorsed by a multiset of
-  issuers with public keys $\gpk_i$. If \trans contains a set of valid
-  transcripts corresponding to the $\langle\Obtain,\Issue\rangle$ interactive
-  protocol executions that issued one or more credentials used to produced \sig,
-  the function outputs a value $\y$ derived from the signer's public key,
-  credentials, message, and signature, as well as a proof of correct inspection.
-  We sometimes abuse notation, and write $\trans[\uid]$ to mean that the \Inspect
-  function is operating only for the obtain transcripts related to user \uid. 
-\item[$1/0 \gets \Judge(\y,\iproof,\sig,\msg,
-  \ldblbrace \gpk_i\rdblbrace_{i \in \Issuers})$.] %
+  over message \msg. If \trans contains a set of valid transcripts corresponding
+  to the $\langle\Obtain,\Issue\rangle$ interactive protocol execution that
+  issued the used to produce \sig, the function outputs a value $\y$ derived
+  from the signer's public key, credential, message, and signature, as well as
+  a proof of correct inspection. We sometimes abuse notation, and write
+  $\trans[\uid]$ to mean that the \Inspect function is operating only for the
+  obtain transcripts related to user \uid.
+\item[$1/0 \gets \Judge(\gpk,\y,\iproof,\sig,\msg)$.] %
   Checks if \iproof is a valid inspection correctness proof for the value \y,
@@
   reject it.  
-\item[$\feval: (\upk,\scred,\msg) \rightarrow 0/1$.] Can be defined by any party,
+\item[$\feval: (\upk,\cred,\msg) \rightarrow 0/1$.] Can be defined by any party,
   although we anticipate that this will typically be done by either singers,
   verifiers, or some governance organization. It defines customized conditions
-  to be met by the owner of a user key \upk and set of credentials \scred, in
+  to be met by the owner of a user key \upk and credential \cred, in
   order to sign a concrete message \msg. Returns $1$ to allow the signing,
   or $0$ to disallow it.
-\item[$\finsp: (\upk,\scred,\msg,\sig) \rightarrow \bin^*$.] Defines what
-  utility value, derived from the user's public key, credentials, signed
-  message, and produced signature (or a subset thereof), should be extractable
-  by the group inspector.
+\item[$\finsp: (\upk,\cred,\msg) \rightarrow \bin^*$.] Defines what
+  utility value, derived from the user's public key, credential, and message
+  should be extractable by the group inspector.
 \end{description}
@@
   \begin{description}
-  \item[\CRED.] Stores credentials obtained by honest users. Thus, it is
-    indexable by \cid. However, we slightly abuse notation and also use
-    $\CRED[\uid]$ as a shorthand for all credentials obtained by honest user
-    \uid, or $\CRED[\scid]$ to refer to a set of credentials with the
-    identifiers in set \scid.
-  \item[\OWNR.] Keeps track of which \uid is the owner of credentials obtained
-    by honest users; i.e., $\OWNR[\cid]$ returns the \uid that obtained
-    credential with identifier \cid.
-  \item[\ATTR.] Keeps track of the attributes assigned to a credential, as well
-    as the credential identifiers used to attest for any arbitrary claims
-    required for issuance. This table can be indexed by credential identifier
-    \cid.
-  \item[\GRP.] Keeps track of the group to which a credential belongs to; i.e.,
-    the group of the issuer who issued the credential. This table can be indexed
-    by credential identifier \cid.
+  \item[\CRED.] Stores information related to credentials obtained by honest
+    users. Thus, it is indexable by \cid. More specifically, it stores tuples of
+    the form $(\uid,\cred,\gid,\attrs,\scid)$, where \uid is the identity of the
+    owner of the credential, \cred (when available) is the credential itself,
+    \gid is the identifier of the group to which the credential belongs, \attrs
+    are the attributes included in \cred, and \scid are the identifiers of any
+    additional credential that \uid used to request \cred.
+  \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
+    ``\uid such that $\CRED[\cid] = (\uid, \cdot, \cdot, \cdot, \cdot)$''.
+  \item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
+    ``\attrs such that $\CRED[\cid] = (\cdot, \cdot, \cdot, \attrs, \cdot)$''.
+  \item[\GRP.] For notational convenience, when we write $\GRP[\cid]$ we mean
+    ``\gid such that $\CRED[\cid] = (\cdot, \gid, \cdot, \cdot, \cdot)$''.
   \end{description}
-\item[STables for signatures]:
+\item[Tables for signatures]:
   \begin{description}
@@
           \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
-          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
           \langle \cdot, \utrans \rangle \gets
@@
           \Issue(\PRVIK[\gid],\PUBUK[\uid], \attrs,
-          \ldblbrace \GK[\sgid] \rdblbrace) \rangle \\
-          \trans[\cid] \gets \utrans;~\GRP[\cid] \gets \gid \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \attrs) \\
+          \ldblbrace \CRED[\scid] \rdblbrace) \rangle \\
+          \trans[\cid] \gets \utrans \\
+          \CRED[\cid] \gets (\uid, \cdot, \gid, \attrs, \scid) \\
           \pcreturn \top \\          
@@
           \hspace*{50pt} \adv \rangle \\
-          \CRED[\cid] \gets \cred;~\GRP[\cid] \gets \gid \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \attrs) \\
+          \CRED[\cid] \gets (\uid, \cdot, \gid, \attrs, \scid) \\          
           \pcreturn \top \\
@@
         \procedure{$\INSPECT(\gid,\sig,\msg)$}{%
-          \textrm{Let}~\uid~\textrm{be s.t.}~(\sig,\msg,\scid,\uattrs,\dattrs,\sgid)
+          \textrm{Let}~\uid~\textrm{be s.t.}~(\cid,\sig,\msg,\feval)
           \in \SIG[\uid] \\
-          \pcif \sig \in \CSIG: \pcreturn \bot \\
-          (\y,\oproof) \gets
-          \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\GK[\sgid]) \\
-          \pcreturn (\y,\oproof)
+          (\y,\iproof) \gets
+          \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg) \\
+          \pcif \CSIG[\sig] \neq \bot: \\
+          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\sig_{1-b},\msg,\feval)$} \\
+          \pcind (\y_{1-b},\iproof_{1-b}) \gets
+          \Inspect(\GK[\gid],\PRVOK[\gid],\\
+          \hspace*{107pt} \trans,\sig_{1-b},\msg) \\
+          \pcind \pcif \y_{1-b} \neq \y: \pcreturn \bot \\
+          \pcreturn (\y,\iproof)
         }
@@
           \hspace*{60pt} \Issue(\PRVIK[\gid],\PUBUK[\uid],\attrs,
-          \ldblbrace \GK[\sgid] \rdblbrace ) \rangle \\
-          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid,\attrs) \\
-          \GRP[\cid] \gets \gid \\
+          \ldblbrace \CRED[\scid] \rdblbrace ) \rangle \\
+          \trans[\cid] \gets \utrans \\
+          \CRED[\cid] \gets (\uid, \cred, \gid, \attrs, \scid) \\
           \pcreturn \top \\
@@
 
-        \procedure{$\SIGN(\uid,\msg,\feval,\ldblbrace\scid\rdblbrace )$}{%
-          \pcif \uid \notin \HU: \pcreturn \bot \\
-          \cred \gets \CRED[\cid] \\
-          \sig \gets \Sign(\PRVUK[\uid],\msg,\ldblbrace\CRED[\scid]\rdblbrace) \\
+        \procedure{$\SIGN(\uid,\cid,\msg,\feval)$}{%
+          \pcif \uid \notin \HU \lor \CRED[\cid] = \bot: \pcreturn \bot \\
+          \sig \gets \Sign(\GK[\GRP[\cid]],\PRVUK[\uid],\msg,\CRED[\cid]) \\
           \SIG[\uid] \gets \SIG[\uid] \cup
-          \lbrace (\sig,\msg,\feval,\scid) \rbrace \\
+          \lbrace (\cid,\sig,\msg,\feval) \rbrace \\
           \pcreturn \sig \\
@@
 
-        \procedure{$\CHALb(\uid_{0,1},\msg,\feval,
-          \ldblbrace (\cscid_{0,1},\sgid) \rdblbrace))$}{%          
+        \procedure{$\CHALb(\cuid_{0,1},\ccid_{0,1},\msg,\feval)$}{%
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
-          \pcif \exists \gid \in \sgid~\st~\gid \in \CO: \pcreturn \bot \\
+          \pcif \gid = \GRP[\ccid_0] \neq \GRP[\ccid_1]: \pcreturn \bot \\
+          \pcif \gid \in \CO: \pcreturn \bot \\
           \pcif \feval(\PUBUK[\uid_0],\CRED[\scid_0],\msg) \neq \\
@@
           \pcreturn \bot \\
-          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\feval, \\
-          \hspace*{42pt}
-          \ldblbrace (\GK[\sgid],\CRED[\scid_b]) \rdblbrace) \\
-          \CSIG \gets \CSIG \cup
-          \lbrace (\csig,\msg,\feval,\cscid_b,\sgid) \rbrace \\
-          \pcreturn \csig
+          \csig_b \gets \Sign(\GK[\gid],\PRVUK[\cuid_b],\CRED[\ccid_b],
+          \msg,\feval) \\
+          \csig_{1-b} \gets \Sign(\GK[\gid],\PRVUK[\cuid_{1-b}],\CRED[\ccid_{1-b}],
+          \msg,\feval) \\          
+          \CSIG[\csig_b] \gets 
+          \lbrace (\csig_{1-b},\msg,\feval) \rbrace \\
+          \pcreturn \csig_b
         }
@@
     \parm \gets \Setup(1^\secpar) \\
-    (\uid,\msg,\feval,\ldblbrace \scid \rdblbrace)
+    (\uid,\cid,\msg,\feval)
     \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS}(\parm) \\
-    \sig \gets \Sign(\PRVUK[\uid],\msg,\feval,
-    \ldblbrace \CRED[\scid] \rdblbrace ) \\
-    \pcif \Verify(\sig,\msg,\GK[\sgid]) = 0: \pcreturn 1~
+    \sig \gets \Sign(\GK[\cid],\PRVUK[\uid],\cid,\msg,\feval) \\
+    \pcif \Verify(\GK[\cid],\sig,\msg) = 0: \pcreturn 1~
     \pccomment{\sig fails to verify} \\
-    \pcif \CorrectIssue(\uid,\ldblbrace \scid \rdblbrace)
-    = 0: \pcreturn 1~
-    \pccomment{Some \cid should not have been issued} \\
-    \pcif \CorrectEval(\uid,\msg,\feval,\ldblbrace \scid \rdblbrace)
+    \pcif \CorrectIssue(\uid,\cid) = 0: \pcreturn 1~
+    \pccomment{\cid should not have been issued} \\
+    \pcif \CorrectEval(\uid,\cid,\msg,\feval)
     = 0: \pcreturn 1~
     \pccomment{\msg should not have been signed}\\
-    \pcif \CorrectInspect(\uid,\msg,\ldblbrace \scid \rdblbrace,
-    \sig) = 0: \pcreturn 1~
+    \pcif \CorrectInspect(\uid,\cid,\msg,\sig) = 0: \pcreturn 1~
     \pccomment{Some inspection of \sig is invalid}\\
@@
 
-  \procedure{$\CorrectIssue(\uid,\ldblbrace \scid \rdblbrace)$}{
-    \forall \cid \in \scid~\textrm{parse}~\ATTR[\cid]~\textrm{as}~
-    (\scid^\cid,\attrs^\cid) \\
-    \forall \gid \in \GRP[\scid]~\textrm{parse}~\GK[\gid]~\textrm{as}~
+  \procedure{$\CorrectIssue(\uid,\cid)$}{
+    \gid \gets \GRP[\cid] \\
+    \textrm{Parse}~\ATTR[\cid]~\textrm{as}~(\attrs^\cid,\scid^\cid);~
+    \textrm{Parse}~\GK[\gid]~\textrm{as}~
     ((\cdot,\fissue^\gid),\cdot) \\        
-    \pcif \exists \cid \in \scid, \gid \in \GRP[\scid]~\st~
-    \fissue^\gid(\PUBUK[\uid],\attrs^\cid,\CRED[\scid]^\cid) = 0: 
+    \pcif \fissue^\gid(\PUBUK[\uid],\attrs^\cid,\CRED[\scid]^\cid) = 0: 
     \pcreturn 0 \\
@@
 
-  \procedure{$\CorrectEval(\uid,\msg,\feval,\ldblbrace \scid \rdblbrace)$}{
-    \pcif \feval(\PUBUK[\uid],\CRED[\scid],\msg) = 0: \pcreturn 0 \\
+  \procedure{$\CorrectEval(\uid,\cid,\msg,\feval)$}{
+    \pcif \feval(\PUBUK[\uid],\CRED[\cid],\msg) = 0: \pcreturn 0 \\
     \pcreturn 1 \\
@@
 
-  \procedure{$\CorrectInspect(\uid,\msg,\ldblbrace \scid \rdblbrace, \sig)$}{
-    \textrm{Let}~\sgid \gets \GRP[\scid];~
-    \forall \gid \in \sgid~\textrm{parse}~\GK[\sgid]~\textrm{as}~
-    (\cdot,(\cdot,\finsp^\gid)) \\
-    \pccomment{\sig cannot be inspected by a suitable inspector} \\
-    \pcif \exists \gid \in \sgid~\st~
-    \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\GK[\sgid]) = \bot: \pcreturn 0 \\
-    \pccomment{An $(\y,\iproof)$ pair is rejected by \Judge
+  \procedure{$\CorrectInspect(\uid,\cid,\msg,\sig)$}{
+    \textrm{Let}~\gid \gets \GRP[\cid];~
+    \textrm{Parse}~\GK[\gid]~\textrm{as}~(\cdot,(\cdot,\finsp^\gid)) \\
+    \pccomment{\sig cannot be inspected} \\
+    \pcif \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg) = \bot: \pcreturn 0 \\
+    \pccomment{The produced $(\y,\iproof)$ pair is rejected by \Judge
       % \todo{This must be conditioned on \feval = 0!}
     } \\
-    \pcif \exists \gid \in \sgid~\st~
-    (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\GK[\sgid]) \land \\
-    \pcind
-    \Judge(\y,\iproof,\sig,\msg,\GK[\sgid]) = 0):
+    \pcif (\y,\iproof) \gets \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg)
+    \land
+    \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 0): \\
+    \pcind \pcreturn 0 \\
+    \pccomment{\y is the wrong value} \\
+    \pcif \y \neq \finsp^\gid(\PUBUK[\uid],\CRED[\cid],\msg)):
     \pcreturn 0 \\
-    \pccomment{\y is the wrong value for some $\finsp^\gid$} \\
-    \pcif \exists \gid \in \sgid~\st~
-    \y \neq \finsp^\gid(\PUBUK[\uid],\CRED[\scid],\msg,\sig)): \pcreturn 0 \\
+    \pcreturn 1
   }
@@
 the holder of a successfully shown credential, beyond that he owns a credential
-attesting for the claimed function of the attributes it contains. In both GS and
-AC, it is also typically required that
+attesting for the claimed predicate of the attributes it contains. In both GS
+and AC, it is also typically required that
 multiple signatures/presentations by the users are unlinkable. The approach to
@@
 signatures. In anonymous credentials, the game must further constraint the
-adversary to output credentials that have some common function of (a subset of)
-its attributes.
+adversary to output credentials that both meet the same (challenge) predicate
+of their attributes.
 
@@
 inspection functions, which is again a generalization over group signatures,
-as discussed in the sequel. The formal specification of the anonymity game is
+as discussed in the sequel. Other than this, the overall approach is the same:
+the adversary picks two honestly obtained credentials, and one of them (set
+by the $b$ value defining the $anon-b$ game) is used to program the \CHALb
+oracle. The formal specification of the anonymity game is
 given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,\CU\rbrace
@@
      \parm \gets \Setup(1^\secpar) \\
-     (\cscid_0,\cscid_1,\status) \gets \adv^{\Oanonc}(\choose,\parm) \\
+     (\ccid_0,\ccid_1,\status) \gets \adv^{\Oanonc}(\choose,\parm) \\
      b^* \gets \adv^{\Oanong} (\guess,\status) \\
@@
 is frequent in group signatures, ore any other function computable from the
-user public key, its credentials, and produced signature. \todo{Delve more in
-  this.}
+user public key, its credentials, and produced signature. Moreover, note that
+our notion is even stronger than the conventional ``CCA-like'' anonymity notion
+that gives the adversary access to the open oracle, only restricting it when
+trying to open challenge signature. Precisely the introduction of generic
+inspection functions allows us to \underline{\emph{let the adversary open
+    challenge signatures $\csig_b$}} as long as the counterpart $\csig_{1-b}$
+makes \Inspect produce the same \y value as output. This is certainly not
+possible when using conventional opening, since it directly outputs the identity
+of the signer -- which cannot be the same for different challenge users.
 
 \paragraph{Traceability.} %
-Traceability is one of the unforgeability-related properties in group
-signatures. It captures that any signature accepted by \Verify needs to open
-to one of the users that joined the group. While there is no traceability notion
-in anonymous credentials, it is natural to map it to their unforgeability
-property; if only because both require the issuer to be honest. Unforgeability
-in anonymous credentials typically ensures that no adversary can get a verifier
-to accept a credential presentation requiring a set of attributes that is not
-contained in one of the credentials controlled by the adversary.
+% Traceability is one of the unforgeability-related properties in group
+% signatures. It captures that any signature accepted by \Verify needs to open
+% to one of the users that joined the group. While there is no traceability notion
+% in anonymous credentials, it is natural to map it to their unforgeability
+% property; if only because both require the issuer to be honest. Unforgeability
+% in anonymous credentials typically ensures that no adversary can get a verifier
+% to accept a credential presentation requiring a set of attributes that is not
+% contained in one of the credentials controlled by the adversary.
 
-Our notion of traceability for \UAS is inspired by both. First, we restrict to
-signatures that are accepted by \Verify. For any such signature, \Inspect has to
-create a valid output (i.e., must not abort). The output of \Inspect has to be
-accepted by \Judge too. Moreover, there must exist one user (either honest or
-corrupt) who used his public key to obtain one or more credentials that allowed
-him to produce a signature which, once inspected, returns \y. The formal
+% Our notion of traceability for \UAS is inspired by both. First, we restrict to
+% signatures that are accepted by \Verify. For any such signature, \Inspect has to
+% create a valid output (i.e., must not abort). The output of \Inspect has to be
+% accepted by \Judge too. Moreover, there must exist one user (either honest or
+% corrupt) who used his public key to obtain one or more credentials that allowed
+% him to produce a signature which, once inspected, returns \y.
+In group signatures, traceability ensures that, in the presence of an honest
+issuer, every signature accepted by the verify algorithm must have been created
+by a user that joined the group.  With conventional opening, this is essentially
+checked by requesting the adversary to produce a signature, opening it, and
+checking whether or not it comes from a group member; i.e., this ensures that
+inspection cannot be forged in the presence of an honest issuer.
+%
+The somehow equivalent property in anonymous credentials is unforgeability. It
+requires that, again in the presence of an honest issuer, no adversary can
+succeed in a credential presentation for attributes (or predicates of them) that
+are not contained in a legitimately issued credential it controls. In other
+words, that the evaluation of the credential attributes was not forged.
+%
+Both notions have an equivalent in \UAS. That is, we need to ensure that, in the
+presence of an honest issuer, no signature accepted by \Verify can result in a
+wrong inspection, nor it can have been obtained by a wrong evaluation of some
+credential. Note, however, that \UAS offer the adversary yet another way to
+break traceability/unforgeability. Namely, an adversary can attempt to
+illegitimately obtain a credential that later enables it to produce untraceable
+signatures; i.e., signatures that evaluate correctly, or for which \Inspect
+returns the appropiate value, yet the adversary should not have been able to
+obtain a credential that allowed it to produce such signatures. Our notion of
+traceability/unforgeability thus challenges the adversary to produce a signature
+that breaks any of those conditions. The formal
 definition of the traceability experiment is given in \figref{fig:exp-uas-trace},
@@
 \begin{figure}[htp!]
-%  \begin{minipage}[t]{\textwidth}
     \procedure{$\ExpTrace(1^\secpar)$}{%
       \parm \gets \Setup(1^\secpar) \\
-      (\sig,\dattrs,\msg,\sgid) \gets
-      \adv^{\Otrace}(\parm) \\
-      \pcreturn 1~\pcif: \\
-      \pcind \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 1~\land~(
-      \IssueForge(\sig,\msg,\dattrs,\sgid) = 1~\lor \\
-      \pcind \pcind \EvalForge(\sig,\msg,\dattrs,\sgid) = 1~\lor~
-      \InspectForge(\sig,\msg,\dattrs,\sgid) = 1) \\
+      (\gid,\sig,\msg) \gets \adv^{\Otrace}(\parm) \\
+      \pcif \Verify(\GK[\gid],\sig,\msg) = 0: \pcreturn 0 \\
+      \pcif \EvalForge(\gid,\sig,\msg) = 1 \land
+      \InspectForge(\gid,\sig,\msg) = 1: \\
+      \pcind \pcreturn 1 \\
       \pcreturn 0 \\
@@
 
-  % \end{minipage}
-  % \begin{minipage}[t]{0.5\textwidth}
-    \procedure{$\IssueForge(\sig,\msg,\dattrs,\sgid)$}{%
-      \pcif \exists \uid~\st~\Identify(\uid,\sig) = 1 \land
-      \fissue(\PUBUK[\uid],\attrs,\CRED[\uid]) = 0 \\
+    \procedure{$\EvalForge(\gid,\sig,\msg)$}{%
+      \pcif \exists \uid~\st~\Identify(\uid,\sig) = 1~\land \\
+      \pcind \pccomment{\uid does not own a \cred that satisfies \feval...} \\
+      \pcind (\nexists \cred \in \CRED[\uid]~\st~
+      \feval(\PUBUK[\uid],\cred,\msg) = 1 ~\lor \\
+      \hspace*{13pt} \pccomment{... or \uid does, but \cred was itself obtained
+        fraudulently} \\
+      \hspace*{13pt} (\exists \cred \in \CRED[\uid]~\st~
+      \feval(\PUBUK[\uid],\cred,\msg) = 1~\land \\
+      \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
+      \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
+        $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\
       \pcind \pcreturn 1 \\
@@
 
-    \procedure{$\EvalForge(\sig,\msg,\dattrs,\sgid)$}{%
-      \pccomment{\todo{This assumes that there is no $\cred \in \CRED[\uid]$ \st~
-          $\feval(\PUBUK[\uid],\CRED[\uid],\msg) = 0$, but}} \\
-      \pccomment{\todo{$\feval(\PUBUK[\uid],\CRED[\uid]\setminus \cred,\msg) = 1$}} \\
-      \pcif \exists \uid~\st~\Identify(\uid,\sig) = 1 \land
-      \feval(\PUBUK[\uid],\CRED[\uid],\msg) = 0 \\
-      \pcind \pcreturn 1 \\
-      \pcelse \pcreturn 0 \\
-    }
-
-    \procedure{$\InspectForge(\sig,\msg,\dattrs,\sgid)$}{%
-      \pcreturn 1~\pcif: \\
-      \pcind \pccomment{All \Obtain transcripts fail to inspect \sig} \\
-      \pcind \nexists \gid \in \sgid:
-      \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\sgid) \neq \bot~\lor \\
+    \procedure{$\InspectForge(\gid,\sig,\msg)$}{%
+      \pccomment{All \Obtain transcripts fail to inspect \sig} \\
+      \pcif \Inspect(\PRVOK[\gid],\trans,\sig,\msg) \neq \bot~\lor \\
       \pcind \pccomment{A valid transcript exists, but ...} \\
-      \pcind \exists\gid \in \sgid, \exists \uid~\st~
-      \Inspect(\PRVOK[\gid],\trans[\uid],\sig,\msg,\dattrs) =
+      \pcind \exists \uid~\st~\Inspect(\PRVOK[\gid],\trans[\uid],\sig,\msg) =
       (\y,\iproof)~\land (\\
       \pcind \pcind \pccomment{... the proof is rejected by \Judge ...} \\
-      \pcind \pcind \Judge(\y,\iproof,\sig,\msg,\dattrs,\GK[\sgid]) = 0~\lor \\
-      \pcind \pcind \pccomment{... or \Judge accepts the proof, but \Inspect
-      returns an invalid value \y} \\
-      \pcind \pcind \y = \finsp(\PUBUK[\uid],\CRED[\uid],\msg,\sig) \\
-      \pcind ) \\      
+      \pcind \pcind \Judge(\y,\iproof,\sig,\msg,\GK[\sgid]) = 0~\lor \\
+      \pcind \pcind \pccomment{... or \uid does not own a \cred for which
+        \finsp outputs \y} \\
+      \pcind \pcind \nexists \cred \in \CRED[\uid]~\st~
+      \y = \finsp(\PUBUK[\uid],\cred,\msg)~\lor \\
+      \pcind \pcind \pccomment{... or \uid does, but \cred was itself obtained
+        fraudulently} \\
+      \pcind \pcind (\exists \cred \in \CRED[\uid]~\st~
+      \feval(\PUBUK[\uid],\cred,\msg) = 1~\land \\
+      \pcind \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
+      \pcind \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
+        $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\      
+      \pcind \pcreturn 1 \\      
       \pcreturn 0
     }
-%  \end{minipage}      
   \caption{Traceability experiment for \UAS schemes.}
@@
 \paragraph{Discussion on the generality of traceability in \UAS schemes.} %
-Note that this notion of traceability is, again, strictly more general than
-both group signatures and anonymous credentials. On the group signatures side,
-it all depends on the \Inspect function. If we set it to the traditional
-inspection function, where it returns the identity (index) of the signer, then
-our notion of traceability becomes exactly that of conventional group
-signatures. On the other hand, \Inspect may be set to a non-injective function,
-meaning that it can be possible that different user public keys, credentials and
-signature tuples, may produce the same output. In that case, though, our notion
-of traceability ensures that there must exist \emph{at least one} user capable
-of issuing that signature.
-%
-On the anonymous credentials side, note that our definition allows that users
-combine multiple credentials in a ``presentation''. However, in anonymous
-credentials, it is frequent to require that all the attributes proven in a
-presentation must be contained in a single credential. Note though that our
-definition requires all credentials to be tied to the same user identity.
-Therefore, it is a natural extension as (in the real life), it is very frequent
-to combine multiple identifying documents to prove that you are entitled to
-something. Moreover, any specific instantiation that restricts signatures
-to be associated to just one credential directly leads to the previously
-mentioned ``one credential per presentation'' rule.
+\todo{Comment why is this more general than AC and GS independently.}
 
-Finally, note that we can only ensure consistency of the value returned by
-\finsp, for all users, as long as the issuer is honest. This follows from the
-fact that \finsp depends on the user key pair and the credentials that are
-issued to each user. Therefore, a dishonest issuer could create untraceable
-credentials (i.e., issue credentials without updating the \trans table), so that
-the \finsp function outputs whatever desired value, yet it cannot be traced to
-any registered user. That is, this minimality argument is just a generalization
-of the one described in \cite[Section 4.3]{bsz05}. This is also consistent with
-the unforgeability requirement of anonymous credentials systems, as a corrupt
-issuer can grant arbitrary credentials to any user, and therefore honest
-issuers are required.
+Note also that we have implicitly assumed an unforgeability relaxation in the
+sense that we do not consider a forgery the fact that an adversary can obtain
+credentials that do not meet the \fissue predicate \emph{as long as they are
+  not used to produced untraceable signatures}. Indeed, this is in line with
+previous work \cite[Section 3.3.3]{ckl+15}, and it does make sense as, in the
+real world, being able to fraudulently obtain credentials that cannot be used
+later to authenticate, does not pose a risk.
+
+% Note that this notion of traceability is, again, strictly more general than
+% both group signatures and anonymous credentials.
+% %
+% On the group signatures side,
+% it all depends on the \Inspect function. If we set it to the traditional
+% inspection function, where it returns the identity (index) of the signer, then
+% our notion of traceability becomes roughly that of conventional group
+% signatures\footnote{With the exception that, in \UAS, the same user can own
+%   multiple credentials -- all of which must return the same identity}.
+% On the other hand, \Inspect may be set to a non-injective function,
+% meaning that it can be possible that different user public keys, credentials and
+% signature tuples, may produce the same output. In that case, though, our notion
+% of traceability ensures that there must exist \emph{at least one} user capable
+% of issuing that signature. Indeed, this is complemented with the non-frameability
+% property, that ensures that the adversary cannot produce a signature that
+% inspects to a value that no corrupt user can produce.
+% %
+
+% Finally, note that we can only ensure consistency of the value returned by
+% \finsp, for all users, as long as the issuer is honest. This follows from the
+% fact that \finsp depends on the user key pair and the credentials that are
+% issued to each user. Therefore, a dishonest issuer could create untraceable
+% credentials (i.e., issue credentials without updating the \trans table), so that
+% the \finsp function outputs whatever desired value, yet it cannot be traced to
+% any registered user. That is, this minimality argument is just a generalization
+% of the one described in \cite[Section 4.3]{bsz05}. This is also consistent with
+% the unforgeability requirement of anonymous credentials systems, as a corrupt
+% issuer can grant arbitrary credentials to any user, and therefore honest
+% issuers are required.
 
@@
 %
+
+The notion of non-frameability in \UAS schemes is unavoidably more subtle than
+in group signatures, though. To see this, we note that, by allowing any
+arbitrary inspection function \finsp to be used, it can be perfectly valid to
+have a signature produced by a corrupted user, output the same \y value upon
+inspection than the one that \finsp outputs when inspecting a signature by an
+honest user. As a concrete example, imagine an inspection function that returns
+the banking account number (or cryptocurrency address) to be used to request
+payment of a fine. In this example, a corrupted user and an honest user could
+both have delegated this to some agency\footnote{\todo{Maybe, come up with a
+    better example.}}, so it makes perfect sense that the inspection function
+returns the same value for both users.
+%
+Thus, in \UAS schemes, we must be more subtle, by necessity.
+
 In \UAS schemes, in order for a user to be framed \todo{...}. The
@@
     \parm \gets \Setup(1^\secpar) \\
-     (\sig,\dattrs,\msg,\sgid,\y,\iproof) \gets
-     \adv^{\Oframe}(\parm) \\
-     \pcreturn 1~\pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 1 \land
-     \Judge(\y,\iproof,\sig,\msg,\dattrs,\GK[\sgid]) = 1~\land \\
+     (\gid,\sig,\msg,\y,\iproof) \gets \adv^{\Oframe}(\parm) \\
+     \pcreturn 1~\pcif \Verify(\GK[\gid],\sig,\msg) = 1 \land
+     \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 1~\land \\
+     \pcind \pccomment{\adv~did not query \SIGN to get \sig, yet \sig originates
+       from an honest \uid, owning a credential that makes \finsp
+       evaluate to \y} \\
      \pcind \exists \uid \in \HU~\st~\Identify(\PRVUK[\uid],\sig) = 1 \land
-     \sig \notin \SIG[\uid] \\
+     (\cdot,\sig,\msg,\cdot) \notin \SIG[\uid]~\land\\
+     \pcind \exists \cred \in \CRED[\uid]~\st~
+     \finsp(\PUBUK[\uid],\cred,\msg) = \y \\
      \pcreturn 0
@@
 
+As an exercise, recall the Sign-Encrypt-Prove approach of group signatures in
+\cite{bsz05}. Roughly, there, a users' membership credential is a signature by
+the issuer of the user's public key. Then, a group signature is a signature
+over the message to be group-signed, signed with the user's private key, an
+encryption of the user's membership credential, and a NIZK proving that the
+private key used to sign the message corresponds to the public key in the
+encrypted membership credential. The opener just keeps a list of the public
+keys and the ``identity'' (index within the member list) of the user. Then,
+inspection (opening) simply consists of having the inspector decrypt the
+encrypted membership credential in the group signature, and find the matching
+public key in the members' list. Take the trivial inspection function
+$\finsp(\upk,\cred,\msg,\sig) = \cred$. Inspection in an \UAS scheme that uses
+this trivial \finsp function is equivalent to conventional opening. Then,
+following this exercise, our non-frameability definition for this inspection
+function would read as \todo{...}
+
 \subsection{Transformation to Interactive Presentations}

### 2022-02-27 prism-backend/research/gsac/uas-model.tex
First potentially stable model for UAS. I'm sure it will still change, though.

@@
 issuer, every signature accepted by the verify algorithm must have been created
-by a user that joined the group.  With conventional opening, this is essentially
+by a user who joined the group.  With conventional opening, this is essentially
 checked by requesting the adversary to produce a signature, opening it, and
-checking whether or not it comes from a group member; i.e., this ensures that
-inspection cannot be forged in the presence of an honest issuer.
+checking whether or not it comes from a group member; i.e., this ensures that,
+as long as there are verifiable inspections, inspection cannot be forged in the
+presence of an honest issuer.
 %
@@
 are not contained in a legitimately issued credential it controls. In other
-words, that the evaluation of the credential attributes was not forged.
+words, that the evaluation of the credential attributes cannot be forged.
 %
@@
 \paragraph{Discussion on the generality of traceability in \UAS schemes.} %
-\todo{Comment why is this more general than AC and GS independently.}
+The notion of traceability we present for \UAS is strictly more general than
+the corresponding one for group signatures. This is again the case as a direct
+consequence of the fact that \Inspect, which can return an arbitrary function
+of the signer's credential (and signed message), is a generalization of the
+conventional \Open -- if we make \Inspect return just the identity of the
+signer, then we get something similar to the usual notion of traceability.
+Although, even in that case, we need to take into account attributes, and the
+fact that the same user may obtain multiple credentials (that is why, even when
+having \Inspect return the identity of the signer, our notion is not exactly
+the same). And, in this sense, the unforgeability notion that \UAS have is
+equivalent to that of anonymous credentials. It would seem, though, that we do
+not need the traceability part of group signature; after all, it is the
+protection against wrong claims on attributes what enables meaningful and
+flexible authentication. However, the type of protection against misuses of
+the inspection functionality that we can get with an honest issuer (as in
+traceability) is much higher than without an honest user (as in
+non-frameability). Specifically, with an honest issuer we can ensure that
+the adversary cannot even alter the value returned by \Inspect on signatures
+by corrupt users. Whereas, with a corrupt issuer, all we can ensure is that
+the adversary cannot forge a signature from an honest user for which \Inspect
+returns the same value as a signature by that honest user would produce.
+Traceability is, therefore, a core property to ensure accountability
+\todo{Discuss this in more detail somewhere else.}
 
@@
 previous work \cite[Section 3.3.3]{ckl+15}, and it does make sense as, in the
-real world, being able to fraudulently obtain credentials that cannot be used
-later to authenticate, does not pose a risk.
-
-% Note that this notion of traceability is, again, strictly more general than
-% both group signatures and anonymous credentials.
-% %
-% On the group signatures side,
-% it all depends on the \Inspect function. If we set it to the traditional
-% inspection function, where it returns the identity (index) of the signer, then
-% our notion of traceability becomes roughly that of conventional group
-% signatures\footnote{With the exception that, in \UAS, the same user can own
-%   multiple credentials -- all of which must return the same identity}.
-% On the other hand, \Inspect may be set to a non-injective function,
-% meaning that it can be possible that different user public keys, credentials and
-% signature tuples, may produce the same output. In that case, though, our notion
-% of traceability ensures that there must exist \emph{at least one} user capable
-% of issuing that signature. Indeed, this is complemented with the non-frameability
-% property, that ensures that the adversary cannot produce a signature that
-% inspects to a value that no corrupt user can produce.
-% %
-
-% Finally, note that we can only ensure consistency of the value returned by
-% \finsp, for all users, as long as the issuer is honest. This follows from the
-% fact that \finsp depends on the user key pair and the credentials that are
-% issued to each user. Therefore, a dishonest issuer could create untraceable
-% credentials (i.e., issue credentials without updating the \trans table), so that
-% the \finsp function outputs whatever desired value, yet it cannot be traced to
-% any registered user. That is, this minimality argument is just a generalization
-% of the one described in \cite[Section 4.3]{bsz05}. This is also consistent with
-% the unforgeability requirement of anonymous credentials systems, as a corrupt
-% issuer can grant arbitrary credentials to any user, and therefore honest
-% issuers are required.
+real world, being able to fraudulently obtain credentials that cannot be later
+used to authenticate, does not pose a risk. However, an adversary breaking
+the issue policy defined by \fissue to get a credential and later using it to
+create a valid signature (i.e., meeting \feval or \finsp) is considered a
+forgery by our definition.
 
@@
 that signatures by different (possibly corrupt) users are linked, or directly
-by having open proofs output the identity of a user who did not create the
-signature being opened.
-%
+by having inspection proofs output the identity of a user who did not create the
+signature being inspected.
 
@@
 both have delegated this to some agency\footnote{\todo{Maybe, come up with a
-    better example.}}, so it makes perfect sense that the inspection function
-returns the same value for both users.
+    better example. How about spam filters that apply some sort of classification
+    engine? \finsp could be this engine, and emails by many different users could
+    be classified just as ``Spam'' or ``Not spam''}}, so it makes perfect sense
+that the inspection function returns the same value for both users.
 %
-Thus, in \UAS schemes, we must be more subtle, by necessity.
-
-In \UAS schemes, in order for a user to be framed \todo{...}. The
-non-frameability property for \UAS schemes is formally defined in
-\figref{fig:exp-uas-frame}, where $\Oframe \gets \lbrace\HU,\CU\rbrace\GEN,
+Thus, in \UAS schemes, we must be more subtle, by necessity. Note that we cannot
+just require that no adversary can produce a signature for which inspection
+returns the same value as it would for a signature honestly generated by an
+uncorrupted user. This is again the case since inspection may be non-injective,
+which means that inspection of a signature by some corrupted user may
+legitimately produce the same value as that of an honest user. Thus, we need
+to further refine the definition by requiring that (i) no adversary can produce
+a signature that is recognized (via \Identify) as originating from an honest
+user \uid, (ii) who owns a credential that makes \finsp return a valid \y value
+(i.e., generated by \Inspect along with a proof, and accepted by \Judge), (iii)
+without having queried the \SIGN oracle before. This non-frameability property
+for \UAS schemes is formally defined in \figref{fig:exp-uas-frame}, where
+$\Oframe \gets \lbrace\HU,\CU\rbrace\GEN,
 \lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN$
@@
 
-\paragraph{Discussion.} %
-\todo{Argue that our properties cover (and augment) a direct combination
-  (even if possible) of their GS and AC counterparts. Specifically, anonymity
-  of \GSAC is stronger than anonymity in GS and AC, and the same for trace and
-  non-frame.}
+\paragraph{Discussion on the generality of non-frameability in \UAS schemes.} %
+Anonymous credentials do not have non-frameability property and, thus, it is
+hard to make a comparison. However, we can draw some connections with AC schemes
+that support revocation, as revocation is somehow equivalent to linking, which
+is a type of inspection available in group signatures. In this sense, note that
+basic revocation (without straight deanonymization) can be trivially achieved
+through our generic \Inspect function. For instance, one could set \finsp to
+be a pseudorandom number seeded with the user's public key (or credential). In
+this sense, \Inspect could be essentially seen as a Verifiable Random Function.
+If we compare with group signatures, our notion is again more general than the
+conventional one. Indeed, in typical group signatures, \Open returns the
+identity of the signer, and thus does non-frameability not allow the same value
+to be returned when opening signatures by different users. Otherwise, a
+corrupted user controlled by the adversary could be able to create a signature
+opening to some honest user (hence, framing him). But this is again possible
+with our definition which, in case of making \Inspect equal \Open, becomes
+equivalent to conventional non-frameability. However, it also allows more
+generic situations in which signatures by different users may return the same
+value.
+
+\subsection{Functionality ``Transformations''}
+\label{ssec:transformations}
 
@@
 
-As an exercise, recall the Sign-Encrypt-Prove approach of group signatures in
-\cite{bsz05}. Roughly, there, a users' membership credential is a signature by
-the issuer of the user's public key. Then, a group signature is a signature
-over the message to be group-signed, signed with the user's private key, an
-encryption of the user's membership credential, and a NIZK proving that the
-private key used to sign the message corresponds to the public key in the
-encrypted membership credential. The opener just keeps a list of the public
-keys and the ``identity'' (index within the member list) of the user. Then,
-inspection (opening) simply consists of having the inspector decrypt the
-encrypted membership credential in the group signature, and find the matching
-public key in the members' list. Take the trivial inspection function
-$\finsp(\upk,\cred,\msg,\sig) = \cred$. Inspection in an \UAS scheme that uses
-this trivial \finsp function is equivalent to conventional opening. Then,
-following this exercise, our non-frameability definition for this inspection
-function would read as \todo{...}
-
-\subsection{Transformation to Interactive Presentations}
-\label{ssec:interactivetransform}
+\subsubsection{Transformation to Interactive Presentations}
+\label{sssec:interactivetransform}
 
 \todo{Is it possible to give it in some generic sense?}
+
+\subsubsection{Combining Multiple Credentials in One Presentation}
+
+\todo{I think this might be possible if we can use \fissue so that any user can
+  create arbitrary groups, where he is the issuer, an can thus run
+  \Obtain,\Issue protocols to combine credentials from other groups. This is
+  probably inefficient (or, at least, more than doing so wihtout having to
+  creat ad hoc groups), but at least allows the enhanced functionality...}
 

### 2022-02-28 prism-backend/research/gsac/introduction-uas.tex
Creating a separate document for UAS.

\section{Introduction}
\label{sec:introduction}

\commentwho{Jesus}{The following will most probably change completely if we
  are to submit this for publication (it least, it probably needs some deep
  reorganisation). However, this should capture tha main ideas.}

In this work, we focus on the generalization of privacy-preserving cryptographic
systems for authentication and identification. Two major research lines within
cryptography that work in this space are group signatures (GS) and anonymous
credentials (AC). In fact, despite having followed separate paths, the overall
approaches to build them are quite similar in a general sense. Consequently,
both have fed from each other.
%
\todo{Introduce GSs and ACs in two/three sentences each.}
%
On the one hand, their security models hold important similarities. Security in
group signatures is typically captured with game-based definitions, where the
main properties are anonymity, traceability and non-frameability. Anonymity
ensures privacy, essentially requiring that group signatures do not leak
information about their signer. Traceability and non-frameability are
unforgeability-related properties. Traceability requires that any valid group
signature must have been created by a user who joined the group;
non-frameability requires that no adversary can create a signature that somehow
``blames'' an honest user. Of course, variations in the functionality of group
signatures frequently require specialized properties, but these three are always
the main ones. In anonymous credentials, security is also usually captured with
game-based definitions (although UC models also exist). But, for anonymous
credentials, the main properties (again, up to variations) are simply anonymity
and unforgeability. Anonymity captures a similar privacy notion than group
signatures. Unforgeability of anonymous credentials also maps more clearly to
traceability in group signatures (non-frameability assumes a corrupt issuer,
which must be honest in traceability and unforgeability), and requires that
no adversary can succeed in proving ownership of a credential it does not own.
In both cases -- anonymity and unforgeability in anonymous credentials -- the
focus is on preventing leakage (anonymity) or forging (unforgeability) of the
attributes in a credential. Since group signatures do not (usually) have
attributes, this is a core difference in the modelling.

The first thing that raises attention here is the fact that, despite following
very similar approaches to build them, there is no equivalent property for
non-frameability in anonymous credentials. The most probable reason is that
anonymous credentials do not include the concept of ``opening'' which, in
group signatures, allows to extract the identity of the signer and is essential
to the non-frameability definition\footnote{Exceptions exist \cite{dl21}, but
  the definition is much easier with opening.}. Something similar (more limited
than opening, though) is sometimes considered by means of revocation of
anonymous credentials -- revoking credentials is essentially equivalent to
being able to link signatures by the same signer, which is considered in some
variants of group signatures \needcite. However, while revocation may be enough
if we aim to use credentials ``just'' for authentication, if we target more
advanced use cases, we may need to learn something else from the credential (or
its owner), beyond whether or not it has been revoked. Then, without an
equivalent to non-frameability, we would not be able to make any security claim
in the presence of dishonest issuers. On the other hand, it is
also noteworthy that the literature of group signatures has barely explored
the inclusion of attributes. With the exception of a few works on Attribute-Based
Group Signatures (ABGS) \needcite, members of a group in group signatures just
get a credential attesting for their membership to the group. Moreover, the
existence of attributes in anonymous credentials would seem to have been
instrumental in the surge of real-world use cases in the past few years. Indeed,
initiatives such as W3C's Verifiable Credentials (VCs) \needcite, or large
projects such as Idemix \needcite, which has in turn influenced VCs, are heavily
based on concepts from the anonymous credential literature, even to the point
that Idemix and its ``blockchain-based successor'', Indy \needcite, are now a
type of verifiable credentials \needcite.

Following the previous reasoning, we identify two aspects in which we can
improve group signatures and anonymous credentials. The first is by coming up
with some sort of primitive that combines both lines. That is, a scheme which
supports both (a variant of) opening and non-frameability as well as
attribute-based credentials. This seemingly natural evolution would thus
enable rich use cases in which accountable (by means of opening) and expressive
(by means of the attributes) authentication is necessary. While this is in
line with the previously mentioned ABGS works, we argue that our approach
is more general and flexible. Still, we anticipate that this may not be enough
to reach a scheme that can adapt to the majority of situations that may arise in
the real world. The reason is that the issuance and opening capabilities in the
previous schemes are generally either too rigid or have lacked a formal analysis
so far. For instance, in group signatures, the issuance protocol has barely been
the focus of study. Essentially, this interactive protocol requires the
prospective member to prove, in zero-knowledge, knowledge of a secret key
that will be attested in the membership credential. On the other hand, multiple
variants of the issuance protocol exist in anonymous credentials: protocols that
assume that the issuer knows all the attributes to be included in the credential,
protocols that allow blind issuance of attributes, protocols that let the user
leverage attributes in previous credentials, protocols that include ad hoc
rules at issuance time to enable extra functionality, such as delegation
\todo{cross-check that all this, especially the latter, is correct; and add
  cites}, etc. The problem is that a single change in this aspect, requires to
completely rethink the model. Something similar happens with the inspection
capabilities in group signatures. This frequently takes the shape of opening,
but many variants also exist, message-depdendent opening, linking, or variants
of linking, such as restricted linking only by other members of the group,
user controlled linking, or sequential linking \needcite. Again, any small
change in the inspection capabilities requires a full redesign of the model.
This rigidness in inspection is specially crucial, as inspection is the key
to the very nature of the privacy notion in group signatures. Taking this into
account, it is understandable that many have tried to find some sort of
equilibrium between full anonymity (no inspection at all), and full
accountability (by means of conventional open). Thus, we aim at finding a
generic way to support multiple variants of inspection, from the common model.
Finally, actual evaluation of group signatures is the last component that is
too rigid. Namely, in group signatures, when verifying a signature, either it
has been rightly produced by a group member using his secret key and membership
credential, or not. Luckily for us, anonymous credentials have done a great job
in supporting high expressiveness into what a presentation can tell beyond just
proving knowledge of a (group) key. Thus, by integreating anonymous credentials
and group signatures in a sort of combined primitive, we get \emph{for free}
the benefits of this high expressiveness that previous work on anonymous
credentials have reached in regards to what one can prove given a credential.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:

### 2022-02-28 prism-backend/research/gsac/model-uas.tex
Creating a separate document for UAS.

--- 2022-02-27 prism-backend/research/gsac/uas-model.tex
@@
 \label{sec:model-uas}
-
-\textcolor{red}{\textbf{WARNING:} The syntax and oracles below should be close
-  to what we want. The game definitions should may be farther (especially
-  traceability and non-frameability), but I'm having trouble with this level
-  of abstraction without having some concrete scheme to consult on. Therefore,
-  I'll start with a generic construction and then iterate the model again.
-  Thus, note that the current modelling is, essentially, wrong.}
-
-Universal Anonymous Signatures.
 
@@
 
-\subsection{Functionality ``Transformations''}
+\subsection{Functionality ``Transformations'' and Special Cases}
 \label{ssec:transformations}
-
-\todo{It would be nice to prove that a \GSAC scheme to which we remove the
-  \Open/\Judge functions becomes an AC scheme. And conversely, a \GSAC scheme
-  where all credentials have no attributes, and where we restrict to only
-  one credential per user, becomes a conventional GS scheme.}
 
@@
   probably inefficient (or, at least, more than doing so wihtout having to
-  creat ad hoc groups), but at least allows the enhanced functionality...}
+  create ad hoc groups), but at least allows the enhanced functionality...}
+
+\subsubsection{Restricting to Conventional GS and AC Schemes}
+
+\todo{It would be nice to prove that a \GSAC scheme to which we remove the
+  \Open/\Judge functions becomes an AC scheme. And conversely, a \GSAC scheme
+  where all credentials have no attributes, and where we restrict to only
+  one credential per user, becomes a conventional GS scheme.}
+
+\subsubsection{Group Signatures with Message Dependent Opening}
+
+\todo{Describe what type of \finsp would be needed to achieve a functionality
+  similar to that of GS-MDO. Does this fit our model straight away? Maybe also
+  show how other types of GS could be ``mimicked'' (e.g., GS only with linking).
+  This would also be good to test if the model is as generic as I think it is}
+
+\subsubsection{Ring Signatures}
+
+\todo{Can we leverage the \fissue and/or \feval predicates to make our model
+  suitable for some sort of Ring Signature scheme?}
 
@@
 %%% mode: latex
-%%% TeX-master: "gsac"
+%%% TeX-master: "uas"
 %%% End:

### 2022-03-01 prism-backend/research/gsac/model-uas.tex
Made a pass before sharing.

@@
 \label{sec:model-uas}
+
+We now define our model for Universal Anonymous Signatures. At a very high
+level, it is a combination of the main models for group signatures and
+anonymous credentials -- we try to extract the most useful features from both.
+Instead of considering just one group, as in group signatures, we directly and
+explicitly include support for multiple issuers as in anonymous credentials.
+Moreover, instead of letting each user own a single credential, we allow
+multiple credentials per user, even within the same group. This of course
+makes us put forward refined notions of anonymity, traceability and
+non-frameability. Note that, property-wise, we keep the three main properties
+from group signatures, rather than sticking to the two usual properties of
+anonymous credentials (anonymity and unforgeability). This is a consequence
+of keeping the inspection capability from group signatures, which we consider
+crucial in order to ensure some sort of accountability even in very adversarial
+contexts where the issuer may be corrupt.
+%
+But, as stated in the introduction, we go beyond just combining anonymous
+credentials and group signatures, and include support for arbitrary policies
+during issuance, signing, and inspection. Consequently, our model needs to
+capture the flexibility that these policies provide. In short, manipulations of
+the issuance policy are only considered forgeries if the adversary manages to
+create a valid signature using a credential that was obtained by dishonestly
+manipulating the issuance policy (we discuss this further in the traceability
+definition). Signing policies are taken into account both in the anonymity
+property, where we need to restrict that both credentials used to produce the
+challenge signatures always satisfy the policy, and in traceability.
+\commentwho{Jesus}{Think a bit more about the following claim, and update if
+  needed.}
+We cannot give any assurance on the signing policies when the issuers are
+corrupt, and thus they are not considered in the non-frameability property.
+Inspection policies are considered both in traceability and non-frameability,
+where the adversary wins if it manages to somehow alter the correct output of
+\Inspect. What is even suprising, is that given the possible non-injectivity of
+the inspection function lets us reach an even stronger notion of anonymity.
+Namely, \uline{we can allow the adversary to open challenge signatures, as
+  long as the inspection function outputs the same value for both}. We give more
+details on these aspects in the actual definitions of the security properties.
+%
+Finally, from a functional perspective, we require that both issuer and
+inspector fix the issuance predicate \fiss and inspection function \finsp when
+generating their public keys. Indeed, both will be part of the common group key.
+This also makes our definitions easier, as supporting multiple issuance
+predicate and inspection functions per group would require to consider many
+special cases -- and, anyway, that would probably end up being equivalent to
+just requiring that a new group needs to be created per each $(\fissue,\$finsp)$
+pair. On the other hand, signing policies can be defined at signing time (in
+practice, most probably by the verifiers). This is in line with the usual
+practice in anonymous credentials, that let users prove arbitrary claims on
+their credentials, as long as they are met by the contained attributes.
 
@@
   is for now.}
-
-\commentwho{Jesus}{I'm moving to a syntax that applies arbitrary functions over
-  the credentials, at different points (issuance, evaluation, and inspection).
-  Concretely, I'm moving away from the selective disclosure type of syntax.
-  However, it is my intention that selective disclosure becomes an especial case
-  of this. That is, the syntax should support both credentials with plain
-  selective attribute disclosure, and ``functional'' credentials.}
 
@@
 \cite{dl21,fgl21,gl19}. More concretely, the \Identify function, defined as $1/0
-\gets \Identify(\usk,\sig)$, conveys meaning to our non-frameability definition
-conditioned on the fact that, given a signature \sig accepted by \Verify,
-\Identify returns $1$ for exactly one \usk.
+\gets \Identify(\usk,\sig)$, conveys meaning to our definitions conditioned on
+the fact that, given a signature \sig accepted by \Verify, \Identify returns $1$
+for exactly one \usk.
 
@@
 we use \cid; for groups, \gid. For credentials and groups, we use bold font to
-denote sets: i.e., \scid and \sgid denot sets of credential and group
+denote sets: i.e., \scid and \sgid denote sets of credential and group
 identifiers. All tables/sets are initialized as empty tables/sets, denoted
@@
 identity of the user -- which can certainly be the member index itself, as it
-is frequent in group signatures, ore any other function computable from the
+is frequent in group signatures, or any other function computable from the
 user public key, its credentials, and produced signature. Moreover, note that
@@
 trying to open challenge signature. Precisely the introduction of generic
-inspection functions allows us to \underline{\emph{let the adversary open
+inspection functions allows us to \uline{\emph{let the adversary open
     challenge signatures $\csig_b$}} as long as the counterpart $\csig_{1-b}$
@@
 The notion of traceability we present for \UAS is strictly more general than
-the corresponding one for group signatures. This is again the case as a direct
+the corresponding one for group signatures. This is again a direct
 consequence of the fact that \Inspect, which can return an arbitrary function
@@
 equivalent to that of anonymous credentials. It would seem, though, that we do
-not need the traceability part of group signature; after all, it is the
+not need the traceability part of group signatures; after all, it is the
 protection against wrong claims on attributes what enables meaningful and
@@
 the adversary cannot even alter the value returned by \Inspect on signatures
-by corrupt users. Whereas, with a corrupt issuer, all we can ensure is that
+by corrupt users, nor the output of the signing predicate \feval. Whereas, with
+a corrupt issuer, all we can ensure is that
 the adversary cannot forge a signature from an honest user for which \Inspect
-returns the same value as a signature by that honest user would produce.
-Traceability is, therefore, a core property to ensure accountability
-\todo{Discuss this in more detail somewhere else.}
+returns the same value as a signature by that honest user would produce; and,
+certainly, a corrupt issuer can arbitrarily issue credentials meeting any
+desired predicate \feval .Traceability is, therefore, a core property to ensure
+accountability.
 
@@
 arbitrary inspection function \finsp to be used, it can be perfectly valid to
-have a signature produced by a corrupted user, output the same \y value upon
+have a signature produced by a corrupted user output the same \y value upon
 inspection than the one that \finsp outputs when inspecting a signature by an
@@
      \finsp(\PUBUK[\uid],\cred,\msg) = \y \\
+     \pccomment{\todo{I don't think we can give any assurance about \feval here,
+         given that issuers are corrupt. But still, think about it.}} \\
      \pcreturn 0
@@
 conventional one. Indeed, in typical group signatures, \Open returns the
-identity of the signer, and thus does non-frameability not allow the same value
+identity of the signer, and thus non-frameability does not allow the same value
 to be returned when opening signatures by different users. Otherwise, a
@@
 \label{ssec:transformations}
+
+\commentwho{Jesus}{This section is aimed at showing the ``universality'' of
+  our model. If I'm not mistaken, ideally, it should support the following
+  variations (except the transformation to interactive presentations,
+  probably).}
 
@@
 
-\todo{Can we leverage the \fissue and/or \feval predicates to make our model
-  suitable for some sort of Ring Signature scheme?}
+\todo{Can we come up with a (\fissue,\feval,\finsp) tuple that allows us to
+  somehow mimic ring signatures (i.e., ``a group signature without issuer nor
+  opening''? Does the model support this?}
 

### 2022-03-04 prism-backend/research/gsac/model-uas.tex
Working on syntax for generic construction.

@@
 Finally, from a functional perspective, we require that both issuer and
-inspector fix the issuance predicate \fiss and inspection function \finsp when
+inspector fix the issuance predicate \fissue and inspection function \finsp when
 generating their public keys. Indeed, both will be part of the common group key.

### 2022-03-16 prism-backend/research/gsac/model-uas.tex
Updating model and generic construction.

@@
 special cases -- and, anyway, that would probably end up being equivalent to
-just requiring that a new group needs to be created per each $(\fissue,\$finsp)$
+just requiring that a new group needs to be created per each $(\fissue,\finsp)$
 pair. On the other hand, signing policies can be defined at signing time (in
@@
   \Obtain(\usk,\attrs,\ldblbrace (gpk_i,\cred_i)\rdblbrace_{i \in \Issuers}),
-  \Issue(\isk,\upk,\attrs,\ldblbrace (\gpk_i,\cred_i) \rdblbrace_{i \in \Issuers})
+  \Issue(\isk,\upk,\attrs,\ldblbrace \gpk_i) \rdblbrace_{i \in \Issuers})
   \rangle$.] %
@@
   \sig over message \msg, meeting the conditions defined by \feval.
-\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Checks whether \sig is a valid
-  signature, over message \msg, from a user in the group with public key \gpk.
-\item[$(\y,\iproof)/\bot \gets \Inspect(\gpk,\osk,\trans,\sig,\msg)$.] %
+\item[$1/0 \gets \Verify(\gpk,\sig,\msg,\feval)$.] Checks whether \sig is a
+  valid signature, over message \msg, from a user in the group with public key
+  \gpk, for signing function \feval.
+\item[$(\y,\iproof)/\bot \gets \Inspect(\gpk,\osk,\trans,\sig,\msg,\feval)$.] %
   Executed by the inspector with private key \osk. Receives a signature \sig
-  over message \msg. If \trans contains a set of valid transcripts corresponding
+  over message \msg and evaluation function \feval. If \trans contains a set of
+  valid transcripts corresponding
   to the $\langle\Obtain,\Issue\rangle$ interactive protocol execution that
-  issued the used to produce \sig, the function outputs a value $\y$ derived
-  from the signer's public key, credential, message, and signature, as well as
-  a proof of correct inspection. We sometimes abuse notation, and write
+  issued the credential used to produce \sig, the function outputs a value $\y$
+  derived from the signer's public key, credential, message, and signature, as
+  well as a proof of correct inspection. We sometimes abuse notation, and write
   $\trans[\uid]$ to mean that the \Inspect function is operating only for the
   obtain transcripts related to user \uid.
-\item[$1/0 \gets \Judge(\gpk,\y,\iproof,\sig,\msg)$.] %
+\item[$1/0 \gets \Judge(\gpk,\y,\iproof,\sig,\msg,\feval)$.] %
   Checks if \iproof is a valid inspection correctness proof for the value \y,
@@
   reject it.  
-\item[$\feval: (\upk,\cred,\msg) \rightarrow 0/1$.] Can be defined by any party,
-  although we anticipate that this will typically be done by either singers,
-  verifiers, or some governance organization. It defines customized conditions
-  to be met by the owner of a user key \upk and credential \cred, in
-  order to sign a concrete message \msg. Returns $1$ to allow the signing,
-  or $0$ to disallow it.
-\item[$\finsp: (\upk,\cred,\msg) \rightarrow \bin^*$.] Defines what
-  utility value, derived from the user's public key, credential, and message
-  should be extractable by the group inspector.
+\item[$\feval: (\upk,\cred,\msg) \rightarrow \varrngfeval$.] Can be defined by any
+  party, although we anticipate that this will typically be done by either
+  signers, verifiers, or some governance organization. It defines customized
+  conditions to be met by the owner of a user key \upk and credential \cred,
+  in order to sign a concrete message \msg. Its outputs  $\varrngfeval$ must
+  belong in a well defined set \rngfeval, with the restriction that it must
+  return $0$ when the conditions for signing are not met.
+\item[$\finsp: (\varrngfeval,\upk,\cred,\msg) \rightarrow \varrngfinsp$.]
+  Defines what utility value, derived from the user's public key, credential,
+  and message should be extractable by the group inspector. Note that \finsp
+  also receives as input a value in the range of the \feval function, \rngfeval.
+  This will allow inspection logic to depend on the value produced by the
+  evaluation function. The output of \finsp is a value \varrngfinsp, which must
+  belong in a well defined set \rngfinsp.
 \end{description}
@@
           (\y,\iproof) \gets
-          \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg) \\
+          \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg,\feval) \\
           \pcif \CSIG[\sig] \neq \bot: \\
@@
           \Inspect(\GK[\gid],\PRVOK[\gid],\\
-          \hspace*{107pt} \trans,\sig_{1-b},\msg) \\
+          \hspace*{107pt} \trans,\sig_{1-b},\msg,\feval) \\
           \pcind \pcif \y_{1-b} \neq \y: \pcreturn \bot \\
@@
           \pcif \uid \notin \HU \lor \CRED[\cid] = \bot: \pcreturn \bot \\
-          \sig \gets \Sign(\GK[\GRP[\cid]],\PRVUK[\uid],\msg,\CRED[\cid]) \\
+          \sig \gets \Sign(\GK[\GRP[\cid]],\PRVUK[\uid],\msg,\CRED[\cid],\feval) \\
           \SIG[\uid] \gets \SIG[\uid] \cup
@@
 Correctness of \UAS schemes is formalized through the experiment in
-\figref{fig:exp-uas-corr}. It states that a signature for some message \msg,
-revealing attributes \dattrs, which was honestly produced through a (set of)
-credentials obtained by an honest user interacting with honest issuer(s), with a
-set of attributes \attrs such that $\dattrs \subseteq \attrs$, must be accepted
-by \Verify. Moreover, an honestly produced correctness proof of opening for such
-signature, revealing the public key pair of the user, must also be accepted by
-\Judge.
+\figref{fig:exp-uas-corr}. It states that a signature over any arbitrary message
+and valid function \feval \todo{Should we explicitly check \feval in the game?
+  If so, how?},
+produced honestly by an honest user \uid with credential \cid, is accepted by
+\Verify. Moreover, upon issuance of the credential \cid, it must have met the
+conditions set by \fissue. Similarly, the value returnd by \Inspect must be
+accepted by \Judge, and must match the output of applying \finsp on \feval, the
+credential, user key, and message.
 
@@
     \sig \gets \Sign(\GK[\cid],\PRVUK[\uid],\cid,\msg,\feval) \\
-    \pcif \Verify(\GK[\cid],\sig,\msg) = 0: \pcreturn 1~
+    \pcif \Verify(\GK[\cid],\sig,\msg,\feval) = 0: \pcreturn 1~
     \pccomment{\sig fails to verify} \\
@@
     \pccomment{\cid should not have been issued} \\
-    \pcif \CorrectEval(\uid,\cid,\msg,\feval)
-    = 0: \pcreturn 1~
-    \pccomment{\msg should not have been signed}\\
-    \pcif \CorrectInspect(\uid,\cid,\msg,\sig) = 0: \pcreturn 1~
-    \pccomment{Some inspection of \sig is invalid}\\
+    % \pcif \CorrectEval(\uid,\cid,\msg,\feval)
+    % = 0: \pcreturn 1~
+    % \pccomment{\msg should not have been signed} \\
+    \pcif \CorrectEvalInspect(\uid,\cid,\msg,\sig,\feval) = 0: \pcreturn 1~
+    \pccomment{The combination of evaluation and inspection is wrong} \\
     \pcreturn 0 \\
@@
 
-  \procedure{$\CorrectEval(\uid,\cid,\msg,\feval)$}{
-    \pcif \feval(\PUBUK[\uid],\CRED[\cid],\msg) = 0: \pcreturn 0 \\
-    \pcreturn 1 \\
-  }
+  % \procedure{$\CorrectEval(\uid,\cid,\msg,\feval)$}{
+  %   \pcif \feval(\PUBUK[\uid],\CRED[\cid],\msg) = 0: \pcreturn 0 \\
+  %   \pcreturn 1 \\
+  % }
 
-  \procedure{$\CorrectInspect(\uid,\cid,\msg,\sig)$}{
+  \procedure{$\CorrectEvalInspect(\uid,\cid,\msg,\sig,\feval)$}{
     \textrm{Let}~\gid \gets \GRP[\cid];~
@@
     \pccomment{\sig cannot be inspected} \\
-    \pcif \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg) = \bot: \pcreturn 0 \\
+    \pcif \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg,\feval) = \bot: \pcreturn 0 \\
     \pccomment{The produced $(\y,\iproof)$ pair is rejected by \Judge
@@
     } \\
-    \pcif (\y,\iproof) \gets \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg)
+    \pcif (\y,\iproof) \gets \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg,\feval)
     \land
-    \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 0): \\
+    \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 0: \\
     \pcind \pcreturn 0 \\
     \pccomment{\y is the wrong value} \\
-    \pcif \y \neq \finsp^\gid(\PUBUK[\uid],\CRED[\cid],\msg)):
+    \pcif \y \neq \finsp^\gid(\feval(\PUBUK[\uid],\CRED[\cid],\msg),
+    \PUBUK[\uid],\CRED[\cid],\msg)):
     \pcreturn 0 \\
@@
 \INSPECT)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace
-\GEN,\lbrace\II,\OO\rbrace,\CORR,\OBTAIN,\SIGN,\INSPECT,\CHALb)$
+\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN,\INSPECT,\CHALb)$
 
@@
       \parm \gets \Setup(1^\secpar) \\
-      (\gid,\sig,\msg) \gets \adv^{\Otrace}(\parm) \\
-      \pcif \Verify(\GK[\gid],\sig,\msg) = 0: \pcreturn 0 \\
-      \pcif \EvalForge(\gid,\sig,\msg) = 1 \land
-      \InspectForge(\gid,\sig,\msg) = 1: \\
+      (\gid,\sig,\msg,\feval) \gets \adv^{\Otrace}(\parm) \\
+      \pcif \Verify(\GK[\gid],\sig,\msg,\feval) = 0: \pcreturn 0 \\
+      \pcif \EvalInspectForge(\gid,\sig,\msg,\feval) = 1 \\%\land
+%      \InspectForge(\gid,\sig,\msg,\feval) = 1: \\
       \pcind \pcreturn 1 \\
@@
 
-    \procedure{$\EvalForge(\gid,\sig,\msg)$}{%
-      \pcif \exists \uid~\st~\Identify(\uid,\sig) = 1~\land \\
-      \pcind \pccomment{\uid does not own a \cred that satisfies \feval...} \\
-      \pcind (\nexists \cred \in \CRED[\uid]~\st~
-      \feval(\PUBUK[\uid],\cred,\msg) = 1 ~\lor \\
-      \hspace*{13pt} \pccomment{... or \uid does, but \cred was itself obtained
-        fraudulently} \\
-      \hspace*{13pt} (\exists \cred \in \CRED[\uid]~\st~
-      \feval(\PUBUK[\uid],\cred,\msg) = 1~\land \\
-      \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
-      \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
-        $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\
-      \pcind \pcreturn 1 \\
-      \pcelse \pcreturn 0 \\
-    }
+    % \procedure{$\EvalForge(\gid,\sig,\msg,\feval)$}{%
+    %   \pcif \exists \uid~\st~\Identify(\uid,\sig) = 1~\land \\
+    %   \pcind \pccomment{\uid does not own a \cred that satisfies \feval...} \\
+    %   \pcind (\nexists \cred \in \CRED[\uid]~\st~
+    %   \feval(\PUBUK[\uid],\cred,\msg) \neq 0 ~\lor \\
+    %   \hspace*{13pt} \pccomment{... or \uid does, but \cred was itself obtained
+    %     fraudulently} \\
+    %   \hspace*{13pt} (\exists \cred \in \CRED[\uid]~\st~
+    %   \feval(\PUBUK[\uid],\cred,\msg) \neq 0~\land \\
+    %   \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
+    %   \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
+    %     $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\
+    %   \pcind \pcreturn 1 \\
+    %   \pcelse \pcreturn 0 \\
+    % }
 
-    \procedure{$\InspectForge(\gid,\sig,\msg)$}{%
+    \procedure{$\EvalInspectForge(\gid,\sig,\msg,\feval)$}{%
       \pccomment{All \Obtain transcripts fail to inspect \sig} \\
@@
       \pcind \pcind \nexists \cred \in \CRED[\uid]~\st~
-      \y = \finsp(\PUBUK[\uid],\cred,\msg)~\lor \\
+      \y = \finsp(\feval(\PUBUK[\uid],\cred,\msg),
+      \PUBUK[\uid],\cred,\msg)~\lor \\
       \pcind \pcind \pccomment{... or \uid does, but \cred was itself obtained
@@
       \pcind \pcind (\exists \cred \in \CRED[\uid]~\st~
-      \feval(\PUBUK[\uid],\cred,\msg) = 1~\land \\
+      y = \finsp(\feval(\PUBUK[\uid],\cred,\msg),
+      \PUBUK[\uid],\cred,\msg)~\land \\
       \pcind \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
@@
     \parm \gets \Setup(1^\secpar) \\
-     (\gid,\sig,\msg,\y,\iproof) \gets \adv^{\Oframe}(\parm) \\
-     \pcreturn 1~\pcif \Verify(\GK[\gid],\sig,\msg) = 1 \land
+     (\gid,\sig,\msg,\feval,\y,\iproof) \gets \adv^{\Oframe}(\parm) \\
+     \pcreturn 1~\pcif \Verify(\GK[\gid],\sig,\msg,\feval) = 1 \land
      \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 1~\land \\
@@
      \pcind \exists \cred \in \CRED[\uid]~\st~
-     \finsp(\PUBUK[\uid],\cred,\msg) = \y \\
-     \pccomment{\todo{I don't think we can give any assurance about \feval here,
-         given that issuers are corrupt. But still, think about it.}} \\
+     \finsp(\feval(\PUBUK[\uid],\cred,\msg),\PUBUK[\uid],\cred,\msg) = \y \\
+%     \pccomment{\todo{I don't think we can give any assurance about \feval here,
+%         given that issuers are corrupt. But still, think about it.}} \\
      \pcreturn 0

### 2022-04-02 prism-backend/research/gsac/introduction.tex
Merged GSAC and UAS into uas.tex paper. Defining concrete instantiation of GSAC.

--- 2022-02-06 prism-backend/research/gsac/introduction.tex
@@
 
-In this work, we combine two closely related schemes -- group signatures (GS)
-and anonymous credentials (AC) -- which, for some reason, have followed a
-separate path up to now, beyond individual constructions from both fields
-drawing inspiration (and techniques) from one another. This combination is in
-some sense a natural evolution, which we do believe may have relevant impact in
-practical settings. On the one hand, anonymous credentials enable a richer
-functionality in regards to what one can prove about his own identity, in a
-privacy-preserving way. Academic proof of this is the fact that AC systems have
-naturally evolved to enabling arbitrary claims that only reveal the minimally
-possible 1-bit of information \needcite. Also, AC systems have been proposed to
-go even beyond what one can prove about his identity, covering also orthogonal
-functionality such as delegation \needcite, or aggregation of multiple
-credentials into one \needcite. Even outside academia, prominent
-technical workgroups \needcite, startups \needcite, and big techs \needcite are
-promoting and adopting solutions which are directly inspired by AC systems. On
-the other hand, GS 
-schemes have inspection functionality (e.g., opening and linking of signatures)
-at their core, which is reflected formally through non-frameability properties.
-This has originated a large body of research focusing on the construction and
-formalisation of variants of these notions \needcite. Consequently, group
-signatures tend to be proposed for scenarios that require some sort of
-de-anonymization \needcite. Indeed, this is not possible in ACs, which at most
-support revocation of issued credentials, which essentially can compare to
-linking, but not to opening-related notions.
+\commentwho{Jesus}{The following will most probably change completely if we
+  are to submit this for publication (it least, it probably needs some deep
+  reorganisation). However, this should capture tha main ideas.}
 
-Our goal is to get the best of both worlds: leverage the richer functionality
-of ACs in what respects to proving, in a privacy-preserving manner, useful
-claims on one's identity; and, at the same time support, through inspection
-capabilities, use cases that may require some sort of de-anonymiztion. We
-could target the ideal case of allowing to create proofs of arbitrary predicates
-on one's identity (as some AC systems do), as well as provide flexible or several
-notions of non-frameability. However, this being -- as far as we know -- the
-first work that explores this intersection, we opt for keeping things simple
-for the sake of facilitating technical precission and readability, and fostering
-discussion. Therefore, we focus on the case of selective attribute disclosure
-for ACs, and conventional opening for GSs, building a GSAC scheme that supports
-both.
+In this work, we focus on the generalization of privacy-preserving cryptographic
+systems for authentication and identification. Two major research lines within
+cryptography that work in this space are group signatures (GS) and anonymous
+credentials (AC). In fact, despite having followed separate paths, the overall
+approaches to build them are quite similar in a general sense. Consequently,
+both have fed from each other.
+%
+In short, GSs allow a group of users, accepted into the group by an issuer, to
+create signatures on behalf of the group, without revealing their identity. Only
+an opener/inspector can (sometimes partially) deanonymize these signatures. In
+ACs, users obtain credentials, typically containing multiple attributes, from
+trusted issuers. Subsequently, users can prove ownership of these credentials,
+usually revealing only subsets (or arbitrary claims) of these attritubes, while
+keeping the rest hidden.
+
+On the one hand, the security models of GS and AC hold important similarities.
+Security in group signatures is typically captured with game-based definitions,
+where the main properties are anonymity, traceability and non-frameability.
+Anonymity ensures privacy, essentially requiring that group signatures do not
+leak information about their signer. Traceability and non-frameability are
+unforgeability-related properties. Traceability requires that any valid group
+signature must have been created by a user who joined the group;
+non-frameability requires that no adversary can create a signature that somehow
+``blames'' an honest user. Of course, variations in the functionality of group
+signatures frequently require specialized properties, but these three are always
+the main ones. In anonymous credentials, security is also usually captured with
+game-based definitions (although UC models also exist). But, for anonymous
+credentials, the main properties (again, up to variations) are simply anonymity
+and unforgeability. Anonymity captures a similar privacy notion than group
+signatures. Unforgeability of anonymous credentials also maps more clearly to
+traceability in group signatures (non-frameability assumes a corrupt issuer,
+which must be honest in traceability and unforgeability), and requires that
+no adversary can succeed in proving ownership of a credential it does not own.
+In both cases -- anonymity and unforgeability in anonymous credentials -- the
+focus is on preventing leakage (anonymity) or forging (unforgeability) of the
+attributes in a credential. Since group signatures do not (usually) have
+attributes, this is a core difference in the modelling.
+
+The first thing that raises attention here is the fact that, despite following
+very similar approaches to build them, there is no equivalent property for
+non-frameability in anonymous credentials. The most probable reason is that
+anonymous credentials do not include the concept of ``opening'' which, in
+group signatures, allows to extract the identity of the signer and is essential
+to the non-frameability definition\footnote{Exceptions exist \cite{dl21}, but
+  the definition is much easier with opening.}. Something similar (more limited
+than opening, though) is sometimes considered by means of revocation of
+anonymous credentials -- revoking credentials is essentially equivalent to
+being able to link signatures by the same signer, which is considered in some
+variants of group signatures \needcite. However, while revocation may be enough
+if we aim to use credentials ``just'' for authentication, if we target more
+advanced use cases, we may need to learn something else from the credential (or
+its owner), beyond whether or not it has been revoked. Then, without an
+equivalent to non-frameability, we would not be able to make any security claim
+in the presence of dishonest issuers. On the other hand, it is
+also noteworthy that the literature of group signatures has barely explored
+the inclusion of attributes. With the exception of a few works on Attribute-Based
+Group Signatures (ABGS) \needcite, members of a group in group signatures just
+get a credential attesting for their membership to the group. Moreover, the
+existence of attributes in anonymous credentials would seem to have been
+instrumental in the surge of real-world use cases in the past few years. Indeed,
+initiatives such as W3C's Verifiable Credentials (VCs) \needcite, or large
+projects such as Idemix \needcite, which has in turn influenced VCs, are heavily
+based on concepts from the anonymous credential literature, even to the point
+that Idemix and its ``blockchain-based successor'', Indy \needcite, are now a
+type of verifiable credentials \needcite.
+
+Following the previous reasoning, we identify two aspects in which we can
+improve group signatures and anonymous credentials. The first is by coming up
+with some sort of primitive that combines both lines. That is, a scheme which
+supports both (a variant of) opening and non-frameability as well as
+attribute-based credentials. This seemingly natural evolution would thus
+enable rich use cases in which accountable (by means of opening) and expressive
+(by means of the attributes) authentication is necessary. While this is in
+line with the previously mentioned ABGS works, we argue that our approach
+is more general and flexible. Still, we anticipate that this may not be enough
+to reach a scheme that can adapt to the majority of situations that may arise in
+the real world. The reason is that the issuance and opening capabilities in the
+previous schemes are generally either too rigid or have lacked a formal analysis
+so far. For instance, in group signatures, the issuance protocol has barely been
+the focus of study. Essentially, this interactive protocol requires the
+prospective member to prove, in zero-knowledge, knowledge of a secret key
+that will be attested in the membership credential. On the other hand, multiple
+variants of the issuance protocol exist in anonymous credentials: protocols that
+assume that the issuer knows all the attributes to be included in the credential,
+protocols that allow blind issuance of attributes, protocols that let the user
+leverage attributes in previous credentials, protocols that include ad hoc
+rules at issuance time to enable extra functionality, such as delegation
+\todo{cross-check that all this, especially the latter, is correct; and add
+  cites}, etc. The problem is that a single change in this aspect, requires to
+completely rethink the model. Something similar happens with the inspection
+capabilities in group signatures. This frequently takes the shape of opening,
+but many variants also exist, message-depdendent opening, linking, or variants
+of linking, such as restricted linking only by other members of the group,
+user controlled linking, or sequential linking \needcite. Again, any small
+change in the inspection capabilities requires a full redesign of the model.
+This rigidness in inspection is specially crucial, as inspection is the key
+to the very nature of the privacy notion in group signatures. Taking this into
+account, it is understandable that many have tried to find some sort of
+equilibrium between full anonymity (no inspection at all), and full
+accountability (by means of conventional open). Thus, we aim at finding a
+generic way to support multiple variants of inspection, from the common model.
+Finally, actual evaluation of group signatures is the last component that is
+too rigid. Namely, in group signatures, when verifying a signature, either it
+has been rightly produced by a group member using his secret key and membership
+credential, or not. Luckily for us, anonymous credentials have done a great job
+in supporting high expressiveness into what a presentation can tell beyond just
+proving knowledge of a (group) key. Thus, by integreating anonymous credentials
+and group signatures in a sort of combined primitive, we get \emph{for free}
+the benefits of this high expressiveness that previous work on anonymous
+credentials have reached in regards to what one can prove given a credential.
 
@@
 %%% mode: latex
-%%% TeX-master: "sok-privsig"
+%%% TeX-master: "uas"
 %%% End:

### 2022-04-02 prism-backend/research/gsac/model-uas.tex
Merged GSAC and UAS into uas.tex paper. Defining concrete instantiation of GSAC.

@@
-\section{Model for \UAS Schemes}
-\label{sec:model-uas}
+\subsection{Model for \UAS Schemes}
+\label{ssec:model-uas}
 
@@
 
-\subsection{Syntax}
-\label{ssec:syntax}
+\subsubsection{Syntax}
+\label{sssec:syntax}
 
@@
 \item[$(\y,\iproof)/\bot \gets \Inspect(\gpk,\osk,\trans,\sig,\msg,\feval)$.] %
+  \todo{I think we do not need \trans here, see the generic construction. (This
+    was somehow inherited from \cite{bsz05}.) However, if we do remove it, we'd
+    need to redefine the traceability game -- it'd need to depend on \Identify,
+    which kind of makes sense too.}
   Executed by the inspector with private key \osk. Receives a signature \sig
@@
   attributes \attrs. \fissue may run checks on a (possibly empty) set of
-  additional credentials \scred, which may further be used for blind issuance
-  \commentwho{Jesus}{can it?}. \fissue returns $1$ to accept a request, $0$ to
-  reject it.  
-\item[$\feval: (\upk,\cred,\msg) \rightarrow \varrngfeval$.] Can be defined by any
-  party, although we anticipate that this will typically be done by either
+  additional credentials \scred, all bound to \upk, which may further be used
+  for blind issuance \commentwho{Jesus}{can it?}. \fissue returns $1$ to accept
+  a request, $0$ to reject it.  
+\item[$\feval: (\upk,\cred,\msg) \rightarrow \varrngfeval$.] Can be defined by
+  any party, although we anticipate that this will typically be done by either
   signers, verifiers, or some governance organization. It defines customized
   conditions to be met by the owner of a user key \upk and credential \cred,
-  in order to sign a concrete message \msg. Its outputs  $\varrngfeval$ must
-  belong in a well defined set \rngfeval, with the restriction that it must
-  return $0$ when the conditions for signing are not met.
+  bound to \upk, in order to sign a concrete message \msg. Its outputs
+  $\varrngfeval$ must belong in a well defined set \rngfeval, with the
+  restriction that it must return $0$ when the conditions for signing are not
+  met.
 \item[$\finsp: (\varrngfeval,\upk,\cred,\msg) \rightarrow \varrngfinsp$.]
@@
 
-\subsection{Security Properties}
-\label{ssec:security}
+\subsubsection{Security Properties}
+\label{sssec:security}
 
@@
 
-\subsection{Functionality ``Transformations'' and Special Cases}
-\label{ssec:transformations}
-
-\commentwho{Jesus}{This section is aimed at showing the ``universality'' of
-  our model. If I'm not mistaken, ideally, it should support the following
-  variations (except the transformation to interactive presentations,
-  probably).}
-
-\subsubsection{Transformation to Interactive Presentations}
-\label{sssec:interactivetransform}
-
-\todo{Is it possible to give it in some generic sense?}
-
-\subsubsection{Combining Multiple Credentials in One Presentation}
-
-\todo{I think this might be possible if we can use \fissue so that any user can
-  create arbitrary groups, where he is the issuer, an can thus run
-  \Obtain,\Issue protocols to combine credentials from other groups. This is
-  probably inefficient (or, at least, more than doing so wihtout having to
-  create ad hoc groups), but at least allows the enhanced functionality...}
-
-\subsubsection{Restricting to Conventional GS and AC Schemes}
-
-\todo{It would be nice to prove that a \GSAC scheme to which we remove the
-  \Open/\Judge functions becomes an AC scheme. And conversely, a \GSAC scheme
-  where all credentials have no attributes, and where we restrict to only
-  one credential per user, becomes a conventional GS scheme.}
-
-\subsubsection{Group Signatures with Message Dependent Opening}
-
-\todo{Describe what type of \finsp would be needed to achieve a functionality
-  similar to that of GS-MDO. Does this fit our model straight away? Maybe also
-  show how other types of GS could be ``mimicked'' (e.g., GS only with linking).
-  This would also be good to test if the model is as generic as I think it is}
-
-\subsubsection{Ring Signatures}
-
-\todo{Can we come up with a (\fissue,\feval,\finsp) tuple that allows us to
-  somehow mimic ring signatures (i.e., ``a group signature without issuer nor
-  opening''? Does the model support this?}
-
 %%% Local Variables:

### 2022-04-04 prism-backend/research/gsac/app-gsac.tex
Seemingly stable model anc concrete instantiation for GSAC.

--- 2022-02-06 prism-backend/research/gsac/model.tex
@@
-\section{Model for GSAC Systems}
-\label{sec:model}
+\section{GSAC Detailed Formalisation}
+\label{app:gsac-formal}
 
-While group signatures and anonymous credentials share quite common syntax and
-security properties, which are even frequently formalised in a similar way,
-there are aspects that need to be considered with care.
-
-The first choice that has to be made is whether to make sign/show and
-verification a non-interactive or an interactive process -- in group signatures,
-we are in the former case, whereas in anonymous credentials, we are in the
-latter. While both options are of course valid, this has direct impact in the
-modelling. We choose the non-interactive approach, and then prove how to
-generically translate it into an interactive process. The reason is that this
-results in a more flexible building block, suitable for a wider set of
-scenarios. And, syntactically, it seems more natural to combine two
-non-interactive processes into an interactive one, than the other way around.
-
-We also need to take into account that, in group signature schemes, users only
-get one membership credential -- typically bound to their personal secret
-key --, which they then use to create as many group signatures as they want. On
-the other hand, in anonymous credentials, users can get as many credentials as
-they desire, which can (typically) then be showed also arbitrarily many times.
-In this regard, we follow a somehow intermediate approach: users own a single
-personal secret key, which they can use to get as many credentials as they wish.
-Subsequently, they can use any of those credentials to create GSAC signatures.
-This has, as expected, some nuanced impact in the modelling. For instance, in
-group signatures, tracing and non-frameability are frequently dependent on the
-open function, which (among other things) returns an index pointing to the join
-transcript associated with the user who produced the signature given by the
-adversary as a response to the game's challenge. In our approach, though, each
-user may have many such transcripts -- one per credential that the user
-obtains. However, note that what actually provides meaning to these notions
-is not the index; but the associated user key pair, which is moreover necessary
-to prove that the opening has been performed honestly. Thus, with some
-restructuring of the corresponding games, we can still capture the main
-meaning of these traceability and non-frameability notions from group
-signatures. This also impacts anonymity, since in group signatures, this is
-modelled by challenging the adversary to guess which user (which implicitly
-translates to ``which user credential'') out of two challenge users was
-leveraged to produce the challenge signature. But again, in our case, users may
-have multiple credentials. However, it seems sufficient to adopt a similar
-anonymity flavour to that of anonymous credentials, where the adversary has to
-distinguish between presentations (signatures) produced from two arbitrary
-credentials, independently on whether these credentials were obtained by the
-same user, or not.
-
-Getting closer to the anonymity definition of anonymous credentials also has the
-side effect to introduce the notions of attributes for free into the domain of
-group signatures -- which, up to now, had considered membership credentials
-\emph{without} attributes. Yet another side effect of introducing multiple
-attributes (if we think from a group signature perspective) is that, in order
-to avoid trivial wins, the anonymity game has to enforce that both challenge
-credentials reveal the same predicate on their attributes.
-
-In the model described below, we follow closely the definitions from
-\cite{bsz05} for group signatures, and \cite{fhs19} for anonymous credentials
-(which are in turn influenced by \cite{bsz05}).
-
-\subsection{Syntax}
-\label{ssec:syntax}
-
-\begin{description}
-\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
-  returns a global system parameter variable \parm.
-\item[$(\ipk,\isk) \gets \IKeyGen(\parm)$.] Given global system parameters
-  \parm, returns the issuer's key pair. Hereafter, we assume that the public
-  part \ipk is added to the group public key \gpk.
-\item[$(\opk,\osk) \gets \OKeyGen(\parm)$.] Given global system parameters
-  \parm, returns an opener's key pair. Hereafter, we assume that the public part
-  \opk is added to the group public key \gpk.
-\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
-  \parm, returns a user's key pair.
-\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle \Obtain(\gpk,\usk,\Attrs),\Issue(\gpk,\isk,\upk,\Attrs) \rangle$.]
-  This interactive protocol lets a user with key pair (\upk,\usk) running the
-  \Obtain process, obtain a credential \cred with attributes \Attrs, by
-  communicating with an issuer, with private key \isk, running the \Issue
-  counterpart. The user outputs the produced credential \cred, while the issuer
-  outputs the protocol transcript \utrans for the produced credential.
-\item[$\sig \gets \Sign(\gpk,\usk,\cred,\Attrs,\DAttrs,\msg)$.] The user with
-  with secret key \usk, who obtained a credential \cred for attributes \Attrs,
-  produces a signature over message \msg, revealing subset \DAttrs of \Attrs.
-\item[$1/0 \gets \Verify(\gpk,\sig,\DAttrs,\msg)$.] Checks whether \sig is a
-  valid signature revealing the attribute set \DAttrs of its signing credential,
-  over message \msg.
-\item[$(\upk,\oproof) \gets \Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg)$.]
-  Given a signature \sig over message \msg, produced by a credential with
-  attributes containing the set \DAttrs, associated to transcript \utrans,
-  returns the user public key that was used to obtain the credential, and a
-  proof of opening correctness \oproof.  
-\item[$1/0 \gets \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg)$.] Checks if
-  \oproof is a valid opening correctness proof stating that the user with public
-  key \upk generated the signature \sig over message \msg, by using a credential
-  with attributes containing the set \DAttrs. 
-\end{description}
-
-The correctness and security properties are defined with the help of the
-following sets of oracles, and global variables that help oracles and games
-keep consistent state.
-
-\paragraph{Global Variables.} %
-All the honestly generated users (i.e., all honestly generated user key pairs,
-since we assume a one-to-one relationship between user and user key pair), as
-well as all honestly generated credentials, are assigned identifiers. That we
-typically write as \uid for users, and \cid for credentials. The adversary can
-refer to any individual user or credential using the corresponding identifier --
-even though he may not know the actual contents of the key pairs or credentials.
-In games that involve challenge user or credential identifiers, we use \cuid and
-\ccid to refer to these challenge user/credential.
-%
-The games, usually through the oracles, keep track of the users (through
-set \USK) and credentials (through table \CRED) that are created as a result of
-oracle calls by the adversary, as well as the attributes that each credential
-is associated (through table \ATTR), and the user to which each credential has
-been issued to (through table \OWNR). We use the user and credential identifiers
-to reference specific user key pairs, credentials, and credential attributes.
-For instance, $\USK[\uid]$ refers to the user key pair corresponding to user
-with identifier \uid, $\PUBUSK[\uid]$ refers to the public key of that key pair,
-and $\PRVUSK[\uid]$ to the private key; credential $\CRED[\cid]$ refers to the
-credential data associated to the credential with identifier \cid; $\ATTR[\cid]$
-is the set of attributes that was assigned to the credential with identifier
-\cid; and $\OWNR[\cid]$ is set to the \uid corresponding to the user that
-credential \cid was issued to.
-%
-Additionally, the games keep track of all honest and corrupt users that have
-been generated, through sets \HU and \CU, respectively. They also keep track of
-the signatures that have been honestly produced, through the \SIG table. Since
-signatures are produced through credentials, the \SIG table is indexed with
-{\cid}s.
-%
-All global variables are initially set by the games to undefined values (denoted
-with $\bot$, and all tables/sets are initialized as empty tables/sets, denoted
-with $\empty$. Also, for readability, we abuse the syntax as follows: we write
-$\CRED[\uid]$ to mean $\CRED[\cid]$ for all $\cid$ such that
-$\OWNR[\cid] = \uid$; \todo{Something else?}
-
-\paragraph{Oracles.} %
-Oracles are the interface of the adversary with the corresponding games. In
-other words: through these oracles, the game enviroment exposes to the adversary
-functionality that could otherwise be executed only by honest parties with
-private knowledge -- knowledge that would make the adversary capable of
-trivially breaking the security properties formalized in the experiments.
-In the game-based definitions of our GSAC model, we leverage the following
-oracles, which are formally defined in \figref{fig:oracles}
-
-\begin{description}
-\item[$\HUGEN$.] Adds a new honest user to the game, by honestly generating
-  the user's key pair.
-\item[$\CUGEN$.] If the specified user identifier is not already in the game,
-  sets the user public key to a value given by the adversary. If it already
-  exists, and is associated to an honest user, then it reveals to the adversary
-  the user's secret key.
-\item[$\OBTISS$.] Lets the adversary add a new honestly generated credential to
-  the game, on behalf of an honest user.
-\item[$\OBTAIN$.] Enables the adversary to play the role of a dishonest issuer
-  in games that support it, by letting it interact with honest users who want to
-  receive credentials.
-\item[$\ISSUE$.] Allows the adversary to play the role of dishonest users,
-  requesting an honest issuer to produce credentials fo them.
-\item[$\SIGN$.] Lets the adversary get signatures from credentials belonging
-  to honest users.
-\item[$\OPEN$.] Given an honestly produced signature, lets the adversary learn
-  which credential was used to produce it.
-\item[$\CHALb$.] Upon receiving two challenge credentials, a common intersecting
-  set of attributes, and a message, returns a signature produced by one of these
-  two credentials, defined by the bit $b$, which is established in the anonymity
-  game.
-\end{description}
+\subsection{Detailed Oracles}
+\label{sapp:gsac-oracles}
 
 {%\setlength\intextsep{\sep}
-  \begin{figure*}[htp!]
+  \begin{figure*}[ht!]
     \centering
@@
 
+        \procedure{$\RREG(i)$}{%
+          \pcreturn \trans[i] \\
+        }
+
         \procedure{$\HUGEN(\uid)$}{%
@@
           \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
-          \pcind \pcreturn (\USK[\uid],\CRED[\uid]) \\
-          \pcelse: \USK[\uid] = (\upk,\bot) \\          
+          \pcind \pcreturn (\UK[\uid],\CRED[\uid]) \\
+          \pcelse: \UK[\uid] = (\upk,\bot) \\          
           \pcreturn \top \\
@@
           \langle \cred, \utrans \rangle \gets
-          \langle \Obtain(\gpk,\PRVUSK[\uid],\Attrs), \\
+          \langle \Obtain(\gpk,\PRVUK[\uid],\Attrs), \\
           \pcind \pcind \pcind \pcind \pcind \pcind
-          \Issue(\gpk,\isk,\PUBUSK[\uid],\Attrs) \rangle \\
+          \Issue(\gpk,\isk,\Attrs) \rangle \\
           \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
@@
           \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\gpk,\PRVUSK[\uid],\Attrs),\Adv \rangle \\
+          \langle \Obtain(\gpk,\PRVUK[\uid],\Attrs),\adv \rangle \\
           \CRED[\cid] \gets \cred \\
@@
 
+        \procedure{$\WREG(i,\rho)$}{%
+          \trans[i] \gets \rho \\
+        }
+
         \procedure{$\ISSUE(\uid,\cid,\Attrs)$}{%
@@
           \langle \cdot, \utrans \rangle \gets
-          \langle \Adv, \Issue(\gpk,\isk,\PUBUSK[\uid],\Attrs) \rangle \\
+          \langle \adv, \Issue(\gpk,\isk,\Attrs) \rangle \\
           \trans[\cid] \gets \utrans \\
@@
           \cred \gets \CRED[\cid] \\
-          \sig \gets \Sign(\gpk,\PRVUSK[\uid],\cred,\ATTR[\cid],\DAttrs,\msg) \\
+          \sig \gets \Sign(\gpk,\PRVUK[\uid],\cred,\DAttrs,\msg) \\
           \SIG[\cid] \gets \SIG[\cid] \cup \lbrace (\sig,\DAttrs,\msg) \rbrace \\
@@
           \textrm{Let}~\cid~\textrm{be s.t.}~(\sig,\DAttrs,\msg) \in \SIG[\cid] \\
-          \pcif \textrm{no such \cid exists, or there is more than one}:
-          \pcreturn \bot \\
-          \pcif \trans[\cid] = \bot: \pcreturn \bot \\
-          (\upk,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
-          \pcreturn (\upk,\oproof) \\
+          \pcif \textrm{no such \cid exists, or there is more than one}: \\
+          \pcind \pcreturn \bot \\
+          \pcif \sig \in \CSIG: \pcreturn \bot \\
+          (\upk,\Attrs,\oproof) \gets
+          \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
+%          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
+%          \CCRED \gets \CCRED \cup \lbrace \cid \rbrace \\
+          \pcreturn (\upk,\Attrs,\oproof) \\
         }
@@
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
-          \csig \gets \Sign(\gpk,\USK[\cuid_b],\CRED[\ccid_b],
-          \ATTR[\ccid_b],\DAttrs,\msg) \\
+ %         \pcif \ccid_0 \in \CCRED \lor \ccid_1 \in \CCRED: \pcreturn \bot \\
+          \csig \gets \Sign(\gpk,\PRVUK[\cuid_b],\CRED[\ccid_b],
+          \DAttrs,\msg) \\
+          \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
           \pcreturn \csig
@@
 
-    \caption{Detailed oracles available in our model.}
+    \caption{Detailed oracles available in our model for \GSAC schemes.}
     \label{fig:oracles}
@@
 
-\paragraph{Correctness.} %
-Correctness of GSAC schemes is formalized through the experiment in
-\figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
-revealing attributes \DAttrs, which was honestly produced though a credential
-that was obtained by an honest user interacting with an honest issuer, with a
-set of attributes \Attrs such that $\DAttrs \subseteq \Attrs$, must be accepted
-by \Verify. Moreover, an honestly produced correctness proof of opening for such
-signature, revealing the public key pair of the user, must also be accepted by
-\Judge.
-
-\begin{figure}[htp!]
-  \procedure{$\ExpCorrect(1^\secpar)$}{%
-     \parm \gets \Setup(1^\secpar) \\
-     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
-     \gpk \gets (\ipk,\opk) \\
-    (\cid,\Attrs,\DAttrs,\msg) \gets \adv^{\HUGEN,\OBTISS}(\gpk) \\
-    \pcif \DAttrs \nsubseteq \Attrs \lor \Attrs \nsubseteq \ATTR[\cid] :
-    \pcreturn \bot \\
-    \sig \gets \Sign(\gpk,\USK[\OWNR[\cid]],\CRED[\cid],\Attrs,\DAttrs,\msg) \\
-    (\upk,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
-    \pcif \Verify(\gpk, \sig, \DAttrs,\msg) = 0 \lor
-    \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0:
-    \pcreturn 1 \\
-    \pcreturn 0
-  }
-  \caption{Correctness experiment for GSAC schemes.}
-  \label{fig:exp-gsac-corr}
-  \end{figure}
-
-\subsection{Security Properties}
-\label{ssec:security}
-
-\subsection{Tranformation to Interactive Presentations}
-\label{ssec:interactivetransform}
+\subsection{Detailed Proofs}
+\label{sapp:gsac-proofs}
 

### 2022-04-04 prism-backend/research/gsac/construction-uas.tex
Seemingly stable model anc concrete instantiation for GSAC.

\section{A Generic \UAS Construction}
\label{sec:gen-construction}

In this section, we give a generic construction of an \UAS scheme, based on
generic building blocks. In \secref{sec:instantiation}, we give a concrete
instantiation.

\subsection{Building Blocks}
\label{ssec:bblocks}

\subsubsection{Commitments}

\todo{Introduce, and summarise correctness and security.}

\begin{description}
  \item[$\Cparm \gets \CSetup(\Csecpar).$]
  \item[$(\Ccom,\Copn) \gets \CCommit(\Cparm,\msg).$] 
  \item[$\Cproof \gets \CProve(\Ccom,\Copn,\msg).$]    
  \item[$1/0 \gets \CVerify(\Cproof,\Ccom).$] 
\end{description}

\subsubsection{Signatures with Proofs of Knowledge}

As put forward in \cite{cl02}, a generic way to build anonymous credentials
requires a digital signature scheme with efficient protocols for proving
knowledge of a digital signature, and signing committed values. This approach
also has much in common with the Sign-Randomize-Prove (SRP) approach to build
group signatures \needcite. Thus, even a priori, it seems a good core component
to build something that is actually in betwween GS and AC. In the sequel, we use
\RS to refer to schemes of this type, which must provide the functionality
specified by the following syntax:

\begin{description}
\item[$(\RSvk,\RSsk) \gets \RSKeyGen(\RSsecpar,\RSlen)$.] Generates a key pair,
  consisting on the signig key \RSsk and the verification key \RSvk, which
  support sigining blocks of up to \RSlen messages.
\item[$\RSsig \gets \RSSign(\RSsk,\msgset,\cmsgset)$.] Given signing key \RSsk,
  a set of messages \msgset, and a set of commitments to messages, where
  $|\msgset + \cmsgset| \le \RSlen$, returns a signature \RSsig.
\item[$1/0 \gets \RSVerify(\RSvk,\RSsig,\amsgset)$.] Given a verification key
  \RSvk, a signature \RSsig, supposedly over set of messages \amsgset which may
  contain commitments to messages, returns $1$ or $0$. \todo{Assume that, within
    \amsgset, it is possible to know which are commitments and wich plain
    messages?}
\item[$\RSproof/\bot \gets \RSProve(\RSsig,\amsgset,\D)$.] Given signature
  \RSsig, over set of messages (and commitments to messages) \amsgset, out of
  which those indexed by set \D are to be revealed, creates a proof of knowledge
  \RSproof of \RSsig.
\item[$1/0 \gets \RSProveVer(\RSproof,\msgset)$.] Given a proof of knowledge of
  a signature over a set of messages, which includes \msgset, returns $1$ or
  $0$.
\end{description}

\todo{Summarise correctness and security.}

\subsubsection{Digital Signatures}

\todo{Introduce, and summarise correctness and security.}

\begin{description}
\item[$(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$.]
\item[$\Ssig \gets \SSign(\Ssk,\msg)$.]
\item[$1/0 \gets \SVerify(\Svk,\Ssig,\msg)$.]  
\end{description}

\subsubsection{Encryption}

\todo{Introduce, and summarise correctness and security.}

\begin{description}
\item[$(\Eek,\Edk) \gets \EKeyGen(\Esecpar)$.]
\item[$\Ec \gets \EEnc(\Eek,\msg)$.]
\item[$\msg \gets \EDec(\Edk,\Ec)$.]
\end{description}

\subsubsection{Non-Interactive ZK Proofs of Knowledge}

\todo{Introduce, and summarise correctness and security.}

\begin{description}
\item[$\NIZKcrs\gets \NIZKSetup(\NIZKsecpar)$.]
\item[$\NIZKproof \gets \NIZKProve(\NIZKcrs,\NIZKx,\NIZKw)$.]
\item[$1/0 \gets \NIZKVerify(\NIZKcrs,\NIZKproof,\NIZKx)$.]
\end{description}

We use $\NIZK^\Lang$ to denote a \NIZK which is used to prove statements on a
given NP language \Lang.

\subsubsection{Signature Proofs of Knowledge}

\todo{Introduce, and summarise correctness and security.}

\begin{description}
\item[$\SPKproof \gets \SPKProve(\SPKmsg,\SPKx,\SPKw)$.]
\item[$1/0 \gets \SPKVerify(\SPKproof,\SPKmsg,\NIZKx)$.]
\end{description}

We use $\SPK^\Lang$ to denote an \SPK which is used to prove statements on a
given NP language \Lang.

\subsection{Generic Construction \CUASGen}

\todo{Many variables need renaming here.}

\paragraph{$\parm \gets \Setup(\secpar)$.} %
\begin{itemize}
  \item Parse \secpar as $(\Csecpar,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
  \item $\Cparm \gets \CSetup(\Csecpar)$
  \item $\NIZKparm \gets \NIZKSetup(\NIZKsecpar)$
  \item Return $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
\end{itemize}

\paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
\begin{itemize}
\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
\item $(\RSvk,\RSsk) \gets \RSKeyGen(\RSsecpar)$  
\item $\sig_{\fissue} \gets \RSSign(\RSsk,\fissue,\bot)$
\item $\ipk \gets (\RSvk,\fissue,\sig_{\fissue})$
\item $\isk \gets \RSsk$
\item Return $(\ipk,\isk)$
\end{itemize}

\paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
\begin{itemize}
\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
\item $(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$
\item $(\Eek,\Edk) \gets \EKeyGen(\Esecpar)$
\item $\sig_{\finsp} \gets \SSign(\Ssk,\finsp)$
\item $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$
\item $\osk \gets (\Ssk,\Edk)$
\item Return $(\opk,\osk)$
\end{itemize}

\paragraph{$(\upk,\usk) \gets \UKeyGen(\parm)$.} %
\begin{itemize}
\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
\item $(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$
\item Return $(\Svk,\Ssk)$
\end{itemize}

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\attrs,\ldblbrace (gpk_i,\cred_i)\rdblbrace_{i \in \Issuers}),
  \Issue(\isk,\upk,\attrs,\ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})
  \rangle$.} %
We define the NP language $\LangIss = \lbrace (\usk,
\ldblbrace \cred_i \rdblbrace_{i \in \Issuers}): \fissue(\usk,\attrs,\ldblbrace
(\gpk_i,\cred_i) \rdblbrace_{i \in \Issuers}) = 1 \land \Ccom = \CCommit(\usk)
\rbrace$ \todo{\fissue needs to ensure that all {\cred}s are linked to \usk. How
  to capture this?} The interactive protocol from a user to obtain a credential
from an issuer of the system is as follows:

\begin{itemize}
\item Issuer: $\ch \gets \bin^*$; Send \ch to User.
\item User:
  \begin{itemize}    
  \item $\Ccom_{\usk} \gets \CCommit(\usk)$
  % \item $\SPKproof^{\Lang} \gets
  %   \SPK \lbrace (\usk): \Ccom_{\usk} = \CCommit(\Cparm,\usk) \rbrace (\ch)$
  \item $\SPKproof^{\LangIss} \gets \SPKProve^{\LangIss}
    (\ch,(\attrs,\Ccom_{\usk}, \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers}),
    (\usk,\ldblbrace \cred_i \rdblbrace_{i \in \Issuers}))$
  \item Send $(\attrs,\Ccom_{\usk},\SPKproof^{\LangIss})$ to Issuer
  \end{itemize}
\item Issuer:
  \begin{itemize}
%  \item $1 \stackrel{?}{=} \SPKVerify(\SPKproof^{\Lang},\Ccom_{\upk})$
  \item $1 \stackrel{?}{=} \SPKVerify(\SPKproof^{\LangIss},\ch,
    (\attrs,\Ccom_{\usk}, \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers}))$
  \item $\cred \gets \RSSign(\isk,\attrs,\Ccom_{\usk})$
  \item $\utrans \gets (\Ccom_{\usk},\cred,\attrs)$
  \item Send \cred to User and output \utrans.
  \end{itemize}
\item User:
  \begin{itemize}
  \item $1 \stackrel{?}{=} \RSVerify(\RSvk,\cred,(\attrs,\Ccom_{\usk}))$
  \item Output \cred
  \end{itemize}   
\end{itemize}

\paragraph{$\sig \gets \Sign(\gpk,\usk,\cred,\msg,\feval)$.} %
We define the NP language $\LangSig = \lbrace (\upk,\cred,\y):
\SVerify(\sig,\upk) = 1~\land~\Ec = \EEnc(\Eek,\y)~\land~
\y = \finsp(\feval(\upk,\cred,\msg),\upk,\cred,\msg)\rbrace$. The
signing algorithm is defined as follows:
\todo{Argue that the composition of \finsp and \feval is not redundant even
  though both depend on the same arguments. Namely, because \feval is defined
  on a per-signature basis (akin to the policies of ACs), and \finsp is defined
  once per group (akin to the open function in GSs). Hence, \finsp cannot just
  be defined to ``contain'' \feval at setup time.}

\begin{itemize}
\item Parse \gpk as $(\ipk,\opk)$
\item Parse \ipk as $(\RSvk,\fissue,\sig_{\fissue})$; Verify $\sig_{\fissue}$
\item Parse \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$; Verify $\sig_{\finsp}$
\item $\sig' \gets \SSign(\usk,\msg)$
%\item $b \gets \feval(\upk,\cred,\msg)$
\item % If $b=0$: 
  $\y \gets \finsp(\feval(\upk,\cred,\msg),
  \upk,\cred,\msg)$%; else $\y = \bot$.
\item $\Ec \gets \EEnc(\Eek,\y)$
\item $\SPKproof^{\LangSig} \gets \SPKProve^{\LangSig}(\msg,(\Ec,\sig'),
  (\upk,\cred,\y))$
\item Return $(\Ec,\sig',\SPKproof^{\LangSig})$
\end{itemize}

\paragraph{$1/0 \gets \Verify(\gpk,\sig,\msg,\feval)$.} %
\begin{itemize}
\item Parse \sig as $(\Ec,\sig',\SPKproof^{\LangSig})$
\item Return $\SPKVerify^{\LangSig}(\SPKproof^{\LangSig},\msg,(\Ec,\sig'))$ 
\end{itemize}

\paragraph{$(\y,\iproof)/\bot \gets \Inspect(\gpk,\osk,\trans,\sig,\msg,\feval)$.} %

We follow the approach of \cite{bsz05} for verifiable openings. Namely, we
define an NP language $\LangVerIns = \lbrace (\Eek,\Edk,r):
(\Eek,\Edk) = \EKeyGen(\Esecpar;r) \land \y = \EDec(\Edk,\c) \rbrace$.

\begin{itemize}
\item Parse \osk as $(\Ssk,\Edk)$; \gpk as
  $(\cdot,(\Svk,\Eek,\finsp,\sig_{\finsp}))$
\item  $1 \stackrel{?}{=} \Verify(\gpk,\sig,\msg,\feval)$  
\item $\y \gets \EDec(\Edk,\c)$
\item $\NIZKproof^{\LangVerIns} \gets \NIZKProve(\NIZKcrs,(\c,\y),(\Eek,\Edk,r))$
\item Return $\NIZKproof^{\LangVerIns}$
\end{itemize}

\paragraph{$1/0 \gets \Judge(\gpk,\y,\iproof,\sig,\msg)$.} %

\begin{itemize}
\item  $1 \stackrel{?}{=} \Verify(\gpk,\sig,\msg,\feval)$
\item Parse \sig as $(\c,\cdot,\cdot)$  
\item Return $\NIZKVerify(\NIZKcrs,\iproof,(\c,\y))$
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:

### 2022-04-04 prism-backend/research/gsac/introduction.tex
Seemingly stable model anc concrete instantiation for GSAC.

@@
 
-In this work, we focus on the generalization of privacy-preserving cryptographic
-systems for authentication and identification. Two major research lines within
-cryptography that work in this space are group signatures (GS) and anonymous
-credentials (AC). In fact, despite having followed separate paths, the overall
-approaches to build them are quite similar in a general sense. Consequently,
-both have fed from each other.
+Two major research lines within cryptography that work in the space of
+privacy-preserving authentication and identfication are group
+signatures (GS) and anonymous credentials (AC). In fact, despite having followed
+separate paths, the overall approaches to build them are quite similar in a
+general sense.
 %
@@
 create signatures on behalf of the group, without revealing their identity. Only
-an opener/inspector can (sometimes partially) deanonymize these signatures. In
-ACs, users obtain credentials, typically containing multiple attributes, from
-trusted issuers. Subsequently, users can prove ownership of these credentials,
-usually revealing only subsets (or arbitrary claims) of these attritubes, while
-keeping the rest hidden.
+an opener can (sometimes partially) deanonymize these signatures. In ACs, users
+obtain credentials, typically containing multiple attributes, from trusted
+issuers. Subsequently, users can prove ownership of these credentials, usually
+revealing only subsets (or arbitrary claims) of these attritubes, while keeping
+the rest hidden. Both GSs and ACs are used for authentication.
+
+\paragraph{Accountability in GSs and identification in ACs.} %
+\todo{Take inspiration from the SoK paper on accountability to argue that
+  accountability is needed to prevent misbehaviour and support utility in
+  a privacy-preserving manner.}
+Typically, GSs make special focus in accountability (via opening), while ACs
+place more attention in dealing with identifying information of the credential
+owners.
+%
+Indeed, the opening functionality has been a core component of GSs. Even for
+GS variants that do not have opening, there is always some mechanism that
+allows to somehow ``correlate'' a signature with its signer -- even when this is
+controlled by the signers themselves, as in \cite{dl21} \needcite. Still, even
+when group signatures can be opened in the conventional sense, the notion of
+\emph{identity} that is obtained from this deanonymization is too lax. Most
+frequently, opening just returns an integer (e.g., $i$), which can
+be associated to a user who joined the system (the $i$-th). Who this ($i$-th)
+user is, or what identifies him/her, is left as out of scope.
+%
+On the other hand, the capability to encode authenticated identifying
+information via attributes within a credential, and then prove claims about
+those attributes without revealing more than strictly needed, is probably the
+most attractive feature of ACs. Through these attributes (and claims over
+them), ACs actually allow building systems where the participating entities
+know \emph{who} they are interacting with. However, if a credential owner
+misbehaves, typically not much can be done beyond (in some schemes) blacklisting
+the credential. Even when we do not want to somehow penalize a credential owner,
+but rather be able to apply some utility (alas, partially deanonymizing)
+function \emph{after the authentication has taken place}, not having some sort
+of ``accountability'' mechanism (like GSs' open) in ACs makes it impossible.
+
+It is reasonable that accountability and identification have followed separate
+paths. After all, they are challenging features on their own. Even more, when
+combined with privacy, as is the case for GSs and ACs. However, real world use
+cases claim for both \emph{at the same time} and \emph{in a flexible manner}.
+
+\subsection{Our Contributions}
+\label{ssec:contributions}
+
+In this work, we focus on the generalization of privacy-preserving cryptographic
+systems for authentication and identification. Our approach towards this
+generalization comes in two steps: first,
 

### 2022-04-04 prism-backend/research/gsac/model-gsac.tex
Seemingly stable model anc concrete instantiation for GSAC.

--- 2022-02-09 prism-backend/research/gsac/model.tex
@@
-\section{Model for \GSAC Schemes}
-\label{sec:model}
-
-\todo{Big doubt in this model. Currently, \Open (and \OPEN) return the public
-  key and credential of the signer along with the correctness proof. This is
-  as opposed to conventional practice, in which just an index and the proof
-  are returned. It is also intentional, as in the future I'd
-  like to extend \Open to a sort of functional version, where instead we return
-  a function of the user (secret or public) key, the credential, and the
-  signed message. However, I am not sure yet if this will be too strong to be
-  realized. If it is possible, though, our model would be stronger in this
-  sense. And also, I like this better, as by outputing an index, but then
-  requiring \Judge to use the public key (as in \cite{bsz05}) you impose the
-  need to create ad hoc protocols so that the \Judge learns the actual public
-  key, which in the real world can lead to very bad practices... (Such as
-  integrating the Judge inside the Opener, and not making the correctness
-  proof public -- hence, full trust in the Opener+Judge; or implementations
-  of \Open that directly output the public key instead of the index for
-  convenience, but in that case, deviating from the model and thus without
-  security guarantees.)}
+\subsection{Model for \GSAC}
+\label{ssec:model-gsac}
 
@@
 \item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle \Obtain(\gpk,\usk,\Attrs),\Issue(\gpk,\isk,\upk,\Attrs) \rangle$.]
+  \langle \Obtain(\gpk,\usk,\Attrs),\Issue(\gpk,\isk,\Attrs) \rangle$.]
   This interactive protocol lets a user with key pair (\upk,\usk) running the
@@
   over message \msg.
-\item[$(\upk,\cred,\oproof)/\bot \gets
-  \Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg)$.]
+\item[$(\upk,\Attrs,\oproof)/\bot \gets
+  \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg)$.]
   Given a signature \sig over message \msg, produced by a credential with
-  attributes containing the set \DAttrs, associated to transcript \utrans,
-  returns the user public key that was used to obtain the credential used for
-  producing \sig, the credential, and a proof of opening correctness \oproof; or
-  $\bot$ if the opening process fails.  
-\item[$1/0 \gets \Judge(\gpk,\upk,\cred,\oproof,\sig,\DAttrs,\msg)$.] Checks if
-  \oproof is a valid opening correctness proof stating that the user with public
-  key \upk generated the signature \sig over message \msg, by using credential
-  \cred with attributes containing the set \DAttrs. 
+  attributes containing the set \DAttrs owned by a user with key \upk, returns
+  the attribute set \Attrs encoded in the credential used to create the
+  signature, and a proof of opening correctness \oproof; or $\bot$ if the
+  opening process fails.
+\item[$1/0 \gets \Judge(\gpk,\upk,\Attrs,\oproof,\sig,\DAttrs,
+  \msg)$.] Checks if \oproof is a valid opening correctness proof stating that
+  the user with key \upk and attributes \Attrs generated signature \sig over
+  message \msg, revealing attributes $\DAttrs \subseteq \Attrs$. 
 \end{description}
@@
 
-\paragraph{Global Variables.} %
+\paragraph{Global variables.} %
 All the honestly generated users (i.e., all honestly generated user key pairs,
@@
 write $\CRED[\uid]$ to mean $\CRED[\cid]$ for all $\cid$ such that
-$\OWNR[\cid] = \uid$; \todo{Something else?}
+$\OWNR[\cid] = \uid$; we also sometimes use \upk as a ``synonym'' of \uid, as it
+is possible to do a reverse lookup from the \UK table (i.e., $\CRED[\upk]$ can
+be replaced by $\CRED[\uid]~\st~\UK[\uid]=(\upk,\cdot)$); \todo{Something else?}
 
@@
 In the game-based definitions of our \GSAC model, we leverage the following
-oracles, which are formally defined in \figref{fig:oracles}
+oracles, which are formally defined in \appref{app:gsac-formal}.
 
 \begin{description}
-\item[$\HUGEN$.] Adds a new honest user to the game, by honestly generating
+\item[\RREG.] Reads the given transcript table entry.
+\item[\WREG.] Sets a transcript table entry to the given value.
+\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
   the user's key pair.
-\item[$\CUGEN$.] If the specified user identifier is not already in the game,
+\item[\CUGEN.] If the specified user identifier is not already in the game,
   sets the user public key to a value given by the adversary. If it already
@@
   the user's secret key.
-\item[$\OBTISS$.] Lets the adversary add a new honestly generated credential to
+\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
   the game, on behalf of an honest user.
-\item[$\OBTAIN$.] Enables the adversary to play the role of a dishonest issuer
+\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
   in games that support it, by letting it interact with honest users who want to
   receive credentials.
-\item[$\ISSUE$.] Allows the adversary to play the role of dishonest users,
+\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
   requesting an honest issuer to produce credentials fo them.
-\item[$\SIGN$.] Lets the adversary get signatures from credentials belonging
+\item[\SIGN.] Lets the adversary get signatures from credentials belonging
   to honest users.
-\item[$\OPEN$.] Given an honestly produced signature, lets the adversary learn
+\item[\OPEN.] Given an honestly produced signature, lets the adversary learn
   which credential was used to produce it.
-\item[$\CHALb$.] Upon receiving two challenge credentials, a common intersecting
+\item[\CHALb.] Upon receiving two challenge credentials, a common intersecting
   set of attributes, and a message, returns a signature produced by one of these
@@
 \end{description}
-
-{%\setlength\intextsep{\sep}
-  \begin{figure*}[htp!]
-    \centering
-    \scalebox{0.9}{
-
-      \begin{minipage}[t]{0.55\textwidth}
-
-        \procedure{$\HUGEN(\uid)$}{%
-          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
-          (\upk,\usk) \gets \UKeyGen(\parm) \\
-          \USK[\uid] \gets (\upk,\usk);
-          \HU \gets \HU \cup \lbrace  \uid \rbrace \\
-          \pcreturn \top \\
-        }
-
-        \procedure{$\CUGEN(\uid,\upk)$}{%
-          \pcif \uid \in \CU: \pcreturn \bot \\
-          \CU \gets \CU \cup \lbrace \uid \rbrace \\          
-          \pcif \uid \in \HU: \\
-          \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
-          \pcind \pcreturn (\USK[\uid],\CRED[\uid]) \\
-          \pcelse: \USK[\uid] = (\upk,\bot) \\          
-          \pcreturn \top \\
-        }
-
-        \procedure{$\OBTISS(\uid,\cid,\Attrs)$}{%
-          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
-          \langle \cred, \utrans \rangle \gets
-          \langle \Obtain(\gpk,\PRVUSK[\uid],\Attrs), \\
-          \pcind \pcind \pcind \pcind \pcind \pcind
-          \Issue(\gpk,\isk,\PUBUSK[\uid],\Attrs) \rangle \\
-          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
-          \pcreturn \top \\
-        }
-
-        \procedure{$\OBTAIN(\uid,\cid,\Attrs)$}{%
-          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
-          \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\gpk,\PRVUSK[\uid],\Attrs),\adv \rangle \\
-          \CRED[\cid] \gets \cred \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
-          \pcreturn \top \\
-        }
-
-      \end{minipage}
-    }
-    \scalebox{0.9}{
-
-      \begin{minipage}[t]{.5\textwidth}
-
-        \procedure{$\ISSUE(\uid,\cid,\Attrs)$}{%
-          \pcif \uid \notin \CU: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
-          \langle \cdot, \utrans \rangle \gets
-          \langle \adv, \Issue(\gpk,\isk,\PUBUSK[\uid],\Attrs) \rangle \\
-          \trans[\cid] \gets \utrans \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
-          \pcreturn \top \\          
-        }
-
-        \procedure{$\SIGN(\cid,\DAttrs,\msg)$}{%
-          \uid \gets \OWNR[\cid] \\
-          \pcif \uid \notin \HU: \pcreturn \bot \\
-          \cred \gets \CRED[\cid] \\
-          \sig \gets \Sign(\gpk,\PRVUSK[\uid],\cred,\DAttrs,\msg) \\
-          \SIG[\cid] \gets \SIG[\cid] \cup \lbrace (\sig,\DAttrs,\msg) \rbrace \\
-          \pcreturn \sig \\
-        }
-
-        \procedure{$\OPEN(\sig)$}{%
-          \textrm{Let}~\cid~\textrm{be s.t.}~(\sig,\DAttrs,\msg) \in \SIG[\cid] \\
-          \pcif \textrm{no such \cid exists, or there is more than one}: \\
-          \pcind \pcreturn \bot \\
-          \pcif \sig \in \CSIG: \pcreturn \bot \\
-          (\upk,\cred,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
-%          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
-%          \CCRED \gets \CCRED \cup \lbrace \cid \rbrace \\
-          \pcreturn (\upk,\cred,\oproof) \\
-        }
-
-        \procedure{$\CHALb(\ccid_0,\ccid_1,\DAttrs,\msg)$}{%
-          \pcif \ATTR[\ccid_0] \cap \ATTR[\ccid_1] \nsubseteq \DAttrs:
-          \pcreturn \bot \\
-          \pcif \cuid_0 \neq \bot \lor \cuid_1 \neq \bot: \pcreturn \bot \\
-          \cuid_0 = \OWNR[\ccid_0];~\cuid_1 = \OWNR[\ccid_1] \\
-          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
- %         \pcif \ccid_0 \in \CCRED \lor \ccid_1 \in \CCRED: \pcreturn \bot \\
-          \csig \gets \Sign(\gpk,\PRVUSK[\cuid_b],\CRED[\ccid_b],
-          \DAttrs,\msg) \\
-          \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
-          \pcreturn \csig
-        }
-
-      \end{minipage}
-
-    }
-
-    \caption{Detailed oracles available in our model.}
-    \label{fig:oracles}
-  \end{figure*}
-}
 
@@
 \begin{figure}[htp!]
-  \procedure{$\ExpCorrect(1^\secpar)$}{%
+  \procedure{$\ExpGSACCorrect(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
@@
      \gpk \gets (\ipk,\opk) \\
-    (\cid,\DAttrs,\msg) \gets \adv^{\HUGEN,\OBTISS}(\gpk) \\
+    (\cid,\DAttrs,\msg) \gets \adv^{\HUGEN,\OBTISS,\RREG}(\gpk) \\
     \pcif \DAttrs \nsubseteq \ATTR[\cid] :
     \pcreturn \bot \\
-    \sig \gets \Sign(\gpk,\PRVUSK[\OWNR[\cid]],\CRED[\cid],\DAttrs,\msg) \\
-    (\upk,\oproof) \gets \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
+    \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\DAttrs,\msg) \\
+    (\upk,\Attrs,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) \\
     \pcif \Verify(\gpk, \sig, \DAttrs,\msg) = 0 \lor
-    \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0:
-    \pcreturn 1 \\
+    \Judge(\gpk,\upk,\Attrs,\oproof,\sig,\DAttrs,\msg) = 0~\lor\\
+     \pcind \DAttrs \nsubseteq \Attrs \lor \Attrs \neq \ATTR[\cid]: \\
+     \pcind \pcreturn 1 \\
     \pcreturn 0
@@
 signatures. In anonymous credentials, the game must further constraint the
-adversary to output credentials that have some common subset of attributes, and
+adversary to pick credentials that have some common subset of attributes, and
 to use that common subset to request the challenge presentations. Here, we need
@@
 \begin{figure}[htp!]
-  \procedure{$\ExpAnonb(1^\secpar)$}{%
+  \procedure{$\ExpGSACAnonb(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
@@
      (\cid_0,\cid_1,\status) \gets
-     \adv^{\HUGEN,\CUGEN,\OBTAIN,\SIGN,\OPEN}(\choose,\gpk,\isk) \\
+     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN}(\choose,\gpk,\isk) \\
      b^* \gets
-     \adv^{\HUGEN,\CUGEN,\OBTAIN,\SIGN,\OPEN,\CHALb}(\guess,\gpk,\isk,\status) \\
+     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN,\CHALb}(\guess,\gpk,\isk,\status) \\
      \pcreturn b^*
@@
 \begin{definition}{(Anonymity of \GSAC)}
-  We define the advantage \AdvAnon of $\adv$ against \ExpAnonb as
-  $\AdvAnon=|\Pr\lbrack\ExpAnono(1^\secpar)=1\rbrack-
-  \Pr\lbrack\ExpAnonz(1^\secpar)=1\rbrack|$.
+  We define the advantage \AdvGSACAnon of $\adv$ against \ExpGSACAnonb as
+  $\AdvGSACAnon=|\Pr\lbrack\ExpGSACAnono(1^\secpar)=1\rbrack-
+  \Pr\lbrack\ExpGSACAnonz(1^\secpar)=1\rbrack|$.
   %
@@
 is able to produce a $(\sig,\DAttrs,\msg)$ tuple that is accepted by \Verify,
-but either cannot be opened, it can be opened by the proof is rejected by
-\Judge, or even though it is accepted by \Judge, there was no issued credential
-(honest or not) that contained the set of attributes \DAttrs. We formally
-define traceability in the \ExpTrace experiment in \figref{fig:exp-gsac-trace}.
+but either cannot be opened, it can be opened but the proof is rejected by
+\Judge, or even though it is accepted by \Judge, there is no credential issued
+to the user pointed to by \Open that contains the set of attributes \DAttrs. We
+formally define traceability in the \ExpTrace experiment in
+\figref{fig:exp-gsac-trace}.
 
 \begin{figure}[htp!]
-  \procedure{$\ExpTrace(1^\secpar)$}{%
+  \procedure{$\ExpGSACTrace(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
@@
     (\sig,\DAttrs,\msg) \gets
-     \adv^{\HUGEN,\CUGEN,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
+    \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
     \pcreturn 1~\pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 1~\land~( \\
-     \pcind \pccomment{All \Obtain transcripts fail to open \sig} \\
-     \pcind \forall \utrans \in \trans:
-     \Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg) = \bot~\lor \\
-     \pcind \pccomment{Such transcript exists, but ...} \\
-     \pcind \exists~\utrans~\st~\Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg) =
-     (\upk,\cred,\oproof)~\land (\\
-     \pcind \pcind \pccomment{... the opening proof is rejected by \Judge ...} \\
-     \pcind \pcind \Judge(\gpk,\upk,\cred,\oproof,\sig,\DAttrs,\msg) = 0~\lor \\
-     \pcind \pcind \pccomment{... or \Judge accepts the proof, but \DAttrs was
-       not issued to any credential} \\
-     \pcind \pcind \DAttrs \nsubseteq \ATTR[\cred] \\
-     \pcind ) \\
+    \pcind \pccomment{\Open fails} \\
+    \pcind \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) = \bot~\lor \\
+    \pcind \pccomment{\Open succeeds, but ...} \\
+    \pcind \Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg) =
+    (\upk,\Attrs,\oproof)~\land\\
+    \pcind \pcind \pccomment{... the proof is rejected by \Judge, or
+      it is accepted but \DAttrs is not contained in \Attrs} \\
+    \pcind \pcind (\Judge(\gpk,\upk,\Attrs,\oproof,\sig,\DAttrs,\msg) = 0
+    \lor \DAttrs \nsubseteq \Attrs) \\
     ) \\
@@
 \begin{definition}{(Traceability of \GSAC)}
-  We define the advantage \AdvTrace of $\adv$ against \ExpTrace as
-  $\AdvTrace=\Pr\lbrack\ExpTrace(1^\secpar)=1\rbrack$.
+  We define the advantage \AdvGSACTrace of $\adv$ against \ExpGSACTrace as
+  $\AdvGSACTrace=\Pr\lbrack\ExpGSACTrace(1^\secpar)=1\rbrack$.
   %
   A \GSAC scheme satisfies traceability if, for any p.p.t. adversary $\adv$,
-  \AdvTrace is a negligible function of $1^\secpar$.
+  \AdvGSACTrace is a negligible function of $1^\secpar$.
 \end{definition}
@@
 In \GSAC schemes, in order for a user to be framed, the adversary first needs to
-create a $(\sig,\DAttrs,\msg,\upk,\cred,\oproof)$ such that the signature,
+create a $(\sig,\DAttrs,\msg,\upk,\Attrs,\oproof)$ such that the signature,
 attributes, and message are accepted by \Verify, and which, along with the user
-public key, credential, and open correctness proof, are accepted by \Judge.
+public key, and open correctness proof, are accepted by \Judge.
 Then, the adversary wins the game if the owner of the credential is honest, but
-the signature was not produced via the \SIGN oracle, or if the public key output
-by the adversary does not match the public key associated to the credential
-owner.
-%
-Note that, as in anonymity, this notion of non-frameability is even stronger
-to that of group signatures, since our \Open function returns both the public
-key and the credential that were used to create the signature.
+the signature was not produced via the \SIGN oracle, or if the set of attribute
+disclosed in the signature are not contained in the set of attributes revealed
+during \Open.
 
 \begin{figure}[htp!]
-  \procedure{$\ExpNonframe(1^\secpar)$}{%
+  \procedure{$\ExpGSACNonframe(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
@@
      \gpk \gets (\ipk,\opk) \\
-     (\sig,\DAttrs,\msg,\upk,\cred,\oproof) \gets
-     \adv^{\HUGEN,\CUGEN,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
+     (\sig,\DAttrs,\msg,\upk,\Attrs,\oproof) \gets
+     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
+     \textrm{Let}~\uid~\textrm{be st}~\PUBUK[\uid] = (\upk,\cdot) \\
      \pcreturn 1~\pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 1 \land 
-     \OWNR[\cred] \in \HU \\%\land \cred \notin \CCRED~\land\\
-     \pcind \Judge(\gpk,\upk,\cred,\oproof,\sig,\DAttrs,\msg) = 1~\land \\
-     \pcind \pccomment{\sig was not produced by \SIGN, or \upk and \cred do not match} \\
-     \pcind (\sig \notin \SIG[\OWNR[\cred]] \lor \PUBUSK[\OWNR[\cred]] \neq \upk) \\
+     \Judge(\gpk,\upk,\Attrs,\oproof,\sig,\DAttrs,\msg) = 1~\land \\
+     \pcind \uid \in \HU \land (\sig \notin \SIG[\uid] \lor
+     \DAttrs \nsubseteq \Attrs) \\
      \pcreturn 0
@@
 \begin{definition}{(Non-frameability of \GSAC)}
-  We define the advantage \AdvNonframe of $\adv$ against \ExpNonframe as
-  $\AdvNonframe=\Pr\lbrack\ExpNonframe(1^\secpar)=1\rbrack$.
+  We define the advantage \AdvGSACNonframe of $\adv$ against \ExpGSACNonframe as
+  $\AdvGSACNonframe=\Pr\lbrack\ExpGSACNonframe(1^\secpar)=1\rbrack$.
   %
@@
 \paragraph{Discussion.} %
+\todo{Modelling choices: HU and CU lists are typically updated in join protocols
+  in the GS literature. Here, it is best to follow the AC literature, as a same
+  user (key) may be associated to multiple join protocols. So there are HUGEN
+  and CUGEN oracles.}
+
 \todo{Argue that our properties cover (and augment) a direct combination
@@
 
-\subsection{Tranformation to Interactive Presentations}
-\label{ssec:interactivetransform}
-
-\todo{Is it possible to give it in some generic sense?}
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "gsac"
+%%% TeX-master: "uas"
 %%% End:

### 2022-04-04 prism-backend/research/gsac/sec-gsac.tex
Seemingly stable model anc concrete instantiation for GSAC.

\section{\GSAC: Merging Group Signatures and Anonymous Credentials}
\label{sec:gsac}

\todo{Some intro here}

\input{model-gsac.tex}
\input{construction-gsac.tex}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:

### 2022-04-04 prism-backend/research/gsac/transformations.tex
Seemingly stable model anc concrete instantiation for GSAC.

\section{Relationships of UAS With Other Schemes}
\label{ssec:transformations}

\commentwho{Jesus}{This section is aimed at showing the ``universality'' of
  our model. If I'm not mistaken, ideally, it should support the following
  variations (except the transformation to interactive presentations,
  probably).}

\subsection{Transformation to Interactive Presentations}
\label{ssec:interactivetransform}

\todo{Is it possible to give it in some generic sense?}

\subsection{Combining Multiple Credentials in One Presentation}

\todo{I think this might be possible if we can use \fissue so that any user can
  create arbitrary groups, where he is the issuer, an can thus run
  \Obtain,\Issue protocols to combine credentials from other groups. This is
  probably inefficient (or, at least, more than doing so wihtout having to
  create ad hoc groups), but at least allows the enhanced functionality...}

\subsection{Restricting to Conventional GS and AC Schemes}

\todo{It would be nice to prove that a \GSAC scheme to which we remove the
  \Open/\Judge functions becomes an AC scheme. And conversely, a \GSAC scheme
  where all credentials have no attributes, and where we restrict to only
  one credential per user, becomes a conventional GS scheme.}

\subsection{Group Signatures with Message Dependent Opening}

\todo{Describe what type of \finsp would be needed to achieve a functionality
  similar to that of GS-MDO. Does this fit our model straight away? Maybe also
  show how other types of GS could be ``mimicked'' (e.g., GS only with linking).
  This would also be good to test if the model is as generic as I think it is}

\subsection{Ring Signatures}

\todo{Can we come up with a (\fissue,\feval,\finsp) tuple that allows us to
  somehow mimic ring signatures (i.e., ``a group signature without issuer nor
  opening''? Does the model support this?}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:

### 2022-04-05 prism-backend/research/gsac/preliminaries.tex
Merged GSAC and UAS into uas.tex paper. Defining concrete instantiation of GSAC.
Seemingly stable model anc concrete instantiation for GSAC.
Working on generic construction of GSAC.

@@
 
-\subsection{Building Blocks}
-\label{ssec:bblocks}
+\subsection{Cryptographic Building Blocks}
+\label{ssec:cryptobblocks}
+
+\todo{NIZKs.}
+
+\subsubsection{Notation}
+\label{ssec:notation}
+
+\todo{Attribute space. Used in generic construction of GSAC for now. Define it
+  to be the set of bitstrings of some length.}
+
+\todo{\Attrs and \DAttrs (in \secref{ssec:construction-gsac}, they are treated
+  as indices, but I think that's not the case elsewhere).}
+
+\todo{In \secref{ssec:construction-gsac}, we assume that all messages and
+  attributes can be encoded as elements in $\ZZ^*_p$.}
 

### 2022-04-08 prism-backend/research/gsac/model-uas.tex
Refined UAS model.

@@
 \label{ssec:model-uas}
+
+\comment{\textbf{DISCLAIMER}: I've done a major rewriting of most
+  properties. For now, please ignore the text until I have been able to sync
+  it.}
 
@@
   \langle
-  \Obtain(\usk,\attrs,\ldblbrace (gpk_i,\cred_i)\rdblbrace_{i \in \Issuers}),
-  \Issue(\isk,\upk,\attrs,\ldblbrace \gpk_i) \rdblbrace_{i \in \Issuers})
+  \Obtain(\usk,\lbrace (\cred_i,\ipk_i)\rbrace_{i \in \Issuers},\attrs),
+  \Issue(\isk,\lbrace \ipk_i \rbrace_{i \in \Issuers},\attrs))
   \rangle$.] %
   This interactive protocol lets a user with key pair (\upk,\usk) running the
-  \Obtain process, obtain a credential \cred from an issuer in the system, on
-  attribute set $\attrs$ plus, possibly, blinded attributes attested by
-  previously obtained credentials $\cred_i$, from a multiset of other issuers
-  (which may include the one to whom a new credential is being requested) with
-  public keys $\gpk_i$. The user outputs the produced credential \cred, while
+  \Obtain process, receive a credential \cred from an issuer in the system, on
+  attribute set $\attrs$. The user leverages a set of $(\cred_i,\ipk_i)$ pairs,
+  where $\cred_i$ is a credential obtained from the issuer with public
+  key $\ipk_i$. The user outputs the produced credential \cred, while
   the issuer outputs the protocol transcript \utrans for the produced
@@
   credential belongs is available from the credential itself, and therefore
-  omit the $\gpk_i$ values from the syntax, unless necessary to avoid ambiguity.
-\item[$\sig \gets \Sign(\gpk,\usk,\cred,\msg,\feval)$.]
-  The user with with secret key \usk and credential \cred, produces a signature
-  \sig over message \msg, meeting the conditions defined by \feval.
-\item[$1/0 \gets \Verify(\gpk,\sig,\msg,\feval)$.] Checks whether \sig is a
-  valid signature, over message \msg, from a user in the group with public key
-  \gpk, for signing function \feval.
-\item[$(\y,\iproof)/\bot \gets \Inspect(\gpk,\osk,\trans,\sig,\msg,\feval)$.] %
+  omit the $\ipk_i$ values from the syntax, unless necessary to avoid ambiguity.
+\item[$\sig \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
+  \rbrace_{i \in \Issuers},\msg,\feval)$.] %
+  The user with with secret key \usk, owner of credentials $\cred_i$, signs
+  \msg, so that the inspector with public key \opk may open it if needed.
+  Evaluation function \feval is used to produce the signature.
+\item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
+  \msg,\feval)$.] Checks whether \sig is a valid signature over message \msg,
+  from a user in the group with credentials issued by issuers with public keys
+  $\ipk_i$, for evaluation function \feval and inspector key \opk.
+\item[$(\y,\iproof)/\bot \gets \Inspect(\osk,\lbrace \ipk_i
+  \rbrace_{i \in \Issuers},\sig,\msg,\feval)$.] %
   \todo{I think we do not need \trans here, see the generic construction. (This
-    was somehow inherited from \cite{bsz05}.) However, if we do remove it, we'd
-    need to redefine the traceability game -- it'd need to depend on \Identify,
-    which kind of makes sense too.}
+    was somehow inherited from \cite{bsz05}.) However, if it is indeed not
+    needed, it is noteworthy that we include/need it in \GSAC, but not here.
+    Justify/understand better why!}
   Executed by the inspector with private key \osk. Receives a signature \sig
-  over message \msg and evaluation function \feval. If \trans contains a set of
-  valid transcripts corresponding 
-  to the $\langle\Obtain,\Issue\rangle$ interactive protocol execution that
-  issued the credential used to produce \sig, the function outputs a value $\y$
-  derived from the signer's public key, credential, message, and signature, as
-  well as a proof of correct inspection. We sometimes abuse notation, and write
-  $\trans[\uid]$ to mean that the \Inspect function is operating only for the
-  obtain transcripts related to user \uid.
-\item[$1/0 \gets \Judge(\gpk,\y,\iproof,\sig,\msg,\feval)$.] %
+  over message \msg and evaluation function \feval. If \sig is valid, the
+  function outputs a value $\y$ derived from the signer's public key,
+  credentials, message, and signature, as well as a proof of correct
+  inspection.
+\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\y,\iproof,
+  \sig,\msg,\feval)$.] %
   Checks if \iproof is a valid inspection correctness proof for the value \y,
-  obtained by applying \Inspect to the the signature \sig over message \msg. 
+  obtained by applying \Inspect to the the signature \sig over message \msg,
+  and for evaluation function \feval. 
 \end{description}
@@
 \begin{description}
-\item[$\fissue: (\upk, \attrs,\scred) \rightarrow 0/1$.] Defined by issuers,
+\item[$\fissue: (\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\attrs)
+  \rightarrow 0/1$.] Defined by issuers for the credentials they grant,
   governs what customized conditions an issuer requires in order to issue
@@
   attributes \attrs. \fissue may run checks on a (possibly empty) set of
-  additional credentials \scred, all bound to \upk, which may further be used
-  for blind issuance \commentwho{Jesus}{can it?}. \fissue returns $1$ to accept
-  a request, $0$ to reject it.  
-\item[$\feval: (\upk,\cred,\msg) \rightarrow \varrngfeval$.] Can be defined by
+  additional credentials $\cred_i$, all bound to \upk, and possibly issued
+  by other issuers. \fissue returns $1$ to accept a request, $0$ to reject it.  
+\item[$\feval: (\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\msg)
+  \rightarrow \varrngfeval$.] Can be defined by
   any party, although we anticipate that this will typically be done by either
   signers, verifiers, or some governance organization. It defines customized
-  conditions to be met by the owner of a user key \upk and credential \cred,
+  conditions to be met by the owner of a user key \upk and credentials $\cred_i$,
   bound to \upk, in order to sign a concrete message \msg. Its outputs
@@
   met.
-\item[$\finsp: (\varrngfeval,\upk,\cred,\msg) \rightarrow \varrngfinsp$.]
-  Defines what utility value, derived from the user's public key, credential,
-  and message should be extractable by the group inspector. Note that \finsp
-  also receives as input a value in the range of the \feval function, \rngfeval.
-  This will allow inspection logic to depend on the value produced by the
-  evaluation function. The output of \finsp is a value \varrngfinsp, which must
-  belong in a well defined set \rngfinsp.
+\item[$\finsp: (\varrngfeval,\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
+  \msg) \rightarrow \varrngfinsp$.]
+  Chosen by inspectors. It defines what utility value, derived from the user's
+  public key, credentials, and message, should be extractable by an inspector.
+  Note that \finsp also receives as input a value in the range of the \feval
+  function, \rngfeval. This will allow inspection logic to depend on the value
+  produced by the evaluation function. The output of \finsp is a value
+  \varrngfinsp, which must belong in a well defined set \rngfinsp.
 \end{description}
+
+We emphasize that, even though \finsp and \feval seem redundant, they are not.
+To see this, observe that \finsp is defined by inspectors, and will be fixed in
+all signatures ``inspectable'' by the inspector that defined it. On the other
+hand, \feval can be defined by (e.g.) verifiers and, as such, it can be changed
+on a per-signature basis, even if the signatures use the same \finsp. Thus,
+\feval can (and is intended to) be programmed to contain the conditions set by
+(e.g.) verifiers for signatures they receive; whereas \finsp can (and is intended
+to) be programmed to extract specific utility values when needed, which may
+depend on the checks required by the verifier a signature was intended to.
 
@@
     public key.
-  \item[\GK.] We bundle public keys for issuers and inspectors into a common
-    public key for each group. We use the table \GK for that purpose which,
-    consequently, can also be indexed by \gid.
   \end{description}
@@
     ``\attrs such that $\CRED[\cid] = (\cdot, \cdot, \cdot, \attrs, \cdot)$''.
-  \item[\GRP.] For notational convenience, when we write $\GRP[\cid]$ we mean
-    ``\gid such that $\CRED[\cid] = (\cdot, \gid, \cdot, \cdot, \cdot)$''.
+  \item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
+    ``\iid such that $\CRED[\cid] = (\cdot, \iid, \cdot, \cdot, \cdot)$''.
   \end{description}
@@
   user already exists and is honest, corrupts it.
+\item[\RREG.] Reads the given transcript table entry.
+\item[\WREG.] Sets a transcript table entry to the given value.
 \item[\OBTISS.] Lets the adversary add a new honestly generated credential to
@@
 
-        \procedure{$\IGEN(\gid,\fissue)$}{%
-          \pcif \gid \in \HI \lor \gid \in \CI: \pcreturn \bot \\
+        \procedure{$\IGEN(\iid,\fissue)$}{%
+          \pcif \iid \in \HI \lor \iid \in \CI: \pcreturn \bot \\
           (\ipk,\isk) \gets \IKeyGen(\parm) \\
-          \IK[\gid] \gets ((\ipk,\fissue),\isk) \\
-          \HI \gets \HI \cup \lbrace \gid \rbrace \\
-          \GK[\gid] \gets ((\ipk,\fissue),\cdot) \\
+          \IK[\iid] \gets ((\ipk,\fissue),\isk) \\
+          \HI \gets \HI \cup \lbrace \iid \rbrace \\
           \pcreturn \ipk \\
@@
 
-        \procedure{$\ICORR(\gid)$}{%
-          \pcif \gid \in \CI \lor \gid \notin \HI: \pcreturn \bot \\
-          \HI \gets \HI \setminus \lbrace \gid \rbrace \\
+        \procedure{$\ICORR(\iid)$}{%
+          \pcif \iid \in \CI \lor \iid \notin \HI: \pcreturn \bot \\
+          \HI \gets \HI \setminus \lbrace \iid \rbrace \\
           \CI \gets \CI \cup \lbrace \gid \rbrace \\
@@
           \HU \gets \HU \cup \lbrace  \uid \rbrace \\
-          \pcreturn \top
+          \pcreturn \top \\
+        }
+
+        \procedure{$\RREG(i)$}{%
+          \pcreturn \trans[i]
         }
@@
 
-        \procedure{$\OGEN(\gid,\feval,\finsp)$}{%
-          \pcif \gid \in \HO \lor \gid \in \CO: \pcreturn \bot \\
+        \procedure{$\OGEN(\oid,\finsp)$}{%
+          \pcif \oid \in \HO \lor \oid \in \CO: \pcreturn \bot \\
           (\opk,\osk) \gets \OKeyGen(\parm) \\
-          \OK[\gid] \gets ((\opk,\finsp),\osk) \\
-          \HO \gets \HO \cup \lbrace \gid \rbrace \\
-          \GK[\gid] \gets (\cdot,(\opk,\finsp)) \\
+          \OK[\oid] \gets ((\opk,\finsp),\osk) \\
+          \HO \gets \HO \cup \lbrace \oid \rbrace \\
           \pcreturn \opk \\
@@
 
-        \procedure{$\OCORR(\gid)$}{%
-          \pcif \gid \in \CO \lor \gid \notin \HO: \pcreturn \bot \\
-          \HO \gets \HO \setminus \lbrace \gid \rbrace \\
-          \CO \gets \CO \cup \lbrace \gid \rbrace \\
+        \procedure{$\OCORR(\oid)$}{%
+          \pcif \oid \in \CO \lor \oid \notin \HO: \pcreturn \bot \\
+          \HO \gets \HO \setminus \lbrace \oid \rbrace \\
+          \CO \gets \CO \cup \lbrace \oid \rbrace \\
           \pcreturn \osk \\
@@
           \pcelse: \UK[\uid] = (\upk,\bot) \\          
-          \pcreturn \top
+          \pcreturn \top \\
+        }
+
+        \procedure{$\WREG(i,\rho)$}{%
+          \trans[i] \gets \rho
         }
@@
 
-        \procedure{$\ISSUE(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
+        \procedure{$\ISSUE(\cid,\uid,\iid,\attrs,\siid)$}{%
           \pcif \uid \notin \CU: \pcreturn \bot \\          
-          \pcif \gid \notin \HI: \pcreturn \bot \\
-          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
+          \pcif \iid \notin \HI: \pcreturn \bot \\
+          \pcif \exists \iid' \in \ISR[\scid] \notin \HI: \pcreturn \bot \\
           \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
           \langle \cdot, \utrans \rangle \gets
-          \langle \adv, \\
-          \hspace*{45pt}
-          \Issue(\PRVIK[\gid],\PUBUK[\uid], \attrs,
-          \ldblbrace \CRED[\scid] \rdblbrace) \rangle \\
+          \langle \adv, 
+          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
           \trans[\cid] \gets \utrans \\
-          \CRED[\cid] \gets (\uid, \cdot, \gid, \attrs, \scid) \\
+          \CRED[\cid] \gets (\uid, \cdot, \iid, \attrs, \cdot, \siid) \\
           \pcreturn \top \\          
@@
 
-        \procedure{$\OBTAIN(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
+        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
           \pcif \uid \notin \HU: \pcreturn \bot \\
-          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
+          \pcif \iid \notin \CI: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
+          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot: \pcreturn \bot \\
           \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\PRVUK[\uid],\attrs, 
-          \ldblbrace \CRED[\scid] \rdblbrace), \\
-          \hspace*{50pt} \adv \rangle \\
-          \CRED[\cid] \gets (\uid, \cdot, \gid, \attrs, \scid) \\          
+          \langle \Obtain(\PRVUK[\uid],\CRED[\scid],\attrs),\adv \rangle \\
+          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
           \pcreturn \top \\
@@
 
-        \procedure{$\INSPECT(\gid,\sig,\msg)$}{%
-          \textrm{Let}~\uid~\textrm{be s.t.}~(\cid,\sig,\msg,\feval)
-          \in \SIG[\uid] \\
-          (\y,\iproof) \gets
-          \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg,\feval) \\
-          \pcif \CSIG[\sig] \neq \bot: \\
-          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\sig_{1-b},\msg,\feval)$} \\
-          \pcind (\y_{1-b},\iproof_{1-b}) \gets
-          \Inspect(\GK[\gid],\PRVOK[\gid],\\
-          \hspace*{107pt} \trans,\sig_{1-b},\msg,\feval) \\
-          \pcind \pcif \y_{1-b} \neq \y: \pcreturn \bot \\
-          \pcreturn (\y,\iproof)
+        \procedure{$\CHALb(\oid,\cscid_{0,1},\msg,\feval)$}{%
+          \pcif \pcfor d \in \bin~\exists \ccid_d,{\ccid}'_d \in \cscid_d~\st \\
+          \pcind \OWNR[\ccid_d] \neq \OWNR[{\ccid}'_d]: \\
+          \pcind \pcreturn \bot \\
+          \cuid_0 \gets \OWNR[\cscid_0]; \cuid_1 \gets \OWNR[\cscid_1] \\
+          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
+          \pcif \oid \in \CO: \pcreturn \bot \\
+          % \pcif \feval(\PUBUK[\cuid_0],\CRED[\cscid_0],\msg) \neq \\
+          % \pcind \feval(\PUBUK[\cuid_1],\CRED[\cscid_1],\msg):
+          % \pcreturn \bot \\
+          \csig_b \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid],\CRED[\cscid_b],
+          \msg,\feval) \\
+          \csig_{1-b} \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid],
+          \CRED[\cscid_{1-b}],\msg,\feval) \\          
+          \CSIG[\csig_b] \gets 
+          \lbrace (\csig_{1-b},\msg,\feval) \rbrace \\
+          \pcreturn \csig_b
         }
@@
 
-        \procedure{$\OBTISS(\cid,\uid,\gid,\attrs,\ldblbrace\scid\rdblbrace)$}{%
+        \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\scid)$}{%
           \pcif \uid \notin \HU: \pcreturn \bot \\
-          \pcif \gid \notin \HI: \pcreturn \bot \\
-          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
-          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot:
+          \pcif \iid \notin \HI: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
+          \pcif \exists \iid' \in \ISR[\scid]~\st~\iid' \notin \HI: \pcreturn \bot \\
+          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot:
           \pcreturn \bot \\
           \langle \cred, \utrans \rangle \gets
-          \langle \Obtain(\PRVUK[\uid],\attrs,
-          \ldblbrace \CRED[\scid] \rdblbrace), \\
-          \hspace*{60pt} \Issue(\PRVIK[\gid],\PUBUK[\uid],\attrs,
-          \ldblbrace \CRED[\scid] \rdblbrace ) \rangle \\
+          \langle \Obtain(\PRVUK[\uid],\CRED[\scid],\attrs), \\
+          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\scid],\attrs)
+          \rangle \\
           \trans[\cid] \gets \utrans \\
-          \CRED[\cid] \gets (\uid, \cred, \gid, \attrs, \scid) \\
+          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
           \pcreturn \top \\
@@
 
-        \procedure{$\SIGN(\uid,\cid,\msg,\feval)$}{%
-          \pcif \uid \notin \HU \lor \CRED[\cid] = \bot: \pcreturn \bot \\
-          \sig \gets \Sign(\GK[\GRP[\cid]],\PRVUK[\uid],\msg,\CRED[\cid],\feval) \\
+        \procedure{$\SIGN(\oid,\scid,\msg,\feval)$}{%
+          \pcif \exists \cid,\cid' \in \scid~\st~\OWNR[\cid] \neq \OWNR[\cid']:
+          \pcreturn \bot \\
+          \uid \gets \OWNR[\scid] \\
+          \pcif \uid \notin \HU \lor
+          \exists \cid \in \scid~\st~\CRED[\cid] = \bot: \pcreturn \bot \\
+          \sig \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,\feval) \\
           \SIG[\uid] \gets \SIG[\uid] \cup
-          \lbrace (\cid,\sig,\msg,\feval) \rbrace \\
+          \lbrace (\oid,\scid,\sig,\msg,\feval) \rbrace \\
           \pcreturn \sig \\
@@
 
-        \procedure{$\CHALb(\cuid_{0,1},\ccid_{0,1},\msg,\feval)$}{%
-          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
-          \pcif \gid = \GRP[\ccid_0] \neq \GRP[\ccid_1]: \pcreturn \bot \\
-          \pcif \gid \in \CO: \pcreturn \bot \\
-          \pcif \feval(\PUBUK[\uid_0],\CRED[\scid_0],\msg) \neq \\
-          \pcind \feval(\PUBUK[\uid_1],\CRED[\scid_1],\msg):
-          \pcreturn \bot \\
-          \csig_b \gets \Sign(\GK[\gid],\PRVUK[\cuid_b],\CRED[\ccid_b],
-          \msg,\feval) \\
-          \csig_{1-b} \gets \Sign(\GK[\gid],\PRVUK[\cuid_{1-b}],\CRED[\ccid_{1-b}],
-          \msg,\feval) \\          
-          \CSIG[\csig_b] \gets 
-          \lbrace (\csig_{1-b},\msg,\feval) \rbrace \\
-          \pcreturn \csig_b
+        \procedure{$\INSPECT(\oid,\sig,\msg)$}{%
+          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\sig,\msg,\feval)
+          \in \SIG[\uid] \\
+          (\y,\iproof) \gets
+          \Inspect(\PRVOK[\oid],\GK[\scid],\sig,\msg,\feval) \\
+          \pcif \CSIG[\sig] \neq \bot: \\
+          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\sig_{1-b},\msg,\feval)$} \\
+          \pcind (\y_{1-b},\iproof_{1-b}) \gets
+          \Inspect(\PRVOK[\oid],\IK[\siid],\\
+          \hspace*{107pt} \sig_{1-b},\msg,\feval) \\
+          \pcind \pcif \y_{1-b} \neq \y: \pcreturn \bot \\
+          \pcreturn (\y,\iproof)
         }
@@
     \parm \gets \Setup(1^\secpar) \\
-    (\uid,\cid,\msg,\feval)
-    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS}(\parm) \\
-    \sig \gets \Sign(\GK[\cid],\PRVUK[\uid],\cid,\msg,\feval) \\
-    \pcif \Verify(\GK[\cid],\sig,\msg,\feval) = 0: \pcreturn 1~
+    (\uid,\oid,\scid,\msg,\feval)
+    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
+    \sig \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
+    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = 0: \pcreturn 1~
     \pccomment{\sig fails to verify} \\
-    \pcif \CorrectIssue(\uid,\cid) = 0: \pcreturn 1~
-    \pccomment{\cid should not have been issued} \\
+    \pcif \CorrectIssue(\uid,\scid) = 0: \pcreturn 1~
+    \pccomment{Some \cid should not have been issued} \\
     % \pcif \CorrectEval(\uid,\cid,\msg,\feval)
@@
     % \pccomment{\msg should not have been signed} \\
-    \pcif \CorrectEvalInspect(\uid,\cid,\msg,\sig,\feval) = 0: \pcreturn 1~
+    \pcif \CorrectEvalInspect(\oid,\uid,\scid,\msg,\sig,\feval) = 0: \pcreturn 1~
     \pccomment{The combination of evaluation and inspection is wrong} \\
@@
 
-  \procedure{$\CorrectIssue(\uid,\cid)$}{
-    \gid \gets \GRP[\cid] \\
-    \textrm{Parse}~\ATTR[\cid]~\textrm{as}~(\attrs^\cid,\scid^\cid);~
-    \textrm{Parse}~\GK[\gid]~\textrm{as}~
+  \procedure{$\CorrectIssue(\uid,\scid)$}{
+    \pcfor \cid \in \scid \pcdo: \\
+    \pcind \iid \gets \ISR[\cid] \\
+    \pcind \textrm{Parse}~\ATTR[\cid]~\textrm{as}~(\attrs^\cid,\scid^\cid);~
+    \textrm{Parse}~\IK[\iid]~\textrm{as}~
     ((\cdot,\fissue^\gid),\cdot) \\        
-    \pcif \fissue^\gid(\PUBUK[\uid],\attrs^\cid,\CRED[\scid]^\cid) = 0: 
+    \pcind \pcif \fissue^\gid(\PUBUK[\uid],\CRED[\scid]^\cid,\attrs^\cid) = 0: 
     \pcreturn 0 \\
@@
 
-  \procedure{$\CorrectEvalInspect(\uid,\cid,\msg,\sig,\feval)$}{
-    \textrm{Let}~\gid \gets \GRP[\cid];~
-    \textrm{Parse}~\GK[\gid]~\textrm{as}~(\cdot,(\cdot,\finsp^\gid)) \\
+  \procedure{$\CorrectEvalInspect(\oid,\uid,\scid,\msg,\sig,\feval)$}{
+    \textrm{Parse}~\OK[\oid]~\textrm{as}~((\cdot,\finsp^\gid),\cdot) \\
     \pccomment{\sig cannot be inspected} \\
-    \pcif \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg,\feval) = \bot: \pcreturn 0 \\
+    \pcif \Inspect(\PRVOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = \bot:
+    \pcreturn 0 \\
     \pccomment{The produced $(\y,\iproof)$ pair is rejected by \Judge
@@
     } \\
-    \pcif (\y,\iproof) \gets \Inspect(\GK[\gid],\PRVOK[\gid],\trans,\sig,\msg,\feval)
-    \land
-    \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 0: \\
+    \pcif (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\PUBIK[\scid],\sig,
+    \msg,\feval) \land
+    \Judge(\PUBOK[\oid],\PUBIK[\scid],\y,\iproof,\sig,\msg,\feval) = 0: \\
     \pcind \pcreturn 0 \\
     \pccomment{\y is the wrong value} \\
-    \pcif \y \neq \finsp^\gid(\feval(\PUBUK[\uid],\CRED[\cid],\msg),
-    \PUBUK[\uid],\CRED[\cid],\msg)):
+    \pcif \y \neq \finsp^\gid(\feval(\PUBUK[\uid],\CRED[\scid],\msg),
+    \PUBUK[\uid],\CRED[\scid],\msg)):
     \pcreturn 0 \\
@@
 given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,\CU\rbrace
-\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN,
+\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,
 \INSPECT)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace
-\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN,\INSPECT,\CHALb)$
+\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\INSPECT,\CHALb)$
 
@@
      \parm \gets \Setup(1^\secpar) \\
-     (\ccid_0,\ccid_1,\status) \gets \adv^{\Oanonc}(\choose,\parm) \\
+     (\cscid_0,\cscid_1,\status) \gets \adv^{\Oanonc}(\choose,\parm) \\
      b^* \gets \adv^{\Oanong} (\guess,\status) \\
@@
 of the signer -- which cannot be the same for different challenge users.
+
+\paragraph{Unforgeability.}
+
+\begin{figure}[htp!]
+    \procedure{$\ExpForgeIssue(1^\secpar)$}{%
+      \parm \gets \Setup(1^\secpar) \\
+      \cid \gets \adv^{\Oforgeissue}(\parm) \\
+      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
+      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
+      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
+      w \gets \ExtractIssue(\trans[\cid]) \\
+      \pcif w = \bot: \pcreturn 1 \\
+      \textrm{Parse}~w~\textrm{as}~(\usk,\lbrace (\cred_i,\ipk_i)
+      \rbrace_{i \in \Issuers})  \\      
+      \pcif \fissue(\usk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
+      \ATTR[\cid]) = 0: \pcreturn 1 \\
+      \pcreturn 0
+    }
+  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
+  \label{fig:exp-uas-unfor-issue}
+\end{figure}
+
+\begin{figure}[htp!]
+    \procedure{$\ExpForgeSign(1^\secpar)$}{%
+      \parm \gets \Setup(1^\secpar) \\
+      (\oid,\siid,\sig,\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
+      \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\msg,\feval) \in \SIG[\uid]: \pcreturn 0 \\
+      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\msg,\feval) = 0: \pcreturn 0 \\
+      (\y,\iproof) \gets \Inspect(\PRVOK[\oid],\siid,\trans,\sig,\msg) \\
+      \pcif \y = \bot \lor \iproof = \bot \lor       
+      \Judge(\PUBOK[\oid],\PUBIK[\siid],\y,\iproof,\sig,\msg,\feval) = 0: \pcreturn 0 \\
+      (\usk,\scred) \gets \ExtractSign(\oid,\siid,\sig,\msg,\feval) \\
+      %\pcif \usk = \bot \lor \scred = \bot: \pcreturn 1 \\
+      \pcif \finsp(\feval(\usk,\scred,\msg),\usk,\scred,\msg)
+      \neq \y: \pcreturn 1 \\
+      %\text{\todo{Need to check \feval independently here?}} \\
+      \pcreturn 0
+    }
+  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
+  \label{fig:exp-uas-unfor-sign}
+\end{figure}
 
@@
 where $\Otrace \gets \lbrace\HU,\CU\rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,
-\ISSUE,\SIGN,\INSPECT$.
+\ISSUE,\RREG,\SIGN,\INSPECT$.
 
-\begin{figure}[htp!]
-    \procedure{$\ExpTrace(1^\secpar)$}{%
-      \parm \gets \Setup(1^\secpar) \\
-      (\gid,\sig,\msg,\feval) \gets \adv^{\Otrace}(\parm) \\
-      \pcif \Verify(\GK[\gid],\sig,\msg,\feval) = 0: \pcreturn 0 \\
-      \pcif \EvalInspectForge(\gid,\sig,\msg,\feval) = 1 \\%\land
-%      \InspectForge(\gid,\sig,\msg,\feval) = 1: \\
-      \pcind \pcreturn 1 \\
-      \pcreturn 0 \\
-    }
+% \begin{figure}[htp!]
+%     \procedure{$\ExpTrace(1^\secpar)$}{%
+%       \parm \gets \Setup(1^\secpar) \\
+%       (\sgid,\sig,\msg,\feval) \gets \adv^{\Otrace}(\parm) \\
+%       \pcif \Verify(\GK[\sgid],\sig,\msg,\feval) = 0: \pcreturn 0 \\
+%       (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\sgid,\trans,\sig,\msg) \\
+%       \pcif \y = \bot \lor \iproof = \bot \lor       
+%       \Judge(\GK[\sgid],\y,\iproof,\sig,\msg,\feval) = 0: \pcreturn 0 \\
+%       \pcif \EvalForge(\sgid,\sig,\msg,\feval) = 1 \lor
+%       \IssueForge() = 1: \pcreturn 1 \\
+%       \pcreturn 0 \\
+%       % \pcind \pcind \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
+%       % \pcind \pcind \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
+%       %   $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\      
+%       % \pcind \pcind \pcreturn 1 \\      
+%     }
 
-    % \procedure{$\EvalForge(\gid,\sig,\msg,\feval)$}{%
-    %   \pcif \exists \uid~\st~\Identify(\uid,\sig) = 1~\land \\
-    %   \pcind \pccomment{\uid does not own a \cred that satisfies \feval...} \\
-    %   \pcind (\nexists \cred \in \CRED[\uid]~\st~
-    %   \feval(\PUBUK[\uid],\cred,\msg) \neq 0 ~\lor \\
-    %   \hspace*{13pt} \pccomment{... or \uid does, but \cred was itself obtained
-    %     fraudulently} \\
-    %   \hspace*{13pt} (\exists \cred \in \CRED[\uid]~\st~
-    %   \feval(\PUBUK[\uid],\cred,\msg) \neq 0~\land \\
-    %   \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
-    %   \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
+%     \procedure{$\EvalForge(\sgid,\sig,\msg,\feval)$}{%
+%       (\uid,\usk,\scred) \gets \ExtractSign(\sgid,\sig,\msg,\feval) \\
+%       \pcif \uid = \bot \lor \usk = \bot \lor \scred = \bot: \pcreturn 1 \\
+%       \pcif \finsp(\feval(\PUBUK[\uid],\scred,\msg),\PUBUK[\uid],\scred,\msg)
+%       \neq \y: \pcreturn 1 \\      
+%     }
+
+%     \procedure{$\IssueForge()$}{%
+%       \pcfor \cred \in \scred: \\
+%       \pcind \scred' \gets \ExtractIssue()
+%       \pcif \exists \cred \in \scred~\st~
+%       \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0 \\
+%       \pcind \textrm{where $\CRED[\cid]=\cred$ and
 %         $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\      
 %       \pcind \pcreturn 1 \\      
-    %   \pcelse \pcreturn 0 \\
 %     }
 
-    \procedure{$\EvalInspectForge(\gid,\sig,\msg,\feval)$}{%
-      \pccomment{All \Obtain transcripts fail to inspect \sig} \\
-      \pcif \Inspect(\PRVOK[\gid],\trans,\sig,\msg) \neq \bot~\lor \\
-      \pcind \pccomment{A valid transcript exists, but ...} \\
-      \pcind \exists \uid~\st~\Inspect(\PRVOK[\gid],\trans[\uid],\sig,\msg) =
-      (\y,\iproof)~\land (\\
-      \pcind \pcind \pccomment{... the proof is rejected by \Judge ...} \\
-      \pcind \pcind \Judge(\y,\iproof,\sig,\msg,\GK[\sgid]) = 0~\lor \\
-      \pcind \pcind \pccomment{... or \uid does not own a \cred for which
-        \finsp outputs \y} \\
-      \pcind \pcind \nexists \cred \in \CRED[\uid]~\st~
-      \y = \finsp(\feval(\PUBUK[\uid],\cred,\msg),
-      \PUBUK[\uid],\cred,\msg)~\lor \\
-      \pcind \pcind \pccomment{... or \uid does, but \cred was itself obtained
-        fraudulently} \\
-      \pcind \pcind (\exists \cred \in \CRED[\uid]~\st~
-      y = \finsp(\feval(\PUBUK[\uid],\cred,\msg),
-      \PUBUK[\uid],\cred,\msg)~\land \\
-      \pcind \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
-      \pcind \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
-        $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\      
-      \pcind \pcreturn 1 \\      
-      \pcreturn 0
-    }
-  \caption{Traceability experiment for \UAS schemes.}
-  \label{fig:exp-uas-trace}
-\end{figure}
+%     \procedure{$\ExtractSign(\sig,\msg,\feval,\sgid)$}{%
+%       \pcif \exists \cred,\cred' \in \scred~\st~\OWNR[\cred] \neq \OWNR[\cred']:
+%       \pcreturn (\bot,\bot,\bot) \\
+%       \pcif \nexists \uid~\st~\SUK[\uid] = \usk: \pcreturn (\bot,\bot,\bot) \\
+%       \pcif \uid \neq \OWNR[\scred]: \pcreturn (\bot,\bot,\bot) \\
+%       \todo{Return the \uid, \usk and \scred used to produce \sig} \\      
+%     }
+
+%     \procedure{$\ExtractIssue()$}{%
+%       \todo{Return the \scred used to fetch \cred} 
+%     }
+
+%     % \procedure{$\EvalForge(\gid,\sig,\msg,\feval)$}{%
+%     %   \pcif \exists \uid~\st~\Identify(\uid,\sig) = 1~\land \\
+%     %   \pcind \pccomment{\uid does not own a \cred that satisfies \feval...} \\
+%     %   \pcind (\nexists \cred \in \CRED[\uid]~\st~
+%     %   \feval(\PUBUK[\uid],\cred,\msg) \neq 0 ~\lor \\
+%     %   \hspace*{13pt} \pccomment{... or \uid does, but \cred was itself obtained
+%     %     fraudulently} \\
+%     %   \hspace*{13pt} (\exists \cred \in \CRED[\uid]~\st~
+%     %   \feval(\PUBUK[\uid],\cred,\msg) \neq 0~\land \\
+%     %   \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
+%     %   \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
+%     %     $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\
+%     %   \pcind \pcreturn 1 \\
+%     %   \pcelse \pcreturn 0 \\
+%     % }
+
+%     \procedure{$\EvalInspectForge(\gid,\sig,\msg,\feval)$}{%
+%       \pcfor \gid \in \sgid: \\
+%       \pcind \pccomment{\sig cannot be inspected} \\
+%       \pcind \pcif \Inspect(\PRVOK[\gid],\sgid,\trans,\sig,\msg) \neq \bot~\lor \\
+%       \pcind \pcind \pccomment{A valid transcript exists, but ...} \\
+%       \pcind \pcind \Inspect(\PRVOK[\gid],\sgid,\trans,\sig,\msg) =
+%       (\y,\iproof)~\land (\\
+%       \pcind \pcind \pcind \pccomment{... the proof is rejected by \Judge ...} \\
+%       \pcind  \pcind \pcind \Judge(\GK[\sgid],\y,\iproof,\sig,\msg,\feval) = 0~\lor \\
+%       \pcind  \pcind \pcind \Judge(\GK[\sgid],\y,\iproof,\sig,\msg,\feval) = 1
+%       \land \exists \uid~\st~\Identify(\uid,\sig) = 1 \land \\
+%       % \pcind \pcind \pcind \pccomment{... or \uid does not own a \cred for which
+%       %   \finsp outputs \y} \\
+%       % \pcind \pcind \pcind \nexists \cred \in \CRED[\uid]~\st~
+%       % \y = \finsp(\feval(\PUBUK[\uid],\cred,\msg),
+%       % \PUBUK[\uid],\cred,\msg)~\lor \\
+%       \pcind \pcind \pcind \pccomment{... or \uid does, but \cred was itself obtained
+%         fraudulently} \\
+%       \pcind \pcind \pcind (\exists \cred \in \CRED[\uid]~\st~
+%       y = \finsp(\feval(\PUBUK[\uid],\cred,\msg),
+%       \PUBUK[\uid],\cred,\msg)~\land \\
+%       \pcind \pcind \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
+%       \pcind \pcind \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
+%         $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\      
+%       \pcind \pcind \pcreturn 1 \\      
+%       \pcreturn 0
+%     }
+%   \caption{Traceability experiment for \UAS schemes.}
+%   \label{fig:exp-uas-trace}
+% \end{figure}
 
@@
 $\Oframe \gets \lbrace\HU,\CU\rbrace\GEN,
-\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN$
+\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG,\OBTAIN,\SIGN$
 
@@
     \parm \gets \Setup(1^\secpar) \\
-     (\gid,\sig,\msg,\feval,\y,\iproof) \gets \adv^{\Oframe}(\parm) \\
-     \pcreturn 1~\pcif \Verify(\GK[\gid],\sig,\msg,\feval) = 1 \land
-     \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 1~\land \\
-     \pcind \pccomment{\adv~did not query \SIGN to get \sig, yet \sig originates
-       from an honest \uid, owning a credential that makes \finsp
-       evaluate to \y} \\
-     \pcind \exists \uid \in \HU~\st~\Identify(\PRVUK[\uid],\sig) = 1 \land
-     (\cdot,\sig,\msg,\cdot) \notin \SIG[\uid]~\land\\
-     \pcind \exists \cred \in \CRED[\uid]~\st~
-     \finsp(\feval(\PUBUK[\uid],\cred,\msg),\PUBUK[\uid],\cred,\msg) = \y \\
-%     \pccomment{\todo{I don't think we can give any assurance about \feval here,
-%         given that issuers are corrupt. But still, think about it.}} \\
+    (\oid,\siid,\sig,\msg,\feval,\y,\iproof) \gets \adv^{\Oframe}(\parm) \\
+    \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\msg,\feval) \in \SIG[\uid]: \pcreturn 0 \\
+    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\msg,\feval) = 0: \pcreturn 0 \\
+    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\y,\iproof,\sig,\msg) = 0: \pcreturn 0 \\
+    (\usk,\scred) \gets \ExtractSign(\oid,\siid,\sig,\msg,\feval) \\
+    %\pcif \usk = \bot \lor \scred = \bot: \pcreturn 1 \\
+    \pcif \exists \uid \in \HU~\st~\PRVUK[\uid] = \usk: \pcreturn 1 \\
     \pcreturn 0
   }
-  \caption{Non-frameability experiment for \UAS schemes.}
+  \caption{Experiment for non-frameability on \UAS schemes.}
   \label{fig:exp-uas-frame}
@@
 
-\begin{definition}{(Non-frameability of \GSAC)}
+\commentwho{Jesus}{Current intuition of non-frame: Since issuer is corrupt,
+  basically \adv~ can create signatures that open to any value. All we can
+  hope for is that no forgery can exist that ``extracts'' to an honest user.}
+
+% \begin{figure}[htp!]
+%   \procedure{$\ExpNonframe(1^\secpar)$}{%
+%     \parm \gets \Setup(1^\secpar) \\
+%      (\gid,\sig,\msg,\feval,\y,\iproof) \gets \adv^{\Oframe}(\parm) \\
+%      \pcreturn 1~\pcif \Verify(\GK[\gid],\sig,\msg,\feval) = 1 \land
+%      \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 1~\land \\
+%      \pcind \pccomment{\adv~did not query \SIGN to get \sig, yet \sig originates
+%        from an honest \uid, owning a credential that makes \finsp
+%        evaluate to \y} \\
+%      \pcind \exists \uid \in \HU~\st~\Identify(\PRVUK[\uid],\sig) = 1 \land
+%      (\cdot,\sig,\msg,\cdot) \notin \SIG[\uid]~\land\\
+%      \pcind \exists \cred \in \CRED[\uid]~\st~
+%      \finsp(\feval(\PUBUK[\uid],\cred,\msg),\PUBUK[\uid],\cred,\msg) = \y \\
+% %     \pccomment{\todo{I don't think we can give any assurance about \feval here,
+% %         given that issuers are corrupt. But still, think about it.}} \\
+%      \pcreturn 0 \\
+%      kk from former trace \\
+%      \pcind \pcind \pcind \pccomment{... or \uid does not own a \cred for which
+%        \finsp outputs \y} \\
+%      \pcind \pcind \pcind \nexists \cred \in \CRED[\uid]~\st~
+%      \y = \finsp(\feval(\PUBUK[\uid],\cred,\msg),
+%      \PUBUK[\uid],\cred,\msg)~\lor \\     
+%   }
+%   \caption{Non-frameability experiment for \UAS schemes.}
+%   \label{fig:exp-uas-frame}
+% \end{figure}
+
+\begin{definition}{(Non-frameability of \UAS)}
   We define the advantage \AdvNonframe of $\adv$ against \ExpNonframe as

### 2022-04-11 prism-backend/research/gsac/model-uas.tex
Refined UAS model. Seems ok, but need to add extractability definition.

@@
 
-In the following, we assume a setting with multiple groups. For simplicity,
-we assume that each has its own issuer and inspector.
-
-\todo{Are generalizations where different groups can share issuer or inspector
-  straight forward?}
+An \UAS scheme is composed by the following algorithms.
 
@@
   requestors meet the conditions to be issued a credential, an issuer runs
-  \IKeyGen to generate its issuing key pair. Hereafter, we assume that the
-  public part \ipk is added to the group public key \gpk, as well as \fissue.
+  \IKeyGen to generate its issuing key pair. 
 \item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
@@
   will be extractable from those pairs that do not meet conditions defined
-  at signing time (typically, by verifiers). Hereafter, we assume that the
-  public part \opk is added to the group public key \gpk, along with \finsp.
-\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
-  \parm, returns a user's key pair.
+  at signing time (typically, by verifiers).
+\item[$\usk \gets \UKeyGen(\parm)$.] Given global system parameters
+  \parm, returns a user's secret key.
 \item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
@@
   \rangle$.] %
-  This interactive protocol lets a user with key pair (\upk,\usk) running the
+  This interactive protocol lets a user with key \usk running the
   \Obtain process, receive a credential \cred from an issuer in the system, on
@@
   omit the $\ipk_i$ values from the syntax, unless necessary to avoid ambiguity.
-\item[$\sig \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
+\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
   \rbrace_{i \in \Issuers},\msg,\feval)$.] %
-  The user with with secret key \usk, owner of credentials $\cred_i$, signs
-  \msg, so that the inspector with public key \opk may open it if needed.
-  Evaluation function \feval is used to produce the signature.
+  Upon receiving a user secret key \usk, inspector public key \opk, a set of
+  credential-issuer pairs $(\cred_i,\ipk_i)$, a message \msg and evaluation
+  function \feval, returns signature \sig and value \yeval.
 \item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
-  \msg,\feval)$.] Checks whether \sig is a valid signature over message \msg,
-  from a user in the group with credentials issued by issuers with public keys
-  $\ipk_i$, for evaluation function \feval and inspector key \opk.
-\item[$(\y,\iproof)/\bot \gets \Inspect(\osk,\lbrace \ipk_i
-  \rbrace_{i \in \Issuers},\sig,\msg,\feval)$.] %
+  \yeval,\msg,\feval)$.] Checks whether $(\sig,\yeval)$ is a valid signature
+  over message \msg, from a user with credentials issued by issuers with public
+  keys $\ipk_i$, for evaluation function \feval and inspector key \opk.
+\item[$(\yinsp,\iproof)/\bot \gets \Inspect(\osk,\lbrace \ipk_i
+  \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
   \todo{I think we do not need \trans here, see the generic construction. (This
@@
     Justify/understand better why!}
-  Executed by the inspector with private key \osk. Receives a signature \sig
-  over message \msg and evaluation function \feval. If \sig is valid, the
-  function outputs a value $\y$ derived from the signer's public key,
+  Executed by the inspector with private key \osk. Receives a signature $(\sig,
+  \yeval)$ over message \msg and evaluation function \feval, generated using
+  credentials issued by the issuers with public keys $\ipk_i$. If \sig is valid,
+  the function outputs a value $\yinsp$ derived from the signer's public key,
   credentials, message, and signature, as well as a proof of correct
   inspection.
-\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\y,\iproof,
-  \sig,\msg,\feval)$.] %
-  Checks if \iproof is a valid inspection correctness proof for the value \y,
-  obtained by applying \Inspect to the the signature \sig over message \msg,
-  and for evaluation function \feval. 
+\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\yinsp,
+  \iproof,\sig,\yeval,\msg,\feval)$.] %
+  Checks if \iproof is a valid inspection correctness proof for the value \yinsp,
+  obtained by applying \Inspect to the the signature $(\sig,\yeval)$ over
+  message \msg, and for evaluation function \feval. 
 \end{description}
-
-The correctness and security properties are defined with the help of the
-following sets of oracles, and global variables that help oracles and games
-keep consistent state.
 
@@
 \item[$\fissue: (\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\attrs)
-  \rightarrow 0/1$.] Defined by issuers for the credentials they grant,
-  governs what customized conditions an issuer requires in order to issue
-  credentials, when receiving a request from user with public key \upk, for
-  attributes \attrs. \fissue may run checks on a (possibly empty) set of
-  additional credentials $\cred_i$, all bound to \upk, and possibly issued
-  by other issuers. \fissue returns $1$ to accept a request, $0$ to reject it.  
+  \rightarrow 0/1$.] Chosen by issuers within a family of functions \famfissue,
+  the issuance function defines what customized conditions an issuer requires
+  in order to issue credentials, when receiving a request from user with public
+  key \upk, for attributes \attrs. \fissue may run checks on a (possibly empty)
+  set of additional credentials $\cred_i$, all bound to \upk, and possibly
+  issued by other issuers. \fissue returns $1$ to accept a request, $0$ to
+  reject it.
 \item[$\feval: (\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\msg)
-  \rightarrow \varrngfeval$.] Can be defined by
-  any party, although we anticipate that this will typically be done by either
-  signers, verifiers, or some governance organization. It defines customized
-  conditions to be met by the owner of a user key \upk and credentials $\cred_i$,
-  bound to \upk, in order to sign a concrete message \msg. Its outputs
-  $\varrngfeval$ must belong in a well defined set \rngfeval, with the
-  restriction that it must return $0$ when the conditions for signing are not
-  met.
-\item[$\finsp: (\varrngfeval,\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
-  \msg) \rightarrow \varrngfinsp$.]
-  Chosen by inspectors. It defines what utility value, derived from the user's
-  public key, credentials, and message, should be extractable by an inspector.
+  \rightarrow \yeval$.] Evaluation functions, from a family of functions
+  \famfeval, can be set on a per-signature basis. The evaluation function
+  defines customized conditions to be met by the owner of a user key \upk and
+  credentials $\cred_i$, bound to \upk, in order to sign a concrete message
+  \msg. Its outputs \yeval must belong in a well defined set \rngfeval.
+\item[$\finsp: (\yeval,\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
+  \msg) \rightarrow \yinsp$.]
+  Chosen by inspectors from a family of functions \famfinsp. The inspection
+  functions define what utility value, derived from the user's public key,
+  credentials, and signed message, should be extractable by an inspector.
   Note that \finsp also receives as input a value in the range of the \feval
@@
   produced by the evaluation function. The output of \finsp is a value
-  \varrngfinsp, which must belong in a well defined set \rngfinsp.
+  \yinsp, which must belong in a well defined set \rngfinsp.
 \end{description}
@@
 
-\paragraph{Helper Function \Identify.} In addition, we make use of a helper
+\paragraph{Helper Function \Identify.} %
+\todo{We use extract now...} In addition, we make use of a helper
 function \Identify for some of our definitions. This function receives
@@
     i.e., they are sets of {\uid}s.
-  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers.
-    Since we assume only one issuer per group, they are sets of {\gid}s.
-  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) inspectors.
-    Since we assume only one inspector per group, they are sets of {\gid}s.
+  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers;
+    i.e., they are sets of {\iid}s.
+  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) inspectors;
+    i.e., they are sets of {\oid}s.
   \end{description}
@@
   \begin{description}
-  \item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$.
-    To refer to the key pair of a specific user, we use $\UK[\uid]$. \PUBUK
-    is a shorthand to refer to the public part, and \PRVUK refers to the
-    private part -- we may also index both by \uid.
-  \item[\IK, \PUBIK and \PRVIK.] Same as \UK, but for issuer key pairs. In
-    addition, \IK also includes the \fissue function, which is part of the
-    public key.
-  \item[\OK, \PUBOK, \PRVOK.] Same as \UK, but for inspector key pairs. In
-    addition, \OK also includes the \finsp function, which is part of the
-    public key.
+  \item[\UK.] \UK maintains user keys $\usk$. To refer to the key of a specific
+    user, we use $\UK[\uid]$. 
+  \item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
+    $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
+    use \PUBIK to refer to the public component, which also includes the \fissue
+    function; and \PRVIK refers to the private component of the key pair.
+  \item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for inspector key pairs. Instead
+    of \fissue, \OK includes the \finsp function.
   \end{description}
@@
     users. Thus, it is indexable by \cid. More specifically, it stores tuples of
-    the form $(\uid,\cred,\gid,\attrs,\scid)$, where \uid is the identity of the
+    the form $(\uid,\cred,\iid,\attrs,\scid)$, where \uid is the identity of the
     owner of the credential, \cred (when available) is the credential itself,
-    \gid is the identifier of the group to which the credential belongs, \attrs
-    are the attributes included in \cred, and \scid are the identifiers of any
-    additional credential that \uid used to request \cred.
+    \iid is the identifier of the credential issuer, \attrs are the attributes
+    included in \cred, and \scid are the identifiers of the credentials (if any)
+    that \uid used to request \cred.
   \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
@@
   \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
-    of honest users.
-  \item[\CSIG.] Maintains challenge signatures, generated via the \CHALb oracle,
-    by one of the challenge users in the anonymity game.
+    of honest users. Entries of this table are $(\oid,\scid,\sig,\yeval,\msg,
+    \feval)$,
+    where \oid is the inspector chosen for the signature, \scid is the set of
+    credentials used for signing, \feval is the evaluation function, and \sig
+    and \msg are the produced signature and signed message.
+  \item[\CSIG.] Maintains challenge signatures output to the adversary; i.e.,
+    the table is indexable by challenge signatures \csig.
+    Each entry contains also $\cuid_b$ and $\scid_b$ the challenge user and
+    credential identifiers set used to produce \csig; as well as the
+    corresponding challenge user and credential set indexed by the complementary
+    $1-b$; the signed message \msg and evaluation function \feval, the result of
+    \feval, \yeval, and the inspector identifier \oid.
   \end{description}
@@
           \pcif \iid \in \HI \lor \iid \in \CI: \pcreturn \bot \\
+          \pcif \fissue \notin \famfissue: \pcreturn \bot \\
           (\ipk,\isk) \gets \IKeyGen(\parm) \\
@@
           \pcif \oid \in \HO \lor \oid \in \CO: \pcreturn \bot \\
+          \pcif \finsp \notin \famfinsp: \pcreturn \bot \\
           (\opk,\osk) \gets \OKeyGen(\parm) \\
@@
 
-        \procedure{$\CHALb(\oid,\cscid_{0,1},\msg,\feval)$}{%
-          \pcif \pcfor d \in \bin~\exists \ccid_d,{\ccid}'_d \in \cscid_d~\st \\
-          \pcind \OWNR[\ccid_d] \neq \OWNR[{\ccid}'_d]: \\
-          \pcind \pcreturn \bot \\
-          \cuid_0 \gets \OWNR[\cscid_0]; \cuid_1 \gets \OWNR[\cscid_1] \\
+        \procedure{$\CHALb(\oid,\cuid_{0,1},\cscid_{0,1},\msg,\feval)$}{%
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
           \pcif \oid \in \CO: \pcreturn \bot \\
-          % \pcif \feval(\PUBUK[\cuid_0],\CRED[\cscid_0],\msg) \neq \\
-          % \pcind \feval(\PUBUK[\cuid_1],\CRED[\cscid_1],\msg):
-          % \pcreturn \bot \\
-          \csig_b \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid],\CRED[\cscid_b],
-          \msg,\feval) \\
-          \csig_{1-b} \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid],
-          \CRED[\cscid_{1-b}],\msg,\feval) \\          
+          \pcif \yeval = \feval(\PUBUK[\cuid_0],\CRED[\cscid_0],\msg) \neq \\
+          \pcind \feval(\PUBUK[\cuid_1],\CRED[\cscid_1],\msg):
+          \pcreturn \bot \\
+          (\yeval,\csig_b) \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid], \\
+          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
+          (\yeval,\csig_{1-b}) \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid], \\
+          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
           \CSIG[\csig_b] \gets 
-          \lbrace (\csig_{1-b},\msg,\feval) \rbrace \\
+          \lbrace (\oid,\cuid_b,\cscid_b,\msg,\feval,\yeval,\\
+          \hspace*{74pt}\cuid_{1-b},\csig_{1-b},\cscid_{1-b})
+          \rbrace \\
           \pcreturn \csig_b
@@
 
-        \procedure{$\SIGN(\oid,\scid,\msg,\feval)$}{%
-          \pcif \exists \cid,\cid' \in \scid~\st~\OWNR[\cid] \neq \OWNR[\cid']:
-          \pcreturn \bot \\
-          \uid \gets \OWNR[\scid] \\
-          \pcif \uid \notin \HU \lor
-          \exists \cid \in \scid~\st~\CRED[\cid] = \bot: \pcreturn \bot \\
-          \sig \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,\feval) \\
+        \procedure{$\SIGN(\oid,\uid,\scid,\msg,\feval)$}{%
+          \pcif \uid \notin \HU: \pcreturn \bot \\
+          (\sig,\yeval) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,
+          \feval) \\
           \SIG[\uid] \gets \SIG[\uid] \cup
-          \lbrace (\oid,\scid,\sig,\msg,\feval) \rbrace \\
+          \lbrace (\oid,\scid,\sig,\yeval,\msg,\feval) \rbrace \\
           \pcreturn \sig \\
@@
 
-        \procedure{$\INSPECT(\oid,\sig,\msg)$}{%
-          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\sig,\msg,\feval)
+        \procedure{$\INSPECT(\oid,\sig,\yeval,\msg)$}{%
+          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\sig,\yeval,\msg,\feval)
           \in \SIG[\uid] \\
-          (\y,\iproof) \gets
-          \Inspect(\PRVOK[\oid],\GK[\scid],\sig,\msg,\feval) \\
+          (\yinsp,\iproof) \gets
+          \Inspect(\PRVOK[\oid],\GK[\scid],\sig,\yeval,\msg,\feval) \\
           \pcif \CSIG[\sig] \neq \bot: \\
-          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\sig_{1-b},\msg,\feval)$} \\
-          \pcind (\y_{1-b},\iproof_{1-b}) \gets
+          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
+            \feval,\yeval$} \\
+          \hspace*{83pt}\cuid_{1-b},\csig_{1-b},\scid_{1-b}) \\
+          \pcind (\yinsp',\iproof') \gets
           \Inspect(\PRVOK[\oid],\IK[\siid],\\
           \hspace*{107pt} \sig_{1-b},\msg,\feval) \\
-          \pcind \pcif \y_{1-b} \neq \y: \pcreturn \bot \\
-          \pcreturn (\y,\iproof)
+          \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
+          \pcreturn (\yinsp,\iproof)
         }
@@
 \figref{fig:exp-uas-corr}. It states that a signature over any arbitrary message
-and valid function \feval \todo{Should we explicitly check \feval in the game?
-  If so, how?},
-produced honestly by an honest user \uid with credential \cid, is accepted by
-\Verify. Moreover, upon issuance of the credential \cid, it must have met the
-conditions set by \fissue. Similarly, the value returnd by \Inspect must be
-accepted by \Judge, and must match the output of applying \finsp on \feval, the
-credential, user key, and message.
+and valid function \feval produced honestly leveraging credential set \scid,
+owned by user \uid, is accepted by \Verify. Moreover, all the credentials in
+\scid met the conditions set by the corresponding \fissue defined by the issuer
+which issued each credential. Similarly, the output \yeval of \feval matches the
+value produced by \Sign alognside with \sig; and the value produced by \Inspect
+is accepted by \Judge, and matches the output of applying \finsp on \yeval, the
+credentials, user key, and message.
+
+\begin{definition}{(Correctness of \UAS)}
+  An \UAS scheme is correct if, for any p.p.t. adversary $\adv$, \ExpCorrect
+   outputs 1 with negligible probability.
+\end{definition}
 
@@
     \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
-    \sig \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
+    \pcif \feval \notin \famfeval: \pcreturn 0 \\
+    \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
+    (\sig,\yeval) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
     \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = 0: \pcreturn 1~
@@
     \pccomment{Some \cid should not have been issued} \\
-    % \pcif \CorrectEval(\uid,\cid,\msg,\feval)
-    % = 0: \pcreturn 1~
-    % \pccomment{\msg should not have been signed} \\
-    \pcif \CorrectEvalInspect(\oid,\uid,\scid,\msg,\sig,\feval) = 0: \pcreturn 1~
-    \pccomment{The combination of evaluation and inspection is wrong} \\
+    \pcif \CorrectEval(\oid,\uid,\scid,\msg,\sig,\yeval,\feval) = 0: \pcreturn 1~
+    \pccomment{The result of evaluation is wrong} \\
+    \pcif \CorrectInspect(\oid,\uid,\scid,\msg,\sig,\yeval,\feval) = 0: \pcreturn 1~
+    \pccomment{The result of inspection is wrong} \\
     \pcreturn 0 \\
@@
 
-  % \procedure{$\CorrectEval(\uid,\cid,\msg,\feval)$}{
-  %   \pcif \feval(\PUBUK[\uid],\CRED[\cid],\msg) = 0: \pcreturn 0 \\
-  %   \pcreturn 1 \\
-  % }
+  \procedure{$\CorrectEval(\oid,\uid,\scid,\msg,\sig,\yeval,\feval)$}{%
+    \pcif \feval(\UK[\uid],\CRED[\scid],\msg) \neq \yeval: \pcreturn 0 \\
+    \pcreturn 1 \\
+  }
 
-  \procedure{$\CorrectEvalInspect(\oid,\uid,\scid,\msg,\sig,\feval)$}{
+  \procedure{$\CorrectInspect(\oid,\uid,\scid,\msg,\sig,\yeval,\feval)$}{
     \textrm{Parse}~\OK[\oid]~\textrm{as}~((\cdot,\finsp^\gid),\cdot) \\
     \pccomment{\sig cannot be inspected} \\
-    \pcif \Inspect(\PRVOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = \bot:
+    \pcif \Inspect(\PRVOK[\oid],\PUBIK[\scid],\sig,\yeval,\msg,\feval) = \bot:
     \pcreturn 0 \\
-    \pccomment{The produced $(\y,\iproof)$ pair is rejected by \Judge
-      % \todo{This must be conditioned on \feval = 0!}
-    } \\
-    \pcif (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\PUBIK[\scid],\sig,
-    \msg,\feval) \land
-    \Judge(\PUBOK[\oid],\PUBIK[\scid],\y,\iproof,\sig,\msg,\feval) = 0: \\
+    \pccomment{The produced $(\y,\iproof)$ pair is rejected by \Judge} \\
+    \pcif (\yinsp,\iproof) \gets \Inspect(\PRVOK[\gid],\PUBIK[\scid],\sig,
+    \msg,\feval)~\land \\
+    \hspace*{10pt}
+    \Judge(\PUBOK[\oid],\PUBIK[\scid],\y,\iproof,\sig,\yeval,\msg,\feval) = 0: \\
     \pcind \pcreturn 0 \\
-    \pccomment{\y is the wrong value} \\
-    \pcif \y \neq \finsp^\gid(\feval(\PUBUK[\uid],\CRED[\scid],\msg),
-    \PUBUK[\uid],\CRED[\scid],\msg)):
+    \pccomment{\yinsp is the wrong value} \\
+    \pcif \yinsp \neq \finsp^\gid(\yeval,\UK[\uid],\CRED[\scid],\msg)):
     \pcreturn 0 \\
@@
 In our notion of anonymity for \UAS, we need to merge the previous constraints.
-Furthermore, a key difference with group signatures is that the game requires
-the adversary to output credential identifiers, rather than user identifiers.
-Specifically, this means that the adversary may actually output two credentials
-that belong to the same user. Therefore, in some sense, the anonymity we get is
-more general than that of group signatures. Moreover, in order to prevent
-trivial wins by the adversary, we have to restrict that the challenge signatures
-belong to a group that has been ``programmed'' with the same evaluation and
-inspection functions, which is again a generalization over group signatures,
-as discussed in the sequel. Other than this, the overall approach is the same:
-the adversary picks two honestly obtained credentials, and one of them (set
-by the $b$ value defining the $anon-b$ game) is used to program the \CHALb
-oracle. The formal specification of the anonymity game is
-given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,\CU\rbrace
-\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,
-\INSPECT)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace
-\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\INSPECT,\CHALb)$
+In order to prevent trivial wins by the adversary, we have to restrict that the
+evaluation function outputs the same value for both user-credentials pairs. Very
+interestingly, since our inspection functionality does not (necessarily) output
+the identity of the signer, \uline{we can even allow the adversary to
+  inspect challenge signatures, as long as they produce the same output upon
+  inspection}. Other than this, the overall approach is similar: as in group
+signatures and anonymous credentials, the adversary picks two pairs of honest
+users and credential sets. We also require the adversary to pick an evaluation
+function and an inspector (hence, an inspection function). Then, the
+user-credential pair defind by the value of $b$ (unknown to the adversary) is
+used to program the \CHALb oracle. The formal specification of the anonymity
+game is given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,
+\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,
+\WREG,\SIGN,\INSPECT)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,
+\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\INSPECT,\CHALb)$
 
@@
      \parm \gets \Setup(1^\secpar) \\
-     (\cscid_0,\cscid_1,\status) \gets \adv^{\Oanonc}(\choose,\parm) \\
+     (\cuid_0,\cscid_0,\cuid_1,\cscid_1,\feval,\status) \gets \adv^{\Oanonc}
+     (\choose,\parm) \\
+     \pcif \feval \notin \famfeval: \pcreturn \bot \\
      b^* \gets \adv^{\Oanong} (\guess,\status) \\
@@
 
-\paragraph{Unforgeability.}
+Note that we could actually remove the requirement that the evaluation function
+has to produce the same output on both challenge user-credentials pairs.
+However, by doing so, we would force all constructions to maintain private the
+output of \feval. We opt not to require that, though, as it directly allows
+our model to cover interesting use cases -- such as restricting to selective
+disclosure, or privacy-preserving variants of functional signatures \todo{check
+  the latter, and perhaps expand}.
+
+\paragraph{Unforgeability.} In anonymous credentials, unforgeability requires
+that no adversary can succeed in a credential presentation for attributes that
+are not contained in a legitimately issued credential (set) it controls. Note
+that, for this, assuming honest issuers is essential as, otherwise, the
+adversary can get credentials on any attribute set it wants.
+%
+The somehow equivalent property in group signatures, inasmuch it also requires
+honest issuers, is traceability. It captures the security of the
+inspection-related functionality (e.g., \Inspect and \Judge) over signatures
+that produced by potentially malicious signers, in the presence of an honest
+issuer. In a nutshell, it ensures that every signature accepted by
+the verification algorithm must have been created by a user who joined the
+group, and that the result of \Inspect (and thus, \Judge) over such a valid
+signature is consistent with its signer. With conventional opening, this is
+essentially checked by requesting the adversary to produce a signature,
+obtaining -- via open -- the ``identifier'' of the user who produced the
+signature. Schemes
+that do not have conventional opening resort to more subtle techniques, like
+matching keys extracted during join transcripts, with keys used for signing
+(see, e.g., \cite{dl21}). Thus, even though for more subtle reasons (the need
+for reliable bookkeeping during joins) than for anonymous credentials, honest
+issuers are required for traceability of group signatures too.
+
+In \UAS schemes, users can prove claims over the attributes they own
+-- attested via obtained credentials -- through the \feval function. Thus, we
+need to capture the same unforgeability requirement as in anonymous credentials.
+Namely, that the \yeval value returned by \Sign along with the signature,
+matches the expected one from the specified \feval function.
+On the other hand, the inspection capabilities of \UAS schemes also call for a
+traceability-like property. However, note that, as opposed to group signatures,
+$\langle \Obtain,\Issue \rangle$ protocols are over credentials rather than
+users -- although, ultimately, credentials must be owned by some user.
+However, we need to ensure that all signatures have been produced by credentials
+that have been obtained from an (honest) issuer. Furthermore, since \Inspect
+does not return the actual identity of the signer, but a function \finsp of it
+(and other arguments), we need to make sure that the output of \Inspect
+matches the output of \finsp. As in group signatures with non-conventional open,
+we resort to extraction-based techniques. All this is captured via \ExpForgeSign
+in \figref{fig:exp-uas-unfor-issue}. Therein, the adversary is challenged to
+produce a signature $(\sig,\yeval)$ over message \msg and for evaluation
+function \feval; as well as the identifiers for the inspector (\oid) and
+credential issuers (\siid) used to compute the signature. As in traditional
+group signatures, the adversary wins if the signature is accepted by \Verify,
+yet \Inspect or \Judge fail. Then, the game extracts the user key and
+credentials used to produce the signature. From it, the game checks if the
+output of \feval matches the \yeval value produced by the adversry -- this
+mimics the behaviour of unforgeability in anonymous credentials. Finally, the
+game also checks that the output of \Inspect (even if accepted by \Judge)
+matches the output of \finsp. If there is any mismatch in the last two checks,
+the adversary wins the game.
+
+\UAS schemes include yet another generalisation that requires unforgeability-like
+security, though. Concretely, the issuance function \fissue. Thus, an \UAS
+scheme needs to make sure that no credential is issued unless its corresponding
+request meets the defined issuance policy. From the point of view of group
+signatures, this may seem redundant. After all, if all valid signatures produce
+consistent evaluation and inspection results, given the employed user key,
+credentials, and signed message, the notion of traceability seems to be
+satisfied. However, from the point of view of anonymous credentials, an attacker
+being able to obtain a credential, even though it does not meet the required
+conditions to have it issued, is clearly problematic: it would allow to prove
+claims over attributes it does not really ``own'' (even if the output of \Sign
+and \Inspect are consistent with the values returned by \feval and \finsp, and
+the credential was obtained via an $\langle \Obtain,\Issue \rangle$). To capture
+this, we define the \ExpForgeIssue experiment. In the experiment, the adversary
+is challenged to produce a credential identifier that must be associated to an
+existing $\langle \Obtain,\Issue \rangle$ interaction -- thus, the corresponding
+\trans entry must exist (which we can check, as the issuer is honest).
+The adversary wins if, either the extraction process fails, or the extracted
+user secret key and credentials make the corresponding issuance function fail.
+
+For both \ExpForgeIssue and \ExpForgeSign, the adversary is given access to the
+oracle set $\Oforgeissue = \Oforgesign \gets \lbrace\HU,\CU\rbrace\GEN,\IGEN,
+\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\INSPECT$.
 
@@
       \parm \gets \Setup(1^\secpar) \\
-      (\oid,\siid,\sig,\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
-      \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\msg,\feval) \in \SIG[\uid]: \pcreturn 0 \\
-      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\msg,\feval) = 0: \pcreturn 0 \\
-      (\y,\iproof) \gets \Inspect(\PRVOK[\oid],\siid,\trans,\sig,\msg) \\
-      \pcif \y = \bot \lor \iproof = \bot \lor       
-      \Judge(\PUBOK[\oid],\PUBIK[\siid],\y,\iproof,\sig,\msg,\feval) = 0: \pcreturn 0 \\
-      (\usk,\scred) \gets \ExtractSign(\oid,\siid,\sig,\msg,\feval) \\
-      %\pcif \usk = \bot \lor \scred = \bot: \pcreturn 1 \\
-      \pcif \finsp(\feval(\usk,\scred,\msg),\usk,\scred,\msg)
-      \neq \y: \pcreturn 1 \\
-      %\text{\todo{Need to check \feval independently here?}} \\
+      (\oid,\siid,\sig,\yeval,\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
+      \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in
+      \SIG[\uid]: \pcreturn 0 \\
+      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\yeval,\msg,\feval) = 0:
+      \pcreturn 0 \\
+      (\yinsp,\iproof) \gets \Inspect(\PRVOK[\oid],\siid,\sig,\yeval,\msg) \\
+      \pcif \yinsp = \bot \lor \iproof = \bot \lor       
+      \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg,\feval)
+      = 0: \pcreturn 0 \\
+      (\usk,\scred) \gets \ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \\
+      \pcif \feval(\usk,\scred,\msg) \neq \yeval: \pcreturn 1 \\
+      \pcif \finsp(\yeval,\usk,\scred,\msg) \neq \yinsp: \pcreturn 1 \\
       \pcreturn 0
@@
 
-\paragraph{Traceability.} %
-% Traceability is one of the unforgeability-related properties in group
-% signatures. It captures that any signature accepted by \Verify needs to open
-% to one of the users that joined the group. While there is no traceability notion
-% in anonymous credentials, it is natural to map it to their unforgeability
-% property; if only because both require the issuer to be honest. Unforgeability
-% in anonymous credentials typically ensures that no adversary can get a verifier
-% to accept a credential presentation requiring a set of attributes that is not
-% contained in one of the credentials controlled by the adversary.
-
-% Our notion of traceability for \UAS is inspired by both. First, we restrict to
-% signatures that are accepted by \Verify. For any such signature, \Inspect has to
-% create a valid output (i.e., must not abort). The output of \Inspect has to be
-% accepted by \Judge too. Moreover, there must exist one user (either honest or
-% corrupt) who used his public key to obtain one or more credentials that allowed
-% him to produce a signature which, once inspected, returns \y.
-In group signatures, traceability ensures that, in the presence of an honest
-issuer, every signature accepted by the verify algorithm must have been created
-by a user who joined the group.  With conventional opening, this is essentially
-checked by requesting the adversary to produce a signature, opening it, and
-checking whether or not it comes from a group member; i.e., this ensures that,
-as long as there are verifiable inspections, inspection cannot be forged in the
-presence of an honest issuer.
+\begin{definition}{(Unforgeable issuance of \UAS)}
+  We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
+  $\AdvForgeIssue=\Pr\lbrack\ExpForgeIssue(1^\secpar)=1\rbrack$.
   %
-The somehow equivalent property in anonymous credentials is unforgeability. It
-requires that, again in the presence of an honest issuer, no adversary can
-succeed in a credential presentation for attributes (or predicates of them) that
-are not contained in a legitimately issued credential it controls. In other
-words, that the evaluation of the credential attributes cannot be forged.
-%
-Both notions have an equivalent in \UAS. That is, we need to ensure that, in the
-presence of an honest issuer, no signature accepted by \Verify can result in a
-wrong inspection, nor it can have been obtained by a wrong evaluation of some
-credential. Note, however, that \UAS offer the adversary yet another way to
-break traceability/unforgeability. Namely, an adversary can attempt to
-illegitimately obtain a credential that later enables it to produce untraceable
-signatures; i.e., signatures that evaluate correctly, or for which \Inspect
-returns the appropiate value, yet the adversary should not have been able to
-obtain a credential that allowed it to produce such signatures. Our notion of
-traceability/unforgeability thus challenges the adversary to produce a signature
-that breaks any of those conditions. The formal
-definition of the traceability experiment is given in \figref{fig:exp-uas-trace},
-where $\Otrace \gets \lbrace\HU,\CU\rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,
-\ISSUE,\RREG,\SIGN,\INSPECT$.
-
-% \begin{figure}[htp!]
-%     \procedure{$\ExpTrace(1^\secpar)$}{%
-%       \parm \gets \Setup(1^\secpar) \\
-%       (\sgid,\sig,\msg,\feval) \gets \adv^{\Otrace}(\parm) \\
-%       \pcif \Verify(\GK[\sgid],\sig,\msg,\feval) = 0: \pcreturn 0 \\
-%       (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\sgid,\trans,\sig,\msg) \\
-%       \pcif \y = \bot \lor \iproof = \bot \lor       
-%       \Judge(\GK[\sgid],\y,\iproof,\sig,\msg,\feval) = 0: \pcreturn 0 \\
-%       \pcif \EvalForge(\sgid,\sig,\msg,\feval) = 1 \lor
-%       \IssueForge() = 1: \pcreturn 1 \\
-%       \pcreturn 0 \\
-%       % \pcind \pcind \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
-%       % \pcind \pcind \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
-%       %   $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\      
-%       % \pcind \pcind \pcreturn 1 \\      
-%     }
-
-%     \procedure{$\EvalForge(\sgid,\sig,\msg,\feval)$}{%
-%       (\uid,\usk,\scred) \gets \ExtractSign(\sgid,\sig,\msg,\feval) \\
-%       \pcif \uid = \bot \lor \usk = \bot \lor \scred = \bot: \pcreturn 1 \\
-%       \pcif \finsp(\feval(\PUBUK[\uid],\scred,\msg),\PUBUK[\uid],\scred,\msg)
-%       \neq \y: \pcreturn 1 \\      
-%     }
-
-%     \procedure{$\IssueForge()$}{%
-%       \pcfor \cred \in \scred: \\
-%       \pcind \scred' \gets \ExtractIssue()
-%       \pcif \exists \cred \in \scred~\st~
-%       \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0 \\
-%       \pcind \textrm{where $\CRED[\cid]=\cred$ and
-%         $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\      
-%       \pcind \pcreturn 1 \\      
-%     }
-
-%     \procedure{$\ExtractSign(\sig,\msg,\feval,\sgid)$}{%
-%       \pcif \exists \cred,\cred' \in \scred~\st~\OWNR[\cred] \neq \OWNR[\cred']:
-%       \pcreturn (\bot,\bot,\bot) \\
-%       \pcif \nexists \uid~\st~\SUK[\uid] = \usk: \pcreturn (\bot,\bot,\bot) \\
-%       \pcif \uid \neq \OWNR[\scred]: \pcreturn (\bot,\bot,\bot) \\
-%       \todo{Return the \uid, \usk and \scred used to produce \sig} \\      
-%     }
-
-%     \procedure{$\ExtractIssue()$}{%
-%       \todo{Return the \scred used to fetch \cred} 
-%     }
-
-%     % \procedure{$\EvalForge(\gid,\sig,\msg,\feval)$}{%
-%     %   \pcif \exists \uid~\st~\Identify(\uid,\sig) = 1~\land \\
-%     %   \pcind \pccomment{\uid does not own a \cred that satisfies \feval...} \\
-%     %   \pcind (\nexists \cred \in \CRED[\uid]~\st~
-%     %   \feval(\PUBUK[\uid],\cred,\msg) \neq 0 ~\lor \\
-%     %   \hspace*{13pt} \pccomment{... or \uid does, but \cred was itself obtained
-%     %     fraudulently} \\
-%     %   \hspace*{13pt} (\exists \cred \in \CRED[\uid]~\st~
-%     %   \feval(\PUBUK[\uid],\cred,\msg) \neq 0~\land \\
-%     %   \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
-%     %   \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
-%     %     $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\
-%     %   \pcind \pcreturn 1 \\
-%     %   \pcelse \pcreturn 0 \\
-%     % }
-
-%     \procedure{$\EvalInspectForge(\gid,\sig,\msg,\feval)$}{%
-%       \pcfor \gid \in \sgid: \\
-%       \pcind \pccomment{\sig cannot be inspected} \\
-%       \pcind \pcif \Inspect(\PRVOK[\gid],\sgid,\trans,\sig,\msg) \neq \bot~\lor \\
-%       \pcind \pcind \pccomment{A valid transcript exists, but ...} \\
-%       \pcind \pcind \Inspect(\PRVOK[\gid],\sgid,\trans,\sig,\msg) =
-%       (\y,\iproof)~\land (\\
-%       \pcind \pcind \pcind \pccomment{... the proof is rejected by \Judge ...} \\
-%       \pcind  \pcind \pcind \Judge(\GK[\sgid],\y,\iproof,\sig,\msg,\feval) = 0~\lor \\
-%       \pcind  \pcind \pcind \Judge(\GK[\sgid],\y,\iproof,\sig,\msg,\feval) = 1
-%       \land \exists \uid~\st~\Identify(\uid,\sig) = 1 \land \\
-%       % \pcind \pcind \pcind \pccomment{... or \uid does not own a \cred for which
-%       %   \finsp outputs \y} \\
-%       % \pcind \pcind \pcind \nexists \cred \in \CRED[\uid]~\st~
-%       % \y = \finsp(\feval(\PUBUK[\uid],\cred,\msg),
-%       % \PUBUK[\uid],\cred,\msg)~\lor \\
-%       \pcind \pcind \pcind \pccomment{... or \uid does, but \cred was itself obtained
-%         fraudulently} \\
-%       \pcind \pcind \pcind (\exists \cred \in \CRED[\uid]~\st~
-%       y = \finsp(\feval(\PUBUK[\uid],\cred,\msg),
-%       \PUBUK[\uid],\cred,\msg)~\land \\
-%       \pcind \pcind \pcind \pcind \fissue(\PUBUK[\uid],\attrs^\cid,\scred^\cid) = 0, \\
-%       \pcind \pcind \pcind \pcind \textrm{where $\CRED[\cid]=\cred$ and
-%         $(\attrs^\cid,\scred^\cid) \gets \ATTR[\cid]$})): \\      
-%       \pcind \pcind \pcreturn 1 \\      
-%       \pcreturn 0
-%     }
-%   \caption{Traceability experiment for \UAS schemes.}
-%   \label{fig:exp-uas-trace}
-% \end{figure}
-
-\begin{definition}{(Traceability of \UAS)}
-  We define the advantage \AdvTrace of $\adv$ against \ExpTrace as
-  $\AdvTrace=\Pr\lbrack\ExpTrace(1^\secpar)=1\rbrack$.
-  %
-  A \UAS scheme satisfies traceability if, for any p.p.t. adversary $\adv$,
-  \AdvTrace is a negligible function of $1^\secpar$.
+  A \UAS scheme has unforgeable issuance if, for any p.p.t. adversary $\adv$,
+  \AdvForgeIssue is a negligible function of $1^\secpar$.
 \end{definition}
 
-\paragraph{Discussion on the generality of traceability in \UAS schemes.} %
+\begin{definition}{(Unforgeable signing of \UAS)}
+  We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
+  $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
+  %
+  A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
+  \AdvForgeSign is a negligible function of $1^\secpar$.
+\end{definition}
+
+For short, we say that an \UAS scheme that has both unforgeable issuance and
+signing, is an unforgeable \UAS scheme.
+
+\paragraph{Discussion on the generality of unforgeability in \UAS schemes.} %
+\todo{Re-check and re-write as needed}.
 The notion of traceability we present for \UAS is strictly more general than
@@
 Non-frameability variants are a core unforgeability-type property in group
-signatures. However, no
-similar property is modeled for anonymous credentials (\todo{see the discussion
-  in \secref{sec:introduction} for further detail}). It is a quite strong
-property, as it must be ensured even in the presence of dishonest issuer and
-opener. Intuitively, it prevents the adversary from creating a signature that
-frames an honest user. Depending on the inspection capabilities of the scheme,
+signatures. However, no similar property is modeled for anonymous credentials
+(\todo{see the discussion in \secref{sec:introduction} for further detail. Also,
+consider conditional anonymity notions pointed to by Elizabeth}). It is a quite
+strong property, as it must be ensured even in the presence of dishonest issuer
+and opener. Intuitively, it prevents the adversary from creating a signature
+that can be (even in some generic sense) associated to an honest user who did
+not produce it. Depending on the inspection capabilities of the scheme,
 this framing could be done in different ways; i.e., by convincing third parties
@@
 The notion of non-frameability in \UAS schemes is unavoidably more subtle than
-in group signatures, though. To see this, we note that, by allowing any
-arbitrary inspection function \finsp to be used, it can be perfectly valid to
-have a signature produced by a corrupted user output the same \y value upon
-inspection than the one that \finsp outputs when inspecting a signature by an
-honest user. As a concrete example, imagine an inspection function that returns
-the banking account number (or cryptocurrency address) to be used to request
-payment of a fine. In this example, a corrupted user and an honest user could
-both have delegated this to some agency\footnote{\todo{Maybe, come up with a
-    better example. How about spam filters that apply some sort of classification
-    engine? \finsp could be this engine, and emails by many different users could
-    be classified just as ``Spam'' or ``Not spam''}}, so it makes perfect sense
-that the inspection function returns the same value for both users.
+in group signatures, though. To see this, we note that, by allowing arbitrary
+evaluation and inspection functions to be used, it can be perfectly valid to
+have a signature produced by a corrupted user output the same \yeval or \yinsp
+values than the one that \feval or \finsp output when evaluating or inspecting
+a signature by an honest user. As a concrete example, imagine an inspection
+function that returns the banking account number (or cryptocurrency address) to
+be used to request payment of a fine. In this example, a corrupted user and an
+honest user could both have delegated this to some agency\footnote{\todo{Maybe,
+    come up with a better example. How about spam filters that apply some sort
+    of classification engine? \finsp could be this engine, and emails by many
+    different users could be classified just as ``Spam'' or ``Not spam''}}, so
+it makes perfect sense that the inspection function returns the same value for
+both users.
 %
-Thus, in \UAS schemes, we must be more subtle, by necessity. Note that we cannot
-just require that no adversary can produce a signature for which inspection
-returns the same value as it would for a signature honestly generated by an
-uncorrupted user. This is again the case since inspection may be non-injective,
-which means that inspection of a signature by some corrupted user may
-legitimately produce the same value as that of an honest user. Thus, we need
-to further refine the definition by requiring that (i) no adversary can produce
-a signature that is recognized (via \Identify) as originating from an honest
-user \uid, (ii) who owns a credential that makes \finsp return a valid \y value
-(i.e., generated by \Inspect along with a proof, and accepted by \Judge), (iii)
-without having queried the \SIGN oracle before. This non-frameability property
-for \UAS schemes is formally defined in \figref{fig:exp-uas-frame}, where
+More generally, since the issuer is dishonest in non-frameability properties
+and, in \UAS, the value produced by \Inspect may depend on the attributes
+included in user credentials, the adversary may even be able to just produce
+``legitimate'' inspections that output any desired value.
+
+Thus, we again need to resort to extraction techniques. In the non-frameability
+definition for \UAS, given in experiment \ExpNonframe in
+\figref{fig:exp-uas-frame}, the adversary is challenged to produce a signature
+and inspection proof that accepted by \Verify and \Judge, respectively. From
+the signature, we then extract the secret key of the signer, and match it
+against the secret keys of the honest users. The adversary wins if there is a
+match (and the signature, of course, has not been queried to \SIGN). In the
+game, the adversary has access to the oracles in 
 $\Oframe \gets \lbrace\HU,\CU\rbrace\GEN,
@@
     \parm \gets \Setup(1^\secpar) \\
-    (\oid,\siid,\sig,\msg,\feval,\y,\iproof) \gets \adv^{\Oframe}(\parm) \\
-    \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\msg,\feval) \in \SIG[\uid]: \pcreturn 0 \\
-    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\msg,\feval) = 0: \pcreturn 0 \\
-    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\y,\iproof,\sig,\msg) = 0: \pcreturn 0 \\
-    (\usk,\scred) \gets \ExtractSign(\oid,\siid,\sig,\msg,\feval) \\
-    %\pcif \usk = \bot \lor \scred = \bot: \pcreturn 1 \\
+    (\oid,\siid,\sig,\yeval,\msg,\feval,\yinsp,\iproof) \gets
+    \adv^{\Oframe}(\parm) \\
+    \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in \SIG[\uid]:
+    \pcreturn 0 \\
+    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\yeval,\msg,\feval) = 0:
+    \pcreturn 0 \\
+    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg) = 0:
+    \pcreturn 0 \\
+    (\usk,\scred) \gets \ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \\
     \pcif \exists \uid \in \HU~\st~\PRVUK[\uid] = \usk: \pcreturn 1 \\
@@
 \end{figure}
-
-\commentwho{Jesus}{Current intuition of non-frame: Since issuer is corrupt,
-  basically \adv~ can create signatures that open to any value. All we can
-  hope for is that no forgery can exist that ``extracts'' to an honest user.}
-
-% \begin{figure}[htp!]
-%   \procedure{$\ExpNonframe(1^\secpar)$}{%
-%     \parm \gets \Setup(1^\secpar) \\
-%      (\gid,\sig,\msg,\feval,\y,\iproof) \gets \adv^{\Oframe}(\parm) \\
-%      \pcreturn 1~\pcif \Verify(\GK[\gid],\sig,\msg,\feval) = 1 \land
-%      \Judge(\GK[\gid],\y,\iproof,\sig,\msg) = 1~\land \\
-%      \pcind \pccomment{\adv~did not query \SIGN to get \sig, yet \sig originates
-%        from an honest \uid, owning a credential that makes \finsp
-%        evaluate to \y} \\
-%      \pcind \exists \uid \in \HU~\st~\Identify(\PRVUK[\uid],\sig) = 1 \land
-%      (\cdot,\sig,\msg,\cdot) \notin \SIG[\uid]~\land\\
-%      \pcind \exists \cred \in \CRED[\uid]~\st~
-%      \finsp(\feval(\PUBUK[\uid],\cred,\msg),\PUBUK[\uid],\cred,\msg) = \y \\
-% %     \pccomment{\todo{I don't think we can give any assurance about \feval here,
-% %         given that issuers are corrupt. But still, think about it.}} \\
-%      \pcreturn 0 \\
-%      kk from former trace \\
-%      \pcind \pcind \pcind \pccomment{... or \uid does not own a \cred for which
-%        \finsp outputs \y} \\
-%      \pcind \pcind \pcind \nexists \cred \in \CRED[\uid]~\st~
-%      \y = \finsp(\feval(\PUBUK[\uid],\cred,\msg),
-%      \PUBUK[\uid],\cred,\msg)~\lor \\     
-%   }
-%   \caption{Non-frameability experiment for \UAS schemes.}
-%   \label{fig:exp-uas-frame}
-% \end{figure}
 
@@
 \paragraph{Discussion on the generality of non-frameability in \UAS schemes.} %
+\todo{Re-check and re-write as needed}.
 Anonymous credentials do not have non-frameability property and, thus, it is

### 2022-04-12 prism-backend/research/gsac/construction-uas.tex
Slightly refined UAS model. Working on generic construction.

@@
 
-\subsubsection{Commitments}
+\paragraph{Vector Commitment schemes.} %
+Defined as a tuple $(\CSetup,\CCommit)$. Algorithm $\Cparm \gets
+\CSetup(\Csecpar)$ produces the parameters for committing to values. $\Ccom
+\gets \CCommit(\Cparm, \msgset; r)$ produces a commitment \Ccom over a set of
+messages \msgset, from which we may omit randomness $r$. \todo{Informally define
+  hiding and binding, leaving formal definitions to the appendix.}
 
-\todo{Introduce, and summarise correctness and security.}
+\paragraph{Encryption.} %
+Defined as a tuple $(\ESetup,\EKeyGen,\EEnc,\EDec)$. Algorithm $\Eparm \gets
+\ESetup(\Esecpar)$ produces public parameters for the other algorithms.
+$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$ generates the encryption-decryption key
+pair, algorithm $\Ec \gets \EEnc(\Eek,\msg)$ encrypts message \msg with
+encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\Edk,
+\Ec)$ decrypts ciphertexts using decryption key \Edk. \todo{Informally define
+  security properties we'll need.}
 
-\begin{description}
-  \item[$\Cparm \gets \CSetup(\Csecpar).$]
-  \item[$(\Ccom,\Copn) \gets \CCommit(\Cparm,\msg).$] 
-  \item[$\Cproof \gets \CProve(\Ccom,\Copn,\msg).$]    
-  \item[$1/0 \gets \CVerify(\Cproof,\Ccom).$] 
-\end{description}
+\paragraph{Digital Signatures.} %
+Defined as a tuple $(\SSetup,\SKeyGen,\SSign,\SVerify)$. Algorithm $\Sparm \gets
+\SSetup(\Ssecpar)$ produces public parameters for the other algorithms.
+$(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$ generates the verification-signing key
+pair, algorithm $\Ssig \gets \SSign(\Ssk,\msg)$ signs message \msg with
+signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\Svk,
+\Ssig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
+verification key \Svk. \todo{Informally define security properties we'll need.}
 
-\subsubsection{Signatures with Proofs of Knowledge}
+\paragraph{Non-Interactive Zero-Knowledge.} %
+We use non-interactive zero-knowledge proofs of knowledge (NIZK), in the CRS
+model \needcite. Informally, a NIZK scheme over an NP relation \NIZKRel is
+defined as a tuple $(\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel,
+\NIZKVerify^\NIZKRel)$. Algorithm $\NIZKcrs \gets \NIZKSetup^\NIZKRel
+(\NIZKsecpar)$ produces the common reference string \NIZKcrs. $\NIZKproof/\bot
+\gets \NIZKProve^\NIZKRel(\NIZKcrs,\NIZKw,\NIZKx)$ creates a NIZK proof of
+knowledge of witness \NIZKw for \NIZKx such that $(\NIZKw,\NIZKx) \in \NIZKRel$.
+$1/0 \gets \NIZKVerify^\NIZKRel(\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof.
+\todo{Informally define security properties we'll need.}
 
-As put forward in \cite{cl02}, a generic way to build anonymous credentials
-requires a digital signature scheme with efficient protocols for proving
-knowledge of a digital signature, and signing committed values. This approach
-also has much in common with the Sign-Randomize-Prove (SRP) approach to build
-group signatures \needcite. Thus, even a priori, it seems a good core component
-to build something that is actually in betwween GS and AC. In the sequel, we use
-\RS to refer to schemes of this type, which must provide the functionality
-specified by the following syntax:
+\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
+We use signature schemes that allow signing messages, or commitments to messages,
+in blocks, and are compatible with (efficient) proof systems over the produced
+signature and signed (commitments to) messages. For this purpose, we define such
+schemes as a tuple $(\SBCMSetup,\SBCMKeyGen,\SBCMSign,\SBCMVerify)$. Algorithm
+$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$ produces the public parameters for the
+scheme. $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$ produces a
+verification-signing key
+pair. Algorithm $\SBCMsig \gets \SBCMSign(\SBCMsk,\Ccom,\msgset)$ produces a
+signature over a set of committed messages \Ccom and a set of messages
+\msgset, where either \Ccom or \msgset may be empty. $1/0 \gets
+\SBCMVerify(\SBCMvk,\SBCMsig,\overline{\msgset})$ verifies a signature \SBCMsig
+over message set $\overline{\msgset}$, which must contain both the messages that
+were signed as commitments as well as those signed in ``the clear''. In
+addition, the produced signatures must be compatible with (efficient) NIZK
+proofs of knowledge of a signature, and of (arbitrary) claims over the signed
+(committed) messages.
+\todo{Informally define security properties we'll need.}
 
-\begin{description}
-\item[$(\RSvk,\RSsk) \gets \RSKeyGen(\RSsecpar,\RSlen)$.] Generates a key pair,
-  consisting on the signig key \RSsk and the verification key \RSvk, which
-  support sigining blocks of up to \RSlen messages.
-\item[$\RSsig \gets \RSSign(\RSsk,\msgset,\cmsgset)$.] Given signing key \RSsk,
-  a set of messages \msgset, and a set of commitments to messages, where
-  $|\msgset + \cmsgset| \le \RSlen$, returns a signature \RSsig.
-\item[$1/0 \gets \RSVerify(\RSvk,\RSsig,\amsgset)$.] Given a verification key
-  \RSvk, a signature \RSsig, supposedly over set of messages \amsgset which may
-  contain commitments to messages, returns $1$ or $0$. \todo{Assume that, within
-    \amsgset, it is possible to know which are commitments and wich plain
-    messages?}
-\item[$\RSproof/\bot \gets \RSProve(\RSsig,\amsgset,\D)$.] Given signature
-  \RSsig, over set of messages (and commitments to messages) \amsgset, out of
-  which those indexed by set \D are to be revealed, creates a proof of knowledge
-  \RSproof of \RSsig.
-\item[$1/0 \gets \RSProveVer(\RSproof,\msgset)$.] Given a proof of knowledge of
-  a signature over a set of messages, which includes \msgset, returns $1$ or
-  $0$.
-\end{description}
+% \subsubsection{Commitments}
 
-\todo{Summarise correctness and security.}
+% \todo{Introduce, and summarise correctness and security.}
 
-\subsubsection{Digital Signatures}
+% \begin{description}
+%   \item[$\Cparm \gets \CSetup(\Csecpar).$]
+%   \item[$(\Ccom,\Copn) \gets \CCommit(\Cparm,\msg).$] 
+%   \item[$\Cproof \gets \CProve(\Ccom,\Copn,\msg).$]    
+%   \item[$1/0 \gets \CVerify(\Cproof,\Ccom).$] 
+% \end{description}
 
-\todo{Introduce, and summarise correctness and security.}
+% \subsubsection{Signatures with Proofs of Knowledge}
 
-\begin{description}
-\item[$(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$.]
-\item[$\Ssig \gets \SSign(\Ssk,\msg)$.]
-\item[$1/0 \gets \SVerify(\Svk,\Ssig,\msg)$.]  
-\end{description}
+% As put forward in \cite{cl02}, a generic way to build anonymous credentials
+% requires a digital signature scheme with efficient protocols for proving
+% knowledge of a digital signature, and signing committed values. This approach
+% also has much in common with the Sign-Randomize-Prove (SRP) approach to build
+% group signatures \needcite. Thus, even a priori, it seems a good core component
+% to build something that is actually in betwween GS and AC. In the sequel, we use
+% \RS to refer to schemes of this type, which must provide the functionality
+% specified by the following syntax:
 
-\subsubsection{Encryption}
+% \begin{description}
+% \item[$(\RSvk,\RSsk) \gets \RSKeyGen(\RSsecpar,\RSlen)$.] Generates a key pair,
+%   consisting on the signig key \RSsk and the verification key \RSvk, which
+%   support sigining blocks of up to \RSlen messages.
+% \item[$\RSsig \gets \RSSign(\RSsk,\msgset,\cmsgset)$.] Given signing key \RSsk,
+%   a set of messages \msgset, and a set of commitments to messages, where
+%   $|\msgset + \cmsgset| \le \RSlen$, returns a signature \RSsig.
+% \item[$1/0 \gets \RSVerify(\RSvk,\RSsig,\amsgset)$.] Given a verification key
+%   \RSvk, a signature \RSsig, supposedly over set of messages \amsgset which may
+%   contain commitments to messages, returns $1$ or $0$. \todo{Assume that, within
+%     \amsgset, it is possible to know which are commitments and wich plain
+%     messages?}
+% \item[$\RSproof/\bot \gets \RSProve(\RSsig,\amsgset,\D)$.] Given signature
+%   \RSsig, over set of messages (and commitments to messages) \amsgset, out of
+%   which those indexed by set \D are to be revealed, creates a proof of knowledge
+%   \RSproof of \RSsig.
+% \item[$1/0 \gets \RSProveVer(\RSproof,\msgset)$.] Given a proof of knowledge of
+%   a signature over a set of messages, which includes \msgset, returns $1$ or
+%   $0$.
+% \end{description}
 
-\todo{Introduce, and summarise correctness and security.}
+% \todo{Summarise correctness and security.}
 
-\begin{description}
-\item[$(\Eek,\Edk) \gets \EKeyGen(\Esecpar)$.]
-\item[$\Ec \gets \EEnc(\Eek,\msg)$.]
-\item[$\msg \gets \EDec(\Edk,\Ec)$.]
-\end{description}
+% \subsubsection{Digital Signatures}
 
-\subsubsection{Non-Interactive ZK Proofs of Knowledge}
+% \todo{Introduce, and summarise correctness and security.}
 
-\todo{Introduce, and summarise correctness and security.}
+% \begin{description}
+% \item[$(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$.]
+% \item[$\Ssig \gets \SSign(\Ssk,\msg)$.]
+% \item[$1/0 \gets \SVerify(\Svk,\Ssig,\msg)$.]  
+% \end{description}
 
-\begin{description}
-\item[$\NIZKcrs\gets \NIZKSetup(\NIZKsecpar)$.]
-\item[$\NIZKproof \gets \NIZKProve(\NIZKcrs,\NIZKx,\NIZKw)$.]
-\item[$1/0 \gets \NIZKVerify(\NIZKcrs,\NIZKproof,\NIZKx)$.]
-\end{description}
+% \subsubsection{Encryption}
 
-We use $\NIZK^\Lang$ to denote a \NIZK which is used to prove statements on a
-given NP language \Lang.
+% \todo{Introduce, and summarise correctness and security.}
 
-\subsubsection{Signature Proofs of Knowledge}
+% \begin{description}
+% \item[$(\Eek,\Edk) \gets \EKeyGen(\Esecpar)$.]
+% \item[$\Ec \gets \EEnc(\Eek,\msg)$.]
+% \item[$\msg \gets \EDec(\Edk,\Ec)$.]
+% \end{description}
 
-\todo{Introduce, and summarise correctness and security.}
+% \subsubsection{Non-Interactive ZK Proofs of Knowledge}
 
-\begin{description}
-\item[$\SPKproof \gets \SPKProve(\SPKmsg,\SPKx,\SPKw)$.]
-\item[$1/0 \gets \SPKVerify(\SPKproof,\SPKmsg,\NIZKx)$.]
-\end{description}
+% \todo{Introduce, and summarise correctness and security.}
 
-We use $\SPK^\Lang$ to denote an \SPK which is used to prove statements on a
-given NP language \Lang.
+% \begin{description}
+% \item[$\NIZKcrs\gets \NIZKSetup(\NIZKsecpar)$.]
+% \item[$\NIZKproof \gets \NIZKProve(\NIZKcrs,\NIZKx,\NIZKw)$.]
+% \item[$1/0 \gets \NIZKVerify(\NIZKcrs,\NIZKproof,\NIZKx)$.]
+% \end{description}
+
+% We use $\NIZK^\Lang$ to denote a \NIZK which is used to prove statements on a
+% given NP language \Lang.
+
+% \subsubsection{Signature Proofs of Knowledge}
+
+% \todo{Introduce, and summarise correctness and security.}
+
+% \begin{description}
+% \item[$\SPKproof \gets \SPKProve(\SPKmsg,\SPKx,\SPKw)$.]
+% \item[$1/0 \gets \SPKVerify(\SPKproof,\SPKmsg,\NIZKx)$.]
+% \end{description}
+
+% We use $\SPK^\Lang$ to denote an \SPK which is used to prove statements on a
+% given NP language \Lang.
 
 \subsection{Generic Construction \CUASGen}
+\label{ssec:generic-construction-uas}
+
+We use three different NP relations in our generic construction. Namely,
+$\NIZKRel_{\Issue}$ for issuance, $\NIZKRel_{\Sign}$ for signing, and
+$\NIZKRel_{\Inspect}$ for inspection. We will be defining them in the
+corresponding protocol/algorithm.
 
@@
 
-\paragraph{$\parm \gets \Setup(\secpar)$.} %
+\paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
 \begin{itemize}
-  \item Parse \secpar as $(\Csecpar,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
+\item Parse \secpar as $(\Csecpar,\NIZKsecpar,\SBCMsecpar,\Esecpar,\AttrSpace)$
 \item $\Cparm \gets \CSetup(\Csecpar)$
-  \item $\NIZKparm \gets \NIZKSetup(\NIZKsecpar)$
-  \item Return $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
+\item $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$
+\item $\Sparm \gets \SSetup(\Ssecpar)$  
+\item $\Eparm \gets \ESetup(\Esecpar)$
+\item $\NIZKcrs_{\Issue} \gets \NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$
+\item $\NIZKcrs_{\Sign} \gets \NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$
+\item $\NIZKcrs_{\Inspect} \gets \NIZKSetup^{\NIZKRel_{\Inspect}}(\NIZKsecpar)$
+\item Return $(\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
+  \NIZKcrs_{\Sign},\NIZKcrs_{\Inspect},\AttrSpace)$
 \end{itemize}
@@
 \begin{itemize}
-\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
-\item $(\RSvk,\RSsk) \gets \RSKeyGen(\RSsecpar)$  
-\item $\sig_{\fissue} \gets \RSSign(\RSsk,\fissue,\bot)$
-\item $\ipk \gets (\RSvk,\fissue,\sig_{\fissue})$
-\item $\isk \gets \RSsk$
+\item Parse \parm as $(\cdot,\SBCMparm,\Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$
+\item $(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$
+\item $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$  
+\item $\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$
+\item $\ipk \gets (\Svk,\fissue,\sig_{\fissue})$
+\item $\isk \gets \Ssk$
 \item Return $(\ipk,\isk)$
@@
 \begin{itemize}
-\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
-\item $(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$
-\item $(\Eek,\Edk) \gets \EKeyGen(\Esecpar)$
+\item Parse \parm as $(\cdot,\cdot,\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$
+\item $(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$
+\item $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$
 \item $\sig_{\finsp} \gets \SSign(\Ssk,\finsp)$
@@
 
-\paragraph{$(\upk,\usk) \gets \UKeyGen(\parm)$.} %
+\paragraph{$\usk \gets \UKeyGen(\parm)$.} %
 \begin{itemize}
-\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar)$
-\item $(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$
-\item Return $(\Svk,\Ssk)$
+\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar,\AttrSpace)$
+\item $\usk \getr \AttrSpace$
+\item Return \usk
 \end{itemize}
@@
   \langle
-  \Obtain(\usk,\attrs,\ldblbrace (gpk_i,\cred_i)\rdblbrace_{i \in \Issuers}),
-  \Issue(\isk,\upk,\attrs,\ldblbrace \gpk_i \rdblbrace_{i \in \Issuers})
+  \Obtain(\usk,\ldblbrace (\cred_i,\ipk_i)\rdblbrace_{i \in \Issuers},\attrs),
+  \Issue(\isk,\upk,\attrs,\ldblbrace \ipk_i \rdblbrace_{i \in \Issuers},\attrs)
   \rangle$.} %
-We define the NP language $\LangIss = \lbrace (\usk,
-\ldblbrace \cred_i \rdblbrace_{i \in \Issuers}): \fissue(\usk,\attrs,\ldblbrace
-(\gpk_i,\cred_i) \rdblbrace_{i \in \Issuers}) = 1 \land \Ccom = \CCommit(\usk)
-\rbrace$ \todo{\fissue needs to ensure that all {\cred}s are linked to \usk. How
-  to capture this?} The interactive protocol from a user to obtain a credential
-from an issuer of the system is as follows:
+To obtain a new credential, a user with secret key usk and credentials $\cred_i$,
+issued by issuers with public keys $\ipk_i$, requests a signature on commitments
+of both the user key and a new random credential identifier -- similarly to
+\GSAC. In addition, the user proves that the issuance function \fissue
+established by the issuer is satisfied by the $\cred_i$ credentials and its user
+secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace (\usk,
+\credid,\scred), (\Ccom,\attrs): \Ccom = \CCommit((\usk,\credid)) \land
+\fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in \scred, \usk \in \cred
+\rbrace$. \todo{Refine the notation for $\attr \in \cred$. Also, need to make
+  the {\ipk}s explicit in it.} The interactive protocol from a user to obtain a
+credential from an issuer of the system is as follows:
 
 \begin{itemize}
-\item Issuer: $\ch \gets \bin^*$; Send \ch to User.
-\item User:
-  \begin{itemize}    
-  \item $\Ccom_{\usk} \gets \CCommit(\usk)$
-  % \item $\SPKproof^{\Lang} \gets
-  %   \SPK \lbrace (\usk): \Ccom_{\usk} = \CCommit(\Cparm,\usk) \rbrace (\ch)$
-  \item $\SPKproof^{\LangIss} \gets \SPKProve^{\LangIss}
-    (\ch,(\attrs,\Ccom_{\usk}, \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers}),
-    (\usk,\ldblbrace \cred_i \rdblbrace_{i \in \Issuers}))$
-  \item Send $(\attrs,\Ccom_{\usk},\SPKproof^{\LangIss})$ to Issuer
-  \end{itemize}
-\item Issuer:
-  \begin{itemize}
-%  \item $1 \stackrel{?}{=} \SPKVerify(\SPKproof^{\Lang},\Ccom_{\upk})$
-  \item $1 \stackrel{?}{=} \SPKVerify(\SPKproof^{\LangIss},\ch,
-    (\attrs,\Ccom_{\usk}, \ldblbrace \gpk_i \rdblbrace_{i \in \Issuers}))$
-  \item $\cred \gets \RSSign(\isk,\attrs,\Ccom_{\usk})$
-  \item $\utrans \gets (\Ccom_{\usk},\cred,\attrs)$
-  \item Send \cred to User and output \utrans.
-  \end{itemize}
-\item User:
-  \begin{itemize}
-  \item $1 \stackrel{?}{=} \RSVerify(\RSvk,\cred,(\attrs,\Ccom_{\usk}))$
-  \item Output \cred
-  \end{itemize}   
+\item \uline{User}: Compute a fresh credential identifier $\credid \getr
+  \AttrSpace$, and commit to it along with the user secret key with
+  $\Ccom \gets \CCommit((\usk,\credid))$. Compute proof $\NIZKproof \gets
+  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\credid,\scred),
+  (\Ccom,\attrs))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
+\item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
+  (\NIZKcrs_{\Issue},(\Ccom,\attrs))$, and abort if it fails. Then, compute
+  the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,\attrs)$.
+  Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\cred,\NIZKproof)$.
+\item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
+  \attrs \cup \lbrace \usk,\credid \rbrace)$. Reject if verification fails.
+  Otherwise, return \cred.
 \end{itemize}

### 2022-04-12 prism-backend/research/gsac/model-uas.tex
Slightly refined UAS model. Working on generic construction.

@@
 
-\paragraph{Helper Function \Identify.} %
-\todo{We use extract now...} In addition, we make use of a helper
-function \Identify for some of our definitions. This function receives
-a signature and a user secret key, and determines whether the latter was used
-to produce the former. This is in line with previous works on DAA
-\cite{bfg+11,cdl16} and group signatures without traditional open functions
-\cite{dl21,fgl21,gl19}. More concretely, the \Identify function, defined as $1/0
-\gets \Identify(\usk,\sig)$, conveys meaning to our definitions conditioned on
-the fact that, given a signature \sig accepted by \Verify, \Identify returns $1$
-for exactly one \usk.
+\paragraph{Helper functions \ExtractIssue and \ExtractSign.} In our modelling,
+we assume the existence of two functions, \ExtractIssue and \ExtractSign. They
+are not functions available in the actual scheme, but rather to the challenger,
+in the experiments we use to formalize security fof \UAS. Indeed, similar
+techniques have been used before to prove security in privacy-preserving schemes
+with some sort of accountability, but that do not offer conventional opening as
+vanilla group signatures. For instance, see related works on DAA
+\cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}
+More concretely, both functions are as follows:
+
+\begin{description}
+\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\scred)$.] Receives an
+$\langle \Obtain, \Issue \rangle$ transcript, and returns the credentials (if
+any) and user secret key used during the execution of the protocol. It clearly
+needs an honest issuer as, otherwise, the transcripts won't be available.
+Consequently, we only use it to define the properties that require an honest
+issuer.
+\item[$\ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,\scred)$.]
+Receives a signature pair $(\sig,\yeval)$, as well as the inspector identifier
+\oid, and the identifiers of all issuers of the credentials used to produce the
+signature over \msg, and for \feval. It outputs the user secret key
+and credentials used to generate the signature.
+\end{description}
+
+Note that, both for \ExtractIssue and \ExtractSign, in the case of transcripts
+and signatures by honest users, it is enough to have access to the corresponding
+state information (described below) maintained by the challenger in our
+experiments. For join transcripts of corrupt users, or dishonestly produced
+signatures, we do need to perform actual extraction. How to do this will depend
+on each specific construction. Certainly, the challenger needs special
+knowledge/power such as decryption trapdoors, the ability to rewind the game, or
+program random oracles; the approach needs thus to depend on the concrete
+construction. Although, for the case of \ExtractIssue, online extractability
+(or alternative requirements, such as non-parallel or logarithmic number of
+joins) is necessary. \todo{\needcite Paper from Camenisch and Shoup on the need
+  for online extractability?} \todo{How do we do this in our construction(s)?
+  Can we be more specific here? Also, this poses an interesting question: Is
+  extraction a requirement for this kind of schemes? Can we find alternative
+  definitions?}
 
@@
 
+% \paragraph{Extractability.} %
+% \commentwho{Jesus}{I have a doubt here. On one hand, modelling the
+%   extractability-related properties here as in \cite{lnpy21} would lead to
+%   redundancy with the current unforgeability properties. I do like the
+%   precission in the definition of \cite{lnpy21}; but I do not like that,
+%   within the extractability property, they include ``domain-specific''
+%   concepts (e.g., open, etc.) On the other hand, we could model extractability
+%   as (an extension of) the Identify approach in e.g. \cite{gl19,dl21}. What
+%   I like about that is that it would not be redundant (we just assume the
+%   existance of a function extracting some secret values). What I do not like,
+%   is that the definition is not as precise as in \cite{lnpy12}. Namely, at the
+%   design stage, one just has to informally describe what Identify-Extract does;
+%   then, what it *really* does, has to be defined in the security proofs. That
+%   is, its definition is somehow deferred, which makes the presentation a bit
+%   harder to follow, IMO.}
+
+% Before getting into the ``actual'' security properties, we introduce an
+% auxiliary yet crucial property, extractability, that will allow us to formally
+% define unforgeability-related properties in a meaningful way. More concretely,
+% we require issuance extractability, and signing extractability. Informally, with
+% issuance extractability we require that given an additional trapdoor generated
+% at setup time, it is possible to extract the witnesses (user secret key and
+% credentials) used to request issuance of a new credential, from its $\langle
+% \Obtain,\Issue \rangle$ transcript. With signing extractability, we refer to the
+% requirement to be able to extract, given an additional trapdoor, the user secret
+% key and credentials used to produce any (possibly maliciously generated)
+% signature. The need to differentiate both comes from the fact that, for issuance
+% extractability, we need to assume honest issuers -- as otherwise, the $\langle
+% \Obtain,\Issue\rangle$ transcripts may
+% just not exist. Other than that, both properties are essentially the same: given
+% some proof an instance of an NP relation, they allow extracting the
+% corresponding witnesses. The need to resort to this extraction technique comes
+% from the fact of not including a conventional opening functionality. Indeed,
+% this has been used (at times, somehow implicitly) in related works on DAA
+% \cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}.
+
+% In more detail, we require the existence of three additional algorithms,
+% \ExtractSetup, \ExtractIssue, and \ExtractSign, as follows:
+
+% \begin{description}
+% \item[$\ExtractSetup(1^\secpar) \rightarrow (\parm,\extracttrap)$.] \todo{Describe,
+%     and mention that it must be indistinguishable from \Setup.}
+% \item[$\ExtractIssue(\extracttrap,\utrans) \rightarrow (\usk,\scred)$.] \todo{Describe.}
+% \item[$\ExtractSign(\extracttrap,\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,\scred)$.]
+%   \todo{Describe.}
+% \end{description}
+
+% With these algorithms, we formally define the issuance extractability and
+% signing extractability properties as shown in \figref{fig:exp-uas-extract}.
+
+% \begin{figure}[htp!]
+%   \procedure{$\ExpExtractIssue(\utrans)$}{%
+%     \pcreturn (\usk,\scred) \\    
+%   }
+
+%   \procedure{$\ExpExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
+%     \pcreturn (\usk,\scred)
+%   }
+
+%   \caption{Issuance and signing extractability experiments for \UAS schemes.}
+%   \label{fig:exp-uas-extract}
+% \end{figure}
+
+% \begin{definition}{(Extractable issuance of \UAS)}
+%   We define the advantage \AdvExtractIssue of $\adv$ against \ExpExtractIssue as
+%   $\AdvExtractIssue=\Pr\lbrack\ExpExtractIssue(1^\secpar)=1\rbrack$.
+%   %
+%   A \UAS scheme has extractable issuance if, for any p.p.t. adversary $\adv$,
+%   \AdvExtractIssue is a negligible function of $1^\secpar$.
+% \end{definition}
+
+% \begin{definition}{(Extractable signing of \UAS)}
+%   We define the advantage \AdvExtractSign of $\adv$ against \ExpExtractSign as
+%   $\AdvExtractSign=\Pr\lbrack\ExpExtractSign(1^\secpar)=1\rbrack$.
+%   %
+%   A \UAS scheme has extractable signing if, for any p.p.t. adversary $\adv$,
+%   \AdvExtractSign is a negligible function of $1^\secpar$.
+% \end{definition}
+
+% For short, we say that an \UAS scheme that has both extractable issuance and
+% signing, is an extractable \UAS scheme.
+
 \paragraph{Anonymity.} %

### 2022-04-13 prism-backend/research/gsac/construction-uas.tex
Added generic construction of UAS. Seems ok.

@@
 \paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
-\begin{itemize}
-\item Parse \secpar as $(\Csecpar,\NIZKsecpar,\SBCMsecpar,\Esecpar,\AttrSpace)$
-\item $\Cparm \gets \CSetup(\Csecpar)$
-\item $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$
-\item $\Sparm \gets \SSetup(\Ssecpar)$  
-\item $\Eparm \gets \ESetup(\Esecpar)$
-\item $\NIZKcrs_{\Issue} \gets \NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$
-\item $\NIZKcrs_{\Sign} \gets \NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$
-\item $\NIZKcrs_{\Inspect} \gets \NIZKSetup^{\NIZKRel_{\Inspect}}(\NIZKsecpar)$
-\item Return $(\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
-  \NIZKcrs_{\Sign},\NIZKcrs_{\Inspect},\AttrSpace)$
-\end{itemize}
+The setup process essentially consists on generating the public parameters
+for all the building blocks. In detail, it parses \secpar as $(\Csecpar,
+\NIZKsecpar,\SBCMsecpar,\Esecpar,\AttrSpace)$. Then, run $\Cparm \gets
+\CSetup(\Csecpar)$, $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$, $\Sparm \gets
+\SSetup(\Ssecpar)$, $\Eparm \gets \ESetup(\Esecpar)$, $\NIZKcrs_{\Issue} \gets
+\NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$, $\NIZKcrs_{\Sign} \gets
+\NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$, and $\NIZKcrs_{\Inspect} \gets
+\NIZKSetup^{\NIZKRel_{\Inspect}}(\NIZKsecpar)$. Return $(\Cparm,\SBCMparm,
+\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Inspect},
+\AttrSpace)$
 
 \paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
-\begin{itemize}
-\item Parse \parm as $(\cdot,\SBCMparm,\Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$
-\item $(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$
-\item $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$  
-\item $\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$
-\item $\ipk \gets (\Svk,\fissue,\sig_{\fissue})$
-\item $\isk \gets \Ssk$
-\item Return $(\ipk,\isk)$
-\end{itemize}
+To generate its key pair, each issuer first parses \parm as $(\cdot,\SBCMparm,
+\Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets
+\SKeyGen(\Sparm)$, $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$,
+$\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$, $\ipk \gets (\Svk,\fissue,
+\sig_{\fissue})$, $\isk \gets \Ssk$ and return $(\ipk,\isk)$.
 
 \paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
-\begin{itemize}
-\item Parse \parm as $(\cdot,\cdot,\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$
-\item $(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$
-\item $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$
-\item $\sig_{\finsp} \gets \SSign(\Ssk,\finsp)$
-\item $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$
-\item $\osk \gets (\Ssk,\Edk)$
-\item Return $(\opk,\osk)$
-\end{itemize}
+To generate its key pair, each inspectur first parses \parm as $(\cdot,\cdot,
+\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets \SKeyGen
+(\Sparm)$, $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, $\sig_{\finsp} \gets \SSign
+(\Ssk,\finsp)$, $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$, and $\osk \gets
+(\Ssk,\Edk)$. Finally, returns $(\opk,\osk)$.
 
 \paragraph{$\usk \gets \UKeyGen(\parm)$.} %
-\begin{itemize}
-\item Parse \parm as $(\Cparm,\NIZKsecpar,\RSsecpar,\Ssecpar,\Esecpar,\AttrSpace)$
-\item $\usk \getr \AttrSpace$
-\item Return \usk
-\end{itemize}
+Each user, prior to requesting credentials, generates his secret key by parsing
+\parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\AttrSpace)$, and picking randomly
+$\usk \getr \AttrSpace$. Finally, return \usk.
 
 \paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle
-  \Obtain(\usk,\ldblbrace (\cred_i,\ipk_i)\rdblbrace_{i \in \Issuers},\attrs),
-  \Issue(\isk,\upk,\attrs,\ldblbrace \ipk_i \rdblbrace_{i \in \Issuers},\attrs)
-  \rangle$.} %
+  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\upk,\scred,\attrs)\rangle$.} %
 To obtain a new credential, a user with secret key usk and credentials $\cred_i$,
@@
 
-\paragraph{$\sig \gets \Sign(\gpk,\usk,\cred,\msg,\feval)$.} %
-We define the NP language $\LangSig = \lbrace (\upk,\cred,\y):
-\SVerify(\sig,\upk) = 1~\land~\Ec = \EEnc(\Eek,\y)~\land~
-\y = \finsp(\feval(\upk,\cred,\msg),\upk,\cred,\msg)\rbrace$. The
-signing algorithm is defined as follows:
-\todo{Argue that the composition of \finsp and \feval is not redundant even
-  though both depend on the same arguments. Namely, because \feval is defined
-  on a per-signature basis (akin to the policies of ACs), and \finsp is defined
-  once per group (akin to the open function in GSs). Hence, \finsp cannot just
-  be defined to ``contain'' \feval at setup time.}
+\paragraph{$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
+In the signing algorithm, we make use of the following relation:
+$\NIZKRel_{\Sign} = \lbrace (\usk,\scred,\yinsp),(\msg,\feval,\yeval,\Ec,\sipk)
+: \Ec = \EEnc(\Eek,\yinsp) \land \yeval = \feval(\usk,\scred,\msg) \land
+\yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
+\SBCMVerify(\ipk,\cred,\attrs_{\cred} \cup \lbrace \usk,\credid \rbrace) = 1)
+\rbrace$, where we make two syntax abuses, to ease readability: with
+$\attrs_{\cred}$ we refer to the attributes in credential \cred, which its
+legitimate owner can recover easily (e.g., from secure storage); and, as stated
+before, $\ipk_{\cred}$ denotes the issuer public key of credential \cred, which
+we also assume to be easily recoverable from \cred, by its legitimate owner.
+\todo{Maybe, try to think of clearer naming conventions.}
+%
+From this, in order to produce a valid signature, the user first evaluates
+$\yeval \gets \feval (\usk,\scred,\msg)$, and decides whether or not to continue
+with the signing process -- this may depend, e.g., on the inspection policy of
+\opk, as the output of \feval may influence whether the user will be
+de-anonymizable or not, depending on the \finsp function in \opk.
+%
+Then, the user parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
+$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
+compute $\yinsp \gets \finsp(\yeval,\usk,\scred,\msg)$, and encrypt it with
+\Eek by running $\Ec \gets \EEnc(\Eek,\yeval)$. Finally, the user computes
+$\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
+\yinsp))$ and  outputs $(\sig = (\NIZKproof,\Ec),\yeval)$.
 
-\begin{itemize}
-\item Parse \gpk as $(\ipk,\opk)$
-\item Parse \ipk as $(\RSvk,\fissue,\sig_{\fissue})$; Verify $\sig_{\fissue}$
-\item Parse \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$; Verify $\sig_{\finsp}$
-\item $\sig' \gets \SSign(\usk,\msg)$
-%\item $b \gets \feval(\upk,\cred,\msg)$
-\item % If $b=0$: 
-  $\y \gets \finsp(\feval(\upk,\cred,\msg),
-  \upk,\cred,\msg)$%; else $\y = \bot$.
-\item $\Ec \gets \EEnc(\Eek,\y)$
-\item $\SPKproof^{\LangSig} \gets \SPKProve^{\LangSig}(\msg,(\Ec,\sig'),
-  (\upk,\cred,\y))$
-\item Return $(\Ec,\sig',\SPKproof^{\LangSig})$
-\end{itemize}
+\paragraph{$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval)$.} %
+The ``cryptographic'' side of the verification essentially consists on checking
+the NIZK proof. That is, parse \sig as $(\NIZKproof,\Ec)$ and check whether
+$\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,\sipk)) = 1$. In
+addition, the verifier may further check whether \yeval meets its needs.
 
-\paragraph{$1/0 \gets \Verify(\gpk,\sig,\msg,\feval)$.} %
-\begin{itemize}
-\item Parse \sig as $(\Ec,\sig',\SPKproof^{\LangSig})$
-\item Return $\SPKVerify^{\LangSig}(\SPKproof^{\LangSig},\msg,(\Ec,\sig'))$ 
-\end{itemize}
+\paragraph{$(\yinsp,\NIZKproof)/\bot \gets
+  \Inspect(\osk,\sipk,\sig,\yeval,\msg,\feval)$.} %
+We first define NIZK relation $\NIZKRel_{\Inspect} = \lbrace (\osk),(\Ec,\yinsp)
+: \yinsp = \EDec(\osk,\Ec) \rbrace$.
+%
+For inspection, the inspector first verifies the signature by running $\Verify(
+\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the verification succeeds, it parses
+\sig as $(\NIZKproof,\Ec)$, decrypts \Ec by running $\yeval \gets \EDec(\osk,
+\Ec)$, and computes $\NIZKproof_{\Inspect} \gets \NIZKProve^{\NIZKRel_{\Inspect}}
+(\NIZKcrs_{\Inspect},(\osk),(\Ec,\yinsp))$. It returns $(\yinsp,
+\NIZKproof_{\Inspect})$.
 
-\paragraph{$(\y,\iproof)/\bot \gets \Inspect(\gpk,\osk,\trans,\sig,\msg,\feval)$.} %
-
-We follow the approach of \cite{bsz05} for verifiable openings. Namely, we
-define an NP language $\LangVerIns = \lbrace (\Eek,\Edk,r):
-(\Eek,\Edk) = \EKeyGen(\Esecpar;r) \land \y = \EDec(\Edk,\c) \rbrace$.
-
-\begin{itemize}
-\item Parse \osk as $(\Ssk,\Edk)$; \gpk as
-  $(\cdot,(\Svk,\Eek,\finsp,\sig_{\finsp}))$
-\item  $1 \stackrel{?}{=} \Verify(\gpk,\sig,\msg,\feval)$  
-\item $\y \gets \EDec(\Edk,\c)$
-\item $\NIZKproof^{\LangVerIns} \gets \NIZKProve(\NIZKcrs,(\c,\y),(\Eek,\Edk,r))$
-\item Return $\NIZKproof^{\LangVerIns}$
-\end{itemize}
-
-\paragraph{$1/0 \gets \Judge(\gpk,\y,\iproof,\sig,\msg)$.} %
-
-\begin{itemize}
-\item  $1 \stackrel{?}{=} \Verify(\gpk,\sig,\msg,\feval)$
-\item Parse \sig as $(\c,\cdot,\cdot)$  
-\item Return $\NIZKVerify(\NIZKcrs,\iproof,(\c,\y))$
-\end{itemize}
+\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\sig,\yeval,\msg)$.} %
+To assess the validity of an inspection proof, first check the signature
+by running $\Verify(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the check succeeds,
+parse \sig as $((\cdot,\Ec),\cdot)$ and verify \NIZKproof with $\NIZKVerify
+(\NIZKcrs_{\Inspect},\NIZKproof,(\Ec,\yinsp))$. Accept it the NIZK verification
+passes, and reject otherwise.
 

### 2022-04-13 prism-backend/research/gsac/construction-uas.tex
Some refining of UAS generic construction.

@@
 
-% \subsubsection{Commitments}
-
-% \todo{Introduce, and summarise correctness and security.}
-
-% \begin{description}
-%   \item[$\Cparm \gets \CSetup(\Csecpar).$]
-%   \item[$(\Ccom,\Copn) \gets \CCommit(\Cparm,\msg).$] 
-%   \item[$\Cproof \gets \CProve(\Ccom,\Copn,\msg).$]    
-%   \item[$1/0 \gets \CVerify(\Cproof,\Ccom).$] 
-% \end{description}
-
-% \subsubsection{Signatures with Proofs of Knowledge}
-
-% As put forward in \cite{cl02}, a generic way to build anonymous credentials
-% requires a digital signature scheme with efficient protocols for proving
-% knowledge of a digital signature, and signing committed values. This approach
-% also has much in common with the Sign-Randomize-Prove (SRP) approach to build
-% group signatures \needcite. Thus, even a priori, it seems a good core component
-% to build something that is actually in betwween GS and AC. In the sequel, we use
-% \RS to refer to schemes of this type, which must provide the functionality
-% specified by the following syntax:
-
-% \begin{description}
-% \item[$(\RSvk,\RSsk) \gets \RSKeyGen(\RSsecpar,\RSlen)$.] Generates a key pair,
-%   consisting on the signig key \RSsk and the verification key \RSvk, which
-%   support sigining blocks of up to \RSlen messages.
-% \item[$\RSsig \gets \RSSign(\RSsk,\msgset,\cmsgset)$.] Given signing key \RSsk,
-%   a set of messages \msgset, and a set of commitments to messages, where
-%   $|\msgset + \cmsgset| \le \RSlen$, returns a signature \RSsig.
-% \item[$1/0 \gets \RSVerify(\RSvk,\RSsig,\amsgset)$.] Given a verification key
-%   \RSvk, a signature \RSsig, supposedly over set of messages \amsgset which may
-%   contain commitments to messages, returns $1$ or $0$. \todo{Assume that, within
-%     \amsgset, it is possible to know which are commitments and wich plain
-%     messages?}
-% \item[$\RSproof/\bot \gets \RSProve(\RSsig,\amsgset,\D)$.] Given signature
-%   \RSsig, over set of messages (and commitments to messages) \amsgset, out of
-%   which those indexed by set \D are to be revealed, creates a proof of knowledge
-%   \RSproof of \RSsig.
-% \item[$1/0 \gets \RSProveVer(\RSproof,\msgset)$.] Given a proof of knowledge of
-%   a signature over a set of messages, which includes \msgset, returns $1$ or
-%   $0$.
-% \end{description}
-
-% \todo{Summarise correctness and security.}
-
-% \subsubsection{Digital Signatures}
-
-% \todo{Introduce, and summarise correctness and security.}
-
-% \begin{description}
-% \item[$(\Svk,\Ssk) \gets \SKeyGen(\Ssecpar)$.]
-% \item[$\Ssig \gets \SSign(\Ssk,\msg)$.]
-% \item[$1/0 \gets \SVerify(\Svk,\Ssig,\msg)$.]  
-% \end{description}
-
-% \subsubsection{Encryption}
-
-% \todo{Introduce, and summarise correctness and security.}
-
-% \begin{description}
-% \item[$(\Eek,\Edk) \gets \EKeyGen(\Esecpar)$.]
-% \item[$\Ec \gets \EEnc(\Eek,\msg)$.]
-% \item[$\msg \gets \EDec(\Edk,\Ec)$.]
-% \end{description}
-
-% \subsubsection{Non-Interactive ZK Proofs of Knowledge}
-
-% \todo{Introduce, and summarise correctness and security.}
-
-% \begin{description}
-% \item[$\NIZKcrs\gets \NIZKSetup(\NIZKsecpar)$.]
-% \item[$\NIZKproof \gets \NIZKProve(\NIZKcrs,\NIZKx,\NIZKw)$.]
-% \item[$1/0 \gets \NIZKVerify(\NIZKcrs,\NIZKproof,\NIZKx)$.]
-% \end{description}
-
-% We use $\NIZK^\Lang$ to denote a \NIZK which is used to prove statements on a
-% given NP language \Lang.
-
-% \subsubsection{Signature Proofs of Knowledge}
-
-% \todo{Introduce, and summarise correctness and security.}
-
-% \begin{description}
-% \item[$\SPKproof \gets \SPKProve(\SPKmsg,\SPKx,\SPKw)$.]
-% \item[$1/0 \gets \SPKVerify(\SPKproof,\SPKmsg,\NIZKx)$.]
-% \end{description}
-
-% We use $\SPK^\Lang$ to denote an \SPK which is used to prove statements on a
-% given NP language \Lang.
-
 \subsection{Generic Construction \CUASGen}
@@
 secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace (\usk,
-\credid,\scred), (\Ccom,\attrs): \Ccom = \CCommit((\usk,\credid)) \land
-\fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in \scred, \usk \in \cred
-\rbrace$. \todo{Refine the notation for $\attr \in \cred$. Also, need to make
-  the {\ipk}s explicit in it.} The interactive protocol from a user to obtain a
-credential from an issuer of the system is as follows:
+\scred), (\Ccom,\attrs): \Ccom = \CCommit(usk) \land \fissue(\usk,\scred,
+\attrs) = 1 \land \forall \cred \in \scred, \SBCMVerify(\ipk_{\cred},\cred,
+\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1 \rbrace$. The interactive protocol
+for a user to obtain a credential from an issuer of the system is as follows:
 
 \begin{itemize}
-\item \uline{User}: Compute a fresh credential identifier $\credid \getr
-  \AttrSpace$, and commit to it along with the user secret key with
-  $\Ccom \gets \CCommit((\usk,\credid))$. Compute proof $\NIZKproof \gets
-  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\credid,\scred),
-  (\Ccom,\attrs))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
+\item \uline{User}: Commit to the user secret key with $\Ccom \gets
+  \CCommit(\usk)$. Compute proof $\NIZKproof \gets
+  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred),(\Ccom,
+  \attrs))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
 \item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
@@
 \item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
-  \attrs \cup \lbrace \usk,\credid \rbrace)$. Reject if verification fails.
+  \attrs \cup \lbrace \usk \rbrace)$. Reject if verification fails.
   Otherwise, return \cred.
@@
 \yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
-\SBCMVerify(\ipk,\cred,\attrs_{\cred} \cup \lbrace \usk,\credid \rbrace) = 1)
+\SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1)
 \rbrace$, where we make two syntax abuses, to ease readability: with

### 2022-04-13 prism-backend/research/gsac/model-uas.tex
Some refining of UAS generic construction.

@@
   \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
-  \todo{I think we do not need \trans here, see the generic construction. (This
-    was somehow inherited from \cite{bsz05}.) However, if it is indeed not
-    needed, it is noteworthy that we include/need it in \GSAC, but not here.
-    Justify/understand better why!}
   Executed by the inspector with private key \osk. Receives a signature $(\sig,

### 2022-04-18 prism-backend/research/gsac/app-building-blocks.tex
Added some BB definitions.

\section{Cryptographic Building Blocks}
\label{app:crypto-building-blocks}

\subsection{Digital Signatures}
\label{sapp:digital-signatures}

Defined as a tuple $(\SSetup,\SKeyGen,\SSign,\SVerify)$. Algorithm $\Sparm \gets
\SSetup(\Ssecpar)$ produces public parameters for the other algorithms.
$(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$ generates the verification-signing key
pair, algorithm $\Ssig \gets \SSign(\Ssk,\msg)$ signs message \msg with
signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\Svk,
\Ssig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
verification key \Svk. \todo{Informally define security properties we'll need.}

\subsection{Public-Key Encryption}
\label{sapp:pk-encryption}

Defined as a tuple $(\ESetup,\EKeyGen,\EEnc,\EDec)$. Algorithm $\Eparm \gets
\ESetup(\Esecpar)$ produces public parameters for the other algorithms.
$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$ generates the encryption-decryption key
pair, algorithm $\Ec \gets \EEnc(\Eek,\msg)$ encrypts message \msg with
encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\Edk,
\Ec)$ decrypts ciphertexts using decryption key \Edk. \todo{Informally define
  security properties we'll need.}

\subsection{Vector Commitments}
\label{sapp:vector-commitments}

Defined as a tuple $(\CSetup,\CCommit)$. Algorithm $\Cparm \gets
\CSetup(\Csecpar)$ produces the parameters for committing to values. $\Ccom
\gets \CCommit(\Cparm, \msgset; r)$ produces a commitment \Ccom over a set of
messages \msgset, from which we may omit randomness $r$. \todo{Informally define
  hiding and binding, leaving formal definitions to the appendix.}

\subsection{Signatures on Blocks of Committed Messages}
\label{sapp:sbcm}

We use signature schemes that allow signing messages, or commitments to messages,
in blocks, and are compatible with (efficient) proof systems over the produced
signature and signed (commitments to) messages. For this purpose, we define such
schemes as a tuple $(\SBCMSetup,\SBCMKeyGen,\SBCMSign,\SBCMVerify)$. Algorithm
$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$ produces the public parameters for the
scheme. $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$ produces a
verification-signing key
pair. Algorithm $\SBCMsig \gets \SBCMSign(\SBCMsk,\Ccom,\msgset)$ produces a
signature over a set of committed messages \Ccom and a set of messages
\msgset, where either \Ccom or \msgset may be empty. $1/0 \gets
\SBCMVerify(\SBCMvk,\SBCMsig,\overline{\msgset})$ verifies a signature \SBCMsig
over message set $\overline{\msgset}$, which must contain both the messages that
were signed as commitments as well as those signed in ``the clear''. In
addition, the produced signatures must be compatible with (efficient) NIZK
proofs of knowledge of a signature, and of (arbitrary) claims over the signed
(committed) messages.
\todo{Informally define security properties we'll need.}

\subsection{Non-Interactive Zero-Knowledge Proofs of Knowledge}
\label{sapp:nizk}

Let \NIZKRel be an NP relation defined by pairs of elements $(\NIZKx,\NIZKw)$,
where \NIZKx is a statement and \NIZKw a witness proving that $(\NIZKx,\NIZKw)
\in \NIZKRel$. For concrete relations, we write $\NIZKRel = \lbrace (\NIZKx),
(\NIZKw): f(x,w) \rbrace$, where $f(x,w)$ is a boolean predicate denoting the
concrete conditions that \NIZKx and \NIZKw need to meet. The set of all $(\NIZKx,
\NIZKw) \in \NIZKRel$ is called the language, or \NIZKLang, for \NIZKRel.
$\NIZKx \notin \NIZKLang$ means that there is no $\NIZKw$ such that $(\NIZKx,
\NIZKw) \in \NIZKRel$. \todo{Check this definition.}

We use non-interactive zero-knowledge proofs of knowledge (NIZKPoK, or, for
short, NIZK) over NP relations, in the Common Reference String (CRS) model
\needcite. A NIZK system is a tuple $(\NIZKSetup,\NIZKProve,\NIZKVerify)$,
defined as follows \cite{gos06}:

\begin{description}
\item[$\NIZKcrs \gets \NIZKSetup(\NIZKsecpar)$.] Generates a CRS \NIZKcrs from
  security parameters \NIZKsecpar.
\item[$\NIZKproof \gets \NIZKProve(\NIZKcrs,\NIZKx,\NIZKw)$.] Given \NIZKcrs,
  statement \NIZKx, and witness \NIZKw, creates a proof \NIZKproof.
\item[$1/0 \gets \NIZKVerify(\NIZKcrs,\NIZKproof,\NIZKx)$.] Checks whether
  \NIZKproof is a valid proof for \NIZKx.
\end{description}

Moreover, a NIZK system has additional algorithms $(\NIZKSimI,\NIZKSimII)$ and
$(\NIZKExtI,\NIZKExtII)$ defined as follows:

\begin{description}
\item[$(\NIZKcrs,\NIZKext) \gets \NIZKSimI(\NIZKsecpar)$.] Produces a \NIZKcrs
  as the \NIZKSetup algorithm, along with a \todo{simulation} trapdoor.
  % The output of \NIZKSimI is required to be indistinguishable from that of
  % \NIZKSetup.
\item[$\NIZKproof \gets \NIZKSimII(\NIZKcrs,\NIZKext,\NIZKx)$.] Given a
  \todo{simulation} trapdoor, and a statement $\NIZKx \in \NIZKLang$,
  produces a simulated proof \NIZKproof of $\NIZKx \in \NIZKLang$.
\item[$(\NIZKcrs,\NIZKext) \gets \NIZKExtI(\NIZKsecpar)$.] Produces a \NIZKcrs
  as the \NIZKSetup algorithm, along with an extraction trapdoor \NIZKext.
\item[$\NIZKw \gets \NIZKExtII(\NIZKcrs,\NIZKext,\NIZKx,\NIZKproof)$.] Given
  an extraction trapdoor \NIZKext produced by \NIZKExtI, and a proof \NIZKproof
  for $\NIZKext \in \NIZKLang$, returns a valid \NIZKw for \NIZKx.
\end{description}

When we want to make explicit the NP relation \NIZKRel to which the previous
algorithms refer to, we use $\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel$, 
$\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and subindex when clear
from context. Altogether, the tuple $(\Setup,\Prove,\Verify,\ExtI,\ExtII,\SimI,
\SimII)$ needs to meet the following properties:

\paragraph{Completeness.} %
Ensures that, for any $(\NIZKx,\NIZKw) \in \NIZKRel)$, any honest prover will be
able to create a proof \NIZKproof that is accepted by any honest verifier, with
overwhelming probability. More precisely, $\Pr\lbrack\ExpNIZKComp\rbrack = 1$
with overwhelming probability, for any p.p.t. \adv, for \ExpNIZKComp in
\figref{fig:nizk-games}.

\paragraph{Soundness.} %
Ensures that no adversary can create proofs accepted by \Verify, for
statements $\NIZKx \notin \NIZKLang$, except with negligible probability. That
is, for \ExpNIZKSound as in \figref{fig:nizk-games}, $\Pr\lbrack\ExpNIZKSound\rbrack
= 1$ with overwhelming probability. If this holds only against p.p.t.
adversaries, we talk of Non-Interactive \emph{arguments}, while if soundness
holds even against unbounded adversaries, we talks about Non-Interactive proofs.

\paragraph{Knowledge extraction.} %
For all possible adversaries computing a valid proof \NIZKproof over a statement
$\NIZKx \in \NIZKLang$, computed using a \NIZKcrs produced by \ExtI and given
\NIZKext also produced by \ExtI, \ExtII outputs a witness \NIZKw such that
$(\NIZKx,\NIZKw) \in \NIZKRel$. That is, for all valid statements in the
language and a proof, we can extract a valid witness given some special
knowledge ($\NIZKext$). \todo{Capture either here or in the game that the
  output of \ExtI needs to be indistinguishable to the output of \Setup.}

\paragraph{Zero-knowledge.} %
Intuitively, captures that no information can be learned from an statement and
proof pair, beyond their validity (or not). This is captured by requiring the
adversary to distinguish between a run in the real world ($b=0$), where the
setup is done with \Setup, and $\adv$ has access to an honest prover
\Prove; and a run in an ideal world ($b=1$), where the setup is run by
a simulator \SimI, and proofs are generated by \SimII, except when $\adv$
specifies $(\NIZKx,\NIZKw) \notin \NIZKRel$.

\begin{figure}[ht!]
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpNIZKComp(\secpar)$}{%
      \NIZKcrs \gets \Setup(\secpar) \\
      (\NIZKx,\NIZKw) \gets \adv(\NIZKcrs) \\
      \pcif (\NIZKx,\NIZKw) \notin \NIZKRel: \pcreturn 0 \\
      \NIZKproof \gets \Prove(\NIZKcrs,\NIZKx,\NIZKw) \\
      b \gets \Verify(\NIZKcrs,\NIZKproof,\NIZKx) \\
      \pcreturn b \\
    }
    \procedure{$\ExpNIZKExt(\secpar)$}{%
      (\NIZKcrs,\NIZKext) \gets \ExtI(\secpar) \\
      (\NIZKx,\NIZKproof) \gets \adv(\NIZKcrs) \\
      \NIZKw \gets \NIZKExtII(\NIZKcrs,\NIZKext,\NIZKx,\NIZKproof) \\
      \pcif \Verify(\NIZKcrs,\NIZKproof,\NIZKx) = 1 \land
      (\NIZKx,\NIZKw) \notin \NIZKRel: \\
      \pcind \pcreturn 0 \\
      \pcreturn 1
    }    
  \end{minipage}
  \begin{minipage}[t]{0.5\textwidth}
    \procedure{$\ExpNIZKSound(\secpar)$}{%
      \NIZKcrs \gets \Setup(\secpar) \\
      (\NIZKproof,\NIZKx) \gets \adv(\NIZKcrs) \\
      \pcif \NIZKx \notin \NIZKLang \land
      \Verify(\NIZKcrs,\NIZKproof,\NIZKx): \\
      \pcind \pcreturn 0 \\
      \pcreturn 1 \\
    }
    \procedure{$\ExpNIZKZKb(\secpar)$}{%
      \pcif b = 0: \\
      \pcind \NIZKcrs \gets \Setup(\secpar) \\
      \pcind \pcreturn \adv^{\Prove(\NIZKcrs,\cdot,\cdot)}(\NIZKcrs) \\
      \pcif b = 1: \\
      \pcind (\NIZKcrs,\NIZKext) \gets \SimI(\secpar) \\
      \pcind \pcreturn \adv^{\Sim'(\NIZKcrs,\NIZKext,\cdot,\cdot)}(\NIZKcrs),~
      \textrm{where} \\
      \pcind \Sim'(\NIZKcrs,\NIZKext,\NIZKx,\NIZKw)~\textrm{returns} \\
      \pcind \pcind \SimII(\NIZKcrs,\NIZKext,\NIZKx)~\pcif (\NIZKx,\NIZKw)
      \in \NIZKRel \\
      \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel
    }    
  \end{minipage}
  \label{fig:nizk-games}
  \caption{Games for NIZK schemes.}
\end{figure}

\iffalse
\paragraph{Simulation Soundness.} %
\fi

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:

### 2022-04-18 prism-backend/research/gsac/construction-uas.tex
Added some BB definitions.

@@
-\section{A Generic \UAS Construction}
+\section{\CUASGen: A Generic \UAS Construction}
 \label{sec:gen-construction}
@@
 
-\paragraph{Encryption.} %
+\paragraph{Public-Key Encryption.} %
 Defined as a tuple $(\ESetup,\EKeyGen,\EEnc,\EDec)$. Algorithm $\Eparm \gets
@@
 for all the building blocks. In detail, it parses \secpar as $(\Csecpar,
-\NIZKsecpar,\SBCMsecpar,\Esecpar,\AttrSpace)$. Then, run $\Cparm \gets
+\NIZKsecpar,\SBCMsecpar,\Esecpar)$. Then, run $\Cparm \gets
 \CSetup(\Csecpar)$, $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$, $\Sparm \gets
@@
 \paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
-To generate its key pair, each inspectur first parses \parm as $(\cdot,\cdot,
+To generate its key pair, each inspector first parses \parm as $(\cdot,\cdot,
 \cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets \SKeyGen
@@
   \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\upk,\scred,\attrs)\rangle$.} %
-To obtain a new credential, a user with secret key usk and credentials $\cred_i$,
-issued by issuers with public keys $\ipk_i$, requests a signature on commitments
-of both the user key and a new random credential identifier -- similarly to
-\GSAC. In addition, the user proves that the issuance function \fissue
-established by the issuer is satisfied by the $\cred_i$ credentials and its user
-secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace (\usk,
-\scred), (\Ccom,\attrs): \Ccom = \CCommit(usk) \land \fissue(\usk,\scred,
+The protocol is run between an issuer, and a user with secret key \usk and
+credentials \scred, where each $\cred \in \scred$ is issued by an issuer with
+public key $\ipk_{\cred}$ (which we assume that the user can easily retrieve,
+e.g., from secure storage, given \cred), and attests attributes
+$\attrs_{\cred}$. The user
+requests a signature on a commitment to the user key, as well as on the
+attributes in \attrs. In addition, the user proves that the issuance function
+\fissue established by the issuer is satisfied by the credentials in $\scred$
+and its user secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace
+(\usk,\scred), (\Ccom,\attrs): \Ccom = \CCommit(usk) \land \fissue(\usk,\scred,
 \attrs) = 1 \land \forall \cred \in \scred, \SBCMVerify(\ipk_{\cred},\cred,
@@
 \item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
-  (\NIZKcrs_{\Issue},(\Ccom,\attrs))$, and abort if it fails. Then, compute
-  the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,\attrs)$.
-  Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\cred,\NIZKproof)$.
+  (\NIZKcrs_{\Issue},\NIZKproof,(\Ccom,\attrs))$, and abort if it fails. Then,
+  compute the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,
+  \attrs)$. Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\cred,
+  \NIZKproof)$.
 \item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
@@
 \SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1)
-\rbrace$, where we make two syntax abuses, to ease readability: with
-$\attrs_{\cred}$ we refer to the attributes in credential \cred, which its
-legitimate owner can recover easily (e.g., from secure storage); and, as stated
-before, $\ipk_{\cred}$ denotes the issuer public key of credential \cred, which
-we also assume to be easily recoverable from \cred, by its legitimate owner.
-\todo{Maybe, try to think of clearer naming conventions.}
+\rbrace$ where, for each $\cred \in \scred$, $\attrs_{\cred}$ and $\ipk_{\cred}$
+are as in $\langle \Obtain,\Issue \rangle$.
 %
@@
 $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
-\yinsp))$ and  outputs $(\sig = (\NIZKproof,\Ec),\yeval)$.
+\yinsp),(\msg,\feval,\yeval,\Ec,\sipk))$ and  outputs $(\sig = (\NIZKproof,\Ec),
+\yeval)$.
 
@@
 \Ec)$, and computes $\NIZKproof_{\Inspect} \gets \NIZKProve^{\NIZKRel_{\Inspect}}
-(\NIZKcrs_{\Inspect},(\osk),(\Ec,\yinsp))$. It returns $(\yinsp,
+(\NIZKcrs_{\Inspect},\osk,(\Ec,\yinsp))$. It returns $(\yinsp,
 \NIZKproof_{\Inspect})$.

### 2022-04-18 prism-backend/research/gsac/model-uas.tex
Added some BB definitions.

@@
   \begin{description}
-  \item[\CRED.] Stores information related to credentials obtained by honest
-    users. Thus, it is indexable by \cid. More specifically, it stores tuples of
-    the form $(\uid,\cred,\iid,\attrs,\scid)$, where \uid is the identity of the
-    owner of the credential, \cred (when available) is the credential itself,
-    \iid is the identifier of the credential issuer, \attrs are the attributes
-    included in \cred, and \scid are the identifiers of the credentials (if any)
-    that \uid used to request \cred.
+  \item[\CRED.] Stores information related to credentials obtained by users in
+    the system. Thus, it is indexable by \cid. More specifically, it stores
+    tuples of the form $(\uid,\cred,\iid,\attrs,\scid)$, where \uid is the
+    identity of the owner of the credential, \cred (when available) is the
+    credential itself, \iid is the identifier of the credential issuer, \attrs
+    are the attributes included in \cred, and \scid are the identifiers of the
+    credentials (if any) that \uid used to request \cred. For notational
+    convenience, we may use $\CRED[\scid]$ to refer to $\CRED[\cid]$ for all
+    $\cid \in \scid$. Also, when clear from context, we sometimes use
+    $\CRED[\cid]$ (resp. $\CRED[\scid]$ to mean \cred (resp. \scred) in
+    $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,\cdot)$ (resp. $\CRED[\scid]$).
   \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
@@
     of honest users. Entries of this table are $(\oid,\scid,\sig,\yeval,\msg,
-    \feval)$,
-    where \oid is the inspector chosen for the signature, \scid is the set of
-    credentials used for signing, \feval is the evaluation function, and \sig
-    and \msg are the produced signature and signed message.
+    \feval)$, where \oid is the inspector chosen for the signature, \scid is the
+    set of credentials used for signing, \feval is the evaluation function, and
+    \sig and \msg are the produced signature and signed message.
   \item[\CSIG.] Maintains challenge signatures output to the adversary; i.e.,
@@
 \begin{definition}{(Correctness of \UAS)}
+  \label{def:correctness-uas}
   An \UAS scheme is correct if, for any p.p.t. adversary $\adv$, \ExpCorrect
@@
     (\sig,\yeval) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
-    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = 0: \pcreturn 1~
-    \pccomment{\sig fails to verify} \\
-    \pcif \CorrectIssue(\uid,\scid) = 0: \pcreturn 1~
-    \pccomment{Some \cid should not have been issued} \\
-    \pcif \CorrectEval(\oid,\uid,\scid,\msg,\sig,\yeval,\feval) = 0: \pcreturn 1~
-    \pccomment{The result of evaluation is wrong} \\
-    \pcif \CorrectInspect(\oid,\uid,\scid,\msg,\sig,\yeval,\feval) = 0: \pcreturn 1~
-    \pccomment{The result of inspection is wrong} \\
-    \pcreturn 0 \\
-  }
-
-  \procedure{$\CorrectIssue(\uid,\scid)$}{
+    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = 0: \pcreturn 1 \\
     \pcfor \cid \in \scid \pcdo: \\
-    \pcind \iid \gets \ISR[\cid] \\
-    \pcind \textrm{Parse}~\ATTR[\cid]~\textrm{as}~(\attrs^\cid,\scid^\cid);~
-    \textrm{Parse}~\IK[\iid]~\textrm{as}~
-    ((\cdot,\fissue^\gid),\cdot) \\        
-    \pcind \pcif \fissue^\gid(\PUBUK[\uid],\CRED[\scid]^\cid,\attrs^\cid) = 0: 
-    \pcreturn 0 \\
-    \pcreturn 1 \\   
-  }
-
-  \procedure{$\CorrectEval(\oid,\uid,\scid,\msg,\sig,\yeval,\feval)$}{%
-    \pcif \feval(\UK[\uid],\CRED[\scid],\msg) \neq \yeval: \pcreturn 0 \\
-    \pcreturn 1 \\
-  }
-
-  \procedure{$\CorrectInspect(\oid,\uid,\scid,\msg,\sig,\yeval,\feval)$}{
-    \textrm{Parse}~\OK[\oid]~\textrm{as}~((\cdot,\finsp^\gid),\cdot) \\
-    \pccomment{\sig cannot be inspected} \\
-    \pcif \Inspect(\PRVOK[\oid],\PUBIK[\scid],\sig,\yeval,\msg,\feval) = \bot:
-    \pcreturn 0 \\
-    \pccomment{The produced $(\y,\iproof)$ pair is rejected by \Judge} \\
-    \pcif (\yinsp,\iproof) \gets \Inspect(\PRVOK[\gid],\PUBIK[\scid],\sig,
-    \msg,\feval)~\land \\
-    \hspace*{10pt}
-    \Judge(\PUBOK[\oid],\PUBIK[\scid],\y,\iproof,\sig,\yeval,\msg,\feval) = 0: \\
-    \pcind \pcreturn 0 \\
-    \pccomment{\yinsp is the wrong value} \\
-    \pcif \yinsp \neq \finsp^\gid(\yeval,\UK[\uid],\CRED[\scid],\msg)):
-    \pcreturn 0 \\
-    \pcreturn 1
+    \pcind \textrm{Let}~\scred^{\cid}~\textrm{be the credentials used to obtain}
+    ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,\fissue^{\cid}),\cdot)\\
+    \pcind \pcif \fissue^{\cid}(\PUBUK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
+    \pcif \feval(\UK[\uid],\CRED[\scid],\msg) \neq \yeval: \pcreturn 1 \\
+    (\yinsp,\iproof) \gets \Inspect(\PRVOK[\gid],\PUBIK[\scid],\sig,\msg,\feval) \\
+    \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\y,\iproof,\sig,\yeval,\msg,\feval)
+    = 0 \lor \yinsp \neq \finsp^\gid(\yeval,\UK[\uid],\CRED[\scid],\msg)): \\
+    \pcind \pcreturn 1 \\
+    \pcreturn 0
   }
@@
 \begin{definition}{(Anonymity of \UAS)}
+  \label{def:anonymity-uas}  
   We define the advantage \AdvAnon of $\adv$ against \ExpAnonb as
@@
 \begin{definition}{(Unforgeable issuance of \UAS)}
+  \label{def:issue-forge-uas}  
   We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
@@
 \begin{definition}{(Unforgeable signing of \UAS)}
+  \label{def:sign-forge-uas}  
   We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
@@
 \begin{definition}{(Non-frameability of \UAS)}
+  \label{def:frame-uas}
   We define the advantage \AdvNonframe of $\adv$ against \ExpNonframe as

### 2022-04-18 prism-backend/research/gsac/transformations.tex
Added some BB definitions.

@@
 
-\subsection{Combining Multiple Credentials in One Presentation}
-
-\todo{I think this might be possible if we can use \fissue so that any user can
-  create arbitrary groups, where he is the issuer, an can thus run
-  \Obtain,\Issue protocols to combine credentials from other groups. This is
-  probably inefficient (or, at least, more than doing so wihtout having to
-  create ad hoc groups), but at least allows the enhanced functionality...}
-
 \subsection{Restricting to Conventional GS and AC Schemes}
@@
   one credential per user, becomes a conventional GS scheme.}
+
+\todo{Also, restrict \UAS to ``plain'' \GSAC.}
 
@@
 
+\subsection{Functional Signatures}
+
+\todo{I think that, by making \yeval explicit, \UAS is essentially a
+  privacy-preserving extension to Functional Signatures. Still, I read that paper
+  quite some time ago. Re-check.}
+
 %%% Local Variables:

### 2022-04-19 prism-backend/research/gsac/construction-uas.tex
First draft of forge-issue proof. Working on forge-sign. Refined properties.

@@
 \paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\upk,\scred,\attrs)\rangle$.} %
+  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\upk,\sipk,\attrs)\rangle$.} %
 The protocol is run between an issuer, and a user with secret key \usk and
@@
 e.g., from secure storage, given \cred), and attests attributes
-$\attrs_{\cred}$. The user
-requests a signature on a commitment to the user key, as well as on the
-attributes in \attrs. In addition, the user proves that the issuance function
-\fissue established by the issuer is satisfied by the credentials in $\scred$
+$\attrs_{\cred}$. For readability we write $\attrs_{\scred}$ as abbreviation for
+$\lbrace \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for
+$\sipk_{\scred}$. The user requests a signature on a commitment to the user key,
+as well as on the attributes in \attrs. In addition, the user proves that the
+issuance function \fissue established by the issuer is satisfied by the
+credentials in $\scred$
 and its user secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace
-(\usk,\scred), (\Ccom,\attrs): \Ccom = \CCommit(usk) \land \fissue(\usk,\scred,
-\attrs) = 1 \land \forall \cred \in \scred, \SBCMVerify(\ipk_{\cred},\cred,
+(\usk,\scred,\attrs_{\scred}), (\Ccom,\attrs,\sipk_{\scred}): \Ccom = \CCommit(usk) \land
+\fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in \scred,
+\SBCMVerify(\ipk_{\cred},\cred,
 \attrs_{\cred} \cup \lbrace \usk \rbrace) = 1 \rbrace$. The interactive protocol
@@
   \CCommit(\usk)$. Compute proof $\NIZKproof \gets
-  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred),(\Ccom,
-  \attrs))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
+  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred,\attrs_{\scred}),
+  (\Ccom,\attrs))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
 \item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
-  (\NIZKcrs_{\Issue},\NIZKproof,(\Ccom,\attrs))$, and abort if it fails. Then,
+  (\NIZKcrs_{\Issue},\NIZKproof,(\Ccom,\attrs,\sipk))$, and abort if it fails. Then,
   compute the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,
-  \attrs)$. Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\cred,
-  \NIZKproof)$.
+  \attrs)$. Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\sipk,
+  \cred,\NIZKproof)$.
 \item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
@@
 In the signing algorithm, we make use of the following relation:
-$\NIZKRel_{\Sign} = \lbrace (\usk,\scred,\yinsp),(\msg,\feval,\yeval,\Ec,\sipk)
-: \Ec = \EEnc(\Eek,\yinsp) \land \yeval = \feval(\usk,\scred,\msg) \land
+$\NIZKRel_{\Sign} = \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r),(\msg,\feval,
+\yeval,\Ec,\sipk_{\scred},\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land \yeval =
+\feval(\usk,\scred,\msg) \land
 \yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
 \SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1)
-\rbrace$ where, for each $\cred \in \scred$, $\attrs_{\cred}$ and $\ipk_{\cred}$
-are as in $\langle \Obtain,\Issue \rangle$.
+\rbrace$ where, for each $\cred \in \scred$, $\attrs_{\cred}$ and $\ipk_{\cred}$,
+as well as $\attrs_{\scred}$ and $\sipk_{\scred}$ are as in $\langle \Obtain,
+\Issue \rangle$.
 %
@@
 compute $\yinsp \gets \finsp(\yeval,\usk,\scred,\msg)$, and encrypt it with
-\Eek by running $\Ec \gets \EEnc(\Eek,\yeval)$. Finally, the user computes
+\Eek by running $\Ec \gets \EEnc(\Eek,\yeval;r)$ for some fresh randomness $r$.
+Finally, the user computes
 $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
-\yinsp),(\msg,\feval,\yeval,\Ec,\sipk))$ and  outputs $(\sig = (\NIZKproof,\Ec),
-\yeval)$.
+\attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek))$ and
+outputs $(\sig = (\NIZKproof,\Ec),\yeval)$.
 

### 2022-04-19 prism-backend/research/gsac/model-uas.tex
First draft of forge-issue proof. Working on forge-sign. Refined properties.

@@
 \item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
-  returns a global system parameter variable \parm.
+  returns a global system parameter variable \parm. We assume that \parm are
+  available to all the other functions, even if not explicitly listed in their
+  input parameters.
 \item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
@@
 \paragraph{Helper functions \ExtractIssue and \ExtractSign.} In our modelling,
-we assume the existence of two functions, \ExtractIssue and \ExtractSign. They
-are not functions available in the actual scheme, but rather to the challenger,
-in the experiments we use to formalize security fof \UAS. Indeed, similar
-techniques have been used before to prove security in privacy-preserving schemes
-with some sort of accountability, but that do not offer conventional opening as
-vanilla group signatures. For instance, see related works on DAA
-\cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}
-More concretely, both functions are as follows:
+we assume the existence of three functions, \Identify, \ExtractIssue and
+\ExtractSign. They are not functions available in the actual scheme, but rather
+to the challenger, in the experiments we use to formalize security fof \UAS.
+Indeed, similar techniques have been used before to prove security in
+privacy-preserving schemes with some sort of accountability, but that do not
+offer conventional opening as vanilla group signatures. For instance, see
+related works on DAA \cite{bfg+11,cdl16} and group signature variants
+\cite{dl21,fgl21,gl19,lnpy21}. More concretely, both functions are as follows:
 
 \begin{description}
-\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\scred)$.] Receives an
-$\langle \Obtain, \Issue \rangle$ transcript, and returns the credentials (if
-any) and user secret key used during the execution of the protocol. It clearly
-needs an honest issuer as, otherwise, the transcripts won't be available.
+\item[$\Identify(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
+  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
+  Otherwise, it returns $0$.
+\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\scred,\attrs_{\scred})$.]
+  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
+  credentials (if any), their attributes, and the user secret key used during
+  the execution of the $\langle\Obtain,\Issue\rangle$ protocol. It clearly needs
+  an honest issuer as, otherwise, the transcripts won't be available.
   Consequently, we only use it to define the properties that require an honest
@@
 
-Note that, both for \ExtractIssue and \ExtractSign, in the case of transcripts
-and signatures by honest users, it is enough to have access to the corresponding
-state information (described below) maintained by the challenger in our
-experiments. For join transcripts of corrupt users, or dishonestly produced
-signatures, we do need to perform actual extraction. How to do this will depend
-on each specific construction. Certainly, the challenger needs special
-knowledge/power such as decryption trapdoors, the ability to rewind the game, or
-program random oracles; the approach needs thus to depend on the concrete
-construction. Although, for the case of \ExtractIssue, online extractability
-(or alternative requirements, such as non-parallel or logarithmic number of
-joins) is necessary. \todo{\needcite Paper from Camenisch and Shoup on the need
+Note that, both for the three functions, in the case of credentials,
+transcripts, and signatures by honest users, it is enough to have access to the
+corresponding state information (described below) maintained by the challenger
+in our experiments. For credentials and join transcripts of corrupt users, or
+dishonestly produced signatures, we do need to perform actual extraction. How to
+do this will depend on each specific construction. Certainly, the challenger
+needs special knowledge/power such as decryption trapdoors, the ability to
+rewind the game, or program random oracles; the approach needs thus to depend on
+the concrete construction. Although, for the case of \ExtractIssue, online
+extractability (or alternative requirements, such as non-parallel or logarithmic
+number of joins) is necessary. %
+\todo{\needcite Paper from Camenisch and Shoup on the need
   for online extractability?} \todo{How do we do this in our construction(s)?
@@
 
-% \paragraph{Extractability.} %
-% \commentwho{Jesus}{I have a doubt here. On one hand, modelling the
-%   extractability-related properties here as in \cite{lnpy21} would lead to
-%   redundancy with the current unforgeability properties. I do like the
-%   precission in the definition of \cite{lnpy21}; but I do not like that,
-%   within the extractability property, they include ``domain-specific''
-%   concepts (e.g., open, etc.) On the other hand, we could model extractability
-%   as (an extension of) the Identify approach in e.g. \cite{gl19,dl21}. What
-%   I like about that is that it would not be redundant (we just assume the
-%   existance of a function extracting some secret values). What I do not like,
-%   is that the definition is not as precise as in \cite{lnpy12}. Namely, at the
-%   design stage, one just has to informally describe what Identify-Extract does;
-%   then, what it *really* does, has to be defined in the security proofs. That
-%   is, its definition is somehow deferred, which makes the presentation a bit
-%   harder to follow, IMO.}
-
-% Before getting into the ``actual'' security properties, we introduce an
-% auxiliary yet crucial property, extractability, that will allow us to formally
-% define unforgeability-related properties in a meaningful way. More concretely,
-% we require issuance extractability, and signing extractability. Informally, with
-% issuance extractability we require that given an additional trapdoor generated
-% at setup time, it is possible to extract the witnesses (user secret key and
-% credentials) used to request issuance of a new credential, from its $\langle
-% \Obtain,\Issue \rangle$ transcript. With signing extractability, we refer to the
-% requirement to be able to extract, given an additional trapdoor, the user secret
-% key and credentials used to produce any (possibly maliciously generated)
-% signature. The need to differentiate both comes from the fact that, for issuance
-% extractability, we need to assume honest issuers -- as otherwise, the $\langle
-% \Obtain,\Issue\rangle$ transcripts may
-% just not exist. Other than that, both properties are essentially the same: given
-% some proof an instance of an NP relation, they allow extracting the
-% corresponding witnesses. The need to resort to this extraction technique comes
-% from the fact of not including a conventional opening functionality. Indeed,
-% this has been used (at times, somehow implicitly) in related works on DAA
-% \cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}.
-
-% In more detail, we require the existence of three additional algorithms,
-% \ExtractSetup, \ExtractIssue, and \ExtractSign, as follows:
-
-% \begin{description}
-% \item[$\ExtractSetup(1^\secpar) \rightarrow (\parm,\extracttrap)$.] \todo{Describe,
-%     and mention that it must be indistinguishable from \Setup.}
-% \item[$\ExtractIssue(\extracttrap,\utrans) \rightarrow (\usk,\scred)$.] \todo{Describe.}
-% \item[$\ExtractSign(\extracttrap,\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,\scred)$.]
-%   \todo{Describe.}
-% \end{description}
-
-% With these algorithms, we formally define the issuance extractability and
-% signing extractability properties as shown in \figref{fig:exp-uas-extract}.
-
-% \begin{figure}[htp!]
-%   \procedure{$\ExpExtractIssue(\utrans)$}{%
-%     \pcreturn (\usk,\scred) \\    
-%   }
-
-%   \procedure{$\ExpExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
-%     \pcreturn (\usk,\scred)
-%   }
-
-%   \caption{Issuance and signing extractability experiments for \UAS schemes.}
-%   \label{fig:exp-uas-extract}
-% \end{figure}
-
-% \begin{definition}{(Extractable issuance of \UAS)}
-%   We define the advantage \AdvExtractIssue of $\adv$ against \ExpExtractIssue as
-%   $\AdvExtractIssue=\Pr\lbrack\ExpExtractIssue(1^\secpar)=1\rbrack$.
-%   %
-%   A \UAS scheme has extractable issuance if, for any p.p.t. adversary $\adv$,
-%   \AdvExtractIssue is a negligible function of $1^\secpar$.
-% \end{definition}
-
-% \begin{definition}{(Extractable signing of \UAS)}
-%   We define the advantage \AdvExtractSign of $\adv$ against \ExpExtractSign as
-%   $\AdvExtractSign=\Pr\lbrack\ExpExtractSign(1^\secpar)=1\rbrack$.
-%   %
-%   A \UAS scheme has extractable signing if, for any p.p.t. adversary $\adv$,
-%   \AdvExtractSign is a negligible function of $1^\secpar$.
-% \end{definition}
-
-% For short, we say that an \UAS scheme that has both extractable issuance and
-% signing, is an extractable \UAS scheme.
-
 \paragraph{Anonymity.} %
@@
       \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
-      w \gets \ExtractIssue(\trans[\cid]) \\
-      \pcif w = \bot: \pcreturn 1 \\
-      \textrm{Parse}~w~\textrm{as}~(\usk,\lbrace (\cred_i,\ipk_i)
-      \rbrace_{i \in \Issuers})  \\      
-      \pcif \fissue(\usk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
-      \ATTR[\cid]) = 0: \pcreturn 1 \\
+      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trans[\cid]) \\
+      \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
+      \exists \cred \in \scred~\st~\Identify(\usk,\attrs_{\cred},\cred) = 0: \\
+      \pcind \pcreturn 1 \\
       \pcreturn 0
@@
       (\yinsp,\iproof) \gets \Inspect(\PRVOK[\oid],\siid,\sig,\yeval,\msg) \\
-      \pcif \yinsp = \bot \lor \iproof = \bot \lor       
-      \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg,\feval)
+      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg,\feval)
       = 0: \pcreturn 0 \\
-      (\usk,\scred) \gets \ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \\
+      (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets \ExtractSign(\oid,\siid,\sig,
+      \yeval,\msg,\feval) \\
       \pcif \feval(\usk,\scred,\msg) \neq \yeval: \pcreturn 1 \\
-      \pcif \finsp(\yeval,\usk,\scred,\msg) \neq \yinsp: \pcreturn 1 \\
+      \pcif \finsp(\yeval,\usk,\scred,\msg) \neq \yinsp \lor \yinsp \neq \yinsp':
+      \pcreturn 1 \\
+      \pcif \exists \cred \in \scred~\st~\Identify(\usk,\attrs_{\cred},\cred) = 0:
+      \pcreturn 1 \\
       \pcreturn 0

### 2022-04-19 prism-backend/research/gsac/security-uas.tex
First draft of forge-issue proof. Working on forge-sign. Refined properties.

\subsection{Correctness and Security of \CUASGen}
\label{ssec:security-uas}

First, we define the \Identify, \ExtractIssue and \ExtractSign functions that
are needed for some of the properties to be meaningful, in
\figref{fig:helper-funcs}.

\begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \procedure{$\ExtractIssue(\parm,\trans)$}{%
      \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Issue},\cdot,
        \cdot,\cdot)$; $\NIZKcrs_{\Issue}$ as $(\NIZKcrs,\NIZKext)$; and
        \trans as $(\Ccom,\attrs,\sipk,\cred,\NIZKproof)$} \\
      \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\Ccom,\attrs,\sipk)): 
      \pcreturn \bot \\
      (\usk,\scred,\attrs_{\scred}) \gets \NIZKExtII(\NIZKcrs,\NIZKext,
      (\Ccom,\attrs,\sipk),\NIZKproof) \\
      \pcreturn (\usk,\scred,\attrs_{\scred}) \\
    }

    \procedure{$\ExtractSign(\parm,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
      \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
        \cdot,\cdot)$; $\NIZKcrs_{\Sign}$ as $(\NIZKcrs,\NIZKext)$; and
        \sig as $(\NIZKproof,\Ec)$} \\
      \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \get
        \PUBIK[\siid]$} \\
      \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,
      \sipk,\opk)): \pcreturn \bot \\
      (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets \NIZKExtII(\NIZKcrs,\NIZKext,
      (\msg,\feval,\yeval,\Ec,\sipk,\opk),\NIZKproof) \\
      \pcreturn (\usk,\scred,\attrs_{\scred},\yinsp) \\
    }

    \procedure{$\Identify(\usk,\attrs_{\cred},\cred)$}{%
      \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup
      \lbrace \usk \rbrace) \\
    }    
  \end{minipage}
  \label{fig:helper-funcs}
  \caption{Definition of helper functions \Identify, \ExtractIssue and
    \ExtractSign, for \CUASGen.}
\end{figure}

\begin{theorem}[Correctness of \CUASGen]
  \label{thm:correctness-uas}
  If the underlying schemes for vector commitments, encryption, digital
  signatures, signatures on blocks of committed messages, and NIZKs are
  correct, our generic construction \CUASGen satisfies correctness as
  defined in \defref{def:correctness-uas}.
\end{theorem}

\begin{proof}[\thmref{thm:correctness-uas}]
  \todo{XXX}
\end{proof}

\begin{theorem}[Anonymity of \CUASGen]
  \label{thm:anonymity-uas}
  If the underlying encryption scheme is \todo{IND-CCA}, the vector commitment
  scheme is \todo{binding}, the scheme for signatures on blocks of committed
  messages is \todo{XXX}, and the NIZKs used for $\NIZKRel_{\Issue},
  \NIZKRel_{\Sign}$, and $\NIZKRel_{\Inspect}$ are \todo{zero-knowledge} and
  \todo{simulation-sound?}, our \CUASGen construction satisfies anonymity as
  defined in \defref{def:anonymity-uas}.
\end{theorem}

\begin{proof}[\thmref{thm:anonymity-uas}]
\end{proof}

\begin{theorem}[Issuance unforgeability of \CUASGen]
  \label{thm:issue-forge-uas}
  If the underlying scheme for signatures on blocks of committed messages is
  existentially unforgeable, and the NIZK used for $\NIZKRel_{\Issue}$ is
  knowledge extractable and sound, then our \CUASGen construction satisfies
  issuance unforgeability as defined in \defref{def:issue-forge-uas}, except
  with negligible probability.
\end{theorem}

\todo{\usk belongs to \AttrSpace! I think this can lead to malleability attacks.
  Make them disjoint?}

\begin{proof}[\thmref{thm:issue-forge-uas}]
  We show that the probability that \fissue outputs $0$ is negligible, as well
  as the probability that the extracted \usk is not the one that was used to
  request some of the credentials employed to obtain the credential specified by
  the adversary.
  %
  For this purpose, we define two games, $G_0=\ExpForgeIssue$, and $G_1$, which
  is exactly the same, but where, within the \Setup algorithm, we replace
  $\NIZKSetup^{\Issue}$ with $\NIZKExtI^{\Issue}$. As per the definition of
  \NIZK in \appref{sapp:nizk}, both games are indistinguishable.

  Now, observe that the adversary is required to output a credential
  identifier for which associated entries in \trans and \CRED exist; moreover,
  if such a credential was produced by an issuer, we must have access to those
  entries, as issuers are assumed to be honest.
  %
  Then, given that $\NIZKRel_{\Issue}$ is knowledge extractable, in game $G_1$
  we can apply the \NIZKExtII function, which produces a tuple $(\usk,\scred,
  \attrs_{\scred})$ from $\utrans = (\Ccom,\attrs,\sipk,\cred,\NIZKproof)$.
  %
  Since \NIZKproof is accepted by \ExtractIssue, from the soundness of \NIZK and
  existential unforgeability of \SBCM, we know that all $\cred \in \scred$ are
  valid signatures over \usk, and their respective $\attrs_{\cred}$. Thus,
  \Identify returns $1$ for all $(\usk,\attrs_{\cred},\cred)$ tuples.
  Moreover, all the credentials in \scred given to \fissue belong to the same
  user, who is the owner of \usk.
  %
  Finally, since issuers are honest, we know that $\ATTR[\cid] = \attrs$ and,
  consequently, $\fissue(\usk,\scred,\ATTR[\cid]) = \fissue(\usk,\scred,\attrs)
  = 1$, due to the soundness of \NIZK.
  %
  \qed
\end{proof}

\begin{theorem}[Signing unforgeability of \CUASGen]
  \label{thm:sign-forge-uas}  
\end{theorem}

\begin{proof}[\thmref{thm:sign-forge-uas}]
  As for \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
  and $G_1$, which is exactly the same, but where, within the \Setup algorithm,
  we replace $\NIZKSetup^{\Sign}$ with $\NIZKExtI^{\Sign}$. As per the
  definition of \NIZK in \appref{sapp:nizk}, both games are indistinguishable.
  %
  First, observe that, for the adversary to win the game, the signature it
  outputs cannot be an honestly produced signature -- via a call to the \SIGN
  oracle. Moreover, the signature is accepted by \Verify. Hence, the underlying
  NIZK proof \NIZKproof is accepted by \NIZKVerify due to soundness of the
  NIZK scheme; and \NIZKExtII produces a $(\usk,\scred,\attrs_{\scred},
  \yinspect,r)$ tuple after knowledge extractability of NIZK.

  and an honest
  execution of \Inspect produces a result that is accepted by \Judge.
  \qed
\end{proof}

\begin{theorem}[Non-frameability of \CUASGen]
  \label{thm:frame-uas}
\end{theorem}

\begin{proof}[\thmref{thm:frame-uas}]
\end{proof}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:

### 2022-04-21 prism-backend/research/gsac/app-building-blocks.tex
Added formalisation of commitment schemes.

@@
 
-Defined as a tuple $(\SSetup,\SKeyGen,\SSign,\SVerify)$. Algorithm $\Sparm \gets
-\SSetup(\Ssecpar)$ produces public parameters for the other algorithms.
-$(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$ generates the verification-signing key
-pair, algorithm $\Ssig \gets \SSign(\Ssk,\msg)$ signs message \msg with
-signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\Svk,
-\Ssig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
-verification key \Svk. \todo{Informally define security properties we'll need.}
+We rely on digital signatures as a core building block. A digital signature
+provides the functionality defined by the following syntax:
+
+\begin{description}
+\item[$\Sparm \gets \SSetup(\Ssecpar)$.] It produces public parameters for the
+  other algorithms, given an input security parameter \Ssecpar.
+\item[$(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$.] Generates a verification-signing
+  key pair.
+\item[$\Ssig \gets \SSign(\Ssk,\msg)$.] Signs message \msg with signing key
+  \Ssk, producing signature \Ssig,  
+\item[$1/0 \gets \SVerify(\Svk,\Ssig,\msg)$.] Checks whether \Ssig is a valid
+  signature over \msg, under verification key \Svk.
+\end{description}
+
+A digital signature scheme is correct if honestly generated signatures, using
+honestly generated key pairs, are always accepted by \SVerify. \todo{define more
+  formally?}
+%
+A digital signature scheme \S has existential unforgeability if, for all p.p.t.
+adversaries $\adv$, $\Pr[\ExpEUF = 1]$ is a negligible function of the
+security parameter.
+
+\begin{figure}[ht!]
+  \begin{minipage}[t]{0.5\textwidth}
+    \procedure{$\ExpEUF(\Ssecpar)$}{%
+      \Sparm \gets \SSetup(\Ssecpar) \\
+      (\Svk,\Ssk) \gets \SKeyGen(\Sparm) \\
+      (\Ssig,\msg) \gets \adv^{\SSign(\Ssk,\cdot)}(\Svk) \\
+      \pcif \SVerify(\Svk,\Ssig,\msg) = 0: \pcreturn 0 \\
+      \pcif \msg~\textrm{was not queried to \SSign}: \pcreturn 1 \\
+      \pcreturn 0
+    }
+  \end{minipage}
+  \label{fig:euf-game}
+  \caption{Existential Unforgeability Game.}
+\end{figure}
 
@@
 
-\subsection{Vector Commitments}
-\label{sapp:vector-commitments}
+\subsection{Commitments}
+\label{sapp:commitments}
 
-Defined as a tuple $(\CSetup,\CCommit)$. Algorithm $\Cparm \gets
-\CSetup(\Csecpar)$ produces the parameters for committing to values. $\Ccom
-\gets \CCommit(\Cparm, \msgset; r)$ produces a commitment \Ccom over a set of
-messages \msgset, from which we may omit randomness $r$. \todo{Informally define
-  hiding and binding, leaving formal definitions to the appendix.}
+A commitment scheme is defined by the following algorithms:
+
+\begin{description}
+\item[$\Cparm \gets \CSetup(\Csecpar)$.] Given a security parameter \Csecpar,
+  returns the public parameters \Cparm to commit messages.
+\item[$\Ccom \gets \CCommit(\Cparm,\msg,r)$.] Given the public parameters and
+  a message \msg, outputs a commitment \Ccom to \msg, for which randomness $r$
+  from some predefind randomness space $\mathcal{R}$ is used.
+\end{description}
+
+Opening a commitment \Ccom means revealing the message \msg and randomness $r$
+that were used to produce \Ccom. Commitment schemes are required to be binding
+and (usually) hiding:
+
+\begin{description}
+\item[Binding.] Intuitively, the binding property of commitment schemes means
+  that no adversary can change the message that has been committed to. More
+  formally, $\Pr[\ExpComBind = 1]$ must be a negligible function of the security
+  parameter.
+\item[Hiding.] The hiding property captures that no adversary should be able to
+  learn the message that was committed, when given only the commitment. This is
+  formally defined through \ExpComHideb, where $|\Pr[\ExpComHideb=1|b=1] -
+  \Pr[\ExpComHideb=1|b=0]|$ must be a negligible function of the security
+  parameter.
+\end{description}
+
+\begin{figure}[ht!]
+  \begin{minipage}[t]{0.5\textwidth}
+    \procedure{$\ExpComBind(\secpar)$}{%
+      \Cparm \gets \CSetup(\secpar) \\
+      (\msg_0,r_0,\msg_1,r_1) \gets \adv(\Cparm) \\
+      \Ccom_0 \gets \CCommit(\Cparm,\msg_0,r_0) \\
+      \Ccom_1 \gets \CCommit(\Cparm,\msg_1,r_1) \\
+      \pcif \msg_0 \neq \msg_1 \land \Ccom_0 = \Ccom_1: \pcreturn 1 \\
+      \pcreturn 0
+    }
+  \end{minipage}
+  \begin{minipage}[t]{0.5\textwidth}
+    \procedure{$\ExpComHideb(\secpar)$}{%
+      \Cparm \gets \CSetup(\secpar) \\
+      (\msg_0,\msg_1,st) \gets \adv(\Cparm) \\
+      r \getr \mathcal{R} \\
+      \Ccom \gets \CCommit(\Cparm,\msg_b,r) \\
+      b' \gets \adv(st,\Ccom) \\
+      \pcreturn b'
+    }
+  \end{minipage}
+  \label{fig:nizk-games}
+  \caption{Games for commitment schemes.}
+\end{figure}
+
+\paragraph{Commitments on Blocks of Messages.} We also use an extension
+of commitment schemes that allows committing to multiple messages at once. The
+properties we need are the same, and their definitions are extended in the
+natural way. Namely, $\CCommit$ receives a vector/block of messages, \msgset
+instead of a single message. In the games, the adversary returns sets of
+messages and, in the binding game, the comparison $\msg_0 \neq \msg_1$ now
+compares sets $\msgset_0$ and $\msgset_1$, which must differ in at least one
+element. This extension is straight-forward, for instance, from Pedersen
+commitments \cite{bcc+15}.
 

### 2022-04-21 prism-backend/research/gsac/security-uas.tex
Added formalisation of commitment schemes.

@@
         \sig as $(\NIZKproof,\Ec)$} \\
-      \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \get
+      \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \gets
         \PUBIK[\siid]$} \\
@@
   issuance unforgeability as defined in \defref{def:issue-forge-uas}, except
-  with negligible probability.
+  with negligible probability. \todo{EUF of \SBCM?}
 \end{theorem}
@@
   \label{thm:sign-forge-uas}
+  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is sound and knowledge
+  extractable, the NIZK scheme for $\NIZKRel_{\Inspect}$ is sound and knowledge
+  extractable, and \SBCM is existentially unforgeable, then our \CUASGen
+  construction satisfies signing unforgeability as defined in
+  \defref{def:sign-forge-uas}, except with negligible probability.
 \end{theorem}
@@
   definition of \NIZK in \appref{sapp:nizk}, both games are indistinguishable.
+
+  In order to define the winning conditions for the adversary in the signing
+  unforgeability game, consider the following events:
+
+  \begin{description}
+  \item[$V$.] Where $V = \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval) = 1$.
+  \item[$J$.] Where $J = \Judge(\opk,\sipk,\yinsp,\iproof,\sig,\yeval,\msg,
+    \feval) = 0$.
+  \item[$L$.] Where $L = (\msg,\feval,\yeval,\Ec,\sipk,\opk) \in
+    \NIZKLang^{\Sign}$.    
+  \item[$I$.] Where $I = \exists \cred \in \scred~\st~\Identify(\usk,
+    \attrs_{\cred},\msg) = 0$.
+  \end{description}
+
+  $\adv$ wins if $V \land (J \lor I) = (\overline{L} \land V \land (J \lor I))
+  \lor (L \land V \land (J \lor I))$.
   %
-  First, observe that, for the adversary to win the game, the signature it
-  outputs cannot be an honestly produced signature -- via a call to the \SIGN
-  oracle. Moreover, the signature is accepted by \Verify. Hence, the underlying
-  NIZK proof \NIZKproof is accepted by \NIZKVerify due to soundness of the
-  NIZK scheme; and \NIZKExtII produces a $(\usk,\scred,\attrs_{\scred},
-  \yinspect,r)$ tuple after knowledge extractability of NIZK.
+  $V$ implies that $(\msg,\feval,\yeval,\Ec,\sipk,\opk) \in \NIZKRel^{\Sign}$.
+  Thus, after soundness of $\NIZK^{\Sign}$, the probability of $\overline{L}
+  \land V \land (J \lor I)$ is negligible in the security parameter.
+  %
+  For $(L \land V \land (J \lor I))$ to be satisfied, there are three cases:
+  \begin{enumerate}
+  \item $L \land V \land J \land \overline{I}$. The game returns 1 in step 6.
+  \item $L \land V \land J \land I$.  The game returns 1 in step 6.
+  \item $L \land V \land \overline{J} \land I$. The game returns 1 in step 10. 
+  \end{enumerate}
 
-  and an honest
-  execution of \Inspect produces a result that is accepted by \Judge.
+  In case 1, $L \land V$ implies that $(\msg,\feval,\yeval,\Ec,\sipk,\opk) \in
+  \NIZKRel^{\Sign}$. More concretely, soundness of $NIZK^{\Sign}$ implies that
+  $\Ec = \EEnc(\opk,\yinsp;r)$, for $\yinsp$ and $r$ known to the signer. Since
+  $(\yinsp,\iproof)$ is generated honestly by the challenger from
+  $(\opk,\sipk,\sig = (\NIZKproof_{\Sign},\Ec),\yeval,\msg)$, correctness of
+  public key encryption implies that $\EDec(\osk,\Ec) = \yinsp$. Consequently,
+  the probability of $L \land V \land J \land \overline{I}$ = 0, as \Judge
+  checks precisely that \Ec is a correct encryption of \yinsp under \opk.
+
+  The analysis for case 2 is the same as for case 1.
+
+  For case 3, $(\msg,\feval,\yeval,\Ec,\sipk,\opk) \in \NIZKRel^{\Sign}$,
+  $\Judge(\opk,\sipk,\yinsp,\iproof,\sig,\yeval,\msg,\feval)
+  = 1$, but there exists some credential \cred for which $\Identify(\usk,
+  \attrs_{\cred},\msg)=0$. Note that \usk, $\attrs_{\cred}$ and \cred (for all
+  $\cred \in \scred$) are output by \ExtractSign. Thus, after the knowledge
+  extraction property and soudness of $\NIZK^{\Sign}$, $(\msg,\feval,\yeval,\Ec,
+  \sipk,\opk) \in \NIZKRel^{\Sign}$, which more concretely means that
+  $\SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1
+  = \Identify(\usk,\attrs_{\cred},\cred)$, for all $\cred \in \scred$. The
+  probability of case 3 is therefore $0$.
+  %
+  Moreover, since \SBCMVerify returns $1$ for all $\cred \in \scred$, it must
+  be that all of them were obtained via queries to the \ISSUE or \OBTISS
+  oracles. Otherwise, if there exists some \cred that was not obtained via
+  a call to these oracles, the pair $(\lbrace \usk \rbrace \cup \attrs_{\cred},
+  \cred)$ constitutes an existential forgery of \SBCM.
+
+  Cases 1, 2 and 3 above account for winning conditions at steps 6 and 10.
+  % 
+  Additionally, $\adv$ wins at step 8 if $\feval(\usk,\scred,\msg) \neq \yeval$,
+  where \yeval is the value output by the adversary in step 2. However, since
+  $\Verify(\opk,\sipk,\sig,\yeval,\msg,\feval) = 1$, soundness of $NIZK^{\Sign}$
+  implies that this has negligible probability.
+  %
+  Similarly, $\adv$ wins at step 9 if (1) $\finsp(\yeval,\usk,\scred,\msg) \neq
+  \yinsp$, where \yinsp is the value output by \Inspect at line 5; or if (2)
+  $\yinsp \neq \yinsp'$, where $\yinsp'$ is the value extracted by \ExtractSign
+  at step 7. For (1), soundness of $\NIZK^{\Sign}$ ensures that \yinsp is the
+  correct evaluation of \finsp, whereas soundness of $\NIZK^{\Inspect}$ and
+  correctness of the public key encryption ensure that this is also the value
+  output by \Inspect. Thus, the probability of $\adv$ winning the game because
+  of (1) is negligible. Finally, for (2), knowledge extractability of
+  $\NIZK^{\Inspect}$ and correctness of the public key encryption ensure that
+  the $\yinsp'$ value extracted by \NIZKExtII matches the value produced by
+  \Inspect.
+  %
   \qed
@@
   \label{thm:frame-uas}
+  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is sound and knowledge
+  extractable, and the \SBCM scheme is existentially unforgeable, then our
+  \CUASGen construction satisfies non-frameability as defined in
+  \defref{def:frame-uas}, except with negligible probability.  
 \end{theorem}
@@
 \begin{proof}[\thmref{thm:frame-uas}]
+  As for \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpNonframe$,
+  and $G_1$, which is exactly the same, but where, within the \Setup algorithm,
+  we replace $\NIZKSetup^{\Sign}$ with $\NIZKExtI^{\Sign}$. As per the
+  definition of \NIZK in \appref{sapp:nizk}, both games are indistinguishable.
+
+  Next, assume that the adversary wins in $G_1$. This means that $G_1$ outputs
+  $1$ at step 7, which implies that the signature and inspection proof produced
+  by the adversary at step 2 are accepted respectively by \Verify at step 4, and
+  by \Judge at step 5. This means that 
 \end{proof}

### 2022-04-24 prism-backend/research/gsac/app-building-blocks.tex
Proof on non-frameability. Some other minor edits.

@@
   \end{minipage}
-  \label{fig:nizk-games}
+  \label{fig:com-games}
   \caption{Games for commitment schemes.}
@@
 
-\subsection{Non-Interactive Zero-Knowledge Proofs of Knowledge}
+\subsection{Simulation-Extractable Non-Interactive Zero-Knowledge
+  Proofs of Knowledge}
 \label{sapp:nizk}
@@
 (\NIZKw): f(x,w) \rbrace$, where $f(x,w)$ is a boolean predicate denoting the
-concrete conditions that \NIZKx and \NIZKw need to meet. The set of all $(\NIZKx,
-\NIZKw) \in \NIZKRel$ is called the language, or \NIZKLang, for \NIZKRel.
-$\NIZKx \notin \NIZKLang$ means that there is no $\NIZKw$ such that $(\NIZKx,
-\NIZKw) \in \NIZKRel$. \todo{Check this definition.}
+concrete conditions that \NIZKx and \NIZKw need to meet. The set of all \NIZKx
+such that there exists a \NIZKw for which $(\NIZKx,\NIZKw) \in \NIZKRel$ is the
+language, or \NIZKLang, for \NIZKRel. $\NIZKx \notin \NIZKLang$ means that
+there is no $\NIZKw$ such that $(\NIZKx,\NIZKw) \in \NIZKRel$.
 
@@
 
-Moreover, a NIZK system has additional algorithms $(\NIZKSimI,\NIZKSimII)$ and
-$(\NIZKExtI,\NIZKExtII)$ defined as follows:
+Any zero-knowledge proof of knowledge must meet completeness, soundness and
+zero-knowledge,properties. We further need an extra property, called
+\emph{simulation-extractability} \cite{cl06}, which amplifies the security
+requirements of simulation soundness.
+%
+To define more formally the properties we need, we have to define three extra
+algorithms:
 
 \begin{description}
-\item[$(\NIZKcrs,\NIZKext) \gets \NIZKSimI(\NIZKsecpar)$.] Produces a \NIZKcrs
-  as the \NIZKSetup algorithm, along with a \todo{simulation} trapdoor.
-  % The output of \NIZKSimI is required to be indistinguishable from that of
-  % \NIZKSetup.
-\item[$\NIZKproof \gets \NIZKSimII(\NIZKcrs,\NIZKext,\NIZKx)$.] Given a
-  \todo{simulation} trapdoor, and a statement $\NIZKx \in \NIZKLang$,
+\item[$(\NIZKcrs,\NIZKtrap) \gets \NIZKSimSetup(\NIZKsecpar)$.] Produces a
+  \NIZKcrs as the \NIZKSetup algorithm, along with a trapdoor \NIZKtrap.
+\item[$\NIZKproof \gets \NIZKSim(\NIZKcrs,\NIZKtrap,\NIZKx)$.] Given a trapdoor
+  \NIZKtrap produced by \NIZKSimSetup, and a statement $\NIZKx \in \NIZKLang$,
   produces a simulated proof \NIZKproof of $\NIZKx \in \NIZKLang$.
-\item[$(\NIZKcrs,\NIZKext) \gets \NIZKExtI(\NIZKsecpar)$.] Produces a \NIZKcrs
-  as the \NIZKSetup algorithm, along with an extraction trapdoor \NIZKext.
-\item[$\NIZKw \gets \NIZKExtII(\NIZKcrs,\NIZKext,\NIZKx,\NIZKproof)$.] Given
-  an extraction trapdoor \NIZKext produced by \NIZKExtI, and a proof \NIZKproof
-  for $\NIZKext \in \NIZKLang$, returns a valid \NIZKw for \NIZKx.
+\item[$\NIZKw \gets \NIZKExtract(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKproof)$.] Given
+  a trapdoor \NIZKtrap produced by \NIZKSimSetup, and a proof \NIZKproof for
+  $\NIZKx \in \NIZKLang$, returns a valid \NIZKw for \NIZKx.
 \end{description}
@@
 $\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and subindex when clear
-from context. Altogether, the tuple $(\Setup,\Prove,\Verify,\ExtI,\ExtII,\SimI,
-\SimII)$ needs to meet the following properties:
+from context. Altogether, the tuple $(\Setup,\Prove,\Verify,\SimSetup,\Sim,
+\Extract)$ needs to meet the following properties:
 
 \paragraph{Completeness.} %
-Ensures that, for any $(\NIZKx,\NIZKw) \in \NIZKRel)$, any honest prover will be
+Ensures that, for any $(\NIZKx,\NIZKw) \in \NIZKRel$, any honest prover will be
 able to create a proof \NIZKproof that is accepted by any honest verifier, with
@@
 
-\paragraph{Knowledge extraction.} %
-For all possible adversaries computing a valid proof \NIZKproof over a statement
-$\NIZKx \in \NIZKLang$, computed using a \NIZKcrs produced by \ExtI and given
-\NIZKext also produced by \ExtI, \ExtII outputs a witness \NIZKw such that
-$(\NIZKx,\NIZKw) \in \NIZKRel$. That is, for all valid statements in the
-language and a proof, we can extract a valid witness given some special
-knowledge ($\NIZKext$). \todo{Capture either here or in the game that the
-  output of \ExtI needs to be indistinguishable to the output of \Setup.}
-
 \paragraph{Zero-knowledge.} %
-Intuitively, captures that no information can be learned from an statement and
+Intuitively, captures that no information can be learned from a statement and
 proof pair, beyond their validity (or not). This is captured by requiring the
@@
 setup is done with \Setup, and $\adv$ has access to an honest prover
-\Prove; and a run in an ideal world ($b=1$), where the setup is run by
-a simulator \SimI, and proofs are generated by \SimII, except when $\adv$
-specifies $(\NIZKx,\NIZKw) \notin \NIZKRel$.
+\Prove; and a run in an ideal world ($b=1$), where the setup is replaced by
+\SimSetup, and proofs are simulated with the help of the trapdoor produced by
+\SimSetup, except when $\adv$ specifies $(\NIZKx,\NIZKw) \notin \NIZKRel$. Note
+that, in the context of simulation-extractable NIZK, this property not only
+requires that the simulated proofs are indistinguishable to the real ones; it
+also requires that \SimSetup is indistinguishable from \Setup. All this is
+formalised by requiring that $|\Pr[\ExpNIZKZKb(\secpar) = 1 | b = 1] -
+\Pr[\ExpNIZKZKb(\secpar) = 1 | b = 0]$ be a negligible function of \secpar,
+where \ExpNIZKZKb is as defined in \figref{fig:nizk-games}.
+
+\paragraph{Simulation-Extractability.} As stated, simulation-extractability
+is an extension to simulation soundness. In a nutshell,
+simulation-extractability requires that, even after having received a polynomial
+number of simulated proofs of knowledge, no adversary can output a valid proof
+of knowledge from which no witness can be extracted. It implies simulation
+soundness, which ``just'' requires that no adversary can produce a valid proof
+after having seen polynomially many simulated proofs (but does not guarantee
+extraction). Formally, for simulation-extractability we require that
+$\Pr[\ExpNIZKSimExt] = 1$ is a negligible function of \secpar, where
+\ExpNIZKSimExt is defined in \figref{fig:nizk-games}.
 
@@
     }
-    \procedure{$\ExpNIZKExt(\secpar)$}{%
-      (\NIZKcrs,\NIZKext) \gets \ExtI(\secpar) \\
-      (\NIZKx,\NIZKproof) \gets \adv(\NIZKcrs) \\
-      \NIZKw \gets \NIZKExtII(\NIZKcrs,\NIZKext,\NIZKx,\NIZKproof) \\
+    \procedure{$\ExpNIZKSimExt(\secpar)$}{%
+      (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\secpar) \\
+      (\NIZKx,\NIZKproof) \gets \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}
+      (\NIZKcrs) \\
+      \pcind \textrm{Where}~\Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
+      \pcind \pcind
+      \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw) \in \NIZKRel \\
+      \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel \\
+      \NIZKw' \gets \Extract(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKproof) \\
       \pcif \Verify(\NIZKcrs,\NIZKproof,\NIZKx) = 1 \land
-      (\NIZKx,\NIZKw) \notin \NIZKRel: \\
-      \pcind \pcreturn 0 \\
-      \pcreturn 1
+      (\NIZKx,\NIZKw') \notin \NIZKRel~\land \\
+      \pcind \NIZKx~\textrm{was not queried to $\Sim$ via $\Sim'$}: \\
+      \pcind \pcreturn 1 \\
+      \pcreturn 0
     }    
@@
     }
+
     \procedure{$\ExpNIZKZKb(\secpar)$}{%
@@
       \pcif b = 1: \\
-      \pcind (\NIZKcrs,\NIZKext) \gets \SimI(\secpar) \\
-      \pcind \pcreturn \adv^{\Sim'(\NIZKcrs,\NIZKext,\cdot,\cdot)}(\NIZKcrs),~
+      \pcind (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\secpar) \\
+      \pcind \pcreturn \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}(\NIZKcrs),~
       \textrm{where} \\
-      \pcind \Sim'(\NIZKcrs,\NIZKext,\NIZKx,\NIZKw)~\textrm{returns} \\
-      \pcind \pcind \SimII(\NIZKcrs,\NIZKext,\NIZKx)~\pcif (\NIZKx,\NIZKw)
+      \pcind \Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
+      \pcind \pcind \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw)
       \in \NIZKRel \\
@@
   \label{fig:nizk-games}
-  \caption{Games for NIZK schemes.}
+  \caption{Games for Simulation-Extractable NIZK schemes.}
 \end{figure}
 
-\iffalse
-\paragraph{Simulation Soundness.} %
-\fi
+As studied in \cite{cl06}, simulation-extractable NIZKPoKs formalize the concept
+of ``signatures of knowledge'' (see, e.g., \cite{cs97}). Which basically means
+that, given an $(\NIZKx,\NIZKw)$ pair from an NP relation, we can treat \NIZKx
+as a public key, and \NIZKw as its corresponding private key, and leverage them
+to build digital signature schemes -- with the advantage of being able to do so
+while proving arbitrary claims, as long as they can be represented as an NP
+relation. We note that, given a simulation-extractable NIZK system, it is
+straightforward to build a signature of knowledge by adding the message to be
+signed in the statement of the NIZK.
 

### 2022-04-24 prism-backend/research/gsac/security-uas.tex
Proof on non-frameability. Some other minor edits.

@@
       \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Issue},\cdot,
-        \cdot,\cdot)$; $\NIZKcrs_{\Issue}$ as $(\NIZKcrs,\NIZKext)$; and
+        \cdot,\cdot)$; $\NIZKcrs_{\Issue}$ as $(\NIZKcrs,\NIZKtrap)$; and
         \trans as $(\Ccom,\attrs,\sipk,\cred,\NIZKproof)$} \\
@@
       \pcreturn \bot \\
-      (\usk,\scred,\attrs_{\scred}) \gets \NIZKExtII(\NIZKcrs,\NIZKext,
+      (\usk,\scred,\attrs_{\scred}) \gets \NIZKExtract(\NIZKcrs,\NIZKtrap,
       (\Ccom,\attrs,\sipk),\NIZKproof) \\
@@
       \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
-        \cdot,\cdot)$; $\NIZKcrs_{\Sign}$ as $(\NIZKcrs,\NIZKext)$; and
+        \cdot,\cdot)$; $\NIZKcrs_{\Sign}$ as $(\NIZKcrs,\NIZKtrap)$; and
         \sig as $(\NIZKproof,\Ec)$} \\
@@
       \sipk,\opk)): \pcreturn \bot \\
-      (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets \NIZKExtII(\NIZKcrs,\NIZKext,
+      (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets \NIZKExtract(\NIZKcrs,\NIZKtrap,
       (\msg,\feval,\yeval,\Ec,\sipk,\opk),\NIZKproof) \\
@@
   existentially unforgeable, and the NIZK used for $\NIZKRel_{\Issue}$ is
-  knowledge extractable and sound, then our \CUASGen construction satisfies
+  simulation extractable and sound, then our \CUASGen construction satisfies
   issuance unforgeability as defined in \defref{def:issue-forge-uas}, except
@@
   is exactly the same, but where, within the \Setup algorithm, we replace
-  $\NIZKSetup^{\Issue}$ with $\NIZKExtI^{\Issue}$. As per the definition of
+  $\NIZKSetup^{\Issue}$ with $\NIZKSimSetup^{\Issue}$. As per the definition of
   \NIZK in \appref{sapp:nizk}, both games are indistinguishable.
@@
   Then, given that $\NIZKRel_{\Issue}$ is knowledge extractable, in game $G_1$
-  we can apply the \NIZKExtII function, which produces a tuple $(\usk,\scred,
+  we can apply the \NIZKExtract function, which produces a tuple $(\usk,\scred,
   \attrs_{\scred})$ from $\utrans = (\Ccom,\attrs,\sipk,\cred,\NIZKproof)$.
@@
   \label{thm:sign-forge-uas}
-  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is sound and knowledge
-  extractable, the NIZK scheme for $\NIZKRel_{\Inspect}$ is sound and knowledge
+  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is sound and simulation
+  extractable, the NIZK scheme for $\NIZKRel_{\Inspect}$ is sound and simulation
   extractable, and \SBCM is existentially unforgeable, then our \CUASGen
@@
   and $G_1$, which is exactly the same, but where, within the \Setup algorithm,
-  we replace $\NIZKSetup^{\Sign}$ with $\NIZKExtI^{\Sign}$. As per the
+  we replace $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. As per the
   definition of \NIZK in \appref{sapp:nizk}, both games are indistinguishable.
 
-  In order to define the winning conditions for the adversary in the signing
-  unforgeability game, consider the following events:
+  From $G_1$, and in order to define the winning conditions for the adversary
+  in the signing unforgeability game, consider the following events:
 
@@
   \attrs_{\cred},\msg)=0$. Note that \usk, $\attrs_{\cred}$ and \cred (for all
-  $\cred \in \scred$) are output by \ExtractSign. Thus, after the knowledge
-  extraction property and soudness of $\NIZK^{\Sign}$, $(\msg,\feval,\yeval,\Ec,
-  \sipk,\opk) \in \NIZKRel^{\Sign}$, which more concretely means that
-  $\SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1
-  = \Identify(\usk,\attrs_{\cred},\cred)$, for all $\cred \in \scred$. The
-  probability of case 3 is therefore $0$.
+  $\cred \in \scred$) are output by \ExtractSign. Thus, after the
+  simulation-extractability property and soudness of $\NIZK^{\Sign}$, $(\msg,
+  \feval,\yeval,\Ec,\sipk,\opk) \in \NIZKRel^{\Sign}$, which more concretely
+  means that $\SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup \lbrace \usk
+  \rbrace) = 1 = \Identify(\usk,\attrs_{\cred},\cred)$, for all $\cred \in
+  \scred$. The probability of case 3 is therefore $0$.
   %
@@
   output by \Inspect. Thus, the probability of $\adv$ winning the game because
-  of (1) is negligible. Finally, for (2), knowledge extractability of
+  of (1) is negligible. Finally, for (2), simulation-extractability of
   $\NIZK^{\Inspect}$ and correctness of the public key encryption ensure that
-  the $\yinsp'$ value extracted by \NIZKExtII matches the value produced by
+  the $\yinsp'$ value extracted by \NIZKExtract matches the value produced by
   \Inspect.
@@
   \label{thm:frame-uas}
-  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is sound and knowledge
-  extractable, and the \SBCM scheme is existentially unforgeable, then our
-  \CUASGen construction satisfies non-frameability as defined in
-  \defref{def:frame-uas}, except with negligible probability.  
+  If the underlying NIZK schemes are zero-knowledge and the scheme used for
+  $\NIZK^{\Sign}$ is simulation-extractable, and the commitment scheme is
+  hiding, then our \CUASGen construction satisfies non-frameability as defined
+  in \defref{def:frame-uas}, except with negligible probability.
 \end{theorem}
@@
 \begin{proof}[\thmref{thm:frame-uas}]
-  As for \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpNonframe$,
-  and $G_1$, which is exactly the same, but where, within the \Setup algorithm,
-  we replace $\NIZKSetup^{\Sign}$ with $\NIZKExtI^{\Sign}$. As per the
-  definition of \NIZK in \appref{sapp:nizk}, both games are indistinguishable.
+  We prove that, given an adversary $\adv$ against non-frameability of \CUASGen,
+  we can build an adversary \advB that breaks the hiding property of the
+  underlying commitment scheme, with non-negligible probability.
 
-  Next, assume that the adversary wins in $G_1$. This means that $G_1$ outputs
-  $1$ at step 7, which implies that the signature and inspection proof produced
-  by the adversary at step 2 are accepted respectively by \Verify at step 4, and
-  by \Judge at step 5. This means that 
+  We start from $G_0=\ExpNonframe$. $\adv$ makes queries to the oracles in
+  \Oframe.
+
+  For $G_1$, within \Setup, we replace the \Setup algorithms for the three
+  NIZKs (\Issue, \Sign and \Inspect) with their corresponding \SimSetup
+  variants. Consequently, the corresponding queries to \Prove are also
+  simulated via the simulator. By the zero-knowledge property of the NIZK
+  systems, $G_1$ is indistinguishable from $G_0$.
+
+  We build adversary \advB against hiding of commitments from $G_1$ against
+  non-frameability. In the hiding game (see \figref{fig:com-games}), \advB first
+  picks two messages $\msg_0$ and $\msg_1$, and then receives a commitment \Ccom
+  of $\msg_b$. Let \advB pick both $\msg_0$ and $\msg_1$ from \AttrSpace. Then,
+  \advB initializes $G_1$ for $\adv$ against non-frameability, and randomly
+  picks a number $u \getr [1,q]$, where $q$ can be as large as \advB wants, but
+  will be the maximum number of honest users to let $\adv$ add to the game.
+  Then, when $\adv$ asks to create the $u$-th user, \advB ignores the call to
+  \UKeyGen. For every call that $\adv$ makes to the \OBTAIN oracle associated to
+  the $u$-th user, \advB uses the commitment \Ccom received as challenge in its
+  game against the hiding property of commmitments, and uses it as commitment to
+  the $u$-th user's \usk. \advB then simulates all the NIZK proofs associated to
+  the $u$-th user, in calls to \OBTAIN, \SIGN and \INSPECT. Again, due to the
+  zero-knowledge property of the associated NIZK systems, the outputs of the
+  moddified oracles are indistinguishable from the original outputs (as \Ccom
+  is a valid commitment of a user secret key). Eventually, $\adv$ outputs a
+  $(\sig,\yeval,\msg,\feval,\yinsp,\iproof)$ tuple that is accepted by \Verify
+  and \Judge. Due to simulation extractability of $NIZK^{\Sign}$, \ExtractSign
+  must be able to produce a $(\usk,\scred,\attrs_{\scred},\yinsp')$ tuple. Since
+  $\adv$ wins the
+  non-frameability game with non-neglibible probability, with probability $1/q$,
+  the \usk value belongs to the $u$-th honest user, so it must be equal to
+  either $\msg_0$ or $\msg_1$; \advB responds accordingly to its challenge in
+  the game for the hiding property of the commmitment scheme. By assumption,
+  \advB wins with non-negligible probability.
+  %
+  \qed
 \end{proof}

### 2022-04-26 prism-backend/research/gsac/model-uas.tex
Added formalisation of commitment schemes.
UAS anonymity proof.

@@
   in \secref{sec:uac-instantiation}.}
+
+\todo{Do our definitions protect from absurd schemes that leak \usk or \scred via
+  \fissue or \feval (I guess \finsp is ok)? E.g., $\feval(\usk,\scred,\msg) =
+  \usk$ deanonymizes the signer. I guess that anonymity should prevent that.
+  But check.}
 
@@
           \pcreturn \bot \\
+          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
           (\yeval,\csig_b) \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid], \\
@@
           \rbrace \\
-          \pcreturn \csig_b
+          \pcreturn (\csig_b,\yeval)
         }
@@
           \lbrace (\oid,\scid,\sig,\yeval,\msg,\feval) \rbrace \\
-          \pcreturn \sig \\
+          \pcreturn (\sig,\yeval) \\
         }
@@
 \begin{figure}[htp!]
-  \procedure{$\ExpAnonb(1^\secpar)$}{%
+  \procedure[linenumbering]{$\ExpAnonb(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
@@
   the latter, and perhaps expand}.
+
+\todo{Mention (probably, in future work?) that since the public keys of the
+  credential issuers are assumed to be public, we must enforce that challenge
+  users with same issuers per credential are used in the challenge oracle. This
+  is to avoid trivial wins. But not sure if the naive extension of hiding also
+  the issuers would make sense in the real world (which issuers are trusted?)}
 
@@
 \begin{figure}[htp!]
-    \procedure{$\ExpForgeIssue(1^\secpar)$}{%
+    \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
       \parm \gets \Setup(1^\secpar) \\
@@
 \begin{figure}[htp!]
-    \procedure{$\ExpForgeSign(1^\secpar)$}{%
+    \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
       \parm \gets \Setup(1^\secpar) \\
@@
       \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg,\feval)
-      = 0: \pcreturn 0 \\
+      = 0: \pcreturn 1 \\
       (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets \ExtractSign(\oid,\siid,\sig,
@@
 \begin{figure}[htp!]
-  \procedure{$\ExpNonframe(1^\secpar)$}{%
+  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
@@
     \pcreturn 0 \\
-    (\usk,\scred) \gets \ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \\
+    (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets
+    \ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \\
     \pcif \exists \uid \in \HU~\st~\PRVUK[\uid] = \usk: \pcreturn 1 \\

### 2022-04-26 prism-backend/research/gsac/security-uas.tex
UAS anonymity proof.

@@
   \label{thm:anonymity-uas}
-  If the underlying encryption scheme is \todo{IND-CCA}, the vector commitment
-  scheme is \todo{binding}, the scheme for signatures on blocks of committed
-  messages is \todo{XXX}, and the NIZKs used for $\NIZKRel_{\Issue},
-  \NIZKRel_{\Sign}$, and $\NIZKRel_{\Inspect}$ are \todo{zero-knowledge} and
-  \todo{simulation-sound?}, our \CUASGen construction satisfies anonymity as
+  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge and
+  simulation-extractable, our \CUASGen construction satisfies anonymity as
   defined in \defref{def:anonymity-uas}.
@@
 \begin{proof}[\thmref{thm:anonymity-uas}]
+  In this proof, we restrict to the case in which the adversary can only make
+  one query to the challenge oracle. Note however that the generalization to
+  polynomially many queries given in \cite{bsz05} applies here too (with the
+  corresponding security loss). Thus, proving security for one query to the
+  challenge oracle is enough.
+
+  We start from $G_0=\ExpAnonb$, and define game $G_1$ to be exactly the same
+  as $G_0$, except that, within the $\Setup$ algorithm, we replace
+  $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. By simulation
+  extractability, $G_1$ is indistinguishable from $G_0$.
+
+  From $G_1$, we consider $G^0_1$, which we define to be $G_1$, for $b=0$
+  (i.e., \ExpAnonz, using $\NIZKSimSetup^{\Sign}$). The challenge sent to the
+  adversary is $(\csig_0,\yeval) \gets \Sign(\PRVUK[\cuid_0],\PUBOK[\oid],
+  \CRED[\scid_0],\msg,\feval)$, where $\csig_0 = (\pi_0,\Ec_{\yinsp})$, with
+  $\pi_0 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
+  \Ec_{\yinsp},\PUBIK[\scid_0],\PUBOK[\oid]),(\PRVUK[\cuid_0],
+  \CRED[\scid_0],\attrs_{\scid_0},\yinsp,r))$ and $\Ec_{\yinsp} =
+  \EEnc(\PUBOK[\oid],\yinsp;r)$.
+  %
+  Further, we build $G_2^0$ from $G_1^0$ by simulating the proof $\pi_0$. That
+  is, in $G_{2,0}$, $\csig_0 = (\pi_0^s,\Ec_{\yinsp})$, where $\pi^s_0 =
+  \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
+  \Ec_{\yinsp},\PUBIK[\scid_0],\PUBOK[\oid]))$. By zero-knowledgeness
+  of $\NIZK^{\Sign}$, $G_2^0$ is indistinguishable from $G_1^0$.
+
+  Similarly, we consider $G_1^1$ and $G_2^1$. That is, $G_1^1$ is $G_1$
+  for $b=1$, where the challenge
+  sent to the adversary is $(\csig_1,\yeval) \gets \Sign(\PRVUK[\cuid_1],
+  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,
+  \Ec_{\yinsp})$, with $\pi_1 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
+  (\msg,\feval,\yeval,\Ec_{\yinsp},\PUBIK[\scid_1],\PUBOK[\oid]),
+  (\PRVUK[\cuid_1],\CRED[\scid_1],\attrs_{\scid_1},\yinsp,r'))$ and $\Ec_{\yinsp}
+  = \EEnc(\PUBOK[\oid],\yinsp;r')$. As before, $G_2^1$ is built from $G_1^1$,
+  simulating $\pi_1$. That is, in $G_2^1$, $\csig_1 = (\pi_1^s,\Ec_{\yinsp})$,
+  where $\pi^s_1 = \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,
+  \feval,\yeval,\Ec_{\yinsp},\PUBIK[\scid_1],\PUBOK[\oid]))$. Again, by
+  zero-knowledge of $\NIZK^{\Sign}$, $G_2^1$ is indistinguishable from $G_1^1$.
+  Note also that $G_2^1=G_2^0$, as in the challenge oracle, used in the
+  anonymity game, we restrict to $\PUBIK[\scid_0] = \PUBIK[\scid_1]$.
+
+  Finally, consider the definition of $\AdvAnon=|\Pr\lbrack
+  \ExpAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpAnonz(1^\secpar)=1\rbrack|$. As
+  argued, $G_1$ is indistinguishable from $\ExpAnonb$, thus
+  $\AdvAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
+  G_1^0(1^\secpar)=1\rbrack| \approx
+  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
+  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
+  \AdvAnon is negligible.
+  %
+  \qed
 \end{proof}
@@
   issuance unforgeability as defined in \defref{def:issue-forge-uas}, except
-  with negligible probability. \todo{EUF of \SBCM?}
+  with negligible probability.
 \end{theorem}
@@
   %
-  Then, given that $\NIZKRel_{\Issue}$ is knowledge extractable, in game $G_1$
+  Then, given that $\NIZKRel_{\Issue}$ is knowledge extractable (which is implied
+  by simulation-extractability), in game $G_1$
   we can apply the \NIZKExtract function, which produces a tuple $(\usk,\scred,
@@
   $\cred \in \scred$) are output by \ExtractSign. Thus, after the
-  simulation-extractability property and soudness of $\NIZK^{\Sign}$, $(\msg,
+  simulation-extractability property and soundness of $\NIZK^{\Sign}$, $(\msg,
   \feval,\yeval,\Ec,\sipk,\opk) \in \NIZKRel^{\Sign}$, which more concretely
@@
   zero-knowledge property of the associated NIZK systems, the outputs of the
-  moddified oracles are indistinguishable from the original outputs (as \Ccom
+  modified oracles are indistinguishable from the original outputs (as \Ccom
   is a valid commitment of a user secret key). Eventually, $\adv$ outputs a

### 2022-04-27 prism-backend/research/gsac/app-gsac.tex
Generic GSAC construction. Some reorganisation.

@@
           \pcif \sig \in \CSIG: \pcreturn \bot \\
-          (\upk,\Attrs,\oproof) \gets
-          \Open(\gpk,\osk,\trans[\cid],\sig,\DAttrs,\msg) \\
+          (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\DAttrs,\msg) \\
 %          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
 %          \CCRED \gets \CCRED \cup \lbrace \cid \rbrace \\
-          \pcreturn (\upk,\Attrs,\oproof) \\
+          \pcreturn (\upk,\oproof) \\
         }
@@
         \procedure{$\CHALb(\ccid_0,\ccid_1,\DAttrs,\msg)$}{%
-          \pcif \ATTR[\ccid_0] \cap \ATTR[\ccid_1] \nsubseteq \DAttrs:
+          \pcif \DAttrs \nsubseteq \ATTR[\ccid_0] \cap \ATTR[\ccid_1]:
           \pcreturn \bot \\
@@
 
+\subsection{Concrete Instantiation with BBS+}
+\label{sapp:gsac-instantiation}
+
+Intuitively, the credentials that we generate for our \GSAC construction are
+Pedersen commitments to $(\usk,\credid,\Attrs)$ tuples; i.e., they have
+the following structure: $\gen{h}_0^r\gen{h}_1^{\usk}\prod_{i \in [2,\nattrs+1]}
+\gen{h}_i^{\Attrs_i}$, where the exponent in $\gen{h_0}$ is a fresh random value
+that ensures hiding, the exponent in $\gen{h_1}$ encodes the user private
+key, and the remaining attributes are encoded in different
+exponentiations. This will actually be part of a BBS+ signature, which makes it
+easy to add subsequent and efficient zero-knowledge proofs. Concretely, we will
+be using several \NIZK proof systems, one for the $\langle \Obtain,\Issue
+\rangle$ interactive protocol, another for signing, and a third one for opening.
+Each will have its own relation, that we define in the corresponding algorithm.
+The concrete algorithms are as follows.
+
+\paragraph{$\Setup(\secpar,\nattrs) \rightarrow \parm$.} %
+Generates a bilinear group $\BB = (p,\GG_1,\GG_2,\GG_T,\gen{g}_1,\gen{g}_2,e) \gets
+\PGen(\secpar)$, $\nattrs+4$ additional generators $\gen{g},\gen{h},\gen{h}_0,...,
+\gen{h}_{\nattrs+1}$ of $\GG_1$. Returns $\parm \gets
+(\secpar,\nattrs,\BB,\gen{g},\gen{h},\gen{h}_0,...,\gen{h}_{\nattrs+1})$.
+
+\paragraph{$\IKeyGen(\parm) \rightarrow (\ipk,\isk)$.} %
+Parses \parm as $(\secpar,\dots)$ and runs $\NIZKcrs \gets \NIZKSetup(\secpar)$.
+Outputs $\isk \gets \ZZ^*_p$, and $\ipk \gets (\NIZKcrs,\gen{g}_2^{\isk})$.
+
+\paragraph{$\OKeyGen(\parm) \rightarrow (\opk,\osk)$.} %
+Outputs $\osk \gets \ZZ^*_p$, and $\opk \gets \gen{g}^{\osk}$. This is the
+opener's ElGamal encryption key pair \needcite.
+
+\paragraph{$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.} %
+Outputs $\usk \gets \ZZ^*_p$, and $\upk \gets \gen{h}_1^{\usk}$. \upk will
+simply be used to compute Pedersen commitments \needcite to \usk. However,
+it is useful to precompute it, and we treat it as a sort of ``public key''.
+
+\paragraph{$\langle \Obtain(\gpk,\usk,\Attrs),\Issue(\gpk,\isk,\Attrs) \rangle
+  \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.} %
+This interactive protocol is essentially a BBS+ signing  process. The user
+commits to its private key, proves knowledge of the corresponding private
+key, and asks the issuer to sign the commitment, along with any other arbitraty
+set of revealed attributes \Attrs. For proving knowledge of the private key, we
+define relation $\NIZKRel_{\Issue} = \lbrace (r, \usk), \Ccom: \Ccom =
+\gen{h}_0^r\gen{h}_1^{\usk}\rbrace$.
+
+\begin{itemize}
+\item \underline{User}: Fetch fresh randomness $r \getr \ZZ^*_p,
+  \Ccom \gets \gen{h}_0^r\gen{h}_1^{\usk}$, and compute $\NIZKproof \gets
+  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs,(r,\usk),
+  \Ccom)$. Send $(\Ccom,\NIZKproof)$ to Issuer.
+\item \underline{Issuer}: Run $\NIZKVerify^{\NIZKRel_{\Issue}}(\NIZKcrs,\Ccom,
+  \NIZKproof)$ and return $0$ if it fails. Else, compute
+  $x,\tilde{s} \getr \ZZ^*_p, A \gets
+  (\gen{g}_1\Ccom h_0^{\tilde{s}} \prod_{i \in \Attrs}
+  \gen{h}_i^{\Attrs_i})^{1/(\isk+x)}$.
+  Send $(A,x,\tilde{s})$ to User, and output $\utrans \gets
+  (\Ccom,(A,x,\tilde{s}),\Attrs,\NIZKproof)$.
+\item \underline{User}: If $A = 1_{\GG_1}$: return $0$. Else, compute
+  $s \gets r + \tilde{s}$. If $e(A,\gen{g}_2)^xe(A,\ipk) \neq
+  e(\gen{g}_1\Ccom\gen{h}_0^{\tilde{s}}\prod_{i \in \Attrs}\gen{h}_i^{\Attrs_i},
+  \gen{g}_2)$: return $0$. Else, return
+  $(A,x,s)$.
+\end{itemize}
+
+\paragraph{$\Sign(\gpk,\usk,\cred,\DAttrs,\msg) \rightarrow \sig$.} %
+To create a signature, the user first randomizes its BBS+ credential \cred and
+encrypts its public key \upk (note that $\upk=\gen{h}_1^{\usk}$ with the
+opener's encryption key. Then, we extend the usual NIZK protocol for proving
+knowledge of BBS+ signatures \cite{cdl16b} to, in addition to proving knowledge
+of a signature (which, for us is the user credential), also prove that the
+attribute encoding \usk within the credential match the encrypted value.
+Finally, the user commits to \msg, and includes this commitment within the
+proof. For this, we define relation
+$\NIZKRel_{\Sign}= \lbrace (r,\usk,\Attrs,r_2,r_3,s',\msg),(\DAttrs,c_1,c_2,
+\Cmsg): \Cmsg = \gen{h}^\msg \land c_1 = g^r \land c_2 = \opk^r\gen{h}_1^{\usk}
+\land \hat{A}/d = (A')^{-x}\gen{h}_0^{r_2} \land
+\gen{g}_1 \prod_{i \in \DAttrs} \gen{h}_i^{\Attrs_i} =
+d^{r_3}\gen{h}_0^{-s'}\gen{h}_1^{-\usk}
+\prod_{i \notin \DAttrs} \gen{h}_i^{-\Attrs_i} \rbrace$.
+
+\begin{itemize}
+\item Parse \gpk as $(\ipk,\opk)$, and \cred as $(A,x,s)$.
+\item Re-randomize \cred as $r_1,r_2 \getr
+  \ZZ^*_p, r_3 \gets r_1^{-1}, s' \gets s - r_2r_3$, $A' \gets A^{r_1},
+  \hat{A} \gets (A')^{-x}(\gen{g}_1\gen{h}_0^s\gen{h}_1^{\usk}
+  \prod_{i \in \Attrs}\gen{h}_i^{\Attrs_i})^{r_1}$,
+  $d \gets (\gen{g}_1\gen{h}_0^s\gen{h}_1^{\usk}
+  \prod_{i \in \Attrs}\gen{h}_i^{\Attrs_i})^{r_1}\gen{h}_0^{-r_2}$.
+\item Encrypt $\upk=\gen{h}_1^{\usk}$ with ElGamal as $r \getr \ZZ^*_p,
+  c \gets (c_1 = \gen{g}^r,c_2 = \opk^r\gen{h}_1^{\usk})$.
+\item Compute $\Cmsg \gets \gen{h}^\msg$ and
+  $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs,
+  (r,\usk,\Attrs,r_2,r_3,s',\msg), (\DAttrs,c_1,c_2,\Cmsg))$.
+\item Return $\sig \gets (c=(c_1,c_2),(A',\hat{A},d),\NIZKproof)$.
+\end{itemize}
+
+\paragraph{$\Verify(\gpk,\sig,\DAttrs,\msg) \rightarrow 1/0$.} %
+Parse \gpk as $(\ipk,\opk)$ and $\sig$ as $(c=(c_1,c_2),
+(A',\hat{A},d), \NIZKproof)$. Check that $A' \neq 1_{\GG_1}$ and $e(A',\ipk) =
+e(\hat{A},\gen{g}_2)$. Compute $\Cmsg \gets \gen{h}^\msg,$ and return
+$\NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs,(\DAttrs,c_1,c_2,\Cmsg),
+\NIZKproof)$.
+
+\paragraph{$\Open(\gpk,\osk,\sig,\DAttrs,\msg)
+  \rightarrow (\upk,\oproof)/\bot$.} %
+For open algorithms, we define the following relation for correct decryption of
+ElGamal ciphertexts: $\NIZKRel_{\Open} = \lbrace \osk,(c_1,c_2,\msg):
+c_2/c_1^{\osk} = \msg \rbrace$. Given $\NIZKRel_{\Open}$, the opener first,
+checks that $\Verify$ accepts the signature, and aborts otherwise. If \sig
+is accepted, then parses \sig as $(c=(c_1,c_2),\cdot,\cdot)$.
+Sets $\upk \gets c_2/c_1^{\osk}$. Finally, computes the proof of correct
+decryption by running $\oproof \gets \NIZKProve^{\NIZKRel_{\Open}}(\NIZKcrs,
+\osk,(\upk,c_1,c_2))$, and returns $(\upk,\oproof)$.
+
+\paragraph{$\Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg)
+  \rightarrow 1/0$.} %
+First, check that $\Verify$ accepts \sig, and abort otherwise. If the signature
+is accepted, then parse \sig as $(c=(c_1,c_2),\cdot,\cdot)$ and return
+$\NIZKVerify^{\NIZKRel_{\Open}}(\NIZKcrs,(c_1,c_2,\upk),\oproof)$.
+
+% \commentwho{Jesus}{For consistency with \UAS, maybe remove the need to return
+%   \Attrs in \Open, and return \DAttrs instead. Then, we do not need to pass
+%   \trans as a parameter to \Open, as \DAttrs is already attested for in the
+%   signature being opened. It also makes sense from the point of view that we
+%   are already revealing \upk, which would allow tracing; but otherwise don't
+%   reveal anything else about the attributes of \upk -- attributes that whoever
+%   requested the signature (the verifier) didn't seem to consider necessary, as
+%   s/he only requested \DAttrs. Still, if we make this modification, mention the
+%   possibility to return \Attrs, and the option to do it via adding \trans as a
+%   parameter to \Open (or including an encryption of all attributes in the
+%   signature, which is probably unrealistic.)}
+
 %%% Local Variables:

### 2022-04-27 prism-backend/research/gsac/construction-uas.tex
Added formalisation of commitment schemes.
Generic GSAC construction. Some reorganisation.

@@
-\section{\CUASGen: A Generic \UAS Construction}
-\label{sec:gen-construction}
+\subsection{\CUASGen: A Generic \UAS Construction}
+\label{ssec:generic-construction-uas}
 
@@
 instantiation.
-
-\subsection{Building Blocks}
-\label{ssec:bblocks}
-
-\paragraph{Vector Commitment schemes.} %
-Defined as a tuple $(\CSetup,\CCommit)$. Algorithm $\Cparm \gets
-\CSetup(\Csecpar)$ produces the parameters for committing to values. $\Ccom
-\gets \CCommit(\Cparm, \msgset; r)$ produces a commitment \Ccom over a set of
-messages \msgset, from which we may omit randomness $r$. \todo{Informally define
-  hiding and binding, leaving formal definitions to the appendix.}
-
-\paragraph{Public-Key Encryption.} %
-Defined as a tuple $(\ESetup,\EKeyGen,\EEnc,\EDec)$. Algorithm $\Eparm \gets
-\ESetup(\Esecpar)$ produces public parameters for the other algorithms.
-$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$ generates the encryption-decryption key
-pair, algorithm $\Ec \gets \EEnc(\Eek,\msg)$ encrypts message \msg with
-encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\Edk,
-\Ec)$ decrypts ciphertexts using decryption key \Edk. \todo{Informally define
-  security properties we'll need.}
-
-\paragraph{Digital Signatures.} %
-Defined as a tuple $(\SSetup,\SKeyGen,\SSign,\SVerify)$. Algorithm $\Sparm \gets
-\SSetup(\Ssecpar)$ produces public parameters for the other algorithms.
-$(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$ generates the verification-signing key
-pair, algorithm $\Ssig \gets \SSign(\Ssk,\msg)$ signs message \msg with
-signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\Svk,
-\Ssig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
-verification key \Svk. \todo{Informally define security properties we'll need.}
-
-\paragraph{Non-Interactive Zero-Knowledge.} %
-We use non-interactive zero-knowledge proofs of knowledge (NIZK), in the CRS
-model \needcite. Informally, a NIZK scheme over an NP relation \NIZKRel is
-defined as a tuple $(\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel,
-\NIZKVerify^\NIZKRel)$. Algorithm $\NIZKcrs \gets \NIZKSetup^\NIZKRel
-(\NIZKsecpar)$ produces the common reference string \NIZKcrs. $\NIZKproof/\bot
-\gets \NIZKProve^\NIZKRel(\NIZKcrs,\NIZKw,\NIZKx)$ creates a NIZK proof of
-knowledge of witness \NIZKw for \NIZKx such that $(\NIZKw,\NIZKx) \in \NIZKRel$.
-$1/0 \gets \NIZKVerify^\NIZKRel(\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof.
-\todo{Informally define security properties we'll need.}
-
-\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
-We use signature schemes that allow signing messages, or commitments to messages,
-in blocks, and are compatible with (efficient) proof systems over the produced
-signature and signed (commitments to) messages. For this purpose, we define such
-schemes as a tuple $(\SBCMSetup,\SBCMKeyGen,\SBCMSign,\SBCMVerify)$. Algorithm
-$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$ produces the public parameters for the
-scheme. $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$ produces a
-verification-signing key
-pair. Algorithm $\SBCMsig \gets \SBCMSign(\SBCMsk,\Ccom,\msgset)$ produces a
-signature over a set of committed messages \Ccom and a set of messages
-\msgset, where either \Ccom or \msgset may be empty. $1/0 \gets
-\SBCMVerify(\SBCMvk,\SBCMsig,\overline{\msgset})$ verifies a signature \SBCMsig
-over message set $\overline{\msgset}$, which must contain both the messages that
-were signed as commitments as well as those signed in ``the clear''. In
-addition, the produced signatures must be compatible with (efficient) NIZK
-proofs of knowledge of a signature, and of (arbitrary) claims over the signed
-(committed) messages.
-\todo{Informally define security properties we'll need.}
-
-\subsection{Generic Construction \CUASGen}
-\label{ssec:generic-construction-uas}
 
@@
   \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred,\attrs_{\scred}),
-  (\Ccom,\attrs))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
+  (\Ccom,\attrs,\sipk_{\scred}))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
 \item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
@@
 the NIZK proof. That is, parse \sig as $(\NIZKproof,\Ec)$ and check whether
-$\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,\sipk)) = 1$. In
+$\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,\sipk,\opk)) = 1$. In
 addition, the verifier may further check whether \yeval meets its needs.
@@
 
+%\input{security-uas.tex}
+
 %%% Local Variables:

### 2022-04-27 prism-backend/research/gsac/model-gsac.tex
GSAC without returning full attrs on open.
Generic GSAC construction. Some reorganisation.

@@
 
-\subsection{Syntax}
-\label{ssec:syntax}
+\subsubsection{Syntax}
+\label{sssec:syntax-gsac}
 
@@
   over message \msg.
-\item[$(\upk,\Attrs,\oproof)/\bot \gets
-  \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg)$.]
+\item[$(\upk,\oproof)/\bot \gets
+  \Open(\gpk,\osk,\sig,\DAttrs,\msg)$.]
   Given a signature \sig over message \msg, produced by a credential with
-  attributes containing the set \DAttrs owned by a user with key \upk, returns
-  the attribute set \Attrs encoded in the credential used to create the
-  signature, and a proof of opening correctness \oproof; or $\bot$ if the
+  attributes containing the set \DAttrs, returns the public key \upk of the
+  signer, and a proof of opening correctness \oproof; or $\bot$ if the
   opening process fails.
-\item[$1/0 \gets \Judge(\gpk,\upk,\Attrs,\oproof,\sig,\DAttrs,
+\item[$1/0 \gets \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,
   \msg)$.] Checks if \oproof is a valid opening correctness proof stating that
-  the user with key \upk and attributes \Attrs generated signature \sig over
-  message \msg, revealing attributes $\DAttrs \subseteq \Attrs$. 
+  the user with key \upk generated signature \sig over message \msg, revealing
+  attributes $\DAttrs$. 
 \end{description}
@@
 
+\begin{definition}{(Correctness of \GSAC)}
+  \label{def:correctness-gsac}
+  A \GSAC scheme is correct if, for any p.p.t. adversary $\adv$, \ExpGSACCorrect
+  outputs 1 with negligible probability.
+\end{definition}
+
 \begin{figure}[htp!]
@@
     \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\DAttrs,\msg) \\
-    (\upk,\Attrs,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) \\
+    (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\DAttrs,\msg) \\
     \pcif \Verify(\gpk, \sig, \DAttrs,\msg) = 0 \lor
-    \Judge(\gpk,\upk,\Attrs,\oproof,\sig,\DAttrs,\msg) = 0~\lor\\
-     \pcind \DAttrs \nsubseteq \Attrs \lor \Attrs \neq \ATTR[\cid]: \\
+    \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0: \\
      \pcind \pcreturn 1 \\
@@
 
-\subsection{Security Properties}
-\label{ssec:security}
+\todo{Correctness definition.}
+
+\subsubsection{Security Properties}
+\label{sssec:security-gsac}
 
@@
 \begin{definition}{(Anonymity of \GSAC)}
+  \label{def:anonymity-gsac}
   We define the advantage \AdvGSACAnon of $\adv$ against \ExpGSACAnonb as
@@
     \pcind \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) = \bot~\lor \\
-    \pcind \pccomment{\Open succeeds, but ...} \\
-    \pcind \Open(\gpk,\osk,\utrans,\sig,\DAttrs,\msg) =
-    (\upk,\Attrs,\oproof)~\land\\
-    \pcind \pcind \pccomment{... the proof is rejected by \Judge, or
-      it is accepted but \DAttrs is not contained in \Attrs} \\
-    \pcind \pcind (\Judge(\gpk,\upk,\Attrs,\oproof,\sig,\DAttrs,\msg) = 0
-    \lor \DAttrs \nsubseteq \Attrs) \\
+    \pcind \pccomment{\Open succeeds, but the proof is rejected by \Judge} \\
+    \pcind \Open(\gpk,\osk,\sig,\DAttrs,\msg) =
+    (\upk,\oproof) \land \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0 \\
     ) \\
@@
 \begin{definition}{(Traceability of \GSAC)}
+  \label{def:trace-gsac}
   We define the advantage \AdvGSACTrace of $\adv$ against \ExpGSACTrace as
@@
      \gpk \gets (\ipk,\opk) \\
-     (\sig,\DAttrs,\msg,\upk,\Attrs,\oproof) \gets
+     (\sig,\DAttrs,\msg,\upk,\oproof) \gets
      \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
@@
      \pcreturn 1~\pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 1 \land 
-     \Judge(\gpk,\upk,\Attrs,\oproof,\sig,\DAttrs,\msg) = 1~\land \\
-     \pcind \uid \in \HU \land (\sig \notin \SIG[\uid] \lor
-     \DAttrs \nsubseteq \Attrs) \\
+     \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 1~\land \\
+     \pcind \uid \in \HU \land \sig \notin \SIG[\uid] \\
      \pcreturn 0
@@
 \begin{definition}{(Non-frameability of \GSAC)}
+  \label{def:frame-gsac}
   We define the advantage \AdvGSACNonframe of $\adv$ against \ExpGSACNonframe as

### 2022-04-27 prism-backend/research/gsac/preliminaries.tex
Slightly refined UAS model. Working on generic construction.
Generic GSAC construction. Some reorganisation.

@@
 
-\todo{NIZKs.}
+\paragraph{Vector Commitment schemes.} %
+Defined as a tuple $(\CSetup,\CCommit)$. Algorithm $\Cparm \gets
+\CSetup(\Csecpar)$ produces the parameters for committing to values. $\Ccom
+\gets \CCommit(\Cparm, \msgset; r)$ produces a commitment \Ccom over a set of
+messages \msgset, from which we may omit randomness $r$. \todo{Informally define
+  hiding and binding, leaving formal definitions to the appendix.}
 
-\subsubsection{Notation}
+\paragraph{Public-Key Encryption.} %
+Defined as a tuple $(\ESetup,\EKeyGen,\EEnc,\EDec)$. Algorithm $\Eparm \gets
+\ESetup(\Esecpar)$ produces public parameters for the other algorithms.
+$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$ generates the encryption-decryption key
+pair, algorithm $\Ec \gets \EEnc(\Eek,\msg)$ encrypts message \msg with
+encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\Edk,
+\Ec)$ decrypts ciphertexts using decryption key \Edk. \todo{Informally define
+  security properties we'll need.}
+
+\paragraph{Digital Signatures.} %
+Defined as a tuple $(\SSetup,\SKeyGen,\SSign,\SVerify)$. Algorithm $\Sparm \gets
+\SSetup(\Ssecpar)$ produces public parameters for the other algorithms.
+$(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$ generates the verification-signing key
+pair, algorithm $\Ssig \gets \SSign(\Ssk,\msg)$ signs message \msg with
+signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\Svk,
+\Ssig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
+verification key \Svk. \todo{Informally define security properties we'll need.}
+
+\paragraph{Non-Interactive Zero-Knowledge.} %
+We use non-interactive zero-knowledge proofs of knowledge (NIZK), in the CRS
+model \needcite. Informally, a NIZK scheme over an NP relation \NIZKRel is
+defined as a tuple $(\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel,
+\NIZKVerify^\NIZKRel)$. Algorithm $\NIZKcrs \gets \NIZKSetup^\NIZKRel
+(\NIZKsecpar)$ produces the common reference string \NIZKcrs. $\NIZKproof/\bot
+\gets \NIZKProve^\NIZKRel(\NIZKcrs,\NIZKw,\NIZKx)$ creates a NIZK proof of
+knowledge of witness \NIZKw for \NIZKx such that $(\NIZKw,\NIZKx) \in \NIZKRel$.
+$1/0 \gets \NIZKVerify^\NIZKRel(\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof.
+\todo{Informally define security properties we'll need.}
+
+\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
+We use signature schemes that allow signing messages, or commitments to messages,
+in blocks, and are compatible with (efficient) proof systems over the produced
+signature and signed (commitments to) messages. For this purpose, we define such
+schemes as a tuple $(\SBCMSetup,\SBCMKeyGen,\SBCMSign,\SBCMVerify)$. Algorithm
+$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$ produces the public parameters for the
+scheme. $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$ produces a
+verification-signing key
+pair. Algorithm $\SBCMsig \gets \SBCMSign(\SBCMsk,\Ccom,\msgset)$ produces a
+signature over a set of committed messages \Ccom and a set of messages
+\msgset, where either \Ccom or \msgset may be empty. $1/0 \gets
+\SBCMVerify(\SBCMvk,\SBCMsig,\overline{\msgset})$ verifies a signature \SBCMsig
+over message set $\overline{\msgset}$, which must contain both the messages that
+were signed as commitments as well as those signed in ``the clear''. In
+addition, the produced signatures must be compatible with (efficient) NIZK
+proofs of knowledge of a signature, and of (arbitrary) claims over the signed
+(committed) messages.
+\todo{Informally define security properties we'll need.}
+
+\subsection{Notation}
 \label{ssec:notation}
@@
 
+\todo{In \secref{ssec:generic-construction-uas} we use $\usk \in \cred$ to
+  denote the claim ``\usk is an attribute attested in \cred''.}
+
 %%% Local Variables:

### 2022-04-27 prism-backend/research/gsac/security-gsac.tex
Generic GSAC construction. Some reorganisation.

\subsection{Correctness and Security of \GSACGen}
\label{ssec:security-gsac}

\begin{theorem}[Correctness of \GSACGen]
  \label{thm:correctness-gsac}
  If the underlying schemes for \todo{xxx}, our generic construction \GSACGen
  satisfies correctness as defined in \defref{def:correctness-gsac}.
\end{theorem}

\begin{proof}[\thmref{thm:correctness-gsac}]
  \todo{XXX}
\end{proof}

\begin{theorem}[Anonymity of \GSACGen]
  \label{thm:anonymity-gsac}
  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge and
  simulation-extractable, our \GSACGen construction satisfies anonymity as
  defined in \defref{def:anonymity-gsac}.
\end{theorem}

\begin{proof}[\thmref{thm:anonymity-gsac}]
  %
  \qed
\end{proof}

\begin{theorem}[Traceability of \GSACGen]
  \label{thm:trace-gsac}
  If the underlying scheme for \todo{xxx}, then our \GSACGen construction
  satisfies traceability as defined in \defref{def:trace-gsac}, except
  with negligible probability.
\end{theorem}

\todo{\usk belongs to \AttrSpace! I think this can lead to malleability attacks.
  Make them disjoint?}

\begin{proof}[\thmref{thm:trace-gsac}]
  \qed
\end{proof}

\begin{theorem}[Non-frameability of \GSACGen]
  \label{thm:frame-gsac}
  If the underlying schemes for \todo{xxx}, then our \GSACGen construction
  satisfies non-frameability as defined in \defref{def:frame-gsac}, except with
  negligible probability.
\end{theorem}

\begin{proof}[\thmref{thm:frame-gsac}]
  \qed
\end{proof}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "gsac"
%%% End:

### 2022-04-29 prism-backend/research/gsac/app-building-blocks.tex
Proving traceability of GSAC. Need to formalize SBCM and Encryption first...

@@
   returns the public parameters \Cparm to commit messages.
-\item[$\Ccom \gets \CCommit(\Cparm,\msg,r)$.] Given the public parameters and
+\item[$\Ccom \gets \CCommit(\Cparm,\msg;r)$.] Given the public parameters and
   a message \msg, outputs a commitment \Ccom to \msg, for which randomness $r$
-  from some predefind randomness space $\mathcal{R}$ is used.
+  from some predefined randomness space $\mathcal{R}$ is used.
 \end{description}
@@
 \end{description}
+
+\todo{Commitments with proofs, needed for \SBCM.}
 
@@
 
-\subsection{Signatures on Blocks of Committed Messages}
+\subsection{Signatures over Blocks of Committed Messages}
 \label{sapp:sbcm}
 
-We use signature schemes that allow signing messages, or commitments to messages,
-in blocks, and are compatible with (efficient) proof systems over the produced
-signature and signed (commitments to) messages. For this purpose, we define such
-schemes as a tuple $(\SBCMSetup,\SBCMKeyGen,\SBCMSign,\SBCMVerify)$. Algorithm
-$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$ produces the public parameters for the
-scheme. $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$ produces a
-verification-signing key
-pair. Algorithm $\SBCMsig \gets \SBCMSign(\SBCMsk,\Ccom,\msgset)$ produces a
-signature over a set of committed messages \Ccom and a set of messages
-\msgset, where either \Ccom or \msgset may be empty. $1/0 \gets
-\SBCMVerify(\SBCMvk,\SBCMsig,\overline{\msgset})$ verifies a signature \SBCMsig
-over message set $\overline{\msgset}$, which must contain both the messages that
-were signed as commitments as well as those signed in ``the clear''. In
-addition, the produced signatures must be compatible with (efficient) NIZK
-proofs of knowledge of a signature, and of (arbitrary) claims over the signed
-(committed) messages.
-\todo{Informally define security properties we'll need.}
+\todo{Formal models on signatures over blocks of committed messages? I'm just
+  informally stating a model here, but there must be some more formal
+  reference...}
+
+We use signature schemes that allow signing messages and commitments to messages
+in blocks (\SBCM), and are also compatible with (efficient) proof systems over
+the produced signature and signed (commitments to) messages. Such schemes build
+on a predefined scheme for commitments on blocks of messages \C (see
+\secref{sapp:commitments}). The algorithms composing an \SBCM scheme are as
+follows:
+
+\begin{description}
+\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
+  for the other algorithms, given an input security parameter \Ssecpar.
+\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
+  verification-signing key pair.
+\item[$\SBCMsig \gets \langle \SBCMCom(\overline{\smsg},\smsg),
+  \SBCMSign(\SBCMsk,\smsg) \rangle$.] An interactive protocol between two
+  parties with shared input a block of messages \smsg. The party running
+  \SBCMCom further knows a set of messages $\overline{\smsg}$ to be
+  block-committed and then signed along with \smsg. The party running \SBCMSign
+  controls the signing key \SBCMsk. As a result, both parties get signature
+  \SBCMSig.
+\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\smsg)$.] Checks whether \SBCMsig
+  is a valid signature over the set of messages \smsg (independently on whether
+  the messages where signed as commitments or not), under verification key
+  \SBCMvk.
+\end{description}
+
+In addition, we require that the produced signatures must be compatible with
+(efficient) NIZK proofs of knowledge of a signature, and of (arbitrary) claims
+over the signed (committed) messages.
+
+Informally, an \SBCM scheme is correct if signatures generated between an honest
+party running \SBCMCom with message sets $\overline{\smsg}$ and \smsg, and an
+honest signer running \SBCMSign over \smsg, for honestly generated parameters
+and key pairs, results in a signature over $\smsg \cup \overline{\smsg} $that is
+accepted by \SBCMVerify.
+
+A digital signature scheme is correct if honestly generated signatures, using
+honestly generated key pairs, are always accepted by \SVerify. \todo{define more
+  formally?}
+%
+A digital signature scheme \S has existential unforgeability if, for all p.p.t.
+adversaries $\adv$, $\Pr[\ExpEUF = 1]$ is a negligible function of the
+security parameter.
+
+\begin{figure}[ht!]
+  \begin{minipage}[t]{0.5\textwidth}
+    \procedure{$\ExpSBCMEUF(\Ssecpar)$}{%
+      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
+      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
+      (\SBCMsig,\smsg) \gets
+      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
+      \pcif \SVerify(\SBCMvk,\SBCMsig,\smsg) = 0: \pcreturn 0 \\
+      \pcif \nexists (\smsg',\sCcom=\CCommit(\Cparm,\smsg''))~\st~
+      (\lbrace \smgs' \rbrace \cup \lbrace \smgs'' \rbrace) \subseteq \smsg
+      \textrm{a query}~()~\textrm{was made to \SBCMSign}: \pcreturn 1 \\
+      \pcreturn 0
+    }
+  \end{minipage}
+  \label{fig:euf-game}
+  \caption{Existential Unforgeability Game.}
+\end{figure}
 

### 2022-04-29 prism-backend/research/gsac/model-gsac.tex
Proving traceability of GSAC. Need to formalize SBCM and Encryption first...

@@
 \begin{figure}[htp!]
-  \procedure{$\ExpGSACAnonb(1^\secpar)$}{%
+  \procedure[linenumbering]{$\ExpGSACAnonb(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
@@
 but either cannot be opened, it can be opened but the proof is rejected by
-\Judge, or even though it is accepted by \Judge, there is no credential issued
-to the user pointed to by \Open that contains the set of attributes \DAttrs. We
+\Judge, or even though it is accepted by \Judge, there is no credential
+controlled by the adversary that contains the set of attributes \DAttrs. We
 formally define traceability in the \ExpTrace experiment in
@@
 \begin{figure}[htp!]
-  \procedure{$\ExpGSACTrace(1^\secpar)$}{%
+  \procedure[linenumbering]{$\ExpGSACTrace(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
@@
     \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
-    \pcreturn 1~\pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 1~\land~( \\
-    \pcind \pccomment{\Open fails} \\
-    \pcind \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) = \bot~\lor \\
-    \pcind \pccomment{\Open succeeds, but the proof is rejected by \Judge} \\
-    \pcind \Open(\gpk,\osk,\sig,\DAttrs,\msg) =
-    (\upk,\oproof) \land \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0 \\
-    ) \\
+    \pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 0: \pcreturn 0 \\
+    \pcif \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) = \bot: \pcreturn 1 \\
+    \textrm{Let}~(\upk,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) \\
+    \pcif \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0: \pcreturn 1 \\
+    \pcelse \pcif \forall \uid \in \CU, \nexists (\uid,\cdot,\Attrs) \in
+    \CRED~\st~\DAttrs \subseteq \Attrs: \pcreturn 1 \\
     \pcreturn 0
@@
 \begin{figure}[htp!]
-  \procedure{$\ExpGSACNonframe(1^\secpar)$}{%
+  \procedure[linenumbering]{$\ExpGSACNonframe(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
@@
 
+\todo{Other modelling choice: We could return the full set of attributes
+  contained in the credential used for creating an opened signature, but that
+  would require either complicating the proof, or access to the transcripts log
+  at open time, which I opted to avoid for better compatibility with \UAS.}
+
 \todo{Argue that our properties cover (and augment) a direct combination

### 2022-04-29 prism-backend/research/gsac/security-gsac.tex
Proving traceability of GSAC. Need to formalize SBCM and Encryption first...

@@
   If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge and
-  simulation-extractable, our \GSACGen construction satisfies anonymity as
-  defined in \defref{def:anonymity-gsac}.
+  simulation-extractable, and the encryption system is IND-CCA secure,
+  our \GSACGen construction satisfies anonymity as defined in
+  \defref{def:anonymity-gsac}.
 \end{theorem}
@@
 \begin{proof}[\thmref{thm:anonymity-gsac}]
+  We prove that the probability of an adversary distinguishing signatures by
+  challenge users is negligible. For the proof, we restrict to the case of
+  allowing only one query to the challenge oracle. The extension to a polynomial
+  number of queries given in \cite{bsz05} applies here, with the corresponding
+  security loss.
+
+  We begin with game $G_0=\ExpGSACAnonb$. From it, we build $G_1$, where we
+  simply replace the \NIZKSetup functions for $\NIZKRel_{\Sign}$ and
+  $\NIZKRel_{\Open}$ within the \Setup algorithm. $G_1$ is indistinguishable
+  from $G_0$ due to the zero-knowledge property of the NIZK systems.
+
+  From $G_1$, we build $G_2$, where within the challenge signature produced by
+  \CHALb, we replace the \Ccom value encrypted within \Sign, with a random
+  string of the appropriate length (e.g., the same length of the encrypted
+  message in $G_1$). The corresponding proof for $\NIZKRel_{\Sign}$ is thus
+  also simulated. The zero-knowledge and simulation-extractability properties
+  of the NIZKs for $\NIZKRel_{\Sign}$, and IND-CCA of the encryption
+  scheme, ensure that the result is indistinguishable to the adversary.
+
+  Now, observe that in $G_2$, the challenge signature received by the adversary
+  is completely independent from the challenge bit $b$. Moreover, as argued,
+  $G_2$ is indistinguishable from $G_0$, where the adversary plays the original
+  \ExpGSACAnonb game. Thus, our generic construction of \GSAC satisfies
+  anonymity, except with negligible probability.
   %
@@
   \label{thm:trace-gsac}
-  If the underlying scheme for \todo{xxx}, then our \GSACGen construction
-  satisfies traceability as defined in \defref{def:trace-gsac}, except
-  with negligible probability.
+  If the underlying NIZK schemes for $\NIZKRel_{\Sign}$ %and $\NIZKRel_{\Open}$
+  is sound, and the signature scheme for blocks of committed messages is
+  existentially unforgeable, then our \GSACGen construction satisfies
+  traceability as defined in \defref{def:trace-gsac}, except with negligible
+  probability.
 \end{theorem}
@@
 \begin{proof}[\thmref{thm:trace-gsac}]
+  Assuming the NIZK systems are sound, we build an adversary against existential
+  unforgeability of the signature scheme for blocks of committed messages.
+  %
+  Consider the following events:
+
+  \begin{description}
+  \item[$O$.] The \Open algorithm returns $\bot$.
+  \item[$J$.] The \Judge algorithm returns $0$.
+  \item[$D$.] No credential owned by a user in \CU contains \DAttrs.
+  \end{description}
+
+  Given these events, the adversary wins if:
+
+  \begin{description}
+  \item[$W_1 = O$.] \Open returns $\bot$ (line 5 of \ExpGSACTrace).
+  \item[$W_2 = \overline{O} \land J$.] \Open does not fail, but \Judge rejects
+    the output of \Open (line 7 of \ExpGSACTrace).
+  \item[$W_3 = \overline{O} \land \overline{J} \land D$.] \Open does not fail,
+    \Judge accepts the output by \Open, but no corrupt user has a credential
+    containing \DAttrs (line 8 of \ExpGSACTrace).
+  \end{description}
+
+  Clearly, since the group signature is verified at step 4 of the game, if
+  verification succeeds, soundness of $\NIZK_{\Sign}$ implies that $(\Ccom_m,
+  \Ec,\DAttrs) \in \NIZKLang_{\Sign}$, except with negligible probability, say
+  $2^{-\NIZKsecpar}$. Also, observe that each of the winning events for the
+  adversary described above are disjoint. Thus:
+
+  \begin{equation}
+    \AdvGSACTrace(\secpar) = \Pr[W_1]+\Pr[W_2]+\Pr[W_3]+2^{-\NIZKsecpar}
+  \end{equation}
+
+  $\Pr[W_1]=0$ is directly deduced from the fact that $(\Ccom_m,\Ec,\DAttrs)
+  \in \NIZKLang_{\Sign}$ due to soundness of $\NIZKRel_{\Sign}$. Concretely,
+  we know that \Open does not abort due to rejection of the signature by
+  \Verify (as this is checked in line 4 of \ExpGSACTrace too) and, thus,
+  $\Ec = \EEnc(\opk,\Ccom)$ which, by correctness of the encryption algorithm,
+  implies that $\Ccom = \EDec(\osk,\Ec)$, where $\upk=\Ccom=\CCommit(\usk;0)$.
+  Completeness of $\NIZK_{\Open}$ thus implies that the \Open algorithm can
+  compute the opening proof \oproof, and return $(\upk,\oproof)$.
+
+  $\Pr[W_2] = 0$ is similarly deduced from soundness of $\NIZKRel_{\Sign}$ and
+  completeness of $\NIZKRel_{\Open}$, since the opening proof is computed
+  honestly in line 6 of \ExpGSACTrace.
+
+  Finally, assume that there is an adversary $\adv$ against \ExpNonTrace that
+  wins by event $W_3$. We build an adversary against unforgeability of the
+  signature scheme on blocks of committed messages.
+
   \qed

### 2022-05-02 prism-backend/research/gsac/app-building-blocks.tex
Proofs for GSAC done (except correctnes...)

@@
 A digital signature scheme is correct if honestly generated signatures, using
-honestly generated key pairs, are always accepted by \SVerify. \todo{define more
-  formally?}
+honestly generated key pairs, are always accepted by \SVerify. 
 %
 A digital signature scheme \S has existential unforgeability if, for all p.p.t.
-adversaries $\adv$, $\Pr[\ExpEUF = 1]$ is a negligible function of the
+adversaries $\adv$, $\Pr[\ExpEUF(\Ssecpar) = 1]$ is a negligible function of the
 security parameter.
@@
 \begin{figure}[ht!]
-  \begin{minipage}[t]{0.5\textwidth}
+  \begin{minipage}[t]{\textwidth}
+    \centering
     \procedure{$\ExpEUF(\Ssecpar)$}{%
@@
 
-Defined as a tuple $(\ESetup,\EKeyGen,\EEnc,\EDec)$. Algorithm $\Eparm \gets
-\ESetup(\Esecpar)$ produces public parameters for the other algorithms.
-$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$ generates the encryption-decryption key
-pair, algorithm $\Ec \gets \EEnc(\Eek,\msg)$ encrypts message \msg with
-encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\Edk,
-\Ec)$ decrypts ciphertexts using decryption key \Edk. \todo{Informally define
-  security properties we'll need.}
+A public-key encryption scheme is defined by the following algorithms:
+
+\begin{description}
+\item[$\Eparm \gets \ESetup(\Esecpar)$.] Produces public parameters \Eparm given
+  a security parameter \Esecpar.
+\item[$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$.] Given public parameters \Eparm,
+  produces an encryption-decryption keypair $(\Eek,\Edk)$.
+\item[$\Ec \gets \EEnc(\Eek,\msg)$.] Encrypts message \msg with encryption key
+  \Eek, producing ciphertext \Ec.
+\item[$\msg \gets \EDec(\Edk,\Ec)$.] Decrypts ciphertext \Ec with decryption key
+  \Edk.
+\end{description}
+
+A public-key encryption scheme is correct if, given a honestly generated key
+pair $(\Eek,\Edk)$, produced with honestly generated parameters \Eparm,
+$\Pr[\EDec(\Edk,\EEnc(\Eek,\msg))=\msg] = 1$ with overwhelming probability.
+
+A public-key encryption scheme has IND-CCA2 security if
+$\Pr[\ExpINDCCAiio(\Esecpar) = 1] - \Pr[\ExpINDCCAiiz(\Esecpar) = 1]|$ is
+a negligible function of \Esecpar, for any p.p.t. adversary \adv, where
+\ExpINDCCAiib is as defined in \figref{fig:indcca2-game}.
+
+\begin{figure}[ht!]
+  \begin{minipage}[t]{\textwidth}
+    \centering      
+    \procedure{$\ExpINDCCAiib(\Esecpar)$}{%
+      \Eparm \gets \ESetup(\Esecpar) \\
+      (\Eek,\Edk) \gets \EKeyGen(\Eparm) \\
+      b^* \gets \adv^{\ELR(b,\cdot,\cdot),\EDEC(\Edk,\cdot)}(\Eek),
+      ~\textrm{where:} \\
+      \pcind \ELR(b,\msg_0,\msg_1)~\textrm{returns}~\EEnc(\Eek,\msg_b),
+      ~\textrm{and} \\
+      \pcind \EDEC(\Edk,\Ec)~\textrm{returns}~\EDec(\Edk,\Ec) \\
+      \pcif \EDEC~\textrm{has been called with an output of \ELR, abort} \\
+      \pcreturn b^*
+    }
+  \end{minipage}
+  \label{fig:indcca2-game}
+  \caption{IND-CCA2 Game.}
+\end{figure}
 
@@
   that no adversary can change the message that has been committed to. More
-  formally, $\Pr[\ExpComBind = 1]$ must be a negligible function of the security
-  parameter.
+  formally, $\Pr[\ExpComBind(\Csecpar) = 1]$ must be a negligible function of
+  the security parameter.
 \item[Hiding.] The hiding property captures that no adversary should be able to
   learn the message that was committed, when given only the commitment. This is
-  formally defined through \ExpComHideb, where $|\Pr[\ExpComHideb=1|b=1] -
-  \Pr[\ExpComHideb=1|b=0]|$ must be a negligible function of the security
-  parameter.
+  formally defined through \ExpComHideb, where $|\Pr[\ExpComHideb(\Csecpar)=1|
+  b=1] - \Pr[\ExpComHideb(\Csecpar)=1|b=0]|$ must be a negligible function of
+  the security parameter.
 \end{description}
-
-\todo{Commitments with proofs, needed for \SBCM.}
 
@@
   \begin{minipage}[t]{0.5\textwidth}
-    \procedure{$\ExpComBind(\secpar)$}{%
-      \Cparm \gets \CSetup(\secpar) \\
+    \procedure{$\ExpComBind(\Csecpar)$}{%
+      \Cparm \gets \CSetup(\Csecpar) \\
       (\msg_0,r_0,\msg_1,r_1) \gets \adv(\Cparm) \\
@@
   informally stating a model here, but there must be some more formal
-  reference...}
+  reference... \cite{cl02,asm06,ps16} all kind of allow signatures on blocks of
+  (committed) messages, but they seem to use ad hoc models.}
 
@@
   verification-signing key pair.
-\item[$\SBCMsig \gets \langle \SBCMCom(\overline{\smsg},\smsg),
+\item[$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},\smsg),
   \SBCMSign(\SBCMsk,\smsg) \rangle$.] An interactive protocol between two
@@
   controls the signing key \SBCMsk. As a result, both parties get signature
-  \SBCMSig.
+  \SBCMsig over $\smsg \cup \overline{\smsg}$.
 \item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\smsg)$.] Checks whether \SBCMsig
@@
 
+\paragraph{Correctness.} %
 Informally, an \SBCM scheme is correct if signatures generated between an honest
@@
 honest signer running \SBCMSign over \smsg, for honestly generated parameters
-and key pairs, results in a signature over $\smsg \cup \overline{\smsg} $that is
+and key pairs, results in a signature over $\smsg \cup \overline{\smsg}$ that is
 accepted by \SBCMVerify.
 
-A digital signature scheme is correct if honestly generated signatures, using
-honestly generated key pairs, are always accepted by \SVerify. \todo{define more
-  formally?}
-%
-A digital signature scheme \S has existential unforgeability if, for all p.p.t.
-adversaries $\adv$, $\Pr[\ExpEUF = 1]$ is a negligible function of the
-security parameter.
+\paragraph{Unforgeability.} %
+It must be unfeasible for an adversary to produce signatures over blocks of
+messages that have not been signed (in plain, or committed shape) by the
+signer. More formally, an \SBCM scheme is unforgeable if, for all p.p.t.
+adversaries $\adv$, $\Pr[\ExpSBCMOMF(\SBCMsecpar) = 1]$, as defined in
+\figref{fig:sbcm-games}, is a negligible function of the security parameter.
+Note that this follows the ``one-more-forgery'' type of definition of blind
+signatures \cite{bold02}.
+
+\paragraph{Blindness.} %
+Finally, the signer must not learn the plaintext values of the messages that are
+signed in committed form. Note that this is a weaker notion than the usual
+blindness property of blind signature schemes, where it is required that the
+adversary cannot link a signature to the signing process that produced it.
+Formally, blindness for \SBCM schemes is defined as in \ExpSBCMBlindb in
+\figref{fig:sbcm-games}. An \SBCM scheme is blind if, for all p.p.t.
+adversaries $\adv$, $|\Pr[\ExpSBCMBlindo(\SBCMsecpar) = 1] -
+\Pr[\ExpSBCMBlindz(\SBCMsecpar) = 1]|$ is a negligible function of the security
+parameter.
 
 \begin{figure}[ht!]
-  \begin{minipage}[t]{0.5\textwidth}
-    \procedure{$\ExpSBCMEUF(\Ssecpar)$}{%
+  \begin{minipage}[t]{\textwidth}
+    \centering
+
+    \procedure{$\ExpSBCMOMF(\SBCMsecpar)$}{%
       \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
       (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
-      (\SBCMsig,\smsg) \gets
+      ((\sig_1,\smsg_1),\dots,(\sig_{n+1},\smsg_{n+1})) \gets
       \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
-      \pcif \SVerify(\SBCMvk,\SBCMsig,\smsg) = 0: \pcreturn 0 \\
-      \pcif \nexists (\smsg',\sCcom=\CCommit(\Cparm,\smsg''))~\st~
-      (\lbrace \smgs' \rbrace \cup \lbrace \smgs'' \rbrace) \subseteq \smsg
-      \textrm{a query}~()~\textrm{was made to \SBCMSign}: \pcreturn 1 \\
+      \pcif \exists i \in [n+1]~\st~\SBCMVerify(\SBCMvk,\sig_i,\smsg_i) = 0:
+      \pcreturn 0 \\
+      \pcif \exists i \neq j \in [n+1]~\st~\smsg_i = \smsg_j: \pcreturn 0 \\
+      \pcif \langle \cdot, \SBCMSign(\SBCMsk,\cdot)\rangle~
+      \textrm{was called more than $k$ times}: \pcreturn 0 \\
+      \pcreturn 1 \\
+    }
+
+    \procedure{$\ExpSBCMBlindb(\SBCMsecpar)$}{%
+      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
+      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
+      (\overline{\smsg}_0,\overline{\smsg}_1,\smsg) \gets
+      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
+      \csig \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg}_b,\smsg),
+      \SBCMSign(\SBCMsk,\smsg) \rangle \\
+      b^* \gets \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk,
+      \csig) \\
+      \pcif b = b^*: \pcreturn 1 \\
       \pcreturn 0
@@
   \end{minipage}
-  \label{fig:euf-game}
-  \caption{Existential Unforgeability Game.}
+  \label{fig:sbcm-games}
+  \caption{Games for \SBCM schemes.}
 \end{figure}
+
+\todo{BBS+ is proven to have EUF, but nothing is said against OMF. Relationship?}
 
@@
 able to create a proof \NIZKproof that is accepted by any honest verifier, with
-overwhelming probability. More precisely, $\Pr\lbrack\ExpNIZKComp\rbrack = 1$
-with overwhelming probability, for any p.p.t. \adv, for \ExpNIZKComp in
-\figref{fig:nizk-games}.
+overwhelming probability. More precisely, $\Pr\lbrack\ExpNIZKComp(\NIZKsecpar)
+\rbrack = 1$ with overwhelming probability, for any p.p.t. \adv, for
+\ExpNIZKComp in \figref{fig:nizk-games}.
 
@@
 statements $\NIZKx \notin \NIZKLang$, except with negligible probability. That
-is, for \ExpNIZKSound as in \figref{fig:nizk-games}, $\Pr\lbrack\ExpNIZKSound\rbrack
-= 1$ with overwhelming probability. If this holds only against p.p.t.
-adversaries, we talk of Non-Interactive \emph{arguments}, while if soundness
-holds even against unbounded adversaries, we talks about Non-Interactive proofs.
+is, for \ExpNIZKSound as in \figref{fig:nizk-games}, $\Pr\lbrack\ExpNIZKSound
+(\NIZKsecpar)\rbrack=1$ with overwhelming probability. If this holds only
+against p.p.t. adversaries, we talk of Non-Interactive \emph{arguments}, while
+if soundness holds even against unbounded adversaries, we talks about
+Non-Interactive proofs.
 
@@
 also requires that \SimSetup is indistinguishable from \Setup. All this is
-formalised by requiring that $|\Pr[\ExpNIZKZKb(\secpar) = 1 | b = 1] -
-\Pr[\ExpNIZKZKb(\secpar) = 1 | b = 0]$ be a negligible function of \secpar,
+formalised by requiring that $|\Pr[\ExpNIZKZKb(\NIZKsecpar) = 1 | b = 1] -
+\Pr[\ExpNIZKZKb(\NIZKsecpar) = 1 | b = 0]$ be a negligible function of \secpar,
 where \ExpNIZKZKb is as defined in \figref{fig:nizk-games}.
@@
 extraction). Formally, for simulation-extractability we require that
-$\Pr[\ExpNIZKSimExt] = 1$ is a negligible function of \secpar, where
-\ExpNIZKSimExt is defined in \figref{fig:nizk-games}.
+$\Pr[\ExpNIZKSimExt(\NIZKsecpar)] = 1$ is a negligible function of \secpar,
+where \ExpNIZKSimExt is defined in \figref{fig:nizk-games}.
 
@@
   \begin{minipage}[t]{0.5\textwidth}
-    \procedure{$\ExpNIZKComp(\secpar)$}{%
-      \NIZKcrs \gets \Setup(\secpar) \\
+    \procedure{$\ExpNIZKComp(\NIZKsecpar)$}{%
+      \NIZKcrs \gets \Setup(\NIZKsecpar) \\
       (\NIZKx,\NIZKw) \gets \adv(\NIZKcrs) \\
@@
     }
-    \procedure{$\ExpNIZKSimExt(\secpar)$}{%
-      (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\secpar) \\
+    \procedure{$\ExpNIZKSimExt(\NIZKsecpar)$}{%
+      (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\NIZKsecpar) \\
       (\NIZKx,\NIZKproof) \gets \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}
@@
   \begin{minipage}[t]{0.5\textwidth}
-    \procedure{$\ExpNIZKSound(\secpar)$}{%
-      \NIZKcrs \gets \Setup(\secpar) \\
+    \procedure{$\ExpNIZKSound(\NIZKsecpar)$}{%
+      \NIZKcrs \gets \Setup(\NIZKsecpar) \\
       (\NIZKproof,\NIZKx) \gets \adv(\NIZKcrs) \\
@@
 
-    \procedure{$\ExpNIZKZKb(\secpar)$}{%
+    \procedure{$\ExpNIZKZKb(\NIZKsecpar)$}{%
       \pcif b = 0: \\
-      \pcind \NIZKcrs \gets \Setup(\secpar) \\
+      \pcind \NIZKcrs \gets \Setup(\NIZKsecpar) \\
       \pcind \pcreturn \adv^{\Prove(\NIZKcrs,\cdot,\cdot)}(\NIZKcrs) \\

### 2022-05-02 prism-backend/research/gsac/app-gsac.tex
Proving traceability of GSAC. Need to formalize SBCM and Encryption first...
Proofs for GSAC done (except correctnes...)

@@
           \Issue(\gpk,\isk,\Attrs) \rangle \\
-          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets \cred \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
+          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets (\uid,\cred,\Attrs) \\
           \pcreturn \top \\
@@
           \langle \Obtain(\gpk,\PRVUK[\uid],\Attrs),\adv \rangle \\
-          \CRED[\cid] \gets \cred \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
+          \CRED[\cid] \gets (\uid,\cred,\Attrs) \\
           \pcreturn \top \\
@@
           \langle \adv, \Issue(\gpk,\isk,\Attrs) \rangle \\
-          \trans[\cid] \gets \utrans \\
-          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets \Attrs \\
+          \trans[\cid] \gets \utrans;~
+          \CRED[\cid] \gets (\uid,\cdot,\Attrs) \\
           \pcreturn \top \\          
@@
 \label{sapp:gsac-proofs}
+
+\commentwho{Jesus}{Strictly, in our generic construction we require IND-CCA (is
+  that a strict requirement? or can it be downgraded to IND-CPA?), but in the
+  following concrete instantiation, we use ElGamal, which is IND-CPA. However,
+  we actually ``lift'' ElGamal with NIZKs of the encrypted plaintexts, which is
+  essentially IND-CCA as far as I know. Still, make sure to mention that.}
+
+\begin{proof}[\thmref{thm:correctness-gsac}]
+  \todo{XXX}
+\end{proof}
+
+\begin{proof}[\thmref{thm:anonymity-gsac}]
+  We prove that the probability of an adversary distinguishing signatures by
+  challenge users is negligible. For the proof, we restrict to the case of
+  allowing only one query to the challenge oracle. The extension to a polynomial
+  number of queries given in \cite{bsz05} applies here, with the corresponding
+  security loss.
+
+  We begin with game $G_0=\ExpGSACAnonb$. From it, we build $G_1$, where we
+  simply replace the \NIZKSetup functions for $\NIZKRel_{\Sign}$ and
+  $\NIZKRel_{\Open}$ within the \Setup algorithm. $G_1$ is indistinguishable
+  from $G_0$ due to the zero-knowledge property of the NIZK systems.
+
+  From $G_1$, we build $G_2$, where within the challenge signature produced by
+  \CHALb, we replace the \Ccom value encrypted within \Sign with a random
+  string of the appropriate length (e.g., the same length of the encrypted
+  message in $G_1$). The corresponding proof for $\NIZKRel_{\Sign}$ is thus
+  also simulated. The zero-knowledge and simulation-extractability properties
+  of the NIZKs for $\NIZKRel_{\Sign}$, and IND-CCA of the encryption
+  scheme, ensure that the result is indistinguishable to the adversary.
+
+  Now, observe that in $G_2$, the challenge signature received by the adversary
+  is completely independent from the challenge bit $b$. Moreover, as argued,
+  $G_2$ is indistinguishable from $G_0$, where the adversary plays the original
+  \ExpGSACAnonb game. Thus, our generic construction of \GSAC satisfies
+  anonymity, except with negligible probability.
+  %
+  \qed
+\end{proof}
+
+\begin{proof}[\thmref{thm:trace-gsac}]
+  Assuming the NIZK systems are sound, we build an adversary against existential
+  unforgeability of the signature scheme for blocks of committed messages.
+  %
+  Consider the following events:
+
+  \begin{description}
+  \item[$O$.] The \Open algorithm returns $\bot$.
+  \item[$J$.] The \Judge algorithm returns $0$.
+  \item[$D$.] No credential owned by a user in \CU contains \DAttrs.
+  \end{description}
+
+  Given these events, the adversary wins if:
+
+  \begin{description}
+  \item[$W_1 = O$.] \Open returns $\bot$ (line 5 of \ExpGSACTrace).
+  \item[$W_2 = \overline{O} \land J$.] \Open does not fail, but \Judge rejects
+    the output of \Open (line 7 of \ExpGSACTrace).
+  \item[$W_3 = \overline{O} \land \overline{J} \land D$.] \Open does not fail,
+    \Judge accepts the output by \Open, but no corrupt user has a credential
+    containing \DAttrs (line 8 of \ExpGSACTrace).
+  \end{description}
+
+  Clearly, since the group signature is verified at step 4 of the game, if
+  verification succeeds, soundness of $\NIZK_{\Sign}$ implies that $(\Ccom_m,
+  \Ec,\DAttrs) \in \NIZKLang_{\Sign}$, except with negligible probability
+  $2^{-\NIZKsecpar}$. Also, observe that each of the winning events for the
+  adversary described above are disjoint. Thus:
+
+  \begin{equation}
+    \AdvGSACTrace(\secpar) = \Pr[W_1]+\Pr[W_2]+\Pr[W_3]+\negl(\NIZKsecpar)
+  \end{equation}
+
+  $\Pr[W_1]=0$ is directly deduced from the fact that $(\Ccom_m,\Ec,\DAttrs)
+  \in \NIZKLang_{\Sign}$ due to soundness of $\NIZKRel_{\Sign}$. Concretely,
+  we know that \Open does not abort due to rejection of the signature by
+  \Verify (as this is checked in line 4 of \ExpGSACTrace too) and, thus,
+  $\Ec = \EEnc(\opk,\Ccom)$ which, by correctness of the encryption algorithm,
+  implies that $\Ccom = \EDec(\osk,\Ec)$, where $\upk=\Ccom=\CCommit(\usk;0)$.
+  Completeness of $\NIZK_{\Open}$ thus implies that the \Open algorithm can
+  compute the opening proof \oproof, and return $(\upk,\oproof)$.
+
+  $\Pr[W_2] = 0$ is similarly deduced from soundness of $\NIZK_{\Sign}$ and
+  completeness of $\NIZK_{\Open}$, since the opening proof is computed
+  honestly in line 6 of \ExpGSACTrace.
+
+  Finally, assume that there is an adversary $\adv$ against \ExpGSACTrace that
+  wins by event $W_3$. Then, it is straight forward to build an adversary \advB
+  against unforgeability of the signature scheme on blocks of committed
+  messages. Namely, \advB creates the parameters with \Setup and the opening
+  key pair with \OKeyGen, but instead of running \IKeyGen, sets the verification
+  key to the one received in the \ExpSBCMOMF game. In calls by $\adv$ to \OBTISS
+  and \ISSUE oracles, \advB replaces the \Issue algorithm with corresponding
+  calls to its $\langle \cdot,\SBCMSign \rangle$ oracle. The other oracles are
+  unchanged. Without loss of generality, suppose that $\adv$ makes a total of
+  $n$ queries to \OBTISS and \ISSUE, combined; which implies that \advB makes
+  a total of $n$ queries to its own oracle. If, in such an execution, $\adv$
+  wins by event $W_3$, it means that it has produced a signature \sig, revealing
+  attribute set \DAttrs, that is accepted by \Verify, for which \Open does not
+  fail, and for which an honestly generated open proof is accepted by \Judge,
+  but such that no issued credential contains \DAttrs. Soundness of
+  $\NIZK_{\Sign}$ implies that \sig is a valid signature over $\Attrs \cup
+  \lbrace \usk \rbrace$, and $\DAttrs \subseteq \Attrs$; but \sig has not been
+  produced via a call to the $\langle \cdot,\SBCMSign \rangle$ oracle. Thus,
+  \advB can output at least $n+1$ valid signatures, which contradicts security
+  of \SBCM.
+  %
+  By assumption of security of \SBCM, $\Pr[W_3]$ must therefore be negligible in
+  $\SBCMsecpar$ and, consequently: $\AdvGSACTrace(\secpar) = \negl(\SBCMsecpar)+
+  \negl(\NIZKsecpar)$, which is negligible.  
+  \qed
+\end{proof}
+
+\begin{proof}[\thmref{thm:frame-gsac}]
+  We build an adversary \advB who, given an adversary $\adv$ against
+  \ExpGSACNonframe, breaks the hiding property of \C.
+
+  To do so, we start with $G_0=\ExpGSACNonframe$. From $G_0$, we build $G_1$
+  by replacing $\NIZKSetup^{\NIZKRel_{\Issue}}$ and  $\NIZKSetup^{\NIZKRel_{\Sign}}$
+  with $\NIZKSimSetup^{\NIZKRel_{\Issue}}$ and $\NIZKSimSetup^{\NIZKRel_{\Sign}}$,
+  within the \Setup algorithm. Due to the zero-knowledge property of both
+  $\NIZK^{\NIZKRel_{\Issue}}$ and $\NIZK^{\NIZKRel_{\Sign}}$, $G_1$ is
+  indistinguishable from $G_0$.
+
+  We now build \advB from $G_1$. Recall that \advB is an adversary against
+  hiding of \C and, thus, receives a commitment \Ccom, committing to one out
+  of two possible messages, $\msg_0$ and $\msg_1$, which \advB picks at random
+  from $\AttrSpace$. \advB initializes everything as $G_1$ and, in addition,
+  chooses a random integer $u \in [q]$, where $q$ will be the maximim number of
+  users to let $\adv$ create via calls to the \HUGEN oracle (note though that
+  $q$ can be as large as desired, as it remains a polynomial function of the
+  security parameter). In the $u$-th call to the \HUGEN oracle, \advB ignores
+  sets $(\upk,\usk)$ to $(\Ccom,\bot)$. Calls to the \OBTAIN and \SIGN oracles
+  are dealt with as usual, except when $\adv$ requests credentials or signatures
+  on behalf of the $u$-th user. In that cases, \advB simulates the corresponding
+  NIZK proofs by calling $\NIZKSim^{\NIZKRel_{\Issue}}$ or
+  $\NIZKSim^{\NIZKRel_{\Sign}}$, respectively. Due to the
+  simulation-extractability property of both NIZK systems, the output produced
+  by the oracles is indistinguishable from that in $G_1$ and, consequently, from
+  $G_0=\ExpGSACNonframe$.
+
+  Finally, assume that $\adv$ wins \ExpGSACNonframe with non-negligible
+  probability. This means that it outputs a $(\sig = (\Ec,\pi_\sig),\DAttrs,
+  \msg,\upk,\pi)$, where $(\sig,\DAttrs,\msg)$ are accepted by \Verify, and
+  $(\upk,\pi,\sig,\DAttrs,\msg)$ are accepted by \Judge. Thus, after soundness
+  of $\NIZK^{\NIZKRel_{\Sign}}$ and $\NIZK^{\NIZKRel_{\Open}}$, we know that
+  \upk is the correct public key associated to an honest user \uid, but as per
+  the winning condition, \sig has not been produced via a call to the \SIGN
+  oracle for a \cid owned by \uid. Therefore, we can extract the \usk
+  corresponding to \upk from the $\pi_{\sig}$ proof. Since executions in the
+  environment prepared by \advB are indistinguishable to $\adv$ from executions
+  of $G_0$, we can assume that the probability that the \uid associated to the
+  \sig output by $\adv$ equals $1/q$. In that case, \usk precisely matches
+  $\msg_b$, and \advB wins the hiding game against \C. Since we assume \C
+  to be hiding, this probability must therefore be negligible.   
+  \qed
+\end{proof}
 

### 2022-05-02 prism-backend/research/gsac/security-gsac.tex
Proofs for GSAC done (except correctnes...)

--- 2022-04-27 prism-backend/research/gsac/security-gsac.tex
@@
 \label{ssec:security-gsac}
+
+For the sake of brevity, here we just enuntiate the main theorems related to
+correctness and security of \GSAC, and defer the full proofs to
+\appref{sapp:gsac-proofs}.
 
@@
 
-\begin{proof}[\thmref{thm:correctness-gsac}]
-  \todo{XXX}
-\end{proof}
-
 \begin{theorem}[Anonymity of \GSACGen]
   \label{thm:anonymity-gsac}
-  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge and
-  simulation-extractable, our \GSACGen construction satisfies anonymity as
-  defined in \defref{def:anonymity-gsac}.
+  If the underlying $\NIZK^{\NIZKRel_{\Sign}}$ scheme is zero-knowledge and
+  simulation-extractable, and the encryption system is IND-CCA secure,
+  our \GSACGen construction satisfies anonymity as defined in
+  \defref{def:anonymity-gsac}.
 \end{theorem}
-
-\begin{proof}[\thmref{thm:anonymity-gsac}]
-  %
-  \qed
-\end{proof}
 
@@
   \label{thm:trace-gsac}
-  If the underlying scheme for \todo{xxx}, then our \GSACGen construction
-  satisfies traceability as defined in \defref{def:trace-gsac}, except
-  with negligible probability.
+  If the underlying $\NIZK^{\NIZKRel_{\Sign}}$ scheme is sound, the
+  $\NIZK^{\NIZKRel_{\Open}}$ is  complete, the public-key encryption algorithm
+  is correct, and the signature scheme for blocks of committed messages is
+  one-more unforgeable, then our \GSACGen construction satisfies traceability as
+  defined in \defref{def:trace-gsac}, except with negligible
+  probability.
 \end{theorem}
-
-\todo{\usk belongs to \AttrSpace! I think this can lead to malleability attacks.
-  Make them disjoint?}
-
-\begin{proof}[\thmref{thm:trace-gsac}]
-  \qed
-\end{proof}
 
@@
   \label{thm:frame-gsac}
-  If the underlying schemes for \todo{xxx}, then our \GSACGen construction
+  If the underlying scheme for $\NIZK^{\NIZKRel_{\Issue}}$,
+  $\NIZK^{\NIZKRel_{\Sign}}$ and $\NIZK^{\NIZKRel_{\Open}}$ are sound,
+  zero-knowledge, and simulation-extractable, and
+  the commitment scheme \C is hiding, then our generic \GSACGen construction
   satisfies non-frameability as defined in \defref{def:frame-gsac}, except with
@@
 \end{theorem}
-
-\begin{proof}[\thmref{thm:frame-gsac}]
-  \qed
-\end{proof}
 

### 2022-05-02 prism-backend/research/gsac/model-gsac.tex
Proofs for GSAC done (except correctnes...)
Some intro text.

@@
   \label{def:correctness-gsac}
-  A \GSAC scheme is correct if, for any p.p.t. adversary $\adv$, \ExpGSACCorrect
-  outputs 1 with negligible probability.
+  A \GSAC scheme is correct if, for any p.p.t. adversary $\adv$,
+  $\Pr[\ExpGSACCorrect(1^\secpar) = 1]$ is a negligible function of \secpar.
 \end{definition}
@@
 \end{figure}
-
-\todo{Correctness definition.}
 
@@
     \pcif \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0: \pcreturn 1 \\
-    \pcelse \pcif \forall \uid \in \CU, \nexists (\uid,\cdot,\Attrs) \in
-    \CRED~\st~\DAttrs \subseteq \Attrs: \pcreturn 1 \\
+    \pcelse \pcif \forall \uid \in \CU \cup \HU, \nexists (\uid,\cdot,\Attrs)
+    \in \CRED~\st~\DAttrs \subseteq \Attrs: \pcreturn 1 \\
     \pcreturn 0
@@
 
-\paragraph{Discussion.} %
+\subsubsection{A note comparing \GSAC with group signatures and
+  anonymous credentials.} %
+
+\GSAC is a direct combination of group signatures and anonymous credentials.
+%
+On the one hand, by restricting to credentials without attributes (i.e., where
+the only attribute is the user secret key), we get a vanilla group signature
+scheme. Although, strictly, our scheme allows users to fetch more than one
+credential -- which goes beyond vanilla group signatures -- this can be
+trivially ``compensated'' by requiring users to prove ownership of a
+conventional digital identity during the $\langle \Obtain,\Issue \rangle$
+protocol\footnote{This is indeed common practice, but also frequently ommitted
+  in research papers.}.
+%
+On the other hand, by instantiating a \GSAC scheme (e.g., as \GSACGen) and simply
+throwing out the opener's key pair (thus, making \Open and \Judge useless), one
+gets a vanilla anonymous credential system. Or, keeping \osk, one can build an
+anonymous credential system with blacklisting, which can be directly built via
+the \Open function.
+
+\todo{Can we do formal proofs here of $GSAC \implies$ GS and $GSAC \implies AC$?}
+
+\iffalse
 \todo{Modelling choices: HU and CU lists are typically updated in join protocols
@@
 
-\todo{Argue that our properties cover (and augment) a direct combination
-  (even if possible) of their GS and AC counterparts. Specifically, anonymity
-  of \GSAC is stronger than anonymity in GS and AC, and the same for trace and
-  non-frame.}
-
 \todo{It would be nice to prove that a \GSAC scheme to which we remove the
@@
   one credential per user, becomes a conventional GS scheme.}
+\fi
 

### 2022-05-02 prism-backend/research/gsac/sec-gsac.tex
Generic GSAC construction. Some reorganisation.
Some intro text.

@@
-\section{\GSAC: Merging Group Signatures and Anonymous Credentials}
+\section{\GSAC: Merging Group Signatures and Anonymous
+  Credentials}
 \label{sec:gsac}
 
-\todo{Some intro here}
+\todo{I think we should extend ``vanilla'' \GSAC to return the full \Attrs
+  in \Open, but without needing \trans as a parameter to \Open (for compatibility
+  with \UAS). This can be done by encrypting all attributes, including their
+  ciphertext in the signature, and proving they are part of the credential. This
+  would render the scheme too costly, but helps in arguing in favour of \UAS.}
+
+Before moving into our full-fledged scheme for universal anonymous signatures,
+we take a first step which, albeit somehow obvious and simple, helps understand
+our final goal. Namely, we give a scheme that combines in a quite direct manner
+the functionality of group signature schemes, and that of anonymous credential
+schemes.
+
+\paragraph{Why is this merge necessary in the real world?} %
+Despite being an \emph{a priori} simple combination of both schemes we argue
+that such a combination:
+
+\begin{itemize}
+\item Enables a natural way to incorporate accountability within 
+  privacy-preserving identities. Furthermore, it does so in a formal way,
+  via the traceability notion and, crucially, the non-frameability one,
+  (which is not present in anonymous credentials).
+\item Provides meaning to the conventional \Open functionality of group
+  signatures, which traditionally has only required that an abstract concept of
+  ``identity'' be returned. Concretely, assuming honest issuance (which is
+  already a requirement in anonymous credentials; and in group signatures for
+  traceability), we can make specific claims about the attributes associated to
+  de-anonymized signers. Otherwise, without integrating attributes within the
+  issued credentials, the value returned by \Open serves barely for blacklisting
+  or similar functionalities -- but otherwise gives no information straight away
+  about the signer's identity, forcing implementors to rely to non-cryptographic
+  means to retrieve such information.
+\end{itemize}
+
+\paragraph{Intuition of our design and construction.} %
+Functionally, we combine both worlds. Namely, a user can get as many credentials
+as s/he wants -- although all are tied to the same user key --, and signatures
+(or credential presentations) of the same credential must be unlinkable. In this
+simplified first step, we restrict to selective attribute disclosure, meaning
+that signatures produced by a credential reveal only a subset of the attributes
+in that credential. Given such a signature, there is a trusted opener who can
+de-anonymize its signer, producing back its public key, as well as a proof of
+correct opening.
+
+With respect to the model, privacy-wise this direct combination requires that
+any two signatures (credential presentations) reveal nothing about the
+credential used to produce them, beyond the revealed attributes. For this first
+step, security-wise we stick to the conventional separation of
+unforgeability-related properties in group signatures. That is, traceability
+requires that, in the presence of an honest issuer, all valid signatures must
+originate from a credential issued by the issuer; and, moreover, that no
+user can claim having attributes that have not been issued to a single
+credential. As in group signatures, if the issuer is corrupt, all we can hope
+for is that honest users do not get undeserved blame; but, other than that,
+the adversary can obviously obtain credentials with arbitrary attributes. Still,
+note that this is a clear gain with respect to conventional anonymous credential
+systems, which offer no security against a malicious issuer.
+
+Finally, in this first step, we restrict ourselves to signatures/presentations
+involving only one credential and, as stated, to selective attribute disclosure.
 
@@
 \input{construction-gsac.tex}
+\input{security-gsac.tex}
 

### 2022-05-03 prism-backend/research/gsac/app-building-blocks.tex
Formalising SBM and SBCM from SBM.

@@
 
+\subsection{Signatures over Blocks of Messages}
+\label{sapp:sbm}
+
+\todo{Intro to \SBM (CL,BBS+,PS...)}
+
 \subsection{Signatures over Blocks of Committed Messages}
@@
 
-\todo{Formal models on signatures over blocks of committed messages? I'm just
-  informally stating a model here, but there must be some more formal
-  reference... \cite{cl02,asm06,ps16} all kind of allow signatures on blocks of
-  (committed) messages, but they seem to use ad hoc models.}
+To the best of our knowledge, models of existing schemes for signing blocks of
+messages like \cite{cl02,asm06,ps16} target precisely the case of signing blocks
+of \emph{plain} messages, as described in \appref{sapp:sbm}. However, for our
+generic constructions, we need interactive signing protocols between a user
+and a signer, where the user has a block of messages to sign blindly, and both
+receive a common block of messages to be also included in the resulting
+signature. This is precisely the case of partially blind signatures, that
+collapse to blind signatures when there is no common message between user
+and signer; and to conventional signatures when the user does not input a
+message to be blindly signed \cite{ao00}. Partially blind signatures, as
+blind signatures \cite{ps96}, cannot be modelled with the conventional security
+against existential forgeries. Simply because the user is actually expected to
+be able to create signatures on messages unknown to the signer, which formally
+translates into the impossibility to check whether a signature output by the
+adversary is over a message that has been queried to the signing oracle or not.
+Instead of using the conventional existential unforgeability property,
+(partially) blind signature schemes move to the ``one-more'' paradigm, which
+demands that no adversary can produce $n+1$ signatures after having interacted
+with the signing oracle at most $n$ times.
 
-We use signature schemes that allow signing messages and commitments to messages
-in blocks (\SBCM), and are also compatible with (efficient) proof systems over
-the produced signature and signed (commitments to) messages. Such schemes build
-on a predefined scheme for commitments on blocks of messages \C (see
-\secref{sapp:commitments}). The algorithms composing an \SBCM scheme are as
-follows:
+Informally, the mentioned \SBM schemes \cite{cl02,asm06,ps16} and related works
+\cite{cdl16b} \todo{check} describe ways to support signing committed blocks of
+messages. But do not give security models of the resulting construction, nor
+of course prove its security. As we aim at using this variant as a generic
+building block, we give a formal model of such extension, that we call
+Signatures over Blocks of Committed Messages (\SBCM), from a generic \SBM model.
+The algorithms composing an \SBCM scheme are as follows:
 
@@
   \SBCMsig over $\smsg \cup \overline{\smsg}$.
-\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\smsg)$.] Checks whether \SBCMsig
-  is a valid signature over the set of messages \smsg (independently on whether
-  the messages where signed as commitments or not), under verification key
-  \SBCMvk.
+\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\widetilde{\smsg})$.] Checks
+  whether \SBCMsig is a valid signature over the set of messages
+  $\widetilde{\smsg}$ (independently on whether the messages where signed as
+  commitments or not), under verification key \SBCMvk.
 \end{description}
 
-In addition, we require that the produced signatures must be compatible with
-(efficient) NIZK proofs of knowledge of a signature, and of (arbitrary) claims
-over the signed (committed) messages.
+Note that these functionality is just a generalization of partially blind
+signature schemes, where both user and signer can produce signatures over
+blocks of (committed) messages. The correctness and security properties are
+then defined as follows.
 
@@
 
-\todo{BBS+ is proven to have EUF, but nothing is said against OMF. Relationship?}
+Finally, in addition, we require that the produced signatures must be compatible
+with (efficient) NIZK proofs of knowledge of a signature, and of (arbitrary)
+claims over the signed (committed) messages.
+
+\subsubsection{From EUF-secure \SBM schemes to OMF-secure \SBCM
+  schemes} %
+\todo{Describe and prove.}
 
@@
 We use non-interactive zero-knowledge proofs of knowledge (NIZKPoK, or, for
-short, NIZK) over NP relations, in the Common Reference String (CRS) model
-\needcite. A NIZK system is a tuple $(\NIZKSetup,\NIZKProve,\NIZKVerify)$,
-defined as follows \cite{gos06}:
+short, NIZK) over NP relations, in the Common Reference String (CRS) model. A
+NIZK system is a tuple $(\NIZKSetup,\NIZKProve,\NIZKVerify)$, defined as follows
+\cite{gos06}:
 

### 2022-05-03 prism-backend/research/gsac/app-gsac.tex
Formalising SBM and SBCM from SBM.

@@
 
+\subsubsection{\GSAC with Interactive Presentations}
+\label{ssap:interactive-gsac}
+
+Next, we sketch proofs of security for the case of \GSAC with interactive
+presentations like in the case of anonymous credentials.
+
+\paragraph{Anonymity.} To see why the interactive variant is anonymous, assume
+an adversary $\adv$ against anonymity in that case. We build \advB against the
+non-interactive \ExpGSACAnonb as follows. \advB initializes everything as in the
+\ExpGSACAnonb game. When $\adv$ initiates a call to its interactive \SIGN (resp.
+\CHALb) oracle, \advB picks a random number, and sends it to the adversary,
+along with the response of its own (non-interactive) \SIGN (resp. \CHALb)
+oracle where, to the message passed as parameter to its oracle, concatenates the
+produced random number. After such simulation, \advB just outputs whatever
+$\adv$ outputs. Clearly, the simulation is perfect and, if $\adv$ wins with
+non-negligible probability in the interactive case, then so does \advB in the
+non-interactive case.
+
+\paragraph{Traceability.} The simulation described for the anonymity case (i.e.,
+\advB choosing the random numbers, and concatenating them to the message to be
+signed) applies here too. Thus, an adversary against traceability in the
+interactive case, can be used to build an adversary that breaks traceability in
+the non-interactive counterpart.
+
+\paragraph{Non-frameability.} The simulation described for the anonymity case
+(i.e., \advB choosing the random numbers, and concatenating them to the message
+to be signed) applies here too. Thus, an adversary against non-frameability in
+the interactive case, can be used to build an adversary that breaks
+non-frameability in the non-interactive counterpart.
+
 \subsection{Concrete Instantiation with BBS+}

### 2022-05-03 prism-backend/research/gsac/extensions-gsac.tex
Formalising SBM and SBCM from SBM.

--- 2022-05-02 prism-backend/research/gsac/model-gsac.tex
@@
-\subsection{Model for \GSAC}
-\label{ssec:model-gsac}
+\subsection{\GSAC Variants}
+\label{ssec:variants-gsac}
 
-While group signatures and anonymous credentials share quite common syntax and
-security properties, which are even frequently formalised in a similar way,
-there are aspects that need to be considered with care.
+\paragraph{\GSAC with interactive presentations.} %
+In group signatures, the signing and verification process is non-interactive.
+That is, a group member produces a signature and eventually sends it to the
+verifier, who can check it without further interaction. Nevertheless, in
+anonymous credentials, this process is typically interactive, and consists of
+at least one round-trip. This can be useful, for instance, when some notion of
+freshness is necessary.
 
-The first choice that has to be made is whether to make sign/show and
-verification a non-interactive or an interactive process -- in group signatures,
-we are in the former case, whereas in anonymous credentials, we are in the
-latter. While both options are of course valid, this has direct impact in the
-modelling. We choose the non-interactive approach, and then prove how to
-generically translate it into an interactive process \todo{do we?}. The reason
-is that this results in a more flexible building block, suitable for a wider set
-of scenarios. And, syntactically, it seems more natural to combine two
-non-interactive processes into an interactive one, than the other way around.
+The approach to turn our non-interactive singing-verification into an
+interactive protocol that ensures freshness is evident: prior to signing the
+message, we require that the honest verifier sends to the user a number picked
+uniformly at random from an appropriate domain, which must be concatenated to
+the signed message. We sketch a proof for why does this result in a secure
+\GSAC scheme with interactive signing and verification in
+\appref{ssap:interactive-gsac}
 
-We also need to take into account that, in group signature schemes, users only
-get one membership credential -- typically bound to their personal secret
-key --, which they then use to create as many group signatures as they want. On
-the other hand, in anonymous credentials, users can get as many credentials as
-they desire, which can (typically) then be showed also arbitrarily many times.
-In this regard, we follow a somehow intermediate approach: users own a single
-personal secret key, which they can use to get as many credentials as they wish.
-Subsequently, they can use any of those credentials to create \GSAC signatures.
-This has, as expected, some nuanced impact in the modelling. For instance, in
-group signatures, tracing and non-frameability are frequently dependent on the
-open function, which (among other things) returns an index pointing to the join
-transcript associated with the user who produced the signature given by the
-adversary as a response to the game's challenge. In our approach, though, each
-user may have many such transcripts -- one per credential that the user
-obtains. However, note that what actually provides meaning to these notions
-is not the index; but the associated user key pair, which is moreover necessary
-to prove that the opening has been performed honestly. Thus, with some
-restructuring of the corresponding games, we can still capture the main
-meaning of these traceability and non-frameability notions from group
-signatures. This also impacts anonymity, since in group signatures, this is
-modelled by challenging the adversary to guess which user (which implicitly
-translates to ``which user credential'') out of two challenge users was
-leveraged to produce the challenge signature. But again, in our case, users may
-have multiple credentials. However, it seems sufficient to adopt a similar
-anonymity flavour to that of anonymous credentials, where the adversary has to
-distinguish between presentations (signatures) produced from two arbitrary
-credentials, independently on whether these credentials were obtained by the
-same user, or not.
-
-Getting closer to the anonymity definition of anonymous credentials also has the
-side effect to introduce the notions of attributes for free into the domain of
-group signatures -- which, up to now, had considered membership credentials
-\emph{without} attributes. Yet another side effect of introducing multiple
-attributes (if we think from a group signature perspective) is that, in order
-to avoid trivial wins, the anonymity game has to enforce that both challenge
-credentials reveal the same predicate on their attributes.
-\commentwho{Jesus}{Again, taking into account ABGS, this is no longer true.
-  Cross-check and re-write.}
-
-In the model described below, we follow closely the definitions from
-\cite{bsz05} for group signatures, and \cite{fhs19} for anonymous credentials
-(which are in turn influenced by \cite{bsz05}).
-
-\subsubsection{Syntax}
-\label{sssec:syntax-gsac}
-
-\begin{description}
-\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
-  returns a global system parameter variable \parm.
-\item[$(\ipk,\isk) \gets \IKeyGen(\parm)$.] Given global system parameters
-  \parm, returns the issuer's key pair. Hereafter, we assume that the public
-  part \ipk is added to the group public key \gpk.
-\item[$(\opk,\osk) \gets \OKeyGen(\parm)$.] Given global system parameters
-  \parm, returns an opener's key pair. Hereafter, we assume that the public part
-  \opk is added to the group public key \gpk.
-\item[$(\upk,\usk) \gets \UKeyGen(\parm)$.] Given global system parameters
-  \parm, returns a user's key pair.
-\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle \Obtain(\gpk,\usk,\Attrs),\Issue(\gpk,\isk,\Attrs) \rangle$.]
-  This interactive protocol lets a user with key pair (\upk,\usk) running the
-  \Obtain process, obtain a credential \cred with attributes \Attrs, by
-  communicating with an issuer, with private key \isk, running the \Issue
-  counterpart. The user outputs the produced credential \cred, while the issuer
-  outputs the protocol transcript \utrans for the produced credential.
-\item[$\sig \gets \Sign(\gpk,\usk,\cred,\DAttrs,\msg)$.] The user with
-  with secret key \usk, who obtained a credential \cred, produces a signature
-  \sig over message \msg, revealing subset of attributes \DAttrs in \cred.
-\item[$1/0 \gets \Verify(\gpk,\sig,\DAttrs,\msg)$.] Checks whether \sig is a
-  valid signature revealing the attribute set \DAttrs of its signing credential,
-  over message \msg.
-\item[$(\upk,\oproof)/\bot \gets
-  \Open(\gpk,\osk,\sig,\DAttrs,\msg)$.]
-  Given a signature \sig over message \msg, produced by a credential with
-  attributes containing the set \DAttrs, returns the public key \upk of the
-  signer, and a proof of opening correctness \oproof; or $\bot$ if the
-  opening process fails.
-\item[$1/0 \gets \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,
-  \msg)$.] Checks if \oproof is a valid opening correctness proof stating that
-  the user with key \upk generated signature \sig over message \msg, revealing
-  attributes $\DAttrs$. 
-\end{description}
-
-The correctness and security properties are defined with the help of the
-following sets of oracles, and global variables that help oracles and games
-keep consistent state.
-
-\paragraph{Global variables.} %
-All the honestly generated users (i.e., all honestly generated user key pairs,
-since we assume a one-to-one relationship between user and user key pair), as
-well as all honestly generated credentials, are assigned identifiers. Wex
-typically write as \uid for users' identifiers, and \cid for credentials'. The
-adversary can
-refer to any individual user or credential using the corresponding identifier --
-even though he may not know the actual contents of the key pairs or credentials.
-In games that involve challenge user or credential identifiers, we use \cuid and
-\ccid to refer to these challenge user/credential.
-%
-The games, usually through the oracles, keep track of the users (through
-set \UK) and credentials (through table \CRED) that are created as a result of
-oracle calls by the adversary, as well as the attributes that each credential
-is associated (through table \ATTR), and the user to which each credential has
-been issued to (through table \OWNR). We use the user and credential identifiers
-to reference specific user key pairs, credentials, and credential attributes.
-For instance, $\UK[\uid]$ refers to the user key pair corresponding to user
-with identifier \uid, $\PUBUK[\uid]$ refers to the public key of that key pair,
-and $\PRVUK[\uid]$ to the private key; credential $\CRED[\cid]$ refers to the
-credential data associated to the credential with identifier \cid; $\ATTR[\cid]$
-is the set of attributes that was assigned to the credential with identifier
-\cid; and $\OWNR[\cid]$ is set to the \uid corresponding to the user that
-credential \cid was issued to.
-%
-Additionally, the games keep track of all honest and corrupt users that have
-been generated, through sets \HU and \CU, respectively. They also keep track of
-the signatures that have been honestly produced, through the \SIG table. Since
-signatures are produced through credentials, the \SIG table is indexed with
-{\cid}s. For the anonymity game, we also need to keep track of the challenge
-signatures that the adversary has obtained, in order to prevent trivial wins
-by allowing any of them to be opened. 
-%
-All global variables are initially set by the games to empty values (denoted
-with $\bot$), and all tables/sets are initialized as empty tables/sets, denoted
-with $\emptyset$. Also, for readability, we abuse the syntax as follows: we
-write $\CRED[\uid]$ to mean $\CRED[\cid]$ for all $\cid$ such that
-$\OWNR[\cid] = \uid$; we also sometimes use \upk as a ``synonym'' of \uid, as it
-is possible to do a reverse lookup from the \UK table (i.e., $\CRED[\upk]$ can
-be replaced by $\CRED[\uid]~\st~\UK[\uid]=(\upk,\cdot)$); \todo{Something else?}
-
-\paragraph{Oracles.} %
-Oracles are the interface of the adversary with the corresponding games. In
-other words: through these oracles, the game enviroment exposes to the adversary
-functionality that could otherwise be executed only by honest parties with
-private knowledge -- knowledge that would make the adversary capable of
-trivially breaking the security properties formalized in the experiments.
-In the game-based definitions of our \GSAC model, we leverage the following
-oracles, which are formally defined in \appref{app:gsac-formal}.
-
-\begin{description}
-\item[\RREG.] Reads the given transcript table entry.
-\item[\WREG.] Sets a transcript table entry to the given value.
-\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
-  the user's key pair.
-\item[\CUGEN.] If the specified user identifier is not already in the game,
-  sets the user public key to a value given by the adversary. If it already
-  exists, and is associated to an honest user, then it reveals to the adversary
-  the user's secret key.
-\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
-  the game, on behalf of an honest user.
-\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
-  in games that support it, by letting it interact with honest users who want to
-  receive credentials.
-\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
-  requesting an honest issuer to produce credentials fo them.
-\item[\SIGN.] Lets the adversary get signatures from credentials belonging
-  to honest users.
-\item[\OPEN.] Given an honestly produced signature, lets the adversary learn
-  which credential was used to produce it.
-\item[\CHALb.] Upon receiving two challenge credentials, a common intersecting
-  set of attributes, and a message, returns a signature produced by one of these
-  two credentials, defined by the bit $b$, which is established in the anonymity
-  game.
-\end{description}
-
-\paragraph{Correctness.} %
-Correctness of \GSAC schemes is formalized through the experiment in
-\figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
-revealing attributes \DAttrs, which was honestly produced though a credential
-that was obtained by an honest user interacting with an honest issuer, with a
-set of attributes \Attrs such that $\DAttrs \subseteq \Attrs$, must be accepted
-by \Verify. Moreover, an honestly produced correctness proof of opening for such
-signature, revealing the public key pair of the user, must also be accepted by
-\Judge.
-
-\begin{definition}{(Correctness of \GSAC)}
-  \label{def:correctness-gsac}
-  A \GSAC scheme is correct if, for any p.p.t. adversary $\adv$,
-  $\Pr[\ExpGSACCorrect(1^\secpar) = 1]$ is a negligible function of \secpar.
-\end{definition}
-
-\begin{figure}[htp!]
-  \procedure{$\ExpGSACCorrect(1^\secpar)$}{%
-     \parm \gets \Setup(1^\secpar) \\
-     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
-     \gpk \gets (\ipk,\opk) \\
-    (\cid,\DAttrs,\msg) \gets \adv^{\HUGEN,\OBTISS,\RREG}(\gpk) \\
-    \pcif \DAttrs \nsubseteq \ATTR[\cid] :
-    \pcreturn \bot \\
-    \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\DAttrs,\msg) \\
-    (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\DAttrs,\msg) \\
-    \pcif \Verify(\gpk, \sig, \DAttrs,\msg) = 0 \lor
-    \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0: \\
-     \pcind \pcreturn 1 \\
-    \pcreturn 0
-  }
-  \caption{Correctness experiment for \GSAC schemes.}
-  \label{fig:exp-gsac-corr}
-\end{figure}
-
-\subsubsection{Security Properties}
-\label{sssec:security-gsac}
-
-\paragraph{Anonymity.} %
-In group signatures, anonymity captures that no adversary must be able to learn,
-from any group signature, anything about its signer. In anonymous credentials,
-it requires that no adversary should learn anything about the holder of a
-credential that has been successfully shown, beyond that he owns a credential
-containing the revealed attributes. In both GS and AC, it is also typically
-required that
-multiple signatures/presentations by the users are unlinkable. The approach to
-formally state this property is in both cases frequently the same: the adversary
-picks two (honest) users (or credentials in the AC case), the game randomly
-chooses one of them, and lets the adversary request challenge
-signatures/presentations from it. The adversary wins if it succeeds in guessing
-which was the chosen user/credential better than guessing at random. In group
-signatures, the game must also restrict the adversary from opening challenge
-signatures. In anonymous credentials, the game must further constraint the
-adversary to pick credentials that have some common subset of attributes, and
-to use that common subset to request the challenge presentations. Here, we need
-to take into account both. Furthermore, a key difference with group signatures
-is that the game requires the adversary to output credential identifiers, rather
-than user identifiers. Specifically, this means that the adversary may actually
-output two credentials that belong to the same user. Therefore, in some sense,
-the anonymity we get is more general than that of group signatures. The formal
-specification of the anonymity game is given in \figref{fig:exp-gsac-anonb}.
-%
-Similarly, this notion of anonymity is also stronger than the notion of
-anonymity in both group signatures and anonymous credentials, in the sense
-that calls to the \OPEN oracle reveal the public key and credential of the users
-that (via the \SIGN and \CHALb oracles) create the signatures that the adversary
-sees. Therefore, all security relies \emph{only} on the user secret key.
-
-\begin{figure}[htp!]
-  \procedure[linenumbering]{$\ExpGSACAnonb(1^\secpar)$}{%
-     \parm \gets \Setup(1^\secpar) \\
-     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
-     \gpk \gets (\ipk,\opk) \\
-     (\cid_0,\cid_1,\status) \gets
-     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN}(\choose,\gpk,\isk) \\
-     b^* \gets
-     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN,\CHALb}(\guess,\gpk,\isk,\status) \\
-     \pcreturn b^*
-  }
-  \caption{Anonymity experiment for \GSAC schemes.}
-  \label{fig:exp-gsac-anonb}
-\end{figure}
-
-\begin{definition}{(Anonymity of \GSAC)}
-  \label{def:anonymity-gsac}
-  We define the advantage \AdvGSACAnon of $\adv$ against \ExpGSACAnonb as
-  $\AdvGSACAnon=|\Pr\lbrack\ExpGSACAnono(1^\secpar)=1\rbrack-
-  \Pr\lbrack\ExpGSACAnonz(1^\secpar)=1\rbrack|$.
-  %
-  A \GSAC scheme satisfies anonymity if, for any p.p.t. adversary $\adv$,
-  \AdvAnon is a negligible function of $1^\secpar$.
-\end{definition}
-
-\paragraph{Traceability.} %
-Traceability is one of the unforgeability-related properties in group
-signatures. It captures that any signature accepted by \Verify needs to open
-to one of the users that joined the group. While there is no traceability notion
-in anonymous credentials, it is natural to map it to their unforgeability
-property; if only because both require the issuer to be honest. Unforgeability
-in anonymous credentials typically ensures that no adversary can get a verifier
-to accept a credential presentation requiring a set of attributes that is not
-contained in one of the credentials controlled by the adversary.
-%
-Our notion of traceability for \GSAC combines both requirements. It assumes an
-honest issuer, as otherwise the adversary can create untraceable credentials at
-will. The game then lets the adversary add honest and corrupt users, create
-honest signatures, and open them. The adversary wins if, after this interaction,
-is able to produce a $(\sig,\DAttrs,\msg)$ tuple that is accepted by \Verify,
-but either cannot be opened, it can be opened but the proof is rejected by
-\Judge, or even though it is accepted by \Judge, there is no credential
-controlled by the adversary that contains the set of attributes \DAttrs. We
-formally define traceability in the \ExpTrace experiment in
-\figref{fig:exp-gsac-trace}.
-
-\begin{figure}[htp!]
-  \procedure[linenumbering]{$\ExpGSACTrace(1^\secpar)$}{%
-    \parm \gets \Setup(1^\secpar) \\
-    (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
-    \gpk \gets (\ipk,\opk) \\
-    (\sig,\DAttrs,\msg) \gets
-    \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
-    \pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 0: \pcreturn 0 \\
-    \pcif \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) = \bot: \pcreturn 1 \\
-    \textrm{Let}~(\upk,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) \\
-    \pcif \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0: \pcreturn 1 \\
-    \pcelse \pcif \forall \uid \in \CU \cup \HU, \nexists (\uid,\cdot,\Attrs)
-    \in \CRED~\st~\DAttrs \subseteq \Attrs: \pcreturn 1 \\
-    \pcreturn 0
-  }
-  \caption{Traceability experiment for \GSAC schemes.}
-  \label{fig:exp-gsac-trace}
-\end{figure}
-
-\begin{definition}{(Traceability of \GSAC)}
-  \label{def:trace-gsac}
-  We define the advantage \AdvGSACTrace of $\adv$ against \ExpGSACTrace as
-  $\AdvGSACTrace=\Pr\lbrack\ExpGSACTrace(1^\secpar)=1\rbrack$.
-  %
-  A \GSAC scheme satisfies traceability if, for any p.p.t. adversary $\adv$,
-  \AdvGSACTrace is a negligible function of $1^\secpar$.
-\end{definition}
-
-\paragraph{Non-frameability.} %
-Non-frameability variants are a core unforgeability-type property in group
-signatures. However, no
-similar property is modelled for anonymous credentials (\todo{see the discussion
-  in \secref{sec:introduction} for further detail}). It is a quite strong
-property, as it must be ensured even in the presence of dishonest issuer and
-opener. Intuitively, it prevents the adversary from creating a signature that
-frames an honest user. Depending on the inspection capabilities of the scheme,
-this framing could be done in different ways; i.e., by convincing third parties
-that signatures by different (possibly corrupt) users are linked, or directly
-by having open proofs output the identity of a user who did not create the
-signature being opened.
-%
-In \GSAC schemes, in order for a user to be framed, the adversary first needs to
-create a $(\sig,\DAttrs,\msg,\upk,\Attrs,\oproof)$ such that the signature,
-attributes, and message are accepted by \Verify, and which, along with the user
-public key, and open correctness proof, are accepted by \Judge.
-Then, the adversary wins the game if the owner of the credential is honest, but
-the signature was not produced via the \SIGN oracle, or if the set of attribute
-disclosed in the signature are not contained in the set of attributes revealed
-during \Open.
-
-\begin{figure}[htp!]
-  \procedure[linenumbering]{$\ExpGSACNonframe(1^\secpar)$}{%
-    \parm \gets \Setup(1^\secpar) \\
-     (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
-     \gpk \gets (\ipk,\opk) \\
-     (\sig,\DAttrs,\msg,\upk,\oproof) \gets
-     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
-     \textrm{Let}~\uid~\textrm{be st}~\PUBUK[\uid] = (\upk,\cdot) \\
-     \pcreturn 1~\pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 1 \land 
-     \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 1~\land \\
-     \pcind \uid \in \HU \land \sig \notin \SIG[\uid] \\
-     \pcreturn 0
-  }
-  \caption{Non-frameability experiment for \GSAC schemes.}
-  \label{fig:exp-gsac-frame}
-\end{figure}
-
-\begin{definition}{(Non-frameability of \GSAC)}
-  \label{def:frame-gsac}
-  We define the advantage \AdvGSACNonframe of $\adv$ against \ExpGSACNonframe as
-  $\AdvGSACNonframe=\Pr\lbrack\ExpGSACNonframe(1^\secpar)=1\rbrack$.
-  %
-  A \GSAC scheme satisfies non-frameability if, for any p.p.t. adversary $\adv$,
-  \AdvNonframe is a negligible function of $1^\secpar$.
-\end{definition}
-
-\subsubsection{A note comparing \GSAC with group signatures and
-  anonymous credentials.} %
+\paragraph{Comparing \GSAC with group signatures and anonymous
+  credentials.} %
 
@@
 %
-On the other hand, by instantiating a \GSAC scheme (e.g., as \GSACGen) and simply
+On the other hand, by instantiating a \GSAC scheme and simply
 throwing out the opener's key pair (thus, making \Open and \Judge useless), one

### 2022-05-03 prism-backend/research/gsac/model-gsac.tex
Formalising SBM and SBCM from SBM.

--- 2022-04-29 prism-backend/research/gsac/model-gsac.tex
@@
 latter. While both options are of course valid, this has direct impact in the
-modelling. We choose the non-interactive approach, and then prove how to
-generically translate it into an interactive process \todo{do we?}. The reason
+modelling. We choose the non-interactive approach, and then sketch how to
+generically (and trivially) translate it into an interactive process. The reason
 is that this results in a more flexible building block, suitable for a wider set
@@
 same user, or not.
-
+%
 Getting closer to the anonymity definition of anonymous credentials also has the
@@
 credentials reveal the same predicate on their attributes.
-\commentwho{Jesus}{Again, taking into account ABGS, this is no longer true.
-  Cross-check and re-write.}
 
@@
 
-\subsubsection{Syntax}
+\subsubsection{Syntax for \GSAC schemes}
 \label{sssec:syntax-gsac}
@@
 since we assume a one-to-one relationship between user and user key pair), as
-well as all honestly generated credentials, are assigned identifiers. Wex
-typically write as \uid for users' identifiers, and \cid for credentials'. The
+well as all honestly generated credentials, are assigned identifiers. We
+typically write \uid for users' identifiers, and \cid for credentials'. The
 adversary can
@@
 %
-The games, usually through the oracles, keep track of the users (through
-set \UK) and credentials (through table \CRED) that are created as a result of
-oracle calls by the adversary, as well as the attributes that each credential
-is associated (through table \ATTR), and the user to which each credential has
-been issued to (through table \OWNR). We use the user and credential identifiers
-to reference specific user key pairs, credentials, and credential attributes.
+The games keep track of the user keys (through set \UK) and credentials (through
+table \CRED) that are created as a result of oracle calls by the adversary. We
+use the user and credential identifiers to reference specific user key pairs,
+credentials, and credential attributes.
 For instance, $\UK[\uid]$ refers to the user key pair corresponding to user
@@
 %
-All global variables are initially set by the games to empty values (denoted
-with $\bot$), and all tables/sets are initialized as empty tables/sets, denoted
-with $\emptyset$. Also, for readability, we abuse the syntax as follows: we
+All global variables are assumed to be initially set by the games to empty
+values, and all tables/sets are initialized as empty tables/sets. Also, for
+readability, we abuse the syntax as follows: we
 write $\CRED[\uid]$ to mean $\CRED[\cid]$ for all $\cid$ such that
-$\OWNR[\cid] = \uid$; we also sometimes use \upk as a ``synonym'' of \uid, as it
-is possible to do a reverse lookup from the \UK table (i.e., $\CRED[\upk]$ can
-be replaced by $\CRED[\uid]~\st~\UK[\uid]=(\upk,\cdot)$); \todo{Something else?}
+$\OWNR[\cid] = \uid$.% ; we also sometimes use \upk as a ``synonym'' of \uid, as it
+% is possible to do a reverse lookup from the \UK table (i.e., $\CRED[\upk]$ can
+% be replaced by $\CRED[\uid]~\st~\UK[\uid]=(\upk,\cdot)$); \todo{Something else?}
 
@@
 \item[\ISSUE.] Allows the adversary to play the role of dishonest users,
-  requesting an honest issuer to produce credentials fo them.
+  requesting an honest issuer to produce credentials for them.
 \item[\SIGN.] Lets the adversary get signatures from credentials belonging
@@
 \item[\OPEN.] Given an honestly produced signature, lets the adversary learn
-  which credential was used to produce it.
+  the public key of the user who produced it.
 \item[\CHALb.] Upon receiving two challenge credentials, a common intersecting
@@
 \figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
-revealing attributes \DAttrs, which was honestly produced though a credential
+revealing attributes \DAttrs, which was honestly produced through a credential
 that was obtained by an honest user interacting with an honest issuer, with a
@@
 
-\todo{Correctness definition.}
-
-\subsubsection{Security Properties}
+\subsubsection{Security Properties of \GSAC Schemes}
 \label{sssec:security-gsac}
@@
 In group signatures, anonymity captures that no adversary must be able to learn,
-from any group signature, anything about its signer. In anonymous credentials,
-it requires that no adversary should learn anything about the holder of a
-credential that has been successfully shown, beyond that he owns a credential
-containing the revealed attributes. In both GS and AC, it is also typically
-required that
+from any group signature, anything about its signer. In anonymous credentials
+(with selective disclosure), it requires that no adversary should learn anything
+about the holder of a credential that has been successfully shown, beyond that
+he owns a credential containing the revealed attributes. In both GS and AC, it
+is also typically required that
 multiple signatures/presentations by the users are unlinkable. The approach to
@@
 output two credentials that belong to the same user. Therefore, in some sense,
-the anonymity we get is more general than that of group signatures. The formal
+the anonymity we get is more general than that of group signatures, as in \GSAC,
+like in anonymous credentials, the adversary may request signatures from
+different credentials, but belonging to the same user. The formal
 specification of the anonymity game is given in \figref{fig:exp-gsac-anonb}.
-%
-Similarly, this notion of anonymity is also stronger than the notion of
-anonymity in both group signatures and anonymous credentials, in the sense
-that calls to the \OPEN oracle reveal the public key and credential of the users
-that (via the \SIGN and \CHALb oracles) create the signatures that the adversary
-sees. Therefore, all security relies \emph{only} on the user secret key.
 
@@
 \Judge, or even though it is accepted by \Judge, there is no credential
-controlled by the adversary that contains the set of attributes \DAttrs. We
-formally define traceability in the \ExpTrace experiment in
-\figref{fig:exp-gsac-trace}.
+that contains the set of attributes \DAttrs. We formally define traceability in
+the \ExpTrace experiment in \figref{fig:exp-gsac-trace}.
 
@@
 Non-frameability variants are a core unforgeability-type property in group
-signatures. However, no
-similar property is modelled for anonymous credentials (\todo{see the discussion
-  in \secref{sec:introduction} for further detail}). It is a quite strong
+signatures. However, no similar property is modelled for anonymous credentials
+(see the discussion in \todo{\secref{sec:introduction}} for further detail). It
+is a quite strong
 property, as it must be ensured even in the presence of dishonest issuer and
@@
 In \GSAC schemes, in order for a user to be framed, the adversary first needs to
-create a $(\sig,\DAttrs,\msg,\upk,\Attrs,\oproof)$ such that the signature,
+create a $(\sig,\DAttrs,\msg,\upk,\oproof)$ tuple such that the signature,
 attributes, and message are accepted by \Verify, and which, along with the user
@@
 Then, the adversary wins the game if the owner of the credential is honest, but
-the signature was not produced via the \SIGN oracle, or if the set of attribute
-disclosed in the signature are not contained in the set of attributes revealed
-during \Open.
+the signature was not produced via the \SIGN oracle.
+
+%, or if the set of attribute disclosed in the signature are not contained in the
+% set of attributes revealed during \Open.
 
@@
 
-\paragraph{Discussion.} %
-\todo{Modelling choices: HU and CU lists are typically updated in join protocols
-  in the GS literature. Here, it is best to follow the AC literature, as a same
-  user (key) may be associated to multiple join protocols. So there are HUGEN
-  and CUGEN oracles.}
-
-\todo{Other modelling choice: We could return the full set of attributes
-  contained in the credential used for creating an opened signature, but that
-  would require either complicating the proof, or access to the transcripts log
-  at open time, which I opted to avoid for better compatibility with \UAS.}
-
-\todo{Argue that our properties cover (and augment) a direct combination
-  (even if possible) of their GS and AC counterparts. Specifically, anonymity
-  of \GSAC is stronger than anonymity in GS and AC, and the same for trace and
-  non-frame.}
-
-\todo{It would be nice to prove that a \GSAC scheme to which we remove the
-  \Open/\Judge functions becomes an AC scheme. And conversely, a \GSAC scheme
-  where all credentials have no attributes, and where we restrict to only
-  one credential per user, becomes a conventional GS scheme.}
-
 %%% Local Variables:

### 2022-05-03 prism-backend/research/gsac/preliminaries.tex
Proofs for GSAC done (except correctnes...)
Formalising SBM and SBCM from SBM.

--- 2022-04-05 prism-backend/research/gsac/preliminaries.tex
@@
-\section{Preliminaries}
+{Preliminaries}
 \label{sec:preliminaries}
@@
 
-\todo{NIZKs.}
+Next we introduce the main building blocks we will be using in our
+constructions. More detailed definitions and references appear in
+\appref{app:crypto-building-blocks}.
 
-\subsubsection{Notation}
+\paragraph{Digital Signatures.} %
+Defined as a tuple $(\SSetup,\SKeyGen,\SSign,\SVerify)$. Algorithm $\Sparm \gets
+\SSetup(\Ssecpar)$ produces public parameters for the other algorithms.
+$(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$ generates the verification-signing key
+pair, algorithm $\Ssig \gets \SSign(\Ssk,\msg)$ signs message \msg with
+signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\Svk,
+\Ssig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
+verification key \Svk. We rely on existentially unforgeable digital signature
+schemes.
+
+\paragraph{Public-Key Encryption.} %
+Defined as a tuple $(\ESetup,\EKeyGen,\EEnc,\EDec)$. Algorithm $\Eparm \gets
+\ESetup(\Esecpar)$ produces public parameters for the other algorithms.
+$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$ generates the encryption-decryption key
+pair, algorithm $\Ec \gets \EEnc(\Eek,\msg)$ encrypts message \msg with
+encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\Edk,
+\Ec)$ decrypts ciphertexts using decryption key \Edk. We rely on \todo{IND-CCA}
+public-key encryption schemes.
+
+\paragraph{(Vector) Commitment Schemes.} %
+Defined as a tuple $(\CSetup,\CCommit)$. Algorithm $\Cparm \gets
+\CSetup(\Csecpar)$ produces the parameters for committing to values. $\Ccom
+\gets \CCommit(\Cparm, \smsg; r)$ produces a commitment \Ccom over a set of
+messages \smsg, using randomness $r$ (which we may omit when explicitly
+stating it is not necessary). We will further use commitment schemes that
+allow committing to vectors of messages. Therein, the \CCommit algorithm simply
+receives a vector of messages. In both cases, we require hiding and binding
+(vector) commitment schemes.
+
+\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
+We use signature schemes that allow signing blocks of messages, or commitments
+to blocks of messages, and which are furthermore compatible with (efficient)
+proof systems over the produced signature and signed (commitments to) messages.
+For this purpose, we define such schemes as a tuple $(\SBCMSetup,\SBCMKeyGen,
+\SBCMCom,\SBCMSign,\SBCMVerify)$. Algorithm $\SBCMparm \gets
+\SBCMSetup(\SBCMsecpar)$ produces the public parameters for the scheme.
+$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$ produces a verification-signing
+key pair. $\SBCMsig/\bot \gets\langle \SBCMCom(\SBCMvk,\overline{smsg},\smsg),
+\SBCMSign(\SBCMsk,\smsg) \rangle$ is an interactive protocol between a user, who
+runs \SBCMCom and has a set of messages $\overline{\smsg}$ to be block-committed,
+and a signer, who owns signing key \SBCMsk; both also receive common input a
+block of messages \smsg. The output of the protocol is a signature over
+$\overline{\smsg} \cup \smsg$. Algorithm $1/0 \gets \SBCMVerify(\SBCMvk,
+\SBCMsig,\widetilde{\smsg})$ verifies a signature \SBCMsig over message set
+$\widetilde{\smsg}$, which must contain both the messages that were signed as
+a block commitment as well as those signed in ``the clear''. In addition, the
+produced signatures must be compatible with (efficient) NIZK proofs of knowledge
+of a signature, and of (arbitrary) claims over the signed (committed) messages.
+An \SBCM scheme must provide \todo{one-more-forgery} type of security.
+
+\paragraph{Non-Interactive Zero-Knowledge.} %
+We use non-interactive zero-knowledge proofs of knowledge (NIZK), in the CRS
+model. Informally, a NIZK scheme over an NP relation \NIZKRel is defined as a
+tuple $(\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel,\NIZKVerify^\NIZKRel)$.
+Algorithm $\NIZKcrs \gets \NIZKSetup^\NIZKRel(\NIZKsecpar)$ produces the common
+reference string \NIZKcrs. $\NIZKproof/\bot \gets \NIZKProve^\NIZKRel(\NIZKcrs,
+\NIZKx,\NIZKw)$ creates a NIZK proof of knowledge of witness \NIZKw for \NIZKx
+such that $(\NIZKw,\NIZKx) \in \NIZKRel$. $1/0 \gets \NIZKVerify^\NIZKRel
+(\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof. Within NIZK systems, we
+further need schemes that provide simulation-extractability, which in a nutshell
+means that no adversary can produce a proof from which we cannot extract a
+witness, even after seeing polynomially many simulated proofs. To model
+simulation-extractable NIZKs, we further need algorithms \NIZKSimSetup,
+\NIZKSim, and \NIZKExtract, that allow simulating proofs and extracting
+witnesses. The properties we build on are completeness, soundness,
+zero-knowledgeness, and simulation-extractability.
+
+\subsection{Notation}
 \label{ssec:notation}
@@
 
+\todo{In \secref{ssec:generic-construction-uas} we use $\usk \in \cred$ to
+  denote the claim ``\usk is an attribute attested in \cred''.}
+
+\todo{In GSAC traceability proof, we use $\negl(\cdot)$ to denote negligible
+  functions.}
+
 %%% Local Variables:

### 2022-05-03 prism-backend/research/gsac/sec-gsac.tex
Formalising SBM and SBCM from SBM.

@@
   ciphertext in the signature, and proving they are part of the credential. This
-  would render the scheme too costly, but helps in arguing in favour of \UAS.}
+  would render the scheme too costly, but helps in arguing in favour of \UAS.
+  Still, leaving that for after having updated the \UAS section, to see how
+  it fits the global picture.}
 
@@
 
-\paragraph{Intuition of our design and construction.} %
+\paragraph{Intuition for our design and construction.} %
 Functionally, we combine both worlds. Namely, a user can get as many credentials
@@
 requires that, in the presence of an honest issuer, all valid signatures must
-originate from a credential issued by the issuer; and, moreover, that no
-user can claim having attributes that have not been issued to a single
-credential. As in group signatures, if the issuer is corrupt, all we can hope
-for is that honest users do not get undeserved blame; but, other than that,
-the adversary can obviously obtain credentials with arbitrary attributes. Still,
-note that this is a clear gain with respect to conventional anonymous credential
-systems, which offer no security against a malicious issuer.
-
+originate from a credential issued by the issuer; and, from the AC domain, we
+import the requirement that no user can claim having attributes that have not
+been issued to a single credential. As in group signatures, if the issuer is
+corrupt, all we can hope for is that honest users do not get undeserved blame;
+but, other than that, the adversary can obviously obtain credentials with
+arbitrary attributes. Still, note that this is a clear gain with respect to
+conventional anonymous credential systems, which offer no security against a
+malicious issuer.
+%
 Finally, in this first step, we restrict ourselves to signatures/presentations
-involving only one credential and, as stated, to selective attribute disclosure.
+involving only one credential, to a system with only one issuer and opener  and,
+as stated, to selective attribute disclosure.
 
@@
 \input{security-gsac.tex}
+\input{extensions-gsac.tex}
 

### 2022-05-03 prism-backend/research/gsac/sec-uas.tex
Seemingly stable model anc concrete instantiation for GSAC.
Refined UAS model. Seems ok, but need to add extractability definition.
Added some BB definitions.
Formalising SBM and SBCM from SBM.

--- 2022-04-04 prism-backend/research/gsac/sec-gsac.tex
@@
-\section{\GSAC: Merging Group Signatures and Anonymous Credentials}
-\label{sec:gsac}
+\section{From \GSAC to \UAS}
+\label{sec:uas}
 
-\todo{Some intro here}
+\GSAC is a very interesting exercise that showcases the advantages of direct
+combination of group signatures and anonymous credentials. However, it also
+inherits a main limitation: it is too strict in regards to the utility it
+offers. The most excruciating example of this fact is that in \GSAC, via \Open,
+one can only get the actual identity of the signer. Even though with the inclusion
+of attributes the concept of ``identity'' can now be meaningfully defined, we
+may not want to fully de-anonymize the signer. Instead, we may be interested in
+revealing arbitrary functions of its identity and the signed message. Also, for
+the sake of illustation, we restricted to the case of selective disclosure, and
+to only one credential per signature. Then, the natural question is whether we
+can model an extension to \GSAC that is compatible both with constructions with
+that support selective disclosure, and with constructions that support arbitrary
+claims on the
+credential attributes; and, as it is also common in the anonymous credentials
+(or verifiable credentials \needcite) domains, to allow credential holders to
+combine multiple credentials into one signature/presentation. Similarly, we can
+also generalize \GSAC by allowing users to leverage previously obtained
+credentials in order to obtain new ones; possibly, applying arbitrary issuance
+policies. In a nutshell, our generalization of \GSAC into Universal Anonymous
+Signatures (\UAS), enables:
 
-\input{model-gsac.tex}
-\input{construction-gsac.tex}
+\begin{itemize}
+\item Using previously obtained credentials to request new ones, applying
+  arbitrary policies to the credentials involved in the request, in
+  order to determine whether the new issuance should proceed or not.
+\item Modulating the type of utility one wants to get directly from signatures.
+  That is, let signatures disclose a subset of the attributes in the credentials
+  involved in the signing process, prove arbitrary claims over those attributes,
+  or even reveal absolutely nothing at all beyond that that an owner of a valid
+  credential created the signature.
+\item Defining arbitrary de-anonymization functions, over the signer's
+  credentials and signed message. This can range from producing the user public
+  key (as in group signatures), to disallowing any kind of de-anonymization,
+  passing through any intermediate de-anonymization function, like revealing
+  the nationality of the signer, or its banking account number, even if this
+  was not revealed at the signing stage.
+\end{itemize}
+
+Furthermore, to make the concept more flexible, we no longer restrict to the
+case of one issuer and one opener. Instead, \UAS supports multiple issuers (as
+in generalized variants of anonymous credentials), as well as multiple openers,
+each one with a predefined inspection function. Thus, it supports use cases like
+having a user produce a signature with credentials obtained from issuers A and
+B, which can be inspected by opener C; but later use the same credentials
+from issuers A and B, to produce a signature that can be inspected by opener D.
+A consequence of this is that the concept of ``group'', which was very present
+in \GSAC, is now blurred in \UAS, and we get closer to the context of anonymous
+credentials -- while still offering the accountability we inherit from \GSAC
+via \Open and \Judge.
+
+\input{model-uas.tex}
+\input{construction-uas.tex}
+\input{security-uas.tex}
 

### 2022-05-04 prism-backend/research/gsac/app-building-blocks.tex
Updated SBCM definition, and gen constructions of UAS and GSAC accordingly. SBCM proofs pending.

@@
 commitments \cite{bcc+15}.
-
-\subsection{Signatures over Blocks of Messages}
-\label{sapp:sbm}
-
-\todo{Intro to \SBM (CL,BBS+,PS...)}
-
-\subsection{Signatures over Blocks of Committed Messages}
-\label{sapp:sbcm}
-
-To the best of our knowledge, models of existing schemes for signing blocks of
-messages like \cite{cl02,asm06,ps16} target precisely the case of signing blocks
-of \emph{plain} messages, as described in \appref{sapp:sbm}. However, for our
-generic constructions, we need interactive signing protocols between a user
-and a signer, where the user has a block of messages to sign blindly, and both
-receive a common block of messages to be also included in the resulting
-signature. This is precisely the case of partially blind signatures, that
-collapse to blind signatures when there is no common message between user
-and signer; and to conventional signatures when the user does not input a
-message to be blindly signed \cite{ao00}. Partially blind signatures, as
-blind signatures \cite{ps96}, cannot be modelled with the conventional security
-against existential forgeries. Simply because the user is actually expected to
-be able to create signatures on messages unknown to the signer, which formally
-translates into the impossibility to check whether a signature output by the
-adversary is over a message that has been queried to the signing oracle or not.
-Instead of using the conventional existential unforgeability property,
-(partially) blind signature schemes move to the ``one-more'' paradigm, which
-demands that no adversary can produce $n+1$ signatures after having interacted
-with the signing oracle at most $n$ times.
-
-Informally, the mentioned \SBM schemes \cite{cl02,asm06,ps16} and related works
-\cite{cdl16b} \todo{check} describe ways to support signing committed blocks of
-messages. But do not give security models of the resulting construction, nor
-of course prove its security. As we aim at using this variant as a generic
-building block, we give a formal model of such extension, that we call
-Signatures over Blocks of Committed Messages (\SBCM), from a generic \SBM model.
-The algorithms composing an \SBCM scheme are as follows:
-
-\begin{description}
-\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
-  for the other algorithms, given an input security parameter \Ssecpar.
-\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
-  verification-signing key pair.
-\item[$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},\smsg),
-  \SBCMSign(\SBCMsk,\smsg) \rangle$.] An interactive protocol between two
-  parties with shared input a block of messages \smsg. The party running
-  \SBCMCom further knows a set of messages $\overline{\smsg}$ to be
-  block-committed and then signed along with \smsg. The party running \SBCMSign
-  controls the signing key \SBCMsk. As a result, both parties get signature
-  \SBCMsig over $\smsg \cup \overline{\smsg}$.
-\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\widetilde{\smsg})$.] Checks
-  whether \SBCMsig is a valid signature over the set of messages
-  $\widetilde{\smsg}$ (independently on whether the messages where signed as
-  commitments or not), under verification key \SBCMvk.
-\end{description}
-
-Note that these functionality is just a generalization of partially blind
-signature schemes, where both user and signer can produce signatures over
-blocks of (committed) messages. The correctness and security properties are
-then defined as follows.
-
-\paragraph{Correctness.} %
-Informally, an \SBCM scheme is correct if signatures generated between an honest
-party running \SBCMCom with message sets $\overline{\smsg}$ and \smsg, and an
-honest signer running \SBCMSign over \smsg, for honestly generated parameters
-and key pairs, results in a signature over $\smsg \cup \overline{\smsg}$ that is
-accepted by \SBCMVerify.
-
-\paragraph{Unforgeability.} %
-It must be unfeasible for an adversary to produce signatures over blocks of
-messages that have not been signed (in plain, or committed shape) by the
-signer. More formally, an \SBCM scheme is unforgeable if, for all p.p.t.
-adversaries $\adv$, $\Pr[\ExpSBCMOMF(\SBCMsecpar) = 1]$, as defined in
-\figref{fig:sbcm-games}, is a negligible function of the security parameter.
-Note that this follows the ``one-more-forgery'' type of definition of blind
-signatures \cite{bold02}.
-
-\paragraph{Blindness.} %
-Finally, the signer must not learn the plaintext values of the messages that are
-signed in committed form. Note that this is a weaker notion than the usual
-blindness property of blind signature schemes, where it is required that the
-adversary cannot link a signature to the signing process that produced it.
-Formally, blindness for \SBCM schemes is defined as in \ExpSBCMBlindb in
-\figref{fig:sbcm-games}. An \SBCM scheme is blind if, for all p.p.t.
-adversaries $\adv$, $|\Pr[\ExpSBCMBlindo(\SBCMsecpar) = 1] -
-\Pr[\ExpSBCMBlindz(\SBCMsecpar) = 1]|$ is a negligible function of the security
-parameter.
-
-\begin{figure}[ht!]
-  \begin{minipage}[t]{\textwidth}
-    \centering
-
-    \procedure{$\ExpSBCMOMF(\SBCMsecpar)$}{%
-      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
-      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
-      ((\sig_1,\smsg_1),\dots,(\sig_{n+1},\smsg_{n+1})) \gets
-      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
-      \pcif \exists i \in [n+1]~\st~\SBCMVerify(\SBCMvk,\sig_i,\smsg_i) = 0:
-      \pcreturn 0 \\
-      \pcif \exists i \neq j \in [n+1]~\st~\smsg_i = \smsg_j: \pcreturn 0 \\
-      \pcif \langle \cdot, \SBCMSign(\SBCMsk,\cdot)\rangle~
-      \textrm{was called more than $k$ times}: \pcreturn 0 \\
-      \pcreturn 1 \\
-    }
-
-    \procedure{$\ExpSBCMBlindb(\SBCMsecpar)$}{%
-      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
-      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
-      (\overline{\smsg}_0,\overline{\smsg}_1,\smsg) \gets
-      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
-      \csig \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg}_b,\smsg),
-      \SBCMSign(\SBCMsk,\smsg) \rangle \\
-      b^* \gets \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk,
-      \csig) \\
-      \pcif b = b^*: \pcreturn 1 \\
-      \pcreturn 0
-    }
-  \end{minipage}
-  \label{fig:sbcm-games}
-  \caption{Games for \SBCM schemes.}
-\end{figure}
-
-Finally, in addition, we require that the produced signatures must be compatible
-with (efficient) NIZK proofs of knowledge of a signature, and of (arbitrary)
-claims over the signed (committed) messages.
-
-\subsubsection{From EUF-secure \SBM schemes to OMF-secure \SBCM
-  schemes} %
-\todo{Describe and prove.}
 
@@
 
+\iffalse
+\subsection{Signatures over Blocks of Messages}
+\label{sapp:sbm}
+
+A signature scheme on blocks of messages (\SBM) allows a signer to create a
+single signature over a set of messages. The resulting signature is typically
+more concise than just creating multiple signatures, and typical schemes
+\cite{cl02,asm06,ps16} are additionally compatible with efficient proof
+protocols over the signed messages. The functionality offered by an \SBM scheme
+is as follow:
+
+\begin{description}
+\item[$\SBMparm \gets \SBMSetup(\SBMsecpar)$.] It produces public parameters
+  for the other algorithms, given an input security parameter \SBMsecpar.
+\item[$(\SBMvk,\SBMsk) \gets \SBMKeyGen(\SBMparm)$.] Generates a
+  verification-signing key pair.
+\item[$\SBMsig \gets \SBMSign(\SBMsk,\smsg)$.] Produces a signature \sig, over
+  a block of messages \smsg, using signing key \SBMsk.
+\item[$1/0 \gets \SBMVerify(\SBMvk,\SBMsig,\widetilde{\smsg})$.] Checks
+  whether \SBMsig is a valid signature over the set of messages \smsg, under
+  verification key \SBMvk.
+\end{description}
+
+An \SBM scheme must satisfy correctness and unforgeability properties.
+
+\paragraph{Correctness.} %
+Informally, an \SBM scheme is correct if signatures generated between an honest
+party running running \SBMSign over \smsg, for honestly generated parameters
+and key pairs, results in a signature over $\smsg \cup \overline{\smsg}$ that is
+accepted by \SBMVerify.
+
+\paragraph{Unforgeability.} %
+It must be unfeasible for an adversary to produce signatures over blocks of
+messages that have not been signed by the signer. More formally, an \SBM scheme
+is unforgeable if, for all p.p.t. adversaries $\adv$, $\Pr[\ExpSBMEUF
+(\SBMsecpar) = 1]$, as defined in \figref{fig:sbm-games}, is a negligible
+function of the security parameter.
+
+\begin{figure}[ht!]
+  \begin{minipage}[t]{\textwidth}
+    \centering    
+    \procedure{$\ExpSBMEUF(\SBMsecpar)$}{%
+      \SBMparm \gets \SBMSetup(\SBMsecpar) \\
+      (\SBMvk,\SBMsk) \gets \SBMKeyGen(\SBMparm) \\
+      (\SBMsig,\smsg) \gets \adv^{\SSign(\SBMsk,\cdot)}(\SBMvk) \\
+      \pcif \SBMVerify(\SBMvk,\SBMsig,\smsg) = 0: \pcreturn 0 \\
+      \pcif \smsg~\textrm{was not queried to \SBMSign}: \pcreturn 1 \\
+      \pcreturn 0
+    }
+  \end{minipage}
+  \label{fig:sbm-games}
+  \caption{Unforgeability game for \SBM schemes.}
+\end{figure}
+\fi
+
+\subsection{Signatures over Blocks of Committed Messages}
+\label{sapp:sbcm}
+
+For our generic constructions, we use interactive signing protocols between a
+user and a signer, where the user has a block of messages to sign blindly, and
+both receive a common block of messages to be also included in the resulting
+signature. This is precisely the case of partially blind signatures, that
+collapse to blind signatures when there is no common message between user
+and signer; and to conventional signatures when the user does not input a
+message to be blindly signed \cite{ao00}. Partially blind signatures, as
+blind signatures \cite{ps96}, cannot be modelled with the conventional security
+against existential forgeries. Simply because the user is actually expected to
+be able to create signatures on messages unknown to the signer, which formally
+translates into the impossibility to check whether a signature output by the
+adversary is over a message that has been queried to the signing oracle or not.
+Thus, instead of using the conventional existential unforgeability property,
+(partially) blind signature schemes move to the ``one-more'' paradigm, which
+demands that no adversary can produce $n+1$ distinct signatures after having
+interacted with the signing oracle at most $n$ times.
+
+To the best of our knowledge, models of existing schemes for signing blocks of
+messages like \cite{cl02,asm06,ps16,cdl16b} target the case of signing blocks
+of \emph{plain} messages, and are subsequently informally extended to support
+signing commitments to blocks of messages via interactive protocols. However,
+they do not support signing both committed and plain messages (although the
+extension is trivial); and, more importantly, do not give security models of
+the resulting construction, nor of course prove its security. While the
+extension seems straightforward, the modelling needs to be changed due to the
+mentioned nuance of the conventional EUF notion not being compatible with
+interactive signing protocols where the signer does not learn (some of) the
+signed message(s). As we aim at using this variant as a generic building block,
+we briefly model such a scheme for Signatures over Blocks of Committed Messages
+(\SBCM).
+
+The syntax for an \SBCM scheme is as follows:
+
+\begin{description}
+\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
+  for the other algorithms, given an input security parameter \SBCMsecpar.
+\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
+  verification-signing key pair.
+\item[$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},\smsg),
+  \SBCMSign(\SBCMsk,\smsg) \rangle$.] An interactive protocol between two
+  parties with shared input a block of messages \smsg. The party running
+  \SBCMCom further knows a set of messages $\overline{\smsg}$ to be
+  block-committed and then signed along with \smsg. The party running \SBCMSign
+  controls the signing key \SBCMsk. As a result, both parties get signature
+  \SBCMsig over $\smsg \cup \overline{\smsg}$.
+\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\overline{\smsg},\smsg)$.] Checks
+  whether \SBCMsig is a valid signature over the set of messages
+  $\overline{\smsg}$ and \smsg, under verification key \SBCMvk.
+\end{description}
+
+Note that these functionality is just a generalization of partially blind
+signature schemes, where both user and signer can produce signatures over
+blocks of (committed) messages. The correctness and security properties are
+then defined as follows.
+
+\paragraph{Correctness.} %
+Informally, an \SBCM scheme is correct if signatures generated between an honest
+party running \SBCMCom with message sets $\overline{\smsg}$ and \smsg, and an
+honest signer running \SBCMSign over \smsg, for honestly generated parameters
+and key pairs, results in a signature over $\overline{\smsg}$ and \smsg that is
+accepted by \SBCMVerify.
+
+\paragraph{Unforgeability.} %
+It must be unfeasible for an adversary to produce signatures over blocks of
+messages that have not been signed (in plain, or committed shape) by the
+signer. More formally, an \SBCM scheme is unforgeable if, for all p.p.t.
+adversaries $\adv$, $\Pr[\ExpSBCMOMF(\SBCMsecpar) = 1]$, as defined in
+\figref{fig:sbcm-games}, is a negligible function of the security parameter.
+Note that this follows the ``one-more-forgery'' type of definition of blind
+signatures \cite{bold02}.
+
+\paragraph{Blindness.} %
+Finally, the signer must not learn the plaintext values of the messages that are
+signed in committed form. Note that this is a weaker notion than the usual
+blindness property of blind signature schemes, where it is required that the
+adversary cannot link a signature to the signing process that produced it.
+Formally, blindness for \SBCM schemes is defined as in \ExpSBCMBlindb in
+\figref{fig:sbcm-games}. An \SBCM scheme is blind if, for all p.p.t.
+adversaries $\adv$, $|\Pr[\ExpSBCMBlindo(\SBCMsecpar) = 1] -
+\Pr[\ExpSBCMBlindz(\SBCMsecpar) = 1]|$ is a negligible function of the security
+parameter.
+
+\begin{figure}[ht!]
+  \begin{minipage}[t]{\textwidth}
+    \centering
+
+    \procedure{$\ExpSBCMOMF(\SBCMsecpar)$}{%
+      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
+      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
+      ((\sig_1,\overline{\smsg}_1, \smsg_1),\dots,
+      (\sig_{n+1},\overline{\smsg}_{n+1},\smsg_{n+1})) \gets
+      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
+      \pcif \exists i \in [n+1]~\st~\SBCMVerify(\SBCMvk,\sig_i,
+      \overline{\smsg}_i,\smsg_i) = 0: \pcreturn 0 \\
+      \pcif \exists i \neq j \in [n+1]~\st~\smsg_i = \smsg_j \land
+      \overline{\smsg}_i = \overline{\smsg}_j: \pcreturn 0 \\
+      \pcif \langle \cdot, \SBCMSign(\SBCMsk,\cdot)\rangle~
+      \textrm{was called more than $k$ times}: \pcreturn 0 \\
+      \pcreturn 1 \\
+    }
+
+    \procedure{$\ExpSBCMBlindb(\SBCMsecpar)$}{%
+      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
+      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
+      (\overline{\smsg}_0,\overline{\smsg}_1,\smsg) \gets
+      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
+      \csig \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg}_b,\smsg),
+      \SBCMSign(\SBCMsk,\smsg) \rangle \\
+      b^* \gets \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk,
+      \csig) \\
+      \pcif b = b^*: \pcreturn 1 \\
+      \pcreturn 0
+    }
+  \end{minipage}
+  \label{fig:sbcm-games}
+  \caption{Games for \SBCM schemes.}
+\end{figure}
+
+Finally, in addition, we require that the produced signatures must be compatible
+with (efficient) NIZK proofs of knowledge of a signature, and of (arbitrary)
+claims over the signed (committed) messages.
+
+\subsection{An Instantiation of \SBCM with BBS+}
+
+Next, we give an instantiation of an \SBCM scheme, based on BBS+ signatures.
+We emphasize again that this is essentially equivalent to the protocol for
+signing committed block of messages in \cite{asm06} and, also, to the equivalent
+ones in \cite{cl02,ps16} (although not for BBS+ signatures). The main difference
+being that we allow merging committed blocks of messages and blocks of
+(plaintext) messages into the same signature.
+%
+Note also that, in our instantiation, we just include a generic \NIZK, for some
+relation over witness $\overline{\smsg}$ (i.e., the messages to be blindly
+signed), and statement $(\Ccom,\smsg)$ (i.e., their block commitment, and the
+plainly signed messages). This is intentional, as we want to support cases where
+proving arbitrary predicates is possible (as opposed to ``just'' proving that
+the commitment is over the messages in $\overline{\smsg}$).
+%
+When we want to make explicit the relation over which the employed \NIZK is
+defined, we add a $\NIZKRel$ superscript to the algorithms.
+
+\paragraph{$\SBCMparm \gets \SBCMSetup(\SBCMsecpar,\nattrs,\tnattrs)$.} %
+Generates a bilinear group $\BB = (p,\GG_1,\GG_2,\GG_T,\gen{g}_1,\gen{g}_2,e)
+\gets \PGen(\SBCMsecpar)$, and $\nattrs+\tnattrs+1$ additional generators
+$\gen{g}$, $\gen{h}_1,...,\gen{h}_{\nattrs}$,$\gen{\th}_1,...,\gen{\th}_{\tnattrs}$
+of $\GG_1$. Returns $\SBCMparm \gets (\SBCMsecpar,\nattrs,\tnattrs,\BB,
+\gen{g},\gen{h}_1,...,\gen{h}_{\nattrs},\gen{\th}_1,...,\gen{\th}_{\tnattrs})$.
+We assume that \SBCMparm is available to all other algorithms, even when not
+explicitly passed as an argument.
+
+\paragraph{$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.} %
+Parses \SBCMparm as $(\cdot,\cdot,(p,\GG_1,\GG_2,\GG_T,\gen{g}_1,\gen{g}_2,e),
+\dots$ $\NIZKcrs \gets \NIZKSetup(\secpar)$. Outputs $\SBCMsk \gets \ZZ^*_p$,
+and $\SBCMvk \gets (\NIZKcrs,\gen{g}_2^{\SBCMsk})$.
+
+\paragraph{$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},
+  \smsg), \SBCMSign(\SBCMsk,\smsg) \rangle$.} %
+
+\begin{itemize}
+\item \underline{User}: If $|\smsg|>\nattrs$ or $|\overline{\smsg}|>\tnattrs$,
+  abort. Else, fetch fresh randomness $r \getr \ZZ^*_p$, compute $\Ccom \gets
+  \gen{g}^r\prod_{i \in [|\overline{\smsg}|]}\gen{\th}_i^{\overline{\smsg}_i}$,
+  and $\NIZKproof \gets \NIZKProve(\NIZKcrs,(r,\overline{\smsg}),\Ccom)$.
+  Send $(\Ccom,\NIZKproof)$ to Issuer.
+\item \underline{Signer}: If $|\smsg|>\nattrs$, abort. Else, run $\NIZKVerify
+  (\NIZKcrs,\Ccom,\NIZKproof)$ and return $0$ if it fails. Else, compute
+  $x,\tilde{s} \getr \ZZ^*_p, A \gets (\gen{g}_1\Ccom \gen{g}^{\tilde{s}}
+  \prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i})^{1/(\SBCMsk+x)}$. Send
+  $(A,x,\tilde{s})$ to User.
+\item \underline{User}: If $A = 1_{\GG_1}$: return $0$. Else, compute
+  $s \gets r + \tilde{s}$. If $e(A,\gen{g}_2)^xe(A,\SBCMvk) \neq
+  e(\gen{g}_1\Ccom\gen{g}^{\tilde{s}}\prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i},
+  \gen{g}_2)$: return $0$. Else, return $(A,x,s)$.
+\end{itemize}
+
+\paragraph{$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\overline{\smsg},\smsg)$.} %
+To verify a signature \SBCMsig, for message set $\overline{\smsg}$ that was
+signed as a block commitment, and message set \smsg, signed as plaintext, parse
+\SBCMsig as $(A,x,s)$ and check if $e(A,\gen{g}_2^x\SBCMvk) =
+e(\gen{g}_1\gen{g}^s\prod_{i \in |\overline{\smsg}|}\gen{h}^{\overline{\smsg}_i}
+\prod_{i \in |\smsg|}\gen{h}^{\smsg_i},\gen{g}_2)$
+
+\paragraph{Proving Knowledge of Signature.} %
+Note that proving knowledge of a BBS+ signature as produced in our \SBCM variant
+is essentially the same as in \cite{asm06,cdl16b}, only needing to account for
+the different basis for messages signed in committed and plain form.
+
+\subsubsection{Security.} Next, we sketch that the given BBS+ interactive
+signing protocol is correct and OMF-secure.
+
+\paragraph{Correctness.} \todo{XXX}
+
+\paragraph{OMF security.} \todo{YYY}
+
 %%% Local Variables:

### 2022-05-04 prism-backend/research/gsac/construction-uas.tex
Updated SBCM definition, and gen constructions of UAS and GSAC accordingly. SBCM proofs pending.

@@
 \paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\upk,\sipk,\attrs)\rangle$.} %
+  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle$.} %
 The protocol is run between an issuer, and a user with secret key \usk and
@@
 \attrs_{\cred} \cup \lbrace \usk \rbrace) = 1 \rbrace$. The interactive protocol
-for a user to obtain a credential from an issuer of the system is as follows:
+for a user to obtain a credential from an issuer of the system is then simply an
+execution of the interactive signing protocol of an \SBCM scheme, where the user
+runs $\SBCMCom(\ipk,\usk,\attrs)$, and the issuer runs $\SBCMSign(\isk,\attrs)$;
+in both cases, using $\NIZKRel_{\Issue}$ as \NIZK relation.
 
+\iffalse
 \begin{itemize}
@@
 \end{itemize}
+\fi
 

### 2022-05-05 prism-backend/research/gsac/app-gsac.tex
Making a pass.

@@
 
-        \procedure{$\OBTISS(\uid,\cid,\Attrs)$}{%
+        \procedure{$\OBTISS(\uid,\cid,\attrs)$}{%
           \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
@@
           \langle \cred, \utrans \rangle \gets
-          \langle \Obtain(\gpk,\PRVUK[\uid],\Attrs), \\
+          \langle \Obtain(\gpk,\PRVUK[\uid],\attrs), \\
           \pcind \pcind \pcind \pcind \pcind \pcind
-          \Issue(\gpk,\isk,\Attrs) \rangle \\
-          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets (\uid,\cred,\Attrs) \\
+          \Issue(\gpk,\isk,\attrs) \rangle \\
+          \trans[\cid] \gets \utrans;~\CRED[\cid] \gets (\uid,\cred,\attrs) \\
           \pcreturn \top \\
@@
 
-        \procedure{$\OBTAIN(\uid,\cid,\Attrs)$}{%
+        \procedure{$\OBTAIN(\uid,\cid,\attrs)$}{%
           \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
@@
           \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\gpk,\PRVUK[\uid],\Attrs),\adv \rangle \\
-          \CRED[\cid] \gets (\uid,\cred,\Attrs) \\
+          \langle \Obtain(\gpk,\PRVUK[\uid],\attrs),\adv \rangle \\
+          \CRED[\cid] \gets (\uid,\cred,\attrs) \\
           \pcreturn \top \\
@@
 
-        \procedure{$\ISSUE(\uid,\cid,\Attrs)$}{%
+        \procedure{$\ISSUE(\uid,\cid,\attrs)$}{%
           \pcif \uid \notin \CU: \pcreturn \bot \\
@@
           \langle \cdot, \utrans \rangle \gets
-          \langle \adv, \Issue(\gpk,\isk,\Attrs) \rangle \\
+          \langle \adv, \Issue(\gpk,\isk,\attrs) \rangle \\
           \trans[\cid] \gets \utrans;~
-          \CRED[\cid] \gets (\uid,\cdot,\Attrs) \\
+          \CRED[\cid] \gets (\uid,\cdot,\attrs) \\
           \pcreturn \top \\          
@@
 
-        \procedure{$\SIGN(\cid,\DAttrs,\msg)$}{%
+        \procedure{$\SIGN(\cid,\dattrs,\msg)$}{%
           \uid \gets \OWNR[\cid] \\
@@
           \cred \gets \CRED[\cid] \\
-          \sig \gets \Sign(\gpk,\PRVUK[\uid],\cred,\DAttrs,\msg) \\
-          \SIG[\cid] \gets \SIG[\cid] \cup \lbrace (\sig,\DAttrs,\msg) \rbrace \\
+          \sig \gets \Sign(\gpk,\PRVUK[\uid],\cred,\dattrs,\msg) \\
+          \SIG[\cid] \gets \SIG[\cid] \cup \lbrace (\sig,\dattrs,\msg) \rbrace \\
           \pcreturn \sig \\
@@
           \pcif \sig \in \CSIG: \pcreturn \bot \\
-          (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\DAttrs,\msg) \\
+          (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\dattrs,\msg) \\
 %          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
@@
 
-        \procedure{$\CHALb(\ccid_0,\ccid_1,\DAttrs,\msg)$}{%
-          \pcif \DAttrs \nsubseteq \ATTR[\ccid_0] \cap \ATTR[\ccid_1]:
+        \procedure{$\CHALb(\ccid_0,\ccid_1,\dattrs,\msg)$}{%
+          \pcif \dattrs \nsubseteq \ATTR[\ccid_0] \cap \ATTR[\ccid_1]:
           \pcreturn \bot \\
@@
           \csig \gets \Sign(\gpk,\PRVUK[\cuid_b],\CRED[\ccid_b],
-          \DAttrs,\msg) \\
+          \dattrs,\msg) \\
           \CSIG \gets \CSIG \cup \lbrace \csig \rbrace \\
@@
   \item[$J$.] The \Judge algorithm returns $0$.
-  \item[$D$.] No credential owned by a user in \CU contains \DAttrs.
+  \item[$D$.] No credential owned by a user in \CU contains \dattrs.
   \end{description}
@@
     \Judge accepts the output by \Open, but no corrupt user has a credential
-    containing \DAttrs (line 8 of \ExpGSACTrace).
+    containing \dattrs (line 8 of \ExpGSACTrace).
   \end{description}
@@
   verification succeeds, soundness of $\NIZK_{\Sign}$ implies that $(\Ccom_m,
-  \Ec,\DAttrs) \in \NIZKLang_{\Sign}$, except with negligible probability
+  \Ec,\dattrs) \in \NIZKLang_{\Sign}$, except with negligible probability
   $2^{-\NIZKsecpar}$. Also, observe that each of the winning events for the
@@
 
-  $\Pr[W_1]=0$ is directly deduced from the fact that $(\Ccom_m,\Ec,\DAttrs)
+  $\Pr[W_1]=0$ is directly deduced from the fact that $(\Ccom_m,\Ec,\dattrs)
   \in \NIZKLang_{\Sign}$ due to soundness of $\NIZKRel_{\Sign}$. Concretely,
@@
   wins by event $W_3$, it means that it has produced a signature \sig, revealing
-  attribute set \DAttrs, that is accepted by \Verify, for which \Open does not
+  attribute set \dattrs, that is accepted by \Verify, for which \Open does not
   fail, and for which an honestly generated open proof is accepted by \Judge,
-  but such that no issued credential contains \DAttrs. Soundness of
-  $\NIZK_{\Sign}$ implies that \sig is a valid signature over $\Attrs \cup
-  \lbrace \usk \rbrace$, and $\DAttrs \subseteq \Attrs$; but \sig has not been
+  but such that no issued credential contains \dattrs. Soundness of
+  $\NIZK_{\Sign}$ implies that \sig is a valid signature over $\attrs \cup
+  \lbrace \usk \rbrace$, and $\dattrs \subseteq \attrs$; but \sig has not been
   produced via a call to the $\langle \cdot,\SBCMSign \rangle$ oracle. Thus,
@@
   Finally, assume that $\adv$ wins \ExpGSACNonframe with non-negligible
-  probability. This means that it outputs a $(\sig = (\Ec,\pi_\sig),\DAttrs,
-  \msg,\upk,\pi)$, where $(\sig,\DAttrs,\msg)$ are accepted by \Verify, and
-  $(\upk,\pi,\sig,\DAttrs,\msg)$ are accepted by \Judge. Thus, after soundness
+  probability. This means that it outputs a $(\sig = (\Ec,\pi_\sig),\dattrs,
+  \msg,\upk,\pi)$, where $(\sig,\dattrs,\msg)$ are accepted by \Verify, and
+  $(\upk,\pi,\sig,\dattrs,\msg)$ are accepted by \Judge. Thus, after soundness
   of $\NIZK^{\NIZKRel_{\Sign}}$ and $\NIZK^{\NIZKRel_{\Open}}$, we know that
@@
 Intuitively, the credentials that we generate for our \GSAC construction are
-Pedersen commitments to $(\usk,\credid,\Attrs)$ tuples; i.e., they have
+Pedersen commitments to $(\usk,\credid,\attrs)$ tuples; i.e., they have
 the following structure: $\gen{h}_0^r\gen{h}_1^{\usk}\prod_{i \in [2,\nattrs+1]}
-\gen{h}_i^{\Attrs_i}$, where the exponent in $\gen{h_0}$ is a fresh random value
+\gen{h}_i^{\attrs_i}$, where the exponent in $\gen{h_0}$ is a fresh random value
 that ensures hiding, the exponent in $\gen{h_1}$ encodes the user private
@@
 
-\paragraph{$\langle \Obtain(\gpk,\usk,\Attrs),\Issue(\gpk,\isk,\Attrs) \rangle
+\paragraph{$\langle \Obtain(\gpk,\usk,\attrs),\Issue(\gpk,\isk,\attrs) \rangle
   \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.} %
@@
 key, and asks the issuer to sign the commitment, along with any other arbitraty
-set of revealed attributes \Attrs. For proving knowledge of the private key, we
+set of revealed attributes \attrs. For proving knowledge of the private key, we
 define relation $\NIZKRel_{\Issue} = \lbrace (r, \usk), \Ccom: \Ccom =
@@
   $x,\tilde{s} \getr \ZZ^*_p, A \gets
-  (\gen{g}_1\Ccom h_0^{\tilde{s}} \prod_{i \in \Attrs}
-  \gen{h}_i^{\Attrs_i})^{1/(\isk+x)}$.
+  (\gen{g}_1\Ccom h_0^{\tilde{s}} \prod_{i \in \attrs}
+  \gen{h}_i^{\attrs_i})^{1/(\isk+x)}$.
   Send $(A,x,\tilde{s})$ to User, and output $\utrans \gets
-  (\Ccom,(A,x,\tilde{s}),\Attrs,\NIZKproof)$.
+  (\Ccom,(A,x,\tilde{s}),\attrs,\NIZKproof)$.
 \item \underline{User}: If $A = 1_{\GG_1}$: return $0$. Else, compute
   $s \gets r + \tilde{s}$. If $e(A,\gen{g}_2)^xe(A,\ipk) \neq
-  e(\gen{g}_1\Ccom\gen{h}_0^{\tilde{s}}\prod_{i \in \Attrs}\gen{h}_i^{\Attrs_i},
+  e(\gen{g}_1\Ccom\gen{h}_0^{\tilde{s}}\prod_{i \in \attrs}\gen{h}_i^{\attrs_i},
   \gen{g}_2)$: return $0$. Else, return
@@
 
-\paragraph{$\Sign(\gpk,\usk,\cred,\DAttrs,\msg) \rightarrow \sig$.} %
+\paragraph{$\Sign(\gpk,\usk,\cred,\dattrs,\msg) \rightarrow \sig$.} %
 To create a signature, the user first randomizes its BBS+ credential \cred and
@@
 proof. For this, we define relation
-$\NIZKRel_{\Sign}= \lbrace (r,\usk,\Attrs,r_2,r_3,s',\msg),(\DAttrs,c_1,c_2,
+$\NIZKRel_{\Sign}= \lbrace (r,\usk,\attrs,r_2,r_3,s',\msg),(\dattrs,c_1,c_2,
 \Cmsg): \Cmsg = \gen{h}^\msg \land c_1 = g^r \land c_2 = \opk^r\gen{h}_1^{\usk}
 \land \hat{A}/d = (A')^{-x}\gen{h}_0^{r_2} \land
-\gen{g}_1 \prod_{i \in \DAttrs} \gen{h}_i^{\Attrs_i} =
+\gen{g}_1 \prod_{i \in \dattrs} \gen{h}_i^{\attrs_i} =
 d^{r_3}\gen{h}_0^{-s'}\gen{h}_1^{-\usk}
-\prod_{i \notin \DAttrs} \gen{h}_i^{-\Attrs_i} \rbrace$.
+\prod_{i \notin \dattrs} \gen{h}_i^{-\attrs_i} \rbrace$.
 
@@
   \hat{A} \gets (A')^{-x}(\gen{g}_1\gen{h}_0^s\gen{h}_1^{\usk}
-  \prod_{i \in \Attrs}\gen{h}_i^{\Attrs_i})^{r_1}$,
+  \prod_{i \in \attrs}\gen{h}_i^{\attrs_i})^{r_1}$,
   $d \gets (\gen{g}_1\gen{h}_0^s\gen{h}_1^{\usk}
-  \prod_{i \in \Attrs}\gen{h}_i^{\Attrs_i})^{r_1}\gen{h}_0^{-r_2}$.
+  \prod_{i \in \attrs}\gen{h}_i^{\attrs_i})^{r_1}\gen{h}_0^{-r_2}$.
 \item Encrypt $\upk=\gen{h}_1^{\usk}$ with ElGamal as $r \getr \ZZ^*_p,
@@
   $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs,
-  (r,\usk,\Attrs,r_2,r_3,s',\msg), (\DAttrs,c_1,c_2,\Cmsg))$.
+  (r,\usk,\attrs,r_2,r_3,s',\msg), (\dattrs,c_1,c_2,\Cmsg))$.
 \item Return $\sig \gets (c=(c_1,c_2),(A',\hat{A},d),\NIZKproof)$.
@@
 
-\paragraph{$\Verify(\gpk,\sig,\DAttrs,\msg) \rightarrow 1/0$.} %
+\paragraph{$\Verify(\gpk,\sig,\dattrs,\msg) \rightarrow 1/0$.} %
 Parse \gpk as $(\ipk,\opk)$ and $\sig$ as $(c=(c_1,c_2),
@@
 e(\hat{A},\gen{g}_2)$. Compute $\Cmsg \gets \gen{h}^\msg,$ and return
-$\NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs,(\DAttrs,c_1,c_2,\Cmsg),
+$\NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs,(\dattrs,c_1,c_2,\Cmsg),
 \NIZKproof)$.
 
-\paragraph{$\Open(\gpk,\osk,\sig,\DAttrs,\msg)
+\paragraph{$\Open(\gpk,\osk,\sig,\dattrs,\msg)
   \rightarrow (\upk,\oproof)/\bot$.} %
@@
 
-\paragraph{$\Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg)
+\paragraph{$\Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg)
   \rightarrow 1/0$.} %
@@
 % \commentwho{Jesus}{For consistency with \UAS, maybe remove the need to return
-%   \Attrs in \Open, and return \DAttrs instead. Then, we do not need to pass
-%   \trans as a parameter to \Open, as \DAttrs is already attested for in the
+%   \attrs in \Open, and return \dattrs instead. Then, we do not need to pass
+%   \trans as a parameter to \Open, as \dattrs is already attested for in the
 %   signature being opened. It also makes sense from the point of view that we
@@
 %   requested the signature (the verifier) didn't seem to consider necessary, as
-%   s/he only requested \DAttrs. Still, if we make this modification, mention the
-%   possibility to return \Attrs, and the option to do it via adding \trans as a
+%   s/he only requested \dattrs. Still, if we make this modification, mention the
+%   possibility to return \attrs, and the option to do it via adding \trans as a
 %   parameter to \Open (or including an encryption of all attributes in the

### 2022-05-05 prism-backend/research/gsac/conclusion.tex
Merged GSAC and UAS into uas.tex paper. Defining concrete instantiation of GSAC.
Making a pass.

@@
 
+Some notes on future work, to expand/refine/remove:
+
+\begin{itemize}
+\item Add support for open functions over sets of previously issued signatures.
+  This would cover existing schemes like \cite{dl21}, and possibly cool cases
+  such as training AI models on private data, in a federated manner, without
+  revealing the identity of the node running the model.
+\item Currently, in \UAS, we need to restrict challenge users to present
+  credentials issued by the same set of issuers. Technically, I guess that this
+  could be done by making the issuers' public keys part of the witness (although,
+  at what cost?). But then, how would verifiers be able to determine whether
+  they trust the issuers of the credentials used to compute the signature? It
+  would be as if an employer has to accept a University degree, without knowing
+  which university issued it.  
+\item Potentially very cool improvement in the modelling: maybe we can leverage
+  a decentralized append-only bulletin board (so, a blockchain) to reduce trust
+  on the issuers (except identity proofing, we could probably eliminate it...)
+  That would be quite innovative, as in GS literature, the issuer has so far
+  alwasy been thought to be necessarily honest. (Disclaimer: this was Ezequiel's
+  suggestion!)
+\item The current syntax of \UAS does not seem to support blind issuance. This
+  would however be trivial to achieve by adding a set of attributes to be
+  blindly issued in the \Obtain algorithm, and then requiring that they are
+  validated in \fissue. In the generic construction, this would be directly
+  supported too, as a block of messages to be signed as part of the block
+  commitment.
+\end{itemize}
+
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "sok-privsig"
+%%% TeX-master: "uas"
 %%% End:

### 2022-05-05 prism-backend/research/gsac/construction-uas.tex
Making a pass.

@@
 In this section, we give a generic construction of an \UAS scheme, based on
-generic building blocks. In \secref{sec:instantiation}, we give a concrete
+generic building blocks. In \todo{\secref{sec:instantiation}}, we give a concrete
 instantiation.
 
-We use three different NP relations in our generic construction. Namely,
-$\NIZKRel_{\Issue}$ for issuance, $\NIZKRel_{\Sign}$ for signing, and
-$\NIZKRel_{\Inspect}$ for inspection. We will be defining them in the
-corresponding protocol/algorithm.
+We use three different NP relations in our generic construction. Namely:
 
-\todo{Many variables need renaming here.}
+\begin{description}
+\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs the rules for issuing
+  new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
+  (\usk,\scred,\attrs_{\scred}), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
+  \CCommit(usk) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
+  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1 \rbrace$,
+  where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
+  \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
+  Basically, this relation requires that, in order to issue a credential with
+  attribtes \attr, and bound to \usk, the requester has to commit to \usk and
+  prove knowledge of it, as well as prove that all additional credentials needed
+  for the issuing to be granted, meet some defined policy \fissue.
+\item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
+  verifiers define them. Governs what utility information is directly revealed
+  by signatures. It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
+  \attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec =
+  \EEnc(\Eek,\yinsp;r) \land \yeval = \feval(\usk,\scred,\msg) \land
+  \yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
+  \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$, with
+  $\attrs_{\scred}$ and $\sipk_{\scred}$ as in $\NIZKRel_{\Issue}$. In a
+  nutshell, this relation ensures that signatures will produce the correct
+  signature evaluation and opening values, and that any credential used to
+  create the signature is bound to the same \usk key.
+\item[$\NIZKRel_{\Open}$:] Set by openers, governs the utility information
+  to be extracted by the \Open algorithm. It is defined as $\NIZKRel_{\Open} =
+  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$. It proves
+  that the decryption of the opening utility value has been done correctly.
+\end{description}
 
@@
 \NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$, $\NIZKcrs_{\Sign} \gets
-\NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$, and $\NIZKcrs_{\Inspect} \gets
-\NIZKSetup^{\NIZKRel_{\Inspect}}(\NIZKsecpar)$. Return $(\Cparm,\SBCMparm,
-\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Inspect},
-\AttrSpace)$
+\NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$, and $\NIZKcrs_{\Open} \gets
+\NIZKSetup^{\NIZKRel_{\Open}}(\NIZKsecpar)$. Return $(\Cparm,\SBCMparm,
+\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Open},
+\AttrSpace)$. Note that many of these parameter setup algorithms can
+actually be run by separate entities (respecting some commonalities like,
+e.g., same pairing-friendly curves). For instance, each opener could
+run its own \ESetup algorithm, or each verifier its
+$\NIZKSetup^{\NIZKRel_{\Sign}}$, to advertise the signing evaluation functions
+it accepts. For simplicity of exposition, we bundle them together here.
 
@@
 \paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
-To generate its key pair, each inspector first parses \parm as $(\cdot,\cdot,
+To generate its key pair, each opener first parses \parm as $(\cdot,\cdot,
 \cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets \SKeyGen
@@
 e.g., from secure storage, given \cred), and attests attributes
-$\attrs_{\cred}$. For readability we write $\attrs_{\scred}$ as abbreviation for
-$\lbrace \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for
-$\sipk_{\scred}$. The user requests a signature on a commitment to the user key,
+$\attrs_{\cred}$. The user requests a signature on a commitment to the user key,
 as well as on the attributes in \attrs. In addition, the user proves that the
@@
 credentials in $\scred$
-and its user secret key. For this, we define relation $\NIZKRel_{\Issue} = \lbrace
-(\usk,\scred,\attrs_{\scred}), (\Ccom,\attrs,\sipk_{\scred}): \Ccom = \CCommit(usk) \land
-\fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in \scred,
-\SBCMVerify(\ipk_{\cred},\cred,
-\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1 \rbrace$. The interactive protocol
-for a user to obtain a credential from an issuer of the system is then simply an
-execution of the interactive signing protocol of an \SBCM scheme, where the user
-runs $\SBCMCom(\ipk,\usk,\attrs)$, and the issuer runs $\SBCMSign(\isk,\attrs)$;
-in both cases, using $\NIZKRel_{\Issue}$ as \NIZK relation.
+and its user secret key. For this, we use relation $\NIZKRel_{\Issue}$, as
+defined above. The interactive protocol for a user to obtain a credential from
+an issuer of the system is then simply an execution of the interactive signing
+protocol of an \SBCM scheme, where the user runs $\SBCMCom(\ipk,\usk,\attrs)$,
+and the issuer runs $\SBCMSign(\isk,\attrs)$; in both cases, using
+$\NIZKRel_{\Issue}$ as \NIZK relation. The credential \cred produced by the user
+is the result of the interactive signing protocol, and the \utrans entry for
+the issuer is its transcript which is a $(\Ccom,\attrs,\sipk,\cred,\pi)$ tuple.
 
@@
 \paragraph{$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
-In the signing algorithm, we make use of the following relation:
-$\NIZKRel_{\Sign} = \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r),(\msg,\feval,
-\yeval,\Ec,\sipk_{\scred},\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land \yeval =
-\feval(\usk,\scred,\msg) \land
-\yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
-\SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup \lbrace \usk \rbrace) = 1)
-\rbrace$ where, for each $\cred \in \scred$, $\attrs_{\cred}$ and $\ipk_{\cred}$,
-as well as $\attrs_{\scred}$ and $\sipk_{\scred}$ are as in $\langle \Obtain,
-\Issue \rangle$.
+In the signing algorithm, we make use of relation $\NIZKRel_{\Sign}$.
 % 
@@
 $\yeval \gets \feval (\usk,\scred,\msg)$, and decides whether or not to continue
-with the signing process -- this may depend, e.g., on the inspection policy of
+with the signing process -- this may depend, e.g., on the opening policy of
 \opk, as the output of \feval may influence whether the user will be
@@
 \paragraph{$(\yinsp,\NIZKproof)/\bot \gets
-  \Inspect(\osk,\sipk,\sig,\yeval,\msg,\feval)$.} %
-We first define NIZK relation $\NIZKRel_{\Inspect} = \lbrace (\osk),(\Ec,\yinsp)
-: \yinsp = \EDec(\osk,\Ec) \rbrace$.
+  \Open(\osk,\sipk,\sig,\yeval,\msg,\feval)$.} %
+Here we leverage relation $\NIZKRel_{\Open}$.
 %
-For inspection, the inspector first verifies the signature by running $\Verify(
-\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the verification succeeds, it parses
+To open a signature, the opener first verifies the signature by running $\Verify
+(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the verification succeeds, it parses
 \sig as $(\NIZKproof,\Ec)$, decrypts \Ec by running $\yeval \gets \EDec(\osk,
-\Ec)$, and computes $\NIZKproof_{\Inspect} \gets \NIZKProve^{\NIZKRel_{\Inspect}}
-(\NIZKcrs_{\Inspect},\osk,(\Ec,\yinsp))$. It returns $(\yinsp,
-\NIZKproof_{\Inspect})$.
+\Ec)$, and computes $\NIZKproof_{\Open} \gets \NIZKProve^{\NIZKRel_{\Open}}
+(\NIZKcrs_{\Open},\osk,(\Ec,\yinsp))$. It returns $(\yinsp,
+\NIZKproof_{\Open})$.
 
 \paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\sig,\yeval,\msg)$.} %
-To assess the validity of an inspection proof, first check the signature
+To assess the validity of an opening proof, first check the signature
 by running $\Verify(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the check succeeds,
 parse \sig as $((\cdot,\Ec),\cdot)$ and verify \NIZKproof with $\NIZKVerify
-(\NIZKcrs_{\Inspect},\NIZKproof,(\Ec,\yinsp))$. Accept it the NIZK verification
+(\NIZKcrs_{\Open},\NIZKproof,(\Ec,\yinsp))$. Accept it the NIZK verification
 passes, and reject otherwise.

### 2022-05-05 prism-backend/research/gsac/extensions-gsac.tex
Making a pass.

@@
 anonymous credential system with blacklisting, which can be directly built via
-the \Open function.
+the \Open function -- although at the cost of fully de-anonymizing blacklisted
+credentials, which is much more invasive than just blacklisting.
 

### 2022-05-05 prism-backend/research/gsac/model-gsac.tex
Making a pass.

@@
 \item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle \Obtain(\gpk,\usk,\Attrs),\Issue(\gpk,\isk,\Attrs) \rangle$.]
+  \langle \Obtain(\gpk,\usk,\attrs),\Issue(\gpk,\isk,\attrs) \rangle$.]
   This interactive protocol lets a user with key pair (\upk,\usk) running the
-  \Obtain process, obtain a credential \cred with attributes \Attrs, by
+  \Obtain process, obtain a credential \cred with attributes \attrs, by
   communicating with an issuer, with private key \isk, running the \Issue
@@
   outputs the protocol transcript \utrans for the produced credential.
-\item[$\sig \gets \Sign(\gpk,\usk,\cred,\DAttrs,\msg)$.] The user with
+\item[$\sig \gets \Sign(\gpk,\usk,\cred,\dattrs,\msg)$.] The user with
   with secret key \usk, who obtained a credential \cred, produces a signature
-  \sig over message \msg, revealing subset of attributes \DAttrs in \cred.
-\item[$1/0 \gets \Verify(\gpk,\sig,\DAttrs,\msg)$.] Checks whether \sig is a
-  valid signature revealing the attribute set \DAttrs of its signing credential,
+  \sig over message \msg, revealing subset of attributes \dattrs in \cred.
+\item[$1/0 \gets \Verify(\gpk,\sig,\dattrs,\msg)$.] Checks whether \sig is a
+  valid signature revealing the attribute set \dattrs of its signing credential,
   over message \msg.
 \item[$(\upk,\oproof)/\bot \gets
-  \Open(\gpk,\osk,\sig,\DAttrs,\msg)$.]
+  \Open(\gpk,\osk,\sig,\dattrs,\msg)$.]
   Given a signature \sig over message \msg, produced by a credential with
-  attributes containing the set \DAttrs, returns the public key \upk of the
+  attributes containing the set \dattrs, returns the public key \upk of the
   signer, and a proof of opening correctness \oproof; or $\bot$ if the
   opening process fails.
-\item[$1/0 \gets \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,
+\item[$1/0 \gets \Judge(\gpk,\upk,\oproof,\sig,\dattrs,
   \msg)$.] Checks if \oproof is a valid opening correctness proof stating that
   the user with key \upk generated signature \sig over message \msg, revealing
-  attributes $\DAttrs$. 
+  attributes $\dattrs$. 
 \end{description}
@@
 \figref{fig:exp-gsac-corr}. It states that a signature for some message \msg,
-revealing attributes \DAttrs, which was honestly produced through a credential
+revealing attributes \dattrs, which was honestly produced through a credential
 that was obtained by an honest user interacting with an honest issuer, with a
-set of attributes \Attrs such that $\DAttrs \subseteq \Attrs$, must be accepted
+set of attributes \attrs such that $\dattrs \subseteq \attrs$, must be accepted
 by \Verify. Moreover, an honestly produced correctness proof of opening for such
@@
      \gpk \gets (\ipk,\opk) \\
-    (\cid,\DAttrs,\msg) \gets \adv^{\HUGEN,\OBTISS,\RREG}(\gpk) \\
-    \pcif \DAttrs \nsubseteq \ATTR[\cid] :
+    (\cid,\dattrs,\msg) \gets \adv^{\HUGEN,\OBTISS,\RREG}(\gpk) \\
+    \pcif \dattrs \nsubseteq \ATTR[\cid] :
     \pcreturn \bot \\
-    \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\DAttrs,\msg) \\
-    (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\DAttrs,\msg) \\
-    \pcif \Verify(\gpk, \sig, \DAttrs,\msg) = 0 \lor
-    \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0: \\
+    \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\dattrs,\msg) \\
+    (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\dattrs,\msg) \\
+    \pcif \Verify(\gpk, \sig, \dattrs,\msg) = 0 \lor
+    \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 0: \\
      \pcind \pcreturn 1 \\
@@
 honest signatures, and open them. The adversary wins if, after this interaction,
-is able to produce a $(\sig,\DAttrs,\msg)$ tuple that is accepted by \Verify,
+is able to produce a $(\sig,\dattrs,\msg)$ tuple that is accepted by \Verify,
 but either cannot be opened, it can be opened but the proof is rejected by
 \Judge, or even though it is accepted by \Judge, there is no credential
-that contains the set of attributes \DAttrs. We formally define traceability in
+that contains the set of attributes \dattrs. We formally define traceability in
 the \ExpTrace experiment in \figref{fig:exp-gsac-trace}.
@@
     \gpk \gets (\ipk,\opk) \\
-    (\sig,\DAttrs,\msg) \gets
+    (\sig,\dattrs,\msg) \gets
     \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
-    \pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 0: \pcreturn 0 \\
-    \pcif \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) = \bot: \pcreturn 1 \\
-    \textrm{Let}~(\upk,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) \\
-    \pcif \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0: \pcreturn 1 \\
-    \pcelse \pcif \forall \uid \in \CU \cup \HU, \nexists (\uid,\cdot,\Attrs)
-    \in \CRED~\st~\DAttrs \subseteq \Attrs: \pcreturn 1 \\
+    \pcif \Verify(\gpk,\sig,\dattrs,\msg) = 0: \pcreturn 0 \\
+    \pcif \Open(\gpk,\osk,\trans,\sig,\dattrs,\msg) = \bot: \pcreturn 1 \\
+    \textrm{Let}~(\upk,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,\dattrs,\msg) \\
+    \pcif \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 0: \pcreturn 1 \\
+    \pcelse \pcif \forall \uid \in \CU \cup \HU, \nexists (\uid,\cdot,\attrs)
+    \in \CRED~\st~\dattrs \subseteq \attrs: \pcreturn 1 \\
     \pcreturn 0
@@
 In \GSAC schemes, in order for a user to be framed, the adversary first needs to
-create a $(\sig,\DAttrs,\msg,\upk,\oproof)$ tuple such that the signature,
+create a $(\sig,\dattrs,\msg,\upk,\oproof)$ tuple such that the signature,
 attributes, and message are accepted by \Verify, and which, along with the user
@@
      \gpk \gets (\ipk,\opk) \\
-     (\sig,\DAttrs,\msg,\upk,\oproof) \gets
+     (\sig,\dattrs,\msg,\upk,\oproof) \gets
      \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
      \textrm{Let}~\uid~\textrm{be st}~\PUBUK[\uid] = (\upk,\cdot) \\
-     \pcreturn 1~\pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 1 \land 
-     \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 1~\land \\
+     \pcreturn 1~\pcif \Verify(\gpk,\sig,\dattrs,\msg) = 1 \land 
+     \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 1~\land \\
      \pcind \uid \in \HU \land \sig \notin \SIG[\uid] \\

### 2022-05-05 prism-backend/research/gsac/model-uas.tex
Making a pass.

@@
 
-\comment{\textbf{DISCLAIMER}: I've done a major rewriting of most
-  properties. For now, please ignore the text until I have been able to sync
-  it.}
+We now define our model for Universal Anonymous Signatures. Property-wise, we
+maintain anonymity, non-frameability, and include two extra unforgeability
+properties: unforgeability of issuance, which ensures that issuance policies
+are not circumvented; and unforgeability of signatures, guaranteeing that
+signing policies are respected, as well as soundness of opening.
 
-We now define our model for Universal Anonymous Signatures. At a very high
-level, it is a combination of the main models for group signatures and
-anonymous credentials -- we try to extract the most useful features from both.
-Instead of considering just one group, as in group signatures, we directly and
-explicitly include support for multiple issuers as in anonymous credentials.
-Moreover, instead of letting each user own a single credential, we allow
-multiple credentials per user, even within the same group. This of course
-makes us put forward refined notions of anonymity, traceability and
-non-frameability. Note that, property-wise, we keep the three main properties
-from group signatures, rather than sticking to the two usual properties of
-anonymous credentials (anonymity and unforgeability). This is a consequence
-of keeping the inspection capability from group signatures, which we consider
-crucial in order to ensure some sort of accountability even in very adversarial
-contexts where the issuer may be corrupt.
-%
-But, as stated in the introduction, we go beyond just combining anonymous
-credentials and group signatures, and include support for arbitrary policies
-during issuance, signing, and inspection. Consequently, our model needs to
-capture the flexibility that these policies provide. In short, manipulations of
-the issuance policy are only considered forgeries if the adversary manages to
-create a valid signature using a credential that was obtained by dishonestly
-manipulating the issuance policy (we discuss this further in the traceability
-definition). Signing policies are taken into account both in the anonymity
-property, where we need to restrict that both credentials used to produce the
-challenge signatures always satisfy the policy, and in traceability.
-\commentwho{Jesus}{Think a bit more about the following claim, and update if
-  needed.}
-We cannot give any assurance on the signing policies when the issuers are
-corrupt, and thus they are not considered in the non-frameability property.
-Inspection policies are considered both in traceability and non-frameability,
-where the adversary wins if it manages to somehow alter the correct output of
-\Inspect. What is even suprising, is that given the possible non-injectivity of
-the inspection function lets us reach an even stronger notion of anonymity.
-Namely, \uline{we can allow the adversary to open challenge signatures, as
-  long as the inspection function outputs the same value for both}. We give more
-details on these aspects in the actual definitions of the security properties.
-%
-Finally, from a functional perspective, we require that both issuer and
-inspector fix the issuance predicate \fissue and inspection function \finsp when
-generating their public keys. Indeed, both will be part of the common group key.
-This also makes our definitions easier, as supporting multiple issuance
-predicate and inspection functions per group would require to consider many
-special cases -- and, anyway, that would probably end up being equivalent to
-just requiring that a new group needs to be created per each $(\fissue,\finsp)$
-pair. On the other hand, signing policies can be defined at signing time (in
-practice, most probably by the verifiers). This is in line with the usual
-practice in anonymous credentials, that let users prove arbitrary claims on
-their credentials, as long as they are met by the contained attributes.
+From a functional perspective, we require that each issuer and opener fix
+the issuance predicate \fissue and opener function \finsp when generating
+their public keys. On the other hand, signature evaluation functions \feval can
+be defined at signing time. This is in line with the usual practice in anonymous
+credentials, that let
+users prove arbitrary claims on their credentials, as long as they are met by
+the contained attributes. In practice, most probably, the signing policy to be
+employed in each signature will be defined by the verifier (or jointly between
+user and verifier), including the specification of which inspector will be
+able to post-process signatures\footnote{See, for instance, the concept of
+  presentation exchanges, or requests, in the context of Verifiable Credentials:
+  \url{https://identity.foundation/presentation-exchange/} (last access, May
+  5th, 2022).}. Beyond these general policies, which already give much
+flexibility, the syntax for \UAS supports multiple issuers and openers, and
+lets users leverage multiple credentials to request issuance of new ones, and
+to produce signatures.
 
-\subsubsection{Syntax}
-\label{sssec:syntax}
-
-An \UAS scheme is composed by the following algorithms.
-
-\todo{The notation for multisets is not strictly correct. Still, leaving it as
-  is for now.}
+\subsubsection{Syntax.} An \UAS scheme is composed by the following algorithms:
 
@@
 \item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
-  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
-  its inspecting key pair. The function \finsp defines the type of utility that
-  will be extractable from those pairs that do not meet conditions defined
-  at signing time (typically, by verifiers).
+  parameters \parm, and function \finsp, an opener runs \OKeyGen to generate
+  its opening key pair. The function \finsp defines the type of utility that
+  will be extractable from signatures.
 \item[$\usk \gets \UKeyGen(\parm)$.] Given global system parameters
@@
   the issuer outputs the protocol transcript \utrans for the produced
-  credential. To ease notation, we assume that the group to which each
-  credential belongs is available from the credential itself, and therefore
-  omit the $\ipk_i$ values from the syntax, unless necessary to avoid ambiguity.
+  credential. To ease notation, we assume that the issuer public key associated
+  to credential is available from the credential itself, and therefore
+  omit the $\ipk_i$ values from the syntax, unless necessary to avoid
+  ambiguity.
 \item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
   \rbrace_{i \in \Issuers},\msg,\feval)$.] %
-  Upon receiving a user secret key \usk, inspector public key \opk, a set of
+  Upon receiving a user secret key \usk, opener public key \opk, a set of
   credential-issuer pairs $(\cred_i,\ipk_i)$, a message \msg and evaluation
@@
   keys $\ipk_i$, for evaluation function \feval and inspector key \opk.
-\item[$(\yinsp,\iproof)/\bot \gets \Inspect(\osk,\lbrace \ipk_i
+\item[$(\yinsp,\iproof)/\bot \gets \Open(\osk,\lbrace \ipk_i
   \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
-  Executed by the inspector with private key \osk. Receives a signature $(\sig,
+  Executed by the opener with private key \osk. Receives a signature $(\sig,
   \yeval)$ over message \msg and evaluation function \feval, generated using
   credentials issued by the issuers with public keys $\ipk_i$. If \sig is valid,
-  the function outputs a value $\yinsp$ derived from the signer's public key,
-  credentials, message, and signature, as well as a proof of correct
-  inspection.
+  the function outputs a value $\yinsp$.
 \item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\yinsp,
   \iproof,\sig,\yeval,\msg,\feval)$.] %
-  Checks if \iproof is a valid inspection correctness proof for the value \yinsp,
-  obtained by applying \Inspect to the the signature $(\sig,\yeval)$ over
+  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
+  obtained by applying \Open to the the signature $(\sig,\yeval)$ over
   message \msg, and for evaluation function \feval. 
@@
 
-\paragraph{Issuance, evaluation, and inspection functions.} %
+\paragraph{Issuance, evaluation, and opening functions.} %
 We emphasize that, both in our syntax definition, as well as on the following
@@
 their computation. We introduce them next, \todo{and will give concrete examples
-  in \secref{sec:uac-instantiation}.}
-
-\todo{Do our definitions protect from absurd schemes that leak \usk or \scred via
-  \fissue or \feval (I guess \finsp is ok)? E.g., $\feval(\usk,\scred,\msg) =
-  \usk$ deanonymizes the signer. I guess that anonymity should prevent that.
-  But check.}
+  in \secref{sec:uas-instantiation}.}
 
 \begin{description}
-\item[$\fissue: (\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\attrs)
+\item[$\fissue: (\usk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\attrs)
   \rightarrow 0/1$.] Chosen by issuers within a family of functions \famfissue,
   the issuance function defines what customized conditions an issuer requires
-  in order to issue credentials, when receiving a request from user with public
-  key \upk, for attributes \attrs. \fissue may run checks on a (possibly empty)
-  set of additional credentials $\cred_i$, all bound to \upk, and possibly
+  in order to issue credentials, when receiving a request from user with secret
+  key \usk, for attributes \attrs. \fissue may run checks on a (possibly empty)
+  set of additional credentials $\cred_i$, all bound to \usk, and possibly
   issued by other issuers. \fissue returns $1$ to accept a request, $0$ to
   reject it.
-\item[$\feval: (\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\msg)
-  \rightarrow \yeval$.] Evaluation functions, from a family of functions
-  \famfeval, can be set on a per-signature basis. The evaluation function
-  defines customized conditions to be met by the owner of a user key \upk and
-  credentials $\cred_i$, bound to \upk, in order to sign a concrete message
-  \msg. Its outputs \yeval must belong in a well defined set \rngfeval.
-\item[$\finsp: (\yeval,\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
+\item[$\feval: (\usk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\msg)
+  \rightarrow \yeval$.] Signing evaluation functions, from a family of functions
+  \famfeval, can be set on a per-signature basis. They receive the user secret
+  key \usk, credentials $\cred_i$, and message to be signed \msg, and can be
+  used to control the information related to the signer that will be revealed
+  alongside a signature, and to modulate the behaviour of \finsp. Its outputs
+  \yeval must belong in a well defined set \rngfeval.
+\item[$\finsp: (\yeval,\usk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
   \msg) \rightarrow \yinsp$.]
-  Chosen by inspectors from a family of functions \famfinsp. The inspection
-  functions define what utility value, derived from the user's public key,
-  credentials, and signed message, should be extractable by an inspector.
+  Chosen by openers from a family of functions \famfinsp. The opening
+  functions define what utility value, derived from the user's secret key,
+  credentials, and signed message, should be extractable by an opener.
   Note that \finsp also receives as input a value in the range of the \feval
-  function, \rngfeval. This will allow inspection logic to depend on the value
+  function, \rngfeval. This allows opening logic to depend on the value
   produced by the evaluation function. The output of \finsp is a value
@@
 To see this, observe that \finsp is defined by inspectors, and will be fixed in
-all signatures ``inspectable'' by the inspector that defined it. On the other
-hand, \feval can be defined by (e.g.) verifiers and, as such, it can be changed
-on a per-signature basis, even if the signatures use the same \finsp. Thus,
-\feval can (and is intended to) be programmed to contain the conditions set by
-(e.g.) verifiers for signatures they receive; whereas \finsp can (and is intended
-to) be programmed to extract specific utility values when needed, which may
-depend on the checks required by the verifier a signature was intended to.
+all signatures that can be opened by the opener who defined it. On the other
+hand, \feval can be defined by (e.g.) verifiers on a per-signature basis, even
+if the signatures use the same \finsp. Thus, \feval can be programmed to contain
+the conditions set by (e.g.) verifiers for signatures they receive; whereas
+\finsp can be programmed to extract specific utility values when needed, which
+may depend on the checks required by the verifier a signature was intended to.
 
-\paragraph{Helper functions \ExtractIssue and \ExtractSign.} In our modelling,
-we assume the existence of three functions, \Identify, \ExtractIssue and
-\ExtractSign. They are not functions available in the actual scheme, but rather
-to the challenger, in the experiments we use to formalize security fof \UAS.
-Indeed, similar techniques have been used before to prove security in
+\paragraph{Helper functions \Identify, \ExtractIssue and \ExtractSign.} In our
+modelling, we assume the existence of three functions, \Identify, \ExtractIssue
+and \ExtractSign. They are not functions available in the actual scheme, but
+rather to the challenger in the experiments we use to formalize security fof
+\UAS. Indeed, similar techniques have been used before to prove security in
 privacy-preserving schemes with some sort of accountability, but that do not
@@
   issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
-  Otherwise, it returns $0$.
+  Otherwise, it returns $0$. In order to be meaningful, this requires that,
+  for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
+  \Identify return $1$.
 \item[$\ExtractIssue(\utrans) \rightarrow (\usk,\scred,\attrs_{\scred})$.]
@@
   issuer.
-\item[$\ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,\scred)$.]
-  Receives a signature pair $(\sig,\yeval)$, as well as the inspector identifier
-  \oid, and the identifiers of all issuers of the credentials used to produce the
-  signature over \msg, and for \feval. It outputs the user secret key
-  and credentials used to generate the signature.
+\item[$\ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,
+  \scred)$.] Receives a signature pair $(\sig,\yeval)$, as well as the opener
+  identifier \oid, and the identifiers of all issuers of the credentials used to
+  produce the signature over \msg, and for \feval. It outputs the user secret
+  key and credentials used to generate the signature.
 \end{description}
 
-Note that, both for the three functions, in the case of credentials,
-transcripts, and signatures by honest users, it is enough to have access to the
-corresponding state information (described below) maintained by the challenger
-in our experiments. For credentials and join transcripts of corrupt users, or
+Note that, for the three functions, in the case of credentials, transcripts,
+and signatures by honest users, it is enough to have access to the corresponding
+state information (described below) maintained by the challenger in our
+experiments. For credentials and join transcripts of corrupt users, or
 dishonestly produced signatures, we do need to perform actual extraction. How to
@@
 needs special knowledge/power such as decryption trapdoors, the ability to
-rewind the game, or program random oracles; the approach needs thus to depend on
-the concrete construction. Although, for the case of \ExtractIssue, online
-extractability (or alternative requirements, such as non-parallel or logarithmic
-number of joins) is necessary. %
-\todo{\needcite Paper from Camenisch and Shoup on the need
-  for online extractability?} \todo{How do we do this in our construction(s)?
-  Can we be more specific here? Also, this poses an interesting question: Is
-  extraction a requirement for this kind of schemes? Can we find alternative
-  definitions?}
+rewind the game, or program random oracles. The approach needs thus to depend on
+the concrete construction, although. Although, for the case of \ExtractIssue,
+online extractability \needcite (or alternative requirements, such as
+non-parallel or logarithmic number of joins) is necessary.
 
@@
 adversary. Users are referred to with user identifiers, \uid; for credentials,
-we use \cid; for groups, \gid. For credentials and groups, we use bold font to
-denote sets: i.e., \scid and \sgid denote sets of credential and group
-identifiers. All tables/sets are initialized as empty tables/sets, denoted
-with $\emptyset$.
+we use \cid; for issuers, \iid; and for openers, \oid. In all cases, we use bold
+font to denote sets: e.g., \scid and \siid denote sets of credential and issuer
+identifiers. All tables/sets are initialized as empty tables/sets.
 
@@
     i.e., they are sets of {\iid}s.
-  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) inspectors;
+  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) openers;
     i.e., they are sets of {\oid}s.
@@
     function; and \PRVIK refers to the private component of the key pair.
-  \item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for inspector key pairs. Instead
+  \item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
     of \fissue, \OK includes the \finsp function.
@@
     of honest users. Entries of this table are $(\oid,\scid,\sig,\yeval,\msg,
-    \feval)$, where \oid is the inspector chosen for the signature, \scid is the
-    set of credentials used for signing, \feval is the evaluation function, and
-    \sig and \msg are the produced signature and signed message.
+    \feval)$, where \oid is the opener chosen for the signature, \scid is the
+    set of credentials used for signing, \feval is the signing evaluation
+    function, and \sig and \msg are the produced signature and signed message.
   \item[\CSIG.] Maintains challenge signatures output to the adversary; i.e.,
@@
     corresponding challenge user and credential set indexed by the complementary
-    $1-b$; the signed message \msg and evaluation function \feval, the result of
-    \feval, \yeval, and the inspector identifier \oid.
+    $1-b$; the signed message \msg and signing evaluation function \feval, the
+    result of \feval, \yeval, and the opener identifier \oid.
   \end{description}
@@
   to honest users.
-\item[\OPEN.] Given an honestly produced signature, lets the adversary learn
-  which credential was used to produce it.
-\item[\CHALb.] Upon receiving two challenge credentials, a common intersecting
-  set of attributes, and a message, returns a signature produced by one of these
-  two credentials, defined by the bit $b$, which is established in the anonymity
-  game.
+\item[\OPEN.] Given an honestly produced signature, outputs the result of the
+  opening function, along with a correctness proof.
+\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
+  singing evaluation function and a message, returns a signature produced by one
+  of these two user and credential sets, defined by the bit $b$, which is
+  established in the anonymity game.
 \end{description}
@@
 
-        \procedure{$\INSPECT(\oid,\sig,\yeval,\msg)$}{%
+        \procedure{$\OPEN(\oid,\sig,\yeval,\msg)$}{%
           \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\sig,\yeval,\msg,\feval)
@@
 which issued each credential. Similarly, the output \yeval of \feval matches the
-value produced by \Sign alognside with \sig; and the value produced by \Inspect
+value produced by \Sign alongside with \sig; and the value produced by \Open
 is accepted by \Judge, and matches the output of applying \finsp on \yeval, the
@@
   \label{def:correctness-uas}
-  An \UAS scheme is correct if, for any p.p.t. adversary $\adv$, \ExpCorrect
-   outputs 1 with negligible probability.
+  An \UAS scheme is correct if, for any p.p.t. adversary $\adv$,
+  $\ExpCorrect(1^\secpar)$ outputs 1 with negligible probability.
 \end{definition}
@@
   }  
-
   \caption{Correctness experiment for \UAS schemes.}
@@
 In order to prevent trivial wins by the adversary, we have to restrict that the
-evaluation function outputs the same value for both user-credentials pairs. Very
-interestingly, since our inspection functionality does not (necessarily) output
-the identity of the signer, \uline{we can even allow the adversary to
-  inspect challenge signatures, as long as they produce the same output upon
-  inspection}. Other than this, the overall approach is similar: as in group
-signatures and anonymous credentials, the adversary picks two pairs of honest
-users and credential sets. We also require the adversary to pick an evaluation
-function and an inspector (hence, an inspection function). Then, the
+signing evaluation function outputs the same value for both user-credentials
+pairs. Very interestingly, since our opening functionality does not
+(necessarily) output the identity of the signer, \uline{we can even allow the
+  adversary to open challenge signatures, as long as they produce the same
+  output}. Other than this, the overall approach is similar: as
+in group signatures and anonymous credentials, the adversary picks two pairs of
+honest users and credential sets. We also require the adversary to pick an
+evaluation function and an opener (hence, an opening function). Then, the
 user-credential pair defind by the value of $b$ (unknown to the adversary) is
@@
 \CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,
-\WREG,\SIGN,\INSPECT)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,
-\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\INSPECT,\CHALb)$
+\WREG,\SIGN,\OPEN)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,
+\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$
 
@@
 This notion of anonymity is more general than that of group signatures in the
-sense that calls to the \INSPECT oracle reveal an arbitrary function of the
+sense that calls to the \OPEN oracle reveal an arbitrary function of the
 identity of the user -- which can certainly be the member index itself, as it
 is frequent in group signatures, or any other function computable from the
-user public key, its credentials, and produced signature. Moreover, note that
+user key, its credentials, and signed message. Moreover, note that
 our notion is even stronger than the conventional ``CCA-like'' anonymity notion
@@
 trying to open challenge signature. Precisely the introduction of generic
-inspection functions allows us to \uline{\emph{let the adversary open
-    challenge signatures $\csig_b$}} as long as the counterpart $\csig_{1-b}$
-makes \Inspect produce the same \y value as output. This is certainly not
+opening functions allows us to let the adversary open challenge signatures
+$\csig_b$ as long as the counterpart $\csig_{1-b}$
+makes \Open produce the same \y value as output. This is certainly not
 possible when using conventional opening, since it directly outputs the identity
@@
 
-\todo{Mention (probably, in future work?) that since the public keys of the
-  credential issuers are assumed to be public, we must enforce that challenge
-  users with same issuers per credential are used in the challenge oracle. This
-  is to avoid trivial wins. But not sure if the naive extension of hiding also
-  the issuers would make sense in the real world (which issuers are trusted?)}
-
 \paragraph{Unforgeability.} In anonymous credentials, unforgeability requires
@@
 honest issuers, is traceability. It captures the security of the
-inspection-related functionality (e.g., \Inspect and \Judge) over signatures
+open-related functionality (e.g., \Open and \Judge) over signatures
 that produced by potentially malicious signers, in the presence of an honest
@@
 the verification algorithm must have been created by a user who joined the
-group, and that the result of \Inspect (and thus, \Judge) over such a valid
+group, and that the result of \Open (and thus, \Judge) over such a valid
 signature is consistent with its signer. With conventional opening, this is
@@
 
-In \UAS schemes, users can prove claims over the attributes they own
--- attested via obtained credentials -- through the \feval function. Thus, we
-need to capture the same unforgeability requirement as in anonymous credentials.
-Namely, that the \yeval value returned by \Sign along with the signature,
-matches the expected one from the specified \feval function.
-On the other hand, the inspection capabilities of \UAS schemes also call for a
+In our \UAS scheme we need to allow users prove claims over the attributes they
+own -- attested via obtained credentials -- through the \feval function.
+Roughly, we capture this roughly as in unforgeability requirement of anonymous
+credentials. Namely, that the \yeval value returned by \Sign along with the
+signature, matches the expected one from the specified \feval function.
+On the other hand, the opening capabilities of \UAS schemes also call for a
 traceability-like property. However, note that, as opposed to group signatures,
@@
 users -- although, ultimately, credentials must be owned by some user.
-However, we need to ensure that all signatures have been produced by credentials
-that have been obtained from an (honest) issuer. Furthermore, since \Inspect
+Furthermore, since \Open
 does not return the actual identity of the signer, but a function \finsp of it
-(and other arguments), we need to make sure that the output of \Inspect
+(and other arguments), we need to make sure that the output of \Open
 matches the output of \finsp. As in group signatures with non-conventional open,
@@
 produce a signature $(\sig,\yeval)$ over message \msg and for evaluation
-function \feval; as well as the identifiers for the inspector (\oid) and
+function \feval; as well as the identifiers for the opener (\oid) and
 credential issuers (\siid) used to compute the signature. As in traditional
 group signatures, the adversary wins if the signature is accepted by \Verify,
-yet \Inspect or \Judge fail. Then, the game extracts the user key and
+yet \Open or \Judge fail. Then, the game extracts the user key and
 credentials used to produce the signature. From it, the game checks if the
-output of \feval matches the \yeval value produced by the adversry -- this
+output of \feval matches the \yeval value produced by the adversary -- this
 mimics the behaviour of unforgeability in anonymous credentials. Finally, the
-game also checks that the output of \Inspect (even if accepted by \Judge)
+game also checks that the output of \Open (even if accepted by \Judge)
 matches the output of \finsp. If there is any mismatch in the last two checks,
-the adversary wins the game.
+or some of the credentials used to produce the signature do not correspond to
+the secret key that was allegedly used to request them, the adversary wins the
+game.
 
-\UAS schemes include yet another generalisation that requires unforgeability-like
-security, though. Concretely, the issuance function \fissue. Thus, an \UAS
-scheme needs to make sure that no credential is issued unless its corresponding
+Our \UAS scheme includes yet another generalisation that requires unforgeability-like
+security, though. Concretely, the issuance function \fissue. We need to make
+sure that no credential is issued unless its corresponding
 request meets the defined issuance policy. From the point of view of group
 signatures, this may seem redundant. After all, if all valid signatures produce
-consistent evaluation and inspection results, given the employed user key,
+consistent evaluation and opening results, given the employed user key,
 credentials, and signed message, the notion of traceability seems to be
 satisfied. However, from the point of view of anonymous credentials, an attacker
-being able to obtain a credential, even though it does not meet the required
+being able to obtain a credential, even when it does not meet the required
 conditions to have it issued, is clearly problematic: it would allow to prove
 claims over attributes it does not really ``own'' (even if the output of \Sign
-and \Inspect are consistent with the values returned by \feval and \finsp, and
-the credential was obtained via an $\langle \Obtain,\Issue \rangle$). To capture
-this, we define the \ExpForgeIssue experiment. In the experiment, the adversary
-is challenged to produce a credential identifier that must be associated to an
-existing $\langle \Obtain,\Issue \rangle$ interaction -- thus, the corresponding
-\trans entry must exist (which we can check, as the issuer is honest).
-The adversary wins if, either the extraction process fails, or the extracted
-user secret key and credentials make the corresponding issuance function fail.
+and \Open are consistent with the values returned by \feval and \finsp, and
+the credential was obtained via an $\langle \Obtain,\Issue \rangle$ run). To
+capturethis, we define the \ExpForgeIssue experiment. In the experiment, the
+adversary is challenged to produce a credential identifier that must be
+associated to an existing $\langle \Obtain,\Issue \rangle$ interaction -- thus,
+the corresponding \trans entry must exist (which we can check, as the issuer is
+honest). The adversary wins if, either the extraction process fails, or the
+extracted user secret key and credentials make the corresponding issuance
+function fail.
 
@@
 oracle set $\Oforgeissue = \Oforgesign \gets \lbrace\HU,\CU\rbrace\GEN,\IGEN,
-\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\INSPECT$.
+\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.
 
@@
 \paragraph{Discussion on the generality of unforgeability in \UAS schemes.} %
-\todo{Re-check and re-write as needed}.
-The notion of traceability we present for \UAS is strictly more general than
-the corresponding one for group signatures. This is again a direct
-consequence of the fact that \Inspect, which can return an arbitrary function
-of the signer's credential (and signed message), is a generalization of the
-conventional \Open -- if we make \Inspect return just the identity of the
-signer, then we get something similar to the usual notion of traceability.
-Although, even in that case, we need to take into account attributes, and the
-fact that the same user may obtain multiple credentials (that is why, even when
-having \Inspect return the identity of the signer, our notion is not exactly
-the same). And, in this sense, the unforgeability notion that \UAS have is
-equivalent to that of anonymous credentials. It would seem, though, that we do
-not need the traceability part of group signatures; after all, it is the
-protection against wrong claims on attributes what enables meaningful and
-flexible authentication. However, the type of protection against misuses of
-the inspection functionality that we can get with an honest issuer (as in
-traceability) is much higher than without an honest user (as in
-non-frameability). Specifically, with an honest issuer we can ensure that
-the adversary cannot even alter the value returned by \Inspect on signatures
-by corrupt users, nor the output of the signing predicate \feval. Whereas, with
-a corrupt issuer, all we can ensure is that
-the adversary cannot forge a signature from an honest user for which \Inspect
+The notion of signature unforgeability we present for \UAS is strictly more
+general than the corresponding one of traceability for group signatures. This is
+again a direct consequence of the fact that \Open can return an arbitrary
+function of the signer's key and credentials (and signed message), whic is a
+strict generalization of the conventional \Open. Although, even in that case, we
+need to take into account attributes, and the fact that the same user may obtain
+multiple credentials (that is why, even when having \Open return the identity of
+the signer, our notion is not exactly the same). In this sense, the sign
+unforgeability notion for \UAS is equivalent to that of anonymous
+credentials. It would seem, though, that we do not need the traceability part of
+group signatures; after all, it is the protection against wrong claims on
+attributes what enables meaningful and flexible authentication. However, the
+type of protection against misuses of the open functionality that we can
+get with an honest issuer (as in traceability) is much higher than without an
+honest issuer (as in non-frameability). Specifically, with an honest issuer we
+can ensure that the adversary cannot even alter the value returned by \Open on
+signatures by corrupt users, nor the output of the signing predicate \feval.
+Whereas, with a corrupt issuer, all we can ensure is that
+the adversary cannot forge a signature from an honest user for which \Open
 returns the same value as a signature by that honest user would produce; and,
 certainly, a corrupt issuer can arbitrarily issue credentials meeting any
-desired predicate \feval .Traceability is, therefore, a core property to ensure
-accountability.
+desired predicate \feval. Signing unforgeability is, therefore, a core property
+to ensure accountability.
 
-Note also that we have implicitly assumed an unforgeability relaxation in the
-sense that we do not consider a forgery the fact that an adversary can obtain
-credentials that do not meet the \fissue predicate \emph{as long as they are
-  not used to produced untraceable signatures}. Indeed, this is in line with
-previous work \cite[Section 3.3.3]{ckl+15}, and it does make sense as, in the
-real world, being able to fraudulently obtain credentials that cannot be later
-used to authenticate, does not pose a risk. However, an adversary breaking
-the issue policy defined by \fissue to get a credential and later using it to
-create a valid signature (i.e., meeting \feval or \finsp) is considered a
-forgery by our definition.
+Similarly, by adding the related notion of issuance unforgeability, we ensure
+that no credential can be issued that did not meet the corresponding issuance
+policy. This is again something not necessary in group signatures (with
+verifiable openings), where \Judge accepting the opening proof implies that
+there is a valid join transcript associated to the membership credential used
+to produce the signature. However, in \UAS, even though that transcript exists,
+we need to make sure that the issuance policy was satisfied -- and this is not
+something (easily) extractable from the signature.
 
@@
 that can be (even in some generic sense) associated to an honest user who did
-not produce it. Depending on the inspection capabilities of the scheme,
+not produce it. Depending on the opening capabilities of the scheme,
 this framing could be done in different ways; i.e., by convincing third parties
 that signatures by different (possibly corrupt) users are linked, or directly
-by having inspection proofs output the identity of a user who did not create the
-signature being inspected.
+by having opening proofs output the identity of a user who did not create the
+signature being opened.
 
@@
 in group signatures, though. To see this, we note that, by allowing arbitrary
-evaluation and inspection functions to be used, it can be perfectly valid to
+evaluation and open functions to be used, it can be perfectly valid to
 have a signature produced by a corrupted user output the same \yeval or \yinsp
-values than the one that \feval or \finsp output when evaluating or inspecting
-a signature by an honest user. As a concrete example, imagine an inspection
-function that returns the banking account number (or cryptocurrency address) to
-be used to request payment of a fine. In this example, a corrupted user and an
-honest user could both have delegated this to some agency\footnote{\todo{Maybe,
-    come up with a better example. How about spam filters that apply some sort
-    of classification engine? \finsp could be this engine, and emails by many
-    different users could be classified just as ``Spam'' or ``Not spam''}}, so
-it makes perfect sense that the inspection function returns the same value for
-both users.
+values than the ones output when evaluating or opening a signature by an honest
+user. As a concrete example, imagine an open function that returns the
+nationality of the signer. In any country, there will be many users (corrupt or
+not) sharing nationality.
 %
 More generally, since the issuer is dishonest in non-frameability properties
-and, in \UAS, the value produced by \Inspect may depend on the attributes
+and, in \UAS, the value produced by \Open may depend on the attributes
 included in user credentials, the adversary may even be able to just produce
-``legitimate'' inspections that output any desired value.
+``legitimate'' openings that output any desired value.
 
@@
 \figref{fig:exp-uas-frame}, the adversary is challenged to produce a signature
-and inspection proof that accepted by \Verify and \Judge, respectively. From
+and opening proof that is accepted by \Verify and \Judge, respectively. From
 the signature, we then extract the secret key of the signer, and match it
 against the secret keys of the honest users. The adversary wins if there is a
-match (and the signature, of course, has not been queried to \SIGN). In the
-game, the adversary has access to the oracles in 
-$\Oframe \gets \lbrace\HU,\CU\rbrace\GEN,
-\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG,\OBTAIN,\SIGN$
+match and the signature has not been queried to \SIGN. In the game, the
+adversary has access to the oracles in $\Oframe \gets \lbrace\HU,\CU\rbrace\GEN,
+\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG,\OBTAIN,\SIGN$.
 
@@
 \paragraph{Discussion on the generality of non-frameability in \UAS schemes.} %
-\todo{Re-check and re-write as needed}.
 Anonymous credentials do not have non-frameability property and, thus, it is
@@
 basic revocation (without straight deanonymization) can be trivially achieved
-through our generic \Inspect function. For instance, one could set \finsp to
+through our generic \Open function. For instance, one could set \finsp to
 be a pseudorandom number seeded with the user's public key (or credential). In
-this sense, \Inspect could be essentially seen as a Verifiable Random Function.
-If we compare with group signatures, our notion is again more general than the
-conventional one. Indeed, in typical group signatures, \Open returns the
-identity of the signer, and thus non-frameability does not allow the same value
-to be returned when opening signatures by different users. Otherwise, a
-corrupted user controlled by the adversary could be able to create a signature
-opening to some honest user (hence, framing him). But this is again possible
-with our definition which, in case of making \Inspect equal \Open, becomes
-equivalent to conventional non-frameability. However, it also allows more
-generic situations in which signatures by different users may return the same
-value.
+this sense, \Open could be essentially seen as a Verifiable Random Function.
+If we compare with group signatures, our notion is also more general than the
+conventional one, again for the same reason as sign unforgeability (i.e., \Open
+can return any value, not just the signer's identity). Thus, the need to extract
+the signer's data in order to detect if a framing has taken place.
 

### 2022-05-05 prism-backend/research/gsac/sec-gsac.tex
Making a pass.

@@
 
-\todo{I think we should extend ``vanilla'' \GSAC to return the full \Attrs
+\todo{I think we should extend ``vanilla'' \GSAC to return the full \attrs
   in \Open, but without needing \trans as a parameter to \Open (for compatibility

### 2022-05-05 prism-backend/research/gsac/sec-uas.tex
Making a pass.

@@
 offers. The most excruciating example of this fact is that in \GSAC, via \Open,
-one can only get the actual identity of the signer. Even though with the inclusion
-of attributes the concept of ``identity'' can now be meaningfully defined, we
+one can only get the actual identity of the signer. Even though the inclusion
+of attributes makes the concept of ``identity'' meaningful, we
 may not want to fully de-anonymize the signer. Instead, we may be interested in
@@
 credential attributes; and, as it is also common in the anonymous credentials
-(or verifiable credentials \needcite) domains, to allow credential holders to
+(or verifiable credentials\footnote{\url{https://www.w3.org/TR/vc-data-model/}.
+  Last access, May 5th, 2022.}) domains, to allow credential holders to
 combine multiple credentials into one signature/presentation. Similarly, we can
@@
   passing through any intermediate de-anonymization function, like revealing
-  the nationality of the signer, or its banking account number, even if this
-  was not revealed at the signing stage.
+  concrete attributes, or functions of them.
 \end{itemize}

### 2022-05-06 prism-backend/research/gsac/model-uas.tex
Fixed error in unfor-sign property and proof.

@@
 
-\paragraph{Helper functions \Identify, \ExtractIssue and \ExtractSign.} In our
-modelling, we assume the existence of three functions, \Identify, \ExtractIssue
-and \ExtractSign. They are not functions available in the actual scheme, but
-rather to the challenger in the experiments we use to formalize security fof
-\UAS. Indeed, similar techniques have been used before to prove security in
-privacy-preserving schemes with some sort of accountability, but that do not
-offer conventional opening as vanilla group signatures. For instance, see
-related works on DAA \cite{bfg+11,cdl16} and group signature variants
-\cite{dl21,fgl21,gl19,lnpy21}. More concretely, both functions are as follows:
+\paragraph{Helper functions \ExtractIssue, \ExtractSign, \IdentifyCred, and
+  \IdentifyUK.} In our modelling, we assume the existence of four functions,
+\ExtractIssue, \ExtractSign, \IdentifyCred, and \IdentifyUK. They are not
+functions available in the actual scheme, but rather to the challenger in the
+experiments we use to formalize security of \UAS schemes. Similar techniques
+have been used before to prove security in privacy-preserving schemes with some
+sort of accountability, but that do not offer conventional opening as vanilla
+group signatures. For instance, see related works on DAA \cite{bfg+11,cdl16} and
+group signature variants \cite{dl21,fgl21,gl19,lnpy21}. More concretely, these
+functions are as follows:
 
 \begin{description}
-\item[$\Identify(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
+\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
+  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
+  credentials (if any) and their attributes that were involved
+  in the request. It clearly needs an honest issuer as, otherwise, the
+  transcripts won't be available. Consequently, we only use it to define the
+  properties that require an honest issuer.
+\item[$\ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,
+  \scred,\attrs_{\scred},\yinsp)$.] Receives a signature pair $(\sig,\yeval)$,
+  as well as the opener identifier \oid, and the identifiers of all issuers of
+  the credentials used to produce the signature over \msg, and for \feval. It
+  outputs the user secret key and credentials (with their attributes) used to
+  generate the signature, and the value returned by the opening fuction.
+\item[$\IdentifyCred(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
   issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
@@
   for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
-  \Identify return $1$.
-\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\scred,\attrs_{\scred})$.]
-  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
-  credentials (if any), their attributes, and the user secret key used during
-  the execution of the $\langle\Obtain,\Issue\rangle$ protocol. It clearly needs
-  an honest issuer as, otherwise, the transcripts won't be available.
-  Consequently, we only use it to define the properties that require an honest
-  issuer.
-\item[$\ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,
-  \scred)$.] Receives a signature pair $(\sig,\yeval)$, as well as the opener
-  identifier \oid, and the identifiers of all issuers of the credentials used to
-  produce the signature over \msg, and for \feval. It outputs the user secret
-  key and credentials used to generate the signature.
+  \IdentifyCred return $1$.
+\item[$\IdentifyUK(\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret key.
+  This is trivial for honest users, for which this must be a one-to-one
+  relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
+  to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
+  to \uid, extract the used secret key, and check if there is a match. Note that
+  this does not guarantee that there will be only one \usk per corrupt \uid,
+  though. Also, when used for corrupt users, this can only be used when the
+  issuer is honest.  
 \end{description}
 
-Note that, for the three functions, in the case of credentials, transcripts,
+Note that, for all the helper functions, in the case of credentials, transcripts,
 and signatures by honest users, it is enough to have access to the corresponding
@@
 rewind the game, or program random oracles. The approach needs thus to depend on
-the concrete construction, although. Although, for the case of \ExtractIssue,
+the concrete construction. \todo{Although, for the case of \ExtractIssue,
 online extractability \needcite (or alternative requirements, such as
-non-parallel or logarithmic number of joins) is necessary.
+non-parallel or logarithmic number of joins) is necessary.}
 
@@
           \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
-          (\upk,\usk) \gets \UKeyGen(\parm) \\
-          \UK[\uid] \gets (\upk,\usk);
+          \usk \gets \UKeyGen(\parm) \\
+          \UK[\uid] \gets \usk;
           \HU \gets \HU \cup \lbrace  \uid \rbrace \\
@@
 
-        \procedure{$\CUGEN(\uid,\upk)$}{%          
+        \procedure{$\CUGEN(\uid)$}{%          
           \pcif \uid \in \CU: \pcreturn \bot \\
@@
           \pcind \pcreturn (\UK[\uid],\CRED[\uid]) \\
-          \pcelse: \UK[\uid] = (\upk,\bot) \\          
+          \pcelse: \UK[\uid] = \bot \\          
           \pcreturn \top \\
@@
           \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\PRVUK[\uid],\CRED[\scid],\attrs),\adv \rangle \\
+          \langle \Obtain(\UK[\uid],\CRED[\scid],\attrs),\adv \rangle \\
           \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
@@
           \pcif \oid \in \CO: \pcreturn \bot \\
-          \pcif \yeval = \feval(\PUBUK[\cuid_0],\CRED[\cscid_0],\msg) \neq \\
-          \pcind \feval(\PUBUK[\cuid_1],\CRED[\cscid_1],\msg):
+          \pcif \yeval = \feval(\UK[\cuid_0],\CRED[\cscid_0],\msg) \neq \\
+          \pcind \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg):
           \pcreturn \bot \\
           \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
-          (\yeval,\csig_b) \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid], \\
+          (\yeval,\csig_b) \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
           \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
-          (\yeval,\csig_{1-b}) \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid], \\
+          (\yeval,\csig_{1-b}) \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
           \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
@@
           \langle \cred, \utrans \rangle \gets
-          \langle \Obtain(\PRVUK[\uid],\CRED[\scid],\attrs), \\
+          \langle \Obtain(\UK[\uid],\CRED[\scid],\attrs), \\
           \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\scid],\attrs)
@@
           \pcif \uid \notin \HU: \pcreturn \bot \\
-          (\sig,\yeval) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,
+          (\sig,\yeval) \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,
           \feval) \\
@@
     \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
-    (\sig,\yeval) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
+    (\sig,\yeval) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
     \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = 0: \pcreturn 1 \\
@@
     ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,\fissue^{\cid}),\cdot)\\
-    \pcind \pcif \fissue^{\cid}(\PUBUK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
+    \pcind \pcif \fissue^{\cid}(\UK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
     \pcif \feval(\UK[\uid],\CRED[\scid],\msg) \neq \yeval: \pcreturn 1 \\
@@
       \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
-      \exists \cred \in \scred~\st~\Identify(\usk,\attrs_{\cred},\cred) = 0: \\
+      \exists \cred \in \scred~\st~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0: \\
       \pcind \pcreturn 1 \\
+%      \pcif \nexists \uid~\st~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
       \pcreturn 0
@@
       \pcreturn 1 \\
-      \pcif \exists \cred \in \scred~\st~\Identify(\usk,\attrs_{\cred},\cred) = 0:
+      \pcif \exists \cred \in \scred~\st~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
       \pcreturn 1 \\
+      \pcif \nexists \uid~\st~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
       \pcreturn 0
@@
     \ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \\
-    \pcif \exists \uid \in \HU~\st~\PRVUK[\uid] = \usk: \pcreturn 1 \\
+    \pcif \exists \uid \in \HU~\st~\UK[\uid] = \usk: \pcreturn 1 \\
     \pcreturn 0

### 2022-05-06 prism-backend/research/gsac/security-uas.tex
Making a pass.
Fixed error in unfor-sign property and proof.

@@
 
-First, we define the \Identify, \ExtractIssue and \ExtractSign functions that
-are needed for some of the properties to be meaningful, in
+First, we define the \ExtractIssue, \ExtractSign, \IdentifyCred and \IdentifyUK
+functions that are needed for some of the properties to be meaningful, in
 \figref{fig:helper-funcs}.
@@
   \begin{minipage}[t]{\textwidth}
-    \procedure{$\ExtractIssue(\parm,\trans)$}{%
+    \procedure{$\ExtractIssue(\parm,\utrans)$}{%
       \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Issue},\cdot,
         \cdot,\cdot)$; $\NIZKcrs_{\Issue}$ as $(\NIZKcrs,\NIZKtrap)$; and
-        \trans as $(\Ccom,\attrs,\sipk,\cred,\NIZKproof)$} \\
+        \utrans as $(\Ccom,\sipk,\cred,\NIZKproof)$} \\
       \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\Ccom,\attrs,\sipk)): 
@@
       (\Ccom,\attrs,\sipk),\NIZKproof) \\
-      \pcreturn (\usk,\scred,\attrs_{\scred}) \\
+      \pcreturn (\usk,\attrs,\scred,\attrs_{\scred}) \\
     }
@@
       \sipk,\opk)): \pcreturn \bot \\
-      (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets \NIZKExtract(\NIZKcrs,\NIZKtrap,
-      (\msg,\feval,\yeval,\Ec,\sipk,\opk),\NIZKproof) \\
+      (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets \NIZKExtract(\NIZKcrs,
+      \NIZKtrap, (\msg,\feval,\yeval,\Ec,\sipk,\opk),\NIZKproof) \\
       \pcreturn (\usk,\scred,\attrs_{\scred},\yinsp) \\
@@
 
-    \procedure{$\Identify(\usk,\attrs_{\cred},\cred)$}{%
-      \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup
-      \lbrace \usk \rbrace) \\
+    \procedure{$\IdentifyCred(\usk,\attrs_{\cred},\cred)$}{%
+      \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
+    }
+
+    \procedure{$\IdentifyUK(\uid,\usk)$}{%
+      \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
+      \pcfor \cid~\st~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
+      \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trans[\cid]) \\
+      \pcind \pcif \usk = \usk': \pcreturn 1 \\
+      \pcreturn 0
     }
@@
   \label{fig:helper-funcs}
-  \caption{Definition of helper functions \Identify, \ExtractIssue and
-    \ExtractSign, for \CUASGen.}
+  \caption{Definition of helper functions \ExtractIssue, \ExtractSign,
+    \IdentifyCred, and \IdentifyUK, for \CUASGen.}
 \end{figure}
@@
   \label{thm:anonymity-uas}
-  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge and
-  simulation-extractable, our \CUASGen construction satisfies anonymity as
-  defined in \defref{def:anonymity-uas}.
+  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge, our
+  \CUASGen construction satisfies anonymity as defined in
+  \defref{def:anonymity-uas}.
 \end{theorem}
@@
   as $G_0$, except that, within the $\Setup$ algorithm, we replace
-  $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. By simulation
-  extractability, $G_1$ is indistinguishable from $G_0$.
+  $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. By zero-knowledgeness,
+  $G_1$ is indistinguishable from $G_0$.
 
@@
   zero-knowledge of $\NIZK^{\Sign}$, $G_2^1$ is indistinguishable from $G_1^1$.
-  Note also that $G_2^1=G_2^0$, as in the challenge oracle, used in the
+  Note also that $G_2^1=G_2^0$ as, in the challenge oracle used in the
   anonymity game, we restrict to $\PUBIK[\scid_0] = \PUBIK[\scid_1]$.
@@
   \label{thm:issue-forge-uas}
-  If the underlying scheme for signatures on blocks of committed messages is
-  existentially unforgeable, and the NIZK used for $\NIZKRel_{\Issue}$ is
-  simulation extractable and sound, then our \CUASGen construction satisfies
-  issuance unforgeability as defined in \defref{def:issue-forge-uas}, except
-  with negligible probability.
+  If the underlying NIZK used for $\NIZKRel_{\Issue}$ is simulation extractable
+  and sound, then our \CUASGen construction satisfies issuance unforgeability as
+  defined in \defref{def:issue-forge-uas}, except with negligible probability.
 \end{theorem}
-
-\todo{\usk belongs to \AttrSpace! I think this can lead to malleability attacks.
-  Make them disjoint?}
 
@@
   %
-  Since \NIZKproof is accepted by \ExtractIssue, from the soundness of \NIZK and
-  existential unforgeability of \SBCM, we know that all $\cred \in \scred$ are
-  valid signatures over \usk, and their respective $\attrs_{\cred}$. Thus,
-  \Identify returns $1$ for all $(\usk,\attrs_{\cred},\cred)$ tuples.
-  Moreover, all the credentials in \scred given to \fissue belong to the same
-  user, who is the owner of \usk.
+  Since \NIZKproof is accepted by \ExtractIssue, from the soundness of \NIZK, we
+  know that all $\cred \in \scred$ are valid signatures over \usk, and their
+  respective $\attrs_{\cred}$. Thus, \IdentifyCred returns $1$ for all $(\usk,
+  \attrs_{\cred},\cred)$ tuples. That is, all the credentials in \scred given
+  to \fissue belong to the same user, who is the owner of \usk.
   %
@@
   \label{thm:sign-forge-uas}
-  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is sound and simulation
-  extractable, the NIZK scheme for $\NIZKRel_{\Inspect}$ is sound and simulation
-  extractable, and \SBCM is existentially unforgeable, then our \CUASGen
-  construction satisfies signing unforgeability as defined in
+  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is zero-knowledge, sound,
+  and simulation extractable, the NIZK scheme for $\NIZKRel_{\Inspect}$ is sound
+  and simulation extractable, and \SBCM is one-more unforgeable, then our
+  \CUASGen construction satisfies signing unforgeability as defined in
   \defref{def:sign-forge-uas}, except with negligible probability.
@@
   As for \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
-  and $G_1$, which is exactly the same, but where, within the \Setup algorithm,
-  we replace $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. As per the
-  definition of \NIZK in \appref{sapp:nizk}, both games are indistinguishable.
+  and $G_1$, which is exactly the same but where, within the \Setup algorithm,
+  we replace $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. After
+  zero-knowledgeness of $\NIZK^{\Sign}$, both games are indistinguishable.
 
@@
     \NIZKLang^{\Sign}$.    
-  \item[$I$.] Where $I = \exists \cred \in \scred~\st~\Identify(\usk,
+  \item[$I$.] Where $I = \exists \cred \in \scred~\st~\IdentifyCred(\usk,
     \attrs_{\cred},\msg) = 0$.
@@
   $\Judge(\opk,\sipk,\yinsp,\iproof,\sig,\yeval,\msg,\feval)
-  = 1$, but there exists some credential \cred for which $\Identify(\usk,
+  = 1$, but there exists some credential \cred for which $\IdentifyCred(\usk,
   \attrs_{\cred},\msg)=0$. Note that \usk, $\attrs_{\cred}$ and \cred (for all
@@
   \feval,\yeval,\Ec,\sipk,\opk) \in \NIZKRel^{\Sign}$, which more concretely
-  means that $\SBCMVerify(\ipk_{\cred},\cred,\attrs_{\cred} \cup \lbrace \usk
-  \rbrace) = 1 = \Identify(\usk,\attrs_{\cred},\cred)$, for all $\cred \in
-  \scred$. The probability of case 3 is therefore $0$.
+  means that, for all $\cred \in \scred$, $\SBCMVerify(\ipk_{\cred},\cred,\usk,
+  \attrs_{\cred}) = 1 = \IdentifyCred(\usk,\attrs_{\cred},\cred)$. The
+  probability of case 3 is therefore $0$.
   %
@@
   oracles. Otherwise, if there exists some \cred that was not obtained via
-  a call to these oracles, the pair $(\lbrace \usk \rbrace \cup \attrs_{\cred},
-  \cred)$ constitutes an existential forgery of \SBCM.
+  a call to these oracles, the tuple $(\usk, \attrs_{\cred}, \cred)$ constitutes
+  a forgery of \SBCM.
 
@@
   \Inspect.
+
+  The only remaining option for $\adv$ to win is via winning condition at line
+  11. At that point, we already know that all credentials are bound to the same
+  user key (otherwise, the adversary wins at line 10). If this key is not
+  associated to any known user, this means that there is no matching $\langle
+  \Obtain,\Issue\rangle$ transcript for a credential over $\usk$ --i.e., the
+  honest issuer did not issue any credential to \usk. But, as \sig must have
+  been produced with at least one credential (extracted at step 7), then this
+  credential is a forgery, breaking security against one-more forgery of the
+  \SBCM scheme.  
   %
@@
   must be able to produce a $(\usk,\scred,\attrs_{\scred},\yinsp')$ tuple. Since
-  $\adv$ wins the
-  non-frameability game with non-neglibible probability, with probability $1/q$,
+  $\adv$ wins the non-frameability game, with probability $1/q$,
   the \usk value belongs to the $u$-th honest user, so it must be equal to

### 2022-05-08 prism-backend/research/gsac/transformations-uas.tex
Added high-level descriptions of how to build other schemes from UAS.

\section{Relating \UAS with Other Schemes, and Variations}
\label{ssec:transformations}

In order to justify \UAS's universality, in this section we describe how does
\UAS schemes relate with other similar systems. \todo{The relationships seem
  quite straightforward; thus, we only informally sketch how one could build
  other schemes (or something very similar to them) from \UAS, and leave the
  formal analysis for futher work.}
%
As a first (informal) observation, we note that the same transformation to
interactive presentations as described in \GSAC applies here.

\subsection{\GSAC from \UAS}
Take the generic construction for \UAS in \secref{ssec:generic-construction-uas}.
First, consider the constant issuance function $\fissue^1(\usk,\scred,\attrs) =
1$. Next, consider $\finsp^{\upk}(\yeval,\usk,\scred,\msg) \coloneqq
\CCommit(\usk;0)$, and $\feval^{\dattrs}(\usk,\cred,\msg) \coloneqq \dattrs(\cred)$,
where $\dattrs(\cred)$ is the function returning the attributes indexed by
\dattrs within \cred (which we can assume to be easy to do with proper
encoding). It is straightforward to see that an \UAS scheme with $\fissue^1$
as issuance function, $\feval^{\dattrs}$ as signing evaluation function, and
$\finsp^{\upk}$ as opening function, is an implementation of the functionality
described for \GSAC --which, in addition, lets the signer use more than one
credential per signature; although this can of course be restricted
implementation-wise.
%
Furthermore, the anonymity, sign unforgeability, and non-frameability properties
of \UAS directly imply the anonymity, traceability, and non-frameability
properties of \GSAC.

\paragraph{Vanilla Group Signatures and Anonymous Credentials from \UAS.} As a
corollary to the previous analysis, recall that, in \secref{ssec:variants-gsac}
we proved that \GSAC implies both group signatures and anonymous credentials.
Thus, since \UAS implies \GSAC, \UAS implies also both group signatures and
anonymous credentials.

\subsection{\UAS with Multiple Openers}
We briefly mention that we have defined \UAS signatures as being ``openable'' by
only one opener. However, since there is no tight relation between issuer and
opener (as in conventional group signatures), note that it is trivial to extend
to the case with multiple openers per signature. In that case, the
$\NIZKRel_{\Sign}$ relation should be extended to include proofs of correct
encryption of the \yinsp values produced by each chosen opener.
Similarly, the sign unforgeability and non-frameability definitions should be
extended to check correctness of the corresponding extra open values.

\subsection{Group Signatures with Message Dependent Opening}

In \cite{khk+19}, one of the first group signature schemes with a certain
flexibility in the open-related functionality was introduced. Briefly, a group
signature scheme with message dependent opening works as a conventional group
signature scheme, with the addition that it is only possible to open signatures
over specific messages (e.g., text with offensive language). For this, the
authors introduce an extra authority, the admitter, who creates a
``message-specific token'' for each message that they deem unacceptable.
These message-specific tokens are later needed by the opener, in order to open
signatures over unacceptable messages.

\UAS can implement this functionality in a straightforward manner. Define
$\finsp^{\smsg}(\yeval,\usk,\cred,\msg) \coloneqq \lbrace \pcif \msg \in \smsg:
\pcreturn \CCommit(\usk;0); \pcelse \pcreturn \bot \rbrace$. Also, let
$\feval^0(\usk,\scred,\msg) \coloneqq \pcreturn 0$. Then, \UAS with $\fissue^1$
as issuance function, $\feval^0$ as signing evaluation function, and
$\finsp^{\smsg}$ as opening function, implements a message-dependent opening
group signature scheme -- again, restricting to one credential per user and
signature, as before. Moreover, it implements the same functionality without
an extra authority.

\todo{In \cite{khk+19}, the authors prove that GS-MDO implies identity-based
  encryption. \UAS implying GS-MDO would thus imply IBE, but we do not use
  IBE in our constructions. Is there some connection between some of the main
  building blocks we use, and IBE?}

\subsection{Ring Signatures}

In a nutshell, ring signatures \needcite are like group signatures where
rather than having an issuer accepting users into a group, any user can create
an ad hoc group composed by himself, and any arbitrary set of other users that
have advertised their public keys in some publicly accessible way. Also, in
ring signatures no de-anonymization is possible\footnote{At least, in vanilla
  ring signatures. Some variants allow some sort of linkability; for instance
  \needcite}, although the most distinguishing property is probably the lack of
issuer, which has led some relevant systems like Monero%
\footnote{\url{https://www.getmonero.org/resources/moneropedia/ringsignatures.html}.
  Last access on May 8th, 2022.} to opt for ring signatures rather than, e.g.,
group signatures.

To reach (vanilla) ring signatures from \UAS, we have to slightly alter our
generic construction. This is due to the fact that the NP relation
$\NIZKRel^{\Sign}$ defined in \secref{ssec:generic-construction-uas} reveals the
issuers' public keys. This is a problem as, intuitively, the signer in a ring
signature is a sort of issuer for the ad hoc group. To hide the issuer, we
replace the NP relation in \secref{ssec:generic-construction-uas} with
$\NIZKRel^{\Sign-prv} \coloneqq \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r,
\sipk_{\scred}),(\msg,\feval,\yeval,\Ec,\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land
\yeval = \feval(\usk,\scred,\msg) \land \yinsp = \finsp(\yeval,\usk,\scred,\msg)
\land \forall \cred \in \scred,\SBCMVerify(\ipk_{\cred},\cred,\usk,
\attrs_{\cred}) = 1) \rbrace$. That is, the public keys of the issuers are now
part of the witness in the NP relation, which means that they will not
be revealed in the proofs.
%
Besides $\NIZKRel^{\Sign-prv}$, let $ring$ be an ad hoc set containing the
public keys of the users that the signer wants to include in its ad hoc group.
We define $\fissue^{ring}(\usk,\scred,\attrs) \coloneqq \lbrace \pcif \attrs
\subseteq ring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1; \pcelse
\pcreturn 0 \rbrace$. That is, if we let the attributes in a credential be
public keys, this function means that a credential will be issued if all the
public keys specified as attributes to be included in the credential are part of
the union of the ad hoc ring and the public key of the signer. We also define
$\feval^{\attrs}(\usk,\cred,\msg) \coloneqq \lbrace \pcif \CCommit(\usk;0) \in
\attrs: \pcreturn \attrs(\cred); \pcelse \pcreturn \bot \rbrace$, where
$\attrs(\cred)$ is the function that returns all the attributes encoded in a
credential. That is, if the public key of the signer is included in the ring,
return all the attributes in the credential (i.e., all the public keys in the
ring); otherwise, abort. Finally, let $\finsp^0(\yeval,\usk,\cred,\msg) = 0$.

Then, an \UAS scheme with $\NIZKRel^{\Sign-prv}$ as NP relation for
$\NIZK^{\Sign}$, and $\fissue^{ring}$, $\feval^{\attrs}$, and $\finsp^0$ is
intuitively a ring signature scheme. To see this, observe that any user can
act as an issuer. Thus, the owner of \usk can issue to himself a credential
for any arbitrary ring it desires. While the $\NIZKRel^{\Issue}$ reveals the
issuer's public key, note that this is irrelevant, as the issuer is the user
himself. Then, the newly defined $\NIZKRel^{\Sign-prv}$ does exactly the same
as in our original \UAS scheme, but without revealing the issuer's public key.
$\feval^{\attrs}$ reveals all the attributes in the credential, which are
the public keys of the ring, including the signer's public key. This is actually
what ring signatures do: the signer, who is the owner of the private key
associated to one of the public keys in the ring, advertises which are the
public keys in the ring, and proves knowledge of one of them. If the NIZK
proof verifies, this means that the signer is indeed the owner of such a private
key. Finally, since $\finsp^0$ returns always $0$, then no de-anonymization is
possible.

\subsection{Multimodal Private Signatures}

\commentwho{Jesus}{How to cite the Crypto22 paper?}

To show that Multimodal Private Signatures (MPS) \needcite can be built from
\UAS, we need to give an alternative, simulation-based, definition of the
anonymity property. In the simulation-based approach, we require the adversary
to guess the bit $b$ defining whether it is interacting with the real world,
where it gets signatures by real users, or with a simulation, where all
signatures are simulated and do not contain information about the signer.
This alternative formulation is given in \figref{fig:exp-uas-simanon}, where
$\Osimanon = (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,
\OO\rbrace\CORR,\OBTAIN,\WREG)$.

\begin{figure}[htp!]

  \centering
  \procedure[linenumbering]{$\ExpSimAnonb(1^\secpar)$}{%
    \pcif b = 0: \\
    \parm \gets \Setup(1^\secpar) \\    
    \pcind b^* \gets \adv^{\Osimanon,\SIGN,\OPEN}(\parm) \\
    \pcelse: \\
    \parm \gets \SIMSETUP(1^\secpar) \\
    \pcind b^* \gets \adv^{\Osimanon,\SIMSIGN,\SIMOPEN}(\parm) \\    
    \pcreturn b^*
  }

  \caption{Simulation-based anonymity experiment for \UAS schemes.}
  \label{fig:exp-uas-simanon}
\end{figure}

\begin{definition}{(Simulatable Anonymity of \UAS)}
  \label{def:sim-anonymity-uas}  
  We define the advantage \AdvSimAnon of $\adv$ against \ExpSimAnonb as
  $\AdvSimAnon=|\Pr\lbrack\ExpSimAnono(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpSimAnonz(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies simulatable anonymity if there exists simulators
  \SIMSETUP, \SIMSIGN and \SIMOPEN such that, for any p.p.t. adversary $\adv$,
  \AdvSimAnon is a negligible function of $1^\secpar$.
\end{definition}

Note that, for our generic construction \CUASGen, \SIMSETUP, \SIMSIGN, and
\SIMOPEN are straightforward, as all we need to do is:

\begin{itemize}
\item To build \SIMSETUP, just replace the $\NIZKSetup^{\Sign}$ and
  $\NIZKSetup^{\Open}$ algorithms within \Setup, by their respective
  $\NIZKSimSetup$ algorithms.
\item To build \SIMSIGN from the \SIGN oracle, just simulate the NIZK proof
  contained in the signatures produced by the \Sign algorithm.
\item To build \SIMOPEN from the \OPEN oracle, just simulate the NIZK proof
  showing opening correctness, instead of producing them as in the \Open
  algorithm.
\end{itemize}

Indistinguishability then follows from the zero-knowledge property of each
corresponding NIZK system. Since both scenarios are indistinguishable, and
all signature-related proofs received by the adversary in the simulation do not
depend on any witness (as they are simulated), then it follows that the
adversary cannot gain any information about signers in the real world.

With this alternative definition, we can achieve a generalisation of MPS
basically by, insted of returning the plaintext \yeval value, returning an
encryption of it under the inspector's public key; additionally proving 
that the value used to compute the output of \finsp is the plaintext \yeval
value. In more detail, given any \feval function, we first define an
encrypted variant $\feval^{enc}(\usk,\scred,\msg) \coloneqq \lbrace \yeval
\gets \feval(\usk,\scred,\msg); \yeval' \gets \EEnc(\opk,\yeval); \pcreturn
\yeval' \rbrace$.
%
Naturally, the $\NIZKRel_{\Sign}$ has to be correspondigly extended, as
$\NIZKRel_{\Sign}^{enc} = \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r),(\msg,
\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land
\yeval = \EEnc(\opk,\feval(\usk,\scred,\msg)) \land \yinsp = \finsp(\feval(\usk,
\scred,\msg),\usk,\scred,\msg) \land \forall \cred \in \scred,
\SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$.

Given this approach, the need to provide an alternative definition for anonymity
is clearer. Namely, in the original \CHALb oracle, we restrict that the
signatures produced by both challenge users output the same \yeval value.
However, if instead of returning the plaintext \yeval value, we return an
encrypted version of it (as we do in the variant just described), this clearly
becomes unachievable.

\todo{It would seem that the simulation-based anonymity definition is more
  general. Can we prove that? Concretely, if it is also good for selective
  disclosure, we may just adopt it as default.}

\subsection{Delegatable Credentials}

Building delegatable credentials is also straightforward, thanks to the \fissue
function. For instance, take the simplification of level-based delegation, where
the owner of a credential of level $n$ can only issue credentials of level
$n+1$. Without loss of generality, assume that the credential level is encoded
in the first attribute of the credential, which we denote with $a_1$. In this
context, any owner of a credential of level $n$ can define an issuance function
$\fissue^n \coloneqq \lbrace \pcif a_1 = n+1: \pcreturn 1; \pcelse \pcreturn 0
\rbrace$.

\subsection{Functional Signatures}

\todo{I think that, by making \yeval explicit, \UAS is essentially a
  privacy-preserving extension to Functional Signatures. Still, I read that paper
  quite some time ago. Re-check.}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:

### 2022-05-09 prism-backend/research/gsac/app-building-blocks.tex
Added sketch of security proof for SBCM. Updated GSAC model to include attrs on Open. Other minor edits.

@@
 
-    \procedure{$\ExpSBCMOMF(\SBCMsecpar)$}{%
+    \procedure[linenumbering]{$\ExpSBCMOMF(\SBCMsecpar)$}{%
       \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
@@
       \pcif \langle \cdot, \SBCMSign(\SBCMsk,\cdot)\rangle~
-      \textrm{was called more than $k$ times}: \pcreturn 0 \\
-      \pcreturn 1 \\
+      \textrm{was called more than $n$ times}: \pcreturn 0 \\
+      \pcreturn 1
     }
 
-    \procedure{$\ExpSBCMBlindb(\SBCMsecpar)$}{%
+    \vspace*{0.5em}
+
+    \procedure[linenumbering]{$\ExpSBCMBlindb(\SBCMsecpar)$}{%
       \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
@@
 \subsubsection{Security.} Next, we sketch that the given BBS+ interactive
-signing protocol is correct and OMF-secure.
+signing protocol is correct, OMF-secure, and ensures blindness.
 
@@
 
-\paragraph{OMF security.} \todo{YYY}
+\paragraph{OMF security.} The proof for OMF security is essentially the
+same as that of EUF security for BBS+ signatures \cite{cdl16b}, which gives a
+reduction against the $q$-SDH problem. There is only one exception: in the proof
+for BBS+ EUF-security, when the adversary against EUF-security queries a
+signature, the simulator (the adversary against $q$-SDH) has to simulate the
+signature. For this, it requires the $l$ messages in the message set to be
+signed, which in plain BBS+ it is not a problem, as they are received in the
+clear. In the case of \SBCM, however, some of the messages to be signed are
+received as part of a commitment. Note however that, in \SBCM, besides receiving
+the commitment, we also receive a NIZK proof of knowledge of the corresponding
+messages. Thus, the adversary against $q$-SDH in the OMF case only needs to
+extract the witnesses from the proof. This is doable after soundness of NIZK.
+If the NIZK also has online-extractability, then we do not need to impose
+further requirements. If it is not, then the \SBCM scheme should not allow
+parallel signing requests, or limit the total number of signatures to be
+created to a logarithmic function of the security parameter (which is probably
+not reasonable in most cases; although it may be for group signature-like
+settings). We refer to \cite[Lemma 1]{cdl16b} for the full details of the proof
+of EUF security in BBS+.
+%
+\todo{If needed, do the actual proof. Should essentially be a copy-paste of
+  that in \cite{cdl16b}...}
+
+\paragraph{Blindness.} Blindness of \SBCM is a direct consequence of the
+hiding property of the underlying block commitment scheme. Indeed, assume an
+adversary $\adv$ against blindness of \SBCM. Then, $\adv$ can be used by
+\advB against the hiding property of the commitment scheme in a straightforward
+manner. That is, once $\adv$ outputs its two sets of messages to be signed in
+committed form (i.e., $\overline{\smsg}_0$ and $\overline{\smsg}_1$, it feeds
+them directly to its environment in \ExpComHideb; \advB awaits for the response
+(a commitment of $\overline{\smsg}_b$), and forwards it to $\adv$. Finally,
+\advB outputs whatever $\adv$ outputs. Clearly, if $\adv$ wins the blindness
+game for \SBCM with non-negligible probability, so does \advB agains the hiding
+game of the commitment scheme.
 

### 2022-05-09 prism-backend/research/gsac/app-gsac.tex
Added sketch of security proof for SBCM. Updated GSAC model to include attrs on Open. Other minor edits.

@@
           \pcif \sig \in \CSIG: \pcreturn \bot \\
-          (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\dattrs,\msg) \\
+          (\upk,\attrs,\oproof) \gets \Open(\gpk,\osk,\sig,\dattrs,\msg) \\
 %          \OSIG \gets \OSIG \cup \lbrace (\sig,\upk,\cred) \rbrace \\
 %          \CCRED \gets \CCRED \cup \lbrace \cid \rbrace \\
-          \pcreturn (\upk,\oproof) \\
+          \pcreturn (\upk,\attrs,\oproof) \\
         }
@@
 
-\commentwho{Jesus}{Strictly, in our generic construction we require IND-CCA (is
-  that a strict requirement? or can it be downgraded to IND-CPA?), but in the
-  following concrete instantiation, we use ElGamal, which is IND-CPA. However,
-  we actually ``lift'' ElGamal with NIZKs of the encrypted plaintexts, which is
-  essentially IND-CCA as far as I know. Still, make sure to mention that.}
+\todo{Need to update the proofs with the updated definitions, now returning
+  \attrs as part of \Open.}
+
+\commentwho{Jesus}{Strictly, in our generic construction we require IND-CCA, but
+  in the following concrete instantiation, we use ElGamal, which is IND-CPA.
+  However, we actually ``lift'' ElGamal with NIZKs of the encrypted plaintexts,
+  which is essentially IND-CCA as far as I know. Still, make sure to mention
+  that.}
 
@@
 proof. For this, we define relation
-$\NIZKRel_{\Sign}= \lbrace (r,\usk,\attrs,r_2,r_3,s',\msg),(\dattrs,c_1,c_2,
-\Cmsg): \Cmsg = \gen{h}^\msg \land c_1 = g^r \land c_2 = \opk^r\gen{h}_1^{\usk}
+$\NIZKRel_{\Sign}= \lbrace (r,t_1,\dots,t_n,\usk,\attrs,r_2,r_3,s',\msg),(\dattrs,c_1,c_2,
+\Cmsg,\sEc^{\attrs},n): \Cmsg = \gen{h}^\msg \land c_1 = g^r \land c_2 = \opk^r\gen{h}_1^{\usk}
+\land \sEc^{\attrs}_{1,1} = g^{t_1} \land \sEc^{\attrs}_{1,2} = \opk^{t_1}\gen{h}_2^{\attrs_1}
+\land \dots
+\land \sEc^{\attrs}_{n,1} = g^{t_n} \land \sEc^{\attrs}_{n,2} = \opk^{t_n}\gen{h}_{n+1}^{\attrs_n}
 \land \hat{A}/d = (A')^{-x}\gen{h}_0^{r_2} \land
@@
   $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs,
-  (r,\usk,\attrs,r_2,r_3,s',\msg), (\dattrs,c_1,c_2,\Cmsg))$.
-\item Return $\sig \gets (c=(c_1,c_2),(A',\hat{A},d),\NIZKproof)$.
+  (r,t_1,\dots,t_n,\usk,\attrs,r_2,r_3,s',\msg), (\dattrs,c_1,c_2,\Cmsg,
+  \sEc^{\attrs},n))$.
+\item Return $\sig \gets (c=(c_1,c_2),\sEc^{\attrs},(A',\hat{A},d),\NIZKproof)$.
 \end{itemize}
@@
 \paragraph{$\Verify(\gpk,\sig,\dattrs,\msg) \rightarrow 1/0$.} %
-Parse \gpk as $(\ipk,\opk)$ and $\sig$ as $(c=(c_1,c_2),
+Parse \gpk as $(\ipk,\opk)$ and $\sig$ as $(c=(c_1,c_2),\sEc^{\attrs},
 (A',\hat{A},d), \NIZKproof)$. Check that $A' \neq 1_{\GG_1}$ and $e(A',\ipk) =
 e(\hat{A},\gen{g}_2)$. Compute $\Cmsg \gets \gen{h}^\msg,$ and return
-$\NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs,(\dattrs,c_1,c_2,\Cmsg),
-\NIZKproof)$.
+$\NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs,(\dattrs,c_1,c_2,\Cmsg,\sEc^{\attrs},
+n),\NIZKproof)$.
 
 \paragraph{$\Open(\gpk,\osk,\sig,\dattrs,\msg)
-  \rightarrow (\upk,\oproof)/\bot$.} %
+  \rightarrow (\upk,\attrs,\oproof)/\bot$.} %
 For open algorithms, we define the following relation for correct decryption of
 ElGamal ciphertexts: $\NIZKRel_{\Open} = \lbrace \osk,(c_1,c_2,\msg):
-c_2/c_1^{\osk} = \msg \rbrace$. Given $\NIZKRel_{\Open}$, the opener first,
+c_2/c_1^{\osk} = \msg \rbrace$. Given $\NIZKRel_{\Open}$, the opener first
 checks that $\Verify$ accepts the signature, and aborts otherwise. If \sig
-is accepted, then parses \sig as $(c=(c_1,c_2),\cdot,\cdot)$.
-Sets $\upk \gets c_2/c_1^{\osk}$. Finally, computes the proof of correct
-decryption by running $\oproof \gets \NIZKProve^{\NIZKRel_{\Open}}(\NIZKcrs,
-\osk,(\upk,c_1,c_2))$, and returns $(\upk,\oproof)$.
+is accepted, then parses \sig as $(c=(c_1,c_2),\sEc^{\attrs},\cdot,\cdot)$.
+Sets $\upk \gets c_2/c_1^{\osk}$, and
+$\attrs_i \gets \sEc^{\attrs}_{i,2}/(\sEc^{\attrs}_{i,1})^{\osk}$. Finally,
+computes the proof of correct decryption by running $\oproof \gets
+(\NIZKProve^{\NIZKRel_{\Open}}(\NIZKcrs,\osk,(\upk,c_1,c_2)),
+\NIZKProve^{\NIZKRel_{\Open}}(\NIZKcrs,\osk,(\attrs_1,\sEc^{\attrs}_{1,1},\sEc^{\attrs}_{1,2})),
+\dots,
+\NIZKProve^{\NIZKRel_{\Open}}(\NIZKcrs,\osk,(\attrs_n,\sEc^{\attrs}_{n,1},\sEc^{\attrs}_{n,2})))$,
+and returns $(\upk,(\attrs_1,\dots,\attrs_n),\oproof)$.
 
-\paragraph{$\Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg)
+\paragraph{$\Judge(\gpk,\upk,\attrs,\oproof,\sig,\dattrs,\msg)
   \rightarrow 1/0$.} %
 First, check that $\Verify$ accepts \sig, and abort otherwise. If the signature
-is accepted, then parse \sig as $(c=(c_1,c_2),\cdot,\cdot)$ and return
-$\NIZKVerify^{\NIZKRel_{\Open}}(\NIZKcrs,(c_1,c_2,\upk),\oproof)$.
+is accepted, then parse \sig as $(c=(c_1,c_2),\sEc^{\attrs},\cdot,\cdot)$,
+parse \oproof as $(\oproof_0,\oproof_1,\dots,\oproof_n)$ and
+return $\NIZKVerify^{\NIZKRel_{\Open}}(\NIZKcrs,(c_1,c_2,\upk),\oproof_0) \land
+\NIZKVerify^{\NIZKRel_{\Open}}(\NIZKcrs,(\sEc^{\attrs}_{1,1},\sEc^{\attrs}_{1,2},\attrs_1),\oproof_1) \land
+\dots \land
+\NIZKVerify^{\NIZKRel_{\Open}}(\NIZKcrs,(\sEc^{\attrs}_{n,1},\sEc^{\attrs}_{n,2},\attrs_n),\oproof_n)$.
 

### 2022-05-09 prism-backend/research/gsac/preliminaries.tex
Making a pass.
Added sketch of security proof for SBCM. Updated GSAC model to include attrs on Open. Other minor edits.

@@
 encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\Edk,
-\Ec)$ decrypts ciphertexts using decryption key \Edk. We rely on \todo{IND-CCA}
+\Ec)$ decrypts ciphertexts using decryption key \Edk. We rely on IND-CCA
 public-key encryption schemes.
@@
 
-\todo{\Attrs and \DAttrs (in \secref{ssec:construction-gsac}, they are treated
+\todo{\attrs and \dattrs (in \secref{ssec:construction-gsac}, they are treated
   as indices, but I think that's not the case elsewhere).}

### 2022-05-10 prism-backend/research/gsac/app-gsac.tex
Updated GSAC and UAS proofs based on updated non-frame definiton.

@@
 
-\begin{proof}[\thmref{thm:correctness-gsac}]
+\begin{proof}[\thmref{thm:correctness-gsac}; Correctness of \GSACGen]
   \todo{XXX}
@@
 
-\begin{proof}[\thmref{thm:anonymity-gsac}]
+\begin{proof}[\thmref{thm:anonymity-gsac}; Anonymity of \GSACGen]
   We prove that the probability of an adversary distinguishing signatures by
@@
   From $G_1$, we build $G_2$, where within the challenge signature produced by
-  \CHALb, we replace the \Ccom value encrypted within \Sign with a random
-  string of the appropriate length (e.g., the same length of the encrypted
-  message in $G_1$). The corresponding proof for $\NIZKRel_{\Sign}$ is thus
+  \CHALb, we replace the values encrypted within \Sign (\Ccom, and all the
+  attributes in \attrs) with random strings of the appropriate length (e.g.,
+  the same length of their corresponding encrypted messages in $G_1$). The
+  proof for $\NIZKRel_{\Sign}$ is thus
   also simulated. The zero-knowledge and simulation-extractability properties
@@
 
-\begin{proof}[\thmref{thm:trace-gsac}]
+\begin{proof}[\thmref{thm:trace-gsac}; Traceability of \GSACGen]
   Assuming the NIZK systems are sound, we build an adversary against existential
@@
   \item[$J$.] The \Judge algorithm returns $0$.
-  \item[$D$.] No credential owned by a user in \CU contains \dattrs.
+  \item[$D$.] No credential owned by a user in \CU over \attrs contains \dattrs.
   \end{description}
@@
     \Judge accepts the output by \Open, but no corrupt user has a credential
-    containing \dattrs (line 8 of \ExpGSACTrace).
+    over \attrs, containing \dattrs (line 8 of \ExpGSACTrace).
   \end{description}
@@
   verification succeeds, soundness of $\NIZK_{\Sign}$ implies that $(\Ccom_m,
-  \Ec,\dattrs) \in \NIZKLang_{\Sign}$, except with negligible probability
-  $2^{-\NIZKsecpar}$. Also, observe that each of the winning events for the
-  adversary described above are disjoint. Thus:
+  \Ec,\sEc^{\attrs},\dattrs,n) \in \NIZKLang_{\Sign}$, except with negligible
+  probability $2^{-\NIZKsecpar}$. Also, observe that each of the winning events
+  for the adversary described above are disjoint. Thus:
 
@@
 
-  $\Pr[W_1]=0$ is directly deduced from the fact that $(\Ccom_m,\Ec,\dattrs)
+  $\Pr[W_1]=0$ is directly deduced from the fact that $(\Ccom_m,\Ec,
+  \sEc^{\attrs},\dattrs,n)
   \in \NIZKLang_{\Sign}$ due to soundness of $\NIZKRel_{\Sign}$. Concretely,
@@
   \Verify (as this is checked in line 4 of \ExpGSACTrace too) and, thus,
-  $\Ec = \EEnc(\opk,\Ccom)$ which, by correctness of the encryption algorithm,
-  implies that $\Ccom = \EDec(\osk,\Ec)$, where $\upk=\Ccom=\CCommit(\usk;0)$.
+  $\Ec = \EEnc(\opk,\Ccom)$ (resp. $\sEc^{\attrs}_i = \EEnc(\opk,\attrs_i;
+  \forall i \in [n]$) which, by correctness of the encryption algorithm,
+  implies that $\Ccom = \EDec(\osk,\Ec)$ (resp. $\attrs_i =
+  \EDec(\osk,\sEc^{\attrs}_i)$, where $\upk=\Ccom=\CCommit(\usk;0)$.
   Completeness of $\NIZK_{\Open}$ thus implies that the \Open algorithm can
-  compute the opening proof \oproof, and return $(\upk,\oproof)$.
+  compute the opening proof \oproof, and return $(\upk,\attrs,\oproof)$.
 
@@
   fail, and for which an honestly generated open proof is accepted by \Judge,
-  but such that no issued credential contains \dattrs. Soundness of
-  $\NIZK_{\Sign}$ implies that \sig is a valid signature over $\attrs \cup
-  \lbrace \usk \rbrace$, and $\dattrs \subseteq \attrs$; but \sig has not been
-  produced via a call to the $\langle \cdot,\SBCMSign \rangle$ oracle. Thus,
-  \advB can output at least $n+1$ valid signatures, which contradicts security
-  of \SBCM.
+  but such that no issued credential over attritube set \attrs that contains
+  \dattrs. Soundness of $\NIZK_{\Sign}$ implies that \sig is a valid signature
+  over $\attrs \cup \lbrace \usk \rbrace$, and $\dattrs \subseteq \attrs$; but
+  \sig has not been produced via a call to the $\langle \cdot,\SBCMSign \rangle$
+  oracle. Thus, \advB can output at least $n+1$ valid signatures, which
+  contradicts security of \SBCM.
   %
@@
 
-\begin{proof}[\thmref{thm:frame-gsac}]
-  We build an adversary \advB who, given an adversary $\adv$ against
-  \ExpGSACNonframe, breaks the hiding property of \C.
+\begin{proof}[\thmref{thm:frame-gsac}; Non-frameability of \GSACGen]
+  Consider the following events:
+
+  \begin{description}
+  \item[$U \coloneqq \uid \in \HU$.] The user identifier associated to the
+    signature does not belong to an honest user.
+  \item[$S \coloneqq \sig \notin \SIG\lbrack \uid \rbrack$.] The signature was
+    not produced via a call to the \SIGN oracle.
+  \item[$A \coloneqq \dattrs \not\subseteq \attrs$.] The revealed attributes are
+    note a subset of the attributes output by $\adv$ and accepted by \Judge.
+  \end{description}
+
+  $\adv$ wins if:
+
+  \begin{enumerate}
+  \item $U \land S$. The adversary outputs a signature framing an honest user
+    who did not produce it.
+  \item $U \land A$. The adversary outputs a signature framing an honest user,
+    since the revealed attributes are not a subset of the attributes accepted
+    by \Judge.
+  \end{enumerate}
+
+  The probability of $\adv$ winning due to $U \land A$ is negligible, after
+  soundness of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.
+
+  Concerning $U \land S$, we build an adversary \advB who, given an adversary
+  $\adv$ against \ExpGSACNonframe via this condition, breaks the hiding property
+  of \C.
 
@@
   users to let $\adv$ create via calls to the \HUGEN oracle (note though that
-  $q$ can be as large as desired, as it remains a polynomial function of the
-  security parameter). In the $u$-th call to the \HUGEN oracle, \advB ignores
-  sets $(\upk,\usk)$ to $(\Ccom,\bot)$. Calls to the \OBTAIN and \SIGN oracles
+  $q$ can be as large as desired, as long as it remains a polynomial function of
+  the security parameter). In the $u$-th call to the \HUGEN oracle, \advB
+  ignores $(\upk,\usk)$ to $(\Ccom,\bot)$. Calls to the \OBTAIN and \SIGN oracles
   are dealt with as usual, except when $\adv$ requests credentials or signatures
@@
   Finally, assume that $\adv$ wins \ExpGSACNonframe with non-negligible
-  probability. This means that it outputs a $(\sig = (\Ec,\pi_\sig),\dattrs,
-  \msg,\upk,\pi)$, where $(\sig,\dattrs,\msg)$ are accepted by \Verify, and
-  $(\upk,\pi,\sig,\dattrs,\msg)$ are accepted by \Judge. Thus, after soundness
+  probability. This means that it outputs a $(\sig = (\Ec,\sEc^{\attrs},
+  \pi_\sig),\dattrs,\msg,\upk,\attrs,\oproof)$, where $(\sig,\dattrs,\msg)$ are
+  accepted by \Verify, and $(\upk,\attrs,\oproof,\sig,\dattrs,\msg)$ are
+  accepted by \Judge. Thus, after soundness
   of $\NIZK^{\NIZKRel_{\Sign}}$ and $\NIZK^{\NIZKRel_{\Open}}$, we know that

### 2022-05-10 prism-backend/research/gsac/security-gsac.tex
Updated GSAC and UAS proofs based on updated non-frame definiton.

@@
   \label{thm:frame-gsac}
-  If the underlying scheme for $\NIZK^{\NIZKRel_{\Issue}}$,
-  $\NIZK^{\NIZKRel_{\Sign}}$ and $\NIZK^{\NIZKRel_{\Open}}$ are sound,
-  zero-knowledge, and simulation-extractable, and
-  the commitment scheme \C is hiding, then our generic \GSACGen construction
-  satisfies non-frameability as defined in \defref{def:frame-gsac}, except with
-  negligible probability.
+  If the scheme for $\NIZK^{\Issue}$ is zero-knowledge, the scheme for
+  $\NIZK^{\Sign}$ is zero-knowledge and sound, the scheme for $\NIZK^{\Open}$ is
+  sound, and the commitment scheme \C is hiding, then our generic \GSACGen
+  construction satisfies non-frameability as defined in \defref{def:frame-gsac},
+  except with negligible probability.
 \end{theorem}

### 2022-05-10 prism-backend/research/gsac/security-uas.tex
Updated GSAC and UAS proofs based on updated non-frame definiton.

@@
 
-\begin{proof}[\thmref{thm:correctness-uas}]
+\begin{proof}[\thmref{thm:correctness-uas}; Correctness of \CUASGen]
   \todo{XXX}
@@
 
-\begin{proof}[\thmref{thm:anonymity-uas}]
+\begin{proof}[\thmref{thm:anonymity-uas}; Anonymity of \CUASGen]
   In this proof, we restrict to the case in which the adversary can only make
@@
 
-\begin{proof}[\thmref{thm:issue-forge-uas}]
+\begin{proof}[\thmref{thm:issue-forge-uas}; Issue unforgeability of \CUASGen]
   We show that the probability that \fissue outputs $0$ is negligible, as well
@@
 
-\begin{proof}[\thmref{thm:sign-forge-uas}]
+\begin{proof}[\thmref{thm:sign-forge-uas}; Sign unforgeability of \CUASGen]
   As for \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
@@
   \label{thm:frame-uas}
-  If the underlying NIZK schemes are zero-knowledge and the scheme used for
-  $\NIZK^{\Sign}$ is simulation-extractable, and the commitment scheme is
-  hiding, then our \CUASGen construction satisfies non-frameability as defined
-  in \defref{def:frame-uas}, except with negligible probability.
+  If the underlying scheme for $\NIZK^{\Issue}$ is zero-knowledge, the scheme
+  for $\NIZK^{\Sign}$ is zero-knowledge, sound and simulation-extractable, the
+  scheme for $\NIZK^{\Open}$ is zero-knowledge and sound, and the commitment
+  scheme is hiding, then our \CUASGen construction satisfies non-frameability as
+  defined in \defref{def:frame-uas}, except with negligible probability.
 \end{theorem}
 
-\begin{proof}[\thmref{thm:frame-uas}]
-  We prove that, given an adversary $\adv$ against non-frameability of \CUASGen,
-  we can build an adversary \advB that breaks the hiding property of the
-  underlying commitment scheme, with non-negligible probability.
+\begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]
+  First, note that the adversary wins if it produces a signature that traces to
+  an honest user (which, in our case, is tested by checking whether the
+  extracted \usk belongs ot an honest user); and, in addition, either (1) the
+  signature was not produced via a call to the \SIGN oracle, or (2) the opening
+  value output by the adversary and accepted by \Judge, does not match the
+  extracted one (i.e., the one used as witness to $\NIZKRel^{\Sign}$). Note that
+  the probability of (2) is negligible due to soundness of $\NIZK^{\Sign}$ and
+  $\NIZK^{\Open}$, given that \Verify and \Judge accept the signature and
+  opening proof.
+
+  Next we prove that, given an adversary $\adv$ against non-frameability of
+  \CUASGen, under condition (1) above, we can build an adversary \advB that
+  breaks the hiding property of the underlying commitment scheme, with
+  non-negligible probability.
 

### 2022-05-10 prism-backend/research/gsac/uas.tex
Creating a separate document for UAS.
Made a pass before sharing.
Working on syntax for generic construction.
Merged GSAC and UAS into uas.tex paper. Defining concrete instantiation of GSAC.
Refined UAS model.
Added some BB definitions.
Formalising SBM and SBCM from SBM.
Added high-level descriptions of how to build other schemes from UAS.
Improved (lengthy) abstract.

--- 2022-02-06 prism-backend/research/gsac/gsac.tex
@@
 \usepackage{hyperref}
+\usepackage{mathtools}
 
-\title{Group Signatures Meet Anonymous Credentials: Or, How to Build
-  Privacy Preserving Identities with Accountability}
+\title{Universal Anonymous Signatures}
 \author{}
@@
 \input{symbols.tex}
+\input{symbols-gsac.tex}
+\input{symbols-uas.tex}
 
@@
 \begin{abstract}
-  \comment{\textbf{DISCLAIMER}: Please, keep in mind that this is a working
-    draft. Its main use in its current state is to foster debate on the topics
-    it deals with. Do not take anything written here as ground truth.}  
+  Much work has been done in the last 4 decades on privacy-preserving
+  identities and authentication that tries to incorporate some sort of utility
+  and accountability without losing (too much) privacy. Among the most relevant
+  efforts we can find group signatures and anonymous credentials.
+  %
+  Anonymous credentials (AC) let users obtain attestations by trusted
+  issuers on certain attributes -- thus implicitly defining the concept of
+  identity as ``a set of attributes'' -- and allow credential owners to prove
+  claims on these attributes. Indeed, this has proven to be very
+  flexible, to the point that it has served as inspiration to design W3C's
+  Verifiable Credentials, a relevant industry-led effort. However, the
+  accountability offered by anonymous credentials is quite limited; frequently
+  restricted to blacklisting, if present at all.
+  %
+  On the other hand, group signatures (GS) have traditionally focused on plain
+  authentication without attributes (except very few exceptions), making instead
+  more emphasis on the accountability side. That is, not only allowing full
+  deanonymization, but also variants such as sequential linking, user-controlled
+  anonymity, or even full unlinkability.
+  %
+  Not surprisingly, GS and AC share very common syntax, models and frequently
+  also constructions.
+
+  We argue that, for the real world, both functionalities are essential. Taking
+  advantage of their similarities, we first propose a trivial combination, that
+  we refer to with the original \GSAC acronym. Through \GSAC, we
+  showcase the benefits of even a simple combination. We give a common syntax,
+  security model, and generic construction for \GSAC.
+  %
+  Next, we acknowledge that even \GSAC has strong limitations. Namely, it is too
+  strict in the rules one can apply during issuance of credentials, and signing
+  and opening of the produced signatures. While generalizations along these
+  lines have been explored independently in the GS and AC domains, to the best
+  of our knowledge, no single scheme offers full flexibility.
+  We define a syntax, security model, and give a generic
+  construction for a scheme meeting these requirements. Given its high
+  flexibility to cater for different needs, we name it Universal Anonymous
+  Signatures (\UAS). Indeed, an \UAS scheme lets issuers decide on issuance
+  policies, which easily enable advanced use cases such as delegation, or
+  issuance conditioned identity-related claims. It can also be used to build
+  schemes that allow signers prove arbitrary claims on their identities, as well
+  as deciding on which should be the opening authority that can apply some
+  commonly agreed deanonymization function over the signer's identity (which is
+  now well-defined, given the incorporation of attributes from the AC domain).
+  %
+  The techniques and building blocks we leverage are well known. The challenge
+  is, rather, on the definitional side.
 \end{abstract}
@@
 \input{preliminaries.tex}
-\input{model.tex}
-\input{construction.tex}
-%\input{benchmarks.tex}
+\input{sec-gsac.tex}
+\input{sec-uas.tex}
+\input{benchmarks.tex}
 \input{conclusion.tex}
@@
 \bibliographystyle{splncs04}
-\bibliography{gsac}
+\bibliography{uas}
 
-% \appendix
+\appendix
+
+\input{app-building-blocks.tex}
+\input{app-gsac.tex}
 
@@
 %%% mode: latex
-%%% TeX-master: ucl.tex
+%%% TeX-master: "uas"
 %%% End:

### 2022-05-10 prism-backend/research/gsac/introduction.tex
Added sketch of security proof for SBCM. Updated GSAC model to include attrs on Open. Other minor edits.
Working on intro.

--- 2022-02-13 prism-backend/research/gsac/introduction.tex
@@
 
-\commentwho{Jesus}{The following will most probably change completely if we
-  are to submit this for publication. However, this should capture tha main
-  ideas.}
+% What is the context for this research? Introduce previous works on this topic,
+% in one paragraph. (Privacy-preserving identities, with accountability (APPI))
+Successful identity representation, management, and usage are, on its own, among
+the toughest problems in the Internet and digital communications at large
+\needcite. Just as an illustration, think
+of usernames and passwords, which end up being unmanageable as soon as we need
+to start remembering a few \needcite; or traditional vertical PKIs, like X.509,
+which are too rigid, and frequently require too much trust \needcite; or
+horizontal PKIs, such as PGP, that are also too rigid, and do not scale well
+\needcite. If, in addition, we require privacy, the scenario becomes even more
+challenging. Technologies like OpenID and OAuth \needcite make identity more
+manageable (from the point of view of service providers) through Single Sign
+On solutions. But this comes at the cost of introducing centralization points
+that gain way too much knowledge beyond what is actually necessary. Holding
+users accountable, or extracting utility out of their actions, is trivial in
+this cases -- although that comes at the cost of barely having privacy.
 
-In this work, we combine two closely related schemes -- group signatures (GS)
-and anonymous credentials (AC) -- which have followed a
-separate path up to now, beyond individual constructions from both fields
-drawing inspiration (and techniques) from one another. This combination is in
-some sense a natural evolution, which we do believe may have relevant impact in
-practical settings. On the one hand, anonymous credentials enable a richer
-functionality in regards to what one can prove about his own identity, in a
-privacy-preserving way. Academic proof of this is the fact that AC systems have
-naturally evolved to enabling arbitrary claims that only reveal the minimally
-possible 1-bit of information \needcite. Also, AC systems have been proposed to
-go even beyond what one can prove about his identity, covering also orthogonal
-functionality such as delegation \needcite, or aggregation of multiple
-credentials into one \needcite. Even outside academia, prominent
-technical workgroups \needcite, startups \needcite, and big techs \needcite are
-promoting and adopting solutions which are directly inspired by AC systems. On
-the other hand, GS 
-schemes have inspection functionality (e.g., opening and linking of signatures)
-at their core, which is reflected formally through non-frameability properties.
-This has originated a large body of research focusing on the construction and
-formalisation of variants of these notions \needcite. Consequently, group
-signatures tend to be proposed for scenarios that require some sort of
-de-anonymization \needcite. Indeed, this is not possible in ACs, which at most
-support revocation of issued credentials, which essentially can compare to
-linking, but not to opening-related notions.
+% What are the main approaches of previous works to achieve APPI? How are they
+% lacking? If possible, use titled paragraphs to emphasize the main points.
 
-Our goal is to get the best of both worlds: leverage the richer functionality
-of ACs in what respects to proving, in a privacy-preserving manner, useful
-claims on one's identity; and, at the same time support, through inspection
-capabilities, use cases that may require some sort of de-anonymization. This is
-not the first work that somehow follows this direction, though --
-Attribute-Based Group Signatures, covered in \secref{ssec:related}, propose
-group signatures with attributes (although mentions to AC works from the ABGS
-papers are non-existent, so the resemblance seems circumstancial). However, we
-believe that ABGS lack the flexibility that has made AC schemes gain popularity
-recently. Hence, we propose a different approach that directly integrates GS
-features and properties with those of AC, as closely as possible to their
-original notions.
+From a cryptographic point of view, and combining both privacy and
+identity/authentication requirements, group signatures (GS) and anonymous
+credentials (AC) are surely among the most well known advanced schemes that
+aim at addressing subsets of the previous problems. However, they typically fall
+short of enabling utility or accountability without sacrificing privacy.
+
+\paragraph{Limitations of Group Signatures.} %
+For instance, in a vanilla GS scheme, a group of users can create a signature on
+behalf of the group, without revealing the specific user who created it. At any
+later point in time, an authority can extract from such group signature the
+``identity'' of it signer (process called \emph{opening}). We find here two main
+drawbacks:
+
+\begin{enumerate}
+\item This usually results in a sort of all-or-nothing approach. 
+\item The concept of ``identity'' is barely defined.
+\end{enumerate}
+
+Concerning (1), either the signer is anonymous (before opening); or fully
+deanonymized (after opening). Some variants on the traditional opening do not
+fully deanonymize, but incorporate some other strict tradeoff. Like giving the
+users full control \cite{dl21}, only allowing linking \needcite, or some
+arbitrary extension such as allowing deanonymization only to the eyes of other
+group members \needcite, or sequential linkability \cite{dl21}. While these
+variants may be very suitable for concrete settings, it is not hard to see that
+adapting them to other scenarios will be hard -- if possible at all.
+
+Concerning (2), it is even surprising that, during the almost 30 years of
+research in group signatures, the notion of ``identity'' of a group member
+mostly reduces to an integer representing the order in which a user joined
+the group -- or, at the most, some long-term public key. Thus, even with
+notorious efforts to generalize accountability in group signatures,
+re-identifying the signer from an index still forces to assume an external
+ecosystem that endows that index with actual real world identyfing information.
+Needless to say, this introduces further points of centralization, and
+trust assumptions.
+
+\paragraph{Limitations of Anonymous Credentials.} %
+In a vanilla AC scheme, an (set of) issuer(s) grant credentials to users,
+attesting for attributes that these users own. For intance, their age,
+nationality, blood type, etc. Users can later prove arbitrary claims over
+these attributes -- the most simple being selective disclosure; i.e., just
+plainly revealing a subset of the attributes in a credential. Even from basic
+selective disclosure, realistic applications can be built. The rationale being
+that these attributes actually establish direct links with real identifying
+information. However, accountability is barely considered, being blacklisting
+of credentials almost the only explored variant.
+
+While this may initially seem ok, closer thought quickly shows limitations. For
+instance, think of a user who authenticates with an anonymous credential to get
+in a night club. If the user proves being over the age limit, s/he will be let
+in. However, if some time later, s/he is diagnosed positive in some contagious
+disease, blacklisting does not serve any purpose. Incentivation mechanisms also
+fit very well: a scenario in which a user authenticates anonymously to perform
+some action that may receive some reward later will also not be implementable
+with a credential scheme that only provides blacklisting. The problem is not
+only practical, though. Without having suitable models to cater for these needs,
+existing schemes just cannot be proven secure easily if they were to be used
+to approximate solutions to the previous problems.
+
+Given the previous, there is one first logical question: \emph{Can we come up
+  with a scheme that combines the utility of AC with the accountability of
+  GS?} But even then, we may run into a too rigid scheme. Thus, the follow-up
+question would be: \emph{Can we design this combined scheme, such that it covers
+a wide range of real world scenarios?}
+
+%% 2 pages max for the previous; end with introduction (1-2 sentences) to what
+%% would be ideal.
+
+% Contributions first a small paragraph with an overview. Then one titled
+% paragraph per contribution. Linking when possible with previous limitations.
+\subsection{Our Contributions}
+\label{ssec:contributions}
+
+In this work, we make our attempt on addressing both questions.
 

### 2022-05-10 prism-backend/research/gsac/uas.tex
Working on intro.

@@
   and accountability without losing (too much) privacy. Among the most relevant
-  efforts we can find group signatures and anonymous credentials.
+  efforts we can find group signatures (GS) and anonymous credentials (AC).
   %
-  Anonymous credentials (AC) let users obtain attestations by trusted
+  AC let users obtain attestations by trusted
   issuers on certain attributes -- thus implicitly defining the concept of
@@
   claims on these attributes. Indeed, this has proven to be very
-  flexible, to the point that it has served as inspiration to design W3C's
+  flexible, to the point that it inspired the design of W3C's
   Verifiable Credentials, a relevant industry-led effort. However, the
-  accountability offered by anonymous credentials is quite limited; frequently
-  restricted to blacklisting, if present at all.
+  accountability in AC schemes is quite limited; frequently restricted to
+  blacklisting, if present at all.
   %
-  On the other hand, group signatures (GS) have traditionally focused on plain
+  On the other hand, GS have traditionally focused on plain
   authentication without attributes (except very few exceptions), making instead
@@
 
-  We argue that, for the real world, both functionalities are essential. Taking
+  We argue that, in the real world, both functionalities are essential. Taking
   advantage of their similarities, we first propose a trivial combination, that
-  we refer to with the original \GSAC acronym. Through \GSAC, we
-  showcase the benefits of even a simple combination. We give a common syntax,
+  we refer to with the imaginative \GSAC acronym. Through \GSAC, we showcase
+  the benefits that even a simple combination brings. We give a common syntax,
   security model, and generic construction for \GSAC.
   %
-  Next, we acknowledge that even \GSAC has strong limitations. Namely, it is too
+  Next, we acknowledge that \GSAC has limitations. Namely, it is too
   strict in the rules one can apply during issuance of credentials, and signing
@@
   The techniques and building blocks we leverage are well known. The challenge
-  is, rather, on the definitional side.
+  is, rather, on the definitional side. To further evidence the universality of
+  \UAS, we show how more restricted schemes can be built from vanilla \UAS.
 \end{abstract}

### 2022-05-11 prism-backend/research/gsac/conclusion.tex
Intro and conclusions done. Revised abstract.

--- 2022-02-06 prism-backend/research/gsac/conclusion.tex
@@
 
-\comment{This section is just a placeholder for now...}
+In this work, we have described how a direct combination of the group signatures
+(GS) and anonymous credentials (AC) research lines results in a scheme that can
+bring benefit to real world use cases. Going further, we generalized such simple
+combination into Universal Anonymous Signatures, or \UAS. Our model for \UAS
+covers straight away a large subset of GS and AC variants, while still giving
+system designers the flexibility to decide on the specific tradeoff between
+privacy, utility, accountability and computational overhead that fits their
+setting best. More concretely, our model for \UAS supports arbitrary issuance
+policies, signature evaluation functions, and opening functions, without losing
+definitional meaning. We also gave a generic construction from well known
+building blocks, and prove that it meets our security model.
+
+Even though the generalization effort we do is significant, there are still
+ways to go further.
+%
+For instance, we do not hide the issuer(s) of the
+credential(s) employed to produce a signature (resp., request a new credential).
+Thus, we can only ensure privacy among signatures (resp., credential requests)
+that involve credentials issued by the same issuer set. While hiding the issuers
+of the involved credentials is certainly possible (we show how to do it at
+signing time, in order to build ring signatures), we argue that it may be
+desirable to leave it as is, at least, initially. The reason being that issuers
+are still what conveys trust to a system where credentials contain attributes
+attested by these issuers. Indeed, if it is already hard for verifiers to decide
+whether or not to trust an unanonymous issuer, one can imagine that it would be
+even harder to decide whether or not to trust an anonymous one. This question
+is core to the domain of trust registries \needcite, for instance.
+%
+A second desirable improvement, perhaps clearer from a technical point of view,
+is to extend our model to support non-trivial utility and accountability across
+multiple signatures from the same signer. More concretely, let our \feval and
+\finsp functions (and perhaps also \fissue?) operate on multiple signatures by
+the same \usk. That can lead to an extended \UAS scheme which would support
+advanced use cases such as rate limiting (or $k$-TAA \cite{asm06}); or might
+be even privately training an AI model based on one's authenticated
+past activity, and prove that the model has been trained honestly.
 

### 2022-05-11 prism-backend/research/gsac/introduction.tex
Intro and conclusions done. Revised abstract.

@@
 
-In this work, we make our attempt on addressing both questions.
+In this work, we make our attempt on addressing both questions. We start with a
+direct combination of GS and AC. While this does not pose many definitional nor
+technical challenges, it is a good exercise to showcase benefits obtained from
+even a simple combination. This directly answers in the affirmative our first
+question above. However, a direct combination does not address at all the
+flexibility that we aim at -- simply because it inherits the limitations of
+the vanilla GS and AC approaches we build on. Thus, we make an extra step with
+the goal to add such flexibility, spanning three diretions, allowing:
+
+\begin{itemize}
+\item Arbitrary issuance policies.
+\item Arbitrary signature evaluation functions.
+\item Arbitrary opening functions.
+\end{itemize}
+
+As we discuss next, this directly gives place to a scheme that can be seen as a
+strict generalization of many existing GS and AC schemes. To achieve it, we
+encounter some definitional challenges, although the result is a simple-enough
+model that still follows main practices of its GS and AC ancestors.
+Interestingly, despite the challenges for the modelling, we show a generic
+construction from well known building blocks.
+
+\paragraph{\GSAC: Direct combination of GS and AC.} %
+As stated, on the one hand GS lacks mechanisms to add useful identifying
+information associated to signers, but has well grounded mechanisms for
+accountability. On the other hand, AC is in the exact opposite situation. Thus,
+taking advantage of their frequently shared approaches, we merge them in an
+attempt to reach a scheme that is good in both aspects.
+
+In fact, taking this unifying path is a low hanging fruit if one looks at recent
+works. For instance, BBS+ signatures \cite{asm06,cdl16b} have been used recently
+to build both group signatures \cite{gl19,dl21,fgl21}, but are also one of the
+main candidates to incorporate anonymity into verifiable credentials%
+\footnote{``W3C Credential Exchange using BBS+ Signatures'',
+  \url{https://github.com/hyperledger/aries-rfcs/blob/main/features/0646-bbs-credentials/README.md}. Last access May 11th, 2020.}.%
+The interest of the verifiable credentials community in BBS+ is not accidental,
+though, as BBS+ follow the CL signatures line of work \cite{cl02}. CL signatures
+allow creating a single signature over a set of messages, which can be directly
+used to bundle a set of attributes (messages) into the same signature
+(credential). Indeed, this was the trigger for some of the first, and possibly
+the most fruitful branch of, anonymous credentials systems \cite{cl01,cl04}
+\needcite. Other very closely related signature scheme, PS16 \cite{ps16} can
+also be used to build group signatures, see \cite[Appendix A.1]{ps15} or
+\cite{cdl+20}; as well as anonymous credentials \cite[Appendix A.2]{ps15} or
+\cite{sms+19}.
+
+While GS and AC schemes share many internal aspects, they do differ in some,
+even beyond the obvious differences in functionality. In those cases, our
+approach is to adopt the one that seems more general.
+%
+For instance,
+anonymous credentials typically employ interactive credential presentations,
+meaning that a credential owner and a verifier run an interactive
+protocol by means of which the verifier gets convinced that the credential owner
+indeed owns a credential meeting some requirement defined in terms of the
+attributes it attests. On the other hand, in the GS domain, signing and
+verification are non-interactive processes. We follow the non-interactive
+approach, and then show how to trivially convert it into an interactive
+protocol.
+%
+Another difference lies in the fact that, in group signatures, each member gets
+only one membership credential, while in anonymous credentials, users can get
+arbitrarily many (different) credentials. This is natural, as in group
+signatures the only goal is to prove membership into a group and, thus, one
+credential is enough. But, in anonymous credentials, the same user can own
+multiple credentials (even from the same issuer), each attesting a different
+set of attributes. On this occasion, our logical decission is to lean towards
+anonymous credentials, as we aim at supporting arbitrarily many attributes per
+credential.
+
+An exception to this rule is that, in our modelling of \GSAC, we restrict to
+only one issuer and one credential per signature. This is not the most general
+choice, though, as in AC schemes it is frequent to assume a scenario with
+multiple issuers, and let users leverage multiple credentials in the same
+presentation. This is merely for definitional simplicity, and we ``fix'' it
+in \UAS.
+
+Additionally, within the AC domain, some works allow proving arbitrary claims
+over the attributes in a credential \needcite; while others simply allow
+selectively disclose subsets of these attributes. For \GSAC, we do the latter.
+Despite not being the most general option (although it is more general than the
+GS approach, as it does not even have attributes), it is enough to illustrate
+the advantages of unifying both worlds. Again, in \UAS we generalize this
+aspect.
+
+Finally, modelling-wise we also have two choices: follow a UC-based definition
+\needcite, or a game-based one \needcite. Independently on the pros and cons of
+each, in GS the standard is the game-based approach
+\cite{bmw03,bsz05,bcc+16,kty04,ky05}, although close relatives to GS, like DAA, prefer the
+UC approach \needcite. On the AC line of work, while some UC models exist
+\needcite, game-based definitions also seem prevalent \cite{fhs19} \needcite.
+Thus, the logical choice (at least, for a first step) seems to be game-based
+definitions. Concretely, we take strong inspiration from \cite{bsz05} for the
+GS branch, and from \cite{fhs19} for the AC one.
+
+\subsubsection{\UAS: Generalizing \GSAC.} %
+\GSAC is the first step towards achieving identity and authentication systems
+with both utility and accountability, yet it presents some limitations. Some we
+have already mentioned: it models a system with only one issuer, only allows
+using one credential to produce a signature, and only supports selective
+disclosure. We overview other limitations, that we address also with \UAS.
+
+\paragraph{Generalizing issuance protocols.} %
+In \GSAC, it is also not possible to leverage previously obtained credentials in
+order to obtain new ones -- from the same issuer, or from another. Note that, if
+we want to be really flexible, addressing this does not just mean letting the
+user specify a set of credentials in the interactive protocol for obtaining a
+new one. Concretely: What do we want to allow the user to prove with those extra
+credentials? This is essentially the same case as in interactive credential
+presentations. Thus, it seems reasonable to allow the same flexibility: namely,
+proving arbitrary claims over the attributes in the credentials involved in the
+request, without revealing them. We make only one exception, though: we do not
+include support to blindly carry attributes from one credential used in the
+request, to the new credential. This is indeed possible in some schemes
+\needcite. However, we argue that, by including support to merge multiple
+credentials into the same signature, this is no longer necessary. And indeed
+it is even realistic, as it does not make much sense to expect that an issuer
+attests an attribute that he cannot access in the clear (even despite it being
+attested by some other issuer). In any case, adding support to prove arbitrary
+claims at issuance time does introduce additional modelling needs. Namely, we
+need to give a generic predicate definition, say \fissue. Then, our model needs
+to make sure that, during the interactive issuance protocol, satisfaction of
+this predicate is ensured. This is not straightforward, though. One option is,
+as \cite{ckl+15} does for their issuance tokens, interpret that, if no
+illegitimately obtained credential is used to produce a signature, then this
+does no harm; so we only need to check at signature verification time that all
+involved credentials were legitimately obtained. However, this turns into a
+convoluted definition, which requires to mix claims of actions performed during
+credential issuance with actions performed during signing (credential
+presentation in \cite{ckl+15}). Instead, we opt for creating two separate
+unforgeability-related properties: one capturing security at issuance time, and
+another capturing security at signature creation time. Naturally, both require
+honest issuers, as we detail later on.
+
+\paragraph{Generalizing signature generation.} %
+Another generalization point is on the utility revealed at signing time. As
+stated, in \GSAC we restrict to selective disclosure. This is already a
+generalization with respect to GS, where this is not considered, possibly with
+the only exception of \cite{khad07a,khad07b,emo09,aa14}. These works on
+Attribute-Based Group Signatures (ABGS) are however too restricive:
+\cite{khad07a,khad07b,aa14} only consider fixed rules to apply over an
+attribute set in order to be able to create signatures (i.e., if a different
+ruleset is to be applied, a new group is needed). \cite{emo09} allows some
+alterations to previous rules, but instead require updates of the group public
+key, which is probably unacceptable in most situations. Instead of following the
+ABGS approach, we adopt the AC one, and simply require that the signer has to
+prove some arbitrary claim over the attributes in the credentials s/he uses to
+create a signature. This is thus orthogonal to group/issuer public key
+generation, which is what forces ABGS to update them every time a change in the
+rules takes place. Our approach to allow revealing arbitrary utility information
+at signing time is to let signers/verifiers decide on a \emph{signature
+  evaluation function}, \feval, which operates on the user secret key, the
+user credentials, and the signed message. This \feval function thus defines what
+verifiers (or third parties) will learn straight away from a valid signature.
+Note though that signing does not only reduce to simply computing (and proving)
+\feval's output. In addition, users have to prove that all the employed
+credentials are bound to the same user key, and that the opening information
+(more on this next) is also correct. This means that it is perfectly valid to
+define \feval functions that reveal absolutely nothing (e.g., always output
+$0$), and yet have a meaningful signing operation. Modelling-wise, this forces
+us to restrict that, in the anonymity property, the produced challenge
+signatures must produce the same \feval output, which may seem too strong,
+although it seems hard to avoid. The only alternative we find is actually a
+useful generalization, which is to formulate anonymity with a simulation-based
+approach. While still compatible with cases in which the output of \feval has
+the same in both challenge signatures, it additionally allows useful
+constructions in which the output of \feval is encrypted, e.g., under the
+opener's key. In this way, only the opener will learn it, when/if needed -- it
+removes utility at signing time, but gives more flexibility at opening time,
+without sacrificing privacy.
+
+\paragraph{Generalizing accountability.} %
+Finally, the last generalization point is on accountability. In \GSAC, we simply
+added conventional opening functionality of GS. Recent works have taken a next
+step towards generalizing this. For instance, in BiAS \cite{lnpy21}, the user
+learns on a per signature basis whether its signature will be deanonymizable or
+not, depending on whether a given policy (over the message, user identity, and
+some NP witness) is satisfied. This is even generalized further in MPS \needcite%
+\footnote{\textcolor{orange}{The MPS work and our \UAS generalization have been
+    simultaneously designed. Coincidentally, an early MPS draft came to our
+    knowledge as part of a peer-review process while we were working on \UAS.
+    Consequently, even though \UAS had already essentially been specified by
+    then, MPS has influenced our work, and an acknowledgement in that regard is
+    in order.}},
+where, somewhat like in \UAS, it is also possible to output any arbitrary
+function of the user identity. In \UAS, we define a function \finsp to govern
+what identifying information is revealed upon signature opening. There is one
+crucial difference, though. Both BiAS and MPS rely on a vaguely defined concept
+of ``identity''. That is, it
+is not clear how to interpret the fact that the output of a function depends
+on someone's identity, when this identity boils down to a member index or
+long-term public key. On more practical terms, it seems hard to avoid having
+to rely on yet extra third parties that vouch for extra identifying information
+associated to those member indexes or public keys; or to use the member
+indexes/public keys as labels to a somewhat publicly verifiable table with
+information about that user (which seems to go against privacy). Note that, by
+explicitly including \emph{meaningful} identifying information in the shape of
+attested attributes into the membership credentials (which \UAS inherits from
+its AC ancestor), producing an output that depends on the identity of the
+signer does have ``real-world'' meaning. We also note that our signature
+evaluation function has an equivalent in MPS, which also receives the signer's
+identity as a parameter. Therefore, the same rationale applies.
+%
+Yet another generalization on the accountability side is that, by adhering to
+the multiple issuer setting, the concept of group (very present in GS) gets
+blurred in \UAS. Somehow naturally, we also allow multiple openers and, what is
+more important in practical terms, there is no tight relation between issuer
+and opener. That is, a user who obtained a credential from issuer $I_A$, can use
+it to produce a signature which can be opened by opener $O_1$, and later use
+that same credential to produce another signature openable by opener $O_2$.
+Furthermore, while we define a syntax where only one opener is considered, the
+extension to multiple openers per signature is trivial (with the corresponding
+unavoidable loss in privacy).
+
+On the definitional side, incorporating this flexible opening policies leads to
+considering alternative definitions. This was already observed in prior GS works
+that do not rely on traditional opening \cite{gl19,dl21,fgl21}. These works
+follow the line of DAA, where a helper Identify function is added that formally
+allows to test whether a user (key) is indeed the signer behind a signature
+(necessary for traceability/unforgeability), or if it is not (necessary for
+non-frameability). This is however not enough in our case since, as we rely on
+further pieces of information to produce the utility and accountability outputs
+(concretely, the message and the identity of the signer; not just its signing
+key). Thus, we need to explicitly resort to extraction helper functions, as
+\cite{lnpy21}. Looking at our generic construction, this seems a natural choice,
+and easy to achieve via zero-knowledge proof of knowledge systems. However, it
+raises an interesting theoretical question of whether it is possible to
+build, or even model, systems like \UAS without relying on extraction.
+
+\paragraph{Universality of \UAS.} %
+As stated, a main goal of \UAS is to reach a general enough model that covers a
+large enough portion of the functionality modelled by previous GS and AC works,
+and even goes beyond (e.g., through the \fissue, \feval and \finsp functions).
+To showcase the universality of \UAS, we describe how, given a generic
+construction of \UAS, the \fissue, \feval, and \finsp functions can be used to
+come up with generic constructions of very well known schemes in the GS and AC
+domains. Directly, \UAS is a generalization of \GSAC, which we prove to be a
+strict generalization of vanilla GS and vanilla AC. Consequently, vanilla GS and
+AC are a strict subset of \UAS. We also show how to build MPS schemes \needcite
+which is on itself a generalization of BiAS \cite{lnpy21}; as well as group
+signatures with message-dependent opening \cite{ehk+19}, or delegatable
+anonymous credentials \needcite.
+%
+Interestingly, ``pure'' ring signatures \cite{rst06} can also be built from
+\UAS, where with ``pure'' we mean that \UAS-based ring signatures do not require
+an actual issuer -- i.e., users can act as issuers. This may even be suprising,
+given that we build on
+group signatures, where having no issuer of group credentials is just not
+possible\footnote{Nobatly, mimicking ring signatures without issuers is
+  trivially not possible in MPS, as its model does not support multiple
+  issuers. This seems crucial as, in essence, a ring signature is a group
+  signature where every user can become an issuer.}. Moreover, the
+unforgeability notion, that requires trust on the issuer in the setting of group
+signatures, is still applicable here, as long as the verifier trusts all
+the public keys involved in the \UAS-based ring signature (just the same
+as in conventional ring signatures). \todo{Although, on this regard, it is
+  interesting to explore how attributes come into the picture.}
+
+\subsubsection{Is the extra overhead reasonable?} %
+Finally, a logical question to ask, of the utmost pratical relevance and
+especially given the generalization points we include, is whether all this
+overhead is worthy, or even acceptable, in the real world. Obviously, without
+concrete instantiations all we can do is abstractly argue about this. In this
+regard, we make an important observation, though: the \UAS model we propose is
+meaningful even when defining \fissue, \feval and \finsp to be the trivial
+issuance, signature evaluation, and opening functions. More concretely, one
+perfectly can: (1) set \fissue to return always $1$, implying that no extra
+constrain is placed on the credentials used to request a new one; (2) define
+\feval to be a constant function, meaning that no signature reveals any
+identifying information on its signer; and (3), let \finsp always return the
+user's public key, as in conventional group signatures; or also a constant
+function, meaning that no revocation is possible. Even in those cases, we reach
+a scheme that may be suitable for certain scenarios, as it would basically be
+a vanilla GS or AC scheme, or GSAC, with similar computational costs.
+This means that a system designer that builds on an \UAS scheme can apply
+whatever tradeoff between privacy, utility, accountability, and extra costs
+is most suitable to his setting, without the need to model everything from
+scratch if the need to tweak something arises.
 

### 2022-05-11 prism-backend/research/gsac/uas.tex
Intro and conclusions done. Revised abstract.

@@
 
+\setcounter{tocdepth}{2}
+
 \title{Universal Anonymous Signatures}
-\author{}
+\author{Jesus Diaz\inst{1} \and Markulf Kohlweiss\inst{2}}
+
+\institute{Input Output Global,\\
+\email{jesus.diazvico@iohk.io},\\
+\and
+Input Output Global and University of Edinburgh,\\
+\email{markulf.kohlweiss@ed.ac.uk}}
 
@@
 \begin{document}
-\maketitle
+{\def\addcontentsline#1#2#3{}\maketitle}%\maketitle
 
@@
   identity as ``a set of attributes'' -- and allow credential owners to prove
-  claims on these attributes. Indeed, this has proven to be very
-  flexible, to the point that it inspired the design of W3C's
-  Verifiable Credentials, a relevant industry-led effort. However, the
-  accountability in AC schemes is quite limited; frequently restricted to
-  blacklisting, if present at all.
+  claims on these attributes. While this has proven to be very
+  flexible, accountability in AC schemes is quite limited; frequently restricted
+  to blacklisting, if present at all.
   %
-  On the other hand, GS have traditionally focused on plain
-  authentication without attributes (except very few exceptions), making instead
-  more emphasis on the accountability side. That is, not only allowing full
+  On the other hand, GS have traditionally focused on plain authentication
+  without attributes, making instead more emphasis on the accountability side.
+  That is, not only allowing full
   deanonymization, but also variants such as sequential linking, user-controlled
@@
   We argue that, in the real world, both functionalities are essential. Taking
-  advantage of their similarities, we first propose a trivial combination, that
-  we refer to with the imaginative \GSAC acronym. Through \GSAC, we showcase
-  the benefits that even a simple combination brings. We give a common syntax,
-  security model, and generic construction for \GSAC.
+  advantage of their similarities, we first propose a trivial combination,
+  \GSAC, showcasing the benefits even a simple combination brings. We give a
+  common syntax, security model, and generic construction for \GSAC.
   %
-  Next, we acknowledge that \GSAC has limitations. Namely, it is too
-  strict in the rules one can apply during issuance of credentials, and signing
-  and opening of the produced signatures. While generalizations along these
+  Next, we generalize \GSAC into our Universal Anonymous Signatures (\UAS)
+  proposal by allowing arbitrary policies at issuance, signing and opening
+  time, among other improvements. While generalizations along these
   lines have been explored independently in the GS and AC domains, to the best
-  of our knowledge, no single scheme offers full flexibility.
-  We define a syntax, security model, and give a generic
-  construction for a scheme meeting these requirements. Given its high
-  flexibility to cater for different needs, we name it Universal Anonymous
-  Signatures (\UAS). Indeed, an \UAS scheme lets issuers decide on issuance
-  policies, which easily enable advanced use cases such as delegation, or
-  issuance conditioned identity-related claims. It can also be used to build
-  schemes that allow signers prove arbitrary claims on their identities, as well
-  as deciding on which should be the opening authority that can apply some
-  commonly agreed deanonymization function over the signer's identity (which is
-  now well-defined, given the incorporation of attributes from the AC domain).
+  of our knowledge, no single scheme offers such full flexibility.
+  We define a syntax, security model, and give a generic construction for a
+  scheme meeting these requirements. Furthermore, we show how our model for
+  \UAS is a generalization of previous well known schemes in the GS and AC
+  domains.
   %
@@
 
+\tableofcontents
+
 \input{introduction.tex}
@@
 \input{sec-uas.tex}
-\input{benchmarks.tex}
+%\input{benchmarks.tex}
 \input{conclusion.tex}

### 2022-05-12 prism-backend/research/gsac/app-gsac.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

@@
 
-\todo{Need to update the proofs with the updated definitions, now returning
-  \attrs as part of \Open.}
-
-\commentwho{Jesus}{Strictly, in our generic construction we require IND-CCA, but
+\jdv{Strictly, in our generic construction we require IND-CCA, but
   in the following concrete instantiation, we use ElGamal, which is IND-CPA.
   However, we actually ``lift'' ElGamal with NIZKs of the encrypted plaintexts,
-  which is essentially IND-CCA as far as I know. Still, make sure to mention
-  that.}
+  but this not may be enough. Check and look for alternatives if not good.}
 
 \begin{proof}[\thmref{thm:correctness-gsac}; Correctness of \GSACGen]
-  \todo{XXX}
+  By correctness of \SBCM and the NIZK for $\NIZKRel^{\Issue}$, an honestly
+  obtained credential \cid, from an honest issuer, is a valid \SBCM signature
+  over
+  attribute set $\ATTR[\cid]$, associated to the user key of some honest user
+  which, by convention, we denote with $\OWNR[\cid]$ -- thus, the secret key
+  bound to the credential is $\PRVUK[\OWNR[\cid]]=\usk$. Since, at line 3 of the
+  \ExpGSACCorrect game the environment checks that the \dattrs set output by
+  $\adv$ is contained within the chosen credential \cid, again by correctness of
+  \SBCM, the encryption scheme, and correctness of the NIZK for
+  $\NIZKRel_{\Sign}$, \Sign succeeds with overwhelming
+  probability, and \sig contains an encryption, under \opk, of $\ATTR[\cid]$,
+  and due to correctness of the commitment scheme \C, also of $\upk =
+  \CCommit(\usk;0)$. Additionally, correctness of the NIZK for
+  $\NIZKRel_{\Open}$ ensures that \Open is able to decrypt them back into \upk,
+  and that $\attrs=
+  \ATTR[\cid]$, respectively. Finally, correctness of the NIZK for
+  $\NIZKRel_{\Sign}$ and the NIZK for $\NIZKRel_{\Open}$ ensure that \Verify and
+  \Judge accept the signature and opening proof, respectively, with overwhelming
+  probability.
 \end{proof}
@@
 Outputs $\osk \gets \ZZ^*_p$, and $\opk \gets \gen{g}^{\osk}$. This is the
-opener's ElGamal encryption key pair \needcite.
+opener's ElGamal encryption key pair.
 
@@
 Outputs $\usk \gets \ZZ^*_p$, and $\upk \gets \gen{h}_1^{\usk}$. \upk will
-simply be used to compute Pedersen commitments \needcite to \usk. However,
+simply be used to compute Pedersen commitments to \usk. However,
 it is useful to precompute it, and we treat it as a sort of ``public key''.

### 2022-05-12 prism-backend/research/gsac/extensions-gsac.tex
Added high-level descriptions of how to build other schemes from UAS.
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

@@
 uniformly at random from an appropriate domain, which must be concatenated to
-the signed message. We sketch a proof for why does this result in a secure
+the signed message. If there is no need to actually sign a message, then the
+message is set to an empty string, and the user only signs the random number.
+%
+Syntactically, instead of having non-interactive $\sig \gets \Sign(\gpk,\usk,
+\cred,\dattrs,\msg)$ and $1/0 \gets \Verify(\gpk,\sig,\dattrs,\msg)$ algorithms,
+we have a $1/0 \gets \langle \Sign(\gpk,\usk,\cred,\dattrs),\Verify(\gpk,
+\dattrs) \rangle$ interactive protocol.
+%
+We sketch a proof for why does this result in a secure
 \GSAC scheme with interactive signing and verification in
@@
 
-\todo{Can we do formal proofs here of $GSAC \implies$ GS and $GSAC \implies AC$?}
+\jdv{Can we do formal proofs here of $GSAC \implies$ GS and $GSAC \implies AC$?}
 

### 2022-05-12 prism-backend/research/gsac/introduction.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

@@
 Successful identity representation, management, and usage are, on its own, among
-the toughest problems in the Internet and digital communications at large
-\needcite. Just as an illustration, think
+the toughest problems in the Internet and digital communications at large%
+\footnote{``Digital identity is one of the 21st century's biggest challenges'':
+  \url{https://www.maddyness.com/uk/2021/11/04/digital-identity-is-one-of-the-21st-centurys-biggest-challenges/}. Last access, May 12th, 2022.}.
+Just as an illustration, think
 of usernames and passwords, which end up being unmanageable as soon as we need
-to start remembering a few \needcite; or traditional vertical PKIs, like X.509,
-which are too rigid, and frequently require too much trust \needcite; or
-horizontal PKIs, such as PGP, that are also too rigid, and do not scale well
-\needcite. If, in addition, we require privacy, the scenario becomes even more
-challenging. Technologies like OpenID and OAuth \needcite make identity more
+to start remembering a few%
+\footnote{``The problem of passwords and how to deal with it'': \url{https://www.computerweekly.com/feature/The-problem-of-passwords-and-how-to-deal-with-it}. Last access,
+May 12th, 2022.}; or traditional vertical PKIs, like X.509 \cite{rfc5280},
+which are too rigid, and frequently require too much trust; or
+horizontal PKIs, such as PGP, that are also too rigid, and are hard to manage
+and scale\footnote{``What's the matter with PGP?'': \url{https://blog.cryptographyengineering.com/2014/08/13/whats-matter-with-pgp/}. Last access, May 12th, 2022}.
+If, in addition, we require privacy, the scenario becomes even more
+challenging. Technologies like OpenID\footnote{\url{https://openid.net/}. Last
+  access, May 12th, 2022.} and OAuth\footnote{\url{https://oauth.net/}. Last
+  access, May 12th, 2022.} make identity more
 manageable (from the point of view of service providers) through Single Sign
@@
 fully deanonymize, but incorporate some other strict tradeoff. Like giving the
-users full control \cite{dl21}, only allowing linking \needcite, or some
+users full control \cite{dl21}, only allowing de-anonymization based on the
+signed message \cite{ehk+19}, or some
 arbitrary extension such as allowing deanonymization only to the eyes of other
-group members \needcite, or sequential linkability \cite{dl21}. While these
+group members \cite{manu06}, or sequential linkability \cite{dl21}. While these
 variants may be very suitable for concrete settings, it is not hard to see that
@@
 (credential). Indeed, this was the trigger for some of the first, and possibly
-the most fruitful branch of, anonymous credentials systems \cite{cl01,cl04}
-\needcite. Other very closely related signature scheme, PS16 \cite{ps16} can
+the most fruitful branch of, anonymous credentials systems (see
+\cite{cl01,cl02,cl04}, among others). Other very closely related signature
+scheme, PS16 \cite{ps16} can
 also be used to build group signatures, see \cite[Appendix A.1]{ps15} or
@@
 Additionally, within the AC domain, some works allow proving arbitrary claims
-over the attributes in a credential \needcite; while others simply allow
+over the attributes in a credential \cite{bcc+09,cklm14,dmm+18,fhs19}; while
+others simply allow to
 selectively disclose subsets of these attributes. For \GSAC, we do the latter.
@@
 Finally, modelling-wise we also have two choices: follow a UC-based definition
-\needcite, or a game-based one \needcite. Independently on the pros and cons of
-each, in GS the standard is the game-based approach
-\cite{bmw03,bsz05,bcc+16,kty04,ky05}, although close relatives to GS, like DAA, prefer the
-UC approach \needcite. On the AC line of work, while some UC models exist
-\needcite, game-based definitions also seem prevalent \cite{fhs19} \needcite.
+\cite{cane20}, or a game-based one \cite{shoup04}. Independently on the pros and
+cons of each, in GS the standard is the game-based approach
+\cite{bmw03,bsz05,bcc+16,kty04,ky05}, although close relatives to GS, like DAA,
+prefer the UC approach \cite{cdl16,cdl16b,ccd+17,cdl17}. On the AC line of work,
+while some UC models exist \cite{}, game-based definitions also seem prevalent
+\cite{bcc+09,cks10,cl11,cklm12,cmz14,dmm+18,fhs19}.
 Thus, the logical choice (at least, for a first step) seems to be game-based
@@
 request, to the new credential. This is indeed possible in some schemes
-\needcite. However, we argue that, by including support to merge multiple
+\cite{bcl04}. However, we argue that, by including support to merge multiple
 credentials into the same signature, this is no longer necessary. And indeed
@@
 signatures with message-dependent opening \cite{ehk+19}, or delegatable
-anonymous credentials \needcite.
+anonymous credentials \cite{bcc+09,cklm14}.
 %
@@
 the public keys involved in the \UAS-based ring signature (just the same
-as in conventional ring signatures). \todo{Although, on this regard, it is
+as in conventional ring signatures). \jdv{Although, on this regard, it is
   interesting to explore how attributes come into the picture.}

### 2022-05-12 prism-backend/research/gsac/model-uas.tex
Updated GSAC and UAS proofs based on updated non-frame definiton.
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

@@
 employed in each signature will be defined by the verifier (or jointly between
-user and verifier), including the specification of which inspector will be
+user and verifier), including the specification of which opener will be
 able to post-process signatures\footnote{See, for instance, the concept of
@@
   over message \msg, from a user with credentials issued by issuers with public
-  keys $\ipk_i$, for evaluation function \feval and inspector key \opk.
+  keys $\ipk_i$, for evaluation function \feval and opener key \opk.
 \item[$(\yinsp,\iproof)/\bot \gets \Open(\osk,\lbrace \ipk_i
@@
 on user-private data). Also, in all cases, the user has to prove correctness of
-their computation. We introduce them next, \todo{and will give concrete examples
-  in \secref{sec:uas-instantiation}.}
+their computation. We introduce them next, and give concrete examples for
+building specific well-known restrictions of \UAS in
+\secref{sec:transformations}.
 
@@
 We emphasize that, even though \finsp and \feval seem redundant, they are not.
-To see this, observe that \finsp is defined by inspectors, and will be fixed in
+To see this, observe that \finsp is defined by openers, and will be fixed in
 all signatures that can be opened by the opener who defined it. On the other
@@
 rewind the game, or program random oracles. The approach needs thus to depend on
-the concrete construction. \todo{Although, for the case of \ExtractIssue,
-online extractability \needcite (or alternative requirements, such as
-non-parallel or logarithmic number of joins) is necessary.}
+the concrete construction. \jdv{Although, for the case of \ExtractIssue,
+  online extractability (or alternative requirements, such as non-parallel or
+  logarithmic number of joins) is necessary.}
 
@@
   the associated issuance function.
-\item[\OGEN.] Adds a new inspector to the game, generating its key pair and
+\item[\OGEN.] Adds a new opener to the game, generating its key pair and
   setting the associated evaluation and inspection functions.
@@
   key to the adversary.
-\item[\OCORR.] Corrupts an existing (and honest) inspector, by giving its secret
+\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
   key to the adversary.  
@@
     \caption{Detailed oracles available in our model (1/2). Oracles for
-      generating key material for users, issuers, and inspectors.}
+      generating key material for users, issuers, and openers.}
     \label{fig:oracles1}
@@
           (\yinsp,\iproof) \gets
-          \Inspect(\PRVOK[\oid],\GK[\scid],\sig,\yeval,\msg,\feval) \\
+          \Open(\PRVOK[\oid],\GK[\scid],\sig,\yeval,\msg,\feval) \\
           \pcif \CSIG[\sig] \neq \bot: \\
@@
           \pcind (\yinsp',\iproof') \gets
-          \Inspect(\PRVOK[\oid],\IK[\siid],\\
+          \Open(\PRVOK[\oid],\IK[\siid],\\
           \hspace*{107pt} \sig_{1-b},\msg,\feval) \\
@@
 \begin{figure}[htp!]
-  \procedure{$\ExpCorrect(1^\secpar)$}{%
+  \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
@@
     \pcif \feval(\UK[\uid],\CRED[\scid],\msg) \neq \yeval: \pcreturn 1 \\
-    (\yinsp,\iproof) \gets \Inspect(\PRVOK[\gid],\PUBIK[\scid],\sig,\msg,\feval) \\
+    (\yinsp,\iproof) \gets \Open(\PRVOK[\gid],\PUBIK[\scid],\sig,\msg,\feval) \\
     \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\y,\iproof,\sig,\yeval,\msg,\feval)
@@
 our model to cover interesting use cases -- such as restricting to selective
-disclosure, or privacy-preserving variants of functional signatures \todo{check
+disclosure, or privacy-preserving variants of functional signatures \jdv{check
   the latter, and perhaps expand}.
@@
       \pcreturn 0 \\
-      (\yinsp,\iproof) \gets \Inspect(\PRVOK[\oid],\siid,\sig,\yeval,\msg) \\
+      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\sig,\yeval,\msg) \\
       \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg,\feval)
@@
 Non-frameability variants are a core unforgeability-type property in group
-signatures. However, no similar property is modeled for anonymous credentials
-(\todo{see the discussion in \secref{sec:introduction} for further detail. Also,
-consider conditional anonymity notions pointed to by Elizabeth}). It is a quite
-strong property, as it must be ensured even in the presence of dishonest issuer
-and opener. Intuitively, it prevents the adversary from creating a signature
-that can be (even in some generic sense) associated to an honest user who did
-not produce it. Depending on the opening capabilities of the scheme,
-this framing could be done in different ways; i.e., by convincing third parties
-that signatures by different (possibly corrupt) users are linked, or directly
-by having opening proofs output the identity of a user who did not create the
-signature being opened.
+signatures. However, no similar property is modeled for anonymous credentials.
+It is a quite strong property, as it must be ensured even in the presence of
+dishonest issuer and opener. Intuitively, it prevents the adversary from
+creating a signature that can be (even in some generic sense) associated to an
+honest user who did not produce it. Depending on the opening capabilities of the
+scheme, this framing could be done in different ways; i.e., by convincing third
+parties that signatures by different (possibly corrupt) users are linked, or
+directly by having opening proofs output the identity of a user who did not
+create the signature being opened.
 
@@
     \adv^{\Oframe}(\parm) \\
-    \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in \SIG[\uid]:
-    \pcreturn 0 \\
+%    \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in \SIG[\uid]:
+%    \pcreturn 0 \\
     \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\yeval,\msg,\feval) = 0:
@@
     \ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \\
-    \pcif \exists \uid \in \HU~\st~\UK[\uid] = \usk: \pcreturn 1 \\
+    \pcif \exists \uid \in \HU~\st~\UK[\uid] = \usk~\land \\
+    \pcind (\nexists (\cdot,\cdot,\sig,\yeval,\msg,\feval) \in \SIG[\uid]
+    \lor \yinsp \neq \yinsp'): \pcreturn 1 \\
     \pcreturn 0

### 2022-05-12 prism-backend/research/gsac/preliminaries.tex
Working on intro.
Intro and conclusions done. Revised abstract.
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

@@
-{Preliminaries}
+\section{Preliminaries}
 \label{sec:preliminaries}
 
+\iffalse
 \subsection{Related Work}
@@
 % considered as a different user).
+\fi
 
@@
 \paragraph{Digital Signatures.} %
-Defined as a tuple $(\SSetup,\SKeyGen,\SSign,\SVerify)$. Algorithm $\Sparm \gets
-\SSetup(\Ssecpar)$ produces public parameters for the other algorithms.
-$(\Svk,\Ssk) \gets \SKeyGen(\Sparm)$ generates the verification-signing key
-pair, algorithm $\Ssig \gets \SSign(\Ssk,\msg)$ signs message \msg with
-signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\Svk,
-\Ssig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
+Defined as a tuple (\SSetup,\SKeyGen,\SSign,\SVerify). Algorithm $\parm \gets
+\SSetup(\secpar)$ produces public parameters for the other algorithms.
+$(\vk,\sk) \gets \SKeyGen(\parm)$ generates the verification-signing key
+pair, algorithm $\sig \gets \SSign(\sk,\msg)$ signs message \msg with
+signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\vk,
+\sig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
 verification key \Svk. We rely on existentially unforgeable digital signature
@@
 \paragraph{Public-Key Encryption.} %
-Defined as a tuple $(\ESetup,\EKeyGen,\EEnc,\EDec)$. Algorithm $\Eparm \gets
-\ESetup(\Esecpar)$ produces public parameters for the other algorithms.
-$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$ generates the encryption-decryption key
-pair, algorithm $\Ec \gets \EEnc(\Eek,\msg)$ encrypts message \msg with
-encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\Edk,
+Defined as a tuple (\ESetup,\EKeyGen,\EEnc,\EDec). Algorithm $\parm \gets
+\ESetup(\secpar)$ produces public parameters for the other algorithms.
+$(\ek,\dk) \gets \EKeyGen(\parm)$ generates the encryption-decryption key
+pair, algorithm $\Ec \gets \EEnc(\ek,\msg)$ encrypts message \msg with
+encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\dk,
 \Ec)$ decrypts ciphertexts using decryption key \Edk. We rely on IND-CCA
@@
 
-\paragraph{(Vector) Commitment Schemes.} %
-Defined as a tuple $(\CSetup,\CCommit)$. Algorithm $\Cparm \gets
-\CSetup(\Csecpar)$ produces the parameters for committing to values. $\Ccom
-\gets \CCommit(\Cparm, \smsg; r)$ produces a commitment \Ccom over a set of
+\paragraph{(Block) Commitment Schemes.} %
+Defined as a tuple (\CSetup,\CCommit). Algorithm $\parm \gets
+\CSetup(\secpar)$ produces the parameters for committing to values. $\Ccom
+\gets \CCommit(\parm, \smsg; r)$ produces a commitment \Ccom over a set of
 messages \smsg, using randomness $r$ (which we may omit when explicitly
@@
 allow committing to vectors of messages. Therein, the \CCommit algorithm simply
-receives a vector of messages. In both cases, we require hiding and binding
-(vector) commitment schemes.
-
-\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
-We use signature schemes that allow signing blocks of messages, or commitments
-to blocks of messages, and which are furthermore compatible with (efficient)
-proof systems over the produced signature and signed (commitments to) messages.
-For this purpose, we define such schemes as a tuple $(\SBCMSetup,\SBCMKeyGen,
-\SBCMCom,\SBCMSign,\SBCMVerify)$. Algorithm $\SBCMparm \gets
-\SBCMSetup(\SBCMsecpar)$ produces the public parameters for the scheme.
-$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$ produces a verification-signing
-key pair. $\SBCMsig/\bot \gets\langle \SBCMCom(\SBCMvk,\overline{smsg},\smsg),
-\SBCMSign(\SBCMsk,\smsg) \rangle$ is an interactive protocol between a user, who
-runs \SBCMCom and has a set of messages $\overline{\smsg}$ to be block-committed,
-and a signer, who owns signing key \SBCMsk; both also receive common input a
-block of messages \smsg. The output of the protocol is a signature over
-$\overline{\smsg} \cup \smsg$. Algorithm $1/0 \gets \SBCMVerify(\SBCMvk,
-\SBCMsig,\widetilde{\smsg})$ verifies a signature \SBCMsig over message set
-$\widetilde{\smsg}$, which must contain both the messages that were signed as
-a block commitment as well as those signed in ``the clear''. In addition, the
-produced signatures must be compatible with (efficient) NIZK proofs of knowledge
-of a signature, and of (arbitrary) claims over the signed (committed) messages.
-An \SBCM scheme must provide \todo{one-more-forgery} type of security.
+receives a block of messages. In both cases, we require hiding and binding
+(block) commitment schemes.
 
@@
 model. Informally, a NIZK scheme over an NP relation \NIZKRel is defined as a
-tuple $(\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel,\NIZKVerify^\NIZKRel)$.
-Algorithm $\NIZKcrs \gets \NIZKSetup^\NIZKRel(\NIZKsecpar)$ produces the common
-reference string \NIZKcrs. $\NIZKproof/\bot \gets \NIZKProve^\NIZKRel(\NIZKcrs,
+tuple ($\NIZKSetupRel$,$\NIZKProveRel$,$\NIZKVerify^\NIZKRel$).
+Algorithm $\NIZKcrs \gets \NIZKSetupRel(\NIZKsecpar)$ produces the common
+reference string \NIZKcrs. $\NIZKproof/\bot \gets \NIZKProveRel(\NIZKcrs,
 \NIZKx,\NIZKw)$ creates a NIZK proof of knowledge of witness \NIZKw for \NIZKx
-such that $(\NIZKw,\NIZKx) \in \NIZKRel$. $1/0 \gets \NIZKVerify^\NIZKRel
+such that $(\NIZKw,\NIZKx) \in \NIZKRel$. $1/0 \gets \NIZKVerifyRel
 (\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof. Within NIZK systems, we
@@
 
+\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
+We use signature schemes that allow signing blocks of messages, or commitments
+to blocks of messages, and which are furthermore compatible with (efficient)
+proof systems over the produced signature and signed (commitments to) messages.
+For this purpose, we define such schemes as a tuple (\SBCMSetup,\SBCMKeyGen,
+\SBCMCom,\SBCMSign,\SBCMVerify). Algorithm $\parm \gets \SBCMSetup(\secpar)$
+produces the public parameters for the scheme.
+$(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing
+key pair. $\\sig/\bot \gets\langle \SBCMCom(\vk,\overline{\smsg},\smsg),
+  \SBCMSign(\sk,\smsg) \rangle$ is an interactive protocol between a user, who
+runs \SBCMCom and has a set of messages $\overline{\smsg}$ to be block-committed,
+and a signer, who owns signing key \SBCMsk; both also receive common input a
+block of messages \smsg. The output of the protocol is a signature over
+$\overline{\smsg} \cup \smsg$. Algorithm $1/0 \gets \SBCMVerify(\vk,
+\sig,\overline{\smsg},\smsg)$ verifies a signature \SBCMsig over message set
+$\overline{\smsg} \cup \smsg$. In addition, the
+produced signatures must be compatible with (efficient) NIZK proofs of knowledge
+of a signature, and of (arbitrary) claims over the signed (committed) messages.
+An \SBCM scheme must provide one-more-forgery type of security.
+
 \subsection{Notation}
@@
 
-\todo{Attribute space. Used in generic construction of GSAC for now. Define it
-  to be the set of bitstrings of some length.}
+We use common notation habits. $y \gets A(x)$ means that algorithm $A$, on input
+$x$, produces output $y$. When $A$ is a probabilistic process, and we want to
+make explicit the randomness $r$, we use $y \gets A(x;r)$. $\langle y_A,y_B \gets
+\langle A(x_A),B(x_B)\rangle$ denotes algorithms $A$ and $B$, running an
+interactive protocol, where $A$ receives $x_A$ as input and produces $y_A$ as
+output, and $B$ receives $x_B$ and produces $y_B$.
+%
+Our generic constructions
+rely on the previously defined building blocks, which share common (but different
+tokens): e.g., we will resort to several NIZK proofs instances. To distinguish
+them, we may use subscripts or superscripts: e.g., $\NIZKRel_A$ denotes the
+NP relation used within some algorithm $A$, $\NIZKSetupRel$ means that
+the setup algorithm of an underlying NIZK system is performed associated to
+relation $\NIZKRel$; $\SBCMparm$ are the public parameters for an \SBCM scheme,
+and $\Eparm$ are the public parameters for an encryption scheme. Variables
+written in bold font denote sets, e.g., while we use \ipk to denote a single
+issuer public key, \sipk denotes a set of issuer's public keys.
+%
+We also assume the existence of a well defined attribute space over which
+issuers in our schemes can issue credentials on. We denote this set with
+\AttrSpace.
 
-\todo{\attrs and \dattrs (in \secref{ssec:construction-gsac}, they are treated
-  as indices, but I think that's not the case elsewhere).}
+% \todo{Attribute space. Used in generic construction of GSAC for now. Define it
+%   to be the set of bitstrings of some length.}
 
-\todo{In \secref{ssec:construction-gsac}, we assume that all messages and
-  attributes can be encoded as elements in $\ZZ^*_p$.}
+% \todo{\attrs and \dattrs (in \secref{ssec:construction-gsac}, they are treated
+%   as indices, but I think that's not the case elsewhere).}
 
-\todo{In \secref{ssec:generic-construction-uas} we use $\usk \in \cred$ to
-  denote the claim ``\usk is an attribute attested in \cred''.}
+% \todo{In \secref{ssec:construction-gsac}, we assume that all messages and
+%   attributes can be encoded as elements in $\ZZ^*_p$.}
 
-\todo{In GSAC traceability proof, we use $\negl(\cdot)$ to denote negligible
-  functions.}
+% \todo{In \secref{ssec:generic-construction-uas} we use $\usk \in \cred$ to
+%   denote the claim ``\usk is an attribute attested in \cred''.}
+
+% \todo{In GSAC traceability proof, we use $\negl(\cdot)$ to denote negligible
+%   functions.}
 

### 2022-05-12 prism-backend/research/gsac/sec-gsac.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

@@
 \label{sec:gsac}
-
-\todo{I think we should extend ``vanilla'' \GSAC to return the full \attrs
-  in \Open, but without needing \trans as a parameter to \Open (for compatibility
-  with \UAS). This can be done by encrypting all attributes, including their
-  ciphertext in the signature, and proving they are part of the credential. This
-  would render the scheme too costly, but helps in arguing in favour of \UAS.
-  Still, leaving that for after having updated the \UAS section, to see how
-  it fits the global picture.}
 

### 2022-05-12 prism-backend/research/gsac/sec-uas.tex
Added high-level descriptions of how to build other schemes from UAS.
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

@@
 in generalized variants of anonymous credentials), as well as multiple openers,
-each one with a predefined inspection function. Thus, it supports use cases like
+each one with a predefined open function. Thus, it supports use cases like
 having a user produce a signature with credentials obtained from issuers A and
@@
 \input{security-uas.tex}
+\input{transformations-uas.tex}
 

### 2022-05-12 prism-backend/research/gsac/security-gsac.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

@@
   \label{thm:correctness-gsac}
-  If the underlying schemes for \todo{xxx}, our generic construction \GSACGen
+  If the underlying \SBCM, encryption, and commitment schemes are correct, and
+  the NIZK systems for $NIZKRel_{\Issue}$, $NIZKRel_{\Sign}$, and $NIZKRel_{\Open}$
+  are also correct, our generic construction \GSACGen
   satisfies correctness as defined in \defref{def:correctness-gsac}.
@@
   \label{thm:frame-gsac}
-  If the scheme for $\NIZK^{\Issue}$ is zero-knowledge, the scheme for
-  $\NIZK^{\Sign}$ is zero-knowledge and sound, the scheme for $\NIZK^{\Open}$ is
+  If the NIZK schemes for $\NIZKRel_{\Issue}$ is zero-knowledge, the scheme for
+  $\NIZKRel_{\Sign}$ is zero-knowledge and sound, the scheme for $\NIZKRel_{\Open}$ is
   sound, and the commitment scheme \C is hiding, then our generic \GSACGen

### 2022-05-12 prism-backend/research/gsac/security-uas.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

@@
   \label{thm:correctness-uas}
-  If the underlying schemes for vector commitments, encryption, digital
-  signatures, signatures on blocks of committed messages, and NIZKs are
-  correct, our generic construction \CUASGen satisfies correctness as
+  If the underlying schemes for commitments, encryption and \SBCM, are correct,
+  as well as the NIZKs for $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
+  $\NIZKRel_{\Open}$, our generic construction \CUASGen satisfies correctness as
   defined in \defref{def:correctness-uas}.
@@
 \begin{proof}[\thmref{thm:correctness-uas}; Correctness of \CUASGen]
-  \todo{XXX}
+  By correctness of \SBCM and the NIZK for $\NIZKRel_{\Sign}$, the signature
+  produced at line 5 of \ExpCorrect is accepted at line 6 by \Verify.
+  Moreover, all the credentials employed to honestly produce the signature,
+  identified with \scid, meet their respective issuance policies due to
+  correctness of the NIZK for $\NIZKRel_{\Issue}$, so no $\fissue^\cid$ check
+  returns $0$ at line 9. Similarly, as $\feval \in \famfeval$ is checked at
+  line 3, and due to correctness of the NIZK for $\NIZKRel_{\Sign}$, the
+  output of \feval matches \yeval at line $10$, which is furthermore computed
+  over $\usk=\UK[\uid]$ due to correctness of the commitment scheme. Finally,
+  correctness of the NIZKs for $\NIZKRel_{\Sign}$ and $\NIZKRel_{\Open}$, and
+  correctness of the encryption scheme, ensure that \Judge accepts the proof
+  produced by \Open, and \yinsp is the correct value for the chosen
+  $\finsp^{\oid}$.
 \end{proof}
@@
   If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is zero-knowledge, sound,
-  and simulation extractable, the NIZK scheme for $\NIZKRel_{\Inspect}$ is sound
+  and simulation extractable, the NIZK scheme for $\NIZKRel_{\Open}$ is sound
   and simulation extractable, and \SBCM is one-more unforgeable, then our
@@
   Similarly, $\adv$ wins at step 9 if (1) $\finsp(\yeval,\usk,\scred,\msg) \neq
-  \yinsp$, where \yinsp is the value output by \Inspect at line 5; or if (2)
+  \yinsp$, where \yinsp is the value output by \Open at line 5; or if (2)
   $\yinsp \neq \yinsp'$, where $\yinsp'$ is the value extracted by \ExtractSign
   at step 7. For (1), soundness of $\NIZK^{\Sign}$ ensures that \yinsp is the
-  correct evaluation of \finsp, whereas soundness of $\NIZK^{\Inspect}$ and
+  correct evaluation of \finsp, whereas soundness of $\NIZK^{\Open}$ and
   correctness of the public key encryption ensure that this is also the value
-  output by \Inspect. Thus, the probability of $\adv$ winning the game because
+  output by \Open. Thus, the probability of $\adv$ winning the game because
   of (1) is negligible. Finally, for (2), simulation-extractability of
-  $\NIZK^{\Inspect}$ and correctness of the public key encryption ensure that
+  $\NIZK^{\Open}$ and correctness of the public key encryption ensure that
   the $\yinsp'$ value extracted by \NIZKExtract matches the value produced by
-  \Inspect.
+  \Open.
 
@@
   For $G_1$, within \Setup, we replace the \Setup algorithms for the three
-  NIZKs (\Issue, \Sign and \Inspect) with their corresponding \SimSetup
+  NIZKs (\Issue, \Sign and \Open) with their corresponding \SimSetup
   variants. Consequently, the corresponding queries to \Prove are also

### 2022-05-12 prism-backend/research/gsac/transformations-uas.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.

@@
 \section{Relating \UAS with Other Schemes, and Variations}
-\label{ssec:transformations}
+\label{sec:transformations}
 
 In order to justify \UAS's universality, in this section we describe how does
-\UAS schemes relate with other similar systems. \todo{The relationships seem
+\UAS schemes relate with other similar systems. \jdv{The relationships seem
   quite straightforward; thus, we only informally sketch how one could build
@@
 
-\todo{In \cite{khk+19}, the authors prove that GS-MDO implies identity-based
+\jdv{In \cite{khk+19}, the authors prove that GS-MDO implies identity-based
   encryption. \UAS implying GS-MDO would thus imply IBE, but we do not use
@@
 
-In a nutshell, ring signatures \needcite are like group signatures where
+In a nutshell, ring signatures \cite{rst06} are like group signatures where
 rather than having an issuer accepting users into a group, any user can create
@@
   ring signatures. Some variants allow some sort of linkability; for instance
-  \needcite}, although the most distinguishing property is probably the lack of
-issuer, which has led some relevant systems like Monero%
+  \cite{lww04}}, although the most distinguishing property is probably the lack
+of issuer, which has led some relevant systems like Monero%
 \footnote{\url{https://www.getmonero.org/resources/moneropedia/ringsignatures.html}.
@@
 basically by, insted of returning the plaintext \yeval value, returning an
-encryption of it under the inspector's public key; additionally proving 
+encryption of it under the opener's public key; additionally proving 
 that the value used to compute the output of \finsp is the plaintext \yeval
@@
 
-\todo{It would seem that the simulation-based anonymity definition is more
+\jdv{It would seem that the simulation-based anonymity definition is more
   general. Can we prove that? Concretely, if it is also good for selective
@@
 
-\subsection{Functional Signatures}
-
-\todo{I think that, by making \yeval explicit, \UAS is essentially a
+\jdv{\subsection{Functional Signatures}}
+\jdv{I think that, by making \yeval explicit, \UAS is essentially a
   privacy-preserving extension to Functional Signatures. Still, I read that paper

### 2022-05-12 prism-backend/research/gsac/introduction.tex
Hotfix for bug in url hyperlink...

@@
 \footnote{``Digital identity is one of the 21st century's biggest challenges'':
-  \url{https://www.maddyness.com/uk/2021/11/04/digital-identity-is-one-of-the-21st-centurys-biggest-challenges/}. Last access, May 12th, 2022.}.
+  \href{https://www.maddyness.com/uk/2021/11/04/digital-identity-is-one-of-the-21st-centurys-biggest-challenges/}{https://www.maddyness.com/uk/2021/11/04/digital-identity-is-one-of-the-21st-centurys-biggest-challenges/}.
+Last access, May 12th, 2022.}.
 Just as an illustration, think

### 2022-05-13 prism-backend/research/gsac/app-building-blocks.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.
Quick full pass (excl. appendices).

@@
 
-\subsection{An Instantiation of \SBCM with BBS+}
+\subsubsection{An Instantiation of \SBCM with BBS+}
 
@@
 
-\subsubsection{Security.} Next, we sketch that the given BBS+ interactive
-signing protocol is correct, OMF-secure, and ensures blindness.
-
-\paragraph{Correctness.} \todo{XXX}
+\paragraph{Correctness.} Correctness is direct from correctness of the
+commitment scheme, the NIZK system, and BBS+.
 
@@
 %
-\todo{If needed, do the actual proof. Should essentially be a copy-paste of
+\jdv{If needed, do the actual proof. Should essentially be a copy-paste of
   that in \cite{cdl16b}...}

### 2022-05-13 prism-backend/research/gsac/conclusion.tex
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.
Quick full pass (excl. appendices).

@@
 attested by these issuers. Indeed, if it is already hard for verifiers to decide
-whether or not to trust an unanonymous issuer, one can imagine that it would be
+whether or not to trust a non-anonymous issuer, one can imagine that it would be
 even harder to decide whether or not to trust an anonymous one. This question
-is core to the domain of trust registries \needcite, for instance.
+is core to the domain of trust registries, for instance.
 %

### 2022-05-13 prism-backend/research/gsac/construction-uas.tex
Fixed error in unfor-sign property and proof.
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.
Quick full pass (excl. appendices).

@@
 In this section, we give a generic construction of an \UAS scheme, based on
-generic building blocks. In \todo{\secref{sec:instantiation}}, we give a concrete
-instantiation.
-
-We use three different NP relations in our generic construction. Namely:
+generic building blocks. We use three different NP relations in our generic
+construction. Namely:
 
 \begin{description}
-\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs the rules for issuing
-  new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
-  (\usk,\scred,\attrs_{\scred}), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
-  \CCommit(usk) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
+\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs via \fissue the rules for
+  issuing new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
+  (\usk,\scred,\attrs_{\scred},r), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
+  \CCommit(usk;r) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
   \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1 \rbrace$,
@@
 \item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
-  verifiers define them. Governs what utility information is directly revealed
-  by signatures. It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
+  verifiers define them. Governs via \feval and \finsp what utility
+  information is directly revealed by signatures, or extracted by openers.
+  It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
   \attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec =
@@
   create the signature is bound to the same \usk key.
-\item[$\NIZKRel_{\Open}$:] Set by openers, governs the utility information
-  to be extracted by the \Open algorithm. It is defined as $\NIZKRel_{\Open} =
-  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$. It proves
-  that the decryption of the opening utility value has been done correctly.
+\item[$\NIZKRel_{\Open}$:] Ensures that the utility information extracted by
+  the \Open algorithm is correct. It is defined as $\NIZKRel_{\Open} =
+  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$.
 \end{description}
@@
 (\Ssk,\finsp)$, $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$, and $\osk \gets
-(\Ssk,\Edk)$. Finally, returns $(\opk,\osk)$.
+(\Ssk,\Edk)$.
 
@@
 \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\AttrSpace)$, and picking randomly
-$\usk \getr \AttrSpace$. Finally, return \usk.
+$\usk \getr \AttrSpace$.
 

### 2022-05-13 prism-backend/research/gsac/introduction.tex
Quick full pass (excl. appendices).

@@
 users accountable, or extracting utility out of their actions, is trivial in
-this cases -- although that comes at the cost of barely having privacy.
+these cases -- although that comes at the cost of barely having privacy.
 
@@
 
-Concerning (2), it is even surprising that, during the almost 30 years of
+Concerning (2), it is even surprising that, during the roughly 30 years of
 research in group signatures, the notion of ``identity'' of a group member
@@
 even a simple combination. This directly answers in the affirmative our first
-question above. However, a direct combination does not address at all the
+question above. However, a direct combination does not achieve at all the
 flexibility that we aim at -- simply because it inherits the limitations of
@@
 The interest of the verifiable credentials community in BBS+ is not accidental,
-though, as BBS+ follow the CL signatures line of work \cite{cl02}. CL signatures
+though, as BBS+ follows the CL signatures line of work \cite{cl02}. CL signatures
 allow creating a single signature over a set of messages, which can be directly
@@
 over the attributes in a credential \cite{bcc+09,cklm14,dmm+18,fhs19}; while
-others simply allow to
-selectively disclose subsets of these attributes. For \GSAC, we do the latter.
+others simply allow to selectively disclose subsets of these attributes
+\cite{cks10,cl11,cdhk15,hs21}. For \GSAC, we do the latter.
 Despite not being the most general option (although it is more general than the
@@
 prefer the UC approach \cite{cdl16,cdl16b,ccd+17,cdl17}. On the AC line of work,
-while some UC models exist \cite{}, game-based definitions also seem prevalent
-\cite{bcc+09,cks10,cl11,cklm12,cmz14,dmm+18,fhs19}.
+while some UC models exist \cite{cks10}, game-based definitions also seem
+prevalent \cite{bcc+09,cl11,cklm12,cmz14,dmm+18,fhs19}.
 Thus, the logical choice (at least, for a first step) seems to be game-based
@@
 \subsubsection{\UAS: Generalizing \GSAC.} %
-\GSAC is the first step towards achieving identity and authentication systems
-with both utility and accountability, yet it presents some limitations. Some we
-have already mentioned: it models a system with only one issuer, only allows
-using one credential to produce a signature, and only supports selective
-disclosure. We overview other limitations, that we address also with \UAS.
+\GSAC is the first step towards achieving privacy-preserving identity and
+authentication systems with both utility and accountability, yet it presents
+some limitations. Some we have already mentioned: it models a system with only
+one issuer, only allows using one credential to produce a signature, and only
+supports selective disclosure. We overview other limitations, that we address
+also with \UAS.
 
@@
 approach. While still compatible with cases in which the output of \feval has
-the same in both challenge signatures, it additionally allows useful
+the same value in both challenge signatures, it additionally allows useful
 constructions in which the output of \feval is encrypted, e.g., under the

### 2022-05-13 prism-backend/research/gsac/model-gsac.tex
Added sketch of security proof for SBCM. Updated GSAC model to include attrs on Open. Other minor edits.
Updated GSAC and UAS proofs based on updated non-frame definiton.
First complete readable draft. Still has some pending stuff and needs refinement, but should be shareable.
Quick full pass (excl. appendices).

@@
 group signatures, tracing and non-frameability are frequently dependent on the
-open function, which (among other things) returns an index pointing to the join
-transcript associated with the user who produced the signature given by the
-adversary as a response to the game's challenge. In our approach, though, each
-user may have many such transcripts -- one per credential that the user
-obtains. However, note that what actually provides meaning to these notions
-is not the index; but the associated user key pair, which is moreover necessary
+open function, which (among other things) returns an member index. In our
+approach, though, each user may have many such transcripts -- one per credential
+that the user obtains. However, note that what actually provides meaning to
+these notions is not the index; but the attributes in the credential, which is
+moreover necessary
 to prove that the opening has been performed honestly. Thus, with some
@@
 credentials reveal the same predicate on their attributes.
-
-In the model described below, we follow closely the definitions from
-\cite{bsz05} for group signatures, and \cite{fhs19} for anonymous credentials
-(which are in turn influenced by \cite{bsz05}).
 
@@
   over message \msg.
-\item[$(\upk,\oproof)/\bot \gets
+\item[$(\upk,\attrs,\oproof)/\bot \gets
   \Open(\gpk,\osk,\sig,\dattrs,\msg)$.]
@@
   attributes containing the set \dattrs, returns the public key \upk of the
-  signer, and a proof of opening correctness \oproof; or $\bot$ if the
-  opening process fails.
-\item[$1/0 \gets \Judge(\gpk,\upk,\oproof,\sig,\dattrs,
-  \msg)$.] Checks if \oproof is a valid opening correctness proof stating that
-  the user with key \upk generated signature \sig over message \msg, revealing
-  attributes $\dattrs$. 
+  signer, and the attribute set \attrs contained in the credential used to
+  generate the signature, along with a proof of opening correctness \oproof; or
+  $\bot$ if the opening process fails.
+\item[$1/0 \gets \Judge(\gpk,\upk,\attrs,\oproof,\sig,\dattrs,
+  \msg)$.] Checks if \oproof is a valid opening proof for the
+  statement: ``The owner of a credential over attribute set \attrs, and owner
+  of public key \upk, created signature \sig, which reveals attribute set
+  $\dattrs \subseteq \attrs$''.
 \end{description}
@@
 The correctness and security properties are defined with the help of the
-following sets of oracles, and global variables that help oracles and games
+following sets of oracles and global variables that help oracles and games
 keep consistent state.
@@
 %
-The games keep track of the user keys (through set \UK) and credentials (through
+The games keep track of the user keys (through table \UK) and credentials (through
 table \CRED) that are created as a result of oracle calls by the adversary. We
@@
 Additionally, the games keep track of all honest and corrupt users that have
-been generated, through sets \HU and \CU, respectively. They also keep track of
+been generated through sets \HU and \CU, respectively. They also keep track of
 the signatures that have been honestly produced, through the \SIG table. Since
@@
 values, and all tables/sets are initialized as empty tables/sets. Also, for
-readability, we abuse the syntax as follows: we
+readability, we abuse the syntax and
 write $\CRED[\uid]$ to mean $\CRED[\cid]$ for all $\cid$ such that
@@
 \begin{description}
-\item[\RREG.] Reads the given transcript table entry.
-\item[\WREG.] Sets a transcript table entry to the given value.
 \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
@@
   requesting an honest issuer to produce credentials for them.
+\item[\RREG.] Reads the given transcript table entry.
+\item[\WREG.] Sets a transcript table entry to the given value.  
 \item[\SIGN.] Lets the adversary get signatures from credentials belonging
@@
 by \Verify. Moreover, an honestly produced correctness proof of opening for such
-signature, revealing the public key pair of the user, must also be accepted by
-\Judge.
+signature, revealing the public key pair of the user and credential attributes,
+must also be accepted by \Judge.
 
@@
 \begin{figure}[htp!]
-  \procedure{$\ExpGSACCorrect(1^\secpar)$}{%
+  \procedure[linenumbering]{$\ExpGSACCorrect(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
@@
     \sig \gets \Sign(\gpk,\PRVUK[\OWNR[\cid]],\CRED[\cid],\dattrs,\msg) \\
-    (\upk,\oproof) \gets \Open(\gpk,\osk,\sig,\dattrs,\msg) \\
+    (\upk,\attrs,\oproof) \gets \Open(\gpk,\osk,\sig,\dattrs,\msg) \\
     \pcif \Verify(\gpk, \sig, \dattrs,\msg) = 0 \lor
-    \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 0: \\
+    \Judge(\gpk,\upk,\attrs,\oproof,\sig,\dattrs,\msg) = 0: \\
      \pcind \pcreturn 1 \\
@@
     \pcif \Open(\gpk,\osk,\trans,\sig,\dattrs,\msg) = \bot: \pcreturn 1 \\
-    \textrm{Let}~(\upk,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,\dattrs,\msg) \\
-    \pcif \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 0: \pcreturn 1 \\
+    \textrm{Let}~(\upk,\attrs,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,
+    \dattrs,\msg) \\
+    \pcif \Judge(\gpk,\upk,\attrs,\oproof,\sig,\dattrs,\msg) = 0: \pcreturn 1 \\
     \pcelse \pcif \forall \uid \in \CU \cup \HU, \nexists (\uid,\cdot,\attrs)
-    \in \CRED~\st~\dattrs \subseteq \attrs: \pcreturn 1 \\
+    \in \CRED \lor \dattrs \not\subseteq \attrs: \pcreturn 1 \\
     \pcreturn 0
@@
 Non-frameability variants are a core unforgeability-type property in group
-signatures. However, no similar property is modelled for anonymous credentials
-(see the discussion in \todo{\secref{sec:introduction}} for further detail). It
-is a quite strong
+signatures. However, no similar property is modelled for anonymous credentials.
+It is a quite strong
 property, as it must be ensured even in the presence of dishonest issuer and
@@
 In \GSAC schemes, in order for a user to be framed, the adversary first needs to
-create a $(\sig,\dattrs,\msg,\upk,\oproof)$ tuple such that the signature,
+create a $(\sig,\dattrs,\msg,\upk,\attrs,\oproof)$ tuple such that the signature,
 attributes, and message are accepted by \Verify, and which, along with the user
-public key, and open correctness proof, are accepted by \Judge.
+public key, and open correctness proof, are accepted by \Judge; or, alternatively,
+produce a signature revealing \dattrs, which is accepted by \Verify, and \Judge
+accepts \attrs as the attribute set in the used credential owned by \upk, but
+$\dattrs \not\subseteq \attrs$.
 Then, the adversary wins the game if the owner of the credential is honest, but
@@
      \gpk \gets (\ipk,\opk) \\
-     (\sig,\dattrs,\msg,\upk,\oproof) \gets
+     (\sig,\dattrs,\msg,\upk,\attrs,\oproof) \gets
      \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN}(\gpk,\isk,\osk) \\
+     \pcif \Verify(\gpk,\sig,\dattrs,\msg) = 0: \pcreturn 0 \\
+     \pcif \Judge(\gpk,\upk,\attrs,\oproof,\sig,\dattrs,\msg) = 0: \pcreturn 0 \\
      \textrm{Let}~\uid~\textrm{be st}~\PUBUK[\uid] = (\upk,\cdot) \\
-     \pcreturn 1~\pcif \Verify(\gpk,\sig,\dattrs,\msg) = 1 \land 
-     \Judge(\gpk,\upk,\oproof,\sig,\dattrs,\msg) = 1~\land \\
-     \pcind \uid \in \HU \land \sig \notin \SIG[\uid] \\
+     \pcif \textrm{no such \uid exists}: \pcreturn 0 \\
+     \pcif \uid \in \HU \land (\sig \notin \SIG[\uid]
+     \lor \dattrs \not\subseteq \attrs): \pcreturn 1 \\
      \pcreturn 0

### 2022-05-13 prism-backend/research/gsac/model-uas.tex
Quick full pass (excl. appendices).

@@
 are not circumvented; and unforgeability of signatures, guaranteeing that
-signing policies are respected, as well as soundness of opening.
+signature evaluation policies are respected, as well as soundness of opening.
 
@@
 users prove arbitrary claims on their credentials, as long as they are met by
-the contained attributes. In practice, most probably, the signing policy to be
+the contained attributes. In practice, most probably, the signature evaluation
+policy to be
 employed in each signature will be defined by the verifier (or jointly between
@@
 
-\subsubsection{Syntax.} An \UAS scheme is composed by the following algorithms:
+\subsubsection{Syntax.} An \UAS scheme is composed by the following algorithms,
+where for readability we assume that issuer public keys (\ipk) are extractable
+from credentials:
 
@@
   \langle
-  \Obtain(\usk,\lbrace (\cred_i,\ipk_i)\rbrace_{i \in \Issuers},\attrs),
-  \Issue(\isk,\lbrace \ipk_i \rbrace_{i \in \Issuers},\attrs))
+  \Obtain(\usk,\scred,\attrs),
+  \Issue(\isk,\sipk,\attrs))
   \rangle$.] %
@@
   \Obtain process, receive a credential \cred from an issuer in the system, on
-  attribute set $\attrs$. The user leverages a set of $(\cred_i,\ipk_i)$ pairs,
-  where $\cred_i$ is a credential obtained from the issuer with public
-  key $\ipk_i$. The user outputs the produced credential \cred, while
+  attribute set $\attrs$. The user leverages a set of credentials \scred,
+  each with a matching issuer key in \sipk.
+  The user outputs the produced credential \cred, while
   the issuer outputs the protocol transcript \utrans for the produced
-  credential. To ease notation, we assume that the issuer public key associated
-  to credential is available from the credential itself, and therefore
-  omit the $\ipk_i$ values from the syntax, unless necessary to avoid
-  ambiguity.
-\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
-  \rbrace_{i \in \Issuers},\msg,\feval)$.] %
+  credential.
+\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.] %
   Upon receiving a user secret key \usk, opener public key \opk, a set of
-  credential-issuer pairs $(\cred_i,\ipk_i)$, a message \msg and evaluation
+  credentials \scred, a message \msg and evaluation
   function \feval, returns signature \sig and value \yeval.
-\item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
-  \yeval,\msg,\feval)$.] Checks whether $(\sig,\yeval)$ is a valid signature
+\item[$1/0 \gets \Verify(\opk, \sipk,\sig,\yeval,\msg,\feval)$.]
+  Checks whether $(\sig,\yeval)$ is a valid signature
   over message \msg, from a user with credentials issued by issuers with public
-  keys $\ipk_i$, for evaluation function \feval and opener key \opk.
-\item[$(\yinsp,\iproof)/\bot \gets \Open(\osk,\lbrace \ipk_i
-  \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
+  keys in \sipk, for evaluation function \feval and opener key \opk.
+\item[$(\yinsp,\iproof)/\bot \gets \Open(\osk,\sipk,\sig,\yeval,\msg,\feval)$.]
   Executed by the opener with private key \osk. Receives a signature $(\sig,
   \yeval)$ over message \msg and evaluation function \feval, generated using
-  credentials issued by the issuers with public keys $\ipk_i$. If \sig is valid,
+  credentials issued by the issuers with public keys in \sipk. If \sig is valid,
   the function outputs a value $\yinsp$.
-\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\yinsp,
-  \iproof,\sig,\yeval,\msg,\feval)$.] %
+\item[$1/0 \gets \Judge(\opk,\sipk,\yinsp,\iproof,\sig,\yeval,\msg,\feval)$.] %
   Checks if \iproof is a valid opening correctness proof for the value \yinsp,
@@
 \begin{description}
-\item[$\fissue: (\usk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\attrs)
+\item[$\fissue: (\usk,\scred,\attrs)
   \rightarrow 0/1$.] Chosen by issuers within a family of functions \famfissue,
@@
   key \usk, for attributes \attrs. \fissue may run checks on a (possibly empty)
-  set of additional credentials $\cred_i$, all bound to \usk, and possibly
+  set of additional credentials \scred, all bound to \usk, and possibly
   issued by other issuers. \fissue returns $1$ to accept a request, $0$ to
   reject it.
-\item[$\feval: (\usk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\msg)
+\item[$\feval: (\usk,\scred,\msg)
   \rightarrow \yeval$.] Signing evaluation functions, from a family of functions
   \famfeval, can be set on a per-signature basis. They receive the user secret
-  key \usk, credentials $\cred_i$, and message to be signed \msg, and can be
+  key \usk, credentials \scred, and message to be signed \msg. \feval can be
   used to control the information related to the signer that will be revealed
@@
   \yeval must belong in a well defined set \rngfeval.
-\item[$\finsp: (\yeval,\usk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
-  \msg) \rightarrow \yinsp$.]
+\item[$\finsp: (\yeval,\usk,\scred,\msg) \rightarrow \yinsp$.]
   Chosen by openers from a family of functions \famfinsp. The opening
@@
 \paragraph{Helper functions \ExtractIssue, \ExtractSign, \IdentifyCred, and
-  \IdentifyUK.} In our modelling, we assume the existence of four functions,
-\ExtractIssue, \ExtractSign, \IdentifyCred, and \IdentifyUK. They are not
+  \IdentifyUK.} In our modelling, we assume the existence of fhese four
+functions. They are not
 functions available in the actual scheme, but rather to the challenger in the
@@
 \item[$\IdentifyUK(\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret key.
-  This is trivial for honest users, for which this must be a one-to-one
+  This is trivial for honest users, for which there must be a one-to-one
   relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
@@
   though. Also, when used for corrupt users, this can only be used when the
-  issuer is honest.  
+  issuer is honest, as transcripts are needed. 
 \end{description}
@@
 experiments. For credentials and join transcripts of corrupt users, or
-dishonestly produced signatures, we do need to perform actual extraction. How to
-do this will depend on each specific construction. Certainly, the challenger
+dishonestly produced signatures, we do need to perform actual extraction.
+Certainly, the challenger
 needs special knowledge/power such as decryption trapdoors, the ability to
 rewind the game, or program random oracles. The approach needs thus to depend on
-the concrete construction. \jdv{Although, for the case of \ExtractIssue,
-  online extractability (or alternative requirements, such as non-parallel or
-  logarithmic number of joins) is necessary.}
+the concrete construction. \jdv{Although, for the case of \ExtractIssue and
+  \IdentifyUK, online extractability (or alternative requirements, such as
+  non-parallel or logarithmic number of joins) is necessary.}
 
@@
 \begin{description}
-\item[Tables for parties]:
+\item[Sets for parties]:
   \begin{description}
@@
 \paragraph{Oracles.} %
-Oracles are the interface of the adversary with the corresponding games. In
-other words: through these oracles, the game environment exposes to the adversary
-functionality that could otherwise be executed only by honest parties with
-private knowledge -- knowledge that would make the adversary capable of
-trivially breaking the security properties formalized in the experiments.
 In the game-based definitions of our \UAS model, we leverage the following
@@
 \item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
-  user already exists and is honest, corrupts it.
+  user already exists and is honest, corrupts it, leaking its key and
+  credentials.
 \item[\RREG.] Reads the given transcript table entry.
@@
           \pcif \iid \notin \HI: \pcreturn \bot \\
-          \pcif \exists \iid' \in \ISR[\scid] \notin \HI: \pcreturn \bot \\
+          %\pcif \exists \iid' \in \ISR[\scid] \notin \HI: \pcreturn \bot \\
           \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
@@
           \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
-          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot: \pcreturn \bot \\
+          %\pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot: \pcreturn \bot \\
           \langle \cred, \cdot \rangle \gets
@@
           \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
-          \pcif \exists \iid' \in \ISR[\scid]~\st~\iid' \notin \HI: \pcreturn \bot \\
-          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot:
+          %\pcif \exists \iid' \in \ISR[\scid]~\st~\iid' \notin \HI: \pcreturn \bot \\
+          %\pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot:
           \pcreturn \bot \\
@@
           (\yinsp,\iproof) \gets
-          \Open(\PRVOK[\oid],\GK[\scid],\sig,\yeval,\msg,\feval) \\
+          \Open(\PRVOK[\oid],\PUBIK[\scid],\sig,\yeval,\msg,\feval) \\
           \pcif \CSIG[\sig] \neq \bot: \\
@@
 \figref{fig:exp-uas-corr}. It states that a signature over any arbitrary message
-and valid function \feval produced honestly leveraging credential set \scid,
+and valid function \feval, produced honestly leveraging credential set \scid,
 owned by user \uid, is accepted by \Verify. Moreover, all the credentials in
-\scid met the conditions set by the corresponding \fissue defined by the issuer
+\scid meet the conditions set by the corresponding \fissue defined by the issuer
 which issued each credential. Similarly, the output \yeval of \feval matches the
@@
 \paragraph{Anonymity.} %
-In group signatures, anonymity captures that no adversary must be able to learn,
-from any group signature, the identity (e.g., member index) of its signer. In 
-anonymous credentials, it requires that no adversary should learn anything about
-the holder of a successfully shown credential, beyond that he owns a credential
-attesting for the claimed predicate of the attributes it contains. In both GS
-and AC, it is also typically required that
-multiple signatures/presentations by the users are unlinkable. The approach to
-formally state this property is in both cases frequently the same: the adversary
-picks two (honest) users (or credentials in the AC case), the game randomly
-chooses one of them, and lets the adversary request challenge
-signatures/presentations from it. The adversary wins if it succeeds in guessing
-which was the chosen user/credential better than guessing at random. In group
-signatures, the game must also restrict the adversary from opening challenge
-signatures. In anonymous credentials, the game must further constraint the
-adversary to output credentials that both meet the same (challenge) predicate
-of their attributes.
-
-In our notion of anonymity for \UAS, we need to merge the previous constraints.
-In order to prevent trivial wins by the adversary, we have to restrict that the
+In addition to the considerations made for \GSAC (see \secref{ssec:model-gsac}),
+in our notion of anonymity for \UAS,
+in order to prevent trivial wins by the adversary, we have to restrict that the
 signing evaluation function outputs the same value for both user-credentials
@@
 disclosure, or privacy-preserving variants of functional signatures \jdv{check
-  the latter, and perhaps expand}.
+  the latter}, although we show how to do that in \secref{sec:transformations}.
 
@@
 
-In our \UAS scheme we need to allow users prove claims over the attributes they
+In our \UAS scheme we allow users prove claims over the attributes they
 own -- attested via obtained credentials -- through the \feval function.
-Roughly, we capture this roughly as in unforgeability requirement of anonymous
-credentials. Namely, that the \yeval value returned by \Sign along with the
-signature, matches the expected one from the specified \feval function.
+Roughly, we capture this as in unforgeability requirement of anonymous
+credentials. Namely, we check that the \yeval value returned by \Sign along with
+the signature, matches the expected one from the specified \feval function.
 On the other hand, the opening capabilities of \UAS schemes also call for a
@@
 the credential was obtained via an $\langle \Obtain,\Issue \rangle$ run). To
-capturethis, we define the \ExpForgeIssue experiment. In the experiment, the
+capture this, we define the \ExpForgeIssue experiment. In the experiment, the
 adversary is challenged to produce a credential identifier that must be
@@
 again a direct consequence of the fact that \Open can return an arbitrary
-function of the signer's key and credentials (and signed message), whic is a
+function of the signer's key and credentials (and signed message), which is a
 strict generalization of the conventional \Open. Although, even in that case, we
@@
 there is a valid join transcript associated to the membership credential used
-to produce the signature. However, in \UAS, even though that transcript exists,
-we need to make sure that the issuance policy was satisfied -- and this is not
-something (easily) extractable from the signature.
+to produce the signature. However, in \UAS, given that the credentials contain
+attributes, even though that transcript exists, we need to make sure that the
+issuance policy over these attributes was satisfied -- and this is not something
+(easily) extractable from the signature.
 
 \paragraph{Non-frameability.} %
-Non-frameability variants are a core unforgeability-type property in group
-signatures. However, no similar property is modeled for anonymous credentials.
-It is a quite strong property, as it must be ensured even in the presence of
-dishonest issuer and opener. Intuitively, it prevents the adversary from
-creating a signature that can be (even in some generic sense) associated to an
-honest user who did not produce it. Depending on the opening capabilities of the
-scheme, this framing could be done in different ways; i.e., by convincing third
-parties that signatures by different (possibly corrupt) users are linked, or
-directly by having opening proofs output the identity of a user who did not
-create the signature being opened.
-
 The notion of non-frameability in \UAS schemes is unavoidably more subtle than
-in group signatures, though. To see this, we note that, by allowing arbitrary
+in group signatures. To see this, we note that, by allowing arbitrary
 evaluation and open functions to be used, it can be perfectly valid to
@@
 against the secret keys of the honest users. The adversary wins if there is a
-match and the signature has not been queried to \SIGN. In the game, the
+match and the signature has not been queried to \SIGN, or if the value \yinsp
+output by the adversary is accepted by \Judge, yet it is different from the
+extracted $\yinsp'$ value. In the game, the
 adversary has access to the oracles in $\Oframe \gets \lbrace\HU,\CU\rbrace\GEN,

### 2022-05-13 prism-backend/research/gsac/preliminaries.tex
Quick full pass (excl. appendices).

@@
 \SBCMCom,\SBCMSign,\SBCMVerify). Algorithm $\parm \gets \SBCMSetup(\secpar)$
-produces the public parameters for the scheme.
+produces the public parameters for the scheme. %
 $(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing
-key pair. $\\sig/\bot \gets\langle \SBCMCom(\vk,\overline{\smsg},\smsg),
+key pair. $\sig/\bot \gets\langle \SBCMCom(\vk,\overline{\smsg},\smsg),
   \SBCMSign(\sk,\smsg) \rangle$ is an interactive protocol between a user, who
 runs \SBCMCom and has a set of messages $\overline{\smsg}$ to be block-committed,
-and a signer, who owns signing key \SBCMsk; both also receive common input a
+and a signer, who owns signing key \sk; both also receive common input a
 block of messages \smsg. The output of the protocol is a signature over
 $\overline{\smsg} \cup \smsg$. Algorithm $1/0 \gets \SBCMVerify(\vk,
-\sig,\overline{\smsg},\smsg)$ verifies a signature \SBCMsig over message set
+\sig,\overline{\smsg},\smsg)$ verifies a signature \sig over message set
 $\overline{\smsg} \cup \smsg$. In addition, the
@@
 
-We use common notation habits. $y \gets A(x)$ means that algorithm $A$, on input
-$x$, produces output $y$. When $A$ is a probabilistic process, and we want to
-make explicit the randomness $r$, we use $y \gets A(x;r)$. $\langle y_A,y_B \gets
-\langle A(x_A),B(x_B)\rangle$ denotes algorithms $A$ and $B$, running an
+We follow common notation habits. $y \gets A(x)$ means that algorithm $A$, on
+input $x$, produces output $y$. When $A$ is a probabilistic process, and we want
+to make explicit the randomness $r$, we use $y \gets A(x;r)$. $\langle y_A,y_B
+\gets \langle A(x_A),B(x_B)\rangle$ denotes algorithms $A$ and $B$, running an
 interactive protocol, where $A$ receives $x_A$ as input and produces $y_A$ as
@@
 written in bold font denote sets, e.g., while we use \ipk to denote a single
-issuer public key, \sipk denotes a set of issuer's public keys.
+issuer public key, \sipk denotes a set of issuer's public keys. To refer to
+a specific element of a set, we use subindexes, e.g., $\sipk_i$ is the $i$-th
+\ipk within \sipk.
 %

### 2022-05-13 prism-backend/research/gsac/sec-gsac.tex
Quick full pass (excl. appendices).

@@
   privacy-preserving identities. Furthermore, it does so in a formal way,
-  via the traceability notion and, crucially, the non-frameability one,
+  via the traceability notion and, crucially, the non-frameability one
   (which is not present in anonymous credentials).
@@
 Functionally, we combine both worlds. Namely, a user can get as many credentials
-as s/he wants -- although all are tied to the same user key --, and signatures
+as s/he wants -- although all are bound to the same user key --, and signatures
 (or credential presentations) of the same credential must be unlinkable. In this
@@
 any two signatures (credential presentations) reveal nothing about the
-credential used to produce them, beyond the revealed attributes. For this first
-step, security-wise we stick to the conventional separation of
+credential used to produce them, beyond the revealed attributes.
+Security-wise we stick to the conventional separation of
 unforgeability-related properties in group signatures. That is, traceability

### 2022-05-13 prism-backend/research/gsac/sec-uas.tex
Quick full pass (excl. appendices).

@@
 in generalized variants of anonymous credentials), as well as multiple openers,
-each one with a predefined open function. Thus, it supports use cases like
-having a user produce a signature with credentials obtained from issuers A and
-B, which can be inspected by opener C; but later use the same credentials
-from issuers A and B, to produce a signature that can be inspected by opener D.
+each one with a predefined open function. 
 A consequence of this is that the concept of ``group'', which was very present
@@
 via \Open and \Judge.
+%
+Although this may seem an innocent change, it brings much flexibility in
+practice.
 

### 2022-05-13 prism-backend/research/gsac/security-uas.tex
Quick full pass (excl. appendices).

@@
   \label{thm:correctness-uas}
-  If the underlying schemes for commitments, encryption and \SBCM, are correct,
+  If the underlying schemes for commitments, public-key encryption and \SBCM,
+  are correct,
   as well as the NIZKs for $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
@@
   \label{thm:issue-forge-uas}
-  If the underlying NIZK used for $\NIZKRel_{\Issue}$ is simulation extractable
-  and sound, then our \CUASGen construction satisfies issuance unforgeability as
-  defined in \defref{def:issue-forge-uas}, except with negligible probability.
+  If the underlying NIZK used for $\NIZKRel_{\Issue}$ is zero-knowledge,
+  simulation extractable and sound, then our \CUASGen construction satisfies
+  issuance unforgeability as defined in \defref{def:issue-forge-uas}.
 \end{theorem}
@@
   is exactly the same, but where, within the \Setup algorithm, we replace
-  $\NIZKSetup^{\Issue}$ with $\NIZKSimSetup^{\Issue}$. As per the definition of
-  \NIZK in \appref{sapp:nizk}, both games are indistinguishable.
+  $\NIZKSetup^{\Issue}$ with $\NIZKSimSetup^{\Issue}$. Due to zero-knowledgeness
+  of $\NIZK^{\NIZKRel_{\Issue}}$, both games are indistinguishable.
 

### 2022-05-13 prism-backend/research/gsac/transformations-uas.tex
Quick full pass (excl. appendices).

@@
 
-In order to justify \UAS's universality, in this section we describe how does
+In order to justify \UAS's universality, in this section we describe how do
 \UAS schemes relate with other similar systems. \jdv{The relationships seem
@@
 only one opener. However, since there is no tight relation between issuer and
-opener (as in conventional group signatures), note that it is trivial to extend
-to the case with multiple openers per signature. In that case, the
+opener (as opposed to conventional group signatures), it is trivial to
+extend to the case with multiple openers per signature. In that case, the
 $\NIZKRel_{\Sign}$ relation should be extended to include proofs of correct
@@
 authors introduce an extra authority, the admitter, who creates a
-``message-specific token'' for each message that they deem unacceptable.
+``message-specific token'' for each message that is deemed unacceptable.
 These message-specific tokens are later needed by the opener, in order to open
@@
   ring signatures. Some variants allow some sort of linkability; for instance
-  \cite{lww04}}, although the most distinguishing property is probably the lack
+  \cite{lww04}.}, although the most distinguishing property is probably the lack
 of issuer, which has led some relevant systems like Monero%
@@
 generic construction. This is due to the fact that the NP relation
-$\NIZKRel^{\Sign}$ defined in \secref{ssec:generic-construction-uas} reveals the
+$\NIZKRel_{\Sign}$ defined in \secref{ssec:generic-construction-uas} reveals the
 issuers' public keys. This is a problem as, intuitively, the signer in a ring
@@
 %
-Besides $\NIZKRel^{\Sign-prv}$, let $ring$ be an ad hoc set containing the
+Besides $\NIZKRel^{\Sign-prv}$, let \sring be an ad hoc set containing the
 public keys of the users that the signer wants to include in its ad hoc group.
-We define $\fissue^{ring}(\usk,\scred,\attrs) \coloneqq \lbrace \pcif \attrs
-\subseteq ring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1; \pcelse
+We define $\fissue^{\sring}(\usk,\scred,\attrs) \coloneqq \lbrace \pcif \attrs
+\subseteq \sring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1; \pcelse
 \pcreturn 0 \rbrace$. That is, if we let the attributes in a credential be
@@
 possible.
+%
+Interestingly, this construction based on \UAS allows adding extra attributes
+(beyond the public keys in the ring) to the produced signatures, which may be
+useful for real world use cases.
 
 \subsection{Multimodal Private Signatures}
-
-\commentwho{Jesus}{How to cite the Crypto22 paper?}
 
@@
 \scred,\msg),\usk,\scred,\msg) \land \forall \cred \in \scred,
-\SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$.
+\SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$. This would
+also seem to require that the used public-key encryption scheme is IND-CCA.
 
@@
 $n+1$. Without loss of generality, assume that the credential level is encoded
-in the first attribute of the credential, which we denote with $a_1$. In this
-context, any owner of a credential of level $n$ can define an issuance function
-$\fissue^n \coloneqq \lbrace \pcif a_1 = n+1: \pcreturn 1; \pcelse \pcreturn 0
-\rbrace$.
+in the first attribute of the credential (after the \usk), which we denote with
+$a_1$. In this context, any owner of a credential of level $n$ can define an
+issuance function $\fissue^n \coloneqq \lbrace \pcif a_1 = n+1: \pcreturn 1;
+\pcelse \pcreturn 0 \rbrace$.
 

### 2022-05-14 prism-backend/research/gsac/sec-uas.tex
Added fig-table sketching proof components.

@@
 to only one credential per signature. Then, the natural question is whether we
-can model an extension to \GSAC that is compatible both with constructions with
+can model an extension to \GSAC that is compatible both with constructions
 that support selective disclosure, and with constructions that support arbitrary
@@
 policies. In a nutshell, our generalization of \GSAC into Universal Anonymous
-Signatures (\UAS), enables:
+Signatures (\UAS), captured in \figref{fig:proof-blocks-uas}, enables:
 
 \begin{itemize}
-\item Using previously obtained credentials to request new ones, applying
-  arbitrary policies to the credentials involved in the request, in
-  order to determine whether the new issuance should proceed or not.
-\item Modulating the type of utility one wants to get directly from signatures.
-  That is, let signatures disclose a subset of the attributes in the credentials
-  involved in the signing process, prove arbitrary claims over those attributes,
-  or even reveal absolutely nothing at all beyond that that an owner of a valid
-  credential created the signature.
-\item Defining arbitrary de-anonymization functions, over the signer's
-  credentials and signed message. This can range from producing the user public
-  key (as in group signatures), to disallowing any kind of de-anonymization,
-  passing through any intermediate de-anonymization function, like revealing
-  concrete attributes, or functions of them.
+\item Using previously obtained credentials to request new ones, applying a
+  configurable policy defined via an issuance function \fissue, which determines
+  whether the new issuance should proceed or not.
+\item Modulating the type of utility one wants to get directly from signatures,
+  via a signature evaluation function \feval. \feval can be programmed to reveal
+  nothing, selective disclosure, arbitrary claims over the credentials'
+  attributes, etc.
+\item Defining arbitrary accountability information that will be extractable by
+  openers through an opening function \finsp. This can range from no information
+  at all, to functions on subsets of the attributes, to full de-anonymization.
 \end{itemize}
+
+\begin{figure}[ht!]
+  \input{figures/proof-blocks-uas.tex}
+  \caption{Comparison of statements proved per operation in \GSAC and \UAS.
+    $K(x)$ means proving knowledge of $x$; $E(y)$ means proving correct
+    encryption of $y$; $D(z)$ means proving correct decryption of $z$. In
+    \UAS, solid boxes span configurable statements that control issuance; dashed
+    boxes span configurable statements that control utility; dotted boxes span
+    configurable statements that control accountability. Unboxed statements are
+    fixed, and are thus common to all \GSAC/\UAS schemes.}
+  \label{fig:proof-blocks-uas}
+\end{figure}
 

### 2022-05-14 prism-backend/research/gsac/transformations-uas.tex
Added table summarizing UAS variants. Equations in align environment.

@@
 
-In order to justify \UAS's universality, in this section we describe how do
-\UAS schemes relate with other similar systems. \jdv{The relationships seem
-  quite straightforward; thus, we only informally sketch how one could build
-  other schemes (or something very similar to them) from \UAS, and leave the
-  formal analysis for futher work.}
-%
-As a first (informal) observation, we note that the same transformation to
-interactive presentations as described in \GSAC applies here.
+In order to justify \UAS's universality, in this section we describe how can
+we leverage our \UAS scheme to build other known schemes, only by specifying
+different issuance, signature evaluation, and opening functions; as well as,
+occasionally, some minor variations in some NIZK relations. Table
+\tabref{tab:uas-alt-funcs} summarizes the different functions we use in our
+subsequent variations of \UAS. \jdv{The relationships seem quite
+  straightforward; thus, we only informally sketch how one could build other
+  schemes (or something very similar to them) from \UAS, and leave the formal
+  analysis for futher work.}
+
+\begin{table}[ht!]
+  \begin{tabular}{c | c | c | c | c | c}
+    \bf Target scheme & \bf $\NIZKRel_{\Sign}$ variant & \bf \fissue variant & \bf \feval variant & \bf \finsp variant & \bf  Defined in \\
+    \hline
+    \GSAC & None & $\fissue^1$ & $\feval^{\dattrs}$ & $\finsp^{\upk}$
+    & \secref{ssec:uas-gsac} \\
+    \bf GS-MDO & None & $\fissue^1$ & $\feval^0$ & $\finsp^{\smsg}$
+    & \secref{ssec:uas-gsmdo} \\
+    \bf Ring sigs. & $\NIZKRel_{\Sign-prv}$ & $\fissue^{\sring}$ & $\feval^{\attrs}$ & $\finsp^0$ & \secref{ssec:uas-ring} \\
+    \bf MPS\footnote{Building MPS from \UAS also requires a simple definitional change. See
+    \secref{ssec:uas-mps}.} & $\NIZKRel_{\Sign-enc}$ & Any & $\feval^{enc}$ & Any & \secref{ssec:uas-mps} \\
+    \bf Delegatable creds & None & $\fissue^n$ & Any & Any & \secref{ssec:uas-delcred} \\
+  \end{tabular}
+  \caption{How to build related schemes from \UAS.}
+  \label{tab:uas-alt-funcs}
+\end{table}
 
 \subsection{\GSAC from \UAS}
+\label{ssec:uas-gsac}
+
 Take the generic construction for \UAS in \secref{ssec:generic-construction-uas}.
-First, consider the constant issuance function $\fissue^1(\usk,\scred,\attrs) =
-1$. Next, consider $\finsp^{\upk}(\yeval,\usk,\scred,\msg) \coloneqq
-\CCommit(\usk;0)$, and $\feval^{\dattrs}(\usk,\cred,\msg) \coloneqq \dattrs(\cred)$,
-where $\dattrs(\cred)$ is the function returning the attributes indexed by
+First, consider the constant issuance function $\fissue^1$, the signature
+evaluation function $\feval^{\dattrs}$, and the opening function $\finsp^{\upk}$,
+as defined in \esref{eq:uas-gsac-funcs}
+
+\begin{align}
+  & \fissue^1(\usk,\scred,\attrs) \coloneqq 1 \nonumber \\
+  & \feval^{\dattrs}(\usk,\cred,\msg) \coloneqq \dattrs(\cred)
+  & \finsp^{\upk}(\yeval,\usk,\scred,\msg) \coloneqq \CCommit(\usk;0) \nonumber \\
+    \label{eq:uas-gsac-funcs}
+\end{align}
+
+Where $\dattrs(\cred)$ is the function returning the attributes indexed by
 \dattrs within \cred (which we can assume to be easy to do with proper
@@
 \subsection{\UAS with Multiple Openers}
+\label{ssec:uas-multiopen}
+
 We briefly mention that we have defined \UAS signatures as being ``openable'' by
@@
 \subsection{Group Signatures with Message Dependent Opening}
+\label{ssec:uas-gsmdo}
 
@@
 These message-specific tokens are later needed by the opener, in order to open
-signatures over unacceptable messages.
+signatures over unacceptable messages. \UAS can implement this functionality in
+a straightforward manner, by leveraging $\fissue^1$ as defined in
+\esref{eq:uas-gsac-funcs}, and $\feval^0$ and $\finsp^{\smsg}$, as defined in
+\esref{eq:uas-gsmdo-funcs}.
 
-\UAS can implement this functionality in a straightforward manner. Define
-$\finsp^{\smsg}(\yeval,\usk,\cred,\msg) \coloneqq \lbrace \pcif \msg \in \smsg:
-\pcreturn \CCommit(\usk;0); \pcelse \pcreturn \bot \rbrace$. Also, let
-$\feval^0(\usk,\scred,\msg) \coloneqq \pcreturn 0$. Then, \UAS with $\fissue^1$
-as issuance function, $\feval^0$ as signing evaluation function, and
-$\finsp^{\smsg}$ as opening function, implements a message-dependent opening
-group signature scheme -- again, restricting to one credential per user and
-signature, as before. Moreover, it implements the same functionality without
-an extra authority.
+\begin{align}
+  & \feval^0(\usk,\scred,\msg) \coloneqq \pcreturn 0 \nonumber \\
+  & \finsp^{\smsg}(\yeval,\usk,\cred,\msg) \coloneqq \lbrace \pcif \msg \in \smsg:
+    \pcreturn \CCommit(\usk;0); \pcelse \pcreturn \bot \rbrace
+    \label{eq:uas-gsmdo-funcs}
+\end{align}
 
@@
 \subsection{Ring Signatures}
+\label{ssec:uas-ring}
 
@@
 replace the NP relation in \secref{ssec:generic-construction-uas} with
-$\NIZKRel^{\Sign-prv} \coloneqq \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r,
-\sipk_{\scred}),(\msg,\feval,\yeval,\Ec,\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land
-\yeval = \feval(\usk,\scred,\msg) \land \yinsp = \finsp(\yeval,\usk,\scred,\msg)
-\land \forall \cred \in \scred,\SBCMVerify(\ipk_{\cred},\cred,\usk,
-\attrs_{\cred}) = 1) \rbrace$. That is, the public keys of the issuers are now
-part of the witness in the NP relation, which means that they will not
-be revealed in the proofs.
-%
-Besides $\NIZKRel^{\Sign-prv}$, let \sring be an ad hoc set containing the
-public keys of the users that the signer wants to include in its ad hoc group.
-We define $\fissue^{\sring}(\usk,\scred,\attrs) \coloneqq \lbrace \pcif \attrs
+$\NIZKRel_{\Sign-prv}$. We also use issuance function $\fissue^{\sring}$,
+signature evaluation function $\feval^{\attrs}$, and opening function
+$\finsp^0$. All of them are specified in \esref{eq:uas-ring-funcs}.
+
+\begin{align}
+  & \NIZKRel_{\Sign-prv} \coloneqq \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r,
+    \sipk_{\scred}),(\msg,\feval,\yeval,\Ec,\Eek): \nonumber \\
+  & \hspace*{6.405em}\Ec = \EEnc(\Eek,\yinsp;r) \land \nonumber \\
+  & \hspace*{6.40em}\forall \cred \in \scred,\SBCMVerify(\ipk_{\cred},\cred,\usk,
+    \attrs_{\cred}) = 1) \land \nonumber \\
+  & \hspace*{6.40em}\yeval = \feval(\usk,\scred,\msg) \land
+    \yinsp = \finsp(\yeval,\usk,\scred,\msg)
+     \rbrace \nonumber \\
+  & \fissue^{\sring}(\usk,\scred,\attrs) \coloneqq \lbrace \pcif \attrs
     \subseteq \sring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1; \pcelse
-\pcreturn 0 \rbrace$. That is, if we let the attributes in a credential be
-public keys, this function means that a credential will be issued if all the
-public keys specified as attributes to be included in the credential are part of
-the union of the ad hoc ring and the public key of the signer. We also define
-$\feval^{\attrs}(\usk,\cred,\msg) \coloneqq \lbrace \pcif \CCommit(\usk;0) \in
-\attrs: \pcreturn \attrs(\cred); \pcelse \pcreturn \bot \rbrace$, where
-$\attrs(\cred)$ is the function that returns all the attributes encoded in a
-credential. That is, if the public key of the signer is included in the ring,
-return all the attributes in the credential (i.e., all the public keys in the
-ring); otherwise, abort. Finally, let $\finsp^0(\yeval,\usk,\cred,\msg) = 0$.
+    \pcreturn 0 \rbrace \nonumber \\
+  & \feval^{\attrs}(\usk,\cred,\msg) \coloneqq \lbrace \pcif \CCommit(\usk;0) \in
+    \attrs: \pcreturn \attrs(\cred); \pcelse \pcreturn \bot \rbrace \nonumber \\
+  & \finsp^0(\yeval,\usk,\cred,\msg) \coloneqq 0 \label{eq:uas-ring-funcs}
+\end{align}
+
+Where \sring is some (arbitrary) ad hoc set containing the public keys of the
+users that the signer wants to include in its ring. In $\NIZKRel_{\Sign-prv}$
+the public keys of the issuers are now part of the witness in the NP relation,
+which means that they will not be revealed in the proofs. Also, observe that, if
+we let the attributes in a credential be public keys, $\fissue^{\sring}$ means
+that a credential will be issued if all the public keys specified as attributes
+to be included in the credential are part of the union of the ring and the
+public key of the signer. To build $\feval^{\attrs}$, we define $\attrs(\cred)$
+to be the function that returns all the attributes encoded in a credential.
+Then, if the public key of the signer is included in the ring, $\feval^{\attrs}$
+returns all the attributes in the credential (i.e., all the public keys in the
+ring); otherwise, it aborts. Finally, let $\finsp^0$ disallows any
+de-anonymization.
 
@@
 \subsection{Multimodal Private Signatures}
+\label{ssec:uas-mps}
 
@@
 With this alternative definition, we can achieve a generalisation of MPS
-basically by, insted of returning the plaintext \yeval value, returning an
+basically by, instead of returning the plaintext \yeval value, returning an
 encryption of it under the opener's public key; additionally proving 
 that the value used to compute the output of \finsp is the plaintext \yeval
-value. In more detail, given any \feval function, we first define an
-encrypted variant $\feval^{enc}(\usk,\scred,\msg) \coloneqq \lbrace \yeval
+value. In more detail, we define an extended $\NIZKRel_{\Sign-enc}$ relation,
+and, given any \feval function, a variant $\feval^{enc}$ operating on an
+encryption of \yeval. Both are specified in \esref{eq:uas-mps-funcs}.
+
+\begin{align}
+  & \NIZKRel_{\Sign-enc} \coloneqq \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r),
+    (\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \nonumber \\
+  & \hspace*{6.00em}\Ec = \EEnc(\Eek,\yinsp;r) \land \nonumber \\
+  & \hspace*{6.00em}\forall \cred \in \scred,\SBCMVerify(\ipk_{\cred},\cred,\usk,
+  \attrs_{\cred}) = 1) \land \nonumber \\
+  & \hspace*{6.00em}\yeval = \EEnc(\opk,\feval(\usk,\scred,\msg)) \land \nonumber \\
+  & \hspace*{6.00em}\yinsp = \finsp(\feval(\usk,\scred,\msg),\usk,\scred,\msg)
+    \rbrace \nonumber \\
+  & \feval^{enc}(\usk,\scred,\msg) \coloneqq \lbrace \yeval
     \gets \feval(\usk,\scred,\msg); \yeval' \gets \EEnc(\opk,\yeval); \pcreturn
-\yeval' \rbrace$.
-%
-Naturally, the $\NIZKRel_{\Sign}$ has to be correspondigly extended, as
-$\NIZKRel_{\Sign}^{enc} = \lbrace (\usk,\scred,\attrs_{\scred},\yinsp,r),(\msg,
-\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec = \EEnc(\Eek,\yinsp;r) \land
-\yeval = \EEnc(\opk,\feval(\usk,\scred,\msg)) \land \yinsp = \finsp(\feval(\usk,
-\scred,\msg),\usk,\scred,\msg) \land \forall \cred \in \scred,
-\SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$. This would
-also seem to require that the used public-key encryption scheme is IND-CCA.
+    \yeval' \rbrace \label{eq:uas-mps-funcs}
+\end{align}
+
+This would also require that the public-key encryption scheme is IND-CCA.
 
@@
 \subsection{Delegatable Credentials}
+\label{ssec:uas-delcred}
 
@@
 $a_1$. In this context, any owner of a credential of level $n$ can define an
-issuance function $\fissue^n \coloneqq \lbrace \pcif a_1 = n+1: \pcreturn 1;
-\pcelse \pcreturn 0 \rbrace$.
+issuance function $\fissue^n$, as in \eref{eq:uas-delcred-func}.
+
+\begin{align}
+  \fissue^n \coloneqq \lbrace \pcif a_1 = n+1: \pcreturn 1;
+  \pcelse \pcreturn 0 \rbrace \label{eq:uas-delcred-func}
+\end{align}
 

### 2022-05-18 prism-backend/research/gsac/model-gsac.tex
Minor edits and fixing typos.

@@
 formally state this property is in both cases frequently the same: the adversary
-picks two (honest) users (or credentials in the AC case), the game randomly
-chooses one of them, and lets the adversary request challenge
-signatures/presentations from it. The adversary wins if it succeeds in guessing
-which was the chosen user/credential better than guessing at random. In group
-signatures, the game must also restrict the adversary from opening challenge
-signatures. In anonymous credentials, the game must further constraint the
+requests signatures from one out of two challenge users/credentials, where the
+one actually producing the signatures is defined by a bit $b$. The adversary
+wins if it succeeds in guessing which was the chosen user/credential better than
+guessing at random. In group signatures, the game must also restrict the
+adversary from opening challenge
+signatures. In anonymous credentials, the game must constraint the
 adversary to pick credentials that have some common subset of attributes, and
@@
      \gpk \gets (\ipk,\opk) \\
-     (\cid_0,\cid_1,\status) \gets
-     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN}(\choose,\gpk,\isk) \\
      b^* \gets
-     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN,\CHALb}(\guess,\gpk,\isk,\status) \\
+     \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN,\CHALb}(\gpk,\isk,\status) \\
      \pcreturn b^*
@@
     (\sig,\dattrs,\msg) \gets
-    \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
+    \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN}(\gpk,\osk) \\
     \pcif \Verify(\gpk,\sig,\dattrs,\msg) = 0: \pcreturn 0 \\

### 2022-05-18 prism-backend/research/gsac/model-uas.tex
Minor edits and fixing typos.

@@
           \pcif \oid \in \CO: \pcreturn \bot \\
+          \pcif \feval \notin \famfeval: \pcreturn \bot \\          
           \pcif \yeval = \feval(\UK[\cuid_0],\CRED[\cscid_0],\msg) \neq \\
@@
           \pcif \uid \notin \HU: \pcreturn \bot \\
+          \pcif \feval \notin \famfeval: \pcreturn \bot \\
           (\sig,\yeval) \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,
@@
   output}. Other than this, the overall approach is similar: as
-in group signatures and anonymous credentials, the adversary picks two pairs of
-honest users and credential sets. We also require the adversary to pick an
-evaluation function and an opener (hence, an opening function). Then, the
-user-credential pair defind by the value of $b$ (unknown to the adversary) is
-used to program the \CHALb oracle. The formal specification of the anonymity
-game is given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,
-\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,
-\WREG,\SIGN,\OPEN)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,
-\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$
+in group signatures and anonymous credentials, the adversary asks for challenge
+signatures from either one of two honest users and credential sets -- bit $b$,
+unkown to the adversary, defining which one is used. Note that the adversary
+also has to pick a signature valuation function \feval, as well as an opener
+(passed as arguments to the \SIGN and \CHALb oracles). The formal specification
+of the anonymity game is given in \figref{fig:exp-uas-anonb}, where $\Oanon
+\gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace
+\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$
 
 \begin{figure}[htp!]
+  \centering
   \procedure[linenumbering]{$\ExpAnonb(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
-     (\cuid_0,\cscid_0,\cuid_1,\cscid_1,\feval,\status) \gets \adv^{\Oanonc}
-     (\choose,\parm) \\
-     \pcif \feval \notin \famfeval: \pcreturn \bot \\
-     b^* \gets \adv^{\Oanong} (\guess,\status) \\
+     b^* \gets \adv^{\Oanon} (\status,\parm) \\
      \pcreturn b^*

### 2022-05-24 prism-backend/research/gsac/transformations-uas.tex
Fixed typo.
Full proofs for security of CUASRing.

@@
   & \fissue^1(\usk,\scred,\attrs) \coloneqq 1 \nonumber \\
-  & \feval^{\dattrs}(\usk,\cred,\msg) \coloneqq \dattrs(\cred)
-  & \finsp^{\upk}(\yeval,\usk,\scred,\msg) \coloneqq \CCommit(\usk;0) \nonumber \\
+  & \feval^{\dattrs}(\usk,\cred,\msg) \coloneqq \dattrs(\cred) \nonumber \\
+  & \finsp^{\upk}(\yeval,\usk,\scred,\msg) \coloneqq \CCommit(\usk;0)
     \label{eq:uas-gsac-funcs}
@@
 \label{ssec:uas-ring}
+\todo{This subsection needs much refinement.}
 
@@
 
+\todo{Explain the following better...}
 To reach (vanilla) ring signatures from \UAS, we have to slightly alter our
@@
 $\NIZKRel_{\Sign}$ defined in \secref{ssec:generic-construction-uas} reveals the
-issuers' public keys. This is a problem as, intuitively, the signer in a ring
+public key of the issuer of each credential used to produce the signatures.
+This is a problem as, intuitively, the signer in a ring
 signature is a sort of issuer for the ad hoc group. To hide the issuer, we
@@
 
-Where \sring is some (arbitrary) ad hoc set containing the public keys of the
-users that the signer wants to include in its ring. In $\NIZKRel_{\Sign-prv}$
+Where $\usk \gets \isk$ for each issuer/user and, consequently 
+\sring is some (arbitrary) ad hoc set containing the public keys of the
+users (issuers) that the signer wants to include in its ring%
+\footnote{Note that, implicitly, this conditions that the space of issuer public
+  keys is a subset of \AttrSpace. If this is not the case ``by default'', this
+  can be achieved via some appropriate mapping (e.g., an FDH or a XOF
+  \needcite). That is, instead of having the ring be a set of {\ipk}s, we
+  have the ring be a set of $F({\ipk}s)$, where $F$ is an appropriate mapping.
+  For simplicity of exposition, we assume that the space of issuer public keys
+  is compatible with \AttrSpace.}.
+In $\NIZKRel_{\Sign-prv}$
 the public keys of the issuers are now part of the witness in the NP relation,

### 2022-05-24 prism-backend/research/gsac/app-model-related.tex
Adding missing appendix.

\section{Models of Related Schemes}
\label{app:related-models}

In the following subsections we reproduce models of related schemes in the
literature. Then, we give concrete \fissue, \feval and \finsp functions that
make \UAS mimic their functionality. Finally, we prove for each case that
\UAS -- restricted with the corresponding functions -- indeed meets their
security models, thus proving that \UAS is a generalization of all of them.

\subsection{Group Signatures}
\label{sapp:related-models-gs}

We adopt the model in \cite{bsz05}, where security of group signatures is
defined according to the games in \figref{fig:model-gs}.

\subsection{Group Signatures with Message Dependent Opening}
\label{sapp:related-models-gsmdo}

\subsection{Ring Signatures}
\label{sapp:related-models-rs}

We adopt the model in \cite{bkm06}, where security of ring signatures is
defined according to the games in \figref{fig:model-rs}. A ring signature
scheme consists of three algorithms $(KeyGen,Sign,Verify)$. Roughly,
$((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar)$ produces $n$
signing key pairs, $\sig \gets Sign(\sk_i,R,\msg)$ creates a signature for
anonymity set $R \subseteq \lbrace \pk_1, \dots, \pk_t \rbrace$, using secret
key $\sk_i$, associated to some $\pk_i \in R$; and $1/0 \gets Verify(R,\sig,
\msg)$ checks if \sig is a valid signature over \msg for ring $R$.

\begin{figure}[ht!]
  \centering
  \scalebox{0.9}{      
    \begin{minipage}[t]{0.55\textwidth}        
      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (i_0,i_1,R,\msg,\st) \gets \adv^{SIGN}(\pk_1,\dots,\pk_n) \\
        \pcif % R \not\subseteq \lbrace [n] \rbrace \lor
        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \notin R \lor %\\
        i_0 = i_1: \pcreturn \bot \\
        \sig \gets Sign(\sk_{i_b},R,\msg)) \\
        b^* \gets \adv(\sig,\st) \\
        \pcreturn b^*
      }        
    \end{minipage}
  }
  \scalebox{0.9}{      
    \begin{minipage}[t]{.5\textwidth}
      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
        (R,\sig,\msg) \gets \adv^{SIGN,CORR}(\pk_1,\dots,\pk_n) \\
        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
        \pcreturn 1~\pcif R \subseteq [n] \setminus CU = \emptyset~\land \\
        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg) \\
        \pcreturn 0
      }       
    \end{minipage}      
  }
  \caption{Security games for ring signatures \cite{bkm06}. The SIGN oracle
    accepts a $(i,R,\msg)$ tuple, where $pk_i$ must be part of $R$, and
    returns $\sig \gets Sign(\sk_i,R,\msg)$. The oracle $CORR$ accepts an
    index $i$, and lets $\adv$ learn $\sk_i$. Corrupted user indexes are
    added to list $CU$.}
  \label{fig:model-rs}  
\end{figure}

Intuitively, a ring signature scheme $rs$ is anonymous if, for every p.p.t.
\adv, $|\Pr[\Exp^{anon-1}_{\adv,rs}(1^\secpar)] = 1| -
|\Pr[\Exp^{anon-1}_{\adv,rs}(1^\secpar)] = 0|$ is a negligible function of
$1^\secpar$; and a ring signature scheme $rs$ is unforgeable if, for every
p.p.t. \adv, the probability that $\Exp^{forge}_{\adv,rs}(1^\secpar)$ returns
$1$ is also negligible in $1^\secpar$. For short, we say that a ring signature
scheme meeting both anonymity and unforgeability as specified above, is a secure
ring signature scheme.

\subsubsection{\CUASRing Construction.} %
We prove that, as specified in \secref{ssec:uas-ring}, our \CUASGen construction
for \UAS, with alternative NIZK relationship $\NIZKRel_{\Sign-prv}$ for signing,
issuance function $\fissue^{\sring}$, signature evaluation function
$\feval^{\attrs}$, and inspection function $\finsp^0$, is a secure ring
signature scheme. Thus, in this section, when we write \CUASGen, we refer to
its specific variant built from the previous modifications.

\begin{description}  
\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in \CUASGen, but using
  $\NIZKRel_{\Sign-prv}$ instead of $\NIZKRel_{\Sign}$.  
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] As in \CUASGen, using
  $\fissue^{\sring}$.  
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp).$] As in \CUASGen, where every
  opener that wants to be a valid opener in \CUASRing, needs to set \finsp to
  $\finsp^0$.  
\item[$\usk \gets \UKeyGen(\parm).$] Can only be run after \IKeyGen. Let 
  $\usk \gets \isk$.
\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
  The user picks a ring from an (publicly) available list of issuers (users),
  i.e. $\sring \gets \lbrace \ipk_i \rbrace_{i \in [t]}$, for some $t$. Then,
  runs the $\langle \Obtain,\Issue \rangle$ protocol as in \CUASGen, acting both
  as user and as issuer, and using $\fissue^{\sring}$ as issuance function.
  \attrs are the public keys of the users (issuers) to be included in the ring.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval).$] As in
  \CUASGen, using $\feval^{\attrs}$ as sign evaluation function, using
  as credential for signing the credential used in the desired $\langle \Obtain,
  \Issue \rangle$ protocol and, as \opk, any previously registered \opk (i.e.,
  such that $\finsp=\finsp^0$).
\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in \CUASGen.
  Note that $\sipk = \sring$, and $\feval=\feval^{\attrs}$.
\item[$\Open$ and $\Judge$.] As in \CUASGen. Note that $\finsp=\finsp^0$.
\end{description}

\todo{I guess we need to show that changing the NIZK for signing does not affect
  security. This leads to ``What are the conditions that need to be checked/cannot
  be altered in the default NIZK sign, that make \CUASGen secure?'' }

\paragraph{Security of \CUASRing.} %
We prove next that our \CUASRing construction is anonymous and unforgeable, if
the underlying \CUASGen construction is secure.

\begin{theorem}[Anonymity of \CUASRing]
  If the base \CUASGen construction is anonymous according to
  \defref{def:anonymity-uas}, then \CUASRing is an anonymous ring signature
  scheme.
\end{theorem}

\begin{proof}
  Assume $\adv$ is an adversary against ring signature anonymity for \CUASRing.
  Then, we build \advB against anonymity of \CUASGen. Concretely, \advB first
  generates $n$ keypairs by running its \IGEN (with $\fissue^{\sring}$) and
  \HUGEN oracles, and runs \OGEN at least once (with $\finsp^0$). Then, invokes
  $\adv$ passing as public keys the public keys of the $n$ generated issuers
  (users in \CUASRing). $\adv$'s $SIGN(i,R,\msg)$ queries are processed as
  follows. If user $i$ has not yet produced a credential for ring $R$, \advB
  makes a call to its \OBTAIN oracle, using $R$ as attribute set. If such a
  credential was already produced, then reuse it. Then, \advB uses the
  corresponding user and credential identifiers as parameters to a query to its
  own \SIGN oracle (specifying $\feval^{\attrs}$ as signature evaluation
  function). Eventually, $\adv$ outputs two user indexes, a ring $R$, and
  message \msg. If the checks at line 4 of \figref{fig:model-rs} pass, \advB
  generates the challenge signature by calling its own \CHALb oracle, and passes
  the result to $\adv$. Finally, \advB outputs whatever $\adv$ outputs.
  %
  \qed
\end{proof}

\begin{theorem}[Unforgeability of \CUASRing]
  If the base \CUASGen construction is non-frameable according to
  \defref{def:frame-uas}, then \CUASRing is an unforgeable ring signature
  scheme.
\end{theorem}

\begin{proof}
  Assume $\adv$ against unforgeability of \CUASRing wins the game. We build
  \advB winning the non-frameability game of \CUASGen with the same probability.
  %
  \advB prepares the environment as the adversary \advB against anonymity,
  and answers \adv's queries to the $SIGN$ oracle also as in the anonymity
  proof. To answer \adv's queries to its $CORR$ oracle, \advB leverages the
  \ICORR oracle in the non-frameability game for \UAS. Finally, \advB outputs
  whatever $\adv$ outputs.

  Note that, if $\adv$ wins its game, it means that the public keys of the
  issuers in $R$ all belong to uncorrupted users. Since the signature is
  accepted by $Verify$ at line 3 of the ring signature unforgeability game,
  there exists some \uid with an \usk matching the check at line 6 in the
  non-frameability game. Moreover, since $\adv$ never queried its $SIGN$
  oracle, then by construction there cannot exist a matching entry in the
  $\SIG[\uid]$ table. Thus, \advB wins the non-frameability game whenever
  $\adv$ wins its unforgeability game. Since \CUASGen is non-frameable, then
  this probability must be negligible.
  %
  \qed
\end{proof}

\subsection{Anonymous Credentials}
\label{sapp:related-models-ac}

We adopt the model in \cite{fhs19}, where security of anonymous credentials
(with selective disclosure) is defined according to the games in
\figref{fig:model-ac}.

\subsection{Delegatable Anonymous Credentials}
\label{sapp:related-models-dac}

\subsection{Multimodal Private Signatures}
\label{sapp:related-models-mps}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas"
%%% End:

### 2022-05-26 prism-backend/research/gsac/app-model-related.tex
Added proofs for UAS => GS and UAS => AC.

@@
-\section{Models of Related Schemes}
+\section{\UAS-Based Instantiations of Related Schemes}
 \label{app:related-models}
@@
 
-We adopt the model in \cite{bsz05}, where security of group signatures is
-defined according to the games in \figref{fig:model-gs}.
+We adopt the model in \cite{bsz05}. In this abstraction
+of group signatures, the opener returns an index uniquely identifying the group
+member that created a signature, along with a correctness proof. For ease of
+exposition, assume that, w.l.o.g., this index is just the public key that the
+group member chooses when joining the group\footnote{The user public key is
+  assumed to be accessible from a public table in \cite{bsz05}, so it is direct
+  to translate the public key into an index, if needed.}. A group signature
+scheme, according to \cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign,
+\Verify, \Open and \Judge algorithms, as well as an $\langle\Obtain,\Issue
+\rangle$ interactive protocol. Their description is very similar to that of
+\GSAC, so we refer to \cite{bsz05} for detailed descriptions. For ease of
+reference, we replicate the security games in \figref{fig:model-gs}.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.45\textwidth}        
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gs}(1^\secpar)$}{%
+        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
+        d \gets \adv^{\mathcal{O}^{anon}}(\gpk,\isk) \\
+        \pcreturn d 
+      }
+
+      \vspace*{5em}
+
+      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gs}(1^\secpar)$}{%
+        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
+        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
+        (\gpk,\osk,\isk) \\
+        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
+        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
+        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
+        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
+        GSig(\PRVUK[\upk],\msg) \\
+        \pcreturn 0
+      }       
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.55\textwidth}
+      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gs}(1^\secpar)$}{%
+        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
+        (\msg,\sig) \gets \adv^{\mathcal{O}^{trace}}(\gpk,\osk) \\
+        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
+        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
+        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
+        = 0: \\ 
+        \pcind \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for group signatures \cite{bsz05}, only with minor    
+    ``harmless'' edits to compare easier with \CUASGS. Concretely, since we
+    output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
+    $\upk \notin \HU \cup \CU$. For the oracles' definitions, check the
+    referenced paper.
+    $\mathcal{O}^{anon} \gets \lbrace Ch,Open,SndToU,WReg,USK,CrptU \rbrace$,
+    $\mathcal{O}^{trace} \gets \lbrace SndToI,AddU,RReg,USK,CrptU \rbrace$,
+    and $\mathcal{O}^{frame} \gets \lbrace SndToU,WReg,GSig,USK,CrptU \rbrace$.
+  }
+  \label{fig:model-gs}  
+\end{figure}
+
+\subsubsection{\CUASGS construction.} %
+We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
+construction for \UAS, restricted to $\fissue^1$ as issuance function,
+$\feval^0$ as signature evaluation function, and $\finsp^{\upk}$ as opening
+function, is a secure group signature scheme according to the \cite{bsz05}
+model. We first quickly define the algorithms, and then prove security.
+
+\begin{description}
+\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
+  of \CUASGen, and one instance of \IKeyGen and \OKeyGen. Assigns the public
+  keys to \gpk.
+\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \UKeyGen from \CUASGen, and
+  computes $\CCommit(\usk;0)$ as \upk.
+\item[$\langle \cred,\utrans \rangle \gets
+  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
+  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Note that, to
+  constraint to only one credential per user, it suffices to require the user
+  to prove that the ``randomness'' it uses when committing to its private key
+  is actually $0$, and check whether the received commitment has been seen
+  before. For details, see the BBS+ instantiation of the underlying \SBCM
+  building block in \secref{sapp:sbcm}.
+\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
+  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen.
+  Simply returns \sig.
+\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
+  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
+  outputs.
+\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
+  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
+  0,\msg,\feval^0)$. Note that, internally, the latter call to \Open runs
+  $\finsp^{\upk}$, where $\upk = \CCommit(\usk;0)$, just as proved in $\langle
+  \Obtain,\Issue\rangle$.
+\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
+  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
+  0,\msg)$.
+\end{description}
+
+\paragraph{Security of \CUASGS.} %
+We prove that our \CUASGS construction is a secure group signature scheme,
+according to \cite{bsz05}, if the underlying \CUASGen construction is secure.
+
+\begin{theorem}[Anonymity of \CUASGS]
+  If the base \CUASGen construction is anonymous according to
+  \defref{def:anonymity-uas}, then \CUASRing is an anonymous group signature
+  scheme.
+\end{theorem}
+
+\todo{Introducing $(f,g,h)-\CUASGen$ naming convention. Describe it elsewhere.}
+
+\begin{proof}
+  Assume an adversary \adv~ against anonymity in \CUASGS. This directly leads
+  to an adverary \advB against anonymity of the $(\fissue^1,\feval^0,
+  \finsp^{\upk})-\CUASGen$ instance.
+
+  Concretely, observe that calls to \adv's $Ch,Open,SndToU,WReg,USK,CrptU$
+  oracles can be directly simulated by calls to \advB's oracles $\CHALb,
+  \OPEN,\HUGEN,\WREG,\CUGEN$ oracles. Thus, if \adv~ guesses its bit $b$
+  with non-negligible probability, this directly leads to a non-negligible
+  probability of guessing \advB's challenge bit.
+  \qed
+\end{proof}
+
+\begin{theorem}[Traceability of \CUASGS]
+  If the base \CUASGen construction has unforgeable signing according to
+  \defref{def:sign-forge-uas}, then \CUASGS is a traceable group signature
+  scheme.
+\end{theorem}
+
+\begin{proof}
+  Assume an adversary \adv~ against traceability in \CUASGS. We build an
+  adversary \advB against sign unforgeability of the $(\fissue^1,\feval^0,
+  \finsp^{\upk})-\CUASGen$ instance.
+
+  \advB's simulation of \adv~ environment is as in the proof for anonymity
+  of \CUASGS. \advB simply outputs whatever \adv~ outputs in line 2 of its
+  traceability game. Note that, as \CUASGS is a specific instantiation of
+  \CUASGen, whenever \CUASGS accepts a signature, so does \CUASGen. Concretely,
+  assume that \adv~ wins the traceability game in \figref{fig:model-gs} with
+  $\upk \notin \HU \cup \CU$ at line 5. This implies that the check at line 11
+  of the sign unforgeability game (\figref{fig:exp-uas-unfor-sign}) for \CUASGen
+  outputs $0$ for all known {\uid}s. Similarly, if \adv~ wins the traceability
+  game with condition $\Judge(\dots)=0$ at line 5, then \advB wins its sign
+  unforgeability game with the corresponding check at line 6 in
+  \figref{fig:exp-uas-unfor-sign}.
+  %
+  \qed
+\end{proof}
+
+\begin{theorem}[Non-frameability of \CUASGS]
+  If the base \CUASGen construction is non-frameable according to
+  \defref{def:frame-uas}, then \CUASGS is a traceable group signature
+  scheme.
+\end{theorem}
+
+\begin{proof}
+  Assume an adversary \adv~ against non-frameability in \CUASGS. We build an
+  adversary \advB against non-frameability of the $(\fissue^1,\feval^0,
+  \finsp^{\upk})-\CUASGen$ instance.
+
+  \advB's simulation of \adv~ environment is as in the proof for anonymity
+  of \CUASGS. \advB simply outputs whatever \adv~ outputs at line 2 of its
+  game. Observe that a winning condition for \adv~ directly implies a winning
+  condition for \advB. Concretely, if $\upk \in \HU \land \PRVUK[\upk] \neq
+  \bot$ in \adv's game, then $\exists \uid \in \HU~\suchthat~\UK[\uid]=\usk$
+  for \advB (line 6 of its game). Similarly, if \Judge returns $1$ in \adv's
+  game, \advB's \Judge also returns $1$ at line 4. Finally, if \adv~ does not
+  corrupt the owner of \upk, then $\uid \in \HU$ in \advB's game, and if \adv
+  does not query its $SIGN$ oracle, then there does not exist a matching entry
+  in $\SIG[\uid]$ for \advB either. Consequently, as stated, \advB wins its
+  non-frameability every time that \adv does.
+  \qed
+\end{proof}
 
@@
 \subsubsection{\CUASRing Construction.} %
-We prove that, as specified in \secref{ssec:uas-ring}, our \CUASGen construction
+We show that, as specified in \secref{ssec:uas-ring}, our \CUASGen construction
 for \UAS, with alternative NIZK relationship $\NIZKRel_{\Sign-prv}$ for signing,
@@
 \paragraph{Security of \CUASRing.} %
-We prove next that our \CUASRing construction is anonymous and unforgeable, if
+We prove that our \CUASRing construction is anonymous and unforgeable, if
 the underlying \CUASGen construction is secure.
@@
 We adopt the model in \cite{fhs19}, where security of anonymous credentials
-(with selective disclosure) is defined according to the games in
-\figref{fig:model-ac}.
+(with selective disclosure). Therein, an anonymous credential scheme is
+defined via $OrgKeyGen$ and $UserKeyGen$ algorithms (roughly equivalent to
+\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
+interactive protocols. The issuance interactive protocol is equivalent to
+the issuance protocol in \UAS. Similarly, $Show,Verify$ is equivalent to
+the interactive extension of \Sign and \Verify in \UAS, which we show how
+to build in \secref{ssec:variants-gsac} (for \GSAC, but the case for \UAS is
+equivalent). The security definitions rely on $HU, CU, ObtIss, Obtain, Issue,
+Show$, and $LoR$ oracles, which are essentially equivalent to our \HUGEN,
+\CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb oracles. We refer to
+\cite{fhs19} for the full details. For ease of reference, we summarize the
+security definitions in \cite{fig:model-ac}, with inocuous adaptations to
+make them more suitable for comparison with our definitions.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.4\textwidth}        
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
+        b^* \gets \adv^{HU,CU,Obtain,Show,LoR} \\
+        \pcreturn b^*
+      }        
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.6\textwidth}
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
+        (\opk,\osk) \gets OrgKeyGen(1^\secpar) \\        
+        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\opk) \\
+        (\cdot,b) \gets \langle \adv(\st),\Verify(\opk,D) \rangle \\
+        \pcif b = 1 \land \forall j: \OWNR[j] \in \CU
+        \implies D \not\subseteq \ATTR[j]: \\
+        \pcind \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for anonymous credentials with selective disclosure
+    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
+    \secref{ssec:model-uas}.}
+  \label{fig:model-ac}  
+\end{figure}
+
+\subsubsection{\CUASAC Construction.} %
+We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
+construction for \UAS, restricted to $\fissue^1$ as issuance function,
+$\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as opening
+function, is a secure anonymous credential scheme according to the \cite{fhs19}
+model. We first quickly define the algorithms, and then prove security. Note
+that, for better alignment with \UAS, we add a common setup process which is
+part of $OrgKeyGen$ in \cite{fhs19}. The change is inocuous functionality- and
+security-wise, though.
+
+\begin{description}
+\item[$\parm \gets \Setup(1^\secpar)$.] Runs \Setup from our \CUASGen
+  construction.
+\item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs \IKeyGen from our
+  \CUASGen construction, setting $\fissue^1$ as issuance function.
+\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] Runs \UKeyGen from the
+  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
+\item[$\langle \cred/\bot,\top/\bot \rangle \gets
+  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
+  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
+  $\fissue^1$ as issuance function.
+\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
+  \Verify(\opk,\dattrs) \rangle$.]
+  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
+  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
+  open function.
+\end{description}
+
+\paragraph{Security of \CUASAC.} %
+We prove that \CUASAC is an anonymous and unforgeable anonymous credential
+scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
+is anonymous and has unforgeable signing. Note that issuance unforgeability
+of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
+leveraging other credentials not any fixed custom issuance policy. Thus,
+signature unforgeability from \UAS is enough.
+
+\begin{theorem}[Anonymity of \CUASAC]
+  If the base \CUASGen construction is anonymous according to
+  \defref{def:anonymity-uas}, then \CUASAC is an anonymous AC scheme
+  according to \cite{fhs19}.
+\end{theorem}
+
+\begin{proof}
+  Given \adv~ against anonymity of \CUASAC as defined in \cite{fhs19}, we build
+  an adversary \advB against anonymity of \CUASGen as defined in
+  \defref{def:anonymity-uas}.
+
+  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
+  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR$, \advB redirects to
+  \HUGEN,\CUGEN,\OBTAIN,\SIGN,\CHALb, respectively. Note that ``translating''
+  the inputs from the former into inputs for the latter is trivial.
+  Obviously, if \adv~ wins in its anonymity game, then so does \advB with the
+  same probability.
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability of \CUASAC]
+  If the base \CUASGen construction has sign unforgeability according to
+  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
+\end{theorem}
+
+\begin{proof}
+  Given \adv~ against unforgeability of \CUASAC as defined in \cite{fhs19}, we
+  build an adversary \advB against sign unforgeability of \CUASGen as defined in
+  \defref{def:sign-forge-uas}.
+
+  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
+  that \adv~ wins its game. Note that, since $b=1$ in line 4 of the
+  unforgeability game of \figref{fig:model-ac}, then by construction, \Verify
+  also returns $1$ in the sign unforgeability game of \UAS. In addition, if
+  there is no corrupt user with a credential containing $D$, then this leads to
+  \advB winning at line 8 in \figref{fig:exp-uas-unfor-sign}, as no credential
+  owned by a corrupt user that can be extracted can make the $\feval^{\dattrs}$
+  function output $\yeval=D$. Thus, \advB wins with the same probability as
+  \adv~ does.  
+  %
+  \qed
+\end{proof}
 

### 2022-05-28 prism-backend/research/gsac/app-model-related.tex
Added proofs for GS-MDO and DAC special cases.

@@
     $\mathcal{O}^{anon} \gets \lbrace Ch,Open,SndToU,WReg,USK,CrptU \rbrace$,
-    $\mathcal{O}^{trace} \gets \lbrace SndToI,AddU,RReg,USK,CrptU \rbrace$,
+    $\mathcal{O}^{trace} \gets \lbrace SndToI,AddU,RReg,GSig,USK,CrptU \rbrace$,
     and $\mathcal{O}^{frame} \gets \lbrace SndToU,WReg,GSig,USK,CrptU \rbrace$.
@@
   If the base \CUASGen construction is non-frameable according to
-  \defref{def:frame-uas}, then \CUASGS is a traceable group signature
+  \defref{def:frame-uas}, then \CUASGS is a non-frameable group signature
   scheme.
@@
 \label{sapp:related-models-gsmdo}
+
+We cannot build the exact same functionality, nor follow the exact same security
+model as in the group signatures with message dependent opening (GS-MDO) scheme
+described in \cite{ehk+19}. Simply because, therein, the opening functionality
+is divided in two authorities: the admitter, who decides which messages are
+subject to be opened or not, and generates a token that enables opening
+signatures over such messages; and the opener, who performs the actual opening,
+but cannot do it without the tokens generated by the admitter. Intuitively, this
+can be seen as a sort of ``distribution'' of the opening capability. We define
+a variant of this model in which the admitter and opener are combined back into
+one entity (the opener), who can only open signatures over predefined messages,
+but cannot open any other signature. Moreover, our variant directly supports the
+scenario of multiple such openers, each being able to open only signatures
+over different messages. Note that it would not be hard to apply thresholding
+techniques to extend this case so that our ``unified'' opener role is shared
+across multiple entities, who have to cooperate in order to open a signature
+\needcite, thus achieving something very close ``in spirit'' to the scheme in
+\cite{ehk+19}. In addition, while \cite{ehk+19} follows the static group
+signature setting, we move to the dynamic one. Informally, our variant of GS-MDO
+is composed of the following algorithms: \Setup,
+\IKeyGen, \OKeyGen, \UKeyGen, \Sign, \Verify, \Open; as well as the $\langle
+\Obtain, \Issue \rangle$ interactive protocol. \OKeyGen generates an opening
+key pair which is already configured to open signatures only over some fixed
+(but arbitrary) set of messages. The remaining algorithms are as usual, so we
+defer a more detailed description to the construction. The oracles are the same
+as in \UAS. The resulting security model is given in \figref{fig:model-gsmdo},
+which we adapt from \cite{ehk+19}.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.45\textwidth}        
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gsmdo}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets \IKeyGen(\parm) \\
+        b^* \gets \adv^{\mathcal{O}^{anon}}(\parm,\ipk) \\
+        \pcreturn b^*
+      }
+
+      \vspace*{5em}
+
+      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gsmdo}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets \IKeyGen(\parm) \\
+        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
+        (\ipk,\isk) \\
+        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
+        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
+        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
+        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
+        GSig(\PRVUK[\upk],\msg) \\
+        \pcreturn 0
+      }       
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.55\textwidth}
+      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gsmdo}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets \IKeyGen(\parm) \\
+        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{trace}}
+        (\ipk,\opk,\osk) \\
+        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
+        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
+        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
+        = 0: \\ 
+        \pcind \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for our GS-MDO variant.
+    $\mathcal{O}^{anon} \gets \lbrace \OGEN^{\smsg},\HUGEN,\CUGEN,\WREG,
+    \OBTAIN,\SIGN,\OPEN,\CHALb \rbrace$; $\mathcal{O}^{trace} \gets \lbrace
+    \OGEN,\HUGEN,\CUGEN,\ISSUE,\OBTISS,\RREG,\SIGN \rbrace$;
+    $\mathcal{O}^{frame} \gets \lbrace \OGEN,\HUGEN,\CUGEN,\WREG,
+    \OBTAIN,\SIGN \rbrace$. $\OGEN^{\smsg}$ is like \OGEN, but only accepting
+    functions of type $\finsp^{\smsg}$.
+  }
+  \label{fig:model-gsmdo}  
+\end{figure}
+
+\subsubsection{\CUASGSMDO construction.} %
+We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
+construction for \UAS, restricted to $\fissue^1$ as issuance function,
+$\feval^0$ as signature evaluation function, and $\finsp^{\smsg}$ as opening
+function, is a secure group signature scheme with message dependent opening
+as modelled in \figref{fig:model-gsmdo}. We first quickly define the algorithms,
+and then prove security.
+
+\begin{description}
+\item[$\parm \gets \Setup(1^\secpar)$.] Like in vanilla \CUASGen.
+\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Like the \UKeyGen function for
+  \CUASGS, in \secref{sapp:related-models-gs}.
+\item[$\langle \cred,\utrans \rangle \gets
+  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Like the corresponding
+  protocol in in vanilla \CUASGS, \secref{sapp:related-model-gs}.
+\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Like in vanilla \CUASGen, limited
+  on evaluation functions $\feval^0$ and opening functions $\finsp^{\smsg}$.
+\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Like in vanilla \CUASGen.
+\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Like in vanilla
+  \CUASGen.
+\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Like in vanilla \CUASGen.
+\end{description}
+
+\paragraph{Security of \CUASGSMDO.} %
+Our \CUASGSMDO construction is a secure group signature scheme,
+according to the model in \figref{fig:model-gsmdo}, if the underlying \CUASGen
+construction is secure.
+
+Note that both  model construction are essentially restrictions to the model
+and construction of \CUASGen. Thus, security directly follows from security of
+\CUASGen.
+
+% \begin{theorem}[Anonymity of \CUASGSMDO]
+%   If the base \CUASGen construction is anonymous according to
+%   \defref{def:anonymity-uas}, then \CUASGSMDO is an anonymous group signature
+%   scheme.
+% \end{theorem}
+
+% \begin{proof}
+
+%   \qed
+% \end{proof}
+
+% \begin{theorem}[Traceability of \CUASGSMDO]
+%   If the base \CUASGen construction has unforgeable signing according to
+%   \defref{def:sign-forge-uas}, then \CUASGSMDO is a traceable group signature
+%   scheme.
+% \end{theorem}
+
+% \begin{proof}
+%   Traceability follows directly from the corresponding proof for \CUASGS.
+%   \qed
+% \end{proof}
+
+% \begin{theorem}[Non-frameability of \CUASGSMDO]
+%   If the base \CUASGen construction is non-frameable according to
+%   \defref{def:frame-uas}, then \CUASGSMDO is a non-frameable group signature
+%   scheme.
+% \end{theorem}
+
+% \begin{proof}
+%   Non-frameability follows directly from the corresponding proof for \CUASGS.
+%   \qed
+% \end{proof}
 
@@
   \CUASGen, using $\feval^{\attrs}$ as sign evaluation function, using
-  as credential for signing the credential used in the desired $\langle \Obtain,
-  \Issue \rangle$ protocol and, as \opk, any previously registered \opk (i.e.,
-  such that $\finsp=\finsp^0$).
+  as credential for signing the credential obtained in the desired $\langle
+  \Obtain,\Issue \rangle$ session and, as \opk, any previously registered \opk
+  (i.e., such that $\finsp=\finsp^0$).
 \item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in \CUASGen.
@@
 
+\todo{Naming gets a bit confusing here, as \cite{fhs19} use \opk as ``organization
+  public key'' and we use it as ``opener public key'', etc. Make some renaming
+  (probably, adopt our naming convention).}
+
 We adopt the model in \cite{fhs19}, where security of anonymous credentials
@@
 \begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.] Runs \Setup from our \CUASGen
-  construction.
+\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
+    and $(\opk',\osk') \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
+    construction. Returns $\parm \gets (\parm',\opk')$.
 \item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs \IKeyGen from our
@@
   using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
-  open function.
+  open function, with $\opk'$ from \parm as opener public key.
 \end{description}
@@
 
+We give a simple definition for delegatable anonymous credentials extending
+the anonymous credential model in \cite{fhs19}. Next, we briefly describe a
+construction based on $(\fissue^n,\feval^{n,\dattrs},\finsp^0)$-\CUASGen, and
+show that it satisfies our basic notion of delegatable anonymous credentials.
+Roughly, a delegatable anonymous credential scheme is an anononymous credential
+scheme in which every issuer of level $n$ can only issue credentials of level
+$n+1$. For simplicity, we restrict to the case of using only one credential per
+signature, but the generalization is trivial. Note that, in addition to the
+algorithms in \secref{sapp:related-models-ac}, we add a helper function $level$
+which, given an issuer's public key and its alleged level, returns $1$ if the
+level is correct, or $0$ otherwise.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.4\textwidth}        
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,dac}(1^\secpar)$}{%
+        b^* \gets \adv^{HU,CU,obtain,Show,LoR} \\
+        \pcreturn b^*
+      }        
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.6\textwidth}
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\        
+        (D,n+1,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\opk) \\
+        (\cdot,b) \gets \langle \adv(\st),\Verify(\opk,
+        D \cup \lbrace n+1 \rbrace)\rangle \\
+        \pcif b = 0: \pcreturn 0 \\
+        \pcif(\forall j: \OWNR[j] \in \CU \implies D \cup \lbrace n+1 \rbrace
+        \not\subseteq \ATTR[j])~\lor\\
+        \pcind level(\opk,n) = 0: \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for delegatable anonymous credentials with selective
+    disclosure based on \cite{fhs19}. \OWNR and \ATTR tables are essentially as
+    in \secref{ssec:model-uas}. $level(\opk,n)$ is a helper function that
+    returns the $1$ if the level of \opk is $n$, or $0$ otherwise.}
+  \label{fig:model-dac}  
+\end{figure}
+
+\subsubsection{\CUASDAC Construction.} %
+We adopt the simplification that the level of an issuer is encoded in its public
+key, and anybody can check the issuer's level via some publicly accessible
+mechanism. This can be ensured, e.g., by having each issuer post its
+  public key along with a proof of ownership of a level $n$ credential -- which
+  can be trivially done in \CUASGen.
+
+  \begin{description}
+  \item[$\parm \gets \Setup(1^\secpar)$.] As in \CUASAC.
+\item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs a variant of \IKeyGen from
+  our \CUASGen construction where, instead of using a conventional signature
+  scheme, the issuer leverages its own anonymous credential of level $n$ to
+  create a signature in which it only reveals the credential level. That is,
+  $\sig_{is} \gets \CUASGen.Sign(\isk,\opk',\cred,\msg_{is},\feval^{0,n})$,
+  for some random $\msg_{is}$, and $\opk'$ from \parm, where $\feval^{0,n}$ is a
+  signing evaluation function that reveals no attribute other than the level
+  of the credential. Let $\opk_{n-1}$ be the issuer of the credential \cred
+  (i.e., an issuer with level $n-1$). The current issuer of level $n$ publishes
+  its public key as $(\opk_{n-1},\fissue^n,\sig_{is},\msg_{is})$.
+\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] As in \CUASAC.
+\item[$\langle \cred/\bot,\top/\bot \rangle \gets
+  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
+  As in \CUASAC.
+\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
+  \Verify(\opk,\dattrs) \rangle$.]
+  As in \CUASAC, but using $\feval^{\dattrs,n}$ as signature evaluation
+  function.
+\end{description}
+
+\paragraph{Security of \CUASDAC.} %
+We need to define $level(\opk,n)$. This function first parses \parm
+as $(\parm',\opk')$, and \opk as $(\opk_{n-1},\fissue^n,\sig_{is},\msg_{is})$,
+and returns $\CUASGen.Verify(\opk_{n-1},\opk',\sig_{is},n,\msg_{is},
+\feval^{0,n})$.
+
+Given $level$, the security proofs are as for \CUASAC, with the addition that,
+in the unforgeability game, an adversary winning because of $level(\opk,n) = 0$
+can be directly used to break the sign unforgeability property of the underlying
+\CUASGen scheme.
+
 \subsection{Multimodal Private Signatures}

### 2022-05-28 prism-backend/research/gsac/transformations-uas.tex
Added proofs for UAS => GS and UAS => AC.
Added proofs for GS-MDO and DAC special cases.

@@
     \hline
+    GS & None & $\fissue^1$ & $\feval^0$ & $\finsp^{\upk}$ & Implied by \GSAC \\
+    AC\footnote{We show how to build ACs with selective disclosure, but ACs for
+    arbitrary claims are direct too.} & None & $\fissue^1$ & $\feval^{\dattrs}$ & $\finsp^0$ & Implied by \GSAC \\
     \GSAC & None & $\fissue^1$ & $\feval^{\dattrs}$ & $\finsp^{\upk}$
     & \secref{ssec:uas-gsac} \\
-    \bf GS-MDO & None & $\fissue^1$ & $\feval^0$ & $\finsp^{\smsg}$
+    \bf GS-MDO\footnote{We achieve something similar to GS-MDO, but not the
+    exact same model as in \cite{ehk+19}} & None & $\fissue^1$ & $\feval^0$ & $\finsp^{\smsg}$
     & \secref{ssec:uas-gsmdo} \\
@@
     \secref{ssec:uas-mps}.} & $\NIZKRel_{\Sign-enc}$ & Any & $\feval^{enc}$ & Any & \secref{ssec:uas-mps} \\
-    \bf Delegatable creds & None & $\fissue^n$ & Any & Any & \secref{ssec:uas-delcred} \\
+    \bf Delegatable creds & None & $\fissue^n$ & $\feval^n$ & Any & \secref{ssec:uas-delcred} \\
   \end{tabular}
@@
 Building delegatable credentials is also straightforward, thanks to the \fissue
-function. For instance, take the simplification of level-based delegation, where
-the owner of a credential of level $n$ can only issue credentials of level
-$n+1$. Without loss of generality, assume that the credential level is encoded
-in the first attribute of the credential (after the \usk), which we denote with
-$a_1$. In this context, any owner of a credential of level $n$ can define an
-issuance function $\fissue^n$, as in \eref{eq:uas-delcred-func}.
+and \feval functions. For instance, take the simplification of level-based
+delegation, where the owner of a credential of level $n$ can only issue
+credentials of level $n+1$. Without loss of generality, assume that the
+credential level is encoded in the first attribute of the credential (after the
+\usk), which we denote with $a_1$. In this context, any owner of a credential of
+level $n$ can define an issuance function $\fissue^n$, as in
+\eref{eq:uas-delcred-func}. Similarly, we may just have the signing evaluation
+function reveal the level of each credential used for signing, along with any
+other desired attribute, as in $\feval^{\dattrs,n}$, in
+\eref{eq:uas-delcred-func}. Note that it is straightforward to create more
+complex functions in both cases which, for instance, also take into account
+roles, or hiding the level but ensuring that it meets whatever desired rules.
 
 \begin{align}
-  \fissue^n \coloneqq \lbrace \pcif a_1 = n+1: \pcreturn 1;
-  \pcelse \pcreturn 0 \rbrace \label{eq:uas-delcred-func}
+  & \fissue^n(\usk,\scred,\attrs) \coloneqq \lbrace \pcif a_1 = n+1: \pcreturn 1;
+  \pcelse \pcreturn 0 \rbrace \nonumber \\
+  & \feval^{\dattrs,n}(\usk,\scred,\msg) \coloneqq \lbrace \pcreturn
+    \dattrs(\scred),a_1(\scred) \rbrace  
+  \label{eq:uas-delcred-func}
 \end{align}

### 2022-06-02 prism-backend/research/gsac/model-uas.tex
Full proofs for security of CUASRing.
Added proofs for GS-MDO and DAC special cases.
Upgrading model.

@@
 \begin{description}
-\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
+\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
   returns a global system parameter variable \parm. We assume that \parm are
@@
   input parameters.
-\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
+\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given global system
   parameters \parm, and the function \fissue to be used to check that credential
@@
   \IKeyGen to generate its issuing key pair. 
-\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
+\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given global system
   parameters \parm, and function \finsp, an opener runs \OKeyGen to generate
@@
   will be extractable from signatures.
-\item[$\usk \gets \UKeyGen(\parm)$.] Given global system parameters
+\item[$\UKeyGen(\parm) \rightarrow \usk$.] Given global system parameters
   \parm, returns a user's secret key.
-\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle
+\item[$\langle
   \Obtain(\usk,\scred,\attrs),
   \Issue(\isk,\sipk,\attrs))
-  \rangle$.] %
+  \rangle \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.] %
   This interactive protocol lets a user with key \usk running the
@@
   credential.
-\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.] %
+\item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval,\ceval)$.] %
   Upon receiving a user secret key \usk, opener public key \opk, a set of
   credentials \scred, a message \msg and evaluation
-  function \feval, returns signature \sig and value \yeval.
-\item[$1/0 \gets \Verify(\opk, \sipk,\sig,\yeval,\msg,\feval)$.]
-  Checks whether $(\sig,\yeval)$ is a valid signature
+  function \feval, returns signature \sig, a plaintext value \yeval,
+  and an encrypted value \ceval. For readability, we use \Sig to denote
+  the tuple $(\sig,\yeval,\ceval)$.
+\item[$\Verify(\opk, \sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
+  Checks whether $\Sig = (\sig,\yeval,\ceval)$ is a valid signature
   over message \msg, from a user with credentials issued by issuers with public
   keys in \sipk, for evaluation function \feval and opener key \opk.
-\item[$(\yinsp,\iproof)/\bot \gets \Open(\osk,\sipk,\sig,\yeval,\msg,\feval)$.]
+\item[$\Open(\osk,\sipk,\sig,\yeval,\msg,\feval) \rightarrow
+  (\yinsp,\iproof)/\bot$.]
   Executed by the opener with private key \osk. Receives a signature $(\sig,
@@
   the function outputs a value $\yinsp$.
-\item[$1/0 \gets \Judge(\opk,\sipk,\yinsp,\iproof,\sig,\yeval,\msg,\feval)$.] %
+\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
   Checks if \iproof is a valid opening correctness proof for the value \yinsp,
-  obtained by applying \Open to the the signature $(\sig,\yeval)$ over
-  message \msg, and for evaluation function \feval. 
+  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval,\ceval)$
+  over message \msg, and for evaluation function \feval. 
 \end{description}
@@
 \item[$\feval: (\usk,\scred,\msg)
-  \rightarrow \yeval$.] Signing evaluation functions, from a family of functions
-  \famfeval, can be set on a per-signature basis. They receive the user secret
-  key \usk, credentials \scred, and message to be signed \msg. \feval can be
-  used to control the information related to the signer that will be revealed
-  alongside a signature, and to modulate the behaviour of \finsp. Its outputs
-  \yeval must belong in a well defined set \rngfeval.
-\item[$\finsp: (\yeval,\usk,\scred,\msg) \rightarrow \yinsp$.]
+  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
+  family of functions \famfeval, can be set on a per-signature basis. They
+  receive the user secret key \usk, credentials \scred, and message to be signed
+  \msg. \feval can be used to control the information related to the signer that
+  will be revealed alongside a signature, and to modulate the behaviour of
+  \finsp. Its outputs two values, $\yeval^0$ and $\yeval^1$, where the former
+  is revealed in plaintext along with the signature, and $\yeval^1$ is encrypted
+  and used to modulate the behaviour of \finsp. Both values must belong in a
+  well defined set \rngfeval. For readability, we write
+  $\Yeval = (\yeval^0,\yeval^1)$.
+\item[$\finsp: (\Yeval,\usk,\scred,\msg) \rightarrow \yinsp$.]
   Chosen by openers from a family of functions \famfinsp. The opening
@@
   Note that \finsp also receives as input a value in the range of the \feval
-  function, \rngfeval. This allows opening logic to depend on the value
+  function, $\rngfeval^2$. This allows opening logic to depend on the values
   produced by the evaluation function. The output of \finsp is a value
@@
   properties that require an honest issuer.
-\item[$\ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,
-  \scred,\attrs_{\scred},\yinsp)$.] Receives a signature pair $(\sig,\yeval)$,
+\item[$\ExtractSign(\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
+  \scred,\attrs_{\scred},\yinsp)$.] Receives a signature \Sig,
   as well as the opener identifier \oid, and the identifiers of all issuers of
@@
   \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
-    of honest users. Entries of this table are $(\oid,\scid,\sig,\yeval,\msg,
+    of honest users. Entries of this table are $(\oid,\scid,\sig,\Yeval,\msg,
     \feval)$, where \oid is the opener chosen for the signature, \scid is the
@@
           \HI \gets \HI \setminus \lbrace \iid \rbrace \\
-          \CI \gets \CI \cup \lbrace \gid \rbrace \\
+          \CI \gets \CI \cup \lbrace \iid \rbrace \\
           \pcreturn \isk \\
@@
           \pcif \oid \in \CO \lor \oid \notin \HO: \pcreturn \bot \\
+          \pcif \exists (\oid,\cdot,\cdot,\cdot,\cdot,
+          \cdot,\cdot,\cdot,\cdot) \in \CSIG: \pcreturn \bot \\
           \HO \gets \HO \setminus \lbrace \oid \rbrace \\
@@
           \pcif \feval \notin \famfeval: \pcreturn \bot \\          
-          \pcif \yeval = \feval(\UK[\cuid_0],\CRED[\cscid_0],\msg) \neq \\
-          \pcind \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg):
-          \pcreturn \bot \\
+          (\yeval,\cdot) \gets \feval(\UK[\cuid_0],\CRED[\cscid_0],\msg) \\
+          ({\yeval}',\cdot) \gets \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg) \\
+          \pcif \yeval \neq {\yeval}': \pcreturn \bot \\
           \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
-          (\yeval,\csig_b) \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
+          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
           \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
-          (\yeval,\csig_{1-b}) \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
+          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
           \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
-          \CSIG[\csig_b] \gets 
-          \lbrace (\oid,\cuid_b,\cscid_b,\msg,\feval,\yeval,\\
-          \hspace*{74pt}\cuid_{1-b},\csig_{1-b},\cscid_{1-b})
+          \CSIG[\cSig_b] \gets 
+          \lbrace (\oid,\cuid_b,\cscid_b,\msg,\feval,\\
+          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b})
           \rbrace \\
-          \pcreturn (\csig_b,\yeval)
+          \pcreturn \cSig_b
         }
@@
           \pcif \feval \notin \famfeval: \pcreturn \bot \\
-          (\sig,\yeval) \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,
-          \feval) \\
+          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,\feval) \\
           \SIG[\uid] \gets \SIG[\uid] \cup
-          \lbrace (\oid,\scid,\sig,\yeval,\msg,\feval) \rbrace \\
-          \pcreturn (\sig,\yeval) \\
+          \lbrace (\oid,\scid,\Sig,\msg,\feval) \rbrace \\
+          \pcreturn \Sig \\
         }
 
-        \procedure{$\OPEN(\oid,\sig,\yeval,\msg)$}{%
-          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\sig,\yeval,\msg,\feval)
+        \procedure{$\OPEN(\oid,\Sig,\msg)$}{%
+          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\msg,\feval)
           \in \SIG[\uid] \\
+%          \textrm{Parse}~\Sig~\textrm{as}~(\sig,\yeval,\ceval) \\
           (\yinsp,\iproof) \gets
-          \Open(\PRVOK[\oid],\PUBIK[\scid],\sig,\yeval,\msg,\feval) \\
-          \pcif \CSIG[\sig] \neq \bot: \\
-          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
-            \feval,\yeval$} \\
-          \hspace*{83pt}\cuid_{1-b},\csig_{1-b},\scid_{1-b}) \\
+          \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
+          \pcif \CSIG[\Sig] \neq \bot: \\
+          \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
+            \feval$} \\
+          \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b}) \\
           \pcind (\yinsp',\iproof') \gets
           \Open(\PRVOK[\oid],\IK[\siid],\\
-          \hspace*{107pt} \sig_{1-b},\msg,\feval) \\
+          \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
           \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
@@
     \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
-    (\sig,\yeval) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
-    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\sig,\msg,\feval) = 0: \pcreturn 1 \\
+    (\Sig = (\sig,\yeval,\ceval)) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,
+    \feval) \\
+    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
     \pcfor \cid \in \scid \pcdo: \\
@@
     \pcind \pcif \fissue^{\cid}(\UK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
-    \pcif \feval(\UK[\uid],\CRED[\scid],\msg) \neq \yeval: \pcreturn 1 \\
-    (\yinsp,\iproof) \gets \Open(\PRVOK[\gid],\PUBIK[\scid],\sig,\msg,\feval) \\
-    \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\y,\iproof,\sig,\yeval,\msg,\feval)
-    = 0 \lor \yinsp \neq \finsp^\gid(\yeval,\UK[\uid],\CRED[\scid],\msg)): \\
+    (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\scid],\msg) \\
+    \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
+    (\yinsp,\iproof) \gets \Open(\PRVOK[\gid],\PUBIK[\scid],\Sig,\msg,\feval) \\
+    \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
+    = 0~\lor \\
+    \pcind \yinsp \neq \finsp^\gid(\yeval,\yeval^1,\UK[\uid],\CRED[\scid],\msg)): \\
     \pcind \pcreturn 1 \\
@@
 \paragraph{Anonymity.} %
+Informally, anonymity must capture two requirements: (1) interactive credential
+issuance protocols do not leak any information about the user requesting them;
+and (2), signatures do not leak any information about the signer.
+
+\todo{XXX}
+We follow a simulation-based approach to define anonymity in \UAS.
+
+simulation-based, definition of the
+anonymity property. In the simulation-based approach, we require the adversary
+to guess the bit $b$ defining whether it is interacting with the real world,
+where it gets signatures by real users, or with a simulation, where all
+signatures are simulated and do not contain information about the signer.
+This alternative formulation is given in \figref{fig:exp-uas-simanon}, where
+$\Osimanon = (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,
+\OO\rbrace\CORR,\WREG)$.
+
+\begin{figure}[htp!]
+
+  \centering
+  \procedure[linenumbering]{$\ExpSimAnonb(1^\secpar)$}{%
+    \pcif b = 0: \\
+    \parm \gets \Setup(1^\secpar) \\    
+    \pcind b^* \gets \adv^{\Osimanon,\OBTAIN,\SIGN,\OPEN}(\parm) \\
+    \pcelse: \\
+    \parm \gets \SIMSETUP(1^\secpar) \\
+    \pcind b^* \gets \adv^{\Osimanon,\SIMOBTAIN,\SIMSIGN,\SIMOPEN}(\parm) \\    
+    \pcreturn b^*
+  }
+
+  \caption{Simulation-based anonymity experiment for \UAS schemes.}
+  \label{fig:exp-uas-simanon}
+\end{figure}
+
+\begin{definition}{(Simulatable Anonymity of \UAS)}
+  \label{def:sim-anonymity-uas}  
+  We define the advantage \AdvSimAnon of $\adv$ against \ExpSimAnonb as
+  $\AdvSimAnon=|\Pr\lbrack\ExpSimAnono(1^\secpar)=1\rbrack-
+  \Pr\lbrack\ExpSimAnonz(1^\secpar)=1\rbrack|$.
+  %
+  An \UAS scheme satisfies simulatable anonymity if there exists simulators
+  \SIMSETUP, \SIMOBTAIN, \SIMSIGN and \SIMOPEN such that, for any p.p.t.
+  adversary $\adv$, \AdvSimAnon is a negligible function of $1^\secpar$.
+\end{definition}
+
+\iffalse
 In addition to the considerations made for \GSAC (see \secref{ssec:model-gsac}),
@@
   the latter}, although we show how to do that in \secref{sec:transformations}.
+\fi
 
@@
       \parm \gets \Setup(1^\secpar) \\
-      (\oid,\siid,\sig,\yeval,\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
-      \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in
+      (\oid,\siid,\Sig=(\sig,\yeval,\ceval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
+      \pcif \exists \uid~\st~(\cdot,\cdot,\Sig,\msg,\feval) \in
       \SIG[\uid]: \pcreturn 0 \\
@@
       \pcreturn 0 \\
-      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\sig,\yeval,\msg) \\
+      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
       \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg,\feval)
       = 0: \pcreturn 1 \\
-      (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets \ExtractSign(\oid,\siid,\sig,
-      \yeval,\msg,\feval) \\
-      \pcif \feval(\usk,\scred,\msg) \neq \yeval: \pcreturn 1 \\
-      \pcif \finsp(\yeval,\usk,\scred,\msg) \neq \yinsp \lor \yinsp \neq \yinsp':
+      (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets \ExtractSign(\oid,\siid,\Sig,
+      \msg,\feval) \\
+      (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
+      \pcif \yeval \neq \yeval^0: \pcreturn 1 \\
+      \pcif \finsp(\yeval^0,\yeval^1,,\usk,\scred,\msg) \neq \yinsp
+      \lor \yinsp \neq \yinsp':
       \pcreturn 1 \\
@@
     \parm \gets \Setup(1^\secpar) \\
-    (\oid,\siid,\sig,\yeval,\msg,\feval,\yinsp,\iproof) \gets
+    (\oid,\siid,\Sig,\msg,\feval,\yinsp,\iproof) \gets
     \adv^{\Oframe}(\parm) \\
@@
 %    \pcreturn 0 \\
-    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\yeval,\msg,\feval) = 0:
+    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
     \pcreturn 0 \\
-    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg) = 0:
+    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
     \pcreturn 0 \\
     (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets
-    \ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \\
+    \ExtractSign(\oid,\siid,\Sig,\msg,\feval) \\
     \pcif \exists \uid \in \HU~\st~\UK[\uid] = \usk~\land \\
-    \pcind (\nexists (\cdot,\cdot,\sig,\yeval,\msg,\feval) \in \SIG[\uid]
+    \pcind (\nexists (\cdot,\cdot,\Sig,\msg,\feval) \in \SIG[\uid]
     \lor \yinsp \neq \yinsp'): \pcreturn 1 \\

### 2022-06-03 prism-backend/research/gsac/app-building-blocks.tex
Upgrading definitions and proofs.

@@
 
+\paragraph{Augmenting with NIZKs.} %
+\todo{This is quite informal. Perhaps expand...} 
+In the previous \SBCM scheme, it is straightforward to require that the party
+running \SBCMCom proves some arbitrary claim over the messages to be signed
+(both those in committed or plaintext form). This can be done by having this
+party add a NIZK over the corresponding NP statement. We will be using this
+extension, and use $\SBCM^{\NIZKRel}$ to denote such an \SBCM with proofs for
+claims in \NIZKRel.
+
 Finally, in addition, we require that the produced signatures must be compatible

### 2022-06-03 prism-backend/research/gsac/construction-uas.tex
Upgrading definitions and proofs.

@@
   It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
-  \attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec =
-  \EEnc(\Eek,\yinsp;r) \land \yeval = \feval(\usk,\scred,\msg) \land
-  \yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
-  \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$, with
-  $\attrs_{\scred}$ and $\sipk_{\scred}$ as in $\NIZKRel_{\Issue}$. In a
+  \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
+  \sipk_{\scred},\Eek): \ceval = \EEnc(\Eek,\yeval^1;r) \land \cinsp= \EEnc
+  (\Eek,\yinsp;r') \land (\yeval^0,\yeval^1) = \feval(\usk,\scred,\msg) \land
+  \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \land \forall \cred \in
+  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$,
+  with $\attrs_{\scred}$ and $\sipk_{\scred}$ as in $\NIZKRel_{\Issue}$. In a
   nutshell, this relation ensures that signatures will produce the correct
@@
 \paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle$.} %
-The protocol is run between an issuer, and a user with secret key \usk and
-credentials \scred, where each $\cred \in \scred$ is issued by an issuer with
+  \langle\Obtain(\usk,\ipk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle$.} %
+The protocol is run between an issuer with key pair $(\ipk,\isk)$, and a user
+with secret key \usk and credentials \scred, where each $\cred \in \scred$ is
+issued by an issuer with
 public key $\ipk_{\cred}$ (which we assume that the user can easily retrieve,
@@
 
-\paragraph{$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
+\paragraph{$\Sig \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
 In the signing algorithm, we make use of relation $\NIZKRel_{\Sign}$.
@@
 From this, in order to produce a valid signature, the user first evaluates
-$\yeval \gets \feval (\usk,\scred,\msg)$, and decides whether or not to continue
-with the signing process -- this may depend, e.g., on the opening policy of
-\opk, as the output of \feval may influence whether the user will be
-de-anonymizable or not, depending on the \finsp function in \opk.
+$(\yeval^0,\yeval^1) \gets \feval (\usk,\scred,\msg)$, and decides whether or
+not to continue with the signing process -- this may depend, e.g., on the
+opening policy of \opk, as the output of \feval may influence whether the user
+will be de-anonymizable or not, depending on the \finsp function in \opk.
 %
@@
 $\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
-compute $\yinsp \gets \finsp(\yeval,\usk,\scred,\msg)$, and encrypt it with
-\Eek by running $\Ec \gets \EEnc(\Eek,\yeval;r)$ for some fresh randomness $r$.
-Finally, the user computes
+compute $\yinsp \gets \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg)$, and
+separately encrypts both $\yeval^1$ and \yinsp with \Eek by running
+$\ceval \gets \EEnc(\Eek,\yeval^1;r)$ and $\cinsp \gets \EEnc(\Eek,\yeval^1;
+r')$ for some fresh randomness $r,r'$. Finally, the user computes
 $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
-\attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek))$ and
-outputs $(\sig = (\NIZKproof,\Ec),\yeval)$.
+\attrs_{\scred},\yeval^1,\yinsp,r),(\msg,\feval,\yeval^0,\ceval,\cinsp,
+\sipk_{\scred},\Eek))$ and outputs $(\sig = (\NIZKproof,\cinsp),\yeval,
+\ceval)$.
 
-\paragraph{$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval)$.} %
+\paragraph{$1/0 \gets \Verify(\opk,\sipk,\Sig,\msg,\feval)$.} %
 The ``cryptographic'' side of the verification essentially consists on checking
-the NIZK proof. That is, parse \sig as $(\NIZKproof,\Ec)$ and check whether
-$\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,\sipk,\opk)) = 1$. In
-addition, the verifier may further check whether \yeval meets its needs.
+the NIZK proof. That is, parse \Sig as $(\sig = (\NIZKproof,\cinsp),\yeval,
+\ceval)$ and check whether $\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,
+\ceval,\cinsp,\sipk,\opk)) = 1$. In addition, the verifier may further check
+whether \yeval meets its needs.
 
 \paragraph{$(\yinsp,\NIZKproof)/\bot \gets
-  \Open(\osk,\sipk,\sig,\yeval,\msg,\feval)$.} %
+  \Open(\osk,\sipk,\Sig,\msg,\feval)$.} %
 Here we leverage relation $\NIZKRel_{\Open}$.
@@
 To open a signature, the opener first verifies the signature by running $\Verify
-(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the verification succeeds, it parses
-\sig as $(\NIZKproof,\Ec)$, decrypts \Ec by running $\yeval \gets \EDec(\osk,
-\Ec)$, and computes $\NIZKproof_{\Open} \gets \NIZKProve^{\NIZKRel_{\Open}}
-(\NIZKcrs_{\Open},\osk,(\Ec,\yinsp))$. It returns $(\yinsp,
-\NIZKproof_{\Open})$.
+(\opk,\sipk, \Sig,\msg,\feval)$. If verification succeeds, it parses
+\Sig as $(\sig=(\NIZKproof,\cinsp),\yeval,\ceval)$, decrypts \Ec by running $\yinsp
+\gets \EDec(\osk,\cinsp)$, and computes $\NIZKproof_{\Open} \gets
+\NIZKProve^{\NIZKRel_{\Open}}(\NIZKcrs_{\Open},\osk,(\cinsp,\yinsp))$. It
+returns $(\yinsp,\NIZKproof_{\Open})$.
 
@@
 by running $\Verify(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the check succeeds,
-parse \sig as $((\cdot,\Ec),\cdot)$ and verify \NIZKproof with $\NIZKVerify
-(\NIZKcrs_{\Open},\NIZKproof,(\Ec,\yinsp))$. Accept it the NIZK verification
-passes, and reject otherwise.
+parse \sig as $((\cdot,\cinsp),\cdot)$ and verify \NIZKproof with $\NIZKVerify
+(\NIZKcrs_{\Open},\NIZKproof,(\cinsp,\yinsp))$. Accept it the NIZK
+verification passes, and reject otherwise.
 

### 2022-06-03 prism-backend/research/gsac/model-uas.tex
Upgrading definitions and proofs.

@@
 \item[$\langle
-  \Obtain(\usk,\scred,\attrs),
+  \Obtain(\usk,\ipk,\scred,\attrs),
   \Issue(\isk,\sipk,\attrs))
@@
           \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\UK[\uid],\CRED[\scid],\attrs),\adv \rangle \\
+          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\CRED[\scid],\attrs),\adv \rangle \\
           \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
@@
     = 0~\lor \\
-    \pcind \yinsp \neq \finsp^\gid(\yeval,\yeval^1,\UK[\uid],\CRED[\scid],\msg)): \\
+    \pcind \yinsp \neq \finsp^\gid((\yeval,\yeval^1),\UK[\uid],\CRED[\scid],\msg)): \\
     \pcind \pcreturn 1 \\
@@
 issuance protocols do not leak any information about the user requesting them;
-and (2), signatures do not leak any information about the signer.
-
-\todo{XXX}
-We follow a simulation-based approach to define anonymity in \UAS.
-
-simulation-based, definition of the
-anonymity property. In the simulation-based approach, we require the adversary
-to guess the bit $b$ defining whether it is interacting with the real world,
-where it gets signatures by real users, or with a simulation, where all
-signatures are simulated and do not contain information about the signer.
-This alternative formulation is given in \figref{fig:exp-uas-simanon}, where
-$\Osimanon = (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,
-\OO\rbrace\CORR,\WREG)$.
+and (2) signatures do not leak any information about the signer. In both cases,
+any leakage must be limited to whatever the user decides to reveal, for
+instance, through arbitrary predicates on the attributes of the credentials used
+for issuance and signing. We follow a simulation-based approach to capture this.
+Basically, the adversary is challenged to distinguish between real and ideal
+executions. In both worlds, the adversary can generate and corrupt honest users,
+issuers, and openers. Then, in the real world, the adversary has access to
+oracles that allow requesting credentials on behalf of honest users, create
+signatures by honest users, and open signatures by honest users. In the ideal
+world, these three oracles are replaced by simulated counterparts, which produce
+outputs independent of the users' secrets. This formulation is given in
+\figref{fig:exp-uas-simanon}, where $\Osimanon = (\lbrace\HU,\CU\rbrace\GEN,
+\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG)$.
 
@@
     \pcif b = 0: \\
-    \parm \gets \Setup(1^\secpar) \\    
+    \pcind \parm \gets \Setup(1^\secpar) \\    
     \pcind b^* \gets \adv^{\Osimanon,\OBTAIN,\SIGN,\OPEN}(\parm) \\
     \pcelse: \\
-    \parm \gets \SIMSETUP(1^\secpar) \\
+    \pcind (\parm,\NIZKtrap) \gets \SIMSETUP(1^\secpar) \\
     \pcind b^* \gets \adv^{\Osimanon,\SIMOBTAIN,\SIMSIGN,\SIMOPEN}(\parm) \\    
@@
   \caption{Simulation-based anonymity experiment for \UAS schemes.}
-  \label{fig:exp-uas-simanon}
+  \label{fig:exp-uas-anonb}
 \end{figure}
 
-\begin{definition}{(Simulatable Anonymity of \UAS)}
-  \label{def:sim-anonymity-uas}  
+\begin{definition}{(Anonymity of \UAS)}
+  \label{def:anonymity-uas}  
   We define the advantage \AdvSimAnon of $\adv$ against \ExpSimAnonb as
@@
       \SIG[\uid]: \pcreturn 0 \\
-      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\yeval,\msg,\feval) = 0:
+      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
       \pcreturn 0 \\
       (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
-      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg,\feval)
+      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
       = 0: \pcreturn 1 \\
@@
       \pcif \yeval \neq \yeval^0: \pcreturn 1 \\
-      \pcif \finsp(\yeval^0,\yeval^1,,\usk,\scred,\msg) \neq \yinsp
+      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp
       \lor \yinsp \neq \yinsp':
@@
 \begin{figure}[htp!]
-  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
+  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$ \todo{Updated win conditions here. Update proof.}}{%
     \parm \gets \Setup(1^\secpar) \\
-    (\oid,\siid,\Sig,\msg,\feval,\yinsp,\iproof) \gets
+    (\oid,\siid,\Sig=(\sig,\yeval,\ceval),\msg,\feval,\yinsp,\iproof) \gets
     \adv^{\Oframe}(\parm) \\
@@
     \ExtractSign(\oid,\siid,\Sig,\msg,\feval) \\
-    \pcif \exists \uid \in \HU~\st~\UK[\uid] = \usk~\land \\
-    \pcind (\nexists (\cdot,\cdot,\Sig,\msg,\feval) \in \SIG[\uid]
-    \lor \yinsp \neq \yinsp'): \pcreturn 1 \\
+    (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg)~\pccomment{\todo{New}} \\
+    \pcif \nexists \uid \in \HU~\st~\UK[\uid] = \usk: \pcreturn 0 \\
+    \pcif \nexists (\cdot,\cdot,\Sig,\msg,\feval) \in \SIG[\uid]: \pcreturn 1 \\
+    \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp \lor
+    \yinsp \neq \yinsp': \pcreturn 1~\pccomment{\todo{1st or part is new}} \\
+    \pcif \yeval \neq \yeval^0: \pcreturn 1~\pccomment{\todo{New}} \\
     \pcreturn 0

### 2022-06-03 prism-backend/research/gsac/sec-uas.tex
Upgrading definitions and proofs.

@@
     $K(x)$ means proving knowledge of $x$; $E(y)$ means proving correct
-    encryption of $y$; $D(z)$ means proving correct decryption of $z$. In
-    \UAS, solid boxes span configurable statements that control issuance; dashed
-    boxes span configurable statements that control utility; dotted boxes span
-    configurable statements that control accountability. Unboxed statements are
-    fixed, and are thus common to all \GSAC/\UAS schemes.}
+    encryption of $y$; $D(z)$ means proving correct decryption of (an encryption
+    of) $z$. In \UAS, solid boxes span configurable statements that control
+    issuance; dashed boxes span configurable statements that control utility;
+    dotted boxes span configurable statements that control accountability.
+    Unboxed statements are fixed, and are thus common to all \GSAC/\UAS
+    schemes.\todo{Add a new $\finsp^1$ at opening time, that also relies on
+    $\yinsp^1$? Does this enable some use case?}}
   \label{fig:proof-blocks-uas}

### 2022-06-03 prism-backend/research/gsac/security-uas.tex
Upgrading definitions and proofs.

@@
   line 3, and due to correctness of the NIZK for $\NIZKRel_{\Sign}$, the
-  output of \feval matches \yeval at line $10$, which is furthermore computed
-  over $\usk=\UK[\uid]$ due to correctness of the commitment scheme. Finally,
-  correctness of the NIZKs for $\NIZKRel_{\Sign}$ and $\NIZKRel_{\Open}$, and
-  correctness of the encryption scheme, ensure that \Judge accepts the proof
-  produced by \Open, and \yinsp is the correct value for the chosen
-  $\finsp^{\oid}$.
+  output of \feval matches $\yeval^0$ at line $11$, which must have been
+  computed over $\usk=\UK[\uid]$, as in line $10$, due to correctness of the
+  commitment scheme. Finally, correctness of the NIZKs for $\NIZKRel_{\Sign}$
+  and $\NIZKRel_{\Open}$, and correctness of the encryption scheme, ensure that
+  \Judge accepts the proof produced by \Open, and \yinsp is the correct value
+  for the chosen $\finsp^{\oid}$.
 \end{proof}
@@
 \begin{proof}[\thmref{thm:anonymity-uas}; Anonymity of \CUASGen]
+  First, we define \SimSetup, \SIMOBTAIN, \SIMSIGN and \SIMOPEN as in
+  \figref{fig:anon-sim}.
+
+  \begin{figure}[ht!]
+  \begin{minipage}[t]{\textwidth}
+    \procedure{$\SimSetup(\secpar,\AttrSpace)$}{%
+      \textrm{Parse}~\secpar~\textrm{as}~(\cdot,\secpar_{\NIZK},\cdot,\cdot) \\
+      (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue})
+      \gets \NIZKSimSetup^{\NIZKRel_{\Issue}}(\secpar_{\NIZK}) \\
+      (\NIZKcrs_{\Sign},\NIZKtrap_{\Sign})
+      \gets \NIZKSimSetup^{\NIZKRel_{\Sign}}(\secpar_{\NIZK}) \\
+      (\NIZKcrs_{\Open},\NIZKtrap_{\Open})
+      \gets \NIZKSimSetup^{\NIZKRel_{\Open}}(\secpar_{\NIZK}) \\
+      \textrm{Compute}~\Cparm,\SBCMparm,\Sparm,\Eparm~\textrm{as in}~\Setup \\
+      \pcreturn ((\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
+      \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
+      (\NIZKtrap_{\Issue},\NIZKtrap_{\Sign},\NIZKtrap_{\Open})) \\
+    }
+
+    \begin{minipage}[t]{\textwidth}
+      \begin{minipage}[t]{0.5\textwidth}
+        \procedure{$\SIMOBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
+          \pcif \uid \notin \HU: \pcreturn \bot \\
+          \pcif \iid \notin \CI: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
+          \sipk_{\scred} \gets \PUBIK[\scid] \\
+          \langle \cred, \cdot \rangle \gets
+          \langle SimObt(\attrs,\PUBIK[\iid],\sipk_{\scred}),\adv \rangle \\
+          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
+          \pcreturn \top \\      
+        }
+        \end{minipage}
+        \begin{minipage}[t]{0.5\textwidth}
+          \procedure{$SimObt(\attrs,\sipk_{\scred})$}{%
+            \textrm{Runs \SBCM}
+            \textrm{Runs like \Obtain, replacing calls to
+            $\NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
+            (\Ccom,\attrs,\sipk_{\scred}),
+            (\usk,\scred,\attrs_{\scred},r))$ with calls to
+            $\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\NIZKtrap_{\Issue},
+            (\Ccom,\attrs,\sipk_{\scred}))$}
+        }
+        \end{minipage}
+      \end{minipage}
+    \procedure{$\SIMSIGN(\oid,\uid,\scid,\msg,\feval)$}{%
+      \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
+    }
+
+    \procedure{$\SIMOPEN(\oid,\Sig,\msg)$}{%
+      \pcreturn 0
+    }
+  \end{minipage}
+  \label{fig:sim-anon}
+  \caption{Definition of \SimSetup, \SIMOBTAIN, \SIMSIGN, and \SIMOPEN for
+    anonymity in \CUASGen.}
+\end{figure}
+
+  \iffalse
   In this proof, we restrict to the case in which the adversary can only make
@@
   \AdvAnon is negligible.
+  \fi
   %

### 2022-06-07 prism-backend/research/gsac/app-building-blocks.tex
Updated sign-unforgeability proof.

@@
 (both those in committed or plaintext form). This can be done by having this
-party add a NIZK over the corresponding NP statement. We will be using this
-extension, and use $\SBCM^{\NIZKRel}$ to denote such an \SBCM with proofs for
-claims in \NIZKRel.
+party add a NIZK over the corresponding NP statement, which has later to be
+verified by the party running \SBCMSign. We will be using this extension, and
+use $\SBCM^{\NIZKRel}$ to denote such an \SBCM with proofs for claims in
+\NIZKRel.
 

### 2022-06-07 prism-backend/research/gsac/app-gsac.tex
Quick full pass (excl. appendices).
Minor edits and fixing typos.
Updated sign-unforgeability proof.

@@
           \pcreturn \bot \\
-          \pcif \cuid_0 \neq \bot \lor \cuid_1 \neq \bot: \pcreturn \bot \\
           \cuid_0 = \OWNR[\ccid_0];~\cuid_1 = \OWNR[\ccid_1] \\
@@
 
-\subsection{Detailed Proofs}
+\subsection{Correctness and Security Proofs}
 \label{sapp:gsac-proofs}
@@
 
-  We begin with game $G_0=\ExpGSACAnonb$. From it, we build $G_1$, where we
+  We begin with game $G_0=\ExpGSACSigAnonb$. From it, we build $G_1$, where we
   simply replace the \NIZKSetup functions for $\NIZKRel_{\Sign}$ and
@@
   $G_2$ is indistinguishable from $G_0$, where the adversary plays the original
-  \ExpGSACAnonb game. Thus, our generic construction of \GSAC satisfies
+  \ExpGSACSigAnonb game. Thus, our generic construction of \GSAC satisfies
   anonymity, except with negligible probability.
@@
 
-\paragraph{Anonymity.} To see why the interactive variant is anonymous, assume
-an adversary $\adv$ against anonymity in that case. We build \advB against the
-non-interactive \ExpGSACAnonb as follows. \advB initializes everything as in the
-\ExpGSACAnonb game. When $\adv$ initiates a call to its interactive \SIGN (resp.
-\CHALb) oracle, \advB picks a random number, and sends it to the adversary,
-along with the response of its own (non-interactive) \SIGN (resp. \CHALb)
-oracle where, to the message passed as parameter to its oracle, concatenates the
-produced random number. After such simulation, \advB just outputs whatever
-$\adv$ outputs. Clearly, the simulation is perfect and, if $\adv$ wins with
-non-negligible probability in the interactive case, then so does \advB in the
-non-interactive case.
+\paragraph{Issuance Anonymity.} \todo{XXX}
+
+\paragraph{Signature Anonymity.} To see why the interactive variant is
+anonymous, assume an adversary $\adv$ against anonymity in that case. We build
+\advB against the non-interactive \ExpGSACSigAnonb as follows. \advB initializes
+everything as in the \ExpGSACSigAnonb game. When $\adv$ initiates a call to its
+interactive \SIGN (resp. \CHALb) oracle, \advB picks a random number, and sends
+it to the adversary, along with the response of its own (non-interactive) \SIGN
+(resp. \CHALb) oracle where, to the message passed as parameter to its oracle,
+concatenates the produced random number. After such simulation, \advB just
+outputs whatever $\adv$ outputs. Clearly, the simulation is perfect and, if
+$\adv$ wins with non-negligible probability in the interactive case, then so
+does \advB in the non-interactive case.
 

### 2022-06-07 prism-backend/research/gsac/construction-uas.tex
Updated sign-unforgeability proof.

@@
   \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
-  \sipk_{\scred},\Eek): \ceval = \EEnc(\Eek,\yeval^1;r) \land \cinsp= \EEnc
-  (\Eek,\yinsp;r') \land (\yeval^0,\yeval^1) = \feval(\usk,\scred,\msg) \land
-  \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \land \forall \cred \in
-  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$,
-  with $\attrs_{\scred}$ and $\sipk_{\scred}$ as in $\NIZKRel_{\Issue}$. In a
+  \sipk_{\scred},\Eek,\widetilde{\Eek}): \ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)
+  \land \cinsp= \EEnc (\Eek,\yinsp;r') \land (\yeval^0,\yeval^1) = \feval(\usk,
+  \scred,\msg) \land \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \land
+  \forall \cred \in \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred})
+  = 1) \rbrace$, with $\attrs_{\scred}$ and $\sipk_{\scred}$ as in
+  $\NIZKRel_{\Issue}$. In a
   nutshell, this relation ensures that signatures will produce the correct
@@
 %
-Then, the user parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
-$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
-compute $\yinsp \gets \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg)$, and
-separately encrypts both $\yeval^1$ and \yinsp with \Eek by running
-$\ceval \gets \EEnc(\Eek,\yeval^1;r)$ and $\cinsp \gets \EEnc(\Eek,\yeval^1;
-r')$ for some fresh randomness $r,r'$. Finally, the user computes
-$\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
-\attrs_{\scred},\yeval^1,\yinsp,r),(\msg,\feval,\yeval^0,\ceval,\cinsp,
-\sipk_{\scred},\Eek))$ and outputs $(\sig = (\NIZKproof,\cinsp),\yeval,
-\ceval)$.
+The user also computes a random encryption key pair with $(\widetilde{\Eek},
+\widetilde{\Edk}) \gets \EKeyGen(\Eparm)$. Then, the user parses \opk as $(\Svk,\Eek,
+\finsp,\sig_{\finsp})$ and checks that $\Verify(\Svk,\sig_{\finsp},\finsp) = 1$
+(note that this step may be cached), to compute $\yinsp \gets \finsp((\yeval^0,
+\yeval^1),\usk,\scred,\msg)$, and separately encrypts both $\yeval^1$ and
+\yinsp by running $\ceval \gets \EEnc(\widetilde{\Eek},\yeval^1;r)$ and $\cinsp \gets
+\EEnc(\Eek,\yinsp; r')$ for some fresh randomness $r,r'$. Finally, the user
+computes $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,
+\scred, \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
+\sipk_{\scred},\Eek,\widetilde{\Eek}))$ and outputs $(\sig = (\NIZKproof,\ceval,
+\cinsp),\yeval^0)$.
 
@@
 
-\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\sig,\yeval,\msg)$.} %
+\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\Sig,\msg)$.} %
 To assess the validity of an opening proof, first check the signature
-by running $\Verify(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the check succeeds,
-parse \sig as $((\cdot,\cinsp),\cdot)$ and verify \NIZKproof with $\NIZKVerify
-(\NIZKcrs_{\Open},\NIZKproof,(\cinsp,\yinsp))$. Accept it the NIZK
+by running $\Verify(\opk,\sipk,\Sig,\msg,\feval)$. If the check succeeds,
+parse \Sig as $((\cdot,\cinsp),\cdot,\cdot)$ and verify \NIZKproof with
+$\NIZKVerify(\NIZKcrs_{\Open},\NIZKproof,(\cinsp,\yinsp))$. Accept it the NIZK
 verification passes, and reject otherwise.

### 2022-06-07 prism-backend/research/gsac/model-gsac.tex
Updated sign-unforgeability proof.

@@
 \begin{figure}[htp!]
-  \procedure[linenumbering]{$\ExpGSACAnonb(1^\secpar)$}{%
+  \procedure[linenumbering]{$\ExpGSACSigAnonb(1^\secpar)$}{%
+    \parm \gets \Setup(1^\secpar) \\
+    (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
+    \gpk \gets (\ipk,\opk) \\
+    b^* \gets
+    \adv^{\HUGEN,\CUGEN,\WREG,\OBTAIN,\SIGN,\OPEN,\OBTCHALb}(\gpk,\isk,\status) \\
+    \pcreturn b^*
+  }
+
+  \vspace*{0.5em}
+
+  \procedure[linenumbering]{$\ExpGSACSigAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
@@
   }
-  \caption{Anonymity experiment for \GSAC schemes.}
+  \caption{Issuance and signature anonymity experiments for \GSAC schemes.}
   \label{fig:exp-gsac-anonb}
@@
 
-\begin{definition}{(Anonymity of \GSAC)}
-  \label{def:anonymity-gsac}
-  We define the advantage \AdvGSACAnon of $\adv$ against \ExpGSACAnonb as
-  $\AdvGSACAnon=|\Pr\lbrack\ExpGSACAnono(1^\secpar)=1\rbrack-
-  \Pr\lbrack\ExpGSACAnonz(1^\secpar)=1\rbrack|$.
+\begin{definition}{(Issuance anonymity of \GSAC)}
+  \label{def:iss-anonymity-gsac}
+  We define the advantage \AdvGSACIssAnon of $\adv$ against \ExpGSACIssAnonb as
+  $\AdvGSACIssAnon=|\Pr\lbrack\ExpGSACIssAnono(1^\secpar)=1\rbrack-
+  \Pr\lbrack\ExpGSACIssAnonz(1^\secpar)=1\rbrack|$.
   %
-  A \GSAC scheme satisfies anonymity if, for any p.p.t. adversary $\adv$,
-  \AdvAnon is a negligible function of $1^\secpar$.
+  A \GSAC scheme satisfies issuance anonymity if, for any p.p.t. adversary
+  $\adv$, \AdvGSACIssAnon is a negligible function of $1^\secpar$.
+\end{definition}
+
+\begin{definition}{(Signature anonymity of \GSAC)}
+  \label{def:sig-anonymity-gsac}
+  We define the advantage \AdvGSACSigAnon of $\adv$ against \ExpGSACSigAnonb as
+  $\AdvGSACSigAnon=|\Pr\lbrack\ExpGSACSigAnono(1^\secpar)=1\rbrack-
+  \Pr\lbrack\ExpGSACSigAnonz(1^\secpar)=1\rbrack|$.
+  %
+  A \GSAC scheme satisfies signature anonymity if, for any p.p.t. adversary
+  $\adv$, \AdvGSACSigAnon is a negligible function of $1^\secpar$.
 \end{definition}

### 2022-06-07 prism-backend/research/gsac/model-uas.tex
Updated sign-unforgeability proof.

@@
   credential.
-\item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval,\ceval)$.] %
+\item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
   Upon receiving a user secret key \usk, opener public key \opk, a set of
   credentials \scred, a message \msg and evaluation
-  function \feval, returns signature \sig, a plaintext value \yeval,
-  and an encrypted value \ceval. For readability, we use \Sig to denote
-  the tuple $(\sig,\yeval,\ceval)$.
+  function \feval, returns signature \sig, and a plaintext value \yeval. For
+  readability, we use \Sig to denote the tuple $(\sig,\yeval)$.
 \item[$\Verify(\opk, \sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
-  Checks whether $\Sig = (\sig,\yeval,\ceval)$ is a valid signature
+  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
   over message \msg, from a user with credentials issued by issuers with public
   keys in \sipk, for evaluation function \feval and opener key \opk.
-\item[$\Open(\osk,\sipk,\sig,\yeval,\msg,\feval) \rightarrow
+\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
   (\yinsp,\iproof)/\bot$.]
-  Executed by the opener with private key \osk. Receives a signature $(\sig,
-  \yeval)$ over message \msg and evaluation function \feval, generated using
-  credentials issued by the issuers with public keys in \sipk. If \sig is valid,
-  the function outputs a value $\yinsp$.
+  Executed by the opener with private key \osk. Receives a signature $\Sig=
+  (\sig,\yeval)$ over message \msg and evaluation function \feval,
+  generated using credentials issued by the issuers with public keys in \sipk.
+  If \Sig is valid, the function outputs a value $\yinsp$.
 \item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
   Checks if \iproof is a valid opening correctness proof for the value \yinsp,
-  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval,\ceval)$
+  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
   over message \msg, and for evaluation function \feval. 
@@
 \item[$\ExtractSign(\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
-  \scred,\attrs_{\scred},\yinsp)$.] Receives a signature \Sig,
+  \scred,\attrs_{\scred},\yeval^1,\yinsp)$.] Receives a signature \Sig,
   as well as the opener identifier \oid, and the identifiers of all issuers of
@@
 
-        \procedure{$\ISSUE(\cid,\uid,\iid,\attrs,\siid)$}{%
-          \pcif \uid \notin \CU: \pcreturn \bot \\          
-          \pcif \iid \notin \HI: \pcreturn \bot \\
-          %\pcif \exists \iid' \in \ISR[\scid] \notin \HI: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
-          \langle \cdot, \utrans \rangle \gets
-          \langle \adv, 
-          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
-          \trans[\cid] \gets \utrans \\
-          \CRED[\cid] \gets (\uid, \cdot, \iid, \attrs, \cdot, \siid) \\
-          \pcreturn \top \\          
-        }
-
-        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
-          \pcif \uid \notin \HU: \pcreturn \bot \\
-          \pcif \iid \notin \CI: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
-          %\pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot: \pcreturn \bot \\
-          \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\CRED[\scid],\attrs),\adv \rangle \\
-          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
-          \pcreturn \top \\
-        }
-
-        \procedure{$\CHALb(\oid,\cuid_{0,1},\cscid_{0,1},\msg,\feval)$}{%
-          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
-          \pcif \oid \in \CO: \pcreturn \bot \\
-          \pcif \feval \notin \famfeval: \pcreturn \bot \\          
-          (\yeval,\cdot) \gets \feval(\UK[\cuid_0],\CRED[\cscid_0],\msg) \\
-          ({\yeval}',\cdot) \gets \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg) \\
-          \pcif \yeval \neq {\yeval}': \pcreturn \bot \\
-          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
-          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
-          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
-          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
-          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
-          \CSIG[\cSig_b] \gets 
-          \lbrace (\oid,\cuid_b,\cscid_b,\msg,\feval,\\
-          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b})
-          \rbrace \\
-          \pcreturn \cSig_b
-        }
-
-      \end{minipage}
-    }
-    \scalebox{0.9}{
-
-      \begin{minipage}[t]{.5\textwidth}
-
         \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\scid)$}{%
@@
           \pcif \iid \notin \HI: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
           %\pcif \exists \iid' \in \ISR[\scid]~\st~\iid' \notin \HI: \pcreturn \bot \\
           %\pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot:
-          \pcreturn \bot \\
           \langle \cred, \utrans \rangle \gets
@@
 
+        \procedure{$\ISSUE(\cid,\uid,\iid,\attrs,\siid)$}{%
+          \pcif \uid \notin \CU: \pcreturn \bot \\          
+          \pcif \iid \notin \HI: \pcreturn \bot \\
+          %\pcif \exists \iid' \in \ISR[\scid] \notin \HI: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
+          \langle \cdot, \utrans \rangle \gets
+          \langle \adv, 
+          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
+          \trans[\cid] \gets \utrans \\
+          \CRED[\cid] \gets (\uid, \cdot, \iid, \attrs, \cdot, \siid) \\
+          \pcreturn \top \\          
+        }
+
         \procedure{$\SIGN(\oid,\uid,\scid,\msg,\feval)$}{%
@@
           \pcif \feval \notin \famfeval: \pcreturn \bot \\
+          \pcif \exists \cid \in \scid~\suchthat~\cid \in \CRED~\land \\
+          \pcind \exists \cid' \in \scid~\suchthat~\cid' \in \CCRED: \pcreturn \bot \\
           \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,\feval) \\
+          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\cscid],\msg) \\
           \SIG[\uid] \gets \SIG[\uid] \cup
-          \lbrace (\oid,\scid,\Sig,\msg,\feval) \rbrace \\
+          \lbrace (\oid,\scid,\Sig,\Yeval,\msg,\feval) \rbrace \\
           \pcreturn \Sig \\
@@
         \procedure{$\OPEN(\oid,\Sig,\msg)$}{%
-          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\msg,\feval)
+          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\Yeval,\msg,\feval)
           \in \SIG[\uid] \\
@@
           \pcif \CSIG[\Sig] \neq \bot: \\
-          \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
-            \feval$} \\
-          \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b}) \\
-          \pcind (\yinsp',\iproof') \gets
+          \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,
+            \Yeval,\msg,\feval$} \\          
+          \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b},
+          \TYeval) \\
+          %\pcind \pcif \yeval^1 \neq \tyeval^1: \pcreturn \bot \\          
+          \pcind (\tyinsp,\tiproof) \gets
           \Open(\PRVOK[\oid],\IK[\siid],\\
           \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
-          \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
+          \pcind \pcif \tyinsp \neq \yinsp: \pcreturn \bot \\
           \pcreturn (\yinsp,\iproof)
+        }
+
+      \end{minipage}
+    }
+    \scalebox{0.9}{
+
+      \begin{minipage}[t]{.5\textwidth}
+
+        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
+          \pcif \uid \notin \HU: \pcreturn \bot \\
+          \pcif \iid \notin \CI: \pcreturn \bot \\
+          \pcif \exists \cid' \in \scid~\suchthat~\cid' \in \CRED~\land \\
+          \pcind \exists \cid'' \in \scid~\suchthat~\cid'' \in \CCRED: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
+          %\pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot: \pcreturn \bot \\
+          \langle \cred, \cdot \rangle \gets
+          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\CRED[\scid],\attrs),\adv \rangle \\
+          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
+          \pcreturn \top \\
+        }
+
+        \procedure{$\OBTCHALb(\cid,\iid,\cuid_{0,1},\cscid_{0,1},\attrs)$}{%
+          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
+          \pcif \iid \notin \CI: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
+          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
+          \in \CRED~\land \\
+          \pcind \exists \cid'' \in \cscid_d~\suchthat~\cid'' \in \CCRED:
+          \pcreturn \bot \\
+          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
+          \pcif \fissue(\UK[\cuid_0],\cscid_0,\attrs) \neq
+          \fissue(\UK[\cuid_1],\cscid_1,\attrs) \\
+          \langle \cred, \cdot \rangle \gets
+          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\CRED[\scid_b],\attrs),\adv \rangle \\
+          \CCRED[\cid] \gets (\cuid_b, \cred, \iid, \attrs, \scid_b, \siid) \\
+          \pcreturn \top \\
+        }
+
+        \procedure{$\CHALb(\oid,\cuid_{0,1},\cscid_{0,1},\msg,\feval)$}{%
+          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
+          \pcif \oid \in \CO: \pcreturn \bot \\
+          \pcif \feval \notin \famfeval: \pcreturn \bot \\          
+          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\CRED[\cscid_0],
+          \msg) \\
+          \TYeval = (\tyeval^0,\tyeval^1) \gets
+          \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg) \\
+          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
+          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
+          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
+          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
+          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
+          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
+          \CSIG[\cSig_b] \gets 
+          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
+          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
+          \pcreturn \cSig_b
         }
@@
     \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
-    (\Sig = (\sig,\yeval,\ceval)) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,
+    (\Sig = (\sig,\yeval)) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,
     \feval) \\
@@
 \paragraph{Anonymity.} %
+\iffalse
 Informally, anonymity must capture two requirements: (1) interactive credential
@@
 \begin{definition}{(Anonymity of \UAS)}
-  \label{def:anonymity-uas}  
+  \label{def:sign-anonymity-uas}  
   We define the advantage \AdvSimAnon of $\adv$ against \ExpSimAnonb as
@@
 \end{definition}
+\fi
 
-\iffalse
 In addition to the considerations made for \GSAC (see \secref{ssec:model-gsac}),
@@
 (passed as arguments to the \SIGN and \CHALb oracles). The formal specification
-of the anonymity game is given in \figref{fig:exp-uas-anonb}, where $\Oanon
+of the anonymity game is given in \figref{fig:exp-uas-anonb}, where
+$\OIssAnon \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,
+\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\OBTCHALb)$, and $\OSigAnon
 \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace
-\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$
+\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$.
 
-\begin{figure}[htp!]
+\begin{figure*}[htp!]
   \centering
-  \procedure[linenumbering]{$\ExpAnonb(1^\secpar)$}{%
+  \scalebox{0.9}{
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure[linenumbering]{$\ExpIssAnonb(1^\secpar)$}{%
         \parm \gets \Setup(1^\secpar) \\
-     b^* \gets \adv^{\Oanon} (\status,\parm) \\
+        b^* \gets \adv^{\OIssAnon} (\status,\parm) \\
         \pcreturn b^*
       }
-  \caption{Anonymity experiment for \UAS schemes.}
+    \end{minipage}
+
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure[linenumbering]{$\ExpSigAnonb(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        b^* \gets \adv^{\OSigAnon} (\status,\parm) \\
+        \pcreturn b^*
+      }
+    \end{minipage}
+  }
+  \caption{Issuance and signature anonymity experiments for \UAS schemes.}
   \label{fig:exp-uas-anonb}
-\end{figure}
+\end{figure*}
 
-\begin{definition}{(Anonymity of \UAS)}
-  \label{def:anonymity-uas}  
-  We define the advantage \AdvAnon of $\adv$ against \ExpAnonb as
-  $\AdvAnon=|\Pr\lbrack\ExpAnono(1^\secpar)=1\rbrack-
-  \Pr\lbrack\ExpAnonz(1^\secpar)=1\rbrack|$.
+\begin{definition}{(Issuance anonymity in \UAS)}
+  \label{def:issue-anonymity-uas}  
+  We define the advantage \AdvIssAnon of $\adv$ against \ExpIssAnonb as
+  $\AdvIssAnon=|\Pr\lbrack\ExpIssAnono(1^\secpar)=1\rbrack-
+  \Pr\lbrack\ExpIssAnonz(1^\secpar)=1\rbrack|$.
   %
-  An \UAS scheme satisfies anonymity if, for any p.p.t. adversary $\adv$,
-  \AdvAnon is a negligible function of $1^\secpar$.
+  An \UAS scheme satisfies issuance anonymity if, for any p.p.t. adversary
+  $\adv$, \AdvIssAnon is a negligible function of $1^\secpar$.
+\end{definition}
+
+\begin{definition}{(Signature anonymity in \UAS)}
+  \label{def:sign-anonymity-uas}  
+  We define the advantage \AdvSigAnon of $\adv$ against \ExpSigAnonb as
+  $\AdvSigAnon=|\Pr\lbrack\ExpSigAnono(1^\secpar)=1\rbrack-
+  \Pr\lbrack\ExpSigAnonz(1^\secpar)=1\rbrack|$.
+  %
+  An \UAS scheme satisfies signature anonymity if, for any p.p.t. adversary
+  $\adv$, \AdvSigAnon is a negligible function of $1^\secpar$.
 \end{definition}
@@
   the latter}, although we show how to do that in \secref{sec:transformations}.
-\fi
 
@@
       \parm \gets \Setup(1^\secpar) \\
-      (\oid,\siid,\Sig=(\sig,\yeval,\ceval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
-      \pcif \exists \uid~\st~(\cdot,\cdot,\Sig,\msg,\feval) \in
+      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
+      \pcif \exists \uid~\st~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
       \SIG[\uid]: \pcreturn 0 \\
@@
       = 0: \pcreturn 1 \\
-      (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets \ExtractSign(\oid,\siid,\Sig,
+      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets \ExtractSign(\oid,\siid,\Sig,
       \msg,\feval) \\
       (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
-      \pcif \yeval \neq \yeval^0: \pcreturn 1 \\
-      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp
+      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
+      \pcreturn 1 \\
+      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp'
       \lor \yinsp \neq \yinsp':
@@
     \parm \gets \Setup(1^\secpar) \\
-    (\oid,\siid,\Sig=(\sig,\yeval,\ceval),\msg,\feval,\yinsp,\iproof) \gets
+    (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
     \adv^{\Oframe}(\parm) \\
@@
     \pcreturn 0 \\
-    (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets
+    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets
     \ExtractSign(\oid,\siid,\Sig,\msg,\feval) \\
-    (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg)~\pccomment{\todo{New}} \\
+%    (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg)~\pccomment{\todo{New}} \\
     \pcif \nexists \uid \in \HU~\st~\UK[\uid] = \usk: \pcreturn 0 \\
-    \pcif \nexists (\cdot,\cdot,\Sig,\msg,\feval) \in \SIG[\uid]: \pcreturn 1 \\
+    \pcif \nexists (\cdot,\cdot,\Sig,(\yeval^0,\yeval^1),\msg,\feval)
+    \in \SIG[\uid]: \pcreturn 1 \\
     \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp \lor
-    \yinsp \neq \yinsp': \pcreturn 1~\pccomment{\todo{1st or part is new}} \\
+    \tyeval^1 \neq \yeval^1 \lor \yinsp \neq \yinsp': \pcreturn 1~\pccomment{\todo{1st or part is new}} \\
     \pcif \yeval \neq \yeval^0: \pcreturn 1~\pccomment{\todo{New}} \\

### 2022-06-07 prism-backend/research/gsac/security-gsac.tex
Updated sign-unforgeability proof.

@@
 
-\begin{theorem}[Anonymity of \GSACGen]
-  \label{thm:anonymity-gsac}
+\begin{theorem}[Issuance anonymity of \GSACGen]
+  \label{thm:iss-anonymity-gsac}
+  \todo{XXX}
+\end{theorem}
+
+\begin{theorem}[Signature anonymity of \GSACGen]
+  \label{thm:sig-anonymity-gsac}
   If the underlying $\NIZK^{\NIZKRel_{\Sign}}$ scheme is zero-knowledge and
@@
   our \GSACGen construction satisfies anonymity as defined in
-  \defref{def:anonymity-gsac}.
+  \defref{def:sig-anonymity-gsac}.
 \end{theorem}

### 2022-06-07 prism-backend/research/gsac/security-uas.tex
Updated sign-unforgeability proof.

@@
       (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets \NIZKExtract(\NIZKcrs,
-      \NIZKtrap, (\msg,\feval,\yeval,\Ec,\sipk,\opk),\NIZKproof) \\
-      \pcreturn (\usk,\scred,\attrs_{\scred},\yinsp) \\
+      \NIZKtrap, (\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk,\opk,\widetilde{\Eek}),
+      \NIZKproof) \\
+      \pcreturn (\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \\
     }
@@
       \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
-      \pcfor \cid~\st~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
+      \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
       \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trans[\cid]) \\
@@
 
-\begin{theorem}[Anonymity of \CUASGen]
-  \label{thm:anonymity-uas}
-  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge, our
-  \CUASGen construction satisfies anonymity as defined in
-  \defref{def:anonymity-uas}.
+\begin{theorem}[Signature anonymity of \CUASGen]
+  \label{thm:sign-anonymity-uas}
+  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge, and the
+  public-key encryption scheme is IND-CCA secure, our \CUASGen construction
+  satisfies signature anonymity as defined in \defref{def:sign-anonymity-uas}.
 \end{theorem}
 
-\begin{proof}[\thmref{thm:anonymity-uas}; Anonymity of \CUASGen]
+\begin{proof}[\thmref{thm:sign-anonymity-uas}; Signature anonymity of \CUASGen]
+  \iffalse
   First, we define \SimSetup, \SIMOBTAIN, \SIMSIGN and \SIMOPEN as in
@@
         \gets \NIZKSimSetup^{\NIZKRel_{\Open}}(\secpar_{\NIZK}) \\
-      \textrm{Compute}~\Cparm,\SBCMparm,\Sparm,\Eparm~\textrm{as in}~\Setup \\
-      \pcreturn ((\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
+        \textrm{Compute}~\parm \gets (\Cparm,\SBCMparm,\Sparm,\Eparm)~
+        \textrm{as in}~\Setup \\
+        \pcreturn ((\parm,\NIZKcrs_{\Issue},
         \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
@@
       \begin{minipage}[t]{\textwidth}
-      \begin{minipage}[t]{0.5\textwidth}
+        \begin{minipage}[t]{0.55\textwidth}
           \procedure{$\SIMOBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
@@
         \end{minipage}
-        \begin{minipage}[t]{0.5\textwidth}
-          \procedure{$SimObt(\attrs,\sipk_{\scred})$}{%
-            \textrm{Runs \SBCM}
-            \textrm{Runs like \Obtain, replacing calls to
-            $\NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
-            (\Ccom,\attrs,\sipk_{\scred}),
-            (\usk,\scred,\attrs_{\scred},r))$ with calls to
-            $\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\NIZKtrap_{\Issue},
-            (\Ccom,\attrs,\sipk_{\scred}))$}
+        \begin{minipage}[t]{0.45\textwidth}
+          \procedure{$SimObt(\attrs,\ipk,\sipk_{\scred})$}{%
+            \textrm{Runs $\langle \SBCMCom^{\NIZKRel_{\Issue}},\adv \rangle$} \\
+            \pcind \textrm{using $\NIZKSim^{\NIZKRel_{\Issue}}
+              (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue},\cdot)$} \\
+            \pcind \textrm{instead of $\NIZKProve^{\NIZKRel_{\Issue}}
+              (\NIZKcrs_{\Issue},\cdot,\cdot)$}
           }
@@
       \end{minipage}
+
+      \begin{minipage}[t]{\textwidth}
+        \begin{minipage}[t]{0.55\textwidth}
           \procedure{$\SIMSIGN(\oid,\uid,\scid,\msg,\feval)$}{%
-      \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
+            \pcif \uid \notin \HU: \pcreturn \bot \\
+            \pcif \feval \notin \famfeval: \pcreturn \bot \\
+            \Sig \gets SimSign(\PUBOK[\oid],\msg,\feval) \\
+            \SIG[\uid] \gets \SIG[\uid] \cup
+            \lbrace (\oid,\scid,\Sig,\msg,\feval) \rbrace \\
+            \pcreturn \Sig \\
           }
+        \end{minipage}
+        \begin{minipage}[t]{0.45\textwidth}
+          \procedure{$SimSign(\opk,\msg,\feval)$}{%
+            \textrm{Like}~\Sign()~\textrm{using} \\
+            \pcind \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
+            \NIZKtrap_{\Sign},\cdot) \\
+            \pcind \textrm{instead of}~\NIZKProve^{\NIZKRel_{\Sign}}
+            (\NIZKcrs_{\Sign},\cdot,\cdot)        
+          }
+        \end{minipage}
+      \end{minipage}
 
+      \begin{minipage}[t]{\textwidth}
+        \begin{minipage}[t]{0.55\textwidth}
           \procedure{$\SIMOPEN(\oid,\Sig,\msg)$}{%
-      \pcreturn 0
+            \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\msg,\feval)
+            \in \SIG[\uid] \\
+            % \textrm{Parse}~\Sig~\textrm{as}~(\sig,\yeval,\ceval) \\
+            (\yinsp,\iproof) \gets
+            SimOpen(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
+            \pcif \CSIG[\Sig] \neq \bot: \\
+            \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
+              \feval$} \\
+            \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b}) \\
+            \pcind (\yinsp',\iproof') \gets
+            \Open(\PRVOK[\oid],\IK[\siid],\\
+            \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
+            \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
+            \pcreturn (\yinsp,\iproof)          
           }
+        \end{minipage}
+        \begin{minipage}[t]{0.45\textwidth}
+          \procedure{$SimOpen(\opk,\msg,\feval)$}{%
+          }
+        \end{minipage}
+      \end{minipage}    
     \end{minipage}
@@
   \end{figure}
+  \fi
 
-  \iffalse
   In this proof, we restrict to the case in which the adversary can only make
@@
 
-  We start from $G_0=\ExpAnonb$, and define game $G_1$ to be exactly the same
+  We start from $G_0=\ExpSigAnonb$, and define game $G_1$ to be exactly the same
   as $G_0$, except that, within the $\Setup$ algorithm, we replace
@@
   From $G_1$, we consider $G^0_1$, which we define to be $G_1$, for $b=0$
-  (i.e., \ExpAnonz, using $\NIZKSimSetup^{\Sign}$). The challenge sent to the
+  (i.e., \ExpSigAnonz, using $\NIZKSimSetup^{\Sign}$). The challenge sent to the
   adversary is $(\csig_0,\yeval) \gets \Sign(\PRVUK[\cuid_0],\PUBOK[\oid],
@@
   $\pi_0 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
-  \Ec_{\yinsp},\PUBIK[\scid_0],\PUBOK[\oid]),(\PRVUK[\cuid_0],
-  \CRED[\scid_0],\attrs_{\scid_0},\yinsp,r))$ and $\Ec_{\yinsp} =
-  \EEnc(\PUBOK[\oid],\yinsp;r)$.
+  \ceval,\cinsp,\PUBIK[\scid_0],\widetilde{\Eek},\PUBOK[\oid]),(\PRVUK[\cuid_0],
+  \CRED[\scid_0],\attrs_{\scid_0},\yeval^1,\yinsp,r,r'))$, $\ceval = \EEnc
+  (\widetilde{\Eek},\yeval^1;r)$, and $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$.
   % 
   Further, we build $G_2^0$ from $G_1^0$ by simulating the proof $\pi_0$. That
-  is, in $G_{2,0}$, $\csig_0 = (\pi_0^s,\Ec_{\yinsp})$, where $\pi^s_0 =
+  is, in $G_2^0$, $\csig_0 = (\pi_0^s,\ceval,\cinsp)$, where $\pi^s_0 =
   \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
-  \Ec_{\yinsp},\PUBIK[\scid_0],\PUBOK[\oid]))$. By zero-knowledgeness
+  \ceval,\cinsp,\PUBIK[\scid_0],\PUBOK[\oid]))$. By zero-knowledgeness
   of $\NIZK^{\Sign}$, $G_2^0$ is indistinguishable from $G_1^0$.
@@
   sent to the adversary is $(\csig_1,\yeval) \gets \Sign(\PRVUK[\cuid_1],
-  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,
-  \Ec_{\yinsp})$, with $\pi_1 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
-  (\msg,\feval,\yeval,\Ec_{\yinsp},\PUBIK[\scid_1],\PUBOK[\oid]),
-  (\PRVUK[\cuid_1],\CRED[\scid_1],\attrs_{\scid_1},\yinsp,r'))$ and $\Ec_{\yinsp}
-  = \EEnc(\PUBOK[\oid],\yinsp;r')$. As before, $G_2^1$ is built from $G_1^1$,
-  simulating $\pi_1$. That is, in $G_2^1$, $\csig_1 = (\pi_1^s,\Ec_{\yinsp})$,
-  where $\pi^s_1 = \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,
-  \feval,\yeval,\Ec_{\yinsp},\PUBIK[\scid_1],\PUBOK[\oid]))$. Again, by
-  zero-knowledge of $\NIZK^{\Sign}$, $G_2^1$ is indistinguishable from $G_1^1$.
-  Note also that $G_2^1=G_2^0$ as, in the challenge oracle used in the
-  anonymity game, we restrict to $\PUBIK[\scid_0] = \PUBIK[\scid_1]$.
+  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,\ceval,
+  \cinsp)$, with $\pi_1 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
+  (\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
+  \PUBOK[\oid]),(\PRVUK[\cuid_1],\CRED[\scid_1],\attrs_{\scid_1},\yeval^1,
+  \yinsp,r,r'))$, $\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)$, and
+  $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$. As before, $G_2^1$ is built from
+  $G_1^1$, simulating $\pi_1$. That is, in $G_2^1$, $\csig_1 = (\pi_1^s,\ceval,
+  \cinsp)$, where $\pi^s_1 = \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
+  \NIZKtrap,(\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
+  \PUBOK[\oid]))$. Again, by zero-knowledge of $\NIZK^{\Sign}$, $G_2^1$ is
+  indistinguishable from $G_1^1$. Note also that $G_2^1$ and $G_2^0$ are
+  indistinguishable, due to the IND-CCA property of the encryption scheme
+  (so, the \ceval values in $\pi^s_0$ and $\pi^s_1$ are indistinguishable),
+  in the  challenge oracle used in the anonymity game, we restrict to
+  $\PUBIK[\scid_0] = \PUBIK[\scid_1]$, and the respective \cinsp values encrypt
+  the same \yinsp value.
 
-  Finally, consider the definition of $\AdvAnon=|\Pr\lbrack
-  \ExpAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpAnonz(1^\secpar)=1\rbrack|$. As
-  argued, $G_1$ is indistinguishable from $\ExpAnonb$, thus
-  $\AdvAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
+  Finally, consider the definition of $\AdvSigAnon=|\Pr\lbrack
+  \ExpSigAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpSigAnonz(1^\secpar)=1\rbrack|$. As
+  argued, $G_1$ is indistinguishable from $\ExpSigAnonb$, thus
+  $\AdvSigAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
   G_1^0(1^\secpar)=1\rbrack| \approx
@@
   G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
-  \AdvAnon is negligible.
-  \fi
+  \AdvSigAnon is negligible.
   % 
@@
 
-\begin{proof}[\thmref{thm:issue-forge-uas}; Issue unforgeability of \CUASGen]
+\begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
   We show that the probability that \fissue outputs $0$ is negligible, as well
@@
   \label{thm:sign-forge-uas}
-  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is zero-knowledge, sound,
-  and simulation extractable, the NIZK scheme for $\NIZKRel_{\Open}$ is sound
-  and simulation extractable, and \SBCM is one-more unforgeable, then our
-  \CUASGen construction satisfies signing unforgeability as defined in
+  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
+  extractable,the NIZK scheme for $\NIZKRel_{\Open}$ is complete, the public-key
+  encryption scheme is correct, and \SBCM is correct and one-more unforgeable,
+  then our \CUASGen construction satisfies signing unforgeability as defined in
   \defref{def:sign-forge-uas}, except with negligible probability.
@@
 \begin{proof}[\thmref{thm:sign-forge-uas}; Sign unforgeability of \CUASGen]
-  As for \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
+  As in \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
   and $G_1$, which is exactly the same but where, within the \Setup algorithm,
@@
   zero-knowledgeness of $\NIZK^{\Sign}$, both games are indistinguishable.
+  %
+  Next, we show that an adversary winning $G_1$ can be used to break the
+  one-more unforgeability property of \SBCM.
 
-  From $G_1$, and in order to define the winning conditions for the adversary
-  in the signing unforgeability game, consider the following events:
+  If the verification at line 4 holds, then $(\msg,\feval,\yeval,\ceval,
+  \cinsp,\sipk,\opk,\widetilde{\Eek}) \in \NIZKLang^{\Sign}$. Then:
+  %
 
-  \begin{description}
-  \item[$V$.] Where $V = \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval) = 1$.
-  \item[$J$.] Where $J = \Judge(\opk,\sipk,\yinsp,\iproof,\sig,\yeval,\msg,
-    \feval) = 0$.
-  \item[$L$.] Where $L = (\msg,\feval,\yeval,\Ec,\sipk,\opk) \in
-    \NIZKLang^{\Sign}$.    
-  \item[$I$.] Where $I = \exists \cred \in \scred~\st~\IdentifyCred(\usk,
-    \attrs_{\cred},\msg) = 0$.
-  \end{description}
+  \paragraph{(a) \Judge accepts $(\yinsp,\iproof)$.} %
+  Simulation extractability of $\NIZK^{\Sign}$ thus ensures that $\cinsp =
+  \EEnc(\Eek,\yinsp)$, and since the $(\yinsp,\iproof)$ is generated honestly at
+  line 5, then \yinsp is the correct decryption of \cinsp, and  correctness of
+  $\NIZK^{\Open}$ ensures that \Judge outputs $1$ at line 6.
 
-  $\adv$ wins if $V \land (J \lor I) = (\overline{L} \land V \land (J \lor I))
-  \lor (L \land V \land (J \lor I))$.
-  %
-  $V$ implies that $(\msg,\feval,\yeval,\Ec,\sipk,\opk) \in \NIZKRel^{\Sign}$.
-  Thus, after soundness of $\NIZK^{\Sign}$, the probability of $\overline{L}
-  \land V \land (J \lor I)$ is negligible in the security parameter.
-  %
-  For $(L \land V \land (J \lor I))$ to be satisfied, there are three cases:
-  \begin{enumerate}
-  \item $L \land V \land J \land \overline{I}$. The game returns 1 in step 6.
-  \item $L \land V \land J \land I$.  The game returns 1 in step 6.
-  \item $L \land V \land \overline{J} \land I$. The game returns 1 in step 10. 
-  \end{enumerate}
+  \paragraph{(b) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
+    pair.} Also, due to simulation extractability of $\NIZK^{\Sign}$:
 
-  In case 1, $L \land V$ implies that $(\msg,\feval,\yeval,\Ec,\sipk,\opk) \in
-  \NIZKRel^{\Sign}$. More concretely, soundness of $NIZK^{\Sign}$ implies that
-  $\Ec = \EEnc(\opk,\yinsp;r)$, for $\yinsp$ and $r$ known to the signer. Since
-  $(\yinsp,\iproof)$ is generated honestly by the challenger from
-  $(\opk,\sipk,\sig = (\NIZKproof_{\Sign},\Ec),\yeval,\msg)$, correctness of
-  public key encryption implies that $\EDec(\osk,\Ec) = \yinsp$. Consequently,
-  the probability of $L \land V \land J \land \overline{I}$ = 0, as \Judge
-  checks precisely that \Ec is a correct encryption of \yinsp under \opk.
+  \begin{itemize}
+  \item $\yeval^0 = \yeval$, where $(\yeval^0,\cdot) = \feval(\usk,\scred,
+    \msg)$, and $\yeval$ is as output by \adv~at step 2.    
+  \item $\tyeval^1 = \yeval^1$, where $(\cdot,\yeval^1) = \feval(\usk,\scred,
+    \msg)$, and $\tyeval^1$ is as extracted by \ExtractSign at line 7.
+  \end{itemize}
 
-  The analysis for case 2 is the same as for case 1.
+  Thus, the probability of \adv~winning at line 9 is $0$.
 
-  For case 3, $(\msg,\feval,\yeval,\Ec,\sipk,\opk) \in \NIZKRel^{\Sign}$,
-  $\Judge(\opk,\sipk,\yinsp,\iproof,\sig,\yeval,\msg,\feval)
-  = 1$, but there exists some credential \cred for which $\IdentifyCred(\usk,
-  \attrs_{\cred},\msg)=0$. Note that \usk, $\attrs_{\cred}$ and \cred (for all
-  $\cred \in \scred$) are output by \ExtractSign. Thus, after the
-  simulation-extractability property and soundness of $\NIZK^{\Sign}$, $(\msg,
-  \feval,\yeval,\Ec,\sipk,\opk) \in \NIZKRel^{\Sign}$, which more concretely
-  means that, for all $\cred \in \scred$, $\SBCMVerify(\ipk_{\cred},\cred,\usk,
-  \attrs_{\cred}) = 1 = \IdentifyCred(\usk,\attrs_{\cred},\cred)$. The
-  probability of case 3 is therefore $0$.
-  %
-  Moreover, since \SBCMVerify returns $1$ for all $\cred \in \scred$, it must
-  be that all of them were obtained via queries to the \ISSUE or \OBTISS
-  oracles. Otherwise, if there exists some \cred that was not obtained via
-  a call to these oracles, the tuple $(\usk, \attrs_{\cred}, \cred)$ constitutes
-  a forgery of \SBCM.
+  \paragraph{(c) The output of \finsp matches the output of \Open.} %
+  After (a), the \yinsp value output by \Open is the correct decryption of
+  \cinsp. After (b), the $(\yeval^0=\yeval,\yeval^1)$ values output by
+  \ExtractSign match the evaluation of \feval. Thus, simulation extractability
+  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\usk,\scred,\msg)
+  = \yinsp$ and, also, that \yinsp matches the $\yinsp'$ value extracted by
+  \ExtractSign. Thus, the probability of \adv~winning at line 10 is $0$.
 
-  Cases 1, 2 and 3 above account for winning conditions at steps 6 and 10.
-  % 
-  Additionally, $\adv$ wins at step 8 if $\feval(\usk,\scred,\msg) \neq \yeval$,
-  where \yeval is the value output by the adversary in step 2. However, since
-  $\Verify(\opk,\sipk,\sig,\yeval,\msg,\feval) = 1$, soundness of $NIZK^{\Sign}$
-  implies that this has negligible probability.
-  %
-  Similarly, $\adv$ wins at step 9 if (1) $\finsp(\yeval,\usk,\scred,\msg) \neq
-  \yinsp$, where \yinsp is the value output by \Open at line 5; or if (2)
-  $\yinsp \neq \yinsp'$, where $\yinsp'$ is the value extracted by \ExtractSign
-  at step 7. For (1), soundness of $\NIZK^{\Sign}$ ensures that \yinsp is the
-  correct evaluation of \finsp, whereas soundness of $\NIZK^{\Open}$ and
-  correctness of the public key encryption ensure that this is also the value
-  output by \Open. Thus, the probability of $\adv$ winning the game because
-  of (1) is negligible. Finally, for (2), simulation-extractability of
-  $\NIZK^{\Open}$ and correctness of the public key encryption ensure that
-  the $\yinsp'$ value extracted by \NIZKExtract matches the value produced by
-  \Open.
+  \paragraph{(d) All {\cred}s are bound to the same \usk.} %
+  $\NIZKRel^{\Sign}$ includes a condition that $\forall \cred \in \scred,
+  \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1$. Thus, simulation
+  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
+  credentials involved in the signature contain \usk as their user key (first)
+  attribute. Consequently, \IdentifyCred returns $1$ for all the involved
+  credentials, and the probability of \adv~winning at line 11 is $0$.
 
+  \paragraph{(e) \usk must belong to a known user.} %
   The only remaining option for $\adv$ to win is via winning condition at line
-  11. At that point, we already know that all credentials are bound to the same
-  user key (otherwise, the adversary wins at line 10). If this key is not
-  associated to any known user, this means that there is no matching $\langle
-  \Obtain,\Issue\rangle$ transcript for a credential over $\usk$ --i.e., the
-  honest issuer did not issue any credential to \usk. But, as \sig must have
-  been produced with at least one credential (extracted at step 7), then this
-  credential is a forgery, breaking security against one-more forgery of the
-  \SBCM scheme.  
+  12, meaning that \IdentifyUK fails to find an honest or corrupt users with
+  a \usk matching the one used to request the credentials used to produce the
+  signature output by \adv. However, at line 12, we already know that all
+  credentials are valid signatures by the issuer and that, also, all are bound
+  to the same user key. If this key is not associated to any known user, this
+  means that there is no matching $\langle\Obtain,\Issue\rangle$ transcript for
+  a credential over \usk --i.e., the honest issuer did not issue any credential
+  to \usk. But, as \sig must have been produced with at least one credential
+  (extracted at step 7), then this credential is a forgery, breaking security
+  against one-more forgery of the \SBCM scheme.
   %

### 2022-06-08 prism-backend/research/gsac/security-uas.tex
Updated UAS proofs. Missing proof for new property obt-anon.

@@
   \label{thm:frame-uas}
-  If the underlying scheme for $\NIZK^{\Issue}$ is zero-knowledge, the scheme
-  for $\NIZK^{\Sign}$ is zero-knowledge, sound and simulation-extractable, the
-  scheme for $\NIZK^{\Open}$ is zero-knowledge and sound, and the commitment
-  scheme is hiding, then our \CUASGen construction satisfies non-frameability as
-  defined in \defref{def:frame-uas}, except with negligible probability.
+  If the underlying scheme for $\NIZK^{\Issue}$ is zero-knowledge, the schemes
+  for $\NIZK^{\Sign}$ are zero-knowledge and simulation-extractable, and the
+  commitment scheme is hiding, then our \CUASGen construction satisfies
+  non-frameability as defined in \defref{def:frame-uas}, except with negligible
+  probability.
 \end{theorem}
@@
 \begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]
-  First, note that the adversary wins if it produces a signature that traces to
-  an honest user (which, in our case, is tested by checking whether the
-  extracted \usk belongs ot an honest user); and, in addition, either (1) the
-  signature was not produced via a call to the \SIGN oracle, or (2) the opening
-  value output by the adversary and accepted by \Judge, does not match the
-  extracted one (i.e., the one used as witness to $\NIZKRel^{\Sign}$). Note that
-  the probability of (2) is negligible due to soundness of $\NIZK^{\Sign}$ and
-  $\NIZK^{\Open}$, given that \Verify and \Judge accept the signature and
-  opening proof.
-
-  Next we prove that, given an adversary $\adv$ against non-frameability of
-  \CUASGen, under condition (1) above, we can build an adversary \advB that
-  breaks the hiding property of the underlying commitment scheme, with
-  non-negligible probability.
+  We prove that, given an adversary $\adv$ against non-frameability of
+  \CUASGen, we can build an adversary \advB that breaks the hiding property of
+  the underlying commitment scheme, with non-negligible probability.
 
   We start from $G_0=\ExpNonframe$. $\adv$ makes queries to the oracles in
-  \Oframe.
-
-  For $G_1$, within \Setup, we replace the \Setup algorithms for the three
-  NIZKs (\Issue, \Sign and \Open) with their corresponding \SimSetup
+  \Oframe. For $G_1$, within \Setup, we replace the \Setup algorithms for the
+  three NIZKs (\Issue, \Sign and \Open) with their corresponding \SimSetup
   variants. Consequently, the corresponding queries to \Prove are also
   simulated via the simulator. By the zero-knowledge property of the NIZK
-  systems, $G_1$ is indistinguishable from $G_0$.
+  systems, $G_1$ is indistinguishable from $G_0$. In the sequel, we build on
+  top of $G_1$, depending on whether or not a matching \Sig is found in \SIG,
+  in line 7.
 
-  We build adversary \advB against hiding of commitments from $G_1$ against
-  non-frameability. In the hiding game (see \figref{fig:com-games}), \advB first
-  picks two messages $\msg_0$ and $\msg_1$, and then receives a commitment \Ccom
-  of $\msg_b$. Let \advB pick both $\msg_0$ and $\msg_1$ from \AttrSpace. Then,
-  \advB initializes $G_1$ for $\adv$ against non-frameability, and randomly
-  picks a number $u \getr [1,q]$, where $q$ can be as large as \advB wants, but
-  will be the maximum number of honest users to let $\adv$ add to the game.
-  Then, when $\adv$ asks to create the $u$-th user, \advB ignores the call to
-  \UKeyGen. For every call that $\adv$ makes to the \OBTAIN oracle associated to
-  the $u$-th user, \advB uses the commitment \Ccom received as challenge in its
-  game against the hiding property of commmitments, and uses it as commitment to
-  the $u$-th user's \usk. \advB then simulates all the NIZK proofs associated to
-  the $u$-th user, in calls to \OBTAIN, \SIGN and \INSPECT. Again, due to the
-  zero-knowledge property of the associated NIZK systems, the outputs of the
-  modified oracles are indistinguishable from the original outputs (as \Ccom
-  is a valid commitment of a user secret key). Eventually, $\adv$ outputs a
-  $(\sig,\yeval,\msg,\feval,\yinsp,\iproof)$ tuple that is accepted by \Verify
-  and \Judge. Due to simulation extractability of $NIZK^{\Sign}$, \ExtractSign
-  must be able to produce a $(\usk,\scred,\attrs_{\scred},\yinsp')$ tuple. Since
-  $\adv$ wins the non-frameability game, with probability $1/q$,
-  the \usk value belongs to the $u$-th honest user, so it must be equal to
-  either $\msg_0$ or $\msg_1$; \advB responds accordingly to its challenge in
-  the game for the hiding property of the commmitment scheme. By assumption,
-  \advB wins with non-negligible probability.
+  \paragraph{(a) A matching \Sig exists in \SIG.} %
+  If we can find a matching \Sig in \SIG, for some \uid, then \adv~does not win
+  at line 7 of the game. Given that the signature is accepted by \Verify at line
+  3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
+  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, since the $(\yinsp,\iproof)$
+  pair output by \adv~is accepted by \Judge, simulation extractability of
+  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at line 9 pass.
+  Hence, the probability that the adversary wins at either lines 8 or 9 is $0$,
+  after simulation extractability of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.
+
+  \paragraph{(b) No matching \Sig exists in \SIG.} %
+  This means that \adv~creates an \UAS forgery. We leverage such an adversary
+  against $G_1$ to break the hiding property of the underlying commitment
+  scheme (see \appref{sapp:commitments}). For each new honest user \uid creation
+  request by \adv~(via \HUGEN),
+  \advB leverages its own $COM$ oracle to embed its challenges in the commitment
+  scheme into credentials of the \UAS non-frameability game. More precisely, in
+  calls to \HUGEN by \adv, \advB does not call \UKeyGen and instead picks two
+  random messages, $\msg_0^{\uid},\msg_1^{\uid}$, both from \AttrSpace. Whenever
+  a query to \OBTAIN is made by \adv~on behalf of \uid, \advB makes a call to
+  its $COM$ oracle, to get a commitment \Ccom for $\usk^{\uid}=\msg_b^{\uid}$
+  (for \advB's challenge bit $b$). Then,  \advB uses \Ccom in its \SBCMCom part
+  of the underlying \SBCM interactive signing protocol, and simulates the
+  corresponding $\NIZK^{\Issue}$ proof. Due to the zero-knowledge property, the
+  produced output is indistinguishable to that of the real execution. Similarly,
+  \advB can simulate the calls to the \SIGN and \OPEN oracles due to
+  simulation extractability of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.
+  %
+  Eventually, $\adv$ outputs a $(\oid,\siid,\Sig,\msg,\feval,\yinsp,\iproof)$
+  tuple that is accepted by \Verify and \Judge. Due to simulation extractability
+  of $NIZK^{\Sign}$, \ExtractSign must be able to produce a $(\usk,\scred,
+  \attrs_{\scred}, \tyeval^1,\yinsp')$ tuple. As, by assumption (line 6),  there
+  exists an \uid matching that \usk, all \advB has to do is find the
+  \uid for which \usk was used as either $\msg_0$ or $\msg_1$ in its hiding
+  game. Thus, \advB wins its hiding game with the same probability than \adv~
+  has to win the non-frameability game.
   %

### 2022-06-09 prism-backend/research/gsac/model-uas.tex
Updated UAS proofs. Missing proof for new property obt-anon.
Added proof for issue-anon.

@@
         \procedure{$\SIGN(\oid,\uid,\scid,\msg,\feval)$}{%
-          \pcif \uid \notin \HU: \pcreturn \bot \\
+          \pcif \uid \notin \HU \cup \lbrace \bot \rbrace: \pcreturn \bot \\
+          \pcif \uid = \bot \land \exists \cid' \in \scid~\suchthat~
+          \cid' \notin \CCRED: \\
+          \pcind \pcreturn \bot \\
+          \pcif \uid = \bot: \uid \gets \OWNR[\scid] \\
           \pcif \feval \notin \famfeval: \pcreturn \bot \\
-          \pcif \exists \cid \in \scid~\suchthat~\cid \in \CRED~\land \\
-          \pcind \exists \cid' \in \scid~\suchthat~\cid' \in \CCRED: \pcreturn \bot \\
           \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,\feval) \\
-          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\cscid],\msg) \\
+          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\scid],\msg) \\
           \SIG[\uid] \gets \SIG[\uid] \cup
@@
           \pcif \iid \notin \CI: \pcreturn \bot \\
-          \pcif \exists \cid' \in \scid~\suchthat~\cid' \in \CRED~\land \\
-          \pcind \exists \cid'' \in \scid~\suchthat~\cid'' \in \CCRED: \pcreturn \bot \\
+          \pcif \exists \cid' \in \scid~\suchthat~\cid' \in \CCRED: \pcreturn \bot \\
           \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
@@
 
-        \procedure{$\OBTCHALb(\cid,\iid,\cuid_{0,1},\cscid_{0,1},\attrs)$}{%
+        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1})$}{%
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
@@
           \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
-          \in \CRED~\land \\
-          \pcind \exists \cid'' \in \cscid_d~\suchthat~\cid'' \in \CCRED:
-          \pcreturn \bot \\
+          \in \CRED: \\
+          \pcind \pcreturn \bot \\
+          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
           \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
@@
           \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\CRED[\scid_b],\attrs),\adv \rangle \\
-          \CCRED[\cid] \gets (\cuid_b, \cred, \iid, \attrs, \scid_b, \siid) \\
+          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\CRED[\cscid_b],\attrs),\adv \rangle \\
+          \CCRED[\cid] \gets (\cuid_b, \cred, \iid, \attrs, \cscid_b, \siid) \\
           \pcreturn \top \\
@@
 \fi
+We need to ensure that no information is leaked about users requesting a
+credential, nor about signers. The latter is typically captured in group
+signatures by letting the adversary request challenge signatures, produced
+by a challenge user picked randomly out of two users chosen by the adversary,
+and requiring the adversary to guess which one was used. In what is frequently
+called CCA-like anonymity, the adversary is given access to the opener,
+except for challenge signatures. We follow this approach in what we call
+signature anonymity. We need however to restrict that challenge signatures
+produce the same \yeval value, to prevent trivail wins by the adversary. On
+the other hand, since it is possible that both challenge signatures produce
+the same \yinsp value, we can model a stronger CCA-like variant, in which the
+adversary is allowed to open challenge signatures for the cases in which the
+\yinsp value is the same for both challenge users.
 
-In addition to the considerations made for \GSAC (see \secref{ssec:model-gsac}),
-in our notion of anonymity for \UAS,
-in order to prevent trivial wins by the adversary, we have to restrict that the
-signing evaluation function outputs the same value for both user-credentials
-pairs. Very interestingly, since our opening functionality does not
-(necessarily) output the identity of the signer, \uline{we can even allow the
-  adversary to open challenge signatures, as long as they produce the same
-  output}. Other than this, the overall approach is similar: as
-in group signatures and anonymous credentials, the adversary asks for challenge
-signatures from either one of two honest users and credential sets -- bit $b$,
-unkown to the adversary, defining which one is used. Note that the adversary
-also has to pick a signature valuation function \feval, as well as an opener
-(passed as arguments to the \SIGN and \CHALb oracles). The formal specification
-of the anonymity game is given in \figref{fig:exp-uas-anonb}, where
+In addition to signature anonymity, we need to take into account that, as in
+some anonymous credential schemes, a single user may have multiple credentials.
+Moreover, these credentials can be obtained from different issuers, or from the
+same issuer but for different attributes. Thus, it seems logical to require that
+the adversary cannot determine whether any two credential requests originate
+from the same signer, or not. To model this, we define the issuance anonymity
+game. Intuitively, we let the adversary obtain challenge credentials on behalf
+of two honest challenge users, but without knowing to which concrete challenge
+user we actually issue the produced credentials. To prevent trivial wins, we
+have to make additional restrictions. Namely, the two sets of challenge user and
+supporting credentials for requesting the challenge credential need to satisfy
+the same issuance policy, and these supporting credentials cannot include
+credentials that have been obtained via the conventional \OBTAIN oracle.
+The adversary is then allowed to interact with all the other oracles (except the
+one producing challenge signatures, which is not needed), with the only further
+constraint that any call to the \SIGN oracle that leverages challenge
+credentials cannot specify the user identifier (the oracle ``knows'' which one
+out of the two challenge users it needs to use). As usual, after interacting in
+an arbitrary way with the oracles, the adversary needs to guess the bit $b$
+defining which challenge user was employed to produce the challenge credentials.
+
+% In addition to the considerations made for \GSAC (see \secref{ssec:model-gsac}),
+% in our notion of anonymity for \UAS,
+% in order to prevent trivial wins by the adversary, we have to restrict that the
+% signing evaluation function outputs the same value for both user-credentials
+% pairs. Very interestingly, since our opening functionality does not
+% (necessarily) output the identity of the signer, \uline{we can even allow the
+%   adversary to open challenge signatures, as long as they produce the same
+%   output}. Other than this, the overall approach is similar: as
+% in group signatures and anonymous credentials, the adversary asks for challenge
+% signatures from either one of two honest users and credential sets -- bit $b$,
+% unkown to the adversary, defining which one is used. Note that the adversary
+% also has to pick a signature valuation function \feval, as well as an opener
+% (passed as arguments to the \SIGN and \CHALb oracles).
+The formal specification of the anonymity games is given in
+\figref{fig:exp-uas-anonb}, where
 $\OIssAnon \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,
@@
       \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
-      \exists \cred \in \scred~\st~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0: \\
+      \exists \cred \in \scred~\suchthat~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0: \\
       \pcind \pcreturn 1 \\
@@
       (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
-      \pcif \exists \uid~\st~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
+      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
       \SIG[\uid]: \pcreturn 0 \\
@@
       \pcreturn 1 \\
-      \pcif \exists \cred \in \scred~\st~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
+      \pcif \exists \cred \in \scred~\suchthat~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
       \pcreturn 1 \\
-      \pcif \nexists \uid~\st~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
+      \pcif \nexists \uid~\suchthat~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
       \pcreturn 0
@@
 \begin{figure}[htp!]
-  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$ \todo{Updated win conditions here. Update proof.}}{%
+  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
@@
     \pcreturn 0 \\
-    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets
+    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
     \ExtractSign(\oid,\siid,\Sig,\msg,\feval) \\
 %    (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg)~\pccomment{\todo{New}} \\
-    \pcif \nexists \uid \in \HU~\st~\UK[\uid] = \usk: \pcreturn 0 \\
+    \pcif \nexists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \pcreturn 0 \\
     \pcif \nexists (\cdot,\cdot,\Sig,(\yeval^0,\yeval^1),\msg,\feval)
     \in \SIG[\uid]: \pcreturn 1 \\
-    \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp \lor
-    \tyeval^1 \neq \yeval^1 \lor \yinsp \neq \yinsp': \pcreturn 1~\pccomment{\todo{1st or part is new}} \\
-    \pcif \yeval \neq \yeval^0: \pcreturn 1~\pccomment{\todo{New}} \\
+    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
+    \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp
+    \lor \yinsp \neq \yinsp': \pcreturn 1 \\
     \pcreturn 0

### 2022-06-09 prism-backend/research/gsac/security-uas.tex
Added proof for issue-anon.

@@
   for the chosen $\finsp^{\oid}$.
+\end{proof}
+
+\begin{theorem}[Issuance anonymity of \CUASGen]
+  \label{thm:iss-anonymity-uas}
+  If the NIZK systems used for $\NIZKRel_{\Issue}$ and $\NIZKRel_{\Sign}$ are
+  zero-knowledge, our \CUASGen construction satisfies issuance anonymity as
+  defined in \defref{def:iss-anonymity-uas}.
+\end{theorem}
+
+\begin{proof}[\thmref{thm:iss-anonymity-uas}; Issuance anonymity of \CUASGen]
+  We prove the special case in which the adversary makes only one query to the
+  \OBTCHALb oracle. The generalization to polynomially many queries follows from
+  a standard hybrid argument.
+
+  Let $G_0=\ExpIssAnonb(1^\secpar)$. We define $G_1$ by replacing the calls to
+  \NIZKSetup in $G_0$, for the $\NIZK^{\Issue}$ and $\NIZK^{\Sign}$ systems by
+  calls to their corresponding \NIZKSimSetup. By zero-knowledgeness of the
+  NIZKs, both games are indistinguishable.
+
+  Next, we simulate the NIZK proofs produced by \Obtain within the \OBTCHALb
+  oracle and, consequently, the NIZK proofs produced by \Sign in \SIGN for
+  signatures from the challenge user and credentials. Then, we show that the
+  adversary cannot distinguish executions for $b=0$ from executions for $b=1$,
+  except with negligible probabability.
+
+  More concretely, on the one hand, let $G_1^0$ to be $G_1$, conditioned on
+  $b=0$. Concretely, the proofs sent by the challenge user $\cuid_0$ to the
+  adversarial issuer are of
+  the form $\pi^*_0 =\NIZKProve^{\NIZKRel_{\Issue}}(\crs_{\Issue},(\UK[\cuid_0],
+  \CCRED[\cscid_0],\ATTR[\cscid_0],r),(\CCom,\attrs,\PUBIK[\cscid_0]))$. The
+  NIZK proofs included in the signatures produced by $\cuid_0$ are defined
+  correspondingly, but for $\NIZK^{\NIZKRel_{\Sign}}$. From $G_1^0$, we define
+  $G_2^0$, but instead of using \NIZKProve, we use \NIZKSim (for both \Issue
+  and \Sign). That is, the proofs for credential requests are generated as
+  $\pi^s_0 =\NIZKSim^{\NIZKRel_{\Issue}}(\crs_{\Issue},\tau,(\CCom,\attrs,
+  \PUBIK[\cscid_0]))$. By zero-knowledge of the NIZK systems for \Issue and
+  \Sign, $G_2^0$ is indistinguishable from $G_1^0$.
+
+  On the other hand, following the same process for $G_1^1$ and $G_2^1$.
+  Concretely, for the case of the proofs at issuance time, they are of the
+  shape $\pi^s_1 =\NIZKSim^{\NIZKRel_{\Issue}}(\crs_{\Issue},\tau,(\CCom,\attrs,
+  \PUBIK[\cscid_1]))$. Note first that $\PUBIK[\cscid_1] = \PUBIK[\cscid_0]$,
+  by definition of the \OBTCHAL oracle. Hence, the produced proofs are exactly
+  the same independently on the value of the bit $b$.
+
+  Thus, $\AdvIssAnon=|\Pr\lbrack
+  \ExpIssAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpIssAnonz(1^\secpar)=1\rbrack|$.
+  As argued, $G_1$ is indistinguishable from $\ExpIssAnonb$, so
+  $\AdvIssAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
+  G_1^0(1^\secpar)=1\rbrack| \approx
+  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
+  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
+  \AdvIssAnon is negligible.
+
 \end{proof}
@@
   indistinguishable, due to the IND-CCA property of the encryption scheme
-  (so, the \ceval values in $\pi^s_0$ and $\pi^s_1$ are indistinguishable),
+  (so, the \ceval values in $\csig_0$ and $\csig_1$ are indistinguishable),
   in the  challenge oracle used in the anonymity game, we restrict to
   $\PUBIK[\scid_0] = \PUBIK[\scid_1]$, and the respective \cinsp values encrypt
-  the same \yinsp value.
+  the same \yinsp value (and, otherwise, \adv~is not allowed to open it).
 

### 2022-06-13 prism-backend/research/gsac/app-model-related.tex
Defining DAC.

@@
 (with selective disclosure). Therein, an anonymous credential scheme is
-defined via $OrgKeyGen$ and $UserKeyGen$ algorithms (roughly equivalent to
+defined via $OrgKeyGen$ (which we rename to $IssKeyGen$, and $UserKeyGen$
+algorithms (roughly equivalent to
 \IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
@@
   \scalebox{0.9}{      
-    \begin{minipage}[t]{0.4\textwidth}        
+    \begin{minipage}[t]{0.5\textwidth}        
       \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
-        b^* \gets \adv^{HU,CU,Obtain,Show,LoR} \\
+        \parm \gets \Setup(1^\secpar) \\
+        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\parm) \\
         \pcreturn b^*
@@
   \scalebox{0.9}{      
-    \begin{minipage}[t]{.6\textwidth}
+    \begin{minipage}[t]{.5\textwidth}
       \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
-        (\opk,\osk) \gets OrgKeyGen(1^\secpar) \\        
+        \parm \gets \Setup(1^\secpar) \\
+        (\opk,\osk) \gets IssKeyGen(\parm) \\        
         (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\opk) \\
@@
 \item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
-    and $(\opk',\osk') \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
+    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
     construction. Returns $\parm \gets (\parm',\opk')$.
-\item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs \IKeyGen from our
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
   \CUASGen construction, setting $\fissue^1$ as issuance function.
-\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] Runs \UKeyGen from the
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
   \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
-  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
+  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
   Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
   $\fissue^1$ as issuance function.
-\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
-  \Verify(\opk,\dattrs) \rangle$.]
+\item[$1/0 \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
+  \Verify(\ipk,\dattrs) \rangle$.]
   Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
@@
   To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
-  that \adv~ wins its game. Note that, since $b=1$ in line 4 of the
+  that \adv~ wins its game. Note that, since $b=1$ in line 5 of the
   unforgeability game of \figref{fig:model-ac}, then by construction, \Verify
@@
   there is no corrupt user with a credential containing $D$, then this leads to
-  \advB winning at line 8 in \figref{fig:exp-uas-unfor-sign}, as no credential
+  \advB winning at line 9 in \figref{fig:exp-uas-unfor-sign}, as no credential
   owned by a corrupt user that can be extracted can make the $\feval^{\dattrs}$
-  function output $\yeval=D$. Thus, \advB wins with the same probability as
+  function output $\yeval^0=D$. Thus, \advB wins with the same probability as
   \adv~ does.  
@@
 
+\todo{Rewrite when the full rewriting of the paper is done. For now, just
+  adapting the construction.}
 We give a simple definition for delegatable anonymous credentials extending
-the anonymous credential model in \cite{fhs19}. Next, we briefly describe a
-construction based on $(\fissue^n,\feval^{n,\dattrs},\finsp^0)$-\CUASGen, and
+the anonymous credential model in \cite{fhs19}, but drawing inspiration from
+\cite{bcc+09}. Next, we briefly describe a construction based on $(\fissue^n,
+\feval^{n,\dattrs},\finsp^0)$-\CUASGen, and
 show that it satisfies our basic notion of delegatable anonymous credentials.
@@
     \begin{minipage}[t]{0.4\textwidth}
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,dac}(1^\secpar)$}{%
-        b^* \gets \adv^{HU,CU,obtain,Show,LoR} \\
+      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
+        \pcreturn b^*
+      }
+      \vspace*{0.5em}
+
+      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
         \pcreturn b^*
@@
         \parm \gets \Setup(1^\secpar) \\        
-        (D,n+1,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\opk) \\
+        (D,n+1,\st) \gets \adv^{\mathcal{O}_{forge}}(\parm,\opk) \\
         (\cdot,b) \gets \langle \adv(\st),\Verify(\opk,
@@
   \caption{Security games for delegatable anonymous credentials with selective
-    disclosure based on \cite{fhs19}. \OWNR and \ATTR tables are essentially as
-    in \secref{ssec:model-uas}. $level(\opk,n)$ is a helper function that
-    returns the $1$ if the level of \opk is $n$, or $0$ otherwise.}
+    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
+    CU,Obtain,Issue,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon} \gets \lbrace
+    HU,CU,Obtain,Issue,Show,SigLoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace
+    HU,CU,ObtIss,Issue,Show \rbrace$. $IssLor$ is equivalent to \OBTCHALb in
+    \UAS, whereas $SigLor$ is equivalent to \CHALb. Also, \OWNR and \ATTR
+    tables are essentially as in \secref{ssec:model-uas}.
+    $level(\opk,n)$ is a helper function that returns the $1$ if the level of
+    \opk is $n$, or $0$ otherwise.}
   \label{fig:model-dac}  
@@
 \subsubsection{\CUASDAC Construction.} %
+In a nutshell, we distinguish between top-level issuers, and users who delegate
+their credentials, thus acting as lower-level issuers. Top-level issuers are
+exactly as issuers in \CUASGen. Lower-level issuers need to make public an
+issuance public key that reveals the attributes they are willing to delegate,
+and their credential level. The issuance function has to prove that the
+requestor is asking
+for a credential that: (1) increments the credential level exactly by one, and
+(2) the requested attributes are a subset of those that the low-level issuer
+can delegate. Note that both conditions apply recursively. To prevent
+mix-and-match attacks, in each (lower-level) credential we include as attributes
+a ``serial number'' of the immediately upper level credential, and another one
+for the credential being issued (\todo{see figure}). For a credential of
+level $n$, the evaluation function must output a chain of proofs of knowledge of
+a sequence of credentials of levels $n$ up to $1$, with matching serial number
+pairs.
+
+More concretely, we define issuance functions for low-level issuers to have
+the following structure:
+
+\begin{align}
+  & \fissue^{n,r_n,\attrs}(\usk,\scred,\attrs') \coloneqq \lbrace
+    \pcif \attrs'_1 = n+1 \land \attrs'_2 = r_n \land
+    \attrs'_{[4..t]} \subseteq \attrs: \pcreturn 1; \pcelse \pcreturn 0
+    \rbrace \nonumber \\
+  &  \feval^{n,\dattrs}(\usk,\cred,\msg) \coloneqq \lbrace \textrm{Parse \cred
+    as }(\cred',\Sig,r); \pi \gets K(\cred') \rbrace
+\end{align}
+\todo{XXXX}
+
+Where $n$ is its depth in the delegation chain, $\attrs'_3$ must be some serial
+number chosen by the issuer for the new credential, and $r_n$ is a random number
+serving as serial number for the issuer's credential (chosen by its parent
+issuer), and \attrs is the attribute set that it can delegate. Note that this
+issuance funcion expects the first attribute of the requested credential to
+encode the credential depth, the second attribute to encode the serial number
+of the issuer's credential, and the third attribute to encode the random
+number (chosen uniformly by the issuer) that will serve as identifier of the
+produced credential. All other attributes only need to meet the condition of
+being contained in the attributes \attrs of the issuer's credential.
+
+\begin{description}
+\item[$\parm \gets \Setup(1^\secpar)$.] As in \CUASAC.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If the issuer is a top-level
+  issuer, $IssKeyGen$ simply runs \IKeyGen in \CUASAC. If it is a lower-level
+  issuer (say, of level $n>1$), this is in fact a user, who has already run
+  $UserKeyGen$ below (and thus, \IKeyGen), and owns a credential  over
+  attributes \attrs, issued by some higher-level issuer. Thus, instead of
+  running \SBCMKeyGen, sets $\isk \gets \usk$, and its issuance function to
+  $\fissue^{n,r_n,\attrs}$. % The
+  % lower-level issuer also runs $(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
+  % \feval^{\dattrs})$, where $\feval^{\dattrs}$ is as defined as in
+  % \appref{sapp:related-models-ac}, and thus reveals the attributes that the
+  % low-level issuer can delegate. That is, by definition of $\feval^{\dattrs}$,
+  % given the \attrs defined in $\fissue^{n,r_n,\attrs}$, $\yeval = \attrs$ (also,
+  % note that the issuer's credential may contain other non-delegatable
+  % attributes).
+  Finally, the lower-level issuer sets $\ipk \gets (\ipk,n,r_n,\attrs,
+  \fissue^{n,r_n,\attrs})$.
+\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
+  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
+  $\usk \gets \isk$.
+\item[$\langle \cred/\bot,\top/\bot \rangle \gets
+  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
+  We assume that the set \attrs of attributes to be included in the credential
+  are of the form $(n+1,r_n,r_{n+1},\attrs')$, where $n+1$ is the level of the
+  credential to be issued, $r_n$ is the identifier of the issuer's credential
+  (or some special fixed value if it is a top level credential), $r_{n+1}$ is
+  a serial number for the new credential, chosen by the issuer, and $\attrs'$
+  is the attributes being requested by the user. Both issuer and user agree on
+  these values beforehand. If the issuer is top-level, this protocol runs as in
+  \CUASAC, for \attrs as above. Else, if the issuer is not top-level (say, it
+  has level $n>1$), the protocol in \CUASAC is augmented as follows:
+
+  \begin{itemize}
+  \item \uline{User}: $r \gets \bin^l$ (for some appropriate $l$).
+  \item \uline{User,Issuer}: Run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
+    for \attrs as specified above.
+  \item \uline{Issuer}: $\Sig=(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
+    \feval^{n,\dattrs})$. Where \cred is the issuer's $n$-th level credential,
+    and $\feval^{n,\dattrs}$ is as in \appref{sapp:related-models-ac}, plus
+    revealing the credential level (encoded in \cred's first attribute).
+  \item \uline{User}: Accept if $\Verify(\opk,\ipk,\Sig,r,\feval^{n,\dattrs})=
+    1$, and return $(\cred,\ipk,\Sig,r)$ as $(n+1)$-level credential, where
+    \cred is the credential produced in the interactive protocol at step 2.
+    Otherwise, reject.
+  \end{itemize}
+
+  Note that, basically, the issuer proves that it owns a credential of level $n$
+  over the attributes it is delegating.
+
+\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
+  \Verify(\opk,\dattrs) \rangle$.]
+  As in \CUASAC, but using $\feval^{n,\dattrs}$ as signature evaluation
+  function.
+\end{description}
+
+\iffalse
 We adopt the simplification that the level of an issuer is encoded in its public
@@
 \CUASGen scheme.
+\fi
 

### 2022-06-13 prism-backend/research/gsac/security-uas.tex
Defining DAC.

@@
   adversarial issuer are of
-  the form $\pi^*_0 =\NIZKProve^{\NIZKRel_{\Issue}}(\crs_{\Issue},(\UK[\cuid_0],
-  \CCRED[\cscid_0],\ATTR[\cscid_0],r),(\CCom,\attrs,\PUBIK[\cscid_0]))$. The
+  the form $\pi^*_0 =\NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\UK[\cuid_0],
+  \CCRED[\cscid_0],\ATTR[\cscid_0],r),(\Ccom,\attrs,\PUBIK[\cscid_0]))$. The
   NIZK proofs included in the signatures produced by $\cuid_0$ are defined
@@
   and \Sign). That is, the proofs for credential requests are generated as
-  $\pi^s_0 =\NIZKSim^{\NIZKRel_{\Issue}}(\crs_{\Issue},\tau,(\CCom,\attrs,
+  $\pi^s_0 =\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\tau,(\Ccom,\attrs,
   \PUBIK[\cscid_0]))$. By zero-knowledge of the NIZK systems for \Issue and
@@
   Concretely, for the case of the proofs at issuance time, they are of the
-  shape $\pi^s_1 =\NIZKSim^{\NIZKRel_{\Issue}}(\crs_{\Issue},\tau,(\CCom,\attrs,
+  shape $\pi^s_1 =\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\tau,(\Ccom,\attrs,
   \PUBIK[\cscid_1]))$. Note first that $\PUBIK[\cscid_1] = \PUBIK[\cscid_0]$,
-  by definition of the \OBTCHAL oracle. Hence, the produced proofs are exactly
+  by definition of the \OBTCHALb oracle. Hence, the produced proofs are exactly
   the same independently on the value of the bit $b$.

### 2022-06-15 prism-backend/research/gsac/app-model-related.tex
Seemingly valid construction of DAC from UAS. Proof pending.

--- 2022-05-28 prism-backend/research/gsac/app-model-related.tex
@@
 
-\todo{Naming gets a bit confusing here, as \cite{fhs19} use \opk as ``organization
-  public key'' and we use it as ``opener public key'', etc. Make some renaming
-  (probably, adopt our naming convention).}
-
 We adopt the model in \cite{fhs19}, where security of anonymous credentials
 (with selective disclosure). Therein, an anonymous credential scheme is
-defined via $OrgKeyGen$ and $UserKeyGen$ algorithms (roughly equivalent to
+defined via $OrgKeyGen$ (which we rename to $IssKeyGen$, and $UserKeyGen$
+algorithms (roughly equivalent to
 \IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
@@
   \scalebox{0.9}{      
-    \begin{minipage}[t]{0.4\textwidth}        
+    \begin{minipage}[t]{0.5\textwidth}        
       \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
-        b^* \gets \adv^{HU,CU,Obtain,Show,LoR} \\
+        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
+        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
         \pcreturn b^*
@@
   \scalebox{0.9}{      
-    \begin{minipage}[t]{.6\textwidth}
+    \begin{minipage}[t]{.5\textwidth}
       \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
-        (\opk,\osk) \gets OrgKeyGen(1^\secpar) \\        
-        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\opk) \\
-        (\cdot,b) \gets \langle \adv(\st),\Verify(\opk,D) \rangle \\
-        \pcif b = 1 \land \forall j: \OWNR[j] \in \CU
-        \implies D \not\subseteq \ATTR[j]: \\
+        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
+        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
+        (\cdot,b) \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
+        \pcif b = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
+        \land D \subseteq \ATTR[j]): \\% \forall j, \OWNR[j] \in \CU
+        % \implies D \not\subseteq \ATTR[j]: \\
         \pcind \pcreturn 1 \\
@@
 that, for better alignment with \UAS, we add a common setup process which is
-part of $OrgKeyGen$ in \cite{fhs19}. The change is inocuous functionality- and
+part of $IssKeyGen$ in \cite{fhs19}. The change is inocuous functionality- and
 security-wise, though.
@@
 \item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
-    and $(\opk',\osk') \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
-    construction. Returns $\parm \gets (\parm',\opk')$.
-\item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs \IKeyGen from our
+    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
+    construction. Returns $\parm \gets (\parm',\opk)$.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
   \CUASGen construction, setting $\fissue^1$ as issuance function.
-\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] Runs \UKeyGen from the
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
   \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
-  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
+  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
   Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
   $\fissue^1$ as issuance function.
-\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
-  \Verify(\opk,\dattrs) \rangle$.]
+\item[$1/0 \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
+  \Verify(\ipk,\dattrs) \rangle$.]
   Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
@@
 
-We give a simple definition for delegatable anonymous credentials extending
-the anonymous credential model in \cite{fhs19}. Next, we briefly describe a
-construction based on $(\fissue^n,\feval^{n,\dattrs},\finsp^0)$-\CUASGen, and
-show that it satisfies our basic notion of delegatable anonymous credentials.
-Roughly, a delegatable anonymous credential scheme is an anononymous credential
-scheme in which every issuer of level $n$ can only issue credentials of level
-$n+1$. For simplicity, we restrict to the case of using only one credential per
-signature, but the generalization is trivial. Note that, in addition to the
-algorithms in \secref{sapp:related-models-ac}, we add a helper function $level$
-which, given an issuer's public key and its alleged level, returns $1$ if the
-level is correct, or $0$ otherwise.
+To showcase the feasibility of building delegatable anonymous credentials (DAC)
+from \UAS, we give a simple definition for a DAC scheme, extending
+\cite{fhs19} and inspired by \cite{bcc+09}. Note however that, unlike the
+latter, our simple scheme built from \CUASGen does not ensure privacy of the
+delegation chain -- but it does, however, ensure that a (not top-level) issuer
+can only delegate attributes contained in a credential it owns. Also, for
+simplicity, we restrict to the case of using one credential per
+signature/interactive credential presentation, and assume that all parties use
+the same opener and \finsp function.
+%
+The functionality is thus defined as in \appref{sapp:related-models-ac}, i.e.,
+we have $Setup$, $IssKeyGen$ and $UserKeyGen$ algorithms, and $Obtain,Issue$ and
+$Show,Verify$ interactive protocols.
+%
+In the modelling for this setting, since there are multiple issuers, in addition
+to the oracles in \appref{sapp:related-models-ac}, we use $HI$ and $CI$ oracles,
+equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
+issuers, and corrupt existing ones, respectively. The issuance and sign
+anonymity properties are as before. For unforgeability, we still require
+that no adversary can authenticate using a set of attributes that have not been
+issued to a corrupt user. In addition, we require that for any possible
+successful authentication protocol using a level-$n$ credential, we can extract
+a chain of credentials of length $n$ such that each level-$i$ credential can
+be used successfully to authenticate a level-$(i+1)$ credential up to the
+level-$n$ credential, and that the attributes revealed in the level-$n$
+authentication are contained in all the credentials up the chain.
+
+% \todo{Rewrite when the full rewriting of the paper is done. For now, just
+%   adapting the construction.}
+% We give a simple definition for delegatable anonymous credentials extending
+% the anonymous credential model in \cite{fhs19}, but drawing inspiration from
+% \cite{bcc+09}. Next, we briefly describe a construction based on $(\fissue^n,
+% \feval^{n,\dattrs},\finsp^0)$-\CUASGen, and
+% show that it satisfies our basic notion of delegatable anonymous credentials.
+% Roughly, a delegatable anonymous credential scheme is an anononymous credential
+% scheme in which every issuer of level $n$ can only issue credentials of level
+% $n+1$. For simplicity, we restrict to the case of using only one credential per
+% signature, but the generalization is trivial. Note that, in addition to the
+% algorithms in \secref{sapp:related-models-ac}, we add a helper function $level$
+% which, given an issuer's public key and its alleged level, returns $1$ if the
+% level is correct, or $0$ otherwise.
 
@@
     \begin{minipage}[t]{0.4\textwidth}
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,dac}(1^\secpar)$}{%
-        b^* \gets \adv^{HU,CU,obtain,Show,LoR} \\
+      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        %(\opk,\osk) \gets \OKeyGen(\parm) \\
+        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
+        \pcreturn b^*
+      }
+      \vspace*{0.75em}
+
+      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+%        (\opk,\osk) \gets \OKeyGen(\parm) \\        
+        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
         \pcreturn b^*
@@
         \parm \gets \Setup(1^\secpar) \\
-        (D,n+1,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\opk) \\
-        (\cdot,b) \gets \langle \adv(\st),\Verify(\opk,
-        D \cup \lbrace n+1 \rbrace)\rangle \\
+        (D=(n,D'),\ipk_n,\st) \gets
+        \adv^{\mathcal{O}_{forge}}(\parm) \\
+        (\cdot,b) \gets \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
         \pcif b = 0: \pcreturn 0 \\
-        \pcif(\forall j: \OWNR[j] \in \CU \implies D \cup \lbrace n+1 \rbrace
-        \not\subseteq \ATTR[j])~\lor\\
-        \pcind level(\opk,n) = 0: \pcreturn 1 \\
+        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
+        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
+        \textrm{Let \utrans be the transcript of $\langle \adv(\st),
+          \Verify(\cdot,\cdot)\rangle$} \\        
+        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
+        \gets ExtractChain(\utrans) \\ 
+        % D \cup \lbrace n+1 \rbrace)\rangle \\        
+        \pcif \exists i \in [1,n]~\suchthat~
+        \langle Show(\ipk_{i-1},\attrs(\cred_{i}),(i,D'),\cred_{i}), \\
+        \hspace*{8em}Verify(\ipk_{i-1},(i,D')) \rangle
+        = \langle \cdot,0\rangle \\%~\lor % \\
+        % \pcind \attrs(\cred_i) \not\subseteq \attrs(\cred_{i-1}):
+        \pcind \pcreturn 1 \\
+%        \pcif(\forall j: \OWNR[j] \in \CU \implies D \cup \lbrace n+1 \rbrace
+%        \not\subseteq \ATTR[j])~\lor\\
+%        \pcind level(\opk,n) = 0: \pcreturn 1 \\
         \pcreturn 0
@@
   \caption{Security games for delegatable anonymous credentials with selective
-    disclosure based on \cite{fhs19}. \OWNR and \ATTR tables are essentially as
-    in \secref{ssec:model-uas}. $level(\opk,n)$ is a helper function that
-    returns the $1$ if the level of \opk is $n$, or $0$ otherwise.}
+    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
+    CU,HI,CI,Obtain,Issue,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon} \gets
+    \lbrace HU,CU,HI,CI,Obtain,Issue,Show,SigLoR\rbrace$. $\mathcal{O}_{forge}
+    \gets \lbrace HU,CU,HI,CI,ObtIss,Issue,Show \rbrace$. $IssLor$ is equivalent
+    to \OBTCHALb in \UAS, whereas $SigLor$ is equivalent to \CHALb. Also, \OWNR
+    and \ATTR tables are essentially as in \secref{ssec:model-uas}. With $D =
+    (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
+    which denotes the level of the credential used for authentication.}
   \label{fig:model-dac}  
@@
 \subsubsection{\CUASDAC Construction.} %
+In a delegatable AC (DAC) scheme, all users are (or may be) also issuers. We
+only distinguish between top-level issuers, who have level $n=0$, and
+lower-level issuers, who have level $n>0$. In our \CUASDAC scheme, we assume
+that the first attribute (after the user's secret key) encodes the level of
+the credential. That is, $\attrs_1=n$, for a credential of level $n$. In
+addition, all users (i.e., with $n>0$) who want to delegate have to publicly
+list:
+
+\begin{enumerate}
+\item The level $n$ of the credential they delegate.
+\item Their public key \ipk.
+\item An \UAS signature proving knowledge of a credential of level $n$, and over
+  the attributes that this level-$n$ issuer is delegating.
+\item The \ipk of the parent issuer.
+\item Their $\fissue^{n,\dattrs}$ function.
+\item An $\feval^{n,\dattrs}$ function used to produce the signature at item 2.
+\end{enumerate}
+
+We assume that, from an \ipk, it is possible to find the corresponding issuer
+(e.g., using the previously mentioned public list). The mentioned
+$\fissue^{n,\dattrs}$ functions must follow the pattern in \esref{eq:funcs-dac}.
+Namely, the issuance function checks that the first requested attribute equals
+$n+1$, and that all requested attributes are a subset of the attribute set
+\dattrs being delegated by the level-$n$ issuer. In addition, signature
+evaluation functions $\feval^{n,\dattrs}$, also shown in \esref{eq:funcs-dac},
+must reveal the level of the credential used to produce the \UAS signature at
+item 2, and reveal a set of attributes \dattrs that the level-$n$ issuer
+delegates. Verifiers can then trivially check if the set of revealed attributes
+are contained within the attributes delegatable by the parent issuer%
+\footnote{Of course, additional checks may be added in both functions, this is
+  the bare minimum.}. \figref{fig:XXX} depicts a sample of the delegation chain
+that this structure creates.
+
+\begin{align}
+  & \fissue^{n,\dattrs}(\usk,\cred,\attrs) \coloneqq \lbrace
+    \pcif \attrs_1 = n+1 \land \attrs \subseteq \dattrs: \pcreturn 1; \pcelse \pcreturn 0
+    \rbrace \nonumber \\
+  & \feval^{n,\dattrs}(\usk,\cred,\msg) \coloneqq \lbrace
+    \pcreturn (\attrs_1(\cred),\dattrs(\cred)) \rbrace
+  \label{eq:funcs-dac}
+\end{align}
+
+From this high-level description, we define the algorithms of \CUASDAC:
+
+\begin{description}
+\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
+    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
+    construction. Returns $\parm \gets (\parm',\opk)$. Note that $\finsp^0$ can
+    be replaced by any desired opening function.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $n=0$, simply run \IKeyGen as
+  in \CUASAC. If $n>0$, note that this is a user who wants to delegate a
+  previously obtained credential \cred. Thus, it has already run $UserKeyGen$
+  below, which internally also runs \IKeyGen as in \CUASGen and sets $\usk \gets
+  \isk$. In addition, the level-$n$ issuer picks a random message $r$ and
+  computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
+  \feval^{n,\dattrs})$, for the \dattrs set it wants to reveal -- which must
+  include the attributes to delegate, and the credential level. It then
+  publishes $(n,\ipk,\Sig,\ipk^{n-1},\fissue^{n,\dattrs},\feval^{n,\dattrs})$,
+  where $\ipk^{n-1}$ is the public key of the parent issuer,
+  $\fissue^{n,\dattrs}$ is an issuance function as described in
+  \esref{eq:funcs-dac}, and $\feval^{n,\dattrs}$ is also as in
+  \esref{eq:funcs-dac}, revealing the attributes that the issuer is willing to
+  delegate..
+\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
+  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
+  $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
+  credentials.
+\item[$\langle \cred/\bot,\top/\bot \rangle \gets
+  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
+  If $n>0$, the user first finds the corresponding $(n,\ipk,\Sig,\ipk^{n-1},
+  \fissue^{n,\dattrs},\feval^{n,\dattrs})$ tuple, and checks \Sig running
+  \Verify as in \CUASGen (with the retrieved $\feval^{n,\dattrs}$). Then,
+  user and level-$n$ issuer run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
+  using $\fissue^{n,\dattrs}$ as issuance function. If $n=0$, then both run
+  $\langle\Obtain,\Issue\rangle$ as in \CUASGen, using the \fissue function
+  required by the issuer.
+\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
+  \Verify(\opk,\dattrs) \rangle$.] As in \CUASGen. Concretely, arbitrary
+  \feval functions can be used -- not necessarily $\feval^{n,\dattrs}$.
+\end{description}
+
+\iffalse
 We adopt the simplification that the level of an issuer is encoded in its public

### 2022-06-15 prism-backend/research/gsac/model-uas.tex
Seemingly valid construction of DAC from UAS. Proof pending.

@@
   \rangle \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.] %
-  This interactive protocol lets a user with key \usk running the
-  \Obtain process, receive a credential \cred from an issuer in the system, on
-  attribute set $\attrs$. The user leverages a set of credentials \scred,
-  each with a matching issuer key in \sipk.
-  The user outputs the produced credential \cred, while
-  the issuer outputs the protocol transcript \utrans for the produced
-  credential.
+  This interactive protocol lets a user with key \usk running the \Obtain
+  process, receive a credential \cred from an issuer in the system, on attribute
+  set $\attrs$. The user leverages a set of credentials \scred, each with a
+  matching issuer key in \sipk (ommitted in \Obtain for readability). The user
+  outputs the produced credential \cred, while the issuer outputs the protocol
+  transcript \utrans for the produced credential.
 \item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
   Upon receiving a user secret key \usk, opener public key \opk, a set of
-  credentials \scred, a message \msg and evaluation
-  function \feval, returns signature \sig, and a plaintext value \yeval. For
-  readability, we use \Sig to denote the tuple $(\sig,\yeval)$.
+  credentials \scred, a message \msg and evaluation function \feval, returns
+  signature \sig, and a plaintext value \yeval. For readability, we assume
+  that, for each $\cred \in \scred$, we can get the corresponding issuer public
+  key \ipk; also, we use use \Sig to denote the tuple $(\sig,\yeval)$.
 \item[$\Verify(\opk, \sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]

### 2022-06-16 prism-backend/research/gsac/app-model-related.tex
Refined definition for unforgeability in DAC, and proof.

@@
   using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
-  open function, with $\opk'$ from \parm as opener public key.
+  open function, with \opk from \parm as opener public key.
 \end{description}
@@
 \begin{theorem}[Anonymity of \CUASAC]
-  If the base \CUASGen construction is anonymous according to
-  \defref{def:anonymity-uas}, then \CUASAC is an anonymous AC scheme
+  \label{thm:anon-cuasac}
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
   according to \cite{fhs19}.
@@
   an adversary \advB against anonymity of \CUASGen as defined in
-  \defref{def:anonymity-uas}.
+  \defref{def:sign-anonymity-uas}.
 
@@
 \begin{theorem}[Unforgeability of \CUASAC]
+  \label{thm:forge-cuasac}
   If the base \CUASGen construction has sign unforgeability according to
@@
 
-To showcase the feasibility of building delegatable anonymous credentials (DAC)
-from \UAS, we give a simple definition for a DAC scheme, extending
-\cite{fhs19} and inspired by \cite{bcc+09}. Note however that, unlike the
-latter, our simple scheme built from \CUASGen does not ensure privacy of the
-delegation chain -- but it does, however, ensure that a (not top-level) issuer
-can only delegate attributes contained in a credential it owns. Also, for
-simplicity, we restrict to the case of using one credential per
-signature/interactive credential presentation, and assume that all parties use
-the same opener and \finsp function.
+We give a simple definition for a Delegatable Anonymous Credentials (DAC)
+scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
+our simple scheme built from \CUASGen does not ensure privacy of the delegation
+chain -- which could be achieved by making \feval output projective proofs like
+in \cite{bcc+09}, but since our goal is to showcase the feasibility of building
+DAC from \UAS, we leave that out for brevity. Our simple scheme does, however,
+ensure that a (not top-level) issuer can only delegate attributes contained in a
+credential it owns. Also, for simplicity, we restrict to the case of using one
+credential per signature/interactive credential presentation, and assume that
+all parties use the same opener and \finsp function.
 %
 The functionality is thus defined as in \appref{sapp:related-models-ac}, i.e.,
-we have $Setup$, $IssKeyGen$ and $UserKeyGen$ algorithms, and $Obtain,Issue$ and
-$Show,Verify$ interactive protocols.
+we have $Setup$, $IssKeyGen$ and $UserKeyGen$ algorithms, and $\langle Obtain,
+Issue \rangle$ and $\langle Show,Verify \rangle$ interactive protocols.
 %
@@
 
-% \todo{Rewrite when the full rewriting of the paper is done. For now, just
-%   adapting the construction.}
-% We give a simple definition for delegatable anonymous credentials extending
-% the anonymous credential model in \cite{fhs19}, but drawing inspiration from
-% \cite{bcc+09}. Next, we briefly describe a construction based on $(\fissue^n,
-% \feval^{n,\dattrs},\finsp^0)$-\CUASGen, and
-% show that it satisfies our basic notion of delegatable anonymous credentials.
-% Roughly, a delegatable anonymous credential scheme is an anononymous credential
-% scheme in which every issuer of level $n$ can only issue credentials of level
-% $n+1$. For simplicity, we restrict to the case of using only one credential per
-% signature, but the generalization is trivial. Note that, in addition to the
-% algorithms in \secref{sapp:related-models-ac}, we add a helper function $level$
-% which, given an issuer's public key and its alleged level, returns $1$ if the
-% level is correct, or $0$ otherwise.
-
 \begin{figure}[ht!]
@@
         \parm \gets \Setup(1^\secpar) \\
-        %(\opk,\osk) \gets \OKeyGen(\parm) \\
         b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
@@
         \parm \gets \Setup(1^\secpar) \\
-%        (\opk,\osk) \gets \OKeyGen(\parm) \\        
-        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
+        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
         \pcreturn b^*
@@
         \gets ExtractChain(\utrans) \\ 
-        % D \cup \lbrace n+1 \rbrace)\rangle \\        
         \pcif \exists i \in [1,n]~\suchthat~
-        \langle Show(\ipk_{i-1},\attrs(\cred_{i}),(i,D'),\cred_{i}), \\
-        \hspace*{8em}Verify(\ipk_{i-1},(i,D')) \rangle
-        = \langle \cdot,0\rangle \\%~\lor % \\
-        % \pcind \attrs(\cred_i) \not\subseteq \attrs(\cred_{i-1}):
+        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
+        \pcind D' \not\subseteq \ATTR[\iid]) \land
+        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
         \pcind \pcreturn 1 \\
-%        \pcif(\forall j: \OWNR[j] \in \CU \implies D \cup \lbrace n+1 \rbrace
-%        \not\subseteq \ATTR[j])~\lor\\
-%        \pcind level(\opk,n) = 0: \pcreturn 1 \\
         \pcreturn 0
@@
     disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
-    CU,HI,CI,Obtain,Issue,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon} \gets
-    \lbrace HU,CU,HI,CI,Obtain,Issue,Show,SigLoR\rbrace$. $\mathcal{O}_{forge}
-    \gets \lbrace HU,CU,HI,CI,ObtIss,Issue,Show \rbrace$. $IssLor$ is equivalent
-    to \OBTCHALb in \UAS, whereas $SigLor$ is equivalent to \CHALb. Also, \OWNR
-    and \ATTR tables are essentially as in \secref{ssec:model-uas}. With $D =
+    CU,HI,CI,Obtain,Issue,Obtiss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon}
+    \gets \lbrace HU,CU,HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$.
+    $\mathcal{O}_{forge} \gets \lbrace HU,CU,HI,CI,Obtain,ObtIss,Issue,Show
+    \rbrace$. $IssLor$ is equivalent to \OBTCHALb in \UAS, whereas $SigLor$ is
+    equivalent to \CHALb. Also, \OWNR and \ATTR tables are essentially as in
+    \secref{ssec:model-uas}. $\ISR[\ipk]$, in this case, returns the identifier
+    of the issuer with public key \ipk. With $D =
     (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
@@
 \item The \ipk of the parent issuer.
-\item Their $\fissue^{n,\dattrs}$ function.
+\item The $\fissue^{n,\dattrs}$ function they will require for delegating.
 \item An $\feval^{n,\dattrs}$ function used to produce the signature at item 2.
@@
 must reveal the level of the credential used to produce the \UAS signature at
-item 2, and reveal a set of attributes \dattrs that the level-$n$ issuer
+item 2, as well as the set of attributes \dattrs that the level-$n$ issuer
 delegates. Verifiers can then trivially check if the set of revealed attributes
 are contained within the attributes delegatable by the parent issuer%
-\footnote{Of course, additional checks may be added in both functions, this is
+\footnote{Additional checks may be added in both functions, but this is
   the bare minimum.}. \figref{fig:XXX} depicts a sample of the delegation chain
@@
 \item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
-  \Verify(\opk,\dattrs) \rangle$.] As in \CUASGen. Concretely, arbitrary
-  \feval functions can be used -- not necessarily $\feval^{n,\dattrs}$.
+  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of \CUASGen.  
 \end{description}
+
+\paragraph{Security of \CUASDAC.} %
+We prove that \CUASDAC is an anonymous and unforgeable DAC scheme, according to
+the model in \figref{fig:model-dac}, if the underlying \CUASGen construction has
+anonymous issuance and signing, and has unforgeable issuance and signing.
+
+\begin{theorem}[Issuance anonymity of \CUASDAC]
+  If the base \CUASGen construction has issuance anonymity according to
+  \defref{def:issue-anonymity-uas}, then \CUASDAC also has issuance anonymity.
+\end{theorem}
+
+\begin{proof}
+  Given \adv~ against issuance anonymity of \CUASDAC as defined in
+  $\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
+  issuance anonymity of \CUASGen as defined in \defref{def:issue-anonymity-uas}.
+
+  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
+  oracle, i.e.: for calls to $HU,CU,HI,CI,Obtain,Show,IssLoR$, \advB redirects
+  to \HUGEN,\CUGEN,\IGEN,\ICORR,\OBTAIN,\SIGN,\OBTCHALb, respectively. Note that
+  ``translating'' the inputs from the former into inputs for the latter is
+  trivial. Obviously, if \adv~ wins in its issuance anonymity game, then so does
+  \advB with the  same probability.
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Signature anonymity of \CUASDAC]
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASDAC also has signature anonymity.
+\end{theorem}
+
+\begin{proof}
+  This is the same as in \thmref{thm:anon-cuasac}.
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability of \CUASAC]
+  If the base \CUASGen construction has issuance and signature unforgeability
+  according to \defref{def:issue-forge-uas} and \defref{def:sign-forge-uas}, and
+  non-frameability according to \defref{def:frame-uas}, then \CUASAC is an
+  unforgeable AC scheme.
+\end{theorem}
+
+\begin{proof}
+  First, we define the $ExtractChain(\utrans)$ function for our construction.
+  Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows for the approach
+    to transform non-interactive signature and verification in \UAS to interactive
+    presentations, as described in \secref{ssec:variants-gsac}.}, where $r$ is a
+  fresh random number produced by the environment (acting as honest verifier),
+  and \Sig is a \CUASGen signature over $r$. Thus, $ExtractChain$ leverages
+  \ExtractSign from \CUASGen (see \secref{ssec:security-uas}) to get the
+  credential and associated \ipk used to produce \Sig. Note that, for this
+  \ipk, $\ipk = \ipk_{n-1}$ in $\Exp^{forge}_{\adv,dac}$. In \CUASDAC, we can
+  leverage $\ipk_{n-1}$ to fetch from the public list a signature $\Sig_{n-1}$
+  generated by the issuer owner of $\ipk_{n-1}$. Again, we apply \ExtractSign
+  from \CUASGen, to get the credential one layer up in the chain.
+  $ExtractChain$ repeats this step, until reaching the top level credential,
+  issued by $\ipk_0$.
+
+  For the proof, we first replace within $Setup$ the $\NIZKSetup$ algorithms for
+  issuance and signing with their corresponding $\NIZKSetup$. Due to their
+  zero-knowledge property, the resulting game is indistinguishable. Also, note
+  that $ExtractChain$ succeeds to extract the corresponding credential chain,
+  due to simulation extractability of the NIZKs.
+
+  From the previous, the same reasoning as in \thmref{thm:forge-cuasac} applies
+  to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
+  suppose that, from \utrans obtained at line 6, $ExtractChain$ outputs a
+  delegation chain that makes \adv~win at line 10. This means that an
+  uncorrupted issuer at position $i-1$ of the chain did not own a credential
+  containing $D'$, but the issuer at position $i$ does. Then, either of the
+  following must happen:
+
+  \begin{itemize}
+  \item The credential of the issuer at position $i$ is a forgery, meaning that
+    it is a valid signature by the issuer at position $i-1$, who did not produce
+    it. This can be used to break signature non-frameability of \CUASGen.
+  \item The credential of the issuer at position $i$ is not a forgery, meaning
+    that it is a valid signature by the issuer at position $i-1$, who produced
+    it. But this contradicts the conditions required by $\fissue^{n,\dattrs}$,
+    and therefore breaks issuance unforgeability of \CUASGen.
+  \end{itemize}
+  %
+  \qed
+\end{proof}
 

### 2022-06-17 prism-backend/research/gsac/app-model-related.tex
Added model and proofs for Revocable ACs.

@@
         (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
-        (\cdot,b) \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
+        \langle \cdot,(b,\utrans) \rangle
+        \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
         \pcif b = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
@@
   $\fissue^1$ as issuance function.
-\item[$1/0 \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
-  \Verify(\ipk,\dattrs) \rangle$.]
+\item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
+  \gets \langle Show(\ipk,\attrs,\dattrs,
+  \cred),\Verify(\ipk,\dattrs) \rangle$.]
   Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
@@
 leveraging other credentials not any fixed custom issuance policy. Thus,
-signature unforgeability from \UAS is enough.
+signature unforgeability from \UAS is enough. Note that AC schemes modelled
+as in \cite{fhs19} do not have issuance anonymity, as the user public key
+is passed to the issuer.
 
@@
   \scalebox{0.9}{      
-    \begin{minipage}[t]{0.4\textwidth}
+    \begin{minipage}[t]{0.45\textwidth}
       \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
@@
         b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
+        \pccomment{Abort if challenge creds belong to} \\
+        \pccomment{users with different delegation chains} \\
         \pcreturn b^*
       }
-      \vspace*{0.75em}
+      \vspace*{0.5em}
 
@@
         b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
+        \pccomment{Abort if challenge sigs belong to} \\
+        \pccomment{users with different delegation chains} \\
         \pcreturn b^*
@@
   \scalebox{0.9}{      
-    \begin{minipage}[t]{.6\textwidth}
+    \begin{minipage}[t]{.55\textwidth}
       \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
@@
         \adv^{\mathcal{O}_{forge}}(\parm) \\
-        (\cdot,b) \gets \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
+        \langle\cdot,(b,\utrans)\rangle \gets
+        \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
         \pcif b = 0: \pcreturn 0 \\
@@
         \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
-        \textrm{Let \utrans be the transcript of $\langle \adv(\st),
-          \Verify(\cdot,\cdot)\rangle$} \\        
         (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
@@
     disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
-    CU,HI,CI,Obtain,Issue,Obtiss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon}
+    CU,HI,CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon}
     \gets \lbrace HU,CU,HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$.
@@
   required by the issuer.
-\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
+\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle
+  \gets \langle Show(\opk,\attrs,\dattrs,\cred),
   \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of \CUASGen.  
@@
 
-\iffalse
-We adopt the simplification that the level of an issuer is encoded in its public
-key, and anybody can check the issuer's level via some publicly accessible
-mechanism. This can be ensured, e.g., by having each issuer post its
-  public key along with a proof of ownership of a level $n$ credential -- which
-  can be trivially done in \CUASGen.
+\subsection{Revocable Anonymous Credentials}
+\label{sapp:related-models-rac}
+
+In \cite{cks10}, revocable anonymous credentials are proposed. From \CUASGen, it
+is straightforward to build an AC system with verifier local revocation, like in
+\cite{bs04}. Basically, all credentials get an identifier as first attribute,
+and \feval functions prove that the opener can retrieve that identifier. Then,
+in case of needing to revoke a concrete credential, any verifier can interact
+with the opener to add an identifier to its own revocation list (alternatively,
+there can be a public list of revoked credentials). Having \feval functions
+prove that the credential identifier does not belong to that list thus directly
+implements privacy-preserving revocation. We first give a simple model in
+\figref{fig:model-rac}, extending that in \appref{sapp:related-models-ac}. As
+before, for simplicity we assume only one credential is used per authentication
+(the extension being direct). To the functionality in
+\appref{sapp:related-models-ac}, we now explicitly add the $OKeyGen$ function
+(equivalent to \OKeyGen, with a fixed \finsp function),
+which generates the opener key pair, extend $Verify$ to receive also a list $L$
+of revoked identifiers, and we add a function (and corresponding oracle) $id/\bot
+\gets RetrieveCredId(\osk,\utrans)$ that can extract the identifier of the
+credential used in a presentation transcript \utrans -- and which is essentially
+equivalent to \Open in \UAS. For simplicity, we do not include the equivalent to
+verifiable openings, but this would be straightforward.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.45\textwidth}
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\opk,\osk) \gets \OKeyGen(\parm) \\        
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
+        b^* \gets \adv^{\mathcal{O}_{anon}}(\parm,\ipk,\opk) \\
+        \pcreturn b^*
+      }        
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.55\textwidth}
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\opk,\osk) \gets \OKeyGen(\parm) \\        
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\
+        (D,L,\st) \gets
+        \adv^{\mathcal{O}_{forge}}(\parm,\ipk) \\
+        \langle \cdot,(b,\utrans)\rangle
+        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
+        \pcif b = 0: \pcreturn 0 \\
+        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
+        \land D \subseteq \ATTR[j]): \pcreturn 1 \\    
+        h \gets RetrieveCredHandle(\osk,\utrans) \\
+        \pcif h \in L \lor h = \bot: \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for revocable anonymous credentials with selective
+    disclosure based on \cite{fhs19}. 
+    $\mathcal{O}_{anon} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
+    ReqCredHandle,LoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace HU,CU,
+    Obtain,ObtIss,Issue,Show,ReqCredHandle \rbrace$. $ReqCredHandle$ is
+    equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
+    Also, \OWNR and \ATTR tables are essentially as in \secref{ssec:model-uas}.}
+  \label{fig:model-rac}  
+\end{figure}
+
+\subsubsection{\CUASRAC Construction.} %
+
+For our RAC construction, we define signature evaluation and opening functions
+as follows:
+
+\begin{align}
+  & \feval^{\dattrs,F,V,L}(\usk,\cred,\msg) \coloneqq
+    \lbrace
+    \pcif F(V,\attrs_1(\cred)) \in L: \pcreturn (0,0);
+    \pcelse \pcreturn (\dattrs(\cred),V)
+    \rbrace \nonumber \\
+  & \finsp^{F}((\yeval^0,\yeval^1),\usk,\cred,\msg) \coloneqq
+    \lbrace
+    \pcif \yeval^0 \neq 0: \pcreturn F(\yeval^1,\attrs_1(\cred));
+    \pcelse \pcreturn 0
+     \rbrace
+  \label{eq:funcs-rac}
+\end{align}
+
+Where, $\feval^{\dattrs,F,V,L}$ is parameterized with a one-way function $F$
+(e.g., a cryptographic hash), some constant subset \dattrs of attributes to be
+selectively disclosed by signers, a string identifying the verifier $V$ and a
+list $L$ of ``revocation handles'' by this verifier. If the credential used for
+signing has been revoked (i.e., if $F(V,id) \in L$), then \feval returns $0$, as
+an indication that the signature should be rejected by the verifier. Otherwise,
+it sets $\yeval^0 \gets \dattrs(\cred)$, and $\yeval^1 \gets V$ -- note that
+$\yeval^1$ will be encrypted with a single-use key pair.
+%
+On the other hand, $\finsp^{F}$ outputs $F(\yeval^1,\attrs_1(\cred))$, allowing
+valid signatures to be locally revocable by $V$ at a later stage, since
+$\yeval^1=V$.
 
 \begin{description}
-  \item[$\parm \gets \Setup(1^\secpar)$.] As in \CUASAC.
-\item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs a variant of \IKeyGen from
-  our \CUASGen construction where, instead of using a conventional signature
-  scheme, the issuer leverages its own anonymous credential of level $n$ to
-  create a signature in which it only reveals the credential level. That is,
-  $\sig_{is} \gets \CUASGen.Sign(\isk,\opk',\cred,\msg_{is},\feval^{0,n})$,
-  for some random $\msg_{is}$, and $\opk'$ from \parm, where $\feval^{0,n}$ is a
-  signing evaluation function that reveals no attribute other than the level
-  of the credential. Let $\opk_{n-1}$ be the issuer of the credential \cred
-  (i.e., an issuer with level $n-1$). The current issuer of level $n$ publishes
-  its public key as $(\opk_{n-1},\fissue^n,\sig_{is},\msg_{is})$.
-\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] As in \CUASAC.
+\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
+  \CUASGen.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
+  \CUASGen construction, setting $\fissue^1$ as issuance function.
+\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
+  \CUASGen construction, setting $\finsp^F$ as opening function.
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
+  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
-  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
-  As in \CUASAC.
-\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
-  \Verify(\opk,\dattrs) \rangle$.]
-  As in \CUASAC, but using $\feval^{\dattrs,n}$ as signature evaluation
-  function.
+  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
+  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
+  $\fissue^1$ as issuance function.
+\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
+  \Verify(\ipk,\dattrs) \rangle$.]
+  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
+  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
+  $\finsp^F$ as open function.
+\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
+  Outputs the revocation handle $h$ for the credential used in the interactive
+  presentation associated to \utrans. Note that $h$ is verifier-dependent.
 \end{description}
 
-\paragraph{Security of \CUASDAC.} %
-We need to define $level(\opk,n)$. This function first parses \parm
-as $(\parm',\opk')$, and \opk as $(\opk_{n-1},\fissue^n,\sig_{is},\msg_{is})$,
-and returns $\CUASGen.Verify(\opk_{n-1},\opk',\sig_{is},n,\msg_{is},
-\feval^{0,n})$.
-
-Given $level$, the security proofs are as for \CUASAC, with the addition that,
-in the unforgeability game, an adversary winning because of $level(\opk,n) = 0$
-can be directly used to break the sign unforgeability property of the underlying
-\CUASGen scheme.
-\fi
+\paragraph{Security of \CUASRAC.} %
+We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
+scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
+is anonymous and has unforgeable signing. Note that issuance unforgeability
+of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
+leveraging other credentials not any fixed custom issuance policy. Thus,
+signature unforgeability from \UAS is enough. Note that AC schemes modelled
+as in \cite{fhs19} do not have issuance anonymity, as the user public key
+is passed to the issuer.
+
+\begin{theorem}[Anonymity of \CUASRAC]
+  \label{thm:anon-cuasac}
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASAC is an
+  anonymous AC scheme according to \cite{fhs19}.
+\end{theorem}
+
+\begin{proof}
+  Given \adv~ against anonymity of \CUASRAC as defined in
+  \figref{fig:model-rac}, we build an adversary \advB against anonymity of
+  \CUASGen as defined in \defref{def:sign-anonymity-uas}.
+
+  First observe that, given a revocation handle $F(V,id)$ extracted from any
+  credential showing, it is not possible to extract $id$, as $F$ is one-way.
+
+  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
+  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
+  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, of \OPEN respectively.
+  Note that ``translating'' the inputs from the former into inputs for the
+  latter is trivial. Also, observe that $ReqCredHandle$ essentially refuses to
+  open transcripts from challenge users (signatures, in the non-interactive
+  equivalent), as $F(V,\attrs_1(\ccid_0) \neq F(V,\attrs_1(\ccid_1)$ with
+  overwhelming probability (see the $\tyinsp \neq \yinsp$) check in
+  \figref{fig:oracles2}. Obviously, if \adv~ wins in its anonymity game, then
+  so does \advB with the same probability.
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability of \CUASRAC]
+  If the base \CUASGen construction has sign unforgeability according to
+  \defref{def:sign-forge-uas}, and $F$ is one-way, then \CUASRAC is an
+  unforgeable RAC scheme.
+\end{theorem}
+
+\begin{proof}
+  Given \adv~ against unforgeability of \CUASRAC as defined in
+  \figref{fig:model-rac}, we build an adversary \advB against sign
+  unforgeability of \CUASGen as defined in \defref{def:sign-forge-uas}.
+
+  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
+  that \adv~ wins its game via the winning condition of line 6 in the RAC
+  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
+  that the probability of \adv~ winning its game via the winning condition at
+  line 9 is negligible, due to soundness of the NIZK scheme used for signing,
+  and the one-wayness of $F$ in $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.  
+  %
+  \qed
+\end{proof}
 

### 2022-06-18 prism-backend/research/gsac/app-model-related.tex
UAS => MPS.

@@
 
+Multimodal Private Signatures (or, rather, a close relative, see next) are
+directly implementable with a restriction of \UAS. Concretely, by restricting to
+a system with one issuer and one opener, one credential per user, one attribute
+per credential (the user secret key), $\fissue^1$ issuance functions, and
+\feval functions that only use the $\yeval^1$ output -- which we denote with
+$\feval^{\yeval^1}$.
+
+There are some differences, though. On the one hand, our signature anonymity
+property is somehow in the middle of MPS's privacy-1 and privacy-2 variants.
+Their privacy-1 variant is the traditional anonymity property of group
+signatures, in which the opener is honest and the adversary can call the opening
+oracle except for challenge signatures. In their privacy-2 variant, the opener
+is fully corrupt (i.e., \adv~ receives \osk), but the adversary can only be
+challenged with signatures that produce the same \yinsp value ($G_{j_b}(id_b)$
+in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
+(getting ther \osk), but the challenge signatures must have been generated using
+the key of an uncorrupted opener; still, \adv~can call the open oracle for
+challenge signatures, as long as they have the same \yinsp value. We believe
+that these differences are mostly of theoretical interest, though, and it does
+not seem hard to move from one to the other \todo{check}. In practice,
+what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$
+in MPS) that has too much granularity in their ranges, will lead to a barely
+private system. This is a known issue, for instance, in functional encryption
+\needcite.
+
+On the other hand, our issuance-related properties (issuance anonymity and
+issuance unforgeability) are unachievable by MPS. Issuance anonymity simply does
+not make sense in MPS, as it only supports one credential (without attributes)
+per user. Issuance unforgeability does not make sense either, since there are no
+configurable issuance policies in MPS -- instead, they have the fixed policy of
+``proving knowledge of a user secret key''. These extensions are not trivial
+from a theoretical point of view, and also have a big impact in the practicality
+of the resulting system. Also, MPS does not include verifiable openings. While
+this is easy to add, we consider it to be essential, given that the proposed
+generalization of opening allows the opener to output ``any value''. Hence, the
+need to ensure that the produced value is the legitimate one, seems to be more
+necessary than ever. Finally, our \feval function is a generalization of $F$ in
+MPS, as it allows two outputs: one will be returned in the clear along with the
+signature, and the other will be encrypted. Still both computations are proved
+correct. Making part of the output unencrypted allows implementing very useful
+variants such as anonymous credentials with selective disclosure -- as shown
+before.
+
+For the model of MPS schemes, we refer to the original paper \needcite.
+
+\subsection{\CUASMPS construction.} %
+As mentioned, any $(\fissue^1,\feval^{\yeval^1},\finsp^\ast)$-restriction of
+\CUASGen with only one issuer and opener, one credential per user, and one
+attribute per credential (the user secret key), implements an MPS scheme where
+$F=\feval^{\yeval^1}$ and $G=\finsp^\ast$. The restriction to one credential per
+user, and one attribute per credential, can be done as in
+\appref{sapp:related-models-gs}. Finally, note that, in MPS, $G$ is further
+parameterized with a value $j$, which essentially is the result of applying $F$
+to the message and signer identity, and is not leaked to the opener nor any
+other third party. The equivalent in \UAS is the $\yeval^1$ value, which is
+encrypted with a single-use key pair, and is an input of \yinsp.
+
+\paragraph{Security of \CUASMPS.} %
+As stated, we restrict to privacy-1 of MPS. Unforgeability-1 in MPS is
+equivalent to sign unforgeability in \UAS. Unforgeability-2 in MPS is
+equivalent to non-frameability in \UAS. Finally note that, in UAS, we do not
+explicitly model extractability, but rather make it an inherent requirement in
+the unforgeability and non-frameability definitions. Thus, our \CUASMPS
+construction also ensures MPS-extractability.
+
+\begin{theorem}[Privacy-1 of \CUASMPS]
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASMPS satisfies privacy-1
+  according to \needcite.
+\end{theorem}
+
+\begin{proof}
+  The proof is direct, by observing that the models are equivalent.
+
+  First, note that, in MPS the adversary is required to output a function $F$,
+  challenge message, and a pair of user secret keys and witnesses (in \UAS, the
+  witnesses are the credentials). This is precisely what \CHALb requires as
+  input in our \UAS modelling.
+
+  Next, in MPS, validity of the output of $F$ is checked. In MPS, this
+  translates to checking that $F$ does not ouptut $0$. In UAS, this is checked
+  in the \SIGN and \CHALb oracles, which abort if the output produced by \feval
+  does not belong in \rngfeval -- a well defined set of acceptable outputs by
+  the chosen \feval.
+
+  The MPS adversary is then allowed to make more oracle queries, and outputs a
+  response bit. Just as in \UAS. Thus, if \CUASMPS satisfies signature
+  anonymity, it is also an MPS scheme satisfying privacy-1.  
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Extractability of \CUASMPS]
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, then it is an extractable MPS scheme.
+\end{theorem}
+
+\begin{proof}
+  The proof is direct, as the conditions checked in the extractability
+  experiment in MPS are also checked in the signature unforgeability experiment
+  for \UAS.
+
+  Concretely, \Verify must accept the signature, and the ouptut of \feval and
+  \finsp, computed with the values extracted by \ExtractSign, must respectively
+  match those output by the adversary (for \feval), and computed honestly by the
+  signature unforgeability (for \finsp).  
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability-1 of \CUASMPS]
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
+  defined in \needcite.
+\end{theorem}
+
+\begin{proof}
+  For an MPS scheme to satisfy type-1 unforgeability, it has to be extractable.
+  This is directly satisfied by signature unforgeability in \UAS.
+  %
+  Next, the adversary wins in the unforgeability-1 MPS experiment if it manages
+  to produce a signature that has not been produced via a call to their \SIGN
+  oracle, nor it can be associated to an corrupt user. Indeed, if that happens,
+  then such adversary can be used to build an adversary winning the signature
+  unforgeability game against \CUASMPS, through winning condition at line 12 --
+  as \IdentifyUK does not return 1 for any known \uid. Thus, if \CUASMPS has
+  signature unforgeability, it also satisfies unforgeability-1 of MPS schemes.
+  %
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability-2 of \CUASMPS]
+  If the base \CUASGen construction has non-frameability according to
+  \defref{def:frame-uas}, then \CUASMPS satisfies unforgeability-2 as
+  defined in \needcite.
+\end{theorem}
+
+\begin{proof}
+  For an MPS scheme to have type-2 unforgeability, it has to be extractable.
+  This is directly satisfied by non-frameability in UAS (a similar reasoning
+  as for signature unforgeability and extractability applies here).
+  %
+  Next, in MPS, the adversary wins if the produced signature has not been
+  output by the \SIGN oracle, but Extract outputs the identifier of an honest
+  user. This is the same check done in lines 9 and 10 of the non-frameability
+  game in \UAS. Therefore, if \CUASMPS satisfies non-frameability as defined in
+  \defref{def:frame-uas}, it also satisfies type-2 unforgeability in MPS.
+  \qed
+\end{proof}
+
 %%% Local Variables:

### 2022-06-18 prism-backend/research/gsac/conclusion-paper.tex
Beginning refurbishment of the paper.

--- 2022-05-05 prism-backend/research/gsac/conclusion.tex
@@
 
-\comment{This section is just a placeholder for now...}
-
-Some notes on future work, to expand/refine/remove:
-
-\begin{itemize}
-\item Add support for open functions over sets of previously issued signatures.
-  This would cover existing schemes like \cite{dl21}, and possibly cool cases
-  such as training AI models on private data, in a federated manner, without
-  revealing the identity of the node running the model.
-\item Currently, in \UAS, we need to restrict challenge users to present
-  credentials issued by the same set of issuers. Technically, I guess that this
-  could be done by making the issuers' public keys part of the witness (although,
-  at what cost?). But then, how would verifiers be able to determine whether
-  they trust the issuers of the credentials used to compute the signature? It
-  would be as if an employer has to accept a University degree, without knowing
-  which university issued it.  
-\item Potentially very cool improvement in the modelling: maybe we can leverage
-  a decentralized append-only bulletin board (so, a blockchain) to reduce trust
-  on the issuers (except identity proofing, we could probably eliminate it...)
-  That would be quite innovative, as in GS literature, the issuer has so far
-  alwasy been thought to be necessarily honest. (Disclaimer: this was Ezequiel's
-  suggestion!)
-\item The current syntax of \UAS does not seem to support blind issuance. This
-  would however be trivial to achieve by adding a set of attributes to be
-  blindly issued in the \Obtain algorithm, and then requiring that they are
-  validated in \fissue. In the generic construction, this would be directly
-  supported too, as a block of messages to be signed as part of the block
-  commitment.
-\end{itemize}
+[1 page max]
 
@@
 %%% mode: latex
-%%% TeX-master: "uas"
+%%% TeX-master: "uas-paper"
 %%% End:

### 2022-06-18 prism-backend/research/gsac/introduction-paper.tex
Beginning refurbishment of the paper.

\section{Introduction}
\label{sec:introduction}

% [4 pages max]

%% Brief description of main precedents (simple words)
Privacy-preserving digital signature and authentication systems have been a
prolific field of study in the last few decades. Anonymous credentials
\cite{chau85} and group signatures \cite{ch91} are among the most relevant ones.
\todo{Other closely related schemes?}
While there are many variants, the high-level idea is common: after obtaining a
credential, users can authenticate anonymously and indistinguishably from other
users with similar credentials.

%% Usefulness of main precedents / motivation
The usefulness of these systems stems from the combination, within a single
primitive, of seemingly contradictory concepts: anonymity, authentication, and
utility.

Anonymous credentials focus on utility at authentication time. For
instance, encoding multiple attributes within a credential and allowing to
selectively disclose a subset of them (or arbitrary predicates) at
authentication time. The real world applications of such systems is direct,
e.g., to prove ``Over 18''-type of claims. Indeed, anonymous credentials are
making their own way to become a foundational block of ``anoncreds''%
\footnote{\url{https://hyperledger-indy.readthedocs.io/projects/sdk/en/latest/docs/design/002-anoncreds/README.html}. Last access, June 18th, 2022.},
the privacy-preserving cousin of W3C's Verifiable Credentials%
\footnote{\url{https://www.w3.org/TR/vc-data-model/}. Last access, June 18th,
  2022.}.

Group signatures enhance utility after authentication, by allowing partial
reidentification, like linking of signatures, or even full deanonymization.
While direct applications of group signatures seem hard to find, Direct
Anonymous Attestation (DAA) \cite{bcc04,bl07,cdl16b} has been deployed to
millions of computing devices into what's called TPM (Trusted Privacy Module)%
\footnote{\url{https://trustedcomputinggroup.org/resource/trusted-platform-module-tpm-summary/}. Last access, June 18th, 2022.}.
Indeed, DAA is a very close relative of group signatures, where the signer is
divided into two components (trusted and partially trusted), and treats signing
and verification as an interactive protocol.

%% Previous works summary w/ refs directly related contribs of UAS
%% (or, tech approaches of main precedents)

%% Main drawbacks of precedents

%% Our results; TLDR (simple words)

%% Our results; Tech nuances

%% Our techniques

%%% E.g., describe how we compatibilize both with AC sel disc., ring sigs, and MPS

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas-paper"
%%% End:

### 2022-06-18 prism-backend/research/gsac/uas-paper.tex
Beginning refurbishment of the paper.

--- 2022-05-11 prism-backend/research/gsac/uas.tex
@@
 \usepackage{mathtools}
+\usepackage{multirow}
+\usepackage{footnote}
+\makesavenoteenv{tabular}
+\makesavenoteenv{table}
+
+%% Set/unset to activate/deactivate author comments
+\def\authnotes{1}
+
+%%% Allows line-breaks in math formulae after commas
+\AtBeginDocument{%
+  \mathchardef\mathcomma\mathcode`\,
+  \mathcode`\,="8000 
+}
+{\catcode`,=\active
+  \gdef,{\mathcomma\discretionary{}{}{}}
+}
+
+%%%
 
@@
 \begin{abstract}
-  Much work has been done in the last 4 decades on privacy-preserving
-  identities and authentication that tries to incorporate some sort of utility
-  and accountability without losing (too much) privacy. Among the most relevant
-  efforts we can find group signatures (GS) and anonymous credentials (AC).
-  %
-  AC let users obtain attestations by trusted
-  issuers on certain attributes -- thus implicitly defining the concept of
-  identity as ``a set of attributes'' -- and allow credential owners to prove
-  claims on these attributes. While this has proven to be very
-  flexible, accountability in AC schemes is quite limited; frequently restricted
-  to blacklisting, if present at all.
-  %
-  On the other hand, GS have traditionally focused on plain authentication
-  without attributes, making instead more emphasis on the accountability side.
-  That is, not only allowing full
-  deanonymization, but also variants such as sequential linking, user-controlled
-  anonymity, or even full unlinkability.
-  %
-  Not surprisingly, GS and AC share very common syntax, models and frequently
-  also constructions.
-
-  We argue that, in the real world, both functionalities are essential. Taking
-  advantage of their similarities, we first propose a trivial combination,
-  \GSAC, showcasing the benefits even a simple combination brings. We give a
-  common syntax, security model, and generic construction for \GSAC.
-  %
-  Next, we generalize \GSAC into our Universal Anonymous Signatures (\UAS)
-  proposal by allowing arbitrary policies at issuance, signing and opening
-  time, among other improvements. While generalizations along these
-  lines have been explored independently in the GS and AC domains, to the best
-  of our knowledge, no single scheme offers such full flexibility.
-  We define a syntax, security model, and give a generic construction for a
-  scheme meeting these requirements. Furthermore, we show how our model for
-  \UAS is a generalization of previous well known schemes in the GS and AC
-  domains.
-  %
-  The techniques and building blocks we leverage are well known. The challenge
-  is, rather, on the definitional side. To further evidence the universality of
-  \UAS, we show how more restricted schemes can be built from vanilla \UAS.
+  \todo{XXX}
 \end{abstract}
 
-\tableofcontents
-
-\input{introduction.tex}
-\input{preliminaries.tex}
-\input{sec-gsac.tex}
-\input{sec-uas.tex}
-%\input{benchmarks.tex}
-\input{conclusion.tex}
+\input{introduction-paper.tex}
+\input{preliminaries-paper.tex}
+\input{formal-uas.tex}
+\input{relationships.tex}
+\input{conclusion-paper.tex}
 
 \bibliographystyle{splncs04}
-\bibliography{uas}
+\bibliography{uas-paper}
 
-\appendix
+% \appendix
 
-\input{app-building-blocks.tex}
-\input{app-gsac.tex}
+% \input{app-building-blocks.tex}
+% \input{app-gsac.tex}
+% \input{app-model-related.tex}
 

### 2022-06-20 prism-backend/research/gsac/introduction-paper.tex
Initial new intro (missing references).

@@
 %% Brief description of main precedents (simple words)
+\paragraph{Anonymous authentication and signatures.} %
 Privacy-preserving digital signature and authentication systems have been a
@@
 \cite{chau85} and group signatures \cite{ch91} are among the most relevant ones.
-\todo{Other closely related schemes?}
 While there are many variants, the high-level idea is common: after obtaining a
@@
 %% Usefulness of main precedents / motivation
-The usefulness of these systems stems from the combination, within a single
-primitive, of seemingly contradictory concepts: anonymity, authentication, and
-utility.
+Their usefulness stems from the combination, within a single primitive, of
+seemingly contradictory concepts: anonymity, authentication, and utility; where
+utility can appear in the shape of information revealed at signature/authentication
+time, or after (in the latter case, typically called accountability).
 
-Anonymous credentials focus on utility at authentication time. For
+\paragraph{Utility at authentication-time and after authentication-time.} %
+Anonymous credentials (AC) focus on utility at authentication time. For
 instance, encoding multiple attributes within a credential and allowing to
-selectively disclose a subset of them (or arbitrary predicates) at
-authentication time. The real world applications of such systems is direct,
-e.g., to prove ``Over 18''-type of claims. Indeed, anonymous credentials are
-making their own way to become a foundational block of ``anoncreds''%
+selectively disclose a subset of them, or even arbitrary predicates.
+The real world applications of such systems are direct,
+e.g., to prove ``Over 18''-type of claims. Indeed, the scientific research
+behind anonymous credentials is making its own way to become a foundational
+block of the technology some call ``anoncreds''%
 \footnote{\url{https://hyperledger-indy.readthedocs.io/projects/sdk/en/latest/docs/design/002-anoncreds/README.html}. Last access, June 18th, 2022.},
@@
 
-Group signatures enhance utility after authentication, by allowing partial
-reidentification, like linking of signatures, or even full deanonymization.
-While direct applications of group signatures seem hard to find, Direct
-Anonymous Attestation (DAA) \cite{bcc04,bl07,cdl16b} has been deployed to
+Group signatures (GS) enhance utility after authentication, by allowing partial
+reidentification like linking of signatures, or even full deanonymization.
+While actual applications of group signatures seem hard to find in the real
+world, Direct Anonymous Attestation (DAA) \cite{bcc04,bl07,cdl16b} has been deployed to
 millions of computing devices into what's called TPM (Trusted Privacy Module)%
@@
 Indeed, DAA is a very close relative of group signatures, where the signer is
-divided into two components (trusted and partially trusted), and treats signing
-and verification as an interactive protocol.
+divided into two components (trusted and partially trusted), and signing
+and verification are turned into an interactive protocol.
 
@@
 %% (or, tech approaches of main precedents)
+\paragraph{Evolution of AC and GS.} %
+As the previous shows, AC and GS systems have followed separate paths, although
+there are some exceptions. Functionality-wise, Attribute-Based Group Signatures
+(ABGS) introduce attributes into the credentials issued to group members, who
+can later use them to prove pre-fixed claims \cite{emo09,aa14}. Hidden-identity
+signatures also add attributes into the credentials, with the aim of preventing
+the opener (the trusted party who can deanonymize signers) from having to rely
+on the issuer in order to perform the opening \cite{ks07}. Some AC schemes have
+also tried to incorporate some sort of utility after authentication, like AC
+schemes with revocation \cite{cks10}, or with ``watchlists'' \needcite.
+
+This separation does not hold in the approaches to build them, though. The
+probably most fruitful way to design and instantiate AC systems
+is with CL-type signatures \cite{cl02}. But the fact that they support efficient
+zero-knowledge protocols for proving knowledge of a signature, makes them very
+suitable to build GS schemes -- even without exploiting the possibility to
+encode many attributes. Indeed, BBS+ signatures \cite{bbs04,cdl16b} have been
+used to design and instantiate GS schemes \cite{gl19,dl21}, as well as  PS16
+signatures \cite{ps16,cdl+20}. Both are CL-like signature schemes, and thus
+can be (and have been) used to design AC schemes \needcite.
+
+Also, both AC and GS branches have experienced praiseworthy efforts towards
+generalization. In the AC domain, malleable signatures are used as core building
+block in \cite{cklm14}, to allow building both conventional AC and Delegatable
+AC systems, depending on the transformation supported by the malleable
+signatures. In GS, very recently, BiAS \cite{lnpy21} and MPS \needcite
+flexibilize the tradeoff between anonymity and accountability.
 
 %% Main drawbacks of precedents
+\paragraph{Limitations of GS and AC.} %
+However, even the generalization efforts that have independently taken place in
+GS and AC, are quickly seen to have limited applicability in the real world.
+On the GS side, even though MPS achieves a nice balance on when a signature is
+deanonymizable and what information can be extracted from it, upon closer look,
+this information is somehow meaningless. To understand it, consider how does the
+generic construction work. Roughly, the signer encrypts the output of an
+arbitrary function of its ``identity'', and proves correctness of this
+computation. Yet, the concept of ``identity'' is not defined at all (it is a
+value within some undefined domain). Thus, it seems hard to associate any real
+world meaning to a function of something that is not clearly defined. In any
+case, proving membership to a group may be enough in some use cases, but
+definitely not as a general tool -- that is, GS  offer minimal utility at
+signing time.
+%
+On the other hand, ACs have a well defined concept of identity (the attributes
+encoded within a credential), yet their utility-after-authentication
+capabilities are 
+minimal -- something on which their GS counterpart has done decades of research.
+A somehow indirect proof of this is that the AC line of work does not even
+consider what security we can get in the presence of malicious issuers, which
+is precisely captured in the non-frameability properties of GS.
 
+\subsection{Our Contribution} 
 %% Our results; TLDR (simple words)
 
+\paragraph{General model for anonymous signatures.} %
+Acknowledging that the strengths of AC are the weaknesses of GS, and vice versa,
+we come up with a unified model. In a nutshell, we give a sytnax and model for
+anonymous signatures -- which can be turned into an interactive authentication
+system -- with attribute-enabled credentials, and generalized utility
+both at authentication/signature-time, and after. We also generalize the
+credential issuance process, subsuming an even larger set of previously
+known schemes. Given its generalization power, we refer to schemes meeting this
+model as Universal Anonymous Signatures.
+
+\paragraph{Generic construction, and connections with previous schemes.} %
+We give a generic construction based on well-known building blocks, and prove
+its security in the proposed model. To prove its universality, we show how
+restrictions of our generic construction directly imply the direct ancestors of
+UAS: group signatures and anonymous credentials. This includes not only their
+vanilla versions, but also relevant variants, such as MPS \needcite, (a modified
+version of) group signatures with message-dependent opening \cite{seh+12}, or
+anonymous credentials with revocation \cite{cks10}. We also show how minimal
+variations in our generic construction -- and leveraging the generalization of
+the issuance protocol -- allow us to build ring signatures \cite{rst06} or
+delegatable anonymous credentials \cite{bcc+09}. The most interesting part being
+that, while we prove implications with other previously known schemes, our
+generalization approach allows to merge features of them: e.g., one can easily
+model and instantiate GSs with with no revocation at all, ACs with full
+de-anonymization, or anything in between.
+
 %% Our results; Tech nuances
+\paragraph{Modelling challenges.} %
+Combining features of GS and AC into a unified model unavoidably brings
+complexity. For instance, we allow proving arbitrary claims over previously
+obtained credentials at issuance time, in order to inform the issuance
+decission. Thus, it is necessary to
+include unforgeability assurances already at that point -- something not
+considered in previous works. Also, in order to meet the general practice in AC,
+the model for \UAS includes multiple issuers, requiring careful bookkeeping to
+prevent trivial wins. Interestingly, this generalization also paves the way to
+include multiple openers, each with its own opening functionality -- also
+requiring careful bookkeeping. While powerful from a practical point of view,
+this introduces similar limitations privacy-wise as in functional encryption
+schemes \needcite -- e.g., privacy cannot be ensured if some chosen opening
+function produces different outputs for different users. However, on this
+occasion, it is the signer (perhaps jointly with the verifier) who decides the
+opening policy. Thus, the user is in full control of how deanonymizable its
+signatures will be. This flexibility on the opening values also leads to the
+need of using extraction-based techniques for the modelling, since we cannot
+expect that opening outputs the real identity of the signer. This comes as no
+surprise, though, as it was already observed in GS schemes with non-conventional
+opening \cite{dl21}, in DAA schemes \cite{cdl16,cdl16b} or in AC schemes that
+need to ensure correctness of information generated before authentication, like
+delegatable credentials \cite{bcc+09}, that prove validity of the delegation
+chain. In fact, simulation-extractability seems to be most useful here,
+something that was also observed in \cite{cl06} for producing signatures out of
+knowledge of witnesses for concrete NP statements.
+
+A crucial aspect to cater for all possible variants that we aim to subsume, is
+the incorporation of ``placeholders'' enabling customization. We introduce abstract
+functions whose computation needs to be proven correct by the user. Depending on
+the choice of these functions, one can instantiate a different related scheme,
+which is anyway secure according to our \UAS model. And
+besides them, we have to enable tweaking what utility information is (or can be)
+revealed at signing-time and after, in a robust manner -- a scheme that allows
+proving some claim at signing time, but a somehow contradictory one afterwards,
+is of little use. Hence, the statements proving correctness of computation by
+the signer need to include cross-references. This is also very useful, as one
+can modulate the information to be revealed after signing-time, with the
+information revealed at signing-time, allowing policies such as ``deanonymize
+only if 18+ years old''.
 
 %% Our techniques
+%%% E.g., describe how we compatibilize both with AC sel disc., ring sigs, and MPS
+\paragraph{Our approach.} %
+The high-level idea for our generic construction is simple. Credentials are
+signatures over blocks of messages (some signed in committed form), where each
+message can be a different attribute, and a user who wants to simultaneously
+leverage multiple credentials needs to bound all of them to the same key. We add
+three generic functions: \fissue, leveraged by users to
+prove claims over attributes in other credentials, in order to get a new one;
+\feval, proving correctness of the utility revealed at signing time; and \finsp,
+proving correctness of the utility extractable after signing. The latter is, in
+addition, fed and modulated with the output of \feval. The output of \feval is
+actually double: one part is shared in the clear along with the signature, and
+the other is encrypted, so that it can be used to tweak -- in a privacy-enhanced
+manner -- the behaviour of \finsp. The output of \finsp is encrypted with an
+opener's key. The pattern of the statements proven in each function is
+summarised in \figref{fig:proof-blocks-uas}.
 
-%%% E.g., describe how we compatibilize both with AC sel disc., ring sigs, and MPS
+\begin{figure}[ht!]
+  \centering
+  \input{figures/proof-blocks-uas.tex}
+  \caption{Summary of statements proved per operation in \UAS.
+    $K(x)$ means proving knowledge of $x$; $E(y)$ means proving correct
+    encryption of $y$; $D(z)$ means proving correct decryption of (an encryption
+    of) $z$. Solid boxes span configurable statements that control issuance;
+    dashed boxes span configurable statements that control utility at signing
+    time; dotted boxes span configurable statements that control utility after
+    signing time (accountability). Unboxed statements are fixed, and are thus
+    common to all \UAS restrictions.}
+  \label{fig:proof-blocks-uas}
+\end{figure}
+
+From this generic construction, \CUASGen, one can already build known (and more
+functionality-limited) schemes from what we call \emph{restrictions} of
+\CUASGen simply by giving concrete definitions of \fissue, \feval, and \finsp.
+Yet, the model remains the same, and we prove that if such restrictions of
+\CUASGen are secure in the \UAS model, they lead to secure constructions for
+the related primitives (GS variants, AC variants, etc). To define our generic
+construction, we also specify concrete NP relations for the underlying NIZK
+proofs for issuing, signing, and opening. Again with (unavoidable) minor variations
+of these NP relations -- concretely to the one used for signing -- we show how
+our \CUASGen variant can securely build ring signatures. That is, we prove that,
+by simply tweaking a function, and treating all users as issuers, group
+signatures an ring signatures are in essence the same thing.
+
+We emphasize that, while -- already before \UAS -- it may have not seemed hard
+to build either of these primitives from another, the core of our contribution
+is that, with \UAS, one just needs to give concrete definitions of three
+functions. Security of the final primitive then automatically follows from the
+fact that it is a secure instantiation of an \UAS scheme. We believe that this
+is a powerful notion, that may finally allow research lines (AC and GS) that
+have followed different paths to benefit from the findings of each other.
+\figref{fig:relations} graphically summarizes the relations we prove between
+\UAS and other schemes -- although, of course, many more are probably
+achievable.
+
+\begin{figure}[ht!]
+  \centering
+  \input{figures/relations.tex}
+  \caption{Summary of schemes that can be instantiated as restrictions of our
+    generic construction, \CUASGen, and proved secure under our \UAS model.
+    $\CUASGen^{\ast}$ denotes that minor changes to the basic construction
+    beyond the concrete $(\fissue,\feval,\finsp)$-restrictions are needed.
+    Between parenthesis we show the adopted reference model, and the section
+    offering full detail.
+  }
+  \label{fig:relations}
+\end{figure}
+
+Before proceeding with our \UAS syntax and model in \secref{xxx}, generic
+construction \CUASGen in \secref{xxx}, and relationships with other primitives
+in \secref{xxx}, we give some preliminaries in \secref{xxx}. We conclude in
+\secref{xxx}.
 

### 2022-06-21 prism-backend/research/gsac/formal-uas.tex
Beginning refurbishment of the paper.
Working on re-structure.

--- 2022-06-18 prism-backend/research/gsac/conclusion-paper.tex
@@
-\section{Conclusion}
-\label{sec:conclusion}
+\section{Formalizing \UAS}
+\label{sec:formal-uas}
 
-[1 page max]
+% [11 pages max]
+
+Next we formalize our notion of Universal Anonymous Signatures
+(\UAS). We define its syntax, model, and give a generic construction which
+we prove secure according to our model.
+
+The main contribution of this section is giving a simple syntax and model that
+still allow spanning a wide variety of related schemes. We combine aspects of GS
+and AC schemes -- and, therefore, rely heavily on previous works --,
+generalizing whenever possible. Like in ACs, there are multiple issuers, and
+each user can get one or more credentials from any of them. We incorporate
+openers, as in GSs, but there is no tight relationship between issuer
+and opener. Signing and verification are non-interactive processes like in GS
+schemes, but we show how to convert to an interactive one like in ACs. Finally,
+we incorporate functions that allow tweaking the behaviour at issuance,
+signature generation, and verification times; while signatures contain all the
+necessary information to check that all computations are performed correctly.
+
+\subsection{Syntax}
+\label{ssec:syntax-uas}
+
+An \UAS scheme is composed by the following algorithms:
+
+\begin{description}
+\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
+  returns a global system parameter variable \parm. We assume that \parm are
+  available to all the other functions, even if not explicitly listed in their
+  input parameters.
+\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given \parm, and the
+  function \fissue for checking that credential requestors meet the conditions
+  to be issued a credential, an issuer runs \IKeyGen to generate its issuing key
+  pair. 
+\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
+  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
+  The function \finsp defines the type of utility that will be extractable from
+  signatures.
+\item[$\UKeyGen(\parm) \rightarrow \usk$.] Given \parm, returns a user's secret
+  key.
+\item[$\langle
+  \Obtain(\usk,\ipk,\scred,\attrs),
+  \Issue(\isk,\sipk,\attrs))
+  \rangle \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.] %
+  This interactive protocol lets a user with key \usk running the \Obtain
+  process, receive a credential \cred from an issuer in the system, on attribute
+  set $\attrs$. The user leverages a set of credentials \scred, each with a
+  matching issuer key in \sipk (ommitted in \Obtain for readability). The user
+  outputs the produced credential \cred, while the issuer outputs the protocol
+  transcript \utrans for the produced credential.
+\item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
+  Upon receiving a user secret key \usk, opener public key \opk, a set of
+  credentials \scred, a message \msg and evaluation function \feval, returns
+  signature \sig, and a plaintext value \yeval. For readability, we assume
+  that, for each $\cred \in \scred$, we can get the corresponding issuer public
+  key \ipk; also, we use use \Sig to denote the tuple $(\sig,\yeval)$.
+\item[$\Verify(\opk, \sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
+  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
+  over message \msg, from a user with credentials issued by issuers with public
+  keys in \sipk, for evaluation function \feval and opener key \opk.
+\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
+  (\yinsp,\iproof)/\bot$.]
+  Executed by the opener with private key \osk. Receives a signature $\Sig=
+  (\sig,\yeval)$ over message \msg and evaluation function \feval,
+  generated using credentials issued by the issuers with public keys in \sipk.
+  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
+  correct opening \iproof.
+\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
+  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
+  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
+  over message \msg, and for evaluation function \feval. 
+\end{description}
+
+\paragraph{Issuance, evaluation, and opening functions.} %
+We emphasize that, both in our syntax definition, as well as on the following
+modelling, we make use of three different and abstract functions: \fissue,
+\feval and \finsp. The three functions are introduced to allow customized
+governance of the resulting instantiation of an \UAS scheme. They will be
+defined by different parties, but in all cases, they are run by users (maybe,
+on user-private data). Also, in all cases, the user has to prove correctness of
+their computation. We introduce them next, and give concrete examples for
+building specific well-known restrictions of \UAS in
+\secref{sec:transformations}.
+
+\begin{description}
+\item[$\fissue: (\usk,\scred,\attrs)
+  \rightarrow 0/1$.] Chosen by issuers within a family of functions \famfissue,
+  the issuance function defines what customized conditions an issuer requires
+  in order to issue credentials, when receiving a request from user with secret
+  key \usk, for attributes \attrs. \fissue may run checks on a (possibly empty)
+  set of additional credentials \scred, all bound to \usk, and possibly
+  issued by other issuers. \fissue returns $1$ to accept a request, $0$ to
+  reject it.
+\item[$\feval: (\usk,\scred,\msg)
+  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
+  family of functions \famfeval, can be set on a per-signature basis. They
+  receive the user secret key \usk, credentials \scred, and message to be signed
+  \msg. \feval can be used to control the information related to the signer that
+  will be revealed alongside a signature, and to modulate the behaviour of
+  \finsp. Its outputs two values, $\yeval^0$ and $\yeval^1$, where the former
+  is revealed in plaintext along with the signature, and $\yeval^1$ is encrypted
+  and used to modulate the behaviour of \finsp. Both values must belong in a
+  well defined set \rngfeval. For readability, we write
+  $\Yeval = (\yeval^0,\yeval^1)$.
+\item[$\finsp: (\Yeval,\usk,\scred,\msg) \rightarrow \yinsp$.]
+  Chosen by openers from a family of functions \famfinsp. The opening
+  functions define what utility value, derived from the user's secret key,
+  credentials, and signed message, should be extractable by an opener.
+  Note that \finsp also receives as input a value in the range of the \feval
+  function, $\rngfeval^2$. This allows opening logic to depend on the values
+  produced by the evaluation function. The output of \finsp is a value
+  \yinsp, which must belong in a well defined set \rngfinsp.
+\end{description}
+
+We emphasize that, even though \finsp and \feval seem redundant, they are not.
+To see this, observe that \finsp is defined by openers, and will be fixed in
+all signatures that can be opened by the opener who defined it. On the other
+hand, \feval can be defined by (e.g.) verifiers on a per-signature basis, even
+if the signatures use the same \finsp. Thus, \feval can be programmed to contain
+the conditions set by (e.g.) verifiers for signatures they receive; whereas
+\finsp can be programmed to extract specific utility values when needed, which
+may depend on the checks required by the verifier a signature was intended to.
+
+To summarize the previous, we depict in \figref{fig:uas-signature} the structure
+of an \UAS signature, including its main components and how they enable the
+previously stated generalization claims.
+
+\begin{figure}[ht!]
+  \centering
+  %\input{figures/uas-signature.tex}
+  \caption{Structure of an \UAS signature.}
+  \label{fig:uas-signature}
+\end{figure}
+
+\subsection{Model for \UAS Schemes}
+\label{ssec:model-uas}
+
+We now define our model for Universal Anonymous Signatures. Property-wise, we
+maintain anonymity, non-frameability, and include two extra unforgeability
+properties: unforgeability of issuance, which ensures that issuance policies
+are not circumvented; and unforgeability of signatures, guaranteeing that
+signature evaluation policies are respected, as well as soundness of opening.
+
+From a functional perspective, we require that each issuer and opener fix
+the issuance predicate \fissue and opener function \finsp when generating
+their public keys. On the other hand, signature evaluation functions \feval can
+be defined at signing time. This is in line with the usual practice in anonymous
+credentials, that let
+users prove arbitrary claims on their credentials, as long as they are met by
+the contained attributes. In practice, most probably, the signature evaluation
+policy to be
+employed in each signature will be defined by the verifier (or jointly between
+user and verifier), including the specification of which opener will be
+able to post-process signatures\footnote{See, for instance, the concept of
+  presentation exchanges, or requests, in the context of Verifiable Credentials:
+  \url{https://identity.foundation/presentation-exchange/} (last access, May
+  5th, 2022).}. Beyond these general policies, which already give much
+flexibility, the syntax for \UAS supports multiple issuers and openers, and
+lets users leverage multiple credentials to request issuance of new ones, and
+to produce signatures.
+
+\paragraph{Global Variables.} %
+The environment manages several global variables in the games posed to the
+adversary. Users are referred to with user identifiers, \uid; for credentials,
+we use \cid; for issuers, \iid; and for openers, \oid. In all cases, we use bold
+font to denote sets: e.g., \scid and \siid denote sets of credential and issuer
+identifiers. All tables/sets are initialized as empty tables/sets.
+
+\begin{description}
+\item[Sets for parties]:
+  \begin{description}
+  \item[\HU and \CU.] Keep track of honest (\HU) and corrupted (\CU) users;
+    i.e., they are sets of {\uid}s.
+  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers;
+    i.e., they are sets of {\iid}s.
+  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) openers;
+    i.e., they are sets of {\oid}s.
+  \end{description}
+\item[Tables for keys]:
+  \begin{description}
+  \item[\UK.] \UK maintains user keys $\usk$. To refer to the key of a specific
+    user, we use $\UK[\uid]$. 
+  \item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
+    $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
+    use \PUBIK to refer to the public component, which also includes the \fissue
+    function; and \PRVIK refers to the private component of the key pair.
+  \item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
+    of \fissue, \OK includes the \finsp function.
+  \end{description}
+\item[Tables for credentials-related data]:
+  \begin{description}
+  \item[\CRED.] Stores information related to credentials obtained by users in
+    the system. Thus, it is indexable by \cid. More specifically, it stores
+    tuples of the form $(\uid,\cred,\iid,\attrs,\scid)$, where \uid is the
+    identity of the owner of the credential, \cred (when available) is the
+    credential itself, \iid is the identifier of the credential issuer, \attrs
+    are the attributes included in \cred, and \scid are the identifiers of the
+    credentials (if any) that \uid used to request \cred. For notational
+    convenience, we may use $\CRED[\scid]$ to refer to $\CRED[\cid]$ for all
+    $\cid \in \scid$. Also, when clear from context, we sometimes use
+    $\CRED[\cid]$ (resp. $\CRED[\scid]$ to mean \cred (resp. \scred) in
+    $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,\cdot)$ (resp. $\CRED[\scid]$).
+  \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
+    ``\uid such that $\CRED[\cid] = (\uid, \cdot, \cdot, \cdot, \cdot)$''.
+  \item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
+    ``\attrs such that $\CRED[\cid] = (\cdot, \cdot, \cdot, \attrs, \cdot)$''.
+  \item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
+    ``\iid such that $\CRED[\cid] = (\cdot, \iid, \cdot, \cdot, \cdot)$''.
+  \end{description}
+\item[Tables for signatures]:
+  \begin{description}
+  \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
+    of honest users. Entries of this table are $(\oid,\scid,\sig,\Yeval,\msg,
+    \feval)$, where \oid is the opener chosen for the signature, \scid is the
+    set of credentials used for signing, \feval is the signing evaluation
+    function, and \sig and \msg are the produced signature and signed message.
+  \item[\CSIG.] Maintains challenge signatures output to the adversary; i.e.,
+    the table is indexable by challenge signatures \csig.
+    Each entry contains also $\cuid_b$ and $\scid_b$ the challenge user and
+    credential identifiers set used to produce \csig; as well as the
+    corresponding challenge user and credential set indexed by the complementary
+    $1-b$; the signed message \msg and signing evaluation function \feval, the
+    result of \feval, \yeval, and the opener identifier \oid.
+  \end{description}
+\end{description}
+
+\paragraph{Oracles.} %
+In the game-based definitions of our \UAS model, we leverage the following
+oracles, which are formally defined in \figref{fig:oracles1} and
+\figref{fig:oracles2}.
+
+\begin{description}
+\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
+  the associated issuance function.
+\item[\OGEN.] Adds a new opener to the game, generating its key pair and
+  setting the associated evaluation and inspection functions.
+\item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
+  key to the adversary.
+\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
+  key to the adversary.  
+\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
+  the user's key pair.
+\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
+  user already exists and is honest, corrupts it, leaking its key and
+  credentials.
+\item[\RREG.] Reads the given transcript table entry.
+\item[\WREG.] Sets a transcript table entry to the given value.
+\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
+  the game, on behalf of an honest user.
+\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
+  in games that support it, by letting it interact with honest users who want to
+  receive credentials.
+\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
+  requesting an honest issuer to produce credentials for them.
+\item[\SIGN.] Lets the adversary get signatures from credentials belonging
+  to honest users.
+\item[\OPEN.] Given an honestly produced signature, outputs the result of the
+  opening function, along with a correctness proof.
+\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
+  singing evaluation function and a message, returns a signature produced by one
+  of these two user and credential sets, defined by the bit $b$, which is
+  established in the anonymity game.
+\end{description}
+
+{%\setlength\intextsep{\sep}
+  \begin{figure*}[htp!]
+    \centering
+    \scalebox{0.9}{
+
+      \begin{minipage}[t]{0.55\textwidth}
+
+        \procedure{$\IGEN(\iid,\fissue)$}{%
+          \pcif \iid \in \HI \lor \iid \in \CI: \pcreturn \bot \\
+          \pcif \fissue \notin \famfissue: \pcreturn \bot \\
+          (\ipk,\isk) \gets \IKeyGen(\parm) \\
+          \IK[\iid] \gets ((\ipk,\fissue),\isk) \\
+          \HI \gets \HI \cup \lbrace \iid \rbrace \\
+          \pcreturn \ipk \\
+        }
+
+        \procedure{$\ICORR(\iid)$}{%
+          \pcif \iid \in \CI \lor \iid \notin \HI: \pcreturn \bot \\
+          \HI \gets \HI \setminus \lbrace \iid \rbrace \\
+          \CI \gets \CI \cup \lbrace \iid \rbrace \\
+          \pcreturn \isk \\
+        }
+
+        \procedure{$\HUGEN(\uid)$}{%
+          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
+          \usk \gets \UKeyGen(\parm) \\
+          \UK[\uid] \gets \usk;
+          \HU \gets \HU \cup \lbrace  \uid \rbrace \\
+          \pcreturn \top \\
+        }
+
+        \procedure{$\RREG(i)$}{%
+          \pcreturn \trans[i]
+        }
+
+      \end{minipage}
+    }
+    \scalebox{0.9}{
+
+      \begin{minipage}[t]{.5\textwidth}
+
+        \procedure{$\OGEN(\oid,\finsp)$}{%
+          \pcif \oid \in \HO \lor \oid \in \CO: \pcreturn \bot \\
+          \pcif \finsp \notin \famfinsp: \pcreturn \bot \\
+          (\opk,\osk) \gets \OKeyGen(\parm) \\
+          \OK[\oid] \gets ((\opk,\finsp),\osk) \\
+          \HO \gets \HO \cup \lbrace \oid \rbrace \\
+          \pcreturn \opk \\
+        }
+
+        \procedure{$\OCORR(\oid)$}{%
+          \pcif \oid \in \CO \lor \oid \notin \HO: \pcreturn \bot \\
+          \pcif \exists (\oid,\cdot,\cdot,\cdot,\cdot,
+          \cdot,\cdot,\cdot,\cdot) \in \CSIG: \pcreturn \bot \\
+          \HO \gets \HO \setminus \lbrace \oid \rbrace \\
+          \CO \gets \CO \cup \lbrace \oid \rbrace \\
+          \pcreturn \osk \\
+        }
+
+        \procedure{$\CUGEN(\uid)$}{%          
+          \pcif \uid \in \CU: \pcreturn \bot \\
+          \CU \gets \CU \cup \lbrace \uid \rbrace \\          
+          \pcif \uid \in \HU: \\
+          \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
+          \pcind \pcreturn (\UK[\uid],\CRED[\uid]) \\
+          \pcelse: \UK[\uid] = \bot \\          
+          \pcreturn \top \\
+        }
+
+        \procedure{$\WREG(i,\rho)$}{%
+          \trans[i] \gets \rho
+        }
+
+      \end{minipage}
+
+    }
+
+    \caption{Detailed oracles available in our model (1/2). Oracles for
+      generating key material for users, issuers, and openers.}
+    \label{fig:oracles1}
+  \end{figure*}
+}
+
+{%\setlength\intextsep{\sep}
+  \begin{figure*}[htp!]
+    \centering
+    \scalebox{0.9}{
+
+      \begin{minipage}[t]{0.55\textwidth}
+
+        \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\scid)$}{%
+          \pcif \uid \notin \HU: \pcreturn \bot \\
+          \pcif \iid \notin \HI: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
+          \langle \cred, \utrans \rangle \gets
+          \langle \Obtain(\UK[\uid],\CRED[\scid],\attrs), \\
+          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\scid],\attrs)
+          \rangle \\
+          \trans[\cid] \gets \utrans \\
+          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
+          \pcreturn \top \\
+        }
+
+        \procedure{$\ISSUE(\cid,\uid,\iid,\attrs,\siid)$}{%
+          \pcif \uid \notin \CU: \pcreturn \bot \\          
+          \pcif \iid \notin \HI: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
+          \langle \cdot, \utrans \rangle \gets
+          \langle \adv, 
+          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
+          \trans[\cid] \gets \utrans \\
+          \CRED[\cid] \gets (\uid, \cdot, \iid, \attrs, \cdot, \siid) \\
+          \pcreturn \top \\          
+        }
+
+        \procedure{$\SIGN(\oid,\uid,\scid,\msg,\feval)$}{%
+          \pcif \uid \notin \HU \cup \lbrace \bot \rbrace: \pcreturn \bot \\
+          \pcif \uid = \bot \land \exists \cid' \in \scid~\suchthat~
+          \cid' \notin \CCRED: \\
+          \pcind \pcreturn \bot \\
+          \pcif \uid = \bot: \uid \gets \OWNR[\scid] \\
+          \pcif \feval \notin \famfeval: \pcreturn \bot \\
+          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,\feval) \\
+          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\scid],\msg) \\
+          \pcif \Yeval \notin \rngfeval: \pcreturn \bot \\
+          \SIG[\uid] \gets \SIG[\uid] \cup
+          \lbrace (\oid,\scid,\Sig,\Yeval,\msg,\feval) \rbrace \\
+          \pcreturn \Sig \\
+        }
+
+        \procedure{$\OPEN(\oid,\Sig,\msg)$}{%
+          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\Yeval,\msg,\feval)
+          \in \SIG[\uid] \\
+          (\yinsp,\iproof) \gets
+          \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
+          \pcif \CSIG[\Sig] \neq \bot: \\
+          \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,
+            \Yeval,\msg,\feval$} \\          
+          \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b},
+          \TYeval) \\
+          \pcind (\tyinsp,\tiproof) \gets
+          \Open(\PRVOK[\oid],\IK[\siid],\\
+          \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
+          \pcind \pcif \tyinsp \neq \yinsp: \pcreturn \bot \\
+          \pcreturn (\yinsp,\iproof)
+        }
+
+      \end{minipage}
+    }
+    \scalebox{0.9}{
+
+      \begin{minipage}[t]{.5\textwidth}
+
+        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
+          \pcif \uid \notin \HU: \pcreturn \bot \\
+          \pcif \iid \notin \CI: \pcreturn \bot \\
+          \pcif \exists \cid' \in \scid~\suchthat~\cid' \in \CCRED: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
+          \langle \cred, \cdot \rangle \gets
+          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\CRED[\scid],\attrs),\adv \rangle \\
+          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
+          \pcreturn \top \\
+        }
+
+        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1})$}{%
+          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
+          \pcif \iid \notin \CI: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
+          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
+          \in \CRED: \\
+          \pcind \pcreturn \bot \\
+          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
+          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
+          \pcif \fissue(\UK[\cuid_0],\cscid_0,\attrs) \neq
+          \fissue(\UK[\cuid_1],\cscid_1,\attrs) \\
+          \langle \cred, \cdot \rangle \gets
+          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\CRED[\cscid_b],\attrs),\adv \rangle \\
+          \CCRED[\cid] \gets (\cuid_b, \cred, \iid, \attrs, \cscid_b, \siid) \\
+          \pcreturn \top \\
+        }
+
+        \procedure{$\CHALb(\oid,\cuid_{0,1},\cscid_{0,1},\msg,\feval)$}{%
+          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
+          \pcif \oid \in \CO: \pcreturn \bot \\
+          \pcif \feval \notin \famfeval: \pcreturn \bot \\          
+          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\CRED[\cscid_0],
+          \msg) \\
+          \TYeval = (\tyeval^0,\tyeval^1) \gets
+          \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg) \\
+          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
+          \pcif \Yeval \notin \rngfeval \lor \TYeval \notin \rngfeval:
+          \pcreturn \bot \\
+          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
+          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
+          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
+          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
+          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
+          \CSIG[\cSig_b] \gets 
+          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
+          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
+          \pcreturn \cSig_b
+        }
+
+      \end{minipage}
+
+    }
+
+    \caption{Detailed oracles available in our model (2/2). Oracles for
+      obtaining credentials, signatures, and processing them.}
+    \label{fig:oracles2}
+  \end{figure*}
+}
+
+\paragraph{Helper functions \ExtractIssue, \ExtractSign, \IdentifyCred, and
+  \IdentifyUK.} In our modelling, we assume the existence of fhese four
+functions. They are not
+functions available in the actual scheme, but rather to the challenger in the
+experiments we use to formalize security of \UAS schemes. Similar techniques
+have been used before to prove security in privacy-preserving schemes with some
+sort of accountability, but that do not offer conventional opening as vanilla
+group signatures. For instance, see related works on DAA \cite{bfg+11,cdl16} and
+group signature variants \cite{dl21,fgl21,gl19,lnpy21}. More concretely, these
+functions are as follows:
+
+\begin{description}
+\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
+  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
+  credentials (if any) and their attributes that were involved
+  in the request. It clearly needs an honest issuer as, otherwise, the
+  transcripts won't be available. Consequently, we only use it to define the
+  properties that require an honest issuer.
+\item[$\ExtractSign(\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
+  \scred,\attrs_{\scred},\yeval^1,\yinsp)$.] Receives a signature \Sig,
+  as well as the opener identifier \oid, and the identifiers of all issuers of
+  the credentials used to produce the signature over \msg, and for \feval. It
+  outputs the user secret key and credentials (with their attributes) used to
+  generate the signature, and the value returned by the opening fuction.
+\item[$\IdentifyCred(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
+  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
+  Otherwise, it returns $0$. In order to be meaningful, this requires that,
+  for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
+  \IdentifyCred return $1$.
+\item[$\IdentifyUK(\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret key.
+  This is trivial for honest users, for which there must be a one-to-one
+  relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
+  to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
+  to \uid, extract the used secret key, and check if there is a match. Note that
+  this does not guarantee that there will be only one \usk per corrupt \uid,
+  though. Also, when used for corrupt users, this can only be used when the
+  issuer is honest, as transcripts are needed. 
+\end{description}
+
+Note that, for all the helper functions, in the case of credentials, transcripts,
+and signatures by honest users, it is enough to have access to the corresponding
+state information (described below) maintained by the challenger in our
+experiments. For credentials and join transcripts of corrupt users, or
+dishonestly produced signatures, we do need to perform actual extraction.
+Certainly, the challenger
+needs special knowledge/power such as decryption trapdoors, the ability to
+rewind the game, or program random oracles. The approach needs thus to depend on
+the concrete construction. \jdv{Although, for the case of \ExtractIssue and
+  \IdentifyUK, online extractability (or alternative requirements, such as
+  non-parallel or logarithmic number of joins) is necessary.}
+
+\paragraph{Correctness.} %
+Correctness of \UAS schemes is formalized through the experiment in
+\figref{fig:exp-uas-corr}. It states that a signature over any arbitrary message
+and valid function \feval, produced honestly leveraging credential set \scid,
+owned by user \uid, is accepted by \Verify. Moreover, all the credentials in
+\scid meet the conditions set by the corresponding \fissue defined by the issuer
+which issued each credential. Similarly, the output \yeval of \feval matches the
+value produced by \Sign alongside with \sig; and the value produced by \Open
+is accepted by \Judge, and matches the output of applying \finsp on \yeval, the
+credentials, user key, and message.
+
+\begin{definition}{(Correctness of \UAS)}
+  \label{def:correctness-uas}
+  An \UAS scheme is correct if, for any p.p.t. adversary $\adv$,
+  $\ExpCorrect(1^\secpar)$ outputs 1 with negligible probability.
+\end{definition}
+
+\begin{figure}[htp!]
+  \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
+    \parm \gets \Setup(1^\secpar) \\
+    (\uid,\oid,\scid,\msg,\feval)
+    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
+    \pcif \feval \notin \famfeval: \pcreturn 0 \\
+    \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
+    (\Sig = (\sig,\yeval)) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,
+    \feval) \\
+    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
+    \pcfor \cid \in \scid \pcdo: \\
+    \pcind \textrm{Let}~\scred^{\cid}~\textrm{be the credentials used to obtain}
+    ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,\fissue^{\cid}),\cdot)\\
+    \pcind \pcif \fissue^{\cid}(\UK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
+    (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\scid],\msg) \\
+    \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
+    (\yinsp,\iproof) \gets \Open(\PRVOK[\gid],\PUBIK[\scid],\Sig,\msg,\feval) \\
+    \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
+    = 0~\lor \\
+    \pcind \yinsp \neq \finsp^\gid((\yeval,\yeval^1),\UK[\uid],\CRED[\scid],\msg)): \\
+    \pcind \pcreturn 1 \\
+    \pcreturn 0
+  }  
+  \caption{Correctness experiment for \UAS schemes.}
+  \label{fig:exp-uas-corr}
+\end{figure}
+
+\subsubsection{Security Properties}
+\label{sssec:security}
+
+\paragraph{Anonymity.} %
+\iffalse
+Informally, anonymity must capture two requirements: (1) interactive credential
+issuance protocols do not leak any information about the user requesting them;
+and (2) signatures do not leak any information about the signer. In both cases,
+any leakage must be limited to whatever the user decides to reveal, for
+instance, through arbitrary predicates on the attributes of the credentials used
+for issuance and signing. We follow a simulation-based approach to capture this.
+Basically, the adversary is challenged to distinguish between real and ideal
+executions. In both worlds, the adversary can generate and corrupt honest users,
+issuers, and openers. Then, in the real world, the adversary has access to
+oracles that allow requesting credentials on behalf of honest users, create
+signatures by honest users, and open signatures by honest users. In the ideal
+world, these three oracles are replaced by simulated counterparts, which produce
+outputs independent of the users' secrets. This formulation is given in
+\figref{fig:exp-uas-simanon}, where $\Osimanon = (\lbrace\HU,\CU\rbrace\GEN,
+\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG)$.
+
+\begin{figure}[htp!]
+
+  \centering
+  \procedure[linenumbering]{$\ExpSimAnonb(1^\secpar)$}{%
+    \pcif b = 0: \\
+    \pcind \parm \gets \Setup(1^\secpar) \\    
+    \pcind b^* \gets \adv^{\Osimanon,\OBTAIN,\SIGN,\OPEN}(\parm) \\
+    \pcelse: \\
+    \pcind (\parm,\NIZKtrap) \gets \SIMSETUP(1^\secpar) \\
+    \pcind b^* \gets \adv^{\Osimanon,\SIMOBTAIN,\SIMSIGN,\SIMOPEN}(\parm) \\    
+    \pcreturn b^*
+  }
+
+  \caption{Simulation-based anonymity experiment for \UAS schemes.}
+  \label{fig:exp-uas-anonb}
+\end{figure}
+
+\begin{definition}{(Anonymity of \UAS)}
+  \label{def:sign-anonymity-uas}  
+  We define the advantage \AdvSimAnon of $\adv$ against \ExpSimAnonb as
+  $\AdvSimAnon=|\Pr\lbrack\ExpSimAnono(1^\secpar)=1\rbrack-
+  \Pr\lbrack\ExpSimAnonz(1^\secpar)=1\rbrack|$.
+  %
+  An \UAS scheme satisfies simulatable anonymity if there exists simulators
+  \SIMSETUP, \SIMOBTAIN, \SIMSIGN and \SIMOPEN such that, for any p.p.t.
+  adversary $\adv$, \AdvSimAnon is a negligible function of $1^\secpar$.
+\end{definition}
+\fi
+We need to ensure that no information is leaked about users requesting a
+credential, nor about signers. The latter is typically captured in group
+signatures by letting the adversary request challenge signatures, produced
+by a challenge user picked randomly out of two users chosen by the adversary,
+and requiring the adversary to guess which one was used. In what is frequently
+called CCA-like anonymity, the adversary is given access to the opener,
+except for challenge signatures. We follow this approach in what we call
+signature anonymity. We need however to restrict that challenge signatures
+produce the same \yeval value, to prevent trivail wins by the adversary. On
+the other hand, since it is possible that both challenge signatures produce
+the same \yinsp value, we can model a stronger CCA-like variant, in which the
+adversary is allowed to open challenge signatures for the cases in which the
+\yinsp value is the same for both challenge users.
+
+In addition to signature anonymity, we need to take into account that, as in
+some anonymous credential schemes, a single user may have multiple credentials.
+Moreover, these credentials can be obtained from different issuers, or from the
+same issuer but for different attributes. Thus, it seems logical to require that
+the adversary cannot determine whether any two credential requests originate
+from the same signer, or not. To model this, we define the issuance anonymity
+game. Intuitively, we let the adversary obtain challenge credentials on behalf
+of two honest challenge users, but without knowing to which concrete challenge
+user we actually issue the produced credentials. To prevent trivial wins, we
+have to make additional restrictions. Namely, the two sets of challenge user and
+supporting credentials for requesting the challenge credential need to satisfy
+the same issuance policy, and these supporting credentials cannot include
+credentials that have been obtained via the conventional \OBTAIN oracle.
+The adversary is then allowed to interact with all the other oracles (except the
+one producing challenge signatures, which is not needed), with the only further
+constraint that any call to the \SIGN oracle that leverages challenge
+credentials cannot specify the user identifier (the oracle ``knows'' which one
+out of the two challenge users it needs to use). As usual, after interacting in
+an arbitrary way with the oracles, the adversary needs to guess the bit $b$
+defining which challenge user was employed to produce the challenge credentials.
+
+The formal specification of the anonymity games is given in
+\figref{fig:exp-uas-anonb}, where
+$\OIssAnon \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,
+\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\OBTCHALb)$, and $\OSigAnon
+\gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace
+\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$.
+
+\begin{figure*}[htp!]
+  \centering
+  \scalebox{0.9}{
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure[linenumbering]{$\ExpIssAnonb(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        b^* \gets \adv^{\OIssAnon} (\status,\parm) \\
+        \pcreturn b^*
+      }
+    \end{minipage}
+
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure[linenumbering]{$\ExpSigAnonb(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        b^* \gets \adv^{\OSigAnon} (\status,\parm) \\
+        \pcreturn b^*
+      }
+    \end{minipage}
+  }
+  \caption{Issuance and signature anonymity experiments for \UAS schemes.}
+  \label{fig:exp-uas-anonb}
+\end{figure*}
+
+\begin{definition}{(Issuance anonymity in \UAS)}
+  \label{def:issue-anonymity-uas}  
+  We define the advantage \AdvIssAnon of $\adv$ against \ExpIssAnonb as
+  $\AdvIssAnon=|\Pr\lbrack\ExpIssAnono(1^\secpar)=1\rbrack-
+  \Pr\lbrack\ExpIssAnonz(1^\secpar)=1\rbrack|$.
+  %
+  An \UAS scheme satisfies issuance anonymity if, for any p.p.t. adversary
+  $\adv$, \AdvIssAnon is a negligible function of $1^\secpar$.
+\end{definition}
+
+\begin{definition}{(Signature anonymity in \UAS)}
+  \label{def:sign-anonymity-uas}  
+  We define the advantage \AdvSigAnon of $\adv$ against \ExpSigAnonb as
+  $\AdvSigAnon=|\Pr\lbrack\ExpSigAnono(1^\secpar)=1\rbrack-
+  \Pr\lbrack\ExpSigAnonz(1^\secpar)=1\rbrack|$.
+  %
+  An \UAS scheme satisfies signature anonymity if, for any p.p.t. adversary
+  $\adv$, \AdvSigAnon is a negligible function of $1^\secpar$.
+\end{definition}
+
+\paragraph{Discussion on the generality of anonymity in \UAS schemes.} %
+% This notion of anonymity is more general than that of group signatures in the
+% sense that calls to the \OPEN oracle reveal an arbitrary function of the
+% identity of the user -- which can certainly be the member index itself, as it
+% is frequent in group signatures, or any other function computable from the
+% user key, its credentials, and signed message. Moreover, note that
+% our notion is even stronger than the conventional ``CCA-like'' anonymity notion
+% that gives the adversary access to the open oracle, only restricting it when
+% trying to open challenge signature. Precisely the introduction of generic
+% opening functions allows us to let the adversary open challenge signatures
+% $\csig_b$ as long as the counterpart $\csig_{1-b}$
+% makes \Open produce the same \y value as output. This is certainly not
+% possible when using conventional opening, since it directly outputs the identity
+% of the signer -- which cannot be the same for different challenge users.
+
+% Note that we could actually remove the requirement that the evaluation function
+% has to produce the same output on both challenge user-credentials pairs.
+% However, by doing so, we would force all constructions to maintain private the
+% output of \feval. We opt not to require that, though, as it directly allows
+% our model to cover interesting use cases -- such as restricting to selective
+% disclosure, or privacy-preserving variants of functional signatures \jdv{check
+%   the latter}, although we show how to do that in \secref{sec:transformations}.
+
+\paragraph{Unforgeability.} In anonymous credentials, unforgeability requires
+that no adversary can succeed in a credential presentation for attributes that
+are not contained in a legitimately issued credential (set) it controls. Note
+that, for this, assuming honest issuers is essential as, otherwise, the
+adversary can get credentials on any attribute set it wants.
+%
+The somehow equivalent property in group signatures, inasmuch it also requires
+honest issuers, is traceability. It captures the security of the
+open-related functionality (e.g., \Open and \Judge) over signatures
+that produced by potentially malicious signers, in the presence of an honest
+issuer. In a nutshell, it ensures that every signature accepted by
+the verification algorithm must have been created by a user who joined the
+group, and that the result of \Open (and thus, \Judge) over such a valid
+signature is consistent with its signer. With conventional opening, this is
+essentially checked by requesting the adversary to produce a signature,
+obtaining -- via open -- the ``identifier'' of the user who produced the
+signature. Schemes
+that do not have conventional opening resort to more subtle techniques, like
+matching keys extracted during join transcripts, with keys used for signing
+(see, e.g., \cite{dl21}). Thus, even though for more subtle reasons (the need
+for reliable bookkeeping during joins) than for anonymous credentials, honest
+issuers are required for traceability of group signatures too.
+
+In our \UAS scheme we allow users prove claims over the attributes they
+own -- attested via obtained credentials -- through the \feval function.
+Roughly, we capture this as in unforgeability requirement of anonymous
+credentials. Namely, we check that the \yeval value returned by \Sign along with
+the signature, matches the expected one from the specified \feval function.
+On the other hand, the opening capabilities of \UAS schemes also call for a
+traceability-like property. However, note that, as opposed to group signatures,
+$\langle \Obtain,\Issue \rangle$ protocols are over credentials rather than
+users -- although, ultimately, credentials must be owned by some user.
+Furthermore, since \Open
+does not return the actual identity of the signer, but a function \finsp of it
+(and other arguments), we need to make sure that the output of \Open
+matches the output of \finsp. As in group signatures with non-conventional open,
+we resort to extraction-based techniques. All this is captured via \ExpForgeSign
+in \figref{fig:exp-uas-unfor-issue}. Therein, the adversary is challenged to
+produce a signature $(\sig,\yeval)$ over message \msg and for evaluation
+function \feval; as well as the identifiers for the opener (\oid) and
+credential issuers (\siid) used to compute the signature. As in traditional
+group signatures, the adversary wins if the signature is accepted by \Verify,
+yet \Open or \Judge fail. Then, the game extracts the user key and
+credentials used to produce the signature. From it, the game checks if the
+output of \feval matches the \yeval value produced by the adversary -- this
+mimics the behaviour of unforgeability in anonymous credentials. Finally, the
+game also checks that the output of \Open (even if accepted by \Judge)
+matches the output of \finsp. If there is any mismatch in the last two checks,
+or some of the credentials used to produce the signature do not correspond to
+the secret key that was allegedly used to request them, the adversary wins the
+game.
+
+Our \UAS scheme includes yet another generalisation that requires unforgeability-like
+security, though. Concretely, the issuance function \fissue. We need to make
+sure that no credential is issued unless its corresponding
+request meets the defined issuance policy. From the point of view of group
+signatures, this may seem redundant. After all, if all valid signatures produce
+consistent evaluation and opening results, given the employed user key,
+credentials, and signed message, the notion of traceability seems to be
+satisfied. However, from the point of view of anonymous credentials, an attacker
+being able to obtain a credential, even when it does not meet the required
+conditions to have it issued, is clearly problematic: it would allow to prove
+claims over attributes it does not really ``own'' (even if the output of \Sign
+and \Open are consistent with the values returned by \feval and \finsp, and
+the credential was obtained via an $\langle \Obtain,\Issue \rangle$ run). To
+capture this, we define the \ExpForgeIssue experiment. In the experiment, the
+adversary is challenged to produce a credential identifier that must be
+associated to an existing $\langle \Obtain,\Issue \rangle$ interaction -- thus,
+the corresponding \trans entry must exist (which we can check, as the issuer is
+honest). The adversary wins if, either the extraction process fails, or the
+extracted user secret key and credentials make the corresponding issuance
+function fail.
+
+For both \ExpForgeIssue and \ExpForgeSign, the adversary is given access to the
+oracle set $\Oforgeissue = \Oforgesign \gets \lbrace\HU,\CU\rbrace\GEN,\IGEN,
+\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.
+
+\begin{figure}[htp!]
+    \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
+      \parm \gets \Setup(1^\secpar) \\
+      \cid \gets \adv^{\Oforgeissue}(\parm) \\
+      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
+      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
+      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
+      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trans[\cid]) \\
+      \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
+      \exists \cred \in \scred~\suchthat~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0: \\
+      \pcind \pcreturn 1 \\
+      \pcreturn 0
+    }
+  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
+  \label{fig:exp-uas-unfor-issue}
+\end{figure}
+
+\begin{figure}[htp!]
+    \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
+      \parm \gets \Setup(1^\secpar) \\
+      (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
+      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
+      \SIG[\uid]: \pcreturn 0 \\
+      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
+      \pcreturn 0 \\
+      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
+      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
+      = 0: \pcreturn 1 \\
+      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets \ExtractSign(\oid,\siid,\Sig,
+      \msg,\feval) \\
+      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
+      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1
+      \lor \Yeval \notin \rngfeval:
+      \pcreturn 1 \\
+      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp'
+      \lor \yinsp \neq \yinsp':
+      \pcreturn 1 \\
+      \pcif \exists \cred \in \scred~\suchthat~
+      \IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
+      \pcreturn 1 \\
+      \pcif \nexists \uid~\suchthat~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
+      \pcreturn 0
+    }
+  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
+  \label{fig:exp-uas-unfor-sign}
+\end{figure}
+
+\begin{definition}{(Unforgeable issuance of \UAS)}
+  \label{def:issue-forge-uas}  
+  We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
+  $\AdvForgeIssue=\Pr\lbrack\ExpForgeIssue(1^\secpar)=1\rbrack$.
+  %
+  A \UAS scheme has unforgeable issuance if, for any p.p.t. adversary $\adv$,
+  \AdvForgeIssue is a negligible function of $1^\secpar$.
+\end{definition}
+
+\begin{definition}{(Unforgeable signing of \UAS)}
+  \label{def:sign-forge-uas}  
+  We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
+  $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
+  %
+  A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
+  \AdvForgeSign is a negligible function of $1^\secpar$.
+\end{definition}
+
+For short, we say that an \UAS scheme that has both unforgeable issuance and
+signing, is an unforgeable \UAS scheme.
+
+\paragraph{Discussion on the generality of unforgeability in \UAS schemes.} %
+% The notion of signature unforgeability we present for \UAS is strictly more
+% general than the corresponding one of traceability for group signatures. This is
+% again a direct consequence of the fact that \Open can return an arbitrary
+% function of the signer's key and credentials (and signed message), which is a
+% strict generalization of the conventional \Open. Although, even in that case, we
+% need to take into account attributes, and the fact that the same user may obtain
+% multiple credentials (that is why, even when having \Open return the identity of
+% the signer, our notion is not exactly the same). In this sense, the sign
+% unforgeability notion for \UAS is equivalent to that of anonymous
+% credentials. It would seem, though, that we do not need the traceability part of
+% group signatures; after all, it is the protection against wrong claims on
+% attributes what enables meaningful and flexible authentication. However, the
+% type of protection against misuses of the open functionality that we can
+% get with an honest issuer (as in traceability) is much higher than without an
+% honest issuer (as in non-frameability). Specifically, with an honest issuer we
+% can ensure that the adversary cannot even alter the value returned by \Open on
+% signatures by corrupt users, nor the output of the signing predicate \feval.
+% Whereas, with a corrupt issuer, all we can ensure is that
+% the adversary cannot forge a signature from an honest user for which \Open
+% returns the same value as a signature by that honest user would produce; and,
+% certainly, a corrupt issuer can arbitrarily issue credentials meeting any
+% desired predicate \feval. Signing unforgeability is, therefore, a core property
+% to ensure accountability.
+
+% Similarly, by adding the related notion of issuance unforgeability, we ensure
+% that no credential can be issued that did not meet the corresponding issuance
+% policy. This is again something not necessary in group signatures (with
+% verifiable openings), where \Judge accepting the opening proof implies that
+% there is a valid join transcript associated to the membership credential used
+% to produce the signature. However, in \UAS, given that the credentials contain
+% attributes, even though that transcript exists, we need to make sure that the
+% issuance policy over these attributes was satisfied -- and this is not something
+% (easily) extractable from the signature.
+
+\paragraph{Non-frameability.} %
+The notion of non-frameability in \UAS schemes is unavoidably more subtle than
+in group signatures. To see this, we note that, by allowing arbitrary
+evaluation and open functions to be used, it can be perfectly valid to
+have a signature produced by a corrupted user output the same \yeval or \yinsp
+values than the ones output when evaluating or opening a signature by an honest
+user. As a concrete example, imagine an open function that returns the
+nationality of the signer. In any country, there will be many users (corrupt or
+not) sharing nationality.
+%
+More generally, since the issuer is dishonest in non-frameability properties
+and, in \UAS, the value produced by \Open may depend on the attributes
+included in user credentials, the adversary may even be able to just produce
+``legitimate'' openings that output any desired value.
+
+Thus, we again need to resort to extraction techniques. In the non-frameability
+definition for \UAS, given in experiment \ExpNonframe in
+\figref{fig:exp-uas-frame}, the adversary is challenged to produce a signature
+and opening proof that is accepted by \Verify and \Judge, respectively. From
+the signature, we then extract the secret key of the signer, and match it
+against the secret keys of the honest users. The adversary wins if there is a
+match and the signature has not been queried to \SIGN, or if the value \yinsp
+output by the adversary is accepted by \Judge, yet it is different from the
+extracted $\yinsp'$ value. In the game, the
+adversary has access to the oracles in $\Oframe \gets \lbrace\HU,\CU\rbrace\GEN,
+\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG,\OBTAIN,\SIGN$.
+
+\begin{figure}[htp!]
+  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
+    \parm \gets \Setup(1^\secpar) \\
+    (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
+    \adv^{\Oframe}(\parm) \\
+    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
+    \pcreturn 0 \\
+    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
+    \pcreturn 0 \\
+    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
+    \ExtractSign(\oid,\siid,\Sig,\msg,\feval) \\
+    \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg)
+    \pccomment{\todo{Added this line -- check line refs.}} \\
+    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1
+    \lor \Yeval \notin \rngfeval: \pcreturn 1 \\
+    \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
+    \lor \yinsp \neq \yinsp': \pcreturn 1 \\    
+    \pcif \nexists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \pcreturn 0 \\
+    \pcif \nexists (\cdot,\cdot,\Sig,\Yeval,\msg,\feval)
+    \in \SIG[\uid]: \pcreturn 1 \\
+    \pcreturn 0
+  }
+  \caption{Experiment for non-frameability on \UAS schemes.}
+  \label{fig:exp-uas-frame}
+\end{figure}
+
+\begin{definition}{(Non-frameability of \UAS)}
+  \label{def:frame-uas}
+  We define the advantage \AdvNonframe of $\adv$ against \ExpNonframe as
+  $\AdvNonframe=\Pr\lbrack\ExpNonframe(1^\secpar)=1\rbrack$.
+  %
+  An \UAS scheme satisfies non-frameability if, for any p.p.t. adversary $\adv$,
+  \AdvNonframe is a negligible function of $1^\secpar$.
+\end{definition}
+
+\paragraph{Discussion on the generality of non-frameability in \UAS schemes.} %
+% Anonymous credentials do not have non-frameability property and, thus, it is
+% hard to make a comparison. However, we can draw some connections with AC schemes
+% that support revocation, as revocation is somehow equivalent to linking, which
+% is a type of inspection available in group signatures. In this sense, note that
+% basic revocation (without straight deanonymization) can be trivially achieved
+% through our generic \Open function. For instance, one could set \finsp to
+% be a pseudorandom number seeded with the user's public key (or credential). In
+% this sense, \Open could be essentially seen as a Verifiable Random Function.
+% If we compare with group signatures, our notion is also more general than the
+% conventional one, again for the same reason as sign unforgeability (i.e., \Open
+% can return any value, not just the signer's identity). Thus, the need to extract
+% the signer's data in order to detect if a framing has taken place.
+
+\subsection{\CUASGen: A Generic \UAS Construction}
+\label{ssec:generic-construction-uas}
+
+In this section, we give a generic construction of an \UAS scheme, based on
+generic building blocks. We use three different NP relations in our generic
+construction. Namely:
+
+\begin{description}
+\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs via \fissue the rules for
+  issuing new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
+  (\usk,\scred,\attrs_{\scred},r), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
+  \CCommit(usk;r) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
+  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1 \rbrace$,
+  where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
+  \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
+  Basically, this relation requires that, in order to issue a credential with
+  attribtes \attr, and bound to \usk, the requester has to commit to \usk and
+  prove knowledge of it, as well as prove that all additional credentials needed
+  for the issuing to be granted, meet some defined policy \fissue.
+\item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
+  verifiers define them. Governs via \feval and \finsp what utility
+  information is directly revealed by signatures, or extracted by openers.
+  It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
+  \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
+  \sipk_{\scred},\Eek,\widetilde{\Eek}): \ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)
+  \land \cinsp= \EEnc (\Eek,\yinsp;r') \land (\yeval^0,\yeval^1) = \feval(\usk,
+  \scred,\msg) \land \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \land
+  \forall \cred \in \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred})
+  = 1) \rbrace$, with $\attrs_{\scred}$ and $\sipk_{\scred}$ as in
+  $\NIZKRel_{\Issue}$. In a
+  nutshell, this relation ensures that signatures will produce the correct
+  signature evaluation and opening values, and that any credential used to
+  create the signature is bound to the same \usk key.
+\item[$\NIZKRel_{\Open}$:] Ensures that the utility information extracted by
+  the \Open algorithm is correct. It is defined as $\NIZKRel_{\Open} =
+  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$.
+\end{description}
+
+\paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
+The setup process essentially consists on generating the public parameters
+for all the building blocks. In detail, it parses \secpar as $(\Csecpar,
+\NIZKsecpar,\SBCMsecpar,\Esecpar)$. Then, run $\Cparm \gets
+\CSetup(\Csecpar)$, $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$, $\Sparm \gets
+\SSetup(\Ssecpar)$, $\Eparm \gets \ESetup(\Esecpar)$, $\NIZKcrs_{\Issue} \gets
+\NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$, $\NIZKcrs_{\Sign} \gets
+\NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$, and $\NIZKcrs_{\Open} \gets
+\NIZKSetup^{\NIZKRel_{\Open}}(\NIZKsecpar)$. Return $(\Cparm,\SBCMparm,
+\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Open},
+\AttrSpace)$. Note that many of these parameter setup algorithms can
+actually be run by separate entities (respecting some commonalities like,
+e.g., same pairing-friendly curves). For instance, each opener could
+run its own \ESetup algorithm, or each verifier its
+$\NIZKSetup^{\NIZKRel_{\Sign}}$, to advertise the signing evaluation functions
+it accepts. For simplicity of exposition, we bundle them together here.
+
+\paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
+To generate its key pair, each issuer first parses \parm as $(\cdot,\SBCMparm,
+\Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets
+\SKeyGen(\Sparm)$, $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$,
+$\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$, $\ipk \gets (\Svk,\fissue,
+\sig_{\fissue})$, $\isk \gets \Ssk$ and return $(\ipk,\isk)$.
+
+\paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
+To generate its key pair, each opener first parses \parm as $(\cdot,\cdot,
+\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets \SKeyGen
+(\Sparm)$, $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, $\sig_{\finsp} \gets \SSign
+(\Ssk,\finsp)$, $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$, and $\osk \gets
+(\Ssk,\Edk)$.
+
+\paragraph{$\usk \gets \UKeyGen(\parm)$.} %
+Each user, prior to requesting credentials, generates his secret key by parsing
+\parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\AttrSpace)$, and picking randomly
+$\usk \getr \AttrSpace$.
+
+\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
+  \langle\Obtain(\usk,\ipk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle$.} %
+The protocol is run between an issuer with key pair $(\ipk,\isk)$, and a user
+with secret key \usk and credentials \scred, where each $\cred \in \scred$ is
+issued by an issuer with
+public key $\ipk_{\cred}$ (which we assume that the user can easily retrieve,
+e.g., from secure storage, given \cred), and attests attributes
+$\attrs_{\cred}$. The user requests a signature on a commitment to the user key,
+as well as on the attributes in \attrs. In addition, the user proves that the
+issuance function \fissue established by the issuer is satisfied by the
+credentials in $\scred$
+and its user secret key. For this, we use relation $\NIZKRel_{\Issue}$, as
+defined above. The interactive protocol for a user to obtain a credential from
+an issuer of the system is then simply an execution of the interactive signing
+protocol of an \SBCM scheme, where the user runs $\SBCMCom(\ipk,\usk,\attrs)$,
+and the issuer runs $\SBCMSign(\isk,\attrs)$; in both cases, using
+$\NIZKRel_{\Issue}$ as \NIZK relation. The credential \cred produced by the user
+is the result of the interactive signing protocol, and the \utrans entry for
+the issuer is its transcript which is a $(\Ccom,\attrs,\sipk,\cred,\pi)$ tuple.
+
+\iffalse
+\begin{itemize}
+\item \uline{User}: Commit to the user secret key with $\Ccom \gets
+  \CCommit(\usk)$. Compute proof $\NIZKproof \gets
+  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred,\attrs_{\scred}),
+  (\Ccom,\attrs,\sipk_{\scred}))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
+\item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
+  (\NIZKcrs_{\Issue},\NIZKproof,(\Ccom,\attrs,\sipk))$, and abort if it fails. Then,
+  compute the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,
+  \attrs)$. Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\sipk,
+  \cred,\NIZKproof)$.
+\item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
+  \attrs \cup \lbrace \usk \rbrace)$. Reject if verification fails.
+  Otherwise, return \cred.
+\end{itemize}
+\fi
+
+\paragraph{$\Sig \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
+In the signing algorithm, we make use of relation $\NIZKRel_{\Sign}$.
+% 
+From this, in order to produce a valid signature, the user first evaluates
+$(\yeval^0,\yeval^1) \gets \feval (\usk,\scred,\msg)$, and decides whether or
+not to continue with the signing process -- this may depend, e.g., on the
+opening policy of \opk, as the output of \feval may influence whether the user
+will be de-anonymizable or not, depending on the \finsp function in \opk.
+%
+The user also computes a random encryption key pair with $(\widetilde{\Eek},
+\widetilde{\Edk}) \gets \EKeyGen(\Eparm)$. Then, the user parses \opk as $(\Svk,\Eek,
+\finsp,\sig_{\finsp})$ and checks that $\Verify(\Svk,\sig_{\finsp},\finsp) = 1$
+(note that this step may be cached), to compute $\yinsp \gets \finsp((\yeval^0,
+\yeval^1),\usk,\scred,\msg)$, and separately encrypts both $\yeval^1$ and
+\yinsp by running $\ceval \gets \EEnc(\widetilde{\Eek},\yeval^1;r)$ and $\cinsp \gets
+\EEnc(\Eek,\yinsp; r')$ for some fresh randomness $r,r'$. Finally, the user
+computes $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,
+\scred, \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
+\sipk_{\scred},\Eek,\widetilde{\Eek}))$ and outputs $(\sig = (\NIZKproof,\ceval,
+\cinsp),\yeval^0)$.
+
+\paragraph{$1/0 \gets \Verify(\opk,\sipk,\Sig,\msg,\feval)$.} %
+The ``cryptographic'' side of the verification essentially consists on checking
+the NIZK proof. That is, parse \Sig as $(\sig = (\NIZKproof,\cinsp),\yeval,
+\ceval)$ and check whether $\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,
+\ceval,\cinsp,\sipk,\opk)) = 1$. In addition, the verifier may further check
+whether \yeval meets its needs.
+
+\paragraph{$(\yinsp,\NIZKproof)/\bot \gets
+  \Open(\osk,\sipk,\Sig,\msg,\feval)$.} %
+Here we leverage relation $\NIZKRel_{\Open}$.
+%
+To open a signature, the opener first verifies the signature by running $\Verify
+(\opk,\sipk, \Sig,\msg,\feval)$. If verification succeeds, it parses
+\Sig as $(\sig=(\NIZKproof,\cinsp),\yeval,\ceval)$, decrypts \Ec by running $\yinsp
+\gets \EDec(\osk,\cinsp)$, and computes $\NIZKproof_{\Open} \gets
+\NIZKProve^{\NIZKRel_{\Open}}(\NIZKcrs_{\Open},\osk,(\cinsp,\yinsp))$. It
+returns $(\yinsp,\NIZKproof_{\Open})$.
+
+\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\Sig,\msg)$.} %
+To assess the validity of an opening proof, first check the signature
+by running $\Verify(\opk,\sipk,\Sig,\msg,\feval)$. If the check succeeds,
+parse \Sig as $((\cdot,\cinsp),\cdot,\cdot)$ and verify \NIZKproof with
+$\NIZKVerify(\NIZKcrs_{\Open},\NIZKproof,(\cinsp,\yinsp))$. Accept it the NIZK
+verification passes, and reject otherwise.
+
+\subsection{Correctness and Security of \CUASGen}
+\label{ssec:security-uas}
+
+First, we define the \ExtractIssue, \ExtractSign, \IdentifyCred and \IdentifyUK
+functions that are needed for some of the properties to be meaningful, in
+\figref{fig:helper-funcs}.
+
+\begin{figure}[ht!]
+  \begin{minipage}[t]{\textwidth}
+    \procedure{$\ExtractIssue(\parm,\utrans)$}{%
+      \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Issue},\cdot,
+        \cdot,\cdot)$; $\NIZKcrs_{\Issue}$ as $(\NIZKcrs,\NIZKtrap)$; and
+        \utrans as $(\Ccom,\sipk,\cred,\NIZKproof)$} \\
+      \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\Ccom,\attrs,\sipk)): 
+      \pcreturn \bot \\
+      (\usk,\scred,\attrs_{\scred}) \gets \NIZKExtract(\NIZKcrs,\NIZKtrap,
+      (\Ccom,\attrs,\sipk),\NIZKproof) \\
+      \pcreturn (\usk,\attrs,\scred,\attrs_{\scred}) \\
+    }
+
+    \procedure{$\ExtractSign(\parm,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
+      \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
+        \cdot,\cdot)$; $\NIZKcrs_{\Sign}$ as $(\NIZKcrs,\NIZKtrap)$; and
+        \sig as $(\NIZKproof,\Ec)$} \\
+      \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \gets
+        \PUBIK[\siid]$} \\
+      \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,
+      \sipk,\opk)): \pcreturn \bot \\
+      (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets \NIZKExtract(\NIZKcrs,
+      \NIZKtrap, (\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk,\opk,\widetilde{\Eek}),
+      \NIZKproof) \\
+      \pcreturn (\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \\
+    }
+
+    \procedure{$\IdentifyCred(\usk,\attrs_{\cred},\cred)$}{%
+      \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
+    }
+
+    \procedure{$\IdentifyUK(\uid,\usk)$}{%
+      \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
+      \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
+      \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trans[\cid]) \\
+      \pcind \pcif \usk = \usk': \pcreturn 1 \\
+      \pcreturn 0
+    }
+  \end{minipage}
+  \label{fig:helper-funcs}
+  \caption{Definition of helper functions \ExtractIssue, \ExtractSign,
+    \IdentifyCred, and \IdentifyUK, for \CUASGen.}
+\end{figure}
+
+\begin{theorem}[Correctness of \CUASGen]
+  \label{thm:correctness-uas}
+  If the underlying schemes for commitments, public-key encryption and \SBCM,
+  are correct,
+  as well as the NIZKs for $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
+  $\NIZKRel_{\Open}$, our generic construction \CUASGen satisfies correctness as
+  defined in \defref{def:correctness-uas}.
+\end{theorem}
+
+\begin{proof}[\thmref{thm:correctness-uas}; Correctness of \CUASGen]
+  By correctness of \SBCM and the NIZK for $\NIZKRel_{\Sign}$, the signature
+  produced at line 5 of \ExpCorrect is accepted at line 6 by \Verify.
+  Moreover, all the credentials employed to honestly produce the signature,
+  identified with \scid, meet their respective issuance policies due to
+  correctness of the NIZK for $\NIZKRel_{\Issue}$, so no $\fissue^\cid$ check
+  returns $0$ at line 9. Similarly, as $\feval \in \famfeval$ is checked at
+  line 3, and due to correctness of the NIZK for $\NIZKRel_{\Sign}$, the
+  output of \feval matches $\yeval^0$ at line $11$, which must have been
+  computed over $\usk=\UK[\uid]$, as in line $10$, due to correctness of the
+  commitment scheme. Finally, correctness of the NIZKs for $\NIZKRel_{\Sign}$
+  and $\NIZKRel_{\Open}$, and correctness of the encryption scheme, ensure that
+  \Judge accepts the proof produced by \Open, and \yinsp is the correct value
+  for the chosen $\finsp^{\oid}$.
+\end{proof}
+
+\begin{theorem}[Issuance anonymity of \CUASGen]
+  \label{thm:iss-anonymity-uas}
+  If the NIZK systems used for $\NIZKRel_{\Issue}$ and $\NIZKRel_{\Sign}$ are
+  zero-knowledge, our \CUASGen construction satisfies issuance anonymity as
+  defined in \defref{def:iss-anonymity-uas}.
+\end{theorem}
+
+\begin{proof}[\thmref{thm:iss-anonymity-uas}; Issuance anonymity of \CUASGen]
+  We prove the special case in which the adversary makes only one query to the
+  \OBTCHALb oracle. The generalization to polynomially many queries follows from
+  a standard hybrid argument.
+
+  Let $G_0=\ExpIssAnonb(1^\secpar)$. We define $G_1$ by replacing the calls to
+  \NIZKSetup in $G_0$, for the $\NIZK^{\Issue}$ and $\NIZK^{\Sign}$ systems by
+  calls to their corresponding \NIZKSimSetup. By zero-knowledgeness of the
+  NIZKs, both games are indistinguishable.
+
+  Next, we simulate the NIZK proofs produced by \Obtain within the \OBTCHALb
+  oracle and, consequently, the NIZK proofs produced by \Sign in \SIGN for
+  signatures from the challenge user and credentials. Then, we show that the
+  adversary cannot distinguish executions for $b=0$ from executions for $b=1$,
+  except with negligible probabability.
+
+  More concretely, on the one hand, let $G_1^0$ to be $G_1$, conditioned on
+  $b=0$. Concretely, the proofs sent by the challenge user $\cuid_0$ to the
+  adversarial issuer are of
+  the form $\pi^*_0 =\NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\UK[\cuid_0],
+  \CCRED[\cscid_0],\ATTR[\cscid_0],r),(\Ccom,\attrs,\PUBIK[\cscid_0]))$. The
+  NIZK proofs included in the signatures produced by $\cuid_0$ are defined
+  correspondingly, but for $\NIZK^{\NIZKRel_{\Sign}}$. From $G_1^0$, we define
+  $G_2^0$, but instead of using \NIZKProve, we use \NIZKSim (for both \Issue
+  and \Sign). That is, the proofs for credential requests are generated as
+  $\pi^s_0 =\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\tau,(\Ccom,\attrs,
+  \PUBIK[\cscid_0]))$. By zero-knowledge of the NIZK systems for \Issue and
+  \Sign, $G_2^0$ is indistinguishable from $G_1^0$.
+
+  On the other hand, following the same process for $G_1^1$ and $G_2^1$.
+  Concretely, for the case of the proofs at issuance time, they are of the
+  shape $\pi^s_1 =\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\tau,(\Ccom,\attrs,
+  \PUBIK[\cscid_1]))$. Note first that $\PUBIK[\cscid_1] = \PUBIK[\cscid_0]$,
+  by definition of the \OBTCHALb oracle. Hence, the produced proofs are exactly
+  the same independently on the value of the bit $b$.
+
+  Thus, $\AdvIssAnon=|\Pr\lbrack
+  \ExpIssAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpIssAnonz(1^\secpar)=1\rbrack|$.
+  As argued, $G_1$ is indistinguishable from $\ExpIssAnonb$, so
+  $\AdvIssAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
+  G_1^0(1^\secpar)=1\rbrack| \approx
+  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
+  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
+  \AdvIssAnon is negligible.
+
+\end{proof}
+
+\begin{theorem}[Signature anonymity of \CUASGen]
+  \label{thm:sign-anonymity-uas}
+  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge, and the
+  public-key encryption scheme is IND-CCA secure, our \CUASGen construction
+  satisfies signature anonymity as defined in \defref{def:sign-anonymity-uas}.
+\end{theorem}
+
+\begin{proof}[\thmref{thm:sign-anonymity-uas}; Signature anonymity of \CUASGen]
+  \iffalse
+  First, we define \SimSetup, \SIMOBTAIN, \SIMSIGN and \SIMOPEN as in
+  \figref{fig:anon-sim}.
+
+  \begin{figure}[ht!]
+    \begin{minipage}[t]{\textwidth}
+      \procedure{$\SimSetup(\secpar,\AttrSpace)$}{%
+        \textrm{Parse}~\secpar~\textrm{as}~(\cdot,\secpar_{\NIZK},\cdot,\cdot) \\
+        (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue})
+        \gets \NIZKSimSetup^{\NIZKRel_{\Issue}}(\secpar_{\NIZK}) \\
+        (\NIZKcrs_{\Sign},\NIZKtrap_{\Sign})
+        \gets \NIZKSimSetup^{\NIZKRel_{\Sign}}(\secpar_{\NIZK}) \\
+        (\NIZKcrs_{\Open},\NIZKtrap_{\Open})
+        \gets \NIZKSimSetup^{\NIZKRel_{\Open}}(\secpar_{\NIZK}) \\
+        \textrm{Compute}~\parm \gets (\Cparm,\SBCMparm,\Sparm,\Eparm)~
+        \textrm{as in}~\Setup \\
+        \pcreturn ((\parm,\NIZKcrs_{\Issue},
+        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
+        (\NIZKtrap_{\Issue},\NIZKtrap_{\Sign},\NIZKtrap_{\Open})) \\
+      }
+
+      \begin{minipage}[t]{\textwidth}
+        \begin{minipage}[t]{0.55\textwidth}
+          \procedure{$\SIMOBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
+            \pcif \uid \notin \HU: \pcreturn \bot \\
+            \pcif \iid \notin \CI: \pcreturn \bot \\
+            \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
+            \sipk_{\scred} \gets \PUBIK[\scid] \\
+            \langle \cred, \cdot \rangle \gets
+            \langle SimObt(\attrs,\PUBIK[\iid],\sipk_{\scred}),\adv \rangle \\
+            \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
+            \pcreturn \top \\      
+          }
+        \end{minipage}
+        \begin{minipage}[t]{0.45\textwidth}
+          \procedure{$SimObt(\attrs,\ipk,\sipk_{\scred})$}{%
+            \textrm{Runs $\langle \SBCMCom^{\NIZKRel_{\Issue}},\adv \rangle$} \\
+            \pcind \textrm{using $\NIZKSim^{\NIZKRel_{\Issue}}
+              (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue},\cdot)$} \\
+            \pcind \textrm{instead of $\NIZKProve^{\NIZKRel_{\Issue}}
+              (\NIZKcrs_{\Issue},\cdot,\cdot)$}
+          }
+        \end{minipage}
+      \end{minipage}
+
+      \begin{minipage}[t]{\textwidth}
+        \begin{minipage}[t]{0.55\textwidth}
+          \procedure{$\SIMSIGN(\oid,\uid,\scid,\msg,\feval)$}{%
+            \pcif \uid \notin \HU: \pcreturn \bot \\
+            \pcif \feval \notin \famfeval: \pcreturn \bot \\
+            \Sig \gets SimSign(\PUBOK[\oid],\msg,\feval) \\
+            \SIG[\uid] \gets \SIG[\uid] \cup
+            \lbrace (\oid,\scid,\Sig,\msg,\feval) \rbrace \\
+            \pcreturn \Sig \\
+          }
+        \end{minipage}
+        \begin{minipage}[t]{0.45\textwidth}
+          \procedure{$SimSign(\opk,\msg,\feval)$}{%
+            \textrm{Like}~\Sign()~\textrm{using} \\
+            \pcind \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
+            \NIZKtrap_{\Sign},\cdot) \\
+            \pcind \textrm{instead of}~\NIZKProve^{\NIZKRel_{\Sign}}
+            (\NIZKcrs_{\Sign},\cdot,\cdot)        
+          }
+        \end{minipage}
+      \end{minipage}
+
+      \begin{minipage}[t]{\textwidth}
+        \begin{minipage}[t]{0.55\textwidth}
+          \procedure{$\SIMOPEN(\oid,\Sig,\msg)$}{%
+            \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\msg,\feval)
+            \in \SIG[\uid] \\
+            % \textrm{Parse}~\Sig~\textrm{as}~(\sig,\yeval,\ceval) \\
+            (\yinsp,\iproof) \gets
+            SimOpen(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
+            \pcif \CSIG[\Sig] \neq \bot: \\
+            \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
+              \feval$} \\
+            \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b}) \\
+            \pcind (\yinsp',\iproof') \gets
+            \Open(\PRVOK[\oid],\IK[\siid],\\
+            \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
+            \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
+            \pcreturn (\yinsp,\iproof)          
+          }
+        \end{minipage}
+        \begin{minipage}[t]{0.45\textwidth}
+          \procedure{$SimOpen(\opk,\msg,\feval)$}{%
+          }
+        \end{minipage}
+      \end{minipage}    
+    \end{minipage}
+    \label{fig:sim-anon}
+    \caption{Definition of \SimSetup, \SIMOBTAIN, \SIMSIGN, and \SIMOPEN for
+      anonymity in \CUASGen.}
+  \end{figure}
+  \fi
+
+  In this proof, we restrict to the case in which the adversary can only make
+  one query to the challenge oracle. Note however that the generalization to
+  polynomially many queries given in \cite{bsz05} applies here too (with the
+  corresponding security loss). Thus, proving security for one query to the
+  challenge oracle is enough.
+
+  We start from $G_0=\ExpSigAnonb$, and define game $G_1$ to be exactly the same
+  as $G_0$, except that, within the $\Setup$ algorithm, we replace
+  $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. By zero-knowledgeness,
+  $G_1$ is indistinguishable from $G_0$.
+
+  From $G_1$, we consider $G^0_1$, which we define to be $G_1$, for $b=0$
+  (i.e., \ExpSigAnonz, using $\NIZKSimSetup^{\Sign}$). The challenge sent to the
+  adversary is $(\csig_0,\yeval) \gets \Sign(\PRVUK[\cuid_0],\PUBOK[\oid],
+  \CRED[\scid_0],\msg,\feval)$, where $\csig_0 = (\pi_0,\Ec_{\yinsp})$, with
+  $\pi_0 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
+  \ceval,\cinsp,\PUBIK[\scid_0],\widetilde{\Eek},\PUBOK[\oid]),(\PRVUK[\cuid_0],
+  \CRED[\scid_0],\attrs_{\scid_0},\yeval^1,\yinsp,r,r'))$, $\ceval = \EEnc
+  (\widetilde{\Eek},\yeval^1;r)$, and $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$.
+  % 
+  Further, we build $G_2^0$ from $G_1^0$ by simulating the proof $\pi_0$. That
+  is, in $G_2^0$, $\csig_0 = (\pi_0^s,\ceval,\cinsp)$, where $\pi^s_0 =
+  \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
+  \ceval,\cinsp,\PUBIK[\scid_0],\PUBOK[\oid]))$. By zero-knowledgeness
+  of $\NIZK^{\Sign}$, $G_2^0$ is indistinguishable from $G_1^0$.
+
+  Similarly, we consider $G_1^1$ and $G_2^1$. That is, $G_1^1$ is $G_1$
+  for $b=1$, where the challenge
+  sent to the adversary is $(\csig_1,\yeval) \gets \Sign(\PRVUK[\cuid_1],
+  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,\ceval,
+  \cinsp)$, with $\pi_1 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
+  (\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
+  \PUBOK[\oid]),(\PRVUK[\cuid_1],\CRED[\scid_1],\attrs_{\scid_1},\yeval^1,
+  \yinsp,r,r'))$, $\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)$, and
+  $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$. As before, $G_2^1$ is built from
+  $G_1^1$, simulating $\pi_1$. That is, in $G_2^1$, $\csig_1 = (\pi_1^s,\ceval,
+  \cinsp)$, where $\pi^s_1 = \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
+  \NIZKtrap,(\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
+  \PUBOK[\oid]))$. Again, by zero-knowledge of $\NIZK^{\Sign}$, $G_2^1$ is
+  indistinguishable from $G_1^1$. Note also that $G_2^1$ and $G_2^0$ are
+  indistinguishable, due to the IND-CCA property of the encryption scheme
+  (so, the \ceval values in $\csig_0$ and $\csig_1$ are indistinguishable),
+  in the  challenge oracle used in the anonymity game, we restrict to
+  $\PUBIK[\scid_0] = \PUBIK[\scid_1]$, and the respective \cinsp values encrypt
+  the same \yinsp value (and, otherwise, \adv~is not allowed to open it).
+
+  Finally, consider the definition of $\AdvSigAnon=|\Pr\lbrack
+  \ExpSigAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpSigAnonz(1^\secpar)=1\rbrack|$. As
+  argued, $G_1$ is indistinguishable from $\ExpSigAnonb$, thus
+  $\AdvSigAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
+  G_1^0(1^\secpar)=1\rbrack| \approx
+  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
+  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
+  \AdvSigAnon is negligible.
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Issuance unforgeability of \CUASGen]
+  \label{thm:issue-forge-uas}
+  If the underlying NIZK used for $\NIZKRel_{\Issue}$ is zero-knowledge,
+  simulation extractable and sound, then our \CUASGen construction satisfies
+  issuance unforgeability as defined in \defref{def:issue-forge-uas}.
+\end{theorem}
+
+\begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
+  We show that the probability that \fissue outputs $0$ is negligible, as well
+  as the probability that the extracted \usk is not the one that was used to
+  request some of the credentials employed to obtain the credential specified by
+  the adversary.
+  %
+  For this purpose, we define two games, $G_0=\ExpForgeIssue$, and $G_1$, which
+  is exactly the same, but where, within the \Setup algorithm, we replace
+  $\NIZKSetup^{\Issue}$ with $\NIZKSimSetup^{\Issue}$. Due to zero-knowledgeness
+  of $\NIZK^{\NIZKRel_{\Issue}}$, both games are indistinguishable.
+
+  Now, observe that the adversary is required to output a credential
+  identifier for which associated entries in \trans and \CRED exist; moreover,
+  if such a credential was produced by an issuer, we must have access to those
+  entries, as issuers are assumed to be honest.
+  %
+  Then, given that $\NIZKRel_{\Issue}$ is knowledge extractable (which is implied
+  by simulation-extractability), in game $G_1$
+  we can apply the \NIZKExtract function, which produces a tuple $(\usk,\scred,
+  \attrs_{\scred})$ from $\utrans = (\Ccom,\attrs,\sipk,\cred,\NIZKproof)$.
+  %
+  Since \NIZKproof is accepted by \ExtractIssue, from the soundness of \NIZK, we
+  know that all $\cred \in \scred$ are valid signatures over \usk, and their
+  respective $\attrs_{\cred}$. Thus, \IdentifyCred returns $1$ for all $(\usk,
+  \attrs_{\cred},\cred)$ tuples. That is, all the credentials in \scred given
+  to \fissue belong to the same user, who is the owner of \usk.
+  %
+  Finally, since issuers are honest, we know that $\ATTR[\cid] = \attrs$ and,
+  consequently, $\fissue(\usk,\scred,\ATTR[\cid]) = \fissue(\usk,\scred,\attrs)
+  = 1$, due to the soundness of \NIZK.
+  %
+  \qed
+\end{proof}
+
+\begin{theorem}[Signing unforgeability of \CUASGen]
+  \label{thm:sign-forge-uas}
+  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
+  extractable,the NIZK scheme for $\NIZKRel_{\Open}$ is complete, the public-key
+  encryption scheme is correct, and \SBCM is correct and one-more unforgeable,
+  then our \CUASGen construction satisfies signing unforgeability as defined in
+  \defref{def:sign-forge-uas}, except with negligible probability.
+\end{theorem}
+
+\begin{proof}[\thmref{thm:sign-forge-uas}; Sign unforgeability of \CUASGen]
+  As in \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
+  and $G_1$, which is exactly the same but where, within the \Setup algorithm,
+  we replace $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. After
+  zero-knowledgeness of $\NIZK^{\Sign}$, both games are indistinguishable.
+  %
+  Next, we show that an adversary winning $G_1$ can be used to break the
+  one-more unforgeability property of \SBCM.
+
+  If the verification at line 4 holds, then $(\msg,\feval,\yeval,\ceval,
+  \cinsp,\sipk,\opk,\widetilde{\Eek}) \in \NIZKLang^{\Sign}$. Then:
+  %
+
+  \paragraph{(a) \Judge accepts $(\yinsp,\iproof)$.} %
+  Simulation extractability of $\NIZK^{\Sign}$ thus ensures that $\cinsp =
+  \EEnc(\Eek,\yinsp)$, and since the $(\yinsp,\iproof)$ is generated honestly at
+  line 5, then \yinsp is the correct decryption of \cinsp, and  correctness of
+  $\NIZK^{\Open}$ ensures that \Judge outputs $1$ at line 6.
+
+  \paragraph{(b) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
+    pair.} Also, due to simulation extractability of $\NIZK^{\Sign}$:
+
+  \begin{itemize}
+  \item $\yeval^0 = \yeval$, where $(\yeval^0,\cdot) = \feval(\usk,\scred,
+    \msg)$, and $\yeval$ is as output by \adv~at step 2.    
+  \item $\tyeval^1 = \yeval^1$, where $(\cdot,\yeval^1) = \feval(\usk,\scred,
+    \msg)$, and $\tyeval^1$ is as extracted by \ExtractSign at line 7.
+  \end{itemize}
+
+  Thus, the probability of \adv~winning at line 9 is $0$.
+
+  \paragraph{(c) The output of \finsp matches the output of \Open.} %
+  After (a), the \yinsp value output by \Open is the correct decryption of
+  \cinsp. After (b), the $(\yeval^0=\yeval,\yeval^1)$ values output by
+  \ExtractSign match the evaluation of \feval. Thus, simulation extractability
+  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\usk,\scred,\msg)
+  = \yinsp$ and, also, that \yinsp matches the $\yinsp'$ value extracted by
+  \ExtractSign. Thus, the probability of \adv~winning at line 10 is $0$.
+
+  \paragraph{(d) All {\cred}s are bound to the same \usk.} %
+  $\NIZKRel^{\Sign}$ includes a condition that $\forall \cred \in \scred,
+  \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1$. Thus, simulation
+  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
+  credentials involved in the signature contain \usk as their user key (first)
+  attribute. Consequently, \IdentifyCred returns $1$ for all the involved
+  credentials, and the probability of \adv~winning at line 11 is $0$.
+
+  \paragraph{(e) \usk must belong to a known user.} %
+  The only remaining option for $\adv$ to win is via winning condition at line
+  12, meaning that \IdentifyUK fails to find an honest or corrupt users with
+  a \usk matching the one used to request the credentials used to produce the
+  signature output by \adv. However, at line 12, we already know that all
+  credentials are valid signatures by the issuer and that, also, all are bound
+  to the same user key. If this key is not associated to any known user, this
+  means that there is no matching $\langle\Obtain,\Issue\rangle$ transcript for
+  a credential over \usk --i.e., the honest issuer did not issue any credential
+  to \usk. But, as \sig must have been produced with at least one credential
+  (extracted at step 7), then this credential is a forgery, breaking security
+  against one-more forgery of the \SBCM scheme.
+  %
+  \qed
+\end{proof}
+
+\begin{theorem}[Non-frameability of \CUASGen]
+  \label{thm:frame-uas}
+  If the underlying scheme for $\NIZK^{\Issue}$ is zero-knowledge, the schemes
+  for $\NIZK^{\Sign}$ are zero-knowledge and simulation-extractable, and the
+  commitment scheme is hiding, then our \CUASGen construction satisfies
+  non-frameability as defined in \defref{def:frame-uas}, except with negligible
+  probability.
+\end{theorem}
+
+\begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]
+  We prove that, given an adversary $\adv$ against non-frameability of
+  \CUASGen, we can build an adversary \advB that breaks the hiding property of
+  the underlying commitment scheme, with non-negligible probability.
+
+  We start from $G_0=\ExpNonframe$. $\adv$ makes queries to the oracles in
+  \Oframe. For $G_1$, within \Setup, we replace the \Setup algorithms for the
+  three NIZKs (\Issue, \Sign and \Open) with their corresponding \SimSetup
+  variants. Consequently, the corresponding queries to \Prove are also
+  simulated via the simulator. By the zero-knowledge property of the NIZK
+  systems, $G_1$ is indistinguishable from $G_0$. In the sequel, we build on
+  top of $G_1$, depending on whether or not a matching \Sig is found in \SIG,
+  in line 7.
+
+  \paragraph{(a) A matching \Sig exists in \SIG.} %
+  If we can find a matching \Sig in \SIG, for some \uid, then \adv~does not win
+  at line 7 of the game. Given that the signature is accepted by \Verify at line
+  3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
+  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, since the $(\yinsp,\iproof)$
+  pair output by \adv~is accepted by \Judge, simulation extractability of
+  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at line 9 pass.
+  Hence, the probability that the adversary wins at either lines 8 or 9 is $0$,
+  after simulation extractability of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.
+
+  \paragraph{(b) No matching \Sig exists in \SIG.} %
+  This means that \adv~creates an \UAS forgery. We leverage such an adversary
+  against $G_1$ to break the hiding property of the underlying commitment
+  scheme (see \appref{sapp:commitments}). For each new honest user \uid creation
+  request by \adv~(via \HUGEN),
+  \advB leverages its own $COM$ oracle to embed its challenges in the commitment
+  scheme into credentials of the \UAS non-frameability game. More precisely, in
+  calls to \HUGEN by \adv, \advB does not call \UKeyGen and instead picks two
+  random messages, $\msg_0^{\uid},\msg_1^{\uid}$, both from \AttrSpace. Whenever
+  a query to \OBTAIN is made by \adv~on behalf of \uid, \advB makes a call to
+  its $COM$ oracle, to get a commitment \Ccom for $\usk^{\uid}=\msg_b^{\uid}$
+  (for \advB's challenge bit $b$). Then,  \advB uses \Ccom in its \SBCMCom part
+  of the underlying \SBCM interactive signing protocol, and simulates the
+  corresponding $\NIZK^{\Issue}$ proof. Due to the zero-knowledge property, the
+  produced output is indistinguishable to that of the real execution. Similarly,
+  \advB can simulate the calls to the \SIGN and \OPEN oracles due to
+  simulation extractability of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.
+  %
+  Eventually, $\adv$ outputs a $(\oid,\siid,\Sig,\msg,\feval,\yinsp,\iproof)$
+  tuple that is accepted by \Verify and \Judge. Due to simulation extractability
+  of $NIZK^{\Sign}$, \ExtractSign must be able to produce a $(\usk,\scred,
+  \attrs_{\scred}, \tyeval^1,\yinsp')$ tuple. As, by assumption (line 6),  there
+  exists an \uid matching that \usk, all \advB has to do is find the
+  \uid for which \usk was used as either $\msg_0$ or $\msg_1$ in its hiding
+  game. Thus, \advB wins its hiding game with the same probability than \adv~
+  has to win the non-frameability game.
+  %
+  \qed
+\end{proof}
+
+\subsection{\CUASGen with Interactive Sign and Verify}
+\label{ssec:interactive-uas}
+
+\todo{The following was written for \GSAC. It should apply for \UAS, but check
+  and adapt.}
+
+In group signatures, the signing and verification process is non-interactive.
+That is, a group member produces a signature and eventually sends it to the
+verifier, who can check it without further interaction. Nevertheless, in
+anonymous credentials, this process is typically interactive, and consists of
+at least one round-trip. This can be useful, for instance, when some notion of
+freshness is necessary.
+
+The approach to turn our non-interactive singing-verification into an
+interactive protocol that ensures freshness is evident: prior to signing the
+message, we require that the honest verifier sends to the user a number picked
+uniformly at random from an appropriate domain, which must be concatenated to
+the signed message. If there is no need to actually sign a message, then the
+message is set to an empty string, and the user only signs the random number.
+%
+Syntactically, instead of having non-interactive $\sig \gets \Sign(\gpk,\usk,
+\cred,\dattrs,\msg)$ and $1/0 \gets \Verify(\gpk,\sig,\dattrs,\msg)$ algorithms,
+we have a $1/0 \gets \langle \Sign(\gpk,\usk,\cred,\dattrs),\Verify(\gpk,
+\dattrs) \rangle$ interactive protocol.
+%
+We sketch next a proof for why does this result in a secure \GSAC scheme with
+interactive signing and verification.
+
+\paragraph{Issuance Anonymity.} \todo{XXX}
+
+\paragraph{Signature Anonymity.} To see why the interactive variant is
+anonymous, assume an adversary $\adv$ against anonymity in that case. We build
+\advB against the non-interactive \ExpGSACSigAnonb from \adv~ as follows. \advB
+initializes
+everything as in the \ExpGSACSigAnonb game. When $\adv$ initiates a call to its
+interactive \SIGN (resp. \CHALb) oracle, \advB picks a random number, and sends
+it to the adversary, along with the response of its own (non-interactive) \SIGN
+(resp. \CHALb) oracle where, to the message passed as parameter to its oracle,
+concatenates the produced random number. After such simulation, \advB just
+outputs whatever $\adv$ outputs. Clearly, the simulation is perfect and, if
+$\adv$ wins with non-negligible probability in the interactive case, then so
+does \advB in the non-interactive case.
+
+\paragraph{Traceability.} The simulation described for the anonymity case (i.e.,
+\advB choosing the random numbers, and concatenating them to the message to be
+signed) applies here too. Thus, an adversary against traceability in the
+interactive case, can be used to build an adversary that breaks traceability in
+the non-interactive counterpart.
+
+\paragraph{Non-frameability.} The simulation described for the anonymity case
+(i.e., \advB choosing the random numbers, and concatenating them to the message
+to be signed) applies here too. Thus, an adversary against non-frameability in
+the interactive case, can be used to build an adversary that breaks
+non-frameability in the non-interactive counterpart.
 

### 2022-06-21 prism-backend/research/gsac/preliminaries-paper.tex
Beginning refurbishment of the paper.
Working on re-structure.

--- 2022-02-06 prism-backend/research/gsac/preliminaries.tex
@@
 
-\subsection{Related Work}
-\label{ssec:related}
+% [3 pages max; 1.5 prelim, 1.5 GSAC]
 
-\todo{\textbf{IMPORTANT!} There actually seems to be closely related work
-  on Attribute-Based Group Signatures (ABGS): \cite{khad07,emo09,aa14}.}
+\subsection{Cryptographic Building Blocks}
+\label{ssec:cryptobblocks}
 
-\subsection{Building Blocks}
-\label{ssec:bblocks}
+Next we introduce the main building blocks we will be using in our
+constructions. More detailed definitions and references appear in
+\appref{app:crypto-building-blocks}.
+
+\paragraph{Digital Signatures.} %
+Defined as a tuple (\SSetup,\SKeyGen,\SSign,\SVerify). Algorithm $\parm \gets
+\SSetup(\secpar)$ produces public parameters for the other algorithms.
+$(\vk,\sk) \gets \SKeyGen(\parm)$ generates the verification-signing key
+pair, algorithm $\sig \gets \SSign(\sk,\msg)$ signs message \msg with
+signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\vk,
+\sig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
+verification key \Svk. We rely on existentially unforgeable digital signature
+schemes.
+
+\paragraph{Public-Key Encryption.} %
+Defined as a tuple (\ESetup,\EKeyGen,\EEnc,\EDec). Algorithm $\parm \gets
+\ESetup(\secpar)$ produces public parameters for the other algorithms.
+$(\ek,\dk) \gets \EKeyGen(\parm)$ generates the encryption-decryption key
+pair, algorithm $\Ec \gets \EEnc(\ek,\msg)$ encrypts message \msg with
+encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\dk,
+\Ec)$ decrypts ciphertexts using decryption key \Edk. We rely on IND-CCA
+public-key encryption schemes.
+
+\paragraph{(Block) Commitment Schemes.} %
+Defined as a tuple (\CSetup,\CCommit). Algorithm $\parm \gets
+\CSetup(\secpar)$ produces the parameters for committing to values. $\Ccom
+\gets \CCommit(\parm, \smsg; r)$ produces a commitment \Ccom over a set of
+messages \smsg, using randomness $r$ (which we may omit when explicitly
+stating it is not necessary). We will further use commitment schemes that
+allow committing to vectors of messages. Therein, the \CCommit algorithm simply
+receives a block of messages. In both cases, we require hiding and binding
+(block) commitment schemes.
+
+\paragraph{Non-Interactive Zero-Knowledge.} %
+We use non-interactive zero-knowledge proofs of knowledge (NIZK), in the CRS
+model. Informally, a NIZK scheme over an NP relation \NIZKRel is defined as a
+tuple ($\NIZKSetupRel$,$\NIZKProveRel$,$\NIZKVerify^\NIZKRel$).
+Algorithm $\NIZKcrs \gets \NIZKSetupRel(\NIZKsecpar)$ produces the common
+reference string \NIZKcrs. $\NIZKproof/\bot \gets \NIZKProveRel(\NIZKcrs,
+\NIZKx,\NIZKw)$ creates a NIZK proof of knowledge of witness \NIZKw for \NIZKx
+such that $(\NIZKw,\NIZKx) \in \NIZKRel$. $1/0 \gets \NIZKVerifyRel
+(\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof. Within NIZK systems, we
+further need schemes that provide simulation-extractability, which in a nutshell
+means that no adversary can produce a proof from which we cannot extract a
+witness, even after seeing polynomially many simulated proofs. To model
+simulation-extractable NIZKs, we further need algorithms \NIZKSimSetup,
+\NIZKSim, and \NIZKExtract, that allow simulating proofs and extracting
+witnesses. The properties we build on are completeness, soundness,
+zero-knowledgeness, and simulation-extractability.
+
+\paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
+We use signature schemes that allow signing blocks of messages, or commitments
+to blocks of messages, and which are furthermore compatible with (efficient)
+proof systems over the produced signature and signed (commitments to) messages.
+For this purpose, we define such schemes as a tuple (\SBCMSetup,\SBCMKeyGen,
+\SBCMCom,\SBCMSign,\SBCMVerify). Algorithm $\parm \gets \SBCMSetup(\secpar)$
+produces the public parameters for the scheme. %
+$(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing
+key pair. $\sig/\bot \gets\langle \SBCMCom(\vk,\overline{\smsg},\smsg),
+  \SBCMSign(\sk,\smsg) \rangle$ is an interactive protocol between a user, who
+runs \SBCMCom and has a set of messages $\overline{\smsg}$ to be block-committed,
+and a signer, who owns signing key \sk; both also receive common input a
+block of messages \smsg. The output of the protocol is a signature over
+$\overline{\smsg} \cup \smsg$. Algorithm $1/0 \gets \SBCMVerify(\vk,
+\sig,\overline{\smsg},\smsg)$ verifies a signature \sig over message set
+$\overline{\smsg} \cup \smsg$. In addition, the
+produced signatures must be compatible with (efficient) NIZK proofs of knowledge
+of a signature, and of (arbitrary) claims over the signed (committed) messages.
+An \SBCM scheme must provide one-more-forgery type of security.
+
+\subsection{Notation}
+\label{ssec:notation}
+
+We follow common notation habits. $y \gets A(x)$ means that algorithm $A$, on
+input $x$, produces output $y$. When $A$ is a probabilistic process, and we want
+to make explicit the randomness $r$, we use $y \gets A(x;r)$. $\langle y_A,y_B
+\rangle \gets \langle A(x_A),B(x_B)\rangle$ denotes algorithms $A$ and $B$,
+running an interactive protocol, where $A$ receives $x_A$ as input and produces
+$y_A$ as output, and $B$ receives $x_B$ and produces $y_B$.
+%
+Our generic constructions rely on the previously defined building blocks, which
+share common (but different)
+tokens: e.g., we will resort to several NIZK proofs instances. To distinguish
+them, we may use subscripts or superscripts: e.g., $\NIZKRel_A$ denotes the
+NP relation used within some algorithm $A$, $\NIZKSetupRel$ means that
+the setup algorithm of an underlying NIZK system is performed associated to
+relation $\NIZKRel$; $\SBCMparm$ are the public parameters for an \SBCM scheme,
+and $\Eparm$ are the public parameters for an encryption scheme. Variables
+written in bold font denote sets, e.g., while we use \ipk to denote a single
+issuer public key, \sipk denotes a set of issuer's public keys. To refer to
+a specific element of a set, we use subindexes, e.g., $\sipk_i$ is the $i$-th
+\ipk within \sipk.
+%
+We also assume the existence of a well defined attribute space over which
+issuers in our schemes can issue credentials on. We denote this set with
+\AttrSpace.
 
@@
 %%% mode: latex
-%%% TeX-master: "gsac"
+%%% TeX-master: "uas-paper"
 %%% End:

### 2022-06-21 prism-backend/research/gsac/relationships.tex
Beginning refurbishment of the paper.
Working on re-structure.

--- 2022-06-18 prism-backend/research/gsac/conclusion-paper.tex
@@
-\section{Conclusion}
-\label{sec:conclusion}
+\section{Relationships with Other Schemes}
+\label{sec:relationships}
 
-[1 page max]
+% [11 pages max]
+
+In the following subsections we reproduce models of related schemes in the
+literature. Then, we give concrete \fissue, \feval and \finsp functions that
+make \UAS mimic their functionality. Finally, we prove for each case that
+\UAS -- restricted with the corresponding functions -- indeed meets their
+security models, thus proving that \UAS is a generalization of all of them.
+
+\subsection{Group Signatures}
+\label{sapp:related-models-gs}
+
+We adopt the model in \cite{bsz05}. In this abstraction
+of group signatures, the opener returns an index uniquely identifying the group
+member that created a signature, along with a correctness proof. For ease of
+exposition, assume that, w.l.o.g., this index is just the public key that the
+group member chooses when joining the group\footnote{The user public key is
+  assumed to be accessible from a public table in \cite{bsz05}, so it is direct
+  to translate the public key into an index, if needed.}. A group signature
+scheme, according to \cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign,
+\Verify, \Open and \Judge algorithms, as well as an $\langle\Obtain,\Issue
+\rangle$ interactive protocol. Their description is very similar to that of
+\GSAC, so we refer to \cite{bsz05} for detailed descriptions. For ease of
+reference, we replicate the security games in \figref{fig:model-gs}.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.45\textwidth}        
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gs}(1^\secpar)$}{%
+        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
+        d \gets \adv^{\mathcal{O}^{anon}}(\gpk,\isk) \\
+        \pcreturn d 
+      }
+
+      \vspace*{5em}
+
+      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gs}(1^\secpar)$}{%
+        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
+        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
+        (\gpk,\osk,\isk) \\
+        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
+        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
+        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
+        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
+        GSig(\PRVUK[\upk],\msg) \\
+        \pcreturn 0
+      }       
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.55\textwidth}
+      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gs}(1^\secpar)$}{%
+        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
+        (\msg,\sig) \gets \adv^{\mathcal{O}^{trace}}(\gpk,\osk) \\
+        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
+        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
+        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
+        = 0: \\ 
+        \pcind \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for group signatures \cite{bsz05}, only with minor    
+    ``harmless'' edits to compare easier with \CUASGS. Concretely, since we
+    output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
+    $\upk \notin \HU \cup \CU$. For the oracles' definitions, check the
+    referenced paper.
+    $\mathcal{O}^{anon} \gets \lbrace Ch,Open,SndToU,WReg,USK,CrptU \rbrace$,
+    $\mathcal{O}^{trace} \gets \lbrace SndToI,AddU,RReg,GSig,USK,CrptU \rbrace$,
+    and $\mathcal{O}^{frame} \gets \lbrace SndToU,WReg,GSig,USK,CrptU \rbrace$.
+  }
+  \label{fig:model-gs}  
+\end{figure}
+
+\subsubsection{\CUASGS construction.} %
+We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
+construction for \UAS, restricted to $\fissue^1$ as issuance function,
+$\feval^0$ as signature evaluation function, and $\finsp^{\upk}$ as opening
+function, is a secure group signature scheme according to the \cite{bsz05}
+model. We first quickly define the algorithms, and then prove security.
+
+\begin{description}
+\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
+  of \CUASGen, and one instance of \IKeyGen and \OKeyGen. Assigns the public
+  keys to \gpk.
+\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \UKeyGen from \CUASGen, and
+  computes $\CCommit(\usk;0)$ as \upk.
+\item[$\langle \cred,\utrans \rangle \gets
+  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
+  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Note that, to
+  constraint to only one credential per user, it suffices to require the user
+  to prove that the ``randomness'' it uses when committing to its private key
+  is actually $0$, and check whether the received commitment has been seen
+  before. For details, see the BBS+ instantiation of the underlying \SBCM
+  building block in \secref{sapp:sbcm}.
+\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
+  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen.
+  Simply returns \sig.
+\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
+  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
+  outputs.
+\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
+  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
+  0,\msg,\feval^0)$. Note that, internally, the latter call to \Open runs
+  $\finsp^{\upk}$, where $\upk = \CCommit(\usk;0)$, just as proved in $\langle
+  \Obtain,\Issue\rangle$.
+\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
+  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
+  0,\msg)$.
+\end{description}
+
+\paragraph{Security of \CUASGS.} %
+We prove that our \CUASGS construction is a secure group signature scheme,
+according to \cite{bsz05}, if the underlying \CUASGen construction is secure.
+
+\begin{theorem}[Anonymity of \CUASGS]
+  If the base \CUASGen construction is anonymous according to
+  \defref{def:anonymity-uas}, then \CUASRing is an anonymous group signature
+  scheme.
+\end{theorem}
+
+\todo{Introducing $(f,g,h)-\CUASGen$ naming convention. Describe it elsewhere.}
+
+\begin{proof}
+  Assume an adversary \adv~ against anonymity in \CUASGS. This directly leads
+  to an adverary \advB against anonymity of the $(\fissue^1,\feval^0,
+  \finsp^{\upk})-\CUASGen$ instance.
+
+  Concretely, observe that calls to \adv's $Ch,Open,SndToU,WReg,USK,CrptU$
+  oracles can be directly simulated by calls to \advB's oracles $\CHALb,
+  \OPEN,\HUGEN,\WREG,\CUGEN$ oracles. Thus, if \adv~ guesses its bit $b$
+  with non-negligible probability, this directly leads to a non-negligible
+  probability of guessing \advB's challenge bit.
+  \qed
+\end{proof}
+
+\begin{theorem}[Traceability of \CUASGS]
+  If the base \CUASGen construction has unforgeable signing according to
+  \defref{def:sign-forge-uas}, then \CUASGS is a traceable group signature
+  scheme.
+\end{theorem}
+
+\begin{proof}
+  Assume an adversary \adv~ against traceability in \CUASGS. We build an
+  adversary \advB against sign unforgeability of the $(\fissue^1,\feval^0,
+  \finsp^{\upk})-\CUASGen$ instance.
+
+  \advB's simulation of \adv~ environment is as in the proof for anonymity
+  of \CUASGS. \advB simply outputs whatever \adv~ outputs in line 2 of its
+  traceability game. Note that, as \CUASGS is a specific instantiation of
+  \CUASGen, whenever \CUASGS accepts a signature, so does \CUASGen. Concretely,
+  assume that \adv~ wins the traceability game in \figref{fig:model-gs} with
+  $\upk \notin \HU \cup \CU$ at line 5. This implies that the check at line 11
+  of the sign unforgeability game (\figref{fig:exp-uas-unfor-sign}) for \CUASGen
+  outputs $0$ for all known {\uid}s. Similarly, if \adv~ wins the traceability
+  game with condition $\Judge(\dots)=0$ at line 5, then \advB wins its sign
+  unforgeability game with the corresponding check at line 6 in
+  \figref{fig:exp-uas-unfor-sign}.
+  %
+  \qed
+\end{proof}
+
+\begin{theorem}[Non-frameability of \CUASGS]
+  If the base \CUASGen construction is non-frameable according to
+  \defref{def:frame-uas}, then \CUASGS is a non-frameable group signature
+  scheme.
+\end{theorem}
+
+\begin{proof}
+  Assume an adversary \adv~ against non-frameability in \CUASGS. We build an
+  adversary \advB against non-frameability of the $(\fissue^1,\feval^0,
+  \finsp^{\upk})-\CUASGen$ instance.
+
+  \advB's simulation of \adv~ environment is as in the proof for anonymity
+  of \CUASGS. \advB simply outputs whatever \adv~ outputs at line 2 of its
+  game. Observe that a winning condition for \adv~ directly implies a winning
+  condition for \advB. Concretely, if $\upk \in \HU \land \PRVUK[\upk] \neq
+  \bot$ in \adv's game, then $\exists \uid \in \HU~\suchthat~\UK[\uid]=\usk$
+  for \advB (line 6 of its game). Similarly, if \Judge returns $1$ in \adv's
+  game, \advB's \Judge also returns $1$ at line 4. Finally, if \adv~ does not
+  corrupt the owner of \upk, then $\uid \in \HU$ in \advB's game, and if \adv
+  does not query its $SIGN$ oracle, then there does not exist a matching entry
+  in $\SIG[\uid]$ for \advB either. Consequently, as stated, \advB wins its
+  non-frameability every time that \adv does.
+  \qed
+\end{proof}
+
+\subsection{Group Signatures with Message Dependent Opening}
+\label{sapp:related-models-gsmdo}
+
+We cannot build the exact same functionality, nor follow the exact same security
+model as in the group signatures with message dependent opening (GS-MDO) scheme
+described in \cite{ehk+19}. Simply because, therein, the opening functionality
+is divided in two authorities: the admitter, who decides which messages are
+subject to be opened or not, and generates a token that enables opening
+signatures over such messages; and the opener, who performs the actual opening,
+but cannot do it without the tokens generated by the admitter. Intuitively, this
+can be seen as a sort of ``distribution'' of the opening capability. We define
+a variant of this model in which the admitter and opener are combined back into
+one entity (the opener), who can only open signatures over predefined messages,
+but cannot open any other signature. Moreover, our variant directly supports the
+scenario of multiple such openers, each being able to open only signatures
+over different messages. Note that it would not be hard to apply thresholding
+techniques to extend this case so that our ``unified'' opener role is shared
+across multiple entities, who have to cooperate in order to open a signature
+\needcite, thus achieving something very close ``in spirit'' to the scheme in
+\cite{ehk+19}. In addition, while \cite{ehk+19} follows the static group
+signature setting, we move to the dynamic one. Informally, our variant of GS-MDO
+is composed of the following algorithms: \Setup,
+\IKeyGen, \OKeyGen, \UKeyGen, \Sign, \Verify, \Open; as well as the $\langle
+\Obtain, \Issue \rangle$ interactive protocol. \OKeyGen generates an opening
+key pair which is already configured to open signatures only over some fixed
+(but arbitrary) set of messages. The remaining algorithms are as usual, so we
+defer a more detailed description to the construction. The oracles are the same
+as in \UAS. The resulting security model is given in \figref{fig:model-gsmdo},
+which we adapt from \cite{ehk+19}.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.45\textwidth}        
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gsmdo}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets \IKeyGen(\parm) \\
+        b^* \gets \adv^{\mathcal{O}^{anon}}(\parm,\ipk) \\
+        \pcreturn b^*
+      }
+
+      \vspace*{5em}
+
+      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gsmdo}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets \IKeyGen(\parm) \\
+        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
+        (\ipk,\isk) \\
+        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
+        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
+        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
+        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
+        GSig(\PRVUK[\upk],\msg) \\
+        \pcreturn 0
+      }       
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.55\textwidth}
+      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gsmdo}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets \IKeyGen(\parm) \\
+        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{trace}}
+        (\ipk,\opk,\osk) \\
+        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
+        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
+        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
+        = 0: \\ 
+        \pcind \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for our GS-MDO variant.
+    $\mathcal{O}^{anon} \gets \lbrace \OGEN^{\smsg},\HUGEN,\CUGEN,\WREG,
+    \OBTAIN,\SIGN,\OPEN,\CHALb \rbrace$; $\mathcal{O}^{trace} \gets \lbrace
+    \OGEN,\HUGEN,\CUGEN,\ISSUE,\OBTISS,\RREG,\SIGN \rbrace$;
+    $\mathcal{O}^{frame} \gets \lbrace \OGEN,\HUGEN,\CUGEN,\WREG,
+    \OBTAIN,\SIGN \rbrace$. $\OGEN^{\smsg}$ is like \OGEN, but only accepting
+    functions of type $\finsp^{\smsg}$.
+  }
+  \label{fig:model-gsmdo}  
+\end{figure}
+
+\subsubsection{\CUASGSMDO construction.} %
+We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
+construction for \UAS, restricted to $\fissue^1$ as issuance function,
+$\feval^0$ as signature evaluation function, and $\finsp^{\smsg}$ as opening
+function, is a secure group signature scheme with message dependent opening
+as modelled in \figref{fig:model-gsmdo}. We first quickly define the algorithms,
+and then prove security.
+
+\begin{description}
+\item[$\parm \gets \Setup(1^\secpar)$.] Like in vanilla \CUASGen.
+\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Like the \UKeyGen function for
+  \CUASGS, in \secref{sapp:related-models-gs}.
+\item[$\langle \cred,\utrans \rangle \gets
+  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Like the corresponding
+  protocol in in vanilla \CUASGS, \secref{sapp:related-model-gs}.
+\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Like in vanilla \CUASGen, limited
+  on evaluation functions $\feval^0$ and opening functions $\finsp^{\smsg}$.
+\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Like in vanilla \CUASGen.
+\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Like in vanilla
+  \CUASGen.
+\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Like in vanilla \CUASGen.
+\end{description}
+
+\paragraph{Security of \CUASGSMDO.} %
+Our \CUASGSMDO construction is a secure group signature scheme,
+according to the model in \figref{fig:model-gsmdo}, if the underlying \CUASGen
+construction is secure.
+
+Note that both  model construction are essentially restrictions to the model
+and construction of \CUASGen. Thus, security directly follows from security of
+\CUASGen.
+
+% \begin{theorem}[Anonymity of \CUASGSMDO]
+%   If the base \CUASGen construction is anonymous according to
+%   \defref{def:anonymity-uas}, then \CUASGSMDO is an anonymous group signature
+%   scheme.
+% \end{theorem}
+
+% \begin{proof}
+
+%   \qed
+% \end{proof}
+
+% \begin{theorem}[Traceability of \CUASGSMDO]
+%   If the base \CUASGen construction has unforgeable signing according to
+%   \defref{def:sign-forge-uas}, then \CUASGSMDO is a traceable group signature
+%   scheme.
+% \end{theorem}
+
+% \begin{proof}
+%   Traceability follows directly from the corresponding proof for \CUASGS.
+%   \qed
+% \end{proof}
+
+% \begin{theorem}[Non-frameability of \CUASGSMDO]
+%   If the base \CUASGen construction is non-frameable according to
+%   \defref{def:frame-uas}, then \CUASGSMDO is a non-frameable group signature
+%   scheme.
+% \end{theorem}
+
+% \begin{proof}
+%   Non-frameability follows directly from the corresponding proof for \CUASGS.
+%   \qed
+% \end{proof}
+
+\subsection{Ring Signatures}
+\label{sapp:related-models-rs}
+
+We adopt the model in \cite{bkm06}, where security of ring signatures is
+defined according to the games in \figref{fig:model-rs}. A ring signature
+scheme consists of three algorithms $(KeyGen,Sign,Verify)$. Roughly,
+$((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar)$ produces $n$
+signing key pairs, $\sig \gets Sign(\sk_i,R,\msg)$ creates a signature for
+anonymity set $R \subseteq \lbrace \pk_1, \dots, \pk_t \rbrace$, using secret
+key $\sk_i$, associated to some $\pk_i \in R$; and $1/0 \gets Verify(R,\sig,
+\msg)$ checks if \sig is a valid signature over \msg for ring $R$.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.55\textwidth}        
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
+        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
+        (i_0,i_1,R,\msg,\st) \gets \adv^{SIGN}(\pk_1,\dots,\pk_n) \\
+        \pcif % R \not\subseteq \lbrace [n] \rbrace \lor
+        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \notin R \lor %\\
+        i_0 = i_1: \pcreturn \bot \\
+        \sig \gets Sign(\sk_{i_b},R,\msg)) \\
+        b^* \gets \adv(\sig,\st) \\
+        \pcreturn b^*
+      }        
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.5\textwidth}
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
+        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
+        (R,\sig,\msg) \gets \adv^{SIGN,CORR}(\pk_1,\dots,\pk_n) \\
+        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
+        \pcreturn 1~\pcif R \subseteq [n] \setminus CU = \emptyset~\land \\
+        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg) \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for ring signatures \cite{bkm06}. The SIGN oracle
+    accepts a $(i,R,\msg)$ tuple, where $pk_i$ must be part of $R$, and
+    returns $\sig \gets Sign(\sk_i,R,\msg)$. The oracle $CORR$ accepts an
+    index $i$, and lets $\adv$ learn $\sk_i$. Corrupted user indexes are
+    added to list $CU$.}
+  \label{fig:model-rs}  
+\end{figure}
+
+Intuitively, a ring signature scheme $rs$ is anonymous if, for every p.p.t.
+\adv, $|\Pr[\Exp^{anon-1}_{\adv,rs}(1^\secpar)] = 1| -
+|\Pr[\Exp^{anon-1}_{\adv,rs}(1^\secpar)] = 0|$ is a negligible function of
+$1^\secpar$; and a ring signature scheme $rs$ is unforgeable if, for every
+p.p.t. \adv, the probability that $\Exp^{forge}_{\adv,rs}(1^\secpar)$ returns
+$1$ is also negligible in $1^\secpar$. For short, we say that a ring signature
+scheme meeting both anonymity and unforgeability as specified above, is a secure
+ring signature scheme.
+
+\subsubsection{\CUASRing Construction.} %
+We show that, as specified in \secref{ssec:uas-ring}, our \CUASGen construction
+for \UAS, with alternative NIZK relationship $\NIZKRel_{\Sign-prv}$ for signing,
+issuance function $\fissue^{\sring}$, signature evaluation function
+$\feval^{\attrs}$, and inspection function $\finsp^0$, is a secure ring
+signature scheme. Thus, in this section, when we write \CUASGen, we refer to
+its specific variant built from the previous modifications.
+
+\begin{description}  
+\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in \CUASGen, but using
+  $\NIZKRel_{\Sign-prv}$ instead of $\NIZKRel_{\Sign}$.  
+\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] As in \CUASGen, using
+  $\fissue^{\sring}$.  
+\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp).$] As in \CUASGen, where every
+  opener that wants to be a valid opener in \CUASRing, needs to set \finsp to
+  $\finsp^0$.  
+\item[$\usk \gets \UKeyGen(\parm).$] Can only be run after \IKeyGen. Let 
+  $\usk \gets \isk$.
+\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
+  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
+  The user picks a ring from an (publicly) available list of issuers (users),
+  i.e. $\sring \gets \lbrace \ipk_i \rbrace_{i \in [t]}$, for some $t$. Then,
+  runs the $\langle \Obtain,\Issue \rangle$ protocol as in \CUASGen, acting both
+  as user and as issuer, and using $\fissue^{\sring}$ as issuance function.
+  \attrs are the public keys of the users (issuers) to be included in the ring.
+\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval).$] As in
+  \CUASGen, using $\feval^{\attrs}$ as sign evaluation function, using
+  as credential for signing the credential obtained in the desired $\langle
+  \Obtain,\Issue \rangle$ session and, as \opk, any previously registered \opk
+  (i.e., such that $\finsp=\finsp^0$).
+\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in \CUASGen.
+  Note that $\sipk = \sring$, and $\feval=\feval^{\attrs}$.
+\item[$\Open$ and $\Judge$.] As in \CUASGen. Note that $\finsp=\finsp^0$.
+\end{description}
+
+\todo{I guess we need to show that changing the NIZK for signing does not affect
+  security. This leads to ``What are the conditions that need to be checked/cannot
+  be altered in the default NIZK sign, that make \CUASGen secure?'' }
+
+\paragraph{Security of \CUASRing.} %
+We prove that our \CUASRing construction is anonymous and unforgeable, if
+the underlying \CUASGen construction is secure.
+
+\begin{theorem}[Anonymity of \CUASRing]
+  If the base \CUASGen construction is anonymous according to
+  \defref{def:anonymity-uas}, then \CUASRing is an anonymous ring signature
+  scheme.
+\end{theorem}
+
+\begin{proof}
+  Assume $\adv$ is an adversary against ring signature anonymity for \CUASRing.
+  Then, we build \advB against anonymity of \CUASGen. Concretely, \advB first
+  generates $n$ keypairs by running its \IGEN (with $\fissue^{\sring}$) and
+  \HUGEN oracles, and runs \OGEN at least once (with $\finsp^0$). Then, invokes
+  $\adv$ passing as public keys the public keys of the $n$ generated issuers
+  (users in \CUASRing). $\adv$'s $SIGN(i,R,\msg)$ queries are processed as
+  follows. If user $i$ has not yet produced a credential for ring $R$, \advB
+  makes a call to its \OBTAIN oracle, using $R$ as attribute set. If such a
+  credential was already produced, then reuse it. Then, \advB uses the
+  corresponding user and credential identifiers as parameters to a query to its
+  own \SIGN oracle (specifying $\feval^{\attrs}$ as signature evaluation
+  function). Eventually, $\adv$ outputs two user indexes, a ring $R$, and
+  message \msg. If the checks at line 4 of \figref{fig:model-rs} pass, \advB
+  generates the challenge signature by calling its own \CHALb oracle, and passes
+  the result to $\adv$. Finally, \advB outputs whatever $\adv$ outputs.
+  %
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability of \CUASRing]
+  If the base \CUASGen construction is non-frameable according to
+  \defref{def:frame-uas}, then \CUASRing is an unforgeable ring signature
+  scheme.
+\end{theorem}
+
+\begin{proof}
+  Assume $\adv$ against unforgeability of \CUASRing wins the game. We build
+  \advB winning the non-frameability game of \CUASGen with the same probability.
+  %
+  \advB prepares the environment as the adversary \advB against anonymity,
+  and answers \adv's queries to the $SIGN$ oracle also as in the anonymity
+  proof. To answer \adv's queries to its $CORR$ oracle, \advB leverages the
+  \ICORR oracle in the non-frameability game for \UAS. Finally, \advB outputs
+  whatever $\adv$ outputs.
+
+  Note that, if $\adv$ wins its game, it means that the public keys of the
+  issuers in $R$ all belong to uncorrupted users. Since the signature is
+  accepted by $Verify$ at line 3 of the ring signature unforgeability game,
+  there exists some \uid with an \usk matching the check at line 6 in the
+  non-frameability game. Moreover, since $\adv$ never queried its $SIGN$
+  oracle, then by construction there cannot exist a matching entry in the
+  $\SIG[\uid]$ table. Thus, \advB wins the non-frameability game whenever
+  $\adv$ wins its unforgeability game. Since \CUASGen is non-frameable, then
+  this probability must be negligible.
+  %
+  \qed
+\end{proof}
+
+\subsection{Anonymous Credentials}
+\label{sapp:related-models-ac}
+
+We adopt the model in \cite{fhs19}, where security of anonymous credentials
+(with selective disclosure). Therein, an anonymous credential scheme is
+defined via $OrgKeyGen$ (which we rename to $IssKeyGen$, and $UserKeyGen$
+algorithms (roughly equivalent to
+\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
+interactive protocols. The issuance interactive protocol is equivalent to
+the issuance protocol in \UAS. Similarly, $Show,Verify$ is equivalent to
+the interactive extension of \Sign and \Verify in \UAS, which we show how
+to build in \secref{ssec:variants-gsac} (for \GSAC, but the case for \UAS is
+equivalent). The security definitions rely on $HU, CU, ObtIss, Obtain, Issue,
+Show$, and $LoR$ oracles, which are essentially equivalent to our \HUGEN,
+\CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb oracles. We refer to
+\cite{fhs19} for the full details. For ease of reference, we summarize the
+security definitions in \cite{fig:model-ac}, with inocuous adaptations to
+make them more suitable for comparison with our definitions.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.5\textwidth}        
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
+        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
+        \pcreturn b^*
+      }        
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.5\textwidth}
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
+        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
+        \langle \cdot,(b,\utrans) \rangle
+        \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
+        \pcif b = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
+        \land D \subseteq \ATTR[j]): \\% \forall j, \OWNR[j] \in \CU
+        % \implies D \not\subseteq \ATTR[j]: \\
+        \pcind \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for anonymous credentials with selective disclosure
+    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
+    \secref{ssec:model-uas}.}
+  \label{fig:model-ac}  
+\end{figure}
+
+\subsubsection{\CUASAC Construction.} %
+We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
+construction for \UAS, restricted to $\fissue^1$ as issuance function,
+$\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as opening
+function, is a secure anonymous credential scheme according to the \cite{fhs19}
+model. We first quickly define the algorithms, and then prove security. Note
+that, for better alignment with \UAS, we add a common setup process which is
+part of $IssKeyGen$ in \cite{fhs19}. The change is inocuous functionality- and
+security-wise, though.
+
+\begin{description}
+\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
+    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
+    construction. Returns $\parm \gets (\parm',\opk)$.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
+  \CUASGen construction, setting $\fissue^1$ as issuance function.
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
+  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
+\item[$\langle \cred/\bot,\top/\bot \rangle \gets
+  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
+  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
+  $\fissue^1$ as issuance function.
+\item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
+  \gets \langle Show(\ipk,\attrs,\dattrs,
+  \cred),\Verify(\ipk,\dattrs) \rangle$.]
+  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
+  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
+  open function, with \opk from \parm as opener public key.
+\end{description}
+
+\paragraph{Security of \CUASAC.} %
+We prove that \CUASAC is an anonymous and unforgeable anonymous credential
+scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
+is anonymous and has unforgeable signing. Note that issuance unforgeability
+of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
+leveraging other credentials not any fixed custom issuance policy. Thus,
+signature unforgeability from \UAS is enough. Note that AC schemes modelled
+as in \cite{fhs19} do not have issuance anonymity, as the user public key
+is passed to the issuer.
+
+\begin{theorem}[Anonymity of \CUASAC]
+  \label{thm:anon-cuasac}
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
+  according to \cite{fhs19}.
+\end{theorem}
+
+\begin{proof}
+  Given \adv~ against anonymity of \CUASAC as defined in \cite{fhs19}, we build
+  an adversary \advB against anonymity of \CUASGen as defined in
+  \defref{def:sign-anonymity-uas}.
+
+  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
+  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR$, \advB redirects to
+  \HUGEN,\CUGEN,\OBTAIN,\SIGN,\CHALb, respectively. Note that ``translating''
+  the inputs from the former into inputs for the latter is trivial.
+  Obviously, if \adv~ wins in its anonymity game, then so does \advB with the
+  same probability.
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability of \CUASAC]
+  \label{thm:forge-cuasac}
+  If the base \CUASGen construction has sign unforgeability according to
+  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
+\end{theorem}
+
+\begin{proof}
+  Given \adv~ against unforgeability of \CUASAC as defined in \cite{fhs19}, we
+  build an adversary \advB against sign unforgeability of \CUASGen as defined in
+  \defref{def:sign-forge-uas}.
+
+  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
+  that \adv~ wins its game. Note that, since $b=1$ in line 5 of the
+  unforgeability game of \figref{fig:model-ac}, then by construction, \Verify
+  also returns $1$ in the sign unforgeability game of \UAS. In addition, if
+  there is no corrupt user with a credential containing $D$, then this leads to
+  \advB winning at line 9 in \figref{fig:exp-uas-unfor-sign}, as no credential
+  owned by a corrupt user that can be extracted can make the $\feval^{\dattrs}$
+  function output $\yeval^0=D$. Thus, \advB wins with the same probability as
+  \adv~ does.  
+  %
+  \qed
+\end{proof}
+
+\subsection{Delegatable Anonymous Credentials}
+\label{sapp:related-models-dac}
+
+We give a simple definition for a Delegatable Anonymous Credentials (DAC)
+scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
+our simple scheme built from \CUASGen does not ensure privacy of the delegation
+chain -- which could be achieved by making \feval output projective proofs like
+in \cite{bcc+09}, but since our goal is to showcase the feasibility of building
+DAC from \UAS, we leave that out for brevity. Our simple scheme does, however,
+ensure that a (not top-level) issuer can only delegate attributes contained in a
+credential it owns. Also, for simplicity, we restrict to the case of using one
+credential per signature/interactive credential presentation, and assume that
+all parties use the same opener and \finsp function.
+%
+The functionality is thus defined as in \appref{sapp:related-models-ac}, i.e.,
+we have $Setup$, $IssKeyGen$ and $UserKeyGen$ algorithms, and $\langle Obtain,
+Issue \rangle$ and $\langle Show,Verify \rangle$ interactive protocols.
+%
+In the modelling for this setting, since there are multiple issuers, in addition
+to the oracles in \appref{sapp:related-models-ac}, we use $HI$ and $CI$ oracles,
+equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
+issuers, and corrupt existing ones, respectively. The issuance and sign
+anonymity properties are as before. For unforgeability, we still require
+that no adversary can authenticate using a set of attributes that have not been
+issued to a corrupt user. In addition, we require that for any possible
+successful authentication protocol using a level-$n$ credential, we can extract
+a chain of credentials of length $n$ such that each level-$i$ credential can
+be used successfully to authenticate a level-$(i+1)$ credential up to the
+level-$n$ credential, and that the attributes revealed in the level-$n$
+authentication are contained in all the credentials up the chain.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.45\textwidth}
+      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
+        \pccomment{Abort if challenge creds belong to} \\
+        \pccomment{users with different delegation chains} \\
+        \pcreturn b^*
+      }
+      \vspace*{0.5em}
+
+      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
+        \pccomment{Abort if challenge sigs belong to} \\
+        \pccomment{users with different delegation chains} \\
+        \pcreturn b^*
+      }        
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.55\textwidth}
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (D=(n,D'),\ipk_n,\st) \gets
+        \adv^{\mathcal{O}_{forge}}(\parm) \\
+        \langle\cdot,(b,\utrans)\rangle \gets
+        \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
+        \pcif b = 0: \pcreturn 0 \\
+        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
+        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
+        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
+        \gets ExtractChain(\utrans) \\ 
+        \pcif \exists i \in [1,n]~\suchthat~
+        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
+        \pcind D' \not\subseteq \ATTR[\iid]) \land
+        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
+        \pcind \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for delegatable anonymous credentials with selective
+    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
+    CU,HI,CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon}
+    \gets \lbrace HU,CU,HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$.
+    $\mathcal{O}_{forge} \gets \lbrace HU,CU,HI,CI,Obtain,ObtIss,Issue,Show
+    \rbrace$. $IssLor$ is equivalent to \OBTCHALb in \UAS, whereas $SigLor$ is
+    equivalent to \CHALb. Also, \OWNR and \ATTR tables are essentially as in
+    \secref{ssec:model-uas}. $\ISR[\ipk]$, in this case, returns the identifier
+    of the issuer with public key \ipk. With $D =
+    (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
+    which denotes the level of the credential used for authentication.}
+  \label{fig:model-dac}  
+\end{figure}
+
+\subsubsection{\CUASDAC Construction.} %
+In a delegatable AC (DAC) scheme, all users are (or may be) also issuers. We
+only distinguish between top-level issuers, who have level $n=0$, and
+lower-level issuers, who have level $n>0$. In our \CUASDAC scheme, we assume
+that the first attribute (after the user's secret key) encodes the level of
+the credential. That is, $\attrs_1=n$, for a credential of level $n$. In
+addition, all users (i.e., with $n>0$) who want to delegate have to publicly
+list:
+
+\begin{enumerate}
+\item The level $n$ of the credential they delegate.
+\item Their public key \ipk.
+\item An \UAS signature proving knowledge of a credential of level $n$, and over
+  the attributes that this level-$n$ issuer is delegating.
+\item The \ipk of the parent issuer.
+\item The $\fissue^{n,\dattrs}$ function they will require for delegating.
+\item An $\feval^{n,\dattrs}$ function used to produce the signature at item 2.
+\end{enumerate}
+
+We assume that, from an \ipk, it is possible to find the corresponding issuer
+(e.g., using the previously mentioned public list). The mentioned
+$\fissue^{n,\dattrs}$ functions must follow the pattern in \esref{eq:funcs-dac}.
+Namely, the issuance function checks that the first requested attribute equals
+$n+1$, and that all requested attributes are a subset of the attribute set
+\dattrs being delegated by the level-$n$ issuer. In addition, signature
+evaluation functions $\feval^{n,\dattrs}$, also shown in \esref{eq:funcs-dac},
+must reveal the level of the credential used to produce the \UAS signature at
+item 2, as well as the set of attributes \dattrs that the level-$n$ issuer
+delegates. Verifiers can then trivially check if the set of revealed attributes
+are contained within the attributes delegatable by the parent issuer%
+\footnote{Additional checks may be added in both functions, but this is
+  the bare minimum.}. \figref{fig:XXX} depicts a sample of the delegation chain
+that this structure creates.
+
+\begin{align}
+  & \fissue^{n,\dattrs}(\usk,\cred,\attrs) \coloneqq \lbrace
+    \pcif \attrs_1 = n+1 \land \attrs \subseteq \dattrs: \pcreturn 1; \pcelse \pcreturn 0
+    \rbrace \nonumber \\
+  & \feval^{n,\dattrs}(\usk,\cred,\msg) \coloneqq \lbrace
+    \pcreturn (\attrs_1(\cred),\dattrs(\cred)) \rbrace
+  \label{eq:funcs-dac}
+\end{align}
+
+From this high-level description, we define the algorithms of \CUASDAC:
+
+\begin{description}
+\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
+    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
+    construction. Returns $\parm \gets (\parm',\opk)$. Note that $\finsp^0$ can
+    be replaced by any desired opening function.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $n=0$, simply run \IKeyGen as
+  in \CUASAC. If $n>0$, note that this is a user who wants to delegate a
+  previously obtained credential \cred. Thus, it has already run $UserKeyGen$
+  below, which internally also runs \IKeyGen as in \CUASGen and sets $\usk \gets
+  \isk$. In addition, the level-$n$ issuer picks a random message $r$ and
+  computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
+  \feval^{n,\dattrs})$, for the \dattrs set it wants to reveal -- which must
+  include the attributes to delegate, and the credential level. It then
+  publishes $(n,\ipk,\Sig,\ipk^{n-1},\fissue^{n,\dattrs},\feval^{n,\dattrs})$,
+  where $\ipk^{n-1}$ is the public key of the parent issuer,
+  $\fissue^{n,\dattrs}$ is an issuance function as described in
+  \esref{eq:funcs-dac}, and $\feval^{n,\dattrs}$ is also as in
+  \esref{eq:funcs-dac}, revealing the attributes that the issuer is willing to
+  delegate..
+\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
+  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
+  $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
+  credentials.
+\item[$\langle \cred/\bot,\top/\bot \rangle \gets
+  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
+  If $n>0$, the user first finds the corresponding $(n,\ipk,\Sig,\ipk^{n-1},
+  \fissue^{n,\dattrs},\feval^{n,\dattrs})$ tuple, and checks \Sig running
+  \Verify as in \CUASGen (with the retrieved $\feval^{n,\dattrs}$). Then,
+  user and level-$n$ issuer run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
+  using $\fissue^{n,\dattrs}$ as issuance function. If $n=0$, then both run
+  $\langle\Obtain,\Issue\rangle$ as in \CUASGen, using the \fissue function
+  required by the issuer.
+\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle
+  \gets \langle Show(\opk,\attrs,\dattrs,\cred),
+  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of \CUASGen.  
+\end{description}
+
+\paragraph{Security of \CUASDAC.} %
+We prove that \CUASDAC is an anonymous and unforgeable DAC scheme, according to
+the model in \figref{fig:model-dac}, if the underlying \CUASGen construction has
+anonymous issuance and signing, and has unforgeable issuance and signing.
+
+\begin{theorem}[Issuance anonymity of \CUASDAC]
+  If the base \CUASGen construction has issuance anonymity according to
+  \defref{def:issue-anonymity-uas}, then \CUASDAC also has issuance anonymity.
+\end{theorem}
+
+\begin{proof}
+  Given \adv~ against issuance anonymity of \CUASDAC as defined in
+  $\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
+  issuance anonymity of \CUASGen as defined in \defref{def:issue-anonymity-uas}.
+
+  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
+  oracle, i.e.: for calls to $HU,CU,HI,CI,Obtain,Show,IssLoR$, \advB redirects
+  to \HUGEN,\CUGEN,\IGEN,\ICORR,\OBTAIN,\SIGN,\OBTCHALb, respectively. Note that
+  ``translating'' the inputs from the former into inputs for the latter is
+  trivial. Obviously, if \adv~ wins in its issuance anonymity game, then so does
+  \advB with the  same probability.
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Signature anonymity of \CUASDAC]
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASDAC also has signature anonymity.
+\end{theorem}
+
+\begin{proof}
+  This is the same as in \thmref{thm:anon-cuasac}.
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability of \CUASAC]
+  If the base \CUASGen construction has issuance and signature unforgeability
+  according to \defref{def:issue-forge-uas} and \defref{def:sign-forge-uas}, and
+  non-frameability according to \defref{def:frame-uas}, then \CUASAC is an
+  unforgeable AC scheme.
+\end{theorem}
+
+\begin{proof}
+  First, we define the $ExtractChain(\utrans)$ function for our construction.
+  Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows for the approach
+    to transform non-interactive signature and verification in \UAS to interactive
+    presentations, as described in \secref{ssec:variants-gsac}.}, where $r$ is a
+  fresh random number produced by the environment (acting as honest verifier),
+  and \Sig is a \CUASGen signature over $r$. Thus, $ExtractChain$ leverages
+  \ExtractSign from \CUASGen (see \secref{ssec:security-uas}) to get the
+  credential and associated \ipk used to produce \Sig. Note that, for this
+  \ipk, $\ipk = \ipk_{n-1}$ in $\Exp^{forge}_{\adv,dac}$. In \CUASDAC, we can
+  leverage $\ipk_{n-1}$ to fetch from the public list a signature $\Sig_{n-1}$
+  generated by the issuer owner of $\ipk_{n-1}$. Again, we apply \ExtractSign
+  from \CUASGen, to get the credential one layer up in the chain.
+  $ExtractChain$ repeats this step, until reaching the top level credential,
+  issued by $\ipk_0$.
+
+  For the proof, we first replace within $Setup$ the $\NIZKSetup$ algorithms for
+  issuance and signing with their corresponding $\NIZKSetup$. Due to their
+  zero-knowledge property, the resulting game is indistinguishable. Also, note
+  that $ExtractChain$ succeeds to extract the corresponding credential chain,
+  due to simulation extractability of the NIZKs.
+
+  From the previous, the same reasoning as in \thmref{thm:forge-cuasac} applies
+  to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
+  suppose that, from \utrans obtained at line 6, $ExtractChain$ outputs a
+  delegation chain that makes \adv~win at line 10. This means that an
+  uncorrupted issuer at position $i-1$ of the chain did not own a credential
+  containing $D'$, but the issuer at position $i$ does. Then, either of the
+  following must happen:
+
+  \begin{itemize}
+  \item The credential of the issuer at position $i$ is a forgery, meaning that
+    it is a valid signature by the issuer at position $i-1$, who did not produce
+    it. This can be used to break signature non-frameability of \CUASGen.
+  \item The credential of the issuer at position $i$ is not a forgery, meaning
+    that it is a valid signature by the issuer at position $i-1$, who produced
+    it. But this contradicts the conditions required by $\fissue^{n,\dattrs}$,
+    and therefore breaks issuance unforgeability of \CUASGen.
+  \end{itemize}
+  %
+  \qed
+\end{proof}
+
+\subsection{Revocable Anonymous Credentials}
+\label{sapp:related-models-rac}
+
+In \cite{cks10}, revocable anonymous credentials are proposed. From \CUASGen, it
+is straightforward to build an AC system with verifier local revocation, like in
+\cite{bs04}. Basically, all credentials get an identifier as first attribute,
+and \feval functions prove that the opener can retrieve that identifier. Then,
+in case of needing to revoke a concrete credential, any verifier can interact
+with the opener to add an identifier to its own revocation list (alternatively,
+there can be a public list of revoked credentials). Having \feval functions
+prove that the credential identifier does not belong to that list thus directly
+implements privacy-preserving revocation. We first give a simple model in
+\figref{fig:model-rac}, extending that in \appref{sapp:related-models-ac}. As
+before, for simplicity we assume only one credential is used per authentication
+(the extension being direct). To the functionality in
+\appref{sapp:related-models-ac}, we now explicitly add the $OKeyGen$ function
+(equivalent to \OKeyGen, with a fixed \finsp function),
+which generates the opener key pair, extend $Verify$ to receive also a list $L$
+of revoked identifiers, and we add a function (and corresponding oracle) $id/\bot
+\gets RetrieveCredId(\osk,\utrans)$ that can extract the identifier of the
+credential used in a presentation transcript \utrans -- and which is essentially
+equivalent to \Open in \UAS. For simplicity, we do not include the equivalent to
+verifiable openings, but this would be straightforward.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.45\textwidth}
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\opk,\osk) \gets \OKeyGen(\parm) \\        
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
+        b^* \gets \adv^{\mathcal{O}_{anon}}(\parm,\ipk,\opk) \\
+        \pcreturn b^*
+      }        
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.55\textwidth}
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\opk,\osk) \gets \OKeyGen(\parm) \\        
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\
+        (D,L,\st) \gets
+        \adv^{\mathcal{O}_{forge}}(\parm,\ipk) \\
+        \langle \cdot,(b,\utrans)\rangle
+        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
+        \pcif b = 0: \pcreturn 0 \\
+        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
+        \land D \subseteq \ATTR[j]): \pcreturn 1 \\    
+        h \gets RetrieveCredHandle(\osk,\utrans) \\
+        \pcif h \in L \lor h = \bot: \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for revocable anonymous credentials with selective
+    disclosure based on \cite{fhs19}. 
+    $\mathcal{O}_{anon} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
+    ReqCredHandle,LoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace HU,CU,
+    Obtain,ObtIss,Issue,Show,ReqCredHandle \rbrace$. $ReqCredHandle$ is
+    equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
+    Also, \OWNR and \ATTR tables are essentially as in \secref{ssec:model-uas}.}
+  \label{fig:model-rac}  
+\end{figure}
+
+\subsubsection{\CUASRAC Construction.} %
+
+For our RAC construction, we define signature evaluation and opening functions
+as follows:
+
+\begin{align}
+  & \feval^{\dattrs,F,V,L}(\usk,\cred,\msg) \coloneqq
+    \lbrace
+    \pcif F(V,\attrs_1(\cred)) \in L: \pcreturn (0,0);
+    \pcelse \pcreturn (\dattrs(\cred),V)
+    \rbrace \nonumber \\
+  & \finsp^{F}((\yeval^0,\yeval^1),\usk,\cred,\msg) \coloneqq
+    \lbrace
+    \pcif \yeval^0 \neq 0: \pcreturn F(\yeval^1,\attrs_1(\cred));
+    \pcelse \pcreturn 0
+     \rbrace
+  \label{eq:funcs-rac}
+\end{align}
+
+Where, $\feval^{\dattrs,F,V,L}$ is parameterized with a one-way function $F$
+(e.g., a cryptographic hash), some constant subset \dattrs of attributes to be
+selectively disclosed by signers, a string identifying the verifier $V$ and a
+list $L$ of ``revocation handles'' by this verifier. If the credential used for
+signing has been revoked (i.e., if $F(V,id) \in L$), then \feval returns $0$, as
+an indication that the signature should be rejected by the verifier. Otherwise,
+it sets $\yeval^0 \gets \dattrs(\cred)$, and $\yeval^1 \gets V$ -- note that
+$\yeval^1$ will be encrypted with a single-use key pair.
+%
+On the other hand, $\finsp^{F}$ outputs $F(\yeval^1,\attrs_1(\cred))$, allowing
+valid signatures to be locally revocable by $V$ at a later stage, since
+$\yeval^1=V$.
+
+\begin{description}
+\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
+  \CUASGen.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
+  \CUASGen construction, setting $\fissue^1$ as issuance function.
+\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
+  \CUASGen construction, setting $\finsp^F$ as opening function.
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
+  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
+\item[$\langle \cred/\bot,\top/\bot \rangle \gets
+  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
+  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
+  $\fissue^1$ as issuance function.
+\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
+  \Verify(\ipk,\dattrs) \rangle$.]
+  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
+  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
+  $\finsp^F$ as open function.
+\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
+  Outputs the revocation handle $h$ for the credential used in the interactive
+  presentation associated to \utrans. Note that $h$ is verifier-dependent.
+\end{description}
+
+\paragraph{Security of \CUASRAC.} %
+We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
+scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
+is anonymous and has unforgeable signing. Note that issuance unforgeability
+of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
+leveraging other credentials not any fixed custom issuance policy. Thus,
+signature unforgeability from \UAS is enough. Note that AC schemes modelled
+as in \cite{fhs19} do not have issuance anonymity, as the user public key
+is passed to the issuer.
+
+\begin{theorem}[Anonymity of \CUASRAC]
+  \label{thm:anon-cuasac}
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASAC is an
+  anonymous AC scheme according to \cite{fhs19}.
+\end{theorem}
+
+\begin{proof}
+  Given \adv~ against anonymity of \CUASRAC as defined in
+  \figref{fig:model-rac}, we build an adversary \advB against anonymity of
+  \CUASGen as defined in \defref{def:sign-anonymity-uas}.
+
+  First observe that, given a revocation handle $F(V,id)$ extracted from any
+  credential showing, it is not possible to extract $id$, as $F$ is one-way.
+
+  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
+  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
+  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, of \OPEN respectively.
+  Note that ``translating'' the inputs from the former into inputs for the
+  latter is trivial. Also, observe that $ReqCredHandle$ essentially refuses to
+  open transcripts from challenge users (signatures, in the non-interactive
+  equivalent), as $F(V,\attrs_1(\ccid_0) \neq F(V,\attrs_1(\ccid_1)$ with
+  overwhelming probability (see the $\tyinsp \neq \yinsp$) check in
+  \figref{fig:oracles2}. Obviously, if \adv~ wins in its anonymity game, then
+  so does \advB with the same probability.
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability of \CUASRAC]
+  If the base \CUASGen construction has sign unforgeability according to
+  \defref{def:sign-forge-uas}, and $F$ is one-way, then \CUASRAC is an
+  unforgeable RAC scheme.
+\end{theorem}
+
+\begin{proof}
+  Given \adv~ against unforgeability of \CUASRAC as defined in
+  \figref{fig:model-rac}, we build an adversary \advB against sign
+  unforgeability of \CUASGen as defined in \defref{def:sign-forge-uas}.
+
+  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
+  that \adv~ wins its game via the winning condition of line 6 in the RAC
+  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
+  that the probability of \adv~ winning its game via the winning condition at
+  line 9 is negligible, due to soundness of the NIZK scheme used for signing,
+  and the one-wayness of $F$ in $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.  
+  %
+  \qed
+\end{proof}
+
+\subsection{Multimodal Private Signatures}
+\label{sapp:related-models-mps}
+
+Multimodal Private Signatures (or, rather, a close relative, see next) are
+directly implementable with a restriction of \UAS. Concretely, by restricting to
+a system with one issuer and one opener, one credential per user, one attribute
+per credential (the user secret key), $\fissue^1$ issuance functions, and
+\feval functions that only use the $\yeval^1$ output -- which we denote with
+$\feval^{\yeval^1}$.
+
+There are some differences, though. On the one hand, our signature anonymity
+property is somehow in the middle of MPS's privacy-1 and privacy-2 variants.
+Their privacy-1 variant is the traditional anonymity property of group
+signatures, in which the opener is honest and the adversary can call the opening
+oracle except for challenge signatures. In their privacy-2 variant, the opener
+is fully corrupt (i.e., \adv~ receives \osk), but the adversary can only be
+challenged with signatures that produce the same \yinsp value ($G_{j_b}(id_b)$
+in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
+(getting ther \osk), but the challenge signatures must have been generated using
+the key of an uncorrupted opener; still, \adv~can call the open oracle for
+challenge signatures, as long as they have the same \yinsp value. We believe
+that these differences are mostly of theoretical interest, though, and it does
+not seem hard to move from one to the other \todo{check}. In practice,
+what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$
+in MPS) that has too much granularity in their ranges, will lead to a barely
+private system. This is a known issue, for instance, in functional encryption
+\needcite.
+
+On the other hand, our issuance-related properties (issuance anonymity and
+issuance unforgeability) are unachievable by MPS. Issuance anonymity simply does
+not make sense in MPS, as it only supports one credential (without attributes)
+per user. Issuance unforgeability does not make sense either, since there are no
+configurable issuance policies in MPS -- instead, they have the fixed policy of
+``proving knowledge of a user secret key''. These extensions are not trivial
+from a theoretical point of view, and also have a big impact in the practicality
+of the resulting system. Also, MPS does not include verifiable openings. While
+this is easy to add, we consider it to be essential, given that the proposed
+generalization of opening allows the opener to output ``any value''. Hence, the
+need to ensure that the produced value is the legitimate one, seems to be more
+necessary than ever. Finally, our \feval function is a generalization of $F$ in
+MPS, as it allows two outputs: one will be returned in the clear along with the
+signature, and the other will be encrypted. Still both computations are proved
+correct. Making part of the output unencrypted allows implementing very useful
+variants such as anonymous credentials with selective disclosure -- as shown
+before.
+
+For the model of MPS schemes, we refer to the original paper \needcite.
+
+\subsubsection{\CUASMPS construction.} %
+As mentioned, any $(\fissue^1,\feval^{\yeval^1},\finsp^\ast)$-restriction of
+\CUASGen with only one issuer and opener, one credential per user, and one
+attribute per credential (the user secret key), implements an MPS scheme where
+$F=\feval^{\yeval^1}$ and $G=\finsp^\ast$. The restriction to one credential per
+user, and one attribute per credential, can be done as in
+\appref{sapp:related-models-gs}. Finally, note that, in MPS, $G$ is further
+parameterized with a value $j$, which essentially is the result of applying $F$
+to the message and signer identity, and is not leaked to the opener nor any
+other third party. The equivalent in \UAS is the $\yeval^1$ value, which is
+encrypted with a single-use key pair, and is an input of \yinsp.
+
+\paragraph{Security of \CUASMPS.} %
+As stated, we restrict to privacy-1 of MPS. Unforgeability-1 in MPS is
+equivalent to sign unforgeability in \UAS. Unforgeability-2 in MPS is
+equivalent to non-frameability in \UAS. Finally note that, in UAS, we do not
+explicitly model extractability, but rather make it an inherent requirement in
+the unforgeability and non-frameability definitions. Thus, our \CUASMPS
+construction also ensures MPS-extractability.
+
+\begin{theorem}[Privacy-1 of \CUASMPS]
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASMPS satisfies privacy-1
+  according to \needcite.
+\end{theorem}
+
+\begin{proof}
+  The proof is direct, by observing that the models are equivalent.
+
+  First, note that, in MPS the adversary is required to output a function $F$,
+  challenge message, and a pair of user secret keys and witnesses (in \UAS, the
+  witnesses are the credentials). This is precisely what \CHALb requires as
+  input in our \UAS modelling.
+
+  Next, in MPS, validity of the output of $F$ is checked. In MPS, this
+  translates to checking that $F$ does not ouptut $0$. In UAS, this is checked
+  in the \SIGN and \CHALb oracles, which abort if the output produced by \feval
+  does not belong in \rngfeval -- a well defined set of acceptable outputs by
+  the chosen \feval.
+
+  The MPS adversary is then allowed to make more oracle queries, and outputs a
+  response bit. Just as in \UAS. Thus, if \CUASMPS satisfies signature
+  anonymity, it is also an MPS scheme satisfying privacy-1.  
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Extractability of \CUASMPS]
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, then it is an extractable MPS scheme.
+\end{theorem}
+
+\begin{proof}
+  The proof is direct, as the conditions checked in the extractability
+  experiment in MPS are also checked in the signature unforgeability experiment
+  for \UAS.
+
+  Concretely, \Verify must accept the signature, and the ouptut of \feval and
+  \finsp, computed with the values extracted by \ExtractSign, must respectively
+  match those output by the adversary (for \feval), and computed honestly by the
+  signature unforgeability (for \finsp).  
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability-1 of \CUASMPS]
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
+  defined in \needcite.
+\end{theorem}
+
+\begin{proof}
+  For an MPS scheme to satisfy type-1 unforgeability, it has to be extractable.
+  This is directly satisfied by signature unforgeability in \UAS.
+  %
+  Next, the adversary wins in the unforgeability-1 MPS experiment if it manages
+  to produce a signature that has not been produced via a call to their \SIGN
+  oracle, nor it can be associated to an corrupt user. Indeed, if that happens,
+  then such adversary can be used to build an adversary winning the signature
+  unforgeability game against \CUASMPS, through winning condition at line 12 --
+  as \IdentifyUK does not return 1 for any known \uid. Thus, if \CUASMPS has
+  signature unforgeability, it also satisfies unforgeability-1 of MPS schemes.
+  %
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability-2 of \CUASMPS]
+  If the base \CUASGen construction has non-frameability according to
+  \defref{def:frame-uas}, then \CUASMPS satisfies unforgeability-2 as
+  defined in \needcite.
+\end{theorem}
+
+\begin{proof}
+  For an MPS scheme to have type-2 unforgeability, it has to be extractable.
+  This is directly satisfied by non-frameability in UAS (a similar reasoning
+  as for signature unforgeability and extractability applies here).
+  %
+  Next, in MPS, the adversary wins if the produced signature has not been
+  output by the \SIGN oracle, but Extract outputs the identifier of an honest
+  user. This is the same check done in lines 9 and 10 of the non-frameability
+  game in \UAS. Therefore, if \CUASMPS satisfies non-frameability as defined in
+  \defref{def:frame-uas}, it also satisfies type-2 unforgeability in MPS.
+  \qed
+\end{proof}
 

### 2022-06-22 prism-backend/research/gsac/formal-uas.tex
Small pass.

@@
 still allow spanning a wide variety of related schemes. We combine aspects of GS
-and AC schemes -- and, therefore, rely heavily on previous works --,
-generalizing whenever possible. Like in ACs, there are multiple issuers, and
-each user can get one or more credentials from any of them. We incorporate
-openers, as in GSs, but there is no tight relationship between issuer
-and opener. Signing and verification are non-interactive processes like in GS
-schemes, but we show how to convert to an interactive one like in ACs. Finally,
-we incorporate functions that allow tweaking the behaviour at issuance,
-signature generation, and verification times; while signatures contain all the
-necessary information to check that all computations are performed correctly.
+and AC schemes, generalizing whenever possible. Like in ACs, there are multiple
+issuers, and each user can get one or more credentials from any of them; and,
+also, use more than one credential simultaneously to produce a signature. We
+incorporate openers, as in GSs, but there is no tight relationship between
+issuer and opener. As a consequence, signers (potentially along with verifiers)
+may choose, on a per-signature basis, the policies governing the utility
+information extractable from a signature. Signing and verification are
+non-interactive processes like in GS schemes, but we show how to convert to an
+interactive one as in ACs. Finally, we incorporate functions that allow
+tweaking the conditions checked at credential issuance and signature generation
+times, including the information that an opener will be able to extract from a
+signature. This flexibilizes the scheme even beyond the loose relationship
+between issuer and opener.
 
@@
 \paragraph{Issuance, evaluation, and opening functions.} %
-We emphasize that, both in our syntax definition, as well as on the following
-modelling, we make use of three different and abstract functions: \fissue,
-\feval and \finsp. The three functions are introduced to allow customized
-governance of the resulting instantiation of an \UAS scheme. They will be
-defined by different parties, but in all cases, they are run by users (maybe,
-on user-private data). Also, in all cases, the user has to prove correctness of
-their computation. We introduce them next, and give concrete examples for
-building specific well-known restrictions of \UAS in
-\secref{sec:transformations}.
+We introduce three functions in our syntax and model. Through them,
+it is possible to modulate the behaviour of the resulting instantiation, by
+controling the conditions upon which a new credential can be issued, or the
+information revealed at signing time, or after signing. In all cases, it is
+the user who computes them, and has to prove correctness of such computation.
+We give concrete examples in \secref{sec:relationships}, and define them next:
 
@@
 \item[$\fissue: (\usk,\scred,\attrs)
-  \rightarrow 0/1$.] Chosen by issuers within a family of functions \famfissue,
-  the issuance function defines what customized conditions an issuer requires
-  in order to issue credentials, when receiving a request from user with secret
-  key \usk, for attributes \attrs. \fissue may run checks on a (possibly empty)
-  set of additional credentials \scred, all bound to \usk, and possibly
-  issued by other issuers. \fissue returns $1$ to accept a request, $0$ to
+  \rightarrow 0/1$.] Chosen by each issuer within a family of functions
+  \famfissue, the issuance function defines the customized conditions required
+  by the issuer to grant a credential over attributes \attrs, when requested by
+  a user with secret key \usk, potentially leveraging a set of previously
+  obtained credentials \scred. \fissue returns $1$ to accept a request, $0$ to
   reject it.
@@
   receive the user secret key \usk, credentials \scred, and message to be signed
-  \msg. \feval can be used to control the information related to the signer that
-  will be revealed alongside a signature, and to modulate the behaviour of
-  \finsp. Its outputs two values, $\yeval^0$ and $\yeval^1$, where the former
-  is revealed in plaintext along with the signature, and $\yeval^1$ is encrypted
-  and used to modulate the behaviour of \finsp. Both values must belong in a
-  well defined set \rngfeval. For readability, we write
-  $\Yeval = (\yeval^0,\yeval^1)$.
+  \msg. \feval outputs two values, $\yeval^0$ and $\yeval^1$, where the former
+  is revealed in plaintext along with the signature, and $\yeval^1$ is
+  encrypted. Both can be used to modulate the bevahiour of \finsp, and must
+  belong in a well defined set \rngfeval. For readability, we write $\Yeval =
+  (\yeval^0,\yeval^1)$.
 \item[$\finsp: (\Yeval,\usk,\scred,\msg) \rightarrow \yinsp$.]
@@
   functions define what utility value, derived from the user's secret key,
-  credentials, and signed message, should be extractable by an opener.
-  Note that \finsp also receives as input a value in the range of the \feval
-  function, $\rngfeval^2$. This allows opening logic to depend on the values
-  produced by the evaluation function. The output of \finsp is a value
-  \yinsp, which must belong in a well defined set \rngfinsp.
+  credentials, and signed message, should be extractable by an opener. Its
+  behaviour can be modulated by \Yeval, and its output a value \yinsp, which
+  must belong in a well defined set \rngfinsp.
 \end{description}
 
-We emphasize that, even though \finsp and \feval seem redundant, they are not.
-To see this, observe that \finsp is defined by openers, and will be fixed in
-all signatures that can be opened by the opener who defined it. On the other
-hand, \feval can be defined by (e.g.) verifiers on a per-signature basis, even
-if the signatures use the same \finsp. Thus, \feval can be programmed to contain
-the conditions set by (e.g.) verifiers for signatures they receive; whereas
-\finsp can be programmed to extract specific utility values when needed, which
-may depend on the checks required by the verifier a signature was intended to.
+\feval and \finsp may seem redundant. However, observe that the former is chosen
+on a per-signature basis, and probably after negotiation between signer and
+verifier. As such, it governs the information revealed at signing time. On the
+other hand, \finsp governs the information that may be revealed after signing.
+Moreover, it is defined by openers, and even though signers and verifiers
+may negotiate to use any opener for a given signature, it is not possible for
+an opener to change the chosen function.
 
@@
 
-\subsection{Model for \UAS Schemes}
+\subsection{Security Model}
 \label{ssec:model-uas}
 
-We now define our model for Universal Anonymous Signatures. Property-wise, we
-maintain anonymity, non-frameability, and include two extra unforgeability
-properties: unforgeability of issuance, which ensures that issuance policies
-are not circumvented; and unforgeability of signatures, guaranteeing that
-signature evaluation policies are respected, as well as soundness of opening.
-
-From a functional perspective, we require that each issuer and opener fix
-the issuance predicate \fissue and opener function \finsp when generating
-their public keys. On the other hand, signature evaluation functions \feval can
-be defined at signing time. This is in line with the usual practice in anonymous
-credentials, that let
-users prove arbitrary claims on their credentials, as long as they are met by
-the contained attributes. In practice, most probably, the signature evaluation
-policy to be
-employed in each signature will be defined by the verifier (or jointly between
-user and verifier), including the specification of which opener will be
-able to post-process signatures\footnote{See, for instance, the concept of
-  presentation exchanges, or requests, in the context of Verifiable Credentials:
-  \url{https://identity.foundation/presentation-exchange/} (last access, May
-  5th, 2022).}. Beyond these general policies, which already give much
-flexibility, the syntax for \UAS supports multiple issuers and openers, and
-lets users leverage multiple credentials to request issuance of new ones, and
-to produce signatures.
+We define the security expected from an \UAS scheme using a game-based approach.
+An \UAS scheme must ensure privacy at credential issuance, meaning that two
+runs of the credential issuance protocol should not leak any information beyond
+necessary about the user requesting the credential. Note that this is now
+crucial for privacy since, as AC schemes, \UAS allows multiple credentials per
+user -- thus, knowing what credential a user requests can lead to user
+profiling. It must also ensure signature privacy, meaning that no information
+can be learned, from a signature, by third parties beyond what the user agrees
+to reveal, and what may be extractable by the chosen opener.
+Issuance unforgeability requires that \UAS schemes ensure that the claims used
+to support a credential request cannot be falsified (issuance unforgeability).
+Similarly, signature unforgeability requires that no adversary should be able to
+falsify the correctness proofs for the claims included in the signatures. In
+both cases (issuance and signature unforgeability), we introduce the notion of
+traceability in GS, requiring that all credentials involved in the corresponding
+process have to be associated to a known user. Finally, \UAS schemes inherit the
+useful non-frameability property of GS schemes which, even in the worst-case
+scenario of having a corrupt issuer. In this case, although we cannot ensure
+anything regarding correctness of the claims, we can ensure that no honest user
+can be framed with having created a signature that s/he did not create --
+although the concept may get a bit blurred, as there is no traditional opening.
+%
+We describe next the global variables and oracles that we use in our modelling.
 
 \paragraph{Global Variables.} %
-The environment manages several global variables in the games posed to the
-adversary. Users are referred to with user identifiers, \uid; for credentials,
-we use \cid; for issuers, \iid; and for openers, \oid. In all cases, we use bold
-font to denote sets: e.g., \scid and \siid denote sets of credential and issuer
+Users are referred to with user identifiers, \uid; for credentials, we use \cid;
+for issuers, \iid; and for openers, \oid. In all cases, we use bold font to
+denote sets: e.g., \scid and \siid denote sets of credential and issuer
 identifiers. All tables/sets are initialized as empty tables/sets.
@@
 \begin{description}
-\item[Sets for parties]:
-  \begin{description}
-  \item[\HU and \CU.] Keep track of honest (\HU) and corrupted (\CU) users;
-    i.e., they are sets of {\uid}s.
-  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers;
-    i.e., they are sets of {\iid}s.
-  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) openers;
-    i.e., they are sets of {\oid}s.
-  \end{description}
-\item[Tables for keys]:
-  \begin{description}
+\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
+  track of honest users/issuers/openers. They are sets of
+  {\uid}s/{\iid}s/{\oid}s.
+\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
+  track of corrupt users/issuers/openers. They are sets of
+  {\uid}s/{\iid}s/{\oid}s.    
 \item[\UK.] \UK maintains user keys $\usk$. To refer to the key of a specific
@@
   of \fissue, \OK includes the \finsp function.
-  \end{description}
-\item[Tables for credentials-related data]:
-  \begin{description}
 \item[\CRED.] Stores information related to credentials obtained by users in
   the system. Thus, it is indexable by \cid. More specifically, it stores
-    tuples of the form $(\uid,\cred,\iid,\attrs,\scid)$, where \uid is the
+  tuples of the form $(\uid,\cred,\iid,\attrs,\scid,\siid)$, where \uid is the
   identity of the owner of the credential, \cred (when available) is the
   credential itself, \iid is the identifier of the credential issuer, \attrs
-    are the attributes included in \cred, and \scid are the identifiers of the
-    credentials (if any) that \uid used to request \cred. For notational
+  are the attributes included in \cred, \scid are the identifiers of the
+  credentials (if any) that \uid used to request \cred, and \siid the issuers
+  of those credentials. For notational
   convenience, we may use $\CRED[\scid]$ to refer to $\CRED[\cid]$ for all
@@
   $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,\cdot)$ (resp. $\CRED[\scid]$).
+\item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
+  issuance anonymity game.
 \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
@@
   ``\iid such that $\CRED[\cid] = (\cdot, \iid, \cdot, \cdot, \cdot)$''.
-  \end{description}
-\item[Tables for signatures]:
-  \begin{description}
-  \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
-    of honest users. Entries of this table are $(\oid,\scid,\sig,\Yeval,\msg,
-    \feval)$, where \oid is the opener chosen for the signature, \scid is the
-    set of credentials used for signing, \feval is the signing evaluation
-    function, and \sig and \msg are the produced signature and signed message.
-  \item[\CSIG.] Maintains challenge signatures output to the adversary; i.e.,
-    the table is indexable by challenge signatures \csig.
-    Each entry contains also $\cuid_b$ and $\scid_b$ the challenge user and
-    credential identifiers set used to produce \csig; as well as the
+\item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
+  this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
+  the opener, \scid is the set of credentials used for
+  signing, \feval is the signing evaluation function, and \sig and \msg are the
+  produced signature and signed message.
+\item[\CSIG.] Maintains challenge signatures output to the adversary in the
+  signature anonymity game, and is indexable by challenge signatures \csig.
+  Each entry contains also $\cuid_b$ and $\cscid_b$, respectively the challenge
+  user  and credential identifiers set used to produce \csig; as well as the
   corresponding challenge user and credential set indexed by the complementary
   $1-b$; the signed message \msg and signing evaluation function \feval, the
-    result of \feval, \yeval, and the opener identifier \oid.
-  \end{description}
+  result of \feval, \Yeval, and the opener identifier \oid.
 \end{description}
@@
   the game, on behalf of an honest user.
-\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
-  in games that support it, by letting it interact with honest users who want to
-  receive credentials.
+\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer, by
+  letting it interact with honest users who want to receive credentials.
 \item[\ISSUE.] Allows the adversary to play the role of dishonest users,
@@
   opening function, along with a correctness proof.
+\item[\OBTCHALb.] Upon receiving a target credential identifier, two challenge
+  users and credential sets, an honest issuer identifier, and a set of
+  attributes, issues a credential for the challenge user and credential set
+  defined by the bit $b$. 
 \item[\CHALb.] Upon receiving two challenge users and credential sets, a common
   singing evaluation function and a message, returns a signature produced by one
-  of these two user and credential sets, defined by the bit $b$, which is
-  established in the anonymity game.
+  of these two user and credential sets, defined by the bit $b$.
 \end{description}
@@
 \paragraph{Helper functions \ExtractIssue, \ExtractSign, \IdentifyCred, and
-  \IdentifyUK.} In our modelling, we assume the existence of fhese four
-functions. They are not
+  \IdentifyUK.} We assume the existence of these four functions. They are not
 functions available in the actual scheme, but rather to the challenger in the
@@
   Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
-  credentials (if any) and their attributes that were involved
-  in the request. It clearly needs an honest issuer as, otherwise, the
-  transcripts won't be available. Consequently, we only use it to define the
-  properties that require an honest issuer.
+  credentials (if any) and their attributes involved in the request. It 
+  needs an honest issuer as, otherwise, the transcripts won't be available.
 \item[$\ExtractSign(\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
@@
   as well as the opener identifier \oid, and the identifiers of all issuers of
-  the credentials used to produce the signature over \msg, and for \feval. It
-  outputs the user secret key and credentials (with their attributes) used to
-  generate the signature, and the value returned by the opening fuction.
+  the credentials used to produce the signature over \msg, and for \feval.
+  It outputs the user secret key and credentials (with their attributes) used to
+  generate the signature, and the $\yeval^1$ and \yinsp values.
 \item[$\IdentifyCred(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
@@
   to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
-  to \uid, extract the used secret key, and check if there is a match. Note that
-  this does not guarantee that there will be only one \usk per corrupt \uid,
-  though. Also, when used for corrupt users, this can only be used when the
-  issuer is honest, as transcripts are needed. 
+  to \uid, extract the used secret key, and check if there is a match. In the
+  latter case, there is no guarantee of getting a one-to-one relationship
+  between \usk and \uid. Also, when used for corrupt users, this can only be
+  used when the issuer is honest, as transcripts are needed. 
 \end{description}
 
-Note that, for all the helper functions, in the case of credentials, transcripts,
-and signatures by honest users, it is enough to have access to the corresponding
-state information (described below) maintained by the challenger in our
-experiments. For credentials and join transcripts of corrupt users, or
-dishonestly produced signatures, we do need to perform actual extraction.
-Certainly, the challenger
-needs special knowledge/power such as decryption trapdoors, the ability to
-rewind the game, or program random oracles. The approach needs thus to depend on
-the concrete construction. \jdv{Although, for the case of \ExtractIssue and
-  \IdentifyUK, online extractability (or alternative requirements, such as
-  non-parallel or logarithmic number of joins) is necessary.}
+% Note that, for all the helper functions, in the case of credentials, transcripts,
+% and signatures by honest users, it is enough to have access to the corresponding
+% state information (described below) maintained by the challenger in our
+% experiments. For credentials and join transcripts of corrupt users, or
+% dishonestly produced signatures, we do need to perform actual extraction.
+% Certainly, the challenger
+% needs special knowledge/power such as decryption trapdoors, the ability to
+% rewind the game, or program random oracles. The approach needs thus to depend on
+% the concrete construction. \jdv{Although, for the case of \ExtractIssue and
+%   \IdentifyUK, online extractability (or alternative requirements, such as
+%   non-parallel or logarithmic number of joins) is necessary.}
 
@@
 \scid meet the conditions set by the corresponding \fissue defined by the issuer
-which issued each credential. Similarly, the output \yeval of \feval matches the
+which issued each credential. Similarly, the output of \feval matches the
 value produced by \Sign alongside with \sig; and the value produced by \Open
-is accepted by \Judge, and matches the output of applying \finsp on \yeval, the
+is accepted by \Judge, and matches the output of applying \finsp on \Yeval, the
 credentials, user key, and message.
@@
       \pcind \pcreturn 1 \\
+      \pcif \scred \neq \emptyset \land
+      \nexists \uid~\suchthat~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1~
+      \pccomment{\todo{New! Update proofs.}} \\
       \pcreturn 0

### 2022-06-23 prism-backend/research/gsac/app-interactive.tex
More passes.

--- 2022-06-18 prism-backend/research/gsac/conclusion-paper.tex
@@
-\section{Conclusion}
-\label{sec:conclusion}
+\section{\CUASGen with Interactive Sign and Verify}
+\label{app:interactive-uas}
 
-[1 page max]
+\todo{The following was written for \GSAC. It should apply for \UAS, but check
+  and adapt.}
+\todo{Markulf's comment on non-transferability and non-deniability of each
+  option.}
+
+In group signatures, the signing and verification process is non-interactive.
+That is, a group member produces a signature and eventually sends it to the
+verifier, who can check it without further interaction. Nevertheless, in
+anonymous credentials, this process is typically interactive, and consists of
+at least one round-trip. This can be useful, for instance, when some notion of
+freshness is necessary.
+
+The approach to turn our non-interactive singing-verification into an
+interactive protocol that ensures freshness is evident: prior to signing the
+message, we require that the honest verifier sends to the user a number picked
+uniformly at random from an appropriate domain, which must be concatenated to
+the signed message. If there is no need to actually sign a message, then the
+message is set to an empty string, and the user only signs the random number.
+%
+Syntactically, instead of having non-interactive $\sig \gets \Sign(\gpk,\usk,
+\cred,\dattrs,\msg)$ and $1/0 \gets \Verify(\gpk,\sig,\dattrs,\msg)$ algorithms,
+we have a $1/0 \gets \langle \Sign(\gpk,\usk,\cred,\dattrs),\Verify(\gpk,
+\dattrs) \rangle$ interactive protocol.
+%
+We sketch next a proof for why does this result in a secure \GSAC scheme with
+interactive signing and verification.
+
+\paragraph{Issuance Anonymity.} \todo{XXX}
+
+\paragraph{Signature Anonymity.} To see why the interactive variant is
+anonymous, assume an adversary $\adv$ against anonymity in that case. We build
+\advB against the non-interactive \ExpGSACSigAnonb from \adv~ as follows. \advB
+initializes
+everything as in the \ExpGSACSigAnonb game. When $\adv$ initiates a call to its
+interactive \SIGN (resp. \CHALb) oracle, \advB picks a random number, and sends
+it to the adversary, along with the response of its own (non-interactive) \SIGN
+(resp. \CHALb) oracle where, to the message passed as parameter to its oracle,
+concatenates the produced random number. After such simulation, \advB just
+outputs whatever $\adv$ outputs. Clearly, the simulation is perfect and, if
+$\adv$ wins with non-negligible probability in the interactive case, then so
+does \advB in the non-interactive case.
+
+\paragraph{Traceability.} The simulation described for the anonymity case (i.e.,
+\advB choosing the random numbers, and concatenating them to the message to be
+signed) applies here too. Thus, an adversary against traceability in the
+interactive case, can be used to build an adversary that breaks traceability in
+the non-interactive counterpart.
+
+\paragraph{Non-frameability.} The simulation described for the anonymity case
+(i.e., \advB choosing the random numbers, and concatenating them to the message
+to be signed) applies here too. Thus, an adversary against non-frameability in
+the interactive case, can be used to build an adversary that breaks
+non-frameability in the non-interactive counterpart.
 

### 2022-06-23 prism-backend/research/gsac/formal-uas.tex
More passes.

@@
 may choose, on a per-signature basis, the policies governing the utility
-information extractable from a signature. Signing and verification are
-non-interactive processes like in GS schemes, but we show how to convert to an
-interactive one as in ACs. Finally, we incorporate functions that allow
-tweaking the conditions checked at credential issuance and signature generation
-times, including the information that an opener will be able to extract from a
-signature. This flexibilizes the scheme even beyond the loose relationship
-between issuer and opener.
+information extractable from a signature. Finally, we incorporate functions that
+allow tweaking the conditions checked at credential issuance and signature
+generation times, including the information that an opener will be able to
+extract from a signature. This flexibilizes the scheme even beyond the loose
+relationship between issuer and opener.
 
@@
 an opener to change the chosen function.
+
+\begin{definition}{(\CUASGen restrictions)}
+  \label{def:uas-restrictions}
+  Let \CUASGen be a generic construction of an \UAS scheme, secure according to
+  the model defined in \secref{ssec:model-uas}, and three functions $\fissue^a$,
+  $\feval^b$, $\finsp^c$ compatible with the previous definitions. We say that
+  \CUASGen, instantiated with $\fissue^a$, $\feval^b$, and $\finsp^c$, is a
+  $(\fissue^a,\feval^b,\finsp^c)$-restriction of \CUASGen.
+\end{definition}
 
@@
 \paragraph{Anonymity.} %
-\iffalse
-Informally, anonymity must capture two requirements: (1) interactive credential
-issuance protocols do not leak any information about the user requesting them;
-and (2) signatures do not leak any information about the signer. In both cases,
-any leakage must be limited to whatever the user decides to reveal, for
-instance, through arbitrary predicates on the attributes of the credentials used
-for issuance and signing. We follow a simulation-based approach to capture this.
-Basically, the adversary is challenged to distinguish between real and ideal
-executions. In both worlds, the adversary can generate and corrupt honest users,
-issuers, and openers. Then, in the real world, the adversary has access to
-oracles that allow requesting credentials on behalf of honest users, create
-signatures by honest users, and open signatures by honest users. In the ideal
-world, these three oracles are replaced by simulated counterparts, which produce
-outputs independent of the users' secrets. This formulation is given in
-\figref{fig:exp-uas-simanon}, where $\Osimanon = (\lbrace\HU,\CU\rbrace\GEN,
-\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG)$.
-
-\begin{figure}[htp!]
-
-  \centering
-  \procedure[linenumbering]{$\ExpSimAnonb(1^\secpar)$}{%
-    \pcif b = 0: \\
-    \pcind \parm \gets \Setup(1^\secpar) \\    
-    \pcind b^* \gets \adv^{\Osimanon,\OBTAIN,\SIGN,\OPEN}(\parm) \\
-    \pcelse: \\
-    \pcind (\parm,\NIZKtrap) \gets \SIMSETUP(1^\secpar) \\
-    \pcind b^* \gets \adv^{\Osimanon,\SIMOBTAIN,\SIMSIGN,\SIMOPEN}(\parm) \\    
-    \pcreturn b^*
-  }
-
-  \caption{Simulation-based anonymity experiment for \UAS schemes.}
-  \label{fig:exp-uas-anonb}
-\end{figure}
-
-\begin{definition}{(Anonymity of \UAS)}
-  \label{def:sign-anonymity-uas}  
-  We define the advantage \AdvSimAnon of $\adv$ against \ExpSimAnonb as
-  $\AdvSimAnon=|\Pr\lbrack\ExpSimAnono(1^\secpar)=1\rbrack-
-  \Pr\lbrack\ExpSimAnonz(1^\secpar)=1\rbrack|$.
-  %
-  An \UAS scheme satisfies simulatable anonymity if there exists simulators
-  \SIMSETUP, \SIMOBTAIN, \SIMSIGN and \SIMOPEN such that, for any p.p.t.
-  adversary $\adv$, \AdvSimAnon is a negligible function of $1^\secpar$.
-\end{definition}
-\fi
-We need to ensure that no information is leaked about users requesting a
-credential, nor about signers. The latter is typically captured in group
-signatures by letting the adversary request challenge signatures, produced
-by a challenge user picked randomly out of two users chosen by the adversary,
-and requiring the adversary to guess which one was used. In what is frequently
-called CCA-like anonymity, the adversary is given access to the opener,
-except for challenge signatures. We follow this approach in what we call
-signature anonymity. We need however to restrict that challenge signatures
-produce the same \yeval value, to prevent trivail wins by the adversary. On
-the other hand, since it is possible that both challenge signatures produce
-the same \yinsp value, we can model a stronger CCA-like variant, in which the
-adversary is allowed to open challenge signatures for the cases in which the
-\yinsp value is the same for both challenge users.
-
-In addition to signature anonymity, we need to take into account that, as in
-some anonymous credential schemes, a single user may have multiple credentials.
-Moreover, these credentials can be obtained from different issuers, or from the
-same issuer but for different attributes. Thus, it seems logical to require that
-the adversary cannot determine whether any two credential requests originate
-from the same signer, or not. To model this, we define the issuance anonymity
-game. Intuitively, we let the adversary obtain challenge credentials on behalf
-of two honest challenge users, but without knowing to which concrete challenge
-user we actually issue the produced credentials. To prevent trivial wins, we
-have to make additional restrictions. Namely, the two sets of challenge user and
-supporting credentials for requesting the challenge credential need to satisfy
-the same issuance policy, and these supporting credentials cannot include
-credentials that have been obtained via the conventional \OBTAIN oracle.
-The adversary is then allowed to interact with all the other oracles (except the
-one producing challenge signatures, which is not needed), with the only further
-constraint that any call to the \SIGN oracle that leverages challenge
-credentials cannot specify the user identifier (the oracle ``knows'' which one
-out of the two challenge users it needs to use). As usual, after interacting in
-an arbitrary way with the oracles, the adversary needs to guess the bit $b$
-defining which challenge user was employed to produce the challenge credentials.
+Users may see their privacy compromised through their interactions with issuers
+to request a credential, or via the signatures they produce. Thus, we define two
+games to define the privacy expected in those situations.
+
+The issuance anonymity game captures that, given polymomially many
+credential issuance interactions, the adversary gains no information about the
+user(s) behind them. For this, we allow the adversary to control targetted
+issuers and openers (although it may also add honest ones), and add honest and
+corrupt users. The adversary can also obtain credentials, produce signatures,
+and open them. We need to make some limitations to prevent trivial wins: first,
+when querying the oracle for obtaining a challenge credential out of two
+possible user-credential set pairs, the issuance protocol must either succeed or
+fail for both; also, the adversary can open signatures produced with credential
+sets containing challenge credentials $\cred_b$, only if the output of \Open is
+the same as with the complementary $\cred_{1-b}$ 
+\todo{this is not done in the oracles. Fix.} (note that any other signature
+can be open).
+Intuitively, if the adversary cannot distinguish arbitrary runs with all oracles
+(provided the previous constraint) when he gets challenge credentials $\cred_b$
+from runs with credentials $\cred_{1-b}$, then the issuance protocol is
+privacy-preserving.
+
+The signature anonymity game is similar to the traditional one in GS schemes.
+It captures that the signatures produced by system users do not leak information
+about their identity beyond what is already revealed via $\yeval^0$ and what
+may be revealed via \yinsp. Concretely, the adversary can interact with oracles
+as in the issuance anonymity game, except that instead of obtaining challenge
+credentials, it obtains challenge signatures. These signatures must have been
+produced via the \CHALb oracle, which ensures that the $\yeval^0$ value is the
+same for both input sets -- otherwise, rejects creating the signature. We also
+allow opening signatures; even challenge $\cSig_b$ signatures, as long as the
+\yinsp value of the counterpart $\cSig_{1-b}$ is the same. Note that this is
+stronger than the traditional CCA-like security of group signatures, where no
+challenge signature can be open.
 
@@
         \parm \gets \Setup(1^\secpar) \\
-        b^* \gets \adv^{\OIssAnon} (\status,\parm) \\
+        b^* \gets \adv^{\OIssAnon} (\parm) \\
         \pcreturn b^*
@@
         \parm \gets \Setup(1^\secpar) \\
-        b^* \gets \adv^{\OSigAnon} (\status,\parm) \\
+        b^* \gets \adv^{\OSigAnon} (\parm) \\
         \pcreturn b^*
@@
 
-\paragraph{Discussion on the generality of anonymity in \UAS schemes.} %
-% This notion of anonymity is more general than that of group signatures in the
-% sense that calls to the \OPEN oracle reveal an arbitrary function of the
-% identity of the user -- which can certainly be the member index itself, as it
-% is frequent in group signatures, or any other function computable from the
-% user key, its credentials, and signed message. Moreover, note that
-% our notion is even stronger than the conventional ``CCA-like'' anonymity notion
-% that gives the adversary access to the open oracle, only restricting it when
-% trying to open challenge signature. Precisely the introduction of generic
-% opening functions allows us to let the adversary open challenge signatures
-% $\csig_b$ as long as the counterpart $\csig_{1-b}$
-% makes \Open produce the same \y value as output. This is certainly not
-% possible when using conventional opening, since it directly outputs the identity
-% of the signer -- which cannot be the same for different challenge users.
-
-% Note that we could actually remove the requirement that the evaluation function
-% has to produce the same output on both challenge user-credentials pairs.
-% However, by doing so, we would force all constructions to maintain private the
-% output of \feval. We opt not to require that, though, as it directly allows
-% our model to cover interesting use cases -- such as restricting to selective
-% disclosure, or privacy-preserving variants of functional signatures \jdv{check
-%   the latter}, although we show how to do that in \secref{sec:transformations}.
-
-\paragraph{Unforgeability.} In anonymous credentials, unforgeability requires
-that no adversary can succeed in a credential presentation for attributes that
-are not contained in a legitimately issued credential (set) it controls. Note
-that, for this, assuming honest issuers is essential as, otherwise, the
-adversary can get credentials on any attribute set it wants.
-%
-The somehow equivalent property in group signatures, inasmuch it also requires
-honest issuers, is traceability. It captures the security of the
-open-related functionality (e.g., \Open and \Judge) over signatures
-that produced by potentially malicious signers, in the presence of an honest
-issuer. In a nutshell, it ensures that every signature accepted by
-the verification algorithm must have been created by a user who joined the
-group, and that the result of \Open (and thus, \Judge) over such a valid
-signature is consistent with its signer. With conventional opening, this is
-essentially checked by requesting the adversary to produce a signature,
-obtaining -- via open -- the ``identifier'' of the user who produced the
-signature. Schemes
-that do not have conventional opening resort to more subtle techniques, like
-matching keys extracted during join transcripts, with keys used for signing
-(see, e.g., \cite{dl21}). Thus, even though for more subtle reasons (the need
-for reliable bookkeeping during joins) than for anonymous credentials, honest
-issuers are required for traceability of group signatures too.
-
-In our \UAS scheme we allow users prove claims over the attributes they
-own -- attested via obtained credentials -- through the \feval function.
-Roughly, we capture this as in unforgeability requirement of anonymous
-credentials. Namely, we check that the \yeval value returned by \Sign along with
-the signature, matches the expected one from the specified \feval function.
-On the other hand, the opening capabilities of \UAS schemes also call for a
-traceability-like property. However, note that, as opposed to group signatures,
-$\langle \Obtain,\Issue \rangle$ protocols are over credentials rather than
-users -- although, ultimately, credentials must be owned by some user.
-Furthermore, since \Open
-does not return the actual identity of the signer, but a function \finsp of it
-(and other arguments), we need to make sure that the output of \Open
-matches the output of \finsp. As in group signatures with non-conventional open,
-we resort to extraction-based techniques. All this is captured via \ExpForgeSign
-in \figref{fig:exp-uas-unfor-issue}. Therein, the adversary is challenged to
-produce a signature $(\sig,\yeval)$ over message \msg and for evaluation
-function \feval; as well as the identifiers for the opener (\oid) and
-credential issuers (\siid) used to compute the signature. As in traditional
-group signatures, the adversary wins if the signature is accepted by \Verify,
-yet \Open or \Judge fail. Then, the game extracts the user key and
-credentials used to produce the signature. From it, the game checks if the
-output of \feval matches the \yeval value produced by the adversary -- this
-mimics the behaviour of unforgeability in anonymous credentials. Finally, the
-game also checks that the output of \Open (even if accepted by \Judge)
-matches the output of \finsp. If there is any mismatch in the last two checks,
-or some of the credentials used to produce the signature do not correspond to
-the secret key that was allegedly used to request them, the adversary wins the
-game.
-
-Our \UAS scheme includes yet another generalisation that requires unforgeability-like
-security, though. Concretely, the issuance function \fissue. We need to make
-sure that no credential is issued unless its corresponding
-request meets the defined issuance policy. From the point of view of group
-signatures, this may seem redundant. After all, if all valid signatures produce
-consistent evaluation and opening results, given the employed user key,
-credentials, and signed message, the notion of traceability seems to be
-satisfied. However, from the point of view of anonymous credentials, an attacker
-being able to obtain a credential, even when it does not meet the required
-conditions to have it issued, is clearly problematic: it would allow to prove
-claims over attributes it does not really ``own'' (even if the output of \Sign
-and \Open are consistent with the values returned by \feval and \finsp, and
-the credential was obtained via an $\langle \Obtain,\Issue \rangle$ run). To
-capture this, we define the \ExpForgeIssue experiment. In the experiment, the
-adversary is challenged to produce a credential identifier that must be
-associated to an existing $\langle \Obtain,\Issue \rangle$ interaction -- thus,
-the corresponding \trans entry must exist (which we can check, as the issuer is
-honest). The adversary wins if, either the extraction process fails, or the
-extracted user secret key and credentials make the corresponding issuance
-function fail.
-
-For both \ExpForgeIssue and \ExpForgeSign, the adversary is given access to the
+\paragraph{On the generality of anonymity in \UAS schemes.} %
+From the point of view of the achieved privacy, depending on how one defines
+\fissue, \feval and \finsp, it is easy to see that the resulting scheme would
+have different privacy level. For instance, a scheme that has very granular
+\feval outputs barely provides privacy. Or a scheme for which most signatures
+include the same \finsp value has less accountability, but higher privacy.
+%
+This is a natural consequence of the fact that, with different choices of those
+functions, one can mimic the behaviour of (more restricted) schemes. For
+instance, by setting \finsp to output the signer's public key, and \feval to
+output nothing, one gets the same anonymity as in vanilla group signatures
+(concretely, no challenge signature can be opened). Or, if \feval outputs any
+arbitrary subset of the attributes in the used credential(s), and \finsp outputs
+any constant value, then we get the same anonymity as in conventional selective
+disclosure anonymous credential schemes, where any pair of users with different
+subset of revealed attributes are clearly distinguishable. The impact of \fissue
+is somehow orthogonal to the previous, but can be seen as a kind of equivalent
+to \feval, at issuance time.
+%
+Importantly, note that the model is agnostic to the concrete instantiation of
+these functions, and just cares about whether their outputs are equal or not,
+in order to avoid trivial wins by the adversary.
+
+\paragraph{Unforgeability.} \UAS inherits from AC and GS schemes two different
+notions of unforgeability: from AC schemes, the notion that no adversary can
+prove claims unless it owns credentials with the proper attributes; from GS
+schemes, that only credential owners can produce valid signatures. \UAS also
+has verifiable openings as some group signature schemes, which sits somewhere
+in between, and we must ensure that the values output by \Open are correct and
+trace back to a user with consistent credentials. All the previous is captured
+by a signature unforgeability property. We define this by allowing the adversary
+to call any oracle, except the one for corrupting issuers. The adversary wins if
+it produces a valid signature over some message that: (1), opens to a wrong
+value, or to a value that cannot be processed by \Judge; (2), is not consistent
+with the expected \Yeval value; or (3), cannot be associated to known
+credentials owned by a known user.
+
+Again, since \UAS schemes (may) require proving claims at issuance time, we
+need to ensure that those claims cannot be forged by an adversary without the
+proper attributes. In this case, since we (need to) assume trusted issuers, we
+can condition on having the $\langle \Obtain,\Issue \rangle$ transcripts
+available for analysis. Thus, the adversary -- with access to the same oracles
+as above -- is challenged to output a credential identifier for a credential
+that exists in \CRED and (1), the conditions required by \fissue were not
+satisfied, or some of the credentials used to support the request does not
+belong to the requesting user; or (2) all credentials used to support the
+request are bound to the same secret key, but that secret key does not belong
+to any known user. The issuance unforgeability notion formalizes this.
+
+For both \ExpForgeIssue (in \figref{fig:exp-uas-unfor-issue}) and \ExpForgeSign
+(in \figref{fig:exp-uas-unfor-sign}), the adversary is given access to the
 oracle set $\Oforgeissue = \Oforgesign \gets \lbrace\HU,\CU\rbrace\GEN,\IGEN,
@@
 
-\paragraph{Discussion on the generality of unforgeability in \UAS schemes.} %
-% The notion of signature unforgeability we present for \UAS is strictly more
-% general than the corresponding one of traceability for group signatures. This is
-% again a direct consequence of the fact that \Open can return an arbitrary
-% function of the signer's key and credentials (and signed message), which is a
-% strict generalization of the conventional \Open. Although, even in that case, we
-% need to take into account attributes, and the fact that the same user may obtain
-% multiple credentials (that is why, even when having \Open return the identity of
-% the signer, our notion is not exactly the same). In this sense, the sign
-% unforgeability notion for \UAS is equivalent to that of anonymous
-% credentials. It would seem, though, that we do not need the traceability part of
-% group signatures; after all, it is the protection against wrong claims on
-% attributes what enables meaningful and flexible authentication. However, the
-% type of protection against misuses of the open functionality that we can
-% get with an honest issuer (as in traceability) is much higher than without an
-% honest issuer (as in non-frameability). Specifically, with an honest issuer we
-% can ensure that the adversary cannot even alter the value returned by \Open on
-% signatures by corrupt users, nor the output of the signing predicate \feval.
-% Whereas, with a corrupt issuer, all we can ensure is that
-% the adversary cannot forge a signature from an honest user for which \Open
-% returns the same value as a signature by that honest user would produce; and,
-% certainly, a corrupt issuer can arbitrarily issue credentials meeting any
-% desired predicate \feval. Signing unforgeability is, therefore, a core property
-% to ensure accountability.
-
-% Similarly, by adding the related notion of issuance unforgeability, we ensure
-% that no credential can be issued that did not meet the corresponding issuance
-% policy. This is again something not necessary in group signatures (with
-% verifiable openings), where \Judge accepting the opening proof implies that
-% there is a valid join transcript associated to the membership credential used
-% to produce the signature. However, in \UAS, given that the credentials contain
-% attributes, even though that transcript exists, we need to make sure that the
-% issuance policy over these attributes was satisfied -- and this is not something
-% (easily) extractable from the signature.
+\paragraph{On the generality of unforgeability in \UAS schemes.} %
+Regarding the information revealed at signature time ($\yeval^0$), \UAS's
+unforgeability notion is equivalent to that of known AC schemes. It is the
+generalization of the information output at opening time ($\yinsp$), only
+present up to know in MPS \needcite what makes the notion of unforgeability more
+subtle. The fact that multiple users may produce signatures opening to the same
+value necessarily forces to generalize what is a forgery -- and, certainly,
+resorting to extraction-based techniques seems unavoidable.
+
+As for anonymity, note that by tweaking the \fissue, \feval and \finsp
+functions, one can easily mimic behaviour of more restricted schemes. For
+instance, \feval, along with the $\yeval^0$ output, allows revealing
+authenticated attribute-related information alongside the signatures, as in AC
+schemes. Or, with \fissue, rules for delegation can be easily encoded, leading
+to delegatable schemes.
 
@@
 values than the ones output when evaluating or opening a signature by an honest
-user. As a concrete example, imagine an open function that returns the
-nationality of the signer. In any country, there will be many users (corrupt or
-not) sharing nationality.
+user.
 %
@@
 included in user credentials, the adversary may even be able to just produce
-``legitimate'' openings that output any desired value.
-
-Thus, we again need to resort to extraction techniques. In the non-frameability
-definition for \UAS, given in experiment \ExpNonframe in
+``legitimate'' openings that output any desired value. Note that this is a
+relevant property, as it tells us the minimal unforgeability expectations we
+can have, even against malicious issuers and openers.
+
+In the non-frameability definition for \UAS, given in experiment \ExpNonframe in
 \figref{fig:exp-uas-frame}, the adversary is challenged to produce a signature
 and opening proof that is accepted by \Verify and \Judge, respectively. From
-the signature, we then extract the secret key of the signer, and match it
-against the secret keys of the honest users. The adversary wins if there is a
-match and the signature has not been queried to \SIGN, or if the value \yinsp
-output by the adversary is accepted by \Judge, yet it is different from the
-extracted $\yinsp'$ value. In the game, the
-adversary has access to the oracles in $\Oframe \gets \lbrace\HU,\CU\rbrace\GEN,
-\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG,\OBTAIN,\SIGN$.
+the signature, we then extract the secret data used to generate it. The
+adversary wins if the signature and opening proof are accepted, but the \yeval
+or \yinsp values do not match what they should be based on the extracted data;
+or if the signature can be associated to the secret key of an honest user who
+did not produce it (i.e., no matching call to \SIGN exists). In the game, the
+adversary has access to the oracles in $\Oframe \gets
+\lbrace\HU,\CU\rbrace\GEN, \lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,
+\WREG,\OBTAIN,\SIGN$.
 
@@
 
-\paragraph{Discussion on the generality of non-frameability in \UAS schemes.} %
+\paragraph{On the generality of non-frameability in \UAS schemes.} %
+The notion captured in \UAS is a sort of extension of the non-frameability
+notion in group signatures, in two aspects. First, by defining a very granular
+\finsp function (one that outputs the signers public key, or equivalent),
+we get a scheme in which it is not possible to frame a user at all. Yet, by
+defining a coarser \finsp function (e.g., one that outputs the nationality of
+the signer), while framing a single user is still not possible (the checks in
+lines 9 an 10 avoid it), in practice, there will be a set of ``potential
+candidates to frame'' (e.g., all users of the given nationality). This can be
+seen as a useful feature in many use cases, though.
+%
+The second aspect follows a similar reasoning, but through \feval. However, this
+type of functionality revealing information at signing time is not available in
+group signatures. Also, even though it is available in anonymous credentials, no
+equivalent property has been considered, to the best of our knowledge. Thus,
+through \UAS schemes, we extend the unforgeability expectations against corrupt
+issuers, to the AC domain.
+
 % Anonymous credentials do not have non-frameability property and, thus, it is
@@
 \begin{description}
-\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs via \fissue the rules for
-  issuing new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
+\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs the rules for issuing new
+  credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
   (\usk,\scred,\attrs_{\scred},r), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
-  \CCommit(usk;r) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
-  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1 \rbrace$,
+  \CCommit(usk;r) \land \forall \cred \in \scred,\SBCMVerify(\ipk_{\cred},\cred,
+  \usk,\attrs_{\cred}) = 1 \land \fissue(\usk,\scred,\attrs) = 1 \rbrace$,
   where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
   \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
-  Basically, this relation requires that, in order to issue a credential with
-  attribtes \attr, and bound to \usk, the requester has to commit to \usk and
-  prove knowledge of it, as well as prove that all additional credentials needed
-  for the issuing to be granted, meet some defined policy \fissue.
+  The relation requires that the owner commits to, and proves knowledge of,
+  \usk. It also requires that any additional credential supporting the request
+  be a valid credential (signed by some other issuer) and bound to \usk.
+  Finally, the policy defined by \fissue needs to be satisfied.
 \item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
   verifiers define them. Governs via \feval and \finsp what utility
-  information is directly revealed by signatures, or extracted by openers.
+  information is directly revealed by signatures, or extractable by openers.
   It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
@@
 
+Note that, besides the extensibility introduced via \fissue, \feval and
+\finsp, some aspects of the previous functions could be modified (e.g., one
+could require issuer public keys to be kept private). However, the previous
+relations seem generic enough for a wide variety of applications.
+%
+From the previous relations, we define the functionality as follows:
+
 \paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
-The setup process essentially consists on generating the public parameters
-for all the building blocks. In detail, it parses \secpar as $(\Csecpar,
-\NIZKsecpar,\SBCMsecpar,\Esecpar)$. Then, run $\Cparm \gets
+The setup process essentially generates the public parameters for all the
+building blocks. It parses \secpar as $(\Csecpar,\NIZKsecpar,\SBCMsecpar,
+\Esecpar)$. Then, run $\Cparm \gets
 \CSetup(\Csecpar)$, $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$, $\Sparm \gets
@@
 \Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Open},
-\AttrSpace)$. Note that many of these parameter setup algorithms can
-actually be run by separate entities (respecting some commonalities like,
-e.g., same pairing-friendly curves). For instance, each opener could
-run its own \ESetup algorithm, or each verifier its
-$\NIZKSetup^{\NIZKRel_{\Sign}}$, to advertise the signing evaluation functions
-it accepts. For simplicity of exposition, we bundle them together here.
+\AttrSpace)$. Many of these parameter setup algorithms can
+actually be run by separate entities. For simplicity of exposition, we bundle
+them together here.
 
 \paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
-To generate its key pair, each issuer first parses \parm as $(\cdot,\SBCMparm,
+Each issuer first parses \parm as $(\cdot,\SBCMparm,
 \Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets
@@
 \paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
-To generate its key pair, each opener first parses \parm as $(\cdot,\cdot,
+Each opener first parses \parm as $(\cdot,\cdot,
 \cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets \SKeyGen
@@
 with secret key \usk and credentials \scred, where each $\cred \in \scred$ is
-issued by an issuer with
-public key $\ipk_{\cred}$ (which we assume that the user can easily retrieve,
+issued by an issuer with public key $\ipk_{\cred} \in \sipk$ (which we assume
+that the user can easily retrieve,
 e.g., from secure storage, given \cred), and attests attributes
@@
 is the result of the interactive signing protocol, and the \utrans entry for
-the issuer is its transcript which is a $(\Ccom,\attrs,\sipk,\cred,\pi)$ tuple.
-
-\iffalse
-\begin{itemize}
-\item \uline{User}: Commit to the user secret key with $\Ccom \gets
-  \CCommit(\usk)$. Compute proof $\NIZKproof \gets
-  \NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\usk,\scred,\attrs_{\scred}),
-  (\Ccom,\attrs,\sipk_{\scred}))$. Send $(\Ccom,\NIZKproof)$ to Issuer.
-\item \uline{Issuer}: Verify \NIZKproof with $\NIZKVerify^{\NIZKRel_{\Issue}}
-  (\NIZKcrs_{\Issue},\NIZKproof,(\Ccom,\attrs,\sipk))$, and abort if it fails. Then,
-  compute the credential by running $\cred \gets \SBCMSign(\SBCMsk,\Ccom,
-  \attrs)$. Send \cred to User. Output $\utrans \gets (\Ccom,\attrs,\sipk,
-  \cred,\NIZKproof)$.
-\item \uline{User}: Verify the credential with $\SBCMVerify(\SBCMvk,\cred,
-  \attrs \cup \lbrace \usk \rbrace)$. Reject if verification fails.
-  Otherwise, return \cred.
-\end{itemize}
-\fi
+the issuer is its transcript, which is a $(\Ccom,\attrs,\sipk,\cred,\pi)$ tuple.
 
@@
 % 
-From this, in order to produce a valid signature, the user first evaluates
-$(\yeval^0,\yeval^1) \gets \feval (\usk,\scred,\msg)$, and decides whether or
-not to continue with the signing process -- this may depend, e.g., on the
-opening policy of \opk, as the output of \feval may influence whether the user
-will be de-anonymizable or not, depending on the \finsp function in \opk.
-%
-The user also computes a random encryption key pair with $(\widetilde{\Eek},
+The user first evaluates $(\yeval^0,\yeval^1) \gets \feval (\usk,\scred,\msg)$,
+and computes a random encryption key pair with $(\widetilde{\Eek},
 \widetilde{\Edk}) \gets \EKeyGen(\Eparm)$. Then, the user parses \opk as $(\Svk,\Eek,
 \finsp,\sig_{\finsp})$ and checks that $\Verify(\Svk,\sig_{\finsp},\finsp) = 1$
-(note that this step may be cached), to compute $\yinsp \gets \finsp((\yeval^0,
+(this step may be cached), to compute $\yinsp \gets \finsp((\yeval^0,
 \yeval^1),\usk,\scred,\msg)$, and separately encrypts both $\yeval^1$ and
@@
 \sipk_{\scred},\Eek,\widetilde{\Eek}))$ and outputs $(\sig = (\NIZKproof,\ceval,
-\cinsp),\yeval^0)$.
+\cinsp),\yeval^0)$. Note that, depending on the value of \Yeval and \yinsp, the
+user may decide to abort the signing if the resulting values are too
+privacy-threatening.
 
 \paragraph{$1/0 \gets \Verify(\opk,\sipk,\Sig,\msg,\feval)$.} %
-The ``cryptographic'' side of the verification essentially consists on checking
+The ``cryptographic'' side of the verification consists on checking
 the NIZK proof. That is, parse \Sig as $(\sig = (\NIZKproof,\cinsp),\yeval,
@@
 verification passes, and reject otherwise.
+
+\paragraph{Interactive Credential Presentation.} In \appref{app:interactive-uas}
+we show how to convert the non-interactive signing and verification processes
+into an interactive protocol. While the transformation is quite straightforward,
+it is of high relevance for real world use cases.
 
@@
 \begin{theorem}[Issuance anonymity of \CUASGen]
-  \label{thm:iss-anonymity-uas}
+  \label{thm:issue-anonymity-uas}
   If the NIZK systems used for $\NIZKRel_{\Issue}$ and $\NIZKRel_{\Sign}$ are
   zero-knowledge, our \CUASGen construction satisfies issuance anonymity as
-  defined in \defref{def:iss-anonymity-uas}.
+  defined in \defref{def:issue-anonymity-uas}.
 \end{theorem}
 
-\begin{proof}[\thmref{thm:iss-anonymity-uas}; Issuance anonymity of \CUASGen]
+\begin{proof}[\thmref{thm:issue-anonymity-uas}; Issuance anonymity of \CUASGen]
   We prove the special case in which the adversary makes only one query to the
@@
 
-\subsection{\CUASGen with Interactive Sign and Verify}
-\label{ssec:interactive-uas}
-
-\todo{The following was written for \GSAC. It should apply for \UAS, but check
-  and adapt.}
-
-In group signatures, the signing and verification process is non-interactive.
-That is, a group member produces a signature and eventually sends it to the
-verifier, who can check it without further interaction. Nevertheless, in
-anonymous credentials, this process is typically interactive, and consists of
-at least one round-trip. This can be useful, for instance, when some notion of
-freshness is necessary.
-
-The approach to turn our non-interactive singing-verification into an
-interactive protocol that ensures freshness is evident: prior to signing the
-message, we require that the honest verifier sends to the user a number picked
-uniformly at random from an appropriate domain, which must be concatenated to
-the signed message. If there is no need to actually sign a message, then the
-message is set to an empty string, and the user only signs the random number.
-%
-Syntactically, instead of having non-interactive $\sig \gets \Sign(\gpk,\usk,
-\cred,\dattrs,\msg)$ and $1/0 \gets \Verify(\gpk,\sig,\dattrs,\msg)$ algorithms,
-we have a $1/0 \gets \langle \Sign(\gpk,\usk,\cred,\dattrs),\Verify(\gpk,
-\dattrs) \rangle$ interactive protocol.
-%
-We sketch next a proof for why does this result in a secure \GSAC scheme with
-interactive signing and verification.
-
-\paragraph{Issuance Anonymity.} \todo{XXX}
-
-\paragraph{Signature Anonymity.} To see why the interactive variant is
-anonymous, assume an adversary $\adv$ against anonymity in that case. We build
-\advB against the non-interactive \ExpGSACSigAnonb from \adv~ as follows. \advB
-initializes
-everything as in the \ExpGSACSigAnonb game. When $\adv$ initiates a call to its
-interactive \SIGN (resp. \CHALb) oracle, \advB picks a random number, and sends
-it to the adversary, along with the response of its own (non-interactive) \SIGN
-(resp. \CHALb) oracle where, to the message passed as parameter to its oracle,
-concatenates the produced random number. After such simulation, \advB just
-outputs whatever $\adv$ outputs. Clearly, the simulation is perfect and, if
-$\adv$ wins with non-negligible probability in the interactive case, then so
-does \advB in the non-interactive case.
-
-\paragraph{Traceability.} The simulation described for the anonymity case (i.e.,
-\advB choosing the random numbers, and concatenating them to the message to be
-signed) applies here too. Thus, an adversary against traceability in the
-interactive case, can be used to build an adversary that breaks traceability in
-the non-interactive counterpart.
-
-\paragraph{Non-frameability.} The simulation described for the anonymity case
-(i.e., \advB choosing the random numbers, and concatenating them to the message
-to be signed) applies here too. Thus, an adversary against non-frameability in
-the interactive case, can be used to build an adversary that breaks
-non-frameability in the non-interactive counterpart.
-
 %%% Local Variables:

### 2022-06-23 prism-backend/research/gsac/introduction-paper.tex
Working on re-structure.
More passes.

@@
 message can be a different attribute, and a user who wants to simultaneously
-leverage multiple credentials needs to bound all of them to the same key. We add
+leverage multiple credentials needs to bind all of them to the same key. We add
 three generic functions: \fissue, leveraged by users to
@@
   \centering
+  \scalebox{0.9}{
     \input{figures/proof-blocks-uas.tex}
+  }
   \caption{Summary of statements proved per operation in \UAS.
@@
     signing time (accountability). Unboxed statements are fixed, and are thus
-    common to all \UAS restrictions.}
+    common to all \UAS restrictions. $\usk \coloneqq$ user secret key; $\scred
+    \coloneqq$ set of credentials.}
   \label{fig:proof-blocks-uas}
@@
   \centering
+  \scalebox{0.9}{
     \input{figures/relations.tex}
+  }
   \caption{Summary of schemes that can be instantiated as restrictions of our

### 2022-06-23 prism-backend/research/gsac/relationships.tex
More passes.

@@
 
-In the following subsections we reproduce models of related schemes in the
-literature. Then, we give concrete \fissue, \feval and \finsp functions that
-make \UAS mimic their functionality. Finally, we prove for each case that
-\UAS -- restricted with the corresponding functions -- indeed meets their
-security models, thus proving that \UAS is a generalization of all of them.
+In the following, to showcase the generality of \UAS and \CUASGen, we reproduce
+models of related schemes in the literature -- some of them slightly adapted.
+Then, we give concrete $(\fissue,\feval,\finsp)$-\CUASGen restrictions and prove
+that they securely instantiate the models for the presented schemes.
 
 \subsection{Group Signatures}
-\label{sapp:related-models-gs}
+\label{ssec:related-models-gs}
 
@@
 
-\todo{Introducing $(f,g,h)-\CUASGen$ naming convention. Describe it elsewhere.}
-
 \begin{proof}
@@
 
-\subsection{Group Signatures with Message Dependent Opening}
-\label{sapp:related-models-gsmdo}
-
-We cannot build the exact same functionality, nor follow the exact same security
-model as in the group signatures with message dependent opening (GS-MDO) scheme
-described in \cite{ehk+19}. Simply because, therein, the opening functionality
-is divided in two authorities: the admitter, who decides which messages are
-subject to be opened or not, and generates a token that enables opening
-signatures over such messages; and the opener, who performs the actual opening,
-but cannot do it without the tokens generated by the admitter. Intuitively, this
-can be seen as a sort of ``distribution'' of the opening capability. We define
-a variant of this model in which the admitter and opener are combined back into
-one entity (the opener), who can only open signatures over predefined messages,
-but cannot open any other signature. Moreover, our variant directly supports the
-scenario of multiple such openers, each being able to open only signatures
-over different messages. Note that it would not be hard to apply thresholding
-techniques to extend this case so that our ``unified'' opener role is shared
-across multiple entities, who have to cooperate in order to open a signature
-\needcite, thus achieving something very close ``in spirit'' to the scheme in
-\cite{ehk+19}. In addition, while \cite{ehk+19} follows the static group
-signature setting, we move to the dynamic one. Informally, our variant of GS-MDO
-is composed of the following algorithms: \Setup,
-\IKeyGen, \OKeyGen, \UKeyGen, \Sign, \Verify, \Open; as well as the $\langle
-\Obtain, \Issue \rangle$ interactive protocol. \OKeyGen generates an opening
-key pair which is already configured to open signatures only over some fixed
-(but arbitrary) set of messages. The remaining algorithms are as usual, so we
-defer a more detailed description to the construction. The oracles are the same
-as in \UAS. The resulting security model is given in \figref{fig:model-gsmdo},
-which we adapt from \cite{ehk+19}.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.45\textwidth}        
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gsmdo}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets \IKeyGen(\parm) \\
-        b^* \gets \adv^{\mathcal{O}^{anon}}(\parm,\ipk) \\
-        \pcreturn b^*
-      }
-
-      \vspace*{5em}
-
-      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gsmdo}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets \IKeyGen(\parm) \\
-        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
-        (\ipk,\isk) \\
-        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
-        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
-        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
-        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
-        GSig(\PRVUK[\upk],\msg) \\
-        \pcreturn 0
-      }       
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.55\textwidth}
-      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gsmdo}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets \IKeyGen(\parm) \\
-        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{trace}}
-        (\ipk,\opk,\osk) \\
-        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
-        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
-        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
-        = 0: \\ 
-        \pcind \pcreturn 1 \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for our GS-MDO variant.
-    $\mathcal{O}^{anon} \gets \lbrace \OGEN^{\smsg},\HUGEN,\CUGEN,\WREG,
-    \OBTAIN,\SIGN,\OPEN,\CHALb \rbrace$; $\mathcal{O}^{trace} \gets \lbrace
-    \OGEN,\HUGEN,\CUGEN,\ISSUE,\OBTISS,\RREG,\SIGN \rbrace$;
-    $\mathcal{O}^{frame} \gets \lbrace \OGEN,\HUGEN,\CUGEN,\WREG,
-    \OBTAIN,\SIGN \rbrace$. $\OGEN^{\smsg}$ is like \OGEN, but only accepting
-    functions of type $\finsp^{\smsg}$.
-  }
-  \label{fig:model-gsmdo}  
-\end{figure}
-
-\subsubsection{\CUASGSMDO construction.} %
-We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
-construction for \UAS, restricted to $\fissue^1$ as issuance function,
-$\feval^0$ as signature evaluation function, and $\finsp^{\smsg}$ as opening
-function, is a secure group signature scheme with message dependent opening
-as modelled in \figref{fig:model-gsmdo}. We first quickly define the algorithms,
-and then prove security.
-
-\begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.] Like in vanilla \CUASGen.
-\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Like the \UKeyGen function for
-  \CUASGS, in \secref{sapp:related-models-gs}.
-\item[$\langle \cred,\utrans \rangle \gets
-  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Like the corresponding
-  protocol in in vanilla \CUASGS, \secref{sapp:related-model-gs}.
-\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Like in vanilla \CUASGen, limited
-  on evaluation functions $\feval^0$ and opening functions $\finsp^{\smsg}$.
-\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Like in vanilla \CUASGen.
-\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Like in vanilla
-  \CUASGen.
-\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Like in vanilla \CUASGen.
-\end{description}
-
-\paragraph{Security of \CUASGSMDO.} %
-Our \CUASGSMDO construction is a secure group signature scheme,
-according to the model in \figref{fig:model-gsmdo}, if the underlying \CUASGen
-construction is secure.
-
-Note that both  model construction are essentially restrictions to the model
-and construction of \CUASGen. Thus, security directly follows from security of
-\CUASGen.
-
-% \begin{theorem}[Anonymity of \CUASGSMDO]
-%   If the base \CUASGen construction is anonymous according to
-%   \defref{def:anonymity-uas}, then \CUASGSMDO is an anonymous group signature
-%   scheme.
-% \end{theorem}
-
-% \begin{proof}
-
-%   \qed
-% \end{proof}
-
-% \begin{theorem}[Traceability of \CUASGSMDO]
-%   If the base \CUASGen construction has unforgeable signing according to
-%   \defref{def:sign-forge-uas}, then \CUASGSMDO is a traceable group signature
-%   scheme.
-% \end{theorem}
-
-% \begin{proof}
-%   Traceability follows directly from the corresponding proof for \CUASGS.
-%   \qed
-% \end{proof}
-
-% \begin{theorem}[Non-frameability of \CUASGSMDO]
-%   If the base \CUASGen construction is non-frameable according to
-%   \defref{def:frame-uas}, then \CUASGSMDO is a non-frameable group signature
-%   scheme.
-% \end{theorem}
-
-% \begin{proof}
-%   Non-frameability follows directly from the corresponding proof for \CUASGS.
-%   \qed
-% \end{proof}
-
 \subsection{Ring Signatures}
-\label{sapp:related-models-rs}
+\label{ssec:related-models-rs}
 
@@
 \subsection{Anonymous Credentials}
-\label{sapp:related-models-ac}
+\label{ssec:related-models-ac}
 
@@
 \subsection{Delegatable Anonymous Credentials}
-\label{sapp:related-models-dac}
+\label{ssec:related-models-dac}
 
@@
 
-\subsection{Revocable Anonymous Credentials}
-\label{sapp:related-models-rac}
-
-In \cite{cks10}, revocable anonymous credentials are proposed. From \CUASGen, it
-is straightforward to build an AC system with verifier local revocation, like in
-\cite{bs04}. Basically, all credentials get an identifier as first attribute,
-and \feval functions prove that the opener can retrieve that identifier. Then,
-in case of needing to revoke a concrete credential, any verifier can interact
-with the opener to add an identifier to its own revocation list (alternatively,
-there can be a public list of revoked credentials). Having \feval functions
-prove that the credential identifier does not belong to that list thus directly
-implements privacy-preserving revocation. We first give a simple model in
-\figref{fig:model-rac}, extending that in \appref{sapp:related-models-ac}. As
-before, for simplicity we assume only one credential is used per authentication
-(the extension being direct). To the functionality in
-\appref{sapp:related-models-ac}, we now explicitly add the $OKeyGen$ function
-(equivalent to \OKeyGen, with a fixed \finsp function),
-which generates the opener key pair, extend $Verify$ to receive also a list $L$
-of revoked identifiers, and we add a function (and corresponding oracle) $id/\bot
-\gets RetrieveCredId(\osk,\utrans)$ that can extract the identifier of the
-credential used in a presentation transcript \utrans -- and which is essentially
-equivalent to \Open in \UAS. For simplicity, we do not include the equivalent to
-verifiable openings, but this would be straightforward.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.45\textwidth}
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\opk,\osk) \gets \OKeyGen(\parm) \\        
-        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
-        b^* \gets \adv^{\mathcal{O}_{anon}}(\parm,\ipk,\opk) \\
-        \pcreturn b^*
-      }        
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.55\textwidth}
-      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\opk,\osk) \gets \OKeyGen(\parm) \\        
-        (\ipk,\isk) \gets IssKeyGen(\parm) \\
-        (D,L,\st) \gets
-        \adv^{\mathcal{O}_{forge}}(\parm,\ipk) \\
-        \langle \cdot,(b,\utrans)\rangle
-        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
-        \pcif b = 0: \pcreturn 0 \\
-        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
-        \land D \subseteq \ATTR[j]): \pcreturn 1 \\    
-        h \gets RetrieveCredHandle(\osk,\utrans) \\
-        \pcif h \in L \lor h = \bot: \pcreturn 1 \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for revocable anonymous credentials with selective
-    disclosure based on \cite{fhs19}. 
-    $\mathcal{O}_{anon} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
-    ReqCredHandle,LoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace HU,CU,
-    Obtain,ObtIss,Issue,Show,ReqCredHandle \rbrace$. $ReqCredHandle$ is
-    equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
-    Also, \OWNR and \ATTR tables are essentially as in \secref{ssec:model-uas}.}
-  \label{fig:model-rac}  
-\end{figure}
-
-\subsubsection{\CUASRAC Construction.} %
-
-For our RAC construction, we define signature evaluation and opening functions
-as follows:
-
-\begin{align}
-  & \feval^{\dattrs,F,V,L}(\usk,\cred,\msg) \coloneqq
-    \lbrace
-    \pcif F(V,\attrs_1(\cred)) \in L: \pcreturn (0,0);
-    \pcelse \pcreturn (\dattrs(\cred),V)
-    \rbrace \nonumber \\
-  & \finsp^{F}((\yeval^0,\yeval^1),\usk,\cred,\msg) \coloneqq
-    \lbrace
-    \pcif \yeval^0 \neq 0: \pcreturn F(\yeval^1,\attrs_1(\cred));
-    \pcelse \pcreturn 0
-     \rbrace
-  \label{eq:funcs-rac}
-\end{align}
-
-Where, $\feval^{\dattrs,F,V,L}$ is parameterized with a one-way function $F$
-(e.g., a cryptographic hash), some constant subset \dattrs of attributes to be
-selectively disclosed by signers, a string identifying the verifier $V$ and a
-list $L$ of ``revocation handles'' by this verifier. If the credential used for
-signing has been revoked (i.e., if $F(V,id) \in L$), then \feval returns $0$, as
-an indication that the signature should be rejected by the verifier. Otherwise,
-it sets $\yeval^0 \gets \dattrs(\cred)$, and $\yeval^1 \gets V$ -- note that
-$\yeval^1$ will be encrypted with a single-use key pair.
-%
-On the other hand, $\finsp^{F}$ outputs $F(\yeval^1,\attrs_1(\cred))$, allowing
-valid signatures to be locally revocable by $V$ at a later stage, since
-$\yeval^1=V$.
-
-\begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
-  \CUASGen.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
-  \CUASGen construction, setting $\fissue^1$ as issuance function.
-\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
-  \CUASGen construction, setting $\finsp^F$ as opening function.
-\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
-  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
-\item[$\langle \cred/\bot,\top/\bot \rangle \gets
-  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
-  $\fissue^1$ as issuance function.
-\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
-  \Verify(\ipk,\dattrs) \rangle$.]
-  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
-  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
-  $\finsp^F$ as open function.
-\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
-  Outputs the revocation handle $h$ for the credential used in the interactive
-  presentation associated to \utrans. Note that $h$ is verifier-dependent.
-\end{description}
-
-\paragraph{Security of \CUASRAC.} %
-We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
-scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
-is anonymous and has unforgeable signing. Note that issuance unforgeability
-of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
-leveraging other credentials not any fixed custom issuance policy. Thus,
-signature unforgeability from \UAS is enough. Note that AC schemes modelled
-as in \cite{fhs19} do not have issuance anonymity, as the user public key
-is passed to the issuer.
-
-\begin{theorem}[Anonymity of \CUASRAC]
-  \label{thm:anon-cuasac}
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASAC is an
-  anonymous AC scheme according to \cite{fhs19}.
-\end{theorem}
-
-\begin{proof}
-  Given \adv~ against anonymity of \CUASRAC as defined in
-  \figref{fig:model-rac}, we build an adversary \advB against anonymity of
-  \CUASGen as defined in \defref{def:sign-anonymity-uas}.
-
-  First observe that, given a revocation handle $F(V,id)$ extracted from any
-  credential showing, it is not possible to extract $id$, as $F$ is one-way.
-
-  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
-  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
-  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, of \OPEN respectively.
-  Note that ``translating'' the inputs from the former into inputs for the
-  latter is trivial. Also, observe that $ReqCredHandle$ essentially refuses to
-  open transcripts from challenge users (signatures, in the non-interactive
-  equivalent), as $F(V,\attrs_1(\ccid_0) \neq F(V,\attrs_1(\ccid_1)$ with
-  overwhelming probability (see the $\tyinsp \neq \yinsp$) check in
-  \figref{fig:oracles2}. Obviously, if \adv~ wins in its anonymity game, then
-  so does \advB with the same probability.
-  % 
-  \qed
-\end{proof}
-
-\begin{theorem}[Unforgeability of \CUASRAC]
-  If the base \CUASGen construction has sign unforgeability according to
-  \defref{def:sign-forge-uas}, and $F$ is one-way, then \CUASRAC is an
-  unforgeable RAC scheme.
-\end{theorem}
-
-\begin{proof}
-  Given \adv~ against unforgeability of \CUASRAC as defined in
-  \figref{fig:model-rac}, we build an adversary \advB against sign
-  unforgeability of \CUASGen as defined in \defref{def:sign-forge-uas}.
-
-  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
-  that \adv~ wins its game via the winning condition of line 6 in the RAC
-  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
-  that the probability of \adv~ winning its game via the winning condition at
-  line 9 is negligible, due to soundness of the NIZK scheme used for signing,
-  and the one-wayness of $F$ in $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.  
-  %
-  \qed
-\end{proof}
-
 \subsection{Multimodal Private Signatures}
-\label{sapp:related-models-mps}
+\label{ssec:related-models-mps}
 

### 2022-06-24 prism-backend/research/gsac/formal-uas.tex
Restructured some content.

@@
 \begin{description}
-\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs the rules for issuing new
-  credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
+\item[$\NIZKRel_{\Issue}$:] For NIZK proofs at issuance time. It is defined as
+  $\NIZKRel_{\Issue} = \lbrace
   (\usk,\scred,\attrs_{\scred},r), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
@@
   Finally, the policy defined by \fissue needs to be satisfied.
-\item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
-  verifiers define them. Governs via \feval and \finsp what utility
-  information is directly revealed by signatures, or extractable by openers.
-  It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
+\item[$\NIZKRel_{\Sign}$:] For NIZK proofs at signing time. It is defined as
+  $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
   \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
@@
   = 1) \rbrace$, with $\attrs_{\scred}$ and $\sipk_{\scred}$ as in
-  $\NIZKRel_{\Issue}$. In a
-  nutshell, this relation ensures that signatures will produce the correct
-  signature evaluation and opening values, and that any credential used to
-  create the signature is bound to the same \usk key.
-\item[$\NIZKRel_{\Open}$:] Ensures that the utility information extracted by
-  the \Open algorithm is correct. It is defined as $\NIZKRel_{\Open} =
+  $\NIZKRel_{\Issue}$. This relation ensures that signatures will produce the
+  correct signature evaluation and opening values, and that any credential used
+  to create the signature is bound to the same \usk key.
+\item[$\NIZKRel_{\Open}$:] For NIZK proofs at opening time. Ensures that the
+  utility information extracted by the \Open algorithm is correct. It is defined
+  as $\NIZKRel_{\Open} =
   \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$.
@@
 
-First, we define the \ExtractIssue, \ExtractSign, \IdentifyCred and \IdentifyUK
-functions that are needed for some of the properties to be meaningful, in
-\figref{fig:helper-funcs}.
-
-\begin{figure}[ht!]
-  \begin{minipage}[t]{\textwidth}
-    \procedure{$\ExtractIssue(\parm,\utrans)$}{%
-      \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Issue},\cdot,
-        \cdot,\cdot)$; $\NIZKcrs_{\Issue}$ as $(\NIZKcrs,\NIZKtrap)$; and
-        \utrans as $(\Ccom,\sipk,\cred,\NIZKproof)$} \\
-      \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\Ccom,\attrs,\sipk)): 
-      \pcreturn \bot \\
-      (\usk,\scred,\attrs_{\scred}) \gets \NIZKExtract(\NIZKcrs,\NIZKtrap,
-      (\Ccom,\attrs,\sipk),\NIZKproof) \\
-      \pcreturn (\usk,\attrs,\scred,\attrs_{\scred}) \\
-    }
-
-    \procedure{$\ExtractSign(\parm,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
-      \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
-        \cdot,\cdot)$; $\NIZKcrs_{\Sign}$ as $(\NIZKcrs,\NIZKtrap)$; and
-        \sig as $(\NIZKproof,\Ec)$} \\
-      \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \gets
-        \PUBIK[\siid]$} \\
-      \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,
-      \sipk,\opk)): \pcreturn \bot \\
-      (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets \NIZKExtract(\NIZKcrs,
-      \NIZKtrap, (\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk,\opk,\widetilde{\Eek}),
-      \NIZKproof) \\
-      \pcreturn (\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \\
-    }
-
-    \procedure{$\IdentifyCred(\usk,\attrs_{\cred},\cred)$}{%
-      \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
-    }
-
-    \procedure{$\IdentifyUK(\uid,\usk)$}{%
-      \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
-      \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
-      \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trans[\cid]) \\
-      \pcind \pcif \usk = \usk': \pcreturn 1 \\
-      \pcreturn 0
-    }
-  \end{minipage}
-  \label{fig:helper-funcs}
-  \caption{Definition of helper functions \ExtractIssue, \ExtractSign,
-    \IdentifyCred, and \IdentifyUK, for \CUASGen.}
-\end{figure}
+We state the correctness and security theorems next. For lack of space, we defer
+the proofs to \appref{app:uas-proofs}.
 
@@
   If the underlying schemes for commitments, public-key encryption and \SBCM,
-  are correct,
-  as well as the NIZKs for $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
-  $\NIZKRel_{\Open}$, our generic construction \CUASGen satisfies correctness as
-  defined in \defref{def:correctness-uas}.
+  are correct, as well as the NIZKs for $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$,
+  and $\NIZKRel_{\Open}$, our generic construction \CUASGen satisfies
+  correctness as defined in \defref{def:correctness-uas}.
 \end{theorem}
-
-\begin{proof}[\thmref{thm:correctness-uas}; Correctness of \CUASGen]
-  By correctness of \SBCM and the NIZK for $\NIZKRel_{\Sign}$, the signature
-  produced at line 5 of \ExpCorrect is accepted at line 6 by \Verify.
-  Moreover, all the credentials employed to honestly produce the signature,
-  identified with \scid, meet their respective issuance policies due to
-  correctness of the NIZK for $\NIZKRel_{\Issue}$, so no $\fissue^\cid$ check
-  returns $0$ at line 9. Similarly, as $\feval \in \famfeval$ is checked at
-  line 3, and due to correctness of the NIZK for $\NIZKRel_{\Sign}$, the
-  output of \feval matches $\yeval^0$ at line $11$, which must have been
-  computed over $\usk=\UK[\uid]$, as in line $10$, due to correctness of the
-  commitment scheme. Finally, correctness of the NIZKs for $\NIZKRel_{\Sign}$
-  and $\NIZKRel_{\Open}$, and correctness of the encryption scheme, ensure that
-  \Judge accepts the proof produced by \Open, and \yinsp is the correct value
-  for the chosen $\finsp^{\oid}$.
-\end{proof}
 
@@
 
-\begin{proof}[\thmref{thm:issue-anonymity-uas}; Issuance anonymity of \CUASGen]
-  We prove the special case in which the adversary makes only one query to the
-  \OBTCHALb oracle. The generalization to polynomially many queries follows from
-  a standard hybrid argument.
-
-  Let $G_0=\ExpIssAnonb(1^\secpar)$. We define $G_1$ by replacing the calls to
-  \NIZKSetup in $G_0$, for the $\NIZK^{\Issue}$ and $\NIZK^{\Sign}$ systems by
-  calls to their corresponding \NIZKSimSetup. By zero-knowledgeness of the
-  NIZKs, both games are indistinguishable.
-
-  Next, we simulate the NIZK proofs produced by \Obtain within the \OBTCHALb
-  oracle and, consequently, the NIZK proofs produced by \Sign in \SIGN for
-  signatures from the challenge user and credentials. Then, we show that the
-  adversary cannot distinguish executions for $b=0$ from executions for $b=1$,
-  except with negligible probabability.
-
-  More concretely, on the one hand, let $G_1^0$ to be $G_1$, conditioned on
-  $b=0$. Concretely, the proofs sent by the challenge user $\cuid_0$ to the
-  adversarial issuer are of
-  the form $\pi^*_0 =\NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\UK[\cuid_0],
-  \CCRED[\cscid_0],\ATTR[\cscid_0],r),(\Ccom,\attrs,\PUBIK[\cscid_0]))$. The
-  NIZK proofs included in the signatures produced by $\cuid_0$ are defined
-  correspondingly, but for $\NIZK^{\NIZKRel_{\Sign}}$. From $G_1^0$, we define
-  $G_2^0$, but instead of using \NIZKProve, we use \NIZKSim (for both \Issue
-  and \Sign). That is, the proofs for credential requests are generated as
-  $\pi^s_0 =\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\tau,(\Ccom,\attrs,
-  \PUBIK[\cscid_0]))$. By zero-knowledge of the NIZK systems for \Issue and
-  \Sign, $G_2^0$ is indistinguishable from $G_1^0$.
-
-  On the other hand, following the same process for $G_1^1$ and $G_2^1$.
-  Concretely, for the case of the proofs at issuance time, they are of the
-  shape $\pi^s_1 =\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\tau,(\Ccom,\attrs,
-  \PUBIK[\cscid_1]))$. Note first that $\PUBIK[\cscid_1] = \PUBIK[\cscid_0]$,
-  by definition of the \OBTCHALb oracle. Hence, the produced proofs are exactly
-  the same independently on the value of the bit $b$.
-
-  Thus, $\AdvIssAnon=|\Pr\lbrack
-  \ExpIssAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpIssAnonz(1^\secpar)=1\rbrack|$.
-  As argued, $G_1$ is indistinguishable from $\ExpIssAnonb$, so
-  $\AdvIssAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
-  G_1^0(1^\secpar)=1\rbrack| \approx
-  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
-  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
-  \AdvIssAnon is negligible.
-
-\end{proof}
-
 \begin{theorem}[Signature anonymity of \CUASGen]
@@
 
-\begin{proof}[\thmref{thm:sign-anonymity-uas}; Signature anonymity of \CUASGen]
-  \iffalse
-  First, we define \SimSetup, \SIMOBTAIN, \SIMSIGN and \SIMOPEN as in
-  \figref{fig:anon-sim}.
-
-  \begin{figure}[ht!]
-    \begin{minipage}[t]{\textwidth}
-      \procedure{$\SimSetup(\secpar,\AttrSpace)$}{%
-        \textrm{Parse}~\secpar~\textrm{as}~(\cdot,\secpar_{\NIZK},\cdot,\cdot) \\
-        (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue})
-        \gets \NIZKSimSetup^{\NIZKRel_{\Issue}}(\secpar_{\NIZK}) \\
-        (\NIZKcrs_{\Sign},\NIZKtrap_{\Sign})
-        \gets \NIZKSimSetup^{\NIZKRel_{\Sign}}(\secpar_{\NIZK}) \\
-        (\NIZKcrs_{\Open},\NIZKtrap_{\Open})
-        \gets \NIZKSimSetup^{\NIZKRel_{\Open}}(\secpar_{\NIZK}) \\
-        \textrm{Compute}~\parm \gets (\Cparm,\SBCMparm,\Sparm,\Eparm)~
-        \textrm{as in}~\Setup \\
-        \pcreturn ((\parm,\NIZKcrs_{\Issue},
-        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
-        (\NIZKtrap_{\Issue},\NIZKtrap_{\Sign},\NIZKtrap_{\Open})) \\
-      }
-
-      \begin{minipage}[t]{\textwidth}
-        \begin{minipage}[t]{0.55\textwidth}
-          \procedure{$\SIMOBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
-            \pcif \uid \notin \HU: \pcreturn \bot \\
-            \pcif \iid \notin \CI: \pcreturn \bot \\
-            \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
-            \sipk_{\scred} \gets \PUBIK[\scid] \\
-            \langle \cred, \cdot \rangle \gets
-            \langle SimObt(\attrs,\PUBIK[\iid],\sipk_{\scred}),\adv \rangle \\
-            \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
-            \pcreturn \top \\      
-          }
-        \end{minipage}
-        \begin{minipage}[t]{0.45\textwidth}
-          \procedure{$SimObt(\attrs,\ipk,\sipk_{\scred})$}{%
-            \textrm{Runs $\langle \SBCMCom^{\NIZKRel_{\Issue}},\adv \rangle$} \\
-            \pcind \textrm{using $\NIZKSim^{\NIZKRel_{\Issue}}
-              (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue},\cdot)$} \\
-            \pcind \textrm{instead of $\NIZKProve^{\NIZKRel_{\Issue}}
-              (\NIZKcrs_{\Issue},\cdot,\cdot)$}
-          }
-        \end{minipage}
-      \end{minipage}
-
-      \begin{minipage}[t]{\textwidth}
-        \begin{minipage}[t]{0.55\textwidth}
-          \procedure{$\SIMSIGN(\oid,\uid,\scid,\msg,\feval)$}{%
-            \pcif \uid \notin \HU: \pcreturn \bot \\
-            \pcif \feval \notin \famfeval: \pcreturn \bot \\
-            \Sig \gets SimSign(\PUBOK[\oid],\msg,\feval) \\
-            \SIG[\uid] \gets \SIG[\uid] \cup
-            \lbrace (\oid,\scid,\Sig,\msg,\feval) \rbrace \\
-            \pcreturn \Sig \\
-          }
-        \end{minipage}
-        \begin{minipage}[t]{0.45\textwidth}
-          \procedure{$SimSign(\opk,\msg,\feval)$}{%
-            \textrm{Like}~\Sign()~\textrm{using} \\
-            \pcind \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
-            \NIZKtrap_{\Sign},\cdot) \\
-            \pcind \textrm{instead of}~\NIZKProve^{\NIZKRel_{\Sign}}
-            (\NIZKcrs_{\Sign},\cdot,\cdot)        
-          }
-        \end{minipage}
-      \end{minipage}
-
-      \begin{minipage}[t]{\textwidth}
-        \begin{minipage}[t]{0.55\textwidth}
-          \procedure{$\SIMOPEN(\oid,\Sig,\msg)$}{%
-            \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\msg,\feval)
-            \in \SIG[\uid] \\
-            % \textrm{Parse}~\Sig~\textrm{as}~(\sig,\yeval,\ceval) \\
-            (\yinsp,\iproof) \gets
-            SimOpen(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
-            \pcif \CSIG[\Sig] \neq \bot: \\
-            \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
-              \feval$} \\
-            \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b}) \\
-            \pcind (\yinsp',\iproof') \gets
-            \Open(\PRVOK[\oid],\IK[\siid],\\
-            \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
-            \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
-            \pcreturn (\yinsp,\iproof)          
-          }
-        \end{minipage}
-        \begin{minipage}[t]{0.45\textwidth}
-          \procedure{$SimOpen(\opk,\msg,\feval)$}{%
-          }
-        \end{minipage}
-      \end{minipage}    
-    \end{minipage}
-    \label{fig:sim-anon}
-    \caption{Definition of \SimSetup, \SIMOBTAIN, \SIMSIGN, and \SIMOPEN for
-      anonymity in \CUASGen.}
-  \end{figure}
-  \fi
-
-  In this proof, we restrict to the case in which the adversary can only make
-  one query to the challenge oracle. Note however that the generalization to
-  polynomially many queries given in \cite{bsz05} applies here too (with the
-  corresponding security loss). Thus, proving security for one query to the
-  challenge oracle is enough.
-
-  We start from $G_0=\ExpSigAnonb$, and define game $G_1$ to be exactly the same
-  as $G_0$, except that, within the $\Setup$ algorithm, we replace
-  $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. By zero-knowledgeness,
-  $G_1$ is indistinguishable from $G_0$.
-
-  From $G_1$, we consider $G^0_1$, which we define to be $G_1$, for $b=0$
-  (i.e., \ExpSigAnonz, using $\NIZKSimSetup^{\Sign}$). The challenge sent to the
-  adversary is $(\csig_0,\yeval) \gets \Sign(\PRVUK[\cuid_0],\PUBOK[\oid],
-  \CRED[\scid_0],\msg,\feval)$, where $\csig_0 = (\pi_0,\Ec_{\yinsp})$, with
-  $\pi_0 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
-  \ceval,\cinsp,\PUBIK[\scid_0],\widetilde{\Eek},\PUBOK[\oid]),(\PRVUK[\cuid_0],
-  \CRED[\scid_0],\attrs_{\scid_0},\yeval^1,\yinsp,r,r'))$, $\ceval = \EEnc
-  (\widetilde{\Eek},\yeval^1;r)$, and $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$.
-  % 
-  Further, we build $G_2^0$ from $G_1^0$ by simulating the proof $\pi_0$. That
-  is, in $G_2^0$, $\csig_0 = (\pi_0^s,\ceval,\cinsp)$, where $\pi^s_0 =
-  \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
-  \ceval,\cinsp,\PUBIK[\scid_0],\PUBOK[\oid]))$. By zero-knowledgeness
-  of $\NIZK^{\Sign}$, $G_2^0$ is indistinguishable from $G_1^0$.
-
-  Similarly, we consider $G_1^1$ and $G_2^1$. That is, $G_1^1$ is $G_1$
-  for $b=1$, where the challenge
-  sent to the adversary is $(\csig_1,\yeval) \gets \Sign(\PRVUK[\cuid_1],
-  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,\ceval,
-  \cinsp)$, with $\pi_1 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
-  (\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
-  \PUBOK[\oid]),(\PRVUK[\cuid_1],\CRED[\scid_1],\attrs_{\scid_1},\yeval^1,
-  \yinsp,r,r'))$, $\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)$, and
-  $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$. As before, $G_2^1$ is built from
-  $G_1^1$, simulating $\pi_1$. That is, in $G_2^1$, $\csig_1 = (\pi_1^s,\ceval,
-  \cinsp)$, where $\pi^s_1 = \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
-  \NIZKtrap,(\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
-  \PUBOK[\oid]))$. Again, by zero-knowledge of $\NIZK^{\Sign}$, $G_2^1$ is
-  indistinguishable from $G_1^1$. Note also that $G_2^1$ and $G_2^0$ are
-  indistinguishable, due to the IND-CCA property of the encryption scheme
-  (so, the \ceval values in $\csig_0$ and $\csig_1$ are indistinguishable),
-  in the  challenge oracle used in the anonymity game, we restrict to
-  $\PUBIK[\scid_0] = \PUBIK[\scid_1]$, and the respective \cinsp values encrypt
-  the same \yinsp value (and, otherwise, \adv~is not allowed to open it).
-
-  Finally, consider the definition of $\AdvSigAnon=|\Pr\lbrack
-  \ExpSigAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpSigAnonz(1^\secpar)=1\rbrack|$. As
-  argued, $G_1$ is indistinguishable from $\ExpSigAnonb$, thus
-  $\AdvSigAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
-  G_1^0(1^\secpar)=1\rbrack| \approx
-  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
-  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
-  \AdvSigAnon is negligible.
-  % 
-  \qed
-\end{proof}
-
 \begin{theorem}[Issuance unforgeability of \CUASGen]
@@
 \end{theorem}
-
-\begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
-  We show that the probability that \fissue outputs $0$ is negligible, as well
-  as the probability that the extracted \usk is not the one that was used to
-  request some of the credentials employed to obtain the credential specified by
-  the adversary.
-  %
-  For this purpose, we define two games, $G_0=\ExpForgeIssue$, and $G_1$, which
-  is exactly the same, but where, within the \Setup algorithm, we replace
-  $\NIZKSetup^{\Issue}$ with $\NIZKSimSetup^{\Issue}$. Due to zero-knowledgeness
-  of $\NIZK^{\NIZKRel_{\Issue}}$, both games are indistinguishable.
-
-  Now, observe that the adversary is required to output a credential
-  identifier for which associated entries in \trans and \CRED exist; moreover,
-  if such a credential was produced by an issuer, we must have access to those
-  entries, as issuers are assumed to be honest.
-  %
-  Then, given that $\NIZKRel_{\Issue}$ is knowledge extractable (which is implied
-  by simulation-extractability), in game $G_1$
-  we can apply the \NIZKExtract function, which produces a tuple $(\usk,\scred,
-  \attrs_{\scred})$ from $\utrans = (\Ccom,\attrs,\sipk,\cred,\NIZKproof)$.
-  %
-  Since \NIZKproof is accepted by \ExtractIssue, from the soundness of \NIZK, we
-  know that all $\cred \in \scred$ are valid signatures over \usk, and their
-  respective $\attrs_{\cred}$. Thus, \IdentifyCred returns $1$ for all $(\usk,
-  \attrs_{\cred},\cred)$ tuples. That is, all the credentials in \scred given
-  to \fissue belong to the same user, who is the owner of \usk.
-  %
-  Finally, since issuers are honest, we know that $\ATTR[\cid] = \attrs$ and,
-  consequently, $\fissue(\usk,\scred,\ATTR[\cid]) = \fissue(\usk,\scred,\attrs)
-  = 1$, due to the soundness of \NIZK.
-  %
-  \qed
-\end{proof}
 
@@
 
-\begin{proof}[\thmref{thm:sign-forge-uas}; Sign unforgeability of \CUASGen]
-  As in \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
-  and $G_1$, which is exactly the same but where, within the \Setup algorithm,
-  we replace $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. After
-  zero-knowledgeness of $\NIZK^{\Sign}$, both games are indistinguishable.
-  %
-  Next, we show that an adversary winning $G_1$ can be used to break the
-  one-more unforgeability property of \SBCM.
-
-  If the verification at line 4 holds, then $(\msg,\feval,\yeval,\ceval,
-  \cinsp,\sipk,\opk,\widetilde{\Eek}) \in \NIZKLang^{\Sign}$. Then:
-  %
-
-  \paragraph{(a) \Judge accepts $(\yinsp,\iproof)$.} %
-  Simulation extractability of $\NIZK^{\Sign}$ thus ensures that $\cinsp =
-  \EEnc(\Eek,\yinsp)$, and since the $(\yinsp,\iproof)$ is generated honestly at
-  line 5, then \yinsp is the correct decryption of \cinsp, and  correctness of
-  $\NIZK^{\Open}$ ensures that \Judge outputs $1$ at line 6.
-
-  \paragraph{(b) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
-    pair.} Also, due to simulation extractability of $\NIZK^{\Sign}$:
-
-  \begin{itemize}
-  \item $\yeval^0 = \yeval$, where $(\yeval^0,\cdot) = \feval(\usk,\scred,
-    \msg)$, and $\yeval$ is as output by \adv~at step 2.    
-  \item $\tyeval^1 = \yeval^1$, where $(\cdot,\yeval^1) = \feval(\usk,\scred,
-    \msg)$, and $\tyeval^1$ is as extracted by \ExtractSign at line 7.
-  \end{itemize}
-
-  Thus, the probability of \adv~winning at line 9 is $0$.
-
-  \paragraph{(c) The output of \finsp matches the output of \Open.} %
-  After (a), the \yinsp value output by \Open is the correct decryption of
-  \cinsp. After (b), the $(\yeval^0=\yeval,\yeval^1)$ values output by
-  \ExtractSign match the evaluation of \feval. Thus, simulation extractability
-  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\usk,\scred,\msg)
-  = \yinsp$ and, also, that \yinsp matches the $\yinsp'$ value extracted by
-  \ExtractSign. Thus, the probability of \adv~winning at line 10 is $0$.
-
-  \paragraph{(d) All {\cred}s are bound to the same \usk.} %
-  $\NIZKRel^{\Sign}$ includes a condition that $\forall \cred \in \scred,
-  \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1$. Thus, simulation
-  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
-  credentials involved in the signature contain \usk as their user key (first)
-  attribute. Consequently, \IdentifyCred returns $1$ for all the involved
-  credentials, and the probability of \adv~winning at line 11 is $0$.
-
-  \paragraph{(e) \usk must belong to a known user.} %
-  The only remaining option for $\adv$ to win is via winning condition at line
-  12, meaning that \IdentifyUK fails to find an honest or corrupt users with
-  a \usk matching the one used to request the credentials used to produce the
-  signature output by \adv. However, at line 12, we already know that all
-  credentials are valid signatures by the issuer and that, also, all are bound
-  to the same user key. If this key is not associated to any known user, this
-  means that there is no matching $\langle\Obtain,\Issue\rangle$ transcript for
-  a credential over \usk --i.e., the honest issuer did not issue any credential
-  to \usk. But, as \sig must have been produced with at least one credential
-  (extracted at step 7), then this credential is a forgery, breaking security
-  against one-more forgery of the \SBCM scheme.
-  %
-  \qed
-\end{proof}
-
 \begin{theorem}[Non-frameability of \CUASGen]
@@
 
-\begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]
-  We prove that, given an adversary $\adv$ against non-frameability of
-  \CUASGen, we can build an adversary \advB that breaks the hiding property of
-  the underlying commitment scheme, with non-negligible probability.
-
-  We start from $G_0=\ExpNonframe$. $\adv$ makes queries to the oracles in
-  \Oframe. For $G_1$, within \Setup, we replace the \Setup algorithms for the
-  three NIZKs (\Issue, \Sign and \Open) with their corresponding \SimSetup
-  variants. Consequently, the corresponding queries to \Prove are also
-  simulated via the simulator. By the zero-knowledge property of the NIZK
-  systems, $G_1$ is indistinguishable from $G_0$. In the sequel, we build on
-  top of $G_1$, depending on whether or not a matching \Sig is found in \SIG,
-  in line 7.
-
-  \paragraph{(a) A matching \Sig exists in \SIG.} %
-  If we can find a matching \Sig in \SIG, for some \uid, then \adv~does not win
-  at line 7 of the game. Given that the signature is accepted by \Verify at line
-  3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
-  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, since the $(\yinsp,\iproof)$
-  pair output by \adv~is accepted by \Judge, simulation extractability of
-  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at line 9 pass.
-  Hence, the probability that the adversary wins at either lines 8 or 9 is $0$,
-  after simulation extractability of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.
-
-  \paragraph{(b) No matching \Sig exists in \SIG.} %
-  This means that \adv~creates an \UAS forgery. We leverage such an adversary
-  against $G_1$ to break the hiding property of the underlying commitment
-  scheme (see \appref{sapp:commitments}). For each new honest user \uid creation
-  request by \adv~(via \HUGEN),
-  \advB leverages its own $COM$ oracle to embed its challenges in the commitment
-  scheme into credentials of the \UAS non-frameability game. More precisely, in
-  calls to \HUGEN by \adv, \advB does not call \UKeyGen and instead picks two
-  random messages, $\msg_0^{\uid},\msg_1^{\uid}$, both from \AttrSpace. Whenever
-  a query to \OBTAIN is made by \adv~on behalf of \uid, \advB makes a call to
-  its $COM$ oracle, to get a commitment \Ccom for $\usk^{\uid}=\msg_b^{\uid}$
-  (for \advB's challenge bit $b$). Then,  \advB uses \Ccom in its \SBCMCom part
-  of the underlying \SBCM interactive signing protocol, and simulates the
-  corresponding $\NIZK^{\Issue}$ proof. Due to the zero-knowledge property, the
-  produced output is indistinguishable to that of the real execution. Similarly,
-  \advB can simulate the calls to the \SIGN and \OPEN oracles due to
-  simulation extractability of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.
-  %
-  Eventually, $\adv$ outputs a $(\oid,\siid,\Sig,\msg,\feval,\yinsp,\iproof)$
-  tuple that is accepted by \Verify and \Judge. Due to simulation extractability
-  of $NIZK^{\Sign}$, \ExtractSign must be able to produce a $(\usk,\scred,
-  \attrs_{\scred}, \tyeval^1,\yinsp')$ tuple. As, by assumption (line 6),  there
-  exists an \uid matching that \usk, all \advB has to do is find the
-  \uid for which \usk was used as either $\msg_0$ or $\msg_1$ in its hiding
-  game. Thus, \advB wins its hiding game with the same probability than \adv~
-  has to win the non-frameability game.
-  %
-  \qed
-\end{proof}
-
 %%% Local Variables:

### 2022-06-24 prism-backend/research/gsac/introduction-paper.tex
Restructured some content.

@@
 
-Before proceeding with our \UAS syntax and model in \secref{xxx}, generic
-construction \CUASGen in \secref{xxx}, and relationships with other primitives
-in \secref{xxx}, we give some preliminaries in \secref{xxx}. We conclude in
-\secref{xxx}.
+We give some preliminaries in \secref{sec:preliminaries}. Then proceed with our
+\UAS syntax, model, and construction, in \secref{sec:formal-uas}, and show
+relationships with other primitives in \secref{sec:relationships}.. We conclude
+in \secref{sec:conclusion}. Deferred proofs and additional information appear
+in the appendices.
 

### 2022-06-24 prism-backend/research/gsac/relationships.tex
Restructured some content.

--- 2022-06-18 prism-backend/research/gsac/conclusion-paper.tex
@@
-\section{Conclusion}
-\label{sec:conclusion}
+\section{Relationships with Other Schemes}
+\label{sec:relationships}
 
-[1 page max]
+% [11 pages max]
+
+In the following, to showcase the generality of \UAS and \CUASGen, we reproduce
+models of related schemes in the literature -- some of them slightly adapted.
+Then, we give concrete $(\fissue,\feval,\finsp)$-\CUASGen restrictions and prove
+that they securely instantiate the models for the presented schemes, if the
+corresponding \CUASGen restriction is a secure \UAS construction. Concretely,
+we rely on the functions described in \figref{fig:func-restrictions}.
+
+\begin{figure}[ht!]
+
+  \scalebox{0.95}{
+    \begin{minipage}[t]{\textwidth}
+      \textbf{Issuance functions:}
+      \begin{align}
+        & \fissue^1(\usk,\scred,\attrs) \coloneqq 1 \nonumber \\
+        & \fissue^{\sring}(\usk,\scred,\attrs) \coloneqq \pcif \attrs
+          \subseteq \sring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1; \pcelse
+          \pcreturn 0 \nonumber \\
+        & \fissue^{n,\dattrs}(\usk,\cred,\attrs) \coloneqq
+          \pcif \attrs_1(\cred) = n+1 \land \dattrs \subseteq \attrs: \pcreturn 1;
+          \pcelse \pcreturn 0 \nonumber
+      \end{align}
+
+      \textbf{Signature evaluation functions:}
+      \begin{align}
+        & \feval^0(\usk,\scred,\msg) \coloneqq \pcreturn (0,\ast) \nonumber \\
+        & \feval^{\dattrs}(\usk,\cred,\msg) \coloneqq \pcreturn
+          (\dattrs(\cred),\ast) \nonumber \\
+        & \feval^{\attrs}(\usk,\cred,\msg) \coloneqq \pcif \CCommit(\usk;0) \in
+          \attrs: \pcreturn (\attrs(\cred),\ast);
+          \pcelse \pcreturn (\bot,\bot) \nonumber \\
+        & \feval^{n,\dattrs}(\usk,\cred,\msg) \coloneqq
+          \pcreturn \pcreturn((\attrs_1(\cred),\dattrs(\cred)),\ast) \nonumber
+      \end{align}
+    \end{minipage}
+  }
+  \vspace*{1em}
+
+  \scalebox{0.95}{
+    \begin{minipage}[t]{0.5\textwidth}
+      \textbf{Open functions:}
+      \begin{align}
+        & \finsp^0(\yeval,\usk,\cred,\msg) \coloneqq 0 \nonumber \\        
+        & \finsp^{\upk}(\yeval,\usk,\scred,\msg) \coloneqq \CCommit(\usk;0) \nonumber
+      \end{align}
+    \end{minipage}
+    \hspace*{5em}
+    % \begin{minipage}[t]{0.47\textwidth}
+    %   \begin{framed}
+    %     $\attrs(\cred)$ returns all attributes in \cred \\
+    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
+    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
+    %     $\ast$ means the output is ignored \\
+    %     $\bot$ means the function fails
+    %   \end{framed}
+    % \end{minipage}
+  }
+  \caption{Functions for the \CUASGen restrictions described next.
+    $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
+    $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
+    attribute in \cred. $\ast$ means the output is ignored (in these examples,
+    we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
+    fails.}
+  \label{fig:func-restrictions}
+\end{figure}
+
+\subsection{Group Signatures}
+\label{ssec:related-models-gs}
+
+We adopt the model in \cite{bsz05}. In this abstraction
+of group signatures, the opener returns an index uniquely identifying the group
+member that created a signature, along with a correctness proof. For ease of
+exposition, assume that, w.l.o.g., this index is just the public key that the
+group member chooses when joining the group\footnote{The user public key is
+  assumed to be accessible from a public table in \cite{bsz05}, so it is direct
+  to translate the public key into an index, if needed.}. A group signature
+scheme, according to \cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign,
+\Verify, \Open and \Judge algorithms, as well as an $\langle\Obtain,\Issue
+\rangle$ interactive protocol. Their intuition is similar to that of
+\UAS, so we refer to \cite{bsz05} for detailed descriptions. For ease of
+reference, we replicate the security games in \figref{fig:model-gs}.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.45\textwidth}        
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gs}(1^\secpar)$}{%
+        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
+        d \gets \adv^{\mathcal{O}^{anon}}(\gpk,\isk) \\
+        \pcreturn d 
+      }
+
+      \vspace*{5em}
+
+      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gs}(1^\secpar)$}{%
+        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
+        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
+        (\gpk,\osk,\isk) \\
+        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
+        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
+        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
+        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
+        GSig(\PRVUK[\upk],\msg) \\
+        \pcreturn 0
+      }       
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.55\textwidth}
+      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gs}(1^\secpar)$}{%
+        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
+        (\msg,\sig) \gets \adv^{\mathcal{O}^{trace}}(\gpk,\osk) \\
+        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
+        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
+        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
+        = 0: \\ 
+        \pcind \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for group signatures \cite{bsz05}, only with minor    
+    ``harmless'' edits to compare easier with \CUASGS. Concretely, since we
+    output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
+    $\upk \notin \HU \cup \CU$. For the oracles' definitions, check the
+    referenced paper.
+    $\mathcal{O}^{anon} \gets \lbrace Ch,Open,SndToU,WReg,USK,CrptU \rbrace$,
+    $\mathcal{O}^{trace} \gets \lbrace SndToI,AddU,RReg,GSig,USK,CrptU \rbrace$,
+    and $\mathcal{O}^{frame} \gets \lbrace SndToU,WReg,GSig,USK,CrptU \rbrace$.
+  }
+  \label{fig:model-gs}  
+\end{figure}
+
+\subsubsection{\CUASGS construction.} %
+We show that the $(\fissue^1,\feval^0,\finsp^{\upk})$-\CUASGen restriction, is
+a secure group signature scheme according to \cite{bsz05}. We first quickly
+define the algorithms, and then prove security.
+
+\begin{description}
+\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
+  of \CUASGen, and one instance of \IKeyGen and \OKeyGen. Assigns the public
+  keys to \gpk.
+\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \UKeyGen from \CUASGen, and
+  computes $\CCommit(\usk;0)$ as \upk.
+\item[$\langle \cred,\utrans \rangle \gets
+  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
+  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Note that, to
+  constraint to only one credential per user, it suffices to require the user
+  to prove that the ``randomness'' it uses when committing to its private key
+  is actually $0$, and check whether the received commitment has been seen
+  before.
+\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
+  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen.
+  Simply returns \sig.
+\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
+  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
+  outputs.
+\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
+  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
+  0,\msg,\feval^0)$. Internally, the call to \Open runs
+  $\finsp^{\upk}$, where $\upk = \CCommit(\usk;0)$, just as proved in $\langle
+  \Obtain,\Issue\rangle$.
+\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
+  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
+  0,\msg)$.
+\end{description}
+
+\paragraph{Security of \CUASGS.} %
+We state next the theorems for the security of \CUASGS. The proofs are available
+in \appref{app:related-proofs}.
+
+\begin{theorem}[Anonymity of \CUASGS]
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASGS is an anonymous group signature
+  scheme.
+\end{theorem}
+
+\begin{theorem}[Traceability of \CUASGS]
+  If the base \CUASGen construction has unforgeable signing according to
+  \defref{def:sign-forge-uas}, then \CUASGS is a traceable group signature
+  scheme.
+\end{theorem}
+
+\begin{theorem}[Non-frameability of \CUASGS]
+  If the base \CUASGen construction is non-frameable according to
+  \defref{def:frame-uas}, then \CUASGS is a non-frameable group signature
+  scheme.
+\end{theorem}
+
+\subsection{Ring Signatures}
+\label{ssec:related-models-rs}
+
+We adopt the model in \cite{bkm06}, where security of ring signatures is
+defined according to the games in \figref{fig:model-rs}. A ring signature
+scheme consists of three algorithms $(KeyGen,Sign,Verify)$. Roughly,
+$((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar)$ produces $n$
+signing key pairs, $\sig \gets Sign(\sk_i,R,\msg)$ creates a signature for
+anonymity set $R \subseteq \lbrace \pk_1, \dots, \pk_t \rbrace$, using secret
+key $\sk_i$, associated to some $\pk_i \in R$; and $1/0 \gets Verify(R,\sig,
+\msg)$ checks if \sig is a valid signature over \msg for ring $R$. We refer
+to \cite{bkm06} for details on the syntax and definitions.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.55\textwidth}        
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
+        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
+        (i_0,i_1,R,\msg,\st) \gets \adv^{SIGN}(\pk_1,\dots,\pk_n) \\
+        \pcif % R \not\subseteq \lbrace [n] \rbrace \lor
+        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \notin R \lor %\\
+        i_0 = i_1: \pcreturn \bot \\
+        \sig \gets Sign(\sk_{i_b},R,\msg)) \\
+        b^* \gets \adv(\sig,\st) \\
+        \pcreturn b^*
+      }        
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.5\textwidth}
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
+        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
+        (R,\sig,\msg) \gets \adv^{SIGN,CORR}(\pk_1,\dots,\pk_n) \\
+        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
+        \pcreturn 1~\pcif R \subseteq [n] \setminus CU = \emptyset~\land \\
+        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg) \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for ring signatures \cite{bkm06}. The SIGN oracle
+    accepts a $(i,R,\msg)$ tuple, with $pk_i \in R$, and
+    returns $\sig \gets Sign(\sk_i,R,\msg)$. The oracle $CORR$ accepts an
+    index $i$, and leaks $\sk_i$ to $\adv$. Corrupted user indexes are
+    added to $CU$.}
+  \label{fig:model-rs}  
+\end{figure}
+
+\subsubsection{\CUASRing Construction.} %
+We first define in \eref{eq:sign-prv} an alternative NP relation for signing,
+$\NIZKRel_{\Sign}^{prv}$, which we use to replace $\NIZKRel_{\Sign}$ in \CUASGen.
+It is essentially the same, except that the issuer public key is kept private,
+and we add an extra check for proving that the issuer public key is one of the
+keys in the ring. We refer to the resulting \CUASGen construction as
+$\CUASGen^{\Sign-prv}$. Since, in the following syntax, we limit to one
+credential per signature, it is easy to see that the modified relation for
+signing does not affect security.
+
+\begin{align}
+  & \NIZKRel_{\Sign}^{prv} \coloneqq \lbrace (\usk,\cred,\yeval^1,\yinsp,r,r',
+    \ipk),(\msg,\feval,\yeval^0,\ceval,\cinsp,\Eek,\widetilde{\Eek},\sring): \nonumber \\
+  & \hspace*{6.405em}\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r) \land
+    \cinsp = \EEnc(\Eek,\yinsp;r') \land \nonumber \\
+  & \hspace*{6.40em}(\yeval^0,\yeval^1) = \feval(\usk,\cred,\msg) \land
+    \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\cred,\msg) \nonumber \\
+  & \hspace*{6.40em}\exists \ipk \in \sring~\suchthat~\SBCMVerify(\ipk,\cred,\usk,
+    \sring) = 1) \rbrace \label{eq:sign-prv}
+\end{align}
+
+From it, we show that the $(\fissue^{\sring},\feval^{\attrs},\finsp^0)$-
+$\CUASGen^{\Sign-prv}$ restriction, is a secure ring signature scheme. We
+restrict to one credential per signature.
+
+\begin{description}  
+\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in $\CUASGen^{\Sign-prv}$.  
+\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] As in
+  $\CUASGen^{\Sign-prv}$, using $\fissue^{\sring}$.  
+\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp).$] As in $\CUASGen^{\Sign-prv}$,
+  restricting \finsp to be $\finsp^0$.  
+\item[$\usk \gets \UKeyGen(\parm).$] Can only be run after \IKeyGen. Let 
+  $\usk \gets \isk$. Note that this does not affect security, as long as
+  $\isk \getr \AttrSpace$.
+\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
+  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
+  The user picks a set of public keys from a publicly available list of issuers
+  (users), i.e. $\sring \gets \lbrace \ipk_i \rbrace_{i \in [t]}$, for some $t$.
+  Then, runs the $\langle \Obtain,\Issue \rangle$ protocol as in
+  $\CUASGen^{\Sign-prv}$, acting both as user and as issuer, using
+  $\fissue^{\sring}$ as issuance function, and $\attrs \gets \sring$.
+\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,\msg,\feval).$] As in
+  $\CUASGen^{\Sign-prv}$, using $\feval^{\attrs}$ as sign evaluation function,
+  using as credential for signing the credential obtained in the desired
+  $\langle \Obtain,\Issue \rangle$ session and, as \opk, any previously
+  registered \opk (i.e., such that $\finsp=\finsp^0$).
+\item[$1/0 \gets \Verify(\opk,\sring,\sig,\yeval,\msg,\feval).$] As in
+  $\CUASGen^{\Sign-prv}$. Note that $\feval=\feval^{\attrs}$.
+\item[$\Open$ and $\Judge$.] As in $\CUASGen^{\Sign-prv}$. Note that
+  $\finsp=\finsp^0$.
+\end{description}
+
+\paragraph{Security of \CUASRing.} %
+We state next the theorems for the security of \CUASRing. The proofs are
+available in \appref{app:related-proofs}.
+
+\begin{theorem}[Anonymity of \CUASRing]
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASRing is an anonymous ring signature
+  scheme.
+\end{theorem}
+
+\begin{theorem}[Unforgeability of \CUASRing]
+  If the base \CUASGen construction is non-frameable according to
+  \defref{def:frame-uas}, then \CUASRing is an unforgeable ring signature
+  scheme.
+\end{theorem}
+
+\subsection{Anonymous Credentials}
+\label{ssec:related-models-ac}
+
+We adopt the model in \cite{fhs19}, for anonymous credentials with selective
+disclosure. Therein, an anonymous credential scheme is
+defined via $OrgKeyGen$ (which we rename to $IssKeyGen$), and $UserKeyGen$
+algorithms (roughly equivalent to
+\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
+interactive protocols. The issuance interactive protocol is equivalent to
+the issuance protocol in \UAS. Similarly, $Show,Verify$ is equivalent to
+the interactive extension of \Sign and \Verify in \UAS, which we show how
+to build in \appref{app:interactive-uas}. The security definitions rely on
+$HU, CU, ObtIss, Obtain, Issue,Show$, and $LoR$ oracles, which are essentially
+equivalent to our \HUGEN, \CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb
+oracles. We refer to \cite{fhs19} for the full details. For ease of reference,
+we summarize the security definitions in \figref{fig:model-ac}, with inocuous
+adaptations to make them more suitable for comparison with our definitions.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.5\textwidth}        
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
+        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
+        \pcreturn b^*
+      }        
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.5\textwidth}
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
+        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
+        \langle \cdot,(b,\utrans) \rangle
+        \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
+        \pcif b = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
+        \land D \subseteq \ATTR[j]): \\% \forall j, \OWNR[j] \in \CU
+        % \implies D \not\subseteq \ATTR[j]: \\
+        \pcind \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for anonymous credentials with selective disclosure
+    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
+    \secref{ssec:model-uas}.}
+  \label{fig:model-ac}  
+\end{figure}
+
+\subsubsection{\CUASAC Construction.} %
+We show that a $(\fissue^1,\feval^{\dattrs},\finsp^0)$-\CUASGen restriction, is
+a secure anonymous credential scheme according to the model in \cite{fhs19}. We
+first quickly define the algorithms, and then prove security. For better
+alignment with \UAS, we add a common setup process which is part of $IssKeyGen$
+in \cite{fhs19}. The change is inocuous functionality- and security-wise.
+
+\begin{description}
+\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar,
+  \AttrSpace)$ and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
+  \CUASGen construction. Returns $\parm \gets (\parm',\opk)$.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
+  \CUASGen construction, setting $\fissue^1$ as issuance function.
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
+  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
+\item[$\langle \cred/\bot,\top/\bot \rangle \gets
+  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
+  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
+  $\fissue^1$ as issuance function.
+\item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
+  \gets \langle Show(\ipk,\attrs,\dattrs,
+  \cred),\Verify(\ipk,\dattrs) \rangle$.]
+  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
+  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
+  open function, with \opk from \parm as opener public key.
+\end{description}
+
+\paragraph{Security of \CUASAC.} %
+We state next the theorems for the security of \CUASAC. The proofs are
+available in \appref{app:related-proofs}.
+
+\begin{theorem}[Anonymity of \CUASAC]
+  \label{thm:anon-cuasac}
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
+  according to \cite{fhs19}.
+\end{theorem}
+
+\begin{theorem}[Unforgeability of \CUASAC]
+  \label{thm:forge-cuasac}
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
+\end{theorem}
+
+\subsection{Delegatable Anonymous Credentials}
+\label{ssec:related-models-dac}
+
+We give a simple definition for a Delegatable Anonymous Credentials (DAC)
+scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
+our simple scheme built from \CUASGen does not ensure privacy of the delegation
+chain -- which could be achieved by making \feval output projective proofs like
+in \cite{bcc+09}, but since our goal is to showcase the feasibility of building
+DAC from \UAS, we leave that out for brevity. Our simple scheme does, however,
+ensure that a (not top-level) issuer can only delegate attributes contained in a
+credential it owns. Also, for simplicity, we restrict to the case of using one
+credential per signature/interactive credential presentation, and assume that
+all parties use the same opener and \finsp function.
+%
+The functionality is thus defined as in \secref{ssec:related-models-ac}, i.e.,
+we have $Setup$, $IssKeyGen$ and $UserKeyGen$ algorithms, and $\langle Obtain,
+Issue \rangle$ and $\langle Show,Verify \rangle$ interactive protocols.
+%
+In the model for this setting, since there are multiple issuers, in addition
+to the oracles in \secref{ssec:related-models-ac}, we use $HI$ and $CI$ oracles,
+equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
+issuers, and corrupt existing ones, respectively. The issuance and sign
+anonymity properties are direct, constraining the adversary to output challenge
+credentials and signatures with the same delegation chain. For unforgeability,
+we still require that no adversary can authenticate using a set of attributes
+that have not been issued to a corrupt user. In addition, we require that for
+any successful authentication using a level-$n$ credential, we
+can extract a chain of credentials of length $n$ such that each level-$i$
+credential can be used successfully to authenticate a level-$(i+1)$ credential
+down to the level-$n$ credential, and the attributes revealed in the
+level-$n$ authentication are contained in all the credentials up the chain.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{0.45\textwidth}
+      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
+        \pccomment{Abort if challenge creds belong to} \\
+        \pccomment{users with different delegation chains} \\
+        \pcreturn b^*
+      }
+      \vspace*{0.5em}
+
+      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
+        \pccomment{Abort if challenge sigs belong to} \\
+        \pccomment{users with different delegation chains} \\
+        \pcreturn b^*
+      }        
+    \end{minipage}
+  }
+  \scalebox{0.9}{      
+    \begin{minipage}[t]{.55\textwidth}
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (D=(n,D'),\ipk_n,\st) \gets
+        \adv^{\mathcal{O}_{forge}}(\parm) \\
+        \langle\cdot,(b,\utrans)\rangle \gets
+        \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
+        \pcif b = 0: \pcreturn 0 \\
+        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
+        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
+        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
+        \gets ExtractChain(\utrans) \\ 
+        \pcif \exists i \in [1,n]~\suchthat~
+        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
+        \pcind D' \not\subseteq \ATTR[\iid]) \land
+        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
+        \pcind \pcreturn 1 \\
+        \pcreturn 0
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for delegatable anonymous credentials with selective
+    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
+    CU,HI,CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon}
+    \gets \lbrace HU,CU,HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$.
+    $\mathcal{O}_{forge} \gets \lbrace HU,CU,HI,CI,Obtain,ObtIss,Issue,Show
+    \rbrace$. $IssLor$ is equivalent to \OBTCHALb in \UAS, whereas $SigLor$ is
+    equivalent to \CHALb. Also, \OWNR and \ATTR tables are essentially as in
+    \secref{ssec:model-uas}. $\ISR[\ipk]$, in this case, returns the identifier
+    of the issuer with public key \ipk. With $D =
+    (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
+    which denotes the level of the credential used for authentication.}
+  \label{fig:model-dac}  
+\end{figure}
+
+\subsubsection{\CUASDAC Construction.} %
+We next give a construction of a delegatable AC (DAC) scheme, based on a
+$(\fissue^{n,\dattrs},\feval^{n,\dattrs},\finsp^0)$-\CUASGen restriction.
+In a DAC scheme, all users are (or may be) also issuers. We only distinguish
+between top-level issuers, who have level $n=0$, and lower-level issuers, who
+have level $n>0$. In our \CUASDAC scheme, we assume that the first attribute
+(after the user's secret key) encodes the level of the credential. That is,
+$\attrs_1=n$, for a credential of level $n$. In addition, all users (i.e., with
+$n>0$) who want to delegate have to publicly list:
+
+\begin{enumerate}
+\item The level $n$ of the credential they delegate.
+\item Their public key \ipk.
+\item An \UAS signature proving knowledge of a credential of level $n$, and over
+  the attributes that this level-$n$ issuer is delegating.
+\item The \ipk of the parent issuer.
+\item The $\fissue^{n,\dattrs}$ function they will require for delegating.
+\item An $\feval^{n,\dattrs}$ function used to produce the signature at item 2.
+\end{enumerate}
+
+We assume that, from an \ipk, it is possible to find the corresponding issuer
+(e.g., using the previously mentioned public list). The mentioned
+$\fissue^{n,\dattrs}$ functions must follow the pattern in \figref{fig:func-restrictions}.
+Namely, the issuance function checks that the first requested attribute equals
+$n+1$, and that all requested attributes are a subset of the attribute set
+\dattrs being delegated by the level-$n$ issuer. In addition, signature
+evaluation functions $\feval^{n,\dattrs}$, also shown in \figref{fig:func-restrictions},
+must reveal the level of the credential used to produce the \UAS signature at
+item 2, as well as the set of attributes \dattrs that the level-$n$ issuer
+delegates. Verifiers can then trivially check if the set of revealed attributes
+are contained within the attributes delegatable by the parent issuer%
+\footnote{Additional checks may be added in both functions, but this is
+  the bare minimum.}. \figref{fig:XXX} depicts a sample of the delegation chain
+that this structure creates.
+%
+From this high-level description, we define the algorithms of \CUASDAC:
+
+\begin{description}
+\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar,
+  \AttrSpace)$ and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
+  \CUASGen construction. Returns $\parm \gets (\parm',\opk)$. Note that
+  $\finsp^0$ can be replaced by any desired opening function.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $n=0$, simply run \IKeyGen as
+  in \CUASAC. If $n>0$, note that this is a user who wants to delegate a
+  previously obtained credential \cred. Thus, it has already run $UserKeyGen$
+  below, which internally also runs \IKeyGen as in \CUASGen and sets $\usk \gets
+  \isk$. In addition, the level-$n$ issuer picks a random message $r$ and
+  computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
+  \feval^{n,\dattrs})$, for the \dattrs set it wants to reveal -- which must
+  include the attributes to delegate, and the credential level. It then
+  publishes $(n,\ipk,\Sig,\ipk^{n-1},\fissue^{n,\dattrs},\feval^{n,\dattrs})$,
+  where $\ipk^{n-1}$ is the public key of the parent issuer,
+  $\fissue^{n,\dattrs}$ is an issuance function as described in
+  \figref{fig:func-restrictions}, and $\feval^{n,\dattrs}$ is also as in
+  \figref{fig:func-restrictions}, revealing the attributes that the issuer is
+  willing to delegate.
+\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
+  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
+  $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
+  credentials. Note that this does not affect security, as long as
+  $\isk \getr \AttrSpace$.
+\item[$\langle \cred/\bot,\top/\bot \rangle \gets
+  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
+  If $n>0$, the user first finds the corresponding $(n,\ipk,\Sig,\ipk^{n-1},
+  \fissue^{n,\dattrs},\feval^{n,\dattrs})$ tuple, and checks \Sig running
+  \Verify as in \CUASGen (with the retrieved $\feval^{n,\dattrs}$). Then,
+  user and level-$n$ issuer run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
+  using $\fissue^{n,\dattrs}$ as issuance function. If $n=0$, then both run
+  $\langle\Obtain,\Issue\rangle$ as in \CUASGen, using the \fissue function
+  required by the issuer.
+\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle
+  \gets \langle Show(\opk,\attrs,\dattrs,\cred),
+  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of \CUASGen.  
+\end{description}
+
+\paragraph{Security of \CUASDAC.} %
+We state next the theorems for the security of \CUASDAC. The proofs are
+available in \appref{app:related-proofs}.
+
+\begin{theorem}[Issuance anonymity of \CUASDAC]
+  If the base \CUASGen construction has issuance anonymity according to
+  \defref{def:issue-anonymity-uas}, then \CUASDAC also has issuance anonymity.
+\end{theorem}
+
+\begin{theorem}[Signature anonymity of \CUASDAC]
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASDAC also has signature anonymity.
+\end{theorem}
+
+\begin{theorem}[Unforgeability of \CUASAC]
+  If the base \CUASGen construction has issuance and signature unforgeability
+  according to \defref{def:issue-forge-uas} and \defref{def:sign-forge-uas}, and
+  non-frameability according to \defref{def:frame-uas}, then \CUASAC is an
+  unforgeable AC scheme.
+\end{theorem}
+
+\subsection{Multimodal Private Signatures}
+\label{ssec:related-models-mps}
+
+Multimodal Private Signatures (or, rather, a close relative, see next) are
+directly implementable as a $(\fissue^1,\feval^{\yeval^1},
+\finsp^{\ast})$-\CUASGen restriction, where $\feval^{\yeval^1}$ is any signature
+evaluation function that ignores the $\yeval^0$ output, and $\finsp^{\ast}$ is
+any open function. Concretely, by restricting to a system with one issuer and
+one opener, one credential per user, one attribute per credential (the user
+secret key)% , $\fissue^1$ issuance functions, and
+% \feval functions that only use the $\yeval^1$ output -- which we denote with
+% $\feval^{\yeval^1}$
+.
+
+There are some differences, though. On the one hand, our signature anonymity
+property is somehow in the middle of MPS's privacy-1 and privacy-2 variants.
+Their privacy-1 variant is the traditional anonymity property of group
+signatures, in which the opener is honest and the adversary can call the opening
+oracle except for challenge signatures. In their privacy-2 variant, the opener
+is fully corrupt (i.e., \adv~ receives \osk), but the adversary can only be
+challenged with signatures that produce the same \yinsp value ($G_{j_b}(id_b)$
+in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
+(getting ther \osk), but the challenge signatures must have been generated using
+the key of an uncorrupted opener; still, \adv~can call the open oracle for
+challenge signatures, as long as they have the same \yinsp value. We believe
+that these differences are mostly of theoretical interest, though, and it does
+not seem hard to move from one to the other \todo{check}. In practice,
+what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$
+in MPS) that has too much granularity in their ranges, will lead to a barely
+private system. This is a known issue, for instance, in functional encryption
+\needcite.
+
+On the other hand, our issuance-related properties (issuance anonymity and
+issuance unforgeability) are unachievable by MPS. Issuance anonymity simply does
+not make sense in MPS, as it only supports one credential (without attributes)
+per user. Issuance unforgeability does not make sense either, since there are no
+configurable issuance policies in MPS -- instead, they have the fixed policy of
+``proving knowledge of a user secret key''. These extensions are not trivial
+from a theoretical point of view, and also have a big impact in the practicality
+of the resulting system. Also, MPS does not include verifiable openings. While
+this is easy to add, we consider it to be essential, given that the proposed
+generalization of opening allows the opener to output ``any value''. Hence, the
+need to ensure that the produced value is the legitimate one, seems to be more
+necessary than ever. Finally, our \feval function is a generalization of $F$ in
+MPS, as it allows two outputs: one will be returned in the clear along with the
+signature, and the other will be encrypted. Still both computations are proved
+correct. Making part of the output unencrypted allows implementing very useful
+variants such as anonymous credentials, as shown before.
+
+For the model of MPS schemes, we refer to the original paper \needcite.
+
+\subsubsection{\CUASMPS construction.} %
+As mentioned, any $(\fissue^1,\feval^{\yeval^1},\finsp^\ast)$-restriction of
+\CUASGen with only one issuer and opener, one credential per user, and one
+attribute per credential (the user secret key), implements an MPS scheme where
+$F=\feval^{\yeval^1}$ and $G=\finsp^\ast$. The restriction to one credential per
+user, and one attribute per credential, can be done as in
+\appref{sapp:related-models-gs}. Finally, note that, in MPS, $G$ is further
+parameterized with a value $j$, which essentially is the result of applying $F$
+to the message and signer identity, and is not leaked to the opener nor any
+other third party. The equivalent in \UAS is the $\yeval^1$ value, which is
+encrypted with a single-use key pair, and is an input of \yinsp.
+
+\paragraph{Security of \CUASMPS.} %
+We state next the theorems for the security of \CUASMPS. The proofs are
+available in \appref{app:related-proofs}.
+
+\begin{theorem}[Privacy-1 of \CUASMPS]
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASMPS satisfies privacy-1
+  according to \needcite.
+\end{theorem}
+
+\begin{theorem}[Extractability of \CUASMPS]
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, then it is an extractable MPS scheme.
+\end{theorem}
+
+\begin{theorem}[Unforgeability-1 of \CUASMPS]
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
+  defined in \needcite.
+\end{theorem}
+
+\begin{theorem}[Unforgeability-2 of \CUASMPS]
+  If the base \CUASGen construction has non-frameability according to
+  \defref{def:frame-uas}, then \CUASMPS satisfies unforgeability-2 as
+  defined in \needcite.
+\end{theorem}
 

### 2022-06-27 prism-backend/research/gsac/formal-uas.tex
Added a paragraph with real-world sample use cases. Fixed some todos.

@@
 Next we formalize our notion of Universal Anonymous Signatures
-(\UAS). We define its syntax, model, and give a generic construction which
+(\UAS). We define its syntax, model, and give a generic construction, which
 we prove secure according to our model.
@@
   functions define what utility value, derived from the user's secret key,
-  credentials, and signed message, should be extractable by an opener. Its
-  behaviour can be modulated by \Yeval, and its output a value \yinsp, which
-  must belong in a well defined set \rngfinsp.
+  credentials used for signing, and signed message, should be extractable by an
+  opener. Its behaviour can be modulated by \Yeval, and it outputs a value
+  \yinsp, which must belong in a well defined set \rngfinsp.
 \end{description}
@@
 \feval and \finsp may seem redundant. However, observe that the former is chosen
-on a per-signature basis, and probably after negotiation between signer and
+on a per-signature basis, probably after negotiation between signer and
 verifier. As such, it governs the information revealed at signing time. On the
@@
   \label{def:uas-restrictions}
-  Let \CUASGen be a generic construction of an \UAS scheme, secure according to
+  Let \CUASGen be a construction of an \UAS scheme, secure according to
   the model defined in \secref{ssec:model-uas}, and three functions $\fissue^a$,
@@
 
-To summarize the previous, we depict in \figref{fig:uas-signature} the structure
-of an \UAS signature, including its main components and how they enable the
-previously stated generalization claims.
-
-\begin{figure}[ht!]
-  \centering
-  %\input{figures/uas-signature.tex}
-  \caption{Structure of an \UAS signature.}
-  \label{fig:uas-signature}
-\end{figure}
+% To summarize the previous, we depict in \figref{fig:uas-signature} the structure
+% of an \UAS signature, including its main components and how they enable the
+% previously stated generalization claims.
+
+% \begin{figure}[ht!]
+%   \centering
+%   %\input{figures/uas-signature.tex}
+%   \caption{Structure of an \UAS signature.}
+%   \label{fig:uas-signature}
+% \end{figure}
 
@@
 crucial for privacy since, as AC schemes, \UAS allows multiple credentials per
-user -- thus, knowing what credential a user requests can lead to user
+user -- thus, knowing what user is requesting which credential can lead to user
 profiling. It must also ensure signature privacy, meaning that no information
-can be learned, from a signature, by third parties beyond what the user agrees
-to reveal, and what may be extractable by the chosen opener.
-Issuance unforgeability requires that \UAS schemes ensure that the claims used
-to support a credential request cannot be falsified (issuance unforgeability).
-Similarly, signature unforgeability requires that no adversary should be able to
-falsify the correctness proofs for the claims included in the signatures. In
-both cases (issuance and signature unforgeability), we introduce the notion of
-traceability in GS, requiring that all credentials involved in the corresponding
-process have to be associated to a known user. Finally, \UAS schemes inherit the
-useful non-frameability property of GS schemes which, even in the worst-case
-scenario of having a corrupt issuer. In this case, although we cannot ensure
-anything regarding correctness of the claims, we can ensure that no honest user
+can be learned by third parties from a signature, beyond what the user chooses
+to reveal, and what may be extractable by the chosen opener. Issuance
+unforgeability requires that \UAS schemes ensure that the claims used to support
+a credential request cannot be falsified (issuance unforgeability). Similarly,
+signature unforgeability requires that no adversary should be able to falsify
+the correctness proofs for the claims included in the signatures. In both cases
+(issuance and signature unforgeability), we require all credentials involved in
+the corresponding process to be associated to a known user. Finally, \UAS
+schemes inherit the useful non-frameability property of GS schemes where even
+the issuer is corrupt. In this case, we can ensure that no honest user
 can be framed with having created a signature that s/he did not create --
@@
           \pcif \iid \notin \HI: \pcreturn \bot \\
+          \pcif \exists \cid' \in \scid~\suchthat~\cid' \in \CCRED: \pcreturn \bot \\
           \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
@@
 
-        \procedure{$\SIGN(\oid,\uid,\scid,\msg,\feval)$}{%
-          \pcif \uid \notin \HU \cup \lbrace \bot \rbrace: \pcreturn \bot \\
-          \pcif \uid = \bot \land \exists \cid' \in \scid~\suchthat~
-          \cid' \notin \CCRED: \\
+        \procedure{$\SIGN(\uid,\oid,\scid,\msg,\feval)$}{%
+          \pcif \uid \notin \HU: \pcreturn \bot \\
+          \pcif \exists \cid,\cid' \in \scid~\suchthat~\cid \in \CRED \land
+          \cid' \in \CCRED: \\
           \pcind \pcreturn \bot \\
-          \pcif \uid = \bot: \uid \gets \OWNR[\scid] \\
           \pcif \feval \notin \famfeval: \pcreturn \bot \\
@@
 
-        \procedure{$\CHALb(\oid,\cuid_{0,1},\cscid_{0,1},\msg,\feval)$}{%
-          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
+        \procedure{$\CHALb(\oid,\cscid_{0,1},\msg,\feval)$}{%
+          \pcif \uid \notin \HU: \pcreturn \bot \\
+          \pcif \pcfor d \in \bin~ \exists \cid,\cid' \in \scid_d~\suchthat \\
+          \pcind \cid \in \CRED \land \cid' \in \CCRED: \pcreturn \bot \\
           \pcif \oid \in \CO: \pcreturn \bot \\
@@
 sets containing challenge credentials $\cred_b$, only if the output of \Open is
-the same as with the complementary $\cred_{1-b}$ 
-\todo{this is not done in the oracles. Fix.} (note that any other signature
+the same as with the complementary $\cred_{1-b}$ (note that any other signature
 can be open).
@@
       \pcind \pcreturn 1 \\
-      \pcif \scred \neq \emptyset \land
-      \nexists \uid~\suchthat~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1~
-      \pccomment{\todo{New! Update proofs.}} \\
       \pcreturn 0
@@
     \ExtractSign(\oid,\siid,\Sig,\msg,\feval) \\
-    \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg)
-    \pccomment{\todo{Added this line -- check line refs.}} \\
+    \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
     \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1

### 2022-06-27 prism-backend/research/gsac/introduction-paper.tex
Added a paragraph with real-world sample use cases. Fixed some todos.

@@
 Privacy-preserving digital signature and authentication systems have been a
-prolific field of study in the last few decades. Anonymous credentials
-\cite{chau85} and group signatures \cite{ch91} are among the most relevant ones.
-While there are many variants, the high-level idea is common: after obtaining a
-credential, users can authenticate anonymously and indistinguishably from other
-users with similar credentials.
+prolific field of study in the last few decades. Anonymous credentials (AC)
+\cite{chau85} and group signatures (GS) \cite{ch91} are among the most relevant
+schemes. While there are many variants, the high-level idea is common: after
+obtaining a credential, users can authenticate anonymously and indistinguishably
+from other users with similar credentials.
 
@@
 
-\paragraph{Utility at authentication-time and after authentication-time.} %
-Anonymous credentials (AC) focus on utility at authentication time. For
-instance, encoding multiple attributes within a credential and allowing to
-selectively disclose a subset of them, or even arbitrary predicates.
-The real world applications of such systems are direct,
-e.g., to prove ``Over 18''-type of claims. Indeed, the scientific research
-behind anonymous credentials is making its own way to become a foundational
-block of the technology some call ``anoncreds''%
+\paragraph{Utility at authentication time and after authentication time.} %
+AC schemes focus on utility at authentication time. For instance, encoding
+multiple attributes within a credential and allowing to selectively disclose a
+subset of them, or even arbitrary predicates. The real world applications of
+such systems are direct, e.g., to prove ``Over 18''-type of claims. Indeed, the
+scientific research behind anonymous credentials is making its own way to become
+a foundational block of the technology some call ``anoncreds''%
 \footnote{\url{https://hyperledger-indy.readthedocs.io/projects/sdk/en/latest/docs/design/002-anoncreds/README.html}. Last access, June 18th, 2022.},
@@
 
-Group signatures (GS) enhance utility after authentication, by allowing partial
-reidentification like linking of signatures, or even full deanonymization.
+GS schemes enhance utility after authentication, by allowing partial
+re-identification like linking of signatures, or even full deanonymization.
 While actual applications of group signatures seem hard to find in the real
-world, Direct Anonymous Attestation (DAA) \cite{bcc04,bl07,cdl16b} has been deployed to
-millions of computing devices into what's called TPM (Trusted Privacy Module)%
+world, Direct Anonymous Attestation (DAA) \cite{bcc04,bl07,cdl16b} has been
+deployed to millions of computing devices into what's called TPM (Trusted
+Privacy Module)%
 \footnote{\url{https://trustedcomputinggroup.org/resource/trusted-platform-module-tpm-summary/}. Last access, June 18th, 2022.}.
@@
 there are some exceptions. Functionality-wise, Attribute-Based Group Signatures
-(ABGS) introduce attributes into the credentials issued to group members, who
-can later use them to prove pre-fixed claims \cite{emo09,aa14}. Hidden-identity
+introduce attributes into the credentials issued to group members, who can later
+use them to prove pre-fixed claims \cite{emo09,aa14}. Hidden identity-based
 signatures also add attributes into the credentials, with the aim of preventing
 the opener (the trusted party who can deanonymize signers) from having to rely
-on the issuer in order to perform the opening \cite{ks07}. Some AC schemes have
-also tried to incorporate some sort of utility after authentication, like AC
-schemes with revocation \cite{cks10}, or with ``watchlists'' \needcite.
+on the issuer in order to return meaningful identifying information when opening
+a signature \cite{ks07}. Some AC schemes have also tried to incorporate some
+sort of utility after authentication, like AC schemes with revocation
+\cite{cks10}, or with ``watchlists'' \needcite.
 
@@
 
-Also, both AC and GS branches have experienced praiseworthy efforts towards
-generalization. In the AC domain, malleable signatures are used as core building
+Also, both AC and GS branches have experienced remarkable efforts towards
+generalisation. In the AC domain, malleable signatures are used as core building
 block in \cite{cklm14}, to allow building both conventional AC and Delegatable
 AC systems, depending on the transformation supported by the malleable
-signatures. In GS, very recently, BiAS \cite{lnpy21} and MPS \needcite
-flexibilize the tradeoff between anonymity and accountability.
+signatures. In GS, very recently, BiAS \cite{lnpy21} and MPS \needcite~
+flexibilize the trade-off between anonymity and accountability.
 
@@
 \paragraph{Limitations of GS and AC.} %
-However, even the generalization efforts that have independently taken place in
+However, even the generalisation efforts that have independently taken place in
 GS and AC, are quickly seen to have limited applicability in the real world.
@@
 deanonymizable and what information can be extracted from it, upon closer look,
-this information is somehow meaningless. To understand it, consider how does the
-generic construction work. Roughly, the signer encrypts the output of an
-arbitrary function of its ``identity'', and proves correctness of this
-computation. Yet, the concept of ``identity'' is not defined at all (it is a
-value within some undefined domain). Thus, it seems hard to associate any real
-world meaning to a function of something that is not clearly defined. In any
-case, proving membership to a group may be enough in some use cases, but
-definitely not as a general tool -- that is, GS  offer minimal utility at
-signing time.
+this information is somehow meaningless. Namely, the notion of identity is not
+well defined and, thus, it is not possible to claim whether the value output by
+their generalised open function makes sense or even if it is legitimate. Also,
+just being able to prove membership at signing time is typically not enough, and
+one needs to prove more general claims. That is precisely what AC schemes do,
+and AC schemes also have a well defined notion of identity via the credential
+attributes. Precisely, it is this defined concept of identity what enables AC
+schemes to state when some information revealed at authentication time is a
+forgery or not. On the other hand, the notion of accountability  is barely
+present in AC schemes. For instance, non-frameability is not even considered
+-- and it is non-frameability what ensures when a user cannot be held
+accountable.
 %
-On the other hand, ACs have a well defined concept of identity (the attributes
-encoded within a credential), yet their utility-after-authentication
-capabilities are 
-minimal -- something on which their GS counterpart has done decades of research.
-A somehow indirect proof of this is that the AC line of work does not even
-consider what security we can get in the presence of malicious issuers, which
-is precisely captured in the non-frameability properties of GS.
+In any case, perhaps the most impractical limitation of all is that too many
+models exist in both fields. Although similar, each model focuses on slightly
+different utility variants, making them hardly comparable. And, of course, AC
+focus only on utility at authentication (signing) time, while GS focus on
+utility after signing (authentication) time. To the best of our knowledge, no
+model exists that combines both, in a general enough manner. In practice, this
+forces system designers to decide which one they do not want to lose -- or,
+which one they will lose.
 
@@
 Acknowledging that the strengths of AC are the weaknesses of GS, and vice versa,
-we come up with a unified model. In a nutshell, we give a sytnax and model for
+we come up with a unified model. In a nutshell, we give a syntax and model for
 anonymous signatures -- which can be turned into an interactive authentication
-system -- with attribute-enabled credentials, and generalized utility
-both at authentication/signature-time, and after. We also generalize the
-credential issuance process, subsuming an even larger set of previously
-known schemes. Given its generalization power, we refer to schemes meeting this
-model as Universal Anonymous Signatures.
+system -- with attribute-enabled credentials, and generalised utility both at
+authentication/signature-time, and after. Concretely, we propose a scheme
+through which it is possible to model revealing arbitrary claims at signing time
+(as in AC), enable conditional release of utility information after signing time
+(as in MPS) and, more importantly, come up with the combination of the previous
+that is more suitable for each scenario. We also generalise the credential
+issuance process, subsuming an even larger set of previously known schemes.
+Given its generalisation power, we refer to schemes meeting this model as
+Universal Anonymous Signatures.
 
@@
 We give a generic construction based on well-known building blocks, and prove
-its security in the proposed model. To prove its universality, we show how
-restrictions of our generic construction directly imply the direct ancestors of
-UAS: group signatures and anonymous credentials. This includes not only their
-vanilla versions, but also relevant variants, such as MPS \needcite, (a modified
-version of) group signatures with message-dependent opening \cite{seh+12}, or
-anonymous credentials with revocation \cite{cks10}. We also show how minimal
-variations in our generic construction -- and leveraging the generalization of
-the issuance protocol -- allow us to build ring signatures \cite{rst06} or
+its security. To prove its universality, we show how restrictions of our generic
+construction directly imply the direct ancestors of UAS: group signatures and
+anonymous credentials. This includes not only their vanilla versions, but also
+relevant variants, such as MPS \needcite, (a modified version of) group
+signatures with message-dependent opening \cite{seh+12}, or anonymous
+credentials with revocation \cite{cks10}. We also show how minimal variations in
+our generic construction allow us to build ring signatures \cite{rst06} or
 delegatable anonymous credentials \cite{bcc+09}. The most interesting part being
 that, while we prove implications with other previously known schemes, our
-generalization approach allows to merge features of them: e.g., one can easily
+generalisation approach allows to merge features of them: e.g., one can easily
 model and instantiate GSs with with no revocation at all, ACs with full
-de-anonymization, or anything in between.
+de-anonymization, or anything in between -- like being able to deanonymize only
+if certain conditions are met.
 
@@
 \paragraph{Modelling challenges.} %
-Combining features of GS and AC into a unified model unavoidably brings
-complexity. For instance, we allow proving arbitrary claims over previously
-obtained credentials at issuance time, in order to inform the issuance
-decission. Thus, it is necessary to
-include unforgeability assurances already at that point -- something not
-considered in previous works. Also, in order to meet the general practice in AC,
-the model for \UAS includes multiple issuers, requiring careful bookkeeping to
-prevent trivial wins. Interestingly, this generalization also paves the way to
+Combining and extending features of GS and AC into a unified model unavoidably
+brings complexity. For instance, we allow proving arbitrary claims over
+previously obtained credentials at issuance time, in order to inform the
+issuance decision. Thus, it is necessary to model unforgeability guarantees
+already at that point -- something not considered in previous works. Also, in
+order to meet the general practice in AC, the model for \UAS includes multiple
+issuers, requiring careful bookkeeping to prevent trivial wins. Interestingly,
+combining this generalisation with the GS world also paves the way to
 include multiple openers, each with its own opening functionality -- also
@@
 this introduces similar limitations privacy-wise as in functional encryption
-schemes \needcite -- e.g., privacy cannot be ensured if some chosen opening
-function produces different outputs for different users. However, on this
-occasion, it is the signer (perhaps jointly with the verifier) who decides the
+schemes \cite{bsw11} -- e.g., revealing too granular information at signing or
+opening time makes privacy go away. However, on this occasion, it is the signer
+(perhaps jointly with the verifier) who decides the signing and
 opening policy. Thus, the user is in full control of how deanonymizable its
-signatures will be. This flexibility on the opening values also leads to the
+signatures will be, and knows it at signature generation time. This flexibility
+on the opening values also leads to the
 need of using extraction-based techniques for the modelling, since we cannot
@@
 A crucial aspect to cater for all possible variants that we aim to subsume, is
-the incorporation of ``placeholders'' enabling customization. We introduce abstract
+the incorporation of ``placeholders'' enabling customisation. We introduce abstract
 functions whose computation needs to be proven correct by the user. Depending on
@@
 
+\paragraph{Sample real-world use cases.} %
+By enabling customization at issuance, signing and opening times, the
+possibilities are large. As an example, consider a social network that requires
+under-age users to get permission from one parent. This can be defined via a
+delegatable credential scheme, checking that the delegation chain of the user
+requesting to join is valid via a policy at issuance time. Later, in order to
+make some post in the system advertising something to be sold in a local
+second-hand page in the social network, the user may need to reveal, at signing
+time, being a citizen of the local area (e.g. city). This can be done via an
+appropriate policy at signing time. If after the product is sold, it proves
+to be defective, the social network may directly output the email of the user
+if s/he is over-age, or the email of the adult in charge if s/he is under-age.
+And that could be achieved via a policy for utility after signing time (at
+opening time). Finally, if, in the same social network, some other
+issuer-user-verifier situation comes up that requires a different set of utility
+choices, just the appropriate functions would need to be changed -- and, given
+that our model allows multiple issuers and openers, both could coexist.
+
 %% Our techniques
 %%% E.g., describe how we compatibilize both with AC sel disc., ring sigs, and MPS
-\paragraph{Our approach.} %
-The high-level idea for our generic construction is simple. Credentials are
-signatures over blocks of messages (some signed in committed form), where each
-message can be a different attribute, and a user who wants to simultaneously
-leverage multiple credentials needs to bind all of them to the same key. We add
-three generic functions: \fissue, leveraged by users to
-prove claims over attributes in other credentials, in order to get a new one;
-\feval, proving correctness of the utility revealed at signing time; and \finsp,
-proving correctness of the utility extractable after signing. The latter is, in
-addition, fed and modulated with the output of \feval. The output of \feval is
+\paragraph{Our construction approach.} %
+The high-level idea for our generic construction \CUASGen is simple. Credentials
+are signatures over blocks of messages (some signed in committed form), where
+each message can be a different attribute, and a user who wants to
+simultaneously leverage multiple credentials needs to bind all of them to the
+same key. We add three generic functions: \fissue, leveraged by users at
+credential issuance time to prove claims over attributes in other credentials,
+in order to get a new one; \feval, proving correctness of the utility revealed
+at signing time; and \finsp, proving correctness of the utility information
+extractable after signing. The latter is, in addition, fed and modulated with
+the output of \feval. The output of \feval is
 actually double: one part is shared in the clear along with the signature, and
@@
     encryption of $y$; $D(z)$ means proving correct decryption of (an encryption
-    of) $z$. Solid boxes span configurable statements that control issuance;
-    dashed boxes span configurable statements that control utility at signing
-    time; dotted boxes span configurable statements that control utility after
-    signing time (accountability). Unboxed statements are fixed, and are thus
-    common to all \UAS restrictions. $\usk \coloneqq$ user secret key; $\scred
-    \coloneqq$ set of credentials.}
+    of) $z$. $\usk \coloneqq$ user secret key; $\scred \coloneqq$ set of
+    credentials.}
   \label{fig:proof-blocks-uas}
@@
 
-From this generic construction, \CUASGen, one can already build known (and more
+From \CUASGen, one can already build known (and more
 functionality-limited) schemes from what we call \emph{restrictions} of
@@
 construction, we also specify concrete NP relations for the underlying NIZK
-proofs for issuing, signing, and opening. Again with (unavoidable) minor variations
-of these NP relations -- concretely to the one used for signing -- we show how
-our \CUASGen variant can securely build ring signatures. That is, we prove that,
-by simply tweaking a function, and treating all users as issuers, group
-signatures an ring signatures are in essence the same thing.
+proofs for issuing, signing, and opening. These NP relations must not be
+considered as immutable, though. Actually, we show how, by making a minor
+variation into the one used for signing, a \CUASGen restriction can securely
+build ring signatures.
 
@@
 is that, with \UAS, one just needs to give concrete definitions of three
-functions. Security of the final primitive then automatically follows from the
-fact that it is a secure instantiation of an \UAS scheme. We believe that this
-is a powerful notion, that may finally allow research lines (AC and GS) that
-have followed different paths to benefit from the findings of each other.
-\figref{fig:relations} graphically summarizes the relations we prove between
-\UAS and other schemes -- although, of course, many more are probably
+functions (or little more). Security of the final primitive then essentially
+follows from the fact that it is a secure instantiation of an \UAS scheme. We
+believe that this is a powerful notion, that may finally allow research lines
+(AC and GS) that have followed different paths to benefit from the findings of
+each other. \figref{fig:relations} graphically summarises the relations we prove
+between \UAS and other schemes -- although, of course, many more are probably
 achievable.
@@
 
+\paragraph{Outline.} %
 We give some preliminaries in \secref{sec:preliminaries}. Then proceed with our
 \UAS syntax, model, and construction, in \secref{sec:formal-uas}, and show
-relationships with other primitives in \secref{sec:relationships}.. We conclude
+relationships with other primitives in \secref{sec:relationships}. We conclude
 in \secref{sec:conclusion}. Deferred proofs and additional information appear

### 2022-06-27 prism-backend/research/gsac/preliminaries-paper.tex
More passes.
Added a paragraph with real-world sample use cases. Fixed some todos.

@@
 
-\subsection{Cryptographic Building Blocks}
-\label{ssec:cryptobblocks}
+%\subsection{Cryptographic Building Blocks}
+%\label{ssec:cryptobblocks}
 
@@
 relation $\NIZKRel$; $\SBCMparm$ are the public parameters for an \SBCM scheme,
-and $\Eparm$ are the public parameters for an encryption scheme. Variables
+and $\Eparm$ are the public parameters for an encryption scheme, etc. Variables
 written in bold font denote sets, e.g., while we use \ipk to denote a single
 issuer public key, \sipk denotes a set of issuer's public keys. To refer to
-a specific element of a set, we use subindexes, e.g., $\sipk_i$ is the $i$-th
+a specific element of a set, we use sub-indexes, e.g., $\sipk_i$ is the $i$-th
 \ipk within \sipk.

### 2022-07-03 prism-backend/research/gsac/app-building-blocks.tex
Updated UAS proofs. Missing proof for new property obt-anon.
Fixing flaws in definitions and non-frame proof. (non-frame not done.)

@@
       \Cparm \gets \CSetup(\secpar) \\
-      (\msg_0,\msg_1,st) \gets \adv(\Cparm) \\
-      r \getr \mathcal{R} \\
-      \Ccom \gets \CCommit(\Cparm,\msg_b,r) \\
-      b' \gets \adv(st,\Ccom) \\
+      b' \gets \adv^{COM(\Cparm,\cdot,\cdot)},~\textrm{where}: \\
+      \pcind COM(\Cparm,\msg_0,\msg_1): \\
+      \pcind \pcind r \getr \mathcal{R};~\pcreturn \CCommit(\Cparm,\msg_b,r) \\
+      % (\msg_0,\msg_1,st) \gets \adv(\Cparm) \\
+      % r \getr \mathcal{R} \\
+      % \Ccom \gets \CCommit(\Cparm,\msg_b,r) \\
+%      b' \gets \adv(st,\Ccom) \\
       \pcreturn b'
@@
 \emph{simulation-extractability} \cite{cl06}, which amplifies the security
-requirements of simulation soundness.
+requirements of (simulation-) soundness.
 %
@@
 algorithms refer to, we use $\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel$, 
-$\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and subindex when clear
-from context. Altogether, the tuple $(\Setup,\Prove,\Verify,\SimSetup,\Sim,
-\Extract)$ needs to meet the following properties:
+$\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and superindex when
+clear from context. Altogether, the tuple $(\Setup,\Prove,\Verify,\SimSetup,
+\Sim,\Extract)$ needs to meet the following properties:
 

### 2022-07-03 prism-backend/research/gsac/formal-uas.tex
Undoing wrong change in model.
Fixing flaws in definitions and non-frame proof. (non-frame not done.)

@@
 
-        \procedure{$\CHALb(\oid,\cscid_{0,1},\msg,\feval)$}{%
-          \pcif \uid \notin \HU: \pcreturn \bot \\
+        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1},\msg,\feval)$}{%
+          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
           \pcif \pcfor d \in \bin~ \exists \cid,\cid' \in \scid_d~\suchthat \\
@@
 
-\paragraph{Helper functions \ExtractIssue, \ExtractSign, \IdentifyCred, and
-  \IdentifyUK.} We assume the existence of these four functions. They are not
-functions available in the actual scheme, but rather to the challenger in the
-experiments we use to formalize security of \UAS schemes. Similar techniques
-have been used before to prove security in privacy-preserving schemes with some
-sort of accountability, but that do not offer conventional opening as vanilla
-group signatures. For instance, see related works on DAA \cite{bfg+11,cdl16} and
-group signature variants \cite{dl21,fgl21,gl19,lnpy21}. More concretely, these
-functions are as follows:
+\paragraph{Helper functions \SimSetup, \ExtractIssue, \ExtractSign,
+  \IdentifyCred, and \IdentifyUK.} We assume the existence of these helper
+functions. They are not functions available in the actual scheme, but rather to
+the challenger in the experiments we use to formalize security of \UAS schemes.
+Consequently, while we introduce them here and specify some conditions they need
+to meet, their full definition is dependent on the construction. We fully define
+them for our generic construction \CUASGen in \appref{app:uas-proofs}. Similar
+techniques have been used before to prove security in privacy-preserving schemes
+with some sort of accountability, but that do not offer conventional opening as
+vanilla group signatures. For instance, see related works on DAA
+\cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}.
+More concretely, these functions are as follows:
 
 \begin{description}
-\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
-  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
-  credentials (if any) and their attributes involved in the request. It 
-  needs an honest issuer as, otherwise, the transcripts won't be available.
-\item[$\ExtractSign(\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
-  \scred,\attrs_{\scred},\yeval^1,\yinsp)$.] Receives a signature \Sig,
+\item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
+  parameter, outputs global (simulated) parameters \parm whose distribution is
+  indistinguishable to that produced by the \Setup algorithm, as well as a
+  trapdoor \trap.
+\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
+  Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
+  and returns the credentials (if any) and their attributes involved in the
+  request. It needs an honest issuer as, otherwise, the transcripts won't be
+  available. 
+\item[$\ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
+  \scred,\attrs_{\scred},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a
+  signature \Sig,
   as well as the opener identifier \oid, and the identifiers of all issuers of
@@
   generate the signature, and the $\yeval^1$ and \yinsp values.
-\item[$\IdentifyCred(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
+\item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
   issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
@@
   \IdentifyCred return $1$.
-\item[$\IdentifyUK(\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret key.
-  This is trivial for honest users, for which there must be a one-to-one
+\item[$\IdentifyUK(\trap,\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret
+  key. This is trivial for honest users, for which there must be a one-to-one
   relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
@@
       \procedure[linenumbering]{$\ExpIssAnonb(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
+        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
         b^* \gets \adv^{\OIssAnon} (\parm) \\
@@
       \procedure[linenumbering]{$\ExpSigAnonb(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
+        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
         b^* \gets \adv^{\OSigAnon} (\parm) \\
@@
     \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
-      \parm \gets \Setup(1^\secpar) \\
+      (\parm,\trap) \gets \SimSetup(1^\secpar) \\
       \cid \gets \adv^{\Oforgeissue}(\parm) \\
@@
       \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
-      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trans[\cid]) \\
+      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
       \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
@@
     \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
-      \parm \gets \Setup(1^\secpar) \\
+      (\parm,\trap) \gets \Setup(1^\secpar) \\
       (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
@@
       = 0: \pcreturn 1 \\
-      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets \ExtractSign(\oid,\siid,\Sig,
-      \msg,\feval) \\
+      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets
+      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
       \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
@@
   \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
-    \parm \gets \Setup(1^\secpar) \\
+    (\parm,\trap) \gets \SimSetup(1^\secpar) \\
     (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
@@
     (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
-    \ExtractSign(\oid,\siid,\Sig,\msg,\feval) \\
+    \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
     \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\

### 2022-07-04 prism-backend/research/gsac/formal-uas.tex
New proof for non-frameability.
Updated theorem statement for non-frameability of CUASGen.

@@
     \pcreturn 0 \\
+    \pcif \exists (\cdot,\cdot,\Sig,\Yeval,\msg,\feval)
+    \in \SIG[\uid]: \pcreturn 0 \\    
     (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
@@
     \lor \yinsp \neq \yinsp': \pcreturn 1 \\    
-    \pcif \nexists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \pcreturn 0 \\
-    \pcif \nexists (\cdot,\cdot,\Sig,\Yeval,\msg,\feval)
-    \in \SIG[\uid]: \pcreturn 1 \\
+    \pcif \exists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \pcreturn 1 \\
     \pcreturn 0
@@
   \label{thm:frame-uas}
-  If the underlying scheme for $\NIZK^{\Issue}$ is zero-knowledge, the schemes
-  for $\NIZK^{\Sign}$ are zero-knowledge and simulation-extractable, and the
-  commitment scheme is hiding, then our \CUASGen construction satisfies
+  If the underlying scheme for $\NIZK^{\Sign}$ is zero-knowledge and simulation
+  extractable, the scheme for $\NIZK^{\Open}$ is simulation-extractable, and
+  \SBCM scheme is blind, then our \CUASGen construction satisfies
   non-frameability as defined in \defref{def:frame-uas}, except with negligible

### 2022-07-04 prism-backend/research/gsac/app-uas-proofs.tex
Adding missing file.

--- 2022-06-13 prism-backend/research/gsac/security-uas.tex
@@
-\subsection{Correctness and Security of \CUASGen}
-\label{ssec:security-uas}
+\section{Correctness and Security Proofs for \CUASGen}
+\label{app:uas-proofs}
 
-First, we define the \ExtractIssue, \ExtractSign, \IdentifyCred and \IdentifyUK
-functions that are needed for some of the properties to be meaningful, in
-\figref{fig:helper-funcs}.
+First, we define the \SimSetup, \ExtractIssue, \ExtractSign, \IdentifyCred and
+\IdentifyUK functions that are needed for some of the properties to be
+meaningful, in \figref{fig:helper-funcs}.
 
 \begin{figure}[ht!]
+  \scalebox{0.9}{
     \begin{minipage}[t]{\textwidth}
-    \procedure{$\ExtractIssue(\parm,\utrans)$}{%
+      \procedure{$\SimSetup(1^\secpar)$}{%
+        \textrm{Parse}~\secpar~\textrm{as}~(\Csecpar,\NIZKsecpar,\SBCMsecpar,
+        \Esecpar). \\
+        \Cparm \gets \CSetup(\Csecpar), \SBCMparm \gets  \SBCMSetup(\SBCMsecpar) \\
+        \Sparm \gets \SSetup(\Ssecpar), \Eparm \gets \ESetup(\Esecpar) \\
+        (\NIZKcrs_{\Issue},\trap_{\Issue}) \gets
+        \NIZKSimSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar) \\
+        (\NIZKcrs_{\Sign},\trap_{\Sign}) \gets
+        \NIZKSimSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar) \\
+        (\NIZKcrs_{\Open},\trap_{\Open}) \gets
+        \NIZKSimSetup^{\NIZKRel_{\Open}}(\NIZKsecpar) \\
+        \pcreturn ((\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
+        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace), \\
+        \pcind (\trap_{\Issue},\trap_{\Sign},\trap_{\Open})) \\
+      }
+
+      \procedure{$\ExtractIssue(\parm,\trap,\utrans)$}{%
         \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Issue},\cdot,
-        \cdot,\cdot)$; $\NIZKcrs_{\Issue}$ as $(\NIZKcrs,\NIZKtrap)$; and
+          \cdot,\cdot)$} \\
+        \textrm{Parse \trap as $(\trap_{\Issue},\cdot,\cdot)$, and
           \utrans as $(\Ccom,\sipk,\cred,\NIZKproof)$} \\
-      \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\Ccom,\attrs,\sipk)): 
-      \pcreturn \bot \\
-      (\usk,\scred,\attrs_{\scred}) \gets \NIZKExtract(\NIZKcrs,\NIZKtrap,
+        \pcif \NIZKVerify^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
+        \NIZKproof,(\Ccom,\attrs,\sipk)): \pcreturn \bot \\
+        (\usk,\scred,\attrs_{\scred}) \gets
+        \NIZKExtract^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
+        \trap_{\Issue},
         (\Ccom,\attrs,\sipk),\NIZKproof) \\
@@
 
-    \procedure{$\ExtractSign(\parm,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
+      \procedure{$\ExtractSign(\parm,\trap,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
         \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
-        \cdot,\cdot)$; $\NIZKcrs_{\Sign}$ as $(\NIZKcrs,\NIZKtrap)$; and
-        \sig as $(\NIZKproof,\Ec)$} \\
+          \cdot)$} \\
+        \textrm{Parse \trap as $(\cdot,\trap_{\Sign},\cdot)$, and
+          \sig as $(\NIZKproof,\ceval,\cinsp)$} \\
         \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \gets
           \PUBIK[\siid]$} \\
-      \pcif \NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,
-      \sipk,\opk)): \pcreturn \bot \\
-      (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets \NIZKExtract(\NIZKcrs,
-      \NIZKtrap, (\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk,\opk,\widetilde{\Eek}),
+        \pcif \NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKproof,
+        (\msg,\feval,\yeval,\Ec,\sipk,\opk)): \pcreturn \bot \\
+        (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets
+        \NIZKExtract^{\NIZKRel_{\Sign}}(\NIZKcrs^{\NIZKRel_{\Sign}},
+        \NIZKtrap_{\Sign},
+        (\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk,\opk,\widetilde{\Eek}),
         \NIZKproof) \\
@@
 
-    \procedure{$\IdentifyCred(\usk,\attrs_{\cred},\cred)$}{%
+      \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred)$}{%
         \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
@@
 
-    \procedure{$\IdentifyUK(\uid,\usk)$}{%
+      \procedure{$\IdentifyUK(\parm,\trap,\uid,\usk)$}{%
         \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
         \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
-      \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trans[\cid]) \\
+        \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trap,\trans[\cid]) \\
         \pcind \pcif \usk = \usk': \pcreturn 1 \\
@@
     \end{minipage}
+  }
   \label{fig:helper-funcs}
@@
 
-\begin{theorem}[Correctness of \CUASGen]
-  \label{thm:correctness-uas}
-  If the underlying schemes for commitments, public-key encryption and \SBCM,
-  are correct,
-  as well as the NIZKs for $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
-  $\NIZKRel_{\Open}$, our generic construction \CUASGen satisfies correctness as
-  defined in \defref{def:correctness-uas}.
-\end{theorem}
+\subsection{Correctness}
 
@@
 
-\begin{theorem}[Issuance anonymity of \CUASGen]
-  \label{thm:iss-anonymity-uas}
-  If the NIZK systems used for $\NIZKRel_{\Issue}$ and $\NIZKRel_{\Sign}$ are
-  zero-knowledge, our \CUASGen construction satisfies issuance anonymity as
-  defined in \defref{def:iss-anonymity-uas}.
-\end{theorem}
+\subsection{Issuance Anonymity}
 
-\begin{proof}[\thmref{thm:iss-anonymity-uas}; Issuance anonymity of \CUASGen]
+\begin{proof}[\thmref{thm:issue-anonymity-uas}; Issuance anonymity of \CUASGen]
   We prove the special case in which the adversary makes only one query to the
@@
 
-\begin{theorem}[Signature anonymity of \CUASGen]
-  \label{thm:sign-anonymity-uas}
-  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge, and the
-  public-key encryption scheme is IND-CCA secure, our \CUASGen construction
-  satisfies signature anonymity as defined in \defref{def:sign-anonymity-uas}.
-\end{theorem}
+\subsection{Signature Anonymity}
 
 \begin{proof}[\thmref{thm:sign-anonymity-uas}; Signature anonymity of \CUASGen]
-  \iffalse
-  First, we define \SimSetup, \SIMOBTAIN, \SIMSIGN and \SIMOPEN as in
-  \figref{fig:anon-sim}.
-
-  \begin{figure}[ht!]
-    \begin{minipage}[t]{\textwidth}
-      \procedure{$\SimSetup(\secpar,\AttrSpace)$}{%
-        \textrm{Parse}~\secpar~\textrm{as}~(\cdot,\secpar_{\NIZK},\cdot,\cdot) \\
-        (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue})
-        \gets \NIZKSimSetup^{\NIZKRel_{\Issue}}(\secpar_{\NIZK}) \\
-        (\NIZKcrs_{\Sign},\NIZKtrap_{\Sign})
-        \gets \NIZKSimSetup^{\NIZKRel_{\Sign}}(\secpar_{\NIZK}) \\
-        (\NIZKcrs_{\Open},\NIZKtrap_{\Open})
-        \gets \NIZKSimSetup^{\NIZKRel_{\Open}}(\secpar_{\NIZK}) \\
-        \textrm{Compute}~\parm \gets (\Cparm,\SBCMparm,\Sparm,\Eparm)~
-        \textrm{as in}~\Setup \\
-        \pcreturn ((\parm,\NIZKcrs_{\Issue},
-        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
-        (\NIZKtrap_{\Issue},\NIZKtrap_{\Sign},\NIZKtrap_{\Open})) \\
-      }
-
-      \begin{minipage}[t]{\textwidth}
-        \begin{minipage}[t]{0.55\textwidth}
-          \procedure{$\SIMOBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
-            \pcif \uid \notin \HU: \pcreturn \bot \\
-            \pcif \iid \notin \CI: \pcreturn \bot \\
-            \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
-            \sipk_{\scred} \gets \PUBIK[\scid] \\
-            \langle \cred, \cdot \rangle \gets
-            \langle SimObt(\attrs,\PUBIK[\iid],\sipk_{\scred}),\adv \rangle \\
-            \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
-            \pcreturn \top \\      
-          }
-        \end{minipage}
-        \begin{minipage}[t]{0.45\textwidth}
-          \procedure{$SimObt(\attrs,\ipk,\sipk_{\scred})$}{%
-            \textrm{Runs $\langle \SBCMCom^{\NIZKRel_{\Issue}},\adv \rangle$} \\
-            \pcind \textrm{using $\NIZKSim^{\NIZKRel_{\Issue}}
-              (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue},\cdot)$} \\
-            \pcind \textrm{instead of $\NIZKProve^{\NIZKRel_{\Issue}}
-              (\NIZKcrs_{\Issue},\cdot,\cdot)$}
-          }
-        \end{minipage}
-      \end{minipage}
-
-      \begin{minipage}[t]{\textwidth}
-        \begin{minipage}[t]{0.55\textwidth}
-          \procedure{$\SIMSIGN(\oid,\uid,\scid,\msg,\feval)$}{%
-            \pcif \uid \notin \HU: \pcreturn \bot \\
-            \pcif \feval \notin \famfeval: \pcreturn \bot \\
-            \Sig \gets SimSign(\PUBOK[\oid],\msg,\feval) \\
-            \SIG[\uid] \gets \SIG[\uid] \cup
-            \lbrace (\oid,\scid,\Sig,\msg,\feval) \rbrace \\
-            \pcreturn \Sig \\
-          }
-        \end{minipage}
-        \begin{minipage}[t]{0.45\textwidth}
-          \procedure{$SimSign(\opk,\msg,\feval)$}{%
-            \textrm{Like}~\Sign()~\textrm{using} \\
-            \pcind \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
-            \NIZKtrap_{\Sign},\cdot) \\
-            \pcind \textrm{instead of}~\NIZKProve^{\NIZKRel_{\Sign}}
-            (\NIZKcrs_{\Sign},\cdot,\cdot)        
-          }
-        \end{minipage}
-      \end{minipage}
-
-      \begin{minipage}[t]{\textwidth}
-        \begin{minipage}[t]{0.55\textwidth}
-          \procedure{$\SIMOPEN(\oid,\Sig,\msg)$}{%
-            \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\msg,\feval)
-            \in \SIG[\uid] \\
-            % \textrm{Parse}~\Sig~\textrm{as}~(\sig,\yeval,\ceval) \\
-            (\yinsp,\iproof) \gets
-            SimOpen(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
-            \pcif \CSIG[\Sig] \neq \bot: \\
-            \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
-              \feval$} \\
-            \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b}) \\
-            \pcind (\yinsp',\iproof') \gets
-            \Open(\PRVOK[\oid],\IK[\siid],\\
-            \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
-            \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
-            \pcreturn (\yinsp,\iproof)          
-          }
-        \end{minipage}
-        \begin{minipage}[t]{0.45\textwidth}
-          \procedure{$SimOpen(\opk,\msg,\feval)$}{%
-          }
-        \end{minipage}
-      \end{minipage}    
-    \end{minipage}
-    \label{fig:sim-anon}
-    \caption{Definition of \SimSetup, \SIMOBTAIN, \SIMSIGN, and \SIMOPEN for
-      anonymity in \CUASGen.}
-  \end{figure}
-  \fi
 
@@
 
-\begin{theorem}[Issuance unforgeability of \CUASGen]
-  \label{thm:issue-forge-uas}
-  If the underlying NIZK used for $\NIZKRel_{\Issue}$ is zero-knowledge,
-  simulation extractable and sound, then our \CUASGen construction satisfies
-  issuance unforgeability as defined in \defref{def:issue-forge-uas}.
-\end{theorem}
+\subsection{Issuance Unforgeability}
 
@@
 
-\begin{theorem}[Signing unforgeability of \CUASGen]
-  \label{thm:sign-forge-uas}
-  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
-  extractable,the NIZK scheme for $\NIZKRel_{\Open}$ is complete, the public-key
-  encryption scheme is correct, and \SBCM is correct and one-more unforgeable,
-  then our \CUASGen construction satisfies signing unforgeability as defined in
-  \defref{def:sign-forge-uas}, except with negligible probability.
-\end{theorem}
+\subsection{Signature Unforgeability}
 
-\begin{proof}[\thmref{thm:sign-forge-uas}; Sign unforgeability of \CUASGen]
+\begin{proof}[\thmref{thm:sign-forge-uas}; Signature unforgeability of \CUASGen]
   As in \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
@@
 
-\begin{theorem}[Non-frameability of \CUASGen]
-  \label{thm:frame-uas}
-  If the underlying scheme for $\NIZK^{\Issue}$ is zero-knowledge, the schemes
-  for $\NIZK^{\Sign}$ are zero-knowledge and simulation-extractable, and the
-  commitment scheme is hiding, then our \CUASGen construction satisfies
-  non-frameability as defined in \defref{def:frame-uas}, except with negligible
-  probability.
-\end{theorem}
+\subsection{Non-Frameability}
 
 \begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]
-  We prove that, given an adversary $\adv$ against non-frameability of
-  \CUASGen, we can build an adversary \advB that breaks the hiding property of
-  the underlying commitment scheme, with non-negligible probability.
 
-  We start from $G_0=\ExpNonframe$. $\adv$ makes queries to the oracles in
-  \Oframe. For $G_1$, within \Setup, we replace the \Setup algorithms for the
-  three NIZKs (\Issue, \Sign and \Open) with their corresponding \SimSetup
-  variants. Consequently, the corresponding queries to \Prove are also
-  simulated via the simulator. By the zero-knowledge property of the NIZK
-  systems, $G_1$ is indistinguishable from $G_0$. In the sequel, we build on
-  top of $G_1$, depending on whether or not a matching \Sig is found in \SIG,
-  in line 7.
+  % We prove that, if the NIZK system used for $\NIZKRel_{\Sign}$ and
+  % $\NIZKRel_{\Open}$ is zero-knowledge and simulation-extractable, and \SBCM is
+  % blind, then our \CUASGen construction is secure.
 
-  \paragraph{(a) A matching \Sig exists in \SIG.} %
-  If we can find a matching \Sig in \SIG, for some \uid, then \adv~does not win
-  at line 7 of the game. Given that the signature is accepted by \Verify at line
-  3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
+  First, suppose that the \Sig that \adv~outputs at line 2 exists in
+  \SIG, for some \uid. Then, Given that the signature is accepted by \Verify at
+  line 3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
   \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, since the $(\yinsp,\iproof)$
   pair output by \adv~is accepted by \Judge, simulation extractability of
-  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at line 9 pass.
-  Hence, the probability that the adversary wins at either lines 8 or 9 is $0$,
-  after simulation extractability of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.
+  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 8 and 9
+  pass. Hence, the probability that the adversary wins at either lines 8 or 9 is
+  negligible, after simulation extractability of $\NIZK^{\Sign}$ and
+  $\NIZK^{\Open}$.
 
-  \paragraph{(b) No matching \Sig exists in \SIG.} %
-  This means that \adv~creates an \UAS forgery. We leverage such an adversary
-  against $G_1$ to break the hiding property of the underlying commitment
-  scheme (see \appref{sapp:commitments}). For each new honest user \uid creation
-  request by \adv~(via \HUGEN),
-  \advB leverages its own $COM$ oracle to embed its challenges in the commitment
-  scheme into credentials of the \UAS non-frameability game. More precisely, in
-  calls to \HUGEN by \adv, \advB does not call \UKeyGen and instead picks two
-  random messages, $\msg_0^{\uid},\msg_1^{\uid}$, both from \AttrSpace. Whenever
-  a query to \OBTAIN is made by \adv~on behalf of \uid, \advB makes a call to
-  its $COM$ oracle, to get a commitment \Ccom for $\usk^{\uid}=\msg_b^{\uid}$
-  (for \advB's challenge bit $b$). Then,  \advB uses \Ccom in its \SBCMCom part
-  of the underlying \SBCM interactive signing protocol, and simulates the
-  corresponding $\NIZK^{\Issue}$ proof. Due to the zero-knowledge property, the
-  produced output is indistinguishable to that of the real execution. Similarly,
-  \advB can simulate the calls to the \SIGN and \OPEN oracles due to
-  simulation extractability of $\NIZK^{\Sign}$ and $\NIZK^{\Open}$.
+  Next, suppose that the \Sig output by \adv~at line 2 does not exist in \SIG.
+  We prove that zero-knowledge and simulation extractability of
+  $\NIZKRel_{\Sign}$, and blindness of \SBCM, ensure that this only happens with
+  negligible probability.
+  The crucial observation is that, as in \cite{cl06} \CUASGen's \Sign algorithm
+  produces a signature of knowledge for the relation defined by
+  $\NIZKRel^{\Sign}$. That is, given $(x,w) \in \NIZKRel^{\Sign}$, one can
+  compare $x$ and $w$ to the public and private key of a signature algorithm,
+  respectively. In $\NIZKRel^{\Sign}$, $(\usk,\scred,\attrs_{\scred},\yeval^1,
+  \yinsp,r,r')$ is the private key ($w$), and $(\msg,\feval,\yeval^0,\ceval,
+  \cinsp,\sipk_{\scred},\Eek,\widetilde{\Eek})$ is the public key ($x$).
   %
-  Eventually, $\adv$ outputs a $(\oid,\siid,\Sig,\msg,\feval,\yinsp,\iproof)$
-  tuple that is accepted by \Verify and \Judge. Due to simulation extractability
-  of $NIZK^{\Sign}$, \ExtractSign must be able to produce a $(\usk,\scred,
-  \attrs_{\scred}, \tyeval^1,\yinsp')$ tuple. As, by assumption (line 6),  there
-  exists an \uid matching that \usk, all \advB has to do is find the
-  \uid for which \usk was used as either $\msg_0$ or $\msg_1$ in its hiding
-  game. Thus, \advB wins its hiding game with the same probability than \adv~
-  has to win the non-frameability game.
+  From this, we prove that an adversary has only negligible probability to forge
+  a signature as originating from an honest user without calling the \SIGN
+  oracle. The strategy is similar to that in \cite[Theorem 2.1]{cl06}.
+
+  Consider game $G_1$, which is equivalent to $G_0 = \ExpNonframe$, except that
+  in the \Sign function within the \SIGN oracle, we simulate the NIZK proof.
+  After the zero-knowledge property of $\NIZK^{\NIZKRel_{\Sign}}$, $G_1$ is
+  indistinguishable from $G_0$. Now, in $G_1$, simulation extractability of
+  $\NIZK^{\NIZKRel_{\Sign}}$ ensures that \ExtractSign must output a valid
+  witness for $(\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk_{\scred},\Eek,
+  \widetilde{\Eek})$. Note that this witness must include some \usk which,
+  for \adv~to win the game, must belong to an honest user. However, since the
+  user (whichever it is) has not been corrupted, its \usk has not been leaked
+  to \adv~via corruption queries (nor via \SIGN queries, where the proof of
+  knowledge within \Sign is now simulated). Moreover, blindness of \SBCM ensures
+  that the issuer (who is potentially corrupt), did not learn \usk either during
+  calls to \OBTAIN. Thus, the probability that $\UK[\uid] = \usk$ for $\uid \in
+  \HU$ and \Sig produced by the adversary, is negligible.
   %

### 2022-07-04 prism-backend/research/gsac/app-related-proofs.tex
More missing files.

--- 2022-06-16 prism-backend/research/gsac/app-model-related.tex
@@
-\section{\UAS-Based Instantiations of Related Schemes}
-\label{app:related-models}
+\section{Proofs for Relationships with Other Schemes}
+\label{app:related-proofs}
 
-In the following subsections we reproduce models of related schemes in the
-literature. Then, we give concrete \fissue, \feval and \finsp functions that
-make \UAS mimic their functionality. Finally, we prove for each case that
-\UAS -- restricted with the corresponding functions -- indeed meets their
-security models, thus proving that \UAS is a generalization of all of them.
+\subsection{Security of \CUASGS}
 
-\subsection{Group Signatures}
-\label{sapp:related-models-gs}
-
-We adopt the model in \cite{bsz05}. In this abstraction
-of group signatures, the opener returns an index uniquely identifying the group
-member that created a signature, along with a correctness proof. For ease of
-exposition, assume that, w.l.o.g., this index is just the public key that the
-group member chooses when joining the group\footnote{The user public key is
-  assumed to be accessible from a public table in \cite{bsz05}, so it is direct
-  to translate the public key into an index, if needed.}. A group signature
-scheme, according to \cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign,
-\Verify, \Open and \Judge algorithms, as well as an $\langle\Obtain,\Issue
-\rangle$ interactive protocol. Their description is very similar to that of
-\GSAC, so we refer to \cite{bsz05} for detailed descriptions. For ease of
-reference, we replicate the security games in \figref{fig:model-gs}.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.45\textwidth}        
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gs}(1^\secpar)$}{%
-        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
-        d \gets \adv^{\mathcal{O}^{anon}}(\gpk,\isk) \\
-        \pcreturn d 
-      }
-
-      \vspace*{5em}
-
-      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gs}(1^\secpar)$}{%
-        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
-        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
-        (\gpk,\osk,\isk) \\
-        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
-        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
-        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
-        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
-        GSig(\PRVUK[\upk],\msg) \\
-        \pcreturn 0
-      }       
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.55\textwidth}
-      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gs}(1^\secpar)$}{%
-        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
-        (\msg,\sig) \gets \adv^{\mathcal{O}^{trace}}(\gpk,\osk) \\
-        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
-        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
-        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
-        = 0: \\ 
-        \pcind \pcreturn 1 \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for group signatures \cite{bsz05}, only with minor    
-    ``harmless'' edits to compare easier with \CUASGS. Concretely, since we
-    output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
-    $\upk \notin \HU \cup \CU$. For the oracles' definitions, check the
-    referenced paper.
-    $\mathcal{O}^{anon} \gets \lbrace Ch,Open,SndToU,WReg,USK,CrptU \rbrace$,
-    $\mathcal{O}^{trace} \gets \lbrace SndToI,AddU,RReg,GSig,USK,CrptU \rbrace$,
-    and $\mathcal{O}^{frame} \gets \lbrace SndToU,WReg,GSig,USK,CrptU \rbrace$.
-  }
-  \label{fig:model-gs}  
-\end{figure}
-
-\subsubsection{\CUASGS construction.} %
-We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
-construction for \UAS, restricted to $\fissue^1$ as issuance function,
-$\feval^0$ as signature evaluation function, and $\finsp^{\upk}$ as opening
-function, is a secure group signature scheme according to the \cite{bsz05}
-model. We first quickly define the algorithms, and then prove security.
-
-\begin{description}
-\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
-  of \CUASGen, and one instance of \IKeyGen and \OKeyGen. Assigns the public
-  keys to \gpk.
-\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \UKeyGen from \CUASGen, and
-  computes $\CCommit(\usk;0)$ as \upk.
-\item[$\langle \cred,\utrans \rangle \gets
-  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
-  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Note that, to
-  constraint to only one credential per user, it suffices to require the user
-  to prove that the ``randomness'' it uses when committing to its private key
-  is actually $0$, and check whether the received commitment has been seen
-  before. For details, see the BBS+ instantiation of the underlying \SBCM
-  building block in \secref{sapp:sbcm}.
-\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
-  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen.
-  Simply returns \sig.
-\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
-  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
-  outputs.
-\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
-  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
-  0,\msg,\feval^0)$. Note that, internally, the latter call to \Open runs
-  $\finsp^{\upk}$, where $\upk = \CCommit(\usk;0)$, just as proved in $\langle
-  \Obtain,\Issue\rangle$.
-\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
-  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
-  0,\msg)$.
-\end{description}
-
-\paragraph{Security of \CUASGS.} %
 We prove that our \CUASGS construction is a secure group signature scheme,
@@
 \end{theorem}
-
-\todo{Introducing $(f,g,h)-\CUASGen$ naming convention. Describe it elsewhere.}
 
@@
 
-\subsection{Group Signatures with Message Dependent Opening}
-\label{sapp:related-models-gsmdo}
+\subsection{Security of \CUASRing}
 
-We cannot build the exact same functionality, nor follow the exact same security
-model as in the group signatures with message dependent opening (GS-MDO) scheme
-described in \cite{ehk+19}. Simply because, therein, the opening functionality
-is divided in two authorities: the admitter, who decides which messages are
-subject to be opened or not, and generates a token that enables opening
-signatures over such messages; and the opener, who performs the actual opening,
-but cannot do it without the tokens generated by the admitter. Intuitively, this
-can be seen as a sort of ``distribution'' of the opening capability. We define
-a variant of this model in which the admitter and opener are combined back into
-one entity (the opener), who can only open signatures over predefined messages,
-but cannot open any other signature. Moreover, our variant directly supports the
-scenario of multiple such openers, each being able to open only signatures
-over different messages. Note that it would not be hard to apply thresholding
-techniques to extend this case so that our ``unified'' opener role is shared
-across multiple entities, who have to cooperate in order to open a signature
-\needcite, thus achieving something very close ``in spirit'' to the scheme in
-\cite{ehk+19}. In addition, while \cite{ehk+19} follows the static group
-signature setting, we move to the dynamic one. Informally, our variant of GS-MDO
-is composed of the following algorithms: \Setup,
-\IKeyGen, \OKeyGen, \UKeyGen, \Sign, \Verify, \Open; as well as the $\langle
-\Obtain, \Issue \rangle$ interactive protocol. \OKeyGen generates an opening
-key pair which is already configured to open signatures only over some fixed
-(but arbitrary) set of messages. The remaining algorithms are as usual, so we
-defer a more detailed description to the construction. The oracles are the same
-as in \UAS. The resulting security model is given in \figref{fig:model-gsmdo},
-which we adapt from \cite{ehk+19}.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.45\textwidth}        
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gsmdo}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets \IKeyGen(\parm) \\
-        b^* \gets \adv^{\mathcal{O}^{anon}}(\parm,\ipk) \\
-        \pcreturn b^*
-      }
-
-      \vspace*{5em}
-
-      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gsmdo}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets \IKeyGen(\parm) \\
-        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
-        (\ipk,\isk) \\
-        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
-        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
-        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
-        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
-        GSig(\PRVUK[\upk],\msg) \\
-        \pcreturn 0
-      }       
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.55\textwidth}
-      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gsmdo}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets \IKeyGen(\parm) \\
-        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{trace}}
-        (\ipk,\opk,\osk) \\
-        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
-        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
-        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
-        = 0: \\ 
-        \pcind \pcreturn 1 \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for our GS-MDO variant.
-    $\mathcal{O}^{anon} \gets \lbrace \OGEN^{\smsg},\HUGEN,\CUGEN,\WREG,
-    \OBTAIN,\SIGN,\OPEN,\CHALb \rbrace$; $\mathcal{O}^{trace} \gets \lbrace
-    \OGEN,\HUGEN,\CUGEN,\ISSUE,\OBTISS,\RREG,\SIGN \rbrace$;
-    $\mathcal{O}^{frame} \gets \lbrace \OGEN,\HUGEN,\CUGEN,\WREG,
-    \OBTAIN,\SIGN \rbrace$. $\OGEN^{\smsg}$ is like \OGEN, but only accepting
-    functions of type $\finsp^{\smsg}$.
-  }
-  \label{fig:model-gsmdo}  
-\end{figure}
-
-\subsubsection{\CUASGSMDO construction.} %
-We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
-construction for \UAS, restricted to $\fissue^1$ as issuance function,
-$\feval^0$ as signature evaluation function, and $\finsp^{\smsg}$ as opening
-function, is a secure group signature scheme with message dependent opening
-as modelled in \figref{fig:model-gsmdo}. We first quickly define the algorithms,
-and then prove security.
-
-\begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.] Like in vanilla \CUASGen.
-\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Like the \UKeyGen function for
-  \CUASGS, in \secref{sapp:related-models-gs}.
-\item[$\langle \cred,\utrans \rangle \gets
-  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Like the corresponding
-  protocol in in vanilla \CUASGS, \secref{sapp:related-model-gs}.
-\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Like in vanilla \CUASGen, limited
-  on evaluation functions $\feval^0$ and opening functions $\finsp^{\smsg}$.
-\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Like in vanilla \CUASGen.
-\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Like in vanilla
-  \CUASGen.
-\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Like in vanilla \CUASGen.
-\end{description}
-
-\paragraph{Security of \CUASGSMDO.} %
-Our \CUASGSMDO construction is a secure group signature scheme,
-according to the model in \figref{fig:model-gsmdo}, if the underlying \CUASGen
-construction is secure.
-
-Note that both  model construction are essentially restrictions to the model
-and construction of \CUASGen. Thus, security directly follows from security of
-\CUASGen.
-
-% \begin{theorem}[Anonymity of \CUASGSMDO]
-%   If the base \CUASGen construction is anonymous according to
-%   \defref{def:anonymity-uas}, then \CUASGSMDO is an anonymous group signature
-%   scheme.
-% \end{theorem}
-
-% \begin{proof}
-
-%   \qed
-% \end{proof}
-
-% \begin{theorem}[Traceability of \CUASGSMDO]
-%   If the base \CUASGen construction has unforgeable signing according to
-%   \defref{def:sign-forge-uas}, then \CUASGSMDO is a traceable group signature
-%   scheme.
-% \end{theorem}
-
-% \begin{proof}
-%   Traceability follows directly from the corresponding proof for \CUASGS.
-%   \qed
-% \end{proof}
-
-% \begin{theorem}[Non-frameability of \CUASGSMDO]
-%   If the base \CUASGen construction is non-frameable according to
-%   \defref{def:frame-uas}, then \CUASGSMDO is a non-frameable group signature
-%   scheme.
-% \end{theorem}
-
-% \begin{proof}
-%   Non-frameability follows directly from the corresponding proof for \CUASGS.
-%   \qed
-% \end{proof}
-
-\subsection{Ring Signatures}
-\label{sapp:related-models-rs}
-
-We adopt the model in \cite{bkm06}, where security of ring signatures is
-defined according to the games in \figref{fig:model-rs}. A ring signature
-scheme consists of three algorithms $(KeyGen,Sign,Verify)$. Roughly,
-$((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar)$ produces $n$
-signing key pairs, $\sig \gets Sign(\sk_i,R,\msg)$ creates a signature for
-anonymity set $R \subseteq \lbrace \pk_1, \dots, \pk_t \rbrace$, using secret
-key $\sk_i$, associated to some $\pk_i \in R$; and $1/0 \gets Verify(R,\sig,
-\msg)$ checks if \sig is a valid signature over \msg for ring $R$.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.55\textwidth}        
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
-        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
-        (i_0,i_1,R,\msg,\st) \gets \adv^{SIGN}(\pk_1,\dots,\pk_n) \\
-        \pcif % R \not\subseteq \lbrace [n] \rbrace \lor
-        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \notin R \lor %\\
-        i_0 = i_1: \pcreturn \bot \\
-        \sig \gets Sign(\sk_{i_b},R,\msg)) \\
-        b^* \gets \adv(\sig,\st) \\
-        \pcreturn b^*
-      }        
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.5\textwidth}
-      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
-        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
-        (R,\sig,\msg) \gets \adv^{SIGN,CORR}(\pk_1,\dots,\pk_n) \\
-        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
-        \pcreturn 1~\pcif R \subseteq [n] \setminus CU = \emptyset~\land \\
-        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg) \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for ring signatures \cite{bkm06}. The SIGN oracle
-    accepts a $(i,R,\msg)$ tuple, where $pk_i$ must be part of $R$, and
-    returns $\sig \gets Sign(\sk_i,R,\msg)$. The oracle $CORR$ accepts an
-    index $i$, and lets $\adv$ learn $\sk_i$. Corrupted user indexes are
-    added to list $CU$.}
-  \label{fig:model-rs}  
-\end{figure}
-
-Intuitively, a ring signature scheme $rs$ is anonymous if, for every p.p.t.
-\adv, $|\Pr[\Exp^{anon-1}_{\adv,rs}(1^\secpar)] = 1| -
-|\Pr[\Exp^{anon-1}_{\adv,rs}(1^\secpar)] = 0|$ is a negligible function of
-$1^\secpar$; and a ring signature scheme $rs$ is unforgeable if, for every
-p.p.t. \adv, the probability that $\Exp^{forge}_{\adv,rs}(1^\secpar)$ returns
-$1$ is also negligible in $1^\secpar$. For short, we say that a ring signature
-scheme meeting both anonymity and unforgeability as specified above, is a secure
-ring signature scheme.
-
-\subsubsection{\CUASRing Construction.} %
-We show that, as specified in \secref{ssec:uas-ring}, our \CUASGen construction
-for \UAS, with alternative NIZK relationship $\NIZKRel_{\Sign-prv}$ for signing,
-issuance function $\fissue^{\sring}$, signature evaluation function
-$\feval^{\attrs}$, and inspection function $\finsp^0$, is a secure ring
-signature scheme. Thus, in this section, when we write \CUASGen, we refer to
-its specific variant built from the previous modifications.
-
-\begin{description}  
-\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in \CUASGen, but using
-  $\NIZKRel_{\Sign-prv}$ instead of $\NIZKRel_{\Sign}$.  
-\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] As in \CUASGen, using
-  $\fissue^{\sring}$.  
-\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp).$] As in \CUASGen, where every
-  opener that wants to be a valid opener in \CUASRing, needs to set \finsp to
-  $\finsp^0$.  
-\item[$\usk \gets \UKeyGen(\parm).$] Can only be run after \IKeyGen. Let 
-  $\usk \gets \isk$.
-\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
-  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
-  The user picks a ring from an (publicly) available list of issuers (users),
-  i.e. $\sring \gets \lbrace \ipk_i \rbrace_{i \in [t]}$, for some $t$. Then,
-  runs the $\langle \Obtain,\Issue \rangle$ protocol as in \CUASGen, acting both
-  as user and as issuer, and using $\fissue^{\sring}$ as issuance function.
-  \attrs are the public keys of the users (issuers) to be included in the ring.
-\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval).$] As in
-  \CUASGen, using $\feval^{\attrs}$ as sign evaluation function, using
-  as credential for signing the credential obtained in the desired $\langle
-  \Obtain,\Issue \rangle$ session and, as \opk, any previously registered \opk
-  (i.e., such that $\finsp=\finsp^0$).
-\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in \CUASGen.
-  Note that $\sipk = \sring$, and $\feval=\feval^{\attrs}$.
-\item[$\Open$ and $\Judge$.] As in \CUASGen. Note that $\finsp=\finsp^0$.
-\end{description}
-
-\todo{I guess we need to show that changing the NIZK for signing does not affect
-  security. This leads to ``What are the conditions that need to be checked/cannot
-  be altered in the default NIZK sign, that make \CUASGen secure?'' }
-
-\paragraph{Security of \CUASRing.} %
 We prove that our \CUASRing construction is anonymous and unforgeable, if
@@
 
-\subsection{Anonymous Credentials}
-\label{sapp:related-models-ac}
+\subsection{Security of \CUASAC}
 
-We adopt the model in \cite{fhs19}, where security of anonymous credentials
-(with selective disclosure). Therein, an anonymous credential scheme is
-defined via $OrgKeyGen$ (which we rename to $IssKeyGen$, and $UserKeyGen$
-algorithms (roughly equivalent to
-\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
-interactive protocols. The issuance interactive protocol is equivalent to
-the issuance protocol in \UAS. Similarly, $Show,Verify$ is equivalent to
-the interactive extension of \Sign and \Verify in \UAS, which we show how
-to build in \secref{ssec:variants-gsac} (for \GSAC, but the case for \UAS is
-equivalent). The security definitions rely on $HU, CU, ObtIss, Obtain, Issue,
-Show$, and $LoR$ oracles, which are essentially equivalent to our \HUGEN,
-\CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb oracles. We refer to
-\cite{fhs19} for the full details. For ease of reference, we summarize the
-security definitions in \cite{fig:model-ac}, with inocuous adaptations to
-make them more suitable for comparison with our definitions.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.5\textwidth}        
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
-        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
-        \pcreturn b^*
-      }        
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.5\textwidth}
-      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
-        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
-        (\cdot,b) \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
-        \pcif b = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
-        \land D \subseteq \ATTR[j]): \\% \forall j, \OWNR[j] \in \CU
-        % \implies D \not\subseteq \ATTR[j]: \\
-        \pcind \pcreturn 1 \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for anonymous credentials with selective disclosure
-    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
-    \secref{ssec:model-uas}.}
-  \label{fig:model-ac}  
-\end{figure}
-
-\subsubsection{\CUASAC Construction.} %
-We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
-construction for \UAS, restricted to $\fissue^1$ as issuance function,
-$\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as opening
-function, is a secure anonymous credential scheme according to the \cite{fhs19}
-model. We first quickly define the algorithms, and then prove security. Note
-that, for better alignment with \UAS, we add a common setup process which is
-part of $IssKeyGen$ in \cite{fhs19}. The change is inocuous functionality- and
-security-wise, though.
-
-\begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
-    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
-    construction. Returns $\parm \gets (\parm',\opk)$.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
-  \CUASGen construction, setting $\fissue^1$ as issuance function.
-\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
-  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
-\item[$\langle \cred/\bot,\top/\bot \rangle \gets
-  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
-  $\fissue^1$ as issuance function.
-\item[$1/0 \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
-  \Verify(\ipk,\dattrs) \rangle$.]
-  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
-  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
-  open function, with \opk from \parm as opener public key.
-\end{description}
-
-\paragraph{Security of \CUASAC.} %
 We prove that \CUASAC is an anonymous and unforgeable anonymous credential
@@
 
-\subsection{Delegatable Anonymous Credentials}
-\label{sapp:related-models-dac}
+\subsection{Security of \CUASDAC}
 
-We give a simple definition for a Delegatable Anonymous Credentials (DAC)
-scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
-our simple scheme built from \CUASGen does not ensure privacy of the delegation
-chain -- which could be achieved by making \feval output projective proofs like
-in \cite{bcc+09}, but since our goal is to showcase the feasibility of building
-DAC from \UAS, we leave that out for brevity. Our simple scheme does, however,
-ensure that a (not top-level) issuer can only delegate attributes contained in a
-credential it owns. Also, for simplicity, we restrict to the case of using one
-credential per signature/interactive credential presentation, and assume that
-all parties use the same opener and \finsp function.
-%
-The functionality is thus defined as in \appref{sapp:related-models-ac}, i.e.,
-we have $Setup$, $IssKeyGen$ and $UserKeyGen$ algorithms, and $\langle Obtain,
-Issue \rangle$ and $\langle Show,Verify \rangle$ interactive protocols.
-%
-In the modelling for this setting, since there are multiple issuers, in addition
-to the oracles in \appref{sapp:related-models-ac}, we use $HI$ and $CI$ oracles,
-equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
-issuers, and corrupt existing ones, respectively. The issuance and sign
-anonymity properties are as before. For unforgeability, we still require
-that no adversary can authenticate using a set of attributes that have not been
-issued to a corrupt user. In addition, we require that for any possible
-successful authentication protocol using a level-$n$ credential, we can extract
-a chain of credentials of length $n$ such that each level-$i$ credential can
-be used successfully to authenticate a level-$(i+1)$ credential up to the
-level-$n$ credential, and that the attributes revealed in the level-$n$
-authentication are contained in all the credentials up the chain.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.4\textwidth}
-      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
-        \pcreturn b^*
-      }
-      \vspace*{0.75em}
-
-      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
-        \pcreturn b^*
-      }        
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.6\textwidth}
-      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (D=(n,D'),\ipk_n,\st) \gets
-        \adv^{\mathcal{O}_{forge}}(\parm) \\
-        (\cdot,b) \gets \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
-        \pcif b = 0: \pcreturn 0 \\
-        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
-        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
-        \textrm{Let \utrans be the transcript of $\langle \adv(\st),
-          \Verify(\cdot,\cdot)\rangle$} \\        
-        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
-        \gets ExtractChain(\utrans) \\ 
-        \pcif \exists i \in [1,n]~\suchthat~
-        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
-        \pcind D' \not\subseteq \ATTR[\iid]) \land
-        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
-        \pcind \pcreturn 1 \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for delegatable anonymous credentials with selective
-    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
-    CU,HI,CI,Obtain,Issue,Obtiss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon}
-    \gets \lbrace HU,CU,HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$.
-    $\mathcal{O}_{forge} \gets \lbrace HU,CU,HI,CI,Obtain,ObtIss,Issue,Show
-    \rbrace$. $IssLor$ is equivalent to \OBTCHALb in \UAS, whereas $SigLor$ is
-    equivalent to \CHALb. Also, \OWNR and \ATTR tables are essentially as in
-    \secref{ssec:model-uas}. $\ISR[\ipk]$, in this case, returns the identifier
-    of the issuer with public key \ipk. With $D =
-    (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
-    which denotes the level of the credential used for authentication.}
-  \label{fig:model-dac}  
-\end{figure}
-
-\subsubsection{\CUASDAC Construction.} %
-In a delegatable AC (DAC) scheme, all users are (or may be) also issuers. We
-only distinguish between top-level issuers, who have level $n=0$, and
-lower-level issuers, who have level $n>0$. In our \CUASDAC scheme, we assume
-that the first attribute (after the user's secret key) encodes the level of
-the credential. That is, $\attrs_1=n$, for a credential of level $n$. In
-addition, all users (i.e., with $n>0$) who want to delegate have to publicly
-list:
-
-\begin{enumerate}
-\item The level $n$ of the credential they delegate.
-\item Their public key \ipk.
-\item An \UAS signature proving knowledge of a credential of level $n$, and over
-  the attributes that this level-$n$ issuer is delegating.
-\item The \ipk of the parent issuer.
-\item The $\fissue^{n,\dattrs}$ function they will require for delegating.
-\item An $\feval^{n,\dattrs}$ function used to produce the signature at item 2.
-\end{enumerate}
-
-We assume that, from an \ipk, it is possible to find the corresponding issuer
-(e.g., using the previously mentioned public list). The mentioned
-$\fissue^{n,\dattrs}$ functions must follow the pattern in \esref{eq:funcs-dac}.
-Namely, the issuance function checks that the first requested attribute equals
-$n+1$, and that all requested attributes are a subset of the attribute set
-\dattrs being delegated by the level-$n$ issuer. In addition, signature
-evaluation functions $\feval^{n,\dattrs}$, also shown in \esref{eq:funcs-dac},
-must reveal the level of the credential used to produce the \UAS signature at
-item 2, as well as the set of attributes \dattrs that the level-$n$ issuer
-delegates. Verifiers can then trivially check if the set of revealed attributes
-are contained within the attributes delegatable by the parent issuer%
-\footnote{Additional checks may be added in both functions, but this is
-  the bare minimum.}. \figref{fig:XXX} depicts a sample of the delegation chain
-that this structure creates.
-
-\begin{align}
-  & \fissue^{n,\dattrs}(\usk,\cred,\attrs) \coloneqq \lbrace
-    \pcif \attrs_1 = n+1 \land \attrs \subseteq \dattrs: \pcreturn 1; \pcelse \pcreturn 0
-    \rbrace \nonumber \\
-  & \feval^{n,\dattrs}(\usk,\cred,\msg) \coloneqq \lbrace
-    \pcreturn (\attrs_1(\cred),\dattrs(\cred)) \rbrace
-  \label{eq:funcs-dac}
-\end{align}
-
-From this high-level description, we define the algorithms of \CUASDAC:
-
-\begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
-    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
-    construction. Returns $\parm \gets (\parm',\opk)$. Note that $\finsp^0$ can
-    be replaced by any desired opening function.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $n=0$, simply run \IKeyGen as
-  in \CUASAC. If $n>0$, note that this is a user who wants to delegate a
-  previously obtained credential \cred. Thus, it has already run $UserKeyGen$
-  below, which internally also runs \IKeyGen as in \CUASGen and sets $\usk \gets
-  \isk$. In addition, the level-$n$ issuer picks a random message $r$ and
-  computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
-  \feval^{n,\dattrs})$, for the \dattrs set it wants to reveal -- which must
-  include the attributes to delegate, and the credential level. It then
-  publishes $(n,\ipk,\Sig,\ipk^{n-1},\fissue^{n,\dattrs},\feval^{n,\dattrs})$,
-  where $\ipk^{n-1}$ is the public key of the parent issuer,
-  $\fissue^{n,\dattrs}$ is an issuance function as described in
-  \esref{eq:funcs-dac}, and $\feval^{n,\dattrs}$ is also as in
-  \esref{eq:funcs-dac}, revealing the attributes that the issuer is willing to
-  delegate..
-\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
-  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
-  $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
-  credentials.
-\item[$\langle \cred/\bot,\top/\bot \rangle \gets
-  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  If $n>0$, the user first finds the corresponding $(n,\ipk,\Sig,\ipk^{n-1},
-  \fissue^{n,\dattrs},\feval^{n,\dattrs})$ tuple, and checks \Sig running
-  \Verify as in \CUASGen (with the retrieved $\feval^{n,\dattrs}$). Then,
-  user and level-$n$ issuer run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
-  using $\fissue^{n,\dattrs}$ as issuance function. If $n=0$, then both run
-  $\langle\Obtain,\Issue\rangle$ as in \CUASGen, using the \fissue function
-  required by the issuer.
-\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
-  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of \CUASGen.  
-\end{description}
-
-\paragraph{Security of \CUASDAC.} %
 We prove that \CUASDAC is an anonymous and unforgeable DAC scheme, according to
@@
 
-\iffalse
-We adopt the simplification that the level of an issuer is encoded in its public
-key, and anybody can check the issuer's level via some publicly accessible
-mechanism. This can be ensured, e.g., by having each issuer post its
-  public key along with a proof of ownership of a level $n$ credential -- which
-  can be trivially done in \CUASGen.
+\subsection{Security of \CUASMPS}
 
-  \begin{description}
-  \item[$\parm \gets \Setup(1^\secpar)$.] As in \CUASAC.
-\item[$(\opk,\osk) \gets OrgKeyGen(\parm)$.] Runs a variant of \IKeyGen from
-  our \CUASGen construction where, instead of using a conventional signature
-  scheme, the issuer leverages its own anonymous credential of level $n$ to
-  create a signature in which it only reveals the credential level. That is,
-  $\sig_{is} \gets \CUASGen.Sign(\isk,\opk',\cred,\msg_{is},\feval^{0,n})$,
-  for some random $\msg_{is}$, and $\opk'$ from \parm, where $\feval^{0,n}$ is a
-  signing evaluation function that reveals no attribute other than the level
-  of the credential. Let $\opk_{n-1}$ be the issuer of the credential \cred
-  (i.e., an issuer with level $n-1$). The current issuer of level $n$ publishes
-  its public key as $(\opk_{n-1},\fissue^n,\sig_{is},\msg_{is})$.
-\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] As in \CUASAC.
-\item[$\langle \cred/\bot,\top/\bot \rangle \gets
-  \langle \Obtain(\usk,\opk,\attrs),\Issue(\osk,\upk,\attrs) \rangle$.]
-  As in \CUASAC.
-\item[$1/0 \gets \langle Show(\opk,\attrs,\dattrs,\cred),
-  \Verify(\opk,\dattrs) \rangle$.]
-  As in \CUASAC, but using $\feval^{\dattrs,n}$ as signature evaluation
-  function.
-\end{description}
+As stated, we restrict to privacy-1 of MPS. Unforgeability-1 in MPS is
+equivalent to sign unforgeability in \UAS. Unforgeability-2 in MPS is
+equivalent to non-frameability in \UAS. Finally note that, in UAS, we do not
+explicitly model extractability, but rather make it an inherent requirement in
+the unforgeability and non-frameability definitions. Thus, our \CUASMPS
+construction also ensures MPS-extractability.
 
-\paragraph{Security of \CUASDAC.} %
-We need to define $level(\opk,n)$. This function first parses \parm
-as $(\parm',\opk')$, and \opk as $(\opk_{n-1},\fissue^n,\sig_{is},\msg_{is})$,
-and returns $\CUASGen.Verify(\opk_{n-1},\opk',\sig_{is},n,\msg_{is},
-\feval^{0,n})$.
+\begin{theorem}[Privacy-1 of \CUASMPS]
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASMPS satisfies privacy-1
+  according to \needcite.
+\end{theorem}
 
-Given $level$, the security proofs are as for \CUASAC, with the addition that,
-in the unforgeability game, an adversary winning because of $level(\opk,n) = 0$
-can be directly used to break the sign unforgeability property of the underlying
-\CUASGen scheme.
-\fi
+\begin{proof}
+  The proof is direct, by observing that the models are equivalent.
 
-\subsection{Multimodal Private Signatures}
-\label{sapp:related-models-mps}
+  First, note that, in MPS the adversary is required to output a function $F$,
+  challenge message, and a pair of user secret keys and witnesses (in \UAS, the
+  witnesses are the credentials). This is precisely what \CHALb requires as
+  input in our \UAS modelling.
+
+  Next, in MPS, validity of the output of $F$ is checked. In MPS, this
+  translates to checking that $F$ does not ouptut $0$. In UAS, this is checked
+  in the \SIGN and \CHALb oracles, which abort if the output produced by \feval
+  does not belong in \rngfeval -- a well defined set of acceptable outputs by
+  the chosen \feval.
+
+  The MPS adversary is then allowed to make more oracle queries, and outputs a
+  response bit. Just as in \UAS. Thus, if \CUASMPS satisfies signature
+  anonymity, it is also an MPS scheme satisfying privacy-1.  
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Extractability of \CUASMPS]
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, then it is an extractable MPS scheme.
+\end{theorem}
+
+\begin{proof}
+  The proof is direct, as the conditions checked in the extractability
+  experiment in MPS are also checked in the signature unforgeability experiment
+  for \UAS.
+
+  Concretely, \Verify must accept the signature, and the ouptut of \feval and
+  \finsp, computed with the values extracted by \ExtractSign, must respectively
+  match those output by the adversary (for \feval), and computed honestly by the
+  signature unforgeability (for \finsp).  
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability-1 of \CUASMPS]
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
+  defined in \needcite.
+\end{theorem}
+
+\begin{proof}
+  For an MPS scheme to satisfy type-1 unforgeability, it has to be extractable.
+  This is directly satisfied by signature unforgeability in \UAS.
+  %
+  Next, the adversary wins in the unforgeability-1 MPS experiment if it manages
+  to produce a signature that has not been produced via a call to their \SIGN
+  oracle, nor it can be associated to an corrupt user. Indeed, if that happens,
+  then such adversary can be used to build an adversary winning the signature
+  unforgeability game against \CUASMPS, through winning condition at line 12 --
+  as \IdentifyUK does not return 1 for any known \uid. Thus, if \CUASMPS has
+  signature unforgeability, it also satisfies unforgeability-1 of MPS schemes.
+  %
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability-2 of \CUASMPS]
+  If the base \CUASGen construction has non-frameability according to
+  \defref{def:frame-uas}, then \CUASMPS satisfies unforgeability-2 as
+  defined in \needcite.
+\end{theorem}
+
+\begin{proof}
+  For an MPS scheme to have type-2 unforgeability, it has to be extractable.
+  This is directly satisfied by non-frameability in UAS (a similar reasoning
+  as for signature unforgeability and extractability applies here).
+  %
+  Next, in MPS, the adversary wins if the produced signature has not been
+  output by the \SIGN oracle, but Extract outputs the identifier of an honest
+  user. This is the same check done in lines 9 and 10 of the non-frameability
+  game in \UAS. Therefore, if \CUASMPS satisfies non-frameability as defined in
+  \defref{def:frame-uas}, it also satisfies type-2 unforgeability in MPS.
+  \qed
+\end{proof}
 

### 2022-07-04 prism-backend/research/gsac/app-related-extra.tex
More missing files.

--- 2022-06-17 prism-backend/research/gsac/app-model-related.tex
@@
-\section{\UAS-Based Instantiations of Related Schemes}
-\label{app:related-models}
-
-In the following subsections we reproduce models of related schemes in the
-literature. Then, we give concrete \fissue, \feval and \finsp functions that
-make \UAS mimic their functionality. Finally, we prove for each case that
-\UAS -- restricted with the corresponding functions -- indeed meets their
-security models, thus proving that \UAS is a generalization of all of them.
-
-\subsection{Group Signatures}
-\label{sapp:related-models-gs}
-
-We adopt the model in \cite{bsz05}. In this abstraction
-of group signatures, the opener returns an index uniquely identifying the group
-member that created a signature, along with a correctness proof. For ease of
-exposition, assume that, w.l.o.g., this index is just the public key that the
-group member chooses when joining the group\footnote{The user public key is
-  assumed to be accessible from a public table in \cite{bsz05}, so it is direct
-  to translate the public key into an index, if needed.}. A group signature
-scheme, according to \cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign,
-\Verify, \Open and \Judge algorithms, as well as an $\langle\Obtain,\Issue
-\rangle$ interactive protocol. Their description is very similar to that of
-\GSAC, so we refer to \cite{bsz05} for detailed descriptions. For ease of
-reference, we replicate the security games in \figref{fig:model-gs}.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.45\textwidth}        
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gs}(1^\secpar)$}{%
-        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
-        d \gets \adv^{\mathcal{O}^{anon}}(\gpk,\isk) \\
-        \pcreturn d 
-      }
-
-      \vspace*{5em}
-
-      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gs}(1^\secpar)$}{%
-        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
-        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
-        (\gpk,\osk,\isk) \\
-        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
-        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
-        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
-        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
-        GSig(\PRVUK[\upk],\msg) \\
-        \pcreturn 0
-      }       
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.55\textwidth}
-      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gs}(1^\secpar)$}{%
-        (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
-        (\msg,\sig) \gets \adv^{\mathcal{O}^{trace}}(\gpk,\osk) \\
-        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
-        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
-        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
-        = 0: \\ 
-        \pcind \pcreturn 1 \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for group signatures \cite{bsz05}, only with minor    
-    ``harmless'' edits to compare easier with \CUASGS. Concretely, since we
-    output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
-    $\upk \notin \HU \cup \CU$. For the oracles' definitions, check the
-    referenced paper.
-    $\mathcal{O}^{anon} \gets \lbrace Ch,Open,SndToU,WReg,USK,CrptU \rbrace$,
-    $\mathcal{O}^{trace} \gets \lbrace SndToI,AddU,RReg,GSig,USK,CrptU \rbrace$,
-    and $\mathcal{O}^{frame} \gets \lbrace SndToU,WReg,GSig,USK,CrptU \rbrace$.
-  }
-  \label{fig:model-gs}  
-\end{figure}
-
-\subsubsection{\CUASGS construction.} %
-We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
-construction for \UAS, restricted to $\fissue^1$ as issuance function,
-$\feval^0$ as signature evaluation function, and $\finsp^{\upk}$ as opening
-function, is a secure group signature scheme according to the \cite{bsz05}
-model. We first quickly define the algorithms, and then prove security.
-
-\begin{description}
-\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
-  of \CUASGen, and one instance of \IKeyGen and \OKeyGen. Assigns the public
-  keys to \gpk.
-\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \UKeyGen from \CUASGen, and
-  computes $\CCommit(\usk;0)$ as \upk.
-\item[$\langle \cred,\utrans \rangle \gets
-  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
-  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Note that, to
-  constraint to only one credential per user, it suffices to require the user
-  to prove that the ``randomness'' it uses when committing to its private key
-  is actually $0$, and check whether the received commitment has been seen
-  before. For details, see the BBS+ instantiation of the underlying \SBCM
-  building block in \secref{sapp:sbcm}.
-\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
-  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen.
-  Simply returns \sig.
-\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
-  returns whatever $\Verify(\opk,\ipk,\sig,0,\msg,\feval^0)$ from \CUASGen
-  outputs.
-\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Parses \gpk as
-  $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
-  0,\msg,\feval^0)$. Note that, internally, the latter call to \Open runs
-  $\finsp^{\upk}$, where $\upk = \CCommit(\usk;0)$, just as proved in $\langle
-  \Obtain,\Issue\rangle$.
-\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
-  \opk)$, and returns whatever \CUASGen outputs in $\Judge(\opk,\upk,\pi,\sig,
-  0,\msg)$.
-\end{description}
-
-\paragraph{Security of \CUASGS.} %
-We prove that our \CUASGS construction is a secure group signature scheme,
-according to \cite{bsz05}, if the underlying \CUASGen construction is secure.
-
-\begin{theorem}[Anonymity of \CUASGS]
-  If the base \CUASGen construction is anonymous according to
-  \defref{def:anonymity-uas}, then \CUASRing is an anonymous group signature
-  scheme.
-\end{theorem}
-
-\todo{Introducing $(f,g,h)-\CUASGen$ naming convention. Describe it elsewhere.}
-
-\begin{proof}
-  Assume an adversary \adv~ against anonymity in \CUASGS. This directly leads
-  to an adverary \advB against anonymity of the $(\fissue^1,\feval^0,
-  \finsp^{\upk})-\CUASGen$ instance.
-
-  Concretely, observe that calls to \adv's $Ch,Open,SndToU,WReg,USK,CrptU$
-  oracles can be directly simulated by calls to \advB's oracles $\CHALb,
-  \OPEN,\HUGEN,\WREG,\CUGEN$ oracles. Thus, if \adv~ guesses its bit $b$
-  with non-negligible probability, this directly leads to a non-negligible
-  probability of guessing \advB's challenge bit.
-  \qed
-\end{proof}
-
-\begin{theorem}[Traceability of \CUASGS]
-  If the base \CUASGen construction has unforgeable signing according to
-  \defref{def:sign-forge-uas}, then \CUASGS is a traceable group signature
-  scheme.
-\end{theorem}
-
-\begin{proof}
-  Assume an adversary \adv~ against traceability in \CUASGS. We build an
-  adversary \advB against sign unforgeability of the $(\fissue^1,\feval^0,
-  \finsp^{\upk})-\CUASGen$ instance.
-
-  \advB's simulation of \adv~ environment is as in the proof for anonymity
-  of \CUASGS. \advB simply outputs whatever \adv~ outputs in line 2 of its
-  traceability game. Note that, as \CUASGS is a specific instantiation of
-  \CUASGen, whenever \CUASGS accepts a signature, so does \CUASGen. Concretely,
-  assume that \adv~ wins the traceability game in \figref{fig:model-gs} with
-  $\upk \notin \HU \cup \CU$ at line 5. This implies that the check at line 11
-  of the sign unforgeability game (\figref{fig:exp-uas-unfor-sign}) for \CUASGen
-  outputs $0$ for all known {\uid}s. Similarly, if \adv~ wins the traceability
-  game with condition $\Judge(\dots)=0$ at line 5, then \advB wins its sign
-  unforgeability game with the corresponding check at line 6 in
-  \figref{fig:exp-uas-unfor-sign}.
-  %
-  \qed
-\end{proof}
-
-\begin{theorem}[Non-frameability of \CUASGS]
-  If the base \CUASGen construction is non-frameable according to
-  \defref{def:frame-uas}, then \CUASGS is a non-frameable group signature
-  scheme.
-\end{theorem}
-
-\begin{proof}
-  Assume an adversary \adv~ against non-frameability in \CUASGS. We build an
-  adversary \advB against non-frameability of the $(\fissue^1,\feval^0,
-  \finsp^{\upk})-\CUASGen$ instance.
-
-  \advB's simulation of \adv~ environment is as in the proof for anonymity
-  of \CUASGS. \advB simply outputs whatever \adv~ outputs at line 2 of its
-  game. Observe that a winning condition for \adv~ directly implies a winning
-  condition for \advB. Concretely, if $\upk \in \HU \land \PRVUK[\upk] \neq
-  \bot$ in \adv's game, then $\exists \uid \in \HU~\suchthat~\UK[\uid]=\usk$
-  for \advB (line 6 of its game). Similarly, if \Judge returns $1$ in \adv's
-  game, \advB's \Judge also returns $1$ at line 4. Finally, if \adv~ does not
-  corrupt the owner of \upk, then $\uid \in \HU$ in \advB's game, and if \adv
-  does not query its $SIGN$ oracle, then there does not exist a matching entry
-  in $\SIG[\uid]$ for \advB either. Consequently, as stated, \advB wins its
-  non-frameability every time that \adv does.
-  \qed
-\end{proof}
+\section{Relationships with More Schemes}
+\label{app:related-extra}
 
@@
 
-\subsection{Ring Signatures}
-\label{sapp:related-models-rs}
-
-We adopt the model in \cite{bkm06}, where security of ring signatures is
-defined according to the games in \figref{fig:model-rs}. A ring signature
-scheme consists of three algorithms $(KeyGen,Sign,Verify)$. Roughly,
-$((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar)$ produces $n$
-signing key pairs, $\sig \gets Sign(\sk_i,R,\msg)$ creates a signature for
-anonymity set $R \subseteq \lbrace \pk_1, \dots, \pk_t \rbrace$, using secret
-key $\sk_i$, associated to some $\pk_i \in R$; and $1/0 \gets Verify(R,\sig,
-\msg)$ checks if \sig is a valid signature over \msg for ring $R$.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.55\textwidth}        
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rs}(1^\secpar)$}{%
-        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
-        (i_0,i_1,R,\msg,\st) \gets \adv^{SIGN}(\pk_1,\dots,\pk_n) \\
-        \pcif % R \not\subseteq \lbrace [n] \rbrace \lor
-        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \notin R \lor %\\
-        i_0 = i_1: \pcreturn \bot \\
-        \sig \gets Sign(\sk_{i_b},R,\msg)) \\
-        b^* \gets \adv(\sig,\st) \\
-        \pcreturn b^*
-      }        
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.5\textwidth}
-      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rs}(1^\secpar)$}{%
-        ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
-        (R,\sig,\msg) \gets \adv^{SIGN,CORR}(\pk_1,\dots,\pk_n) \\
-        \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
-        \pcreturn 1~\pcif R \subseteq [n] \setminus CU = \emptyset~\land \\
-        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg) \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for ring signatures \cite{bkm06}. The SIGN oracle
-    accepts a $(i,R,\msg)$ tuple, where $pk_i$ must be part of $R$, and
-    returns $\sig \gets Sign(\sk_i,R,\msg)$. The oracle $CORR$ accepts an
-    index $i$, and lets $\adv$ learn $\sk_i$. Corrupted user indexes are
-    added to list $CU$.}
-  \label{fig:model-rs}  
-\end{figure}
-
-Intuitively, a ring signature scheme $rs$ is anonymous if, for every p.p.t.
-\adv, $|\Pr[\Exp^{anon-1}_{\adv,rs}(1^\secpar)] = 1| -
-|\Pr[\Exp^{anon-1}_{\adv,rs}(1^\secpar)] = 0|$ is a negligible function of
-$1^\secpar$; and a ring signature scheme $rs$ is unforgeable if, for every
-p.p.t. \adv, the probability that $\Exp^{forge}_{\adv,rs}(1^\secpar)$ returns
-$1$ is also negligible in $1^\secpar$. For short, we say that a ring signature
-scheme meeting both anonymity and unforgeability as specified above, is a secure
-ring signature scheme.
-
-\subsubsection{\CUASRing Construction.} %
-We show that, as specified in \secref{ssec:uas-ring}, our \CUASGen construction
-for \UAS, with alternative NIZK relationship $\NIZKRel_{\Sign-prv}$ for signing,
-issuance function $\fissue^{\sring}$, signature evaluation function
-$\feval^{\attrs}$, and inspection function $\finsp^0$, is a secure ring
-signature scheme. Thus, in this section, when we write \CUASGen, we refer to
-its specific variant built from the previous modifications.
-
-\begin{description}  
-\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in \CUASGen, but using
-  $\NIZKRel_{\Sign-prv}$ instead of $\NIZKRel_{\Sign}$.  
-\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] As in \CUASGen, using
-  $\fissue^{\sring}$.  
-\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp).$] As in \CUASGen, where every
-  opener that wants to be a valid opener in \CUASRing, needs to set \finsp to
-  $\finsp^0$.  
-\item[$\usk \gets \UKeyGen(\parm).$] Can only be run after \IKeyGen. Let 
-  $\usk \gets \isk$.
-\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
-  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
-  The user picks a ring from an (publicly) available list of issuers (users),
-  i.e. $\sring \gets \lbrace \ipk_i \rbrace_{i \in [t]}$, for some $t$. Then,
-  runs the $\langle \Obtain,\Issue \rangle$ protocol as in \CUASGen, acting both
-  as user and as issuer, and using $\fissue^{\sring}$ as issuance function.
-  \attrs are the public keys of the users (issuers) to be included in the ring.
-\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval).$] As in
-  \CUASGen, using $\feval^{\attrs}$ as sign evaluation function, using
-  as credential for signing the credential obtained in the desired $\langle
-  \Obtain,\Issue \rangle$ session and, as \opk, any previously registered \opk
-  (i.e., such that $\finsp=\finsp^0$).
-\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in \CUASGen.
-  Note that $\sipk = \sring$, and $\feval=\feval^{\attrs}$.
-\item[$\Open$ and $\Judge$.] As in \CUASGen. Note that $\finsp=\finsp^0$.
-\end{description}
-
-\todo{I guess we need to show that changing the NIZK for signing does not affect
-  security. This leads to ``What are the conditions that need to be checked/cannot
-  be altered in the default NIZK sign, that make \CUASGen secure?'' }
-
-\paragraph{Security of \CUASRing.} %
-We prove that our \CUASRing construction is anonymous and unforgeable, if
-the underlying \CUASGen construction is secure.
-
-\begin{theorem}[Anonymity of \CUASRing]
-  If the base \CUASGen construction is anonymous according to
-  \defref{def:anonymity-uas}, then \CUASRing is an anonymous ring signature
-  scheme.
-\end{theorem}
-
-\begin{proof}
-  Assume $\adv$ is an adversary against ring signature anonymity for \CUASRing.
-  Then, we build \advB against anonymity of \CUASGen. Concretely, \advB first
-  generates $n$ keypairs by running its \IGEN (with $\fissue^{\sring}$) and
-  \HUGEN oracles, and runs \OGEN at least once (with $\finsp^0$). Then, invokes
-  $\adv$ passing as public keys the public keys of the $n$ generated issuers
-  (users in \CUASRing). $\adv$'s $SIGN(i,R,\msg)$ queries are processed as
-  follows. If user $i$ has not yet produced a credential for ring $R$, \advB
-  makes a call to its \OBTAIN oracle, using $R$ as attribute set. If such a
-  credential was already produced, then reuse it. Then, \advB uses the
-  corresponding user and credential identifiers as parameters to a query to its
-  own \SIGN oracle (specifying $\feval^{\attrs}$ as signature evaluation
-  function). Eventually, $\adv$ outputs two user indexes, a ring $R$, and
-  message \msg. If the checks at line 4 of \figref{fig:model-rs} pass, \advB
-  generates the challenge signature by calling its own \CHALb oracle, and passes
-  the result to $\adv$. Finally, \advB outputs whatever $\adv$ outputs.
-  %
-  \qed
-\end{proof}
-
-\begin{theorem}[Unforgeability of \CUASRing]
-  If the base \CUASGen construction is non-frameable according to
-  \defref{def:frame-uas}, then \CUASRing is an unforgeable ring signature
-  scheme.
-\end{theorem}
-
-\begin{proof}
-  Assume $\adv$ against unforgeability of \CUASRing wins the game. We build
-  \advB winning the non-frameability game of \CUASGen with the same probability.
-  %
-  \advB prepares the environment as the adversary \advB against anonymity,
-  and answers \adv's queries to the $SIGN$ oracle also as in the anonymity
-  proof. To answer \adv's queries to its $CORR$ oracle, \advB leverages the
-  \ICORR oracle in the non-frameability game for \UAS. Finally, \advB outputs
-  whatever $\adv$ outputs.
-
-  Note that, if $\adv$ wins its game, it means that the public keys of the
-  issuers in $R$ all belong to uncorrupted users. Since the signature is
-  accepted by $Verify$ at line 3 of the ring signature unforgeability game,
-  there exists some \uid with an \usk matching the check at line 6 in the
-  non-frameability game. Moreover, since $\adv$ never queried its $SIGN$
-  oracle, then by construction there cannot exist a matching entry in the
-  $\SIG[\uid]$ table. Thus, \advB wins the non-frameability game whenever
-  $\adv$ wins its unforgeability game. Since \CUASGen is non-frameable, then
-  this probability must be negligible.
-  %
-  \qed
-\end{proof}
-
-\subsection{Anonymous Credentials}
-\label{sapp:related-models-ac}
-
-We adopt the model in \cite{fhs19}, where security of anonymous credentials
-(with selective disclosure). Therein, an anonymous credential scheme is
-defined via $OrgKeyGen$ (which we rename to $IssKeyGen$, and $UserKeyGen$
-algorithms (roughly equivalent to
-\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
-interactive protocols. The issuance interactive protocol is equivalent to
-the issuance protocol in \UAS. Similarly, $Show,Verify$ is equivalent to
-the interactive extension of \Sign and \Verify in \UAS, which we show how
-to build in \secref{ssec:variants-gsac} (for \GSAC, but the case for \UAS is
-equivalent). The security definitions rely on $HU, CU, ObtIss, Obtain, Issue,
-Show$, and $LoR$ oracles, which are essentially equivalent to our \HUGEN,
-\CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb oracles. We refer to
-\cite{fhs19} for the full details. For ease of reference, we summarize the
-security definitions in \cite{fig:model-ac}, with inocuous adaptations to
-make them more suitable for comparison with our definitions.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.5\textwidth}        
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
-        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
-        \pcreturn b^*
-      }        
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.5\textwidth}
-      \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
-        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
-        \langle \cdot,(b,\utrans) \rangle
-        \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
-        \pcif b = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
-        \land D \subseteq \ATTR[j]): \\% \forall j, \OWNR[j] \in \CU
-        % \implies D \not\subseteq \ATTR[j]: \\
-        \pcind \pcreturn 1 \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for anonymous credentials with selective disclosure
-    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
-    \secref{ssec:model-uas}.}
-  \label{fig:model-ac}  
-\end{figure}
-
-\subsubsection{\CUASAC Construction.} %
-We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
-construction for \UAS, restricted to $\fissue^1$ as issuance function,
-$\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as opening
-function, is a secure anonymous credential scheme according to the \cite{fhs19}
-model. We first quickly define the algorithms, and then prove security. Note
-that, for better alignment with \UAS, we add a common setup process which is
-part of $IssKeyGen$ in \cite{fhs19}. The change is inocuous functionality- and
-security-wise, though.
-
-\begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar)$
-    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
-    construction. Returns $\parm \gets (\parm',\opk)$.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
-  \CUASGen construction, setting $\fissue^1$ as issuance function.
-\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
-  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
-\item[$\langle \cred/\bot,\top/\bot \rangle \gets
-  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
-  $\fissue^1$ as issuance function.
-\item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
-  \gets \langle Show(\ipk,\attrs,\dattrs,
-  \cred),\Verify(\ipk,\dattrs) \rangle$.]
-  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
-  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
-  open function, with \opk from \parm as opener public key.
-\end{description}
-
-\paragraph{Security of \CUASAC.} %
-We prove that \CUASAC is an anonymous and unforgeable anonymous credential
-scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
-is anonymous and has unforgeable signing. Note that issuance unforgeability
-of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
-leveraging other credentials not any fixed custom issuance policy. Thus,
-signature unforgeability from \UAS is enough. Note that AC schemes modelled
-as in \cite{fhs19} do not have issuance anonymity, as the user public key
-is passed to the issuer.
-
-\begin{theorem}[Anonymity of \CUASAC]
-  \label{thm:anon-cuasac}
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
-  according to \cite{fhs19}.
-\end{theorem}
-
-\begin{proof}
-  Given \adv~ against anonymity of \CUASAC as defined in \cite{fhs19}, we build
-  an adversary \advB against anonymity of \CUASGen as defined in
-  \defref{def:sign-anonymity-uas}.
-
-  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
-  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR$, \advB redirects to
-  \HUGEN,\CUGEN,\OBTAIN,\SIGN,\CHALb, respectively. Note that ``translating''
-  the inputs from the former into inputs for the latter is trivial.
-  Obviously, if \adv~ wins in its anonymity game, then so does \advB with the
-  same probability.
-  % 
-  \qed
-\end{proof}
-
-\begin{theorem}[Unforgeability of \CUASAC]
-  \label{thm:forge-cuasac}
-  If the base \CUASGen construction has sign unforgeability according to
-  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
-\end{theorem}
-
-\begin{proof}
-  Given \adv~ against unforgeability of \CUASAC as defined in \cite{fhs19}, we
-  build an adversary \advB against sign unforgeability of \CUASGen as defined in
-  \defref{def:sign-forge-uas}.
-
-  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
-  that \adv~ wins its game. Note that, since $b=1$ in line 5 of the
-  unforgeability game of \figref{fig:model-ac}, then by construction, \Verify
-  also returns $1$ in the sign unforgeability game of \UAS. In addition, if
-  there is no corrupt user with a credential containing $D$, then this leads to
-  \advB winning at line 9 in \figref{fig:exp-uas-unfor-sign}, as no credential
-  owned by a corrupt user that can be extracted can make the $\feval^{\dattrs}$
-  function output $\yeval^0=D$. Thus, \advB wins with the same probability as
-  \adv~ does.  
-  %
-  \qed
-\end{proof}
-
-\subsection{Delegatable Anonymous Credentials}
-\label{sapp:related-models-dac}
-
-We give a simple definition for a Delegatable Anonymous Credentials (DAC)
-scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
-our simple scheme built from \CUASGen does not ensure privacy of the delegation
-chain -- which could be achieved by making \feval output projective proofs like
-in \cite{bcc+09}, but since our goal is to showcase the feasibility of building
-DAC from \UAS, we leave that out for brevity. Our simple scheme does, however,
-ensure that a (not top-level) issuer can only delegate attributes contained in a
-credential it owns. Also, for simplicity, we restrict to the case of using one
-credential per signature/interactive credential presentation, and assume that
-all parties use the same opener and \finsp function.
-%
-The functionality is thus defined as in \appref{sapp:related-models-ac}, i.e.,
-we have $Setup$, $IssKeyGen$ and $UserKeyGen$ algorithms, and $\langle Obtain,
-Issue \rangle$ and $\langle Show,Verify \rangle$ interactive protocols.
-%
-In the modelling for this setting, since there are multiple issuers, in addition
-to the oracles in \appref{sapp:related-models-ac}, we use $HI$ and $CI$ oracles,
-equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
-issuers, and corrupt existing ones, respectively. The issuance and sign
-anonymity properties are as before. For unforgeability, we still require
-that no adversary can authenticate using a set of attributes that have not been
-issued to a corrupt user. In addition, we require that for any possible
-successful authentication protocol using a level-$n$ credential, we can extract
-a chain of credentials of length $n$ such that each level-$i$ credential can
-be used successfully to authenticate a level-$(i+1)$ credential up to the
-level-$n$ credential, and that the attributes revealed in the level-$n$
-authentication are contained in all the credentials up the chain.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.45\textwidth}
-      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
-        \pccomment{Abort if challenge creds belong to} \\
-        \pccomment{users with different delegation chains} \\
-        \pcreturn b^*
-      }
-      \vspace*{0.5em}
-
-      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
-        \pccomment{Abort if challenge sigs belong to} \\
-        \pccomment{users with different delegation chains} \\
-        \pcreturn b^*
-      }        
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.55\textwidth}
-      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (D=(n,D'),\ipk_n,\st) \gets
-        \adv^{\mathcal{O}_{forge}}(\parm) \\
-        \langle\cdot,(b,\utrans)\rangle \gets
-        \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
-        \pcif b = 0: \pcreturn 0 \\
-        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
-        \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
-        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
-        \gets ExtractChain(\utrans) \\ 
-        \pcif \exists i \in [1,n]~\suchthat~
-        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
-        \pcind D' \not\subseteq \ATTR[\iid]) \land
-        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
-        \pcind \pcreturn 1 \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for delegatable anonymous credentials with selective
-    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
-    CU,HI,CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon}
-    \gets \lbrace HU,CU,HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$.
-    $\mathcal{O}_{forge} \gets \lbrace HU,CU,HI,CI,Obtain,ObtIss,Issue,Show
-    \rbrace$. $IssLor$ is equivalent to \OBTCHALb in \UAS, whereas $SigLor$ is
-    equivalent to \CHALb. Also, \OWNR and \ATTR tables are essentially as in
-    \secref{ssec:model-uas}. $\ISR[\ipk]$, in this case, returns the identifier
-    of the issuer with public key \ipk. With $D =
-    (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
-    which denotes the level of the credential used for authentication.}
-  \label{fig:model-dac}  
-\end{figure}
-
-\subsubsection{\CUASDAC Construction.} %
-In a delegatable AC (DAC) scheme, all users are (or may be) also issuers. We
-only distinguish between top-level issuers, who have level $n=0$, and
-lower-level issuers, who have level $n>0$. In our \CUASDAC scheme, we assume
-that the first attribute (after the user's secret key) encodes the level of
-the credential. That is, $\attrs_1=n$, for a credential of level $n$. In
-addition, all users (i.e., with $n>0$) who want to delegate have to publicly
-list:
-
-\begin{enumerate}
-\item The level $n$ of the credential they delegate.
-\item Their public key \ipk.
-\item An \UAS signature proving knowledge of a credential of level $n$, and over
-  the attributes that this level-$n$ issuer is delegating.
-\item The \ipk of the parent issuer.
-\item The $\fissue^{n,\dattrs}$ function they will require for delegating.
-\item An $\feval^{n,\dattrs}$ function used to produce the signature at item 2.
-\end{enumerate}
-
-We assume that, from an \ipk, it is possible to find the corresponding issuer
-(e.g., using the previously mentioned public list). The mentioned
-$\fissue^{n,\dattrs}$ functions must follow the pattern in \esref{eq:funcs-dac}.
-Namely, the issuance function checks that the first requested attribute equals
-$n+1$, and that all requested attributes are a subset of the attribute set
-\dattrs being delegated by the level-$n$ issuer. In addition, signature
-evaluation functions $\feval^{n,\dattrs}$, also shown in \esref{eq:funcs-dac},
-must reveal the level of the credential used to produce the \UAS signature at
-item 2, as well as the set of attributes \dattrs that the level-$n$ issuer
-delegates. Verifiers can then trivially check if the set of revealed attributes
-are contained within the attributes delegatable by the parent issuer%
-\footnote{Additional checks may be added in both functions, but this is
-  the bare minimum.}. \figref{fig:XXX} depicts a sample of the delegation chain
-that this structure creates.
-
-\begin{align}
-  & \fissue^{n,\dattrs}(\usk,\cred,\attrs) \coloneqq \lbrace
-    \pcif \attrs_1 = n+1 \land \attrs \subseteq \dattrs: \pcreturn 1; \pcelse \pcreturn 0
-    \rbrace \nonumber \\
-  & \feval^{n,\dattrs}(\usk,\cred,\msg) \coloneqq \lbrace
-    \pcreturn (\attrs_1(\cred),\dattrs(\cred)) \rbrace
-  \label{eq:funcs-dac}
-\end{align}
-
-From this high-level description, we define the algorithms of \CUASDAC:
-
-\begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
-    and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our \CUASGen
-    construction. Returns $\parm \gets (\parm',\opk)$. Note that $\finsp^0$ can
-    be replaced by any desired opening function.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $n=0$, simply run \IKeyGen as
-  in \CUASAC. If $n>0$, note that this is a user who wants to delegate a
-  previously obtained credential \cred. Thus, it has already run $UserKeyGen$
-  below, which internally also runs \IKeyGen as in \CUASGen and sets $\usk \gets
-  \isk$. In addition, the level-$n$ issuer picks a random message $r$ and
-  computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
-  \feval^{n,\dattrs})$, for the \dattrs set it wants to reveal -- which must
-  include the attributes to delegate, and the credential level. It then
-  publishes $(n,\ipk,\Sig,\ipk^{n-1},\fissue^{n,\dattrs},\feval^{n,\dattrs})$,
-  where $\ipk^{n-1}$ is the public key of the parent issuer,
-  $\fissue^{n,\dattrs}$ is an issuance function as described in
-  \esref{eq:funcs-dac}, and $\feval^{n,\dattrs}$ is also as in
-  \esref{eq:funcs-dac}, revealing the attributes that the issuer is willing to
-  delegate..
-\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
-  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
-  $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
-  credentials.
-\item[$\langle \cred/\bot,\top/\bot \rangle \gets
-  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  If $n>0$, the user first finds the corresponding $(n,\ipk,\Sig,\ipk^{n-1},
-  \fissue^{n,\dattrs},\feval^{n,\dattrs})$ tuple, and checks \Sig running
-  \Verify as in \CUASGen (with the retrieved $\feval^{n,\dattrs}$). Then,
-  user and level-$n$ issuer run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
-  using $\fissue^{n,\dattrs}$ as issuance function. If $n=0$, then both run
-  $\langle\Obtain,\Issue\rangle$ as in \CUASGen, using the \fissue function
-  required by the issuer.
-\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle
-  \gets \langle Show(\opk,\attrs,\dattrs,\cred),
-  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of \CUASGen.  
-\end{description}
-
-\paragraph{Security of \CUASDAC.} %
-We prove that \CUASDAC is an anonymous and unforgeable DAC scheme, according to
-the model in \figref{fig:model-dac}, if the underlying \CUASGen construction has
-anonymous issuance and signing, and has unforgeable issuance and signing.
-
-\begin{theorem}[Issuance anonymity of \CUASDAC]
-  If the base \CUASGen construction has issuance anonymity according to
-  \defref{def:issue-anonymity-uas}, then \CUASDAC also has issuance anonymity.
-\end{theorem}
-
-\begin{proof}
-  Given \adv~ against issuance anonymity of \CUASDAC as defined in
-  $\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
-  issuance anonymity of \CUASGen as defined in \defref{def:issue-anonymity-uas}.
-
-  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
-  oracle, i.e.: for calls to $HU,CU,HI,CI,Obtain,Show,IssLoR$, \advB redirects
-  to \HUGEN,\CUGEN,\IGEN,\ICORR,\OBTAIN,\SIGN,\OBTCHALb, respectively. Note that
-  ``translating'' the inputs from the former into inputs for the latter is
-  trivial. Obviously, if \adv~ wins in its issuance anonymity game, then so does
-  \advB with the  same probability.
-  % 
-  \qed
-\end{proof}
-
-\begin{theorem}[Signature anonymity of \CUASDAC]
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASDAC also has signature anonymity.
-\end{theorem}
-
-\begin{proof}
-  This is the same as in \thmref{thm:anon-cuasac}.
-  % 
-  \qed
-\end{proof}
-
-\begin{theorem}[Unforgeability of \CUASAC]
-  If the base \CUASGen construction has issuance and signature unforgeability
-  according to \defref{def:issue-forge-uas} and \defref{def:sign-forge-uas}, and
-  non-frameability according to \defref{def:frame-uas}, then \CUASAC is an
-  unforgeable AC scheme.
-\end{theorem}
-
-\begin{proof}
-  First, we define the $ExtractChain(\utrans)$ function for our construction.
-  Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows for the approach
-    to transform non-interactive signature and verification in \UAS to interactive
-    presentations, as described in \secref{ssec:variants-gsac}.}, where $r$ is a
-  fresh random number produced by the environment (acting as honest verifier),
-  and \Sig is a \CUASGen signature over $r$. Thus, $ExtractChain$ leverages
-  \ExtractSign from \CUASGen (see \secref{ssec:security-uas}) to get the
-  credential and associated \ipk used to produce \Sig. Note that, for this
-  \ipk, $\ipk = \ipk_{n-1}$ in $\Exp^{forge}_{\adv,dac}$. In \CUASDAC, we can
-  leverage $\ipk_{n-1}$ to fetch from the public list a signature $\Sig_{n-1}$
-  generated by the issuer owner of $\ipk_{n-1}$. Again, we apply \ExtractSign
-  from \CUASGen, to get the credential one layer up in the chain.
-  $ExtractChain$ repeats this step, until reaching the top level credential,
-  issued by $\ipk_0$.
-
-  For the proof, we first replace within $Setup$ the $\NIZKSetup$ algorithms for
-  issuance and signing with their corresponding $\NIZKSetup$. Due to their
-  zero-knowledge property, the resulting game is indistinguishable. Also, note
-  that $ExtractChain$ succeeds to extract the corresponding credential chain,
-  due to simulation extractability of the NIZKs.
-
-  From the previous, the same reasoning as in \thmref{thm:forge-cuasac} applies
-  to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
-  suppose that, from \utrans obtained at line 6, $ExtractChain$ outputs a
-  delegation chain that makes \adv~win at line 10. This means that an
-  uncorrupted issuer at position $i-1$ of the chain did not own a credential
-  containing $D'$, but the issuer at position $i$ does. Then, either of the
-  following must happen:
-
-  \begin{itemize}
-  \item The credential of the issuer at position $i$ is a forgery, meaning that
-    it is a valid signature by the issuer at position $i-1$, who did not produce
-    it. This can be used to break signature non-frameability of \CUASGen.
-  \item The credential of the issuer at position $i$ is not a forgery, meaning
-    that it is a valid signature by the issuer at position $i-1$, who produced
-    it. But this contradicts the conditions required by $\fissue^{n,\dattrs}$,
-    and therefore breaks issuance unforgeability of \CUASGen.
-  \end{itemize}
-  %
-  \qed
-\end{proof}
-
 \subsection{Revocable Anonymous Credentials}
@@
 
-Where, $\feval^{\dattrs,F,V,L}$ is parameterized with a one-way function $F$
+Where, $\feval^{\dattrs,F,V,L}$ is parameterized with a one-way and
+collision-resistant function $F$
 (e.g., a cryptographic hash), some constant subset \dattrs of attributes to be
@@
   If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASAC is an
-  anonymous AC scheme according to \cite{fhs19}.
+  \defref{def:sign-anonymity-uas}, and $F$ is one-way and collision-resistant,
+  then \CUASAC is an anonymous AC scheme according to \cite{fhs19}.
 \end{theorem}
@@
   First observe that, given a revocation handle $F(V,id)$ extracted from any
-  credential showing, it is not possible to extract $id$, as $F$ is one-way.
+  credential showing, it is not possible to extract $id$, as $F$ is one-way
+  and collision-resistant.
 
@@
   If the base \CUASGen construction has sign unforgeability according to
-  \defref{def:sign-forge-uas}, and $F$ is one-way, then \CUASRAC is an
-  unforgeable RAC scheme.
+  \defref{def:sign-forge-uas}, and $F$ is one-way and collision-resistant, then
+  \CUASRAC is an unforgeable RAC scheme.
 \end{theorem}
@@
   line 9 is negligible, due to soundness of the NIZK scheme used for signing,
-  and the one-wayness of $F$ in $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.  
+  and the one-wayness and collision-resistance of $F$ in
+  $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.
   % 
@@
 
-\subsection{Multimodal Private Signatures}
-\label{sapp:related-models-mps}
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "uas"
+%%% TeX-master: "uas-paper"
 %%% End:

### 2022-07-10 prism-backend/research/gsac/app-model-related.tex
Beginning refurbishment of the paper.
Defining Extract* and Identify* properties.

@@
 
-\subsection{\CUASMPS construction.} %
+\subsubsection{\CUASMPS construction.} %
 As mentioned, any $(\fissue^1,\feval^{\yeval^1},\finsp^\ast)$-restriction of
@@
   unforgeability game against \CUASMPS, through winning condition at line 12 --
-  as \IdentifyUK does not return 1 for any known \uid. Thus, if \CUASMPS has
+  as \IdentifySig does not return 1 for any known \uid. Thus, if \CUASMPS has
   signature unforgeability, it also satisfies unforgeability-1 of MPS schemes.

### 2022-07-10 prism-backend/research/gsac/app-uas-proofs.tex
Defining Extract* and Identify* properties.

@@
 First, we define the \SimSetup, \ExtractIssue, \ExtractSign, \IdentifyCred and
-\IdentifyUK functions that are needed for some of the properties to be
+\IdentifySig functions that are needed for some of the properties to be
 meaningful, in \figref{fig:helper-funcs}.
@@
 
-      \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred)$}{%
-        \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
+      % \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred)$}{%
+      %   \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
+      % }
+
+      \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred,\ipk)$}{%
+        \pcreturn \SBCMVerify(\ipk,\cred,\usk,\attrs_{\cred}) \\
       }
 
-      \procedure{$\IdentifyUK(\parm,\trap,\uid,\usk)$}{%
+      \procedure{$\IdentifySig(\parm,\trap,\usk,\scred,\Sig)$}{%
         \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
@@
       }
+
+      % \procedure{$\IdentifySig(\parm,\trap,\uid,\usk)$}{%
+      %   \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
+      %   \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
+      %   \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trap,\trans[\cid]) \\
+      %   \pcind \pcif \usk = \usk': \pcreturn 1 \\
+      %   \pcreturn 0
+      % }
+
     \end{minipage}
@@
   \caption{Definition of helper functions \ExtractIssue, \ExtractSign,
-    \IdentifyCred, and \IdentifyUK, for \CUASGen.}
+    \IdentifyCred, and \IdentifySig, for \CUASGen.}
 \end{figure}
@@
 
-  We start from $G_0=\ExpSigAnonb$, and define game $G_1$ to be exactly the same
-  as $G_0$, except that, within the $\Setup$ algorithm, we replace
-  $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. By zero-knowledgeness,
-  $G_1$ is indistinguishable from $G_0$.
-
-  From $G_1$, we consider $G^0_1$, which we define to be $G_1$, for $b=0$
-  (i.e., \ExpSigAnonz, using $\NIZKSimSetup^{\Sign}$). The challenge sent to the
+  We start from $G_0=\ExpSigAnonb$.  %
+  From $G_0$, we consider $G^0_0 = \ExpSigAnonz$. The challenge sent to the
   adversary is $(\csig_0,\yeval) \gets \Sign(\PRVUK[\cuid_0],\PUBOK[\oid],
@@
   % 
-  Further, we build $G_2^0$ from $G_1^0$ by simulating the proof $\pi_0$. That
-  is, in $G_2^0$, $\csig_0 = (\pi_0^s,\ceval,\cinsp)$, where $\pi^s_0 =
+  Further, we build $G_1^0$ from $G_0^0$ by simulating the proof $\pi_0$. That
+  is, in $G_1^0$, $\csig_0 = (\pi_0^s,\ceval,\cinsp)$, where $\pi^s_0 =
   \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
   \ceval,\cinsp,\PUBIK[\scid_0],\PUBOK[\oid]))$. By zero-knowledgeness
-  of $\NIZK^{\Sign}$, $G_2^0$ is indistinguishable from $G_1^0$.
+  of $\NIZK^{\Sign}$, $G_1^0$ is indistinguishable from $G_0^0$.
 
-  Similarly, we consider $G_1^1$ and $G_2^1$. That is, $G_1^1$ is $G_1$
-  for $b=1$, where the challenge
+  Similarly, we consider $G_0^1$ and $G_1^1$. That is, $G_0^1 = \ExpSigAnono$,
+  where the challenge
   sent to the adversary is $(\csig_1,\yeval) \gets \Sign(\PRVUK[\cuid_1],
@@
   \yinsp,r,r'))$, $\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)$, and
-  $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$. As before, $G_2^1$ is built from
-  $G_1^1$, simulating $\pi_1$. That is, in $G_2^1$, $\csig_1 = (\pi_1^s,\ceval,
+  $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$. As before, build $G_1^1$ from
+  $G_0^1$, simulating $\pi_1$. That is, in $G_1^1$, $\csig_1 = (\pi_1^s,\ceval,
   \cinsp)$, where $\pi^s_1 = \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
   \NIZKtrap,(\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
-  \PUBOK[\oid]))$. Again, by zero-knowledge of $\NIZK^{\Sign}$, $G_2^1$ is
-  indistinguishable from $G_1^1$. Note also that $G_2^1$ and $G_2^0$ are
+  \PUBOK[\oid]))$. Again, by zero-knowledge of $\NIZK^{\Sign}$, $G_1^1$ is
+  indistinguishable from $G_0^1$. Note also that $G_1^1$ and $G_1^0$ are
   indistinguishable, due to the IND-CCA property of the encryption scheme
@@
   Finally, consider the definition of $\AdvSigAnon=|\Pr\lbrack
-  \ExpSigAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpSigAnonz(1^\secpar)=1\rbrack|$. As
-  argued, $G_1$ is indistinguishable from $\ExpSigAnonb$, thus
-  $\AdvSigAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
-  G_1^0(1^\secpar)=1\rbrack| \approx
-  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
-  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
-  \AdvSigAnon is negligible.
+  \ExpSigAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpSigAnonz(1^\secpar)=1\rbrack|
+  = |\Pr\lbrack G_0^1(1^\secpar)=1\rbrack-\Pr\lbrack
+  G_0^0(1^\secpar)=1\rbrack| \approx
+  |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
+  G_1^0(1^\secpar)=1\rbrack|$, which is negligible.
   % 
@@
   The only remaining option for $\adv$ to win is via winning condition at line
-  12, meaning that \IdentifyUK fails to find an honest or corrupt users with
+  12, meaning that \IdentifySig fails to find an honest or corrupt users with
   a \usk matching the one used to request the credentials used to produce the
@@
   pair output by \adv~is accepted by \Judge, simulation extractability of
-  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 8 and 9
-  pass. Hence, the probability that the adversary wins at either lines 8 or 9 is
+  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 7 and 8
+  pass. Hence, the probability that the adversary wins at either lines 7 or 8 is
   negligible, after simulation extractability of $\NIZK^{\Sign}$ and

### 2022-07-10 prism-backend/research/gsac/formal-uas.tex
Defining Extract* and Identify* properties.

@@
 \begin{description}
-\item[$\fissue: (\usk,\scred,\attrs)
+\item[$\fissue: (\usk,\attrs_{\scred},\attrs)
   \rightarrow 0/1$.] Chosen by each issuer within a family of functions
@@
   a user with secret key \usk, potentially leveraging a set of previously
-  obtained credentials \scred. \fissue returns $1$ to accept a request, $0$ to
-  reject it.
-\item[$\feval: (\usk,\scred,\msg)
+  obtained credentials with attributes $\attrs_\scred$. \fissue returns $1$ to
+  accept a request, $0$ to reject it.
+\item[$\feval: (\usk,\attrs_{\scred},\msg)
   \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
   family of functions \famfeval, can be set on a per-signature basis. They
-  receive the user secret key \usk, credentials \scred, and message to be signed
+  receive the user secret key \usk, a set $\attrs_{\scred}$ of attributes in the
+  credenetial used for signing, and message to be signed
   \msg. \feval outputs two values, $\yeval^0$ and $\yeval^1$, where the former
@@
   (\yeval^0,\yeval^1)$.
-\item[$\finsp: (\Yeval,\usk,\scred,\msg) \rightarrow \yinsp$.]
+\item[$\finsp: (\Yeval,\usk,\attrs_{\scred},\msg) \rightarrow \yinsp$.]
   Chosen by openers from a family of functions \famfinsp. The opening
@@
 \paragraph{Helper functions \SimSetup, \ExtractIssue, \ExtractSign,
-  \IdentifyCred, and \IdentifyUK.} We assume the existence of these helper
+  \IdentifyCred, and \IdentifySig.} We assume the existence of these helper
 functions. They are not functions available in the actual scheme, but rather to
@@
   generate the signature, and the $\yeval^1$ and \yinsp values.
-\item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
-  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
-  Otherwise, it returns $0$. In order to be meaningful, this requires that,
-  for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
+\item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
+  \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
+  secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
+  $0$.
+
+  The \IdentifyCred function defined by \UAS constructions must satisfy that
+  for any \cred obtained as the result of an $\langle \Obtain,\Issue \rangle$
+  interaction with an honest issuer, there exists \emph{exactly one} set of
+  $(\usk,\attrs_{\cred})$ such that \IdentifyCred equals $1$.
+  %In order to be meaningful, this requires that,
+  %for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
   \IdentifyCred return $1$.
-\item[$\IdentifyUK(\trap,\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret
-  key. This is trivial for honest users, for which there must be a one-to-one
-  relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
-  to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
-  to \uid, extract the used secret key, and check if there is a match. In the
-  latter case, there is no guarantee of getting a one-to-one relationship
-  between \usk and \uid. Also, when used for corrupt users, this can only be
-  used when the issuer is honest, as transcripts are needed. 
+\item[$\IdentifySig(\trap,\usk,\scred,\Sig)$.] Returns $1$ is $(\usk,\scred)$
+  are the secret key and credential set used to produce \Sig, otherwise, returns
+  $0$.
+
+  The \IdentifySig function defined by \UAS constructions must satisfy that, for
+  signatures accepted by \Verify, there must exist \emph{exactly one} $(\usk,
+  \scred)$ combination that makes \IdentifySig return $1$.
+  % . This is trivial for honest users, for which there must be a one-to-one
+  % relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
+  % to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
+  % to \uid, extract the used secret key, and check if there is a match. In the
+  % latter case, there is no guarantee of getting a one-to-one relationship
+  % between \usk and \uid. Also, when used for corrupt users, this can only be
+  % used when the issuer is honest, as transcripts are needed. 
 \end{description}
@@
 
+Security of an \UAS scheme is defined in terms of anonymity, unforgeability and
+non-frameability. Where the first two have variants covering issuance and
+signatures \todo{argue why issuance non-frameability does not make sense}.
+%
+However, as stated, we make use of some helper functions: \ExtractIssue and
+\ExtractSign, which let us recover the witnesses used to produce a credential
+or a signautre; and \IdentifyCred, and \IdentifySig, which associate credentials
+and signatures to user identifiers \uid. Both types of functions have been used
+before. For instance, the extraction-type are used in \cite{lnpy21,nps22}, and
+functions of the identify-type are used in \cite{bfg+11,cdl16,gl19,dl21,fgl21}.
+\todo{Re-write after done.} Indeed, it seems hard to avoid resorting to these
+techniques when there is no traditional notion of opening.
+
+\paragraph{Extractability.} %
+We require that the witnesses used to produce each credential and signature can
+be extracted from the corresponding \utrans and signature, respectively.
+Furthermore, in order for our generalized notion of utility to have meaning, it
+is required that, whenever a credential is issued by an honest issuer, or a
+signature is accepted by \Verify, the extracted values produce the same value as
+the chosen \fissue, \feval and \finsp functions. We capture this in the
+\ExpExtractIssue and \ExpExtractSign games, which are crucial in the
+unforgeability and non-frameability requirements.
+
+\begin{figure*}[htp!]
+  \centering
+  \scalebox{0.9}{
+    \begin{minipage}[t]{0.6\textwidth}
+      \procedure[linenumbering]{$\ExpExtractIssue(1^\secpar)$}{%
+        (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
+        \cid \gets \adv^{\todo{\OExtIss}}(\parm) \\
+        (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
+        \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0: \pcreturn 1 \\
+        \pcreturn 0
+      }
+    \end{minipage}
+    \vspace*{0.5em}
+
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure[linenumbering]{$\ExpExtractSign(1^\secpar)$}{%
+        (\parm, \trap) \gets \SimSetup(1^\secpar) \\
+	(\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets
+        \adv^{\todo{\OExtSig}}(\parm) \\
+	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
+	(\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \gets        
+        \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
+        (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
+        \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
+        \pcreturn 1 \\
+        \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
+        \pcreturn 1 \\
+	\pcreturn 0
+      }
+    \end{minipage}
+  }
+  \caption{Extractability experiments for \UAS schemes.}
+  \label{fig:exp-uas-extract}
+\end{figure*}
+
+\paragraph{Identifiability.} %
+On their own, the extractability properties only ensure that the produced
+credentials and signatures have been produced by leveraging knowledge of some
+witnesses. However, they do not establish any relationship between those
+witnesses and the identity of their owner(s). While the way in which witnesses
+are associated to user identifiers\footnote{We avoid the term \emph{user
+    identity}, as that is very context-specific.} is dependent on the
+construction, we impose some constraints that all schemes need to satisfy.
+Namely, it must be possible to associate any credential (obtained from an honest
+issuer), or any signature accepted by \Verify, to exactly one user identifier.
+
+\begin{figure*}[htp!]
+  \centering
+  \scalebox{0.9}{
+    \begin{minipage}[t]{0.6\textwidth}
+      \procedure[linenumbering]{$\ExpIdentifyCred(1^\secpar)$}{%
+        (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
+        \cid \gets \adv^{\todo{\OIdCred}}(\parm) \\
+        (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
+        \suid \gets \IdentifyCred(\trap,\usk,\scred,\attrs_{\scred},\ipk_{\cred}) \\
+        \pcif |\suid| \neq 1: \pcreturn 1 \\
+        \pcreturn 0
+      }
+    \end{minipage}
+    \vspace*{0.5em}
+
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure[linenumbering]{$\ExpIdentifySign(1^\secpar)$}{%
+        (\parm, \trap) \gets \SimSetup(1^\secpar) \\
+	(\oid,\siid,\Sig,\msg,\feval) \gets \adv^{\todo{\OIdSig}}(\parm) \\
+	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
+	(\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \gets
+        \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
+	\suid \gets \IdentifySig(\trap,\usk,\scred,\Sig) \\
+	\pcif |\suid| \neq 1: \pcreturn 1 \\
+	\pcreturn 0
+      }
+    \end{minipage}
+  }
+  \caption{Identifiability experiments for \UAS schemes.}
+  \label{fig:exp-uas-identify}
+\end{figure*}
+
+\begin{definition}{(Identifiable credentials in \UAS)}
+  \label{def:identify-cred-uas}  
+  We define the advantage \AdvIdCred of $\adv$ against \ExpIdentifyCred as
+  $\AdvIdCred=|\Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack-
+  \Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack|$.
+  %
+  An \UAS scheme satisfies identifiable credentials if, for any p.p.t. adversary
+  $\adv$, \AdvIdentifyCred is a negligible function of $1^\secpar$.
+\end{definition}
+
+\begin{definition}{(Identifiable signatures in \UAS)}
+  \label{def:identify-sig-uas}  
+  We define the advantage \AdvIdSig of $\adv$ against \ExpIdentifySign as
+  $\AdvIdSig=|\Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack-
+  \Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack|$.
+  %
+  An \UAS scheme satisfies identifiable signature if, for any p.p.t. adversary
+  $\adv$, \AdvIdSig is a negligible function of $1^\secpar$.
+\end{definition}
+
 \paragraph{Anonymity.} %
@@
       \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
-      \exists \cred \in \scred~\suchthat~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0: \\
+      \exists \cred \in \scred~\suchthat~\IdentifyCred(\trap,\usk,
+      \attrs_{\cred},\cred,\ipk) = 0: \\
       \pcind \pcreturn 1 \\
@@
       \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
-      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1
-      \lor \Yeval \notin \rngfeval:
+      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
       \pcreturn 1 \\
-      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp'
-      \lor \yinsp \neq \yinsp':
+      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
       \pcreturn 1 \\
       \pcif \exists \cred \in \scred~\suchthat~
-      \IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
+      \IdentifyCred(\tau,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) = 0:
       \pcreturn 1 \\
-      \pcif \nexists \uid~\suchthat~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
+      \pcif \nexists \uid~\suchthat~\IdentifySig(\trap,\usk,\scred,\Sig) = 1:
+      \pcreturn 1 \pccomment{\todo{\uid-\usk}} \\
       \pcreturn 0
@@
 \begin{figure}[htp!]
+  \centering
   \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
@@
     \pcreturn 0 \\
-    \pcif \exists (\cdot,\cdot,\Sig,\Yeval,\msg,\feval)
-    \in \SIG[\uid]: \pcreturn 0 \\    
     (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
@@
     \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
-    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1
-    \lor \Yeval \notin \rngfeval: \pcreturn 1 \\
+    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
     \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
     \lor \yinsp \neq \yinsp': \pcreturn 1 \\   
-    \pcif \exists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \pcreturn 1 \\
+    \pcif \exists \uid \in \HU~\suchthat~\UK[\uid] = \usk \land
+    (\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\uid]: \\
+    \pcind \pcreturn 1 \\
     \pcreturn 0

### 2022-07-11 prism-backend/research/gsac/formal-uas.tex
Re-defining extract* and identify*, and adapting the rest of the properties.

@@
 \begin{description}
-\item[$\fissue: (\usk,\attrs_{\scred},\attrs)
-  \rightarrow 0/1$.] Chosen by each issuer within a family of functions
-  \famfissue, the issuance function defines the customized conditions required
-  by the issuer to grant a credential over attributes \attrs, when requested by
-  a user with secret key \usk, potentially leveraging a set of previously
-  obtained credentials with attributes $\attrs_\scred$. \fissue returns $1$ to
-  accept a request, $0$ to reject it.
+\item[$\fissue: (\usk,\attrs,\attrs_{\scred}) \rightarrow 0/1$.] Chosen
+  by each issuer within a family of functions \famfissue, the issuance function
+  defines the customized conditions required by the issuer to grant a credential
+  over attributes \attrs, when requested by a user with secret key \usk,
+  potentially leveraging a set of previously obtained credentials with
+  attributes $\attrs_\scred$. \fissue returns $1$ to accept a request, $0$ to
+  reject it.
 \item[$\feval: (\usk,\attrs_{\scred},\msg)
@@
   receive the user secret key \usk, a set $\attrs_{\scred}$ of attributes in the
-  credenetial used for signing, and message to be signed
+  credential used for signing, and message to be signed
   \msg. \feval outputs two values, $\yeval^0$ and $\yeval^1$, where the former
@@
 Security of an \UAS scheme is defined in terms of anonymity, unforgeability and
-non-frameability. Where the first two have variants covering issuance and
-signatures \todo{argue why issuance non-frameability does not make sense}.
-%
-However, as stated, we make use of some helper functions: \ExtractIssue and
-\ExtractSign, which let us recover the witnesses used to produce a credential
-or a signautre; and \IdentifyCred, and \IdentifySig, which associate credentials
-and signatures to user identifiers \uid. Both types of functions have been used
-before. For instance, the extraction-type are used in \cite{lnpy21,nps22}, and
-functions of the identify-type are used in \cite{bfg+11,cdl16,gl19,dl21,fgl21}.
-\todo{Re-write after done.} Indeed, it seems hard to avoid resorting to these
-techniques when there is no traditional notion of opening.
+non-frameability. In addition, we make use of some helper functions:
+\ExtractIssue and \ExtractSign, which let us recover the witnesses used to
+produce a credential or a signautre; and \IdentifyCred, and \IdentifySig, which
+associate credentials and signatures to user identifiers \uid. Both types of
+functions have been used before. For instance, the extraction type are used in
+\cite{lnpy21,nps22}, and functions of the identify type are used in
+\cite{bfg+11,cdl16,gl19,dl21,fgl21}. Indeed, it seems hard to avoid resorting to
+these techniques when there is no traditional notion of opening. Since, mostly
+the unforgeability and non-frameability properties build on the extractability
+and identifiability ones, we define them first. Then, we proceed with the usual
+notions.
 
@@
 be extracted from the corresponding \utrans and signature, respectively.
-Furthermore, in order for our generalized notion of utility to have meaning, it
-is required that, whenever a credential is issued by an honest issuer, or a
-signature is accepted by \Verify, the extracted values produce the same value as
-the chosen \fissue, \feval and \finsp functions. We capture this in the
-\ExpExtractIssue and \ExpExtractSign games, which are crucial in the
-unforgeability and non-frameability requirements.
+Furthermore, in order for our generalized notion of utility to be sound, it
+is required that, whenever a credential is issued by an honest issuer, \fissue
+accepts the extracted witnesses; and whenever a signature is accepted by
+\Verify, the extracted witnesses match the expected outputs by \feval and
+\finsp. We capture this in the \ExpExtractIssue and \ExpExtractSign games, which
+are crucial in the unforgeability and non-frameability requirements.
+
+In the extractability variant for credentials, \ExpExtractIssue, the adversary
+wins if it manages to get a credential from an honest user, such that the
+issuance predicate \fissue rejects the extracted witnesses.
+%
+In the variant for signatures, \ExpExtractSign, the adversary wins if the
+witnesses extracted from a signature accepted by \Verify make \feval and \finsp
+output inconsistent values.
+%
+The oracles available in \ExpExtractIssue is, $\OExt \gets (\lbrace\HU,\CU
+\rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN)$. Note that,
+honest issuers are required, as we rely on the availability of $\langle \Obtain,
+\Issue \rangle$ transcripts to assist on the extraction. On the other hand,
+for \ExpExtractSign, as we extract directly from signatures, honest issuers are
+not a requirement, so the adversary is given access to $\ICORR$ too.
 
@@
         (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
-        \cid \gets \adv^{\todo{\OExtIss}}(\parm) \\
+        \cid \gets \adv^{\OExt}(\parm) \\
         (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
@@
 	(\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets
-        \adv^{\todo{\OExtSig}}(\parm) \\
+        \adv^{\OExt,\ICORR}(\parm) \\
 	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
@@
 \paragraph{Identifiability.} %
-On their own, the extractability properties only ensure that the produced
-credentials and signatures have been produced by leveraging knowledge of some
-witnesses. However, they do not establish any relationship between those
-witnesses and the identity of their owner(s). While the way in which witnesses
-are associated to user identifiers\footnote{We avoid the term \emph{user
-    identity}, as that is very context-specific.} is dependent on the
-construction, we impose some constraints that all schemes need to satisfy.
-Namely, it must be possible to associate any credential (obtained from an honest
-issuer), or any signature accepted by \Verify, to exactly one user identifier.
+On their own, the extractability properties only ensure that credentials and
+signatures have been produced by leveraging knowledge of some witnesses.
+However, they do not establish any relationship between those witnesses and
+users. While the actual technicalities of doing so is dependent on the
+construction, we can, modelling-wise, enforce constraints that associate
+user identifiers ({\uid}s, tracked by the game environment) with potential
+witnesses. Namely, we require that it must be possible to associate any
+credential (obtained from an honest issuer), or any signature accepted by
+\Verify, with exactly one user identifier.
+
+As for extractability, we define two variants. For credentials, in
+\ExpIdentifyCred we require the adversary to output the identifier of a
+credential obtained from an honest issuer. The adversary wins if, given the
+witnesses extracted from the corresponding transcript, the \IdentifyCred helper
+function outputs a set \suid of user identifiers with cardinality different than
+$1$.
+%
+Similarly, for signatures, the adversary wins if it is able to produce a
+signature from which the extracted witnesses, when passed to \IdentifySig,
+output a set \suid of user identifiers with cardinality different than $1$.
+%
+The oracles are as in the extractability experiments. Namely, in the
+\ExpIdentifyCred game, the adversary has access to $\OId \gets (\lbrace\HU,\CU
+\rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN)$, while in
+\ExpIdentifySign it also has access to \ICORR. The same reasoning applies.
 
@@
         (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
-        \cid \gets \adv^{\todo{\OIdCred}}(\parm) \\
+        \cid \gets \adv^{\OId}(\parm) \\
         (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
-        \suid \gets \IdentifyCred(\trap,\usk,\scred,\attrs_{\scred},\ipk_{\cred}) \\
-        \pcif |\suid| \neq 1: \pcreturn 1 \\
+        \pcfor \cred \in \scred: \\
+        \pcind \suid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
+        \pcind \pcif |\suid| \neq 1: \pcreturn 1 \\
+        \pcind \pcif \suid~\textrm{differs from previous iterations}: \\
+        \pcind \pcind \pcreturn 1 \\
         \pcreturn 0
@@
         (\parm, \trap) \gets \SimSetup(1^\secpar) \\
-	(\oid,\siid,\Sig,\msg,\feval) \gets \adv^{\todo{\OIdSig}}(\parm) \\
+	(\oid,\siid,\Sig,\msg,\feval) \gets \adv^{\OId,\ICORR}(\parm) \\
 	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
@@
   %
-  An \UAS scheme satisfies identifiable credentials if, for any p.p.t. adversary
-  $\adv$, \AdvIdentifyCred is a negligible function of $1^\secpar$.
+  An \UAS scheme \emph{with extractable issuance} satisfies identifiable
+  credentials if, for any p.p.t. adversary $\adv$, \AdvIdCred is a negligible
+  function of $1^\secpar$.
 \end{definition}
@@
   \label{def:identify-sig-uas}  
-  We define the advantage \AdvIdSig of $\adv$ against \ExpIdentifySign as
-  $\AdvIdSig=|\Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack-
+  We define the advantage \AdvIdSign of $\adv$ against \ExpIdentifySign as
+  $\AdvIdSign=|\Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack-
   \Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack|$.
   %
-  An \UAS scheme satisfies identifiable signature if, for any p.p.t. adversary
-  $\adv$, \AdvIdSig is a negligible function of $1^\secpar$.
+  An \UAS scheme \emph{with extractable signatures} satisfies identifiable
+  signature if, for any p.p.t. adversary $\adv$, \AdvIdSign is a negligible
+  function of $1^\secpar$.
 \end{definition}
@@
       \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
-      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
+      \IK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
       (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
-      \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
-      \exists \cred \in \scred~\suchthat~\IdentifyCred(\trap,\usk,
-      \attrs_{\cred},\cred,\ipk) = 0: \\
-      \pcind \pcreturn 1 \\
+      \pccomment{\ExpIdentifyCred enforces the same \uid is
+        returned for all \scred} \\
+      \uid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
+      \pcif \uid \notin \HU \cup \CU: 
+      %\pcif % \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
+%      \exists \cred \in \scred~\suchthat~\IdentifyCred(\trap,\usk,
+%      \attrs_{\cred},\cred,\ipk_{\cred}) = 0: \\
+      \pcreturn 1 \\
       \pcreturn 0
@@
       = 0: \pcreturn 1 \\
-      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets
+      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
       \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
-      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
-      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
-      \pcreturn 1 \\
-      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
-      \pcreturn 1 \\
-      \pcif \exists \cred \in \scred~\suchthat~
-      \IdentifyCred(\tau,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) = 0:
-      \pcreturn 1 \\
-      \pcif \nexists \uid~\suchthat~\IdentifySig(\trap,\usk,\scred,\Sig) = 1:
-      \pcreturn 1 \pccomment{\todo{\uid-\usk}} \\
+      % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
+      % \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
+      % \pcreturn 1 \\
+      % \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
+      % \pcreturn 1 \\
+      \uid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
+      \uid' \gets \IdentifySig(\trap,\usk,\scred,\Sig) \\
+      \pcif \uid \neq \uid' \lor \uid \notin \HU \cup \CU: \pcreturn 1 \\
+      %\pcif \exists \cred \in \scred~\suchthat~
+%      \IdentifyCred(\tau,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) = 0:
+      % \pcreturn 1 \\
+      % \pcif \nexists \uid~\suchthat~\IdentifySig(\trap,\usk,\scred,\Sig) = 1:
+      % \pcreturn 1 \pccomment{\todo{\uid-\usk}} \\
       \pcreturn 0
@@
   %
-  A \UAS scheme has unforgeable issuance if, for any p.p.t. adversary $\adv$,
-  \AdvForgeIssue is a negligible function of $1^\secpar$.
+  A \UAS scheme \emph{with identifiable credentials} has unforgeable issuance
+  if, for any p.p.t. adversary $\adv$, \AdvForgeIssue is a negligible function
+  of $1^\secpar$.
 \end{definition}
@@
   %
-  A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
-  \AdvForgeSign is a negligible function of $1^\secpar$.
+  A \UAS scheme \emph{with identifiable signatures} has unforgeable signing if,
+  for any p.p.t. adversary $\adv$, \AdvForgeSign is a negligible function of
+  $1^\secpar$.
 \end{definition}
@@
     \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
-    \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
-    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
-    \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
-    \lor \yinsp \neq \yinsp': \pcreturn 1 \\   
+    % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
+    % \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
+    % \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
+    % \lor \yinsp \neq \yinsp': \pcreturn 1 \\
+    \pcif \yinsp \neq \yinsp': \pcreturn 1 \\
     \pcif \exists \uid \in \HU~\suchthat~\UK[\uid] = \usk \land

### 2022-07-15 prism-backend/research/gsac/formal-uas.tex
Some deep syntax re-writing.

--- 2022-07-04 prism-backend/research/gsac/formal-uas.tex
@@
 relationship between issuer and opener.
+
+\paragraph{Users and credentials.} %
+We model a scheme in which every single user may have multiple credentials.
+Moreover, previously obtained credentials can be leveraged simultaneously to
+obtain a new one. In this setting, a perhaps too strict assumption we make is
+that, once a user gets compromised, all of the credentials owned by that user
+are compromised too. While there may be real world situations for which this is
+too aggressive, it is certainly a worst-case scenario, and greatly simplifies
+the modelling.
+%
+Somehow related, we model a scheme in which users generate their secret keys in
+a standalone way, and then leverage their keys to request credentials.
+Therefore, if one ``user'' generates (e.g.) two keys, and then uses each of
+these keys to request multiple credentials, then from the point of view of our
+modelling, we see this \emph{cryptographically} as two different users.
 
@@
 \item[$\langle
-  \Obtain(\usk,\ipk,\scred,\attrs),
+  \Obtain(\usk,\ipk,\sCred,\attrs),
   \Issue(\isk,\sipk,\attrs))  
-  \rangle \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.] %
+  \rangle \rightarrow \langle \Cred/\bot,\utrans/\bot
+  \rangle$.] %
   This interactive protocol lets a user with key \usk running the \Obtain
-  process, receive a credential \cred from an issuer in the system, on attribute
-  set $\attrs$. The user leverages a set of credentials \scred, each with a
-  matching issuer key in \sipk (ommitted in \Obtain for readability). The user
-  outputs the produced credential \cred, while the issuer outputs the protocol
-  transcript \utrans for the produced credential.
-\item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
+  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$ from an
+  issuer in the system, where \cid is a unique identifier for the credential,
+  \ipk is the issuer's public key and \cred is the actual credential, on
+  attribute set \attrs. The user may leverage a set of previously obtained
+  credentials $\sCred=\lbrace (\cid_i,\cattrs_i,\cred_i,\ipk_i)
+  \rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for readability. The
+  user outputs the produced credential \Cred, while the issuer outputs the
+  corresponding protocol transcript \utrans.
+\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
   Upon receiving a user secret key \usk, opener public key \opk, a set of
-  credentials \scred, a message \msg and evaluation function \feval, returns
-  signature \sig, and a plaintext value \yeval. For readability, we assume
-  that, for each $\cred \in \scred$, we can get the corresponding issuer public
-  key \ipk; also, we use use \Sig to denote the tuple $(\sig,\yeval)$.
-\item[$\Verify(\opk, \sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
+  credentials \sCred, a message \msg and evaluation function \feval, returns
+  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
+  tuple $(\sig,\yeval)$.
+\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
   Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
@@
 \begin{description}
-\item[$\fissue: (\usk,\scred,\attrs)
-  \rightarrow 0/1$.] Chosen by each issuer within a family of functions
-  \famfissue, the issuance function defines the customized conditions required
-  by the issuer to grant a credential over attributes \attrs, when requested by
-  a user with secret key \usk, potentially leveraging a set of previously
-  obtained credentials \scred. \fissue returns $1$ to accept a request, $0$ to
-  reject it.
-\item[$\feval: (\usk,\scred,\msg)
+\item[$\fissue: (\usk,\attrs,\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]})
+  \rightarrow 0/1$.] Chosen
+  by each issuer within a family of functions \famfissue, the issuance function
+  defines the customized conditions required by the issuer to grant a credential
+  over attributes \attrs, when requested by a user with secret key \usk,
+  leveraging a set of $n$ previously obtained credentials with identifiers and
+  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where $n$
+  may be $0$ if no previously obtained credential is used). \fissue returns $1$
+  to accept a request, $0$ to reject it.
+\item[$\feval: (\usk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
   \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
   family of functions \famfeval, can be set on a per-signature basis. They
-  receive the user secret key \usk, credentials \scred, and message to be signed
-  \msg. \feval outputs two values, $\yeval^0$ and $\yeval^1$, where the former
-  is revealed in plaintext along with the signature, and $\yeval^1$ is
-  encrypted. Both can be used to modulate the bevahiour of \finsp, and must
-  belong in a well defined set \rngfeval. For readability, we write $\Yeval =
-  (\yeval^0,\yeval^1)$.
-\item[$\finsp: (\Yeval,\usk,\scred,\msg) \rightarrow \yinsp$.]
+  receive the user secret key \usk, a set of credentials with identifiers and
+  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
+  $n \ge 1$), and the message to be signed \msg. \feval outputs two values,
+  $\yeval^0$ and $\yeval^1$, which can be used to modulate the bevahiour of
+  \finsp, and must belong in a well defined set \rngfeval. For readability, we
+  write $\Yeval = (\yeval^0,\yeval^1)$.
+\item[$\finsp: (\Yeval,\usk,\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},\msg)
+  \rightarrow \yinsp$.]
   Chosen by openers from a family of functions \famfinsp. The opening
-  functions define what utility value, derived from the user's secret key,
-  credentials used for signing, and signed message, should be extractable by an
-  opener. Its behaviour can be modulated by \Yeval, and it outputs a value
-  \yinsp, which must belong in a well defined set \rngfinsp.
+  functions define what utility value (derived from the user's secret key,
+  credentials' identifiers and attributes used for signing, and signed message)
+  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
+  and it outputs a value \yinsp, which must belong in a well defined set
+  \rngfinsp.
 \end{description}
 
-\feval and \finsp may seem redundant. However, observe that the former is chosen
-on a per-signature basis, probably after negotiation between signer and
-verifier. As such, it governs the information revealed at signing time. On the
-other hand, \finsp governs the information that may be revealed after signing.
-Moreover, it is defined by openers, and even though signers and verifiers
+\feval and \finsp may seem redundant. However, the former is chosen on a
+per-signature basis, probably after negotiation between signer and verifier, and
+governs the information revealed at signing time. On the other hand, \finsp
+governs the information that may be revealed after signing, and is defined by
+openers when they set up their key pair. Thus even though signers and verifiers
 may negotiate to use any opener for a given signature, it is not possible for
-an opener to change the chosen function.
+an opener to change the chosen function. In the sequel, we restrict to
+\UAS-acceptable functions, which we will also use to give \CUASGen restrictions.
+Both concepts are defined next.
+
+\begin{definition}{(\UAS-acceptable functions)}
+  \label{def:uas-acc-func}
+  We say that a \fissue (similarly, \feval or \finsp) function chosen from some
+  family \famfissue (similarly, \famfeval or \famfinsp) is \UAS-acceptable if it
+  is one-way with respect to \usk. That is, given the output of \fissue
+  (similarly, \feval or \finsp), it is at least computationally unfeasible to
+  recover the \usk value used to produce it.
+\end{definition}
 
@@
 Users are referred to with user identifiers, \uid; for credentials, we use \cid;
-for issuers, \iid; and for openers, \oid. In all cases, we use bold font to
-denote sets: e.g., \scid and \siid denote sets of credential and issuer
-identifiers. All tables/sets are initialized as empty tables/sets.
+for issuers, \iid; and for openers, \oid. % In all cases, we use bold font to
+% denote sets: e.g., \scid and \siid denote sets of credential and issuer
+% identifiers. All tables/sets are initialized as empty tables/sets.
 
@@
   the system. Thus, it is indexable by \cid. More specifically, it stores
-  tuples of the form $(\uid,\cred,\iid,\attrs,\scid,\siid)$, where \uid is the
-  identity of the owner of the credential, \cred (when available) is the
-  credential itself, \iid is the identifier of the credential issuer, \attrs
-  are the attributes included in \cred, \scid are the identifiers of the
-  credentials (if any) that \uid used to request \cred, and \siid the issuers
-  of those credentials. For notational
-  convenience, we may use $\CRED[\scid]$ to refer to $\CRED[\cid]$ for all
-  $\cid \in \scid$. Also, when clear from context, we sometimes use
-  $\CRED[\cid]$ (resp. $\CRED[\scid]$ to mean \cred (resp. \scred) in
-  $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,\cdot)$ (resp. $\CRED[\scid]$).
+  tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
+  \rbrace_{i \in [n]})$, where \uid is the identifier of the owner of the
+  credential, \cred (when available) is the credential itself, \iid is the
+  identifier of the credential issuer, \attrs are the attributes included in
+  \cred, $n$ is the number of credentials used to support this request, and
+  $(\cid_i,\iid_i)$ for $i \in [n]$ are the corresponding credential and issuer
+  identifiers. For notational convenience, we may use $\CRED[\scid]$
+  to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
+  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$ to
+  mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
+  \cdot,\cdot)$ (resp. $\CRED[\scid]$).
 \item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
@@
 \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
-  ``\uid such that $\CRED[\cid] = (\uid, \cdot, \cdot, \cdot, \cdot)$''.
+  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$''. We
+  may also use \OWNR over a set of {\cid}s (\scid). In that case, our convention
+  is that $\OWNR[\scid]$ returns $\bot$ if not all passed {\cid}s belong to the
+  same \uid.
 \item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
-  ``\attrs such that $\CRED[\cid] = (\cdot, \cdot, \cdot, \attrs, \cdot)$''.
+  ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
 \item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
-  ``\iid such that $\CRED[\cid] = (\cdot, \iid, \cdot, \cdot, \cdot)$''.
+  ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
 \item[\SIG.] Maintains signatures generated via the \SIGN oracle. Entries of
   this table are $(\oid,\scid,\sig,\Yeval,\msg,\feval)$ tuples, where \oid is
-  the opener, \scid is the set of credentials used for
+  the opener, \scid is the set of identifiers of the credentials used for
   signing, \feval is the signing evaluation function, and \sig and \msg are the
@@
 
-        \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\scid)$}{%
+        \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
+          \rbrace_{i \in [n]})$}{%
           \pcif \uid \notin \HU: \pcreturn \bot \\
           \pcif \iid \notin \HI: \pcreturn \bot \\
-          \pcif \exists \cid' \in \scid~\suchthat~\cid' \in \CCRED: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
-          \langle \cred, \utrans \rangle \gets
-          \langle \Obtain(\UK[\uid],\CRED[\scid],\attrs), \\
-          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\scid],\attrs)
+          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
+          \pcreturn \bot \\
+          \langle \Cred, \utrans \rangle \gets
+          \langle \Obtain(\UK[\uid],\CRED[\lbrace \cid_i\rbrace_{[n]}],\attrs), \\
+          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\lbrace \cid_i\rbrace_{[n]}],\attrs)
           \rangle \\
           \trans[\cid] \gets \utrans \\
-          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
+          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, n,
+          \lbrace(\cid_i,\iid_i)\rbrace_{i\in[n]}) \\
           \pcreturn \top \\
@@
 
-        \procedure{$\ISSUE(\cid,\uid,\iid,\attrs,\siid)$}{%
+        \procedure{$\ISSUE(\cid,\uid,\iid,\attrs,\siid=\lbrace \iid_i
+          \rbrace_{i\in[n]})$}{%
           \pcif \uid \notin \CU: \pcreturn \bot \\          
           \pcif \iid \notin \HI: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
+          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
+          \pcreturn \bot \\
           \langle \cdot, \utrans \rangle \gets
@@
           \trans[\cid] \gets \utrans \\
-          \CRED[\cid] \gets (\uid, \cdot, \iid, \attrs, \cdot, \siid) \\
+          \CRED[\cid] \gets (\uid,\cdot,\iid,\attrs,n,\lbrace(\cdot,\iid_i)
+          \rbrace_{i\in[n]}) \\
           \pcreturn \top \\          
@@
 
-        \procedure{$\SIGN(\uid,\oid,\scid,\msg,\feval)$}{%
+        \procedure{$\SIGN(\uid,\oid,\scid=\lbrace\cid_i\rbrace_{i\in[n]},\msg,
+          \feval)$}{%
           \pcif \uid \notin \HU: \pcreturn \bot \\
-          \pcif \exists \cid,\cid' \in \scid~\suchthat~\cid \in \CRED \land
-          \cid' \in \CCRED: \\
+          \pcif \exists i \neq j \in [n]~\suchthat~\cid_i \in \CRED \land
+          \cid_j \in \CCRED: \\
           \pcind \pcreturn \bot \\
           \pcif \feval \notin \famfeval: \pcreturn \bot \\
-          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,\feval) \\
-          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\scid],\msg) \\
+          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
+          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\scid,\msg) \\
           \pcif \Yeval \notin \rngfeval: \pcreturn \bot \\
@@
           \pcind (\tyinsp,\tiproof) \gets
-          \Open(\PRVOK[\oid],\IK[\siid],\\
+          \Open(\PRVOK[\oid],\IK[\ISR[\scid]],\\
           \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
@@
 
-        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
+        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
+          \rbrace_{i\in[n]})$}{%
           \pcif \uid \notin \HU: \pcreturn \bot \\
           \pcif \iid \notin \CI: \pcreturn \bot \\
-          \pcif \exists \cid' \in \scid~\suchthat~\cid' \in \CCRED: \pcreturn \bot \\
+          \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
           \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
-          \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\CRED[\scid],\attrs),\adv \rangle \\
-          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
+          \langle \Cred, \cdot \rangle \gets
+          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\lbrace \cid_i\rbrace_{[n]},
+          \attrs),\adv \rangle \\
+          \CRED[\cid] \gets (\uid,\cred,\iid,\attrs,n,\lbrace(\cid_i,\iid_i)
+          \rbrace_{i\in[n]}) \\
           \pcreturn \top \\
@@
         \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1})$}{%
+          \textrm{\todo{\scid notation}} \\
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
@@
           \fissue(\UK[\cuid_1],\cscid_1,\attrs) \\
-          \langle \cred, \cdot \rangle \gets
-          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\CRED[\cscid_b],\attrs),\adv \rangle \\
-          \CCRED[\cid] \gets (\cuid_b, \cred, \iid, \attrs, \cscid_b, \siid) \\
+          \langle \Cred, \cdot \rangle \gets
+          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\cscid_b,\attrs),\adv \rangle \\
+          \CCRED[\ccid_b] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
           \pcreturn \top \\
@@
         \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1},\msg,\feval)$}{%
+          \textrm{\todo{\scid notation}} \\                    
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
@@
           \pcif \feval \notin \famfeval: \pcreturn \bot \\          
-          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\CRED[\cscid_0],
+          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\cscid_0,
           \msg) \\
           \TYeval = (\tyeval^0,\tyeval^1) \gets
-          \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg) \\
+          \feval(\UK[\cuid_1],\cscid_1,\msg) \\
           \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
@@
           \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
-          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
+          \hspace*{71pt}\cscid_b,\msg,\feval) \\
           \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
-          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
+          \hspace*{80pt}\cscid_{1-b},\msg,\feval) \\          
           \CSIG[\cSig_b] \gets 
@@
 
-\paragraph{Helper functions \SimSetup, \ExtractIssue, \ExtractSign,
-  \IdentifyCred, and \IdentifyUK.} We assume the existence of these helper
-functions. They are not functions available in the actual scheme, but rather to
-the challenger in the experiments we use to formalize security of \UAS schemes.
-Consequently, while we introduce them here and specify some conditions they need
-to meet, their full definition is dependent on the construction. We fully define
-them for our generic construction \CUASGen in \appref{app:uas-proofs}. Similar
-techniques have been used before to prove security in privacy-preserving schemes
-with some sort of accountability, but that do not offer conventional opening as
-vanilla group signatures. For instance, see related works on DAA
-\cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}.
-More concretely, these functions are as follows:
+\paragraph{Helper functions \SimSetup, \ExtractIssue, and \ExtractSign.}
+%, \IdentifyCred, and \IdentifySig.}
+We assume the existence of these helper functions. They are not functions
+available in the actual scheme, but rather to the challenger in the experiments
+we use to formalize security of \UAS schemes.
+% Consequently, while we introduce them here and specify some conditions they need
+% to meet, their definition is dependent on the construction.
+\todo{Better describe this when finished making changes.}
+% We fully define
+% them for our generic construction \CUASGen in \appref{app:uas-proofs}. Similar
+% techniques have been used before to prove security in privacy-preserving schemes
+% with some sort of accountability, but that do not offer conventional opening as
+% vanilla group signatures. For instance, see related works on DAA
+% \cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}.
+% More concretely, these functions are as follows:
 
@@
   trapdoor \trap.
-\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
+\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\usk,\sCred=
+  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]})$.]
   Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
-  and returns the credentials (if any) and their attributes involved in the
-  request. It needs an honest issuer as, otherwise, the transcripts won't be
-  available. 
-\item[$\ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
-  \scred,\attrs_{\scred},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a
-  signature \Sig,
-  as well as the opener identifier \oid, and the identifiers of all issuers of
-  the credentials used to produce the signature over \msg, and for \feval.
-  It outputs the user secret key and credentials (with their attributes) used to
+  and returns the credential set \sCred, if any, involved in the request. It
+  needs an honest issuer as, otherwise, the transcripts won't be available. 
+\item[$\ExtractSign(\trap,\oid,\lbrace \iid_i \rbrace_{i \in [n]},\Sig,\msg,
+  \feval) \rightarrow (\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
+  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a signature
+  \Sig, as well as the opener identifier \oid, and the identifiers of all
+  issuers of the credentials used to produce the signature over \msg, and for
+  \feval. It outputs the user secret key and credential set \sCred used to
   generate the signature, and the $\yeval^1$ and \yinsp values.
-\item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
-  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
-  Otherwise, it returns $0$. In order to be meaningful, this requires that,
-  for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
-  \IdentifyCred return $1$.
-\item[$\IdentifyUK(\trap,\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret
-  key. This is trivial for honest users, for which there must be a one-to-one
-  relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
-  to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
-  to \uid, extract the used secret key, and check if there is a match. In the
-  latter case, there is no guarantee of getting a one-to-one relationship
-  between \usk and \uid. Also, when used for corrupt users, this can only be
-  used when the issuer is honest, as transcripts are needed. 
+% \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
+%   \cred has been issued over attributes $\attrs_{\cred}$ and for a user with
+%   secret key \usk, by honest issuer with public key \ipk. Otherwise, it returns
+%   $0$.
+
+%   The \IdentifyCred function defined by \UAS constructions must satisfy that
+%   for any \cred obtained as the result of an $\langle \Obtain,\Issue \rangle$
+%   interaction with an honest issuer, there exists \emph{exactly one} set of
+%   $(\usk,\attrs_{\cred})$ such that \IdentifyCred equals $1$.
+%   %In order to be meaningful, this requires that,
+%   %for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
+%   \IdentifyCred return $1$.
+% \item[$\IdentifySig(\trap,\usk,\scred,\Sig)$.] Returns $1$ is $(\usk,\scred)$
+%   are the secret key and credential set used to produce \Sig, otherwise, returns
+%   $0$.
+
+%   The \IdentifySig function defined by \UAS constructions must satisfy that, for
+%   signatures accepted by \Verify, there must exist \emph{exactly one} $(\usk,
+%   \scred)$ combination that makes \IdentifySig return $1$.
+%   % . This is trivial for honest users, for which there must be a one-to-one
+%   % relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
+%   % to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
+%   % to \uid, extract the used secret key, and check if there is a match. In the
+%   % latter case, there is no guarantee of getting a one-to-one relationship
+%   % between \usk and \uid. Also, when used for corrupt users, this can only be
+%   % used when the issuer is honest, as transcripts are needed. 
 \end{description}
@@
   \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
+    \textrm{\todo{This needs updating}} \\
     \parm \gets \Setup(1^\secpar) \\
@@
     \pcind \pcif \fissue^{\cid}(\UK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
-    (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\scid],\msg) \\
+    (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\scid,\msg) \\
     \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
@@
     = 0~\lor \\
-    \pcind \yinsp \neq \finsp^\gid((\yeval,\yeval^1),\UK[\uid],\CRED[\scid],\msg)): \\
+    \pcind \yinsp \neq \finsp^\gid((\yeval,\yeval^1),\UK[\uid],\scid,\msg)): \\
     \pcind \pcreturn 1 \\
@@
 \label{sssec:security}
+
+Security of an \UAS scheme is defined in terms of anonymity, unforgeability and
+non-frameability. In addition, we define two auxiliary properties for defining
+the expected behaviour of the \ExtractIssue and \ExtractSign functions.
+\todo{The following may need to be moved elsewhere and/or re-written.}
+For instance, the extraction type are used in
+\cite{lnpy21,nps22}, and functions of the identify type are used in
+\cite{bfg+11,cdl16,gl19,dl21,fgl21}. Indeed, it seems hard to avoid resorting to
+these techniques when there is no traditional notion of opening. Since, mostly
+the unforgeability and non-frameability properties build on the extractability
+and identifiability ones, we define them first. Then, we proceed with the usual
+notions.
+
+% \todo{Maybe do some drawing of the cred tree.}
+
+% In the following, we use some custom notation to refer to the tree-like
+% relationships that may be built between credentials and, more concretely, their
+% related data (like {\usk}s, {\cid}s, and attribute sets {\attrs}s) when a user
+% leverages previously obtained credentials in order to obtain new ones. To
+% facilitate the explanation, we refer to \figref{fig:cred-tree}. In a nutshell,
+% we use $tree_{\cid}$ to refer to the whole tree of {\cid}s that have been used
+% to produce the credential with identifier \cid -- and, similarly, $tree_{\usk}$
+% for {\usk}s, and $tree_{\attrs}$ for attribute sets.
+
+% \begin{figure}[htp!]
+%   \centering
+%   \includegraphics[width=0.5\textwidth]{figures/cred-tree.png}
+%   \caption{Credential trees, and their corresponding notation.
+%     We use $Tree_x$, where $x \in \lbrace \usk,\cid,\attrs \rbrace$ to
+%     denote the whole tree of {\usk}s, {\cid}s, and {\attrs}s. \\
+%     \todo{Move to Tikz.}}
+%   \label{fig:cred-tree}
+% \end{figure}
+
+% \paragraph{Extractability.} %
+% We require that the witnesses used to produce each credential and signature can
+% be extracted from the corresponding \utrans and signature, respectively.
+% Furthermore, in order for our generalized notion of utility to be sound, it
+% is required that, whenever a credential is issued by an honest issuer, \fissue
+% accepts the extracted witnesses; and whenever a signature is accepted by
+% \Verify, the extracted witnesses match the expected outputs by \feval and
+% \finsp. We capture this in the \ExpExtractIssue and \ExpExtractSign games, which
+% are crucial in the unforgeability and non-frameability requirements.
+
+% In the extractability variant for credentials, \ExpExtractIssue, the adversary
+% wins if it manages to get a credential produced by an honest issuer, such that
+% the issuance predicate \fissue rejects the extracted witnesses, or if some of
+% the involved credentials is associated to a different \usk.
+% %
+% In the variant for signatures, \ExpExtractSign, the adversary wins if the
+% witnesses extracted from a signature accepted by \Verify make \feval and \finsp
+% output inconsistent values.
+% %
+% The oracles available in \ExpExtractIssue is, $\OExt \gets (\lbrace\HU,\CU
+% \rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN)$. Note that,
+% for \ExpExtractIssue, honest issuers are required, as we rely on the
+% availability of $\langle \Obtain,\Issue \rangle$ transcripts to assist on the
+% extraction. On the other hand, for \ExpExtractSign, as we extract directly from
+% signatures, honest issuers are not a requirement, so the adversary is given
+% access to $\ICORR$ too.
+
+% \begin{figure*}[htp!]
+%   \centering
+%   \scalebox{0.9}{
+%     \begin{minipage}[t]{0.6\textwidth}
+%       \procedure[linenumbering]{$\ExpExtractIssue(1^\secpar)$}{%
+%         (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
+%         \cid \gets \adv^{\OExt}(\parm) \\
+%         (\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \gets
+%         \ExtractIssue(\trap,\trans[\cid]) \\
+%         \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
+%         \trans[\cid_i]) \\
+%         \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
+%         \pcif \fissue(\usk,\ATTR[\cid],\lbrace \cid_i \rbrace_{i \in [n]},
+%         \lbrace\attrs_i\rbrace_{i \in [n]}) = 0: \\
+%         \pcind \pcreturn 1 \\
+%         \pcreturn 0
+%       }
+%     \end{minipage}
+%     \vspace*{0.5em}
+
+%     \begin{minipage}[t]{0.5\textwidth}
+%       \procedure[linenumbering]{$\ExpExtractSign(1^\secpar)$}{%
+%         (\parm, \trap) \gets \SimSetup(1^\secpar) \\
+% 	(\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets
+%         \adv^{\OExt,\ICORR}(\parm) \\
+% 	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
+% 	(\usk,\lbrace (\cid_i,\attrs_{\cid_i},\cdot) \rbrace_{i\in[n]},
+%         \yeval^1,\yinsp) \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
+%         (\yeval^0,\yeval^1) \gets \feval(\usk,\lbrace\cid_i\rbrace_{i \in [n]},
+%         \lbrace\attrs_i\rbrace_{i \in [n]}, \msg) \\
+%         \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
+%         \pcreturn 1 \\
+%         \pcif \finsp((\yeval^0,\yeval^1),\usk,\lbrace\cid_i\rbrace_{i \in [n]},
+%         \lbrace\attrs_i\rbrace_{i \in [n]},\msg) \neq \yinsp:
+%         \pcreturn 1 \\
+% 	\pcreturn 0
+%       }
+%     \end{minipage}
+%   }
+%   \caption{Extractability experiments for \UAS schemes.}
+%   \label{fig:exp-uas-extract}
+% \end{figure*}
+
+% \paragraph{Identifiability.} %
+% On their own, the extractability properties only ensure that credentials and
+% signatures have been produced by leveraging knowledge of some witnesses.
+% However, they do not establish any relationship between those witnesses and
+% users. While the actual technicalities of doing so is dependent on the
+% construction, we can, modelling-wise, enforce constraints that associate
+% user identifiers ({\uid}s, tracked by the game environment) with potential
+% witnesses. Namely, we require that it must be possible to associate any
+% credential (obtained from an honest issuer), or any signature accepted by
+% \Verify, with exactly one user identifier.
+
+% As for extractability, we define two variants. For credentials, in
+% \ExpIdentifyCred we require the adversary to output the identifier of a
+% credential obtained from an honest issuer. The adversary wins if, given the
+% witnesses extracted from the corresponding transcript, the \IdentifyCred helper
+% function outputs a set \suid of user identifiers with cardinality different than
+% $1$.
+% %
+% Similarly, for signatures, the adversary wins if it is able to produce a
+% signature from which the extracted witnesses, when passed to \IdentifySig,
+% output a set \suid of user identifiers with cardinality different than $1$.
+% %
+% The oracles are as in the extractability experiments. Namely, in the
+% \ExpIdentifyCred game, the adversary has access to $\OId \gets (\lbrace\HU,\CU
+% \rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN)$, while in
+% \ExpIdentifySign it also has access to \ICORR. The same reasoning applies.
+
+% \begin{figure*}[htp!]
+%   \centering
+%   \scalebox{0.9}{
+%     \begin{minipage}[t]{0.6\textwidth}
+%       \procedure[linenumbering]{$\ExpIdentifyCred(1^\secpar)$}{%
+%         (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
+%         \cid \gets \adv^{\OId}(\parm) \\
+%         (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
+%         \pcfor \cred \in \scred: \\
+%         \pcind \suid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
+%         \pcind \pcif |\suid| \neq 1: \pcreturn 1 \\
+%         \pcind \pcif \suid~\textrm{differs from previous iterations}: \\
+%         \pcind \pcind \pcreturn 1 \\
+%         \pcreturn 0
+%       }
+%     \end{minipage}
+%     \vspace*{0.5em}
+
+%     \begin{minipage}[t]{0.5\textwidth}
+%       \procedure[linenumbering]{$\ExpIdentifySign(1^\secpar)$}{%
+%         (\parm, \trap) \gets \SimSetup(1^\secpar) \\
+% 	(\oid,\siid,\Sig,\msg,\feval) \gets \adv^{\OId,\ICORR}(\parm) \\
+% 	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
+% 	(\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \gets
+%         \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
+% 	\suid \gets \IdentifySig(\trap,\usk,\scred,\Sig) \\
+% 	\pcif |\suid| \neq 1: \pcreturn 1 \\
+% 	\pcreturn 0
+%       }
+%     \end{minipage}
+%   }
+%   \caption{Identifiability experiments for \UAS schemes.}
+%   \label{fig:exp-uas-identify}
+% \end{figure*}
+
+% \begin{definition}{(Identifiable credentials in \UAS)}
+%   \label{def:identify-cred-uas}  
+%   We define the advantage \AdvIdCred of $\adv$ against \ExpIdentifyCred as
+%   $\AdvIdCred=|\Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack-
+%   \Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack|$.
+%   %
+%   An \UAS scheme \emph{with extractable issuance} satisfies identifiable
+%   credentials if, for any p.p.t. adversary $\adv$, \AdvIdCred is a negligible
+%   function of $1^\secpar$.
+% \end{definition}
+
+% \begin{definition}{(Identifiable signatures in \UAS)}
+%   \label{def:identify-sig-uas}  
+%   We define the advantage \AdvIdSign of $\adv$ against \ExpIdentifySign as
+%   $\AdvIdSign=|\Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack-
+%   \Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack|$.
+%   %
+%   An \UAS scheme \emph{with extractable signatures} satisfies identifiable
+%   signature if, for any p.p.t. adversary $\adv$, \AdvIdSign is a negligible
+%   function of $1^\secpar$.
+% \end{definition}
 
@@
 
-For both \ExpForgeIssue (in \figref{fig:exp-uas-unfor-issue}) and \ExpForgeSign
-(in \figref{fig:exp-uas-unfor-sign}), the adversary is given access to the
-oracle set $\Oforgeissue = \Oforgesign \gets \lbrace\HU,\CU\rbrace\GEN,\IGEN,
-\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.
+For both \ExpForgeIssue and \ExpForgeSign (in \figref{fig:exp-uas-unfor}), the
+adversary is given access to the oracle set $\Oforgeissue = \Oforgesign \gets
+\lbrace\HU,\CU\rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.
 
 \begin{figure}[htp!]
+  \centering
+  \scalebox{0.9}{
+    \begin{minipage}[t]{0.57\textwidth}
       \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
@@
         \cid \gets \adv^{\Oforgeissue}(\parm) \\
-      \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 0 \\
-      \textrm{Parse}~\CRED[\cid]~\textrm{as}~(\cdot,\cdot,\iid,\cdot,\cdot);~
-      \IK[\iid]~\textrm{as}~((\ipk,\fissue),\cdot) \\
-      (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
-      \pcif \fissue(\usk,\scred,\ATTR[\cid]) = 0 \lor
-      \exists \cred \in \scred~\suchthat~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0: \\
+        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \\
+        \pcind \pcreturn 0 \\
+        % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
+        (\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \\
+        \hspace*{5em}\gets \ExtractIssue(\trap,\trans[\cid]) \\
+        % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
+        % \trans[\cid_i]) \\
+        % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
+        \pcif \fissue(\usk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
+        \rbrace_{i\in[n]}) = 0: \\
         \pcind \pcreturn 1 \\
+        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
         \pcreturn 0
       }
-  \caption{Experiment for unforgeability of credential issuance in \UAS schemes.}
-  \label{fig:exp-uas-unfor-issue}
-\end{figure}
-
-\begin{figure}[htp!]
+    \end{minipage}
+    \begin{minipage}[t]{0.5\textwidth}
       \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
@@
         = 0: \pcreturn 1 \\
-      (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp',r) \gets
-      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
-      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
-      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1
-      \lor \Yeval \notin \rngfeval:
+        % (\usk,\sCred,\tyeval^1,\yinsp') \gets
+        % \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
+        % \pcif \yinsp \neq \yinsp': \pcreturn 1 \\
+        % \pcreturn 0
+	(\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
+        \yeval^1,\yinsp') \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
+        (\yeval^0,\yeval^1) \gets \feval(\usk,\lbrace(\cid_i,\attrs_i)
+        \rbrace_{i\in[n]}, \msg) \\
+        \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
         \pcreturn 1 \\
-      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp'
-      \lor \yinsp \neq \yinsp':
+        \pcif \finsp((\yeval^0,\yeval^1),\usk,\lbrace(\cid_i,\attrs_i)
+        \rbrace_{i\in[n]},\msg)
+        \neq \yinsp \lor \yinsp \neq \yinsp':
         \pcreturn 1 \\
-      \pcif \exists \cred \in \scred~\suchthat~
-      \IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
-      \pcreturn 1 \\
-      \pcif \nexists \uid~\suchthat~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
+        \pcif \OWNR[\scid] \notin \HU \cup \CU: \pcreturn 1 \\
         \pcreturn 0        
       }      
-  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
-  \label{fig:exp-uas-unfor-sign}
+    \end{minipage}
+  }
+  \caption{Experiments for credential issuance and signature unforgeability in
+    \UAS schemes.}
+  \label{fig:exp-uas-unfor}
 \end{figure}
+
+% \begin{figure}[htp!]
+%     \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
+%       (\parm,\trap) \gets \Setup(1^\secpar) \\
+%       (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
+%       \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
+%       \SIG[\uid]: \pcreturn 0 \\
+%       \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
+%       \pcreturn 0 \\
+%       (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
+%       \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
+%       = 0: \pcreturn 1 \\
+%       (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
+%       \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
+%       % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
+%       % \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
+%       % \pcreturn 1 \\
+%       % \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
+%       % \pcreturn 1 \\
+%       \uid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
+%       \uid' \gets \IdentifySig(\trap,\usk,\scred,\Sig) \\
+%       \pcif \uid \neq \uid' \lor \uid \notin \HU \cup \CU: \pcreturn 1 \\
+%       %\pcif \exists \cred \in \scred~\suchthat~
+% %      \IdentifyCred(\tau,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) = 0:
+%       % \pcreturn 1 \\
+%       % \pcif \nexists \uid~\suchthat~\IdentifySig(\trap,\usk,\scred,\Sig) = 1:
+%       % \pcreturn 1 \pccomment{\todo{\uid-\usk}} \\
+%       \pcreturn 0
+%     }
+%   \caption{Experiment for unforgeability of signatures in \UAS schemes.}
+%   \label{fig:exp-uas-unfor-sign}
+% \end{figure}
 
@@
 \begin{figure}[htp!]  
+  \centering
+  \scalebox{0.9}{
     \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
@@
       \pcreturn 0 \\
-    \pcif \exists (\cdot,\cdot,\Sig,\Yeval,\msg,\feval)
-    \in \SIG[\uid]: \pcreturn 0 \\    
-    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
+      (\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},\tyeval^1,\yinsp') \gets
       \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
-    \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
-    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1
-    \lor \Yeval \notin \rngfeval: \pcreturn 1 \\
-    \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
-    \lor \yinsp \neq \yinsp': \pcreturn 1 \\    
-    \pcif \exists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \pcreturn 1 \\
+      % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
+      % \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1: \pcreturn 1 \\
+      % \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
+      % \lor \yinsp \neq \yinsp': \pcreturn 1 \\
+      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\lbrace (\cid_i,
+      \attrs_i)\rbrace_i{i\in[n]}, \msg) \\
+      \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
+      \pcreturn 1 \\
+      \pcif \finsp((\yeval^0,\yeval^1),\usk,\lbrace(\cid_i,\attrs_i)
+      \rbrace_{i\in[n]},\msg)
+      \neq \yinsp \lor \yinsp \neq \yinsp': \\
+      \pcind \pcreturn 1 \\
+      \pcif \OWNR[\scid] \in \HU \land
+      (\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\OWNR[\scid]]: \\
+      \pcind \pcreturn 1 \\
       \pcreturn 0
+    }
   }
@@
 generic building blocks. We use three different NP relations in our generic
-construction. Namely:
+construction. Namely: $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
+$\NIZKRel_{\Open}$, described next and specified in CS notation \needcite
+in \figref{fig:nizkrels}.
 
 \begin{description}
-\item[$\NIZKRel_{\Issue}$:] For NIZK proofs at issuance time. It is defined as
-  $\NIZKRel_{\Issue} = \lbrace
-  (\usk,\scred,\attrs_{\scred},r), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
-  \CCommit(usk;r) \land \forall \cred \in \scred,\SBCMVerify(\ipk_{\cred},\cred,
-  \usk,\attrs_{\cred}) = 1 \land \fissue(\usk,\scred,\attrs) = 1 \rbrace$,
-  where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
-  \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
-  The relation requires that the owner commits to, and proves knowledge of,
-  \usk. It also requires that any additional credential supporting the request
-  be a valid credential (signed by some other issuer) and bound to \usk.
-  Finally, the policy defined by \fissue needs to be satisfied.
-\item[$\NIZKRel_{\Sign}$:] For NIZK proofs at signing time. It is defined as
-  $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
-  \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
-  \sipk_{\scred},\Eek,\widetilde{\Eek}): \ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)
-  \land \cinsp= \EEnc (\Eek,\yinsp;r') \land (\yeval^0,\yeval^1) = \feval(\usk,
-  \scred,\msg) \land \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \land
-  \forall \cred \in \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred})
-  = 1) \rbrace$, with $\attrs_{\scred}$ and $\sipk_{\scred}$ as in
-  $\NIZKRel_{\Issue}$. This relation ensures that signatures will produce the
-  correct signature evaluation and opening values, and that any credential used
-  to create the signature is bound to the same \usk key.
+\item[$\NIZKRel_{\Issue}$:] For NIZK proofs at issuance time. Requires that the
+  owner commits to, and proves knowledge of, \usk. It also requires that any
+  additional credential supporting the request be a valid credential (signed by
+  some issuer) and bound to \usk. Finally, it also enforces the
+  corresponding \fissue policy.
+\item[$\NIZKRel_{\Sign}$:] For NIZK proofs at signing time. Ensures that
+  signatures ``encode'' the correct signature evaluation and opening values, and
+  that any credential used to create the signature is bound to the same \usk.
 \item[$\NIZKRel_{\Open}$:] For NIZK proofs at opening time. Ensures that the
-  utility information extracted by the \Open algorithm is correct. It is defined
-  as $\NIZKRel_{\Open} =
-  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$.
+  utility information extracted by the \Open algorithm is correct.
 \end{description}
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.9}{
+    \input{figures/nizk.tex}
+  }
+  \caption{CS specification of the NP relations used in \CUASGen.}
+  \label{fig:nizkrels}
+\end{figure}
 
@@
 %
-From the previous relations, we define the functionality as follows:
+From them, we build \CUASGen as follows.
 
@@
 \paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle\Obtain(\usk,\ipk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle$.} %
+  \langle\Obtain(\usk,\ipk,\lbrace (\cid_i,\cattrs_i,\cred_i) \rbrace_{i\in[n]},
+  \attrs),\Issue(\isk,\lbrace \ipk_i \rbrace_{i\in[n]},\attrs)\rangle$.} %
 The protocol is run between an issuer with key pair $(\ipk,\isk)$, and a user
-with secret key \usk and credentials \scred, where each $\cred \in \scred$ is
-issued by an issuer with public key $\ipk_{\cred} \in \sipk$ (which we assume
-that the user can easily retrieve,
-e.g., from secure storage, given \cred), and attests attributes
-$\attrs_{\cred}$. The user requests a signature on a commitment to the user key,
+with secret key \usk and credentials $\lbrace \cred_i \rbrace_{i\in[n]}$, where
+each $\cred_i$ is issued the corresponding issuer with public key $\ipk_i$, and
+attests attributes $\cattrs_i$. The user requests a signature on a commitment to
+the user key,
 as well as on the attributes in \attrs. In addition, the user proves that the
 issuance function \fissue established by the issuer is satisfied by the
-credentials in $\scred$
-and its user secret key. For this, we use relation $\NIZKRel_{\Issue}$, as
-defined above. The interactive protocol for a user to obtain a credential from
-an issuer of the system is then simply an execution of the interactive signing
-protocol of an \SBCM scheme, where the user runs $\SBCMCom(\ipk,\usk,\attrs)$,
-and the issuer runs $\SBCMSign(\isk,\attrs)$; in both cases, using
+$\cred_i$ credentials and its user secret key. For this, we use relation
+$\NIZKRel_{\Issue}$, as defined above. The interactive protocol for a user to
+obtain a credential from an issuer of the system is then simply an execution of
+the interactive signing
+protocol of an \SBCM scheme, where the user runs $\SBCMCom(\ipk,\usk,\lbrace,
+\cid, \attrs \rbrace)$, and the issuer runs $\SBCMSign(\isk,\lbrace \cid, \attrs
+\rbrace)$, for some commonly agreed and fresh \cid, and using
 $\NIZKRel_{\Issue}$ as \NIZK relation. The credential \cred produced by the user
 is the result of the interactive signing protocol, and the \utrans entry for
-the issuer is its transcript, which is a $(\Ccom,\attrs,\sipk,\cred,\pi)$ tuple.
-
-\paragraph{$\Sig \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
+the issuer is its transcript, which is a $(\Ccom,\lbrace \cid, \attrs\rbrace,
+\lbrace \ipk_i\rbrace_{i\in[n]},\cred,\pi)$ tuple.
+
+\paragraph{$\Sig \gets \Sign(\usk,\opk,
+  \sCred=(\lbrace (\cid_i,\cattrs_i,\cred_i,\ipk_i)\rbrace_{i\in[n]}),
+  \msg,\feval)$.} %
 In the signing algorithm, we make use of relation $\NIZKRel_{\Sign}$.
 % 
-The user first evaluates $(\yeval^0,\yeval^1) \gets \feval (\usk,\scred,\msg)$,
-and computes a random encryption key pair with $(\widetilde{\Eek},
-\widetilde{\Edk}) \gets \EKeyGen(\Eparm)$. Then, the user parses \opk as $(\Svk,\Eek,
-\finsp,\sig_{\finsp})$ and checks that $\Verify(\Svk,\sig_{\finsp},\finsp) = 1$
+The user first evaluates $\Yeval = (\yeval^0,\yeval^1) \gets \feval (\usk,
+\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$.
+Then, parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
+$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$
 (this step may be cached), to compute $\yinsp \gets \finsp((\yeval^0,
-\yeval^1),\usk,\scred,\msg)$, and separately encrypts both $\yeval^1$ and
-\yinsp by running $\ceval \gets \EEnc(\widetilde{\Eek},\yeval^1;r)$ and $\cinsp \gets
-\EEnc(\Eek,\yinsp; r')$ for some fresh randomness $r,r'$. Finally, the user
+\yeval^1),\usk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$, and encrypts
+\yinsp by running $\cinsp \gets \EEnc(\Eek,\yinsp; r)$ for some fresh randomness
+$r$. Finally, the user
 computes $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,
-\scred, \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
-\sipk_{\scred},\Eek,\widetilde{\Eek}))$ and outputs $(\sig = (\NIZKproof,\ceval,
-\cinsp),\yeval^0)$. Note that, depending on the value of \Yeval and \yinsp, the
-user may decide to abort the signing if the resulting values are too
-privacy-threatening.
-
-\paragraph{$1/0 \gets \Verify(\opk,\sipk,\Sig,\msg,\feval)$.} %
+\lbrace(\cid_i,\cattrs_i,\cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r),(\msg,
+\feval,\yeval^0,\cinsp,\lbrace \ipk_i\rbrace_{i\in[n]},\Eek))$ and outputs
+$(\sig = (\NIZKproof,\cinsp),\yeval^0)$. Note that, depending on the value of
+\Yeval and \yinsp, the user may decide to abort
+the signing if the resulting values are too privacy-threatening.
+
+\paragraph{$1/0 \gets \Verify(\opk,\sipk=\lbrace\ipk_i\rbrace_{i\in[n]},
+  \Sig,\msg,\feval)$.} %
 The ``cryptographic'' side of the verification consists on checking
-the NIZK proof. That is, parse \Sig as $(\sig = (\NIZKproof,\cinsp),\yeval,
-\ceval)$ and check whether $\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,
-\ceval,\cinsp,\sipk,\opk)) = 1$. In addition, the verifier may further check
+the NIZK proof. That is, parse \Sig as $(\sig = (\NIZKproof,\cinsp),\yeval)$ and
+check whether $\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,
+\cinsp,\sipk,\opk)) = 1$. In addition, the verifier may further check
 whether \yeval meets its needs.
@@
 (\opk,\sipk, \Sig,\msg,\feval)$. If verification succeeds, it parses
-\Sig as $(\sig=(\NIZKproof,\cinsp),\yeval,\ceval)$, decrypts \Ec by running $\yinsp
+\Sig as $(\sig=(\NIZKproof,\cinsp),\yeval)$, decrypts \Ec by running $\yinsp
 \gets \EDec(\osk,\cinsp)$, and computes $\NIZKproof_{\Open} \gets
@@
 by running $\Verify(\opk,\sipk,\Sig,\msg,\feval)$. If the check succeeds,
-parse \Sig as $((\cdot,\cinsp),\cdot,\cdot)$ and verify \NIZKproof with
+parse \Sig as $((\cdot,\cinsp),\cdot)$ and verify \NIZKproof with
 $\NIZKVerify(\NIZKcrs_{\Open},\NIZKproof,(\cinsp,\yinsp))$. Accept it the NIZK

### 2022-07-15 prism-backend/research/gsac/relationships.tex
Added a paragraph with real-world sample use cases. Fixed some todos.
Some deep syntax re-writing.

@@
 
-  \scalebox{0.95}{
+  \scalebox{0.9}{
     \begin{minipage}[t]{\textwidth}
@@
       \begin{align}
-        & \fissue^1(\usk,\scred,\attrs) \coloneqq 1 \nonumber \\
-        & \fissue^{\sring}(\usk,\scred,\attrs) \coloneqq \pcif \attrs
-          \subseteq \sring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1; \pcelse
-          \pcreturn 0 \nonumber \\
-        & \fissue^{n,\dattrs}(\usk,\cred,\attrs) \coloneqq
-          \pcif \attrs_1(\cred) = n+1 \land \dattrs \subseteq \attrs: \pcreturn 1;
+        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
+        & \fissue^{\sring}(\usk,\attrs,\cdot) \coloneqq \pcif \attrs
+          \subseteq \sring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1;
+          \pcelse \pcreturn 0 \nonumber \\
+        & \fissue^{l,\dattrs}(\usk,\attrs,(\cid,\cattrs)) \coloneqq
+          \pcif \attrs_1 = l+1 \land \attrs \subseteq
+          \lbrace \cattrs_i \rbrace_{i\in\dattrs}: \pcreturn 1;
           \pcelse \pcreturn 0 \nonumber
@@
       \begin{align}
-        & \feval^0(\usk,\scred,\msg) \coloneqq \pcreturn (0,\ast) \nonumber \\
-        & \feval^{\dattrs}(\usk,\cred,\msg) \coloneqq \pcreturn
-          (\dattrs(\cred),\ast) \nonumber \\
-        & \feval^{\attrs}(\usk,\cred,\msg) \coloneqq \pcif \CCommit(\usk;0) \in
-          \attrs: \pcreturn (\attrs(\cred),\ast);
-          \pcelse \pcreturn (\bot,\bot) \nonumber \\
-        & \feval^{n,\dattrs}(\usk,\cred,\msg) \coloneqq
-          \pcreturn \pcreturn((\attrs_1(\cred),\dattrs(\cred)),\ast) \nonumber
+        & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
+        & \feval^{\dattrs}(\cdot,(\cid,\attrs),\cdot)
+          \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
+          \nonumber \\
+        & \feval^{\sring}(\usk,(\cid,\attrs),\cdot)
+          \coloneqq \pcif \CCommit(\usk;0) \in \attrs:
+          \pcreturn (\attrs,\ast);
+          \pcelse \pcreturn \bot \nonumber \\
+        & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
+          \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
+          \nonumber
       \end{align}
@@
 
-  \scalebox{0.95}{
+  \scalebox{0.9}{
     \begin{minipage}[t]{0.5\textwidth}
@@
       \begin{align}
-        & \finsp^0(\yeval,\usk,\cred,\msg) \coloneqq 0 \nonumber \\        
-        & \finsp^{\upk}(\yeval,\usk,\scred,\msg) \coloneqq \CCommit(\usk;0) \nonumber
+        & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
+        & \finsp^{\upk}(\cdot,\usk,\cdot,\cdot) \coloneqq \CCommit(\usk;0)
+          \nonumber
       \end{align}
@@
   \caption{Functions for the \CUASGen restrictions described next.
-    $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
-    $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
-    attribute in \cred. $\ast$ means the output is ignored (in these examples,
-    we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
-    fails.}
+    For readability, we use ``$\cdot$'' to denote input arguments that are
+    ignored; and ``$\ast$'' to denote output values that can be set to anything
+    (but should be ignored). $\bot$ means the function fails.}
+    % $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
+    % $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
+    % attribute in \cred. $\ast$ means the output is ignored (in these examples,
+    % we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
+    % fails.}
   \label{fig:func-restrictions}
@@
 \item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,\msg,\feval).$] As in
-  $\CUASGen^{\Sign-prv}$, using $\feval^{\attrs}$ as sign evaluation function,
+  $\CUASGen^{\Sign-prv}$, using $\feval^{\sring}$ as sign evaluation function,
   using as credential for signing the credential obtained in the desired
@@
 challenge signatures, as long as they have the same \yinsp value. We believe
-that these differences are mostly of theoretical interest, though, and it does
-not seem hard to move from one to the other \todo{check}. In practice,
+that these differences are mostly of theoretical interest, though. In practice,
 what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$

### 2022-07-18 prism-backend/research/gsac/app-building-blocks.tex
Applying comments by Markulf.

@@
 running \SBCMCom proves some arbitrary claim over the messages to be signed
-(both those in committed or plaintext form). This can be done by having this
-party add a NIZK over the corresponding NP statement, which has later to be
-verified by the party running \SBCMSign. We will be using this extension, and
-use $\SBCM^{\NIZKRel}$ to denote such an \SBCM with proofs for claims in
+(both those in committed or plaintext form), as well as over possibly extra
+auxiliary data. This can be done by having this party add a NIZK over the
+corresponding NP statement, which has later to be verified by the party running
+\SBCMSign.
+%
+We use this extension in our \CUASGen construction, and thus extend the previous
+syntax for interactive signing  as follows, to account for an extra NIZK
+relation \NIZKRel proving that a pair of statement $x$ and witness $w$ belong
 \NIZKRel.
+
+\begin{description}
+\item[$\SBCMsig/\bot \gets \langle \SBCMCom^{\NIZKRel}(\SBCMvk,\overline{\smsg},
+  \smsg,(x,w)),\SBCMSign^{\NIZKRel}(\SBCMsk,\smsg,x) \rangle$.] As before, but
+  the party running \SBCMCom, who owns witness $w$ for $x$ in \NIZKRel, proves
+  in zero-knowledge to the party running \SBCMSign that $(x,w) \in \NIZKRel$.
+\end{description}
 
@@
 
+Note that, if needed, it is straightforward to augment the proof \NIZKproof
+produced by the user in the first step with an extended proof that also proves
+that $(x,w) \in \NIZKRel$, for some other relation \NIZKRel, thus implementing
+the augmented interface $\langle\SBCMCom^\NIZKRel,\SBCMSign^\NIZKRel\rangle$ as
+described earlier.
+
 \paragraph{$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\overline{\smsg},\smsg)$.} %

### 2022-07-18 prism-backend/research/gsac/formal-uas.tex
Applying comments by Markulf.

@@
   signatures.
-\item[$\UKeyGen(\parm) \rightarrow \usk$.] Given \parm, returns a user's secret
-  key.
+\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
+  key pair.
 \item[$\langle
@@
 \begin{description}
-\item[$\fissue: (\usk,\attrs,\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]})
-  \rightarrow 0/1$.] Chosen
+\item[$\fissue: ((\upk,\usk),\attrs,\lbrace (\cid_i,\cattrs_i)
+  \rbrace_{i \in [n]}) \rightarrow 0/1$.] Chosen
   by each issuer within a family of functions \famfissue, the issuance function
   defines the customized conditions required by the issuer to grant a credential
-  over attributes \attrs, when requested by a user with secret key \usk,
+  over attributes \attrs, when requested by a user with key pair $(\upk,\usk)$,
   leveraging a set of $n$ previously obtained credentials with identifiers and
@@
   to accept a request, $0$ to reject it.
-\item[$\feval: (\usk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
+\item[$\feval: ((\upk,\usk),\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
   \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
   family of functions \famfeval, can be set on a per-signature basis. They
-  receive the user secret key \usk, a set of credentials with identifiers and
-  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
-  $n \ge 1$), and the message to be signed \msg. \feval outputs two values,
-  $\yeval^0$ and $\yeval^1$, which can be used to modulate the bevahiour of
-  \finsp, and must belong in a well defined set \rngfeval. For readability, we
-  write $\Yeval = (\yeval^0,\yeval^1)$.
-\item[$\finsp: (\Yeval,\usk,\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},\msg)
-  \rightarrow \yinsp$.]
+  receive the user key pair $(\upk,\usk)$, a set of credentials with identifiers
+  and attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
+  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
+  values, $\yeval^0$ and $\yeval^1$, which can be used to modulate the bevahiour
+  of \finsp, and must belong in a well defined set \rngfeval. For readability,
+  we write $\Yeval = (\yeval^0,\yeval^1)$.
+\item[$\finsp: (\Yeval,(\upk,\usk),\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},
+  \msg) \rightarrow \yinsp$.]
   Chosen by openers from a family of functions \famfinsp. The opening
@@
   family \famfissue (similarly, \famfeval or \famfinsp) is \UAS-acceptable if it
-  is one-way with respect to \usk. That is, given the output of \fissue
+  is one-way with respect to $(\upk,\usk)$. That is, given the output of \fissue
   (similarly, \feval or \finsp), it is at least computationally unfeasible to
-  recover the \usk value used to produce it.
+  recover the $(\upk,\usk)$ value used to produce it.
 \end{definition}
@@
 (issuance and signature unforgeability), we require all credentials involved in
-the corresponding process to be associated to a known user. Finally, \UAS
+the corresponding process to be associated to a known user key. Finally, \UAS
 schemes inherit the useful non-frameability property of GS schemes where even
@@
 Users are referred to with user identifiers, \uid; for credentials, we use \cid;
-for issuers, \iid; and for openers, \oid. % In all cases, we use bold font to
-% denote sets: e.g., \scid and \siid denote sets of credential and issuer
-% identifiers. All tables/sets are initialized as empty tables/sets.
+for issuers, \iid; and for openers, \oid.  In all cases, we use bold font to
+denote sets: e.g., \scid and \siid denote sets of credential and issuer
+identifiers. All tables/sets are initialized as empty tables/sets. For
+notational convenience, we often use these identifiers instead of the
+corresponding user/issuer/opener keys.
 
@@
   {\uid}s/{\iid}s/{\oid}s.    
-\item[\UK.] \UK maintains user keys $\usk$. To refer to the key of a specific
-  user, we use $\UK[\uid]$. 
+\item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$. To
+  refer to the key of a specific user, we use $\UK[\uid]$. \PUBUK indexes the
+  public keys, and \PRVUK the private keys.
 \item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
@@
           \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
-          \usk \gets \UKeyGen(\parm) \\
-          \UK[\uid] \gets \usk;
+          (\upk,\usk) \gets \UKeyGen(\parm) \\
+          \UK[\uid] \gets (\upk,\usk);
           \HU \gets \HU \cup \lbrace  \uid \rbrace \\
@@
           \langle \Cred, \utrans \rangle \gets
-          \langle \Obtain(\UK[\uid],\CRED[\lbrace \cid_i\rbrace_{[n]}],\attrs), \\
-          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\lbrace \cid_i\rbrace_{[n]}],\attrs)
+          \langle \Obtain(\UK[\uid],\CRED[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs), \\
+          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs)
           \rangle \\
@@
 
-        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1})$}{%
-          \textrm{\todo{\scid notation}} \\
+        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=
+          \lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
@@
           \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
+          \pcif \exists i\in[n]~\suchthat~
+          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
           \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
@@
           \pcind \pcreturn \bot \\
-          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
           \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
@@
 
-        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1},\msg,\feval)$}{%
-          \textrm{\todo{\scid notation}} \\                    
+        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1}=
+          \lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]},\msg,\feval)$}{%
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
-          \pcif \pcfor d \in \bin~ \exists \cid,\cid' \in \scid_d~\suchthat \\
-          \pcind \cid \in \CRED \land \cid' \in \CCRED: \pcreturn \bot \\
-          \pcif \oid \in \CO: \pcreturn \bot \\
+          \pcif \exists i\in[n]~\suchthat~
+          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
           \pcif \feval \notin \famfeval: \pcreturn \bot \\
@@
           \pcreturn \bot \\          
-          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
           \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
@@
   trapdoor \trap.
-\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\usk,\sCred=
+\item[$\ExtractIssue(\trap,\utrans) \rightarrow ((\upk,\usk),\sCred=
   \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]})$.]
@@
 \item[$\ExtractSign(\trap,\oid,\lbrace \iid_i \rbrace_{i \in [n]},\Sig,\msg,
-  \feval) \rightarrow (\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
+  \feval) \rightarrow ((\upk,\usk),\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
   \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a signature
@@
 Security of an \UAS scheme is defined in terms of anonymity, unforgeability and
-non-frameability. In addition, we define two auxiliary properties for defining
-the expected behaviour of the \ExtractIssue and \ExtractSign functions.
-\todo{The following may need to be moved elsewhere and/or re-written.}
-For instance, the extraction type are used in
-\cite{lnpy21,nps22}, and functions of the identify type are used in
-\cite{bfg+11,cdl16,gl19,dl21,fgl21}. Indeed, it seems hard to avoid resorting to
-these techniques when there is no traditional notion of opening. Since, mostly
-the unforgeability and non-frameability properties build on the extractability
-and identifiability ones, we define them first. Then, we proceed with the usual
-notions.
+non-frameability. We now introduce and formally define the corresponding
+properties.
+% In addition, we define two auxiliary properties for defining
+% the expected behaviour of the \ExtractIssue and \ExtractSign functions.
+% \todo{The following may need to be moved elsewhere and/or re-written.}
+% For instance, the extraction type are used in
+% \cite{lnpy21,nps22}, and functions of the identify type are used in
+% \cite{bfg+11,cdl16,gl19,dl21,fgl21}. Indeed, it seems hard to avoid resorting to
+% these techniques when there is no traditional notion of opening. Since, mostly
+% the unforgeability and non-frameability properties build on the extractability
+% and identifiability ones, we define them first. Then, we proceed with the usual
+% notions.
 
@@
         % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
-        (\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \\
+        ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \\
         \hspace*{5em}\gets \ExtractIssue(\trap,\trans[\cid]) \\
@@
         % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
-        \pcif \fissue(\usk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
+        \pcif \fissue((\upk,\usk),\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
         \rbrace_{i\in[n]}) = 0: \\
@@
         % \pcreturn 0
-	(\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
+	((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
         \yeval^1,\yinsp') \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
-        (\yeval^0,\yeval^1) \gets \feval(\usk,\lbrace(\cid_i,\attrs_i)
+        (\yeval^0,\yeval^1) \gets \feval((\upk,\usk),\lbrace(\cid_i,\attrs_i)
         \rbrace_{i\in[n]}, \msg) \\
@@
         \pcreturn 1 \\
-        \pcif \finsp((\yeval^0,\yeval^1),\usk,\lbrace(\cid_i,\attrs_i)
+        \pcif \finsp((\yeval^0,\yeval^1),(\upk,\usk),\lbrace(\cid_i,\attrs_i)
         \rbrace_{i\in[n]},\msg)
@@
       \pcreturn 0 \\
-      (\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},\tyeval^1,\yinsp') \gets
+      ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},\tyeval^1,\yinsp') \gets
       \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
@@
       % \lor \yinsp \neq \yinsp': \pcreturn 1 \\
-      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\lbrace (\cid_i,
+      \Yeval=(\yeval^0,\yeval^1) \gets \feval((\upk,\usk),\lbrace (\cid_i,
       \attrs_i)\rbrace_i{i\in[n]}, \msg) \\
@@
       \pcreturn 1 \\
-      \pcif \finsp((\yeval^0,\yeval^1),\usk,\lbrace(\cid_i,\attrs_i)
+      \pcif \finsp((\yeval^0,\yeval^1),(\upk,\usk),\lbrace(\cid_i,\attrs_i)
       \rbrace_{i\in[n]},\msg)
@@
   }
-  \caption{CS specification of the NP relations used in \CUASGen.}
+  \caption{CS specification of the NP relations used in \CUASGen.
+  \todo{Is $\C = \CCommit(\usk;r)$ needed now that \upk is added?}}
   \label{fig:nizkrels}
@@
 
-Note that, besides the extensibility introduced via \fissue, \feval and
-\finsp, some aspects of the previous functions could be modified (e.g., one
-could require issuer public keys to be kept private). However, the previous
-relations seem generic enough for a wide variety of applications.
-%
 From them, we build \CUASGen as follows.
@@
 The setup process essentially generates the public parameters for all the
-building blocks. It parses \secpar as $(\Csecpar,\NIZKsecpar,\SBCMsecpar,
-\Esecpar)$. Then, run $\Cparm \gets
-\CSetup(\Csecpar)$, $\SBCMparm \gets  \SBCMSetup(\SBCMsecpar)$, $\Sparm \gets
-\SSetup(\Ssecpar)$, $\Eparm \gets \ESetup(\Esecpar)$, $\NIZKcrs_{\Issue} \gets
-\NIZKSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar)$, $\NIZKcrs_{\Sign} \gets
-\NIZKSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar)$, and $\NIZKcrs_{\Open} \gets
-\NIZKSetup^{\NIZKRel_{\Open}}(\NIZKsecpar)$. Return $(\Cparm,\SBCMparm,
-\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Open},
-\AttrSpace)$. Many of these parameter setup algorithms can
-actually be run by separate entities. For simplicity of exposition, we bundle
-them together here.
+building blocks. It runs $\Cparm \gets \CSetup(\secpar)$, $\SBCMparm \gets
+\SBCMSetup(\secpar)$, $\Sparm \gets \SSetup(\secpar)$, $\Eparm \gets
+\ESetup(\secpar)$, $\NIZKcrs_{\Issue} \gets \NIZKSetup^{\NIZKRel_{\Issue}}
+(\secpar)$, $\NIZKcrs_{\Sign} \gets \NIZKSetup^{\NIZKRel_{\Sign}}(\secpar)$, and
+$\NIZKcrs_{\Open} \gets \NIZKSetup^{\NIZKRel_{\Open}}(\secpar)$. Return $
+(\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},
+\NIZKcrs_{\Open},\AttrSpace)$. % Many of these parameter setup algorithms can
+% actually be run by separate entities. For simplicity of exposition, we bundle
+% them together here.
 
@@
 \SKeyGen(\Sparm)$, $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$,
-$\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$, $\ipk \gets (\Svk,\fissue,
-\sig_{\fissue})$, $\isk \gets \Ssk$ and return $(\ipk,\isk)$.
+$\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$, $\ipk \gets (\SBCMparm,\Svk,
+\fissue,\sig_{\fissue})$, $\isk \gets \Ssk$ and return $(\ipk,\isk)$.
 
@@
 (\Sparm)$, $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, $\sig_{\finsp} \gets \SSign
-(\Ssk,\finsp)$, $\opk \gets (\Svk,\Eek,\finsp,\sig_{\finsp})$, and $\osk \gets
-(\Ssk,\Edk)$.
+(\Ssk,\finsp)$, $\opk \gets (\Sparm,\Svk,\Eek,\finsp,\sig_{\finsp})$, and $\osk
+\gets (\Ssk,\Edk)$.
 
 \paragraph{$\usk \gets \UKeyGen(\parm)$.} %
-Each user, prior to requesting credentials, generates his secret key by parsing
-\parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\AttrSpace)$, and picking randomly
-$\usk \getr \AttrSpace$.
+Each user, prior to requesting credentials, generates his secret key by picking
+randomly $\usk \getr \AttrSpace$. Set $\upk \gets \CCommit(\usk;0)$.
 
@@
 with secret key \usk and credentials $\lbrace \cred_i \rbrace_{i\in[n]}$, where
-each $\cred_i$ is issued the corresponding issuer with public key $\ipk_i$, and
+each $\cred_i$ is issued by an issuer with public key $\ipk_i$, and
 attests attributes $\cattrs_i$. The user requests a signature on a commitment to
-the user key,
-as well as on the attributes in \attrs. In addition, the user proves that the
-issuance function \fissue established by the issuer is satisfied by the
-$\cred_i$ credentials and its user secret key. For this, we use relation
-$\NIZKRel_{\Issue}$, as defined above. The interactive protocol for a user to
-obtain a credential from an issuer of the system is then simply an execution of
-the interactive signing
-protocol of an \SBCM scheme, where the user runs $\SBCMCom(\ipk,\usk,\lbrace,
-\cid, \attrs \rbrace)$, and the issuer runs $\SBCMSign(\isk,\lbrace \cid, \attrs
-\rbrace)$, for some commonly agreed and fresh \cid, and using
-$\NIZKRel_{\Issue}$ as \NIZK relation. The credential \cred produced by the user
-is the result of the interactive signing protocol, and the \utrans entry for
-the issuer is its transcript, which is a $(\Ccom,\lbrace \cid, \attrs\rbrace,
-\lbrace \ipk_i\rbrace_{i\in[n]},\cred,\pi)$ tuple.
+the user key, as well as on the attributes in \attrs. In addition, the user
+proves that the issuance function \fissue established by the issuer is satisfied
+by the $\cred_i$ credentials and its user secret key. This is achieved through
+an execution of an \SBCM interactive signing protocol with $\NIZKRel_{\Issue}$
+as NP relation -- which contains the verification that \fissue returns $1$,
+among other checks as described earlier. Concretely, the user runs
+$\SBCMCom^{\NIZKRel_{\Issue}}(\ipk,\usk,(\cid,\attrs),\lbrace (\cid_i,\cattrs_i,
+\cred_i)\rbrace_{i\in[n]},\lbrace \ipk_i \rbrace_{i\in[n]})$, and the issuer
+runs $\SBCMSign^{\NIZKRel_{\Issue}}(\isk,(\cid,\attrs),\lbrace\ipk_i
+\rbrace_{i\in[n]})$, for some commonly agreed and fresh \cid. The credential
+\cred produced by the user is the result of the interactive signing protocol,
+and the \utrans entry for the issuer is its transcript, which is a $(\Ccom,
+\lbrace \cid,\attrs\rbrace,\lbrace \ipk_i \rbrace_{i\in[n]},\cred,\pi)$ tuple.
 
@@
 
+\subsection{\CUASGen variants}
+\label{ssec:variants}
+
+In previous subsections, we have described a main construction for \CUASGen,
+where generalization is achieved by allowing system designers to specify
+concrete \fissue, \feval and \finsp functions depending on their needs. Note
+however that alternative constructions are possible, that are close to \CUASGen,
+but differ in key aspects while still meeting the \UAS model. We briefly
+describe them next, as we leverage them to build related schemes. Security
+proofs are deferred to \appref{app:uas-variants-proofs}
+
+\paragraph{$\CUASGen^{prv-iss}$: Tweaking $\NIZKRel_{\Sign}$ for issuer
+  privacy.} %
+In \CUASGen, it is required that the identity of the issuer of each credential
+used to produce a signature is revealed. This seems reasonable for usual
+situations since, intuitively, it would seem hard for a verifier to accept a
+signature produced with a credential without knowing if the issuer is
+trustworthy. However, there may also be cases in which relaxations are
+acceptable. For instance, it may be enough to know that the issuer belongs to
+some set of well-known issuers. From a more theoretical point of view, this is
+also interesting, as it allows to mimic ring signatures from \UAS constructions.
+\todo{XXX}
+
+\paragraph{$\CUASGen^{usr-iss}$: Collapsing issuers and users.} %
+On occasions, it may be useful to not make a distinction between issuers and
+users. For instance, for credential delegation, or in decentralized identity
+systems. In both cases, users may end up acting as issuers themselves.
+\todo{XXX}
+
 %%% Local Variables:

### 2022-07-18 prism-backend/research/gsac/preliminaries-paper.tex
Defining Extract* and Identify* properties.
Applying comments by Markulf.

@@
 tuple ($\NIZKSetupRel$,$\NIZKProveRel$,$\NIZKVerify^\NIZKRel$).
-Algorithm $\NIZKcrs \gets \NIZKSetupRel(\NIZKsecpar)$ produces the common
+Algorithm $\NIZKcrs \gets \NIZKSetupRel(\secpar)$ produces the common
 reference string \NIZKcrs. $\NIZKproof/\bot \gets \NIZKProveRel(\NIZKcrs,
@@
 $(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing
-key pair. $\sig/\bot \gets\langle \SBCMCom(\vk,\overline{\smsg},\smsg),
-  \SBCMSign(\sk,\smsg) \rangle$ is an interactive protocol between a user, who
-runs \SBCMCom and has a set of messages $\overline{\smsg}$ to be block-committed,
-and a signer, who owns signing key \sk; both also receive common input a
-block of messages \smsg. The output of the protocol is a signature over
+key pair. $\sig/\bot \gets\langle \SBCMCom^{\NIZKRel}(\vk,\overline{\smsg},
+\smsg,(x,w)),\SBCMSign^\NIZKRel(\sk,\smsg,x) \rangle$ is an interactive protocol
+between a user, who runs \SBCMCom and has a set of messages $\overline{\smsg}$
+to be block-committed, and a signer, who owns signing key \sk; both also receive
+common input a block of messages \smsg. In addition, the user knows a pair
+$(x,w) \in \NIZKRel$, and proves (in zero-knowledge) knowledge of $w$ to the
+signer. The output of the protocol is a signature over
 $\overline{\smsg} \cup \smsg$. Algorithm $1/0 \gets \SBCMVerify(\vk,
-\sig,\overline{\smsg},\smsg)$ verifies a signature \sig over message set
+\sig,\overline{\smsg},\smsg)$ verifies a signature \sig over message vector
 $\overline{\smsg} \cup \smsg$. In addition, the
@@
 \AttrSpace.
+%
+Except when otherwise stated, we assume that, given a credential \cred, the
+public key of its issuer, $\ipk_{\cred}$ can be retrieved. Similarly, the
+attribute set contained in a credential \cred is denoted $\attrs_{\cred}$.
 

### 2022-07-19 prism-backend/research/gsac/formal-uas.tex
Done with main pass after Markulf's comments.

@@
         \procedure{$\OPEN(\oid,\Sig,\msg)$}{%
-          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\Yeval,\msg,\feval)
+          \textrm{Let}~\uid~\textrm{be s.t.}~(\cdot,\scid,\Sig,\Yeval,\cdot,
+          \feval)
           \in \SIG[\uid] \\
@@
           \pcind (\tyinsp,\tiproof) \gets
-          \Open(\PRVOK[\oid],\IK[\ISR[\scid]],\\
+          \Open(\PRVOK[\oid],\PUBIK[\scid],\\
           \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
@@
 
-        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=
-          \lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
+        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
+          \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
@@
 
-        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1}=
-          \lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]},\msg,\feval)$}{%
+        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1}=$\\
+          \hspace*{5em}$\lbrace (\ccid_{0,i},\ccid_{1,i})
+          \rbrace_{i\in[n]},\msg,\feval)$}{%
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
           \pcif \exists i\in[n]~\suchthat~
-          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
+          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \\
+          \pcind \pcreturn \bot \\
           \pcif \feval \notin \famfeval: \pcreturn \bot \\
@@
     \caption{Detailed oracles available in our model (2/2). Oracles for
-      obtaining credentials, signatures, and processing them.}
+      obtaining credentials, signatures, and processing them.
+    \markulf{No concurrent issuing. \adv~is stateful.}}
     \label{fig:oracles2}
@@
 % rewind the game, or program random oracles. The approach needs thus to depend on
-% the concrete construction. \jdv{Although, for the case of \ExtractIssue and
+% the concrete construction. \jesus{Although, for the case of \ExtractIssue and
 %   \IdentifyUK, online extractability (or alternative requirements, such as
@@
 \begin{figure}[htp!]
+  \centering
+  \scalebox{0.9}{
     \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
-    \textrm{\todo{This needs updating}} \\
       \parm \gets \Setup(1^\secpar) \\
@@
       \pcfor \cid \in \scid \pcdo: \\
-    \pcind \textrm{Let}~\scred^{\cid}~\textrm{be the credentials used to obtain}
-    ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,\fissue^{\cid}),\cdot)\\
-    \pcind \pcif \fissue^{\cid}(\UK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
-    (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\scid,\msg) \\
+      \pcind \textrm{Parse}~\CRED[\cid]~\textrm{as}~
+      (\cdot,\cdot,\cdot,\attrs,n,\lbrace(\cid_i,\cdot)\rbrace_{i\in[n]}));
+%      \pcind \textrm{Let}~\scid^{\cid}~\textrm{be the {\cid}s used to obtain}
+%      ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,
+%      \fissue^{\cid}),\cdot)\\
+      \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot)\\
+      \pcind \pcif \fissue(\UK[\uid],\attrs,
+      (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) = 0: \pcreturn 1 \\
+      (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],(\scid,\ATTR[\scid]),\msg) \\
       \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
-    (\yinsp,\iproof) \gets \Open(\PRVOK[\gid],\PUBIK[\scid],\Sig,\msg,\feval) \\
+      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
       \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
       = 0~\lor \\
-    \pcind \yinsp \neq \finsp^\gid((\yeval,\yeval^1),\UK[\uid],\scid,\msg)): \\
+      \pcind \yinsp \neq \finsp^\oid((\yeval,\yeval^1),
+      \UK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
       \pcind \pcreturn 1 \\
       \pcreturn 0
+    }
   }
@@
   \scalebox{0.9}{
-    \begin{minipage}[t]{0.57\textwidth}
+    \begin{minipage}[t]{\textwidth}
       \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
@@
         \cid \gets \adv^{\Oforgeissue}(\parm) \\
-        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \\
-        \pcind \pcreturn 0 \\
+        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
+        \pcreturn 0 \\
         % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
-        ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \\
-        \hspace*{5em}\gets \ExtractIssue(\trap,\trans[\cid]) \\
+        ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
+        \gets \ExtractIssue(\trap,\trans[\cid]) \\
         % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
@@
         \pcif \fissue((\upk,\usk),\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
-        \rbrace_{i\in[n]}) = 0: \\
-        \pcind \pcreturn 1 \\
+        \rbrace_{i\in[n]}) = 0:
+        \pcreturn 1 \\
         \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
@@
       }
-    \end{minipage}
-    \begin{minipage}[t]{0.5\textwidth}
+      \vspace*{0.5em}
+
+    % \end{minipage}    
+    % \begin{minipage}[t]{\textwidth}
       \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
@@
         \pcreturn 1 \\
-        \pcif \OWNR[\scid] \notin \HU \cup \CU: \pcreturn 1 \\
+%        \textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
+        \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin \HU \cup \CU:
+        \pcreturn 1 \\
         \pcreturn 0        
@@
       \pcind \pcreturn 1 \\
+      \textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
       \pcif \OWNR[\scid] \in \HU \land
@@
 
-\paragraph{$\parm \gets \Setup(\secpar,\AttrSpace)$.} %
+\paragraph{$\parm \gets \Setup(\secpar)$.} %
 The setup process essentially generates the public parameters for all the
@@
 (\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},
-\NIZKcrs_{\Open},\AttrSpace)$. % Many of these parameter setup algorithms can
+\NIZKcrs_{\Open})$. % Many of these parameter setup algorithms can
 % actually be run by separate entities. For simplicity of exposition, we bundle
@@
 
+\markulf{Put proofs here for XXXX?}\jesus{I can't parse XXXX.}
+
 \subsection{\CUASGen variants}
@@
 but differ in key aspects while still meeting the \UAS model. We briefly
-describe them next, as we leverage them to build related schemes. Security
-proofs are deferred to \appref{app:uas-variants-proofs}
-
-\paragraph{$\CUASGen^{prv-iss}$: Tweaking $\NIZKRel_{\Sign}$ for issuer
-  privacy.} %
-In \CUASGen, it is required that the identity of the issuer of each credential
-used to produce a signature is revealed. This seems reasonable for usual
-situations since, intuitively, it would seem hard for a verifier to accept a
-signature produced with a credential without knowing if the issuer is
-trustworthy. However, there may also be cases in which relaxations are
-acceptable. For instance, it may be enough to know that the issuer belongs to
-some set of well-known issuers. From a more theoretical point of view, this is
-also interesting, as it allows to mimic ring signatures from \UAS constructions.
-\todo{XXX}
+describe them next, as we leverage them to build related schemes. \todo{Security
+proofs are deferred to \appref{app:uas-variants-proofs}.}
 
@@
 users. For instance, for credential delegation, or in decentralized identity
-systems. In both cases, users may end up acting as issuers themselves.
-\todo{XXX}
+systems. In both cases, users may end up acting as issuers themselves. The
+algorithms are as in \CUASGen, except that there is no \UKeyGen -- or, rather,
+the steps run by \UKeyGen are exactly the same as in \IKeyGen. Concretely,
+$\usk \gets \isk$ and $\upk \gets \ipk$, where \isk and \ipk are generated
+as in \IKeyGen.
+
+\paragraph{$\CUASGen^{hide-iss}$: $\NIZKRel_{\Sign}$ with issuer hiding.} %
+In \CUASGen and $\CUASGen^{usr-iss}$, it is required that the identity of the
+issuer of each credential involved in a signature is revealed. This seems
+reasonable for usual situations since, intuitively, it seems hard that a
+verifier accepts a signature produced with a credential without knowing if the
+credential's issuer is trustworthy. However, there may be cases in which
+relaxations are acceptable. For instance, it may be enough to know that the
+issuer belongs to some set of well-known issuers. We merge this with the
+previous extension that collapses issuers and users. Although it would also be
+possible to apply the modification to \CUASGen independently, from a theoretical
+point of view, the combined extension interesting, as it allows to mimic ring
+signatures.
+
+We show the modified NIZK relation for signing in \figref{fig:nizk-ring}. For
+notational simplicity, we restrict to just one credential per signature.
+%
+Modelling-wise, no changes are needed. Perhaps notably, in this case, the
+anonymity property is still required to enforce that both challenge signatures
+are associated to the same set of (potential) issuers -- otherwise, it is
+trivial to distinguish signatures.
+
+\begin{figure}[ht!]
+  \scalebox{0.9}{
+    \input{figures/nizk-ring.tex}
+  }
+  \caption{$\NIZKRel^{hide-iss}_{\Sign}$ relation for $\CUASGen^{hide-iss}$.}
+  \label{fig:nizk-ring}
+\end{figure}
 

### 2022-07-19 prism-backend/research/gsac/introduction-paper.tex
Done with main pass after Markulf's comments.

@@
   \caption{Summary of schemes that can be instantiated as restrictions of our
-    generic construction, \CUASGen, and proved secure under our \UAS model.
-    $\CUASGen^{\ast}$ denotes that minor changes to the basic construction
-    beyond the concrete $(\fissue,\feval,\finsp)$-restrictions are needed.
-    Between parenthesis we show the adopted reference model, and the section
-    offering full detail.
-  }
+    generic constructions, $\CUASGen^{\ast}$, and proved secure under our \UAS
+    model. Between parenthesis we show the adopted reference model, and the
+    section offering full detail.}
   \label{fig:relations}

### 2022-07-19 prism-backend/research/gsac/relationships.tex
Applying comments by Markulf.
Done with main pass after Markulf's comments.

@@
         & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
-        & \fissue^{\sring}(\usk,\attrs,\cdot) \coloneqq \pcif \attrs
-          \subseteq \sring \cup \lbrace \CCommit(\usk;0) \rbrace: \pcreturn 1;
-          \pcelse \pcreturn 0 \nonumber \\
-        & \fissue^{l,\dattrs}(\usk,\attrs,(\cid,\cattrs)) \coloneqq
-          \pcif \attrs_1 = l+1 \land \attrs \subseteq
-          \lbrace \cattrs_i \rbrace_{i\in\dattrs}: \pcreturn 1;
-          \pcelse \pcreturn 0 \nonumber
+        & \fissue^{single,L}((\upk,\cdot),\cdot,\cdot) \coloneqq
+          \pcreturn \upk \notin L
+          \nonumber \\
+        & \fissue^{\sring}((\upk,\cdot),\attrs,\cdot) \coloneqq
+          \pcreturn (\attrs \subseteq \sring \land \upk \in \sring) \nonumber \\
+        & \fissue^{l,\dattrs}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
+          \pcreturn (\attrs_1 = l+1 \land \attrs \subseteq
+          \lbrace \cattrs_i \rbrace_{i\in\dattrs}) \nonumber
       \end{align}
@@
           \nonumber \\
-        & \feval^{\sring}(\usk,(\cid,\attrs),\cdot)
-          \coloneqq \pcif \CCommit(\usk;0) \in \attrs:
+        & \feval^{\sring}((\upk,\cdot),(\cid,\attrs),\cdot)
+          \coloneqq \pcif \upk \in \attrs:
           \pcreturn (\attrs,\ast);
@@
   \scalebox{0.9}{
-    \begin{minipage}[t]{0.5\textwidth}
+    \begin{minipage}[t]{\textwidth}
       \textbf{Open functions:}
@@
         & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
-        & \finsp^{\upk}(\cdot,\usk,\cdot,\cdot) \coloneqq \CCommit(\usk;0)
+        & \finsp^{\upk}(\cdot,(\upk,\cdot),\cdot,\cdot) \coloneqq
+          \pcreturn \upk % \CCommit(\usk;0)
           \nonumber
@@
 exposition, assume that, w.l.o.g., this index is just the public key that the
-group member chooses when joining the group\footnote{The user public key is
-  assumed to be accessible from a public table in \cite{bsz05}, so it is direct
+group member chooses\markulf{can he choose an existing public key?} when joining the group\footnote{The user public key is
+  assumed to be accessible from a public table in \cite{bsz05}, so it is easy
   to translate the public key into an index, if needed.}. A group signature
@@
 \subsubsection{\CUASGS construction.} %
-We show that the $(\fissue^1,\feval^0,\finsp^{\upk})$-\CUASGen restriction, is
-a secure group signature scheme according to \cite{bsz05}. We first quickly
-define the algorithms, and then prove security.
+We show that the $(\fissue^{single,L},\feval^0,\finsp^{\upk})$-\CUASGen
+restriction, is a secure group signature scheme according to \cite{bsz05}.
+Observe that the $\fissue^{single,L}$ function is further parameterized with
+a list $L$ maintained by the issuer and must be fetched by users prior to
+joining. It restricts that any user can have at most one credential (associated
+to a same user key pair). We first quickly define the algorithms, and then
+prove security.
 
@@
   keys to \gpk.
-\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \UKeyGen from \CUASGen, and
-  computes $\CCommit(\usk;0)$ as \upk.
+\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \UKeyGen from \CUASGen.
 \item[$\langle \cred,\utrans \rangle \gets
   \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
-  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Note that, to
-  constraint to only one credential per user, it suffices to require the user
-  to prove that the ``randomness'' it uses when committing to its private key
-  is actually $0$, and check whether the received commitment has been seen
-  before.
+  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$.
 \item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
-  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen.
-  Simply returns \sig.
+  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen --
+  note that $0$ is the constant output of $\feval^0$.
 \item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
@@
   $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
-  0,\msg,\feval^0)$. Internally, the call to \Open runs
-  $\finsp^{\upk}$, where $\upk = \CCommit(\usk;0)$, just as proved in $\langle
-  \Obtain,\Issue\rangle$.
+  0,\msg,\feval^0)$. Internally, the call to \Open runs $\finsp^{\upk}$.
 \item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
@@
   \defref{def:sign-forge-uas}, then \CUASGS is a traceable group signature
-  scheme.
+  scheme.\markulf{Hiding of $Com(\usk;0)$?}
 \end{theorem}
@@
         (i_0,i_1,R,\msg,\st) \gets \adv^{SIGN}(\pk_1,\dots,\pk_n) \\
-        \pcif % R \not\subseteq \lbrace [n] \rbrace \lor
-        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \notin R \lor %\\
-        i_0 = i_1: \pcreturn \bot \\
-        \sig \gets Sign(\sk_{i_b},R,\msg)) \\
+        \pcif R \not\subseteq \lbrace \pk_i \rbrace_{i\in[n]} \lor
+        \lbrace \pk_{i_0},\pk_{i_1} \rbrace \not\subseteq R~\lor \\ %\\
+        \pcind i_0 = i_1: \pcreturn \bot \\
+        \sig \gets Sign(\sk_{i_b},R,\msg) \\
         b^* \gets \adv(\sig,\st) \\
@@
         \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
-        \pcreturn 1~\pcif R \subseteq [n] \setminus CU = \emptyset~\land \\
-        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg) \\
-        \pcreturn 0
+        \pcreturn (R \subseteq \lbrace \pk_i \rbrace_{i\in[n]} \setminus
+        CU~\land \\
+        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg))
       }       
@@
   }
-  \caption{Security games for ring signatures \cite{bkm06}. The SIGN oracle
-    accepts a $(i,R,\msg)$ tuple, with $pk_i \in R$, and
-    returns $\sig \gets Sign(\sk_i,R,\msg)$. The oracle $CORR$ accepts an
-    index $i$, and leaks $\sk_i$ to $\adv$. Corrupted user indexes are
-    added to $CU$.}
+  \caption{Security games for ring signatures \cite{bkm06}. The $SIGN$ oracle
+    accepts $(i,R,\msg)$ tuples, with $pk_i \in R$, adds the tuple to a list of
+    queries, and returns $\sig \gets Sign(\sk_i,R,\msg)$. $CORR$
+    accepts an index $i$, and leaks $\sk_i$ to $\adv$. Corrupted users are added
+    to $CU$.}
   \label{fig:model-rs}  
@@
 \subsubsection{\CUASRing Construction.} %
-We first define in \eref{eq:sign-prv} an alternative NP relation for signing,
-$\NIZKRel_{\Sign}^{prv}$, which we use to replace $\NIZKRel_{\Sign}$ in \CUASGen.
-It is essentially the same, except that the issuer public key is kept private,
-and we add an extra check for proving that the issuer public key is one of the
-keys in the ring. We refer to the resulting \CUASGen construction as
-$\CUASGen^{\Sign-prv}$. Since, in the following syntax, we limit to one
-credential per signature, it is easy to see that the modified relation for
-signing does not affect security.
+Building a ring signature scheme according to the model in \figref{fig:model-rs}
+is essentially a $(\fissue^{\sring},\feval^{\sring},\finsp^0)$-restriction of
+our $\CUASGen^{hide-iss}$ construction. Concretely, for any desired ring, the
+signer (who is also the issuer) simply must set $\sipk=\sring$. The construction
+is as follows:
 
-\begin{align}
-  & \NIZKRel_{\Sign}^{prv} \coloneqq \lbrace (\usk,\cred,\yeval^1,\yinsp,r,r',
-    \ipk),(\msg,\feval,\yeval^0,\ceval,\cinsp,\Eek,\widetilde{\Eek},\sring): \nonumber \\
-  & \hspace*{6.405em}\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r) \land
-    \cinsp = \EEnc(\Eek,\yinsp;r') \land \nonumber \\
-  & \hspace*{6.40em}(\yeval^0,\yeval^1) = \feval(\usk,\cred,\msg) \land
-    \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\cred,\msg) \nonumber \\
-  & \hspace*{6.40em}\exists \ipk \in \sring~\suchthat~\SBCMVerify(\ipk,\cred,\usk,
-    \sring) = 1) \rbrace \label{eq:sign-prv}
-\end{align}
+% \begin{align}
+%   & \NIZKRel_{\Sign}^{prv} \coloneqq \lbrace (\usk,\cred,\yeval^1,\yinsp,r,r',
+%     \ipk),(\msg,\feval,\yeval^0,\ceval,\cinsp,\Eek,\widetilde{\Eek},\sring): \nonumber \\
+%   & \hspace*{6.405em}\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r) \land
+%     \cinsp = \EEnc(\Eek,\yinsp;r') \land \nonumber \\
+%   & \hspace*{6.40em}(\yeval^0,\yeval^1) = \feval(\usk,\cred,\msg) \land
+%     \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\cred,\msg) \nonumber \\
+%   & \hspace*{6.40em}\exists \ipk \in \sring~\suchthat~\SBCMVerify(\ipk,\cred,\usk,
+%     \sring) = 1) \rbrace \label{eq:sign-prv}
+% \end{align}
 
-From it, we show that the $(\fissue^{\sring},\feval^{\attrs},\finsp^0)$-
-$\CUASGen^{\Sign-prv}$ restriction, is a secure ring signature scheme. We
-restrict to one credential per signature.
+% From it, we show that the $(\fissue^{\sring},\feval^{\attrs},\finsp^0)$-
+% $\CUASGen^{\Sign-prv}$ restriction, is a secure ring signature scheme. We
+% restrict to one credential per signature.
 
 \begin{description}
-\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in $\CUASGen^{\Sign-prv}$.  
-\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] As in
-  $\CUASGen^{\Sign-prv}$, using $\fissue^{\sring}$.  
-\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp).$] As in $\CUASGen^{\Sign-prv}$,
-  restricting \finsp to be $\finsp^0$.  
-\item[$\usk \gets \UKeyGen(\parm).$] Can only be run after \IKeyGen. Let 
-  $\usk \gets \isk$. Note that this does not affect security, as long as
-  $\isk \getr \AttrSpace$.
+%\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in $\CUASGen^{hide-iss}$.
+\item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
+  $\parm \gets \Setup(\secpar)$ from $\CUASGen^{hide-iss}$, as well as $n$
+  instances of $(\ipk_i,\isk_i) \gets \IKeyGen(\parm,\fissue^{\sring})$, and
+  $(\opk,\osk) \gets \OKeyGen(\parm,\finsp^0)$.
+  \jesus{This syntax restricts to fixing the rings at setup time. But the
+    RS syntax in \cite{bkm06} is also somehow static already, in that it does
+    not allow adding users on the fly. Is it ok?}
 \item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
   \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
-  The user picks a set of public keys from a publicly available list of issuers
-  (users), i.e. $\sring \gets \lbrace \ipk_i \rbrace_{i \in [t]}$, for some $t$.
-  Then, runs the $\langle \Obtain,\Issue \rangle$ protocol as in
-  $\CUASGen^{\Sign-prv}$, acting both as user and as issuer, using
-  $\fissue^{\sring}$ as issuance function, and $\attrs \gets \sring$.
+  A user, with $\usk=\isk_i$ and $\upk=\ipk_i$ for some $i \in [n]$, self-issues
+  to itself a credential for the ring \sring chosen at setup time. Then, runs
+  the $\langle \Obtain,\Issue \rangle$ protocol as in $\CUASGen^{hide-iss}$,
+  acting both as user and as issuer, using $\fissue^{\sring}$ as issuance
+  function, and $\attrs \gets \sring$.
 \item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,\msg,\feval).$] As in
-  $\CUASGen^{\Sign-prv}$, using $\feval^{\sring}$ as sign evaluation function,
-  using as credential for signing the credential obtained in the desired
-  $\langle \Obtain,\Issue \rangle$ session and, as \opk, any previously
-  registered \opk (i.e., such that $\finsp=\finsp^0$).
-\item[$1/0 \gets \Verify(\opk,\sring,\sig,\yeval,\msg,\feval).$] As in
-  $\CUASGen^{\Sign-prv}$. Note that $\feval=\feval^{\attrs}$.
-\item[$\Open$ and $\Judge$.] As in $\CUASGen^{\Sign-prv}$. Note that
-  $\finsp=\finsp^0$.
+  $\CUASGen^{hide-iss}$, using $\feval^{\sring}$ as sign evaluation function,
+  using as signing credential the self-issued credential.
+\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in
+  $\CUASGen^{hide-iss}$. Note that $\sipk=\sring$, and $\feval=\feval^{\sring}$.
+% \item[$\Open$ and $\Judge$.] As in $\CUASGen^{\Sign-prv}$. Note that
+%   $\finsp=\finsp^0$.
 \end{description}
@@
 \IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
-interactive protocols. The issuance interactive protocol is equivalent to
-the issuance protocol in \UAS. Similarly, $Show,Verify$ is equivalent to
+interactive protocols. The issuance interactive protocol corresponds to
+the issuance protocol in \UAS. Similarly, $Show,Verify$ corresponds to
 the interactive extension of \Sign and \Verify in \UAS, which we show how
@@
 oracles. We refer to \cite{fhs19} for the full details. For ease of reference,
-we summarize the security definitions in \figref{fig:model-ac}, with inocuous
-adaptations to make them more suitable for comparison with our definitions.
+we summarize the security definitions in \figref{fig:model-ac}.% , with inocuous
+% adaptations to make them more suitable for comparison with our definitions --
+% namely, we explicitly add a common setup process which is part of $IssKeyGen$
+% in \cite{fhs19}.
 
@@
       \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,ac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
+ %       \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
         b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
@@
       \procedure[linenumbering]{$\Exp^{forge}_{\adv,ac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
+%        \parm \gets \Setup(1^\secpar) \\
+        (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
         (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
@@
         \gets \langle \adv(\st),\Verify(\ipk,D) \rangle \\
-        \pcif b = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
-        \land D \subseteq \ATTR[j]): \\% \forall j, \OWNR[j] \in \CU
+        \pcreturn (b = 1 \land \nexists j~\suchthat \\
+        \pcind (\OWNR[j] \in \CU
+        \land D \subseteq \ATTR[j])) % \forall j, \OWNR[j] \in \CU
         % \implies D \not\subseteq \ATTR[j]: \\
-        \pcind \pcreturn 1 \\
-        \pcreturn 0
+        %\pcind \pcreturn 1 \\
+        %\pcreturn 0
       }       
@@
   \caption{Security games for anonymous credentials with selective disclosure
-    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in
-    \secref{ssec:model-uas}.}
+    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in \UAS. \adv~wins
+    the unforgeability game if it authenticates successfully while revealing
+    attributes not contained in adversarially controlled credentials.}
   \label{fig:model-ac}  
@@
 a secure anonymous credential scheme according to the model in \cite{fhs19}. We
-first quickly define the algorithms, and then prove security. For better
-alignment with \UAS, we add a common setup process which is part of $IssKeyGen$
-in \cite{fhs19}. The change is inocuous functionality- and security-wise.
+first quickly define the algorithms, and then prove security.
 
 \begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar,
-  \AttrSpace)$ and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
-  \CUASGen construction. Returns $\parm \gets (\parm',\opk)$.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
-  \CUASGen construction, setting $\fissue^1$ as issuance function.
-\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
-  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
+% \item[$\parm \gets \Setup(1^\secpar)$.] Runs $\parm' \gets \Setup(1^\secpar,
+%   \AttrSpace)$ and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
+%   \CUASGen construction. Returns $\parm \gets (\parm',\opk)$.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] $\parm' \gets
+  \Setup(1^\secpar)$ and $(\opk,\osk) \gets \OKeyGen(\parm',
+  \finsp^0)$ from \CUASGen, and sets $\parm \gets (\parm',\opk)$. Then,
+  runs \IKeyGen, also from \CUASGen, setting $\fissue^1$ as issuance function.
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from \CUASGen.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
@@
   \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
+  \markulf{Hiding of $pk_U$?}
 \end{theorem}
@@
 scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
-our simple scheme built from \CUASGen does not ensure privacy of the delegation
-chain -- which could be achieved by making \feval output projective proofs like
-in \cite{bcc+09}, but since our goal is to showcase the feasibility of building
-DAC from \UAS, we leave that out for brevity. Our simple scheme does, however,
-ensure that a (not top-level) issuer can only delegate attributes contained in a
-credential it owns. Also, for simplicity, we restrict to the case of using one
-credential per signature/interactive credential presentation, and assume that
-all parties use the same opener and \finsp function.
+our simple scheme built from $\CUASGen^{usr-iss}$ does not ensure privacy of the
+delegation chain -- which could be achieved by making \feval output projective
+proofs like in \cite{bcc+09}, but since our goal is to showcase the feasibility
+of building DAC from \UAS, we leave that out for brevity. Our simple scheme
+does, however, ensure that a (not top-level) issuer can only delegate attributes
+contained in a credential it owns. Also, for simplicity, we restrict to the case
+of using one credential per signature/interactive credential presentation, and
+assume that all parties use the same opener and \finsp function.
 %
-The functionality is thus defined as in \secref{ssec:related-models-ac}, i.e.,
-we have $Setup$, $IssKeyGen$ and $UserKeyGen$ algorithms, and $\langle Obtain,
-Issue \rangle$ and $\langle Show,Verify \rangle$ interactive protocols.
+The functionality is thus defined almost as in \secref{ssec:related-models-ac},
+i.e., we have $Setup$, $IssKeyGen$ algorithms, and $\langle Obtain,Issue\rangle$
+and $\langle Show,Verify \rangle$ interactive protocols; but we do not have
+$UserKeyGen$, as this collapses with $IssKeyGen$.
 %
@@
 that have not been issued to a corrupt user. In addition, we require that for
-any successful authentication using a level-$n$ credential, we
-can extract a chain of credentials of length $n$ such that each level-$i$
+any successful authentication using a level-$l$ credential, we
+can extract a chain of credentials of length $l$ such that each level-$i$
 credential can be used successfully to authenticate a level-$(i+1)$ credential
-down to the level-$n$ credential, and the attributes revealed in the
-level-$n$ authentication are contained in all the credentials up the chain.
+down to the level-$l$ credential, and the attributes revealed in the
+level-$l$ authentication are contained in all the credentials up the chain.
 
@@
         \parm \gets \Setup(1^\secpar) \\
-        (D=(n,D'),\ipk_n,\st) \gets
+        (D=(l,D'),\ipk_l,\st) \gets
         \adv^{\mathcal{O}_{forge}}(\parm) \\
         \langle\cdot,(b,\utrans)\rangle \gets
-        \langle \adv(\st),\Verify(\ipk_n,D)\rangle \\
+        \langle \adv(\st),\Verify(\ipk_l,D)\rangle \\
         \pcif b = 0: \pcreturn 0 \\
@@
         \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
-        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,n]})
+        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,l]})
         \gets ExtractChain(\utrans) \\ 
-        \pcif \exists i \in [1,n]~\suchthat~
+        \pcif \exists i \in [1,l]~\suchthat~
         \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
@@
   \caption{Security games for delegatable anonymous credentials with selective
-    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HU,
-    CU,HI,CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon}
-    \gets \lbrace HU,CU,HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$.
-    $\mathcal{O}_{forge} \gets \lbrace HU,CU,HI,CI,Obtain,ObtIss,Issue,Show
-    \rbrace$. $IssLor$ is equivalent to \OBTCHALb in \UAS, whereas $SigLor$ is
-    equivalent to \CHALb. Also, \OWNR and \ATTR tables are essentially as in
-    \secref{ssec:model-uas}. $\ISR[\ipk]$, in this case, returns the identifier
-    of the issuer with public key \ipk. With $D =
-    (n,D')$ we mean that the first attribute in the revealed set $D$ is $n$,
-    which denotes the level of the credential used for authentication.}
+    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HI,
+    CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon} \gets
+    \lbrace HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$. $\mathcal{O}_{forge}
+    \gets \lbrace HI,CI,Obtain,ObtIss,Issue,Show\rbrace$. $IssLor$ corresponds
+    to \OBTCHALb in \UAS, whereas $SigLor$ corresponds to \CHALb. Also, \OWNR
+    and \ATTR tables are essentially as in \secref{ssec:model-uas}.
+    $\ISR[\ipk]$, in this case, returns the identifier of the issuer with public
+    key \ipk. With $D = (l,D')$ we mean that the first attribute in the revealed
+    set $D$ is $l$, which denotes the level of the credential used for
+    authentication.}
   \label{fig:model-dac}  
@@
 \subsubsection{\CUASDAC Construction.} %
-We next give a construction of a delegatable AC (DAC) scheme, based on a
-$(\fissue^{n,\dattrs},\feval^{n,\dattrs},\finsp^0)$-\CUASGen restriction.
-In a DAC scheme, all users are (or may be) also issuers. We only distinguish
-between top-level issuers, who have level $n=0$, and lower-level issuers, who
-have level $n>0$. In our \CUASDAC scheme, we assume that the first attribute
-(after the user's secret key) encodes the level of the credential. That is,
-$\attrs_1=n$, for a credential of level $n$. In addition, all users (i.e., with
-$n>0$) who want to delegate have to publicly list:
+We next give a construction of a delegatable AC (DAC) scheme, in the shape of
+a $(\fissue^{l,\dattrs},\feval^{l,\dattrs},\finsp^0)$-$\CUASGen^{usr-iss}$
+restriction. In a DAC scheme, all users are (or may be) also issuers. We only
+distinguish between top-level issuers, who have level $l=0$, and lower-level
+issuers, who have level $l>0$. In our \CUASDAC scheme, we assume that the first
+attribute (after the user's secret key) encodes the level of the credential.
+That is, $\attrs_1=l$, for a credential of level $l$. In addition, all users
+(i.e., with $l>0$) who want to delegate have to publicly list:
 
 \begin{enumerate}
-\item The level $n$ of the credential they delegate.
+\item The level $l$ of the credential they delegate.
 \item Their public key \ipk.
-\item An \UAS signature proving knowledge of a credential of level $n$, and over
-  the attributes that this level-$n$ issuer is delegating.
+\item An \UAS signature proving knowledge of a credential of level $l$, and over
+  the attributes that this level-$l$ issuer is delegating.
 \item The \ipk of the parent issuer.
-\item The $\fissue^{n,\dattrs}$ function they will require for delegating.
-\item An $\feval^{n,\dattrs}$ function used to produce the signature at item 2.
+\item The $\fissue^{l,\dattrs}$ function they will require for delegating.
+\item An $\feval^{l,\dattrs}$ function used to produce the signature at item 3.
 \end{enumerate}
@@
 (e.g., using the previously mentioned public list). The mentioned
-$\fissue^{n,\dattrs}$ functions must follow the pattern in \figref{fig:func-restrictions}.
+$\fissue^{l,\dattrs}$ functions must follow the pattern in \figref{fig:func-restrictions}.
 Namely, the issuance function checks that the first requested attribute equals
-$n+1$, and that all requested attributes are a subset of the attribute set
-\dattrs being delegated by the level-$n$ issuer. In addition, signature
-evaluation functions $\feval^{n,\dattrs}$, also shown in \figref{fig:func-restrictions},
+$l+1$, and that all requested attributes are a subset of the attribute set
+\dattrs being delegated by the level-$l$ issuer. In addition, signature
+evaluation functions $\feval^{l,\dattrs}$, also shown in \figref{fig:func-restrictions},
 must reveal the level of the credential used to produce the \UAS signature at
-item 2, as well as the set of attributes \dattrs that the level-$n$ issuer
+item 2, as well as the set of attributes \dattrs that the level-$l$ issuer
 delegates. Verifiers can then trivially check if the set of revealed attributes
@@
 \footnote{Additional checks may be added in both functions, but this is
-  the bare minimum.}. \figref{fig:XXX} depicts a sample of the delegation chain
-that this structure creates.
+  the bare minimum.}.
 %
@@
 \begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar,
-  \AttrSpace)$ and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
-  \CUASGen construction. Returns $\parm \gets (\parm',\opk)$. Note that
-  $\finsp^0$ can be replaced by any desired opening function.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $n=0$, simply run \IKeyGen as
-  in \CUASAC. If $n>0$, note that this is a user who wants to delegate a
-  previously obtained credential \cred. Thus, it has already run $UserKeyGen$
-  below, which internally also runs \IKeyGen as in \CUASGen and sets $\usk \gets
-  \isk$. In addition, the level-$n$ issuer picks a random message $r$ and
-  computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
-  \feval^{n,\dattrs})$, for the \dattrs set it wants to reveal -- which must
+\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
+  and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
+  $\CUASGen^{usr-iss}$ construction. Returns $\parm \gets (\parm',\opk)$. Note
+  that $\finsp^0$ can be replaced by any desired opening function.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $l=0$, simply run \IKeyGen as
+  in $\CUASGen^{usr-iss}$. If $l>0$, this level-$l$ issuer picks a random
+  message $r$ and computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
+  \feval^{l,\dattrs})$, for the \dattrs set it wants to reveal -- which must
   include the attributes to delegate, and the credential level. It then
-  publishes $(n,\ipk,\Sig,\ipk^{n-1},\fissue^{n,\dattrs},\feval^{n,\dattrs})$,
-  where $\ipk^{n-1}$ is the public key of the parent issuer,
-  $\fissue^{n,\dattrs}$ is an issuance function as described in
-  \figref{fig:func-restrictions}, and $\feval^{n,\dattrs}$ is also as in
+  publishes $(l,\ipk,\Sig,\ipk^{l-1},\fissue^{l,\dattrs},\feval^{l,\dattrs})$,
+  where $\ipk^{l-1}$ is the public key of the parent issuer,
+  $\fissue^{l,\dattrs}$ is an issuance function as described in
+  \figref{fig:func-restrictions}, and $\feval^{l,\dattrs}$ is also as in
   \figref{fig:func-restrictions}, revealing the attributes that the issuer is
   willing to delegate.
-\item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
-  also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
-  $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
-  credentials. Note that this does not affect security, as long as
-  $\isk \getr \AttrSpace$.
+% \item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
+%   also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
+%   $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
+%   credentials. Note that this does not affect security, as long as
+%   $\isk \getr \AttrSpace$.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
   \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  If $n>0$, the user first finds the corresponding $(n,\ipk,\Sig,\ipk^{n-1},
-  \fissue^{n,\dattrs},\feval^{n,\dattrs})$ tuple, and checks \Sig running
-  \Verify as in \CUASGen (with the retrieved $\feval^{n,\dattrs}$). Then,
-  user and level-$n$ issuer run $\langle\Obtain,\Issue\rangle$ as in \CUASGen,
-  using $\fissue^{n,\dattrs}$ as issuance function. If $n=0$, then both run
-  $\langle\Obtain,\Issue\rangle$ as in \CUASGen, using the \fissue function
-  required by the issuer.
+  If $l>0$, the user first finds the corresponding $(l,\ipk,\Sig,\ipk^{n-1},
+  \fissue^{l,\dattrs},\feval^{l,\dattrs})$ tuple, and checks \Sig running
+  \Verify as in $\CUASGen^{usr-iss}$ (with the retrieved $\feval^{l,\dattrs}$).
+  Then, user and level-$l$ issuer run $\langle\Obtain,\Issue\rangle$ as in
+  $\CUASGen^{usr-iss}$, using $\fissue^{l,\dattrs}$ as issuance function. If
+  $l=0$, then both run $\langle\Obtain,\Issue\rangle$ as in
+  $\CUASGen^{usr-iss}$, using the \fissue function required by the issuer.
 \item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle
   \gets \langle Show(\opk,\attrs,\dattrs,\cred),
-  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of \CUASGen.  
+  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of
+  $\CUASGen^{usr-iss}$.  
 \end{description}

### 2022-07-26 prism-backend/research/gsac/formal-uas.tex
Migrating from fissue being a predicate to it being a function.

@@
 \item[$\langle
-  \Obtain(\usk,\ipk,\sCred,\attrs),
-  \Issue(\isk,\sipk,\attrs))  
-  \rangle \rightarrow \langle \Cred/\bot,\utrans/\bot
+  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
+  \Issue(\isk,\cidi,\sipk,\attrs))  
+  \rangle \rightarrow \langle \Cred/\bot,R/\bot
   \rangle$.] %
   This interactive protocol lets a user with key \usk running the \Obtain
-  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$ from an
-  issuer in the system, where \cid is a unique identifier for the credential,
-  \ipk is the issuer's public key and \cred is the actual credential, on
-  attribute set \attrs. The user may leverage a set of previously obtained
-  credentials $\sCred=\lbrace (\cid_i,\cattrs_i,\cred_i,\ipk_i)
-  \rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for readability. The
-  user outputs the produced credential \Cred, while the issuer outputs the
-  corresponding protocol transcript \utrans.
+  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$
+  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
+  the credential, where issuer and user randomly pick \cidi and \cidu,
+  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
+  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
+  on attribute set \attrs. The user may leverage a set of previously obtained
+  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
+  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
+  readability. The user outputs the produced credential \Cred, while the issuer
+  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
+  the \fissue defined by the issuer, and $\utrans$ being the transcript of
+  the communication.
 \item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
@@
 \begin{description}
-\item[$\fissue: ((\upk,\usk),\attrs,\lbrace (\cid_i,\cattrs_i)
-  \rbrace_{i \in [n]}) \rightarrow 0/1$.] Chosen
+\item[$\fissue: (\upk,\attrs,\lbrace (\cid_i,\cattrs_i)
+  \rbrace_{i \in [n]}) \rightarrow \yissue$.] Chosen
   by each issuer within a family of functions \famfissue, the issuance function
   defines the customized conditions required by the issuer to grant a credential
-  over attributes \attrs, when requested by a user with key pair $(\upk,\usk)$,
+  over attributes \attrs, when requested by a user with public key \upk,
   leveraging a set of $n$ previously obtained credentials with identifiers and
-  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where $n$
-  may be $0$ if no previously obtained credential is used). \fissue returns $1$
-  to accept a request, $0$ to reject it.
-\item[$\feval: ((\upk,\usk),\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
+  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
+  $n$ may be $0$ if no previously obtained credential is used). \fissue returns
+  a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
+  convention that $\yissue = 0$ means that the issuance request is denied.
+\item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
   \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
   family of functions \famfeval, can be set on a per-signature basis. They
-  receive the user key pair $(\upk,\usk)$, a set of credentials with identifiers
+  receive the user public key \upk, a set of credentials with identifiers
   and attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
@@
   we write $\Yeval = (\yeval^0,\yeval^1)$.
-\item[$\finsp: (\Yeval,(\upk,\usk),\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},
+\item[$\finsp: (\Yeval,\upk,\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},
   \msg) \rightarrow \yinsp$.]
@@
 
-\begin{definition}{(\UAS-acceptable functions)}
-  \label{def:uas-acc-func}
-  We say that a \fissue (similarly, \feval or \finsp) function chosen from some
-  family \famfissue (similarly, \famfeval or \famfinsp) is \UAS-acceptable if it
-  is one-way with respect to $(\upk,\usk)$. That is, given the output of \fissue
-  (similarly, \feval or \finsp), it is at least computationally unfeasible to
-  recover the $(\upk,\usk)$ value used to produce it.
-\end{definition}
+% \begin{definition}{(\UAS-acceptable functions)}
+%   \label{def:uas-acc-func}
+%   We say that a \fissue (similarly, \feval or \finsp) function chosen from some
+%   family \famfissue (similarly, \famfeval or \famfinsp) is \UAS-acceptable if it
+%   is one-way with respect to $(\upk,\usk)$. That is, given the output of \fissue
+%   (similarly, \feval or \finsp), it is at least computationally unfeasible to
+%   recover the $(\upk,\usk)$ value used to produce it.
+% \end{definition}
 
@@
   is that $\OWNR[\scid]$ returns $\bot$ if not all passed {\cid}s belong to the
-  same \uid.
+  same \uid. Since $\bot$ is not a valid \uid, all conditions checking
+  membership of the output of \OWNR to a list of users equal false if \OWNR
+  returns $\bot$.
 \item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
@@
 
-        \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
-          \rbrace_{i \in [n]})$}{%
-          \pcif \uid \notin \HU: \pcreturn \bot \\
-          \pcif \iid \notin \HI: \pcreturn \bot \\
+        \procedure{$\OBTISS(\cid=(\cidi,\cidu),\uid,\iid,\attrs,$\\
+          \hspace*{4.25em}$\lbrace (\cid_i,\iid_i) \rbrace_{i \in [n]})$}{%
+          \pcif \uid \notin \HU \lor \iid \notin \HI: \pcreturn \bot \\
           \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
@@
           \pcreturn \bot \\
-          \langle \Cred, \utrans \rangle \gets
-          \langle \Obtain(\UK[\uid],\CRED[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs), \\
-          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs)
+          \langle \Cred, R \rangle \gets
+          \langle \Obtain(\UK[\uid],\cidu,\CRED[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs), \\
+          \hspace*{50pt} \Issue(\PRVIK[\iid],\cidi,\ISR[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs)
           \rangle \\
-          \trans[\cid] \gets \utrans \\
+          \trans[\cid] \gets R \\
           \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, n,
@@
 
-        \procedure{$\ISSUE(\cid,\uid,\iid,\attrs,\siid=\lbrace \iid_i
-          \rbrace_{i\in[n]})$}{%
-          \pcif \uid \notin \CU: \pcreturn \bot \\          
-          \pcif \iid \notin \HI: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
-          \pcreturn \bot \\
-          \langle \cdot, \utrans \rangle \gets
+        \procedure{$\ISSUE(\cidi,\uid,\iid,\attrs,\siid=
+          \lbrace \iid_i\rbrace_{i\in[n]})$}{%
+          \pcif \uid \notin \CU \lor \iid \notin \HI: \pcreturn \bot \\
+          \pcif \CRED[(\cidi,\cdot)] \neq \bot \lor \CCRED[(\cidi,\cdot)]
+          \neq \bot: \\
+          \pcind \pcreturn \bot \\
+          \langle \cdot, R \rangle \gets
           \langle \adv, 
-          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
-          \trans[\cid] \gets \utrans \\
-          \CRED[\cid] \gets (\uid,\cdot,\iid,\attrs,n,\lbrace(\cdot,\iid_i)
+          \Issue(\PRVIK[\iid],\cidi,\siid,\attrs) \rangle \\
+          \trans[(\cidi,\cdot)] \gets R \\
+          \CRED[(\cidi,\cdot)] \gets (\uid,\cdot,\iid,\attrs,n,\lbrace(\cdot,
+          \iid_i)
           \rbrace_{i\in[n]}) \\
@@
           \feval)$}{%
-          \pcif \uid \notin \HU: \pcreturn \bot \\
+          \pcif \uid \notin \HU \lor \feval \notin \famfeval: \pcreturn \bot \\
           \pcif \exists i \neq j \in [n]~\suchthat~\cid_i \in \CRED \land
@@
           \pcind \pcreturn \bot \\
-          \pcif \feval \notin \famfeval: \pcreturn \bot \\
           \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
           \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\scid,\msg) \\
-          \pcif \Yeval \notin \rngfeval: \pcreturn \bot \\
           \SIG[\uid] \gets \SIG[\uid] \cup
@@
 
-        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
+        \procedure{$\OBTAIN(\cidu,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
           \rbrace_{i\in[n]})$}{%
-          \pcif \uid \notin \HU: \pcreturn \bot \\
-          \pcif \iid \notin \CI: \pcreturn \bot \\
+          \pcif \uid \notin \HU \lor \iid \notin \CI: \pcreturn \bot \\
           \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
+          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor \CCRED[(\cidu,\cdot)] \neq
+          \bot: \\
+          \pcind \pcreturn \bot \\
           \langle \Cred, \cdot \rangle \gets
-          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\lbrace \cid_i\rbrace_{[n]},
+          \langle \Obtain(\UK[\uid],\cidu,\PUBIK[\iid],\lbrace \cid_i\rbrace_{[n]},
           \attrs),\adv \rangle \\
-          \CRED[\cid] \gets (\uid,\cred,\iid,\attrs,n,\lbrace(\cid_i,\iid_i)
-          \rbrace_{i\in[n]}) \\
+          \CRED[(\cdot,\cidu)] \gets (\uid,\cred,\iid,\attrs,n,\lbrace(\cid_i,
+          \iid_i) \rbrace_{i\in[n]}) \\
           \pcreturn \top \\
@@
 
-        \procedure{$\OBTCHALb(\cid,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
+        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
           \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
@@
           \pcif \iid \notin \CI: \pcreturn \bot \\
-          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
+          \pcif \CRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
           \pcif \exists i\in[n]~\suchthat~
@@
           \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
-          \pcif \fissue(\UK[\cuid_0],\cscid_0,\attrs) \neq
-          \fissue(\UK[\cuid_1],\cscid_1,\attrs) \\
+          \pcif 0(\fissue(\PUBUK[\cuid_0],\cscid_0,\attrs)) \neq \\
+          \pcind 0(\fissue(\PUBUK[\cuid_1],\cscid_1,\attrs)): \pcreturn \bot \\
           \langle \Cred, \cdot \rangle \gets
-          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\cscid_b,\attrs),\adv \rangle \\
-          \CCRED[\ccid_b] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
+          \langle \Obtain(\PRVUK[\cuid_b],\cidu,\PUBIK[\iid],\cscid_b,\attrs),
+          \adv \rangle \\
+          \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
           \pcreturn \top \\
@@
           \pcif \feval \notin \famfeval: \pcreturn \bot \\
-          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\cscid_0,
+          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\cuid_0],\cscid_0,
           \msg) \\
           \TYeval = (\tyeval^0,\tyeval^1) \gets
-          \feval(\UK[\cuid_1],\cscid_1,\msg) \\
+          \feval(\PUBUK[\cuid_1],\cscid_1,\msg) \\
           \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\   
-          \pcif \Yeval \notin \rngfeval \lor \TYeval \notin \rngfeval:
-          \pcreturn \bot \\          
-          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
-          \hspace*{71pt}\cscid_b,\msg,\feval) \\
-          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
-          \hspace*{80pt}\cscid_{1-b},\msg,\feval) \\          
+          \cSig_b \gets \Sign(\PRVUK[\cuid_b],\PUBOK[\oid],\cscid_b,\msg,
+          \feval) \\
+          \cSig_{1-b} \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid],\cscid_{1-b},\msg,\feval) \\          
           \CSIG[\cSig_b] \gets 
@@
       \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
-      (\Sig = (\sig,\yeval)) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,
+      (\Sig = (\sig,\yeval)) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,
       \feval) \\
@@
       \pcind \textrm{Parse}~\CRED[\cid]~\textrm{as}~
-      (\cdot,\cdot,\cdot,\attrs,n,\lbrace(\cid_i,\cdot)\rbrace_{i\in[n]}));
+      (\cdot,\cdot,\cdot,\attrs,n,\lbrace(\cid_i,\cdot)\rbrace_{i\in[n]})) \\
 %      \pcind \textrm{Let}~\scid^{\cid}~\textrm{be the {\cid}s used to obtain}
@@
 %      \fissue^{\cid}),\cdot)\\
+      \pcind \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
       \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot)\\
-      \pcind \pcif \fissue(\UK[\uid],\attrs,
-      (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) = 0: \pcreturn 1 \\
-      (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],(\scid,\ATTR[\scid]),\msg) \\
+      \pcind \pcif \fissue(\PUBUK[\uid],\attrs,
+      (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) \neq \yissue:
+      \pcreturn 1 \\
+      (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],(\scid,\ATTR[\scid]),\msg) \\
       \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
@@
       \pcind \yinsp \neq \finsp^\oid((\yeval,\yeval^1),
-      \UK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
+      \PUBUK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
       \pcind \pcreturn 1 \\
@@
         \pcreturn 0 \\
+        \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans) \\
         % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
         ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
-        \gets \ExtractIssue(\trap,\trans[\cid]) \\
+        \gets \ExtractIssue(\trap,\utrans) \\
         % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
@@
         % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
-        \pcif \fissue((\upk,\usk),\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
-        \rbrace_{i\in[n]}) = 0:
+        \pcif \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
+        \rbrace_{i\in[n]}) = \yissue:
         \pcreturn 1 \\
@@
         \yeval^1,\yinsp') \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
-        (\yeval^0,\yeval^1) \gets \feval((\upk,\usk),\lbrace(\cid_i,\attrs_i)
+        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
         \rbrace_{i\in[n]}, \msg) \\
@@
         \pcreturn 1 \\
-        \pcif \finsp((\yeval^0,\yeval^1),(\upk,\usk),\lbrace(\cid_i,\attrs_i)
+        \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
         \rbrace_{i\in[n]},\msg)
@@
       % \lor \yinsp \neq \yinsp': \pcreturn 1 \\
-      \Yeval=(\yeval^0,\yeval^1) \gets \feval((\upk,\usk),\lbrace (\cid_i,
+      \Yeval=(\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace (\cid_i,
       \attrs_i)\rbrace_i{i\in[n]}, \msg) \\
@@
       \pcreturn 1 \\
-      \pcif \finsp((\yeval^0,\yeval^1),(\upk,\usk),\lbrace(\cid_i,\attrs_i)
+      \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
       \rbrace_{i\in[n]},\msg)
@@
   \caption{CS specification of the NP relations used in \CUASGen.
-  \todo{Is $\C = \CCommit(\usk;r)$ needed now that \upk is added?}}
+  \todo{Is $\C = \CCommit(\usk;r)$ at Issue needed now that \upk is added?}}
   \label{fig:nizkrels}
@@
 
-\paragraph{$\usk \gets \UKeyGen(\parm)$.} %
+\paragraph{$(\upk,\usk) \gets \UKeyGen(\parm)$.} %
 Each user, prior to requesting credentials, generates his secret key by picking
@@
 \paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle\Obtain(\usk,\ipk,\lbrace (\cid_i,\cattrs_i,\cred_i) \rbrace_{i\in[n]},
-  \attrs),\Issue(\isk,\lbrace \ipk_i \rbrace_{i\in[n]},\attrs)\rangle$.} %
+  \langle\Obtain(\usk,\cidu,\ipk,\lbrace (\cid_i,\cattrs_i,\cred_i) \rbrace_{i\in[n]},
+  \attrs),\Issue(\isk,\cidi,\lbrace \ipk_i \rbrace_{i\in[n]},\attrs)\rangle$.} %
 The protocol is run between an issuer with key pair $(\ipk,\isk)$, and a user
@@
 attests attributes $\cattrs_i$. The user requests a signature on a commitment to
-the user key, as well as on the attributes in \attrs. In addition, the user
-proves that the issuance function \fissue established by the issuer is satisfied
-by the $\cred_i$ credentials and its user secret key. This is achieved through
-an execution of an \SBCM interactive signing protocol with $\NIZKRel_{\Issue}$
-as NP relation -- which contains the verification that \fissue returns $1$,
-among other checks as described earlier. Concretely, the user runs
-$\SBCMCom^{\NIZKRel_{\Issue}}(\ipk,\usk,(\cid,\attrs),\lbrace (\cid_i,\cattrs_i,
-\cred_i)\rbrace_{i\in[n]},\lbrace \ipk_i \rbrace_{i\in[n]})$, and the issuer
-runs $\SBCMSign^{\NIZKRel_{\Issue}}(\isk,(\cid,\attrs),\lbrace\ipk_i
-\rbrace_{i\in[n]})$, for some commonly agreed and fresh \cid. The credential
-\cred produced by the user is the result of the interactive signing protocol,
-and the \utrans entry for the issuer is its transcript, which is a $(\Ccom,
-\lbrace \cid,\attrs\rbrace,\lbrace \ipk_i \rbrace_{i\in[n]},\cred,\pi)$ tuple.
+the user key, as well as on $\cid=(\cidi,\cidu)$ and the attributes in \attrs.
+In addition, the user proves correct computation of the \fissue function set by
+the issuer based on the $\cred_i$ credentials and its user key pair.
+This is essentially achieved through an execution of an \SBCM interactive
+signing protocol with $\NIZKRel_{\Issue}$ as NP relation. Since \fissue is
+evaluated by the user, but depends on the \cidi value chosen by the issuer, the
+issuer first needs to send \cidi to the user.
+Then both issuer and user interact to produce the \SBCM signature, where the
+user runs $\SBCMCom^{\NIZKRel_{\Issue}}(\ipk,\usk,(\cid,\attrs),\lbrace (\cid_i,
+\cattrs_i,\cred_i)\rbrace_{i\in[n]},\lbrace \ipk_i \rbrace_{i\in[n]})$, and the
+issuer runs $\SBCMSign^{\NIZKRel_{\Issue}}(\isk,(\cid,\attrs),\lbrace\ipk_i
+\rbrace_{i\in[n]})$. The credential \cred produced by the user is the result of
+the interactive signing protocol, whereas the issuer produces $(\yissue,
+\utrans)$, where \yissue is the output of \fissue, and \utrans is the
+communication transcript, which is a $(\Ccom,(\cid,\attrs),\lbrace
+\ipk_i \rbrace_{i\in[n]},\cred,\pi)$ tuple.
 

### 2022-07-26 prism-backend/research/gsac/relationships.tex
Migrating from fissue being a predicate to it being a function.

@@
         & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
-        & \fissue^{single,L}((\upk,\cdot),\cdot,\cdot) \coloneqq
+        & \fissue^{single,L}(\upk,\cdot,\cdot) \coloneqq
           \pcreturn \upk \notin L
           \nonumber \\
-        & \fissue^{\sring}((\upk,\cdot),\attrs,\cdot) \coloneqq
-          \pcreturn (\attrs \subseteq \sring \land \upk \in \sring) \nonumber \\
+        & \fissue^{\sring}(\upk,\attrs,\cdot) \coloneqq
+          \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber \\
         & \fissue^{l,\dattrs}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
           \pcreturn (\attrs_1 = l+1 \land \attrs \subseteq
-          \lbrace \cattrs_i \rbrace_{i\in\dattrs}) \nonumber
+          \cup_{i\in\dattrs} \cattrs_i) \nonumber
       \end{align}
@@
           \nonumber \\
-        & \feval^{\sring}((\upk,\cdot),(\cid,\attrs),\cdot)
-          \coloneqq \pcif \upk \in \attrs:
-          \pcreturn (\attrs,\ast);
+        & \feval^{\sring,\dattrs}(\upk,(\cid,\attrs),\cdot)
+          \coloneqq \pcif \upk \in \lbrace \attrs_i \rbrace_{i\in\dattrs}
+          \subseteq \sring:
+          \pcreturn (\lbrace \attrs_i \rbrace_{i\in\dattrs},\ast);
           \pcelse \pcreturn \bot \nonumber \\
@@
         & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
-        & \finsp^{\upk}(\cdot,(\upk,\cdot),\cdot,\cdot) \coloneqq
+        & \finsp^{\upk}(\cdot,\upk,\cdot,\cdot) \coloneqq
           \pcreturn \upk % \CCommit(\usk;0)
@@
 Building a ring signature scheme according to the model in \figref{fig:model-rs}
-is essentially a $(\fissue^{\sring},\feval^{\sring},\finsp^0)$-restriction of
-our $\CUASGen^{hide-iss}$ construction. Concretely, for any desired ring, the
-signer (who is also the issuer) simply must set $\sipk=\sring$. The construction
-is as follows:
+is essentially a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
+of our $\CUASGen^{hide-iss}$ construction. The construction is as follows:
 
@@
   $\parm \gets \Setup(\secpar)$ from $\CUASGen^{hide-iss}$, as well as $n$
-  instances of $(\ipk_i,\isk_i) \gets \IKeyGen(\parm,\fissue^{\sring})$, and
-  $(\opk,\osk) \gets \OKeyGen(\parm,\finsp^0)$.
-  \jesus{This syntax restricts to fixing the rings at setup time. But the
-    RS syntax in \cite{bkm06} is also somehow static already, in that it does
-    not allow adding users on the fly. Is it ok?}
+  instances of $(\ipk_i,\isk_i) \gets \IKeyGen(\parm,\fissue^{\sring})$, where
+  $\sring = \lbrace \ipk_i \rbrace_{i\in[n]}$, and $(\opk,\osk) \gets
+  \OKeyGen(\parm,\finsp^0)$. 
 \item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
-  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle.$]
-  A user, with $\usk=\isk_i$ and $\upk=\ipk_i$ for some $i \in [n]$, self-issues
-  to itself a credential for the ring \sring chosen at setup time. Then, runs
-  the $\langle \Obtain,\Issue \rangle$ protocol as in $\CUASGen^{hide-iss}$,
-  acting both as user and as issuer, using $\fissue^{\sring}$ as issuance
-  function, and $\attrs \gets \sring$.
+  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk=\attrs,\attrs)\rangle.$]
+  A user, with $\usk=\isk_i$ and $\upk=\ipk_i$ for some $i \in [n]$, acts both
+  as user and issuer to self-issue a credential for an attribute set \attrs such
+  that $\attrs \subseteq \sring$, where \sring is the set of public keys used to
+  define $\fissue^{\sring}$.
 \item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,\msg,\feval).$] As in
-  $\CUASGen^{hide-iss}$, using $\feval^{\sring}$ as sign evaluation function,
-  using as signing credential the self-issued credential.
+  $\CUASGen^{hide-iss}$, using $\feval^{\sring,\dattrs}$ as evaluation
+  function, using as signing credential the self-issued credential. Note that
+  $\dattrs \subseteq \attrs = \sring$ defines the subring to use for the
+  produced signature.
 \item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in
-  $\CUASGen^{hide-iss}$. Note that $\sipk=\sring$, and $\feval=\feval^{\sring}$.
-% \item[$\Open$ and $\Judge$.] As in $\CUASGen^{\Sign-prv}$. Note that
-%   $\finsp=\finsp^0$.
+  $\CUASGen^{hide-iss}$, making $\sipk=\yeval=\lbrace \ipk_i
+  \rbrace_{i\in\dattrs}$.
 \end{description}
+
+%Note that by using, e.g., $\finsp^{\upk}$, we essentially get a ring signature
+%scheme with linkability via an opener.
 

### 2022-07-28 prism-backend/research/gsac/formal-uas.tex
Migrated syntax, model and construction where issuers=users. RS construction fixed.

@@
 
+\todo{Clarify that, for us, issuers and users are essentially the same thing.}
+
 \subsection{Syntax}
@@
   input parameters.
-\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given \parm, and the
-  function \fissue for checking that credential requestors meet the conditions
-  to be issued a credential, an issuer runs \IKeyGen to generate its issuing key
-  pair. 
+\item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
+  \KeyGen to generate its user key pair. 
 \item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
@@
   signatures.
-\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
-  key pair.
+\item[$\ISet((\upk,\usk),\fissue) \rightarrow \ipk$.] Given a user key
+  pair, and an issuance function \fissue for checking that credential requestors
+  meet some conditions to be issued a credential, an existing user runs \ISet to
+  extend the user public key, enabling this user to issue credentials meeting
+  \fissue.
+%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
+%  key pair.
 \item[$\langle
@@
 \paragraph{Global Variables.} %
+\todo{Clarify that {\iid}s are just {\uid}s.}
 Users are referred to with user identifiers, \uid; for credentials, we use \cid;
@@
 \begin{description}
-\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
-  the associated issuance function.
+% \item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
+%   the associated issuance function.
+\item[\UGEN.] Adds a new user to the game, generating its keypair.  
 \item[\OGEN.] Adds a new opener to the game, generating its key pair and
   setting the associated evaluation and inspection functions.
-\item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
-  key to the adversary.
+% \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
+%   key to the adversary.
+\item[\ISET.] ``Upgrades'' an user to become an issuer, specifying its
+  associated issuance function.
+\item[\UCORR.] Corrupts an existing (and honest) user, by giving its secret
+  key to the adversary. If the user was also an issuer, it becomes a corrupt
+  issuer too.
 \item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
   key to the adversary.
-\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
-  the user's key pair.
-\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
-  user already exists and is honest, corrupts it, leaking its key and
-  credentials.
+% \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
+%   the user's key pair.
+% \item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
+%   user already exists and is honest, corrupts it, leaking its key and
+%   credentials.
 \item[\RREG.] Reads the given transcript table entry.
@@
 
-        \procedure{$\IGEN(\iid,\fissue)$}{%
-          \pcif \iid \in \HI \lor \iid \in \CI: \pcreturn \bot \\
+        % \procedure{$\IGEN(\iid,\fissue)$}{%
+        %   \pcif \iid \in \HI \lor \iid \in \CI: \pcreturn \bot \\
+        %   \pcif \fissue \notin \famfissue: \pcreturn \bot \\
+        %   (\ipk,\isk) \gets \IKeyGen(\parm) \\
+        %   \IK[\iid] \gets ((\ipk,\fissue),\isk) \\
+        %   \HI \gets \HI \cup \lbrace \iid \rbrace \\
+        %   \pcreturn \ipk \\
+        % }
+
+        % \procedure{$\ICORR(\iid)$}{%
+        %   \pcif \iid \in \CI \lor \iid \notin \HI: \pcreturn \bot \\
+        %   \HI \gets \HI \setminus \lbrace \iid \rbrace \\
+        %   \CI \gets \CI \cup \lbrace \iid \rbrace \\
+        %   \pcreturn \isk \\
+        % }
+
+        % \procedure{$\HUGEN(\uid)$}{%
+        %   \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
+        %   (\upk,\usk) \gets \UKeyGen(\parm) \\
+        %   \UK[\uid] \gets (\upk,\usk);
+        %   \HU \gets \HU \cup \lbrace  \uid \rbrace \\
+        %   \pcreturn \top \\
+        % }
+
+        \procedure{$\UGEN(\uid)$}{%
+          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
+          (\upk,\usk) \gets \KeyGen(\parm) \\
+          \UK[\uid] \gets (\upk,\usk) \\
+          \HU \gets \HU \cup \lbrace \uid \rbrace \\
+          \pcreturn \upk \\
+        }
+
+        \procedure{$\ISET(\uid,\fissue)$}{%
+          \pcif \uid \notin \HU \cup \CU: \pcreturn \bot \\
+          \pcif \uid \in \HI \cup \CI: \pcreturn \bot \\
           \pcif \fissue \notin \famfissue: \pcreturn \bot \\
-          (\ipk,\isk) \gets \IKeyGen(\parm) \\
-          \IK[\iid] \gets ((\ipk,\fissue),\isk) \\
-          \HI \gets \HI \cup \lbrace \iid \rbrace \\
+          \ipk \gets \ISet(\UK[\uid],\fissue) \\
+          \IK[\uid] \gets ((\ipk,\fissue),\PRVUK[\uid]) \\
+          \pcif \uid \in \HU: \HI \gets \HI \cup \lbrace \uid \rbrace \\
+          \pcif \uid \in \CU: \CI \gets \CI \cup \lbrace \uid \rbrace \\
           \pcreturn \ipk \\
         }
-
-        \procedure{$\ICORR(\iid)$}{%
-          \pcif \iid \in \CI \lor \iid \notin \HI: \pcreturn \bot \\
-          \HI \gets \HI \setminus \lbrace \iid \rbrace \\
-          \CI \gets \CI \cup \lbrace \iid \rbrace \\
-          \pcreturn \isk \\
-        }
-
-        \procedure{$\HUGEN(\uid)$}{%
-          \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
-          (\upk,\usk) \gets \UKeyGen(\parm) \\
-          \UK[\uid] \gets (\upk,\usk);
-          \HU \gets \HU \cup \lbrace  \uid \rbrace \\
-          \pcreturn \top \\
-        }
-
-        \procedure{$\RREG(i)$}{%
-          \pcreturn \trans[i]
-        }
-
-      \end{minipage}
-    }
-    \scalebox{0.9}{
-
-      \begin{minipage}[t]{.5\textwidth}
 
@@
           \HO \gets \HO \cup \lbrace \oid \rbrace \\
-          \pcreturn \opk \\
+          \pcreturn \opk
+        }
+
+      \end{minipage}
+    }
+    \scalebox{0.9}{
+
+      \begin{minipage}[t]{.5\textwidth}
+
+        \procedure{$\UCORR(\uid)$}{%
+          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
+          \pcif \uid \in \HI \cup \CI: \pcreturn \bot \\
+          \HU \gets \HU \setminus \lbrace \uid \rbrace \\
+          \CU \gets \CU \cup \lbrace \uid \rbrace \\
+          \pcreturn (\PRVUK[\uid],\CRED[\uid]) \\
+        }
+
+        \procedure{$\ICORR(\uid)$}{%
+          \pcif \uid \notin \HI: \pcreturn \bot \\
+          \HI \gets \HI \setminus \lbrace \uid \rbrace \\
+          \CI \gets \CI \cup \lbrace \uid \rbrace \\
+          \pcreturn(\PRVUK[\uid],\CRED[\uid]) \\
         }
@@
 
-        \procedure{$\CUGEN(\uid)$}{%          
-          \pcif \uid \in \CU: \pcreturn \bot \\
-          \CU \gets \CU \cup \lbrace \uid \rbrace \\          
-          \pcif \uid \in \HU: \\
-          \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
-          \pcind \pcreturn (\UK[\uid],\CRED[\uid]) \\
-          \pcelse: \UK[\uid] = \bot \\          
-          \pcreturn \top \\
+        % \procedure{$\CUGEN(\uid)$}{%          
+        %   \pcif \uid \in \CU: \pcreturn \bot \\
+        %   \CU \gets \CU \cup \lbrace \uid \rbrace \\          
+        %   \pcif \uid \in \HU: \\
+        %   \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
+        %   \pcind \pcreturn (\UK[\uid],\CRED[\uid]) \\
+        %   \pcelse: \UK[\uid] = \bot \\          
+        %   \pcreturn \top \\
+        % }
+
+        \procedure{$\RREG(i)$}{%
+          \pcreturn \trans[i] \\
         }
@@
   needs an honest issuer as, otherwise, the transcripts won't be available. 
-\item[$\ExtractSign(\trap,\oid,\lbrace \iid_i \rbrace_{i \in [n]},\Sig,\msg,
+\item[$\ExtractSign(\trap,\opk,\lbrace \ipk_i \rbrace_{i \in [n]},\Sig,\msg,
   \feval) \rightarrow ((\upk,\usk),\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
@@
   \feval. It outputs the user secret key and credential set \sCred used to
-  generate the signature, and the $\yeval^1$ and \yinsp values.
+  generate the signature, and the $\yeval^1$ and \yinsp values. For notational
+  convenience, we overload this function and use \oid and \iid instead of the
+  actual opener and issuers' key pairs.
 % \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
@@
       (\uid,\oid,\scid,\msg,\feval)
-      \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
+      \gets \adv^{\UGEN,\OGEN,\ISET,\OBTISS,\RREG}(\parm) \\
       \pcif \feval \notin \famfeval: \pcreturn 0 \\
@@
       \pcind \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
-      \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot)\\
+      \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
       \pcind \pcif \fissue(\PUBUK[\uid],\attrs,
@@
 \figref{fig:exp-uas-anonb}, where
-$\OIssAnon \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,
-\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\OBTCHALb)$, and $\OSigAnon
-\gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace
+$\OIssAnon \gets (\lbrace\OO,\UU\rbrace\GEN,\ISET,\ISET,\lbrace\II,
+\OO,\UU\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\OBTCHALb)$, and $\OSigAnon
+\gets (\lbrace\OO,\UU\rbrace\GEN,\ISET,\ISET,\lbrace\II,\OO,\UU\rbrace
 \CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$.
@@
 adversary is given access to the oracle set $\Oforgeissue = \Oforgesign \gets
-\lbrace\HU,\CU\rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.
+\lbrace\OO,\UU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace\CORR,\OBTISS,\ISSUE,\RREG,
+\SIGN,\OPEN$.
 
@@
         \pcreturn 0 \\
-        \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans) \\
+        \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
+        \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
         % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
@@
 adversary has access to the oracles in $\Oframe \gets
-\lbrace\HU,\CU\rbrace\GEN, \lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,
+\lbrace\OO,\UU\rbrace\GEN,\ISET,\lbrace\II,\OO,\UU\rbrace\CORR,
 \WREG,\OBTAIN,\SIGN$.
@@
 From them, we build \CUASGen as follows.
+\todo{Check if \SSetup etc is still needed...}
 
@@
 
-\paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
-Each issuer first parses \parm as $(\cdot,\SBCMparm,
-\Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets
-\SKeyGen(\Sparm)$, $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$,
-$\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$, $\ipk \gets (\SBCMparm,\Svk,
-\fissue,\sig_{\fissue})$, $\isk \gets \Ssk$ and return $(\ipk,\isk)$.
+% \paragraph{$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.} %
+% Each issuer first parses \parm as $(\cdot,\SBCMparm,
+% \Sparm,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets
+% \SKeyGen(\Sparm)$, $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$,
+% $\sig_{\fissue} \gets \SSign(\Ssk,\fissue)$, $\ipk \gets (\SBCMparm,\Svk,
+% \fissue,\sig_{\fissue})$, $\isk \gets \Ssk$ and return $(\ipk,\isk)$.
+
+\paragraph{$(\upk,\usk) \gets \KeyGen(\parm)$.} %
+Each user first parses \parm as $(\cdot,\SBCMparm,
+\cdot,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\SBCMvk,\SBCMsk) \gets
+\SBCMKeyGen(\SBCMparm)$, $\upk \gets (\parm,\SBCMvk)$, $\usk \gets \SBCMsk$,
+and returns $(\upk,\usk)$.
 
@@
 
-\paragraph{$(\upk,\usk) \gets \UKeyGen(\parm)$.} %
-Each user, prior to requesting credentials, generates his secret key by picking
-randomly $\usk \getr \AttrSpace$. Set $\upk \gets \CCommit(\usk;0)$.
+\paragraph{$\ipk \gets \ISet((\upk,\usk),\fissue)$.} %
+A user willing to become an issuer just sets $\ipk \gets (\upk,\fissue)$, and
+returns \ipk.
 
@@
 \yeval^1),\usk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$, and encrypts
-\yinsp by running $\cinsp \gets \EEnc(\Eek,\yinsp; r)$ for some fresh randomness
-$r$. Finally, the user
+\yinsp by running $\cinsp \gets \EEnc(\Eek,\yinsp; r')$ for some fresh
+randomness $r'$. Finally, the user
 computes $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,
@@
 concrete \fissue, \feval and \finsp functions depending on their needs. Note
-however that alternative constructions are possible, that are close to \CUASGen,
-but differ in key aspects while still meeting the \UAS model. We briefly
-describe them next, as we leverage them to build related schemes. \todo{Security
-proofs are deferred to \appref{app:uas-variants-proofs}.}
-
-\paragraph{$\CUASGen^{usr-iss}$: Collapsing issuers and users.} %
-On occasions, it may be useful to not make a distinction between issuers and
-users. For instance, for credential delegation, or in decentralized identity
-systems. In both cases, users may end up acting as issuers themselves. The
-algorithms are as in \CUASGen, except that there is no \UKeyGen -- or, rather,
-the steps run by \UKeyGen are exactly the same as in \IKeyGen. Concretely,
-$\usk \gets \isk$ and $\upk \gets \ipk$, where \isk and \ipk are generated
-as in \IKeyGen.
+however that alternative constructions are of course possible that, while
+still be close to \CUASGen, may differ in key aspects while still meeting the
+\UAS model. We briefly one such variant next, that we leverage to build related
+schemes. \todo{Security proofs are deferred to \appref{app:uas-variants-proofs}.}
+
+% \paragraph{$\CUASGen^{usr-iss}$: Collapsing issuers and users.} %
+% On occasions, it may be useful to not make a distinction between issuers and
+% users. For instance, for credential delegation, or in decentralized identity
+% systems. In both cases, users may end up acting as issuers themselves. The
+% algorithms are as in \CUASGen, except that there is no \UKeyGen -- or, rather,
+% the steps run by \UKeyGen are exactly the same as in \IKeyGen. Concretely,
+% $\usk \gets \isk$ and $\upk \gets \ipk$, where \isk and \ipk are generated
+% as in \IKeyGen.
 

### 2022-07-28 prism-backend/research/gsac/relationships.tex
Migrated syntax, model and construction where issuers=users. RS construction fixed.

@@
         & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
-        & \fissue^{single,L}(\upk,\cdot,\cdot) \coloneqq
-          \pcreturn \upk \notin L
+        & \fissue^{single,F,I,L}(\upk,\cdot,\cdot) \coloneqq
+          \pcif F(I||\upk) \in L~\pcreturn 0;~\pcelse \pcreturn F(I||\upk)
           \nonumber \\
@@
 restriction, is a secure group signature scheme according to \cite{bsz05}.
-Observe that the $\fissue^{single,L}$ function is further parameterized with
+Observe that the $\fissue^{single,F,I,L}$ function is further parameterized with
 a list $L$ maintained by the issuer and must be fetched by users prior to
@@
 \item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
-  of \CUASGen, and one instance of \IKeyGen and \OKeyGen. Assigns the public
-  keys to \gpk.
-\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \UKeyGen from \CUASGen.
+  of \CUASGen, and one instance of \KeyGen and \ISet with
+  $\fissue^{single,F,I,L}$ (both for the same user, who will be the only issuer
+  in the GS scheme) and \OKeyGen. Assigns the public keys to \gpk.
+\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \KeyGen from \CUASGen.
 \item[$\langle \cred,\utrans \rangle \gets
@@
 \item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
-  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen --
-  note that $0$ is the constant output of $\feval^0$.
+  runs $(\sig,0) \gets \Sign(\usk,\opk,\cred,\msg,\feval^0)$ from \CUASGen,
+  where $\yeval = 0$ is the constant output of $\feval^0$.
 \item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
@@
 is essentially a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
-of our $\CUASGen^{hide-iss}$ construction. The construction is as follows:
+of our $\CUASGen^{hide-iss}$ construction. In a nutshell, we let users self-issue
+credentials where the attributes are (a subset of encodings of) the public keys
+of the users in the system -- including their own public key. Then, a ring
+signature is just a $\CUASGen^{hide-iss}$ signature that reveals a subset of
+the attributes -- i.e., a subset of the keys of the users in the system. In more
+detail, the construction is as follows:
 
@@
 \item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
-  $\parm \gets \Setup(\secpar)$ from $\CUASGen^{hide-iss}$, as well as $n$
-  instances of $(\ipk_i,\isk_i) \gets \IKeyGen(\parm,\fissue^{\sring})$, where
-  $\sring = \lbrace \ipk_i \rbrace_{i\in[n]}$, and $(\opk,\osk) \gets
-  \OKeyGen(\parm,\finsp^0)$. 
-\item[$\langle \cred,\bot,\utrans,\bot \rangle \gets
-  \langle \Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk=\attrs,\attrs)\rangle.$]
-  A user, with $\usk=\isk_i$ and $\upk=\ipk_i$ for some $i \in [n]$, acts both
-  as user and issuer to self-issue a credential for an attribute set \attrs such
-  that $\attrs \subseteq \sring$, where \sring is the set of public keys used to
-  define $\fissue^{\sring}$.
-\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\cred,\msg,\feval).$] As in
-  $\CUASGen^{hide-iss}$, using $\feval^{\sring,\dattrs}$ as evaluation
-  function, using as signing credential the self-issued credential. Note that
-  $\dattrs \subseteq \attrs = \sring$ defines the subring to use for the
-  produced signature.
-\item[$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval).$] As in
-  $\CUASGen^{hide-iss}$, making $\sipk=\yeval=\lbrace \ipk_i
-  \rbrace_{i\in\dattrs}$.
+  $\parm \gets \Setup(\secpar)$ from $\CUASGen^{hide-iss}$. Then, for each of
+  the $i \in [n]$ users to generate, run $(\upk_i,\usk_i) \gets \KeyGen(\parm)$,
+  and $\ipk_i \gets \ISet((\upk_i,\usk_i),\fissue^{\sring})$, where $\sring =
+  \lbrace \upk_i \rbrace_{i\in[n]}$. Run also $(\opk,\osk) \gets \OKeyGen(\parm,
+  \finsp^0)$. Set $\pk_i \gets (\ipk_i,\opk)$ and $\sk_i \gets \usk_i$, for
+  $i\in[n]$.
+\item[$\Sig \gets \Sign(\sk_i,R,\msg).$]
+  The signing user, with $\sk_i=\usk$ and $\pk_i=(\ipk_i,\opk)$ for some $i \in
+  [n]$, where $\pk_i \in R$, first acts both as user and issuer to self-issue a
+  credential \Cred over an attribute set \attrs such that $\attrs \subseteq
+  \sring$. The user picks some \dattrs such that $\dattrs \subseteq [|\attrs|]$,
+  and computes the ring signature by running $\Sig = (\sig,\yeval) \gets
+  \Sign(\usk,\opk,\Cred,\msg,\feval^{\sring,\dattrs})$ from
+  $\CUASGen^{hide-iss}$. Note that \dattrs defines the public keys within
+  $\attrs \subseteq \sring$ to be revealed through \yeval.
+\item[$1/0 \gets Verify(R,\Sig,\msg)$.] Parses \Sig as $(\sig,\yeval)$ and
+  runs $\Verify(\opk,\yeval=\lbrace \ipk_i\rbrace_{i\in\dattrs},\sig,\yeval,
+  \msg,\feval^{\sring,\dattrs})$ as in $\CUASGen^{hide-iss}$.
 \end{description}

### 2022-07-28 prism-backend/research/gsac/app-related-extra.tex
Moved RAC to main body, and DAC to app. Sync'ed RAC with new syntax.

@@
 
-\subsection{Revocable Anonymous Credentials}
-\label{sapp:related-models-rac}
+\subsection{Delegatable Anonymous Credentials}
+\label{ssec:related-models-dac}
 
-In \cite{cks10}, revocable anonymous credentials are proposed. From \CUASGen, it
-is straightforward to build an AC system with verifier local revocation, like in
-\cite{bs04}. Basically, all credentials get an identifier as first attribute,
-and \feval functions prove that the opener can retrieve that identifier. Then,
-in case of needing to revoke a concrete credential, any verifier can interact
-with the opener to add an identifier to its own revocation list (alternatively,
-there can be a public list of revoked credentials). Having \feval functions
-prove that the credential identifier does not belong to that list thus directly
-implements privacy-preserving revocation. We first give a simple model in
-\figref{fig:model-rac}, extending that in \appref{sapp:related-models-ac}. As
-before, for simplicity we assume only one credential is used per authentication
-(the extension being direct). To the functionality in
-\appref{sapp:related-models-ac}, we now explicitly add the $OKeyGen$ function
-(equivalent to \OKeyGen, with a fixed \finsp function),
-which generates the opener key pair, extend $Verify$ to receive also a list $L$
-of revoked identifiers, and we add a function (and corresponding oracle) $id/\bot
-\gets RetrieveCredId(\osk,\utrans)$ that can extract the identifier of the
-credential used in a presentation transcript \utrans -- and which is essentially
-equivalent to \Open in \UAS. For simplicity, we do not include the equivalent to
-verifiable openings, but this would be straightforward.
+We give a simple definition for a Delegatable Anonymous Credentials (DAC)
+scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
+our simple scheme built from $\CUASGen^{usr-iss}$ does not ensure privacy of the
+delegation chain -- which could be achieved by making \feval output projective
+proofs like in \cite{bcc+09}, but since our goal is to showcase the feasibility
+of building DAC from \UAS, we leave that out for brevity. Our simple scheme
+does, however, ensure that a (not top-level) issuer can only delegate attributes
+contained in a credential it owns. Also, for simplicity, we restrict to the case
+of using one credential per signature/interactive credential presentation, and
+assume that all parties use the same opener and \finsp function.
+%
+The functionality is thus defined almost as in \secref{ssec:related-models-ac},
+i.e., we have $Setup$, $IssKeyGen$ algorithms, and $\langle Obtain,Issue\rangle$
+and $\langle Show,Verify \rangle$ interactive protocols; but we do not have
+$UserKeyGen$, as this collapses with $IssKeyGen$.
+%
+In the model for this setting, since there are multiple issuers, in addition
+to the oracles in \secref{ssec:related-models-ac}, we use $HI$ and $CI$ oracles,
+equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
+issuers, and corrupt existing ones, respectively. The issuance and sign
+anonymity properties are direct, constraining the adversary to output challenge
+credentials and signatures with the same delegation chain. For unforgeability,
+we still require that no adversary can authenticate using a set of attributes
+that have not been issued to a corrupt user. In addition, we require that for
+any successful authentication using a level-$l$ credential, we
+can extract a chain of credentials of length $l$ such that each level-$i$
+credential can be used successfully to authenticate a level-$(i+1)$ credential
+down to the level-$l$ credential, and the attributes revealed in the
+level-$l$ authentication are contained in all the credentials up the chain.
 
@@
     \begin{minipage}[t]{0.45\textwidth}
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
+      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
         \parm \gets \Setup(1^\secpar) \\
-        (\opk,\osk) \gets \OKeyGen(\parm) \\        
-        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
-        b^* \gets \adv^{\mathcal{O}_{anon}}(\parm,\ipk,\opk) \\
+        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
+        \pccomment{Abort if challenge creds belong to} \\
+        \pccomment{users with different delegation chains} \\
+        \pcreturn b^*
+      }
+      \vspace*{0.5em}
+
+      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
+        \pccomment{Abort if challenge sigs belong to} \\
+        \pccomment{users with different delegation chains} \\
         \pcreturn b^*
@@
     \begin{minipage}[t]{.55\textwidth}
-      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
         \parm \gets \Setup(1^\secpar) \\
-        (\opk,\osk) \gets \OKeyGen(\parm) \\        
-        (\ipk,\isk) \gets IssKeyGen(\parm) \\
-        (D,L,\st) \gets
-        \adv^{\mathcal{O}_{forge}}(\parm,\ipk) \\
-        \langle \cdot,(b,\utrans)\rangle
-        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
+        (D=(l,D'),\ipk_l,\st) \gets
+        \adv^{\mathcal{O}_{forge}}(\parm) \\
+        \langle\cdot,(b,\utrans)\rangle \gets
+        \langle \adv(\st),\Verify(\ipk_l,D)\rangle \\
         \pcif b = 0: \pcreturn 0 \\
@@
         \land D \subseteq \ATTR[j]): \pcreturn 1 \\        
-        h \gets RetrieveCredHandle(\osk,\utrans) \\
-        \pcif h \in L \lor h = \bot: \pcreturn 1 \\
+        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,l]})
+        \gets ExtractChain(\utrans) \\ 
+        \pcif \exists i \in [1,l]~\suchthat~
+        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
+        \pcind D' \not\subseteq \ATTR[\iid]) \land
+        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
+        \pcind \pcreturn 1 \\
         \pcreturn 0
@@
   }
-  \caption{Security games for revocable anonymous credentials with selective
-    disclosure based on \cite{fhs19}. 
-    $\mathcal{O}_{anon} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
-    ReqCredHandle,LoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace HU,CU,
-    Obtain,ObtIss,Issue,Show,ReqCredHandle \rbrace$. $ReqCredHandle$ is
-    equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
-    Also, \OWNR and \ATTR tables are essentially as in \secref{ssec:model-uas}.}
-  \label{fig:model-rac}  
+  \caption{Security games for delegatable anonymous credentials with selective
+    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HI,
+    CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon} \gets
+    \lbrace HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$. $\mathcal{O}_{forge}
+    \gets \lbrace HI,CI,Obtain,ObtIss,Issue,Show\rbrace$. $IssLor$ corresponds
+    to \OBTCHALb in \UAS, whereas $SigLor$ corresponds to \CHALb. Also, \OWNR
+    and \ATTR tables are essentially as in \secref{ssec:model-uas}.
+    $\ISR[\ipk]$, in this case, returns the identifier of the issuer with public
+    key \ipk. With $D = (l,D')$ we mean that the first attribute in the revealed
+    set $D$ is $l$, which denotes the level of the credential used for
+    authentication.}
+  \label{fig:model-dac}  
 \end{figure}
 
-\subsubsection{\CUASRAC Construction.} %
-
-For our RAC construction, we define signature evaluation and opening functions
-as follows:
+\subsubsection{\CUASDAC Construction.} %
+We next give a construction of a delegatable AC (DAC) scheme, in the shape of
+a $(\fissue^{l,\dattrs},\feval^{l,\dattrs},\finsp^0)$-$\CUASGen^{usr-iss}$
+restriction, where the $\finsp^0$ function is as defined in
+\figref{fig:func-restrictions}, and the \fissue and \feval variants are as
+defined next:
 
 \begin{align}
-  & \feval^{\dattrs,F,V,L}(\usk,\cred,\msg) \coloneqq
-    \lbrace
-    \pcif F(V,\attrs_1(\cred)) \in L: \pcreturn (0,0);
-    \pcelse \pcreturn (\dattrs(\cred),V)
-    \rbrace \nonumber \\
-  & \finsp^{F}((\yeval^0,\yeval^1),\usk,\cred,\msg) \coloneqq
-    \lbrace
-    \pcif \yeval^0 \neq 0: \pcreturn F(\yeval^1,\attrs_1(\cred));
-    \pcelse \pcreturn 0
-     \rbrace
+  & \fissue^{l,\dattrs}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
+    \pcreturn (\attrs_1 = l+1 \land \attrs \subseteq
+    \cup_{i\in\dattrs} \cattrs_i) \nonumber
+  & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
+    \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
     \label{eq:funcs-rac}
@@
 
-Where, $\feval^{\dattrs,F,V,L}$ is parameterized with a one-way and
-collision-resistant function $F$
-(e.g., a cryptographic hash), some constant subset \dattrs of attributes to be
-selectively disclosed by signers, a string identifying the verifier $V$ and a
-list $L$ of ``revocation handles'' by this verifier. If the credential used for
-signing has been revoked (i.e., if $F(V,id) \in L$), then \feval returns $0$, as
-an indication that the signature should be rejected by the verifier. Otherwise,
-it sets $\yeval^0 \gets \dattrs(\cred)$, and $\yeval^1 \gets V$ -- note that
-$\yeval^1$ will be encrypted with a single-use key pair.
+. In a DAC scheme, all users are (or may be) also issuers. We only
+distinguish between top-level issuers, who have level $l=0$, and lower-level
+issuers, who have level $l>0$. In our \CUASDAC scheme, we assume that the first
+attribute (after the user's secret key) encodes the level of the credential.
+That is, $\attrs_1=l$, for a credential of level $l$. In addition, all users
+(i.e., with $l>0$) who want to delegate have to publicly list:
+
+\begin{enumerate}
+\item The level $l$ of the credential they delegate.
+\item Their public key \ipk.
+\item An \UAS signature proving knowledge of a credential of level $l$, and over
+  the attributes that this level-$l$ issuer is delegating.
+\item The \ipk of the parent issuer.
+\item The $\fissue^{l,\dattrs}$ function they will require for delegating.
+\item An $\feval^{l,\dattrs}$ function used to produce the signature at item 3.
+\end{enumerate}
+
+We assume that, from an \ipk, it is possible to find the corresponding issuer
+(e.g., using the previously mentioned public list). The mentioned
+$\fissue^{l,\dattrs}$ functions must follow the pattern in \figref{fig:func-restrictions}.
+Namely, the issuance function checks that the first requested attribute equals
+$l+1$, and that all requested attributes are a subset of the attribute set
+\dattrs being delegated by the level-$l$ issuer. In addition, signature
+evaluation functions $\feval^{l,\dattrs}$, also shown in \figref{fig:func-restrictions},
+must reveal the level of the credential used to produce the \UAS signature at
+item 2, as well as the set of attributes \dattrs that the level-$l$ issuer
+delegates. Verifiers can then trivially check if the set of revealed attributes
+are contained within the attributes delegatable by the parent issuer%
+\footnote{Additional checks may be added in both functions, but this is
+  the bare minimum.}.
 %
-On the other hand, $\finsp^{F}$ outputs $F(\yeval^1,\attrs_1(\cred))$, allowing
-valid signatures to be locally revocable by $V$ at a later stage, since
-$\yeval^1=V$.
+From this high-level description, we define the algorithms of \CUASDAC:
 
 \begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
-  \CUASGen.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \IKeyGen from our
-  \CUASGen construction, setting $\fissue^1$ as issuance function.
-\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
-  \CUASGen construction, setting $\finsp^F$ as opening function.
-\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from the
-  \CUASGen construction, and computes $\CCommit(\usk;0)$ as \upk.
+\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
+  and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
+  $\CUASGen^{usr-iss}$ construction. Returns $\parm \gets (\parm',\opk)$. Note
+  that $\finsp^0$ can be replaced by any desired opening function.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $l=0$, simply run \IKeyGen as
+  in $\CUASGen^{usr-iss}$. If $l>0$, this level-$l$ issuer picks a random
+  message $r$ and computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
+  \feval^{l,\dattrs})$, for the \dattrs set it wants to reveal -- which must
+  include the attributes to delegate, and the credential level. It then
+  publishes $(l,\ipk,\Sig,\ipk^{l-1},\fissue^{l,\dattrs},\feval^{l,\dattrs})$,
+  where $\ipk^{l-1}$ is the public key of the parent issuer,
+  $\fissue^{l,\dattrs}$ is an issuance function as described in
+  \figref{fig:func-restrictions}, and $\feval^{l,\dattrs}$ is also as in
+  \figref{fig:func-restrictions}, revealing the attributes that the issuer is
+  willing to delegate.
+% \item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
+%   also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
+%   $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
+%   credentials. Note that this does not affect security, as long as
+%   $\isk \getr \AttrSpace$.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
   \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
-  $\fissue^1$ as issuance function.
-\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,\attrs,\dattrs,\cred),
-  \Verify(\ipk,\dattrs) \rangle$.]
-  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
-  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
-  $\finsp^F$ as open function.
-\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
-  Outputs the revocation handle $h$ for the credential used in the interactive
-  presentation associated to \utrans. Note that $h$ is verifier-dependent.
+  If $l>0$, the user first finds the corresponding $(l,\ipk,\Sig,\ipk^{n-1},
+  \fissue^{l,\dattrs},\feval^{l,\dattrs})$ tuple, and checks \Sig running
+  \Verify as in $\CUASGen^{usr-iss}$ (with the retrieved $\feval^{l,\dattrs}$).
+  Then, user and level-$l$ issuer run $\langle\Obtain,\Issue\rangle$ as in
+  $\CUASGen^{usr-iss}$, using $\fissue^{l,\dattrs}$ as issuance function. If
+  $l=0$, then both run $\langle\Obtain,\Issue\rangle$ as in
+  $\CUASGen^{usr-iss}$, using the \fissue function required by the issuer.
+\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle
+  \gets \langle Show(\opk,\attrs,\dattrs,\cred),
+  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of
+  $\CUASGen^{usr-iss}$.  
 \end{description}
 
-\paragraph{Security of \CUASRAC.} %
-We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
-scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
-is anonymous and has unforgeable signing. Note that issuance unforgeability
-of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
-leveraging other credentials not any fixed custom issuance policy. Thus,
-signature unforgeability from \UAS is enough. Note that AC schemes modelled
-as in \cite{fhs19} do not have issuance anonymity, as the user public key
-is passed to the issuer.
+\paragraph{Security of \CUASDAC.} % 
+We prove that \CUASDAC is an anonymous and unforgeable DAC scheme, according to
+the model in \figref{fig:model-dac}, if the underlying \CUASGen construction has
+anonymous issuance and signing, and has unforgeable issuance and signing.
 
-\begin{theorem}[Anonymity of \CUASRAC]
-  \label{thm:anon-cuasac}
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, and $F$ is one-way and collision-resistant,
-  then \CUASAC is an anonymous AC scheme according to \cite{fhs19}.
+\begin{theorem}[Issuance anonymity of \CUASDAC]
+  If the base \CUASGen construction has issuance anonymity according to
+  \defref{def:issue-anonymity-uas}, then \CUASDAC also has issuance anonymity.
 \end{theorem}
@@
 \begin{proof}
-  Given \adv~ against anonymity of \CUASRAC as defined in
-  \figref{fig:model-rac}, we build an adversary \advB against anonymity of
-  \CUASGen as defined in \defref{def:sign-anonymity-uas}.
-
-  First observe that, given a revocation handle $F(V,id)$ extracted from any
-  credential showing, it is not possible to extract $id$, as $F$ is one-way
-  and collision-resistant.
+  Given \adv~ against issuance anonymity of \CUASDAC as defined in
+  $\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
+  issuance anonymity of \CUASGen as defined in \defref{def:issue-anonymity-uas}.
 
   To simulate oracle calls by \adv, \advB simply redirects to its corresponding
-  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
-  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, of \OPEN respectively.
-  Note that ``translating'' the inputs from the former into inputs for the
-  latter is trivial. Also, observe that $ReqCredHandle$ essentially refuses to
-  open transcripts from challenge users (signatures, in the non-interactive
-  equivalent), as $F(V,\attrs_1(\ccid_0) \neq F(V,\attrs_1(\ccid_1)$ with
-  overwhelming probability (see the $\tyinsp \neq \yinsp$) check in
-  \figref{fig:oracles2}. Obviously, if \adv~ wins in its anonymity game, then
-  so does \advB with the same probability.
+  oracle, i.e.: for calls to $HU,CU,HI,CI,Obtain,Show,IssLoR$, \advB redirects
+  to \HUGEN,\CUGEN,\IGEN,\ICORR,\OBTAIN,\SIGN,\OBTCHALb, respectively. Note that
+  ``translating'' the inputs from the former into inputs for the latter is
+  trivial. Obviously, if \adv~ wins in its issuance anonymity game, then so does
+  \advB with the  same probability.
   % 
@@
 
-\begin{theorem}[Unforgeability of \CUASRAC]
-  If the base \CUASGen construction has sign unforgeability according to
-  \defref{def:sign-forge-uas}, and $F$ is one-way and collision-resistant, then
-  \CUASRAC is an unforgeable RAC scheme.
+\begin{theorem}[Signature anonymity of \CUASDAC]
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASDAC also has signature anonymity.
 \end{theorem}
@@
 \begin{proof}
-  Given \adv~ against unforgeability of \CUASRAC as defined in
-  \figref{fig:model-rac}, we build an adversary \advB against sign
-  unforgeability of \CUASGen as defined in \defref{def:sign-forge-uas}.
+  This is the same as in \thmref{thm:anon-cuasac}.
+  % 
+  \qed
+\end{proof}
 
-  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
-  that \adv~ wins its game via the winning condition of line 6 in the RAC
-  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
-  that the probability of \adv~ winning its game via the winning condition at
-  line 9 is negligible, due to soundness of the NIZK scheme used for signing,
-  and the one-wayness and collision-resistance of $F$ in
-  $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.
+\begin{theorem}[Unforgeability of \CUASAC]
+  If the base \CUASGen construction has issuance and signature unforgeability
+  according to \defref{def:issue-forge-uas} and \defref{def:sign-forge-uas}, and
+  non-frameability according to \defref{def:frame-uas}, then \CUASAC is an
+  unforgeable AC scheme.
+\end{theorem}
+
+\begin{proof}
+  First, we define the $ExtractChain(\utrans)$ function for our construction.
+  Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows for the approach
+    to transform non-interactive signature and verification in \UAS to interactive
+    presentations, as described in \secref{ssec:variants-gsac}.}, where $r$ is a
+  fresh random number produced by the environment (acting as honest verifier),
+  and \Sig is a \CUASGen signature over $r$. Thus, $ExtractChain$ leverages
+  \ExtractSign from \CUASGen (see \secref{ssec:security-uas}) to get the
+  credential and associated \ipk used to produce \Sig. Note that, for this
+  \ipk, $\ipk = \ipk_{n-1}$ in $\Exp^{forge}_{\adv,dac}$. In \CUASDAC, we can
+  leverage $\ipk_{n-1}$ to fetch from the public list a signature $\Sig_{n-1}$
+  generated by the issuer owner of $\ipk_{n-1}$. Again, we apply \ExtractSign
+  from \CUASGen, to get the credential one layer up in the chain.
+  $ExtractChain$ repeats this step, until reaching the top level credential,
+  issued by $\ipk_0$.
+
+  For the proof, we first replace within $Setup$ the $\NIZKSetup$ algorithms for
+  issuance and signing with their corresponding $\NIZKSetup$. Due to their
+  zero-knowledge property, the resulting game is indistinguishable. Also, note
+  that $ExtractChain$ succeeds to extract the corresponding credential chain,
+  due to simulation extractability of the NIZKs.
+
+  From the previous, the same reasoning as in \thmref{thm:forge-cuasac} applies
+  to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
+  suppose that, from \utrans obtained at line 6, $ExtractChain$ outputs a
+  delegation chain that makes \adv~win at line 10. This means that an
+  uncorrupted issuer at position $i-1$ of the chain did not own a credential
+  containing $D'$, but the issuer at position $i$ does. Then, either of the
+  following must happen:
+
+  \begin{itemize}
+  \item The credential of the issuer at position $i$ is a forgery, meaning that
+    it is a valid signature by the issuer at position $i-1$, who did not produce
+    it. This can be used to break signature non-frameability of \CUASGen.
+  \item The credential of the issuer at position $i$ is not a forgery, meaning
+    that it is a valid signature by the issuer at position $i-1$, who produced
+    it. But this contradicts the conditions required by $\fissue^{n,\dattrs}$,
+    and therefore breaks issuance unforgeability of \CUASGen.
+  \end{itemize}
   %

### 2022-07-28 prism-backend/research/gsac/app-related-proofs.tex
Moved RAC to main body, and DAC to app. Sync'ed RAC with new syntax.

@@
 
-\subsection{Security of \CUASDAC}
+\subsection{Security of \CUASRAC}
 
-We prove that \CUASDAC is an anonymous and unforgeable DAC scheme, according to
-the model in \figref{fig:model-dac}, if the underlying \CUASGen construction has
-anonymous issuance and signing, and has unforgeable issuance and signing.
+We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
+scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
+is anonymous and has unforgeable signing. Note that issuance unforgeability
+of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
+leveraging other credentials not any fixed custom issuance policy. Thus,
+signature unforgeability from \UAS is enough. Note that AC schemes modelled
+as in \cite{fhs19} do not have issuance anonymity, as the user public key
+is passed to the issuer.
 
-\begin{theorem}[Issuance anonymity of \CUASDAC]
-  If the base \CUASGen construction has issuance anonymity according to
-  \defref{def:issue-anonymity-uas}, then \CUASDAC also has issuance anonymity.
+\begin{theorem}[Anonymity of \CUASRAC]
+  \label{thm:anon-cuasac}
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, and $F$ is one-way and collision-resistant,
+  then \CUASAC is an anonymous AC scheme according to \cite{fhs19}.
 \end{theorem}
@@
 \begin{proof}
-  Given \adv~ against issuance anonymity of \CUASDAC as defined in
-  $\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
-  issuance anonymity of \CUASGen as defined in \defref{def:issue-anonymity-uas}.
+  Given \adv~ against anonymity of \CUASRAC as defined in
+  \figref{fig:model-rac}, we build an adversary \advB against anonymity of
+  \CUASGen as defined in \defref{def:sign-anonymity-uas}.
+
+  First observe that, given a revocation handle $F(V,id)$ extracted from any
+  credential showing, it is not possible to extract $id$, as $F$ is one-way
+  and collision-resistant.
 
   To simulate oracle calls by \adv, \advB simply redirects to its corresponding
-  oracle, i.e.: for calls to $HU,CU,HI,CI,Obtain,Show,IssLoR$, \advB redirects
-  to \HUGEN,\CUGEN,\IGEN,\ICORR,\OBTAIN,\SIGN,\OBTCHALb, respectively. Note that
-  ``translating'' the inputs from the former into inputs for the latter is
-  trivial. Obviously, if \adv~ wins in its issuance anonymity game, then so does
-  \advB with the  same probability.
+  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
+  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, of \OPEN respectively.
+  Note that ``translating'' the inputs from the former into inputs for the
+  latter is trivial. Also, observe that $ReqCredHandle$ essentially refuses to
+  open transcripts from challenge users (signatures, in the non-interactive
+  equivalent), as $F(V,\attrs_1(\ccid_0) \neq F(V,\attrs_1(\ccid_1)$ with
+  overwhelming probability (see the $\tyinsp \neq \yinsp$) check in
+  \figref{fig:oracles2}. Obviously, if \adv~ wins in its anonymity game, then
+  so does \advB with the same probability.
   % 
@@
 
-\begin{theorem}[Signature anonymity of \CUASDAC]
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASDAC also has signature anonymity.
+\begin{theorem}[Unforgeability of \CUASRAC]
+  If the base \CUASGen construction has sign unforgeability according to
+  \defref{def:sign-forge-uas}, and $F$ is one-way and collision-resistant, then
+  \CUASRAC is an unforgeable RAC scheme.
 \end{theorem}
@@
 \begin{proof}
-  This is the same as in \thmref{thm:anon-cuasac}.
-  % 
-  \qed
-\end{proof}
+  Given \adv~ against unforgeability of \CUASRAC as defined in
+  \figref{fig:model-rac}, we build an adversary \advB against sign
+  unforgeability of \CUASGen as defined in \defref{def:sign-forge-uas}.
 
-\begin{theorem}[Unforgeability of \CUASAC]
-  If the base \CUASGen construction has issuance and signature unforgeability
-  according to \defref{def:issue-forge-uas} and \defref{def:sign-forge-uas}, and
-  non-frameability according to \defref{def:frame-uas}, then \CUASAC is an
-  unforgeable AC scheme.
-\end{theorem}
-
-\begin{proof}
-  First, we define the $ExtractChain(\utrans)$ function for our construction.
-  Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows for the approach
-    to transform non-interactive signature and verification in \UAS to interactive
-    presentations, as described in \secref{ssec:variants-gsac}.}, where $r$ is a
-  fresh random number produced by the environment (acting as honest verifier),
-  and \Sig is a \CUASGen signature over $r$. Thus, $ExtractChain$ leverages
-  \ExtractSign from \CUASGen (see \secref{ssec:security-uas}) to get the
-  credential and associated \ipk used to produce \Sig. Note that, for this
-  \ipk, $\ipk = \ipk_{n-1}$ in $\Exp^{forge}_{\adv,dac}$. In \CUASDAC, we can
-  leverage $\ipk_{n-1}$ to fetch from the public list a signature $\Sig_{n-1}$
-  generated by the issuer owner of $\ipk_{n-1}$. Again, we apply \ExtractSign
-  from \CUASGen, to get the credential one layer up in the chain.
-  $ExtractChain$ repeats this step, until reaching the top level credential,
-  issued by $\ipk_0$.
-
-  For the proof, we first replace within $Setup$ the $\NIZKSetup$ algorithms for
-  issuance and signing with their corresponding $\NIZKSetup$. Due to their
-  zero-knowledge property, the resulting game is indistinguishable. Also, note
-  that $ExtractChain$ succeeds to extract the corresponding credential chain,
-  due to simulation extractability of the NIZKs.
-
-  From the previous, the same reasoning as in \thmref{thm:forge-cuasac} applies
-  to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
-  suppose that, from \utrans obtained at line 6, $ExtractChain$ outputs a
-  delegation chain that makes \adv~win at line 10. This means that an
-  uncorrupted issuer at position $i-1$ of the chain did not own a credential
-  containing $D'$, but the issuer at position $i$ does. Then, either of the
-  following must happen:
-
-  \begin{itemize}
-  \item The credential of the issuer at position $i$ is a forgery, meaning that
-    it is a valid signature by the issuer at position $i-1$, who did not produce
-    it. This can be used to break signature non-frameability of \CUASGen.
-  \item The credential of the issuer at position $i$ is not a forgery, meaning
-    that it is a valid signature by the issuer at position $i-1$, who produced
-    it. But this contradicts the conditions required by $\fissue^{n,\dattrs}$,
-    and therefore breaks issuance unforgeability of \CUASGen.
-  \end{itemize}
+  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
+  that \adv~ wins its game via the winning condition of line 6 in the RAC
+  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
+  that the probability of \adv~ winning its game via the winning condition at
+  line 9 is negligible, due to soundness of the NIZK scheme used for signing,
+  and the one-wayness and collision-resistance of $F$ in
+  $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.
   % 

### 2022-07-28 prism-backend/research/gsac/relationships.tex
Moved RAC to main body, and DAC to app. Sync'ed RAC with new syntax.

@@
         & \fissue^{single,F,I,L}(\upk,\cdot,\cdot) \coloneqq
-          \pcif F(I||\upk) \in L~\pcreturn 0;~\pcelse \pcreturn F(I||\upk)
+          \pcif F(I,\upk) \in L~\pcreturn 0;~\pcelse \pcreturn F(I,\upk)
           \nonumber \\
         & \fissue^{\sring}(\upk,\attrs,\cdot) \coloneqq
-          \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber \\
-        & \fissue^{l,\dattrs}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
-          \pcreturn (\attrs_1 = l+1 \land \attrs \subseteq
-          \cup_{i\in\dattrs} \cattrs_i) \nonumber
+          \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber
       \end{align}
@@
         & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
-        & \feval^{\dattrs}(\cdot,(\cid,\attrs),\cdot)
+        & \feval^{\dattrs}(\cdot,(\cdot,\attrs),\cdot)
           \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
           \nonumber \\
-        & \feval^{\sring,\dattrs}(\upk,(\cid,\attrs),\cdot)
+        & \feval^{\sring,\dattrs}(\upk,(\cdot,\attrs),\cdot)
           \coloneqq \pcif \upk \in \lbrace \attrs_i \rbrace_{i\in\dattrs}
@@
           \pcreturn (\lbrace \attrs_i \rbrace_{i\in\dattrs},\ast);
-          \pcelse \pcreturn \bot \nonumber \\
-        & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
-          \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
+          \pcelse \pcreturn (0,\ast) \nonumber \\
+        & \feval^{\dattrs,F,V,L}(\upk,((\cidi,\cidu),\attrs),\cdot) \coloneqq
+          \nonumber \\
+        & \hspace*{2em}\pcif F(V,\cidi) \in L \lor F(V,\cidu) \in L:
+          \pcreturn (0,\ast) \nonumber \\
+        & \hspace*{2em}\pcelse \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},V)
         \nonumber   
@@
           \pcreturn \upk % \CCommit(\usk;0)
+          \nonumber \\
+        & \finsp^{F}((\yeval^0,\yeval^1),\cdot,((\cidi,\cidu),\attrs),\cdot)
+          \coloneqq \nonumber \\
+        & \hspace*{2em}\pcif \yeval^0 \neq 0:
+          \pcreturn (F(\yeval^1,\cidi),F(\yeval^1,\cidu)) \nonumber \\
+        & \hspace*{2em}\pcelse \pcreturn 0
           \nonumber
@@
     ignored; and ``$\ast$'' to denote output values that can be set to anything
-    (but should be ignored). $\bot$ means the function fails.}
+    (but should be ignored).}
     % $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
@@
 \subsubsection{\CUASGS construction.} %
-We show that the $(\fissue^{single,L},\feval^0,\finsp^{\upk})$-\CUASGen
+We show that the $(\fissue^{single,F,IL},\feval^0,\finsp^{\upk})$-\CUASGen
 restriction, is a secure group signature scheme according to \cite{bsz05}.
@@
 \begin{description}
-\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs the \Setup algorithm
-  of \CUASGen, and one instance of \KeyGen and \ISet with
-  $\fissue^{single,F,I,L}$ (both for the same user, who will be the only issuer
-  in the GS scheme) and \OKeyGen. Assigns the public keys to \gpk.
+\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs \Setup from \CUASGen,
+  and one instance of \KeyGen and \ISet with $\fissue^{single,F,I,L}$ (both for
+  the same user, who will be the only issuer in the GS scheme) and \OKeyGen.
+  Assigns the public keys to \gpk.
 \item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Runs \KeyGen from \CUASGen.
@@
   \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
-  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$.
+  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. If the issuer
+  gets $\yissue = 0$, rejects issuing a new credential. Otherwise, it completes
+  the protocol and adds $\yissue$ to $L$.
 \item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
@@
 We adopt the model in \cite{fhs19}, for anonymous credentials with selective
-disclosure. Therein, an anonymous credential scheme is
-defined via $OrgKeyGen$ (which we rename to $IssKeyGen$), and $UserKeyGen$
-algorithms (roughly equivalent to
-\IKeyGen and \UKeyGen for \UAS), and $Obtain,Issue$ and $Show,Verify$
-interactive protocols. The issuance interactive protocol corresponds to
+disclosure. Therein, an anonymous credential scheme is defined via $OrgKeyGen$
+(which we rename to $IssKeyGen$, and is equivalent to \KeyGen+\ISet in \UAS),
+and $UserKeyGen$ (\KeyGen in \UAS) algorithms, and $Obtain,Issue$ and $Show,
+Verify$ interactive protocols. The issuance interactive protocol corresponds to
 the issuance protocol in \UAS. Similarly, $Show,Verify$ corresponds to
@@
 to build in \appref{app:interactive-uas}. The security definitions rely on
-$HU, CU, ObtIss, Obtain, Issue,Show$, and $LoR$ oracles, which are essentially
-equivalent to our \HUGEN, \CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb
-oracles. We refer to \cite{fhs19} for the full details. For ease of reference,
-we summarize the security definitions in \figref{fig:model-ac}.% , with inocuous
+$HU, CU, ObtIss, Obtain, Issue, Show$, and $LoR$ oracles, which are essentially
+equivalent to our \UGEN, \UCORR, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb
+oracles\footnote{The $CU$ oracle in \cite{fhs19} actually allows the adversary
+  to create corrupt user secret keys, while in our corruption model, corrupt
+  users have keys generated by the system that are later learned by the
+  adversary. This is however for notational simplicity -- and, indeed, in our
+  construction, all users need to prove knowledge of the \usk, which would be
+  consistent with the stronger corruption model in \cite{fhs19}}. We refer to
+\cite{fhs19} for the full details. For ease of reference, we summarize the
+security definitions in \figref{fig:model-ac}.% , with inocuous
 % adaptations to make them more suitable for comparison with our definitions --
@@
 
-\subsection{Delegatable Anonymous Credentials}
-\label{ssec:related-models-dac}
+\subsection{Revocable Anonymous Credentials}
+\label{sapp:related-models-rac}
 
-We give a simple definition for a Delegatable Anonymous Credentials (DAC)
-scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
-our simple scheme built from $\CUASGen^{usr-iss}$ does not ensure privacy of the
-delegation chain -- which could be achieved by making \feval output projective
-proofs like in \cite{bcc+09}, but since our goal is to showcase the feasibility
-of building DAC from \UAS, we leave that out for brevity. Our simple scheme
-does, however, ensure that a (not top-level) issuer can only delegate attributes
-contained in a credential it owns. Also, for simplicity, we restrict to the case
-of using one credential per signature/interactive credential presentation, and
-assume that all parties use the same opener and \finsp function.
-%
-The functionality is thus defined almost as in \secref{ssec:related-models-ac},
-i.e., we have $Setup$, $IssKeyGen$ algorithms, and $\langle Obtain,Issue\rangle$
-and $\langle Show,Verify \rangle$ interactive protocols; but we do not have
-$UserKeyGen$, as this collapses with $IssKeyGen$.
-%
-In the model for this setting, since there are multiple issuers, in addition
-to the oracles in \secref{ssec:related-models-ac}, we use $HI$ and $CI$ oracles,
-equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
-issuers, and corrupt existing ones, respectively. The issuance and sign
-anonymity properties are direct, constraining the adversary to output challenge
-credentials and signatures with the same delegation chain. For unforgeability,
-we still require that no adversary can authenticate using a set of attributes
-that have not been issued to a corrupt user. In addition, we require that for
-any successful authentication using a level-$l$ credential, we
-can extract a chain of credentials of length $l$ such that each level-$i$
-credential can be used successfully to authenticate a level-$(i+1)$ credential
-down to the level-$l$ credential, and the attributes revealed in the
-level-$l$ authentication are contained in all the credentials up the chain.
+In \cite{cks10}, revocable anonymous credentials are proposed. From \CUASGen, it
+is straightforward to build an AC system with verifier local revocation, like in
+\cite{bs04}. Basically, we leverage the $\cid=(\cidi,\cidu)$ identifiers,
+encoded as attributes, to define a $(\feval,\finsp)$ function pair that: (1)
+ensures that opening outputs a one-way function of the {\cid}s concatenated with
+the verifier name; and (2) ensures that, if the {\cid}s have been added to a
+revocation list by the verifier, the verifier will know it -- and hence will be
+able to reject the signature. We first give a simple model in
+\figref{fig:model-rac}, extending that in \secref{ssec:related-models-ac}.
+Concretely, to the functionality in \secref{ssec:related-models-ac}, we now
+explicitly add
+the $OKeyGen$ function (equivalent to \OKeyGen, with a fixed \finsp function),
+which generates the opener key pair, extend $Verify$ to receive also a list $L$
+of revoked identifiers, and we add a function (and corresponding oracle) $id/\bot
+\gets RetrieveCredId(\osk,\utrans)$ that can extract the identifier of the
+credential used in a presentation transcript \utrans -- and which is essentially
+equivalent to \Open in \UAS. For simplicity, we do not include the equivalent to
+verifiable openings, but this would be straightforward.
 
@@
     \begin{minipage}[t]{0.45\textwidth}
-      \procedure[linenumbering]{$\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$}{%
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
         \parm \gets \Setup(1^\secpar) \\
-        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
-        \pccomment{Abort if challenge creds belong to} \\
-        \pccomment{users with different delegation chains} \\
-        \pcreturn b^*
-      }
-      \vspace*{0.5em}
-
-      \procedure[linenumbering]{$\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
-        \pccomment{Abort if challenge sigs belong to} \\
-        \pccomment{users with different delegation chains} \\
+        (\opk,\osk) \gets \OKeyGen(\parm) \\        
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
+        b^* \gets \adv^{\mathcal{O}_{anon}}(\parm,\ipk,\opk) \\
         \pcreturn b^*
@@
     \begin{minipage}[t]{.55\textwidth}
-      \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
         \parm \gets \Setup(1^\secpar) \\
-        (D=(l,D'),\ipk_l,\st) \gets
-        \adv^{\mathcal{O}_{forge}}(\parm) \\
-        \langle\cdot,(b,\utrans)\rangle \gets
-        \langle \adv(\st),\Verify(\ipk_l,D)\rangle \\
+        (\opk,\osk) \gets \OKeyGen(\parm) \\        
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\
+        (D,L,\st) \gets
+        \adv^{\mathcal{O}_{forge}}(\parm,\ipk) \\
+        \langle \cdot,(b,\utrans)\rangle
+        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
         \pcif b = 0: \pcreturn 0 \\
@@
         \land D \subseteq \ATTR[j]): \pcreturn 1 \\    
-        (ipk_0, \lbrace (\ipk_i,\cred_i) \rbrace_{i \in [1,l]})
-        \gets ExtractChain(\utrans) \\ 
-        \pcif \exists i \in [1,l]~\suchthat~
-        \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
-        \pcind D' \not\subseteq \ATTR[\iid]) \land
-        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
-        \pcind \pcreturn 1 \\
+        h \gets RetrieveCredHandle(\osk,\utrans) \\
+        \pcif h \in L \lor h = \bot: \pcreturn 1 \\
         \pcreturn 0
@@
   }
-  \caption{Security games for delegatable anonymous credentials with selective
-    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HI,
-    CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon} \gets
-    \lbrace HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$. $\mathcal{O}_{forge}
-    \gets \lbrace HI,CI,Obtain,ObtIss,Issue,Show\rbrace$. $IssLor$ corresponds
-    to \OBTCHALb in \UAS, whereas $SigLor$ corresponds to \CHALb. Also, \OWNR
-    and \ATTR tables are essentially as in \secref{ssec:model-uas}.
-    $\ISR[\ipk]$, in this case, returns the identifier of the issuer with public
-    key \ipk. With $D = (l,D')$ we mean that the first attribute in the revealed
-    set $D$ is $l$, which denotes the level of the credential used for
-    authentication.}
-  \label{fig:model-dac}  
+  \caption{Security games for revocable anonymous credentials with selective
+    disclosure based on \cite{fhs19}. 
+    $\mathcal{O}_{anon} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
+    ReqCredHandle,LoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace HU,CU,
+    Obtain,ObtIss,Issue,Show,ReqCredHandle \rbrace$. $ReqCredHandle$ is
+    equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
+    Also, \OWNR and \ATTR tables are essentially as in \secref{ssec:model-uas}.}
+  \label{fig:model-rac}  
 \end{figure}
 
-\subsubsection{\CUASDAC Construction.} %
-We next give a construction of a delegatable AC (DAC) scheme, in the shape of
-a $(\fissue^{l,\dattrs},\feval^{l,\dattrs},\finsp^0)$-$\CUASGen^{usr-iss}$
-restriction. In a DAC scheme, all users are (or may be) also issuers. We only
-distinguish between top-level issuers, who have level $l=0$, and lower-level
-issuers, who have level $l>0$. In our \CUASDAC scheme, we assume that the first
-attribute (after the user's secret key) encodes the level of the credential.
-That is, $\attrs_1=l$, for a credential of level $l$. In addition, all users
-(i.e., with $l>0$) who want to delegate have to publicly list:
-
-\begin{enumerate}
-\item The level $l$ of the credential they delegate.
-\item Their public key \ipk.
-\item An \UAS signature proving knowledge of a credential of level $l$, and over
-  the attributes that this level-$l$ issuer is delegating.
-\item The \ipk of the parent issuer.
-\item The $\fissue^{l,\dattrs}$ function they will require for delegating.
-\item An $\feval^{l,\dattrs}$ function used to produce the signature at item 3.
-\end{enumerate}
-
-We assume that, from an \ipk, it is possible to find the corresponding issuer
-(e.g., using the previously mentioned public list). The mentioned
-$\fissue^{l,\dattrs}$ functions must follow the pattern in \figref{fig:func-restrictions}.
-Namely, the issuance function checks that the first requested attribute equals
-$l+1$, and that all requested attributes are a subset of the attribute set
-\dattrs being delegated by the level-$l$ issuer. In addition, signature
-evaluation functions $\feval^{l,\dattrs}$, also shown in \figref{fig:func-restrictions},
-must reveal the level of the credential used to produce the \UAS signature at
-item 2, as well as the set of attributes \dattrs that the level-$l$ issuer
-delegates. Verifiers can then trivially check if the set of revealed attributes
-are contained within the attributes delegatable by the parent issuer%
-\footnote{Additional checks may be added in both functions, but this is
-  the bare minimum.}.
+\subsubsection{\CUASRAC Construction.} %
+Briefly, we build a revocable anonymous credential as a $(\fissue^1,
+\feval^{\dattrs,F,V,L},\finsp^{F})$-\CUASGen restriction. The \feval is
+parameterized with a one-way and collision-resistant function $F$
+(e.g., a cryptographic hash), a string identifying the verifier $V$ and a
+list $L$ of ``revocation handles'' by $V$. 
 %
-From this high-level description, we define the algorithms of \CUASDAC:
+Since credentials in \CUASGen have two identifiers (\cidi, chosen by the issuer;
+and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally computes
+$F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval sets $\yeval^0$
+to $0$, which the verifier interprets as ``revoked credential''. Otherwise,
+it sets $\yeval^0 \gets \dattrs(\cred)$ and $\yeval^1 \gets V$; $\yeval^1$ is
+then used by $\finsp^F$ to compute $\yinsp \gets (F(\yeval^1,\cidi),
+F(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
+it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
+%
+In more detail, the algorithms are as follows:
 
 \begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.]  Runs $\parm' \gets \Setup(1^\secpar)$
-  and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
-  $\CUASGen^{usr-iss}$ construction. Returns $\parm \gets (\parm',\opk)$. Note
-  that $\finsp^0$ can be replaced by any desired opening function.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $l=0$, simply run \IKeyGen as
-  in $\CUASGen^{usr-iss}$. If $l>0$, this level-$l$ issuer picks a random
-  message $r$ and computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
-  \feval^{l,\dattrs})$, for the \dattrs set it wants to reveal -- which must
-  include the attributes to delegate, and the credential level. It then
-  publishes $(l,\ipk,\Sig,\ipk^{l-1},\fissue^{l,\dattrs},\feval^{l,\dattrs})$,
-  where $\ipk^{l-1}$ is the public key of the parent issuer,
-  $\fissue^{l,\dattrs}$ is an issuance function as described in
-  \figref{fig:func-restrictions}, and $\feval^{l,\dattrs}$ is also as in
-  \figref{fig:func-restrictions}, revealing the attributes that the issuer is
-  willing to delegate.
-% \item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
-%   also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
-%   $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
-%   credentials. Note that this does not affect security, as long as
-%   $\isk \getr \AttrSpace$.
+\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
+  \CUASGen.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from our
+  \CUASGen construction, setting $\fissue^1$ as issuance function.
+\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
+  \CUASGen construction, setting $\finsp^F$ as opening function.
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from the
+  \CUASGen construction.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
   \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  If $l>0$, the user first finds the corresponding $(l,\ipk,\Sig,\ipk^{n-1},
-  \fissue^{l,\dattrs},\feval^{l,\dattrs})$ tuple, and checks \Sig running
-  \Verify as in $\CUASGen^{usr-iss}$ (with the retrieved $\feval^{l,\dattrs}$).
-  Then, user and level-$l$ issuer run $\langle\Obtain,\Issue\rangle$ as in
-  $\CUASGen^{usr-iss}$, using $\fissue^{l,\dattrs}$ as issuance function. If
-  $l=0$, then both run $\langle\Obtain,\Issue\rangle$ as in
-  $\CUASGen^{usr-iss}$, using the \fissue function required by the issuer.
-\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle
-  \gets \langle Show(\opk,\attrs,\dattrs,\cred),
-  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of
-  $\CUASGen^{usr-iss}$.  
+  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
+  $\fissue^1$ as issuance function.
+\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
+  \attrs,\dattrs,\cred),
+  \Verify(\ipk,\dattrs) \rangle$.]
+  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
+  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
+  $\finsp^F$ as open function.
+\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
+  Gets $(\sig,\yeval)$ from the $\langle Show,\Verify\rangle$ transcript
+  \utrans, and runs \Open from \CUASGen. If $\yeval^0 \neq 0$ (i.e., the
+  signature was created by a non-revoked credential), this returns $(F(V,\cidi),
+  F(V,\cidu))$, which the verifier can add to its revocation list $L$.
 \end{description}
 
-\paragraph{Security of \CUASDAC.} %
-We state next the theorems for the security of \CUASDAC. The proofs are
+\paragraph{Security of \CUASRAC.} %
+We state next the theorems for the security of \CUASRAC. The proofs are
 available in \appref{app:related-proofs}.
 
-\begin{theorem}[Issuance anonymity of \CUASDAC]
-  If the base \CUASGen construction has issuance anonymity according to
-  \defref{def:issue-anonymity-uas}, then \CUASDAC also has issuance anonymity.
+\begin{theorem}[Issuance anonymity of \CUASRAC]
+  \todo{review}
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, and $F$ is one-way and collision-resistant,
+  then \CUASAC is an anonymous AC scheme according to \cite{fhs19}.  
 \end{theorem}
 
-\begin{theorem}[Signature anonymity of \CUASDAC]
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASDAC also has signature anonymity.
-\end{theorem}
-
-\begin{theorem}[Unforgeability of \CUASAC]
-  If the base \CUASGen construction has issuance and signature unforgeability
-  according to \defref{def:issue-forge-uas} and \defref{def:sign-forge-uas}, and
-  non-frameability according to \defref{def:frame-uas}, then \CUASAC is an
-  unforgeable AC scheme.
+\begin{theorem}[Unforgeability of \CUASRAC]
+  If the base \CUASGen construction has sign unforgeability according to
+  \defref{def:sign-forge-uas}, and $F$ is one-way and collision-resistant, then
+  \CUASRAC is an unforgeable RAC scheme.
 \end{theorem}

### 2022-07-28 prism-backend/research/gsac/relationships.tex
Updates in MPS construction.

@@
 Multimodal Private Signatures (or, rather, a close relative, see next) are
-directly implementable as a $(\fissue^1,\feval^{\yeval^1},
+directly implementable as a $(\fissue^{single,F,I,L},\feval^{\yeval^1},
 \finsp^{\ast})$-\CUASGen restriction, where $\feval^{\yeval^1}$ is any signature
@@
 \subsubsection{\CUASMPS construction.} %
-As mentioned, any $(\fissue^1,\feval^{\yeval^1},\finsp^\ast)$-restriction of
-\CUASGen with only one issuer and opener, one credential per user, and one
-attribute per credential (the user secret key), implements an MPS scheme where
-$F=\feval^{\yeval^1}$ and $G=\finsp^\ast$. The restriction to one credential per
-user, and one attribute per credential, can be done as in
-\appref{sapp:related-models-gs}. Finally, note that, in MPS, $G$ is further
-parameterized with a value $j$, which essentially is the result of applying $F$
-to the message and signer identity, and is not leaked to the opener nor any
-other third party. The equivalent in \UAS is the $\yeval^1$ value, which is
-encrypted with a single-use key pair, and is an input of \yinsp.
+As mentioned, any $(\fissue^{single,F,I,L},\feval^{\yeval^1},
+\finsp^\ast)$-restriction of \CUASGen with only one issuer and opener, one
+credential per user, and one attribute per credential (the user secret key),
+implements an MPS scheme where $F=\feval^{\yeval^1}$ and $G=\finsp^\ast$.
+With these functions, the construction is essentially as in
+\secref{ssec:related-models-gs}.
+%
+Finally, note that, in MPS, $G$ is further parameterized with a value $j$, which
+essentially is the result of applying $F$ to the message and signer identity,
+and is not leaked to the opener nor any other third party. The equivalent in
+\UAS is the $\yeval^1$ value, which is encrypted with a single-use key pair, and
+is an input of \yinsp.
 

### 2022-08-02 prism-backend/research/gsac/app-building-blocks.tex
Done with main pass after Markulf's comments.
Updating proofs.

@@
 In the previous \SBCM scheme, it is straightforward to require that the party
-running \SBCMCom proves some arbitrary claim over the messages to be signed
-(both those in committed or plaintext form), as well as over possibly extra
-auxiliary data. This can be done by having this party add a NIZK over the
-corresponding NP statement, which has later to be verified by the party running
-\SBCMSign.
+running \SBCMCom proves, in zero knowledge, some arbitrary claim over the
+messages to be signed (both those in committed or plaintext form), as well as
+over possibly extra auxiliary data. This can be done by having this party add a
+NIZK over the corresponding NP statement, which has later to be verified by the
+party running \SBCMSign.
+%
+Clearly, if the base \SBCM scheme satisfies blindness, then extending it with a
+zero-knowledge NIZK proof over the (blindly) signed messages, still maintains
+blindness (the adversary cannot distinguish which committed messages set is
+signed, in the blindness game).
 %
@@
 %
-\jdv{If needed, do the actual proof. Should essentially be a copy-paste of
+\jesus{If needed, do the actual proof. Should essentially be a copy-paste of
   that in \cite{cdl16b}...}
@@
 (a commitment of $\overline{\smsg}_b$), and forwards it to $\adv$. Finally,
-\advB outputs whatever $\adv$ outputs. Clearly, if $\adv$ wins the blindness
-game for \SBCM with non-negligible probability, so does \advB agains the hiding
+\advB outputs whatever $\adv$ outputs. If $\adv$ wins the blindness
+game for \SBCM with non-negligible probability, so does \advB against the hiding
 game of the commitment scheme.

### 2022-08-02 prism-backend/research/gsac/app-uas-proofs.tex
Some deep syntax re-writing.
Updating proofs.

@@
 
-First, we define the \SimSetup, \ExtractIssue, \ExtractSign, \IdentifyCred and
-\IdentifySig functions that are needed for some of the properties to be
-meaningful, in \figref{fig:helper-funcs}.
+\todo{Do we only need this for \fissue function?}
+First, we formally define now what do we mean with \UAS-acceptable \fissue,
+complementing the informal \defref{def:uas-acc-func}.
 
 \begin{figure}[ht!]
+  \centering  
+  \scalebox{0.9}{
+    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
+      \parm \gets \Setup(1^\secpar) \\
+      \pcfor d\in\bin: \\
+      \pcind (\upk_d,\usk_d) \gets \KeyGen(\parm) \\
+      \pcind (\st,\attrs, \lbrace (\cidi_d,\cidu_d,\cattrs_{d,i}) \rbrace_{i\in[n]})
+      \gets \adv(\st,\upk_0,\upk_1) \\
+      \yissue^* \gets \fissue(\upk_b,
+      \lbrace (\cidi_b,\cattrs_{b,i}) \rbrace_{i\in[n]},
+      \attrs) \\
+      b^* \gets \adv(\st,\yissue*) \\
+      \pcreturn b=b^*
+    }
+  }
+  \label{fig:uas-acceptable}
+  \caption{Formal definition of \UAS-acceptable \fissue functions.}
+\end{figure}
+
+Next, we define the \SimSetup, \ExtractIssue, \ExtractSign functions. \SimSetup
+(formally defined in \figref{fig:helper-funcs}).essentially replaces the
+\Setup algorithm of each NIZK with the corresponding \NIZKSimSetup algorithm,
+and returns the generated parameters along with the
+trapdoors. \ExtractIssue and \ExtractSign simply run the \Extract functions
+of the corresponding \NIZK scheme, leveraging the trapdoor produced during
+\SimSetup. Note that, due to the zero-knowledge and simulation extractability
+properties (respectively) of the underlying NIZKs, the result of \SimSetup
+is indistinguishable from that of \Setup, and the extracted values match those
+used as witnesses in the proofs.
+
+\begin{figure}[ht!]
+  \centering  
   \scalebox{0.9}{
@@
         \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace), \\
-        \pcind (\trap_{\Issue},\trap_{\Sign},\trap_{\Open})) \\
+        \pcind (\trap_{\Issue},\trap_{\Sign},\trap_{\Open}))
       }
 
-      \procedure{$\ExtractIssue(\parm,\trap,\utrans)$}{%
-        \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Issue},\cdot,
-          \cdot,\cdot)$} \\
-        \textrm{Parse \trap as $(\trap_{\Issue},\cdot,\cdot)$, and
-          \utrans as $(\Ccom,\sipk,\cred,\NIZKproof)$} \\
-        \pcif \NIZKVerify^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
-        \NIZKproof,(\Ccom,\attrs,\sipk)): \pcreturn \bot \\
-        (\usk,\scred,\attrs_{\scred}) \gets
-        \NIZKExtract^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
-        \trap_{\Issue},
-        (\Ccom,\attrs,\sipk),\NIZKproof) \\
-        \pcreturn (\usk,\attrs,\scred,\attrs_{\scred}) \\
-      }
-
-      \procedure{$\ExtractSign(\parm,\trap,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
-        \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
-          \cdot)$} \\
-        \textrm{Parse \trap as $(\cdot,\trap_{\Sign},\cdot)$, and
-          \sig as $(\NIZKproof,\ceval,\cinsp)$} \\
-        \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \gets
-          \PUBIK[\siid]$} \\
-        \pcif \NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKproof,
-        (\msg,\feval,\yeval,\Ec,\sipk,\opk)): \pcreturn \bot \\
-        (\usk,\scred,\attrs_{\scred},\yinsp,r) \gets
-        \NIZKExtract^{\NIZKRel_{\Sign}}(\NIZKcrs^{\NIZKRel_{\Sign}},
-        \NIZKtrap_{\Sign},
-        (\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk,\opk,\widetilde{\Eek}),
-        \NIZKproof) \\
-        \pcreturn (\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \\
-      }
-
-      % \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred)$}{%
-      %   \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
+      % \procedure{$\ExtractIssue(\parm,\trap,\utrans)$}{%
+      %   \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Issue},\cdot,
+      %     \cdot,\cdot)$} \\
+      %   \textrm{Parse \trap as $(\trap_{\Issue},\cdot,\cdot)$, and
+      %     \utrans as $(\Ccom,\sipk,\cred,\NIZKproof)$} \\
+      %   \pcif \NIZKVerify^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
+      %   \NIZKproof,(\Ccom,\attrs,\sipk)): \pcreturn \bot \\
+      %   (\usk,\credid,\scred,\attrs_{\scred}) \gets
+      %   \NIZKExtract^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
+      %   \trap_{\Issue},
+      %   (\Ccom,\attrs,\sipk),\NIZKproof) \\
+      %   \textrm{Let \credid be}~\suchthat~\trans[\credid] = \utrans;
+      %   \uid \gets \OWNR[\credid] \\        
+      %   \pcif \uid \in \HU \land \UK[\uid] \neq \usk: \pcreturn \bot \\
+      %   \pcelse: \\
+      %   \pcind \pcif \UK[\uid] = \bot: \UK[\uid] \gets \usk \\
+      %   \pcind \pcelse \pcif \UK[\uid] \neq \usk: \pcreturn 0 \\
+      %   \pcreturn (\uid,\usk,\credid,\scred,\attrs_{\scred}) \\
       % }
 
-      \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred,\ipk)$}{%
-        \pcreturn \SBCMVerify(\ipk,\cred,\usk,\attrs_{\cred}) \\
-      }
+      % \procedure{$\ExtractSign(\parm,\trap,\oid,\siid,\sig,\yeval,\msg,\feval)$}{%
+      %   \textrm{Parse \parm as $(\cdot,\cdot,\cdot,\cdot,\cdot,\NIZKcrs_{\Sign},
+      %     \cdot)$} \\
+      %   \textrm{Parse \trap as $(\cdot,\trap_{\Sign},\cdot)$, and
+      %     \sig as $(\NIZKproof,\ceval,\cinsp)$} \\
+      %   \textrm{Parse $\PUBOK[\oid]$ as $(\opk,\cdot)$ and let $\sipk \gets
+      %     \PUBIK[\siid]$} \\
+      %   \pcif \NIZKVerify^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKproof,
+      %   (\msg,\feval,\yeval,\Ec,\sipk,\opk)): \pcreturn \bot \\
+      %   (\usk,\scredid,\scred,\attrs_{\scred},\yinsp,r) \gets
+      %   \NIZKExtract^{\NIZKRel_{\Sign}}(\NIZKcrs^{\NIZKRel_{\Sign}},
+      %   \NIZKtrap_{\Sign},
+      %   (\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk,\opk,\widetilde{\Eek}),
+      %   \NIZKproof) \\
+      %   \pcif \exists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \\
+      %   \pcreturn (\uid,\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \\
+      %   \pcelse \textrm{\todo{Need to add \cid as explicit attribute to the
+      %       credentials (chosen by issuer) so that can bookkeep.}} \\
+      %   \pcelse \textrm{\todo{then adapt the rest}} \\
+      %   \pcind \pcelse \pcif \UK[\uid] \neq \usk: \pcreturn 0 \\
+      %   \pcreturn (\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \\
+      % }
 
-      \procedure{$\IdentifySig(\parm,\trap,\usk,\scred,\Sig)$}{%
-        \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
-        \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
-        \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trap,\trans[\cid]) \\
-        \pcind \pcif \usk = \usk': \pcreturn 1 \\
-        \pcreturn 0
-      }
+      % % \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred)$}{%
+      % %   \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
+      % % }
 
-      % \procedure{$\IdentifySig(\parm,\trap,\uid,\usk)$}{%
+      % \procedure{$\IdentifyCred(\parm,\trap,\usk,\attrs_{\cred},\cred,\ipk)$}{%
+      %   \pcreturn \SBCMVerify(\ipk,\cred,\usk,\attrs_{\cred}) \\
+      % }
+
+      % \procedure{$\IdentifySig(\parm,\trap,\usk,\scred,\Sig)$}{%
       %   \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
@@
 
+      % % \procedure{$\IdentifySig(\parm,\trap,\uid,\usk)$}{%
+      % %   \pcif \uid \in \HU: \pcreturn \usk = \UK[\uid] \\
+      % %   \pcfor \cid~\suchthat~\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot) \\
+      % %   \pcind (\usk',\cdot,\cdot,\cdot) \gets \ExtractIssue(\parm,\trap,\trans[\cid]) \\
+      % %   \pcind \pcif \usk = \usk': \pcreturn 1 \\
+      % %   \pcreturn 0
+      % % }
+
     \end{minipage}
@@
   \label{fig:helper-funcs}
-  \caption{Definition of helper functions \ExtractIssue, \ExtractSign,
-    \IdentifyCred, and \IdentifySig, for \CUASGen.}
+  \caption{Definition of helper function \SimSetup, for \CUASGen.}
 \end{figure}
@@
 \begin{proof}[\thmref{thm:issue-anonymity-uas}; Issuance anonymity of \CUASGen]
-  We prove the special case in which the adversary makes only one query to the
-  \OBTCHALb oracle. The generalization to polynomially many queries follows from
-  a standard hybrid argument.
+  % We prove the special case in which the adversary makes only one query to the
+  % \OBTCHALb oracle. The generalization to polynomially many queries follows from
+  % a standard hybrid argument.
 
-  Let $G_0=\ExpIssAnonb(1^\secpar)$. We define $G_1$ by replacing the calls to
-  \NIZKSetup in $G_0$, for the $\NIZK^{\Issue}$ and $\NIZK^{\Sign}$ systems by
-  calls to their corresponding \NIZKSimSetup. By zero-knowledgeness of the
-  NIZKs, both games are indistinguishable.
+  First, observe that, excluding the \yissue value output revealed to the issuer
+  during the interactive issuance protocol, \CUASGen essentially runs an
+  interactive signing protocol of an \SBCM scheme, augmented with a
+  zero-knowledge NIZK for $\NIZKRel_{\Issue}$. As stated in \appref{sapp:sbcm},
+  blindness of the (non-augmented) \SBCM scheme, and the zero-knowledge property
+  of the NIZK for $\NIZKRel_{\Issue}$, ensure that the challenge credentials are
+  indistinguishable between thesmselves. Concretely, we can replace the NIZK
+  proofs sent by the user by simulated proofs.
 
-  Next, we simulate the NIZK proofs produced by \Obtain within the \OBTCHALb
-  oracle and, consequently, the NIZK proofs produced by \Sign in \SIGN for
-  signatures from the challenge user and credentials. Then, we show that the
-  adversary cannot distinguish executions for $b=0$ from executions for $b=1$,
-  except with negligible probabability.
-
-  More concretely, on the one hand, let $G_1^0$ to be $G_1$, conditioned on
-  $b=0$. Concretely, the proofs sent by the challenge user $\cuid_0$ to the
-  adversarial issuer are of
-  the form $\pi^*_0 =\NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},(\UK[\cuid_0],
-  \CCRED[\cscid_0],\ATTR[\cscid_0],r),(\Ccom,\attrs,\PUBIK[\cscid_0]))$. The
-  NIZK proofs included in the signatures produced by $\cuid_0$ are defined
-  correspondingly, but for $\NIZK^{\NIZKRel_{\Sign}}$. From $G_1^0$, we define
-  $G_2^0$, but instead of using \NIZKProve, we use \NIZKSim (for both \Issue
-  and \Sign). That is, the proofs for credential requests are generated as
-  $\pi^s_0 =\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\tau,(\Ccom,\attrs,
-  \PUBIK[\cscid_0]))$. By zero-knowledge of the NIZK systems for \Issue and
-  \Sign, $G_2^0$ is indistinguishable from $G_1^0$.
-
-  On the other hand, following the same process for $G_1^1$ and $G_2^1$.
-  Concretely, for the case of the proofs at issuance time, they are of the
-  shape $\pi^s_1 =\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\tau,(\Ccom,\attrs,
-  \PUBIK[\cscid_1]))$. Note first that $\PUBIK[\cscid_1] = \PUBIK[\cscid_0]$,
-  by definition of the \OBTCHALb oracle. Hence, the produced proofs are exactly
-  the same independently on the value of the bit $b$.
-
-  Thus, $\AdvIssAnon=|\Pr\lbrack
-  \ExpIssAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpIssAnonz(1^\secpar)=1\rbrack|$.
-  As argued, $G_1$ is indistinguishable from $\ExpIssAnonb$, so
-  $\AdvIssAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
-  G_1^0(1^\secpar)=1\rbrack| \approx
-  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
-  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
-  \AdvIssAnon is negligible.
-
+  Finally, note that, to avoid trivial wins by the adversary, the issuance
+  anonymity game requires that \fissue either rejects (returns $\yissue=0$) for
+  both challenge users, or it accepts for both (returns $\yissue \neq 0$).
+  Moreover, in the latter case, since we require that \fissue functions are
+  \UAS-acceptable functions, the resulting \yissue value is hiding with respect
+  to the input arguments. Thus, adding \yissue does not allow the adversary to
+  distinguish credential issuance protocols.  
 \end{proof}

### 2022-08-02 prism-backend/research/gsac/formal-uas.tex
Moved RAC to main body, and DAC to app. Sync'ed RAC with new syntax.
Updating proofs.

@@
 \begin{description}
-\item[$\fissue: (\upk,\attrs,\lbrace (\cid_i,\cattrs_i)
-  \rbrace_{i \in [n]}) \rightarrow \yissue$.] Chosen
+\item[$\fissue: (\upk,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]},\attrs)
+  \rightarrow \yissue$.] Chosen
   by each issuer within a family of functions \famfissue, the issuance function
@@
   (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
-  values, $\yeval^0$ and $\yeval^1$, which can be used to modulate the bevahiour
-  of \finsp, and must belong in a well defined set \rngfeval. For readability,
+  values, $\yeval^0$ and $\yeval^1$. $\yeval^0$ is output directly alongside the
+  signature,  both can in addition be used to modulate the behaviour of
+  \finsp, and must belong in a well defined set \rngfeval. For readability,
   we write $\Yeval = (\yeval^0,\yeval^1)$.
@@
 an opener to change the chosen function. In the sequel, we restrict to
-\UAS-acceptable functions, which we will also use to give \CUASGen restrictions.
-Both concepts are defined next.
-
-% \begin{definition}{(\UAS-acceptable functions)}
-%   \label{def:uas-acc-func}
-%   We say that a \fissue (similarly, \feval or \finsp) function chosen from some
-%   family \famfissue (similarly, \famfeval or \famfinsp) is \UAS-acceptable if it
-%   is one-way with respect to $(\upk,\usk)$. That is, given the output of \fissue
-%   (similarly, \feval or \finsp), it is at least computationally unfeasible to
-%   recover the $(\upk,\usk)$ value used to produce it.
-% \end{definition}
+\UAS-acceptable functions, defined as follows:
+
+\begin{definition}{(\UAS-acceptable functions)}
+  \label{def:uas-acc-func}
+  We say that a \fissue function chosen from some family \famfissue is
+  \UAS-acceptable if its outputs are hiding with respect to its \upk and
+  $\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]}$ inputs.
+  %
+  Similarly, a \feval function chosen from some family \famfeval is
+  \UAS-acceptable if the $\yeval^1$ component of its output is hiding with
+  respect to its \upk and $\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]}$ inputs.
+\end{definition}
+
+That is, at a high level we require that \fissue and \feval functions do not
+reveal anything about the signer. \todo{Since the concept is quite intuitive, we
+  defer the formal definition to \appref{app:XXX}}. We give in
+\secref{ssec:generic-construction-uas}
+a generic \CUASGen construction that assumes \UAS-acceptable functions. Next, we
+define the concept of \CUASGen restrictions. Briefly, these are special cases of
+our generic construction that target a concrete variant of the utility-privacy
+tradeoff by defining concrete \fissue, \feval and \finsp functions. Security of
+\CUASGen implies security of its restrictions, as long as the chosen functions
+are \CUASGen-acceptable.
 
@@
 \end{definition}
-
-% To summarize the previous, we depict in \figref{fig:uas-signature} the structure
-% of an \UAS signature, including its main components and how they enable the
-% previously stated generalization claims.
-
-% \begin{figure}[ht!]
-%   \centering
-%   %\input{figures/uas-signature.tex}
-%   \caption{Structure of an \UAS signature.}
-%   \label{fig:uas-signature}
-% \end{figure}
 
@@
           \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,\feval) \\
-          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\scid,\msg) \\
+          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],\scid,\msg) \\
           \SIG[\uid] \gets \SIG[\uid] \cup
@@
           \pcif \iid \notin \CI: \pcreturn \bot \\
-          \pcif \CRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
+          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor
+          \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
           \pcif \exists i\in[n]~\suchthat~
@@
 \begin{description}
-\item[$\NIZKRel_{\Issue}$:] For NIZK proofs at issuance time. Requires that the
-  owner commits to, and proves knowledge of, \usk. It also requires that any
+\item[$\NIZKRel_{\Issue}$:] For NIZK proofs at issuance time. Requires users to
+  prove knowledge of \usk and the related \upk. It also requires that any
   additional credential supporting the request be a valid credential (signed by
-  some issuer) and bound to \usk. Finally, it also enforces the
-  corresponding \fissue policy.
+  some issuer) and bound to \upk, and enforces the corresponding \fissue policy.
 \item[$\NIZKRel_{\Sign}$:] For NIZK proofs at signing time. Ensures that
   signatures ``encode'' the correct signature evaluation and opening values, and
-  that any credential used to create the signature is bound to the same \usk.
+  that any credential used to create the signature is bound to the same \upk.
 \item[$\NIZKRel_{\Open}$:] For NIZK proofs at opening time. Ensures that the
@@
   }
-  \caption{CS specification of the NP relations used in \CUASGen.
-  \todo{Is $\C = \CCommit(\usk;r)$ at Issue needed now that \upk is added?}}
+  \caption{CS specification of the NP relations used in \CUASGen.}
   \label{fig:nizkrels}
@@
 From them, we build \CUASGen as follows.
-\todo{Check if \SSetup etc is still needed...}
 
@@
 building blocks. It runs $\Cparm \gets \CSetup(\secpar)$, $\SBCMparm \gets
-\SBCMSetup(\secpar)$, $\Sparm \gets \SSetup(\secpar)$, $\Eparm \gets
-\ESetup(\secpar)$, $\NIZKcrs_{\Issue} \gets \NIZKSetup^{\NIZKRel_{\Issue}}
-(\secpar)$, $\NIZKcrs_{\Sign} \gets \NIZKSetup^{\NIZKRel_{\Sign}}(\secpar)$, and
-$\NIZKcrs_{\Open} \gets \NIZKSetup^{\NIZKRel_{\Open}}(\secpar)$. Return $
-(\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},
-\NIZKcrs_{\Open})$. % Many of these parameter setup algorithms can
-% actually be run by separate entities. For simplicity of exposition, we bundle
-% them together here.
+\SBCMSetup(\secpar)$, $\Eparm \gets \ESetup(\secpar)$, $\NIZKcrs_{\Issue} \gets
+\NIZKSetup^{\NIZKRel_{\Issue}}(\secpar)$, $\NIZKcrs_{\Sign} \gets
+\NIZKSetup^{\NIZKRel_{\Sign}}(\secpar)$, and $\NIZKcrs_{\Open} \gets
+\NIZKSetup^{\NIZKRel_{\Open}}(\secpar)$. Return $(\Cparm,\SBCMparm,\Eparm,
+\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Open})$.
 
@@
 \paragraph{$(\upk,\usk) \gets \KeyGen(\parm)$.} %
-Each user first parses \parm as $(\cdot,\SBCMparm,
-\cdot,\cdot,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\SBCMvk,\SBCMsk) \gets
-\SBCMKeyGen(\SBCMparm)$, $\upk \gets (\parm,\SBCMvk)$, $\usk \gets \SBCMsk$,
-and returns $(\upk,\usk)$.
+Each user first parses \parm as $(\cdot,\SBCMparm,\cdot,\cdot,\cdot,\cdot)$.
+Then, runs $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$, $\upk \gets (\parm,
+\SBCMvk)$, $\usk \gets \SBCMsk$, and returns $(\upk,\usk)$.
 
 \paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
-Each opener first parses \parm as $(\cdot,\cdot,
-\cdot,\Eparm,\cdot,\cdot,\cdot,\cdot)$. Then, runs $(\Svk,\Ssk) \gets \SKeyGen
-(\Sparm)$, $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, $\sig_{\finsp} \gets \SSign
-(\Ssk,\finsp)$, $\opk \gets (\Sparm,\Svk,\Eek,\finsp,\sig_{\finsp})$, and $\osk
-\gets (\Ssk,\Edk)$.
+Each opener parses \parm as $(\cdot,\cdot,\Eparm,\cdot,\cdot,\cdot)$.
+Then, runs $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, and sets, $\opk \gets (\Eek,
+\finsp)$, and $\osk \gets \Edk$.
 
@@
 A user willing to become an issuer just sets $\ipk \gets (\upk,\fissue)$, and
-returns \ipk.
+publishes \ipk.
 
@@
 In addition, the user proves correct computation of the \fissue function set by
-the issuer based on the $\cred_i$ credentials and its user key pair.
+the issuer based on the $\cred_i$ credentials and its user public key.
 This is essentially achieved through an execution of an \SBCM interactive
@@
 evaluated by the user, but depends on the \cidi value chosen by the issuer, the
-issuer first needs to send \cidi to the user.
-Then both issuer and user interact to produce the \SBCM signature, where the
+issuer first needs to send \cidi.
+Then both interact to produce the \SBCM signature, where the
 user runs $\SBCMCom^{\NIZKRel_{\Issue}}(\ipk,\usk,(\cid,\attrs),\lbrace (\cid_i,
@@
 \utrans)$, where \yissue is the output of \fissue, and \utrans is the
-communication transcript, which is a $(\Ccom,(\cid,\attrs),\lbrace
-\ipk_i \rbrace_{i\in[n]},\cred,\pi)$ tuple.
+communication transcript of the signing protocol.% , which is a $(\Ccom,(\cid,\attrs),\lbrace
+% \ipk_i \rbrace_{i\in[n]},\cred,\pi)$ tuple (see \appref{sapp:sbcm} for details).
 
@@
 % 
-The user first evaluates $\Yeval = (\yeval^0,\yeval^1) \gets \feval (\usk,
-\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$.
-Then, parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
-$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$
-(this step may be cached), to compute $\yinsp \gets \finsp((\yeval^0,
-\yeval^1),\usk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$, and encrypts
+The user first evaluates $\Yeval = (\yeval^0,\yeval^1) \gets \feval (\upk,
+\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$. Then, parses \opk as $(\Eek,
+\finsp)$, computes $\yinsp \gets \finsp((\yeval^0,\yeval^1),\upk,
+\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$, and encrypts
 \yinsp by running $\cinsp \gets \EEnc(\Eek,\yinsp; r')$ for some fresh
@@
   \label{thm:issue-anonymity-uas}
-  If the NIZK systems used for $\NIZKRel_{\Issue}$ and $\NIZKRel_{\Sign}$ are
-  zero-knowledge, our \CUASGen construction satisfies issuance anonymity as
-  defined in \defref{def:issue-anonymity-uas}.
+  If the \SBCM scheme is blinding, the NIZK system used for $\NIZKRel_{\Issue}$ 
+  is zero-knowledge, and \fissue is a \CUASGen-acceptable function, our \CUASGen
+  construction satisfies issuance anonymity as defined in
+  \defref{def:issue-anonymity-uas}.
 \end{theorem}

### 2022-08-02 prism-backend/research/gsac/relationships.tex
Updating proofs.

@@
         & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
-        & \fissue^{single,F,I,L}(\upk,\cdot,\cdot) \coloneqq
-          \pcif F(I,\upk) \in L~\pcreturn 0;~\pcelse \pcreturn F(I,\upk)
+        & \fissue^{single,F,I}(\upk,\cdot,\cdot) \coloneqq \pcreturn F(I,\upk)
           \nonumber \\
@@
 \subsubsection{\CUASGS construction.} %
-We show that the $(\fissue^{single,F,IL},\feval^0,\finsp^{\upk})$-\CUASGen
+\todo{Clarify how $\fissue^{single,F,I}$ works! This is also common with other
+  constructions...}
+We show that the $(\fissue^{single,F,I},\feval^0,\finsp^{\upk})$-\CUASGen
 restriction, is a secure group signature scheme according to \cite{bsz05}.
-Observe that the $\fissue^{single,F,I,L}$ function is further parameterized with
+Observe that the $\fissue^{single,F,I}$ function is further parameterized with
 a list $L$ maintained by the issuer and must be fetched by users prior to
@@
 \item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs \Setup from \CUASGen,
-  and one instance of \KeyGen and \ISet with $\fissue^{single,F,I,L}$ (both for
+  and one instance of \KeyGen and \ISet with $\fissue^{single,F,I}$ (both for
   the same user, who will be the only issuer in the GS scheme) and \OKeyGen.
@@
 it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
+Note that, in the $\feval^{\dattrs,F,V,L}$ function, $L$ is a sort of variable.
+However, each verifier $V$ may just update its own list with some reasonable
+frequency (e.g., daily), and use a pre-compiled version of
+$\feval^{\dattrs,F,V,L}$ in which $L$ is actually a constant.
 %
@@
 Multimodal Private Signatures (or, rather, a close relative, see next) are
-directly implementable as a $(\fissue^{single,F,I,L},\feval^{\yeval^1},
+directly implementable as a $(\fissue^{single,F,I},\feval^{\yeval^1},
 \finsp^{\ast})$-\CUASGen restriction, where $\feval^{\yeval^1}$ is any signature
@@
 \subsubsection{\CUASMPS construction.} %
-As mentioned, any $(\fissue^{single,F,I,L},\feval^{\yeval^1},
+As mentioned, any $(\fissue^{single,F,I},\feval^{\yeval^1},
 \finsp^\ast)$-restriction of \CUASGen with only one issuer and opener, one

### 2022-08-05 prism-backend/research/gsac/app-building-blocks.tex
Updating proofs.

@@
 \begin{figure}[ht!]
+  \scalebox{0.9}{  
     \begin{minipage}[t]{\textwidth}
@@
     \end{minipage}
+  }
   \label{fig:euf-game}
@@
     \end{minipage}
+  }
   \label{fig:indcca2-game}
@@
 \begin{figure}[ht!]
+  \scalebox{0.9}{
     \begin{minipage}[t]{0.5\textwidth}
@@
     \end{minipage}
+  }
   \label{fig:com-games}
@@
     \end{minipage}
+  }
   \label{fig:nizk-games}
@@
 \begin{figure}[ht!]
+  \scalebox{0.9}{
     \begin{minipage}[t]{\textwidth}
@@
     \end{minipage}
+  }
   \label{fig:sbm-games}
@@
         (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
-      (\overline{\smsg}_0,\overline{\smsg}_1,\smsg) \gets
-      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
-      \csig \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg}_b,\smsg),
-      \SBCMSign(\SBCMsk,\smsg) \rangle \\
-      b^* \gets \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk,
-      \csig) \\
-      \pcif b = b^*: \pcreturn 1 \\
-      \pcreturn 0
+        % (\st,\overline{\smsg}_0,\overline{\smsg}_1,\smsg) \gets
+        % \adv(\SBCMvk,\SBCMsk) \\
+        b^* \gets %\langle \SBCMCom(\SBCMvk,\overline{\smsg}_b,\smsg),
+        \adv^{\langle COM(\SBCMvk,\overline{\smsg}_{\bin},\smsg),\cdot\rangle}(\SBCMsk) \\
+        \pcreturn b = b^*
       }
     \end{minipage}
+  }
   \label{fig:sbcm-games}
-  \caption{Games for \SBCM schemes.}
+  \caption{Games for \SBCM schemes. The $COM$ oracle in \ExpSBCMBlindb receives
+    $\overline{\smsg}_0$ and $\overline{\smsg}_1$, and runs a $\langle
+    \SBCMCom(\SBCMvk,\overline{\smsg}_b,\smsg),\cdot\rangle$ protocol with the
+    adversary acting as signer.}
 \end{figure}
@@
 %
-Clearly, if the base \SBCM scheme satisfies blindness, then extending it with a
+If the base \SBCM scheme satisfies blindness, then extending it with a
 zero-knowledge NIZK proof over the (blindly) signed messages, still maintains
-blindness (the adversary cannot distinguish which committed messages set is
+blindness (the adversary cannot distinguish which committed message set is
 signed, in the blindness game).

### 2022-08-05 prism-backend/research/gsac/app-uas-proofs.tex
Updating proofs.

@@
       \parm \gets \Setup(1^\secpar) \\
-      \pcfor d\in\bin: \\
-      \pcind (\upk_d,\usk_d) \gets \KeyGen(\parm) \\
-      \pcind (\st,\attrs, \lbrace (\cidi_d,\cidu_d,\cattrs_{d,i}) \rbrace_{i\in[n]})
-      \gets \adv(\st,\upk_0,\upk_1) \\
-      \yissue^* \gets \fissue(\upk_b,
-      \lbrace (\cidi_b,\cattrs_{b,i}) \rbrace_{i\in[n]},
-      \attrs) \\
+      (\upk,\usk) \gets \KeyGen(\parm) \\
+      (\st,\attrs, \lbrace (\cidi,\cidu,\cattrs_i) \rbrace_{i\in[n]})
+      \gets \adv(\upk) \\
+      \pcif b=0:
+      \yissue^* \gets \fissue(\upk,\lbrace (\cidi,\cattrs_i)
+      \rbrace_{i\in[n]},\attrs) \\
+      \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
       b^* \gets \adv(\st,\yissue*) \\
@@
 Next, we define the \SimSetup, \ExtractIssue, \ExtractSign functions. \SimSetup
-(formally defined in \figref{fig:helper-funcs}).essentially replaces the
+(formally defined in \figref{fig:helper-funcs}) essentially replaces the
 \Setup algorithm of each NIZK with the corresponding \NIZKSimSetup algorithm,
@@
 \begin{proof}[\thmref{thm:issue-anonymity-uas}; Issuance anonymity of \CUASGen]
-  % We prove the special case in which the adversary makes only one query to the
-  % \OBTCHALb oracle. The generalization to polynomially many queries follows from
-  % a standard hybrid argument.
+  We prove the special case in which the adversary makes only one query to the
+  \OBTCHALb oracle. The generalization to polynomially many queries follows
+  from a standard hybrid argument.
 
-  First, observe that, excluding the \yissue value output revealed to the issuer
-  during the interactive issuance protocol, \CUASGen essentially runs an
-  interactive signing protocol of an \SBCM scheme, augmented with a
-  zero-knowledge NIZK for $\NIZKRel_{\Issue}$. As stated in \appref{sapp:sbcm},
-  blindness of the (non-augmented) \SBCM scheme, and the zero-knowledge property
-  of the NIZK for $\NIZKRel_{\Issue}$, ensure that the challenge credentials are
-  indistinguishable between thesmselves. Concretely, we can replace the NIZK
-  proofs sent by the user by simulated proofs.
+  We start from the \ExpIssAnonb, as defined in \figref{fig:exp-uas-anonb}.
 
-  Finally, note that, to avoid trivial wins by the adversary, the issuance
-  anonymity game requires that \fissue either rejects (returns $\yissue=0$) for
-  both challenge users, or it accepts for both (returns $\yissue \neq 0$).
-  Moreover, in the latter case, since we require that \fissue functions are
-  \UAS-acceptable functions, the resulting \yissue value is hiding with respect
-  to the input arguments. Thus, adding \yissue does not allow the adversary to
-  distinguish credential issuance protocols.  
+  Game 1: We simulate the NIZK proof corresponding to $\NIZKRel_{\Issue}$ that
+  the \OBTCHALb oracle produces when queried by \adv. The zero-knowledge
+  property of the NIZK system ensures that game 1 is indistinguishable from
+  the original experiment.
+
+  Game 2: In queries to \OBTCHALb, before simulating the NIZK proof, we replace
+  the produced \yissue value with a random element from \rngfissue. Since
+  \fissue is a \UAS-acceptable function, game 2 is indistinguishable from game
+  1.
+
+  From an adversary \adv~against Game 2, we can build an adversary \advB against
+  \SBCM's blindness property. The simulation that
+  \advB does is straightforward. \advB runs Game 2 for \adv, randomly picking
+  a number $q < n$, where $n$ is the number of users that \adv~creates via
+  \UGEN, and assigning to the $q$-th user the $(\SBCMvk,\SBCMsk)$ key pair
+  that \advB receives in its blindness game. Then, when \adv~makes a query
+  to its \OBTCHALb oracle, if the chosen issuer is the $q$-th user, \advB
+  forwards \adv's messages to its own $\langle COM(\SBCMvk,
+  \overline{\smsg}_{\bin},\smsg),\cdot\rangle$ oracle. Finally, \advB outputs
+  whatever \adv~does. Note that, since in Game 2 we replace the \yissue value
+  with a random value, and simulate the $\NIZKRel_{\Issue}$ proof, \adv~is not
+  receiving information about the blindly signed messages beyond what \advB
+  forwards from its own oracle. Thus, if \adv~wins in its game, \advB wins in
+  its blindness game. However, since \advB has to guess the correct user
+  that \adv~will use as issuer in its \OBTCHALb oracle, we have a $1/n$ security
+  loss, where $n$ is the total number of users created by \adv.
+  %
+  \qed
 \end{proof}
@@
   adversary is $(\csig_0,\yeval) \gets \Sign(\PRVUK[\cuid_0],\PUBOK[\oid],
-  \CRED[\scid_0],\msg,\feval)$, where $\csig_0 = (\pi_0,\Ec_{\yinsp})$, with
+  \CRED[\scid_0],\msg,\feval)$, where $\csig_0 = (\pi_0,\cinsp)$, with
   $\pi_0 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
-  \ceval,\cinsp,\PUBIK[\scid_0],\widetilde{\Eek},\PUBOK[\oid]),(\PRVUK[\cuid_0],
-  \CRED[\scid_0],\attrs_{\scid_0},\yeval^1,\yinsp,r,r'))$, $\ceval = \EEnc
-  (\widetilde{\Eek},\yeval^1;r)$, and $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$.
+  \cinsp,\lbrace\PUBIK[\scid_{i,0}]\rbrace_{i\in[n]},\PUBOK[\oid]),
+  (\PUBUK[\cuid_0],\PRVUK[\cuid_0],\lbrace (\scid_{i,0},\attrs_{i,0},
+  \CRED[\scid_{i,0}]) \rbrace_{i\in[n]},\yeval^1,\yinsp,r,r'))$, and $\cinsp =
+  \EEnc(\PUBOK[\oid],\yinsp;r')$, for some random $r,r'$ and $n \ge 0$.
   % 
@@
   \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
-  \ceval,\cinsp,\PUBIK[\scid_0],\PUBOK[\oid]))$. By zero-knowledgeness
-  of $\NIZK^{\Sign}$, $G_1^0$ is indistinguishable from $G_0^0$.
+  \cinsp,\lbrace\PUBIK[\scid_{i,0}]\rbrace_{i\in[n]},\PUBOK[\oid]))$. By
+  zero-knowledgeness of $\NIZK^{\Sign}$, $G_1^0$ is indistinguishable from
+  $G_0^0$.
 
@@
   sent to the adversary is $(\csig_1,\yeval) \gets \Sign(\PRVUK[\cuid_1],
-  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,\ceval,
+  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,
   \cinsp)$, with $\pi_1 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
-  (\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
-  \PUBOK[\oid]),(\PRVUK[\cuid_1],\CRED[\scid_1],\attrs_{\scid_1},\yeval^1,
-  \yinsp,r,r'))$, $\ceval = \EEnc(\widetilde{\Eek},\yeval^1;r)$, and
-  $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$. As before, build $G_1^1$ from
-  $G_0^1$, simulating $\pi_1$. That is, in $G_1^1$, $\csig_1 = (\pi_1^s,\ceval,
-  \cinsp)$, where $\pi^s_1 = \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
-  \NIZKtrap,(\msg,\feval,\yeval,\ceval,\cinsp,\PUBIK[\scid_1],\widetilde{\Eek},
-  \PUBOK[\oid]))$. Again, by zero-knowledge of $\NIZK^{\Sign}$, $G_1^1$ is
-  indistinguishable from $G_0^1$. Note also that $G_1^1$ and $G_1^0$ are
-  indistinguishable, due to the IND-CCA property of the encryption scheme
-  (so, the \ceval values in $\csig_0$ and $\csig_1$ are indistinguishable),
-  in the  challenge oracle used in the anonymity game, we restrict to
-  $\PUBIK[\scid_0] = \PUBIK[\scid_1]$, and the respective \cinsp values encrypt
-  the same \yinsp value (and, otherwise, \adv~is not allowed to open it).
+  (\msg,\feval,\yeval,
+  \cinsp,\lbrace\PUBIK[\scid_{i,1}]\rbrace_{i\in[n]},\PUBOK[\oid]),
+  (\PUBUK[\cuid_1],\PRVUK[\cuid_1],\lbrace (\scid_{i,1},\attrs_{i,1},
+  \CRED[\scid_{i,1}]) \rbrace_{i\in[n]},\yeval^1,\yinsp,r,r'))$, and
+  $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$, for random $r,r'$ and $n \ge 0$. As
+  before, build $G_1^1$ from $G_0^1$, simulating $\pi_1$. That is, in $G_1^1$,
+  $\csig_1 = (\pi_1^s,\ceval,\cinsp)$, where $\pi^s_1 =
+  \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
+  \cinsp,\lbrace\PUBIK[\scid_{i,1}]\rbrace_{i\in[n]},\PUBOK[\oid]))$. Again, by
+  zero-knowledge of $\NIZK^{\Sign}$, $G_1^1$ is
+  indistinguishable from $G_0^1$.
+
+  Note that, at this point, $G_1^1$ and $G_1^0$ are indistinguishable.
+  Concretely, the challenge signatures they produce have the structure $\Sig_b =
+  ((\pi_b,\cinsp),\yeval)$ where, to prevent trivial wins, \yeval is enforced
+  (in the \SIGN oracle) to be the same for both challenge users, and \cinsp
+  either encrypts the same value for both users, or \adv~cannot query the \OPEN
+  oracle. \SIGN also enforces that $\PUBIK[\scid_0] = \PUBIK[\scid_1]$. Finally,
+  the proofs $\pi_b$ are simulated, and thus reveal no information about the
+  signer keys or credentials.
 
@@
 \begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
-  We show that the probability that \fissue outputs $0$ is negligible, as well
-  as the probability that the extracted \usk is not the one that was used to
-  request some of the credentials employed to obtain the credential specified by
-  the adversary.
+  We show that the probability that \fissue outputs a wrong $\yinsp$ value is
+  negligible, as well as the probability that the credential identifier does not
+  belong to an existing (honest or corrupt) user.
+
+  Observe that the adversary is required to output a credential identifier for
+  which associated entries in \trans and \CRED exist; moreover, if such a
+  credential was produced by an issuer, we must have access to those entries, as
+  issuers are assumed to be honest in this game.
   %
-  For this purpose, we define two games, $G_0=\ExpForgeIssue$, and $G_1$, which
-  is exactly the same, but where, within the \Setup algorithm, we replace
-  $\NIZKSetup^{\Issue}$ with $\NIZKSimSetup^{\Issue}$. Due to zero-knowledgeness
-  of $\NIZK^{\NIZKRel_{\Issue}}$, both games are indistinguishable.
+  Since we can access $\trans[\cid] = (\yissue,\utrans)$, and \utrans contains
+  a NIZK proof $\NIZKproof_{\Issue}$ proving knowledge by the user of a witness
+  in $\NIZKRel_{\Issue}$, which is simulation extractable, \ExtractIssue
+  produces a tuple $(\upk,\usk,\lbrace (\cid_i,\attrs_i,\cred_i)
+  \rbrace_{i\in[n]}$.
+  %
+  From the fact that issuers are honest, we know that $\ATTR[\cid]$ must match
+  the attribute set \attrs used by user and issuer in the issuance protocol.
+  Thus, from  soundness of the NIZK system, the $(\upk,\lbrace (\cid_i,\attrs_i,
+  \cred_i) \rbrace_{i\in[n]}$ values within the extracted tuple, along with
+  $\ATTR[\cid] = \attrs$ must make \fissue output \yissue, except with
+  negligible probability. Moreover, soundness of the NIZK system also implies
+  that all credentials are bound to the same \usk, which is associated to the
+  extracted \upk.
 
-  Now, observe that the adversary is required to output a credential
-  identifier for which associated entries in \trans and \CRED exist; moreover,
-  if such a credential was produced by an issuer, we must have access to those
-  entries, as issuers are assumed to be honest.
-  %
-  Then, given that $\NIZKRel_{\Issue}$ is knowledge extractable (which is implied
-  by simulation-extractability), in game $G_1$
-  we can apply the \NIZKExtract function, which produces a tuple $(\usk,\scred,
-  \attrs_{\scred})$ from $\utrans = (\Ccom,\attrs,\sipk,\cred,\NIZKproof)$.
-  %
-  Since \NIZKproof is accepted by \ExtractIssue, from the soundness of \NIZK, we
-  know that all $\cred \in \scred$ are valid signatures over \usk, and their
-  respective $\attrs_{\cred}$. Thus, \IdentifyCred returns $1$ for all $(\usk,
-  \attrs_{\cred},\cred)$ tuples. That is, all the credentials in \scred given
-  to \fissue belong to the same user, who is the owner of \usk.
-  %
-  Finally, since issuers are honest, we know that $\ATTR[\cid] = \attrs$ and,
-  consequently, $\fissue(\usk,\scred,\ATTR[\cid]) = \fissue(\usk,\scred,\attrs)
-  = 1$, due to the soundness of \NIZK.
-  %
+  Finally, suppose that the extracted \upk does not belong to a \uid in
+  $\HU \cup \CU$. Then, the produced credential is a forgery. \todo{How to
+    extract the forgery in this case?? I think that expanding the definition
+    so that it requires \adv~to produce a valid signature would make things
+    much easier...}
   \qed
@@
 \begin{proof}[\thmref{thm:sign-forge-uas}; Signature unforgeability of \CUASGen]
-  As in \thmref{thm:issue-forge-uas}, we define two games, $G_0=\ExpForgeSign$,
-  and $G_1$, which is exactly the same but where, within the \Setup algorithm,
-  we replace $\NIZKSetup^{\Sign}$ with $\NIZKSimSetup^{\Sign}$. After
-  zero-knowledgeness of $\NIZK^{\Sign}$, both games are indistinguishable.
-  %
-  Next, we show that an adversary winning $G_1$ can be used to break the
+  We show that an adversary \adv~winning \ExpForgeSign can be used to break the
   one-more unforgeability property of \SBCM.
 
-  If the verification at line 4 holds, then $(\msg,\feval,\yeval,\ceval,
-  \cinsp,\sipk,\opk,\widetilde{\Eek}) \in \NIZKLang^{\Sign}$. Then:
+  If the verification at line 4 of \ExpForgeSign holds, then $(\msg,\feval,
+  \yeval,\cinsp,\sipk,\opk,\widetilde{\Eek}) \in \NIZKLang^{\Sign}$. Then:
   %
@@
   Simulation extractability of $\NIZK^{\Sign}$ thus ensures that $\cinsp =
-  \EEnc(\Eek,\yinsp)$, and since the $(\yinsp,\iproof)$ is generated honestly at
+  \EEnc(\Eek,\yinsp)$, and since $(\yinsp,\iproof)$ is generated honestly at
   line 5, then \yinsp is the correct decryption of \cinsp, and  correctness of
@@
   \begin{itemize}
-  \item $\yeval^0 = \yeval$, where $(\yeval^0,\cdot) = \feval(\usk,\scred,
-    \msg)$, and $\yeval$ is as output by \adv~at step 2.    
-  \item $\tyeval^1 = \yeval^1$, where $(\cdot,\yeval^1) = \feval(\usk,\scred,
-    \msg)$, and $\tyeval^1$ is as extracted by \ExtractSign at line 7.
+  \item $\yeval^0 = \yeval$, where $(\yeval^0,\cdot) = \feval(\upk,\lbrace
+    (\cid_i,\attrs_i) \rbrace_{i\in[n]},\msg)$, and $\yeval$ is as output by
+    \adv~at step 2.    
+  \item $\tyeval^1 = \yeval^1$, where $(\cdot,\yeval^1) = \feval(\upk,\lbrace
+    (\cid_i,\attrs_i)\rbrace_{i\in[n]},\msg)$, and $\tyeval^1$ is as extracted
+    by \ExtractSign at line 7.
   \end{itemize}
 
-  Thus, the probability of \adv~winning at line 9 is $0$.
+  Thus, the probability of \adv~winning at line 9 is negligible, due to
+  simulation extractability of $\NIZK^{\Sign}$.
 
@@
   \ExtractSign match the evaluation of \feval. Thus, simulation extractability
-  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\usk,\scred,\msg)
-  = \yinsp$ and, also, that \yinsp matches the $\yinsp'$ value extracted by
-  \ExtractSign. Thus, the probability of \adv~winning at line 10 is $0$.
+  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\upk,\lbrace
+  (\cid_i,\attrs_i)\rbrace_{i\in[n]},\msg) = \yinsp$ and, also, that \yinsp
+  matches the $\yinsp'$ value extracted by \ExtractSign. Thus, the probability
+  of \adv~winning at line 10 is negligible due to simulation extractability
+  of $\NIZK^{\Sign}$.
 
   \paragraph{(d) All {\cred}s are bound to the same \usk.} %
-  $\NIZKRel^{\Sign}$ includes a condition that $\forall \cred \in \scred,
-  \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1$. Thus, simulation
+  $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
+  \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
   extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all

### 2022-08-05 prism-backend/research/gsac/formal-uas.tex
Updating proofs.

@@
 \label{sec:formal-uas}
+
+\jesus{Adding a \uid into \HU or \CU within an oracle that is executed by end
+  users in the real world is a bit weird if not clarified. Some arguments may
+  be possible.}
 
@@
 
-\begin{definition}{(\UAS-acceptable functions)}
+\begin{definition}{(\UAS-acceptable \fissue functions)}
   \label{def:uas-acc-func}
   We say that a \fissue function chosen from some family \famfissue is
-  \UAS-acceptable if its outputs are hiding with respect to its \upk and
-  $\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]}$ inputs.
-  %
-  Similarly, a \feval function chosen from some family \famfeval is
-  \UAS-acceptable if the $\yeval^1$ component of its output is hiding with
-  respect to its \upk and $\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]}$ inputs.
+  \UAS-acceptable if, conditioned on it returning a non-zero value, the
+  value it produces is indistinguishable from random.
+  % %
+  % Similarly, a \feval function chosen from some family \famfeval is
+  % \UAS-acceptable if the $\yeval^1$ component of its output is hiding with
+  % respect to its \upk and $\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]}$ inputs.
 \end{definition}
@@
 
-        \procedure{$\SIGN(\uid,\oid,\scid=\lbrace\cid_i\rbrace_{i\in[n]},\msg,
+        \procedure{$\SIGN(\oid,\scid=\lbrace\cid_i\rbrace_{i\in[n]},\msg,
           \feval)$}{%
+          \uid \gets \OWNR[\scid] \\
           \pcif \uid \notin \HU \lor \feval \notin \famfeval: \pcreturn \bot \\
@@
 
-        \procedure{$\CHALb(\cuid_{0,1},\oid,\cscid_{0,1}=$\\
-          \hspace*{5em}$\lbrace (\ccid_{0,i},\ccid_{1,i})
+        \procedure{$\CHALb(\oid,\cscid_{0,1}=
+          \lbrace (\ccid_{0,i},\ccid_{1,i})
           \rbrace_{i\in[n]},\msg,\feval)$}{%
+          \pcfor d\in\bin: \cuid_d \gets \OWNR[\cscid_d] \\
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
@@
         \pcif \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
-        \rbrace_{i\in[n]}) = \yissue:
+        \rbrace_{i\in[n]}) \neq \yissue:
         \pcreturn 1 \\
-        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
+        \pcif \nexists \uid~\suchthat~\PUBUK[\uid]=\upk \land
+        \uid \in \HU \cup \CU: \pcreturn 1 \\
+%        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
         \pcreturn 0
@@
 
+\todo{Need to make the $\cid_i$s explicity in the \SBCMVerify clauses of
+  $\NIZK^{\Issue}$ and $\NIZK^{\Sign}$.}
 \begin{figure}[ht!]
@@
 issuer runs $\SBCMSign^{\NIZKRel_{\Issue}}(\isk,(\cid,\attrs),\lbrace\ipk_i
-\rbrace_{i\in[n]})$. The credential \cred produced by the user is the result of
+\rbrace_{i\in[n]})$. Observe that, within this protocol, the user sends a NIZK
+proof $\NIZKproof_{\Issue}$ ensuring that it knows a valid witness $(\upk,\usk,
+\lbrace (\cid_i,\cattrs_i,\cred_i)\rbrace_{i \in [n]},r)$ for the relation
+$\NIZKRel_{\Issue}$. The credential \cred produced by the user is the result of
 the interactive signing protocol, whereas the issuer produces $(\yissue,
@@
   If the \SBCM scheme is blinding, the NIZK system used for $\NIZKRel_{\Issue}$ 
-  is zero-knowledge, and \fissue is a \CUASGen-acceptable function, our \CUASGen
+  is zero-knowledge, and \fissue is a \UAS-acceptable function, our \CUASGen
   construction satisfies issuance anonymity as defined in

### 2022-08-08 prism-backend/research/gsac/app-uas-proofs.tex
Updated proofs for sign-unforgeability, and non-frameability.

@@
   If the verification at line 4 of \ExpForgeSign holds, then $(\msg,\feval,
-  \yeval,\cinsp,\sipk,\opk,\widetilde{\Eek}) \in \NIZKLang^{\Sign}$. Then:
+  \yeval,\cinsp,\sipk,\opk) \in \NIZKLang^{\Sign}$. Then:
   %
@@
   \EEnc(\Eek,\yinsp)$, and since $(\yinsp,\iproof)$ is generated honestly at
-  line 5, then \yinsp is the correct decryption of \cinsp, and  correctness of
+  line 5, then \yinsp is the correct decryption of \cinsp, and completeness of
   $\NIZK^{\Open}$ ensures that \Judge outputs $1$ at line 6.
@@
   \paragraph{(c) The output of \finsp matches the output of \Open.} %
-  After (a), the \yinsp value output by \Open is the correct decryption of
+  After (a), and correctness of the public key encryption algorihtm, the \yinsp
+  value output by \Open is the correct decryption of
   \cinsp. After (b), the $(\yeval^0=\yeval,\yeval^1)$ values output by
@@
   extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
-  credentials involved in the signature contain \usk as their user key (first)
-  attribute. Consequently, \IdentifyCred returns $1$ for all the involved
-  credentials, and the probability of \adv~winning at line 11 is $0$.
-
-  \paragraph{(e) \usk must belong to a known user.} %
-  The only remaining option for $\adv$ to win is via winning condition at line
-  12, meaning that \IdentifySig fails to find an honest or corrupt users with
-  a \usk matching the one used to request the credentials used to produce the
-  signature output by \adv. However, at line 12, we already know that all
-  credentials are valid signatures by the issuer and that, also, all are bound
-  to the same user key. If this key is not associated to any known user, this
-  means that there is no matching $\langle\Obtain,\Issue\rangle$ transcript for
-  a credential over \usk --i.e., the honest issuer did not issue any credential
-  to \usk. But, as \sig must have been produced with at least one credential
-  (extracted at step 7), then this credential is a forgery, breaking security
-  against one-more forgery of the \SBCM scheme.
+  credentials involved in the signature contain the same \usk as their user key
+  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
+  returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
+  \uid exists (but not because more than one \cid belongs to different {\uid}s).
+  Assume that no such \uid exists. Clearly, such a signature breaks the one-more
+  forgery property of \SBCM, as it cannot have been produced via a call to
+  \SIGN, which only accepts {\cid}s that belong to known {\uid}s. Therefore, the
+  probability that \adv~wins at line 11 is negligible, given simulation
+  extractability of $\NIZK^{\Sign}$, and correctness and one-more forgery
+  security of \SBCM.
   %
@@
 
-  First, suppose that the \Sig that \adv~outputs at line 2 exists in
-  \SIG, for some \uid. Then, Given that the signature is accepted by \Verify at
+  First, suppose that, in the check done at line 10, the \Sig that \adv~outputs
+  at line 2 exists in \SIG, for some \uid. In that case, given that the
+  signature is accepted by \Verify at
   line 3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
@@
   $\NIZK^{\NIZKRel_{\Sign}}$ ensures that \ExtractSign must output a valid
-  witness for $(\msg,\feval,\yeval^0,\ceval,\cinsp,\sipk_{\scred},\Eek,
-  \widetilde{\Eek})$. Note that this witness must include some \usk which,
+  witness for $(\msg,\feval,\yeval^0,\cinsp,\lbrace ipk_i \rbrace_{i\in[n]},
+  \Eek)$. Note that this witness must include some \usk which,
   for \adv~to win the game, must belong to an honest user. However, since the

### 2022-08-08 prism-backend/research/gsac/formal-uas.tex
Updated proofs for sign-unforgeability, and non-frameability.

@@
 \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
-  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$''. We
-  may also use \OWNR over a set of {\cid}s (\scid). In that case, our convention
-  is that $\OWNR[\scid]$ returns $\bot$ if not all passed {\cid}s belong to the
-  same \uid. Since $\bot$ is not a valid \uid, all conditions checking
-  membership of the output of \OWNR to a list of users equal false if \OWNR
-  returns $\bot$.
+  ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$'', or
+  $\bot$ if there is no wuch \uid. We may also use \OWNR over a set of {\cid}s
+  (\scid). In that case, our convention is that $\OWNR[\scid]$ returns $\bot$ if
+  not all passed {\cid}s belong to the same \uid. Since $\bot$ is not a valid
+  \uid, all conditions checking membership of the output of \OWNR to a list of
+  users equal false if \OWNR returns $\bot$.
 \item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
@@
   If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
-  extractable,the NIZK scheme for $\NIZKRel_{\Open}$ is complete, the public-key
-  encryption scheme is correct, and \SBCM is correct and one-more unforgeable,
-  then our \CUASGen construction satisfies signing unforgeability as defined in
-  \defref{def:sign-forge-uas}, except with negligible probability.
+  extractable, the scheme for $\NIZKRel_{\Open}$ is complete, the public key
+  encryption algorithm is correct, and the \SBCM scheme is correct and one-more
+  unforgeable, then our \CUASGen construction satisfies signing unforgeability
+  as defined in \defref{def:sign-forge-uas}, except with negligible probability.
 \end{theorem}

### 2022-08-11 prism-backend/research/gsac/app-related-proofs.tex
Forgot to push some changes...
Reviewed proofs of related schemes up to AC. Added ref to MPS eprint.

@@
 \begin{theorem}[Anonymity of \CUASGS]
-  If the base \CUASGen construction is anonymous according to
-  \defref{def:anonymity-uas}, then \CUASRing is an anonymous group signature
-  scheme.
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASGS is an anonymous group
+  signature scheme.
 \end{theorem}
@@
   oracles can be directly simulated by calls to \advB's oracles $\CHALb,
-  \OPEN,\HUGEN,\WREG,\CUGEN$ oracles. Thus, if \adv~ guesses its bit $b$
+  \OPEN,\HUGEN,\WREG,\CUGEN,\UCORR$ oracles. Thus, if \adv~guesses its bit $b$
   with non-negligible probability, this directly leads to a non-negligible
@@
 \begin{theorem}[Traceability of \CUASGS]
-  If the base \CUASGen construction has unforgeable signing according to
-  \defref{def:sign-forge-uas}, then \CUASGS is a traceable group signature
+  If the base \CUASGen construction is unforgeable according to
+  \defref{def:forge-uas}, then \CUASGS is a traceable group signature
   scheme.
@@
 \begin{proof}
-  Assume an adversary \adv~ against traceability in \CUASGS. We build an
-  adversary \advB against sign unforgeability of the $(\fissue^1,\feval^0,
-  \finsp^{\upk})-\CUASGen$ instance.
+  Assume an adversary \adv~against traceability in \CUASGS. We build an
+  adversary \advB against unforgeability of the $(\fissue^1,\feval^0,
+  \finsp^{\upk})-\CUASGen$ restriction.
 
-  \advB's simulation of \adv~ environment is as in the proof for anonymity
-  of \CUASGS. \advB simply outputs whatever \adv~ outputs in line 2 of its
-  traceability game. Note that, as \CUASGS is a specific instantiation of
-  \CUASGen, whenever \CUASGS accepts a signature, so does \CUASGen. Concretely,
-  assume that \adv~ wins the traceability game in \figref{fig:model-gs} with
-  $\upk \notin \HU \cup \CU$ at line 5. This implies that the check at line 11
-  of the sign unforgeability game (\figref{fig:exp-uas-unfor-sign}) for \CUASGen
-  outputs $0$ for all known {\uid}s. Similarly, if \adv~ wins the traceability
-  game with condition $\Judge(\dots)=0$ at line 5, then \advB wins its sign
-  unforgeability game with the corresponding check at line 6 in
-  \figref{fig:exp-uas-unfor-sign}.
+  \advB's simulation of \adv's environment is as in the proof for anonymity
+  of \CUASGS. \advB simply outputs whatever \adv~outputs in line 2 of its
+  traceability game. Note that, whenever \CUASGS accepts a signature, so does
+  \CUASGen. Concretely,
+  assume that \adv~wins the traceability game in \figref{fig:model-gs} with
+  $\upk \notin \HU \cup \CU$ at line 5. This implies that, in line 14 of the
+  \UAS unforgeability game (\figref{fig:exp-uas-unfor}) $\OWNR[\lbrace \cid_i
+  \rbrace_{i\in[n]}]$ returns an \uid which is not in either \HU or \CU.
+  Similarly, if \adv~wins the traceability game with condition $\Judge(\dots)=0$
+  at line 5, then \advB wins its unforgeability game with the corresponding
+  check at line 6 in \figref{fig:exp-uas-unfor}.
   %
@@
 \begin{proof}
-  Assume an adversary \adv~ against non-frameability in \CUASGS. We build an
+  Assume an adversary \adv~against non-frameability in \CUASGS. We build an
   adversary \advB against non-frameability of the $(\fissue^1,\feval^0,
@@
 
-  \advB's simulation of \adv~ environment is as in the proof for anonymity
-  of \CUASGS. \advB simply outputs whatever \adv~ outputs at line 2 of its
-  game. Observe that a winning condition for \adv~ directly implies a winning
-  condition for \advB. Concretely, if $\upk \in \HU \land \PRVUK[\upk] \neq
-  \bot$ in \adv's game, then $\exists \uid \in \HU~\suchthat~\UK[\uid]=\usk$
-  for \advB (line 6 of its game). Similarly, if \Judge returns $1$ in \adv's
-  game, \advB's \Judge also returns $1$ at line 4. Finally, if \adv~ does not
-  corrupt the owner of \upk, then $\uid \in \HU$ in \advB's game, and if \adv
-  does not query its $SIGN$ oracle, then there does not exist a matching entry
-  in $\SIG[\uid]$ for \advB either. Consequently, as stated, \advB wins its
-  non-frameability every time that \adv does.
+  \advB's simulation of \adv's~environment is as in the proof for anonymity
+  of \CUASGS. \advB simply outputs whatever \adv~outputs at line 2 of its
+  game. Observe that the winning condition for \adv~directly implies a winning
+  condition for \advB. Concretely, if \adv~wins its game, \advB wins its game
+  in line 11 of \ExpNonframe.
   \qed
@@
 We prove that our \CUASRing construction is anonymous and unforgeable, if
-the underlying \CUASGen construction is secure.
+the underlying $\CUASGen^{hide-iss}$ construction is secure.
 
 \begin{theorem}[Anonymity of \CUASRing]
-  If the base \CUASGen construction is anonymous according to
-  \defref{def:anonymity-uas}, then \CUASRing is an anonymous ring signature
+  If the base $\CUASGen^{hide-iss}$ construction is anonymous according to
+  \defref{def:sign-anonymity-uas}, then \CUASRing is an anonymous ring signature
   scheme.
@@
   Then, we build \advB against anonymity of \CUASGen. Concretely, \advB first
-  generates $n$ keypairs by running its \IGEN (with $\fissue^{\sring}$) and
-  \HUGEN oracles, and runs \OGEN at least once (with $\finsp^0$). Then, invokes
-  $\adv$ passing as public keys the public keys of the $n$ generated issuers
-  (users in \CUASRing). $\adv$'s $SIGN(i,R,\msg)$ queries are processed as
-  follows. If user $i$ has not yet produced a credential for ring $R$, \advB
-  makes a call to its \OBTAIN oracle, using $R$ as attribute set. If such a
-  credential was already produced, then reuse it. Then, \advB uses the
-  corresponding user and credential identifiers as parameters to a query to its
-  own \SIGN oracle (specifying $\feval^{\attrs}$ as signature evaluation
-  function). Eventually, $\adv$ outputs two user indexes, a ring $R$, and
-  message \msg. If the checks at line 4 of \figref{fig:model-rs} pass, \advB
-  generates the challenge signature by calling its own \CHALb oracle, and passes
-  the result to $\adv$. Finally, \advB outputs whatever $\adv$ outputs.
+  generates $n$ key pairs for \adv simulating $KeyGen$ in \adv's game. Since
+  $KeyGen$ simply uses algorithms of $\CUASGen^{hide-iss}$, \advB can do this
+  directly via its own \HUGEN, \ISET, and \OGEN oracles, specifying
+  $\fissue^{\sring}$ as issuance function, and $\finsp^0$ as opening function.
+  Then, \advB invokes $\adv$ passing the $n$ produced public keys, and
+  answers $\adv$'s $SIGN(i,R,\msg)$ queries as follows. If user $i$ has not yet
+  produced a credential for ring $\pk_i \in R$, \advB makes a call to its
+  \OBTAIN oracle, using $R$ as attribute set. If such a credential was already
+  produced, \advB simply reuses it. Then, \advB uses the corresponding user and
+  credential identifiers as parameters to a query to its own \SIGN oracle
+  (specifying $\feval^{\attrs}$ as signature evaluation function). Eventually,
+  $\adv$ outputs two user indexes, a ring $R$, and message \msg. If the checks
+  at lines 3-4 of \figref{fig:model-rs} pass, \advB generates the challenge
+  signature by calling its own \CHALb oracle, and passes the result to $\adv$.
+  Finally, \advB outputs whatever $\adv$ outputs.
   %
+  The simulation of \adv's anonymity game is perfect, and \advB wins its game
+  whenever \adv does.
   \qed
@@
 \begin{theorem}[Unforgeability of \CUASRing]
-  If the base \CUASGen construction is non-frameable according to
+  If the base $\CUASGen^{hide-iss}$ construction is non-frameable according to
   \defref{def:frame-uas}, then \CUASRing is an unforgeable ring signature
@@
   accepted by $Verify$ at line 3 of the ring signature unforgeability game,
-  there exists some \uid with an \usk matching the check at line 6 in the
-  non-frameability game. Moreover, since $\adv$ never queried its $SIGN$
+  it is also accepted by \Verify in the \UAS non-frameability game. But,
+  moreover, given the construction of $Verify$ in \CUASRing, there is some
+  honest \usk within $R$ that produced the signature, so $\OWNR[\scid] \in \HU$
+  in \advB's non-frameability game. Also, since $\adv$ never queried its $SIGN$
   oracle, then by construction there cannot exist a matching entry in the
@@
 scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
-is anonymous and has unforgeable signing. Note that issuance unforgeability
-of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
-leveraging other credentials not any fixed custom issuance policy. Thus,
-signature unforgeability from \UAS is enough. Note that AC schemes modelled
-as in \cite{fhs19} do not have issuance anonymity, as the user public key
-is passed to the issuer.
+is anonymous and unforgeable. Note that AC schemes modelled as in \cite{fhs19}
+do not have issuance anonymity, as the user public key is passed to the issuer.
 
@@
 \begin{proof}
-  Given \adv~ against anonymity of \CUASAC as defined in \cite{fhs19}, we build
+  Given \adv~against anonymity of \CUASAC as defined in \cite{fhs19}, we build
   an adversary \advB against anonymity of \CUASGen as defined in
@@
   the inputs from the former into inputs for the latter is trivial.
-  Obviously, if \adv~ wins in its anonymity game, then so does \advB with the
+  Obviously, if \adv~wins in its anonymity game, then so does \advB with the
   same probability.
@@
   \label{thm:forge-cuasac}
-  If the base \CUASGen construction has sign unforgeability according to
-  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
+  If the base \CUASGen construction is unforgeable according to
+  \defref{def:forge-uas}, then \CUASAC is an unforgeable AC scheme.
 \end{theorem}
@@
 \begin{proof}
-  Given \adv~ against unforgeability of \CUASAC as defined in \cite{fhs19}, we
-  build an adversary \advB against sign unforgeability of \CUASGen as defined in
-  \defref{def:sign-forge-uas}.
+  Given \adv~against unforgeability of \CUASAC as defined in \cite{fhs19}, we
+  build an adversary \advB against unforgeability of \CUASGen as defined in
+  \defref{def:forge-uas}.
 
-  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
-  that \adv~ wins its game. Note that, since $b=1$ in line 5 of the
+  To simulate oracle calls by \adv, \advB acts as in the anonymity proof
+  ($ObtIss$ and $Issue$ for \adv~correspond to \OBTISS and \ISSUE for \advB).
+  Assume that \adv~wins its game. Note that, since $b=1$ in line 4 of the
   unforgeability game of \figref{fig:model-ac}, then by construction, \Verify
-  also returns $1$ in the sign unforgeability game of \UAS. In addition, if
+  also returns $1$ in the unforgeability game of \UAS. In addition, if
   there is no corrupt user with a credential containing $D$, then this leads to
-  \advB winning at line 9 in \figref{fig:exp-uas-unfor-sign}, as no credential
+  \advB winning at line 12 in \figref{fig:exp-uas-unfor}, as no credential
   owned by a corrupt user that can be extracted can make the $\feval^{\dattrs}$
   function output $\yeval^0=D$. Thus, \advB wins with the same probability as
-  \adv~ does.  
+  \adv~does.  
   %
@@
 \begin{theorem}[Anonymity of \CUASRAC]
-  \label{thm:anon-cuasac}
+  \label{thm:anon-cuasrac}
   If the base \CUASGen construction has signature anonymity according to
@@
   \defref{def:sign-anonymity-uas}, then \CUASMPS satisfies privacy-1
-  according to \needcite.
+  according to \cite{ngsy22}.
 \end{theorem}
@@
   \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
-  defined in \needcite.
+  defined in \cite{ngsy22}.
 \end{theorem}
@@
   \defref{def:frame-uas}, then \CUASMPS satisfies unforgeability-2 as
-  defined in \needcite.
+  defined in \cite{ngsy22}.
 \end{theorem}

### 2022-08-11 prism-backend/research/gsac/app-uas-proofs.tex
Reviewed proofs of related schemes up to AC. Added ref to MPS eprint.

@@
 \label{app:uas-proofs}
-
-\todo{Do we only need this for \fissue function?}
-First, we formally define now what do we mean with \UAS-acceptable \fissue,
-complementing the informal \defref{def:uas-acc-func}.
-
-\begin{figure}[ht!]
-  \centering  
-  \scalebox{0.9}{
-    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
-      \parm \gets \Setup(1^\secpar) \\
-      (\upk,\usk) \gets \KeyGen(\parm) \\
-      (\st,\attrs, \lbrace (\cidi,\cidu,\cattrs_i) \rbrace_{i\in[n]})
-      \gets \adv(\upk) \\
-      \pcif b=0:
-      \yissue^* \gets \fissue(\upk,\lbrace (\cidi,\cattrs_i)
-      \rbrace_{i\in[n]},\attrs) \\
-      \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
-      b^* \gets \adv(\st,\yissue*) \\
-      \pcreturn b=b^*
-    }
-  }
-  \label{fig:uas-acceptable}
-  \caption{Formal definition of \UAS-acceptable \fissue functions.}
-\end{figure}
 
@@
   a number $q < n$, where $n$ is the number of users that \adv~creates via
-  \UGEN, and assigning to the $q$-th user the $(\SBCMvk,\SBCMsk)$ key pair
+  \HUGEN, and assigning to the $q$-th user the $(\SBCMvk,\SBCMsk)$ key pair
   that \advB receives in its blindness game. Then, when \adv~makes a query
@@
 
-\subsection{Issuance Unforgeability}
+% \subsection{Issuance Unforgeability}
 
-\begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
-  We show that the probability that \fissue outputs a wrong $\yinsp$ value is
-  negligible, as well as the probability that the credential identifier does not
-  belong to an existing (honest or corrupt) user.
+% \begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
+%   We show that the probability that \fissue outputs a wrong $\yinsp$ value is
+%   negligible, as well as the probability that the credential identifier does not
+%   belong to an existing (honest or corrupt) user.
 
-  Observe that the adversary is required to output a credential identifier for
-  which associated entries in \trans and \CRED exist; moreover, if such a
-  credential was produced by an issuer, we must have access to those entries, as
-  issuers are assumed to be honest in this game.
-  %
-  Since we can access $\trans[\cid] = (\yissue,\utrans)$, and \utrans contains
-  a NIZK proof $\NIZKproof_{\Issue}$ proving knowledge by the user of a witness
-  in $\NIZKRel_{\Issue}$, which is simulation extractable, \ExtractIssue
-  produces a tuple $(\upk,\usk,\lbrace (\cid_i,\attrs_i,\cred_i)
-  \rbrace_{i\in[n]}$.
-  %
-  From the fact that issuers are honest, we know that $\ATTR[\cid]$ must match
-  the attribute set \attrs used by user and issuer in the issuance protocol.
-  Thus, from  soundness of the NIZK system, the $(\upk,\lbrace (\cid_i,\attrs_i,
-  \cred_i) \rbrace_{i\in[n]}$ values within the extracted tuple, along with
-  $\ATTR[\cid] = \attrs$ must make \fissue output \yissue, except with
-  negligible probability. Moreover, soundness of the NIZK system also implies
-  that all credentials are bound to the same \usk, which is associated to the
-  extracted \upk.
+%   Observe that the adversary is required to output a credential identifier for
+%   which associated entries in \trans and \CRED exist; moreover, if such a
+%   credential was produced by an issuer, we must have access to those entries, as
+%   issuers are assumed to be honest in this game.
+%   %
+%   Since we can access $\trans[\cid] = (\yissue,\utrans)$, and \utrans contains
+%   a NIZK proof $\NIZKproof_{\Issue}$ proving knowledge by the user of a witness
+%   in $\NIZKRel_{\Issue}$, which is simulation extractable, \ExtractIssue
+%   produces a tuple $(\upk,\usk,\lbrace (\cid_i,\attrs_i,\cred_i)
+%   \rbrace_{i\in[n]}$.
+%   %
+%   From the fact that issuers are honest, we know that $\ATTR[\cid]$ must match
+%   the attribute set \attrs used by user and issuer in the issuance protocol.
+%   Thus, from  soundness of the NIZK system, the $(\upk,\lbrace (\cid_i,\attrs_i,
+%   \cred_i) \rbrace_{i\in[n]}$ values within the extracted tuple, along with
+%   $\ATTR[\cid] = \attrs$ must make \fissue output \yissue, except with
+%   negligible probability. Moreover, soundness of the NIZK system also implies
+%   that all credentials are bound to the same \usk, which is associated to the
+%   extracted \upk.
 
-  Finally, suppose that the extracted \upk does not belong to a \uid in
-  $\HU \cup \CU$. Then, the produced credential is a forgery. \todo{How to
-    extract the forgery in this case?? I think that expanding the definition
-    so that it requires \adv~to produce a valid signature would make things
-    much easier...}
-  \qed
-\end{proof}
+%   Finally, suppose that the extracted \upk does not belong to a \uid in
+%   $\HU \cup \CU$. Then, the produced credential is a forgery. \todo{How to
+%     extract the forgery in this case?? I think that expanding the definition
+%     so that it requires \adv~to produce a valid signature would make things
+%     much easier...}
+%   \qed
+% \end{proof}
 
-\subsection{Signature Unforgeability}
+\subsection{Unforgeability}
 
-\begin{proof}[\thmref{thm:sign-forge-uas}; Signature unforgeability of \CUASGen]
-  We show that an adversary \adv~winning \ExpForgeSign can be used to break the
+\begin{proof}[\thmref{thm:forge-uas}; Signature unforgeability of \CUASGen]
+  We show that an adversary \adv~winning \ExpForge can be used to break the
   one-more unforgeability property of \SBCM.
 
-  If the verification at line 4 of \ExpForgeSign holds, then $(\msg,\feval,
+  If the verification at line 4 of \ExpForge holds, then $(\msg,\feval,
   \yeval,\cinsp,\sipk,\opk) \in \NIZKLang^{\Sign}$. Then:
@@
   \paragraph{(a) \Judge accepts $(\yinsp,\iproof)$.} %
-  Simulation extractability of $\NIZK^{\Sign}$ thus ensures that $\cinsp =
+  Simulation extractability of $\NIZK^{\Sign}$ ensures that $\cinsp =
   \EEnc(\Eek,\yinsp)$, and since $(\yinsp,\iproof)$ is generated honestly at
@@
 
-  \paragraph{(b) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
+  \paragraph{(b) All used credentials were correctly issued.} %
+  Since issuers are assumed to be honest, we have access to the $\trans[\cid_i]$
+  transcript for all credentials involved in producing the signature. Given
+  simulation extractability of $\NIZK^{\Issue}$, \ExtractIssue outputs a valid
+  witness $(\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
+  \rbrace_{j\in[n_j]})$ from each $\trans[\cid_i]$. This, concretely, implies
+  that the $\yissue^i$ value available in $\trans[\cid_i]$ matches the one
+  output by \fissue. Similarly, due to simulation extractability, the set of
+  credentials $\lbrace \cid_{i,j}\rbrace_{j\in[n_i]}$ used to request credential
+  $\cid_i$ cannot include credentials owned by different users, as this
+  condition is ensured by $\NIZKRel_{\Issue}$. Thus, $\uid = \OWNR[\lbrace
+  \cid_{i,j} \rbrace_{j\in[n_i]}] \neq \bot$. Now, assume that $\uid \notin \HU
+  \cup \CU$. This, in addition to the fact that {\usk}s are produced uniformly
+  at random, means that $\cred_i$ is not bound to a \usk owned by a known
+  user. But then, $\cred_i$ cannot have been produced via \OBTISS or \ISSUE,
+  which only accept request from known {\uid}s (either in \HU or \CU,
+  respectively). Thus, $\cred_i$ is a valid \SBCM signature, that has not been
+  produced via an honest query, which breaks the one-more forgery property of
+  \SBCM.
+
+  \paragraph{(c) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
     pair.} Also, due to simulation extractability of $\NIZK^{\Sign}$:
@@
 
-  Thus, the probability of \adv~winning at line 9 is negligible, due to
+  Thus, the probability of \adv~winning at line 12 is negligible, due to
   simulation extractability of $\NIZK^{\Sign}$.
 
-  \paragraph{(c) The output of \finsp matches the output of \Open.} %
+  \paragraph{(d) The output of \finsp matches the output of \Open.} %
   After (a), and correctness of the public key encryption algorihtm, the \yinsp
   value output by \Open is the correct decryption of
-  \cinsp. After (b), the $(\yeval^0=\yeval,\yeval^1)$ values output by
+  \cinsp. After (c), the $(\yeval^0=\yeval,\yeval^1)$ values output by
   \ExtractSign match the evaluation of \feval. Thus, simulation extractability
@@
   matches the $\yinsp'$ value extracted by \ExtractSign. Thus, the probability
-  of \adv~winning at line 10 is negligible due to simulation extractability
+  of \adv~winning at line 13 is negligible due to simulation extractability
   of $\NIZK^{\Sign}$.
 
-  \paragraph{(d) All {\cred}s are bound to the same \usk.} %
+  \paragraph{(e) All {\cred}s are bound to the same \usk.} %
   $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
@@
   \uid exists (but not because more than one \cid belongs to different {\uid}s).
-  Assume that no such \uid exists. Clearly, such a signature breaks the one-more
-  forgery property of \SBCM, as it cannot have been produced via a call to
-  \SIGN, which only accepts {\cid}s that belong to known {\uid}s. Therefore, the
-  probability that \adv~wins at line 11 is negligible, given simulation
-  extractability of $\NIZK^{\Sign}$, and correctness and one-more forgery
-  security of \SBCM.
+  Assume that no such \uid exists. Such a signature breaks the one-more
+  forgery property of \SBCM, as it has not been produced via a call to \SIGN
+  (it is not in $\SIG$). Therefore, the probability that \adv~wins at line 14 is
+  negligible, given simulation extractability of $\NIZK^{\Sign}$, and
+  correctness and one-more forgery security of \SBCM.
   %
@@
 
-  First, suppose that, in the check done at line 10, the \Sig that \adv~outputs
-  at line 2 exists in \SIG, for some \uid. In that case, given that the
-  signature is accepted by \Verify at
+  First, suppose that the \Sig that \adv~outputs at line 2 exists in \SIG, for
+  some \uid. In that case, the signature is accepted by \Verify at
   line 3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
-  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, since the $(\yinsp,\iproof)$
+  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, if the $(\yinsp,\iproof)$
   pair output by \adv~is accepted by \Judge, simulation extractability of
@@
 
-  Next, suppose that the \Sig output by \adv~at line 2 does not exist in \SIG.
-  We prove that zero-knowledge and simulation extractability of
-  $\NIZKRel_{\Sign}$, and blindness of \SBCM, ensure that this only happens with
+  Next, we prove that, after zero-knowledge and simulation extractability of
+  $\NIZKRel_{\Sign}$, and blindness of \SBCM, $\Sig \in \SIG$ except with
   negligible probability.
+  %
   The crucial observation is that, as in \cite{cl06} \CUASGen's \Sign algorithm
@@
   compare $x$ and $w$ to the public and private key of a signature algorithm,
-  respectively. In $\NIZKRel^{\Sign}$, $(\usk,\scred,\attrs_{\scred},\yeval^1,
-  \yinsp,r,r')$ is the private key ($w$), and $(\msg,\feval,\yeval^0,\ceval,
-  \cinsp,\sipk_{\scred},\Eek,\widetilde{\Eek})$ is the public key ($x$).
+  respectively. In $\NIZKRel^{\Sign}$, $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
+  \cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r,r')$ is the private key ($w$), and
+  $(\msg,\feval,\yeval^0,\cinsp,\lbrace \ipk_i \rbrace_{i\in[n]},\Eek)$ is the
+  public key ($x$).
   %
@@
   indistinguishable from $G_0$. Now, in $G_1$, simulation extractability of
-  $\NIZK^{\NIZKRel_{\Sign}}$ ensures that \ExtractSign must output a valid
+  $\NIZK^{\NIZKRel_{\Sign}}$ ensures that \ExtractSign outputs a valid
   witness for $(\msg,\feval,\yeval^0,\cinsp,\lbrace ipk_i \rbrace_{i\in[n]},

### 2022-08-11 prism-backend/research/gsac/formal-uas.tex
Reviewed proofs of related schemes up to AC. Added ref to MPS eprint.

@@
   signatures.
-\item[$\ISet((\upk,\usk),\fissue) \rightarrow \ipk$.] Given a user key
+\item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
   pair, and an issuance function \fissue for checking that credential requestors
@@
 \begin{description}
-\item[$\fissue: (\upk,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]},\attrs)
+\item[$\fissue: (\upk,\usk,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]},\attrs)
   \rightarrow \yissue$.] Chosen
@@
   defines the customized conditions required by the issuer to grant a credential
-  over attributes \attrs, when requested by a user with public key \upk,
+  over attributes \attrs, when requested by a user with key pair $(\upk,\usk)$,
   leveraging a set of $n$ previously obtained credentials with identifiers and
@@
   convention that $\yissue = 0$ means that the issuance request is denied.
+  \fissue functions must be \UAS-acceptable, as defined in
+  \defref{def:uas-acc-func}.
 \item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
@@
 may negotiate to use any opener for a given signature, it is not possible for
-an opener to change the chosen function. In the sequel, we restrict to
-\UAS-acceptable functions, defined as follows:
+an opener to change the chosen function.
+
+Concerning \fissue functions, our \UAS model requires them to be \UAS-acceptable
+functions.  At a high level, this requires that \fissue functions do not reveal
+anything about the signer's data used as input. This is formally captured in
+\figref{fig:uas-acceptable}.
+
+\begin{figure}[ht!]
+  \centering  
+  \scalebox{0.9}{
+    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
+      \parm \gets \Setup(1^\secpar) \\
+      (\upk,\usk) \gets \KeyGen(\parm) \\
+      (\st,\attrs, \lbrace (\cidi,\cidu,\cattrs_i) \rbrace_{i\in[n]})
+      \gets \adv(\upk) \\
+      \pcif b=0:
+      \yissue^* \gets \fissue(\upk,\usk,\lbrace (\cidi,\cattrs_i)
+      \rbrace_{i\in[n]},\attrs) \\
+      \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
+      b^* \gets \adv(\st,\yissue^*) \\
+      \pcreturn b^*
+    }
+  }
+  \label{fig:uas-acceptable}
+  \caption{Formal definition of \UAS-acceptable \fissue functions.}
+\end{figure}
 
@@
   \label{def:uas-acc-func}
-  We say that a \fissue function chosen from some family \famfissue is
-  \UAS-acceptable if, conditioned on it returning a non-zero value, the
-  value it produces is indistinguishable from random.
-  % %
-  % Similarly, a \feval function chosen from some family \famfeval is
-  % \UAS-acceptable if the $\yeval^1$ component of its output is hiding with
-  % respect to its \upk and $\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]}$ inputs.
+  A \fissue function is \UAS acceptable if, for any p.p.t. adversary \adv,
+  $|\Pr[\Exp^{\UAS-acc-1}_\adv(1^\secpar)=1]-\Pr[\Exp^{\UAS-acc-0}_\adv
+  (1^\secpar)=0]|$ is a negligible function of $1^\secpar$.
 \end{definition}
 
-That is, at a high level we require that \fissue and \feval functions do not
-reveal anything about the signer. \todo{Since the concept is quite intuitive, we
-  defer the formal definition to \appref{app:XXX}}. We give in
-\secref{ssec:generic-construction-uas}
-a generic \CUASGen construction that assumes \UAS-acceptable functions. Next, we
-define the concept of \CUASGen restrictions. Briefly, these are special cases of
-our generic construction that target a concrete variant of the utility-privacy
-tradeoff by defining concrete \fissue, \feval and \finsp functions. Security of
-\CUASGen implies security of its restrictions, as long as the chosen functions
-are \CUASGen-acceptable.
+A \UAS construction thus can only be secure if the \fissue function it uses is
+\UAS-acceptable.
+%
+Next, we define the concept of \CUASGen restrictions. Briefly, these are special
+cases of our generic construction that target a concrete variant of the
+utility-privacy tradeoff by defining concrete \fissue, \feval and \finsp
+functions. Security of \CUASGen implies security of its restrictions, as long as
+the chosen functions are \CUASGen-acceptable.
 
@@
 %   the associated issuance function.
-\item[\UGEN.] Adds a new user to the game, generating its keypair.  
+\item[\HUGEN.] Adds a new honest user to the game, generating its keypair.
+\item[\HUGEN.] Adds a new corrupt user to the game, setting its \upk to the
+  value given by the adversary.  
 \item[\OGEN.] Adds a new opener to the game, generating its key pair and
@@
 
-        \procedure{$\UGEN(\uid)$}{%
+        \procedure{$\HUGEN(\uid)$}{%
           \pcif \uid \in \HU \lor \uid \in \CU: \pcreturn \bot \\
@@
 
-        \procedure{$\ISET(\uid,\fissue)$}{%
-          \pcif \uid \notin \HU \cup \CU: \pcreturn \bot \\
+        \procedure{$\UCORR(\uid)$}{%
+          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
           \pcif \uid \in \HI \cup \CI: \pcreturn \bot \\
-          \pcif \fissue \notin \famfissue: \pcreturn \bot \\
-          \ipk \gets \ISet(\UK[\uid],\fissue) \\
-          \IK[\uid] \gets ((\ipk,\fissue),\PRVUK[\uid]) \\
-          \pcif \uid \in \HU: \HI \gets \HI \cup \lbrace \uid \rbrace \\
-          \pcif \uid \in \CU: \CI \gets \CI \cup \lbrace \uid \rbrace \\
-          \pcreturn \ipk \\
+          \HU \gets \HU \setminus \lbrace \uid \rbrace \\
+          \CU \gets \CU \cup \lbrace \uid \rbrace \\
+          \pcreturn (\PRVUK[\uid],\CRED[\uid]) \\
+        }
+
+        \procedure{$\ICORR(\uid)$}{%
+          \pcif \uid \notin \HI: \pcreturn \bot \\
+          \HI \gets \HI \setminus \lbrace \uid \rbrace \\
+          \CI \gets \CI \cup \lbrace \uid \rbrace \\
+          \pcreturn(\PRVUK[\uid],\CRED[\uid]) \\
         }
@@
 
-        \procedure{$\UCORR(\uid)$}{%
-          \pcif \uid \in \CU \lor \uid \notin \HU: \pcreturn \bot \\
+        \procedure{$\CUGEN(\uid,\upk)$}{%          
+          \pcif \uid \in \HU \lor \CU: \pcreturn \bot \\
+          \CU \gets \CU \cup \lbrace \uid \rbrace \\          
+          \UK[\uid] = (\upk,\bot) \\          
+          \pcreturn \top \\
+        }
+
+        \procedure{$\ISET(\uid,\fissue)$}{%
+          \pcif \uid \notin \HU \cup \CU: \pcreturn \bot \\
           \pcif \uid \in \HI \cup \CI: \pcreturn \bot \\
-          \HU \gets \HU \setminus \lbrace \uid \rbrace \\
-          \CU \gets \CU \cup \lbrace \uid \rbrace \\
-          \pcreturn (\PRVUK[\uid],\CRED[\uid]) \\
-        }
-
-        \procedure{$\ICORR(\uid)$}{%
-          \pcif \uid \notin \HI: \pcreturn \bot \\
-          \HI \gets \HI \setminus \lbrace \uid \rbrace \\
-          \CI \gets \CI \cup \lbrace \uid \rbrace \\
-          \pcreturn(\PRVUK[\uid],\CRED[\uid]) \\
+          \pcif \fissue \notin \famfissue: \pcreturn \bot \\
+          \ipk \gets \ISet(\PUBUK[\uid],\PRVUK[\uid],\fissue) \\
+          \IK[\uid] \gets ((\ipk,\fissue),\PRVUK[\uid]) \\
+          \pcif \uid \in \HU: \HI \gets \HI \cup \lbrace \uid \rbrace \\
+          \pcif \uid \in \CU: \CI \gets \CI \cup \lbrace \uid \rbrace \\
+          \pcreturn \ipk \\
         }
@@
         }
-
-        % \procedure{$\CUGEN(\uid)$}{%          
-        %   \pcif \uid \in \CU: \pcreturn \bot \\
-        %   \CU \gets \CU \cup \lbrace \uid \rbrace \\          
-        %   \pcif \uid \in \HU: \\
-        %   \pcind \HU \gets \HU \setminus \lbrace \uid \rbrace; \\
-        %   \pcind \pcreturn (\UK[\uid],\CRED[\uid]) \\
-        %   \pcelse: \UK[\uid] = \bot \\          
-        %   \pcreturn \top \\
-        % }
 
@@
           \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
-          \pcif 0(\fissue(\PUBUK[\cuid_0],\cscid_0,\attrs)) \neq \\
-          \pcind 0(\fissue(\PUBUK[\cuid_1],\cscid_1,\attrs)): \pcreturn \bot \\
+          \pcif 0(\fissue(\PUBUK[\cuid_0],\PRVUK[\cuid_0],\cscid_0,\attrs)) \neq \\
+          \pcind 0(\fissue(\PUBUK[\cuid_1],\PRVUK[\cuid_1],\cscid_1,\attrs)):
+          \pcreturn \bot \\
           \langle \Cred, \cdot \rangle \gets
@@
       (\uid,\oid,\scid,\msg,\feval)
-      \gets \adv^{\UGEN,\OGEN,\ISET,\OBTISS,\RREG}(\parm) \\
+      \gets \adv^{\HUGEN,\OGEN,\ISET,\OBTISS,\RREG}(\parm) \\
       \pcif \feval \notin \famfeval: \pcreturn 0 \\
@@
       \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
-      \pcind \pcif \fissue(\PUBUK[\uid],\attrs,
+      \pcind \pcif \fissue(\PUBUK[\uid],\PRVUK[\uid],\attrs,
       (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) \neq \yissue:
@@
 \label{sssec:security}
+
+\todo{All the following assumes \UAS-acceptable \fissue functions.}
 
@@
 The formal specification of the anonymity games is given in
-\figref{fig:exp-uas-anonb}, where
-$\OIssAnon \gets (\lbrace\OO,\UU\rbrace\GEN,\ISET,\ISET,\lbrace\II,
-\OO,\UU\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\OBTCHALb)$, and $\OSigAnon
-\gets (\lbrace\OO,\UU\rbrace\GEN,\ISET,\ISET,\lbrace\II,\OO,\UU\rbrace
-\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$.
+\figref{fig:exp-uas-anonb}.
 
@@
   }
-  \caption{Issuance and signature anonymity experiments for \UAS schemes.}
+  \caption{Issuance and signature anonymity experiments for \UAS schemes.
+    $\OIssAnon \gets (\lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,
+    \OO,\UU\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\OBTCHALb)$, and $\OSigAnon
+    \gets (\lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,\OO,\UU\rbrace
+    \CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$}
   \label{fig:exp-uas-anonb}
@@
 trace back to a user with consistent credentials. All the previous is captured
-by a signature unforgeability property. We define this by allowing the adversary
+by an unforgeability property. We define this by allowing the adversary
 to call any oracle, except the one for corrupting issuers. The adversary wins if
@@
 credentials owned by a known user.
-
-Again, since \UAS schemes (may) require proving claims at issuance time, we
+%
+In addition, \UAS schemes allow proving claims at issuance time. Thus, we
 need to ensure that those claims cannot be forged by an adversary without the
-proper attributes. In this case, since we (need to) assume trusted issuers, we
-can condition on having the $\langle \Obtain,\Issue \rangle$ transcripts
-available for analysis. Thus, the adversary -- with access to the same oracles
-as above -- is challenged to output a credential identifier for a credential
-that exists in \CRED and (1), the conditions required by \fissue were not
-satisfied, or some of the credentials used to support the request does not
-belong to the requesting user; or (2) all credentials used to support the
-request are bound to the same secret key, but that secret key does not belong
-to any known user. The issuance unforgeability notion formalizes this.
-
-For both \ExpForgeIssue and \ExpForgeSign (in \figref{fig:exp-uas-unfor}), the
-adversary is given access to the oracle set $\Oforgeissue = \Oforgesign \gets
-\lbrace\OO,\UU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace\CORR,\OBTISS,\ISSUE,\RREG,
-\SIGN,\OPEN$.
+proper attributes. To ensure this, besides the winning conditions stated above,
+the adversary also wins the unforgeability game if the produced signature
+was produced with a credential for which the conditions required by \fissue were
+not satisfied.
+%
+\ExpForge is formally defined in \figref{fig:exp-uas-unfor}).
+
+\todo{Mention that, in this definition, a credential that does not meet \fissue
+  is not considered a forgery unless it is used to produce a signature. This is
+  consistent with other works -- e.g., Camenisch, Krenn, Lehmann...}
 
@@
     \begin{minipage}[t]{\textwidth}
-      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
-        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
-        \cid \gets \adv^{\Oforgeissue}(\parm) \\
-        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
-        \pcreturn 0 \\
-        \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
-        \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
-        % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
-        ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
-        \gets \ExtractIssue(\trap,\utrans) \\
-        % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
-        % \trans[\cid_i]) \\
-        % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
-        \pcif \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
-        \rbrace_{i\in[n]}) \neq \yissue:
-        \pcreturn 1 \\
-        \pcif \nexists \uid~\suchthat~\PUBUK[\uid]=\upk \land
-        \uid \in \HU \cup \CU: \pcreturn 1 \\
-%        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
-        \pcreturn 0
-      }
-      \vspace*{0.5em}
+%       \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
+%         (\parm,\trap) \gets \SimSetup(1^\secpar) \\
+%         \cid \gets \adv^{\Oforgeissue}(\parm) \\
+%         \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
+%         \pcreturn 0 \\
+%         \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
+%         \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
+%         % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
+%         ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
+%         \gets \ExtractIssue(\trap,\utrans) \\
+%         % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
+%         % \trans[\cid_i]) \\
+%         % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
+%         \pcif \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
+%         \rbrace_{i\in[n]}) \neq \yissue:
+%         \pcreturn 1 \\
+%         \pcif \OWNR[\lbrace\cid_i\rbrace_{i\in[n]}\cup\cid] \notin \HU \cup \CU:
+%         \pcreturn 1 \\
+% %        \pcif \nexists \uid~\suchthat~\PUBUK[\uid]=\upk \land
+% %        \uid \in \HU \cup \CU: \pcreturn 1 \\
+% %        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
+%         \pcreturn 0
+%       }
+%       \vspace*{0.5em}
 
@@
     % \begin{minipage}[t]{\textwidth}
-      \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
+      \procedure[linenumbering]{$\ExpForge(1^\secpar)$}{%
         (\parm,\trap) \gets \Setup(1^\secpar) \\
-        (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
+        (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
         \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
@@
         % \pcreturn 0
-	((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
+	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
         \yeval^1,\yinsp') \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
+        \pcif \exists i\in[n]~\suchthat~
+        \fissue(\upk,\usk,\attrs_i,\lbrace(\cid_{i,j},\attrs_{i,j})
+        \rbrace_{j\in[n_i]}) \neq \yissue^i \lor
+        \OWNR[\lbrace\cid_{i,j}\rbrace_{j\in[n_i]}]\notin \HU \cup \CU, \\
+        \pcind \textrm{where}~(\yissue^i,\utrans) \gets \trans[\cid_i]~\textrm{and}~
+        (\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
+        \rbrace_{j\in[n_i]}) \gets \ExtractIssue(\trap,\utrans]): \\
+        \pcind \pcreturn 1 \\        
         (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
@@
   }
-  \caption{Experiments for credential issuance and signature unforgeability in
-    \UAS schemes.}
+  \caption{Unforgeability experiments in \UAS schemes.
+    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
+    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.}
   \label{fig:exp-uas-unfor}
@@
 
-\begin{definition}{(Unforgeable issuance of \UAS)}
-  \label{def:issue-forge-uas}  
-  We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
-  $\AdvForgeIssue=\Pr\lbrack\ExpForgeIssue(1^\secpar)=1\rbrack$.
+% \begin{definition}{(Unforgeable issuance of \UAS)}
+%   \label{def:issue-forge-uas}  
+%   We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
+%   $\AdvForgeIssue=\Pr\lbrack\ExpForgeIssue(1^\secpar)=1\rbrack$.
+%   %
+%   A \UAS scheme has unforgeable issuance if, for any p.p.t. adversary $\adv$,
+%   \AdvForgeIssue is a negligible function of $1^\secpar$.
+% \end{definition}
+
+% \begin{definition}{(Unforgeable signing of \UAS)}
+%   \label{def:sign-forge-uas}  
+%   We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
+%   $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
+%   %
+%   A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
+%   \AdvForgeSign is a negligible function of $1^\secpar$.
+% \end{definition}
+
+% For short, we say that an \UAS scheme that has both unforgeable issuance and
+% signing, is an unforgeable \UAS scheme.
+
+\begin{definition}{(Unforgeability of \UAS)}
+  \label{def:forge-uas}  
+  We define the advantage \AdvForge of $\adv$ against \ExpForge as $\AdvForge=
+  \Pr\lbrack\ExpForge(1^\secpar)=1\rbrack$.
   %
-  A \UAS scheme has unforgeable issuance if, for any p.p.t. adversary $\adv$,
-  \AdvForgeIssue is a negligible function of $1^\secpar$.
+  A \UAS scheme is unforgeable if, for any p.p.t. adversary $\adv$, \AdvForge is
+  a negligible function of $1^\secpar$.
 \end{definition}
-
-\begin{definition}{(Unforgeable signing of \UAS)}
-  \label{def:sign-forge-uas}  
-  We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
-  $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
-  %
-  A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
-  \AdvForgeSign is a negligible function of $1^\secpar$.
-\end{definition}
-
-For short, we say that an \UAS scheme that has both unforgeable issuance and
-signing, is an unforgeable \UAS scheme.
 
@@
 
-As for anonymity, note that by tweaking the \fissue, \feval and \finsp
+As with anonymity, by tweaking the \fissue, \feval and \finsp
 functions, one can easily mimic behaviour of more restricted schemes. For
@@
 or if the signature can be associated to the secret key of an honest user who
-did not produce it (i.e., no matching call to \SIGN exists). In the game, the
-adversary has access to the oracles in $\Oframe \gets
-\lbrace\OO,\UU\rbrace\GEN,\ISET,\lbrace\II,\OO,\UU\rbrace\CORR,
-\WREG,\OBTAIN,\SIGN$.
+did not produce it (i.e., no matching call to \SIGN exists).
 
@@
   }
-  \caption{Experiment for non-frameability on \UAS schemes.}
+  \caption{Experiment for non-frameability on \UAS schemes.
+    $\Oframe \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,\OO,\UU\rbrace
+    \CORR,\WREG,\OBTAIN,\SIGN$.}
   \label{fig:exp-uas-frame}
@@
 
-\paragraph{Interactive Credential Presentation.} In \appref{app:interactive-uas}
-we show how to convert the non-interactive signing and verification processes
-into an interactive protocol. While the transformation is quite straightforward,
-it is of high relevance for real world use cases.
-
 \subsection{Correctness and Security of \CUASGen}
@@
   and $\NIZKRel_{\Open}$, our generic construction \CUASGen satisfies
-  correctness as defined in \defref{def:correctness-uas}.
+  correctness as defined in \defref{def:correctness-uas}, except with negligible
+  probability.
 \end{theorem}
@@
   construction satisfies issuance anonymity as defined in
-  \defref{def:issue-anonymity-uas}.
+  \defref{def:issue-anonymity-uas}, except with negligible probability.
 \end{theorem}
@@
   If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge, and the
-  public-key encryption scheme is IND-CCA secure, our \CUASGen construction
-  satisfies signature anonymity as defined in \defref{def:sign-anonymity-uas}.
+  public-key encryption scheme is IND-CCA secure, and \fissue is
+  \UAS-acceptable, our \CUASGen construction
+  satisfies signature anonymity as defined in \defref{def:sign-anonymity-uas},
+  except with negligible probability.
 \end{theorem}
 
-\begin{theorem}[Issuance unforgeability of \CUASGen]
-  \label{thm:issue-forge-uas}
-  If the underlying NIZK used for $\NIZKRel_{\Issue}$ is zero-knowledge,
-  simulation extractable and sound, then our \CUASGen construction satisfies
-  issuance unforgeability as defined in \defref{def:issue-forge-uas}.
-\end{theorem}
-
-\begin{theorem}[Signing unforgeability of \CUASGen]
-  \label{thm:sign-forge-uas}
+% \begin{theorem}[Issuance unforgeability of \CUASGen]
+%   \label{thm:issue-forge-uas}
+%   If the underlying NIZK used for $\NIZKRel_{\Issue}$ is zero-knowledge,
+%   simulation extractable and sound, then our \CUASGen construction satisfies
+%   issuance unforgeability as defined in \defref{def:issue-forge-uas}.
+% \end{theorem}
+
+% \begin{theorem}[Signing unforgeability of \CUASGen]
+%   \label{thm:sign-forge-uas}
+%   If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
+%   extractable, the scheme for $\NIZKRel_{\Open}$ is complete, the public key
+%   encryption algorithm is correct, and the \SBCM scheme is correct and one-more
+%   unforgeable, then our \CUASGen construction satisfies signing unforgeability
+%   as defined in \defref{def:sign-forge-uas}, except with negligible probability.
+% \end{theorem}
+
+\begin{theorem}[Unforgeability of \CUASGen]
+  \label{thm:forge-uas}
   If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
   extractable, the scheme for $\NIZKRel_{\Open}$ is complete, the public key
-  encryption algorithm is correct, and the \SBCM scheme is correct and one-more
-  unforgeable, then our \CUASGen construction satisfies signing unforgeability
-  as defined in \defref{def:sign-forge-uas}, except with negligible probability.
+  encryption algorithm is correct, the \SBCM scheme is correct and one-more
+  unforgeable, and \fissue is \UAS-acceptable, then our \CUASGen construction
+  satisfies unforgeability as defined in \defref{def:sign-forge-uas}, except
+  with negligible probability.
 \end{theorem}
@@
   If the underlying scheme for $\NIZK^{\Sign}$ is zero-knowledge and simulation
-  extractable, the scheme for $\NIZK^{\Open}$ is simulation-extractable, and
-  \SBCM scheme is blind, then our \CUASGen construction satisfies
-  non-frameability as defined in \defref{def:frame-uas}, except with negligible
-  probability.
+  extractable, the scheme for $\NIZK^{\Open}$ is simulation-extractable, the
+  \SBCM scheme is blind, and \fissue is \UAS-acceptable, then our \CUASGen
+  construction satisfies non-frameability as defined in \defref{def:frame-uas},
+  except with negligible probability.
 \end{theorem}
@@
 however that alternative constructions are of course possible that, while
-still be close to \CUASGen, may differ in key aspects while still meeting the
-\UAS model. We briefly one such variant next, that we leverage to build related
-schemes. \todo{Security proofs are deferred to \appref{app:uas-variants-proofs}.}
+still meeting the \UAS model, may differ from \CUASGen. We briefly one such
+variant next, that we leverage to build related schemes.
+\todo{Security proofs are deferred to \appref{app:uas-variants-proofs}.}
 
@@
 relaxations are acceptable. For instance, it may be enough to know that the
-issuer belongs to some set of well-known issuers. We merge this with the
-previous extension that collapses issuers and users. Although it would also be
-possible to apply the modification to \CUASGen independently, from a theoretical
-point of view, the combined extension interesting, as it allows to mimic ring
-signatures.
+issuer belongs to some set of well-known issuers. Beyond practical applications,
+this extension is also interesting from a theoretical point of view, as it
+allows us to prove that ring signatures can be seen as a special case of a \UAS
+scheme (cf. \secref{ssec:related-models-rs}).
 
@@
 
+\paragraph{Interactive Credential Presentation.}
+\todo{Does this meet the model? If not, we should move this elsewhere.}
+In \appref{app:interactive-uas}
+we show how to convert the non-interactive signing and verification processes
+into an interactive protocol. While the transformation is quite straightforward,
+it is of high relevance for real world use cases.
+
 %%% Local Variables:

### 2022-08-11 prism-backend/research/gsac/relationships.tex
Reviewed proofs of related schemes up to AC. Added ref to MPS eprint.

@@
 In the following, to showcase the generality of \UAS and \CUASGen, we reproduce
-models of related schemes in the literature -- some of them slightly adapted.
+models of related schemes in the literature.
 Then, we give concrete $(\fissue,\feval,\finsp)$-\CUASGen restrictions and prove
@@
 corresponding \CUASGen restriction is a secure \UAS construction. Concretely,
-we rely on the functions described in \figref{fig:func-restrictions}.
+we rely on the functions described in \figref{fig:func-restrictions}. Observe
+that all the \fissue functions listed in \figref{fig:func-restrictions} are
+\UAS-acceptable. Specifically, $\fissue^1$ and $\fissue^{\sring}$ are trivially
+\UAS-acceptable (for $\rngfissue = \bin$); whereas $\fissue^{single,F,I}$ is
+\UAS-acceptable if $F$ is a secure PRF \needcite.
 
@@
       \begin{align}
-        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
-        & \fissue^{single,F,I}(\upk,\cdot,\cdot) \coloneqq \pcreturn F(I,\upk)
+        & \fissue^1(\cdot,\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
+        & \fissue^{single,F,I}(\cdot,\usk,\cdot,\cdot) \coloneqq \pcreturn
+          F(I,\usk)
           \nonumber \\
-        & \fissue^{\sring}(\upk,\attrs,\cdot) \coloneqq
+        & \fissue^{\sring}(\upk,\cdot,\attrs,\cdot) \coloneqq
           \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber
@@
 exposition, assume that, w.l.o.g., this index is just the public key that the
-group member chooses\markulf{can he choose an existing public key?} when joining the group\footnote{The user public key is
-  assumed to be accessible from a public table in \cite{bsz05}, so it is easy
-  to translate the public key into an index, if needed.}. A group signature
+group member generates randomly when joining the group\footnote{The user public
+  key is assumed to be accessible from a public table in \cite{bsz05}, so it is
+  easy to translate the public key into an index, if needed.}. A group signature
 scheme, according to \cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign,
@@
         \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
-        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
-        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
+        \pcreturn (\upk \in \HU \land \PRVUK[\upk] \neq \bot \land
+        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1)~\land \\
         \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
-        GSig(\PRVUK[\upk],\msg) \\
-        \pcreturn 0
+        GSig(\PRVUK[\upk],\msg)
       }       
@@
 \subsubsection{\CUASGS construction.} %
-\todo{Clarify how $\fissue^{single,F,I}$ works! This is also common with other
-  constructions...}
 We show that the $(\fissue^{single,F,I},\feval^0,\finsp^{\upk})$-\CUASGen
 restriction, is a secure group signature scheme according to \cite{bsz05}.
-Observe that the $\fissue^{single,F,I}$ function is further parameterized with
-a list $L$ maintained by the issuer and must be fetched by users prior to
-joining. It restricts that any user can have at most one credential (associated
-to a same user key pair). We first quickly define the algorithms, and then
-prove security.
+As stated, the $\fissue^{single,F,I}$ is an \UAS-acceptable function if $F$ is a
+PRF. In that case, its output is a random-looking string that depends on the
+user secret key \usk, and a string $I$ uniquely identifying the user. Thus, it
+will be the same per $(\usk,I)$ pair, and can be used by issuer $I$ to prevent
+issuing more than one credential per user -- without enabling linking across
+issuers. Basically, each issuer maintains a list of received $\yissue = F(\usk,
+I)$ values, and rejects issuing a credential for already existing \yissue
+values. From this, the GS algorithms are as follows:
 
@@
   \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Runs $\langle\Obtain,
-  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. If the issuer
-  gets $\yissue = 0$, rejects issuing a new credential. Otherwise, it completes
-  the protocol and adds $\yissue$ to $L$.
+  \Issue\rangle$ as in \CUASGen, with $\attrs \gets \emptyset$. Upon receiving
+  the \yissue value, the issuer checks if it already exists in a list $L$
+  (initially set to $\emptyset$); if it exists, aborts issuance. Otherwise, it
+  completes the protocol and adds $\yissue$ to $L$.
 \item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
@@
 \begin{theorem}[Traceability of \CUASGS]
-  If the base \CUASGen construction has unforgeable signing according to
-  \defref{def:sign-forge-uas}, then \CUASGS is a traceable group signature
-  scheme.\markulf{Hiding of $Com(\usk;0)$?}
+  If the base \CUASGen construction is unforgeable according to
+  \defref{def:forge-uas}, then \CUASGS is a traceable group signature scheme.
 \end{theorem}
@@
 \item[$1/0 \gets Verify(R,\Sig,\msg)$.] Parses \Sig as $(\sig,\yeval)$ and
-  runs $\Verify(\opk,\yeval=\lbrace \ipk_i\rbrace_{i\in\dattrs},\sig,\yeval,
-  \msg,\feval^{\sring,\dattrs})$ as in $\CUASGen^{hide-iss}$.
+  runs $\Verify(\opk,\yeval,\Sig,\msg,\feval^{\sring,\dattrs})$ as in
+  $\CUASGen^{hide-iss}$. Note that, in valid signatures, $\yeval = \lbrace
+  \ipk_i\rbrace_{i\in\dattrs}$.
 \end{description}
@@
 \begin{theorem}[Anonymity of \CUASRing]
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASRing is an anonymous ring signature
-  scheme.
+  If the base $\CUASGen^{hide-iss}$ construction has signature anonymity
+  according to \defref{def:sign-anonymity-uas}, then \CUASRing is an anonymous
+  ring signature scheme.
 \end{theorem}
@@
 $HU, CU, ObtIss, Obtain, Issue, Show$, and $LoR$ oracles, which are essentially
-equivalent to our \UGEN, \UCORR, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb
+equivalent to our \HUGEN, \CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb
 oracles\footnote{The $CU$ oracle in \cite{fhs19} actually allows the adversary
@@
 %   \CUASGen construction. Returns $\parm \gets (\parm',\opk)$.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] $\parm' \gets
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] From \CUASGen, run $\parm' \gets
   \Setup(1^\secpar)$ and $(\opk,\osk) \gets \OKeyGen(\parm',
-  \finsp^0)$ from \CUASGen, and sets $\parm \gets (\parm',\opk)$. Then,
-  runs \IKeyGen, also from \CUASGen, setting $\fissue^1$ as issuance function.
-\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \UKeyGen from \CUASGen.
+  \finsp^0)$, and set $\parm \gets (\parm',\opk)$. Run $(\upk,\usk) \gets
+  \KeyGen(\parm')$ and $\ipk \gets \ISet(\upk,\usk,\fissue^1)$. Set $\isk \gets
+  \usk$.
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from \CUASGen.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
   \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
-  $\fissue^1$ as issuance function.
+  Runs $\langle \Obtain,\Issue \rangle$ from \CUASGen.
 \item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
@@
   \cred),\Verify(\ipk,\dattrs) \rangle$.]
-  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
-  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
-  open function, with \opk from \parm as opener public key.
+  Runs the interactive extension of \Sign and \Verify of \CUASGen, using
+  $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as open
+  function, with \opk from \parm as opener public key.
 \end{description}
@@
   \label{thm:forge-cuasac}
-  If the base \CUASGen construction has signature unforgeability according to
+  If the base \CUASGen construction is unforgeabile according to
   \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
@@
 encoded as attributes, to define a $(\feval,\finsp)$ function pair that: (1)
-ensures that opening outputs a one-way function of the {\cid}s concatenated with
-the verifier name; and (2) ensures that, if the {\cid}s have been added to a
-revocation list by the verifier, the verifier will know it -- and hence will be
-able to reject the signature. We first give a simple model in
+ensures that opening outputs the evaluation of a PRF of the {\cid}s concatenated
+with the verifier name; and (2) ensures that, if some {\cid} of the credentials
+used to produce a signature have been added to a revocation list by the
+verifier, the verifier will know it -- and hence will be able to reject the
+signature. We first give a simple model in
 \figref{fig:model-rac}, extending that in \secref{ssec:related-models-ac}.
@@
 Briefly, we build a revocable anonymous credential as a $(\fissue^1,
-\feval^{\dattrs,F,V,L},\finsp^{F})$-\CUASGen restriction. The \feval is
-parameterized with a one-way and collision-resistant function $F$
-(e.g., a cryptographic hash), a string identifying the verifier $V$ and a
-list $L$ of ``revocation handles'' by $V$. 
+\feval^{\dattrs,F,V,L},\finsp^{F})$-\CUASGen restriction. \feval is
+parameterized with a PRF $F$, a string identifying the verifier $V$ and a
+list $L$ of ``revocation handles'' by $V$. Note that these can be hardcoded,
+though: $F$ can be common to all verifiers, $V$ is also fixed (per verifier),
+and $L$ can be updated with some reasonable frequency -- e.g., daily -- so that
+the cost of recomputing $\feval^{\dattrs,F,V,L}$ is not high.
 %
@@
 to $0$, which the verifier interprets as ``revoked credential''. Otherwise,
-it sets $\yeval^0 \gets \dattrs(\cred)$ and $\yeval^1 \gets V$; $\yeval^1$ is
+it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
+$\yeval^1 \gets V$. $\yeval^1$ is
 then used by $\finsp^F$ to compute $\yinsp \gets (F(\yeval^1,\cidi),
@@
 it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
-Note that, in the $\feval^{\dattrs,F,V,L}$ function, $L$ is a sort of variable.
-However, each verifier $V$ may just update its own list with some reasonable
-frequency (e.g., daily), and use a pre-compiled version of
-$\feval^{\dattrs,F,V,L}$ in which $L$ is actually a constant.
 %
@@
   using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
-  $\finsp^F$ as open function.
+  $\finsp^F$ as open function. If $\yeval^0 = 0$, the signature is rejected.
 \item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
-  Gets $(\sig,\yeval)$ from the $\langle Show,\Verify\rangle$ transcript
+  Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
   \utrans, and runs \Open from \CUASGen. If $\yeval^0 \neq 0$ (i.e., the
@@
 \begin{theorem}[Unforgeability of \CUASRAC]
-  If the base \CUASGen construction has sign unforgeability according to
-  \defref{def:sign-forge-uas}, and $F$ is one-way and collision-resistant, then
+  If the base \CUASGen construction is unforgeable according to
+  \defref{def:forge-uas}, and $F$ is one-way and collision-resistant, then
   \CUASRAC is an unforgeable RAC scheme.
@@
 evaluation function that ignores the $\yeval^0$ output, and $\finsp^{\ast}$ is
-any open function. Concretely, by restricting to a system with one issuer and
-one opener, one credential per user, one attribute per credential (the user
-secret key)% , $\fissue^1$ issuance functions, and
-% \feval functions that only use the $\yeval^1$ output -- which we denote with
-% $\feval^{\yeval^1}$
-.
+any open function. Concretely, this restricts to a system with one issuer and
+one opener, one credential per user, no attributes in the credentials.
 
@@
 
-On the other hand, our issuance-related properties (issuance anonymity and
-issuance unforgeability) are unachievable by MPS. Issuance anonymity simply does
-not make sense in MPS, as it only supports one credential (without attributes)
-per user. Issuance unforgeability does not make sense either, since there are no
-configurable issuance policies in MPS -- instead, they have the fixed policy of
+On the other hand, anonymous issuance, and the capability to customize issuance
+policies are unachievable by MPS. Anonymous issuance simply does not make sense
+in MPS, as it only supports one credential (without attributes) per user.
+Customized issuance is achieved in \UAS via the \fissue functions, with no
+equivalent in MPS -- instead, MPS has the fixed policy of
 ``proving knowledge of a user secret key''. These extensions are not trivial
@@
 
-For the model of MPS schemes, we refer to the original paper \needcite.
+For the model of MPS schemes, we refer to the original paper \cite{ngsy22}.
 
@@
 As mentioned, any $(\fissue^{single,F,I},\feval^{\yeval^1},
-\finsp^\ast)$-restriction of \CUASGen with only one issuer and opener, one
-credential per user, and one attribute per credential (the user secret key),
-implements an MPS scheme where $F=\feval^{\yeval^1}$ and $G=\finsp^\ast$.
-With these functions, the construction is essentially as in
+\finsp^\ast)$-restriction implements an MPS scheme where $F=\feval^{\yeval^1}$
+and $G=\finsp^\ast$. With these functions, the construction is essentially as in
 \secref{ssec:related-models-gs}.
@@
 \begin{theorem}[Extractability of \CUASMPS]
-  If the base \CUASGen construction has signature unforgeability according to
-  \defref{def:sign-forge-uas}, then it is an extractable MPS scheme.
+  If the base \CUASGen construction is unforgeable according to
+  \defref{def:forge-uas}, then it is an extractable MPS scheme.
 \end{theorem}
@@
 \begin{theorem}[Unforgeability-1 of \CUASMPS]
-  If the base \CUASGen construction has signature unforgeability according to
+  If the base \CUASGen construction is unforgeable according to
   \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
-  defined in \needcite.
+  defined in \cite{ngsy22}.
 \end{theorem}

### 2022-08-12 prism-backend/research/gsac/app-related-proofs.tex
Updating proofs of UAS => MPS

@@
   \label{thm:anon-cuasac}
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
-  according to \cite{fhs19}.
+  If the base \CUASGen construction is anonymous according to
+  \defref{def:anonymity-uas}, then \CUASAC is an anonymous AC scheme according
+  to \cite{fhs19}.
 \end{theorem}
@@
 scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
-is anonymous and has unforgeable signing. Note that issuance unforgeability
-of \CUASGen is not needed, as the model in \cite{fhs19} does not allow
-leveraging other credentials not any fixed custom issuance policy. Thus,
-signature unforgeability from \UAS is enough. Note that AC schemes modelled
-as in \cite{fhs19} do not have issuance anonymity, as the user public key
-is passed to the issuer.
+has signature anonymity and is unforgeable.
 
@@
   If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, and $F$ is one-way and collision-resistant,
-  then \CUASAC is an anonymous AC scheme according to \cite{fhs19}.
+  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASAC is an
+  anonymous AC scheme according to \cite{fhs19}.
 \end{theorem}
@@
 
-  First observe that, given a revocation handle $F(V,id)$ extracted from any
-  credential showing, it is not possible to extract $id$, as $F$ is one-way
-  and collision-resistant.
+  First observe that, given a revocation handles $F(V,\cidi)$ and $F(V,\cidu)$
+  extracted from any credential showing, it is not possible to extract $\cidi$
+  nor $\cidu$, as $F$ is one-way.
 
@@
   oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
-  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, of \OPEN respectively.
+  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, or \OPEN, respectively.
   Note that ``translating'' the inputs from the former into inputs for the
-  latter is trivial. Also, observe that $ReqCredHandle$ essentially refuses to
-  open transcripts from challenge users (signatures, in the non-interactive
-  equivalent), as $F(V,\attrs_1(\ccid_0) \neq F(V,\attrs_1(\ccid_1)$ with
-  overwhelming probability (see the $\tyinsp \neq \yinsp$) check in
-  \figref{fig:oracles2}. Obviously, if \adv~ wins in its anonymity game, then
-  so does \advB with the same probability.
+  latter is trivial. Also, observe that $ReqCredHandle$/\OPEN essentially
+  refuses to open transcripts from challenge users (signatures, in the
+  non-interactive equivalent), as $F(V,\ccidi_0) \neq F(V,\ccidi_1)$ (and,
+  similarly, for $\ccidu_b$) with overwhelming probability (see the $\tyinsp
+  \neq \yinsp$) check in \figref{fig:oracles2}. Obviously, if \adv~wins in its
+  anonymity game, then so does \advB with the same probability.
   % 
@@
 \begin{theorem}[Unforgeability of \CUASRAC]
-  If the base \CUASGen construction has sign unforgeability according to
-  \defref{def:sign-forge-uas}, and $F$ is one-way and collision-resistant, then
+  If the base \CUASGen construction has unforgeability according to
+  \defref{def:forge-uas}, and $F$ is one-way, then
   \CUASRAC is an unforgeable RAC scheme.
@@
 \begin{proof}
-  Given \adv~ against unforgeability of \CUASRAC as defined in
-  \figref{fig:model-rac}, we build an adversary \advB against sign
-  unforgeability of \CUASGen as defined in \defref{def:sign-forge-uas}.
+  Given \adv~against unforgeability of \CUASRAC as defined in
+  \figref{fig:model-rac}, we build an adversary \advB against unforgeability of
+  \CUASGen as defined in \defref{def:forge-uas}.
 
   To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
-  that \adv~ wins its game via the winning condition of line 6 in the RAC
+  that \adv~wins its game via the winning condition of line 7 in the RAC
   unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
-  that the probability of \adv~ winning its game via the winning condition at
+  that the probability of \adv~winning its game via the winning condition at
   line 9 is negligible, due to soundness of the NIZK scheme used for signing,
-  and the one-wayness and collision-resistance of $F$ in
-  $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.
+  and the one-wayness of $F$ in $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.
   % 
@@
 
-As stated, we restrict to privacy-1 of MPS. Unforgeability-1 in MPS is
-equivalent to sign unforgeability in \UAS. Unforgeability-2 in MPS is
-equivalent to non-frameability in \UAS. Finally note that, in UAS, we do not
+As stated, we restrict to privacy-1 of MPS (although, as discussed, we actually
+achieve something slightly stronger). Unforgeability-1 in MPS is
+implied by unforgeability in \UAS (where the latter also covers unforgeability
+of \fissue evaluations, plus verifiable openings). Unforgeability-2 in MPS is
+equivalent to non-frameability in \UAS (where the latter also includes
+framing via verifiable openings). Finally note that, in UAS, we do not
 explicitly model extractability, but rather make it an inherent requirement in
@@
 \begin{proof}  
-  The proof is direct, by observing that the models are equivalent.
+  Note that the privacy-1 game in MPS and the signature anonymity game in \UAS
+  are, in essence, equivalent. Thus, given an adversary \adv~that breaks
+  privacy-1 of \CUASMPS as defined for MPS, it is easy to build an adversary
+  \advB breaking signature anonymity of the underlying \CUASGen, as defined in
+  \UAS.
 
-  First, note that, in MPS the adversary is required to output a function $F$,
-  challenge message, and a pair of user secret keys and witnesses (in \UAS, the
-  witnesses are the credentials). This is precisely what \CHALb requires as
-  input in our \UAS modelling.
+  \advB simply leverages its own oracles in order to answer oracle queries from
+  \adv: $\mathcal{O}_{read},\mathcal{O}_{write},\mathcal{O}_{CU},\mathcal{O}_{HU},
+  \mathcal{O}_{sig},\mathcal{O}_{open}$ in MPS correspond to \RREG, \WREG,
+  \CUGEN, \HUGEN, \SIGN and \OPEN in \UAS, respectively. The output given by
+  \adv~in the first stage of the MPS game is then directly used as input to
+  \advB's \CHALb oracle. Finally, \advB outputs whatever \adv~outputs.
 
-  Next, in MPS, validity of the output of $F$ is checked. In MPS, this
-  translates to checking that $F$ does not ouptut $0$. In UAS, this is checked
-  in the \SIGN and \CHALb oracles, which abort if the output produced by \feval
-  does not belong in \rngfeval -- a well defined set of acceptable outputs by
-  the chosen \feval.
-
-  The MPS adversary is then allowed to make more oracle queries, and outputs a
-  response bit. Just as in \UAS. Thus, if \CUASMPS satisfies signature
-  anonymity, it is also an MPS scheme satisfying privacy-1.  
+  Since the simulation is direct, it is easy to see that, whenever \adv~wins,
+  so does \advB.
   % 
@@
 \begin{theorem}[Extractability of \CUASMPS]
-  If the base \CUASGen construction has signature unforgeability according to
-  \defref{def:sign-forge-uas}, then it is an extractable MPS scheme.
+  If the base \CUASGen construction has non-frameability according to
+  \defref{def:frame-uas}, then \CUASMPS is an extractable MPS scheme.
 \end{theorem}
@@
 \begin{proof}  
-  The proof is direct, as the conditions checked in the extractability
-  experiment in MPS are also checked in the signature unforgeability experiment
-  for \UAS.
+  The proof is direct, as the winning conditions in the extractability
+  experiment in MPS are also winning conditions in the non-frameability
+  experiment for \UAS. That is, an adversary \adv~against extractability of
+  \CUASMPS, as defined in MPS, can be used to build an adversary \advB breaking
+  non-frameability of \CUASGen, as defined in the \UAS model.
 
-  Concretely, \Verify must accept the signature, and the ouptut of \feval and
-  \finsp, computed with the values extracted by \ExtractSign, must respectively
-  match those output by the adversary (for \feval), and computed honestly by the
-  signature unforgeability (for \finsp).  
+  \advB simulates \adv's game essentially as in the privacy-1 proof. Note also
+  that \adv~receives the issuer's secret key. This can be obtained by \advB via
+  its \ICORR oracle. Eventually, \adv~outputs a $(F,M,\Sigma)$ tuple, which
+  corresponds to $(\feval^{g,MPS},\msg,\Sig)$ (with $g=F$ in MPS) in \CUASGen,
+  which \advB outputs in its own game. In addition, \advB outputs as $(\yinsp,
+  \pi)$ values the output of \Open over $(\Sig,\msg)$ -- which internally
+  computes $\finsp^{h,MPS}$, for $h=G$ in MPS.
+  % 
+  Note that the $\feval^{g,MPS}$ and $\finsp^{h,MPS}$ functions in \CUASMPS
+  mimic the behaviour of MPS's $F$ and $G$, respectively. Thus, if \adv wins
+  because $F$ returns $0$ when evaluated on the extracted values, then \advB
+  wins at line 7 of the non-frameability game, as a legitimately computed
+  $\feval^{g,MSP}$ function cannot output $0$. Similarly, if \adv~wins because
+  the value returned by an honestly computed open function over the adversarial
+  $(F,M,\Sigma)$ tuple does not match the output of $G$ over the extracted
+  values, \advB wins at line 9: note that \advB returns the \yinsp value that
+  \Open outputs (when computed honestly over \adv's output), whereas
+  $\finsp^{g,MSP}=G$; thus, if both values differ in \adv's game, then they also
+  differ in \advB's game.
+  %
   \qed
@@
 \begin{theorem}[Unforgeability-1 of \CUASMPS]
-  If the base \CUASGen construction has signature unforgeability according to
-  \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
-  defined in \cite{ngsy22}.
+  If the base \CUASGen construction is unforgeable according to
+  \defref{def:forge-uas}, then \CUASMPS satisfies unforgeability-1 as defined in
+  \cite{ngsy22}.
 \end{theorem}
@@
 \begin{proof}
-  For an MPS scheme to satisfy type-1 unforgeability, it has to be extractable.
-  This is directly satisfied by signature unforgeability in \UAS.
-  %
-  Next, the adversary wins in the unforgeability-1 MPS experiment if it manages
-  to produce a signature that has not been produced via a call to their \SIGN
-  oracle, nor it can be associated to an corrupt user. Indeed, if that happens,
-  then such adversary can be used to build an adversary winning the signature
-  unforgeability game against \CUASMPS, through winning condition at line 12 --
-  as \IdentifySig does not return 1 for any known \uid. Thus, if \CUASMPS has
-  signature unforgeability, it also satisfies unforgeability-1 of MPS schemes.
+  Given an adversary \adv~against unforgeability-1 of \CUASMPS, as defined in
+  the MPS model, we build \advB that breaks unforgeability of the underyling
+  \CUASGen, as defined for \UAS.
+
+  Simulation of \adv's oracles by \advB is again direct (as in previous proofs).
+  Now, suppose that \adv~wins. Then, by assumption, the identity extracted by
+  \adv~(which maps to a $\cid$ for \advB), does not belong to the set of corrupt
+  users in \adv's game. By construction of \advB, then, $\OWNR[\cid] \notin \CU$
+  in \advB's unforgeability game.
+  \todo{The following seems wrong.}
+  But it cannot belong to an honest user either,  
+  as \adv's signature does not exist in \SIG. Otherwise, suppose it belongs to
+  an honest user (in list \HU of \advB's game). Then, it breaks one-more
+  unforgeability of the \SBCM scheme used by \CUASGen, as it is a valid.
   %
@@
 \begin{proof}
-  For an MPS scheme to have type-2 unforgeability, it has to be extractable.
-  This is directly satisfied by non-frameability in UAS (a similar reasoning
-  as for signature unforgeability and extractability applies here).
+  Given an adversary \adv~against unforgeability-2 of \CUASMPS, as defined in
+  the MPS model, we build \advB that breaks non-frameability of the underyling
+  \CUASGen, as defined for \UAS.
+
+  Simulation of \adv's oracles by \advB is as in the unforgeability-1 proof.
+  \advB outputs whatever \adv~outputs, adding a $(\yinsp,iproof)$ pair, honestly
+  generated from \adv's output. Note that the winning condition of \adv~
+  requires that the produced signature belongs to an honest user, without
+  having been produced via a call to the signing oracle. By construction of
+  \advB, this directly makes \advB win in line 11 of the non-frameability game.
   %
-  Next, in MPS, the adversary wins if the produced signature has not been
-  output by the \SIGN oracle, but Extract outputs the identifier of an honest
-  user. This is the same check done in lines 9 and 10 of the non-frameability
-  game in \UAS. Therefore, if \CUASMPS satisfies non-frameability as defined in
-  \defref{def:frame-uas}, it also satisfies type-2 unforgeability in MPS.
   \qed

### 2022-08-12 prism-backend/research/gsac/app-uas-proofs.tex
Updating proofs of UAS => MPS

@@
   \uid exists (but not because more than one \cid belongs to different {\uid}s).
-  Assume that no such \uid exists. Such a signature breaks the one-more
-  forgery property of \SBCM, as it has not been produced via a call to \SIGN
-  (it is not in $\SIG$). Therefore, the probability that \adv~wins at line 14 is
-  negligible, given simulation extractability of $\NIZK^{\Sign}$, and
-  correctness and one-more forgery security of \SBCM.
+  Assume that no such \uid exists. Then, the {$\cred_i$}s extracted by
+  \ExtractSign cannot have been produced via a call to either \OBTISS or \ISSUE,
+  since they only accepts calls from known {\uid}s (either in \HU or \CU,
+  respectively). Since, by simulation extractability of $\NIZK^{\Sign}$, at
+  least one such credential must have been used to produce the signature, then
+  this breaks the one-more forgery property of the underlying \SBCM.
   %

### 2022-08-12 prism-backend/research/gsac/formal-uas.tex
Updating proofs of UAS => MPS

@@
   consistent with other works -- e.g., Camenisch, Krenn, Lehmann...}
+\todo{Require that $n>=1$ in the creds used to produce a signature...}
 
@@
 generalization of the information output at opening time ($\yinsp$), only
-present up to know in MPS \needcite what makes the notion of unforgeability more
-subtle. The fact that multiple users may produce signatures opening to the same
-value necessarily forces to generalize what is a forgery -- and, certainly,
+present up to know in MPS \cite{ngsy22} what makes the notion of unforgeability
+more subtle. The fact that multiple users may produce signatures opening to the
+same value necessarily forces to generalize what is a forgery -- and, certainly,
 resorting to extraction-based techniques seems unavoidable.

### 2022-08-12 prism-backend/research/gsac/relationships.tex
Updating proofs of UAS => MPS

@@
         & \hspace*{2em}\pcelse \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},V)
-        \nonumber   
+          \nonumber \\
+        & \feval^{g,MPS}(\upk,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},\msg)
+          \coloneqq \nonumber \\
+        & \hspace*{2em}\pcif g(\upk,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},
+          \msg) = 0: \pcreturn \bot \nonumber \\
+        & \hspace*{2em}\pcelse \pcreturn (\ast,g(\upk,\lbrace
+          (\cid_i,\attrs_i) \rbrace_{i\in[n]},\msg)) \nonumber
       \end{align}
@@
         & \hspace*{2em}\pcelse \pcreturn 0
-          \nonumber
+          \nonumber \\
+        & \finsp^{h,MPS}((\cdot,\yeval^1),\upk,\cid,\attrs,\cdot) \coloneqq
+          \pcreturn h(\yeval^1,\upk,\cid,\attrs) \nonumber         
       \end{align}
@@
     ignored; and ``$\ast$'' to denote output values that can be set to anything
-    (but should be ignored).}
-    % $\attrs(\cred)$ returns all attributes in \cred. $\dattrs(\cred)$ returns
-    % $\dattrs \subseteq \attrs(\cred)$. $\attrs_i(\cred)$ returns $i$-th
-    % attribute in \cred. $\ast$ means the output is ignored (in these examples,
-    % we use this to mean that $\yeval^1$ is unused. $\bot$ means the function
-    % fails.}
+    (but should be ignored). $\bot$ means that the function fails.}
   \label{fig:func-restrictions}
@@
   If the base \CUASGen construction is unforgeabile according to
-  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
+  \defref{def:forge-uas}, then \CUASAC is an unforgeable AC scheme.
   \markulf{Hiding of $pk_U$?}
@@
 which generates the opener key pair, extend $Verify$ to receive also a list $L$
-of revoked identifiers, and we add a function (and corresponding oracle) $id/\bot
-\gets RetrieveCredId(\osk,\utrans)$ that can extract the identifier of the
-credential used in a presentation transcript \utrans -- and which is essentially
-equivalent to \Open in \UAS. For simplicity, we do not include the equivalent to
-verifiable openings, but this would be straightforward.
+of revoked credential identifiers, and we add a function (and corresponding
+oracle) $cid/\bot \gets RetrieveCredId(\osk,\utrans)$ that can extract an
+identifier of the credential used in a presentation transcript \utrans -- and
+which is essentially equivalent to \Open in \UAS. For simplicity, we do not
+include the equivalent to verifiable openings, but this would be
+straightforward.
 
@@
     equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
-    Also, \OWNR and \ATTR tables are essentially as in \secref{ssec:model-uas}.}
+    In particular, this implies that it rejects queries for transcripts related
+    to challenge users. Also, \OWNR and \ATTR tables are essentially as in
+    \secref{ssec:model-uas}.}
   \label{fig:model-rac}  
@@
 
-\begin{theorem}[Issuance anonymity of \CUASRAC]
-  \todo{review}
+\begin{theorem}[Anonymity of \CUASRAC]
   If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, and $F$ is one-way and collision-resistant,
-  then \CUASAC is an anonymous AC scheme according to \cite{fhs19}.  
+  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASRAC is an
+  anonymous AC scheme according to \cite{fhs19}.  
 \end{theorem}
@@
   If the base \CUASGen construction is unforgeable according to
-  \defref{def:forge-uas}, and $F$ is one-way and collision-resistant, then
-  \CUASRAC is an unforgeable RAC scheme.
+  \defref{def:forge-uas}, and $F$ is one-way, then \CUASRAC is an unforgeable
+  RAC scheme.
 \end{theorem}
+
+Note that, if we aim at global credential (resp. user) revocation rather than
+verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
+pair (resp., \upk), and no assumption regarding $F$ is needed.
 
@@
 \finsp^\ast)$-restriction implements an MPS scheme where $F=\feval^{\yeval^1}$
-and $G=\finsp^\ast$. With these functions, the construction is essentially as in
-\secref{ssec:related-models-gs}.
+and $G=\finsp^\ast$. With these functions, the construction is direct.
+\CUASMPS's setup runs \CUASGen's \Setup, \OKeyGen, and generates the issuer key
+pair by running \KeyGen and \ISet (with $\fissue^1$). For MPS's join, \CUASMPS
+runs first \KeyGen to generate the user key pair, and then proceeds as in
+\CUASGen. \Sign, \Verify and \Open, are as in \CUASGen.
 %
@@
 and is not leaked to the opener nor any other third party. The equivalent in
-\UAS is the $\yeval^1$ value, which is encrypted with a single-use key pair, and
-is an input of \yinsp.
+\UAS is the $\yeval^1$ value which, in \CUASGen, is encrypted with a single-use
+key pair, and is an input of \yinsp.
 

### 2022-08-13 prism-backend/research/gsac/app-related-proofs.tex
Updated proofs for UAS=>MPS.

@@
   Simulation of \adv's oracles by \advB is again direct (as in previous proofs).
-  Now, suppose that \adv~wins. Then, by assumption, the identity extracted by
-  \adv~(which maps to a $\cid$ for \advB), does not belong to the set of corrupt
-  users in \adv's game. By construction of \advB, then, $\OWNR[\cid] \notin \CU$
-  in \advB's unforgeability game.
-  \todo{The following seems wrong.}
-  But it cannot belong to an honest user either,  
-  as \adv's signature does not exist in \SIG. Otherwise, suppose it belongs to
-  an honest user (in list \HU of \advB's game). Then, it breaks one-more
-  unforgeability of the \SBCM scheme used by \CUASGen, as it is a valid.
+  Now, suppose that \adv~wins -- i.e., the identity extracted by \adv~does not
+  belong to the set of corrupt users in \adv's game. By construction of \advB
+  (identities in \adv's game map to a $\cid$ for \advB), $\OWNR[\cid] \notin
+  \CU$ in \advB's unforgeability game either.
+  % 
+  However, in order for \advB to win in its own game, we need to prove also that
+  the produced identity does not belong to a user in \HU either. Suppose that it
+  does. Simulation extractability ensures that the credentials extracted by
+  \adv~all belong to the same user (by assumption, in \HU) -- i.e., they are
+  bound to its \usk. Moreover, since \adv~wins its game, the signature output by
+  \adv~has not been obtained via its \SIGN oracle. But, given that the user is
+  honest, its \usk has been produced uniformly at random, and has not been
+  leaked to \adv~(as the issuer is also honest). Thus, the probability that
+  the extracted credentials belong to an honest user is negligible and, if
+  \adv~wins its game, \advB also does.
   %
@@
   Simulation of \adv's oracles by \advB is as in the unforgeability-1 proof.
-  \advB outputs whatever \adv~outputs, adding a $(\yinsp,iproof)$ pair, honestly
+  \advB outputs whatever \adv~outputs, adding a $(\yinsp,\iproof)$ pair, honestly
   generated from \adv's output. Note that the winning condition of \adv~

### 2022-08-13 prism-backend/research/gsac/app-uas-proofs.tex
Updated proofs for UAS=>MPS.

@@
 
-  \paragraph{(e) All {\cred}s are bound to the same \usk.} %
+  \paragraph{(e) All {\cred}s are bound to the \usk of a known \uid.} %
   $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
@@
   \ExtractSign cannot have been produced via a call to either \OBTISS or \ISSUE,
-  since they only accepts calls from known {\uid}s (either in \HU or \CU,
+  since they only accept calls from known {\uid}s (either in \HU or \CU,
   respectively). Since, by simulation extractability of $\NIZK^{\Sign}$, at
@@
 \begin{proof}[\thmref{thm:frame-uas}; Non-frameability of \CUASGen]
+  \label{prf:frame-uas}
 
@@
 
-  First, suppose that the \Sig that \adv~outputs at line 2 exists in \SIG, for
-  some \uid. In that case, the signature is accepted by \Verify at
-  line 3, and after simulation extractability of $\NIZK^{\Sign}$, $\yeval =
-  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, if the $(\yinsp,\iproof)$
+  Since the signature output by \adv~is accepted by \Verify at line 4,
+  simulation extractability of $\NIZK^{\Sign}$ ensures that $\yeval = \yeval^0$,
+  and $\tyeval^1 = \yeval^1$. Similarly, if the $(\yinsp,\iproof)$
   pair output by \adv~is accepted by \Judge, simulation extractability of
-  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 7 and 8
-  pass. Hence, the probability that the adversary wins at either lines 7 or 8 is
+  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 8 and 9
+  pass. Hence, the probability that the adversary wins at either lines 8 or 9 is
   negligible, after simulation extractability of $\NIZK^{\Sign}$ and
@@
   Next, we prove that, after zero-knowledge and simulation extractability of
-  $\NIZKRel_{\Sign}$, and blindness of \SBCM, $\Sig \in \SIG$ except with
-  negligible probability.
+  $\NIZKRel_{\Sign}$, and blindness of \SBCM, no credential from an honest user
+  can be extracted from the signature output by \adv, except with negligible
+  probability.
   %
@@
   witness for $(\msg,\feval,\yeval^0,\cinsp,\lbrace ipk_i \rbrace_{i\in[n]},
-  \Eek)$. Note that this witness must include some \usk which,
-  for \adv~to win the game, must belong to an honest user. However, since the
-  user (whichever it is) has not been corrupted, its \usk has not been leaked
-  to \adv~via corruption queries (nor via \SIGN queries, where the proof of
-  knowledge within \Sign is now simulated). Moreover, blindness of \SBCM ensures
-  that the issuer (who is potentially corrupt), did not learn \usk either during
-  calls to \OBTAIN. Thus, the probability that $\UK[\uid] = \usk$ for $\uid \in
-  \HU$ and \Sig produced by the adversary, is negligible.
+  \Eek)$. Note that this witness must include some \usk which, in case of
+  being owned by an honest user, has not been leaked to \adv~--as the user
+  has not been corrupted, nor the \usk has been leaked via \SIGN queries,
+  where the proof of knowledge within \Sign is now simulated). Moreover,
+  blindness of \SBCM ensures that the issuer (who is potentially corrupt), did
+  not learn \usk either during calls to \OBTAIN. Thus, since \usk is picked
+  uniformly at random by honest users, the probability that $\UK[\uid] = \usk$
+  for $\uid \in \HU$ and \Sig produced by the adversary, is negligible.
   %

### 2022-08-13 prism-backend/research/gsac/app-related-proofs.tex
Added proof sketch for hide-iss.

@@
   answers $\adv$'s $SIGN(i,R,\msg)$ queries as follows. If user $i$ has not yet
-  produced a credential for ring $\pk_i \in R$, \advB makes a call to its
-  \OBTAIN oracle, using $R$ as attribute set. If such a credential was already
+  produced a credential for ring $R$, where $\pk_i \in R$, \advB makes a call to
+  its \OBTAIN oracle, using $R$ as attribute set. If such a credential was already
   produced, \advB simply reuses it. Then, \advB uses the corresponding user and
@@
   in \advB's non-frameability game. Also, since $\adv$ never queried its $SIGN$
-  oracle, then by construction there cannot exist a matching entry in the
+  oracle, then by construction there cannot exist a matching entry in \advB's
   $\SIG[\uid]$ table. Thus, \advB wins the non-frameability game whenever

### 2022-08-13 prism-backend/research/gsac/app-uas-proofs.tex
Added proof sketch for hide-iss.

@@
   user. But then, $\cred_i$ cannot have been produced via \OBTISS or \ISSUE,
-  which only accept request from known {\uid}s (either in \HU or \CU,
+  which only accept requests from known {\uid}s (either in \HU or \CU,
   respectively). Thus, $\cred_i$ is a valid \SBCM signature, that has not been
@@
 
+\subsection{Security of $\CUASGen^{hide-iss}$}
+\label{sapp:sec-hide-iss}
+
+The only aspect that changes from \CUASGen to $\CUASGen^{hide-iss}$ is the
+relationship used for signing, where we hide the specific issuer who produced
+the (now only) credential used for signing.
+%
+This change does not affect the proofs for issuance anonymity, nor signature
+anonymity.
+%
+Concerning unforgeability, note that the credential that is used to produce the
+\UAS signature still needs to originate from a \uid in either \HU or \CU.
+Otherwise, such credential, extracted by \ExtractSign, is a forgery and breaks
+the one-more forgery property of \SBCM. Moreover, such credential must exist,
+due to simulation extractability of the underlying NIZK.
+%
+The proof for non-frameability is also unaffected by the change.
+
+Thus, if \CUASGen is a secure \UAS scheme, so is $\CUASGen^{hide-iss}$.
+
 %%% Local Variables:

### 2022-08-13 prism-backend/research/gsac/formal-uas.tex
Updated proofs for UAS=>MPS.
Added proof sketch for hide-iss.

@@
       \adv^{\Oframe}(\parm) \\
+      \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\msg,\feval) \in
+      \SIG[\uid]: \pcreturn 0 \\
       \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
@@
       \pcind \pcreturn 1 \\
-      \textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
-      \pcif \OWNR[\scid] \in \HU \land
-      (\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\OWNR[\scid]]: \\
-      \pcind \pcreturn 1 \\
+      %\textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
+      \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \in \HU: % \land
+      %(\cdot,\cdot,\Sig,\Yeval,\msg,\feval) \notin \SIG[\OWNR[\scid]]: \\
+      \pcreturn 1 \\
       \pcreturn 0
@@
 %
-Modelling-wise, no changes are needed. Perhaps notably, in this case, the
+Modelling-wise, no changes are needed. Perhaps notably, even in this case, the
 anonymity property is still required to enforce that both challenge signatures
 are associated to the same set of (potential) issuers -- otherwise, it is
-trivial to distinguish signatures.
+trivial to distinguish signatures. Security for $\CUASGen^{hide-iss}$, based on
+security of \CUASGen, is sketched in \appref{sapp:sec-hide-iss}.
 
@@
 
-\paragraph{Interactive Credential Presentation.}
+\paragraph{Interactive Credential Presentations.}
 \todo{Does this meet the model? If not, we should move this elsewhere.}

### 2022-08-16 prism-backend/research/gsac/app-uas-proofs.tex
Added proof sketch for interactive variant.

@@
 
+\subsection{Security of $\CUASGen^{int}$}
+\label{sapp:sec-interactive}
+
+\paragraph{Issuance Anonymity.} Since issuance anonymity is independent of
+whether signature/authentication is interactive or not, the proof for issuance
+anonymity in $\CUASGen^{int}$ is the same as for \CUASGen.
+
+\paragraph{Signature Anonymity.} To see why the interactive variant has
+signature anonymity, assume an adversary \adv~that breaks it. We build \advB
+against the non-interactive \ExpSigAnonb from \adv~as follows. \advB initializes
+everything as in the \ExpSigAnonb game. When \adv~initiates a call to its
+interactive \SIGN (resp. \CHALb) oracle, \advB forwards it to its own oracle
+(but concatenating the random number to the message to be signed). \advB
+forwards the response from its oracle to \adv. After such simulation, \advB just
+outputs whatever $\adv$ outputs. Clearly, the simulation is perfect and, if
+\adv~wins with non-negligible probability in the interactive case, then so
+does \advB in the non-interactive case. Specifically, note that, since the \Sign
+algorithm is probabilistic, even if a malicious verifier picks the same random
+number in several queries (to the same or different users), the result will be
+indistinguishable with overwhelming probability.
+
+\paragraph{Unforgeability and non-frameability.} The simulation described for
+the anonymity case (i.e., \advB choosing the random numbers, and concatenating
+them to the message to be signed by the oracle) applies here too. Since the
+interactive protocol includes non-interactive proofs for the $\NIZKRel^{\Sign}$
+and $\NIZKRel^{Open}$ relations, the proofs for unforgeability and
+non-frameability of \CUASGen still apply.
+
 %%% Local Variables:

### 2022-08-16 prism-backend/research/gsac/formal-uas.tex
Added proof sketch for interactive variant.

@@
 construction. Namely: $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
-$\NIZKRel_{\Open}$, described next and specified in CS notation \needcite
+$\NIZKRel_{\Open}$, described next and specified in CS notation \cite{cs97}
 in \figref{fig:nizkrels}.
@@
 
-\paragraph{Interactive Credential Presentations.}
-\todo{Does this meet the model? If not, we should move this elsewhere.}
-In \appref{app:interactive-uas}
-we show how to convert the non-interactive signing and verification processes
-into an interactive protocol. While the transformation is quite straightforward,
-it is of high relevance for real world use cases.
+\paragraph{$\CUASGen^{int}$: Interactive Credential Presentations with replay
+  protection.}
+%
+In group signatures, signing and verification are non-interactive processes;
+whereas in anonymous credentials, they are an interactive protocol. \CUASGen
+targets the non-interactive approach. Now, we sketch how to transform this into
+an interactive protocol that ensures replay protection.
+
+Modelling-wise, this requires to replace the \Sign and \Verify functions with
+a single $\langle 1/0,(\yeval,\utrans_{\Sig})/\bot \rangle \gets \langle
+\Sign(\usk,\opk,\sCred,\msg,\feval), \Verify(\opk,\sipk,\msg,\feval) \rangle$,
+where $\utrans_{\Sig}$ is the transcript of the protocol, and is logged now in
+an equivalent of the \SIG table (\CSIG for challenge transcripts). The \SIGN
+and \CHALb oracles now also accept a random value from the adversary, but
+are otherwise adapted in the natural way, where the signer is always honest, but
+the verifier is played by the adversary (e.g., similar to the \OBTAIN oracle).
+
+The construction is also simple. Basically, prior to signing the message, we
+require that the verifier sends to the user a number picked uniformly at random
+from an appropriate domain, which must be concatenated to the signed message. If
+there is no need to actually sign a message, then the message is set to an empty
+string, and the user only signs the random number.
+%
+If the logic within the \feval and \finsp functions needs to ignore the random
+value $rnd$ sent by the verifier, note that it is trivial to transform these
+functions so that they treat the message concatenated with $rnd$ as a pair
+$(\msg,rnd)$, and simply ignore $rnd$.
+
+We sketch security of $\CUASGen^{int}$ in \appref{sapp:sec-interactive} assuming
+the same security properties as in \UAS. Note that extra properties may be
+needed in some scenarios. For instance, informally, the non-interactive version
+does not provide deniability and, thus, our transform to the interactive case
+does not provide it either. On the other hand, transferability is possible in
+both cases, which may be useful, e.g., in situations where chaining multiple
+requests is needed.
+%
+However, since probably the most common use of interactive presentations simply
+worry about preventing replay attacks, we leave a more detailed analysis of
+possible transforms (still meeting the \UAS model) out of scope.
 

### 2022-08-16 prism-backend/research/gsac/introduction-paper.tex
Added proof sketch for interactive variant.

@@
 AC systems, depending on the transformation supported by the malleable
-signatures. In GS, very recently, BiAS \cite{lnpy21} and MPS \needcite~
+signatures. In GS, very recently, BiAS \cite{lnpy21} and MPS \cite{ngsy22}
 flexibilize the trade-off between anonymity and accountability.
@@
 anonymous credentials. This includes not only their vanilla versions, but also
-relevant variants, such as MPS \needcite, (a modified version of) group
+relevant variants, such as MPS \cite{ngsy22}, (a modified version of) group
 signatures with message-dependent opening \cite{seh+12}, or anonymous

### 2022-08-17 prism-backend/research/gsac/formal-uas.tex
Applying changes after pass.

@@
 
-\jesus{Adding a \uid into \HU or \CU within an oracle that is executed by end
-  users in the real world is a bit weird if not clarified. Some arguments may
-  be possible.}
-
 % [11 pages max]
@@
 (\UAS). We define its syntax, model, and give a generic construction, which
-we prove secure according to our model.
+we prove secure.
 
@@
 generation times, including the information that an opener will be able to
-extract from a signature. This flexibilizes the scheme even beyond the loose
-relationship between issuer and opener.
+extract from a signature.
 
@@
 modelling, we see this \emph{cryptographically} as two different users.
-
-\todo{Clarify that, for us, issuers and users are essentially the same thing.}
+This may seem too ideal to model real world situations. However, we argue that
+this can in fact be very close to reality, where a well-known issuer, after
+properly identifying a user, attests the (possibly blinded) public key this
+user proves control of. Indeed, our model and syntax support exactly this
+approach, by allowing users to leverage previously obtained credentials in
+order to request new ones.
+
+\paragraph{Users and issuers.} %
+Finally, a relevant aspect of our approach is that users and issuers are
+essentially the same thing: just an entity with a key pair. The difference is
+that, when users wish to become issuers, they have to advertise their public
+keys, along with their conditions for granting credentials. For simplicity, we
+just assume that they somehow ``publish their public keys''. In practice, this
+may be done in several ways, depending on the situation: self-signing, relying
+on external PKIs, bulletin-boards, etc.
+%
+This approach has actually been used before to model delegatable anonymous
+credentials \cite{bcc+09}, and it turns out to be also very useful for our
+approach to build ring signatures from \UAS.
 
@@
   returns a global system parameter variable \parm. We assume that \parm are
-  available to all the other functions, even if not explicitly listed in their
-  input parameters.
+  available to all the other functions.
 \item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
@@
   \rangle$.] %
-  This interactive protocol lets a user with key \usk running the \Obtain
-  process, receive a credential $\Cred=(\cid,\attrs,\cred,\ipk)$
+  This interactive protocol lets a user with key \usk receive a credential
+  $\Cred=(\cid,\attrs,\cred,\ipk)$
   from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
@@
   outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
-  the \fissue defined by the issuer, and $\utrans$ being the transcript of
-  the communication.
+  the \fissue function defined by the issuer, and $\utrans$ being the transcript
+  of the communication.
 \item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
@@
   (\sig,\yeval)$ over message \msg and evaluation function \feval,
-  generated using credentials issued by the issuers with public keys in \sipk.
+  generated using credentials by issuers with public keys in \sipk.
   If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
@@
 it is possible to modulate the behaviour of the resulting instantiation, by
-controling the conditions upon which a new credential can be issued, or the
+controling the conditions upon which a new credential can be issued, the
 information revealed at signing time, or after signing. In all cases, it is
@@
 \begin{description}
-\item[$\fissue: (\upk,\usk,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]},\attrs)
+\item[$\fissue: (\upk,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]},\attrs)
   \rightarrow \yissue$.] Chosen
@@
   defines the customized conditions required by the issuer to grant a credential
-  over attributes \attrs, when requested by a user with key pair $(\upk,\usk)$,
+  over attributes \attrs, when requested by a user with public key \upk,
   leveraging a set of $n$ previously obtained credentials with identifiers and
@@
   receive the user public key \upk, a set of credentials with identifiers
-  and attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
+  and attributes $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
   (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
@@
   we write $\Yeval = (\yeval^0,\yeval^1)$.
-\item[$\finsp: (\Yeval,\upk,\lbrace \cid_i,\cattrs_i\rbrace_{i \in [n]},
+\item[$\finsp: (\Yeval,\upk,\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]},
   \msg) \rightarrow \yinsp$.]
@@
       \pcif b=0:
-      \yissue^* \gets \fissue(\upk,\usk,\lbrace (\cidi,\cattrs_i)
+      \yissue^* \gets \fissue(\upk,\lbrace (\cidi,\cattrs_i)
       \rbrace_{i\in[n]},\attrs) \\
@@
   \label{def:uas-acc-func}
-  A \fissue function is \UAS acceptable if, for any p.p.t. adversary \adv,
+  A \fissue function is \UAS-acceptable if, for any p.p.t. adversary \adv,
   $|\Pr[\Exp^{\UAS-acc-1}_\adv(1^\secpar)=1]-\Pr[\Exp^{\UAS-acc-0}_\adv
@@
 functions. Security of \CUASGen implies security of its restrictions, as long as
-the chosen functions are \CUASGen-acceptable.
+the chosen \fissue functions are \CUASGen-acceptable.
 
@@
 necessary about the user requesting the credential. Note that this is now
-crucial for privacy since, as AC schemes, \UAS allows multiple credentials per
+crucial for privacy since \UAS allows multiple credentials per
 user -- thus, knowing what user is requesting which credential can lead to user
@@
 can be learned by third parties from a signature, beyond what the user chooses
-to reveal, and what may be extractable by the chosen opener. Issuance
-unforgeability requires that \UAS schemes ensure that the claims used to support
-a credential request cannot be falsified (issuance unforgeability). Similarly,
-signature unforgeability requires that no adversary should be able to falsify
-the correctness proofs for the claims included in the signatures. In both cases
-(issuance and signature unforgeability), we require all credentials involved in
-the corresponding process to be associated to a known user key. Finally, \UAS
-schemes inherit the useful non-frameability property of GS schemes where even
-the issuer is corrupt. In this case, we can ensure that no honest user
-can be framed with having created a signature that s/he did not create --
-although the concept may get a bit blurred, as there is no traditional opening.
+to reveal, and what may be extractable by the chosen opener. Unforgeability
+requires that \UAS schemes ensure that the claims used to support a credential
+request cannot be falsified, and that no adversary is able to falsify
+the correctness proofs for the claims included in the signatures. In addition,
+we require all credentials involved in the corresponding process to be
+associated to a known user key. Finally, \UAS schemes inherit the useful
+non-frameability property of GS schemes where even the issuer is corrupt. In
+this case, we can ensure that no honest user can be framed with having created a
+signature that s/he did not create -- although the concept may get a bit
+blurred, as there is no traditional opening.
 %
@@
 \paragraph{Global Variables.} %
-\todo{Clarify that {\iid}s are just {\uid}s.}
 Users are referred to with user identifiers, \uid; for credentials, we use \cid;
-for issuers, \iid; and for openers, \oid.  In all cases, we use bold font to
-denote sets: e.g., \scid and \siid denote sets of credential and issuer
-identifiers. All tables/sets are initialized as empty tables/sets. For
-notational convenience, we often use these identifiers instead of the
-corresponding user/issuer/opener keys.
+and for openers, \oid. Although issuers are ``extended'' users, and thus can be
+identified by their \uid, we also sometimes use \iid to refer to a user acting
+as issuer, especially, for operations involving both a user and an issuer (this
+also applies for key pairs).
+%
+All tables/sets are initialized as empty tables/sets. For notational
+convenience, we often use these identifiers instead of the corresponding
+user/issuer/opener keys.
+%
+We use the following sets and tables in our definitions:
 
 \begin{description}
-\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
-  track of honest users/issuers/openers. They are sets of
-  {\uid}s/{\iid}s/{\oid}s.
-\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Keep
-  track of corrupt users/issuers/openers. They are sets of
-  {\uid}s/{\iid}s/{\oid}s.    
-\item[\UK, \PUBUK and \PRVUK.] \UK maintains user key pairs $(\upk,\usk)$. To
-  refer to the key of a specific user, we use $\UK[\uid]$. \PUBUK indexes the
-  public keys, and \PRVUK the private keys.
-\item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
-  $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
-  use \PUBIK to refer to the public component, which also includes the \fissue
-  function; and \PRVIK refers to the private component of the key pair.
-\item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
-  of \fissue, \OK includes the \finsp function.
+\item[$\mathsf{H}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
+  honest {\uid}s/{\iid}s/{\oid}s.
+\item[$\mathsf{C}\lbrace\mathsf{U},\mathsf{I},\mathsf{O} \rbrace$.] Sets of
+  corrupt {\uid}s/{\iid}s/{\oid}s.
+\item[\UK,\IK,\OK.] Tables maintaining key pairs of users $(\upk,\usk)$, issuers
+  $(\ipk,\isk)$, and openers $(\opk,\osk)$. They are indexable by \uid,
+  \iid, and \oid, respectively. Also, issuers' public keys contain their \fissue
+  function, and openers' public keys contain their \finsp function.
+\item[\PUBUK,\PUBIK,\PUBOK and \PRVUK,\PRVIK,\PRVOK.] Shorthands referring to
+  public keys of users, issuers or openers ($\mathsf{PXK}$) or their private
+  keys ($\mathsf{SXK}$).
 \item[\CRED.] Stores information related to credentials obtained by users in
@@
   to refer to $\CRED[\cid]$ for all {\cid}s in a set \scid. Also, when clear
-  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$ to
+  from context, we sometimes use $\CRED[\cid]$ (resp. $\CRED[\scid]$) to
   mean \cred (resp. \scred) in $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,
   \cdot,\cdot)$ (resp. $\CRED[\scid]$).
-\item[\CCRED.] Like \CRED, but keeps track of challenge credentials in the
-  issuance anonymity game.
+\item[\CCRED.] Like \CRED, but tracks challenge credentials in the issuance
+  anonymity game.
 \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
@@
 \item[\OGEN.] Adds a new opener to the game, generating its key pair and
-  setting the associated evaluation and inspection functions.
+  setting its evaluation and inspection functions.
 % \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
@@
 \item[\ISET.] ``Upgrades'' an user to become an issuer, specifying its
-  associated issuance function.
-\item[\UCORR.] Corrupts an existing (and honest) user, by giving its secret
+  \fissue function.
+\item[\UCORR.] Corrupts an existing (and honest) user, giving its secret
   key to the adversary. If the user was also an issuer, it becomes a corrupt
@@
   requesting an honest issuer to produce credentials for them.
-\item[\SIGN.] Lets the adversary get signatures from credentials belonging
-  to honest users.
+\item[\SIGN.] Lets the adversary get signatures using credentials from honest
+  users.
 \item[\OPEN.] Given an honestly produced signature, outputs the result of the
@@
 {%\setlength\intextsep{\sep}
-  \begin{figure*}[htp!]
+  \begin{figure*}[ht!]
     \centering
@@
           \feval) \\
-          \cSig_{1-b} \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid],\cscid_{1-b},\msg,\feval) \\          
+          \cSig_{1-b} \gets \Sign(\PRVUK[\cuid_{1-b}],\PUBOK[\oid],\cscid_{1-b},
+          \msg,\feval) \\          
           \CSIG[\cSig_b] \gets 
@@
 \paragraph{Helper functions \SimSetup, \ExtractIssue, and \ExtractSign.}
-%, \IdentifyCred, and \IdentifySig.}
 We assume the existence of these helper functions. They are not functions
 available in the actual scheme, but rather to the challenger in the experiments
-we use to formalize security of \UAS schemes.
-% Consequently, while we introduce them here and specify some conditions they need
-% to meet, their definition is dependent on the construction.
-\todo{Better describe this when finished making changes.}
-% We fully define
-% them for our generic construction \CUASGen in \appref{app:uas-proofs}. Similar
-% techniques have been used before to prove security in privacy-preserving schemes
-% with some sort of accountability, but that do not offer conventional opening as
-% vanilla group signatures. For instance, see related works on DAA
-% \cite{bfg+11,cdl16} and group signature variants \cite{dl21,fgl21,gl19,lnpy21}.
-% More concretely, these functions are as follows:
+we use to formalize security of \UAS schemes. We introduce them here, and define
+they later for our construction.
 
@@
 \item[$\SimSetup(1^\secpar) \rightarrow (\parm,\trap)$.] Given a security
-  parameter, outputs global (simulated) parameters \parm whose distribution is
+  parameter, outputs global parameters \parm whose distribution is
   indistinguishable to that produced by the \Setup algorithm, as well as a
   trapdoor \trap.
-\item[$\ExtractIssue(\trap,\utrans) \rightarrow ((\upk,\usk),\sCred=
+\item[$\ExtractIssue(\trap,\utrans) \rightarrow (\upk,\usk,\sCred=
   \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]})$.]
@@
 \item[$\ExtractSign(\trap,\opk,\lbrace \ipk_i \rbrace_{i \in [n]},\Sig,\msg,
-  \feval) \rightarrow ((\upk,\usk),\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
+  \feval) \rightarrow (\upk,\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
   \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a signature
-  \Sig, as well as the opener identifier \oid, and the identifiers of all
+  \Sig, the opener identifier \oid, and the identifiers of all
   issuers of the credentials used to produce the signature over \msg, and for
@@
   convenience, we overload this function and use \oid and \iid instead of the
-  actual opener and issuers' key pairs.
+  actual keys.
 % \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
@@
 \label{sssec:security}
-
-\todo{All the following assumes \UAS-acceptable \fissue functions.}
-
+%
 Security of an \UAS scheme is defined in terms of anonymity, unforgeability and
@@
 
-The issuance anonymity game captures that, given polymomially many
-credential issuance interactions, the adversary gains no information about the
+The issuance anonymity game captures that, during credential issuance
+interactions, the adversary gains no information about the
 user(s) behind them. For this, we allow the adversary to control targetted
@@
 the same as with the complementary $\cred_{1-b}$ (note that any other signature
-can be open).
+can be opened).
 Intuitively, if the adversary cannot distinguish arbitrary runs with all oracles
-(provided the previous constraint) when he gets challenge credentials $\cred_b$
-from runs with credentials $\cred_{1-b}$, then the issuance protocol is
-privacy-preserving.
-
-The signature anonymity game is similar to the traditional one in GS schemes.
-It captures that the signatures produced by system users do not leak information
+(provided the previous constraints) when he gets challenge credentials
+$\cred_b$, from runs with credentials $\cred_{1-b}$, then the issuance protocol
+is privacy-preserving.
+
+Signature anonymity captures that the signatures produced by system users do not
+leak information
 about their identity beyond what is already revealed via $\yeval^0$ and what
@@
         (\parm,\trap) \gets \SimSetup(1^\secpar) \\
-        b^* \gets \adv^{\OIssAnon} (\parm) \\
+        b^* \gets \adv^{\OAnon,\OBTCHALb} (\parm) \\
         \pcreturn b^*
@@
         (\parm,\trap) \gets \SimSetup(1^\secpar) \\
-        b^* \gets \adv^{\OSigAnon} (\parm) \\
+        b^* \gets \adv^{\OAnon,\CHALb} (\parm) \\
         \pcreturn b^*
@@
   \caption{Issuance and signature anonymity experiments for \UAS schemes.
-    $\OIssAnon \gets (\lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,
-    \OO,\UU\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\OBTCHALb)$, and $\OSigAnon
-    \gets (\lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,\OO,\UU\rbrace
-    \CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$}
+    $\OAnon \gets (\lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\II,
+    \OO,\UU\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN)$.}
   \label{fig:exp-uas-anonb}
@@
 \fissue, \feval and \finsp, it is easy to see that the resulting scheme would
-have different privacy level. For instance, a scheme that has very granular
+have different privacy levels. For instance, a scheme that has very granular
 \feval outputs barely provides privacy. Or a scheme for which most signatures
@@
 
-\paragraph{Unforgeability.} \UAS inherits from AC and GS schemes two different
-notions of unforgeability: from AC schemes, the notion that no adversary can
-prove claims unless it owns credentials with the proper attributes; from GS
-schemes, that only credential owners can produce valid signatures. \UAS also
-has verifiable openings as some group signature schemes, which sits somewhere
-in between, and we must ensure that the values output by \Open are correct and
-trace back to a user with consistent credentials. All the previous is captured
-by an unforgeability property. We define this by allowing the adversary
-to call any oracle, except the one for corrupting issuers. The adversary wins if
-it produces a valid signature over some message that: (1), opens to a wrong
-value, or to a value that cannot be processed by \Judge; (2), is not consistent
-with the expected \Yeval value; or (3), cannot be associated to known
-credentials owned by a known user.
-%
-In addition, \UAS schemes allow proving claims at issuance time. Thus, we
-need to ensure that those claims cannot be forged by an adversary without the
-proper attributes. To ensure this, besides the winning conditions stated above,
-the adversary also wins the unforgeability game if the produced signature
-was produced with a credential for which the conditions required by \fissue were
-not satisfied.
+\paragraph{Unforgeability.} \UAS inherits from AC schemes the notion that no
+adversary can prove claims unless it owns credentials with the proper
+attributes -- although, in \UAS, claims can be proven at issuance time, and
+at signing time; from GS schemes, that only credential owners can produce valid
+signatures. \UAS also has verifiable openings, and we must ensure that the
+values output by \Open are correct and trace back to a user with consistent
+credentials. All the previous is captured by an unforgeability property. We
+define it by allowing the adversary to call any oracle, except the one for
+corrupting issuers. The adversary wins if it produces a valid signature that:
+(1) the produced signature leveraged with a credential for
+which the conditions required by \fissue were not satisfied; (2), opens to a
+wrong value, or to a value that cannot be processed by \Judge; (3), is not
+consistent with the expected \Yeval value; or (4), cannot be associated to
+known credentials owned by a known user.
+%
+Note that, under this definition, we do not consider a forgery a credential that
+was issued without meeting the issuance policy unless it is used to produce
+a signature accepted by \Verify. Indeed, obtaining credentials that cannot be
+used later does not seem to pose a threat in the real world. This approach,
+which greatly simplifies the modelling, has also been used before (e.g.
+\cite{ckl+15}).
 %
 \ExpForge is formally defined in \figref{fig:exp-uas-unfor}).
-
-\todo{Mention that, in this definition, a credential that does not meet \fissue
-  is not considered a forgery unless it is used to produce a signature. This is
-  consistent with other works -- e.g., Camenisch, Krenn, Lehmann...}
-\todo{Require that $n>=1$ in the creds used to produce a signature...}
 
@@
   \label{def:forge-uas}  
-  We define the advantage \AdvForge of $\adv$ against \ExpForge as $\AdvForge=
+  We define advantage \AdvForge of $\adv$ against \ExpForge as $\AdvForge=
   \Pr\lbrack\ExpForge(1^\secpar)=1\rbrack$.
@@
 In this section, we give a generic construction of an \UAS scheme, based on
-generic building blocks. We use three different NP relations in our generic
-construction. Namely: $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and
-$\NIZKRel_{\Open}$, described next and specified in CS notation \cite{cs97}
-in \figref{fig:nizkrels}.
+generic building blocks. We use three different NP relations:
+$\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and $\NIZKRel_{\Open}$, described next
+and specified in CS notation \cite{cs97} in \figref{fig:nizkrels}.
 
@@
 
-\todo{Need to make the $\cid_i$s explicity in the \SBCMVerify clauses of
-  $\NIZK^{\Issue}$ and $\NIZK^{\Sign}$.}
 \begin{figure}[ht!]
@@
 A user willing to become an issuer just sets $\ipk \gets (\upk,\fissue)$, and
-publishes \ipk.
+publishes \ipk. We assume that {\ipk}s are published in some properly (probably
+authenticated) way.
 
@@
   If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge, and the
-  public-key encryption scheme is IND-CCA secure, and \fissue is
-  \UAS-acceptable, our \CUASGen construction
+  public-key encryption scheme is IND-CCA secure, our \CUASGen construction
   satisfies signature anonymity as defined in \defref{def:sign-anonymity-uas},
@@
   extractable, the scheme for $\NIZKRel_{\Open}$ is complete, the public key
-  encryption algorithm is correct, the \SBCM scheme is correct and one-more
-  unforgeable, and \fissue is \UAS-acceptable, then our \CUASGen construction
+  encryption algorithm is correct, and the \SBCM scheme is correct and one-more
+  unforgeable, then our \CUASGen construction
   satisfies unforgeability as defined in \defref{def:sign-forge-uas}, except
@@
   If the underlying scheme for $\NIZK^{\Sign}$ is zero-knowledge and simulation
-  extractable, the scheme for $\NIZK^{\Open}$ is simulation-extractable, the
-  \SBCM scheme is blind, and \fissue is \UAS-acceptable, then our \CUASGen
+  extractable, the scheme for $\NIZK^{\Open}$ is simulation-extractable, and the
+  \SBCM scheme is blind, then our \CUASGen
   construction satisfies non-frameability as defined in \defref{def:frame-uas},
@@
 
-In previous subsections, we have described a main construction for \CUASGen,
-where generalization is achieved by allowing system designers to specify
-concrete \fissue, \feval and \finsp functions depending on their needs. Note
-however that alternative constructions are of course possible that, while
-still meeting the \UAS model, may differ from \CUASGen. We briefly one such
-variant next, that we leverage to build related schemes.
-\todo{Security proofs are deferred to \appref{app:uas-variants-proofs}.}
-
-% \paragraph{$\CUASGen^{usr-iss}$: Collapsing issuers and users.} %
-% On occasions, it may be useful to not make a distinction between issuers and
-% users. For instance, for credential delegation, or in decentralized identity
-% systems. In both cases, users may end up acting as issuers themselves. The
-% algorithms are as in \CUASGen, except that there is no \UKeyGen -- or, rather,
-% the steps run by \UKeyGen are exactly the same as in \IKeyGen. Concretely,
-% $\usk \gets \isk$ and $\upk \gets \ipk$, where \isk and \ipk are generated
-% as in \IKeyGen.
+In previous subsections, we have described our main construction \CUASGen. 
+However, alternative constructions are of course possible that, while
+still meeting the \UAS model, may differ from \CUASGen. We describe one such
+variant next $\CUASGen^{hide-iss}$, that we leverage to build related schemes.
+%
+Similarly, we describe $\CUASGen^{int}$ which transforms \CUASGen by turning the
+non-interactive signature and verification processes into an interactive
+protocol. Strictly speaking, the model changes, but the needed modifications
+are minimal.
+%
+Security proofs are deferred to \appref{app:uas-proofs}.
 
 \paragraph{$\CUASGen^{hide-iss}$: $\NIZKRel_{\Sign}$ with issuer hiding.} %
-In \CUASGen and $\CUASGen^{usr-iss}$, it is required that the identity of the
+In \CUASGen it is required that the identity of the
 issuer of each credential involved in a signature is revealed. This seems

### 2022-08-17 prism-backend/research/gsac/introduction-paper.tex
Applying changes after pass.

@@
 \label{sec:introduction}
+
+\todo{Mention Camenisch, Krenn and Lehmann's work.}
 
@@
 Privacy-preserving digital signature and authentication systems have been a
-prolific field of study in the last few decades. Anonymous credentials (AC)
+prolific field in the last few decades. Anonymous credentials (AC)
 \cite{chau85} and group signatures (GS) \cite{ch91} are among the most relevant
-schemes. While there are many variants, the high-level idea is common: after
-obtaining a credential, users can authenticate anonymously and indistinguishably
-from other users with similar credentials.
+schemes. For both, the high-level idea is common: after obtaining a credential,
+users can authenticate anonymously and indistinguishably from other users with
+similar credentials.
 
@@
 multiple attributes within a credential and allowing to selectively disclose a
-subset of them, or even arbitrary predicates. The real world applications of
-such systems are direct, e.g., to prove ``Over 18''-type of claims. Indeed, the
-scientific research behind anonymous credentials is making its own way to become
-a foundational block of the technology some call ``anoncreds''%
+subset of them. The real world applications of such systems are direct, e.g.,
+to prove ``Over 18''-type of claims. Indeed, the scientific research behind
+anonymous credentials is making its own way to become a foundational block of
+the technology some call ``anoncreds''%
 \footnote{\url{https://hyperledger-indy.readthedocs.io/projects/sdk/en/latest/docs/design/002-anoncreds/README.html}. Last access, June 18th, 2022.},
@@
 However, even the generalisation efforts that have independently taken place in
-GS and AC, are quickly seen to have limited applicability in the real world.
-On the GS side, even though MPS achieves a nice balance on when a signature is
+GS and AC, are quickly seen to have limited applicability in the real world. On
+the GS side, even though MPS achieves a powerful balance on when a signature is
 deanonymizable and what information can be extracted from it, upon closer look,
@@
 one needs to prove more general claims. That is precisely what AC schemes do,
-and AC schemes also have a well defined notion of identity via the credential
+while also providing a well defined notion of identity via credential
 attributes. Precisely, it is this defined concept of identity what enables AC
@@
 different utility variants, making them hardly comparable. And, of course, AC
-focus only on utility at authentication (signing) time, while GS focus on
+focus on utility at authentication (signing) time, while GS focus on
 utility after signing (authentication) time. To the best of our knowledge, no
@@
 system -- with attribute-enabled credentials, and generalised utility both at
-authentication/signature-time, and after. Concretely, we propose a scheme
+signature time, and after. Concretely, we propose a scheme
 through which it is possible to model revealing arbitrary claims at signing time
@@
 \paragraph{Generic construction, and connections with previous schemes.} %
-We give a generic construction based on well-known building blocks, and prove
-its security. To prove its universality, we show how restrictions of our generic
-construction directly imply the direct ancestors of UAS: group signatures and
-anonymous credentials. This includes not only their vanilla versions, but also
-relevant variants, such as MPS \cite{ngsy22}, (a modified version of) group
-signatures with message-dependent opening \cite{seh+12}, or anonymous
-credentials with revocation \cite{cks10}. We also show how minimal variations in
-our generic construction allow us to build ring signatures \cite{rst06} or
-delegatable anonymous credentials \cite{bcc+09}. The most interesting part being
-that, while we prove implications with other previously known schemes, our
-generalisation approach allows to merge features of them: e.g., one can easily
-model and instantiate GSs with with no revocation at all, ACs with full
-de-anonymization, or anything in between -- like being able to deanonymize only
-if certain conditions are met.
+We give a main generic construction based on well-known building blocks, and
+prove its security. To prove its universality, we show how restrictions of our
+generic construction directly imply the direct ancestors of UAS: group
+signatures and anonymous credentials. This includes not only their vanilla
+versions, but also relevant variants, such as MPS \cite{ngsy22}, (a modified
+version of) group signatures with message-dependent opening \cite{seh+12}, or
+anonymous credentials with revocation \cite{cks10} or delegation \cite{bcc+09}.
+Strictly speaking, for AC schemes, we build on a simple transform of our main
+construction and model that turns non-interactive signatures into interactive
+authentication protocols with protection against replay attacks\footnote{This is
+  the well-known folklore approach that has the verifier send a fresh nonce to
+  be signed.}. We further show how to build ring signatures (RS) in the model
+given by \cite{bkm06}, from an alternative construction that improves issuer
+privacy.
+%
+The most interesting part being that, while we prove implications with other
+previously known schemes, our generalisation approach allows to merge features
+of them: e.g., one can easily model and instantiate GSs with with no revocation
+at all, ACs with full de-anonymization, RS with linkability, or anything in
+between -- like being able to deanonymize only if certain conditions are met.
 
@@
 order to meet the general practice in AC, the model for \UAS includes multiple
-issuers, requiring careful bookkeeping to prevent trivial wins. Interestingly,
-combining this generalisation with the GS world also paves the way to
-include multiple openers, each with its own opening functionality -- also
-requiring careful bookkeeping. While powerful from a practical point of view,
-this introduces similar limitations privacy-wise as in functional encryption
+issuers. Interestingly, combining this generalisation with the GS world also
+paves the way to include multiple openers, each with its own opening
+functionality. While powerful from a practical point of view, this introduces
+similar (unavoidable?) limitations privacy-wise as in functional encryption
 schemes \cite{bsw11} -- e.g., revealing too granular information at signing or
@@
 time, being a citizen of the local area (e.g. city). This can be done via an
-appropriate policy at signing time. If after the product is sold, it proves
+appropriate policy at signing time. If, after the product is sold, it proves
 to be defective, the social network may directly output the email of the user
@@
 issuer-user-verifier situation comes up that requires a different set of utility
-choices, just the appropriate functions would need to be changed -- and, given
-that our model allows multiple issuers and openers, both could coexist.
+choices, just the appropriate functions would need to be changed, without the
+need to re-model from scratch (or at all) -- and, given that our model allows
+multiple issuers and openers, with different issuance and opening policies,
+both could coexist.
 
@@
 extractable after signing. The latter is, in addition, fed and modulated with
-the output of \feval. The output of \feval is
-actually double: one part is shared in the clear along with the signature, and
-the other is encrypted, so that it can be used to tweak -- in a privacy-enhanced
-manner -- the behaviour of \finsp. The output of \finsp is encrypted with an
-opener's key. The pattern of the statements proven in each function is
+the output of \feval. The pattern of the statements proven in each function is
 summarised in \figref{fig:proof-blocks-uas}.
@@
 
-From \CUASGen, one can already build known (and more
-functionality-limited) schemes from what we call \emph{restrictions} of
-\CUASGen simply by giving concrete definitions of \fissue, \feval, and \finsp.
-Yet, the model remains the same, and we prove that if such restrictions of
-\CUASGen are secure in the \UAS model, they lead to secure constructions for
-the related primitives (GS variants, AC variants, etc). To define our generic
-construction, we also specify concrete NP relations for the underlying NIZK
-proofs for issuing, signing, and opening. These NP relations must not be
-considered as immutable, though. Actually, we show how, by making a minor
-variation into the one used for signing, a \CUASGen restriction can securely
-build ring signatures.
+From \CUASGen, one can already build known (and more functionality-limited)
+schemes from what we call \emph{restrictions} of \CUASGen simply by giving
+concrete definitions of \fissue, \feval, and \finsp. Yet, the model remains the
+same, and we prove that if such restrictions of \CUASGen are secure in the \UAS
+model, they lead to secure constructions for the related primitives (GS
+variants, AC variants, etc). To define our generic construction, we also specify
+concrete NP relations for the underlying NIZK proofs for issuing, signing, and
+opening. These NP relations must not be considered as immutable, though --
+informally, it would seem that they must simply follow the pattern in
+\figref{fig:proof-blocks-uas}. Actually, as mentioned, we show how by making a
+minor variation into the relation used for signing, a \CUASGen restriction can
+securely build ring signatures.
 
@@
 to build either of these primitives from another, the core of our contribution
-is that, with \UAS, one just needs to give concrete definitions of three
-functions (or little more). Security of the final primitive then essentially
-follows from the fact that it is a secure instantiation of an \UAS scheme. We
-believe that this is a powerful notion, that may finally allow research lines
-(AC and GS) that have followed different paths to benefit from the findings of
-each other. \figref{fig:relations} graphically summarises the relations we prove
-between \UAS and other schemes -- although, of course, many more are probably
+is that, with \UAS, one essentially just needs to give concrete definitions of
+three functions. Security of the final primitive then basically follows from
+the fact that it is a secure instantiation of an \UAS scheme. We believe that
+this is a powerful notion, that may finally allow research lines (AC and GS)
+that have followed different paths to benefit from the findings of each other.
+\figref{fig:relations} graphically summarises the relations we prove between
+\UAS and other schemes -- although, of course, many more are probably
 achievable.
@@
   \caption{Summary of schemes that can be instantiated as restrictions of our
-    generic constructions, $\CUASGen^{\ast}$, and proved secure under our \UAS
-    model. Between parenthesis we show the adopted reference model, and the
-    section offering full detail.}
+    generic constructions and proved secure under our \UAS model. Between
+    parenthesis we show the adopted reference model, and the section offering
+    full detail.}
   \label{fig:relations}

### 2022-08-17 prism-backend/research/gsac/preliminaries-paper.tex
Migrating from fissue being a predicate to it being a function.
Applying changes after pass.

@@
 
-\paragraph{Digital Signatures.} %
-Defined as a tuple (\SSetup,\SKeyGen,\SSign,\SVerify). Algorithm $\parm \gets
-\SSetup(\secpar)$ produces public parameters for the other algorithms.
-$(\vk,\sk) \gets \SKeyGen(\parm)$ generates the verification-signing key
-pair, algorithm $\sig \gets \SSign(\sk,\msg)$ signs message \msg with
-signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\vk,
-\sig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
-verification key \Svk. We rely on existentially unforgeable digital signature
-schemes.
+% \paragraph{Digital Signatures.} %
+% Defined as a tuple (\SSetup,\SKeyGen,\SSign,\SVerify). Algorithm $\parm \gets
+% \SSetup(\secpar)$ produces public parameters for the other algorithms.
+% $(\vk,\sk) \gets \SKeyGen(\parm)$ generates the verification-signing key
+% pair, algorithm $\sig \gets \SSign(\sk,\msg)$ signs message \msg with
+% signing key \Ssk, producing signature \Ssig, and $1/0 \gets \SVerify(\vk,
+% \sig,\msg)$ checks whether \Ssig is a valid signature over \msg, under
+% verification key \Svk. We rely on existentially unforgeable digital signature
+% schemes.
 
@@
 
-\paragraph{(Block) Commitment Schemes.} %
-Defined as a tuple (\CSetup,\CCommit). Algorithm $\parm \gets
-\CSetup(\secpar)$ produces the parameters for committing to values. $\Ccom
-\gets \CCommit(\parm, \smsg; r)$ produces a commitment \Ccom over a set of
-messages \smsg, using randomness $r$ (which we may omit when explicitly
-stating it is not necessary). We will further use commitment schemes that
-allow committing to vectors of messages. Therein, the \CCommit algorithm simply
-receives a block of messages. In both cases, we require hiding and binding
-(block) commitment schemes.
+% \paragraph{(Block) Commitment Schemes.} %
+% Defined as a tuple (\CSetup,\CCommit). Algorithm $\parm \gets
+% \CSetup(\secpar)$ produces the parameters for committing to values. $\Ccom
+% \gets \CCommit(\parm, \smsg; r)$ produces a commitment \Ccom over a set of
+% messages \smsg, using randomness $r$ (which we may omit when explicitly
+% stating it is not necessary). We will further use commitment schemes that
+% allow committing to vectors of messages. Therein, the \CCommit algorithm simply
+% receives a block of messages. In both cases, we require hiding and binding
+% (block) commitment schemes.
 
@@
 %
-Except when otherwise stated, we assume that, given a credential \cred, the
-public key of its issuer, $\ipk_{\cred}$ can be retrieved. Similarly, the
-attribute set contained in a credential \cred is denoted $\attrs_{\cred}$.
+$0(p)$ returns $True$ if $p=0$, or $False$ otherwise.
 

### 2022-08-17 prism-backend/research/gsac/relationships.tex
Applying changes after pass.

@@
       \begin{align}
-        & \fissue^1(\cdot,\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
-        & \fissue^{single,F,I}(\cdot,\usk,\cdot,\cdot) \coloneqq \pcreturn
-          F(I,\usk)
+        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
+        & \fissue^{single,F,I}(\upk,\cdot,\cdot) \coloneqq \pcreturn
+          F(I,\upk)
           \nonumber \\
-        & \fissue^{\sring}(\upk,\cdot,\attrs,\cdot) \coloneqq
+        & \fissue^{\sring}(\upk,\cdot,\attrs) \coloneqq
           \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber
@@
 
-We adopt the model in \cite{bsz05}. In this abstraction
-of group signatures, the opener returns an index uniquely identifying the group
-member that created a signature, along with a correctness proof. For ease of
-exposition, assume that, w.l.o.g., this index is just the public key that the
-group member generates randomly when joining the group\footnote{The user public
-  key is assumed to be accessible from a public table in \cite{bsz05}, so it is
-  easy to translate the public key into an index, if needed.}. A group signature
-scheme, according to \cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign,
-\Verify, \Open and \Judge algorithms, as well as an $\langle\Obtain,\Issue
-\rangle$ interactive protocol. Their intuition is similar to that of
-\UAS, so we refer to \cite{bsz05} for detailed descriptions. For ease of
-reference, we replicate the security games in \figref{fig:model-gs}.
+We adopt the model in \cite{bsz05}. In this abstraction of group signatures, the
+opener returns an index uniquely identifying the group member that created a
+signature, along with a correctness proof. For ease of exposition, assume that,
+w.l.o.g., this index is just the public key that the group member generates
+randomly when joining the group\footnote{The user public key is assumed to be
+  accessible from a public table in \cite{bsz05}, so it is easy to translate the
+  public key into an index, if needed.}. A group signature scheme, according to
+\cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign, \Verify, \Open and
+\Judge algorithms, as well as an $\langle\Obtain,\Issue\rangle$ interactive
+protocol. Their intuition is similar to that of \UAS, so we refer to
+\cite{bsz05} for detailed descriptions. For ease of reference, we replicate the
+security games in \figref{fig:model-gs}.
 
@@
 PRF. In that case, its output is a random-looking string that depends on the
-user secret key \usk, and a string $I$ uniquely identifying the user. Thus, it
-will be the same per $(\usk,I)$ pair, and can be used by issuer $I$ to prevent
-issuing more than one credential per user -- without enabling linking across
-issuers. Basically, each issuer maintains a list of received $\yissue = F(\usk,
-I)$ values, and rejects issuing a credential for already existing \yissue
-values. From this, the GS algorithms are as follows:
+user public key \upk, and a string $I$ uniquely identifying the user. Thus, it
+will be the same per $(\upk,I)$ pair, and can be used by issuer $I$ to prevent
+issuing more than one credential per user. Basically, the issuer maintains a
+list of received $\yissue = F(\upk,I)$ values, and rejects issuing a credential
+for already existing \yissue values. From this, the GS algorithms are as
+follows:
 
@@
   (initially set to $\emptyset$); if it exists, aborts issuance. Otherwise, it
-  completes the protocol and adds $\yissue$ to $L$.
+  completes the protocol and adds $\yissue$ to $L$. It is responsibility of the
+  issuer to maintain $L$.
 \item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Parses \gpk as $(\ipk,\opk)$, and
@@
 disclosure. Therein, an anonymous credential scheme is defined via $OrgKeyGen$
-(which we rename to $IssKeyGen$, and is equivalent to \KeyGen+\ISet in \UAS),
-and $UserKeyGen$ (\KeyGen in \UAS) algorithms, and $Obtain,Issue$ and $Show,
-Verify$ interactive protocols. The issuance interactive protocol corresponds to
-the issuance protocol in \UAS. Similarly, $Show,Verify$ corresponds to
-the interactive extension of \Sign and \Verify in \UAS, which we show how
-to build in \appref{app:interactive-uas}. The security definitions rely on
-$HU, CU, ObtIss, Obtain, Issue, Show$, and $LoR$ oracles, which are essentially
-equivalent to our \HUGEN, \CUGEN, \OBTISS, \OBTAIN, \ISSUE, \SIGN, and \CHALb
-oracles\footnote{The $CU$ oracle in \cite{fhs19} actually allows the adversary
-  to create corrupt user secret keys, while in our corruption model, corrupt
-  users have keys generated by the system that are later learned by the
-  adversary. This is however for notational simplicity -- and, indeed, in our
-  construction, all users need to prove knowledge of the \usk, which would be
-  consistent with the stronger corruption model in \cite{fhs19}}. We refer to
+(which we rename to $IssKeyGen$), and $UserKeyGen$ algorithms, and $Obtain,
+Issue$ and $Show,Verify$ interactive protocols. The security definitions rely on
+$HU, CU, ObtIss, Obtain, Issue, Show$, and $LoR$ oracles. We refer to
 \cite{fhs19} for the full details. For ease of reference, we summarize the
@@
     the unforgeability game if it authenticates successfully while revealing
-    attributes not contained in adversarially controlled credentials.}
+    attributes not contained in adversarially controlled credentials. All
+    oracles in this model have a direct equivalent in \UAS.
+  }
   \label{fig:model-ac}  
@@
 \subsubsection{\CUASAC Construction.} %
-We show that a $(\fissue^1,\feval^{\dattrs},\finsp^0)$-\CUASGen restriction, is
-a secure anonymous credential scheme according to the model in \cite{fhs19}. We
-first quickly define the algorithms, and then prove security.
+We show that a $(\fissue^1,\feval^{\dattrs},\finsp^0)$-$\CUASGen^{int}$
+restriction, is a secure anonymous credential scheme according to the model in
+\cite{fhs19}. We first quickly define the algorithms, and then prove security.
 
@@
 %   \CUASGen construction. Returns $\parm \gets (\parm',\opk)$.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] From \CUASGen, run $\parm' \gets
-  \Setup(1^\secpar)$ and $(\opk,\osk) \gets \OKeyGen(\parm',
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] From $\CUASGen^{int}$, run $\parm'
+  \gets \Setup(1^\secpar)$ and $(\opk,\osk) \gets \OKeyGen(\parm',
   \finsp^0)$, and set $\parm \gets (\parm',\opk)$. Run $(\upk,\usk) \gets
@@
   \usk$.
-\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from \CUASGen.
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from $\CUASGen^{int}$.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
   \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  Runs $\langle \Obtain,\Issue \rangle$ from \CUASGen.
+  Runs $\langle \Obtain,\Issue \rangle$ from $\CUASGen^{int}$.
 \item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
@@
   \cred),\Verify(\ipk,\dattrs) \rangle$.]
-  Runs the interactive extension of \Sign and \Verify of \CUASGen, using
+  Runs the interactive transform of \Sign and \Verify of $\CUASGen^{int}$, using
   $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as open
@@
   \label{thm:anon-cuasac}
-  If the base \CUASGen construction has signature anonymity according to
+  If the base $\CUASGen^{int}$ construction has signature anonymity according to
   \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
@@
   \label{thm:forge-cuasac}
-  If the base \CUASGen construction is unforgeabile according to
+  If the base $\CUASGen^{int}$ construction is unforgeabile according to
   \defref{def:forge-uas}, then \CUASAC is an unforgeable AC scheme.
-  \markulf{Hiding of $pk_U$?}
 \end{theorem}
@@
 \subsection{Revocable Anonymous Credentials}
-\label{sapp:related-models-rac}
+\label{ssec:related-models-rac}
 

### 2022-08-17 prism-backend/research/gsac/introduction-paper.tex
Finishing pass.

@@
 \label{sec:introduction}
-
-\todo{Mention Camenisch, Krenn and Lehmann's work.}
 
@@
 utility after signing (authentication) time. To the best of our knowledge, no
-model exists that combines both, in a general enough manner. In practice, this
-forces system designers to decide which one they do not want to lose -- or,
+model exists that combines both, in a general enough manner. Probably, the
+closest work to ours, in regard to this ``generalization spirit'', is
+\cite{ckl+15}, although it focuses only on anonymous credentials. In practice,
+needing to resort to too specific models forces system designers to decide which
+feature (utility at or after signing time, etc) they do not want to lose -- or,
 which one they will lose.

### 2022-08-17 prism-backend/research/gsac/relationships.tex
Finishing pass.

@@
 \begin{figure}[ht!]
-
-  \scalebox{0.9}{
-    \begin{minipage}[t]{\textwidth}
-      \textbf{Issuance functions:}
-      \begin{align}
-        & \fissue^1(\cdot,\cdot,\cdot) \coloneqq 1 \nonumber \\
-        & \fissue^{single,F,I}(\upk,\cdot,\cdot) \coloneqq \pcreturn
-          F(I,\upk)
-          \nonumber \\
-        & \fissue^{\sring}(\upk,\cdot,\attrs) \coloneqq
-          \pcreturn (\attrs = \sring \land \upk \in \attrs) \nonumber
-      \end{align}
-
-      \textbf{Signature evaluation functions:}
-      \begin{align}
-        & \feval^0(\cdot,\cdot,\cdot) \coloneqq \pcreturn (0,\ast) \nonumber \\
-        & \feval^{\dattrs}(\cdot,(\cdot,\attrs),\cdot)
-          \coloneqq \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},\ast)
-          \nonumber \\
-        & \feval^{\sring,\dattrs}(\upk,(\cdot,\attrs),\cdot)
-          \coloneqq \pcif \upk \in \lbrace \attrs_i \rbrace_{i\in\dattrs}
-          \subseteq \sring:
-          \pcreturn (\lbrace \attrs_i \rbrace_{i\in\dattrs},\ast);
-          \pcelse \pcreturn (0,\ast) \nonumber \\
-        & \feval^{\dattrs,F,V,L}(\upk,((\cidi,\cidu),\attrs),\cdot) \coloneqq
-          \nonumber \\
-        & \hspace*{2em}\pcif F(V,\cidi) \in L \lor F(V,\cidu) \in L:
-          \pcreturn (0,\ast) \nonumber \\
-        & \hspace*{2em}\pcelse \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},V)
-          \nonumber \\
-        & \feval^{g,MPS}(\upk,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},\msg)
-          \coloneqq \nonumber \\
-        & \hspace*{2em}\pcif g(\upk,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},
-          \msg) = 0: \pcreturn \bot \nonumber \\
-        & \hspace*{2em}\pcelse \pcreturn (\ast,g(\upk,\lbrace
-          (\cid_i,\attrs_i) \rbrace_{i\in[n]},\msg)) \nonumber
-      \end{align}
-    \end{minipage}
-  }
-  \vspace*{1em}
-
-  \scalebox{0.9}{
-    \begin{minipage}[t]{\textwidth}
-      \textbf{Open functions:}
-      \begin{align}
-        & \finsp^0(\cdot,\cdot,\cdot,\cdot) \coloneqq 0 \nonumber \\
-        & \finsp^{\upk}(\cdot,\upk,\cdot,\cdot) \coloneqq
-          \pcreturn \upk % \CCommit(\usk;0)
-          \nonumber \\
-        & \finsp^{F}((\yeval^0,\yeval^1),\cdot,((\cidi,\cidu),\attrs),\cdot)
-          \coloneqq \nonumber \\
-        & \hspace*{2em}\pcif \yeval^0 \neq 0:
-          \pcreturn (F(\yeval^1,\cidi),F(\yeval^1,\cidu)) \nonumber \\
-        & \hspace*{2em}\pcelse \pcreturn 0
-          \nonumber \\
-        & \finsp^{h,MPS}((\cdot,\yeval^1),\upk,\cid,\attrs,\cdot) \coloneqq
-          \pcreturn h(\yeval^1,\upk,\cid,\attrs) \nonumber         
-      \end{align}
-    \end{minipage}
-    \hspace*{5em}
-    % \begin{minipage}[t]{0.47\textwidth}
-    %   \begin{framed}
-    %     $\attrs(\cred)$ returns all attributes in \cred \\
-    %     $\dattrs(\cred)$ returns $\dattrs \subseteq \attrs(\cred)$ \\
-    %     $\attrs_i(\cred)$ returns $i$-th attribute in \cred \\
-    %     $\ast$ means the output is ignored \\
-    %     $\bot$ means the function fails
-    %   \end{framed}
-    % \end{minipage}
-  }
+  \input{figures/functions.tex}
   \caption{Functions for the \CUASGen restrictions described next.
@@
     queries, and returns $\sig \gets Sign(\sk_i,R,\msg)$. $CORR$
-    accepts an index $i$, and leaks $\sk_i$ to $\adv$. Corrupted users are added
+    accepts an index $i$, and leaks $\sk_i$. Corrupted users are added
     to $CU$.}
@@
   }
-  \caption{Security games for anonymous credentials with selective disclosure
-    \cite{fhs19}. \OWNR and \ATTR tables are essentially as in \UAS. \adv~wins
-    the unforgeability game if it authenticates successfully while revealing
-    attributes not contained in adversarially controlled credentials. All
-    oracles in this model have a direct equivalent in \UAS.
-  }
+  \caption{Games for anonymous credentials with selective disclosure
+    \cite{fhs19}. \OWNR, \ATTR, and the oracles, are essentially as in
+    \UAS. \adv~wins $\Exp^{forge}_{\adv,ac}$ if it authenticates successfully
+    while revealing attributes not contained in adversarially controlled
+    credentials.}
   \label{fig:model-ac}  
@@
   \cred),\Verify(\ipk,\dattrs) \rangle$.]
-  Runs the interactive transform of \Sign and \Verify of $\CUASGen^{int}$, using
-  $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as open
-  function, with \opk from \parm as opener public key.
+  Runs the interactive $\langle \Sign, \Verify\rangle$ of  $\CUASGen^{int}$,
+  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
+  open function, with \opk from \parm as opener public key.
 \end{description}
@@
 
-In \cite{cks10}, revocable anonymous credentials are proposed. From \CUASGen, it
-is straightforward to build an AC system with verifier local revocation, like in
-\cite{bs04}. Basically, we leverage the $\cid=(\cidi,\cidu)$ identifiers,
-encoded as attributes, to define a $(\feval,\finsp)$ function pair that: (1)
-ensures that opening outputs the evaluation of a PRF of the {\cid}s concatenated
-with the verifier name; and (2) ensures that, if some {\cid} of the credentials
-used to produce a signature have been added to a revocation list by the
-verifier, the verifier will know it -- and hence will be able to reject the
-signature. We first give a simple model in
-\figref{fig:model-rac}, extending that in \secref{ssec:related-models-ac}.
-Concretely, to the functionality in \secref{ssec:related-models-ac}, we now
-explicitly add
-the $OKeyGen$ function (equivalent to \OKeyGen, with a fixed \finsp function),
+In \cite{cks10}, revocable anonymous credentials are proposed. We first give a
+simple model in \figref{fig:model-rac}, extending that in
+\secref{ssec:related-models-ac}. Concretely, to the functionality in
+\secref{ssec:related-models-ac}, we now explicitly add the $OKeyGen$ function,
 which generates the opener key pair, extend $Verify$ to receive also a list $L$
@@
 oracle) $cid/\bot \gets RetrieveCredId(\osk,\utrans)$ that can extract an
-identifier of the credential used in a presentation transcript \utrans -- and
-which is essentially equivalent to \Open in \UAS. For simplicity, we do not
-include the equivalent to verifiable openings, but this would be
-straightforward.
+identifier of the credential used in a presentation transcript \utrans. For
+simplicity, we do not include the equivalent to verifiable openings, but this
+would be straightforward.
 
@@
 \subsubsection{\CUASRAC Construction.} %
-Briefly, we build a revocable anonymous credential as a $(\fissue^1,
-\feval^{\dattrs,F,V,L},\finsp^{F})$-\CUASGen restriction. \feval is
-parameterized with a PRF $F$, a string identifying the verifier $V$ and a
-list $L$ of ``revocation handles'' by $V$. Note that these can be hardcoded,
-though: $F$ can be common to all verifiers, $V$ is also fixed (per verifier),
+Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,F,V,L},
+\finsp^{F})$-$\CUASGen^{int}$ restriction. \feval is parameterized with a PRF
+$F$, a string identifying the verifier $V$ and a list $L$ of ``revocation
+handles'' by $V$. Note that these can be hardcoded, though: $F$ can be common to
+all verifiers, $V$ is also fixed (per verifier),
 and $L$ can be updated with some reasonable frequency -- e.g., daily -- so that
@@
 %
-Since credentials in \CUASGen have two identifiers (\cidi, chosen by the issuer;
-and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally computes
-$F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval sets $\yeval^0$
-to $0$, which the verifier interprets as ``revoked credential''. Otherwise,
-it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
+Since credentials in $\CUASGen^{int}$ have two identifiers (\cidi, chosen by the
+issuer; and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally
+computes $F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval sets
+$\yeval^0$ to $0$, which the verifier interprets as ``revoked credential''.
+Otherwise, it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
 $\yeval^1 \gets V$. $\yeval^1$ is
@@
 \item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from our
-  \CUASGen construction, setting $\fissue^1$ as issuance function.
+  $\CUASGen^{int}$ construction, setting $\fissue^1$ as issuance function.
 \item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
-  \CUASGen construction, setting $\finsp^F$ as opening function.
+  $\CUASGen^{int}$ construction, setting $\finsp^F$ as opening function.
 \item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from the
-  \CUASGen construction.
+  $\CUASGen^{int}$ construction.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
@@
   $\fissue^1$ as issuance function.
-\item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
+\item[$\langle 1/0,(\dattrs,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
   \attrs,\dattrs,\cred),
   \Verify(\ipk,\dattrs) \rangle$.]
-  Runs the interactive extension of \Sign and \Verify of the \CUASGen protocol,
+  Runs the interactive $\langle\Sign,\Verify\rangle$ of $\CUASGen^{int}$,
   using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
-  $\finsp^F$ as open function. If $\yeval^0 = 0$, the signature is rejected.
+  $\finsp^F$ as open function. The \dattrs value output by the verifier is
+  the $\yeval^0$ value produced by \Sign (when accepted by \Verify).
 \item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
   Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
-  \utrans, and runs \Open from \CUASGen. If $\yeval^0 \neq 0$ (i.e., the
+  \utrans, and runs \Open from $\CUASGen^{int}$. If $\yeval^0 \neq 0$ (i.e., the
   signature was created by a non-revoked credential), this returns $(F(V,\cidi),
@@
 \begin{theorem}[Anonymity of \CUASRAC]
-  If the base \CUASGen construction has signature anonymity according to
+  If the base $\CUASGen^{int}$ construction has signature anonymity according to
   \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASRAC is an
@@
 \begin{theorem}[Unforgeability of \CUASRAC]
-  If the base \CUASGen construction is unforgeable according to
+  If the base $\CUASGen^{int}$ construction is unforgeable according to
   \defref{def:forge-uas}, and $F$ is one-way, then \CUASRAC is an unforgeable
@@
 
-Note that, if we aim at global credential (resp. user) revocation rather than
-verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
-pair (resp., \upk), and no assumption regarding $F$ is needed.
+% Note that, if we aim at global credential (resp. user) revocation rather than
+% verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
+% pair (resp., \upk), and no assumption regarding $F$ is needed.
 
@@
 Multimodal Private Signatures (or, rather, a close relative, see next) are
-directly implementable as a $(\fissue^{single,F,I},\feval^{\yeval^1},
-\finsp^{\ast})$-\CUASGen restriction, where $\feval^{\yeval^1}$ is any signature
-evaluation function that ignores the $\yeval^0$ output, and $\finsp^{\ast}$ is
-any open function. Concretely, this restricts to a system with one issuer and
-one opener, one credential per user, no attributes in the credentials.
+directly implementable as a $(\fissue^{single,F,I},\feval^{g,MPS},
+\finsp^{h,MPS})$-\CUASGen restriction. Concretely, this restricts to a system
+with one credential per user and no attributes in the credentials.
 
@@
 private system. This is a known issue, for instance, in functional encryption
-\needcite.
+\cite{bsw11}.
 
-On the other hand, anonymous issuance, and the capability to customize issuance
+On the other hand, anonymous issuance and the capability to customize issuance
 policies are unachievable by MPS. Anonymous issuance simply does not make sense
-in MPS, as it only supports one credential (without attributes) per user.
-Customized issuance is achieved in \UAS via the \fissue functions, with no
+in MPS, as it only supports one credential (without attributes) per user, and
+customized issuance is achieved in \UAS via the \fissue functions, with no
 equivalent in MPS -- instead, MPS has the fixed policy of
 ``proving knowledge of a user secret key''. These extensions are not trivial
-from a theoretical point of view, and also have a big impact in the practicality
+from a modelling point of view, and also have a big impact in the practicality
 of the resulting system. Also, MPS does not include verifiable openings. While
@@
 MPS, as it allows two outputs: one will be returned in the clear along with the
-signature, and the other will be encrypted. Still both computations are proved
-correct. Making part of the output unencrypted allows implementing very useful
-variants such as anonymous credentials, as shown before.
+signature, and the other will be encrypted. Indeed, making part of the output
+unencrypted allows implementing very useful variants such as anonymous
+credentials, as shown before.
 
@@
 \subsubsection{\CUASMPS construction.} %
-As mentioned, any $(\fissue^{single,F,I},\feval^{\yeval^1},
-\finsp^\ast)$-restriction implements an MPS scheme where $F=\feval^{\yeval^1}$
+As mentioned, any $(\fissue^{single,F,I},\feval^{g,MPS},
+\finsp^{h,MPS})$-restriction implements an MPS scheme where $F=\feval^{\yeval^1}$
 and $G=\finsp^\ast$. With these functions, the construction is direct.
@@
 \UAS is the $\yeval^1$ value which, in \CUASGen, is encrypted with a single-use
-key pair, and is an input of \yinsp.
+key pair, and is an input of \finsp.
 
@@
   If the base \CUASGen construction is unforgeable according to
-  \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
+  \defref{def:forge-uas}, then \CUASMPS satisfies unforgeability-1 as
   defined in \cite{ngsy22}.

### 2022-08-17 prism-backend/research/gsac/uas-paper.tex
More passes.
Restructured some content.
Added a paragraph with real-world sample use cases. Fixed some todos.
Fixing flaws in definitions and non-frame proof. (non-frame not done.)
Added the current date in the first page, to distinguish recent versions.
Defining Extract* and Identify* properties.
Some deep syntax re-writing.
Updating proofs.
Added proof sketch for interactive variant.
Finishing pass.

@@
 \usepackage{hyperref}
-\usepackage{mathtools}
+%\usepackage{mathusertools}
 \usepackage{multirow}
 \usepackage{footnote}
+\usepackage{framed}
+\usetikzlibrary{decorations.pathreplacing,calligraphy}
 \makesavenoteenv{tabular}
@@
 %% Set/unset to activate/deactivate author comments
-\def\authnotes{1}
+\def\authnotes{0}
 
@@
 {\def\addcontentsline#1#2#3{}\maketitle}%\maketitle
+\ifnum\authnotes=1
+Version of \today
+\fi
 
 \begin{abstract}
-  \todo{XXX}
+  For decades, anonymous credentials, group signatures, and closely related
+  systems in the domain of privacy-preserving authentication, have relied on
+  common cryptographic building blocks. However, each has its own approach
+  modelling-wise, despite obvious commonalities.
+  %
+  Even within systems of the same type, multiple ``sub-models'' coexist that
+  cater for slightly different requirements.
+
+  In this work, we make a significant generalization effort in order to come
+  up with a flexible game-based model that subsumes (a reasonable subset of)
+  previous models in this domain. The key to this flexibility lies in functional
+  placeholders that, with careful constraints, still allow to capture the
+  usual anonymity, unforgeability and non-frameability properties. We refer
+  to this unified model as \emph{Universal Anonymous Signatures} (\UAS).
+
+  To showcase the generality of our model, we first give a generic construction
+  of \UAS, along with minor variations of this construction that also meet the
+  \UAS model. Then, we prove that well-known related schemes can be built as a
+  special case (restriction) of our generic construction, just by giving
+  concrete definitions of the previously mentioned functional placeholders.
+  In particular, we prove our \UAS model spans (vanila) group signatures, group
+  signatures with message-dependent opening, multimodal private signatures,
+  attribute-based anonymous credentials, revocable anonymous credentials,
+  delegatable anonymous credentials, and ring signatures. This also proves
+  interesting (and, in some sense, folklore) facts, such as the fact that ring
+  signatures can be seen as a multi-issuer group signature scheme, in which
+  every user is also an issuer. Also, it paves the way to come up with
+  ``hybrid'' constructions where one (e.g.) combines features of anonymous
+  credentials (proving predicates at authentication time), with features of
+  group signatures (conditional deanonymization based on attributes of the
+  signer).
+
+  Besides the main theoretical contribution of providing a unified model for
+  many related schemes, we do believe that a (possibly more relevant) practical
+  contribution consists on the fact that system designers and cryptographic
+  engineers may adotp some generic construction of \UAS, and then simply focus
+  on concrete definitions of a few functional placeholders, to tweak the
+  different utility-vs-privacy tradeoff they want to achieve -- without the need
+  to prove everything from scratch, nor needing to switch to a completely
+  different construction if their needs change.
 \end{abstract}
@@
 
-% \appendix
+\appendix
 
-% \input{app-building-blocks.tex}
+\input{app-building-blocks.tex}
+\input{app-uas-proofs.tex}
+%\input{app-interactive.tex}
+\input{app-related-proofs.tex}
+\input{app-related-extra.tex}
 % \input{app-gsac.tex}

### 2022-08-17 prism-backend/research/gsac/formal-uas.tex
Refining

@@
   \cdot,\cdot)$ (resp. $\CRED[\scid]$).
-\item[\CCRED.] Like \CRED, but tracks challenge credentials in the issuance
-  anonymity game.
+\item[\CCRED.] Like \CRED, but tracks challenge credentials.
 \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
@@
   unforgeable, then our \CUASGen construction
-  satisfies unforgeability as defined in \defref{def:sign-forge-uas}, except
+  satisfies unforgeability as defined in \defref{def:forge-uas}, except
   with negligible probability.

### 2022-08-17 prism-backend/research/gsac/introduction-paper.tex
Refining

@@
 encode many attributes. Indeed, BBS+ signatures \cite{bbs04,cdl16b} have been
-used to design and instantiate GS schemes \cite{gl19,dl21}, as well as  PS16
-signatures \cite{ps16,cdl+20}. Both are CL-like signature schemes, and thus
-can be (and have been) used to design AC schemes \needcite.
+used to design and instantiate GS schemes \cite{gl19,dl21}, as is the case for
+PS16 signatures \cite{ps16,cdl+20}.
 
@@
   the well-known folklore approach that has the verifier send a fresh nonce to
-  be signed.}. We further show how to build ring signatures (RS) in the model
-given by \cite{bkm06}, from an alternative construction that improves issuer
-privacy.
+  be signed by the alleged owner of the private key related to a known
+  public key.}. We further show how to
+build ring signatures (RS) in the model given by \cite{bkm06}, from an
+alternative construction that improves issuer privacy.
 %

### 2022-08-17 prism-backend/research/gsac/uas-paper.tex
Refining

--- 2022-06-18 prism-backend/research/gsac/uas-paper.tex
@@
 {\def\addcontentsline#1#2#3{}\maketitle}%\maketitle
+\ifnum\authnotes=1
+Version of \today
+\fi
 
 \begin{abstract}
-  \todo{XXX}
+  For decades, anonymous credentials, group signatures, and closely related
+  systems in the domain of privacy-preserving authentication, have relied on
+  common cryptographic building blocks. However, each has its own approach
+  modelling-wise, despite obvious commonalities.
+  %
+  Even within systems of the same type, multiple ``sub-models'' and
+  constructions coexist that cater for slightly different requirements.
+
+  Previous works, like Camenisch et al in SAC'15, or Nguyen et al in CRYPTO'22
+  generalize aspects of those systems, but still within their own domain --
+  anonymous credentials and group signatures, respectively.
+
+  In this work, we make a significant generalization effort in order to come
+  up with a flexible game-based model that subsumes
+  previous ones. The key to this flexibility lies in functional placeholders
+  that, with careful constraints, still allow to capture generalized notions of
+  the usual anonymity, unforgeability and non-frameability properties. We refer
+  to this unified model as \emph{Universal Anonymous Signatures} (\UAS).
+
+  To showcase the generality of \UAS, we give a main construction, plus two
+  alternative ones that slightly modify it, following our \UAS model.
+  We prove that, from these constructions, we can build multiple variants of
+  group signatures, anonymous credentials, and ring signatures, just by giving
+  concrete definitions of the mentioned functional placeholders.
+
+  Our main theoretical contribution is unifying previously separate
+  (albeit close) systems under the same generalized model. Indeed, such unified
+  model allows to, very easily, build ``hybrid'' systems that combine features
+  of previously separately modelled constructions: e.g., anonymous credentials
+  with conditional deanonymization based on their attributes.
+
+  More practically, this has the consequence that cryptographic
+  engineers and system designers can tweak the desired utility-vs-privacy
+  tradeoff that best suits their needs, just by defining a few functions --
+  but without needing to prove security from scratch or implement
+  a whole system.
 \end{abstract}

### 2022-08-19 prism-backend/research/gsac/app-related-proofs.tex
Refined model for RAC. Conclusion. Complete draft (excl. app. D)

@@
 do not have issuance anonymity, as the user public key is passed to the issuer.
+Note that, for ease of reference to the games in \secref{sec:formal-uas}, we
+reduce to security of \CUASGen rather than to $\CUASGen^{int}$. The
+``translation'' between \CUASGen and $\CUASGen^{int}$ is trivial, though.
 
@@
   If the base \CUASGen construction is anonymous according to
-  \defref{def:anonymity-uas}, then \CUASAC is an anonymous AC scheme according
-  to \cite{fhs19}.
+  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
+  according to \cite{fhs19}.
 \end{theorem}
@@
   Given \adv~against anonymity of \CUASAC as defined in \cite{fhs19}, we build
-  an adversary \advB against anonymity of \CUASGen as defined in
-  \defref{def:sign-anonymity-uas}.
+  an adversary \advB against signature anonymity of \CUASGen as defined
+  in \defref{def:sign-anonymity-uas}.
 
@@
   oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR$, \advB redirects to
-  \HUGEN,\CUGEN,\OBTAIN,\SIGN,\CHALb, respectively. Note that ``translating''
+  \HUGEN,\CUGEN,\OBTAIN,\SIGN,\CHALb, respectively. Note that translating
   the inputs from the former into inputs for the latter is trivial.
@@
 has signature anonymity and is unforgeable.
+%
+As for \CUASAC, we reduce to security of \CUASGen rather than to
+$\CUASGen^{int}$. The ``translation'' between \CUASGen and $\CUASGen^{int}$ is
+again trivial.
 
@@
   If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASAC is an
-  anonymous AC scheme according to \cite{fhs19}.
+  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
+  according to \cite{fhs19}.
 \end{theorem}
@@
   \CUASGen as defined in \defref{def:sign-anonymity-uas}.
-
-  First observe that, given a revocation handles $F(V,\cidi)$ and $F(V,\cidu)$
-  extracted from any credential showing, it is not possible to extract $\cidi$
-  nor $\cidu$, as $F$ is one-way.
+  %
+  But, first observe that, since the revocation oracle is basically an extension
+  of the \OPEN oracle -- also keeping track of the revoked users per verifier --
+  queries involving challenge users are rejected if the revocation handle does
+  not match for both challenge users.
 
@@
   oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
-  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, or \OPEN, respectively.
+  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, or \OPEN (in this case,
+  also keeping track of the queries, per verifier), respectively.
   Note that ``translating'' the inputs from the former into inputs for the
@@
   If the base \CUASGen construction has unforgeability according to
-  \defref{def:forge-uas}, and $F$ is one-way, then
-  \CUASRAC is an unforgeable RAC scheme.
+  \defref{def:forge-uas}, and $F$ is one-way, then \CUASRAC is an
+  unforgeable RAC scheme.
 \end{theorem}
@@
   To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
-  that \adv~wins its game via the winning condition of line 7 in the RAC
+  that \adv~wins its game via the winning condition of line 9 in the RAC
   unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
-  that the probability of \adv~winning its game via the winning condition at
-  line 9 is negligible, due to soundness of the NIZK scheme used for signing,
-  and the one-wayness of $F$ in $\feval^{\dattrs,F,V,L}$ and $\finsp^{F}$.
+  that the probability of \adv~winning its game via condition $h_0 \in L$ at
+  line 11 is negligible, due to soundness of the NIZK for $\NIZKRel_{\Sign}$.
+  Moreover, soundness of NIZK for $\NIZKRel^{\Sign}$ as well as one-wayness
+  of $F$ ensure that, if $h_1 \notin L$, then $b_1 = 1$. Namely, even when given
+  $F(V,\cidi),F(V,\cidu)$ for a credential identified by $(\cidi,\cidu)$ owned
+  by an honest user, and some (potentially malicious) $V$, it is not possible to
+  generate $F(V',\cidi)$ nor $F(V',\cidu)$, for $V'=V$.
   % 

### 2022-08-19 prism-backend/research/gsac/app-uas-proofs.tex
Refined model for RAC. Conclusion. Complete draft (excl. app. D)

@@
 \paragraph{Unforgeability and non-frameability.} The simulation described for
-the anonymity case (i.e., \advB choosing the random numbers, and concatenating
-them to the message to be signed by the oracle) applies here too. Since the
+the anonymity case (i.e., \advB concatenating the random numbers
+to the message to be signed by the oracle) applies here too. Since the
 interactive protocol includes non-interactive proofs for the $\NIZKRel^{\Sign}$

### 2022-08-19 prism-backend/research/gsac/conclusion-paper.tex
Added a paragraph with real-world sample use cases. Fixed some todos.
Refined model for RAC. Conclusion. Complete draft (excl. app. D)

@@
 
-[1 page max]
+We present a general model for privacy-preserving signatures and authentication,
+and provide a generic construction, secure in our model, that allows
+different privacy-vs-utility tradeoffs to be reached.
+%
+Then, we prove that well-known schemes are special cases of our generic
+construction. The implied schemes include group signatures, anonymous
+credentials (with and without revocation), ring signatures, or the recently
+proposed multimodal private signatures.
+
+The flexibility of our model is achieved via functional placeholders that
+modulate the behaviour at credential issuance time, the utility
+information ``leaked'' along with the produced signatures, and the utility
+information extractable from already produced signatures. These functions are
+computed by the users themselves, who need to prove correct computation.
+Our setting also combines features of anonymous credential schemes, like
+attribute-based credentials and multiple issuers, which we extend with openers
+(like in group signatures), but also enabling that multiple openers coexist.
+This further increases the flexibility, by removing the tight issuer-opener
+coupling in previous works.
+
+For future work, an obvious line is to come up with (and implement) concrete
+instantiations of our generic construction in order to evaluate efficiency in
+real-world use cases. Also, it may be interesting to come up with alternative
+generic constructions -- for instance, based on structure-preserving signatures.
+%
+Finally, in this work we focus only on utility over \emph{one} signature. But
+extending our model and constructions to span utility over \emph{multiple}
+signatures promises to be interesting, both regarding its modelling and the
+potential use cases.
 

### 2022-08-19 prism-backend/research/gsac/relationships.tex
Refined model for RAC. Conclusion. Complete draft (excl. app. D)

@@
 We adopt the model in \cite{fhs19}, for anonymous credentials with selective
-disclosure. Therein, an anonymous credential scheme is defined via $OrgKeyGen$
-(which we rename to $IssKeyGen$), and $UserKeyGen$ algorithms, and $Obtain,
+disclosure, which restricts to one credential per presentation. Therein, an
+anonymous credential scheme is defined via $OrgKeyGen$ (which we rename to
+$IssKeyGen$), and $UserKeyGen$ algorithms, and $Obtain,
 Issue$ and $Show,Verify$ interactive protocols. The security definitions rely on
@@
 
-In \cite{cks10}, revocable anonymous credentials are proposed. We first give a
-simple model in \figref{fig:model-rac}, extending that in
+In \cite{cks10,ckl+15}, revocable anonymous credentials are proposed. We first
+give a simple model in \figref{fig:model-rac}, extending that in
 \secref{ssec:related-models-ac}. Concretely, to the functionality in
@@
   \scalebox{0.9}{      
-    \begin{minipage}[t]{0.45\textwidth}
+    \begin{minipage}[t]{0.43\textwidth}
       \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
@@
         (\ipk,\isk) \gets IssKeyGen(\parm) \\        
-        b^* \gets \adv^{\mathcal{O}_{anon}}(\parm,\ipk,\opk) \\
+        b^* \gets \adv^{\mathcal{O}_{rac},LoR}(\parm,\ipk,\opk) \\
         \pcreturn b^*
@@
   \scalebox{0.9}{      
-    \begin{minipage}[t]{.55\textwidth}
+    \begin{minipage}[t]{.57\textwidth}
       \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
@@
         (\ipk,\isk) \gets IssKeyGen(\parm) \\
-        (D,L,\st) \gets
-        \adv^{\mathcal{O}_{forge}}(\parm,\ipk) \\
-        \langle \cdot,(b,\utrans)\rangle
+        (\cid,D,L,\st) \gets
+        \adv^{\mathcal{O}_{rac}}(\parm,\ipk,\opk) \\
+        \langle \cdot,(b_0,\utrans_0)\rangle
         \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
-        \pcif b = 0: \pcreturn 0 \\
-        \pcif \nexists j~\suchthat~(\OWNR[j] \in \CU
-        \land D \subseteq \ATTR[j]): \pcreturn 1 \\    
-        h \gets RetrieveCredHandle(\osk,\utrans) \\
-        \pcif h \in L \lor h = \bot: \pcreturn 1 \\
+        \langle \cdot,(b_1,\utrans_1)\rangle
+        \gets \langle Show(\ipk,\ATTR[\cid],D,\CRED[\cid]), \\
+        \hspace*{7.25em}\Verify(\ipk,D,L)\rangle \\
+        \pcif \OWNR[\cid] \notin \HU \lor
+        D \not\subseteq \ATTR[\cid]: \pcreturn 0 \\
+        \pcif b_0 = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
+        \land D \subseteq \ATTR[j]): \\
+        \pcind \pcreturn 1 \\
+        h_{\bin} \gets RetrieveCredHandle(\osk,\utrans_{\bin}) \\
+        \pcif h_0 \in L \lor (h_1 \notin L \land b_1 = 0): \pcreturn 1 \\
         \pcreturn 0
@@
     disclosure based on \cite{fhs19}. 
-    $\mathcal{O}_{anon} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
-    ReqCredHandle,LoR\rbrace$. $\mathcal{O}_{forge} \gets \lbrace HU,CU,
-    Obtain,ObtIss,Issue,Show,ReqCredHandle \rbrace$. $ReqCredHandle$ is
-    equivalent to \OPEN, operating on transcripts \utrans instead of signatures.
-    In particular, this implies that it rejects queries for transcripts related
-    to challenge users. Also, \OWNR and \ATTR tables are essentially as in
-    \secref{ssec:model-uas}.}
+    $\mathcal{O}_{rac} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
+    ReqCredHandle\rbrace$. $ReqCredHandle$ is
+    equivalent to \OPEN, operating on transcripts \utrans instead of signatures
+    but, in addition, keeps a list of revoked users (per verifier), based on the
+    queries it receives. In $\Exp^{forge}_{\adv,rac}$, \adv~wins if it
+    authenticates using a revoked credential or with insufficient attributes, or
+    if it prevents an honest user from authenticating using a non-revoked
+    credential.}
   \label{fig:model-rac}  
@@
 issuer; and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally
-computes $F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval sets
-$\yeval^0$ to $0$, which the verifier interprets as ``revoked credential''.
+computes $F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval aborts.
 Otherwise, it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
@@
   $\fissue^1$ as issuance function.
-\item[$\langle 1/0,(\dattrs,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
+\item[$\langle 1/0,(\yeval,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
   \attrs,\dattrs,\cred),
@@
   using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
-  $\finsp^F$ as open function. The \dattrs value output by the verifier is
-  the $\yeval^0$ value produced by \Sign (when accepted by \Verify).
+  $\finsp^F$ as open function. The \yeval value output by the verifier, when
+  it accepts, is the $\yeval^0$ value produced by \Sign.
 \item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
   Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
-  \utrans, and runs \Open from $\CUASGen^{int}$. If $\yeval^0 \neq 0$ (i.e., the
-  signature was created by a non-revoked credential), this returns $(F(V,\cidi),
+  \utrans, and runs \Open from $\CUASGen^{int}$. This returns $(F(V,\cidi),
   F(V,\cidu))$, which the verifier can add to its revocation list $L$.
@@
   If the base $\CUASGen^{int}$ construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, and $F$ is one-way, then \CUASRAC is an
-  anonymous AC scheme according to \cite{fhs19}.  
+  \defref{def:sign-anonymity-uas}, then \CUASRAC is an anonymous AC scheme
+  according to \cite{fhs19}.  
 \end{theorem}
@@
   If the base $\CUASGen^{int}$ construction is unforgeable according to
-  \defref{def:forge-uas}, and $F$ is one-way, then \CUASRAC is an unforgeable
-  RAC scheme.
+  \defref{def:forge-uas}, and $F$ is a one-way function, then \CUASRAC is an
+  unforgeable RAC scheme.
 \end{theorem}
 
-% Note that, if we aim at global credential (resp. user) revocation rather than
-% verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
-% pair (resp., \upk), and no assumption regarding $F$ is needed.
+Note that, if we aim at global credential (resp. user) revocation rather than
+verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
+pair (resp., \upk), and no assumption regarding $F$ is needed.
 

### 2022-08-21 prism-backend/research/gsac/conclusion-paper.tex
Pass on main body.

@@
 computed by the users themselves, who need to prove correct computation.
-Our setting also combines features of anonymous credential schemes, like
+Our setting combines features of anonymous credential schemes, like
 attribute-based credentials and multiple issuers, which we extend with openers
@@
 extending our model and constructions to span utility over \emph{multiple}
-signatures promises to be interesting, both regarding its modelling and the
-potential use cases.
+signatures promises to be interesting, both regarding its modelling, the
+potential use cases, and the generalization capabilities.
 

### 2022-08-21 prism-backend/research/gsac/formal-uas.tex
Pass on main body.

@@
 incorporate openers, as in GSs, but there is no tight relationship between
-issuer and opener. As a consequence, signers (potentially along with verifiers)
+issuer and opener. As a consequence, users (potentially along with verifiers)
 may choose, on a per-signature basis, the policies governing the utility
@@
 Somehow related, we model a scheme in which users generate their secret keys in
-a standalone way, and then leverage their keys to request credentials.
-Therefore, if one ``user'' generates (e.g.) two keys, and then uses each of
-these keys to request multiple credentials, then from the point of view of our
-modelling, we see this \emph{cryptographically} as two different users.
-This may seem too ideal to model real world situations. However, we argue that
-this can in fact be very close to reality, where a well-known issuer, after
-properly identifying a user, attests the (possibly blinded) public key this
-user proves control of. Indeed, our model and syntax support exactly this
-approach, by allowing users to leverage previously obtained credentials in
-order to request new ones.
+a standalone way, and then leverage these keys to request credentials. This may
+seem too ideal as a model for real world situations, as we cannot know how
+many keys a user has generated. However, we argue that this can in fact be very
+close to reality, where a well-known issuer, after properly identifying a user,
+attests the (possibly blinded) public key this user proves control of. Indeed,
+our model and syntax support exactly this approach, by allowing users to
+leverage previously obtained credentials in order to request new ones.
+A consequence of this is that, if ``one user'' generates (e.g.) two keys, and
+then uses each of these keys to request multiple credentials, then from the
+point of view of our modelling, we see this \emph{cryptographically} as two
+different users -- and, anyway, that same ``user'' cannot combine credentials
+bound to different keys.
 
@@
 may be done in several ways, depending on the situation: self-signing, relying
-on external PKIs, bulletin-boards, etc.
+on external PKIs, bulletin boards, etc.
 %
@@
   returns a global system parameter variable \parm. We assume that \parm are
-  available to all the other functions.
+  available to all other functions.
 \item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
@@
   credentials \sCred, a message \msg and evaluation function \feval, returns
-  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
+  signature \sig, and a value \yeval. We use use \Sig to denote the
   tuple $(\sig,\yeval)$.
@@
 the user who computes them, and has to prove correctness of such computation.
-We give concrete examples in \secref{sec:relationships}, and define them next:
+We give concrete examples in \secref{sec:relationships}.
 
 \begin{description}
-\item[$\fissue: (\upk,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]},\attrs)
+\item[$\fissue: (\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]})
   \rightarrow \yissue$.] Chosen
@@
   defines the customized conditions required by the issuer to grant a credential
-  over attributes \attrs, when requested by a user with public key \upk,
+  with identifier $\cid = (\cidi,\cidu)$, over attributes \attrs, when requested
+  by a user with public key \upk,
   leveraging a set of $n$ previously obtained credentials with identifiers and
@@
   a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
-  convention that $\yissue = 0$ means that the issuance request is denied.
-  \fissue functions must be \UAS-acceptable, as defined in
-  \defref{def:uas-acc-func}.
+  convention that $\yissue = 0$ means that the issuance request is denied; and
+  $\yissue \neq 0$ means that the request is approved. \fissue functions must be
+  \UAS-acceptable, as defined in \defref{def:uas-acc-func}.
 \item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
@@
   (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
-  values, $\yeval^0$ and $\yeval^1$. $\yeval^0$ is output directly alongside the
-  signature,  both can in addition be used to modulate the behaviour of
-  \finsp, and must belong in a well defined set \rngfeval. For readability,
-  we write $\Yeval = (\yeval^0,\yeval^1)$.
+  values, $\yeval^0$ and $\yeval^1$. Both must belong in a well defined set
+  \rngfeval. For readability, we write $\Yeval = (\yeval^0,\yeval^1)$.
 \item[$\finsp: (\Yeval,\upk,\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]},
@@
       \pcif b=0:
-      \yissue^* \gets \fissue(\upk,\lbrace (\cidi,\cattrs_i)
-      \rbrace_{i\in[n]},\attrs) \\
+      \yissue^* \gets \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)
+      \rbrace_{i\in[n]}) \\
       \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
@@
 %
-All tables/sets are initialized as empty tables/sets. For notational
-convenience, we often use these identifiers instead of the corresponding
-user/issuer/opener keys.
-%
-We use the following sets and tables in our definitions:
+For notational convenience, we often use these identifiers instead of the
+corresponding user/issuer/opener keys.
+%
+All tables/sets are initialized as empty tables/sets. We use the following sets
+and tables in our definitions:
 
@@
 \item[\HUGEN.] Adds a new honest user to the game, generating its keypair.
-\item[\HUGEN.] Adds a new corrupt user to the game, setting its \upk to the
+\item[\CUGEN.] Adds a new corrupt user to the game, setting its \upk to the
   value given by the adversary.  
@@
 %   key to the adversary.
-\item[\ISET.] ``Upgrades'' an user to become an issuer, specifying its
+\item[\ISET.] ``Upgrades'' a user to become an issuer, specifying its
   \fissue function.
@@
           \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
-          \pcif 0(\fissue(\PUBUK[\cuid_0],\PRVUK[\cuid_0],\cscid_0,\attrs)) \neq \\
-          \pcind 0(\fissue(\PUBUK[\cuid_1],\PRVUK[\cuid_1],\cscid_1,\attrs)):
+          \pcif 0(\fissue(\PUBUK[\cuid_0],(\cdot,\cidu),\attrs,\lbrace (\ccid_{0,i},\ATTR[\ccid_{0,i}])\rbrace_{i\in[n]})) \neq \\
+          \pcind 0(\fissue(\PUBUK[\cuid_1],(\cdot,\cidu),\attrs,\lbrace (\ccid_{1,i},\ATTR[\ccid_{1,i}])\rbrace_{i\in[n]})):
           \pcreturn \bot \\
@@
       \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
-      \pcind \pcif \fissue(\PUBUK[\uid],\PRVUK[\uid],\attrs,
+      \pcind \pcif \fissue(\PUBUK[\uid],\cid,\attrs,
       (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) \neq \yissue:
@@
 possible user-credential set pairs, the issuance protocol must either succeed or
-fail for both; also, the adversary can open signatures produced with credential
-sets containing challenge credentials $\cred_b$, only if the output of \Open is
-the same as with the complementary $\cred_{1-b}$ (note that any other signature
-can be opened).
-Intuitively, if the adversary cannot distinguish arbitrary runs with all oracles
-(provided the previous constraints) when he gets challenge credentials
+fail for both; also, the adversary cannot mix challenge and non-challenge
+credentials in the same call to the \SIGN oracle -- but can otherwise open
+any signature. With these restrictions, if the adversary cannot distinguish
+arbitrary runs with all oracles when he gets challenge credentials
 $\cred_b$, from runs with credentials $\cred_{1-b}$, then the issuance protocol
@@
 
-\paragraph{On the generality of anonymity in \UAS schemes.} %
-From the point of view of the achieved privacy, depending on how one defines
-\fissue, \feval and \finsp, it is easy to see that the resulting scheme would
-have different privacy levels. For instance, a scheme that has very granular
-\feval outputs barely provides privacy. Or a scheme for which most signatures
-include the same \finsp value has less accountability, but higher privacy.
-%
-This is a natural consequence of the fact that, with different choices of those
-functions, one can mimic the behaviour of (more restricted) schemes. For
-instance, by setting \finsp to output the signer's public key, and \feval to
-output nothing, one gets the same anonymity as in vanilla group signatures
-(concretely, no challenge signature can be opened). Or, if \feval outputs any
-arbitrary subset of the attributes in the used credential(s), and \finsp outputs
-any constant value, then we get the same anonymity as in conventional selective
-disclosure anonymous credential schemes, where any pair of users with different
-subset of revealed attributes are clearly distinguishable. The impact of \fissue
-is somehow orthogonal to the previous, but can be seen as a kind of equivalent
-to \feval, at issuance time.
-%
-Importantly, note that the model is agnostic to the concrete instantiation of
-these functions, and just cares about whether their outputs are equal or not,
-in order to avoid trivial wins by the adversary.
-
 \paragraph{Unforgeability.} \UAS inherits from AC schemes the notion that no
@@
 corrupting issuers. The adversary wins if it produces a valid signature that:
-(1) the produced signature leveraged with a credential for
+(1) the produced signature leveraged a credential for
 which the conditions required by \fissue were not satisfied; (2), opens to a
@@
         \pcif \exists i\in[n]~\suchthat~
-        \fissue(\upk,\usk,\attrs_i,\lbrace(\cid_{i,j},\attrs_{i,j})
+        \fissue(\upk,\cid_i,\attrs_i,\lbrace(\cid_{i,j},\attrs_{i,j})
         \rbrace_{j\in[n_i]}) \neq \yissue^i \lor
-        \OWNR[\lbrace\cid_{i,j}\rbrace_{j\in[n_i]}]\notin \HU \cup \CU, \\
+        \OWNR[\cid_i \cup \lbrace\cid_{i,j}\rbrace_{j\in[n_i]}]\notin \HU \cup \CU, \\
         \pcind \textrm{where}~(\yissue^i,\utrans) \gets \trans[\cid_i]~\textrm{and}~
         (\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
-        \rbrace_{j\in[n_i]}) \gets \ExtractIssue(\trap,\utrans]): \\
+        \rbrace_{j\in[n_i]}) \gets \ExtractIssue(\trap,\utrans): \\
         \pcind \pcreturn 1 \\        
@@
 
-\paragraph{On the generality of unforgeability in \UAS schemes.} %
-Regarding the information revealed at signature time ($\yeval^0$), \UAS's
-unforgeability notion is equivalent to that of known AC schemes. It is the
-generalization of the information output at opening time ($\yinsp$), only
-present up to know in MPS \cite{ngsy22} what makes the notion of unforgeability
-more subtle. The fact that multiple users may produce signatures opening to the
-same value necessarily forces to generalize what is a forgery -- and, certainly,
-resorting to extraction-based techniques seems unavoidable.
-
-As with anonymity, by tweaking the \fissue, \feval and \finsp
-functions, one can easily mimic behaviour of more restricted schemes. For
-instance, \feval, along with the $\yeval^0$ output, allows revealing
-authenticated attribute-related information alongside the signatures, as in AC
-schemes. Or, with \fissue, rules for delegation can be easily encoded, leading
-to delegatable schemes.
-
 \paragraph{Non-frameability.} %
 The notion of non-frameability in \UAS schemes is unavoidably more subtle than
-in group signatures. To see this, we note that, by allowing arbitrary
-evaluation and open functions to be used, it can be perfectly valid to
-have a signature produced by a corrupted user output the same \yeval or \yinsp
-values than the ones output when evaluating or opening a signature by an honest
-user.
+in group signatures\footnote{As far as we know, non-frameability has not been
+  considered in anonymous credential schemes. Thus, \UAS is the first scheme
+  that concretely models what can we expect, unforgeability-wise, in the
+  presence of malicious issuers in the AC domain.}. To see
+this, note that, by allowing arbitrary evaluation and open functions to be used,
+it can be perfectly valid to have a signature produced by a corrupted user
+output the same \yeval or \yinsp values than the ones output when evaluating or
+opening a signature by an honest user.
 %
@@
 included in user credentials, the adversary may even be able to just produce
-``legitimate'' openings that output any desired value. Note that this is a
-relevant property, as it tells us the minimal unforgeability expectations we
+``legitimate'' openings that output any desired value. Note anyway that this is
+a relevant property, as it tells us the minimal unforgeability expectations we
 can have, even against malicious issuers and openers.
@@
 
-\paragraph{On the generality of non-frameability in \UAS schemes.} %
-The notion captured in \UAS is a sort of extension of the non-frameability
-notion in group signatures, in two aspects. First, by defining a very granular
-\finsp function (one that outputs the signers public key, or equivalent),
-we get a scheme in which it is not possible to frame a user at all. Yet, by
-defining a coarser \finsp function (e.g., one that outputs the nationality of
-the signer), while framing a single user is still not possible (the checks in
-lines 9 an 10 avoid it), in practice, there will be a set of ``potential
-candidates to frame'' (e.g., all users of the given nationality). This can be
-seen as a useful feature in many use cases, though.
-%
-The second aspect follows a similar reasoning, but through \feval. However, this
-type of functionality revealing information at signing time is not available in
-group signatures. Also, even though it is available in anonymous credentials, no
-equivalent property has been considered, to the best of our knowledge. Thus,
-through \UAS schemes, we extend the unforgeability expectations against corrupt
-issuers, to the AC domain.
-
-% Anonymous credentials do not have non-frameability property and, thus, it is
-% hard to make a comparison. However, we can draw some connections with AC schemes
-% that support revocation, as revocation is somehow equivalent to linking, which
-% is a type of inspection available in group signatures. In this sense, note that
-% basic revocation (without straight deanonymization) can be trivially achieved
-% through our generic \Open function. For instance, one could set \finsp to
-% be a pseudorandom number seeded with the user's public key (or credential). In
-% this sense, \Open could be essentially seen as a Verifiable Random Function.
-% If we compare with group signatures, our notion is also more general than the
-% conventional one, again for the same reason as sign unforgeability (i.e., \Open
-% can return any value, not just the signer's identity). Thus, the need to extract
-% the signer's data in order to detect if a framing has taken place.
+% \paragraph{Tradeoffs in privacy and security.} %
+% Note that, depending on how granular the behaviour and output of the \fissue,
+% \feval and \finsp functions are, the less private the resulting \UAS
+% instantiation would be, and vice versa. In some sense, this is captured in the
+% model as, the more granular the outputs are, the more constrained is the
+% adversary.
+% %
+% For instance, a \feval function that reveals all the attributes of the signing
+% credentials provides even less privacy than a conventional signature scheme. Or
+% a scheme that reveals all those attributes via \finsp is even more accountable
+% that a vanilla group signature scheme, as it directly gives away more personal
+% information than a public key.
+% %
+% Equivalent reasoning happens with \fissue, although there the behaviour (whether
+% a request is accepted or not) is what is more telling, rather than the output
+% of the function on its own.
+
+% Similarly, unforgeability and non-frameability in \UAS cannot just be concerned
+% on whether a signature is produced by a (set of) legitimately obtained
+% credentials. It must also worry about whether the values output by \feval and
+% \finsp are consistent. That is, a user who does not have a credential proving
+% some claim, should not be able to prove it. Conversely, if a user does not own
+% a credential that can produce some concrete \yeval or \yinsp values, should not
+% be ``suspicious'' of having produced a signature with those values. Moreover,
+% it may be possible that more than one user produces signatures evaluating (via
+% \yeval) or opening (via \yinsp) to the same values -- and it does not mean that
+% any of those users is being framed.
 
@@
 generic building blocks. We use three different NP relations:
-$\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and $\NIZKRel_{\Open}$, described next
+\RelIss, \RelSig, and \RelIns, described next
 and specified in CS notation \cite{cs97} in \figref{fig:nizkrels}.
@@
 \begin{description}
-\item[$\NIZKRel_{\Issue}$:] For NIZK proofs at issuance time. Requires users to
+\item[\RelIss:] For NIZK proofs at issuance time. Requires users to
   prove knowledge of \usk and the related \upk. It also requires that any
@@
   some issuer) and bound to \upk, and enforces the corresponding \fissue policy.
-\item[$\NIZKRel_{\Sign}$:] For NIZK proofs at signing time. Ensures that
+\item[\RelSig:] For NIZK proofs at signing time. Ensures that
   signatures ``encode'' the correct signature evaluation and opening values, and
   that any credential used to create the signature is bound to the same \upk.
-\item[$\NIZKRel_{\Open}$:] For NIZK proofs at opening time. Ensures that the
+\item[\RelIns:] For NIZK proofs at opening time. Ensures that the
   utility information extracted by the \Open algorithm is correct.
@@
 This is essentially achieved through an execution of an \SBCM interactive
-signing protocol with $\NIZKRel_{\Issue}$ as NP relation. Since \fissue is
+signing protocol with \RelIss as NP relation. Since \fissue is
 evaluated by the user, but depends on the \cidi value chosen by the issuer, the
@@
 \lbrace (\cid_i,\cattrs_i,\cred_i)\rbrace_{i \in [n]},r)$ for the relation
-$\NIZKRel_{\Issue}$. The credential \cred produced by the user is the result of
+\RelIss. The credential \cred produced by the user is the result of
 the interactive signing protocol, whereas the issuer produces $(\yissue,
@@
   \msg,\feval)$.} %
-In the signing algorithm, we make use of relation $\NIZKRel_{\Sign}$.
+In the signing algorithm, we make use of relation \RelSig.
 % 
@@
   \Open(\osk,\sipk,\Sig,\msg,\feval)$.} %
-Here we leverage relation $\NIZKRel_{\Open}$.
+Here we leverage relation \RelIns.
 %
@@
   \label{thm:correctness-uas}
-  If the underlying schemes for commitments, public-key encryption and \SBCM,
-  are correct, as well as the NIZKs for $\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$,
-  and $\NIZKRel_{\Open}$, our generic construction \CUASGen satisfies
+  If the underlying schemes for public-key encryption and \SBCM are correct, as
+  well as the NIZKs for \RelIss, \RelSig,
+  and \RelIns, our generic construction \CUASGen satisfies
   correctness as defined in \defref{def:correctness-uas}, except with negligible
@@
   \label{thm:issue-anonymity-uas}
-  If the \SBCM scheme is blinding, the NIZK system used for $\NIZKRel_{\Issue}$ 
+  If the \SBCM scheme is blinding, the NIZK system used for \RelIss 
   is zero-knowledge, and \fissue is a \UAS-acceptable function, our \CUASGen
@@
   \label{thm:sign-anonymity-uas}
-  If the NIZK system used for $\NIZKRel_{\Sign}$ is zero-knowledge, and the
+  If the NIZK system used for \RelSig is zero-knowledge, and the
   public-key encryption scheme is IND-CCA secure, our \CUASGen construction
@@
 %   \label{thm:issue-forge-uas}
-%   If the underlying NIZK used for $\NIZKRel_{\Issue}$ is zero-knowledge,
+%   If the underlying NIZK used for \RelIss is zero-knowledge,
 %   simulation extractable and sound, then our \CUASGen construction satisfies
@@
 %   \label{thm:sign-forge-uas}
-%   If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
-%   extractable, the scheme for $\NIZKRel_{\Open}$ is complete, the public key
+%   If the underlying NIZK scheme for \RelSig is simulation
+%   extractable, the scheme for \RelIns is complete, the public key
 %   encryption algorithm is correct, and the \SBCM scheme is correct and one-more
@@
   \label{thm:forge-uas}
-  If the underlying NIZK scheme for $\NIZKRel_{\Sign}$ is simulation
-  extractable, the scheme for $\NIZKRel_{\Open}$ is complete, the public key
-  encryption algorithm is correct, and the \SBCM scheme is correct and one-more
-  unforgeable, then our \CUASGen construction
-  satisfies unforgeability as defined in \defref{def:forge-uas}, except
-  with negligible probability.
+  If the underlying NIZK system for \RelSig is simulation extractable, the NIZK
+  system for \RelIns is complete, the public key encryption algorithm is
+  correct, and the \SBCM scheme is correct and one-more unforgeable, then our
+  \CUASGen construction satisfies unforgeability as defined in
+  \defref{def:forge-uas}, except with negligible probability.
 \end{theorem}
@@
   \label{thm:frame-uas}
-  If the underlying scheme for $\NIZK^{\Sign}$ is zero-knowledge and simulation
-  extractable, the scheme for $\NIZK^{\Open}$ is simulation-extractable, and the
+  If the underlying NIZK system for \RelSig is zero-knowledge and simulation
+  extractable, the NIZK system for \RelIns is simulation-extractable, and the
   \SBCM scheme is blind, then our \CUASGen
@@
 still meeting the \UAS model, may differ from \CUASGen. We describe one such
-variant next $\CUASGen^{hide-iss}$, that we leverage to build related schemes.
-%
-Similarly, we describe $\CUASGen^{int}$ which transforms \CUASGen by turning the
+variant next \CUASGenHideIss, that we leverage to build related schemes.
+%
+Similarly, we describe \CUASGenInt which transforms \CUASGen by turning the
 non-interactive signature and verification processes into an interactive
@@
 
-\paragraph{$\CUASGen^{hide-iss}$: $\NIZKRel_{\Sign}$ with issuer hiding.} %
+\paragraph{\CUASGenHideIss: \RelSig with issuer hiding.} %
 In \CUASGen it is required that the identity of the
@@
 are associated to the same set of (potential) issuers -- otherwise, it is
-trivial to distinguish signatures. Security for $\CUASGen^{hide-iss}$, based on
+trivial to distinguish signatures. Security for \CUASGenHideIss, based on
 security of \CUASGen, is sketched in \appref{sapp:sec-hide-iss}.
@@
   }
-  \caption{$\NIZKRel^{hide-iss}_{\Sign}$ relation for $\CUASGen^{hide-iss}$.}
+  \caption{$\NIZKRel^{hide-iss}_{\Sign}$ relation for \CUASGenHideIss.}
   \label{fig:nizk-ring}
@@
 
-\paragraph{$\CUASGen^{int}$: Interactive Credential Presentations with replay
+\paragraph{\CUASGenInt: Interactive Credential Presentations with replay
   protection.}
@@
 
-We sketch security of $\CUASGen^{int}$ in \appref{sapp:sec-interactive} assuming
+We sketch security of \CUASGenInt in \appref{sapp:sec-interactive} assuming
 the same security properties as in \UAS. Note that extra properties may be

### 2022-08-21 prism-backend/research/gsac/introduction-paper.tex
Pass on main body.

@@
 similar credentials. 
-
+%
 %% Usefulness of main precedents / motivation
@@
 divided into two components (trusted and partially trusted), and signing
-and verification are turned into an interactive protocol.
+and verification are interactive.
 
@@
 This separation does not hold in the approaches to build them, though. The
-probably most fruitful way to design and instantiate AC systems
-is with CL-type signatures \cite{cl02}. But the fact that they support efficient
+probably most fruitful way to instantiate AC is with CL-type signatures
+\cite{cl02}. But the fact that they support efficient
 zero-knowledge protocols for proving knowledge of a signature, makes them very
@@
 used to design and instantiate GS schemes \cite{gl19,dl21}, as is the case for
-PS16 signatures \cite{ps16,cdl+20}.
+PS16 signatures \cite{ps16,cdl+20} -- both, CL-type signatures.
 
@@
 present in AC schemes. For instance, non-frameability is not even considered
--- and it is non-frameability what ensures when a user cannot be held
+-- and it is non-frameability what ensures when cannot a user be held
 accountable.
@@
 model exists that combines both, in a general enough manner. Probably, the
-closest work to ours, in regard to this ``generalization spirit'', is
-\cite{ckl+15}, although it focuses only on anonymous credentials. In practice,
-needing to resort to too specific models forces system designers to decide which
-feature (utility at or after signing time, etc) they do not want to lose -- or,
-which one they will lose.
+most ambitious work in this regard is \cite{ckl+15}, although it focuses only on
+anonymous credentials. In practice, needing to resort to too specific models
+forces system designers to decide which feature (utility at or after signing
+time, etc) they do not want to lose -- or, which one they will lose.
 
@@
 Acknowledging that the strengths of AC are the weaknesses of GS, and vice versa,
-we come up with a unified model. In a nutshell, we give a syntax and model for
-anonymous signatures -- which can be turned into an interactive authentication
-system -- with attribute-enabled credentials, and generalised utility both at
-signature time, and after. Concretely, we propose a scheme
+and the inconvenience in practice of having a miriad of similar-but-different
+models, we come up with a unified one. In a nutshell, we give a syntax and model
+for anonymous signatures -- which can be turned into an interactive
+authentication system -- with attribute-enabled credentials, and generalised
+utility both at signature time, and after. Concretely, we propose a scheme
 through which it is possible to model revealing arbitrary claims at signing time
@@
 prove its security. To prove its universality, we show how restrictions of our
-generic construction directly imply the direct ancestors of UAS: group
+generic construction directly imply ancestors of UAS: group
 signatures and anonymous credentials. This includes not only their vanilla
@@
 build ring signatures (RS) in the model given by \cite{bkm06}, from an
-alternative construction that improves issuer privacy.
+alternative \UAS construction that improves issuer privacy.
 %
@@
 at all, ACs with full de-anonymization, RS with linkability, or anything in
-between -- like being able to deanonymize only if certain conditions are met.
+between.
 
@@
 issuance decision. Thus, it is necessary to model unforgeability guarantees
-already at that point -- something not considered in previous works. Also, in
+already at that point -- something not considered in previous works as far as
+we know. Also, in
 order to meet the general practice in AC, the model for \UAS includes multiple
@@
 A crucial aspect to cater for all possible variants that we aim to subsume, is
-the incorporation of ``placeholders'' enabling customisation. We introduce abstract
-functions whose computation needs to be proven correct by the user. Depending on
-the choice of these functions, one can instantiate a different related scheme,
-which is anyway secure according to our \UAS model. And
-besides them, we have to enable tweaking what utility information is (or can be)
-revealed at signing-time and after, in a robust manner -- a scheme that allows
-proving some claim at signing time, but a somehow contradictory one afterwards,
-is of little use. Hence, the statements proving correctness of computation by
-the signer need to include cross-references. This is also very useful, as one
-can modulate the information to be revealed after signing-time, with the
-information revealed at signing-time, allowing policies such as ``deanonymize
-only if 18+ years old''.
+the incorporation of ``functional placeholders'' enabling customisation. We
+introduce abstract functions whose computation needs to be proven correct by the
+user. Depending on the choice of these functions, one can instantiate a
+different related scheme, which is anyway secure according to our \UAS model.
+We also allow to modulate the information to be revealed after signing time,
+with the information revealed at signing time, allowing policies such as
+``deanonymize only if 18+ years old''.
 
 \paragraph{Sample real-world use cases.} %
-By enabling customization at issuance, signing and opening times, the
+By enabling customization at issuance, signing and opening times, as well as
+multiple uncoupled issuers and openers, the
 possibilities are large. As an example, consider a social network that requires
@@
 if s/he is over-age, or the email of the adult in charge if s/he is under-age.
-And that could be achieved via a policy for utility after signing time (at
-opening time). Finally, if, in the same social network, some other
+And that could be achieved via a policy for utility at opening time. Finally,
+if, in the same social network, some other
 issuer-user-verifier situation comes up that requires a different set of utility
 choices, just the appropriate functions would need to be changed, without the
-need to re-model from scratch (or at all) -- and, given that our model allows
-multiple issuers and openers, with different issuance and opening policies,
-both could coexist.
+need to re-model from scratch (or at all).
 
@@
 this is a powerful notion, that may finally allow research lines (AC and GS)
-that have followed different paths to benefit from the findings of each other.
-\figref{fig:relations} graphically summarises the relations we prove between
-\UAS and other schemes -- although, of course, many more are probably
+that have followed different paths to easily benefit from the findings of each
+other. \figref{fig:relations} graphically summarises the relations we prove
+between \UAS and other schemes -- although, of course, many more are probably
 achievable.

### 2022-08-21 prism-backend/research/gsac/relationships.tex
Pass on main body.

@@
 \UAS-acceptable (for $\rngfissue = \bin$); whereas $\fissue^{single,F,I}$ is
-\UAS-acceptable if $F$ is a secure PRF \needcite.
+\UAS-acceptable if $F$ is a secure PRF \cite{kl14}.
 
@@
         (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
-        d \gets \adv^{\mathcal{O}^{anon}}(\gpk,\isk) \\
+        d \gets \adv^{\mathcal{O}_{anon}}(\gpk,\isk) \\
         \pcreturn d 
@@
         (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
-        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
+        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}_{frame}}
         (\gpk,\osk,\isk) \\
@@
         (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
-        (\msg,\sig) \gets \adv^{\mathcal{O}^{trace}}(\gpk,\osk) \\
+        (\msg,\sig) \gets \adv^{\mathcal{O}_{trace}}(\gpk,\osk) \\
         \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
@@
     referenced paper.
-    $\mathcal{O}^{anon} \gets \lbrace Ch,Open,SndToU,WReg,USK,CrptU \rbrace$,
-    $\mathcal{O}^{trace} \gets \lbrace SndToI,AddU,RReg,GSig,USK,CrptU \rbrace$,
-    and $\mathcal{O}^{frame} \gets \lbrace SndToU,WReg,GSig,USK,CrptU \rbrace$.
+    $\mathcal{O}_{anon} \gets \lbrace \oracle{Ch},\oracle{Open},\oracle{SndToU},
+    \oracle{WReg},\oracle{USK},\oracle{CrptU} \rbrace$,
+    $\mathcal{O}_{trace} \gets \lbrace \oracle{SndToI},\oracle{AddU},
+    \oracle{RReg},\oracle{GSig},\oracle{USK},\oracle{CrptU} \rbrace$,
+    and $\mathcal{O}_{frame} \gets \lbrace \oracle{SndToU},\oracle{WReg},
+    \oracle{GSig},\oracle{USK},\oracle{CrptU} \rbrace$.
   }
@@
 PRF. In that case, its output is a random-looking string that depends on the
-user public key \upk, and a string $I$ uniquely identifying the user. Thus, it
+user public key \upk, and a string $I$ uniquely identifying the issuer. Thus, it
 will be the same per $(\upk,I)$ pair, and can be used by issuer $I$ to prevent
@@
 \paragraph{Security of \CUASGS.} %
-We state next the theorems for the security of \CUASGS. The proofs are available
-in \appref{app:related-proofs}.
+Our \CUASGS construction is an anonymous, traceable, and non-frameable group
+signature scheme, according to the model in \cite{bsz05}. For space constraints,
+proofs are deferred to \appref{app:related-proofs}.
 
-\begin{theorem}[Anonymity of \CUASGS]
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASGS is an anonymous group signature
-  scheme.
-\end{theorem}
+% \begin{theorem}[Anonymity of \CUASGS]
+%   If the base \CUASGen construction has signature anonymity according to
+%   \defref{def:sign-anonymity-uas}, then \CUASGS is an anonymous group signature
+%   scheme.
+% \end{theorem}
 
-\begin{theorem}[Traceability of \CUASGS]
-  If the base \CUASGen construction is unforgeable according to
-  \defref{def:forge-uas}, then \CUASGS is a traceable group signature scheme.
-\end{theorem}
+% \begin{theorem}[Traceability of \CUASGS]
+%   If the base \CUASGen construction is unforgeable according to
+%   \defref{def:forge-uas}, then \CUASGS is a traceable group signature scheme.
+% \end{theorem}
 
-\begin{theorem}[Non-frameability of \CUASGS]
-  If the base \CUASGen construction is non-frameable according to
-  \defref{def:frame-uas}, then \CUASGS is a non-frameable group signature
-  scheme.
-\end{theorem}
+% \begin{theorem}[Non-frameability of \CUASGS]
+%   If the base \CUASGen construction is non-frameable according to
+%   \defref{def:frame-uas}, then \CUASGS is a non-frameable group signature
+%   scheme.
+% \end{theorem}
 
@@
         ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
-        (i_0,i_1,R,\msg,\st) \gets \adv^{SIGN}(\pk_1,\dots,\pk_n) \\
+        (i_0,i_1,R,\msg,\st) \gets \adv^{\oracle{SIGN}}(\pk_1,\dots,\pk_n) \\
         \pcif R \not\subseteq \lbrace \pk_i \rbrace_{i\in[n]} \lor
@@
         ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
-        (R,\sig,\msg) \gets \adv^{SIGN,CORR}(\pk_1,\dots,\pk_n) \\
+        (R,\sig,\msg) \gets \adv^{\oracle{SIGN},\oracle{CORR}}
+        (\pk_1,\dots,\pk_n) \\
         \pcif Verify(R,\sig,\msg) = 0: \pcreturn 0 \\
@@
   }
-  \caption{Security games for ring signatures \cite{bkm06}. The $SIGN$ oracle
-    accepts $(i,R,\msg)$ tuples, with $pk_i \in R$, adds the tuple to a list of
-    queries, and returns $\sig \gets Sign(\sk_i,R,\msg)$. $CORR$
-    accepts an index $i$, and leaks $\sk_i$. Corrupted users are added
-    to $CU$.}
+  \caption{Security games for ring signatures \cite{bkm06}. The $\oracle{SIGN}$
+    oracle accepts $(i,R,\msg)$ tuples, with $pk_i \in R$, adds the tuple to a
+    list of queries, and returns $\sig \gets Sign(\sk_i,R,\msg)$.
+    $\oracle{CORR}$ accepts an index $i$, and leaks $\sk_i$. Corrupted users are
+    added to $CU$.}
   \label{fig:model-rs}  
@@
 is essentially a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
-of our $\CUASGen^{hide-iss}$ construction. In a nutshell, we let users self-issue
+of our \CUASGenHideIss construction. In a nutshell, we let users self-issue
 credentials where the attributes are (a subset of encodings of) the public keys
 of the users in the system -- including their own public key. Then, a ring
-signature is just a $\CUASGen^{hide-iss}$ signature that reveals a subset of
+signature is just a \CUASGenHideIss signature that reveals a subset of
 the attributes -- i.e., a subset of the keys of the users in the system. In more
@@
 \begin{description}
-%\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in $\CUASGen^{hide-iss}$.
+%\item[$\parm \gets \Setup(\secpar,\AttrSpace)$.] As in \CUASGenHideIss.
 \item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
-  $\parm \gets \Setup(\secpar)$ from $\CUASGen^{hide-iss}$. Then, for each of
+  $\parm \gets \Setup(\secpar)$ from \CUASGenHideIss. Then, for each of
   the $i \in [n]$ users to generate, run $(\upk_i,\usk_i) \gets \KeyGen(\parm)$,
@@
   \Sign(\usk,\opk,\Cred,\msg,\feval^{\sring,\dattrs})$ from
-  $\CUASGen^{hide-iss}$. Note that \dattrs defines the public keys within
+  \CUASGenHideIss. Note that \dattrs defines the public keys within
   $\attrs \subseteq \sring$ to be revealed through \yeval.
@@
   runs $\Verify(\opk,\yeval,\Sig,\msg,\feval^{\sring,\dattrs})$ as in
-  $\CUASGen^{hide-iss}$. Note that, in valid signatures, $\yeval = \lbrace
+  \CUASGenHideIss. Note that, in valid signatures, $\yeval = \lbrace
   \ipk_i\rbrace_{i\in\dattrs}$.
@@
 \paragraph{Security of \CUASRing.} %
-We state next the theorems for the security of \CUASRing. The proofs are
-available in \appref{app:related-proofs}.
+Our \CUASRing construction is an anonymous and unforgeable ring signature
+scheme, according to the model in \cite{bkm06}. For space constraints,
+proofs are deferred to \appref{app:related-proofs}.
 
-\begin{theorem}[Anonymity of \CUASRing]
-  If the base $\CUASGen^{hide-iss}$ construction has signature anonymity
-  according to \defref{def:sign-anonymity-uas}, then \CUASRing is an anonymous
-  ring signature scheme.
-\end{theorem}
+% \begin{theorem}[Anonymity of \CUASRing]
+%   If the base \CUASGenHideIss construction has signature anonymity
+%   according to \defref{def:sign-anonymity-uas}, then \CUASRing is an anonymous
+%   ring signature scheme.
+% \end{theorem}
 
-\begin{theorem}[Unforgeability of \CUASRing]
-  If the base $\CUASGen^{hide-iss}$ construction is non-frameable according to
-  \defref{def:frame-uas}, then \CUASRing is an unforgeable ring signature
-  scheme.
-\end{theorem}
+% \begin{theorem}[Unforgeability of \CUASRing]
+%   If the base \CUASGenHideIss construction is non-frameable according to
+%   \defref{def:frame-uas}, then \CUASRing is an unforgeable ring signature
+%   scheme.
+% \end{theorem}
 
@@
 anonymous credential scheme is defined via $OrgKeyGen$ (which we rename to
-$IssKeyGen$), and $UserKeyGen$ algorithms, and $Obtain,
-Issue$ and $Show,Verify$ interactive protocols. The security definitions rely on
-$HU, CU, ObtIss, Obtain, Issue, Show$, and $LoR$ oracles. We refer to
-\cite{fhs19} for the full details. For ease of reference, we summarize the
-security definitions in \figref{fig:model-ac}.% , with inocuous
+$IssKeyGen$), and $UserKeyGen$ algorithms, and $\langle Obtain,Issue\rangle$
+and $\langle Show,Verify \rangle$ interactive protocols. We
+refer to \cite{fhs19} for the full details. For ease of reference, we summarize
+the security definitions in \figref{fig:model-ac}.% , with inocuous
 % adaptations to make them more suitable for comparison with our definitions --
@@
         (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
-        b^* \gets \adv^{HU,CU,Obtain,Show,LoR}(\isk) \\
+        b^* \gets \adv^{\oracle{HU},\oracle{CU},\oracle{Obtain},
+          \oracle{Show},\oracle{LoR}}(\isk) \\
         \pcreturn b^*
@@
         (\ipk,\isk) \gets IssKeyGen(1^\secpar) \\        
-        (D,\st) \gets \adv^{HU,CU,ObtIss,Issue,Show}(\ipk) \\
+        (D,\st) \gets \adv^{\oracle{HU},\oracle{CU},\oracle{ObtIss},
+          \oracle{Issue},\oracle{Show}}(\ipk) \\
         \langle \cdot,(b,\utrans) \rangle
@@
 \subsubsection{\CUASAC Construction.} %
-We show that a $(\fissue^1,\feval^{\dattrs},\finsp^0)$-$\CUASGen^{int}$
+We show that a $(\fissue^1,\feval^{\dattrs},\finsp^0)$-\CUASGenInt
 restriction, is a secure anonymous credential scheme according to the model in
@@
 %   \CUASGen construction. Returns $\parm \gets (\parm',\opk)$.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] From $\CUASGen^{int}$, run $\parm'
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] From \CUASGenInt, run $\parm'
   \gets \Setup(1^\secpar)$ and $(\opk,\osk) \gets \OKeyGen(\parm',
@@
   \usk$.
-\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from $\CUASGen^{int}$.
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from \CUASGenInt.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
   \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  Runs $\langle \Obtain,\Issue \rangle$ from $\CUASGen^{int}$.
-\item[$\langle 1/0,((1,\utrans)/(0,\utrans)\rangle
+  Runs $\langle \Obtain,\Issue \rangle$ from \CUASGenInt.
+\item[$\langle 1/0,((\yeval,\utrans)/(0,\utrans)\rangle
   \gets \langle Show(\ipk,\attrs,\dattrs,
   \cred),\Verify(\ipk,\dattrs) \rangle$.]
-  Runs the interactive $\langle \Sign, \Verify\rangle$ of  $\CUASGen^{int}$,
+  Runs the interactive $\langle \Sign, \Verify\rangle$ of  \CUASGenInt,
   using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
-  open function, with \opk from \parm as opener public key.
+  open function, with \opk from \parm as opener public key. The \yeval value
+  output by the verifier, when it accepts, is the $\yeval^0$ value produced by
+  \Sign in \CUASGenInt.
 \end{description}
@@
 \paragraph{Security of \CUASAC.} %
-We state next the theorems for the security of \CUASAC. The proofs are
-available in \appref{app:related-proofs}.
+Our \CUASAC construction is an anonymous and unforgeable anonymous credential
+scheme, according to the model in \cite{fhs19}. For space constraints,
+proofs are deferred to \appref{app:related-proofs}.
 
-\begin{theorem}[Anonymity of \CUASAC]
-  \label{thm:anon-cuasac}
-  If the base $\CUASGen^{int}$ construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
-  according to \cite{fhs19}.
-\end{theorem}
+% \begin{theorem}[Anonymity of \CUASAC]
+%   \label{thm:anon-cuasac}
+%   If the base \CUASGenInt construction has signature anonymity according to
+%   \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
+%   according to \cite{fhs19}.
+% \end{theorem}
 
-\begin{theorem}[Unforgeability of \CUASAC]
-  \label{thm:forge-cuasac}
-  If the base $\CUASGen^{int}$ construction is unforgeabile according to
-  \defref{def:forge-uas}, then \CUASAC is an unforgeable AC scheme.
-\end{theorem}
+% \begin{theorem}[Unforgeability of \CUASAC]
+%   \label{thm:forge-cuasac}
+%   If the base \CUASGenInt construction is unforgeabile according to
+%   \defref{def:forge-uas}, then \CUASAC is an unforgeable AC scheme.
+% \end{theorem}
 
@@
         (\ipk,\isk) \gets IssKeyGen(\parm) \\        
-        b^* \gets \adv^{\mathcal{O}_{rac},LoR}(\parm,\ipk,\opk) \\
+        b^* \gets \adv^{\mathcal{O}_{rac},\oracle{LoR}}(\parm,\ipk,\opk) \\
         \pcreturn b^*
@@
     disclosure based on \cite{fhs19}. 
-    $\mathcal{O}_{rac} \gets \lbrace HU,CU,Obtain,Issue,ObtIss,Show,
-    ReqCredHandle\rbrace$. $ReqCredHandle$ is
+    $\mathcal{O}_{rac} \gets \lbrace \oracle{HU},\oracle{CU},\oracle{Obtain},
+    \oracle{Issue},\oracle{ObtIss},\oracle{Show},\oracle{ReqCredHandle}\rbrace$.
+    $\oracle{ReqCredHandle}$ is
     equivalent to \OPEN, operating on transcripts \utrans instead of signatures
@@
     queries it receives. In $\Exp^{forge}_{\adv,rac}$, \adv~wins if it
-    authenticates using a revoked credential or with insufficient attributes, or
-    if it prevents an honest user from authenticating using a non-revoked
-    credential.}
+    authenticates using a revoked credential or despite not having the required
+    attributes, or if it prevents an honest user from authenticating using a
+    non-revoked credential.}
   \label{fig:model-rac}  
@@
 Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,F,V,L},
-\finsp^{F})$-$\CUASGen^{int}$ restriction. \feval is parameterized with a PRF
-$F$, a string identifying the verifier $V$ and a list $L$ of ``revocation
-handles'' by $V$. Note that these can be hardcoded, though: $F$ can be common to
-all verifiers, $V$ is also fixed (per verifier),
-and $L$ can be updated with some reasonable frequency -- e.g., daily -- so that
+\finsp^{F})$-\CUASGenInt restriction. \feval is defined via a set of
+attributes \dattrs to reveal (e.g., age, etc.), a PRF $F$, a string identifying
+the verifier $V$ and a list $L$ of revocation handles by $V$. Note that,
+these ``extra parameters'' can be hardcoded, though: $F$ can be a fixed PRF for
+all verifiers, \dattrs and $V$ are also fixed (per verifier), and $L$ can be
+updated per verifier with some reasonable frequency -- e.g., daily -- so that
 the cost of recomputing $\feval^{\dattrs,F,V,L}$ is not high.
 %
-Since credentials in $\CUASGen^{int}$ have two identifiers (\cidi, chosen by the
+Since credentials in \CUASGenInt have two identifiers (\cidi, chosen by the
 issuer; and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally
@@
 \item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
-  \CUASGen.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from our
-  $\CUASGen^{int}$ construction, setting $\fissue^1$ as issuance function.
-\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from our
-  $\CUASGen^{int}$ construction, setting $\finsp^F$ as opening function.
-\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from the
-  $\CUASGen^{int}$ construction.
+  \CUASGenInt.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from
+  \CUASGenInt, setting $\fissue^1$ as issuance function.
+\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from \CUASGenInt,
+  setting $\finsp^F$ as opening function.
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from \CUASGenInt.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
   \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGen, using
+  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGenInt, using
   $\fissue^1$ as issuance function.
@@
   \Verify(\ipk,\dattrs) \rangle$.]
-  Runs the interactive $\langle\Sign,\Verify\rangle$ of $\CUASGen^{int}$,
+  Runs the interactive $\langle\Sign,\Verify\rangle$ of \CUASGenInt,
   using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
   $\finsp^F$ as open function. The \yeval value output by the verifier, when
-  it accepts, is the $\yeval^0$ value produced by \Sign.
+  it accepts, is the $\yeval^0$ value produced by \Sign in \CUASGenInt.
 \item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
   Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
-  \utrans, and runs \Open from $\CUASGen^{int}$. This returns $(F(V,\cidi),
+  \utrans, and runs \Open from \CUASGenInt. This returns $(F(V,\cidi),
   F(V,\cidu))$, which the verifier can add to its revocation list $L$.
@@
 \paragraph{Security of \CUASRAC.} %
-We state next the theorems for the security of \CUASRAC. The proofs are
-available in \appref{app:related-proofs}.
+Our \CUASRAC construction is an anonymous and unforgeable revocable anonymous
+credential scheme, according to the model in \figref{fig:model-rac}. For space
+constraints, proofs are deferred to \appref{app:related-proofs}.
 
-\begin{theorem}[Anonymity of \CUASRAC]
-  If the base $\CUASGen^{int}$ construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASRAC is an anonymous AC scheme
-  according to \cite{fhs19}.  
-\end{theorem}
+% \begin{theorem}[Anonymity of \CUASRAC]
+%   If the base \CUASGenInt construction has signature anonymity according to
+%   \defref{def:sign-anonymity-uas}, then \CUASRAC is an anonymous AC scheme
+%   according to \cite{fhs19}.  
+% \end{theorem}
 
-\begin{theorem}[Unforgeability of \CUASRAC]
-  If the base $\CUASGen^{int}$ construction is unforgeable according to
-  \defref{def:forge-uas}, and $F$ is a one-way function, then \CUASRAC is an
-  unforgeable RAC scheme.
-\end{theorem}
-
-Note that, if we aim at global credential (resp. user) revocation rather than
-verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
-pair (resp., \upk), and no assumption regarding $F$ is needed.
+% \begin{theorem}[Unforgeability of \CUASRAC]
+%   If the base \CUASGenInt construction is unforgeable according to
+%   \defref{def:forge-uas}, and $F$ is a one-way function, then \CUASRAC is an
+%   unforgeable RAC scheme.
+% \end{theorem}
 
@@
 customized issuance is achieved in \UAS via the \fissue functions, with no
-equivalent in MPS -- instead, MPS has the fixed policy of
+equivalent in MPS -- instead, MPS can be seen as having the fixed policy of
 ``proving knowledge of a user secret key''. These extensions are not trivial
@@
 unencrypted allows implementing very useful variants such as anonymous
-credentials, as shown before.
+credentials with selective disclosure, as shown before.
 
@@
 \subsubsection{\CUASMPS construction.} %
-As mentioned, any $(\fissue^{single,F,I},\feval^{g,MPS},
-\finsp^{h,MPS})$-restriction implements an MPS scheme where $F=\feval^{\yeval^1}$
-and $G=\finsp^\ast$. With these functions, the construction is direct.
+As mentioned, a $(\fissue^{single,F,I},\feval^{g,MPS},
+\finsp^{h,MPS})$-restriction implements an MPS scheme where $F=\feval^{g,MPS}$
+and $G=\finsp^{h,MPS}$. With these functions, the construction is direct.
 \CUASMPS's setup runs \CUASGen's \Setup, \OKeyGen, and generates the issuer key
-pair by running \KeyGen and \ISet (with $\fissue^1$). For MPS's join, \CUASMPS
-runs first \KeyGen to generate the user key pair, and then proceeds as in
-\CUASGen. \Sign, \Verify and \Open, are as in \CUASGen.
+pair by running \KeyGen and \ISet (with $\fissue^{single,F,I}$). For MPS's join,
+\CUASMPS runs first \KeyGen to generate the user key pair, and then proceeds as
+in \CUASGen. \Sign, \Verify and \Open, are as in \CUASGen.
 %
@@
 \paragraph{Security of \CUASMPS.} %
-We state next the theorems for the security of \CUASMPS. The proofs are
-available in \appref{app:related-proofs}.
+Our \CUASMPS construction satisfies the privacy-1, extractability,
+unforgeability-1 and unforgeability-2 definitions of an MPS system, as modelled
+in \cite{ngsy22}. For space constraints, proofs are deferred to
+\appref{app:related-proofs}.
 
-\begin{theorem}[Privacy-1 of \CUASMPS]
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASMPS satisfies privacy-1
-  according to \cite{ngsy22}.
-\end{theorem}
+% \begin{theorem}[Privacy-1 of \CUASMPS]
+%   If the base \CUASGen construction has signature anonymity according to
+%   \defref{def:sign-anonymity-uas}, then \CUASMPS satisfies privacy-1
+%   according to \cite{ngsy22}.
+% \end{theorem}
 
-\begin{theorem}[Extractability of \CUASMPS]
-  If the base \CUASGen construction is unforgeable according to
-  \defref{def:forge-uas}, then it is an extractable MPS scheme.
-\end{theorem}
+% \begin{theorem}[Extractability of \CUASMPS]
+%   If the base \CUASGen construction is unforgeable according to
+%   \defref{def:forge-uas}, then it is an extractable MPS scheme.
+% \end{theorem}
 
-\begin{theorem}[Unforgeability-1 of \CUASMPS]
-  If the base \CUASGen construction is unforgeable according to
-  \defref{def:forge-uas}, then \CUASMPS satisfies unforgeability-1 as
-  defined in \cite{ngsy22}.
-\end{theorem}
+% \begin{theorem}[Unforgeability-1 of \CUASMPS]
+%   If the base \CUASGen construction is unforgeable according to
+%   \defref{def:forge-uas}, then \CUASMPS satisfies unforgeability-1 as
+%   defined in \cite{ngsy22}.
+% \end{theorem}
 
-\begin{theorem}[Unforgeability-2 of \CUASMPS]
-  If the base \CUASGen construction has non-frameability according to
-  \defref{def:frame-uas}, then \CUASMPS satisfies unforgeability-2 as
-  defined in \cite{ngsy22}.
-\end{theorem}
+% \begin{theorem}[Unforgeability-2 of \CUASMPS]
+%   If the base \CUASGen construction has non-frameability according to
+%   \defref{def:frame-uas}, then \CUASMPS satisfies unforgeability-2 as
+%   defined in \cite{ngsy22}.
+% \end{theorem}
 

### 2022-08-21 prism-backend/research/gsac/app-uas-proofs.tex
Updated correctness.

@@
 \begin{proof}[\thmref{thm:correctness-uas}; Correctness of \CUASGen]
-  By correctness of \SBCM and the NIZK for $\NIZKRel_{\Sign}$, the signature
-  produced at line 5 of \ExpCorrect is accepted at line 6 by \Verify.
+  By correctness of \SBCM and the NIZK for \RelSig, the signature
+  produced at line 4 of \ExpCorrect is accepted at line 5 by \Verify.
   Moreover, all the credentials employed to honestly produce the signature,
-  identified with \scid, meet their respective issuance policies due to
-  correctness of the NIZK for $\NIZKRel_{\Issue}$, so no $\fissue^\cid$ check
-  returns $0$ at line 9. Similarly, as $\feval \in \famfeval$ is checked at
-  line 3, and due to correctness of the NIZK for $\NIZKRel_{\Sign}$, the
-  output of \feval matches $\yeval^0$ at line $11$, which must have been
-  computed over $\usk=\UK[\uid]$, as in line $10$, due to correctness of the
-  commitment scheme. Finally, correctness of the NIZKs for $\NIZKRel_{\Sign}$
-  and $\NIZKRel_{\Open}$, and correctness of the encryption scheme, ensure that
-  \Judge accepts the proof produced by \Open, and \yinsp is the correct value
-  for the chosen $\finsp^{\oid}$.
+  identified with \scid, meet their respective (honest) issuance policies due to
+  correctness of the NIZK for \RelIss, so no $\fissue^{\cid}$ check
+  returns $\neq \yissue^i$ at line 10. Similarly, as $\feval \in \famfeval$ is
+  checked at line 3, and due to correctness of the NIZK for \RelSig,
+  the output of \feval matches \yeval at line $12$. Finally, correctness of the
+  NIZKs for \RelSig and \RelIns, and correctness of the encryption scheme,
+  ensure that \Judge accepts the proof produced by \Open, and \yinsp is the
+  correct value for the (honestly) chosen \finsp.
 \end{proof}

### 2022-08-31 prism-backend/research/gsac/functionality.tex
Preliminary version of a 4-pages-long 'one-pager'.

\section{How Does It Work?}
\label{sec:functionality}

In UAS, there are three types of entities: issuers, users, and openers. However,
cryptographically speaking, users and issuers are the same, with the only
exception that issuers advertise their public keys, and policy for issuance.

Users receive credentials from issuers -- a user can own multiple credentials,
even from the same issuer. Then, users leverage (one or more of) these
credentials to produce a signature. As part of producing a signature, users
may need to reveal arbitrary facts related to their credentials and, in
addition, specify an opener. If the need arises, this opener can extract further
information from the signature and involved credentials, in a process that is
known as \emph{opening} a signature. Crucially, no more information than what
the user chooses to reveal can be learned from the signature; yet, the verifier
gets full certainty that the signature comes from a user with a (set of) valid
credential(s). This high-level usage is defined in \figref{fig:functionality}

\begin{figure}[ht!]
  \centering
  % \input{figures/functionality-op.tex}
  \includegraphics[width=0.8\textwidth]{figures/uas-functionality.png}
  \caption{Sketch of the functionality in UAS schemes, and how the main actors
    interact through this functionality.}
  \label{fig:functionality}
\end{figure}

What makes UAS flexible, though, is the possibility to configure even on a
per-signature basis, the information that will be revelealed, at what time. We
do this via three \emph{functional placeholders}:

\begin{description}
\item[Issuance functions, \fissue:] Issuers are required to specify what
  conditions need to be satisfied by users asking them for credentials. This is
  especially useful when a user wants (or needs) to leverage previously obtained
  credentials (from the same or a different issuer) in order to support its new
  request.
\item[Signature evaluation functions, \feval:] To produce a signature, verifiers
  require that signers prove arbitrary facts over (a subset of) their
  credentials, including revealing specific attributes. This requirement is
  specified, on a per-signature basis, via a signature evaluation function,
  which may also be dependent on the signed message.
\item[Opening functions, \finsp:] On certain scenarios, after a signature is
  produced by its signer, additional information may be required. Opening
  functions control what information can be extracted in such cases, dependent
  on the signer's credentials, the signed message and, also, on the output of
  the evaluation function. In any case, only openers chosen by the signer will
  be able to extract this information.
\end{description}

In a nutshell, UAS provides the general framework for theoretical security and
privacy analysis -- and the $(\fissue,\feval,\finsp)$ functions define the
actual utility-vs-privacy tradeoff that is achieved. Importantly, since these
functions depend on user-private data, they have to be computed by the user.
But, at the same time, issuers, verifiers, and openers need to have certainty
that they have been computed correctly. Thus, zero-knowledge proofs%
\footnote{See, for instance, the Wikipedia entry, for a gentle introduction to
  the topic: \url{https://en.wikipedia.org/wiki/Zero-knowledge_proof}. Last
  access, August 30th, 2022.} play a crucial role in UAS.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas-onepager"
%%% End:

### 2022-08-31 prism-backend/research/gsac/introduction-onepager.tex
Preliminary version of a 4-pages-long 'one-pager'.

\section{Introduction}
\label{sec:introduction}

Identity management is one of the hardest problems in the digital domain%
\footnote{\url{https://www.maddyness.com/uk/2021/11/04/digital-identity-is-one-of-the-21st-centurys-biggest-challenges/}. Last access, August 30th, 2022.}.
It requires to address needs that are already complex on their own, such as:

\begin{itemize}
\item Establishing a connection between a digital persona and a physical one.
\item Interoperability across solutions.
\item Security and privacy, without sacrificing functionality.
\end{itemize}

As usual, the third item makes things even more complicated and, still, is
essential. Without proper handling of one's secrets, impersonation is trivial.
Without robust privacy protection mechanisms, high user adoption is unlikely,
and regulatory compliance, impossible. Yet, adding security makes systems less
usable, and adding privacy typically comes at the cost of using functionality.

From the previous, is not surprising that (privacy-preserving and secure)
digital identity has been a fertile ground for research. Indeed, at least for
the last four decades, it has been a recurring topic in the main cryptography
and security academic venues. Also, roughly during the last decade, it has
received increased attention in the industry\footnote{See, for instance, the
  Idemix and PrivacyABC projects, the W3C DID and Verifiable Credentials
  specification efforts, or the related ``anoncreds'' working group, etc.}

In fact, if one tries to get up to date with the latest advances in the domain,
a non-negligible added complexity is to navigate through the vast amount of
previous work. Quickly, seemingly incompatible systems arise, that offer a
different privacy-vs-utility tradeoff: from private systems that do not lose
utility at the cost of introducing a fully trusted third party who can revoke
anyone's privacy; to fully private systems that do not allow privacy revocation,
but lose all utility; passing through many things in between. Needing to make a
hard decission for a concrete privacy-vs-utility tradeoff is one of the big
drawbacks of existing systems.

We introduce here Universal Anonymous Signatures -- UAS, for short. UAS
is a flexible framework for privacy-preserving identities. Cryptographically,
it generalizes much work done durng the last 40 years. In UAS, identities are
sets of attested attributes, which have proven to be a powerful way to represent
physical-world identities. In addition, UAS enables that arbitrary claims are
proven based on these attributes, both at the time that a signature is verified
and, also \uline{afterwards} -- if needed and the request is granted by an
authority chosen by the signer. The claims to be proven are chosen by the
verifier (possibly jointly with the signer), but the signer is fully aware of
the information that will or may be revealed, if any. Indeed, the option to
reveal extra customizable information after the signature has been produced
enables very relevant use cases and, as we will see, makes a big difference in
addressing the privacy-vs-utility tradeoff. Finally, UAS is compatible with
industry efforts that focus on interoperability, such as W3C's Verifiable
Credentials or Anoncreds.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas-onepager"
%%% End:

### 2022-08-31 prism-backend/research/gsac/status.tex
Preliminary version of a 4-pages-long 'one-pager'.

\section{Where Are We?}
\label{sec:status}

Currently, we are completing our first iteration of foundational research. We
have a formal security model, generic construction, and security proofs for our
construction. This means that we have a solid common ground from which we can
start building concrete instantiations of UAS (such as those in
\secref{sec:use-cases}), and evaluate their performance in the real world.

Moreover, we are also beginning to work on integrating UAS within Atala Prism%
\footnote{\url{https://atalaprism.io}. Last access, August 30th, 2022.}, the
Self-Sovereign Identity (SSI) product from IOG\footnote{\url{https://iog.io}.
  Last access, August 30th, 2022.}, built atop of Cardano%
\footnote{\url{https://cardano.org}. Last access, August 30th, 2022.}, and
compliant with the most relevant specifications in the SSI domain.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "uas-onepager"
%%% End:

### 2022-09-13 prism-backend/research/gsac/app-related-extra.tex
Applying changes after pass.
Updated GS-MDO and DAC appendices.

@@
 signatures over such messages; and the opener, who performs the actual opening,
-but cannot do it without the tokens generated by the admitter. Intuitively, this
-can be seen as a sort of ``distribution'' of the opening capability. We define
-a variant of this model in which the admitter and opener are combined back into
-one entity (the opener), who can only open signatures over predefined messages,
-but cannot open any other signature. Moreover, our variant directly supports the
-scenario of multiple such openers, each being able to open only signatures
-over different messages. Note that it would not be hard to apply thresholding
-techniques to extend this case so that our ``unified'' opener role is shared
-across multiple entities, who have to cooperate in order to open a signature
-\needcite, thus achieving something very close ``in spirit'' to the scheme in
-\cite{ehk+19}. In addition, while \cite{ehk+19} follows the static group
-signature setting, we move to the dynamic one. Informally, our variant of GS-MDO
-is composed of the following algorithms: \Setup,
-\IKeyGen, \OKeyGen, \UKeyGen, \Sign, \Verify, \Open; as well as the $\langle
-\Obtain, \Issue \rangle$ interactive protocol. \OKeyGen generates an opening
-key pair which is already configured to open signatures only over some fixed
-(but arbitrary) set of messages. The remaining algorithms are as usual, so we
-defer a more detailed description to the construction. The oracles are the same
-as in \UAS. The resulting security model is given in \figref{fig:model-gsmdo},
-which we adapt from \cite{ehk+19}.
+but cannot do it without the tokens generated by the admitter. Intuitively,
+this can be seen as a sort of ``distribution'' of the opening capability. We
+define a variant in which the admitter and opener are combined
+back into one entity (the opener), who can only open signatures over predefined
+messages, but cannot open any other signature.
+% Moreover, our variant directly supports the
+% scenario of multiple such openers, each being able to open only signatures
+% over different messages.
+Note that it should still be possible to apply
+thresholding techniques to extend this case so that our ``unified'' opener role
+is shared across multiple entities, who have to cooperate in order to open a
+signature \cite{cdl+20}, thus achieving something very close ``in spirit'' to
+the scheme in \cite{ehk+19}. In addition, while \cite{ehk+19} follows the static
+group signature setting, we move to the dynamic one.
 
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.45\textwidth}        
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gsmdo}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets \IKeyGen(\parm) \\
-        b^* \gets \adv^{\mathcal{O}^{anon}}(\parm,\ipk) \\
-        \pcreturn b^*
-      }
+Informally, our variant of GS-MDO is composed of the same algorithms as the
+group signature model in \secref{ssec:related-models-gs}, with the exception
+that the $KeyGen$ algorithm also receives the $\finsp^{\smsg}$ function, defined
+as in \eref{eq:finspmsg}, and used to set up the opener.
 
-      \vspace*{5em}
+\begin{align}
+  & \finsp^{\smsg}(\cdot,\upk,\cdot,\msg) \coloneqq
+    \pcif \msg \in \smsg: \pcreturn \upk;~\pcelse \pcreturn 0
+    \label{eq:finspmsg}
+\end{align}
 
-      \procedure[linenumbering]{$\Exp^{frame}_{\adv,gsmdo}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets \IKeyGen(\parm) \\
-        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{frame}}
-        (\ipk,\isk) \\
-        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
-        \pcreturn 1~\pcif \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
-        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
-        \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
-        GSig(\PRVUK[\upk],\msg) \\
-        \pcreturn 0
-      }       
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.55\textwidth}
-      \procedure[linenumbering]{$\Exp^{trace}_{\adv,gsmdo}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\ipk,\isk) \gets \IKeyGen(\parm) \\
-        (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}^{trace}}
-        (\ipk,\opk,\osk) \\
-        \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
-        (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
-        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
-        = 0: \\ 
-        \pcind \pcreturn 1 \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for our GS-MDO variant.
-    $\mathcal{O}^{anon} \gets \lbrace \OGEN^{\smsg},\HUGEN,\CUGEN,\WREG,
-    \OBTAIN,\SIGN,\OPEN,\CHALb \rbrace$; $\mathcal{O}^{trace} \gets \lbrace
-    \OGEN,\HUGEN,\CUGEN,\ISSUE,\OBTISS,\RREG,\SIGN \rbrace$;
-    $\mathcal{O}^{frame} \gets \lbrace \OGEN,\HUGEN,\CUGEN,\WREG,
-    \OBTAIN,\SIGN \rbrace$. $\OGEN^{\smsg}$ is like \OGEN, but only accepting
-    functions of type $\finsp^{\smsg}$.
-  }
-  \label{fig:model-gsmdo}  
-\end{figure}
+The model is exactly the same as in
+\figref{fig:model-gs}. Note that this directly constraints anonymity in a
+similar way than \cite{ehk+19}: therein, anonymity (against admitter and opener,
+in respective properties that we unify since we do not distinguish the roles) is
+ensured only for messages that have not been ``disallowed''. In our case, as
+specified next, a message is disallowed by adding it to the \smsg set given to
+$KeyGen$ via $\finsp^{\smsg}$. Thus, if the adversary calls \oracle{Open} with a
+signature over a message that has been disallowed, \oracle{Open} rejects the
+query, as it would otherwise return different values for each challenge user
+(cf. \figref{fig:oracles2}); otherwise, if the message is allowed, the oracle
+returns the result of \Open -- just as in \cite{ehk+19}.
+
+Note that, for simplicity and to build upon our \CUASGS construction, we
+describe a variant where the set of messages to disallow is defined once via
+$KeyGen$. However, separating this into a dedicated \OKeyGen function that can
+be called multiple times, and thus allowing multiple openers, each with a
+different set of disallowed messages, is trivial -- and again, our definition
+of the \oracle{Open} oracle takes care of everything, as every challenge
+signature is produced over the same opener key.
+
+% \begin{figure}[ht!]
+%   \centering
+%   \scalebox{0.9}{      
+%     \begin{minipage}[t]{0.45\textwidth}        
+%       \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,gsmdo}(1^\secpar)$}{%
+%         (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
+%         b^* \gets \adv^{\mathcal{O}_{anon}}(\gpk,\isk) \\
+%         \pcreturn b^*
+%       }
+
+%       \vspace*{5em}
+
+%       \procedure[linenumbering]{$\Exp^{frame}_{\adv,gsmdo}(1^\secpar)$}{%
+%         (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
+%         (\msg,\sig,\upk,\tau) \gets \adv^{\mathcal{O}_{frame}}
+%         (\gpk,\osk,\isk) \\
+%         \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
+%         \pcreturn \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
+%         \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
+%         \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
+%         GSig(\PRVUK[\upk],\msg)
+%       }       
+%     \end{minipage}
+%   }
+%   \scalebox{0.9}{      
+%     \begin{minipage}[t]{.55\textwidth}
+%       \procedure[linenumbering]{$\Exp^{trace}_{\adv,gsmdo}(1^\secpar)$}{%
+%         (\gpk,\isk,\osk) \gets KeyGen(1^\secpar) \\
+%         (\msg,\sig) \gets \adv^{\mathcal{O}_{trace}}
+%         (\gpk,\osk) \\
+%         \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
+%         (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
+%         \pcreturn \upk \notin \HU \cup \CU \lor
+%         \Judge(\gpk,\upk,\msg,\sig,\tau) = 0
+%       }       
+%     \end{minipage}      
+%   }
+%   \caption{Security games for our GS-MDO variant.
+%     $\mathcal{O}^{anon} \gets \lbrace \OGEN^{\smsg},\HUGEN,\CUGEN,\WREG,
+%     \OBTAIN,\SIGN,\OPEN,\CHALb \rbrace$; $\mathcal{O}^{trace} \gets \lbrace
+%     \OGEN,\HUGEN,\CUGEN,\ISSUE,\OBTISS,\RREG,\SIGN \rbrace$;
+%     $\mathcal{O}^{frame} \gets \lbrace \OGEN,\HUGEN,\CUGEN,\WREG,
+%     \OBTAIN,\SIGN \rbrace$. $\OGEN^{\smsg}$ is like \OGEN, but only accepting
+%     functions of type $\finsp^{\smsg}$.
+%   }
+%   \label{fig:model-gsmdo}  
+% \end{figure}
 
 \subsubsection{\CUASGSMDO construction.} %
-We show that, as specified in \tabref{tab:uas-alt-funcs}, our \CUASGen
-construction for \UAS, restricted to $\fissue^1$ as issuance function,
-$\feval^0$ as signature evaluation function, and $\finsp^{\smsg}$ as opening
-function, is a secure group signature scheme with message dependent opening
-as modelled in \figref{fig:model-gsmdo}. We first quickly define the algorithms,
-and then prove security.
+Our \CUASGSMDO construction is essentially a $(\fissue^{single,F,I},\feval^0,
+\finsp^{\smsg})$-\CUASGen restriction, where $\fissue^{single,F,I}$ and
+$\feval^0$ are as in \figref{fig:func-restrictions}, and $\finsp^{\smsg}$, is as
+described in \eref{eq:finspmsg}. Since the construction is essentially a variant
+of our \CUASGen-based construction for group signatures, we describe it making
+reference to \CUASGS, in \secref{ssec:related-models-gs}:
 
 \begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.] Like in vanilla \CUASGen.
-\item[$(\upk,\usk) \gets \UKeyGen(1^\secpar)$.] Like the \UKeyGen function for
-  \CUASGS, in \secref{sapp:related-models-gs}.
+\item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar,\finsp)$.] Runs exactly as in
+  \CUASGS, except that it now receives an opening function, which must be of
+  the type $\finsp^{\smsg}$, for some \smsg.
+\item[$(\upk,\usk) \gets UKG(1^\secpar)$.] Like in \CUASGS.  
 \item[$\langle \cred,\utrans \rangle \gets
-  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Like the corresponding
-  protocol in in vanilla \CUASGS, \secref{sapp:related-model-gs}.
-\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Like in vanilla \CUASGen, limited
-  on evaluation functions $\feval^0$ and opening functions $\finsp^{\smsg}$.
-\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Like in vanilla \CUASGen.
-\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Like in vanilla
-  \CUASGen.
-\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Like in vanilla \CUASGen.
+  \langle\Obtain(\usk,\ipk),\Issue(\isk,\upk)\rangle$.] Like in \CUASGS.
+\item[$\sig \gets \Sign(\gpk,\cred,\msg)$.] Like in \CUASGS.
+\item[$1/0 \gets \Verify(\gpk,\sig,\msg)$.] Like in \CUASGS.
+\item[$(\upk,\pi) \gets \Open(\gpk,\osk,\trans,\sig,\msg)$.] Like in
+  \CUASGS.
+\item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Like in \CUASGen. Note that
+  \gpk includes an \opk with an opening fuction of type $\finsp^{\smsg}$.
 \end{description}
@@
 \paragraph{Security of \CUASGSMDO.} %
-Our \CUASGSMDO construction is a secure group signature scheme,
-according to the model in \figref{fig:model-gsmdo}, if the underlying \CUASGen
-construction is secure.
-
-Note that both  model construction are essentially restrictions to the model
-and construction of \CUASGen. Thus, security directly follows from security of
-\CUASGen.
-
-% \begin{theorem}[Anonymity of \CUASGSMDO]
-%   If the base \CUASGen construction is anonymous according to
-%   \defref{def:anonymity-uas}, then \CUASGSMDO is an anonymous group signature
-%   scheme.
-% \end{theorem}
-
-% \begin{proof}
-
-%   \qed
-% \end{proof}
-
-% \begin{theorem}[Traceability of \CUASGSMDO]
-%   If the base \CUASGen construction has unforgeable signing according to
-%   \defref{def:sign-forge-uas}, then \CUASGSMDO is a traceable group signature
-%   scheme.
-% \end{theorem}
-
-% \begin{proof}
-%   Traceability follows directly from the corresponding proof for \CUASGS.
-%   \qed
-% \end{proof}
-
-% \begin{theorem}[Non-frameability of \CUASGSMDO]
-%   If the base \CUASGen construction is non-frameable according to
-%   \defref{def:frame-uas}, then \CUASGSMDO is a non-frameable group signature
-%   scheme.
-% \end{theorem}
-
-% \begin{proof}
-%   Non-frameability follows directly from the corresponding proof for \CUASGS.
-%   \qed
-% \end{proof}
+Our \CUASGSMDO construction is a secure group signature scheme, if the
+underlying \CUASGen construction is secure.
+%
+Note that our construction for group signatures, \CUASGS, is a restriction to
+the construction of \CUASGen and, in turn, \CUASGSMDO is a restriction of
+\CUASGS, where we only accept opening functions of type $\finsp^{\smsg}$ --
+more constrained than the $\finsp^{\upk}$ functions used in \CUASGS. Thus, the
+security arguments given for \CUASGS in \appref{app:related-proofs}, apply
+directly here.
 
 \subsection{Delegatable Anonymous Credentials}
-\label{ssec:related-models-dac}
+\label{sapp:related-models-dac}
 
@@
 scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
-our simple scheme built from $\CUASGen^{usr-iss}$ does not ensure privacy of the
-delegation chain -- which could be achieved by making \feval output projective
-proofs like in \cite{bcc+09}, but since our goal is to showcase the feasibility
-of building DAC from \UAS, we leave that out for brevity. Our simple scheme
+our simple scheme built from \CUASGenInt does not ensure privacy of the
+delegation chain, which means that only actions by users with the same
+delegation chain are indistinguishable -- this can make sense, for instance,
+for organisations composed by many members. Delegation chain privacy could be
+achieved by making \feval output projective proofs like in \cite{bcc+09}, but we
+leave that out of scope for brevity. Our simple scheme
 does, however, ensure that a (not top-level) issuer can only delegate attributes
@@
 %
-The functionality is thus defined almost as in \secref{ssec:related-models-ac},
-i.e., we have $Setup$, $IssKeyGen$ algorithms, and $\langle Obtain,Issue\rangle$
+The syntax is thus defined almost as in \secref{ssec:related-models-ac},
+i.e., we have a $Setup$ algorithm, and $\langle Obtain,Issue\rangle$
 and $\langle Show,Verify \rangle$ interactive protocols; but we do not have
-$UserKeyGen$, as this collapses with $IssKeyGen$.
+$IssKeyGen$, as now, as in \cite{bcc+09} (and our \UAS model), issuers collapse
+with users -- instead, we have an $KG$ and $ISet$ algorithms, with the same
+meaning as in \UAS.
 %
@@
 to the oracles in \secref{ssec:related-models-ac}, we use $HI$ and $CI$ oracles,
-equivalent to \IGEN and \ICORR in our \UAS model, which allow adding honest
-issuers, and corrupt existing ones, respectively. The issuance and sign
-anonymity properties are direct, constraining the adversary to output challenge
-credentials and signatures with the same delegation chain. For unforgeability,
-we still require that no adversary can authenticate using a set of attributes
-that have not been issued to a corrupt user. In addition, we require that for
-any successful authentication using a level-$l$ credential, we
-can extract a chain of credentials of length $l$ such that each level-$i$
-credential can be used successfully to authenticate a level-$(i+1)$ credential
-down to the level-$l$ credential, and the attributes revealed in the
-level-$l$ authentication are contained in all the credentials up the chain.
+for creating honest and corrupt issuers, which can be simulated via \HUGEN,
+\CUGEN, \ISET and \ICORR in our \UAS model.
+%
+The issuance and sign anonymity properties are direct, constraining the
+adversary to output challenge credentials and signatures with the same
+delegation chain. For unforgeability, we still require that no adversary can
+authenticate using a set of attributes that have not been issued to a corrupt
+user. In addition, we require that for any successful authentication using a
+level-$l$ credential, we can extract a chain of credentials of length $l$ such
+that each level-$i$ credential can be used successfully to authenticate the
+level-$(i+1)$ credential, all the way down to the level-$l$ credential, and the
+attributes revealed in the level-$l$ authentication are contained in all the
+credentials up the chain. For this extraction, we assume in the model the
+existence of a helper function $(\ipk_0,\lbrace (\ipk_i,\cred_i)
+\rbrace_{i\in[1,l]}) \gets ExtractChain(\utrans)$ that outputs a sequence of
+public keys and credentials from the root issuer $\ipk_0$ to the actual
+credential used to sign $(\ipk_l,\cred_l)$.
 
@@
         \parm \gets \Setup(1^\secpar) \\
-        b^* \gets \adv^{\mathcal{O}_{iss-anon}}(\parm) \\
+        b^* \gets \adv^{\mathcal{O}_{dac},\oracle{IssLoR}}(\parm) \\
         \pccomment{Abort if challenge creds belong to} \\
@@
         \parm \gets \Setup(1^\secpar) \\
-        b^* \gets \adv^{\mathcal{O}_{sig-anon}}(\parm) \\
+        b^* \gets \adv^{\mathcal{O}_{dac,\oracle{SigLoR}}}(\parm) \\
         \pccomment{Abort if challenge sigs belong to} \\
@@
       \procedure[linenumbering]{$\Exp^{forge}_{\adv,dac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
+        \parm \gets \SimSetup(1^\secpar) \\
         (D=(l,D'),\ipk_l,\st) \gets
-        \adv^{\mathcal{O}_{forge}}(\parm) \\
+        \adv^{\mathcal{O}_{dac}}(\parm) \\
         \langle\cdot,(b,\utrans)\rangle \gets
@@
         \iid = \ISR[\ipk_{i-1}] \notin \CI~\land \\
-        \pcind D' \not\subseteq \ATTR[\iid]) \land
-        D' \subseteq \ATTR[\ISR[\ipk_i]]: \\
+        \pcind D' \not\subseteq \ATTR[\iid]: \\
         \pcind \pcreturn 1 \\
@@
   \caption{Security games for delegatable anonymous credentials with selective
-    disclosure based on \cite{fhs19}. $\mathcal{O}_{iss-anon} \gets \lbrace HI,
-    CI,Obtain,Issue,ObtIss,Show,IssLoR\rbrace$, $\mathcal{O}_{sig-anon} \gets
-    \lbrace HI,CI,Obtain,Issue,ObtIss,Show,SigLoR\rbrace$. $\mathcal{O}_{forge}
-    \gets \lbrace HI,CI,Obtain,ObtIss,Issue,Show\rbrace$. $IssLor$ corresponds
-    to \OBTCHALb in \UAS, whereas $SigLor$ corresponds to \CHALb. Also, \OWNR
+    disclosure based on \cite{fhs19}. $\mathcal{O}_{dac} \gets \lbrace
+    \oracle{HI},\oracle{CI},\oracle{Obtain},\oracle{Issue},\oracle{ObtIss},
+    \oracle{Show}\rbrace$. $\oracle{IssLor}$ corresponds to \OBTCHALb in \UAS,
+    whereas $\oracle{SigLor}$ corresponds to \CHALb. Also, \OWNR
     and \ATTR tables are essentially as in \secref{ssec:model-uas}.
@@
 We next give a construction of a delegatable AC (DAC) scheme, in the shape of
-a $(\fissue^{l,\dattrs},\feval^{l,\dattrs},\finsp^0)$-$\CUASGen^{usr-iss}$
+a $(\fissue^{l,D},\feval^{l,\dattrs},\finsp^0)$-\CUASGenInt
 restriction, where the $\finsp^0$ function is as defined in
@@
 \begin{align}
-  & \fissue^{l,\dattrs}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
-    \pcreturn (\attrs_1 = l+1 \land \attrs \subseteq
-    \cup_{i\in\dattrs} \cattrs_i) \nonumber
+  & \fissue^{l,D}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
+    \pcreturn \attrs_1 = l+1 \land \cattrs \subseteq D \nonumber \\
   & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
     \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
-    \label{eq:funcs-rac}
+    \label{eq:funcs-dac}
 \end{align}
 
-. In a DAC scheme, all users are (or may be) also issuers. We only
+In a DAC scheme, all users are (or may be) also issuers. We only
 distinguish between top-level issuers, who have level $l=0$, and lower-level
 issuers, who have level $l>0$. In our \CUASDAC scheme, we assume that the first
-attribute (after the user's secret key) encodes the level of the credential.
-That is, $\attrs_1=l$, for a credential of level $l$. In addition, all users
-(i.e., with $l>0$) who want to delegate have to publicly list:
+attribute (after the user's secret key and credential identifiers) encodes the
+level of the credential. That is, $\attrs_1=l$, for a credential of level $l$.
+In addition, all users (i.e., with $l>0$) who want to delegate have to publicly
+list:
 
@@
 \item An \UAS signature proving knowledge of a credential of level $l$, and over
-  the attributes that this level-$l$ issuer is delegating.
+  the attributes $D$ that this level-$l$ issuer is delegating.
 \item The \ipk of the parent issuer.
-\item The $\fissue^{l,\dattrs}$ function they will require for delegating.
-\item An $\feval^{l,\dattrs}$ function used to produce the signature at item 3.
+\item The $\fissue^{l,D}$ function they will require for delegating.
+\item An $\feval^{l,D}$ function used to produce the signature at item 3.
 \end{enumerate}
@@
 We assume that, from an \ipk, it is possible to find the corresponding issuer
-(e.g., using the previously mentioned public list). The mentioned
-$\fissue^{l,\dattrs}$ functions must follow the pattern in \figref{fig:func-restrictions}.
+(e.g., using the previously mentioned public list). The
+$\fissue^{l,D}$ functions must follow the pattern in \figref{fig:func-restrictions}.
 Namely, the issuance function checks that the first requested attribute equals
-$l+1$, and that all requested attributes are a subset of the attribute set
-\dattrs being delegated by the level-$l$ issuer. In addition, signature
-evaluation functions $\feval^{l,\dattrs}$, also shown in \figref{fig:func-restrictions},
+$l+1$, and that the remaining attributes are a subset of the attribute set
+D being delegated by the level-$l$ issuer. In addition, signature
+evaluation functions $\feval^{l,D}$, also shown in \figref{fig:func-restrictions},
 must reveal the level of the credential used to produce the \UAS signature at
-item 2, as well as the set of attributes \dattrs that the level-$l$ issuer
+item 3, as well as the set of attributes \dattrs that the level-$l$ issuer
 delegates. Verifiers can then trivially check if the set of revealed attributes
@@
 \footnote{Additional checks may be added in both functions, but this is
-  the bare minimum.}.
+  the bare minimum.} -- this $\feval^{l,D}$ function is just the same as the
+$\feval^{l,\dattrs}$ function in \esref{eq:funcs-dac}, but where $D=\dattrs$,
+which is required to verify the \UAS signature produced at step 3.
 %
-From this high-level description, we define the algorithms of \CUASDAC:
+From this high-level description, we define the concrete algorithms of \CUASDAC:
 
@@
   that $\finsp^0$ can be replaced by any desired opening function.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] If $l=0$, simply run \IKeyGen as
-  in $\CUASGen^{usr-iss}$. If $l>0$, this level-$l$ issuer picks a random
-  message $r$ and computes $\Sig = (\sig,\yeval) \gets \Sign(\usk,\opk,\cred,r,
-  \feval^{l,\dattrs})$, for the \dattrs set it wants to reveal -- which must
-  include the attributes to delegate, and the credential level. It then
-  publishes $(l,\ipk,\Sig,\ipk^{l-1},\fissue^{l,\dattrs},\feval^{l,\dattrs})$,
-  where $\ipk^{l-1}$ is the public key of the parent issuer,
-  $\fissue^{l,\dattrs}$ is an issuance function as described in
-  \figref{fig:func-restrictions}, and $\feval^{l,\dattrs}$ is also as in
-  \figref{fig:func-restrictions}, revealing the attributes that the issuer is
-  willing to delegate.
-% \item[$(\upk,\usk) \gets UserKeyGen(\opk)$.] All users in this scheme are
-%   also issuers. Thus, a new user runs first \IKeyGen as in \CUASGen. Then, sets
-%   $\usk \gets \isk$ and stores \ipk, which may be needed to delegate obtained
-%   credentials. Note that this does not affect security, as long as
-%   $\isk \getr \AttrSpace$.
+\item[$(\upk,\usk) \gets KG(\parm)$.] As in \CUASGenInt.
+\item[$\ipk \gets ISet(\upk,\usk,\fissue^{l,D})$.] If $l = 0$, then just
+  run $\ipk \gets \ISet(\upk,\usk,\fissue^{l,D})$, and publish $(0,\ipk,\bot,
+  \bot,\fissue,\bot)$, for any \fissue function required by the level-$0$
+  issuer. Else,  
+  if $l > 0$ (the entity running the algorithm owns a level-$l$ credential
+  issued by a level-$(l-1)$ issuer, containing attributes $D$) run $\ipk' \gets
+  \ISet(\upk,\usk,\fissue^{l,D})$ as in \CUASGenInt. Then, obtain $\Sig \gets
+  \CUASGenInt.\Sign(\usk,\opk,\Cred,\msg,\feval^{l,D})$, where \opk is the
+  opener public key in \parm, \msg is some random message, and \Cred is the
+  level-$l$ credential owned by the current issuer. Then, set
+  $\ipk \gets (l,\ipk',\Sig,\ipk^{l-1},\fissue^{l,D},\feval^{l,D})$, where
+  $\ipk^{l-1}$ is the public key of the level-$(l-1)$ issuer.
 \item[$\langle \cred/\bot,\top/\bot \rangle \gets
   \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  If $l>0$, the user first finds the corresponding $(l,\ipk,\Sig,\ipk^{n-1},
-  \fissue^{l,\dattrs},\feval^{l,\dattrs})$ tuple, and checks \Sig running
-  \Verify as in $\CUASGen^{usr-iss}$ (with the retrieved $\feval^{l,\dattrs}$).
-  Then, user and level-$l$ issuer run $\langle\Obtain,\Issue\rangle$ as in
-  $\CUASGen^{usr-iss}$, using $\fissue^{l,\dattrs}$ as issuance function. If
-  $l=0$, then both run $\langle\Obtain,\Issue\rangle$ as in
-  $\CUASGen^{usr-iss}$, using the \fissue function required by the issuer.
+  The user first finds the corresponding $(l,\ipk,\Sig,\ipk^{n-1},\fissue^{l,D},
+  \feval^{l,D})$ tuple. If $l>0$, the user checks \Sig running \Verify as in
+  \CUASGenInt (with the retrieved $\feval^{l,D}$) and then, user and level-$l$
+  issuer run $\langle\Obtain,\Issue\rangle$ as in \CUASGenInt, using
+  $\fissue^{l,D}$ as issuance function. If $l=0$, then user and issuer
+  run $\langle\Obtain,\Issue\rangle$ as in \CUASGenInt, using the \fissue
+  function specified in the issuer's tuple.
 \item[$\langle 1/0,(1,\utrans)/(0,\utrans)\rangle
   \gets \langle Show(\opk,\attrs,\dattrs,\cred),
-  \Verify(\opk,\dattrs) \rangle$.] As in the interactive variant of
-  $\CUASGen^{usr-iss}$.  
+  \Verify(\opk,\dattrs) \rangle$.] As in \CUASGenInt.
 \end{description}
@@
 We prove that \CUASDAC is an anonymous and unforgeable DAC scheme, according to
-the model in \figref{fig:model-dac}, if the underlying \CUASGen construction has
-anonymous issuance and signing, and has unforgeable issuance and signing.
+the (interactive version of the) model in \figref{fig:model-dac}, if the
+underlying \CUASGenInt construction has anonymous issuance and signing, and is
+unforgeable.
 
 \begin{theorem}[Issuance anonymity of \CUASDAC]
-  If the base \CUASGen construction has issuance anonymity according to
-  \defref{def:issue-anonymity-uas}, then \CUASDAC also has issuance anonymity.
+  If the base \CUASGenInt construction has issuance anonymity according to
+  (the interactive version of) \defref{def:issue-anonymity-uas}, then \CUASDAC
+  also has issuance anonymity.
 \end{theorem}
@@
 \begin{proof}
-  Given \adv~ against issuance anonymity of \CUASDAC as defined in
+  Given \adv~against issuance anonymity of \CUASDAC as defined in
   $\Exp^{iss-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
-  issuance anonymity of \CUASGen as defined in \defref{def:issue-anonymity-uas}.
+  issuance anonymity of \CUASGenInt.
 
   To simulate oracle calls by \adv, \advB simply redirects to its corresponding
-  oracle, i.e.: for calls to $HU,CU,HI,CI,Obtain,Show,IssLoR$, \advB redirects
-  to \HUGEN,\CUGEN,\IGEN,\ICORR,\OBTAIN,\SIGN,\OBTCHALb, respectively. Note that
-  ``translating'' the inputs from the former into inputs for the latter is
-  trivial. Obviously, if \adv~ wins in its issuance anonymity game, then so does
-  \advB with the  same probability.
+  oracle, i.e.: for calls to \oracle{HU},\oracle{CU},\oracle{Obtain},
+  \oracle{Show},\oracle{IssLoR}, \advB redirects to the \CUASGenInt oracles
+  \HUGEN,\CUGEN,\OBTAIN,\SIGN,\OBTCHALb, respectively. \oracle{HI} (resp.
+  \oracle{CI}) is simulated by calling \HUGEN (resp. \CUGEN) and \ISET
+  sequentially and for the same \uid, plus a call to \SIGN in the case of
+  honest issuers of level $l>0$, to generate the signature \Sig that the
+  (honest) issuer has to publish.
+  %
+  If \adv~wins in its issuance anonymity game, then so does \advB with the same
+  probability, as the simulation is perfect.
   % 
@@
 \begin{theorem}[Signature anonymity of \CUASDAC]
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASDAC also has signature anonymity.
+  If the base \CUASGenInt construction has signature anonymity according to
+  (the interactive version of) \defref{def:sign-anonymity-uas}, then \CUASDAC
+  also has signature anonymity.
 \end{theorem}
@@
 \begin{proof}
-  This is the same as in \thmref{thm:anon-cuasac}.
+  Given \adv~ against signature anonymity of \CUASDAC as defined in
+  $\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
+  signature anonymity of \CUASGenInt.
+  %
+  \adv's oracles are simulated as in the proof for issuance anonymity of
+  \CUASDAC -- in this case, \adv's \oracle{SigLoR} oracle corresonds to \advB's
+  \CHALb. Again, the simulation is perfect, and whenever \adv~wins its
+  $\Exp^{sig-anon-b}$ game, so does \advB.
   % 
@@
 \begin{theorem}[Unforgeability of \CUASAC]
-  If the base \CUASGen construction has issuance and signature unforgeability
-  according to \defref{def:issue-forge-uas} and \defref{def:sign-forge-uas}, and
-  non-frameability according to \defref{def:frame-uas}, then \CUASAC is an
+  If the base \CUASGenInt construction is unforgeable according to (the
+  interactive version of) \defref{def:forge-uas}, and non-frameabile according
+  to (the interactive version of) \defref{def:frame-uas}, then \CUASAC is an
   unforgeable AC scheme.
@@
   Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows for the approach
-    to transform non-interactive signature and verification in \UAS to interactive
-    presentations, as described in \secref{ssec:variants-gsac}.}, where $r$ is a
-  fresh random number produced by the environment (acting as honest verifier),
+    to transform non-interactive signature and verification in \UAS to
+    interactive presentations, as described in \secref{ssec:variants}.}, where
+  $r$ is a fresh random number specified by the adversary,
   and \Sig is a \CUASGen signature over $r$. Thus, $ExtractChain$ leverages
@@
   issued by $\ipk_0$.
-
-  For the proof, we first replace within $Setup$ the $\NIZKSetup$ algorithms for
-  issuance and signing with their corresponding $\NIZKSetup$. Due to their
-  zero-knowledge property, the resulting game is indistinguishable. Also, note
-  that $ExtractChain$ succeeds to extract the corresponding credential chain,
-  due to simulation extractability of the NIZKs.
 
@@
     it is a valid signature by the issuer at position $i-1$, who did not produce
-    it. This can be used to break signature non-frameability of \CUASGen.
+    it. This can be used to break signature non-frameability of \CUASGenInt.
   \item The credential of the issuer at position $i$ is not a forgery, meaning
-    that it is a valid signature by the issuer at position $i-1$, who produced
-    it. But this contradicts the conditions required by $\fissue^{n,\dattrs}$,
-    and therefore breaks issuance unforgeability of \CUASGen.
+    that it is a valid signature by the issuer at position $i-1$, who did
+    produce it. But this contradicts the conditions required by $\fissue^{n,D}$,
+    and therefore breaks unforgeability of \CUASGenInt.
   \end{itemize}

### 2022-09-13 prism-backend/research/gsac/formal-uas.tex
Updated correctness.
Updated GS-MDO and DAC appendices.

@@
   \centering  
-  \scalebox{0.9}{
+  \scalebox{0.85}{
     \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
@@
     \centering
-    \scalebox{0.9}{
+    \scalebox{0.85}{
 
@@
     }
-    \scalebox{0.9}{
+    \scalebox{0.85}{
 
@@
   \centering
-  \scalebox{0.9}{
+  \scalebox{0.85}{
     \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
@@
       \gets \adv^{\HUGEN,\OGEN,\ISET,\OBTISS,\RREG}(\parm) \\
-      \pcif \feval \notin \famfeval: \pcreturn 0 \\
-      \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
+      \pcif \feval \notin \famfeval \lor \OWNR[\scid] \neq \uid: \pcreturn 0 \\
       (\Sig = (\sig,\yeval)) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,
@@
       (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
+      \textrm{Parse}~\PUBOK[\oid]~\textrm{as}~((\cdot,\finsp),\cdot) \\
       \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
       = 0~\lor \\
-      \pcind \yinsp \neq \finsp^\oid((\yeval,\yeval^1),
+      \pcind \yinsp \neq \finsp((\yeval,\yeval^1),
       \PUBUK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
@@
 %   \centering
-%   \scalebox{0.9}{
+%   \scalebox{0.85}{
 %     \begin{minipage}[t]{0.6\textwidth}
@@
   \centering
-  \scalebox{0.9}{
+  \scalebox{0.85}{
     \begin{minipage}[t]{0.5\textwidth}
@@
   \centering
-  \scalebox{0.9}{
+  \scalebox{0.85}{
     \begin{minipage}[t]{\textwidth}
@@
       \procedure[linenumbering]{$\ExpForge(1^\secpar)$}{%
-        (\parm,\trap) \gets \Setup(1^\secpar) \\
+        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
         (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
@@
   \centering
-  \scalebox{0.9}{
+  \scalebox{0.85}{
     \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
@@
   \centering
-  \scalebox{0.9}{
+  \scalebox{0.85}{
     \input{figures/nizk.tex}
@@
 \begin{figure}[ht!]
-  \scalebox{0.9}{
+  \scalebox{0.85}{
     \input{figures/nizk-ring.tex}
@@
 Modelling-wise, this requires to replace the \Sign and \Verify functions with
-a single $\langle 1/0,(\yeval,\utrans_{\Sig})/\bot \rangle \gets \langle
-\Sign(\usk,\opk,\sCred,\msg,\feval), \Verify(\opk,\sipk,\msg,\feval) \rangle$,
+an interactive protocol $\langle 1/0,(\yeval,\utrans_{\Sig})/\bot \rangle \gets
+\langle\Sign(\usk,\opk,\sCred,\msg,\feval), \Verify(\opk,\sipk,\msg,\feval)
+\rangle$,
 where $\utrans_{\Sig}$ is the transcript of the protocol, and is logged now in

### 2022-09-13 prism-backend/research/gsac/introduction-paper.tex
Updated GS-MDO and DAC appendices.

@@
 
-A crucial aspect to cater for all possible variants that we aim to subsume, is
-the incorporation of ``functional placeholders'' enabling customisation. We
-introduce abstract functions whose computation needs to be proven correct by the
-user. Depending on the choice of these functions, one can instantiate a
-different related scheme, which is anyway secure according to our \UAS model.
-We also allow to modulate the information to be revealed after signing time,
-with the information revealed at signing time, allowing policies such as
-``deanonymize only if 18+ years old''.
+% A crucial aspect to cater for all possible variants that we aim to subsume, is
+% the incorporation of ``functional placeholders'' enabling customisation. We
+% introduce abstract functions whose computation needs to be proven correct by the
+% user. Depending on the choice of these functions, one can instantiate a
+% different related scheme, which is anyway secure according to our \UAS model.
+% We also allow to modulate the information to be revealed after signing time,
+% with the information revealed at signing time, allowing policies such as
+% ``deanonymize only if 18+ years old''.
 

### 2022-09-16 prism-backend/research/gsac/formal-uas.tex
In depth pass up to sec 3.1.

@@
 \paragraph{Users and credentials.} %
-We model a scheme in which every single user may have multiple credentials.
-Moreover, previously obtained credentials can be leveraged simultaneously to
-obtain a new one. In this setting, a perhaps too strict assumption we make is
-that, once a user gets compromised, all of the credentials owned by that user
-are compromised too. While there may be real world situations for which this is
-too aggressive, it is certainly a worst-case scenario, and greatly simplifies
-the modelling.
-%
-Somehow related, we model a scheme in which users generate their secret keys in
-a standalone way, and then leverage these keys to request credentials. This may
-seem too ideal as a model for real world situations, as we cannot know how
-many keys a user has generated. However, we argue that this can in fact be very
-close to reality, where a well-known issuer, after properly identifying a user,
-attests the (possibly blinded) public key this user proves control of. Indeed,
-our model and syntax support exactly this approach, by allowing users to
-leverage previously obtained credentials in order to request new ones.
-A consequence of this is that, if ``one user'' generates (e.g.) two keys, and
-then uses each of these keys to request multiple credentials, then from the
-point of view of our modelling, we see this \emph{cryptographically} as two
-different users -- and, anyway, that same ``user'' cannot combine credentials
-bound to different keys.
+In our model, every single user may have multiple credentials. In this
+setting, a perhaps too strict assumption we make is that, once a user gets
+compromised, all of the credentials owned by that user are compromised too.
+While there may be real world situations for which this is too aggressive, it is
+certainly a worst-case scenario, and greatly simplifies the modelling.
+%
+% Somehow related, we model a scheme in which users generate their secret keys in
+% a standalone way, and then leverage these keys to request credentials. This may
+% seem too ideal as a model for real world situations, as we cannot know how
+% many keys a user has generated. However, we argue that this can in fact be very
+% close to reality, where a well-known issuer, after properly identifying a user,
+% attests the (possibly blinded) public key this user proves control of. Indeed,
+% our model and syntax support exactly this approach, by allowing users to
+% leverage previously obtained credentials in order to request new ones.
+% A consequence of this is that, if ``one user'' generates (e.g.) two keys, and
+% then uses each of these keys to request multiple credentials, then from the
+% point of view of our modelling, we see this \emph{cryptographically} as two
+% different users -- and, anyway, that same ``user'' cannot combine credentials
+% bound to different keys.
 
 \paragraph{Users and issuers.} %
-Finally, a relevant aspect of our approach is that users and issuers are
-essentially the same thing: just an entity with a key pair. The difference is
-that, when users wish to become issuers, they have to advertise their public
-keys, along with their conditions for granting credentials. For simplicity, we
-just assume that they somehow ``publish their public keys''. In practice, this
-may be done in several ways, depending on the situation: self-signing, relying
-on external PKIs, bulletin boards, etc.
-%
-This approach has actually been used before to model delegatable anonymous
-credentials \cite{bcc+09}, and it turns out to be also very useful for our
-approach to build ring signatures from \UAS.
+A relevant aspect of our model is that users and issuers are basically the
+same: an entity with a key pair. The difference is that, when users wish to
+become issuers, they advertise their public keys, along with their conditions
+for granting credentials. To simplify, we just assume that they somehow
+``publish their public keys'', which can be done in several ways in practice.
+
+\paragraph{Functional placeholders.} %
+We use generic functions to capture, at the design level, that users need
+to prove concrete claims over their private information. Looking a bit ahead,
+the output of these functions is defined in terms of (subsets of) the users'
+key, credentials and attributes, and signed message. But, during our modelling,
+we are only concerned with preventing that the output of these functions can
+be dishonestly altered, and with ensuring that it does not threaten privacy
+beyond what is necessary or unavoidable to reach the flexibility we want.
 
@@
 \item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
-  Upon receiving a user secret key \usk, opener public key \opk, a set of
-  credentials \sCred, a message \msg and evaluation function \feval, returns
+  Upon receiving user secret key \usk, opener public key \opk, 
+  credentials \sCred, message \msg and evaluation function \feval, returns
   signature \sig, and a value \yeval. We use use \Sig to denote the
@@
   (\yinsp,\iproof)/\bot$.]
-  Executed by the opener with private key \osk. Receives a signature $\Sig=
+  Run by the opener with private key \osk. Receives a signature $\Sig=
   (\sig,\yeval)$ over message \msg and evaluation function \feval,
@@
 
-      \begin{minipage}[t]{0.55\textwidth}
-
-        \procedure{$\OBTISS(\cid=(\cidi,\cidu),\uid,\iid,\attrs,$\\
-          \hspace*{4.25em}$\lbrace (\cid_i,\iid_i) \rbrace_{i \in [n]})$}{%
+      \begin{minipage}[t]{0.58\textwidth}
+
+        \procedure{$\OBTISS(\stackrel{\cid}{\pcbox{(\cidi,\cidu)}},\uid,\iid,\attrs,
+          \lbrace (\cid_i,\iid_i) \rbrace_{i \in [n]})$}{%
           \pcif \uid \notin \HU \lor \iid \notin \HI: \pcreturn \bot \\
@@
 
-        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
-          \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
+        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,
+          \stackrel{\cscid_{0,1}}{\pcbox{\lbrace(\ccid_{0,i},\ccid_{1,i})
+            \rbrace_{i\in[n]}}})$}{%
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
@@
           \pcif 0(\fissue(\PUBUK[\cuid_0],(\cdot,\cidu),\attrs,\lbrace (\ccid_{0,i},\ATTR[\ccid_{0,i}])\rbrace_{i\in[n]})) \neq \\
-          \pcind 0(\fissue(\PUBUK[\cuid_1],(\cdot,\cidu),\attrs,\lbrace (\ccid_{1,i},\ATTR[\ccid_{1,i}])\rbrace_{i\in[n]})):
-          \pcreturn \bot \\
+          \pcind 0(\fissue(\PUBUK[\cuid_1],(\cdot,\cidu),\attrs,\lbrace (\ccid_{1,i},\ATTR[\ccid_{1,i}])\rbrace_{i\in[n]})): \\
+          \pcind \pcreturn \bot \\
           \langle \Cred, \cdot \rangle \gets
@@
 
-        \procedure{$\CHALb(\oid,\cscid_{0,1}=
+        \procedure{$\CHALb(\oid,\stackrel{\cscid_{0,1}}{\pcbox{
             \lbrace (\ccid_{0,i},\ccid_{1,i})
-          \rbrace_{i\in[n]},\msg,\feval)$}{%
+            \rbrace_{i\in[n]}}},\msg,\feval)$}{%
           \pcfor d\in\bin: \cuid_d \gets \OWNR[\cscid_d] \\
@@
   \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a signature
-  \Sig, the opener identifier \oid, and the identifiers of all
+  \Sig, the opener public key \opk, and the public keys $\ipk_i$
   issuers of the credentials used to produce the signature over \msg, and for
@@
   }
-  \caption{CS specification of the NP relations used in \CUASGen.}
+  \caption{CS specification of the NP relations used in \CUASGen.
+    % $\boxed{x}$ means the issuer learns $x$, \dboxed{$y$} means the verifier
+    % learns $y$, and \dotboxed{z} means the opener reveals $z$.
+  }
   \label{fig:nizkrels}

### 2022-09-16 prism-backend/research/gsac/introduction-paper.tex
In depth pass up to sec 3.1.

@@
 \paragraph{Anonymous authentication and signatures.} %
-Privacy-preserving digital signature and authentication systems have been a
-prolific field in the last few decades. Anonymous credentials (AC)
-\cite{chau85} and group signatures (GS) \cite{ch91} are among the most relevant
-schemes. For both, the high-level idea is common: after obtaining a credential,
-users can authenticate anonymously and indistinguishably from other users with
-similar credentials. 
+Privacy-preserving signature and authentication systems have been a prolific
+field in the last decades. Anonymous credentials (AC) \cite{chau85} and group
+signatures (GS) \cite{ch91} are among the most relevant schemes. In both, the
+high-level idea is common: users obtain credentials, which can then use to
+authenticate anonymously and indistinguishably from other users with similar
+credentials. 
 %
 %% Usefulness of main precedents / motivation
-Their usefulness stems from the combination, within a single primitive, of
-seemingly contradictory concepts: anonymity, authentication, and utility; where
-utility can appear in the shape of information revealed at signature/authentication
-time, or after (in the latter case, typically called accountability).
+Their usefulness stems from the combination of seemingly contradictory concepts:
+anonymity, authentication, and utility; where utility can appear in the shape of
+information revealed at signature/authentication time, or after (in the latter
+case, typically called accountability).
 
-\paragraph{Utility at authentication time and after authentication time.} %
-AC schemes focus on utility at authentication time. For instance, encoding
-multiple attributes within a credential and allowing to selectively disclose a
-subset of them. The real world applications of such systems are direct, e.g.,
-to prove ``Over 18''-type of claims. Indeed, the scientific research behind
-anonymous credentials is making its own way to become a foundational block of
-the technology some call ``anoncreds''%
+\paragraph{Utility at, and after, authentication time.} %
+AC schemes target utility at authentication time. For instance, allowing
+users to selectively disclose subsets of the attributes in their credentials.
+Their real world applications are direct, e.g., to prove ``Over 18''-type of
+claims. Indeed, the scientific research behind anonymous credentials is becoming
+a foundational block of the technology some call ``anoncreds''%
 \footnote{\url{https://hyperledger-indy.readthedocs.io/projects/sdk/en/latest/docs/design/002-anoncreds/README.html}. Last access, June 18th, 2022.},
@@
 
-GS schemes enhance utility after authentication, by allowing partial
+GS schemes enhance utility after authentication, allowing partial
 re-identification like linking of signatures, or even full deanonymization.
@@
 \paragraph{Evolution of AC and GS.} %
-As the previous shows, AC and GS systems have followed separate paths, although
-there are some exceptions. Functionality-wise, Attribute-Based Group Signatures
-introduce attributes into the credentials issued to group members, who can later
-use them to prove pre-fixed claims \cite{emo09,aa14}. Hidden identity-based
-signatures also add attributes into the credentials, with the aim of preventing
-the opener (the trusted party who can deanonymize signers) from having to rely
-on the issuer in order to return meaningful identifying information when opening
-a signature \cite{ks07}. Some AC schemes have also tried to incorporate some
-sort of utility after authentication, like AC schemes with revocation
-\cite{cks10}, or with ``watchlists'' \needcite.
+AC and GS systems have followed separate paths, with some exceptions.
+Functionality-wise, Attribute-Based Group Signatures add attributes to the
+credentials issued to group members, who can later use them to prove pre-fixed
+claims \cite{emo09,aa14}. Hidden identity-based signatures also add attributes
+to the credentials, with the aim of preventing the opener (the trusted party who
+can deanonymize signers) from having to rely on the issuer in order to return
+meaningful identifying information when opening a signature \cite{ks07}. Some AC
+schemes also incorporate some sort of utility after authentication, like
+AC schemes with revocation \cite{cks10}, or with ``watchlists'' \needcite.
 
@@
 probably most fruitful way to instantiate AC is with CL-type signatures
-\cite{cl02}. But the fact that they support efficient
-zero-knowledge protocols for proving knowledge of a signature, makes them very
-suitable to build GS schemes -- even without exploiting the possibility to
-encode many attributes. Indeed, BBS+ signatures \cite{bbs04,cdl16b} have been
-used to design and instantiate GS schemes \cite{gl19,dl21}, as is the case for
-PS16 signatures \cite{ps16,cdl+20} -- both, CL-type signatures.
+\cite{cl02}. But the fact that CL signatures support efficient ZK protocols for
+proving knowledge of a signature makes them also very suitable to build GS
+schemes. Indeed, BBS+ signatures \cite{bbs04,cdl16b} have been used to design
+and instantiate GS schemes \cite{gl19,dl21}, as is the case for PS16 signatures
+\cite{ps16,cdl+20} -- both, CL-type signatures.
 
-Also, both AC and GS branches have experienced remarkable efforts towards
-generalisation. In the AC domain, malleable signatures are used as core building
-block in \cite{cklm14}, to allow building both conventional AC and Delegatable
-AC systems, depending on the transformation supported by the malleable
-signatures. In GS, very recently, BiAS \cite{lnpy21} and MPS \cite{ngsy22}
-flexibilize the trade-off between anonymity and accountability.
+AC and GS have experienced remarkable efforts towards generalisation. In
+the AC domain, malleable signatures are used as core building block in
+\cite{cklm14}, to allow building both conventional AC and Delegatable AC
+systems, depending on the transformation supported by the malleable signatures.
+Also, \cite{ckl+15} gives a very generic approach to build AC schemes. In GS,
+very recently, BiAS \cite{lnpy21} and MPS \cite{ngsy22} flexibilize the
+trade-off between anonymity and accountability.
 
@@
 However, even the generalisation efforts that have independently taken place in
-GS and AC, are quickly seen to have limited applicability in the real world. On
-the GS side, even though MPS achieves a powerful balance on when a signature is
+GS and AC have limited applicability in the real world. On the GS side, even
+though MPS achieves a powerful balance on when a signature is
 deanonymizable and what information can be extracted from it, upon closer look,
 this information is somehow meaningless. Namely, the notion of identity is not
-well defined and, thus, it is not possible to claim whether the value output by
+well defined and, thus, it is not possible to assess whether the value output by
 their generalised open function makes sense or even if it is legitimate. Also,
-just being able to prove membership at signing time is typically not enough, and
-one needs to prove more general claims. That is precisely what AC schemes do,
-while also providing a well defined notion of identity via credential
-attributes. Precisely, it is this defined concept of identity what enables AC
-schemes to state when some information revealed at authentication time is a
-forgery or not. On the other hand, the notion of accountability  is barely
-present in AC schemes. For instance, non-frameability is not even considered
--- and it is non-frameability what ensures when cannot a user be held
-accountable.
+just being able to prove membership at signing time is typically not enough. In
+other words, in GS, utility at authentication time is very limited -- but this
+is precisely the main strength in AC schemes, which also have a well defined
+notion of identity via attributes. On the other hand, the notion of
+accountability  is barely present in AC schemes. For instance, non-frameability
+is not even considered, and it is non-frameability what prevent honest users
+from being held accountable of dishonest actions they did not take part in.
 %
@@
 models exist in both fields. Although similar, each model focuses on slightly
-different utility variants, making them hardly comparable. And, of course, AC
-focus on utility at authentication (signing) time, while GS focus on
-utility after signing (authentication) time. To the best of our knowledge, no
-model exists that combines both, in a general enough manner. Probably, the
-most ambitious work in this regard is \cite{ckl+15}, although it focuses only on
-anonymous credentials. In practice, needing to resort to too specific models
-forces system designers to decide which feature (utility at or after signing
-time, etc) they do not want to lose -- or, which one they will lose.
+different utility variants, making them hardly comparable. To the best of our
+knowledge, no model exists that combines both fields, in a general enough
+manner. In practice, needing to resort to too specific models forces system
+designers to decide which feature they do not want to lose -- or, which one they
+will lose.
 
@@
 \paragraph{General model for anonymous signatures.} %
-Acknowledging that the strengths of AC are the weaknesses of GS, and vice versa,
-and the inconvenience in practice of having a miriad of similar-but-different
-models, we come up with a unified one. In a nutshell, we give a syntax and model
-for anonymous signatures -- which can be turned into an interactive
-authentication system -- with attribute-enabled credentials, and generalised
-utility both at signature time, and after. Concretely, we propose a scheme
-through which it is possible to model revealing arbitrary claims at signing time
-(as in AC), enable conditional release of utility information after signing time
-(as in MPS) and, more importantly, come up with the combination of the previous
-that is more suitable for each scenario. We also generalise the credential
-issuance process, subsuming an even larger set of previously known schemes.
-Given its generalisation power, we refer to schemes meeting this model as
-Universal Anonymous Signatures.
+We give a syntax and model for anonymous signatures with attribute-enabled
+credentials and, inspired by GS and AC works, generalised utility.
 
-\paragraph{Generic construction, and connections with previous schemes.} %
-We give a main generic construction based on well-known building blocks, and
-prove its security. To prove its universality, we show how restrictions of our
-generic construction directly imply ancestors of UAS: group
-signatures and anonymous credentials. This includes not only their vanilla
-versions, but also relevant variants, such as MPS \cite{ngsy22}, (a modified
-version of) group signatures with message-dependent opening \cite{seh+12}, or
-anonymous credentials with revocation \cite{cks10} or delegation \cite{bcc+09}.
+We observe that in all GS and AC models, concrete
+claims related to user knowledge are proven either at issuance, signature
+generation, and opening times. Typically, at issuance time, the user proves
+knowledge of a secret key; at signing time, she proves that her secret key (and,
+potentially, more attributes) has been attested by some issuer; finally, at
+opening time, the opener proves that some fixed user-related information is
+contained in the de-anonymized signature.
+
+We note that instead of fixing in the model what concrete claim has to
+be made at each point, we can introduce \emph{functional placeholders} to be
+specified at the construction level. Of course, these functions need
+to depend on the user key and/or user credentials, attested attributes and
+signed message. But, in the modelling, we should only be concerned about their
+consistency -- i.e., that whatever is proved, relates to the correct user
+credential, signed message, etc.
+%
+It is through these functional placeholders that we can later tweak what
+information is required and revealed, and when. Given its generalisation
+capabilities, we refer to schemes meeting this model as Universal Anonymous
+Signatures.
+
+But the flexibility obtained from combining models from the AC and GS
+domains into one also brings complexity. For instance, in order to meet
+the general practice in AC, our UAS model includes multiple issuers. Along with
+the combination of GS features, this paves the way to including multiple
+openers, each with its own opening functionality. While powerful from a
+practical point of view, this introduces similar (unavoidable?) limitations
+privacy-wise as in functional encryption schemes \cite{bsw11} -- e.g., revealing
+too granular information at signing or opening time reduces privacy. However, on
+this occasion, signers controls ``how deanonymizable'' their signatures will
+be, and know it at signature generation time. This flexibility on the opening
+values also leads to the need of using extraction-based techniques for the
+modelling, since we cannot expect that opening outputs the real identity of the
+signer. This is no surprise, though, as it was already observed in GS schemes
+with non-conventional opening \cite{dl21}, in DAA schemes \cite{cdl16,cdl16b}.
+In fact, simulation-extractability seems to be most useful here, something that
+was also observed in \cite{cl06} for producing signatures out of knowledge of
+witnesses for concrete NP statements.
+
+\paragraph{Generic construction.} %
+We give \CUASGen, a generic construction of UAS based on well-known
+building blocks, and prove its security. Despite its functional flexibility, our
+construction is simple. Like many previous related schemes, credentials are
+signatures over blocks of messages -- each message encoding a different
+attribute. Users simultaneously leveraging multiple credentials need to prove
+that they are bound to the same key. Utility information to be revealed at
+signing time is output in plaintext, and utility information extractable by
+openers is encrypted under their public key -- in both cases, users prove
+correct computation.
+
+The three functional placeholders mentioned above are \fissue, \feval, and
+\finsp. \fissue is the function that users are required to evaluate at issuance
+time, to prove knowledge of a user key and, potentially, claims over attributes
+in previously obtained credentials. \feval is computed at signing time by the
+user, and controls and proves correctness of the information learned by
+verifiers. Finally, \finsp, although  computed also at signing time by the
+users, proves correctness of the utility information extractable after signing.
+The latter is, in addition, fed and modulated with the output of \feval. Through
+these functions, we define NP statements that need to be proven by different
+algorithms/protocols, summarised in \figref{fig:proof-blocks-uas}.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.85}{
+    \input{figures/proof-blocks-uas.tex}
+  }
+  \caption{Summary of statements proved per operation in \UAS.
+    $K(x)$ means proving knowledge of $x$; $E(y)$ means proving correct
+    encryption of $y$; $D(z)$ means proving correct decryption of (an encryption
+    of) $z$. $\usk \coloneqq$ user secret key; $\scred \coloneqq$ set of
+    credentials.}
+  \label{fig:proof-blocks-uas}
+\end{figure}
+
+\paragraph{Universality.}
+To formally showcase that UAS can indeed claim to be universal, we prove that
+restrictions of our generic construction imply the GS and AC ancestors of UAS.
+But this includes not only their vanilla versions, but also relevant variants,
+such as MPS \cite{ngsy22}, (a modified version of) group signatures with
+message-dependent opening \cite{seh+12}, or anonymous credentials with
+revocation \cite{cks10} or delegation \cite{bcc+09}.
+%
 Strictly speaking, for AC schemes, we build on a simple transform of our main
 construction and model that turns non-interactive signatures into interactive
-authentication protocols with protection against replay attacks\footnote{This is
+authentication protocols with protection against replays\footnote{This is
   the well-known folklore approach that has the verifier send a fresh nonce to
   be signed by the alleged owner of the private key related to a known
-  public key.}. We further show how to
-build ring signatures (RS) in the model given by \cite{bkm06}, from an
-alternative \UAS construction that improves issuer privacy.
+  public key.}. We further build ring signatures (RS) in the model given by
+\cite{bkm06}, from an alternative UAS construction that improves issuer privacy.
 %
-The most interesting part being that, while we prove implications with other
-previously known schemes, our generalisation approach allows to merge features
-of them: e.g., one can easily model and instantiate GSs with with no revocation
-at all, ACs with full de-anonymization, RS with linkability, or anything in
-between.
+The most interesting part being that, while we prove implications with
+previously known schemes, our approach allows to merge their features: e.g.,
+one can easily instantiate GSs with with no revocation at all, ACs
+with full de-anonymization, RS with linkability, etc.
 
-%% Our results; Tech nuances
-\paragraph{Modelling challenges.} %
-Combining and extending features of GS and AC into a unified model unavoidably
-brings complexity. For instance, we allow proving arbitrary claims over
-previously obtained credentials at issuance time, in order to inform the
-issuance decision. Thus, it is necessary to model unforgeability guarantees
-already at that point -- something not considered in previous works as far as
-we know. Also, in
-order to meet the general practice in AC, the model for \UAS includes multiple
-issuers. Interestingly, combining this generalisation with the GS world also
-paves the way to include multiple openers, each with its own opening
-functionality. While powerful from a practical point of view, this introduces
-similar (unavoidable?) limitations privacy-wise as in functional encryption
-schemes \cite{bsw11} -- e.g., revealing too granular information at signing or
-opening time makes privacy go away. However, on this occasion, it is the signer
-(perhaps jointly with the verifier) who decides the signing and
-opening policy. Thus, the user is in full control of how deanonymizable its
-signatures will be, and knows it at signature generation time. This flexibility
-on the opening values also leads to the
-need of using extraction-based techniques for the modelling, since we cannot
-expect that opening outputs the real identity of the signer. This comes as no
-surprise, though, as it was already observed in GS schemes with non-conventional
-opening \cite{dl21}, in DAA schemes \cite{cdl16,cdl16b} or in AC schemes that
-need to ensure correctness of information generated before authentication, like
-delegatable credentials \cite{bcc+09}, that prove validity of the delegation
-chain. In fact, simulation-extractability seems to be most useful here,
-something that was also observed in \cite{cl06} for producing signatures out of
-knowledge of witnesses for concrete NP statements.
+While already before \UAS it may have not seemed hard to build either of these
+primitives from another, with \UAS one essentially just needs to give concrete
+definitions of \fissue, \feval and \finsp in what we call a $(\fissue,\feval,
+\finsp)$-\CUASGen restriction. Security then basically follows from
+the fact that \CUASGen is a secure \UAS scheme. We believe that this is a
+powerful notion, that may finally allow research lines that have
+followed different paths to easily benefit from the findings of each other.
+\figref{fig:relations} graphically summarises the relations we prove between
+\UAS and other schemes -- although, of course, many more are probably
+achievable.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.85}{
+    \input{figures/relations.tex}
+  }
+  \caption{Summary of schemes that can be instantiated as restrictions of our
+    generic constructions and proved secure under our \UAS model. Between
+    parenthesis we show the adopted reference model, and the section offering
+    full detail.}
+  \label{fig:relations}
+\end{figure}
+
+% \paragraph{Modelling challenges.} %
+% Combining and extending features of GS and AC into a unified model unavoidably
+% brings complexity. For instance, we allow proving arbitrary claims over
+% previously obtained credentials at issuance time, in order to inform the
+% issuance decision. Thus, it is necessary to model unforgeability guarantees
+% already at that point -- something not considered in previous works as far as
+% we know. Also, in
+% order to meet the general practice in AC, the model for \UAS includes multiple
+% issuers. Interestingly, combining this generalisation with the GS world also
+% paves the way to include multiple openers, each with its own opening
+% functionality. While powerful from a practical point of view, this introduces
+% similar (unavoidable?) limitations privacy-wise as in functional encryption
+% schemes \cite{bsw11} -- e.g., revealing too granular information at signing or
+% opening time makes privacy go away. However, on this occasion, it is the signer
+% (perhaps jointly with the verifier) who decides the signing and
+% opening policy. Thus, the user is in full control of how deanonymizable its
+% signatures will be, and knows it at signature generation time. This flexibility
+% on the opening values also leads to the
+% need of using extraction-based techniques for the modelling, since we cannot
+% expect that opening outputs the real identity of the signer. This comes as no
+% surprise, though, as it was already observed in GS schemes with non-conventional
+% opening \cite{dl21}, in DAA schemes \cite{cdl16,cdl16b} or in AC schemes that
+% need to ensure correctness of information generated before authentication, like
+% delegatable credentials \cite{bcc+09}, that prove validity of the delegation
+% chain. In fact, simulation-extractability seems to be most useful here,
+% something that was also observed in \cite{cl06} for producing signatures out of
+% knowledge of witnesses for concrete NP statements.
 
@@
 By enabling customization at issuance, signing and opening times, as well as
-multiple uncoupled issuers and openers, the
-possibilities are large. As an example, consider a social network that requires
-under-age users to get permission from one parent. This can be defined via a
-delegatable credential scheme, checking that the delegation chain of the user
-requesting to join is valid via a policy at issuance time. Later, in order to
-make some post in the system advertising something to be sold in a local
+multiple uncoupled issuers and openers, the possibilities are large and
+especially useful in contexts where different parties may have different
+privacy-vs-utility tradeoffs. As an example, consider a social network that
+requires under-age users to get permission from one parent. This can be defined
+via a delegatable credential scheme, checking that the delegation chain of the
+user requesting to join is valid via a policy at issuance time. Later, in order
+to make some post in the system advertising something to be sold in a local
 second-hand page in the social network, the user may need to reveal, at signing
@@
 
-%% Our techniques
-%%% E.g., describe how we compatibilize both with AC sel disc., ring sigs, and MPS
-\paragraph{Our construction approach.} %
-The high-level idea for our generic construction \CUASGen is simple. Credentials
-are signatures over blocks of messages (some signed in committed form), where
-each message can be a different attribute, and a user who wants to
-simultaneously leverage multiple credentials needs to bind all of them to the
-same key. We add three generic functions: \fissue, leveraged by users at
-credential issuance time to prove claims over attributes in other credentials,
-in order to get a new one; \feval, proving correctness of the utility revealed
-at signing time; and \finsp, proving correctness of the utility information
-extractable after signing. The latter is, in addition, fed and modulated with
-the output of \feval. The pattern of the statements proven in each function is
-summarised in \figref{fig:proof-blocks-uas}.
+% %% Our techniques
+% %%% E.g., describe how we compatibilize both with AC sel disc., ring sigs, and MPS
+% \paragraph{Our construction approach.} %
+% The high-level idea for our generic construction \CUASGen is simple. Credentials
+% are signatures over blocks of messages (some signed in committed form), where
+% each message can be a different attribute, and a user who wants to
+% simultaneously leverage multiple credentials needs to bind all of them to the
+% same key. We add three generic functions: \fissue, leveraged by users at
+% credential issuance time to prove claims over attributes in other credentials,
+% in order to get a new one; \feval, proving correctness of the utility revealed
+% at signing time; and \finsp, proving correctness of the utility information
+% extractable after signing. The latter is, in addition, fed and modulated with
+% the output of \feval. The pattern of the statements proven in each function is
+% summarised in \figref{fig:proof-blocks-uas}.
 
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{
-    \input{figures/proof-blocks-uas.tex}
-  }
-  \caption{Summary of statements proved per operation in \UAS.
-    $K(x)$ means proving knowledge of $x$; $E(y)$ means proving correct
-    encryption of $y$; $D(z)$ means proving correct decryption of (an encryption
-    of) $z$. $\usk \coloneqq$ user secret key; $\scred \coloneqq$ set of
-    credentials.}
-  \label{fig:proof-blocks-uas}
-\end{figure}
+% \begin{figure}[ht!]
+%   \centering
+%   \scalebox{0.9}{
+%     \input{figures/proof-blocks-uas.tex}
+%   }
+%   \caption{Summary of statements proved per operation in \UAS.
+%     $K(x)$ means proving knowledge of $x$; $E(y)$ means proving correct
+%     encryption of $y$; $D(z)$ means proving correct decryption of (an encryption
+%     of) $z$. $\usk \coloneqq$ user secret key; $\scred \coloneqq$ set of
+%     credentials.}
+%   \label{fig:proof-blocks-uas}
+% \end{figure}
 
-From \CUASGen, one can already build known (and more functionality-limited)
-schemes from what we call \emph{restrictions} of \CUASGen simply by giving
-concrete definitions of \fissue, \feval, and \finsp. Yet, the model remains the
-same, and we prove that if such restrictions of \CUASGen are secure in the \UAS
-model, they lead to secure constructions for the related primitives (GS
-variants, AC variants, etc). To define our generic construction, we also specify
-concrete NP relations for the underlying NIZK proofs for issuing, signing, and
-opening. These NP relations must not be considered as immutable, though --
-informally, it would seem that they must simply follow the pattern in
-\figref{fig:proof-blocks-uas}. Actually, as mentioned, we show how by making a
-minor variation into the relation used for signing, a \CUASGen restriction can
-securely build ring signatures.
-
-We emphasize that, while -- already before \UAS -- it may have not seemed hard
-to build either of these primitives from another, the core of our contribution
-is that, with \UAS, one essentially just needs to give concrete definitions of
-three functions. Security of the final primitive then basically follows from
-the fact that it is a secure instantiation of an \UAS scheme. We believe that
-this is a powerful notion, that may finally allow research lines (AC and GS)
-that have followed different paths to easily benefit from the findings of each
-other. \figref{fig:relations} graphically summarises the relations we prove
-between \UAS and other schemes -- although, of course, many more are probably
-achievable.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{
-    \input{figures/relations.tex}
-  }
-  \caption{Summary of schemes that can be instantiated as restrictions of our
-    generic constructions and proved secure under our \UAS model. Between
-    parenthesis we show the adopted reference model, and the section offering
-    full detail.}
-  \label{fig:relations}
-\end{figure}
+% From \CUASGen, one can already build known (and more functionality-limited)
+% schemes from what we call \emph{restrictions} of \CUASGen simply by giving
+% concrete definitions of \fissue, \feval, and \finsp. Yet, the model remains the
+% same, and we prove that if such restrictions of \CUASGen are secure in the \UAS
+% model, they lead to secure constructions for the related primitives (GS
+% variants, AC variants, etc). To define our generic construction, we also specify
+% concrete NP relations for the underlying NIZK proofs for issuing, signing, and
+% opening. These NP relations must not be considered as immutable, though --
+% informally, it would seem that they must simply follow the pattern in
+% \figref{fig:proof-blocks-uas}. Actually, as mentioned, we show how by making a
+% minor variation into the relation used for signing, a \CUASGen restriction can
+% securely build ring signatures.
 

### 2022-09-16 prism-backend/research/gsac/preliminaries-paper.tex
In depth pass up to sec 3.1.

@@
 
-Next we introduce the main building blocks we will be using in our
-constructions. More detailed definitions and references appear in
+Next we introduce the main building blocks we use in our constructions. More
+detailed definitions and references appear in
 \appref{app:crypto-building-blocks}.
@@
 \paragraph{Signatures over Blocks of Committed Messages, with proofs.} %
-We use signature schemes that allow signing blocks of messages, or commitments
+We use signature schemes that allow signing blocks of messages, and commitments
 to blocks of messages, and which are furthermore compatible with (efficient)
@@
 share common (but different)
-tokens: e.g., we will resort to several NIZK proofs instances. To distinguish
+tokens: e.g., we resort to several NIZK proofs instances. To distinguish
 them, we may use subscripts or superscripts: e.g., $\NIZKRel_A$ denotes the
@@
 the setup algorithm of an underlying NIZK system is performed associated to
-relation $\NIZKRel$; $\SBCMparm$ are the public parameters for an \SBCM scheme,
-and $\Eparm$ are the public parameters for an encryption scheme, etc. Variables
-written in bold font denote sets, e.g., while we use \ipk to denote a single
-issuer public key, \sipk denotes a set of issuer's public keys. To refer to
-a specific element of a set, we use sub-indexes, e.g., $\sipk_i$ is the $i$-th
-\ipk within \sipk.
+relation $\NIZKRel$; $\parm_X$ are the public parameters for scheme $X$, etc.
+Variables written in bold font denote sets, e.g., while we use \ipk to denote a
+single issuer public key, \sipk denotes a set of issuer's public keys --
+although, when needed, we use explicit notation $\lbrace \ipk_i
+\rbrace_{i\in[n]}$.
 %

### 2022-09-16 prism-backend/research/gsac/uas-paper.tex
In depth pass up to sec 3.1.

--- 2022-06-18 prism-backend/research/gsac/uas-paper.tex
@@
 \usepackage{hyperref}
-\usepackage{mathtools}
+%\usepackage{mathusertools}
 \usepackage{multirow}
+\usepackage{dashbox}
+
+% Box types
+\newcommand\dboxed[1]{\dbox{\ensuremath{#1}}}
+\makeatletter
+\newcommand{\dotboxed}[1]{%
+\tikz[baseline={([yshift=-1ex]current bounding box.center)}] \node [rectangle, minimum width=1ex,dotted,draw,line width=0.6pt] {\normalcolor\m@th$\displaystyle#1$};}
+\makeatother
 \usepackage{footnote}
+\usepackage{framed}
+\usetikzlibrary{decorations.pathreplacing,calligraphy}
 \makesavenoteenv{tabular}
@@
 {\def\addcontentsline#1#2#3{}\maketitle}%\maketitle
+\ifnum\authnotes=1
+Version of \today
+\fi
 
 \begin{abstract}
-  \todo{XXX}
+  For decades, anonymous credentials (AC), group signatures (GS), and
+  related schemes in the field of privacy-preserving authentication, have
+  relied on common cryptographic tools. Yet, each has its own
+  approach modelling-wise. Even within systems of the same type, multiple
+  ``sub-models'' coexist, catering for slightly different needs.
+  %
+  Works like Camenisch et al (SAC'15) or Nguyen et al (CRYPTO'22)
+  generalise some aspects, but still within their own domain -- AC and GS,
+  respectively.
+
+  In this work, we make a further effort in order to come up with a flexible
+  game-based model that generalises and unifies GS and AC schemes. The key to
+  this flexibility lies in functional placeholders
+  that, with careful constraints, still allow to capture generalised notions of
+  the usual anonymity, unforgeability and non-frameability properties. We refer
+  to this unified model as \emph{Universal Anonymous Signatures} (\UAS).
+
+  To showcase the generality of \UAS, we give a construction following our
+  model and prove that, from it, we can easily build multiple
+  variants of group signatures, anonymous credentials, and ring signatures, just
+  by giving concrete definitions of the mentioned functional placeholders.
+
+  Our main theoretical contribution is unifying previously separate (albeit
+  close) systems under the same generalised model. Such unified model also
+  allows to, very easily, build ``hybrid'' systems combining features
+  of previously separately modelled constructions: e.g., anonymous credentials
+  with conditional deanonymization based on their attributes.
+
+  In practice, this means that cryptographic engineers and system designers
+  can reach the desired utility-vs-privacy tradeoff that best suits their needs,
+  just by defining a few functions -- but without needing to prove security from
+  scratch or implement a whole system.
 \end{abstract}

### 2022-09-16 prism-backend/research/gsac/formal-uas.tex
Minor changes.

@@
 we are only concerned with preventing that the output of these functions can
-be dishonestly altered, and with ensuring that it does not threaten privacy
-beyond what is necessary or unavoidable to reach the flexibility we want.
+be altered, and with ensuring that it does not threaten privacy beyond what is
+necessary or unavoidable to reach the flexibility we want.
 
@@
 \paragraph{Issuance, evaluation, and opening functions.} %
-We introduce three functions in our syntax and model. Through them,
-it is possible to modulate the behaviour of the resulting instantiation, by
+We introduce three functions in our syntax and model. Through them, it is
+possible to modulate the behaviour of the resulting instantiation, by
 controling the conditions upon which a new credential can be issued, the
@@
   by each issuer within a family of functions \famfissue, the issuance function
-  defines the customized conditions required by the issuer to grant a credential
+  defines the conditions required by the issuer to grant a credential
   with identifier $\cid = (\cidi,\cidu)$, over attributes \attrs, when requested
-  by a user with public key \upk,
-  leveraging a set of $n$ previously obtained credentials with identifiers and
-  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
-  $n$ may be $0$ if no previously obtained credential is used). \fissue returns
+  by a user with public key \upk, leveraging a set of $n$ previously obtained
+  credentials with identifiers and attributes given by $\lbrace (\cid_i,
+  \cattrs_i) \rbrace_{i \in [n]}$ (where $n$ may be $0$). \fissue returns
   a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
@@
 
-Concerning \fissue functions, our \UAS model requires them to be \UAS-acceptable
-functions. At a high level, this requires that \fissue functions do not reveal
-anything about the signer's data used as input. This is formally captured in
-\figref{fig:uas-acceptable}.
+Concerning \fissue functions, our \UAS model requires them to be
+\UAS-acceptable. At a high level, this requires that \fissue functions do not
+reveal anything about the signer's data used as input. This is formally captured
+in \figref{fig:uas-acceptable}.
+%
+A \UAS construction thus can only be secure if the \fissue functions it uses
+are \UAS-acceptable.
 
@@
 
-A \UAS construction thus can only be secure if the \fissue function it uses is
-\UAS-acceptable.
-%
-Next, we define the concept of \CUASGen restrictions. Briefly, these are special
+Next, we define the concept of \CUASGen restrictions. These are special
 cases of our generic construction that target a concrete variant of the
 utility-privacy tradeoff by defining concrete \fissue, \feval and \finsp
-functions. Security of \CUASGen implies security of its restrictions, as long as
+functions. Security of \CUASGen implies security of its restrictions, if
 the chosen \fissue functions are \CUASGen-acceptable.

### 2022-09-19 prism-backend/research/gsac/app-related-extra.tex
Completed in-depth pass. Some changes pending.

@@
 \subsubsection{\CUASGSMDO construction.} %
-Our \CUASGSMDO construction is essentially a $(\fissue^{single,F,I},\feval^0,
-\finsp^{\smsg})$-\CUASGen restriction, where $\fissue^{single,F,I}$ and
+Our \CUASGSMDO construction is essentially a $(\fissue^{single,H,I},\feval^0,
+\finsp^{\smsg})$-\CUASGen restriction, where $\fissue^{single,H,I}$ and
 $\feval^0$ are as in \figref{fig:func-restrictions}, and $\finsp^{\smsg}$, is as
@@
 directly here.
+
+\subsection{Multimodal Private Signatures}
+\label{ssec:related-models-mps}
+
+Multimodal Private Signatures (or, rather, a close relative, see next) are
+directly implementable as a $(\fissue^{single,H,I},\feval^{F,MPS},
+\finsp^{G,MPS})$-\CUASGen restriction. Concretely, this restricts to a system
+with one credential per user and no attributes in the credentials.
+
+There are some differences, though. On the one hand, our signature anonymity
+property is somehow in the middle of MPS's privacy-1 and privacy-2 variants.
+Their privacy-1 variant is the traditional anonymity property of group
+signatures, in which the opener is honest and the adversary can call the opening
+oracle except for challenge signatures. In their privacy-2 variant, the opener
+is fully corrupt (i.e., \adv~ receives \osk), but the adversary can only be
+challenged with signatures that produce the same \yinsp value ($G_{j_b}(id_b)$
+in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
+(getting ther \osk), but the challenge signatures must have been generated using
+the key of an uncorrupted opener; still, \adv~can call the open oracle for
+challenge signatures, as long as they have the same \yinsp value. We believe
+that these differences are mostly of theoretical interest, though. In practice,
+what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$
+in MPS) that has too much granularity in their ranges, will lead to a barely
+private system. This is a known issue, for instance, in functional encryption
+\cite{bsw11}.
+
+On the other hand, anonymous issuance and the capability to customize issuance
+policies are unachievable by MPS. Anonymous issuance simply does not make sense
+in MPS, as it only supports one credential (without attributes) per user, and
+customized issuance is achieved in \UAS via the \fissue functions, with no
+equivalent in MPS -- instead, MPS can be seen as having the fixed policy of
+``proving knowledge of a user secret key''. These extensions are not trivial
+from a modelling point of view, and also have a big impact in the practicality
+of the resulting system. Also, MPS does not include verifiable openings. While
+this is easy to add, we consider it to be essential, given that the proposed
+generalization of opening allows the opener to output ``any value''. Hence, the
+need to ensure that the produced value is the legitimate one seems to be more
+necessary than ever. Finally, our \feval function is a generalization of $F$ in
+MPS, as it allows two outputs: one will be returned in the clear along with the
+signature, and the other will be encrypted. Indeed, making part of the output
+unencrypted allows implementing very useful variants such as anonymous
+credentials with selective disclosure, as shown before.
+
+For the model of MPS schemes, we refer to the original paper \cite{ngsy22}.
+
+\subsubsection{\CUASMPS construction.} %
+As mentioned, a $(\fissue^{single,H,I},\feval^{F,MPS},
+\finsp^{G,MPS})$-restriction implements an MPS scheme where
+$\fissue^{single,H,I}$ is as in \figref{fig:func-restrictions}, $\feval^{F,MPS}$
+equals MPS's $F$ function, and MPS's $G$ function equals $\finsp^{G,MPS}$, both
+as defined in \esref{eq:funcs-mps}.
+
+\begin{align}
+  \feval^{F,MPS}(\upk,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},\msg)
+  \coloneqq & \nonumber \\
+  & \hspace*{-10em} \pcif F(\upk,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},
+    \msg) = 0: \pcreturn \bot \nonumber \\
+  & \hspace*{-10em} \pcelse: \pcreturn (\ast,F(\upk,\lbrace(\cid_i,\attrs_i)
+    \rbrace_{i\in[n]},\msg)) \nonumber \\
+  \finsp^{G,MPS}((\cdot,\yeval^1),\upk,\cid,\attrs,\cdot) \coloneqq
+  & \nonumber \\
+  & \hspace*{-10em} \pcreturn G(\yeval^1,\upk,\cid,\attrs)
+    \label{eq:funcs-mps}
+\end{align}
+
+With these functions, the construction is direct. \CUASMPS's setup runs
+\CUASGen's \Setup, \OKeyGen, and generates the issuer key pair by running
+\KeyGen and \ISet (with $\fissue^{single,H,I}$). For MPS's join, \CUASMPS runs
+first \KeyGen to generate the user key pair, and then proceeds as in \CUASGen.
+\Sign, \Verify and \Open, are as in \CUASGen.
+
+Finally, note that, in MPS, $G$ is further parameterized with a value $j$, which
+essentially is the result of applying $F$ to the message and signer identity,
+and is not leaked to the opener nor any other third party. The equivalent in
+\UAS is the $\yeval^1$ value which, in \CUASGen, is encrypted with a single-use
+key pair, and is an input of \finsp.
+
+\paragraph{Security of \CUASMPS.} %
+As stated, we restrict to privacy-1 of MPS (although, as
+discussed, we actually achieve something slightly stronger). Unforgeability-1 in
+MPS is implied by unforgeability in \UAS (where the latter also covers
+unforgeability of \fissue evaluations, plus verifiable openings).
+Unforgeability-2 in MPS is equivalent to non-frameability in \UAS (where the
+latter also includes framing via verifiable openings). Finally note that, in
+UAS, we do not explicitly model extractability, but rather make it an inherent
+requirement in the unforgeability and non-frameability definitions. Thus, our
+\CUASMPS construction also ensures MPS-extractability.
+
+\begin{theorem}[Privacy-1 of \CUASMPS]
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASMPS satisfies privacy-1
+  according to \cite{ngsy22}.
+\end{theorem}
+
+\begin{proof}  
+  Note that the privacy-1 game in MPS and the signature anonymity game in \UAS
+  are, in essence, equivalent. Thus, given an adversary \adv~that breaks
+  privacy-1 of \CUASMPS as defined for MPS, it is easy to build an adversary
+  \advB breaking signature anonymity of the underlying \CUASGen, as defined in
+  \UAS.
+
+  \advB simply leverages its own oracles in order to answer oracle queries from
+  \adv: $\mathcal{O}_{read},\mathcal{O}_{write},\mathcal{O}_{CU},\mathcal{O}_{HU},
+  \mathcal{O}_{sig},\mathcal{O}_{open}$ in MPS correspond to \RREG, \WREG,
+  \CUGEN, \HUGEN, \SIGN and \OPEN in \UAS, respectively. The output given by
+  \adv~in the first stage of the MPS game is then directly used as input to
+  \advB's \CHALb oracle. Finally, \advB outputs whatever \adv~outputs.
+
+  Since the simulation is direct, it is easy to see that, whenever \adv~wins,
+  so does \advB.
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Extractability of \CUASMPS]
+  If the base \CUASGen construction has non-frameability according to
+  \defref{def:frame-uas}, then \CUASMPS is an extractable MPS scheme.
+\end{theorem}
+
+\begin{proof}  
+  The proof is direct, as the winning conditions in the extractability
+  experiment in MPS are also winning conditions in the non-frameability
+  experiment for \UAS. That is, an adversary \adv~against extractability of
+  \CUASMPS, as defined in MPS, can be used to build an adversary \advB breaking
+  non-frameability of \CUASGen, as defined in the \UAS model.
+
+  \advB simulates \adv's game essentially as in the privacy-1 proof. Note also
+  that \adv~receives the issuer's secret key. This can be obtained by \advB via
+  its \ICORR oracle. Eventually, \adv~outputs a $(F,M,\Sigma)$ tuple, which
+  corresponds to $(\feval^{g,MPS},\msg,\Sig)$ (with $g=F$ in MPS) in \CUASGen,
+  which \advB outputs in its own game. In addition, \advB outputs as $(\yinsp,
+  \pi)$ values the output of \Open over $(\Sig,\msg)$ -- which internally
+  computes $\finsp^{h,MPS}$, for $h=G$ in MPS.
+  % 
+  Note that the $\feval^{g,MPS}$ and $\finsp^{h,MPS}$ functions in \CUASMPS
+  mimic the behaviour of MPS's $F$ and $G$, respectively. Thus, if \adv wins
+  because $F$ returns $0$ when evaluated on the extracted values, then \advB
+  wins at line 7 of the non-frameability game, as a legitimately computed
+  $\feval^{g,MSP}$ function cannot output $0$. Similarly, if \adv~wins because
+  the value returned by an honestly computed open function over the adversarial
+  $(F,M,\Sigma)$ tuple does not match the output of $G$ over the extracted
+  values, \advB wins at line 9: note that \advB returns the \yinsp value that
+  \Open outputs (when computed honestly over \adv's output), whereas
+  $\finsp^{g,MSP}=G$; thus, if both values differ in \adv's game, then they also
+  differ in \advB's game.
+  %
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability-1 of \CUASMPS]
+  If the base \CUASGen construction is unforgeable according to
+  \defref{def:forge-uas}, then \CUASMPS satisfies unforgeability-1 as defined in
+  \cite{ngsy22}.
+\end{theorem}
+
+\begin{proof}
+  Given an adversary \adv~against unforgeability-1 of \CUASMPS, as defined in
+  the MPS model, we build \advB that breaks unforgeability of the underyling
+  \CUASGen, as defined for \UAS.
+
+  Simulation of \adv's oracles by \advB is again direct (as in previous proofs).
+  Now, suppose that \adv~wins -- i.e., the identity extracted by \adv~does not
+  belong to the set of corrupt users in \adv's game. By construction of \advB
+  (identities in \adv's game map to a $\cid$ for \advB), $\OWNR[\cid] \notin
+  \CU$ in \advB's unforgeability game either.
+  % 
+  However, in order for \advB to win in its own game, we need to prove also that
+  the produced identity does not belong to a user in \HU either. Suppose that it
+  does. Simulation extractability ensures that the credentials extracted by
+  \adv~all belong to the same user (by assumption, in \HU) -- i.e., they are
+  bound to its \usk. Moreover, since \adv~wins its game, the signature output by
+  \adv~has not been obtained via its \SIGN oracle. But, given that the user is
+  honest, its \usk has been produced uniformly at random, and has not been
+  leaked to \adv~(as the issuer is also honest). Thus, the probability that
+  the extracted credentials belong to an honest user is negligible and, if
+  \adv~wins its game, \advB also does.
+  %
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability-2 of \CUASMPS]
+  If the base \CUASGen construction has non-frameability according to
+  \defref{def:frame-uas}, then \CUASMPS satisfies unforgeability-2 as
+  defined in \cite{ngsy22}.
+\end{theorem}
+
+\begin{proof}
+  Given an adversary \adv~against unforgeability-2 of \CUASMPS, as defined in
+  the MPS model, we build \advB that breaks non-frameability of the underyling
+  \CUASGen, as defined for \UAS.
+
+  Simulation of \adv's oracles by \advB is as in the unforgeability-1 proof.
+  \advB outputs whatever \adv~outputs, adding a $(\yinsp,\iproof)$ pair, honestly
+  generated from \adv's output. Note that the winning condition of \adv~
+  requires that the produced signature belongs to an honest user, without
+  having been produced via a call to the signing oracle. By construction of
+  \advB, this directly makes \advB win in line 11 of the non-frameability game.
+  %
+  \qed
+\end{proof}
+
+% \begin{theorem}[Privacy-1 of \CUASMPS]
+%   If the base \CUASGen construction has signature anonymity according to
+%   \defref{def:sign-anonymity-uas}, then \CUASMPS satisfies privacy-1
+%   according to \cite{ngsy22}.
+% \end{theorem}
+
+% \begin{theorem}[Extractability of \CUASMPS]
+%   If the base \CUASGen construction is unforgeable according to
+%   \defref{def:forge-uas}, then it is an extractable MPS scheme.
+% \end{theorem}
+
+% \begin{theorem}[Unforgeability-1 of \CUASMPS]
+%   If the base \CUASGen construction is unforgeable according to
+%   \defref{def:forge-uas}, then \CUASMPS satisfies unforgeability-1 as
+%   defined in \cite{ngsy22}.
+% \end{theorem}
+
+% \begin{theorem}[Unforgeability-2 of \CUASMPS]
+%   If the base \CUASGen construction has non-frameability according to
+%   \defref{def:frame-uas}, then \CUASMPS satisfies unforgeability-2 as
+%   defined in \cite{ngsy22}.
+% \end{theorem}
+
+\subsection{Revocable Anonymous Credentials}
+\label{ssec:related-models-rac}
+
+In \cite{cks10,ckl+15}, revocable anonymous credentials are proposed. We first
+give a simple model in \figref{fig:model-rac}, extending that in
+\secref{ssec:related-models-ac}. Concretely, to the functionality in
+\secref{ssec:related-models-ac}, we now explicitly add the $OKeyGen$ function,
+which generates the opener key pair, extend $Verify$ to receive also a list $L$
+of revoked credential identifiers, and we add a function (and corresponding
+oracle) $cid/\bot \gets RetrieveCredId(\osk,\utrans)$ that can extract an
+identifier of the credential used in a presentation transcript \utrans. For
+simplicity, we do not include the equivalent to verifiable openings, but this
+would be straightforward.
+
+\begin{figure}[ht!]
+  \centering
+  \scalebox{0.85}{      
+    \begin{minipage}[t]{0.43\textwidth}
+      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\opk,\osk) \gets \OKeyGen(\parm) \\        
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
+        b^* \gets \adv^{\mathcal{O}_{rac},\oracle{LoR}}(\parm,\ipk,\opk) \\
+        \pcreturn b^*
+      }
+    \end{minipage}
+  }
+  \scalebox{0.85}{      
+    \begin{minipage}[t]{.57\textwidth}
+      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
+        \parm \gets \Setup(1^\secpar) \\
+        (\opk,\osk) \gets \OKeyGen(\parm) \\        
+        (\ipk,\isk) \gets IssKeyGen(\parm) \\
+        (\cid,D,L,\st) \gets
+        \adv^{\mathcal{O}_{rac}}(\parm,\ipk,\opk) \\
+        \langle \cdot,(b_0,\utrans_0)\rangle
+        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
+        \langle \cdot,(b_1,\utrans_1)\rangle
+        \gets \langle Show(\ipk,\ATTR[\cid],D,\CRED[\cid]), \\
+        \hspace*{7.25em}\Verify(\ipk,D,L)\rangle \\
+        \pcif \OWNR[\cid] \notin \HU \lor
+        D \not\subseteq \ATTR[\cid]: \pcreturn 0 \\
+        \pcif b_0 = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
+        \land D \subseteq \ATTR[j]): \\
+        \pcind \pcreturn 1 \\
+        h_{\bin} \gets RetrieveCredHandle(\osk,\utrans_{\bin}) \\
+        \pcreturn h_0 \in L \lor (h_1 \notin L \land b_1 = 0)
+      }       
+    \end{minipage}      
+  }
+  \caption{Security games for revocable anonymous credentials with selective
+    disclosure based on \cite{fhs19}. 
+    $\mathcal{O}_{rac} \gets \lbrace \oracle{HU},\oracle{CU},\oracle{Obtain},
+    \oracle{Issue},\oracle{ObtIss},\oracle{Show},\oracle{ReqCredHandle}\rbrace$.
+    $\oracle{ReqCredHandle}$ is
+    equivalent to \OPEN, operating on transcripts \utrans instead of signatures
+    but, in addition, keeps a list of revoked users (per verifier), based on the
+    queries it receives. In $\Exp^{forge}_{\adv,rac}$, \adv~wins if it
+    authenticates using a revoked credential or despite not having the required
+    attributes, or if it prevents an honest user from authenticating using a
+    non-revoked credential.}
+  \label{fig:model-rac}  
+\end{figure}
+
+\subsubsection{\CUASRAC Construction.} %
+Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,H,V,L},
+\finsp^{F})$-\CUASGenInt restriction, where $\fissue^1$ is as in
+\figref{fig:func-restrictions}, and $\feval^{\dattrs,H,V,L}$ and $\finsp^{H}$
+are ase specified in \esref{eq:funcs-rac}.
+
+\begin{align}
+  \feval^{\dattrs,H,V,L}(\upk,((\cidi,\cidu),\attrs),\cdot) \coloneqq &
+    \nonumber \\
+  & \hspace*{-10em} \pcif F(V,\cidi) \in L \lor F(V,\cidu) \in L: \pcreturn \bot
+  \nonumber \\
+  & \hspace*{-10em} \pcelse \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},V) \nonumber \\
+  \finsp^{F}((\cdot,\yeval^1),\cdot,((\cidi,\cidu),\attrs),\cdot)
+  \coloneqq  & \nonumber \\
+  & \hspace*{-10em} \pcreturn (F(\yeval^1,\cidi),F(\yeval^1,\cidu))
+  \label{eq:funcs-rac}
+\end{align}
+
+Concretely, $\feval^{\dattrs,H,V,L}$ is defined via a set of attributes \dattrs
+to reveal (e.g., age, etc.), a PRF $F$, a string identifying the verifier $V$
+and a list $L$ of revocation handles by $V$. Note that, these ``extra
+parameters'' can be hardcoded, though: $F$ can be a fixed PRF for all verifiers,
+\dattrs and $V$ are also fixed (per verifier), and $L$ can be updated per
+verifier with some reasonable frequency -- e.g., daily -- so that the cost of
+recomputing $\feval^{\dattrs,H,V,L}$ is not high.
+%
+Since credentials in \CUASGenInt have two identifiers (\cidi, chosen by the
+issuer; and \cidu, chosen by the user), $\feval^{\dattrs,H,V,L}$ internally
+computes $F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval aborts.
+Otherwise, it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
+$\yeval^1 \gets V$. $\yeval^1$ is
+then used by $\finsp^H$ to compute $\yinsp \gets (H(\yeval^1,\cidi),
+H(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
+it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
+%
+In more detail, the algorithms are as follows:
+
+\begin{description}
+\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
+  \CUASGenInt.
+\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from
+  \CUASGenInt, setting $\fissue^1$ as issuance function.
+\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from \CUASGenInt,
+  setting $\finsp^F$ as opening function.
+\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from \CUASGenInt.
+\item[$\langle \cred/\bot,\top/\bot \rangle \gets
+  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
+  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGenInt, using
+  $\fissue^1$ as issuance function.
+\item[$\langle 1/0,(\yeval,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
+  \attrs,\dattrs,\cred),
+  \Verify(\ipk,\dattrs) \rangle$.]
+  Runs the interactive $\langle\Sign,\Verify\rangle$ of \CUASGenInt,
+  using $\feval^{\dattrs,H,V,L}$ as signature evaluation function, and
+  $\finsp^F$ as open function. The \yeval value output by the verifier, when
+  it accepts, is the $\yeval^0$ value produced by \Sign in \CUASGenInt.
+\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
+  Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
+  \utrans, and runs \Open from \CUASGenInt. This returns $(H(V,\cidi),
+  H(V,\cidu))$, which the verifier can add to its revocation list $L$.
+\end{description}
+
+\paragraph{Security of \CUASRAC.} %
+We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
+scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
+has signature anonymity and is unforgeable.
+%
+As for \CUASAC, we reduce to security of \CUASGen rather than to
+$\CUASGen^{int}$. The ``translation'' between \CUASGen and $\CUASGen^{int}$ is
+again trivial.
+
+\begin{theorem}[Anonymity of \CUASRAC]
+  \label{thm:anon-cuasrac}
+  If the base \CUASGen construction has signature anonymity according to
+  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
+  according to \cite{fhs19}.
+\end{theorem}
+
+\begin{proof}
+  Given \adv~ against anonymity of \CUASRAC as defined in
+  \figref{fig:model-rac}, we build an adversary \advB against anonymity of
+  \CUASGen as defined in \defref{def:sign-anonymity-uas}.
+  %
+  But, first observe that, since the revocation oracle is basically an extension
+  of the \OPEN oracle -- also keeping track of the revoked users per verifier --
+  queries involving challenge users are rejected if the revocation handle does
+  not match for both challenge users.
+
+  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
+  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
+  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, or \OPEN (in this case,
+  also keeping track of the queries, per verifier), respectively.
+  Note that ``translating'' the inputs from the former into inputs for the
+  latter is trivial. Also, observe that $ReqCredHandle$/\OPEN essentially
+  refuses to open transcripts from challenge users (signatures, in the
+  non-interactive equivalent), as $F(V,\ccidi_0) \neq F(V,\ccidi_1)$ (and,
+  similarly, for $\ccidu_b$) with overwhelming probability (see the $\tyinsp
+  \neq \yinsp$) check in \figref{fig:oracles2}. Obviously, if \adv~wins in its
+  anonymity game, then so does \advB with the same probability.
+  % 
+  \qed
+\end{proof}
+
+\begin{theorem}[Unforgeability of \CUASRAC]
+  If the base \CUASGen construction has unforgeability according to
+  \defref{def:forge-uas}, and $F$ is one-way, then \CUASRAC is an
+  unforgeable RAC scheme.
+\end{theorem}
+
+\begin{proof}
+  Given \adv~against unforgeability of \CUASRAC as defined in
+  \figref{fig:model-rac}, we build an adversary \advB against unforgeability of
+  \CUASGen as defined in \defref{def:forge-uas}.
+
+  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
+  that \adv~wins its game via the winning condition of line 9 in the RAC
+  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
+  that the probability of \adv~winning its game via condition $h_0 \in L$ at
+  line 11 is negligible, due to soundness of the NIZK for $\NIZKRel_{\Sign}$.
+  Moreover, soundness of NIZK for $\NIZKRel^{\Sign}$ as well as one-wayness
+  of $F$ ensure that, if $h_1 \notin L$, then $b_1 = 1$. Namely, even when given
+  $F(V,\cidi),F(V,\cidu)$ for a credential identified by $(\cidi,\cidu)$ owned
+  by an honest user, and some (potentially malicious) $V$, it is not possible to
+  generate $F(V',\cidi)$ nor $F(V',\cidu)$, for $V'=V$.
+  % 
+  \qed
+\end{proof}
+
+Note that, if we aim at global credential (resp. user) revocation rather than
+verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
+pair (resp., \upk), and no assumption regarding $F$ is needed.
 

### 2022-09-19 prism-backend/research/gsac/app-related-proofs.tex
Pass on main body.
Completed in-depth pass. Some changes pending.

@@
 
-\subsection{Security of \CUASRAC}
-
-We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
-scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
-has signature anonymity and is unforgeable.
-%
-As for \CUASAC, we reduce to security of \CUASGen rather than to
-$\CUASGen^{int}$. The ``translation'' between \CUASGen and $\CUASGen^{int}$ is
-again trivial.
-
-\begin{theorem}[Anonymity of \CUASRAC]
-  \label{thm:anon-cuasrac}
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
-  according to \cite{fhs19}.
-\end{theorem}
-
-\begin{proof}
-  Given \adv~ against anonymity of \CUASRAC as defined in
-  \figref{fig:model-rac}, we build an adversary \advB against anonymity of
-  \CUASGen as defined in \defref{def:sign-anonymity-uas}.
-  %
-  But, first observe that, since the revocation oracle is basically an extension
-  of the \OPEN oracle -- also keeping track of the revoked users per verifier --
-  queries involving challenge users are rejected if the revocation handle does
-  not match for both challenge users.
-
-  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
-  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
-  redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, or \OPEN (in this case,
-  also keeping track of the queries, per verifier), respectively.
-  Note that ``translating'' the inputs from the former into inputs for the
-  latter is trivial. Also, observe that $ReqCredHandle$/\OPEN essentially
-  refuses to open transcripts from challenge users (signatures, in the
-  non-interactive equivalent), as $F(V,\ccidi_0) \neq F(V,\ccidi_1)$ (and,
-  similarly, for $\ccidu_b$) with overwhelming probability (see the $\tyinsp
-  \neq \yinsp$) check in \figref{fig:oracles2}. Obviously, if \adv~wins in its
-  anonymity game, then so does \advB with the same probability.
-  % 
-  \qed
-\end{proof}
-
-\begin{theorem}[Unforgeability of \CUASRAC]
-  If the base \CUASGen construction has unforgeability according to
-  \defref{def:forge-uas}, and $F$ is one-way, then \CUASRAC is an
-  unforgeable RAC scheme.
-\end{theorem}
-
-\begin{proof}
-  Given \adv~against unforgeability of \CUASRAC as defined in
-  \figref{fig:model-rac}, we build an adversary \advB against unforgeability of
-  \CUASGen as defined in \defref{def:forge-uas}.
-
-  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
-  that \adv~wins its game via the winning condition of line 9 in the RAC
-  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
-  that the probability of \adv~winning its game via condition $h_0 \in L$ at
-  line 11 is negligible, due to soundness of the NIZK for $\NIZKRel_{\Sign}$.
-  Moreover, soundness of NIZK for $\NIZKRel^{\Sign}$ as well as one-wayness
-  of $F$ ensure that, if $h_1 \notin L$, then $b_1 = 1$. Namely, even when given
-  $F(V,\cidi),F(V,\cidu)$ for a credential identified by $(\cidi,\cidu)$ owned
-  by an honest user, and some (potentially malicious) $V$, it is not possible to
-  generate $F(V',\cidi)$ nor $F(V',\cidu)$, for $V'=V$.
-  % 
-  \qed
-\end{proof}
-
-\subsection{Security of \CUASMPS}
-
-As stated, we restrict to privacy-1 of MPS (although, as discussed, we actually
-achieve something slightly stronger). Unforgeability-1 in MPS is
-implied by unforgeability in \UAS (where the latter also covers unforgeability
-of \fissue evaluations, plus verifiable openings). Unforgeability-2 in MPS is
-equivalent to non-frameability in \UAS (where the latter also includes
-framing via verifiable openings). Finally note that, in UAS, we do not
-explicitly model extractability, but rather make it an inherent requirement in
-the unforgeability and non-frameability definitions. Thus, our \CUASMPS
-construction also ensures MPS-extractability.
-
-\begin{theorem}[Privacy-1 of \CUASMPS]
-  If the base \CUASGen construction has signature anonymity according to
-  \defref{def:sign-anonymity-uas}, then \CUASMPS satisfies privacy-1
-  according to \cite{ngsy22}.
-\end{theorem}
-
-\begin{proof}  
-  Note that the privacy-1 game in MPS and the signature anonymity game in \UAS
-  are, in essence, equivalent. Thus, given an adversary \adv~that breaks
-  privacy-1 of \CUASMPS as defined for MPS, it is easy to build an adversary
-  \advB breaking signature anonymity of the underlying \CUASGen, as defined in
-  \UAS.
-
-  \advB simply leverages its own oracles in order to answer oracle queries from
-  \adv: $\mathcal{O}_{read},\mathcal{O}_{write},\mathcal{O}_{CU},\mathcal{O}_{HU},
-  \mathcal{O}_{sig},\mathcal{O}_{open}$ in MPS correspond to \RREG, \WREG,
-  \CUGEN, \HUGEN, \SIGN and \OPEN in \UAS, respectively. The output given by
-  \adv~in the first stage of the MPS game is then directly used as input to
-  \advB's \CHALb oracle. Finally, \advB outputs whatever \adv~outputs.
-
-  Since the simulation is direct, it is easy to see that, whenever \adv~wins,
-  so does \advB.
-  % 
-  \qed
-\end{proof}
-
-\begin{theorem}[Extractability of \CUASMPS]
-  If the base \CUASGen construction has non-frameability according to
-  \defref{def:frame-uas}, then \CUASMPS is an extractable MPS scheme.
-\end{theorem}
-
-\begin{proof}  
-  The proof is direct, as the winning conditions in the extractability
-  experiment in MPS are also winning conditions in the non-frameability
-  experiment for \UAS. That is, an adversary \adv~against extractability of
-  \CUASMPS, as defined in MPS, can be used to build an adversary \advB breaking
-  non-frameability of \CUASGen, as defined in the \UAS model.
-
-  \advB simulates \adv's game essentially as in the privacy-1 proof. Note also
-  that \adv~receives the issuer's secret key. This can be obtained by \advB via
-  its \ICORR oracle. Eventually, \adv~outputs a $(F,M,\Sigma)$ tuple, which
-  corresponds to $(\feval^{g,MPS},\msg,\Sig)$ (with $g=F$ in MPS) in \CUASGen,
-  which \advB outputs in its own game. In addition, \advB outputs as $(\yinsp,
-  \pi)$ values the output of \Open over $(\Sig,\msg)$ -- which internally
-  computes $\finsp^{h,MPS}$, for $h=G$ in MPS.
-  % 
-  Note that the $\feval^{g,MPS}$ and $\finsp^{h,MPS}$ functions in \CUASMPS
-  mimic the behaviour of MPS's $F$ and $G$, respectively. Thus, if \adv wins
-  because $F$ returns $0$ when evaluated on the extracted values, then \advB
-  wins at line 7 of the non-frameability game, as a legitimately computed
-  $\feval^{g,MSP}$ function cannot output $0$. Similarly, if \adv~wins because
-  the value returned by an honestly computed open function over the adversarial
-  $(F,M,\Sigma)$ tuple does not match the output of $G$ over the extracted
-  values, \advB wins at line 9: note that \advB returns the \yinsp value that
-  \Open outputs (when computed honestly over \adv's output), whereas
-  $\finsp^{g,MSP}=G$; thus, if both values differ in \adv's game, then they also
-  differ in \advB's game.
-  %
-  \qed
-\end{proof}
-
-\begin{theorem}[Unforgeability-1 of \CUASMPS]
-  If the base \CUASGen construction is unforgeable according to
-  \defref{def:forge-uas}, then \CUASMPS satisfies unforgeability-1 as defined in
-  \cite{ngsy22}.
-\end{theorem}
-
-\begin{proof}
-  Given an adversary \adv~against unforgeability-1 of \CUASMPS, as defined in
-  the MPS model, we build \advB that breaks unforgeability of the underyling
-  \CUASGen, as defined for \UAS.
-
-  Simulation of \adv's oracles by \advB is again direct (as in previous proofs).
-  Now, suppose that \adv~wins -- i.e., the identity extracted by \adv~does not
-  belong to the set of corrupt users in \adv's game. By construction of \advB
-  (identities in \adv's game map to a $\cid$ for \advB), $\OWNR[\cid] \notin
-  \CU$ in \advB's unforgeability game either.
-  % 
-  However, in order for \advB to win in its own game, we need to prove also that
-  the produced identity does not belong to a user in \HU either. Suppose that it
-  does. Simulation extractability ensures that the credentials extracted by
-  \adv~all belong to the same user (by assumption, in \HU) -- i.e., they are
-  bound to its \usk. Moreover, since \adv~wins its game, the signature output by
-  \adv~has not been obtained via its \SIGN oracle. But, given that the user is
-  honest, its \usk has been produced uniformly at random, and has not been
-  leaked to \adv~(as the issuer is also honest). Thus, the probability that
-  the extracted credentials belong to an honest user is negligible and, if
-  \adv~wins its game, \advB also does.
-  %
-  \qed
-\end{proof}
-
-\begin{theorem}[Unforgeability-2 of \CUASMPS]
-  If the base \CUASGen construction has non-frameability according to
-  \defref{def:frame-uas}, then \CUASMPS satisfies unforgeability-2 as
-  defined in \cite{ngsy22}.
-\end{theorem}
-
-\begin{proof}
-  Given an adversary \adv~against unforgeability-2 of \CUASMPS, as defined in
-  the MPS model, we build \advB that breaks non-frameability of the underyling
-  \CUASGen, as defined for \UAS.
-
-  Simulation of \adv's oracles by \advB is as in the unforgeability-1 proof.
-  \advB outputs whatever \adv~outputs, adding a $(\yinsp,\iproof)$ pair, honestly
-  generated from \adv's output. Note that the winning condition of \adv~
-  requires that the produced signature belongs to an honest user, without
-  having been produced via a call to the signing oracle. By construction of
-  \advB, this directly makes \advB win in line 11 of the non-frameability game.
-  %
-  \qed
-\end{proof}
-
 %%% Local Variables:

### 2022-09-19 prism-backend/research/gsac/formal-uas.tex
Completed in-depth pass. Some changes pending.

@@
 The main contribution of this section is giving a simple syntax and model that
-still allow spanning a wide variety of related schemes. We combine aspects of GS
-and AC schemes, generalizing whenever possible. Like in ACs, there are multiple
-issuers, and each user can get one or more credentials from any of them; and,
-also, use more than one credential simultaneously to produce a signature. We
-incorporate openers, as in GSs, but there is no tight relationship between
-issuer and opener. As a consequence, users (potentially along with verifiers)
-may choose, on a per-signature basis, the policies governing the utility
-information extractable from a signature. Finally, we incorporate functions that
-allow tweaking the conditions checked at credential issuance and signature
-generation times, including the information that an opener will be able to
-extract from a signature.
-
-\paragraph{Users and credentials.} %
-In our model, every single user may have multiple credentials. In this
-setting, a perhaps too strict assumption we make is that, once a user gets
-compromised, all of the credentials owned by that user are compromised too.
-While there may be real world situations for which this is too aggressive, it is
-certainly a worst-case scenario, and greatly simplifies the modelling.
-%
-% Somehow related, we model a scheme in which users generate their secret keys in
-% a standalone way, and then leverage these keys to request credentials. This may
-% seem too ideal as a model for real world situations, as we cannot know how
-% many keys a user has generated. However, we argue that this can in fact be very
-% close to reality, where a well-known issuer, after properly identifying a user,
-% attests the (possibly blinded) public key this user proves control of. Indeed,
-% our model and syntax support exactly this approach, by allowing users to
-% leverage previously obtained credentials in order to request new ones.
-% A consequence of this is that, if ``one user'' generates (e.g.) two keys, and
-% then uses each of these keys to request multiple credentials, then from the
-% point of view of our modelling, we see this \emph{cryptographically} as two
-% different users -- and, anyway, that same ``user'' cannot combine credentials
-% bound to different keys.
-
-\paragraph{Users and issuers.} %
-A relevant aspect of our model is that users and issuers are basically the
-same: an entity with a key pair. The difference is that, when users wish to
-become issuers, they advertise their public keys, along with their conditions
-for granting credentials. To simplify, we just assume that they somehow
-``publish their public keys'', which can be done in several ways in practice.
-
-\paragraph{Functional placeholders.} %
-We use generic functions to capture, at the design level, that users need
-to prove concrete claims over their private information. Looking a bit ahead,
-the output of these functions is defined in terms of (subsets of) the users'
-key, credentials and attributes, and signed message. But, during our modelling,
-we are only concerned with preventing that the output of these functions can
-be altered, and with ensuring that it does not threaten privacy beyond what is
-necessary or unavoidable to reach the flexibility we want.
+still allow spanning a wide variety of related schemes. This is in part
+achieved by combining aspects of GS and AC schemes. Yet, the main tool for
+generalisation are three functional placeholders, governing the conditions to be
+checked during issuance, the information to be revealed alongside signatures,
+and extractable from them. However, at the modelling level we are not concerned
+with the ``code'' of these functions, but only with the correctness of their
+computation, and with capturing security and privacy despite introducing
+configurable functions.
+
+% \paragraph{Users and credentials.} %
+% In our model, every single user may have multiple credentials. In this
+% setting, a perhaps too strict assumption we make is that, once a user gets
+% compromised, all of the credentials owned by that user are compromised too.
+% While there may be real world situations for which this is too aggressive, it is
+% certainly a worst-case scenario, and greatly simplifies the modelling.
+% %
+% % Somehow related, we model a scheme in which users generate their secret keys in
+% % a standalone way, and then leverage these keys to request credentials. This may
+% % seem too ideal as a model for real world situations, as we cannot know how
+% % many keys a user has generated. However, we argue that this can in fact be very
+% % close to reality, where a well-known issuer, after properly identifying a user,
+% % attests the (possibly blinded) public key this user proves control of. Indeed,
+% % our model and syntax support exactly this approach, by allowing users to
+% % leverage previously obtained credentials in order to request new ones.
+% % A consequence of this is that, if ``one user'' generates (e.g.) two keys, and
+% % then uses each of these keys to request multiple credentials, then from the
+% % point of view of our modelling, we see this \emph{cryptographically} as two
+% % different users -- and, anyway, that same ``user'' cannot combine credentials
+% % bound to different keys.
+
+% \paragraph{Users and issuers.} %
+% A relevant aspect of our model is that users and issuers are basically the
+% same: an entity with a key pair. The difference is that, when users wish to
+% become issuers, they advertise their public keys, along with their conditions
+% for granting credentials. To simplify, we just assume that they somehow
+% ``publish their public keys'', which can be done in several ways in practice.
 
@@
 
-An \UAS scheme is composed by the following algorithms:
+Users generate their key pair, and then optionally advertise
+their public key and conditions for issuance in order to become issuers. When
+openers generate their key pairs, they include the function they will apply to
+anonymous signatures. Users can later leverage (one or more of) their
+credentials to request new ones, or to produce an anonymous signature. Issuance
+only succeeds if the user's credentials (if any) meet the issuer's requirements.
+Signatures may directly output some information derived from the user's data.
+Also, each signature has a selected opener (probably, by the user and/or
+verifier), who can later \emph{extract only the information that is defined by
+  the chosen opener's key}. When openers extract their information, they also
+prove the correctness of the result.
+
+In detail, an \UAS scheme is composed by the following algorithms:
 
@@
 \item[$\langle
-  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
-  \Issue(\isk,\cidi,\sipk,\attrs))  
+  \Obtain(\usk,\ipk,\sCred,\attrs),
+  \Issue(\isk,\sipk,\attrs))  
   \rangle \rightarrow \langle \Cred/\bot,R/\bot
@@
   outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
-  the \fissue function defined by the issuer, and $\utrans$ being the transcript
-  of the communication.
+  the \fissue function defined by the issuer, and $\utrans=(U,I)$ being the
+  transcript of the communication, where $U$ contains the messages sent by
+  the user, and $I$ those sent by the issuer.
 \item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
@@
 \paragraph{Issuance, evaluation, and opening functions.} %
-We introduce three functions in our syntax and model. Through them, it is
-possible to modulate the behaviour of the resulting instantiation, by
-controling the conditions upon which a new credential can be issued, the
-information revealed at signing time, or after signing. In all cases, it is
-the user who computes them, and has to prove correctness of such computation.
-We give concrete examples in \secref{sec:relationships}.
+These are the functional placeholders that allow modulating the behaviour of the
+resulting instantiation, by controling the conditions upon which new credentials
+can be issued, the information revealed at signing time, or extractable from
+signatures. In all cases, the user who computes them, and proves correctness of
+such computation. We give concrete examples in \secref{sec:relationships}.
 
@@
 \item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
-  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
+  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions (or, simply,
+  evaluation functions), from a
   family of functions \famfeval, can be set on a per-signature basis. They
@@
 governs the information that may be revealed after signing, and is defined by
-openers when they set up their key pair. Thus even though signers and verifiers
-may negotiate to use any opener for a given signature, it is not possible for
-an opener to change the chosen function.
+openers when they set up their key pair.
 
@@
 functions. Security of \CUASGen implies security of its restrictions, if
-the chosen \fissue functions are \CUASGen-acceptable.
+the chosen \fissue function is \CUASGen-acceptable.
 
@@
 requires that \UAS schemes ensure that the claims used to support a credential
-request cannot be falsified, and that no adversary is able to falsify
-the correctness proofs for the claims included in the signatures. In addition,
-we require all credentials involved in the corresponding process to be
-associated to a known user key. Finally, \UAS schemes inherit the useful
+request cannot be falsified, and that no adversary is able to falsify the
+correctness proofs for the claims included in the signatures. In addition, we
+require all credentials involved in the corresponding process to be associated
+to the same, and known, user key. Finally, \UAS schemes inherit the useful
 non-frameability property of GS schemes where even the issuer is corrupt. In
@@
 and for openers, \oid. Although issuers are ``extended'' users, and thus can be
-identified by their \uid, we also sometimes use \iid to refer to a user acting
-as issuer, especially, for operations involving both a user and an issuer (this
-also applies for key pairs).
+identified by their \uid, we mostly use \iid to refer to a user acting as
+issuer, especially, for operations involving both a user and an issuer.
 %
@@
   corrupt {\uid}s/{\iid}s/{\oid}s.
-\item[\UK,\IK,\OK.] Tables maintaining key pairs of users $(\upk,\usk)$, issuers
-  $(\ipk,\isk)$, and openers $(\opk,\osk)$. They are indexable by \uid,
-  \iid, and \oid, respectively. Also, issuers' public keys contain their \fissue
-  function, and openers' public keys contain their \finsp function.
+\item[\UK,\IK,\OK.] Tables storing key pairs of users $(\upk,\usk)$, issuers
+  $(\ipk,\isk)$, and openers $(\opk,\osk)$, indexable by \uid, \iid, and \oid,
+  respectively. Issuers' public keys contain a \fissue function, and
+  openers' public keys contain a \finsp function.
 \item[\PUBUK,\PUBIK,\PUBOK and \PRVUK,\PRVIK,\PRVOK.] Shorthands referring to
@@
   keys ($\mathsf{SXK}$).
-\item[\CRED.] Stores information related to credentials obtained by users in
-  the system. Thus, it is indexable by \cid. More specifically, it stores
+\item[\CRED.] Indexable by \cid, it stores
   tuples of the form $(\uid,\cred,\iid,\attrs,n,\lbrace (\cid_i,\iid_i)
@@
 \item[\CCRED.] Like \CRED, but tracks challenge credentials.
-\item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
+\item[\OWNR.] When we write $\OWNR[\cid]$ we mean
   ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$'', or
-  $\bot$ if there is no wuch \uid. We may also use \OWNR over a set of {\cid}s
-  (\scid). In that case, our convention is that $\OWNR[\scid]$ returns $\bot$ if
+  $\bot$ if there is no wuch \uid. We also use \OWNR over a set of {\cid}s
+  (\scid). In that case, $\OWNR[\scid]$ returns $\bot$ if
   not all passed {\cid}s belong to the same \uid. Since $\bot$ is not a valid
@@
   users equal false if \OWNR returns $\bot$.
-\item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
+\item[\ATTR.] When we write $\ATTR[\cid]$ we mean
   ``\attrs such that $\CRED[\cid] = (\cdot,\cdot,\cdot,\attrs,\cdot,\cdot)$''.
-\item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
+\item[\ISR.] When we write $\ISR[\cid]$ we mean
   ``\iid such that $\CRED[\cid] = (\cdot,\cdot,\iid,\cdot,\cdot,\cdot)$''.
@@
 \item[\OGEN.] Adds a new opener to the game, generating its key pair and
-  setting its evaluation and inspection functions.
+  setting its evaluation and opening functions.
 % \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
@@
 
-        \procedure{$\OBTISS(\stackrel{\cid}{\pcbox{(\cidi,\cidu)}},\uid,\iid,\attrs,
-          \lbrace (\cid_i,\iid_i) \rbrace_{i \in [n]})$}{%
+        \procedure{$\OBTISS(\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
+          \rbrace_{i \in [n]})$}{%
           \pcif \uid \notin \HU \lor \iid \notin \HI: \pcreturn \bot \\
           \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\          
+          \langle \Cred, R \rangle \gets
+          \langle \Obtain(\UK[\uid]\CRED[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs), \\
+          \hspace*{50pt} \Issue(\PRVIK[\iid],\ISR[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs)
+          \rangle \\
+          (\cid = (\cidi,\cidu),\cdot,\cdot,\cdot) \gets \Cred \\
           \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot:
           \pcreturn \bot \\
-          \langle \Cred, R \rangle \gets
-          \langle \Obtain(\UK[\uid],\cidu,\CRED[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs), \\
-          \hspace*{50pt} \Issue(\PRVIK[\iid],\cidi,\ISR[\lbrace \cid_i\rbrace_{i\in[n]}],\attrs)
-          \rangle \\
           \trans[\cid] \gets R \\
@@
 
-        \procedure{$\ISSUE(\cidi,\uid,\iid,\attrs,\siid=
+        \procedure{$\ISSUE(\uid,\iid,\attrs,\siid=
           \lbrace \iid_i\rbrace_{i\in[n]})$}{%
           \pcif \uid \notin \CU \lor \iid \notin \HI: \pcreturn \bot \\          
+          \langle \cdot, R \rangle \gets
+          \langle \adv, 
+          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
+          (\cdot,\cdot,(\cidi,\cdot)) \gets R \\
           \pcif \CRED[(\cidi,\cdot)] \neq \bot \lor \CCRED[(\cidi,\cdot)]
@@
           \pcind \pcreturn \bot \\          
-          \langle \cdot, R \rangle \gets
-          \langle \adv, 
-          \Issue(\PRVIK[\iid],\cidi,\siid,\attrs) \rangle \\
           \trans[(\cidi,\cdot)] \gets R \\
@@
 
-        \procedure{$\OBTAIN(\cidu,\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
+        \procedure{$\OBTAIN(\uid,\iid,\attrs,\lbrace (\cid_i,\iid_i)
           \rbrace_{i\in[n]})$}{%
@@
           \pcif \exists i \in [n]~\suchthat~\cid_i \in \CCRED: \pcreturn \bot \\
+          \pcind \pcreturn \bot \\
+          \langle \Cred, \cdot \rangle \gets
+          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\lbrace \cid_i\rbrace_{[n]},
+          \attrs),\adv \rangle \\
+          (\cid = (\cdot,\cidu), \cdot,\cdot,\cdot) \gets \Cred \\
           \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor \CCRED[(\cidu,\cdot)] \neq
           \bot: \\          
-          \pcind \pcreturn \bot \\
-          \langle \Cred, \cdot \rangle \gets
-          \langle \Obtain(\UK[\uid],\cidu,\PUBIK[\iid],\lbrace \cid_i\rbrace_{[n]},
-          \attrs),\adv \rangle \\
           \CRED[(\cdot,\cidu)] \gets (\uid,\cred,\iid,\attrs,n,\lbrace(\cid_i,
@@
 
-        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,
-          \stackrel{\cscid_{0,1}}{\pcbox{\lbrace(\ccid_{0,i},\ccid_{1,i})
-            \rbrace_{i\in[n]}}})$}{%
+        \procedure{$\OBTCHALb(\cuid_{0,1},\iid,\attrs,
+          \stackrel{\cscid_{\lbrace 0,1 \rbrace}}
+          {\pcbox{\lbrace(\ccid_{0,i},\ccid_{1,i})\rbrace_{i\in[n]}}})$}{%
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
           \pcif \iid \notin \CI: \pcreturn \bot \\
-          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor
-          \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
           \pcif \exists i\in[n]~\suchthat~
@@
           \pcind \pcreturn \bot \\          
+          \langle \Cred, \cdot \rangle \gets
+          \langle \Obtain(\PRVUK[\cuid_b],\PUBIK[\iid],\cscid_b,\attrs),
+          \adv \rangle \\
+          (\cid = (\cidi,\cidu),\cdot,\cdot,\cdot) \gets \Cred \\
           \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
-          \pcif 0(\fissue(\PUBUK[\cuid_0],(\cdot,\cidu),\attrs,\lbrace (\ccid_{0,i},\ATTR[\ccid_{0,i}])\rbrace_{i\in[n]})) \neq \\
-          \pcind 0(\fissue(\PUBUK[\cuid_1],(\cdot,\cidu),\attrs,\lbrace (\ccid_{1,i},\ATTR[\ccid_{1,i}])\rbrace_{i\in[n]})): \\
+          \pcif 0(\fissue(\PUBUK[\cuid_0],\cid,\attrs,\lbrace
+          (\ccid_{0,i},\ATTR[\ccid_{0,i}])\rbrace_{i\in[n]})) \neq \\
+          \pcind 0(\fissue(\PUBUK[\cuid_1],\cid,\attrs,\lbrace
+          (\ccid_{1,i},\ATTR[\ccid_{1,i}])\rbrace_{i\in[n]})): \\
           \pcind \pcreturn \bot \\          
-          \langle \Cred, \cdot \rangle \gets
-          \langle \Obtain(\PRVUK[\cuid_b],\cidu,\PUBIK[\iid],\cscid_b,\attrs),
-          \adv \rangle \\
+          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor
+          \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\          
           \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
@@
 
-        \procedure{$\CHALb(\oid,\stackrel{\cscid_{0,1}}{\pcbox{
+        \procedure{$\CHALb(\oid,\stackrel{\cscid_{\lbrace 0,1 \rbrace}}{\pcbox{
             \lbrace (\ccid_{0,i},\ccid_{1,i})
@@
 we use to formalize security of \UAS schemes. We introduce them here, and define
-they later for our construction.
+them later for our construction.
 
@@
   and returns the credential set \sCred, if any, involved in the request. It
-  needs an honest issuer as, otherwise, the transcripts won't be available. 
+  requires honest issuers for the transcripts to be available. 
 \item[$\ExtractSign(\trap,\opk,\lbrace \ipk_i \rbrace_{i \in [n]},\Sig,\msg,
   \feval) \rightarrow (\upk,\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
-  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives a trapdoor \trap, a signature
-  \Sig, the opener public key \opk, and the public keys $\ipk_i$
-  issuers of the credentials used to produce the signature over \msg, and for
-  \feval. It outputs the user secret key and credential set \sCred used to
-  generate the signature, and the $\yeval^1$ and \yinsp values. For notational
-  convenience, we overload this function and use \oid and \iid instead of the
-  actual keys.
+  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives trapdoor \trap, signature
+  \Sig over \msg and for \feval, opener public key \opk, and public keys
+  $\ipk_i$ from the issuers of the credentials used to produce \Sig. It outputs
+  the user secret key and credential set \sCred used to generate the signature,
+  and the $\yeval^1$ and \yinsp values. For notational convenience, we overload
+  this function and use \oid and \iid instead of the actual keys.
 % \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
@@
 Security of an \UAS scheme is defined in terms of anonymity, unforgeability and
-non-frameability. We now introduce and formally define the corresponding
-properties.
+non-frameability, which we formally define now.
+
 % In addition, we define two auxiliary properties for defining
@@
 
-The issuance anonymity game captures that, during credential issuance
-interactions, the adversary gains no information about the
-user(s) behind them. For this, we allow the adversary to control targetted
-issuers and openers (although it may also add honest ones), and add honest and
+Issuance anonymity captures that, during credential issuance
+interactions, the adversary gains no information about the user(s) behind them,
+beyond what is leaked by the policies required for issuance. For this, we allow
+the adversary to control targetted issuers and openers, and add honest and
 corrupt users. The adversary can also obtain credentials, produce signatures,
-and open them. We need to make some limitations to prevent trivial wins: first,
-when querying the oracle for obtaining a challenge credential out of two
-possible user-credential set pairs, the issuance protocol must either succeed or
-fail for both; also, the adversary cannot mix challenge and non-challenge
-credentials in the same call to the \SIGN oracle -- but can otherwise open
-any signature. With these restrictions, if the adversary cannot distinguish
-arbitrary runs with all oracles when he gets challenge credentials
-$\cred_b$, from runs with credentials $\cred_{1-b}$, then the issuance protocol
-is privacy-preserving.
+and open them. To prevent trivial wins: (1) when querying the oracle for
+obtaining a challenge credential out of two possible user-credential set pairs,
+the issuance protocol must either succeed or fail for both; and (2), the
+adversary cannot mix challenge and non-challenge credentials in the same call to
+the \SIGN oracle -- but can otherwise open any signature. With these
+restrictions, if the adversary cannot distinguish arbitrary runs with all
+oracles when he gets challenge credentials $\cred_b$, from runs with credentials
+$\cred_{1-b}$, then the issuance protocol is privacy-preserving.
 
 Signature anonymity captures that the signatures produced by system users do not
-leak information
-about their identity beyond what is already revealed via $\yeval^0$ and what
-may be revealed via \yinsp. Concretely, the adversary can interact with oracles
-as in the issuance anonymity game, except that instead of obtaining challenge
-credentials, it obtains challenge signatures. These signatures must have been
-produced via the \CHALb oracle, which ensures that the $\yeval^0$ value is the
-same for both input sets -- otherwise, rejects creating the signature. We also
-allow opening signatures; even challenge $\cSig_b$ signatures, as long as the
-\yinsp value of the counterpart $\cSig_{1-b}$ is the same. Note that this is
-stronger than the traditional CCA-like security of group signatures, where no
-challenge signature can be open.
+leak information about their identity beyond what is already revealed via
+$\yeval^0$ and what may be revealed via \yinsp. Concretely, the adversary can
+interact with oracles as in the issuance anonymity game, except that instead of
+obtaining challenge credentials, it obtains challenge signatures. These
+signatures are produced via the \CHALb oracle, which ensures that the $\yeval^0$
+value is the same for both input sets -- otherwise, rejects creating the
+signature. We also allow opening signatures; even challenge $\cSig_b$
+signatures, as long as the \yinsp value of the counterpart $\cSig_{1-b}$ is the
+same. Note that this is stronger than the traditional CCA-like security of group
+signatures, where no challenge signature can be open.
 
@@
 attributes -- although, in \UAS, claims can be proven at issuance time, and
-at signing time; from GS schemes, that only credential owners can produce valid
-signatures. \UAS also has verifiable openings, and we must ensure that the
-values output by \Open are correct and trace back to a user with consistent
-credentials. All the previous is captured by an unforgeability property. We
-define it by allowing the adversary to call any oracle, except the one for
-corrupting issuers. The adversary wins if it produces a valid signature that:
-(1) the produced signature leveraged a credential for
+at signing time; from GS schemes, it inherits that only credential owners can
+produce valid signatures. \UAS also has verifiable openings, and we must ensure
+that the values output by \Open are correct and trace back to a user with
+consistent credentials. All the previous is captured by an unforgeability
+property. We define it by allowing the adversary to call any oracle, except the
+one for corrupting issuers. The adversary wins if it produces a valid signature
+that:  (1) the produced signature leveraged a credential for
 which the conditions required by \fissue were not satisfied; (2), opens to a
@@
 it can be perfectly valid to have a signature produced by a corrupted user
-output the same \yeval or \yinsp values than the ones output when evaluating or
+output the same \Yeval or \yinsp values than the ones output when evaluating or
 opening a signature by an honest user.
@@
 included in user credentials, the adversary may even be able to just produce
-``legitimate'' openings that output any desired value. Note anyway that this is
+``legitimate'' openings to any desired value. Anyway, this is
 a relevant property, as it tells us the minimal unforgeability expectations we
@@
 In this section, we give a generic construction of an \UAS scheme, based on
-generic building blocks. We use three different NP relations:
-\RelIss, \RelSig, and \RelIns, described next
-and specified in CS notation \cite{cs97} in \figref{fig:nizkrels}.
+generic building blocks. We use three different NP relations: \RelIss, \RelSig,
+and \RelIns, described next and specified in CS notation \cite{cs97} in
+\figref{fig:nizkrels}. Crucially, these relations include verifying that the
+comptuation of the \fissue, \feval and \finsp functions has been done correctly.
 
@@
 \item[\RelSig:] For NIZK proofs at signing time. Ensures that
-  signatures ``encode'' the correct signature evaluation and opening values, and
-  that any credential used to create the signature is bound to the same \upk.
+  signatures encode the correct signature evaluation (computed via \feval)
+  and opening values (computed via \finsp), and all the involved
+  credentials are bound to the same \upk.
 \item[\RelIns:] For NIZK proofs at opening time. Ensures that the
-  utility information extracted by the \Open algorithm is correct.
+  utility information extracted by the opener, via the \Open algorithm, is
+  correct.
 \end{description}
@@
 \paragraph{$\parm \gets \Setup(\secpar)$.} %
-The setup process essentially generates the public parameters for all the
-building blocks. It runs $\Cparm \gets \CSetup(\secpar)$, $\SBCMparm \gets
-\SBCMSetup(\secpar)$, $\Eparm \gets \ESetup(\secpar)$, $\NIZKcrs_{\Issue} \gets
-\NIZKSetup^{\NIZKRel_{\Issue}}(\secpar)$, $\NIZKcrs_{\Sign} \gets
-\NIZKSetup^{\NIZKRel_{\Sign}}(\secpar)$, and $\NIZKcrs_{\Open} \gets
-\NIZKSetup^{\NIZKRel_{\Open}}(\secpar)$. Return $(\Cparm,\SBCMparm,\Eparm,
-\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Open})$.
+Essentially generates the public parameters for all the building blocks. It runs
+$\SBCMparm \gets \SBCMSetup(\secpar)$, $\Eparm \gets \ESetup(\secpar)$,
+$\NIZKcrs_{\Issue} \gets \NIZKSetup^{\NIZKRel_{\Issue}}(\secpar)$,
+$\NIZKcrs_{\Sign} \gets \NIZKSetup^{\NIZKRel_{\Sign}}(\secpar)$, and
+$\NIZKcrs_{\Open} \gets \NIZKSetup^{\NIZKRel_{\Open}}(\secpar)$. Return
+$(\SBCMparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Open})$.
 
@@
 \paragraph{$(\upk,\usk) \gets \KeyGen(\parm)$.} %
-Each user first parses \parm as $(\cdot,\SBCMparm,\cdot,\cdot,\cdot,\cdot)$.
+Each user first parses \parm as $(\SBCMparm,\cdot,\cdot,\cdot,\cdot)$.
 Then, runs $(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$, $\upk \gets (\parm,
@@
 \paragraph{$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.} %
-Each opener parses \parm as $(\cdot,\cdot,\Eparm,\cdot,\cdot,\cdot)$.
+Each opener parses \parm as $(\cdot,\Eparm,\cdot,\cdot,\cdot)$.
 Then, runs $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, and sets, $\opk \gets (\Eek,
@@
 \yinsp by running $\cinsp \gets \EEnc(\Eek,\yinsp; r')$ for some fresh
-randomness $r'$. Finally, the user
-computes $\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,
-\lbrace(\cid_i,\cattrs_i,\cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r),(\msg,
+randomness $r'$. Finally, the user computes $\NIZKproof \gets
+\NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\upk,\usk,\lbrace(\cid_i,
+\cattrs_i,\cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r,r'),(\msg,
 \feval,\yeval^0,\cinsp,\lbrace \ipk_i\rbrace_{i\in[n]},\Eek))$ and outputs
@@
 (\opk,\sipk, \Sig,\msg,\feval)$. If verification succeeds, it parses
-\Sig as $(\sig=(\NIZKproof,\cinsp),\yeval)$, decrypts \Ec by running $\yinsp
+\Sig as $(\sig=(\NIZKproof,\cinsp),\yeval)$, runs $\yinsp
 \gets \EDec(\osk,\cinsp)$, and computes $\NIZKproof_{\Open} \gets
@@
 targets the non-interactive approach. Now, we sketch how to transform this into
-an interactive protocol that ensures replay protection.
+an interactive protocol with replay protection.
 

### 2022-09-19 prism-backend/research/gsac/introduction-paper.tex
Minor changes.
Completed in-depth pass. Some changes pending.

@@
 users, proves correctness of the utility information extractable after signing.
-The latter is, in addition, fed and modulated with the output of \feval. Through
-these functions, we define NP statements that need to be proven by different
+The latter is, in addition, fed and modulated with the output of \feval. With
+these functions, we allow achieving configurable utility-vs-privacy tradeoffs
+throughout the whole ``lifecycle'' (from issuance to opening). They also take
+a central role in defining the NP statements that need to be proven by different
 algorithms/protocols, summarised in \figref{fig:proof-blocks-uas}.
@@
     parenthesis we show the adopted reference model, and the section offering
-    full detail.}
+    full detail. \CUASGenInt and \CUASGenHideIss are variations of \CUASGen,
+    described in \secref{sec:formal-uas}.}
   \label{fig:relations}

### 2022-09-19 prism-backend/research/gsac/relationships.tex
Updated GS-MDO and DAC appendices.
Completed in-depth pass. Some changes pending.

@@
 \UAS-acceptable. Specifically, $\fissue^1$ and $\fissue^{\sring}$ are trivially
-\UAS-acceptable (for $\rngfissue = \bin$); whereas $\fissue^{single,F,I}$ is
+\UAS-acceptable (for $\rngfissue = \bin$); whereas $\fissue^{single,H,I}$ is
 \UAS-acceptable if $F$ is a secure PRF \cite{kl14}.
@@
 \begin{figure}[ht!]
+  \centering
+  \scalebox{0.85}{
     \input{figures/functions.tex}
+  }
   \caption{Functions for the \CUASGen restrictions described next.
@@
   \centering
-  \scalebox{0.9}{      
+  \scalebox{0.85}{      
     \begin{minipage}[t]{0.45\textwidth}        
@@
         \pcif \Verify(\gpk,\msg,\sig) = 0: \pcreturn 0 \\
-        \pcreturn (\upk \in \HU \land \PRVUK[\upk] \neq \bot \land
-        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1)~\land \\
+        \pcreturn \upk \in \HU \land \PRVUK[\upk] \neq \bot \land
+        \Judge(\gpk,\upk,\msg,\sig,\tau) = 1~\land \\
         \pcind \adv~\textrm{did not query}~USK(\upk)~\textrm{or}~
@@
   }
-  \scalebox{0.9}{      
+  \scalebox{0.85}{      
     \begin{minipage}[t]{.55\textwidth}
@@
         (\upk, \tau) \gets \Open(\gpk,\osk,\trans,\msg,\sig) \\
-        \pcif \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
-        = 0: \\ 
-        \pcind \pcreturn 1 \\
-        \pcreturn 0
+        \pcreturn \upk \notin \HU \cup \CU \lor \Judge(\gpk,\upk,\msg,\sig,\tau)
+        = 0
       }       
@@
 \subsubsection{\CUASGS construction.} %
-We show that the $(\fissue^{single,F,I},\feval^0,\finsp^{\upk})$-\CUASGen
+We show that the $(\fissue^{single,H,I},\feval^0,\finsp^{\upk})$-\CUASGen
 restriction, is a secure group signature scheme according to \cite{bsz05}.
-As stated, the $\fissue^{single,F,I}$ is an \UAS-acceptable function if $F$ is a
+As stated, $\fissue^{single,H,I}$ is an \UAS-acceptable function if $F$ is a
 PRF. In that case, its output is a random-looking string that depends on the
@@
 list of received $\yissue = F(\upk,I)$ values, and rejects issuing a credential
-for already existing \yissue values. From this, the GS algorithms are as
+for already existing ones. From this, the GS algorithms are as
 follows:
@@
 \item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs \Setup from \CUASGen,
-  and one instance of \KeyGen and \ISet with $\fissue^{single,F,I}$ (both for
+  and one instance of \KeyGen and \ISet with $\fissue^{single,H,I}$ (both for
   the same user, who will be the only issuer in the GS scheme) and \OKeyGen.
@@
   \centering
-  \scalebox{0.9}{      
+  \scalebox{0.85}{      
     \begin{minipage}[t]{0.55\textwidth}        
@@
   }
-  \scalebox{0.9}{      
+  \scalebox{0.85}{      
     \begin{minipage}[t]{.5\textwidth}
@@
 \subsubsection{\CUASRing Construction.} %
-Building a ring signature scheme according to the model in \figref{fig:model-rs}
-is essentially a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
-of our \CUASGenHideIss construction. In a nutshell, we let users self-issue
+We can use a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
+of \CUASGenHideIss to build a ring signature scheme according to the model
+in \figref{fig:model-rs}. In a nutshell, we let users self-issue
 credentials where the attributes are (a subset of encodings of) the public keys
@@
 \item[$((\pk_1,\sk_1),...,(\pk_n,\sk_n)) \gets KeyGen(\secpar)$.] Runs
-  $\parm \gets \Setup(\secpar)$ from \CUASGenHideIss. Then, for each of
+  $\parm \gets \Setup(\secpar)$ from \CUASGenHideIss. For each of
   the $i \in [n]$ users to generate, run $(\upk_i,\usk_i) \gets \KeyGen(\parm)$,
@@
   The signing user, with $\sk_i=\usk$ and $\pk_i=(\ipk_i,\opk)$ for some $i \in
-  [n]$, where $\pk_i \in R$, first acts both as user and issuer to self-issue a
+  [n]$ where $\pk_i \in R$, first acts both as user and issuer to self-issue a
   credential \Cred over an attribute set \attrs such that $\attrs \subseteq
@@
   \centering
-  \scalebox{0.9}{      
+  \scalebox{0.85}{      
     \begin{minipage}[t]{0.5\textwidth}        
@@
 
-\subsection{Revocable Anonymous Credentials}
-\label{ssec:related-models-rac}
-
-In \cite{cks10,ckl+15}, revocable anonymous credentials are proposed. We first
-give a simple model in \figref{fig:model-rac}, extending that in
-\secref{ssec:related-models-ac}. Concretely, to the functionality in
-\secref{ssec:related-models-ac}, we now explicitly add the $OKeyGen$ function,
-which generates the opener key pair, extend $Verify$ to receive also a list $L$
-of revoked credential identifiers, and we add a function (and corresponding
-oracle) $cid/\bot \gets RetrieveCredId(\osk,\utrans)$ that can extract an
-identifier of the credential used in a presentation transcript \utrans. For
-simplicity, we do not include the equivalent to verifiable openings, but this
-would be straightforward.
-
-\begin{figure}[ht!]
-  \centering
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{0.43\textwidth}
-      \procedure[linenumbering]{$\Exp^{anon-b}_{\adv,rac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\opk,\osk) \gets \OKeyGen(\parm) \\        
-        (\ipk,\isk) \gets IssKeyGen(\parm) \\        
-        b^* \gets \adv^{\mathcal{O}_{rac},\oracle{LoR}}(\parm,\ipk,\opk) \\
-        \pcreturn b^*
-      }
-    \end{minipage}
-  }
-  \scalebox{0.9}{      
-    \begin{minipage}[t]{.57\textwidth}
-      \procedure[linenumbering]{$\Exp^{forge}_{\adv,rac}(1^\secpar)$}{%
-        \parm \gets \Setup(1^\secpar) \\
-        (\opk,\osk) \gets \OKeyGen(\parm) \\        
-        (\ipk,\isk) \gets IssKeyGen(\parm) \\
-        (\cid,D,L,\st) \gets
-        \adv^{\mathcal{O}_{rac}}(\parm,\ipk,\opk) \\
-        \langle \cdot,(b_0,\utrans_0)\rangle
-        \gets \langle \adv(\st),\Verify(\ipk,D,L)\rangle \\
-        \langle \cdot,(b_1,\utrans_1)\rangle
-        \gets \langle Show(\ipk,\ATTR[\cid],D,\CRED[\cid]), \\
-        \hspace*{7.25em}\Verify(\ipk,D,L)\rangle \\
-        \pcif \OWNR[\cid] \notin \HU \lor
-        D \not\subseteq \ATTR[\cid]: \pcreturn 0 \\
-        \pcif b_0 = 1 \land \nexists j~\suchthat~(\OWNR[j] \in \CU
-        \land D \subseteq \ATTR[j]): \\
-        \pcind \pcreturn 1 \\
-        h_{\bin} \gets RetrieveCredHandle(\osk,\utrans_{\bin}) \\
-        \pcif h_0 \in L \lor (h_1 \notin L \land b_1 = 0): \pcreturn 1 \\
-        \pcreturn 0
-      }       
-    \end{minipage}      
-  }
-  \caption{Security games for revocable anonymous credentials with selective
-    disclosure based on \cite{fhs19}. 
-    $\mathcal{O}_{rac} \gets \lbrace \oracle{HU},\oracle{CU},\oracle{Obtain},
-    \oracle{Issue},\oracle{ObtIss},\oracle{Show},\oracle{ReqCredHandle}\rbrace$.
-    $\oracle{ReqCredHandle}$ is
-    equivalent to \OPEN, operating on transcripts \utrans instead of signatures
-    but, in addition, keeps a list of revoked users (per verifier), based on the
-    queries it receives. In $\Exp^{forge}_{\adv,rac}$, \adv~wins if it
-    authenticates using a revoked credential or despite not having the required
-    attributes, or if it prevents an honest user from authenticating using a
-    non-revoked credential.}
-  \label{fig:model-rac}  
-\end{figure}
-
-\subsubsection{\CUASRAC Construction.} %
-Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,F,V,L},
-\finsp^{F})$-\CUASGenInt restriction. \feval is defined via a set of
-attributes \dattrs to reveal (e.g., age, etc.), a PRF $F$, a string identifying
-the verifier $V$ and a list $L$ of revocation handles by $V$. Note that,
-these ``extra parameters'' can be hardcoded, though: $F$ can be a fixed PRF for
-all verifiers, \dattrs and $V$ are also fixed (per verifier), and $L$ can be
-updated per verifier with some reasonable frequency -- e.g., daily -- so that
-the cost of recomputing $\feval^{\dattrs,F,V,L}$ is not high.
-%
-Since credentials in \CUASGenInt have two identifiers (\cidi, chosen by the
-issuer; and \cidu, chosen by the user), $\feval^{\dattrs,F,V,L}$ internally
-computes $F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval aborts.
-Otherwise, it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
-$\yeval^1 \gets V$. $\yeval^1$ is
-then used by $\finsp^F$ to compute $\yinsp \gets (F(\yeval^1,\cidi),
-F(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
-it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
-%
-In more detail, the algorithms are as follows:
-
-\begin{description}
-\item[$\parm \gets \Setup(1^\secpar)$.] Runs $\Setup(1^\secpar)$ as in
-  \CUASGenInt.
-\item[$(\ipk,\isk) \gets IssKeyGen(\parm)$.] Runs \KeyGen+\ISet from
-  \CUASGenInt, setting $\fissue^1$ as issuance function.
-\item[$(\ipk,\isk) \gets OKeyGen(\parm)$.] Runs \OKeyGen from \CUASGenInt,
-  setting $\finsp^F$ as opening function.
-\item[$(\upk,\usk) \gets UserKeyGen(\ipk)$.] Runs \KeyGen from \CUASGenInt.
-\item[$\langle \cred/\bot,\top/\bot \rangle \gets
-  \langle \Obtain(\usk,\ipk,\attrs),\Issue(\isk,\upk,\attrs) \rangle$.]
-  Runs the $\langle \Obtain,\Issue \rangle$ protocol from \CUASGenInt, using
-  $\fissue^1$ as issuance function.
-\item[$\langle 1/0,(\yeval,\utrans)/(0,\utrans)\rangle \gets \langle Show(\ipk,
-  \attrs,\dattrs,\cred),
-  \Verify(\ipk,\dattrs) \rangle$.]
-  Runs the interactive $\langle\Sign,\Verify\rangle$ of \CUASGenInt,
-  using $\feval^{\dattrs,F,V,L}$ as signature evaluation function, and
-  $\finsp^F$ as open function. The \yeval value output by the verifier, when
-  it accepts, is the $\yeval^0$ value produced by \Sign in \CUASGenInt.
-\item[$h/\bot \gets RetrieveCredHandle(\osk,\utrans)$.]
-  Gets $(\sig,\yeval^0)$ from the $\langle Show,\Verify\rangle$ transcript
-  \utrans, and runs \Open from \CUASGenInt. This returns $(F(V,\cidi),
-  F(V,\cidu))$, which the verifier can add to its revocation list $L$.
-\end{description}
-
-\paragraph{Security of \CUASRAC.} %
-Our \CUASRAC construction is an anonymous and unforgeable revocable anonymous
-credential scheme, according to the model in \figref{fig:model-rac}. For space
-constraints, proofs are deferred to \appref{app:related-proofs}.
-
-% \begin{theorem}[Anonymity of \CUASRAC]
-%   If the base \CUASGenInt construction has signature anonymity according to
-%   \defref{def:sign-anonymity-uas}, then \CUASRAC is an anonymous AC scheme
-%   according to \cite{fhs19}.  
-% \end{theorem}
-
-% \begin{theorem}[Unforgeability of \CUASRAC]
-%   If the base \CUASGenInt construction is unforgeable according to
-%   \defref{def:forge-uas}, and $F$ is a one-way function, then \CUASRAC is an
-%   unforgeable RAC scheme.
-% \end{theorem}
-
-\subsection{Multimodal Private Signatures}
-\label{ssec:related-models-mps}
-
-Multimodal Private Signatures (or, rather, a close relative, see next) are
-directly implementable as a $(\fissue^{single,F,I},\feval^{g,MPS},
-\finsp^{h,MPS})$-\CUASGen restriction. Concretely, this restricts to a system
-with one credential per user and no attributes in the credentials.
-
-There are some differences, though. On the one hand, our signature anonymity
-property is somehow in the middle of MPS's privacy-1 and privacy-2 variants.
-Their privacy-1 variant is the traditional anonymity property of group
-signatures, in which the opener is honest and the adversary can call the opening
-oracle except for challenge signatures. In their privacy-2 variant, the opener
-is fully corrupt (i.e., \adv~ receives \osk), but the adversary can only be
-challenged with signatures that produce the same \yinsp value ($G_{j_b}(id_b)$
-in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
-(getting ther \osk), but the challenge signatures must have been generated using
-the key of an uncorrupted opener; still, \adv~can call the open oracle for
-challenge signatures, as long as they have the same \yinsp value. We believe
-that these differences are mostly of theoretical interest, though. In practice,
-what matters is that any variant of \feval and \finsp functions ($F$ and $G_j$
-in MPS) that has too much granularity in their ranges, will lead to a barely
-private system. This is a known issue, for instance, in functional encryption
-\cite{bsw11}.
-
-On the other hand, anonymous issuance and the capability to customize issuance
-policies are unachievable by MPS. Anonymous issuance simply does not make sense
-in MPS, as it only supports one credential (without attributes) per user, and
-customized issuance is achieved in \UAS via the \fissue functions, with no
-equivalent in MPS -- instead, MPS can be seen as having the fixed policy of
-``proving knowledge of a user secret key''. These extensions are not trivial
-from a modelling point of view, and also have a big impact in the practicality
-of the resulting system. Also, MPS does not include verifiable openings. While
-this is easy to add, we consider it to be essential, given that the proposed
-generalization of opening allows the opener to output ``any value''. Hence, the
-need to ensure that the produced value is the legitimate one, seems to be more
-necessary than ever. Finally, our \feval function is a generalization of $F$ in
-MPS, as it allows two outputs: one will be returned in the clear along with the
-signature, and the other will be encrypted. Indeed, making part of the output
-unencrypted allows implementing very useful variants such as anonymous
-credentials with selective disclosure, as shown before.
-
-For the model of MPS schemes, we refer to the original paper \cite{ngsy22}.
-
-\subsubsection{\CUASMPS construction.} %
-As mentioned, a $(\fissue^{single,F,I},\feval^{g,MPS},
-\finsp^{h,MPS})$-restriction implements an MPS scheme where $F=\feval^{g,MPS}$
-and $G=\finsp^{h,MPS}$. With these functions, the construction is direct.
-\CUASMPS's setup runs \CUASGen's \Setup, \OKeyGen, and generates the issuer key
-pair by running \KeyGen and \ISet (with $\fissue^{single,F,I}$). For MPS's join,
-\CUASMPS runs first \KeyGen to generate the user key pair, and then proceeds as
-in \CUASGen. \Sign, \Verify and \Open, are as in \CUASGen.
-%
-Finally, note that, in MPS, $G$ is further parameterized with a value $j$, which
-essentially is the result of applying $F$ to the message and signer identity,
-and is not leaked to the opener nor any other third party. The equivalent in
-\UAS is the $\yeval^1$ value which, in \CUASGen, is encrypted with a single-use
-key pair, and is an input of \finsp.
-
-\paragraph{Security of \CUASMPS.} %
-Our \CUASMPS construction satisfies the privacy-1, extractability,
-unforgeability-1 and unforgeability-2 definitions of an MPS system, as modelled
-in \cite{ngsy22}. For space constraints, proofs are deferred to
-\appref{app:related-proofs}.
-
-% \begin{theorem}[Privacy-1 of \CUASMPS]
-%   If the base \CUASGen construction has signature anonymity according to
-%   \defref{def:sign-anonymity-uas}, then \CUASMPS satisfies privacy-1
-%   according to \cite{ngsy22}.
-% \end{theorem}
-
-% \begin{theorem}[Extractability of \CUASMPS]
-%   If the base \CUASGen construction is unforgeable according to
-%   \defref{def:forge-uas}, then it is an extractable MPS scheme.
-% \end{theorem}
-
-% \begin{theorem}[Unforgeability-1 of \CUASMPS]
-%   If the base \CUASGen construction is unforgeable according to
-%   \defref{def:forge-uas}, then \CUASMPS satisfies unforgeability-1 as
-%   defined in \cite{ngsy22}.
-% \end{theorem}
-
-% \begin{theorem}[Unforgeability-2 of \CUASMPS]
-%   If the base \CUASGen construction has non-frameability according to
-%   \defref{def:frame-uas}, then \CUASMPS satisfies unforgeability-2 as
-%   defined in \cite{ngsy22}.
-% \end{theorem}
-
 %%% Local Variables:

### 2022-09-20 prism-backend/research/gsac/formal-uas.tex
Rolled-back to 2 separate unforgeability properties.

@@
 
-% In addition, we define two auxiliary properties for defining
-% the expected behaviour of the \ExtractIssue and \ExtractSign functions.
-% \todo{The following may need to be moved elsewhere and/or re-written.}
-% For instance, the extraction type are used in
-% \cite{lnpy21,nps22}, and functions of the identify type are used in
-% \cite{bfg+11,cdl16,gl19,dl21,fgl21}. Indeed, it seems hard to avoid resorting to
-% these techniques when there is no traditional notion of opening. Since, mostly
-% the unforgeability and non-frameability properties build on the extractability
-% and identifiability ones, we define them first. Then, we proceed with the usual
-% notions.
-
-% \todo{Maybe do some drawing of the cred tree.}
-
-% In the following, we use some custom notation to refer to the tree-like
-% relationships that may be built between credentials and, more concretely, their
-% related data (like {\usk}s, {\cid}s, and attribute sets {\attrs}s) when a user
-% leverages previously obtained credentials in order to obtain new ones. To
-% facilitate the explanation, we refer to \figref{fig:cred-tree}. In a nutshell,
-% we use $tree_{\cid}$ to refer to the whole tree of {\cid}s that have been used
-% to produce the credential with identifier \cid -- and, similarly, $tree_{\usk}$
-% for {\usk}s, and $tree_{\attrs}$ for attribute sets.
-
-% \begin{figure}[htp!]
-%   \centering
-%   \includegraphics[width=0.5\textwidth]{figures/cred-tree.png}
-%   \caption{Credential trees, and their corresponding notation.
-%     We use $Tree_x$, where $x \in \lbrace \usk,\cid,\attrs \rbrace$ to
-%     denote the whole tree of {\usk}s, {\cid}s, and {\attrs}s. \\
-%     \todo{Move to Tikz.}}
-%   \label{fig:cred-tree}
-% \end{figure}
-
-% \paragraph{Extractability.} %
-% We require that the witnesses used to produce each credential and signature can
-% be extracted from the corresponding \utrans and signature, respectively.
-% Furthermore, in order for our generalized notion of utility to be sound, it
-% is required that, whenever a credential is issued by an honest issuer, \fissue
-% accepts the extracted witnesses; and whenever a signature is accepted by
-% \Verify, the extracted witnesses match the expected outputs by \feval and
-% \finsp. We capture this in the \ExpExtractIssue and \ExpExtractSign games, which
-% are crucial in the unforgeability and non-frameability requirements.
-
-% In the extractability variant for credentials, \ExpExtractIssue, the adversary
-% wins if it manages to get a credential produced by an honest issuer, such that
-% the issuance predicate \fissue rejects the extracted witnesses, or if some of
-% the involved credentials is associated to a different \usk.
-% %
-% In the variant for signatures, \ExpExtractSign, the adversary wins if the
-% witnesses extracted from a signature accepted by \Verify make \feval and \finsp
-% output inconsistent values.
-% %
-% The oracles available in \ExpExtractIssue is, $\OExt \gets (\lbrace\HU,\CU
-% \rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN)$. Note that,
-% for \ExpExtractIssue, honest issuers are required, as we rely on the
-% availability of $\langle \Obtain,\Issue \rangle$ transcripts to assist on the
-% extraction. On the other hand, for \ExpExtractSign, as we extract directly from
-% signatures, honest issuers are not a requirement, so the adversary is given
-% access to $\ICORR$ too.
-
-% \begin{figure*}[htp!]
-%   \centering
-%   \scalebox{0.85}{
-%     \begin{minipage}[t]{0.6\textwidth}
-%       \procedure[linenumbering]{$\ExpExtractIssue(1^\secpar)$}{%
-%         (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
-%         \cid \gets \adv^{\OExt}(\parm) \\
-%         (\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \gets
-%         \ExtractIssue(\trap,\trans[\cid]) \\
-%         \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
-%         \trans[\cid_i]) \\
-%         \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
-%         \pcif \fissue(\usk,\ATTR[\cid],\lbrace \cid_i \rbrace_{i \in [n]},
-%         \lbrace\attrs_i\rbrace_{i \in [n]}) = 0: \\
-%         \pcind \pcreturn 1 \\
-%         \pcreturn 0
-%       }
-%     \end{minipage}
-%     \vspace*{0.5em}
-
-%     \begin{minipage}[t]{0.5\textwidth}
-%       \procedure[linenumbering]{$\ExpExtractSign(1^\secpar)$}{%
-%         (\parm, \trap) \gets \SimSetup(1^\secpar) \\
-% 	(\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets
-%         \adv^{\OExt,\ICORR}(\parm) \\
-% 	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
-% 	(\usk,\lbrace (\cid_i,\attrs_{\cid_i},\cdot) \rbrace_{i\in[n]},
-%         \yeval^1,\yinsp) \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
-%         (\yeval^0,\yeval^1) \gets \feval(\usk,\lbrace\cid_i\rbrace_{i \in [n]},
-%         \lbrace\attrs_i\rbrace_{i \in [n]}, \msg) \\
-%         \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
-%         \pcreturn 1 \\
-%         \pcif \finsp((\yeval^0,\yeval^1),\usk,\lbrace\cid_i\rbrace_{i \in [n]},
-%         \lbrace\attrs_i\rbrace_{i \in [n]},\msg) \neq \yinsp:
-%         \pcreturn 1 \\
-% 	\pcreturn 0
-%       }
-%     \end{minipage}
-%   }
-%   \caption{Extractability experiments for \UAS schemes.}
-%   \label{fig:exp-uas-extract}
-% \end{figure*}
-
-% \paragraph{Identifiability.} %
-% On their own, the extractability properties only ensure that credentials and
-% signatures have been produced by leveraging knowledge of some witnesses.
-% However, they do not establish any relationship between those witnesses and
-% users. While the actual technicalities of doing so is dependent on the
-% construction, we can, modelling-wise, enforce constraints that associate
-% user identifiers ({\uid}s, tracked by the game environment) with potential
-% witnesses. Namely, we require that it must be possible to associate any
-% credential (obtained from an honest issuer), or any signature accepted by
-% \Verify, with exactly one user identifier.
-
-% As for extractability, we define two variants. For credentials, in
-% \ExpIdentifyCred we require the adversary to output the identifier of a
-% credential obtained from an honest issuer. The adversary wins if, given the
-% witnesses extracted from the corresponding transcript, the \IdentifyCred helper
-% function outputs a set \suid of user identifiers with cardinality different than
-% $1$.
-% %
-% Similarly, for signatures, the adversary wins if it is able to produce a
-% signature from which the extracted witnesses, when passed to \IdentifySig,
-% output a set \suid of user identifiers with cardinality different than $1$.
-% %
-% The oracles are as in the extractability experiments. Namely, in the
-% \ExpIdentifyCred game, the adversary has access to $\OId \gets (\lbrace\HU,\CU
-% \rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN)$, while in
-% \ExpIdentifySign it also has access to \ICORR. The same reasoning applies.
-
-% \begin{figure*}[htp!]
-%   \centering
-%   \scalebox{0.85}{
-%     \begin{minipage}[t]{0.6\textwidth}
-%       \procedure[linenumbering]{$\ExpIdentifyCred(1^\secpar)$}{%
-%         (\parm, \trap) \gets  \SimSetup(1^\secpar) \\
-%         \cid \gets \adv^{\OId}(\parm) \\
-%         (\usk,\scred,\attrs_{\scred}) \gets \ExtractIssue(\trap,\trans[\cid]) \\
-%         \pcfor \cred \in \scred: \\
-%         \pcind \suid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
-%         \pcind \pcif |\suid| \neq 1: \pcreturn 1 \\
-%         \pcind \pcif \suid~\textrm{differs from previous iterations}: \\
-%         \pcind \pcind \pcreturn 1 \\
-%         \pcreturn 0
-%       }
-%     \end{minipage}
-%     \vspace*{0.5em}
-
-%     \begin{minipage}[t]{0.5\textwidth}
-%       \procedure[linenumbering]{$\ExpIdentifySign(1^\secpar)$}{%
-%         (\parm, \trap) \gets \SimSetup(1^\secpar) \\
-% 	(\oid,\siid,\Sig,\msg,\feval) \gets \adv^{\OId,\ICORR}(\parm) \\
-% 	\pcif \Verify(\oid,\siid,\Sig,\msg,\feval) = 0: \pcreturn 0 \\
-% 	(\usk,\scred,\attrs_{\scred},\yeval^1,\yinsp) \gets
-%         \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
-% 	\suid \gets \IdentifySig(\trap,\usk,\scred,\Sig) \\
-% 	\pcif |\suid| \neq 1: \pcreturn 1 \\
-% 	\pcreturn 0
-%       }
-%     \end{minipage}
-%   }
-%   \caption{Identifiability experiments for \UAS schemes.}
-%   \label{fig:exp-uas-identify}
-% \end{figure*}
-
-% \begin{definition}{(Identifiable credentials in \UAS)}
-%   \label{def:identify-cred-uas}  
-%   We define the advantage \AdvIdCred of $\adv$ against \ExpIdentifyCred as
-%   $\AdvIdCred=|\Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack-
-%   \Pr\lbrack\ExpIdentifyCred(1^\secpar)=1\rbrack|$.
-%   %
-%   An \UAS scheme \emph{with extractable issuance} satisfies identifiable
-%   credentials if, for any p.p.t. adversary $\adv$, \AdvIdCred is a negligible
-%   function of $1^\secpar$.
-% \end{definition}
-
-% \begin{definition}{(Identifiable signatures in \UAS)}
-%   \label{def:identify-sig-uas}  
-%   We define the advantage \AdvIdSign of $\adv$ against \ExpIdentifySign as
-%   $\AdvIdSign=|\Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack-
-%   \Pr\lbrack\ExpIdentifySign(1^\secpar)=1\rbrack|$.
-%   %
-%   An \UAS scheme \emph{with extractable signatures} satisfies identifiable
-%   signature if, for any p.p.t. adversary $\adv$, \AdvIdSign is a negligible
-%   function of $1^\secpar$.
-% \end{definition}
-
 \paragraph{Anonymity.} %
@@
 
-\paragraph{Unforgeability.} \UAS inherits from AC schemes the notion that no
-adversary can prove claims unless it owns credentials with the proper
-attributes -- although, in \UAS, claims can be proven at issuance time, and
-at signing time; from GS schemes, it inherits that only credential owners can
-produce valid signatures. \UAS also has verifiable openings, and we must ensure
-that the values output by \Open are correct and trace back to a user with
-consistent credentials. All the previous is captured by an unforgeability
-property. We define it by allowing the adversary to call any oracle, except the
-one for corrupting issuers. The adversary wins if it produces a valid signature
-that:  (1) the produced signature leveraged a credential for
-which the conditions required by \fissue were not satisfied; (2), opens to a
-wrong value, or to a value that cannot be processed by \Judge; (3), is not
-consistent with the expected \Yeval value; or (4), cannot be associated to
-known credentials owned by a known user.
-%
-Note that, under this definition, we do not consider a forgery a credential that
-was issued without meeting the issuance policy unless it is used to produce
-a signature accepted by \Verify. Indeed, obtaining credentials that cannot be
-used later does not seem to pose a threat in the real world. This approach,
-which greatly simplifies the modelling, has also been used before (e.g.
-\cite{ckl+15}).
-%
-\ExpForge is formally defined in \figref{fig:exp-uas-unfor}).
-
-\begin{figure}[htp!]
-  \centering
-  \scalebox{0.85}{
-    \begin{minipage}[t]{\textwidth}
-%       \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
+\paragraph{Unforgeability.} In \UAS schemes, we need to prevent forging either
+credential requests, or signatures. The latter is mostly a combination of the
+unforgeability of AC schemes, and the traceability of GS schemes with verifiable
+openings. However, issuance unforgeability is a direct consequence of allowing
+proving arbitrary claims already when requesting credentials.
+
+In more detail, issuance unforgeability captures that all the credentials issued
+by an honest issuer meet the requirements set by the corresponding issuance
+function. Moreover, any credential used to support the request needs to belong
+to a known user. Without conventional opening, we need to resort to extraction.
+The adversary is required to output a credential identifier that must correspond
+to an existing credential issuance interaction -- note that the transcript must
+be available to us if it exists, as the issuer is honest. From this transcript,
+we extract the witness used to compute the issuance function, which includes the
+output of the issuance function claimed by the requestor, and the credential
+identifiers of any used credential. The adversary wins if applying the output of
+the issuance function applied to the extracted witness is not consistent, or if
+the credential identifiers do not belong all to the same (known) user.
+
+Signature unforgeability is simply a combination of known requirements in AC and
+GS schemes. Namely, the adversary is required to output a valid signature, and
+wins if the signature: (1) opens to a wrong value, or to a value that cannot be
+processed by \Judge; (2), is not consistent with the expected $\Yeval =
+(\yeval^0,\yeval^1)$ value; or (3), cannot be associated to known credentials
+owned by a known user.
+
+The respective properties, \ExpForgeIssue and \ExpForgeSign, are formally
+defined in \figref{fig:exp-uas-unfor}).
+
+% \begin{figure}[htp!]
+%   \centering
+%   \scalebox{0.85}{
+%     \begin{minipage}[t]{\textwidth}
+%       \procedure[linenumbering]{$\ExpForge(1^\secpar)$}{%
 %         (\parm,\trap) \gets \SimSetup(1^\secpar) \\
-%         \cid \gets \adv^{\Oforgeissue}(\parm) \\
-%         \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
-%         \pcreturn 0 \\
-%         \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
-%         \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
-%         % (\usk,\sCred) \gets \ExtractIssue(\trap,\trans[\cid]) \\
-%         ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]})
-%         \gets \ExtractIssue(\trap,\utrans) \\
-%         % \pcfor i \in [n]: (\usk_i,\cdot) \gets \ExtractIssue(\trap,
-%         % \trans[\cid_i]) \\
-%         % \pcif \exists i \in [n]~\suchthat~\usk \neq \usk_i: \pcreturn 1 \\
-%         \pcif \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
-%         \rbrace_{i\in[n]}) \neq \yissue:
-%         \pcreturn 1 \\
-%         \pcif \OWNR[\lbrace\cid_i\rbrace_{i\in[n]}\cup\cid] \notin \HU \cup \CU:
-%         \pcreturn 1 \\
-% %        \pcif \nexists \uid~\suchthat~\PUBUK[\uid]=\upk \land
-% %        \uid \in \HU \cup \CU: \pcreturn 1 \\
-% %        \pcif \OWNR[\cid] \notin \HU \cup \CU: \pcreturn 1 \\
-%         \pcreturn 0
-%       }
-%       \vspace*{0.5em}
-
-    % \end{minipage}    
-    % \begin{minipage}[t]{\textwidth}
-      \procedure[linenumbering]{$\ExpForge(1^\secpar)$}{%
-        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
-        (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
-        \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
-        \SIG[\uid]: \pcreturn 0 \\
-        \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
-        \pcreturn 0 \\
-        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
-        \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
-        = 0: \pcreturn 1 \\
-        % (\usk,\sCred,\tyeval^1,\yinsp') \gets
-        % \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
-        % \pcif \yinsp \neq \yinsp': \pcreturn 1 \\
-        % \pcreturn 0
-	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
-        \yeval^1,\yinsp') \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
-        \pcif \exists i\in[n]~\suchthat~
-        \fissue(\upk,\cid_i,\attrs_i,\lbrace(\cid_{i,j},\attrs_{i,j})
-        \rbrace_{j\in[n_i]}) \neq \yissue^i \lor
-        \OWNR[\cid_i \cup \lbrace\cid_{i,j}\rbrace_{j\in[n_i]}]\notin \HU \cup \CU, \\
-        \pcind \textrm{where}~(\yissue^i,\utrans) \gets \trans[\cid_i]~\textrm{and}~
-        (\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
-        \rbrace_{j\in[n_i]}) \gets \ExtractIssue(\trap,\utrans): \\
-        \pcind \pcreturn 1 \\        
-        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
-        \rbrace_{i\in[n]}, \msg) \\
-        \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
-        \pcreturn 1 \\
-        \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
-        \rbrace_{i\in[n]},\msg)
-        \neq \yinsp \lor \yinsp \neq \yinsp':
-        \pcreturn 1 \\
-%        \textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
-        \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin \HU \cup \CU:
-        \pcreturn 1 \\        
-        \pcreturn 0        
-      }      
-    \end{minipage}
-  }
-  \caption{Unforgeability experiments in \UAS schemes.
-    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
-    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.}
-  \label{fig:exp-uas-unfor}
-\end{figure}
-
-% \begin{figure}[htp!]
-%     \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
-%       (\parm,\trap) \gets \Setup(1^\secpar) \\
-%       (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
+%         (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
 %         \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
@@
 %         = 0: \pcreturn 1 \\
-%       (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
-%       \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
-%       % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
-%       % \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
-%       % \pcreturn 1 \\
-%       % \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp:
-%       % \pcreturn 1 \\
-%       \uid \gets \IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) \\
-%       \uid' \gets \IdentifySig(\trap,\usk,\scred,\Sig) \\
-%       \pcif \uid \neq \uid' \lor \uid \notin \HU \cup \CU: \pcreturn 1 \\
-%       %\pcif \exists \cred \in \scred~\suchthat~
-% %      \IdentifyCred(\tau,\usk,\attrs_{\cred},\cred,\ipk_{\cred}) = 0:
-%       % \pcreturn 1 \\
-%       % \pcif \nexists \uid~\suchthat~\IdentifySig(\trap,\usk,\scred,\Sig) = 1:
-%       % \pcreturn 1 \pccomment{\todo{\uid-\usk}} \\
+% 	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
+%         \yeval^1,\yinsp') \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
+%         \pcif \exists i\in[n]~\suchthat~
+%         \fissue(\upk,\cid_i,\attrs_i,\lbrace(\cid_{i,j},\attrs_{i,j})
+%         \rbrace_{j\in[n_i]}) \neq \yissue^i \lor
+%         \OWNR[\cid_i \cup \lbrace\cid_{i,j}\rbrace_{j\in[n_i]}]\notin \HU \cup \CU, \\
+%         \pcind \textrm{where}~(\yissue^i,\utrans) \gets \trans[\cid_i]~\textrm{and}~
+%         (\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
+%         \rbrace_{j\in[n_i]}) \gets \ExtractIssue(\trap,\utrans): \\
+%         \pcind \pcreturn 1 \\        
+%         (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
+%         \rbrace_{i\in[n]}, \msg) \\
+%         \pcif \yeval \neq \yeval^0 \lor \yeval^1 \neq \tyeval^1:
+%         \pcreturn 1 \\
+%         \pcif \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
+%         \rbrace_{i\in[n]},\msg)
+%         \neq \yinsp \lor \yinsp \neq \yinsp':
+%         \pcreturn 1 \\
+%         \pcif \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin \HU \cup \CU:
+%         \pcreturn 1 \\        
 %         \pcreturn 0        
 %       }      
-%   \caption{Experiment for unforgeability of signatures in \UAS schemes.}
-%   \label{fig:exp-uas-unfor-sign}
+%     \end{minipage}
+%   }
+%   \caption{Unforgeability experiments in \UAS schemes.
+%     $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
+%     \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.}
+%   \label{fig:exp-uas-unfor}
 % \end{figure}
 
-% \begin{definition}{(Unforgeable issuance of \UAS)}
-%   \label{def:issue-forge-uas}  
-%   We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
-%   $\AdvForgeIssue=\Pr\lbrack\ExpForgeIssue(1^\secpar)=1\rbrack$.
-%   %
-%   A \UAS scheme has unforgeable issuance if, for any p.p.t. adversary $\adv$,
-%   \AdvForgeIssue is a negligible function of $1^\secpar$.
-% \end{definition}
-
-% \begin{definition}{(Unforgeable signing of \UAS)}
-%   \label{def:sign-forge-uas}  
-%   We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
-%   $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
-%   %
-%   A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
-%   \AdvForgeSign is a negligible function of $1^\secpar$.
-% \end{definition}
+\begin{figure}[htp!]
+  \centering
+  \hspace*{-2em}
+  \scalebox{0.85}{
+    \begin{minipage}[t]{0.6\textwidth}
+      \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
+        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
+        \cid \gets \adv^{\Oforge}(\parm) \\
+        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
+        \pcreturn 0 \\
+        (\yissue,\utrans) \gets \trans[\cid];
+        ((\cdot,\fissue),\cdot) \gets \PUBIK[\cid] \\        
+        (\upk,\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \\
+        \pcind \gets \ExtractIssue(\trap,\utrans) \\
+        \pcreturn \OWNR[\lbrace\cid_i\rbrace_{i\in[n]}\cup\cid] \notin \HU \cup
+        \CU~\lor \\
+        \pcind \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
+        \rbrace_{i\in[n]}) \neq \yissue        
+      }      
+    \end{minipage}    
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure[linenumbering=on]{$\ExpForgeSign(1^\secpar)$}{%
+        (\parm,\trap) \gets \SimSetup(1^\secpar) \\
+        (\oid,\siid,\Sig=(\sig,\tyeval^0),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
+        \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
+        \SIG[\uid]~\lor  \\
+        \pcind \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0: \\
+        \pcind \pcreturn 0 \\
+        (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
+	(\upk,\cdot,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
+        \tyeval^1,\tyinsp) % \pcskipln
+        \\
+        \pcind \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
+        (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
+        \rbrace_{i\in[n]}, \msg) \\
+        \pcreturn \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin
+        \HU \cup \CU~\lor \\
+        \pcind \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,
+        \msg,\feval) = 0~\lor \\
+        \pcind \yeval^0 \neq \tyeval^0 \lor \yeval^1 \neq \tyeval^1 \lor
+        \yinsp \neq \tyinsp~\lor\\
+        \pcind \finsp((\yeval^0,\yeval^1),\upk,\lbrace(\cid_i,\attrs_i)
+        \rbrace_{i\in[n]},\msg) \neq \yinsp 
+      }
+    \end{minipage}
+  }
+  \caption{Unforgeability experiments in \UAS schemes.
+    $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
+    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.}
+  \label{fig:exp-uas-unfor}
+\end{figure}
+
+\begin{definition}{(Unforgeable issuance of \UAS)}
+  \label{def:issue-forge-uas}  
+  We define the advantage \AdvForgeIssue of $\adv$ against \ExpForgeIssue as
+  $\AdvForgeIssue=\Pr\lbrack\ExpForgeIssue(1^\secpar)=1\rbrack$.
+  %
+  A \UAS scheme has unforgeable issuance if, for any p.p.t. adversary $\adv$,
+  \AdvForgeIssue is a negligible function of $1^\secpar$.
+\end{definition}
+
+\begin{definition}{(Unforgeable signing of \UAS)}
+  \label{def:sign-forge-uas}  
+  We define the advantage \AdvForgeSign of $\adv$ against \ExpForgeSign as
+  $\AdvForgeSign=\Pr\lbrack\ExpForgeSign(1^\secpar)=1\rbrack$.
+  %
+  A \UAS scheme has unforgeable signing if, for any p.p.t. adversary $\adv$,
+  \AdvForgeSign is a negligible function of $1^\secpar$.
+\end{definition}
 
@@
 
-\begin{definition}{(Unforgeability of \UAS)}
-  \label{def:forge-uas}  
-  We define advantage \AdvForge of $\adv$ against \ExpForge as $\AdvForge=
-  \Pr\lbrack\ExpForge(1^\secpar)=1\rbrack$.
-  %
-  A \UAS scheme is unforgeable if, for any p.p.t. adversary $\adv$, \AdvForge is
-  a negligible function of $1^\secpar$.
-\end{definition}
+% \begin{definition}{(Unforgeability of \UAS)}
+%   \label{def:forge-uas}  
+%   We define advantage \AdvForge of $\adv$ against \ExpForge as $\AdvForge=
+%   \Pr\lbrack\ExpForge(1^\secpar)=1\rbrack$.
+%   %
+%   A \UAS scheme is unforgeable if, for any p.p.t. adversary $\adv$, \AdvForge is
+%   a negligible function of $1^\secpar$.
+% \end{definition}
 

### 2022-09-20 prism-backend/research/gsac/formal-uas.tex
Forgot to update theorems. Need to sync with proofs.

@@
 by an honest issuer meet the requirements set by the corresponding issuance
-function. Moreover, any credential used to support the request needs to belong
-to a known user. Without conventional opening, we need to resort to extraction.
+function. Moreover, any credential used to support a request needs to belong
+to a known user. 
 The adversary is required to output a credential identifier that must correspond
@@
 
-Signature unforgeability is simply a combination of known requirements in AC and
+Signature unforgeability is a combination of known requirements in AC and
 GS schemes. Namely, the adversary is required to output a valid signature, and
@@
 processed by \Judge; (2), is not consistent with the expected $\Yeval =
-(\yeval^0,\yeval^1)$ value; or (3), cannot be associated to known credentials
+(\yeval^0,\yeval^1)$ value; or (3), cannot be associated to credentials
 owned by a known user.
 
-The respective properties, \ExpForgeIssue and \ExpForgeSign, are formally
-defined in \figref{fig:exp-uas-unfor}).
+We formalize the respective properties, \ExpForgeIssue and \ExpForgeSign, in
+\figref{fig:exp-uas-unfor}.
 
@@
 
-% \begin{theorem}[Issuance unforgeability of \CUASGen]
-%   \label{thm:issue-forge-uas}
-%   If the underlying NIZK used for \RelIss is zero-knowledge,
-%   simulation extractable and sound, then our \CUASGen construction satisfies
-%   issuance unforgeability as defined in \defref{def:issue-forge-uas}.
+\begin{theorem}[Issuance unforgeability of \CUASGen]
+  \label{thm:issue-forge-uas}
+  \todo{Update}
+  If the underlying NIZK used for \RelIss is zero-knowledge,
+  simulation extractable and sound, then our \CUASGen construction satisfies
+  issuance unforgeability as defined in \defref{def:issue-forge-uas}.
+\end{theorem}
+
+\begin{theorem}[Signing unforgeability of \CUASGen]
+  \label{thm:sign-forge-uas}
+  \todo{Update}
+  If the underlying NIZK scheme for \RelSig is simulation
+  extractable, the scheme for \RelIns is complete, the public key
+  encryption algorithm is correct, and the \SBCM scheme is correct and one-more
+  unforgeable, then our \CUASGen construction satisfies signing unforgeability
+  as defined in \defref{def:sign-forge-uas}, except with negligible probability.
+\end{theorem}
+
+% \begin{theorem}[Unforgeability of \CUASGen]
+%   \label{thm:forge-uas}
+%   If the underlying NIZK system for \RelSig is simulation extractable, the NIZK
+%   system for \RelIns is complete, the public key encryption algorithm is
+%   correct, and the \SBCM scheme is correct and one-more unforgeable, then our
+%   \CUASGen construction satisfies unforgeability as defined in
+%   \defref{def:forge-uas}, except with negligible probability.
 % \end{theorem}
-
-% \begin{theorem}[Signing unforgeability of \CUASGen]
-%   \label{thm:sign-forge-uas}
-%   If the underlying NIZK scheme for \RelSig is simulation
-%   extractable, the scheme for \RelIns is complete, the public key
-%   encryption algorithm is correct, and the \SBCM scheme is correct and one-more
-%   unforgeable, then our \CUASGen construction satisfies signing unforgeability
-%   as defined in \defref{def:sign-forge-uas}, except with negligible probability.
-% \end{theorem}
-
-\begin{theorem}[Unforgeability of \CUASGen]
-  \label{thm:forge-uas}
-  If the underlying NIZK system for \RelSig is simulation extractable, the NIZK
-  system for \RelIns is complete, the public key encryption algorithm is
-  correct, and the \SBCM scheme is correct and one-more unforgeable, then our
-  \CUASGen construction satisfies unforgeability as defined in
-  \defref{def:forge-uas}, except with negligible probability.
-\end{theorem}
 

### 2022-10-01 prism-backend/research/gsac/app-building-blocks.tex
Refined model for RAC. Conclusion. Complete draft (excl. app. D)
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.

--- 2022-07-18 prism-backend/research/gsac/app-building-blocks.tex
@@
 
+\iffalse
 \subsection{Digital Signatures}
@@
 \end{figure}
+\fi
 
@@
 
-A commitment scheme is defined by the following algorithms:
+Although we don't expose commitments directly in our \UAS scheme or
+constructions, they are an essential part of \SBCM schemes. Thus, we overview
+them briefly next. In a nutshell, a commitment scheme is defined by the
+following algorithms:
 
@@
 extension is trivial); and, more importantly, do not give security models of
-the resulting construction, nor of course prove its security. While the
-extension seems straightforward, the modelling needs to be changed due to the
-mentioned nuance of the conventional EUF notion not being compatible with
+the resulting construction, nor of course prove its security. While extending
+the constructions seems straightforward, the modelling needs to be changed due
+to the mentioned nuance of the conventional EUF notion not being compatible with
 interactive signing protocols where the signer does not learn (some of) the
-signed message(s). As we aim at using this variant as a generic building block,
+signed message(s). As we use this variant as a generic building block,
 we briefly model such a scheme for Signatures over Blocks of Committed Messages
@@
   verification-signing key pair.
-\item[$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},\smsg),
-  \SBCMSign(\SBCMsk,\smsg) \rangle$.] An interactive protocol between two
-  parties with shared input a block of messages \smsg. The party running
-  \SBCMCom further knows a set of messages $\overline{\smsg}$ to be
-  block-committed and then signed along with \smsg. The party running \SBCMSign
-  controls the signing key \SBCMsk. As a result, both parties get signature
-  \SBCMsig over $\smsg \cup \overline{\smsg}$.
-\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\overline{\smsg},\smsg)$.] Checks
-  whether \SBCMsig is a valid signature over the set of messages
-  $\overline{\smsg}$ and \smsg, under verification key \SBCMvk.
+\item[$(\SBCMcom,\pi,r) \gets \SBCMBlind(\SBCMvk,\osmsg,\smsg)$.] A user
+  computes commitment \SBCMcom to request a signature over messages \osmsg (in
+  committed form) and \smsg (in plain form), to signer with verification key
+  \SBCMvk. The output is the commitment \SBCMcom, the randomness $r$ used to
+  compute it, and a proof $\pi$ proving knowledge of \osmsg and \smsg in
+  \SBCMcom.
+\item[$\SBCMbsig \gets \SBCMSign(\SBCMsk,\SBCMcom,\pi,\smsg)$.] The
+  signer, with signing key \SBCMsk, produces a blind signature \SBCMbsig over
+  the messages commited to in commitment \SBCMcom, as well as the messages in
+  \smsg, with associated proof $\pi$.
+\item[$\SBCMsig \gets \SBCMUnblind(\SBCMvk,\SBCMbsig,\SBCMcom,r,\osmsg,\smsg)$.]
+  A user, who requested a signature over \osmsg and \smsg, where \SBCMcom is a
+  commitment over \osmsg using randomness $r$, finalizes the signature,
+  computing \SBCMsig from the signer's partial signature \SBCMbsig.
+\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\osmsg,\smsg)$.] Checks
+  whether \SBCMsig is a valid signature over the set of messages \osmsg and
+  \smsg, under verification key \SBCMvk.
 \end{description}
 
-Note that these functionality is just a generalization of partially blind
-signature schemes, where both user and signer can produce signatures over
-blocks of (committed) messages. The correctness and security properties are
-then defined as follows.
+The correctness and security properties are then defined as follows.
 
@@
 Informally, an \SBCM scheme is correct if signatures generated between an honest
-party running \SBCMCom with message sets $\overline{\smsg}$ and \smsg, and an
-honest signer running \SBCMSign over \smsg, for honestly generated parameters
-and key pairs, results in a signature over $\overline{\smsg}$ and \smsg that is
-accepted by \SBCMVerify.
+party running \SBCMBlind, an honest signer running \SBCMSign fed with the output
+of \SBCMBlind and matching \smsg and signing key pair, and the user finally
+running \SBCMUnblind over the partial signature by the signer and leveraging
+the same randomness as in \SBCMBlind, produces a signature over \osmsg and \smsg
+that is accepted by \SBCMVerify.
 
@@
 signed in committed form. Note that this is a weaker notion than the usual
-blindness property of blind signature schemes, where it is required that the
-adversary cannot link a signature to the signing process that produced it.
-Formally, blindness for \SBCM schemes is defined as in \ExpSBCMBlindb in
-\figref{fig:sbcm-games}. An \SBCM scheme is blind if, for all p.p.t.
+blindness property of (partially) blind signature schemes, where it is
+additionally required that the adversary cannot link a signature to the signing
+process that produced it. Informally, we capture this basically as the blinding
+notion of a commitment scheme -- and formally define it in \ExpSBCMBlindb in
+\figref{fig:sbcm-games}.
+%
+Note that, in the definition, we explicitly do not give back to the adversary
+\adv~any full signature (i.e., after running \SBCMUnblind) obtained from values
+returned by \adv, as this will allow the adversary to trivially check what
+messages (among the ones he chose) was signed. While this may seem a too weak
+notion, it is good enough for our needs, as in our \UAS construction we never
+share actual signatures, but zero-knowledge proofs of knowledge of such
+signatures.
+
+An \SBCM scheme is blind if, for all p.p.t.
 adversaries $\adv$, $|\Pr[\ExpSBCMBlindo(\SBCMsecpar) = 1] -
@@
 \begin{figure}[ht!]
-  \begin{minipage}[t]{\textwidth}
+  \scalebox{0.85}{
+    \begin{minipage}[t]{0.62\textwidth}
       \centering      
-
-    \procedure[linenumbering]{$\ExpSBCMOMF(\SBCMsecpar)$}{%
-      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
-      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
-      ((\sig_1,\overline{\smsg}_1, \smsg_1),\dots,
-      (\sig_{n+1},\overline{\smsg}_{n+1},\smsg_{n+1})) \gets
-      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
-      \pcif \exists i \in [n+1]~\st~\SBCMVerify(\SBCMvk,\sig_i,
-      \overline{\smsg}_i,\smsg_i) = 0: \pcreturn 0 \\
-      \pcif \exists i \neq j \in [n+1]~\st~\smsg_i = \smsg_j \land
-      \overline{\smsg}_i = \overline{\smsg}_j: \pcreturn 0 \\
-      \pcif \langle \cdot, \SBCMSign(\SBCMsk,\cdot)\rangle~
-      \textrm{was called more than $n$ times}: \pcreturn 0 \\
+      \procedure[linenumbering]{$\ExpSBCMOMF(\secpar)$}{%
+        \parm \gets \Setup(\secpar) \\
+        (\vk,\sk) \gets \KeyGen(\parm) \\
+        \lbrace(\sig_i,\overline{\smsg}_i, \smsg_i)\rbrace_{i\in[n]} \gets
+        \adv^{\Sign(\sk,\cdot,\cdot,\cdot)}(\vk) \\
+        \pcif \exists i \in [n]~\st~\Verify(\vk,\sig_i,\osmsg_i,\smsg_i) = 0: \\
+        \pcind \pcreturn 0 \\
+        \pcif \exists i \neq j \in [n]~\st \\
+        \pcind \smsg_i = \smsg_j \land \osmsg_i = \osmsg_j: \pcreturn 0 \\
+        \pcif \adv~\textrm{called}~\Sign(\sk,\cdot,\cdot,\cdot)~
+        \textrm{more than $n$ times}: \\
+        \pcind \pcreturn 0 \\
         \pcreturn 1
       }
-
-    \vspace*{0.5em}
-
-    \procedure[linenumbering]{$\ExpSBCMBlindb(\SBCMsecpar)$}{%
-      \SBCMparm \gets \SBCMSetup(\SBCMsecpar) \\
-      (\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm) \\
-      (\overline{\smsg}_0,\overline{\smsg}_1,\smsg) \gets
-      \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk) \\
-      \csig \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg}_b,\smsg),
-      \SBCMSign(\SBCMsk,\smsg) \rangle \\
-      b^* \gets \adv^{\langle \cdot, \SBCMSign(\SBCMsk,\cdot) \rangle}(\SBCMvk,
-      \csig) \\
-      \pcif b = b^*: \pcreturn 1 \\
-      \pcreturn 0
+      % \procedure[linenumbering]{$\ExpSBCMEUF(\secpar)$}{%
+      %   \parm \gets \SBCMSetup(\secpar) \\
+      %   (\vk,\sk) \gets \SBCMKeyGen(\parm) \\
+      %   (\sig,\overline{\smsg}, \smsg) \gets
+      %   \adv^{\langle \cdot, \SBCMSign(\sk,\cdot) \rangle}(\vk) \\
+      %   \pcif \SBCMVerify(\vk,\sig,\overline{\smsg},\smsg) = 0: \\
+      %   \pcind \pcreturn 0 \\
+      %   \overline{\smsg'} \gets \Extract(\sig,\utrans) \\
+      %   \pcind \textrm{where \utrans is the signing transcript for \sig} \\
+      %   \pcreturn \smsg' \neq \smsg
+      % }
+    \end{minipage}
+      % \vspace*{0.5em}
+    \begin{minipage}[t]{0.43\textwidth}
+      \procedure[linenumbering]{$\ExpSBCMBlindb(\secpar)$}{%
+        \parm \gets \Setup(\secpar) \\
+        (\vk,\sk) \gets \KeyGen(\parm) \\
+        % (\osmsg_0,\osmsg_1) \getr M \pccomment{$M \coloneqq$ message space} \\
+        % (\st,\smsg) \gets \adv(\vk,\sk) \\
+        % \pcfor d \in \bin: \\
+        % \pcind (\com_d,\pi_d,r_d) \gets \SBCMCom(\vk,\osmsg_d,\smsg) \\
+        % \pcind (\st,\bsig_d) \gets \adv(\st,\sk,\com_d,\pi_d,\smsg) \\
+        % \pcind \sig_d \gets \SBCMUnblind(\vk,\bsig_d,r_d,\osmsg_d,\smsg) \\
+        % b^* \gets \adv(\st,\sig_b,\sig_{1-b}) \\       
+        b^* \gets \adv^{BLIND(\cdot,\cdot,\cdot)}(\vk),~\textrm{where:} \\
+        \pcind BLIND(\osmsg_0,\osmsg_1,\smsg): \\
+        \pcind \pcind (\com,\pi,r) \gets \Blind(\vk,\osmsg_b,\smsg); \\
+        \pcind \pcind \pcreturn (\com,\pi) \\
+        \pcreturn b = b^*
       }
     \end{minipage}
+  }
   \label{fig:sbcm-games}
-  \caption{Games for \SBCM schemes.}
+  \caption{Games for \SBCM schemes.
+  }
 \end{figure}
 
-\paragraph{Augmenting with NIZKs.} %
-\todo{This is quite informal. Perhaps expand...} 
-In the previous \SBCM scheme, it is straightforward to require that the party
-running \SBCMCom proves some arbitrary claim over the messages to be signed
-(both those in committed or plaintext form), as well as over possibly extra
-auxiliary data. This can be done by having this party add a NIZK over the
-corresponding NP statement, which has later to be verified by the party running
-\SBCMSign.
+\paragraph{Augmented NIZKs.} %
+Constructions of \SBCM (e.g. \cite{asm06}), as well as the formalization we just
+described, require that the user proves, in zero-knowledge (via a NIZK),
+knowledge of the messages to be signed in committed
+form -- and the blinding factor used to hide them. Note that, in such
+constructions, it is easy to extend their NIZK so that, instead of simply
+proving knowledge of the messages signed in committed form, the party running
+\SBCMBlind proves, in zero knowledge, some arbitrary claim over the messages to
+be signed (both those in committed or plaintext form). This can be done by
+extending the initial NIZK into a more general one. 
 %
-We use this extension in our \CUASGen construction, and thus extend the previous
-syntax for interactive signing  as follows, to account for an extra NIZK
-relation \NIZKRel proving that a pair of statement $x$ and witness $w$ belong
-\NIZKRel.
+It is direct that, if the base \SBCM scheme satisfies blindness, then extending
+it with an arbitrary zero-knowledge NIZK proof over the signed messages, still
+maintains blindness (the adversary cannot distinguish which committed message
+set is signed, in the blindness game).
+%
+We use this extension in our \CUASGen construction. Note that, under this
+extension, we may also need to provide extra information to the \SBCMBlind,
+\SBCMSign and \SBCMUnblind algorithms, as part of the extended statement being
+proven, and new witnesses (even though some may not be part of the messages to
+be signed). To make this explicit, we use the following notation to denote
+that we use a NIZK for relation $\NIZKRel$, with values $x'$ and $w'$ that are
+part of the statement being proven, but are not contained within the actual
+\smsg or \osmsg:
 
-\begin{description}
-\item[$\SBCMsig/\bot \gets \langle \SBCMCom^{\NIZKRel}(\SBCMvk,\overline{\smsg},
-  \smsg,(x,w)),\SBCMSign^{\NIZKRel}(\SBCMsk,\smsg,x) \rangle$.] As before, but
-  the party running \SBCMCom, who owns witness $w$ for $x$ in \NIZKRel, proves
-  in zero-knowledge to the party running \SBCMSign that $(x,w) \in \NIZKRel$.
-\end{description}
+\begin{itemize}
+\item $(\Ccom,\pi,r) \gets \SBCMBlind^\NIZKRel(\vk,\osmsg,\smsg;x',w')$. Like
+  \SBCMBlind, but for relation \NIZKRel, which requires extra values $x'$ and
+  $w'$ for its statement and witnesses, beyond what may be included in \smsg and
+  \osmsg, respectively.
+\item $\SBCMbsig \gets \SBCMSign^\NIZKRel(\sk,\Ccom,\pi,\smsg;x')$. Like
+  \SBCMSign, but for relation \NIZKRel, which requires extra values $x'$
+  for its statement, beyond what may be included in \smsg.
+\item $\SBCMsig \gets \SBCMUnblind^\NIZKRel(\vk,\SBCMbsig,\Ccom,r,\osmsg,\smsg;
+  x',w')$. Like \SBCMUnblind, but for relation \NIZKRel, which requires extra
+  values $x'$ and $w'$ for its statement and witnesses, beyond what may be
+  included in \smsg and \osmsg, respectively.
+\end{itemize}
 
+\paragraph{Proofs of knowledge of a \SBCM signature.} %
 Finally, in addition, we require that the produced signatures must be compatible
-with (efficient) NIZK proofs of knowledge of a signature, and of (arbitrary)
-claims over the signed (committed) messages.
+with (efficient) NIZK proofs of knowledge of a signature.
 
@@
 
-\paragraph{$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},
-  \smsg), \SBCMSign(\SBCMsk,\smsg) \rangle$.} %
-
-\begin{itemize}
-\item \underline{User}: If $|\smsg|>\nattrs$ or $|\overline{\smsg}|>\tnattrs$,
+\paragraph{$(\Ccom,\pi,r) \gets \SBCMBlind(\SBCMvk,\osmsg,\smsg)$.} %
+If $|\smsg |>\nattrs$ or $|\osmsg|>\tnattrs$,
 abort. Else, fetch fresh randomness $r \getr \ZZ^*_p$, compute $\Ccom \gets
@@
 and $\NIZKproof \gets \NIZKProve(\NIZKcrs,(r,\overline{\smsg}),\Ccom)$.
-  Send $(\Ccom,\NIZKproof)$ to Issuer.
-\item \underline{Signer}: If $|\smsg|>\nattrs$, abort. Else, run $\NIZKVerify
-  (\NIZKcrs,\Ccom,\NIZKproof)$ and return $0$ if it fails. Else, compute
-  $x,\tilde{s} \getr \ZZ^*_p, A \gets (\gen{g}_1\Ccom \gen{g}^{\tilde{s}}
-  \prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i})^{1/(\SBCMsk+x)}$. Send
-  $(A,x,\tilde{s})$ to User.
-\item \underline{User}: If $A = 1_{\GG_1}$: return $0$. Else, compute
-  $s \gets r + \tilde{s}$. If $e(A,\gen{g}_2)^xe(A,\SBCMvk) \neq
-  e(\gen{g}_1\Ccom\gen{g}^{\tilde{s}}\prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i},
-  \gen{g}_2)$: return $0$. Else, return $(A,x,s)$.
-\end{itemize}
+Output $(\Ccom,\NIZKproof,r)$.
 
-Note that, if needed, it is straightforward to augment the proof \NIZKproof
-produced by the user in the first step with an extended proof that also proves
-that $(x,w) \in \NIZKRel$, for some other relation \NIZKRel, thus implementing
-the augmented interface $\langle\SBCMCom^\NIZKRel,\SBCMSign^\NIZKRel\rangle$ as
-described earlier.
+\paragraph{$\SBCMbsig \gets \SBCMSign(\SBCMsk,\Ccom,\NIZKproof,\smsg)$.} %
+If $|\smsg|>\nattrs$, abort. Else, run $\NIZKVerify(\NIZKcrs,\Ccom,\NIZKproof)$
+and return $0$ if it fails. Else, compute $x,\tilde{s} \getr \ZZ^*_p, A \gets
+(\gen{g}_1\Ccom \gen{g}^{\tilde{s}} \prod_{i \in |\smsg|}
+\gen{h}_i^{\smsg_i})^{1/(\SBCMsk+x)}$. Return $\SBCMbsig \gets (A,x,\tilde{s})$.
+
+\paragraph{$\SBCMsig \gets \SBCMUnblind(\SBCMvk,\SBCMbsig,\Ccom,r,
+  \osmsg,\smsg)$.} %
+Parse \SBCMbsig as $(A,x,\tilde{s})$
+If $A = 1_{\GG_1}$: return $0$. Else, compute $s \gets r + \tilde{s}$. If
+$e(A,\gen{g}_2)^xe(A,\SBCMvk) \neq e(\gen{g}_1\Ccom\gen{g}^{\tilde{s}}
+\prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i},\gen{g}_2)$: return $0$. Else, return
+$(A,x,s)$.
+
+% \paragraph{$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},
+%   \smsg), \SBCMSign(\SBCMsk,\smsg) \rangle$.} %
+
+% \begin{itemize}
+% \item \underline{User}: If $|\smsg|>\nattrs$ or $|\overline{\smsg}|>\tnattrs$,
+%   abort. Else, fetch fresh randomness $r \getr \ZZ^*_p$, compute $\Ccom \gets
+%   \gen{g}^r\prod_{i \in [|\overline{\smsg}|]}\gen{\th}_i^{\overline{\smsg}_i}$,
+%   and $\NIZKproof \gets \NIZKProve(\NIZKcrs,(r,\overline{\smsg}),\Ccom)$.
+%   Send $(\Ccom,\NIZKproof)$ to Issuer.
+% \item \underline{Signer}: If $|\smsg|>\nattrs$, abort. Else, run $\NIZKVerify
+%   (\NIZKcrs,\Ccom,\NIZKproof)$ and return $0$ if it fails. Else, compute
+%   $x,\tilde{s} \getr \ZZ^*_p, A \gets (\gen{g}_1\Ccom \gen{g}^{\tilde{s}}
+%   \prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i})^{1/(\SBCMsk+x)}$. Send
+%   $(A,x,\tilde{s})$ to User.
+% \item \underline{User}: If $A = 1_{\GG_1}$: return $0$. Else, compute
+%   $s \gets r + \tilde{s}$. If $e(A,\gen{g}_2)^xe(A,\SBCMvk) \neq
+%   e(\gen{g}_1\Ccom\gen{g}^{\tilde{s}}\prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i},
+%   \gen{g}_2)$: return $0$. Else, return $(A,x,s)$.
+% \end{itemize}
 
@@
 
+\paragraph{Augmented NIZKs.} %
+If needed, it is straightforward to augment the proof \NIZKproof used
+in \SBCMBlind, \SBCMSign and \SBCMUnblind  with an extended proof that also
+proves that $(x,w) \in \NIZKRel$, for some other relation \NIZKRel (where
+$\osmsg$ is part of $w$), thus implementing the augmented interface described
+earlier for \SBCM schemes.
+
 \paragraph{Proving Knowledge of Signature.} %
-Note that proving knowledge of a BBS+ signature as produced in our \SBCM variant
+Proving knowledge of a BBS+ signature as produced in our \SBCM variant
 is essentially the same as in \cite{asm06,cdl16b}, only needing to account for
@@
 messages. Thus, the adversary against $q$-SDH in the OMF case only needs to
-extract the witnesses from the proof. This is doable after soundness of NIZK.
+extract the witnesses from the proof. This is doable after soundness of the NIZK
+and binding of the commitment scheme. %
 If the NIZK also has online-extractability, then we do not need to impose
@@
 %
-\jdv{If needed, do the actual proof. Should essentially be a copy-paste of
-  that in \cite{cdl16b}...}
+% \jesus{If needed, do the actual proof. Should essentially be a copy-paste of
+%   that in \cite{cdl16b}...}
 
-\paragraph{Blindness.} Blindness of \SBCM is a direct consequence of the
-hiding property of the underlying block commitment scheme. Indeed, assume an
-adversary $\adv$ against blindness of \SBCM. Then, $\adv$ can be used by
-\advB against the hiding property of the commitment scheme in a straightforward
-manner. That is, once $\adv$ outputs its two sets of messages to be signed in
-committed form (i.e., $\overline{\smsg}_0$ and $\overline{\smsg}_1$, it feeds
-them directly to its environment in \ExpComHideb; \advB awaits for the response
-(a commitment of $\overline{\smsg}_b$), and forwards it to $\adv$. Finally,
-\advB outputs whatever $\adv$ outputs. Clearly, if $\adv$ wins the blindness
-game for \SBCM with non-negligible probability, so does \advB agains the hiding
-game of the commitment scheme.
+\paragraph{Blindness.}
+Blindness of \SBCM is a direct consequence of the hiding property of the
+underlying block commitment scheme. Indeed, assume an adversary $\adv$ against
+blindness of \SBCM. Then, $\adv$ can be used by \advB against the hiding
+property of the commitment scheme in a straightforward manner. Namely, \advB
+sets up the environment for \adv by running the \KeyGen algorithm using the
+\vk it receives. Then, for every query that \adv makes to its $BLIND$ oracle,
+\advB checks that the length of \smsg is acceptable (i.e., less than the
+maximum length allowed by \SBCM), and forwards the query to its own $COM$
+oracle using $\osmsg_0$ and $\osmsg_1$. To the output \Ccom of $COM$, \advB
+appends a simulated proof $\pi$, and forwards $(\Ccom,\pi)$ to \adv. Finally,
+\advB outputs whatever \adv~outputs. The simulation is correct due to the
+zero-knowledge property of the underlying NIZK. Thus, \advB wins whenever
+\adv~does.
 

### 2022-10-01 prism-backend/research/gsac/app-related-extra.tex
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.

@@
 \begin{theorem}[Unforgeability-1 of \CUASMPS]
-  If the base \CUASGen construction is unforgeable according to
-  \defref{def:forge-uas}, then \CUASMPS satisfies unforgeability-1 as defined in
-  \cite{ngsy22}.
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, then \CUASMPS satisfies unforgeability-1 as
+  defined in \cite{ngsy22}.
 \end{theorem}
@@
   Given an adversary \adv~against unforgeability-1 of \CUASMPS, as defined in
-  the MPS model, we build \advB that breaks unforgeability of the underyling
-  \CUASGen, as defined for \UAS.
+  the MPS model, we build \advB that breaks signature unforgeability of the
+  underyling \CUASGen, as defined for \UAS.
 
@@
 \begin{theorem}[Unforgeability of \CUASRAC]
-  If the base \CUASGen construction has unforgeability according to
-  \defref{def:forge-uas}, and $F$ is one-way, then \CUASRAC is an
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, and $F$ is one-way, then \CUASRAC is an
   unforgeable RAC scheme.
@@
   Given \adv~against unforgeability of \CUASRAC as defined in
-  \figref{fig:model-rac}, we build an adversary \advB against unforgeability of
-  \CUASGen as defined in \defref{def:forge-uas}.
+  \figref{fig:model-rac}, we build an adversary \advB against signature
+  unforgeability of \CUASGen as defined in \defref{def:sign-forge-uas}.
 
@@
 
-\begin{theorem}[Unforgeability of \CUASAC]
-  If the base \CUASGenInt construction is unforgeable according to (the
-  interactive version of) \defref{def:forge-uas}, and non-frameabile according
-  to (the interactive version of) \defref{def:frame-uas}, then \CUASAC is an
-  unforgeable AC scheme.
+\begin{theorem}[Unforgeability of \CUASDAC]
+  If the base \CUASGenInt construction has issuance unforgeability according to
+  (the interactive version of) \defref{def:issue-forge-uas}, signature
+  unforgeability according to (the interactive version of)
+  \defref{def:sign-forge-uas}, and non-frameable according to (the interactive
+  version of) \defref{def:frame-uas}, then \CUASDAC is an unforgeable DAC
+  scheme.
 \end{theorem}
@@
   to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
-  suppose that, from \utrans obtained at line 6, $ExtractChain$ outputs a
-  delegation chain that makes \adv~win at line 10. This means that an
+  suppose that from \utrans, $ExtractChain$ outputs at line 6 a
+  delegation chain that makes \adv~win at line 9. This means that an
   uncorrupted issuer at position $i-1$ of the chain did not own a credential
@@
     produce it. But this contradicts the conditions required by $\fissue^{n,D}$,
-    and therefore breaks unforgeability of \CUASGenInt.
+    and therefore breaks issuance unforgeability of \CUASGenInt.
   \end{itemize}

### 2022-10-01 prism-backend/research/gsac/app-related-proofs.tex
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.

@@
 \begin{theorem}[Traceability of \CUASGS]
-  If the base \CUASGen construction is unforgeable according to
-  \defref{def:forge-uas}, then \CUASGS is a traceable group signature
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, then \CUASGS is a traceable group signature
   scheme.
@@
   Assume an adversary \adv~against traceability in \CUASGS. We build an
-  adversary \advB against unforgeability of the $(\fissue^1,\feval^0,
+  adversary \advB against signature unforgeability of the $(\fissue^1,\feval^0,
   \finsp^{\upk})-\CUASGen$ restriction.
@@
   assume that \adv~wins the traceability game in \figref{fig:model-gs} with
-  $\upk \notin \HU \cup \CU$ at line 5. This implies that, in line 14 of the
-  \UAS unforgeability game (\figref{fig:exp-uas-unfor}) $\OWNR[\lbrace \cid_i
-  \rbrace_{i\in[n]}]$ returns an \uid which is not in either \HU or \CU.
+  $\upk \notin \HU \cup \CU$ at line 5. This implies that, in line 10 of the
+  \UAS signature unforgeability game (\figref{fig:exp-uas-unfor}) $\OWNR[\lbrace
+  \cid_i\rbrace_{i\in[n]}]$ returns an \uid which is not in either \HU or \CU.
   Similarly, if \adv~wins the traceability game with condition $\Judge(\dots)=0$
-  at line 5, then \advB wins its unforgeability game with the corresponding
-  check at line 6 in \figref{fig:exp-uas-unfor}.
+  at line 5, then \advB wins its signature unforgeability game with the
+  corresponding check at line 11 in \figref{fig:exp-uas-unfor}.
   %
@@
   \label{thm:forge-cuasac}
-  If the base \CUASGen construction is unforgeable according to
-  \defref{def:forge-uas}, then \CUASAC is an unforgeable AC scheme.
+  If the base \CUASGen construction has signature unforgeability according to
+  \defref{def:sign-forge-uas}, then \CUASAC is an unforgeable AC scheme.
 \end{theorem}
@@
   Given \adv~against unforgeability of \CUASAC as defined in \cite{fhs19}, we
-  build an adversary \advB against unforgeability of \CUASGen as defined in
-  \defref{def:forge-uas}.
+  build an adversary \advB against signature unforgeability of \CUASGen as
+  defined in \defref{def:sign-forge-uas}.
 
@@
   unforgeability game of \figref{fig:model-ac}, then by construction, \Verify
-  also returns $1$ in the unforgeability game of \UAS. In addition, if
+  also returns $1$ in the signature unforgeability game of \UAS. In addition, if
   there is no corrupt user with a credential containing $D$, then this leads to

### 2022-10-01 prism-backend/research/gsac/app-uas-proofs.tex
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.

@@
 of the corresponding \NIZK scheme, leveraging the trapdoor produced during
-\SimSetup. Note that, due to the zero-knowledge and simulation extractability
-properties (respectively) of the underlying NIZKs, the result of \SimSetup
-is indistinguishable from that of \Setup, and the extracted values match those
-used as witnesses in the proofs.
+\SimSetup. Note that, in our games definitions, both algorithms are always run
+over signatures that have already been verified (in the case of \ExtractSign)
+or transcripts maintained by honest issuers (in the case of \ExtractIssue).
+Thus, the zero-knowledge proofs they contain are valid. Concerning \SimSetup,
+due to the zero-knowledge and simulation extractability properties
+(respectively) of the underlying NIZKs, its result is indistinguishable from
+that of \Setup, and the extracted values match those used as witnesses in the
+proofs.
 
@@
         \Esecpar). \\
-        \Cparm \gets \CSetup(\Csecpar), \SBCMparm \gets  \SBCMSetup(\SBCMsecpar) \\
-        \Sparm \gets \SSetup(\Ssecpar), \Eparm \gets \ESetup(\Esecpar) \\
+        % \Cparm \gets \CSetup(\Csecpar), 
+        \SBCMparm \gets  \SBCMSetup(\SBCMsecpar) \\
+        % \Sparm \gets \SSetup(\Ssecpar), 
+        \Eparm \gets \ESetup(\Esecpar) \\
         (\NIZKcrs_{\Issue},\trap_{\Issue}) \gets
@@
         \NIZKSimSetup^{\NIZKRel_{\Open}}(\NIZKsecpar) \\
-        \pcreturn ((\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
-        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace), \\
-        \pcind (\trap_{\Issue},\trap_{\Sign},\trap_{\Open}))
+        \pcreturn ((% \Cparm,
+        \SBCMparm,% \Sparm,
+        \Eparm,\NIZKcrs_{\Issue},
+        \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
+        (\trap_{\Issue},\trap_{\Sign},\trap_{\Open}))
       }
@@
 
-% \subsection{Issuance Unforgeability}
+\subsection{Issuance Unforgeability}
 
-% \begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
-%   We show that the probability that \fissue outputs a wrong $\yinsp$ value is
-%   negligible, as well as the probability that the credential identifier does not
-%   belong to an existing (honest or corrupt) user.
+\begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
+  We show that the probability that \fissue outputs a wrong $\yissue$ value is
+  negligible, as well as the probability that the issued credential, and any
+  supporting credential used in the request, do not all belong to a same known
+  (honest or corrupt) user.
 
-%   Observe that the adversary is required to output a credential identifier for
-%   which associated entries in \trans and \CRED exist; moreover, if such a
-%   credential was produced by an issuer, we must have access to those entries, as
-%   issuers are assumed to be honest in this game.
-%   %
-%   Since we can access $\trans[\cid] = (\yissue,\utrans)$, and \utrans contains
-%   a NIZK proof $\NIZKproof_{\Issue}$ proving knowledge by the user of a witness
-%   in $\NIZKRel_{\Issue}$, which is simulation extractable, \ExtractIssue
-%   produces a tuple $(\upk,\usk,\lbrace (\cid_i,\attrs_i,\cred_i)
-%   \rbrace_{i\in[n]}$.
-%   %
-%   From the fact that issuers are honest, we know that $\ATTR[\cid]$ must match
-%   the attribute set \attrs used by user and issuer in the issuance protocol.
-%   Thus, from  soundness of the NIZK system, the $(\upk,\lbrace (\cid_i,\attrs_i,
-%   \cred_i) \rbrace_{i\in[n]}$ values within the extracted tuple, along with
-%   $\ATTR[\cid] = \attrs$ must make \fissue output \yissue, except with
-%   negligible probability. Moreover, soundness of the NIZK system also implies
-%   that all credentials are bound to the same \usk, which is associated to the
-%   extracted \upk.
+  Observe that we restrict to credentials issued by honest issuers. Thus, if a
+  credential with identifier \cid was issued by an honest issuer, a matching
+  $\trans[\cid]$ entry corresponding to its issuance must exist.
+  %
+  Then, $\trans[\cid] = (\yissue,\utrans)$, and \utrans contains a NIZK proof
+  $\NIZKproof_{\Issue}$ proving knowledge by the (potentially corrupt) user of a
+  witness in $\NIZKRel_{\Issue}$. Since the issuer is honest, it verifies the
+  NIZK as part of the issuance protocol, rejecting if the proof is not valid.
+  Thus, by simulation extractability, \ExtractIssue produces a $(\upk,\usk,
+  \lbrace (\cid_i,\attrs_i,\cred_i) \rbrace_{i\in[n]},(\cid,\attrs,\cred))$
+  tuple. Also due to simulation extractability, the value output by \fissue,
+  when evaluated upon the extracted values, must match the \yissue value
+  associated to $\trans[\cid]$.
 
-%   Finally, suppose that the extracted \upk does not belong to a \uid in
-%   $\HU \cup \CU$. Then, the produced credential is a forgery. \todo{How to
-%     extract the forgery in this case?? I think that expanding the definition
-%     so that it requires \adv~to produce a valid signature would make things
-%     much easier...}
-%   \qed
-% \end{proof}
+  Finally, the adversary wins if the \uid associated to the {\cid}s involved in
+  the request (i.e., both the \cid output by the adversary, as well as those
+  used to support its issuance) is not in \HU or \CU. This can happen if: (1)
+  all {\cid}s have the same owner \uid, but this \uid is different to all known
+  {\uid}s; or (2) $\OWNR[\scid] = \bot$ which, by definition of \OWNR happens if
+  not all of the involved {\cid}s in \scid have the same owner. Since the NIZK
+  used for $\NIZKRel_{\Issue}$ is simulation extractable -- where the issuer
+  verifies that all credentials are bound to the same \usk -- and due to
+  correctness of \SBCM, the probability that (2) happens is negligible, which
+  means that all involved {\cid}s have the same owner. Also, regarding (1), this
+  owner must be in either \HU or \CU as the \cid output by the adversary in step
+  2 has been produced via \ISSUE or \OBTISS which, by definition, only accept
+  known {\uid}s. Thus, the probability that \adv~wins the \ExpForgeIssue game is
+  negligible.
+  \qed
+\end{proof}
 
-\subsection{Unforgeability}
+\subsection{Signature Unforgeability}
 
-\begin{proof}[\thmref{thm:forge-uas}; Signature unforgeability of \CUASGen]
-  We show that an adversary \adv~winning \ExpForge can be used to break the
+\begin{proof}[\thmref{thm:sign-forge-uas}; Signature unforgeability of \CUASGen]
+  We show that an adversary \adv~winning \ExpForgeSign can be used to break the
   one-more unforgeability property of \SBCM.
 
-  If the verification at line 4 of \ExpForge holds, then $(\msg,\feval,
+  If the verification at line 4 of \ExpForgeSign holds, then $(\msg,\feval,
   \yeval,\cinsp,\sipk,\opk) \in \NIZKLang^{\Sign}$. Then:
@@
 
-  \paragraph{(b) All used credentials were correctly issued.} %
-  Since issuers are assumed to be honest, we have access to the $\trans[\cid_i]$
-  transcript for all credentials involved in producing the signature. Given
-  simulation extractability of $\NIZK^{\Issue}$, \ExtractIssue outputs a valid
-  witness $(\cdot,\cdot,\lbrace(\cid_{i,j},\attrs_{i,j},\cred_{i,j})
-  \rbrace_{j\in[n_j]})$ from each $\trans[\cid_i]$. This, concretely, implies
-  that the $\yissue^i$ value available in $\trans[\cid_i]$ matches the one
-  output by \fissue. Similarly, due to simulation extractability, the set of
-  credentials $\lbrace \cid_{i,j}\rbrace_{j\in[n_i]}$ used to request credential
-  $\cid_i$ cannot include credentials owned by different users, as this
-  condition is ensured by $\NIZKRel_{\Issue}$. Thus, $\uid = \OWNR[\lbrace
-  \cid_{i,j} \rbrace_{j\in[n_i]}] \neq \bot$. Now, assume that $\uid \notin \HU
-  \cup \CU$. This, in addition to the fact that {\usk}s are produced uniformly
-  at random, means that $\cred_i$ is not bound to a \usk owned by a known
-  user. But then, $\cred_i$ cannot have been produced via \OBTISS or \ISSUE,
-  which only accept requests from known {\uid}s (either in \HU or \CU,
-  respectively). Thus, $\cred_i$ is a valid \SBCM signature, that has not been
-  produced via an honest query, which breaks the one-more forgery property of
-  \SBCM.
-
-  \paragraph{(c) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
+  \paragraph{(b) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
     pair.} Also, due to simulation extractability of $\NIZK^{\Sign}$:
@@
 
-  \paragraph{(d) The output of \finsp matches the output of \Open.} %
+  \paragraph{(c) The output of \finsp matches the output of \Open.} %
   After (a), and correctness of the public key encryption algorihtm, the \yinsp
@@
 
-  \paragraph{(e) All {\cred}s are bound to the \usk of a known \uid.} %
+  \paragraph{(d) All {\cred}s are bound to the \usk of a known \uid.} %
   $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],

### 2022-10-01 prism-backend/research/gsac/formal-uas.tex
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.

@@
   ``\uid such that $\CRED[\cid] = (\uid,\cdot,\cdot,\cdot,\cdot,\cdot)$'', or
-  $\bot$ if there is no wuch \uid. We also use \OWNR over a set of {\cid}s
+  $\bot$ if there is no such \uid. We also use \OWNR over a set of {\cid}s
   (\scid). In that case, $\OWNR[\scid]$ returns $\bot$ if
@@
     \scalebox{0.85}{
-
+      \hspace*{-2em}
       \begin{minipage}[t]{0.58\textwidth}
@@
           \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
-          (\cdot,\cdot,(\cidi,\cdot)) \gets R \\
+          (\cdot,\cdot,\cid=(\cidi,\cdot)) \gets R \\
           \pcif \CRED[(\cidi,\cdot)] \neq \bot \lor \CCRED[(\cidi,\cdot)]
@@
           \pcind \pcreturn \bot \\          
-          \trans[(\cidi,\cdot)] \gets R \\
-          \CRED[(\cidi,\cdot)] \gets (\uid,\cdot,\iid,\attrs,n,\lbrace(\cdot,
+          \trans[\cid] \gets R \\
+          \CRED[\cid] \gets (\uid,\cdot,\iid,\attrs,n,\lbrace(\cid_i,
           \iid_i)
@@
           \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor \CCRED[(\cidu,\cdot)] \neq
-          \bot: \\          
-          \CRED[(\cdot,\cidu)] \gets (\uid,\cred,\iid,\attrs,n,\lbrace(\cid_i,
+          \bot: \pcreturn \bot \\          
+          \CRED[\cid] \gets (\uid,\cred,\iid,\attrs,n,\lbrace(\cid_i,
           \iid_i) \rbrace_{i\in[n]}) \\
-          \pcreturn \top \\
+          \pcreturn \top
         }
@@
           \stackrel{\cscid_{\lbrace 0,1 \rbrace}}
-          {\pcbox{\lbrace(\ccid_{0,i},\ccid_{1,i})\rbrace_{i\in[n]}}})$}{%
+          {\lbrace(\pcbox{(\ccid_{0,i},\ccid_{1,i})}},\iid_i)\rbrace_{i\in[n]})$}{%
           \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
@@
           \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\          
-          \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
-          \pcreturn \top \\
+          \CCRED[\cid] \gets (\cuid_b,\cred,\iid,\attrs, n,
+          \lbrace(\ccid_{b,i},\iid_i)\rbrace_{i\in[n]}) \\
+          \pcreturn \top
         }
@@
 \item[$\ExtractIssue(\trap,\utrans) \rightarrow (\upk,\usk,\sCred=
-  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]})$.]
-  Receives trapdoor \trap and an $\langle \Obtain, \Issue \rangle$ transcript,
-  and returns the credential set \sCred, if any, involved in the request. It
-  requires honest issuers for the transcripts to be available. 
-\item[$\ExtractSign(\trap,\opk,\lbrace \ipk_i \rbrace_{i \in [n]},\Sig,\msg,
-  \feval) \rightarrow (\upk,\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
-  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives trapdoor \trap, signature
-  \Sig over \msg and for \feval, opener public key \opk, and public keys
-  $\ipk_i$ from the issuers of the credentials used to produce \Sig. It outputs
-  the user secret key and credential set \sCred used to generate the signature,
-  and the $\yeval^1$ and \yinsp values. For notational convenience, we overload
-  this function and use \oid and \iid instead of the actual keys.
+  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]},
+  \Cred=(\cid,\attrs,\cred))$.]
+  Receives trapdoor \trap and a valid $\langle \Obtain, \Issue \rangle$
+  transcript \utrans. It outputs the credential \Cred issued as a result of the
+  interaction in \utrans, along with the involved user key pair $(\upk,\usk)$
+  and, if any, the credential set \sCred used to request \Cred.
+\item[$\ExtractSign(\trap,\Sig) \rightarrow
+  (\upk,\usk,\sCred=\lbrace(\cid_i,\attrs_i,\cred_i)
+  \rbrace_{i \in [n]},\yeval^1,\yinsp)$.] Receives trapdoor \trap and a valid
+  signature \Sig. It outputs the user secret key and credential set \sCred used
+  to generate the signature, and the $\yeval^1$ and \yinsp values. 
 % \item[$\IdentifyCred(\trap,\usk,\attrs_{\cred},\cred,\ipk)$.] Returns $1$ if
@@
 \paragraph{Unforgeability.} In \UAS schemes, we need to prevent forging either
-credential requests, or signatures. The latter is mostly a combination of the
+credential requests, and signatures. The latter is mostly a combination of the
 unforgeability of AC schemes, and the traceability of GS schemes with verifiable
-openings. However, issuance unforgeability is a direct consequence of allowing
-proving arbitrary claims already when requesting credentials.
-
-In more detail, issuance unforgeability captures that all the credentials issued
-by an honest issuer meet the requirements set by the corresponding issuance
-function. Moreover, any credential used to support a request needs to belong
-to a known user. 
-The adversary is required to output a credential identifier that must correspond
-to an existing credential issuance interaction -- note that the transcript must
-be available to us if it exists, as the issuer is honest. From this transcript,
-we extract the witness used to compute the issuance function, which includes the
-output of the issuance function claimed by the requestor, and the credential
-identifiers of any used credential. The adversary wins if applying the output of
-the issuance function applied to the extracted witness is not consistent, or if
-the credential identifiers do not belong all to the same (known) user.
-
-Signature unforgeability is a combination of known requirements in AC and
-GS schemes. Namely, the adversary is required to output a valid signature, and
-wins if the signature: (1) opens to a wrong value, or to a value that cannot be
-processed by \Judge; (2), is not consistent with the expected $\Yeval =
-(\yeval^0,\yeval^1)$ value; or (3), cannot be associated to credentials
-owned by a known user.
-
-We formalize the respective properties, \ExpForgeIssue and \ExpForgeSign, in
-\figref{fig:exp-uas-unfor}.
+openings. However, the need for issuance unforgeability is a consequence of
+allowing to support credential requests with previously obtained credentials --
+functionality which, to the best of our knowledge, \UAS is the first scheme
+to support. In both cases, it is necessary to assume honest issuers.
+
+Signature unforgeability, \ExpForgeSign, is mainly a combination (and
+generalisation) of known requirements in AC and GS schemes. Namely, the
+adversary is required to output a valid signature, from which we extract the
+user key pair, credentials, $\yeval^1$ and \yinsp values used to generate the
+signature. The adversary wins if the signature: (1) opens to a wrong value, or
+to a value that cannot be processed by \Judge; (2), is not consistent with the
+expected $\Yeval = (\yeval^0,\yeval^1)$ value; or (3), cannot be associated to
+credentials owned by a known user. Here, we again need to assume honest issuers.
+Otherwise, it is trivial for the adversary to produce untraceable credentials
+(i.e., that do not appear in any ``log'') which then evaluate to any desired
+value when used to generate a signature.
+
+While it may seem enough to check that no valid signature can be created from
+forged credentials (i.e., credentials that did not meet their issuance policy,
+or are not bound to a known user), note that allowing credentials to
+endorse further credential requests makes this argument insufficient. For
+instance, if we only check the credentials involved in signature generation, it
+is perfectly possible that a forged credential is used to obtain a legitimate
+one, and then use the latter to finally create a valid signature -- concretly,
+such misbehaviour is not prevented by \ExpForgeSign.
+
+We thus extend unforgeability of signatures with issuance unforgeability,
+\ExpForgeIssue. It captures that all honestly issued credentials meet the
+requirements set by the corresponding issuer, and that any further credential
+involved in the request is bound to the same known user. For this, we allow the
+adversary \adv~to interact with the oracles (restricted to honest issuers).
+Eventually, \adv~is challenged to output a credential identifier from which we
+extract the actual witnesses used in the credential request associated to \cid.
+\adv~wins if the issuance function, applied to the extracted values, does not
+meet the expected output, or if not all of the credentials (if any) used to
+support the request belong to a same (known) user. Note that the issuance
+transcript associated to \cid must exist, as we unavoidably need to restrict to
+honest issuers. Indeed, a dishonest issuer cannot be trusted to enforce any
+policy, nor to properly keep all transcripts. In practice, this means that
+dishonest issuers can create arbitrary credentials.
+
+We formalize both properties in \figref{fig:exp-uas-unfor}.
 
@@
         (\parm,\trap) \gets \SimSetup(1^\secpar) \\
+        % (\Cred,\uid,\iid,\oid,\feval,\msg) \gets \adv^{\Oforge}(\parm) \\
+        % \Sig \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\Cred,\msg,\feval) \\
+        % \pcif \Verify(\PUBOK[\oid],\PUBIK[\iid],\Sig,\msg,\feval) = 0: \\
+        % \pcind \pcreturn 0 \\
+        % (\upk,\usk, (\cid,\attrs,\cdot), \cdot, \cdot) \\
+        % \pcind \gets \ExtractSign(\trap,\oid,\iid,\Sig,\msg,\feval) \\
+        % \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 1 \\
+        % (\yissue,\cdot) \gets \trans[\cid];
+        % ((\cdot,\fissue),\cdot) \gets \PUBIK[\cid] \\
+        % \pcif \nexists \lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]}
+        % \in \CRED[\uid]~\suchthat \\
+        % \pcind \fissue(\upk,\cid,\attrs,
+        % \lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]}) = \yissue: \\
+        % \pcind \pcreturn 1
+        % 
+        % ((\upk_1,r_1,\Ccom_1),\dots,(\upk_l,r_l,\Ccom_l),\st) \\
+        % \pcind \gets \adv^{\HUGEN,\CUGEN}(\texttt{choose},\parm) \\
+        % \pcif \exists i\in[l]~\suchthat~\forall \uid,
+        % \upk_i \neq \PUBUK[\uid]:  \\
+        % \pcind \pcreturn 0 \\
+        % \cid \gets \adv^{\Oforge}(\texttt{forge},\st,\parm) \\
         \cid \gets \adv^{\Oforge}(\parm) \\
-        \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot:
-        \pcreturn 0 \\
-        (\yissue,\utrans) \gets \trans[\cid];
-        ((\cdot,\fissue),\cdot) \gets \PUBIK[\cid] \\        
-        (\upk,\usk,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i \in [n]}) \\
-        \pcind \gets \ExtractIssue(\trap,\utrans) \\
-        \pcreturn \OWNR[\lbrace\cid_i\rbrace_{i\in[n]}\cup\cid] \notin \HU \cup
-        \CU~\lor \\
-        \pcind \fissue(\upk,\ATTR[\cid],\lbrace (\cid_i,\attrs_i)
-        \rbrace_{i\in[n]}) \neq \yissue        
+        \pcif \ISR[\cid] \notin \HI \lor \trans[\cid] = \bot: \pcreturn 0 \\
+        (\utrans,\yissue) \gets \trans[\cid] \\
+        (\upk,\cdot,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},\cdot,\attrs,
+        \cdot) \gets \ExtractIssue(\trap,\utrans) \\
+        \textrm{Let $\scid \gets \lbrace \cid_i \rbrace_{i\in[n]} \cup
+          \lbrace \cid \rbrace$} \\
+        \pcreturn \OWNR[\scid] \notin \HU \cup \CU~\lor \\
+        \pcind \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\attrs_i)\rbrace_{i\in[n]})
+        \neq \yissue
       }      
@@
         (\oid,\siid,\Sig=(\sig,\tyeval^0),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
-        \pcif \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
+        \pcif \exists \iid \in \siid~\suchthat~\iid \notin \HI \lor
+        \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
         \SIG[\uid]~\lor  \\
@@
         (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
-	(\upk,\cdot,\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},
+	(\upk,\usk,\lbrace(\cid_i,\attrs_i,\cred_i)\rbrace_{i\in[n]},
         \tyeval^1,\tyinsp) % \pcskipln
         \\
-        \pcind \gets \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
+        \pcind \gets \ExtractSign(\trap,\Sig) \\
         (\yeval^0,\yeval^1) \gets \feval(\upk,\lbrace(\cid_i,\attrs_i)
@@
     $\Oforge \gets \lbrace\OO,\HU,\CU\rbrace\GEN,\ISET,\lbrace\OO,\UU\rbrace
-    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$.}
+    \CORR,\OBTISS,\ISSUE,\RREG,\SIGN,\OPEN$. % In line 10 of \ExpForgeIssue, we
+    % slightly abuse notation to denote that user \uid does not own a set of
+    % credentials with {\cid}s and attributes equal to $\lbrace (\cid_i,\attrs_i)
+    % \rbrace_{i\in[n]}$.
+  }
   \label{fig:exp-uas-unfor}
@@
       ((\upk,\usk),\lbrace(\cid_i,\attrs_i,\cdot)\rbrace_{i\in[n]},\tyeval^1,\yinsp') \gets
-      \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
+      \ExtractSign(\trap,\Sig) \\
       % \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
@@
 \paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
-  \langle\Obtain(\usk,\cidu,\ipk,\lbrace (\cid_i,\cattrs_i,\cred_i) \rbrace_{i\in[n]},
-  \attrs),\Issue(\isk,\cidi,\lbrace \ipk_i \rbrace_{i\in[n]},\attrs)\rangle$.} %
+  \langle\Obtain(\usk,\ipk,\lbrace (\cid_i,\cattrs_i,\cred_i) \rbrace_{i\in[n]},
+  \attrs),\Issue(\isk,\lbrace \ipk_i \rbrace_{i\in[n]},\attrs)\rangle$.} %
 The protocol is run between an issuer with key pair $(\ipk,\isk)$, and a user
@@
 each $\cred_i$ is issued by an issuer with public key $\ipk_i$, and
-attests attributes $\cattrs_i$. The user requests a signature on a commitment to
-the user key, as well as on $\cid=(\cidi,\cidu)$ and the attributes in \attrs.
-In addition, the user proves correct computation of the \fissue function set by
-the issuer based on the $\cred_i$ credentials and its user public key.
-This is essentially achieved through an execution of an \SBCM interactive
-signing protocol with \RelIss as NP relation. Since \fissue is
-evaluated by the user, but depends on the \cidi value chosen by the issuer, the
-issuer first needs to send \cidi.
-Then both interact to produce the \SBCM signature, where the
-user runs $\SBCMCom^{\NIZKRel_{\Issue}}(\ipk,\usk,(\cid,\attrs),\lbrace (\cid_i,
-\cattrs_i,\cred_i)\rbrace_{i\in[n]},\lbrace \ipk_i \rbrace_{i\in[n]})$, and the
-issuer runs $\SBCMSign^{\NIZKRel_{\Issue}}(\isk,(\cid,\attrs),\lbrace\ipk_i
-\rbrace_{i\in[n]})$. Observe that, within this protocol, the user sends a NIZK
-proof $\NIZKproof_{\Issue}$ ensuring that it knows a valid witness $(\upk,\usk,
-\lbrace (\cid_i,\cattrs_i,\cred_i)\rbrace_{i \in [n]},r)$ for the relation
-\RelIss. The credential \cred produced by the user is the result of
-the interactive signing protocol, whereas the issuer produces $(\yissue,
-\utrans)$, where \yissue is the output of \fissue, and \utrans is the
-communication transcript of the signing protocol.% , which is a $(\Ccom,(\cid,\attrs),\lbrace
-% \ipk_i \rbrace_{i\in[n]},\cred,\pi)$ tuple (see \appref{sapp:sbcm} for details).
+attests attributes $\cattrs_i$. The issuer first sends the user a random
+identifier \cidi, which will be one of the signed attributes. The rest
+is essentially a sequence of \SBCMBlind, \SBCMSign, and \SBCMUnblind runs
+between user and issuer, over an extended NIZK for \RelIss (see
+\appref{sapp:sbcm}). Concretely:
+
+\begin{itemize}  
+\item \underline{Issuer}: Randomly pick \cidi. Send \cidi to the user.
+\item \underline{User}: Randomly pick \cidu; let $\cid \gets (\cidi,\cidu)$.
+  Compute $\yissue \gets \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)
+  \rbrace_{i\in[n]})$. Run $(\Ccom,\pi,r) \gets \SBCMBlind^{\RelIss}(\ipk,\usk,
+  \lbrace \cid \rbrace \cup \attrs; \yissue, \lbrace (\cid_i,\cattrs_i)
+  \rbrace_{i\in[n]})$. Send $(\Ccom,\pi)$ to the issuer.
+\item \underline{Issuer}: Run $\SBCMbsig \gets \SBCMSign^{\RelIss}(\isk,\Ccom,
+  \pi,\attrs;\yissue)$. Return \SBCMbsig to the user. Output $((\cidi,\Ccom,\pi,
+  \SBCMbsig),\yissue)$. 
+\item \underline{User}: Run $\SBCMsig \gets \SBCMUnblind^{\RelIss}(\ipk,
+  \SBCMbsig,\Ccom,r,\usk,\lbrace \cid \rbrace \cup \attrs; \yissue, \lbrace
+  (\cid_i,\cattrs_i)\rbrace_{i\in[n]})$. Output $\cred \gets \SBCMsig$.
+\end{itemize}
 
@@
   \label{thm:issue-forge-uas}  
-  \todo{Update}
-  If the underlying NIZK used for \RelIss is zero-knowledge,
-  simulation extractable and sound, then our \CUASGen construction satisfies
+  If the underlying NIZK used for \RelIss is simulation extractable, and the
+  underlying \SBCM scheme is correct, then our \CUASGen construction satisfies
   issuance unforgeability as defined in \defref{def:issue-forge-uas}.
@@
 
-\begin{theorem}[Signing unforgeability of \CUASGen]
+\begin{theorem}[Signature unforgeability of \CUASGen]
   \label{thm:sign-forge-uas}
-  \todo{Update}
-  If the underlying NIZK scheme for \RelSig is simulation
-  extractable, the scheme for \RelIns is complete, the public key
-  encryption algorithm is correct, and the \SBCM scheme is correct and one-more
-  unforgeable, then our \CUASGen construction satisfies signing unforgeability
-  as defined in \defref{def:sign-forge-uas}, except with negligible probability.
+  If the underlying NIZK scheme for \RelSig is simulation extractable, the
+  scheme for \RelIns is complete, the public key encryption algorithm is
+  correct, and the \SBCM scheme is correct and one-more unforgeable, then our
+  \CUASGen construction satisfies signing unforgeability as defined in
+  \defref{def:sign-forge-uas}, except with negligible probability.
 \end{theorem}

### 2022-10-01 prism-backend/research/gsac/preliminaries-paper.tex
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.

@@
 For this purpose, we define such schemes as a tuple (\SBCMSetup,\SBCMKeyGen,
-\SBCMCom,\SBCMSign,\SBCMVerify). Algorithm $\parm \gets \SBCMSetup(\secpar)$
-produces the public parameters for the scheme. %
-$(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing
-key pair. $\sig/\bot \gets\langle \SBCMCom^{\NIZKRel}(\vk,\overline{\smsg},
-\smsg,(x,w)),\SBCMSign^\NIZKRel(\sk,\smsg,x) \rangle$ is an interactive protocol
-between a user, who runs \SBCMCom and has a set of messages $\overline{\smsg}$
-to be block-committed, and a signer, who owns signing key \sk; both also receive
-common input a block of messages \smsg. In addition, the user knows a pair
-$(x,w) \in \NIZKRel$, and proves (in zero-knowledge) knowledge of $w$ to the
-signer. The output of the protocol is a signature over
-$\overline{\smsg} \cup \smsg$. Algorithm $1/0 \gets \SBCMVerify(\vk,
-\sig,\overline{\smsg},\smsg)$ verifies a signature \sig over message vector
-$\overline{\smsg} \cup \smsg$. In addition, the
-produced signatures must be compatible with (efficient) NIZK proofs of knowledge
-of a signature, and of (arbitrary) claims over the signed (committed) messages.
-An \SBCM scheme must provide one-more-forgery type of security.
+\SBCMBlind,\SBCMSign,\SBCMUnblind,\SBCMVerify).
+%
+Algorithm $\parm \gets \SBCMSetup(\secpar)$ produces the public parameters for
+the scheme.
+% 
+$(\vk,\sk) \gets \SBCMKeyGen(\parm)$ produces a verification-signing key pair.
+%
+$(\Ccom,\pi,r) \gets \SBCMBlind^{\NIZKRel}(\vk,\osmsg,\smsg;x',w')$ is run by a
+user who wants to request a signature over $\osmsg \cup \smsg$, where only \smsg
+are revealed to the signer, and $\osmsg$ are to be signed in committed form.
+Moreover, \osmsg (and, possibly, $w'$) are witnesses to some statement defined
+over \smsg (and, possibly, $x'$), for a relationship \NIZKRel.
+%
+$\SBCMbsig \gets \SBCMSign^{\NIZKRel}(\sk,\Ccom,\pi,\smsg; x')$ is run by the
+signer, to produce a partial signature \SBCMbsig over a set of committed
+messages and set \smsg, satisfying relation \NIZKRel.
+%
+$\SBCMsig \gets \SBCMUnblind^{\NIZKRel}(\vk,\SBCMbsig,\Ccom,r,\osmsg,\smsg)$ is
+run by the user to complete a partial signature \SBCMbsig received by the
+signer, over \osmsg (committed to in \Ccom) and \smsg.
+%
+Finally, algorithm $1/0 \gets \SBCMVerify(\vk,\sig,\osmsg,\smsg)$ verifies a
+signature \sig over message vector $\osmsg \cup \smsg$.
+%
+In addition, the produced signatures must be compatible with (efficient) NIZK
+proofs of knowledge of a signature, and of (arbitrary) claims over the signed
+(committed) messages. An \SBCM scheme must provide one-more-forgery type of
+security.
 

### 2022-10-03 prism-backend/research/gsac/formal-uas.tex
Pass.

@@
   available to all other functions.
-\item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
-  \KeyGen to generate its user key pair. 
-\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
+\item[$\KeyGen(\parm) \rightarrow (% \Ccom,r,
+  \upk,\usk)$.] Given \parm, a user
+  runs \KeyGen to generate its user key pair% , and a commitment \Ccom to the
+  % public key, with randomness $r$
+  . 
+\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and
   function \finsp, an opener runs \OKeyGen to generate its opening key pair.
@@
   the \fissue function defined by the issuer, and $\utrans=(U,I)$ being the
-  transcript of the communication, where $U$ contains the messages sent by
-  the user, and $I$ those sent by the issuer.
+  transcript of the communication% , where $U$ contains the messages sent by
+  % the user, and $I$ those sent by the issuer
+  .
 \item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
@@
 These are the functional placeholders that allow modulating the behaviour of the
-resulting instantiation, by controling the conditions upon which new credentials
+resulting instantiation. They controll the conditions upon which new credentials
 can be issued, the information revealed at signing time, or extractable from
-signatures. In all cases, the user who computes them, and proves correctness of
+signatures. In all cases, the user computes them, and proves correctness of
 such computation. We give concrete examples in \secref{sec:relationships}.
@@
 
-\feval and \finsp may seem redundant. However, the former is chosen on a
-per-signature basis, probably after negotiation between signer and verifier, and
-governs the information revealed at signing time. On the other hand, \finsp
-governs the information that may be revealed after signing, and is defined by
-openers when they set up their key pair.
-
 Concerning \fissue functions, our \UAS model requires them to be
-\UAS-acceptable. At a high level, this requires that \fissue functions do not
+\UAS-acceptable. At a high level, this requires that, conditioned on \fissue
+functions accepting the request (i.e., returning a non-zero value), they do not
 reveal anything about the signer's data used as input. This is formally captured
@@
   \scalebox{0.85}{
-    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
+    \procedure[linenumbering=on]{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
       \parm \gets \Setup(1^\secpar) \\
@@
       \gets \adv(\upk) \\
-      \pcif b=0:
-      \yissue^* \gets \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)
+      y \gets \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)
       \rbrace_{i\in[n]}) \\
-      \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
+      \pcif y = 0: \pcreturn \bot \\
+      \pcif b=0: \yissue^* \gets y;~
+      \pcelse:~\yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
       b^* \gets \adv(\st,\yissue^*) \\
@@
 identified by their \uid, we mostly use \iid to refer to a user acting as
-issuer, especially, for operations involving both a user and an issuer.
+issuer, especially for clarity in operations involving both a user and an
+issuer.
 %
@@
 openings. However, the need for issuance unforgeability is a consequence of
-allowing to support credential requests with previously obtained credentials --
-functionality which, to the best of our knowledge, \UAS is the first scheme
-to support. In both cases, it is necessary to assume honest issuers.
+allowing users to leverage previously obtained credentials in new credential
+requests -- functionality which, to the best of our knowledge, \UAS is the first
+scheme to support. In both cases, it is necessary to assume honest issuers.
 
@@
 expected $\Yeval = (\yeval^0,\yeval^1)$ value; or (3), cannot be associated to
-credentials owned by a known user. Here, we again need to assume honest issuers.
+credentials owned by a known user. Here, we need to assume honest issuers.
 Otherwise, it is trivial for the adversary to produce untraceable credentials
@@
 
-While it may seem enough to check that no valid signature can be created from
-forged credentials (i.e., credentials that did not meet their issuance policy,
-or are not bound to a known user), note that allowing credentials to
-endorse further credential requests makes this argument insufficient. For
-instance, if we only check the credentials involved in signature generation, it
-is perfectly possible that a forged credential is used to obtain a legitimate
-one, and then use the latter to finally create a valid signature -- concretly,
-such misbehaviour is not prevented by \ExpForgeSign.
+We could simply check that all the credetnials involved in valid signatures
+satisfy their respective \fissue functions, and belong to known users. However,
+allowing credentials to endorse further credential requests makes this argument
+insufficient. For instance, if we only check the credentials involved in
+signature generation, it is perfectly possible that a forged credential is used
+to obtain a legitimate one, and then use the latter to finally create a valid
+signature -- concretly, such misbehaviour is not prevented by \ExpForgeSign.
 
@@
 meet the expected output, or if not all of the credentials (if any) used to
-support the request belong to a same (known) user. Note that the issuance
-transcript associated to \cid must exist, as we unavoidably need to restrict to
-honest issuers. Indeed, a dishonest issuer cannot be trusted to enforce any
-policy, nor to properly keep all transcripts. In practice, this means that
-dishonest issuers can create arbitrary credentials.
+support the request belong to the same (known) user to whom the new credential
+was issued. Note that the issuance transcript associated to \cid must exist, as
+we unavoidably need to restrict to honest issuers. Indeed, a dishonest issuer
+cannot be trusted to enforce any policy, nor to properly keep all transcripts.
 
@@
     \end{minipage}    
-    \begin{minipage}[t]{0.5\textwidth}
+    \begin{minipage}[t]{0.6\textwidth}
       \procedure[linenumbering=on]{$\ExpForgeSign(1^\secpar)$}{%
@@
         (\oid,\siid,\Sig=(\sig,\tyeval^0),\msg,\feval) \gets \adv^{\Oforge}(\parm) \\
-        \pcif \exists \iid \in \siid~\suchthat~\iid \notin \HI \lor
-        \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
+        \pcif \exists \iid \in \siid~\suchthat~\iid \notin \HI~\lor \\
+        \pcind \exists \uid~\suchthat~(\cdot,\cdot,\Sig,\cdot,\msg,\feval) \in
         \SIG[\uid]~\lor  \\
@@
 
-\begin{definition}{(Unforgeable signing of \UAS)}
+\begin{definition}{(Unforgeable signatures of \UAS)}
   \label{def:sign-forge-uas}  
@@
 \paragraph{Non-frameability.} %
-The notion of non-frameability in \UAS schemes is unavoidably more subtle than
+The notion in \UAS schemes is unavoidably more subtle than
 in group signatures\footnote{As far as we know, non-frameability has not been
@@
 it can be perfectly valid to have a signature produced by a corrupted user
-output the same \Yeval or \yinsp values than the ones output when evaluating or
+output the same \Yeval or \yinsp values than those output when evaluating or
 opening a signature by an honest user.
@@
 and, in \UAS, the value produced by \Open may depend on the attributes
-included in user credentials, the adversary may even be able to just produce
+included in user credentials, the adversary may even be able to produce
 ``legitimate'' openings to any desired value. Anyway, this is
@@
 
-In the non-frameability definition for \UAS, given in experiment \ExpNonframe in
-\figref{fig:exp-uas-frame}, the adversary is challenged to produce a signature
+We formalize non-frameability in \ExpNonframe in \figref{fig:exp-uas-frame}.
+The adversary is challenged to produce a signature
 and opening proof that is accepted by \Verify and \Judge, respectively. From
@@
       \rbrace_{i\in[n]},\msg)
-      \neq \yinsp \lor \yinsp \neq \yinsp': \\
-      \pcind \pcreturn 1 \\
+      \neq \yinsp \lor \yinsp \neq \yinsp': \pcreturn 1 \\
       %\textrm{Let~}\scid \gets \lbrace \cid_i \rbrace_{i\in[n]};
@@
 \item[\RelIss:] For NIZK proofs at issuance time. Requires users to
-  prove knowledge of \usk and the related \upk. It also requires that any
-  additional credential supporting the request be a valid credential (signed by
-  some issuer) and bound to \upk, and enforces the corresponding \fissue policy.
+  prove knowledge of \usk and the related \upk, as well as proving that the
+  credential request is bound to \usk. It also requires that any additional
+  credential supporting the request be a valid credential (signed by some
+  issuer) and bound to \upk, and enforces the corresponding \fissue policy.
 \item[\RelSig:] For NIZK proofs at signing time. Ensures that
@@
 \paragraph{$\parm \gets \Setup(\secpar)$.} %
-Essentially generates the public parameters for all the building blocks. It runs
+Generates the public parameters for all the building blocks. It runs
 $\SBCMparm \gets \SBCMSetup(\secpar)$, $\Eparm \gets \ESetup(\secpar)$,
-$\NIZKcrs_{\Issue} \gets \NIZKSetup^{\NIZKRel_{\Issue}}(\secpar)$,
-$\NIZKcrs_{\Sign} \gets \NIZKSetup^{\NIZKRel_{\Sign}}(\secpar)$, and
-$\NIZKcrs_{\Open} \gets \NIZKSetup^{\NIZKRel_{\Open}}(\secpar)$. Return
-$(\SBCMparm,\Eparm,\NIZKcrs_{\Issue},\NIZKcrs_{\Sign},\NIZKcrs_{\Open})$.
+$\crsiss \gets \NIZKSetup^{\RelIss}(\secpar)$,
+$\crssig \gets \NIZKSetup^{\RelSig}(\secpar)$, and
+$\crsins \gets \NIZKSetup^{\RelIns}(\secpar)$. Return
+$(\SBCMparm,\Eparm,\crsiss,\crssig,\crsins)$.
 
@@
 Each opener parses \parm as $(\cdot,\Eparm,\cdot,\cdot,\cdot)$.
-Then, runs $(\Eek,\Edk) \gets \EKeyGen(\Eparm)$, and sets, $\opk \gets (\Eek,
-\finsp)$, and $\osk \gets \Edk$.
+Then, runs $(\ek,\dk) \gets \EKeyGen(\Eparm)$, and sets, $\opk \gets (\ek,
+\finsp)$, and $\osk \gets \dk$.
 
@@
 with secret key \usk and credentials $\lbrace \cred_i \rbrace_{i\in[n]}$, where
-each $\cred_i$ is issued by an issuer with public key $\ipk_i$, and
+each $\cred_i$ was issued by an issuer with public key $\ipk_i$, and
 attests attributes $\cattrs_i$. The issuer first sends the user a random
 identifier \cidi, which will be one of the signed attributes. The rest
-is essentially a sequence of \SBCMBlind, \SBCMSign, and \SBCMUnblind runs
+is a sequence of \SBCMBlind, \SBCMSign, and \SBCMUnblind runs
 between user and issuer, over an extended NIZK for \RelIss (see
@@
   \rbrace_{i\in[n]})$. Send $(\Ccom,\pi)$ to the issuer.
-\item \underline{Issuer}: Run $\SBCMbsig \gets \SBCMSign^{\RelIss}(\isk,\Ccom,
-  \pi,\attrs;\yissue)$. Return \SBCMbsig to the user. Output $((\cidi,\Ccom,\pi,
-  \SBCMbsig),\yissue)$. 
-\item \underline{User}: Run $\SBCMsig \gets \SBCMUnblind^{\RelIss}(\ipk,
-  \SBCMbsig,\Ccom,r,\usk,\lbrace \cid \rbrace \cup \attrs; \yissue, \lbrace
-  (\cid_i,\cattrs_i)\rbrace_{i\in[n]})$. Output $\cred \gets \SBCMsig$.
+\item \underline{Issuer}: Run $\bsig \gets \SBCMSign^{\RelIss}(\isk,\Ccom,
+  \pi,\attrs;\yissue)$. Return \bsig to the user. Output $((\cidi,\Ccom,\pi,
+  \bsig),\yissue)$. 
+\item \underline{User}: Run $\sig \gets \SBCMUnblind^{\RelIss}(\ipk,
+  \bsig,\Ccom,r,\usk,\lbrace \cid \rbrace \cup \attrs; \yissue, \lbrace
+  (\cid_i,\cattrs_i)\rbrace_{i\in[n]})$. Output $\cred \gets \sig$.
 \end{itemize}
@@
 The user first evaluates $\Yeval = (\yeval^0,\yeval^1) \gets \feval (\upk,
-\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$. Then, parses \opk as $(\Eek,
+\lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$. Then, parses \opk as $(\ek,
 \finsp)$, computes $\yinsp \gets \finsp((\yeval^0,\yeval^1),\upk,
 \lbrace(\cid_i,\cattrs_i)\rbrace_{i\in[n]},\msg)$, and encrypts
-\yinsp by running $\cinsp \gets \EEnc(\Eek,\yinsp; r')$ for some fresh
-randomness $r'$. Finally, the user computes $\NIZKproof \gets
-\NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\upk,\usk,\lbrace(\cid_i,
+\yinsp by running $\cinsp \gets \EEnc(\ek,\yinsp; r')$ for some fresh
+randomness $r'$. Finally, the user computes $\proofsig \gets
+\NIZKProve^{\RelSig}(\crssig,(\upk,\usk,\lbrace(\cid_i,
 \cattrs_i,\cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r,r'),(\msg,
-\feval,\yeval^0,\cinsp,\lbrace \ipk_i\rbrace_{i\in[n]},\Eek))$ and outputs
-$(\sig = (\NIZKproof,\cinsp),\yeval^0)$. Note that, depending on the value of
+\feval,\yeval^0,\cinsp,\lbrace \ipk_i\rbrace_{i\in[n]},\ek))$ and outputs
+$(\sig = (\proofsig,\cinsp),\yeval^0)$. Note that, depending on the value of
 \Yeval and \yinsp, the user may decide to abort
@@
 The ``cryptographic'' side of the verification consists on checking
-the NIZK proof. That is, parse \Sig as $(\sig = (\NIZKproof,\cinsp),\yeval)$ and
-check whether $\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,
-\cinsp,\sipk,\opk)) = 1$. In addition, the verifier may further check
-whether \yeval meets its needs.
-
-\paragraph{$(\yinsp,\NIZKproof)/\bot \gets
+the NIZK proof. That is, parse \Sig as $(\sig = (\proofsig,\cinsp),\yeval)$ and
+check whether $\NIZKVerify^{\RelSig}(\crssig,\proofsig,(\msg,\feval,\yeval,
+\cinsp,\sipk,\opk)) = 1$. Also, the verifier may check whether \yeval meets its
+needs.
+
+\paragraph{$(\yinsp,\proofins)/\bot \gets
   \Open(\osk,\sipk,\Sig,\msg,\feval)$.} %
@@
 %
-To open a signature, the opener first verifies the signature by running $\Verify
-(\opk,\sipk, \Sig,\msg,\feval)$. If verification succeeds, it parses
-\Sig as $(\sig=(\NIZKproof,\cinsp),\yeval)$, runs $\yinsp
-\gets \EDec(\osk,\cinsp)$, and computes $\NIZKproof_{\Open} \gets
-\NIZKProve^{\NIZKRel_{\Open}}(\NIZKcrs_{\Open},\osk,(\cinsp,\yinsp))$. It
-returns $(\yinsp,\NIZKproof_{\Open})$.
-
-\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\Sig,\msg)$.} %
+The opener first verifies the signature by running $\Verify
+(\opk,\sipk, \Sig,\msg,\feval)$. Upon success, it parses
+\Sig as $(\sig=(\proofsig,\cinsp),\yeval)$, runs $\yinsp
+\gets \EDec(\osk,\cinsp)$, and computes $\proofins \gets
+\NIZKProve^{\RelIns}(\crsins,\osk,(\cinsp,\yinsp))$. It
+returns $(\yinsp,\proofins)$.
+
+\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\proofins,\Sig,\msg)$.} %
 To assess the validity of an opening proof, first check the signature
@@
 parse \Sig as $((\cdot,\cinsp),\cdot)$ and verify \NIZKproof with
-$\NIZKVerify(\NIZKcrs_{\Open},\NIZKproof,(\cinsp,\yinsp))$. Accept it the NIZK
+$\NIZKVerify(\crsins,\proofins,(\cinsp,\yinsp))$. Accept it the NIZK
 verification passes, and reject otherwise.
@@
 
-We state the correctness and security theorems next. For lack of space, we defer
-the proofs to \appref{app:uas-proofs}.
+We state the correctness and security theorems next, and defer the proofs to
+\appref{app:uas-proofs}.
 
@@
   If the underlying NIZK system for \RelSig is zero-knowledge and simulation
-  extractable, the NIZK system for \RelIns is simulation-extractable, and the
+  extractable, the NIZK system for \RelIns is simulation extractable, and the
   \SBCM scheme is blind, then our \CUASGen
@@
 \end{theorem}
-
-\markulf{Put proofs here for XXXX?}\jesus{I can't parse XXXX.}
 
@@
 However, since probably the most common use of interactive presentations simply
-worry about preventing replay attacks, we leave a more detailed analysis of
+worries about preventing replay attacks, we leave a more detailed analysis of
 possible transforms (still meeting the \UAS model) out of scope.

### 2022-10-03 prism-backend/research/gsac/introduction-paper.tex
Added back issuance unforgeability to fix issuance flaw. Updated rest of the paper. Proofs can be improved.
Pass.

@@
 schemes also incorporate some sort of utility after authentication, like
-AC schemes with revocation \cite{cks10}, or with ``watchlists'' \needcite.
+AC schemes with revocation \cite{cks10}.
 
@@
 accountability  is barely present in AC schemes. For instance, non-frameability
-is not even considered, and it is non-frameability what prevent honest users
+is not even considered, and it is non-frameability what prevents honest users
 from being held accountable of dishonest actions they did not take part in.
@@
 too granular information at signing or opening time reduces privacy. However, on
-this occasion, signers controls ``how deanonymizable'' their signatures will
+this occasion, signers control ``how deanonymizable'' their signatures will
 be, and know it at signature generation time. This flexibility on the opening
@@
 restrictions of our generic construction imply the GS and AC ancestors of UAS.
-But this includes not only their vanilla versions, but also relevant variants,
+This includes not only their vanilla versions, but also relevant variants,
 such as MPS \cite{ngsy22}, (a modified version of) group signatures with

### 2022-10-03 prism-backend/research/gsac/preliminaries-paper.tex
Pass.

@@
 pair, algorithm $\Ec \gets \EEnc(\ek,\msg)$ encrypts message \msg with
-encryption key \Eek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\dk,
+encryption key \ek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\dk,
 \Ec)$ decrypts ciphertexts using decryption key \Edk. We rely on IND-CCA
@@
 %
-$\SBCMbsig \gets \SBCMSign^{\NIZKRel}(\sk,\Ccom,\pi,\smsg; x')$ is run by the
-signer, to produce a partial signature \SBCMbsig over a set of committed
+$\bsig \gets \SBCMSign^{\NIZKRel}(\sk,\Ccom,\pi,\smsg; x')$ is run by the
+signer, to produce a partial signature \bsig over a set of committed
 messages and set \smsg, satisfying relation \NIZKRel.
 %
-$\SBCMsig \gets \SBCMUnblind^{\NIZKRel}(\vk,\SBCMbsig,\Ccom,r,\osmsg,\smsg)$ is
-run by the user to complete a partial signature \SBCMbsig received by the
+$\sig \gets \SBCMUnblind^{\NIZKRel}(\vk,\bsig,\Ccom,r,\osmsg,\smsg)$ is
+run by the user to complete a partial signature \bsig received by the
 signer, over \osmsg (committed to in \Ccom) and \smsg.
@@
 relation $\NIZKRel$; $\parm_X$ are the public parameters for scheme $X$, etc.
+Similarly, schemes algorithms are prefixed with acronyms identifying the scheme
+(e.g., \ESetup, \NIZKSetup), which we may omit when clear from context.
 Variables written in bold font denote sets, e.g., while we use \ipk to denote a

### 2022-10-03 prism-backend/research/gsac/relationships.tex
Forgot to update theorems. Need to sync with proofs.
Pass.

@@
 \UAS-acceptable (for $\rngfissue = \bin$); whereas $\fissue^{single,H,I}$ is
-\UAS-acceptable if $F$ is a secure PRF \cite{kl14}.
+\UAS-acceptable if $H$ is a secure PRF \cite{kl14}.
 
@@
 signature, along with a correctness proof. For ease of exposition, assume that,
-w.l.o.g., this index is just the public key that the group member generates
-randomly when joining the group\footnote{The user public key is assumed to be
+without loss of generality, this index is just the public key that the group
+member generates randomly when joining the group\footnote{The user public key is
+  assumed to be
   accessible from a public table in \cite{bsz05}, so it is easy to translate the
@@
 
-      \vspace*{5em}
+      \vspace*{3em}
 
@@
   \caption{Security games for group signatures \cite{bsz05}, only with minor    
-    ``harmless'' edits to compare easier with \CUASGS. Concretely, since we
+    ``harmless'' edits to ease comparison with \CUASGS. Concretely, since we
     output {\upk}s instead of indexes, $i=0$ in the traceability game now reads
@@
 restriction, is a secure group signature scheme according to \cite{bsz05}.
-As stated, $\fissue^{single,H,I}$ is an \UAS-acceptable function if $F$ is a
+As stated, $\fissue^{single,H,I}$ is an \UAS-acceptable function if $H$ is a
 PRF. In that case, its output is a random-looking string that depends on the
 user public key \upk, and a string $I$ uniquely identifying the issuer. Thus, it
-will be the same per $(\upk,I)$ pair, and can be used by issuer $I$ to prevent
+will be the same per $(I,\upk)$ pair, and can be used by issuer $I$ to prevent
 issuing more than one credential per user. Basically, the issuer maintains a
-list of received $\yissue = F(\upk,I)$ values, and rejects issuing a credential
+list of received $\yissue = H(I,\upk)$ values, and rejects issuing a credential
 for already existing ones. From this, the GS algorithms are as
@@
 \item[$(\gpk,\isk,\osk) \gets KeyGen(1^\secpar)$.] Runs \Setup from \CUASGen,
-  and one instance of \KeyGen and \ISet with $\fissue^{single,H,I}$ (both for
-  the same user, who will be the only issuer in the GS scheme) and \OKeyGen.
+  and two instances of \KeyGen. One followed by \ISet with $\fissue^{single,H,
+    I}$ for the same user, who will be the issuer; and another for a different
+  user, who will be the opener, followed with \OKeyGen with $\finsp^{\upk}$.
   Assigns the public keys to \gpk.
@@
   $(\ipk,\opk)$, and returns whatever \CUASGen outputs in $\Open(\osk,\ipk,\sig,
-  0,\msg,\feval^0)$. Internally, the call to \Open runs $\finsp^{\upk}$.
+  0,\msg,\feval^0)$, which internally runs $\finsp^{\upk}$.
 \item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Parses \gpk as $(\ipk,
@@
         ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
-        (i_0,i_1,R,\msg,\st) \gets \adv^{\oracle{SIGN}}(\pk_1,\dots,\pk_n) \\
+        (i_0,i_1,R,\msg,\st) \gets \adv^{\oracle{Sign}}(\pk_1,\dots,\pk_n) \\
         \pcif R \not\subseteq \lbrace \pk_i \rbrace_{i\in[n]} \lor
@@
         ((\pk_1,\sk_1),\dots,(\pk_n,\sk_n)) \gets KeyGen(1^\secpar) \\
-        (R,\sig,\msg) \gets \adv^{\oracle{SIGN},\oracle{CORR}}
+        (R,\sig,\msg) \gets \adv^{\oracle{Sign},\oracle{Corr}}
         (\pk_1,\dots,\pk_n) \\
@@
         CU~\land \\
-        \pcind \adv~\textrm{never queried}~SIGN(\cdot,R,\msg))
+        \pcind \adv~\textrm{never queried}~\oracle{Sign}(\cdot,R,\msg))
       }       
@@
   }
-  \caption{Security games for ring signatures \cite{bkm06}. The $\oracle{SIGN}$
+  \caption{Security games for ring signatures \cite{bkm06}. The $\oracle{Sign}$
     oracle accepts $(i,R,\msg)$ tuples, with $pk_i \in R$, adds the tuple to a
     list of queries, and returns $\sig \gets Sign(\sk_i,R,\msg)$.
-    $\oracle{CORR}$ accepts an index $i$, and leaks $\sk_i$. Corrupted users are
+    $\oracle{Corr}$ accepts an index $i$, and leaks $\sk_i$. Corrupted users are
     added to $CU$.}
@@
   [n]$ where $\pk_i \in R$, first acts both as user and issuer to self-issue a
-  credential \Cred over an attribute set \attrs such that $\attrs \subseteq
-  \sring$. The user picks some \dattrs such that $\dattrs \subseteq [|\attrs|]$,
-  and computes the ring signature by running $\Sig = (\sig,\yeval) \gets
+  credential \Cred over an attribute set \attrs such that $\attrs = \sring$. The
+  user picks some \dattrs such that $\dattrs \subseteq [|\attrs|]$, and computes
+  the ring signature by running $\Sig = (\sig,\yeval) \gets
   \Sign(\usk,\opk,\Cred,\msg,\feval^{\sring,\dattrs})$ from
   \CUASGenHideIss. Note that \dattrs defines the public keys within
-  $\attrs \subseteq \sring$ to be revealed through \yeval.
+  $\attrs = \sring$ to be revealed through \yeval.
 \item[$1/0 \gets Verify(R,\Sig,\msg)$.] Parses \Sig as $(\sig,\yeval)$ and
@@
 and $\langle Show,Verify \rangle$ interactive protocols. We
-refer to \cite{fhs19} for the full details. For ease of reference, we summarize
+refer to \cite{fhs19} for the full details. For ease of reference, we give
 the security definitions in \figref{fig:model-ac}.% , with inocuous
@@
   Runs the interactive $\langle \Sign, \Verify\rangle$ of  \CUASGenInt,
-  using $\feval^{\dattrs}$ as signature evaluation function, and $\finsp^0$ as
+  using $\feval^{\dattrs}$ as evaluation function, and $\finsp^0$ as
   open function, with \opk from \parm as opener public key. The \yeval value
-  output by the verifier, when it accepts, is the $\yeval^0$ value produced by
+  output by \Verify, when it accepts, is the $\yeval^0$ value output by
   \Sign in \CUASGenInt.

### 2022-10-03 prism-backend/research/gsac/uas-paper.tex
Pass.

@@
   game-based model that generalises and unifies GS and AC schemes. The key to
-  this flexibility lies in functional placeholders
-  that, with careful constraints, still allow to capture generalised notions of
-  the usual anonymity, unforgeability and non-frameability properties. We refer
-  to this unified model as \emph{Universal Anonymous Signatures} (\UAS).
+  this flexibility lies in functional placeholders that, with careful
+  constraints, allow to capture generalised notions of the usual anonymity,
+  unforgeability and non-frameability properties. We refer to this unified model
+  as \emph{Universal Anonymous Signatures} (\UAS).
 
-  To showcase the generality of \UAS, we give a construction following our
-  model and prove that, from it, we can easily build multiple
-  variants of group signatures, anonymous credentials, and ring signatures, just
-  by giving concrete definitions of the mentioned functional placeholders.
+  To showcase the generality of \UAS, we give a construction following our model
+  and prove that, from it, we can easily build multiple variants of group
+  signatures, anonymous credentials, and even ring signatures, just by giving
+  concrete definitions of the mentioned functional placeholders.
 
-  Our main theoretical contribution is unifying previously separate (albeit
+  Our main theoretical contribution is thus unifying previously separate (albeit
   close) systems under the same generalised model. Such unified model also
-  allows to, very easily, build ``hybrid'' systems combining features
-  of previously separately modelled constructions: e.g., anonymous credentials
-  with conditional deanonymization based on their attributes.
+  allows to, very easily, build ``hybrid'' systems combining features of its
+  ancestors: e.g., anonymous credentials with conditional deanonymization based
+  on their attributes.
 
@@
   can reach the desired utility-vs-privacy tradeoff that best suits their needs,
-  just by defining a few functions -- but without needing to prove security from
-  scratch or implement a whole system.
+  just by defining a few functions -- but without needing to model and prove
+  security from scratch or implement a whole system.
 \end{abstract}

### 2022-10-04 prism-backend/research/gsac/app-related-proofs.tex
30 pages.

@@
 
-We prove that our \CUASGS construction is a secure group signature scheme,
-according to \cite{bsz05}, if the underlying \CUASGen construction is secure.
+We prove that our \CUASGS construction is an anonymous, traceable, and
+non-frameable group signature scheme, according to the model in \cite{bsz05}, if
+the underlying \CUASGen construction is secure.
 
@@
 
-We prove that our \CUASRing construction is anonymous and unforgeable, if
-the underlying $\CUASGen^{hide-iss}$ construction is secure.
+We prove that our \CUASRing construction is anonymous and unforgeable, in the
+model given in \cite{bkm06}, if the underlying $\CUASGen^{hide-iss}$
+construction is secure.
 

### 2022-10-04 prism-backend/research/gsac/app-uas-proofs.tex
30 pages.

@@
 
-Next, we define the \SimSetup, \ExtractIssue, \ExtractSign functions. \SimSetup
-(formally defined in \figref{fig:helper-funcs}) essentially replaces the
-\Setup algorithm of each NIZK with the corresponding \NIZKSimSetup algorithm,
-and returns the generated parameters along with the
+Next, we define the \SimSetup, \ExtractIssue, \ExtractSign, and \VerCred
+functions. \SimSetup (formally defined in \figref{fig:helper-funcs}) essentially
+replaces the \Setup algorithm of each NIZK with the corresponding \NIZKSimSetup
+algorithm, and returns the generated parameters along with the
 trapdoors. \ExtractIssue and \ExtractSign simply run the \Extract functions
@@
 that of \Setup, and the extracted values match those used as witnesses in the
-proofs.
+proofs. Finally, \VerCred simply calls the \SBCMVerify function with the
+received data -- where \usk is signed in committed form, \cid and \attrs in
+plain form, and \cred is their alleged signature by the owner of public key
+\ipk.
 
@@
 \begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
+  We show that, assuming simulation extractability of the NIZK for \RelIss, and
+  correctness and unforgeability of \SBCM, then \CUASGen has issuance
+  unforgeability.
+
+  Observe that we restrict to credentials issued by honest issuers. Thus, if a
+  credential with identifier \cid was issued by an honest issuer, a matching
+  $\trans[\cid]$ entry corresponding to its issuance must exist.
+  %
+  Then, $\trans[\cid] = (\yissue,\utrans)$, and \utrans contains a NIZK proof
+  \proofiss proving knowledge by the (potentially corrupt) user of a witness in
+  \RelIss. Since the issuer is honest, it verifies the NIZK as part of the
+  issuance protocol, rejecting if the proof is not valid. Thus, by simulation
+  extractability, \ExtractIssue produces a $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
+  \cred_i,\ipk_i) \rbrace_{i\in[n]},(\cid,\attrs,\cred,\ipk))$ tuple.
+
+  Since credential \cid was honestly issued, simulation extractability and
+  correctness of \SBCM ensure that \VerCred returns $1$ when run over the values
+  output by \adv, along with the \usk extracted by \ExtractIssue. Also, by
+  simulation extractability, the value output by \fissue, when evaluated upon
+  the extracted values, must match the \yissue value stored alongside
+  $\trans[\cid]$.
+  %
+  In addition, the adversary wins if the \uid associated to the {\cid}s involved
+  in the request (i.e., both the \cid output by the adversary, as well as those
+  used to support its issuance) is not in \HU or \CU. This can happen if: (1)
+  all {\cid}s have the same owner \uid, but this \uid is different to all known
+  {\uid}s; or (2) $\OWNR[\scid] = \bot$ which, by definition of \OWNR happens if
+  not all of the involved {\cid}s in \scid have the same owner. Since the NIZK
+  used for \RelIss is simulation extractable -- where the issuer verifies that
+  all credentials are bound to the same \usk -- and due to correctness of \SBCM,
+  the probability that (2) happens is negligible, which means that all involved
+  {\cid}s have the same owner. Also, regarding (1), this owner must be in either
+  \HU or \CU as the \cid output by the adversary in step 2 has been produced via
+  \ISSUE or \OBTISS which, by definition, only accept known {\uid}s. Thus, the
+  probability that \adv~wins the \ExpForgeIssue game is negligible.
+
+  Finally, the adversary may also win if any of the $\cred_i$ credentials (1) is
+  not a valid signature by its issuer, or (2) if it is a valid signature by some
+  honest issuer who did not produce it. As before, (1) has negligible
+  probability due to simulation extractability of the NIZK for \RelIss. For (2),
+  assume that such a $\cred_i$ exists, then, it is an \SBCM forgery -- i.e., a
+  valid signature, verifiable under $\ipk_i$ belonging to an honest issuer, who
+  did not produce it via a call to \OBTISS or \ISSUE. Thus, it breaks the
+  one-more unforgeability property of \SBCM. By security of \SBCM, the
+  probability that it happens must be negligible.
+\end{proof}
+
+\iffalse
+\begin{proof}[\thmref{thm:issue-forge-uas}; Issuance unforgeability of \CUASGen]
   We show that the probability that \fissue outputs a wrong $\yissue$ value is
@@
 \end{proof}
-
+\fi
 \subsection{Signature Unforgeability}

### 2022-10-04 prism-backend/research/gsac/conclusion-paper.tex
30 pages.

@@
 
-The flexibility of our model is achieved via functional placeholders that
+Flexibility in our model is achieved via functional placeholders that
 modulate the behaviour at credential issuance time, the utility
-information ``leaked'' along with the produced signatures, and the utility
+information revealed along with the produced signatures, and the utility
 information extractable from already produced signatures. These functions are
-computed by the users themselves, who need to prove correct computation.
-Our setting combines features of anonymous credential schemes, like
-attribute-based credentials and multiple issuers, which we extend with openers
-(like in group signatures), but also enabling that multiple openers coexist.
-This further increases the flexibility, by removing the tight issuer-opener
-coupling in previous works.
+computed by the users, who prove correct computation. We include features of
+anonymous credential schemes, like attributes and multiple
+issuers, which we extend with openers (like in group signatures), enabling
+multiple openers to coexist. This further increases flexibility, by removing
+the tight issuer-opener coupling in previous works.
 
@@
 instantiations of our generic construction in order to evaluate efficiency in
-real-world use cases. Also, it may be interesting to come up with alternative
-generic constructions -- for instance, based on structure-preserving signatures.
+real-world use cases. Alternative generic constructions are also of interest --
+for instance, based on structure-preserving signatures.
 %

### 2022-10-04 prism-backend/research/gsac/formal-uas.tex
30 pages.

@@
 \item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and
-  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
-  The function \finsp defines the type of utility that will be extractable from
-  signatures.
+  function \finsp, an opener runs \OKeyGen to generate its key pair. \finsp
+  defines the utility extractable from signatures.
 \item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
@@
 These are the functional placeholders that allow modulating the behaviour of the
-resulting instantiation. They controll the conditions upon which new credentials
-can be issued, the information revealed at signing time, or extractable from
-signatures. In all cases, the user computes them, and proves correctness of
+resulting instantiation. They control the conditions for issuing new
+credentials, the information revealed alongside signatures, or extractable
+from them. In all cases, the user computes them, and proves correctness of
 such computation. We give concrete examples in \secref{sec:relationships}.
@@
   produced signature and signed message.
-\item[\CSIG.] Maintains challenge signatures output to the adversary in the
+\item[\CSIG.] Stores challenge signatures output to the adversary in the
   signature anonymity game, and is indexable by challenge signatures \csig.
@@
 \paragraph{Oracles.} %
-In the game-based definitions of our \UAS model, we leverage the following
-oracles, which are formally defined in \figref{fig:oracles1} and
+We leverage the following oracles, formalized in \figref{fig:oracles1} and
 \figref{fig:oracles2}.
@@
 %   the associated issuance function.
-\item[\HUGEN.] Adds a new honest user to the game, generating its keypair.
-\item[\CUGEN.] Adds a new corrupt user to the game, setting its \upk to the
-  value given by the adversary.  
-\item[\OGEN.] Adds a new opener to the game, generating its key pair and
-  setting its evaluation and opening functions.
+\item[\HUGEN.] Adds a new honest user, generating its keypair.
+\item[\CUGEN.] Adds a new corrupt user. Sets its \upk to the
+  one given by the adversary.  
+\item[\OGEN.] Adds a new opener, generates its key pair and sets its opening
+  function.
 % \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
@@
   \fissue function.
-\item[\UCORR.] Corrupts an existing (and honest) user, giving its secret
-  key to the adversary. If the user was also an issuer, it becomes a corrupt
-  issuer too.
-\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
-  key to the adversary.
+\item[\UCORR.] Corrupts an existing honest user, giving its \usk to the
+  adversary. If the user was also an issuer, it becomes a corrupt issuer too.
+\item[\OCORR.] Corrupts an existing honest opener, giving its \osk to the
+  adversary.
 % \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
@@
     \caption{Detailed oracles available in our model (1/2). Oracles for
-      generating key material for users, issuers, and openers.}
+      key generation.}
     \label{fig:oracles1}
@@
 
-      \begin{minipage}[t]{.5\textwidth}
+      \begin{minipage}[t]{.55\textwidth}
 
@@
 
-\paragraph{Helper functions \SimSetup, \ExtractIssue, and \ExtractSign.}
+\paragraph{Helper functions % \SimSetup, \ExtractIssue, and \ExtractSign
+  .}
 We assume the existence of these helper functions. They are not functions
@@
 \item[$\ExtractIssue(\trap,\utrans) \rightarrow (\upk,\usk,\sCred=
-  \lbrace(\cid_i,\attrs_i,\cred_i) \rbrace_{i \in [n]},
-  \Cred=(\cid,\attrs,\cred))$.]
+  \lbrace(\cid_i,\attrs_i,\cred_i,\ipk_i) \rbrace_{i \in [n]},
+  \Cred=(\cid,\attrs,\cred,\ipk))$.]
   Receives trapdoor \trap and a valid $\langle \Obtain, \Issue \rangle$
@@
   interaction in \utrans, along with the involved user key pair $(\upk,\usk)$
-  and, if any, the credential set \sCred used to request \Cred.
+  and the credential set \sCred used to request \Cred, of size $n$, where $n$
+  may be $0$.
 \item[$\ExtractSign(\trap,\Sig) \rightarrow
@@
 %   % used when the issuer is honest, as transcripts are needed.
+\item[$\VerCred(\usk,\cid,\attrs,\cred,\ipk) \rightarrow 1/0$.] Returns
+  $1$ if \cred is a valid credential with identifier \cid, issued by an issuer
+  with public key \ipk, over attributes \attrs, and bound to user secret key
+  \usk. Otherwise, it returns $0$.
 \end{description}
@@
 requirements set by the corresponding issuer, and that any further credential
-involved in the request is bound to the same known user. For this, we allow the
-adversary \adv~to interact with the oracles (restricted to honest issuers).
-Eventually, \adv~is challenged to output a credential identifier from which we
-extract the actual witnesses used in the credential request associated to \cid.
-\adv~wins if the issuance function, applied to the extracted values, does not
-meet the expected output, or if not all of the credentials (if any) used to
-support the request belong to the same (known) user to whom the new credential
-was issued. Note that the issuance transcript associated to \cid must exist, as
-we unavoidably need to restrict to honest issuers. Indeed, a dishonest issuer
-cannot be trusted to enforce any policy, nor to properly keep all transcripts.
+involved in the request is a valid credential, bound to the same known user. For
+this, we allow the adversary \adv~to interact with the oracles (restricted to
+honest issuers). Eventually, \adv~is challenged to output a credential \Cred
+from which we extract the actual witnesses used in the credential request
+associated to \cid. \adv~wins if the issuance function, applied to the extracted
+values, does not meet the expected output, if not all of the credentials (if
+any) used to endorse the request belong to the same (known) user to whom the new
+credential was issued, or if any of such credentials is a forgery. Note that the
+issuance transcript associated to the credential output by the adversary must
+exist, as we unavoidably need to restrict to honest issuers. Indeed, a dishonest
+issuer cannot be trusted to enforce any policy, nor to properly keep all
+transcripts.
 
@@
   \scalebox{0.85}{
-    \begin{minipage}[t]{0.6\textwidth}
+    \begin{minipage}[t]{0.7\textwidth}
       \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
         (\parm,\trap) \gets \SimSetup(1^\secpar) \\
-        % (\Cred,\uid,\iid,\oid,\feval,\msg) \gets \adv^{\Oforge}(\parm) \\
-        % \Sig \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\Cred,\msg,\feval) \\
-        % \pcif \Verify(\PUBOK[\oid],\PUBIK[\iid],\Sig,\msg,\feval) = 0: \\
-        % \pcind \pcreturn 0 \\
-        % (\upk,\usk, (\cid,\attrs,\cdot), \cdot, \cdot) \\
-        % \pcind \gets \ExtractSign(\trap,\oid,\iid,\Sig,\msg,\feval) \\
-        % \pcif \trans[\cid] = \bot \lor \CRED[\cid] = \bot: \pcreturn 1 \\
-        % (\yissue,\cdot) \gets \trans[\cid];
-        % ((\cdot,\fissue),\cdot) \gets \PUBIK[\cid] \\
-        % \pcif \nexists \lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]}
-        % \in \CRED[\uid]~\suchthat \\
-        % \pcind \fissue(\upk,\cid,\attrs,
-        % \lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]}) = \yissue: \\
-        % \pcind \pcreturn 1
-        % 
-        % ((\upk_1,r_1,\Ccom_1),\dots,(\upk_l,r_l,\Ccom_l),\st) \\
-        % \pcind \gets \adv^{\HUGEN,\CUGEN}(\texttt{choose},\parm) \\
-        % \pcif \exists i\in[l]~\suchthat~\forall \uid,
-        % \upk_i \neq \PUBUK[\uid]:  \\
-        % \pcind \pcreturn 0 \\
-        % \cid \gets \adv^{\Oforge}(\texttt{forge},\st,\parm) \\
+        (\cid,\attrs,\cred,\ipk) \gets \adv^{\Oforge}(\parm) \\
+        \pcif \ISR[\cid] \notin \HI \lor \trans[\cid] = \bot: \pcreturn 0 \\
+        (\utrans,\yissue) \gets \trans[\cid] \\
+        (\upk,\usk,\lbrace \Cred_i \rbrace_{i\in[n]}, \Cred)
+        \gets \ExtractIssue(\trap,\utrans) \\
+        \forall i\in[n], (\cid_i,\attrs_i,\cred_i,\ipk_i) \gets \C_i \\
+        (\cid,\attrs,\cred,\ipk) \gets \C;
+        \scid \gets \lbrace \cid_i \rbrace_{i\in[n]} \cup
+        \lbrace \cid \rbrace \\
+        \pcif \VerCred(\usk,\cid,\attrs,\cred,\ipk) = 0~\lor \\
+        \pcind \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\attrs_i)
+        \rbrace_{i\in[n]}) \neq \yissue~\lor \\
+        \pcind \OWNR[\scid] \notin \HU \cup \CU: \pcreturn 1 \\        
+        \pcif \exists i\in[n]~\suchthat~
+        \VerCred(\usk,\cid_i,\attrs_i,\cred_i,\ipk_i) = 0~\lor \\
+        \pcind (\exists \iid\in\HI~\suchthat~\PUBIK[\iid] = \ipk_i \land
+        \CRED[\cid_i] = \bot~\land \\
+        \pcind \VerCred(\usk,\cid_i,\attrs_i,\cred_i,\ipk_i) = 1):
+        \pcreturn 1 \\        
+        \pcreturn 0
+        %
+        \iffalse
         \cid \gets \adv^{\Oforge}(\parm) \\
@@
         (\utrans,\yissue) \gets \trans[\cid] \\
-        (\upk,\cdot,\lbrace (\cid_i,\attrs_i) \rbrace_{i\in[n]},\cdot,\attrs,
-        \cdot) \gets \ExtractIssue(\trap,\utrans) \\
+        (\upk,\cdot,\lbrace (\cid_i,\attrs_i,\cred_i,\ipk_i) \rbrace_{i\in[n]},
+        \cdot,\attrs,\cdot,\cdot) \\
+        \pcind \gets \ExtractIssue(\trap,\utrans) \\
         \textrm{Let $\scid \gets \lbrace \cid_i \rbrace_{i\in[n]} \cup
@@
         \neq \yissue
+        \fi
       }      
@@
 
-In this section, we give a generic construction of an \UAS scheme, based on
+We give a generic construction of an \UAS scheme, based on
 generic building blocks. We use three different NP relations: \RelIss, \RelSig,
 and \RelIns, described next and specified in CS notation \cite{cs97} in
-\figref{fig:nizkrels}. Crucially, these relations include verifying that the
-comptuation of the \fissue, \feval and \finsp functions has been done correctly.
+\figref{fig:nizkrels}. These relations include verifying that the comptuation of
+the \fissue, \feval and \finsp functions has been done correctly.
 
@@
 A user willing to become an issuer just sets $\ipk \gets (\upk,\fissue)$, and
-publishes \ipk. We assume that {\ipk}s are published in some properly (probably
+publishes \ipk. We assume that {\ipk}s are published in some proper (probably
 authenticated) way.
@@
 
-We state the correctness and security theorems next, and defer the proofs to
+We now state the correctness and security theorems, and defer the proofs to
 \appref{app:uas-proofs}.
@@
   If the underlying NIZK used for \RelIss is simulation extractable, and the
-  underlying \SBCM scheme is correct, then our \CUASGen construction satisfies
-  issuance unforgeability as defined in \defref{def:issue-forge-uas}.
+  underlying \SBCM scheme is correct and one-more unforgeable, then our \CUASGen
+  construction satisfies issuance unforgeability as defined in
+  \defref{def:issue-forge-uas}.
 \end{theorem}
@@
 In group signatures, signing and verification are non-interactive processes;
-whereas in anonymous credentials, they are an interactive protocol. \CUASGen
-targets the non-interactive approach. Now, we sketch how to transform this into
-an interactive protocol with replay protection.
+whereas in anonymous credentials, it is an interactive protocol. While
+\CUASGen targets the non-interactive approach, we sketch how to transform it
+into an interactive protocol with replay protection.
 

### 2022-10-04 prism-backend/research/gsac/introduction-paper.tex
30 pages.

@@
 Privacy-preserving signature and authentication systems have been a prolific
-field in the last decades. Anonymous credentials (AC) \cite{chau85} and group
-signatures (GS) \cite{ch91} are among the most relevant schemes. In both, the
+field for decades. Anonymous credentials (AC) \cite{chau85} and group signatures
+(GS) \cite{ch91} are among the most relevant schemes. In both, the
 high-level idea is common: users obtain credentials, which can then use to
@@
 \paragraph{Evolution of AC and GS.} %
-AC and GS systems have followed separate paths, with some exceptions.
+AC and GS systems have followed separate paths, with exceptions.
 Functionality-wise, Attribute-Based Group Signatures add attributes to the
-credentials issued to group members, who can later use them to prove pre-fixed
+credentials issued to group members, who can later use them to prove fixed
 claims \cite{emo09,aa14}. Hidden identity-based signatures also add attributes
-to the credentials, with the aim of preventing the opener (the trusted party who
+to the credentials, to prevent the opener (the trusted party who
 can deanonymize signers) from having to rely on the issuer in order to return
 meaningful identifying information when opening a signature \cite{ks07}. Some AC
-schemes also incorporate some sort of utility after authentication, like
-AC schemes with revocation \cite{cks10}.
+schemes also incorporate some utility after authentication, like
+revocable AC schemes \cite{cks10}.
 
@@
 \paragraph{Limitations of GS and AC.} %
-However, even the generalisation efforts that have independently taken place in
-GS and AC have limited applicability in the real world. On the GS side, even
-though MPS achieves a powerful balance on when a signature is
-deanonymizable and what information can be extracted from it, upon closer look,
-this information is somehow meaningless. Namely, the notion of identity is not
-well defined and, thus, it is not possible to assess whether the value output by
-their generalised open function makes sense or even if it is legitimate. Also,
-just being able to prove membership at signing time is typically not enough. In
-other words, in GS, utility at authentication time is very limited -- but this
-is precisely the main strength in AC schemes, which also have a well defined
-notion of identity via attributes. On the other hand, the notion of
-accountability  is barely present in AC schemes. For instance, non-frameability
-is not even considered, and it is non-frameability what prevents honest users
-from being held accountable of dishonest actions they did not take part in.
+Even the independent generalisation efforts in both GS and AC
+have limited applicability in the real world. On the GS side, although MPS
+achieves a powerful balance on when a signature is deanonymizable and what
+information can be extracted, upon closer look, this information is somehow
+meaningless. Namely, the notion of identity is not well defined and, thus, it is
+not possible to assess whether the value output by their generalised open
+function makes sense or even if it is legitimate. Also, proving membership at
+signing time is typically not enough. In other words, in GS,
+utility at authentication time is very limited. This is precisely the main
+strength in AC schemes, which also have a well defined notion of identity via
+attributes. Conversely, the notion of accountability  is barely present in AC
+schemes. For instance, non-frameability is not even considered, and it is
+non-frameability what prevents honest users from being held accountable of
+dishonest actions they did not take part in.
 %

### 2022-10-04 prism-backend/research/gsac/preliminaries-paper.tex
30 pages.

@@
 proof systems over the produced signature and signed (commitments to) messages.
-For this purpose, we define such schemes as a tuple (\SBCMSetup,\SBCMKeyGen,
-\SBCMBlind,\SBCMSign,\SBCMUnblind,\SBCMVerify).
+We define such schemes as a tuple (\SBCMSetup, \SBCMKeyGen,
+\SBCMBlind, \SBCMSign, \SBCMUnblind, \SBCMVerify).
 %
@@
 $(\Ccom,\pi,r) \gets \SBCMBlind^{\NIZKRel}(\vk,\osmsg,\smsg;x',w')$ is run by a
-user who wants to request a signature over $\osmsg \cup \smsg$, where only \smsg
-are revealed to the signer, and $\osmsg$ are to be signed in committed form.
+user to request a signature over $\osmsg \cup \smsg$, where \smsg are revealed
+to the signer, but \osmsg are signed in committed form.
 Moreover, \osmsg (and, possibly, $w'$) are witnesses to some statement defined
@@
 signer, to produce a partial signature \bsig over a set of committed
-messages and set \smsg, satisfying relation \NIZKRel.
+messages \osmsg and set \smsg, satisfying relation \NIZKRel.
 %
@@
 run by the user to complete a partial signature \bsig received by the
-signer, over \osmsg (committed to in \Ccom) and \smsg.
+signer.
 %

### 2022-10-04 prism-backend/research/gsac/relationships.tex
30 pages.

@@
 that they securely instantiate the models for the presented schemes, if the
-corresponding \CUASGen restriction is a secure \UAS construction. Concretely,
-we rely on the functions described in \figref{fig:func-restrictions}. Observe
-that all the \fissue functions listed in \figref{fig:func-restrictions} are
-\UAS-acceptable. Specifically, $\fissue^1$ and $\fissue^{\sring}$ are trivially
-\UAS-acceptable (for $\rngfissue = \bin$); whereas $\fissue^{single,H,I}$ is
-\UAS-acceptable if $H$ is a secure PRF \cite{kl14}.
+corresponding \CUASGen restriction is a secure \UAS construction. For lack of
+space, security proofs are deferred to \appref{app:related-proofs}.
+
+For the described \CUASGen restrictions, we rely on the functions described in
+\figref{fig:func-restrictions}. Observe that all the \fissue functions listed in
+\figref{fig:func-restrictions} are \UAS-acceptable. Specifically, $\fissue^1$
+and $\fissue^{\sring}$ are trivially \UAS-acceptable (for $\rngfissue = \bin$);
+whereas $\fissue^{single,H,I}$ is \UAS-acceptable if $H$ is a secure PRF
+\cite{kl14}.
 
@@
 
-We adopt the model in \cite{bsz05}. In this abstraction of group signatures, the
-opener returns an index uniquely identifying the group member that created a
-signature, along with a correctness proof. For ease of exposition, assume that,
-without loss of generality, this index is just the public key that the group
-member generates randomly when joining the group\footnote{The user public key is
+We adopt the model in \cite{bsz05}. In this abstraction, the opener returns an
+index uniquely identifying the group member who created a signature, along with
+a correctness proof. To ease exposition, we assume without loss of generality
+that this index is just the public key that group members generate randomly
+when joining the group\footnote{The user public key is
   assumed to be
   accessible from a public table in \cite{bsz05}, so it is easy to translate the
-  public key into an index, if needed.}. A group signature scheme, according to
-\cite{bsz05}, is composed of $KeyGen$, \UKeyGen, \Sign, \Verify, \Open and
-\Judge algorithms, as well as an $\langle\Obtain,\Issue\rangle$ interactive
+  public key into an index, if needed.}. A group signature scheme in
+\cite{bsz05} is composed of $KeyGen$, \UKeyGen, \Sign, \Verify, \Open and
+\Judge algorithms, and an $\langle\Obtain,\Issue\rangle$ interactive
 protocol. Their intuition is similar to that of \UAS, so we refer to
@@
 \subsubsection{\CUASGS construction.} %
-We show that the $(\fissue^{single,H,I},\feval^0,\finsp^{\upk})$-\CUASGen
-restriction, is a secure group signature scheme according to \cite{bsz05}.
+We show that a $(\fissue^{single,H,I},\feval^0,\finsp^{\upk})$-\CUASGen
+restriction is a secure group signature scheme according to \cite{bsz05}.
 As stated, $\fissue^{single,H,I}$ is an \UAS-acceptable function if $H$ is a
-PRF. In that case, its output is a random-looking string that depends on the
-user public key \upk, and a string $I$ uniquely identifying the issuer. Thus, it
-will be the same per $(I,\upk)$ pair, and can be used by issuer $I$ to prevent
-issuing more than one credential per user. Basically, the issuer maintains a
-list of received $\yissue = H(I,\upk)$ values, and rejects issuing a credential
-for already existing ones. From this, the GS algorithms are as
-follows:
+PRF, as its output is a random-looking string that depends on the user public
+key \upk, and a string $I$ uniquely identifying the issuer. Thus, it is the same
+per $(I,\upk)$ pair, and can be used by issuer $I$ to prevent issuing more than
+one credential per user. Basically, the issuer keeps a list of received
+$\yissue = H(I,\upk)$ values, and rejects issuing a credential for already
+existing ones. From this, the GS algorithms are as follows:
 
@@
 
-\paragraph{Security of \CUASGS.} %
-Our \CUASGS construction is an anonymous, traceable, and non-frameable group
-signature scheme, according to the model in \cite{bsz05}. For space constraints,
-proofs are deferred to \appref{app:related-proofs}.
+% \paragraph{Security of \CUASGS.} %
+% Our \CUASGS construction is an anonymous, traceable, and non-frameable group
+% signature scheme, according to the model in \cite{bsz05}. For space constraints,
+% proofs are deferred to \appref{app:related-proofs}.
 
@@
 \subsubsection{\CUASRing Construction.} %
-We can use a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
-of \CUASGenHideIss to build a ring signature scheme according to the model
-in \figref{fig:model-rs}. In a nutshell, we let users self-issue
-credentials where the attributes are (a subset of encodings of) the public keys
-of the users in the system -- including their own public key. Then, a ring
-signature is just a \CUASGenHideIss signature that reveals a subset of
-the attributes -- i.e., a subset of the keys of the users in the system. In more
-detail, the construction is as follows:
+We use a $(\fissue^{\sring},\feval^{\sring,\dattrs},\finsp^0)$-restriction
+of \CUASGenHideIss to build a ring signature scheme in the model given in
+\figref{fig:model-rs}. Briefly, users self-issue credentials where the
+attributes are (encodings of) the public keys of the users in the system --
+including their own public key. Then, a ring signature is just a
+\CUASGenHideIss signature that reveals a subset of the attributes -- i.e., a
+subset of the keys of the users in the system. The construction
+is as follows:
 
@@
 
-\paragraph{Security of \CUASRing.} %
-Our \CUASRing construction is an anonymous and unforgeable ring signature
-scheme, according to the model in \cite{bkm06}. For space constraints,
-proofs are deferred to \appref{app:related-proofs}.
+% \paragraph{Security of \CUASRing.} %
+% Our \CUASRing construction is an anonymous and unforgeable ring signature
+% scheme, according to the model in \cite{bkm06}. For space constraints,
+% proofs are deferred to \appref{app:related-proofs}.
 
@@
 
-We adopt the model in \cite{fhs19}, for anonymous credentials with selective
+We adopt the model in \cite{fhs19} for anonymous credentials with selective
 disclosure, which restricts to one credential per presentation. Therein, an
@@
 and $\langle Show,Verify \rangle$ interactive protocols. We
-refer to \cite{fhs19} for the full details. For ease of reference, we give
+refer to \cite{fhs19} for the full details. For readability, we give
 the security definitions in \figref{fig:model-ac}.% , with inocuous
@@
 \subsubsection{\CUASAC Construction.} %
-We show that a $(\fissue^1,\feval^{\dattrs},\finsp^0)$-\CUASGenInt
-restriction, is a secure anonymous credential scheme according to the model in
-\cite{fhs19}. We first quickly define the algorithms, and then prove security.
+We build a secure anonymous credential scheme directly from a
+$(\fissue^1,\feval^{\dattrs},\finsp^0)$-\CUASGenInt restriction.
 
@@
 
-\paragraph{Security of \CUASAC.} %
-Our \CUASAC construction is an anonymous and unforgeable anonymous credential
-scheme, according to the model in \cite{fhs19}. For space constraints,
-proofs are deferred to \appref{app:related-proofs}.
+% \paragraph{Security of \CUASAC.} %
+% Our \CUASAC construction is an anonymous and unforgeable anonymous credential
+% scheme, according to the model in \cite{fhs19}. For space constraints,
+% proofs are deferred to \appref{app:related-proofs}.
 

### 2022-10-04 prism-backend/research/gsac/introduction-paper.tex
Spellchecked abstract and intro.

@@
 GS schemes enhance utility after authentication, allowing partial
-re-identification like linking of signatures, or even full deanonymization.
+re-identification like linking of signatures, or even full deanonymisation.
 While actual applications of group signatures seem hard to find in the real
@@
 to the credentials, to prevent the opener (the trusted party who
-can deanonymize signers) from having to rely on the issuer in order to return
+can deanonymise signers) from having to rely on the issuer in order to return
 meaningful identifying information when opening a signature \cite{ks07}. Some AC
@@
 Also, \cite{ckl+15} gives a very generic approach to build AC schemes. In GS,
-very recently, BiAS \cite{lnpy21} and MPS \cite{ngsy22} flexibilize the
+very recently, BiAS \cite{lnpy21} and MPS \cite{ngsy22} flexibilise the
 trade-off between anonymity and accountability.
@@
 have limited applicability in the real world. On the GS side, although MPS
-achieves a powerful balance on when a signature is deanonymizable and what
+achieves a powerful balance on when a signature is deanonymisable and what
 information can be extracted, upon closer look, this information is somehow
@@
 opening time, the opener proves that some fixed user-related information is
-contained in the de-anonymized signature.
+contained in the deanonymised signature.
 
@@
 too granular information at signing or opening time reduces privacy. However, on
-this occasion, signers control ``how deanonymizable'' their signatures will
+this occasion, signers control ``how deanonymisable'' their signatures will
 be, and know it at signature generation time. This flexibility on the opening
@@
 that they are bound to the same key. Utility information to be revealed at
-signing time is output in plaintext, and utility information extractable by
+signing time is output in plain text, and utility information extractable by
 openers is encrypted under their public key -- in both cases, users prove
@@
 The latter is, in addition, fed and modulated with the output of \feval. With
-these functions, we allow achieving configurable utility-vs-privacy tradeoffs
-throughout the whole ``lifecycle'' (from issuance to opening). They also take
+these functions, we allow achieving configurable utility-vs-privacy trade-offs
+throughout the whole ``life-cycle'' (from issuance to opening). They also take
 a central role in defining the NP statements that need to be proven by different
@@
 one can easily instantiate GSs with with no revocation at all, ACs
-with full de-anonymization, RS with linkability, etc.
+with full deanonymisation, RS with linkability, etc.
 
@@
 \paragraph{Sample real-world use cases.} %
-By enabling customization at issuance, signing and opening times, as well as
+By enabling customisation at issuance, signing and opening times, as well as
 multiple uncoupled issuers and openers, the possibilities are large and
 especially useful in contexts where different parties may have different
-privacy-vs-utility tradeoffs. As an example, consider a social network that
+privacy-vs-utility trade-offs. As an example, consider a social network that
 requires under-age users to get permission from one parent. This can be defined

### 2022-10-04 prism-backend/research/gsac/uas-paper.tex
30 pages.
Spellchecked abstract and intro.

@@
 
-%% Set/unset to activate/deactivate author comments
+%% Set/unset to activate/deactivate author comments, anonymous submission, etc.
 \def\authnotes{0}
+\def\anonymous{1}
 
@@
 \title{Universal Anonymous Signatures}
+\ifnum\anonymous=1
+\author{}
+\institute{}
+\fi
+\ifnum\anonymous=0
 \author{Jesus Diaz\inst{1} \and Markulf Kohlweiss\inst{2}}
-
 \institute{Input Output Global,\\
@@
 \email{markulf.kohlweiss@ed.ac.uk}}
+\fi
 
@@
   allows to, very easily, build ``hybrid'' systems combining features of its
-  ancestors: e.g., anonymous credentials with conditional deanonymization based
+  ancestors: e.g., anonymous credentials with conditional deanonymisation based
   on their attributes.
@@
   In practice, this means that cryptographic engineers and system designers
-  can reach the desired utility-vs-privacy tradeoff that best suits their needs,
+  can reach the desired utility-vs-privacy trade-off that best suits their needs,
   just by defining a few functions -- but without needing to model and prove

### 2022-10-04 prism-backend/research/gsac/app-building-blocks.tex
Spellchecked full paper.

@@
 \item[$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$.] Given public parameters \Eparm,
-  produces an encryption-decryption keypair $(\Eek,\Edk)$.
+  produces an encryption-decryption key pair $(\Eek,\Edk)$.
 \item[$\Ec \gets \EEnc(\Eek,\msg)$.] Encrypts message \msg with encryption key
@@
 \in \NIZKRel$. For concrete relations, we write $\NIZKRel = \lbrace (\NIZKx),
-(\NIZKw): f(x,w) \rbrace$, where $f(x,w)$ is a boolean predicate denoting the
+(\NIZKw): f(x,w) \rbrace$, where $f(x,w)$ is a Boolean predicate denoting the
 concrete conditions that \NIZKx and \NIZKw need to meet. The set of all \NIZKx
@@
 algorithms refer to, we use $\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel$, 
-$\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and superindex when
+$\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and super-index when
 clear from context. Altogether, the tuple $(\Setup,\Prove,\Verify,\SimSetup,
@@
 
-As studied in \cite{cl06}, simulation-extractable NIZKPoKs formalize the concept
+As studied in \cite{cl06}, simulation-extractable NIZKPoKs formalise the concept
 of ``signatures of knowledge'' (see, e.g., \cite{cs97}). Which basically means
@@
   signer, with signing key \SBCMsk, produces a blind signature \SBCMbsig over
-  the messages commited to in commitment \SBCMcom, as well as the messages in
+  the messages committed to in commitment \SBCMcom, as well as the messages in
   \smsg, with associated proof $\pi$.
@@
   A user, who requested a signature over \osmsg and \smsg, where \SBCMcom is a
-  commitment over \osmsg using randomness $r$, finalizes the signature,
+  commitment over \osmsg using randomness $r$, finalises the signature,
   computing \SBCMsig from the signer's partial signature \SBCMbsig.
@@
 \paragraph{Augmented NIZKs.} %
-Constructions of \SBCM (e.g. \cite{asm06}), as well as the formalization we just
+Constructions of \SBCM (e.g. \cite{asm06}), as well as the formalisation we just
 described, require that the user proves, in zero-knowledge (via a NIZK),
@@
 Next, we give an instantiation of an \SBCM scheme, based on BBS+ signatures.
-We emphasize again that this is essentially equivalent to the protocol for
+We emphasise again that this is essentially equivalent to the protocol for
 signing committed block of messages in \cite{asm06} and, also, to the equivalent

### 2022-10-04 prism-backend/research/gsac/app-related-extra.tex
Spellchecked full paper.

@@
 \item[$1/0 \gets \Judge(\gpk,\pi,\upk,\sig,\msg)$.] Like in \CUASGen. Note that
-  \gpk includes an \opk with an opening fuction of type $\finsp^{\smsg}$.
+  \gpk includes an \opk with an opening function of type $\finsp^{\smsg}$.
 \end{description}
@@
 in MPS). In our \UAS model, we allow the adversary to corrupt openers at will
-(getting ther \osk), but the challenge signatures must have been generated using
+(getting their \osk), but the challenge signatures must have been generated using
 the key of an uncorrupted opener; still, \adv~can call the open oracle for
@@
 
-On the other hand, anonymous issuance and the capability to customize issuance
+On the other hand, anonymous issuance and the capability to customise issuance
 policies are unachievable by MPS. Anonymous issuance simply does not make sense
 in MPS, as it only supports one credential (without attributes) per user, and
-customized issuance is achieved in \UAS via the \fissue functions, with no
+customised issuance is achieved in \UAS via the \fissue functions, with no
 equivalent in MPS -- instead, MPS can be seen as having the fixed policy of
@@
 this is easy to add, we consider it to be essential, given that the proposed
-generalization of opening allows the opener to output ``any value''. Hence, the
+generalisation of opening allows the opener to output ``any value''. Hence, the
 need to ensure that the produced value is the legitimate one seems to be more
-necessary than ever. Finally, our \feval function is a generalization of $F$ in
+necessary than ever. Finally, our \feval function is a generalisation of $F$ in
 MPS, as it allows two outputs: one will be returned in the clear along with the
@@
 
-Finally, note that, in MPS, $G$ is further parameterized with a value $j$, which
+Finally, note that, in MPS, $G$ is further parameterised with a value $j$, which
 essentially is the result of applying $F$ to the message and signer identity,
@@
   the MPS model, we build \advB that breaks signature unforgeability of the
-  underyling \CUASGen, as defined for \UAS.
+  underlying \CUASGen, as defined for \UAS.
 
@@
   Given an adversary \adv~against unforgeability-2 of \CUASMPS, as defined in
-  the MPS model, we build \advB that breaks non-frameability of the underyling
+  the MPS model, we build \advB that breaks non-frameability of the underlying
   \CUASGen, as defined for \UAS.
@@
 \figref{fig:func-restrictions}, and $\feval^{\dattrs,H,V,L}$ and $\finsp^{H}$
-are ase specified in \esref{eq:funcs-rac}.
+are as specified in \esref{eq:funcs-rac}.
 
@@
   \adv's oracles are simulated as in the proof for issuance anonymity of
-  \CUASDAC -- in this case, \adv's \oracle{SigLoR} oracle corresonds to \advB's
+  \CUASDAC -- in this case, \adv's \oracle{SigLoR} oracle corresponds to \advB's
   \CHALb. Again, the simulation is perfect, and whenever \adv~wins its

### 2022-10-04 prism-backend/research/gsac/app-uas-proofs.tex
Spellchecked full paper.

@@
   We prove the special case in which the adversary makes only one query to the
-  \OBTCHALb oracle. The generalization to polynomially many queries follows
+  \OBTCHALb oracle. The generalisation to polynomially many queries follows
   from a standard hybrid argument.
@@
   In this proof, we restrict to the case in which the adversary can only make
-  one query to the challenge oracle. Note however that the generalization to
+  one query to the challenge oracle. Note however that the generalisation to
   polynomially many queries given in \cite{bsz05} applies here too (with the
@@
   \paragraph{(c) The output of \finsp matches the output of \Open.} %
-  After (a), and correctness of the public key encryption algorihtm, the \yinsp
+  After (a), and correctness of the public key encryption algorithm, the \yinsp
   value output by \Open is the correct decryption of
@@
 signature anonymity, assume an adversary \adv~that breaks it. We build \advB
-against the non-interactive \ExpSigAnonb from \adv~as follows. \advB initializes
+against the non-interactive \ExpSigAnonb from \adv~as follows. \advB initialises
 everything as in the \ExpSigAnonb game. When \adv~initiates a call to its

### 2022-10-04 prism-backend/research/gsac/conclusion-paper.tex
Spellchecked full paper.

@@
 and provide a generic construction, secure in our model, that allows
-different privacy-vs-utility tradeoffs to be reached.
+different privacy-vs-utility trade-offs to be reached.
 %
@@
 signatures promises to be interesting, both regarding its modelling, the
-potential use cases, and the generalization capabilities.
+potential use cases, and the generalisation capabilities.
 

### 2022-10-04 prism-backend/research/gsac/formal-uas.tex
Spellchecked full paper.

@@
-\section{Formalizing \UAS}
+\section{Formalising \UAS}
 \label{sec:formal-uas}
@@
 
-Next we formalize our notion of Universal Anonymous Signatures
+Next we formalise our notion of Universal Anonymous Signatures
 (\UAS). We define its syntax, model, and give a generic construction, which
@@
 \item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
-  pair, and an issuance function \fissue for checking that credential requestors
+  pair, and an issuance function \fissue for checking that credential requesters
   meet some conditions to be issued a credential, an existing user runs \ISet to
@@
 cases of our generic construction that target a concrete variant of the
-utility-privacy tradeoff by defining concrete \fissue, \feval and \finsp
+utility-privacy trade-off by defining concrete \fissue, \feval and \finsp
 functions. Security of \CUASGen implies security of its restrictions, if
@@
 %
-All tables/sets are initialized as empty tables/sets. We use the following sets
+All tables/sets are initialised as empty tables/sets. We use the following sets
 and tables in our definitions:
@@
 \paragraph{Oracles.} %
-We leverage the following oracles, formalized in \figref{fig:oracles1} and
+We leverage the following oracles, formalised in \figref{fig:oracles1} and
 \figref{fig:oracles2}.
@@
 %   the associated issuance function.
-\item[\HUGEN.] Adds a new honest user, generating its keypair.
+\item[\HUGEN.] Adds a new honest user, generating its key pair.
 \item[\CUGEN.] Adds a new corrupt user. Sets its \upk to the
@@
 available in the actual scheme, but rather to the challenger in the experiments
-we use to formalize security of \UAS schemes. We introduce them here, and define
+we use to formalise security of \UAS schemes. We introduce them here, and define
 them later for our construction.
@@
 \paragraph{Correctness.} %
-Correctness of \UAS schemes is formalized through the experiment in
+Correctness of \UAS schemes is formalised through the experiment in
 \figref{fig:exp-uas-corr}. It states that a signature over any arbitrary message
@@
 beyond what is leaked by the policies required for issuance. For this, we allow
-the adversary to control targetted issuers and openers, and add honest and
+the adversary to control targeted issuers and openers, and add honest and
 corrupt users. The adversary can also obtain credentials, produce signatures,
@@
 
-We could simply check that all the credetnials involved in valid signatures
+We could simply check that all the credentials involved in valid signatures
 satisfy their respective \fissue functions, and belong to known users. However,
@@
 to obtain a legitimate one, and then use the latter to finally create a valid
-signature -- concretly, such misbehaviour is not prevented by \ExpForgeSign.
+signature -- concretely, such misbehaviour is not prevented by \ExpForgeSign.
 
@@
 
-We formalize both properties in \figref{fig:exp-uas-unfor}.
+We formalise both properties in \figref{fig:exp-uas-unfor}.
 
@@
 
-We formalize non-frameability in \ExpNonframe in \figref{fig:exp-uas-frame}.
+We formalise non-frameability in \ExpNonframe in \figref{fig:exp-uas-frame}.
 The adversary is challenged to produce a signature
@@
 and \RelIns, described next and specified in CS notation \cite{cs97} in
-\figref{fig:nizkrels}. These relations include verifying that the comptuation of
+\figref{fig:nizkrels}. These relations include verifying that the computation of
 the \fissue, \feval and \finsp functions has been done correctly.

### 2022-10-05 prism-backend/research/gsac/app-building-blocks.tex
Typos and notation fixed. Some important updates pending...

@@
 \begin{description}
-\item[$\Eparm \gets \ESetup(\Esecpar)$.] Produces public parameters \Eparm given
-  a security parameter \Esecpar.
-\item[$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$.] Given public parameters \Eparm,
-  produces an encryption-decryption key pair $(\Eek,\Edk)$.
-\item[$\Ec \gets \EEnc(\Eek,\msg)$.] Encrypts message \msg with encryption key
-  \Eek, producing ciphertext \Ec.
-\item[$\msg \gets \EDec(\Edk,\Ec)$.] Decrypts ciphertext \Ec with decryption key
-  \Edk.
+\item[$\parm \gets \ESetup(\secpar)$.] Produces public parameters \parm given
+  a security parameter \secpar.
+\item[$(\ek,\dk) \gets \EKeyGen(\parm)$.] Given public parameters \parm,
+  produces an encryption-decryption key pair $(\ek,\dk)$.
+\item[$\Ec \gets \EEnc(\ek,\msg)$.] Encrypts message \msg with encryption key
+  \ek, producing ciphertext \c.
+\item[$\msg \gets \EDec(\dk,\Ec)$.] Decrypts ciphertext \Ec with decryption key
+  \dk.
 \end{description}
@@
 A public-key encryption scheme is correct if, given a honestly generated key
-pair $(\Eek,\Edk)$, produced with honestly generated parameters \Eparm,
-$\Pr[\EDec(\Edk,\EEnc(\Eek,\msg))=\msg] = 1$ with overwhelming probability.
+pair $(\ek,\dk)$, produced with honestly generated parameters \Eparm,
+$\Pr[\EDec(\dk,\EEnc(\ek,\msg))=\msg] = 1$ with overwhelming probability.
 
 A public-key encryption scheme has IND-CCA2 security if
-$\Pr[\ExpINDCCAiio(\Esecpar) = 1] - \Pr[\ExpINDCCAiiz(\Esecpar) = 1]|$ is
+$\Pr[\ExpINDCCAiio(\secpar) = 1] - \Pr[\ExpINDCCAiiz(\secpar) = 1]|$ is
 a negligible function of \Esecpar, for any p.p.t. adversary \adv, where
@@
       \centering      
-      \procedure{$\ExpINDCCAiib(\Esecpar)$}{%
-        \Eparm \gets \ESetup(\Esecpar) \\
-        (\Eek,\Edk) \gets \EKeyGen(\Eparm) \\
-        b^* \gets \adv^{\ELR(b,\cdot,\cdot),\EDEC(\Edk,\cdot)}(\Eek),
+      \procedure{$\ExpINDCCAiib(\secpar)$}{%
+        \parm \gets \ESetup(\secpar) \\
+        (\ek,\dk) \gets \EKeyGen(\parm) \\
+        b^* \gets \adv^{\oracle{\ELR}(b,\cdot,\cdot),
+          \oracle{\EDEC}(\dk,\cdot)}(\ek),
         ~\textrm{where:} \\
-        \pcind \ELR(b,\msg_0,\msg_1)~\textrm{returns}~\EEnc(\Eek,\msg_b),
+        \pcind \oracle{\ELR}(b,\msg_0,\msg_1)~\textrm{returns}~\EEnc(\ek,\msg_b),
         ~\textrm{and} \\
-        \pcind \EDEC(\Edk,\Ec)~\textrm{returns}~\EDec(\Edk,\Ec) \\
-        \pcif \EDEC~\textrm{has been called with an output of \ELR, abort} \\
+        \pcind \oracle{\EDEC}(\dk,\Ec)~\textrm{returns}~\EDec(\dk,\Ec) \\
+        \pcif \oracle{\EDEC}~\textrm{has been called with an output of \ELR,
+          abort} \\
         \pcreturn b^*
@@
 
-Although we don't expose commitments directly in our \UAS scheme or
-constructions, they are an essential part of \SBCM schemes. Thus, we overview
-them briefly next. In a nutshell, a commitment scheme is defined by the
-following algorithms:
+Although we don't directly leverage commitments fucntionality in our \UAS scheme
+or constructions, they are an essential part of \SBCM schemes, which we present
+in a following section. Thus, we overview commitment schemes briefly now. In a
+nutshell, a commitment scheme is defined by the following algorithms:
 
 \begin{description}
-\item[$\Cparm \gets \CSetup(\Csecpar)$.] Given a security parameter \Csecpar,
-  returns the public parameters \Cparm to commit messages.
-\item[$\Ccom \gets \CCommit(\Cparm,\msg;r)$.] Given the public parameters and
-  a message \msg, outputs a commitment \Ccom to \msg, for which randomness $r$
+\item[$\parm \gets \CSetup(\secpar)$.] Given a security parameter \secpar,
+  returns the public parameters \parm to commit messages.
+\item[$\Ccom \gets \CCommit(\parm,\msg;r)$.] Given the public parameters and
+  a message \msg, outputs a commitment \com to \msg, for which randomness $r$
   from some predefined randomness space $\mathcal{R}$ is used.
@@
   that no adversary can change the message that has been committed to. More
-  formally, $\Pr[\ExpComBind(\Csecpar) = 1]$ must be a negligible function of
+  formally, $\Pr[\ExpComBind(\secpar) = 1]$ must be a negligible function of
   the security parameter.
@@
   learn the message that was committed, when given only the commitment. This is
-  formally defined through \ExpComHideb, where $|\Pr[\ExpComHideb(\Csecpar)=1|
-  b=1] - \Pr[\ExpComHideb(\Csecpar)=1|b=0]|$ must be a negligible function of
+  formally defined through \ExpComHideb, where $|\Pr[\ExpComHideb(\secpar)=1|
+  b=1] - \Pr[\ExpComHideb(\secpar)=1|b=0]|$ must be a negligible function of
   the security parameter.
@@
     \begin{minipage}[t]{0.5\textwidth}
-      \procedure{$\ExpComBind(\Csecpar)$}{%
-        \Cparm \gets \CSetup(\Csecpar) \\
-        (\msg_0,r_0,\msg_1,r_1) \gets \adv(\Cparm) \\
-        \Ccom_0 \gets \CCommit(\Cparm,\msg_0,r_0) \\
-        \Ccom_1 \gets \CCommit(\Cparm,\msg_1,r_1) \\
+      \procedure{$\ExpComBind(\secpar)$}{%
+        \parm \gets \CSetup(\secpar) \\
+        (\msg_0,r_0,\msg_1,r_1) \gets \adv(\parm) \\
+        \Ccom_0 \gets \CCommit(\parm,\msg_0,r_0) \\
+        \Ccom_1 \gets \CCommit(\parm,\msg_1,r_1) \\
         \pcif \msg_0 \neq \msg_1 \land \Ccom_0 = \Ccom_1: \pcreturn 1 \\
@@
       \procedure{$\ExpComHideb(\secpar)$}{%
-        \Cparm \gets \CSetup(\secpar) \\
-        b' \gets \adv^{COM(\Cparm,\cdot,\cdot)},~\textrm{where}: \\
-        \pcind COM(\Cparm,\msg_0,\msg_1): \\
-        \pcind \pcind r \getr \mathcal{R};~\pcreturn \CCommit(\Cparm,\msg_b,r) \\
+        \parm \gets \CSetup(\secpar) \\
+        b' \gets \adv^{\oracle{COM}(\parm,\cdot,\cdot)},~\textrm{where}: \\
+        \pcind COM(\parm,\msg_0,\msg_1): \\
+        \pcind \pcind r \getr \mathcal{R};~\pcreturn \CCommit(\parm,\msg_b,r) \\
         % (\msg_0,\msg_1,st) \gets \adv(\Cparm) \\
@@
 compares sets $\msgset_0$ and $\msgset_1$, which must differ in at least one
-element. This extension is straight-forward, for instance, from Pedersen
+element. This extension is straightforward, for instance, from Pedersen
 commitments \cite{bcc+15}.
 
-\subsection{Simulation-Extractable Non-Interactive Zero-Knowledge
+\subsection{Simulation Extractable Non-Interactive Zero-Knowledge
   Proofs of Knowledge}
@@
 \begin{description}
-\item[$\NIZKcrs \gets \NIZKSetup(\NIZKsecpar)$.] Generates a CRS \NIZKcrs from
-  security parameters \NIZKsecpar.
+\item[$\NIZKcrs \gets \NIZKSetup(\secpar)$.] Generates a CRS \NIZKcrs from
+  security parameters \secpar.
 \item[$\NIZKproof \gets \NIZKProve(\NIZKcrs,\NIZKx,\NIZKw)$.] Given \NIZKcrs,
@@
 
-Any zero-knowledge proof of knowledge must meet completeness, soundness and
-zero-knowledge,properties. We further need an extra property, called
-\emph{simulation-extractability} \cite{cl06}, which amplifies the security
+Any zero-knowledge proof of knowledge must meet completeness, soundness, and
+zero-knowledge properties. We further need an extra property, called
+\emph{simulation extractability} \cite{cl06}, which amplifies the security
 requirements of (simulation-) soundness.
@@
 \begin{description}
-\item[$(\NIZKcrs,\NIZKtrap) \gets \NIZKSimSetup(\NIZKsecpar)$.] Produces a
+\item[$(\NIZKcrs,\NIZKtrap) \gets \NIZKSimSetup(\secpar)$.] Produces a
   \NIZKcrs as the \NIZKSetup algorithm, along with a trapdoor \NIZKtrap.
@@
 $\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and super-index when
-clear from context. Altogether, the tuple $(\Setup,\Prove,\Verify,\SimSetup,
-\Sim,\Extract)$ needs to meet the following properties:
+clear from context. Altogether, the tuple $(\Setup,\Prove,\Verify,
+\helper{\SimSetup},\helper{\Sim},\helper{\Extract})$ needs to meet the following
+properties:
 
@@
 able to create a proof \NIZKproof that is accepted by any honest verifier, with
-overwhelming probability. More precisely, $\Pr\lbrack\ExpNIZKComp(\NIZKsecpar)
+overwhelming probability. More precisely, $\Pr\lbrack\ExpNIZKComp(\secpar)
 \rbrack = 1$ with overwhelming probability, for any p.p.t. \adv, for
@@
 (\NIZKsecpar)\rbrack=1$ with overwhelming probability. If this holds only
-against p.p.t. adversaries, we talk of Non-Interactive \emph{arguments}, while
-if soundness holds even against unbounded adversaries, we talks about
-Non-Interactive proofs.
+against p.p.t. adversaries, we talk of non-interactive \emph{arguments}, while
+if soundness holds even against unbounded adversaries, we talk about
+non-interactive proofs.
 
@@
 \SimSetup, except when $\adv$ specifies $(\NIZKx,\NIZKw) \notin \NIZKRel$. Note
-that, in the context of simulation-extractable NIZK, this property not only
+that, in the context of simulation extractable NIZK, this property not only
 requires that the simulated proofs are indistinguishable to the real ones; it
 also requires that \SimSetup is indistinguishable from \Setup. All this is
-formalised by requiring that $|\Pr[\ExpNIZKZKb(\NIZKsecpar) = 1 | b = 1] -
-\Pr[\ExpNIZKZKb(\NIZKsecpar) = 1 | b = 0]$ be a negligible function of \secpar,
+formalised by requiring that $|\Pr[\ExpNIZKZKb(\secpar) = 1 | b = 1] -
+\Pr[\ExpNIZKZKb(\secpar) = 1 | b = 0]$ be a negligible function of \secpar,
 where \ExpNIZKZKb is as defined in \figref{fig:nizk-games}.
 
-\paragraph{Simulation-Extractability.} As stated, simulation-extractability
-is an extension to simulation soundness. In a nutshell,
-simulation-extractability requires that, even after having received a polynomial
+\paragraph{Simulation Extractability.} As stated, simulation extractability
+is an extension to simulation soundness, which is in turn an extension to
+knowledge soundness. In a nutshell,
+simulation extractability requires that, even after having received a polynomial
 number of simulated proofs of knowledge, no adversary can output a valid proof
@@
 after having seen polynomially many simulated proofs (but does not guarantee
-extraction). Formally, for simulation-extractability we require that
-$\Pr[\ExpNIZKSimExt(\NIZKsecpar)] = 1$ is a negligible function of \secpar,
+extraction). Formally, for simulation extractability we require that
+$\Pr[\ExpNIZKSimExt(\secpar)] = 1$ is a negligible function of \secpar,
 where \ExpNIZKSimExt is defined in \figref{fig:nizk-games}.
@@
 \begin{figure}[ht!]
-  \scalebox{0.9}{
-    \begin{minipage}[t]{0.5\textwidth}
+  \centering
+  \scalebox{0.85}{
+    \begin{minipage}[t]{0.55\textwidth}
       \procedure{$\ExpNIZKComp(\NIZKsecpar)$}{%
@@
         \NIZKw' \gets \Extract(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKproof) \\
-        \pcif \Verify(\NIZKcrs,\NIZKproof,\NIZKx) = 1 \land
+        \pcreturn \Verify(\NIZKcrs,\NIZKproof,\NIZKx) = 1 \land
         (\NIZKx,\NIZKw') \notin \NIZKRel~\land \\
-        \pcind \NIZKx~\textrm{was not queried to $\Sim$ via $\Sim'$}: \\
-        \pcind \pcreturn 1 \\
-        \pcreturn 0
+        \pcind \NIZKx~\textrm{was not queried to $\Sim$ via $\Sim'$}
       }    
     \end{minipage}
-    \begin{minipage}[t]{0.5\textwidth}
+    \begin{minipage}[t]{0.55\textwidth}
       \procedure{$\ExpNIZKSound(\NIZKsecpar)$}{%
@@
         (\NIZKproof,\NIZKx) \gets \adv(\NIZKcrs) \\
-        \pcif \NIZKx \notin \NIZKLang \land
-        \Verify(\NIZKcrs,\NIZKproof,\NIZKx): \\
-        \pcind \pcreturn 0 \\
-        \pcreturn 1 \\
+        \pcreturn 1 - (\NIZKx \notin \NIZKLang \land
+        \Verify(\NIZKcrs,\NIZKproof,\NIZKx)) \\
       }
@@
   \label{fig:nizk-games}
-  \caption{Games for Simulation-Extractable NIZK schemes.}
+  \caption{Games for Simulation Extractable NIZK schemes.}
 \end{figure}
 
-As studied in \cite{cl06}, simulation-extractable NIZKPoKs formalise the concept
+As studied in \cite{cl06}, simulation extractable NIZKPoKs formalise the concept
 of ``signatures of knowledge'' (see, e.g., \cite{cs97}). Which basically means
@@
 while proving arbitrary claims, as long as they can be represented as an NP
-relation. We note that, given a simulation-extractable NIZK system, it is
+relation. We note that, given a simulation extractable NIZK system, it is
 straightforward to build a signature of knowledge by adding the message to be
@@
 party running running \SBMSign over \smsg, for honestly generated parameters
-and key pairs, results in a signature over $\smsg \cup \overline{\smsg}$ that is
+and key pairs, results in a signature over $\smsg \cup \osmsg$ that is
 accepted by \SBMVerify.
@@
 message to be blindly signed \cite{ao00}. Partially blind signatures, as
-blind signatures \cite{ps96}, cannot be modelled with the conventional security
+blind signatures \cite{ps96}, don't typically follow the conventional security
 against existential forgeries. Simply because the user is actually expected to
@@
 \begin{description}
-\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
+\item[$\parm \gets \SBCMSetup(\secpar)$.] It produces public parameters
   for the other algorithms, given an input security parameter \SBCMsecpar.
-\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
+\item[$(\vk,\SBCMsk) \gets \SBCMKeyGen(\parm)$.] Generates a
   verification-signing key pair.
-\item[$(\SBCMcom,\pi,r) \gets \SBCMBlind(\SBCMvk,\osmsg,\smsg)$.] A user
-  computes commitment \SBCMcom to request a signature over messages \osmsg (in
+\item[$(\Ccom,\pi,r) \gets \SBCMBlind(\vk,\osmsg,\smsg)$.] A user
+  computes commitment \Ccom to request a signature over messages \osmsg (in
   committed form) and \smsg (in plain form), to signer with verification key
-  \SBCMvk. The output is the commitment \SBCMcom, the randomness $r$ used to
+  \vk. The output is the commitment \Ccom, the randomness $r$ used to
   compute it, and a proof $\pi$ proving knowledge of \osmsg and \smsg in
-  \SBCMcom.
-\item[$\SBCMbsig \gets \SBCMSign(\SBCMsk,\SBCMcom,\pi,\smsg)$.] The
-  signer, with signing key \SBCMsk, produces a blind signature \SBCMbsig over
-  the messages committed to in commitment \SBCMcom, as well as the messages in
+  \Ccom.
+\item[$\bsig \gets \SBCMSign(\sk,\Ccom,\pi,\smsg)$.] The
+  signer, with signing key \sk, produces a blind signature \bsig over
+  the messages committed to in commitment \Ccom, as well as the messages in
   \smsg, with associated proof $\pi$.
-\item[$\SBCMsig \gets \SBCMUnblind(\SBCMvk,\SBCMbsig,\SBCMcom,r,\osmsg,\smsg)$.]
-  A user, who requested a signature over \osmsg and \smsg, where \SBCMcom is a
+\item[$\sig \gets \SBCMUnblind(\vk,\bsig,\Ccom,r,\osmsg,\smsg)$.]
+  A user, who requested a signature over \osmsg and \smsg, where \Ccom is a
   commitment over \osmsg using randomness $r$, finalises the signature,
-  computing \SBCMsig from the signer's partial signature \SBCMbsig.
-\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\osmsg,\smsg)$.] Checks
-  whether \SBCMsig is a valid signature over the set of messages \osmsg and
-  \smsg, under verification key \SBCMvk.
+  computing \sig from the signer's partial signature \bsig.
+\item[$1/0 \gets \SBCMVerify(\vk,\sig,\osmsg,\smsg)$.] Checks
+  whether \sig is a valid signature over the set of messages \osmsg and
+  \smsg, under verification key \vk.
 \end{description}
 
-The correctness and security properties are then defined as follows.
+The correctness and security properties are defined as follows.
 
@@
 signer. More formally, an \SBCM scheme is unforgeable if, for all p.p.t.
-adversaries $\adv$, $\Pr[\ExpSBCMOMF(\SBCMsecpar) = 1]$, as defined in
+adversaries $\adv$, $\Pr[\ExpSBCMOMF(\secpar) = 1]$, as defined in
 \figref{fig:sbcm-games}, is a negligible function of the security parameter.
@@
 additionally required that the adversary cannot link a signature to the signing
-process that produced it. Informally, we capture this basically as the blinding
+process that produced it. Informally, we capture this basically as the hiding
 notion of a commitment scheme -- and formally define it in \ExpSBCMBlindb in
@@
 \adv~any full signature (i.e., after running \SBCMUnblind) obtained from values
-returned by \adv, as this will allow the adversary to trivially check what
-messages (among the ones he chose) was signed. While this may seem a too weak
+returned by \adv, as this would allow the adversary to trivially check what
+messages (among the ones he chose) were signed. While this may seem a too weak
 notion, it is good enough for our needs, as in our \UAS construction we never
@@
 An \SBCM scheme is blind if, for all p.p.t.
-adversaries $\adv$, $|\Pr[\ExpSBCMBlindo(\SBCMsecpar) = 1] -
-\Pr[\ExpSBCMBlindz(\SBCMsecpar) = 1]|$ is a negligible function of the security
+adversaries $\adv$, $|\Pr[\ExpSBCMBlindo(\secpar) = 1] -
+\Pr[\ExpSBCMBlindz(\secpar) = 1]|$ is a negligible function of the security
 parameter.
@@
         (\vk,\sk) \gets \KeyGen(\parm) \\
-        \lbrace(\sig_i,\overline{\smsg}_i, \smsg_i)\rbrace_{i\in[n]} \gets
+        \lbrace(\sig_i,\osmsg_i, \smsg_i)\rbrace_{i\in[n]} \gets
         \adv^{\Sign(\sk,\cdot,\cdot,\cdot)}(\vk) \\
@@
         % b^* \gets \adv(\st,\sig_b,\sig_{1-b}) \\       
-        b^* \gets \adv^{BLIND(\cdot,\cdot,\cdot)}(\vk),~\textrm{where:} \\
-        \pcind BLIND(\osmsg_0,\osmsg_1,\smsg): \\
+        b^* \gets \adv^{\oracle{BLIND}
+          (\cdot,\cdot,\cdot)}(\vk),~\textrm{where:} \\
+        \pcind \oracle{BLIND}(\osmsg_0,\osmsg_1,\smsg): \\
         \pcind \pcind (\com,\pi,r) \gets \Blind(\vk,\osmsg_b,\smsg); \\
@@
   \label{fig:sbcm-games}
-  \caption{Games for \SBCM schemes.
-  }
+  \caption{Games for \SBCM schemes.}
 \end{figure}
@@
 maintains blindness (the adversary cannot distinguish which committed message
-set is signed, in the blindness game).
+set is signed, in the blindness game, as long as both challenge messages are
+in the NP language).
 %
@@
   \osmsg, respectively.
-\item $\SBCMbsig \gets \SBCMSign^\NIZKRel(\sk,\Ccom,\pi,\smsg;x')$. Like
+\item $\bsig \gets \SBCMSign^\NIZKRel(\sk,\Ccom,\pi,\smsg;x')$. Like
   \SBCMSign, but for relation \NIZKRel, which requires extra values $x'$
   for its statement, beyond what may be included in \smsg.
-\item $\SBCMsig \gets \SBCMUnblind^\NIZKRel(\vk,\SBCMbsig,\Ccom,r,\osmsg,\smsg;
+\item $\sig \gets \SBCMUnblind^\NIZKRel(\vk,\bsig,\Ccom,r,\osmsg,\smsg;
   x',w')$. Like \SBCMUnblind, but for relation \NIZKRel, which requires extra
@@
 Note also that, in our instantiation, we just include a generic \NIZK, for some
-relation over witness $\overline{\smsg}$ (i.e., the messages to be blindly
+relation over witness \osmsg (i.e., the messages to be blindly
 signed), and statement $(\Ccom,\smsg)$ (i.e., their block commitment, and the
@@
 proving arbitrary predicates is possible (as opposed to ``just'' proving that
-the commitment is over the messages in $\overline{\smsg}$).
+the commitment is over the messages in \osmsg).
 %
@@
 
-\paragraph{$\SBCMparm \gets \SBCMSetup(\SBCMsecpar,\nattrs,\tnattrs)$.} %
+\paragraph{$\parm \gets \SBCMSetup(\secpar,\nattrs,\tnattrs)$.} %
 Generates a bilinear group $\BB = (p,\GG_1,\GG_2,\GG_T,\gen{g}_1,\gen{g}_2,e)
-\gets \PGen(\SBCMsecpar)$, and $\nattrs+\tnattrs+1$ additional generators
+\gets \PGen(\secpar)$, and $\nattrs+\tnattrs+1$ additional generators
 $\gen{g}$, $\gen{h}_1,...,\gen{h}_{\nattrs}$,$\gen{\th}_1,...,\gen{\th}_{\tnattrs}$
-of $\GG_1$. Returns $\SBCMparm \gets (\SBCMsecpar,\nattrs,\tnattrs,\BB,
+of $\GG_1$. Returns $\parm \gets (\secpar,\nattrs,\tnattrs,\BB,
 \gen{g},\gen{h}_1,...,\gen{h}_{\nattrs},\gen{\th}_1,...,\gen{\th}_{\tnattrs})$.
-We assume that \SBCMparm is available to all other algorithms, even when not
+We assume that \parm is available to all other algorithms, even when not
 explicitly passed as an argument.
 
-\paragraph{$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.} %
-Parses \SBCMparm as $(\cdot,\cdot,(p,\GG_1,\GG_2,\GG_T,\gen{g}_1,\gen{g}_2,e),
-\dots$ $\NIZKcrs \gets \NIZKSetup(\secpar)$. Outputs $\SBCMsk \gets \ZZ^*_p$,
-and $\SBCMvk \gets (\NIZKcrs,\gen{g}_2^{\SBCMsk})$.
+\paragraph{$(\vk,\sk) \gets \SBCMKeyGen(\parm)$.} %
+Parses \parm as $(\secpar,\cdot,\cdot,(p,\GG_1,\GG_2,\GG_T,\gen{g}_1,\gen{g}_2,
+e),\dots)$. Computes $\NIZKcrs \gets \NIZKSetup(\secpar)$. Outputs $\sk \gets
+\ZZ^*_p$, and $\vk \gets (\NIZKcrs,\gen{g}_2^{\sk})$.
 
-\paragraph{$(\Ccom,\pi,r) \gets \SBCMBlind(\SBCMvk,\osmsg,\smsg)$.} %
+\paragraph{$(\Ccom,\pi,r) \gets \SBCMBlind(\vk,\osmsg,\smsg)$.} %
 If $|\smsg |>\nattrs$ or $|\osmsg|>\tnattrs$,
 abort. Else, fetch fresh randomness $r \getr \ZZ^*_p$, compute $\Ccom \gets
-\gen{g}^r\prod_{i \in [|\overline{\smsg}|]}\gen{\th}_i^{\overline{\smsg}_i}$,
-and $\NIZKproof \gets \NIZKProve(\NIZKcrs,(r,\overline{\smsg}),\Ccom)$.
+\gen{g}^r\prod_{i \in [|\osmsg|]}\gen{\th}_i^{\osmsg_i}$,
+and $\NIZKproof \gets \NIZKProve(\NIZKcrs,(r,\osmsg),\Ccom)$.
 Output $(\Ccom,\NIZKproof,r)$.
 
-\paragraph{$\SBCMbsig \gets \SBCMSign(\SBCMsk,\Ccom,\NIZKproof,\smsg)$.} %
+\paragraph{$\bsig \gets \SBCMSign(\sk,\Ccom,\NIZKproof,\smsg)$.} %
 If $|\smsg|>\nattrs$, abort. Else, run $\NIZKVerify(\NIZKcrs,\Ccom,\NIZKproof)$
@@
 (\gen{g}_1\Ccom \gen{g}^{\tilde{s}} \prod_{i \in |\smsg|}
-\gen{h}_i^{\smsg_i})^{1/(\SBCMsk+x)}$. Return $\SBCMbsig \gets (A,x,\tilde{s})$.
+\gen{h}_i^{\smsg_i})^{1/(\sk+x)}$. Return $\bsig \gets (A,x,\tilde{s})$.
 
-\paragraph{$\SBCMsig \gets \SBCMUnblind(\SBCMvk,\SBCMbsig,\Ccom,r,
+\paragraph{$\sig \gets \SBCMUnblind(\vk,\bsig,\Ccom,r,
   \osmsg,\smsg)$.} %
-Parse \SBCMbsig as $(A,x,\tilde{s})$
+Parse \bsig as $(A,x,\tilde{s})$
 If $A = 1_{\GG_1}$: return $0$. Else, compute $s \gets r + \tilde{s}$. If
-$e(A,\gen{g}_2)^xe(A,\SBCMvk) \neq e(\gen{g}_1\Ccom\gen{g}^{\tilde{s}}
+$e(A,\gen{g}_2)^xe(A,\vk) \neq e(\gen{g}_1\Ccom\gen{g}^{\tilde{s}}
 \prod_{i \in |\smsg|}\gen{h}_i^{\smsg_i},\gen{g}_2)$: return $0$. Else, return
@@
 
-% \paragraph{$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\overline{\smsg},
+% \paragraph{$\SBCMsig/\bot \gets \langle \SBCMCom(\SBCMvk,\osmsg,
 %   \smsg), \SBCMSign(\SBCMsk,\smsg) \rangle$.} %
@@
 % \begin{itemize}
-% \item \underline{User}: If $|\smsg|>\nattrs$ or $|\overline{\smsg}|>\tnattrs$,
+% \item \underline{User}: If $|\smsg|>\nattrs$ or $|\osmsg|>\tnattrs$,
 %   abort. Else, fetch fresh randomness $r \getr \ZZ^*_p$, compute $\Ccom \gets
-%   \gen{g}^r\prod_{i \in [|\overline{\smsg}|]}\gen{\th}_i^{\overline{\smsg}_i}$,
-%   and $\NIZKproof \gets \NIZKProve(\NIZKcrs,(r,\overline{\smsg}),\Ccom)$.
+%   \gen{g}^r\prod_{i \in [|\osmsg|]}\gen{\th}_i^{\osmsg_i}$,
+%   and $\NIZKproof \gets \NIZKProve(\NIZKcrs,(r,\osmsg),\Ccom)$.
 %   Send $(\Ccom,\NIZKproof)$ to Issuer.
@@
 
-\paragraph{$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\overline{\smsg},\smsg)$.} %
-To verify a signature \SBCMsig, for message set $\overline{\smsg}$ that was
+\paragraph{$1/0 \gets \SBCMVerify(\vk,\sig,\osmsg,\smsg)$.} %
+To verify a signature \sig, for message set \osmsg that was
 signed as a block commitment, and message set \smsg, signed as plaintext, parse
-\SBCMsig as $(A,x,s)$ and check if $e(A,\gen{g}_2^x\SBCMvk) =
-e(\gen{g}_1\gen{g}^s\prod_{i \in |\overline{\smsg}|}\gen{h}^{\overline{\smsg}_i}
+\sig as $(A,x,s)$ and check if $e(A,\gen{g}_2^x\vk) =
+e(\gen{g}_1\gen{g}^s\prod_{i \in |\osmsg|}\gen{h}^{\osmsg_i}
 \prod_{i \in |\smsg|}\gen{h}^{\smsg_i},\gen{g}_2)$
@@
 signed, which in plain BBS+ it is not a problem, as they are received in the
-clear. In the case of \SBCM, however, some of the messages to be signed are
-received as part of a commitment. Note however that, in \SBCM, besides receiving
+clear. In this case, however, some of the messages to be signed are
+received as part of a commitment. Note however that now, besides receiving
 the commitment, we also receive a NIZK proof of knowledge of the corresponding
@@
 and binding of the commitment scheme. %
-If the NIZK also has online-extractability, then we do not need to impose
-further requirements. If it is not, then the \SBCM scheme should not allow
-parallel signing requests, or limit the total number of signatures to be
+If the NIZK also has online extractability, then we do not need to impose
+further requirements. Otherwise, then the scheme should not allow
+parallel signing of requests, or limit the total number of signatures to be
 created to a logarithmic function of the security parameter (which is probably
@@
 \paragraph{Blindness.}
-Blindness of \SBCM is a direct consequence of the hiding property of the
+Blindness is a direct consequence of the hiding property of the
 underlying block commitment scheme. Indeed, assume an adversary $\adv$ against
@@
 property of the commitment scheme in a straightforward manner. Namely, \advB
-sets up the environment for \adv by running the \KeyGen algorithm using the
-\vk it receives. Then, for every query that \adv makes to its $BLIND$ oracle,
-\advB checks that the length of \smsg is acceptable (i.e., less than the
-maximum length allowed by \SBCM), and forwards the query to its own $COM$
-oracle using $\osmsg_0$ and $\osmsg_1$. To the output \Ccom of $COM$, \advB
-appends a simulated proof $\pi$, and forwards $(\Ccom,\pi)$ to \adv. Finally,
-\advB outputs whatever \adv~outputs. The simulation is correct due to the
-zero-knowledge property of the underlying NIZK. Thus, \advB wins whenever
+sets up the environment for \adv~by running the \KeyGen algorithm using the
+\vk it receives. Then, for every query that \adv~makes to its \oracle{BLIND}
+oracle, \advB checks that the length of \smsg is acceptable (i.e., less than the
+maximum length allowed by \SBCM), and forwards the query to its own \oracle{COM}
+oracle using $\osmsg_0$ and $\osmsg_1$. To the output \Ccom of \oracle{COM},
+\advB appends a simulated proof $\pi$, and forwards $(\Ccom,\pi)$ to \adv.
+Finally, \advB outputs whatever \adv~outputs. The simulation is correct due to
+the zero-knowledge property of the underlying NIZK. Thus, \advB wins whenever
 \adv~does.

### 2022-10-05 prism-backend/research/gsac/app-related-extra.tex
Typos and notation fixed. Some important updates pending...

@@
 % over different messages.
-Note that it should still be possible to apply
-thresholding techniques to extend this case so that our ``unified'' opener role
-is shared across multiple entities, who have to cooperate in order to open a
-signature \cite{cdl+20}, thus achieving something very close ``in spirit'' to
+Although we leave it for future work, note that it should still be possible to
+apply thresholding techniques to extend this case so that our ``unified'' opener
+role is shared across multiple entities, who have to cooperate in order to open
+a signature \cite{cdl+20}, thus achieving something very close ``in spirit'' to
 the scheme in \cite{ehk+19}. In addition, while \cite{ehk+19} follows the static
@@
 
-Note that, for simplicity and to build upon our \CUASGS construction, we
+For simplicity and to build upon our \CUASGS construction, we
 describe a variant where the set of messages to disallow is defined once via
@@
 directly implementable as a $(\fissue^{single,H,I},\feval^{F,MPS},
-\finsp^{G,MPS})$-\CUASGen restriction. Concretely, this restricts to a system
-with one credential per user and no attributes in the credentials.
+\finsp^{G,MPS})$-\CUASGen restriction. Concretely, this restricts to a \UAS
+system with one credential per user and no attributes in the credentials.
 
@@
 this is easy to add, we consider it to be essential, given that the proposed
-generalisation of opening allows the opener to output ``any value''. Hence, the
+generalisation of opening allows the opener to output any value. Hence, the
 need to ensure that the produced value is the legitimate one seems to be more
@@
 first \KeyGen to generate the user key pair, and then proceeds as in \CUASGen.
-\Sign, \Verify and \Open, are as in \CUASGen.
+\Sign, \Verify and \Open, are as in \CUASGen -- where, in \Open, we simply
+ignore the opening proof.
 
@@
 \UAS is the $\yeval^1$ value which, in \CUASGen, is encrypted with a single-use
-key pair, and is an input of \finsp.
+key pair, and is an input to \finsp.
 
 \paragraph{Security of \CUASMPS.} %
-As stated, we restrict to privacy-1 of MPS (although, as
+We restrict to privacy-1 of MPS (although, as
 discussed, we actually achieve something slightly stronger). Unforgeability-1 in
-MPS is implied by unforgeability in \UAS (where the latter also covers
-unforgeability of \fissue evaluations, plus verifiable openings).
+MPS is implied by signature unforgeability in \UAS.
 Unforgeability-2 in MPS is equivalent to non-frameability in \UAS (where the
@@
   privacy-1 of \CUASMPS as defined for MPS, it is easy to build an adversary
-  \advB breaking signature anonymity of the underlying \CUASGen, as defined in
-  \UAS.
+  \advB breaking signature anonymity of the underlying \CUASGen construction, as
+  defined in \UAS.
 
@@
   \mathcal{O}_{sig},\mathcal{O}_{open}$ in MPS correspond to \RREG, \WREG,
-  \CUGEN, \HUGEN, \SIGN and \OPEN in \UAS, respectively. The output given by
-  \adv~in the first stage of the MPS game is then directly used as input to
-  \advB's \CHALb oracle. Finally, \advB outputs whatever \adv~outputs.
+  \CUGEN, \HUGEN, \OBTAIN, \SIGN and \OPEN in \UAS, respectively. The output
+  given by \adv~in the first stage of the MPS game is then directly used as
+  input to \advB's \CHALb oracle. Finally, \advB outputs whatever \adv~outputs.
 
@@
   its \ICORR oracle. Eventually, \adv~outputs a $(F,M,\Sigma)$ tuple, which
-  corresponds to $(\feval^{g,MPS},\msg,\Sig)$ (with $g=F$ in MPS) in \CUASGen,
+  corresponds to $(\feval^{F,MPS},\msg,\Sig)$ in \CUASGen,
   which \advB outputs in its own game. In addition, \advB outputs as $(\yinsp,
   \pi)$ values the output of \Open over $(\Sig,\msg)$ -- which internally
-  computes $\finsp^{h,MPS}$, for $h=G$ in MPS.
+  computes $\finsp^{G,MPS}$.
   % 
-  Note that the $\feval^{g,MPS}$ and $\finsp^{h,MPS}$ functions in \CUASMPS
+  Note that the $\feval^{F,MPS}$ and $\finsp^{G,MPS}$ functions in \CUASMPS
   mimic the behaviour of MPS's $F$ and $G$, respectively. Thus, if \adv wins
@@
   wins at line 7 of the non-frameability game, as a legitimately computed
-  $\feval^{g,MSP}$ function cannot output $0$. Similarly, if \adv~wins because
+  $\feval^{F,MSP}$ function cannot output $0$. Similarly, if \adv~wins because
   the value returned by an honestly computed open function over the adversarial
@@
   \Open outputs (when computed honestly over \adv's output), whereas
-  $\finsp^{g,MSP}=G$; thus, if both values differ in \adv's game, then they also
+  $\finsp^{G,MSP}=G$; thus, if both values differ in \adv's game, then they also
   differ in \advB's game.
@@
   belong to the set of corrupt users in \adv's game. By construction of \advB
-  (identities in \adv's game map to a $\cid$ for \advB), $\OWNR[\cid] \notin
+  (identities in \adv's game map to a \cid for \advB), $\OWNR[\cid] \notin
   \CU$ in \advB's unforgeability game either.
@@
   \adv~all belong to the same user (by assumption, in \HU) -- i.e., they are
-  bound to its \usk. Moreover, since \adv~wins its game, the signature output by
+  bound to its \usk. But, since \adv~wins its game, the signature output by
   \adv~has not been obtained via its \SIGN oracle. But, given that the user is
@@
 
-  Simulation of \adv's oracles by \advB is as in the unforgeability-1 proof.
+  Simulation of \adv's oracles by \advB is as in the unforgeability-1 proof
+  (leveraging the \OBTAIN oracle instead of \OBTISS or \ISSUE).
   \advB outputs whatever \adv~outputs, adding a $(\yinsp,\iproof)$ pair, honestly
@@
 Briefly, this is achieved via a $(\fissue^1,\feval^{\dattrs,H,V,L},
-\finsp^{F})$-\CUASGenInt restriction, where $\fissue^1$ is as in
+\finsp^{H})$-\CUASGenInt restriction, where $\fissue^1$ is as in
 \figref{fig:func-restrictions}, and $\feval^{\dattrs,H,V,L}$ and $\finsp^{H}$
@@
     \nonumber \\
-  & \hspace*{-10em} \pcif F(V,\cidi) \in L \lor F(V,\cidu) \in L: \pcreturn \bot
+  & \hspace*{-10em} \pcif H(V,\cidi) \in L \lor H(V,\cidu) \in L: \pcreturn \bot
   \nonumber \\
   & \hspace*{-10em} \pcelse \pcreturn (\lbrace \attrs_i \rbrace_{i\in \dattrs},V) \nonumber \\
-  \finsp^{F}((\cdot,\yeval^1),\cdot,((\cidi,\cidu),\attrs),\cdot)
+  \finsp^{H}((\cdot,\yeval^1),\cdot,((\cidi,\cidu),\attrs),\cdot)
   \coloneqq  & \nonumber \\
-  & \hspace*{-10em} \pcreturn (F(\yeval^1,\cidi),F(\yeval^1,\cidu))
+  & \hspace*{-10em} \pcreturn (H(\yeval^1,\cidi),H(\yeval^1,\cidu))
   \label{eq:funcs-rac}
@@
 Concretely, $\feval^{\dattrs,H,V,L}$ is defined via a set of attributes \dattrs
-to reveal (e.g., age, etc.), a PRF $F$, a string identifying the verifier $V$
+to reveal, a PRF $H$, a string identifying the verifier $V$
 and a list $L$ of revocation handles by $V$. Note that, these ``extra
-parameters'' can be hardcoded, though: $F$ can be a fixed PRF for all verifiers,
+parameters'' can be hardcoded, though: $H$ can be a fixed PRF for all verifiers,
 \dattrs and $V$ are also fixed (per verifier), and $L$ can be updated per
 verifier with some reasonable frequency -- e.g., daily -- so that the cost of
-recomputing $\feval^{\dattrs,H,V,L}$ is not high.
+recomputing $\feval^{\dattrs,H,V,L}$ is not high (of course, revocation of a
+credential is not effectuve until $L$, and the function, is updated).
 %
@@
 issuer; and \cidu, chosen by the user), $\feval^{\dattrs,H,V,L}$ internally
-computes $F(V,\cidi)$ and $F(V,\cidu)$. If either appears in $L$, \feval aborts.
+computes $H(V,\cidi)$ and $H(V,\cidu)$. If either appears in $L$, \feval aborts.
 Otherwise, it sets $\yeval^0 \gets \lbrace \attrs_i \rbrace_{i\in\dattrs}$ and
@@
 H(\yeval^1,\cidu))$. Thus, if the verifier $V$ wants to revoke a credential, all
-it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$.
+it has to do is ask the opener to decrypt $\yinsp$, via $RetrieveCredHandle$,
+and add it to its list $L$.
 %
@@
   using $\feval^{\dattrs,H,V,L}$ as signature evaluation function, and
-  $\finsp^F$ as open function. The \yeval value output by the verifier, when
+  $\finsp^H$ as open function. The \yeval value output by the verifier, when
   it accepts, is the $\yeval^0$ value produced by \Sign in \CUASGenInt.
@@
 We prove that \CUASRAC is an anonymous and unforgeable anonymous credential
-scheme, according to \cite{fhs19}, if the underlying \CUASGen construction
-has signature anonymity and is unforgeable.
+scheme, according to the model in \figref{fig:model-rac}, if the underlying
+\CUASGen construction has signature anonymity and is unforgeable.
 %
 As for \CUASAC, we reduce to security of \CUASGen rather than to
-$\CUASGen^{int}$. The ``translation'' between \CUASGen and $\CUASGen^{int}$ is
+\CUASGenInt. The ``translation'' between \CUASGen and \CUASGenInt is
 again trivial.
@@
   \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
-  according to \cite{fhs19}.
+  according to the model in \figref{fig:model-rac}.
 \end{theorem}
@@
   To simulate oracle calls by \adv, \advB simply redirects to its corresponding
-  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR,ReqCredHandle$, \advB
+  oracle, i.e.: for calls to \oracle{HU}, \oracle{CU}, \oracle{Obtain},
+  \oracle{Show}, \oracle{LoR}, \oracle{ReqCredHandle}, \advB
   redirects to \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, or \OPEN (in this case,
@@
   If the base \CUASGen construction has signature unforgeability according to
-  \defref{def:sign-forge-uas}, and $F$ is one-way, then \CUASRAC is an
+  \defref{def:sign-forge-uas}, and $H$ is a secure PRF, then \CUASRAC is an
   unforgeable RAC scheme.
@@
 
-  To simulate oracle calls by \adv, \advB acts as in the anonymity proof. Assume
-  that \adv~wins its game via the winning condition of line 9 in the RAC
-  unforgeability game. The same reasoning as in \CUASAC applies here. Next, note
-  that the probability of \adv~winning its game via condition $h_0 \in L$ at
-  line 11 is negligible, due to soundness of the NIZK for $\NIZKRel_{\Sign}$.
-  Moreover, soundness of NIZK for $\NIZKRel^{\Sign}$ as well as one-wayness
-  of $F$ ensure that, if $h_1 \notin L$, then $b_1 = 1$. Namely, even when given
-  $F(V,\cidi),F(V,\cidu)$ for a credential identified by $(\cidi,\cidu)$ owned
-  by an honest user, and some (potentially malicious) $V$, it is not possible to
-  generate $F(V',\cidi)$ nor $F(V',\cidu)$, for $V'=V$.
+  To simulate oracle calls by \adv, \advB acts as in the anonymity proof
+  (leveraging \OBTISS and \ISSUE oracles instead of \OBTAIN). Assume that \adv~
+  wins its game via the winning condition of line 9 in the RAC unforgeability
+  game. The same reasoning as in \CUASAC applies here. Next, note that the
+  probability of \adv~winning its game via condition $h_0 \in L$ at line 11 is
+  negligible, due to simulation extractability of the NIZK for \RelSig.
+  Moreover, simulation extractability of the NIZK for \RelSig as well as
+  randomness of $H$ ensure that, if $h_1 \notin L$, then $b_1 = 1$. Namely, even
+  when given $H(V,\cidi),H(V,\cidu)$ for a credential identified by
+  $(\cidi,\cidu)$ owned by an honest user, and some (potentially malicious) $V$,
+  it is not possible to generate $H(V',\cidi)$ nor $H(V',\cidu)$, for $V'=V$.
   % 
@@
 verifier-local revocation, we can have \finsp just output the $(\cidi,\cidu)$
-pair (resp., \upk), and no assumption regarding $F$ is needed.
+pair (resp., \upk), and no assumption regarding $H$ is needed.
 
@@
 for organisations composed by many members. Delegation chain privacy could be
-achieved by making \feval output projective proofs like in \cite{bcc+09}, but we
+achieved by making \feval output projective proofs like in \cite{bcc+09} (or,
+to some extent, building on \CUASGenHideIss rather than on \CUASGen), but we
 leave that out of scope for brevity. Our simple scheme
@@
 existence of a helper function $(\ipk_0,\lbrace (\ipk_i,\cred_i)
-\rbrace_{i\in[1,l]}) \gets ExtractChain(\utrans)$ that outputs a sequence of
-public keys and credentials from the root issuer $\ipk_0$ to the actual
-credential used to sign $(\ipk_l,\cred_l)$.
+\rbrace_{i\in[1,l]}) \gets \helper{ExtractChain}(\utrans)$ that outputs a
+sequence of public keys and credentials from the root issuer $\ipk_0$ to the
+actual credential used to sign $(\ipk_l,\cred_l)$.
 
@@
 level of the credential. That is, $\attrs_1=l$, for a credential of level $l$.
-In addition, all users (i.e., with $l>0$) who want to delegate have to publicly
+In addition, all users (with $l>0$) who want to delegate have to publicly
 list:
@@
   and $(\opk,\osk) \gets \OKeyGen(\parm',\finsp^0)$ from our
-  $\CUASGen^{usr-iss}$ construction. Returns $\parm \gets (\parm',\opk)$. Note
+  \CUASGenInt construction. Returns $\parm \gets (\parm',\opk)$. Note
   that $\finsp^0$ can be replaced by any desired opening function.
@@
 We prove that \CUASDAC is an anonymous and unforgeable DAC scheme, according to
-the (interactive version of the) model in \figref{fig:model-dac}, if the
-underlying \CUASGenInt construction has anonymous issuance and signing, and is
-unforgeable.
+the model in \figref{fig:model-dac}, if the underlying \CUASGenInt construction
+has anonymous issuance and signing, and is unforgeable.
 
@@
   unforgeability according to (the interactive version of)
-  \defref{def:sign-forge-uas}, and non-frameable according to (the interactive
-  version of) \defref{def:frame-uas}, then \CUASDAC is an unforgeable DAC
-  scheme.
+  \defref{def:sign-forge-uas}, and is non-frameable according to (the
+  interactive version of) \defref{def:frame-uas}, then \CUASDAC is an
+  unforgeable DAC scheme.
 \end{theorem}
@@
   credential and associated \ipk used to produce \Sig. Note that, for this
-  \ipk, $\ipk = \ipk_{n-1}$ in $\Exp^{forge}_{\adv,dac}$. In \CUASDAC, we can
-  leverage $\ipk_{n-1}$ to fetch from the public list a signature $\Sig_{n-1}$
-  generated by the issuer owner of $\ipk_{n-1}$. Again, we apply \ExtractSign
-  from \CUASGen, to get the credential one layer up in the chain.
-  $ExtractChain$ repeats this step, until reaching the top level credential,
-  issued by $\ipk_0$.
+  \ipk (of level $n$), $\ipk = \ipk_{n-1}$ in $\Exp^{forge}_{\adv,dac}$. In
+  \CUASDAC, we can leverage $\ipk_{n-1}$ to fetch from the public list a
+  signature $\Sig_{n-1}$ generated by the issuer owner of $\ipk_{n-1}$. Again,
+  we apply \ExtractSign from \CUASGen, to get the credential one layer up in the
+  chain. \helper{ExtractChain} repeats this step, until reaching the top level
+  credential, issued by $\ipk_0$.
 

### 2022-10-05 prism-backend/research/gsac/app-related-proofs.tex
Spellchecked abstract and intro.
Typos and notation fixed. Some important updates pending...

@@
   Assume an adversary \adv~ against anonymity in \CUASGS. This directly leads
-  to an adverary \advB against anonymity of the $(\fissue^1,\feval^0,
+  to an adversary \advB against anonymity of the $(\fissue^1,\feval^0,
   \finsp^{\upk})-\CUASGen$ instance.
 
-  Concretely, observe that calls to \adv's $Ch,Open,SndToU,WReg,USK,CrptU$
+  Concretely, observe that calls to \adv's \oracle{Ch}, \oracle{Open},
+  \oracle{SndToU}, \oracle{WReg}, \oracle{USK}, \oracle{CrptU}
   oracles can be directly simulated by calls to \advB's oracles $\CHALb,
-  \OPEN,\HUGEN,\WREG,\CUGEN,\UCORR$ oracles. Thus, if \adv~guesses its bit $b$
-  with non-negligible probability, this directly leads to a non-negligible
-  probability of guessing \advB's challenge bit.
+  \OPEN,\HUGEN,\OBTAIN,\WREG,\CUGEN,\UCORR$ oracles. Thus, if \adv~guesses its
+  bit $b$ with non-negligible probability, this directly leads to a
+  non-negligible probability of guessing \advB's challenge bit.
   \qed
@@
   \advB's simulation of \adv's environment is as in the proof for anonymity
-  of \CUASGS. \advB simply outputs whatever \adv~outputs in line 2 of its
+  of \CUASGS (leveraging the \OBTISS and \ISSUE oracles, instead of \OBTAIN).
+  \advB simply outputs whatever \adv~outputs in line 2 of its
   traceability game. Note that, whenever \CUASGS accepts a signature, so does
@@
 \begin{proof}
-  Assume $\adv$ is an adversary against ring signature anonymity for \CUASRing.
+  Assume \adv~is an adversary against anonymity for \CUASRing.
   Then, we build \advB against anonymity of \CUASGen. Concretely, \advB first
-  generates $n$ key pairs for \adv simulating $KeyGen$ in \adv's game. Since
+  generates $n$ key pairs for \adv~ simulating $KeyGen$ in \adv's game. Since
   $KeyGen$ simply uses algorithms of $\CUASGen^{hide-iss}$, \advB can do this
@@
   $\fissue^{\sring}$ as issuance function, and $\finsp^0$ as opening function.
-  Then, \advB invokes $\adv$ passing the $n$ produced public keys, and
-  answers $\adv$'s $SIGN(i,R,\msg)$ queries as follows. If user $i$ has not yet
+  Then, \advB invokes $\adv$ passing the $n$ produced public keys, and answers
+  \adv's \oracle{SIGN}(i,R,\msg) queries as follows. If user $i$ has not yet
   produced a credential for ring $R$, where $\pk_i \in R$, \advB makes a call to
@@
   The simulation of \adv's anonymity game is perfect, and \advB wins its game
-  whenever \adv does.
+  whenever \adv~ does.
   \qed
@@
   %
-  \advB prepares the environment as the adversary \advB against anonymity,
-  and answers \adv's queries to the $SIGN$ oracle also as in the anonymity
-  proof. To answer \adv's queries to its $CORR$ oracle, \advB leverages the
-  \ICORR oracle in the non-frameability game for \UAS. Finally, \advB outputs
-  whatever $\adv$ outputs.
+  \advB prepares the environment as the adversary \advB against anonymity, and
+  answers \adv's queries to the \oracle{SIGN} oracle also as in the anonymity
+  proof. To answer \adv's queries to its \oracle{CORR} oracle, \advB leverages
+  the \ICORR oracle in the non-frameability game for \UAS. Finally, \advB
+  outputs whatever $\adv$ outputs.
 
@@
   honest \usk within $R$ that produced the signature, so $\OWNR[\scid] \in \HU$
-  in \advB's non-frameability game. Also, since $\adv$ never queried its $SIGN$
-  oracle, then by construction there cannot exist a matching entry in \advB's
-  $\SIG[\uid]$ table. Thus, \advB wins the non-frameability game whenever
-  $\adv$ wins its unforgeability game. Since \CUASGen is non-frameable, then
-  this probability must be negligible.
+  in \advB's non-frameability game. Also, since $\adv$ never queried its
+  \oracle{SIGN} oracle, then by construction there cannot exist a matching entry
+  in \advB's $\SIG[\uid]$ table. Thus, \advB wins the non-frameability game
+  whenever $\adv$ wins its unforgeability game. Since \CUASGen is non-frameable,
+  then this probability must be negligible.
   %
@@
 do not have issuance anonymity, as the user public key is passed to the issuer.
-Note that, for ease of reference to the games in \secref{sec:formal-uas}, we
+For ease of reference to the games in \secref{sec:formal-uas}, we
 reduce to security of \CUASGen rather than to $\CUASGen^{int}$. The
@@
   \label{thm:anon-cuasac}
-  If the base \CUASGen construction is anonymous according to
+  If the base \CUASGen construction has signature anonymity according to
   \defref{def:sign-anonymity-uas}, then \CUASAC is an anonymous AC scheme
@@
   To simulate oracle calls by \adv, \advB simply redirects to its corresponding
-  oracle, i.e.: for calls to $HU,CU,Obtain,Show,LoR$, \advB redirects to
-  \HUGEN,\CUGEN,\OBTAIN,\SIGN,\CHALb, respectively. Note that translating
+  oracle, i.e.: for calls to \oracle{HU}, \oracle{CU}, \oracle{Obtain},
+  \oracle{Show}, \oracle{LoR}, \advB redirects to
+  \HUGEN, \CUGEN, \OBTAIN, \SIGN, \CHALb, respectively. Note that translating
   the inputs from the former into inputs for the latter is trivial.

### 2022-10-05 prism-backend/research/gsac/app-uas-proofs.tex
Typos and notation fixed. Some important updates pending...

@@
 replaces the \Setup algorithm of each NIZK with the corresponding \NIZKSimSetup
-algorithm, and returns the generated parameters along with the
-trapdoors. \ExtractIssue and \ExtractSign simply run the \Extract functions
-of the corresponding \NIZK scheme, leveraging the trapdoor produced during
-\SimSetup. Note that, in our games definitions, both algorithms are always run
-over signatures that have already been verified (in the case of \ExtractSign)
+algorithm, and returns the generated parameters along with the trapdoors.
+\ExtractIssue and \ExtractSign simply run the \helper{\Extract} functions of the
+corresponding \NIZK scheme, leveraging the trapdoor produced during \SimSetup.
+Note that, in our games definitions, both algorithms are always run over
+signatures that have already been verified (in the case of \ExtractSign)
 or transcripts maintained by honest issuers (in the case of \ExtractIssue).
@@
       \procedure{$\SimSetup(1^\secpar)$}{%
-        \textrm{Parse}~\secpar~\textrm{as}~(\Csecpar,\NIZKsecpar,\SBCMsecpar,
-        \Esecpar). \\
         % \Cparm \gets \CSetup(\Csecpar), 
-        \SBCMparm \gets  \SBCMSetup(\SBCMsecpar) \\
+        \SBCMparm \gets  \SBCMSetup(\secpar) \\
         % \Sparm \gets \SSetup(\Ssecpar), 
-        \Eparm \gets \ESetup(\Esecpar) \\
+        \Eparm \gets \ESetup(\secpar) \\
         (\NIZKcrs_{\Issue},\trap_{\Issue}) \gets
-        \NIZKSimSetup^{\NIZKRel_{\Issue}}(\NIZKsecpar) \\
+        \NIZKSimSetup^{\RelIss}(\secpar) \\
         (\NIZKcrs_{\Sign},\trap_{\Sign}) \gets
-        \NIZKSimSetup^{\NIZKRel_{\Sign}}(\NIZKsecpar) \\
+        \NIZKSimSetup^{\RelSig}(\secpar) \\
         (\NIZKcrs_{\Open},\trap_{\Open}) \gets
-        \NIZKSimSetup^{\NIZKRel_{\Open}}(\NIZKsecpar) \\
+        \NIZKSimSetup^{\RelIns}(\secpar) \\
         \pcreturn ((% \Cparm,
@@
 
-  Game 1: We simulate the NIZK proof corresponding to $\NIZKRel_{\Issue}$ that
+  Game 1: We simulate the NIZK proof corresponding to \RelIss that
   the \OBTCHALb oracle produces when queried by \adv. The zero-knowledge
@@
   Game 2: In queries to \OBTCHALb, before simulating the NIZK proof, we replace
-  the produced \yissue value with a random element from \rngfissue. Since
-  \fissue is a \UAS-acceptable function, game 2 is indistinguishable from game
-  1.
+  the produced \yissue value with a random element from $\rngfissue \setminus
+  0$. Since \fissue is a \UAS-acceptable function, game 2 is indistinguishable
+  from game 1.
 
@@
   a number $q < n$, where $n$ is the number of users that \adv~creates via
-  \HUGEN, and assigning to the $q$-th user the $(\SBCMvk,\SBCMsk)$ key pair
-  that \advB receives in its blindness game. Then, when \adv~makes a query
-  to its \OBTCHALb oracle, if the chosen issuer is the $q$-th user, \advB
-  forwards \adv's messages to its own $\langle COM(\SBCMvk,
-  \overline{\smsg}_{\bin},\smsg),\cdot\rangle$ oracle. Finally, \advB outputs
+  \HUGEN, and assigning to the $q$-th user the \vk key that \advB receives in
+  its blindness game. Then, when \adv~makes a query to its \OBTCHALb oracle, if
+  the chosen issuer is the $q$-th user, \advB forwards \adv's messages to its
+  own \oracle{BLIND} oracle. Finally, \advB outputs \todo{XXXX UPDATE}
   whatever \adv~does. Note that, since in Game 2 we replace the \yissue value
-  with a random value, and simulate the $\NIZKRel_{\Issue}$ proof, \adv~is not
+  with a random value, and simulate the \RelIss proof, \adv~is not
   receiving information about the blindly signed messages beyond what \advB
@@
   Then, $\trans[\cid] = (\yissue,\utrans)$, and \utrans contains a NIZK proof
-  \proofiss proving knowledge by the (potentially corrupt) user of a witness in
+  \NIZKproof proving knowledge by the (potentially corrupt) user of a witness in
   \RelIss. Since the issuer is honest, it verifies the NIZK as part of the
@@
   probability that it happens must be negligible.
+  %
+  \qed
 \end{proof}
@@
   \paragraph{(a) \Judge accepts $(\yinsp,\iproof)$.} %
-  Simulation extractability of $\NIZK^{\Sign}$ ensures that $\cinsp =
+  Simulation extractability of the NIZK for \RelSig ensures that $\cinsp =
   \EEnc(\Eek,\yinsp)$, and since $(\yinsp,\iproof)$ is generated honestly at
   line 5, then \yinsp is the correct decryption of \cinsp, and completeness of
-  $\NIZK^{\Open}$ ensures that \Judge outputs $1$ at line 6.
+  the NIZK for \RelIns ensures that \Judge outputs $1$ at line 6.
 
   \paragraph{(b) $(\yeval^0,\yeval^1)$ are the correct signature evaluation
-    pair.} Also, due to simulation extractability of $\NIZK^{\Sign}$:
+    pair.} Also, due to simulation extractability of the NIZK for \RelSig:
 
@@
   Thus, the probability of \adv~winning at line 12 is negligible, due to
-  simulation extractability of $\NIZK^{\Sign}$.
+  simulation extractability of the NIZK for \RelSig.
 
@@
   \ExtractSign match the evaluation of \feval. Thus, simulation extractability
-  of $\NIZK^{\Sign}$ ensures that $\finsp((\yeval^0,\yeval^1),\upk,\lbrace
+  of the NIZK for \RelSig ensures that $\finsp((\yeval^0,\yeval^1),\upk,\lbrace
   (\cid_i,\attrs_i)\rbrace_{i\in[n]},\msg) = \yinsp$ and, also, that \yinsp
@@
   of \adv~winning at line 13 is negligible due to simulation extractability
-  of $\NIZK^{\Sign}$.
+  of the NIZK for \RelSig.
 
   \paragraph{(d) All {\cred}s are bound to the \usk of a known \uid.} %
-  $\NIZKRel^{\Sign}$ includes a condition that $\forall i\in[n],
+  \RelSig includes a condition that $\forall i\in[n], 
   \SBCMVerify(\ipk_i,\cred_i,\usk,\attrs_i) = 1$. Thus, simulation
-  extractability of $\NIZK^{\Sign}$ and correctness of \SBCM, ensure that all
-  credentials involved in the signature contain the same \usk as their user key
-  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
+  extractability of the NIZK for \RelSig and correctness of \SBCM, ensure that
+  all credentials involved in the signature contain the same \usk as their user
+  key  (first) attribute. Thus, either $\OWNR[\lbrace \cid_i \rbrace_{i\in[n]}]$
   returns some \uid in $\HU \cup \CU$, or it returns $\bot$ because no such
@@
   since they only accept calls from known {\uid}s (either in \HU or \CU,
-  respectively). Since, by simulation extractability of $\NIZK^{\Sign}$, at
+  respectively). Since, by simulation extractability of the NIZK for \RelSig at
   least one such credential must have been used to produce the signature, then
@@
   Since the signature output by \adv~is accepted by \Verify at line 4,
-  simulation extractability of $\NIZK^{\Sign}$ ensures that $\yeval = \yeval^0$,
-  and $\tyeval^1 = \yeval^1$. Similarly, if the $(\yinsp,\iproof)$
+  simulation extractability of the NIZK for \RelSig ensures that $\yeval =
+  \yeval^0$, and $\tyeval^1 = \yeval^1$. Similarly, if the $(\yinsp,\iproof)$
   pair output by \adv~is accepted by \Judge, simulation extractability of
-  $\NIZK^{\Sign}$ and $\NIZK^{\Open}$ implies that both checks at lines 8 and 9
+  the NIZKs for \RelSig and \RelIns implies that both checks at lines 8 and 9
   pass. Hence, the probability that the adversary wins at either lines 8 or 9 is
-  negligible, after simulation extractability of $\NIZK^{\Sign}$ and
-  $\NIZK^{\Open}$.
+  negligible, after simulation extractability of the NIZKs for \RelSig and
+  \RelIns.
 
-  Next, we prove that, after zero-knowledge and simulation extractability of
-  $\NIZKRel_{\Sign}$, and blindness of \SBCM, no credential from an honest user
+  Next, we prove that, after zero-knowledge and simulation extractability of the
+  NIZK for \RelSig, and blindness of \SBCM, no credential from an honest user
   can be extracted from the signature output by \adv, except with negligible
@@
   The crucial observation is that, as in \cite{cl06} \CUASGen's \Sign algorithm
-  produces a signature of knowledge for the relation defined by
-  $\NIZKRel^{\Sign}$. That is, given $(x,w) \in \NIZKRel^{\Sign}$, one can
-  compare $x$ and $w$ to the public and private key of a signature algorithm,
-  respectively. In $\NIZKRel^{\Sign}$, $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
+  produces a signature of knowledge for the relation defined by \RelSig
+  That is, given $(x,w) \in \NIZKRel^{\Sign}$, one can compare $x$ and $w$ to
+  the public and private key of a signature algorithm, respectively. In \RelSig,
+  $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
   \cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r,r')$ is the private key ($w$), and
-  $(\msg,\feval,\yeval^0,\cinsp,\lbrace \ipk_i \rbrace_{i\in[n]},\Eek)$ is the
+  $(\msg,\feval,\yeval^0,\cinsp,\lbrace \ipk_i \rbrace_{i\in[n]},\ek)$ is the
   public key ($x$).
@@
   in the \Sign function within the \SIGN oracle, we simulate the NIZK proof.
-  After the zero-knowledge property of $\NIZK^{\NIZKRel_{\Sign}}$, $G_1$ is
+  After the zero-knowledge property of the NIZK for \RelSig, $G_1$ is
   indistinguishable from $G_0$. Now, in $G_1$, simulation extractability of
-  $\NIZK^{\NIZKRel_{\Sign}}$ ensures that \ExtractSign outputs a valid
+  the NIZK for \RelSig ensures that \ExtractSign outputs a valid
   witness for $(\msg,\feval,\yeval^0,\cinsp,\lbrace ipk_i \rbrace_{i\in[n]},
-  \Eek)$. Note that this witness must include some \usk which, in case of
+  \ek)$. Note that this witness must include some \usk which, in case of
   being owned by an honest user, has not been leaked to \adv~--as the user

### 2022-10-06 prism-backend/research/gsac/app-building-blocks.tex
Fixed some flaws. Still doing passes for minor checks.

@@
 
+Modelling-wise, when using this extension, we need to refine also the
+\oracle{BLIND} oracle used in the blindness game, so that besides the $\osmsg_0$
+and $\osmsg_1$ messages to be signed in committed form, it also receives their
+corresponding extended witnesses and statements. To prevent trivial wins, the
+oracle aborts if any of the two options does not satisfy the relation. That is,
+calls to this oracle are: $\oracle{BLIND}^\NIZKRel((\osmsg_0,x'_0,w'_0),
+(\osmsg_1,x'_1,w'_1),\smsg)$. And, in case $((\smsg,x'_b),(\osmsg_b,w'_b))
+\notin \NIZKRel$, for $b=0,1$, \oracle{BLIND} aborts. Otherwise, the output
+is still $(\Ccom,\pi)$, for some ``extended'' $\pi$.
+
 \paragraph{Proofs of knowledge of a \SBCM signature.} %

### 2022-10-06 prism-backend/research/gsac/app-uas-proofs.tex
Fixed some flaws. Still doing passes for minor checks.

@@
 
-  From an adversary \adv~against Game 2, we can build an adversary \advB against
-  \SBCM's blindness property. The simulation that
-  \advB does is straightforward. \advB runs Game 2 for \adv, randomly picking
-  a number $q < n$, where $n$ is the number of users that \adv~creates via
-  \HUGEN, and assigning to the $q$-th user the \vk key that \advB receives in
-  its blindness game. Then, when \adv~makes a query to its \OBTCHALb oracle, if
-  the chosen issuer is the $q$-th user, \advB forwards \adv's messages to its
-  own \oracle{BLIND} oracle. Finally, \advB outputs \todo{XXXX UPDATE}
-  whatever \adv~does. Note that, since in Game 2 we replace the \yissue value
-  with a random value, and simulate the \RelIss proof, \adv~is not
-  receiving information about the blindly signed messages beyond what \advB
-  forwards from its own oracle. Thus, if \adv~wins in its game, \advB wins in
-  its blindness game. However, since \advB has to guess the correct user
-  that \adv~will use as issuer in its \OBTCHALb oracle, we have a $1/n$ security
-  loss, where $n$ is the total number of users created by \adv.
+  From an adversary \adv~against game 2, we can build an adversary \advB against
+  \SBCM's blindness property. The simulation that \advB does is straightforward.
+  \advB runs game 2 for \adv, using the \SBCM \parm variable it receives, to
+  set up the \SBCM instance for game 2. When \adv~makes a query to its \OBTCHALb
+  oracle, \advB prepares a call to its $\oracle{BLIND}^\RelIss$ oracle, setting
+  $\osmsg_b \gets \PRVUK[\cuid_b]$ as message to be blindly signed and
+  accompanying each $\osmsg_b$ with its corresponding
+  $(\cscid_{i,b},\ATTR[\cscid_{i,b}])$ (for all $i\in[n]$). In the response
+  received from $\oracle{BLIND}^\RelIss$ (which succeeds in case both options
+  are in \RelIss), \advB replaces the proof with a simulated one, and \yissue
+  with a random value (as done in game 2). With the response from \adv, \advB
+  completes the credential running \SBCMUnblind as usual. The rest of the
+  simulation is as in game 2. Finally, \advB outputs whatever \adv~outputs.
+  Again, zero-knowledge of the NIZK for \RelIss, and the fact that \fissue is
+  \UAS-acceptable, ensure that simulation is correct, and \advB wins whenever
+  \adv~does.
   %
@@
   least one such credential must have been used to produce the signature, then
-  this breaks the one-more forgery property of the underlying \SBCM.
+  this breaks the one-more forgery property of the underlying \SBCM scheme.
+
+  \paragraph{(e) All used credentials have been honestly issued.} %
+  Finally, assume that there exists some $\cred_i$ among the ones used to
+  produce the signature such that the credential is valid (i.e., \VerCred
+  returns $1$ for the extracted values), but no matching entry exists in
+  $\CRED[\cid]$. This means that the credential is a valid signature by the
+  honest issuer with public key $\ipk_i$, but it was not produced via a call
+  to \OBTISS or \ISSUE. Thus, it directly breaks the one-more forgery property
+  of the underlying \SBCM scheme.
   %
@@
 
-\subsection{Security of $\CUASGen^{hide-iss}$}
+\subsection{Security of \CUASGenHideIss}
 \label{sapp:sec-hide-iss}
 
-The only aspect that changes from \CUASGen to $\CUASGen^{hide-iss}$ is the
+The only aspect that changes from \CUASGen to \CUASGenHideIss is the
 relationship used for signing, where we hide the specific issuer who produced
@@
 %
-Concerning unforgeability, note that the credential that is used to produce the
-\UAS signature still needs to originate from a \uid in either \HU or \CU.
+Issuance unforgeability is also unaffected by the change. Concerning signature
+unforgeability, note that the credential that is used to produce the \UAS
+signature still needs to originate from a \uid in either \HU or \CU.
 Otherwise, such credential, extracted by \ExtractSign, is a forgery and breaks
@@
 
-Thus, if \CUASGen is a secure \UAS scheme, so is $\CUASGen^{hide-iss}$.
+Thus, if \CUASGen is a secure \UAS scheme, so is \CUASGenHideIss.
 
-\subsection{Security of $\CUASGen^{int}$}
+\subsection{Security of \CUASGenInt}
 \label{sapp:sec-interactive}
@@
 whether signature/authentication is interactive or not, the proof for issuance
-anonymity in $\CUASGen^{int}$ is the same as for \CUASGen.
+anonymity in \CUASGenInt is the same as for \CUASGen.
 
@@
 to the message to be signed by the oracle) applies here too. Since the
-interactive protocol includes non-interactive proofs for the $\NIZKRel^{\Sign}$
-and $\NIZKRel^{Open}$ relations, the proofs for unforgeability and
+interactive protocol includes non-interactive proofs for the \RelSig
+and \RelIns relations, the proofs for unforgeability and
 non-frameability of \CUASGen still apply.

### 2022-10-06 prism-backend/research/gsac/formal-uas.tex
Fixed some flaws. Still doing passes for minor checks.

@@
 
-Signature unforgeability, \ExpForgeSign, is mainly a combination (and
+Signature unforgeability, \ExpForgeSign (see \figref{fig:exp-uas-unfor}),
+is a combination (and
 generalisation) of known requirements in AC and GS schemes. Namely, the
@@
 We thus extend unforgeability of signatures with issuance unforgeability,
-\ExpForgeIssue. It captures that all honestly issued credentials meet the
-requirements set by the corresponding issuer, and that any further credential
+\ExpForgeIssue (see \figref{fig:exp-uas-unfor}). It captures that all honestly
+issued credentials meet the requirements set by the corresponding issuer, and
+that any further credential
 involved in the request is a valid credential, bound to the same known user. For
@@
 transcripts.
-
-We formalise both properties in \figref{fig:exp-uas-unfor}.
 
@@
   \hspace*{-2em}
-  \scalebox{0.85}{
-    \begin{minipage}[t]{0.7\textwidth}
+  \scalebox{0.8}{
+    \begin{minipage}[t]{0.67\textwidth}
       \procedure[linenumbering]{$\ExpForgeIssue(1^\secpar)$}{%
@@
         \pcreturn \OWNR[\lbrace \cid_i \rbrace_{i\in[n]}] \notin
-        \HU \cup \CU~\lor \\
+        \HU \cup \CU \lor (\exists i\in[n]~\suchthat \\
+        \pcind \VerCred(\usk,\cid_i,\attrs_i,\cred_i,\ipk_i)=1 \land
+        \CRED[\cid] = \bot)~\lor \\
         \pcind \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,

### 2022-10-06 prism-backend/research/gsac/formal-uas.tex
Some rewriting..

@@
 this, we allow the adversary \adv~to interact with the oracles (restricted to
-honest issuers). Eventually, \adv~is challenged to output a credential \Cred
-from which we extract the actual witnesses used in the credential request
-associated to \cid. \adv~wins if the issuance function, applied to the extracted
+honest issuers). Eventually, \adv~is challenged to output a credential
+$\Cred=(\cid,\attrs,\cred,\ipk)$. Using \cid, we extract the actual witnesses
+used in the credential request $\utrans[\cid]$. \adv~wins if the issuance
+function, applied to the extracted
 values, does not meet the expected output, if not all of the credentials (if
 any) used to endorse the request belong to the same (known) user to whom the new
-credential was issued, or if any of such credentials is a forgery. Note that the
+credential was issued, or if any of such credentials is not a valid signature by
+its issuer, or it is, but is a forgery. Note that the
 issuance transcript associated to the credential output by the adversary must

### 2022-10-06 prism-backend/research/gsac/app-related-extra.tex
Fixed some flaws. Still doing passes for minor checks.
Minor edits.

@@
 In the model for this setting, since there are multiple issuers, in addition
-to the oracles in \secref{ssec:related-models-ac}, we use $HI$ and $CI$ oracles,
+to the oracles in \secref{ssec:related-models-ac}, we use \oracle{HI} and
+\oracle{CI} oracles,
 for creating honest and corrupt issuers, which can be simulated via \HUGEN,
@@
   & \fissue^{l,D}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
-    \pcreturn \attrs_1 = l+1 \land \cattrs \subseteq D \nonumber \\
+    \pcreturn \cattrs_1 = l \land \attrs_1 = l+1
+    \land \cattrs \subseteq D \land \attrs_{[2..n]} \subseteq \cattrs \nonumber \\
   & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
@@
   %
-  If \adv~wins in its issuance anonymity game, then so does \advB with the same
-  probability, as the simulation is perfect.
+  Note that the issuance anonymity game for DAC is essentially the same as that
+  for \UAS, with the exception that -- to avoid trivial wins -- in the DAC game
+  we do not allow credentials with different delegation chains to be used
+  simultaneously in the challenge oracle.
+  %
+  Thus, if \adv~wins in its game, so does \advB.
   % 
@@
 \begin{proof}
-  Given \adv~ against signature anonymity of \CUASDAC as defined in
+  Given \adv~against signature anonymity of \CUASDAC as defined in
   $\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
@@
   \CUASDAC -- in this case, \adv's \oracle{SigLoR} oracle corresponds to \advB's
-  \CHALb. Again, the simulation is perfect, and whenever \adv~wins its
-  $\Exp^{sig-anon-b}$ game, so does \advB.
+  \CHALb.
+  %
+  Again, the game is the same as for \UAS, only conditioned on the challenge
+  signatures being produced from credentials with the same delegation chain.
+  Thus, whenever \adv~wins its $\Exp^{sig-anon-b}$ game, so does \advB.
   % 
@@
 \begin{proof}
-  First, we define the $ExtractChain(\utrans)$ function for our construction.
-  Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows for the approach
+  First, we define the $\helper{ExtractChain}(\utrans)$ function for our
+  construction. Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows
+    for the approach
     to transform non-interactive signature and verification in \UAS to
     interactive presentations, as described in \secref{ssec:variants}.}, where
-  $r$ is a fresh random number specified by the adversary,
-  and \Sig is a \CUASGen signature over $r$. Thus, $ExtractChain$ leverages
+  $r$ is a fresh random number specified by the adversary, and \Sig is a
+  \CUASGen signature over $r$. Thus, \helper{ExtractChain} leverages
   \ExtractSign from \CUASGen (see \secref{ssec:security-uas}) to get the
@@
   to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
-  suppose that from \utrans, $ExtractChain$ outputs at line 6 a
+  suppose that from \utrans, \helper{ExtractChain} outputs at line 6 a
   delegation chain that makes \adv~win at line 9. This means that an

### 2022-10-06 prism-backend/research/gsac/app-uas-proofs.tex
Minor edits.

@@
   \CRED[\scid_0],\msg,\feval)$, where $\csig_0 = (\pi_0,\cinsp)$, with
-  $\pi_0 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
+  $\pi_0 = \NIZKProve^{\RelSig}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
   \cinsp,\lbrace\PUBIK[\scid_{i,0}]\rbrace_{i\in[n]},\PUBOK[\oid]),
@@
   is, in $G_1^0$, $\csig_0 = (\pi_0^s,\ceval,\cinsp)$, where $\pi^s_0 =
-  \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
+  \NIZKSim^{\RelSig}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
   \cinsp,\lbrace\PUBIK[\scid_{i,0}]\rbrace_{i\in[n]},\PUBOK[\oid]))$. By
-  zero-knowledgeness of $\NIZK^{\Sign}$, $G_1^0$ is indistinguishable from
+  zero-knowledgeness of the NIZK for \RelSig, $G_1^0$ is indistinguishable from
   $G_0^0$.
@@
   \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,
-  \cinsp)$, with $\pi_1 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
+  \cinsp)$, with $\pi_1 = \NIZKProve^{\RelSig}(\NIZKcrs_{\Sign},
   (\msg,\feval,\yeval,
@@
   $\csig_1 = (\pi_1^s,\ceval,\cinsp)$, where $\pi^s_1 =
-  \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
+  \NIZKSim^{\RelSig}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
   \cinsp,\lbrace\PUBIK[\scid_{i,1}]\rbrace_{i\in[n]},\PUBOK[\oid]))$. Again, by
-  zero-knowledge of $\NIZK^{\Sign}$, $G_1^1$ is
+  zero-knowledge of THE NIZK for \RelSig, $G_1^1$ is
   indistinguishable from $G_0^1$.
@@
   produces a signature of knowledge for the relation defined by \RelSig
-  That is, given $(x,w) \in \NIZKRel^{\Sign}$, one can compare $x$ and $w$ to
+  That is, given $(x,w) \in \RelSig$, one can compare $x$ and $w$ to
   the public and private key of a signature algorithm, respectively. In \RelSig,

### 2022-10-06 prism-backend/research/gsac/introduction-paper.tex
Fixed some flaws. Still doing passes for minor checks.
Minor edits.

@@
 a foundational block of the technology some call ``anoncreds''%
-\footnote{\url{https://hyperledger-indy.readthedocs.io/projects/sdk/en/latest/docs/design/002-anoncreds/README.html}. Last access, June 18th, 2022.},
+\footnote{\url{https://hyperledger-indy.readthedocs.io/projects/sdk/en/latest/docs/design/002-anoncreds/README.html}. Last access, October 6th, 2022.},
 the privacy-preserving cousin of W3C's Verifiable Credentials%
-\footnote{\url{https://www.w3.org/TR/vc-data-model/}. Last access, June 18th,
+\footnote{\url{https://www.w3.org/TR/vc-data-model/}. Last access, October 6th,
   2022.}.
@@
 Privacy Module)%
-\footnote{\url{https://trustedcomputinggroup.org/resource/trusted-platform-module-tpm-summary/}. Last access, June 18th, 2022.}.
+\footnote{\url{https://trustedcomputinggroup.org/resource/trusted-platform-module-tpm-summary/}. Last access, October 6th, 2022.}.
 Indeed, DAA is a very close relative of group signatures, where the signer is
@@
 building blocks, and prove its security. Despite its functional flexibility, our
-construction is simple. Like many previous related schemes, credentials are
+construction is simple. Like many related schemes, credentials are
 signatures over blocks of messages -- each message encoding a different

### 2022-10-06 prism-backend/research/gsac/app-related-proofs.tex
Minor edits.

@@
 We prove that our \CUASRing construction is anonymous and unforgeable, in the
-model given in \cite{bkm06}, if the underlying $\CUASGen^{hide-iss}$
+model given in \cite{bkm06}, if the underlying \CUASGenHideIss
 construction is secure.
@@
 \begin{theorem}[Anonymity of \CUASRing]
-  If the base $\CUASGen^{hide-iss}$ construction is anonymous according to
+  If the base \CUASGenHideIss construction is anonymous according to
   \defref{def:sign-anonymity-uas}, then \CUASRing is an anonymous ring signature
@@
   generates $n$ key pairs for \adv~ simulating $KeyGen$ in \adv's game. Since
-  $KeyGen$ simply uses algorithms of $\CUASGen^{hide-iss}$, \advB can do this
+  $KeyGen$ simply uses algorithms of \CUASGenHideIss, \advB can do this
   directly via its own \HUGEN, \ISET, and \OGEN oracles, specifying
@@
 \begin{theorem}[Unforgeability of \CUASRing]
-  If the base $\CUASGen^{hide-iss}$ construction is non-frameable according to
+  If the base \CUASGenHideIss construction is non-frameable according to
   \defref{def:frame-uas}, then \CUASRing is an unforgeable ring signature

### 2022-10-07 prism-backend/research/gsac/app-uas-proofs.tex
Last minute typo fixing.

@@
   set up the \SBCM instance for game 2. When \adv~makes a query to its \OBTCHALb
-  oracle, \advB prepares a call to its $\oracle{BLIND}^\RelIss$ oracle, setting
+  oracle, \advB prepares a call to its $\oracle{BLIND}^{\RelIss}$ oracle, setting
   $\osmsg_b \gets \PRVUK[\cuid_b]$ as message to be blindly signed and
@@
   $(\cscid_{i,b},\ATTR[\cscid_{i,b}])$ (for all $i\in[n]$). In the response
-  received from $\oracle{BLIND}^\RelIss$ (which succeeds in case both options
+  received from $\oracle{BLIND}^{\RelIss}$ (which succeeds in case both options
   are in \RelIss), \advB replaces the proof with a simulated one, and \yissue

### 2022-10-07 prism-backend/research/gsac/introduction-paper.tex
Last minute typo fixing.

@@
 signer. This is no surprise, though, as it was already observed in GS schemes
-with non-conventional opening \cite{dl21}, in DAA schemes \cite{cdl16,cdl16b}.
-In fact, simulation-extractability seems to be most useful here, something that
+with non-conventional opening \cite{dl21}, and DAA schemes \cite{cdl16,cdl16b}.
+In fact, simulation extractability seems to be most useful here, something that
 was also observed in \cite{cl06} for producing signatures out of knowledge of

### 2022-10-07 prism-backend/research/gsac/preliminaries-paper.tex
Last minute typo fixing.

@@
 encryption key \ek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\dk,
-\Ec)$ decrypts ciphertexts using decryption key \Edk. We rely on IND-CCA
+\Ec)$ decrypts ciphertexts using decryption key \dk. We rely on IND-CCA
 public-key encryption schemes.
@@
 (\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof. Within NIZK systems, we
-further need schemes that provide simulation-extractability, which in a nutshell
+further need schemes that provide simulation extractability, which in a nutshell
 means that no adversary can produce a proof from which we cannot extract a
 witness, even after seeing polynomially many simulated proofs. To model
-simulation-extractable NIZKs, we further need algorithms \NIZKSimSetup,
+simulation extractable NIZKs, we further need algorithms \NIZKSimSetup,
 \NIZKSim, and \NIZKExtract, that allow simulating proofs and extracting
 witnesses. The properties we build on are completeness, soundness,
-zero-knowledgeness, and simulation-extractability.
+zero-knowledgeness, and simulation extractability.
 

### 2022-11-03 prism-backend/research/prism-protocol/did_atala.tex
First reasonable ideal functionality of a DID-based PKI.

\section{DIDs in Atala PRISM}
\label{sec:did-atala}

\subsection{Base Functionalities}
\label{ssec:did-funcs}

\paragraph{Append-Only Bulletin Boards.} %
\todo{For now, simplified notion as in \cite{acc+20}.}

\paragraph{Digital Signatures.} %
Maybe build on \IdealFSig from \cite{canetti03}.

\subsection{Functionality \IdealFPKIDID}

Giving an ideal functionality for a DID-based PKI does not seem to be easy. The
difficulty stems from the fact that the W3C specification (see footnote
\todo{X}) is very permissive in regards to what can be seen as a valid DID
method definition. Namely, it simply states the following conditions for any
candidate method, in Section 8.2 of the specification:

\begin{description}
\item[Authentication.] It must define how authorisation is performed.  
\item[Create.] It must specify how controllers create new DIDs.
\item[Read.] It must specify how the contents of a DID can be fetched and
  authenticated.
\item[Update.] It must specify what updates can controllers apply (if any)
  to existing DIDs.
\item[Deactivate.] It must specify if DIDs can be deactivated, and how.
\end{description}

Where the authentication aspect specifically covers the way in which controllers
prove to be entitled to perform create, update, or deactivate operations.

However, since no functional requirements are given as to, e.g., what an update
may be, or what a deactivation implies, it seems hard to define a functionality
that would cover all possible options.
%
We thus take the basic approach to see DID documents as simple dictionaries
(i.e., lists of labels with corresponding values), associated to a common label,
the DID \todo{maybe draw something here}. From this, creating a DID is simply
defining a set (of at least size 1) of initial label-value pairs and get an
identifier associated to them. Updating a DID is essentially a creation, but
over an existing identifier - the functionality just replaces the old contents
with the new ones. And deactivating a DID means removing some of its labels and
associated values, where removing all of them equates to deactivating the whole
DID. Reading a DID just outputs the latest contents of the associated
dictionary.
%
Our expectation is that this permissive approach allows to capture a large
subset of all possible DID method implementations. Note that the functional
restrictions we impose seem to be unavoidable. Namely, we do not specify how
the actual identifiers are computed; instead, we allow the adversary to pick
them. To update a DID, we only require such DID to exist, but otherwise its
contents can be set to something completely new, as long as the caller is the
same party who created it. Finally, deactivating labels within an existing DID
requires that these labels exist -- and, again, that the caller is the same
party who created the DID.
%
We capture this notion in \figref{fig:fpkidid}.

\begin{figure}
  \begin{framed}
    \begin{minipage}[t]{\textwidth}
      \textrm{Upon receiving command \cmd, for session \sid, with
        arguments \args and from party $P$, \IdealFPKIDID operats as
        follows.}
      \textrm{If the received \cmd and \args pair does not meet any of
        the following options, the request is ignored.}
      \textrm{\todo{We assume that the functionality keeps track of the
          received requests.}}
    \end{minipage}
    \vspace*{0.5em}

    \begin{minipage}[t]{0.55\textwidth}
      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \args =
        \lbrace (\lbl_i,\val_i) \rbrace_{i\in[n]}$}{
        \pccomment{\fbox{DID Create operation}} \\
        \ucio{Send}~(\uccmd{Create}, \sid, \args)~\text{to}~\adv \\
        \ucio{Receive}~(\uccmd{ok}, did)~\text{from}~\adv \\
        \pcif \sid = (P,\ssid): \\
        \pcind \DID \gets \DID \cup \lbrace (P,did,\args) \rbrace  
      }
    \end{minipage}
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
        \args = did$}{
        \pccomment{\fbox{DID Read operation}} \\
        \ucio{Send}~(\uccmd{Read},\sid,\args)~\text{to}~\adv \\
        \ucio{Receive}~\uccmd{ok}~\text{from}~\adv \\
        \pcif (\cdot,did,v) \in \DID: \\
        \pcind \ucio{Output}~(\uccmd{Read},\sid,(did,v))~\text{to}~P \\
        \pcelse: \\
        \pcind \ucio{Output}~(\uccmd{Read},\sid,\bot)~\text{to}~P    
      }    
    \end{minipage}
    \vspace*{0.25em} \\
    \begin{minipage}[t]{0.55\textwidth}
      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
        \args = (did, \lbrace (\lbl_i,\val_i) \rbrace_{i\in[n]})$}{      
        \pccomment{\fbox{DID Update operation}} \\
        \ucio{Send}~(\uccmd{Update}, \sid, \args)~\text{to}~\adv \\
        \ucio{Receive}~\uccmd{ok}~\text{from}~\adv \\
        \pcif \sid = (P,\ssid) \land (P,did,v) \in \DID: \\
        \pcind \DID \gets \DID \setminus \lbrace (P,did,v) \rbrace~\cup \\
        \hspace*{7em} \lbrace (P, did, v \cup \args) \rbrace
      }
    \end{minipage}
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \args =
        (did, \lbrace \lbl_i \rbrace_{i\in[n]})$}{
        \pccomment{\fbox{DID Deactivate operation}} \\
        \ucio{Send}~(\uccmd{Deact}, \sid, \args)~\text{to}~\adv \\
        \ucio{Receive}~\uccmd{ok}~\text{from}~\adv \\
        \pcif \sid = (P,\ssid)~\land \\
        \pcind (P,did,v) \in \DID~\land \\
        \pcind \lbrace \lbl_i \rbrace_{i\in[n]} \subseteq \LBL(v): \\
        \pcind v' \gets v \setminus \lbrace (\lbl_i,\cdot) \rbrace_{i\in[n]} \\
        \pcind \DID \gets \DID \setminus \lbrace (P,did,v) \rbrace~\cup \\
        \hspace*{7em}\lbrace (P,did,v') \rbrace
      }
    \end{minipage}
  \end{framed}
  \caption{Ideal DID-based PKI functionality, \IdealFPKIDID.}
  \label{fig:fpkidid}
\end{figure}

\subsubsection{Design choices.} %

\begin{itemize}
\item Add $did$s explicitly. Seems necessary to support multiple DIDs per party?
\end{itemize}
\subsection{\RealPKIDIDAtala Construction}

\subsubsection{Key Types.} %
All operations in Atala PRISM are authenticated, meaning that a cryptographic
key needs to be involved in proving that the operation comes from the intended
party. Currently, 4 types of keys are supported: master keys, for managing DIDs;
issuing keys, for issuing VCs; communication keys, for key-exchange protocols;
and authentication keys, to associate to VCs. For now, for simplicity we leave
communications keys out, and treat master keys, issuing keys and authentication
keys as digital signature key pairs -- \todo{note that extending the protocols
  described next to support key-exchange keys, is direct}.

The public part of each key, as well as some metadata (key identifier, key type,
etc.) is associated to a DID, where multiple keys can be related to the same
DID. Next, we describe how Atala PRISM implements the DID operations (create,
read, update and deactivate/delete) required to be a valid DID method.

\subsection{DID Management}

\todo{For now, this ignores \emph{unpublished} DIDs.}

We next describe the main operations with DIDs in Atala PRISM.

\subsubsection{Create a DID.} %
To create a DID, the user has to specify the number of master keys, issuing
and authentication keys ($n_m,n_i,n_a$) she wants to create, where at least one
master key is required. The process genereates as many keys as required. Then,
a list of the keys, along with their identifiers and type, is created and
used to form a transaction, signed by one of the master keys and submitted
to the blockchain. Let (an encoding of) the hash of such list of keys be $h$.
Then, the produced DID is ``did:prism:h''. We capture this algorithm more
precisely in \figref{fig:cudid}. Therein, for simplicity, we assume that
(w.l.o.g.) the master key that signs the transaction is the first one, and
all the keys to generate are ordered so that the type of key can be inferred
from its position -- this means that keys' identifiers are just counters of
each type (in any case, whatever the implementation is, this need to be done
unambiguosly).

\begin{figure}
  \begin{pchstack}[center, boxed, space=5mm]
    \procedure[linenumbering]{$\DIDCreate(n_m,n_i,n_a)$}{
      \pcif n_m < 1: \pcreturn \bot \\
      \pcfor j \in [n_m]: (\mpk_j,\msk_j) \gets \Sig.\Gen(\secpar) \\
      \pcfor j \in [n_i]: (\ipk_j,\isk_j) \gets \Sig.\Gen(\secpar) \\
      \pcfor j \in [n_a]: (\apk_j,\ask_j) \gets \Sig.\Gen(\secpar) \\
      \st \gets n_m||\lbrace (i,\mpk_i) \rbrace_{i\in[n_m]}|| \\
      \hspace*{2.25em} n_i||\lbrace(n_m+j,\ipk_j)\rbrace_{j\in[n_i]}|| \\
      \hspace*{2.25em} n_a||\lbrace(n_m+n_i+j,\apk_j)\rbrace_{j\in[n_a]}) \\
      h \gets \Hash(\st); \did \gets ``did:prism:''||~h \\
      \tx \gets \texttt{CreateDID} || \did || \st \\
      \sig_{\tx} \gets \Sig.Sign(\msk_1,\tx) \\
      \VDR.Push(\tx,\sig_{\tx}) \\
      \pcreturn (\did,\lbrace (\mpk_j,\msk_j) \rbrace_{j\in[n_m]}, \\
      \hspace*{5.5em}\lbrace (\ipk_j,\isk_j) \rbrace_{j\in[n_i]}, \\
      \hspace*{5.5em}\lbrace (\apk_j,\ask_j) \rbrace_{j\in[n_a]})
    }

    \procedure[linenumbering]{$\DIDUpdate(\did,M,I,A,n'_m,n'_I,n'_A)$}{
      \pcif M \not\subseteq [N_m] \lor I \not\subseteq [n_i] \lor
      A \not\subseteq [N_a]: \\
      \pcind \pcreturn \bot \\
      \pcif M = [N_m] \land n'_m < 1: \pcreturn \bot \\
      N \gets |M| + |I| + |A| \\
      \pcfor j \in [n'_m]: (\mpk_j,\msk_j) \gets \Sig.\Gen(\secpar) \\
      \pcfor j \in [n'_i]: (\ipk_j,\isk_j) \gets \Sig.\Gen(\secpar) \\
      \pcfor j \in [n'_a]: (\apk_j,\ask_j) \gets \Sig.\Gen(\secpar) \\
      \st \gets M||I||A||n'_m||\lbrace (N+i,\mpk_i) \rbrace_{i\in[n'_m]}|| \\
      \hspace*{2.25em} n'_i||\lbrace(N+n'_m+j,\ipk_j)\rbrace_{j\in[n'_i]}|| \\
      \hspace*{2.25em} n'_a||\lbrace(N+n'_m+n'_i+j,\apk_j)\rbrace_{j\in[n'_a]}) \\
      \tx \gets \texttt{UpdateDID} || \did || \st \\
      \sig_{\tx} \gets \Sig.Sign(\overline{\msk},\tx) \\
      \VDR.Push(\tx,\sig_{\tx}) \\
      \pcreturn (\lbrace (\mpk_j,\msk_j) \rbrace_{j\in[n'_m]}, \\
      \hspace*{4em}\lbrace (\ipk_j,\isk_j) \rbrace_{j\in[n'_i]}, \\
      \hspace*{4em}\lbrace (\apk_j,\ask_j) \rbrace_{j\in[n'_a]})
    }  
  \end{pchstack}
  \label{fig:cudid}
  \caption{Algorithms for creating and updating a DID.}
\end{figure}

\subsubsection{Read a DID.} \todo{PRISM nodes keep track of metadata?}

\subsubsection{Update a DID.} %
To update a DID, the alleged owner of the DID must specify the identifiers of
the keys she wants to deactivate, and the number of keys of each type she wants
to add. At least one master key (either new or old) must remain after this
operation. Otherwise, the logic is as in the DID creation process, and it is
specified in \figref{fig:cudid}. Therein, for readability we introduce the
variables $N_m,N_i,N_a$, that keep track of (respectively) the number of master,
issuing and authentication keys issued for the corresponding DID during its
whole lifetime. Similarly, $\overline{MSK}$ denotes the master secret key with
the lower index that has not been deactivated.

\subsubsection{Deactivate a DID.} %
The DID deactivation operation is implicitly implemented via the update
operation. \todo{Confirm.}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "prism-protocol"
%%% End:

### 2022-11-03 prism-backend/research/prism-protocol/preliminaries.tex
First reasonable ideal functionality of a DID-based PKI.

\section{Preliminaries}
\label{sec:preliminaries}

\subsection{Cryptographic Building Blocks}
\label{ssec:bbs}

\todo{Briefly describe algorithms they use.}

\paragraph{Append-Only Bulletin Boards.} %
%\todo{For now, simplified notion as in \cite{acc+20}.}

\paragraph{Digital Signatures.} %
%Maybe build on \IdealFSig from \cite{canetti03}.

\paragraph{Merkle Trees.}

\paragraph{Public Key Infrastructures.} %
% Maybe build on \IdealFCA from \cite{canetti03}.

\subsection{Self-Sovereign Identities}
\label{ssec:ssi}

\paragraph{Decentralised Identifiers (DIDs).} %
Much of the SSI community is built on top of DIDs, which is a W3C Recommendation
since 2022\footnote{\url{https://www.w3.org/TR/did-core}. Last access, 3rd
  November, 2022.}. Essentially, the DID specification defines how to associate
public keys and additional metadata to unique identifiers, leveraging verifiable
data registries (VDR). Whereas there is no concrete requirement on these VDRs,
the typical choice are blockchains, which leads to the ``Decentralised''
adjective for DIDs. The DID specification describes the syntax that identifiers
must follow, as well as the operations (CRUD: Create, Read, Update, Deactivate)
that any DID-compatible mechanism must implement.

That is, a mechanism following the DID specification must enable any user to be
able to register a unique identifier, associate public key material to it, and
manange it. Thus, it is natural to see such a mechamism as an equivalent to
traditional Public Key Infrastructures (PKIs), where different instantiations of
such a mechanism -- e.g., with different approaches to implement the CRUD
methods required by the DID specification, or based on different VDRs -- can be
seen as a different type of DID-based PKI.

\todo{Maybe expand. Also, describe the difference between DID Document, and DID.
  Also describe the concept of DID controller, essential to prevent manipulation
  of DIDs and their documents.}

\paragraph{Verifiable Credentials (VCs).} %
\todo{Describe: Introduction to VCs. Relating to DIDs.}

\subsection{Overview of Atala PRISM}
\label{ssec:overview-prism}

In a nutshell, Atala PRISM builds VCs and DIDs on top of the Cardano blockchain.
More concretely, any entity can create (and manage) a DID, and issuers can issue
VCs associated to a previously existing DID, where Cardano is the chosen VDR.
Users can later leverage VCs to authenticate against any potential verifier, in
a manner that all the information that the verifier needs to (cryptographically)
authenticate the user is contained in the Cardano blockchain.

\todo{Ellaborate more.}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "prism-protocol"
%%% End:

### 2022-11-03 prism-backend/research/prism-protocol/vc_atala.tex
First reasonable ideal functionality of a DID-based PKI.

\section{VCs in Atala PRISM}
\label{sec:vc-atala}

In Atala PRISM, VCs are associated to a DID, with no limit on the number of VCs
per DID. VCs (or just, credentials) can be issued, revoked, and presented --
where a presentation involves both proving and verifying steps.

\subsubsection{VC structure.}
A VC contains at least the DID and issuing key index of the issuer, the DID and
authentication key index of the holder, and a dictionary with further identity
claims (name, nationality, etc.) This data is then signed by the issuing key.
A credential presentation requires the holder to prove control over the
specified authentication key. Issuers are trusted to verify the identity
claims contained in credentials they issue.

\subsubsection{Issuing VCs.}
Issuing a VC involves creating and signing the corresponding data structure, and
publishing it in the blockchain. In Atala PRISM, the publication can be done in
batches, so in the following we treat all publication events as containing a
batch of VCs (of size at least $1$).

The protocol for creating a single VC is as defined in \figref{fig:issuevc}.
Therein, we only describe how the prospective VC holder proves to the issuer
ownership of the DID to be included in the VC. Indeed, this is the only
claim whose correctness can be proved cryptographically; whereas for the other
claims we need to trust the issuer. \figref{fig:issuevc} further captures how
the issuer batches multiple VCs and publishes them in the blockchain.

\begin{figure}
  \scalebox{0.8}{
    \procedure{\VCCreate}{%
      \text{$\mathbf{Holder}(\did_H,\did_I,\ask)$} \> \>
      \text{$\mathbf{Issuer}(\did_I,\isk)$} \> \> \textbf{VDR} \\
      \> \sendmessageright{top=\text{$\did_H$,attrs}} \> \> \> \\
      \> \> \> \sendmessageright{top=$\DID.Read(\did_H)$} \> \\
      \> \> \> \sendmessageleft{top=\apk} \> \\
      \> \> r \getr \ZZ \> \> \\
      \> \sendmessageleft{top=$r$} \> \> \> \\
      \sig \gets \Sig.Sign(\ask,r) \> \> \> \> \\
      \> \sendmessageright{top=\sig} \> \> \> \\
      \> \> \pcif !\Sig.Verify(\apk,\sig,r): \> \> \\
      \> \> \pcind \pcreturn \bot \> \> \\
      \> \> c \gets (\ipk,\apk,attrs) \> \> \\ 
      \> \> vc \gets \Sig.Sign(\isk,c) \> \> \\
      \> \sendmessageleft{top=\text{$(c,vc)$}} \> \> \> \\  
      \pcif !\Sig.Verify(\ipk,vc,c): \> \> \> \> \\
      \pcind \pcreturn \bot \> \> \> \> \\
    }
  }
  \label{fig:issuevc}
  \caption{Algorithms for issuing (creating and publishing) a VC.}
\end{figure}

\subsubsection{Revoking a VC.}

\subsubsection{VC Presentations.}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "prism-protocol"
%%% End:

### 2022-11-06 prism-backend/research/prism-protocol/did_atala.tex
Updates to the construction.

@@
 \label{sec:did-atala}
+
+In this section we first give an ideal functionality for Public-Key
+Infrastructures built atop of DIDs \IdealFPKIDID, and subsequently describe
+Atala PRISM DID method \RealPKIDIDAtala, which is a protocol realizing
+\IdealFPKIDID.
+%
+Before doing so, we introduce some base ideal functionalities upon which we
+rely for \RealPKIDIDAtala. Namely, a simplified notion of append-only bulletin
+boards, and digital signatures.
 
@@
 \paragraph{Append-Only Bulletin Boards.} %
-\todo{For now, simplified notion as in \cite{acc+20}.}
+We adopt a simplified notion of append-only bulletin boards, given in
+\cite{acc+20}. This is a local functionality, that defines an (probably too)
+idealized version of a bulletin board, where no delays in the operations
+occur \todo{We probably want to improve this to use a UC version that
+  supports global functionalities}. For the sake of readability, we reproduce
+the functionality in \figref{fig:faobb}.
+
+\begin{figure}
+  \begin{framed}
+    \begin{minipage}[t]{\textwidth}
+      \textrm{Upon receiving a call $\IdealFaobb(\cmd,\arg)$ from
+        some party $P$ to run command \cmd, with arguments \arg,
+        \IdealFaobb operates as follows.}
+      \textrm{\IdealFaobb maintains a list \aobbl of bit strings.}      
+    \end{minipage}
+    \vspace*{0.5em}
+
+    \begin{minipage}[t]{0.55\textwidth}
+      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Append} \land \arg = x$}{
+        \pccomment{\fbox{Append data to \aobbl}} \\
+        \aobbl \gets \aobbl || x \\
+        \pcif P~\text{is corrupt}:~\ucio{Send}~(\uccmd{Appended},x,P)~\text{to}
+        ~\adv
+      }
+    \end{minipage}
+    \hspace*{1.25em}
+    \begin{minipage}[t]{0.45\textwidth}
+      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Retrieve} \land \arg =
+        \emptyset$}{
+        \pccomment{\fbox{Retrieve the contents of \aobbl}} \\
+        \text{Output}~(\uccmd{Retrieved},\aobbl)~\text{to}~P
+      }
+    \end{minipage}
+  \end{framed}
+  \caption{Ideal append-only bulletin board functionality, \IdealFaobb, from
+    \cite{acc+20}.}
+  \label{fig:faobb}
+\end{figure}
+
+\paragraph{Hashes.} %
+\todo{\IdealFRO.}
 
 \paragraph{Digital Signatures.} %
-Maybe build on \IdealFSig from \cite{canetti03}.
+
+\begin{figure}
+  \begin{framed}
+    \begin{minipage}[t]{\textwidth}
+      \textrm{Upon receiving a call $\IdealFSig(\cmd,\sid,\arg)$ from some party
+        $P$ to run command \cmd, in session \sid, with arguments \arg,
+        \IdealFSig operates as follows.} \\
+      \textrm{\IdealFSig keeps a list \SIG of known signed messages.}      
+    \end{minipage}
+    \vspace*{0.5em}
+
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure[linenumbering]{$\pcif \cmd = \uccmd{KeyGen} \land \arg =
+        \emptyset$}{
+        \pccomment{\fbox{Key Generation}} \\
+        \pcif \sid = (P,\ssid): \\
+        \pcind \ucio{Send}~(\uccmd{KeyGen},\sid)~\text{to}~\adv \\
+        \pcind \ucio{Receive}~(\uccmd{VerKey},\sid,v)~\text{from}~\adv \\
+        \pcind \ucio{Output}~(\uccmd{VerKey},\sid,v)~\text{to}~P \\
+        \pcind \text{Store}~(P,v)
+      }
+      \vspace*{0.25em}
+      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Verify} \land
+        \arg = (\sig,\msg,v')$}{
+        \pccomment{\fbox{Verify a message}} \\
+        \ucio{Send}~(\uccmd{Verify},\sid,\msg,\sig,v)~\text{to}~\adv \\
+        \ucio{Receive}~(\uccmd{Verified},\sid,\msg,\phi)~\text{from}~\adv \\
+        \pcif v' = v \land (\msg,\sig,v,1) \in \SIG: f \gets 1 \\
+        \pcelse \pcif v' = v \land P~\text{is not corrupt}~\land \\
+        \pcind (\msg,\sig',v,1) \notin \SIG: \\
+        \pcind \SIG \gets \SIG \cup \lbrace (\msg,\sig,v,0) \rbrace;
+        f \gets 0 \\
+        \pcelse \pcif (\msg,\sig,v',f') \in \SIG: f \gets f' \\
+        \pcelse: \\
+        \pcind \SIG \gets \SIG \cup \lbrace (\msg,\sig,v',\phi) \rbrace;~
+        f \gets \phi \\
+        \ucio{Output}~(\uccmd{Verified},\sid,\msg,f)
+      }
+    \end{minipage}
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Sign} \land \arg = \msg$}{
+        \pccomment{\fbox{Sign a message}} \\
+        \pcif \sid = (P,\ssid) \\
+        \pcind \ucio{Send}~(\uccmd{Sign},\sid,\msg)~\text{to}~\adv \\
+        \pcind \ucio{Receive}~(\uccmd{Signature},\sid,\msg,\sig)~\text{from}~
+        \adv \\
+        \pcind \pcif (\msg,\sig,v,0) \in \SIG: \\
+        \pcind \pcind \ucio{Output}~(\uccmd{Error}) \\
+        \pcind \pcelse: \\
+        \pcind \pcind \SIG \gets \SIG \cup (\msg,\sig,v,1) \\
+        \pcind \pcind \ucio{Output}~(\uccmd{Signature},\sid,\msg,\sig)
+      }
+    \end{minipage}
+  \end{framed}
+  \caption{Ideal signature functionality, \IdealFSig, from \cite{canetti03}.}
+  \label{fig:faobb}
+\end{figure}
 
@@
 (i.e., lists of labels with corresponding values), associated to a common label,
-the DID \todo{maybe draw something here}. From this, creating a DID is simply
-defining a set (of at least size 1) of initial label-value pairs and get an
-identifier associated to them. Updating a DID is essentially a creation, but
-over an existing identifier - the functionality just replaces the old contents
-with the new ones. And deactivating a DID means removing some of its labels and
-associated values, where removing all of them equates to deactivating the whole
-DID. Reading a DID just outputs the latest contents of the associated
-dictionary.
+the DID. From this, creating a DID is simply defining a set (of at least size 1)
+of initial label-value pairs and get an identifier associated to them. Updating
+a DID is essentially a creation, but over an existing identifier - the
+functionality just replaces the old contents with the new ones, where of course
+both sets don't need to be disjoint. And deactivating a DID means removing some
+of its labels and associated values, where removing all of them equates to
+deactivating the whole DID. Reading a DID just outputs the latest contents of
+the associated dictionary.
 %
@@
 requires that these labels exist -- and, again, that the caller is the same
-party who created the DID.
+party who created the DID. Concretely, note that any further structure beyond
+the label-value dictionary approach, is left as an implementation detail.
 %
-We capture this notion in \figref{fig:fpkidid}.
+Note that we also allow the adversary to pick the values associated to the
+labels in new and updated DIDs. This is a strong requirement that follows the
+argumentation in \cite{canetti03} for ideal digital signatures: namely, this
+means that there is absolutely any requirement on the way in which this values
+are computed (they might not even be conventional public keys). Indeed, this
+seems to match the permissive philosophy of defining DIDs in the W3C DID
+specification.
+%
+\todo{Introduce \P, and re-write this in a more structured manner.}
+%
+We capture the resulting notion in \figref{fig:fpkidid}.
 
@@
     \begin{minipage}[t]{\textwidth}
-      \textrm{Upon receiving command \cmd, for session \sid, with
-        arguments \args and from party $P$, \IdealFPKIDID operats as
-        follows.}
-      \textrm{If the received \cmd and \args pair does not meet any of
+      \textrm{Upon receiving a call $\IdealFPKIDID^{\P}(\cmd,\sid,\arg)$
+        from some party $P$ to run command \cmd, in session \sid, with arguments
+        \arg, $\IdealFPKIDID^{\P}$ operates as follows.}
+      \textrm{If the received \cmd and \arg pair does not meet any of
         the following options, the request is ignored.}
+      \textrm{\P is a boolean predicate defining concrete conditions for
+        acceptable DID creations, updates and deactivations.
+      }
       \textrm{\todo{We assume that the functionality keeps track of the
@@
     \begin{minipage}[t]{0.55\textwidth}
-      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \args =
-        \lbrace (\lbl_i,\val_i) \rbrace_{i\in[n]}$}{
+      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \arg =
+        \lbrace (i,\lbl_i) \rbrace_{i\in[n]}$}{
         \pccomment{\fbox{DID Create operation}} \\
-        \ucio{Send}~(\uccmd{Create}, \sid, \args)~\text{to}~\adv \\
-        \ucio{Receive}~(\uccmd{ok}, did)~\text{from}~\adv \\
-        \pcif \sid = (P,\ssid): \\
-        \pcind \DID \gets \DID \cup \lbrace (P,did,\args) \rbrace  
+        \ucio{Send}~(\uccmd{Create}, \sid, \arg)~\text{to}~\adv \\
+        \ucio{Receive}~(\uccmd{CreateOk}, \sid, did,
+        \lbrace \val_i \rbrace_{i\in[n]}) \\
+        \pcind \text{from}~\adv \\
+        \pcif (P,\did,\cdot) \notin \DID \land
+        \P(\lbrace \lbl_i \rbrace_{i\in[n]}) = 1: \\
+        \pcind \DID \gets \DID \cup \lbrace (P,did,\lbrace
+        (\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
+        \ucio{Output}~(\uccmd{Created},\sid,\did,
+        \lbrace \val_i \rbrace_{i\in[n]})
       }
@@
       \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
-        \args = did$}{
+        \arg = did$}{
         \pccomment{\fbox{DID Read operation}} \\
-        \ucio{Send}~(\uccmd{Read},\sid,\args)~\text{to}~\adv \\
-        \ucio{Receive}~\uccmd{ok}~\text{from}~\adv \\
-        \pcif (\cdot,did,v) \in \DID: \\
-        \pcind \ucio{Output}~(\uccmd{Read},\sid,(did,v))~\text{to}~P \\
+        \ucio{Send}~(\uccmd{Read},\sid,\arg)~\text{to}~\adv \\
+        \ucio{Receive}~(\uccmd{ReadOk},\sid)~\text{from}~\adv \\
+        \pcif (\cdot,did,\sval) \in \DID: \\
+        \pcind \ucio{Output}~(\uccmd{Read},\sid,(did,\sval))~\text{to}~P \\
         \pcelse: \\
@@
       \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
-        \args = (did, \lbrace (\lbl_i,\val_i) \rbrace_{i\in[n]})$}{      
+        \arg = (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{      
         \pccomment{\fbox{DID Update operation}} \\
-        \ucio{Send}~(\uccmd{Update}, \sid, \args)~\text{to}~\adv \\
-        \ucio{Receive}~\uccmd{ok}~\text{from}~\adv \\
-        \pcif \sid = (P,\ssid) \land (P,did,v) \in \DID: \\
-        \pcind \DID \gets \DID \setminus \lbrace (P,did,v) \rbrace~\cup \\
-        \hspace*{7em} \lbrace (P, did, v \cup \args) \rbrace
+        \ucio{Send}~(\uccmd{Update}, \sid, \arg)~\text{to}~\adv \\
+        \ucio{Receive}~(\uccmd{UpdateOk},\sid,
+        \lbrace \val_i \rbrace_{i\in[n]}) \\
+        \pcind \text{from}~\adv \\
+        \pcif (P,did,\sval) \in \DID \land
+        \P(\lbrace \lbl_i \rbrace_{i\in[n]}) = 1: \\
+        \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
+        \hspace*{7em} \lbrace (P, did,
+        \lbrace \lbl_i,\val_i \rbrace_{i\in[n]}) \rbrace
       }
@@
     \begin{minipage}[t]{0.5\textwidth}
-      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \args =
-        (did, \lbrace \lbl_i \rbrace_{i\in[n]})$}{
+      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \arg =
+        (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{
         \pccomment{\fbox{DID Deactivate operation}} \\
-        \ucio{Send}~(\uccmd{Deact}, \sid, \args)~\text{to}~\adv \\
-        \ucio{Receive}~\uccmd{ok}~\text{from}~\adv \\
-        \pcif \sid = (P,\ssid)~\land \\
-        \pcind (P,did,v) \in \DID~\land \\
-        \pcind \lbrace \lbl_i \rbrace_{i\in[n]} \subseteq \LBL(v): \\
-        \pcind v' \gets v \setminus \lbrace (\lbl_i,\cdot) \rbrace_{i\in[n]} \\
-        \pcind \DID \gets \DID \setminus \lbrace (P,did,v) \rbrace~\cup \\
-        \hspace*{7em}\lbrace (P,did,v') \rbrace
+        \ucio{Send}~(\uccmd{Deact}, \sid, \arg)~\text{to}~\adv \\
+        \ucio{Receive}~(\uccmd{DeactOk},\sid)~\text{from}~\adv \\
+        \pcif (P,did,\sval) \in \DID~\land \\
+        \pcind \lbrace \lbl_i \rbrace_{i\in[n]} \subseteq \LBL(\sval): \\
+        \pcind \sval' \gets \sval \setminus \lbrace (\lbl_i,\cdot)
+        \rbrace_{i\in[n]} \\
+        \pcind \pcif \P(\sval') = 1: \\
+        \pcind \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
+        \hspace*{8em}\lbrace (P,did,\sval') \rbrace
       }
@@
 
-\subsubsection{Design choices.} %
+\subsection{The \RealPKIDIDAtala Construction}
 
-\begin{itemize}
-\item Add $did$s explicitly. Seems necessary to support multiple DIDs per party?
-\end{itemize}
-\subsection{\RealPKIDIDAtala Construction}
+We next define the Atala PRISM DID method, following the interfaces defined for
+\IdealFPKIDID. We begin by describing the types of keys supported in Atala
+PRISM, and then specify how sets of such keys can be managed through DIDs in
+Atala.
 
-\subsubsection{Key Types.} %
+\paragraph{Key Types.} %
 All operations in Atala PRISM are authenticated, meaning that a cryptographic
 key needs to be involved in proving that the operation comes from the intended
-party. Currently, 4 types of keys are supported: master keys, for managing DIDs;
-issuing keys, for issuing VCs; communication keys, for key-exchange protocols;
-and authentication keys, to associate to VCs. For now, for simplicity we leave
-communications keys out, and treat master keys, issuing keys and authentication
-keys as digital signature key pairs -- \todo{note that extending the protocols
-  described next to support key-exchange keys, is direct}.
+party. Currently, 4 types of keys are supported: master keys (\MasterKey), for
+operating on DIDs; issuing keys, for issuing VCs (\IssueKey); communication
+keys (\CommKey), for key-exchange protocols; and authentication keys, to
+associate to VCs (\AuthKey).
 
-The public part of each key, as well as some metadata (key identifier, key type,
-etc.) is associated to a DID, where multiple keys can be related to the same
-DID. Next, we describe how Atala PRISM implements the DID operations (create,
-read, update and deactivate/delete) required to be a valid DID method.
+\paragraph{DID Operations.} %
+\todo{For now, this ignores \emph{unpublished} DIDs.}
+\figref{fig:alapkidid} contains the specification of Atala PRISM's DID method,
+which we describe next.
 
-\subsection{DID Management}
-
-\todo{For now, this ignores \emph{unpublished} DIDs.}
-
-We next describe the main operations with DIDs in Atala PRISM.
-
-\subsubsection{Create a DID.} %
-To create a DID, the user has to specify the number of master keys, issuing
-and authentication keys ($n_m,n_i,n_a$) she wants to create, where at least one
-master key is required. The process genereates as many keys as required. Then,
-a list of the keys, along with their identifiers and type, is created and
-used to form a transaction, signed by one of the master keys and submitted
-to the blockchain. Let (an encoding of) the hash of such list of keys be $h$.
-Then, the produced DID is ``did:prism:h''. We capture this algorithm more
-precisely in \figref{fig:cudid}. Therein, for simplicity, we assume that
-(w.l.o.g.) the master key that signs the transaction is the first one, and
-all the keys to generate are ordered so that the type of key can be inferred
-from its position -- this means that keys' identifiers are just counters of
-each type (in any case, whatever the implementation is, this need to be done
-unambiguosly).
+\begin{description}
+\item{\uccmd{Create}.} %
+  To create a DID, the user has to specify the key pairs to create, along with
+  fresh identifiers and their type. For ease of exposition, we assume that the
+  used identifiers just follow a sequence. The predicate \P in Atala simply
+  requires that at least one key pair of \MasterKey type is created. The
+  \uccmd{Create} algorithm creates as many keys of each type as requested,
+  and keeps a list with the identifier, type and public key of each key pair.
+  This list is then hashed into a value \texttt{h}, and the created DID is
+  ``\texttt{\did:prism:h}''. A transaction containing the created list, the
+  DID, and the \texttt{CreateDID} instruction is sent to the blockchain,
+  signed by one of the master keys -- w.l.o.g., we simply use the first one
+  in the list. The DID owner stores locally the list, along with the
+  corresponding private keys.
+\item[\uccmd{Read}.] %
+  Getting the contents of a DID simply requires querying a \todo{PRISM node} for
+  it. The PRISM node returns the associated list, along with all related
+  \texttt{CreateDID} and \texttt{UpdateDID} transactions in the blockchain. If
+  the signatures of these transactions are valid, and the result of applying in
+  order all the operations produces the list returned by the \todo{PRISM node},
+  then the list is an up to date DID Document of the corresponding DID.
+\item[\uccmd{Update}.] %
+  Updating a DID requires to (optionally) specify a list of previously existing
+  key identifiers to remove, and (optionally) specify a list of new key
+  identifiers, and their types, to add. To simplify notation, we just adopt the
+  (equivalent) convention that the caller indicates a list of $(i,\lbl_i)$
+  pairs, which is interpreted as follows. If $i$ is an already existing
+  identifier, the label is ignored and the corresponding key is not removed. If
+  $i$ is a new identifier, then a new key pair of the given type is created.
+  Omitting an existing identifier is then interpreted as the desire to remove
+  the corresponding key pair. Otherwise, the same policy as for \uccmd{Create}
+  applies here. Key pairs for the new keys are generated, and a transaction is
+  sent to the blockchain, signed with one of the master keys in the DID
+  \emph{before applying the update}. This transaction contains a list of the
+  identifiers of the keys to remove, and a list of the identifiers and types
+  of the keys to add.
+\item[\uccmd{Deactivate}.] %
+  A deactivate operation is simply an update operation with no new key
+  identifiers, and that only specifies the existing identifiers that will
+  \emph{not} be deactivated.
+\end{description}
 
 \begin{figure}
-  \begin{pchstack}[center, boxed, space=5mm]
-    \procedure[linenumbering]{$\DIDCreate(n_m,n_i,n_a)$}{
-      \pcif n_m < 1: \pcreturn \bot \\
-      \pcfor j \in [n_m]: (\mpk_j,\msk_j) \gets \Sig.\Gen(\secpar) \\
-      \pcfor j \in [n_i]: (\ipk_j,\isk_j) \gets \Sig.\Gen(\secpar) \\
-      \pcfor j \in [n_a]: (\apk_j,\ask_j) \gets \Sig.\Gen(\secpar) \\
-      \st \gets n_m||\lbrace (i,\mpk_i) \rbrace_{i\in[n_m]}|| \\
-      \hspace*{2.25em} n_i||\lbrace(n_m+j,\ipk_j)\rbrace_{j\in[n_i]}|| \\
-      \hspace*{2.25em} n_a||\lbrace(n_m+n_i+j,\apk_j)\rbrace_{j\in[n_a]}) \\
-      h \gets \Hash(\st); \did \gets ``did:prism:''||~h \\
-      \tx \gets \texttt{CreateDID} || \did || \st \\
-      \sig_{\tx} \gets \Sig.Sign(\msk_1,\tx) \\
-      \VDR.Push(\tx,\sig_{\tx}) \\
-      \pcreturn (\did,\lbrace (\mpk_j,\msk_j) \rbrace_{j\in[n_m]}, \\
-      \hspace*{5.5em}\lbrace (\ipk_j,\isk_j) \rbrace_{j\in[n_i]}, \\
-      \hspace*{5.5em}\lbrace (\apk_j,\ask_j) \rbrace_{j\in[n_a]})
+  \begin{framed}
+    \begin{minipage}[t]{\textwidth}
+      \textrm{Upon receiving a call $\IdealFPKIDID^{\P}(\cmd,\sid,\arg)$
+        from some party $P$ to run command \cmd, in session \sid, with arguments
+        \arg, $\IdealFPKIDID^{\P}$ operates as follows.}
+      \textrm{If the received \cmd and \arg pair does not meet any of
+        the following options, the request is ignored.}
+      \textrm{\P is a boolean predicate defining concrete conditions for
+        acceptable DID creations, updates and deactivations.
       }
+      \textrm{\todo{We assume that the functionality keeps track of the
+          received requests.}}
+    \end{minipage}
+    \vspace*{0.5em}
 
-    \procedure[linenumbering]{$\DIDUpdate(\did,M,I,A,n'_m,n'_I,n'_A)$}{
-      \pcif M \not\subseteq [N_m] \lor I \not\subseteq [n_i] \lor
-      A \not\subseteq [N_a]: \\
-      \pcind \pcreturn \bot \\
-      \pcif M = [N_m] \land n'_m < 1: \pcreturn \bot \\
-      N \gets |M| + |I| + |A| \\
-      \pcfor j \in [n'_m]: (\mpk_j,\msk_j) \gets \Sig.\Gen(\secpar) \\
-      \pcfor j \in [n'_i]: (\ipk_j,\isk_j) \gets \Sig.\Gen(\secpar) \\
-      \pcfor j \in [n'_a]: (\apk_j,\ask_j) \gets \Sig.\Gen(\secpar) \\
-      \st \gets M||I||A||n'_m||\lbrace (N+i,\mpk_i) \rbrace_{i\in[n'_m]}|| \\
-      \hspace*{2.25em} n'_i||\lbrace(N+n'_m+j,\ipk_j)\rbrace_{j\in[n'_i]}|| \\
-      \hspace*{2.25em} n'_a||\lbrace(N+n'_m+n'_i+j,\apk_j)\rbrace_{j\in[n'_a]}) \\
-      \tx \gets \texttt{UpdateDID} || \did || \st \\
-      \sig_{\tx} \gets \Sig.Sign(\overline{\msk},\tx) \\
-      \VDR.Push(\tx,\sig_{\tx}) \\
-      \pcreturn (\lbrace (\mpk_j,\msk_j) \rbrace_{j\in[n'_m]}, \\
-      \hspace*{4em}\lbrace (\ipk_j,\isk_j) \rbrace_{j\in[n'_i]}, \\
-      \hspace*{4em}\lbrace (\apk_j,\ask_j) \rbrace_{j\in[n'_a]})
+    \begin{minipage}[t]{0.55\textwidth}
+      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \arg =
+        \lbrace (i,\lbl_i) \rbrace_{i\in[n]}$}{
+        \pccomment{\fbox{DID Create operation}} \\
+        \st \gets \emptyset \\
+        \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
+        \CommKey,\IssueKey] \lor
+        \nexists i~\suchthat~\lbl_i = \MasterKey: \\
+        \pcind \texttt{Abort} \\
+        \pcfor i \in [n]: \\
+        \pcind \sid' \gets (P,\sid,i) \\
+        \pcind \ucio{Send}~(\uccmd{KeyGen},\sid')~\text{to}~\IdealFSig \\
+        \pcind \ucio{Receive}~(\uccmd{VerKey},\sid',\pk_i)~\text{from}~
+        \IdealFSig \\
+        \pcind \st \gets \st~||~(i,\lbl_i,\pk_i) \\
+        \ucio{Send}~(\uccmd{Hash},\st)~\text{to}~\IdealFRO \\
+        \ucio{Receive}~(\uccmd{Hashed},\st,h)~\text{from}~\IdealFRO \\
+        \did \gets ``did:prism:''||~h \\
+        \text{Locally store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]}) \\
+        \tx \gets (\texttt{CreateDID}, \did, \st) \\
+        \text{Let}~j\in[n]~\text{be the least value s.t.}~\lbl_j = \MasterKey \\
+        \ucio{Send}~(\uccmd{Sign},(P,\sid,j),\msg)~\text{to}~\IdealFSig \\
+        \ucio{Receive}~(\uccmd{Signature},(P,\sid,j),\msg,\sig)~\text{from}~\IdealFSig \\
+        \ucio{Send}~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
+        \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace \pk_i \rbrace_{i\in[n]})
       }
-  \end{pchstack}
-  \label{fig:cudid}
-  \caption{Algorithms for creating and updating a DID.}
+    \end{minipage}
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
+        \arg = did$}{
+        \pccomment{\fbox{DID Read operation}} \\  
+      }    
+    \end{minipage}
+    \vspace*{0.25em} \\
+    \begin{minipage}[t]{0.55\textwidth}
+      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
+        \arg = (did, \lbrace (i,\lbl_i) \rbrace_{i\in\tilde{N}\subseteq [\tilde{n}]})$}{
+        \pccomment{\fbox{DID Update operation}} \\
+        \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
+        \CommKey,\IssueKey] \lor
+        \nexists i~\suchthat~\lbl_i = \MasterKey: \\
+        \pcind \texttt{Abort} \\
+        \text{Read}~(\did,\lbrace (i,\l_i,\pk_i) \rbrace_{i\in[n]})~
+        \text{from local storage} \\
+        \st_{add} \gets \emptyset \\
+        \pcfor i > n \in [\tilde{N}]: \\
+        \pcind \ucio{Send}~(\uccmd{KeyGen},(P,\sid,i))~\text{to}~\IdealFSig \\
+        \pcind \ucio{Receive}~(\uccmd{VerKey},(P,\sid,i),\pk_i)~\text{from}~
+        \IdealFSig \\
+        \pcind \st_{add} \gets \st_{add}~||~(i,\lbl_i,\pk_i) \\
+        \st_{del} \gets [n] \setminus [\tilde{N}] \\
+        \text{Locally store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \\
+        \tx \gets \texttt{UpdateDID}~||~\did~||~\st_{del}~||~\st_{add} \\
+        \text{Let}~j\in[n]~\text{be the least value s.t.}~\lbl_j = \MasterKey \\
+        \ucio{Send}~(\uccmd{Sign},(P,\sid,j),\msg)~\text{to}~\IdealFSig \\
+        \ucio{Receive}~(\uccmd{Signature},(P,\sid,j),\msg,\sig)~\text{from}~\IdealFSig \\
+        \ucio{Send}~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
+        \ucio{Output}~(\uccmd{Updated},\sid,\did,\lbrace \pk_i \rbrace_{i\in[\tilde{N}]})
+      }
+    \end{minipage}
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \arg =
+        (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{
+        \pccomment{\fbox{DID Deactivate operation}} \\
+      }
+    \end{minipage}
+  \end{framed}
+  \caption{Atala PRISM DID-based PKI construction, \RealPKIDIDAtala.}
+  \label{fig:fpkidid}
 \end{figure}
+
+% \begin{figure}
+
+%   \begin{pchstack}[center, boxed, space=5mm]
+%     \procedure[linenumbering]{$\DIDCreate(\lbrace \lbl_i \rbrace_{i\in[n]})$}{
+%       \st \gets \emptyset \\
+%       \pcfor i \in [n]: \\
+%       \pcind \ucio{Send}~(\uccmd{KeyGen},(P,\sid,i))~\text{to}~\IdealFSig \\
+%       \pcind \ucio{Receive}~(\uccmd{VerKey},(P,\sid,i),\pk_i)~\text{from}~
+%       \IdealFSig \\
+%       \pcind \st \gets \st~||~(i,\lbl_i,\pk_i) \\
+%       \ucio{Send}~(\uccmd{Hash},\st)~\text{to}~\IdealFRO \\
+%       \ucio{Receive}~(\uccmd{Hashed},\st,h)~\text{from}~\IdealFRO \\
+%       \did \gets ``did:prism:''||~h \\
+%       \text{Store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]})~
+%       \text{in local storage} \\
+%       \tx \gets (\texttt{CreateDID}, \did, \st) \\
+%       \text{Let}~j\in[n]~\text{be the least value s.t.}~\lbl_j = \texttt{master} \\
+%       \pcif \text{no such $j$ exists}: \todo{abort} \\
+%       \ucio{Send}~(\uccmd{Sign},(P,\sid,j),\msg)~\text{to}~\IdealFSig \\
+%       \ucio{Receive}~(\uccmd{Signature},(P,\sid,j),\msg,\sig)~\text{from}~\IdealFSig \\
+%       \ucio{Send}~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
+%       \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace \pk_i \rbrace_{i\in[n]})
+%     }
+
+%     \procedure[linenumbering]
+%     {$\DIDUpdate(\did,\lbrace \tilde{\lbl}_i
+%       \rbrace_{i\ \in \tilde{N}\subseteq[\tilde{n}]})$}{
+%       \text{Read}~(\did,\lbrace (i,\l_i,\pk_i) \rbrace_{i\in[n]})~
+%       \text{from local storage} \\
+%       \st_{add} \gets \emptyset \\
+%       \pcfor i > n \in [\tilde{N}]: \\
+%       \pcind \ucio{Send}~(\uccmd{KeyGen},(P,\sid,i))~\text{to}~\IdealFSig \\
+%       \pcind \ucio{Receive}~(\uccmd{VerKey},(P,\sid,i),\pk_i)~\text{from}~
+%       \IdealFSig \\
+%       \pcind \st_{add} \gets \st_{add} || (i,\lbl_i,\pk_i) \\
+%       \st_{del} \gets [n] \setminus [\tilde{N}] \\
+%       \text{Store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]})~
+%       \text{in local storage} \\
+%       \tx \gets \texttt{UpdateDID} || \did || \st_{del} || \st_{add} \\
+%       \text{Let}~j\in[n]~\text{be the least value s.t.}~\lbl_j = \texttt{master} \\
+%       \ucio{Send}~(\uccmd{Sign},(P,\sid,j),\msg)~\text{to}~\IdealFSig \\
+%       \ucio{Receive}~(\uccmd{Signature},(P,\sid,j),\msg,\sig)~\text{from}~\IdealFSig \\
+%       \ucio{Send}~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
+%       \ucio{Output}~(\uccmd{Updated},\sid,\did,\lbrace \pk_i \rbrace_{i\in[\tilde{N}]})
+%     }  
+%   \end{pchstack}
+%   \label{fig:cudid}
+%   \caption{Algorithms for creating and updating a DID.}
+% \end{figure}
 

### 2022-11-07 prism-backend/research/prism-protocol/did_atala.tex
1st potential protocol for Atala DID.

@@
         \aobbl \gets \aobbl || x \\
-        \pcif P~\text{is corrupt}:~\ucio{Send}~(\uccmd{Appended},x,P)~\text{to}
+        \pcif P~\text{is corrupt}:~\ucsend~(\uccmd{Appended},x,P)~\text{to}
         ~\adv
@@
         \pcif \sid = (P,\ssid): \\
-        \pcind \ucio{Send}~(\uccmd{KeyGen},\sid)~\text{to}~\adv \\
-        \pcind \ucio{Receive}~(\uccmd{VerKey},\sid,v)~\text{from}~\adv \\
+        \pcind \ucsend~(\uccmd{KeyGen},\sid)~\text{to}~\adv \\
+        \pcind \ucrecv~(\uccmd{VerKey},\sid,v)~\text{from}~\adv \\
         \pcind \ucio{Output}~(\uccmd{VerKey},\sid,v)~\text{to}~P \\
@@
         \pccomment{\fbox{Verify a message}} \\
-        \ucio{Send}~(\uccmd{Verify},\sid,\msg,\sig,v)~\text{to}~\adv \\
-        \ucio{Receive}~(\uccmd{Verified},\sid,\msg,\phi)~\text{from}~\adv \\
+        \ucsend~(\uccmd{Verify},\sid,\msg,\sig,v)~\text{to}~\adv \\
+        \ucrecv~(\uccmd{Verified},\sid,\msg,\phi)~\text{from}~\adv \\
         \pcif v' = v \land (\msg,\sig,v,1) \in \SIG: f \gets 1 \\
@@
         \pcif \sid = (P,\ssid) \\
-        \pcind \ucio{Send}~(\uccmd{Sign},\sid,\msg)~\text{to}~\adv \\
-        \pcind \ucio{Receive}~(\uccmd{Signature},\sid,\msg,\sig)~\text{from}~
+        \pcind \ucsend~(\uccmd{Sign},\sid,\msg)~\text{to}~\adv \\
+        \pcind \ucrecv~(\uccmd{Sig.},\sid,\msg,\sig)~\text{from}~
         \adv \\
@@
         \pcind \pcind \SIG \gets \SIG \cup (\msg,\sig,v,1) \\
-        \pcind \pcind \ucio{Output}~(\uccmd{Signature},\sid,\msg,\sig)
+        \pcind \pcind \ucio{Output}~(\uccmd{Sig.},\sid,\msg,\sig)
       }
@@
   \begin{framed}
+    \scalebox{0.9}{
       \begin{minipage}[t]{\textwidth}
@@
       \end{minipage}
+    }
     \vspace*{0.5em}
 
+    \scalebox{0.9}{
       \begin{minipage}[t]{0.55\textwidth}
@@
           \pccomment{\fbox{DID Create operation}} \\
-        \ucio{Send}~(\uccmd{Create}, \sid, \arg)~\text{to}~\adv \\
-        \ucio{Receive}~(\uccmd{CreateOk}, \sid, did,
-        \lbrace \val_i \rbrace_{i\in[n]}) \\
+          \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\adv \\
+          \ucrecv~(\uccmd{CreateOk}, \sid, did,
+          \lbrace (i, \val_i) \rbrace_{i\in[n]}) \\
           \pcind \text{from}~\adv \\
           \pcif (P,\did,\cdot) \notin \DID \land
-        \P(\lbrace \lbl_i \rbrace_{i\in[n]}) = 1: \\
+          \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 1: \\
           \pcind \DID \gets \DID \cup \lbrace (P,did,\lbrace
-        (\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
+          (i,\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
           \ucio{Output}~(\uccmd{Created},\sid,\did,
-        \lbrace \val_i \rbrace_{i\in[n]})
+          \lbrace (i,\val_i) \rbrace_{i\in[n]})
         }
       \end{minipage}
+    }
+    \scalebox{0.9}{
       \begin{minipage}[t]{0.5\textwidth}
@@
           \pccomment{\fbox{DID Read operation}} \\
-        \ucio{Send}~(\uccmd{Read},\sid,\arg)~\text{to}~\adv \\
-        \ucio{Receive}~(\uccmd{ReadOk},\sid)~\text{from}~\adv \\
+          \ucsend~(\uccmd{Read},\sid,\arg)~\text{to}~\adv \\
+          \ucrecv~(\uccmd{ReadOk},\sid)~\text{from}~\adv \\
           \pcif (\cdot,did,\sval) \in \DID: \\
@@
       \end{minipage}
+    }
     \vspace*{0.25em} \\
+    \scalebox{0.9}{
       \begin{minipage}[t]{0.55\textwidth}
@@
           \pccomment{\fbox{DID Update operation}} \\
-        \ucio{Send}~(\uccmd{Update}, \sid, \arg)~\text{to}~\adv \\
-        \ucio{Receive}~(\uccmd{UpdateOk},\sid,
-        \lbrace \val_i \rbrace_{i\in[n]}) \\
+          \ucsend~(\uccmd{Update}, \sid, \arg)~\text{to}~\adv \\
+          \ucrecv~(\uccmd{UpdateOk},\sid,
+          \lbrace (i,\val_i) \rbrace_{i\in[n]}) \\
           \pcind \text{from}~\adv \\
           \pcif (P,did,\sval) \in \DID \land
-        \P(\lbrace \lbl_i \rbrace_{i\in[n]}) = 1: \\
+          \P(\lbrace (i,\lbl_i) \rbrace_{i\in[n]}) = 1: \\
           \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
           \hspace*{7em} \lbrace (P, did,
-        \lbrace \lbl_i,\val_i \rbrace_{i\in[n]}) \rbrace
+          \lbrace (i,\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
+          \ucio{Output}~(\uccmd{Updated},\sid,
+          (\did,\lbrace (i,\val_i) \rbrace_{i\in[n]}))
         }
       \end{minipage}
+    }
+    \scalebox{0.9}{
       \begin{minipage}[t]{0.5\textwidth}
@@
           \pccomment{\fbox{DID Deactivate operation}} \\
-        \ucio{Send}~(\uccmd{Deact}, \sid, \arg)~\text{to}~\adv \\
-        \ucio{Receive}~(\uccmd{DeactOk},\sid)~\text{from}~\adv \\
+          \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\adv \\
+          \ucrecv~(\uccmd{DeactOk},\sid)~\text{from}~\adv \\
           \pcif (P,did,\sval) \in \DID~\land \\
-        \pcind \lbrace \lbl_i \rbrace_{i\in[n]} \subseteq \LBL(\sval): \\
-        \pcind \sval' \gets \sval \setminus \lbrace (\lbl_i,\cdot)
+          \pcind \lbrace (i,\lbl_i) \rbrace_{i\in[n]} \subseteq \LBL(\sval): \\
+          \pcind \sval' \gets \sval \setminus \lbrace (i,\lbl_i,\cdot)
           \rbrace_{i\in[n]} \\
@@
           \pcind \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
-        \hspace*{8em}\lbrace (P,did,\sval') \rbrace
+          \hspace*{8em}\lbrace (P,did,\sval') \rbrace \\
+          \ucio{Output}~(\uccmd{Deacted},\sid,(\did,\sval'))
         }
       \end{minipage}
+    }
   \end{framed}
@@
 key needs to be involved in proving that the operation comes from the intended
-party. Currently, 4 types of keys are supported: master keys (\MasterKey), for
-operating on DIDs; issuing keys, for issuing VCs (\IssueKey); communication
-keys (\CommKey), for key-exchange protocols; and authentication keys, to
-associate to VCs (\AuthKey).
+party. Atala specifies four key types, that are thus supported in Atala's DID
+method. Namely: master keys (\MasterKey), for operating on DIDs; issuing keys,
+for issuing VCs (\IssueKey); communication keys (\CommKey), for key-exchange
+protocols; and authentication keys, to associate to VCs (\AuthKey).
+
+\paragraph{Custom Notation.} %
+Keys in Atala are identified by indexes. In the following description of the
+\RealPKIDIDAtala construction, given a set of keys, we frequently refer to the
+``master key with lowest index''.  For brevity, given a set \st, we use
+$\LMKI(\st)$ to denote such index.
 
@@
 \todo{For now, this ignores \emph{unpublished} DIDs.}
-\figref{fig:alapkidid} contains the specification of Atala PRISM's DID method,
-which we describe next.
+\figref{fig:atalapkidid1} and \figref{fig:atalapkidid2} contain the
+specification of Atala PRISM's DID method,
+which we describe next. Looking at the \texttt{Create} and \texttt{Update}
+operations, it is clear that $\P(\lbrace \lbl_i \rbrace_{i\in[n]})$ in Atala
+requires that all key labels are of a known type (\MasterKey, \IssueKey,
+\CommKey, or \AuthKey) and that at least one of the keys in the DID Document
+is of type \MasterKey.
 
@@
 \item[\uccmd{Read}.] %
-  Getting the contents of a DID simply requires querying a \todo{PRISM node} for
-  it. The PRISM node returns the associated list, along with all related
-  \texttt{CreateDID} and \texttt{UpdateDID} transactions in the blockchain. If
-  the signatures of these transactions are valid, and the result of applying in
-  order all the operations produces the list returned by the \todo{PRISM node},
-  then the list is an up to date DID Document of the corresponding DID.
+  Getting the contents of a DID simply requires processing the associated
+  transactions in the blockchain. Namely, transactions $(\tx,\sig)$ where $\tx$
+  is either $(\texttt{CreateDID},\did,\cdot)$ or $(\texttt{UpdateDID},\did,
+  \cdot)$. The associated DID Document is the result of applying in an ordered
+  manner (from oldest to newest) all such validly signed transactions.
 \item[\uccmd{Update}.] %
@@
 
-\begin{figure}
+\begin{figure}[ht!]
   \begin{framed}
-    \begin{minipage}[t]{\textwidth}
-      \textrm{Upon receiving a call $\IdealFPKIDID^{\P}(\cmd,\sid,\arg)$
-        from some party $P$ to run command \cmd, in session \sid, with arguments
-        \arg, $\IdealFPKIDID^{\P}$ operates as follows.}
-      \textrm{If the received \cmd and \arg pair does not meet any of
-        the following options, the request is ignored.}
-      \textrm{\P is a boolean predicate defining concrete conditions for
-        acceptable DID creations, updates and deactivations.
-      }
-      \textrm{\todo{We assume that the functionality keeps track of the
-          received requests.}}
-    \end{minipage}
-    \vspace*{0.5em}
-
+    \scalebox{0.9}{
       \begin{minipage}[t]{0.55\textwidth}
-      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \arg =
+        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Create} \land \arg =
           \lbrace (i,\lbl_i) \rbrace_{i\in[n]}$}{
-        \pccomment{\fbox{DID Create operation}} \\
-        \st \gets \emptyset \\
           \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
@@
           \nexists i~\suchthat~\lbl_i = \MasterKey: \\
-        \pcind \texttt{Abort} \\
+          \pcind \texttt{abort} \\
+          \st \gets \emptyset \\
           \pcfor i \in [n]: \\
           \pcind \sid' \gets (P,\sid,i) \\
-        \pcind \ucio{Send}~(\uccmd{KeyGen},\sid')~\text{to}~\IdealFSig \\
-        \pcind \ucio{Receive}~(\uccmd{VerKey},\sid',\pk_i)~\text{from}~
+          \pcind \ucsend~(\uccmd{KeyGen},\sid')~\text{to}~\IdealFSig \\
+          \pcind \ucrecv~(\uccmd{VerKey},\sid',\pk_i)~\text{from}~
           \IdealFSig \\
-        \pcind \st \gets \st~||~(i,\lbl_i,\pk_i) \\
-        \ucio{Send}~(\uccmd{Hash},\st)~\text{to}~\IdealFRO \\
-        \ucio{Receive}~(\uccmd{Hashed},\st,h)~\text{from}~\IdealFRO \\
+          \pcind \st \gets \st \cup \lbrace (i,\lbl_i,\pk_i) \rbrace \\
+          \ucsend~(\uccmd{Hash},\st)~\text{to}~\IdealFRO \\
+          \ucrecv~(\uccmd{Hashed},\st,h)~\text{from}~\IdealFRO \\
           \did \gets ``did:prism:''||~h \\
-        \text{Locally store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]}) \\
           \tx \gets (\texttt{CreateDID}, \did, \st) \\
           \text{Let}~j\in[n]~\text{be the least value s.t.}~\lbl_j = \MasterKey \\
-        \ucio{Send}~(\uccmd{Sign},(P,\sid,j),\msg)~\text{to}~\IdealFSig \\
-        \ucio{Receive}~(\uccmd{Signature},(P,\sid,j),\msg,\sig)~\text{from}~\IdealFSig \\
-        \ucio{Send}~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
+          \ucsend~(\uccmd{Sign},(P,\sid,j),\tx)~\text{to}~\IdealFSig \\
+          \ucrecv~(\uccmd{Sig.},(P,\sid,j),\tx,\sig)~\text{from}~\IdealFSig \\
+          \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
           \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace \pk_i \rbrace_{i\in[n]})
@@
       \end{minipage}
+    }
+    \scalebox{0.9}{
       \begin{minipage}[t]{0.5\textwidth}
-      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
+        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Read} \land
           \arg = did$}{
-        \pccomment{\fbox{DID Read operation}} \\  
+          \ucsend~(\uccmd{Retrieve})~\texttt{to}~\IdealFaobb \\
+          \ucrecv~(\uccmd{Retrieve},L)~\texttt{from}~\IdealFaobb \\
+          \st \gets \emptyset \\
+          L_{\did} \gets (\ast,\did,\ast) \subseteq \DID \\
+          \pcfor (\tx=(\texttt{op},\did,\cdot),\sig) \in L_{\did}: \\
+          \pcind \pk \gets \emptyset \\
+          \pcind \pcif \texttt{op} = \texttt{CreateDID}~\land \\
+          \pcind \pcind \text{no \texttt{CreateDID} appeared before}: \\
+          \pcind \pcind (\cdot,\cdot,\lbrace (i,\lbl_i,\pk_i)
+          \rbrace_{i\in[n]}) \gets \tx \\
+          \pcind \pcind \st \gets \lbrace (i,\lbl_i,\pk_i) \rbrace_{i \in [n]} \\
+          \pcind \pcind j \gets \LMKI(\st); \pk \gets \pk_j \\
+          \pcind \pcif \texttt{op} = \texttt{UpdateDID}: \\
+          \pcind \pcind (\cdot,\cdot,(\st_{del},\st_{add})) \gets \tx \\
+          \pcind \pcind \lbrace i \rbrace_{i\in[n]} \gets \st_{del} \\ 
+          \pcind \pcind \lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \gets \st_{add} \\
+          \pcind \pcind j \gets \LMKI(\st); \pk \gets \pk_j \\
+          \pcind \pcind \st \gets \st \setminus \st_{del} \cup \st_{add} \\
+          \pcind \pcif \pk = \emptyset: \text{abort} \\
+          \pcind \ucsend~(\uccmd{Verify},(P,\sid),\tx,\sig,\pk)~\text{to}~\IdealFSig \\
+          \pcind \ucrecv~(\uccmd{Verified},(P,\sid),\tx,b)~\text{from}~\IdealFSig \\
+          \pcind \pcif b = 0: \text{abort} \\
+          \ucio{Output}~(\uccmd{Read},\sid,(\did,\st))
         }    
       \end{minipage}
-    \vspace*{0.25em} \\
+    }
+  \end{framed}
+  \caption{\texttt{Create} and \texttt{Read} operations in Atala
+    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealFPKIDID
+    in the $(\IdealFRO,\IdealFSig,\IdealFaobb)$-hybrid model.}
+  \label{fig:atalapkidid1}
+\end{figure}
+
+\begin{figure}[ht!]
+  \begin{framed}
+    \scalebox{0.9}{
+      \begin{minipage}[t]{\textwidth}
+        \textrm{We assume that the party running
+          \texttt{Update} and \texttt{Deactivate} operations has an up to date
+          copy $(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]})$ of the DID to
+          modify. Otherwise, a \texttt{Read} operation needs to be run before.}
+      \end{minipage}
+    }
+    \vspace*{0.5em}
+
+    \scalebox{0.90}{          
       \begin{minipage}[t]{0.55\textwidth}
-      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
+        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Update} \land
           \arg = (did, \lbrace (i,\lbl_i) \rbrace_{i\in\tilde{N}\subseteq [\tilde{n}]})$}{
-        \pccomment{\fbox{DID Update operation}} \\
           \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
@@
           \nexists i~\suchthat~\lbl_i = \MasterKey: \\
-        \pcind \texttt{Abort} \\
-        \text{Read}~(\did,\lbrace (i,\l_i,\pk_i) \rbrace_{i\in[n]})~
-        \text{from local storage} \\
+          \pcind \texttt{abort} \\
           \st_{add} \gets \emptyset \\
-        \pcfor i > n \in [\tilde{N}]: \\
-        \pcind \ucio{Send}~(\uccmd{KeyGen},(P,\sid,i))~\text{to}~\IdealFSig \\
-        \pcind \ucio{Receive}~(\uccmd{VerKey},(P,\sid,i),\pk_i)~\text{from}~
+          \pcfor i \in \tilde{N}~\suchthat~ i > n : \\
+          \pcind \ucsend~(\uccmd{KeyGen},(P,\sid,i))~\text{to}~\IdealFSig \\
+          \pcind \ucrecv~(\uccmd{VerKey},(P,\sid,i),\pk_i)~\text{from}~
           \IdealFSig \\
-        \pcind \st_{add} \gets \st_{add}~||~(i,\lbl_i,\pk_i) \\
-        \st_{del} \gets [n] \setminus [\tilde{N}] \\
-        \text{Locally store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \\
-        \tx \gets \texttt{UpdateDID}~||~\did~||~\st_{del}~||~\st_{add} \\
-        \text{Let}~j\in[n]~\text{be the least value s.t.}~\lbl_j = \MasterKey \\
-        \ucio{Send}~(\uccmd{Sign},(P,\sid,j),\msg)~\text{to}~\IdealFSig \\
-        \ucio{Receive}~(\uccmd{Signature},(P,\sid,j),\msg,\sig)~\text{from}~\IdealFSig \\
-        \ucio{Send}~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
+          \pcind \st_{add} \gets \st_{add} \cup \lbrace (i,\lbl_i,\pk_i) \rbrace \\
+          \st_{del} \gets [n] \setminus \tilde{N} \\
+          % \text{Locally store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \\
+          \tx \gets (\texttt{UpdateDID}, \did, (\st_{del}, \st_{add})) \\
+          j \gets \LMKI(\lbrace \lbl_i \rbrace_{i\in\tilde{N}}) \\
+          \ucsend~(\uccmd{Sign},(P,\sid,j),\tx)~\text{to}~\IdealFSig \\
+          \ucrecv~(\uccmd{Sig.},(P,\sid,j),\tx,\sig)~\text{from}~\IdealFSig \\
+          \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
           \ucio{Output}~(\uccmd{Updated},\sid,\did,\lbrace \pk_i \rbrace_{i\in[\tilde{N}]})
@@
       \end{minipage}
-    \begin{minipage}[t]{0.5\textwidth}
-      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \arg =
-        (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{
-        \pccomment{\fbox{DID Deactivate operation}} \\
+    }
+    \scalebox{0.9}{
+      \begin{minipage}[t]{0.45\textwidth}
+        \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Deact} \land \arg =
+          (did, \lbrace (i,\lbl_i) \rbrace_{i\in N \subseteq[n]})$}{       
+          \text{Run as a \texttt{Update} operation}
         }
       \end{minipage}
+    }
   \end{framed}
-  \caption{Atala PRISM DID-based PKI construction, \RealPKIDIDAtala.}
-  \label{fig:fpkidid}
+  \caption{\texttt{Update} and \texttt{Deactivate} operations in Atala
+    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealFPKIDID
+    in the $(\IdealFRO,\IdealFSig,\IdealFaobb)$-hybrid model.}
+  \label{fig:atalapkidid2}
 \end{figure}
 
-% \begin{figure}
+\subsection{Notes for Implementations}
 
-%   \begin{pchstack}[center, boxed, space=5mm]
-%     \procedure[linenumbering]{$\DIDCreate(\lbrace \lbl_i \rbrace_{i\in[n]})$}{
-%       \st \gets \emptyset \\
-%       \pcfor i \in [n]: \\
-%       \pcind \ucio{Send}~(\uccmd{KeyGen},(P,\sid,i))~\text{to}~\IdealFSig \\
-%       \pcind \ucio{Receive}~(\uccmd{VerKey},(P,\sid,i),\pk_i)~\text{from}~
-%       \IdealFSig \\
-%       \pcind \st \gets \st~||~(i,\lbl_i,\pk_i) \\
-%       \ucio{Send}~(\uccmd{Hash},\st)~\text{to}~\IdealFRO \\
-%       \ucio{Receive}~(\uccmd{Hashed},\st,h)~\text{from}~\IdealFRO \\
-%       \did \gets ``did:prism:''||~h \\
-%       \text{Store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]})~
-%       \text{in local storage} \\
-%       \tx \gets (\texttt{CreateDID}, \did, \st) \\
-%       \text{Let}~j\in[n]~\text{be the least value s.t.}~\lbl_j = \texttt{master} \\
-%       \pcif \text{no such $j$ exists}: \todo{abort} \\
-%       \ucio{Send}~(\uccmd{Sign},(P,\sid,j),\msg)~\text{to}~\IdealFSig \\
-%       \ucio{Receive}~(\uccmd{Signature},(P,\sid,j),\msg,\sig)~\text{from}~\IdealFSig \\
-%       \ucio{Send}~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
-%       \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace \pk_i \rbrace_{i\in[n]})
-%     }
+We acknowledge that, in the pseudocode given in \figref{fig:atalapkidid1} and
+\figref{fig:atalapkidid2}, we have favoured notational simplicity over
+implementation efficiency or
+convenience. For instance, it is not really needed that the master key signing a
+transaction is the one with the lowest index -- any such key can actually do it.
+However, it makes notation much easier. Similarly, in practice it may be easier
+to use different ``function arguments'' to denote the set of keys to remove and
+a set of keys to add from/to an existing DID. However, notationally it is
+simpler to follow the chosen (equivalent) approach. Finally, key indexes don't
+need to follow a sequential order.
 
-%     \procedure[linenumbering]
-%     {$\DIDUpdate(\did,\lbrace \tilde{\lbl}_i
-%       \rbrace_{i\ \in \tilde{N}\subseteq[\tilde{n}]})$}{
-%       \text{Read}~(\did,\lbrace (i,\l_i,\pk_i) \rbrace_{i\in[n]})~
-%       \text{from local storage} \\
-%       \st_{add} \gets \emptyset \\
-%       \pcfor i > n \in [\tilde{N}]: \\
-%       \pcind \ucio{Send}~(\uccmd{KeyGen},(P,\sid,i))~\text{to}~\IdealFSig \\
-%       \pcind \ucio{Receive}~(\uccmd{VerKey},(P,\sid,i),\pk_i)~\text{from}~
-%       \IdealFSig \\
-%       \pcind \st_{add} \gets \st_{add} || (i,\lbl_i,\pk_i) \\
-%       \st_{del} \gets [n] \setminus [\tilde{N}] \\
-%       \text{Store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]})~
-%       \text{in local storage} \\
-%       \tx \gets \texttt{UpdateDID} || \did || \st_{del} || \st_{add} \\
-%       \text{Let}~j\in[n]~\text{be the least value s.t.}~\lbl_j = \texttt{master} \\
-%       \ucio{Send}~(\uccmd{Sign},(P,\sid,j),\msg)~\text{to}~\IdealFSig \\
-%       \ucio{Receive}~(\uccmd{Signature},(P,\sid,j),\msg,\sig)~\text{from}~\IdealFSig \\
-%       \ucio{Send}~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
-%       \ucio{Output}~(\uccmd{Updated},\sid,\did,\lbrace \pk_i \rbrace_{i\in[\tilde{N}]})
-%     }  
-%   \end{pchstack}
-%   \label{fig:cudid}
-%   \caption{Algorithms for creating and updating a DID.}
-% \end{figure}
-
-\subsubsection{Read a DID.} \todo{PRISM nodes keep track of metadata?}
-
-\subsubsection{Update a DID.} %
-To update a DID, the alleged owner of the DID must specify the identifiers of
-the keys she wants to deactivate, and the number of keys of each type she wants
-to add. At least one master key (either new or old) must remain after this
-operation. Otherwise, the logic is as in the DID creation process, and it is
-specified in \figref{fig:cudid}. Therein, for readability we introduce the
-variables $N_m,N_i,N_a$, that keep track of (respectively) the number of master,
-issuing and authentication keys issued for the corresponding DID during its
-whole lifetime. Similarly, $\overline{MSK}$ denotes the master secret key with
-the lower index that has not been deactivated.
-
-\subsubsection{Deactivate a DID.} %
-The DID deactivation operation is implicitly implemented via the update
-operation. \todo{Confirm.}
+Somehow related, it is of course not needed to fetch the contents of the whole
+blockchain whenever we want to get an up to date DID Document. Instead, the
+party running the operation can keep a local copy, and just fetch the new
+operations since it last synced. However, again the given simplified notion of
+a blockchain (via \IdealFaobb) eases notation -- and seems good enough for a
+first modelling effort.
 

### 2022-11-11 prism-backend/research/prism-protocol/did_atala.tex
Some work on UC-security of Atala DID.

@@
       \vspace*{0.25em}
-      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Verify} \land
+      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Verif} \land
         \arg = (\sig,\msg,v')$}{
         \pccomment{\fbox{Verify a message}} \\
-        \ucsend~(\uccmd{Verify},\sid,\msg,\sig,v)~\text{to}~\adv \\
-        \ucrecv~(\uccmd{Verified},\sid,\msg,\phi)~\text{from}~\adv \\
+        \ucsend~(\uccmd{Verif},\sid,\msg,\sig,v)~\text{to}~\adv \\
+        \ucrecv~(\uccmd{Verifd},\sid,\msg,\phi)~\text{from}~\adv \\
         \pcif v' = v \land (\msg,\sig,v,1) \in \SIG: f \gets 1 \\
@@
         f \gets \phi \\
-        \ucio{Output}~(\uccmd{Verified},\sid,\msg,f)
+        \ucio{Output}~(\uccmd{Verifd},\sid,\msg,f)
       }
@@
         \pcind \ucsend~(\uccmd{Sign},\sid,\msg)~\text{to}~\adv \\
-        \pcind \ucrecv~(\uccmd{Sig.},\sid,\msg,\sig)~\text{from}~
+        \pcind \ucrecv~(\uccmd{Signed},\sid,\msg,\sig)~\text{from}~
         \adv \\
@@
         \pcind \pcind \SIG \gets \SIG \cup (\msg,\sig,v,1) \\
-        \pcind \pcind \ucio{Output}~(\uccmd{Sig.},\sid,\msg,\sig)
+        \pcind \pcind \ucio{Output}~(\uccmd{Signed},\sid,\msg,\sig)
       }
@@
 \subsection{Functionality \IdealFPKIDID}
+
+\todo{Mention public delayed outputs.}
 
@@
           \pccomment{\fbox{DID Create operation}} \\
+          \pcif \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 0:
+          \text{abort} \\
           \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\adv \\
@@
           \pcind \text{from}~\adv \\
-          \pcif (P,\did,\cdot) \notin \DID \land
-          \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 1: \\
+          \pcif (\cdot,\did,\cdot) \notin \DID: \\
           \pcind \DID \gets \DID \cup \lbrace (P,did,\lbrace
@@
           \pccomment{\fbox{DID Update operation}} \\
+          \pcif \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 0:
+          \text{abort} \\
           \ucsend~(\uccmd{Update}, \sid, \arg)~\text{to}~\adv \\
@@
           \pcind \text{from}~\adv \\
-          \pcif (P,did,\sval) \in \DID \land
-          \P(\lbrace (i,\lbl_i) \rbrace_{i\in[n]}) = 1: \\
+          \pcif (P,did,\sval) \in \DID: \\
           \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
@@
   \begin{framed}
+
+    \scalebox{0.9}{
+      \begin{minipage}[t]{\textwidth}
+        \textrm{Party $P$ running operation \cmd with arguments \arg, in
+          session \sid.}
+      \end{minipage}
+    }
+    \vspace*{0.5em}
+
     \scalebox{0.9}{
@@
           \pcfor i \in [n]: \\
-          \pcind \sid' \gets (P,\sid,i) \\
+          \pcind \sid' \gets ((P,i),\sid) \\
           \pcind \ucsend~(\uccmd{KeyGen},\sid')~\text{to}~\IdealFSig \\
@@
           \tx \gets (\texttt{CreateDID}, \did, \st) \\
-          \text{Let}~j\in[n]~\text{be the least value s.t.}~\lbl_j = \MasterKey \\
-          \ucsend~(\uccmd{Sign},(P,\sid,j),\tx)~\text{to}~\IdealFSig \\
-          \ucrecv~(\uccmd{Sig.},(P,\sid,j),\tx,\sig)~\text{from}~\IdealFSig \\
+          j \gets \LMKI(\st); \sid' \gets ((P,j),\sid) \\
+          \ucsend~(\uccmd{Sign},\sid',\tx)~\text{to}~\IdealFSig \\
+          \ucrecv~(\uccmd{Signed},\sid',\tx,\sig)~\text{from}~\IdealFSig \\
           \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
-          \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace \pk_i \rbrace_{i\in[n]})
+          \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace (i,\pk_i)
+          \rbrace_{i\in[n]})
         }
@@
           \pcind \pcind \st \gets \st \setminus \st_{del} \cup \st_{add} \\
-          \pcind \pcif \pk = \emptyset: \text{abort} \\
-          \pcind \ucsend~(\uccmd{Verify},(P,\sid),\tx,\sig,\pk)~\text{to}~\IdealFSig \\
-          \pcind \ucrecv~(\uccmd{Verified},(P,\sid),\tx,b)~\text{from}~\IdealFSig \\
+          \pcind \pcif \pk = \emptyset: \text{abort}; \pcelse \sid' \gets (P, \sid) \\
+          \pcind \ucsend~(\uccmd{Verif},\sid',\tx,\sig,\pk)~\text{to}~\IdealFSig \\
+          \pcind \ucrecv~(\uccmd{Verifd},\sid',\tx,b)~\text{from}~\IdealFSig \\
           \pcind \pcif b = 0: \text{abort} \\
@@
       \begin{minipage}[t]{\textwidth}
+        \textrm{Party $P$ running operation \cmd with arguments \arg, in
+          session \sid.} \\
         \textrm{We assume that the party running
@@
           \pcfor i \in \tilde{N}~\suchthat~ i > n : \\
-          \pcind \ucsend~(\uccmd{KeyGen},(P,\sid,i))~\text{to}~\IdealFSig \\
-          \pcind \ucrecv~(\uccmd{VerKey},(P,\sid,i),\pk_i)~\text{from}~
+          \pcind \ucsend~(\uccmd{KeyGen},((P,i),\sid))~\text{to}~\IdealFSig \\
+          \pcind \ucrecv~(\uccmd{VerKey},((P,i),\sid),\pk_i)~\text{from}~
           \IdealFSig \\
@@
           j \gets \LMKI(\lbrace \lbl_i \rbrace_{i\in\tilde{N}}) \\
-          \ucsend~(\uccmd{Sign},(P,\sid,j),\tx)~\text{to}~\IdealFSig \\
-          \ucrecv~(\uccmd{Sig.},(P,\sid,j),\tx,\sig)~\text{from}~\IdealFSig \\
+          \ucsend~(\uccmd{Sign},((P,j),\sid),\tx)~\text{to}~\IdealFSig \\
+          \ucrecv~(\uccmd{Signed},((P,j),\sid),\tx,\sig)~\text{from}~\IdealFSig \\
           \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
@@
 
-\subsection{Notes for Implementations}
+\subsubsection{Notes for Implementations.} %
 
@@
 
+\subsection{Security of \RealPKIDIDAtala}
+\label{ssec:sec-didatala}
+
+\todo{Define $\P_{Atala}$}
+
+\begin{theorem}[UC-security of \RealPKIDIDAtala]
+  \label{thm:sec-didatala}
+  \RealPKIDIDAtala UC-realizes $\IdealFPKIDID^{\P_{Atala}}$ in the $(\IdealFRO,
+  \IdealFSig, \IdealFaobb)$-hybrid model.
+\end{theorem}
+
+\begin{proof}
+  We show that \RealPKIDIDAtala UC-realizes \IdealFPKIDID, when configured
+  with policy $\P_{Atala}$. For this, we give a simulator \Sim such that, for
+  any environment \Env, $\Exec_{\RealPKIDIDAtala\adv,\Env} \approx
+  \Exec_{\phiDIDAtala,\Sim,\Env}$,
+  where \phiDIDAtala is a protocol composed with the same parties as
+  \RealPKIDIDAtala but where each party is simply a dummy party that forwards
+  any incoming/outgoing message to the ideal functionality \IdealFPKIDID. The
+  simulator \Sim runs internally a copy of the real-world adversary \adv, as
+  well as the ideal functionalities \IdealFRO, \IdealFSig and \IdealFaobb,
+  and any involved party.
+
+  \begin{description}
+  \item[Simulating DID Create.] %
+    %
+    % Policy check
+    \todo{Policy check not needed by \Sim, right?}
+    When \Sim receives a message $(\uccmd{Create},\sid,\lbrace (i,\lbl_i)
+    \rbrace_{i\in[n]})$ from a (dummy) party $P$, it simulates for \adv~the key
+    generation process of $n$ signing key pairs, by sending $n$
+    $(\uccmd{KeyGen},((P,i),\sid))$ queries to \adv~on
+    behalf of \IdealFSig, and receiving the $n$ corresponding $(\uccmd{VerKey},
+    ((P,i),\sid),\pk_i)$ responses.
+    %
+    % Hash computation
+    \Sim then concatenates all $(i,\lbl_i,\pk_i)$ tuples into \st, and simulates
+    a query to \IdealFRO \todo{do we need programmability or something?}, to set
+    \did as ``$did:prism: h$'' as DID value.
+    %
+    % Tx sim
+    With the DID value, \Sim simulates for \adv~the preparation of transaction
+    \tx. That is, \Sim uses the master key with lower index, $j \gets
+    \LMKI(\st)$, and simulates a query $(\uccmd{Sign},((P,j),\sid),\tx)$ to
+    \IdealFSig, obtaining from \adv~$(\uccmd{Signed},((P,j),\sid),\tx,\sig)$.
+    %
+    % BB append
+    \Sim also simulates appending the $(\tx,\sig)$ tuple to the bulletin board,
+    by sending $(\uccmd{Append},(\tx,\sig))$ to \adv~on behalf of \IdealFaobb.
+    %
+    % Output
+    Finally, \Sim sends the $(\uccmd{CreateOk},\sid,\did,\lbrace (i,\pk_i)
+    \rbrace_{i\in[n]})$ to \IdealFPKIDID.
+    Note that \did is generated uniformly at random. Thus, the probability that
+    \IdealFPKIDID halts because $\did \in \DID$ is negligible, and \IdealFPKIDID
+    outputs $(\uccmd{Created},\sid,\did,\lbrace (i,\val_i) \rbrace_{i\in[n]})$
+    to \Sim.
+  \item[Simulating DID Read.]
+  \item[Simulating DID Update.] 
+  \item[Simulating DID Deactivate.] Directly follows from DID Update.      
+  \end{description}
+\end{proof}
+
 %%% Local Variables:

### 2022-11-22 prism-backend/research/prism-protocol/did_atala.tex
Working on DID proof.

@@
 
+\todo{Syntax using counter indexes doesn't seem a good idea (the simplification
+  does not seem to work for proving security). Maybe change to arbitrary labels
+  (and change current key label name to key type).}
 \todo{Mention public delayed outputs.}
+\todo{If the functionality tries to fetch some entry from a list, and the entry
+  does not exist, then it aborts (assumed for updates).}
 
@@
         \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \arg =
-          \lbrace (i,\lbl_i) \rbrace_{i\in[n]}$}{
+          \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}$}{
           \pccomment{\fbox{DID Create operation}} \\
-          \pcif \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 0:
+          \pcif \P(\lbrace (\lbl_i, \typ_i) \rbrace_{i\in[n]}) = 0:
           \text{abort} \\
@@
           \ucrecv~(\uccmd{CreateOk}, \sid, did,
-          \lbrace (i, \val_i) \rbrace_{i\in[n]}) \\
+          \lbrace (\lbl_i, \val_i) \rbrace_{i\in[n]}) \\
           \pcind \text{from}~\adv \\
@@
           \pcind \DID \gets \DID \cup \lbrace (P,did,\lbrace
-          (i,\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
+          (\lbl_i,\typ_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
           \ucio{Output}~(\uccmd{Created},\sid,\did,
-          \lbrace (i,\val_i) \rbrace_{i\in[n]})
+          \lbrace (\lbl_i,\typ_i,\val_i) \rbrace_{i\in[n]})
         }
@@
         \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
-          \arg = (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{      
+          \arg = (did, \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[\tilde{n}]})$}{
           \pccomment{\fbox{DID Update operation}} \\
-          \pcif \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 0:
-          \text{abort} \\
+          % \pcif \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 0:
+          % \text{abort} \\
+          \pcif (P,\did,\sval) \in DID: \\
+          \pcind \sval_{del} \gets \sval \setminus
+          \lbrace (\lbl_i,\cdot) \rbrace_{i\in[\tilde{n}]} \\ 
+          \pcind \sval_{add} \gets \lbrace (\lbl_i,\typ_i)
+          \rbrace_{i\in[\tilde{n}]} \setminus \sval_{del} \\
+          \pccomment{\todo{Continue here!! XXXX}} \\
           \ucsend~(\uccmd{Update}, \sid, \arg)~\text{to}~\adv \\
@@
 which we describe next. Looking at the \texttt{Create} and \texttt{Update}
-operations, it is clear that $\P(\lbrace \lbl_i \rbrace_{i\in[n]})$ in Atala
-requires that all key labels are of a known type (\MasterKey, \IssueKey,
+operations, it is clear that $\P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]})$ in
+Atala requires that all key labels are of a known type (\MasterKey, \IssueKey,
 \CommKey, or \AuthKey) and that at least one of the keys in the DID Document
@@
 \item[\uccmd{Update}.] %
-  Updating a DID requires to (optionally) specify a list of previously existing
-  key identifiers to remove, and (optionally) specify a list of new key
+  To update a DID, we first assume for ease of exposition that the calling party
+  $P$ has an updated version of the associated DID Document (which included
+  a list of $n$ keys) -- if this is not the case, it suffices to make first a
+  call to \uccmd{Read} for the given DID. \todo{This seems relevant enough to
+    be highlighted in some more visible place, no?}
+  Then, updating a DID requires to (optionally) specify a list of previously
+  existing key identifiers to remove, and (optionally) specify a list of new key
   identifiers, and their types, to add. To simplify notation, we just adopt the
-  (equivalent) convention that the caller indicates a list of $(i,\lbl_i)$
-  pairs, which is interpreted as follows. If $i$ is an already existing
+  (equivalent) convention that the caller indicates a list of $\lbrace (i,
+  \lbl_i) \rbrace_{i\in\tilde{N}\subseteq[\tilde{n}]}$ pairs, where $\tilde{n}$
+  may be smaller or larger than $n$, depending on the desired update. This
+  list is then interpreted as follows. If $i$ is an already existing
   identifier, the label is ignored and the corresponding key is not removed. If
@@
           copy $(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]})$ of the DID to
-          modify. Otherwise, a \texttt{Read} operation needs to be run before.}
+          modify. Otherwise, a \texttt{Read} operation needs to be run before.
+          If no such \did exists, the execution is aborted.}
       \end{minipage}
@@
           \st_{add} \gets \emptyset \\
-          \pcfor i \in \tilde{N}~\suchthat~ i > n : \\
+          \pcfor i \in \tilde{N}~\suchthat~ i > n : \pccomment{$n$ is determined
+            by the local $(\did, \lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]})$
+            copy}\\
           \pcind \ucsend~(\uccmd{KeyGen},((P,i),\sid))~\text{to}~\IdealFSig \\
@@
 
-\todo{Define $\P_{Atala}$}
+Before going into the proofs, observe that the \uccmd{Create} and \uccmd{Update}
+operations in \RealPKIDIDAtala include (in lines 1-2) a policy on the received
+indexes and labels. Concretely, this policy requires that all labels are of a
+known key type, and that at least one of them is of type \MasterKey. In the
+sequel, we use $\P_{Atala}$ to refer to this policy.
 
@@
   \RealPKIDIDAtala but where each party is simply a dummy party that forwards
-  any incoming/outgoing message to the ideal functionality \IdealFPKIDID. The
-  simulator \Sim runs internally a copy of the real-world adversary \adv, as
-  well as the ideal functionalities \IdealFRO, \IdealFSig and \IdealFaobb,
-  and any involved party.
+  every message from \Env to the ideal functionality \IdealFPKIDID, and every
+  response from \IdealFPKIDID back to \Env. The simulator \Sim runs internally a
+  copy of the real-world adversary \adv, as well as the ideal functionalities
+  \IdealFRO, \IdealFSig and \IdealFaobb, and any involved party.
 
@@
     % Policy check
-    \todo{Policy check not needed by \Sim, right?}
-    When \Sim receives a message $(\uccmd{Create},\sid,\lbrace (i,\lbl_i)
-    \rbrace_{i\in[n]})$ from a (dummy) party $P$, it simulates for \adv~the key
+    First, note that \IdealFPKIDID is parameterised with $\P_{Atala}$. Thus,
+    if the input labels don't match the policy, the functionality rejects the
+    request, just as in the real protocol \RealPKIDIDAtala.
+    %
+    % Keys generation
+    Next, when \Sim receives a message $(\uccmd{Create},\sid,\lbrace (i,\lbl_i)
+    \rbrace_{i\in[n]})$ from (dummy) party $P$, it simulates for \adv~the key
     generation process of $n$ signing key pairs, by sending $n$
@@
     behalf of \IdealFSig, and receiving the $n$ corresponding $(\uccmd{VerKey}, 
-    ((P,i),\sid),\pk_i)$ responses.
+    ((P,i), \sid), \pk_i)$ responses.
     %
@@
     Finally, \Sim sends the $(\uccmd{CreateOk},\sid,\did,\lbrace (i,\pk_i)
-    \rbrace_{i\in[n]})$ to \IdealFPKIDID.
-    Note that \did is generated uniformly at random. Thus, the probability that
-    \IdealFPKIDID halts because $\did \in \DID$ is negligible, and \IdealFPKIDID
-    outputs $(\uccmd{Created},\sid,\did,\lbrace (i,\val_i) \rbrace_{i\in[n]})$
-    to \Sim.
+    \rbrace_{i\in[n]})$ to \IdealFPKIDID, and stores the tuple $(\did,\lbrace
+    (i,\lbl_i,\pk_i)\rbrace_{i\in[n]})$.
+    Note that \did is generated by an ideal random oracle (thus, uniformly at
+    random), just as in the real protocol \RealPKIDIDAtala. Thus, the
+    probability that \IdealFPKIDID halts because $\did \in \DID$ is negligible,
+    and \IdealFPKIDID outputs $(\uccmd{Created},\sid,\did,\lbrace (i,\val_i)
+    \rbrace_{i\in[n]})$.
   \item[Simulating DID Read.]
+    %
+    % Ack
+    Upon receiving $(\uccmd{Read},\sid,\did)$ from dummy party P, \Sim simply
+    forwards the message to \adv and waits until receiving the response, which
+    is forwareded back to P.
+    %
+    % Consistent and indistinguishable results
+    Now, we show that the value returned by \IdealFPKIDID is indistinguishable
+    to that of \RealPKIDIDAtala. \todo{Do after Update.}
   \item[Simulating DID Update.]
+    % 
+    % Policy check
+    First, note that \IdealFPKIDID is parameterised with $\P_{Atala}$. Thus,
+    if the input labels don't match the policy, the functionality rejects the
+    request, just as in the real protocol \RealPKIDIDAtala.
+    % 
+    % Read if needed
+    First, \Sim finds in its records the entry $(\did,\lbrace (i,\lbl_i,\pk_i)
+    \rbrace_{i\in[n]})$. If no such \did exists, aborts.
+    %
+    % Simulate generation of new keys
+    Then, \Sim parses the $\lbrace(i,\lbl_i)\rbrace_{i\in\tilde{N}\subseteq
+      [\tilde{n}]}$ for new indexes, and simulates for \adv~one call to the
+    $\uccmd{KeyGen}$ interface of \IdealFSig for each new key, and composes the
+    variable $\st_{add}$ as in the real protocol. Similarly, \Sim initializes
+    variable $\st_{del}$ by looking for indexes in $[n]$ no longer present in
+    $\tilde{N}$.
+    %
+    % Simulate transaction
+    Finally, \Sim prepares the transaction \tx as in the real protocol using
+    variables $\st_{add}$ and $\st_{del}$. For this, a \uccmd{Sign} request is
+    sent to \IdealFSign, and an \uccmd{Append} request is sent to \IdealFaobb.
+    \Sim sends the resulting $(\uccmd{UpdateOK},\sid,\lbrace (i,\pk_i)
+    \rbrace_{i\in[\tilde{N}]})$ back to \IdealFPKIDID.
+    %
+    % Indistinguishability
+    Note that, if \Sim does not abort, then a valid $(P,\did,\sval)$ entry must
+    exist in the \DID state variable of \IdealFPKIDID. Thus, \IdealFPKIDID does
+    not abort in line 6. Then, \IdealFPKIDID
   \item[Simulating DID Deactivate.] Directly follows from DID Update.      

### 2022-11-23 prism-backend/research/prism-protocol/did_atala.tex
Updated ideal func and construction to not-index labels.

@@
 
-Giving an ideal functionality for a DID-based PKI does not seem to be easy. The
-difficulty stems from the fact that the W3C specification (see footnote
+Giving an ideal functionality for a DID-based PKI does not seem to be direct.
+The difficulty stems from the fact that the W3C specification (see footnote
 \todo{X}) is very permissive in regards to what can be seen as a valid DID
@@
 may be, or what a deactivation implies, it seems hard to define a functionality
-that would cover all possible options.
-%
-We thus take the basic approach to see DID documents as simple dictionaries
-(i.e., lists of labels with corresponding values), associated to a common label,
-the DID. From this, creating a DID is simply defining a set (of at least size 1)
-of initial label-value pairs and get an identifier associated to them. Updating
-a DID is essentially a creation, but over an existing identifier - the
-functionality just replaces the old contents with the new ones, where of course
-both sets don't need to be disjoint. And deactivating a DID means removing some
-of its labels and associated values, where removing all of them equates to
-deactivating the whole DID. Reading a DID just outputs the latest contents of
-the associated dictionary.
-%
-Our expectation is that this permissive approach allows to capture a large
+that would cover all possible options (or a significant subset).
+
+\paragraph{Ideal functionality specification.} %
+We take the basic approach to see DID documents as simple dictionaries
+(i.e., lists of labels with corresponding types and values), associated to a
+common label, the DID. Based on this, we define the operations that compose an
+ideal basic functionality for DIDs, as follows:
+
+\begin{description}
+\item[Create interface.] To create a new DID, the functionality exposes a
+  \uccmd{Create} interface that receives a tuple of label and key type values.
+  Then, it asks the adversary to provide a value to each of the specified
+  labels, and the DID value. If the DID value does not exist in the records of
+  the functionality, a new entry (including the dictionary) is created. In order
+  to meet the authentication requirement, the ideal functionality takes note of
+  the party creating the DID, so that subsequent changes in the DID can only be
+  done by this party. We note that more advanced predicates could be defined, by
+  this bare minimum seems to be enough for most (current) DID methods.
+  \todo{Give evidence of the latter?}
+\item[Read interface.] The contents of existing DIDs can be fetched via the
+  \uccmd{Read} interface. It receives a DID value and, if it exists in the
+  functionality's records, returns the associated contents. Note that, if such
+  entry exists, then it is authentic by definition, and thus trivially meets
+  the authentication requirements.
+\item[Update interface.] The contents of existing DIDs can be modified via the
+  \uccmd{Update} interface. It requires to specify the actual DID and two lists:
+  $\sval_d$ with the labels to remove, and $\sval_a$ with the lables of new keys
+  to add (along with their types). The DID must exist in the records of the
+  functionality, and the call must originate from the same party that created
+  it. Note that this covers variants such as using update only to add new keys
+  (e.g. by specifying an empty $\sval_d$), or modifications of existing labels
+  (e.g., by adding an existing label in $\sval_d$, and also in $\sval_a$).
+\item[Deactivate interface.] Deactivating a DID is actually a simplification of
+  the update operation, without specifying new keys to add. This is possible
+  via the \uccmd{Deact} interface. Note that it is not strictly necessary to
+  specify this interface, as it is a special case of \uccmd{Update}. However, we
+  explicitly add it for proximity to the actual DID specification. \todo{Just
+    remove it?}
+\end{description}
+
+Our expectation is that this simple approach allows to capture a large
 subset of all possible DID method implementations. Note that the functional
@@
 the actual identifiers are computed; instead, we allow the adversary to pick
-them. To update a DID, we only require such DID to exist, but otherwise its
-contents can be set to something completely new, as long as the caller is the
-same party who created it. Finally, deactivating labels within an existing DID
+them. To update a DID, we only require such DID to exist and that the caller
+is the party that created it, but otherwise the DID's contents can be set to
+something completely new. Finally, deactivating labels within an existing DID
 requires that these labels exist -- and, again, that the caller is the same
 party who created the DID. Concretely, note that any further structure beyond
-the label-value dictionary approach, is left as an implementation detail.
-%
+the label-type-value dictionary approach, is left as an implementation detail.
+However, enforcing additional structure seems unavoidable in practice (e.g.,
+requiring that all DIDs include keys of certain type). Since this definitely
+has an impact on the behaviour of the ideal functionality, we parameterize it
+with a policy \P, which can operate only on the received labels and key types,
+and from which we only expect to return either $1$ to denote acceptance, or $0$
+to denote rejection.
+
 Note that we also allow the adversary to pick the values associated to the
@@
 specification.
-%
-\todo{Introduce \P, and re-write this in a more structured manner.}
-%
+
 We capture the resulting notion in \figref{fig:fpkidid}.
@@
           \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\adv \\
-          \ucrecv~(\uccmd{CreateOk}, \sid, did,
-          \lbrace (\lbl_i, \val_i) \rbrace_{i\in[n]}) \\
-          \pcind \text{from}~\adv \\
+          \ucrecv~(\uccmd{CreateOk}, \sid, \did,
+          \sval=\lbrace \val_i \rbrace_{i\in[n]}) \\
+          \hspace*{2.8em}\text{from}~\adv \\
           \pcif (\cdot,\did,\cdot) \notin \DID: \\
-          \pcind \DID \gets \DID \cup \lbrace (P,did,\lbrace
+          \pcind \DID \gets \DID \cup \lbrace (P,\did,\lbrace
           (\lbl_i,\typ_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
-          \ucio{Output}~(\uccmd{Created},\sid,\did,
-          \lbrace (\lbl_i,\typ_i,\val_i) \rbrace_{i\in[n]})
+          \ucio{Output}~(\uccmd{Created},\sid,\did,\sval)
         }
@@
           \pccomment{\fbox{DID Read operation}} \\
-          \ucsend~(\uccmd{Read},\sid,\arg)~\text{to}~\adv \\
-          \ucrecv~(\uccmd{ReadOk},\sid)~\text{from}~\adv \\
+          % \ucsend~(\uccmd{Read},\sid,\arg)~\text{to}~\adv \\
+          % \ucrecv~(\uccmd{ReadOk},\sid)~\text{from}~\adv \\
           \pcif (\cdot,did,\sval) \in \DID: \\
@@
       \begin{minipage}[t]{0.55\textwidth}
+        % \arg = (did, \sval= \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]})\$}{
         \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
-          \arg = (did, \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[\tilde{n}]})$}{
+          \arg = (did, \sval_d,\sval_a)$}{
           \pccomment{\fbox{DID Update operation}} \\
-          % \pcif \P(\lbrace (i, \lbl_i) \rbrace_{i\in[n]}) = 0:
-          % \text{abort} \\
-          \pcif (P,\did,\sval) \in DID: \\
-          \pcind \sval_{del} \gets \sval \setminus
-          \lbrace (\lbl_i,\cdot) \rbrace_{i\in[\tilde{n}]} \\ 
-          \pcind \sval_{add} \gets \lbrace (\lbl_i,\typ_i)
-          \rbrace_{i\in[\tilde{n}]} \setminus \sval_{del} \\
-          \pccomment{\todo{Continue here!! XXXX}} \\
-          \ucsend~(\uccmd{Update}, \sid, \arg)~\text{to}~\adv \\
-          \ucrecv~(\uccmd{UpdateOk},\sid,
-          \lbrace (i,\val_i) \rbrace_{i\in[n]}) \\
-          \pcind \text{from}~\adv \\
-          \pcif (P,did,\sval) \in \DID:  \\
-          \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
-          \hspace*{7em} \lbrace (P, did,
-          \lbrace (i,\lbl_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
-          \ucio{Output}~(\uccmd{Updated},\sid,
-          (\did,\lbrace (i,\val_i) \rbrace_{i\in[n]}))
+          \lbrace (\lbl_i^a,\typ_i^a) \rbrace_{i\in[n^a]} \gets \sval_a \\
+          \lbrace \lbl_i^d \rbrace_{i\in[n^d]} \gets \sval_d \\
+          \pcif (P,\did,\sval_0) \notin \DID: \text{abort} \\
+          % \sval_{del} \gets \sval_0 \setminus \sval;
+          % \sval_{add} \gets \sval \setminus \sval_{del} \\          
+          % n'' \gets |\sval_{add}| \\                    
+          \ucsend~(\uccmd{Update}, \sid, \sval_a)~\text{to}~\adv \\
+          \ucrecv~(\uccmd{UpdtOk},\sid,\lbrace \val^a_i \rbrace_{i\in[n^a]})~
+          \text{from}~\adv \\
+          \sval_1 \gets (\sval_0 \setminus \sval_d) \cup
+          \lbrace (\lbl^a_i,\typ^a_i,\val^a_i) \rbrace_{i\in[n^a]} \\
+          \pcif \P(\sval_1) = 0: \text{abort} \\
+          \DID \gets \DID \setminus \lbrace (P,\did,\sval_0) \rbrace \cup
+          \lbrace (P, \did, \sval_1) \rbrace \\
+          \ucio{Output}~(\uccmd{Updated},\sid, (\did,\lbrace \val_a \rbrace_{i\in[n^a]}))
         }
@@
         \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \arg =
-          (did, \lbrace (i,\lbl_i) \rbrace_{i\in[n]})$}{
+          (did, \lbrace \lbl_i \rbrace_{i\in[n]})$}{
           \pccomment{\fbox{DID Deactivate operation}} \\
-          \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\adv \\
-          \ucrecv~(\uccmd{DeactOk},\sid)~\text{from}~\adv \\
-          \pcif (P,did,\sval) \in \DID~\land \\
-          \pcind \lbrace (i,\lbl_i) \rbrace_{i\in[n]} \subseteq \LBL(\sval): \\
-          \pcind \sval' \gets \sval \setminus \lbrace (i,\lbl_i,\cdot)
+          % \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\adv \\
+          % \ucrecv~(\uccmd{DeactOk},\sid)~\text{from}~\adv \\
+          \pcif (P,did,\sval_0) \in \DID: \\
+          \pcind \sval_1 \gets \sval_0 \setminus \lbrace \lbl_i
           \rbrace_{i\in[n]} \\
-          \pcind \pcif \P(\sval') = 1: \\
-          \pcind \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval) \rbrace~\cup \\
-          \hspace*{8em}\lbrace (P,did,\sval') \rbrace \\
-          \ucio{Output}~(\uccmd{Deacted},\sid,(\did,\sval'))
+          \pcind \pcif \P(\sval_1) = 1: \\
+          \pcind \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval_0)
+          \rbrace~\cup \\
+          \hspace*{8em}\lbrace (P,did,\sval_1) \rbrace \\
+          \ucio{Output}~(\uccmd{Deacted},\sid,\did)
         }
@@
   \end{framed}
-  \caption{Ideal DID-based PKI functionality, \IdealFPKIDID.}
+  \caption{Ideal DID-based PKI functionality, \IdealFPKIDID. We abuse set
+    notation, and write $\lbrace (a_i,\dots) \rbrace_{i\in[n]} \setminus
+    \lbrace (b_j,\dots) \rbrace_{j\in[m]}$ to mean subtracting from the first
+    set the elements present in the second set, whenever $a_i = b_j$ for some
+    $i,j$, even if the size of the $(a_i,\dots)$ and $(b_j,\dots)$ tuples do not
+    match.}
   \label{fig:fpkidid}
@@
 \paragraph{Custom Notation.} %
-Keys in Atala are identified by indexes. In the following description of the
+Keys in Atala are identified by labels. In the following description of the
 \RealPKIDIDAtala construction, given a set of keys, we frequently refer to the
-``master key with lowest index''.  For brevity, given a set \st, we use
-$\LMKI(\st)$ to denote such index.
+``master key with lowest label'' (using any order relation, like lexicographic
+order).  For brevity, given a set \st, we use $\LMKL(\st)$ to denote such label.
 
@@
   To create a DID, the user has to specify the key pairs to create, along with
-  fresh identifiers and their type. For ease of exposition, we assume that the
-  used identifiers just follow a sequence. The predicate \P in Atala simply
-  requires that at least one key pair of \MasterKey type is created. The
+  fresh identifiers (labels) and their type. For ease of exposition, we assume
+  that the used identifiers just follow a sequence. The predicate \P in Atala
+  simply requires that at least one key pair of \MasterKey type is created. The
   \uccmd{Create} algorithm creates as many keys of each type as requested,
@@
         \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Create} \land \arg =
-          \lbrace (i,\lbl_i) \rbrace_{i\in[n]}$}{
-          \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
-          \CommKey,\IssueKey] \lor
-          \nexists i~\suchthat~\lbl_i = \MasterKey: \\
-          \pcind \texttt{abort} \\
+          \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}$}{
+          \pcif \exists i~\suchthat~\typ_i \notin [\MasterKey,\AuthKey,
+          \CommKey,\IssueKey]~\lor \\
+          \pcind \nexists i~\suchthat~\typ_i = \MasterKey
+          \lor \exists i,j~\suchthat~\lbl_i = \lbl_j: abort \\
           \st \gets \emptyset \\
           \pcfor i \in [n]: \\
-          \pcind \sid' \gets ((P,i),\sid) \\
+          \pcind \sid' \gets ((P,\lbl_i),\sid) \\
           \pcind \ucsend~(\uccmd{KeyGen},\sid')~\text{to}~\IdealFSig \\
@@
           \IdealFSig \\
-          \pcind \st \gets \st \cup \lbrace (i,\lbl_i,\pk_i) \rbrace \\
+          \pcind \st \gets \st \cup \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace \\
           \ucsend~(\uccmd{Hash},\st)~\text{to}~\IdealFRO \\
@@
           \tx \gets (\texttt{CreateDID}, \did, \st) \\
-          j \gets \LMKI(\st); \sid' \gets ((P,j),\sid) \\
+          j \gets \LMKL(\st); \sid' \gets ((P,j),\sid) \\
           \ucsend~(\uccmd{Sign},\sid',\tx)~\text{to}~\IdealFSig \\
@@
           \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
-          \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace (i,\pk_i)
+          \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace \pk_i
           \rbrace_{i\in[n]})
@@
           \pcind \pcind \text{no \texttt{CreateDID} appeared before}: \\
-          \pcind \pcind (\cdot,\cdot,\lbrace (i,\lbl_i,\pk_i)
+          \pcind \pcind (\cdot,\cdot,\lbrace (\lbl_i,\typ_i,\pk_i)
           \rbrace_{i\in[n]}) \gets \tx \\
-          \pcind \pcind \st \gets \lbrace (i,\lbl_i,\pk_i) \rbrace_{i \in [n]} \\
-          \pcind \pcind j \gets \LMKI(\st); \pk \gets \pk_j \\
+          \pcind \pcind \st \gets \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i \in [n]} \\
           \pcind \pcif \texttt{op} = \texttt{UpdateDID}: \\
-          \pcind \pcind (\cdot,\cdot,(\st_{del},\st_{add})) \gets \tx \\
-          \pcind \pcind \lbrace i \rbrace_{i\in[n]} \gets \st_{del} \\ 
-          \pcind \pcind \lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \gets \st_{add} \\
-          \pcind \pcind j \gets \LMKI(\st); \pk \gets \pk_j \\
-          \pcind \pcind \st \gets \st \setminus \st_{del} \cup \st_{add} \\
-          \pcind \pcif \pk = \emptyset: \text{abort}; \pcelse \sid' \gets (P, \sid) \\
+          \pcind \pcind (\cdot,\cdot,(\st_d,\st_a)) \gets \tx \\
+          \pcind \pcind \lbrace \lbl^d_i \rbrace_{i\in[n^d]} \gets \st_d \\ 
+          \pcind \pcind \lbrace (\lbl^a_i,\typ^a_i,\pk^a_i)
+          \rbrace_{i\in[n^a]} \gets \st_a \\
+          \pcind \pcind \st \gets (\st \setminus \st_d) \cup \st_a \\
+          \pcind j \gets \LMKL(\st); \pk \gets \pk_j \\
+          \pcind \pcif \pk = \emptyset: \text{abort} \\
+          \pcind \pcelse \sid' \gets ((P,j),\sid) \\
           \pcind \ucsend~(\uccmd{Verif},\sid',\tx,\sig,\pk)~\text{to}~\IdealFSig \\
@@
           session \sid.} \\
-        \textrm{We assume that the party running
-          \texttt{Update} and \texttt{Deactivate} operations has an up to date
-          copy $(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]})$ of the DID to
-          modify. Otherwise, a \texttt{Read} operation needs to be run before.
-          If no such \did exists, the execution is aborted.}
       \end{minipage}
@@
     \scalebox{0.90}{          
-      \begin{minipage}[t]{0.55\textwidth}
+      \begin{minipage}[t]{0.6\textwidth}
         \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Update} \land
-          \arg = (did, \lbrace (i,\lbl_i) \rbrace_{i\in\tilde{N}\subseteq [\tilde{n}]})$}{
-          \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
-          \CommKey,\IssueKey] \lor
-          \nexists i~\suchthat~\lbl_i = \MasterKey: \\
-          \pcind \texttt{abort} \\
-          \st_{add} \gets \emptyset \\
-          \pcfor i \in \tilde{N}~\suchthat~ i > n : \pccomment{$n$ is determined
-            by the local $(\did, \lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[n]})$
-            copy}\\
+          \arg = (did, \sval_d, \sval_a)$}{
+          % \pcif \exists i~\suchthat~\typ_i \notin [\MasterKey,\AuthKey,
+          % \CommKey,\IssueKey]~\lor \\
+          % \pcind \nexists i~\suchthat~\typ_i = \MasterKey
+          % \lor \exists i,j~\suchthat~\lbl_i = \lbl_j: abort \\
+          % \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
+          % \CommKey,\IssueKey] \lor
+          % \nexists i~\suchthat~\lbl_i = \MasterKey: \\
+          % \pcind abort \\
+          \text{Run $(\uccmd{Read},\sid,\did)$ to fetch $(\did,\sval)$} \\
+          \pcif \sval = \bot: abort \\
+          \st_a \gets \emptyset;~
+          \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i\in[n]} \gets \sval \\
+          \lbrace \lbl^d_i \rbrace_{i\in[n^d]} \gets \sval^d;~
+          \lbrace (\lbl^a_i,\typ^a_i) \rbrace_{i\in[n^a]} \gets \sval^a \\
+          \sval' \gets (\sval \setminus \sval_d) \cup \sval_a \\
+          \pcif \exists (\cdot,\typ,\cdot) \in \sval' ~\suchthat~\typ \notin
+          [\MasterKey,\AuthKey,\CommKey,\IssueKey]~\lor \\
+          \pcind \nexists (\cdot,\MasterKey,\cdot) \in \sval'
+          \lor \text{\sval' has dupl. labels}: abort \\
+          \pcfor i \in [n^a] \\
           \pcind \ucsend~(\uccmd{KeyGen},((P,i),\sid))~\text{to}~\IdealFSig \\
-          \pcind \ucrecv~(\uccmd{VerKey},((P,i),\sid),\pk_i)~\text{from}~
+          \pcind \ucrecv~(\uccmd{VerKey},((P,i),\sid),\pk^a_i)~\text{from}~
           \IdealFSig \\
-          \pcind \st_{add} \gets \st_{add} \cup \lbrace (i,\lbl_i,\pk_i) \rbrace \\
-          \st_{del} \gets [n] \setminus \tilde{N} \\
+          \pcind \st_a \gets \st_a \cup \lbrace (\lbl^a_i,\typ^a_i,\pk^a_i) \rbrace \\
           % \text{Locally store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \\
-          \tx \gets (\texttt{UpdateDID}, \did, (\st_{del}, \st_{add})) \\
-          j \gets \LMKI(\lbrace \lbl_i \rbrace_{i\in\tilde{N}}) \\
+          \tx \gets (\texttt{UpdateDID}, \did, \sval_d, \st_a) \\
+          j \gets \LMKL(\sval) \\
           \ucsend~(\uccmd{Sign},((P,j),\sid),\tx)~\text{to}~\IdealFSig \\
@@
           \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
-          \ucio{Output}~(\uccmd{Updated},\sid,\did,\lbrace \pk_i \rbrace_{i\in[\tilde{N}]})
+          \ucio{Output}~(\uccmd{Updated},\sid,(\did,\lbrace \pk^a_i \rbrace_{i\in[n^a]}))
         }
@@
         \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Deact} \land \arg =
-          (did, \lbrace (i,\lbl_i) \rbrace_{i\in N \subseteq[n]})$}{       
+          (did, \lbrace \lbl_i \rbrace_{i\in[n]})$}{       
           \text{Run as a \texttt{Update} operation}
@@
 
-Before going into the proofs, observe that the \uccmd{Create} and \uccmd{Update}
-operations in \RealPKIDIDAtala include (in lines 1-2) a policy on the received
-indexes and labels. Concretely, this policy requires that all labels are of a
-known key type, and that at least one of them is of type \MasterKey. In the
-sequel, we use $\P_{Atala}$ to refer to this policy.
+Before going into the proofs, observe that the \uccmd{Create} (in lines 1-2) and
+\uccmd{Update} (in lines 6-7) operations in \RealPKIDIDAtala include a policy on
+the received key labels and types. Concretely, this policy requires that all
+labels are unique, all types are of a known key type, and that at least one of
+them is of type \MasterKey. In the sequel, we use $\P_{Atala}$ to refer to this
+policy.
 
@@
     % Keys generation
-    Next, when \Sim receives a message $(\uccmd{Create},\sid,\lbrace (i,\lbl_i)
-    \rbrace_{i\in[n]})$ from (dummy) party $P$, it simulates for \adv~the key
-    generation process of $n$ signing key pairs, by sending $n$
-    $(\uccmd{KeyGen},((P,i),\sid))$ queries to \adv~on
+    Next, when \Sim receives a message $(\uccmd{Create},\sid,\lbrace (\lbl_i,
+    \typ_i) \rbrace_{i\in[n]})$ from (dummy) party $P$, it simulates for \adv~
+    the key generation process of $n$ signing key pairs, by sending $n$
+    $(\uccmd{KeyGen},((P,\lbl_i),\sid))$ queries to \adv~on
     behalf of \IdealFSig, and receiving the $n$ corresponding $(\uccmd{VerKey}, 
-    ((P,i), \sid), \pk_i)$ responses.
+    ((P,\lbl_i), \sid), \pk_i)$ responses.
     %
     % Hash computation
-    \Sim then concatenates all $(i,\lbl_i,\pk_i)$ tuples into \st, and simulates
-    a query to \IdealFRO \todo{do we need programmability or something?}, to set
-    \did as ``$did:prism: h$'' as DID value.
+    \Sim then concatenates all $(\lbl_i,\typ_i,\pk_i)$ tuples into \st, and
+    simulates a query to \IdealFRO \todo{do we need programmability or
+      something?}, to set \did as ``$did:prism: h$'' as DID value.
     %
@@
     With the DID value, \Sim simulates for \adv~the preparation of transaction
-    \tx. That is, \Sim uses the master key with lower index, $j \gets
-    \LMKI(\st)$, and simulates a query $(\uccmd{Sign},((P,j),\sid),\tx)$ to
+    \tx. That is, \Sim uses the master key with lowest label, $j \gets
+    \LMKL(\st)$, and simulates a query $(\uccmd{Sign},((P,j),\sid),\tx)$ to
     \IdealFSig, obtaining from \adv~$(\uccmd{Signed},((P,j),\sid),\tx,\sig)$.
@@
     % Output
-    Finally, \Sim sends the $(\uccmd{CreateOk},\sid,\did,\lbrace (i,\pk_i)
+    Finally, \Sim sends the $(\uccmd{CreateOk},\sid,\did,\lbrace \pk_i
     \rbrace_{i\in[n]})$ to \IdealFPKIDID, and stores the tuple $(\did,\lbrace
-    (i,\lbl_i,\pk_i)\rbrace_{i\in[n]})$.
+    (\lbl_i,\typ_i,\pk_i)\rbrace_{i\in[n]})$.
     Note that \did is generated by an ideal random oracle (thus, uniformly at
-    random), just as in the real protocol \RealPKIDIDAtala. Thus, the
+    random), just as in the real protocol \RealPKIDIDAtala. Hence, the
     probability that \IdealFPKIDID halts because $\did \in \DID$ is negligible,
-    and \IdealFPKIDID outputs $(\uccmd{Created},\sid,\did,\lbrace (i,\val_i)
+    and \IdealFPKIDID outputs $(\uccmd{Created},\sid,\did,\lbrace \val_i
     \rbrace_{i\in[n]})$.
@@
     variables $\st_{add}$ and $\st_{del}$. For this, a \uccmd{Sign} request is
-    sent to \IdealFSign, and an \uccmd{Append} request is sent to \IdealFaobb.
+    sent to \IdealFSig, and an \uccmd{Append} request is sent to \IdealFaobb.
     \Sim sends the resulting $(\uccmd{UpdateOK},\sid,\lbrace (i,\pk_i)

### 2022-12-03 prism-backend/research/prism-protocol/did_atala.tex
Rewrote ideal functionality using global subroutines.

@@
 In this section we first give an ideal functionality for Public-Key
-Infrastructures built atop of DIDs \IdealFPKIDID, and subsequently describe
+Infrastructures built atop of DIDs \IdealGPKIDID, and subsequently describe
 Atala PRISM DID method \RealPKIDIDAtala, which is a protocol realizing
-\IdealFPKIDID.
+\IdealGPKIDID.
 %
@@
 
-\paragraph{Append-Only Bulletin Boards.} %
-We adopt a simplified notion of append-only bulletin boards, given in
-\cite{acc+20}. This is a local functionality, that defines an (probably too)
-idealized version of a bulletin board, where no delays in the operations
-occur \todo{We probably want to improve this to use a UC version that
-  supports global functionalities}. For the sake of readability, we reproduce
-the functionality in \figref{fig:faobb}.
+\todo{Mention public delayed outputs.}
+\todo{If the functionalities try to fetch some entry from a list, and the entry
+  does not exist, then it aborts (assumed for updates).}
 
-\begin{figure}
+\paragraph{Hashes.} %
+We model hashes as a global subroutine. No participant needs extra power (such
+as programmability or observability), so we use a conventional random oracle --
+called strict random oracle in \cite{cdg+18}. For self-containment, we reproduce
+here the formulation.
+
+\begin{figure}[ht]
   \begin{framed}
     \begin{minipage}[t]{\textwidth}
-      \textrm{Upon receiving a call $\IdealFaobb(\cmd,\arg)$ from
-        some party $P$ to run command \cmd, with arguments \arg,
-        \IdealFaobb operates as follows.}
-      \textrm{\IdealFaobb maintains a list \aobbl of bit strings.}      
+      \textrm{Upon receiving a call $\IdealGRO(\cmd,\sid,\arg)$ from some party
+        $P$ to run command \cmd, in session \sid, with arguments \arg,
+        \IdealGRO operates as follows.} \\
+      \textrm{\IdealGRO keeps a list \hashlist of known hashed messages, and
+        outputs hashes of length $l \gets l(n)$, for some fixed security
+        parameter $n$.}
     \end{minipage}
@@
 
-    \begin{minipage}[t]{0.55\textwidth}
-      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Append} \land \arg = x$}{
-        \pccomment{\fbox{Append data to \aobbl}} \\
-        \aobbl \gets \aobbl || x \\
-        \pcif P~\text{is corrupt}:~\ucsend~(\uccmd{Appended},x,P)~\text{to}
-        ~\adv
+    \centering
+    \procedure{$\pcif \cmd = \uccmd{HashQuery} \land \arg = \msg$}{%
+      \pcif (\msg,h) \notin \hashlist:
+      h \getr \bin^{l}; \hashlist \gets \hashlist \cup \lbrace (\msg,h) \rbrace \\
+      \ucio{Output}~(\uccmd{HashConfirm},h)
+    }
+  \end{framed}
+\end{figure}
+
+\paragraph{Global clock.} %
+Our ideal (global) functionality for a ledger relies on a global clock to model
+delays in appending information. We rely on the ideal global clock functionality
+given in \cite{kkk21}. In a nutshell, the functionality keeps track of the
+parties in the system, and allows them to signal their intention to advance the
+clock's time. When all parties agree on it, the clock's time is incremented. See
+\figref{fig:gclock}.
+
+\begin{figure}[ht]
+  \begin{framed}
+    \begin{minipage}[t]{\textwidth}
+      \textrm{Upon receiving a call $\IdealGclock(\cmd,\arg)$ from
+        some party $P$ to run command \cmd, with arguments \arg,
+        \IdealGclock operates as follows.} \\
+      \textrm{\IdealGclock maintains a variable $t$ with the current itme,
+        a variable $T$ with the list of parties keeping track of the time,
+        and a map $A$ which keeps the parties' (dis)agreements to advance the
+        clock.}
+    \end{minipage}
+    \vspace*{0.5em}
+
+    \begin{minipage}[t]{0.40\textwidth}
+      \procedure{$\pcif \cmd = \uccmd{Register} \land \arg = \emptyset$}{
+        T \gets T \cup \set{P} \\
+        \ucio{Output}~(\uccmd{Registered})~\text{to}~P \\
+      }
+      \procedure{$\pcif \cmd = \uccmd{Update} \land \arg = \emptyset$}{
+        A(P) \gets \top \\
+        \pcif \forall P \in T, A(P) = \top: \\
+        \pcind t \gets t + 1; \forall P \in T, A(P) = \bot \\
+        \pcind \ucio{Send}~(\uccmd{Updated})~\text{to}~P        
       }
@@
     \hspace*{1.25em}
-    \begin{minipage}[t]{0.45\textwidth}
-      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Retrieve} \land \arg =
-        \emptyset$}{
-        \pccomment{\fbox{Retrieve the contents of \aobbl}} \\
-        \text{Output}~(\uccmd{Retrieved},\aobbl)~\text{to}~P
+    \begin{minipage}[t]{0.60\textwidth}
+      \procedure{$\pcif \cmd = \uccmd{Deregister} \land \arg = \emptyset$}{
+        T \gets T \setminus \set{P} \\
+        \text{Output}~(\uccmd{DeregisteredOk})~\text{to}~P \\
+      }
+      \procedure{$\pcif \cmd = \uccmd{Read} \land \arg = \emptyset$}{
+        \text{Output}~(\uccmd{ReadOk},t)~\text{to}~P
       }
@@
   \end{framed}
-  \caption{Ideal append-only bulletin board functionality, \IdealFaobb, from
-    \cite{acc+20}.}
-  \label{fig:faobb}
+  \caption{Ideal subroutine for a global clock, from \cite{kkk21}.}
+  \label{fig:gclock}
 \end{figure}
 
-\paragraph{Hashes.} %
-\todo{\IdealFRO.}
+\paragraph{$\delta$-delay Ledger.} %
+We adopt a ledger notion given in \cite{kkk21}. This is global functionality
+that defines an ideal version of a ledger as a shared subroutine, which models
+the append-only property of ledgers, and the fact that changes take some delay
+until they are applied to the ledger.
+%
+This functionality accepts sending individual transactions to be added to the
+ledger state, fetching (reading) the state of the ledger, and extending the
+ledger by appending (blocks of) transactions to it. Interestingly, it gives the
+adversary control over when to advance the status of each party, as long as
+these advancements ensure the common prefix rule -- where $\ldgState' \prec
+\ldgState$ means that $\ldgState'$ is a prefix of \ldgState. It also relies
+on yet another global functionality, the global clock, to timestamp incoming
+transactions. If a transaction is not appended to an honest party's view before
+the given $\delta$ delay, then the functionality aborts.
+%
+For the sake of readability, we reproduce the functionality in
+\figref{fig:gledger}.
+
+\begin{figure}[ht]
+  \begin{framed}
+    \begin{minipage}[t]{\textwidth}
+      \textrm{Upon receiving a call $\IdealGdledger(\cmd,\arg)$ from
+        some party $P$ to run command \cmd, with arguments \arg,
+        \IdealGdledger operates as follows.} \\
+      \textrm{\IdealGdledger maintains a mapping \ldgMap which associates
+        parties with their view of the ledger.
+        \ldgUtxo is a multiset of unconfirmed transactions.
+        \ldgState is the authoritative ledger state
+        All mappings and (multi-)sets are initialised to empty values.
+      }
+    \end{minipage}
+    \vspace*{0.5em}
+
+    \begin{minipage}[t]{0.40\textwidth}
+      \procedure{$\pcif \cmd = \uccmd{Submit} \land \arg = \ldgTx$}{
+        \ucio{Send}~(\uccmd{Read})~\text{to}~\IdealGclock \\
+        \ucio{Recv}~(\uccmd{ReadOk},t)~\text{from}~\IdealGclock \\
+        \ldgUtxo \gets \ldgUtxo \cup \set{(\ldgTx,t)} \\ 
+        \ucio{Output}~(\uccmd{Transaction},\ldgTx,t)~\text{to}~\adv \\
+      }
+      \procedure{$\pcif \cmd = \uccmd{Extend} \land \arg = \ldgState'$}{
+        \pcif P = \adv \land \ldgState' \subseteq \ldgUtxo: \\
+        \pcind \ldgUtxo \gets \ldgUtxo \setminus \ldgState' \\
+        \pcind \ldgState \gets \ldgState || \ldgState'
+      }
+    \end{minipage}
+    \hspace*{1.25em}
+    \begin{minipage}[t]{0.60\textwidth}
+      \procedure{$\pcif \cmd = \uccmd{Read} \land \arg =
+        \emptyset$}{
+        % \pcif P = \adv: data \gets \ldgState \\
+        % \pcelse: data \gets \ldgMap(P) \\
+        \ucio{Send}~(\uccmd{Read})~\text{to}~\IdealGclock \\
+        \ucio{Recv}~(\uccmd{ReadOk},t)~\text{from}~\IdealGclock \\
+        \pcif \exists (\ldgTx,t') \in \ldgUtxo~\suchthat~|t-t'| > \delta:
+        \pcreturn \bot \\
+        \pcelse \pcif \exists (\ldgTx,t') \in \ldgState~\suchthat~ |t-t'|
+        > \delta~\land \\
+        \pcind \exists P' \in \ldgHonest~\suchthat~(\ldgTx,t') \notin \ldgMap(P'):
+        \pcreturn \bot \\        
+        \text{Output}~(\uccmd{ReadOk}, \ldgHead(\ldgMap(P)))~\text{to}~P \\
+      }
+      \procedure{$\pcif \cmd = \uccmd{Advance} \land \arg = (P',\ldgState')$}{
+        \pcif P = \adv \land \ldgMap(P') \prec \ldgState' \prec \ldgState:
+        \ldgMap(P') \gets \ldgState'
+      }
+    \end{minipage}
+  \end{framed}
+  \caption{Ideal subroutine for a global $\delta$-delay ledger, from
+    \cite{kkk21}.}
+  \label{fig:gledger}
+\end{figure}
 
@@
     \begin{minipage}[t]{0.5\textwidth}
-      \procedure[linenumbering]{$\pcif \cmd = \uccmd{KeyGen} \land \arg =
+      \procedure{$\pcif \cmd = \uccmd{KeyGen} \land \arg =
         \emptyset$}{
@@
       \vspace*{0.25em}
-      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Verif} \land
+      \procedure{$\pcif \cmd = \uccmd{Verif} \land
         \arg = (\sig,\msg,v')$}{
@@
     \begin{minipage}[t]{0.5\textwidth}
-      \procedure[linenumbering]{$\pcif \cmd = \uccmd{Sign} \land \arg = \msg$}{
+      \procedure{$\pcif \cmd = \uccmd{Sign} \land \arg = \msg$}{
         \pccomment{\fbox{Sign a message}} \\
@@
   \caption{Ideal signature functionality, \IdealFSig, from \cite{canetti03}.}
-  \label{fig:faobb}
+  \label{fig:fsig}
 \end{figure}
 
-\subsection{Functionality \IdealFPKIDID}
-
-\todo{Syntax using counter indexes doesn't seem a good idea (the simplification
-  does not seem to work for proving security). Maybe change to arbitrary labels
-  (and change current key label name to key type).}
-\todo{Mention public delayed outputs.}
-\todo{If the functionality tries to fetch some entry from a list, and the entry
-  does not exist, then it aborts (assumed for updates).}
+\subsection{Global Functionality \IdealGPKIDID}
 
@@
 has an impact on the behaviour of the ideal functionality, we parameterize it
-with a policy \P, which can operate only on the received labels and key types,
-and from which we only expect to return either $1$ to denote acceptance, or $0$
-to denote rejection.
+with a policy \P, which can be used as a black box: the functionality invokes
+\P with a set of labels and key types, and receives either $1$ to denote
+acceptance, or $0$ to denote rejection. However, it is not realistic to assume
+that, even corrupted parties will enforce such policies. Thus, our approach is
+to defer policy checking in the ideal functionality until after having
+interacted with the simulator \Sim. Intuitively then, if the output of the
+ideal functionality along with \Sim is indistinguishable to that of the real
+protocol with any real world adversary, then the policy is correctly enforced
+by the real protocol. Looking ahead, the real protocol in turn ``delegates''
+this policy-checking to an ideal append-only bulletin board. \todo{This captures
+  the idea, but refine and re-structure.}
 
@@
       \begin{minipage}[t]{\textwidth}
-        \textrm{Upon receiving a call $\IdealFPKIDID^{\P}(\cmd,\sid,\arg)$
+        \textrm{Upon receiving a call $\IdealGPKIDID^{\P}(\cmd,\sid,\arg)$
           from some party $P$ to run command \cmd, in session \sid, with arguments
-          \arg, $\IdealFPKIDID^{\P}$ operates as follows.}
+          \arg, $\IdealGPKIDID^{\P}$ operates as follows.}
         \textrm{If the received \cmd and \arg pair does not meet any of
@@
         \textrm{\P is a boolean predicate defining concrete conditions for
-          acceptable DID creations, updates and deactivations.
-        }
-        \textrm{\todo{We assume that the functionality keeps track of the
-            received requests.}}
+          acceptable DID creations, updates and deactivations.}
+        \textrm{\didOP is a list of submitted (yet, possibly unconfirmed) DID
+          operations, and \DID is the authoritative state of published DIDs.}
       \end{minipage}
@@
         \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \arg =
-          \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}$}{
-          \pccomment{\fbox{DID Create operation}} \\
-          \pcif \P(\lbrace (\lbl_i, \typ_i) \rbrace_{i\in[n]}) = 0:
-          \text{abort} \\
-          \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\adv \\
+          \setind{(\lbl_i,\typ_i)}{i\in[n]}$}{ 
+          \DID \gets \DIDReadLdg \\
+          \pcif (\did,\cdot) \in \DID \lor
+          \P(\setind{(\lbl_i,\typ_i)}{i\in[n]}) = 0: \\
+          \pcind \pcreturn \bot \\
+          \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\Sim \\
           \ucrecv~(\uccmd{CreateOk}, \sid, \did,
-          \sval=\lbrace \val_i \rbrace_{i\in[n]}) \\
-          \hspace*{2.8em}\text{from}~\adv \\
-          \pcif (\cdot,\did,\cdot) \notin \DID: \\
-          \pcind \DID \gets \DID \cup \lbrace (P,\did,\lbrace
-          (\lbl_i,\typ_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
-          \ucio{Output}~(\uccmd{Created},\sid,\did,\sval)
+          \sval=\setind{\val_i}{i\in[n]}) \\
+          \hspace*{2.7em}\text{from}~\Sim \\          
+          \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock \\
+          \ucrecv~(\uccmd{ReadOk},\tau)~\text{from}~\IdealGclock \\
+          \didOp \gets (\did,\setind{(\lbl_i,\typ_i,\val_i)}{i\in[n]}) \\
+          \didOP \gets \didOP \cup \set{(P,\tau,\didOp)} \\
+          \ucsend~(\uccmd{Submit}, \didOp)~\text{to}~\IdealGdledger \\
+          \ucio{Output}~(\uccmd{ProcessedC},\sid,\did,\sval)
+          % \pcind \DID \gets \DID \cup \lbrace (P,\did,\lbrace
+          % (\lbl_i,\typ_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
+          % \ucio{Output}~(\uccmd{Created},\sid,\did,\sval,t)
         }
@@
         \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
-          \arg = did$}{
-          \pccomment{\fbox{DID Read operation}} \\
-          % \ucsend~(\uccmd{Read},\sid,\arg)~\text{to}~\adv \\
-          % \ucrecv~(\uccmd{ReadOk},\sid)~\text{from}~\adv \\
-          \pcif (\cdot,did,\sval) \in \DID: \\
-          \pcind \ucio{Output}~(\uccmd{Read},\sid,(did,\sval))~\text{to}~P \\
-          \pcelse: \\
-          \pcind \ucio{Output}~(\uccmd{Read},\sid,\bot)~\text{to}~P    
+          \arg = \did$}{
+          \DID \gets \DIDReadLdg \\
+          \pcif (\did,\sval) \notin \DID \lor \P(\sval) = 0: \\
+          \pcind \pcreturn \bot \\
+          \ucio{Output}~(\uccmd{ReadOk},\sid,\did,\sval)~\text{to}~P
         }    
@@
           \arg = (did, \sval_d,\sval_a)$}{
-          \pccomment{\fbox{DID Update operation}} \\
+          \DID \gets \DIDReadLdg \\
+          \pcif (\did,\sval_0) \notin \DID: \pcreturn \bot \\
+          \pcif \P((\sval_0 \setminus \sval_d) \cup \sval_a) = 0:
+          \pcreturn \bot \\
+          \ucsend~(\uccmd{Update}, \sid,\did,\sval_d,\sval_a)~\text{to}~\Sim \\
+          \ucrecv~(\uccmd{UpdOk},\sid,\did,\lbrace \val^a_i \rbrace_{i\in[n^a]})~
+          \text{from}~\Sim \\
+          \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock \\
+          \ucrecv~(\uccmd{ReadOk},\tau)~\text{from}~\IdealGclock \\
           \lbrace (\lbl_i^a,\typ_i^a) \rbrace_{i\in[n^a]} \gets \sval_a \\
-          \lbrace \lbl_i^d \rbrace_{i\in[n^d]} \gets \sval_d \\
-          \pcif (P,\did,\sval_0) \notin \DID: \text{abort} \\
-          % \sval_{del} \gets \sval_0 \setminus \sval;
-          % \sval_{add} \gets \sval \setminus \sval_{del} \\          
-          % n'' \gets |\sval_{add}| \\                    
-          \ucsend~(\uccmd{Update}, \sid, \sval_a)~\text{to}~\adv \\
-          \ucrecv~(\uccmd{UpdtOk},\sid,\lbrace \val^a_i \rbrace_{i\in[n^a]})~
-          \text{from}~\adv \\
+          %\lbrace \lbl_i^d \rbrace_{i\in[n^d]} \gets \sval_d \\          
           \sval_1 \gets (\sval_0 \setminus \sval_d) \cup
-          \lbrace (\lbl^a_i,\typ^a_i,\val^a_i) \rbrace_{i\in[n^a]} \\
-          \pcif \P(\sval_1) = 0: \text{abort} \\
-          \DID \gets \DID \setminus \lbrace (P,\did,\sval_0) \rbrace \cup
-          \lbrace (P, \did, \sval_1) \rbrace \\
-          \ucio{Output}~(\uccmd{Updated},\sid, (\did,\lbrace \val_a \rbrace_{i\in[n^a]}))
+          \setind{(\lbl^a_i,\typ^a_i,\val^a_i)}{i\in[n^a]} \\
+          \didOp \gets (\did,\sval_1);~
+          \didOP \gets \didOP \cup \set{(P,\tau,\didOp)} \\
+          \ucsend~(\uccmd{Submit}, \didOp)~\text{to}~\IdealGdledger \\
+          \ucio{Output}~(\uccmd{ProcessedU},\sid,\did,\didOp)
         }
@@
           (did, \lbrace \lbl_i \rbrace_{i\in[n]})$}{
-          \pccomment{\fbox{DID Deactivate operation}} \\
-          % \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\adv \\
-          % \ucrecv~(\uccmd{DeactOk},\sid)~\text{from}~\adv \\
-          \pcif (P,did,\sval_0) \in \DID: \\
-          \pcind \sval_1 \gets \sval_0 \setminus \lbrace \lbl_i
-          \rbrace_{i\in[n]} \\
-          \pcind \pcif \P(\sval_1) = 1: \\
-          \pcind \pcind \DID \gets \DID \setminus \lbrace (P,did,\sval_0)
-          \rbrace~\cup \\
-          \hspace*{8em}\lbrace (P,did,\sval_1) \rbrace \\
-          \ucio{Output}~(\uccmd{Deacted},\sid,\did)
+          \DID \gets \DIDReadLdg \\
+          \pcif (P,did,\sval_0) \notin \DID: \pcreturn \bot \\
+          \sval_1 \gets \sval_0 \setminus \lbrace \lbl_i \rbrace_{i\in[n]} \\
+          \pcif \P(\sval_1) = 0: \pcreturn \bot \\
+          \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\Sim \\
+          \ucrecv~(\uccmd{DeactOk},\sid)~\text{from}~\Sim \\
+          \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock \\
+          \ucrecv~(\uccmd{ReadOk},\tau)~\text{from}~\IdealGclock \\          
+          \didOp \gets (\did,\sval_1);
+          \didOP \gets \didOP \cup \set{(P,\tau,\didOp)} \\
+          \ucsend~(\uccmd{Submit},\didOp)~\text{to}~\IdealGdledger \\          
+          \ucio{Output}~(\uccmd{ProcessedD},\sid,\did,\didOp)
+        }
+      \end{minipage}
+    }
+    \vspace*{0.25em} \\
+    \scalebox{0.9}{
+      \begin{minipage}[t]{\textwidth}
+        \centering
+        \procedure[linenumbering]{$\DIDReadLdg$}{
+          \ucsend~(\uccmd{Read})~\text{to}~\IdealGdledger~\text{and recv}~
+          (\uccmd{ReadOk},\DID)~\text{back} \\
+          \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock ~\text{and recv}~
+          (\uccmd{ReadOk},\tau)~\text{back} \\
+          \pcif \exists (\cdot,\tau',\didOp) \in \didOP~\suchthat~
+          |\tau - \tau'| > \delta \land \P(\didOp) = 1 \land \didOp \notin \DID:
+          \pcreturn \bot \\
+          \pcreturn \DID
         }
@@
   \end{framed}
-  \caption{Ideal DID-based PKI functionality, \IdealFPKIDID. We abuse set
+  \caption{Ideal DID-based PKI functionality, \IdealGPKIDID. We abuse set
     notation, and write $\lbrace (a_i,\dots) \rbrace_{i\in[n]} \setminus
@@
 We next define the Atala PRISM DID method, following the interfaces defined for
-\IdealFPKIDID. We begin by describing the types of keys supported in Atala
+\IdealGPKIDID. We begin by describing the types of keys supported in Atala
 PRISM, and then specify how sets of such keys can be managed through DIDs in
@@
 order).  For brevity, given a set \st, we use $\LMKL(\st)$ to denote such label.
+
+\paragraph{$\P_{Atala}$ policy.} %
+Before proceeding with the specififying the DID operations in Atala, we define
+its policy on the keys' labels and types.
+
+\begin{figure}[ht]
+  \centering
+  \procedure{$\P_{Atala}(\lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]})$}{    
+    \pcif \exists i\in[n]~\suchthat~\typ_i \notin [\MasterKey,\IssueKey,
+    \CommKey,\AuthKey]: \pcreturn 0~\pccomment{All types must be known} \\   
+    \pcif \not\exists i\in[n]~\suchthat~\typ_i = \MasterKey: \pcreturn 0~
+    \pccomment{There must be at least one master key} \\
+    \pcif \exists i, j \in[n], i \neq j~\suchthat~\lbl_i = \lbl_j: \pcreturn 0~
+    \pccomment{No duplicate labels} \\
+    \pcreturn 1
+  }
+  \caption{Policy $\P_{Atala}$ that all DID documents must meet in Atala.}
+\end{figure}
 
@@
           \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}$}{
-          \pcif \exists i~\suchthat~\typ_i \notin [\MasterKey,\AuthKey,
-          \CommKey,\IssueKey]~\lor \\
-          \pcind \nexists i~\suchthat~\typ_i = \MasterKey
-          \lor \exists i,j~\suchthat~\lbl_i = \lbl_j: abort \\
+          \pcif \P_{Atala}(\lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}) = 0: abort \\
           \st \gets \emptyset \\
@@
           \pcind \st \gets \st \cup \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace \\
-          \ucsend~(\uccmd{Hash},\st)~\text{to}~\IdealFRO \\
-          \ucrecv~(\uccmd{Hashed},\st,h)~\text{from}~\IdealFRO \\
+          \ucsend~(\uccmd{Hash},\st)~\text{to}~\IdealGRO \\
+          \ucrecv~(\uccmd{Hashed},\st,h)~\text{from}~\IdealGRO \\
           \did \gets ``did:prism:''||~h \\
           \tx \gets (\texttt{CreateDID}, \did, \st) \\
-          j \gets \LMKL(\st); \sid' \gets ((P,j),\sid) \\
+          \lbl \gets \LMKL(\st); \sid' \gets ((P,\lbl),\sid) \\
           \ucsend~(\uccmd{Sign},\sid',\tx)~\text{to}~\IdealFSig \\
           \ucrecv~(\uccmd{Signed},\sid',\tx,\sig)~\text{from}~\IdealFSig \\
-          \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
+          \ucsend~(\uccmd{Append},(\tx,\sig))~\text{to}~\IdealGdledger \\
+          \text{Locally store}~
+          (\did, \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i\in[n]}) \\
           \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace \pk_i
@@
           \arg = did$}{
-          \ucsend~(\uccmd{Retrieve})~\texttt{to}~\IdealFaobb \\
-          \ucrecv~(\uccmd{Retrieve},L)~\texttt{from}~\IdealFaobb \\
+          \ucsend~(\uccmd{Retrieve})~\texttt{to}~\IdealGdledger \\
+          \ucrecv~(\uccmd{Retrieve},L)~\texttt{from}~\IdealGdledger \\
           \st \gets \emptyset \\
@@
           \pcind \pcind \st \gets (\st \setminus \st_d) \cup \st_a \\
-          \pcind j \gets \LMKL(\st); \pk \gets \pk_j \\
-          \pcind \pcif \pk = \emptyset: \text{abort} \\
-          \pcind \pcelse \sid' \gets ((P,j),\sid) \\
+          \pcind \lbl \gets \LMKL(\st) \\
+          \pcind \pcif \lbl = \emptyset \lor \P_{Atala}(\st) = 0: \text{skip} \\
+          \pcind \pcelse \sid' \gets ((P,\lbl),\sid) \\
           \pcind \ucsend~(\uccmd{Verif},\sid',\tx,\sig,\pk)~\text{to}~\IdealFSig \\
           \pcind \ucrecv~(\uccmd{Verifd},\sid',\tx,b)~\text{from}~\IdealFSig \\
-          \pcind \pcif b = 0: \text{abort} \\
+          \pcind \pcif b = 0: \text{skip} \\
           \ucio{Output}~(\uccmd{Read},\sid,(\did,\st))
@@
   \caption{\texttt{Create} and \texttt{Read} operations in Atala
-    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealFPKIDID
-    in the $(\IdealFRO,\IdealFSig,\IdealFaobb)$-hybrid model.}
+    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealGPKIDID
+    in the $(\IdealGRO,\IdealFSig,\IdealGdledger)$-hybrid model.}
   \label{fig:atalapkidid1}
@@
           % \pcind abort \\
-          \text{Run $(\uccmd{Read},\sid,\did)$ to fetch $(\did,\sval)$} \\
-          \pcif \sval = \bot: abort \\
+          % \text{Run $(\uccmd{Read},\sid,\did)$ to fetch $(\did,\sval)$} \\
+          % \pcif \sval = \bot: abort \\
+          \text{Fetch}~
+          (\did, \sval=\lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i\in[n]})
+          ~\text{from storage} \\
           \st_a \gets \emptyset;~
           \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i\in[n]} \gets \sval \\
-          \lbrace \lbl^d_i \rbrace_{i\in[n^d]} \gets \sval^d;~
-          \lbrace (\lbl^a_i,\typ^a_i) \rbrace_{i\in[n^a]} \gets \sval^a \\
-          \sval' \gets (\sval \setminus \sval_d) \cup \sval_a \\
-          \pcif \exists (\cdot,\typ,\cdot) \in \sval' ~\suchthat~\typ \notin
-          [\MasterKey,\AuthKey,\CommKey,\IssueKey]~\lor \\
-          \pcind \nexists (\cdot,\MasterKey,\cdot) \in \sval'
-          \lor \text{\sval' has dupl. labels}: abort \\
-          \pcfor i \in [n^a] \\
-          \pcind \ucsend~(\uccmd{KeyGen},((P,i),\sid))~\text{to}~\IdealFSig \\
-          \pcind \ucrecv~(\uccmd{VerKey},((P,i),\sid),\pk^a_i)~\text{from}~
+          \lbrace \lbl^d_i \rbrace_{i\in[n_d]} \gets \sval_d;~
+          \lbrace (\lbl^a_i,\typ^a_i) \rbrace_{i\in[n_a]} \gets \sval_a \\
+          \sval' \gets (\sval \setminus \sval_d) \cup \sval_a
+          \pccomment{\todo{Syntax refinement needed here.}} \\
+          \pcif \P_{Atala}(\sval') = 0: abort \\          
+          \pcfor i \in [n_a] \\
+          \pcind \ucsend~(\uccmd{KeyGen},((P,\lbl_i),\sid))~\text{to}~\IdealFSig \\
+          \pcind \ucrecv~(\uccmd{VerKey},((P,\lbl_i),\sid),\pk^a_i)~\text{from}~
           \IdealFSig \\
@@
           \tx \gets (\texttt{UpdateDID}, \did, \sval_d, \st_a) \\
-          j \gets \LMKL(\sval) \\
-          \ucsend~(\uccmd{Sign},((P,j),\sid),\tx)~\text{to}~\IdealFSig \\
-          \ucrecv~(\uccmd{Signed},((P,j),\sid),\tx,\sig)~\text{from}~\IdealFSig \\
-          \ucsend~(\uccmd{Append},(\msg,\sig))~\text{to}~\IdealFaobb \\
+          \lbl \gets \LMKL(\sval) \\
+          \ucsend~(\uccmd{Sign},((P,\lbl),\sid),\tx)~\text{to}~\IdealFSig \\
+          \ucrecv~(\uccmd{Signed},((P,\lbl),\sid),\tx,\sig)~\text{from}~\IdealFSig \\
+          \ucsend~(\uccmd{Append},(\tx,\sig))~\text{to}~\IdealGdledger \\
+          \text{Locally store}~(\did,\sval) \\
           \ucio{Output}~(\uccmd{Updated},\sid,(\did,\lbrace \pk^a_i \rbrace_{i\in[n^a]}))
@@
         \procedure[linenumbering=on]{$\pcif \cmd = \uccmd{Deact} \land \arg =
-          (did, \lbrace \lbl_i \rbrace_{i\in[n]})$}{       
-          \text{Run as a \texttt{Update} operation}
+          (did, \sval)$}{       
+          \text{Run as a \texttt{Update} operation} \\
+          \text{with $\sval_d \gets \sval$ and $\sval_a \gets \emptyset$}
         }
@@
   \caption{\texttt{Update} and \texttt{Deactivate} operations in Atala
-    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealFPKIDID
-    in the $(\IdealFRO,\IdealFSig,\IdealFaobb)$-hybrid model.}
+    PRISM DID-based PKI protocol, \RealPKIDIDAtala, realising \IdealGPKIDID
+    in the $(\IdealGRO,\IdealFSig,\IdealGdledger)$-hybrid model.}
   \label{fig:atalapkidid2}
@@
 operations since it last synced. However, again the given simplified notion of
-a blockchain (via \IdealFaobb) eases notation -- and seems good enough for a
+a blockchain (via \IdealGdledger) eases notation -- and seems good enough for a
 first modelling effort.
@@
 
+\todo{Do we mention somewhere that {\sid}s have structure $(P,\sid')$? This is
+  used for \Sim to know which party is generating which keys.}
+
 \begin{theorem}[UC-security of \RealPKIDIDAtala]
   \label{thm:sec-didatala}
-  \RealPKIDIDAtala UC-realizes $\IdealFPKIDID^{\P_{Atala}}$ in the $(\IdealFRO,
-  \IdealFSig, \IdealFaobb)$-hybrid model.
+  \RealPKIDIDAtala UC-realizes $\IdealGPKIDID^{\P_{Atala}}$ in the $(\IdealGRO,
+  \IdealFSig, \IdealGdledger)$-hybrid model.
 \end{theorem}
@@
 \begin{proof}
-  We show that \RealPKIDIDAtala UC-realizes \IdealFPKIDID, when configured
+  We show that \RealPKIDIDAtala UC-realizes \IdealGPKIDID, when configured
   with policy $\P_{Atala}$. For this, we give a simulator \Sim such that, for
   any environment \Env, $\Exec_{\RealPKIDIDAtala\adv,\Env} \approx
-  \Exec_{\phiDIDAtala,\Sim,\Env}$,
-  where \phiDIDAtala is a protocol composed with the same parties as
+  \Exec_{\phiDID,\Sim,\Env}$,
+  where \phiDID is a protocol composed with the same parties as
   \RealPKIDIDAtala but where each party is simply a dummy party that forwards
-  every message from \Env to the ideal functionality \IdealFPKIDID, and every
-  response from \IdealFPKIDID back to \Env. The simulator \Sim runs internally a
+  every message from \Env to the ideal functionality \IdealGPKIDID, and every
+  response from \IdealGPKIDID back to \Env. The simulator \Sim runs internally a
   copy of the real-world adversary \adv, as well as the ideal functionalities
-  \IdealFRO, \IdealFSig and \IdealFaobb, and any involved party.
+  \IdealGRO, \IdealFSig and \IdealGdledger, and any involved party.
 
@@
     % 
-    % Policy check
-    First, note that \IdealFPKIDID is parameterised with $\P_{Atala}$. Thus,
-    if the input labels don't match the policy, the functionality rejects the
-    request, just as in the real protocol \RealPKIDIDAtala.
-    %
     % Keys generation
-    Next, when \Sim receives a message $(\uccmd{Create},\sid,\lbrace (\lbl_i,
-    \typ_i) \rbrace_{i\in[n]})$ from (dummy) party $P$, it simulates for \adv~
-    the key generation process of $n$ signing key pairs, by sending $n$
-    $(\uccmd{KeyGen},((P,\lbl_i),\sid))$ queries to \adv~on
-    behalf of \IdealFSig, and receiving the $n$ corresponding $(\uccmd{VerKey}, 
-    ((P,\lbl_i), \sid), \pk_i)$ responses.
+    If \Sim receives a message $(\uccmd{Create},\sid,\lbrace (\lbl_i,\typ_i)
+    \rbrace_{i\in[n]})$ from \IdealGPKIDID, with $\sid=(P,\sid')$, it simulates
+    the key generation process of $n$ signing key pairs run in the real
+    protocol, by sending $n$ queries $(\uccmd{KeyGen},((P,\lbl_i),\sid))$ to
+    \adv~on behalf of \IdealFSig, and receiving the $n$ corresponding
+    $(\uccmd{VerKey},((P,\lbl_i),\sid),\pk_i)$ responses.
     %
@@
     \Sim then concatenates all $(\lbl_i,\typ_i,\pk_i)$ tuples into \st, and
-    simulates a query to \IdealFRO \todo{do we need programmability or
-      something?}, to set \did as ``$did:prism: h$'' as DID value.
+    simulates a query to \IdealGRO, to set \did as ``$did:prism: h$'' as DID
+    value.
     %
@@
     With the DID value, \Sim simulates for \adv~the preparation of transaction
-    \tx. That is, \Sim uses the master key with lowest label, $j \gets
-    \LMKL(\st)$, and simulates a query $(\uccmd{Sign},((P,j),\sid),\tx)$ to
-    \IdealFSig, obtaining from \adv~$(\uccmd{Signed},((P,j),\sid),\tx,\sig)$.
+    \tx. That is, \Sim uses the master key with lowest label, $\lbl \gets
+    \LMKL(\st)$, and simulates a query $(\uccmd{Sign},((P,\lbl),\sid),\tx)$ to
+    \IdealFSig, obtaining from \adv~$(\uccmd{Signed},((P,\lbl),\sid),\tx,\sig)$.
     %
@@
     \Sim also simulates appending the $(\tx,\sig)$ tuple to the bulletin board,
-    by sending $(\uccmd{Append},(\tx,\sig))$ to \adv~on behalf of \IdealFaobb.
+    by sending $(\uccmd{Append},(\tx,\sig))$ to \adv~on behalf of \IdealGdledger.
     %
@@
     Finally, \Sim sends the $(\uccmd{CreateOk},\sid,\did,\lbrace \pk_i
-    \rbrace_{i\in[n]})$ to \IdealFPKIDID, and stores the tuple $(\did,\lbrace
+    \rbrace_{i\in[n]})$ to \IdealGPKIDID, and stores the tuple $(P,\did,\lbrace
     (\lbl_i,\typ_i,\pk_i)\rbrace_{i\in[n]})$.
+    %
+    % Additional considerations
+    \todo{The following should probably go to the argumentation part.}
     Note that \did is generated by an ideal random oracle (thus, uniformly at
     random), just as in the real protocol \RealPKIDIDAtala. Hence, the
-    probability that \IdealFPKIDID halts because $\did \in \DID$ is negligible,
-    and \IdealFPKIDID outputs $(\uccmd{Created},\sid,\did,\lbrace \val_i
-    \rbrace_{i\in[n]})$.
+    probability that \IdealGPKIDID halts because $\did \in \DID$ is negligible,
+    and \IdealGPKIDID outputs $(\uccmd{Created},\sid,\did,\lbrace \val_i=\pk_i
+    \rbrace_{i\in[n]})$ to \IdealGPKIDID.
   \item[Simulating DID Read.]
+    To simulate read operations, when \Sim receives $(\uccmd{Read},\sid,\did)$
+    from \IdealGPKIDID, it first simulates for \adv~the call to \IdealGdledger, to
+    get the current status $L$ of the bulletin board. Then, \Sim reproduces the
+    processing a normal party would do: from older to newer entry in $L$ related
+    to \did, applies the updates in a sequential order -- ignoring any
+    \uccmd{UpdateDID} operation before a \uccmd{CreateDID}, and only applying
+    the first \uccmd{CreateDID}. If, after applying an update, $\P_{Atala}$ is
+    not met by the resulting set of keys and labels, \Sim skips the update.
+    Otherwise, \Sim simulates for \adv~a verification query to \IdealFSig for
+    the transaction corresponding to the update, and skips the update if the
+    signature fails.
     %
-    % Ack
-    Upon receiving $(\uccmd{Read},\sid,\did)$ from dummy party P, \Sim simply
-    forwards the message to \adv and waits until receiving the response, which
-    is forwareded back to P.
-    %
-    % Consistent and indistinguishable results
-    Now, we show that the value returned by \IdealFPKIDID is indistinguishable
-    to that of \RealPKIDIDAtala. \todo{Do after Update.}
+    Finally, if after processing all transactions related to \did, the resulting
+    contents differ from those stored by \Sim in its record $(P,\did,\sval)$,
+    \Sim aborts \todo{Do we need this?}. Otherwise, \Sim returns the processed
+    contents.    
   \item[Simulating DID Update.]
-    % 
-    % Policy check
-    First, note that \IdealFPKIDID is parameterised with $\P_{Atala}$. Thus,
-    if the input labels don't match the policy, the functionality rejects the
-    request, just as in the real protocol \RealPKIDIDAtala.
-    % 
-    % Read if needed
-    First, \Sim finds in its records the entry $(\did,\lbrace (i,\lbl_i,\pk_i)
-    \rbrace_{i\in[n]})$. If no such \did exists, aborts.
-    %
-    % Simulate generation of new keys
-    Then, \Sim parses the $\lbrace(i,\lbl_i)\rbrace_{i\in\tilde{N}\subseteq
-      [\tilde{n}]}$ for new indexes, and simulates for \adv~one call to the
-    $\uccmd{KeyGen}$ interface of \IdealFSig for each new key, and composes the
-    variable $\st_{add}$ as in the real protocol. Similarly, \Sim initializes
-    variable $\st_{del}$ by looking for indexes in $[n]$ no longer present in
-    $\tilde{N}$.
-    %
-    % Simulate transaction
-    Finally, \Sim prepares the transaction \tx as in the real protocol using
-    variables $\st_{add}$ and $\st_{del}$. For this, a \uccmd{Sign} request is
-    sent to \IdealFSig, and an \uccmd{Append} request is sent to \IdealFaobb.
-    \Sim sends the resulting $(\uccmd{UpdateOK},\sid,\lbrace (i,\pk_i)
-    \rbrace_{i\in[\tilde{N}]})$ back to \IdealFPKIDID.
-    %
-    % Indistinguishability
-    Note that, if \Sim does not abort, then a valid $(P,\did,\sval)$ entry must
-    exist in the \DID state variable of \IdealFPKIDID. Thus, \IdealFPKIDID does
-    not abort in line 6. Then, \IdealFPKIDID
+    % Load DID
+    Upon receiving a request from dummy party $P$, \IdealGPKIDID fetches
+    $(P,\did,\sval)$ from its records, and checks if $(\sval \setminus \sval_d)
+    \cup \sval_a$ meets $\P_{Atala}$. If either step fails, \IdealGPKIDID
+    aborts. Else, it sends $(\uccmd{Update},\sid,\did,\sval_d,\sval_a)$ to \Sim.
+    \Sim then retrieves $(P,\did,\sval)$ from its records \todo{this is kept at
+      some point, no?)} and simulates for \adv~the calls to \IdealFSig for the
+    keys in the received $\sval_a$. \Sim gets the key with the lowest label from
+    \sval, with label $\lbl$, bundles the transaction \tx, and simulates a call
+    to \IdealFSig to get a signature over \tx. Finally, \Sim simulates the call
+    to \IdealGdledger, and returns $(\uccmd{Updated},\sid,(\did,\lbrace \val_i
+    \rbrace_{i\in[n_a]}))$ to \IdealGPKIDID, where the $\val_i$'s are the values
+    output by \adv~when creating the new keys via simulated calls to \IdealFSig.
   \item[Simulating DID Deactivate.] Directly follows from DID Update.      
   \end{description}
+  \todo{This to take into account when arguing indistinguishability}:
+  \begin{itemize}
+  \item The records of \Sim are always consistent with \IdealGdledger.
+  \end{itemize}
+
+  % General comments
+  Now, observe that, in all ideal operations, the policy $\P_{Atala}$ is checked
+  on the resulting data structure. If the policy is not satisfied, the
+  functionality aborts. This is also the case for the real world.
+
+  % Create comments
+  Regarding create operations, note that, both in the simulation and in the real
+  world, the resulting \did value is produced in a consistent way -- via a call
+  to \IdealGRO, using the contents of the DID document to create.
+  % Key generation and signature comments
+  Similarly, the (verification) keys used and signatures are defined by \adv~
+  both the real and ideal world -- in the latter, as part of \Sim's simulation
+  of \IdealFSig.
+
 \end{proof}

### 2022-12-03 prism-backend/research/prism-protocol/preliminaries.tex
Rewrote ideal functionality using global subroutines.

@@
 % Maybe build on \IdealFCA from \cite{canetti03}.
+
+\paragraph{Ideal functionality specification.} %
+
+\iffalse
+We take the basic approach to see DID documents as simple dictionaries
+(i.e., lists of labels with corresponding types and values), associated to a
+common label, the DID. Based on this, we define the operations that compose an
+ideal basic functionality for DIDs, as follows:
+
+\begin{description}
+\item[Create interface.] To create a new DID, the functionality exposes a
+  \uccmd{Create} interface that receives a tuple of label and key type values.
+  Then, it asks the adversary to provide a value to each of the specified
+  labels, and the DID value. If the DID value does not exist in the records of
+  the functionality, a new entry (including the dictionary) is created. In order
+  to meet the authentication requirement, the ideal functionality takes note of
+  the party creating the DID, so that subsequent changes in the DID can only be
+  done by this party. We note that more advanced predicates could be defined, by
+  this bare minimum seems to be enough for most (current) DID methods.
+  \todo{Give evidence of the latter?}
+\item[Read interface.] The contents of existing DIDs can be fetched via the
+  \uccmd{Read} interface. It receives a DID value and, if it exists in the
+  functionality's records, returns the associated contents. Note that, if such
+  entry exists, then it is authentic by definition, and thus trivially meets
+  the authentication requirements.
+\item[Update interface.] The contents of existing DIDs can be modified via the
+  \uccmd{Update} interface. It requires to specify the actual DID and two lists:
+  $\sval_d$ with the labels to remove, and $\sval_a$ with the lables of new keys
+  to add (along with their types). The DID must exist in the records of the
+  functionality, and the call must originate from the same party that created
+  it. Note that this covers variants such as using update only to add new keys
+  (e.g. by specifying an empty $\sval_d$), or modifications of existing labels
+  (e.g., by adding an existing label in $\sval_d$, and also in $\sval_a$).
+\item[Deactivate interface.] Deactivating a DID is actually a simplification of
+  the update operation, without specifying new keys to add. This is possible
+  via the \uccmd{Deact} interface. Note that it is not strictly necessary to
+  specify this interface, as it is a special case of \uccmd{Update}. However, we
+  explicitly add it for proximity to the actual DID specification. \todo{Just
+    remove it?}
+\end{description}
+
+Our expectation is that this simple approach allows to capture a large
+subset of all possible DID method implementations. Note that the functional
+restrictions we impose seem to be unavoidable. Namely, we do not specify how
+the actual identifiers are computed; instead, we allow the adversary to pick
+them. To update a DID, we only require such DID to exist and that the caller
+is the party that created it, but otherwise the DID's contents can be set to
+something completely new. Finally, deactivating labels within an existing DID
+requires that these labels exist -- and, again, that the caller is the same
+party who created the DID. Concretely, note that any further structure beyond
+the label-type-value dictionary approach, is left as an implementation detail.
+However, enforcing additional structure seems unavoidable in practice (e.g.,
+requiring that all DIDs include keys of certain type). Since this definitely
+has an impact on the behaviour of the ideal functionality, we parameterize it
+with a policy \P, which can be used as a black box: the functionality invokes
+\P with a set of labels and key types, and receives either $1$ to denote
+acceptance, or $0$ to denote rejection. However, it is not realistic to assume
+that, even corrupted parties will enforce such policies. Thus, our approach is
+to defer policy checking in the ideal functionality until after having
+interacted with the simulator \Sim. Intuitively then, if the output of the
+ideal functionality along with \Sim is indistinguishable to that of the real
+protocol with any real world adversary, then the policy is correctly enforced
+by the real protocol. Looking ahead, the real protocol in turn ``delegates''
+this policy-checking to an ideal append-only bulletin board. \todo{This captures
+  the idea, but refine and re-structure.}
+
+Note that we also allow the adversary to pick the values associated to the
+labels in new and updated DIDs. This is a strong requirement that follows the
+argumentation in \cite{canetti03} for ideal digital signatures: namely, this
+means that there is absolutely any requirement on the way in which this values
+are computed (they might not even be conventional public keys). Indeed, this
+seems to match the permissive philosophy of defining DIDs in the W3C DID
+specification.
+
+We capture the resulting notion in \figref{fig:fpkidid}.
+
+\begin{figure}
+  \begin{framed}
+    \scalebox{0.9}{
+      \begin{minipage}[t]{\textwidth}
+        \textrm{Upon receiving a call $\IdealFPKIDID^{\P}(\cmd,\sid,\arg)$
+          from some party $P$ to run command \cmd, in session \sid, with arguments
+          \arg, $\IdealFPKIDID^{\P}$ operates as follows.}
+        \textrm{If the received \cmd and \arg pair does not meet any of
+          the following options, the request is ignored.}
+        \textrm{\P is a boolean predicate defining concrete conditions for
+          acceptable DID creations, updates and deactivations.
+        }
+        \textrm{\todo{We assume that the functionality keeps track of the
+            received requests.}}
+      \end{minipage}
+    }
+    \vspace*{0.5em}
+
+    \scalebox{0.9}{
+      \begin{minipage}[t]{0.55\textwidth}
+        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \arg =
+          \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}$}{
+          \pcif \P(\lbrace (\lbl_i, \typ_i) \rbrace_{i\in[n]}) = 0:
+          \text{abort} \\                    
+          \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\Sim \\
+          \ucrecv~(\uccmd{CreateOk}, \sid, \did,
+          \sval=\lbrace \val_i \rbrace_{i\in[n]}) \\
+          \hspace*{2.8em}\text{from}~\Sim \\
+          \pcif (\cdot,\did,\cdot) \notin \DID: \\
+          \pcind \DID \gets \DID \cup \lbrace (P,\did,\lbrace
+          (\lbl_i,\typ_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
+          \ucio{Output}~(\uccmd{Created},\sid,\did,\sval)
+        }
+      \end{minipage}
+    }
+    \scalebox{0.9}{
+      \begin{minipage}[t]{0.5\textwidth}
+        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
+          \arg = did$}{
+          \ucsend~(\uccmd{Read},\sid,\arg)~\text{to}~\Sim \\
+          \ucrecv~(\uccmd{ReadOk},\sid)~\text{from}~\Sim \\          
+          \pcif (\cdot,did,\sval) \notin \DID: abort \\
+          \pcif \P(\sval) = 0: abort \\
+          \ucio{Output}~(\uccmd{Read},\sid,(did,\sval))~\text{to}~P
+        }    
+      \end{minipage}
+    }
+    \vspace*{0.25em} \\
+    \scalebox{0.9}{
+      \begin{minipage}[t]{0.55\textwidth}
+        % \arg = (did, \sval= \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]})\$}{
+        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
+          \arg = (did, \sval_d,\sval_a)$}{          
+          % \sval_{del} \gets \sval_0 \setminus \sval;
+          % \sval_{add} \gets \sval \setminus \sval_{del} \\          
+          % n'' \gets |\sval_{add}| \\
+          \pcif (P,\did,\sval_0) \notin \DID: \text{abort} \\
+          \pcif \P((\sval \setminus \sval_d) \cup \sval_a) = 0: \text{abort} \\
+          \ucsend~(\uccmd{Update}, \sid,\did,\sval_d,\sval_a)~\text{to}~\Sim \\
+          \ucrecv~(\uccmd{UpdtOk},\sid,\did,\lbrace \val^a_i \rbrace_{i\in[n^a]})~
+          \text{from}~\Sim \\
+          \lbrace (\lbl_i^a,\typ_i^a) \rbrace_{i\in[n^a]} \gets \sval_a;~
+          \lbrace \lbl_i^d \rbrace_{i\in[n^d]} \gets \sval_d \\          
+          \sval_1 \gets (\sval_0 \setminus \sval_d) \cup
+          \lbrace (\lbl^a_i,\typ^a_i,\val^a_i) \rbrace_{i\in[n^a]} \\          
+          \DID \gets \DID \setminus \lbrace (P,\did,\sval_0) \rbrace \cup
+          \lbrace (P, \did, \sval_1) \rbrace \\
+          \ucio{Output}~(\uccmd{Updated},\sid, (\did,\lbrace \val_a \rbrace_{i\in[n^a]}))
+        }
+      \end{minipage}
+    }
+    \scalebox{0.9}{
+      \begin{minipage}[t]{0.5\textwidth}
+        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \arg =
+          (did, \lbrace \lbl_i \rbrace_{i\in[n]})$}{          
+          \pcif (P,did,\sval_0) \notin \DID: abort \\
+          \sval_1 \gets \sval_0 \setminus \lbrace \lbl_i \rbrace_{i\in[n]} \\
+          \pcif \P(\sval_1) = 0: abort \\
+          \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\Sim \\
+          \ucrecv~(\uccmd{DeactOk},\sid)~\text{from}~\Sim \\          
+          \pcind \DID \gets \DID \setminus \lbrace(P,did,\sval_0)\rbrace~\cup \\
+          \hspace*{7em}\lbrace (P,did,\sval_1) \rbrace \\
+          \ucio{Output}~(\uccmd{Deacted},\sid,\did)
+        }
+      \end{minipage}
+    }
+  \end{framed}
+  \caption{Ideal PKI functionality, \IdealFPKI. We abuse set
+    notation, and write $\lbrace (a_i,\dots) \rbrace_{i\in[n]} \setminus
+    \lbrace (b_j,\dots) \rbrace_{j\in[m]}$ to mean subtracting from the first
+    set the elements present in the second set, whenever $a_i = b_j$ for some
+    $i,j$, even if the size of the $(a_i,\dots)$ and $(b_j,\dots)$ tuples do not
+    match.}
+  \label{fig:fpki}
+\end{figure}
+\fi
 

### 2022-12-16 prism-backend/research/prism-protocol/did_atala.tex
Rewrote ideal functionality using global subroutines.
Commiting before applying more changes. Forgot what I did here...

@@
           operations, and \DID is the authoritative state of published DIDs.}
+        \todo{Think about what happens if two conflicting ops (esp. create)
+          are submitted with diff $t < \delta$.}
+        \todo{Idea: func keeps track of DID ownership, associated to parties.
+          Also, replace \didOP with an UTXO, that gets updated like the delay
+          ledger (i.e., upon applying a new op, remove it from the set.)}
       \end{minipage}
@@
           \setind{(\lbl_i,\typ_i)}{i\in[n]}$}{ 
-          \DID \gets \DIDReadLdg \\
-          \pcif (\did,\cdot) \in \DID \lor
-          \P(\setind{(\lbl_i,\typ_i)}{i\in[n]}) = 0: \\
-          \pcind \pcreturn \bot \\
+          %\DID \gets \DIDReadLdg \\          
           \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\Sim \\
@@
           \hspace*{2.7em}\text{from}~\Sim \\
+          % \pcif (\did,\cdot) \in \DID \lor
+          % \P(\setind{(\lbl_i,\typ_i)}{i\in[n]}) = 0: \\
+          % \pcind \pcreturn \bot \\
           \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock \\
@@
         }
-      \end{minipage}
-    }
-    \scalebox{0.9}{
-      \begin{minipage}[t]{0.5\textwidth}
-        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
-          \arg = \did$}{
-          \DID \gets \DIDReadLdg \\
-          \pcif (\did,\sval) \notin \DID \lor \P(\sval) = 0: \\
-          \pcind \pcreturn \bot \\
-          \ucio{Output}~(\uccmd{ReadOk},\sid,\did,\sval)~\text{to}~P
-        }    
-      \end{minipage}
-    }
         \vspace*{0.25em} \\
-    \scalebox{0.9}{
-      \begin{minipage}[t]{0.55\textwidth}
-        % \arg = (did, \sval= \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]})\$}{
+
         \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
@@
           \DID \gets \DIDReadLdg \\
-          \pcif (\did,\sval_0) \notin \DID: \pcreturn \bot \\
-          \pcif \P((\sval_0 \setminus \sval_d) \cup \sval_a) = 0:
-          \pcreturn \bot \\
+          \pcif (P,\did) \notin \didOWN: \pcreturn \bot \\
+          \pcif (\did,\sval_0) \notin \DID: \pcreturn \bot \\ %\lor (P,\cdot,(\did,\cdot))
+          % \notin \didOP: \\
+          % \pcind \pcreturn \bot \\
+          % \pcif \P((\sval_0 \setminus \sval_d) \cup \sval_a) = 0:
+          % \pcreturn \bot \\
           \ucsend~(\uccmd{Update}, \sid,\did,\sval_d,\sval_a)~\text{to}~\Sim \\
-          \ucrecv~(\uccmd{UpdOk},\sid,\did,\lbrace \val^a_i \rbrace_{i\in[n^a]})~
+          \ucrecv~(\uccmd{UpdOk},\sid,\did,\setind{\val^a_i}{i\in[n^a]})~
           \text{from}~\Sim \\
@@
           \lbrace (\lbl_i^a,\typ_i^a) \rbrace_{i\in[n^a]} \gets \sval_a \\
-          %\lbrace \lbl_i^d \rbrace_{i\in[n^d]} \gets \sval_d \\          
+          % \lbrace \lbl_i^d \rbrace_{i\in[n^d]} \gets \sval_d \\          
           \sval_1 \gets (\sval_0 \setminus \sval_d) \cup
@@
       \begin{minipage}[t]{0.5\textwidth}
+        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
+          \arg = \did$}{
+          \DID \gets \DIDReadLdg \\
+          \pcif (\did,\sval) \notin \DID: \pcreturn \bot \\ % \lor \P(\sval) = 0: \\
+          %\pcind \pcreturn \bot \\
+          \ucio{Output}~(\uccmd{ReadOk},\sid,\did,\sval)~\text{to}~P
+        }
+        \vspace*{0.25em} \\
+
         \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \arg =
@@
           \DID \gets \DIDReadLdg \\
-          \pcif (P,did,\sval_0) \notin \DID: \pcreturn \bot \\
+          \pcif (P,\did) \notin \didOWN: \pcreturn \bot \\                    
+          \pcif (P,did,\sval_0) \notin \DID: \pcreturn \bot \\ % \lor (P,\cdot,(\did,\cdot))
+          % \notin \didOP: \\
+          % \pcind \pcreturn \bot \\
           \sval_1 \gets \sval_0 \setminus \lbrace \lbl_i \rbrace_{i\in[n]} \\
-          \pcif \P(\sval_1) = 0: \pcreturn \bot \\
+          % \pcif \P(\sval_1) = 0: \pcreturn \bot \\
           \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\Sim \\
@@
         }
+%        \vspace*{0.05em} \\
+
+        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Extend} \land \arg =
+          \didOP'$}{
+          \pcif P \neq \Sim \lor \didOP' \subseteq \didOP: \pcreturn \bot \\
+          \DID \gets \DIDReadLdg \\          
+          %\lor~\\
+          %\pcind \exists \didOp \in \didOP'~\suchthat~\P(\didOp) = 0: \\
+          %\pcind \pcreturn \bot \\
+          \pcfor \didOp = (P,\cdot,(\did,\cdot)) \in \didOP': \\
+          \pcind \pcif \P(\didOp,\DID) = 0: \pcreturn \bot \\
+          \pcind \didOWN \gets (P,\did) \\
+          \didOP \gets \didOP \setminus \didOP' \\
+          \ucsend~(\uccmd{Extend},\didOP')~\text{to}~\IdealGledger
+        }
       \end{minipage}
@@
     \vspace*{0.25em} \\
+
     \scalebox{0.9}{

### 2022-12-16 prism-backend/research/prism-protocol/did_atala.tex
New and more generic definition of a global PKI.

--- 2022-12-03 prism-backend/research/prism-protocol/did_atala.tex
@@
 
-\subsection{Base Functionalities}
-\label{ssec:did-funcs}
-
-\todo{Mention public delayed outputs.}
-\todo{If the functionalities try to fetch some entry from a list, and the entry
-  does not exist, then it aborts (assumed for updates).}
-
-\paragraph{Hashes.} %
-We model hashes as a global subroutine. No participant needs extra power (such
-as programmability or observability), so we use a conventional random oracle --
-called strict random oracle in \cite{cdg+18}. For self-containment, we reproduce
-here the formulation.
-
-\begin{figure}[ht]
-  \begin{framed}
-    \begin{minipage}[t]{\textwidth}
-      \textrm{Upon receiving a call $\IdealGRO(\cmd,\sid,\arg)$ from some party
-        $P$ to run command \cmd, in session \sid, with arguments \arg,
-        \IdealGRO operates as follows.} \\
-      \textrm{\IdealGRO keeps a list \hashlist of known hashed messages, and
-        outputs hashes of length $l \gets l(n)$, for some fixed security
-        parameter $n$.}
-    \end{minipage}
-    \vspace*{0.5em}
-
-    \centering
-    \procedure{$\pcif \cmd = \uccmd{HashQuery} \land \arg = \msg$}{%
-      \pcif (\msg,h) \notin \hashlist:
-      h \getr \bin^{l}; \hashlist \gets \hashlist \cup \lbrace (\msg,h) \rbrace \\
-      \ucio{Output}~(\uccmd{HashConfirm},h)
-    }
-  \end{framed}
-\end{figure}
-
-\paragraph{Global clock.} %
-Our ideal (global) functionality for a ledger relies on a global clock to model
-delays in appending information. We rely on the ideal global clock functionality
-given in \cite{kkk21}. In a nutshell, the functionality keeps track of the
-parties in the system, and allows them to signal their intention to advance the
-clock's time. When all parties agree on it, the clock's time is incremented. See
-\figref{fig:gclock}.
-
-\begin{figure}[ht]
-  \begin{framed}
-    \begin{minipage}[t]{\textwidth}
-      \textrm{Upon receiving a call $\IdealGclock(\cmd,\arg)$ from
-        some party $P$ to run command \cmd, with arguments \arg,
-        \IdealGclock operates as follows.} \\
-      \textrm{\IdealGclock maintains a variable $t$ with the current itme,
-        a variable $T$ with the list of parties keeping track of the time,
-        and a map $A$ which keeps the parties' (dis)agreements to advance the
-        clock.}
-    \end{minipage}
-    \vspace*{0.5em}
-
-    \begin{minipage}[t]{0.40\textwidth}
-      \procedure{$\pcif \cmd = \uccmd{Register} \land \arg = \emptyset$}{
-        T \gets T \cup \set{P} \\
-        \ucio{Output}~(\uccmd{Registered})~\text{to}~P \\
-      }
-      \procedure{$\pcif \cmd = \uccmd{Update} \land \arg = \emptyset$}{
-        A(P) \gets \top \\
-        \pcif \forall P \in T, A(P) = \top: \\
-        \pcind t \gets t + 1; \forall P \in T, A(P) = \bot \\
-        \pcind \ucio{Send}~(\uccmd{Updated})~\text{to}~P        
-      }
-    \end{minipage}
-    \hspace*{1.25em}
-    \begin{minipage}[t]{0.60\textwidth}
-      \procedure{$\pcif \cmd = \uccmd{Deregister} \land \arg = \emptyset$}{
-        T \gets T \setminus \set{P} \\
-        \text{Output}~(\uccmd{DeregisteredOk})~\text{to}~P \\
-      }
-      \procedure{$\pcif \cmd = \uccmd{Read} \land \arg = \emptyset$}{
-        \text{Output}~(\uccmd{ReadOk},t)~\text{to}~P
-      }
-    \end{minipage}
-  \end{framed}
-  \caption{Ideal subroutine for a global clock, from \cite{kkk21}.}
-  \label{fig:gclock}
-\end{figure}
-
-\paragraph{$\delta$-delay Ledger.} %
-We adopt a ledger notion given in \cite{kkk21}. This is global functionality
-that defines an ideal version of a ledger as a shared subroutine, which models
-the append-only property of ledgers, and the fact that changes take some delay
-until they are applied to the ledger.
-%
-This functionality accepts sending individual transactions to be added to the
-ledger state, fetching (reading) the state of the ledger, and extending the
-ledger by appending (blocks of) transactions to it. Interestingly, it gives the
-adversary control over when to advance the status of each party, as long as
-these advancements ensure the common prefix rule -- where $\ldgState' \prec
-\ldgState$ means that $\ldgState'$ is a prefix of \ldgState. It also relies
-on yet another global functionality, the global clock, to timestamp incoming
-transactions. If a transaction is not appended to an honest party's view before
-the given $\delta$ delay, then the functionality aborts.
-%
-For the sake of readability, we reproduce the functionality in
-\figref{fig:gledger}.
-
-\begin{figure}[ht]
-  \begin{framed}
-    \begin{minipage}[t]{\textwidth}
-      \textrm{Upon receiving a call $\IdealGdledger(\cmd,\arg)$ from
-        some party $P$ to run command \cmd, with arguments \arg,
-        \IdealGdledger operates as follows.} \\
-      \textrm{\IdealGdledger maintains a mapping \ldgMap which associates
-        parties with their view of the ledger.
-        \ldgUtxo is a multiset of unconfirmed transactions.
-        \ldgState is the authoritative ledger state
-        All mappings and (multi-)sets are initialised to empty values.
-      }
-    \end{minipage}
-    \vspace*{0.5em}
-
-    \begin{minipage}[t]{0.40\textwidth}
-      \procedure{$\pcif \cmd = \uccmd{Submit} \land \arg = \ldgTx$}{
-        \ucio{Send}~(\uccmd{Read})~\text{to}~\IdealGclock \\
-        \ucio{Recv}~(\uccmd{ReadOk},t)~\text{from}~\IdealGclock \\
-        \ldgUtxo \gets \ldgUtxo \cup \set{(\ldgTx,t)} \\ 
-        \ucio{Output}~(\uccmd{Transaction},\ldgTx,t)~\text{to}~\adv \\
-      }
-      \procedure{$\pcif \cmd = \uccmd{Extend} \land \arg = \ldgState'$}{
-        \pcif P = \adv \land \ldgState' \subseteq \ldgUtxo: \\
-        \pcind \ldgUtxo \gets \ldgUtxo \setminus \ldgState' \\
-        \pcind \ldgState \gets \ldgState || \ldgState'
-      }
-    \end{minipage}
-    \hspace*{1.25em}
-    \begin{minipage}[t]{0.60\textwidth}
-      \procedure{$\pcif \cmd = \uccmd{Read} \land \arg =
-        \emptyset$}{
-        % \pcif P = \adv: data \gets \ldgState \\
-        % \pcelse: data \gets \ldgMap(P) \\
-        \ucio{Send}~(\uccmd{Read})~\text{to}~\IdealGclock \\
-        \ucio{Recv}~(\uccmd{ReadOk},t)~\text{from}~\IdealGclock \\
-        \pcif \exists (\ldgTx,t') \in \ldgUtxo~\suchthat~|t-t'| > \delta:
-        \pcreturn \bot \\
-        \pcelse \pcif \exists (\ldgTx,t') \in \ldgState~\suchthat~ |t-t'|
-        > \delta~\land \\
-        \pcind \exists P' \in \ldgHonest~\suchthat~(\ldgTx,t') \notin \ldgMap(P'):
-        \pcreturn \bot \\        
-        \text{Output}~(\uccmd{ReadOk}, \ldgHead(\ldgMap(P)))~\text{to}~P \\
-      }
-      \procedure{$\pcif \cmd = \uccmd{Advance} \land \arg = (P',\ldgState')$}{
-        \pcif P = \adv \land \ldgMap(P') \prec \ldgState' \prec \ldgState:
-        \ldgMap(P') \gets \ldgState'
-      }
-    \end{minipage}
-  \end{framed}
-  \caption{Ideal subroutine for a global $\delta$-delay ledger, from
-    \cite{kkk21}.}
-  \label{fig:gledger}
-\end{figure}
-
-\paragraph{Digital Signatures.} %
-
-\begin{figure}
-  \begin{framed}
-    \begin{minipage}[t]{\textwidth}
-      \textrm{Upon receiving a call $\IdealFSig(\cmd,\sid,\arg)$ from some party
-        $P$ to run command \cmd, in session \sid, with arguments \arg,
-        \IdealFSig operates as follows.} \\
-      \textrm{\IdealFSig keeps a list \SIG of known signed messages.}      
-    \end{minipage}
-    \vspace*{0.5em}
-
-    \begin{minipage}[t]{0.5\textwidth}
-      \procedure{$\pcif \cmd = \uccmd{KeyGen} \land \arg =
-        \emptyset$}{
-        \pccomment{\fbox{Key Generation}} \\
-        \pcif \sid = (P,\ssid): \\
-        \pcind \ucsend~(\uccmd{KeyGen},\sid)~\text{to}~\adv \\
-        \pcind \ucrecv~(\uccmd{VerKey},\sid,v)~\text{from}~\adv \\
-        \pcind \ucio{Output}~(\uccmd{VerKey},\sid,v)~\text{to}~P \\
-        \pcind \text{Store}~(P,v)
-      }
-      \vspace*{0.25em}
-      \procedure{$\pcif \cmd = \uccmd{Verif} \land
-        \arg = (\sig,\msg,v')$}{
-        \pccomment{\fbox{Verify a message}} \\
-        \ucsend~(\uccmd{Verif},\sid,\msg,\sig,v)~\text{to}~\adv \\
-        \ucrecv~(\uccmd{Verifd},\sid,\msg,\phi)~\text{from}~\adv \\
-        \pcif v' = v \land (\msg,\sig,v,1) \in \SIG: f \gets 1 \\
-        \pcelse \pcif v' = v \land P~\text{is not corrupt}~\land \\
-        \pcind (\msg,\sig',v,1) \notin \SIG: \\
-        \pcind \SIG \gets \SIG \cup \lbrace (\msg,\sig,v,0) \rbrace;
-        f \gets 0 \\
-        \pcelse \pcif (\msg,\sig,v',f') \in \SIG: f \gets f' \\
-        \pcelse: \\
-        \pcind \SIG \gets \SIG \cup \lbrace (\msg,\sig,v',\phi) \rbrace;~
-        f \gets \phi \\
-        \ucio{Output}~(\uccmd{Verifd},\sid,\msg,f)
-      }
-    \end{minipage}
-    \begin{minipage}[t]{0.5\textwidth}
-      \procedure{$\pcif \cmd = \uccmd{Sign} \land \arg = \msg$}{
-        \pccomment{\fbox{Sign a message}} \\
-        \pcif \sid = (P,\ssid) \\
-        \pcind \ucsend~(\uccmd{Sign},\sid,\msg)~\text{to}~\adv \\
-        \pcind \ucrecv~(\uccmd{Signed},\sid,\msg,\sig)~\text{from}~
-        \adv \\
-        \pcind \pcif (\msg,\sig,v,0) \in \SIG: \\
-        \pcind \pcind \ucio{Output}~(\uccmd{Error}) \\
-        \pcind \pcelse: \\
-        \pcind \pcind \SIG \gets \SIG \cup (\msg,\sig,v,1) \\
-        \pcind \pcind \ucio{Output}~(\uccmd{Signed},\sid,\msg,\sig)
-      }
-    \end{minipage}
-  \end{framed}
-  \caption{Ideal signature functionality, \IdealFSig, from \cite{canetti03}.}
-  \label{fig:fsig}
-\end{figure}
-
 \subsection{Global Functionality \IdealGPKIDID}
-
-Giving an ideal functionality for a DID-based PKI does not seem to be direct.
-The difficulty stems from the fact that the W3C specification (see footnote
-\todo{X}) is very permissive in regards to what can be seen as a valid DID
-method definition. Namely, it simply states the following conditions for any
-candidate method, in Section 8.2 of the specification:
-
-\begin{description}
-\item[Authentication.] It must define how authorisation is performed.  
-\item[Create.] It must specify how controllers create new DIDs.
-\item[Read.] It must specify how the contents of a DID can be fetched and
-  authenticated.
-\item[Update.] It must specify what updates can controllers apply (if any)
-  to existing DIDs.
-\item[Deactivate.] It must specify if DIDs can be deactivated, and how.
-\end{description}
-
-Where the authentication aspect specifically covers the way in which controllers
-prove to be entitled to perform create, update, or deactivate operations.
-
-However, since no functional requirements are given as to, e.g., what an update
-may be, or what a deactivation implies, it seems hard to define a functionality
-that would cover all possible options (or a significant subset).
-
-\paragraph{Ideal functionality specification.} %
-We take the basic approach to see DID documents as simple dictionaries
-(i.e., lists of labels with corresponding types and values), associated to a
-common label, the DID. Based on this, we define the operations that compose an
-ideal basic functionality for DIDs, as follows:
-
-\begin{description}
-\item[Create interface.] To create a new DID, the functionality exposes a
-  \uccmd{Create} interface that receives a tuple of label and key type values.
-  Then, it asks the adversary to provide a value to each of the specified
-  labels, and the DID value. If the DID value does not exist in the records of
-  the functionality, a new entry (including the dictionary) is created. In order
-  to meet the authentication requirement, the ideal functionality takes note of
-  the party creating the DID, so that subsequent changes in the DID can only be
-  done by this party. We note that more advanced predicates could be defined, by
-  this bare minimum seems to be enough for most (current) DID methods.
-  \todo{Give evidence of the latter?}
-\item[Read interface.] The contents of existing DIDs can be fetched via the
-  \uccmd{Read} interface. It receives a DID value and, if it exists in the
-  functionality's records, returns the associated contents. Note that, if such
-  entry exists, then it is authentic by definition, and thus trivially meets
-  the authentication requirements.
-\item[Update interface.] The contents of existing DIDs can be modified via the
-  \uccmd{Update} interface. It requires to specify the actual DID and two lists:
-  $\sval_d$ with the labels to remove, and $\sval_a$ with the lables of new keys
-  to add (along with their types). The DID must exist in the records of the
-  functionality, and the call must originate from the same party that created
-  it. Note that this covers variants such as using update only to add new keys
-  (e.g. by specifying an empty $\sval_d$), or modifications of existing labels
-  (e.g., by adding an existing label in $\sval_d$, and also in $\sval_a$).
-\item[Deactivate interface.] Deactivating a DID is actually a simplification of
-  the update operation, without specifying new keys to add. This is possible
-  via the \uccmd{Deact} interface. Note that it is not strictly necessary to
-  specify this interface, as it is a special case of \uccmd{Update}. However, we
-  explicitly add it for proximity to the actual DID specification. \todo{Just
-    remove it?}
-\end{description}
-
-Our expectation is that this simple approach allows to capture a large
-subset of all possible DID method implementations. Note that the functional
-restrictions we impose seem to be unavoidable. Namely, we do not specify how
-the actual identifiers are computed; instead, we allow the adversary to pick
-them. To update a DID, we only require such DID to exist and that the caller
-is the party that created it, but otherwise the DID's contents can be set to
-something completely new. Finally, deactivating labels within an existing DID
-requires that these labels exist -- and, again, that the caller is the same
-party who created the DID. Concretely, note that any further structure beyond
-the label-type-value dictionary approach, is left as an implementation detail.
-However, enforcing additional structure seems unavoidable in practice (e.g.,
-requiring that all DIDs include keys of certain type). Since this definitely
-has an impact on the behaviour of the ideal functionality, we parameterize it
-with a policy \P, which can be used as a black box: the functionality invokes
-\P with a set of labels and key types, and receives either $1$ to denote
-acceptance, or $0$ to denote rejection. However, it is not realistic to assume
-that, even corrupted parties will enforce such policies. Thus, our approach is
-to defer policy checking in the ideal functionality until after having
-interacted with the simulator \Sim. Intuitively then, if the output of the
-ideal functionality along with \Sim is indistinguishable to that of the real
-protocol with any real world adversary, then the policy is correctly enforced
-by the real protocol. Looking ahead, the real protocol in turn ``delegates''
-this policy-checking to an ideal append-only bulletin board. \todo{This captures
-  the idea, but refine and re-structure.}
-
-Note that we also allow the adversary to pick the values associated to the
-labels in new and updated DIDs. This is a strong requirement that follows the
-argumentation in \cite{canetti03} for ideal digital signatures: namely, this
-means that there is absolutely any requirement on the way in which this values
-are computed (they might not even be conventional public keys). Indeed, this
-seems to match the permissive philosophy of defining DIDs in the W3C DID
-specification.
-
-We capture the resulting notion in \figref{fig:fpkidid}.
-
-\begin{figure}
-  \begin{framed}
-    \scalebox{0.9}{
-      \begin{minipage}[t]{\textwidth}
-        \textrm{Upon receiving a call $\IdealGPKIDID^{\P}(\cmd,\sid,\arg)$
-          from some party $P$ to run command \cmd, in session \sid, with arguments
-          \arg, $\IdealGPKIDID^{\P}$ operates as follows.}
-        \textrm{If the received \cmd and \arg pair does not meet any of
-          the following options, the request is ignored.}
-        \textrm{\P is a boolean predicate defining concrete conditions for
-          acceptable DID creations, updates and deactivations.}
-        \textrm{\didOP is a list of submitted (yet, possibly unconfirmed) DID
-          operations, and \DID is the authoritative state of published DIDs.}
-      \end{minipage}
-    }
-    \vspace*{0.5em}
-
-    \scalebox{0.9}{
-      \begin{minipage}[t]{0.55\textwidth}
-        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \arg =
-          \setind{(\lbl_i,\typ_i)}{i\in[n]}$}{ 
-          \DID \gets \DIDReadLdg \\
-          \pcif (\did,\cdot) \in \DID \lor
-          \P(\setind{(\lbl_i,\typ_i)}{i\in[n]}) = 0: \\
-          \pcind \pcreturn \bot \\
-          \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\Sim \\
-          \ucrecv~(\uccmd{CreateOk}, \sid, \did,
-          \sval=\setind{\val_i}{i\in[n]}) \\
-          \hspace*{2.7em}\text{from}~\Sim \\          
-          \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock \\
-          \ucrecv~(\uccmd{ReadOk},\tau)~\text{from}~\IdealGclock \\
-          \didOp \gets (\did,\setind{(\lbl_i,\typ_i,\val_i)}{i\in[n]}) \\
-          \didOP \gets \didOP \cup \set{(P,\tau,\didOp)} \\
-          \ucsend~(\uccmd{Submit}, \didOp)~\text{to}~\IdealGdledger \\
-          \ucio{Output}~(\uccmd{ProcessedC},\sid,\did,\sval)
-          % \pcind \DID \gets \DID \cup \lbrace (P,\did,\lbrace
-          % (\lbl_i,\typ_i,\val_i) \rbrace_{i\in[n]}) \rbrace \\
-          % \ucio{Output}~(\uccmd{Created},\sid,\did,\sval,t)
-        }
-      \end{minipage}
-    }
-    \scalebox{0.9}{
-      \begin{minipage}[t]{0.5\textwidth}
-        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
-          \arg = \did$}{
-          \DID \gets \DIDReadLdg \\
-          \pcif (\did,\sval) \notin \DID \lor \P(\sval) = 0: \\
-          \pcind \pcreturn \bot \\
-          \ucio{Output}~(\uccmd{ReadOk},\sid,\did,\sval)~\text{to}~P
-        }    
-      \end{minipage}
-    }
-    \vspace*{0.25em} \\
-    \scalebox{0.9}{
-      \begin{minipage}[t]{0.55\textwidth}
-        % \arg = (did, \sval= \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]})\$}{
-        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
-          \arg = (did, \sval_d,\sval_a)$}{
-          \DID \gets \DIDReadLdg \\
-          \pcif (\did,\sval_0) \notin \DID: \pcreturn \bot \\
-          \pcif \P((\sval_0 \setminus \sval_d) \cup \sval_a) = 0:
-          \pcreturn \bot \\
-          \ucsend~(\uccmd{Update}, \sid,\did,\sval_d,\sval_a)~\text{to}~\Sim \\
-          \ucrecv~(\uccmd{UpdOk},\sid,\did,\lbrace \val^a_i \rbrace_{i\in[n^a]})~
-          \text{from}~\Sim \\
-          \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock \\
-          \ucrecv~(\uccmd{ReadOk},\tau)~\text{from}~\IdealGclock \\
-          \lbrace (\lbl_i^a,\typ_i^a) \rbrace_{i\in[n^a]} \gets \sval_a \\
-          %\lbrace \lbl_i^d \rbrace_{i\in[n^d]} \gets \sval_d \\          
-          \sval_1 \gets (\sval_0 \setminus \sval_d) \cup
-          \setind{(\lbl^a_i,\typ^a_i,\val^a_i)}{i\in[n^a]} \\
-          \didOp \gets (\did,\sval_1);~
-          \didOP \gets \didOP \cup \set{(P,\tau,\didOp)} \\
-          \ucsend~(\uccmd{Submit}, \didOp)~\text{to}~\IdealGdledger \\
-          \ucio{Output}~(\uccmd{ProcessedU},\sid,\did,\didOp)
-        }
-      \end{minipage}
-    }
-    \scalebox{0.9}{
-      \begin{minipage}[t]{0.5\textwidth}
-        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \arg =
-          (did, \lbrace \lbl_i \rbrace_{i\in[n]})$}{
-          \DID \gets \DIDReadLdg \\
-          \pcif (P,did,\sval_0) \notin \DID: \pcreturn \bot \\
-          \sval_1 \gets \sval_0 \setminus \lbrace \lbl_i \rbrace_{i\in[n]} \\
-          \pcif \P(\sval_1) = 0: \pcreturn \bot \\
-          \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\Sim \\
-          \ucrecv~(\uccmd{DeactOk},\sid)~\text{from}~\Sim \\
-          \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock \\
-          \ucrecv~(\uccmd{ReadOk},\tau)~\text{from}~\IdealGclock \\          
-          \didOp \gets (\did,\sval_1);
-          \didOP \gets \didOP \cup \set{(P,\tau,\didOp)} \\
-          \ucsend~(\uccmd{Submit},\didOp)~\text{to}~\IdealGdledger \\          
-          \ucio{Output}~(\uccmd{ProcessedD},\sid,\did,\didOp)
-        }
-      \end{minipage}
-    }
-    \vspace*{0.25em} \\
-    \scalebox{0.9}{
-      \begin{minipage}[t]{\textwidth}
-        \centering
-        \procedure[linenumbering]{$\DIDReadLdg$}{
-          \ucsend~(\uccmd{Read})~\text{to}~\IdealGdledger~\text{and recv}~
-          (\uccmd{ReadOk},\DID)~\text{back} \\
-          \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock ~\text{and recv}~
-          (\uccmd{ReadOk},\tau)~\text{back} \\
-          \pcif \exists (\cdot,\tau',\didOp) \in \didOP~\suchthat~
-          |\tau - \tau'| > \delta \land \P(\didOp) = 1 \land \didOp \notin \DID:
-          \pcreturn \bot \\
-          \pcreturn \DID
-        }
-      \end{minipage}
-    }
-  \end{framed}
-  \caption{Ideal DID-based PKI functionality, \IdealGPKIDID. We abuse set
-    notation, and write $\lbrace (a_i,\dots) \rbrace_{i\in[n]} \setminus
-    \lbrace (b_j,\dots) \rbrace_{j\in[m]}$ to mean subtracting from the first
-    set the elements present in the second set, whenever $a_i = b_j$ for some
-    $i,j$, even if the size of the $(a_i,\dots)$ and $(b_j,\dots)$ tuples do not
-    match.}
-  \label{fig:fpkidid}
-\end{figure}
 
@@
   \label{thm:sec-didatala}
-  \RealPKIDIDAtala UC-realizes $\IdealGPKIDID^{\P_{Atala}}$ in the $(\IdealGRO,
+  \RealPKIDIDAtala UC-realizes $\IdealGPKIDID$ in the $(\IdealGRO,
   \IdealFSig, \IdealGdledger)$-hybrid model.

### 2022-12-16 prism-backend/research/prism-protocol/preliminaries.tex
New and more generic definition of a global PKI.

@@
 
-\todo{Briefly describe algorithms they use.}
+% \todo{Briefly describe algorithms they use.}
 
-\paragraph{Append-Only Bulletin Boards.} %
-%\todo{For now, simplified notion as in \cite{acc+20}.}
+% \paragraph{Append-Only Bulletin Boards.} %
+% %\todo{For now, simplified notion as in \cite{acc+20}.}
+
+% \paragraph{Digital Signatures.} %
+% %Maybe build on \IdealFSig from \cite{canetti03}.
+
+% \paragraph{Merkle Trees.}
+
+% \paragraph{Public Key Infrastructures.} %
+% % Maybe build on \IdealFCA from \cite{canetti03}.
+
+% \subsection{Base Functionalities}
+% \label{ssec:did-funcs}
+
+\todo{Mention public delayed outputs.}
+\todo{If the functionalities try to fetch some entry from a list, and the entry
+  does not exist, then it aborts (assumed for updates).}
+
+\paragraph{Hashes.} %
+We model hashes as a global subroutine. No participant needs extra power (such
+as programmability or observability), so we use a conventional random oracle --
+called strict random oracle in \cite{cdg+18}. For self-containment, we reproduce
+here the formulation.
+
+\begin{figure}[ht]
+  \begin{framed}
+    \begin{minipage}[t]{\textwidth}
+      \textrm{Upon receiving a call $\IdealGRO(\cmd,\sid,\arg)$ from some party
+        $P$ to run command \cmd, in session \sid, with arguments \arg,
+        \IdealGRO operates as follows.} \\
+      \textrm{\IdealGRO keeps a list \hashlist of known hashed messages, and
+        outputs hashes of length $l \gets l(n)$, for some fixed security
+        parameter $n$.}
+    \end{minipage}
+    \vspace*{0.5em}
+
+    \centering
+    \procedure{$\pcif \cmd = \uccmd{HashQuery} \land \arg = \msg$}{%
+      \pcif (\msg,h) \notin \hashlist:
+      h \getr \bin^{l}; \hashlist \gets \hashlist \cup \lbrace (\msg,h) \rbrace \\
+      \ucio{Output}~(\uccmd{HashConfirm},h)
+    }
+  \end{framed}
+\end{figure}
+
+\paragraph{Global clock.} %
+Our ideal (global) functionality for a ledger relies on a global clock to model
+delays in appending information. We rely on the ideal global clock functionality
+given in \cite{kkk21}. In a nutshell, the functionality keeps track of the
+parties in the system, and allows them to signal their intention to advance the
+clock's time. When all parties agree on it, the clock's time is incremented. See
+\figref{fig:gclock}.
+
+\begin{figure}[ht]
+  \begin{framed}
+    \begin{minipage}[t]{\textwidth}
+      \textrm{Upon receiving a call $\IdealGclock(\cmd,\arg)$ from
+        some party $P$ to run command \cmd, with arguments \arg,
+        \IdealGclock operates as follows.} \\
+      \textrm{\IdealGclock maintains a variable $t$ with the current itme,
+        a variable $T$ with the list of parties keeping track of the time,
+        and a map $A$ which keeps the parties' (dis)agreements to advance the
+        clock.}
+    \end{minipage}
+    \vspace*{0.5em}
+
+    \begin{minipage}[t]{0.40\textwidth}
+      \procedure{$\pcif \cmd = \uccmd{Register} \land \arg = \emptyset$}{
+        T \gets T \cup \set{P} \\
+        \ucio{Output}~(\uccmd{Registered})~\text{to}~P \\
+      }
+      \procedure{$\pcif \cmd = \uccmd{Update} \land \arg = \emptyset$}{
+        A(P) \gets \top \\
+        \pcif \forall P \in T, A(P) = \top: \\
+        \pcind t \gets t + 1; \forall P \in T, A(P) = \bot \\
+        \pcind \ucio{Send}~(\uccmd{Updated})~\text{to}~P        
+      }
+    \end{minipage}
+    \hspace*{1.25em}
+    \begin{minipage}[t]{0.60\textwidth}
+      \procedure{$\pcif \cmd = \uccmd{Deregister} \land \arg = \emptyset$}{
+        T \gets T \setminus \set{P} \\
+        \text{Output}~(\uccmd{DeregisteredOk})~\text{to}~P \\
+      }
+      \procedure{$\pcif \cmd = \uccmd{Read} \land \arg = \emptyset$}{
+        \text{Output}~(\uccmd{ReadOk},t)~\text{to}~P
+      }
+    \end{minipage}
+  \end{framed}
+  \caption{Ideal subroutine for a global clock, from \cite{kkk21}.}
+  \label{fig:gclock}
+\end{figure}
+
+\paragraph{$\delta$-delay Ledger.} %
+We adopt a ledger notion given in \cite{kkk21}. This is global functionality
+that defines an ideal version of a ledger as a shared subroutine, which models
+the append-only property of ledgers, and the fact that changes take some delay
+until they are applied to the ledger.
+%
+This functionality accepts sending individual transactions to be added to the
+ledger state, fetching (reading) the state of the ledger, and extending the
+ledger by appending (blocks of) transactions to it. Interestingly, it gives the
+adversary control over when to advance the status of each party, as long as
+these advancements ensure the common prefix rule -- where $\ldgState' \prec
+\ldgState$ means that $\ldgState'$ is a prefix of \ldgState. It also relies
+on yet another global functionality, the global clock, to timestamp incoming
+transactions. If a transaction is not appended to an honest party's view before
+the given $\delta$ delay, then the functionality aborts.
+%
+For the sake of readability, we reproduce the functionality in
+\figref{fig:gledger}.
+
+\begin{figure}[ht]
+  \begin{framed}
+    \begin{minipage}[t]{\textwidth}
+      \textrm{Upon receiving a call $\IdealGdledger(\cmd,\arg)$ from
+        some party $P$ to run command \cmd, with arguments \arg,
+        \IdealGdledger operates as follows.} \\
+      \textrm{\IdealGdledger maintains a mapping \ldgMap which associates
+        parties with their view of the ledger.
+        \ldgUtxo is a multiset of unconfirmed transactions.
+        \ldgState is the authoritative ledger state
+        All mappings and (multi-)sets are initialised to empty values.
+      }
+    \end{minipage}
+    \vspace*{0.5em}
+
+    \begin{minipage}[t]{0.40\textwidth}
+      \procedure{$\pcif \cmd = \uccmd{Submit} \land \arg = \ldgTx$}{
+        \ucio{Send}~(\uccmd{Read})~\text{to}~\IdealGclock \\
+        \ucio{Recv}~(\uccmd{ReadOk},t)~\text{from}~\IdealGclock \\
+        \ldgUtxo \gets \ldgUtxo \cup \set{(\ldgTx,t)} \\ 
+        \ucio{Output}~(\uccmd{Transaction},\ldgTx,t)~\text{to}~\adv \\
+      }
+      \procedure{$\pcif \cmd = \uccmd{Extend} \land \arg = \ldgState'$}{
+        \pcif P = \adv \land \ldgState' \subseteq \ldgUtxo: \\
+        \pcind \ldgUtxo \gets \ldgUtxo \setminus \ldgState' \\
+        \pcind \ldgState \gets \ldgState || \ldgState'
+      }
+    \end{minipage}
+    \hspace*{1.25em}
+    \begin{minipage}[t]{0.60\textwidth}
+      \procedure{$\pcif \cmd = \uccmd{Read} \land \arg =
+        \emptyset$}{
+        % \pcif P = \adv: data \gets \ldgState \\
+        % \pcelse: data \gets \ldgMap(P) \\
+        \ucio{Send}~(\uccmd{Read})~\text{to}~\IdealGclock \\
+        \ucio{Recv}~(\uccmd{ReadOk},t)~\text{from}~\IdealGclock \\
+        \pcif \exists (\ldgTx,t') \in \ldgUtxo~\suchthat~|t-t'| > \delta:
+        \pcreturn \bot \\
+        \pcelse \pcif \exists (\ldgTx,t') \in \ldgState~\suchthat~ |t-t'|
+        > \delta~\land \\
+        \pcind \exists P' \in \ldgHonest~\suchthat~(\ldgTx,t') \notin \ldgMap(P'):
+        \pcreturn \bot \\        
+        \text{Output}~(\uccmd{ReadOk}, \ldgHead(\ldgMap(P)))~\text{to}~P \\
+      }
+      \procedure{$\pcif \cmd = \uccmd{Advance} \land \arg = (P',\ldgState')$}{
+        \pcif P = \adv \land \ldgMap(P') \prec \ldgState' \prec \ldgState:
+        \ldgMap(P') \gets \ldgState'
+      }
+    \end{minipage}
+  \end{framed}
+  \caption{Ideal subroutine for a global $\delta$-delay ledger, from
+    \cite{kkk21}.}
+  \label{fig:gledger}
+\end{figure}
 
 \paragraph{Digital Signatures.} %
-%Maybe build on \IdealFSig from \cite{canetti03}.
 
-\paragraph{Merkle Trees.}
+\begin{figure}
+  \begin{framed}
+    \begin{minipage}[t]{\textwidth}
+      \textrm{Upon receiving a call $\IdealFSig(\cmd,\sid,\arg)$ from some party
+        $P$ to run command \cmd, in session \sid, with arguments \arg,
+        \IdealFSig operates as follows.} \\
+      \textrm{\IdealFSig keeps a list \SIG of known signed messages.}      
+    \end{minipage}
+    \vspace*{0.5em}
 
-\paragraph{Public Key Infrastructures.} %
-% Maybe build on \IdealFCA from \cite{canetti03}.
-
-\paragraph{Ideal functionality specification.} %
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure{$\pcif \cmd = \uccmd{KeyGen} \land \arg =
+        \emptyset$}{
+        \pccomment{\fbox{Key Generation}} \\
+        \pcif \sid = (P,\ssid): \\
+        \pcind \ucsend~(\uccmd{KeyGen},\sid)~\text{to}~\adv \\
+        \pcind \ucrecv~(\uccmd{VerKey},\sid,v)~\text{from}~\adv \\
+        \pcind \ucio{Output}~(\uccmd{VerKey},\sid,v)~\text{to}~P \\
+        \pcind \text{Store}~(P,v)
+      }
+      \vspace*{0.25em}
+      \procedure{$\pcif \cmd = \uccmd{Verif} \land
+        \arg = (\sig,\msg,v')$}{
+        \pccomment{\fbox{Verify a message}} \\
+        \ucsend~(\uccmd{Verif},\sid,\msg,\sig,v)~\text{to}~\adv \\
+        \ucrecv~(\uccmd{Verifd},\sid,\msg,\phi)~\text{from}~\adv \\
+        \pcif v' = v \land (\msg,\sig,v,1) \in \SIG: f \gets 1 \\
+        \pcelse \pcif v' = v \land P~\text{is not corrupt}~\land \\
+        \pcind (\msg,\sig',v,1) \notin \SIG: \\
+        \pcind \SIG \gets \SIG \cup \lbrace (\msg,\sig,v,0) \rbrace;
+        f \gets 0 \\
+        \pcelse \pcif (\msg,\sig,v',f') \in \SIG: f \gets f' \\
+        \pcelse: \\
+        \pcind \SIG \gets \SIG \cup \lbrace (\msg,\sig,v',\phi) \rbrace;~
+        f \gets \phi \\
+        \ucio{Output}~(\uccmd{Verifd},\sid,\msg,f)
+      }
+    \end{minipage}
+    \begin{minipage}[t]{0.5\textwidth}
+      \procedure{$\pcif \cmd = \uccmd{Sign} \land \arg = \msg$}{
+        \pccomment{\fbox{Sign a message}} \\
+        \pcif \sid = (P,\ssid) \\
+        \pcind \ucsend~(\uccmd{Sign},\sid,\msg)~\text{to}~\adv \\
+        \pcind \ucrecv~(\uccmd{Signed},\sid,\msg,\sig)~\text{from}~
+        \adv \\
+        \pcind \pcif (\msg,\sig,v,0) \in \SIG: \\
+        \pcind \pcind \ucio{Output}~(\uccmd{Error}) \\
+        \pcind \pcelse: \\
+        \pcind \pcind \SIG \gets \SIG \cup (\msg,\sig,v,1) \\
+        \pcind \pcind \ucio{Output}~(\uccmd{Signed},\sid,\msg,\sig)
+      }
+    \end{minipage}
+  \end{framed}
+  \caption{Ideal signature functionality, \IdealFSig, from \cite{canetti03}.}
+  \label{fig:fsig}
+\end{figure}
 
@@
 since 2022\footnote{\url{https://www.w3.org/TR/did-core}. Last access, 3rd
-  November, 2022.}. Essentially, the DID specification defines how to associate
+  November, 2022.}. Strictly speaking, a DID is a string that uniquely
+identifies information referring to some entity, whereas such information is
+the DID document. The DID controller is yet another entity who is allowed to
+apply changes to a DID document. In the sequel, for simplicity we assume that
+the controller is also the entity that the information in the DID document
+refers to, but this is not necessarily the case in general.
+
+Essentially, the DID specification defines how to associate
 public keys and additional metadata to unique identifiers, leveraging verifiable
@@
 adjective for DIDs. The DID specification describes the syntax that identifiers
-must follow, as well as the operations (CRUD: Create, Read, Update, Deactivate)
-that any DID-compatible mechanism must implement.
+must follow, as well as the CRUD (Create, Read, Update, Deactivate) operations
+that any DID-compatible mechanism must implement. Concretely:
+
+\begin{description}
+\item[Create.] Must specify how controllers create new DIDs.
+\item[Read.] Must specify how the contents of a DID can be fetched and
+  authenticated.
+\item[Update.] Must specify what updates can controllers apply (if any)
+  to existing DIDs.
+\item[Deactivate.] Must specify if (parts of) existing DIDs can be signaled
+  as no longer valid, and how.
+\end{description}
 
@@
 able to register a unique identifier, associate public key material to it, and
-manange it. Thus, it is natural to see such a mechamism as an equivalent to
-traditional Public Key Infrastructures (PKIs), where different instantiations of
-such a mechanism -- e.g., with different approaches to implement the CRUD
-methods required by the DID specification, or based on different VDRs -- can be
-seen as a different type of DID-based PKI.
+manange it. Thus, as we do here, it is natural to see such a mechanism as an
+specific type of Public Key Infrastructures (PKIs), where different
+approaches to implement the CRUD methods required by the DID specification, or
+based on different VDRs -- can be seen as a different type of DID-based PKI.
 
-\todo{Maybe expand. Also, describe the difference between DID Document, and DID.
-  Also describe the concept of DID controller, essential to prevent manipulation
-  of DIDs and their documents.}
+A final requirement put by the W3C DID specification concerns authorisation.
+Namely, it states (in Section 8.2) that candidate DID methods ``must define how
+authorisation is performed''. This concretely means that DID methods have to
+define the way in which controllers prove to be entitled to perform create,
+update, or deactivate operations.
 

### 2022-12-17 prism-backend/research/prism-protocol/did_atala.tex
Better defined PKI functionality.

@@
-\section{DIDs in Atala PRISM}
+\section{Atala PRISM's \RealPKIDIDAtala: A DID-based PKI}
 \label{sec:did-atala}
 
-In this section we first give an ideal functionality for Public-Key
-Infrastructures built atop of DIDs \IdealGPKIDID, and subsequently describe
-Atala PRISM DID method \RealPKIDIDAtala, which is a protocol realizing
-\IdealGPKIDID.
+In this section we first describe Atala PRISM DID method \RealPKIDIDAtala, and
+prove that it realizes \IdealGPKIDID.
 %
-Before doing so, we introduce some base ideal functionalities upon which we
-rely for \RealPKIDIDAtala. Namely, a simplified notion of append-only bulletin
-boards, and digital signatures.
-
-\subsection{Global Functionality \IdealGPKIDID}
-
-\subsection{The \RealPKIDIDAtala Construction}
-
-We next define the Atala PRISM DID method, following the interfaces defined for
-\IdealGPKIDID. We begin by describing the types of keys supported in Atala
-PRISM, and then specify how sets of such keys can be managed through DIDs in
-Atala.
+We begin by describing the types of keys supported in Atala PRISM, and then
+specify how sets of such keys can be managed through the previously introduced
+dictionaries in \IdealGPKIDID.
 
@@
 its policy on the keys' labels and types.
+\todo{This needs to take into account the caller, and the previous state of the
+  PKI list.}
 

### 2022-12-17 prism-backend/research/prism-protocol/gpkivdu.tex
Better defined PKI functionality.

\section{A PKI with Verifiable Delayed Updates}
\label{sec:pkivdu}

In this section, we present the ideal functionality for a PKI that supports
updates which are:

\begin{itemize}
\item Verifiable: Any party with read access to the PKI storage can check
  that the last state of any stored public key has been produced after
  applying a sequence of authenticated changes to this public key.
\item Delayed: Any party with write access to the PKI storage is guaranteed
  that its requested changes will get applied after at most some predefined
  delayed.
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "prism-protocol"
%%% End:

### 2022-12-17 prism-backend/research/prism-protocol/pkivdu.tex
Better defined PKI functionality.

\section{\IdealGPKIDID: A PKI with Verifiable Delayed Updates}
\label{sec:pkivdu}

In this section, we present the ideal functionality for a PKI that supports
updates which (informally) are:

\begin{itemize}
\item Verifiable: It can be checked that the sequence of changes that lead to
  the current state of a (set of) public key(s) have been applied by their
  legitimate owner.
\item Delayed: Changes to existing (sets of) public keys, or requests to add
  new ones, get applied after at most some predefined delay.
\end{itemize}

\paragraph{The ideal functionality.} %
We take the generic approach to see a PKI as a system that stores dictionaries
(i.e., lists of labels with corresponding types and values), where each
dictionary is associated to a single identifier. The functionality is then
defined in terms of the (CRUD) operations that can be run to manage such
objects. To define the ideal functionality as abstractly as possible, we only
make use of one external (global) subroutine: a clock \IdealGclock.
Indeed, given that the objects stored in the PKI can be modified, and such
objects are in fact public keys used to authenticate entities at concrete points
in time, keeping track of when a mocification takes place, is crucial -- e.g.,
to know if a public key is/was valid at a certain point in time.
%
Otherwise, the functionality simply keeps track of the requested (CRUD)
operations, makes sure that only the entitled party can perform them, and that
the maximum delay is not violated. Note that this delay can be set to any
arbitrarily small value, which means that a delayed PKI is simply a
generalisation of a (non-delayed) PKI.
%
Finally, we parameterize the ideal functionality with a policy \P, that we use
to account for any arbitrary requirements that concrete instantiations may
impose on the contents of the objects managed by the PKI. For instance, some
concrete PKI may refuse to store RSA public keys of length less than $4096$
bits; or, in the DID setting, a DID method may require that all DID Documents
contain an active key of some concrete type.

We now describe the interfaces exposed by \IdealGPKIDID, following the previous
guidelines. They are formally defined in \figref{fig:fpkidid}.

\begin{description}
\item[Create.] Upon receiving the instruction \uccmd{Create}, the functionality
  adds a new set of values $\val_i$, each of type $\typ_i$ and identified with
  label $\lbl_i$. Following the definition in \cite{canetti03} (where the
  adversary chooses the public keys, equivalent to our $\val_i$ values), the
  functionality asks \Sim to provide the $\val_i$ values, as well as the
  identifier to associate to the complete set. If the identifier does not
  already exist in the PKI list \VDRL, the functionality fetches the
  current time from the global clock \IdealGclock, and adds the requested
  operation to the list of unconfirmed operations, \VDROP.
\item[Read.] Upon recieving the instruction \uccmd{Read}, the functionality
  fetches the dictionary associated to identifier \VDRid from the list of
  confirmed operations in the PKI. In addition, the functionality fetches the
  current time from the global clock \IdealGclock and, if there is any
  unconfirmed operation older than the predefined delay, it aborts. Otherwise,
  returns the dictionary associated to \VDRid.
\item[Update.] Receives the instruction \uccmd{Update}, associated to an
  identifier \VDRid, to which the caller whishes to add a set of label and type
  entries $\sval_a$, and from which it whishes to remove a set of labels
  $\sval_d$. If the entry \VDRid exists in the PKI list \VDRL, the functionality
  asks the adversary to provide the values for the new labels. Then, applies the
  additions and removals honestly, gets the current time from \IdealGclock, and
  adds the operation to the list of unconfirmed operations.
\item[Deactivate.] The functionality exposes the interface \uccmd{Deact}, for
  deactivating specific labels within an identifier in the PKI list \VDRL (where
  deactivating all the labels wichin an identifier is equivalent to deactivating
  the whole identifier). If the given identifier exists, the functionality
  removes the given labels from it, fetches the current time, and adds the
  operation to the list of unconfirmed operations.
\end{description}

In addition, the adversary \Sim gets access to an interface \uccmd{Process},
which lets it decide when the operations received by the ideal functionality
get applied. However, if, upon reading the contents of the PKI (via the
\uccmd{Read} interface), some unconfirmed operation is detected that is older
than the predefined delay, the functionality aborts. Note that, as long as the
maximum delay or the policy \P are not violated, the adversary has the
capability to pick in which order are (unconfirmed) operations applied, as it
specifies the operations to be processed.

\todo{The following is a bit messy, but important. Improve writeup.}
Concerning the policy \P, the functionality checks that every operation to be
processed satisfies it. Policies (may) take into account both the contents of
the operation ($\VDROp = (\VDRid,\sval,P,\tau)$) and the current (confirmed)
state of the PKI, \VDRL. Note that the specific set of values \sval in the
unconfirmed operation are always computed in advance by the corresponding
interface (\uccmd{Create}, \uccmd{Update}, or \uccmd{Deactivate}), ensuring that
the value passed to the policy has been correctly processed. In addition, the
functionality does not make any check on the identity of the party who submitted
each operation. Instead, this can be done by the policies, and allows capturing
multiple types of PKIs, e.g., PKIs that support delegation, or those that don't.
\todo{We should at least specify a bit more formally what conditions policies
  need to meet in this regard? How?}

\begin{figure}
  \begin{framed}
    \scalebox{0.9}{
      \begin{minipage}[t]{\textwidth}
        \textrm{Upon receiving a call $\IdealGPKIDID(\cmd,\sid,\arg)$
          from some party $P$ to run command \cmd, in session \sid, with arguments
          \arg, $\IdealGPKIDID$ operates as follows.}
        \textrm{If the received \cmd and \arg pair does not meet any of
          the following options, the request is ignored.}
        \textrm{\P is a boolean predicate defining concrete conditions for
          acceptable operations.}
        \textrm{\didOP is a list of submitted (yet, possibly unconfirmed)
          operations, and \VDRL is the authoritative state of published
          operations.}        
      \end{minipage}
    }
    \vspace*{0.5em}

    \scalebox{0.9}{
      \begin{minipage}[t]{0.57\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Create} \land \arg =
          \setind{(\lbl_i,\typ_i)}{i\in[n]}$}{ 
          \ucsend~(\uccmd{Create}, \sid, \arg)~\text{to}~\Sim \\
          \ucrecv~(\uccmd{CreateOk}, \sid, \VDRid,
          \sval=\setind{\val_i}{i\in[n]}) \\
          \hspace*{2.7em}\text{from}~\Sim \\
          \pcif (\VDRid,\cdot,\cdot,\cdot) \in \VDRL: \pcreturn \bot \\
          \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock \\
          \ucrecv~(\uccmd{ReadOk},\tau)~\text{from}~\IdealGclock \\
          \VDROP \gets \VDROP \cup \set{(\VDRid,
            \setind{(\lbl_i,\typ_i,\val_i)}{i\in[n]},P,\tau)} \\
          \ucio{Output}~(\uccmd{ProcessedC},\sid,\VDRid,\sval)
        }
        \vspace*{0.15em} \\

        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Update} \land
          \arg = (\VDRid, \sval_d,\sval_a)$}{
          \pcif (\VDRid,\sval_0,P,\cdot) \notin \VDRL: \pcreturn \bot \\
          \ucsend~(\uccmd{Update}, \sid,\VDRid,\sval_d,\sval_a)~\text{to}~\Sim \\
          \ucrecv~(\uccmd{UpdOk},\sid,\VDRid,\setind{\val^a_i}{i\in[n^a]})~
          \text{from}~\Sim \\
          \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock \\
          \ucrecv~(\uccmd{ReadOk},\tau)~\text{from}~\IdealGclock \\
          \lbrace (\lbl_i^a,\typ_i^a) \rbrace_{i\in[n^a]} \gets \sval_a \\
          \sval_1 \gets (\sval_0 \setminus \sval_d) \cup
          \setind{(\lbl^a_i,\typ^a_i,\val^a_i)}{i\in[n^a]} \\
          \VDROP \gets \VDROP \cup \set{(\VDRid,\sval_1,P,\tau)} \\
          \ucio{Output}~(\uccmd{ProcessedU},\sid,\VDRid,\sval_1)
        }        
      \end{minipage}
    }
    \scalebox{0.9}{
      \begin{minipage}[t]{0.5\textwidth}
        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Read} \land
          \arg = \VDRid$}{
          \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock \\
          \ucrecv~(\uccmd{ReadOk},\tau)~\text{from}~\IdealGclock \\
          \pcif \exists (\cdot,\cdot,\cdot,\tau') \in \VDROP~\suchthat~
          |\tau-\tau'| > \delta: \\
          \pcind \pcreturn \bot \\
          \pcif (\VDRid,\sval,\cdot,\cdot) \notin \VDRL: \pcreturn \bot \\
          \ucio{Output}~(\uccmd{ReadOk},\sid,\VDRid,\sval)~\text{to}~P
        }
        \vspace*{0.15em} \\

        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Deact} \land \arg =
          (\VDRid, \lbrace \lbl_i \rbrace_{i\in[n]})$}{
          \pcif (\VDRid,\sval_0,P,\cdot) \notin \VDRL: \pcreturn \bot \\ 
          \sval_1 \gets \sval_0 \setminus \lbrace \lbl_i \rbrace_{i\in[n]} \\
          \ucsend~(\uccmd{Deact}, \sid, \arg)~\text{to}~\Sim \\
          \ucrecv~(\uccmd{DeactOk},\sid)~\text{from}~\Sim \\
          \ucsend~(\uccmd{Read})~\text{to}~\IdealGclock \\
          \ucrecv~(\uccmd{ReadOk},\tau)~\text{from}~\IdealGclock \\
          \VDROP \gets \VDROP \cup \set{(\VDRid,\sval_1,P,\tau)} \\
          \ucio{Output}~(\uccmd{ProcessedD},\sid,\VDRid,\sval_1)
        }
        \vspace*{0.15em} \\

        \procedure[linenumbering]{$\pcif \cmd = \uccmd{Process} \land \arg =
          \VDROP'$}{
          \pcif P \neq \Sim \lor \VDROP' \not\subseteq \VDROP: \pcreturn \bot \\
          \pcfor \VDROp = (\VDRid,\sval,P,\tau) \in \VDROP': \\
          \pcind \pcif \P(\VDROp,\VDRL) = 0: \pcreturn \bot \\
          \VDROP \gets \VDROP \setminus \VDROP' \\
          \VDRL \gets \VDRL \cup \VDROP'
        }
      \end{minipage}
    }
  \end{framed}
  \caption{Ideal PKI functionality with delayed verifiable updates,
    \IdealGPKIDID. We abuse set notation, and write $\lbrace (a_i,\dots)
    \rbrace_{i\in[n]} \setminus \lbrace (b_j,\dots) \rbrace_{j\in[m]}$ to mean
    subtracting from the first set the elements present in the second set,
    whenever $a_i = b_j$ for some $i,j$, even if the size of the $(a_i,\dots)$
    and $(b_j,\dots)$ tuples do not match.}
  \label{fig:fpkidid}
\end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "prism-protocol"
%%% End:

### 2022-12-19 prism-backend/research/prism-protocol/did_atala.tex
Beginning proof of Atala DIDs with global subroutines.

@@
 %
-We begin by describing the types of keys supported in Atala PRISM, and then
-specify how sets of such keys can be managed through the previously introduced
-dictionaries in \IdealGPKIDID.
+We begin by describing the types of keys supported in Atala PRISM, and the
+policy \PAtala that all CRUD operations need to meet.
+
+\paragraph{Custom Notation.} %
+Keys in Atala are identified by labels. In the following description of the
+\RealPKIDIDAtala construction, given a set of keys, we frequently refer to the
+``master key with lowest label'' (using any order relation, like lexicographic
+order).  For brevity, given a set \st, we use $\LMKL(\st)$ to denote such label.
 
@@
 
-\paragraph{Custom Notation.} %
-Keys in Atala are identified by labels. In the following description of the
-\RealPKIDIDAtala construction, given a set of keys, we frequently refer to the
-``master key with lowest label'' (using any order relation, like lexicographic
-order).  For brevity, given a set \st, we use $\LMKL(\st)$ to denote such label.
-
-\paragraph{$\P_{Atala}$ policy.} %
+\paragraph{\PAtala policy.} %
 Before proceeding with the specififying the DID operations in Atala, we define
@@
   \centering
-  \procedure{$\P_{Atala}(\lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]})$}{    
+  \procedure{$\PAtala(\lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]})$}{    
     \pcif \exists i\in[n]~\suchthat~\typ_i \notin [\MasterKey,\IssueKey,
@@
   }
-  \caption{Policy $\P_{Atala}$ that all DID documents must meet in Atala.}
+  \caption{Policy \PAtala that all DID documents must meet in Atala.}
 \end{figure}
@@
 \item{\uccmd{Create}.} %
-  To create a DID, the user has to specify the key pairs to create, along with
-  fresh identifiers (labels) and their type. For ease of exposition, we assume
-  that the used identifiers just follow a sequence. The predicate \P in Atala
-  simply requires that at least one key pair of \MasterKey type is created. The
-  \uccmd{Create} algorithm creates as many keys of each type as requested,
-  and keeps a list with the identifier, type and public key of each key pair.
-  This list is then hashed into a value \texttt{h}, and the created DID is
-  ``\texttt{\did:prism:h}''. A transaction containing the created list, the
-  DID, and the \texttt{CreateDID} instruction is sent to the blockchain,
-  signed by one of the master keys -- w.l.o.g., we simply use the first one
-  in the list. The DID owner stores locally the list, along with the
-  corresponding private keys.
+  To create a DID, the user has to specify the fresh identifiers (labels) and
+  types of the key pairs to include in the DID. The \uccmd{Create} algorithm
+  creates as many keys of each type as requested, by leveraging the ideal
+  functionality \IdealFSig, and keeps a list with the identifier, type and
+  public key of each key pair. This list is then hashed into a value \texttt{h}
+  via \IdealGRO, and the created DID is ``\texttt{\did:prism:h}''. A transaction
+  containing the created list, the DID, and the \texttt{CreateDID} instruction
+  is sent to the blockchain via a call to \IdealGdledger, signed by one of the
+  master keys -- w.l.o.g., we 
+  simply use the first one in the list. The DID owner stores locally the list.
 \item[\uccmd{Read}.] %
   Getting the contents of a DID simply requires processing the associated
-  transactions in the blockchain. Namely, transactions $(\tx,\sig)$ where $\tx$
+  transactions in the blockchain. Namely, the interface first fetches all the
+  contents from the \IdealGdledger functionality. Then, transactions the
+  relevant transactions are those with $(\tx,\sig)$ where $\tx$
   is either $(\texttt{CreateDID},\did,\cdot)$ or $(\texttt{UpdateDID},\did,
@@
   a list of $n$ keys) -- if this is not the case, it suffices to make first a
-  call to \uccmd{Read} for the given DID. \todo{This seems relevant enough to
-    be highlighted in some more visible place, no?}
+  call to \uccmd{Read} for the given DID.
+  %
   Then, updating a DID requires to (optionally) specify a list of previously
-  existing key identifiers to remove, and (optionally) specify a list of new key
-  identifiers, and their types, to add. To simplify notation, we just adopt the
-  (equivalent) convention that the caller indicates a list of $\lbrace (i,
-  \lbl_i) \rbrace_{i\in\tilde{N}\subseteq[\tilde{n}]}$ pairs, where $\tilde{n}$
-  may be smaller or larger than $n$, depending on the desired update. This
-  list is then interpreted as follows. If $i$ is an already existing
-  identifier, the label is ignored and the corresponding key is not removed. If
-  $i$ is a new identifier, then a new key pair of the given type is created.
-  Omitting an existing identifier is then interpreted as the desire to remove
-  the corresponding key pair. Otherwise, the same policy as for \uccmd{Create}
-  applies here. Key pairs for the new keys are generated, and a transaction is
-  sent to the blockchain, signed with one of the master keys in the DID
-  \emph{before applying the update}. This transaction contains a list of the
-  identifiers of the keys to remove, and a list of the identifiers and types
-  of the keys to add.
+  existing key labels to remove $\sval_d$, and (optionally) specify a list
+  $\sval_a$ of new key labels and their types to add. The result of removing
+  the labels in $\sval_d$ and adding the new keys in $\sval_a$ must satisfy
+  \PAtala. Key pairs for the new keys are generated via \IdealFSig, and a
+  transaction is sent to the blockchain via \IdealGdledger, signed (again, via
+  \IdealFSig) with one of the master keys in the DID \emph{before applying the
+    update}. This transaction contains a list of the identifiers of the keys to
+  remove, and a list of the identifiers and types of the keys to add.
+  %
+  Note that the DID remains the same, even though the original contents of
+  the associated DID document may change.
 \item[\uccmd{Deactivate}.] %
@@
           \lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}$}{
-          \pcif \P_{Atala}(\lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}) = 0: abort \\
+          \pcif \PAtala(\lbrace (\lbl_i,\typ_i) \rbrace_{i\in[n]}) = 0: abort \\
           \st \gets \emptyset \\
@@
           \ucrecv~(\uccmd{Signed},\sid',\tx,\sig)~\text{from}~\IdealFSig \\
-          \ucsend~(\uccmd{Append},(\tx,\sig))~\text{to}~\IdealGdledger \\
+          \ucsend~(\uccmd{Submit},(\tx,\sig))~\text{to}~\IdealGdledger \\
           \text{Locally store}~
           (\did, \lbrace (\lbl_i,\typ_i,\pk_i) \rbrace_{i\in[n]}) \\
-          \ucio{Output}~(\uccmd{Created},\sid,\did,\lbrace \pk_i
+          \ucio{Output}~(\uccmd{ProcessedC},\sid,\did,\lbrace \pk_i
           \rbrace_{i\in[n]})
@@
           \pcind \lbl \gets \LMKL(\st) \\
-          \pcind \pcif \lbl = \emptyset \lor \P_{Atala}(\st) = 0: \text{skip} \\
+          \pcind \pcif \lbl = \emptyset \lor \PAtala(\st) = 0: \text{skip} \\
           \pcind \pcelse \sid' \gets ((P,\lbl),\sid) \\
@@
           \pcind \pcif b = 0: \text{skip} \\
-          \ucio{Output}~(\uccmd{Read},\sid,(\did,\st))
+          \ucio{Output}~(\uccmd{ReadOk},\sid,\did,\st)
         }    
@@
           \arg = (did, \sval_d, \sval_a)$}{
-          % \pcif \exists i~\suchthat~\typ_i \notin [\MasterKey,\AuthKey,
-          % \CommKey,\IssueKey]~\lor \\
-          % \pcind \nexists i~\suchthat~\typ_i = \MasterKey
-          % \lor \exists i,j~\suchthat~\lbl_i = \lbl_j: abort \\
-          % \pcif \exists i~\suchthat~\lbl_i \notin [\MasterKey,\AuthKey,
-          % \CommKey,\IssueKey] \lor
-          % \nexists i~\suchthat~\lbl_i = \MasterKey: \\
-          % \pcind abort \\
-          % \text{Run $(\uccmd{Read},\sid,\did)$ to fetch $(\did,\sval)$} \\
-          % \pcif \sval = \bot: abort \\
           \text{Fetch}~
@@
           \pccomment{\todo{Syntax refinement needed here.}} \\
-          \pcif \P_{Atala}(\sval') = 0: abort \\          
+          \pcif \PAtala(\sval') = 0: abort \\          
           \pcfor i \in [n_a] \\
@@
           \pcind \st_a \gets \st_a \cup \lbrace (\lbl^a_i,\typ^a_i,\pk^a_i) \rbrace \\
-          % \text{Locally store}~(\did,\lbrace (i,\lbl_i,\pk_i) \rbrace_{i\in[\tilde{n}]} \\
           \tx \gets (\texttt{UpdateDID}, \did, \sval_d, \st_a) \\
@@
           \ucrecv~(\uccmd{Signed},((P,\lbl),\sid),\tx,\sig)~\text{from}~\IdealFSig \\
-          \ucsend~(\uccmd{Append},(\tx,\sig))~\text{to}~\IdealGdledger \\
+          \ucsend~(\uccmd{Submit},(\tx,\sig))~\text{to}~\IdealGdledger \\
           \text{Locally store}~(\did,\sval) \\
-          \ucio{Output}~(\uccmd{Updated},\sid,(\did,\lbrace \pk^a_i \rbrace_{i\in[n^a]}))
+          \ucio{Output}~(\uccmd{ProcessedU},\sid,\did,\lbrace \pk^a_i \rbrace_{i\in[n^a]}) \\
+          \text{\todo{The previous must return all the final pks, not only
+              $pk^a$, to be compatible with deact.}}
         }
@@
           (did, \sval)$}{       
-          \text{Run as a \texttt{Update} operation} \\
-          \text{with $\sval_d \gets \sval$ and $\sval_a \gets \emptyset$}
+          \text{Run as an \texttt{Update} operation with} \\
+          \text{ $\sval_d \gets \sval$ and $\sval_a \gets \emptyset$,
+            and output} \\
+          \text{\uccmd{ProcessedD} instead of \uccmd{ProcessedU}}
         }
@@
 
-Before going into the proofs, observe that the \uccmd{Create} (in lines 1-2) and
-\uccmd{Update} (in lines 6-7) operations in \RealPKIDIDAtala include a policy on
-the received key labels and types. Concretely, this policy requires that all
-labels are unique, all types are of a known key type, and that at least one of
-them is of type \MasterKey. In the sequel, we use $\P_{Atala}$ to refer to this
-policy.
+We prove security of \RealPKIDIDAtala by showing that it UC-emulates
+\IdealGPKIDID. For this, we leverage concretely the results in \cite{bch+20} and
+\cite{bhz21}. In a nutshell, the former extends the notions of UC emulation and
+composition so that they are compatible, in the plain UC model, with global
+subroutines (such as a global clock, a ledger, or a random oracle).
+\cite{bhz21} builds on these results to make them suitable for systems that rely
+simultaneously on multiple global functionalities.
+%
+To make the previous a bit more precise, we replicate here the relevant theorem
+from \cite{bhz21} (in \cite{bch+20}, the same statement appears with only one
+global subroutine).
 
-\todo{Do we mention somewhere that {\sid}s have structure $(P,\sid')$? This is
-  used for \Sim to know which party is generating which keys.}
-
-\begin{theorem}[UC-security of \RealPKIDIDAtala]
-  \label{thm:sec-didatala}
-  \RealPKIDIDAtala UC-realizes $\IdealGPKIDID$ in the $(\IdealGRO,
-  \IdealFSig, \IdealGdledger)$-hybrid model.
+\begin{theorem}[UC emulation with multiple global setups \cite{bhz21}]
+  \label{thm:uc-bhz21}
+  Let $\pi$, $\phi$ and $\gamma_1,\dots,\gamma_n$ be protocols. We say that
+  $\pi$ $\xi$-UC-emulates $\phi$ in the presence of global subroutines
+  $\gamma_1,\dots,\gamma_n$ if protocols $\pi$ and $\phi$ are formulated with
+  respect to a global subroutine $\hat{\gamma}_{\gamma_1,\dots,\gamma_n}$ and
+  $\UCM[\pi,\hat{\gamma}_{\gamma_1,\dots,\gamma_n}]$ $\xi$-emulates protocol
+  $\UCM[\phi,\hat{\gamma}_{\gamma_1,\dots,\gamma_n}]$.
 \end{theorem}
 
+At a high level, to apply the results in \cite{bch+20,bzh21}, we show the global
+subroutines used in \IdealGPKIDID and \RealPKIDIDAtala can be merged into the
+single ``meta'' global subroutine $\hat{\gamma}_{\gamma_1,\dots,\gamma_n}$
+required by \thmref{thm:uc-bhz21}, which furthermore meets the conditions to be
+subsequently suitable for UC-emulation. In addition, we argue that this is
+usually the case for the known realisations of each respective global
+subroutine. (This ensures that our approach is natural, and indeed UC-realisable
+in practice.)
+%
+We then describe how the management protocol \UCM works in conjunction with
+our \IdealGPKIDID and the ``meta'' global subroutines (in the ideal world), and
+with \RealPKIDIDAtala and the ``meta'' global subroutine (in the real world).
+%
+Finally, we show that the latter emulates the former.
+%
+We emphasise that this is merely an application of the results in
+\cite{bch+20,bhz21} to our setting. The previously sketched process is detailed
+next, directly referencing the relevant theorems of the relevant works, when
+appropriate.
+
+\paragraph{The meta-global subroutine \gAtala.} %
+We next show that the global subroutines used in \RealPKIDIDAtala are leveraged
+in a way that is compatible with \cite[Theorem 4.3]{bhz21}. This is not a full
+proof for a concrete application of such theorem, as that would require proving
+that concrete protocols UC-emulate each global functionality. However, we
+initially leave it ``incomplete'' to show that any combination of instantiations
+of our global subroutines can be used to build a secure variant of the Atala
+DID protocol (later, we show the concrete instantiations that Atala currently
+uses). For concreteness, we refer to this ``partial'' property as mergability
+of the global subroutines of Atala into \gAtala.
+
+\begin{lemma}[Mergability of \gAtala]
+  \label{lma:gAtala}
+  Let $\gamma_1 \gets \IdealGdledger$, $\gamma_2 \gets \IdealGRO$, $\gamma_3
+  \gets \IdealGclock$. Then:
+  \begin{enumerate}
+  \item For $i < 3$, $\gamma_i$ is subroutine respecting except for calls to
+    $\gamma_{i+1,\dots,3}$, and $\gamma_3$ is subroutine respecing. All
+  $\gamma_i$'s are subroutine exposing.
+\item For $i>1$, $\gamma_i$ is $\gamma_j$-regular, for all $j \in \set{1,
+    \dots,\i-1}$.
+  \end{enumerate}
+\end{lemma}
+
 \begin{proof}
-  We show that \RealPKIDIDAtala UC-realizes \IdealGPKIDID, when configured
-  with policy $\P_{Atala}$. For this, we give a simulator \Sim such that, for
-  any environment \Env, $\Exec_{\RealPKIDIDAtala\adv,\Env} \approx
-  \Exec_{\phiDID,\Sim,\Env}$,
-  where \phiDID is a protocol composed with the same parties as
-  \RealPKIDIDAtala but where each party is simply a dummy party that forwards
-  every message from \Env to the ideal functionality \IdealGPKIDID, and every
-  response from \IdealGPKIDID back to \Env. The simulator \Sim runs internally a
-  copy of the real-world adversary \adv, as well as the ideal functionalities
-  \IdealGRO, \IdealFSig and \IdealGdledger, and any involved party.
+  \qed
+\end{proof}
 
-  \begin{description}
-  \item[Simulating DID Create.] %
-    % 
-    % Keys generation
-    If \Sim receives a message $(\uccmd{Create},\sid,\lbrace (\lbl_i,\typ_i)
-    \rbrace_{i\in[n]})$ from \IdealGPKIDID, with $\sid=(P,\sid')$, it simulates
-    the key generation process of $n$ signing key pairs run in the real
-    protocol, by sending $n$ queries $(\uccmd{KeyGen},((P,\lbl_i),\sid))$ to
-    \adv~on behalf of \IdealFSig, and receiving the $n$ corresponding
-    $(\uccmd{VerKey},((P,\lbl_i),\sid),\pk_i)$ responses.
-    %
-    % Hash computation
-    \Sim then concatenates all $(\lbl_i,\typ_i,\pk_i)$ tuples into \st, and
-    simulates a query to \IdealGRO, to set \did as ``$did:prism: h$'' as DID
-    value.
-    %
-    % Tx sim
-    With the DID value, \Sim simulates for \adv~the preparation of transaction
-    \tx. That is, \Sim uses the master key with lowest label, $\lbl \gets
-    \LMKL(\st)$, and simulates a query $(\uccmd{Sign},((P,\lbl),\sid),\tx)$ to
-    \IdealFSig, obtaining from \adv~$(\uccmd{Signed},((P,\lbl),\sid),\tx,\sig)$.
-    %
-    % BB append
-    \Sim also simulates appending the $(\tx,\sig)$ tuple to the bulletin board,
-    by sending $(\uccmd{Append},(\tx,\sig))$ to \adv~on behalf of \IdealGdledger.
-    %
-    % Output
-    Finally, \Sim sends the $(\uccmd{CreateOk},\sid,\did,\lbrace \pk_i
-    \rbrace_{i\in[n]})$ to \IdealGPKIDID, and stores the tuple $(P,\did,\lbrace
-    (\lbl_i,\typ_i,\pk_i)\rbrace_{i\in[n]})$.
-    %
-    % Additional considerations
-    \todo{The following should probably go to the argumentation part.}
-    Note that \did is generated by an ideal random oracle (thus, uniformly at
-    random), just as in the real protocol \RealPKIDIDAtala. Hence, the
-    probability that \IdealGPKIDID halts because $\did \in \DID$ is negligible,
-    and \IdealGPKIDID outputs $(\uccmd{Created},\sid,\did,\lbrace \val_i=\pk_i
-    \rbrace_{i\in[n]})$ to \IdealGPKIDID.
-  \item[Simulating DID Read.]
-    To simulate read operations, when \Sim receives $(\uccmd{Read},\sid,\did)$
-    from \IdealGPKIDID, it first simulates for \adv~the call to \IdealGdledger, to
-    get the current status $L$ of the bulletin board. Then, \Sim reproduces the
-    processing a normal party would do: from older to newer entry in $L$ related
-    to \did, applies the updates in a sequential order -- ignoring any
-    \uccmd{UpdateDID} operation before a \uccmd{CreateDID}, and only applying
-    the first \uccmd{CreateDID}. If, after applying an update, $\P_{Atala}$ is
-    not met by the resulting set of keys and labels, \Sim skips the update.
-    Otherwise, \Sim simulates for \adv~a verification query to \IdealFSig for
-    the transaction corresponding to the update, and skips the update if the
-    signature fails.
-    %
-    Finally, if after processing all transactions related to \did, the resulting
-    contents differ from those stored by \Sim in its record $(P,\did,\sval)$,
-    \Sim aborts \todo{Do we need this?}. Otherwise, \Sim returns the processed
-    contents.    
-  \item[Simulating DID Update.]
-    % Load DID
-    Upon receiving a request from dummy party $P$, \IdealGPKIDID fetches
-    $(P,\did,\sval)$ from its records, and checks if $(\sval \setminus \sval_d)
-    \cup \sval_a$ meets $\P_{Atala}$. If either step fails, \IdealGPKIDID
-    aborts. Else, it sends $(\uccmd{Update},\sid,\did,\sval_d,\sval_a)$ to \Sim.
-    \Sim then retrieves $(P,\did,\sval)$ from its records \todo{this is kept at
-      some point, no?)} and simulates for \adv~the calls to \IdealFSig for the
-    keys in the received $\sval_a$. \Sim gets the key with the lowest label from
-    \sval, with label $\lbl$, bundles the transaction \tx, and simulates a call
-    to \IdealFSig to get a signature over \tx. Finally, \Sim simulates the call
-    to \IdealGdledger, and returns $(\uccmd{Updated},\sid,(\did,\lbrace \val_i
-    \rbrace_{i\in[n_a]}))$ to \IdealGPKIDID, where the $\val_i$'s are the values
-    output by \adv~when creating the new keys via simulated calls to \IdealFSig.
-  \item[Simulating DID Deactivate.] Directly follows from DID Update.      
-  \end{description}
-  \todo{This to take into account when arguing indistinguishability}:
-  \begin{itemize}
-  \item The records of \Sim are always consistent with \IdealGdledger.
-  \end{itemize}
+% Before going into the proofs, observe that the \uccmd{Create} (in lines 1-2) and
+% \uccmd{Update} (in lines 6-7) operations in \RealPKIDIDAtala include a policy on
+% the received key labels and types. Concretely, this policy requires that all
+% labels are unique, all types are of a known key type, and that at least one of
+% them is of type \MasterKey. In the sequel, we use \PAtala to refer to this
+% policy.
 
-  % General comments
-  Now, observe that, in all ideal operations, the policy $\P_{Atala}$ is checked
-  on the resulting data structure. If the policy is not satisfied, the
-  functionality aborts. This is also the case for the real world.
+% \todo{Do we mention somewhere that {\sid}s have structure $(P,\sid')$? This is
+%   used for \Sim to know which party is generating which keys.}
 
-  % Create comments
-  Regarding create operations, note that, both in the simulation and in the real
-  world, the resulting \did value is produced in a consistent way -- via a call
-  to \IdealGRO, using the contents of the DID document to create.
-  % Key generation and signature comments
-  Similarly, the (verification) keys used and signatures are defined by \adv~
-  both the real and ideal world -- in the latter, as part of \Sim's simulation
-  of \IdealFSig.
+% \begin{theorem}[UC-security of \RealPKIDIDAtala]
+%   \label{thm:sec-didatala}
+%   \RealPKIDIDAtala UC-realizes $\IdealGPKIDID$ in the $(\IdealGRO,
+%   \IdealFSig, \IdealGdledger)$-hybrid model.
+% \end{theorem}
 
-\end{proof}
+% \begin{proof}
+%   We show that \RealPKIDIDAtala UC-realizes \IdealGPKIDID, when configured
+%   with policy \PAtala. For this, we give a simulator \Sim such that, for
+%   any environment \Env, $\Exec_{\RealPKIDIDAtala\adv,\Env} \approx
+%   \Exec_{\phiDID,\Sim,\Env}$,
+%   where \phiDID is a protocol composed with the same parties as
+%   \RealPKIDIDAtala but where each party is simply a dummy party that forwards
+%   every message from \Env to the ideal functionality \IdealGPKIDID, and every
+%   response from \IdealGPKIDID back to \Env. The simulator \Sim runs internally a
+%   copy of the real-world adversary \adv, as well as the ideal functionalities
+%   \IdealGRO, \IdealFSig and \IdealGdledger, and any involved party.
+
+%   \begin{description}
+%   \item[Simulating DID Create.] %
+%     % 
+%     % Keys generation
+%     If \Sim receives a message $(\uccmd{Create},\sid,\lbrace (\lbl_i,\typ_i)
+%     \rbrace_{i\in[n]})$ from \IdealGPKIDID, with $\sid=(P,\sid')$, it simulates
+%     the key generation process of $n$ signing key pairs run in the real
+%     protocol, by sending $n$ queries $(\uccmd{KeyGen},((P,\lbl_i),\sid))$ to
+%     \adv~on behalf of \IdealFSig, and receiving the $n$ corresponding
+%     $(\uccmd{VerKey},((P,\lbl_i),\sid),\pk_i)$ responses.
+%     %
+%     % Hash computation
+%     \Sim then concatenates all $(\lbl_i,\typ_i,\pk_i)$ tuples into \st, and
+%     simulates a query to \IdealGRO, to set \did as ``$did:prism: h$'' as DID
+%     value.
+%     %
+%     % Tx sim
+%     With the DID value, \Sim simulates for \adv~the preparation of transaction
+%     \tx. That is, \Sim uses the master key with lowest label, $\lbl \gets
+%     \LMKL(\st)$, and simulates a query $(\uccmd{Sign},((P,\lbl),\sid),\tx)$ to
+%     \IdealFSig, obtaining from \adv~$(\uccmd{Signed},((P,\lbl),\sid),\tx,\sig)$.
+%     %
+%     % BB append
+%     \Sim also simulates appending the $(\tx,\sig)$ tuple to the bulletin board,
+%     by sending $(\uccmd{Submit},(\tx,\sig))$ to \adv~on behalf of \IdealGdledger.
+%     %
+%     % Output
+%     Finally, \Sim sends the $(\uccmd{CreateOk},\sid,\did,\lbrace \pk_i
+%     \rbrace_{i\in[n]})$ to \IdealGPKIDID, and stores the tuple $(P,\did,\lbrace
+%     (\lbl_i,\typ_i,\pk_i)\rbrace_{i\in[n]})$.
+%     %
+%     % Additional considerations
+%     \todo{The following should probably go to the argumentation part.}
+%     Note that \did is generated by an ideal random oracle (thus, uniformly at
+%     random), just as in the real protocol \RealPKIDIDAtala. Hence, the
+%     probability that \IdealGPKIDID halts because $\did \in \DID$ is negligible,
+%     and \IdealGPKIDID outputs $(\uccmd{Created},\sid,\did,\lbrace \val_i=\pk_i
+%     \rbrace_{i\in[n]})$ to \IdealGPKIDID.
+%   \item[Simulating DID Read.]
+%     To simulate read operations, when \Sim receives $(\uccmd{Read},\sid,\did)$
+%     from \IdealGPKIDID, it first simulates for \adv~the call to \IdealGdledger, to
+%     get the current status $L$ of the bulletin board. Then, \Sim reproduces the
+%     processing a normal party would do: from older to newer entry in $L$ related
+%     to \did, applies the updates in a sequential order -- ignoring any
+%     \uccmd{UpdateDID} operation before a \uccmd{CreateDID}, and only applying
+%     the first \uccmd{CreateDID}. If, after applying an update, \PAtala is
+%     not met by the resulting set of keys and labels, \Sim skips the update.
+%     Otherwise, \Sim simulates for \adv~a verification query to \IdealFSig for
+%     the transaction corresponding to the update, and skips the update if the
+%     signature fails.
+%     %
+%     Finally, if after processing all transactions related to \did, the resulting
+%     contents differ from those stored by \Sim in its record $(P,\did,\sval)$,
+%     \Sim aborts \todo{Do we need this?}. Otherwise, \Sim returns the processed
+%     contents.    
+%   \item[Simulating DID Update.]
+%     % Load DID
+%     Upon receiving a request from dummy party $P$, \IdealGPKIDID fetches
+%     $(P,\did,\sval)$ from its records, and checks if $(\sval \setminus \sval_d)
+%     \cup \sval_a$ meets \PAtala. If either step fails, \IdealGPKIDID
+%     aborts. Else, it sends $(\uccmd{Update},\sid,\did,\sval_d,\sval_a)$ to \Sim.
+%     \Sim then retrieves $(P,\did,\sval)$ from its records \todo{this is kept at
+%       some point, no?)} and simulates for \adv~the calls to \IdealFSig for the
+%     keys in the received $\sval_a$. \Sim gets the key with the lowest label from
+%     \sval, with label $\lbl$, bundles the transaction \tx, and simulates a call
+%     to \IdealFSig to get a signature over \tx. Finally, \Sim simulates the call
+%     to \IdealGdledger, and returns $(\uccmd{Updated},\sid,(\did,\lbrace \val_i
+%     \rbrace_{i\in[n_a]}))$ to \IdealGPKIDID, where the $\val_i$'s are the values
+%     output by \adv~when creating the new keys via simulated calls to \IdealFSig.
+%   \item[Simulating DID Deactivate.] Directly follows from DID Update.      
+%   \end{description}
+%   \todo{This to take into account when arguing indistinguishability}:
+%   \begin{itemize}
+%   \item The records of \Sim are always consistent with \IdealGdledger.
+%   \end{itemize}
+
+%   % General comments
+%   Now, observe that, in all ideal operations, the policy \PAtala is checked
+%   on the resulting data structure. If the policy is not satisfied, the
+%   functionality aborts. This is also the case for the real world.
+
+%   % Create comments
+%   Regarding create operations, note that, both in the simulation and in the real
+%   world, the resulting \did value is produced in a consistent way -- via a call
+%   to \IdealGRO, using the contents of the DID document to create.
+%   % Key generation and signature comments
+%   Similarly, the (verification) keys used and signatures are defined by \adv~
+%   both the real and ideal world -- in the latter, as part of \Sim's simulation
+%   of \IdealFSig.
+
+% \end{proof}
 

### 2022-12-20 prism-backend/research/prism-protocol/did_atala.tex
Proving UC security of Atala DIDs.

@@
 
-At a high level, to apply the results in \cite{bch+20,bzh21}, we show the global
+At a high level, to apply the results in \cite{bch+20,bhz21}, we show the global
 subroutines used in \IdealGPKIDID and \RealPKIDIDAtala can be merged into the
@@
 usually the case for the known realisations of each respective global
-subroutine. (This ensures that our approach is natural, and indeed UC-realisable
-in practice.)
+subroutine. (This suggests that our approach is natural, and indeed
+UC-realisable in practice.)
 %
 We then describe how the management protocol \UCM works in conjunction with
-our \IdealGPKIDID and the ``meta'' global subroutines (in the ideal world), and
-with \RealPKIDIDAtala and the ``meta'' global subroutine (in the real world).
+our \IdealGPKIDID and the ``meta'' global subroutines in the ideal world (i.e.,
+$\UCM[\IdealGPKIDID,\hat{\gamma}_{\gamma_1,\dots,\gamma_n}]$), and
+with \RealPKIDIDAtala and the ``meta'' global subroutine in the real world
+(i.e., $\UCM[\RealPKIDIDAtala,\hat{\gamma}_{\gamma_1,\dots,\gamma_n}]$).
 %
-Finally, we show that the latter emulates the former.
+Finally, we show that the latter emulates the former. This concludes the proof
+for \thmref{thm:uc-bhz21}.
 %
@@
 \cite{bch+20,bhz21} to our setting. The previously sketched process is detailed
-next, directly referencing the relevant theorems of the relevant works, when
+next, directly referencing the relevant theorems of the corresponding works when
 appropriate.
@@
 \paragraph{The meta-global subroutine \gAtala.} %
+\todo{The idea is here, but the wording is clumsy. Re-write.}
 We next show that the global subroutines used in \RealPKIDIDAtala are leveraged
 in a way that is compatible with \cite[Theorem 4.3]{bhz21}. This is not a full
-proof for a concrete application of such theorem, as that would require proving
+proof for a concrete application of the theorem, as that would require proving
 that concrete protocols UC-emulate each global functionality. However, we
@@
 
-\begin{lemma}[Mergability of \gAtala]
+\begin{lemma}[Mergeability of \gAtala]
   \label{lma:gAtala}
+
   Let $\gamma_1 \gets \IdealGdledger$, $\gamma_2 \gets \IdealGRO$, $\gamma_3
   \gets \IdealGclock$. Then:
+
   \begin{enumerate}
@@
   \item For $i>1$, $\gamma_i$ is $\gamma_j$-regular, for all $j \in \set{1,
-    \dots,\i-1}$.
+      \dots,i-1}$.
   \end{enumerate}
+
 \end{lemma}
@@
 \begin{proof}
+  \todo{In the sequel, when the $\gamma_i$'s should be protocols, not ideal
+    functionalities; e.g., $\gamma_3 = \IdealP_{\IdealGclock}$, not
+    $\IdealGclock$ (the argument should be ok, it is just a wording error).}
+  We start with the first item, for which we briefly recall the notion of
+  subroutine respecting protocols. Intuitively, a protocol $\pi$ is subroutine
+  respecting if, for any session \sid of $\pi$, the main parties of \sid are the
+  only ones that communicate with the outside world; this also means that
+  subparties only accept input and subroutine output from parties in \sid. A
+  more precise definition is available in the 2020 version of \cite{canetti00}.
+
+  Now, the protocol $\IdealP_\IdealF$ associated to an ideal functionality
+  \IdealF is composed of dummy parties that simply relay information back and
+  forth between the environment \Env and \IdealF (and no one else). The dummy
+  parties are the main parties of $\IdealP_\IdealF$, whereas \IdealF is a
+  sub-party.
+
+  In the case of \IdealGclock ($\gamma_3$) and \IdealGRO ($\gamma_2$), their
+  corresponding protocols, $\IdealP_{\IdealGclock}$ and $\IdealP_{\IdealGRO}$
+  are trivially subroutine respecting. Namely, for each session \sid of
+  $\IdealP_{\IdealGclock}$ (resp. $\IdealP_{\IdealGRO}$):
+
+  \begin{itemize}
+  \item \IdealGclock (resp. \IdealGRO) is the only sub-party in the protocol
+    session \sid, and it only accepts input from the main (dummy) parties in
+    $\IdealP_{\IdealGclock}$ (resp. $\IdealP_{\IdealGRO}$) in \sid.
+  \item The main (dummy) parties of session \sid in $\IdealP_{\IdealGclock}$
+    (resp. $\IdealP_{\IdealGRO}$) ignore subroutine outputs from parties other
+    than \IdealGclock (resp. \IdealGRO)'s on session \sid. Similarly,
+    \IdealGclock (resp. \IdealGRO) ignores subroutine outputs.
+  \item \IdealGclock (resp. \IdealGRO) in \sid only passes subroutine output to
+    the main (dummy) parties in \sid.
+  \item Main (dummy) parties in session \sid of $\IdealP_{\IdealGclock}$ (resp.
+    $\IdealGRO$), and \IdealGclock (resp. \IdealGRO)  don't pass input to
+    parties not in \sid. 
+  \end{itemize}
+
+  Next, observe that \IdealGdledger ($\gamma_1$) is also subroutine respecting
+  except for calls to \IdealGclock ($\gamma_3$). Concretely, for each session
+  of the ideal protocol $\IdealP_{\IdealGdledger}$ of \IdealGdledger:
+
+  \begin{itemize}
+  \item Excluding calls to \IdealGclock, \IdealGdledger is the only sub-party in
+    the protocol session \sid, and it only accepts input from the main (dummy)
+    parties in $\IdealP_{\IdealGdledger}$ in \sid.
+  \item The main (dummy) parties of session \sid in $\IdealP_{\IdealGdledger}$
+    ignore subroutine outputs from parties other than \IdealGdledger's on
+    session \sid. Also, \IdealGdledger ignores subroutine outputs from any
+    party, with the exception from parties in \IdealGclock.
+  \item \IdealGdledger in \sid only passes subroutine output to the main (dummy)
+    parties of $\IdealP_{\IdealGdledger}$, and to the parties in \IdealGclock,
+    in \sid.
+  \item Main (dummy) parties in session \sid of $\IdealP_{\IdealGdledger}$ and
+    \IdealGdledger don't pass input to parties not in \sid, with the exception
+    of parties in $\IdealP_{\IdealGclock}$.
+  \end{itemize}
+
+  In summary, $\gamma_3 = \IdealGclock$ and $\gamma_2 = \IdealGRO$ are
+  subroutine respecting (and, obviously, $\gamma_2$ is also subroutine
+  respecting except for calls to $\gamma_3$). Also, $\gamma_1 = \IdealGdledger$
+  is subroutine respecting except for calls to $\gamma_3$ -- and, since
+  $\gamma_1$ does not use $\gamma_2$, it is trivially also subroutine respecting
+  except for calls to $\gamma_2$ and $\gamma_3$.
+
+  Thus, condition 1 of \lmaref{lma:gAtala} is met. Now, we move to condition 2.
+
   \qed
 \end{proof}
+
+\paragraph{The management protocol $\UCM[\IdealGPKIDID,\gAtala]$.}
+
+\paragraph{The management protocol $\UCM[\RealPKIDIDAtala,\gAtala]$.}
+
+\paragraph{$\UCM[\IdealGPKIDID,\gAtala]$ $\xi$-UC emulates
+  $\UCM[\RealPKIDIDAtala,\gAtala]$.}
 

### 2022-12-20 prism-backend/research/prism-protocol/preliminaries.tex
Proving UC security of Atala DIDs.

@@
       h \getr \bin^{l}; \hashlist \gets \hashlist \cup \lbrace (\msg,h) \rbrace \\
-      \ucio{Output}~(\uccmd{HashConfirm},h)
+      \ucio{Output}~(\uccmd{HashConfirm},\sid,h)
     }
@@
     \begin{minipage}[t]{\textwidth}
-      \textrm{Upon receiving a call $\IdealGclock(\cmd,\arg)$ from
-        some party $P$ to run command \cmd, with arguments \arg,
-        \IdealGclock operates as follows.} \\
-      \textrm{\IdealGclock maintains a variable $t$ with the current itme,
+      \textrm{Upon receiving a call $\IdealGclock(\cmd,\sid,\arg)$ from
+        some party $P$ to run command \cmd, in session \sid, with arguments
+        \arg, \IdealGclock operates as follows.} \\
+      \textrm{\IdealGclock maintains a variable $t$ with the current time,
         a variable $T$ with the list of parties keeping track of the time,
@@
         T \gets T \cup \set{P} \\
-        \ucio{Output}~(\uccmd{Registered})~\text{to}~P \\
+        \ucio{Output}~(\uccmd{Registered},\sid)~\text{to}~P \\
       }
@@
         \pcind t \gets t + 1; \forall P \in T, A(P) = \bot \\
-        \pcind \ucio{Send}~(\uccmd{Updated})~\text{to}~P        
+        \pcind \ucio{Send}~(\uccmd{Updated},\sid)~\text{to}~P        
       }
@@
         T \gets T \setminus \set{P} \\
-        \text{Output}~(\uccmd{DeregisteredOk})~\text{to}~P \\
+        \text{Output}~(\uccmd{DeregisteredOk},\sid)~\text{to}~P \\
       }
       \procedure{$\pcif \cmd = \uccmd{Read} \land \arg = \emptyset$}{
-        \text{Output}~(\uccmd{ReadOk},t)~\text{to}~P
+        \text{Output}~(\uccmd{ReadOk},\sid,t)~\text{to}~P
       }
@@
     \begin{minipage}[t]{\textwidth}
-      \textrm{Upon receiving a call $\IdealGdledger(\cmd,\arg)$ from
-        some party $P$ to run command \cmd, with arguments \arg,
-        \IdealGdledger operates as follows.} \\
+      \textrm{Upon receiving a call $\IdealGdledger(\cmd,\sid,\arg)$ from
+        some party $P$ to run command \cmd, in session \sid, with arguments
+        \arg, \IdealGdledger operates as follows.} \\
       \textrm{\IdealGdledger maintains a mapping \ldgMap which associates
@@
       \procedure{$\pcif \cmd = \uccmd{Submit} \land \arg = \ldgTx$}{
-        \ucio{Send}~(\uccmd{Read})~\text{to}~\IdealGclock \\
-        \ucio{Recv}~(\uccmd{ReadOk},t)~\text{from}~\IdealGclock \\
+        \ucio{Send}~(\uccmd{Read},\sid)~\text{to}~\IdealGclock \\
+        \ucio{Recv}~(\uccmd{ReadOk},\sid,t)~\text{from}~\IdealGclock \\
         \ldgUtxo \gets \ldgUtxo \cup \set{(\ldgTx,t)} \\ 
-        \ucio{Output}~(\uccmd{Transaction},\ldgTx,t)~\text{to}~\adv \\
+        \ucio{Output}~(\uccmd{Submitted},\sid,\ldgTx,t)~\text{to}~\adv \\
       }
@@
         % \pcelse: data \gets \ldgMap(P) \\
-        \ucio{Send}~(\uccmd{Read})~\text{to}~\IdealGclock \\
-        \ucio{Recv}~(\uccmd{ReadOk},t)~\text{from}~\IdealGclock \\
+        \ucio{Send}~(\uccmd{Read},\sid)~\text{to}~\IdealGclock \\
+        \ucio{Recv}~(\uccmd{ReadOk},\sid,t)~\text{from}~\IdealGclock \\
         \pcif \exists (\ldgTx,t') \in \ldgUtxo~\suchthat~|t-t'| > \delta:
@@
         \pcreturn \bot \\        
-        \text{Output}~(\uccmd{ReadOk}, \ldgHead(\ldgMap(P)))~\text{to}~P \\
+        \text{Output}~(\uccmd{ReadOk},\sid,\ldgHead(\ldgMap(P)))~\text{to}~P \\
       }

### 2022-12-21 prism-backend/research/prism-protocol/did_atala.tex
.

@@
 \subsubsection{Notes for Implementations.} %
-
+\todo{This needs updating. However, keeping it here until I confirm.}
 We acknowledge that, in the pseudocode given in \figref{fig:atalapkidid1} and
@@
 \label{ssec:sec-didatala}
+
+\commentwho{Jesus}{What follows is essentially right on its own, but I interpreted
+  \cite{bhz21} somehow wrongly. The approach is: (1) merge all (ideal) global
+  subroutines (ledger, RO, clock) into one (\gAtala); (2) prove that theorem 1
+  below is met, where the real protocol is \RealPKIDIDAtala, and the ideal
+  (global) functionality is \IdealGPKIDID -- although we can ignore that it is
+  a global functionality here. Then, it would be nice to prove that Cardano as
+  instantiation of the ledger, and whatever else for RO and clock, allow to
+  instantiate the merged global subroutine (this is what I've mostly done next,
+  to some extent). So, basically, revert the order of what I was trying to do.}
 
@@
 
-\begin{lemma}[Mergeability of \gAtala]
+\begin{lemma}[Mergeability of \gAtala \todo{``Mergeability'' may not be the
+    best term}]
   \label{lma:gAtala}
+
+  % Let $\gamma_1 \gets \IdealGPKIDID$, $\gamma_2 \gets \IdealGdledger$,
+  % $\gamma_3 \gets \IdealGRO$, $\gamma_4 \gets \IdealGclock$. Then:
 
@@
 \begin{proof}
-  \todo{In the sequel, when the $\gamma_i$'s should be protocols, not ideal
-    functionalities; e.g., $\gamma_3 = \IdealP_{\IdealGclock}$, not
-    $\IdealGclock$ (the argument should be ok, it is just a wording error).}
   We start with the first item, for which we briefly recall the notion of
@@
 
+  % The same argument as for \IdealGdledger applies for \IdealGPKIDID, since it
+  % also leverages \IdealGclock ($\gamma_4$) in its definition.
+
   In summary, $\gamma_3 = \IdealGclock$ and $\gamma_2 = \IdealGRO$ are
@@
   $\gamma_1$ does not use $\gamma_2$, it is trivially also subroutine respecting
-  except for calls to $\gamma_2$ and $\gamma_3$.
+  except for calls to $\gamma_2$.
 
-  Thus, condition 1 of \lmaref{lma:gAtala} is met. Now, we move to condition 2.
+  Thus, condition 1 of \lmaref{lma:gAtala} is met, except for the subroutine
+  exposing part. However, even though it is not explicitly stated in their
+  corresponding definitions, it is possible to transform the \IdealGclock,
+  \IdealGRO and \IdealGdledger (by adding a directory ITI and an extra shell
+  taking care of the proper redirections) so that they are actually subroutine
+  exposing - cf \cite[Definition 2.7]{bch+20}. Now, we move to condition 2.
+  Concretely:
 
+  \begin{itemize}
+  \item $\gamma_2$ is $\gamma_1$-regular: The main (dummy) parties in
+    $\gamma_2$ ($\IdealP_{\IdealGRO}$) do not invoke new ITIs of $\gamma_1$
+    ($\IdealP_{\IdealGdledger}$) via messages to the subroutine output tape.
+    Also, the main (dummy) parties of $\IdealP_{\IdealGRO}$ do not have an ITI
+    with code $\IdealP_{\IdealGdledger}$ as subsidiary.
+  \item $\gamma_3$ is $\gamma_2$-regular: The main (dummy) parties in
+    $\gamma_3$ ($\IdealP_{\IdealGclock}$) do not invoke new ITIs of $\gamma_2$
+    ($\IdealP_{\IdealGRO}$) via messages to the subroutine output tape. Also,
+    the main (dummy) parties of $\IdealP_{\IdealGclock}$ do not have an ITI with
+    code $\IdealP_{\IdealGRO}$ as subsidiary.
+  \item $\gamma_3$ is $\gamma_1$-regular: The main (dummy) parties in
+    $\gamma_3$ ($\IdealP_{\IdealGclock}$) do not invoke new ITIs of $\gamma_1$
+    ($\IdealP_{\IdealGdledger}$) via messages to the subroutine output tape --
+    dummy parties in $\gamma_3$ pass subroutine output to parties in $\gamma_1$,
+    but already existing ones. Also, the main (dummy) parties of
+    $\IdealP_{\IdealGclock}$ do not have an ITI with code
+    $\IdealP_{\IdealGdledger}$ as subsidiary.
+  \end{itemize}
+  %
   \qed

### 2022-12-22 prism-backend/research/prism-protocol/did_atala.tex
Structuring proof strategy.

@@
 
-\commentwho{Jesus}{What follows is essentially right on its own, but I interpreted
-  \cite{bhz21} somehow wrongly. The approach is: (1) merge all (ideal) global
-  subroutines (ledger, RO, clock) into one (\gAtala); (2) prove that theorem 1
-  below is met, where the real protocol is \RealPKIDIDAtala, and the ideal
-  (global) functionality is \IdealGPKIDID -- although we can ignore that it is
-  a global functionality here. Then, it would be nice to prove that Cardano as
-  instantiation of the ledger, and whatever else for RO and clock, allow to
-  instantiate the merged global subroutine (this is what I've mostly done next,
-  to some extent). So, basically, revert the order of what I was trying to do.}
+We now prove that \RealPKIDIDAtala $\xi$-UC-emulates \IdealGPKIDID, in the
+presence of global subroutines \IdealGclock, \IdealGRO, and \IdealGdledger.
+Given that (multiple) global subroutines are involved, the proving process
+requires several steps, which we summarise first, and then specify in detail. In
+this process, we rely on recent results in \cite{bch+20,bhz21} as well as,
+naturally, on the UC framework \cite{canetti00}. In a nutshell, the steps we
+take are as follows (here, we are intentionally imprecise on occasions, in
+favour of giving a high-level idea of the overall approach):
+
+\todo{Some diagram would probably help much here.}
+\begin{enumerate}
+\item \emph{(Merging global subroutines into \gAtala)} Following the strategy
+  in \cite{bhz21}, we combine all the global subroutines needed in our protocols
+  into a single (equivalent) one. While merely ``bureaucratic'', this
+  facilitates the analysis in subsequent steps. We refer to this combined
+  global shared subroutine as \gAtala.
+\item \emph{(\gAtala is subroutine respecting)} We show that only main ITIs
+  in \gAtala accept input from ITIs not in \gAtala, no ITI within \gAtala passes
+  input to ITIs not in \gAtala, no ITI in \gAtala expects subroutine output from
+  other ITIs outside of \gAtala, and all subroutine outputs produced within
+  \gAtala are sent to the outside world via \gAtala's main ITIs.
+\item \emph{(\RealPKIDIDAtala is \gAtala-subroutine respecting)} We show that
+  \RealPKIDIDAtala is also subroutine respecting, as just described for \gAtala,
+  except actually for calls to \gAtala. This means that ITIs within
+  \RealPKIDIDAtala may communicate directly with machines in \gAtala without
+  needing to ``pass through'' the main ITIs of \RealPKIDIDAtala, and can
+  communicate with them even if they are not part of \RealPKIDIDAtala's session.
+\item \emph{(\IdealGPKIDID is \gAtala-subroutine respecting)} Same as before,
+  but with \IdealGPKIDID.
+\item \emph{(\gAtala is \RealPKIDIDAtala-regular)} We show that ITIs in \gAtala
+  do not invoke new ITIs of \RealPKIDIDAtala as subroutines, nor call or expect
+  subroutine output from machines of \RealPKIDIDAtala.
+\item \emph{(\gAtala is \IdealGPKIDID-regular)} Same as before, but with
+  \IdealGPKIDID.
+\item \emph{(Executions of $\UCM[\RealPKIDIDAtala,\gAtala]$ are indistinguishable
+    from execution of \RealPKIDIDAtala in the presence of \gAtala)} Given the
+  previous preconditions, \cite[Proposition 3.4]{bch+20} ensures that we can
+  safely apply a transformation $\UCM[\cdot,\cdot]$ to \RealPKIDIDAtala, which
+  allows to leverage the techniques from the plain UC framework.
+\item \emph{(Executions of $\UCM[\IdealGPKIDID,\gAtala]$ are indistinguishable
+    from execution of \IdealGPKIDID in the presence of \gAtala)} Same as before,
+  but with \IdealGPKIDID.
+\item \emph{(\RealPKIDIDAtala $\xi$-UC-emulates \IdealGPKIDID in the presence
+    of \gAtala)} By \cite[Definition 3.1]{bch+20}, if $\UCM[\RealPKIDIDAtala,
+  \gAtala]$ $\xi$-UC-emulates $\UCM[\IdealGPKIDID,\gAtala]$, then
+  \RealPKIDIDAtala $\xi$-UC-emulates \IdealGPKIDID, in the presence
+  of \gAtala.
+\end{enumerate}
+
+We now proceed to specify in more detail the previous steps.
+
+\paragraph{1. Merging global subroutines into \gAtala.} This transformation
+is straightforward, and can be done as in \cite[Definition 4.1]{bhz21}. Namely,
+let $\gamma_1 \gets \IdealGledger$, $\gamma_2 \gets \IdealGRO$, and $\gamma_3
+\gets \IdealGclock$. Then, we define \gAtala to be a functionality that simply
+accepts inputs of type $(\uccmd{query},\sid,i,x)$, and makes a query to
+$\gamma_i$, with input $x$ on session \sid -- e.g., a query $(\uccmd{query},
+\sid,2,(\uccmd{HasQuery},m))$ results in a query $(\uccmd{HashQuery},\sid,m)$ to
+\IdealGRO.
+%
+This allows us to directly apply the results in \cite{bch+20}. \todo{Later, we
+  will get back to arguing that the usual candidates for UC-realising the
+  individual $\gamma_i$'s meet certain properties that make them suitable for
+  UC-realising the ``merged'' functionality \gAtala. Thus, our main results
+  apply when considering real instantiations of the global subroutines, rather
+  than their idealised counterparts.}
+
+\paragraph{2. \gAtala is subroutine respecting.}
+
+\commentwho{Jesus}{Not removing what follows for now,  because it will be
+  useful. But keep on the proof process stated in the previous enumeration.}
 
@@
 
-At a high level, to apply the results in \cite{bch+20,bhz21}, we show the global
-subroutines used in \IdealGPKIDID and \RealPKIDIDAtala can be merged into the
-single ``meta'' global subroutine $\hat{\gamma}_{\gamma_1,\dots,\gamma_n}$
-required by \thmref{thm:uc-bhz21}, which furthermore meets the conditions to be
-subsequently suitable for UC-emulation. In addition, we argue that this is
+At a high level, to apply the results in \cite{bch+20,bhz21}, we merge the
+global subroutines used in \IdealGPKIDID and \RealPKIDIDAtala into a single
+``meta'' global subroutine $\gAtala = \hat{\gamma}_{\gamma_1,\dots,\gamma_n}$
+required by \thmref{thm:uc-bhz21}.
+%
+Then, to prove UC emulation, we follow the approach in \cite{bch+20} and
+describe a management protocol \UCM
+
+which furthermore meets the conditions to be
+subsequently suitable for UC-emulation. In addition, we later argue that this is
 usually the case for the known realisations of each respective global

### 2023-01-04 prism-backend/research/prism-protocol/did_atala.tex
Updated steps in the proof.

@@
 We now prove that \RealPKIDIDAtala $\xi$-UC-emulates \IdealGPKIDID, in the
-presence of global subroutines \IdealGclock, \IdealGRO, and \IdealGdledger.
+presence of global subroutines \IdealGclock, \IdealGRO, and \IdealGdledger,
+as well as local digital signatures functionality \IdealFSig.
 Given that (multiple) global subroutines are involved, the proving process
@@
 \item \emph{(Executions of $\UCM[\RealPKIDIDAtala,\gAtala]$ are indistinguishable
-    from execution of \RealPKIDIDAtala in the presence of \gAtala)} Given the
+    from executions of \RealPKIDIDAtala in the presence of \gAtala)} Given the
   previous preconditions, \cite[Proposition 3.4]{bch+20} ensures that we can
@@
 \item \emph{(Executions of $\UCM[\IdealGPKIDID,\gAtala]$ are indistinguishable
-    from execution of \IdealGPKIDID in the presence of \gAtala)} Same as before,
+    from executions of \IdealGPKIDID in the presence of \gAtala)} Same as before,
   but with \IdealGPKIDID.
@@
 $\gamma_i$, with input $x$ on session \sid -- e.g., a query $(\uccmd{query},
-\sid,2,(\uccmd{HasQuery},m))$ results in a query $(\uccmd{HashQuery},\sid,m)$ to
-\IdealGRO.
+\sid,2,(\uccmd{HashQuery},m))$ results in a query $(\uccmd{HashQuery},\sid,m)$
+to \IdealGRO.
 %
@@
 
-\paragraph{2. \gAtala is subroutine respecting.}
+\paragraph{2. \gAtala is subroutine respecting.} We start by observing that
+all of the $\gamma_i$'s that compose \gAtala are subroutine respecting.
+Concretely, on the one hand:
 
-\commentwho{Jesus}{Not removing what follows for now,  because it will be
+\begin{itemize}
+\item \IdealGclock (resp. \IdealGRO) is the only sub-party in the protocol
+  session \sid, and it only accepts input from the main (dummy) parties in
+  $\IdealP_{\IdealGclock}$ (resp. $\IdealP_{\IdealGRO}$) in \sid.
+\item The main (dummy) parties of session \sid in $\IdealP_{\IdealGclock}$
+  (resp. $\IdealP_{\IdealGRO}$) ignore subroutine outputs from parties other
+  than \IdealGclock (resp. \IdealGRO)'s on session \sid. Similarly,
+  \IdealGclock (resp. \IdealGRO) ignores subroutine outputs.
+\item \IdealGclock (resp. \IdealGRO) in \sid only passes subroutine output to
+  the main (dummy) parties in \sid.
+\item Main (dummy) parties in session \sid of $\IdealP_{\IdealGclock}$ (resp.
+  $\IdealP_{\IdealGRO}$), and \IdealGclock (resp. \IdealGRO)  don't pass input
+  to parties not in \sid. 
+\end{itemize}
+
+On the other hand, \IdealGdledger ($\gamma_1$) is also subroutine respecting
+except for calls to \IdealGclock ($\gamma_3$). Concretely, for each session
+of the ideal protocol $\IdealP_{\IdealGdledger}$ of \IdealGdledger:
+
+\begin{itemize}
+\item Excluding calls to \IdealGclock, \IdealGdledger is the only sub-party in
+  the protocol session \sid, and it only accepts input from the main (dummy)
+  parties in $\IdealP_{\IdealGdledger}$ in \sid.
+\item The main (dummy) parties of session \sid in $\IdealP_{\IdealGdledger}$
+  ignore subroutine outputs from parties other than \IdealGdledger's on
+  session \sid. Also, \IdealGdledger ignores subroutine outputs from any
+  party, with the exception from parties in \IdealGclock.
+\item \IdealGdledger in \sid only passes subroutine output to the main (dummy)
+  parties of $\IdealP_{\IdealGdledger}$, and to \IdealGclock, in \sid.
+\item Main (dummy) parties in session \sid of $\IdealP_{\IdealGdledger}$ and
+  \IdealGdledger don't pass input to parties not in \sid, with the exception
+  of parties in $\IdealP_{\IdealGclock}$.
+\end{itemize}
+
+In \gAtala, the main (dummy) parties of each $\gamma_i$ become main (dummy)
+parties of \gAtala. Thus, from the previous, it is easy to see that \gAtala is
+subroutine respecting. \todo{Perhaps add a figure here -- like the one in my
+  notes.}
+
+\paragraph{3. \RealPKIDIDAtala is \gAtala-subroutine respecting.}
+The only parties with which \RealPKIDIDAtala communicates (concretely, via
+passing subroutine requests, or receiving subroutine responses) that do not
+share the same \sid as \RealPKIDIDAtala, are \IdealGclock, \IdealGRO, and
+\IdealGdledger -- all of them bundled within \gAtala. Thus, \RealPKIDIDAtala is
+\gAtala-subroutine respecting.
+
+\paragraph{4. \IdealGPKIDID is \gAtala-subroutine respecting.}
+As in the previous step, the only parties with which \IdealGPKIDID communicates
+that do not share the same \sid as \IdealGPKIDID, is \IdealGclock, which is
+bundled within \gAtala. Thus, \IdealGPKIDID is also \gAtala-subroutine
+respecting.
+
+\paragraph{5. \gAtala is \RealPKIDIDAtala-regular.} No main party of
+\IdealGdledger, \IdealGRO, or \IdealGclock (respectively, $\gamma_1$,
+$\gamma_2$, and $\gamma_3$), invokes a new ITI of \RealPKIDIDAtala via the
+subroutine output tape or has an ITI with code \RealPKIDIDAtala as subsidiary.
+Since \gAtala bundles all $\gamma_i$'s, the same applies to \gAtala, and
+thus \gAtala is \RealPKIDIDAtala-regular.
+
+\paragraph{6. \gAtala is \IdealGPKIDID-regular.} No main party of
+\IdealGdledger, \IdealGRO, or \IdealGclock (respectively, $\gamma_1$,
+$\gamma_2$, and $\gamma_3$), invokes a new ITI of \IdealGPKIDID via the
+subroutine output tape or has an ITI with code \IdealGPKIDID as subsidiary.
+Since \gAtala bundles all $\gamma_i$'s, the same applies to \gAtala, and
+thus \gAtala is \IdealGPKIDID-regular.
+
+\paragraph{7. Executions of $\UCM[\RealPKIDIDAtala,\gAtala]$ are
+  indistinguishable from executions of \RealPKIDIDAtala in the presence of
+  \gAtala.}
+
+\paragraph{8. Executions of $\UCM[\IdealGPKIDID,\gAtala]$ are indistinguishable
+  from executions of \IdealGPKIDID in the presence of \gAtala.}
+
+\paragraph{9. \RealPKIDIDAtala $\xi$-UC-emulates \IdealGPKIDID in the presence
+  of \gAtala.}
+
+\commentwho{Jesus}{Not removing what follows for now,  because it may/will be
   useful. But keep on the proof process stated in the previous enumeration.}

### 2023-07-21 prism-backend/deprecated/research/article.tex
build: try new build system

--- 2021-10-29 prism-backend/research/article.tex
@@
 
-In this section we will informally describe a protocol to create and manage DIDs (\textbf{D}ecentralized textbf{Id}entifiers), that also allows to manage the creation, revocation and presentation of verifiable credentials.
+In this section we will informally describe a protocol to create and manage DIDs (\textbf{D}ecentralized \textbf{Id}entifiers), that also allows to manage the creation, revocation and presentation of verifiable credentials.
 
@@
       This produces strings of the form $\langle{}encoded\_credentials\rangle{}.\langle{}encoded\_signature\rangle{}$. We call these strings as \emph{signed credentials}.
-\item Now, the issuer takes all the signed credentials, and computes a merkle root from them.
-\item The issuer creates an \emph{IssueBatch} event that contains the merkle root, and signs the event with an \emph{issuing key} associated to his publicly known DID. 
+\item Now, the issuer takes all the signed credentials, and computes a Merkle root from them.
+\item The issuer creates an \emph{IssueBatch} event that contains the Merkle root, and signs the event with an \emph{issuing key} associated to his publicly known DID. 
 \textbf{Note}: Today we use the same issuing key for the event signature and the individual credentials signature, but those could be different keys.
 \item The issuer attaches the signed event to the metadata of a transaction and sends it to the blockchain.
-\item The issuer gives to each user their corresponding signed credential along with their associated merkle inclusion proof.
+\item The issuer gives to each user their corresponding signed credential along with their associated Merkle inclusion proof.
 \end{itemize}
 
-Likewise previous protocol events, all parties will process the transaction once confirmed, validate the event signature and timestamp the merkle root with the time associated to the carrier transaction.
+Likewise previous protocol events, all parties will process the transaction once confirmed, validate the event signature and timestamp the Merkle root with the time associated to the carrier transaction.
 
@@
 \item They revoke all the credentials in a batch.
-      This is done by signing a \emph{RevokeBath} event with a \emph{revocation} key associated to the issuer DID.
-      The signed event contains the merkle root to revoke.
+      This is done by signing a \emph{RevokeBatch} event with a \emph{revocation} key associated to the issuer DID.
+      The signed event contains the Merkle root to revoke.
 \item They revoke specific credentials associated to a batch.
       This is done by signing a \emph{RevokeCredentials} event with a \emph{revocation} key associated to the issuer DID. 
-      The signed event contains both the merkle root associated to the credentials to revoke, and the hashes of the specific credentials to revoke.
+      The signed event contains both the Merkle root associated to the credentials to revoke, and the hashes of the specific credentials to revoke.
 \end{enumerate}
@@
       We also assume that the channel can be identified by an identifier $ch$.
-\item The subject shares his credential and merkle inclusion proof to the verifier.
+\item The subject shares his credential and Merkle inclusion proof to the verifier.
 \item The verifier then: 
 	\begin{itemize}
-	\item computes the merkle root from the inclusion proof and the credential hash;
+	\item computes the Merkle root from the inclusion proof and the credential hash;
 	\item extracts the issuer DID and signing key id from the credential claims,
-	\item retrieves from the state he computed from the blockchain, the timestamps associated to the merkle root and the issuing key, 
-	\item checks if the merkle root or credential hash has been revoked
+	\item retrieves from the state he computed from the blockchain, the timestamps associated to the Merkle root and the issuing key, 
+	\item checks if the Merkle root or credential hash has been revoked
 	\item validates the issuer signature on the credential, and determines if it was signed at a time when the issuer key was valid.
@@
 completed the first phase of the protocol. Digital signatures using the issuer's
-keypair prevent this.
+key pair prevent this.
 
@@
 \footnote{https://tamarin-prover.github.io/ (Last access, October 5th, 2021.)}
-to model our protocol\footnote{Source code for the model available here
-  \url{https://github.com/input-output-hk/atala-prism/blob/research-tamarin-connector/prism-backend/research/formalizations/connector.spthy}
-  \todo{Update to final URL.}}, which is schematized in \figref{fig:e2econnector}
+to model our protocol% \footnote{Source code for the model available here
+  % \url{https://github.com/input-output-hk/atala-prism/blob/research-tamarin-connector/prism-backend/research/formalizations/connector.spthy}
+  % \todo{Update to final URL.}}
+, which is schematized in \figref{fig:e2econnector}
 

### 2023-07-21 prism-backend/project/Dependencies.scala

@@ -1,161 +1,0 @@
-import sbt.Keys.libraryDependencySchemes
-import sbt._
-
-object versions {
-  val bouncycastle = "1.70"
-  val catsScalatest = "3.1.1"
-  val chimney = "0.6.1"
-  val circe = "0.14.1"
-  val circeOptics = "0.14.1"
-  val diffx = "0.7.0"
-  val dockerClient = "8.16.0"
-  val dockerTestkit = "0.9.9"
-  val doobie = "1.0.0-RC2"
-  val enumeratum = "1.7.0"
-  val enumeratumDoobie = "1.7.1"
-  val flyway = "8.5.4"
-  val grpc = "1.45.0"
-  val kamon = "2.4.8"
-  val logback = "1.2.11"
-  val logbackLogstash = "7.0.1"
-  val jaxb = "2.3.1"
-  val mockito = "1.17.5"
-  val playJson = "2.9.1"
-  val postgresql = "42.3.3"
-  val scalatest = "3.2.11"
-  val scalatestplus = s"$scalatest.0"
-  val scalapb = "0.11.6"
-  val sttp = "3.5.1"
-  val slf4j = "1.7.36"
-  val tofu = "0.10.8"
-  val tofuDerevo = "0.13.0"
-  val twirl = "1.5.1"
-  val typesafeConfig = "1.4.2"
-  val fs2 = "3.7.0"
-  val scalaUri = "4.0.0"
-  val prismSdk = "v1.4.1-snapshot-1688975371-7541fd2" // deployed to github packages from sdk branch "node-1.4-extension-sdk"
-  val vaultSdk = "0.1.0-build-2-96cc137d"
-}
-
-object Dependencies {
-  val bouncyBcpkix =
-    "org.bouncycastle" % "bcpkix-jdk15on" % versions.bouncycastle
-  val bouncyBcprov =
-    "org.bouncycastle" % "bcprov-jdk15on" % versions.bouncycastle
-  val chimney = "io.scalaland" %% "chimney" % versions.chimney
-  val circeCore = "io.circe" %% "circe-core" % versions.circe
-  val circeGeneric = "io.circe" %% "circe-generic" % versions.circe
-  val circeGenericExtras = "io.circe" %% "circe-generic-extras" % versions.circe
-  val circeParser = "io.circe" %% "circe-parser" % versions.circe
-  val circeOptics = "io.circe" %% "circe-optics" % versions.circeOptics
[…]

### 2023-07-25 docs/public-docs/article.tex
feat: remove deprecated projects and add new release process

--- 2021-11-22 prism-backend/public-docs/article.tex
@@
 \item The \emph{hash} is encoded in hexadecimal form producing an \emph{encoded\_hash}.
-\item The user DID is constructed as \emph{did:prism:encoded\_hash}.
-\item The user will send in the metadata of a blockchain transaction a signed \emph{CreateDID} event. 
+\item The user's DID is constructed as \emph{did:prism:encoded\_hash}.
+\item The user will a signed \emph{CreateDID} event in the transaction metadata that is submitted to a blockchain.
       The event contains the list of public keys with their identifiers and roles.
@@
 
-When the event added to the blockchain with enough confirmations, all parties will process the event.
+When the event added to the blockchain has enough confirmations, all parties will process the event.
 This is, they will validate the signature, and update their internal knowledge of the updated DID.
@@
 
-Now, we can define the process that a protocol participant must follow to obtain the keys associated to a list. 
+Now, we can define the process that a protocol participant must follow to obtain the keys associated to a DID. 
 We mentioned that a DID can be presented in long form (or as an unpublished DID), or in its short form. Hence, we will describe the process in the two cases.
@@
       The signing key corresponds to the key id in the credentials' claims.
-\item The issuer encodes each signature, and concatenate them to their corresponding credentials using a dot (".") as separator.
-      This produces strings of the form $\langle{}encoded\_credentials\rangle{}.\langle{}encoded\_signature\rangle{}$. We call these strings asa
-      \emph{signed credentials}.
+\item The issuer encodes each signature, and concatenates them to their corresponding credentials using a dot (".") as separator.
+      This produces strings of the form $\langle{}encoded\_credentials\rangle{}.\langle{}encoded\_signature\rangle{}$. We call these strings \emph{signed credentials}.
 \item Now, the issuer takes all the signed credentials, and computes a merkle root from them.

### 2023-07-25 node/src/main/scala/io/iohk/atala/prism/node/cardano/dbsync/CardanoDbSyncClient.scala

@@ -1,0 +1,44 @@
+package io.iohk.atala.prism.node.cardano.dbsync
+
+import cats.Comonad
+import cats.effect.{Async, Resource}
+import io.iohk.atala.prism.metrics.TimeMeasureMetric
+import io.iohk.atala.prism.repositories.TransactorFactory
+import io.iohk.atala.prism.node.cardano.dbsync.repositories.CardanoBlockRepository
+import io.iohk.atala.prism.node.cardano.models.{Block, BlockError}
+import tofu.logging.Logs
+
+trait CardanoDbSyncClient[F[_]] {
+  def getFullBlock(blockNo: Int): F[Either[BlockError.NotFound, Block.Full]]
+  def getLatestBlock: F[Either[BlockError.NoneAvailable.type, Block.Canonical]]
+}
+
+final class CardanoDbSyncClientImpl[F[_]](
+    cardanoBlockRepository: CardanoBlockRepository[F]
+) extends CardanoDbSyncClient[F] {
+  def getFullBlock(blockNo: Int): F[Either[BlockError.NotFound, Block.Full]] =
+    cardanoBlockRepository.getFullBlock(blockNo)
+
+  def getLatestBlock: F[Either[BlockError.NoneAvailable.type, Block.Canonical]] =
+    cardanoBlockRepository.getLatestBlock
+}
+
+object CardanoDbSyncClient {
+  case class Config(dbConfig: TransactorFactory.Config)
+
+  def apply[F[_]: Async: TimeMeasureMetric, R[_]: Comonad](
+      config: Config,
+      logs: Logs[R, F]
+  ): Resource[F, CardanoDbSyncClient[F]] = {
+
+    // Custom transactor since CardanoDbSyncClient can use different DB
+    TransactorFactory
+      .transactor[F](config.dbConfig)
+      .map(transactor => {
+        val cardanoBlockRepository =
+          CardanoBlockRepository.unsafe(transactor, logs)
+
+        new CardanoDbSyncClientImpl(cardanoBlockRepository)
+      })
+  }
+}

### 2023-07-25 prism-backend/common/src/main/scala/io/iohk/atala/prism/utils/GrpcUtils.scala

@@ -1,103 +1,0 @@
-package io.iohk.atala.prism.utils
-
-import java.util.concurrent.TimeUnit
-import cats.effect.{Resource, Sync}
-import com.typesafe.config.Config
-import io.grpc.netty.{GrpcSslContexts, NettyServerBuilder}
-import io.grpc.{Channel, ManagedChannelBuilder, Server, ServerInterceptor, ServerServiceDefinition}
-import io.grpc.protobuf.services.ProtoReflectionService
-
-import java.io.File
-import scala.concurrent.blocking
-import io.grpc.stub.AbstractStub
-import io.iohk.atala.prism.protos.node_api.ScheduleOperationsResponse
-import io.iohk.atala.prism.protos.node_models.OperationOutput
-
-object GrpcUtils {
-
-  def extractSingleOperationOutput(scheduleOperationsResponse: ScheduleOperationsResponse): OperationOutput =
-    scheduleOperationsResponse.outputs match {
-      case Seq(head) => head
-      case outputs =>
-        throw new RuntimeException(s"1 operation output expected but got ${outputs.size}")
-    }
-
-  case class GrpcConfig(port: Int)
-
-  object GrpcConfig {
-    def apply(config: Config): GrpcConfig = GrpcConfig(
-      config.getInt("grpc.port")
-    )
-  }
-
-  case class SslConfig(
-      serverCertificateLocation: String,
-      serverCertificatePrivateKeyLocation: String,
-      serverTrustChainLocation: String
-  )
-
-  object SslConfig {
-    def apply(config: Config): SslConfig =
-      SslConfig(
-        serverCertificateLocation = config.getString("ssl.serverCertificateLocation"),
-        serverCertificatePrivateKeyLocation = config.getString("ssl.serverCertificatePrivateKeyLocation"),
-        serverTrustChainLocation = config.getString("ssl.serverTrustChainLocation")
-      )
-  }
-
-  /** Create a plainttext stub with a given host and port.
-    */
-  def createPlaintextStub[S <: AbstractStub[S]](
-      host: String,
-      port: Int,
-      stub: Channel => S
-  ): S = {
-    val channel = ManagedChannelBuilder
-      .forAddress(host, port)
-      .usePlaintext()
-      .build()
-
-    stub(channel)
-  }
-
-  /** Wrap a [[Server]] into a bracketed resource. The server stops when the resource is released. With the following
-    * scenarios:
-    *   - Server is shut down when there aren't any requests left.
[…]

### 2023-07-25 prism-backend/connector/bin/grpcui.sh

@@ -1,18 +1,0 @@
-#!/usr/bin/env bash
-set -euo pipefail
-
-dir="$( cd "$( dirname "${BASH_SOURCE[0]}" )" >/dev/null 2>&1 && pwd )"
-pushd "$dir"/../.. > /dev/null
-
-grpcui \
-  -plaintext \
-  -import-path protos \
-  -import-path protos/intdemo \
-  -proto protos/admin_api.proto \
-  -proto protos/intdemo/intdemo_api.proto \
-  -proto protos/console_api.proto \
-  -proto protos/connector_api.proto \
-  -proto protos/cstore_api.proto \
-  localhost:50051
-
-popd

### 2023-07-25 prism-backend/connector/src/main/scala/db/migration/V11__IssuerIcons.scala

@@ -1,46 +1,0 @@
-package db.migration
-
-import java.util.{Base64, UUID}
-import org.flywaydb.core.api.migration.{BaseJavaMigration, Context}
-
-import scala.util.Using
-
-class V11__IssuerIcons extends BaseJavaMigration {
-
-  val govPng = decode(
-    "iVBORw0KGgoAAAANSUhEUgAAACgAAAAoCAYAAACM/rhtAAAACXBIWXMAAAsTAAALEwEAmpwYAAAAAXNSR0IArs4c6QAAAARnQU1BAACxjwv8YQUAAAJwSURBVHgBzZg/TFNRFMa/e9turXFUpy4og0ZMNDERDXRSBl8XnFhkVnEyhphIY1yc0MUNFydZ7OIoJDCQQNIODPxL6ASMhLI15XLOu3mFNoVy36H0/pKXvvfubfL13Hu+c3sUWjB3B4eAozw0AhiVxVWgUIahq1YvqLWlSvNQJCw7dB3Xap9p4nv0lmkkUgVVnt/nB9UQl67N0dMAfIAjqlPDLFKHLzhyvohjDGmpkyZCmf7HWaQS2/ARo4Y1iZuCtxzlNS3tffiKUoEO19tfshqek4SUTAYYGwWCF8Ctm/bdzi6wXAJ+/rL3ApS598RAwiyJuNPXfozFjb4GqoeIi2yJc0/PFsdwRMdeQYJM4MMHnefwjxAgExjtOemcc+h+FmfSkCATeJEMXd+EBJnA/wud56z1UuBKyV5nsbNHXjgDCfI9+OmrFdIKe9/Ex/ZjDsiNOuIlVZL8CHBwaPfd7z8ig46IL5BLXPCcjPo2WckN4NuPk4SIyh+bOL9b7rAVLlUg+9qXSeBRG5OuVm3U2nkfZ/zEpHNWuwnkyMzOxDdfFj/+1kmkW5LkBmWVgU37wzunr7gJDEYgpr/PabqbQE4GKRxFh1VwFCgr/A0c6nNvjvxdEyisCg0cDNxN4PgboPgPsWHDdrSZeJWEk4VP07ln1DZJ2+fW/cnGHJa9LTrRbNjPGNXk8mpxl/D+fzEJNBX4CjU1ufVRhK8oFgj9F76SqBe0Wl2
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/ConnectorApp.scala

@@ -1,304 +1,0 @@
-package io.iohk.atala.prism.connector
-
-import cats.effect.unsafe.IORuntime
-import cats.effect.{ExitCode, IO, IOApp, Resource}
-import com.typesafe.config.{Config, ConfigFactory}
-import doobie.util.transactor.Transactor
-import io.grpc.{ManagedChannelBuilder, Server, ServerBuilder}
-import io.iohk.atala.prism.auth.AuthenticatorF
-import io.iohk.atala.prism.auth.grpc._
-import io.iohk.atala.prism.auth.utils.DidWhitelistLoader
-import io.iohk.atala.prism.connector.repositories._
-import io.iohk.atala.prism.connector.services._
-import io.iohk.atala.prism.cviews.CredentialViewsService
-import io.iohk.atala.prism.db.TransactorForStreaming
-import io.iohk.atala.prism.identity.PrismDid
-import io.iohk.atala.prism.intdemo.ConnectorIntegration.ConnectorIntegrationImpl
-import io.iohk.atala.prism.intdemo._
-import io.iohk.atala.prism.intdemo.protos.intdemo_api.{
-  DegreeServiceGrpc,
-  EmploymentServiceGrpc,
-  IDServiceGrpc,
-  InsuranceServiceGrpc
-}
-import io.iohk.atala.prism.logging.TraceId
-import io.iohk.atala.prism.logging.TraceId.IOWithTraceIdContext
-import io.iohk.atala.prism.metrics.UptimeReporter
-import io.iohk.atala.prism.protos.connector_api
-import io.iohk.atala.prism.protos.connector_api.ContactConnectionServiceGrpc
-import io.iohk.atala.prism.protos.cviews_api.CredentialViewsServiceGrpc
-import io.iohk.atala.prism.protos.node_api.NodeServiceGrpc
-import io.iohk.atala.prism.repositories.{SchemaMigrations, TransactorFactory}
-import io.iohk.atala.prism.utils.IOUtils._
-import kamon.Kamon
-import kamon.module.Module
-import org.slf4j.LoggerFactory
-import tofu.logging.Logs
-
-import scala.concurrent.duration._
-import scala.concurrent.{ExecutionContext, ExecutionContextExecutor}
-
-object ConnectorApp extends IOApp {
-  private val port = 50051
-
-  override def run(args: List[String]): IO[ExitCode] = {
-    val server = new ConnectorApp()(ExecutionContext.global)
-    server.start().use(_ => IO.never)
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/errors/package.scala

@@ -1,223 +1,0 @@
-package io.iohk.atala.prism.connector
-
-import derevo.derive
-import io.grpc.Status
-import io.iohk.atala.prism.connector.model.{ConnectionId, MessageId, TokenString}
-import io.iohk.atala.prism.crypto.keys.ECPublicKey
-import io.iohk.atala.prism.errors.PrismError
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.models.ParticipantId
-import shapeless.Coproduct
-import io.iohk.atala.prism.logging.GeneralLoggableInstances._
-import tofu.logging.derivation.loggable
-import tofu.logging.{DictLoggable, LogRenderer, Loggable}
-import tofu.syntax.loggable.TofuLoggableOps
-
-package object errors {
-
-  @derive(loggable)
-  sealed trait ConnectorError extends PrismError
-
-  case class UnknownValueError(tpe: String, value: String) extends ConnectorError {
-    override def toStatus: Status = {
-      Status.UNKNOWN.withDescription(s"Unknown $tpe: $value")
-    }
-  }
-
-  case class InvalidArgumentError(
-      tpe: String,
-      requirement: String,
-      value: String
-  ) extends ConnectorError {
-    override def toStatus: Status = {
-      Status.INVALID_ARGUMENT.withDescription(
-        s"Invalid value for $tpe, expected $requirement, got $value"
-      )
-    }
-  }
-
-  case class InvalidLimitError(err: InvalidArgumentError) extends ConnectorError {
-    override def toStatus: Status = err.toStatus
-  }
-
-  object InvalidLimitError {
-    def apply(value: String): InvalidLimitError =
-      InvalidLimitError(InvalidArgumentError("limit", "positive value", value))
-  }
-
-  @derive(loggable)
-  sealed trait ConnectionsError extends ConnectorError
-
-  object ConnectionsError {
-
-    case class DidConnectionExist(did: DID) extends ConnectionsError {
-      override def toStatus: Status = {
-        Status.ALREADY_EXISTS.withDescription(
-          s"Attempting to accept a connection with a DID: $did. DID is already used for a connection, use a different DID"
-        )
-      }
-    }
-
-    case class PkConnectionExist(pk: ECPublicKey) extends ConnectionsError {
-      override def toStatus: Status = {
-        Status.ALREADY_EXISTS.withDescription(
-          s"Attempting to accept a connection with a public key: $pk. Public key is already used for a connection, use a different Public key"
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/grpc/Utils.scala

@@ -1,43 +1,0 @@
-package io.iohk.atala.prism.connector.grpc
-
-import io.iohk.atala.prism.connector.model
-import io.iohk.atala.prism.connector.model.{ConnectionId, MessageId}
-
-import scala.util.{Failure, Success, Try}
-
-object Utils {
-
-  def getMessageIdField(
-      id: String,
-      fieldName: String
-  ): Try[Option[model.MessageId]] =
-    id match {
-      case "" => Success(None)
-      case id =>
-        model.MessageId
-          .from(id)
-          .fold(
-            _ =>
-              Failure(
-                new IllegalArgumentException(
-                  s"Invalid value for $fieldName, expected valid id, got $id"
-                )
-              ),
-            id => Success(Some(id))
-          )
-    }
-
-  def parseConnectionId(probablyConnectionId: String): Try[ConnectionId] =
-    model.ConnectionId
-      .from(probablyConnectionId)
-      .recoverWith { case _ =>
-        Failure(new IllegalArgumentException("Invalid connectionId value"))
-      }
-
-  def parseMessageId(messageId: String): Try[Option[MessageId]] = {
-    val id = messageId.trim
-    if (id.nonEmpty) MessageId.from(id).map(Some(_))
-    else Try(None)
-  }
-
-}

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/model/ContactConnection.scala

@@ -1,7 +1,0 @@
-package io.iohk.atala.prism.connector.model
-
-final case class ContactConnection(
-    connectionId: Option[ConnectionId],
-    contactToken: Option[TokenString],
-    connectionStatus: ConnectionStatus
-)

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/model/actions/GetConnectionCommunicationKeysRequest.scala

@@ -1,5 +1,0 @@
-package io.iohk.atala.prism.connector.model.actions
-
-import io.iohk.atala.prism.connector.model.ConnectionId
-
-case class GetConnectionCommunicationKeysRequest(connectionId: ConnectionId)

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/model/actions/GetMessageStreamRequest.scala

@@ -1,5 +1,0 @@
-package io.iohk.atala.prism.connector.model.actions
-
-import io.iohk.atala.prism.connector.model.MessageId
-
-case class GetMessageStreamRequest(lastSeenMessageId: Option[MessageId])

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/model/actions/GetMessagesForConnectionRequest.scala

@@ -1,5 +1,0 @@
-package io.iohk.atala.prism.connector.model.actions
-
-import io.iohk.atala.prism.connector.model.ConnectionId
-
-case class GetMessagesForConnectionRequest(connectionId: ConnectionId)

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/model/actions/RegisterDIDRequest.scala

@@ -1,12 +1,0 @@
-package io.iohk.atala.prism.connector.model.actions
-
-import io.iohk.atala.prism.connector.model.{ParticipantLogo, ParticipantType}
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.protos.node_models.SignedAtalaOperation
-
-case class RegisterDIDRequest(
-    name: String,
-    didOrOperation: Either[DID, SignedAtalaOperation],
-    tpe: ParticipantType,
-    logo: ParticipantLogo
-)

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/model/actions/RevokeConnectionRequest.scala

@@ -1,5 +1,0 @@
-package io.iohk.atala.prism.connector.model.actions
-
-import io.iohk.atala.prism.connector.model.ConnectionId
-
-case class RevokeConnectionRequest(connectionId: ConnectionId)

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/model/actions/SendMessageRequest.scala

@@ -1,9 +1,0 @@
-package io.iohk.atala.prism.connector.model.actions
-
-import io.iohk.atala.prism.connector.model.{ConnectionId, MessageId}
-
-case class SendMessageRequest(
-    connectionId: ConnectionId,
-    message: Array[Byte],
-    id: Option[MessageId]
-)

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/model/actions/SendMessagesRequest.scala

@@ -1,16 +1,0 @@
-package io.iohk.atala.prism.connector.model.actions
-
-import cats.data.NonEmptyList
-import io.iohk.atala.prism.connector.model.{MessageId, TokenString}
-
-case class SendMessagesRequest(
-    messages: Option[NonEmptyList[SendMessagesRequest.MessageToSend]]
-)
-
-object SendMessagesRequest {
-  case class MessageToSend(
-      connectionToken: TokenString,
-      message: Array[Byte],
-      id: Option[MessageId]
-  )
-}

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/repositories/ConnectionsRepository.scala

@@ -1,409 +1,0 @@
-package io.iohk.atala.prism.connector.repositories
-
-import cats.{Applicative, Comonad, Functor}
-import cats.data.{EitherT, OptionT}
-import cats.effect.Resource
-import cats.implicits.{catsSyntaxApplicativeId, catsSyntaxEitherId, catsSyntaxOptionId}
-import cats.syntax.either._
-import cats.syntax.comonad._
-import cats.syntax.functor._
-import derevo.derive
-import derevo.tagless.applyK
-import doobie.implicits._
-import doobie.util.transactor.Transactor
-import io.iohk.atala.prism.connector.errors.ConnectionsError._
-import io.iohk.atala.prism.crypto.keys.ECPublicKey
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.utils.syntax.DBConnectionOps
-import io.iohk.atala.prism.connector.errors.{UnknownValueError, _}
-import io.iohk.atala.prism.connector.model._
-import io.iohk.atala.prism.connector.repositories.daos.{
-  ConnectionTokensDAO,
-  ConnectionsDAO,
-  MessagesDAO,
-  ParticipantsDAO
-}
-import io.iohk.atala.prism.connector.repositories.logs.ConnectionsRepositoryLogs
-import io.iohk.atala.prism.connector.repositories.metrics.ConnectionsRepositoryMetrics
-import io.iohk.atala.prism.errors.LoggingContext
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.metrics.TimeMeasureMetric
-import org.slf4j.{Logger, LoggerFactory}
-import shapeless.{:+:, CNil}
-import tofu.higherKind.Mid
-import tofu.logging.{Logs, ServiceLogging}
-import tofu.syntax.monoid.TofuSemigroupOps
-import cats.effect.MonadCancelThrow
-
-@derive(applyK)
-trait ConnectionsRepository[F[_]] {
-
-  import io.iohk.atala.prism.connector.repositories.ConnectionsRepository._
-
-  def insertTokens(
-      initiator: ParticipantId,
-      tokens: List[TokenString]
-  ): F[List[TokenString]]
-
-  def getTokenInfo(
-      token: TokenString
-  ): F[Either[GetTokenInfoError, ParticipantInfo]]
-
-  def addConnectionFromToken(
-      token: TokenString,
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/repositories/RequestNoncesRepository.scala

@@ -1,82 +1,0 @@
-package io.iohk.atala.prism.connector.repositories
-
-import cats.{Applicative, Comonad, Functor}
-import cats.effect.Resource
-import cats.syntax.comonad._
-import cats.syntax.functor._
-import derevo.derive
-import derevo.tagless.applyK
-import doobie.implicits._
-import doobie.util.transactor.Transactor
-import io.iohk.atala.prism.auth.model.RequestNonce
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.utils.syntax.DBConnectionOps
-import io.iohk.atala.prism.connector.repositories.daos.RequestNoncesDAO
-import io.iohk.atala.prism.connector.repositories.logs.RequestNoncesRepositoryLogs
-import io.iohk.atala.prism.connector.repositories.metrics.RequestNoncesRepositoryMetrics
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.metrics.TimeMeasureMetric
-import tofu.higherKind.Mid
-import tofu.logging.{Logs, ServiceLogging}
-import tofu.syntax.monoid.TofuSemigroupOps
-import cats.effect.MonadCancelThrow
-
-@derive(applyK)
-trait RequestNoncesRepository[F[_]] {
-  def burn(participantId: ParticipantId, requestNonce: RequestNonce): F[Unit]
-  def burn(did: DID, requestNonce: RequestNonce): F[Unit]
-}
-
-object RequestNoncesRepository {
-  def apply[F[_]: TimeMeasureMetric: MonadCancelThrow, R[_]: Functor](
-      transactor: Transactor[F],
-      logs: Logs[R, F]
-  ): R[RequestNoncesRepository[F]] =
-    for {
-      serviceLogs <- logs.service[RequestNoncesRepository[F]]
-    } yield {
-      implicit val implicitLogs: ServiceLogging[F, RequestNoncesRepository[F]] =
-        serviceLogs
-      val metrics: RequestNoncesRepository[Mid[F, *]] =
-        new RequestNoncesRepositoryMetrics[F]
-      val logs: RequestNoncesRepository[Mid[F, *]] =
-        new RequestNoncesRepositoryLogs[F]
-      val mid = metrics |+| logs
-      mid attach new RequestNoncesRepositoryPostgresImpl[F](transactor)
-    }
-
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/repositories/daos/ConnectionTokensDAO.scala

@@ -1,47 +1,0 @@
-package io.iohk.atala.prism.connector.repositories.daos
-
-import cats.implicits._
-import doobie.FC
-import doobie.implicits._
-import doobie.implicits.legacy.instant._
-import doobie.util.update.Update
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.connector.model._
-
-import java.time.Instant
-
-object ConnectionTokensDAO {
-  def exists(tokenString: TokenString): doobie.ConnectionIO[Boolean] = {
-    sql"""
-         |SELECT 1 FROM connection_tokens WHERE token = $tokenString
-       """.stripMargin
-      .query[Int]
-      .option
-      .map(_.isDefined)
-  }
-
-  def insert(
-      initiator: ParticipantId,
-      tokens: List[TokenString]
-  ): doobie.ConnectionIO[Unit] = {
-    Update[(TokenString, ParticipantId)]("""
-         |INSERT INTO connection_tokens (token, initiator)
-         |VALUES (?, ?)""".stripMargin)
-      .updateMany(tokens.map(token => token -> initiator))
-      .flatTap { affectedRows =>
-        FC.raiseError(
-          new RuntimeException(
-            s"Unknown error while inserting ${tokens.size} tokens"
-          )
-        ).whenA(tokens.size != affectedRows)
-      }
-      .void
-  }
-
-  def markAsUsed(token: TokenString): doobie.ConnectionIO[Int] = {
-    sql"""
-         |UPDATE connection_tokens
-         |SET used_at = ${Instant.now()}
-         |WHERE token=$token""".stripMargin.update.run
-  }
-}

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/repositories/daos/ConnectionsDAO.scala

@@ -1,214 +1,0 @@
-package io.iohk.atala.prism.connector.repositories.daos
-
-import java.time.Instant
-import cats.data.NonEmptyList
-import doobie.Fragments
-import doobie.implicits._
-import doobie.implicits.legacy.instant._
-import doobie.util.fragments.{in, whereAnd}
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.connector.model.{
-  Connection,
-  ConnectionId,
-  ConnectionInfo,
-  ConnectionStatus,
-  ContactConnection,
-  RawConnection,
-  TokenString
-}
-
-object ConnectionsDAO {
-
-  def insert(
-      initiator: ParticipantId,
-      acceptor: ParticipantId,
-      token: TokenString,
-      connectionStatus: ConnectionStatus
-  ): doobie.ConnectionIO[(ConnectionId, Instant)] = {
-    val connectionId = ConnectionId.random()
-    val instantiatedAt = Instant.now()
-
-    sql"""
-         |INSERT INTO connections (id, initiator, acceptor, token, instantiated_at, status)
-         |VALUES ($connectionId, $initiator, $acceptor, $token, $instantiatedAt, $connectionStatus::CONTACT_CONNECTION_STATUS_TYPE)
-         |RETURNING id, instantiated_at""".stripMargin
-      .query[(ConnectionId, Instant)]
-      .unique
-  }
-
-  def insert(
-      initiator: ParticipantId,
-      acceptor: ParticipantId,
-      instantiatedAt: Instant,
-      token: TokenString
-  ): doobie.ConnectionIO[ConnectionId] = {
-    val connectionId = ConnectionId.random()
-    val connectionStatus: ConnectionStatus = ConnectionStatus.InvitationMissing
-
-    sql"""
-         |INSERT INTO connections (id, initiator, acceptor, token, instantiated_at, status)
-         |VALUES ($connectionId, $initiator, $acceptor, $token, $instantiatedAt, $connectionStatus::CONTACT_CONNECTION_STATUS_TYPE)
-         |RETURNING id""".stripMargin
-      .query[ConnectionId]
-      .unique
-  }
-
-  def exists(connectionId: ConnectionId): doobie.ConnectionIO[Boolean] = {
-    sql"""
-         |SELECT 1 FROM connections WHERE id = $connectionId
-       """.stripMargin
-      .query[Int]
-      .option
-      .map(_.isDefined)
-  }
-
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/repositories/daos/ParticipantsDAO.scala

@@ -1,94 +1,0 @@
-package io.iohk.atala.prism.connector.repositories.daos
-
-import cats.data.OptionT
-import cats.implicits._
-import doobie.FC
-import doobie.implicits._
-import io.iohk.atala.prism.connector.model.{ParticipantInfo, UpdateParticipantProfile, TokenString}
-import io.iohk.atala.prism.crypto.keys.ECPublicKey
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.models.ParticipantId
-
-object ParticipantsDAO {
-  def insert(participant: ParticipantInfo): doobie.ConnectionIO[Unit] = {
-    val ParticipantInfo(id, tpe, publicKey, name, did, logo, operationId) =
-      participant
-    sql"""
-         |INSERT INTO participants (id, tpe, public_key, name, did, logo, operation_id)
-         |VALUES ($id, $tpe, $publicKey, $name, $did, $logo, $operationId)
-       """.stripMargin.update.run.void
-  }
-
-  def findBy(id: ParticipantId): OptionT[doobie.ConnectionIO, ParticipantInfo] =
-    OptionT {
-      sql"""
-         |SELECT id, tpe, public_key, name, did, logo, operation_id
-         |FROM participants
-         |WHERE id = $id
-      """.stripMargin.query[ParticipantInfo].option
-    }
-
-  def findBy(
-      token: TokenString
-  ): OptionT[doobie.ConnectionIO, ParticipantInfo] =
-    OptionT {
-      sql"""
-         |SELECT p.id, p.tpe, p.public_key, p.name, p.did, p.logo, p.operation_id
-         |FROM connection_tokens t
-         |JOIN participants p ON p.id = t.initiator
-         |WHERE t.token = $token
-      """.stripMargin.query[ParticipantInfo].option
-    }
-
-  def findByAvailableToken(
-      token: TokenString
-  ): OptionT[doobie.ConnectionIO, ParticipantInfo] =
-    OptionT {
-      sql"""
-         |SELECT p.id, p.tpe, p.public_key, p.name, p.did, p.logo, p.operation_id
-         |FROM connection_tokens t
-         |JOIN participants p ON p.id = t.initiator
-         |WHERE t.token = $token AND
-         |      used_at IS NULL
-      """.stripMargin.query[ParticipantInfo].option
-    }
-
-  def findByPublicKey(
-      publicKey: ECPublicKey
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/repositories/daos/RequestNoncesDAO.scala

@@ -1,47 +1,0 @@
-package io.iohk.atala.prism.connector.repositories.daos
-
-import doobie.implicits._
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.auth.model.RequestNonce
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-
-object RequestNoncesDAO {
-  def burn(
-      participantId: ParticipantId,
-      requestNonce: RequestNonce
-  ): doobie.ConnectionIO[Unit] = {
-    sql"""
-         |INSERT INTO request_nonces (request_nonce, participant_id)
-         |VALUES ($requestNonce, $participantId)
-         |ON CONFLICT DO NOTHING
-         |RETURNING request_nonce
-         |""".stripMargin.query[RequestNonce].option.map {
-      case Some(_) => ()
-      case None => throw new RuntimeException("The nonce was already used")
-    }
-  }
-
-  def burn(did: DID, requestNonce: RequestNonce): doobie.ConnectionIO[Unit] = {
-    sql"""
-         |INSERT INTO did_request_nonces (request_nonce, did)
-         |VALUES ($requestNonce, $did)
-         |ON CONFLICT DO NOTHING
-         |RETURNING request_nonce
-         |""".stripMargin.query[RequestNonce].option.map {
-      case Some(_) => ()
-      case None => throw new RuntimeException("The nonce was already used")
-    }
-  }
-
-  def available(
-      participantId: ParticipantId,
-      requestNonce: RequestNonce
-  ): doobie.ConnectionIO[Boolean] = {
-    sql"""
-         |SELECT request_nonce
-         |FROM request_nonces
-         |WHERE request_nonce = $requestNonce AND
-         |      participant_id = $participantId
-         |""".stripMargin.query[RequestNonce].option.map(_.isEmpty)
-  }
-}

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/repositories/logs/ConnectionsRepositoryLogs.scala

@@ -1,152 +1,0 @@
-package io.iohk.atala.prism.connector.repositories.logs
-
-import cats.syntax.apply._
-import cats.syntax.applicativeError._
-import cats.syntax.flatMap._
-import io.iohk.atala.prism.connector.errors.ConnectorError
-import io.iohk.atala.prism.connector.model._
-import io.iohk.atala.prism.connector.repositories.ConnectionsRepository
-import io.iohk.atala.prism.connector.repositories.ConnectionsRepository._
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.crypto.keys.ECPublicKey
-import io.iohk.atala.prism.models.ParticipantId
-import tofu.higherKind.Mid
-import tofu.logging.ServiceLogging
-import tofu.syntax.logging._
-import cats.MonadThrow
-
-private[repositories] final class ConnectionsRepositoryLogs[F[
-    _
-]: ServiceLogging[
-  *[_],
-  ConnectionsRepository[F]
-]: MonadThrow]
-    extends ConnectionsRepository[Mid[F, *]] {
-  override def insertTokens(
-      initiator: ParticipantId,
-      tokens: List[TokenString]
-  ): Mid[F, List[TokenString]] =
-    in =>
-      info"inserting tokens $initiator ${tokens.size} entities" *> in
-        .flatTap(result => info"inserting tokens - successfully done, inserted ${result.size} tokens")
-        .onError(errorCause"encountered an error while inserting tokens" (_))
-
-  override def getTokenInfo(
-      token: TokenString
-  ): Mid[F, Either[GetTokenInfoError, ParticipantInfo]] =
-    in =>
-      info"getting token info $token" *> in
-        .flatTap(
-          _.fold(
-            er => error"encountered an error while getting token info ${er.unify: ConnectorError}",
-            info => info"getting token info - successfully done ${info.id}"
-          )
-        )
-        .onError(errorCause"encountered an error while getting token info" (_))
-
-  override def addConnectionFromToken(
-      token: TokenString,
-      didOrPublicKey: Either[DID, ECPublicKey]
-  ): Mid[F, Either[AddConnectionFromTokenError, ConnectionInfo]] =
-    in =>
-      info"adding connection from token $token" *> in
-        .flatTap(
-          _.fold(
-            er => error"encountered an error while adding connection from token ${er.unify: ConnectorError}",
-            info => info"adding connection from token - successfully done ${info.id}"
-          )
-        )
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/repositories/logs/MessagesRepositoryLogs.scala

@@ -1,87 +1,0 @@
-package io.iohk.atala.prism.connector.repositories.logs
-
-import cats.data.NonEmptyList
-import cats.syntax.apply._
-import cats.syntax.applicativeError._
-import cats.syntax.flatMap._
-import io.iohk.atala.prism.connector.errors.ConnectorError
-import io.iohk.atala.prism.connector.model.actions.SendMessagesRequest
-import io.iohk.atala.prism.connector.model.{ConnectionId, Message, MessageId}
-import io.iohk.atala.prism.connector.repositories.MessagesRepository
-import io.iohk.atala.prism.connector.repositories.MessagesRepository._
-import io.iohk.atala.prism.models.ParticipantId
-import tofu.higherKind.Mid
-import tofu.logging.ServiceLogging
-import tofu.syntax.logging._
-import cats.MonadThrow
-
-private[repositories] final class MessagesRepositoryLogs[S[_], F[
-    _
-]: ServiceLogging[*[_], MessagesRepository[S, F]]](implicit
-    monadThrow: MonadThrow[F]
-) extends MessagesRepository[S, Mid[F, *]] {
-  override def insertMessage(
-      sender: ParticipantId,
-      connection: ConnectionId,
-      content: Array[Byte],
-      messageIdOption: Option[MessageId]
-  ): Mid[F, Either[InsertMessageError, MessageId]] =
-    in =>
-      info"inserting message $sender $connection" *> in
-        .flatTap(
-          _.fold(
-            er => error"encountered an error while inserting message ${er.unify: ConnectorError}",
-            id => info"inserting message - successfully done $id"
-          )
-        )
-        .onError(errorCause"encountered an error while inserting message" (_))
-
-  override def insertMessages(
-      sender: ParticipantId,
-      messages: NonEmptyList[SendMessagesRequest.MessageToSend]
-  ): Mid[F, Either[InsertMessagesError, List[MessageId]]] =
-    in =>
-      info"inserting messages $sender" *> in
-        .flatTap(
-          _.fold(
-            er => error"encountered an error while inserting messages ${er.unify: ConnectorError}",
-            ids => info"inserting messages - successfully done, inserted ${ids.size} messages"
-          )
-        )
-        .onError(errorCause"encountered an error while inserting messages" (_))
-
-  override def getMessagesPaginated(
-      recipientId: ParticipantId,
-      limit: Int,
-      lastSeenMessageId: Option[MessageId]
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/repositories/logs/ParticipantsRepositoryLogs.scala

@@ -1,96 +1,0 @@
-package io.iohk.atala.prism.connector.repositories.logs
-
-import cats.syntax.apply._
-import cats.syntax.applicativeError._
-import cats.syntax.flatMap._
-import io.iohk.atala.prism.connector.errors.ConnectorError
-import io.iohk.atala.prism.connector.model.{ParticipantInfo, UpdateParticipantProfile}
-import io.iohk.atala.prism.connector.repositories.ParticipantsRepository
-import io.iohk.atala.prism.connector.repositories.ParticipantsRepository._
-import io.iohk.atala.prism.crypto.keys.ECPublicKey
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.logging.GeneralLoggableInstances._
-import tofu.higherKind.Mid
-import tofu.logging.ServiceLogging
-import tofu.syntax.logging._
-import cats.MonadThrow
-
-private[repositories] final class ParticipantsRepositoryLogs[F[
-    _
-]: ServiceLogging[
-  *[_],
-  ParticipantsRepository[F]
-]: MonadThrow]
-    extends ParticipantsRepository[Mid[F, *]] {
-  override def create(
-      request: ParticipantsRepository.CreateParticipantRequest
-  ): Mid[F, Either[CreateParticipantError, Unit]] =
-    in =>
-      info"creating participant ${request.id}" *> in
-        .flatTap(
-          _.fold(
-            er => error"encountered an error while creating participant ${er.unify: ConnectorError}",
-            _ => info"creating participant - successfully done"
-          )
-        )
-        .onError(
-          errorCause"encountered an error while creating participant" (_)
-        )
-
-  override def findBy(
-      id: ParticipantId
-  ): Mid[F, Either[FindByError, ParticipantInfo]] =
-    in =>
-      info"finding participant $id" *> in
-        .flatTap(
-          _.fold(
-            er => error"encountered an error while finding participant ${er.unify: ConnectorError}",
-            _ => info"finding participant  - successfully done"
-          )
-        )
-        .onError(errorCause"encountered an error while finding participant" (_))
-
-  override def findBy(
-      publicKey: ECPublicKey
-  ): Mid[F, Either[FindByError, ParticipantInfo]] =
-    in =>
-      info"finding participant by public-key $publicKey" *> in
-        .flatTap(
-          _.fold(
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/repositories/metrics/ConnectionsRepositoryMetrics.scala

@@ -1,94 +1,0 @@
-package io.iohk.atala.prism.connector.repositories.metrics
-
-import io.iohk.atala.prism.connector.model._
-import io.iohk.atala.prism.connector.repositories.ConnectionsRepository
-import io.iohk.atala.prism.connector.repositories.ConnectionsRepository._
-import io.iohk.atala.prism.crypto.keys.ECPublicKey
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.metrics.TimeMeasureUtil.MeasureOps
-import io.iohk.atala.prism.metrics.{TimeMeasureMetric, TimeMeasureUtil}
-import io.iohk.atala.prism.models.ParticipantId
-import tofu.higherKind.Mid
-import cats.effect.MonadCancelThrow
-
-private[repositories] final class ConnectionsRepositoryMetrics[F[
-    _
-]: TimeMeasureMetric: MonadCancelThrow]
-    extends ConnectionsRepository[Mid[F, *]] {
-
-  private val repoName = "ConnectionsRepository"
-  private lazy val insertTokensTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "insertTokens")
-  private lazy val getTokenInfoTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "getTokenInfo")
-  private lazy val addConnectionFromTokenTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "addConnectionFromToken")
-  private lazy val revokeConnectionsTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "revokeConnection")
-  private lazy val getConnectionTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "getConnection")
-  private lazy val getConnectionsPaginatedTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "getConnectionsPaginated")
-  private lazy val getOtherSideInfoTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "getOtherSideInfo")
-  private lazy val getConnectionByTokenTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "getConnectionByToken")
-  private lazy val getConnectionsByConnectionTokensTimer =
-    TimeMeasureUtil.createDBQueryTimer(
-      repoName,
-      "getConnectionsByConnectionTokens"
-    )
-
-  override def insertTokens(
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/repositories/metrics/RequestNoncesRepositoryMetrics.scala

@@ -1,31 +1,0 @@
-package io.iohk.atala.prism.connector.repositories.metrics
-
-import io.iohk.atala.prism.auth.model.RequestNonce
-import io.iohk.atala.prism.connector.repositories.RequestNoncesRepository
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.metrics.TimeMeasureUtil.MeasureOps
-import io.iohk.atala.prism.metrics.{TimeMeasureMetric, TimeMeasureUtil}
-import io.iohk.atala.prism.models.ParticipantId
-import tofu.higherKind.Mid
-import cats.effect.MonadCancel
-
-private[repositories] final class RequestNoncesRepositoryMetrics[F[
-    _
-]: TimeMeasureMetric](implicit
-    ce: MonadCancel[F, Throwable]
-) extends RequestNoncesRepository[Mid[F, *]] {
-  private val repoName = "ParticipantsRepository"
-  private lazy val burnById =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "burnById")
-  private lazy val burnByDid =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "burnByDid")
-
-  override def burn(
-      participantId: ParticipantId,
-      requestNonce: RequestNonce
-  ): Mid[F, Unit] =
-    _.measureOperationTime(burnById)
-
-  override def burn(did: DID, requestNonce: RequestNonce): Mid[F, Unit] =
-    _.measureOperationTime(burnByDid)
-}

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/services/HealthService.scala

@@ -1,29 +1,0 @@
-package io.iohk.atala.prism.connector.services
-
-import _root_.grpc.health.v1.health._
-import io.grpc.stub.StreamObserver
-import org.slf4j.LoggerFactory
-
-import scala.concurrent.Future
-
-/** Simple Health service, for now, the service is healthy if the request is received.
-  */
-class HealthService extends HealthGrpc.Health {
-  private val logger = LoggerFactory.getLogger(this.getClass)
-
-  def check(request: HealthCheckRequest): Future[HealthCheckResponse] = {
-    logger.info(s"Replying to health request, service = ${request.service}")
-    Future.successful(servingResponse)
-  }
-
-  def watch(
-      request: HealthCheckRequest,
-      responseObserver: StreamObserver[HealthCheckResponse]
-  ): Unit = {
-    logger.info(s"Watch for health changes, service = ${request.service}")
-    responseObserver.onNext(servingResponse)
-  }
-
-  private val servingResponse =
-    HealthCheckResponse().withStatus(HealthCheckResponse.ServingStatus.SERVING)
-}

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/services/MessageNotificationService.scala

@@ -1,143 +1,0 @@
-package io.iohk.atala.prism.connector.services
-
-import cats.effect._
-import cats.implicits._
-import doobie.implicits._
-import doobie.util.transactor.Transactor
-import fs2.Stream
-import io.iohk.atala.prism.connector.model.{Message, MessageId}
-import io.iohk.atala.prism.connector.repositories.daos.MessagesDAO
-import io.iohk.atala.prism.db.{DbNotificationStreamer, TransactorForStreaming}
-import io.iohk.atala.prism.models.ParticipantId
-import org.slf4j.{Logger, LoggerFactory}
-
-import scala.util.{Failure, Success}
-import cats.effect.Temporal
-import cats.effect.std.Queue
-import cats.effect.unsafe.IORuntime
-
-class MessageNotificationService private (
-    dbNotificationStreamer: DbNotificationStreamer,
-    xa: Transactor[IO],
-    streamQueuesRef: Ref[IO, Map[ParticipantId, Queue[IO, Option[Message]]]]
-)(implicit runtime: IORuntime) {
-  import MessageNotificationService._
-
-  private def enqueue(
-      queue: Queue[IO, Option[Message]],
-      v: Option[Message]
-  ): IO[Unit] =
-    queue.offer(v)
-
-  def stream(recipientId: ParticipantId): Stream[IO, Message] =
-    for {
-      queue <- Stream.eval(Queue.unbounded[IO, Option[Message]])
-      _ <- Stream.eval {
-        for {
-          oldQueue <- streamQueuesRef.modify(oldMap => (oldMap.updated(recipientId, queue), oldMap.get(recipientId)))
-          // Terminate the old queue to prevent its stream from hanging around forever
-          _ <- oldQueue.traverse_(enqueue(_, None))
-        } yield ()
-      }
-      message <- Stream.fromQueueNoneTerminated(queue)
-    } yield message
-
-  def start(): Unit = {
-    val startComputation = for {
-      _ <- dbNotificationStreamer.stream
-        .map { notification =>
-          MessageId.from(notification.payload) match {
-            case Success(notificationId) => Some(notificationId)
-            case Failure(e) =>
-              logger.error(
-                s"DB notification payload could not be parsed as message ID",
-                e
-              )
-              None
-          }
-        }
-        // Ignore malformed IDs
-        .unNone
-        // Query whole message
-        .evalMap(messageId =>
-          MessagesDAO
-            .getMessage(messageId)
-            .map {
-              case Some(message) => Some(message)
-              case None =>
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/services/logs/ConnectionsServiceLogs.scala

@@ -1,160 +1,0 @@
-package io.iohk.atala.prism.connector.services.logs
-
-import cats.syntax.apply._
-import cats.syntax.applicativeError._
-import cats.syntax.flatMap._
-import io.iohk.atala.prism.connector.errors.ConnectorError
-import io.iohk.atala.prism.connector.model.{
-  Connection,
-  ConnectionId,
-  ConnectionInfo,
-  ContactConnection,
-  ParticipantInfo,
-  TokenString
-}
-import io.iohk.atala.prism.connector.repositories.ConnectionsRepository._
-import io.iohk.atala.prism.connector.services.ConnectionsService
-import io.iohk.atala.prism.connector.services.ConnectionsService.GetConnectionCommunicationKeysError
-import io.iohk.atala.prism.crypto.keys.ECPublicKey
-import io.iohk.atala.prism.identity.PrismDid
-import io.iohk.atala.prism.models.ParticipantId
-import tofu.higherKind.Mid
-import tofu.logging.ServiceLogging
-import tofu.syntax.logging._
-import cats.MonadThrow
-
-private[services] class ConnectionsServiceLogs[
-    F[_]: ServiceLogging[*[_], ConnectionsService[F]]: MonadThrow
-] extends ConnectionsService[Mid[F, *]] {
-  override def getConnectionByToken(
-      token: TokenString
-  ): Mid[F, Option[Connection]] =
-    in =>
-      info"getting connection by token $token" *> in
-        .flatTap(res =>
-          info"getting connection by token - successfully done, connection ${res
-              .fold("not found")(_ => "found")}"
-        )
-        .onError(
-          errorCause"encountered an error while getting connection by token" (_)
-        )
-
-  override def generateTokens(
-      userId: ParticipantId,
-      tokensCount: Int
-  ): Mid[F, List[TokenString]] =
-    in =>
-      info"generating tokens $userId, tokens count - $tokensCount" *> in
-        .flatTap(res => info"generating tokens - successfully done, generated ${res.size} tokens")
-        .onError(errorCause"encountered an error while generating tokens" (_))
-
-  override def getTokenInfo(
-      token: TokenString
-  ): Mid[F, Either[GetTokenInfoError, ParticipantInfo]] =
-    in =>
-      info"getting token info $token" *> in
-        .flatTap(res =>
-          res.fold(
-            er => error"encountered an error while getting token info ${er.unify: ConnectorError}",
-            pi => info"getting token info - successfully done ${pi.id}"
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/connector/services/logs/RegistrationServiceLogs.scala

@@ -1,40 +1,0 @@
-package io.iohk.atala.prism.connector.services.logs
-
-import cats.syntax.apply._
-import cats.syntax.applicativeError._
-import cats.syntax.flatMap._
-import io.iohk.atala.prism.connector.errors.ConnectorError
-import io.iohk.atala.prism.connector.model.{ParticipantLogo, ParticipantType}
-import io.iohk.atala.prism.connector.services.RegistrationService
-import io.iohk.atala.prism.connector.services.RegistrationService.RegisterParticipantError
-import io.iohk.atala.prism.identity.PrismDid
-import io.iohk.atala.prism.protos.node_models.SignedAtalaOperation
-import tofu.higherKind.Mid
-import tofu.logging.ServiceLogging
-import tofu.syntax.logging._
-import cats.MonadThrow
-
-private[services] class RegistrationServiceLogs[
-    F[_]: ServiceLogging[*[_], RegistrationService[F]]: MonadThrow
-] extends RegistrationService[Mid[F, *]] {
-  override def register(
-      tpe: ParticipantType,
-      name: String,
-      logo: ParticipantLogo,
-      didOrOperation: Either[PrismDid, SignedAtalaOperation]
-  ): Mid[F, Either[
-    RegisterParticipantError,
-    RegistrationService.RegistrationResult
-  ]] =
-    in =>
-      info"registering participant $name " *> in
-        .flatTap(
-          _.fold(
-            er => error"Encountered an error while registering participant ${er.unify: ConnectorError}",
-            res => info"registering participant - successfully done ${res.did.getSuffix}"
-          )
-        )
-        .onError(
-          errorCause"Encountered an error while registering participant" (_)
-        )
-}

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/cviews/CredentialViewsService.scala

@@ -1,305 +1,0 @@
-package io.iohk.atala.prism.cviews
-
-import cats.effect.unsafe.IORuntime
-import io.circe.Json
-import io.iohk.atala.prism.auth.AuthenticatorF
-import io.iohk.atala.prism.auth.errors.AuthErrorSupport
-import io.iohk.atala.prism.auth.grpc.GrpcAuthenticationHeaderParser.grpcHeader
-import io.iohk.atala.prism.intdemo.DegreeServiceImpl.DegreeCredentialHtmlTemplateData
-import io.iohk.atala.prism.intdemo.EmploymentServiceImpl.EmploymentCredentialHtmlTemplateData
-import io.iohk.atala.prism.intdemo.IdServiceImpl.IdCredentialHtmlTemplateData
-import io.iohk.atala.prism.intdemo.InsuranceServiceImpl.InsuranceCredentialHtmlTemplateData
-import io.iohk.atala.prism.intdemo.html._
-import io.iohk.atala.prism.logging.TraceId.IOWithTraceIdContext
-import io.iohk.atala.prism.metrics.RequestMeasureUtil.measureRequestFuture
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.protos.cviews_api.{GetCredentialViewTemplatesRequest, GetCredentialViewTemplatesResponse}
-import io.iohk.atala.prism.protos.{cviews_api, cviews_models}
-import io.iohk.atala.prism.tracing.Tracing.trace
-import io.iohk.atala.prism.utils.FutureEither.{FutureEitherFOps, FutureEitherOps}
-import io.iohk.atala.prism.utils.syntax._
-import io.iohk.atala.prism.view.HtmlViewImage
-import org.slf4j.{Logger, LoggerFactory}
-
-import scala.concurrent.{ExecutionContext, Future}
-
-class CredentialViewsService(authenticator: AuthenticatorF[ParticipantId, IOWithTraceIdContext])(implicit
-    ec: ExecutionContext,
-    runtime: IORuntime
-) extends cviews_api.CredentialViewsServiceGrpc.CredentialViewsService
-    with AuthErrorSupport {
-
-  val logger: Logger = LoggerFactory.getLogger(this.getClass)
-  private val getCredsViewTemplatesMethodName = "getCredentialViewTemplates"
-
-  override def getCredentialViewTemplates(
-      request: GetCredentialViewTemplatesRequest
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/intdemo/IdCredentialData.scala

@@ -1,30 +1,0 @@
-package io.iohk.atala.prism.intdemo
-
-import java.time.LocalDate
-import io.iohk.atala.prism.utils.Base64Utils
-import io.circe.parser._
-import io.iohk.atala.prism.protos.credential_models
-
-case class IdCredentialData private (name: String, dateOfBirth: LocalDate)
-
-object IdCredentialData {
-  def apply(
-      protobufCredential: credential_models.PlainTextCredential
-  ): IdCredentialData = {
-    val decodedCredential =
-      Base64Utils.decodeUrlToString(protobufCredential.encodedCredential)
-    parse(decodedCredential)
-      .flatMap { json =>
-        val cursor = json.hcursor.downField("credentialSubject")
-        for {
-          name <- cursor.downField("name").as[String]
-          dateOfBirth <- cursor.downField("dateOfBirth").as[LocalDate]
-        } yield IdCredentialData(name, dateOfBirth)
-      }
-      .getOrElse(
-        throw new IllegalStateException(
-          s"The shared id credential is invalid. Document follows: '${decodedCredential}''"
-        )
-      )
-  }
-}

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/intdemo/IntDemoRepository.scala

@@ -1,125 +1,0 @@
-package io.iohk.atala.prism.intdemo
-
-import java.time.LocalDate
-import cats.effect.IO
-import cats.effect.unsafe.IORuntime
-import doobie.implicits._
-import doobie.implicits.legacy.localdate._
-import doobie.util.transactor.Transactor
-import io.iohk.atala.prism.intdemo.IntDemoRepository.valueOf
-import io.iohk.atala.prism.connector.model.TokenString
-import io.iohk.atala.prism.intdemo.protos.intdemo_models
-
-import scala.concurrent.Future
-
-class IntDemoRepository(xa: Transactor[IO])(implicit runtime: IORuntime) {
-
-  def mergeSubjectStatus(
-      token: TokenString,
-      status: intdemo_models.SubjectStatus
-  ): Future[Int] = {
-    IntDemoRepository
-      .mergeStatus(token.token, valueOf(status))
-      .transact(xa)
-      .unsafeToFuture()
-  }
-
-  def findSubjectStatus(
-      token: TokenString
-  ): Future[Option[intdemo_models.SubjectStatus]] = {
-    IntDemoRepository
-      .findStatus(token.token)
-      .transact(xa)
-      .unsafeToFuture()
-  }
-
-  def mergePersonalInfo(
-      token: TokenString,
-      firstName: String,
-      dateOfBirth: LocalDate
-  ): Future[Int] = {
-    IntDemoRepository
-      .mergePersonalInfo(token.token, firstName, dateOfBirth)
-      .transact(xa)
-      .unsafeToFuture()
-  }
-
-  def findPersonalInfo(
-      token: TokenString
-  ): Future[Option[(String, LocalDate)]] = {
-    IntDemoRepository
-      .findPersonalInfo(token.token)
-      .transact(xa)
-      .unsafeToFuture()
-  }
-}
-
-object IntDemoRepository {
-
-  case class DatabaseError(databaseReportedError: Throwable) {
-    override def toString: String = s"Database error: $databaseReportedError"
-  }
-
-  def valueOf(status: intdemo_models.SubjectStatus): Int =
-    status match {
-      case intdemo_models.SubjectStatus.UNCONNECTED =>
-        intdemo_models.SubjectStatus.UNCONNECTED.value
-      case intdemo_models.SubjectStatus.CONNECTED =>
-        intdemo_models.SubjectStatus.CONNECTED.value
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/intdemo/IntDemoService.scala

@@ -1,83 +1,0 @@
-package io.iohk.atala.prism.intdemo
-
-import cats.effect.unsafe.IORuntime
-import io.grpc.stub.StreamObserver
-import io.iohk.atala.prism.intdemo.IntDemoService.log
-import io.iohk.atala.prism.connector.model.{Connection, TokenString}
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.intdemo.protos.{intdemo_api, intdemo_models}
-import io.iohk.atala.prism.protos.credential_models
-import org.slf4j.LoggerFactory
-
-import scala.concurrent.duration.FiniteDuration
-import scala.concurrent.{ExecutionContext, Future}
-
-class IntDemoService[D](
-    issuerId: ParticipantId,
-    connectorIntegration: ConnectorIntegration,
-    intDemoRepository: IntDemoRepository,
-    schedulerPeriod: FiniteDuration,
-    requiredDataLoader: TokenString => Future[Option[D]],
-    proofRequestIssuer: Connection => Future[Unit],
-    getCredential: D => credential_models.PlainTextCredential
-)(implicit ec: ExecutionContext, runtime: IORuntime) {
-
-  def getConnectionToken(
-      request: intdemo_api.GetConnectionTokenRequest
-  ): Future[intdemo_api.GetConnectionTokenResponse] = {
-    for {
-      connectionToken <- connectorIntegration.generateConnectionToken(issuerId)
-      _ <- intDemoRepository.mergeSubjectStatus(
-        connectionToken,
-        intdemo_models.SubjectStatus.UNCONNECTED
-      )
-    } yield {
-      log.debug(
-        s"Generated new connection token in IDService. request = $request, token = ${connectionToken}"
-      )
-      intdemo_api.GetConnectionTokenResponse(connectionToken.token)
-    }
-  }
-
-  private def getStateMachine(
-      connectionToken: TokenString
-  ): IntDemoStateMachine[D] = {
-    new IntDemoStateMachine(
-      requiredDataLoader = requiredDataLoader,
-      getCredential = getCredential,
-      proofRequestIssuer = proofRequestIssuer,
-      connectorIntegration = connectorIntegration,
-      intDemoRepository = intDemoRepository,
-      connectionToken = connectionToken,
-      issuerId = issuerId
-    )
-  }
-
-  def getSubjectStatus(
-      request: intdemo_api.GetSubjectStatusRequest
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/intdemo/grpcServices/EmploymentServiceImpl.scala

@@ -1,230 +1,0 @@
-package io.iohk.atala.prism.intdemo
-
-import cats.effect.unsafe.IORuntime
-
-import java.time.LocalDate
-import io.circe.Json
-import io.circe.Json.fromString
-import io.grpc.stub.StreamObserver
-import io.iohk.atala.prism.intdemo.EmploymentServiceImpl.{
-  RequiredEmploymentData,
-  getRequiredEmploymentData,
-  issuerId,
-  requestIdAndDegreeCredentials
-}
-import io.iohk.atala.prism.utils.Base64Utils
-import io.iohk.atala.prism.intdemo.SharedCredentials.{formatDate, jsonPrinter}
-import io.iohk.atala.prism.connector.model.{Connection, TokenString}
-import io.iohk.atala.prism.credentials.content.CredentialContent
-import io.iohk.atala.prism.intdemo.html.ProofOfEmployment
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.intdemo.protos.intdemo_api
-import io.iohk.atala.prism.protos.credential_models
-
-import scala.concurrent.duration.FiniteDuration
-import scala.concurrent.{ExecutionContext, Future}
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.credentials.json.JsonBasedCredential
-
-import scala.util.Try
-
-class EmploymentServiceImpl(
-    connectorIntegration: ConnectorIntegration,
-    intDemoRepository: IntDemoRepository,
-    schedulerPeriod: FiniteDuration
-)(implicit ec: ExecutionContext, runtime: IORuntime)
-    extends intdemo_api.EmploymentServiceGrpc.EmploymentService {
-
-  val service = new IntDemoService[RequiredEmploymentData](
-    issuerId = issuerId,
-    connectorIntegration = connectorIntegration,
-    intDemoRepository = intDemoRepository,
-    schedulerPeriod = schedulerPeriod,
-    requiredDataLoader = getRequiredEmploymentData(connectorIntegration),
-    proofRequestIssuer = requestIdAndDegreeCredentials(connectorIntegration),
-    getCredential = EmploymentServiceImpl.getEmploymentCredential
-  )
-
-  override def getConnectionToken(
-      request: intdemo_api.GetConnectionTokenRequest
-  ): Future[intdemo_api.GetConnectionTokenResponse] =
-    service.getConnectionToken(request)
-
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/intdemo/grpcServices/InsuranceServiceImpl.scala

@@ -1,243 +1,0 @@
-package io.iohk.atala.prism.intdemo
-
-import cats.effect.unsafe.IORuntime
-import io.circe.Json
-import io.circe.Json.fromString
-import io.grpc.stub.StreamObserver
-import io.iohk.atala.prism.connector.model.Connection
-import io.iohk.atala.prism.connector.model.TokenString
-import io.iohk.atala.prism.credentials.content.CredentialContent
-import io.iohk.atala.prism.credentials.json.JsonBasedCredential
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.intdemo.InsuranceServiceImpl.RequiredInsuranceData
-import io.iohk.atala.prism.intdemo.InsuranceServiceImpl.getInsuranceCredential
-import io.iohk.atala.prism.intdemo.InsuranceServiceImpl.getRequiredInsuranceData
-import io.iohk.atala.prism.intdemo.InsuranceServiceImpl.requestIdAndEmploymentCredentials
-import io.iohk.atala.prism.intdemo.SharedCredentials.formatDate
-import io.iohk.atala.prism.intdemo.SharedCredentials.jsonPrinter
-import io.iohk.atala.prism.intdemo.html.HealthCredential
-import io.iohk.atala.prism.intdemo.protos.intdemo_api
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.protos.credential_models
-import io.iohk.atala.prism.utils.Base64Utils
-
-import java.time.LocalDate
-import scala.concurrent.ExecutionContext
-import scala.concurrent.Future
-import scala.concurrent.duration.FiniteDuration
-import scala.util.Try
-
-class InsuranceServiceImpl(
-    connectorIntegration: ConnectorIntegration,
-    intDemoRepository: IntDemoRepository,
-    schedulerPeriod: FiniteDuration
-)(implicit ec: ExecutionContext, runtime: IORuntime)
-    extends intdemo_api.InsuranceServiceGrpc.InsuranceService {
-
-  val service = new IntDemoService[RequiredInsuranceData](
-    InsuranceServiceImpl.issuerId,
-    connectorIntegration,
-    intDemoRepository,
-    schedulerPeriod,
-    getRequiredInsuranceData(connectorIntegration),
-    requestIdAndEmploymentCredentials(connectorIntegration),
-    getInsuranceCredential
-  )
-
-  override def getConnectionToken(
[…]

### 2023-07-25 prism-backend/connector/src/main/scala/io/iohk/atala/prism/models/ParticipantId.scala

@@ -1,11 +1,0 @@
-package io.iohk.atala.prism.models
-
-import derevo.derive
-import tofu.logging.derivation.loggable
-
-import java.util.UUID
-
-@derive(loggable)
-case class ParticipantId(uuid: UUID) extends AnyVal with UUIDValue
-
-object ParticipantId extends UUIDValue.Builder[ParticipantId]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/connector/ConnectionsRpcSpec.scala

@@ -1,761 +1,0 @@
-package io.iohk.atala.prism.connector
-
-import cats.effect.unsafe.implicits.global
-import cats.syntax.option._
-import com.google.protobuf.ByteString
-import doobie.implicits._
-import io.grpc.{Status, StatusRuntimeException}
-import io.iohk.atala.prism.auth.SignedRpcRequest
-import io.iohk.atala.prism.connector.model.ParticipantType.Holder
-import io.iohk.atala.prism.connector.model._
-import io.iohk.atala.prism.connector.repositories.daos.{ConnectionTokensDAO, ConnectionsDAO, ParticipantsDAO}
-import io.iohk.atala.prism.crypto.EC.{INSTANCE => EC}
-import io.iohk.atala.prism.crypto.ECConfig.{INSTANCE => ECConfig}
-import io.iohk.atala.prism.crypto.keys.{ECKeyPair, ECPublicKey}
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.logging.TraceId
-import io.iohk.atala.prism.protos.connector_api.GetConnectionTokenInfoRequest
-import io.iohk.atala.prism.protos.node_api.GetDidDocumentRequest
-import io.iohk.atala.prism.protos.node_models.{KeyUsage, LedgerData}
-import io.iohk.atala.prism.protos.{connector_api, connector_models, node_api, node_models}
-import io.iohk.atala.prism.utils.syntax._
-import io.iohk.atala.prism.{DIDUtil, auth}
-import org.mockito.captor.ArgCaptor
-import org.mockito.scalatest.MockitoSugar
-import org.scalatest.Assertion
-import org.scalatest.OptionValues._
-
-import java.time.{Instant, LocalDateTime, ZoneOffset}
-import java.util.UUID
-import scala.concurrent.Future
-import scala.util.Random
-
-class ConnectionsRpcSpec extends ConnectorRpcSpecBase with MockitoSugar {
-
-  "GenerateConnectionTokens" should {
-    "generate connection tokens" in {
-      val (keyPair, did) = createDid
-      testConnectionTokensGeneration(keyPair, keyPair.getPublicKey, did)
-    }
-
-    "generate connection tokens using unpublished did" in {
-      val (keyPair, did) = DIDUtil.createUnpublishedDid
-      testConnectionTokensGeneration(keyPair, keyPair.getPublicKey, did)
-    }
-
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/connector/MessagesRpcSpec.scala

@@ -1,647 +1,0 @@
-package io.iohk.atala.prism.connector
-
-import cats.effect.unsafe.implicits.global
-import com.google.protobuf.ByteString
-import doobie.implicits._
-import io.grpc.stub.StreamObserver
-import io.grpc.{Status, StatusRuntimeException}
-import io.iohk.atala.prism.auth.SignedRpcRequest
-import io.iohk.atala.prism.connector.model.MessageId
-import io.iohk.atala.prism.connector.repositories.daos.MessagesDAO
-import io.iohk.atala.prism.crypto.EC.{INSTANCE => EC}
-import io.iohk.atala.prism.crypto.keys.{ECKeyPair, ECPublicKey}
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.logging.TraceId
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.protos.connector_models.MessageToSendByConnectionToken
-import io.iohk.atala.prism.protos.{connector_api, credential_models}
-import io.iohk.atala.prism.{DIDUtil, auth}
-import org.mockito.ArgumentMatchers.any
-import org.mockito.Mockito
-import org.mockito.MockitoSugar._
-import org.mockito.captor.ArgCaptor
-import org.mockito.verification.VerificationWithTimeout
-import org.scalatest.Assertion
-
-import java.util.UUID
-
-class MessagesRpcSpec extends ConnectorRpcSpecBase {
-  private def eventually: VerificationWithTimeout = Mockito.timeout(5000)
-
-  "SendMessage" should {
-    "insert message into database" in {
-      val (keyPair, did) = createDid
-      testSendMessage(keyPair.getPublicKey, keyPair, did)
-    }
-
-    "insert message into database using unpublished did auth" in {
-      val (keyPair, did) = DIDUtil.createUnpublishedDid
-      testSendMessage(keyPair.getPublicKey, keyPair, did)
-    }
-
-    "fail to insert message to database if user provided id is incorrect uuid" in {
-      val (keyPair, did) = createDid
-
-      val issuerId =
-        createIssuer("Issuer", Some(keyPair.getPublicKey), Some(did))
-      val holderId = createHolder("Holder")
-      val connectionId = createConnection(issuerId, holderId)
-      val messageId = "incorrect uuid"
-      val request = connector_api.SendMessageRequest(
-        connectionId = connectionId.toString,
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/connector/RegistrationRpcSpec.scala

@@ -1,287 +1,0 @@
-package io.iohk.atala.prism.connector
-
-import cats.effect.unsafe.implicits.global
-import cats.syntax.option._
-import com.google.protobuf.ByteString
-import doobie.implicits._
-import io.iohk.atala.prism.connector.model._
-import io.iohk.atala.prism.connector.repositories.daos.ParticipantsDAO
-import io.iohk.atala.prism.crypto.EC.{INSTANCE => EC}
-import io.iohk.atala.prism.crypto.Sha256
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.models.{AtalaOperationId, ParticipantId}
-import io.iohk.atala.prism.protos.connector_api.{RegisterDIDRequest, RegisterDIDResponse}
-import io.iohk.atala.prism.protos.node_api.{GetDidDocumentResponse, ScheduleOperationsResponse}
-import io.iohk.atala.prism.protos.node_models.{CreateDIDOutput, DIDData, OperationOutput}
-import io.iohk.atala.prism.protos.{connector_api, node_models}
-import io.iohk.atala.prism.util.KeyUtils.createNodePublicKey
-import org.mockito.ArgumentMatchersSugar.*
-import org.mockito.IdiomaticMockito._
-import org.scalatest.Assertion
-import org.scalatest.OptionValues._
-
-import scala.concurrent.Future
-import scala.util.Try
-
-class RegistrationRpcSpec extends ConnectorRpcSpecBase {
-
-  def createRequest(name: String, logo: Array[Byte]): RegisterDIDRequest = {
-    connector_api
-      .RegisterDIDRequest(name = name)
-      .withLogo(ByteString.copyFrom(logo))
-      .withRole(connector_api.RegisterDIDRequest.Role.issuer)
-      .withCreateDidOperation(node_models.SignedAtalaOperation())
-  }
-
-  "registerDID" should {
-    "work" in {
-      usingApiAs.unlogged { blockingStub =>
-        val expectedDID = DataPreparation.newDID()
-        val name = "iohk"
-        val logo = "none".getBytes()
-        val operationId = AtalaOperationId.random()
-        val createDidResponse = OperationOutput(
-          OperationOutput.Result.CreateDidOutput(CreateDIDOutput(expectedDID.getSuffix)),
-          OperationOutput.OperationMaybe.OperationId(operationId.toProtoByteString)
-        )
-        val request = createRequest(name, logo)
-
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/connector/SignedRequestsAuthenticatorSpec.scala

@@ -1,511 +1,0 @@
-package io.iohk.atala.prism.connector
-
-import cats.Id
-import cats.data.ReaderT
-import cats.effect.IO
-import cats.effect.unsafe.implicits.{global => globalRuntime}
-import io.grpc.Context
-import io.iohk.atala.prism.auth.AuthenticatorF
-import io.iohk.atala.prism.auth.errors.AuthErrorSupport
-import io.iohk.atala.prism.auth.grpc.{GrpcAuthenticationHeader, GrpcAuthenticationHeaderParser}
-import io.iohk.atala.prism.connector.errors.{UnknownValueError, co}
-import io.iohk.atala.prism.connector.model._
-import io.iohk.atala.prism.connector.repositories.{ParticipantsRepository, RequestNoncesRepository}
-import io.iohk.atala.prism.crypto.EC.{INSTANCE => EC}
-import io.iohk.atala.prism.crypto.Sha256
-import io.iohk.atala.prism.crypto.keys.ECPublicKey
-import io.iohk.atala.prism.crypto.signature.ECSignature
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.logging.TraceId
-import io.iohk.atala.prism.logging.TraceId.IOWithTraceIdContext
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.nonce.RequestAuthenticator
-import io.iohk.atala.prism.protos.node_api._
-import io.iohk.atala.prism.protos.{connector_api, node_api, node_models}
-import io.iohk.atala.prism.tracing.Tracing._
-import io.iohk.atala.prism.util.KeyUtils.createNodePublicKey
-import io.iohk.atala.prism.utils.FutureEither.FutureEitherOps
-import io.iohk.atala.prism.utils.IOUtils._
-import io.iohk.atala.prism.{DIDUtil, auth}
-import org.mockito.ArgumentMatchersSugar._
-import org.mockito.IdiomaticMockito._
-import org.mockito.matchers.DefaultValueProvider
-import org.scalatest.Assertion
-import org.scalatest.concurrent.ScalaFutures._
-import org.scalatest.matchers.must.Matchers._
-import org.scalatest.wordspec.AnyWordSpec
-import org.slf4j.{Logger, LoggerFactory}
-import tofu.logging.Logs
-
-import java.util.UUID
-import scala.concurrent.ExecutionContext.Implicits.global
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/connector/repositories/ConnectionsRepositorySpec.scala

@@ -1,526 +1,0 @@
-package io.iohk.atala.prism.connector.repositories
-
-import cats.effect.unsafe.implicits.global
-import cats.syntax.either._
-import com.softwaremill.diffx.generic.auto._
-import com.softwaremill.diffx.scalatest.DiffMustMatcher._
-import doobie.implicits._
-import io.iohk.atala.prism.DIDUtil
-import io.iohk.atala.prism.connector.model._
-import io.iohk.atala.prism.connector.repositories.daos._
-import io.iohk.atala.prism.connector.DataPreparation
-import io.iohk.atala.prism.crypto.EC.{INSTANCE => EC}
-import io.iohk.atala.prism.logging.TraceId
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.repositories.ops.SqlTestOps._
-import io.iohk.atala.prism.utils.IOUtils._
-import org.scalatest.Assertion
-import org.scalatest.OptionValues._
-
-import java.time.{Instant, LocalDateTime, ZoneOffset}
-
-class ConnectionsRepositorySpec extends ConnectorRepositorySpecBase {
-  lazy val connectionsRepository =
-    ConnectionsRepository.unsafe(dbLiftedToTraceIdIO, connectorRepoSpecLogs)
-  lazy val contactsRepository =
-    ParticipantsRepository.unsafe(dbLiftedToTraceIdIO, connectorRepoSpecLogs)
-
-  private def checkConnection(
-      connectionId: ConnectionId,
-      token: TokenString
-  ): Assertion = {
-    sql"""SELECT COUNT(1) FROM connections WHERE id=$connectionId"""
-      .runUnique[Int]() mustBe 1
-    // verify that instantiated_at field is set correctly, to avoid conversion or timezone errors
-    sql"""SELECT COUNT(1) FROM connections
-         |WHERE id = $connectionId
-         |AND instantiated_at > now() - '10 seconds'::interval AND instantiated_at < now()""".stripMargin
-      .runUnique[Int]() mustBe 1
-    sql"""SELECT COUNT(1) FROM connection_tokens WHERE token=$token AND used_at IS NOT NULL"""
-      .runUnique[Int]() mustBe 1
-    sql"""SELECT COUNT(1) FROM connection_tokens WHERE token=$token AND used_at IS NULL"""
-      .runUnique[Int]() mustBe 0
-  }
-
-  "insertToken" should {
-    "correctly generate tokens" in {
-      val issuerId = createIssuer()
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/connector/repositories/ParticipantsRepositorySpec.scala

@@ -1,283 +1,0 @@
-package io.iohk.atala.prism.connector.repositories
-
-import cats.effect.unsafe.implicits.global
-import doobie.implicits._
-import io.iohk.atala.prism.connector.errors.{UnknownValueError, co}
-import io.iohk.atala.prism.connector.model._
-import io.iohk.atala.prism.connector.repositories.daos._
-import io.iohk.atala.prism.connector.DataPreparation
-import io.iohk.atala.prism.connector.repositories.ParticipantsRepository.FindByError
-import io.iohk.atala.prism.crypto.Sha256Digest
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.utils.Base64Utils.decodeURL
-import io.iohk.atala.prism.logging.TraceId
-import io.iohk.atala.prism.logging.TraceId.IOWithTraceIdContext
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.utils.IOUtils._
-import org.scalatest.EitherValues._
-import org.scalatest.OptionValues._
-
-class ParticipantsRepositorySpec extends ConnectorRepositorySpecBase {
-  lazy val participantsRepository: ParticipantsRepository[IOWithTraceIdContext] =
-    ParticipantsRepository.unsafe(dbLiftedToTraceIdIO, connectorRepoSpecLogs)
-  private val canonicalSuffix =
-    "0f753f41e0f3488ba56bd581d153ae9b3c9040cbcc7a63245b4644a265eb3b77"
-  private val encodedStateUsed =
-    "CmEKXxJdCgdtYXN0ZXIwEAFCUAoJc2VjcDI1NmsxEiAel_7KEiez4s_e0u8DyJwLkUnVmUHBuWU-0h01nerSNRohAJlR51Vbk49vagehAwQkFvW_fvyM1qa4ileIEYkXs4pF"
-
-  private val shortDID =
-    DID.buildCanonical(Sha256Digest.fromHex(canonicalSuffix))
-  private val longDID = DID.buildLongForm(
-    Sha256Digest.fromHex(canonicalSuffix),
-    decodeURL(encodedStateUsed)
-  )
-
-  "getParticipant by did" should {
-    "get a participant" in {
-      val id = ParticipantId.random()
-      val did = DataPreparation.newDID()
-      val info = ParticipantInfo(
-        id,
-        ParticipantType.Issuer,
-        None,
-        "issuer",
-        Some(did),
-        None,
-        None
-      )
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/cviews/CredentialViewsServiceSpec.scala

@@ -1,174 +1,0 @@
-package io.iohk.atala.prism.cviews
-
-import cats.effect.unsafe.implicits.global
-import io.grpc.ServerServiceDefinition
-import io.iohk.atala.prism.auth.{AuthenticatorF, SignedRpcRequest}
-import io.iohk.atala.prism.connector.{ConnectorAuthenticator, DataPreparation}
-import io.iohk.atala.prism.connector.repositories.{ParticipantsRepository, RequestNoncesRepository}
-import io.iohk.atala.prism.protos.connector_api.GetCurrentUserRequest
-import io.iohk.atala.prism.protos.cviews_api.{CredentialViewsServiceGrpc, GetCredentialViewTemplatesRequest}
-import io.iohk.atala.prism.utils.IOUtils._
-import io.iohk.atala.prism.view.HtmlViewImage.imageBase64
-import io.iohk.atala.prism.{DIDUtil, RpcSpecBase}
-import org.mockito.MockitoSugar._
-
-import java.io.{File, PrintWriter}
-
-class CredentialViewsServiceSpec extends RpcSpecBase with DIDUtil {
-  private val usingApiAs = usingApiAsConstructor(
-    new CredentialViewsServiceGrpc.CredentialViewsServiceBlockingStub(_, _)
-  )
-
-  private lazy val participantsRepository =
-    ParticipantsRepository.unsafe(dbLiftedToTraceIdIO, testLogs)
-  private lazy val requestNoncesRepository =
-    RequestNoncesRepository.unsafe(dbLiftedToTraceIdIO, testLogs)
-  protected lazy val nodeMock =
-    mock[io.iohk.atala.prism.protos.node_api.NodeServiceGrpc.NodeService]
-  private lazy val authenticator = AuthenticatorF.unsafe(
-    nodeMock,
-    new ConnectorAuthenticator(
-      participantsRepository,
-      requestNoncesRepository
-    ),
-    testLogs
-  )
-
-  private val authenticatorLogger = org.slf4j.LoggerFactory
-    .getLogger(authenticator.getClass)
-    .asInstanceOf[ch.qos.logback.classic.Logger]
-
-  override def services: Seq[ServerServiceDefinition] =
-    Seq(
-      CredentialViewsServiceGrpc.bindService(
-        new CredentialViewsService(authenticator),
-        executionContext
-      )
-    )
-
-  override def beforeEach(): Unit = {
-    super.beforeEach()
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/intdemo/ConnectorIntegrationImplSpec.scala

@@ -1,118 +1,0 @@
-package io.iohk.atala.prism.intdemo
-
-import io.iohk.atala.prism.connector.model.{ConnectionId, MessageId}
-import io.iohk.atala.prism.connector.services.{ConnectionsService, MessagesService}
-import io.iohk.atala.prism.intdemo.ConnectorIntegration.ConnectorIntegrationImpl
-import ConnectorIntegrationImplSpec._
-import cats.effect.unsafe.implicits.{global => globalRuntime}
-import cats.syntax.applicative._
-import cats.syntax.either._
-import io.iohk.atala.prism.connector.repositories.MessagesRepository.InsertMessageError
-import io.iohk.atala.prism.logging.TraceId.IOWithTraceIdContext
-import io.iohk.atala.prism.models.ParticipantId
-import io.iohk.atala.prism.protos.credential_models
-import org.mockito.ArgumentMatchersSugar.{any, argThat, eqTo}
-import org.mockito.MockitoSugar.{mock, times, verify, when}
-import org.scalatest.flatspec.AnyFlatSpec
-import org.scalatest.concurrent.ScalaFutures._
-
-import scala.concurrent.ExecutionContext.Implicits.global
-
-class ConnectorIntegrationImplSpec extends AnyFlatSpec {
-
-  "sendCredential" should "send a decodable credential" in connectorIntegration {
-    (connectorIntegration, messagesService) =>
-      val credential = credential_models.PlainTextCredential(
-        encodedCredential = "encodedCredential",
-        encodedMerkleProof = "Merkle proof"
-      )
-
-      connectorIntegration
-        .sendCredential(senderId, connectionId, credential)
-        .futureValue
-
-      verify(messagesService, times(1)).insertMessage(
-        eqTo(senderId),
-        eqTo(connectionId),
-        decodesTo(credential),
-        eqTo(None)
-      )
-  }
-
-  "sendProofRequest" should "send a decodable proof request" in connectorIntegration {
-    (connectorIntegration, messagesService) =>
-      val proofRequest =
-        credential_models.ProofRequest(
-          typeIds = Seq("a-type-id"),
-          connectionToken = "a-connection-token"
-        )
-
-      connectorIntegration
-        .sendProofRequest(senderId, connectionId, proofRequest)
-        .futureValue
-
-      verify(messagesService, times(1)).insertMessage(
-        eqTo(senderId),
-        eqTo(connectionId),
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/intdemo/EmploymentServiceImplSpec.scala

@@ -1,68 +1,0 @@
-package io.iohk.atala.prism.intdemo
-
-import java.time.LocalDate
-import java.time.format.DateTimeFormatter
-import io.circe.parser.parse
-import io.iohk.atala.prism.intdemo.EmploymentServiceImpl.RequiredEmploymentData
-import Testing._
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import org.scalatest.OptionValues._
-import org.scalatest.flatspec.AnyFlatSpec
-import org.scalatest.matchers.should.Matchers._
-import io.iohk.atala.prism.utils.Base64Utils
-
-class EmploymentServiceImplSpec extends AnyFlatSpec {
-
-  "getEmploymentCredential" should "return a correct employment credential" in {
-    val (name, dateOfBirth) = ("Joe wong", LocalDate.of(1973, 6, 2))
-
-    val idCredential = IdServiceImpl.getIdCredential((name, dateOfBirth))
-    val degreeCredential = DegreeServiceImpl.getDegreeCredential(idCredential)
-
-    val employmentCredential =
-      EmploymentServiceImpl.getEmploymentCredential(
-        RequiredEmploymentData(idCredential, degreeCredential)
-      )
-
-    val issuerDID = s"did:prism:${EmploymentServiceImpl.issuerId.uuid}"
-    val issuanceDate = LocalDate.now()
-    val issuerName = "Decentralized Inc."
-    val issuerAddress = "67 Clasper Way, Herefoot, HF1 0AF"
-    val issuanceKeyId = DID.getDEFAULT_MASTER_KEY_ID
-    val holderName = name
-    val credentialType = EmploymentServiceImpl.credentialTypeId
-    val employmentStartDate = LocalDate.now().minusMonths(1)
-    val employmentStatus = "Full-time"
-
-    // Verify JSON document
-    val jsonString =
-      Base64Utils.decodeUrlToString(employmentCredential.encodedCredential)
-    val document = parse(jsonString).toOption.value.hcursor
-
-    document.jsonStr("issuerDid") shouldBe issuerDID
-    document.jsonStr("issuanceKeyId") shouldBe issuanceKeyId
-    document.jsonStr("issuerName") shouldBe issuerName
-    document.jsonStr("issuerAddress") shouldBe issuerAddress
-    document.jsonStr("issuanceDate") shouldBe DateTimeFormatter.ISO_LOCAL_DATE
-      .format(issuanceDate)
-    document.jsonStr(
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/intdemo/InsuranceServiceImplSpec.scala

@@ -1,91 +1,0 @@
-package io.iohk.atala.prism.intdemo
-
-import java.time.LocalDate
-import java.time.format.DateTimeFormatter
-
-import io.circe.parser.parse
-import io.iohk.atala.prism.intdemo.EmploymentServiceImpl.RequiredEmploymentData
-import io.iohk.atala.prism.intdemo.InsuranceServiceImpl.RequiredInsuranceData
-import org.scalatest.flatspec.AnyFlatSpec
-import org.scalatest.matchers.should.Matchers._
-import Testing._
-import org.scalatest.OptionValues._
-import io.iohk.atala.prism.utils.Base64Utils
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-
-class InsuranceServiceImplSpec extends AnyFlatSpec {
-
-  "getInsuranceCredential" should "return a correct insurance credential" in {
-    val (name, dateOfBirth) = ("Jo Wong", LocalDate.of(1973, 6, 2))
-
-    val idCredential = IdServiceImpl.getIdCredential((name, dateOfBirth))
-    val degreeCredential = DegreeServiceImpl.getDegreeCredential(idCredential)
-    val employmentCredential =
-      EmploymentServiceImpl.getEmploymentCredential(
-        RequiredEmploymentData(idCredential, degreeCredential)
-      )
-    val insuranceCredential =
-      InsuranceServiceImpl.getInsuranceCredential(
-        RequiredInsuranceData(idCredential, employmentCredential)
-      )
-
-    val employmentCredentialData =
-      EmploymentCredentialData(employmentCredential)
-
-    // Verify JSON document
-    val jsonString =
-      Base64Utils.decodeUrlToString(insuranceCredential.encodedCredential)
-    val document = parse(jsonString).toOption.value.hcursor
-
-    val credentialType = InsuranceServiceImpl.credentialTypeId
-    val issuerName = "Verified Insurance Ltd"
-    val issuerDID = s"did:prism:${InsuranceServiceImpl.issuerId.uuid}"
-    val issuanceKeyId = DID.getDEFAULT_MASTER_KEY_ID
-    val issuanceDate = LocalDate.now()
-    val expirationDate = issuanceDate.plusYears(1)
-    val policyNumber = "ABC-123456789"
-    val productClass = "Health Insurance"
-    val holderName = name
-    val holderDateOfBirth = dateOfBirth
-    val currentEmployerName = employmentCredentialData.employerName
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/intdemo/Testing.scala

@@ -1,81 +1,0 @@
-package io.iohk.atala.prism.intdemo
-
-import io.circe.{ACursor, CursorOp, Decoder, FailedCursor, HCursor}
-import org.mockito.Mockito
-import org.mockito.verification.{VerificationMode, VerificationWithTimeout}
-import org.scalatest.exceptions.TestFailedException
-
-private[intdemo] object Testing {
-
-  /** Usage: {{{verify(mock, eventually.times(1)).someMethod()}}}
-    */
-  def eventually: VerificationWithTimeout = Mockito.timeout(1000)
-
-  /** Verifies a method has never been called after an interval of 100 millis. Usage:
-    * {{{verify(mock, neverEver).someMethod()}}}
-    */
-  def neverEver: VerificationMode = Mockito.after(100).never
-
-  /** Returns the contents of the given resource file located in {@code intdemo}.
-    */
-  def readResource(resource: String): String = {
-    try {
-      scala.io.Source.fromResource(s"intdemo/$resource").mkString
-    } catch {
-      case _: Throwable =>
-        throw new RuntimeException(s"Resource $resource not found")
-    }
-  }
-
-  /** Extract fields from JSON using dot notation names. e.g. {{{cursor.jsonStr("a.b.c")}}}
-    * @param cursor
-    *   an HCursor
-    */
-  implicit class CirceFieldAccess(cursor: HCursor) {
-    import org.scalatest.OptionValues._
-    import org.scalactic.source.Position
-
-    def jsonStr(dotName: String): String = jsonVal[String](dotName)
-    def jsonArr(dotName: String): List[String] = jsonVal[List[String]](dotName)
-
-    def jsonVal[T: Decoder](dotName: String): T = {
-      @annotation.tailrec
-      def loop(l: List[String], ac: ACursor): T = {
-        ac match {
-          case failedCursor: FailedCursor =>
-            val errMsg =
-              s"Could not find ${CursorOp.opsToPath(failedCursor.history)} inside ${cursor.value}"
-            val trace = Thread.currentThread.getStackTrace
-
-            /** the exact index of StackTraceElement, in this case 4 is the original function that called jsonStr or
-              * jsonArr, which is what we need in this case
-              */
-            val originalPosition = trace(4)
-            throw new TestFailedException(
-              _ => Some(errMsg),
-              None,
-              Position(
-                fileName = originalPosition.getFileName,
-                filePathname = originalPosition.getClassName,
-                lineNumber = originalPosition.getLineNumber
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/migrations/V22MigrationSpec.scala

@@ -1,255 +1,0 @@
-package io.iohk.atala.prism.migrations
-
-import java.util.UUID
-
-import doobie.implicits._
-import io.iohk.atala.prism.connector.model.ParticipantType
-import io.iohk.atala.prism.daos.BaseDAO
-import io.iohk.atala.prism.connector.repositories.daos._
-import io.iohk.atala.prism.repositories.PostgresMigrationSpec
-import io.iohk.atala.prism.repositories.ops.SqlTestOps.Implicits
-
-class V22MigrationSpec extends PostgresMigrationSpec("V22") with BaseDAO {
-  private def insertIssuer(issuerId: UUID, name: String, did: String): Unit = {
-    sql"""INSERT INTO participants(id, tpe, did, public_key, name, logo)
-         |VALUES ($issuerId, ${ParticipantType.Issuer: ParticipantType}::PARTICIPANT_TYPE, $did, null, $name, '')
-         |""".stripMargin.runUpdate()
-    sql"""INSERT INTO issuers (issuer_id) VALUES ($issuerId)""".runUpdate()
-  }
-
-  private def insertVerifier(
-      verifierId: UUID,
-      name: String,
-      did: String
-  ): Unit = {
-    sql"""INSERT INTO participants(id, tpe, did, public_key, name, logo)
-         |VALUES ($verifierId, ${ParticipantType.Verifier: ParticipantType}::PARTICIPANT_TYPE, $did, null, $name, '')
-         |""".stripMargin.runUpdate()
-    sql"""INSERT INTO verifiers (verifier_id) VALUES ($verifierId)"""
-      .runUpdate()
-  }
-
-  private def insertGroup(
-      issuerId: UUID,
-      groupId: UUID,
-      groupName: String
-  ): Unit = {
-    sql"""INSERT INTO issuer_groups (group_id,issuer_id,name)
-         |VALUES ($groupId, $issuerId, $groupName)
-         |""".stripMargin.runUpdate()
-  }
-
-  private def insertSubject(subjectId: UUID, issuerId: UUID): Unit = {
-    val externalId = UUID.randomUUID()
-    sql"""INSERT INTO issuer_subjects (subject_id , external_id , created_at , connection_status , issuer_id , subject_data)
-         |VALUES ($subjectId, $externalId, now(), 'CONNECTION_MISSING',$issuerId,'{}')
-         |""".stripMargin.runUpdate()
-  }
-
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/migrations/V24MigrationSpec.scala

@@ -1,357 +1,0 @@
-package io.iohk.atala.prism.migrations
-
-import java.util.UUID
-
-import doobie.implicits.toSqlInterpolator
-import doobie.postgres.implicits.pgEnumString
-import doobie.util.invariant.InvalidEnum
-import doobie.Meta
-import enumeratum.{Enum, EnumEntry}
-import enumeratum.EnumEntry.UpperSnakecase
-import io.iohk.atala.prism.connector.model.{ConnectionStatus, ParticipantType}
-import io.iohk.atala.prism.daos.BaseDAO
-import io.iohk.atala.prism.connector.repositories.daos._
-import io.iohk.atala.prism.repositories.PostgresMigrationSpec
-import io.iohk.atala.prism.repositories.ops.SqlTestOps.Implicits
-
-// Models from the legacy cstore, used only in this test
-object LegacyModels {
-  sealed trait IndividualConnectionStatus extends EnumEntry with UpperSnakecase
-
-  object IndividualConnectionStatus extends Enum[IndividualConnectionStatus] {
-    val values = findValues
-
-    case object Created extends IndividualConnectionStatus
-    case object Invited extends IndividualConnectionStatus
-    case object Connected extends IndividualConnectionStatus
-    case object Revoked extends IndividualConnectionStatus
-  }
-}
-
-class V24MigrationSpec extends PostgresMigrationSpec("V24") with BaseDAO {
-
-  import LegacyModels._
-
-  private def insertIssuer(issuerId: UUID, name: String, did: String): Unit = {
-    sql"""INSERT INTO participants(id, tpe, did, public_key, name, logo)
-         |VALUES ($issuerId, ${ParticipantType.Issuer: ParticipantType}::PARTICIPANT_TYPE, $did, null, $name, '')
-         |""".stripMargin.runUpdate()
-  }
-
-  private def insertVerifier(
-      verifierId: UUID,
-      name: String,
-      did: String
-  ): Unit = {
-    sql"""INSERT INTO participants(id, tpe, did, public_key, name, logo)
-         |VALUES ($verifierId, ${ParticipantType.Verifier: ParticipantType}::PARTICIPANT_TYPE, $did, null, $name, '')
-         |""".stripMargin.runUpdate()
-  }
-
-  private def insertGroup(
-      issuerId: UUID,
-      groupId: UUID,
-      groupName: String
-  ): Unit = {
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/migrations/V40MigrationSpec.scala

@@ -1,53 +1,0 @@
-package io.iohk.atala.prism.migrations
-
-import java.util.UUID
-import doobie.implicits._
-import io.iohk.atala.prism.connector.model.ParticipantType
-import io.iohk.atala.prism.daos.BaseDAO
-import io.iohk.atala.prism.connector.repositories.daos._
-import io.iohk.atala.prism.repositories.PostgresMigrationSpec
-import io.iohk.atala.prism.repositories.ops.SqlTestOps.Implicits
-
-class V40MigrationSpec extends PostgresMigrationSpec("V40") with BaseDAO {
-  private val problemDid1 = "did:prism:asdasdasdasdasdaasdasdasdasdasda1"
-  private val problemDid2 = "did:prism:asdasdasdasdasdaasdasdasdasdasda2"
-  private val issuer1Did = "did:prism:issuer1"
-  private val issuer2Did = "did:prism:issuer2"
-
-  private def getActualState: List[String] =
-    sql"SELECT did FROM participants".queryList[String]().toList
-
-  private def insertParticipants(
-      issuerId: UUID,
-      name: String,
-      did: String
-  ): Unit =
-    sql"""INSERT INTO participants(id, tpe, did, public_key, name, logo)
-         |VALUES ($issuerId, ${ParticipantType.Issuer: ParticipantType}::PARTICIPANT_TYPE, $did, null, $name, '')
-         |""".stripMargin.runUpdate()
-
-  test(
-    beforeApply = {
-      insertParticipants(UUID.randomUUID(), "someName1", issuer1Did)
-      insertParticipants(UUID.randomUUID(), "someName2", issuer2Did)
-      insertParticipants(UUID.randomUUID(), "someName3", problemDid1)
-      insertParticipants(UUID.randomUUID(), "someName3", problemDid1)
-      insertParticipants(UUID.randomUUID(), "someName4", problemDid2)
-      insertParticipants(UUID.randomUUID(), "someName4", problemDid2)
-      insertParticipants(UUID.randomUUID(), "someName4", problemDid2)
-      val stateBeforeMigration = getActualState
-      // 7 from initial, 4 originals new, 3 duplicates
-      stateBeforeMigration.size mustBe 14
-      stateBeforeMigration.count(_ == problemDid1) mustBe 2
-      stateBeforeMigration.count(_ == problemDid2) mustBe 3
-    },
-    afterApplied = {
-      val stateAfterMigration = getActualState
[…]

### 2023-07-25 prism-backend/connector/src/test/scala/io/iohk/atala/prism/util/KeyUtils.scala

@@ -1,26 +1,0 @@
-package io.iohk.atala.prism.util
-
-import com.google.protobuf.ByteString
-import io.iohk.atala.prism.crypto.keys.ECPublicKey
-import io.iohk.atala.prism.crypto.ECConfig.{INSTANCE => ECConfig}
-import io.iohk.atala.prism.protos.node_models
-
-object KeyUtils {
-
-  def createNodePublicKey(
-      keyId: String,
-      publicKey: ECPublicKey
-  ): node_models.PublicKey = {
-    val point = publicKey.getCurvePoint
-    val x = ByteString.copyFrom(point.getX.bytes())
-    val y = ByteString.copyFrom(point.getY.bytes())
-    node_models.PublicKey(
-      id = keyId,
-      usage = node_models.KeyUsage.AUTHENTICATION_KEY,
-      keyData = node_models.PublicKey.KeyData.EcKeyData(
-        node_models.ECKeyData(curve = ECConfig.getCURVE_NAME, x = x, y = y)
-      )
-    )
-  }
-
-}

### 2023-07-25 prism-backend/infra/docker/cvp-envoy/build.sh

@@ -1,30 +1,0 @@
-#!/usr/bin/env zsh
-
-usage() {
-  print "Usage: build.sh [[-b] [-p]]
-  Build or push the envoy image for use with compose.
-  -b    build the image
-  -p    push the image
-  "
-  exit 1
-}
-
-build() {
-  docker build -t "895947072537.dkr.ecr.us-east-2.amazonaws.com/cvp-envoy" .
-  exit
-}
-
-push() {
-  docker push "895947072537.dkr.ecr.us-east-2.amazonaws.com/cvp-envoy"
-  exit
-}
-
-while getopts ':bp' arg; do
-  case $arg in
-    (b) build;;
-    (p) push;;
-    (\*) usage;;
-    (\?) usage;;
-  esac
-done
-usage

### 2023-07-25 prism-backend/infra/stage/base/auth/lambda/basic_auth/index.js

@@ -1,24 +1,0 @@
-exports.handler = async (event, context, callback) => {
-
-    const request = event.Records[0].cf.request;
-    const headers = request.headers;
-
-    const user = 'demo';
-    const pass = 'iohk4ever';
-
-    const basicAuthentication = 'Basic ' + new Buffer(user + ':' + pass).toString('base64');
-
-    if (typeof headers.authorization == 'undefined' || headers.authorization[0].value != basicAuthentication) {
-        const body = 'You are not authorized to enter';
-        const response = {
-            status: '401',
-            statusDescription: 'Unauthorized',
-            body: body,
-            headers: {
-                'www-authenticate': [{key: 'WWW-Authenticate', value:'Basic'}]
-            },
-        };
-        callback(null, response);
-    }
-    callback(null, request);
-};

### 2023-07-25 prism-backend/infra/stage/base/cardano/cardano.sh

@@ -1,69 +1,0 @@
-#!/usr/bin/env bash
-set -e
-
-usage() {
-  echo "Usage: cardano.sh [[-a] [-d] [-p] [-s]] <vpc name>
-  Setup Prometheus monitoring for supporting environments.
-  <vpc name> should be the same name as used for vpc creation.
-  -a    apply changes.
-  -p    plan/simulate changes
-  -d    destroy
-  -s    show an (almost) human readable view of the given config
-  -g    create a 'graph.svg' file showing the dependencies of all resources.
-  "
-  exit 1
-}
-
-apply_env() {
-  terraform init -backend-config="key=$state_key" && terraform apply -var "name=$name"
-}
-
-destroy_env() {
-  terraform init -backend-config="key=$state_key" && terraform destroy -var "name=$name"
-}
-
-plan_env() {
-  terraform init -backend-config="key=$state_key" && terraform plan -var "name=$name"
-}
-
-show_env() {
-  terraform init -backend-config="key=$state_key" && terraform show
-}
-
-graph_env () {
-  terraform init -backend-config="key=$state_key" && terraform graph -draw-cycles | dot -Tsvg > graph.svg
-}
-
-action="plan"
-while getopts ':adpsg' arg; do
-  case $arg in
-    (a) action="apply";;
-    (d) action="destroy";;
-    (p) action="plan";;
-    (s) action="show";;
-    (g) action="graph";;
-    (\*) usage
-         exit 1;;
-    (\?) usage
-         exit 1;;
-  esac
-done
-shift $((OPTIND -1))
-
-name=$1
-if [[ -z "${name// }" ]]; then
-  name='prism-test'
-fi
-
-state_key="infra/stage/cardano/$name/terraform.tfstate"
-
-echo "Using name '$name'."
-echo "Performing action '$action'."
-
-case $action in
-  (apply) apply_env;;
-  (destroy) destroy_env;;
-  (plan) plan_env;;
-  (show) show_env;;
-  (graph) graph_env;;
-esac

### 2023-07-25 prism-backend/infra/stage/base/tls/tls.sh

@@ -1,59 +1,0 @@
-#!/usr/bin/env zsh
-set -euo pipefail
-
-usage() {
-  print "Usage: tls.sh [[-a] [-d] [-p] [-s]] <domain name>
-  Setup TLS certificate in ACM.
-  <domain> is a domain name controlled by the account
-  -a    apply changes
-  -p    plan/simulate changes
-  -d    destroy
-  -s    show an (almost) human readable view of the given config
-  "
-  exit 1
-}
-
-apply_env() {
-  terraform init -backend-config="key=$state_key" && terraform apply -var "atala_prism_domain=$atala_prism_domain"
-}
-
-destroy_env() {
-  terraform init -backend-config="key=$state_key" && terraform destroy -var "atala_prism_domain=$atala_prism_domain"
-}
-
-plan_env() {
-  terraform init -backend-config="key=$state_key" && terraform plan -var "atala_prism_domain=$atala_prism_domain"
-}
-
-show_env() {
-    terraform init -backend-config="key=$state_key" && terraform show
-}
-
-action="plan"
-while getopts ':adps' arg; do
-  case $arg in
-    (a) action="apply";;
-    (d) action="destroy";;
-    (p) action="plan";;
-    (s) action="show";;
-    (\*) usage
-         exit 1;;
-    (\?) usage
-         exit 1;;
-  esac
-done
-shift $((OPTIND -1))
-
-atala_prism_domain=${1:-atalaprism.io}
-
-state_key="infra/base/tls/$atala_prism_domain/terraform.tfstate"
-
-print "Using domain name '$atala_prism_domain'."
-print "Performing action '$action'."
-
-case $action in
-  (apply) apply_env;;
-  (destroy) destroy_env;;
-  (plan) plan_env;;
-  (show) show_env;;
-esac

### 2023-07-25 prism-backend/infra/stage/services/prism/geud.sh

@@ -1,6 +1,0 @@
-#!/usr/bin/env bash
-set -euo pipefail
-dir="$( cd "$( dirname "${BASH_SOURCE[0]}" )" >/dev/null 2>&1 && pwd )"
-pushd "$dir" > /dev/null
-GEUD_ENABLED=true ./prism.sh "$@"
-popd > /dev/null

### 2023-07-25 prism-backend/infra/stage/services/prism/intdemo.sh

@@ -1,6 +1,0 @@
-#!/usr/bin/env bash
-set -euo pipefail
-dir="$( cd "$( dirname "${BASH_SOURCE[0]}" )" >/dev/null 2>&1 && pwd )"
-pushd "$dir" > /dev/null
-INTDEMO_ENABLED=true ./prism.sh "$@"
-popd > /dev/null

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/errors/ManagementConsoleErrorSupport.scala

@@ -1,11 +1,0 @@
-package io.iohk.atala.prism.management.console.errors
-
-import io.iohk.atala.prism.errors.ErrorSupport
-
-trait ManagementConsoleErrorSupport extends ErrorSupport[ManagementConsoleError] {
-  override def wrapAsServerError(cause: Throwable): InternalServerError =
-    InternalServerError(cause)
-
-  override def invalidRequest(message: String): ManagementConsoleError =
-    InvalidRequest(message)
-}

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/grpc/ContactsGrpcService.scala

@@ -1,143 +1,0 @@
-package io.iohk.atala.prism.management.console.grpc
-
-import cats.effect.unsafe.IORuntime
-import io.iohk.atala.prism.auth.{AuthAndMiddlewareSupportF, AuthenticatorF}
-import io.iohk.atala.prism.logging.TraceId.IOWithTraceIdContext
-import io.iohk.atala.prism.management.console.errors.{ManagementConsoleError, ManagementConsoleErrorSupport}
-import io.iohk.atala.prism.management.console.integrations.ContactsIntegrationService
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.protos.console_api
-import io.iohk.atala.prism.protos.console_api._
-import io.iohk.atala.prism.utils.FutureEither.{FutureEitherFOps, FutureEitherOps}
-import org.slf4j.{Logger, LoggerFactory}
-
-import scala.concurrent.{ExecutionContext, Future}
-
-class ContactsGrpcService(
-    contactsIntegrationService: ContactsIntegrationService[
-      IOWithTraceIdContext
-    ],
-    val authenticator: AuthenticatorF[ParticipantId, IOWithTraceIdContext]
-)(implicit
-    ec: ExecutionContext,
-    runtime: IORuntime
-) extends console_api.ContactsServiceGrpc.ContactsService
-    with ManagementConsoleErrorSupport
-    with AuthAndMiddlewareSupportF[ManagementConsoleError, ParticipantId] {
-
-  override protected val serviceName: String = "contacts-service"
-  override val IOruntime: IORuntime = runtime
-
-  val logger: Logger = LoggerFactory.getLogger(this.getClass)
-
-  override def createContact(
-      request: CreateContactRequest
-  ): Future[CreateContactResponse] =
-    auth[CreateContact]("createContact", request) { (participantId, query, traceId) =>
-      val maybeGroupName = InstitutionGroup.Name.optional(request.groupName)
-      contactsIntegrationService
-        .createContact(participantId, query, maybeGroupName)
-        .run(traceId)
-        .unsafeToFuture()
-        .toFutureEither
-        .map(c => ProtoCodecs.toContactProto(c.contact, c.connection))
-        .map(console_api.CreateContactResponse().withContact)
-    }
-
-  override def getContacts(
-      request: GetContactsRequest
-  ): Future[GetContactsResponse] =
-    auth[Contact.PaginatedQuery]("getContacts", request) { (participantId, query, traceId) =>
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/grpc/CredentialIssuanceGrpcService.scala

@@ -1,94 +1,0 @@
-package io.iohk.atala.prism.management.console.grpc
-
-import cats.effect.unsafe.IORuntime
-import cats.implicits.{catsSyntaxEitherId, catsSyntaxOptionId}
-import io.iohk.atala.prism.auth.{AuthAndMiddlewareSupportF, AuthenticatorF}
-import io.iohk.atala.prism.logging.TraceId.IOWithTraceIdContext
-import io.iohk.atala.prism.management.console.errors._
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.CredentialIssuancesRepository.{
-  CreateCredentialBulk,
-  CreateCredentialIssuance,
-  GetCredentialIssuance
-}
-import io.iohk.atala.prism.management.console.services.CredentialIssuanceService
-import io.iohk.atala.prism.protos.console_api
-import io.iohk.atala.prism.protos.console_api._
-import io.iohk.atala.prism.protos.console_models.CredentialIssuanceContact
-import io.iohk.atala.prism.utils.FutureEither.FutureEitherOps
-import io.iohk.atala.prism.utils.syntax.InstantToTimestampOps
-import org.slf4j.{Logger, LoggerFactory}
-
-import scala.concurrent.{ExecutionContext, Future}
-
-class CredentialIssuanceGrpcService(
-    credentialIssuanceService: CredentialIssuanceService[IOWithTraceIdContext],
-    val authenticator: AuthenticatorF[ParticipantId, IOWithTraceIdContext]
-)(implicit
-    ec: ExecutionContext,
-    runtime: IORuntime
-) extends console_api.CredentialIssuanceServiceGrpc.CredentialIssuanceService
-    with ManagementConsoleErrorSupport
-    with AuthAndMiddlewareSupportF[ManagementConsoleError, ParticipantId] {
-
-  override protected val serviceName: String = "credential-issuance-service"
-  override val IOruntime: IORuntime = runtime
-
-  val logger: Logger = LoggerFactory.getLogger(this.getClass)
-
-  override def createCredentialIssuance(
-      request: CreateCredentialIssuanceRequest
-  ): Future[CreateCredentialIssuanceResponse] =
-    auth[CreateCredentialIssuance]("createCredentialIssuance", request) { (participantId, query, traceId) =>
-      credentialIssuanceService
-        .createCredentialIssuance(participantId, query)
-        .run(traceId)
-        .unsafeToFuture()
-        .toFutureEither
-        .map { credentialIssuanceId =>
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/grpc/GroupsGrpcService.scala

@@ -1,117 +1,0 @@
-package io.iohk.atala.prism.management.console.grpc
-
-import cats.effect.unsafe.IORuntime
-import cats.syntax.either._
-import cats.syntax.functor._
-import io.iohk.atala.prism.auth.{AuthAndMiddlewareSupportF, AuthenticatorF}
-import io.iohk.atala.prism.logging.TraceId.IOWithTraceIdContext
-import io.iohk.atala.prism.management.console.errors.{ManagementConsoleError, ManagementConsoleErrorSupport}
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.services.GroupsService
-import io.iohk.atala.prism.protos.{console_api, console_models}
-import io.iohk.atala.prism.utils.FutureEither.FutureEitherOps
-import io.iohk.atala.prism.utils.syntax.InstantToTimestampOps
-import org.slf4j.{Logger, LoggerFactory}
-
-import scala.concurrent.{ExecutionContext, Future}
-
-class GroupsGrpcService(
-    groupsService: GroupsService[IOWithTraceIdContext],
-    val authenticator: AuthenticatorF[ParticipantId, IOWithTraceIdContext]
-)(implicit ec: ExecutionContext, runtime: IORuntime)
-    extends console_api.GroupsServiceGrpc.GroupsService
-    with ManagementConsoleErrorSupport
-    with AuthAndMiddlewareSupportF[ManagementConsoleError, ParticipantId] {
-
-  override protected val serviceName: String = "groups-service"
-  override val IOruntime: IORuntime = runtime
-
-  val logger: Logger = LoggerFactory.getLogger(this.getClass)
-
-  override def createGroup(
-      request: console_api.CreateGroupRequest
-  ): Future[console_api.CreateGroupResponse] =
-    auth[CreateInstitutionGroup]("createGroup", request) { (institutionId, request, traceId) =>
-      groupsService
-        .createGroup(institutionId, request)
-        .run(traceId)
-        .unsafeToFuture()
-        .toFutureEither
-        .map { group =>
-          console_api
-            .CreateGroupResponse()
-            .withGroup(
-              console_models
-                .Group()
-                .withId(group.id.toString)
-                .withCreatedAt(group.createdAt.toProtoTimestamp)
-                .withName(group.name.value)
-                .withNumberOfContacts(request.contactIds.size)
-            )
-        }
-    }
-
-  override def getGroups(
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/integrations/CredentialsIntegrationService.scala

@@ -1,361 +1,0 @@
-package io.iohk.atala.prism.management.console.integrations
-
-import cats.data.NonEmptyList
-import cats.effect.{MonadCancelThrow, Resource}
-import cats.syntax.applicative._
-import cats.syntax.applicativeError._
-import cats.syntax.apply._
-import cats.syntax.comonad._
-import cats.syntax.flatMap._
-import cats.syntax.functor._
-import cats.syntax.traverse._
-import cats.{Comonad, Functor, Monad, MonadThrow}
-import derevo.derive
-import derevo.tagless.applyK
-import io.iohk.atala.prism.grpc.ProtoConverter
-import io.iohk.atala.prism.management.console.clients.ConnectorClient
-import io.iohk.atala.prism.management.console.errors
-import io.iohk.atala.prism.management.console.errors.{ManagementConsoleError, ManagementConsoleErrorSupport}
-import io.iohk.atala.prism.management.console.grpc._
-import io.iohk.atala.prism.management.console.integrations.CredentialsIntegrationService.{
-  GenericCredentialWithConnection,
-  GetGenericCredentialsResult
-}
-import io.iohk.atala.prism.management.console.models.GenericCredential.PaginatedQuery
-import io.iohk.atala.prism.management.console.models.PaginatedQueryConstraints.ResultOrdering
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.{ContactsRepository, CredentialsRepository}
-import io.iohk.atala.prism.models.{AtalaOperationId, ConnectionToken}
-import io.iohk.atala.prism.protos.connector_models.ContactConnection
-import io.iohk.atala.prism.protos.console_models.ContactConnectionStatus
-import io.iohk.atala.prism.protos.node_api.GetOperationInfoRequest
-import io.iohk.atala.prism.protos.{connector_models, node_api}
-import org.slf4j.{Logger, LoggerFactory}
-import tofu.Execute
-import tofu.higherKind.Mid
-import tofu.logging.{Logs, ServiceLogging}
-import tofu.syntax.logging._
-
-import scala.concurrent.Future
-
-@derive(applyK)
-trait CredentialsIntegrationService[F[_]] {
-  def revokePublishedCredential(
-      institutionId: ParticipantId,
-      request: RevokePublishedCredential
-  ): F[Either[ManagementConsoleError, AtalaOperationId]]
-
-  def createGenericCredential(
-      participantId: ParticipantId,
-      createGenericCredential: CreateGenericCredential
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/models/GetGroupsResult.scala

@@ -1,6 +1,0 @@
-package io.iohk.atala.prism.management.console.models
-
-case class GetGroupsResult(
-    groups: List[InstitutionGroup.WithContactCount],
-    totalNumberOfRecords: Int
-)

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/models/GetLedgerDataResult.scala

@@ -1,9 +1,0 @@
-package io.iohk.atala.prism.management.console.models
-
-import io.iohk.atala.prism.protos.node_models.LedgerData
-
-case class GetLedgerDataResult(
-    publicationData: Option[LedgerData],
-    revocationData: Option[LedgerData],
-    credentialRevocationData: Option[LedgerData]
-)

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/models/PaginatedQueryConstraints.scala

@@ -1,34 +1,0 @@
-package io.iohk.atala.prism.management.console.models
-
-case class PaginatedQueryConstraints[ScrollId, SortBy, FilterBy](
-    limit: Int = 10,
-    offset: Int = 0,
-    ordering: PaginatedQueryConstraints.ResultOrdering[SortBy],
-    scrollId: Option[ScrollId] = None,
-    filters: Option[FilterBy] = None
-)
-
-object PaginatedQueryConstraints {
-
-  /** Defines how to sort the result while retrieving data
-    *
-    * @param field
-    *   the possible field to sort the result by
-    * @param direction
-    *   whether the result should be sorted in ascending or descending order
-    * @tparam T
-    *   the type used to sort the result
-    */
-  case class ResultOrdering[T](
-      field: T,
-      direction: ResultOrdering.Direction = ResultOrdering.Direction.Ascending
-  )
-
-  object ResultOrdering {
-    sealed trait Direction extends Product with Serializable
-    object Direction {
-      final case object Ascending extends Direction
-      final case object Descending extends Direction
-    }
-  }
-}

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/models/PublishBatch.scala

@@ -1,7 +1,0 @@
-package io.iohk.atala.prism.management.console.models
-
-import io.iohk.atala.prism.protos.node_models.SignedAtalaOperation
-
-case class PublishBatch(
-    signedOperation: SignedAtalaOperation
-)

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/models/PublishCredential.scala

@@ -1,11 +1,0 @@
-package io.iohk.atala.prism.management.console.models
-
-import io.iohk.atala.prism.credentials.CredentialBatchId
-import io.iohk.atala.prism.crypto.MerkleInclusionProof
-
-case class PublishCredential(
-    consoleCredentialId: GenericCredential.Id,
-    credentialBatchId: CredentialBatchId,
-    encodedSignedCredential: String,
-    proofOfInclusion: MerkleInclusionProof
-)

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/models/RegisterDID.scala

@@ -1,5 +1,0 @@
-package io.iohk.atala.prism.management.console.models
-
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-
-case class RegisterDID(did: DID, name: String, logo: ParticipantLogo)

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/ContactsRepository.scala

@@ -1,311 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories
-
-import cats.{Comonad, Functor, Monad}
-import cats.data.OptionT
-import cats.data.EitherT
-import cats.effect._
-import cats.implicits._
-import derevo.tagless.applyK
-import derevo.derive
-import doobie.free._
-import doobie.implicits._
-import doobie.util.transactor.Transactor
-import io.iohk.atala.prism.management.console.errors.ManagementConsoleError
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.daos._
-import io.iohk.atala.prism.management.console.repositories.logs.ContactsRepositoryLogs
-import io.iohk.atala.prism.management.console.repositories.metrics.ContactsRepositoryMetrics
-import io.iohk.atala.prism.metrics.TimeMeasureMetric
-import io.iohk.atala.prism.models.ConnectionToken
-import io.iohk.atala.prism.utils.syntax.DBConnectionOps
-import tofu.higherKind.Mid
-import tofu.logging.{Logs, ServiceLogging}
-import tofu.syntax.monoid.TofuSemigroupOps
-
-import java.time.Instant
-import cats.effect.MonadCancelThrow
-
-@derive(applyK)
-trait ContactsRepository[F[_]] {
-
-  def create(
-      participantId: ParticipantId,
-      contactData: CreateContact,
-      maybeGroupName: Option[InstitutionGroup.Name],
-      createdAt: Instant = Instant.now(),
-      connectionToken: ConnectionToken
-  ): F[Contact]
-
-  def createBatch(
-      institutionId: ParticipantId,
-      request: CreateContact.Batch,
-      connectionTokens: List[ConnectionToken]
-  ): F[Either[ManagementConsoleError, Int]]
-
-  def updateContact(
-      institutionId: ParticipantId,
-      request: UpdateContact
-  ): F[Unit]
-
-  def find(
-      institutionId: ParticipantId,
-      contactId: Contact.Id
-  ): F[Option[Contact.WithDetails]]
-
-  def find(
-      institutionId: ParticipantId,
-      externalId: Contact.ExternalId
-  ): F[Option[Contact]]
-
-  def findByToken(
-      institutionId: ParticipantId,
-      connectionToken: ConnectionToken
-  ): F[Option[Contact]]
-
-  def findContacts(
-      institutionId: ParticipantId,
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/CredentialIssuancesRepository.scala

@@ -1,443 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories
-
-import cats.{Comonad, Functor, Monad}
-import cats.data.EitherT
-import cats.data.Validated.{Invalid, Valid}
-import cats.effect.Resource
-import cats.implicits._
-import derevo.tagless.applyK
-import derevo.derive
-import doobie.free.connection.ConnectionIO
-import doobie.implicits._
-import doobie.util.transactor.Transactor
-import io.circe.Json
-import io.iohk.atala.prism.management.console.errors._
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.daos.CredentialIssuancesDAO.CreateCredentialIssuanceContactGroup
-import io.iohk.atala.prism.management.console.repositories.daos._
-import io.iohk.atala.prism.utils.syntax.DBConnectionOps
-import io.scalaland.chimney.dsl._
-import io.iohk.atala.prism.metrics.TimeMeasureMetric
-import io.iohk.atala.prism.management.console.models.CredentialTypeWithRequiredFields
-import io.iohk.atala.prism.management.console.repositories.CredentialIssuancesRepository.{
-  CreateCredentialBulk,
-  CreateCredentialIssuance
-}
-import io.iohk.atala.prism.management.console.repositories.logs.CredentialIssuancesRepositoryLogs
-import io.iohk.atala.prism.management.console.repositories.metrics.CredentialIssuancesRepositoryMetrics
-import io.iohk.atala.prism.management.console.validations.CredentialDataValidator
-import tofu.higherKind.Mid
-import tofu.logging.{Logs, ServiceLogging}
-import tofu.syntax.monoid.TofuSemigroupOps
-import cats.effect.MonadCancelThrow
-
-@derive(applyK)
-trait CredentialIssuancesRepository[F[_]] {
-
-  def create(
-      participantId: ParticipantId,
-      createCredentialIssuance: CreateCredentialIssuance
-  ): F[Either[ManagementConsoleError, CredentialIssuance.Id]]
-
-  def createBulk(
-      participantId: ParticipantId,
-      credentialsType: CredentialTypeId,
-      issuanceName: String,
-      drafts: List[CreateCredentialBulk.Draft]
-  ): F[Either[ManagementConsoleError, CredentialIssuance.Id]]
-
-  def get(
-      credentialIssuanceId: CredentialIssuance.Id,
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/CredentialTypeCategoryRepository.scala

@@ -1,113 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories
-
-import cats.{Comonad, Functor, Monad}
-import cats.effect.Resource
-import cats.syntax.comonad._
-import cats.syntax.either._
-import derevo.tagless.applyK
-import cats.syntax.functor._
-import derevo.derive
-import doobie.implicits._
-import doobie.util.transactor.Transactor
-import io.iohk.atala.prism.management.console.errors._
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.daos.CredentialTypeCategoryDao
-import io.iohk.atala.prism.utils.syntax.DBConnectionOps
-import io.iohk.atala.prism.metrics.TimeMeasureMetric
-import io.iohk.atala.prism.management.console.repositories.logs.CredentialTypeCategoryRepositoryLogs
-import io.iohk.atala.prism.management.console.repositories.metrics.CredentialTypeCategoryRepositoryMetrics
-import tofu.higherKind.Mid
-import tofu.logging.{Logs, ServiceLogging}
-import tofu.syntax.monoid.TofuSemigroupOps
-import cats.effect.MonadCancelThrow
-
-@derive(applyK)
-trait CredentialTypeCategoryRepository[F[_]] {
-
-  def create(
-      participantId: ParticipantId,
-      createCredentialTypeCategory: CreateCredentialTypeCategory
-  ): F[Either[ManagementConsoleError, CredentialTypeCategory]]
-
-  def findByInstitution(institution: ParticipantId): F[Either[ManagementConsoleError, List[CredentialTypeCategory]]]
-
-  def archive(
-      credentialTypeId: CredentialTypeCategoryId
-  ): F[Either[ManagementConsoleError, CredentialTypeCategory]]
-
-  def unArchive(
-      credentialTypeId: CredentialTypeCategoryId
-  ): F[Either[ManagementConsoleError, CredentialTypeCategory]]
-
-}
-
-object CredentialTypeCategoryRepository {
-
-  def apply[F[_]: TimeMeasureMetric: MonadCancelThrow, R[_]: Functor](
-      transactor: Transactor[F],
-      logs: Logs[R, F]
-  ): R[CredentialTypeCategoryRepository[F]] =
-    for {
-      serviceLogs <- logs.service[CredentialTypeCategoryRepository[F]]
-    } yield {
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/CredentialsRepository.scala

@@ -1,330 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories
-
-import cats.data.Validated.{Invalid, Valid}
-import cats.data.{EitherT, NonEmptyList}
-import cats.effect.{MonadCancelThrow, Resource}
-import cats.syntax.comonad._
-import cats.syntax.functor._
-import cats.{Comonad, Functor, Monad}
-import derevo.derive
-import derevo.tagless.applyK
-import doobie.implicits._
-import doobie.util.transactor.Transactor
-import doobie.{ConnectionIO, FC}
-import io.iohk.atala.prism.credentials.CredentialBatchId
-import io.iohk.atala.prism.crypto.Sha256Digest
-import io.iohk.atala.prism.management.console.errors._
-import io.iohk.atala.prism.management.console.models.GenericCredential.FilterBy
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.daos.{ContactsDAO, CredentialTypeDao, CredentialsDAO}
-import io.iohk.atala.prism.management.console.repositories.logs.CredentialsRepositoryLogs
-import io.iohk.atala.prism.management.console.repositories.metrics.CredentialsRepositoryMetrics
-import io.iohk.atala.prism.management.console.validations.CredentialDataValidator
-import io.iohk.atala.prism.metrics.TimeMeasureMetric
-import io.iohk.atala.prism.models.AtalaOperationId
-import io.iohk.atala.prism.utils.syntax.DBConnectionOps
-import tofu.higherKind.Mid
-import tofu.logging.{Logs, ServiceLogging}
-import tofu.syntax.monoid.TofuSemigroupOps
-
-@derive(applyK)
-trait CredentialsRepository[F[_]] {
-
-  def create(
-      participantId: ParticipantId,
-      data: CreateGenericCredential
-  ): F[Either[ManagementConsoleError, GenericCredential]]
-
-  def getBy(credentialId: GenericCredential.Id): F[Option[GenericCredential]]
-
-  def getBy(
-      issuedBy: ParticipantId,
-      query: GenericCredential.PaginatedQuery,
-      onlyContacts: Option[NonEmptyList[Contact.Id]] = None
-  ): F[List[GenericCredential]]
-
-  def countBy(
-      issuedBy: ParticipantId,
-      maybeFilters: Option[FilterBy],
-      onlyContacts: Option[NonEmptyList[Contact.Id]] = None
-  ): F[Int]
-
-  def getBy(
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/InstitutionGroupsRepository.scala

@@ -1,267 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories
-
-import cats.{Comonad, Functor, Monad}
-import cats.data.EitherT
-import cats.effect.Resource
-import cats.syntax.apply._
-import cats.syntax.applicative._
-import cats.syntax.comonad._
-import cats.syntax.either._
-import cats.syntax.flatMap._
-import cats.syntax.functor._
-import derevo.tagless.applyK
-import derevo.derive
-import doobie.ConnectionIO
-import doobie.implicits._
-import doobie.util.transactor.Transactor
-import io.iohk.atala.prism.management.console.errors._
-import io.iohk.atala.prism.management.console.models.{Contact, GetGroupsResult, InstitutionGroup, ParticipantId}
-import io.iohk.atala.prism.management.console.repositories.daos.InstitutionGroupsDAO
-import io.iohk.atala.prism.management.console.repositories.logs.InstitutionGroupsRepositoryLogs
-import io.iohk.atala.prism.management.console.repositories.metrics.InstitutionGroupsRepositoryMetrics
-import io.iohk.atala.prism.utils.syntax.DBConnectionOps
-import io.iohk.atala.prism.metrics.TimeMeasureMetric
-import tofu.higherKind.Mid
-import tofu.logging.{Logs, ServiceLogging}
-import tofu.syntax.monoid.TofuSemigroupOps
-import cats.effect.MonadCancelThrow
-
-@derive(applyK)
-trait InstitutionGroupsRepository[F[_]] {
-  def create(
-      institutionId: ParticipantId,
-      name: InstitutionGroup.Name,
-      contactIds: Set[Contact.Id]
-  ): F[Either[ManagementConsoleError, InstitutionGroup]]
-
-  def getBy(
-      institutionId: ParticipantId,
-      query: InstitutionGroup.PaginatedQuery
-  ): F[GetGroupsResult]
-
-  def listContacts(
-      institutionId: ParticipantId,
-      groupName: InstitutionGroup.Name
-  ): F[List[Contact]]
-
-  def updateGroup(
-      institutionId: ParticipantId,
-      groupId: InstitutionGroup.Id,
-      contactIdsToAdd: Set[Contact.Id],
-      contactIdsToRemove: Set[Contact.Id],
-      newNameMaybe: Option[InstitutionGroup.Name]
-  ): F[Either[ManagementConsoleError, Unit]]
-
-  def copyGroup(
-      institutionId: ParticipantId,
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/ParticipantsRepository.scala

@@ -1,183 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories
-
-import cats.{Comonad, Functor, Monad}
-import cats.effect.Resource
-import cats.syntax.applicative._
-import cats.syntax.applicativeError._
-import cats.syntax.comonad._
-import cats.syntax.either._
-import cats.syntax.functor._
-import com.typesafe.config.ConfigFactory
-import derevo.tagless.applyK
-import derevo.derive
-import doobie.implicits._
-import doobie.util.transactor.Transactor
-import io.iohk.atala.prism.errors.LoggingContext
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.management.console.config.DefaultCredentialTypeConfig
-import io.iohk.atala.prism.management.console.errors._
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.ParticipantsRepository.{
-  CreateParticipantRequest,
-  UpdateParticipantProfileRequest
-}
-import io.iohk.atala.prism.management.console.repositories.daos.{CredentialTypeDao, ParticipantsDAO}
-import io.iohk.atala.prism.management.console.repositories.logs.ParticipantsRepositoryLogs
-import io.iohk.atala.prism.management.console.repositories.metrics.ParticipantsRepositoryMetrics
-import io.iohk.atala.prism.metrics.TimeMeasureMetric
-import io.iohk.atala.prism.utils.syntax.DBConnectionOps
-import org.postgresql.util.PSQLException
-import org.slf4j.{Logger, LoggerFactory}
-import tofu.higherKind.Mid
-import tofu.logging.{Logs, ServiceLogging}
-import tofu.syntax.monoid.TofuSemigroupOps
-import cats.effect.MonadCancelThrow
-
-@derive(applyK)
-trait ParticipantsRepository[F[_]] {
-
-  def create(
-      request: CreateParticipantRequest
-  ): F[Either[ManagementConsoleError, Unit]]
-
-  def findBy(
-      id: ParticipantId
-  ): F[Either[ManagementConsoleError, ParticipantInfo]]
-
-  def findBy(did: DID): F[Either[ManagementConsoleError, ParticipantInfo]]
-
-  def update(request: UpdateParticipantProfileRequest): F[Unit]
-
-}
-
-object ParticipantsRepository {
-
-  final case class CreateParticipantRequest(
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/daos/ContactsDAO.scala

@@ -1,180 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories.daos
-
-import cats.data.NonEmptyList
-import cats.implicits._
-import doobie._
-import doobie.free.connection
-import doobie.implicits._
-import doobie.implicits.legacy.instant._
-import doobie.util.fragments._
-import io.circe.Json
-import io.iohk.atala.prism.management.console.models.{Contact, CreateContact, ParticipantId, UpdateContact}
-import io.iohk.atala.prism.management.console.repositories.daos.queries.FindContactsQueryBuilder
-import io.iohk.atala.prism.models.ConnectionToken
-
-import java.time.Instant
-
-object ContactsDAO {
-
-  def createContact(
-      participantId: ParticipantId,
-      data: CreateContact,
-      createdAt: Instant,
-      connectionToken: ConnectionToken
-  ): ConnectionIO[Contact] = {
-    val contactId = Contact.Id.random()
-    sql"""
-         |INSERT INTO contacts
-         |  (contact_id, connection_token, contact_data, created_at, created_by, external_id, name)
-         |VALUES
-         |  ($contactId, $connectionToken, ${data.data}, $createdAt, $participantId, ${data.externalId}, ${data.name})
-         |RETURNING contact_id, connection_token, external_id, contact_data, created_at, name
-         |""".stripMargin.query[Contact].unique
-  }
-
-  def createContacts(
-      institutionId: ParticipantId,
-      contacts: List[CreateContact.NoOwner],
-      createdAt: Instant,
-      connectionTokens: List[ConnectionToken]
-  ): ConnectionIO[List[Contact.Id]] = {
-    type CreateContactItem = (
-        Contact.Id,
-        ConnectionToken,
-        Json,
-        Instant,
-        ParticipantId,
-        Contact.ExternalId,
-        String
-    )
-    val contactIds = List.tabulate(contacts.size)(_ => Contact.Id.random())
-    val data = contacts
-      .zip(contactIds)
-      .zip(connectionTokens)
-      .map { case ((item, id), connectionToken) =>
-        (
-          id,
-          connectionToken,
-          item.data,
-          createdAt,
-          institutionId,
-          item.externalId,
-          item.name
-        )
-      }
-
-    val statement =
-      """
-                    |INSERT INTO contacts (contact_id, connection_token, contact_data, created_at, created_by, external_id, name)
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/daos/InstitutionGroupsDAO.scala

@@ -1,223 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories.daos
-
-import cats.data.NonEmptyList
-import cats.implicits.catsStdInstancesForList
-import cats.syntax.functor._
-import doobie.Fragments.{in, whereAnd}
-import doobie._
-import doobie.free.connection
-import doobie.free.connection.{ConnectionIO, unit}
-import doobie.implicits._
-import doobie.implicits.legacy.instant._
-import io.iohk.atala.prism.management.console.models.{Contact, InstitutionGroup, ParticipantId}
-import io.iohk.atala.prism.management.console.repositories.daos.queries.FindGroupsQueryBuilder
-
-import java.time.Instant
-
-object InstitutionGroupsDAO {
-
-  def create(
-      institutionId: ParticipantId,
-      name: InstitutionGroup.Name
-  ): ConnectionIO[InstitutionGroup] = {
-    val groupId = InstitutionGroup.Id.random()
-    val now = Instant.now()
-    sql"""
-         |INSERT INTO institution_groups (group_id, institution_id, name, created_at)
-         |VALUES ($groupId, $institutionId, $name, $now)
-       """.stripMargin.update.run
-      .as(InstitutionGroup(groupId, name, institutionId, now))
-  }
-
-  def update(
-      groupId: InstitutionGroup.Id,
-      newName: InstitutionGroup.Name
-  ): ConnectionIO[Boolean] = {
-    sql"""
-         |UPDATE institution_groups
-         |SET name = $newName
-         |WHERE group_id = $groupId
-       """.stripMargin.update.run.map(_ == 1)
-  }
-
-  def getBy(
-      institutionId: ParticipantId
-  ): ConnectionIO[List[InstitutionGroup.WithContactCount]] = {
-    sql"""
-         |SELECT group_id, name, institution_id, created_at, (
-         |  SELECT COUNT(*)
-         |  FROM contacts_per_group
-         |  WHERE group_id = g.group_id
-         |) AS number_of_contacts
-         |FROM institution_groups g
-         |WHERE institution_id = $institutionId
-         |ORDER BY name
-       """.stripMargin.query[InstitutionGroup.WithContactCount].to[List]
-  }
-
-  def getBy(
-      institutionId: ParticipantId,
-      contactId: Contact.Id
-  ): ConnectionIO[List[InstitutionGroup.WithContactCount]] = {
-    sql"""
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/daos/queries/FindGroupsQueryBuilder.scala

@@ -1,94 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories.daos
-package queries
-
-import io.iohk.atala.prism.management.console.models.{InstitutionGroup, ParticipantId}
-import doobie._
-import doobie.implicits._
-import doobie.implicits.legacy.localdate._
-import doobie.util.fragments._
-
-object FindGroupsQueryBuilder {
-
-  def build(
-      institutionId: ParticipantId,
-      query: InstitutionGroup.PaginatedQuery
-  ): Fragment = {
-
-    val orderBy = orderByFr(query.ordering, "inst_gr.group_id") {
-      case InstitutionGroup.SortBy.Name => "inst_gr.name"
-      case InstitutionGroup.SortBy.CreatedAt => "inst_gr.created_at"
-      case InstitutionGroup.SortBy.NumberOfContacts => "number_of_contacts"
-    }
-
-    selectFr ++
-      fromFr ++
-      joinContactsPerGroupFr(query) ++
-      whereFr(institutionId, query) ++
-      orderBy ++
-      limitFr(query.limit) ++
-      offsetFr(query.offset)
-  }
-
-  def buildTotalNumberOfRecordsQuery(
-      institutionId: ParticipantId,
-      query: InstitutionGroup.PaginatedQuery
-  ): Fragment = {
-    selectCountFr ++
-      fromFr ++
-      joinContactsPerGroupFr(query) ++
-      whereFr(institutionId, query)
-  }
-
-  private def whereFr(
-      institutionId: ParticipantId,
-      query: InstitutionGroup.PaginatedQuery
-  ): Fragment = {
-    val whereInstitution = fr"""inst_gr.institution_id = $institutionId"""
-
-    val whereName = query.filters.flatMap(_.name).map { name =>
-      val regexName = s"%${name.value}%"
-      fr"inst_gr.name ILIKE $regexName"
-    }
-
-    val whereCreatedBefore =
-      query.filters.flatMap(_.createdBefore).map { createdBefore =>
-        fr"inst_gr.created_at::DATE <= $createdBefore"
-      }
-
-    val whereCreatedAfter =
-      query.filters.flatMap(_.createdAfter).map { createdAfter =>
-        fr"inst_gr.created_at::DATE >= $createdAfter"
-      }
-
-    val whereContactId = query.filters.flatMap(_.contactId).map { contactId =>
-      fr"cg.contact_id = $contactId"
-    }
-
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/logs/ContactsRepositoryLogs.scala

@@ -1,147 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories.logs
-
-import cats.syntax.apply._
-import cats.syntax.applicativeError._
-import cats.syntax.flatMap._
-import io.iohk.atala.prism.management.console.errors.ManagementConsoleError
-import io.iohk.atala.prism.management.console.models.Contact.PaginatedQuery
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.ContactsRepository
-import io.iohk.atala.prism.models.ConnectionToken
-import tofu.higherKind.Mid
-import tofu.logging.ServiceLogging
-import tofu.syntax.logging._
-
-import java.time.Instant
-import cats.effect.MonadCancelThrow
-
-private[repositories] final class ContactsRepositoryLogs[F[_]: MonadCancelThrow](implicit
-    l: ServiceLogging[F, ContactsRepository[F]]
-) extends ContactsRepository[Mid[F, *]] {
-
-  override def create(
-      participantId: ParticipantId,
-      contactData: CreateContact,
-      maybeGroupName: Option[InstitutionGroup.Name],
-      createdAt: Instant,
-      connectionToken: ConnectionToken
-  ): Mid[F, Contact] =
-    in =>
-      info"creating contact $participantId ${contactData.externalId}" *> in
-        .flatTap(c => info"creating contact - successfully done ${c.contactId}")
-        .onError(errorCause"encountered an error while creating contact" (_))
-
-  override def createBatch(
-      institutionId: ParticipantId,
-      request: CreateContact.Batch,
-      connectionTokens: List[ConnectionToken]
-  ): Mid[F, Either[ManagementConsoleError, Int]] =
-    in =>
-      info"creating a batch of contacts $institutionId" *> in
-        .flatTap { r =>
-          r.fold(
-            er => error"an error encountered while creating a batch of contacts $er $institutionId",
-            size =>
-              info"creating a batch of contacts - successfully done added contacts batch size = $size $institutionId"
-          )
-        }
-        .onError(errorCause"encountered an error while creating batch" (_))
-
-  override def updateContact(
-      institutionId: ParticipantId,
-      request: UpdateContact
-  ): Mid[F, Unit] =
-    in =>
-      info"updating contact $institutionId ${request.id}" *> in
-        .flatTap(_ => info"updating contact - successfully done")
-        .onError(errorCause"encountered an error while updating contact" (_))
-
-  override def find(
-      institutionId: ParticipantId,
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/logs/ParticipantsRepositoryLogs.scala

@@ -1,71 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories.logs
-
-import cats.syntax.apply._
-import cats.syntax.applicativeError._
-import cats.syntax.flatMap._
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.management.console.errors
-import io.iohk.atala.prism.management.console.models.{ParticipantId, ParticipantInfo}
-import io.iohk.atala.prism.management.console.repositories.ParticipantsRepository
-import tofu.higherKind.Mid
-import tofu.logging.ServiceLogging
-import tofu.syntax.logging._
-import cats.effect.MonadCancelThrow
-
-private[repositories] final class ParticipantsRepositoryLogs[F[
-    _
-]: MonadCancelThrow: ServiceLogging[*[
-  _
-], ParticipantsRepository[F]]]
-    extends ParticipantsRepository[Mid[F, *]] {
-  override def create(
-      request: ParticipantsRepository.CreateParticipantRequest
-  ): Mid[F, Either[errors.ManagementConsoleError, Unit]] =
-    in =>
-      info"creating participant ${request.id}" *> in
-        .flatTap(
-          _.fold(
-            e => error"encountered an error while creating participant $e",
-            r => info"creating participant - successfully done $r"
-          )
-        )
-        .onError(
-          errorCause"encountered an error while creating participant" (_)
-        )
-
-  override def findBy(
-      id: ParticipantId
-  ): Mid[F, Either[errors.ManagementConsoleError, ParticipantInfo]] =
-    in =>
-      info"finding participant $id" *> in
-        .flatTap(
-          _.fold(
-            e => error"encountered an error while finding participant $e",
-            r => info"finding participant - successfully done ${r.id}"
-          )
-        )
-        .onError(errorCause"encountered an error while finding participant" (_))
-
-  override def findBy(
-      did: DID
-  ): Mid[F, Either[errors.ManagementConsoleError, ParticipantInfo]] =
-    in =>
-      info"finding participant ${Option(did.asCanonical().getSuffix)}" *> in
-        .flatTap(
-          _.fold(
-            e => error"encountered an error while finding participant $e",
-            r => info"finding participant - successfully done ${r.id}"
-          )
-        )
-        .onError(errorCause"encountered an error while finding participant" (_))
-
-  override def update(
-      request: ParticipantsRepository.UpdateParticipantProfileRequest
-  ): Mid[F, Unit] =
-    in =>
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/logs/ReceivedCredentialsRepositoryLogs.scala

@@ -1,60 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories.logs
-
-import cats.syntax.apply._
-import cats.syntax.applicativeError._
-import cats.syntax.flatMap._
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.ReceivedCredentialsRepository
-import io.iohk.atala.prism.management.console.repositories.daos.ReceivedCredentialsDAO.ReceivedSignedCredentialData
-import tofu.higherKind.Mid
-import tofu.logging.ServiceLogging
-import tofu.syntax.logging._
-import cats.effect.MonadCancelThrow
-
-private[repositories] final class ReceivedCredentialsRepositoryLogs[F[
-    _
-]: ServiceLogging[
-  *[_],
-  ReceivedCredentialsRepository[F]
-]: MonadCancelThrow]
-    extends ReceivedCredentialsRepository[Mid[F, *]] {
-
-  override def getCredentialsFor(
-      verifierId: ParticipantId,
-      contactId: Option[Contact.Id]
-  ): Mid[F, List[ReceivedSignedCredential]] =
-    in =>
-      info"getting credentials for $verifierId $contactId" *> in
-        .flatTap(list => info"getting credentials for - got ${list.size} entities")
-        .onError(
-          errorCause"encountered an error while getting credentials for" (_)
-        )
-
-  override def createReceivedCredential(
-      data: ReceivedSignedCredentialData
-  ): Mid[F, Unit] =
-    in =>
-      info"creating received credential ${data.contactId} ${data.credentialExternalId}" *> in
-        .flatTap(_ => info"creating received credential - successfully done")
-        .onError(
-          errorCause"encountered an error while creating received credential" (
-            _
-          )
-        )
-
-  override def getLatestCredentialExternalId(
-      verifierId: ParticipantId
-  ): Mid[F, Option[CredentialExternalId]] =
-    in =>
-      info"getting credential external id $verifierId" *> in
-        .flatTap(
-          _.fold(info"getting credential external id - got nothing")(externalId =>
-            info"getting credential external id - $externalId"
-          )
-        )
-        .onError(
-          errorCause"encountered an error while getting credential external id" (
-            _
-          )
-        )
-}

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/logs/RequestNoncesRepositoryLogs.scala

@@ -1,29 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories.logs
-
-import cats.syntax.apply._
-import cats.syntax.applicativeError._
-import cats.syntax.flatMap._
-import io.iohk.atala.prism.auth.model.RequestNonce
-import io.iohk.atala.prism.management.console.models.ParticipantId
-import io.iohk.atala.prism.management.console.repositories.RequestNoncesRepository
-import tofu.higherKind.Mid
-import tofu.logging.ServiceLogging
-import tofu.syntax.logging._
-import cats.effect.MonadCancelThrow
-
-private[repositories] final class RequestNoncesRepositoryLogs[F[
-    _
-]: ServiceLogging[
-  *[_],
-  RequestNoncesRepository[F]
-]: MonadCancelThrow]
-    extends RequestNoncesRepository[Mid[F, *]] {
-  override def burn(
-      participantId: ParticipantId,
-      requestNonce: RequestNonce
-  ): Mid[F, Unit] =
-    in =>
-      info"burning $participantId" *> in
-        .flatTap(_ => info"burning - successfully done")
-        .onError(errorCause"encountered an error while burning" (_))
-}

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/metrics/CredentialTypeCategoryRepositoryMetrics.scala

@@ -1,45 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories.metrics
-
-import cats.effect.MonadCancelThrow
-import io.iohk.atala.prism.management.console.errors.ManagementConsoleError
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.CredentialTypeCategoryRepository
-import io.iohk.atala.prism.metrics.TimeMeasureUtil.MeasureOps
-import io.iohk.atala.prism.metrics.{TimeMeasureMetric, TimeMeasureUtil}
-import tofu.higherKind.Mid
-
-final class CredentialTypeCategoryRepositoryMetrics[F[
-    _
-]: TimeMeasureMetric: MonadCancelThrow]
-    extends CredentialTypeCategoryRepository[Mid[F, *]] {
-  private val repoName = "CredentialTypeCategoryRepository"
-  private lazy val createTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "create")
-  private lazy val archiveTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "archive")
-  private lazy val unArchiveTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "unArchive")
-  private lazy val findByInstitutionTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "findByInstitution")
-
-  override def create(
-      participantId: ParticipantId,
-      createCredentialTypeCategory: CreateCredentialTypeCategory
-  ): Mid[F, Either[ManagementConsoleError, CredentialTypeCategory]] =
-    _.measureOperationTime(createTimer)
-
-  override def archive(
-      credentialTypeId: CredentialTypeCategoryId
-  ): Mid[F, Either[ManagementConsoleError, CredentialTypeCategory]] =
-    _.measureOperationTime(archiveTimer)
-
-  override def unArchive(
-      credentialTypeId: CredentialTypeCategoryId
-  ): Mid[F, Either[ManagementConsoleError, CredentialTypeCategory]] = _.measureOperationTime(unArchiveTimer)
-
-  override def findByInstitution(
-      institution: ParticipantId
-  ): Mid[F, Either[ManagementConsoleError, List[CredentialTypeCategory]]] =
-    _.measureOperationTime(findByInstitutionTimer)
-
-}

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/repositories/metrics/CredentialsRepositoryMetrics.scala

@@ -1,122 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories.metrics
-
-import cats.data.NonEmptyList
-import cats.effect.MonadCancelThrow
-import io.iohk.atala.prism.credentials.CredentialBatchId
-import io.iohk.atala.prism.crypto.Sha256Digest
-import io.iohk.atala.prism.management.console.errors.ManagementConsoleError
-import io.iohk.atala.prism.management.console.models.GenericCredential.PaginatedQuery
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.CredentialsRepository
-import io.iohk.atala.prism.metrics.TimeMeasureUtil.MeasureOps
-import io.iohk.atala.prism.metrics.{TimeMeasureMetric, TimeMeasureUtil}
-import io.iohk.atala.prism.models.AtalaOperationId
-import tofu.higherKind.Mid
-
-final class CredentialsRepositoryMetrics[F[_]: TimeMeasureMetric: MonadCancelThrow]
-    extends CredentialsRepository[Mid[F, *]] {
-
-  private val repoName = "CredentialsRepository"
-  private lazy val createTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "create")
-  private lazy val getByCredentialIdTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "getByCredentialId")
-  private lazy val getByQueryTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "getByQuery")
-  private lazy val countByQueryTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "countByQuery")
-  private lazy val getByMaybeLastSeenCredentialTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "getByMaybeLastSeenCredential")
-  private lazy val getByContactIdTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "getByContactId")
-  private lazy val storePublicationDataTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "storePublicationData")
-  private lazy val markAsSharedTimer =
-    TimeMeasureUtil.createDBQueryTimer(repoName, "markAsShared")
-  private lazy val verifyPublishedCredentialsExistTimer =
-    TimeMeasureUtil.createDBQueryTimer(
-      repoName,
-      "verifyPublishedCredentialsExist"
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/services/ConsoleServiceImpl.scala

@@ -1,161 +1,0 @@
-package io.iohk.atala.prism.management.console.services
-
-import cats.{Comonad, Functor, Monad}
-import cats.effect.Resource
-import cats.syntax.apply._
-import cats.syntax.applicativeError._
-import cats.syntax.comonad._
-import cats.syntax.flatMap._
-import cats.syntax.functor._
-import derevo.derive
-import derevo.tagless.applyK
-import io.iohk.atala.prism.management.console.errors.ManagementConsoleError
-import io.iohk.atala.prism.management.console.integrations.ParticipantsIntegrationService
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.StatisticsRepository
-import tofu.higherKind.Mid
-import tofu.logging.{Logs, ServiceLogging}
-import tofu.syntax.logging._
-import cats.MonadThrow
-
-@derive(applyK)
-trait ConsoleService[F[_]] {
-  def getStatistics(
-      participantId: ParticipantId,
-      getStatistics: GetStatistics
-  ): F[Statistics]
-
-  def registerDID(
-      registerDID: RegisterDID
-  ): F[Either[ManagementConsoleError, Unit]]
-
-  def getCurrentUser(
-      participantId: ParticipantId
-  ): F[Either[ManagementConsoleError, ParticipantInfo]]
-
-  def updateParticipantProfile(
-      participantId: ParticipantId,
-      participantProfile: UpdateParticipantProfile
-  ): F[Unit]
-}
-
-object ConsoleService {
-  def apply[F[_]: MonadThrow, R[_]: Functor](
-      participantsIntegrationService: ParticipantsIntegrationService[F],
-      statisticsRepository: StatisticsRepository[F],
-      logs: Logs[R, F]
-  ): R[ConsoleService[F]] =
-    for {
-      serviceLogs <- logs.service[ConsoleService[F]]
-    } yield {
-      implicit val implicitLogs: ServiceLogging[F, ConsoleService[F]] =
-        serviceLogs
-      val logs: ConsoleService[Mid[F, *]] = new ConsoleServiceLogs[F]
-      val mid = logs
-      mid attach new ConsoleServiceImpl[F](
-        participantsIntegrationService,
-        statisticsRepository
-      )
-    }
-
-  def unsafe[F[_]: MonadThrow, R[_]: Comonad](
-      participantsIntegrationService: ParticipantsIntegrationService[F],
[…]

### 2023-07-25 prism-backend/management-console/src/main/scala/io/iohk/atala/prism/management/console/services/GroupsService.scala

@@ -1,207 +1,0 @@
-package io.iohk.atala.prism.management.console.services
-
-import cats.{Comonad, Functor, Monad}
-import cats.effect.Resource
-import cats.syntax.apply._
-import cats.syntax.applicativeError._
-import cats.syntax.comonad._
-import cats.syntax.flatMap._
-import cats.syntax.functor._
-import derevo.derive
-import derevo.tagless.applyK
-import io.iohk.atala.prism.management.console.errors.ManagementConsoleError
-import io.iohk.atala.prism.management.console.models.InstitutionGroup.PaginatedQuery
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.InstitutionGroupsRepository
-import io.iohk.atala.prism.metrics.TimeMeasureMetric
-import tofu.higherKind.Mid
-import tofu.logging.{Logs, ServiceLogging}
-import tofu.syntax.logging._
-import cats.MonadThrow
-import cats.effect.MonadCancelThrow
-
-@derive(applyK)
-trait GroupsService[F[_]] {
-  def createGroup(
-      institutionId: ParticipantId,
-      createInstitutionGroup: CreateInstitutionGroup
-  ): F[Either[ManagementConsoleError, InstitutionGroup]]
-
-  def getGroups(
-      institutionId: ParticipantId,
-      query: InstitutionGroup.PaginatedQuery
-  ): F[GetGroupsResult]
-
-  def updateGroup(
-      institutionId: ParticipantId,
-      updateInstitutionGroup: UpdateInstitutionGroup
-  ): F[Either[ManagementConsoleError, Unit]]
-
-  def copyGroup(
-      institutionId: ParticipantId,
-      copyInstitutionGroup: CopyInstitutionGroup
-  ): F[Either[ManagementConsoleError, InstitutionGroup]]
-
-  def deleteGroup(
-      institutionId: ParticipantId,
-      deleteInstitutionGroup: DeleteInstitutionGroup
-  ): F[Either[ManagementConsoleError, Unit]]
-
-}
-
-object GroupsService {
-  def apply[F[_]: TimeMeasureMetric: MonadThrow, R[_]: Functor](
-      institutionGroupsRepository: InstitutionGroupsRepository[F],
-      logs: Logs[R, F]
-  ): R[GroupsService[F]] =
-    for {
-      serviceLogs <- logs.service[GroupsService[F]]
-    } yield {
[…]

### 2023-07-25 prism-backend/management-console/src/test/scala/io/iohk/atala/prism/management/console/config/DefaultCredentialTypeConfigSpec.scala

@@ -1,52 +1,0 @@
-package io.iohk.atala.prism.management.console.config
-
-import com.typesafe.config.ConfigFactory
-import io.iohk.atala.prism.credentials.utils.Mustache
-import org.scalatest.matchers.must.Matchers
-import org.scalatest.wordspec.AnyWordSpec
-import io.iohk.atala.prism.interop.KotlinFunctionConverters._
-
-import scala.util.Try
-
-// Check correctness of each credential type defined in DefaultCredentialTypes/default-credential-types.conf
-// sbt "project management-console" "testOnly *DefaultCredentialTypeConfigSpec"
-class DefaultCredentialTypeConfigSpec extends AnyWordSpec with Matchers {
-
-  "defaultCredentialTypes" should {
-    "be valid mustache templates" in {
-      DefaultCredentialTypeConfig(ConfigFactory.load()).defaultCredentialTypes
-        .foreach { defaultCredentialType =>
-          val res: Either[Throwable, String] = Try(
-            Mustache.INSTANCE.render(
-              defaultCredentialType.template,
-              (
-                  (name: String) =>
-                    defaultCredentialType.fields
-                      .find(_.name == name)
-                      .map(_.name)
-                      .orNull
-              ).asKotlin,
-              true
-            )
-          ).toEither
-          res mustBe a[Right[_, _]]
-        }
-    }
-
-    "have unique names within institution" in {
-      val names = DefaultCredentialTypeConfig(
-        ConfigFactory.load()
-      ).defaultCredentialTypes.map(_.name)
-      names.size mustBe names.distinct.size
-    }
-
-    "all have fields with unique name within user defined credential type" in {
-      DefaultCredentialTypeConfig(ConfigFactory.load()).defaultCredentialTypes
-        .foreach { defaultCredentialType =>
-          val fieldNames = defaultCredentialType.fields.map(_.name)
-          fieldNames.size mustBe fieldNames.distinct.size
-        }
-    }
-  }
-
-}

### 2023-07-25 prism-backend/management-console/src/test/scala/io/iohk/atala/prism/management/console/migrations/V18MigrationSpec.scala

@@ -1,60 +1,0 @@
-package io.iohk.atala.prism.management.console.migrations
-
-import doobie.implicits._
-import doobie.implicits.legacy.instant._
-import io.iohk.atala.prism.daos.BaseDAO
-import io.iohk.atala.prism.repositories.PostgresMigrationSpec
-import io.iohk.atala.prism.repositories.ops.SqlTestOps.Implicits
-import org.postgresql.util.PSQLException
-
-import java.time.Instant
-import java.util.UUID
-
-class V18MigrationSpec extends PostgresMigrationSpec("V18") with BaseDAO {
-  val credentialTypeCategoryId = UUID.randomUUID()
-  val issuerId = UUID.randomUUID()
-  val credentialTypeId = UUID.randomUUID()
-
-  def prepare(): Unit = {
-    createParticipant()
-    createCredentialTypeCategory()
-  }
-
-  def createCredentialTypeCategory(): Unit = {
-    sql"""INSERT INTO credential_type_categories (credential_type_category_id, name, state)
-         |VALUES ($credentialTypeCategoryId, 'Some credential type category', 'DRAFT')""".stripMargin
-      .runUpdate()
-  }
-  def createParticipant(): Unit = {
-    sql"""INSERT INTO participants (participant_id, name, did, created_at)
-         |VALUES ($issuerId, 'The Issuer', 'did:prism:theissuer', ${Instant.now})""".stripMargin
-      .runUpdate()
-  }
-
-  def createCredentialType(): Unit = {
-    sql"""INSERT INTO credential_types (credential_type_id, name, institution_id, state, template, created_at, credential_type_category_id)
-         |VALUES ($credentialTypeId, 'The Credential Type', $issuerId, 'DRAFT', 'a template', ${Instant.now}, $credentialTypeCategoryId)""".stripMargin
-      .runUpdate()
-  }
-  def getCategoryIdOfCredentialType(): UUID = {
-    sql"SELECT credential_type_category_id FROM credential_types WHERE credential_type_id = $credentialTypeId"
-      .runUnique[UUID]()
-  }
-
-  test(
-    beforeApply = {
-      prepare()
-      val thrown = intercept[PSQLException] {
-        createCredentialType()
-      }
-      thrown.getMessage.contains(
-        "column \"credential_type_category_id\" of relation \"credential_types\" does not exist"
-      ) mustBe true
-    },
-    afterApplied = {
-      createCredentialType()
[…]

### 2023-07-25 prism-backend/management-console/src/test/scala/io/iohk/atala/prism/management/console/migrations/V19MigrationSpec.scala

@@ -1,37 +1,0 @@
-package io.iohk.atala.prism.management.console.migrations
-
-import doobie.implicits._
-import io.iohk.atala.prism.daos.BaseDAO
-import io.iohk.atala.prism.repositories.PostgresMigrationSpec
-import io.iohk.atala.prism.repositories.ops.SqlTestOps.Implicits
-
-import java.util.UUID
-
-class V19MigrationSpec extends PostgresMigrationSpec("V19") with BaseDAO {
-  val credentialTypeCategoryId = UUID.randomUUID()
-
-  def prepare(): Unit = {
-    createCredentialTypeCategory()
-  }
-
-  def createCredentialTypeCategory(): Unit = {
-    sql"""INSERT INTO credential_type_categories (credential_type_category_id, name, state)
-         |VALUES ($credentialTypeCategoryId, 'Some credential type category', 'DRAFT')""".stripMargin
-      .runUpdate()
-  }
-
-  def getInstitutionIdOfCredentialTypeCategory(): Option[UUID] = {
-    sql"SELECT institution_id FROM credential_type_categories WHERE credential_type_category_id = $credentialTypeCategoryId"
-      .runUnique[Option[UUID]]()
-  }
-
-  test(
-    beforeApply = {
-      prepare()
-    },
-    afterApplied = {
-      getInstitutionIdOfCredentialTypeCategory() mustBe None
-    }
-  )
-
-}

### 2023-07-25 prism-backend/management-console/src/test/scala/io/iohk/atala/prism/management/console/repositories/ContactsRepositorySpec.scala

@@ -1,1409 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories
-
-import cats.effect.IO
-import cats.effect.unsafe.implicits.global
-import io.circe.Json
-import io.iohk.atala.prism.AtalaWithPostgresSpec
-import io.iohk.atala.prism.management.console.DataPreparation
-import io.iohk.atala.prism.management.console.DataPreparation._
-import io.iohk.atala.prism.management.console.errors.{ContactHasExistingCredentials, ContactsInstitutionsDoNotMatch}
-import io.iohk.atala.prism.management.console.models._
-import io.iohk.atala.prism.management.console.repositories.daos.InstitutionGroupsDAO
-import io.iohk.atala.prism.models.ConnectionToken
-import io.iohk.atala.prism.utils.IOUtils._
-import org.scalatest.OptionValues._
-import tofu.logging.Logs
-
-import java.time.{Instant, LocalDate, Period}
-import java.util.UUID
-import scala.util.Try
-
-// sbt "project management-console" "testOnly *ContactsRepositorySpec"
-class ContactsRepositorySpec extends AtalaWithPostgresSpec {
-  import PaginatedQueryConstraints._
-
-  val logs: Logs[IO, IO] = Logs.sync[IO, IO]
-  private val repository = ContactsRepository.unsafe(database, logs)
-  val credentialsRepository = CredentialsRepository.unsafe(database, logs)
-
-  "create" should {
-    "create a new contact and assign it to an specified group" in {
-      val institutionId = createParticipant("Institution-1")
-      val group =
-        createInstitutionGroup(institutionId, InstitutionGroup.Name("Grp 1"))
-      val externalId = Contact.ExternalId.random()
-      val json = Json.obj(
-        "universityId" -> Json.fromString("uid"),
-        "email" -> Json.fromString("d.here@iohk.io"),
-        "admissionDate" -> Json.fromString(LocalDate.now().toString)
-      )
-      val request = CreateContact(
-        externalId,
-        json,
-        "Dusty Here",
-        grpcAuthenticationHeaderDIDBased
-      )
-
-      val result = repository
-        .create(
-          institutionId,
-          request,
-          Some(group.name),
-          connectionToken = ConnectionToken("connectionToken")
-        )
-        .unsafeRunSync()
-      val contact = result
-      contact.data must be(json)
-      contact.externalId must be(externalId)
-
-      // we check that the contact was added to the intended group
-      val contactsInGroupList = repository
[…]

### 2023-07-25 prism-backend/management-console/src/test/scala/io/iohk/atala/prism/management/console/repositories/ParticipantsRepositorySpec.scala

@@ -1,220 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories
-
-import cats.effect.IO
-import cats.effect.unsafe.implicits.global
-import com.typesafe.config.ConfigFactory
-import doobie.implicits._
-import io.iohk.atala.prism.AtalaWithPostgresSpec
-import io.iohk.atala.prism.crypto.EC.{INSTANCE => EC}
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.management.console.DataPreparation
-import io.iohk.atala.prism.management.console.config.DefaultCredentialTypeConfig
-import io.iohk.atala.prism.management.console.errors.{InvalidRequest, UnknownValueError}
-import io.iohk.atala.prism.management.console.models.{
-  ParticipantId,
-  ParticipantInfo,
-  ParticipantLogo,
-  UpdateParticipantProfile
-}
-import io.iohk.atala.prism.management.console.repositories.ParticipantsRepository.CreateParticipantRequest
-import io.iohk.atala.prism.management.console.repositories.daos.ParticipantsDAO
-import io.iohk.atala.prism.utils.IOUtils._
-import org.scalatest.EitherValues._
-import org.scalatest.OptionValues._
-import tofu.logging.Logs
-
-//sbt "project management-console" "testOnly *ParticipantsRepositorySpec"
-class ParticipantsRepositorySpec extends AtalaWithPostgresSpec {
-
-  val logs: Logs[IO, IO] = Logs.sync[IO, IO]
-
-  lazy val participantsRepository =
-    ParticipantsRepository.unsafe(database, logs)
-
-  "getParticipant by did" should {
-    "get a participant" in {
-      val id = ParticipantId.random()
-      val did = DataPreparation.newDID()
-      val info = ParticipantInfo(id, "test-name", did, None)
-      ParticipantsDAO
-        .insert(info)
-        .transact(database)
-        .unsafeRunSync()
-
-      val result = participantsRepository.findBy(did).unsafeRunSync()
-      result.toOption.value must be(info)
-    }
-
-    "return no participant on unknown did" in {
-      ParticipantsDAO
-        .insert(
-          ParticipantInfo(
-            ParticipantId.random(),
-            "test-name",
-            DataPreparation.newDID(),
-            None
-          )
-        )
-        .transact(database)
-        .unsafeRunSync()
-
-      val did = DataPreparation.newDID()
-      val result = participantsRepository.findBy(did).unsafeRunSync()
[…]

### 2023-07-25 prism-backend/management-console/src/test/scala/io/iohk/atala/prism/management/console/repositories/StatisticsRepositorySpec.scala

@@ -1,96 +1,0 @@
-package io.iohk.atala.prism.management.console.repositories
-
-import cats.effect.IO
-import cats.effect.unsafe.implicits.global
-import io.iohk.atala.prism.AtalaWithPostgresSpec
-import io.iohk.atala.prism.management.console.DataPreparation._
-import io.iohk.atala.prism.management.console.models.{InstitutionGroup, TimeInterval}
-import io.iohk.atala.prism.utils.IOUtils._
-import tofu.logging.Logs
-
-import java.time.Instant
-
-class StatisticsRepositorySpec extends AtalaWithPostgresSpec {
-
-  val logs: Logs[IO, IO] = Logs.sync[IO, IO]
-
-  lazy val repository = StatisticsRepository.unsafe(database, logs)
-  lazy val credentialsRepository = CredentialsRepository.unsafe(database, logs)
-
-  "query" should {
-    "work" in {
-      val issuerId = createParticipant("Issuer-1")
-      createInstitutionGroup(issuerId, InstitutionGroup.Name("Grp 1"))
-      createContact(issuerId, "no-invite", None)
-      createContact(issuerId, "pending-connection-1", None)
-      createContact(issuerId, "pending-connection-2", None)
-      val contact3 = createContact(issuerId, "connected", None)
-
-      // credentials
-      val credential1 =
-        createGenericCredential(issuerId, contact3.contactId, "A")
-      createGenericCredential(issuerId, contact3.contactId, "B")
-      publishCredential(issuerId, credential1)
-
-      val result = repository.query(issuerId, None).unsafeRunSync()
-      result.numberOfContacts must be(4)
-
-      result.numberOfGroups must be(1)
-      result.numberOfCredentials must be(2)
-      result.numberOfCredentialsPublished must be(1)
-      result.numberOfCredentialsInDraft must be(1)
-      result.numberOfCredentialsReceived must be(0)
-    }
-
-    "support time interval" in {
-      val issuerId = createParticipant("Issuer-1")
-      createInstitutionGroup(issuerId, InstitutionGroup.Name("Grp 1"))
-      val contact1 = createContact(issuerId, "Contact 1")
-      createGenericCredential(issuerId, contact1.contactId, "A")
-      val credential1 =
-        createGenericCredential(issuerId, contact1.contactId, "B")
-      publishCredential(issuerId, credential1)
-
-      Thread.sleep(
-        50
-      ) // sleep to add some time padding for the inspected interval
-      val start = Instant.now()
-      Thread.sleep(
[…]

### 2023-07-25 prism-backend/management-console/src/test/scala/io/iohk/atala/prism/management/console/services/CredentialTypesCategoryServiceImplSpec.scala

@@ -1,147 +1,0 @@
-package io.iohk.atala.prism.management.console.services
-
-import cats.effect.unsafe.implicits.global
-import io.iohk.atala.prism.management.console.grpc.ProtoCodecs
-import io.iohk.atala.prism.DIDUtil
-import io.iohk.atala.prism.auth.SignedRpcRequest
-import io.iohk.atala.prism.crypto.EC.{INSTANCE => EC}
-import io.iohk.atala.prism.logging.TraceId
-import io.iohk.atala.prism.management.console.DataPreparation._
-import io.iohk.atala.prism.management.console.ManagementConsoleRpcSpecBase
-import io.iohk.atala.prism.management.console.models.{CreateCredentialTypeCategory, CredentialTypeCategoryState}
-import io.iohk.atala.prism.protos.{console_api, console_models}
-import org.scalatest.OptionValues
-
-class CredentialTypesCategoryServiceImplSpec extends ManagementConsoleRpcSpecBase with DIDUtil with OptionValues {
-
-  "CredentialTypeCategoriesServiceImpl" should {
-
-    "return all credential type categories of a given participant" in new Fixtures {
-      val request = console_api.GetCredentialTypeCategoriesRequest()
-
-      val createCredentialTypeCategory1 =
-        CreateCredentialTypeCategory("some category1", CredentialTypeCategoryState.Ready)
-
-      val created = credentialTypeCategoryRepository
-        .create(participantId, createCredentialTypeCategory1)
-        .run(TraceId.generateYOLO)
-        .unsafeRunSync()
-        .toOption
-        .value
-
-      usingApiAsCredentialTypeCategory(
-        SignedRpcRequest.generate(keyPair, did, request)
-      ) { stub =>
-        val result = stub.getCredentialTypeCategories(request)
-        result.credentialTypeCategories mustBe Seq(created).map(ProtoCodecs.toCredentialTypeCategoryProto)
-      }
-    }
-
-    "don't return any credential type categories for participant that does not have any" in new Fixtures {
-      val request = console_api.GetCredentialTypeCategoriesRequest()
-
-      val createCredentialTypeCategory1 =
-        CreateCredentialTypeCategory("some category1", CredentialTypeCategoryState.Ready)
-
-      credentialTypeCategoryRepository
-        .create(participantId, createCredentialTypeCategory1)
-        .run(TraceId.generateYOLO)
-        .unsafeRunSync()
-        .toOption
-        .value
-
[…]

### 2023-07-25 prism-backend/management-console/src/test/scala/io/iohk/atala/prism/management/console/services/CredentialTypesServiceImplSpec.scala

@@ -1,245 +1,0 @@
-package io.iohk.atala.prism.management.console.services
-
-import cats.effect.unsafe.implicits.global
-
-import java.util.UUID
-import io.grpc.StatusRuntimeException
-import org.scalatest.OptionValues
-import io.iohk.atala.prism.DIDUtil
-import io.iohk.atala.prism.auth.SignedRpcRequest
-import io.iohk.atala.prism.crypto.EC.{INSTANCE => EC}
-import io.iohk.atala.prism.logging.TraceId
-import io.iohk.atala.prism.management.console.ManagementConsoleRpcSpecBase
-import io.iohk.atala.prism.protos.{console_api, console_models}
-import io.iohk.atala.prism.management.console.DataPreparation._
-import io.iohk.atala.prism.management.console.models.{
-  CreateCredentialTypeField,
-  CredentialTypeFieldType,
-  CredentialTypeState
-}
-
-class CredentialTypesServiceImplSpec extends ManagementConsoleRpcSpecBase with DIDUtil with OptionValues {
-
-  "CredentialTypesServiceImpl" should {
-
-    "return credential types" in new Fixtures {
-      val request = console_api.GetCredentialTypesRequest()
-
-      // test empty db
-      usingApiAsCredentialType(
-        SignedRpcRequest.generate(keyPair, did, request)
-      ) { stub =>
-        stub.getCredentialTypes(request) mustBe console_api
-          .GetCredentialTypesResponse(credentialTypes = Nil)
-      }
-
-      // create credential type
-      credentialTypeRepository
-        .create(participantId, createCredentialType)
-        .run(TraceId.generateYOLO)
-        .unsafeRunSync()
-
-      // test with data
-      usingApiAsCredentialType(
-        SignedRpcRequest.generate(keyPair, did, request)
-      ) { stub =>
-        val result = stub.getCredentialTypes(request)
-        result.credentialTypes.size mustBe 1
-        result.credentialTypes.head.name mustBe "credenital-type"
-      }
-    }
-
-    "return credential type" in new Fixtures {
-      // create credential type
-      val credentialType =
-        credentialTypeRepository
-          .create(participantId, createCredentialType)
-          .run(TraceId.generateYOLO)
-          .unsafeRunSync()
-          .getOrElse(fail())
-
-      val request =
-        console_api.GetCredentialTypeRequest(credentialTypeId = credentialType.credentialType.id.uuid.toString)
-
-      // test
[…]

### 2023-07-25 prism-backend/management-console/src/test/scala/io/iohk/atala/prism/management/console/services/CredentialsServiceImplSpec.scala

@@ -1,1704 +1,0 @@
-package io.iohk.atala.prism.management.console.services
-
-import cats.data.ReaderT
-import cats.effect.IO
-import cats.effect.unsafe.implicits.global
-import com.google.protobuf.ByteString
-import com.google.protobuf.timestamp.Timestamp
-import io.grpc.StatusRuntimeException
-import io.iohk.atala.prism.DIDUtil
-import io.iohk.atala.prism.auth.SignedRpcRequest
-import io.iohk.atala.prism.credentials.CredentialBatchId
-import io.iohk.atala.prism.crypto.EC.{INSTANCE => EC}
-import io.iohk.atala.prism.crypto.keys.ECKeyPair
-import io.iohk.atala.prism.crypto.{MerkleInclusionProof, MerkleRoot, Sha256, Sha256Digest}
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.logging.TraceId
-import io.iohk.atala.prism.management.console.DataPreparation._
-import io.iohk.atala.prism.management.console.models.{GenericCredential, InstitutionGroup}
-import io.iohk.atala.prism.management.console.{DataPreparation, ManagementConsoleRpcSpecBase}
-import io.iohk.atala.prism.models.{AtalaOperationId, DidSuffix}
-import io.iohk.atala.prism.protos._
-import io.iohk.atala.prism.protos.common_models.OperationStatus.UNKNOWN_OPERATION
-import io.iohk.atala.prism.protos.connector_api.SendMessagesResponse
-import io.iohk.atala.prism.protos.connector_models.MessageToSendByConnectionToken
-import io.iohk.atala.prism.protos.console_models.CredentialStatus.{
-  CREDENTIAL_DRAFT,
-  CREDENTIAL_SENT,
-  CREDENTIAL_SIGNED,
-  CREDENTIAL_STATUS_MISSING
-}
-import io.iohk.atala.prism.protos.console_models.{ContactConnectionStatus, CredentialStatus}
-import io.iohk.atala.prism.protos.node_api.GetOperationInfoResponse
-import io.iohk.atala.prism.protos.node_models.OperationOutput
-import org.mockito.ArgumentMatchersSugar.*
-import org.mockito.IdiomaticMockito.StubbingOps
-import org.mockito.Mockito.verify
-import org.scalatest.OptionValues.convertOptionToValuable
-
-import java.util.UUID
[…]

### 2023-07-25 prism-backend/management-console/src/test/scala/io/iohk/atala/prism/management/console/services/CredentialsStoreServiceImplSpec.scala

@@ -1,395 +1,0 @@
-package io.iohk.atala.prism.management.console.services
-
-import cats.effect.IO
-import cats.effect.unsafe.implicits.global
-import cats.syntax.functor._
-import doobie.implicits._
-import io.iohk.atala.prism.auth.{AuthenticatorF, SignedRpcRequest}
-import io.iohk.atala.prism.crypto.EC.{INSTANCE => EC}
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.logging.TraceId
-import io.iohk.atala.prism.logging.TraceId.IOWithTraceIdContext
-import io.iohk.atala.prism.management.console.grpc.CredentialsStoreGrpcService
-import io.iohk.atala.prism.management.console.models.{CredentialExternalId, ParticipantId, ParticipantLogo}
-import io.iohk.atala.prism.management.console.repositories.ParticipantsRepository.CreateParticipantRequest
-import io.iohk.atala.prism.management.console.repositories.daos._
-import io.iohk.atala.prism.management.console.repositories.{
-  ContactsRepository,
-  ParticipantsRepository,
-  ReceivedCredentialsRepository,
-  RequestNoncesRepository
-}
-import io.iohk.atala.prism.management.console.{DataPreparation, ManagementConsoleAuthenticator}
-import io.iohk.atala.prism.protos.console_api
-import io.iohk.atala.prism.utils.IOUtils._
-import io.iohk.atala.prism.{DIDUtil, RpcSpecBase}
-import org.mockito.MockitoSugar._
-import tofu.logging.Logs
-
-class CredentialsStoreServiceImplSpec extends RpcSpecBase with DIDUtil {
-
-  private val managementConsoleTestLogs: Logs[IO, IOWithTraceIdContext] =
-    Logs.withContext[IO, IOWithTraceIdContext]
-
-  val usingApiAs = usingApiAsConstructor(
-    new console_api.CredentialsStoreServiceGrpc.CredentialsStoreServiceBlockingStub(
-      _,
-      _
-    )
-  )
-
-  private lazy val receivedCredentialsRepository =
-    ReceivedCredentialsRepository.unsafe(
-      dbLiftedToTraceIdIO,
-      managementConsoleTestLogs
-    )
-  private lazy val contactsRepository =
-    ContactsRepository.unsafe(dbLiftedToTraceIdIO, managementConsoleTestLogs)
-  private lazy val participantsRepository =
[…]

### 2023-07-25 prism-backend/node/src/main/scala/io/iohk/atala/prism/node/cardano/dbsync/CardanoDbSyncClient.scala

@@ -1,45 +1,0 @@
-package io.iohk.atala.prism.node.cardano.dbsync
-
-import cats.Comonad
-import cats.effect.{Async, Resource}
-import io.iohk.atala.prism.metrics.TimeMeasureMetric
-import io.iohk.atala.prism.repositories.TransactorFactory
-import io.iohk.atala.prism.node.cardano.dbsync.repositories.CardanoBlockRepository
-import io.iohk.atala.prism.node.cardano.models.{Block, BlockError}
-import tofu.logging.Logs
-
-trait CardanoDbSyncClient[F[_]] {
-  def getFullBlock(blockNo: Int): F[Either[BlockError.NotFound, Block.Full]]
-  def getLatestBlock: F[Either[BlockError.NoneAvailable.type, Block.Canonical]]
-}
-
-final class CardanoDbSyncClientImpl[F[_]](
-    cardanoBlockRepository: CardanoBlockRepository[F]
-) extends CardanoDbSyncClient[F] {
-  def getFullBlock(blockNo: Int): F[Either[BlockError.NotFound, Block.Full]] =
-    cardanoBlockRepository.getFullBlock(blockNo)
-
-  def getLatestBlock: F[Either[BlockError.NoneAvailable.type, Block.Canonical]] =
-    cardanoBlockRepository.getLatestBlock
-}
-
-object CardanoDbSyncClient {
-  case class Config(dbConfig: TransactorFactory.Config)
-
-  def apply[F[_]: Async: TimeMeasureMetric, R[_]: Comonad](
-      config: Config,
-      logs: Logs[R, F]
-  ): Resource[F, CardanoDbSyncClient[F]] = {
-
-    /** Custom transactor since CardanoDbSyncClient can use different DB
-      */
-    TransactorFactory
-      .transactor[F](config.dbConfig)
-      .map(transactor => {
-        val cardanoBlockRepository =
-          CardanoBlockRepository.unsafe(transactor, logs)
-
-        new CardanoDbSyncClientImpl(cardanoBlockRepository)
-      })
-  }
-}

### 2023-07-25 prism-backend/vault/src/main/scala/io/iohk/atala/prism/vault/model/package.scala

@@ -1,36 +1,0 @@
-package io.iohk.atala.prism.vault
-
-import java.time.Instant
-import java.util.UUID
-import io.iohk.atala.prism.crypto.Sha256Digest
-import io.iohk.atala.prism.identity.{PrismDid => DID}
-import io.iohk.atala.prism.models.UUIDValue
-import tofu.logging.derivation.loggable
-import derevo.derive
-
-package object model {
-  final case class CreatePayload(
-      externalId: Payload.ExternalId,
-      hash: Sha256Digest,
-      did: DID,
-      content: Vector[Byte]
-  )
-
-  final case class Payload(
-      id: Payload.Id,
-      externalId: Payload.ExternalId,
-      hash: Sha256Digest,
-      did: DID,
-      content: Vector[Byte],
-      createdAt: Instant
-  )
-
-  object Payload {
-    @derive(loggable)
-    final case class Id(uuid: UUID) extends AnyVal with UUIDValue
-    object Id extends UUIDValue.Builder[Id]
-    @derive(loggable)
-    final case class ExternalId(uuid: UUID) extends AnyVal with UUIDValue
-    object ExternalId extends UUIDValue.Builder[ExternalId]
-  }
-}

### 2023-07-25 prism-backend/vault/src/test/scala/io/iohk/atala/prism/vault/VaultRpcSpecBase.scala

@@ -1,62 +1,0 @@
-package io.iohk.atala.prism.vault
-
-import cats.effect.IO
-import cats.effect.unsafe.implicits.global
-import io.iohk.atala.prism.auth.AuthenticatorF
-import io.iohk.atala.prism.logging.GeneralLoggableInstances._
-import io.iohk.atala.prism.{ApiTestHelper, RpcSpecBase}
-import io.iohk.atala.prism.logging.TraceId.IOWithTraceIdContext
-import io.iohk.atala.prism.protos.vault_api
-import io.iohk.atala.prism.vault.grpc.EncryptedDataVaultGrpcService
-import io.iohk.atala.prism.vault.repositories.{PayloadsRepository, RequestNoncesRepository}
-import io.iohk.atala.prism.vault.services.EncryptedDataVaultService
-import io.iohk.atala.prism.utils.IOUtils._
-import org.mockito.MockitoSugar._
-import tofu.logging.Logs
-
-class VaultRpcSpecBase extends RpcSpecBase {
-
-  override def services =
-    Seq(
-      vault_api.EncryptedDataVaultServiceGrpc
-        .bindService(
-          vaultGrpcService,
-          executionContext
-        )
-    )
-  private val vaultTestLogs: Logs[IO, IOWithTraceIdContext] =
-    Logs.withContext[IO, IOWithTraceIdContext]
-
-  RequestNoncesRepository.PostgresImpl.create(dbLiftedToTraceIdIO, vaultTestLogs)
-
-  lazy val (payloadsRepository, vaultGrpcService) = (for {
-    requestNoncesRepository <- RequestNoncesRepository.PostgresImpl.create(dbLiftedToTraceIdIO, vaultTestLogs)
-    payloadsRepository <- PayloadsRepository.create(dbLiftedToTraceIdIO, vaultTestLogs)
-    nodeMock = mock[io.iohk.atala.prism.protos.node_api.NodeServiceGrpc.NodeService]
-    authenticator = AuthenticatorF.unsafe(
-      nodeMock,
-      new VaultAuthenticator(
-        requestNoncesRepository
-      ),
-      vaultTestLogs
-    )
-    encryptedDataVaultService <- EncryptedDataVaultService.create(payloadsRepository, vaultTestLogs)
-    vaultGrpcService = new EncryptedDataVaultGrpcService(
-      encryptedDataVaultService,
-      authenticator
-    )(
-      executionContext,
[…]
